### 2022-01-07 thesis/appendex/c-symbols.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\chapter{Symbols}
\label{app:symbols}

This appendix summarises the important symbols used throughout the dissertation.
For each symbol, a short description is provided as well as the reference to the
equation that makes use it. Symbols are divided according to the chapter in
which they were introduced and are ordered alphabetically.

\section{Chapter~\ref{chap:anns}: Artificial Neural Networks}
\label{sec:symbols:anns}

\todo[inline]{ref usage}

\begin{description}
    \item
    [\parbox{1cm}{$\alpha$}] Control parameter for leaky ReLU that controls non-zero gradients.

    \item
    [\parbox{1cm}{$\beta$}] Batch size.

    \item
    [\parbox{1cm}{$c$}] Index for classes.

    \item
    [\parbox{1cm}{$C$}] Total number of classes.

    \item
    [\parbox{1cm}{$E$}] Total number of epochs.

    \item
    [\parbox{1cm}{$\epsilon$}] Error value calculated from loss/cost function.

    \item
    [\parbox{1cm}{$f$}] The activation function implemented by the \ac{AN}.

    \item
    [\parbox{1cm}{$f_{AN}$}] The non-linear function represented by the \ac{AN}.

    \item
    [\parbox{1cm}{$\vec{h}$}] The vector representing the activations of the hidden units.

    \item
    [\parbox{1cm}{$h_j$}] The $j$-th hidden unit and thus its activation.

    \item
    [\parbox{1cm}{$i$}] Index for the input dimensions.

    \item
    [\parbox{1cm}{$I$}] Total number of dimensions on the input space.

    \item
    [\parbox{1cm}{$j$}] Index for the hidden layer.

    \item
    [\parbox{1cm}{$J$}] The total number of units in the hidden layer.

    \item
    [\parbox{1cm}{$k$}] Index for the output dimensions.

    \item
    [\parbox{1cm}{$K$}] The total number of dimensions in the output space.

    \item
    [\parbox{1cm}{$\lambda$}] Control parameter for the steepness of sigmoid and hyperbolic tangent activation functions.

    \item
    [\parbox{1cm}{$net$}] The net input signal.

    \item
    [\parbox{1cm}{$net'$}] The augmented net input signal which contains the bias term $\theta$.

    \item
    [\parbox{1cm}{$\mu_i$}] The mean over all input patterns at index $i$.

    \item
    [\parbox{1cm}{$p$}] Index used for patterns in the set of all training data.

    \item
    [\parbox{1cm}{$P$}] Total number of patterns in the training data.

    \item
    [\parbox{1cm}{$\omega_{min}$}] The lower bound of the range for random uniform sampling.

    \item
    [\parbox{1cm}{$\omega_{max}$}] The upper bound of the range for random uniform sampling.

    \item
    [\parbox{1cm}{$\mathbb{R}$}] The real number space.

    \item
    [\parbox{1cm}{$\sigma$}] The standard deviation.

    \item
    [\parbox{1cm}{$\sigma_i^2$}] Unit variance.

    \item
    [\parbox{1cm}{$T$}] The total number of dimensions in the target space.

    \item
    [\parbox{1cm}{$\theta$}] The bias or threshold term.

    \item
    [\parbox{1cm}{$\vec{v}$}] The vector of weights associated with the input.

    \item
    [\parbox{1cm}{$v_i$}] The $i$-th index of the weight vector associated with the input.

    \item
    [\parbox{1cm}{$v_{i,j}$}] The $i,j$-th index of the weight vector between the input and hidden layers.

    \item
    [\parbox{1cm}{$\vec{w}$}] The weight vector between the hidden and output layers.

    \item
    [\parbox{1cm}{$w_{j,k}$}] The $j,k$-th index of the weight vector between the hidden and output layers.

    \item
    [\parbox{1cm}{$\vec{x}$}] The input vector.

    \item
    [\parbox{1cm}{$\vec{x}_p$}] The input vector for pattern $p$.

    \item
    [\parbox{1cm}{$x_i$}] The $i$-th index of the input vector $\vec{x}$

    \item
    [\parbox{1cm}{$x_{i,p}$}] The $i$-th index of the input vector $\vec{x}$ for pattern $p$.

    \item
    [\parbox{1cm}{$x_{i,p}'$}] The pre-processed input at the $i$-th index of the input vector $\vec{x}$ for pattern $p$.

    \item
    [\parbox{1cm}{$x_{i_{min}}$}] The minimum value at the  $i$-th index of the input vector $\vec{x}$  for all patterns in $P$.

    \item
    [\parbox{1cm}{$x_{i_{max}}$}] The maximum value at the  $i$-th index of the input vector $\vec{x}$  for all patterns in $P$.

    \item
    [\parbox{1cm}{$\vec{y}$}] The output vector.

    \item
    [\parbox{1cm}{$\vec{y}_p$}] The output vector for pattern $p$.

    \item
    [\parbox{1cm}{$y_k$}] The $k$-th dimension of the output vector $\vec{y}$.

    \item
    [\parbox{1cm}{$y_{k}'$}] The post-processed output at the $k$-th dimension of the output vector $\vec{y}$.

    \item
    [\parbox{1cm}{$y_{k,p}$}] The $k$-th dimension of the output vector $\vec{y}$ for pattern $p$.

    \item
    [\parbox{1cm}{$y_{k,p}'$}] The post-processed output at the $k$-th dimension of the output vector $\vec{y}$ for pattern $p$.

    \item
    [\parbox{1cm}{$\hat{y}_{k,p}$}] The $k$-th dimension of the target output for pattern $p$. 
\end{description}

### 2022-01-07 thesis/chapters/01-introduction.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\chapter{Introduction}
\label{chap:introduction}

\begin{quote}
    \textit{The Cephalopod retreats and crawls back up against the glass of the fish tank
        evaluating the situation in front of him. In front of him is a glass jar with
        prey inside. The lid is shut tightly. Never before has he encountered such an
        obstacle in nature, prohibiting him from feeding. He curiously swims closer,
        feeling the shape of the jar with his tentacles. He wraps his tentacles over the
        jar and with a small turn and pop, he releases the lid. The experiment is
        repeated and without hesitation, without failure, he opens the jar, faster, more
    efficiently, every time.}
\end{quote}

\Ac{ML} is one of the most popular fields of research in \ac{AI} studies today.
In recent years, \ac{ML} research has seen some notable achievements in the
academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014,
ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016,
ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \ac{ML} research has grown
tremendously over the past decade with successes like AlphaGo, which set new
standards for \ac{AI} capabilities by beating the world's best Go player, Lee
Sedol, 4-1 \cite{ref:san-hun:2016}.  Furthermore, an improvement on AlphaGo,
called AlphaZero, learned to play Go, \textit{tabula rasa} \footnote{Latyn word
meaning to learn from no prior knowledge} and managed to beat AlphaGo, 100-1
\cite{ref:silver:2017}.

Historically, \ac{ML} models were built with a specific purpose in mind and
revolved around specialised applications. A notable development was that of Deep
Blue by IBM \cite{ref:keene:1996}, which managed to play chess at a grand master
level. Deep Blue was able to finish 2-4 against the greatest chess player at the
time, Gary Kasparov. Although Deep Blue lost the tournament, this was a major
breakthrough in the field of \ac{AI}. However, Deep Blue was only able to play
chess and could not be utilised for any other purposes \cite{ref:kelley:2010}.
Today, DeepMind's \ac{RL} algorithm is capable of playing all of the original
Atari games \cite{ref:mnih:2013}, but is still very limited to a small set of
problems that it can solve.

Over the past few years, modern hardware capabilities have improved to the
point where workloads in the field of \ac{ML} that were previously computationally
infeasible, is now possible. One such subfield of \ac{ML} is \acp{ANN}. With
the improvement of hardware came an influx of \ac{ML} researchers that focussed
their attention on the training and generalisation capabilities of \acp{ANN}.

A popular field of focus for studing \acp{ANN} is the training process by which
these models are trained. Today, the most common form of training is
\index{supervised training}supervised learning of \acp{FFNN}, a specific type of
\ac{ANN} \cite{ref:reed:1999}. Training of \acp{ANN} is seen as an optimisation problem.
A search algorithm known as a \index{heuristic}\textit{heuristic}
\cite{ref:pearl:1984} is used to assign the optimal values to the \ac{ANN}
weights such that a specified objective function is minimised.

Although the landscape of what can be solved using \acp{ANN} today
is extensive, there still exists no single model that can be generalised to
solving multiple problem classes, across multiple problem domains. This problem
is known as the \ac{NFL} \cite{ref:wolpert:1997}.

Various attempts have been made to improve the generalisation capabilities of
\acp{ANN}. Examples of techniques used include weight \index{dropout}dropout
\cite{ref:srivastava:2014}, \index{weight decay}weight decay
\cite{ref:krogh:1992}, \index{meta-learning}meta-learning of learning parameters
such as the \index{learning rate}learning rate and \index{momentum}momentum of
gradient-based heuristics \cite{ref:zeiler:2012, ref:lv:2017, ref:darken:1992}
and carefully selecting training data. Other techniques focus on improving
generalisation through model design (architecture and topology). Examples of such
techniques include learning of \ac{ANN} architectures through pruning techniques
\cite{ref:cibas:1996, ref:engelbrecht:1996} or constructive techniques
\cite{ref:hassibi:1994, ref:lecun:1990}, adaptive activation functions
\cite{ref:engelbrecht:1995, ref:fletcher:1994}, and quantum methods
\cite{ref:wan:2017, ref:ricks:2004}.

One promising approach to improving \ac{ANN} generalisation capabilities is the
idea of hybridisation \cite{ref:burke:2013}, which makes use of a combination of
multiple learning paradigms in order to yield better generalisation. For
example, heteregenous approaches have been shown to balance the tradeoff between
exploration and exploitation. \cite{ref:nepomuceno:2013}. This hints towards the
idea that \ac{ML} models could yield better generalisation capabilities if the
learning process and learning mechanism applied is not statically defined, but
rather dynamic and under the control of some control mechanism.

The learning process is influenced by various factors, including the type of
learning technique used, how the model parameters are initialised, the
hyper-parameters used, the constraints of learning and the learning mechanism
itself. In order to yield better generalisation capabilities, the model should
be trained by a learning technique that has at its disposal a more diverse set
of learning behaviours from which it can dynamically select should the need arise
\cite{ref:huang:2009}. In doing so, balancing between exploration and
exploitation of solutions is a dynamic process that would yield better
generalisation capabilities.

An example of dynamically balancing exploitation and exploration during the
search process is done by dynamically adjusting and learning the heuristic
\index{hyper-parameters}\textit{hyper-parameters} as part of the learning
process. This field of study is known as \index{meta-learning}meta-learning
\cite{ref:giraud:2004}. \index{meta-learning}Meta-learning of heuristic
hyper-parameters as applied in the training of \acp{ANN} has shown to yield good
generalisation results \cite{ref:hospedales:2020, ref:vilalta:2002}.

A more recent suggestion related to the field of
\index{meta-learning}meta-learning is to dynamically select and/or adjust the
heuristic used throughout the training process. This approach is about the
hybridisation of heuristics as they are applied to some optimisation problem.
These methods are referred to as \acp{HH} and focus on finding the best
heuristic in \textit{heuristic-space}. One such form of \ac{HH} is a
population-based approach that guides the search process by automatically
selecting heuristics from a heuristic-space to be applied to a collection of
different candidate solutions in the solution-space. This collection of
candidate solutions are referred to as a \textit{population} of
\textit{entities}, where each \textit{entity} is a single candidate solution to
the problem being optimised.

Population-based \acp{HH} implement the strategy of multiple heuristics working
together to solve a problem. However, finding the best heuristic to use is
non-trivial and some \textit{selection strategy} must be used to select the best
heuristic. \acp{HH} that implement such a selection strategy is referred to as
\textit{selection} \acp{HH}. The term \textit{selection} refers to the ability
of the \ac{HH} to select the best heuristic from a pool of low-level heuristics.

These selection \acp{HH} can be further categorised based on what information
they use in the selection strategy. One specific type of selection \ac{HH} is
called a \index{multi-method populated-based meta-heuristic}\textit{multi-method
population-based \index{meta-heuristic}meta-heuristic}
\cite{ref:vanderstockt:2018}. The term \index{multi-method}\textit{multi-method}
refers to the incorporation of different low-level heuristics, with different
search behaviours, into the heuristic-space. The term \textit{population-based}
refers to the utilisation of a population of entities that represent candidate
solutions. Finally, the term \index{meta-heuristic}\textit{meta-heuristics}
refers to the \ac{HH} as a heuristic that does not have any domain knowledge and
only makes use of information from the search process.
\citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} mentioned that \acp{HH}
have been shown to solve a number of problems including bin-packing, examination
timetabling, production scheduling, the traveling salesman problem, vehicle
routing problem and many more.

This thesis focusses on the development of a \ac{HH} to train \acp{FFNN} in a
supervised learning approach.

\section{Problem Statement}
\label{sec:introduction:problem}

Many different heuristics have been developed and used to train \acp{FFNN}
\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.  The problem
lies in the process of finding the best heuristic to train the \ac{FFNN}. This
process is often non-trivial and could be a time-consuming exercise.  Consider
that selection of the best heuristic as applied to optimisation problems, such
as training \acp{FFNN}, is very problem dependent \cite{ref:allen:1996,
ref:drake:2020, ref:pillay:2018}. Furthermore, the \ac{NFL} shows that no single
heuristic performs better than any other heuristic for all problems
\cite{ref:wolpert:1997}.

Careful, systematic selection is thus required to find and select the best
heuristic to train \acp{FFNN}. In the past, researchers selected the best
heuristic by trail and error. A set of heuristics and carefully selected
hyper-parmeters would be implemented, followed by an empirical test to evaluate
the performance of each heuristic for a given problem domain
\cite{ref:pillay:2015}. In this way, researchers were able to determine which
heuristics and which hyper-parameters performed well for different problems.
However, this approach is problematic as it is time-consuming and tedious.

\section{Motivation}
\label{sec:introduction:motivation}

A process is required to alleviate the burden of having to exhaustively test
each implementation of heuristic and hyper-parameters, for every problem being
optimised.

A modern approach is to use \acp{HH} to automated the process for selecting the
best heuristic when applied to some optimisation problem. The best heuristic
might not be a single heuristic, but rather a hybridisation of heuristics
\cite{ref:pillay:2015}. Therefore, careful consideration is required to include
a diverse and applicable set of heuristics to select from that is capable of
solving the given problem. \citeauthor{ref:pillay:2015} \cite{ref:pillay:2015}
mentions that only heuristics that are known to have the potential to solve the
problem must be included in the set of heuristics to select from.

\acp{HH} have been implemented on a wide range of optimisation problems
\cite{ref:grobler:2011, ref:burke:2013, ref:pillay:2015}, but no research has
been found where \acp{HH} have been applied on the training of \acp{FFNN}.

The training of \acp{FFNN} is seen as a computational search problem. \Acl{HH}
as defined by Burke et al. \cite{ref:burke:2010} is ``a search method or
learning mechanism for selecting or generating heuristics to solve computational
search problems". \acp{HH} is a field of research aimed at the automated
selection, combination, adaptation and generation of multiple lower-level
heuristics to efficiently solve computational search problems. This implies that
one should be able to apply \acp{HH} in the context of training \acp{FFNN}.

\citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} mentions that the focus of
\acp{HH} is on automating the development of the \textit{learning mechanism}
used to obtain an appropriate solution for an optimisation problem. The authors
go on to explain that \acp{HH} employ a high-level heuristic that focusses on
finding the best low-level heuristic in heuristic-space that could include
\textit{single-method} and \textit{multi-method} optimistion algorithms
(heuristics). Applying \acp{HH} to train \acp{FFNN} could generally be applied
to multiple problems given that the set of low-level heuristics include
heuristics that have the potential to solve the problem at hand
\cite{ref:burke:2010}. This relieves the burden of having to select the best
heuristic to use by trial and error and is generally applicable to multiple
problems. The automation of the selection process as well as the generalisation
capabilities of \acp{HH}, if applied in the context of training \acp{FFNN},
could reduce the effort required to find the best heuristic to use.

Note that training \acp{FFNN} using \acp{HH} is not to be confused by the
training of \acp{FFNN} using \index{ensemble networks}\textit{ensemble networks}
or \index{query by committees}\textit{query by committees}.
\citeauthor{ref:pappa:2014} \cite{ref:pappa:2014} describes \index{ensemble
networks}ensemble networks as a combination method in
\index{meta-learning}meta-learning whereby multiple \acp{ANN} are jointly used
to solve a problem. Each member network in the ensemble gets trained using a
specified heuristic and generally this heuristic is applied to the same member
throughout the training process. The results of all of the member networks are
then joined together using some mechanism \cite{ref:zhou:2002}. This mechanism
could be weighted averages or majority or weighted voting. \index{ensemble
networks}Ensemble networks do not search through the heuristic space and do not
reselect lower-level heuristics for each member, while \acp{HH} do. There is
thus no hybridisation of heuristics in \index{ensemble networks}ensemble
networks and therefore, no information-sharing between any of the members of the
ensemble, in comparison to \acp{HH} that do incorporate some shared information
space.

Many different types of \acp{HH} have been implemented and shown to solve many
different problems. Some notable examples include the
\index{tabu-search}tabu-search \ac{HH} of Burke et al. \cite{ref:burke:2010} and
the \index{simulated annealing}simulated annealing-based \ac{HH} by Dowsland et
al. \cite{ref:dowsland:2007}.

This research takes a particular interest in developing a high-level heuristic
that makes use of probability theory and Bayesian statistical concepts to guide
the heuristic selection process. This research develops the novel \Ac{BHH}, a
new high-level heuristic that utilises \index{Bayesian analysis}\textit{Bayesian
analysis} as the selection mechanism for a \ac{HH} to select the appropriate
heuristic to train \acp{FFNN}.

\section{Objectives}
\label{sec:introduction:objectives}

The main objectives of this research is focussed on developing a novel \Ac{BHH}
selection mechanism in a \ac{HH} framework that can be used to train \acp{FFNN}.
In order to reach this objective, the following sub-objectives are defined:

\begin{itemize}
    \item
    Conduct a literature study on \acp{ANN} in order to provide
    the necessary background information of the \ac{AN}, \acp{FFNN} and the
    training process.

    \item
    Conduct a literature study on different types of heuristics that have been
    used to train \acp{FFNN}. The literature study will provide the necessary
    background information to understand how the these different heuristics can
    be used in the set of heuristics to be selected to train the \ac{FFNN}.

    \item
    Conduct a literature study on \index{meta-learning}meta-learning and
    \acp{HH} in order to provide the required background information
    necessary to propose and develop a new high-level heuristic.

    \item
    Conduct a literature study on probability theory and Bayesian statistics
    such as Bayesian inference and Bayesian analysis to provide the necessary
    background information required to understand how Bayesian approaches can be
    used as a learning technique.

    \item
    Develop a novel \Ac{BHH} selection mechanism for a \ac{HH} that makes use
    of Bayesian statistics to guide the \ac{HH} search process while training
    \acp{FFNN} on different problems.

    \item
    Conduct an empirical study to show that the developed \Ac{BHH} can
    effectively be used to train \acp{FFNN}.

    \item
    Conduct an empirical study and critically evaluate the performance of the
    developed \Ac{BHH} compared to individual heuristics in the heuristic-space
    as they are used to train \acp{FFNN} on different problems.

    \item
    Conduct an empirical study and critically evaluate the performance of the
    developed \Ac{BHH} as a selection mechanism to other selection mechanisms
    for \acp{HH} as they are used to train \acp{FFNN} on different problems.

    \item
    Conduct an empirical study that investigate variations of the \Ac{BHH} and the
    effects of design decisions and hyper-parameters on the search process.

    \item
    Provide a statistically sound analysis of the results obtained from the
    empirical study.
\end{itemize}

\section{Contributions}
\label{sec:introduction:contributions}

The results obtained from this research contributes to the field of study in the
following ways:

\begin{itemize}
    \item
    To the knowledge of the author, this study provides the first application
    of using \acp{HH} to train \acp{FFNN}.

    \item
    A novel heuristic selection operator is used that focusses on using Bayesian
    statistics to calculate the probability that a heuristic should be selected
    in order to efficiently train \acp{FFNN}. The resulting \ac{HH} is referred
    to as the \Acl{BHH}.

    \item
    The results of the empirical study show that the \Ac{BHH} perform generally
    better than the individual lower-level heuristics as applied to the same
    problems, with statistical significance and certainty.

    \item
    The results of the empirical study show that the \Ac{BHH} is able to select
    the best heuristic to train \ac{FFNN} in general, with statistical
    certainty. This relieves researchers from the burden of having to do this
    selection process manually through trial and error.

    \item
    The results of the empirical study show that the \Ac{BHH}, given a diverse
    set of lower-level heuristics, will generally produce good results when
    applied to multiple problems.

    \item
    Finally, the results of the empirical study show that the \Ac{BHH} is
    capable of utilising \textit{a priori} \footnote{Latin word, meaning "from
    what comes before"} knowledge in which a predefined selection bias is used
    for heuristics the are known to be well suited for certain problems.
\end{itemize}

\section{Thesis Outline}
 \label{sec:introduction:outline}

The remainder of this thesis is structured as follows:

 \begin{itemize}
 	\item
    \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN}
    and the various components that make up an \ac{AN}. The focus is on the
    training of \acp{FFNN} and it is shown how the training of \acp{FFNN} is
    seen as an optimisation problem.

	\item
    \textbf{Chapter~\ref{chap:heuristics}} provides details on various types of
    heuristics and metaheuristics that have been used to train \acp{FFNN}. A
    literature study is done to provide details on the search behaviours, application and
    implementation of each heuristics in the context of training \acp{FFNN}.

	\item
    \textbf{Chapter~\ref{chap:hhs}} presents a literature study on the details
    of \acp{HH} and \index{meta-learning}meta-learning in general. A
    discussion follows on the current landscape of \ac{HH} research. It is shown
    how \acp{HH} is a suitabe approach for training \acp{FFNN}.

    \item
    \textbf{Chapter~\ref{chap:probability}} presents a literature study on
    probability theory. Probability distributions and
    conjugate priors are discussed in detail. The chapter concludes with a
    detailed discussion on Bayesian statistics, specifically focussing on
    Bayesian inference and analysis.

	\item
    \textbf{Chapter~\ref{chap:bhh}} presents the developed \Ac{BHH}. It is shown
    how the \Ac{BHH} is implemented as a selection mechanism in the context of a
    \ac{HH} framework. The \Ac{BHH} is shown to implement a \index{Na\"ive Bayes
    classifier}Na\"ive Bayes classifier. The probabilistic model that is
    implemented is derived and discussed in detail. Finally, the chapter
    concludes with a detailed discussion on how \index{Bayesian
    analysis}Bayesian analysis is used to guide the heuristic selection process.
    The update step (training step) for prior probability concentration
    parameters is derived and discussed in detail. The \Ac{BHH} algorithmic
    implementation, variants and suggested application are presented as well.

	\item
    \textbf{Chapter~\ref{chap:methodology}} presents a detailed description of
    the empirical process and the setup of each experiment. It discusses the
    datasets used, the \ac{FFNN} architecture and topology used, heuristics that
    are used, the configuration of hyper-parameters, initialisation techniques
    used, performance measures used and other smaller details to the
    implementation of each experiment.  Finally discussions follow on how the
    results are analysed. This includes a discussion on the method used to
    determine statistical significance.

    \item
    \textbf{Chapter~\ref{chap:results}} provides and discusses the results of
    the empirical study, in detail. A baseline comparison is done by comparing
    the performance of the \Ac{BHH} to that of all the individual lower-level
    heuristics on all the datasets. These datasets include classification and
    regression problems of various sizes and complexity.  Detailed results are
    presented on the performance of the \Ac{BHH} as a selection mechanism for
    \acp{HH} and a brief comparison is made to other selection mechanisms.
    Finally, results are presented on the effects of the hyper-parameters of the
    \Ac{BHH} on the training process. Discussions follow on how the \Ac{BHH} is
    shown to automate the selection of the best heuristic during the training of
    \acp{FFNN}, as applied to a range of problems, alleviating the burden on
    researchers to apply traditional trial and error approaches. The chapter is
    concluded with a brief argument in favor of the general applicability of the
    \Ac{BHH} to more problem domains.

	\item
    \textbf{Chapter~\ref{chap:conclusion}} summarises the research done in this
    thesis along with a brief overview of findings made throughout the research
    process. A review of the research goals are given and suggestions for future
    research are made.
\end{itemize}

This thesis is accompanied by a full index given at page~\pageref{index} along with the following appendices:

\begin{itemize}
	\item
    \textbf{Appendix~\ref{app:datasets}} provides details on the datasets used
    for the empirical analysis.

 	\item
    \textbf{Appendix~\ref{app:acronyms}} provides a list of the important
    acronyms used or newly defined in the course of this work, as well as their
    associated definitions.

 	\item
    \textbf{Appendix~\ref{app:symbols}} lists and defines the mathematical
    symbols used in this work, categorised according to the relevant chapter
    in which they appear.

 	\item
    \textbf{Appendix~\ref{app:derived_publications}} lists the publications
    derived from this work.
 \end{itemize}

To best view the illustrations, tables and figures presented throughout this
thesis, it is recommended that the thesis be viewed in colour.

### 2022-01-07 thesis/chapters/02-artificial-neural-networks.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\chapter{Artificial Neural Networks}
\label{chap:anns}

\begin{quote}
    \textit{There are an estimated 100 billion neurons in the human brain. That
        means that there are approximately as many neurons in the human brain as
        there are stars in our galaxy. Every one of these neurons are highly
        interconnected with other neurons, yielding a synapse count of 100
        trillion. These neural structures are the result of millions of years
        of evolution. It is with these neural structures that we are able to think,
    learn and dream.}
\end{quote}

The human brain is by far one of the most complicated biological organs in
nature. The human brain is what gives us the ability to think and learn. The
field of \ac{ML} has taken a lot of inspiration from the biological brain which
lead to the development of \acp{ANN} \cite{ref:rosenblatt:1958}. \acp{ANN}
are used throughout this thesis as the model to be trained using \acp{HH}.
Understanding how \acp{ANN} work is an important component of this thesis.

The purpose of this chapter is to provide the necessary background information
needed on \acp{ANN} and is thus structured into five main parts:

\begin{itemize}
    \item
    Section~\ref{sec:anns:bn} gives background information on the \ac{BN}.

    \item
    Section~\ref{sec:anns:an} introduces the \ac{AN} and the various
    components that it is made up of. Brief discussions follow on
    input, \index{weights}weights, \index{net input
    signal}net input signal, \index{biases}biases,
    \index{activation functions}activation functions, and
    output.

    \item
    Discussions on the \ac{BN} and the \ac{AN} set the tone for the \ac{ANN}
    which is discussed in detail in Section~\ref{sec:anns:ann}. Brief
    discussions follow on \ac{ANN} architecture, topology, and
    \acp{FFNN}.

    \item
    Section~\ref{sec:anns:training} gives details on the training process,
    training sets, \index{supervised learning}supervised learning,
    \index{error function}error functions, performance measures
    and stopping conditions.

    \item
    Finally, a brief summary of the chapter is given in
    Section~\ref{sec:anns:summary}.
\end{itemize}

\index{Biological Neuron}
\section{Biological Neuron}
\label{sec:anns:bn}

This section introduces the \ac{BN} and provides the necessary background
information in order to understand how it has inspired the development
of the \ac{AN}.

The biological neural systems are made up of microscopic nerve cells called
neurons \cite{ref:jain:1996}. Figure \ref{fig:biological_neuron} illustrates a
single \ac{BN}.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{biological_neuron.eps}
    \caption[The \index{Biological Neuron}Biological Neuron]{An illustration of
    the \index{Biological Neuron}Biological Neuron.}
    \label{fig:biological_neuron}
\end{figure}

The main parts of the \ac{BN} to focus on includes the cell body, the
\index{dendrites}\textit{dendrites} and the \index{axon}\textit{axon} because these
components are directly modeled in the \ac{AN}. \Acp{NN} are formed by
neurons that connect to each other. This is known as
\index{synaptogenesis}\textit{synaptogenesis} \cite{ref:huttenlocher:1997}.
Connections are made between the \index{axons}axons and
\index{dendrites}dendrites of various neurons. Such a connection is referred to
as a \index{synapse}\textit{synapse}. It is through \index{synapses}synapses
that neurons communicate with each other. Communication takes place by
electro-chemical pulse and is often referred to as an \textit{activation} or
\textit{action potential}.  Communication signals propagate from the
\index{dendrites}dendrites, through the cell body to the axon of a neuron,
provoking a signal in the post-synaptic neuron \cite{ref:engelbrecht:2007}.
Neurons like these are massively interconnected.  The greater the connection
between two neurons, the stronger the communication.  Kennedy
\cite{ref:kennedy:2016} defines stronger \index{Synapse}synapses as ones that
contribute more depolarisation to the neural membrane upon activation than
weaker ones. Stronger \index{Synapse}synapses have a higher probability of
generating an action potential in the post-synaptic neuron. During activation,
the pre-synaptic neuron release neurotransmitters that bind to the post-synaptic
neuron \cite{ref:khanacademy:synapse}. The frequent release of these molecules
cause the \index{synapse}synapse to grow. Connections that grow over time yield
stronger signals, while connections that are weak propagate low intensity
signals and vanish over time. This is how the human brain learns and forgets.
Every time we reinforce a memory in our brains, we ``train'' the neuron and the
connection becomes stronger. This is known as \index{synaptic
plasticity}\textit{synaptic plasticity} \cite{ref:huttenlocher:1997}. this
reinforcement of connections plays a pivotal role in the way we algorithmically
train \acp{ANN}.

\index{Artificial Neuron}
\section{Artificial Neuron}
\label{sec:anns:an}

This section introduces the \ac{AN}. It is shown how the \ac{AN} is modeled
after the \ac{BN} by providing a brief discussion on the various components that
make up the \ac{AN}. Each component is discussed in more detail, including input
modeling, weight modeling, \index{net input signal}net input signal modeling,
biases modeling and output modeling in the \ac{AN}.

\subsection{Components}
\label{sec:anns:components}

The An \ac{AN} implements a nonlinear mapping from $\mathbb{R}^{I}$ to
$\mathbb{R}^{T}$, usually in the ranges $[0,1]$ or $[-1,1]$, depending on the
activation function used \cite{ref:engelbrecht:2007}. This mapping is given
below:

\begin{equation}
    f_{AN} \colon \mathbb{R}^{I} \to \mathbb{R}^{T}
    \label{eq:an_function_mapping}
\end{equation}

\noindent
where $f_{AN}$ is the function mapping produced by the \ac{AN}, $I$
is the total number of dimensions of the input in real-number space $\mathbb{R}$
and $T$ is the total number of dimensions of the target (desired output) in
real-number space.

An illustration of the \ac{AN} is given below:

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{artificial_neuron.eps}
  \caption[The \index{Artificial Neuron}Artificial Neuron]{An illustration of
  the \index{Artificial Neuron}Artificial Neuron.}
  \label{fig:artificial_neuron}
\end{figure}

From Figure~\ref{fig:artificial_neuron}, one can see that the
\ac{AN} is made up of the following components:

\begin{itemize}
    \item
    \textbf{Input:} The input models the activations received from the pre-synaptic neuron
    or from some environment sensor. Input is represented by the input vector
    $\vec{x}$.

    \item
    \textbf{Weights:} The weights model the \index{synapse}synapses and connection
    strengths. Weights are represented by the weight vector, $\vec{v}$.

    \item
    \index{net input signal}\textbf{Net input signal:} The \index{net input signal}netinput signl models
    the net resulting activations from all connected pre-synaptic neurons or
    environment sensors. The \index{net input signal}net input signal is
    represented by $net$.

    \item
    \textbf{Biases:} The biases model a mechanism introduced to influence the strength of the
    activation (output signal) of the \index{AN}\ac{AN}. The bias is
    represented by $\theta$.

    \item
    \index{activation function}\textbf{Activation function:} Models the action potential of the
    \ac{BN}\index{BN} based on the net input signal. The \index{activation
    function}activation function is
    represented by $f$.

    \item
    \textbf{Output:} This output models the activation by the post-synaptic neuron. Output is
    represented by the output vector $\vec{y}$.
\end{itemize}

Each of the above mentioned components are discussed in detail in the following
sections.

\subsection{Input}
\label{sec:anns:an:input}

Input signals are $I$-dimensional vectors of numerical values that are obtained
either through some environment sensor or from other \acp{AN}. Input signals
are often referred to as \index{features}\textit{features} or \index{independent
variables}\textit{independent variables} \cite{ref:francis:2001}. In this
thesis, a single input vector is referred to as a pattern. Input data must first
be pre-processed before it is presented to the \ac{AN}. Input pre-processing
techniques are discussed next.

\subsubsection{Input Pre-processing}
\label{sec:anns:an:input:input_pre_processing}

Input pre-processing can help improve the training process, but also plays an
important role in determining the success of a practical application of the
\ac{ANN} \cite{ref:kuzniar:2017}. The primary purpose of input
pre-processing is to modify the input data so that it can better match predicted
output.

There are many techniques to consider when pre-processing input data. From
scaling to the correct ranges to dealing with incomplete, invalid or even
irrelevant data. For the purposes of this thesis, only data encoding and
normalisation is considered. These topics are now discussed in more detail.

\index{Encoding}
\subsubsection{Encoding}
\label{sec:anns:an:input:encoding}

For qualitative data, such as class labels, the class labels have to be
converted to numerical representations. In general, class labels are encoded as
vectors \cite{ref:srinidhi:2018, ref:brownlee:2017:one-hot}. This thesis makes
use of \index{One-Hot Encoding}\textit{one-hot encoding} of class labels which
yields a $K$-dimensional output vector $\vec{y}$ of $0$'s and a single $1$. Each
element $y_k$ of $\vec{y}$ uniquely refers to a class. An activation, represented by a value
of $1$ at a given index thus represents a given class. Harris and Harris
\cite{ref:harris:2010} describe \index{One-Hot Encoding}one-hot encoding as a
group of vector elements where the representations of classes are represented
with a single high element (represented by $1$) and all the others low
(represented by $0$).

Once data has been encoded into the right form, normalisation is required. This
is discussed next.

\index{Normalisation}
\subsubsection{Normalisation}
\label{sec:anns:an:input:normalisation}

Input data must be normalised and scaled appropriately. In general, input data
is normalised to a range that is appropriate for the \index{Activation
Function}activation function being used. This yields input data in a range that
is comparable to the output produced. For the purpose of this thesis, the
min-max scaler \cite{ref:al:2006} and standard score scaler \cite{ref:jain:2005}
are normalisation techniques that are considered. These are discussed next.

\index{Min-Max Scalar}
\subsubsection{Min-Max Scaler}
\label{sec:anns:an:input:min_max_scaler}

The \index{Min-Max Scaler}min-max scaler scales all values into the range
$[0,1]$. This is also called \index{Unity-based
Normalisation}\textit{unity-based normalisation}. The
\index{min-max scaler}min-max scaler is used as a pre-processing technique for
target values when the \index{sigmoid}\textit{sigmoid} \index{activation
function} activation function is used and is given below:

\begin{equation}
    x_{i,p}'  = \frac{x_{i,p} - x_{i_{min}}}{x_{i_{max}} - x_{i_{min}}}
    \label{eq:min_max_scaler}
\end{equation}

\noindent where $x_{i,p}^{'}$ is the normalised form of $x_{i,p}$, the $i$-th
dimension of the input vector $\vec{x}_p$, $p \in \{1,2, \dots, P \}$, where $P$
is the total number of input patterns. $x_{i_{min}}$ and $x_{i_{max}}$ are
respectfully the minimum and maximum values of the $i$-th dimension for all
input vectors $\vec{x}_p, p \in \{1,2, \dots, P\}$.

\index{Standard Score Scalar}
\subsubsection{Standard Score Scaler}
\label{sec:anns:an:input:standard_score_scaler}

The \index{standard score scaler}standard score scaler, also known as the
\index{z-score scaler}\textit{z-score scaler}, scales features by subtracting
the mean and scaling to the unit variance of each dimension $i$ for all input
patterns $\vec{x}_p, p \in \{1,2, \dots, P\}$. The \index{standard score
scaler}standard score scaler is used as a pre-processing technique for target
values when the \index{hyperbolic tangent}\textit{hyperbolic tangent}
\index{activation function}activation function\index{activation function} is
used. The normalised for of $x_{i,p}^{'}$ as determined by the \index{standard
score scaler}standard score scaler is given in below:

\begin{equation}
    x_{i,p}^{'} = \frac{x_{i,p} - \mu_i}{\sigma^2_i}
    \label{eq:standard_score_scaler}
\end{equation}

\noindent where $\mu_i$ and $\sigma^2_i$ are respectfully the mean and unit
variance of the $i$-th dimension of all input vectors $\vec{x}_p, p \in \{1,2,
\dots, P\}$.

\subsection{Weights}
\label{sec:anns:an:weights}

It was mentioned in Section~\ref{sec:anns:bn} that \index{synapses}synapses can
have strong or weak connections. The connection strength is modeled in the
\ac{AN} as weight vectors of numerical values associated with each dimension $i$
of the input data. Weights can either dampen or strengthen the input data by
some negative or positive numerical value. By changing the weight associated
with a feature, the influence of that particular feature on the predicted output
is changed. Finding the correct value for each weight, to yield optimal output,
is an optimisation problem \cite{ref:thierens:1993}. The initial placement of
these weight vectors in the search-space is very important. Research has shown
that weight initialisation plays an important role in the efficient training of
\acp{ANN} \cite{ref:thimm:1995}. Weight initialisation is discussed next,
followed by some common weight initialisation techniques used.

\index{Weight Initialisation}
\subsubsection{Weight Initialisation}
\label{sec:anns:an:weights:initialisation}

Weight initialisation is the process by which candidate solutions (represented
by the weights of the \ac{AN}) to the problem is placed in the search-space.
Weight initialisation influences the speed of convergence, the probability of
convergence and the generalisation capabilities of \acp{ANN}
\cite{ref:fernandez:2001}. Finding the optimal initialisation values for weights
is non-trivial and can be seen as another optimisation problem. Extensive
research on this topic has been done in the past \cite{ref:de:2016,
ref:erdogmus:2003, ref:yam:2000}.

\index{Weight Initialisation}Weight initialisation is dependent on the
\index{activation function}activation function used. If weights are initialised
to values that are too small, the vanishing gradients problem can occur
\cite{ref:hanin:2018}. If weights are initialised to values that are too big,
output of the activation function would not be in the active range. This leads
to hidden unit saturation and exploding gradients can occur
\cite{ref:hanin:2018, ref:yadav:2018}.

Research have presented many initialisation techniques \cite{ref:erdogmus:2003}.
Some techniques have been developed to address the problems that are mentioned
above \cite{ref:yadav:2018}. However, this thesis will only focus on
\index{random uniform sampling}random uniform sampling, \index{Glorot uniform
sampling}\textit{Glorot uniform (Xavier)} sampling and \index{Glorot normal
sampling}\textit{Glorot normal} sampling \cite{ref:glorot:2010}. These
techniques are briefly discussed next.

\index{random uniform sampling}
\subsubsection{Random Uniform Sampling}
\label{sec:anns:an:weights:random_uniform_sampling}

\index{random uniform sampling}Random uniform sampling initialises weights
uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $w_{i} \sim
\textit{U} (\omega_{min}, \omega_{max})$ where the $\omega_{min}$ and
$\omega_{max}$ are respectfully the lower and upper bounds of the uniform
distribution. Suggested parameter values are $(-1, 1)$ or $(-0.5, 0.5)$
\cite{ref:nguyen:1990}.

\index{Glorot uniform sampling}
\subsubsection{Glorot Uniform Sampling}
\label{sec:anns:an:weights:glorot_uniform_sampling}

\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of
\index{random uniform sampling}random uniform sampling whereby $\omega =
\sqrt{\frac{6}{fanin + fanout}}$ and \index{$fanin$}$fanin$ is the number of
input neurons to the weight vector and \index{$fanout$}$fanout$ is the number of
output neurons from the weight vector.

\index{Glorot Normal Sampling}
\subsubsection{Glorot Normal Sampling}
\label{sec:anns:an:weights:glorot_normal_sampling}

\index{Glorot normal sampling}Glorot normal sampling initialises weights by
sampling from a truncated normal distribution centred on a mean of $0$ and with
$\sigma = \sqrt{\frac{2}{I + K}}$, where $\sigma$ is the standard deviation of
the distribution. $I$ and $K$ are respectfully the number of input and output
units in the weight vector. \index{Glorot normal sampling}Glorot normal sampling
have been shown to decrease training time \cite{ref:glorot:2010}.

\index{net input signal}
\subsection{Net Input Signal}
\label{sec:anns:an:net_input}

\acp{AN} accumulate the net resulting input signal from all input dimensions
into a value called the \index{net input signal}\textit{net input signal},
expressed as $net$. This signal is passed to the \index{Activation
Function}activation function, which provokes an artificial action potential in
the \ac{AN}.

The most common way by which the \index{net input signal}net input signal is
calculated is by means of \acp{SU} \cite{ref:engelbrecht:2007}, which
computes the \index{net input signal}net input signal as the weighted sum of all
input signals as shown below:

\begin{equation}
    net = \sum_{i=1}^{I}{x_{i}v_{i}}
    \label{eq:summation_units}
\end{equation}

\noindent where $x_{i}$ is the $i$-th
dimension of the input vector $\vec{x}$, and $v_{i}$ is the $i$-th dimension of
the weight vector $\vec{v}$, associated with the given input dimension.

\subsection{Biases}
\label{sec:anns:an:biases}

A bias/threshold term $\theta$ is introduced to help translate the output of the
\index{activation function}activation function \cite{ref:benitez:1997}. The
value of $\theta$ must be learned during the training process along with the
weights of the \ac{ANN}. In order to simplify equations, augmented vectors are
used in which input and hidden layers have an additional neuron/unit, called the
\textit{bias unit} \cite{ref:engelbrecht:2007}. Augumented vectors that include
the bias unit to the net input signal is presented next.

\subsubsection{Augmented Net Input Signal}
\label{sec:anns:an:biases:augmented_net_input_signal}

Input layer $x_{I+1}$ has a net input signal $net^{'} = net - \theta$. The value
for $\theta$ is learned along with the weights such that $\theta =
x_{i+1}v_{i+1}$. If a constant value $x_{i+1} = -1$ is used, the equation for
\acp{SU} as given in Equation~\eqref{eq:summation_units} is then completed by
including $\theta$ as shown below:

\begin{equation}
    \begin{split}
        net{'} & = net - \theta \\
             & = \sum_{i=1}^{I} x_i v_i - \theta\\
             & = \sum_{i=1}^{I} x_i v_i + x_{i+1} v_{i+1} \\
             & = \sum_{i=1}^{I+1} x_i v_i
    \label{eq:augmented_vectors}
    \end{split}
\end{equation}

\noindent where $\textit{net}^{'}$ is the augmented net input signal that now
includes the bias term $\theta$.

\subsection{Activation Functions}
\label{sec:anns:an:act_functions}

\index{activation function}Activation functions are used to model the action
potential of the \index{AN}\ac{AN} \cite{ref:ziv:1994, ref:hodgkin:1952}, and is
a function over the augmented \index{net input signal}net input signal. It is
the mechanism that models whether an \index{AN}\ac{AN} fires or not. When the
output produced by the activation function surpasses some threshold value
$\theta$, we consider that neuron to have fired an output signal.
\index{activation function}Activation functions model \textit{phase shift}. In
the context of classification problems, these \index{activation
function}activation functions form decision boundaries between classes. In the
context of regression problems, these \index{activation function}activation
functions try to approximate some function that maps the input data to some
target data.

In general, activation functions produce a non-linear mapping of
$\mathbb{R}^{I}$ to the range $[0,1]$ or $[-1,1]$ as shown below:

\begin{equation}
    f_{AN}: \mathbb{R}^{I} \rightarrow [0,1]
    \label{eq:an_function_mapping_0_1}
\end{equation}

\noindent or

\begin{equation}
    f_{AN}: \mathbb{R}^{I} \rightarrow [-1,1]
    \label{eq:an_function_mapping_minus_1_1}
\end{equation}

\noindent Research in the past have presented many \index{activation
function}activation functions \cite{ref:karlik:2011} of varying ranges. However,
this thesis focuses on the \ac{ReLU} \cite{ref:jarrett:2009, ref:nair:2010}, the
\ac{LReLU} \cite{ref:maas:2013}, the \index{sigmoid}sigmoid \cite{ref:lecun:1988} and the
\index{hyperbolic tangent}hyperbolic tangent \cite{ref:lin:2008} \index{activation
function}activation functions. These \index{activation function}activation
functions are presented next.

\subsubsection{Rectified Linear Unit}
\label{sec:anns:an:act_functions:relu}

The \ac{ReLU} \index{activation function}activation function is an
\index{activation function}activation function defined in the positive part of
its argument. It is defined as:

\begin{equation}
    f(x) = x^{+} = \max(0,x)
    \label{eq:relu}
\end{equation}

\noindent An advantage of \ac{ReLU} is that it is not susceptible to the
\index{vanishing gradient problem}vanishing gradients problem \cite{ref:xu:2015,
ref:maksutov:2018} which occurs when gradients in the first layers of a
multi-layer \ac{ANN} approach zero, and have no effect in the training process.

\subsubsection{Leaky Rectified Linear Unit}
\label{sec:anns:an:act_functions:leaky_relu}

The \ac{LReLU} \index{activation function}activation function is a variant of
the \ac{ReLU} \index{activation function}activation function \cite{ref:xu:2015}.
Similar to \ac{ReLU} it is not susceptible to the \index{vanishing gradients
problem}vanishing gradients problem and it does not suffer from the \index{dying
ReLU problem}dying \ac{ReLU} problem \cite{ref:agarap:2018}, which occurs when
the neurons that use \ac{ReLU} \index{activation functions}activation functions
become \textit{inactive} and only output $0$ due to a negative net input signal.

The \ac{LReLU} \index{activation function}activation function is defines as:

\begin{equation}
    f_{AN}(net - \theta) = 
    \begin{cases}
        net - \theta & \text{if $net \geq \theta $}\\
        \alpha(net - \theta) & \text{otherwise}\\
    \end{cases}
    \label{eq:leaky_relu}
\end{equation}

\noindent
By introducing a parameter $\alpha >
0$, negative \index{Net Input Signals}net input signals will still yield
non-zero activations, resulting in non-zero gradients and avoiding gradient
saturation. Non-zero gradients are required by some heuristics such as
\ac{SGD} in order to be able to effectively train \acp{ANN}
\cite{ref:hanin:2018}.

An illustration of the \ac{LReLU} with various values for $\alpha$ and $\theta =
0$ is given in Graph~\ref{grf:leaky_relu} below:

\begin{graph}[H]
    \centering
    \input{./plots/leaky_relu.tex}
    \caption[The \ac{LReLU} \index{activation function}activation function]{An illustration of the
    \acs{LReLU} \index{activation function}activation function.}
    \label{grf:leaky_relu}
\end{graph}

\subsubsection{Sigmoid}
\label{sec:anns:an:act_functions:sigmoid}

\index{sigmoid}Sigmoid is a very popular \index{activation function}activation
function, because it introduces non-linearity into the model. The
\index{sigmoid}sigmoid \index{activation function}activation function is defined
as:

\begin{equation}
    f_{AN}(net - \theta) = \frac{1}{1+e^{-\lambda(net - \theta)}}
    \label{eq:sigmoid}
\end{equation}

\noindent where $\lambda$ is a control parameter, which controls the steepness
of the function and is usually set to $\lambda = 1$.  \noindent The
\index{sigmoid}sigmoid \index{activation function}activation function is a
continuous variant of the ramp function and yields $f_{AN} \in (0,1)$.

An illustration of the \index{sigmoid}sigmoid \index{Activation
Function}activation function with various values for $\lambda$ and $\theta = 0$
is given below:

\begin{graph}[H]
    \centering
    \resizebox{0.8\textwidth}{!}{\input{./plots/sigmoid.tex}}
    \caption[The \index{sigmoid}sigmoid \index{activation function}activation
    function]{An illustration of the \index{sigmoid}sigmoid \index{Activation
    Function}activation function.}
    \label{grf:sigmoid}
\end{graph}

\subsubsection{Hyperbolic Tangent}
\label{sec:anns:an:act_functions:tanh}

The \index{hyperbolic tangent}hyperbolic tangent \index{activation
function}activation function is similar to the \index{sigmoid}sigmoid
\index{activation function}activation function, but yields output in the range
$(-1, 1)$. The \index{hyperbolic tangent}hyperbolic tangent
\index{activation function}activation function is defined as:

\begin{equation}
    f_{AN}(net - \theta) = \frac{e^{\lambda(net - \theta)}-e^{-\lambda(net - \theta)}}{e^{\lambda(net - \theta)}+e^{-\lambda(net - \theta)}}
    \label{eq:hyperbolic_tangent}
\end{equation}

\noindent The \index{hyperbolic tangent}hyperbolic tangent \index{activation
function}activation function with various values for $\lambda$ and $\theta = 0$
is given below:

\begin{graph}[H]
    \centering
    \resizebox{0.8\textwidth}{!}{\input{./plots/tanh.tex}}
    \vspace{10pt}
    \caption[The \index{hyperbolic tangent}hyperbolic tangent \index{Activation
        Function}activation function]{An illustration of the \index{Hyperbolic
    Tangent}hyperbolic tangent \index{activation function}activation function.}
    \label{grf:hyperbolic_tangent}
\end{graph}

\subsection{Output}
\label{sec:anns:an:output}

Output signals are $K$-dimensional vectors of numerical values that are produced
by the \index{activation function}activation function. Output signals are often
referred to as \textit{predictions}. If target pre-processing was applied, it is
necessary to post-process the output data. A brief discussion on post-processing
techniques follow.

\subsubsection{Output Post-Processing}
\label{sec:anns:an:output:output_post_processing}

Output post-processing is necessary in order to convert data back to their
original ranges. The post-processing techniques that are applicable depend on
the type of problem (regression or classification), input pre-processing
techniques used, as well as the \index{activation function}activation function
used. For the purposes of this thesis, only data decoding, normalisation and
re-scaling techniques are considered.

\subsubsection{Decoding}
\label{sec:anns:an:output:decoding}

Data decoding is used to convert \index{One-Hot Encoding}one-hot encoded vectors
as described in Section~\ref{sec:anns:an:input:encoding} back to class labels.
This is relevant to classification problems where the predicted output is a
\index{One-Hot Encoding}one-hot encoded vector representing a class label.

The high value (represented by $1$) at $y_k$ is used to decode the
\index{One-Hot Encoding}one-hot encoded output vector $\vec{y}$ back to its
corresponding class label.

Normalisation of the output data is used to simplify the decoding process. This
thesis considers \index{softmax}\textit{softmax} and
\index{Argmax}\textit{argmax} normalisation to assist the decoding process.

\subsubsection{Softmax}
\label{sec:anns:an:output:softmax}

The \index{softmax}softmax function, also known as the
\index{softargmax}\textit{softargmax} \cite[p.~184]{ref:goodfellow:2016} or
\index{normalised exponential function}\textit{normalised exponential function}
\cite{ref:bishop:2006} is a generalisation of the logistic function that
converts the $K$-dimensional output vector $\vec{y}$ into a $K$-dimensional
output vector $\vec{y^{'}}$ where each element $y^{'}_k$ is in the range $(0,1)$
and all elements sum up to $1$. This is expressed as follows:

\begin{equation}
    \vec{y^{'}} \colon \mathbb{R}^{K} \to \left\{\vec{y^{'}} \in \mathbb{R}^{K} \vert y^{'}_k \in (0,1), \sum_{k=1}^{K} y_k = 1\right\}
    \label{eq:sum_after_softmax}
\end{equation}

\noindent The softmax function is given as:

\begin{equation}
    y^{'}_k = \frac{e^{y_k}}{\sum_{k = 1}^{K}e^{y_k}}
    \label{eq:softmax}
\end{equation}

\subsubsection{Argmax}
\label{sec:anns:an:output:argmax}

The \index{Argmax}argmax function is similar to the \index{softmax}softmax
function, with the difference that the element $y_k, k \in \{1,2, \dots, K\}$
with the highest output value is set to $1$ and the rest are set to $0$. This
means that all elements still sum to $1$, but the activation is only observed at
index $k$ where the activation is $1$.

The \index{Argmax}argmax function is given as:

\begin{equation}
    y^{'}_k = 
    \begin{cases}
        1 & \text{if $y_k = \max(y_1, y_2, \dots, y_K)$}\\
        0 & \text{otherwise}
        \label{eq:argmax}
    \end{cases}
\end{equation}

\noindent Graph~\ref{grf:softmax_argmax} illustrates the comparison of
transformations of the output vector $\vec{y}$, where the
\index{sigmoid}sigmoid, the \index{softmax}softmax and the \index{argmax}argmax
\index{activation function}activation functions are used.

\begin{graph}[H]
    \centering
    \resizebox{0.8\textwidth}{!}{\input{./plots/output_modifiers.tex}}
    \caption[The results of \index{softmax}softmax and \index{Argmax}argmax]{An
        illustration of \index{softmax}softmax and \index{Argmax}argmax applied
    after the \index{sigmoid}sigmoid \index{activation function}activation function.}
    \label{grf:softmax_argmax}
\end{graph}

\section{Artificial Neural Network}
\label{sec:anns:ann}

This section presents \acp{ANN}. Discussions follow on their applications,
architecture, and topologies. Finally, a specific type of \ac{ANN} called a
\acl{FFNN} is discussed in detail.

\subsection{Applications}
\label{sec:anns:anns:applications}

\acp{ANN} are modelled after our biological brains. The human brain is
biologically and chemically incredibly sophisticated. Trying to model an entire
brain is at this stage not computationally feasible. Sandberg
\cite{ref:sandberg:2008} approximates a computational requirement of 256 000
terabytes/s to emulate the entire brain. Given our shortage in hardware
capabilities, \acp{ANN} have been successfully applied to a range of problem
classes. Engelbrecht \cite{ref:engelbrecht:2007} summarises some common problems
that are solved using \acp{ANN}. These include:

\begin{itemize}
    \item
    \textbf{Classification}: Predicting the class of an input vector
    \cite{ref:khan:2001}.

    \item
    \textbf{Pattern Matching}: Producing closely associated patterns based on an
    input vector \cite{ref:cannady:1998, ref:kumar:1994}.

    \item
    \textbf{Pattern Completion}: Completing the missing parts of an input vector
    \cite{ref:dayhoff:2001}.

    \item
    \textbf{Optimisation}: Producing optimal values of parameters in a
    optimisation problems \cite{ref:specht:1991}.

    \item
    \textbf{Data Mining}: Feature discovery in large datasets
    \cite{ref:singh:2009}.
\end{itemize}

Different \acp{ANN} are built for different types of problems, however, most
applications of \acp{ANN} include some layered architecture. Discussions follow
on \ac{ANN} architecture and topologies.

\subsection{Architecture}
\label{sec:anns:anns:architecture}

\acp{ANN} are collections of \acp{AN} that are organised together to form a
connected network. The architecture of the \ac{ANN} refers to the way in which
these \acp{AN} are organised together as well as the type of \index{Activation
Function}activation function used.

\acp{ANN} are organised in layers where a single layer can contain multiple
\acp{AN}. Generally, each layer makes use of the same \index{activation
function}activation function, but this is not a requirement. Output from one
layer is propagated as input to the next layer. This thesis focusses on the
simplest architecture, containing three particular layers, including the input,
hidden and output layers. \acp{ANN} with this type of architecture is usually
referred to as \textit{shallow} \acp{NN}. The input, hidden and output layers
are discussed next.

The input layer contains the input data to the \ac{ANN}. Since the
input layer simply provides the the input data, some literature do not consider
the input layer as a layer \cite{ref:engelbrecht:2007}.

The hidden layer contains a collection of hidden \acp{AN}. These hidden \acp{AN}
are referred to as \textit{hidden units} or \textit{nodes}. Hidden units are
used if the target data is not linearly separable \cite{ref:engelbrecht:2007}.
It has been shown that \acp{ANN} that incorporate monotonically increasing
differentiable \index{activation function}activation functions can approximate
any continuous function with just one hidden layer, given that the hidden layer
has enough hidden units \cite{ref:hornik:1989}.

The output layer contains the activations or the predictions of the \ac{ANN}.
This layer is used to analyse the accuracy of the prediction and thus the
performance of the \ac{ANN}.

\subsection{Topology}
\label{sec:anns:anns:topology}

The topology of the \ac{ANN} refers to the way \acp{AN} are connected to each
other. Since \acp{AN} are organised in layers, this connectivity is described
layer by layer.

There are many different topologies \cite{ref:miikkulainen:2010}, however, this
thesis only focusses on a \index{fully connected topology}fully connected
topology.

The most common and simplest topology is where each \ac{AN} in one layer is
connected to all \acp{AN} in the next. Fully connected topologies have no
cycles \cite{ref:zell:1994}.

\subsection{Feedforward Neural Networks}
\label{sec:anns:anns:ffnns}

There are many different types of \acp{ANN}. All \acp{ANN} can be described
in terms of their architecture and topology. This research will focus on a
particular \ac{ANN} called a \acl{FFNN} (\acs{FFNN}).

\acp{FFNN} were the first and simplest \acp{ANN} developed
\cite{ref:schmidhuber:2015}. \acp{FFNN} incorporate the basic layers (input,
hidden and output layers) by arranging them in sequential order. In \acp{FFNN}
information moves forward, in one direction, from the input nodes, through the
hidden nodes and finally to the output nodes and depending on the optimisation
algorith used, error correction information can be backpropagated through the
network. It can be said that input is \textit{fed} forward, through the
\ac{ANN}. The \index{activation function}activation function used is problem
dependent. \acp{FFNN} incorporate fully connected topologies amongst the layers
such that no cycles form \cite{ref:zell:1994}.

An illustration of a \ac{FFNN} using a three-layered architecture and a fully
connected topology is given below:

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{feedforward_neural_network.eps}
    \caption[A \index{Feedforward Neural Network}Feedforward neural network]{An
    illustration of a \index{Feedforward Neural Network}feedforward neural network.}
    \label{fig:ffnn}
\end{figure}

In Figure~\ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input
vector $\vec{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer,
$y_k$ refers to the $k$-th dimension in the output vector $\vec{y}$. $v_{i,j}$
refers to the weight associated with input node $x_i$ and the hidden node $h_j$
and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the
output node $y_k$.

With the layered architecture and \index{fully connected topology}fully
connected topology of \acp{FFNN} and assuming the use of \acp{SU}, the output
for the \ac{FFNN} at index $k$, denoted $y_k$ is calculated using:

\begin{equation}
    \label{eq:ffnn}
    \begin{split}
        y_k &= f\left(net_{h,y}\right) \\
            &= f\left(\sum_{j=0}^{J+1} h_j w_{j,k}\right) \\
            &= f\left(\sum_{j=0}^{J+1} f\left(net_{i,h}\right) w_{j,k}\right) \\
            &= f\left(\sum_{j=0}^{J+1} f\left(\sum_{i=0}^{I+1} x_i v_{i,j}\right) w_{j,k}\right) \\ 
    \end{split}
\end{equation}

\noindent The remainder of this thesis makes use of \acp{FFNN} as the \ac{ANN}
of interest and is sometimes referred to as \textit{the model}.

\section{Training}
\label{sec:anns:training}

Section~\ref{sec:anns:an:weights} mentioned that changing the weight associated
with a feature, changes the influence of that particular feature on the
predicted output. \textit{Training} is the process whereby the weights of the
\acp{FFNN} is systematically changed with the aim of improving performance.

Finding the optimal weights that produce the best output is an optimisation
problem and therefore, training of \acp{FFNN} is done using a search function
called a \index{Heuristic}\textit{heuristic}. \index{Heuristic}Heuristics search
for possible solutions in the solution-space and make use of information from
the search-space to guide to process. Heuristics are discussed in detail in
Chapter~\ref{chap:heuristics}.

Details on the training of \acp{FFNN} is presented in this section along with
brief discussions on the training process, generalisation capabilities, training
sets, \index{Supervised Learning}supervised learning, error functions, and
performance measurement.

\subsection{Training Process}
\label{sec:anns:training:process}

During the training process, the \ac{FFNN} is exposed to input data while
trying to predict some expected outcome. From this prediction, a \textit{cost}
is calculated based on the degree to which the predicted output differs from the
expected outcome. This outcome could be predefined and static, or be the result
of an action in a dynamic environment. This cost is used by some
\index{Heuristic}heuristic as a guide to update the weights slightly such that
the performance of the \ac{FFNN} improves over time.

The training process is executed as follows: training data is retrieved and
pre-processed. The pre-processed input data is then split into various datasets.
A loss is calculated by exposing all patterns in the training data to the
\ac{FFNN} and evaluating the  prediction in comparison to the expected or target
output. Exposing the \ac{FFNN} to all training data once is referred to as an
epoch. The \ac{FFNN} is trained for a maximum number of epochs, or until some
stopping condition is reached. After training, the generalisation capabilities
of the \ac{FFNN} is evaluated against never before seen data.

Central to this thesis is the topic of generalisation. Generalisation refers to
the ability of a model to balance under- and overfitting of data. Training a
\ac{FFNN} using a \ac{HH} aims to do exactly that. Overfitting and underfitting
concepts are discussed next.

\subsubsection{Overfitting}
\label{sec:anns:training:overfitting}

\index{Overfitting}Overfitting describes a scenario where the trained model
performs well on training data, but does not generalise well to never before
seen data. \cite{ref:tetko:1995, ref:geron:2017}. Geron \cite{ref:geron:2017}
mentions that \index{overfitting}overfitting occurs when the model is too
complex relative to the noisiness of the training data.

\subsubsection{Underfitting}
\label{sec:anns:training:generalisation_capabilities:underfitting}

\index{underfitting}Underfitting is the opposite of
\index{overfitting}overfitting. Geron \cite{ref:geron:2017} mentions that
\index{underfitting}underfitting occurs when the model is too simple relative to
the underlying structure of the training data.

\subsection{Training Sets}
\label{sec:anns:training:sets}

The input data is split proportionally into a training and testing set. Data in
the training set is used to train the \ac{FFNN} \cite{ref:james:2013}, while the
generalisation capabilities of the \ac{FFNN} is evaluated over the performance
of the trained model when exposed to never before seen data in the testing set.
Some research propose a validation set whereby the trained model is evaluated on
the validation data while hyper-parameters are tuned \cite{ref:brownlee:2017}.

\subsection{Supervised Learning}
\label{sec:anns:training:supervised_learning}

\index{supervised learning}Supervised learning is the process of learning where
the training data that is presented to the \ac{FFNN} includes the desired
solution \cite{ref:geron:2017}.  The \ac{FFNN} learns the mapping function from
the input to the target output \cite{ref:brownlee:2016}. These desired solutions
are referred to as \textit{labels}. \index{supervised learning}Supervised
learning can be used for both classification and regression problems.

There are two types of supervised learning algorithms based on when weights are
updated \cite{ref:engelbrecht:2007}. These include stochastic training and batch
training and is discussed next.

\subsubsection{Stochastic Training}
\label{sec:anns:training:stochastic}

\index{Stochastic Training}Stochastic training, also known as \index{Online
Learning}\textit{online learning}, is a \index{Supervised Learning}supervised
learning variation whereby weights are adjusted after each training pattern is
presented.

If \index{stochasting training}stochastic training is used to train the
\ac{FFNN}, the training data must be shuffled before splitting into sets, in
order to avoid overfitting or memorising the order in which patterns are
presented in the training set \cite{ref:engelbrecht:2007}. It has been shown
that shuffling the training data can speed up convergence
\cite{ref:bengio:2012}.

\subsubsection{Batch Training}
\label{sec:anns:training:batch}

\index{Batch Training}Batch training, also known as \index{Offline
Learning}\textit{offline learning} is a supervised training variation whereby
the weight changes are accumulated and used to adjust the weights once after all
the training patterns have been presented.

\subsubsection{Mini-Batch Training}
\label{sec:anns:training:mini_batch}

Research suggests a trade-off between stochastic and batch training by making
use of mini-batches \cite{ref:bengio:2012}. Mini-batch training is the same as
batch training, however, weights are updated after $\beta$ patterns have been
presented, where $\beta$ is the batch size.

\subsection{Error Functions}
\label{sec:anns:training:error_functions}

An error function, also known as a \index{Loss Function}\index{Cost
Function}\textit{loss/cost function} \cite{ref:changhau:2017} is used to
evaluate the model's capability to approximate output data based on the input
patterns presented. It measures the degree to which the model is capable of
predicting the correct output data.  This error value is used by the
\index{Heuristics}heuristic as a guide during the training process.

This thesis focusses on the following error functions: \ac{SSE}, \ac{MSE},
\ac{RMSE}, \ac{MAE}, \ac{BinXE}, \ac{CatXE} and \ac{SparseCatXE}. Each of these
are discussed next.

\subsubsection{Sum Squared Error}
\label{sec:anns:training:error_functions:sse}

The \ac{SSE} is computed using:

\begin{equation}
    \epsilon = \sum_{p=1}^P \sum_{k=1}^K (\hat{y}_{k,p} - y_{k,p})^2
    \label{eq:sse}
\end{equation}

\noindent where $\hat{y}_{k,p}$ is $k$-th dimension of the target output of
pattern $p$, $y_{k,p}$ is $k$-th dimension of the predicted output vector
$\vec{y}_{p}$ for pattern $p$, $P$ is the number of patterns in the training
set, and $K$ is the number of dimensions in the output vector $\vec{y}$.

\subsubsection{Mean Squared Error}
\label{sec:anns:training:error_functions:mse}

The \ac{MSE} is computed using:

\begin{equation}
    \epsilon = \frac{\sum_{p=1}^P \sum_{k=1}^K (\hat{y}_{k,p} - y_{k,p})^2}{PK}
    \label{eq:mse}
\end{equation}

\subsubsection{Root Mean Squared Error}
\label{sec:anns:training:error_functions:rmse}

The \ac{RMSE} is computed using:

\begin{equation}
    \epsilon = \sqrt{\frac{\sum_{p=1}^P \sum_{k=1}^K (\hat{y}_{k,p} - y_{k,p})^2}{PK}}
    \label{eq:rmse}
\end{equation}

\subsubsection{Mean Absolute Error}
\label{sec:anns:training:error_functions:mae}

The \ac{MAE} is computed using:

\begin{equation}
    \epsilon = \frac{\sum_{p=1}^P \sum_{k=1}^K |\hat{y}_{k,p} - y_{k,p}|}{PK}
    \label{eq:mae}
\end{equation}

\subsubsection{Binary Cross-Entropy}
\label{sec:anns:training:error_functions:bin_xe}

\noindent The \ac{BinXE} is computed using:

\begin{equation}
    \epsilon = -\frac{\sum_{p=1}^P \sum_{k=1}^K (\hat{y}_{k,p} \log{(y_{k,p})} + (1 - \hat{y}_{k,p})\log{(1 - y_{k,p})})}{PK}
    \label{eq:bin_xe}
\end{equation}

\noindent \ac{BinXE} is used in classification problems, where there are only
two classes in the target output data.

\subsubsection{Categorical Cross-Entropy}
\label{sec:anns:training:error_functions:cat_xe}

The \ac{CatXE} is computed using:

\begin{equation}
    \epsilon = -\frac{\sum_{p=1}^P \sum_{k=1}^K \sum_{c=1}^C (\mathbbm{1}_{\hat{y}_{k,p} \in C_c} \log{(y_{k,p} \left[ y_{k,p} \in C_c \right])})}{PK}
  \label{eq:cat_xe}
\end{equation}

\noindent where $\mathbbm{1}$ is the indicator function that the $k$-th index observation
belongs to the $c$-th class. $C$ is the total number of unique class labels. If
$C = 2$, then \ac{BinXE} can be used instead.

\ac{CatXE} is used in classification problems where the target
output or \textit{label} is a one-hot encoded vector.

\subsubsection{Sparse Categorical Cross-Entropy}
\label{sec:anns:training:error_functions:sparse_cat_xe}

The \ac{SparseCatXE} error function is the same as \ac{CatXE} with the only
difference being that the target output or label is a one-hot
embedding of a class represented as an integer, $c \in \{1,2, \dots, C\}$.

\subsection{Performance Measures}
\label{sec:anns:training:performance_measures}

Performance measures play an important role in understanding how well a
\ac{FFNN} has been trained to predict target output. Performance metrics are
used during training on the training set and evaluation on the test set. These
performance metrics provide a mechanism by which different implementations of
\acp{FFNN} and training processes can be compared.

There are many different mechanisms that can be used to measure the performance
of a \ac{FFNN}, however this thesis only focusses on measures of cost such as
loss and speed. Brief discussions follow on loss and speed as performance
measures.

\subsubsection{Loss/Cost}
\label{sec:anns:training:performance_measure:loss_cost}

A measure of cost indicates how well the \ac{FFNN} is able to predict target
output and often include a metric over some distance between the predicted
output and target output. This metric is calculated using an error function as
described in Section~\ref{sec:anns:training:error_functions}.

In the case of classification problems, the loss/cost can be expressed in terms
of \textit{accuracy}. Accuracy refers to the percentage of patterns for which
the \ac{FFNN} was able to successfully predict the target output.

\subsubsection{Speed}
\label{sec:anns:training:performance_measure:speed}

Speed is a performance measure which calculates how fast a \ac{FFNN} can reach
some target goal. Speed is often expressed relative to another performance
measurement metric e.g how many epochs of training is necessary for a \ac{FFNN}
to reach a certain lost/cost threshold. If emperical tests run on simular
enviroments, relative time of execution can be used, but this is less popular.

For this thesis, speed is a measure of performance relative to training
\textit{steps} or \textit{mini-batch} steps.

\subsection{Stopping Conditions}
\label{sec:anns:training:stopping_conditions}

Stopping conditions are required to stop the training process. The goal of the
stopping condition is to try and stop the training process to avoid unnecessary
computational cost or to set a comparible timeframe in which \acp{FFNN} are
trained. Stopping conditions include:

\begin{itemize}
    \item
    \textbf{Max Epochs}: Stop when a maximum number of epochs has been reached.

    \item
    \textbf{Performance Measurement Threshold}: Stop the training when the
    performance measurement metric has reached some acceptable threshold.

    \item
    \textbf{Stagnation}: Stop the training process if no improvements in the
    performance of the model is observed over a window of epochs.

    \item
    \textbf{Overfit}: Stop the training process if the generalisation on the
    test set indicates that the \ac{FFNN} is overfitting the data.
\end{itemize}

\section{Summary}
\label{sec:anns:summary}

This chapter presented background information on the \ac{BN} and it was shown
how neurons connect to each other. Emphasis was put on \index{Synapse}synapses
and how communication happens between neurons. The \ac{AN} was introduced in
Section~\ref{sec:anns:an} and it was shown how the brain inspired the
development of \acp{AN}. Brief discussions followed on the various components
that make up the \ac{AN}. Details on input, weights, \index{net input signal}net
input signal, biases, \index{activation function}activation functions, and
output were provided.  Section~\ref{sec:anns:ann} introduced \acp{ANN}. It was
shown how \acp{AN} are connected together to form networks. \ac{ANN} design was
described in terms of architecture and topologies. Special emphasis was put on
\acp{FFNN} as the model being used throughout the rest of the thesis.
Section~\ref{sec:anns:training} provided the necessary background information
required on the training of \acp{FFNN}. It is emphasised that the training of an
\ac{ANN} is an optimisation problem where optimal values for weights and biases
are sought such that a given cost function is minimised. The training process
was explained and details on training sets was provided. A variant of learning,
called \index{Supervised Learning}supervised learning is presented and led to
the discussion on error functions, performance measures, and stopping
conditions.

Chapter~\ref{chap:heuristics} introduces background information on optimisation
and heuristics.

### 2022-01-07 thesis/chapters/03-heuristics.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\chapter{Heuristics}
\label{chap:heuristics}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{quote}
\it {
  Albert Einstein once said: "Look deep into nature, and then you will understand everything better". Nature has inspired the development of many different optimisation techniques. One such technique investigates the flocking of birds while foraging or in flight. Other techniques are inspired by ants, bees and fungi. 
}
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The fittest will survive \cite[p.~444]{ref:spencer:1864}. This concept drives the evolutionary process. Species either hunt or are being hunted. Over millions of years, the living have evolved some fascinating techniques to improve their chances of survival. These techniques include everything from camouflage, stealth, strength, speed and many more. One well-known example of this is Darwin's Finches as described in the book by David Lack \cite{ref:lack:1983} in 1947. Finches from the Galapagos islands have been found to evolve distinctly different beak shapes and sizes depending on the food sources that were present on the various islands. This process of improvement over time is necessary for species to survive. Determining the ideal survival method is a difficult task and finding an optimal solution to this problem can be seen as a search problem.

The search process is a strategic process in which better solutions to problems are being sought out. This strategic process is executed by search techniques known as Heuristics \todo[inline]{refs}. Training of NNs is itself a search process as the ideal weight values that minimises the cost of the NN are strategically being searched for. HHs takes this concept a step further by searching for the ideal heuristic in heuristic-space, to be used to find optimal solutions to problems.

This chapter provides the necessary background information on heuristics and is structured as follows:

\begin{itemize}
  \item Section~\ref{sec:heuristics:optimisation} provides readers with a  necessary overview of optimisation and the fundamentals that drive search processes. Furthermore it is shown how the training of NNs is an optimisation problem. Various techniques that have been used to train NNs are provided.
  \item Sections~\ref{sec:heuristics:gradient-descent}, \ref{sec:heuristics:adaptive-gradients}, \ref{sec:heuristics:adaptive-delta}, \ref{sec:heuristics:momentum}, \ref{sec:heuristics:rmsprop} and \ref{sec:heuristics:adam} provide details on classic heuristics that make use of mathematical constructs to find optimum solutions to problems. Classic heuristics that are discussed include Gradient Descent (GD) and its various improvements such as Adaptive Gradients (AdaGrad), Adaptive Delta (AdaDelta), GD with Momentum, Root Mean Squared Propagation (RMSProp) and Adaptive Momentum (Adam)\todo[inline]{acronyms}.
  \item Sections~\ref{sec:heuristics:pso}, \ref{sec:heuristics:de} and \ref{sec:heuristics:ga} discusses Meta-Heuristics. In particular, population-based approaches are the focus of these sections and includes detailed discussions on Particle Swarm Optimisation (PSO), Differential Evolution (DE) and Genetic Algorithms (GA).
  \item Section~\ref{sec:heuristics:meta-learning} provides a brief overview of Meta-Learning and shows how it is related to Hyper-Heuristics (HHs).
  \item The chapter is then concluded and summarised in Section~\ref{sec:heuristics:summary}.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Optimisation}
\label{sec:heuristics:optimisation}

Optimisation is the task of finding a solution to a given problem that is better than alternative solutions. Better stated by Oldewage \cite{ref:oldewage:2017}, optimisation is the task of finding values for a set of variables such that some measure of optimality is satisfied given a set of constraints. Engelbrecht \cite{ref:engelbrecht:2007} breaks optimisations problems down into three components:

\begin{itemize}
  \item An \textbf{objective function}: Represents the quantity to be optimised and is used as the "measure of optimality". Optimisation can be defined in terms of the minimisation or maximisation of the objective function $f$. 
  \item A \textbf{set of unknowns or independent variables}: These affect the outcome of the objective function $f$ and is denoted as $x$. $f(x)$ is thus the quantification of the objective function over the unknowns $x$.
  \item A \textbf{set of constraints}: This restrict and limit the values that can be assigned to the unknowns $x$. Optimisation problems that contain must adhere to a set of constraints are referred to as constraint-satisfaction problems (CSPs).
\end{itemize}

The goals of heuristics is to find a set of valid values for $x$ that optimises the objective function while adhering to a set of constraints. Heuristics thus search for solutions, referred to as candidate solutions, in a set of all possible and valid solutions, referred to as the feasible search space.

For HHs this definition is also valid. The HH just searches, on a higher level, for an optimal combination and collaboration of lower level heuristics in a heuristic space that is then used to optimise $f(x)$.

Optimisation problems come in a wide variety of forms. Mostly these functions are defined in terms of the number of variables used (uni- vs. multivariate), the number of objective functions used (single- vs. multi-objective), the degree of linearity (linear vs. quadratic/polynomial), the number of optima (uni- vs. multi-modal), the nature of the environment (static vs. dynamic), the types of variables used (separable vs. inseparable, discrete vs. continuous) and  the set of constraints that the solution has to adhere to (constrained vs unconstrained).

Optima can be defined as local or global optima. Local optima is the best optimisation of $f(x)$ in a neighbourhood of solutions, while the global optima is the best optimisation of $f(x)$ over all solutions in the solution space.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Training of Neural Networks is an Optimisation Problem}
\label{sec:heuristics:nns-optimisation-problem}

In Section~\todo[inline]{ref}, it is mentioned that NNs are universal function approximators. The accuracy of the approximation of a function by the NN is measured by some performance measure as discussed in Section~\todo[inline]{ref}. Given the definition of optimisation problems one can see how the training of NNs adhere to all three components that make up optimisation problems as follows:

\begin{itemize}
  \item \textbf{Objective function:} The objective of a NN is to approximate some function $f$. The ability of a NN to closely approximate $f$, is referred to as the performance of the NN and is  measured by some performance measure as described in Section~\todo[inline]{ref}. This performance measure is seen as the objective function.
  \item \textbf{Set of independent variables:} By strategically fine-tuning the weights of the NN, the quantification of the NN is altered. The weights to be altered are the independent variable of the NN.
  \item \textbf{Set of constraints:} Training of NNs is restricted to produce only valid output, while still performing well over some performance measure.
\end{itemize}

Researchers have used many different techniques to train Neural Networks. Broadly speaking, the most popular techniques include classic heuristics such as Gradient Descent (GD) and its variants and improvements \todo[inline]{ref}. This is largely due to the fact that NNs are trained much faster on GPUs when compared to training on CPUs \todo[inline]{ref} as GPUs as better fitted to compute large blocks of data (vectors/matrices/tensors), typically as NN weights would be represented.

Other techniques used to train NNs include population-based metaheuristics such as PSOs, DEs and GAs \todo[inline]{refs}. Each of the above mentioned techniques are discussed next.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Gradient Descent}
\label{sec:heuristics:gradient-descent}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Adaptive Gradients}
\label{sec:heuristics:adaptive-gradients}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Adaptive Delta}
\label{sec:heuristics:adaptive-delta}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Momentum}
\label{sec:heuristics:momentum}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Root Mean Squared Propagation}
\label{sec:heuristics:rmsprop}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Adaptive Momentum}
\label{sec:heuristics:adam}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Particle Swarm Optimisation}
\label{sec:heuristics:pso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Differential Evolution}
\label{sec:heuristics:de}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Genetic Algorithms}
\label{sec:heuristics:ga}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Meta-Learning}
\label{sec:heuristics:meta-learning}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}
\label{sec:heuristics:summary}

### 2022-01-07 thesis/chapters/05-probability.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\chapter{Probability Test}
\label{chap:probability}

\begin{quotation}
    \textit{I flip the coin in the air. Heads. I flip the coin in the air.
        Tails. I do this, probably hundreds of times, until finally, ten heads
        in a row. Suddenly it hit me. Despite knowing the odds, despite knowing
        that it might take a long time, we still hope, because we know, no
    matter the odds, there is still a chance.}
\end{quotation}

Probability theory finds its application in many fields today ranging from
finance to medicine. It is a powerful tool that allows us to predict the
future, with a certain degree of surity. Probability theory finds its place in
the field of \ac{ML} too. In 1991,
\citeauthor{ref:denker:1991}, \cite{ref:denker:1991} proposed a way to transform
\ac{ANN} outputs to probability distributions . In 1993,
\citeauthor{ref:neal:1993} \cite{ref:neal:1993} developed the first \ac{MCMC}
sampling algorithm for Bayesian \acp{NN}. This shows that probability theory
can be used as a mechanism for learning in \acp{ANN}.

The purpose of this chapter is to provide the necessary background information
needed to understand probability theory as it plays a vital role in the
formulation of the \ac{BHH}.  The chapter is structured as follows:

\begin{itemize}
    \item
    Section~\ref{sec:probability:probability} gives a brief overview of what
    probability is and how it is used.

    \item
    Section~\ref{sec:probability:joint_probability} gives a brief overview of
    how probabilities are interpreted for random events that are considered
    jointly.

    \item
    Section~\ref{sec:probability:cond_probability} introduces conditional
    probability. Brief discussions follow on the \textit{frequentist} view
    of conditional probability as well as the \textit{Bayesian} view of
    conditional probability through \textit{Bayes Theorem}.

    \item
    Section~\ref{sec:probability:likelihood} gives a brief overview of the
    concept of likelihood. A brief discussion follow on how likelihood is used
    alongside probability.

    \item
    Section~\ref{sec:probability:probability_distributions} presents relevant
    probability distributions, including the \index{beta
    distribution}\textit{beta} distribution, the \index{dirichlet
    distribution}\textit{dirichlet} distribution, the \index{bernoulli
    distribution}\textit{bernoulli} distribution, the \index{binomial
    distribution}\textit{binomial} distribution, the \index{categorical
    distribution}\textit{categorical} distributions, and the \index{multinomial
    distribution}\textit{multinomial} distribution.

    \item
    Section~\ref{sec:probability:conjugate_priors} presents the conjugate prior
    probability distributions for the \index{bionomial likelihood}binomial
    likelihood as well as the \index{categorical likelihood}\index{multinomial
    likelihood}categorical/multinomial likelihood.

    \item
    Section~\ref{sec:probability:bayesian_stats} presents \textit{Bayesian}
    statistics. It is shown how Bayes' Theorem can be used as an inferencing
    mechanism. Detailed discussions follow on \index{Bayesian
    optimisation}Bayesian optimisation methods such as \index{Bayesian
    inference}\textit{Bayesian inference} and \index{Bayesian analysis}\textit{Bayesian analysis}.

    \item
    Finally, a brief summary of the chapter is given in
    Section~\ref{sec:probability:conclusion}.
\end{itemize}

\section{Probability}
\label{sec:probability:probability}

In everyday conversation, the term \textit{probability} is a measure of one's
belief in the occurrence of a future event \cite{ref:wackerly:2014}.
Consider flipping an unbiased, fair coin. One could consider the probability of
an outcome, whether it is heads or tails, to be a ratio of the possible number
of outcomes. In the case of a coin, the number of outcomes is just two. This
means that one can \textit{believe} that the coin would land with the head-side
up with $1/2$ odds.

Probability can be inferred and confirmed through past events. The support of
these inferred probabilities get stronger as more and more samples of
independent random events, such as flipping of a fair coin, are gathered.  In
the case of flipping a fair coin, the \ac{CLT} shows that the normalised sum of
events tends toward a normal distribution with a mean value of $0.5$ if the
number of events observed $n$ is large (usually $n \geq 30$)
\cite{ref:wackerly:2014}. This shows that the probability of the coin landing
on heads is $50\%$. An illustration of a coin flipping simulation that shows
the central limit theorem on various sample sizes is provided below:

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{coin_flip_samples_100.png}
        \caption[Coin flip simulation. Samples=100]{100 samples}
        \label{fig:coin_flip_simulation_samples_100}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{coin_flip_samples_10000.png}
        \caption[Coin flip simulation. Samples=100]{10000 samples}
        \label{fig:coin_flip_simulation_samples_10000}
    \end{subfigure}
    \caption{An illustration of the \index{central limit theorem}central limit theorem on a coin flip simulation}
    \label{fig:coin_flip_simulation}
\end{figure}

\section{Joint Probability}
\label{sec:probability:joint_probability}

\section{Conditional Probability}
\label{sec:probability:cond_probability}

\subsection{Frequentist}
\label{sec:probability:cond_probability:frequentist}

\subsection{Bayes Theorem}
\label{sec:probability:cond_probability:bayes_theorem}

\section{Likelihood}
\label{sec:probability:likelihood}

\section{Probability Distributions}
\label{sec:probability:probability_distributions}

\subsection{Beta Distribution}
\label{sec:probability:probability_distributions:beta}

The Beta distribution is a family of univariate continuous probability distributions over some $x$, with support on the interval $[0,1]$. It is parametrised by two shape parameters $\alpha > 0, \alpha \in \mathbb{R}$ and $\beta > 0, \beta \in \mathbb{R}$. The Beta distribution is denoted as $Beta(\alpha, \beta)$. The  PDF of the Beta distribution is given below as:

\begin{equation}
P(x | \alpha, \beta) = f_{Beta}(x; \alpha, \beta) = \frac{1}{B(\alpha, \beta)} x^{\alpha - 1} (1 - x)^{\beta - 1}
\end{equation}

where the normalising  constant $B(\alpha, \beta)$ is defined as:

\begin{equation}
B(\alpha, \beta) = \frac{\Gamma(\alpha)\Gamma(\beta)}{\Gamma(\alpha + \beta)}
\end{equation}

and $\Gamma$ is the Gamma function as defined below:

\begin{equation}
\Gamma(n) = ( n - 1)!
\end{equation}

The Gamma function can also be written as:

\begin{equation}
\Gamma(n+1) = n!
\end{equation}

If should be noted that $\alpha$ and $\beta$ determine the shape of the distribution. There exists a special case when $\alpha = \beta$. This is referred to as the symmetric Beta distribution. In the case where $\alpha = \beta = 1$ the distribution is equivalent to the uniform distribution over all points in its support. The Beta distribution for various values of $\alpha$ and $\beta$, including the symmetric version is presented below in figures (???):

INSERT FIGURE HERE.

The expected value of $x$ is given below as:

\begin{equation}
E[x] = \frac{\alpha}{\alpha + \beta}
\end{equation}

Similarly, the expected value of the natural logarithm of $x$ can be calculated as shown below:

\begin{equation}
E[\ln(x)] = \psi({\alpha}) - \psi(\alpha + \beta)
\end{equation}

where $\psi$ is the logarithmic derivative of the Gamma function, called the Digamma function. The Digamma function is defined below as:

\begin{equation}
\psi(n) = \frac{d}{dn}\ln(\Gamma(n)) = \frac{\Gamma'(n)}{\Gamma(n)}
\end{equation}

Finally, the mode of the distribution is given below as:

\begin{equation}
Mo[x] = E[x] - 1 = \frac{\alpha - 1}{\alpha + \beta - 1}
\end{equation}

\subsection{Dirichlet Distribution}
\label{sec:probability:probability_distributions:dirichlet}

The Dirichlet distribution is a family of multivariate continuous probability distributions over some $x$ in $K$ dimensions. The Dirichlet distribution is the multivariate generalization of the Beta distribution and is thus sometimes referred to by its alternative name, the Multivariate Beta Distribution (MBD). The Dirichlet distribution is parametrised by some vector $\alpha = (\alpha_{1}, \dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} > 0, \alpha_{k} \in \mathbb{R}$. $\alpha$ is referred to as the  concentration parameter. The Dirichlet distribution of order $K \geq 2$ with parameters $\alpha$, denoted $Dir(\alpha)$, has a PDF as given below:

\begin{equation}
P(x | \alpha) =  f_{Dir}(x; K, \alpha) = \frac{1}{B(\alpha)}  \prod_{k=1}^{K} x_{k}^{\alpha_{k} - 1}
\end{equation}

where the normalising constant $B(\alpha)$ is defined as:

\begin{equation}
B(\alpha) = \frac{\prod_{k=1}^{K} \Gamma(\alpha_{k})}{\Gamma(\alpha_{0})}
\end{equation}

and $\alpha_{0}$ is defined as:

\begin{equation}
\alpha_{0} = \sum_{k=1}^{K}\alpha_{k}
\end{equation}

Importantly, the set $\{x_{k}\}_{k=1}^{K}$ belongs to the standard $K-1$ probability simplex $S$, meaning that $x_{K} = 1 - \sum_{k=1}^{K-1}x_{k}$ with support $\forall_{k=1}^{K} x \in [0,1]$. Under the simplex $S$, this means that the sum over all values of the vector $x$ must be 1. The simplex can thus be rewritten as $\sum_{k=1}^{K}x_{k} = 1$.

Similar to the Beta distribution, $\alpha$ determines the shape of the distribution in $K$ dimensions and thus, there also exist a special case, referred to as the symmetric distribution when $\forall_{k=1}^{K} \alpha_{k} = c$, where $c$ is some constant. In the case where $c = 1$, the distribution is referred to as a flat distribution and yields the uniform distribution over all points in $S$. The Dirichlet distribution of order $K = 3$, for various values of $\alpha$ , including the symmetric version is presented in figures (???) below:

INSERT FIGURE HERE.

The expected value of $x$ is given below as:

\begin{equation}
E[x_{k}] = \frac{\alpha_{k}}{\alpha_{0}}
\end{equation}

Similarly, the expected value of the natural logarithm of $x_{k}$ can be calculated as follows:

\begin{equation}
E[\ln(x_{k})] = \psi({\alpha_{k}}) - \psi(\alpha_{0})
\end{equation}

where $\psi$ is the Digamma function as defined in Equation (???). Finally, the mode of the distribution is given as:

\begin{equation}
\begin{split}
	Mo[x_{k}] &= E[{x_{k}] -K^{-1}} \\
		&=  \frac{\alpha_{k} - 1}{\alpha_{0} - K}
\end{split}
\end{equation}

\subsection{Bernoulli Distribution}
\label{sec:probability:probability_distributions:bernoulli}

The Bernoulli distribution is a discrete probability distribution over some random variable $x$ that takes the value of $1$ with probability $\theta$ and $0$ with probability $1-\theta$. It is denoted as $Ber(\theta)$ with support $x \in \{0, 1\}$. In probability theory, the Bernoulli distribution is often used to explain the possible outcomes of a single experiment that asks a \textit{yes-no} question such as flipping a coin (ref ???). The outcome of such an experiment is a boolean value. The Bernoulli distribution has a PMF as given below:

\begin{equation}
P(x | \theta) = f_{Ber}(x; \theta) =
	\begin{cases}
		\theta & \text{if}\ x=1 \\
      	1 - \theta & \text{if}\ x=0
	\end{cases}
\end{equation}

The above equation can also be expressed as:

\begin{equation}
f_{Ber}(x; \theta) = \theta^{x}(1-\theta)^{1-x}
\end{equation}

% (See 3rd paragraph: $https://en.wikipedia.org/wiki/Central_limit_theorem$???). 
\todo[inline]{See comment in code}
The mean of the Bernoulli distribution approaches $\theta$ over many samples as
explained in the Central Limit Theorem The expected value of the distribution is thus given as:

\begin{equation}
E[x] = \theta
\end{equation}

while the mode of the distribution is given as:

\begin{equation}
Mo[x_{k}] = 
\begin{cases}
	0 & \text{if}\ \theta < 0.5 \\
    	0,1 & \text{if}\ \theta = 0.5 \\
    	1 & \text{if}\ \theta > 0.5 \\
\end{cases}
\end{equation}

\subsection{Binomial Distribution}
\label{sec:probability:probability_distributions:bin}

The Binomial distribution is a discrete probability distribution over a random variable $x$ taking on a number of successes, in $N$ sequential independent experiments that each ask a \textit{yes-no} question. The probability of a single independent experiment yielding a success is given as $\theta$ and the Binomial distribution is denoted as $Bin(N, \theta)$ with support $x \in \{0, 1, \dots, N\}$.  It should be noted that the Binomial distribution is the extension of the Bernoulli distribution over $N$ independent sequential experiments and thus, each experiment also yields some boolean outcome. When $N=1$, the experiment is referred to as a Bernoulli trial and the distribution is just a Bernoulli distribution and when $N > 1$, the sequence of outcomes is referred to as a Bernoulli process. The PMF of the Binomial distribution is given as follows:

\begin{equation}
    P(x \vert \theta; N) = f_{Bin}(x; N, \theta) = \binom{N}{x} \theta^{x}(1-\theta)^{1-x}
\end{equation}

The mean of the Binomial distribution is just $N\theta$ given the Central Limit Theorem (See paragraph 3 $https://en.wikipedia.org/wiki/Central_limit_theorem$ ???). The expected value of the Binomial distribution is thus given as:

\begin{equation}
E[x] = N\theta
\end{equation}

while the mode of the distribution is given as:

\begin{align}
\begin{split}
Mo[x_{k}] &= E[x] + \theta \\
	&= N\theta  + \theta \\
	&= (N  + 1)\theta
\end{split}
\end{align}

\subsection{Categorical Distribution}
\label{sec:probability:probability_distributions:categorical}

The Categorical distribution is a discrete probability distribution over some random variable $x$, taking on any one of $K$ possible categories. There is no innate underlying ordering to these categories, so for simplicity, each category is assigned a numerical representative value such that $k = (1, \dots, K)$. The probabilities for all outcomes is given by the probability vector $\theta = (\theta_{1}, \dots, \theta_{K})$.  This means that the probability $P(x=k)=\theta_{k}$, with support $x \in \{1, \dots, K\}$. The Categorical distribution, denoted $Cat(\theta)$ is the generalization of the Bernoulli distribution and is sometimes referred to it by its alternative names, the Generalized Bernoulli Distribution (GBD) or the Multinoulli distribution. In probability theory, the Categorical distribution is often used to explain the outcome of a single experiment with more than two possible outcomes such as rolling a die (ref ??). The PMF of the Categorical distribution is given as:

\begin{equation}
P(x | \theta; K) = f_{Cat}(x; K, \theta) = \prod_{k=1}^{K}\theta_{k}^{[x = k]}
\end{equation}

where $[x = k]$ is the Iversion Bracket (ref ???), yielding 1 if $x = k$ and 0 otherwise. From this, one can conclude that:

\begin{equation}
f_{Cat}(x=k; K, \theta) = \theta_{k}
\end{equation}

The random variable $x$ can also be encoded in binary format, yielding a vector $x = (x_{1}, \dots, x_{K})$ of Bernoulli distributions such that the support is $\forall_{k=1}^{K} x_{k} \in \{0, 1\}$. Importantly, if the outcome of the random event is of category $k$, then $x_{k} = 1$ and $\forall_{j=1}^{K} x_{j} = 0, j \neq k$ so that the standard $K-1$ probability simplex $S$ still holds. The PMF of the Categorical distribution can then be rewritten as follows:

\begin{equation}
f_{Cat}(x; K, \theta) = \prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{k})}
\end{equation}

where $\mathbbm{1}(x_{k})$ is the Indicator Function, yielding 1 if $x_{k} = 1$ and 0 otherwise.

Since there is no innate order to the underlying categories, the mean of the distribution does not yield any relevant information (ref??). The mode of the distribution is given below as:

\begin{equation}
Mo[x] = \argmax_{k}(\theta_{1}, \dots, \theta_{K})
\end{equation}

\subsection{Multinomial Distribution}
\label{sec:probability:probability_distributions:multinomial}

The Multinomial distribution is a discrete probability distribution over some random variable $x = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials. The probabilities for all possible outcomes in a single trial is given by the probability vector $\theta = (\theta_{1}, \dots, \theta_{K})$. The Multinomial distribution, denoted $Mul(N, K, \theta)$, is thus the generalization of the Binomial distribution to $K$ dimensions. Note that when:

\begin{itemize}
	\item When $K$ is 2 and $N = 1$, the Multinomial distribution is the Bernoulli distribution.
	\item When $K$ is 2 and $N > 1$, the Multinomial distribution is the Binomial distribution.
	\item When $K > 2$ and $N = 1$, the Multinomial distribution is the Categorical distribution.
\end{itemize}

The support for the Multinomial is $\forall_{i=1}^{K} x_{k} \in \{1, \dots, N\}, \sum_{k=1}^{K}x_{k} = N$ and the PMF for the Multinomial distribution is given as:

\begin{equation}
P(x | \theta; N; K) = f_{Mul}(x; N, K, \theta) = \frac{N!}{\prod_{k=1}^{K}x_{k}!} \prod_{k=1}^{K}\theta_{k}^{x_{k}}
\end{equation}

Similar to the Categorical distribution, the random variable $x$ can also be encoded in binary format, yielding an $N \times K$ matrix $X$ of Bernoulli distributions. The support is then given as $X \in \{0, 1\}^{N \times K}, \forall_{i=1}^{N}\sum_{k=1}^{K} x_{i,k} = 1$ so that the standard $K-1$ probability simplex $S$ still holds for each trial. The PMF of the Multinomial distribution can then be rewritten as follows:

\begin{equation}
\begin{split}
f_{Mul}(x; N, K, \theta) &= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!}\prod_{i=1}^{N}\prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{i,k})} \\
	&= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!} \prod_{k=1}^{K}\theta_{k}^{\sum_{i=1}^{N}\mathbbm{1}_{1}(x_{i,k})} \\
	&= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!} \prod_{k=1}^{K}\theta_{k}^{N_{k}} \\
\end{split}
\end{equation}

where $N_{k}$ is a summary variable denoting the number of times a category $k$ occurs over all trials in $N$. The reason why the Categorical and Multinomial distributions are presented as binary encoded vectors is to simplify the proof of their conjugate priors as will be shown next. This is further supported by the fact that NNs often use binary encoding of feature vectors. The combination of these probabilitic methods and NNs forms the basic of this research dissertation.

\section{Conjugate Priors}
\label{sec:probability:conjugate_priors}

\subsection{Binomial Likelihood}
\label{sec:probability:conjugate_priors:binom_likelihood}

The conjugate prior to a Bernoulli distribution is the Beta distribution
(ref???). This is shown by demonstrating that the posterior distribution has the
same functional form $\mathcal{A}(v)$ as the prior distribution as follows: \\
\textbf{Setup}:

\begin{itemize}
	\item Let $I$ be a number of independent, identical  (iid) random events.
	\item Let $\alpha \in \mathbb{R}, \alpha > 0$ and $\beta \in \mathbb{R}, \beta >0$ be the shape parameters to the Beta distribution.
	\item Let $\theta$ be the probability of a success. With $\theta | \alpha, \beta \sim Beta(\alpha, \beta)$.
	\item $P(\theta)$ is the prior probability distribution with the functional form $\mathcal{A}(v)$.
	\item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with boolean outcome. That is $x_{i} | \theta \overset{\text{iid}}{\sim} Ber(\theta)$ and thus $\mathcal{L}(x_{i} \vert \theta)$ is the Bernoulli log likelihood.
	\item Let $\mathcal{D}$ denote all the prior data $X, \alpha, \beta$.
	\item Let $N_{1} = \sum_{i=1}^{I} \mathbbm{1}(x_{i} = 1)$ and $N_{0} = \sum_{i=1}^{I} \mathbbm{1}(x_{i} = 0)$.
	\item  The likelihood of the Bernoulli distribution is:

\begin{equation}
\begin{split}
	\mathcal{L}(\mathcal{D}) &=  P(\mathcal{D} | \theta) \\
	&\propto \theta^{N_{1}}(1-\theta)^{N_{0}}
\end{split}
\end{equation}

\end{itemize}

\textbf{Then}:

\begin{itemize}
	\item  By Bayes Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given as:

\begin{equation}
\begin{split}
	P(\theta | \mathcal{D}) &= \frac{P(\mathcal{D} | \theta) P(\theta)}{P(\mathcal{D})}
\end{split}
\end{equation}

	\item Since the denominator sums to $1$, one could get rid of the denominator and constants for the Bernoulli likelihood and the Beta prior, by expressing the posterior as proportional to:

\begin{equation}
\begin{split}
		P(\theta | \mathcal{D}) &\propto \left[\theta^{N_{1}}(1-\theta)^{N_{0}}\right] \left[\theta^{\alpha - 1} (1 - \theta)^{\beta - 1}\right] \\
		&\propto \theta^{(N_{1} + \alpha) - 1}(1-\theta)^{(N_{0} + \beta) - 1} \\
		&\propto Beta(N_{1} + \alpha, N_{0} + \beta) 
\end{split}
\end{equation}

\item Yielding a posterior of the same functional form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N_{1} + \alpha$ and $\beta' = N_{0} + \beta$.

\end{itemize}

This shows that the Beta distribution is the conjugate prior to the Bernoulli likelihood.

Furthermore, it should be noted now that this updating of one's prior beliefs by new evidence as shown above forms the basis for this entire research dissertation. (<<Mention something here about the quote from the master algorithm) >> This is shown in more detail in Chapter (???), however, for now, let us now consider the conjugate prior to the Categorical and Multinomial distributions.

\subsection{Categorical and Multinomial Likelihood}
\label{sec:probability:conjugate_priors:cat_mult_likelihood}

The conjugate prior to a Categorical and Multinomail distribution is the Dirichlet distribution (ref???). Similar to the proof of the conjugate prior for the Bernoulli distribution as shown above, this means that the posterior distribution must have the same functional form $\mathcal{A}(v)$ as the prior distribution. This is shown as follows: \\
\textbf{Setup}:

\begin{itemize}
	\item Let $I$ be a number of independent, identical (iid) random events.
	\item Let $K$ be a number of possible outcomes for each event, with $K \geq 2$.
	\item Let $\alpha = (\alpha_{1}, \dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} \in \mathbb{R}, \alpha_{k} > 0$ be the concentration parameters to the Dirichlet distribution.
	\item Let $\theta = (\theta_{1}, \dots, \theta_{K}), \forall_{k=1}^{K} \theta{k} \in (0,1), \sum_{k}^{K} \theta{k} = 1$ be the probability of each class in $K$ and $\theta$ belongs to the standard $K-1$ probability simplex $S$. With $\theta | \alpha \sim Dir(K, \alpha)$. 
	\item $P(\theta)$ is the prior probability distribution with the functional form $\mathcal{A}(v)$.
	\item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with $K$ possible outcomes. That is $x_{i} | \theta \overset{\text{iid}}{\sim} Cat(\theta)$ and thus $\mathcal{L}(x_{i} \vert \theta)$ is the Categorical log likelihood.
	\item Let $\mathcal{D}$ denote all the prior data $X, \alpha$.
	\item Let $N = (N_{1}, \dots, N_{K}), N_{k} = \sum_{i=1}^{I} \mathbbm{1}(x_{i,k} = 1)$, denote the counts for each occurrence of a class $k$.
	\item The likelihood of the Categorical and Multinomial distributions is:

\begin{equation}
\begin{split}
	\mathcal{L}(\mathcal{D}) &=  P(\mathcal{D} | \theta) \\
	&\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}}
\end{split}
\end{equation}
\end{itemize}

\textbf{Then}:

\begin{itemize}
	\item  By Bayes Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given as:

\begin{equation}
\begin{split}
	P(\theta | \mathcal{D}) &= \frac{P(\mathcal{D} | \theta) P(\theta)}{P(\mathcal{D})}
\end{split}
\end{equation}

	\item Since the denominator sums to $1$, one could get rid of the denominator and constants for the Dirichlet prior, by expressing the posterior as proportional to:

\begin{equation}
\begin{split}
		P(\theta | \mathcal{D}) &\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}} \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} - 1}\\
		&\propto \prod_{k=1}^{K} \theta_{k}^{(N_{k} + \alpha_{k}) - 1} \\
		&\propto Dir(K, N + \alpha) 
\end{split}
\end{equation}

\item Yielding a posterior of the same form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N + \alpha$.

\end{itemize}

This shows that the Dirichlet distribution is the conjugate prior to the Categorical and Multinomial likelihood.

\section{Bayesian Statistics}
\label{sec:probability:bayesian_stats}

\subsection{Bayesian Inference}
\label{sec:probability:bayesian_stats:bayesian_inference}

\subsection{Bayesian Analysis}
\label{sec:probability:bayesian_stats:bayesian_analysis}

\section{Conclusion}
\label{sec:probability:conclusion}

### 2022-01-07 thesis/chapters/06-bayesian-hyper-heuristic.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\chapter{Bayesian Hyper-Heuristic}
\label{chap:bhh}

\begin{quote}
    \textit{
    The result is a ``posterior distribution'' which the agent may use as its new prior in the next step. - Pedro Domingos, The Master Algorithm: How the Quest for the Ultimate Learning Machine Will Remake Our World.
    }
\end{quote}
% \resizebox{\textwidth}{!}{
% Table generated by Excel2LaTeX from sheet 'results'
\begin{table}[htbp]
  \centering
  \caption{Add caption}
  \resizebox{\textwidth}{!}{
    % Table generated by Excel2LaTeX from sheet 'results'
    \begin{tabular}{rcccccccccc}
          & \multicolumn{10}{l}{\textbf{burn\_in}} \\
\cmidrule{2-11}          & \multicolumn{2}{l}{\textbf{0}} & \multicolumn{2}{l}{\textbf{5}} & \multicolumn{2}{l}{\textbf{10}} & \multicolumn{2}{l}{\textbf{15}} & \multicolumn{2}{l}{\textbf{20}} \\
\cmidrule{2-11}    \textbf{dataset} & \textbf{avg} & \textbf{std} & \textbf{avg} & \textbf{std} & \textbf{avg} & \textbf{std} & \textbf{avg} & \textbf{std} & \textbf{avg} & \textbf{std} \\
    \midrule
    abalone & 2.915 & 1.395 & \textbf{2.694} & 1.393 & 2.917 & 1.384 & 2.840 & 1.352 & 3.634 & 1.357 \\
    adult & 1.846 & 0.794 & 1.809 & 0.751 & 2.026 & 0.842 & \textbf{0.000} & 0.000 & \textbf{0.000} & 0.000 \\
    air\_quality & 2.910 & 1.441 & \textbf{2.682} & 1.427 & 2.770 & 1.344 & 3.372 & 1.314 & 3.267 & 1.412 \\
    car   & \textbf{2.362} & 1.231 & 2.588 & 1.425 & 3.298 & 1.392 & 3.380 & 1.271 & 3.372 & 1.401 \\
    fish\_toxicity & 3.063 & 1.459 & \textbf{2.794} & 1.402 & 2.820 & 1.513 & 3.102 & 1.346 & 3.220 & 1.295 \\
    forest\_fires & \textbf{2.816} & 1.330 & 2.849 & 1.383 & 2.865 & 1.409 & 3.377 & 1.398 & 3.092 & 1.471 \\
    housing & \textbf{2.690} & 1.384 & 2.952 & 1.318 & 2.997 & 1.442 & 3.058 & 1.344 & 3.303 & 1.510 \\
    iris  & 2.947 & 1.461 & 2.972 & 1.367 & 3.190 & 1.449 & \textbf{2.771} & 1.369 & 3.119 & 1.387 \\
    mushroom & \textbf{2.206} & 1.249 & 2.938 & 1.298 & 3.161 & 1.297 & 3.144 & 1.401 & 3.523 & 1.501 \\
    parkinsons & \textbf{2.280} & 1.282 & 2.889 & 1.247 & 2.706 & 1.314 & 3.397 & 1.417 & 3.728 & 1.330 \\
    student\_performance & \textbf{2.145} & 1.205 & 2.695 & 1.403 & 3.097 & 1.352 & 3.458 & 1.354 & 3.605 & 1.231 \\
    wine\_quality & 2.970 & 1.437 & 3.011 & 1.304 & \textbf{2.663} & 1.419 & 3.125 & 1.398 & 3.231 & 1.447 \\
    \midrule
    \textbf{overall} & \textbf{2.596} & 1.373 & 2.739 & 1.357 & 2.894 & 1.397 & 3.184 & 1.379 & 3.372 & 1.412 \\
    \end{tabular}%

    }
  \label{tab:addlabel}%
\end{table}%

The above quote was the inspiration for the development of a novel \ac{HH} that uses \index{Bayesian}\textit{Bayesian} probability concepts as a selection mechanism to drive the heuristic selection process. Thus far the reader was presented with all of the necessary background information on \acp{ANN} in Chapter \ref{chap:anns}, low-level \index{Heuristic}heuristics/\index{Optimiser}optimisers in Chapter \ref{chap:heuristics}, \acp{HH} in Chapter \ref{chap:hhs}  and lastly, \index{probability theory}probability theory in Chapter \ref{chap:probability}. These elements form the fundamental components that make up the proposed \Ac{BHH}. A detailed specification on the \Ac{BHH} can now be formulated. This chapter provides the detail around the theory, concept and implementation of the \Ac{BHH} and explains how it used to train \acp{ANN}.

The remainder of the chapter is structured as follows: Section \ref{sec:bhh:overview} provides an overview of the \Ac{BHH} optimiser. Section \ref{sec:bhh:architecture} presents the general architecture, \Ac{HH} framework and the various components that make up the \index{Optimiser}optimiser. Section \ref{sec:bhh:model} discusses the models that can be optimised using the \Ac{BHH}, specifically referring to its application to training \acp{FFNN}. Section \ref{sec:bhh:entity_pool} discusses in more detail the \index{Population}population and its \index{Entity}entities, with specific detail provided on entity (local) and population (global) state and memory. Section \ref{sec:bhh:heuristic_pool} discusses the collection of low-level \index{Heuristic}heuristics, referred to as the \index{Heuristic}Heuristic Pool and puts emphasis on the importance of a diverse set of low-level \index{Heuristic}heuristics. Section \ref{sec:bhh:performance_log} presents the performance log and discusses performance measurement in more detail. Section \ref{sec:bhh:selection_mechanism} presents the \index{Bayesian}\textit{Bayesian} probabilistic model that is used as a selection mechanism . Section \ref{sec:bhh:optimisation} presents the mechanisms by which the probabilistic model can be optimised. Section \ref{sec:bhh:hyper_parameters} summarises and discusses the associated \index{Hyper-Parameters}hyper-parameters and default values. Section \ref{sec:bhh:initialisation} presents the initialisation step in detail and Section \ref{sec:bhh:heuristic} presents the \index{Heuristic}heuristic/update step in detail. The pseudo-code algorithm is given in Section \ref{sec:bhh:algorithm} and the chapter is concluded in Section \ref{sec:bhh:conclusion}.

\section{Overview}
\label{sec:bhh:overview}

This section provides an overview of the workings of the \Ac{BHH}. To start the discussion, consider the following analogy:
\\

\textit{
    Bob is a teacher at a high school. Every year his students perform really well and he wins the prize for best teacher, evaluated by student performance. He is able to do this not just because he is a good teacher, but he understands that each student has a learning technique that works best for him/her. He exploits this concept by tailoring the teaching process to each students such that the result is an optimum mark for that student and by definition, the whole class. Bob knows that it is too timely to get to know each student, so he devises a model that does the allocations for him. This model uses a process of observation. With each evaluation opportunity he experiments by allocating different learning techniques to different students. He evaluates the student for the given opportunity and keeps a log of which learning technique he assigned to the student as well as the outcome. With each evaluation opportunity he updates his model by biasing the assignment process such that students generally get assigned learning techniques that yield the best performance for them.
}\\

The key take-out from the analogy above is the concept that Bob can maximise student performance by updating his beliefs, over time, about which learning technique to assign to which student. He does this by biasing selection/assignment towards the best combinations of student, learning technique
and evaluation opportunity. This is the basic nature of the \Ac{BHH}. The students are analogous to a population of entities. The learning techniques are analogous to heuristics/optimisers. Evaluation opportunities are analogous to time/steps/batches or even problems  and student performance is analogous to model optimisation and performance. Selecting the correct heuristic/optimiser for each entity at each optimisation step is the goal of the \Ac{BHH}. It is shown throughout this chapter that the \Ac{BHH} implements a probabilistic optimisation technique that biases a \index{Gaussian Process}\textit{Gaussian Process} (as described in Chapter \ref{chap:probability}) towards good optimisation and performance.

Formal classification of the \Ac{BHH} is needed. The authors propose classification of the \Ac{BHH} as a \textit{selective-perturbative population-based meta-\index{Hyper-Heuristic}hyper-heuristic}. The breakdown of this classification is argued as follows:

\begin{itemize}
    \item \textbf{Selective-Perturbative:} Following the classification as proposed by Burke et al. \cite{ref:burke:2010} - \textit{Selective}, meaning it has a \index{Heuristic}heuristic selection mechanism that selects from a collection of lower level \index{Heuristic}heuristics' (\index{Heuristic Pool}heuristic pool). \textit{Perturbative} - refers to its ability to combined and/or amended \index{Heuristic}heuristics update steps through a process called \textit{proxying} as will be describe later in this chapter.
    \item \textbf{Population-based:} Follows a population-based approach where a number of different \index{Candidate Solution}candidate solutions, referred to as \index{Entity}\textit{entities} work together to yield a global best solution. There is also the concept of a shared global state or memory.
    \item \textbf{Meta:} Incorporates classical, analytical and  gradient-based low level \index{Heuristic}heuristics (typically from the \ac{ML} research space) as well as meta-heuristics such as other population-based \index{Meta-Heuristic}meta-heuristics (typically from the \ac{CI} and \ac{EC} research spaces) .
    \item \textbf{Hyper-Heuristic:} Searches through the heuristic space while lower level heuristics search through the solution space.
\end{itemize}

More detailed consideration of these elements are required. The following sections break down the \Ac{BHH} into its various parts, starting with a discussion on its architecture next.

\index{Architecture}
\section{Architecture}
\label{sec:bhh:architecture}

This section aims to present the reader with all the high level components in the architecture of the \Ac{BHH}. Burke et al. \cite{ref:burke:2010} proposed an initial framework for \acp{HH} and Grobler \cite{ref:grobler:2015} further proposed a framework for a heterogeneous meta-\ac{HH}. These frameworks have been adapted for the implementation of the \Ac{BHH}. An illustration of the high-level architecture of the \Ac{BHH} is given in Figure \ref{fig:bhh_architecture} below.

\begin{figure}[H]
    \centering
    \includegraphics[width=1.0\textwidth]{bhh_architecture.png}
    \caption[The \index{Bayesian Hyper-Heuristics}Bayesian Hyper-Heuristic Architecture]{An illustration of
    the architecture and high level components of the \index{Bayesian Hyper-Heuristics}Bayesian Hyper-Heuristic.}
    \label{fig:bhh_architecture}
\end{figure}

At a high level, the architecture presented in Figure \ref{fig:bhh_architecture} above groups related elements by the following color groups:

\begin{itemize}
    \item \textbf{Purple:} Everything related to the problem domain and \index{Model}model to be optimised.
    \item \textbf{Gray:} Everything related to \index{Entity}entity (local) and shared \index{Population}population (global) state.
    \item \textbf{Red:} Everything related to \index{Entity}entities and the \index{Population}population. This also marks the components that relay information from the \index{Solution Space}\textit{solution} space.
    \item \textbf{Black:} This is the \index{Domain Barrier}domain barrier, similar to what is presented in Burke et al.'s \cite{ref:burke:2010} framework. It is a constraint on information flow, prohibiting high level components from interacting and relaying information related to the \index{Solution Space}\textit{solution} space.
    \item \textbf{Green:} Various components and strategies. These components form the main processing pipeline of the \Ac{BHH}.
    \item \textbf{Blue:} Operations performed by the \Ac{BHH}. These are complimentary operations to the processing pipeline.
    \item \textbf{Orange:} Everything related to low level \index{Heuristic}heuristics/\index{Optimiser}optimisers. This also marks the components that form part of the \index{Heuristic Space}\textit{heuristic} space.
\end{itemize}

The above grouping are not detailed enough to illustrate their role in the \Ac{BHH}. To ensure the proper clarity is given to each of these elements, a detailed discussion on each of these elements are presented next.

\index{Model}
\section{Model}
\label{sec:bhh:model}

The \index{Model}model refers to the target \index{Model}model to be optimised and is usually expressed as a complex mathematical function. For this thesis, the authors focused specifically on shallow \acp{FFNN} (only one hidden layer). Figure \ref{fig:shallow_ffnn} below presents such a shallow \acp{FFNN}.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\textwidth]{shallow_ffnn.png}
    \caption[Shallow \index{Feedforward Neural Network}Feedforward Neural Network]{An illustration of
    a shallow \index{Feedforward Neural Network}Feedforward Neural Network.}
    \label{fig:shallow_ffnn}
\end{figure}

In theory, this model could take up many different forms, however one has to consider uniformity and representation, as this has an effect on the \Ac{BHH}'s design decisions:

\begin{itemize}
    \item \textbf{Uniformity:} The \index{Model}model and low-level \index{Heuristic}heuristics in the heuristic pool must be compatible. If the model is a discrete function, then only \index{Heuristic}heuristics that are applicable to discrete optimisation problems can be included.
    \item \textbf{Representation:} The \index{Model}model parameters must be presented in a manner that is compatible with low-level \index{Heuristic}heuristics. For example: a flattened 2D tensor of the model's parameters is a good, uniformly consistent representation that all lower-level heuristics can assume.
\end{itemize}

Given these two concepts above, a model is encapsulated and represented by an element known as an \index{Entity}\textit{entity}. As mentioned, the \Ac{BHH} is a \index{Population}\textit{population}-based \Ac{HH}, meaning it contains a collection of these \index{Entity}entities. Consider now a more in-depth look at the \Ac{BHH}'s entity pool.

\index{Entity Pool}
\section{Entity Pool}
\label{sec:bhh:entity_pool}

The \index{Entity Pool}\textit{entity pool} refers to a collection of so-called individual \index{Entity}\textit{entities}. A common naming convention for such a collection is a \textit{population} of entities. These \index{Entity}entities are responsible for representing a \index{Candidate Solution}candidate solution to the \index{Model}model's trainable parameters (\index{Weights}weights). These \index{Entity}entities are often  treated as physical \index{Particle}\textit{particles} in a hyper-dimensional  physical environment. This means that these \index{Entity}entities often model concepts from physics. For example, the candidate solution is represented as the \index{Entity}entity's \textit{position}. Another connection to physics is that an \index{Entity}entity's velocity and acceleration, is analogous to the gradient and momentum of an \index{Entity}entity respectfully. This concept of modeling traits of an entity as physical concept is very useful. It is later shown in Section \ref{sec:bhh:heuristic:proxies} how these concepts allows one to combine different \index{Heuristic}heuristic step operations together through a process of \index{Proxy}\textit{``proxying''}.

There are a number of parameters involved that are related to the \index{Entity Pool}entity pool/\index{Population}population and the individual \index{Entity}entities. These parameters include hyper-parameters and \textit{state} parameters .The following sections briefly discuss these concepts next.

\index{Population Size}
\subsection{Population Size}
\label{sec:bhh:entity_pool:population_size}

\index{Population Size}\textit{Population size} refers to the number of \index{Entity}entities included in the \index{Entity Pool}entity pool/\index{Population}population and is thus a \index{Hyper-Parameter}hyper-parameter of the \Ac{BHH}. The exact \index{Population Size}population size to use is problem dependent (ref ???), however in general, the larger the population the better (ref ???), assuming that entities are initialised to be spread uniformly across the solution search space. The authors propose the following considerations when picking a \index{Population Size}population size:

\begin{itemize}
    \item When considering the lower bound of possible \index{Population Size}population sizes, take into account the highest, minimum \index{Population Size}population size required by all low-level \index{Heuristic}heuristics. For example, if one includes \Ac{DE} into the \index{Heuristic}heuristic pool, one needs a \index{Population Size}population size of at least 4.
    \item When considering the upper bound of possible \index{Population Size}population sizes, take into account that the bigger the \index{Population Size}population size, the more computationally expensive it is to execute the training process. Furthermore, there exists a point of \index{Diminishing Returns}\textit{diminishing returns} where an increase in \index{Population Size}population size does not yield any better outcome (ref ???). To extend on this, consider that the \Ac{BHH} is a \Ac{HH} that utilises a \index{Bayesian}Bayesian probabilistic approach in it's selection mechanism. This means that a larger observed sample size (of entity and heuristic selection events) is needed to statistically and reliably update the selection mechanism's trainable parameters.
\end{itemize}

Following the discussion of \index{Population Size}population size is a brief discussion on a collection of stateful parameters maintained by the population as a whole, as well as individual entities as presented in the following sections.

\index{Population State}
\subsection{Population State}
\label{sec:bhh:entity_pool:population_state}

The \index{Population State}\textit{population state} refers to a collection of stateful (persisted between iterations) parameters that are shared between the \index{Entity}entities in the population. Because the \index{Population State}population state is shared between \index{Entity}entities, this state is also referred to as \index{Global State}\textit{global} state or memory. The \index{Population State}population state contains the following stateful parameters:

\begin{itemize}
    \item \textbf{\textit{entities}}: The list of entities in the population. List size determined by \index{Population Size}population size.
    \item \textbf{\textit{ibest}} and \textbf{\textit{ibest\_loss}}: Refers to the best position and loss achieved by the population for the current iteration/step.
    \item \textbf{\textit{rbest}} and \textbf{\textit{rbest\_loss}}: Refers to the best position and loss achieved by the population for the current replay buffer/window size.
    \item \textbf{\textit{gbest}} and \textbf{\textit{gbest\_loss}}: Refers to the overall/global best position and loss achieved by the population for the entire training process.
\end{itemize}

It is clear from the discussion above that entities share this stateful information and are thus required to update this information as well. This is part of state update operations and will be discussed in more detailed later in Sections \ref{sec:bhh:heuristic} and \ref{sec:bhh:algorithm}. Consider now the stateful parameters as maintained by individual entities.

\index{Entity State}
\subsection{Entity State}
\label{sec:bhh:entity_pool:entity_state}

\index{Heuristic Pool}
\section{Heuristic Pool}
\label{sec:bhh:heuristic_pool}

Inititialisation
Step

\index{Exploration}
\index{Exploitation}
\subsection{Diversity: Exploration, Exploitation and Capability}
\label{sec:bhh:entity_pool:diversity}

\index{Performance Log}
\section{Performance Log}
\label{sec:bhh:performance_log}

\index{Performance Measurement}
\subsection{Performance Measurement}
\label{sec:bhh:performance_log:performance_measurement}

\index{Credit Assignment Strategy}
\subsection{Credit Assignment Strategy}
\label{sec:bhh:performance_log:credit_assignment_strategy}

\index{Pseudo Counts}
\subsection{Pseudo Counts}
\label{sec:bhh:performance_log:pseudo_counts}

\index{Normalisation}
\subsection{Normalisation}
\label{sec:bhh:credit_assignment_strategy:normalisation}

\index{Discounted Rewards}
\subsection{Discounted Rewards}
\label{sec:bhh:credit_assignment_strategy:discounted_rewards}

\index{Pruning}
\subsection{Pruning}
\label{sec:bhh:performance_log:pruning}

\index{Selection Mechanism}
\section{Selection Mechanism}
\label{sec:bhh:selection_mechanism}

\textbf{Setup}:

\begin{itemize}
    \item $I$
    \item $J$
    \item $K$
    \item $L$

    \item $\alpha = (\alpha_{1}, \dots, \alpha_{K})$
    \item $\beta = (\beta_{1,1}, \dots, \beta_{J, K})$
    \item $\gamma = (\gamma_{1,1}, \dots, \gamma_{L, K})$

    \item $\theta \vert \alpha \sim Dir(\theta; K, \alpha)$
    \item $\phi \vert \beta \sim Dir(\phi; K, \beta)^{J}$
    \item $\psi \vert \gamma  \sim Beta(\psi; \gamma_{1}, \gamma_{2})$

    \item $H \vert \theta \sim Mult(I, H; \theta)$
    \item $E_{j} \vert \phi \sim Mult(I, H; \phi)^{J}$
    \item $C \vert \psi \sim Bin(I, \psi)$
\end{itemize}

\index{Random Events}
\subsubsection{Random Events}
\label{sec:bhh:selection_mechanism:random_events}

\index{Independence}
\subsubsection{Independence}
\label{sec:bhh:selection_mechanism:independence}

\index{Bayes' Theorem}
\subsubsection{Bayes' Theorem}
\label{sec:bhh:selection_mechanism:bayes_theorem}

The predictive model by Bayes rule:

\begin{equation}
    \begin{split}
        P(H \vert E, C;  \theta, \phi, \psi)
        &= \frac{
            P(E, C \vert H;  \phi, \psi)  P(H \vert \theta)
            }{
            P(E, C | \theta, \phi, \psi)
        } \\		
        &= \frac{
            P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
            }{
            P(E | \theta, \psi) P(C | \theta, \phi)
        } \\
        &= \frac{
            P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
            }{
            \left[ \sum_{k}^{K} P(E, H=k | \theta, \psi) \right] \left[ \sum_{k}^{K}  P(C, H=k | \theta, \phi) \right]
        } \\
        &= \frac{
            P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
            }{
            \left[ \sum_{k}^{K} P(E | H=k | \phi) P(H=k \vert \theta) \right] \left[ \sum_{k}^{K} P(C | H=k | \psi) P(H=k \vert \theta) \right]
        }
    \end{split}
\end{equation}

One should start to notice the joint probability over events $E$ and $C$ given the selection of a heuristic $H$ denoted by the sums of the products of the separate parts, for $E$ and $C$, in the denominator.

In order to derive the posterior distribution as given in Equestion (ref?? above), one only has to evaluate to proportionality as follows:

\begin{equation}
    \begin{split}
        P(H \vert E, C;  \theta, \phi, \psi) &\propto P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
    \end{split}
\end{equation}

\index{Naïve Bayes}
\subsubsection{Naïve Bayes}
\label{sec:bhh:selection_mechanism:naive_bayes}

One very big assumption that is made by the Naïve Bayes Classifier is that it
assumes that all features are conditionally independent given the class label
(ref ??). \\
The independence between events for the class label $H$ simply yields the PMF of the Multinomial distribution as follows:

\begin{equation}
    \begin{split}
        P(H \vert \theta)
        &\propto \prod_{i=1}^{I} \prod_{k=1}^{K} P(h_{i,k} \vert \theta_{k}) \\
        &\propto \prod_{i=1}^{I} \prod_{k=1}^{K} \theta_{k}^{\mathbbm{1}_{1}(h_{i,k})} \\
        &\propto \prod_{k=1}^{K} \theta_{k}^{\sum_{i=1}^{I} \mathbbm{1}_{1}(h_{i,k})} \\
        &\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}}
    \end{split}
\end{equation}

where $N_{k}$ is a summary variable such that $N_{k} = \sum_{i=i}^{I}
\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the event
$h_{i}$ taking on class $k$, i.e. the count of occurrences of heuristic $k$ in
$I$ independent, identical runs.\\ The independence between events for the
entities feature $E$ given class label $H$ is denoted by the likelihood of $E$
conditional to the occurrence of heuristic $k$ and model parameter $\phi$ as
follows:

\begin{equation}
    \begin{split}
        P(E \vert H;  \phi)
        &\propto \prod_{i=1}^{I} \prod_{j=1}^{J} \prod_{k=1}^{K} P(e_{i,j,k} \vert h_{i,k} ; \phi_{j,k})  \\
        &\propto \prod_{i=1}^{I} \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{\mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})} \\
        &\propto \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{ \sum_{i}^{I} \left[ \mathbbm{1}_{1}(e_{i,j,k}) \mathbbm{1}_{1}(h_{i,k}) \right]} \\
        &\propto \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}}
    \end{split}
\end{equation}

where $N_{j,k}$ is a summary variable such that $N_{j,k} = \sum_{i=i}^{I}
\mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of
occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on
class $k$, i.e. the count of occurrences of both entity entity $e$ and heuristic
$k$ occurring together in $I$ independent, identical runs.\\ Finally, the
independence between events for the performance criteria feature $C$ given class
label $H$ is denoted by the likelihood of $C$ conditional to the occurrence of
heuristic $k$ and model parameter $\psi$ as follows:

\begin{equation}
    \begin{split}
        P(C\vert H;  \psi)
        &\propto\prod_{i=1}^{I} \prod_{k=1}^{K} P(c_{i,k} \vert h_{i,k} ; \psi_{k})  \\
        &\propto \prod_{i=1}^{I} \prod_{k=1}^{K} \psi_{k}^{\mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})} (1 - \psi_{k})^{\mathbbm{1}_{0}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})}\\
        &\propto \prod_{k=1}^{K} \psi_{k}^{\sum_{i=1}^{I} \mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})} (1 - \psi_{k})^{\sum_{i=1}^{I} \mathbbm{1}_{0}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})}\\
        &\propto \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{N_{0,k}} \\
        &\propto \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})}
    \end{split}
\end{equation}

where $N_{k}$ is the summary variable as described for Equation (ref ??) above.
$N_{1,k}$ is a summary variable such that $N_{1,k} = \sum_{i=1}^{I}
\mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of
occurrences of the events $c_{i}$ taking on a success $(c_{i}=1)$ and $h_{i}$
taking on class $k$, i.e. the count of occurrences of both succeeding in the
performance criteria and heuristic $k$ occurring together in $I$ independent,
identical runs. Similarly $N_{0,k} = N_{k} - N_{1,k}$ would denote the count of
occurrences of the events $c_{i}$ taking on a failure $(c_{i}=0)$ and $h_{i}$
taking on class $k$. \\
By the assumptions made by the Naïve Bayes Classifier, one could supplement
Equations (ref ??, ??, ??) above into the proportional evaluation of the
predictive model as given in Equation (ref ??) as follows:

\begin{equation}
    \begin{split}
        P(H \vert E, C;  \theta, \phi, \psi)
    &\propto P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)  \\
    &\propto \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right]
    \end{split}
\end{equation}

\index{Numerical Stability}
\subsubsection{Numerical Stability}
\label{sec:bhh:selection_mechanism:numerical_stability}

\index{Mode Collapse}
\subsubsection{Mode Collapse}
\label{sec:bhh:selection_mechanism:mode_collapse}

\index{Burn In}
\subsubsection{Burn In}
\label{sec:bhh:selection_mechanism:burn_in}

\index{Replay}
\subsubsection{Replay}
\label{sec:bhh:selection_mechanism:replay}

\index{Reanalysis}
\subsubsection{Reanalysis}
\label{sec:bhh:selection_mechanism:reanalysis}

\index{Reselection}
\subsubsection{Reselection}
\label{sec:bhh:selection_mechanism:reselection}

\index{Optimisation}
\section{Optimisation}
\label{sec:bhh:optimisation}

Online learning...

\index{Performance Bias}
\subsection{Performance Bias}
\label{sec:bhh:optimisation:performance_bias}

\index{A Priori Bias}
\subsection{A Priori Bias}
\label{sec:bhh:optimisation:a_priori_bias}

\index{Maximum Likelihood Estimation}
\subsection{Maximum Likelihood Estimation}
\label{sec:bhh:optimisation:mle}

By calculating the Maximum Likelihood Estimate (MLE) of $\theta$, $\phi$ and $\psi$ it can be shown that:

\begin{itemize}
    \item $\hat{\theta}_{k} = E[\theta_{k}] = \frac{N_{k}}{N}$
    \item $\hat{\phi}_{j,k} = E[\phi_{j,k}] = \frac{N_{j,k}}{N_{j}}$
    \item $\hat{\psi}_{k} = E[\psi_{k}] = \frac{N_{1,k}}{N_{k}}$
\end{itemize}

The calculations of the MLE for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and
$\hat{\psi}_{k}$ is now presented.\\
The log likelihood of $\hat{\theta}$, $\hat{\phi}$ and $\hat{\psi}$ as derived
from the Equations (ref ??????) above is given as:

\begin{equation}
    \begin{split}
        & \mathcal{L}(\theta, \phi, \psi) \\
        &= \ln\left(\left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right] \right) \\
        &= \ln \left( \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right) +  \ln \left( \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right) + \ln \left( \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right) \\		
        &= \left( \sum_{j=1}^{J} \sum_{k=1}^{K} N_{j,k} \ ln \left( \phi_{j,k}
        \right) \right) \\
        &+ \left( \sum_{k=1}^{K} N_{1,k} \ln \left( \psi_{k} \right) + \left( N_{k} - N_{1,k} \right) \ln \left( 1 - \psi_{k} \right) \right) + \left( \sum_{k=1}^{K} N_{k} \ln \left( \theta_{k} \right) \right)
    \end{split}
\end{equation}

Consider the log likelihood of $\psi$  as denoted by:

\begin{equation}
    \begin{split}
        \mathcal{L}(\psi) &=  \sum_{k=1}^{K} N_{1,k} \ln \left( \psi_{k} \right) + \left( N_{k} - N_{1,k} \right) \ln \left( 1 - \psi_{k} \right)
    \end{split}
\end{equation}

The MLE for $\hat{\psi_{k}} $ can be calculated by taking the derivative of Equation (ref ?? above) with respect to $\psi_{k}$ and equating to zero as follows:

\begin{equation}
    \begin{split}
        \frac{\partial \mathcal{L}(\psi)}{\partial \psi_{k}} &= N_{1,k} \frac{1}{ \psi_{k}} + \left( N_{k} - N_{1,k} \right) \frac{-1}{ \left( 1 - \psi_{k} \right) } \\
        0 &=  \frac{ N_{1,k} \left( 1 - \psi_{k} \right) +  \left( N_{1,k} - N_{k} \right) \psi_{k}}{ \psi_{k} \left( 1 - \psi_{k} \right) } \\
        0 &=  N_{1,k} \left( 1 - \psi_{k} \right) +  \left( N_{1,k} - N_{k} \right) \psi_{k} \\
        0 &=  N_{1,k} - N_{1,k} \psi_{k}  +  N_{1,k} \psi_{k} - N_{k}\psi_{k} \\
        0 &=  N_{1,k} - N_{k}\psi_{k} \\
        N_{k}\psi_{k} &=  N_{1,k} \\
        \hat{\psi}_{k} &=  \frac{N_{1,k}}{N_{k}} \\
    \end{split}
\end{equation}

The value for $\hat{\theta_{k}} $ can be calculated similarly. However, one has to compensate for the $K-1$ Simplex $S$ by adding error factor $\epsilon$ to correct values for  $\theta$ where $\sum_{k}^{K} \theta_{k} \neq 1$. The new log likelihood function is then:

\begin{equation}
    \begin{split}
        \mathcal{L}(\theta, \epsilon)
        &=  \left( \sum_{k=1}^{K} N_{k} \ln \left( \theta_{k} \right) \right) + \epsilon \left( 1 - \sum_{k=1}^{K} \theta_{k} \right) \\
        &=  \left( \sum_{k=1}^{K} N_{k} \ln \left( \theta_{k} \right) \right) + \left( \epsilon -  \epsilon \sum_{k=1}^{K} \theta_{k} \right)
    \end{split}
\end{equation}

Solving first for $\epsilon$:

\begin{equation}
    \begin{split}
        \frac{\partial \mathcal{L}(\theta, \epsilon)}{\partial \epsilon} &= 1 - \sum_{k=1}^{K} \theta_{k}  \\
        \sum_{k=1}^{K} \theta_{k}  &= 1
    \end{split}
\end{equation}

then for $\theta_{k}$:

\begin{equation}
    \begin{split}
        \frac{\partial \mathcal{L}(\theta, \epsilon)}{\partial \theta_{k}} &=  N_{k} \frac{1}{\theta_{k}}  + \epsilon(-1) \\
        \frac{N_{k}}{\theta_{k}} &= \epsilon \\
        N_{k} &= \theta_{k} \epsilon \\
        \sum_{k=1}^{K} N_{k} &= \sum_{k=1}^{K} \theta_{k} \epsilon \\
        N &= \epsilon \sum_{k=1}^{K} \theta_{k} \\
        N &= \epsilon
    \end{split}
\end{equation}

Substituting back into the Equation yields:

\begin{equation}
    \begin{split}
        N_{k} &= \theta_{k} \epsilon \\
        N_{k} &= \theta_{k} N \\
        \hat{\theta}_{k} &= \frac{N_{k}}{N}\\
    \end{split}
\end{equation}

The value for $\hat{\phi}_{j, k} $ is calculated very similarly. To compensate for the $K-1$ Simplex $S$ an error factor $\lambda = (\lambda_{1}, \dots, \lambda_{J})$ is added. This follows:

\begin{equation}
    \begin{split}
        \mathcal{L}(\phi, \lambda) 
        &=  \left( \sum_{j=1}^{J} \sum_{k=1}^{K} N_{j,k} \ ln \left( \phi_{j,k} \right) \right) + \sum_{j=1}^{J} \lambda_{j} \left( 1 - \sum_{k=1}^{K} \phi_{j,k} \right) \\
        &=  \left( \sum_{j=1}^{J} \sum_{k=1}^{K} N_{j,k} \ ln \left( \phi_{j,k} \right) \right) + \sum_{j=1}^{J} \lambda_{j} - \sum_{j=1}^{J} \lambda_{j} \sum_{k=1}^{K} \phi_{j,k} \\
    \end{split}
\end{equation}

Solving first for $\lambda_{j}$:

\begin{equation}
    \begin{split}
        \frac{\partial \mathcal{L}(\phi, \lambda)}{\partial \lambda_{j}} &= 1 - \sum_{k=1}^{K} \phi_{j,k}  \\
        \sum_{k=1}^{K} \phi_{j,k}  &= 1
    \end{split}
\end{equation}

then for $\phi_{j,k}$:

\begin{equation}
    \begin{split}
        \frac{\partial \mathcal{L}(\phi, \lambda)}{\partial \phi_{j,k}} &= N_{j,k} \frac{1}{\phi_{j,k}}  - \lambda_{j} \\
        \frac{N_{j,k}}{\phi_{jk}} &= \lambda_{j} \\
        N_{j,k} &= \phi_{j,k} \lambda_{j} \\
        \sum_{k=1}^{K} N_{j,k} &= \sum_{k=1}^{K} \phi_{j,k} \lambda_{j} \\
        N_{j} &= \lambda_{j} \sum_{k=1}^{K} \phi_{j,k} \\
        N_{j} &= \lambda_{j}
    \end{split}
\end{equation}

Substituting back into the Equation yields:

\begin{equation}
    \begin{split}
        N_{j,k} &= \phi_{j,k} \lambda_{j} \\
        N_{j,k} &= \phi_{j,k} N_{j} \\
        \hat{\phi}_{j,k} &= \frac{N_{j,k}}{N_{j}}\\
    \end{split}
\end{equation}

\index{Maximum a Posteriori Estimation}
\subsection{Maximum a Posteriori Estimation}
\label{sec:bhh:optimisation:map}

I.e. Bayesian Analysis

Another approach to optimising the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ is to optimise the parameters to their probability distributions. This process is referred to as Bayesian Analysis. This process is of particular importance to this paper as it is used to sample the probabilities of heuristic selection in the selection mechanism to the Bayesian Hyper Heuristic. The detail of this application is described in Chapter (ref??? this chapter).

Bayesian Analysis makes use of the posterior probability distribution. The posterior distribution is simply expressed as:

\begin{equation*}
    \begin{split}
        POSTERIOR \propto LIKELIHOOD \times PRIOR
    \end{split}
\end{equation*}

The likelihood is presented in Equation (ref ???) above. The event $H$ is a multinomial distribution with parameter $\theta$ and from Chapter (ref ?? maybe this chapter) it is known that the prior to a multinomial distribution is a Dirichlet distribution. The prior for $\hat{\theta}_{k}$ is thus presented in Equation (ref??) below:

\begin{equation}
    \begin{split}
        P(\theta | \alpha)
&\propto \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} -1}
    \end{split}
\end{equation}

Furthermore, the event $E$ is also multinomial distribution with parameter $\phi$. The prior for $\hat{\phi}_{j,k}$ is thus presented in Equation (ref??) below:

\begin{equation}
    \begin{split}
        P(\phi | \beta)
&\propto \prod_{j=1}^{J}  \prod_{k=1}^{K} \phi_{j,k}^{\beta_{j,k} -1}
    \end{split}
\end{equation}

Finally,  the event $C$ is a binomial distribution with parameter $\psi$ and from Chapter (ref ?? maybe this chapter) it is known that the prior to a binomial distribution is a Beta distribution. The prior for $\hat{\psi}_{k}$ is thus presented in Equation (ref??) below:

\begin{equation}
    \begin{split}
        P(\psi | \gamma_{1}, \gamma_{2})
&\propto \prod_{k=1}^{K} \psi_{k}^{\gamma_{1,k}} (1- \psi_{k})^{\gamma_{2,k}}
    \end{split}
\end{equation}

Putting the likelihood and priors together yields the posterior distribution as given in Equation (ref ??) below:

\begin{equation}
    \begin{split}
& P(\theta, \phi, \psi \vert H, E, C;  \alpha, \beta, \gamma_{1}, \gamma_{2}) \\
&\propto P(H \vert E, C; \theta, \phi, \psi)P(\theta, \phi, \psi \vert \alpha, \beta, \gamma_{1}, \gamma_{2}) \\
&\propto P(E \vert H; \phi) P(C \vert H; \psi) P(H \vert \theta) P(\phi \vert \beta) P(\psi \vert \gamma_{1}, \gamma_{2}) P(\theta \vert \alpha)  \\
&\propto \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right] \\
&\times \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{\beta_{j,k} - 1} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{\gamma_{1,k} - 1} (1 - \psi_{k})^{\gamma_{2,k} - 1} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} - 1} \right] \\
&\propto \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{(N_{j,k} + \beta_{j,k}) - 1} \right] \\
&\times \left[ \prod_{k=1}^{K} \psi_{k}^{(N_{1,k} + \gamma_{1,k}) - 1} (1 - \psi_{k})^{(N_{0,k} + \gamma_{2,k} )- 1} \right] \\
&\times \left[ \prod_{k=1}^{K} \theta_{k}^{(N_{k} + \alpha_{k}) - 1} \right]
    \end{split}
\end{equation}

From Equation (Ref ??) above, it can be seen that the posterior distribution has the same form as the prior distribution. Meaning that the parameters to the priors can by updated to:

\begin{itemize}
    \item $\alpha_{k}(t+1) = N_{k} + \alpha_{k}(t)$
    \item $\beta_{j,k}(t+1) = N_{j,k} + \beta_{j,k}(t)$
    \item $\gamma_{1,k}(t+1) = N_{1,k} + \gamma_{1,k}(t)$
    \item $\gamma_{2,k}(t+1) = N_{0,k} + \gamma_{2,k}(t)$
\end{itemize}

\index{Hyper-Parameters}
\section{Hyper-Parameters}
\label{sec:bhh:hyper_parameters}

\subsection{Defaults}
\label{sec:bhh:hyper_parameters:defaults}

\index{Initialisation}
\section{Initialisation}
\label{sec:bhh:initialisation}

\index{Heuristic}
\section{Heuristic}
\label{sec:bhh:heuristic}

\index{Proxies}
\subsection{Proxies}
\label{sec:bhh:heuristic:proxies}

\index{Momentum}
\subsection{Momentum}
\label{sec:bhh:heuristic:momentum}

\index{Algorithm}
\section{Algorithm}
\label{sec:bhh:algorithm}

% Algorithm2e comment style
\SetKwComment{Comment}{/* }{ */}
\RestyleAlgo{ruled}
\begin{algorithm}[H]
\caption{The \index{Bayesian Hyper-Heuristic} Bayesian Hyper-Heuristic Optimiser
}
\label{algo:bhh}

\KwData{$n \geq 0$}
\KwResult{$y = x^n$}

$y \gets 1$\;
$X \gets x$\;
$N \gets n$\;

\While{$N \neq 0$}{
  \eIf{$N$ is even}{
    $X \gets X \times X$\;
    $N \gets \frac{N}{2}$ \Comment*[r]{This is a comment}
  }{\If{$N$ is odd}{
      $y \gets y \times X$\;
      $N \gets N - 1$\;
    }
  }
}
\end{algorithm}

\index{Conclusion}
\section{Conclusion}
\label{sec:bhh:conclusion}

### 2022-01-07 thesis/latex/packages.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\usepackage{acro}                   % American Mathematical Society environments}
\usepackage{amsmath}                % American Mathematical Society environments}
\usepackage{amssymb}                % American Mathematical Society Symbols
\usepackage{amsthm}                 % American Mathematical Society Theorems
% \usepackage{algorithm}            % Typeset algorithm captions
\usepackage{booktabs}
\usepackage[ruled,vlined,linesnumbered,noresetcount]{algorithm2e}
\usepackage{bbm}                    % Blackboard variants of Computer Modern Fonts
\usepackage[sorting=none]{biblatex} % BibLaTeX referencing
\usepackage{caption}                % Improved customisation of captions
\usepackage{colortbl}               % Adds colors to tables
\usepackage{datetime}               % Various date operations
\usepackage{fancyhdr}               % Add fancy headers and footers
\usepackage{float}                  % Improved interface for adding floating objects
\usepackage[T1]{fontenc}            % Allows user to select font encodings
\usepackage[bottom]{footmisc}
\usepackage[
a4paper,                            % Paper size
width=150mm,                        % Paper width
top=25mm,                           % Top margin
bottom=25mm,                        % Bottom margin
bindingoffset=6mm,                  % Binding margin
showframe                           % Adds frame to see hbox and vbox
]{geometry}                         % Easy and flexible user interface to customize page layout,
\usepackage[pdftex]{graphicx}                   
\usepackage{ifpdf}                  % Selective setup for PDF compilation
\usepackage[utf8]{inputenc}         % Set the input encoding to UTF-8
\usepackage{imakeidx}               % A general purpose hierarchical index generator
\usepackage{listings}               % Typeset sourcecode listings
\usepackage{lmodern}
\usepackage[final]{microtype}
\usepackage{pgfplots}               % Plot functions
\usepackage{relsize}
\usepackage{subcaption}             % Adds support for sub-figures and sub-captions
\usepackage{texnames}               % BIBTeX, SliTeX, AMSTeX, PiCTeX and TeXsis logos
\usepackage{todonotes}              % Add todo notes functionality
\usepackage{url}                    % URL typesetting
\usepackage{verbatim}               % Multi-line Comments

% Dependency reliant
\usepackage[
bookmarks=true,                         % (option) Build bookmarks
bookmarksnumbered=true                  % (option) Add section numbers to bookmarks
]{hyperref}
\usepackage[all]{hypcap}                % Correct PDF figure links to top of image
\usepackage[ocgcolorlinks]{ocgx2}       % Allows you to create OCGs (Optional Content Groups)

### 2022-01-07 thesis/preamble/abstract.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\pagestyle{empty}

\begin{center}
    \Large
    \textbf{Training Feedforward Neural Networks with Bayesian Hyper-Heuristics}
    \vspace{0.5cm}

    \normalsize
    by
    \vspace{0.5cm}

    \normalsize
    A.N. Schreuder\\
    \ifpdf
        E-mail: \href{mailto:arne@schreuder.ai}{arne@schreuder.ai}
    \else
        E-mail: arne@schreuder.ai
    \fi
    \vspace{1cm}

    \Large
    \textbf{Abstract}
\end{center}

Many different heuristics have been developed and used to train feedforward
neural networks (FFNNs).  However, selection of the best heuristic to train
FFNNs is a time consuming and non-trivial exercise. Careful, systematic
selection is thus required to select the best heuristic. In the past, selection
was done by trial and error. A modern approach is to automate this selection
proses. However, a single approach might not be sufficient. Research has
proposed the use of hybridisation of heuristics. These methods are referred to
as hyper-heuristics (HH) and focus on finding the best heuristic in
heuristic-space by making use of heuristic performance information. One such
form of HH is a population-based approach that guides the search process by
automatically selecting heuristics from a heuristic-pool to be applied to
different entities that represent candidate solutions to the problem-space and
work together to find good solutions. This thesis introduces a novel Bayesian
hyper-heuristic (BHH) to train FFNNs.  Bayesian analysis is used to guide the
selection of lower-level heuristics by updating prior selection probability
distributions with performance biased posteriors. An empirical study is done by
using the BHH to train FFNNs. The performance of the BHH is compared to that of
\todo[inline]{get final number}eight classic heuristics with different search
behaviours.  The emperical test was executed on \todo[inline]{get final
number}ten datasets consisting out of classification and regression problems
with varying characteristics. The BHH is shown to be able to train FFNNs and
provide an automated method for finding the best heuristic to train the
\ac{FFNN}.\\*[1cm]
\noindent
\parbox{\textwidth}{
    \textbf{Keywords:} hyper-heuristics, meta-learning, feedforward neural
    networks, supervised learning, optimisation.
}
\vfill
\newpage

### 2022-01-07 thesis/preamble/acknowledgements.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\pagestyle{empty}
\begin{center}
    \Large
    \textbf{Acknowledgements}
\end{center}

\begin{quotation}
    \noindent
    ``I've made the most important discovery of my life. It's only in
    the mysterious equation of love that any logical reasons can be found. I'm
    only here tonight because of you. You are the only reason I am \ldots you are
    all my reasons.''
\end{quotation}
\begin{flushright}
    Prof. J.F. Nash, Jr.
\end{flushright}

\vspace{0.3cm}
\noindent
I would like to thank the following people, without whom this work would never
have been possible:

\begin{itemize}
    \item
    To my wife, Taylah. Thank you for always believing in me. You are all my
    reasons.

    \item
        To my daughter, Bean\'e. Thank you for giving life meaning.

    \item
        To my son, Aden. I can't wait to meet you!

    \item
        To my parents, Adr\'e and Engela. Thank you for making this possible.

    \item
    To my sister, Jeannie. Thank you for motivating me.

    \item
    To my supervisors, Dr.~A. Bosman, Dr.~C.W. Cleghorn and Prof.~A.P. Engelbrecht. Thank you
    for leading me.

    \item
    To my creator, God. Thank You \ldots for Everything!
\end{itemize}

\vspace{\fill}

\begin{center}
    This project was made possible by the National Research Foundation (NRF).\\
    Thank you for the opportunity.
\end{center}

\vspace{\fill}

\begin{center}
    Finally, this project would not have been possible if it were not for the generous hours and hours of computational time I was given on the Center for High Performance Computing (CHPC) Cluster at the Council for Scientific and Industrial Research (CSIR).
\end{center}

\newpage

### 2022-01-07 thesis/preamble/publication.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\pagestyle{empty}
\vspace*{\fill}
\small

% Publication reference
\noindent
\textsf{Publication:}\\*[2.5mm]
\textsf{
    \fontsize{9}{10pt}
    \selectfont
    \textit{
        A.N. Schreuder. Training Feedforward Neural Networks with Bayesian
        Hyper-Heuristics. Master's Thesis. University of Pretoria,
        Department of Computer Science, Pretoria, South Africa.
        \monthyeardate\today
    }
}
\vspace{1cm}

% Online assets
\noindent
\textsf{Electronic, hyperlinked versions of this thesis, including
data and source code are available online at:}\\*[2.5mm]
\textsf{
    \fontsize{9}{10pt}
    \selectfont
    \url{https://github.com/arneschreuder/masters}
}
\newpage

### 2022-01-07 thesis/preamble/quote.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\pagestyle{empty}
\vspace*{\fill}
\begin{quotation}
    \noindent ``Men go abroad to wonder at the heights of mountains, at the huge
    waves of the sea, at the long courses of the rivers, at the vast compass of
    the ocean, at the circular motions of the stars and they pass by themselves
    without wondering.''
\end{quotation}
\begin{flushright}
    St. Augustine
\end{flushright}
\vspace{1cm}

\begin{quotation}
\noindent
    ``The measure of intelligence is the ability to change.''
\end{quotation}
\begin{flushright}
    Albert Einstein
\end{flushright}
\vspace*{\fill}
\newpage

### 2022-01-07 thesis/preamble/supervisors.tex
Adding thesis
Signed-off-by: Arné Schreuder <arneschreuder@icloud.com>

\pagestyle{empty}
\vspace*{\fill}
\noindent
\parbox{4cm}{\textbf{Supervisor:}} Dr. A. Bosman \\*[2mm]
\parbox{4cm}{\textbf{~}} University of the Pretoria \\*[2mm]
\parbox{4cm}{\textbf{~}} Department of Computer Science\\*[1cm]
\parbox{4cm}{\textbf{Co-Supervisor:}} Dr. C.W. Cleghorn \\*[2mm]
\parbox{4cm}{\textbf{~}} University of the Witwatersrand\\*[2mm]
\parbox{4cm}{\textbf{~}} Department of Computer Science\\*[1cm]
\parbox{4cm}{\textbf{Co-Supervisor:}} Prof. A.P. Engelbrecht \\*[2mm]
\parbox{4cm}{\textbf{~}} University of Stellenbosch\\*[2mm]
\parbox{4cm}{\textbf{~}} Department of Industrial Engineering\\*[1cm]
\parbox{4cm}{\textbf{Degree:}} Master of Science, Computer Science (Artificial
Intelligence)
\newpage

### 2022-01-07 experiments/scripts/bhh_discounted_rewards.sh

@@ -1,3 +1,0 @@
-export TF_CPP_MIN_LOG_LEVEL=3
-export CUDA_VISIBLE_DEVICES=''
-export LOG_LEVEL=0

### 2022-01-07 experiments/scripts/bhh_heuristic_pool.sh

@@ -2,244 +2,6 @@ export TF_CPP_MIN_LOG_LEVEL=3
 export CUDA_VISIBLE_DEVICES=''
 export LOG_LEVEL=0
 
-python bhh.py --dataset=bank --seed=30 --heuristic-pool=gd --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_heuristic_pool,bank,gd,30' >>tracking/progress/bhh_heuristic_pool.txt
-python bhh.py --dataset=bank --seed=1 --heuristic-pool=mh --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_heuristic_pool,bank,mh,1' >>tracking/progress/bhh_heuristic_pool.txt
-python bhh.py --dataset=bank --seed=2 --heuristic-pool=mh --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_heuristic_pool,bank,mh,2' >>tracking/progress/bhh_heuristic_pool.txt
-python bhh.py --dataset=bank --seed=3 --heuristic-pool=mh --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_heuristic_pool,bank,mh,3' >>tracking/progress/bhh_heuristic_pool.txt
-python bhh.py --dataset=bank --seed=4 --heuristic-pool=mh --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_heuristic_pool,bank,mh,4' >>tracking/progress/bhh_heuristic_pool.txt
-python bhh.py --dataset=bank --seed=5 --heuristic-pool=mh --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_heuristic_pool,bank,mh,5' >>tracking/progress/bhh_heuristic_pool.txt
-python bhh.py --dataset=bank --seed=6 --heuristic-pool=mh --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_heuristic_pool,bank,mh,6' >>tracking/progress/bhh_heuristic_pool.txt
[…]

### 2022-01-07 experiments/scripts/bhh_population2.sh

@@ -2,104 +2,6 @@ export TF_CPP_MIN_LOG_LEVEL=3
 export CUDA_VISIBLE_DEVICES=''
 export LOG_LEVEL=0
 
-python bhh.py --dataset=air_quality --seed=28 --heuristic-pool=all --population-size=25 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,air_quality,25,28' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=air_quality --seed=29 --heuristic-pool=all --population-size=25 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,air_quality,25,29' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=air_quality --seed=30 --heuristic-pool=all --population-size=25 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,air_quality,25,30' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=adult --seed=1 --heuristic-pool=all --population-size=10 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,adult,10,1' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=adult --seed=2 --heuristic-pool=all --population-size=10 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,adult,10,2' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=adult --seed=3 --heuristic-pool=all --population-size=10 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,adult,10,3' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=adult --seed=4 --heuristic-pool=all --population-size=10 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,adult,10,4' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=adult --seed=5 --heuristic-pool=all --population-size=10 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,adult,10,5' >>tracking/progress/bhh_population.txt
[…]

### 2022-01-07 experiments/scripts/bhh_population3.sh

@@ -2,86 +2,6 @@ export TF_CPP_MIN_LOG_LEVEL=3
 export CUDA_VISIBLE_DEVICES=''
 export LOG_LEVEL=0
 
-python bhh.py --dataset=bike --seed=24 --heuristic-pool=all --population-size=25 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,bike,25,24' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=bike --seed=25 --heuristic-pool=all --population-size=25 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,bike,25,25' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=bike --seed=26 --heuristic-pool=all --population-size=25 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,bike,25,26' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=bike --seed=27 --heuristic-pool=all --population-size=25 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,bike,25,27' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=bike --seed=28 --heuristic-pool=all --population-size=25 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,bike,25,28' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=bike --seed=29 --heuristic-pool=all --population-size=25 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,bike,25,29' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=bike --seed=30 --heuristic-pool=all --population-size=25 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,bike,25,30' >>tracking/progress/bhh_population.txt
-python bhh.py --dataset=bank --seed=1 --heuristic-pool=all --population-size=10 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
-echo 'bhh_population,bank,10,1' >>tracking/progress/bhh_population.txt
[…]

### 2022-01-07 experiments/scripts/bhh_reanalysis.sh

@@ -2,360 +2,6 @@ export TF_CPP_MIN_LOG_LEVEL=3
 export CUDA_VISIBLE_DEVICES=''
 export LOG_LEVEL=0
 
-python bhh.py --dataset=adult --seed=12 --heuristic-pool=all --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=15 --credit=ibest
-echo 'bhh_reanalysis,adult,15,12' >>tracking/progress/bhh_reanalysis.txt
-python bhh.py --dataset=adult --seed=13 --heuristic-pool=all --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=15 --credit=ibest
-echo 'bhh_reanalysis,adult,15,13' >>tracking/progress/bhh_reanalysis.txt
-python bhh.py --dataset=adult --seed=14 --heuristic-pool=all --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=15 --credit=ibest
-echo 'bhh_reanalysis,adult,15,14' >>tracking/progress/bhh_reanalysis.txt
-python bhh.py --dataset=adult --seed=15 --heuristic-pool=all --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=15 --credit=ibest
-echo 'bhh_reanalysis,adult,15,15' >>tracking/progress/bhh_reanalysis.txt
-python bhh.py --dataset=adult --seed=16 --heuristic-pool=all --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=15 --credit=ibest
-echo 'bhh_reanalysis,adult,15,16' >>tracking/progress/bhh_reanalysis.txt
-python bhh.py --dataset=adult --seed=17 --heuristic-pool=all --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=15 --credit=ibest
-echo 'bhh_reanalysis,adult,15,17' >>tracking/progress/bhh_reanalysis.txt
-python bhh.py --dataset=adult --seed=18 --heuristic-pool=all --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=15 --credit=ibest
-echo 'bhh_reanalysis,adult,15,18' >>tracking/progress/bhh_reanalysis.txt
[…]

### 2022-01-07 experiments/scripts/standalone.sh

@@ -1,676 +1,0 @@
-export TF_CPP_MIN_LOG_LEVEL=3
-export CUDA_VISIBLE_DEVICES=''
-export LOG_LEVEL=0
-
-python heuristic.py --dataset=adult --optimiser=de --seed=25
-echo 'standalone,adult,de,25' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=de --seed=26
-echo 'standalone,adult,de,26' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=de --seed=27
-echo 'standalone,adult,de,27' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=de --seed=28
-echo 'standalone,adult,de,28' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=de --seed=29
-echo 'standalone,adult,de,29' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=de --seed=30
-echo 'standalone,adult,de,30' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=ga --seed=1
-echo 'standalone,adult,ga,1' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=ga --seed=2
-echo 'standalone,adult,ga,2' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=ga --seed=3
-echo 'standalone,adult,ga,3' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=ga --seed=4
-echo 'standalone,adult,ga,4' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=ga --seed=5
-echo 'standalone,adult,ga,5' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=ga --seed=6
-echo 'standalone,adult,ga,6' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=ga --seed=7
-echo 'standalone,adult,ga,7' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=ga --seed=8
-echo 'standalone,adult,ga,8' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=adult --optimiser=ga --seed=9
[…]

### 2022-01-07 experiments/scripts/standalone2.sh

@@ -2,530 +2,6 @@ export TF_CPP_MIN_LOG_LEVEL=3
 export CUDA_VISIBLE_DEVICES=''
 export LOG_LEVEL=0
 
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=19
-echo 'standalone,diabetic,sgd,19' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=20
-echo 'standalone,diabetic,sgd,20' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=21
-echo 'standalone,diabetic,sgd,21' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=22
-echo 'standalone,diabetic,sgd,22' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=23
-echo 'standalone,diabetic,sgd,23' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=24
-echo 'standalone,diabetic,sgd,24' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=25
-echo 'standalone,diabetic,sgd,25' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=26
-echo 'standalone,diabetic,sgd,26' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=27
-echo 'standalone,diabetic,sgd,27' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=28
-echo 'standalone,diabetic,sgd,28' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=29
-echo 'standalone,diabetic,sgd,29' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=sgd --seed=30
-echo 'standalone,diabetic,sgd,30' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=momentum --seed=1
-echo 'standalone,diabetic,momentum,1' >>tracking/progress/standalone.txt
-python heuristic.py --dataset=diabetic --optimiser=momentum --seed=2
[…]

### 2022-01-07 framework/optimisers/bhh.py

@@ -28,6 +28,7 @@ import os
 from typing import List, Tuple
 
 import tensorflow as tf
+from framework.distributions.bernoulli import Bernoulli
 from framework.distributions.beta import Beta
 from framework.distributions.categorical import Categorical
 from framework.distributions.dirichlet import Dirichlet
@@ -620,17 +621,136 @@ class BHH(Optimiser):
         self.population.loss = loss
         self.population.log_state(step=step)
 
+        # Logging
+        self.log_overall_state(step=step)
 
         for j, entity in enumerate(self.population.entities):
-            entity.log_state(step=step)
+            self.log_entities_state(j, step=step)
+            entity.log_state(step)
+
+        for k, heuristic in enumerate(self.heuristic.params.heuristics):
+            self.log_heuristics_state(k, step=step)
+
+        for j, entity in enumerate(self.population.entities):
             for k, heuristic in enumerate(self.heuristic.params.heuristics):
-                self.log_state(j,k,step)
+                self.log_entity_heuristic_state(j,k,step)
 
         return logits, loss
 
-    def log_state(self, j, k, step):
+
+    def log_overall_state(self, step):
         """
         Logs the optimiser's metrics to Tensorboard.
+
+        Parameters
+        ----------
+        step: int
+            The step number.
+        """
+        log_level = int(os.getenv('LOG_LEVEL')
+                        ) if os.getenv('LOG_LEVEL') is not None else 0
+
+        # Only if the log level is 2
+        if self.logger and log_level >= 2:
+            theta = Dirichlet(concentration=self.alpha)
+            psi = Beta(concentration1=self.gamma1, concentration0=self.gamma0)
+
+            self.logger.log_distribution_results(
+                'theta', result=theta(), step=step)
+
+            self.logger.log_distribution_results(
+                'psi', result=psi(), step=step)
+
+            self.logger.log_distribution_results(
+                'HgEC', result=self.HgEC, step=step)
+
+            l_HgEC = Categorical(logits=self.p_HgEC)
+            self.logger.log_distribution_results(
+                'l_HgEC', result=l_HgEC(), step=step)
+
+
+
+    def log_entities_state(self, j, step):
+        """
+        Logs the optimiser's metrics to Tensorboard.
+
+        Parameters
+        ----------
+        j: int
+            The j-th index representing the j-th entity.
+        step: int
[…]

### 2022-09-12 dissertation/chapters/01-introduction.tex
📝 (review): First set of changes

--- 2022-01-07 thesis/chapters/01-introduction.tex
@@
 Sedol, 4-1 \cite{ref:san-hun:2016}.  Furthermore, an improvement on AlphaGo,
-called AlphaZero, learned to play Go, \textit{tabula rasa} \footnote{Latyn word
-meaning to learn from no prior knowledge} and managed to beat AlphaGo, 100-1
+called AlphaZero, learned to play Go, \textit{tabula rasa} \footnote{Latin word
+      meaning to learn from no prior knowledge.} and managed to beat AlphaGo, 100-1
 \cite{ref:silver:2017}.
@@
 point where workloads in the field of \ac{ML} that were previously computationally
-infeasible, is now possible. One such subfield of \ac{ML} is \acp{ANN}. With
-the improvement of hardware came an influx of \ac{ML} researchers that focussed
-their attention on the training and generalisation capabilities of \acp{ANN}.
+infeasible, are now possible.
+One such sub-field of \ac{ML} is \acp{ANN}.
+\acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain \cite{ref:engelbrecht:2007}.
+\acp{ANN} are the digital equivalent of how we currently understand the brain to work.
+\acp{ANN} can be trained, which is the equivalent of ``learnin'' from data.
+Learning gives rise to the ability to apply some form of decision making.
+This ability provides a wide-range of applications from healthcare to finance and yields great interest in the field.
+With the improvement of hardware came an influx of \ac{ML} researchers that focused
+their attention on the training of \acp{ANN}.
 
-A popular field of focus for studing \acp{ANN} is the training process by which
-these models are trained. Today, the most common form of training is
-\index{supervised training}supervised learning of \acp{FFNN}, a specific type of
-\ac{ANN} \cite{ref:reed:1999}. Training of \acp{ANN} is seen as an optimisation problem.
+A popular field of focus for studying \acp{ANN} is the process by which
+these models are trained. \acp{FFNN} are specific types of
+\acp{ANN} \cite{ref:reed:1999}. The most common way of training \acp{FFNN} is
+\index{supervised training}supervised learning.
+Training of \acp{ANN} is seen as an optimisation problem.
+The \ac{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''.
 A search algorithm known as a \index{heuristic}\textit{heuristic}
-\cite{ref:pearl:1984} is used to assign the optimal values to the \ac{ANN}
-weights such that a specified objective function is minimised.
+\cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.
 
@@
 is extensive, there still exists no single model that can be generalised to
-solving multiple problem classes, across multiple problem domains. This problem
-is known as the \ac{NFL} \cite{ref:wolpert:1997}.
+solving multiple problem classes, across multiple problem domains.
+\acs{ANN} training algorithms mostly yield problem specific solutions.
+This means that a particular approach that works well for one domain of problem class, often does not necessarily work for another.
+This problem is known as the \ac{NFL} \cite{ref:wolpert:1997}.
 
+Generalisation of \acp{ANN} refer to the capabilities of the network to either perform well on unseen data or to be applied to other problem domains.
 Various attempts have been made to improve the generalisation capabilities of
@@
 such as the \index{learning rate}learning rate and \index{momentum}momentum of
-gradient-based heuristics \cite{ref:zeiler:2012, ref:lv:2017, ref:darken:1992}
-and carefully selecting training data. Other techniques focus on improving
-generalisation through model design (architecture and topology). Examples of such
+gradient-based heuristics \cite{ref:zeiler:2012, ref:lv:2017, ref:darken:1992},
+and removing or postponing the use of outliers in the training data \cite{ref:reeves:1998}. Other techniques focus on improving
+generalisation through model design.
+Design configurations focus on the layout of the neurons and structure of the \acs{ANN} (architecture) and how neurons are connected to interact (topology).
+Examples of such
 techniques include learning of \ac{ANN} architectures through pruning techniques
@@
 
-One promising approach to improving \ac{ANN} generalisation capabilities is the
-idea of hybridisation \cite{ref:burke:2013}, which makes use of a combination of
-multiple learning paradigms in order to yield better generalisation. For
-example, heteregenous approaches have been shown to balance the tradeoff between
-exploration and exploitation. \cite{ref:nepomuceno:2013}. This hints towards the
-idea that \ac{ML} models could yield better generalisation capabilities if the
-learning process and learning mechanism applied is not statically defined, but
-rather dynamic and under the control of some control mechanism.
-
-The learning process is influenced by various factors, including the type of
-learning technique used, how the model parameters are initialised, the
-hyper-parameters used, the constraints of learning and the learning mechanism
-itself. In order to yield better generalisation capabilities, the model should
-be trained by a learning technique that has at its disposal a more diverse set
-of learning behaviours from which it can dynamically select should the need arise
-\cite{ref:huang:2009}. In doing so, balancing between exploration and
-exploitation of solutions is a dynamic process that would yield better
-generalisation capabilities.
+The performance and capabilities of \acp{ANN} is largely influenced by the learning process used.
+The learning process consists of multiple components.
+These include the type of underlying optimisation algorithm used, how the model parameters are initialised, the hyper-parameters used and the constraints of learning such as allowed search space and boundaries.
+Each of these elements influence how much a particular learning technique might focus on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during training.
 
 An example of dynamically balancing exploitation and exploration during the
-search process is done by dynamically adjusting and learning the heuristic
+search process is by dynamically adjusting and learning the heuristic
 \index{hyper-parameters}\textit{hyper-parameters} as part of the learning
@@
 
-A more recent suggestion related to the field of
-\index{meta-learning}meta-learning is to dynamically select and/or adjust the
-heuristic used throughout the training process. This approach is about the
-hybridisation of heuristics as they are applied to some optimisation problem.
-These methods are referred to as \acp{HH} and focus on finding the best
-heuristic in \textit{heuristic-space}. One such form of \ac{HH} is a
+This dynamic nature of the learning process leads towards the
+idea that \ac{ML} models could yield better generalisation capabilities if the
+learning process and learning mechanism applied are not statically defined, but
+rather dynamic and under the control of some mechanism. Furthermore, a learning technique that has at its disposal a more diverse set
+of learning behaviours from which it can dynamically select (when the need arises) could yield better generalisation capabilities \cite{ref:huang:2009}.
+
+A more recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process.
+This approach focuses on the hybridisation of learning paradigms.
+The main concept behind this paradigm is that the learning process is dynamic and differs from problem to problem.
+A particular learning technique might work well for one problem and not for another.
+At the same time, a particular learning technique might work well for a particular part of the search landscape, but not for another.
+By dynamically combining the best of different learning paradigms throughout the learning process, a trade-off can be made between exploration and exploitation as is required.
+
+One such form of hybridisation of learning paradigms is referred to as \index{heterogeneous learning approaches}\textit{heterogeneous learning approaches}.
+Heterogeneous learning approaches make use of different search behaviours by selecting from a behaviour pool.
+Heterogeneous approaches have shown to balance the trade-off between exploration and exploitation \cite{ref:nepomuceno:2013}.
+
+A step further in the concept of hybridisation of learning paradigms is that of hybridisation of different heuristics as they are applied to some optimisation problem \cite{ref:burke:2013}.
+These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic-space} to solve a specific problem.
+One such form of \ac{HH} is a
 population-based approach that guides the search process by automatically
@@
 non-trivial and some \textit{selection strategy} must be used to select the best
-heuristic. \acp{HH} that implement such a selection strategy is referred to as
+heuristic. \acp{HH} that implement such a selection strategy are referred to as
 \textit{selection} \acp{HH}. The term \textit{selection} refers to the ability
@@
 
-This thesis focusses on the development of a \ac{HH} to train \acp{FFNN} in a
+This dissertation focuses on the development of a \ac{HH} to train \acp{FFNN} in a
 supervised learning approach.
@@
 Many different heuristics have been developed and used to train \acp{FFNN}
-\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.  The problem
-lies in the process of finding the best heuristic to train the \ac{FFNN}. This
+\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
+Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses.
+Finding the best heuristic to train the \ac{FFNN} is required in order to yield optimal results.
+This
 process is often non-trivial and could be a time-consuming exercise.  Consider
@@
 as training \acp{FFNN}, is very problem dependent \cite{ref:allen:1996,
-ref:drake:2020, ref:pillay:2018}. Furthermore, the \ac{NFL} shows that no single
-heuristic performs better than any other heuristic for all problems
-\cite{ref:wolpert:1997}.
+      ref:drake:2020, ref:pillay:2018}.
 
@@
 heuristic by trail and error. A set of heuristics and carefully selected
-hyper-parmeters would be implemented, followed by an empirical test to evaluate
+hyper-parameters would be implemented, followed by an empirical test to evaluate
 the performance of each heuristic for a given problem domain
@@
 heuristics and which hyper-parameters performed well for different problems.
-However, this approach is problematic as it is time-consuming and tedious.
+However, this approach is problematic, because it is time-consuming and tedious.
 
@@
 
-A modern approach is to use \acp{HH} to automated the process for selecting the
+A modern approach is to use \acp{HH} to automate the process of selecting the
 best heuristic when applied to some optimisation problem. The best heuristic
 might not be a single heuristic, but rather a hybridisation of heuristics
-\cite{ref:pillay:2015}. Therefore, careful consideration is required to include
-a diverse and applicable set of heuristics to select from that is capable of
-solving the given problem. \citeauthor{ref:pillay:2015} \cite{ref:pillay:2015}
-mentions that only heuristics that are known to have the potential to solve the
-problem must be included in the set of heuristics to select from.
+\cite{ref:pillay:2015}.
+Therefore, careful consideration is required to include and select from a diverse set of heuristics that is capable of solving the given problem.
+Importantly, only heuristics that are known to have the potential to solve the
+problem are applicable and can be included in the set of heuristics to select from.
 
-\acp{HH} have been implemented on a wide range of optimisation problems
-\cite{ref:grobler:2011, ref:burke:2013, ref:pillay:2015}, but no research has
-been found where \acp{HH} have been applied on the training of \acp{FFNN}.
+In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many
+different problems.
+Some notable examples include the \index{simulated annealing}simulated annealing-based \ac{HH} by \citeauthor{ref:dowsland:2007} \cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \ac{HH} of \citeauthor{ref:burke:2010} \cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by \citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} and work done by \citeauthor{ref:vanderstockt:2018} \cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based metaheuristics in real-valued dynamic optimization.
+However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.
+\citeauthor{ref:nel:2021} \cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
+The shortage of research in this field certainly warrants more exploration.
 
-The training of \acp{FFNN} is seen as a computational search problem. \Acl{HH}
+\acp{FFNN} training is seen as a computational search problem. \Acl{HH}
 as defined by Burke et al. \cite{ref:burke:2010} is ``a search method or
 learning mechanism for selecting or generating heuristics to solve computational
-search problems". \acp{HH} is a field of research aimed at the automated
-selection, combination, adaptation and generation of multiple lower-level
+search problems''. \acp{HH} is a field of research aimed at the automated
+selection, combination, adaptation or generation of multiple lower-level
 heuristics to efficiently solve computational search problems. This implies that
-one should be able to apply \acp{HH} in the context of training \acp{FFNN}.
+it should be possible to apply \acp{HH} in the context \acs{FFNN} training.
 
-\citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} mentions that the focus of
+\citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} mention that the focus of
 \acp{HH} is on automating the development of the \textit{learning mechanism}
-used to obtain an appropriate solution for an optimisation problem. The authors
-go on to explain that \acp{HH} employ a high-level heuristic that focusses on
+used to find the best heuristic to obtain an appropriate solution to an optimisation problem. \citeauthor{ref:grobler:2012} explain that \acp{HH} employ a high-level heuristic that focuses on
 finding the best low-level heuristic in heuristic-space that could include
-\textit{single-method} and \textit{multi-method} optimistion algorithms
-(heuristics). Applying \acp{HH} to train \acp{FFNN} could generally be applied
-to multiple problems given that the set of low-level heuristics include
+\textit{single-method} and \textit{multi-method} optimisation algorithms
+(heuristics). \acp{HH} relieve the burden of having to select the best
+heuristic to use by trial and error. Furthermore, \acp{HH} can generally be applied to multiple
+problems given that the set of low-level heuristics include
 heuristics that have the potential to solve the problem at hand
-\cite{ref:burke:2010}. This relieves the burden of having to select the best
-heuristic to use by trial and error and is generally applicable to multiple
-problems. The automation of the selection process as well as the generalisation
-capabilities of \acp{HH}, if applied in the context of training \acp{FFNN},
-could reduce the effort required to find the best heuristic to use.
+\cite{ref:burke:2010}.
+Automation of the heuristic selection process and the general application to a wider range of problems are characteristics of \acp{HH} that can be beneficial when applied in the context of \acp{FFNN} training.
 
-Note that training \acp{FFNN} using \acp{HH} is not to be confused by the
+Note that training of \acp{FFNN} using \acp{HH} is not to be confused with the
 training of \acp{FFNN} using \index{ensemble networks}\textit{ensemble networks}
 or \index{query by committees}\textit{query by committees}.
-\citeauthor{ref:pappa:2014} \cite{ref:pappa:2014} describes \index{ensemble
+\citeauthor{ref:pappa:2014} \cite{ref:pappa:2014} describe \index{ensemble
       networks}ensemble networks as a combination method in
 \index{meta-learning}meta-learning whereby multiple \acp{ANN} are jointly used
-to solve a problem. Each member network in the ensemble gets trained using a
-specified heuristic and generally this heuristic is applied to the same member
+to solve a problem. Each member network in the ensemble is trained using a
+specified heuristic, and generally this heuristic is applied to the same member
 throughout the training process. The results of all of the member networks are
-then joined together using some mechanism \cite{ref:zhou:2002}. This mechanism
-could be weighted averages or majority or weighted voting. \index{ensemble
-networks}Ensemble networks do not search through the heuristic space and do not
-reselect lower-level heuristics for each member, while \acp{HH} do. There is
-thus no hybridisation of heuristics in \index{ensemble networks}ensemble
-networks and therefore, no information-sharing between any of the members of the
-ensemble, in comparison to \acp{HH} that do incorporate some shared information
-space.
-
-Many different types of \acp{HH} have been implemented and shown to solve many
-different problems. Some notable examples include the
-\index{tabu-search}tabu-search \ac{HH} of Burke et al. \cite{ref:burke:2010} and
-the \index{simulated annealing}simulated annealing-based \ac{HH} by Dowsland et
-al. \cite{ref:dowsland:2007}.
+then joined together using some consensus mechanism \cite{ref:zhou:2002}. This mechanism
+could be weighted averages, majority voting or weighted voting. \index{ensemble
+      networks}Ensemble networks do not search through the heuristic space to find the best training algorithm for each member, while \acp{HH} do.
 
@@
 that makes use of probability theory and Bayesian statistical concepts to guide
-the heuristic selection process. This research develops the novel \Ac{BHH}, a
-new high-level heuristic that utilises \index{Bayesian analysis}\textit{Bayesian
-analysis} as the selection mechanism for a \ac{HH} to select the appropriate
-heuristic to train \acp{FFNN}.
+the heuristic selection process. This research develops the novel \Acf{BHH}, a
+new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian
+      analysis} which combines prior information with new evidence to the parameters of a selection probability distribution.
+This selection probability distribution is the mechanism by which the \ac{HH} selects appropriate
+heuristics to train \acp{FFNN} during the training process (online learning).
 
@@
 
-The main objectives of this research is focussed on developing a novel \Ac{BHH}
+The main objective of this research is focused on developing a novel \Ac{BHH}
 selection mechanism in a \ac{HH} framework that can be used to train \acp{FFNN}.
@@
             used to train \acp{FFNN}. The literature study will provide the necessary
-    background information to understand how the these different heuristics can
+            background information to understand how these different heuristics can
             be used in the set of heuristics to be selected to train the \ac{FFNN}.
@@
 
+      \item Conduct an empirical study to investigate the behavioural characteristics of the \ac{BHH} as it is used to train \acp{FFNN} over a number of different datasets.
+
       \item
@@
       \item
-    Conduct an empirical study and critically evaluate the performance of the
-    developed \Ac{BHH} as a selection mechanism to other selection mechanisms
-    for \acp{HH} as they are used to train \acp{FFNN} on different problems.
-
-    \item
-    Conduct an empirical study that investigate variations of the \Ac{BHH} and the
+            Conduct an empirical study that investigates variations of the \Ac{BHH} and the
             effects of design decisions and hyper-parameters on the search process.
@@
 
-The results obtained from this research contributes to the field of study in the
+The results obtained from this research contribute to the field of study in the
 following ways:
@@
       \item
-    To the knowledge of the author, this study provides the first application
-    of using \acp{HH} to train \acp{FFNN}.
-
-    \item
-    A novel heuristic selection operator is used that focusses on using Bayesian
+            A novel heuristic selection operator is used that focuses on using Bayesian
             statistics to calculate the probability that a heuristic should be selected
@@
       \item
-    The results of the empirical study show that the \Ac{BHH} perform generally
-    better than the individual lower-level heuristics as applied to the same
-    problems, with statistical significance and certainty.
+            The results of the empirical study show  with statistical significance and certainty that the \Ac{BHH} performs generally
+            well on multiple problems.
+It is shown that, for each problem, the \Ac{BHH} performance is comparable to the best low-level heuristics (for the particular problem) included in the heuristic selection pool.
 
@@
             set of lower-level heuristics, will generally produce good results when
-    applied to multiple problems.
+            applied to multiple problems at the same time.
 
@@
             Finally, the results of the empirical study show that the \Ac{BHH} is
-    capable of utilising \textit{a priori} \footnote{Latin word, meaning "from
-    what comes before"} knowledge in which a predefined selection bias is used
-    for heuristics the are known to be well suited for certain problems.
+            capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from
+                  what comes before''.} knowledge in which a predefined selection bias is used
+            for heuristics that are known to be well suited for certain problems.
 \end{itemize}
 
-\section{Thesis Outline}
+\section{Dissertation Outline}
 \label{sec:introduction:outline}
 
-The remainder of this thesis is structured as follows:
+The remainder of this dissertation is structured as follows:
 
@@
             \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN}
-    and the various components that make up an \ac{AN}. The focus is on the
-    training of \acp{FFNN} and it is shown how the training of \acp{FFNN} is
+            and the various components that make up an \acl{AN}. The focus is on the
+            training of \acp{FFNN}. It is shown how the training of \acp{FFNN} is
             seen as an optimisation problem.
@@
             \textbf{Chapter~\ref{chap:heuristics}} provides details on various types of
-    heuristics and metaheuristics that have been used to train \acp{FFNN}. A
+            heuristics and meta-heuristics that have been used to train \acp{FFNN}. A
             literature study is done to provide details on the search behaviours, application and
-    implementation of each heuristics in the context of training \acp{FFNN}.
+            implementation of each heuristic in the context of training \acp{FFNN}.
 
@@
             of \acp{HH} and \index{meta-learning}meta-learning in general. A
-    discussion follows on the current landscape of \ac{HH} research. It is shown
-    how \acp{HH} is a suitabe approach for training \acp{FFNN}.
+            discussion follows on the current landscape of \ac{HH} research and a review of different selection approaches for \acp{HH} is conducted.
+It is shown how \acp{HH} are suitable for \acs{FFNN} training.
 
@@
             conjugate priors are discussed in detail. The chapter concludes with a
-    detailed discussion on Bayesian statistics, specifically focussing on
+            detailed discussion on Bayesian statistics, specifically focusing on
             Bayesian inference and analysis.
@@
             are used, the configuration of hyper-parameters, initialisation techniques
-    used, performance measures used and other smaller details to the
-    implementation of each experiment.  Finally discussions follow on how the
+            used, performance measures used and other smaller details of the
+            implementation of each experiment.  Finally, discussions follow on how the
             results are analysed. This includes a discussion on the method used to
@@
             \textbf{Chapter~\ref{chap:conclusion}} summarises the research done in this
-    thesis along with a brief overview of findings made throughout the research
+            dissertation along with a brief overview of the findings made throughout the research
             process. A review of the research goals are given and suggestions for future
@@
 
-This thesis is accompanied by a full index given at page~\pageref{index} along with the following appendices:
+This dissertation is accompanied by a full index given at page~\pageref{index} along with the following appendices:
 
@@
       \item
+            \textbf{Appendix~\ref{app:statistical_analysis}} provides details on the outcomes of the statistical analyses.
+
+      \item
             \textbf{Appendix~\ref{app:acronyms}} provides a list of the important
@@
       \item
+            \textbf{Appendix~\ref{app:derived_publications}} lists the publications
+            derived from this work.
+
+      \item
             \textbf{Appendix~\ref{app:symbols}} lists and defines the mathematical
@@
             in which they appear.
-
- 	\item
-    \textbf{Appendix~\ref{app:derived_publications}} lists the publications
-    derived from this work.
 \end{itemize}
@@
 To best view the illustrations, tables and figures presented throughout this
-thesis, it is recommended that the thesis be viewed in colour.
+dissertation, it is recommended that the dissertation be viewed in colour.

### 2022-09-12 dissertation/chapters/02-artificial-neural-networks.tex
📝 (review): First set of changes

--- 2022-01-07 thesis/chapters/02-artificial-neural-networks.tex
@@
         means that there are approximately as many neurons in the human brain as
-        there are stars in our galaxy. Every one of these neurons are highly
+        there are stars in our galaxy. Every one of these neurons is highly
         interconnected with other neurons, yielding a synapse count of 100
@@
 lead to the development of \acp{ANN} \cite{ref:rosenblatt:1958}. \acp{ANN}
-are used throughout this thesis as the model to be trained using \acp{HH}.
-Understanding how \acp{ANN} work is an important component of this thesis.
+are used throughout this dissertation as the model to be trained using \acp{HH}.
+Understanding how \acp{ANN} work is an important component of this dissertation.
 
@@
     \item
-    Section~\ref{sec:anns:bn} gives background information on the \ac{BN}.
-
-    \item
-    Section~\ref{sec:anns:an} introduces the \ac{AN} and the various
+    \textbf{Section \ref{sec:anns:bn}} gives background information on the \ac{BN}.
+
+    \item
+    \textbf{Section \ref{sec:anns:an}} introduces the \ac{AN} and the various
     components that it is made up of. Brief discussions follow on
@@
     Discussions on the \ac{BN} and the \ac{AN} set the tone for the \ac{ANN}
-    which is discussed in detail in Section~\ref{sec:anns:ann}. Brief
+    which is discussed in detail in \textbf{Section \ref{sec:anns:ann}}. Brief
     discussions follow on \ac{ANN} architecture, topology, and
@@
     \item
-    Section~\ref{sec:anns:training} gives details on the training process,
+    \textbf{Section \ref{sec:anns:training}} gives details on the training process,
     training sets, \index{supervised learning}supervised learning,
@@
     Finally, a brief summary of the chapter is given in
-    Section~\ref{sec:anns:summary}.
+    \textbf{Section \ref{sec:anns:summary}}.
 \end{itemize}
@@
 
-\begin{figure}[H]
+\begin{figure}[htpb]
     \centering
@@
 
-The main parts of the \ac{BN} to focus on includes the cell body, the
+The main parts of the \ac{BN} to focus on include the cell body, the
 \index{dendrites}\textit{dendrites} and the \index{axon}\textit{axon} because these
@@
 
-The An \ac{AN} implements a nonlinear mapping from $\mathbb{R}^{I}$ to
+The \ac{AN} implements a nonlinear mapping from $\mathbb{R}^{I}$ to
 $\mathbb{R}^{T}$, usually in the ranges $[0,1]$ or $[-1,1]$, depending on the
@@
 where $f_{AN}$ is the function mapping produced by the \ac{AN}, $I$
-is the total number of dimensions of the input in real-number space $\mathbb{R}$
+is the total number of dimensions of the input in real-number space $\mathbb{R}$,
 and $T$ is the total number of dimensions of the target (desired output) in
@@
 
-An illustration of the \ac{AN} is given below:
-
-\begin{figure}[H]
+An illustration of the \ac{AN} is given is Figure \ref{fig:artificial_neuron}.
+
+\begin{figure}[htpb]
   \centering
@@
     \item
-    \index{net input signal}\textbf{Net input signal:} The \index{net input signal}netinput signl models
+    \index{net input signal}\textbf{Net input signal:} The \index{net input signal}net input signal models
     the net resulting activations from all connected pre-synaptic neurons or
@@
     \item
-    \textbf{Output:} This output models the activation by the post-synaptic neuron. Output is
+    \textbf{Output:} The output models the activation by the post-synaptic neuron. Output is
     represented by the output vector $\vec{y}$.
@@
 variables}\textit{independent variables} \cite{ref:francis:2001}. In this
-thesis, a single input vector is referred to as a pattern. Input data must first
+dissertation, a single input vector is referred to as a pattern. Input data must first
 be pre-processed before it is presented to the \ac{AN}. Input pre-processing
@@
 scaling to the correct ranges to dealing with incomplete, invalid or even
-irrelevant data. For the purposes of this thesis, only data encoding and
+irrelevant data. For the purposes of this dissertation, only data encoding and
 normalisation is considered. These topics are now discussed in more detail.
@@
 converted to numerical representations. In general, class labels are encoded as
-vectors \cite{ref:srinidhi:2018, ref:brownlee:2017:one-hot}. This thesis makes
+vectors \cite{ref:srinidhi:2018, ref:brownlee:2017:one-hot}. This dissertation makes
 use of \index{One-Hot Encoding}\textit{one-hot encoding} of class labels which
@@
 \cite{ref:harris:2010} describe \index{One-Hot Encoding}one-hot encoding as a
-group of vector elements where the representations of classes are represented
+group of vector elements where the classes are represented
 with a single high element (represented by $1$) and all the others low
@@
 Function}activation function being used. This yields input data in a range that
-is comparable to the output produced. For the purpose of this thesis, the
+is comparable to the output produced. For the purpose of this dissertation, the
 min-max scaler \cite{ref:al:2006} and standard score scaler \cite{ref:jain:2005}
@@
 \index{activation function}activation function\index{activation function} is
-used. The normalised for of $x_{i,p}^{'}$ as determined by the \index{standard
+used. The normalised form of $x_{i,p}^{'}$ as determined by the \index{standard
 score scaler}standard score scaler is given in below:
@@
 Weight initialisation is the process by which candidate solutions (represented
-by the weights of the \ac{AN}) to the problem is placed in the search-space.
+by the weights of the \ac{AN}) to the problem are placed in the search-space.
 Weight initialisation influences the speed of convergence, the probability of
@@
 output of the activation function would not be in the active range. This leads
-to hidden unit saturation and exploding gradients can occur
+to unit saturation, and exploding gradients can occur
 \cite{ref:hanin:2018, ref:yadav:2018}.
 
-Research have presented many initialisation techniques \cite{ref:erdogmus:2003}.
+Research has presented many initialisation techniques \cite{ref:erdogmus:2003}.
 Some techniques have been developed to address the problems that are mentioned
-above \cite{ref:yadav:2018}. However, this thesis will only focus on
+above \cite{ref:yadav:2018}. However, this dissertation will only focus on
 \index{random uniform sampling}random uniform sampling, \index{Glorot uniform
@@
 units in the weight vector. \index{Glorot normal sampling}Glorot normal sampling
-have been shown to decrease training time \cite{ref:glorot:2010}.
+has been shown to decrease training time \cite{ref:glorot:2010}.
 
@@
 calculated is by means of \acp{SU} \cite{ref:engelbrecht:2007}, which
-computes the \index{net input signal}net input signal as the weighted sum of all
+compute the \index{net input signal}net input signal as the weighted sum of all
 input signals as shown below:
@@
 \textit{bias unit} \cite{ref:engelbrecht:2007}. Augumented vectors that include
-the bias unit to the net input signal is presented next.
+the bias unit to the net input signal are presented next.
 
@@
 
-\index{activation function}Activation functions are used to model the action
+An \index{activation function}activation function is used to model the action
 potential of the \index{AN}\ac{AN} \cite{ref:ziv:1994, ref:hodgkin:1952}, and is
@@
 \begin{equation}
-    f_{AN}: \mathbb{R}^{I} \rightarrow [0,1]
+    f_{AN}: \mathbb{R}^{I} \rightarrow [0,1],
     \label{eq:an_function_mapping_0_1}
@@
 \begin{equation}
-    f_{AN}: \mathbb{R}^{I} \rightarrow [-1,1]
+    f_{AN}: \mathbb{R}^{I} \rightarrow [-1,1].
     \label{eq:an_function_mapping_minus_1_1}
@@
 
-\noindent Research in the past have presented many \index{activation
+\noindent Research in the past has presented many \index{activation
 function}activation functions \cite{ref:karlik:2011} of varying ranges. However,
-this thesis focuses on the \ac{ReLU} \cite{ref:jarrett:2009, ref:nair:2010}, the
+this dissertation focuses on the \ac{ReLU} \cite{ref:jarrett:2009, ref:nair:2010}, the
 \ac{LReLU} \cite{ref:maas:2013}, the \index{sigmoid}sigmoid \cite{ref:lecun:1988} and the
@@
 ref:maksutov:2018} which occurs when gradients in the first layers of a
-multi-layer \ac{ANN} approach zero, and have no effect in the training process.
+multi-layer \ac{ANN} approach zero, and have no effect on the training process.
 
@@
 the \ac{ReLU} \index{activation function}activation function \cite{ref:xu:2015}.
-Similar to \ac{ReLU} it is not susceptible to the \index{vanishing gradients
-problem}vanishing gradients problem and it does not suffer from the \index{dying
+Similar to \ac{ReLU}, it is not susceptible to the \index{vanishing gradients
+problem}vanishing gradients problem, and it does not suffer from the \index{dying
 ReLU problem}dying \ac{ReLU} problem \cite{ref:agarap:2018}, which occurs when
@@
 
-The \ac{LReLU} \index{activation function}activation function is defines as:
+The \ac{LReLU} \index{activation function}activation function is defined as:
 
@@
 An illustration of the \ac{LReLU} with various values for $\alpha$ and $\theta =
-0$ is given in Graph~\ref{grf:leaky_relu} below:
-
-\begin{graph}[H]
+0$ is given in Figure \ref{fig:anns:activation_functions:leaky_relu}.
+
+\begin{figure}[htpb]
     \centering
@@
     \acs{LReLU} \index{activation function}activation function.}
-    \label{grf:leaky_relu}
-\end{graph}
+    \label{fig:anns:activation_functions:leaky_relu}
+\end{figure}
 
@@
 \index{sigmoid}Sigmoid is a very popular \index{activation function}activation
-function, because it introduces non-linearity into the model. The
+function, because it is a continuous differentiable approximation of the step function, which was used in the original perceptron model developed by \citeauthor{ref:rosenblatt:1957} \cite{ref:rosenblatt:1957}.
+The
 \index{sigmoid}sigmoid \index{activation function}activation function is defined
@@
 Function}activation function with various values for $\lambda$ and $\theta = 0$
-is given below:
-
-\begin{graph}[H]
+is given in Figure \ref{fig:anns:activation_functions:sigmoid}.
+
+\begin{figure}[htpb]
     \centering
@@
     Function}activation function.}
-    \label{grf:sigmoid}
-\end{graph}
+    \label{fig:anns:activation_functions:sigmoid}
+\end{figure}
 
@@
 function}activation function with various values for $\lambda$ and $\theta = 0$
-is given below:
-
-\begin{graph}[H]
+is given in Figure \ref{fig:anns:activation_functions:hyperbolic_tangent}.
+
+\begin{figure}[htpb]
     \centering
@@
     Tangent}hyperbolic tangent \index{activation function}activation function.}
-    \label{grf:hyperbolic_tangent}
-\end{graph}
+    \label{fig:anns:activation_functions:hyperbolic_tangent}
+\end{figure}
 
@@
 necessary to post-process the output data. A brief discussion on post-processing
-techniques follow.
+techniques follows.
 
@@
 techniques used, as well as the \index{activation function}activation function
-used. For the purposes of this thesis, only data decoding, normalisation and
+used. For the purposes of this dissertation, only data decoding, normalisation and
 re-scaling techniques are considered.
@@
 Normalisation of the output data is used to simplify the decoding process. This
-thesis considers \index{softmax}\textit{softmax} and
+dissertation considers \index{softmax}\textit{softmax} and
 \index{Argmax}\textit{argmax} normalisation to assist the decoding process.
@@
 
-\noindent Graph~\ref{grf:softmax_argmax} illustrates the comparison of
+\noindent Figure \ref{fig:anns:activation_functions:softmax_argmax} illustrates the comparison of
 transformations of the output vector $\vec{y}$, where the
@@
 
-\begin{graph}[H]
+\begin{figure}[htpb]
     \centering
@@
     after the \index{sigmoid}sigmoid \index{activation function}activation function.}
-    \label{grf:softmax_argmax}
-\end{graph}
+    \label{fig:anns:activation_functions:softmax_argmax}
+\end{figure}
 
@@
 biologically and chemically incredibly sophisticated. Trying to model an entire
-brain is at this stage not computationally feasible. Sandberg
+brain is at this stage not computationally feasible. \citeauthor{ref:sandberg:2008}
 \cite{ref:sandberg:2008} approximates a computational requirement of 256 000
-terabytes/s to emulate the entire brain. Given our shortage in hardware
+terabytes/s to emulate the entire brain. Despite our shortage in hardware
 capabilities, \acp{ANN} have been successfully applied to a range of problem
-classes. Engelbrecht \cite{ref:engelbrecht:2007} summarises some common problems
+classes. \citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} summarises some common problems
 that are solved using \acp{ANN}. These include:
@@
 function}activation function, but this is not a requirement. Output from one
-layer is propagated as input to the next layer. This thesis focusses on the
+layer is propagated as input to the next layer. This dissertation focuses on the
 simplest architecture, containing three particular layers, including the input,
-hidden and output layers. \acp{ANN} with this type of architecture is usually
+hidden and output layers. \acp{ANN} with this type of architecture are usually
 referred to as \textit{shallow} \acp{NN}. The input, hidden and output layers
@@
 The input layer contains the input data to the \ac{ANN}. Since the
-input layer simply provides the the input data, some literature do not consider
+input layer simply provides the input data, some literature does not consider
 the input layer as a layer \cite{ref:engelbrecht:2007}.
@@
 There are many different topologies \cite{ref:miikkulainen:2010}, however, this
-thesis only focusses on a \index{fully connected topology}fully connected
+dissertation only focuses on a \index{fully connected topology}fully connected
 topology.
@@
 information moves forward, in one direction, from the input nodes, through the
-hidden nodes and finally to the output nodes and depending on the optimisation
+hidden nodes and finally to the output nodes, and, depending on the optimisation
 algorith used, error correction information can be backpropagated through the
@@
 An illustration of a \ac{FFNN} using a three-layered architecture and a fully
-connected topology is given below:
-
-\begin{figure}[H]
+connected topology is given in Figure \ref{fig:ffnn}.
+
+\begin{figure}[htpb]
     \centering
@@
 vector $\vec{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer,
-$y_k$ refers to the $k$-th dimension in the output vector $\vec{y}$. $v_{i,j}$
-refers to the weight associated with input node $x_i$ and the hidden node $h_j$
-and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the
+$y_k$ refers to the $k$-th dimension in the output vector $\vec{y}$, $v_{i,j}$
+refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the
 output node $y_k$.
@@
 With the layered architecture and \index{fully connected topology}fully
-connected topology of \acp{FFNN} and assuming the use of \acp{SU}, the output
-for the \ac{FFNN} at index $k$, denoted $y_k$ is calculated using:
+connected topology of \acp{FFNN}, and assuming the use of \acp{SU}, the output
+for the \ac{FFNN} at index $k$, denoted $y_k$, is calculated using:
 
@@
 
-\noindent The remainder of this thesis makes use of \acp{FFNN} as the \ac{ANN}
-of interest and is sometimes referred to as \textit{the model}.
+\noindent The remainder of this dissertation makes use of \acp{FFNN} as the \ac{ANN}
+of interest, sometimes referred to as \textit{the model}.
 
@@
 
-Details on the training of \acp{FFNN} is presented in this section along with
+Details on the training of \acp{FFNN} are presented in this section along with
 brief discussions on the training process, generalisation capabilities, training
@@
 
-Central to this thesis is the topic of generalisation. Generalisation refers to
+Central to this dissertation is the topic of generalisation. Generalisation refers to
 the ability of a model to balance under- and overfitting of data. Training a
@@
 An error function, also known as a \index{Loss Function}\index{Cost
-Function}\textit{loss/cost function} \cite{ref:changhau:2017} is used to
+Function}\textit{loss/cost function} is used to
 evaluate the model's capability to approximate output data based on the input
@@
 
-This thesis focusses on the following error functions: \ac{SSE}, \ac{MSE},
+This dissertation focuses on the following error functions: \ac{SSE}, \ac{MSE},
 \ac{RMSE}, \ac{MAE}, \ac{BinXE}, \ac{CatXE} and \ac{SparseCatXE}. Each of these
@@
 There are many different mechanisms that can be used to measure the performance
-of a \ac{FFNN}, however this thesis only focusses on measures of cost such as
+of a \ac{FFNN}, however this dissertation only focuses on measures of cost such as
 loss and speed. Brief discussions follow on loss and speed as performance
@@
 measurement metric e.g how many epochs of training is necessary for a \ac{FFNN}
-to reach a certain lost/cost threshold. If emperical tests run on simular
-enviroments, relative time of execution can be used, but this is less popular.
-
-For this thesis, speed is a measure of performance relative to training
+to reach a certain lost/cost threshold.
+
+For this dissertation, speed is a measure of performance relative to training
 \textit{steps} or \textit{mini-batch} steps.
@@
 described in terms of architecture and topologies. Special emphasis was put on
-\acp{FFNN} as the model being used throughout the rest of the thesis.
+\acp{FFNN} as the model being used throughout the rest of the dissertation.
 Section~\ref{sec:anns:training} provided the necessary background information
@@
 was explained and details on training sets was provided. A variant of learning,
-called \index{Supervised Learning}supervised learning is presented and led to
+called \index{Supervised Learning}supervised learning was presented and led to
 the discussion on error functions, performance measures, and stopping

### 2022-09-12 dissertation/chapters/03-heuristics.tex
📝 (review): First set of changes

\chapter{Heuristics}
\label{chap:heuristics}

\begin{quotation}
    \textit{``It is not the strongest of the species that survives. It is also not the most intelligent that survives. It is the one that is the most adaptable to change.'' - Charles Darwin}
\end{quotation}

So far the reader has been introduced to the detailed background information on \acp{ANN}. The training process was discussed without any reference to specific optimiser algorithms to execute the training process. Specific reference is made to supervised learning in the context of \ac{FFNN}. This chapter aims to extend to this information by providing the reader with a set of optimisers that have been widely used to train \acp{ANN}. In the context of \acp{HH}, standardisation of terminology is in order and therefore these optimisers fill the role of low-level heuristics and will be referred to as heuristics from this point on.

Many different techniques have been used to train \acp{ANN} \cite{ref:kingma:2014}.  At the time of writing, the majority of work that is published around \ac{ANN} training involves the use of some gradient-based technique \cite{ref:nel:2021}. However, research has shown that these gradient-based techniques do have their disadvantages such as slow-convergence or getting trapped in local optima \cite{ref:mingguang:2009}. Other techniques have also been shown to successfully train \acp{FFNN}. These include meta-heuristics such as  \ac{PSO} \cite{ref:rakitianskaia:2012}\cite{ref:vanwyk:2014}, \ac{DE} \cite{ref:espinal:2011} and \acp{GA} \cite{ref:gupta:1999}. Various heuristics are considered for training \acp{FFNN} as the best heuristic to use is shown to be problem dependent in many cases \cite{ref:kheiri:2017}.

Although there are many different types of heuristics, the list of heuristics specified in this Chapter is by no means exhaustive. Broadly speaking this chapter focuses on two different groups of heuristics. These include classical gradient-based approaches and population-based meta-heuristics. Each technique is discussed in detail. Pseudo-code algorithms are provided and where possible and discussions follow on their advantages, disadvantages, capabilities and limitations. This subset of heuristics were selected for their characteristics and were deemed appropriate and sufficient for the problem at hand. The remainder of this chapter is structured as follows.

\begin{itemize}
    \item \textbf{Section \ref{sec:heuristics:what_is_a_heuristic}} provides a high-level definition for heuristics.

    \item \textbf{Section \ref{sec:heuristics:optimisation}} provides a brief overview of what optimisation is. It is also shown that \ac{FFNN} training is an optimisation problem.

    \item \textbf{Section \ref{sec:heuristics:gd}} presents the reader with the concept of gradient-based heuristics. The basics of \ac{BP} is provided and detailed discussions follow on seven different gradient-based low-level heuristics.

    \item \textbf{Section \ref{sec:heuristics:mh}} presents the reader with three different meta-heuristics that are show to train \acp{FFNN}.

    \item Finally, a summary of the chapter is provided in \textbf{Section \ref{sec:heuristics:summary}}.
\end{itemize}

\section{What is a heuristic?}
\label{sec:heuristics:what_is_a_heuristic}

The term \textit{heuristic} comes from the Latin word \textit{heuristicus} which means ``to find out, discover''. \citeauthor{ref:romanycia:1985} \cite{ref:romanycia:1985} provides a complete study on the history and origins of the term \textit{heuristic}. From their research, a proposal was made to define heuristics in the context of 
\ac{AI}, as any device, be it a program, rule, piece of knowledge, which one is not entirely confident will be useful in providing a practical solution, but which one has reason to believe will be useful and which is added to a problem-solving system in expectation that on average the performance will improve.

In the context of this dissertation, the above definition holds, but can be more clearly specified such that a heuristic refers to an algorithmic search technique that serves as a guide to a search process where some good-performing candidate solution to a optimisation problem is being sought out. Different heuristics make use of different information during the search process \cite{ref:kheiri:2017}. Heuristics such as gradient-based techniques make use of the derivatives obtained by evaluating the \ac{ANN} and thus it can be said that they make use of information directly from the \textit{search space}. On the contrary, heuristics such as meta-heuristics make use of meta-information obtained as a result of evaluating the \ac{FFNN} \cite{ref:blum:2003}. This could be the ranked-performance of a population of candidate solutions, referred to as \textit{entities}. Meta-heuristics are useful when there is imperfect information about the search space \cite{ref:bianchi:2009} and are generally less problem-specific than other heuristic techniques \cite{ref:blum:2003}.

In order to understand the application of heuristics, consider first the concept of optimisation and how that relates to training \acp{FFNN}.

\section{Optimisation}
\label{sec:heuristics:optimisation}

Optimisation is the task of finding a solution to a given problem that is better than alternative solutions. Better stated by Oldewage \cite{ref:oldewage:2017}, optimisation is the task of finding values for a set of variables such that some measure of optimality is satisfied given a set of constraints. Engelbrecht \cite{ref:engelbrecht:2007} breaks optimisations problems down into three components:

\begin{itemize}
  \item An \textbf{objective function}: Represents the quantity to be optimised and is used as the ``measure of optimality''. Optimisation can be defined in terms of the minimisation or maximisation of the objective function $f$.

  \item A \textbf{set of unknowns or independent variables}: These affect the outcome of the objective function $f$ and is denoted as $x$. $f(x)$ is thus the quantification of the objective function over the unknowns $x$.

  \item A \textbf{set of constraints}: These restrict and limit the values that can be assigned to the unknowns $x$. Optimisation problems that contain must adhere to a set of constraints are referred to as \acp{CSP}.
\end{itemize}

The goals of heuristics is to find a set of valid values for $x$ that optimises the objective function while adhering to a set of constraints. Heuristics thus search for solutions, referred to as candidate solutions, in a set of all possible and valid solutions, referred to as the \textit{feasible search space}.

Optimisation problems come in a wide variety of forms. Mostly these functions are defined in terms of the number of variables used (uni- vs. multivariate), the number of objective functions used (single- vs. multi-objective), the degree of linearity (linear vs. quadratic/polynomial), the number of optima (uni- vs. multi-modal), the nature of the environment (static vs. dynamic), the types of variables used (separable vs. inseparable, discrete vs. continuous) and  the set of constraints that the solution has to adhere to (constrained vs unconstrained).

Optima can be defined as local or global optima. Local optima is the best optimisation of $f(x)$ in a neighbourhood of solutions, while the global optima is the best optimisation of $f(x)$ over all solutions in the solution space.

From the components of optimisation that was presented above, it can be said that the training process of an \ac{FFNN} is an optimisation problem. Consider the relationship between optimisation and supervised training of \acp{FFNN} as follows. During training, the \ac{FFNN} is evaluated by means of a loss/cost function as was presented in Chapter \ref{chap:anns}. In the context of optimisation, this loss/cost function is the object function to be minimised. For supervised learning specifically, it was mentioned that a training dataset is used to train the \ac{FFNN}. The inputs to the \ac{ANN} would be these training samples and thus serves the role of independent variables in the context of optimisation. The output of the \ac{ANN} is directly influenced by the \ac{ANN} model parameters, called the \textit{weights} of the network and is thus referred to as the dependent variables. Finally, the goal of training \acp{ANN} is to find the configuration of \textit{weights} such that the performance of the \ac{ANN} is optimal.

The following sections present the various types of heuristics that are of concern to this dissertation and the implementation of the \ac{BHH}.

\section{Gradient-Based Heuristics}
\label{sec:heuristics:gd}

Gradient-based techniques are optimisation technique that makes use of the evaluated gradients of a model in order to optimise the model. Specifically in the context of a minimisation problem, these techniques are called gradient-\textit{descent} heuristics as they minimise the loss/cost function. \Ac{GD} is generally attributed to Cauchy \cite{ref:lemarechal:2012}, who first suggested it in 1847. In 1907 Hadamard \cite{ref:hadamard:1908} independently proposed a similar method.

Although \ac{GD} techniques where not the first techniques used to train \ac{FFNN} 
\cite{ref:engelbrecht:2007}, they are certainly the most popular. \Ac{GD} techniques have become increasingly popular partly due to their simplicity, but mostly due to their low computational overhead compared to other techniques such as meta-heuristics and other second-order derivative methods such as Newtons' method. There are many variants of this technique, however, they all fundamentally apply the same generic \ac{GD} framework called \acl{BP}. The \ac{BP} framework is provided next and all the other gradient-based techniques that follow are built upon this idea.

\subsection{Backpropagation}
\label{sec:heuristics:gd:backpropagation}

\Ac{GD} techniques require the definition of some error function. In the context of training \acp{FFNN}, this error function is referred to as a loss/cost function. Consider the definition of the \ac{SSE} was given in Chapter\ref{algo:bhh} and is presented in Equation \ref{eq:heuristics:gd:sse} below for convenience.

\begin{equation}
    \label{eq:heuristics:gd:sse}
    \epsilon = \sum^{P_{T}}_{p=1}(t_{p} - o_{p})^{2}
\end{equation}

In Equation \ref{eq:heuristics:gd:sse}, $t_{p}$ and $o_{p}$ denote the target and ground truth output for the $p$-th training sample/pattern. $P_{t}$ is the total number of input-target vector pairs in the training set \cite{ref:engelbrecht:2007}.

The aim of \ac{GD} is then to find some candidate solution for the weights of the \ac{FFNN} that minimises the error $\epsilon$. \citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} states that this is done by calculating the gradient of $\epsilon$ in \textit{weight-space} and to move the weight vector along the negative gradient. An illustration of this is given in Figure \ref{fig:heuristics:gd:gd_illustration}.

\begin{figure}[htbp]
    \includegraphics[width=\textwidth]{images/gradient_descent.png}
    \caption{An illustration of \ac{GD} over various timestep showing the minimisation of the error with regard to weight value.}
    \label{fig:heuristics:gd:gd_illustration}
\end{figure}

The update-step for \ac{GD} can then be formulated as is shown in Equations \ref{eq:heuristics:gd:update_step_part_1}-\ref{eq:heuristics:gd:update_step_part_3} below.

\begin{equation}
    \label{eq:heuristics:gd:update_step_part_1}
    w_{i}(t) = w_{i}(t-1) + \Delta w_{i}(t)
\end{equation}

where

\begin{equation}
    \label{eq:heuristics:gd:update_step_part_2}
    \Delta w_{i}(t) = -\eta\frac{\partial \epsilon}{\partial w_{i}}
\end{equation}

and

\begin{equation}
    \label{eq:heuristics:gd:update_step_part_3}
    \frac{\partial \epsilon}{\partial w_{i}} = -2(t_{p} - o_{p})\frac{\partial f}{\partial net_{p}}z_{i,p}
\end{equation}

In Equation \ref{eq:heuristics:gd:update_step_part_2}, $\eta$ is the learning rate. The learning rate is an important hyper-parameter in the \ac{GD} heuristic as it controls the step-size that is taken in the direction of the negative gradient at each timestep.

In the context of \ac{FFNN} training, this error signal is propagated backwards in the network. This algorithm is known as \ac{BP} and was popularised by \citeauthor{ref:werbos:1994} \cite{ref:werbos:1994}. \citeauthor{ref:nel:2021} \cite{ref:nel:2021} states that \ac{BP} provides a procedure for updating the network weights by evaluating the derivatives of the error function $\epsilon$ with respect to the weights. \Ac{BP} consists out of the two phases \cite{ref:engelbrecht:2007}. These include:

\begin{itemize}
    \item \textbf{Feedforward Pass}: During this phase the the output values if calculcated for the \ac{FFNN} for each training pattern.
    \item \textbf{Backward Propagation}: During this phase the error signal that is calculated as is shown above in Equations \ref{eq:heuristics:gd:update_step_part_1}-\ref{eq:heuristics:gd:update_step_part_3} is propagated backwards from the output layer to the input layer of the \ac{FFNN}. Weights are then adjusted as functions of the backpropagated error signal.
\end{itemize}

From the concepts mentioned above, the full \ac{BP} process for training \acp{FFNN} can be formulated. \citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} presents such an example and is given next.

\subsubsection*{Backpropogation of Feedforward Neural Networks}

In order to present the example for \ac{BP} as applied to \acp{FFNN}, a number of assumptions are made. These include:

\begin{itemize}
    \item The \ac{SSE} is used as the objective function.
    \item The sigmoid activation function is used in both the input and output layers.
    \item Biases are included through augmented vectors as was presented in Chapter \ref{chap:anns}
    \item \Acp{SU} are used in the input and output layers.
    \item Stochastic learning is used where a small subset of the training patterns, called a \textit{mini-batch}, is presented at a time (\ac{SGD} is discussed in further detail later in Section \ref{sec:heuristics:gd:sgd}).
\end{itemize}

Then, for each training pattern $z_{p}$ the output of the objective function is given in Equation \ref{eq:heuristics:gd:bp:sse} below.

\begin{equation}
    \label{eq:heuristics:gd:bp:sse}
    \epsilon_{p} = \frac{1}{2}\left(\frac{\sum^{K}_{k=1}(t_{k,p} - o_{k,p})^{2}}{K}\right)
\end{equation}

In Equation \ref{eq:heuristics:gd:bp:sse}, $K$ represents the number of output units and $t_{k,p}$ and $o_{k,p}$ are respectively the target and output values of the $k$-th output unit.

The rest of the derivations are presented only for a single pattern. The subscript $p$ is thus omitted for convenience. The output of each layer is given as

\begin{equation}
    \label{eq:heuristics:gd:bp:output_1}
    o_{k} = f_{o_{k}}(net_{o_{k}}) = \frac{1}{1 + e^{-net_{o_{k}}}}
\end{equation}

and

\begin{equation}
    \label{eq:heuristics:gd:bp:output_2}
    y_{k} = f_{y_{k}}(net_{y_{k}}) = \frac{1}{1 + e^{-net_{y_{k}}}}
\end{equation}

The weights of the \ac{FFNN} are then updated according to Equations \ref{eq:heuristics:gd:bp:output_hto} and \ref{eq:heuristics:gd:bp:output_ith} below.

\begin{equation}
    \label{eq:heuristics:gd:bp:output_hto}
    w_{kj}(t) \hspace{3mm} += \hspace{3mm} \Delta w_{kj}(t) + \alpha \Delta w_{kj}(t - 1)
\end{equation}

\begin{equation}
    \label{eq:heuristics:gd:bp:output_ith}
    v_{ji}(t) \hspace{3mm} += \hspace{3mm} \Delta v_{ji}(t) + \alpha \Delta v_{ji}(t - 1)
\end{equation}

In Equations \ref{eq:heuristics:gd:bp:output_hto} and \ref{eq:heuristics:gd:bp:output_ith} $\alpha$ represents the \textit{momentum} and is discussed in more detail later in Section \ref{sec:heuristics:gd:momentum}. The remainder of the derivations are focused on calculating $\Delta w_{kj}(t)$ and $\Delta v_{ji}(t)$. As such, the reference to time $(t)$ is omitted for convenience.

From Equation \ref{eq:heuristics:gd:bp:output_hto} it follows that

\begin{equation}
    \label{eq:heuristics:gd:bp:partial_output}
    \frac{\partial o_{k}}{\partial net_{o_{k}}} = \frac{\partial f_{o_{k}}}{\partial net_{o_{k}}} = (1 - o_{k})o_{k} = f'_{o_{k}} 
\end{equation}

and

\begin{equation}
    \label{eq:heuristics:gd:bp:partial_hidden}
    \frac{\partial net_{o_{k}}}{\partial w_{kj}} = \frac{\partial}{\partial w_{jk}}\left( \sum^{J+1}_{j=1}w_{kj}y_{j}\right) = y_{j}
\end{equation}

In Equation \ref{eq:heuristics:gd:bp:partial_output} $f'_{o_{k}}$ represents the derivative of the corresponding activation function. From Equations \ref{eq:heuristics:gd:bp:partial_output} and \ref{eq:heuristics:gd:bp:partial_hidden}, using the chain-rule, it follows that

\begin{equation}
    \label{eq:heuristics:gd:bp:partial_output_hidden}
    \begin{split}
        \frac{\partial o_{k}}{\partial w_{kj}}
        &= \frac{\partial o_{k}}{\partial net_{o_{k}}}\frac{\partial net_{o_{k}}}{\partial w_{kj}}\\
        &= (1 - o_{k})o_{k}y_{j}\\
        &= f'_{o_{k}}y_{j}
    \end{split}
\end{equation}

From Equation \ref{eq:heuristics:gd:bp:sse} it follows that

\begin{equation}
    \label{eq:heuristics:gd:bp:partial_error}
    \frac{\partial \epsilon}{\partial o_{k}} = \frac{\partial}{\partial o_{k}}\left( \frac{1}{2} \sum^{K}_{k=1}(t_{k} - o_{k})^{2} \right) = -(t_{k} - o_{k})
\end{equation}

Define the error signal that needs to be back-propagated as $\delta_{o_{k}} = \frac{\partial \epsilon}{\partial net_{o_{k}}}$. Then, from Equations \ref{eq:heuristics:gd:bp:partial_output} and \ref{eq:heuristics:gd:bp:partial_error} it follows that

\begin{equation}
    \label{eq:heuristics:gd:bp:delta_output}
    \begin{split}
        \delta_{o_{k}}
        &= \frac{\partial \epsilon}{\partial net_{o_{k}}}\\
        &= \frac{\partial \epsilon}{\partial o_{k}}\frac{\partial o_{k}}{\partial net_{o_{k}}}\\
        &= -(t_{k} - o_{k})(1 - o_{k})o_{k}\\
        &= -(t_{k} - o_{k})f'_{o_{k}}
    \end{split}
\end{equation}

The changes in the hidden-to-output weights are then computed from Equations \ref{eq:heuristics:gd:bp:partial_output_hidden}, \ref{eq:heuristics:gd:bp:partial_error} and \ref{eq:heuristics:gd:bp:delta_output} as follows.

\begin{equation}
    \label{eq:heuristics:gd:bp:delta_hidden_to_output}
    \begin{split}
        \Delta w_{kj}
        &= \eta \left( - \frac{\partial \epsilon}{\partial w_{kj}} \right)\\
        &= -\eta \frac{\partial \epsilon}{\partial o_{k}}\frac{\partial o_{k}}{\partial w_{kj}}\\
        &= -\eta \delta_{o_{k}}y_{j}
    \end{split}
\end{equation}

Continuing on with the input-to-hidden weights as follows

\begin{equation}
    \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_1}
    \begin{split}
        \frac{\partial y_{j}}{\partial net_{y_{j}}}
        &= \frac{\partial f_{y_{j}}}{\partial net_{y_{j}}}\\
        &= (1 - y_{j})y_{j}\\
        &= f'_{y_{j}}
    \end{split}
\end{equation}

and

\begin{equation}
    \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_2}
    \begin{split}
        \frac{\partial net_{y_{j}}}{\partial v_{ji}}
        &= \frac{\partial}{\partial v_{ji}}\left( \sum^{I+1}_{i=1}v_{ji}z_{i}\right)\\
        &= z_{i}
    \end{split}
\end{equation}

From Equations \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_1} and \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_2} it follows that

\begin{equation}
    \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_3}
    \begin{split}
        \frac{\partial y_{j}}{\partial v_{ji}}
        &= \frac{\partial y_{j}}{\partial net_{y_{j}}}\frac{\partial net_{y_{j}}}{\partial v_{ji}}\\
        &= (1 - y_{j})y_{j}z_{i}\\
        &= f'_{y_{j}}z_{i}
    \end{split}
\end{equation}

and

\begin{equation}
    \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_4}
    \begin{split}
        \frac{\partial net_{o_{k}}}{\partial y_{j}}
        &= \frac{\partial}{\partial y_{j}}\left( \sum^{J+1}_{j=1}w_{kj}y_{j}\right)\\
        &= w_{kj}
    \end{split}
\end{equation}

From Equations \ref{eq:heuristics:gd:bp:delta_hidden_to_output} and \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_4} it follows that

\begin{equation}
    \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_5}
    \begin{split}
        \frac{\partial \epsilon}{\partial y_{j}}
        &= \frac{\partial}{\partial y_{j}}\left( \frac{1}{2} \sum^{K}_{k=1} (t_{k} - o_{k})^{2} \right)\\
        &= \sum^{K}_{k=1}\frac{}{} \frac{\partial \epsilon}{\partial o_{k}} \frac{\partial o_{k}}{\partial net_{o_{k}}} \frac{\partial net_{o_{k}}}{\partial y_{j}}\\
        &= \sum^{K}_{k=1} \frac{\partial \epsilon}{\partial net_{o_{k}}} \frac{\partial net_{o_{k}}}{\partial y_{j}}\\
        &= \sum^{K}_{k=1} \delta_{o_{k}}w_{kj}
    \end{split}
\end{equation}

Define the hidden layer error which needs to be back-propagated from Equations \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_1} and \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_5} as

\begin{equation}
    \label{eq:heuristics:gd:bp:delta_hidden}
    \begin{split}
        \delta_{y_{j}}
        &= \frac{\partial \epsilon}{\partial net_{y_{j}}}\\
        &= \frac{\partial \epsilon}{\partial y_{j}} \frac{\partial y_{j}}{\partial net_{y_{j}}}\\
        &= \sum^{K}_{k=1}\delta_{o_{k}}w_{kj}f'_{y_{j}}
    \end{split}
\end{equation}

Finally, the changes to the input-to-hidden weights can then be calculated from Equations \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_3}, \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_5} and \ref{eq:heuristics:gd:bp:delta_hidden} as follows

\begin{equation}
    \label{eq:heuristics:gd:bp:delta_input_to_hidden}
    \begin{split}
        \Delta v_{ji}
        &= \eta \left( - \frac{\partial \epsilon}{\partial v_{ji}} \right)\\
        &= -\eta \frac{\partial \epsilon}{\partial y_{j}} \frac{\partial y_{j}}{\partial v_{ji}}\\
        &= -\eta \delta_{y_{j}}z_{i}
    \end{split}
\end{equation}

If the \ac{FFNN} include direct weights from the input to output layer, the following additional weight updates are required.

\begin{equation}
    \label{eq:heuristics:gd:bp:delta_input_to_output}
    \begin{split}
        \Delta u_{ki}
        &= \eta \left( - \frac{\partial \epsilon}{\partial u_{ki}} \right)\\
        &= -\eta \frac{\partial \epsilon}{\partial o_{k}} \frac{\partial o_{k}}{\partial u_{ki}}\\
        &= -\eta \delta_{o_{k}}z_{i}
    \end{split}
\end{equation}

In Equation \ref{eq:heuristics:gd:bp:delta_input_to_output} above, $u_{ki}$ is a weight from the $i$-th input unit to the $k$-th output unit.

The derivations above assumed stochastic learning, however, if batch learning is applied, weight updates are given in Equations \ref{eq:heuristics:gd:bp:delta_hidden_to_output_batch_learning} and \ref{eq:heuristics:gd:bp:delta_input_to_hidden_batch_learning} below

\begin{equation}
    \label{eq:heuristics:gd:bp:delta_hidden_to_output_batch_learning}
    \begin{split}
        \Delta w_{kj}(t) = \sum^{P_{T}}_{p=1} \Delta w_{kj,p}(t)
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:heuristics:gd:bp:delta_input_to_hidden_batch_learning}
    \begin{split}
        \Delta v_{kj}(t) = \sum^{P_{T}}_{p=1} \Delta v_{kj,p}(t)
    \end{split}
\end{equation}

where $\Delta w_{kj}(t)$ and $\Delta v_{kj}(t)$ are weight updates for individual patterns $p$ and $P_{T}$ is the total number of patterns in the training set.

Equations \ref{eq:heuristics:gd:bp:sse} through \ref{eq:heuristics:gd:bp:delta_input_to_hidden} provided the reader with the detailed derivations of the \ac{BP} weight-update components as it resolves from the error signal. The following sections provide the reader with variants of the \ac{BP} algorithm as presented in this section.

\subsection{Stochastic Gradient Descent}
\label{sec:heuristics:gd:sgd}

Section \ref{sec:heuristics:gd:backpropagation} already assumed the use of stochastic learning and thus provided the detailed derivation of a specific variant of \ac{BP} called \acl{SGD}. Separation of theory and implementation is done such that the detail of the theory need not be repeated for each gradient-based variant. This section shines light on the algorithmic implementation of \ac{BP} with specific context to \ac{SGD}. The algorithm is provided followed by a simplification of the update-step that provides the basis for the next gradient-based heuristics that follow.

The pseudo-code implementation for the \ac{SGD} algorithm is taken from \cite{ref:engelbrecht:2007} and is presented in Algorithm \ref{algo:heuristics:gd:sgd} below.

\begin{algorithm}[H]
    \caption{The pseudo code algorithm for the \ac{SGD} heuristic.}
    \label{algo:heuristics:gd:sgd}
    \begin{algorithmic}
        \State Initialise weights, $\eta$, $\alpha$ and the number of epochs $t=0$;
        \While{stopping condition not met}
            let $\epsilon_{T} = 0$
            \For{each training pattern p}
                \State Do the feedforward pass phase to calculate $y_{j,p}$ ($\forall j = 1, \dots, J$) and $o_{k,p}$ ($\forall k = 1, \dots, K$);
                \State Compute the output error signals $\delta_{o_{k,p}}$ and the hidden layer error signals $\delta_{y_{j,p}}$;
                \State Adjust the weights $w_{kj}$ and $v_{ji}$ (backpropagation of errors);
                \State $\epsilon_{T}$ += $[\epsilon_{p} = \sum^{K}_{k=1}(t_{k,p} - o_{k,p})^{2}]$;
            \EndFor
            \State $t = t + 1$;
        \EndWhile
    \end{algorithmic}
\end{algorithm}

In order to provide a simplified frame of reference from which the gradient-based heuristics are compared, consider a simplification of the update-step for the weights of the \ac{FFNN} as is done using \ac{SGD} below.

\begin{equation}
    \label{eq:heuristics:gd:sgd}
    \begin{split}
        w = w - \eta \nabla_{w}\mathcal{E}(w)
    \end{split}
\end{equation}

In Equation \ref{eq:heuristics:gd:sgd} $w$ refers to the weights of the \ac{FFNN}, $\eta$ refers to the learning rate as before and $\nabla_{w}\mathcal{E}(w)$ refers to the gradient of the loss/cost function w.r.t the output of the \ac{FFNN} as a result of its weights. Note that all subscripts w.r.t. layers and training patterns are omitted for convenience.

So far detailed mathematical descriptions have been provided to illustrate the concept of \ac{GD} and how it applies to the \ac{SGD} heuristic as applied to \ac{FFNN} training. It was mentioned that \ac{SGD} was one of the first widely used heuristics to train \ac{FFNN}, however, it is not without flaws. With stochastic learning, only one training pattern is presented at each iteration. As such, weight updates are done with high variance and noise \cite{ref:ruder:2016}. An illustration of the the fluctuations caused by \ac{SGD} during training is given in Figure \ref{fig:heuristics:gd:sgd}.

\begin{figure}[htbp]
    \includegraphics[width=\textwidth]{images/sgd.png}
    \caption{An illustration of \ac{SGD} fluctuations during training as taken from \cite{ref:sgd:2006}.}
    \label{fig:heuristics:gd:sgd}
\end{figure}

With batch learning, all the training patterns are presented at once and the \ac{FFNN} converges to the minimum of the loss/cost function w.r.t $w$. However, this is computationally expensive and intractable to implement in many situations. While \ac{SGD} is able to jump out of local minima into new, potentially better local minima \cite{ref:ruder:2016}, it does at first this seems advantageous. However, this complicates convergence to the exact minima as \ac{SGD} can potentially keep overshooting better minima. It is shown that a slow decrease in the learning rate $\eta$ will lead to the same convergence behaviour as with batch learning, almost certainly converging to local or global minima for non-convex and convex optimisation respectively. A compromise to this problem is to include mini-batches of training patterns where a small number of training patterns are presented to the \ac{FFNN} at once. This means that the input patterns from mini-batches are just approximations of the total population of training patterns. According to \citeauthor{ref:ruder:2016} \cite{ref:ruder:2016} this has two main advantages

\begin{itemize}
    \item Reduces the high variance of weight updates which leads to better convergence
    \item Allows for the implementation of \ac{SGD} using highly optimised matrix operations, common to the state-of-the-art \ac{ML} libraries used today.
\end{itemize}

In the context of this dissertation, \ac{SGD} refers to the mini-batch learning implementation. Although mini-batch \ac{SGD} does provide a compromise between single-pattern and batch learning there are still a number of challenges posed by this approach. These include:

\begin{itemize}
    \item The appropriate value to use for the learning rate $\eta$ is difficult to determine and is often problem-specific. A learning rate that is too small causes premature exploitation, leading to slow and bad convergence. On the contrary, a learning rate that is too high may lead to bad learning outcomes as the heuristic keeps overshooting good minima.

    \item Learning rate schedules \cite{ref:robbins:1951} can be introduced to dynamically change the learning rate throughout the training process, however, these schedules and their parameters have to be defined a priori and are thus problem specific \cite{ref:darken:1992}.

    \item The learning rate that has been introduced so far is applied to all weight updates. If the training data is sparse and the features have very different frequencies an equal update to all weights is inefficient. Larger weight updates are required for less frequently occurring features. This problem eludes to the credit assignment problem \cite{ref:rumelhart:1986} common to these \ac{GD} variants.

    \item It is difficult to avoid getting trapped in local minima, especially for highly non-convex loss/cost functions used for \ac{ANN} training. \cite{ref:dauphin:2014} argues that this difficulty arises not from local minima, but from sadle points. Sadle points are points at which one dimensions slopes upwards while another dimension slopes downwards. \cite{ref:ruder:2016} mentions that these sadle points are usually surrounded by plateaus of the same error, leading to gradients that are close to zero in all dimensions.
\end{itemize}

Alternative methods have been proposed that lead to better control over the convergence characteristics caused by \ac{GD} variants. The first of these include \ac{Momentum} and is presented next.

\subsection{Momentum}
\label{sec:heuristics:gd:momentum}

Research shows that \ac{SGD} has difficulty navigating ravines i.e. areas where the surface curves much more steeply in one dimension than in another \cite{ref:sutton:1986}. These ravines are common around local minima. As such, \ac{SGD} is shown to oscillate across the slopes of the ravine while only making minor progress towards the local minima. An illustration of this is given in Figure \ref{fig:heuristics:gd:sgd_with_and_without_momentum}.

\begin{figure}[htbp]
    \includegraphics[width=\textwidth]{images/sgd_with_and_without_momentum.png}
    \caption{An illustration of \ac{SGD} with and without momentum taken from \cite{ref:du:2019}.}
    \label{fig:heuristics:gd:sgd_with_and_without_momentum}
\end{figure}

Momentum \cite{ref:qian:1999} is a variant of the \ac{SGD} that helps accelerate \ac{SGD} in the relevant direction, dampening oscillations. \cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$ of the weight update vector of the previous timestep to the current weight update vector. The accumulation of momentum is presented in Equation \ref{eq:heuristics:gd:momentum_part_1} while the update step is then amended in Equation \ref{eq:heuristics:gd:momentum_part_2} below.

\begin{equation}
    \label{eq:heuristics:gd:momentum_part_1}
    \begin{split}
        v_{t} = \alpha v_{t-1} + \eta \nabla_{w}\mathcal{E}(w)
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:heuristics:gd:momentum_part_2}
    \begin{split}
        w = w - v_{t}
    \end{split}
\end{equation}

By redefining the \ac{SGD} update steps as shown above, the \ac{Momentum} heuristic allows for the increase of momentum for dimensions whose gradients point in the same direction, while simultaneously reducing momentum for dimensions whose gradients change direction, leading to faster convergence and less oscillation. The momentum term $\alpha$ is usually set to 0.9 \cite{ref:engelbrecht:2007}\cite{ref:ruder:2016}.

\subsection{Nesterov Accelerated Gradients}
\label{sec:heuristics:nag}

\Acl{NAG} is a variant of the \ac{Momentum} heuristics developed by Ilya Sutskever \cite{ref:sutskever:2013-2} and is inspired from Yurii Nesterov's \cite{ref:nesterov:1983} work on optimising convex functions. \ac{NAG} provides an improvement to the momentum accumulation term by providing a look-ahead term that better refines the weight update step. In the \ac{NAG} heuristic, the gradient is not calculated w.r.t the current weights, but rather w.r.t the approximate future positions of the weights \cite{ref:ruder:2016}. An illustration of this is taken from Geoffrey Hinton's lecture on mini-batch \ac{GD} \cite{ref:hinton:2012} and is presented in Figure \ref{fig:heuristics:gd:nag} below.

\begin{figure}[htbp]
    \includegraphics[width=\textwidth]{images/nag.png}
    \caption{An illustration of the weight update vector for \ac{NAG} taken from \cite{ref:hinton:2012}.}
    \label{fig:heuristics:gd:nag}
\end{figure}

\citeauthor{ref:ruder:2016} \cite{ref:ruder:2016} explains the update step as is done by \ac{NAG} is follows. \ac{Momentum} first computes the current gradient. This is seen by the small blue vector presented in Figure \ref{fig:heuristics:gd:nag}. A large step is taken in the direction of the updated accumulated gradient, presented by the big blue vector. \ac{NAG} then first takes a big step in the direction of the previous accumulated gradient presented by the brown vector. At this point the gradient is measured and \ac{NAG} then makes a correction (red vector), which results in the complete NAG update (green vector). By anticipating approximate future positions of the weights, the weight update step as defined by \ac{NAG} controls the optimisation process from from going too fast and results in increased responsiveness. The \ac{NAG} weight vector update steps are given in Equations \ref{eq:heuristics:gd:nag_part_1} and \ref{eq:heuristics:gd:nag_part_2} below.

\begin{equation}
    \label{eq:heuristics:gd:nag_part_1}
    \begin{split}
        v_{t} = \alpha v_{t-1} + \eta \nabla_{w}\mathcal{E}(w - \alpha v_{t-1})
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:heuristics:gd:nag_part_2}
    \begin{split}
        w = w - v_{t}
    \end{split}
\end{equation}

The next logical step in the improvement of the weight vector update step is to tailor the update steps for each weight parameter controlling the magnitude of the update step based on the relevance and importance for that dimension.

\subsection{Adaptive Gradients}
\label{sec:heuristics:adagrad}

\Acl{Adagrad} is an adaptation of \ac{SGD} which implements a learning rate for every parameter in the weight vector and is developed by Duchi et al. \cite{ref:duchi:2011}. \citeauthor{ref:ruder:2016} \cite{ref:ruder:2016} mentions that \Ac{Adagrad} adapts the learning rate to the weights, performing small updates (i.e. low learning rates) for weights associated with frequently occurring features and larger updates (i.e. high learning rates) for weights associated with infrequent features. For this reason \ac{Adagrad} is well suited for dealing with situations with very sparse training data.

In the \ac{GD} variants presented thus far, the weight updates have been applied to all weights at once using the same learning rate $\eta$ for all dimensions of the weight update vector. \Ac{Adagrad} uses a different learning rate for every weight $w_{i}$ at every timestep $t$. The weight update step as implemented by \ac{Adagrad} is presented in Equation \ref{eq:heuristics:gd:adagrad_part_1} below.

\begin{equation}
    \label{eq:heuristics:gd:adagrad_part_1}
    \begin{split}
        w_{t+1,i} = w_{t,i} - \frac{\eta}{\sqrt{G_{t,ii} + \epsilon}}.\nabla_{w_{i}}\mathcal{E}(w_{t,i})
    \end{split}
\end{equation}

where $w_{i}$ is the $i$-th dimension of the weight vector, $G_{ii} \in \mathbb{R}^{d \times d}$ is a diagonal matrix where each diagonal element $i,i$ is the sum of the squared of the gradients w.r.t. $w_{i}$ up to timestep $t$ and $\epsilon$ is a smoothing term that avoids division by zero, usually set in the order of $1 \times 10^{-8}$ \cite{ref:ruder:2016}. Since $G_{t}$ contains the sum of the squares of the gradients with respect to all parameters $w$ along its diagonal, the weight update step can be vectorised and updated using the matrix-vector product between $G_{t}$ and $\nabla_{w_{i}}\mathcal{E}(w_{i})$. This is presented in Equation \ref{eq:heuristics:gd:adagrad_part_2} below.

\begin{equation}
    \label{eq:heuristics:gd:adagrad_part_2}
    \begin{split}
        w_{t+1} = w_{t} - \frac{\eta}{\sqrt{G_{t} + \epsilon}} \odot \nabla_{w_{i}}\mathcal{E}(w_{t})
    \end{split}
\end{equation}

\Ac{Adagrad}'s main benefit is that it does not require the need to manually tune the learning rate. However, a problem with \ac{Adagrad} is the accumulation of the sums of squared gradients in the denominator. Since every term that is added is positive, this number keeps growing, leading to a situation where the learning rate shrinks to the point that the heuristic is no longer able to learn. \acl{Adadelta} aims to improve on this problem.

\subsection{Adaptive Learning Rate}
\label{sec:heuristics:adadelta}

In Section \ref{sec:heuristics:adagrad} it was mentioned that one of the main problems of \ac{Adagrad} is that it has an aggressively monotonically decreasing learning rate because of the accumulation of the sum of squared gradients in its denominator. Zeiler \cite{ref:zeiler:2012} presents an improvement on \ac{Adagrad} that eliminates this problem. \citeauthor{ref:ruder:2016} \cite{ref:ruder:2016} mentions that instead of accumulating all past squared gradients as in the case of \ac{Adagrad}, \ac{Adadelta} restricts the window of accumulation to a window with a fixed size $W$. However, storing $W$ previous squared gradients is very inefficient. Instead, the accumulation of the sum of gradients over $W$ steps is defined recursively as a decaying average of all past squared gradients. The moving average $E[g^{2}]_{t}$ at timestep $t$ then depends only a fraction $\alpha$ of the previous average and current gradient, similar to the update step for \ac{Momentum}. In order to simplify the notation of update steps, let $g = \nabla_{w_{i}}\mathcal{E}(w_{t})$. The moving average update step for $E[g^{2}]_{t}$ is then presented in Equation \ref{eq:heuristics:gd:adadelta_part_1} below.

\begin{equation}
    \label{eq:heuristics:gd:adadelta_part_1}
    \begin{split}
        E[g^{2}]_{t} = \alpha E[g^{2}]_{t - 1} + (1 - \alpha)g_{t}^{2}
    \end{split}
\end{equation}

The value for $\alpha$ is set to a similar value, 0.9, as was done with \ac{Momentum}. For sake of clarity, the basic \ac{SGD} update step is rewritten in terms of the weight update vector $\Delta w_{t}$. This is presented in Equations \ref{eq:heuristics:gd:adadelta_part_2} and \ref{eq:heuristics:gd:adadelta_part_2} below.

\begin{equation}
    \label{eq:heuristics:gd:adadelta_part_2}
    \begin{split}
        \Delta w_{t} = -\eta g_{t,i}
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:heuristics:gd:adadelta_part_3}
    \begin{split}
        w_{t+1} = w_{t} + \Delta w_{t}
    \end{split}
\end{equation}

The weight update vector for \ac{Adagrad} as defined in Equation \ref{eq:heuristics:gd:adagrad_part_2} is then rewritten as

\begin{equation}
    \label{eq:heuristics:gd:adagrad_part_2_new}
    \begin{split}
        \Delta w_{t} = - \frac{\eta}{\sqrt{G_{t} + \epsilon}} \odot g_{t}
    \end{split}
\end{equation}

The diagonal matrix $G_{t}$ is then replaced with the decaying average over the past $W$ squared gradients as presented in Equation \ref{eq:heuristics:gd:adadelta_part_4} below.

\begin{equation}
    \label{eq:heuristics:gd:adadelta_part_4}
    \begin{split}
        \Delta w_{t} = - \frac{\eta}{\sqrt{E[g^{2}]_{t} + \epsilon}} g_{t}
    \end{split}
\end{equation}

Since the denominator is the \ac{RMS} error criterion of the gradient, the criteria short-hand notation is used as follows.

\begin{equation}
    \label{eq:heuristics:gd:adadelta_part_5}
    \begin{split}
        \Delta w_{t} = - \frac{\eta}{RMS[g]_{t}} g_{t}
    \end{split}
\end{equation}

\citeauthor{ref:ruder:2016}\cite{ref:ruder:2016} highlights that the original authors \cite{ref:zeiler:2012} noted that the units of the update step as presented in Equation \ref{eq:heuristics:gd:adadelta_part_2} do not match i.e. the update vector should have the same hypothetical units as the weight vector. To realize this, another exponentially decaying average is defined in terms of squared weight updates as is presented in Equation \ref{eq:heuristics:gd:adadelta_part_6} below.

\begin{equation}
    \label{eq:heuristics:gd:adadelta_part_6}
    \begin{split}
        E[\Delta w^{2}]_{t} = \alpha E[\Delta w^{2}]_{t - 1} + (1 - \alpha)\Delta w^{2}
    \end{split}
\end{equation}

The \ac{RMS} error of weight updates is thus

\begin{equation}
    \label{eq:heuristics:gd:adadelta_part_7}
    \begin{split}
        RMS[\Delta w]_{t} = \sqrt{E[\Delta w^{2}]_{t} + \epsilon}
    \end{split}
\end{equation}

Note that $RMS[\Delta w]_{t}$ is unknown at timestep $t$. It is thus approximated with the \ac{RMS} of weight updates until the previous timestep. The learning rate in Equation \ref{eq:heuristics:gd:adadelta_part_5} is then replaced as follows.

\begin{equation}
    \label{eq:heuristics:gd:adadelta_part_8}
    \begin{split}
        \Delta w_{t} = - \frac{RMS[\Delta w]_{t-1}}{RMS[g]_{t}} g_{t}
    \end{split}
\end{equation}

Finally, the weight update step for \ac{Adadelta} is concluded as follows.

\begin{equation}
    \label{eq:heuristics:gd:adadelta_part_9}
    \begin{split}
        w_{t+1} = w_{t} + \Delta w_{t}
    \end{split}
\end{equation}

The main advantage of \ac{Adadelta} is that one does not have to provide a default learning rate a priori as it is no longer included in the weight update step.

\subsection{Root Mean Squared Error Propagation}
\label{sec:heuristics:rmsprop}

\Ac{RMSProp} is a similar heuristic to \ac{Adadelta} presented by Geoffrey Hinton \cite{ref:hinton:2012} and was developed independently around the same time. \citeauthor{ref:ruder:2016}\cite{ref:ruder:2016} mentions that \ac{RMSProp} is in fact the same as the first weight update vector as defined for \ac{Adadelta}. The update step for \ac{RMSProp} is then defined in terms of a decaying running average of gradients squared as is presented again for convenience in Equations \ref{eq:heuristics:gd:rmsprop_part_1} and \ref{eq:heuristics:gd:rmsprop_part_2} below.

\begin{equation}
    \label{eq:heuristics:gd:rmsprop_part_1}
    \begin{split}
        E[g^{2}]_{t} = \alpha E[g^{2}]_{t - 1} + (1 - \alpha)g_{t}^{2}
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:heuristics:gd:rmsprop_part_2}
    \begin{split}
        w_{t+1} = w_{t} - \frac{\eta}{\sqrt{E[g^{2}]_{t} + \epsilon}} g_{t}
    \end{split}
\end{equation}

Note that \ac{RMSProp} still includes the learning rate term $\eta$ meaning that a default learning rate is required a priori. This is one of the disadvantages of \ac{RMSProp}. Hinton suggests $\alpha$ be set to 0.9 and $\eta$ be set to $0.001$ \cite{ref:hinton:2012}.

\subsection{Adaptive Moments Estimation}
\label{sec:heuristics:adam}

\Ac{Adam} is another variant of \ac{SGD} that includes adaptive learning rates and is presented by Kingma et. al \cite{ref:kingma:2014}. However, in addition to storing an exponentially decaying average of past squared gradients like \ac{Adadelta} and \ac{RMSProp}, \ac{Adam} also stores an exponentially decaying average of past gradients $v_{t}$, similar to \ac{Momentum} \cite{ref:ruder:2016}. \citeauthor{ref:heusel:2017} \cite{ref:heusel:2017} uses the analogy that \ac{Momentum} can be seen as a ball running down a slope, while \ac{Adam} behaves like a heavy ball with friction, which thus prefers flat minima in the error surface.

The decaying averages for past gradients and past squared gradients is given in Equations \ref{eq:heuristics:gd:adam_part_1} and \ref{eq:heuristics:gd:adam_part_2} respectively.

\begin{equation}
    \label{eq:heuristics:gd:adam_part_1}
    \begin{split}
        m_{t+1} = \beta_{1}m_{t} + (1 - \beta_{1})g_{t}
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:heuristics:gd:adam_part_2}
    \begin{split}
        v_{t+1} = \beta_{2}v_{t} + (1 - \beta_{2})g^{2}_{t}
    \end{split}
\end{equation}

In Equations \ref{eq:heuristics:gd:adam_part_1} and \ref{eq:heuristics:gd:adam_part_2} above, $\beta_{1}$ and $\beta_{2}$ are decay rates, similar to $\alpha$ for \ac{Momentum}.

\citeauthor{ref:ruder:2016} \cite{ref:ruder:2016} mentions that $v_{t}$ and $w_{t}$ presented above are estimates of the first moment (the mean) and the second moment (the uncentered variance) of the gradients respectively. It is from these moment terms that the name \acl{Adam} is derived. \citeauthor{ref:kingma:2014} \cite{ref:kingma:2014} mentions that because $v_{t}$ and $w_{t}$ is initialised to be vectors of 0's, they are biased towards 0. This is especially true during the initial timesteps and/or when the decay rates $\beta_{1}$ and $\beta_{2}$ are small (i.e. $\beta_{1}$ and $\beta_{2}$ is close to 1). These biases need to be corrected. The bias-corrected first and second moment estimates are presented in Equations \ref{eq:heuristics:gd:adam_bc_first_moment} and \ref{eq:heuristics:gd:adam_bc_second_moment} below.

\begin{equation}
    \label{eq:heuristics:gd:adam_bc_first_moment}
    \begin{split}
        \hat{m}_{t} = \frac{m_{t}}{1 - \beta^{t}_{1}}
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:heuristics:gd:adam_bc_second_moment}
    \begin{split}
        \hat{v}_{t} = \frac{v_{t}}{1 - \beta^{t}_{2}}
    \end{split}
\end{equation}

The \ac{Adam} update rule is then presented in Equation \ref{eq:heuristics:gd:adam} below.

\begin{equation}
    \label{eq:heuristics:gd:adam}
    \begin{split}
        w_{t+1} = w_{t} - \frac{\eta}{\sqrt{\hat{v}_{t}} + \epsilon}\hat{m}_{t}
    \end{split}
\end{equation}

\citeauthor{ref:kingma:2014} \cite{ref:kingma:2014} suggest default values $B_{1}=0.9$, $B_{2}=0.999$ and $\epsilon = 1 \times 10^{-8}$. This section provided the reader with a collection of gradient-based heuristics. The next section introduces meta-heuristics.

\section{Meta-Heuristics}
\label{sec:heuristics:mh}

Gradient-based methods are sensitive to the type of problem that they it applied to, with hyper-parameter selection often dominating the research focus \cite{ref:bengio:2000}\cite{ref:feurer:2019}. In the context of \acp{HH}, it is important to consider a diverse set of low-level heuristics to select from. Apart from gradient-based methods, alternative heuristics must thus be considered. \cite{ref:blum:2003} mentions since the 1980's, a new kind of approximate algorithm has emerged which basically tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space. These methods referred to as metaheuristics. This section aims to introduce the reader to the concept of meta-heuristics. Specifically, this section focuses on population-based meta-heuristics. Three well known meta-heuristics are presented. Each of these have been shown to train \ac{FFNN}. These meta-heuristics include \ac{PSO}, \ac{DE} and \acp{GA}. \cite{ref:carvalho:2006} compared various \ac{PSO} variants for training \acp{FFNN}. \cite{ref:espinal:2011} compared \ac{DE} and \ac{PSO} when applied to \ac{FFNN} training and \cite{ref:gupta:1999} compared \ac{BP} to a \ac{GA} for training \acp{FFNN}.

A formal definition for meta-heuristics is required. The term \aclp{MH} was first introduced by \citeauthor{ref:glover:1986}\cite{ref:glover:1986} in 1986. The world derives from the composition of two Greek words. Heuristic derives from the verb \textit{heuriskein} which means ``to find''. The suffix, \textit{meta} means ``beyond, in an upper level''. Before this term was widely adopted, \acp{MH} were often called \textit{modern heuristics} \cite{ref:reeves:1993}. \cite{ref:blum:2003} mentions that there is a debate as to what the formal defintion of \acp{MH} is and suggests the definition of \acp{MH} to be high level strategies for exploring search spaces by using different methods. \citeauthor{ref:blum:2003} \cite{ref:blum:2003} provides characterists of meta-heuristics. These characterists are given as follows.

\begin{itemize}
    \item \ac{MH} are strategies to guide the search process.

    \item The goal of \acp{MH} is to efficiently explore the search space in order to find (near) optimal solutions.

    \item Techniques that constitute \ac{MH} algorithms range from simple local search to complex learning processes.

    \item \ac{MH} algorithms are approximate and usually non-deterministic.

    \item \acp{MH} may incorporate some mechanism to avoid getting trapped in local minima.

    \item The basic concept of \acp{MH} permit an abstract level description.

    \item \acp{MH} are not problem-specific.

    \item \acp{MH} may make use of domain-specific knowledge  in the form of heuristics that are controlled by the upper level strategy.

    \item Today's more advanced \acp{MH} use search experience (embodied in some form of memory) to guide the search/optimisation process.
\end{itemize}

\citeauthor{ref:blum:2003} \cite{ref:blum:2003} proposes the classification of heuristics as follows:

\begin{itemize}
    \item Nature inspired vs. non-nature inspired.
    \item Population-based vs. single point search.
    \item Dynamic vs. statis objective functions.
    \item One vs. various neighbourhood structures.
    \item Memory usage vs. memory-less methods.
\end{itemize}

The first of these \ac{MH} algorithms that are relevant to this dissertation include \ac{PSO}. The concept of \acp{PSO} is presented and discussed next.

\subsection{Particle Swarm Optimisation}
\label{sec:heuristics:mh:pso}

\Ac{PSO} is a stochastic population-based search algorithm based on the social behaviour of birds in a flock \cite{ref:kennedy:1995}. By definition, the \ac{PSO} heuristic is nature-inspired.  \Acp{PSO} were first presented  by \citeauthor{ref:kennedy:1995}\cite{ref:kennedy:1995}. It was also Kennedy and Eberhart that first applied \acp{PSO} to train of \acp{FFNN} \cite{ref:eberhart:1995}\cite{ref:kennedy:1997}. The application of \acp{PSO} in the context of training \ac{FFNN} have been widely studied \cite{ref:rakitianskaia:2012}\cite{ref:vanwyk:2014} and it has been found to perform well. This section aims to provide the reader with the detail of \ac{PSO} implementation.

In general, this dissertation uses the term \textit{entity} for candidate solutions and a \textit{population} for a collection of entities. \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that in \acp{PSO} individual candidate solutions are referred to as \textit{particles} and the population is referred to as a \textit{swarm}. These particles are ``flown'' through a hyperdimensional space. Changes in particle position is due to social-psychological tendencies of individuals to emulate the success of other individuals. The changes in the particle position are then influenced by the experience or knowledge of the particle's neighbours. It can be said that the position of a particle is thus influenced by the positions of other particles in the swarm resulting in a symbiotic cooperative heuristic. The social behaviour of particles is modeled such that they stochastically return to previously successful regions in the search space.

\citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that the swarm is usually arranged in a predefined structure, called a \textit{neighbourhood topology} that governs the communication between particles. Two different configurations of neighbourhood topologies exists. These are referred to as \textit{Local best (lbest)} \ac{PSO} and \textit{global best (gbest)} \ac{PSO}. There are two main differences between the two approaches in terms of their convergence characteristics \cite{ref:eberhart:1996}. These include:

\begin{itemize}
    \item Due to the larger particle interconnectivity of \textit{gbest} \ac{PSO}, the heuristic converges faster than with \textit{lbest} \ac{PSO}. \cite{ref:engelbrecht:2007} mentions that faster convergence comes at a cost of less diversity.
    \item As a consequence of larger diversity, the \textit{lbest} \ac{PSO} is less susceptible to getting trapped in local minima.
\end{itemize}

\citeauthor{ref:shi:1998}\cite{ref:shi:1998} proposed a modification of the original \ac{PSO} as was presented by \citeauthor{ref:kennedy:1995}. Their implementation focuses on the \textit{gbest} \ac{PSO} with \textit{inertia} weights. This dissertation focuses on their implementation of \textit{global best} \ac{PSO} and is discussed next.

The particles in this configuration has a number of properties associated with them \cite{ref:vanwyk:2014}. These include:

\begin{itemize}
    \item \textbf{Position}: Refers to the candidate solution that is represented by the particle and defines the particle position within the optimisation problem's hyper-dimensional solution space. Let the current position of particle $i$ at timestep $t$ be denoted by $x_{i}(t)$ and let $N$ be the search space dimensionality. 
    \item \textbf{Velocity}: Represents a step size for the particle in the search space. The velocity vector of particle $i$ at timestep $t$ is denoted $v_{i}(t)$. 
    \item \textbf{Solution Quality}: Refers to the evaluation of the particle's position with respect to the objective function. Let $f(x_{i}(t)$ denote the quality of the solution represented by the particle's position.
    \item \textbf{Personal Best Position}: Refers to a cognitive memory construct where each particle keeps track of their personal best position found during optimisation thus far. The personal best position is denoted $y_{i}(t)$.
    \item \textbf{Global Best Position}: Refers to a social memory construct where the each particle has a reference to the best solution found in the particle's neighbourhood thus far. In the case of \text{gbest} \ac{PSO}, the global best position is the best position of the entire swarm. The personal best position is denoted $\hat{y}_{i}(t)$.
\end{itemize}

During initialisation particles are randomly places within the search space by sampling from a uniform distribution such that $x_{i} \sim U(x_{min}, x_{max})$ and the velocity is set to vector of 0 such that $v_{i} = 0$. At timestep 0, the particle's initial position is set to be the particle's personal best solution such that $y_{i}(0) = x_{i}(0)$. The particle's update step is then broken into two parts. These include a velocity update step presented in Equation \ref{eq:heuristics:pso:velocity} followed by a position update step as presented in Equation \ref{eq:heuristics:pso:position} below.

\begin{equation}
    \label{eq:heuristics:pso:velocity}
    \begin{split}
        v_{ij}(t+1) = wv_{ij}(t) + c_{1}r_{1}(t)[y_{ij}(t) - x_{ij}(t)] + c_{2}r_{2}(t)[\hat{y}_{ij}(t) - x_{ij}(t)]
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:heuristics:pso:position}
    \begin{split}
        x_{ij}(t+1) = x_{ij}(t) + v_{ij}(t+1)
    \end{split}
\end{equation}

In Equations \ref{eq:heuristics:pso:velocity} and \ref{eq:heuristics:pso:position}, $i$ refers to the $i$-th particle in the swarm, $j$ refers to the $j$-th dimension of vectors with dimensionality $N$ defined by the optimisation problem. A breakdown of the components introduced above is required. The velocity update step consists of:

\begin{itemize}
    \item \textbf{Previous Velocity}: Denoted by the term $wv_{ij}(t)$. This term represents the particle's momentum and is used to formulate an update step for the particle in the search space. \citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that it forces the particle to maintain a consistent direction, preventing drastic changes in terms of update steps. This term is then scaled by the \textit{inertia} weight control parameter, denoted $w$. Inertia weight was introduced by \citeauthor{ref:shi:1998}\cite{ref:shi:1998} as a mechanism to control the exploration and exploitation abilities of the swarm. It was also introduced as a mechanism to eliminate velocity clamping (discussed later in the section). The introduction of inertia weight was successful in addressing the first objective, however did not quite provide a way to totally eliminate velocity clamping \cite{ref:shi:2001}.

    \item \textbf{Cognitive Component}: Denoted by the term $c_{1}r_{1}(t)[y_{ij} - x_{ij}(t)]$. This component represents the particle's personal  experience. It introduces an attractor to the particle's personal best position so far. The cognitive component is stochastically scaled with random numbers $r{1} \sim U(0,1)^N$ and the cognitive acceleration coefficient $c_{1}$ is used to control the influence of the cognitive attractor.

    \item \textbf{Social Component}: Denoted by the term $c_{2}r_{2}(t)[\hat{y}_{ij} - x_{ij}(t)]$. This component represents the particle's social  experience. It introduces an attractor to the swarm's best position so far. The social component is also stochastically scaled with random numbers $r{2} \sim U(0,1)^N$, while also introducing the social acceleration coefficient $c_{2}$ that is used to control the influence of the social attractor.
\end{itemize}

A concept known as \textit{velocity clamping} is mentioned above. \citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that when \acp{PSO} where first developed, it was possible for particle velocities to become inappropriately large during optimisation leading to situations where particles fly out of the feasible search space. This is known as \textit{swarm explosion} and occurs when there are frequent changes in the global best position. In order to address this issues, the concept of \textit{velocity clamping} was introduced \cite{ref:eberhart:1996}. The idea behind velocity clamping is to restrict particle velocities to some $V_{max}$ threshold, in essence, modeling a form of terminal velocity. Velocity clamping is applied after the velocity update step and is given in Equation \ref{eq:heuristics:pso:velocity_clamping} below.

\begin{equation}
    \label{eq:heuristics:pso:velocity_clamping}
    \begin{split}
        v_{ij}(t+1)= 
        \begin{cases}
            v'_{ij}(t+1) & \text{if } |v'_{ij}(t+1)| < V_{max,j} \\
            -V_{maxj}   & \text{if } v'_{ij}(t+1) \leq -V_{max,j}\\
            V_{maxj}   & \text{if } v'_{ij}(t+1) \geq V_{max,j}
        \end{cases}
    \end{split}
\end{equation}

$V_{max}$ then becomes another hyper-parameter that must be defined a priori. Appropriate values $V_{max}$ may prevent swarm explosion, but also has an effect on the exploration and exploitation of the heuristic. If $V_{max}$ is small, particle update steps are small, resulting in exploitation \cite{ref:eberhart:1996}. If $V_{max}$ is big, it allows for larger update steps, promoting more exploration. A balance is needed between exploration and exploitation. Similar to other strategies, such as learning rate schedules for gradient-based heuristics, adaptive strategies such as those proposed in \cite{ref:fan:2002} have been developed, but are beyond the scope of this dissertation.

It should be noted that the choice of control parameter play a vital role on the behaviour and characteristics of the \ac{PSO}. Van den Berg and Engelbrecht \cite{ref:vandenberg:2007}\cite{ref:vandenberg:2006} have done extensive work on the effects of different values for control parameters. For the purposes of this dissertation, the $c_{1}$ and $c_{2}$ control parameter are set to $1.496180$ and the inertia weight $w$ is set to $0.0729844$ as these correspond to values used in \cite{ref:eberhart:2000} and have been shown to be appropriate for a number of problems.

 An example of the pseudo code implementation of the \textit{gbest} \ac{PSO} is taken from \cite{ref:engelbrecht:2007} and is given in Algorithm \ref{algo:heuristics:pso:gbest} below.

\begin{algorithm}[H]
    \caption{The pseudo code algorithm for the gbest \ac{PSO} heuristic.}
    \label{algo:heuristics:pso:gbest}
    \begin{algorithmic}
        \State Create and initialise an $N_{x}$ dimensional swarm;
        \While{stopping condition not met}
            \For{each particle $i = 1, \dots, N_{s}$}
                \State // Set the personal best position;
                \If{$f(x_{i}) < f(y_{i})$ }
                    \State $y_{i} = x_{i}$;
                \EndIf

                \State // Set the global best position;
                \If{$f(x_{i}) < f(\hat{y})$ }
                    \State $\hat{y} = x_{i}$;
                \EndIf
            \EndFor

            \For{each particle $i = 1, \dots, N_{s}$}
                \State // Perform velocity update step;
                \State $v_{ij} = wv_{ij} + c_{1}r_{1}[y_{ij} - x_{ij}] + c_{2}r_{2}[\hat{y}_{ij} - x_{ij}]$
                \State // Perform position update step;
                \State $x_{ij} = x_{ij} + v_{ij}$
            \EndFor
        \EndWhile
    \end{algorithmic}
\end{algorithm}

This section provided the reader with the implementation details of the \ac{PSO} heuristic. It was mentioned that \ac{PSO} have been used to train \acp{FFNN} on many occasions with successful outcomes. The following section presents the reader with the next population-based \ac{MH} that is considered.

\subsection{Differential Evolution}
\label{sec:heuristics:mh:de}

This section aims to introduce the reader to the next population-based \ac{MH} called \acl{DE}. Similar to \ac{PSO}, \Ac{DE} is a stochastic population-based search strategy developed by Storm and Price \cite{ref:price:2006} in 1995. \Ac{DE} shares a lot of similarities with other evolutionary \ac{MH} paradigms such as \acp{PSO} and \acp{GA}. However, \ac{DE} differs significantly in the sense that it makes use of distance and direction information from the current population to guide the search process \cite{ref:engelbrecht:2007}. Originally, \ac{DE} was focussed on multi-dimensional real-values optimisation problems, but unlike gradient-based heuristics, it does not require any gradient information. This means that \ac{DE} does not require the underlying optimisation problem to be differentiable, meaning that it can be applied to problems that are discrete, noisy and dynamic \cite{ref:rocca:2011}.

Lots of research has been done on using \ac{DE} to train \acp{FFNN}. Some notable work include \cite{ref:ilonen:2003}\cite{ref:slowik:2008}\cite{ref:mingguang:2009}. In these works, the authors often highlight the low computational complexity and simplicity of implementation for \ac{DE}.

Similar to other \acp{EA}, variation from one generation to the next is achieved through the application of crossover and mutation operators. Engelbrecht \cite{ref:engelbrecht:2007} mentions that for other \acp{EA} if both these operators are used, crossover is applied first after which the generated offspring is mutated. For other \acp{EA} mutation step sizes are sampled from some probability distribution. \ac{DE} differs from these implementations in that

\begin{itemize}
    \item mutation is applied first to generate a \textit{trial vector}, which is then used within the crossover operator to produce one offspring and
    \item mutation step sizes are not sampled from prior known probability distributions.
\end{itemize}

In \ac{DE} mutation step sizes are influenced by the differences in positions of different entities in the current population. The positions of entities in the population provide valuable information about the fitness landscape. This is under the assumption that entities are initially uniformly placed in the search space. \ac{DE} aims to exploit this concept in order to find optimal solutions. There are three main components to the \ac{DE} heuristic. These include mutation, crossover and selection operators \cite{ref:price:2006}. Each of these are presented briefly next.

\subsubsection{Mutation}
\label{sec:heuristics:mh:de:mutation}

The purpose of the mutation operator is to produce a trial vector for each entity in the current population by mutating a target vector with a weighted differential \cite{ref:engelbrecht:2007}. This trial vector is used in the crossover operator (discussed next) to produce offspring. The mutation process then follows as such. For each each parent $x_{i}(t)$ generate a trial vector $u_{i}(t)$ as follows.

\begin{itemize}
    \item Select a target vector, $x_{i_{1}}(t)$ from the population the is not the same as the parent i.e. $i \neq i_{1}$.
    \item This is followed by randomly selecting two other individuals $x_{i_{2}}(t)$ and $x_{i_{3}}(t)$. Importantly, all of these entities must be unique such that $i \neq i_{1} \neq i_{2} \neq i_{3}$ and $i_{2}, i_{3} \sim U(1, N_{s}$ where $N_{s}$ is the size of the swarm.
    \item These individual entities are then used to calculate the trial vector by perturbing the target vector as presented in Equation \ref{eq:heuristics:de:mutation} below.
\end{itemize}

\begin{equation}
    \label{eq:heuristics:de:mutation}
    \begin{split}
        u_{i}(t) = x_{i_{1}} + \beta(x_{i_{2}}(t) - x_{i_{3}}(t))
    \end{split}
\end{equation}

In Equation \ref{eq:heuristics:de:mutation} $\beta \in (0, \infty)$ is the scale factor and controls the amplification of the differential variation \cite{ref:engelbrecht:2007}. Note that in the above steps, the selection strategy to select the target vector is not specified. Selection is discussed in Section \ref{sec:heuristics:mh:de:selection} below.

\subsubsection{Crossover}
\label{sec:heuristics:mh:de:crossover}

In the context of \acp{EA}, reproduction and recombination is done through the crossover operation. The same applies to \ac{DE}. The \ac{DE} crossover operator implements a discrete recombination of the trial vector, $u_{i}(t)$ (as was generated in Section \ref{sec:heuristics:mh:de:mutation} above) and the parent vector $x_{i}(t)$ to produce new offspring $x'_{i}(t)$. The crossover operator is given in Equation \ref{eq:heuristics:de:crossover} below.

\begin{equation}
    \label{eq:heuristics:de:crossover}
    \begin{split}
        x'_{ij}(t)= 
        \begin{cases}
            u_{ij}(t) & \text{if } j \in \mathcal{J} \\
            x_{ij}(t)   & \text{otherwise }
        \end{cases}
    \end{split}
\end{equation}

In Equation \ref{eq:heuristics:de:crossover}, $x_{ij}(t)$ refers to the $j$-th element of the vector $x_{i}(t)$ and $\mathcal{J}$ refers to a set of crossover points or indices at which perturbation is done. Different techniques for determining the set, $\mathcal{J}$ has been proposed \cite{ref:storn:1996}\cite{ref:storn:1997}. These include:

\begin{itemize}
    \item \textbf{Binomial crossover}: A crossover mask is generated by randomly selecting indices from the set of possible crossover points $\{1,2,\dots,N_{x}$ where $N_{x}$ is the problem dimension. This techique is presented in Algorithm \ref{algo:heuristics:de:bin} below. In Algorithm \ref{algo:heuristics:de:bin} $p_{r}$ is the crossover probability. The higher the value of $p_{r}$, the more points will be included in the set $\mathcal{J}$. A \textit{Bernoulli} distribution (presented in Chapter \ref{chap:probability} can be used to generate the binomial crossover mask. Note that due to the probabilistic nature of this process, it is possible that no crossover points are selected. To counteract this situation, a randomly selected crossover point $j^{*}$ is included in the set $\mathcal{J}$ such that $\mathcal{J} \neq \emptyset$ where $\emptyset$ is the empty set.
    \item \textbf{Exponential crossover}: \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} states that with exponential crossover a sequence of adjacent crossover points are selected start from some randomly selected crossover index. This means that the set of possible crossover points $\mathcal{J}$ is a circular array in indices. This technique does not require the selection of an additional crossover point $j^{*}$ as this technique includes at the very least one index, which is the starting index that is randomly selected. From this point, the next index is selected until $U(0,1) \geq p_{r}$ or $|\mathcal{J}| = N_{x}$. $p_{r}$ is the same crossover probability as mentioned above for binomial crossover. The implementation of exponential crossover is given in Algorithm \ref{algo:heuristics:de:exp} below.
\end{itemize}

\begin{algorithm}[H]
    \caption{The pseudo code algorithm for the binomial crossover technique for \ac{DE}.}
    \label{algo:heuristics:de:bin}
    \begin{algorithmic}
        \State $j^{*} \sim U(1,N_{x})$;
        \State $\mathcal{J} \gets \mathcal{J} \cup \{j^{*}\}$;
        \For{each $j \in \{1, \dots, N_{x}\}$}
            \If{$U(0,1) < p_{r}$ and $j \neq j^{*}$ }
                \State $\mathcal{J} \gets \mathcal{J} \cup \{j\}$;
            \EndIf
        \EndFor
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
    \caption{The pseudo code algorithm for the exponential crossover technique for \ac{DE}.}
    \label{algo:heuristics:de:exp}
    \begin{algorithmic}
        \State $\mathcal{J} \gets \{\}$;
        \State $j \sim U(0,N_{x} - 1)$;
        \Repeat
            \State $\mathcal{J} \gets \mathcal{J} \cup \{j + 1 \}$;
            \State $j = (j+1) \mod N_{x}$
        \Until{ $U(0,1) \geq p_{r}$ or $|\mathcal{J} = N_{x}$;}
    \end{algorithmic}
\end{algorithm}

\subsubsection{Selection}
\label{sec:heuristics:mh:de:selection}

Selection refers to the technique that is used to determine which entities are included in the mutation operator to produce a trial vector \cite{ref:engelbrecht:2007} as was shown in Section \ref{sec:heuristics:mh:de:mutation} above. Various selection operators have been suggested. With reference to the mutation operator, most \ac{DE} implementations make use of random selection or the best entity is used as the target vector $x_{i_{1}}(t)$. To construct the population for the next generation, deterministic selection is used. As such, a parent is replaced if the offspring produces a better solution that the parent such that $f(x'_{i}(t)) \leq f(x_{i}(t))$. \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} states that this is to ensure the average fitness of the population does not deteriorate.

\subsubsection{General Differential Evolution Algorithm}

Algorithm \ref{algo:heuristics:de:general_de} is taken from \cite{ref:engelbrecht:2007} and presents the general \ac{DE} algorithm. The population is initialised by randomly placing entities in the search space such that the positions of the entities are confined to some search boundary. As such, $x_{ij}(t) \sim U(x_{min,j}, x_{max,j})$, where $x_{min,j}$ and $x_{max,j}$ define the search boundaries.

\begin{algorithm}[H]
    \caption{The pseudo code for the general \ac{DE} heuristic.}
    \label{algo:heuristics:de:general_de}
    \begin{algorithmic}
        \State Set the generation counter, $t = 0$;
        \State Initialise the control parameters, $\beta$ and $p_{r}$
        \While{stopping condition not met}
            \For{each entity $x_{i}(t) \in \mathcal{C}(t)$ }
                \State Evaluate the fitness, $f(x_{i}(t))$;
                \State Create the trial vector, $u_{i}(t)$ by applying the mutation operator;
                \State Create an offspring, $x'_{i}(t)$ by applying the crossover operator;
                \If{$f(x'_{i}(t))$ is better than $f(x_{i}(t))$ }
                    \State Add $x'_{i}(t)$ to $\mathcal{C}(t+1)$;
                \Else
                    \State Add $x_{i}(t)$ to $\mathcal{C}(t+1)$;
                \EndIf
            \EndFor
        \EndWhile
        \State Return the individual with the best fitness as the solution;
    \end{algorithmic}
\end{algorithm}

As with other heuristics, \ac{DE} also contains a set of control parameters. These include:

\begin{itemize}
    \item \textbf{Population size:} The population size has a direct influence on the exploration ability of the \ac{DE} heuristic \cite{ref:engelbrecht:2007}. The larger the population size, the more differential vectors are available and thus, more directions can be explored.

    \item \textbf{Scaling Factor:} The scaling factor, $\beta \in (0, \infty)$ controls the amplification of the differential variations $(x_{i_{2}}(t) - x_{i_{3}}(t))$. A lower scaling factor leads to smaller step sizes and as a result, convergence will take longer. Larger values facilitate exploration, but could cause the algorithm to overshoot. Similar to other heuristics, adaptive mechanisms can be used to dynamically alter the scaling factor throughout the optimisation process, however this is beyond the scope of this dissertation.

    \item \textbf{Recombination Probability:} The probability of recombination, $p_{r}$ has a direct influence on the diversity of the \ac{DE} heuristic \cite{ref:engelbrecht:2007}. This parameter controls the number of elements that are included during crossover. The higher the probability of recombination, the more variation is introduced in the new population. Similar to the scaling factor, dynamic techniques can be used to adjust this value dynamically during optimisation.
\end{itemize}

\subsubsection{DE/$x$/$y$/$z$ Notation}

Many variants of \ac{DE} have been created and researched \cite{ref:mezura:2006}. A general notation for \ac{DE} heuristic variants have been developed by Storn et al. \cite{ref:storn:1996}\cite{ref:storn:1997}. The notation follows the form \textit{DE/$x$/$y$/$z$} where $x$,$y$ and $z$ refer to the components that are used by the particular \ac{DE}. A breakdown of this notation is provided as follows.

\begin{itemize}
    \item \textbf{$x$:} The selection mechanism for the target vector.
    \item \textbf{$y$:} The number of difference vectors to include.
    \item \textbf{$z$:} The type of crossover operator used.
\end{itemize}

For this dissertation, \textit{random} and \textit{best entity} selection, a single difference vector and binomial and exponential crossover is considered. This results in the \ac{DE} notations as follows.

\begin{itemize}
    \item DE/rand/1/bin
    \item DE/best/1/bin
    \item DE/rand/1/exp
    \item DE/best/1/exp
\end{itemize}

This section provided the reader with the details around the implementation of the \ac{DE} heuristic. The last population-based \ac{MH} is presented next.

\subsection{Genetic Algorithms}
\label{sec:heuristics:mh:ga}

\Ac{EC} refers to a collection of nature-inspired optimisation algorithms that lend their foundation to biological evolution. \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that \ac{EC} refers to computer-based problem solving systems that use computational models of evolutionary processes such as natural selection, survival of the fittest and reproduction. It was Charles Darwin's theory of \textit{natural selection} that became the foundation of biological evolution \cite{ref:darwin:1987}. \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} summarises the Darwinian theory of evolution \cite{ref:darwin:2012} as follows. In a world with limited resources and stable populations, each individual competes with others for survival. Those individuals with the ``best'' characteristics (traits) are more likely to survive and to reproduce and those characteristics will be passed on to their offspring. These desirable characteristics are inherited by the following generations and (over time) become dominant among the population. Evolution via natural selection of a randomly chosen population of entities can be seen as a search through the space of possible chromosome values. This makes the \ac{EC} search process a stochastic search for an optimal solution to the given problem.

So far the reader has been introduced to two population-based \acp{MH}. These include \ac{PSO} and \ac{DE}. The \ac{DE} heuristic that was presented in Section \ref{sec:heuristics:mh:de} is one type of \ac{EC} algorithm. This section introduces another population-based, nature-inspired optimisation \ac{EC} algorithm named \aclp{GA}. The detail of the implementation of \acp{GA} is given in this section. Importantly, the application of \acp{GA} is presented in the context of training \acp{FFNN}. \acp{GA} have been widely used to train \acp{FFNN} \cite{ref:montana:1989}\cite{ref:siddique:2001}\cite{ref:miller:1989}. This section shines light on how this is done.

\Acp{GA} where first proposed by Fraser \cite{ref:fraser:1957} and later by Bremermann \cite{ref:bremermann:1962} and Reed et al. \cite{ref:reed:1967}. However, Holland \cite{ref:holland:1992} is widely regarded as the father of \acp{GA}. Similar to \acp{DE}, \acp{GA} are also nature-inspired population-based \acp{MH} and model genetic evolution of entities in a hypothetical population. As with other \acp{EA}, \acp{GA} implement a number of operators that drive the optimisation process.  Primarily, \acp{GA} implement selection, modeling survival of the fittest and crossover, modeling reproduction. The remainder of this section follows the same approach as was done with \ac{DE} where the different operators are discussed. However, it is necessary to first provide the reader with the generic \ac{EC} algorithm. This algorithm is also referred to as the canonical \ac{GA} (CGA) and was proposed by Holland \cite{ref:holland:1992}. The generic \ac{EC} algorithm is taken from \cite{ref:engelbrecht:2007} and is is presented in Algorithm \ref{algo:heuristics:ga:generic_ec} below.

\begin{algorithm}[H]
    \caption{The pseudo code for the generic \ac{EC} heuristic.}
    \label{algo:heuristics:ga:generic_ec}
    \begin{algorithmic}
        \State Let $t = 0$ be the generation counter;
        \State Create an initialise an $N_{x}$-dimensional population, $\mathcal{C}(0)$, to consist of $N_{s}$ individuals;
        \While{stopping condition not met}
            \State Evaluate the fitness, $f(x_{i}(t))$ of each individual $x_{i}(t)$;
            \State Perform reproduction to create offspring;
            \State Select the new population, $\mathcal{C}(t+1)$;
            \State Advance to the new generation, i.e. $t = t + 1$
        \EndWhile
        \State
    \end{algorithmic}
\end{algorithm}

From Algorithm \ref{algo:heuristics:ga:generic_ec} above it can be seen that a number of components influence the search process. These include:

\begin{itemize}
    \item \textbf{Encoding}: Refers to the representation of a candidate solution to some optimisation problem as the chromosomes of some entity.

    \item \textbf{Fitness Function}: Refers to the objective function that measures the fitness of an entity. Fitness refers to the survivability of an entity and measures the strength of a candidate solution represented by the entity's chromosomes.

    \item \textbf{Initialisation}: Refers to the initialisation strategy used to generate the initial population. Often entities' chromosomes are uniformly sampled in the feasible search space for the underlying optimisation problem.

    \item \textbf{Selection}: Refers to the techniques that are used to select entities for reproduction and generation of the new population as well as the selection of genes for mutation. Selection is implemented through selection operators.

    \item \textbf{Reproduction}: Refers to the generation of the next population and is implemented through crossover operators.
\end{itemize}

Note that the initial implementations of \ac{EC} heuristics such as \acp{GA} did not contain a mutation operator as this was only introduced later. The following sections provide the crossover, mutation and selection operators for \acp{GA}.

\subsubsection{Crossover}
\label{sec:heuristics:mh:ga:crossover}

As with \ac{DE}, crossover operators model the reproduction of entities in the population. Broadly speaking, the crossover operators can be divided into three main categories \cite{ref:engelbrecht:2007} and are based on arity of the operator i.e. the number of parents used for reproduction.

\begin{itemize}
    \item \textbf{Asexual: } Offspring is generated from one parent.

    \item \textbf{Sexual: } Offspring is generated from two parents and can produce one or two offspring.

    \item \textbf{Multi-recombination: } Offspring is generated from more than two parents and can produce one or more offspring.
\end{itemize}

\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that crossover operators can be further classified based on their encoding/representation scheme. These include binary-specific operators used for binary representations and operators focussed on floating-point representations. Since the focus is put on training \acp{FFNN}, from this point on, floating-point representations are assumed.

During crossover, parents are selected using a selection operator. Selection operators are discussed later in Section \ref{sec:heuristics:mh:ga:selection}. As with \acp{DE}, recombination is applied probabilistically and thus, selection of a parent does not guarantee reproduction. Each parent has a probability $p_{c}$ of producing offspring. Usually a high crossover probability is used \cite{ref:engelbrecht:2007}. In addition to recombination, \acp{GA} implement a replacement policy where fit offspring can replace weaker parents in the population.

Although floating-point representations of chromosomes are assumed, binary crossover operators can also be used since they produce a mask that defines how parents are recombined. Specifically, in the context of this dissertation, focus is put on \textit{uniform} crossover. Uniform crossover refers to a crossover operator where an $N_{x}$-dimensional crossover mask is generated randomly \cite{ref:syswerda:1989}. Uniform crossover is illustrated in Figure \ref{fig:heuristics:mh:ga:uniform_crossover} below and the algorithm for uniform crossover is given in Algorithm \ref{algo:heuristics:mh:ga:uniform_crossover}.

\begin{figure}[htbp]
    \includegraphics[width=\textwidth]{images/uniform_crossover.png}
    \caption{An illustration of the uniform crossover operator as it applies to sexual recombination, resulting in two new offspring.}
    \label{fig:heuristics:mh:ga:uniform_crossover}
\end{figure}

\begin{algorithm}[H]
    \caption{The pseudo code for the uniform crossover operator as used by \acp{GA}.}
    \label{algo:heuristics:mh:ga:uniform_crossover}
    \begin{algorithmic}
        \State Initialise the mask, $m_{j}(t) = 0 \forall j = 1, \dots, N_{x}$;
        \For{$j = 1$ to $N_{x}$}
            \If{$U(0,1) \leq p_{x}$}
                \State $m_{j}(t) = 1$;
            \EndIf
        \EndFor
        \State
    \end{algorithmic}
\end{algorithm}

In Algorithm \ref{algo:heuristics:mh:ga:uniform_crossover} above, $p_{x}$ is the bitswapping probability.

\subsubsection{Mutation}
\label{sec:heuristics:mh:ga:mutation}

The mutation operator is applied in order to introduce new genetic material into an existing entity \cite{ref:engelbrecht:2007}. In doing so, diversity is added into the genetic characteristics of the population. Mutation is applied at a certain mutation probability $p_{m}$ to each gene of the offspring $x_{i}(t)$ to produce mutated offspring $x'_{i}(t)$. \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that the mutation probability, also referred to as the mutation rate is usually small such that $p_{m} \in [0,1]$ to ensure that good solutions are not distorted too much.

Similar to the crossover operator, mutation operators can be classified according to the representation scheme used. In the context of training 
\acp{FFNN}, binary crossover operators such as the \textit{uniform} mutation operator can be used to generate a mutation mask that specifies which genes are mutated. For the purposes of this dissertation, the application of the mutation operator on $x_{ij}(t)$ results in a small update step for that gene such that $x'_{ij}(t) = x_{ij}(t) + v_{ij}(t)$. In this case, $v_{ij}(t) \sim U(-limit, limit)$ and $limit = \sqrt{\frac{6}{fanin + fanout}}$ as presented for Glorot uniform sampling in \ref{chap:anns}. An adaptation of the uniform mutation operator is then provided in Algorithm \ref{algo:heuristics:mh:ga:uniform_mutation} below.

\begin{algorithm}[H]
    \caption{The pseudo code for the uniform mutation operator as used by \acp{GA}.}
    \label{algo:heuristics:mh:ga:uniform_mutation}
    \begin{algorithmic}
        \For{$j = 1$ to $N_{x}$}
            \If{$U(0,1) \leq p_{m}$}
                \State Sample update step $v_{ij}(t) \sim U(-limit, limit)$
                \State $x'_{ij}(t) = x_{ij}(t) + v_{ij}(t)$;
            \EndIf
        \EndFor
        \State
    \end{algorithmic}
\end{algorithm}

An illustration of the adapted uniform mutation operator is presented in Figure \ref{fig:heuristics:mh:ga:uniform_mutation} below.

\begin{figure}[htbp]
    \includegraphics[width=\textwidth]{images/uniform_mutation.png}
    \caption{An illustration of the adapted uniform mutation operator as it applies to mutated offspring.}
    \label{fig:heuristics:mh:ga:uniform_mutation}
\end{figure}

\subsubsection{Selection}
\label{sec:heuristics:mh:ga:selection}

Selection is a widely used concept in all \acp{EA} and models survival of the fittest in the evolutionary context. The main idea behind the selection operator is to emphasise better solutions \cite{ref:engelbrecht:2007}. This is done in two of the main components of \acp{EA}. These include

\begin{itemize}
    \item \textbf{Selection of the new population: } A new population of candidate solutions are is selected at the end of each generation to serve as the population for the next generation. The new population can be selected from both the parents and offspring. The selection operator is thus responsible for ensuring that good entities survive to the next generation.

    \item \textbf{Reproduction: } Offspring is created through the crossover and/or the mutation operators. In terms of crossover, good solutions should have a high probability of reproducing to ensure that offspring contain genetic material of the best entities. In terms of mutation, selection mechanisms should focus on weaker entities. By mutating weak entities, the hope is to introduce better traits, increasing their chance to survive. 
\end{itemize}

\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that selection operators are characterised by their \textit{selective pressure}. Selective pressure is defined as the speed at which the best entity's solution will occupy the entire population by repeated application of the selection operator alone \cite{ref:back:1994}. A selection operator with a high selective pressure rapidly decreases the diversity in the population. This could lead to premature convergence. A high selective pressure limits the exploration abilities of the population. Similar to other components and operators presented in this chapter, selection mechanisms should maintain a balance between exploration and exploitation.

Various selection mechanisms have been proposed. For the purposes of this dissertation, focus is put on the following selection mechanisms and concepts.

\begin{itemize}
    \item \textbf{Tournament Selection: } Tournament selection selects a group of $N_{ts}$ entities randomly from the population such that $N_{ts} < N_{s}$, where $N_{s}$ is the population size. The performance of the selected $N_{ts}$ entities are then compared and the best entities from this group is selected and returned by the operator. It should be mentioned that for sexual crossover of two parents, tournament selection is applied twice, first for the first parent and the again for the second parent. \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that tournament selection prevents the best entities from dominating provided that $N_{ts}$ is not too large. This results in a lower selective pressure. If $N_{ts}$ is too small, the chances that bad entities will be selected increase.

    \item \textbf{Rank-based Selection: } Rank-based selection uses the rank-ordered fitness values to determine the probability of selection and not the absolute fitness value. It can therefore be said that selection is independent of actual fitness values. \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that the advantage of this approach is that the best entities will not dominate the selection process. Non-deterministic linear sampling selects an entity $x_{i}(t)$ such that $i \sim U(0, U(0, N_{s} - 1))$. Importantly, in the context of a minimisation problem, entities are first sorted in decreasing order of fitness value, assuming that the best heuristic is then contained at index 0, while the worst entity is contained at index $N_{s} - 1$.

    \item \textbf{Elitism: } Elitism refers to the process of ensuring that the best entities from the current population survive to the next generation. The best entities are simply passed on to the next generation without mutation. The more entities that survive to the next generation, the lower the diversity of the new population. It is later shown in \ref{chap:bhh} that the proposed \ac{BHH} can incorporate a form of elitism in its credit assignment strategy.
\end{itemize}

\subsubsection{Control Parameters}
\label{sec:heuristics:mh:ga:control_parameters}

Throughout this section a number of control parameters have been provided that affect the performance of the \ac{GA}. These include the population size $N$, the crossover rate $p_{c}$ and the mutation rate $p_{m}$. \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that these values are usually kept static. However, it is widely accepted that these parameters have a significant impact on the performance of the \ac{GA}.  Finding optimal values for $p_{c}$ and  $p_{m}$ empirically can be a time consuming process. As such, dynamic parameter values can be introduced, however, this is beyond the scope of this dissertation.

\section{Summary}
\label{sec:heuristics:summary}

This chapter provided the reader with detailed background information on different heuristics that have been shown to be able to train \acp{FFNN}. Two main groups of heuristics where discussed. These include gradient-based heuristics and \aclp{MH}. For each of these groups a number of different variants have been discussed. A total of ten different heuristics have been introduced and where possible, their advantages, disadvantages and characteristics have been discussed.

The next chapter aims to build on the foundations provided in this chapter by putting focus on \acp{HH}. It is shown that \acp{MH} implement a heuristic pool of lower-level heuristics such as those presented in this chapter.

### 2022-09-12 dissertation/chapters/04-hyper-heuristics.tex
📝 (review): First set of changes

\chapter{Hyper-Heuristics}
\label{chap:hhs}

\begin{quotation}
    \textit{``Live as if you were to die tomorrow. Learn as if you were to live forever.'' - Mahatma Gandhi}
\end{quotation}

One of the biggest challenges for any \ac{ML} researcher is that it is hard to find optimal configurations. These configurations often include the selection of appropriate models, heuristics and hyper-parameters. The optimal configuration is more often than not, problem-specific and it is difficult to find general approaches that can be applied to many situations. Traditionally, if multiple configurations are to be considered, an empirical process of trial and error is executed. Trial and error approaches are time consuming and illustrates a problem of generalisation of solutions. A modern approach to this problem is to automate this process. Automation of this process can be done by brute force where many different configurations are considered iteratively, sweeping over different configurations one after the other. Only after all configurations have been considered, can an optimal configuration be identified.

A different approach is to find optimal configurations by means of a search process. This means that a higher level optimisation process can be defined where the optimal configurations can be found as part of a search process. It is important to note that this search process is separate from the underlying problem to be solved. A measure of abstraction comes into play. In the context of training \acp{FFNN}, this is equivalent to finding the appropriate heuristic and hyper-parameters at various timesteps throughout the training process.

Automation alone is not enough. It is often the case that a single configuration is not sufficient. A modern suggestion is to include a hybridisation approach where multiple configurations are considered together. This is the nature of \acp{HH}. This is different from \textit{ensemble} \cite{ref:dietterich:2002} approaches in the sense that \acp{HH} provide a single solution, where as \textit{ensembles} make use of the combination of solutions that undergo a net weighted transformation in order to produce a final solution.

So far the reader has been presented with background information on \acp{ANN} and heuristics. This chapter aims to provide the reader with the necessary background information on \acp{HH}. It should be noted that this is a short chapter as the foundations of heuristics have already been presented in Chapter \ref{chap:heuristics}. The remainder of the chapter is structured as follows:

\begin{itemize}
    \item \textbf{Section \ref{sec:hh:meta_learning}} provides the reader with a brief definition and discussion on meta-learning.

    \item \textbf{Section \ref{sec:hh:what_is_a_hh}} presents the concept of a \ac{HH} and a formal definition is provided.

    \item \textbf{Section \ref{sec:hh:classification}} provides a detailed discussion on the classification and types of \acp{HH}.

    \item \textbf{Section \ref{sec:hh:application_to_nn_training}} sheds light on the applications of \acp{HH} in the context of training \acp{NN}.

    \item Finally, a summary of the chapter is provided in \textbf{Section \ref{sec:hh:summary}}.
\end{itemize}

\section{Meta-Learning}
\label{sec:hh:meta_learning}

Meta learning is a branch of metacognition and is concerned with learning about the learning processes. Meta-learning studies how learning systems can increase in efficiency through experience and is broadly defined as the learning process concerned with the concept of \textit{learning to learn} \cite{ref:vilalta:2002}. The goal of meta-learning is to understand if learning itself can become flexible to the problem domain or task under consideration.

\citeauthor{ref:vilalta:2002} \cite{ref:vilalta:2002} mentions that meta-learning differs from base-learning in the scope of the level of adaptation. Meta-learning is concerned with learning how to choosing the right configuration and biases dynamically. On the contrary, for \textit{base}-learning, biases and configurations are predefined and fixed a priori.

\section{What are Hyper-Heuristics?}
\label{sec:hh:what_is_a_hh}

The term \acl{HH} was first used in 1997 \cite{ref:burke:2010} and was used to describe a protocol that combines several \ac{AI} methods in the context of automated theorem proving. The term was independently used in 2000 \cite{ref:cowling:2000} to describe ``heuristics to choose heuristics''.

Formal definition of \acp{HH} is required. \citeauthor{ref:burke:2010}\cite{ref:burke:2010} defines \acp{HH} as search methods or learning mechanism for selecting or generating heuristics to solve computational search problems. Burke goes on to say that \ac{HH} is a high-level approach that, given a particular problem instance and a number of low-level heuristics, can select and apply an appropriate low-level heuristic at each decision point \cite{ref:burke2003}.

\citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} states that \acp{HH} promote the design of more generally applicable search methodologies and tend to performing relatively well on a large set of different problems. This is in contrast to specialised algorithms which typically focus on outperforming the state-of-the-art for a single application.

Importantly, \ac{HH} are concerned with finding the best heuristic in heuristic-space, while the underlying low-level heuristics find solutions in the feasible search space. This level of abstraction is illustrated in Figure \ref{fig:heuristics:hh:hh_algorithm} below.

\begin{figure}[htbp]
    \begin{centering}
        \includegraphics[width=0.8\textwidth]{images/hh_high_level.png}
        \caption{An illustration of abstraction introduced by \acp{HH}.}
        \label{fig:heuristics:hh:hh_algorithm}
    \end{centering}
\end{figure}

One can clearly see from Figure \ref{fig:heuristics:hh:hh_algorithm} the abstraction of the heuristic search process. The two large elliptical figures highlight the entity and heuristic pools, each of these are concerned with their own optimisation process. Note, that at the higher level abstraction, \acp{HH} do not make use of domain specific information such as an entity's position or gradient in the search space.

\citeauthor{ref:grobler:2015}\cite{ref:grobler:2015} mentions that two fundamental ideas behind the notion of \ac{HH} can be identified. Firstly, the recognition that the process of selecting or designing efficient hybrid and/or cooperative heuristics can be regarded as a computational search problem in itself. Secondly, there is significant potential to improve search methodologies by the incorporation of learning mechanisms that can adaptively guide the search. These two fundamental ideas have inspired different types of hyper-heuristics \cite{ref:burke:2010}.

\section{Classification of Hyper-Heuristics}
\label{sec:hh:classification}

\citeauthor{ref:burke:2010}\cite{ref:burke:2010} proposed a modern classification scheme used to classify \acp{HH}. According to the proposed classification scheme, \acp{HH} are classified in two dimensions. These include the nature of the heuristic search space and the source of feedback during learning. Figure \ref{fig:heuristics:hh:classification} was taken from \cite{ref:burke:2010} and summarises the classification scheme for \ac{HH}.

\begin{figure}[htbp]
    \includegraphics[width=\textwidth]{images/hh_classification.png}
    \caption{A classification of \ac{HH} approaches, according to two dimensions: (i) the nature of the heuristic search space, and (ii) the source of feedback during learning.}
    \label{fig:heuristics:hh:classification}
\end{figure}

Each of these groups are briefly discussed next.

\subsection{Selection vs. Generation}

According to the classification proposed by \cite{ref:burke:2010}, the first dimension of classification involves the nature of the search space. Distinction is made between heuristic selection and heuristic generation. For heuristic selection \acp{HH}, methodologies are implemented for choosing or selecting existing low-level heuristics. On the contrary, for heuristic generation \acp{HH}, methodologies  are implemented for generating new heuristics from components of existing heuristics.

Selection mechanisms can include probabilistic methods as is introduced in this dissertation or even some high level \ac{MH}. For generation mechanisms, \ac{EA} are often used \cite{ref:burke:2010}.

\subsection{Construction vs. Perturbation}

The second dimension of classification distinguishes between construction heuristics and perturbation heuristics. Consider first construction heuristics. According to \citeauthor{ref:burke:2010}\cite{ref:burke:2010}, these approaches build a solution incrementally. Starting with an empty solution, the goal is to intelligently select and use construction heuristics to gradually build a complete solution. As such, the \ac{HH} framework is provided with a set of pre-existing construction heuristics. These heuristics are generally problem specific and the challenge is to select the heuristic that is somehow the most suitable for the current problem state. This process is repeated until some final state such as a complete solution, is obtained.

Perturbation heuristics refer to approaches that start with a complete solution, generated either randomly or using simple construction heuristics.  Perturbation heuristics try to iteratively improve the current solution. As such, the hyper-heuristic framework is provided with a set of neighbourhood structures and/or simple local searchers. The goal here it to iteratively select and apply them to the current complete solution. This process continues until a stopping condition has been met. Notice that these approaches do not have a natural termination condition.
This is one of the biggest differences between construction and perturbation heuristics.

\begin{itemize}
    \item (i) low-level heuristic selection, and
    \item (ii) move acceptance strategy. 
\end{itemize}

Heuristic selection can be done in a \textit{non-adaptive} or simple way. This is done either randomly or along a cycle and is based on a prefixed heuristic ordering \cite{ref:cowling:2000}. No learning is involved in these approaches. As an alternative, heuristic selection may incorporate an \textit{adaptive}, \textit{online learning}) mechanism based on the probabilistic weighting of the low-level heuristics \cite{ref:burke:2003} or some type of performance statistics \cite{ref:cowling:2000}. It will later be shown that the proposed \ac{BHH} implements this adaptive selection, perturbation strategy.

The acceptance strategy is an important component of any local search heuristic. \cite{ref:burke:2003} mentions that many acceptance strategies have been explored within \acp{HH}. Move acceptance strategies can be divided into two categories. These include \textit{deterministic} and \textit{non-deterministic}. In general, a move is accepted or rejected, based on the quality of the move and the current solution during a single point search. At any point in the search, deterministic move acceptance methods generate the same result for the same candidate solution(s) used for the acceptance test. However, a different outcome is possible if a non-deterministic approach is used. If the move acceptance test involves other parameters, such as the current time, then these strategies are referred to as non-deterministic strategies \cite{ref:burke:2003}.

\subsection{Online Learning vs. Offline Learning vs. No Learning}

A \ac{HH} is considered to be a learning algorithm when it uses some feedback from the search process. Therefore, non-learning hyper-heuristics are those that do not use any feedback.

With online learning \acp{HH}, learning continues to takes place while the algorithm is solving an instance of the underlying optimisation problem. Task-dependent local properties can be used by the high-level strategy to determine the appropriate low-level heuristic to apply. Examples of online learning approaches within hyper-heuristics include the use of reinforcement learning for heuristic selection and, generally, the use of \acp{MH} as high-level search strategies across a search space of heuristics.

W.r.t offline learning \acp{HH} algorithms, the idea is to gather knowledge in the form of rules or programs, from a set of training instances. The hope is that it would generalise to the process of solving unseen instances. Examples of offline learning approaches within hyper-heuristics include \textit{learning classifier systems}, \textit{case-based reasoning} and \textit{genetic programming}.

\section{Application to Neural Network Training}
\label{sec:hh:application_to_nn_training}

Training of \ac{FFNN} is notorious for being sensitive to configurations made beforehand. \acp{HH} provide a dynamic framework to train \ac{FFNN}. However, at the time of writing, only two examples of published work where found where \ac{HH} are used for training \ac{FFNN}. These include the works of Nel \cite{ref:nel:2021} and Ul et al. \cite{ref:ul:2018}

\section{Summary}
\label{sec:hh:summary}

This chapter provided the reader with the necessary background information on \acp{HH}. A discussion on meta-learning is provided. The definition of a \ac{HH} is given and modern classifications of \ac{HH} types was discussed in detail. It was shown that \ac{HH} can be used to train \acp{FFNN}.

This chapter then concludes the background information of heuristics in general. The next chapter aims to provide the reader with the necessary background information on statistics and probability theory. These concepts are required in order to formulate the proposed \ac{BHH}.

### 2022-09-12 dissertation/chapters/05-probability.tex
📝 (review): First set of changes

\chapter{Probability}
\label{chap:probability}

\begin{quotation}
    \textit{``Probability theory is nothing but common sense reduced to calculation.'' - Pierre-Simon Laplace}
\end{quotation}

Probability theory and statistics can be traced back to as early as the 17th century. In 1718, \citeauthor{ref:demoivre:1718} \cite{ref:demoivre:1718} published the \textit{Doctrine of of Chance}; a book that is widely seen as the first published book on probability theory. In 1763, Thomas Bayes \cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of Bayes' Theorem was introduced. It is from this theorem that the \ac{BHH} was named after.

Probability theory and statistics play a vital role in the \ac{ML} space. A lot of constructs that arise in \ac{ML} originate from the fields of statistics and probability theory. There are many examples of how these two fields overlap. In 1991, \citeauthor{ref:denker:1991}, \cite{ref:denker:1991} proposed a way to transform \ac{ANN} outputs to probability distributions. In 1993,
\citeauthor{ref:neal:1993} \cite{ref:neal:1993} developed the first \ac{MCMC} sampling algorithm for Bayesian \acp{NN}. These are just a  few examples of how the fields of probability theory, statistics and \ac{ML} overlap.

So far the reader has been provided with the problem statement and goals of this dissertation in Chapter \ref{chap:introduction} and a detailed literature study and background information on \acp{ANN} was provided in Chapter \ref{chap:anns}. This chapter aims to provide the reader with the necessary background information on probability theory and statistics. These are big fields and focus is put on the elements that are required to formulate the proposed \ac{BHH}. The remainder of the chapter is structured as follows.

\begin{itemize}
    \item \textbf{Section \ref{sec:probability:overview}} gives a brief overview of what probability is and how it is used.

    \item \textbf{Section \ref{sec:probability:multiple_events}} presents the concept of conditional probability.

    \item \textbf{Section \ref{sec:probability:multiple_events}} presents the two laws of probability related to the intersection and union of multiple events.

    \item \textbf{Section \ref{sec:probability:cond_probability}} introduces conditional probability.

    \item \textbf{Section \ref{sec:probability:bayes_theorem}} introduces Bayes' Theorem, the fundamental theorem upon which the \ac{BHH} is built.

    \item \textbf{Section \ref{sec:probability:probability_distributions}} presents relevant probability distributions.

    \item \textbf{Section \ref{sec:probability:conjugate_priors}} presents the conjugate prior probability distributions for the probability distributions provided in Section \ref{sec:probability:probability_distributions}.

    \item \textbf{Section \ref{sec:probability:bayesian_statistics}} presents \textit{Bayesian} statistics. Brief discussions follow on the \textit{frequentist} view and \textit{Bayesian} view of probability. It is shown how Bayes' Theorem can be used to apply Bayesian statistics a alternative mechanism to do inference. Detailed discussions follow on \index{Bayesian optimisation}Bayesian optimisation methods such as \index{Bayesian analysis}\textit{Bayesian analysis}.

    \item Finally, a summary of the elements discussed in this chapter is provided in \textbf{Section \ref{sec:probability:summary}}.
\end{itemize}

\section{Overview}
\label{sec:probability:overview}

In everyday conversation, the term \textit{probability} is a measure of one's belief in the occurrence of a future event \cite{ref:wackerly:2014}. Probability is a necessary tool used in many fields including physics, biology, chemistry and computer science. These fields contain many cases that generate observations that can not be predicted with absolute certainty \cite{ref:wackerly:2014}. Probability can be be inferred and confirmed through past events. These events are referred to as \textit{random} or \textit{stochastic} events. The probability that a certain event $A$ might occur is denoted $P(A)$. Although these random events cannot be predicted with absolute certainty, the relative frequency with which they occur over many trials if often remarkably stable. Consider flipping an unbiased, fair coin. The coin has two possible outcomes. From this, one can conclude that each side has a $\frac{1}{2}$ or $50\%$ chance of occurring. In statistics, the decimal probability notation is used where $0 <= P(A) <= 1$. Suppose the fair coin is thrown 10 times, one is not guaranteed to observe $0.5$ heads and $0.5$ tails. There is is some probability, although small, that the coin might fall on heads $0/10$ times. The probability of such an event occurring is $0.0009765625$. The \ac{CLT} shows that the normalised sum of events tends toward a normal distribution with a mean value of $0.5$ if the number of events observed $N$, is large \cite{ref:wackerly:2014}. The larger the value of $N$, the higher the confidence of mean probability and relative frequency of the event. The stable long-term relative frequency by which a random event occurs provides an intuitive and meaningful measure of belief that a certain event will occur again at some point in the future \cite{ref:wackerly:2014}. The belief that a random event would occur again sometime in the future, at an expected relative frequency could be useful for decision making. It will later be shown that the proposed \ac{BHH} implements a probabilistic selection mechanism that continuously updates its beliefs such that it learns what the relative frequency by which a heuristic is selected should be.

Probability can also be expressed over multiple random events. For example, consider flipping a fair, unbiased coin and 6-sided dice together. One could then consider the probability of observing a certain outcome for the coin together with a certain outcome for the dice. Multiple random events can be considered together, dependently or conditionally. The following sections provides insight into conditional and joints probabilities.

\section{Conditional Probability and Independence}
\label{sec:probability:cond_probability}

The occurrence of a given random event $A$ can often be dependent on the occurrence of another event $B$. In the field of medicine, an example of this is to calculate the probability of a certain diagnosis of a sick patient given his/her symptoms. This is referred to as the conditional probability between two events. The conditional probability is expressed as $P(A \vert B)$ and is read \textit{the probability of $A$ given $B$}. On the contrary, the \textit{unconditional} probability is the probability of an event, not dependent on any other. The conditional probability of $A$ given $B$ can be expressed as is given in Definition \ref{eq:probability:cond_probability} below \cite{ref:wackerly:2014}.

\begin{definition}[\textbf{Conditional Probability}]
    \label{eq:probability:cond_probability}
    The conditional probability of an event $A$, subject to the occurrence of event $B$ is expressed as

    \begin{equation*}
        P(A \vert B) = \frac{P(A \cap B)}{P(B)}
    \end{equation*}
\end{definition}

where $P(B) > 0$. Notice that conditional probability does not suggest causation. If an event $A$ has a high probability of occurring after observing event $B$, it does not necessarily mean that $A$ is caused by $B$. Conditional probability simply expresses the dependence amongst events.

It could also be the case that the outcome of observing event $A$ is not affected by the occurrence of $B$. In this case, it is said that events $A$ and $B$ are independent. The independence between two events are expressed in Definition \ref{def:probability:cond_probability:independence} below.

\begin{definition}[\textbf{Independence of Events}]
    \label{def:probability:cond_probability:independence}
    Two events, $A$ and $B$ are said to be independent of each other if, and only if the following criteria holds:

    \begin{itemize}
        \item $P(A \vert B) = P(A)$
        \item $P(B \vert A) = P(B)$
        \item $P(A \cap B) = P(A)P(B)$
    \end{itemize}

    otherwise events $A$ and $B$ are said to be \textit{dependent} random events.
\end{definition}

Events can also be considered together. The laws of probability for multiple events are presented next.

\section{Two Laws of Probability for Multiple Events}
\label{sec:probability:multiple_events}

Often times probabilities are calculated by considering multiple random events together. Suppose there are two random events $A$ and $B$, then one can calculate the probability of the union and intersection of these events. From this concept, two laws of probability can be formulated. These are referred to as the \textit{multiplicative} and \textit{additive} laws of probability \cite{ref:wackerly:2014} and is given below in Theorems \ref{th:probability:multiple_events:multiplicative} and \ref{th:probability:multiple_events:additive} respectively.

\begin{theorem}[\textbf{The Multiplicative Law of Probability}]
    \label{th:probability:multiple_events:multiplicative}
    The probability of the intersection of two events $A$ and $B$ is given as

    \begin{equation*}
        \begin{split}
            P(A \cap B)
            &= P(A)P(B \vert A) \\
            &= P(B)P(A \vert B)
        \end{split}
    \end{equation*}

    If $A$ and $B$ are independent, then

    \begin{equation*}
        P(A \cap B) = P(A)P(B)
    \end{equation*}
\end{theorem}

\begin{proof}
    Proof is given from Definition \ref{eq:probability:cond_probability} above.
\end{proof}

\begin{theorem}[\textbf{The Additive Law of Probability}]
    \label{th:probability:multiple_events:additive}
    The probability of the union of two events $A$ and $B$ is given as

    \begin{equation*}
        P(A \cup B) = P(A) + P(B) - P(B \cap A)
    \end{equation*}
\end{theorem}

\begin{proof}
    The proof of the additive law of probability is supported by the Venn Diagram presented in Figure \ref{fig:probability:multiple_events:additive} below. Notice that $A \cup B = A \cup ( \bar{A} \cap B)$, where $A$ and $\bar{A} \cap B$ are mutually exclusive events. Furthermore, consider that $B = (\bar{A} \cap B) \cup (A \cap B)$, where $\bar{A} \cap B$ and $A \cap B$ are mutually exclusive. Then $P(A \cup B) = P(A) + P(\bar{A} \cap B)$ and $P(B) = P(\bar{A} \cap B) + P(A \cap B)$. The equality on the right implies that $P(\bar{A} \cap B) = P(B) - P(A \cap B)$. By substituting the expression for $P(\bar{A} \cap B)$ into the expression for $P(A \cup B)$, one can obtain the result $P(A \cup B) = P(A) + P(B) - P(A \cap B)$.
\end{proof}

\begin{figure}[htbp]
    \includegraphics[width=\textwidth]{images/additive_law_of_probability_proof.png}
    \caption{A Venn-Diagram showing the proof of the additive law of probability for multiple events.}
    \label{fig:probability:multiple_events:additive}
\end{figure}

The next section presents Bayes' Theorem and it is shown how it is related to conditional probability.

\section{Bayes' Theorem}
\label{sec:probability:bayes_theorem}

Bayes' Theorem, named after Thomas Bayes, describes the probability of an event $A$, based on prior knowledge of conditions that might be related to $A$ \cite{ref:zalta:2015}. On order to derive the formal theorem and proof, first consider Definition \ref{def:probability:bayes_theorem:partition} below \cite{ref:zalta:2015}.

\begin{definition}
    \label{def:probability:bayes_theorem:partition}
    For some positive integer, $k$, let the sets $B_{1}, B_{2}, \dots, B_{k}$ be such that

    \begin{enumerate}
        \item $S = B_{1} \cup B_{2} \cup \dots \cup B_{k}$
        \item $B_{i} \cap B_{j} = \emptyset, for i \neq j$
    \end{enumerate}

    Then the collection of sets [$B_{1}$, $B_{2}$, $\dots$, $B_{k}$] is said to be a partition of S. 
\end{definition}

Bayes Theorem is then presented in Theorem \ref{th:probability:bayes_theorem:theorem} below.

\begin{theorem}[\textbf{Bayes' Theorem}]
    \label{th:probability:bayes_theorem:theorem}
    Assume that $[B_{1}, B_{2}, \dots, B_{k}]$ is a partition of $S$ such that $P(B_{i}) > 0$, for $i = 1,2, \dots, k$ then   
    \begin{equation*}
        P(B_{j} \vert A) = \frac{P(A \vert B_{j})P(B_{j})}{\sum_{i=1}^{k} P(A \vert B_{i})P(B_{i})}
    \end{equation*}
\end{theorem}

\begin{proof}
    The proof follows directly from the definition of of conditional probability as was discussed in \ref{sec:probability:cond_probability}. This is shown below

    \begin{equation*}
    \begin{split}
        P(B_{j} \vert A)
        &= \frac{P(A \cap B_{j})}{P(A)}\\
        &= \frac{P(A \vert B_{j})P(B_{j})}{\sum_{i=1}^{k} P(A \vert B_{i})P(B_{i})}
    \end{split}
    \end{equation*}
\end{proof}

One of the many applications of Bayes' Theorem is to do statistical inference. This is referred to as Bayesian inference. The theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.

Bayesian inference is fundamental to Bayesian statistics. Section \ref{sec:probability:bayesian_statistics} presents the detail around Bayesian statistics. However, a brief detour is required to present to the user, a number of probability distributions. These probability distributions are presented next. Consider now a number of probability distributions as they are implemented.

\section{Probability Distributions}
\label{sec:probability:probability_distributions}

Probability distributions are mathematical functions that give the probabilities of the occurrences of different possible outcomes in the experiment. They play a crucial role in the architecture and design of the \ac{BHH}. It will later be shown how the proposed \ac{BHH} makes extensive use of probability distributions and sampling to formulate its selection mechanism. The theory and equations presented in the following sections where all taken from \citeauthor{ref:wackerly:2014} \cite{ref:wackerly:2014}.

\subsection{Beta Distribution}
\label{sec:probability:probability_distributions:beta}

The Beta distribution is a family of univariate continuous probability distributions over some $x$, with support on the interval $[0,1]$ \cite{ref:wackerly:2014}. It is parameterised by two shape parameters $\alpha > 0$, $\alpha \in \mathbb{R}$ and $\beta > 0$, $\beta \in \mathbb{R}$. The Beta distribution is denoted as $Beta(\alpha, \beta)$. The \ac{PDF} of the Beta distribution is given below in Equation \ref{eq:probability:probability_distributions:beta:pdf}.

\begin{equation}
    \label{eq:probability:probability_distributions:beta:pdf}
    P(x \vert \alpha, \beta) = f_{Beta}(x; \alpha, \beta) = \frac{1}{B(\alpha, \beta)} x^{\alpha - 1} (1 - x)^{\beta - 1}
\end{equation}

where the normalising constant $B(\alpha, \beta)$ is defined below in Equation \ref{eq:probability:probability_distributions:beta:norm_const}.

\begin{equation}
    \label{eq:probability:probability_distributions:beta:norm_const}
    B(\alpha, \beta) = \frac{\Gamma(\alpha)\Gamma(\beta)}{\Gamma(\alpha + \beta)}
\end{equation}

and $\Gamma$ is the Gamma function as defined below in Equation \ref{eq:probability:probability_distributions:beta:gamma_func}.

\begin{equation}
    \label{eq:probability:probability_distributions:beta:gamma_func}
    \Gamma(n) = ( n - 1)!
\end{equation}

it should be noted that the Gamma function can also be written as shown in Equation \ref{eq:probability:probability_distributions:beta:gamma_func_alt} below.

\begin{equation}
    \label{eq:probability:probability_distributions:beta:gamma_func_alt}
    \Gamma(n+1) = n!
\end{equation}

It should be noted that $\alpha$ and $\beta$ determine the shape of the distribution. There exists a special case where $\alpha = \beta$. This is referred to as the \textit{symmetric} Beta distribution. In the case where $\alpha = \beta = 1$ the distribution is equivalent to the uniform distribution over all points in its support. The Beta distribution for various values of $\alpha$ and $\beta$, including the symmetric version is presented below in Figure \ref{fig:probability:probability_distributions:beta}.

\begin{figure}[htbp]
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{images/beta_various.png}
        \caption{Beta distribution}
        \label{fig:probability:probability_distributions:beta_normal}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{images/beta_cumulative.png}
        \caption{Cumulative Beta distribution}
        \label{fig:probability:probability_distributions:beta_cumulative}
    \end{subfigure}
    \par\bigskip
    \caption{An illustration of the Beta distribution (left) \cite{ref:beta:2014} as well as the cumulative Beta distribution (right) \cite{ref:cumulativebeta:2014} for various values of $\alpha$ and $\beta$ .}
    \label{fig:probability:probability_distributions:beta}
\end{figure}

The expected value of $x$ is given below in Equation \ref{eq:probability:probability_distributions:beta:expected_value}.

\begin{equation}
    \label{eq:probability:probability_distributions:beta:expected_value}
    E[x] = \frac{\alpha}{\alpha + \beta}
\end{equation}

Similarly, the expected value of the natural logarithm of $x$ can be calculated as shown below in Equation \ref{eq:probability:probability_distributions:beta:expected_value_ln}.

\begin{equation}
    \label{eq:probability:probability_distributions:beta:expected_value_ln}
    E[\ln(x)] = \psi({\alpha}) - \psi(\alpha + \beta)
\end{equation}

where $\psi$ is the logarithmic derivative of the Gamma function, called the \textit{Digamma} function. The Digamma function is given below in Equation \ref{eq:probability:probability_distributions:beta:digamma}.

\begin{equation}
    \label{eq:probability:probability_distributions:beta:digamma}
    \psi(n) = \frac{d}{dn}\ln(\Gamma(n)) = \frac{\Gamma'(n)}{\Gamma(n)}
\end{equation}

Finally, the mode of the distribution is given in Equation \ref{eq:probability:probability_distributions:beta:mode} below.

\begin{equation}
    \label{eq:probability:probability_distributions:beta:mode}
    M[x] = E[x] - 1 = \frac{\alpha - 1}{\alpha + \beta - 1}
\end{equation}

\subsection{Dirichlet Distribution}
\label{sec:probability:probability_distributions:dirichlet}

The Dirichlet distribution is a family of multivariate continuous probability distributions over some $x$ in $K$ dimensions  \cite{ref:wackerly:2014}. The Dirichlet distribution is the multivariate generalization of the Beta distribution and is thus sometimes referred to by its alternative name, the Multivariate Beta Distribution. The Dirichlet distribution is parameterised by some vector $\alpha = (\alpha_{1}$,  $\dots, \alpha_{K})$ $\forall_{k=1}^{K} \alpha_{k} > 0$, $\alpha_{k} \in \mathbb{R}$. $\alpha$ is referred to as the concentration parameter. It is later shown in Chapter \ref{chap:bhh} that this parameter plays a vital role in the optimisation process of the \ac{BHH}. The Dirichlet distribution of order $K \geq 2$ with parameters $\alpha$, denoted $Dir(\alpha)$, has a \ac{PDF} as given in Equation \ref{eq:probability:probability_distributions:dirichlet:pdf} below.

\begin{equation}
    \label{eq:probability:probability_distributions:dirichlet:pdf}
    P(x \vert \alpha) =  f_{Dir}(x; K, \alpha) = \frac{1}{B(\alpha)}  \prod_{k=1}^{K} x_{k}^{\alpha_{k} - 1}
\end{equation}

where the normalising constant $B(\alpha)$ is defined in Equation \ref{eq:probability:probability_distributions:dirichlet:norm_cost}.

\begin{equation}
    \label{eq:probability:probability_distributions:dirichlet:norm_cost}
    B(\alpha) = \frac{\prod_{k=1}^{K} \Gamma(\alpha_{k})}{\Gamma(\alpha_{0})}
\end{equation}

and $\alpha_{0}$ is defined in Equation \ref{eq:probability:probability_distributions:dirichlet:alpha_0} below.

\begin{equation}
    \label{eq:probability:probability_distributions:dirichlet:alpha_0}
    \alpha_{0} = \sum_{k=1}^{K}\alpha_{k}
\end{equation}

Importantly, the set $\{x_{k}\}_{k=1}^{K}$ belongs to the standard $K-1$ probability simplex $S$, meaning that $x_{K} = 1 - \sum_{k=1}^{K-1}x_{k}$ with support $\forall_{k=1}^{K} x \in [0,1]$. Under the simplex $S$, this means that the sum over all values of the vector $x$ must be 1. The simplex can thus be rewritten as $\sum_{k=1}^{K}x_{k} = 1$.

Similar to the Beta distribution, $\alpha$ determines the shape of the distribution in $K$ dimensions and thus, there also exist a special case, referred to as the \textit{symmetric} distribution when $\forall_{k=1}^{K} \alpha_{k} = c$, where $c$ is some constant. In the case where $c = 1$, the distribution is referred to as a \textit{flat} distribution and yields the uniform distribution over all points in $S$. The Dirichlet distribution of order $K = 3$, for various values of $\alpha$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:dirichlet} below.

\begin{figure}[htbp]
    \includegraphics[width=\textwidth]{images/dirichlet.jpg}
    \caption{The \acp{PDF} for the Dirichlet distribution over the 2-simplex. The concentration parameter $\alpha$ is varied. The values of $\alpha$ are set to (1.5, 1.5, 1.5), (5, 5, 5), (1, 2, 2), and (2, 4, 8) respectively, read from top to bottom, left to right. The values of the \ac{PDF} are shown by the color maps with contour lines at equal values as indicated in the color bars \cite{ref:dirichlet:2020}.}
    \label{fig:probability:probability_distributions:dirichlet}
\end{figure}

The expected value of $x$ can be calculated as shown in Equation \ref{eq:probability:probability_distributions:dirichlet:expected_value} below.

\begin{equation}
    \label{eq:probability:probability_distributions:dirichlet:expected_value}
    E[x_{k}] = \frac{\alpha_{k}}{\alpha_{0}}
\end{equation}

Similarly, the expected value of the natural logarithm of $x_{k}$ can be calculated as defined in Equation \ref{eq:probability:probability_distributions:dirichlet:expected_value_ln} below.

\begin{equation}
\label{eq:probability:probability_distributions:dirichlet:expected_value_ln}
    E[\ln(x_{k})] = \psi({\alpha_{k}}) - \psi(\alpha_{0})
\end{equation}

where $\psi$ is the Digamma function as defined in Equation \ref{eq:probability:probability_distributions:beta:digamma}. Finally, the mode of the distribution is given in Equation \ref{eq:probability:probability_distributions:dirichlet:mode} below.

\begin{equation}
    \label{eq:probability:probability_distributions:dirichlet:mode}
    \begin{split}
    	M[x_{k}] &= E[{x_{k}] -K^{-1}} \\
    		&=  \frac{\alpha_{k} - 1}{\alpha_{0} - K}
    \end{split}
\end{equation}

\subsection{Bernoulli Distribution}
\label{sec:probability:probability_distributions:bernoulli}

The Bernoulli distribution is a discrete probability distribution over some random variable $x$ that takes the value of $1$ with probability $\theta$ and $0$ with probability $1-\theta$  \cite{ref:wackerly:2014}. It is denoted as $Ber(\theta)$ with support $x \in \{0, 1\}$. In probability theory, the Bernoulli distribution is often used to explain the possible outcomes of a single experiment that asks a \textit{yes-no} question such as flipping a coin. The outcome of such an experiment is a boolean value. The Bernoulli distribution has a \ac{PMF} as given below in Equation \ref{eq:probability:probability_distributions:bernoulli:pmf}.

\begin{equation}
    \label{eq:probability:probability_distributions:bernoulli:pmf}
    P(x \vert \theta) = f_{Ber}(x; \theta) =
	\begin{cases}
		\theta & \text{if}\ x=1 \\
      	1 - \theta & \text{if}\ x=0
	\end{cases}
\end{equation}

The above equation can also be expressed as show in Equation \ref{eq:probability:probability_distributions:bernoulli:alt} below.

\begin{equation}
    \label{eq:probability:probability_distributions:bernoulli:alt}
    f_{Ber}(x; \theta) = \theta^{x}(1-\theta)^{1-x}
\end{equation}

The mean of the Bernoulli distribution approaches $\theta$ over many samples according to the \ac{CLT} \cite{ref:grinstead:1997}. Figure \ref{fig:probability:probability_distributions:bernoulli:coin} shows a simulation of a fair-coin flipping simulation. One can see how the mean converges to 0.5 for various sample sizes.

\begin{figure}[htbp]
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{images/coin_flip_samples_100.png}
        \caption{100 Samples}
        \label{fig:probability:probability_distributions:bernoulli:coin_100}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{images/coin_flip_samples_10000.png}
        \caption{1000 Samples}
        \label{fig:probability:probability_distributions:bernoulli:coin_1000}
    \end{subfigure}
    \par\bigskip
    \caption{An illustration of the the coin flip situation for different sample sizes that show the convergence of the mean as per the \ac{CLT}.}
    \label{fig:probability:probability_distributions:bernoulli:coin}
\end{figure}

The expected value of the distribution is thus given according to Equation \ref{eq:probability:probability_distributions:bernoulli:expected_value} below.

\begin{equation}
    \label{eq:probability:probability_distributions:bernoulli:expected_value}
    E[x] = \theta
\end{equation}

while the mode of the distribution is given in Equation \ref{eq:probability:probability_distributions:bernoulli:mode} below.

\begin{equation}
    \label{eq:probability:probability_distributions:bernoulli:mode}
    M[x_{k}] = 
    \begin{cases}
    	0 & \text{if}\ \theta < 0.5 \\
        	0,1 & \text{if}\ \theta = 0.5 \\
        	1 & \text{if}\ \theta > 0.5 \\
    \end{cases}
\end{equation}

\subsection{Binomial Distribution}
\label{sec:probability:probability_distributions:bin}

The Binomial distribution is a discrete probability distribution over a random variable $x$ taking on a number of successes in $N$ sequential independent experiments that each ask a \textit{yes-no} question \cite{ref:wackerly:2014}. The probability of a single independent experiment yielding a success is given as $\theta$ and the Binomial distribution is denoted as $Bin(N, \theta)$ with support $x \in \{0, 1, \dots, N\}$.  It should be noted that the Binomial distribution is the extension of the Bernoulli distribution over $N$ independent sequential experiments and thus, each experiment also yields some boolean outcome. When $N=1$, the experiment is referred to as a Bernoulli trial and the distribution is just a Bernoulli distribution. When $N > 1$, the sequence of outcomes is referred to as a Bernoulli process. The \ac{PMF} of the Binomial distribution is given in Equation \ref{eq:probability:probability_distributions:binomial:pmf} below.

\begin{equation}
    \label{eq:probability:probability_distributions:binomial:pmf}
    P(x \vert \theta; N) = f_{Bin}(x; N, \theta) = \binom{N}{x} \theta^{x}(1-\theta)^{1-x}
\end{equation}

Similar to the Bernoulli distribution, the mean of the Binomial distribution is $N\theta$ given the \ac{CLT} as was shown in Figure \ref{fig:probability:probability_distributions:bernoulli:coin}. The expected value of the Binomial distribution is thus given in Equation \ref{eq:probability:probability_distributions:binomial:expected_value} below.

\begin{equation}
    \label{eq:probability:probability_distributions:binomial:expected_value}
    E[x] = N\theta
\end{equation}

The mode of the distribution is given in Equation \ref{eq:probability:probability_distributions:binomial:mode} below.

\begin{align}
    \label{eq:probability:probability_distributions:binomial:mode}
    \begin{split}
    M[x_{k}] &= E[x] + \theta \\
    	&= N\theta  + \theta \\
    	&= (N  + 1)\theta
    \end{split}
\end{align}

\subsection{Categorical Distribution}
\label{sec:probability:probability_distributions:categorical}

The Categorical distribution is a discrete probability distribution over some random variable $x$, taking on any one of $K$ possible categories \cite{ref:wackerly:2014}. There is no innate underlying ordering to these categories and therefore, for simplicity, each category is assigned a numerical representative value such that $k = (1, \dots, K)$. The probabilities for all outcomes is given by the probability vector $\theta = (\theta_{1}, \dots, \theta_{K})$.  This means that the probability $P(x=k)=\theta_{k}$ has support $x \in \{1, \dots, K\}$. The Categorical distribution, denoted $Cat(\theta)$ is the generalization of the Bernoulli distribution and is sometimes referred to it by its alternative names, the generalised Bernoulli Distribution or the Multinoulli distribution. In probability theory, the Categorical distribution is often used to explain the outcome of a single experiment with more than two possible outcomes such as rolling a die \cite{ref:wackerly:2014}. The \ac{PMF} of the Categorical distribution is given in Equation \ref{eq:probability:probability_distributions:categorical:pmf} below.

\begin{equation}
    \label{eq:probability:probability_distributions:categorical:pmf}
    P(x \vert \theta; K) = f_{Cat}(x; K, \theta) = \prod_{k=1}^{K}\theta_{k}^{[x = k]}
\end{equation}

where $[x = k]$ is the Iversion Bracket \cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise. From this, one can conclude that for a given class $k$, the categorical distribution simply yields $\theta_{k}$ as is shown in Equation \ref{eq:probability:probability_distributions:categorical:pmf_k} below.

\begin{equation}
    \label{eq:probability:probability_distributions:categorical:pmf_k}
    f_{Cat}(x=k; K, \theta) = \theta_{k}
\end{equation}

The random variable $x$ can also be encoded in binary format, yielding a vector $x = (x_{1}, \dots, x_{K})$ of Bernoulli distributions such that the support is $\forall_{k=1}^{K} x_{k} \in \{0, 1\}$. Importantly, if the outcome of the random event is of category $k$, then $x_{k} = 1$ and $\forall_{j=1}^{K} x_{j} = 0, j \neq k$ so that the standard $K-1$ probability simplex $S$ still holds. The \ac{PMF} of the Categorical distribution can then be rewritten as follows in Equation \ref{eq:probability:probability_distributions:categorical:pmf_alt} below.

\begin{equation}
    \label{eq:probability:probability_distributions:categorical:pmf_alt}
    f_{Cat}(x; K, \theta) = \prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{k})}
\end{equation}

where $\mathbbm{1}(x_{k})$ is the \textit{indicator function}, yielding 1 if $x_{k} = 1$ and 0 otherwise.

Since there is no innate order to the underlying categories, the mean of the distribution does not yield any relevant information. The mode of the distribution is given in Equation \ref{eq:probability:probability_distributions:categorical:mode} below.

\begin{equation}
    \label{eq:probability:probability_distributions:categorical:mode}
    M[x] = \argmax_{k}(\theta_{1}, \dots, \theta_{K})
\end{equation}

\subsection{Multinomial Distribution}
\label{sec:probability:probability_distributions:multinomial}

The Multinomial distribution is a discrete probability distribution over some random variable $x = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials \cite{ref:wackerly:2014}. The probabilities for all possible outcomes in a single trial is given by the probability vector $\theta = (\theta_{1}, \dots, \theta_{K})$. The Multinomial distribution, denoted $Mul(N, K, \theta)$, is thus the generalization of the Binomial distribution to $K$ dimensions. Consider the following special cases.

\begin{itemize}
	\item When $K$ is 2 and $N = 1$, the Multinomial distribution is the Bernoulli distribution.
	\item When $K$ is 2 and $N > 1$, the Multinomial distribution is the Binomial distribution.
	\item When $K > 2$ and $N = 1$, the Multinomial distribution is the Categorical distribution.
\end{itemize}

The support for the Multinomial is $\forall_{i=1}^{K} x_{k} \in \{1, \dots, N\}, \sum_{k=1}^{K}x_{k} = N$ and the \ac{PMF} for the Multinomial distribution is given below in Equation \ref{eq:probability:probability_distributions:multinomial:pmf}.

\begin{equation}
    \label{eq:probability:probability_distributions:multinomial:pmf}
    P(x \vert \theta; N; K) = f_{Mul}(x; N, K, \theta) = \frac{N!}{\prod_{k=1}^{K}x_{k}!} \prod_{k=1}^{K}\theta_{k}^{x_{k}}
\end{equation}

Similar to the Categorical distribution, the random variable $x$ can also be encoded in binary format, yielding an $N \times K$ matrix $X$ of Bernoulli distributions. The support is then given as $X \in \{0, 1\}^{N \times K}, \forall_{i=1}^{N}\sum_{k=1}^{K} x_{i,k} = 1$ so that the standard $K-1$ probability simplex $S$ still holds for each trial. The \ac{PMF} of the Multinomial distribution can then be rewritten as is presented in Equation \ref{eq:probability:probability_distributions:multinomial:pmf_alt}

\begin{equation}
    \label{eq:probability:probability_distributions:multinomial:pmf_alt}
    \begin{split}
    f_{Mul}(x; N, K, \theta) &= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!}\prod_{i=1}^{N}\prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{i,k})} \\
    	&= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!} \prod_{k=1}^{K}\theta_{k}^{\sum_{i=1}^{N}\mathbbm{1}_{1}(x_{i,k})} \\
    	&= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!} \prod_{k=1}^{K}\theta_{k}^{N_{k}} \\
    \end{split}
\end{equation}

where $N_{k}$ is a summary variable denoting the number of times a category $k$ occurs over all trials in $N$.

The reason why the Categorical and Multinomial distributions are presented as binary encoded vectors is to simplify the proof of their conjugate priors as will be shown next. This is further supported by the fact that \acp{NN} often use binary encoding of feature vectors. The combination of these probabilistic methods and \acp{NN} forms the basic of this dissertation.

\section{Conjugate Priors}
\label{sec:probability:conjugate_priors}

\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} states that conjugate priors are prior probability distributions that results in posterior distributions that are of the same functional form $\mathcal{A}(v)$ as the prior, but with different parameter values. This section considers the conjugate priors for the Binomial likelihood and Categorical/Multinomial likelihood. Each of these are presented next.

\subsection{Binomial Likelihood}
\label{sec:probability:conjugate_priors:binom_likelihood}

The conjugate prior to a Bernoulli distribution is the Beta distribution
\cite{ref:wackerly:2014}. This is shown by demonstrating that the posterior distribution has the
same functional form $\mathcal{A}(v)$ as the prior distribution as follows. \\\\
\textbf{Setup}:

\begin{itemize}
	\item Let $I$ be a number of independent, identical  (iid) random events.

	\item Let $\alpha \in \mathbb{R}, \alpha > 0$ and $\beta \in \mathbb{R}, \beta >0$ be the shape parameters to the Beta distribution.

	\item Let $\theta$ be the probability of a success. With $\theta | \alpha, \beta \sim Beta(\alpha, \beta)$.

	\item $P(\theta)$ is the prior probability distribution with the functional form $\mathcal{A}(v)$.

	\item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with boolean outcome. That is $x_{i} | \theta \overset{\text{iid}}{\sim} Ber(\theta)$ and thus $\mathcal{L}(x_{i} \vert \theta)$ is the Bernoulli likelihood.

	\item Let $\mathcal{D}$ denote all the prior data $X$, parameterised by $\alpha$, $\beta$.

	\item Let $N_{1} = \sum_{i=1}^{I} \mathbbm{1}(x_{i} = 1)$ and $N_{0} = \sum_{i=1}^{I} \mathbbm{1}(x_{i} = 0)$.
\end{itemize}

The Bernoulli likelihood is then given in Equation \ref{eq:probability:conjugate_priors:binom_likelihood:likelihood} below.

\begin{equation}
    \label{eq:probability:conjugate_priors:binom_likelihood:likelihood}
    \begin{split}
    	\mathcal{L}(\mathcal{D}) &=  P(\mathcal{D} | \theta) \\
    	&\propto \theta^{N_{1}}(1-\theta)^{N_{0}}
    \end{split}
\end{equation}

By Bayes Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation \ref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.

\begin{equation}
\begin{split}
    \label{eq:probability:conjugate_priors:binom_likelihood:posterior}
	P(\theta \vert \mathcal{D}) &= \frac{P(\mathcal{D} | \theta) P(\theta)}{P(\mathcal{D})}
\end{split}
\end{equation}

Since the denominator sums to $1$, one could get rid of the denominator and constants for the Bernoulli likelihood and the Beta prior, by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation \ref{eq:probability:conjugate_priors:binom_likelihood:posterior_propto} below.

\begin{equation}
    \label{eq:probability:conjugate_priors:binom_likelihood:posterior_propto}
    \begin{split}
    		P(\theta | \mathcal{D}) &\propto \left[\theta^{N_{1}}(1-\theta)^{N_{0}}\right] \left[\theta^{\alpha - 1} (1 - \theta)^{\beta - 1}\right] \\
    		&\propto \theta^{(N_{1} + \alpha) - 1}(1-\theta)^{(N_{0} + \beta) - 1} \\
    		&\propto Beta(N_{1} + \alpha, N_{0} + \beta) 
    \end{split}
\end{equation}

It is show that the posterior distribution is of the same functional form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N_{1} + \alpha$ and $\beta' = N_{0} + \beta$. This shows that the Beta distribution is the conjugate prior to the Bernoulli likelihood.

\subsection{Categorical and Multinomial Likelihood}
\label{sec:probability:conjugate_priors:cat_mult_likelihood}

The conjugate prior to a Categorical and Multinomail distribution is the Dirichlet distribution \cite{ref:wackerly:2014}. Similar to the proof of the conjugate prior for the Bernoulli distribution as shown in Section \ref{eq:probability:conjugate_priors:binom_likelihood:posterior} above, this means that the posterior distribution must have the same functional form $\mathcal{A}(v)$ as the prior distribution. This is shown as follows. \\\\
\textbf{Setup}:

\begin{itemize}
	\item Let $I$ be a number of independent, identical (iid) random events.

	\item Let $K$ be a number of possible outcomes for each event, with $K \geq 2$.

	\item Let $\alpha = (\alpha_{1}, \dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} \in \mathbb{R}, \alpha_{k} > 0$ be the concentration parameters to the Dirichlet distribution.

	\item Let $\theta = (\theta_{1}, \dots, \theta_{K}), \forall_{k=1}^{K} \theta{k} \in (0,1), \sum_{k}^{K} \theta{k} = 1$ be the probability of each class in $K$ and $\theta$ belongs to the standard $K-1$ probability simplex $S$. With $\theta | \alpha \sim Dir(K, \alpha)$.

	\item $P(\theta)$ is the prior probability distribution with the functional form $\mathcal{A}(v)$.

	\item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with $K$ possible outcomes. That is $x_{i} | \theta \overset{\text{iid}}{\sim} Cat(\theta)$ and thus $\mathcal{L}(x_{i} \vert \theta)$ is the Categorical likelihood.

	\item Let $\mathcal{D}$ denote all the prior data $X$, parameterised by $\alpha$.

	\item Let $N = (N_{1}, \dots, N_{K}), N_{k} = \sum_{i=1}^{I} \mathbbm{1}(x_{i,k} = 1)$, denote the counts for each occurrence of a class $k$.
\end{itemize}

The likelihood of the Categorical and Multinomial distributions is then given in Equation \ref{eq:probability:conjugate_priors:mult_likelihood:likelihood} below.

\begin{equation}
    \label{eq:probability:conjugate_priors:mult_likelihood:likelihood}
    \begin{split}
    	\mathcal{L}(\mathcal{D}) &=  P(\mathcal{D} | \theta) \\
    	&\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}}
    \end{split}
\end{equation}

By Bayes Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation \ref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.

\begin{equation}
    \label{eq:probability:conjugate_priors:mult_likelihood:posterior}
    \begin{split}
    	P(\theta \vert \mathcal{D}) &= \frac{P(\mathcal{D} \vert \theta) P(\theta)}{P(\mathcal{D})}
    \end{split}
\end{equation}

Since the denominator sums to $1$, one could get rid of the denominator and constants for the Dirichlet prior,by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation \ref{eq:probability:conjugate_priors:mult_likelihood:posterior_propto} below.

\begin{equation}
    \label{eq:probability:conjugate_priors:mult_likelihood:posterior_propto}
    \begin{split}
    	P(\theta \vert \mathcal{D}) &\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}} \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} - 1}\\
    	&\propto \prod_{k=1}^{K} \theta_{k}^{(N_{k} + \alpha_{k}) - 1} \\
    	&\propto Dir(K, N + \alpha) 
    \end{split}
\end{equation}

Is it shown that the posterior distribution is of the same form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N + \alpha$. This shows that the Dirichlet distribution is the conjugate prior to the Categorical and Multinomial likelihood.

The next section aims to provide the reader with the concept of Bayesian statistics and it is shown how Bayesian inference and Bayesian analysis can be used to to train a \ac{HH}.

\section{Bayesian Statistics}
\label{sec:probability:bayesian_statistics}

In general, there are two main views to probability and statistics. These include the \textit{frequentist} and the \textit{Bayesian} view of statistics. Naturally, Bayesian statistics is based on Bayes' Theorem as was presented in Section \ref{sec:probability:bayes_theorem}. Bayesian statistics describe the probability of an event in terms of some belief based on previous knowledge of the event and the conditions under which the event happens \cite{ref:hackenberger:2019}. To introduce the concept of Bayesian inference and analysis, one first need to understand the difference between these two approaches. Bayesian statistics out-date the frequentist approach, but lacked interest in the early days partly because of the limited applications where the conjugate priors where known \cite{ref:hackenberger:2019}. More recent advancements in mathematical methods popularised the Bayesian approach again. A notable contribution to this switch was the invention of \ac{MCMC} in the 1950's. This family of algorithms allowed for the construction of random sampling algorithms from a probability distribution which allows for the calculation of Bayesian hierarchical models \cite{ref:hackenberger:2019}. Soon after followed one of the earliest papers that use Bayesian statistics in the field of medicine in 1982 \cite{ref:ashby:2006}.

The difference between the frequentist approach and the Bayesian approach can be illustrated using an example. \citeauthor{ref:hackenberger:2019} \cite{ref:hackenberger:2019} suggests an experiment that investigates whether the sex ration in some hypothetical mice population is $1:1$. Two experiments can be designed. In the first experiment, mice are randomly selected until the first male is chosen. The result in this experiment will then be the total number of mice chosen by sex. For the second experiment, exactly seven mice are randomly selected. The result of the second experiment would be the number of males and females in a sample of seven. Suppose the outcome of the experiment was $FFFFFFM$, where $F$ represents a female and $M$ represents a male. If the experimental design is not known ahead of time, the result is useless. Consider the $P$-value for each of these experiments. The P-value is the probability of obtaining results at least as extreme as the observed results of a statistical hypothesis test \cite{ref:beers:2022}. For the first experiment, the $P$-value is $0.031$ and for the second experiment, the $P$-value is $0.227$. Using a confidence level of $\alpha = 0.05$, one would conclude opposite outcomes for these two experiments when it comes to rejecting the null hypothesis, despite using the same data. The reason for this difference is because of the difference in their null distributions. The first approach uses a geometrical approach and the second used a binomial approach as is illustrated on Figure \ref{fig:probability:bayesian_statistics:mouse_experiment_outcome} below.

\begin{figure}[htbp]
    \includegraphics[width=\textwidth]{images/mouse_experiment_outcome.jpg}
    \caption{The experimental outcomes for the mice-population experiments as was taken from \cite{ref:hackenberger:2019} .}
    \label{fig:probability:bayesian_statistics:mouse_experiment_outcome}
\end{figure}

If Bayesian statistics is used then the experimental design that was chosen does not matter. In Bayesian statistics it is common to use a Beta distribution as a prior distribution. If the prior distribution is sampled from $Beta(3,3)$ then using Bayesian analysis, the posterior distribution, according to the outcomes of this experiment, would yield $Beta(9,4)$. The process by which this is done is shown later in this section. The $Beta$ distribution was presented in Section \ref{sec:probability:probability_distributions:beta}. \citeauthor{ref:hackenberger:2019} \cite{ref:hackenberger:2019} mentions that the $Beta$ distribution can be seen as a probability distribution of the occurrence of specific parameters. From the information that is now known about the $Beta$ distribution, it is possible to calculate the probability that the sex ratio in this mice population is not 1:1 with the $Beta$ distribution as a prior, yielding a $P$-value of $0.92$. This means that there is a probability of $92\%$ that the mice population is not 1:1, regardless of experiment design. This is illustrated in Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} below.

\begin{figure}[htbp]
    \includegraphics[width=\textwidth]{images/mouse_experiment_distributions.jpg}
    \caption{An illustration of the prior and posterior probability distributions for the outcomes of the mice-population experiment, using a $Beta$ prior, as was taken from \cite{ref:hackenberger:2019}.}
    \label{fig:probability:bayesian_statistics:mouse_distributions}
\end{figure}

One can see from Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} how the posterior distribution differs from the prior distribution. This is the nature of Bayesian analysis and is presented in more detail next.

\subsection{Bayesian Analysis}
\label{sec:probability:bayesian_statistics:bayesian_analysis}

Bayesian analysis is the process by which prior beliefs are updated as a result of observing new data/evidence. Similar to the approaches followed above to explain Bayesian statistics, a proposal is made to explain Bayesian analysis by means of an example taken from \cite{ref:wackerly:2014}. Let $Y_{1}, Y_{2}, \dots, Y_{N}$ denote the random variable that is observed over a sample size of $N$. Then the likelihood of the sample is given as $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$. In the discrete case this function is defined to be the joint probability $P(Y_{1} = y_{1}, Y_{2} = y_{2}, \dots, Y_{N} = y_{n})$ and the continuous case yields the joint density of $Y_{1}, Y_{2}, \dots, Y_{N}$, evaluated at $y_{1}, y_{2}, \dots, y_{n}$. The Bayesian view models the parameter $\theta$ as a random variable with a probability distribution. This probability distribution is referred to as the prior distribution of $\theta$. The symbol $\theta$ is included in the notation of $\mathcal{L}$ as an argument to illustrate that this function is dependent explicitly on the value of $\theta$. Importantly, this prior distribution is specified before any data is collected and represents the theoretical prior knowledge about $\theta$. Assume that the parameter $\theta$ has a continuous distribution with density $g(\theta)$ that has no unknown parameters. Considering the likelihood of the data and the prior on $\theta$, then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ is given in Equation \ref{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood} below.

\begin{equation}
    \label{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood}
    f(y_{1}, y_{2}, \dots, y_{n}, \theta) = \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)
\end{equation}

The marginal density or mass function of $Y_{1}, Y_{2}, \dots, Y_{N}$ is given in Equation \ref{eq:probability:bayesian_statistic:bayesian_analysis:marginal_density} below.

\begin{equation}
    \label{eq:probability:bayesian_statistic:bayesian_analysis:marginal_density}
    m(y_{1}, y_{2}, \dots, y_{n}) = \int_{-\infty}^{\infty} \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)d\theta
\end{equation}

Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$ according to Bayes' Theorem is given in Equation \ref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.

\begin{equation}
    \label{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density}
    g^{*}(\theta \vert y_{1}, y_{2}, \dots, y_{n}) = \frac{\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)}{\int_{-\infty}^{\infty} \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)d\theta}
\end{equation}

\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} mentions that the posterior density summarises all the pertinent information about the parameter $\theta$ by making use of the information contained in the prior for $\theta$ as well as the information in the observed data/evidence. Consider now how Bayesian analysis can used to update the priors on $\theta$ based on newly observed data. As with the example above, the below is taken from \cite{ref:wackerly:2014}.

Let $Y_{1}, Y_{2}, \dots, Y_{N}$ denote a random sample from a $Bernoulli$ distribution where $P(Y_{i} = 1) = \theta$ and $P(Y_{i} = 0) = 1 - \theta$ and the prior distribution for $\theta$ is $Beta(\alpha, \beta)$. The formulation of the posterior distribution for $p$ is then shown as follows. Since the $Bernoulli$ probability function can be written as

\begin{equation*}
    P(y_{i} \vert \theta) = \theta^{y_{i}}(1 - \theta)^{1-y_{i}}
\end{equation*}

where $y_{i} = \{0,1\}$ and $0 < \theta < 1$. The likelihood $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$ is

\begin{equation*}
    \begin{split}
        \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)
        &= P(y_{1}, y_{2}, \dots, y_{n} \vert \theta)\\
        &= \theta^{y_{1}}(1-\theta)^{1 - y_{1}} \times \theta^{y_{2}}(1-\theta)^{1 - y_{2}} \times \dots \times \theta^{y_{n}}(1-\theta)^{1 - y_{n}}\\
        &= \theta^{\sum y_{i}}(1-\theta)^{n-\sum y_{i}}
    \end{split}
\end{equation*}

Then

\begin{equation*}
    \begin{split}
        f(y_{1}, y_{2}, \dots, y_{n}, \theta)
        &= \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)\\
        &= \theta^{\sum y_{i}}(1-\theta)^{n-\sum y_{i}} \times \frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\alpha - 1}(1 - \theta)^{\beta  - 1}\\
        &= \frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}
    \end{split}
\end{equation*}

The marginal density of $Y_{1}, Y_{2}, \dots Y_{N}$ is then given as

\begin{equation*}
    \begin{split}
        m(y_{1}, y_{2}, \dots, y_{n})
        &= \int_{0}^{1}\frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}d\theta\\
        &= \frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\frac{\Gamma(\sum y_{i} + \alpha)\Gamma(n - \sum y_{i} + \beta)}{\Gamma(n + \alpha + \beta)}
    \end{split}
\end{equation*}

Finally, the posterior density of $\theta$ is given as

\begin{equation*}
    \begin{split}
        g^{*}(\theta \vert y_{1}, y_{2}, \dots, y_{n})
        &= \frac{\frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}}{\frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\frac{\Gamma(\sum y_{i} + \alpha)\Gamma(n - \sum y_{i} + \beta)}{\Gamma(n + \alpha + \beta)}}\\
        &= \frac{\Gamma(n + \alpha + \beta)}{\Gamma(\sum y_{i} + \alpha)\Gamma(n - \sum y_{i} + \beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}
    \end{split}
\end{equation*}

From the above, one can see that the posterior density has the same functional shape $\mathcal{A}(v)$ as the prior, yielding the update on prior parameters as $\alpha^{*} = \sum y_{i} + \alpha$ and $\beta^{*} = n - \sum y_{i} + \beta$.

\section{Summary}
\label{sec:probability:summary}

This chapter provided the reader with all the necessary background on probability theory and statistics that is required to formulate the \ac{BHH}. Detailed mathematical descriptions have been provided on probability distributions and proofs of conjugate priors are provided with detailed mathematical descriptions. Bayesian statistics have been presented in detailed and finally, it has been shown how Bayesian analysis works. The formulation of the \ac{BHH} is provided in the next chapter.

### 2022-09-12 dissertation/chapters/06-bayesian-hyper-heuristic.tex
📝 (review): First set of changes

\chapter{Bayesian Hyper-Heuristic}
\label{chap:bhh}

\begin{quote}
    \textit{
    ``The result is a posterior distribution which the agent may use as its new prior in the next step.'' - Pedro Domingos, The Master Algorithm: How the Quest for the Ultimate Learning Machine Will Remake Our World.
    }
\end{quote}

The above quote was the inspiration for the development of a novel \ac{HH} that uses \index{Bayesian}\textit{Bayesian} probability concepts as a selection mechanism to drive the heuristic selection process. Thus far the reader was presented with all of the necessary background information on \acp{ANN} in Chapter \ref{chap:anns}, low-level \index{heuristic}heuristics/\index{Optimiser}optimisers in Chapter \ref{chap:heuristics}, \acp{HH} in Chapter \ref{chap:hhs}  and lastly, \index{probability theory}probability theory in Chapter \ref{chap:probability}. These elements form the fundamental components that make up the proposed \Ac{BHH}. A detailed specification on the \Ac{BHH} can now be formulated. This chapter provides the detail around the theory, concept and implementation of the \Ac{BHH} and explains how it used to train \acp{ANN}. It is shown throughout this chapter that the \Ac{BHH} implements a probabilistic optimisation technique that implements and biases a \index{Gaussian Process}\textit{Gaussian process} towards good optimisation and performance. The remainder of the chapter is structured as follows:

\begin{itemize}
    \item \textbf{Section \ref{sec:bhh:overview}} provides a brief overview of the \Ac{BHH} optimiser.

    \item \textbf{Section \ref{sec:bhh:architecture}} presents the general architecture, \Ac{HH} framework and the various components that make up the \index{Optimiser}optimiser.

     \item \textbf{Section \ref{sec:bhh:heuristic_pool}} discusses the collection of low-level \index{heuristic}heuristics, referred to as the \index{heuristic}\textit{heuristic pool} and puts emphasis on the importance of a diverse set of low-level \index{heuristic}heuristics.

    \item \textbf{Section \ref{sec:bhh:entity_pool}} discusses the detail of the \index{Population}population and its \index{entity}entities, with specific detail provided on entity (local) and population (global) state and memory.

    \item \textbf{Section \ref{sec:bhh:initialisation_step}} presents the initialisation strategy in detail.

    \item \textbf{Section \ref{sec:bhh:selection_mechanism}} presents the \index{Bayesian}\textit{Bayesian} probabilistic model that is used as a selection mechanism.

    \item \textbf{Section \ref{sec:bhh:heuristic_entity_selections}} discusses heuristic-entity selections and how these two concepts are utilised together.

    \item \textbf{Section\ref{sec:bhh:model}} discusses the models that can be optimised using the \Ac{BHH}, specifically referring to its application to training \acp{FFNN}.

    \item \textbf{Section \ref{sec:bhh:train_test_datasets}} briefly discussed the role of the train and test datasets during training.

    \item \textbf{Section \ref{sec:bhh:loss_function}} discusses model evaluation and the role of the loss/cost function.

    \item \textbf{Section \ref{sec:bhh:domain_barrier}} discusses the domain barrier that exists between the high-level \ac{BHH} and low-level heuristics in the \index{heuristic pool}heuristic pool.

    \item \textbf{Section \ref{sec:bhh:performance_log}} presents the performance log and discusses performance measurement in more detail.

    \item \textbf{Section \ref{sec:bhh:credit_assignment_strategy}} discussed credit assignment and move acceptance strategies in detail.

    \item \textbf{Section \ref{sec:bhh:optimisation_step}} presents the learning mechanisms by which the probabilistic model can be optimised.

    \item \textbf{Section \ref{sec:bhh:hyper_parameters}} summarises and discusses the associated \index{hyper-parameters}hyper-parameters and default values.

    \item The pseudo-code algorithm for the \ac{BHH} is given in \textbf{Section \ref{sec:bhh:algorithm}}.

    \item Finally, a summary of the chapter is provide in \textbf{Section \ref{sec:bhh:summary}}.
\end{itemize}

\section{Overview}
\label{sec:bhh:overview}

This section provides an overview of the workings of the \Ac{BHH}. To start the discussion, consider the following analogy:\\
\\
\textit{
    Bob is a teacher at a high school. Every year his students perform really well and he wins the prize for best teacher, evaluated by student performance. He is able to do this not just because he is a good teacher, but he understands that each student has a learning technique that works best for him/her. He exploits this concept by tailoring the teaching process to each students such that the result is an optimum mark for that student and by definition, the whole class. Bob knows that it is too timely to get to know each student, so he devises a model that does the allocations for him. This model uses a process of observation. With each evaluation opportunity he experiments by allocating different learning techniques to different students. He evaluates the student for the given opportunity and keeps a log of which learning technique he assigned to the student as well as the outcome. With each evaluation opportunity he updates his model by biasing the assignment process such that students generally get assigned learning techniques that yield the best performance for them.
}\\
\\
The key take-out from the analogy above is the concept that Bob can maximise student performance by updating his beliefs, over time, about which learning technique to assign to which (type of) student. He does this by biasing selection/assignment towards the best combinations of student, learning technique
and evaluation opportunity. This is the basic nature of the \Ac{BHH}. The students are analogous to a population of entities. The learning techniques are analogous to heuristics/optimisers. Evaluation opportunities are analogous to optimisation problems to be optimised. Student performance is analogous to optimisation capability and performance measurement. The general goal of the \ac{BHH} can be summarised as aiming to select and managing the appropriate  heuristic/optimiser and update step for each entity, at each optimisation step, while optimising some underlying model, which for this dissertation, is to train \acp{FFNN}.

Formal classification of the \Ac{BHH} is needed. Burke et al. \cite{ref:burke:2010} proposed a classification mechanism that was discussed in detail in Chapter \ref{chap:hhs}. The same classification mechanism is used to classify the \ac{BHH}. For the first dimension of the classification, the authors propose that the \Ac{BHH} be classified as a \textit{selection} \ac{HH}. For the second dimension of the classification proposed, the authors propose that the \Ac{BHH} be classified as utilising \textit{perturbation} low-level heuristics. Furthermore, the \ac{BHH} is also classified as a population-based approach that includes meta-heuristics. Burke et al. \cite{ref:burke:2010} further proposed the classification of \acp{HH} according to the source of the feedback used during learning. It can thus be said that the \ac{BHH} employs online learning according to this criteria, classifying it as an \textit{adaptive} \ac{HH}. A \textit{population-based, selection, meta-hyper-heuristic that utilised perturbation of low-level heuristics and online learning} seems like an mouthful, but technically, that is it's full and formal classification. A breakdown and motivation of these classifications is given below:

\begin{itemize}
    \item \textbf{Population-Based:} The \ac{BHH} follows a population-based approach where a number of different \index{candidate solution}candidate solutions, referred to as \index{entity}\textit{entities} work together to yield a global best solution. There is also the concept of a shared global state or memory.

    \item \textbf{Selection:} The \ac{BHH} implements a \index{heuristic}heuristic selection mechanism that selects from a collection of lower level \index{heuristic}heuristics' in a so-called \index{heuristic hool}\textit{heuristic pool}. There is also a measure of acceptance criteria through credit assignment strategies.

    \item \textbf{Meta:} Incorporates the classical/analytical gradient-based low level \index{heuristic}heuristics (typically from the \ac{ML} research space) as well as meta-heuristics such as other population-based \index{Meta-Heuristic}meta-heuristics (typically \ac{EC} research space).

    \item \textbf{Hyper-Heuristic:} There exists a domain barrier where the \ac{BHH} searches through the \textit{heuristic space} while lower level heuristics search through the \textit{solution space}.

    \item \textbf{Perturbation of Low-Level Heuristics:} Refers to the iterative optimisation approach followed by the \ac{BHH}. The \ac{BHH} considers a number of randomly initialised candidate solutions in the form of entities in a population. It is applied in an iterative manner, during the training process. It generally employs the two main processes of \acp{HH} with perturbation of heuristics. These include a \textit{selection step} that selects from low-level heuristics and applies them to entities/candidate solutions. It also includes an \textit{acceptance strategy}. The \ac{BHH} maintains entity and population state through update step operations that proxy update steps from different heuristics. More details on this concept is given later in Section \ref{sec:bhh:heuristic:proxies}.

    \item \textbf{Online Learning:} Refers to the source of the feedback used during training. The \ac{BHH} optimises, at a higher level, the selection and application of the \index{heuristic-space}\textit{heuristic-space} while low-level heuristics optimise entities' solution to the underlying model, in this case a \ac{FFNN}. This happens during training time, yielding the classification of utilising \textit{online} learning.
\end{itemize}

More detailed consideration of these elements are required. The following sections break down the \Ac{BHH} into its various parts, starting with a discussion on the high-level architecture next.

\index{Architecture}
\section{Architecture}
\label{sec:bhh:architecture}

This section aims to present the reader with all the high level components in the architecture of the \Ac{BHH}. Burke et al. \cite{ref:burke:2010} proposed an initial framework for \acp{HH} and Grobler \cite{ref:grobler:2015} further proposed a framework for a heterogeneous meta-\ac{HH}. These frameworks have been adapted for the implementation of the \Ac{BHH}. An illustration of the high-level architecture of the \Ac{BHH} is given in Figure \ref{fig:bhh_architecture} below.

\begin{figure}[H]
    \centering
    \includegraphics[width=1.0\textwidth]{bhh_architecture.png}
    \caption[The \index{Bayesian Hyper-Heuristics}Bayesian Hyper-Heuristic Architecture]{An illustration of
    the architecture and high level components of the \index{Bayesian Hyper-Heuristics}Bayesian Hyper-Heuristic.}
    \label{fig:bhh_architecture}
\end{figure}

At a high level, the architecture presented in Figure \ref{fig:bhh_architecture} above, presents the following main components:

\begin{itemize}
    \item \textbf{Heuristic Pool}: Contains a collection of low-level \index{heuristic}heuristics/\index{optimiser}optimisers. This is the \index{heuristic space}\textit{heuristic} space. Each heuristic has a proxy that is used to relay heuristic state update operations.

    \item \textbf{Entity Pool}: A collection of \index{entity}entities in a \index{population}population. These entities represent candidate solutions to the model. Each entity has its own state, but there is also a shared global population state.

    \item \textbf{Initialisation Step}: This is the execution of some initialisation strategy that determines how the entities in the entity pool (population) and the heuristics in the heuristic pool are initialised.

    \item \textbf{Selection Mechanism}: This is the implementation of the selection mechanism of selection \acp{HH}. In the case of the \ac{BHH}, the selection mechanism is a Bayesian probabilistic model.

    \item \textbf{Heuristic-Entity Selections}: This is the results of the selection mechanism. Heuristics are sampled/selected for each entity. Each entity's state will thus be manipulated by that particular heuristic's proxy methods.

    \item \textbf{Model}: The \index{model}model to be optimised. This forms the problem domain. In the case of this dissertation, the model is a \ac{FFNN}.Technically the model here simply refers to the architectural structure of the model, while entities represent that candidate solution (weights) to the model.

    \item \textbf{Train and Test Datasets}: The training set is used to train the model while the test set is used to evaluate the model's generalisation capabilities.

    \item \textbf{Loss/Cost Function}: The loss/cost function is the metric  by which the model is evaluated. In the case of supervised learning, the loss/cost function is a measure of distance between predicted output and the ground truth.

    \item \textbf{Domain Barrier}: A constraint on information flow, prohibiting high level components in the \index{heuristic space}\textit{heuristic} space from interacting and relaying information related to the \index{solution space}\textit{solution} space.

    \item \textbf{Performance Log}: Contains a record of heuristic-entity performance at each step of the training process.

    \item \textbf{Credit Assignment Strategy}: Implements a specific strategy to determine if the performance of an entity-heuristic combination is better than others or not.

    \item \textbf{Update Step}: The high level heuristic update step. This involves the mechanism by with the \ac{BHH} is optimised.
\end{itemize}

The above components are not described in enough detailed to properly illustrate their role in the \Ac{BHH}. To ensure proper clarity is given to each of these elements, a detailed discussion on each of these elements are presented next.

\index{Heuristic Pool}
\section{Heuristic Pool}
\label{sec:bhh:heuristic_pool}

This section discusses the concept of the heuristic pool, as implemented by the \ac{BHH}. Generally speaking, they heuristic pool is just a collection of low-level heuristics and make up the set of possible heuristics to select from. This is referred to as \text{heuristic space}. Importantly, since \acp{HH} optimise in heuristic space, it is from these lower-level heuristics that the \ac{BHH} must select and apply. The heuristic pool can then be defined in terms of size and/or heuristics that are included in the pool. These two aspects pose very important design choices. Both of these concepts can be empirically tested, however, one could argue the choice of design. Fundamentally, these design choices are about diversity. A brief discussion is given next on the trade-offs between exploration, exploitation and capability.

\index{Exploration}
\index{Exploitation}
\subsection{Diversity: Exploration, Exploitation and Capability}
\label{sec:bhh:heuristic_pool:diversity}

As with all \acp{HH}, the heuristics to be included in the heuristic pool is of great importance and should be carefully decided upon. A heuristic's eligibility for inclusion is determined by the following factors:

\begin{itemize}
    \item \textbf{Capability}: Certain heuristics are only capable of solving or optimising for certain problem types and domains. Examples include continuous vs. discrete, differentiable vs.  non-differentiable or static vs. dynamic problems.

    \item \textbf{Exploration and Exploitation Trade-off}: Some heuristics explore or exploit more than others. This could be due to the nature of the implementation or due to some hyper-parameter such as a learning rate.
\end{itemize}

An argument for diversity must thus be made. One of the benefits of \acp{HH} in general is that it will learn which heuristics to apply and when. The trade-off between exploration and exploitation should thus be outsourced to the \ac{BHH} itself. By including a diverse set of heuristics, based on the criteria mentioned above, the \ac{BHH} will learn to select and apply the appropriate heuristic at the appropriate time throughout the training process, naturally balancing a trade-off between exploration and exploitation. Heuristics that initially explore a lot should be selected when exploration is needed and heuristics that exploit a lot should be selected accordingly.

Notice however that diversity can not be achieved by simply including many different heuristics. The \ac{BHH} is still constraint by heuristic pool size. Consider that for every heuristic that is included, the demand for samples size required to learn with statistical certainty exponentially increases. Not only does a large heuristic pool drastically complicate the learning that is required by the \ac{BHH}, but it also drastically complicates the process of maintaining state. The next section provides the concept of heuristic update step proxies, an important component of the \ac{BHH}.

\index{Proxies}
\subsection{Proxies}
\label{sec:bhh:heuristic:proxies}

The concept of proxies arise from the sparsity of state as maintained by different heuristics. Since heuristics maintain different states, there is an uncertainty of state transition when switching between heuristics. Consider an example where the heuristic pool consists of just two heuristics. One heuristic is a gradient-based heuristic that maintains momentum such as \ac{Adam}. The other is a meta-heuristic that does not require a gradient at all such as \ac{PSO}. Both these heuristics track different parameters in their state. For \ac{Adam}, the expected gradient mean and variance is maintained, while the \ac{PSO} maintains record of the gbest and pbest solutions all of entities. A solution to this is to proxy heuristic state update operations. This allows us to maintain state in two parts:

\begin{itemize}
    \item \textbf{Primary State}: This refers to state the is originally maintained by a heuristic. The selected heuristic simply applies the normal state update operations to its state.

    \item \textbf{Proxied State}: This refers to state that is not directly maintained by the current selected heuristic, but can be updated by outsourcing the required state update operation to another heuristic.
\end{itemize}

Effectively this means that both primary and proxied state elements must be maintained together. Since entities represent candidate solutions, which are a form of state, entities are ideal components to store these state parameters. Thus, entities are extended to include the primary state elements of all the underlying low-level heuristics as well as the candidate solution (weights) for the model. At each heuristic-entity application step, all state elements per entity are updated either by primary method or by proxied method. The \ac{BHH} thus incorporates a state update operation proxy mapping as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.

\begin{table}[htbp]
	\centering
	\caption{State update operation proxy mapping example.}
	\label{tab:bhh:heuristic_pool:proxy_mapping_example}%
	\par\bigskip
	\resizebox{0.5\textwidth}{!}{
        \begin{tabular}{ccccc}
              &       & \multicolumn{3}{c}{State Parameter} \\
    \cmidrule{3-5}          &       & 1     & 2     & 3 \\
    \cmidrule{3-5}    \multirow{3}[1]{*}{Heuristic} & A     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} \\
              & B     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A} \\
              & C     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A} \\
        \end{tabular}%
    }
\end{table}%

From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when heuristic A is selected, it will outsource state update operations from heuristic B, for state parameter 2. Heuristic B will outsource from heuristic A, for state parameter 3. Finally, heuristic C will outsource from heuristic A and B, for state parameters 2 and 3 respectively. In this way, all heuristics maintain all the state parameters.

Notice however that this is a simple concept in principle, but requires detailed decomposition of the heuristics included in the heuristic pool.  Overlapping and unique state parameters must be identified so that a proxy mapping such as the one given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} can be constructed. A suggestion to simplify this process is to borrow concepts from the equations of motion from physics. These include \textit{position}, \textit{velocity}, \textit{acceleration} and \textit{momentum}. Expressing heuristic update steps according to these parameters drastically simplify the process. However, it is possible that heuristics implement unique state parameters that do not overlap, these have to be catered for in the proxy mapping.

These state parameters and update operations should not be considered in isolation. An example of this is position and velocity. Consider for example heuristics such as \acl{DE} and \aclp{GA}. These heuristics recombine entities. In this case, the concept of an equation of motion does not entirely make sense, since the displacement of its position is not a result of maintaining velocity or momentum, but rather by pure displacement through recombination. In this particular case, a solution to this is to apply the recombination operation to all secondary state parameters as well or to nullify secondary state parameters. Unfortunately there is no general solution and each heuristic must be carefully considered. The \ac{BHH} incorporates both of these approaches. The next section provides the reader with details around the entity pool.

\index{Entity Pool}
\section{Entity Pool}
\label{sec:bhh:entity_pool}

This section presents the details around the \index{entity pool}\textit{entity pool}. The \index{entity pool}entity pool refers to a collection of so-called individual \index{entity}\textit{entities}. A common naming convention for such a collection is a \textit{population} of entities. Similar to the heuristic pool that was described in Section \ref{sec:bhh:heuristic_pool} above, the entity pool size is an important design choice. The correct population size is thus a hyper-parameter that can be empirically evaluated.

The entity pool maintains two different types of state. These include entity (local) and population (global) state. Each of these are discussed in more detail next.

\index{Entity State}
\subsection{Entity State}
\label{sec:bhh:entity_pool:entity_state}

\index{entity}Entities represent \index{candidate solution}candidate solutions to the \index{model}model's trainable parameters (weights) and other heuristic-specific state parameters as was just discussed above in Section \ref{sec:bhh:heuristic:proxies}. It can be said that entities implement \textit{local} state. It was mentioned that these \index{entity}entities can be treated as physical \index{particle}\textit{particles} in a hyper-dimensional physical environment. This means that these \index{entity}entities model concepts from physics. For example, the candidate solution is represented as the \index{entity}entity's \textit{position} and an \index{entity}entity's velocity and acceleration, is analogous to the gradient and momentum of an \index{entity}entity respectfully. Examples of \index{Entity State}entity state parameters as derived from various low-level heuristics is given as follows:

\begin{itemize}
    \item \textbf{position}: General parameter that represents the actual candidate solution and is thus a primary state parameter for all heuristics.

    \item \textbf{velocity}: Directly implemented by heuristics such as \acp{PSO} can be derived proportionally from the gradient for gradient-based heuristics such as \ac{Momentum}.

    \item \textbf{gradient}: The last know gradient as derived from gradient-based heuristics.

    \item \textbf{position delta}: The last computed position delta between the current timestep and the previous timestep.

    \item \textbf{sum of the gradients squared}: As required and maintained by heuristics such as \ac{Adagrad}.

    \item \textbf{expected position delta variance}: As required and maintained by heuristics such as \ac{Adadelta}.

    \item \textbf{expected gradient mean}: As required and maintained by heuristics such as \ac{Momentum}, \ac{NAG} and \ac{Adam}.

    \item \textbf{expected gradient variance}: As required and maintained by heuristics such as \ac{RMSProp}, \ac{Adadelta} and \ac{Adam}.

    \item \textbf{personal best position}: Parameter that tracks that best known position by the entity thus far. As required and maintained by heuristics such as \ac{PSO}.

    \item \textbf{personal best loss}: Parameter that tracks that best known loss by the entity thus far. As required and maintained by heuristics such as \ac{PSO}.

    \item \textbf{loss}: General parameter that tracks the loss as achieved by the the entity throughout training.
\end{itemize}

From the list above it should become clear that entity state becomes increasingly complicated as the number of distinct heuristics included in the heuristic pool increases. Consider next the global state that is maintained.

\index{Population State}
\subsection{Population State}
\label{sec:bhh:entity_pool:population_state}

The \index{Population State}\textit{population state} refers to a collection of parameters that are shared between the \index{entity}entities in the population. This state is also referred to as \index{global state}\textit{global} state and represents the entity pool's memory of the population. The \index{population state}population state generally contains state parameters that are of importance to multiple heuristics and usually track the state of the population as a whole and not individual heuristic states. Some examples of population state that can arise from different heuristics is given below:

\begin{itemize}
    \item \textbf{\textit{entities}}: Naturally, the population state contains the list of entities in the population. List size determined by \index{Population Size}population size. Naturally this list contains multiple entities as with population based approaches such as \acp{PSO} and \acp{GA}.

    \item \textbf{\textit{ibest}} and \textbf{\textit{ibest loss}}: Refers to the best position and loss achieved by the population for the current iteration/step. This parameter is introduced by the \ac{BHH} itself through the requirements of the \textit{ibest} credit assignment strategy.

    \item \textbf{\textit{rbest}} and \textbf{\textit{rbest loss}}: Refers to the best position and loss achieved by the population for the current replay buffer/window size. This parameter is introduced by the \ac{BHH} itself through the requirements of the \textit{rbest} credit assignment strategy.

    \item \textbf{\textit{gbest}} and \textbf{\textit{gbest loss}}: Refers to the overall/global best position and loss achieved by the population for the entire training process. This parameter is introduced by heuristics such as \acp{PSO} and is also introduced by the \ac{BHH} itself through the requirements of the \textit{gbest} credit assignment strategy.
\end{itemize}

The reader was now introduced to both the heuristic pool and entity pool. The next section considers how the \ac{BHH} is initialised and makes specific reference to how these two pools of elements are initialised.

\section{Heuristic-Entity Selections}
\label{sec:bhh:heuristic_entity_selections}

The \ac{BHH} selects from the heuristic pool a low-level heuristic to be applied to an entity. The outcome of this selection process is a table that tracks which heuristic has been selected for which entity. The selection process is executed by the selection mechanism of the \ac{BHH} and is discussed later in Section \ref{sec:bhh:selection_mechanism}. These heuristic-entity combinations are applied to an underlying model. The next section provides clarity on the model component from the architecture of the \ac{BHH}.

\index{Model}
\section{Model}
\label{sec:bhh:model}

The \index{Model}model refers to the target \index{model}model to be optimised and is usually expressed as a complex mathematical function. For this dissertation, the authors focused specifically on shallow \acp{FFNN} (only one hidden layer). Figure \ref{fig:shallow_ffnn} below presents such a shallow \acp{FFNN}.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\textwidth]{shallow_ffnn.png}
    \caption[Shallow \index{Feedforward Neural Network}Feedforward Neural Network]{An illustration of
    a shallow \index{Feedforward Neural Network}Feedforward Neural Network.}
    \label{fig:shallow_ffnn}
\end{figure}

\section{Train and Test Datasets}
\label{sec:bhh:train_test_datasets}

The training of \ac{FFNN} is a supervised learning problem as was highlighted in Chapter \ref{chap:anns}. Therefore, the \ac{BHH} trains the model on training data from the training set, while is reserves an unseen set of test data in the test dataset for evaluation. It should be mentioned that the goal of the \ac{BHH} is to generalise well to the test set across a number of problem domains. As was previously mentioned, the test set should be sufficiently large to truly evaluate for generalisation capabilities. For the \ac{BHH}, it is proposed to have a 80-20\% split between the training and test set.

\section{Loss/Cost Function}
\label{sec:bhh:loss_function}

Chapter \ref{chap:anns} presented the concept of a loss/cost function that is used to evaluate the performance of \acp{ANN}. The \ac{BHH} uses this loss/cost function to evaluate the performance of a heuristic-entity combination. For classification problems, generally some entropy loss is used. For classification problems with 2 classes, \ac{BinXE} is used and for classification problems with more than 2 classes, the \ac{SparseCatXE} is used. For regression problems it is recommended to use some mean error measurement such as \ac{MSE} or \ac{RMSE}.

The loss/cost function is very important as this metric is used to evaluate model performance as a result of the application of a heuristic to an entity's candidate solution. The \ac{BHH} used this performance metric to bias towards good heuristic-entity combinations.  The continuous valued cost/loss function is translated into a discrete valued representation through a credit assignment strategy that is implemented in the \ac{BHH}. The credit assignment strategies is discussed in Section \ref{sec:bhh:credit_assignment_strategy}.

\section{Domain Barrier}
\label{sec:bhh:domain_barrier}

The domain barrier presents the boundary of information flow between the heuristic space and the solution space. It is mentioned in Section \ref{sec:bhh:loss_function} that the heuristic-entity loss is used by the \ac{BHH}. Notice that the \ac{BHH} uses this performance information and no information from the solution space itself. Furthermore, the \ac{BHH} maps this loss to a credit assignment problem as is mentioned by Burke et al. \cite{ref:burke:2010}. The \ac{BHH} at a high level, is not aware of the actual candidate solution that is represented by the entity, but rather just that there is a candidate solution with a unique identifier that, together with a heuristic, produced a certain level of performance. The domain barrier is a feature that occurs in al \acp{HH}.  Burke et al. \cite{ref:burke:2010} states that the \ac{HH} collects domain-independent information from the domain barrier. A number of examples of domain independent information is given, these include the number of heuristics, the changes in evaluation function, whether a new solution was found or generated, the distance between two solutions, whether it has become stuck.

\index{Performance Log}
\section{Performance Log}
\label{sec:bhh:performance_log}

Recall that the \ac{BHH} incorporates a Bayesian probabilistic implementation. Evidence is required to train the \ac{BHH}. The performance log is used to keep memory of a slice of the performance history. The performance log is simply a tabular implementation that tracks random events. The \ac{BHH} suggests the following metrics to keep track of in the performance log:

\begin{itemize}
    \item \textbf{step}: The current mini-batch step.

    \item \textbf{heuristic}: The selected heuristics' index.

    \item \textbf{entity}: The applied entity's index.

    \item \textbf{loss}: The heuristic-entity performance metric.

    \item \textbf{ibest loss}: Keeps track of the \textit{iteration} best loss. Thus, the best loss value achieved by all all entity-heuristic combinations for a single mini-batch step.

    \item \textbf{rbest loss}:  Keeps track of the \textit{replay} best loss. Thus, the best loss value achieved by all all entity-heuristic combinations over all mini-batch steps currently in the performance log.

    \item \textbf{gbest loss}:  Keeps track of the \textit{global} best loss. Thus, the best loss value achieved by all all entity-heuristic combinations over all mini-batch steps thus far.
\end{itemize}

The performance log as implemented by the \ac{BHH} is given in Table \ref{tab:bhh:performance_log:performance_log_example} below.

\begin{table}[htbp]
	\centering
	\caption{Performance log example showing the first 5 entity's selected heuristics for step 1 and their resulting performance measurements.}
	\label{tab:bhh:performance_log:performance_log_example}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
        \begin{tabular}{cccccccc}
            \textbf{step} & \textbf{entity} & \textbf{heuristic} & \textbf{loss} & \textbf{ibest loss} & \textbf{pbest Loss} & \textbf{rbest loss} & \textbf{gbest loss} \\
            \midrule
            1     & 1     & 1     & 0.016444 & 0.016444 & 0.016444 & 0.016444 & 0.016444 \\
            1     & 2     & 2     & 0.337965 & 0.016444 & 0.337965 & 0.016444 & 0.016444 \\
            1     & 3     & 1     & 0.134781 & 0.016444 & 0.134781 & 0.016444 & 0.016444 \\
            1     & 4     & 1     & 0.998719 & 0.016444 & 0.998719 & 0.016444 & 0.016444 \\
            1     & 5     & 3     & 0.708702 & 0.016444 & 0.708702 & 0.016444 & 0.016444 \\
        \end{tabular}%
    }
\end{table}%

The performance log itself introduces a number of design considerations as well. Since the log contains a slice of memory, there should exists a trade-off between the following parameters:

\begin{itemize}
    \item \textbf{performance log size}: The larger the performance log, the longer memory is retained.The performance log size controls the recency of evidence from which new beliefs must be derived. This parameter is called the \textit{replay} window size, a term borrowed from \ac{RL} and should be empirically tested. If the replay window size is too small, it does not accumulate enough samples/evidence to really statistically make accurate classifications. If the replay window size is too back, the \ac{BHH} might remember too much of past performance and it could be that past performance is not indicative of future performance during the training process. Notice then that the performance log must be pruned to maintain a fixed replay window size. Dynamic replay window sizes is left as a research component for the future.

    \item \textbf{performance log reanalysis}: Consider the temporal nature of the performance log. Since it tracks all random events across all steps in the training process, it is needed to reanalyse the performance log appropriately in order to update the past information in the performance log with newly added data. An example of this is when a new rbest value has been found. Then the entire performance log's rbest loss must be updated.
\end{itemize}

The performance log should be considered along with the selection of credit assignment strategy used. These are discussed next.

\index{Credit Assignment Strategy}
\section{Credit Assignment Strategy}
\label{sec:bhh:credit_assignment_strategy}

The credit assignment strategy is an implementation that maps a continuous performance metric into a discrete credit metric. This component implements the ``move acceptance'' process as proposed by Özcan et al. \cite{ref:ozcan:2006,ref:ozcan:2008}. It determines if a given performance is deemed good or not. This simple discrete transformation is subject to the credit assignment problem as discussed by Burke et al. \cite{ref:burke:2010}. A good credit assignment strategy will correctly allocate credit to the appropriate heuristic-entity combination. THe magnitude of this credit is to be empirically tested.  It is later shown how these credit metrics are used to accumulate ``pseudo counts'' which concentrates/biases heuristic selection towards good performing heuristics. The \ac{BHH} propose the following initial credit assignment strategies.

\begin{itemize}
    \item \textbf{ibest}: Credit is assigned to the heuristic-entity combination that set the \textit{ibest} loss value, meaning that it is the entity-heuristic combination that achieved the best performance in the current mini-batch iteration.

    \item \textbf{pbest}: Credit is assigned to the heuristic-entity combination that set the \textit{pbest} loss value, meaning that it is the entity-heuristic combination that was able to improve on it's personal best past performance loss.

    \item \textbf{rbest}: Credit is assigned to the heuristic-entity combination that set the \textit{rbest} loss value, meaning that it is the entity-heuristic combination that achieved the best performance in the current replay window.

    \item \textbf{gbest}: Credit is assigned to the heuristic-entity combination that set the \textit{gbest} loss value, meaning that it is the entity-heuristic combination that achieved the overall best performance so far.

    \item \textbf{symmetric}: A credit assignment strategy that gives credit to all entity-heuristic combinations regardless of performance. This credit assignment strategy suggests that ``symmetric'' credit assignment be given. As a result, any bias that arise from uncertainty or as a result of an untrained \ac{BHH} model, in the beginning, is maintained and further strengthened throughout the training process . Notice that this credit assignment strategy does not randomly assign credit, it simply assigns credit to the all events that are a result of random selection, which could be possibly be biased.
\end{itemize}

The implementation of a credit assignment strategy is a pure, stateless function that translates input $P$ from the performance log into output $C$ as is given in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example} below.

\begin{table}[htbp]
	\centering
	\caption{Credit assignment strategy output table showing \textit{ibest} credit assignment for the first 5 entity's and their selected heuristics for step 1 of the training process.}
	\label{tab:bhh:credit_assignment_strategy:credit_assignment_example}%
	\par\bigskip
	\resizebox{0.4\textwidth}{!}{
        \begin{tabular}{cccc}
            \textbf{step} & \textbf{entity} & \textbf{heuristic} & \textbf{credit} \\
            \midrule
            1     & 1     & 1     & true \\
            1     & 2     & 2     & false \\
            1     & 3     & 1     & false \\
            1     & 4     & 1     & false \\
            1     & 5     & 3     & false \\
        \end{tabular}%
    }
\end{table}%

Credit assignment is a key component of the \ac{BHH} is it will later be shown in Section \ref{sec:bhh:optimisation_step} how these credit assignments are used to optimise the \ac{BHH}. First, it is necessary to present the selection mechanism.

\index{Selection Mechanism}
\section{Selection Mechanism}
\label{sec:bhh:selection_mechanism}

This section aims to provide the reader with the detail around the selection mechanism as it is implemented by the \ac{BHH}. It is mentioned throughout this document that the \ac{BHH} implements a predictive model based on Bayesian probabilistic concepts. In probabilistic modeling it is necessary to identify all the random events that can occur.

\index{Random Events}
\subsection{Random Events}
\label{sec:bhh:selection_mechanism:random_events}

Observation of random events is treated as evidence. In the context of a Bayesian approach, this evidence is used to update prior beliefs. The \ac{BHH} distinguishes between the following events:

\begin{itemize}
    \item \textbf{$H$}: The event of observing \textit{heuristics}.
    \item \textbf{$E$}: The event of observing \textit{entities}. 
    \item \textbf{$C$}: The event of observing \textit{credit assignments}.
\end{itemize}

It should be noted that this information is observed direclty from the performance log presented in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example} above. From the above list, the event $C$ is dependent on the occurrence of $H$ and $E$. However, for simplification, an argument for independence can be made.

\index{Independence}
\subsection{Independence}
\label{sec:bhh:selection_mechanism:independence}

The dependence between random events can have a drastic impact on the probabilistic model that is implemented. For simplicity, the \ac{BHH} assumes independence between events, although the event $C$ is clearly dependent on the occurrence of $H$ and $E$. Notice that the \ac{BHH} is fundamentally a classifier, classifying which heuristic to select given an entity and performance criteria. It is later shown in Section \ref{sec:bhh:selection_mechanism:naive_bayes} that the \ac{BHH} implements a Naïve Bayes classifier. Domingos et al. \cite{ref:domingos:1997} mentions that although Bayesian classifiers’ probability estimates are only optimal under quadratic loss if the independence assumption holds, the classifier itself can be optimal under zero-one loss (misclassification rate) even when this assumption is violated by a wide margin. This means that independence can be assumed when the probabilistic model is used as a classifier and not to get real probabilities. Evaluating for proportionality and not precision allows for the assumption of independence.

\index{Bayes' Theorem}
\subsection{Bayes' Theorem}
\label{sec:bhh:selection_mechanism:bayes_theorem}

Section \ref{sec:bhh:selection_mechanism:random_events} presented the reader with the random events that are observed by the \ac{BHH} and Section \ref{sec:bhh:selection_mechanism:independence} provided an argument for independence between events. Chapter \ref{chap:probability} presented Bayes Theorem, but for convenience, it is given again in Equation \ref{eq:bhh:selection_mechanism:bayes_theorem} below.

\begin{equation}
    \label{eq:bhh:selection_mechanism:bayes_theorem}
    P(A \vert B) = \frac{P(B \vert A)P(A)}{P(B)}
\end{equation}

As was indicated in Section \ref{sec:bhh:selection_mechanism:independence}, Equation \ref{eq:bhh:selection_mechanism:bayes_theorem} can be evaluated for proportionality since the \ac{BHH} is not concerned with actual accurate selection probabilities, but rather implements a Bayesian classifier. The resulting proportionality is expressed in Equation \ref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} below

\begin{equation}
    \label{eq:bhh:selection_mechanism:bayes_theorem_prop_to}
    P(A \vert B) \propto P(B \vert A)P(A)
\end{equation}

Notice how the Equation \ref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} implements a Bayesian conditionally. This conditionality can be extended to include multiple criteria. The next section shows how the Bayesian classifier is implemented by providing the detail around the implemented predictive model.

\subsection{Predictive Model}
\label{sec:bhh:selection_mechanism:predictive_model}

Finally the reader is presented with the underlying predictive model as implemented by the \ac{BHH}. This component is arguably the most important component of the entire \ac{BHH} as it fundamentally drives the output of the \ac{BHH}. Bayes Theorem as was shown again in Section \ref{sec:bhh:selection_mechanism:bayes_theorem} above can be used to implement a predictive model to predict which heuristic to select, given the conditionality of a particular entity and a particular credit assignment criteria is met. Consider the following setup. Let

\begin{itemize}
    \item $I$: Denote the maximum number of instances in the replay window.
    \item $J$: Denote the entity pool (population) size.
    \item $K$: Denote the heuristic pool size.
    \item $L$: Denote the number of credit assignment output classes. Since the output of credit assignment is boolean, $L = 2$.

    \item $\alpha = (\alpha_{1}, \dots, \alpha_{K})$: Denote the concentration parameters for the heuristic probability distribution.
    \item $\beta = (\beta_{1}, \dots, \beta_{K})^{J}$: Denote the concentration parameters for the entity-heuristic probability distributions.
    \item $\gamma = (\gamma_{1}, \dots, \gamma_{K})^{L}$: Denote the concentration parameters for the credit-heuristic probability distribution.

    \item $\theta \vert \alpha \sim Dir(\alpha; K)$: Denote the heuristic probability distribution, implementing a Dirchlet probability distribution parameterised by $\alpha$ and $K$. Heuristic selection probabilities are sampled from this distribution.
    \item $\phi \vert \beta \sim Dir(\beta; K)^{J}$: Denote the entity-heuristic probability distribution, implementing a Dirchlet probability distribution parameterised by $\beta$ and $K$ for each entity in the entity pool with population size $J$. Entity-heuristic probabilities are sampled from this distribution.
    \item $\psi \vert \gamma_{1}, \gamma_{0}  \sim Beta(\gamma_{1}, \gamma_{0})$: Denote the credit-heuristic probability distribution, implementing a Beta probability distribution parameterised by $\gamma_{1}$ and $\gamma_{0}$. Credit-heuristic probabilities are sampled from this distribution.

    \item $H \vert \theta \sim Mult(\theta; I, K)$: Denote the distribution of heuristics (event $H$), implementing a Multinomial distribution, parameterised by the sampled heuristic selection probability $\theta$, the heuristic pool size $K$ and maximum number of instances $I$.
    \item $E \vert \phi \sim Mult(\phi; I, K)^{J}$: Denote the distribution of entity-heuristic combinations (event $E$), implementing a Multinomial distribution, parameterised by the sampled entity-heuristic selection probability $\phi$, the heuristic pool size $K$ and maximum number of instances $I$, for each entity in $J$.
    \item $C \vert \psi \sim Bin(\psi, I)$: Denote the distribution of credit-heuristic combinations (event $C$), implementing a Binomial distribution, parameterised by the sampled credit-heuristic selection probability $\psi$ and the maximum number of instances $I$.
\end{itemize}

The parameterised predictive model, as derived from Bayes theorem presented in Equation \ref{eq:bhh:selection_mechanism:bayes_theorem} is then given in Equation \ref{eq:bhh:selection_mechanism:predictive_model} below.

\begin{equation}
    \label{eq:bhh:selection_mechanism:predictive_model}
    \begin{split}
        P(H \vert E, C;  \theta, \phi, \psi)
        &= \frac{
            P(E, C \vert H;  \phi, \psi)  P(H \vert \theta)
            }{
            P(E, C \vert \theta, \phi, \psi)
        } \\		
        &= \frac{
            P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
            }{
            P(E \vert \theta, \psi) P(C \vert \theta, \phi)
        } \\
        &= \frac{
            P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
            }{
            \left[ \sum_{k}^{K} P(E, H=k \vert \theta, \psi) \right] \left[ \sum_{k}^{K}  P(C, H=k \vert \theta, \phi) \right]
        } \\
        &= \frac{
            P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
            }{
            \left[ \sum_{k}^{K} P(E \vert H=k \vert \phi) P(H=k \vert \theta) \right] \left[ \sum_{k}^{K} P(C \vert H=k \vert \psi) P(H=k \vert \theta) \right]
        }
    \end{split}
\end{equation}

Notice the joint probability over events $E$ and $C$ given the selection of a heuristic $H$ denoted by the sums of the products of the separate parts, for $E$ and $C$, in the denominator. The calculation in the denominator can be intractable as has been previously indicated. However, in order to derive the posterior distribution as given in Equation \ref{eq:bhh:selection_mechanism:bayes_theorem}), one only has to evaluate to proportionality as is given in Equation \ref{eq:bhh:selection_mechanism:predictive_model_prop_to} below.

\begin{equation}
    \label{eq:bhh:selection_mechanism:predictive_model_prop_to}
    \begin{split}
        P(H \vert E, C;  \theta, \phi, \psi) &\propto P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
    \end{split}
\end{equation}

The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $H$, given allocation to entity $E$ and credit $C$, parameterised by sampled $\theta$, $\phi$ and $\psi$. These parameters are in turn parameterised by concentrations $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$ which denote the prior beliefs of the \ac{BHH}.

\index{Naïve Bayes}
\subsection{Naïve Bayes}
\label{sec:bhh:selection_mechanism:naive_bayes}

This section aims to dissect the probabilistic model that is presented in Equestion \ref{eq:bhh:selection_mechanism:predictive_model_prop_to}. It has been established in Section \ref{sec:bhh:selection_mechanism:independence} that for \index{Naïve Bayes} naïve Bayes classifiers, independence between events can be assumed. The following derived \acp{PMF} are provided as fundamental building blocks that are later shown to be used in the optimisation process of the \ac{BHH} as is shown in Section \ref{sec:bhh:optimisation_step}.

The independence between events for the class label $H$ simply yields the \ac{PMF} of the Multinomial distribution as presented in Equation \ref{eq:bhh:selection_mechanism:naive_bayes:h_pmf} below.

\begin{equation}
    \label{eq:bhh:selection_mechanism:naive_bayes:h_pmf}
    \begin{split}
        P(H \vert \theta)
        &\propto \prod_{i=1}^{I} \prod_{k=1}^{K} P(h_{i,k} \vert \theta_{k}) \\
        &\propto \prod_{i=1}^{I} \prod_{k=1}^{K} \theta_{k}^{\mathbbm{1}_{1}(h_{i,k})} \\
        &\propto \prod_{k=1}^{K} \theta_{k}^{\sum_{i=1}^{I} \mathbbm{1}_{1}(h_{i,k})} \\
        &\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}}
    \end{split}
\end{equation}

Where $N_{k}$ is a summary variable such that $N_{k} = \sum_{i=i}^{I}
\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the event
$h_{i}$ taking on class $k$, i.e. the count of occurrences of heuristic $k$ in
$I$ independent, identical runs.

The independence between events $E$ given class label $H$ is denoted by the likelihood of $E$
conditional to the occurrence of heuristic $k$ and model parameter $\phi$ as
presented in Equation \ref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} below.

\begin{equation}
    \label{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf}
    \begin{split}
        P(E \vert H;  \phi)
        &\propto \prod_{i=1}^{I} \prod_{j=1}^{J} \prod_{k=1}^{K} P(e_{i,j,k} \vert h_{i,k} ; \phi_{j,k})  \\
        &\propto \prod_{i=1}^{I} \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{\mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})} \\
        &\propto \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{ \sum_{i}^{I} \left[ \mathbbm{1}_{1}(e_{i,j,k}) \mathbbm{1}_{1}(h_{i,k}) \right]} \\
        &\propto \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}}
    \end{split}
\end{equation}

Where $N_{j,k}$ is a summary variable such that $N_{j,k} = \sum_{i=i}^{I}
\mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of
occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on
class $k$, i.e. the count of occurrences of both entity entity $e$ and heuristic
$k$ occurring together in $I$ independent, identical runs.

Finally, the independence between events for the performance criteria feature $C$ given class
label $H$ is denoted by the likelihood of $C$ conditional to the occurrence of
heuristic $k$ and model parameter $\psi$ as given in Equation \ref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} below.

\begin{equation}
    \label{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf}
    \begin{split}
        P(C\vert H;  \psi)
        &\propto\prod_{i=1}^{I} \prod_{k=1}^{K} P(c_{i,k} \vert h_{i,k} ; \psi_{k})  \\
        &\propto \prod_{i=1}^{I} \prod_{k=1}^{K} \psi_{k}^{\mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})} (1 - \psi_{k})^{\mathbbm{1}_{0}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})}\\
        &\propto \prod_{k=1}^{K} \psi_{k}^{\sum_{i=1}^{I} \mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})} (1 - \psi_{k})^{\sum_{i=1}^{I} \mathbbm{1}_{0}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})}\\
        &\propto \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{N_{0,k}} \\
        &\propto \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})}
    \end{split}
\end{equation}

Where $N_{k}$ is the summary variable as described for Equation \ref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above.
$N_{1,k}$ is a summary variable such that $N_{1,k} = \sum_{i=1}^{I}
\mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of
occurrences of the events $c_{i}$ taking on a success $(c_{i}=1)$ and $h_{i}$
taking on class $k$, i.e. the count of occurrences of both succeeding in the
performance criteria and heuristic $k$ occurring together in $I$ independent,
identical runs. Similarly $N_{0,k} = N_{k} - N_{1,k}$ would denote the count of
occurrences of the events $c_{i}$ taking on a failure $(c_{i}=0)$ and $h_{i}$
taking on class $k$.

Given the assumptions of the naïve Bayes classifier, one could supplement Equations \ref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}, \ref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} and \ref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above into the proportional evaluation of the predictive model as given in Equation \ref{eq:bhh:selection_mechanism:predictive_model_prop_to}. This is presented in Equation \ref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} below.

\begin{equation}
    \label{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf}
    \begin{split}
        P(H \vert E, C;  \theta, \phi, \psi)
        &\propto P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)  \\
        &\propto \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right]
    \end{split}
\end{equation}

Computationally the equation presented in Equation \ref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} will underflow if the resulting probabilities are very small.

\index{Numerical Stability}
\subsection{Numerical Stability}
\label{sec:bhh:selection_mechanism:numerical_stability}

When evaluating for Equation \ref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf}, the numerical stability is shown to underflow if the resulting probabilities from its parts are very small. Multiplying multiple fractional parameters leads to an even smaller fractional number. Probabilities might be very low at some points during training. Consider an example where training has stagnated, effectively leading to a scenario where a credit assignment strategy never fulfills a credit assignment, yielding an extremely small probability for $\psi$. A solution to this problem is to apply the \textit{log-sum-exp trick}, parameterising distributions no longer using logits rather than probabilities. The transformation of Equation \ref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} using the log-sum-exp trick is given below in Equation \ref{eq:bhh:selection_mechanism:numerical_stability:log_sum_exp}.

\begin{equation}
    \label{eq:bhh:selection_mechanism:numerical_stability:log_sum_exp}
    \begin{split}
        LSE(P(h_{k} \vert e_{j}, c_{1};  \theta, \phi, \psi)) = \ln(\exp(\phi_{j,k}) +  \exp(\psi_{k}) + \exp(\theta_{k}))
    \end{split}
\end{equation}

The log-sum-exp trick as shown above caters for very small probabilities, however, there might be a situation where  a random event is never seen, purely by chance. This results in a scenario referred to as \textit{mode collapse} and is discussed next.

\index{Mode Collapse}
\subsection{Mode Collapse}
\label{sec:bhh:selection_mechanism:mode_collapse}

Mode collapse is the situation that occurs where the selective pressure towards a heuristic is close to zero, as a results of random sampling, low initial bias or bad performance. This leads to a situation where to probabilistic model continually decrease the selective pressure until the selection probability of that heuristic is 0, yielding no further observations of that particular random event. This could be problematic and should be addressed.

The \ac{BHH} addresses this issue by:

\begin{itemize}
    \item Using \textit{symmetric} initialisation of the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$.

    \item Setting the lower-bound of the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$ to 1, so that a selection probability of 0 is highly improbable.

    \item Continuously resampling heuristics throughout the training process, before and after optimisation, eliminating mode collapse as a result of just random sampling.
\end{itemize}

Another suggestion is to ensure that at least one of every heuristic is always selected during training. The \ac{BHH} does not incorporate this model as this could result in a situation where a bad choice of heuristic is continually used throughout the training process, possibly resulting in bad update steps/selections. Instead the \ac{BHH} relies on the underlying learning process to control the selective pressure according to performance and nothing else. If this leads to a situation where mode collapse occurs, the \ac{BHH} accepts this outcome.

This section briefly touched on parameter initialisation. The next section discusses the initialisation process of the \ac{BHH} in detail.

\section{Initialisation Step}
\label{sec:bhh:initialisation_step}

This section sheds light into the initialisation of the \ac{BHH} and how it applies to the heuristic and entity pools. Since the heuristic pool is a collection of stateless heuristic proxy operations, there is no explicit initialisation that is applied to the heuristic pool itself. On the contrary, the entity pool is stateful and maintain candidate solutions. Chapter \ref{chap:anns} presented various initialisation strategies to randomly place candidate solutions in the solution space. The \ac{BHH} can make use of any of these initialisation strategies and as such, by default makes use of \index{Glorot uniform sampling}Glorot uniform sampling. All other entity state parameters are initialised to be zero.

The selection mechanism also requires initialisation. Section \ref{sec:bhh:selection_mechanism:predictive_model} introduces the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$. These parameters \textit{symmetrically} initialised, meaning that they are all initialised to the value of one in all dimensions. Section \ref{sec:bhh:optimisation_step:a_priori_bias} shows that these concentration parameters can be used to introduce \textit{a priori} biases based on expert knowledge. The next section provides the detail around the selection mechanism that is implemented by the \ac{BHH}.

\section{Optimisation Step}
\label{sec:bhh:optimisation_step}

Thus far the reader has been presented with all the fundamental components of the \ac{BHH}. The final step that is missing is to present the optimisation step by which the optimisation process takes place. This section aims to provide a solid  mathematical explanation to show exactly how the \ac{BHH} is able to learn.

The \ac{BHH} is an adaptive \ac{HH}, meaning that it implements online learning. Online learning refers to the continuous learning process that is executed by the \ac{BHH} while training is taking place. Throughout the training process, concentration parameters are updated strategically to guide the selection mechanism towards heuristics that perform well. The learning capability of the \ac{BHH} lies in the careful updating of these concentration parameters.

Generally there are two different techniques that are used to train naïve Bayes classifiers. The frequentist approach implements \ac{MLE} and the Bayesian approach implements \ac{MAP}. These methods are provided in Sections \ref{sec:bhh:optimisation_step:mle} and \ref{sec:bhh:optimisation_step:map} respectively. It should be mentioned that the \ac{BHH} makes use of \ac{MAP} to optimise the underlying model, however, the authors deem it necessary to provide the details of \ac{MLE} as it contains fundamental mathematical building blocks that are required to understand \ac{MAP}.

It has been established that the \ac{BHH} is a selective \ac{HH} that biases heuristic selection towards a certain performance bias. The concept of performance biases is discussed next.

\index{Performance Bias}
\subsection{Performance Bias}
\label{sec:bhh:optimisation_step:performance_bias}

The intent of the \ac{BHH} is to gather evidence that is can use to update its prior beliefs about which heuristics perform well during training. These beliefs are represented by the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$. A change in prior beliefs is represented by a change in these concentration parameters. Sections \ref{sec:bhh:optimisation_step:mle} and \ref{sec:bhh:optimisation_step:map} show how the concentration parameters are updated throughout the training process, yielding the mechanism by which optimisation takes place.

Specifically, it can be said, that the optimisation process employed by the \ac{BHH} updates \textit{pseudo counts} of events that it observes in its performance logs. These pseudo counts track the occurrence of a heuristic, an entity and resulting performance of these two elements. Through the credit assignment strategy that was discussed in Section \ref{sec:bhh:credit_assignment_strategy}, these pseudo counts are biased towards entity-heuristic combinations that meet credit requirements and yield credit allocations i.e. credit pseudo counts. It is through this concept that the \ac{BHH} is able to bias selection towards performance.

The above mentioned concepts discuss heuristic selection bias by means of online learning. Another possibility is to introduce \textit{a priori} information in the form of expert knowledge. This concept is discussed next.

\index{A Priori Bias}
\subsection{A Priori Bias}
\label{sec:bhh:optimisation_step:a_priori_bias}

Section \ref{sec:bhh:optimisation_step:performance_bias} above discusses the role of concentration parameters on the \ac{BHH}. It is further mentioned in Section \ref{sec:bhh:initialisation_step} that these concentration parameters are symmetrically initialised. This simply means that they are uniformly initialised to all have the value of one in all dimensions.

Consider that the intent of the \ac{BHH} is to learn which heuristics to select during training. An expert can inject expert knowledge into the \ac{BHH} by means of these concentration parameters. An example of this is given as follows. It might be well known that a particular heuristic will perform well on a given problem domain. This could be through empirical analysis, part experiences, logical reasoning and deduction or simply by nature of the heuristic itself. A slight bias can be introduced to this heuristic before training starts but slightly scaling the initialised concentration parameter for that particular heuristic so that is more than the other concentration parameters. The \ac{BHH} interprets this encoded concentration parameter as a prior belief and aims to update this parameter as new evidence is collected. The next section introduces the mathematics behind \ac{MLE}.

\index{Maximum Likelihood Estimation}
\subsection{Maximum Likelihood Estimation}
\label{sec:bhh:optimisation_step:mle}

In probability theory and statistics, \ac{MLE} is a method that estimates the parameters of some assumed prior probability distribution given newly observed data and evidence. This section shows that the values for $\theta$, $\phi$ and $\psi$ can be estimated by \ac{MLE} to yield equations \ref{eq:bhh:optimisation_step:mle:theta}, \ref{eq:bhh:optimisation_step:mle:phi} and \ref{eq:bhh:optimisation_step:mle:psi} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:theta}
    \begin{split}
        \hat{\theta}_{k} = E[\theta_{k}] = \frac{N_{k}}{N}
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:phi}
    \begin{split}
        \hat{\phi}_{j,k} = E[\phi_{j,k}] = \frac{N_{j,k}}{N_{j}}
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:psi}
    \begin{split}
        \hat{\psi}_{k} = E[\psi_{k}] = \frac{N_{1,k}}{N_{k}}
    \end{split}
\end{equation}

The calculations of the \ac{MLE} for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and
$\hat{\psi}_{k}$ are now presented. The log likelihood of $\hat{\theta}$, $\hat{\phi}$ and $\hat{\psi}$ as derived
from the Equation \ref{eq:bhh:selection_mechanism:predictive_model_prop_to} is given in Equation \ref{eq:bhh:optimisation_step:mle:log_likelihood_all} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:log_likelihood_all}
    \begin{split}
        & \mathcal{L}(\theta, \phi, \psi) \\
        &= \ln\left(\left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right] \right) \\
        &= \ln \left( \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right) +  \ln \left( \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right) + \ln \left( \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right) \\		
        &= \left( \sum_{j=1}^{J} \sum_{k=1}^{K} N_{j,k} \ ln \left( \phi_{j,k}
        \right) \right) \\
        &+ \left( \sum_{k=1}^{K} N_{1,k} \ln \left( \psi_{k} \right) + \left( N_{k} - N_{1,k} \right) \ln \left( 1 - \psi_{k} \right) \right) + \left( \sum_{k=1}^{K} N_{k} \ln \left( \theta_{k} \right) \right)
    \end{split}
\end{equation}

Equation \ref{eq:bhh:optimisation_step:mle:log_likelihood_all} can be broken down into each of its factors. Consider the log likelihood of $\psi$  as denoted by Equation \ref{eq:bhh:optimisation_step:mle:log_likelihood_psi} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:log_likelihood_psi}
    \begin{split}
        \mathcal{L}(\psi) &=  \sum_{k=1}^{K} N_{1,k} \ln \left( \psi_{k} \right) + \left( N_{k} - N_{1,k} \right) \ln \left( 1 - \psi_{k} \right)
    \end{split}
\end{equation}

The MLE for $\hat{\psi_{k}} $ can be calculated by taking the derivative of Equation \ref{eq:bhh:optimisation_step:mle:log_likelihood_psi} with respect to $\psi_{k}$ and equating to zero as presented in Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_psi} as follows.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_psi}
    \begin{split}
        \frac{\partial \mathcal{L}(\psi)}{\partial \psi_{k}} &= N_{1,k} \frac{1}{ \psi_{k}} + \left( N_{k} - N_{1,k} \right) \frac{-1}{ \left( 1 - \psi_{k} \right) } \\
        0 &=  \frac{ N_{1,k} \left( 1 - \psi_{k} \right) +  \left( N_{1,k} - N_{k} \right) \psi_{k}}{ \psi_{k} \left( 1 - \psi_{k} \right) } \\
        0 &=  N_{1,k} \left( 1 - \psi_{k} \right) +  \left( N_{1,k} - N_{k} \right) \psi_{k} \\
        0 &=  N_{1,k} - N_{1,k} \psi_{k}  +  N_{1,k} \psi_{k} - N_{k}\psi_{k} \\
        0 &=  N_{1,k} - N_{k}\psi_{k} \\
        N_{k}\psi_{k} &=  N_{1,k} \\
        \hat{\psi}_{k} &=  \frac{N_{1,k}}{N_{k}} \\
    \end{split}
\end{equation}

The value for $\hat{\theta_{k}} $ can be calculated similarly. However, one has to compensate for the $K-1$ simplex $S$ by adding error factor $\epsilon$ to correct values for  $\theta$ where $\sum_{k}^{K} \theta_{k} \neq 1$. The new log likelihood function is then given in Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_1} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_1}
    \begin{split}
        \mathcal{L}(\theta, \epsilon)
        &=  \left( \sum_{k=1}^{K} N_{k} \ln \left( \theta_{k} \right) \right) + \epsilon \left( 1 - \sum_{k=1}^{K} \theta_{k} \right) \\
        &=  \left( \sum_{k=1}^{K} N_{k} \ln \left( \theta_{k} \right) \right) + \left( \epsilon -  \epsilon \sum_{k=1}^{K} \theta_{k} \right)
    \end{split}
\end{equation}

Solving first for $\epsilon$ yields Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_2} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_2}
    \begin{split}
        \frac{\partial \mathcal{L}(\theta, \epsilon)}{\partial \epsilon} &= 1 - \sum_{k=1}^{K} \theta_{k}  \\
        \sum_{k=1}^{K} \theta_{k}  &= 1
    \end{split}
\end{equation}

Then solving for $\theta_{k}$ yields Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} as presented below.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3}
    \begin{split}
        \frac{\partial \mathcal{L}(\theta, \epsilon)}{\partial \theta_{k}} &=  N_{k} \frac{1}{\theta_{k}}  + \epsilon(-1) \\
        \frac{N_{k}}{\theta_{k}} &= \epsilon \\
        N_{k} &= \theta_{k} \epsilon \\
        \sum_{k=1}^{K} N_{k} &= \sum_{k=1}^{K} \theta_{k} \epsilon \\
        N &= \epsilon \sum_{k=1}^{K} \theta_{k} \\
        N &= \epsilon
    \end{split}
\end{equation}

Substituting back into the Equation yields Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_4} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_4}
    \begin{split}
        N_{k} &= \theta_{k} \epsilon \\
        N_{k} &= \theta_{k} N \\
        \hat{\theta}_{k} &= \frac{N_{k}}{N}\\
    \end{split}
\end{equation}

The value for $\hat{\phi}_{j, k} $ is calculated very similarly. To compensate for the $K-1$ simplex $S$ an error factor $\lambda = (\lambda_{1}, \dots, \lambda_{J})$ is added. This follows in Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_1} as is presented below.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_1}
    \begin{split}
        \mathcal{L}(\phi, \lambda) 
        &=  \left( \sum_{j=1}^{J} \sum_{k=1}^{K} N_{j,k} \ ln \left( \phi_{j,k} \right) \right) + \sum_{j=1}^{J} \lambda_{j} \left( 1 - \sum_{k=1}^{K} \phi_{j,k} \right) \\
        &=  \left( \sum_{j=1}^{J} \sum_{k=1}^{K} N_{j,k} \ ln \left( \phi_{j,k} \right) \right) + \sum_{j=1}^{J} \lambda_{j} - \sum_{j=1}^{J} \lambda_{j} \sum_{k=1}^{K} \phi_{j,k} \\
    \end{split}
\end{equation}

Solving first for $\lambda_{j}$ yields Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_2} as is given below.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_2}
    \begin{split}
        \frac{\partial \mathcal{L}(\phi, \lambda)}{\partial \lambda_{j}} &= 1 - \sum_{k=1}^{K} \phi_{j,k}  \\
        \sum_{k=1}^{K} \phi_{j,k}  &= 1
    \end{split}
\end{equation}

Then solving for $\phi_{j,k}$ yields Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3}
    \begin{split}
        \frac{\partial \mathcal{L}(\phi, \lambda)}{\partial \phi_{j,k}} &= N_{j,k} \frac{1}{\phi_{j,k}}  - \lambda_{j} \\
        \frac{N_{j,k}}{\phi_{jk}} &= \lambda_{j} \\
        N_{j,k} &= \phi_{j,k} \lambda_{j} \\
        \sum_{k=1}^{K} N_{j,k} &= \sum_{k=1}^{K} \phi_{j,k} \lambda_{j} \\
        N_{j} &= \lambda_{j} \sum_{k=1}^{K} \phi_{j,k} \\
        N_{j} &= \lambda_{j}
    \end{split}
\end{equation}

Substituting back into the Equation yields equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_4} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_4}
    \begin{split}
        N_{j,k} &= \phi_{j,k} \lambda_{j} \\
        N_{j,k} &= \phi_{j,k} N_{j} \\
        \hat{\phi}_{j,k} &= \frac{N_{j,k}}{N_{j}}\\
    \end{split}
\end{equation}

This section provided the mathematical derivations of the MLE equations for $\theta$, $\phi$ and $\psi$. The next section provides the detail around \ac{MAP}, the optimisation process utilised by the \ac{BHH}.

\index{Maximum a Posteriori Estimation}
\subsection{Maximum a Posteriori Estimation}
\label{sec:bhh:optimisation_step:map}

Another approach to optimising the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ is to optimise the parameters by their probability distributions' parameters. This process is referred to as \index{Bayesian analysis}\textit{Bayesian analysis}. This section provides the mathematical details of the Bayesian analysis and \ac{MAP} as it is implemented by the \ac{BHH}.

Bayesian analysis makes use of the \textit{posterior} probability distribution. The posterior distribution is simply expressed as:

\begin{equation*}
    \label{eq:bhh:optimisation_step:map:bayesian_analysis_lamens}
    \begin{split}
        POSTERIOR \propto LIKELIHOOD \times PRIOR
    \end{split}
\end{equation*}

The likelihood is presented in Equation \ref{eq:bhh:optimisation_step:map:bayesian_analysis_lamens} above. The event $H$ is a multinomial distribution with parameter $\theta$. It is known that the conjugate prior to a multinomial distribution is a Dirichlet distribution (see Chapter \ref{chap:probability}. The \textit{prior} probability distribution for  $\theta_{k}$ is thus presented in Equation \ref{eq:bhh:optimisation_step:map:map_theta_prior} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:map:map_theta_prior}
    \begin{split}
        P(\theta | \alpha)
&\propto \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} -1}
    \end{split}
\end{equation}

Furthermore, the event $E$ is also a multinomial distribution with parameter $\phi$. The \textit{prior} probability distribution for $\phi_{j,k}$ is thus presented in Equation \ref{eq:bhh:optimisation_step:map:map_phi_prior} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:map:map_phi_prior}
    \begin{split}
        P(\phi \vert \beta)
&\propto \prod_{j=1}^{J}  \prod_{k=1}^{K} \phi_{j,k}^{\beta_{j,k} -1}
    \end{split}
\end{equation}

Finally, the event $C$ is a binomial distribution with parameter $\psi$. It is known that the conjugate prior to a binomial distribution is a Beta distribution (see Chapter \ref{chap:probability}). The prior probability distribution for $\psi_{k}$ is thus presented in Equation \ref{eq:bhh:optimisation_step:map:map_psi_prior} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:map:map_psi_prior}
    \begin{split}
        P(\psi | \gamma_{1}, \gamma_{0})
&\propto \prod_{k=1}^{K} \psi_{k}^{\gamma_{1,k}} (1- \psi_{k})^{\gamma_{2,k}}
    \end{split}
\end{equation}

Putting the likelihood and priors together yields the posterior distribution as given in Equation \ref{eq:bhh:optimisation_step:map:map_psi_prior} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:map:posterior}
    \begin{split}
& P(\theta, \phi, \psi \vert H, E, C;  \alpha, \beta, \gamma_{1}, \gamma_{0}) \\
&\propto P(H \vert E, C; \theta, \phi, \psi)P(\theta, \phi, \psi \vert \alpha, \beta, \gamma_{1}, \gamma_{0}) \\
&\propto P(E \vert H; \phi) P(C \vert H; \psi) P(H \vert \theta) P(\phi \vert \beta) P(\psi \vert \gamma_{1}, \gamma_{0}) P(\theta \vert \alpha)  \\
&\propto \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right] \\
&\times \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{\beta_{j,k} - 1} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{\gamma_{1,k} - 1} (1 - \psi_{k})^{\gamma_{2,k} - 1} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} - 1} \right] \\
&\propto \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{(N_{j,k} + \beta_{j,k}) - 1} \right] \\
&\times \left[ \prod_{k=1}^{K} \psi_{k}^{(N_{1,k} + \gamma_{1,k}) - 1} (1 - \psi_{k})^{(N_{0,k} + \gamma_{2,k} )- 1} \right] \\
&\times \left[ \prod_{k=1}^{K} \theta_{k}^{(N_{k} + \alpha_{k}) - 1} \right]
    \end{split}
\end{equation}

From Equation \ref{eq:bhh:optimisation_step:map:posterior} above, it can be seen that the posterior distribution has the same form $\mathcal{A}(v)$ as the prior distribution. The concentration update operations can then be given in equations \ref{eq:bhh:optimisation_step:map:alpha_update_operation}, \ref{eq:bhh:optimisation_step:map:beta_update_operation}, \ref{eq:bhh:optimisation_step:map:gamma1_update_operation} and \ref{eq:bhh:optimisation_step:map:gamma2_update_operation} below.

\begin{equation}
    \label{eq:bhh:optimisation_step:map:alpha_update_operation}
    \begin{split}
        \alpha_{k}(t+1) = N_{k} + \alpha_{k}(t)
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:bhh:optimisation_step:map:beta_update_operation}
    \begin{split}
        \beta_{j,k}(t+1) = N_{j,k} + \beta_{j,k}(t)
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:bhh:optimisation_step:map:gamma1_update_operation}
    \begin{split}
        \gamma_{1,k}(t+1) = N_{1,k} + \gamma_{1,k}(t)
    \end{split}
\end{equation}

\begin{equation}
    \label{eq:bhh:optimisation_step:map:gamma2_update_operation}
    \begin{split}
        \gamma_{2,k}(t+1) = N_{0,k} + \gamma_{2,k}(t)
    \end{split}
\end{equation}

It can be seen that the prior and posterior probability distributions are of the same shape $\mathcal{A}(v)$. It can therefore be said that the \ac{BHH} implements a Gaussian process. Since the reselection of heuristics happen at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration. It can thus be said that the \ac{BHH} implements a \ac{HMM}.

The section concludes the optimisation process that is implemented by the \ac{BHH}. Throughout this chapter a number of hyper-parameters have been identified. These are summarised and discussed in the next section.

\index{Hyper-Parameters}
\section{Hyper-Parameters}
\label{sec:bhh:hyper_parameters}

This section provides the reader with a breakdown of all the hyper-parameters that were identified and briefly mentioned in this chapter. Some logical arguments can be made as to what their values should be, however it is still up to empirical analysis to determine the effects of certain hyper-parameter design decisions. Were possible, a range of possible values is provided. Each of the hyper-parameters are discussed in their own sections next.

\index{Heuristic Pool}
\subsection{Heuristic Pool}
\label{sec:bhh:hyper_parameters:heuristic_pool}

Section \ref{sec:bhh:heuristic_pool} provided the reader with the context and detail of the heuristic pool as it is included in the architecture of the \ac{BHH}. A detailed discussion was given around the importance of diversity and balancing exploration and exploitation capabilities. The heuristic pool hyper-parameter refers to the heuristic-pool configuration that is used. This configuration should account for the following factors.

\begin{itemize}
    \item The type of low-level heuristics to include in the heuristic pool. This dissertation investigates two main groups including gradient-based and meta-heuristics. 
    \item The low-level heuristic's hyper-parameters. At a lower-level, each of these heuristics have their own set of hyper-parameters.
    \item The heuristic pool size. This refers to the number of heuristics in the heuristic pool.
\end{itemize}

The granularity of design choices at a high level is not as strict for the \ac{BHH} as it is for low-level heuristics. If one is unsure as to which low-level hyper-parameters to use, one could simply include multiple configurations of that low-level heuristic, each just with its own unique hyper-parameter configurations. Take note that it has not been established yet if this is to the benefit or detriment of \ac{BHH}. These configurations increase the heuristic pool size and could also counteract eachother.  It is thus still important to include relevant heuristics that is appropriate to the underlying problem being solved. These heuristics should contain a balance between exploration and exploitation, either through the nature of their implementation or through careful hyper-parameter selection. Often times hyper-parameter schedules are used. This is also possible with the \ac{BHH}.

\index{Population Size}
\subsection{Population Size}
\label{sec:bhh:hyper_parameters:population_size}

\index{Population Size}\textit{Population size} refers to the number of \index{entity}entities included in the \index{Entity Pool}entity pool/\index{Population}population. The exact \index{Population Size}population size to use is to be determined empirically. Naturely, an assumption is made that a larger population could lead to better results, assuming that entities are initialised to be spread uniformly across the solution search space. Oldewage \cite{ref:oldewage:2017} mentions that a large number of particles (entities) may be able to traverse a greater portion of the search space as every particle provides additional information about the search space. However, it is to be determined if this is indeed the case for the \ac{BHH}. The authors propose the following considerations when picking a \index{population size}population size:

\begin{itemize}
    \item When considering the lower bound of possible \index{population size}population sizes, take into account the highest, minimum \index{population size}population size required by all low-level \index{heuristic}heuristics. For example, if one includes \Ac{DE} into the \index{heuristic}heuristic pool, one needs a \index{population size}population size of at least 4. For \acp{PSO}, the minimum population size is 3.
    \item When considering the upper bound of possible \index{population size}population sizes, take into account that the bigger the \index{population size}population size, the more computationally expensive it is to execute the training process. Furthermore, there could exists a point of \index{diminishing returns}\textit{diminishing returns} where an increase in \index{population size}population size does not yield any better outcome. Once again, this is to be empirically tested. To extend on this, consider that the \Ac{BHH} is a \Ac{HH} that utilises a \index{Bayesian}Bayesian probabilistic approach in it's selection mechanism. This means that a larger observed sample size (of entity and heuristic selection events) is needed to statistically and reliably update the selection mechanism's trainable parameters.
\end{itemize}

\subsection{Credit}
\label{sec:bhh:hyper_parameters:credit}

The credit hyper-parameter refers to the credit assignment strategy that is used. This dissertation proposed 5 different credit assignment strategies that were presented in Section \ref{sec:bhh:credit_assignment_strategy}. The choice of credit assignment is assumed to be problem-dependent, however, this is to be empirically tested. Apart from the credit assignment strategy itself, one has to consider the following components related to credit assignment:

\begin{itemize}
    \item When to apply credit?
    \item What should the credit assignment score be (default = 1)
    \item To what degree should credit assignment be allocated to past results in the performance log
\end{itemize}

It should be noted that this dissertation proposed an initial set of credit assignment strategies that are discrete in outcome. Perhaps an alternative is to include some measure of success, not just an indicator of success. This allows for the implementation of continuous valued outcomes from the credit assignment strategies. Take into account that this could also drastically increase the complexity of the underlying predictive model implemented by the \ac{BHH}.

A number of other hyper-parameters are specifically included to address the above challenges. These include \textit{reselection}, \textit{replay} and \textit{reanalysis window sizes} along with \textit{burn in}, \textit{discounted rewards} and \textit{normalisation}. These are discussed next.

\index{Reselection}
\subsection{Reselection}
\label{sec:bhh:hyper_parameters:reselection}

The reselection window size is a hyper-parameter that controls how often heuristic selections are resampled from the heuristic distribution, parameterised by the heuristic selection probability that is learnt as was discussed in Section \ref{sec:bhh:selection_mechanism:predictive_model}. The choice of reselection should be influenced by the following considerations. If reselection happens too frequently, it does not allow heuristics sufficient time to smooth out update steps which could be detrimental to the outcomes of the \ac{BHH}. If reselection happens too infrequently, it does not allow for sufficient room to collect samples/evidence from which learning is done. Naturally, the correct reselection window size to use is to be determined empirically.

\index{Replay}
\subsection{Replay}
\label{sec:bhh:hyper_parameters:replay}

The replay window size is a hyper-parameter that controls how much historical performance information is kept in memory for the \ac{BHH} to learn from. This is a parameter that is borrowed from \ac{RL} and aims to control the effect that past performances has on the \ac{BHH}. An assumption is made that the correct replay window size  to use could be problem dependent. However, logical arguments can be deduced. A replay window size that is too small includes little to no memory. This results in a situation where the \ac{BHH} simply looks at the most recent evidence that is collected and nothing more. This could be a beneficial or detrimental to the \ac{BHH}. On the contrary, if the replay window size is big, then the \ac{BHH} tracks a longer history of past performances. Once again, the this could be beneficial or detrimental to the \ac{BHH}.

\index{Reanalysis}
\subsection{Reanalysis}
\label{sec:bhh:hyper_parameters:reanalysis}

The reanalysis window size is a hyper-parameter that controls how often the \ac{BHH} updates its past beliefs (priors). Consider that this parameter goes hand in hand with the reselection and replay window sizes. If the reanalysis window is too small, the \ac{BHH} prematurely updates its priors. Similar to other hyper-parameters discussed thus far, the correct value to use for the reanalysis window size is to be determined empirically. However, some logical exclusions can be made. A reanalysis window size that is smaller than the reselection window size does not make sense, since the effects of reanalysis is only realised during reselection. A reanalysis window size that is too big could lead to a situation where the delay in updating priors could be detrimental to the outcomes of the \ac{BHH}.

\index{Burn In}
\subsection{Burn In}
\label{sec:bhh:hyper_parameters:burn_in}

Burn in is a hyper-parameter that is borrowed from \ac{MCMC} and aims to delay the learning process of the \ac{BHH}. The intent of this hyper-parameter is to determine if heuristics need time to execute before reselection starts. Notice that a delay in the learning process does not mean that reselection doesn't occur or performance information is not collected in the replay window. Therefore, it should be noted that the burn in window size, reselection window size and replay window size should be considered together. If the replay size is smaller than the burn in window size, no performance information is accumulated and the \ac{BHH} essentially starts with a prior that is no better than the initial symmetric initialisation that was done.

\index{Discounted Rewards}
\subsection{Discounted Rewards}
\label{sec:bhh:hyper_parameters:discounted_rewards}

Discounted rewards is another hyper-parameter that is borrowed from \ac{RL}. This hyper-parameter is a flag that determines if discounted rewards is enabled or not. Discounted rewards refers to an operation where the credit assignments for past performance is exponentially decreased further into the past. An exponential decay factor or 0.5 is proposed. The intent of the discounted rewards flag is to scale the effect of past performances that are further back into the performance log such that they have a smaller impact than more recent evidence on the performance achieved by the \ac{BHH}.

\index{Normalisation}
\subsection{Normalisation}
\label{sec:bhh:hyper_parameters:normalisation}

Normalisation is a hyper-parameter that aims to provide a mechanism of control for the degree to which exploration is allowed. Figure \ref{sec:bhh:hyper_parameters:discounted_rewards:normalisation} shows the effect of different concentrations ($\alpha$ and $\beta$) on the Beta distribution. By normalising the concentration parameters for the \ac{BHH} ($\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$), the variance of the selection probability distributions increase, allowing for sampled probabilities further from the mean and thus allowing for more exploration.

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{images/beta_1_1.png}
        \caption{$\alpha=1$, $\beta=1$}
        \label{sec:bhh:hyper_parameters:normalisation_beta_1_1}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{images/beta_5_5.png}
        \caption{$\alpha=5$, $\beta=5$}
        \label{sec:bhh:hyper_parameters:normalisation_beta_5_5}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{images/beta_20_20.png}
        \caption{$\alpha=20$, $\beta=20$}
        \label{sec:bhh:hyper_parameters:normalisation_beta_20_20}
    \end{subfigure}
    \par\bigskip
    \caption{Beta distribution with varying $\alpha$ and $\beta$ values.}
    \label{sec:bhh:hyper_parameters:discounted_rewards:normalisation}
\end{figure}

This concludes the hyper-parameters that are used by the \ac{BHH}. The following section discusses the default value for proxied update step operations.

\subsection{Defaults}
\label{sec:bhh:hyper_parameters:defaults}

Section \ref{sec:bhh:heuristic:proxies} provided the reader with the concept of proxied heuristic update step operations. As was mentioned in Section \ref{sec:bhh:hyper_parameters:heuristic_pool}, low-level heuristics each have their own set of hyper-parameters as well. This means that a set of default low-level parameters must be allocated specifically for these proxies. Consider a scenario where two instances of \ac{Adam} is included in the heuristic pool. Each has its own set of hyper-parameters that (should) differ from each other. In the case of \ac{Adam}, there are 4 hyper-parameters that include learning rate, $\beta1$, $\beta2$ and $\epsilon$. If another heuristic needs to proxy \ac{Adam}'s ``expected gradient mean operation'', a default $\beta1$ parameter must be supplied. Notice that this is only the case where multiple instances of a heuristic is included and there is uncertainty about which instance's hyper-parameters to use for the proxied heuristic update steps. If there is only one instance of a particular heuristic, that instance's hyper-parameters are used. The next section provides the reader with the pseudo-code algorithm for the \ac{BHH}.

\section{Algorithm}
\label{sec:bhh:algorithm}

This section provides the reader with a high level pseudo-code implementation of the \ac{BHH}. This is given in Algorithm \ref{algo:bhh} below.

\begin{algorithm}[H]
    \caption{The pseudo code for the \index{Bayesian Hyper-Heuristic} Bayesian Hyper-Heuristic optimiser}
    \label{algo:bhh}
    \begin{algorithmic}
        \State step $\gets 0$

        \State select initial heuristics 
        \State initialise population and entities
        \State evaluate entities' initial position
        \State update population state

        \While{stopping condition not met}
        	\For{all entities in entity pool}
        	    \If{selected heuristic is gradient-based}
        	        \State get gradients
        	    \EndIf

        		\State apply low-level heuristic and proxy operations
        		\State update population state
        		\State log performance to performance log

        		\If {step < burn-in window size}
        			\State select heuristic
        		\Else
        			\If {step $\mathbin{\%}$ reanalysis window size = 0}
        				\State apply Bayesian analysis
        			\EndIf

        			\If {step $\mathbin{\%}$ reselection window size = 0}
        				\State select heuristic
        			\EndIf

        			\If {step > replay window size}
        				\State prune performance log
        			\EndIf
        	    \EndIf
        	\EndFor
        	\State step $\gets$ step + $1$
        \EndWhile
    \end{algorithmic}
\end{algorithm}

\section{Summary}
\label{sec:bhh:summary}

This chapter provided the reader with extensive detail on the inner workings and design of the \ac{BHH}. The \ac{BHH} was formally classified and the details around various components of the \ac{BHH}'s architecture was presented. Formal mathematical descriptions of the Bayesian selection method have been provided. The optimisation process, by means of Bayesian analysis has been presented and a pseudo code implementation of the \ac{BHH} was presented.

This concludes the background information and literature studies that is required to propose a methodology for an empirical process. This methodology is provided in the next chapter.

### 2022-09-12 dissertation/chapters/07-methodology.tex
📝 (review): First set of changes

\chapter{Methodology}
\label{chap:methodology}

\begin{quote}
    \textit{Observation, reason and experimentation make up what we call the scientific method. $\sim$ Richard P. Feynman}
\end{quote}

Chapter \ref{chap:introduction} set out the objectives of the dissertation. These objectives can broadly be split between background information and an empirical component. So far, chapters \ref{chap:introduction}-\ref{chap:bhh} provided the necessary background information. This chapter now provides the detailed specification of the methodology that is followed for the empirical process and the analysis of the results. The remainder of the chapter is structured as follows:

\begin{itemize}
    \item \textbf{Section \ref{sec:methodology:overview}} provides a brief overview of the entire empirical process, leaving the detail to subsequent sections.

    \item \textbf{Section \ref{sec:methodology:datasets}} presents the detail around the datasets that are used.

    \item \textbf{Section \ref{sec:methodology:model}} provides the details of the models (\acs{FFNN}s) that are being trained.

    \item \textbf{Section \ref{sec:methodology:heuristics}} presents the detail around the different \index{heuristic}heuristics that are used along with their hyper-parameters.

    \item \textbf{Section \ref{sec:methodology:baseline_bhh}} provides the detail of the configuration of the \acs{BHH} baseline.

    \item \textbf{Section \ref{sec:methodology:performance_measures}} sheds light into the performance evaluation measures that are used.

    \item \textbf{Section \ref{sec:methodology:stopping_conditions}} discusses the stopping conditions that are used.

    \item \textbf{Section \ref{sec:methodology:experiments}} presents the different experimental groups that is executed.

    \item \textbf{Section \ref{sec:methodology:implementation}} sheds some light as to the implementation and execution of the empirical process.

    \item \textbf{Section \ref{sec:methodology:statistical_analysis}} presents the procedures that are followed in during the statistical analysis of the results.

    \item Finally, a summary of the chapter is provided in \textbf{Section \ref{sec:methodology:summary}}
\end{itemize}

\section{Overview of Empirical Process}
\label{sec:methodology:overview}

The purpose of the empirical process is to present and execute a carefully crafted experiment/test that produces data that can be used to reject of verify some hypothesis about the element under investigation. This dissertation has outlined a set of 3 objectives that require such empirical processes to evaluate the \ac{BHH}. This section outlines what these empirical processes entail.

Each empirical test sets out some configuration of elements to be evaluated. These generally include a set of parameters that are altered between experiments. Each experiment is evaluated by means of a performance measurement. In the context of training \acp{FFNN}, the underlying model (\ac{NN}) is trained across a number of datasets. Each dataset is split into a training and test set. The training set is used to train the model, while the test set is used to evaluate the model. Training epochs are split into mini-batch iterations, with each dataset containing a specified mini-batch size. Evaluation takes place at every mini-batch step. These experiments contain a number of components, each with a set of paramaters. Due to the stochastic nature of the experiments, each experiment is repeated over a number of runs to provide sufficient sample for statistical certainty. Each run contains a different random seed. Each evaluation's results are analysed for statistical significance. It is from these statistical analyses that findings and conclusions are then made.

Detail around each of these elements are now provided, starting with the datasets that are used.

\section{Datasets}
\label{sec:methodology:datasets}

This section provides the detail around the different datasets that are used throughout the empirical process. These datasets originate from the UCI Machine Learning Repository \cite{ref:uci:2022}. Datasets are grouped by problem type and include 8 classification and 7 regression datasets. The classification datasets are given in Table \ref{tab:methodology:datasets:classification} and the regression datasets are given in Table \ref{tab:methodology:datasets:regression} below.

\begin{table}[htbp]
    \centering
    \caption{Classification datasets}
    \label{tab:methodology:datasets:classification}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
        \begin{tabular}{ccccccccc}
            \textbf{dataset} & \textbf{output} & \textbf{types} & \textbf{attributes} & \textbf{classes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation} \\
            \midrule
            iris  & multivariate & real  & 4     & 3     & 150   & 16    & 10    & \cite{ref:fisher:1936} \\
            car   & multivariate & categorical & 6     & 4     & 1728  & 128   & 14    & \cite{ref:bohanec:1988} \\
            abalone & multivariate & categorical, integer, real & 8     & 28    & 4177  & 256   & 17    & \cite{ref:waugh:1995} \\
            mushroom & multivariate & categorical & 22    & 2     & 8214  & 512   & 17    & \cite{ref:schlimmer:1987} \\
            wine\_quality & multivariate & real  & 12    & 11    & 4898  & 256   & 20    & \cite{ref:cortez:2009} \\
            bank  & multivariate & real  & 17    & 2     & 45211 & 512   & 89    & \cite{ref:moro:2014} \\
            diabetic & multivariate & integer & 55    & 3     & 100000 & 1024  & 98    & \cite{ref:strack:2014} \\
            adult & multivariate & categorical, integer & 14    & 2     & 48842 & 256   & 191   & \cite{ref:kohavi:1996} \\
        \end{tabular}%
    }
\end{table}%

\begin{table}[htbp]
    \centering
    \caption{Regression datasets}
    \label{tab:methodology:datasets:regression}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
        \begin{tabular}{cccccccc}
            \textbf{dataset} & \textbf{output} & \textbf{types} & \textbf{attributes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation} \\
            \midrule
            fish\_toxicity & multivariate & real  & 7     & 908   & 64    & 15    & \cite{ref:cassotti:2015} \\
            housing & univariate & real  & 13    & 506   & 32    & 16    & \cite{ref:harrison:1978} \\
            forest\_fires & multivariate & real  & 13    & 517   & 32    & 17    & \cite{ref:cortez:2007} \\
            student\_performance & multivariate & integer & 33    & 649   & 32    & 21    & \cite{ref:cortez:2008} \\
            parkinsons & multivariate & integer, real & 26    & 5875  & 256   & 23    & \cite{ref:tsanas:2009} \\
            air\_quality & multivariate, timeseries & real  & 15    & 9358  & 256   & 37    & \cite{ref:de:2008} \\
            bike  & univariate & integer, real & 16    & 17389 & 256   & 68    & \cite{ref:fanaee:2014} \\
        \end{tabular}%
    }
\end{table}%

Details on how the datasets where preprocessed and prepared is given in Appendix \ref{app:datasets}. The concept of class balancing is briefly discussed next.

\subsection{Class Balancing}

A number of classification datasets as given in Table \ref{tab:methodology:datasets:classification} above contain unbalanced classes. A decision was made to not make use of class balancing. This was simply to eliminate as many variables adn factors in the empirical process as possible, as it is already a complicated process.  It is therefore suggested that the \ac{BHH} first be studied under the assumption of balanced classes and then only apply class balancing. In future research opportunities, class balancing should be utilised.

The next section presents the models and the configurations that are used.

\section{Models}
\label{sec:methodology:model}

As the title of the dissertation suggests, these empirical process are focused on the training of \acp{FFNN}. In theory, one should be able to swap these \acp{FFNN} out for any other mathematical model that can be optimised. All models that are trained in this dissertation are shallow \acp{NN}, meaning they only have one hidden layer. The architecture of a model is dependent on the dataset being trained on, the type of problem it is (classification or regression), the number of input dimensions and the number of output dimensions. The models and their configuration, as it is used for each dataset, is given below in Table \ref{tab:methodology:models:configurations}

% Table generated by Excel2LaTeX from sheet 'Model Configurations'
\begin{table}[htbp]
    \centering
    \caption{Model configurations}
    \label{tab:methodology:models:configurations}%
    \par\bigskip
    \resizebox{\textwidth}{!}{
        \begin{tabular}{rcccccccc}
            \textbf{dataset} & \textbf{inputs} & \textbf{hidden} & \textbf{output} & \textbf{biases} & \textbf{parameters} & \textbf{topology} & \textbf{l1 activation} & \textbf{l2 activation} \\
            \midrule
            fish\_toxicity & 6     & 3     & 1     & yes   & 25    & dense & LReLU ($\alpha = 0.3$) & sigmoid \\
            iris  & 4     & 5     & 3     & yes   & 43    & dense & LReLU ($\alpha = 0.3$) & softmax \\
            air\_quality & 12    & 8     & 1     & yes   & 113   & dense & LReLU ($\alpha = 0.3$) & sigmoid \\
            housing & 13    & 8     & 1     & yes   & 121   & dense & LReLU ($\alpha = 0.3$) & sigmoid \\
            wine\_quality & 13    & 10    & 7     & yes   & 217   & dense & LReLU ($\alpha = 0.3$) & softmax \\
            parkinsons & 21    & 10    & 1     & yes   & 231   & dense & LReLU ($\alpha = 0.3$) & sigmoid \\
            car   & 21    & 10    & 4     & yes   & 264   & dense & LReLU ($\alpha = 0.3$) & softmax \\
            forest\_fires & 43    & 16    & 1     & yes   & 721   & dense & LReLU ($\alpha = 0.3$) & sigmoid \\
            abalone & 10    & 36    & 28    & yes   & 1432  & dense & LReLU ($\alpha = 0.3$) & softmax \\
            bank  & 51    & 32    & 1     & yes   & 1697  & dense & LReLU ($\alpha = 0.3$) & softmax \\
            bike  & 61    & 32    & 1     & yes   & 2017  & dense & LReLU ($\alpha = 0.3$) & sigmoid \\
            student\_performance & 99    & 32    & 1     & yes   & 3233  & dense & LReLU ($\alpha = 0.3$) & sigmoid \\
            adult & 108   & 64    & 1     & yes   & 7041  & dense & LReLU ($\alpha = 0.3$) & softmax \\
            mushroom & 117   & 64    & 1     & yes   & 7617  & dense & LReLU ($\alpha = 0.3$) & softmax \\
            diabetic & 2369  & 32    & 3     & yes   & 75939 & dense & LReLU ($\alpha = 0.3$) & softmax \\
        \end{tabular}%
    }
\end{table}%

It should be noted that for the classification problems, the \index{softmax}softmax activation is not actually part of the model. It is just added for predictive output and is not needed during evaluation. The loss functions (\ac{SparseCatXE} and \ac{BinXE}) that are used contains a \index{softmax}softmax function. Models' initial weights are initialised by means of \index{Glorot uniform sampling}Glorot uniform sampling.

\section{Heuristics/Optimisers}
\label{sec:methodology:heuristics}

This section provides the details of the standalone \index{heuristic}heuristics/optimisers that are used in the empirical process.

Table \ref{tab:methodology:heuristics} contain a list of all the standalone \index{heuristic}heuristics that are used as well as their hyper-parameter configuration.

% Table generated by Excel2LaTeX from sheet 'BHH Baseline'
\begin{table}[htbp]
    \centering
    \caption{Heuristics/optimisers and their hyper-parameter configuration of their}
    \label{tab:methodology:heuristics}%
    \par\bigskip
    \resizebox{0.8\textwidth}{!}{

        \begin{tabular}{llll}
            \textbf{heuristic} & \textbf{configuration} & \textbf{value} & \textbf{citation} \\
            \midrule
            sgd   & learning\_rate & 0.1**0.01 & \cite{ref:sutskever:2013} \\
            momentum & learning\_rate & 0.1**0.01 & \cite{ref:sutskever:2013} \\
                  & momentum & 0.9   &  \\
            nag   & learning\_rate & 0.1**0.01 & \cite{ref:sutskever:2013} \\
                  & momentum & 0.9   &  \\
            adagrad & learning\_rate & 0.1**0.01 & \cite{ref:duchi:2011} \\
                  & epsilon & 1E-07 &  \\
            rmsprop & learning\_rate & 0.1**0.01 & \cite{ref:hinton:2012} \\
                  & rho   & 0.95  &  \\
                  & epsilon & 1E-07 &  \\
            adadelta & learning\_rate & 1.0**0.95 & \cite{ref:zeiler:2012} \\
                  & rho   & 0.95  &  \\
                  & epsilon & 0.0000001 &  \\
            adam  & learning\_rate & 0.1**0.01 & \cite{ref:kingma:2014} \\
                  & beta1 & 0.9   &  \\
                  & beta2 & 0.95  &  \\
                  & epsilon & 1E-07 &  \\
            pso   & population\_size & 10    & \cite{ref:van:2010} \\
                  & learning\_rate & 0.1**0.01 &  \\
                  & inertia\_weight (w) & 0.729844 &  \\
                  & cognitive\_control (c1) & 1.49618 &  \\
                  & social\_control (c2) & 1.49618 &  \\
                  & velocity\_clip\_min & -1.0  &  \\
                  & velocity\_clip\_max & 1.0   &  \\
            de    & population\_size & 10    & \cite{ref:mezura:2006} \\
                  & selection\_strategy & best  &  \\
                  & xo\_strategy & exp   &  \\
                  & recombination probability & 0.9**0.1 &  \\
                  & beta  & 2.0**0.1 &  \\
            ga    & population\_size & 10    & \cite{ref:lambora:2019} \\
                  & selection\_strategy & rand  &  \\
                  & xo\_strategy & bin   &  \\
                  & mutation\_rate & 0.2**0.05 &  \\
        \end{tabular}%
    }
\end{table}%

Take note that for Table \ref{tab:methodology:heuristics}, values that contains an asterisk ($*$) are configured on a schedule with the initial value depicted first and the decay rate is depicted last. The number of steps is the total number of steps for that particular dataset it is being applied to.

Also take note that a learning rate was added to the \ac{PSO} as an attempt to avoid overshooting solutions later in the training process. This parameter does not traditionally form part of the \ac{PSO}, but it was found to work sufficiently here.

The next section provides the details around the \ac{BHH} baseline.

TODO: Proxy Mapping Table

\section{BHH Baseline}
\label{sec:methodology:baseline_bhh}

The \ac{BHH} baseline is a name given to a specific configuration of the \ac{BHH}, which during development, has been found to provide reasonable performance. It was decided that this configuration will be the cornerstone configuration from which all other \index{heuristic}heuristics and their configurations are evaluated. The \ac{BHH} baseline represents the main component that is evaluated in this dissertation. The configuration for the \ac{BHH} baseline is given in Table \ref{tab:methodology:bhh_baseline_configuration} below:

% Table generated by Excel2LaTeX from sheet 'BHH Baseline'
\begin{table}[htbp]
  \centering
    \caption{BHH baseline configurations}
    \label{tab:methodology:bhh_baseline_configuration}%
    \par\bigskip
    \resizebox{0.8\textwidth}{!}{
        \begin{tabular}{rrcc}
            \multicolumn{1}{c}{\textbf{hyper-heuristic}} & \multicolumn{1}{c}{\textbf{variant}} & \textbf{configuration} & \textbf{value} \\
            \midrule
            \multicolumn{1}{l}{bhh} & \multicolumn{1}{l}{baseline} & heuristic\_pool & all \\
                  &       & population & 5 \\
                  &       & credit & ibest \\
                  &       & reselection & 10 \\
                  &       & replay & 10 \\
                  &       & reanalysis & 10 \\
                  &       & normalise & false \\
                  &       & discounted\_rewards & false \\
        \end{tabular}%
    }
\end{table}%

Table \ref{tab:methodology:bhh_baseline_configuration} refers to the \index{heuristic}heuristic pool that is used as \textit{all}. This refers to a configuration where the heuristic pool contains all the low-level heuristics as presented in Section \ref{sec:methodology:heuristics}. This list of low-level \index{heuristic}heuristics naturally also then form the list of standalone heuristics/optimisers to which the \ac{BHH} is compared and analysed as is described later in  Section \ref{sec:methodology:experiments:standalone_optimisers}. Specifically the finer details of the implementation of the \ac{BHH}, the low-level \index{heuristic}heuristic pool and how it is used is given in Chapter \ref{chap:bhh}.

\section{Performance Measures}
\label{sec:methodology:performance_measures}

This section sheds light into the performance measures that are used to evaluate the different experimental runs.

Chapter \ref{chap:anns} provided the reader with a number of techniques that are used to evaluate \ac{FFNN} performance during training. Broadly these techniques measure the output of some loss/cost function and accuracy for classification problems. For the classifications problems, the loss metrics used included \ac{SparseCatXE} and \ac{BinXE}. Their accuracy equivalent metrics are then also used. For regression problems, \ac{RMSE} is used as a loss metric.

As mentioned in the preceding sections, datasets are split into a training set and a test dataset. The training set is used to train the model and the test set is used to test the model. Evaluation takes place at the end of each mini-batch iteration. Loss and accuracy is measured for both training and test datasets and is captured at each mini-batch iteration.

Post processing of the results yield a average rank (by test loss metric) between configurations at each mini-batch step across all runs. This test loss metric and rank then form experimental results that are then statistically analysed.

\section{Stopping Conditions}
\label{sec:methodology:stopping_conditions}

This section sheds light on the stopping conditions that are used.

Early stopping is a technique where training is prematurely stopped due to training saturation. A popular technique for early stopping includes a check to see if the validation/test loss has improved in the last $k$ steps. If the loss has not improved, the training is halted and the last best model weights are used.

It was decided not to use early stopping in this empirical process. Since the \ac{BHH} is a novel \ac{HH}, there are lots of uncertainty around its performance. It is unsure as to how the \ac{BHH} will behave, should overfitting take place. By eliminating early stop, the \ac{BHH} is evaluated until a maximum number of epochs (30) is reached. It is recommended that future research make use of early stopping.

The different experimental groups are given next.

\section{Experiments}
\label{sec:methodology:experiments}

This section presents the experimental groups that form part of the empirical process. There are broadly 3 main groups. These include a behavioural case study, a critical evaluation of the \ac{BHH} baseline's performance compared to other standalone low-level \index{heuristic}heuristics and finally an analysis of different \ac{BHH} variants is done by analysing the effects of different parameter values on the outcomes of the \ac{BHH}. Each of these sections are discussed in more detail below.

\subsection{Behavioural Case Study}
\label{sec:methodology:experiments:case_study}

This experimental group is concerned with objectively studying the behaviour of the \ac{BHH} baseline across a number of runs. This is meant to be an introductory analysis of the \ac{BHH} and includes analysis of the selection mechanism as well as the perturbative nature of the \ac{BHH}. It is important to mention that this experimental group is not meant to be statistically analysed, but to rather provide a detailed visual analysis of a number of hand-picked example runs, to determine if the \ac{BHH} is behaving as expected. It also provides a gentle introduction to the \ac{BHH}'s inner workings. From these observations, it is determined if the \ac{BHH} is learning and that selection is indeed biasing towards better performance. It also provides an opportunity to determine the outcome of the perturbative component of the \ac{BHH} which includes proxied \index{heuristic}heuristic update step operations.

Two different configurations of the \ac{BHH} baseline is trained using the iris dataset \cite{ref:fisher:1936}. These configurations include a replay window size of 10 (short memory) and a high replay window size of 250 (long memory). Each configuration is repeat 3 times. Finally these configurations are compared to a run that is purely random.

The analysis is primarily done by dissecting the output of various parameters and studying the plots of their values. From these plots, conclusions about the \ac{BHH}'s behaviour is made.

\subsection{Standalone Optimisers}
\label{sec:methodology:experiments:standalone_optimisers}

THis section presents the details with the experimental group that focuses on evaluating the performance of the \ac{BHH} with that of standalone \index{heuristics}/optimisers.

For this experimental group, the heuristics and optimisers as presented in Section \ref{sec:methodology:heuristics} are used, along with their specified parameters. Each of these are then compared to that of the \ac{BHH} baseline configuration which is presented in Section \ref{sec:methodology:baseline_bhh}.

The next section provides the details around different \ac{BHH} variants that are evaluated.

\subsection{BHH Variants}
\label{sec:methodology:experiments:bhh_variants}

This section provides the details of the experimental group that focuses on \ac{BHH} variants and the effect that different hyper-parameter configurations can have on the outcome of the \ac{BHH}.

The different variants and their possible configurations is given in Table \ref{tab:methodology:experiments:bhh_variants} below.

\begin{table}[htbp]
    \centering
    \caption{BHH variants and their configuration}
    \label{tab:methodology:experiments:bhh_variants}%
    \par\bigskip
    \resizebox{0.9\textwidth}{!}{
        \begin{tabular}{rcc}
            \multicolumn{1}{c}{\textbf{hyper-heuristic}} & \textbf{variant} & \textbf{values} \\
            \midrule
            \multicolumn{1}{l}{bhh} & heuristic\_pool & all,gd,mh \\
            & population & 5,10,15,20,25 \\
            & credit & ibest,pbest,rbest,gbest,symmetric \\
            & reselection & 1,5,10,15,20 \\
            & replay & 1,5,10,15,20 \\
            & reanalysis & 1,5,10,15,20 \\
            & burn\_in & 0,5,10,15,20 \\
            & normalise & false,true \\
            & discounted\_rewards & false,true \\
        \end{tabular}%
    }
\end{table}%

Take note that the \index{heuristics}heuristic pool options \textit{gd} and \textit{mh} refers to the \index{heuristics}heuristic pool configurations where the heuristic pools contain only gradient-descent heuristics or only \{index{meta-heuristics}meta-heuristics  respectively.

The next section explains in detail how the results are statistically analysed.

\section{Statistical Analysis}
\label{sec:methodology:statistical_analysis}

This section provides the detail of the process that is used to execute the statistical analysis of the results.

Various experimental groups and the details of the configuration is given in the preceding sections. Each of these experimental groups are statistically analysed on their own. To ensure there is statistically sufficient sample, each experimental group and configuration is trained for 30 epochs, repeated over 30 runs. As it is mentioned above, the results contain performance evaluation data in the form of training and testing, loss and accuracy measurements. Each experimental run is then ranked by these metrics. Each run is executed using a unique seeding value such such that each run is identical in its setup and configuration (apart from seeding values) and independent of the other runs.

Each experimental group goes through a set of steps that are followed during the statistical analysis process. First, the descriptive analysis is done to ensure that each experiment has the required data it needs. This includes 30 runs per configuration, across 15 datasets, across the applicable number of experimental configurations set up by that particular experimental group. The spread of the data is analysed to evaluate for overfit and outliers are identified. The skewness of the results is evaluated per dataset and the \index{Shapiro-Wilk}Shapiro-Wilk test for normality ($\alpha$ = 0.001) is used to determine in the results are normally distributed. The full statistical analysis reports are presented in Appendix \ref{app:statistical_analysis} and provides descriptive plots of the data's distribution. Furthermore, the \index{Levene}Levene's test for equality of variance ($\alpha$ = 0.001) is used.

Dependent on the outcomes of the above statistical tests, the appropriate statistical significance test is then executed. For configurations of independent variables where there are only 2 classes, the Mann-Whitney U\index{Mann-Whitney U} independent samples t-Test ($\alpha$ = 0.001) is executed and for configurations of 3 or more configuration classes, the \ac{ANOVA} statistical test ($\alpha$ = 0.001) is used. The\index{Kruskal-Wallis} Kruskal-Wallis ranked non-parametric test for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.

As mentioned earlier in the chapter, results are analysed for statistical significance over all the steps during the training process across all runs. This helps determine if there is statistical difference in the execution of various experimental configurations, throughout the entire training process, but also to cater for overfitting, which is to be studied as well.

Regardless of the statistical test that is used, a post-hoc Tukey honest significant difference test ($\alpha$ = 0.001) is used from which significant ranking is retrieved. Descriptive and critical difference plots are then retrieved from these results to provide visual aid, but all conclusions are made from statistically analysed data as mentioned above.

\section{Implementation and Execution}
\label{sec:methodology:implementation}

This section sheds some light as to the details of the implementation and execution of the empircal process.

All implementation is done from first principles in Python 3.9 using Tensorflow 2.7 and Tensorflow Probability 0.15.0. Most underlying function are reused from the Tensorflow library, however, all heuristics/optimisers are implemented from first principles to fit the \ac{HH} framework that was developed. All source code and data is provided is resources in this dissertation.

It should be noted that this implementation makes heavy use of CPU processing, due to the nature of modeling flattening for the \index{heuristic}heuristics. For this reason, execution is much more timely and costly than with GPU training. The authors hope that as the \ac{BHH} evolves, that better GPU implementations may speed up execution times.

With regards to the computational power that was used the execute this empirical process. All experiments were run on the CHPC's cluster. This included 14 servers each running 24-56 cores and 256GB memory each. The entire empirical process took 6 days.

\section{Summary}
\label{sec:methodology:summary}

This chapter provided the detail around the methodology that is used to execute the empirical process. The datasets, models and heuristics that are used during the empirical process have been presented in detail. A baseline \ac{BHH} has been formulated. The empirical process was defined in terms of a number of different experiments and finally, the process of statistical analysis of the results was provided.

The results and findings of the empirical process are presented in the following chapter.

### 2022-09-12 dissertation/chapters/08-results.tex
📝 (review): First set of changes

\chapter{Results}
\label{chap:results}

\begin{quote}
    \textit{
    ``Without data, you are just another person with an opinion.'' - W. Edwards Deming
    }
\end{quote}

The last step in the scientific process requires the presentation and objective discussion of empirical findings with good statistical backing. From the problem statements and motivations made in Chapter \ref{chap:introduction}, goals have been defined that broadly include literature studies and a sound empirical process. Thus far, the reader has been provided with a vast scope of background information relevant to the development of the \Acs{BHH}. Chapters \ref{chap:introduction} - \ref{chap:probability} provided the background information, literature studies and existing landscape of research for \acp{ANN}, \index{heuristic}heuristics/\index{optimiser}optimisers, \acp{HH} and probability theory. These elements all share common elements that are required to understand the proposed \Acp{BHH} which was presented in Chapter \ref{chap:bhh}. The details around the empirical process was formally proposed in the methodology as presented in Chapter \ref{chap:methodology}. Finally, the results for the empirical process can be presented and this chapter aims to provide these results.

As a reminder, the empirical process is split into two main experimental groups. These include a behavioural case study and set of comparative studies. This chapter is organised into the same logical pattern. Each of these experimental groups is provided as its own section for detailed analysis and discussion of findings. The remainder of the chapter is structured as follows:

\begin{itemize}
    \item \textbf{Section \ref{sec:results:overview}} provides a brief overview of the general empirical process, high level discussion points and a brief discussion on results interpretation.

    \item \textbf{Section \ref{sec:results:case_study}} provides a detailed analysis of the behaviour of the \Acs{BHH} over a few example runs during training and testing and is meant to introduce the analysis of the \Acs{BHH} from a behavioural characteristic point of view. In this section, focus is put on the learning process itself and to determine what happens during training. It aims to provide insight into ``how'' and ``when'' the \Acs{BHH} learning happens.

    \item \textbf{Section \ref{sec:results:standalone}} provides the first of a series of comparative studies. This section presents the comparative analysis that studies the performance capabilities of the baseline configuration of the \Acs{BHH} to that of standalone/individual low level \index{heuristic}heuristics/\index{optimiser}optimisers. The sections that follow focus on the effect of various parameters on the \Acs{BHH}.

    \item \textbf{Sections \ref{sec:results:heuristic_pool}} - \ref{sec:results:discounted_rewards} capture the results of these empirical processes and focus on the configuration of the \textit{heuristic pool}, the \textit{population size}, \textit{credit assignment strategies}, \textit{reselection} window size, \textit{replay} window size, \textit{reanalysis} window size, \textit{burn in}, \textit{normalisation} and \textit{discounted rewards}, respectfully.

    \item \textbf{Section \ref{sec:results:computational_requirements}} contains a brief discussion on the computational requirements.

    \item \textbf{Section \ref{sec:results:overfitting}} provides a brief discussion on overfitting.

    \item Finally, a summary of the findings is given in \textbf{Section \ref{sec:results:summary}}.
\end{itemize}

\section{Overview}
\label{sec:results:overview}

This section aims to provide a general high level discussion on the outcomes of the empirical process as an introduction to the more detailed discussions to follow. Consider again the goals that have been defined in \ref{chap:introduction}. The empirical component addresses three different angles of analysis:

\begin{enumerate}
    \item Analysing the behaviour of the \Acs{BHH} during training and testing to determine if the the concept works and that the \Acs{BHH} is indeed learning. This component looks at the \Acs{BHH} in isolation and simply evaluates the outcomes of its behaviour over a few example runs and repeats this process for two groups of \Acs{BHH} variants based on \textit{replay} window size.

    \item Comparing the performance capabilities of the \Acs{BHH} to that of well-known low-level \index{heuristic}heuristics that are well researched and understood. This component looks at how the \Acs{BHH} performs given a frame of reference to compare to. Careful consideration of results interpretation must be given here and is discussed in more detail below.

    \item Analysing the effects of various configurations of hyper-parameters for the \Acs{BHH}. This component looks at which parameters have a statistically significant impact on the outcomes of the \Acs{BHH}.
\end{enumerate}

It is important to briefly discuss how results should be interpreted. Traditionally, for typical low-level heuristic training, evaluation of performance is done at a chosen point in time and based on a particular dependent variable. This could be a fixed number of training steps/epochs, early stopped conditions or any other stopping condition. The metric of interest could be a loss value, an accuracy or a rank. Algorithms/heuristics in question are then logically ranked/organised according to their final solution and conclusions are made based on these findings. However, the following arguments suggest an alternative approach for this empirical study:

\begin{itemize}
    \item
    Since there does not exist any research on this specific implementation of \acp{HH} and its application to \acs{FFNN} training, there is no clear point at which it is known that the learning of the \acs{BHH} becomes detrimental to the training process. For example, there exists a currently unknown point during training where the performance bias towards the ``best'' \index{heuristic}heuristic no longer yield improved training or test generalisation outcomes. To cater for this, a fixed maximum number of training epochs have been chosen that empirically have been shown to be sufficient to notice diminishing returns in the outcome. \index{Early stopping}Early stopping was considered, but purposefully not implemented. This is to allow the study of the behaviour and capabilities of the \Acs{BHH} up to and beyond the point of diminishing returns.

    \item
    The training process is to some degree analogous and comparable to a dynamic optimisation problem as previously discussed. This means that the performance of \index{heuristic}heuristics, and thus the \Acs{BHH}, vary at different times during the training process. This hints to the hypothesis that was set in Chapter \ref{chap:introduction} and suggests that there is no single \index{heuristic}heuristic that is always the best \index{heuristic}heuristic to use during all of training. Rather, there exists an applicable, relevant \index{heuristic}heuristic (or combination of \index{heuristic}heuristics) to use at a given point in time during the training process and can change as the process continues. This means the selected \index{heuristic}heuristic at time step $t$ is not necessarily the best heuristic to select at timestamp $t+1$. This argument is further supported by the fact that these experiments are trained on mini-batches, resulting in a lot of noise during training. This noise can cause the \Ac{BHH} to want to "correct" a certain learnt belief. This introduces the same challenges as with \Ac{RL}: Consider delayed rewards, size of rewards, unlearning behaviour that is no longer required, all of which affect the training process throughout and not just at the point of stopping.
\end{itemize}

Based on the points made above, each experimental group is to be evaluated in isolation and has a specific area of focus. For all experimental groups, heuristics are evaluated during \textbf{all} the steps of the training and testing process. For this reason, ranking \index{heuristic}heuristic should not necessarily lead to the conclusion that one heuristic is \textit{better} than another, but rather, that there is a statistically significant difference between the outcomes of heuristics, relative to the entire training and testing process for a given experimental group. The authors suggest further research to include early stopping conditions for the ranking to make entirely sense. However, that does not mean the ranking approach is useless. It still provides a measure of comparison and is indeed indicative of statistically significant outcomes.

The points that have been discussed above have been observed during the empirical process. It is shown in the succeeding sections that the \Acs{BHH} is capable of training \Acp{FFNN} and that it does so relatively well. It is shown that the \Acs{BHH} is generally capable of providing good test generalisations when compared to existing low-level \index{heuristic}heuristics. However, it is shown that the majority of the influence of the \Acs{BHH} occurs during the first few epochs of the training process. Initially uniformly randomised candidate solutions has more room to learn in the initial phases of training in comparison to later phases where learning has become stagnated. It is also shown that this pivotal point of diminishing return is problem specific. Further to this pivotal point, it is shown that the \Acs{BHH} is subject to over-fitting, quite drastically. There are various conclusions that can be made from this point, but the detail is left to the relevant sections to follow.

The following section provides the results and findings for a behavioural case study of the \Acp{BHH} on the iris dataset.

\section{Case Study}
\label{sec:results:case_study}

This section provides a study on the behaviour of the \Acs{BHH} during training and testing. It is important to mention that this experimental group does not necessarily focus on the exact metrics, but rather on the general behaviour of the \Ac{BHH}. This means that statistical analysis and statistical certainty as is not required. Instead, a number of example runs have been executed purely for the intent of analysing behaviour. Furthermore, this behavioural case study is executed on a very small, but well-known toy dataset called \textit{iris}. Iris is not usually considered for full empirical processes due to its size and simplicity. Although there are fourteen other datasets to choose from, iris provides a very simple, relevant and relate-able case study that illustrate the necessary points sufficiently.

Figure \ref{fig:results:case_study:iris:metric_plots} illustrate these runs during training and testing. Take note of the legend as provided in Figure \ref{fig:results:case_study:iris:legend}. There are two variants of the \Acs{BHH} included here, each with three repeated runs, seeded according to run number:

\begin{itemize}
    \item \Acp{BHH} with a very \textbf{short memory}, i.e. replay windows size = 10
    \item \Acp{BHH} with a very \textbf{long memory}, i.e. replay windows size = 250
\end{itemize}

These two groups have been chosen as their parameters have been shown to provide drastically different outcomes from each other during training and forms a good basis for behavioural analysis. For more details on replay window size, see Section \ref{sec:results:replay}.

A breakdown of the run notation as provided in Figure \ref{fig:results:case_study:iris:legend} is then given as follows:

\begin{itemize}
    \item \textbf{iris} - The dataset in question
    \item \textbf{bhh} - The heuristic in question
    \item \textbf{hp:all} - The heuristic pool (hp) in question. ``All'' refers to all the implemented lower-level heuristics including both classical gradient-based heuristics/optimisers as well as meta-heuristics.
    \item \textbf{ps:5} - The population size (ps) in question. In this case, population size = 5.
    \item \textbf{bi:0} - The burn in window size (bi) in question. In this case, burn in window size = 0.
    \item \textbf{rp:10} - The replay window size (rp) in question. In this case, replay window size = 10.
    \item \textbf{rs:10} - The reselection window size (rp) in question. In this case, reselection window size = 10.
    \item \textbf{ra:10} - The reanalysis window size (rp) in question. In this case, reanalysis window size = 10.
    \item \textbf{nm:False} - The normalisation flag (nm) in question. In this case, normalisation is disabled.
    \item \textbf{ct:ibest} - The credit assignment strategy (ct) in question. In this case, the credit assignment strategy used is \textit{ibest}.
    \item \textbf{dr:False} - The discounted rewards flag (dr) in question. In this case, discounted rewards is disabled.
\end{itemize}

From figure \ref{fig:results:case_study:iris:metric_plots} it is shown that the \Acs{BHH} exhibit similar behaviours to that of lower-level heuristics. Figures \ref{fig:results:case_study:iris:train:loss} and \ref{fig:results:case_study:iris:train:accuracy} illustrates a smooth training process, converging to a well-known minimum loss for the iris dataset. In Figures \ref{fig:results:case_study:iris:test:loss} and \ref{fig:results:case_study:iris:test:accuracy} it is shown that the \Acs{BHH} generalised well on the test set. Generalisation improved up to about epoch 10 before overfitting starts occurring. From this, it can be concluded that most of the learning, for this particular dataset, takes place in the first 10 epochs of the training process. From this point onwards, the \Acs{BHH} tries to undo ``bad'' selections made earlier. It is interesting to notice that despite overfitting, the \Acs{BHH} was able to ``correct'' itself to some degree (up to epoch 20), but never really converged back on the minimum it reached up to epoch 10. Early stopping should prohibit this from happening, but this is left for further research.

\begin{figure}[htbp]
    \begin{subfigure}{0.49\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/train_loss.png}
        \caption{Train loss}
        \label{fig:results:case_study:iris:train:loss}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/test_loss.png}
        \caption{Test loss}
        \label{fig:results:case_study:iris:test:loss}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.49\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/train_accuracy.png}
        \caption{Train accuracy}
        \label{fig:results:case_study:iris:train:accuracy}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/test_accuracy.png}
        \caption{Test accuracy}
        \label{fig:results:case_study:iris:test:accuracy}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{\textwidth}
    	\centering
        \includegraphics[width=0.35\textwidth]{analysis/bhh_case_study/iris/legend.png}
        \caption{Legend}
        \label{fig:results:case_study:iris:legend}
    \end{subfigure}
    \par\bigskip
    \caption{Train and test behaviour of the \Ac{BHH} baseline for different configurations of replay window size}
    \label{fig:results:case_study:iris:metric_plots}
\end{figure}

A high level view of the train and test metric plots is good for drawing high level conclusions, but more detail is required. Figure \ref{fig:results:case_study:iris:alpha} aims to provide more detail as to what is happening during training and plots the value of $\alpha$ during training. Each sub-figure represents the value of $\alpha$ for a particular index, representing a particular \index{heuristic}heuristic. From sub-figures \ref{fig:results:case_study:iris:alpha:0}, \ref{fig:results:case_study:iris:alpha:2} and \ref{fig:results:case_study:iris:alpha:6}, the effect of a larger replay value is clear. Although a more detailed discussed on replay window sizes is left for Section \ref{sec:results:replay}, one can clearly see the accumulation of ``knowledge''/``evidence'' in the concentration parameter $\alpha$. It should be noticeable then from these sub-figures how $\alpha$ changes over time for runs with lower replay window sizes and is indicative of the learning capabilities of the \Ac{BHH}.  From these changes, one can formulate a prediction of which \index{heuristic}heuristics are then likely to be selected in the next steps.

Figures \ref{fig:results:case_study:iris:alpha:5} and \ref{fig:results:case_study:iris:alpha:9} contain a run in orange that shows how the concentration for a particular heuristic (\Acs{Adadelta} and \Acs{DE}) and can change over time. This suggests that the \Acs{BHH} has the ability to dynamically switch between heuristics as the need requires. This concept bears similarities to dynamic optimisation algorithms. It can thus be said that an observation is made that the \Acs{BHH} is able to learn (to some degree) to balance exploration and exploitation by dynamically changing the heuristic of interest at that point in time. Notice that it has not yet been established if the attempt to balance leads to good or bad outcomes. However, this is a still a useful feature of the \Acs{BHH} and warrants further discussion and reasoning. These statements further support the hypothesis that there might not be a no single specific heuristic that is the best heuristic to train the \Acs{FFNN} during the entire training process. In the succeeding sections, it is shown how this statement is further supported as the behaviour of the \Acs{BHH} is shown to be problem-dependent.

A clear distinction between Figures \ref{fig:results:case_study:iris:metric_plots} and \ref{fig:results:case_study:iris:alpha} should be pointed out. Figures \ref{fig:results:case_study:iris:metric_plots} plot metrics for every epoch, while Figure \ref{fig:results:case_study:iris:alpha} plot metrics for every mini-batch iteration. This is a subtle difference in visualisation, but nonetheless important. A more fine-grained visualisation illustrates the learning opportunities better since it is clear that a single step of learning happens on a single mini-batch iteration. This is important to keep in mind for various different sizes of datasets.

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[0].png}
        \caption{$\alpha_{0}$ - \Acs{SGD}}
        \label{fig:results:case_study:iris:alpha:0}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[1].png}
        \caption{$\alpha_{1}$ - \Acs{Momentum}}
        \label{fig:results:case_study:iris:alpha:1}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[2].png}
        \caption{$\alpha_{2}$ - \Acs{NAG}}
        \label{fig:results:case_study:iris:alpha:2}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[3].png}
        \caption{$\alpha_{3}$ - \Acs{Adagrad}}
        \label{fig:results:case_study:iris:alpha:3}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[4].png}
        \caption{$\alpha_{4}$ - \Acs{RMSProp}}
        \label{fig:results:case_study:iris:alpha:4}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[5].png}
        \caption{$\alpha_{5}$ - \Acs{Adadelta}}
        \label{fig:results:case_study:iris:alpha:5}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[6].png}
        \caption{$\alpha_{6}$ - \Acs{Adam}}
        \label{fig:results:case_study:iris:alpha:6}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[7].png}
        \caption{$\alpha_{7}$ - \Acs{PSO}}
        \label{fig:results:case_study:iris:alpha:7}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[8].png}
        \caption{$\alpha_{8}$ - \Acs{GA}}
        \label{fig:results:case_study:iris:alpha:8}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[9].png}
        \caption{$\alpha_{9}$ - \Acs{DE}}
        \label{fig:results:case_study:iris:alpha:9}
    \end{subfigure}
    \par\bigskip
    \caption{Change in the concentration of $\alpha$ during training for various heuristics}
    \label{fig:results:case_study:iris:alpha}
\end{figure}

Due to the Bayesian nature of the \Acs{BHH}, one can expect the plots from figure \ref{fig:results:case_study:iris:alpha} to drive the plots presented in \ref{fig:results:case_study:iris:p_theta} as these two parameters are related. The parameter $\alpha$ is the concentration parameter for the Dirichlet probability distribution represented by $\theta$. The reader is now urged to consider Figures \ref{fig:results:case_study:iris:alpha:6} and \ref{fig:results:case_study:iris:p_theta:6} together. These two figures illustrate the above mentioned Bayesian concepts well. It should be noted that as $\alpha$ changes, $\theta$ will change. More specifically, the longer the ``memory'' of the \Acs{BHH} the greater the magnitude of $\alpha$ resulting in a sampled selection probability $\theta$ that converges to the ``learnt'' expected selection probability ($E\left[\theta\right]$). The impact of this concept (retained memory) is addressed in Sections \ref{sec:results:replay}.

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[0].png}
        \caption{$P(\theta_{0} | \alpha)$ - \Acs{SGD}}
        \label{fig:results:case_study:iris:p_theta:0}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[1].png}
        \caption{$P(\theta_{1} | \alpha)$ - \Acs{Momentum}}
        \label{fig:results:case_study:iris:p_theta:1}
    \end{subfigure}
    \par\medskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[2].png}
        \caption{$P(\theta_{2} | \alpha)$ - \Acs{NAG}}
        \label{fig:results:case_study:iris:p_theta:2}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[3].png}
        \caption{$P(\theta_{3} | \alpha)$ - \Acs{Adagrad}}
        \label{fig:results:case_study:iris:p_theta:3}
    \end{subfigure}
    \par\medskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[4].png}
        \caption{$P(\theta_{4} | \alpha)$ - \Acs{RMSProp}}
        \label{fig:results:case_study:iris:p_theta:4}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[5].png}
        \caption{$P(\theta_{5} | \alpha)$ - \Acs{Adadelta}}
        \label{fig:results:case_study:iris:p_theta:5}
    \end{subfigure}
    \par\medskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[6].png}
        \caption{$P(\theta_{6} | \alpha)$ - \Acs{Adam}}
        \label{fig:results:case_study:iris:p_theta:6}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[7].png}
        \caption{$P(\theta_{7} | \alpha)$ - \Acs{PSO}}
        \label{fig:results:case_study:iris:p_theta:7}
    \end{subfigure}
    \par\medskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[8].png}
        \caption{$P(\theta_{8} | \alpha)$ - \Acs{GA}}
        \label{fig:results:case_study:iris:p_theta:8}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[9].png}
        \caption{$P(\theta_{9} | \alpha)$ - \Acs{DE}}
        \label{fig:results:case_study:iris:p_theta:9}
    \end{subfigure}
    \par\medskip
	\caption{Change in the sampled selection probability of $\theta$ during training for various heuristics}
	\label{fig:results:case_study:iris:p_theta}
\end{figure}

Another observation that can be made from Figures \ref{fig:results:case_study:iris:alpha} and \ref{fig:results:case_study:iris:p_theta} is that none of the runs are the same. This is of course due to the stochastic nature of the \Acs{BHH} and the noise caused by using mini-batches. However, it highlights the fact that the learning process for the \Acs{BHH} has to be adaptive from run to run. This is evident in the plots presented in Figure \ref{fig:results:case_study:iris:p_H} as one can see how the \index{heuristic}heuristic selection probability changes over time. This is proof that the \Ac{BHH} is learning something, but it is yet to be established what exactly it is learning. It is said that the \Acs{BHH} updates its \textit{beliefs} (prior knowledge) about which heuristic to select by biasing selection towards \index{heuristic}heuristic performance. It can therefore be concluded that any learning that is done, is done as a result of learning from performance. Since the performance criteria mechanism for the \Ac{BHH}, called the \textit{credit assignment strategy} marks a successful event as one meeting the performance criteria. Although this event is very much a local event, the continuous application of it over all runs means that learning does account for positive learning towards the overall performance goals.

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[0].png}
        \caption{$P\left(h_{0} | \theta \right)$ - \Acs{SGD}}
        \label{fig:results:case_study:iris:p_H:0}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[1].png}
        \caption{$P\left(h_{1} | \theta \right)$ - \Acs{Momentum}}
        \label{fig:results:case_study:iris:p_H:1}
    \end{subfigure}
    \par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[2].png}
		\caption{$P\left(h_{2} | \theta \right)$ - \Acs{NAG}}
		\label{fig:results:case_study:iris:p_H:2}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[3].png}
		\caption{$P\left(h_{3} | \theta \right)$ - \Acs{Adagrad}}
		\label{fig:results:case_study:iris:p_H:3}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[4].png}
		\caption{$P\left(h_{4} | \theta \right)$ - \Acs{RMSProp}}
		\label{fig:results:case_study:iris:p_H:4}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[5].png}
		\caption{$P\left(h_{5} | \theta \right)$ - \Acs{Adadelta}}
		\label{fig:results:case_study:iris:p_H:5}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[6].png}
		\caption{$P\left(h_{6} | \theta \right)$ - \Acs{Adam}}
		\label{fig:results:case_study:iris:p_H:6}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[7].png}
		\caption{$P\left(h_{7} | \theta \right)$ - \Acs{PSO}}
		\label{fig:results:case_study:iris:p_H:7}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[8].png}
		\caption{$P\left(h_{8} | \theta \right)$ - \Acs{GA}}
		\label{fig:results:case_study:iris:p_H:8}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[9].png}
		\caption{$P\left(h_{9} | \theta \right)$ - \Acs{DE}}
		\label{fig:results:case_study:iris:p_H:9}
	\end{subfigure}
	\par\medskip
	\caption{Change in the prior heuristic selection probability $P\left(H\right | \theta )$ as the \Ac{BHH} learns during training}
	\label{fig:results:case_study:iris:p_H}
\end{figure}

Consider now Figure \ref{fig:results:case_study:iris:p_theta:6} again, but this time include a configuration of the \Acs{BHH} where no \index{Bayesian Analysis}Bayesian Analysis takes place, resulting in a purely random \index{heuristic}heuristic selection probability throughout. Such an configuration is given in Figure \ref{fig:results:case_study:iris:no_learn:metrics} below for the sampled \index{heuristic}heuristic selection probability for \Acs{Adam} (gray).

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/no_learning_theta.png}
        \caption{$P(\theta_{6} | \alpha)$}
        \label{fig:results:case_study:iris:no_learn:p_theta}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/no_learning_test_loss.png}
        \caption{Test loss}
        \label{fig:results:case_study:iris:no_learn:test:loss}
    \end{subfigure}
    \par\bigskip
    \caption{Comparing baseline \Acp{BHH} to that of a \Ac{BHH} with pure random selection.}
    \label{fig:results:case_study:iris:no_learn:metrics}
\end{figure}

One can see that the random configuration (gray) illustrated almost a fixed pattern behaviour, from which we can draw the following conclusions:

\begin{itemize}
    \item Despite a completely random heuristic selection probability, the underlying \Acs{BHH} was still able to learn and perform relatively well. If the ability to learn is then purely based on the \textit{perturbative} components of the \Acs{BHH} it can be concluded that the proxied heuristic step operations are successful.

    \item This shows that the \Acs{BHH} selection mechanism is indeed facilitating a learning process and since \Acs{Adam} is known to perform well on the iris dataset, it can be concluded that the learning process is successful and beneficial to the outcome of the \Acs{BHH}.
\end{itemize}

The statements made above conclude the successful working of the \Acs{BHH}. Both the perturbative element (through proxied heuristic update steps) and the selection mechanism (through Bayesian analysis) is shown to work successfully. Figure \ref{fig:results:case_study:iris:p_HgEC} shows the resulting output of the predictive model for each of the five entities in the heuristic pool. This predicted heuristic selection probability is used to parameterise a new categorical distribution from which the heuristics are finally sampled and (re)selected.

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[0][6].png}
        \caption{$P\left(h_{6}|e_{0},c_{1}\right)$ - entity 0 + \Acs{Adam} }
        \label{fig:results:case_study:iris:p_HgEC:0:6}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[1][6].png}
        \caption{$P\left(h_{6}|e_{1},c_{1}\right)$ - entity 1 + \Acs{Adam} }
        \label{fig:results:case_study:iris:p_HgEC:1:6}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[2][6].png}
        \caption{$P\left(h_{6}|e_{2},c_{1}\right)$ - entity 2 + \Acs{Adam} }
        \label{fig:results:case_study:iris:p_HgEC:2:6}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[3][6].png}
        \caption{$P\left(h_{6}|e_{3},c_{1}\right)$ - entity 3 + \Acs{Adam} }
        \label{fig:results:case_study:iris:p_HgEC:3:6}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.5\textwidth]{analysis/bhh_case_study/iris/p_HgEC[4][6].png}
        \caption{$P\left(h_{6}|e_{4},c_{1}\right)$ - entity 4 + \Acs{Adam} }
        \label{fig:results:case_study:iris:p_HgEC:4:6}
    \end{subfigure}
    \par\bigskip
    \caption{Change in the realised output of the predictive model $P\left(H|E,C;\theta,\phi,\psi \right)$ showcasing the selection of the \Acs{Adam} optimiser/low-level heuristic as an example}
    \label{fig:results:case_study:iris:p_HgEC}
\end{figure}

Figure \ref{fig:results:case_study:iris:HgEC} show the resulting selected \index{heuristic}heuristic, per entity, over time. From these plots, one can see how convergence on \Acs{Adam} occurs at least at some point during training for the majority of the entities.

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[0].png}
        \caption{HgEC\lbrack0\rbrack - entity 0}
        \label{fig:results:case_study:iris:HgEC:0}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[1].png}
        \caption{HgEC\lbrack1\rbrack - entity 1}
        \label{fig:results:case_study:iris:HgEC:1}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[2].png}
        \caption{HgEC\lbrack2\rbrack - entity 2}
        \label{fig:results:case_study:iris:HgEC:2}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[3].png}
        \caption{HgEC\lbrack3\rbrack - entity 3}
        \label{fig:results:case_study:iris:HgEC:3}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.5\textwidth]{analysis/bhh_case_study/iris/HgEC[4].png}
        \caption{HgEC\lbrack4\rbrack - entity 4}
        \label{fig:results:case_study:iris:HgEC:4}
    \end{subfigure}
    \par\bigskip
    \caption{Change in selected heuristics (HgEC) during training for various entities}
    \label{fig:results:case_study:iris:HgEC}
\end{figure}

Finally, Figure \ref{fig:results:case_study:iris:adam:HgEC} below shows all of the probabilistic components involved in the selection mechanism of the \Ac{BHH}.

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[6].png}
		\caption{$\alpha_{6}$ - \Acs{Adam}}
		\label{fig:results:case_study:iris:adam:alpha:6}
	\end{subfigure}
    \begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[6].png}
		\caption{$P(\theta_{6} | \alpha)$ - \Acs{Adam}}
		\label{fig:results:case_study:iris:adam:p_theta:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[6].png}
		\caption{$P\left(h_{6} | \theta \right)$ - \Acs{Adam}}
		\label{fig:results:case_study:iris:adam:p_H:6}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[1][6].png}
        \caption{$P\left(h_{6}|e_{1},c_{1}\right)$ - entity 1 + \Acs{Adam} }
        \label{fig:results:case_study:iris:adam:p_HgEC:1:6}
    \end{subfigure}
    \par\bigskip
	\begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.5\textwidth]{analysis/bhh_case_study/iris/HgEC[1].png}
        \caption{HgEC\lbrack1\rbrack - entity 1}
        \label{fig:results:case_study:iris:adam:HgEC:1}
    \end{subfigure}
    \par\bigskip
	\caption{An illustration that shows the effects of learning as for \Acs{Adam}}
	\label{fig:results:case_study:iris:adam:HgEC}
\end{figure}

The behaviour of the \Ac{BHH} has been studied and it is found to be successful in its intent to learn which \index{heuristic}heuristics to use throughout the training process. It has also been shown that the training of the \acp{FFNN} with \Acp{BHH} is done by means of a \index{heuristic}heuristic selection mechanism and proxied \index{heuristic}heuristic update steps, both which have been shown to attribute to the successful training of the \acp{FFNN}.

Although these observations are good, these are still high level and not based on any statistical data. It is purely based on observation over a few runs. The following section aims to provide the first set of conclusions based on a statistically certain comparison of the \Ac{BHH}'s performance to that of standalone low-level \index{heuristic}heuristics.

\section{Standalone vs BHH Baseline}
\label{sec:results:standalone}

This section provides the empirical results of the experiment group that compare the performance of the \Ac{BHH} to that of well-known, standalone, low-level heuristics. Table \ref{tab:results:standalone:metrics} below shows the count, average and standard deviation of the ranks achieved by die various heuristics for all timestamps, across all datasets. Furthermore, the table orders the \index{heuristic}heuristics by a normalised overall rank.

\begin{table}[htbp]
  \centering
    \caption{Empirical results showcasing rank statistics for different standalone \index{heuristic}heuristics compared to the baseline \acs{BHH} across multiple datasets}
    \label{tab:results:standalone:metrics}%
    \par\bigskip
  \resizebox{\textwidth}{!}{
    \begin{tabular}{rcccccccccccc}
    \textbf{step} & \multicolumn{1}{l}{\textbf{(All)}} &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{1-2}          &       &       &       &       &       &       &       &       &       &       &       &  \\
          &       & \multicolumn{1}{l}{\textbf{heuristic}} &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{3-3}    \textbf{dataset} & \multicolumn{1}{l}{\textbf{statistic}} & \textbf{adagrad} & \textbf{adam} & \textbf{nag} & \textbf{rmsprop} & \textbf{bhh} & \textbf{adadelta} & \textbf{ga} & \textbf{sgd} & \textbf{pso} & \textbf{momentum} & \textbf{de} \\
    \midrule
    abalone & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.0323} & 2.2086 & 3.8108 & 4.0849 & 5.1430 & 4.7151 & 9.1839 & 6.9043 & 9.3914 & 7.9441 & 10.5817 \\
          & std   & 1.3436 & 1.5671 & 1.2760 & 2.2093 & 1.9327 & 1.1671 & 0.9030 & 0.7740 & 1.5268 & 0.9717 & 1.1291 \\
    adult & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 5.1570 & 6.3559 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4914} & 5.6968 & 10.1710 & 2.4720 & 7.7688 & 2.8237 & 9.6043 & 3.6688 & 9.0140 \\
          & std   & 1.2838 & 1.4823 & 0.6870 & 1.4006 & 2.2688 & 1.2974 & 1.3461 & 1.1988 & 1.6718 & 1.3834 & 1.5614 \\
    air\_quality & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 3.0688 & 4.4849 & 3.2527 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9269} & 5.4989 & 4.4204 & 6.3785 & 8.7548 & 8.1151 & 9.8301 & 9.2688 \\
          & std   & 1.8148 & 2.0087 & 1.7266 & 2.0466 & 2.5018 & 2.5575 & 1.7707 & 1.4074 & 1.9775 & 1.3046 & 1.9578 \\
    bank  & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 2.4161 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9882} & 3.8516 & 3.1591 & 5.4688 & 5.0108 & 9.0505 & 7.2301 & 9.9043 & 7.3892 & 10.5312 \\
          & std   & 1.3873 & 1.3985 & 1.4056 & 1.8653 & 1.7489 & 0.9864 & 0.9955 & 0.9144 & 1.2374 & 0.8907 & 1.0445 \\
    bike  & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6710} & 3.2559 & 5.4247 & 5.4140 & 3.5903 & 4.3774 & 7.2591 & 8.3656 & 7.4000 & 8.7441 & 10.4978 \\
          & std   & 1.1854 & 3.2580 & 0.9310 & 3.7231 & 1.0534 & 1.0684 & 1.0992 & 1.3163 & 1.6037 & 1.2745 & 1.2717 \\
    car   & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 3.8591 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5022} & 5.0839 & 2.0946 & 2.9720 & 6.5903 & 8.9301 & 8.4108 & 7.0118 & 9.0731 & 10.4720 \\
          & std   & 0.8054 & 1.1602 & 0.6925 & 1.1095 & 1.0151 & 1.4439 & 1.2877 & 1.2333 & 1.2970 & 1.1743 & 1.2916 \\
    diabetic & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 2.6129 & 6.0634 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7473} & 5.8387 & 7.9452 & 2.5129 & 9.2409 & 5.1968 & 8.7527 & 5.5516 & 10.5376 \\
          & std   & 1.3914 & 1.6944 & 1.2492 & 2.0128 & 2.4141 & 1.3843 & 1.2206 & 1.2711 & 0.9424 & 1.3025 & 1.0607 \\
    fish\_toxicity & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 3.6032 & 3.0742 & 4.8742 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.0462} & 4.8387 & 6.5785 & 5.5419 & 9.6462 & 6.2484 & 10.2731 & 8.2753 \\
          & std   & 2.0999 & 2.0463 & 2.2127 & 1.8158 & 2.2145 & 2.7393 & 2.2031 & 1.2726 & 2.4357 & 1.1959 & 2.0085 \\
    forest\_fires & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 4.1269 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.4634} & 4.6075 & 4.0860 & 4.4172 & 5.2011 & 5.8978 & 8.8591 & 5.2172 & 9.7538 & 10.3699 \\
          & std   & 2.4170 & 2.2577 & 1.7329 & 2.4576 & 2.5304 & 2.5924 & 1.9010 & 1.0073 & 2.6924 & 1.0954 & 1.7882 \\
    housing & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 3.0043 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9484} & 3.9495 & 3.2505 & 3.7720 & 6.2290 & 6.4538 & 9.4570 & 8.1570 & 9.3140 & 9.4645 \\
          & std   & 1.6877 & 1.5719 & 2.0695 & 1.7785 & 1.9772 & 2.1729 & 1.6569 & 1.3649 & 1.9825 & 1.3537 & 1.8465 \\
    iris  & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 5.1613 & 3.0269 & 3.0462 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3925} & 4.3624 & 9.4419 & 6.6667 & 8.4839 & 6.9333 & 9.1344 & 7.3505 \\
          & std   & 1.2630 & 1.9064 & 1.6829 & 1.5569 & 2.4400 & 1.6211 & 1.4704 & 1.2011 & 3.6375 & 1.2817 & 2.7492 \\
    mushroom & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 3.6548 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8935} & 5.3484 & 2.2183 & 3.1484 & 5.5613 & 9.6634 & 7.9290 & 6.7774 & 9.0559 & 10.7495 \\
          & std   & 0.8854 & 1.5571 & 0.8150 & 1.1594 & 2.0245 & 0.9914 & 0.9675 & 0.8373 & 0.7826 & 0.9205 & 1.2513 \\
    parkinsons & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 2.2925 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.0376} & 6.2882 & 3.1634 & 3.8269 & 5.5226 & 6.5172 & 9.7839 & 7.0301 & 10.5785 & 8.9591 \\
          & std   & 1.2860 & 1.4103 & 1.1341 & 1.9798 & 1.4677 & 1.8893 & 1.3465 & 0.9741 & 1.4772 & 1.1491 & 1.1386 \\
    student\_performance & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495} & 9.6022 & 2.7731 & 10.5204 & 4.8806 & 2.8742 & 5.9376 & 5.6280 & 9.1957 & 5.6731 & 6.6656 \\
          & std   & 1.5171 & 1.8140 & 1.7252 & 1.1290 & 2.5544 & 1.5612 & 1.5940 & 1.7346 & 0.8806 & 1.6999 & 1.4815 \\
    wine\_quality & count & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930   & 930 \\
          & avg   & 2.9774 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9634} & 3.7194 & 3.2624 & 4.6140 & 5.2989 & 8.6882 & 7.3806 & 9.3785 & 8.0796 & 10.6376 \\
          & std   & 1.7194 & 1.4491 & 1.6072 & 1.4218 & 1.5987 & 1.9742 & 1.2730 & 0.9310 & 1.4409 & 1.0672 & 1.1360 \\
    \midrule
    \textbf{overall} & \textbf{avg} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{3.1925}} & \textbf{3.5913} & \textbf{3.9513} & \textbf{4.0770} & \textbf{4.9766} & \textbf{5.1204} & \textbf{7.5452} & \textbf{7.6569} & \textbf{7.9411} & \textbf{8.2709} & \textbf{9.5584} \\
    \textbf{normalised} & \textbf{rank} & \cellcolor[rgb]{ .388,  .745,  .482}\textbf{1} & \cellcolor[rgb]{ .51,  .78,  .486}\textbf{2} & \cellcolor[rgb]{ .631,  .816,  .494}\textbf{3} & \cellcolor[rgb]{ .753,  .851,  .502}\textbf{4} & \cellcolor[rgb]{ .875,  .886,  .51}\textbf{5} & \cellcolor[rgb]{ 1,  .922,  .518}\textbf{6} & \cellcolor[rgb]{ .996,  .824,  .502}\textbf{7} & \cellcolor[rgb]{ .992,  .722,  .482}\textbf{8} & \cellcolor[rgb]{ .984,  .616,  .459}\textbf{9} & \cellcolor[rgb]{ .98,  .514,  .439}\textbf{10} & \cellcolor[rgb]{ .973,  .412,  .42}\textbf{11} \\
    \end{tabular}%
    }
\end{table}%

From Table \ref{tab:results:standalone:metrics} it can be seen that \index{heuristic}heuristic performance is problem/dataset specific. Despite this fact, it can be seen that the \Ac{BHH} managed to perform fairly well across almost all datasets (apart from the adult dataset for which discussions follow later) and achieved a normalised overall rank of 5 out of 12. As mentioned before, the rank should be taken with a pinch of salt, however, it does show the general capabilities of the \Ac{BHH}. It is expected that the performance of the \Ac{BHH} should be close to that of the best \index{heuristic}heuristic for that particular dataset. Both the rank and test loss metrics are indicative of this. Table \ref{tab:results:standalone:anova} shows the results of the ANOVA statistical test and it shows that the results are statistically significant between the heuristics.

\begin{table}[htbp]
	\centering
	\caption{ANOVA - Rank - Standalone vs BHH Baseline}
	\label{tab:results:standalone:anova}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrr}
			\toprule
			Cases & Sum of Squares & df & Mean Square & F & p  \\
			\cmidrule[0.4pt]{1-6}
			dataset & $248.990$ & $14$ & $17.785$ & $6.515$ & $<$ .001  \\
			heuristic & $699163.514$ & $10$ & $69916.351$ & $25612.484$ & $<$ .001  \\
			dataset * heuristic & $421571.950$ & $140$ & $3011.228$ & $1103.104$ & $<$ .001  \\
			Residuals & $418433.761$ & $153285$ & $2.730$ & &  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
		\end{tabular}
	}
\end{table}

\begin{table}[htbp]
	\centering
	\caption{Post Hoc Comparisons - Standalone vs BHH Baseline}
	\label{tab:results:standalone:post_hoc}%
	\par\bigskip
	\resizebox{0.7\textwidth}{!}{
		\begin{tabular}{lrrrrrrr}
			\toprule
			\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
			\cline{4-5}
			$ $ & $ $ & Mean Difference & Lower & Upper & SE & t & p$_{tukey}$  \\
			\cmidrule[0.4pt]{1-8}
			adadelta & adagrad & $1.928$ & $1.864$ & $1.992$ & $0.020$ & $97.455$ & $<$ .001  \\
			$ $ & adam & $1.529$ & $1.466$ & $1.593$ & $0.020$ & $77.298$ & $<$ .001  \\
			 & bhh & $0.144$ & $0.080$ & $0.207$ & $0.020$ & $7.269$ & $<$ .001  \\
			 & de & $-4.438$ & $-4.502$ & $-4.374$ & $0.020$ & $-224.330$ & $<$ .001  \\
			 & ga & $-2.425$ & $-2.488$ & $-2.361$ & $0.020$ & $-122.570$ & $<$ .001  \\
			 & momentum & $-3.150$ & $-3.214$ & $-3.087$ & $0.020$ & $-159.251$ & $<$ .001  \\
			 & nag & $1.169$ & $1.106$ & $1.233$ & $0.020$ & $59.100$ & $<$ .001  \\
			 & pso & $-2.821$ & $-2.884$ & $-2.757$ & $0.020$ & $-142.583$ & $<$ .001  \\
			 & rmsprop & $1.043$ & $0.980$ & $1.107$ & $0.020$ & $52.744$ & $<$ .001  \\
			 & sgd & $-2.536$ & $-2.600$ & $-2.473$ & $0.020$ & $-128.216$ & $<$ .001  \\
			adagrad & adam & $-0.399$ & $-0.462$ & $-0.335$ & $0.020$ & $-20.158$ & $<$ .001  \\
			$ $ & bhh & $-1.784$ & $-1.848$ & $-1.720$ & $0.020$ & $-90.187$ & $<$ .001  \\
			 & de & $-6.366$ & $-6.430$ & $-6.302$ & $0.020$ & $-321.786$ & $<$ .001  \\
			 & ga & $-4.353$ & $-4.416$ & $-4.289$ & $0.020$ & $-220.026$ & $<$ .001  \\
			 & momentum & $-5.078$ & $-5.142$ & $-5.015$ & $0.020$ & $-256.707$ & $<$ .001  \\
			 & nag & $-0.759$ & $-0.822$ & $-0.695$ & $0.020$ & $-38.355$ & $<$ .001  \\
			 & pso & $-4.749$ & $-4.812$ & $-4.685$ & $0.020$ & $-240.039$ & $<$ .001  \\
			 & rmsprop & $-0.885$ & $-0.948$ & $-0.821$ & $0.020$ & $-44.711$ & $<$ .001  \\
			 & sgd & $-4.464$ & $-4.528$ & $-4.401$ & $0.020$ & $-225.671$ & $<$ .001  \\
			adam & bhh & $-1.385$ & $-1.449$ & $-1.322$ & $0.020$ & $-70.029$ & $<$ .001  \\
			$ $ & de & $-5.967$ & $-6.031$ & $-5.903$ & $0.020$ & $-301.628$ & $<$ .001  \\
			 & ga & $-3.954$ & $-4.018$ & $-3.890$ & $0.020$ & $-199.868$ & $<$ .001  \\
			 & momentum & $-4.680$ & $-4.743$ & $-4.616$ & $0.020$ & $-236.549$ & $<$ .001  \\
			 & nag & $-0.360$ & $-0.424$ & $-0.296$ & $0.020$ & $-18.197$ & $<$ .001  \\
			 & pso & $-4.350$ & $-4.414$ & $-4.286$ & $0.020$ & $-219.881$ & $<$ .001  \\
			 & rmsprop & $-0.486$ & $-0.549$ & $-0.422$ & $0.020$ & $-24.553$ & $<$ .001  \\
			 & sgd & $-4.066$ & $-4.129$ & $-4.002$ & $0.020$ & $-205.513$ & $<$ .001  \\
			bhh & de & $-4.582$ & $-4.645$ & $-4.518$ & $0.020$ & $-231.599$ & $<$ .001  \\
			$ $ & ga & $-2.569$ & $-2.632$ & $-2.505$ & $0.020$ & $-129.839$ & $<$ .001  \\
			 & momentum & $-3.294$ & $-3.358$ & $-3.231$ & $0.020$ & $-166.520$ & $<$ .001  \\
			 & nag & $1.025$ & $0.962$ & $1.089$ & $0.020$ & $51.831$ & $<$ .001  \\
			 & pso & $-2.965$ & $-3.028$ & $-2.901$ & $0.020$ & $-149.852$ & $<$ .001  \\
			 & rmsprop & $0.900$ & $0.836$ & $0.963$ & $0.020$ & $45.476$ & $<$ .001  \\
			 & sgd & $-2.680$ & $-2.744$ & $-2.617$ & $0.020$ & $-135.485$ & $<$ .001  \\
			de & ga & $2.013$ & $1.949$ & $2.077$ & $0.020$ & $101.760$ & $<$ .001  \\
			$ $ & momentum & $1.287$ & $1.224$ & $1.351$ & $0.020$ & $65.079$ & $<$ .001  \\
			 & nag & $5.607$ & $5.543$ & $5.671$ & $0.020$ & $283.431$ & $<$ .001  \\
			 & pso & $1.617$ & $1.554$ & $1.681$ & $0.020$ & $81.747$ & $<$ .001  \\
			 & rmsprop & $5.481$ & $5.418$ & $5.545$ & $0.020$ & $277.075$ & $<$ .001  \\
			 & sgd & $1.901$ & $1.838$ & $1.965$ & $0.020$ & $96.115$ & $<$ .001  \\
			ga & momentum & $-0.726$ & $-0.789$ & $-0.662$ & $0.020$ & $-36.681$ & $<$ .001  \\
			$ $ & nag & $3.594$ & $3.530$ & $3.658$ & $0.020$ & $181.670$ & $<$ .001  \\
			 & pso & $-0.396$ & $-0.460$ & $-0.332$ & $0.020$ & $-20.013$ & $<$ .001  \\
			 & rmsprop & $3.468$ & $3.405$ & $3.532$ & $0.020$ & $175.315$ & $<$ .001  \\
			 & sgd & $-0.112$ & $-0.175$ & $-0.048$ & $0.020$ & $-5.645$ & $<$ .001  \\
			momentum & nag & $4.320$ & $4.256$ & $4.383$ & $0.020$ & $218.352$ & $<$ .001  \\
			$ $ & pso & $0.330$ & $0.266$ & $0.393$ & $0.020$ & $16.668$ & $<$ .001  \\
			 & rmsprop & $4.194$ & $4.130$ & $4.258$ & $0.020$ & $211.996$ & $<$ .001  \\
			 & sgd & $0.614$ & $0.550$ & $0.678$ & $0.020$ & $31.036$ & $<$ .001  \\
			nag & pso & $-3.990$ & $-4.054$ & $-3.926$ & $0.020$ & $-201.683$ & $<$ .001  \\
			$ $ & rmsprop & $-0.126$ & $-0.189$ & $-0.062$ & $0.020$ & $-6.356$ & $<$ .001  \\
			 & sgd & $-3.706$ & $-3.769$ & $-3.642$ & $0.020$ & $-187.316$ & $<$ .001  \\
			pso & rmsprop & $3.864$ & $3.800$ & $3.928$ & $0.020$ & $195.328$ & $<$ .001  \\
			$ $ & sgd & $0.284$ & $0.221$ & $0.348$ & $0.020$ & $14.367$ & $<$ .001  \\
			rmsprop & sgd & $-3.580$ & $-3.644$ & $-3.516$ & $0.020$ & $-180.960$ & $<$ .001  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 11 estimates (confidence intervals corrected using the tukey method).} \\
			% \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
			% \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
		\end{tabular}
	}
\end{table}

Table \ref{tab:results:standalone:post_hoc} presents the results of the Post Hoc Tukey test and Figure \ref{fig:results:standalone:descriptive:descriptive} provides a descriptive plot that provides an alternative visualisation to see how the performance of the \Ac{BHH} compares across datasets and how it compares to other low-level heuristics.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/standalone/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of standalone heuristics compared to the baseline \Acs{BHH} per dataset, across all runs and steps.}
	\label{fig:results:standalone:descriptive:descriptive}
\end{figure}

Figure \ref{fig:results:standalone:descriptive:cd} provides the critical difference plots for the average ranks of the heuristics across all datasets. From this one can see five statistically significant groups of heuristics, with the \Ac{BHH} falling in the middle in group three.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/standalone/figures/cd/overall.png}
	\caption{Critical difference plots between the average ranks of standalone heuristics compared to the baseline \Acs{BHH}, across all datasets, runs and steps.}
	\label{fig:results:standalone:descriptive:cd}
\end{figure}

Figure \ref{fig:results:standalone:figures:car} provides example training and test loss and accuracy plots for all heuristics for the car dataset and Figure \ref{fig:results:standalone:figures:iris} provides the same plots, but for the iris dataset. These plots are provided to visualise the training and test outcomes over time. Figure \ref{fig:results:standalone:figures:loss:test:iris} was included to show how drastic the overfitting can become if early stopping is not employed. One can see that most of the gradient-based heuristics performed as expected, by the population-based approaches really struggle after learning has become stagnated. This is an important concept, because one has to remember that the \Ac{BHH} might ``try-out'' a certain heuristic and in a single step could cause the heuristic to generalise badly on the test set. Once again, the noise of mini-batches plays a large role here.

Finally, a collection of test loss plots for various datasets is given in Figures \ref{fig:results:standalone:figures:test:loss:various1} and \ref{fig:results:standalone:figures:test:loss:various2}.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/train/loss/car.png}
        \caption{Train loss}
        \label{fig:results:standalone:figures:loss:train:car}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/car.png}
        \caption{Test loss}
        \label{fig:results:standalone:figures:loss:test:car}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/train/accuracy/car.png}
        \caption{Train accuracy}
        \label{fig:results:standalone:figures:accuracy:train:car}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/accuracy/car.png}
        \caption{Test accuracy}
        \label{fig:results:standalone:figures:accuracy:test:car}
	\end{subfigure}
	\par\bigskip
	\caption{Standalone vs. \Acs{BHH} baseline - train, test loss and accuracy - dataset: car}
	\label{fig:results:standalone:figures:car}
\end{figure}

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/train/loss/iris.png}
        \caption{Train loss}
        \label{fig:results:standalone:figures:loss:train:iris}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/iris.png}
        \caption{Test loss}
        \label{fig:results:standalone:figures:loss:test:iris}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/train/accuracy/iris.png}
        \caption{Train accuracy}
        \label{fig:results:standalone:figures:accuracy:train:iris}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/accuracy/iris.png}
        \caption{Test accuracy}
        \label{fig:results:standalone:figures:accuracy:test:iris}
	\end{subfigure}
	\par\bigskip
	\caption{Standalone vs. \Acs{BHH} baseline - train, test loss and accuracy - dataset: iris}
	\label{fig:results:standalone:figures:iris}
\end{figure}

\begin{figure}[htbp]
	\begin{subfigure}{0.48\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/air_quality.png}
        \caption{air\_quality}
        \label{fig:results:standalone:figures:test:loss:air_quality}
	\end{subfigure}
    \begin{subfigure}{0.48\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/bank.png}
        \caption{bank}
        \label{fig:results:standalone:figures:test:loss:bank}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/bike.png}
        \caption{bike}
        \label{fig:results:standalone:figures:test:loss:bike}
	\end{subfigure}
    \begin{subfigure}{0.48\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/fish_toxicity.png}
        \caption{fish\_toxicity}
        \label{fig:results:standalone:figures:test:loss:fish_toxicity}
	\end{subfigure}
	\caption{Standalone vs. \Acs{BHH} baseline - test loss across different datasets part 1}
	\label{fig:results:standalone:figures:test:loss:various1}
\end{figure}

\begin{figure}[htbp]
	\begin{subfigure}{0.48\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/forest_fires.png}
        \caption{forest\_fires}
        \label{fig:results:standalone:figures:test:loss:forest_fires}
	\end{subfigure}
    \begin{subfigure}{0.48\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/housing.png}
        \caption{housing}
        \label{fig:results:standalone:figures:test:loss:housing}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/parkinsons.png}
        \caption{parkinsons}
        \label{fig:results:standalone:figures:test:loss:parkinsons}
	\end{subfigure}
    \begin{subfigure}{0.48\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/wine_quality.png}
        \caption{wine\_quality}
        \label{fig:results:standalone:figures:test:loss:wine_quality}
	\end{subfigure}
	\caption{Standalone vs. \Acs{BHH} baseline - test loss across different datasets part 2}
	\label{fig:results:standalone:figures:test:loss:various2}
\end{figure}

From this experimental group it was shown that the \Ac{BHH} was able to perform relatively well, but was not able to outperform the best \index{heuristic}heuristics. This is understandable as there is a lot of noise that makes the learning process imperfect. Although learning was shown to be successful, there are many suggestions that could lead to better outcomes. One such a suggestion is to add a validation step, similar to that of \ac{MCMC} (ref???), before concentration parameters are accepted and updated. Another is to provide the \Ac{BHH} with expert knowledge in its priors. For example: if it is known that a certain heuristic works well for a certain dataset, one could bias the priors by biasing the value of  $\alpha$, the concentration parameter for the prior probability distribution, to have an higher initial selection probability (compared to uniform/symmetric selection) for \Ac{Adam}. This is a major advantage that the \Ac{BHH} has above other heuristics, the ability to provide expert prior knowledge if needed.

The experiment is deemed successful and the results show promise for the field of \Acp{HH} in general, but specifically in training \Acp{FFNN}. The following sections delve into the hyper-parameters of the \Ac{BHH} and how it impacts its performance.

\section{Heuristic Pool}
\label{sec:results:heuristic_pool}

This section provides the empirical results for an experimental group where the heuristic pool configuration is studied in comparison to the baseline \Ac{BHH}. As a reminder to the reader, the heuristic pool refers to the collection of low-level heuristics from which the \Ac{BHH} can select. The baseline \Ac{BHH} has a heuristic pool configuration that includes all ten of the low-level heuristics including gradient-based heuristics and meta-heuristics. Two alternative heuristic pools are then considered for investigation. These includes a configuration where the heuristic pool only consist out of gradient-based low-level heuristics and the other configuration includes only meta-heuristics. Table \ref{tab:results:heuristic_pool:metrics} presents the results of the average ranks, per heuristic, per dataset, across all runs, similar to what has been done for other experiments in this chapter.

\begin{table}[htbp]
  \centering
  \caption{Empirical results showcasing rank statistics for different heuristic pool configurations used by the \acs{BHH} across multiple datasets}
    \label{tab:results:heuristic_pool:metrics}%
    \par\bigskip
  \resizebox{\textwidth}{!}{
    \begin{tabular}{rccccccccc}
    \textbf{step} & \multicolumn{1}{l}{\textbf{(All)}} &       &       &       &       &       &       &       &  \\
\cmidrule{1-2}          &       &       &       &       &       &       &       &       &  \\
          & \multicolumn{1}{l}{\textbf{pool}} & \multicolumn{1}{l}{\textbf{metrics}} &       &       &       &       &       &       &  \\
\cmidrule{2-3}          & \textbf{all} &       &       & \textbf{gd} &       &       & \textbf{mh} &       &  \\
\cmidrule{2-10}    \textbf{dataset} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} \\
    \midrule
    abalone & 930   & 1.7946 & 0.6411 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3828} & 0.5604 & 930   & 2.8226 & 0.4198 \\
    adult & 930   & 2.8484 & 0.5058 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.1559} & 0.4077 & 930   & 1.8989 & 0.4104 \\
    air\_quality & 930   & 2.1871 & 0.8153 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6828} & 0.7506 & 930   & 2.1301 & 0.7883 \\
    bank  & 930   & 1.7731 & 0.5617 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3215} & 0.4920 & 930   & 2.9054 & 0.3341 \\
    bike  & 930   & 1.6247 & 0.5529 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4387} & 0.5321 & 930   & 2.9366 & 0.2808 \\
    car   & 930   & 1.5903 & 0.5113 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4409} & 0.5180 & 930   & 2.9688 & 0.2275 \\
    diabetic & 930   & 2.4516 & 0.7353 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.2806} & 0.5756 & 930   & 2.2677 & 0.5798 \\
    fish\_toxicity & 930   & 1.9903 & 0.8485 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8344} & 0.7684 & 930   & 2.1753 & 0.7959 \\
    forest\_fires & 930   & 2.0667 & 0.8338 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8269} & 0.7813 & 930   & 2.1065 & 0.8066 \\
    housing & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6043} & 0.6869 & 930   & 1.6602 & 0.6648 & 930   & 2.7355 & 0.5238 \\
    iris  & 930   & 1.8581 & 0.8005 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7806} & 0.7272 & 930   & 2.3613 & 0.7960 \\
    mushroom & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5204} & 0.5815 & 930   & 1.5484 & 0.5273 & 930   & 2.9312 & 0.2890 \\
    parkinsons & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5570} & 0.6238 & 930   & 1.6011 & 0.5915 & 930   & 2.8419 & 0.4448 \\
    student\_performance & 930   & 1.9828 & 0.8220 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7903} & 0.8480 & 930   & 2.2269 & 0.7152 \\
    wine\_quality & 930   & 1.5785 & 0.5498 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935} & 0.5630 & 930   & 2.9280 & 0.2938 \\
    \midrule
    \textbf{overall} & \textbf{13950} & \textbf{1.8952} & \textbf{0.7730} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.5492}} & \textbf{0.6651} & \textbf{13950} & \textbf{2.5491} & \textbf{0.6684} \\
    \end{tabular}%
    }
\end{table}%

As one would expect, the \index{heuristic pool}heuristic pool for gradient-based-only \index{heuristic}heuristics consistently do significantly better than the baseline and the meta-heuristic configurations. This is to be expected for the following reasons:

\begin{itemize}
    \item Gradient-based approaches are currently the state-of-the art in \Ac{FFNN} training and is the standard approach for doing so. (Ref???)

    \item Switching between gradient-based approaches are easier as they require very little proxied state operations. Where they do require proxied state operations, almost all of them borrow from \Ac{Adam}, one of the best gradient-based heuristics at the time of writing.

    \item All the meta-heuristics included are population-based. Since an entire population can be updated at once, the impact of a wrong selection is much larger.
\end{itemize}

Although it is quite intuitive that the gradient-based \index{heuristic}heuristics would perform well, it does place a constraint on the \Ac{BHH} that the correct heuristics have to be included in the heuristic pool for the \Ac{BHH} to perform similar to the best heuristics. However, if a general pool of heuristics with a wide set of capabilities and characteristics is included, the \Ac{BHH} should perform reasonably well and generalise well on the test set. From the results presented throughout this section, it is shown that the performance of the \Ac{BHH} is itself problem-dependent. Therefore, one can not expect the \Ac{BHH} to perform equally well on all datasets. Earlier in Figure \ref{tab:results:standalone:metrics} it was shown that the \Ac{BHH} performed well on all datasets except for adult dataset. This is due to overfitting chaos early-on as will be shown later. However, if the gradient-only heuristic pool configuration was used, the \Ac{BHH} would've performed much better. As a reminder to the reader, the goal of this dissertation is not to develop a universal best heuristic, but rather one that could automate the tedious process of heuristic and parameter search, saving a lot of time.

Table \ref{tab:results:heuristic_pool:anova} provides the results of the ANOVA statistical test and one can see the statistical significance of the results.

\begin{table}[htbp]
	\centering
	\caption{ANOVA - Rank - BHH Variant: Heuristic Pool}
	\label{tab:results:heuristic_pool:anova}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrr}
			\toprule
			Cases & Sum of Squares & df & Mean Square & F & p  \\
			\cmidrule[0.4pt]{1-6}
			dataset & $2.710$ & $14$ & $0.194$ & $0.495$ & $0.938$  \\
			heuristic\_pool & $7193.497$ & $2$ & $3596.749$ & $9192.243$ & $<$ .001  \\
			dataset * heuristic\_pool & $4376.103$ & $28$ & $156.289$ & $399.430$ & $<$ .001  \\
			Residuals & $16357.497$ & $41805$ & $0.391$ & &  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
		\end{tabular}	
	}
\end{table}

Similar to the analysis for other experimental groups, the post hoc tukey test results are given in Table \ref{tab:results:heuristic_pool:post_hoc} below. From this table one can see how statistically different the gradient-based heuristic pool performs from the other configurations.

\begin{table}[htbp]
	\centering
	\caption{Post Hoc Comparisons - BHH Variant: Heuristic Pool}
	\label{tab:results:heuristic_pool:post_hoc}%
	\par\bigskip
	\resizebox{\textwidth}{!}
	{
		\begin{tabular}{lrrrrrrr}
			\toprule
			\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
			\cline{4-5}
			$ $ & $ $ & Mean Difference & Lower & Upper & SE & t & p$_{tukey}$  \\
			\cmidrule[0.4pt]{1-8}
			all & gd & $0.346$ & $0.328$ & $0.364$ & $0.007$ & $46.189$ & $<$ .001  \\
			$ $ & mh & $-0.654$ & $-0.671$ & $-0.636$ & $0.007$ & $-87.306$ & $<$ .001  \\
			gd & mh & $-1.000$ & $-1.017$ & $-0.982$ & $0.007$ & $-133.495$ & $<$ .001  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 3 estimates (confidence intervals corrected using the tukey method).} \\
			% \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
			% \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
		\end{tabular}
	}
\end{table}

Figure \ref{fig:results:heuristic_pool:descriptive:descriptive} provides the descriptive plots for this experimental group. It shows the average rank achieved by heuristics across different datasets. Once again, we can see how the performance of the heuristics are problem-dependent.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_heuristic_pool/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying heuristic pools per dataset, across all runs and steps.}
	\label{fig:results:heuristic_pool:descriptive:descriptive}
\end{figure}

As with the other sections, figure \ref{fig:results:heuristic_pool:descriptive:cd} provides the critical difference plots and finally, example test loss plots are given in Figure \ref{fig:results:heuristic_pool:figures:loss}.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_heuristic_pool/figures/cd/overall.png}
	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying heuristic pools across all datasets, runs and steps.}
	\label{fig:results:heuristic_pool:descriptive:cd}
\end{figure}

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_heuristic_pool/figures/test/loss/abalone.png}
        \caption{abalone}
        \label{fig:results:heuristic_pool:figures:loss1}
	\end{subfigure}
		\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_heuristic_pool/figures/test/loss/wine_quality.png}
        \caption{wine\_quality}
        \label{fig:results:heuristic_pool:figures:loss2}
	\end{subfigure}
	\caption{\Acs{BHH} Heuristic Pool - example test loss plots for varying heuristic pools}
	\label{fig:results:heuristic_pool:figures:loss}
\end{figure}

In this section it was established that the choice of heuristic pool has a significant impact on the outcome of the \Ac{BHH}. It was shown that the gradient-only pool significantly performs better than the baseline configuration that includes all the heuristics and the meta-heuristic-only pool.

The following section presents the empirical results for the experimental group that focuses on studying the effects of population size on the \Ac{BHH}.

\section{Population}
\label{sec:results:population}

This section investigates the effects of population size on the \Ac{BHH}. Initially the expectation was that a larger population size would perform best as this is the general consensus for population-based \index{heuristic}heuristics (ref ????). However, it has been found that population size is largely problem-dependent with some datasets preferring a small population size and others a large population size. Table \ref{tab:results:population:metrics} presents these empirical results.

\begin{table}[htbp]
  \centering
      \caption{Empirical results showcasing rank statistics for different population size values used by the \acs{BHH} across multiple datasets}
    \label{tab:results:population:metrics}%
    	\par\bigskip
  \resizebox{\textwidth}{!}{
  \begin{tabular}{rccccccccccccccc}
    \textbf{step} & \multicolumn{1}{l}{\textbf{(All)}} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{1-2}          &       &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
          & \multicolumn{1}{l}{\textbf{population}} & \multicolumn{1}{l}{\textbf{metrics}} &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{2-3}          & \multicolumn{1}{l}{\textbf{5}} &       &       & \multicolumn{1}{l}{\textbf{10}} &       &       & \multicolumn{1}{l}{\textbf{15}} &       &       & \multicolumn{1}{l}{\textbf{20}} &       &       & \multicolumn{1}{l}{\textbf{25}} &       &  \\
\cmidrule{2-16}    \textbf{dataset} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} \\
    \midrule
    abalone & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4387} & 1.3396 & 930   & 2.7452 & 1.3922 & 930   & 3.0129 & 1.3865 & 930   & 3.4065 & 1.3513 & 930   & 3.3968 & 1.3514 \\
    adult & 930   & 3.5720 & 1.4693 & 930   & 3.2828 & 1.3751 & 930   & 2.8108 & 1.3625 & 930   & 2.6484 & 1.3222 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3634} & 1.3063 \\
    air\_quality & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7527} & 1.4283 & 930   & 2.9258 & 1.3904 & 930   & 2.9656 & 1.3791 & 930   & 3.3140 & 1.3789 & 930   & 3.0419 & 1.4374 \\
    bank  & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8129} & 1.4102 & 930   & 3.1591 & 1.4348 & 930   & 2.9989 & 1.4199 & 930   & 3.0505 & 1.4438 & 930   & 2.9785 & 1.3414 \\
    bike  & 930   & 3.8957 & 1.3355 & 930   & 2.8688 & 1.2850 & 930   & 2.9645 & 1.3447 & 930   & 2.7430 & 1.3762 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5280} & 1.3278 \\
    car   & 930   & 3.1892 & 1.3915 & 930   & 3.0409 & 1.3945 & 930   & 3.0398 & 1.4523 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8559} & 1.3938 & 930   & 2.8742 & 1.4151 \\
    diabetic & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7978} & 1.5078 & 930   & 2.9387 & 1.4133 & 930   & 3.2129 & 1.4525 & 930   & 2.9613 & 1.3036 & 930   & 3.0892 & 1.3534 \\
    fish\_toxicity & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8151} & 1.4249 & 930   & 3.0409 & 1.4288 & 930   & 3.0925 & 1.3230 & 930   & 3.1280 & 1.4073 & 930   & 2.9237 & 1.4634 \\
    forest\_fires & 930   & 3.0172 & 1.4026 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9215} & 1.3800 & 930   & 2.9806 & 1.3833 & 930   & 3.0968 & 1.4124 & 930   & 2.9839 & 1.4879 \\
    housing & 930   & 2.8366 & 1.4040 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8258} & 1.3802 & 930   & 2.9753 & 1.4393 & 930   & 2.9849 & 1.4111 & 930   & 3.3774 & 1.3680 \\
    iris  & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301} & 1.3038 & 930   & 2.8731 & 1.3970 & 930   & 3.0505 & 1.4129 & 930   & 3.1860 & 1.4251 & 930   & 3.0602 & 1.4987 \\
    mushroom & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7989} & 1.2052 & 930   & 2.9441 & 1.3250 & 930   & 3.0462 & 1.4521 & 930   & 3.1366 & 1.4940 & 930   & 3.0538 & 1.5664 \\
    parkinsons & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6645} & 1.4411 & 930   & 3.1065 & 1.3272 & 930   & 3.0247 & 1.4265 & 930   & 3.0495 & 1.4420 & 930   & 3.1548 & 1.3810 \\
    student\_performance & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6376} & 1.4357 & 930   & 2.8645 & 1.4108 & 930   & 3.1548 & 1.4042 & 930   & 3.2387 & 1.3970 & 930   & 3.1043 & 1.3395 \\
    wine\_quality & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5505} & 1.3165 & 930   & 2.7817 & 1.4152 & 930   & 3.1581 & 1.3841 & 930   & 3.1806 & 1.3941 & 930   & 3.3290 & 1.4140 \\
    \midrule
    \textbf{overall} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9073}} & \textbf{1.4377} & \textbf{13950} & \textbf{2.9546} & \textbf{1.3904} & \textbf{13950} & \textbf{3.0325} & \textbf{1.4045} & \textbf{13950} & \textbf{3.0654} & \textbf{1.4108} & \textbf{13950} & \textbf{3.0173} & \textbf{1.4306} \\
    \end{tabular}%
    }
\end{table}%

Tables \ref{tab:results:population:anova} presents the ANOVA statistical test results and Table \ref{tab:results:population:post_hoc} presents the post hoc Tukey test results. Both these tables present the results as statistically significant.

\begin{table}[htbp]
	\centering
	\caption{ANOVA - Rank - BHH Variant: Population}
	\label{tab:results:population:anova}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
        \begin{tabular}{lrrrrr}
			\toprule
			Cases & Sum of Squares & df & Mean Square & F & p  \\
			\cmidrule[0.4pt]{1-6}
			dataset & $17.974$ & $14$ & $1.284$ & $0.659$ & $0.816$  \\
			population & $225.672$ & $4$ & $56.418$ & $28.961$ & $<$ .001  \\
			dataset * population & $3879.662$ & $56$ & $69.280$ & $35.564$ & $<$ .001  \\
			Residuals & $135730.233$ & $69675$ & $1.948$ & &  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
		\end{tabular}
	}

\end{table}

\begin{table}[htbp]
	\centering
	\caption{Post Hoc Comparisons - BHH Variant: Population}
	\label{tab:results:population:post_hoc}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
        \begin{tabular}{lrrrrrrr}
			\toprule
			\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
			\cline{4-5}
			$ $ & $ $ & Mean Difference & Lower & Upper & SE & t & p$_{tukey}$  \\
			\cmidrule[0.4pt]{1-8}
			$5$ & $10$ & $-0.047$ & $-0.093$ & $-0.002$ & $0.017$ & $-2.831$ & $0.037$  \\
			$ $ & $15$ & $-0.125$ & $-0.171$ & $-0.080$ & $0.017$ & $-7.494$ & $<$ .001  \\
			 & $20$ & $-0.158$ & $-0.204$ & $-0.112$ & $0.017$ & $-9.458$ & $<$ .001  \\
			 & $25$ & $-0.110$ & $-0.156$ & $-0.064$ & $0.017$ & $-6.580$ & $<$ .001  \\
			$10$ & $15$ & $-0.078$ & $-0.124$ & $-0.032$ & $0.017$ & $-4.663$ & $<$ .001  \\
			$ $ & $20$ & $-0.111$ & $-0.156$ & $-0.065$ & $0.017$ & $-6.627$ & $<$ .001  \\
			 & $25$ & $-0.063$ & $-0.108$ & $-0.017$ & $0.017$ & $-3.749$ & $0.002$  \\
			$15$ & $20$ & $-0.033$ & $-0.078$ & $0.013$ & $0.017$ & $-1.965$ & $0.283$  \\
			$ $ & $25$ & $0.015$ & $-0.030$ & $0.061$ & $0.017$ & $0.914$ & $0.892$  \\
			$20$ & $25$ & $0.048$ & $0.003$ & $0.094$ & $0.017$ & $2.878$ & $0.033$  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
			% \multicolumn{8}{p{0.5\linewidth}}{$ $ * p $<$ .05, ** p < .01, *** p < .001} \\
			% \multicolumn{8}{p{0.5\linewidth}}{* $$} \\
			% \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
			% \multicolumn{8}{p{0.5\linewidth}}{** $$} \\
		\end{tabular}
	}
\end{table}

From the descriptive plots given in Figure \ref{fig:results:population:descriptive:descriptive} one can see how radically different the outcomes are for each dataset. This clearly shows that population size, in most cases prefer a small population size, but there are multiple cases where a larger population size is preferred. Consider the plots for the abalone and adult datasets in this figure. They exhibit opposite outcomes for population size. Abalone prefers a small population size, while adult prefers larger population sizes. This makes the population size relatively problem dependent with a general tendency to prefer smaller population sizes.

Another interesting observation to make is that for many of the descriptive plots such as for student\_performance, fish\_toxicity, iris, mushroom and bank, the average rank and population size is not linearly correlated which suggests an interesting opportunity for further investigation.

Postulate for a moment why in some cases a smaller population size could be preferred. A larger population size means more combinations of heuristics and entities. Statistically these require many more samples to be able to achieve the same level of learning as with smaller populations. Since the nature of the \Ac{BHH} is in statistical and probabilistic components it makes sense that a larger sample leads to a harder learning and training process. As a reminder to the reader, the \ac{BHH} selection mechanism is a posterior probability distribution that is dependent on an entity and performance criteria. The larger the number of entities, the bigger the number of combinations in which this posterior distribution can be realises. Furthermore, with larger population sizes, the difficulty of managing and maintaining consistent entity state from iteration to iteration, between the switching of heuristics, increases drastically. This means that invalid selections and bad state update operations are more likely to propagate throughout the population. This argument is yet to be determined empirically, but it could be that the outcome of population size could be determined by the difference in importance between the selection mechanism's influence on the outcome or the perturbative mechanism's influence.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_population/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying population sizes per dataset, across all runs and steps.}
	\label{fig:results:population:descriptive:descriptive}
\end{figure}

As with the other experimental groups, the critical difference plot for the various population sizes over all datasets is given in Figure \ref{fig:results:population:descriptive:cd}. The plot here shows just exactly how problem-depenent the population size is. This is evident from the insignificance between population sizes is you consider their performance over all datasets, yet the descriptive plots from Figure \ref{fig:results:population:descriptive:descriptive} clearly show statistically significant results for each configuration of population size for each dataset.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_population/figures/cd/overall.png}
	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying population sizes across all datasets, runs and steps.}
	\label{fig:results:population:descriptive:cd}
\end{figure}

Typically, as with the other sections, Figure \ref{fig:results:population:figures:loss} presents some example test loss plots for the bike and housing datasets. Here one can clearly see the differences in the runs for the various population size configurations.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_population/figures/test/loss/bike.png}
        \caption{bike}
        \label{fig:results:population:figures:loss1}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_population/figures/test/loss/housing.png}
        \caption{housing}
        \label{fig:results:population:figures:loss2}
	\end{subfigure}
	\caption{\Acs{BHH} Population - example test loss plots for \Acsp{BHH} with varying population sizes} 
	\label{fig:results:population:figures:loss}
\end{figure}

 Alternative to the test loss plots is Figure \ref{fig:results:population:figures:loss} which was carefully selected. This figure plots the test accuracy for adult, the dataset for which the \Ac{BHH} performed worst compared to standalone heuristics as was shown in Section \ref{sec:results:standalone}. One can see that early stopping measures would've stopped the training process early ($< 5$ epochs), but since there is no early stopping, overfitting takes place in drastic effect. Notice how all population size configurations suffer from this problem.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_population/figures/test/accuracy/adult.png}
        \caption{adult}
        \label{fig:results:population:figures:accuracy1}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_population/figures/test/accuracy/car.png}
        \caption{car}
        \label{fig:results:population:figures:accuracy2}
	\end{subfigure}
	\caption{\Acs{BHH} Population - example test accuracy plots for \Acsp{BHH} with varying population sizes}
	\label{fig:results:population:figures:accuracy}
\end{figure}

Another suggestion for investigation could be the relationship between entity population size and heuristic pool size. As a reminder, the baseline \ac{BHH} has a default population size of 5. From the results, we can see that this was also the population size that performed well. In fact, it is the only case where population size $<$ heuristic pool size (10). There could thus exists some relationship between these parameters, perhaps such that population size $ < $ heuristic pool size. Thus certainly warrants for further investigation in the future.

In this section it was found that population size does have a significant impact on the outcomes of the \Ac{BHH} and surprisingly, it was found that a smaller population size is preferred instead of large ones. The following section provides a detailed analysis of the credit assignment strategies.

\section{Credit}
\label{sec:results:credit}

This section provides the empirical results for the experimental group that focuses on studying the effects of different credit assignment strategies on the outcomes of the \Ac{BHH}. As a reminder to the reader, the \Ac{BHH} baseline makes use of the \textit{ibest} credit assignment strategy. The empirical results are presented in Table \ref{tab:results:credit:metrics} below. At first glance, it should be noticed that the selection of the correct credit assignment strategy to use is very problem-dependent.

\begin{table}[htbp]
  \centering
      \caption{Empirical results showcasing rank statistics for different \index{credit}credit assignment strategies used by the \acs{BHH} across multiple datasets}
    \label{tab:results:credit:metrics}%
    \par\bigskip
  \resizebox{\textwidth}{!}{
    \begin{tabular}{rccccccccccccccc}
    \textbf{step} & \multicolumn{1}{l}{\textbf{(All)}} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{1-2}          &       &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
          & \multicolumn{1}{l}{\textbf{credit}} & \multicolumn{1}{l}{\textbf{metrics}} &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{2-3}          & \multicolumn{1}{l}{\textbf{ibest}} &       &       & \multicolumn{1}{l}{\textbf{pbest}} &       &       & \multicolumn{1}{l}{\textbf{rbest}} &       &       & \multicolumn{1}{l}{\textbf{gbest}} &       &       & \multicolumn{1}{l}{\textbf{symmetric}} &       &  \\
\cmidrule{2-16}    \textbf{dataset} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} \\
    \midrule
    abalone & 930   & 3.1677 & 1.3188 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613} & 1.4588 & 930   & 2.9968 & 1.3993 & 930   & 2.9667 & 1.4547 & 930   & 3.0075 & 1.4214 \\
    adult & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177 & 930   & 2.6763 & 1.5019 & 930   & 2.8065 & 1.5003 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177 & 930   & 3.3538 & 1.5682 \\
    air\_quality & 930   & 3.1312 & 1.3472 & 930   & 3.0376 & 1.3566 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5914} & 1.4646 & 930   & 3.1280 & 1.3358 & 930   & 3.1118 & 1.4871 \\
    bank  & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8591} & 1.3442 & 930   & 2.9903 & 1.4320 & 930   & 2.8882 & 1.4098 & 930   & 3.0441 & 1.4154 & 930   & 3.2183 & 1.4424 \\
    bike  & 930   & 3.0527 & 1.3401 & 930   & 3.0086 & 1.3935 & 930   & 3.0667 & 1.4825 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3393 & 930   & 2.9978 & 1.5028 \\
    car   & 930   & 3.1151 & 1.3562 & 930   & 3.0312 & 1.4826 & 930   & 3.2516 & 1.4024 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6892} & 1.3540 & 930   & 2.9129 & 1.4111 \\
    diabetic & 930   & 2.8914 & 1.3488 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6269} & 1.4171 & 930   & 3.4151 & 1.3653 & 930   & 2.8925 & 1.3620 & 930   & 3.1742 & 1.4487 \\
    fish\_toxicity & 930   & 3.1516 & 1.4360 & 930   & 2.9903 & 1.4521 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.4748 & 930   & 3.2043 & 1.2988 & 930   & 2.8957 & 1.3579 \\
    forest\_fires & 930   & 3.0968 & 1.2771 & 930   & 3.1806 & 1.3040 & 930   & 2.8559 & 1.3562 & 930   & 3.1215 & 1.5018 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7452} & 1.5627 \\
    housing & 930   & 2.9011 & 1.4938 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8527} & 1.3168 & 930   & 2.9022 & 1.3974 & 930   & 3.3108 & 1.3243 & 930   & 3.0333 & 1.4833 \\
    iris  & 930   & 3.1892 & 1.4281 & 930   & 3.0839 & 1.4412 & 930   & 3.0591 & 1.3755 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8237} & 1.4085 & 930   & 2.8441 & 1.3844 \\
    mushroom & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8075} & 1.4594 & 930   & 3.0183 & 1.4107 & 930   & 2.8957 & 1.3985 & 930   & 3.0839 & 1.4178 & 930   & 3.1720 & 1.3813 \\
    parkinsons & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5645} & 1.4835 & 930   & 2.8925 & 1.3429 & 930   & 3.5065 & 1.2190 & 930   & 3.0796 & 1.3920 & 930   & 2.9570 & 1.4548 \\
    student\_performance & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6624} & 1.3124 & 930   & 3.0290 & 1.4067 & 930   & 3.1892 & 1.3821 & 930   & 2.7978 & 1.4702 & 930   & 3.3215 & 1.3938 \\
    wine\_quality & 930   & 3.1871 & 1.3080 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366} & 1.4706 & 930   & 3.0140 & 1.3712 & 930   & 2.9419 & 1.4115 & 930   & 3.2204 & 1.4300 \\
    \midrule
    \textbf{overall} & \textbf{13950} & \textbf{2.9475} & \textbf{1.3805} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9277}} & \textbf{1.4222} & \textbf{13950} & \textbf{3.0131} & \textbf{1.4209} & \textbf{13950} & \textbf{2.9596} & \textbf{1.3921} & \textbf{13950} & \textbf{3.0644} & \textbf{1.4594} \\
    \end{tabular}%
    }
\end{table}%

Table \ref{tab:results:credit:anova} provides the ANOVA statistical test results and it can be seen that these credit assignment strategies are indeed statistically signficant from each other. Table \ref{tab:results:credit:post_hoc} provides the post hoc Tukey test results.

\begin{table}[htbp]
	\centering
		\caption{ANOVA - Rank - BHH Variant: Credit}
	\label{tab:results:credit:anova}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		%----- Requires booktabs package -----%
        \begin{tabular}{lrrrrr}
			\toprule
			Cases & Sum of Squares & df & Mean Square & F & p  \\
			\cmidrule[0.4pt]{1-6}
			dataset & $289.361$ & $14$ & $20.669$ & $10.532$ & $<$ .001  \\
			credit & $172.812$ & $4$ & $43.203$ & $22.015$ & $<$ .001  \\
			dataset * credit & $2680.102$ & $56$ & $47.859$ & $24.387$ & $<$ .001  \\
			Residuals & $136733.281$ & $69675$ & $1.962$ & &  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
		\end{tabular}
	}
\end{table}

\begin{table}[htbp]
	\centering
	\caption{Post Hoc Comparisons - BHH Variant: Credit}
	\label{tab:results:credit:post_hoc}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrrrr}
			\toprule
			\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
			\cline{4-5}
			$ $ & $ $ & Mean Difference & Lower & Upper & SE & t & p$_{tukey}$  \\
			\cmidrule[0.4pt]{1-8}
			gbest & ibest & $0.012$ & $-0.034$ & $0.058$ & $0.017$ & $0.718$ & $0.952$  \\
			$ $ & pbest & $0.032$ & $-0.014$ & $0.078$ & $0.017$ & $1.898$ & $0.319$  \\
			 & rbest & $-0.054$ & $-0.099$ & $-0.008$ & $0.017$ & $-3.192$ & $0.012$  \\
			 & symmetric & $-0.105$ & $-0.151$ & $-0.059$ & $0.017$ & $-6.248$ & $<$ .001  \\
			ibest & pbest & $0.020$ & $-0.026$ & $0.066$ & $0.017$ & $1.180$ & $0.763$  \\
			$ $ & rbest & $-0.066$ & $-0.111$ & $-0.020$ & $0.017$ & $-3.910$ & $<$ .001  \\
			 & symmetric & $-0.117$ & $-0.163$ & $-0.071$ & $0.017$ & $-6.966$ & $<$ .001  \\
			pbest & rbest & $-0.085$ & $-0.131$ & $-0.040$ & $0.017$ & $-5.090$ & $<$ .001  \\
			$ $ & symmetric & $-0.137$ & $-0.182$ & $-0.091$ & $0.017$ & $-8.146$ & $<$ .001  \\
			rbest & symmetric & $-0.051$ & $-0.097$ & $-0.005$ & $0.017$ & $-3.056$ & $0.019$  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
			% \multicolumn{8}{p{0.5\linewidth}}{$ $ * p $<$ .05, ** p < .01, *** p < .001} \\
			% \multicolumn{8}{p{0.5\linewidth}}{* $$} \\
			% \multicolumn{8}{p{0.5\linewidth}}{** $$} \\
			% \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
		\end{tabular}
	}
\end{table}

The descriptive plots as presented in Figure \ref{fig:results:credit:descriptive:descriptive} shows how different credit assignment strategies are prefered for different datasets. Interestingly, for the forest fires dataset, the preferred credit assignment strategy is statistically the \textit{symmetric} credit assignment strategy. As a reminder to the reader, the symmetric credit assignment strategy marks all performance outcomes as successful and thus as a result, no performance bias occurs, rendering the selection mechanism for the \Ac{BHH} useless since priors will never be updated. Notice that this does not necessarily make the symmetric credit assignment strategy completely random. With the random strategy, a single heuristic is selected and gets a successful count, where with symmetric credit assignment strategy gives a successful count for all selected heuristics.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_credit/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying credit assignment strategies per dataset, across all runs and steps.}
	\label{fig:results:credit:descriptive:descriptive}
\end{figure}

The critical difference provided in Figure \ref{fig:results:credit:descriptive:cd} supports the statement that the selection of the credit assignment strategy to use is problem-dependent.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_credit/figures/cd/overall.png}
	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying credit assignment strategies across all datasets, runs and steps.}
	\label{fig:results:credit:descriptive:cd}
\end{figure}

Figure \ref{fig:results:credit:figures:accuracy} provides good example test accuracy plots as for the car and iris datasets and Figure \ref{fig:results:credit:figures:loss} provides example test loss plots as for the abalone and student\_performance datasets. Figure \ref{fig:results:credit:figures:loss2} have been included to show the effects of the credit assignment stategies after overfitting has started.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_credit/figures/test/accuracy/car.png}
        \caption{car}
        \label{fig:results:credit:figures:accuracy1}
	\end{subfigure}
		\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_credit/figures/test/accuracy/iris.png}
        \caption{iris}
        \label{fig:results:credit:figures:accuracy2}
	\end{subfigure}
	\caption{\Acs{BHH} Credit - example test accuracy plots for varying credit assignment strategies}
	\label{fig:results:credit:figures:accuracy}
\end{figure}

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_credit/figures/test/loss/abalone.png}
        \caption{abalone}
        \label{fig:results:credit:figures:loss1}
	\end{subfigure}
		\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_credit/figures/test/loss/student_performance.png}
        \caption{student\_performance}
        \label{fig:results:credit:figures:loss2}
	\end{subfigure}
	\caption{\Acs{BHH} Credit - example test loss plots for varying credit assignment strategies}
	\label{fig:results:credit:figures:loss}
\end{figure}

This section has shown that there is a statistical difference between the outcomes of different credit assignment strategies per dataset. However, the choice of credit assignment strategy to use is shown to be problem-dependent.

The following section presents the findings for an experimental group which includes different reselection configurations.

\section{Reselection}
\label{sec:results:reselection}

This section provides the results for the next experimental group, which focuses on different reselection window sizes. As a reminder to the reader, the reselection window is the parameter that controls how often new \index{heuristic}heuristics are selected. The baseline \Ac{BHH} makes use of a reselection window size of 10.

Table \ref{tab:results:reselection:metrics} provides the empirical results for this experimental group. From these results it can be seen that a larger reselection window size is generally preferred. From a statistical point of view this makes sense. By lowering the frequency by which reselections happen, the \Ac{BHH} accumulates more information per entity, \index{heuristic}heuristic and credit combination. Since the \Ac{BHH} makes use of a probabilistic model, the bigger the sample size the better. However, this parameter can not be considered in isolation. Consider the replay window size and the reanalysis window size. These two parameters put constraints on the window of information that is considered for learning. If reselection is large, it does not make sense for the replay size to be low since the \Ac{BHH} will just forget information before reselection has occured. Furthermore, as mentioned before, there is inherently a trade-off between exploration and exploitation that is required, even at a \ac{HH} level. Admittidly, it is difficult to balance the trade-off between exploration and exploitation. Further research could investigate dynamic techniques such as parameter schedules.

Another possibility to consider is that larger reselection window sizes could be required because of noise. Perhaps there are too many noisy elements between iterations such that the \Ac{BHH} then requires a more stable configuration to learn sufficiently. Much more investigations is required here to confirm if this is the case, however, this was out of the scope for this dissertation. However, from a argumentative side it does make sense. Every time reselection occurs, state update operations also change due to the perturbative nature of the \Ac{BHH}. This could lead to many invalid selections, which in turn leads to bad state updates and ultimately affect the learning process negatively. Allowing selected low-level \index{heuristic}heuristic more time to run and learn allows for more consistent state update operations between iterations, catering best for noise introduced through mini-batch iterations and invalid selections.  Such investigation should pair well with early stopping and the suggestion that was made in \ref{sec:results:standalone} to add a validation step before a state update operations occur. This should insure that the update step operations only occur when needed and when valid. Nonetheless, an interesting result. The remainder of this section simply provides the results in similar fashion to the sections before.

\begin{table}[htbp]
    \centering
    \caption{Empirical results showcasing rank statistics for different reselection values used by the \acs{BHH} across multiple datasets}
    \label{tab:results:reselection:metrics}%
    \par\bigskip
    \resizebox{\textwidth}{!}{
    \begin{tabular}{rccccccccccccccc}
    \textbf{step} & \multicolumn{1}{l}{\textbf{(All)}} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{1-2}          &       &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
          & \multicolumn{1}{l}{\textbf{reselection}} & \multicolumn{1}{l}{\textbf{metrics}} &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{2-3}          & \multicolumn{1}{l}{\textbf{1}} &       &       & \multicolumn{1}{l}{\textbf{5}} &       &       & \multicolumn{1}{l}{\textbf{10}} &       &       & \multicolumn{1}{l}{\textbf{15}} &       &       & \multicolumn{1}{l}{\textbf{20}} &       &  \\
\cmidrule{2-16}    \textbf{dataset} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} \\
    \midrule
    abalone & 930   & 4.3548 & 0.9760 & 930   & 2.8473 & 1.2885 & 930   & 2.7505 & 1.2622 & 930   & 2.5602 & 1.2988 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4871} & 1.3182 \\
    adult & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7097} & 1.2671 & 930   & 4.4559 & 1.0052 & 930   & 3.4398 & 1.0453 & 930   & 2.7656 & 0.9837 & 930   & 2.3065 & 1.0670 \\
    air\_quality & 930   & 3.7355 & 1.4046 & 930   & 3.4075 & 1.3790 & 930   & 2.9688 & 1.2783 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4237} & 1.2281 & 930   & 2.4645 & 1.2906 \\
    bank  & 930   & 4.5677 & 0.7039 & 930   & 3.6323 & 1.1271 & 930   & 2.4237 & 1.1333 & 930   & 2.2462 & 1.1139 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1301} & 1.0957 \\
    bike  & 930   & 4.7935 & 0.6124 & 930   & 3.9204 & 0.6480 & 930   & 2.5161 & 0.8632 & 930   & 2.0763 & 0.9007 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6935} & 0.8911 \\
    car   & 930   & 4.6409 & 0.7847 & 930   & 2.9527 & 1.1581 & 930   & 2.6548 & 1.1748 & 930   & 2.5312 & 1.2440 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2204} & 1.2169 \\
    diabetic & 930   & 3.0129 & 1.0478 & 930   & 4.4624 & 0.8688 & 930   & 2.7957 & 1.1753 & 930   & 2.6065 & 1.4391 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1226} & 1.2639 \\
    fish\_toxicity & 930   & 3.7484 & 1.2377 & 930   & 3.1376 & 1.3174 & 930   & 3.0344 & 1.4062 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4656} & 1.3039 & 930   & 2.6140 & 1.4318 \\
    forest\_fires & 930   & 3.8194 & 1.4330 & 930   & 3.2720 & 1.2477 & 930   & 2.8656 & 1.3464 & 930   & 2.8194 & 1.3048 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2237} & 1.2186 \\
    housing & 930   & 4.1892 & 1.0993 & 930   & 3.0172 & 1.2882 & 930   & 2.5871 & 1.3541 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5312} & 1.2654 & 930   & 2.6753 & 1.3399 \\
    iris  & 930   & 2.9839 & 1.4244 & 930   & 2.9710 & 1.3165 & 930   & 3.3462 & 1.4182 & 930   & 3.0140 & 1.4054 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6849} & 1.4289 \\
    mushroom & 930   & 4.2065 & 1.2356 & 930   & 2.9688 & 1.2992 & 930   & 2.5860 & 1.2336 & 930   & 2.7882 & 1.3397 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4505} & 1.2259 \\
    parkinsons & 930   & 4.7645 & 0.7563 & 930   & 3.1882 & 1.0208 & 930   & 2.2957 & 1.2089 & 930   & 2.4968 & 1.1282 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2548} & 1.0973 \\
    student\_performance & 930   & 3.9710 & 1.0942 & 930   & 4.0226 & 1.1196 & 930   & 2.4774 & 1.2206 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495} & 1.2002 & 930   & 2.2796 & 1.1324 \\
    wine\_quality & 930   & 4.0688 & 1.1220 & 930   & 2.9204 & 1.2934 & 930   & 2.9559 & 1.3831 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4032} & 1.3779 & 930   & 2.6516 & 1.2796 \\
    \midrule
    \textbf{overall} & \textbf{13950} & \textbf{3.9044} & \textbf{1.3641} & \textbf{13950} & \textbf{3.4118} & \textbf{1.2914} & \textbf{13950} & \textbf{2.7799} & \textbf{1.2811} & \textbf{13950} & \textbf{2.5318} & \textbf{1.2660} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.3506}} & \textbf{1.2541} \\
    \end{tabular}%
    }
\end{table}%

Table \ref{tab:results:reselection:anova} provides the ANOVA statistical test results where one can see the statistical significance of the results. As with the other sections, Table \ref{tab:results:reselection:post_hoc} provides the post hoc Tukey test results. From this table, one can see the statistical significance that exists between all the different reselection window sizes.

\begin{table}[htbp]
	\centering
	\caption{ANOVA - Rank - BHH Variant: Reselection}
	\label{tab:results:reselection:anova}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrr}
			\toprule
			Cases & Sum of Squares & df & Mean Square & F & p  \\
			\cmidrule[0.4pt]{1-6}
			dataset & $18.065$ & $14$ & $1.290$ & $0.895$ & $0.564$  \\
			reselection & $23391.735$ & $4$ & $5847.934$ & $4055.181$ & $<$ .001  \\
			dataset * reselection & $15911.336$ & $56$ & $284.131$ & $197.027$ & $<$ .001  \\
			Residuals & $100477.574$ & $69675$ & $1.442$ & &   \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
		\end{tabular}
	}
\end{table}

\begin{table}[htbp]
	\centering
	\caption{Post Hoc Comparisons - BHH Variant: Reselection}
	\label{tab:results:reselection:post_hoc}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrrrr}
			\toprule
			\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
			\cline{4-5}
			$ $ & $ $ & Mean Difference & Lower & Upper & SE & t & p$_{tukey}$  \\
			\cmidrule[0.4pt]{1-8}
			$1$ & $5$ & $0.493$ & $0.453$ & $0.532$ & $0.014$ & $34.265$ & $<$ .001  \\
			$ $ & $10$ & $1.125$ & $1.085$ & $1.164$ & $0.014$ & $78.211$ & $<$ .001  \\
			 & $15$ & $1.373$ & $1.333$ & $1.412$ & $0.014$ & $95.461$ & $<$ .001  \\
			 & $20$ & $1.554$ & $1.515$ & $1.593$ & $0.014$ & $108.064$ & $<$ .001  \\
			$5$ & $10$ & $0.632$ & $0.593$ & $0.671$ & $0.014$ & $43.946$ & $<$ .001  \\
			$ $ & $15$ & $0.880$ & $0.841$ & $0.919$ & $0.014$ & $61.196$ & $<$ .001  \\
			 & $20$ & $1.061$ & $1.022$ & $1.100$ & $0.014$ & $73.799$ & $<$ .001  \\
			$10$ & $15$ & $0.248$ & $0.209$ & $0.287$ & $0.014$ & $17.250$ & $<$ .001  \\
			$ $ & $20$ & $0.429$ & $0.390$ & $0.468$ & $0.014$ & $29.853$ & $<$ .001  \\
			$15$ & $20$ & $0.181$ & $0.142$ & $0.220$ & $0.014$ & $12.603$ & $<$ .001  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
			% \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
			% \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
		\end{tabular}
	}
\end{table}

The outcome of this experimental group is best illustrated in Figure \ref{fig:results:reselection:descriptive:descriptive} which provides the reader with descriptive plots of the reselection window size. For this experimental group, even though the outcomes are slightly different per dataset, it can be seen that there is a general pattern here that suggests larger selection window sizes across all datasets. The only real exception to this is the adult dataset, for which it has already been establish that the \Ac{BHH} overfits drastically. There is a slight difference in outcome in the diabetic dataset and that could also be for the same reason.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying reselection values per dataset, across all runs and steps.}
	\label{fig:results:reselection:descriptive:descriptive}
\end{figure}

The critical difference plot as presented in \ref{fig:results:reselection:descriptive:cd} visually illustrates the statistical significance between average ranks achieved by the baseline \Ac{BHH} with various reselection windows size values.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/cd/overall.png}
	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying reselection values across all datasets, runs and steps.}
	\label{fig:results:reselection:descriptive:cd}
\end{figure}

Finally, Figure \ref{fig:results:reselection:figures:loss} provide example test loss plots for car and housing datasets where one can clearly see the difference in test loss outcomes with the larger reselection windows sizes is seen to perform best.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/test/loss/car.png}
        \caption{car}
        \label{fig:results:reselection:figures:loss1}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/test/loss/housing.png}
        \caption{housing}
        \label{fig:results:reselection:figures:loss2}
	\end{subfigure}
	\caption{\Acs{BHH} Selection - example test loss plots for \Acsp{BHH} with varying reselection window sizes} 
	\label{fig:results:reselection:figures:loss}
\end{figure}

The section has shown that a longer reselection window size is generally preferred. However, it has been identified that this component requires more investigation as to why this is the case. The next sections are closely related to reselection window sizes as they also influence the intervals between learning/selection. The next sections provides the results for the experimental group that focuses on the effects of different replay windows sizes and reanalysis window sizes.

\section{Replay}
\label{sec:results:replay}

In the previous section it was mentioned how the reselection windows size parameter is closely related to the replay window size and these parameters do have an impact on each other. This section provides the empirical results for the experimental group that focuses on the effects of different replay window sizes on the \Ac{BHH}. As a reminder to the reader, the replay window is the size of the \Ac{BHH}'s memory buffer i.e. how much information is kept in the performance log. If this number is low the \Ac{BHH} quickly forgets and if the number is too high it remembers information that is no longer applicable. Similar to some of the other parameters discussed in this chapter, it is then clear that this parameter is also subject to a balance between exploration and exploitation. The same recommendations that was made for reselection window sizes also account for replay window size.

Table \ref{tab:results:replay:metrics} present the empirical results for this experimental group. It can be seen that the best value for the replay window size overall is 5, which is slightly smaller than the \Ac{BHH} baseline, but this value is clearly problem-dependent. This is further supported by the results presented in the ANOVA statistical test in Table \ref{tab:results:replay:anova} as well as the post hoc Tykey test presented in Table \ref{tab:results:replay:post_hoc}.

\begin{table}[htbp]
    \centering
    \caption{Empirical results showcasing rank statistics for different replay window sizes used by the \acs{BHH} across multiple datasets}
    \label{tab:results:replay:metrics}%
    \par\bigskip
    \resizebox{\textwidth}{!}{
    \begin{tabular}{rccccccccccccccc}
    \textbf{step} & \multicolumn{1}{l}{\textbf{(All)}} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{1-2}          &       &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
          & \multicolumn{1}{l}{\textbf{replay}} & \multicolumn{1}{l}{\textbf{metrics}} &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{2-3}          & \multicolumn{1}{l}{\textbf{1}} &       &       & \multicolumn{1}{l}{\textbf{5}} &       &       & \multicolumn{1}{l}{\textbf{10}} &       &       & \multicolumn{1}{l}{\textbf{15}} &       &       & \multicolumn{1}{l}{\textbf{20}} &       &  \\
\cmidrule{2-16}    \textbf{dataset} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} \\
    \midrule
    abalone & 930   & 3.0258 & 1.3816 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6785} & 1.4551 & 930   & 3.1968 & 1.3460 & 930   & 3.0903 & 1.3851 & 930   & 3.0086 & 1.4503 \\
    adult & 930   & 2.8785 & 1.3824 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8269} & 1.3595 & 930   & 2.9430 & 1.4804 & 930   & 3.0538 & 1.3714 & 930   & 2.9645 & 1.5686 \\
    air\_quality & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3851 & 930   & 3.0151 & 1.4970 & 930   & 2.9978 & 1.4294 & 930   & 2.9505 & 1.2966 & 930   & 3.1624 & 1.4430 \\
    bank  & 930   & 2.9484 & 1.4597 & 930   & 3.0570 & 1.4731 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8602} & 1.3439 & 930   & 3.0172 & 1.4202 & 930   & 3.1172 & 1.3592 \\
    bike  & 930   & 2.9602 & 1.2739 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7366} & 1.3401 & 930   & 3.1452 & 1.4478 & 930   & 2.9226 & 1.4174 & 930   & 3.2355 & 1.5274 \\
    car   & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7054} & 1.3572 & 930   & 2.8376 & 1.3898 & 930   & 3.0763 & 1.3723 & 930   & 3.3269 & 1.4631 & 930   & 3.0538 & 1.4086 \\
    diabetic & 930   & 3.2473 & 1.3690 & 930   & 3.3247 & 1.4058 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5935} & 1.3719 & 930   & 2.8075 & 1.3844 & 930   & 3.0269 & 1.4113 \\
    fish\_toxicity & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7269} & 1.4190 & 930   & 3.0785 & 1.4896 & 930   & 3.1774 & 1.3980 & 930   & 2.9892 & 1.3865 & 930   & 3.0280 & 1.3373 \\
    forest\_fires & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8054} & 1.4926 & 930   & 2.9151 & 1.3812 & 930   & 2.9914 & 1.4081 & 930   & 3.0591 & 1.4111 & 930   & 3.2290 & 1.3416 \\
    housing & 930   & 3.1548 & 1.3007 & 930   & 2.9774 & 1.4068 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8548} & 1.4501 & 930   & 3.0355 & 1.4898 & 930   & 2.9774 & 1.4037 \\
    iris  & 930   & 3.0720 & 1.3757 & 930   & 3.1581 & 1.4187 & 930   & 3.2204 & 1.3919 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6183} & 1.3964 & 930   & 2.9312 & 1.4102 \\
    mushroom & 930   & 3.0538 & 1.3243 & 930   & 3.1430 & 1.4369 & 930   & 3.0419 & 1.4140 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613} & 1.3823 & 930   & 2.8957 & 1.4966 \\
    parkinsons & 930   & 3.1720 & 1.3719 & 930   & 2.8430 & 1.2437 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6731} & 1.4535 & 930   & 3.1172 & 1.4189 & 930   & 3.1946 & 1.4977 \\
    student\_performance & 930   & 3.0398 & 1.3684 & 930   & 2.9226 & 1.4106 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6548} & 1.4028 & 930   & 3.0935 & 1.3225 & 930   & 3.2892 & 1.4874 \\
    wine\_quality & 930   & 3.1742 & 1.4300 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7323} & 1.4556 & 930   & 3.1581 & 1.4179 & 930   & 3.0419 & 1.3565 & 930   & 2.8935 & 1.3624 \\
    \midrule
    \textbf{overall} & \textbf{13950} & \textbf{2.9892} & \textbf{1.3892} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9497}} & \textbf{1.4224} & \textbf{13950} & \textbf{2.9723} & \textbf{1.4224} & \textbf{13950} & \textbf{2.9990} & \textbf{1.4021} & \textbf{13950} & \textbf{3.0672} & \textbf{1.4400} \\
    \end{tabular}%
    }
\end{table}%

\begin{table}[htbp]
	\centering
	\caption{ANOVA - Rank - BHH Variant: Replay}
	\label{tab:results:replay:anova}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrr}
			\toprule
			Cases & Sum of Squares & df & Mean Square & F & p  \\
			\cmidrule[0.4pt]{1-6}
			dataset & $19.257$ & $14$ & $1.375$ & $0.695$ & $0.781$  \\
			replay & $109.057$ & $4$ & $27.264$ & $13.784$ & $<$ .001  \\
			dataset * replay & $1876.507$ & $56$ & $33.509$ & $16.941$ & $<$ .001  \\
			Residuals & $137815.766$ & $69675$ & $1.978$ & &  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
		\end{tabular}
	}
\end{table}

\begin{table}[htbp]
	\centering
	\caption{Post Hoc Comparisons - BHH Variant: Replay}
    \label{tab:results:replay:post_hoc}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrrrr}
			\toprule
			\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
			\cline{4-5}
			$ $ & $ $ & Mean Difference & Lower & Upper & SE & t & p$_{tukey}$  \\
			\cmidrule[0.4pt]{1-8}
			$1$ & $5$ & $0.039$ & $-0.006$ & $0.085$ & $0.017$ & $2.346$ & $0.131$  \\
			$ $ & $10$ & $0.017$ & $-0.029$ & $0.063$ & $0.017$ & $1.005$ & $0.853$  \\
			 & $15$ & $-0.010$ & $-0.056$ & $0.036$ & $0.017$ & $-0.579$ & $0.978$  \\
			 & $20$ & $-0.078$ & $-0.124$ & $-0.032$ & $0.017$ & $-4.627$ & $<$ .001  \\
			$5$ & $10$ & $-0.023$ & $-0.069$ & $0.023$ & $0.017$ & $-1.341$ & $0.666$  \\
			$ $ & $15$ & $-0.049$ & $-0.095$ & $-0.003$ & $0.017$ & $-2.924$ & $0.028$  \\
			 & $20$ & $-0.117$ & $-0.163$ & $-0.071$ & $0.017$ & $-6.973$ & $<$ .001  \\
			$10$ & $15$ & $-0.027$ & $-0.073$ & $0.019$ & $0.017$ & $-1.584$ & $0.508$  \\
			$ $ & $20$ & $-0.095$ & $-0.141$ & $-0.049$ & $0.017$ & $-5.632$ & $<$ .001  \\
			$15$ & $20$ & $-0.068$ & $-0.114$ & $-0.022$ & $0.017$ & $-4.048$ & $<$ .001  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
			% \multicolumn{8}{p{0.5\linewidth}}{$ $ * p $<$ .05, ** p < .01, *** p < .001} \\
			% \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
			% \multicolumn{8}{p{0.5\linewidth}}{* $$} \\
			% \multicolumn{8}{p{0.5\linewidth}}{** $$} \\
		\end{tabular}
	}
\end{table}

The descriptive plots presented in Figure \ref{fig:results:replay:descriptive:cd} show the effect of different replay window sizes per dataset. The reader is reminded that the baseline \Ac{BHH} has a replay window size of 10. This value seems to be the best replay window size for the parkinsons and student performance datasets. There is no clear patterns between datasets. This makes sense, since each dataset has different training requirements, error landscapes and search spaces. In some situations a short memory is required to explore more and in other situations a longer memory is needed. An interesting opportunity for further research is to investigate how this value changes at different steps in the training process.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_replay/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying replay window sizes per dataset, across all runs and steps.}
	\label{fig:results:replay:descriptive:descriptive}
\end{figure}

The critical difference plots show insignificant differences between overall average rank across all datasets. This is visual confirmation how the best value for the replay window size is problem dependent.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_replay/figures/cd/overall.png}
	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying replay window sizes across all datasets, runs and steps.}
	\label{fig:results:replay:descriptive:cd}
\end{figure}

As with the other experimental groups, Figure \ref{fig:results:replay:figures:loss} provide example test loss plots for the car and student performance datasets. These two datasets have been carefully selected to showcase a successful case where no overfitting took place(car dataset), while also showing the results of a case where overfitting is clear (student performance dataset). This highlight the extent of overfitting that can occur, supporting the idea to use early stop as suggested before. Furthermore, the overfit plot is show to illustrate the effects of invalid selections and the effect is has along with noise. Consider the large variance that occurs between runs at the point of overfitting in Figure \ref{fig:results:replay:figures:loss} as for the student performance dataset.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_replay/figures/test/loss/car.png}
        \caption{car}
        \label{fig:results:replay:figures:loss1}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_replay/figures/test/loss/student_performance.png}
        \caption{student\_performance}
        \label{fig:results:replay:figures:loss2}
	\end{subfigure}
	\caption{\Acs{BHH} Replay - example test loss plots for \Acsp{BHH} with varying replay window sizes} 
	\label{fig:results:replay:figures:loss}
\end{figure}

In this section it was shown that replay window size configurations are problem-dependent.The replay window size was shown to be related to the reselection window size. The next section provides the empirical results for the the next related hyper-parameter, the reanalysis window size.

\section{Reanalysis}
\label{sec:results:reanalysis}

This section provides the empirical results for the experimental group that focuses on the reanalysis window size and the effect it has on the outcomes of the \Ac{BHH}. As a reminder to the reader, the reanalsysis window size is another hyper-parameter which aims to provide a balance between exploration and exploitation by delaying or accelerating the update of beliefs/priors in the \Ac{BHH}. This parameter is related to the reselection window size as well as the replay window size. The configuration of these three parameters determine how often reselection occurs and if reselection occurs, what data should be considered. The reanalysis window size delays or acceleration the addition or removal or information from the performance log, while the replay window size controls how much data is kept in the performance log. The baseline \Ac{BHH} uses a reanalysis value that is equal to the reselection value, which is 10.

Table \ref{tab:results:reanalysis:metrics} as before provides the empirical results for this experimental group. The results show that in general, the baseline reanalysis window size of 10 yielded the best outcomes overall. However, similar to the outcomes of the replay window size, one can clearly see that the best value for the reanalysis window size is also largely problem dependent.

\begin{table}[htbp]
    \centering
    \caption{Empirical results showcasing rank statistics for different reanalysis values used by the \acs{BHH} across multiple datasets}
    \label{tab:results:reanalysis:metrics}%
    \par\bigskip
    \resizebox{\textwidth}{!}{\begin{tabular}{rccccccccccccccc}
    \textbf{step} & \multicolumn{1}{l}{\textbf{(All)}} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{1-2}          &       &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
          & \multicolumn{1}{l}{\textbf{reanalysis}} & \multicolumn{1}{l}{\textbf{metrics}} &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{2-3}          & \multicolumn{1}{l}{\textbf{1}} &       &       & \multicolumn{1}{l}{\textbf{5}} &       &       & \multicolumn{1}{l}{\textbf{10}} &       &       & \multicolumn{1}{l}{\textbf{15}} &       &       & \multicolumn{1}{l}{\textbf{20}} &       &  \\
\cmidrule{2-16}    \textbf{dataset} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} \\
    \midrule
    abalone & 930   & 2.9849 & 1.3965 & 930   & 3.0699 & 1.4423 & 930   & 3.1710 & 1.3205 & 930   & 2.9441 & 1.4447 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301} & 1.4433 \\
    adult & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523 & 930   & 2.7914 & 1.7091 & 930   & 3.0151 & 1.7236 \\
    air\_quality & 930   & 2.9613 & 1.3442 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8387} & 1.4383 & 930   & 3.2559 & 1.4024 & 930   & 3.0538 & 1.4200 & 930   & 2.8903 & 1.4297 \\
    bank  & 930   & 3.1161 & 1.4322 & 930   & 3.0452 & 1.3827 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7355} & 1.3985 & 930   & 2.9280 & 1.4028 & 930   & 3.1753 & 1.4151 \\
    bike  & 930   & 3.1409 & 1.2581 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.3914 & 930   & 3.1946 & 1.3653 & 930   & 3.0978 & 1.4978 & 930   & 2.8086 & 1.4905 \\
    car   & 930   & 3.1237 & 1.4229 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7237} & 1.3575 & 930   & 2.8763 & 1.2987 & 930   & 3.1538 & 1.3846 & 930   & 3.1226 & 1.5473 \\
    diabetic & 930   & 3.2452 & 1.3050 & 930   & 3.0720 & 1.3913 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7785} & 1.4067 & 930   & 3.0290 & 1.4249 & 930   & 2.8753 & 1.4940 \\
    fish\_toxicity & 930   & 3.1452 & 1.3620 & 930   & 3.0032 & 1.4455 & 930   & 3.2172 & 1.3639 & 930   & 3.1000 & 1.4088 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5344} & 1.3879 \\
    forest\_fires & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8398} & 1.3690 & 930   & 3.1215 & 1.4707 & 930   & 3.0043 & 1.3181 & 930   & 2.8860 & 1.3535 & 930   & 3.1484 & 1.5261 \\
    housing & 930   & 3.3129 & 1.3107 & 930   & 2.9892 & 1.3927 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6871} & 1.4833 & 930   & 2.6968 & 1.4965 & 930   & 3.3140 & 1.2356 \\
    iris  & 930   & 3.1204 & 1.3010 & 930   & 3.0968 & 1.3909 & 930   & 3.1269 & 1.4320 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366} & 1.4492 & 930   & 3.0194 & 1.4352 \\
    mushroom & 930   & 2.9312 & 1.3794 & 930   & 3.1538 & 1.4031 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8473} & 1.3836 & 930   & 3.1215 & 1.4530 & 930   & 2.9032 & 1.4714 \\
    parkinsons & 930   & 2.9688 & 1.3850 & 930   & 3.0086 & 1.3559 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6129} & 1.4814 & 930   & 3.1032 & 1.3804 & 930   & 3.3065 & 1.3778 \\
    student\_performance & 930   & 2.9409 & 1.4118 & 930   & 3.1849 & 1.3804 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710} & 1.4097 & 930   & 3.1258 & 1.3655 & 930   & 2.9774 & 1.4675 \\
    wine\_quality & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8032} & 1.4440 & 930   & 2.9204 & 1.3042 & 930   & 3.2022 & 1.4104 & 930   & 2.9247 & 1.3491 & 930   & 3.1495 & 1.5171 \\
    \midrule
    \textbf{overall} & \textbf{13950} & \textbf{2.9747} & \textbf{1.3710} & \textbf{13950} & \textbf{2.9315} & \textbf{1.3960} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.8978}} & \textbf{1.3999} & \textbf{13950} & \textbf{2.9728} & \textbf{1.4464} & \textbf{13950} & \textbf{3.0047} & \textbf{1.4805} \\
    \end{tabular}%
    }

\end{table}%

Tables \ref{tab:results:reanalysis:anova} and \ref{tab:results:reanalysis:post_hoc} provide the ANOVA and post hoc Tukey statistical test results respectively. From these results one can see the statistical certainty of the results, with the post hoc Tukey test indicating statistical significant differences between individual reanalysis window size configurations.

\begin{table}[htbp]
	\centering
	\caption{ANOVA - Rank - BHH Variant: Reanalysis}
	\label{tab:results:reanalysis:anova}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrr}
			\toprule
			Cases & Sum of Squares & df & Mean Square & F & p  \\
			\cmidrule[0.4pt]{1-6}
			dataset & $1814.177$ & $14$ & $129.584$ & $66.508$ & $<$ .001  \\
			reanalysis & $97.535$ & $4$ & $24.384$ & $12.515$ & $<$ .001  \\
			dataset * reanalysis & $2924.722$ & $56$ & $52.227$ & $26.805$ & $<$ .001  \\
			Residuals & $135755.285$ & $69675$ & $1.948$ &  &  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
		\end{tabular}
	}
\end{table}

\begin{table}[htbp]
	\centering
	\caption{Post Hoc Comparisons - BHH Variant: Reanalysis}
	\label{tab:results:reanalysis:post_hoc}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrrrr}
			\toprule
			\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
			\cline{4-5}
			$ $ & $ $ & Mean Difference & Lower & Upper & SE & t & p$_{tukey}$  \\
			\cmidrule[0.4pt]{1-8}
			$1$ & $5$ & $0.043$ & $-0.002$ & $0.089$ & $0.017$ & $2.586$ & $0.073$  \\
			$ $ & $10$ & $0.077$ & $0.031$ & $0.123$ & $0.017$ & $4.602$ & $<$ .001  \\
			 & $15$ & $0.002$ & $-0.044$ & $0.047$ & $0.017$ & $0.112$ & $1.000$  \\
			 & $20$ & $-0.030$ & $-0.076$ & $0.016$ & $0.017$ & $-1.793$ & $0.378$  \\
			$5$ & $10$ & $0.034$ & $-0.012$ & $0.079$ & $0.017$ & $2.016$ & $0.258$  \\
			$ $ & $15$ & $-0.041$ & $-0.087$ & $0.004$ & $0.017$ & $-2.475$ & $0.096$  \\
			 & $20$ & $-0.073$ & $-0.119$ & $-0.028$ & $0.017$ & $-4.379$ & $<$ .001  \\
			$10$ & $15$ & $-0.075$ & $-0.121$ & $-0.029$ & $0.017$ & $-4.491$ & $<$ .001  \\
			$ $ & $20$ & $-0.107$ & $-0.152$ & $-0.061$ & $0.017$ & $-6.395$ & $<$ .001  \\
			$15$ & $20$ & $-0.032$ & $-0.077$ & $0.014$ & $0.017$ & $-1.904$ & $0.315$  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
			% \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
			% \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
		\end{tabular}
	}
\end{table}

It can be seen from Figure \ref{fig:results:reanalysis:descriptive:descriptive} for all datasets that a pivot point exists in the results at reanalysis window size 10. More specifically, it should be stated that a pivot point exists at the configuration points where the reanalsysis window is equal to the reselection window. Since the baseline \Ac{BHH} has reselection and reanalys window sizes of 10, this pivot point can be seen at reanalysis window size 10 for all datasets. At this point, the performance either reach a minimum or a maximum for almost all the different configurations. From this, it can be concluded that the reanalysis window size is also problem dependent and that the relationship between the reselection, replay and reanalysis window sizes is clear.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_reanalysis/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying reanalysis window sizes per dataset, across all runs and steps.}
	\label{fig:results:reanalysis:descriptive:descriptive}
\end{figure}

The critical difference plots beyween the outcomes of different reanalysis window states on the \Ac{BHH} is given in Figure \ref{fig:results:reanalysis:descriptive:cd} from which we can see there is no statistically significant diference between the outcomes overall across all datasets. This further supports the statement that the reanalysis window size is also problem dependent.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_reanalysis/figures/cd/overall.png}
	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying reanalysis window sizes across all datasets, runs and steps.}
	\label{fig:results:reanalysis:descriptive:cd}
\end{figure}

Finally, Figure \ref{fig:results:reanalysis:figures:loss} provides some example test loss plots for the forest fires and parkinsons datasets. These figures showcase how the majority of progress in training and learning is made within the first five epochs.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_reanalysis/figures/test/loss/forest_fires.png}
        \caption{forest\_fires}
        \label{fig:results:reanalysis:figures:loss1}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_reanalysis/figures/test/loss/parkinsons.png}
        \caption{parkinsons}
        \label{fig:results:reanalysis:figures:loss2}
	\end{subfigure}
	\caption{\Acs{BHH} Reanalysis - example test loss plots for \Acsp{BHH} with varying reanalysis window sizes} 
	\label{fig:results:reanalysis:figures:loss}
\end{figure}

This section has shown that the reanalysis window size is largely problem dependent. A relationship between the reselection, replay and reanalysis window sizes has been identified and it has been concluded that in general a good configuration of reanalysis window size is one where the reanalysis size is equal to the reselection window size, similar to the baseline \Ac{BHH}. Given the relationship between the reselection, replay and reanalysis window sizes, a suggestion can be made to eliminate a hyper-parameter by removing the notion of reanalysis and simply making use of the  reselection window size, since these two parameters work best when they are equal. The next section provides the reader with the empirical results for burn in window size.

\section{Burn In}
\label{sec:results:burn_in}

So far a handful of hyper-parameters have been investigated. It should be noted that a large overarching goal of all these parameters is to get a better understanding of their effects on exploration and exploitation and how that impacts the \Ac{BHH}. So far the results have all shown to yield statistically significant results, with a lot of parameters being shown to be problem-dependent. This section aims to further to the investigation by considering the experimental group that focuses on different burn in window sizes and the effects it has on the \Ac{BHH}. As a reminder to the reader, the burn in window size is a hyper-parameter that defines a delay in the \Ac{BHH} before any learning starts happening. This means that selection, replay and reanalysis window sizes still affect when and how often learning occurs, but burn in controls when learning starts.

As with the other experimental groups, Table \ref{tab:results:burn_in:metrics} provide the empirical results. The empirical results indicate a relationship between the burn in window size and the average rank outcome. It can be seen that a lower burn in rate leads to better results. Infact, the results show on most occasions that no burn in is the best configuration. This outcome makes sense since it has already been established that most of the progress and learning is happening in the initial steps of training. If a burn in value is big, it causes the \Ac{BHH} to miss this opportunity to learn. Take note, even without learning anything before the burn in, the underlying heuristics are still all good and would still lead to decent results. Afterall, this is proof that the proxied state update operations work well

\begin{table}[htbp]
  \centering
  \caption{Empirical results showcasing rank statistics for different \index{burn in}burn in values used by the \acs{BHH} across multiple datasets}
    \label{tab:results:burn_in:metrics}%
    \par\bigskip
  \resizebox{\textwidth}{!}{
    \begin{tabular}{rccccccccccccccc}
    \textbf{step} & \multicolumn{1}{l}{(All)} &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{1-2}          &       &       &       &       &       &       &       &       &       &       &       &       &       &       &  \\
          & \multicolumn{1}{l}{\textbf{burn\_in}} & \multicolumn{1}{l}{\textbf{results}} &       &       &       &       &       &       &       &       &       &       &       &       &  \\
\cmidrule{2-3}          & \textbf{0} &       &       & \textbf{5} &       &       & \textbf{10} &       &       & \textbf{15} &       &       & \textbf{20} &       &  \\
\cmidrule{2-16}    \textbf{dataset} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} \\
    \midrule
    abalone & 930   & 2.9151 & 1.3952 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6935} & 1.3934 & 930   & 2.9172 & 1.3837 & 930   & 2.8398 & 1.3524 & 930   & 3.6344 & 1.3574 \\
    adult & 930   & 2.7366 & 1.4475 & 930   & 2.6430 & 1.3817 & 930   & 2.9892 & 1.4111 & 930   & 3.1731 & 1.4477 & 930   & 3.1355 & 1.4130 \\
    air\_quality & 930   & 2.9097 & 1.4408 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6817} & 1.4270 & 930   & 2.7699 & 1.3443 & 930   & 3.3720 & 1.3137 & 930   & 3.2667 & 1.4119 \\
    bike  & 930   & 1.9237 & 0.9808 & 930   & 2.1806 & 1.0238 & 930   & 2.9237 & 1.2739 & 930   & 3.5054 & 1.1859 & 930   & 4.4667 & 0.8514 \\
    car   & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3624} & 1.2315 & 930   & 2.5882 & 1.4246 & 930   & 3.2978 & 1.3922 & 930   & 3.3796 & 1.2711 & 930   & 3.3720 & 1.4009 \\
    fish\_toxicity & 930   & 3.0634 & 1.4589 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7935} & 1.4021 & 930   & 2.8204 & 1.5131 & 930   & 3.1022 & 1.3461 & 930   & 3.2204 & 1.2949 \\
    forest\_fires & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8161} & 1.3301 & 930   & 2.8495 & 1.3830 & 930   & 2.8645 & 1.4092 & 930   & 3.3774 & 1.3976 & 930   & 3.0925 & 1.4709 \\
    housing & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6903} & 1.3837 & 930   & 2.9516 & 1.3176 & 930   & 2.9968 & 1.4425 & 930   & 3.0581 & 1.3435 & 930   & 3.3032 & 1.5101 \\
    iris  & 930   & 2.9473 & 1.4608 & 930   & 2.9720 & 1.3675 & 930   & 3.1903 & 1.4493 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710} & 1.3694 & 930   & 3.1194 & 1.3872 \\
    mushroom & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2065} & 1.2486 & 930   & 2.9376 & 1.2977 & 930   & 3.1613 & 1.2966 & 930   & 3.1441 & 1.4015 & 930   & 3.5226 & 1.5006 \\
    parkinsons & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2796} & 1.2822 & 930   & 2.8892 & 1.2474 & 930   & 2.7065 & 1.3143 & 930   & 3.3968 & 1.4175 & 930   & 3.7280 & 1.3295 \\
    student\_performance & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1452} & 1.2052 & 930   & 2.6946 & 1.4032 & 930   & 3.0968 & 1.3525 & 930   & 3.4581 & 1.3539 & 930   & 3.6054 & 1.2312 \\
    wine\_quality & 930   & 2.9699 & 1.4373 & 930   & 3.0108 & 1.3041 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6634} & 1.4186 & 930   & 3.1247 & 1.3980 & 930   & 3.2312 & 1.4471 \\
    bank  & 930   & 2.7301 & 1.3210 & 930   & 2.8194 & 1.3350 & 930   & 2.8570 & 1.4848 & 930   & 2.9312 & 1.3841 & 930   & 3.6624 & 1.3391 \\
    \midrule
    \textbf{overall} & \textbf{13020} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.6211}} & \textbf{1.3814} & \textbf{13020} & \textbf{2.7647} & \textbf{1.3553} & \textbf{13020} & \textbf{2.9468} & \textbf{1.4045} & \textbf{13020} & \textbf{3.1881} & \textbf{1.3754} & \textbf{13020} & \textbf{3.4543} & \textbf{1.4061} \\
    \end{tabular}%
    }
\end{table}%

As before, Tables \ref{tab:results:burn_in:anova} and \ref{tab:results:burn_in:post_hoc} provide the ANOVA and post hoc Tukey test results respectively. These tables show the statistical significance of the results.

\begin{table}[htbp]
	\centering
	\caption{ANOVA - Rank - BHH Variant: Burn In}
	\label{tab:results:burn_in:anova}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrr}
			\toprule
			Cases & Sum of Squares & df & Mean Square & F & p  \\
			\cmidrule[0.4pt]{1-6}
			dataset & $17.977$ & $14$ & $1.284$ & $0.696$ & $0.781$  \\
			burn\_in & $6332.995$ & $4$ & $1583.249$ & $858.000$ & $<$ .001  \\
			dataset * burn\_in & $4955.754$ & $56$ & $88.496$ & $47.958$ & $<$ .001  \\
			Residuals & $128569.751$ & $69675$ & $1.845$ & &  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
		\end{tabular}
	}
\end{table}

\begin{table}[htbp]
	\centering
	\caption{Post Hoc Comparisons - BHH Variant: Burn In}
	\label{tab:results:burn_in:post_hoc}%
	\par\bigskip
	\resizebox{\textwidth}{!}
	{
		\begin{tabular}{lrrrrrrr}
			\toprule
			\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
			\cline{4-5}
			$ $ & $ $ & Mean Difference & Lower & Upper & SE & t & p$_{tukey}$  \\
			\cmidrule[0.4pt]{1-8}
			$0$ & $5$ & $-0.154$ & $-0.198$ & $-0.109$ & $0.016$ & $-9.449$ & $<$ .001  \\
			$ $ & $10$ & $-0.360$ & $-0.404$ & $-0.315$ & $0.016$ & $-22.107$ & $<$ .001  \\
			 & $15$ & $-0.584$ & $-0.629$ & $-0.540$ & $0.016$ & $-35.923$ & $<$ .001  \\
			 & $20$ & $-0.845$ & $-0.890$ & $-0.801$ & $0.016$ & $-51.975$ & $<$ .001  \\
			$5$ & $10$ & $-0.206$ & $-0.250$ & $-0.162$ & $0.016$ & $-12.658$ & $<$ .001  \\
			$ $ & $15$ & $-0.431$ & $-0.475$ & $-0.386$ & $0.016$ & $-26.474$ & $<$ .001  \\
			 & $20$ & $-0.692$ & $-0.736$ & $-0.647$ & $0.016$ & $-42.525$ & $<$ .001  \\
			$10$ & $15$ & $-0.225$ & $-0.269$ & $-0.180$ & $0.016$ & $-13.817$ & $<$ .001  \\
			$ $ & $20$ & $-0.486$ & $-0.530$ & $-0.441$ & $0.016$ & $-29.868$ & $<$ .001  \\
			$15$ & $20$ & $-0.261$ & $-0.305$ & $-0.217$ & $0.016$ & $-16.051$ & $<$ .001  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
			% \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
			% \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
		\end{tabular}
	}
\end{table}

The best illustration of the relationship between the burn in value and the average rank is best shown in Figure \ref{fig:results:burn_in:descriptive:descriptive} which provides a descriptive plot showing the difference in outcome by burn in window size and dataset. From these plots one can see that there is some problem dependence, but in general, there is a pattern that snows that lower burn in window sizes are best. There are cases where absolutely no burn in is also not the best, but rather a small, non-zero burn in window size is preferable. See the descriptive plots for fish toxicity, abalone, adult and air quality datasets in Figure \ref{fig:results:burn_in:descriptive:descriptive}.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_burn_in/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying burn in values per dataset, across all runs and steps.}
	\label{fig:results:burn_in:descriptive:descriptive}
\end{figure}

The critical difference plot as presented in Figure \ref{fig:results:burn_in:descriptive:cd} shows the statistical significance between burn in window sizes overall, across all datasets. One can clearly see from this plot that little to no burn in is preferred in most of the cases.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_burn_in/figures/cd/overall.png}
	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying burn in values across all datasets, runs and steps.}
	\label{fig:results:burn_in:descriptive:cd}
\end{figure}

Figure \ref{fig:results:burn_in:figures:loss} provides the test loss plots for different burn in window sizes for the bike and student performance datasets. Once again, an example is given of no overfitting (bike dataset) and another of drastic overfitting (student performance dataset). It should be clear from Figure \ref{fig:results:burn_in:figures:loss2} how a larger burn in window size has a greater effect on the overfitting. This makes sense, since the \Ac{BHH} only starts to try to learn when most of the progress in \ac{FFNN} training has already been achieved at that point. At this point, almost no heuristic, no matter how good, is yielding any positive outcomes, resulting in the \Ac{BHH} learning to make bad selections. After this point it has been shown to be difficult for the \Ac{BHH} to recover.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_burn_in/figures/test/loss/bike.png}
        \caption{bike}
        \label{fig:results:burn_in:figures:loss1}
	\end{subfigure}
		\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_burn_in/figures/test/loss/student_performance.png}
        \caption{student\_performance}
        \label{fig:results:burn_in:figures:loss2}
	\end{subfigure}
	\caption{\Acs{BHH} Burn In - example test loss plots for varying burn in values}
	\label{fig:results:burn_in:figures:loss}
\end{figure}

This section provided the empirical results for the experimental group that focuses on burn in window sizes. It has been show that, in general, a lower burn in window size is preferred. The next sections provide investigation into the normalisation and discounted rewards hyper-parameter flags.

\section{Normalise}
\label{sec:results:normalise}

This section presents the empirical results for the experimental group that focuses on normalisation of pseudo counts and the effects it has on the outcomes of the \Ac{BHH}. As a reminder to the reader this normalisation effect aims to promote exploration since it rescales the metric by which priors are updated. It could happen that the \Ac{BHH} gets stuck in some local optima and simply picks the same \index{heuristic}heursistic over and over again, resulting in other heuristics not being selected at all. This is referred to as \textit{mode-collapse} and is discussed in Chapter \ref{chap:methodology}. Normalisation is an attempt to then reset beliefs proportionally back to the initial symmetric starting concentration of 1.

Table \ref{tab:results:normalise:metrics} present the empirical results for this experimental group. From the table one can see that in general, no normalisation yields the best results, however, it should be pointed out that this parameter is problem-dependent, yielding better results for the bank, fish toxicity, forest fires, iris and wine quality datasets when normalisation is enabled.

\begin{table}[htbp]
  \centering
      \caption{Empirical results showcasing rank statistics for \index{normalisation}normalisation toggled by the \acs{BHH} across multiple datasets}
    \label{tab:results:normalise:metrics}%
     \par\bigskip
  \resizebox{\textwidth}{!}{
    \begin{tabular}{rcccccc}
    \textbf{step} & \multicolumn{1}{l}{\textbf{(All)}} &       &       &       &       &  \\
\cmidrule{1-2}          &       &       &       &       &       &  \\
          & \multicolumn{1}{l}{\textbf{normalisation}} & \multicolumn{1}{l}{\textbf{metric}} &       &       &       &  \\
\cmidrule{2-3}          & \multicolumn{1}{l}{\textbf{FALSE}} &       &       & \multicolumn{1}{l}{\textbf{TRUE}} &       &  \\
\cmidrule{2-7}    \textbf{dataset} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} \\
    \midrule
    abalone & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935} & 0.5002 & 930   & 1.5065 & 0.5002 \\
    adult & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4710} & 0.4994 & 930   & 1.4968 & 0.5003 \\
    air\_quality & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4892} & 0.5002 & 930   & 1.5108 & 0.5002 \\
    bank  & 930   & 1.5484 & 0.4979 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4516} & 0.4979 \\
    bike  & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4978} & 0.5003 & 930   & 1.5022 & 0.5003 \\
    car   & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4258} & 0.4947 & 930   & 1.5742 & 0.4947 \\
    diabetic & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4753} & 0.4997 & 930   & 1.5247 & 0.4997 \\
    fish\_toxicity & 930   & 1.5505 & 0.4977 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4495} & 0.4977 \\
    forest\_fires & 930   & 1.5054 & 0.5002 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4946} & 0.5002 \\
    housing & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4720} & 0.4995 & 930   & 1.5280 & 0.4995 \\
    iris  & 930   & 1.5645 & 0.4961 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4355} & 0.4961 \\
    mushroom & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4323} & 0.4957 & 930   & 1.5667 & 0.4958 \\
    parkinsons & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4000} & 0.4902 & 930   & 1.6000 & 0.4902 \\
    student\_performance & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3892} & 0.4878 & 930   & 1.6108 & 0.4878 \\
    wine\_quality & 930   & 1.5473 & 0.4980 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4527} & 0.4980 \\
    \midrule
    \textbf{overall} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4842}} & \textbf{0.4998} & \textbf{13950} & \textbf{1.5136} & \textbf{0.4998} \\
    \end{tabular}%
    }
\end{table}%

Similar to the other experimental groups, Tables \ref{tab:results:normalise:anova} and \ref{tab:results:normalise:post_hoc} provide the ANOVA and post hoc Tukey statistical test results. These tables show that the results are indeed statistical significance.

\begin{table}[htbp]
	\centering
	\caption{ANOVA - Rank - BHH Variant: Normalise}
	\label{tab:results:normalise:anova}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrr}
			\toprule
			Cases & Sum of Squares & df & Mean Square & F & p  \\
			\cmidrule[0.4pt]{1-6}
			dataset & $0.450$ & $14$ & $0.032$ & $0.130$ & $1.000$  \\
			normalisation & $6.055$ & $1$ & $6.055$ & $24.490$ & $<$ .001  \\
			dataset * normalisation & $78.266$ & $14$ & $5.590$ & $22.613$ & $<$ .001  \\
			Residuals & $6890.195$ & $27870$ & $0.247$ & &  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
		\end{tabular}
	}

\end{table}

\begin{table}[htbp]
	\centering
	\caption{Post Hoc Comparisons - BHH Variant: Normalise}
	\label{tab:results:normalise:post_hoc}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
	    \begin{tabular}{lrrrrrrr}
			\toprule
			\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
			\cline{4-5}
			$ $ & $ $ & Mean Difference & Lower & Upper & SE & t & p$_{tukey}$  \\
			\cmidrule[0.4pt]{1-8}
			False & True & $-0.029$ & $-0.041$ & $-0.018$ & $0.006$ & $-4.949$ & $<$ .001  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
			% \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
			% \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
		\end{tabular}
	}
\end{table}

From the descriptive plots provided in Figure \ref{fig:results:normalise:descriptive:descriptive}, one can see how normalisation is problem dependent and in many cases, normalisation provides not statistically significant difference. This is further evident in Figure \ref{fig:results:normalise:descriptive:cd} which shows no statistically significant difference overall across all datasets.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_normalise/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with normalisation toggled per dataset, across all runs and steps.}
	\label{fig:results:normalise:descriptive:descriptive}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_normalise/figures/cd/overall.png}
	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with normalisation toggled across all datasets, runs and steps.}
	\label{fig:results:normalise:descriptive:cd}
\end{figure}

As with the other experimental groups, Figure \ref{fig:results:normalise:figures:loss} provides example test loss plots with normalisation enabled and disabled for the bank and housing datasets. For these particular plots, there is no real clear distinction between the outcomes of normalisation. Since the effect of this parameter is neglibly small, the authors do not deem this parameter as important as the others although it has been shown to provide some statistically significant differences for some datasets.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_normalise/figures/test/loss/bank.png}
        \caption{bank}
        \label{fig:results:normalise:figures:loss1}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_normalise/figures/test/loss/housing.png}
        \caption{housing}
        \label{fig:results:normalise:figures:loss2}
	\end{subfigure}
	\caption{\Acs{BHH} Normalise - example test loss plots for \Acs{BHH} with normalisation toggled} 
	\label{fig:results:normalise:figures:loss}
\end{figure}

This section provided the empirical results for the experimental group that focuses on the effects of normalisation of pseudo counts on the \Ac{BHH}. Although it has been shown to yield interesting results with normalisation not being required in general, while normalisation is preferred for other datasets, the authors conclude that the importance of this parameter is of such nature that it does not have such a significant impact on the \Ac{BHH} as with the other parameters.

The next section considers the empirical results for an experimental group that focus on an alternative strategy to the normalisation approach by providing a discounted rewards flag on the pseudo counts.

\section{Discounted Rewards}
\label{sec:results:discounted_rewards}

This section presents the empirical results for an experimental group that focuses on the effects of discounted rewards on the \Ac{BHH}. As a reminder to the reader, discounted rewards is an strategy that attempts to exponentially decrease the impact of evidence in the performance log for evidence that is further back in history. This concept is borrowed from \Ac{RL} (ref???). The intent of the discounted rewards approach is to determine if a longer memory can be used where importance is placed on more recent evidence. Similar to other parameters discussed so far, this parameter also attempts to provide a mechanism to balance exploration and exploitation.

Table \ref{tab:results:discounted_rewards:metrics} provides the empirical results for this experimental group. One can see from the results that the outcomes bear resemblance to the outcomes of the normalisation experimental group. It is found that discounted rewards are generally not required while there are some cases that do benefit from it. This means that the effect of discounted rewards is also problem-dependent.

\begin{table}[htbp]
  \centering
      \caption{Empirical results showcasing rank statistics for \index{discounted rewards}discounted rewards toggled by the \acs{BHH} across multiple datasets}
    \label{tab:results:discounted_rewards:metrics}%
    \par\bigskip
  \resizebox{\textwidth}{!}{
    \begin{tabular}{rcccccc}
    step  & \multicolumn{1}{l}{(All)} &       &       &       &       &  \\
\cmidrule{1-2}          &       &       &       &       &       &  \\
          & \multicolumn{1}{l}{\textbf{dr}} & \multicolumn{1}{l}{\textbf{metrics}} &       &       &       &  \\
\cmidrule{2-3}          & \multicolumn{1}{l}{\textbf{FALSE}} &       &       & \multicolumn{1}{l}{\textbf{TRUE}} &       &  \\
\cmidrule{2-7}    \textbf{dataset} & \textbf{count} & \textbf{avg} & \textbf{std} & \textbf{count} & \textbf{avg} & \textbf{std} \\
    \midrule
    abalone & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4914} & 0.5002 & 930   & 1.5086 & 0.5002 \\
    adult & 930   & 1.5011 & 0.5003 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4645} & 0.4990 \\
    air\_quality & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4613} & 0.4988 & 930   & 1.5387 & 0.4988 \\
    bank  & 930   & 1.5161 & 0.5000 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4839} & 0.5000 \\
    bike  & 930   & 1.5011 & 0.5003 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003 \\
    car   & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4280} & 0.4950 & 930   & 1.5720 & 0.4950 \\
    diabetic & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4699} & 0.4994 & 930   & 1.5301 & 0.4994 \\
    fish\_toxicity & 930   & 1.5011 & 0.5003 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003 \\
    forest\_fires & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4742} & 0.4996 & 930   & 1.5258 & 0.4996 \\
    housing & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4237} & 0.4944 & 930   & 1.5763 & 0.4944 \\
    iris  & 930   & 1.5903 & 0.4920 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4097} & 0.4920 \\
    mushroom & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3946} & 0.4890 & 930   & 1.5806 & 0.4937 \\
    parkinsons & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3710} & 0.4833 & 930   & 1.6290 & 0.4833 \\
    student\_performance & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4398} & 0.4966 & 930   & 1.5602 & 0.4966 \\
    wine\_quality & 930   & 1.5570 & 0.4970 & 930   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4430} & 0.4970 \\
    \midrule
    \textbf{overall} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4747}} & \textbf{0.4994} & \textbf{13950} & \textbf{1.5214} & \textbf{0.4996} \\
    \end{tabular}%
    }
\end{table}%

Tables \ref{tab:results:discounted_rewards:anova} and \ref{tab:results:discounted_rewards:post_hoc} provide the ANOVA and post hoc Tukey statistical test results from which it can be seen that the results are statistically significant.

\begin{table}[htbp]
	\centering
	\caption{ANOVA - Rank - BHH Variant: Discounted Rewards}
	\label{tab:results:discounted_rewards:anova}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrr}
			\toprule
			Cases & Sum of Squares & df & Mean Square & F & p  \\
			\cmidrule[0.4pt]{1-6}
			dataset & $0.727$ & $14$ & $0.052$ & $0.210$ & $0.999$  \\
			discounted\_rewards & $15.190$ & $1$ & $15.190$ & $61.607$ & $<$ .001  \\
			dataset * discounted\_rewards & $87.282$ & $14$ & $6.234$ & $25.285$ & $<$ .001  \\
			Residuals & $6871.694$ & $27870$ & $0.247$ & $ $ & $ $  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
		\end{tabular}
	}
\end{table}

\begin{table}[htbp]
	\centering
	\caption{Post Hoc Comparisons - BHH Variant: Discounted Rewards}
	\label{tab:results:discounted_rewards:post_hoc}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{lrrrrrrr}
			\toprule
			\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
			\cline{4-5}
			$ $ & $ $ & Mean Difference & Lower & Upper & SE & t & p$_{tukey}$  \\
			\cmidrule[0.4pt]{1-8}
			False & True & $-0.047$ & $-0.058$ & $-0.035$ & $0.006$ & $-7.849$ & $<$ .001  \\
			\bottomrule
			% \addlinespace[1ex]
			% \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
			% \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
			% \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
		\end{tabular}
	}
\end{table}

The descriptive plots as presented in Figure \ref{fig:results:discounted_rewards:descriptive:descriptive} shows how some datasets benefit from discounted rewards while others do not. This makes sense, since some datasets might have different training requirements that require long memory of state, the error landscapes could vastly differ or simply contain more noise due to mini-batch training.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_discounted_rewards/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with discounted rewards toggled per datasets, across all runs and steps.}
	\label{fig:results:discounted_rewards:descriptive:descriptive}
\end{figure}

The critical difference plot as presented in Figure \ref{fig:results:discounted_rewards:descriptive:cd} shows that there is not statistically significant difference between enabling and disabling discounted rewards overall, across all datasets, once again suggesting problem-dependence.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_discounted_rewards/figures/cd/overall.png}
	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with discounted rewards toggled across all datasets, runs and steps.}
	\label{fig:results:discounted_rewards:descriptive:cd}
\end{figure}

Figure \ref{fig:results:discounted_rewards:figures:loss} provides example plots of test loss when discounted rewards is enabled and disabled for the air quality and fish toxity datasets.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_discounted_rewards/figures/test/loss/air_quality.png}
        \caption{air\_quality}
        \label{fig:results:discounted_rewards:figures:loss1}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_discounted_rewards/figures/test/loss/fish_toxicity.png}
        \caption{fish\_toxicity}
        \label{fig:results:discounted_rewards:figures:loss2}
	\end{subfigure}
	\caption{\Acs{BHH} Discounted Rewards - example test loss plots for discounted rewards toggled on and off}
	\label{fig:results:discounted_rewards:figures:loss}
\end{figure}

This section presented the finding and results for the experimental group that focuses on discounted rewards of evidence in the performance log. It has been shown that the outcome of this parameter on the \Ac{BHH} is problem dependent. However, the authors deem this parameter to be less important than the other hyper-parameters since their influence is much bigger on the outcome of the \Ac{BHH} than that of discounted rewards.

This concludes the formal experimental groups and empirical aspects to be evaluated. The next section aims to provide more insight into overfitting that occurs with the \Ac{BHH}.

\section{Overfitting}
\label{sec:results:overfitting}

Throughout this chapter the topic of overfitting was raised on multiple occasions. The authors deem it necessary to dedicate a section to specifically discuss and summarise the effects of overfitting on the \Ac{BHH}. Take note of the fact that overfitting could be the results of many aspects. Overfitting is often the result of noise caused by mini-batch iterations. Overfitting could be the result of training and test sets that do not have the same approximate distributions. Investigation into the data is required. Consider again the experimental group that focused on \index{heuristic}heuristic pool configurations. Three different configurations were considered of which the gradient-only \index{heuristic}heuristics pool performed best. It should be observed that overfitting occurs much less frequently when the \index{heuristic}heuristics pool contains only the gradient-based low-level \index{heuristic}heuristics. Figure \ref{fig:results:overfitting:figures:gd-overfit} below contains the only case where overfitting occurs when the gradient-only heuristic pool is used.

\begin{figure}[htbp]
	\centering
    \includegraphics[width=\textwidth]{analysis/overfitting/student_performance.png}
    \caption{Example test loss plot where the \Ac{BHH}-gd is shown to overfit }
    \label{fig:results:overfitting:figures:gd-overfit}
\end{figure}

One can then conclude that most of the overfitting occurs as a result of the inclusion of the meta-heuristics. To some extent this does make sense, since the proxied update step operations for these heuristics do not map as well between meta-heuristics as they do with gradient-based heuristics and thus an update step that occurs when switching from a \acs{PSO} to a \acs{GA} for example might maintain a state of momentum in a certain direction and then as a result of cross-over end up in a totally opposite direction, resulting in the entity vastly overshooting any optima. Van Wyk \cite{ref:vanwyk:2014} did a detailed analysis of overfitting that occurs when training \acp{FFNN} using \acp{PSO}. Although the same velocity clamping techniques were used as suggested in Van Wyk's work, they are not guaranteed to avoid overfitting. Another technique would be to nullify and reset velocites and momentum, but this could then be detrimental to the other heuristics. Since the \Ac{BHH} includes a \acs{PSO} in the heuristic pool, one could expect similar results.

Another aspect to remember is that when overfitting starts, the \Ac{BHH} has no notion of negative progress, since it merely maps the best of the evidence it observes. A strategy of picking the ``lesser of two evils''. It will then continue to bias toward the best of the heuristics even though the underlying entities have vastly overshot good solutions.

Credit should however be given to the \Ac{BHH} for its ability to learn positively in such a short timespan. It has been indicated that the update step for the \Ac{BHH} happens at each mini-batch iteration. If a large dataset is presented, that means that the majority of training takes place in a small number of epochs. This leaves a very small window for the \Ac{BHH} to actually learn relevant and useful information from the \index{heuristic}heuristic-space.

Once overfitting has occurred, it is difficult to undo. Therefore the best recommendation is to just use early stopping criteria. A suggestion is to simply stop training after $k$-iterations have not yielded better test set generalisation results.

As a last example, Figure \ref{fig:results:overfitting:figures:loss} shows two examples where overfitting is very obviously noticable.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/test/loss/student_performance.png}
        \caption{student\_performance}
        \label{fig:results:overfitting:figures:loss1}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/test/loss/adult.png}
        \caption{adult}
        \label{fig:results:overfitting:figures:loss2}
	\end{subfigure}
	\caption{\Acs{BHH} overfitting behaviour for varying selection window sizes and datasets}
	\label{fig:results:overfitting:figures:loss}
\end{figure}

The natural steps that follow on this empirical process is to apply early stopping conditions and plot for every mini-batch iteration. This is left for future research. The following section briefly talks about the practical implications for the \Ac{BHH}.

\section{Computational Requirements}
\label{sec:results:computational_requirements}

This section shines some light into the practical applications of the \Ac{BHH}. All population-based approach are generally more computationally expensive than individual candidate solution approaches. This is because of the number of function evaluations they have to do. This is even worse for \acp{HH} since some \acp{HH} require multiple runs, re-evaluations and some have very large memory footprints. This notion is further emphasised when training \acp{FFNN}, since training a single \ac{NN} is already computationally expensive, let alone a whole population.

Specifically, the \Ac{BHH} admittedly has quite a high computational overhead and a relatively large memory footprint. Consider the following aspects that attribute to this fact:

\begin{itemize}
    \item The \Ac{BHH} contains a population of entities.
    \item Each entity maintains a set of state variable that represent all the underlying states of various low-level \index{heuristic}heuristics in its \index{heuristic}heuristic pool.
    \item The \Ac{BHH} sometimes have to re-evaluate heuristics. Some heuristics evaluate after the update step while others first step and then evaluate.
    \item The \Ac{BHH} maintains a global population state.
    \item The \Ac{BHH} maintains a performance log of variable length that needs to be maintained.
    \item The \Ac{BHH} has to apply credit assignment strategies multiple times during a single step to ensure that the correct performance state is maintained.
    \item Thrashing between CPU and GPU execution, such as training the \Acs{FFNN} and then updating the performance log, drastically slows down the training process and calls for rethinking of  implementation. 
\end{itemize}

There are many suggestions that could be made as to how the \ac{BHH} can be improved upon, but those concepts are left for future research. It should just be noted since there is a trade-off involved here. In Chapter \ref{chap:introduction} it is mentioned that the intent of a \ac{HH} is to eliminate the need for a tedious process of trial and error to find a heuristic that can train a \ac{FFNN} sufficiently. The gain in computational time should still be less than the time it would need to follow the trial and error approach for the use of the \Ac{BHH} to be justified.

The next section captures a summary of all of the results.

\section{Summary of Results}
\label{sec:results:summary}

This section aims to provide a brief summary of the results before conclusions are made in the next chapter. This chapter was split into multiple experimental groups and their findings are given as:

\begin{itemize}
    \item Section \ref{sec:results:case_study} presented a case study that was done on the behavour of the \Ac{BHH} during training and testing. It was shown to be able to train \acp{FFNN} well. Detailed analysis was done and it was shown that the \Ac{BHH} does indeed learn and that the general learning is positive towards the overall goals. Both the selection mechanism as well as the perturbative component was shown to work well.

    \item Section \ref{sec:results:standalone} presented an empirical test that was executed to compare the \Ac{BHH}'s performance to that of standalone low-level heuristics. It was found that the \Ac{BHH} performed reasonably well and is able to generalise well on the test set especially considering overfitting conditions that can be avoided in future work. Although the \Ac{BHH} was able to generalise well to the test set, it was not able to perform better than the absolute best low-level heuristic on all occasions. It was mentioned here that the \Ac{BHH} has the advantage to bias prior knowledge towards well known heuristics to aid in the learning process.

    \item Section \ref{sec:results:heuristic_pool} presented an empirical test to compare different heuristic pool configurations. It was found that the gradient-only heuristic pool performed best.

    \item Section \ref{sec:results:population} presented an empirical test to evaluate the effect of population size on the \Ac{BHH}. It was found that population size is shown to be problem-dependent.

    \item Section \ref{sec:results:credit} presented an empirical test to evaluate credit assignment strategies and it was found that the choice of credit assignment strategy to use is problem-dependent.

    \item Section \ref{sec:results:reselection} presented an empirical test to evaluate different reselection window sizes. It was found that the the \Ac{BHH} prefers larger reselection window sizes to give it more time to gather evidence.

    \item Section \ref{sec:results:replay} presented an empirical test to evaluate different replay window sizes and it was found that the choice of replay window size is problem dependent.

    \item Section \ref{sec:results:reanalysis} presented an empirical test to evaluate different reanalysis window sizes and it was also found to be problem dependent.

    \item Section \ref{sec:results:burn_in} presented an empirical test to evaluate different burn in window sizes. In general it was found that limited to no burn in was preferred, giving the \Ac{BHH} the opportunity to start learning as soon as possible.

    \item Sections \ref{sec:results:normalise} investigated the impacts of normalising pseudo counts for the concentration parameter updates before they are updated. It was found that the choice to enable normalisation or not is problem dependent but generally showed not to be necessary. For that reason the authors deem the impact of this parameter to be negligibly small. Small enough to consider for removal in future work.

    \item Sections \ref{sec:results:discounted_rewards} investigated the impacts of discounted rewards in the performance logs for events further back in history. Similar outcomes to that of the normalisation flag parameter was found. In future work, this parameter can be removed.
\end{itemize}

This chapter presented various angles of analysis to ensure that the \Ac{BHH} is properly analysed and studied. As far as was required, all empirical test were analysed for statistical significance and the results of these tests have been provided. Various example plots and figures have been provided as visual aid to try better illustrate the outcomes of the empirical process. Deeper insight into all of the parameters have been given as far as possible. In general, the outcome of the entire empirical process is deemed successful and the \Ac{BHH} shows potential for future research work. The following chapter provides a conclusion of the entire dissertation and the work that is presented here.

### 2022-09-12 dissertation/chapters/09-conclusion.tex
📝 (review): First set of changes

\chapter{Conclusion}
\label{chap:conclusion}

\begin{quote}
    \textit{
    I am sorry to have made such a long speech, but I did not have time to make a shorter one. - Winston Churchill
    }
\end{quote}

Finally, the research objectives that have been set out in this dissertation must be concluded. This chapter provides a summary of the research that has been done.

The remainder of the chapter is structured as follows:

\begin{itemize}
    \item \textbf{Section \ref{sec:conclusion:research_goals}} provides a review of the problem statement, objectives and motivations behind the research.

    \item \textbf{Section \ref{sec:conclusion:background_info}} summarises the background information that was covered.

    \item \textbf{Section \ref{sec:conclusion:bhh}} provides a brief recap of the \ac{BHH} and its implementation.

    \item \textbf{Section \ref{sec:conclusion:methodology}} provides a brief recap of the methodology and the empirical process that was followed.

    \item \textbf{Section \ref{sec:conclusion:results}} summarises the research findings.

    \item \textbf{Section \ref{sec:conclusion:further_research}} discuss further research opportunities.

    \item \textbf{Section \ref{sec:conclusion:documentation_and_data}} briefly discusses some supplementary and supporting material related to the research, as made available by the authors either as external sources or in the appendices of this dissertation.

    \item Finally, \textbf{Section \ref{sec:conclusion:closing_statements}} provides the closing statements of the dissertation.
\end{itemize}

\section{Reviewing Research Objectives}
\label{sec:conclusion:research_goals}

This section briefly reviews the problem statement, motivations and research objectives that was set out in Chapter \ref{chap:introduction} of this dissertation.

The main area of focus for this research stems from the problem statement which identified the difficult and tedious problem of heuristic selection for \ac{FFNN} training. Often times this process is non-trivial and very time-consuming. It has been identified that there is no easy way to know which heuristic to select to train \acp{FFNN}. Traditionally, an iterative approach of trial-and-error was followed. This process involves a tedious process of careful consideration and selection, often at the expense of the researcher's resources.  This research has identified the possibility of using a relatively new approach, referred to as \acp{HH} to automate this selection process. \ac{HH} has been shown to provide a general solution to this problem. The consequences of such approach being successful could provide a mechanism that saves a lot of time and could provide a more generalised solution to heuristic selection.

Investigation was done into the landscapes of existing solutions to train \acp{FFNN} as well as \acp{HH}. Though there exists many applications of \acp{HH} there are little to no published work on using \acp{HH} to train \acp{FFNN}. The only work that was found include the work by \citeauthor{ref:nel:2021} \cite{ref:nel:2021}.

Other existing techniques from other problem domains were investigated. \ac{RL}, meta-learning, online, one-shot and probabilistic learning approached were considered. Bayesian probability theory showed promise and the \Ac{BHH} was conceptualised.

The research objectives were defined and are summarised as follows:

\begin{itemize}
    \item Conduct literature studies on all related topics that are relevant to the development of the \ac{BHH}. These include \ac{ANN}, \index{heuristic}heuristics/optimisers, meta-learning, \acp{HH}, probability theory and Bayesian statistics.

    \item Develop a novel \ac{BHH} that has both a selective and perturbative element. For the selection mechanism, Bayesian statistics and \ac{MAP} is used. For the perturbative element, proxied low-level \index{heuristic}heuristic update steps are used.

    \item Conduct an empirical study to show that the \ac{BHH} is able to train \acp{FFNN} effectively on a number of different datasets.

    \item Conduct an empirical study to study the behavioural characteristics of the \ac{BHH}.

    \item Conduct an empirical study to critically evaluate the performance of the \ac{BHH} to those of traditional, low-level \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.

    \item Conduct an empirical study to evaluate variants of the \ac{BHH} to study the impacts of various design decisions on the outcomes of the \ac{BHH}.

    \item Provide a statistically sound evaluation of outcomes with statistical significance tests driving the conclusions of the outcomes.
\end{itemize}

As one can see, the research set out to do in this dissertation was quite extensive and also identifies many different opportunities for future research.

The next sections aim to provide brief summaries of the work that was done, followed by a conclusion of the outcomes of each.

\section{Summary of Background Information}
\label{sec:conclusion:background_info}

Chapters \ref{chap:introduction} - \ref{chap:probability} provided the reader with background information that is necessary to understand the components that are discussed and developed in this work. These chapters respectively provided background information, literature reviews and landscape analyses into \acp{ANN}, \index{heuristic}heuristics/optimisers, \acp{HH} and meta-learning, probability theory and Bayesian statistics.

It should be mentioned that there are many resources available on the above mentioned topics in their own right. However, the intersection of these topics, especially \acp{ANN} and \acp{HH} are close to non-existent and calls for much more research and publication. This dissertation aims to provide a manifesto of these topics and how they are bring together to show that \acp{HH} can be used to train \acp{FFNN}.

From these topics, it can be concluded that the necessary background information that was provisioned for in the objectives for the dissertation have been provided. The next section gives a summary of the novel \ac{BHH} that was developed.

\section{Summary of Bayesian Hyper-Heuristics}
\label{sec:conclusion:bhh}

The main takeaway point from this dissertation is the development of a novel \ac{BHH}. Chapter \ref{chap:bhh} provides the details and implementation of the \ac{BHH} and provides the reader with various design decisions that could control/affect the outcomes of the \ac{BHH}.

It was shown how the \ac{BHH} implements a Bayesian probabilistic model and makes use of online learning to select \index{heuristic}heuristics dynamically throughout the training process. This probabilistic model forms the selection mechanism for the \ac{BHH}.

Furthermore, it is shown that selection alone is not enough and that a measure of transition between \index{heuristic}heuristics is needed. Entity and \index{heuristic}heuristic state and state-manipulation formed the cornerstone of this topic. A technique that deconstructs \index{heuristic}heuristics into their initialisation and update steps is proposed. This technique then allows for the proxying of update step operations as they are required by different \index{heuristic}heuristics. Though this solves the transition problem between \index{heuristic}heuristics, is has been indicated that does not guarantee stable search processes. This does raise opportunities for further research which is summarised below in Section \ref{sec:conclusion:further_research}.

The simplicity of the \ac{BHH} and various challenges related to it have been highlighted. Of these challenge include:

\begin{itemize}
    \item Catering for overfitting by early stopping conditions.
    \item Catering for invalid selections.
    \item Catering for invalid or stale entity and \index{heuristic}heuristic states.
    \item Catering for mode-collapse where a \index{heuristic}heuristic is either always selected or never selected.
    \item Catering for a trade-off between exploration and exploitation.
\end{itemize}

After the development of the \ac{BHH}, the authors presented the methodology used to execute the empirical process. The details of which is summarised in the next section.

\section{Summary of Methodology}
\label{sec:conclusion:methodology}

As discussed above, the research objectives defined a number of empirical tests to be executed. Each one of the empirical tests is referred to as an experimental group. Various experimental groups have been identified and is listed below:

\begin{itemize}
    \item A case-study on the behaviour of the \ac{BHH} during training and testing to understand the workings of the \ac{BHH} and to see if the \ac{BHH} is able to train \acp{FFNN}.
    \item A comparative analysis between the performance of standalone \index{heuristic}heuristics and the baseline \ac{BHH} when training \acp{FFNN}.
    \item A comparative analysis between variants of the \ac{BHH} that include:
        \begin{itemize}
            \item Different \index{heuristic}heuristic pool configurations.
            \item Different population sizes.
            \item Different credit assignment strategies.
            \item Different reselection window sizes.
            \item Different replay window sizes.
            \item Different reanalysis window sizes.
            \item Different burn in window sizes.
            \item Enabling and disabling normalisation of pseudo counts in the performance log.
            \item Enabling and disabling discounted rewards of pseudo counts in the performance log.
        \end{itemize}
\end{itemize}

Each experimental group is run against a set of 15 datasets, consisting of regression and classification problems, split between uni- and multimodal problems. Each experimental group is repeated over 30 runs for statistical certainty. The statistical analysis process was discussed and ANOVA, post hoc Tukey, independent T-test and Kruskal-Wallis formed part of the statistical test repertoir.

In order to allow for the studying of the \ac{BHH} even after training has saturated and overfitting has occured, all experimental groups are run for 30 epochs, way more than what has been empirically found to be necessary. This also meant that no early stopping conditions were used.

The next section provides a summary of all the results, findings and conclusions related to the empirical process is given next.

\section{Summary of Results}
\label{sec:conclusion:results}

All empirical tests where successfully executed and statistically evaluate as described in the methodology presented in Chapter \ref{chap:methodology}. From these evaluations a number of conclusions are made, each described briefly in the sub-sections below:

\subsection{\ac{BHH} behavioural case study}
\label{sec:conclusion:results:summary:case_study}

For this experimental group it was found that the \ac{BHH} is able to train \acp{FFNN} relatively well. It was shown how the \ac{BHH} is able to learn and that the learning is in a positive direction towards the overall objectives of the \ac{BHH}. Furthermore, it was shown in isolation that both the selection mechanism as well as the perturbative component of the \ac{BHH} was successful in their own rights, resulting in a \ac{HH} that is able to select and combine \index{heuristic}heuristics as needed.

It was shown how the \ac{BHH} drastically overfits at some point during training for a number of datasets. Although it is known that early stopping conditions would prohibit this from happening, other solutions have also been proposed. These include:

\begin{itemize}
    \item \index{heuristic}Heuristic selection acceptance criteria: where a selection is only deemed valid if it does indeed improve on performance.

    \item State reset: to avoid overshooting solutions due to momentum.

    \item Various techniques to balance exploration and exploitation.
\end{itemize}

Various example plots on training and test datasets have been provided and detailed plots of the inner-workings of the \ac{BHH} have been presented to support the findings and arguments.

\subsection{Standalone vs. \ac{BHH} Baseline}
\label{sec:conclusion:results:summary:standalone}

For this experimental group the baseline \ac{BHH} was found to perform relatively well in comparison to the standalone low-level \index{heuristic}heuristics. Overall the \ac{BHH} ranked 5th out of 11 with performances close to that of the best \index{heuristic}heuristics. Unfortunately, the \ac{BHH} was not entirely able to beat the best heuristics on all occasions, but did perform comparatively well in all cases. The empirical results, statistical tests, descriptive plots and plots of example runs are given to support findings and conclusions.

\subsection{\ac{BHH} Variant: Heuristic pool}
\label{sec:conclusion:results:summary:heuristic_pool}

For this experimental group, different configurations of \index{heuristic}heuristic pools were considered. Three different configurations were evaluated. It was found that the gradient-only \ac{BHH} variant performed significantly better than the configurations that included all of the heuristics and one that included only the meta-heuristics. It was shown that the inclusion of meta-heuristics cause the \ac{BHH} to overfit much more drastically due to the nature of their update step operations.

\subsection{\ac{BHH} Variant: Population Size}
\label{sec:conclusion:results:summary:population_size}

For this experimental group, various different population sizes are evaluated. It was found that the population size is largely problem-dependent. An interesting observation was made where some cases where shown where the relationship between population size and performance is not linear, but rather parabolic or even polynomial in some cases. This warrants for further investigation and could serve as a good opportunity for future research.

\subsection{\ac{BHH} Variant: Credit}
\label{sec:conclusion:results:summary:credit}

For this experimental group, various different credit assignment strategies were evaluated. It was found that the choice of credit assignment strategy to use is largely problem-dependent. Two cases were highlighted where symmetric credit assignment was preferred, which suggests that for that dataset \index{heuristic}heuristic selection doesn't matter, only the proxied update step operations are sufficient.

\subsection{\ac{BHH} Variant: Reselection}
\label{sec:conclusion:results:summary:reselection}

For this experimental group different reselection window sizes were evaluated. It was found that a larger reselection size is generally preferred. A bigger reselection window sizes lead to a longer timeframe to learn before reselection has to occur. The increase in number of samples of evidence, per entity-heuristic combination in the performance log is argued to be the reason for this. However, that means that the reselection and replay window size parameter are related. If the reselection window size is large, the replay window size should be large as well.

\subsection{\ac{BHH} Variant: Replay}
\label{sec:conclusion:results:summary:replay}

For this experimental group, different replay windows sizes were evaluated. It was found that the replay window is problem-dependent with some dataset preferring short memory and other preferring long memory. Take note of the relationship between the reselection, replay and reanalysis window sizes. The value of the one does influence the value of other and should be carefully selection together.

\subsection{\ac{BHH} Variant: Reanalysis}
\label{sec:conclusion:results:summary:reanalysis}

For this experimental group different reanalysis window sizes were evaluated. It was also found that the reanalysis window size is problem-dependent. Given the relationship between the reselection, replay and reanalysis window sizes, a suggestion to eliminate hyper-parameters is to remove the notion of reanalysis and merge with reselection. Reselection is shown to correlate with reanalysis and thus can be removed by just setting the reanalysis window size equal to the reselection size.

\subsection{\ac{BHH} Variant: Burn In}
\label{sec:conclusion:results:summary:burn_in}

For this experimental group different burn in window sizes were evaluated. It was found that in general no burn in is preferred, but some exceptions preferring just a very small burn in. In general is was shown that large burn in values are not good.

\subsection{\ac{BHH} Variant: Normalise}
\label{sec:conclusion:results:summary:normalise}

For this experimental group an empirical test was conducted to determine the effects of normalisation of pseudo counts in the performance log. The choice of this parameter was shown to be problem depedent.

\subsection{\ac{BHH} Variant: Discounted Rewards}
\label{sec:conclusion:results:summary:discounted_rewards}

It can be concluded that the outcomes of the empirical process were successful and that the scientific process has been followed accordingly. From this, it can be concluded that all of the objective of the dissertation have been met and that the research can be concluded. The next section provides a brief discussion of further research opportunities that stem from this work.

\section{Further Research}
\label{sec:conclusion:further_research}

Throughout this dissertation, many different opportunities have been identified for future research. This section contains a summmary of these topics.

\subsubsection{Prior Knowledge}

The \ac{BHH} initialises the concentrations for its distributions symmetrically (a value of 1 for all indices). Symmetric initialisation contains no prior bias and assumes uniform sampling at first. It has been identified that expert knowledge can be incorporated into the \ac{BHH} by carefully providing the initial concentration for the distributions. This research would then evaluate if such prior information has a positive impact on the outcomes of the \ac{BHH}.

\subsubsection{Early Stopping}

It has been shown that the \ac{BHH} suffers drastically from overfitting as the majority of learning happens during the first few epochs (large datasets have more mini-batch iterations per epoch) resulting in the majority of the training process, which span 30 epochs, to try recover from overfitting. Early stop was purposefully not utilised in this research in order to see how the \ac{BHH} would behave after training has saturated. Early stopping could provide valuable insight into the actual ranked performance of the \ac{BHH} since overfitting would then no longer be present and a ranked performance evaluation can be done at some point in time.

\subsubsection{Entity Search}

For this dissertation, even though the predictive model implemented by the \ac{BHH} includes entity consideration, it does not sample from an entity pool, but rather keeps the entire entity pool and just switch allocated heuristics. The \ac{BHH}, as is, can be used to learn which entities to select as well. The hypothesis is that this would result in better combinations of entities and heuristics, more often, which should have a positive effect on the outcomes of the \ac{BHH}

\subsubsection{Models}

For this dissertation, focus was put on training \acp{FFNN}. However, in theory one should be able to swap out \acp{FFNN} for any other mathematical model that can be optimised. Suggestions include \acp{DNN}, \acp{RNN} and dynamic optimisation problems.

\subsubsection{Credit Search}

Credit assignment in the context of this dissertation was has 2 outcomes, true and false. Therefore, credit assignment and by definition performance evaluation is modeled as a \index{binomial distribution} distribution with a \index{beta probability distribution}beta probability distribution as a prior probability distribution. Heuristic selection has multiple possible outcomes, yielding a index associated with a heuristic. Therefore, heuristic selection is modeled as a \index{multionomial}multinomial/\index{categorical}categorical with a dirichlet probability distribution as a prior probability distribution. Since the dirichlet-multinomial distributions are the multivariate extensions of the beta-binomial distributions, it show be possible to extend credit assignment to a multivariate version. A suggestion then is to learn which credit assignment to select. The results of this have show that credit assignment is problem-dependent. Therefore, include credit selection as part of the selection pool implemented by the \ac{BHH}. One could then include multiple strategies, each with varying exploration-exploitation trade-off.

\subsubsection{Selection Validation}

The intent behind a selection validation mechanism is to confirm that selections are successful before they are utilised. In other words, a small verification window where it is decided whether the outcomes of a selection mechanism was beneficial to the learning outcomes or not. These selection validations are based on an ``acceptance criterion'' that a selection has to pass before it is validated. Inclusion of a selection validation mechanism for the \ac{BHH} could yield interesting outcomes.

\subsubsection{Dynamic Reselection Window Size Strategies}

It was shown that generally larger reselection window sizes are required. It was shown that there is a relationship between the reselection, replay and reanalysis window sizes. There is an inherent trade-off between exploration and exploitation and therefore, investigation into dynamic sizing strategies could be prove to yield interesting outcomes.

\subsubsection{Heuristic Pools}

This dissertation only considered 3 different configurations of the heuristic pool. The following alternative  configurations could be considered:

\begin{itemize}
    \item Multiple of the same heuristic, but with different hyper-parameter values.
    \item Very large or very small heuristic pool sizes.
    \item Inclusion of black-box optimisers such as CMA-ES.
    \item Ensemble pools where the heuristic selection is a selection of a ensemble configuration.
\end{itemize}

\subsubsection{Parameter Pools}

Throughout this dissertation, many of the findings have been said to be "problem-dependent". A possible solution to this is to apply the \ac{BHH} then for all parameters, not just heuristics. This means to include hyper-parameters such as learning rate, which can be "learnt" during training. This eliminates a lot of the burden to tediously fine-tune and optimise hyper-params.

This could also provide opportunity to investigate other \ac{FFNN} paradigms such as neural architecture search (ref ???) by including various parameters, that describe the \ac{NN} architecture. The \ac{BHH} slection mechanism can then include these elements for learning as well.

\subsubsection{Models}

This dissertation focused on \acp{FFNN} as the underlying model to be trained. However, other models can also be considered.

\section{Documentation and Data}
\label{sec:conclusion:documentation_and_data}

All data, source code, logs, configurations, scripts and analysis is hosted at: \url{https://github.com/arneschreuder/masters.ai} with raw empirical data made available on Google Cloud project id: masters-287321.

\section{Closing Statements}
\label{sec:conclusion:closing_statements}

The research that is presented in this dissertation included the development and detailed analysis of a novel \ac{BHH}. This chapter presented a review of the research objectives. In conclusion it is found that all of the research objectives have been met. The empirical process was sound and the research outcome have been shown to be statistically significant. This concludes the research presented in this document

### 2022-09-12 dissertation/latex/packages.tex
📝 (review): First set of changes

--- 2022-01-07 thesis/latex/packages.tex
@@
 \usepackage{amsthm}                 % American Mathematical Society Theorems
-% \usepackage{algorithm}            % Typeset algorithm captions
+\usepackage{algorithm}            % Typeset algorithm captions
+\usepackage{algpseudocode}
 \usepackage{booktabs}
-\usepackage[ruled,vlined,linesnumbered,noresetcount]{algorithm2e}
+% \usepackage[ruled,vlined,linesnumbered,noresetcount]{algorithm2e}
 \usepackage{bbm}                    % Blackboard variants of Computer Modern Fonts
-\usepackage[sorting=none]{biblatex} % BibLaTeX referencing
+\usepackage[sorting=nyt, sortcites=true, maxbibnames=6, maxcitenames=1]{biblatex} % BibLaTeX referencing
 \usepackage{caption}                % Improved customisation of captions
@@
 bindingoffset=6mm,                  % Binding margin
-showframe                           % Adds frame to see hbox and vbox
+% showframe                           % Adds frame to see hbox and vbox
 ]{geometry}                         % Easy and flexible user interface to customize page layout,
@@
 \usepackage[final]{microtype}
+\usepackage{multirow}
 \usepackage{pgfplots}               % Plot functions
@@
 \usepackage[
+draft=false,
 bookmarks=true,                         % (option) Build bookmarks
@@
 \usepackage[all]{hypcap}                % Correct PDF figure links to top of image
-\usepackage[ocgcolorlinks]{ocgx2}       % Allows you to create OCGs (Optional Content Groups)
+% \usepackage[ocgcolorlinks]{ocgx2}       % Allows you to create OCGs (Optional Content Groups)

### 2022-09-12 dissertation/preamble/abstract.tex
📝 (review): First set of changes

\pagestyle{empty}

\begin{center}
    \Large
    \textbf{Training Feedforward Neural Networks with Bayesian Hyper-Heuristics}
    \vspace{0.5cm}

    \normalsize
    by
    \vspace{0.5cm}

    \normalsize
    A.N. Schreuder\\
    \ifpdf
        E-mail: \href{mailto:an.schreuder@up.ac.za}{an.schreuder@up.ac.za}
    \else
        E-mail: an.schreuder@up.ac.za
    \fi
    \vspace{1cm}

    \Large
    \textbf{Abstract}
\end{center}

Many different heuristics have been developed and used to train \acfp{FFNN}.  However, selection of the best heuristic to train
\acsp{FFNN} is a time consuming and non-trivial exercise. Careful, systematic
selection is thus required to ensure that the best heuristic is used to train the \acsp{FFNN}. In the past, selection
was done by trial and error. A modern approach is to automate the heuristic selection
process. Often it is found that a single approach is not sufficient. Research has
proposed the use of hybridisation of heuristics. One such approach is referred to
as \acfp{HH}. \acsp{HH} focus on dynamically finding the best heuristic or combinations of heuristics in
heuristic-space by making use of heuristic performance information during training time. One such
implementation of a \acs{HH} is a population-based approach that guides the search process by
dynamically selecting heuristics from a heuristic-pool to be applied to
different entities that represent candidate solutions to the problem-space and
work together to find good solutions. This dissertation introduces a novel population-based \Acf{BHH}. An empirical study is done by
using the \acs{BHH} to train \acsp{FFNN}. An in-depth behaviour analysis is done and the performance of the \acs{BHH} is compared to that of ten popular low-level heuristics each with different search
behaviours. The chosen heuristic pool consists out of classic gradient-based heuristics as well as meta-heuristics. The empirical process was executed on fifteen datasets consisting of classification and regression problems
with varying characteristics. Results are analysed for statistical significance and the \acs{BHH} is shown to be able to train \acsp{FFNN} well and provide an automated method for finding the best heuristic to train the \acsp{FFNN} at various stages of the training process.\\*[1cm]
\noindent
\parbox{\textwidth}{
    \textbf{Keywords:} hyper-heuristics, meta-learning, feedforward neural
    networks, supervised learning, Bayesian statistics.
}
\vfill
\newpage

### 2022-09-12 dissertation/preamble/acknowledgements.tex
📝 (review): First set of changes

--- 2022-01-07 thesis/preamble/acknowledgements.tex
@@
 \begin{itemize}
-    \item
-    To my wife, Taylah. Thank you for always believing in me. You are all my
-    reasons.
+    \item To my wife, Taylah. You are all my reasons.
 
-    \item
-        To my daughter, Bean\'e. Thank you for giving life meaning.
+    \item To my daughters, Bean\'e and  Aleah. Thank you for giving life meaning.
 
-    \item
-        To my son, Aden. I can't wait to meet you!
+    \item To my parents, Adr\'e and Engela. Thank you for always believing in me.
 
-    \item
-        To my parents, Adr\'e and Engela. Thank you for making this possible.
+    \item To my sister, Jeannie and her husband, Jaco. Thank you for always motivating me.
 
-    \item
-    To my sister, Jeannie. Thank you for motivating me.
+    \item To my supervisors, Dr. A. Bosman, Prof. C.W. Cleghorn and Prof. A.P. Engelbrecht. Thank you for not giving up on me.
 
-    \item
-    To my supervisors, Dr.~A. Bosman, Dr.~C.W. Cleghorn and Prof.~A.P. Engelbrecht. Thank you
-    for leading me.
-
-    \item
-    To my creator, God. Thank You \ldots for Everything!
+    \item To my creator, God. Thank You \ldots for everything!
 \end{itemize}
@@
 \begin{center}
-    This project was made possible by the National Research Foundation (NRF).\\
-    Thank you for the opportunity.
-\end{center}
-
-\vspace{\fill}
-
-\begin{center}
-    Finally, this project would not have been possible if it were not for the generous hours and hours of computational time I was given on the Center for High Performance Computing (CHPC) Cluster at the Council for Scientific and Industrial Research (CSIR).
+    This project was made possible by the National Research Foundation (NRF) and the Center for High Performance Computing (CHPC) Cluster at the Council for Scientific and Industrial Research (CSIR).
 \end{center}

### 2022-09-12 dissertation/preamble/publication.tex
📝 (review): First set of changes

--- 2022-01-07 thesis/preamble/publication.tex
@@
     \textit{
-        A.N. Schreuder. Training Feedforward Neural Networks with Bayesian
-        Hyper-Heuristics. Master's Thesis. University of Pretoria,
+        Schreuder, A.N. Training Feedforward Neural Networks with Bayesian
+        Hyper-Heuristics. Master's Dissertation. University of Pretoria,
         Department of Computer Science, Pretoria, South Africa.
-        \monthyeardate\today
+        2022
     }
@@
 \noindent
-\textsf{Electronic, hyperlinked versions of this thesis, including
+\textsf{Electronic, hyperlinked versions of this dissertation, including
 data and source code are available online at:}\\*[2.5mm]
@@
     \selectfont
-    \url{https://github.com/arneschreuder/masters}
+    \url{https://github.com/arneschreuder/masters.ai}
 }

### 2022-09-12 dissertation/preamble/titlepage.tex
📝 (review): First set of changes

\pagestyle{empty}
\pagenumbering{Alph}
\begin{titlepage}
    \begin{center}
        % Logo
        \includegraphics[width=0.5\textwidth]{up_logo.eps}
        \vspace{2cm}

        % Title
        \Huge
        \textsf{Training Feedforward Neural Networks with Bayesian
        Hyper-Heuristics}
        \vspace{1cm}

        \large
        \textsf{by}
        \vspace{1cm}

        % Author
        \large
        \textsf{A.N. Schreuder}
        \vfill

        % Degree
        \normalsize
        \textsf{
            Submitted in partial fulfilment of the requirements for the degree\\
            Master of Science, Computer Science (Artificial Intelligence)\\
            in the Faculty of Engineering, Built Environment and Information
            Technology (EBIT)\\
            University of Pretoria,\\
            Pretoria.
        }
        \vspace{2cm}

        % Date
        \normalsize
        \textsf{\monthyeardate\today}
    \end{center}
\end{titlepage}
\newpage

### 2022-09-14 dissertation/chapters/01-introduction.tex
🗑️ (dissertation): Removing artifacts

@@
-\chapter{Introduction}
-\label{chap:introduction}
+\chapter{Introduction}\label{chap:introduction}
 
-\begin{quote}
-      \textit{The Cephalopod retreats and crawls back up against the glass of the fish tank
-            evaluating the situation in front of him. In front of him is a glass jar with
-            prey inside. The lid is shut tightly. Never before has he encountered such an
-            obstacle in nature, prohibiting him from feeding. He curiously swims closer,
-            feeling the shape of the jar with his tentacles. He wraps his tentacles over the
-            jar and with a small turn and pop, he releases the lid. The experiment is
-            repeated and without hesitation, without failure, he opens the jar, faster, more
-            efficiently, every time.}
-\end{quote}
+\begin{quotation}
+      \textit{``It is better to solve one problem five different ways, than to solve five problems one way.'' - George Polya}
+\end{quotation}
 
@@
 \cite{ref:silver:2017}.
-
-Historically, \ac{ML} models were built with a specific purpose in mind and
-revolved around specialised applications. A notable development was that of Deep
-Blue by IBM \cite{ref:keene:1996}, which managed to play chess at a grand master
-level. Deep Blue was able to finish 2-4 against the greatest chess player at the
-time, Gary Kasparov. Although Deep Blue lost the tournament, this was a major
-breakthrough in the field of \ac{AI}. However, Deep Blue was only able to play
-chess and could not be utilised for any other purposes \cite{ref:kelley:2010}.
-Today, DeepMind's \ac{RL} algorithm is capable of playing all of the original
-Atari games \cite{ref:mnih:2013}, but is still very limited to a small set of
-problems that it can solve.
 
@@
 \cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.
+
+This dissertation focuses on the development of a specific type of heuristic, called a \acl{HH} to train \acp{FFNN} in a supervised learning approach.
+In particular, this chapter provides the reader with a brief overview of the problem domain and outlines the research problem, objectives and purpose.
+
+The remainder of the chapter is presented as follows:
+
+\begin{itemize}
+      \item \textbf{Section \ref{sec:introduction:summary_problem_domain}} provides the reader with brief summary of the problem domain.
+
+      \item \textbf{Section \ref{sec:introduction:problem}} outlines the research problem being addressed in this dissertation.
+
+      \item \textbf{Section \ref{sec:introduction:motivation}} provides motivations as to why this research is important and valuable to the field.
+
+      \item \textbf{Section \ref{sec:introduction:objectives}} presents the reader with research objectives.
+      \item
+      \item \textbf{Section \ref{sec:introduction:contributions}} outlines the contributions of this research to the field.
+
+      \item Finally, a full dissertation outline is provided in \textbf{Section \ref{sec:introduction:outline}}.
+\end{itemize}
+
+\section{Summary of Problem Domain}
+\label{sec:introduction:summary_problem_domain}
+
+Historically, \ac{ML} models were built with a specific purpose in mind and
+revolved around specialised applications. A notable development was that of Deep
+Blue by IBM \cite{ref:keene:1996}, which managed to play chess at a grand master
+level. Deep Blue was able to finish 2-4 against the greatest chess player at the
+time, Gary Kasparov. Although Deep Blue lost the tournament, this was a major
+breakthrough in the field of \ac{AI}. However, Deep Blue was only able to play
+chess and could not be utilised for any other purposes \cite{ref:kelley:2010}.
+Today, DeepMind's \ac{RL} algorithm is capable of playing all of the original
+Atari games \cite{ref:mnih:2013}, but is still very limited to a small set of
+problems that it can solve.
 
@@
 
-This dissertation focuses on the development of a \ac{HH} to train \acp{FFNN} in a
-supervised learning approach.
+The following section outlines the research problem that this dissertation aims to focus on and is followed by a discussion as to why this research endevour is important and valuable to the field.
 

### 2022-09-14 dissertation/chapters/01-introduction.tex
📝 (chapter 1): Review

@@
 \Ac{ML} is one of the most popular fields of research in \ac{AI} studies today.
-In recent years, \ac{ML} research has seen some notable achievements in the
-academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014,
-      ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016,
-      ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.  \ac{ML} research has grown
-tremendously over the past decade with successes like AlphaGo, which set new
-standards for \ac{AI} capabilities by beating the world's best Go player, Lee
-Sedol, 4-1 \cite{ref:san-hun:2016}.  Furthermore, an improvement on AlphaGo,
-called AlphaZero, learned to play Go, \textit{tabula rasa} \footnote{Latin word
-      meaning to learn from no prior knowledge.} and managed to beat AlphaGo, 100-1
-\cite{ref:silver:2017}.
+In recent years, \ac{ML} research has seen some notable achievements in academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.
+\ac{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \ac{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1 \cite{ref:san-hun:2016}.
+Furthermore, an improvement on AlphaGo, called AlphaZero, learned to play Go, \textit{tabula rasa} \footnote{Latin word meaning to learn from no prior knowledge.} and managed to beat AlphaGo, 100-1 \cite{ref:silver:2017}.
 
-Over the past few years, modern hardware capabilities have improved to the
-point where workloads in the field of \ac{ML} that were previously computationally
-infeasible, are now possible.
+Over the past few years, modern hardware capabilities have improved to the point where workloads in the field of \ac{ML} that were previously computationally infeasible, are now possible.
 One such sub-field of \ac{ML} is \acp{ANN}.
@@
 \acp{ANN} are the digital equivalent of how we currently understand the brain to work.
-\acp{ANN} can be trained, which is the equivalent of ``learnin'' from data.
+\acp{ANN} can be trained, which is the equivalent of ``learning'' from data.
 Learning gives rise to the ability to apply some form of decision making.
 This ability provides a wide-range of applications from healthcare to finance and yields great interest in the field.
-With the improvement of hardware came an influx of \ac{ML} researchers that focused
-their attention on the training of \acp{ANN}.
+With the improvement of hardware came an influx of \ac{ML} researchers that focused their attention on the training of \acp{ANN}.
 
-A popular field of focus for studying \acp{ANN} is the process by which
-these models are trained. \acp{FFNN} are specific types of
-\acp{ANN} \cite{ref:reed:1999}. The most common way of training \acp{FFNN} is
-\index{supervised training}supervised learning.
+A popular field of focus for studying \acp{ANN} is the process by which these models are trained.
+\Acfp{FFNN} are specific types of \acp{ANN} \cite{ref:reed:1999}.
+The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input and comparing the produced output to that of predefined target data.
 Training of \acp{ANN} is seen as an optimisation problem.
 The \ac{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''.
-A search algorithm known as a \index{heuristic}\textit{heuristic}
-\cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.
+A search algorithm known as a \index{heuristic}\textit{heuristic} \cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.
 
@@
 In particular, this chapter provides the reader with a brief overview of the problem domain and outlines the research problem, objectives and purpose.
-
 The remainder of the chapter is presented as follows:
@@
 \begin{itemize}
-      \item \textbf{Section \ref{sec:introduction:summary_problem_domain}} provides the reader with brief summary of the problem domain.
+      \item \textbf{Section \ref{sec:introduction:summary_research_domain}} provides the reader with brief summary of the problem domain.
+This section also provides a review of the history that lead to related \ac{ANN} research.
 
@@
 
-      \item \textbf{Section \ref{sec:introduction:objectives}} presents the reader with research objectives.
-      \item
+      \item \textbf{Section \ref{sec:introduction:objectives}} presents the reader with research objectives and outlines the goals of this dissertation.
+
       \item \textbf{Section \ref{sec:introduction:contributions}} outlines the contributions of this research to the field.
@@
 
-\section{Summary of Problem Domain}
-\label{sec:introduction:summary_problem_domain}
+The reader is presented with the summary of the research domain next.
 
-Historically, \ac{ML} models were built with a specific purpose in mind and
-revolved around specialised applications. A notable development was that of Deep
-Blue by IBM \cite{ref:keene:1996}, which managed to play chess at a grand master
-level. Deep Blue was able to finish 2-4 against the greatest chess player at the
-time, Gary Kasparov. Although Deep Blue lost the tournament, this was a major
-breakthrough in the field of \ac{AI}. However, Deep Blue was only able to play
-chess and could not be utilised for any other purposes \cite{ref:kelley:2010}.
-Today, DeepMind's \ac{RL} algorithm is capable of playing all of the original
-Atari games \cite{ref:mnih:2013}, but is still very limited to a small set of
-problems that it can solve.
+\section{Summary of Research Domain}\label{sec:introduction:summary_research_domain}
 
-Although the landscape of what can be solved using \acp{ANN} today
-is extensive, there still exists no single model that can be generalised to
-solving multiple problem classes, across multiple problem domains.
+In order to grasp all the concepts that are included in this disseration, it is important to briefly review the landscape of the research fields that are involved, and led to the research work in this disseration.
+This section provides the reader with a brief summary of the research field and outlines key concepts  that contribute to the topics addressed and discussed in this disseration.
+
+Historically, \ac{ML} models were built with a specific purpose in mind and revolved around specialised applications.
+A notable development was that of Deep Blue by IBM \cite{ref:keene:1996}, which managed to play chess at a grand master level.
+Deep Blue was able to finish 2-4 against the greatest chess player at the time, Gary Kasparov.
+Although Deep Blue lost the tournament, this was a major breakthrough in the field of \ac{AI}.
+However, Deep Blue was only able to play chess and could not be utilised for any other purposes \cite{ref:kelley:2010}.
+Today, DeepMind's \ac{RL} algorithm is capable of playing all of the original Atari games \cite{ref:mnih:2013}, but is still very limited to a small set of problems that it can solve.
+Although the computational requirements were lagging behind, these achievements where impressive at the time.
+
+Although the landscape of what can be solved using \acp{ANN} today is extensive, there still exists no single model that can be generalised to solving multiple problem classes, across multiple problem domains.
 \acs{ANN} training algorithms mostly yield problem specific solutions.
@@
 Generalisation of \acp{ANN} refer to the capabilities of the network to either perform well on unseen data or to be applied to other problem domains.
-Various attempts have been made to improve the generalisation capabilities of
-\acp{ANN}. Examples of techniques used include weight \index{dropout}dropout
-\cite{ref:srivastava:2014}, \index{weight decay}weight decay
-\cite{ref:krogh:1992}, \index{meta-learning}meta-learning of learning parameters
-such as the \index{learning rate}learning rate and \index{momentum}momentum of
-gradient-based heuristics \cite{ref:zeiler:2012, ref:lv:2017, ref:darken:1992},
-and removing or postponing the use of outliers in the training data \cite{ref:reeves:1998}. Other techniques focus on improving
-generalisation through model design.
+Various attempts have been made to improve the generalisation capabilities of \acp{ANN}.
+Examples of techniques used include weight \index{dropout}dropout \cite{ref:srivastava:2014}, \index{weight decay}weight decay \cite{ref:krogh:1992}, \index{meta-learning}meta-learning of learning parameters such as the \index{learning rate}learning rate and \index{momentum}momentum of gradient-based heuristics \cite{ref:zeiler:2012, ref:lv:2017, ref:darken:1992}, and removing or postponing the use of outliers in the training data \cite{ref:reeves:1998}.
+Other techniques focus on improving generalisation through model design.
 Design configurations focus on the layout of the neurons and structure of the \acs{ANN} (architecture) and how neurons are connected to interact (topology).
-Examples of such
-techniques include learning of \ac{ANN} architectures through pruning techniques
-\cite{ref:cibas:1996, ref:engelbrecht:1996} or constructive techniques
-\cite{ref:hassibi:1994, ref:lecun:1990}, adaptive activation functions
-\cite{ref:engelbrecht:1995, ref:fletcher:1994}, and quantum methods
-\cite{ref:wan:2017, ref:ricks:2004}.
+Examples of such techniques include learning of \ac{ANN} architectures through pruning techniques \cite{ref:cibas:1996, ref:engelbrecht:1996} or constructive techniques \cite{ref:hassibi:1994, ref:lecun:1990}, adaptive activation functions \cite{ref:engelbrecht:1995, ref:fletcher:1994}, and quantum methods \cite{ref:wan:2017, ref:ricks:2004}.
 
@@
 
-An example of dynamically balancing exploitation and exploration during the
-search process is by dynamically adjusting and learning the heuristic
-\index{hyper-parameters}\textit{hyper-parameters} as part of the learning
-process. This field of study is known as \index{meta-learning}meta-learning
-\cite{ref:giraud:2004}. \index{meta-learning}Meta-learning of heuristic
-hyper-parameters as applied in the training of \acp{ANN} has shown to yield good
-generalisation results \cite{ref:hospedales:2020, ref:vilalta:2002}.
+An example of dynamically balancing exploitation and exploration during the search process is by dynamically adjusting and learning the heuristic \index{hyper-parameters}\textit{hyper-parameters} as part of the learning process.
+This field of study is known as \index{meta-learning}meta-learning \cite{ref:giraud:2004}.
+\index{meta-learning}Meta-learning of heuristic hyper-parameters as applied in the training of \acp{ANN} has shown to yield good generalisation results \cite{ref:hospedales:2020, ref:vilalta:2002}.
 
-This dynamic nature of the learning process leads towards the
-idea that \ac{ML} models could yield better generalisation capabilities if the
-learning process and learning mechanism applied are not statically defined, but
-rather dynamic and under the control of some mechanism. Furthermore, a learning technique that has at its disposal a more diverse set
-of learning behaviours from which it can dynamically select (when the need arises) could yield better generalisation capabilities \cite{ref:huang:2009}.
+The dynamic nature of the learning process leads towards the idea that \ac{ML} models could yield better generalisation capabilities if the learning process and learning mechanism applied are not statically defined, but rather dynamic and under the control of some mechanism.
+Furthermore, a learning technique that has at its disposal a more diverse set of learning behaviours from which it can dynamically select (when the need arises) could yield better generalisation capabilities \cite{ref:huang:2009}.
 
@@
 These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic-space} to solve a specific problem.
-One such form of \ac{HH} is a
-population-based approach that guides the search process by automatically
-selecting heuristics from a heuristic-space to be applied to a collection of
-different candidate solutions in the solution-space. This collection of
-candidate solutions are referred to as a \textit{population} of
-\textit{entities}, where each \textit{entity} is a single candidate solution to
-the problem being optimised.
+One such form of \ac{HH} is a population-based approach that guides the search process by automatically selecting heuristics from a heuristic-space to be applied to a collection of different candidate solutions in the solution-space.
+This collection of candidate solutions are referred to as a \textit{population} of \textit{entities}, where each \textit{entity} is a single candidate solution to the problem being optimised.
 
-Population-based \acp{HH} implement the strategy of multiple heuristics working
-together to solve a problem. However, finding the best heuristic to use is
-non-trivial and some \textit{selection strategy} must be used to select the best
-heuristic. \acp{HH} that implement such a selection strategy are referred to as
-\textit{selection} \acp{HH}. The term \textit{selection} refers to the ability
-of the \ac{HH} to select the best heuristic from a pool of low-level heuristics.
+Population-based \acp{HH} implement the strategy of multiple heuristics working together to solve a problem.
+However, finding the best heuristic to use is non-trivial and some \textit{selection strategy} must be used to select the best heuristic.
+\acp{HH} that implement such a selection strategy are referred to as \textit{selection} \acp{HH}.
+The term \textit{selection} refers to the ability of the \ac{HH} to select the best heuristic from a pool of low-level heuristics.
 
-These selection \acp{HH} can be further categorised based on what information
-they use in the selection strategy. One specific type of selection \ac{HH} is
-called a \index{multi-method populated-based meta-heuristic}\textit{multi-method
-      population-based \index{meta-heuristic}meta-heuristic}
-\cite{ref:vanderstockt:2018}. The term \index{multi-method}\textit{multi-method}
-refers to the incorporation of different low-level heuristics, with different
-search behaviours, into the heuristic-space. The term \textit{population-based}
-refers to the utilisation of a population of entities that represent candidate
-solutions. Finally, the term \index{meta-heuristic}\textit{meta-heuristics}
-refers to the \ac{HH} as a heuristic that does not have any domain knowledge and
-only makes use of information from the search process.
-\citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} mentioned that \acp{HH}
-have been shown to solve a number of problems including bin-packing, examination
-timetabling, production scheduling, the traveling salesman problem, vehicle
-routing problem and many more.
+These selection \acp{HH} can be further categorised based on what information they use in the selection strategy.
+One specific type of selection \ac{HH} is called a \index{multi-method populated-based meta-heuristic}\textit{multi-method population-based \index{meta-heuristic}meta-heuristic} \cite{ref:vanderstockt:2018}.
+The term \index{multi-method}\textit{multi-method} refers to the incorporation of different low-level heuristics, with different search behaviours, into the heuristic-space.
+The term \textit{population-based} refers to the utilisation of a population of entities that represent candidate solutions.
+Finally, the term \index{meta-heuristic}\textit{meta-heuristics} refers to the \ac{HH} as a heuristic that does not have any domain knowledge and only makes use of information from the search process.
+\citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} mentioned that \acp{HH} have been shown to solve a number of problems including bin-packing, examination timetabling, production scheduling, the traveling salesman problem, vehicle routing problem and many more.
 
@@
 
-\section{Problem Statement}
-\label{sec:introduction:problem}
+\section{Problem Statement}\label{sec:introduction:problem}
 
-Many different heuristics have been developed and used to train \acp{FFNN}
-\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
+Many different heuristics have been developed and used to train \acp{FFNN} \cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
 Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses.
 Finding the best heuristic to train the \ac{FFNN} is required in order to yield optimal results.
-This
-process is often non-trivial and could be a time-consuming exercise.  Consider
-that selection of the best heuristic as applied to optimisation problems, such
-as training \acp{FFNN}, is very problem dependent \cite{ref:allen:1996,
-      ref:drake:2020, ref:pillay:2018}.
+This process is often non-trivial and could be a time-consuming exercise.
+Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is very problem dependent \cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
 
-Careful, systematic selection is thus required to find and select the best
-heuristic to train \acp{FFNN}. In the past, researchers selected the best
-heuristic by trail and error. A set of heuristics and carefully selected
-hyper-parameters would be implemented, followed by an empirical test to evaluate
-the performance of each heuristic for a given problem domain
-\cite{ref:pillay:2015}. In this way, researchers were able to determine which
-heuristics and which hyper-parameters performed well for different problems.
+Careful, systematic selection is thus required to find and select the best heuristic to train \acp{FFNN}.
+In the past, researchers selected the best heuristic by trail and error.
+A set of heuristics and carefully selected hyper-parameters would be implemented, followed by an empirical test to evaluate the performance of each heuristic for a given problem domain \cite{ref:pillay:2015}.
+In this way, researchers were able to determine which heuristics and which hyper-parameters performed well for different problems.
 However, this approach is problematic, because it is time-consuming and tedious.
 
-\section{Motivation}
-\label{sec:introduction:motivation}
+The following section provides the authors motivation for this research and outlines the value that this research brings to the field.
 
-A process is required to alleviate the burden of having to exhaustively test
-each implementation of heuristic and hyper-parameters, for every problem being
-optimised.
+\section{Motivation}\label{sec:introduction:motivation}
 
-A modern approach is to use \acp{HH} to automate the process of selecting the
-best heuristic when applied to some optimisation problem. The best heuristic
-might not be a single heuristic, but rather a hybridisation of heuristics
-\cite{ref:pillay:2015}.
+Section \ref{sec:introduction:problem} provides the reader with the research problem being addressed in this disseration.
+This section provides compelling arguments for why this research is important and valuable to the field.
+
+A process is required to alleviate the burden of having to exhaustively test each implementation of heuristic and hyper-parameters, for every problem being optimised.
+
+A modern approach is to use \acp{HH} to automate the process of selecting the best heuristic when applied to some optimisation problem.
+The best heuristic might not be a single heuristic, but rather a hybridisation of heuristics \cite{ref:pillay:2015}.
 Therefore, careful consideration is required to include and select from a diverse set of heuristics that is capable of solving the given problem.
-Importantly, only heuristics that are known to have the potential to solve the
-problem are applicable and can be included in the set of heuristics to select from.
+Importantly, only heuristics that are known to have the potential to solve the problem are applicable and can be included in the set of heuristics to select from.
 
-In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many
-different problems.
+In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
 Some notable examples include the \index{simulated annealing}simulated annealing-based \ac{HH} by \citeauthor{ref:dowsland:2007} \cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \ac{HH} of \citeauthor{ref:burke:2010} \cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by \citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} and work done by \citeauthor{ref:vanderstockt:2018} \cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based metaheuristics in real-valued dynamic optimization.
@@
 
-\acp{FFNN} training is seen as a computational search problem. \Acl{HH}
-as defined by Burke et al. \cite{ref:burke:2010} is ``a search method or
-learning mechanism for selecting or generating heuristics to solve computational
-search problems''. \acp{HH} is a field of research aimed at the automated
-selection, combination, adaptation or generation of multiple lower-level
-heuristics to efficiently solve computational search problems. This implies that
-it should be possible to apply \acp{HH} in the context \acs{FFNN} training.
+\acp{FFNN} training is seen as a computational search problem.
+\Acl{HH} as defined by Burke et al.
+\cite{ref:burke:2010} is ``a search method or learning mechanism for selecting or generating heuristics to solve computational search problems''.
+\acp{HH} is a field of research aimed at the automated selection, combination, adaptation or generation of multiple lower-level heuristics to efficiently solve computational search problems.
+This implies that it should be possible to apply \acp{HH} in the context \acs{FFNN} training.
 
-\citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} mention that the focus of
-\acp{HH} is on automating the development of the \textit{learning mechanism}
-used to find the best heuristic to obtain an appropriate solution to an optimisation problem. \citeauthor{ref:grobler:2012} explain that \acp{HH} employ a high-level heuristic that focuses on
-finding the best low-level heuristic in heuristic-space that could include
-\textit{single-method} and \textit{multi-method} optimisation algorithms
-(heuristics). \acp{HH} relieve the burden of having to select the best
-heuristic to use by trial and error. Furthermore, \acp{HH} can generally be applied to multiple
-problems given that the set of low-level heuristics include
-heuristics that have the potential to solve the problem at hand
-\cite{ref:burke:2010}.
+\citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} mention that the focus of \acp{HH} is on automating the development of the \textit{learning mechanism} used to find the best heuristic to obtain an appropriate solution to an optimisation problem.
+\citeauthor{ref:grobler:2012} explain that \acp{HH} employ a high-level heuristic that focuses on finding the best low-level heuristic in heuristic-space that could include \textit{single-method} and \textit{multi-method} optimisation algorithms (heuristics).
+\acp{HH} relieve the burden of having to select the best heuristic to use by trial and error.
+Furthermore, \acp{HH} can generally be applied to multiple problems given that the set of low-level heuristics include heuristics that have the potential to solve the problem at hand \cite{ref:burke:2010}.
 Automation of the heuristic selection process and the general application to a wider range of problems are characteristics of \acp{HH} that can be beneficial when applied in the context of \acp{FFNN} training.
 
-Note that training of \acp{FFNN} using \acp{HH} is not to be confused with the
-training of \acp{FFNN} using \index{ensemble networks}\textit{ensemble networks}
-or \index{query by committees}\textit{query by committees}.
-\citeauthor{ref:pappa:2014} \cite{ref:pappa:2014} describe \index{ensemble
-      networks}ensemble networks as a combination method in
-\index{meta-learning}meta-learning whereby multiple \acp{ANN} are jointly used
-to solve a problem. Each member network in the ensemble is trained using a
-specified heuristic, and generally this heuristic is applied to the same member
-throughout the training process. The results of all of the member networks are
-then joined together using some consensus mechanism \cite{ref:zhou:2002}. This mechanism
-could be weighted averages, majority voting or weighted voting. \index{ensemble
-      networks}Ensemble networks do not search through the heuristic space to find the best training algorithm for each member, while \acp{HH} do.
+Note that training of \acp{FFNN} using \acp{HH} is not to be confused with the training of \acp{FFNN} using \index{ensemble networks}\textit{ensemble networks} or \index{query by committees}\textit{query by committees}.
+\citeauthor{ref:pappa:2014} \cite{ref:pappa:2014} describe \index{ensemble networks}ensemble networks as a combination method in \index{meta-learning}meta-learning whereby multiple \acp{ANN} are jointly used to solve a problem.
+Each member network in the ensemble is trained using a specified heuristic, and generally this heuristic is applied to the same member throughout the training process.
+The results of all of the member networks are then joined together using some consensus mechanism \cite{ref:zhou:2002}.
+This mechanism could be weighted averages, majority voting or weighted voting.
+\index{ensemble networks}Ensemble networks do not search through the heuristic space to find the best training algorithm for each member, while \acp{HH} do.
 
-This research takes a particular interest in developing a high-level heuristic
-that makes use of probability theory and Bayesian statistical concepts to guide
-the heuristic selection process. This research develops the novel \Acf{BHH}, a
-new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian
-      analysis} which combines prior information with new evidence to the parameters of a selection probability distribution.
-This selection probability distribution is the mechanism by which the \ac{HH} selects appropriate
-heuristics to train \acp{FFNN} during the training process (online learning).
+This research takes a particular interest in developing a high-level heuristic that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process.
+This research develops the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian analysis} which combines prior information with new evidence to the parameters of a selection probability distribution.
+This selection probability distribution is the mechanism by which the \ac{HH} selects appropriate heuristics to train \acp{FFNN} during the training process (online learning).
 
-\section{Objectives}
-\label{sec:introduction:objectives}
+\section{Objectives}\label{sec:introduction:objectives}
 
-The main objective of this research is focused on developing a novel \Ac{BHH}
-selection mechanism in a \ac{HH} framework that can be used to train \acp{FFNN}.
+The main objective of this research is focused on developing a novel \Ac{BHH} selection mechanism in a \ac{HH} framework that can be used to train \acp{FFNN}.
 In order to reach this objective, the following sub-objectives are defined:
@@
 \begin{itemize}
-      \item
-            Conduct a literature study on \acp{ANN} in order to provide
-            the necessary background information of the \ac{AN}, \acp{FFNN} and the
-            training process.
+      \item Conduct a literature study on \acp{ANN} in order to provide the necessary background information of the \ac{AN}, \acp{FFNN} and the training process.
 
-      \item
-            Conduct a literature study on different types of heuristics that have been
-            used to train \acp{FFNN}. The literature study will provide the necessary
-            background information to understand how these different heuristics can
-            be used in the set of heuristics to be selected to train the \ac{FFNN}.
+      \item Conduct a literature study on different types of heuristics that have been used to train \acp{FFNN}.
+The literature study will provide the necessary background information to understand how these different heuristics can be used in the set of heuristics to be selected to train the \ac{FFNN}.
 
-      \item
-            Conduct a literature study on \index{meta-learning}meta-learning and
-            \acp{HH} in order to provide the required background information
-            necessary to propose and develop a new high-level heuristic.
+      \item Conduct a literature study on \index{meta-learning}meta-learning and \acp{HH} in order to provide the required background information necessary to propose and develop a new high-level heuristic.
 
-      \item
-            Conduct a literature study on probability theory and Bayesian statistics
-            such as Bayesian inference and Bayesian analysis to provide the necessary
-            background information required to understand how Bayesian approaches can be
-            used as a learning technique.
+      \item Conduct a literature study on probability theory and Bayesian statistics such as Bayesian inference and Bayesian analysis to provide the necessary background information required to understand how Bayesian approaches can be used as a learning technique.
 
-      \item
-            Develop a novel \Ac{BHH} selection mechanism for a \ac{HH} that makes use
-            of Bayesian statistics to guide the \ac{HH} search process while training
-            \acp{FFNN} on different problems.
+      \item Develop a novel \Ac{BHH} selection mechanism for a \ac{HH} that makes use of Bayesian statistics to guide the \ac{HH} search process while training \acp{FFNN} on different problems.
 
-      \item
-            Conduct an empirical study to show that the developed \Ac{BHH} can
-            effectively be used to train \acp{FFNN}.
+      \item Conduct an empirical study to show that the developed \Ac{BHH} can effectively be used to train \acp{FFNN}.
 
@@
 
-      \item
-            Conduct an empirical study and critically evaluate the performance of the
-            developed \Ac{BHH} compared to individual heuristics in the heuristic-space
-            as they are used to train \acp{FFNN} on different problems.
+      \item Conduct an empirical study and critically evaluate the performance of the developed \Ac{BHH} compared to individual heuristics in the heuristic-space as they are used to train \acp{FFNN} on different problems.
 
-      \item
-            Conduct an empirical study that investigates variations of the \Ac{BHH} and the
-            effects of design decisions and hyper-parameters on the search process.
+      \item Conduct an empirical study that investigates variations of the \Ac{BHH} and the effects of design decisions and hyper-parameters on the search process.
 
-      \item
-            Provide a statistically sound analysis of the results obtained from the
-            empirical study.
+      \item Provide a statistically sound analysis of the results obtained from the empirical study.
 \end{itemize}
 
-\section{Contributions}
-\label{sec:introduction:contributions}
+The following section outlines the research contributions that this disseration hope to bring to the field.
+
+\section{Contributions}\label{sec:introduction:contributions}
 
@@
 \begin{itemize}
-      \item
-            A novel heuristic selection operator is used that focuses on using Bayesian
-            statistics to calculate the probability that a heuristic should be selected
-            in order to efficiently train \acp{FFNN}. The resulting \ac{HH} is referred
-            to as the \Acl{BHH}.
+      \item A novel heuristic selection operator is used that focuses on usi ng Bayesianstatistics to calculate the probability that a heuristic should be selectedin order to efficiently train \acp{FFNN}.
+The resulting \ac{HH} is referredto as the \Acl{BHH}.
 
-      \item
-            The results of the empirical study show  with statistical significance and certainty that the \Ac{BHH} performs generally
-            well on multiple problems.
+      \item The results of the empirical study show with statistical significance and certainty that the \Ac{BHH} performs generally well on multiple problems.
 It is shown that, for each problem, the \Ac{BHH} performance is comparable to the best low-level heuristics (for the particular problem) included in the heuristic selection pool.
 
-      \item
-            The results of the empirical study show that the \Ac{BHH} is able to select
-            the best heuristic to train \ac{FFNN} in general, with statistical
-            certainty. This relieves researchers from the burden of having to do this
-            selection process manually through trial and error.
+      \item The results of the empirical study show that the \Ac{BHH} is able to select the best heuristic to train \ac{FFNN} in general, with statistical certainty.
+This relieves researchers from the burden of having to do this selection process manually through trial and error.
 
-      \item
-            The results of the empirical study show that the \Ac{BHH}, given a diverse
-            set of lower-level heuristics, will generally produce good results when
-            applied to multiple problems at the same time.
+      \item The results of the empirical study show that the \Ac{BHH}, given a diverse set of lower-level heuristics, will generally produce good results when applied to multiple problems at the same time.
 
-      \item
-            Finally, the results of the empirical study show that the \Ac{BHH} is
-            capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from
-                  what comes before''.} knowledge in which a predefined selection bias is used
-            for heuristics that are known to be well suited for certain problems.
+      \item Finally, the results of the empirical study show that the \Ac{BHH} is capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from what comes before''.} knowledge in which a predefined selection bias is used for heuristics that are known to be well suited for certain problems.
 \end{itemize}
 
-\section{Dissertation Outline}
-\label{sec:introduction:outline}
+\section{Dissertation Outline}\label{sec:introduction:outline}
 
@@
 \begin{itemize}
-      \item
-            \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN}
-            and the various components that make up an \acl{AN}. The focus is on the
-            training of \acp{FFNN}. It is shown how the training of \acp{FFNN} is
-            seen as an optimisation problem.
+      \item \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN} and the various components that make up an \acl{AN}.
+The focus is on the training of \acp{FFNN}.
+It is shown how the training of \acp{FFNN} is seen as an optimisation problem.
 
-      \item
-            \textbf{Chapter~\ref{chap:heuristics}} provides details on various types of
-            heuristics and meta-heuristics that have been used to train \acp{FFNN}. A
-            literature study is done to provide details on the search behaviours, application and
-            implementation of each heuristic in the context of training \acp{FFNN}.
+      \item \textbf{Chapter~\ref{chap:heuristics}} provides details on various types of heuristics and meta-heuristics that have been used to train \acp{FFNN}.
+A literature study is done to provide details on the search behaviours, application and implementation of each heuristic in the context of training \acp{FFNN}.
 
-      \item
-            \textbf{Chapter~\ref{chap:hhs}} presents a literature study on the details
-            of \acp{HH} and \index{meta-learning}meta-learning in general. A
-            discussion follows on the current landscape of \ac{HH} research and a review of different selection approaches for \acp{HH} is conducted.
+      \item \textbf{Chapter~\ref{chap:hhs}} presents a literature study on the details of \acp{HH} and \index{meta-learning}meta-learning in general.
+A discussion follows on the current landscape of \ac{HH} research and a review of different selection approaches for \acp{HH} is conducted.
 It is shown how \acp{HH} are suitable for \acs{FFNN} training.
 
-      \item
-            \textbf{Chapter~\ref{chap:probability}} presents a literature study on
-            probability theory. Probability distributions and
-            conjugate priors are discussed in detail. The chapter concludes with a
-            detailed discussion on Bayesian statistics, specifically focusing on
-            Bayesian inference and analysis.
+      \item \textbf{Chapter~\ref{chap:probability}} presents a literature study on probability theory.
+Probability distributions and conjugate priors are discussed in detail.
+The chapter concludes with a detailed discussion on Bayesian statistics, specifically focusing on Bayesian inference and analysis.
 
-      \item
-            \textbf{Chapter~\ref{chap:bhh}} presents the developed \Ac{BHH}. It is shown
-            how the \Ac{BHH} is implemented as a selection mechanism in the context of a
-            \ac{HH} framework. The \Ac{BHH} is shown to implement a \index{Na\"ive Bayes
-                  classifier}Na\"ive Bayes classifier. The probabilistic model that is
-            implemented is derived and discussed in detail. Finally, the chapter
-            concludes with a detailed discussion on how \index{Bayesian
-                  analysis}Bayesian analysis is used to guide the heuristic selection process.
-            The update step (training step) for prior probability concentration
-            parameters is derived and discussed in detail. The \Ac{BHH} algorithmic
-            implementation, variants and suggested application are presented as well.
+      \item \textbf{Chapter~\ref{chap:bhh}} presents the developed \Ac{BHH}.
+It is shown how the \Ac{BHH} is implemented as a selection mechanism in the context of a \ac{HH} framework.
+The \Ac{BHH} is shown to implement a \index{Na\"ive Bayes classifier}Na\"ive Bayes classifier.
+The probabilistic model that is implemented is derived and discussed in detail.
+Finally, the chapter concludes with a detailed discussion on how \index{Bayesian analysis}Bayesian analysis is used to guide the heuristic selection process.
+The update step (training step) for prior probability concentration parameters is derived and discussed in detail.
+The \Ac{BHH} algorithmic implementation, variants and suggested application are presented as well.
 
-      \item
-            \textbf{Chapter~\ref{chap:methodology}} presents a detailed description of
-            the empirical process and the setup of each experiment. It discusses the
-            datasets used, the \ac{FFNN} architecture and topology used, heuristics that
-            are used, the configuration of hyper-parameters, initialisation techniques
-            used, performance measures used and other smaller details of the
-            implementation of each experiment.  Finally, discussions follow on how the
-            results are analysed. This includes a discussion on the method used to
-            determine statistical significance.
+      \item \textbf{Chapter~\ref{chap:methodology}} presents a detailed description of the empirical process and the setup of each experiment.
+It discusses the datasets used, the \ac{FFNN} architecture and topology used, heuristics that are used, the configuration of hyper-parameters, initialisation techniques used, performance measures used and other smaller details of the implementation of each experiment.
+Finally, discussions follow on how the results are analysed.
+This includes a discussion on the method used to determine statistical significance.
 
-      \item
-            \textbf{Chapter~\ref{chap:results}} provides and discusses the results of
-            the empirical study, in detail. A baseline comparison is done by comparing
-            the performance of the \Ac{BHH} to that of all the individual lower-level
-            heuristics on all the datasets. These datasets include classification and
-            regression problems of various sizes and complexity.  Detailed results are
-            presented on the performance of the \Ac{BHH} as a selection mechanism for
-            \acp{HH} and a brief comparison is made to other selection mechanisms.
-            Finally, results are presented on the effects of the hyper-parameters of the
-            \Ac{BHH} on the training process. Discussions follow on how the \Ac{BHH} is
-            shown to automate the selection of the best heuristic during the training of
-            \acp{FFNN}, as applied to a range of problems, alleviating the burden on
-            researchers to apply traditional trial and error approaches. The chapter is
-            concluded with a brief argument in favor of the general applicability of the
-            \Ac{BHH} to more problem domains.
+      \item \textbf{Chapter~\ref{chap:results}} provides and discusses the results of the empirical study, in detail.
+A baseline comparison is done by comparing the performance of the \Ac{BHH} to that of all the individual lower-level heuristics on all the datasets.
+These datasets include classification and regression problems of various sizes and complexity.
+Detailed results are presented on the performance of the \Ac{BHH} as a selection mechanism for \acp{HH} and a brief comparison is made to other selection mechanisms.
+Finally, results are presented on the effects of the hyper-parameters of the \Ac{BHH} on the training process.
+Discussions follow on how the \Ac{BHH} is shown to automate the selection of the best heuristic during the training of \acp{FFNN}, as applied to a range of problems, alleviating the burden on researchers to apply traditional trial and error approaches.
+The chapter is concluded with a brief argument in favor of the general applicability of the \Ac{BHH} to more problem domains.
 
-      \item
-            \textbf{Chapter~\ref{chap:conclusion}} summarises the research done in this
-            dissertation along with a brief overview of the findings made throughout the research
-            process. A review of the research goals are given and suggestions for future
-            research are made.
+      \item \textbf{Chapter~\ref{chap:conclusion}} summarises the research done in this dissertation along with a brief overview of the findings made throughout the research process.
+A review of the research goals are given and suggestions for future research are made.
 \end{itemize}
@@
 \begin{itemize}
-      \item
-            \textbf{Appendix~\ref{app:datasets}} provides details on the datasets used
-            for the empirical analysis.
+      \item \textbf{Appendix~\ref{app:datasets}} provides details on the datasets used for the empirical analysis.
 
-      \item
-            \textbf{Appendix~\ref{app:statistical_analysis}} provides details on the outcomes of the statistical analyses.
+      \item \textbf{Appendix~\ref{app:statistical_analysis}} provides details on the outcomes of the statistical analyses.
 
-      \item
-            \textbf{Appendix~\ref{app:acronyms}} provides a list of the important
-            acronyms used or newly defined in the course of this work, as well as their
-            associated definitions.
+      \item \textbf{Appendix~\ref{app:acronyms}} provides a list of the important acronyms used or newly defined in the course of this work, as well as their associated definitions.
 
-      \item
-            \textbf{Appendix~\ref{app:derived_publications}} lists the publications
-            derived from this work.
+      \item \textbf{Appendix~\ref{app:derived_publications}} lists the publications derived from this work.
 
-      \item
-            \textbf{Appendix~\ref{app:symbols}} lists and defines the mathematical
-            symbols used in this work, categorised according to the relevant chapter
-            in which they appear.
+      \item \textbf{Appendix~\ref{app:symbols}} lists and defines the mathematical symbols used in this work, categorised according to the relevant chapter in which they appear.
 \end{itemize}
 
-To best view the illustrations, tables and figures presented throughout this
-dissertation, it is recommended that the dissertation be viewed in colour.
+To best view the illustrations, tables and figures presented throughout this dissertation, it is recommended that the dissertation be viewed in colour.
+
+The following chapter provides the reader with the background information required on \acp{ANN}.

### 2022-09-14 dissertation/chapters/01-introduction.tex
📝 (chapter1): Review fixes

@@
 \ac{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \ac{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1 \cite{ref:san-hun:2016}.
-Furthermore, an improvement on AlphaGo, called AlphaZero, learned to play Go, \textit{tabula rasa} \footnote{Latin word meaning to learn from no prior knowledge.} and managed to beat AlphaGo, 100-1 \cite{ref:silver:2017}.
+Furthermore, an improvement on AlphaGo, called AlphaZero, learned to play Go  \textit{tabula rasa} \footnote{Latin word meaning to learn from no prior knowledge.} and managed to beat AlphaGo, 100-1 \cite{ref:silver:2017}.
 
@@
 \acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain \cite{ref:engelbrecht:2007}.
-\acp{ANN} are the digital equivalent of how we currently understand the brain to work.
 \acp{ANN} can be trained, which is the equivalent of ``learning'' from data.
@@
 
+\Acfp{FFNN} are specific types of \acp{ANN} \cite{ref:reed:1999}.
 A popular field of focus for studying \acp{ANN} is the process by which these models are trained.
-\Acfp{FFNN} are specific types of \acp{ANN} \cite{ref:reed:1999}.
 The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input and comparing the produced output to that of predefined target data.
@@
 
-In order to grasp all the concepts that are included in this disseration, it is important to briefly review the landscape of the research fields that are involved, and led to the research work in this disseration.
+In order to grasp all the concepts that are included in this disseration, it is important to briefly review the landscape of the research fields that form the basis for the research in this disseration.
 This section provides the reader with a brief summary of the research field and outlines key concepts that contribute to the topics addressed and discussed in this disseration.
@@
 \acs{ANN} training algorithms mostly yield problem specific solutions.
-This means that a particular approach that works well for one domain of problem class, often does not necessarily work for another.
+This means that a particular approach that works well for one domain or problem class, often does not necessarily work for another.
 This problem is known as the \ac{NFL} \cite{ref:wolpert:1997}.
@@
 
-A more recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process.
+A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process.
 This approach focuses on the hybridisation of learning paradigms.
@@
 
-The following section provides the authors motivation for this research and outlines the value that this research brings to the field.
+The following section provides the authors' motivation for this research and outlines the value that this research brings to the field.
 
@@
 
+In Section \ref{sec:introduction:problem} above, it is mentioned that finding the best heuristic to train \acp{FFNN} is a timely and tedious process.
 A modern approach is to use \acp{HH} to automate the process of selecting the best heuristic when applied to some optimisation problem.
@@
 In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
-Some notable examples include the \index{simulated annealing}simulated annealing-based \ac{HH} by \citeauthor{ref:dowsland:2007} \cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \ac{HH} of \citeauthor{ref:burke:2010} \cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by \citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} and work done by \citeauthor{ref:vanderstockt:2018} \cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based metaheuristics in real-valued dynamic optimization.
+Some notable examples include the \index{simulated annealing}simulated annealing-based \ac{HH} by \citeauthor{ref:dowsland:2007} \cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \ac{HH} of \citeauthor{ref:burke:2010} \cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by \citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} and work done by \citeauthor{ref:vanderstockt:2018} \cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based metaheuristics in real-valued dynamic optimization.
 However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.
@@
 This research takes a particular interest in developing a high-level heuristic that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process.
-This research develops the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian analysis} which combines prior information with new evidence to the parameters of a selection probability distribution.
+This research develops the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
 This selection probability distribution is the mechanism by which the \ac{HH} selects appropriate heuristics to train \acp{FFNN} during the training process (online learning).
@@
 
-      \item Conduct a literature study on \index{meta-learning}meta-learning and \acp{HH} in order to provide the required background information necessary to propose and develop a new high-level heuristic.
+      \item Conduct a literature study on \index{meta-learning}meta-learning and \acp{HH} in order to provide the required background information necessary to propose and develop a new high-level heuristic and selection mechanism.
 
@@
 
-The following section outlines the research contributions that this disseration hope to bring to the field.
+The following section outlines the research contributions that this disseration yields.
 
@@
 \begin{itemize}
-      \item A novel heuristic selection operator is used that focuses on usi ng Bayesianstatistics to calculate the probability that a heuristic should be selectedin order to efficiently train \acp{FFNN}.
-The resulting \ac{HH} is referredto as the \Acl{BHH}.
+      \item A novel heuristic selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acp{FFNN}.
+The resulting \ac{HH} is referred to as the \Acl{BHH}.
 

### 2022-09-21 scripts/analyse.py
✨ (feat): Review, analysis script updated

@@ -15,61 +15,73 @@ ANALYSIS_CONFIG = {
 		'view': 'bhh_burn_in',
 		'friendly': 'Burn In',
 		'column': 'burn_in',
-		'param_count': 5
+		'param_count': 5,
+		'order': ['0', '5', '10', '15', '20']
 	},
 	'bhh_credit': {
 		'view': 'bhh_credit',
 		'friendly': 'Credit',
 		'column': 'credit',
-		'param_count': 5
+		'param_count': 5,
+		'order': ['ibest', 'pbest', 'rbest', 'gbest', 'symmetric']
 	},
 	'bhh_discounted_rewards': {
 		'view': 'bhh_discounted_rewards',
 		'friendly': 'Discounted Rewards',
 		'column': 'discounted_rewards',
-		'param_count': 2
+		'param_count': 2,
+		'order': ['true', 'false']
 	},
 	'bhh_heuristic_pool': {
 		'view': 'bhh_heuristic_pool',
 		'friendly': 'Heuristic Pool',
 		'column': 'heuristic_pool',
-		'param_count': 3
+		'param_count': 3,
+		'order': ['all', 'gd', 'mh']
 	},
 	'bhh_normalise': {
 		'view': 'bhh_normalise',
 		'friendly': 'Normalisation',
 		'column': 'normalisation',
-		'param_count': 2
+		'param_count': 2,
+		'order': ['true', 'false']
 	},
 	'bhh_population': {
 		'view': 'bhh_population',
 		'friendly': 'Population',
 		'column': 'population',
-		'param_count': 5
+		'param_count': 5,
+		'order': ['5', '10', '15', '20', '25']
 	},
 	'bhh_reanalysis': {
 		'view': 'bhh_reanalysis',
 		'friendly': 'Reanalysis',
 		'column': 'reanalysis',
-		'param_count': 5
+		'param_count': 5,
+		'order': ['1', '5', '10', '15', '20']
 	},
 	'bhh_replay': {
 		'view': 'bhh_replay',
 		'friendly': 'Replay',
 		'column': 'replay',
-		'param_count': 5
+		'param_count': 5,
+		'order': ['1', '5', '10', '15', '20']
 	},
 	'bhh_reselection': {
 		'view': 'bhh_reselection',
 		'friendly': 'Reselection',
 		'column': 'reselection',
[…]

### 2022-09-21 scripts/clear_figures.sh

@@ -3,3 +3,4 @@
 set -ex
 
 find analysis -regex '.*figures.*.png' -exec rm -f {} \;
+find analysis -regex '.*figures.*.pdf' -exec rm -f {} \;

### 2022-09-21 scripts/concat_csvs.sh

@@ -2,6 +2,6 @@
 
 set -ex
 
-rm -rf data/master.data
-echo "id,dataset,heuristic,heuristic_pool,population,burn_in,replay,reselection,reanalysis,normalisation,credit,discounted_rewards,run,step,wall_time,tag,value" >data/master.data
-find data -name '*.csv' | while read fn; do cat "$fn" >>data/master.data; done
+rm -rf data/master.csv
+echo "id,dataset,heuristic,heuristic_pool,population,burn_in,replay,reselection,reanalysis,normalisation,credit,discounted_rewards,run,step,wall_time,tag,value" >data/master.csv
+find data -name '*.csv' -not -name 'master.csv' | while read fn; do cat "$fn" >>data/master.csv; done

### 2022-09-21 dissertation/chapters/08-results.tex
✨ (review): Adding data and analysis

@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/train_loss.png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/train_loss.png}
 		\caption{Train loss}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/test_loss.png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/test_loss.png}
 		\caption{Test loss}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/train_accuracy.png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/train_accuracy.png}
 		\caption{Train accuracy}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/test_accuracy.png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/test_accuracy.png}
 		\caption{Test accuracy}
@@
 		\centering
-        \includegraphics[width=0.35\textwidth]{analysis/bhh_case_study/iris/legend.png}
+		\includegraphics[width=0.35\textwidth]{bhh_case_study/iris/legend.png}
 		\caption{Legend}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[0].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[0].png}
 		\caption{$\alpha_{0}$ - \Acs{SGD}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[1].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[1].png}
 		\caption{$\alpha_{1}$ - \Acs{Momentum}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[2].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[2].png}
 		\caption{$\alpha_{2}$ - \Acs{NAG}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[3].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[3].png}
 		\caption{$\alpha_{3}$ - \Acs{Adagrad}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[4].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[4].png}
 		\caption{$\alpha_{4}$ - \Acs{RMSProp}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[5].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[5].png}
 		\caption{$\alpha_{5}$ - \Acs{Adadelta}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[6].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[6].png}
 		\caption{$\alpha_{6}$ - \Acs{Adam}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[7].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[7].png}
 		\caption{$\alpha_{7}$ - \Acs{PSO}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[8].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[8].png}
 		\caption{$\alpha_{8}$ - \Acs{GA}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[9].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[9].png}
 		\caption{$\alpha_{9}$ - \Acs{DE}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[0].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[0].png}
 		\caption{$P(\theta_{0} | \alpha)$ - \Acs{SGD}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[1].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[1].png}
 		\caption{$P(\theta_{1} | \alpha)$ - \Acs{Momentum}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[2].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[2].png}
 		\caption{$P(\theta_{2} | \alpha)$ - \Acs{NAG}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[3].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[3].png}
 		\caption{$P(\theta_{3} | \alpha)$ - \Acs{Adagrad}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[4].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[4].png}
 		\caption{$P(\theta_{4} | \alpha)$ - \Acs{RMSProp}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[5].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[5].png}
 		\caption{$P(\theta_{5} | \alpha)$ - \Acs{Adadelta}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[6].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[6].png}
 		\caption{$P(\theta_{6} | \alpha)$ - \Acs{Adam}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[7].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[7].png}
 		\caption{$P(\theta_{7} | \alpha)$ - \Acs{PSO}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[8].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[8].png}
 		\caption{$P(\theta_{8} | \alpha)$ - \Acs{GA}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[9].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[9].png}
 		\caption{$P(\theta_{9} | \alpha)$ - \Acs{DE}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[0].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[0].png}
 		\caption{$P\left(h_{0} | \theta \right)$ - \Acs{SGD}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[1].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[1].png}
 		\caption{$P\left(h_{1} | \theta \right)$ - \Acs{Momentum}}
@@
 		\centering
-		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[2].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[2].png}
 		\caption{$P\left(h_{2} | \theta \right)$ - \Acs{NAG}}
@@
 		\centering
-		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[3].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[3].png}
 		\caption{$P\left(h_{3} | \theta \right)$ - \Acs{Adagrad}}
@@
 		\centering
-		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[4].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[4].png}
 		\caption{$P\left(h_{4} | \theta \right)$ - \Acs{RMSProp}}
@@
 		\centering
-		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[5].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[5].png}
 		\caption{$P\left(h_{5} | \theta \right)$ - \Acs{Adadelta}}
@@
 		\centering
-		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[6].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[6].png}
 		\caption{$P\left(h_{6} | \theta \right)$ - \Acs{Adam}}
@@
 		\centering
-		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[7].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[7].png}
 		\caption{$P\left(h_{7} | \theta \right)$ - \Acs{PSO}}
@@
 		\centering
-		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[8].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[8].png}
 		\caption{$P\left(h_{8} | \theta \right)$ - \Acs{GA}}
@@
 		\centering
-		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[9].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[9].png}
 		\caption{$P\left(h_{9} | \theta \right)$ - \Acs{DE}}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/no_learning_theta.png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/no_learning_theta.png}
 		\caption{$P(\theta_{6} | \alpha)$}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/no_learning_test_loss.png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/no_learning_test_loss.png}
 		\caption{Test loss}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[0][6].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[0][6].png}
 		\caption{$P\left(h_{6}|e_{0},c_{1}\right)$ - entity 0 + \Acs{Adam} }
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[1][6].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[1][6].png}
 		\caption{$P\left(h_{6}|e_{1},c_{1}\right)$ - entity 1 + \Acs{Adam} }
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[2][6].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[2][6].png}
 		\caption{$P\left(h_{6}|e_{2},c_{1}\right)$ - entity 2 + \Acs{Adam} }
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[3][6].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[3][6].png}
 		\caption{$P\left(h_{6}|e_{3},c_{1}\right)$ - entity 3 + \Acs{Adam} }
@@
 		\centering
-        \includegraphics[width=0.5\textwidth]{analysis/bhh_case_study/iris/p_HgEC[4][6].png}
+		\includegraphics[width=0.5\textwidth]{bhh_case_study/iris/p_HgEC[4][6].png}
 		\caption{$P\left(h_{6}|e_{4},c_{1}\right)$ - entity 4 + \Acs{Adam} }
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[0].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[0].png}
 		\caption{HgEC\lbrack0\rbrack - entity 0}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[1].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[1].png}
 		\caption{HgEC\lbrack1\rbrack - entity 1}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[2].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[2].png}
 		\caption{HgEC\lbrack2\rbrack - entity 2}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[3].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[3].png}
 		\caption{HgEC\lbrack3\rbrack - entity 3}
@@
 		\centering
-        \includegraphics[width=0.5\textwidth]{analysis/bhh_case_study/iris/HgEC[4].png}
+		\includegraphics[width=0.5\textwidth]{bhh_case_study/iris/HgEC[4].png}
 		\caption{HgEC\lbrack4\rbrack - entity 4}
@@
 		\centering
-		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[6].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[6].png}
 		\caption{$\alpha_{6}$ - \Acs{Adam}}
@@
 		\centering
-		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[6].png}
+		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[6].png}
 		\caption{$P(\theta_{6} | \alpha)$ - \Acs{Adam}}
@@
 		\centering
-        \includegraphics[width=0.5\textwidth]{analysis/bhh_case_study/iris/HgEC[1].png}
+		\includegraphics[width=0.5\textwidth]{bhh_case_study/iris/HgEC[1].png}
 		\caption{HgEC\lbrack1\rbrack - entity 1}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/standalone/figures/descriptive/descriptive.png}
+	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.png}
 	\caption{Descriptive plots between the average ranks of standalone heuristics compared to the baseline \Acs{BHH} per dataset, across all runs and steps.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/standalone/figures/cd/overall.png}
+	\includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
 	\caption{Critical difference plots between the average ranks of standalone heuristics compared to the baseline \Acs{BHH}, across all datasets, runs and steps.}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/train/loss/car.png}
+		\includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
 		\caption{Train loss}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/car.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
 		\caption{Test loss}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/train/accuracy/car.png}
+		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
 		\caption{Train accuracy}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/accuracy/car.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
 		\caption{Test accuracy}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/train/loss/iris.png}
+		\includegraphics[width=\textwidth]{standalone/figures/train/loss/iris.pdf}
 		\caption{Train loss}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/iris.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/iris.pdf}
 		\caption{Test loss}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/train/accuracy/iris.png}
+		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/iris.pdf}
 		\caption{Train accuracy}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/accuracy/iris.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/iris.pdf}
 		\caption{Test accuracy}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/air_quality.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/air_quality.pdf}
 		\caption{air\_quality}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/bank.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/bank.pdf}
 		\caption{bank}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/bike.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/bike.pdf}
 		\caption{bike}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/fish_toxicity.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/fish_toxicity.pdf}
 		\caption{fish\_toxicity}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/forest_fires.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/forest_fires.pdf}
 		\caption{forest\_fires}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/housing.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/housing.pdf}
 		\caption{housing}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/parkinsons.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/parkinsons.pdf}
 		\caption{parkinsons}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/standalone/figures/test/loss/wine_quality.png}
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/wine_quality.pdf}
 		\caption{wine\_quality}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_heuristic_pool/figures/descriptive/descriptive.png}
+	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.png}
 	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying heuristic pools per dataset, across all runs and steps.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_heuristic_pool/figures/cd/overall.png}
+	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/cd/overall.pdf}
 	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying heuristic pools across all datasets, runs and steps.}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_heuristic_pool/figures/test/loss/abalone.png}
+		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/abalone.pdf}
 		\caption{abalone}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_heuristic_pool/figures/test/loss/wine_quality.png}
+		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/wine_quality.pdf}
 		\caption{wine\_quality}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_population/figures/descriptive/descriptive.png}
+	\includegraphics[width=\textwidth]{bhh_population/figures/descriptive/descriptive.png}
 	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying population sizes per dataset, across all runs and steps.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_population/figures/cd/overall.png}
+	\includegraphics[width=\textwidth]{bhh_population/figures/cd/overall.pdf}
 	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying population sizes across all datasets, runs and steps.}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_population/figures/test/loss/bike.png}
+		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/bike.pdf}
 		\caption{bike}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_population/figures/test/loss/housing.png}
+		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/housing.pdf}
 		\caption{housing}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_population/figures/test/accuracy/adult.png}
+		\includegraphics[width=\textwidth]{bhh_population/figures/test/accuracy/adult.pdf}
 		\caption{adult}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_population/figures/test/accuracy/car.png}
+		\includegraphics[width=\textwidth]{bhh_population/figures/test/accuracy/car.pdf}
 		\caption{car}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_credit/figures/descriptive/descriptive.png}
+	\includegraphics[width=\textwidth]{bhh_credit/figures/descriptive/descriptive.png}
 	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying credit assignment strategies per dataset, across all runs and steps.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_credit/figures/cd/overall.png}
+	\includegraphics[width=\textwidth]{bhh_credit/figures/cd/overall.pdf}
 	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying credit assignment strategies across all datasets, runs and steps.}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_credit/figures/test/accuracy/car.png}
+		\includegraphics[width=\textwidth]{bhh_credit/figures/test/accuracy/car.pdf}
 		\caption{car}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_credit/figures/test/accuracy/iris.png}
+		\includegraphics[width=\textwidth]{bhh_credit/figures/test/accuracy/iris.pdf}
 		\caption{iris}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_credit/figures/test/loss/abalone.png}
+		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/abalone.pdf}
 		\caption{abalone}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_credit/figures/test/loss/student_performance.png}
+		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/student_performance.pdf}
 		\caption{student\_performance}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/descriptive/descriptive.png}
+	\includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.png}
 	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying reselection values per dataset, across all runs and steps.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/cd/overall.png}
+	\includegraphics[width=\textwidth]{bhh_reselection/figures/cd/overall.pdf}
 	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying reselection values across all datasets, runs and steps.}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/test/loss/car.png}
+		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/car.pdf}
 		\caption{car}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/test/loss/housing.png}
+		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/housing.pdf}
 		\caption{housing}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_replay/figures/descriptive/descriptive.png}
+	\includegraphics[width=\textwidth]{bhh_replay/figures/descriptive/descriptive.png}
 	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying replay window sizes per dataset, across all runs and steps.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_replay/figures/cd/overall.png}
+	\includegraphics[width=\textwidth]{bhh_replay/figures/cd/overall.pdf}
 	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying replay window sizes across all datasets, runs and steps.}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_replay/figures/test/loss/car.png}
+		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/car.pdf}
 		\caption{car}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_replay/figures/test/loss/student_performance.png}
+		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/student_performance.pdf}
 		\caption{student\_performance}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_reanalysis/figures/descriptive/descriptive.png}
+	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/descriptive/descriptive.png}
 	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying reanalysis window sizes per dataset, across all runs and steps.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_reanalysis/figures/cd/overall.png}
+	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/cd/overall.pdf}
 	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying reanalysis window sizes across all datasets, runs and steps.}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_reanalysis/figures/test/loss/forest_fires.png}
+		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/forest_fires.pdf}
 		\caption{forest\_fires}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_reanalysis/figures/test/loss/parkinsons.png}
+		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/parkinsons.pdf}
 		\caption{parkinsons}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_burn_in/figures/descriptive/descriptive.png}
+	\includegraphics[width=\textwidth]{bhh_burn_in/figures/descriptive/descriptive.png}
 	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying burn in values per dataset, across all runs and steps.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_burn_in/figures/cd/overall.png}
+	\includegraphics[width=\textwidth]{bhh_burn_in/figures/cd/overall.pdf}
 	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying burn in values across all datasets, runs and steps.}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_burn_in/figures/test/loss/bike.png}
+		\includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/bike.pdf}
 		\caption{bike}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_burn_in/figures/test/loss/student_performance.png}
+		\includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/student_performance.pdf}
 		\caption{student\_performance}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_normalise/figures/descriptive/descriptive.png}
+	\includegraphics[width=\textwidth]{bhh_normalise/figures/descriptive/descriptive.png}
 	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with normalisation toggled per dataset, across all runs and steps.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_normalise/figures/cd/overall.png}
+	\includegraphics[width=\textwidth]{bhh_normalise/figures/cd/overall.pdf}
 	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with normalisation toggled across all datasets, runs and steps.}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_normalise/figures/test/loss/bank.png}
+		\includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/bank.pdf}
 		\caption{bank}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_normalise/figures/test/loss/housing.png}
+		\includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/housing.pdf}
 		\caption{housing}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_discounted_rewards/figures/descriptive/descriptive.png}
+	\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/descriptive/descriptive.png}
 	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with discounted rewards toggled per datasets, across all runs and steps.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{analysis/bhh_discounted_rewards/figures/cd/overall.png}
+	\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/cd/overall.pdf}
 	\caption{Critical Difference plots between the average ranks of \Acsp{BHH} with discounted rewards toggled across all datasets, runs and steps.}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_discounted_rewards/figures/test/loss/air_quality.png}
+		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/air_quality.pdf}
 		\caption{air\_quality}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_discounted_rewards/figures/test/loss/fish_toxicity.png}
+		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/fish_toxicity.pdf}
 		\caption{fish\_toxicity}
@@
 It should be observed that overfitting occurs much less frequently when the \index{heuristic}heuristics pool contains only the gradient-based low-level \index{heuristic}heuristics.
-Figure \ref{fig:results:overfitting:figures:gd-overfit} below contains the only case where overfitting occurs when the gradient-only heuristic pool is used.
-
-\begin{figure}[htbp]
-	\centering
-    \includegraphics[width=\textwidth]{analysis/overfitting/student_performance.png}
-    \caption{Example test loss plot where the \Ac{BHH}-gd is shown to overfit }
-    \label{fig:results:overfitting:figures:gd-overfit}
-\end{figure}
+Figure !!!!!!!!FIXME!!!!!!!!!!
+below contains the only case where overfitting occurs when the gradient-only heuristic pool is used.
+
+% TOOD: OLD REFERENCE
+% \ref{fig:results:overfitting:figures:gd-overfit}
+
+% TODO: REPLACE THIS
+% \begin{figure}[htbp]
+% 	\centering
+%     \includegraphics[width=\textwidth]{overfitting/student_performance.png}
+%     \caption{Example test loss plot where the \Ac{BHH}-gd is shown to overfit }
+%     \label{fig:results:overfitting:figures:gd-overfit}
+% \end{figure}
 
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/test/loss/student_performance.png}
+		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/student_performance.pdf}
 		\caption{student\_performance}
@@
 		\centering
-        \includegraphics[width=\textwidth]{analysis/bhh_reselection/figures/test/loss/adult.png}
+		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/adult.pdf}
 		\caption{adult}
@@
 
-    \item Section \ref{sec:results:population} presented an empirical test to evaluate the effect of population size on the \Ac{BHH}.
-It was found that population size is shown to be problem-dependent.
+	\item Section \ref{sec:results:population} presented an empirical test to evaluate the effect of population size on the \Ac{BHH}. It was found that population size is shown to be problem-dependent.
 

### 2022-09-21 dissertation/chapters/09-conclusion.tex
✨ (review): Adding data and analysis

@@
 
-All data, source code, logs, configurations, scripts and analysis is hosted at: \url{https://github.com/arneschreuder/masters.ai} with raw empirical data made available on Google Cloud project id: masters-287321.
+All data, source code, logs, configurations, scripts and analysis is hosted at: \url{https://github.com/arneschreuder/masters.ai} with raw empirical data made available on Google Cloud project id: masters-363209.
 

### 2022-09-21 scripts/do_you_still_love_me.sh

@@ -4,7 +4,7 @@ set -ex
 
 bash scripts/clear_csvs.sh
 bash scripts/clear_figures.sh
-bash scripts/get_progress.sh
+# bash scripts/get_progress.sh
 python scripts/export.py --data-dir=data
 bash scripts/concat_csvs.sh
 bash scripts/upload_master_data.sh

### 2022-09-21 scripts/tf_events_to_csv.py

@@ -1,168 +1,0 @@
-
-
-import argparse
-import os
-import re
-
-import cuid
-import pandas as pd
-import tensorflow as tf
-from tensorflow.core.util import event_pb2
-from tensorflow.python.framework import tensor_util
-from tensorflow.python.lib.io import tf_record
-
-COLUMNS = [
-	'id',
-	'dataset',
-	'heuristic',
-	'heuristic_pool',
-	'population',
-	'burn_in',
-	'replay',
-	'reselection',
-	'reanalysis',
-	'normalisation',
-	'credit',
-	'discounted_rewards',
-	'run',
-	'step',
-	'wall_time',
-	'tag',
-	'value'
-]
-DATA_DIR = None
-PATH = None
-
-def parse_arguments():
-	global DATA_DIR
-	global PATH
-
-	# Parser
-	parser = argparse.ArgumentParser(
-			description="Export TensorBoard tf.event data to csv"
-	)
-
-	# Basic Params
-	parser.add_argument(
-			"--data-dir",
-			type=str,
-			required=True,
-			help="The directory that contains the data"
-	)
-	args = parser.parse_args()
-	DATA_DIR = args.data_dir
-	PATH = os.path.join(os.getcwd(), DATA_DIR)
-
-def print_banner():
-    global DATA_DIR
-
-    print("")
-    print("====================================================================")
-    print("Export TensorBoard tf.event data to csv")
-    print("====================================================================")
-    print("Data Directory: {}".format(DATA_DIR))
-    print("====================================================================")
-    print("")
-
-def my_summary_iterator(path):
-	for r in tf_record.tf_record_iterator(path):
-		yield event_pb2.Event.FromString(r)
-
-def export_events(path):
-	global COLUMNS
-
-	directory = os.path.abspath(os.path.join(path, os.pardir))
-	filename = os.path.basename(path)
-	data_filepath = "{}/{}.csv".format(directory, filename)
-
-	if os.path.isfile(data_filepath):
-		print("Skipped: {}".format(data_filepath))
-		return
-
-	experiment = str(directory).replace(os.getcwd() + '/data/', '')
-	experiment_parts = experiment.split('/')
-	dataset = experiment_parts[0]
-	heuristic = experiment_parts[1]
-	config = experiment_parts[2]
-	config_parts = config.split('_')
-	run = experiment_parts[3]
-
-	# Extract parameters
[…]

### 2022-09-21 scripts/upload_master_data.sh

@@ -1,9 +1,9 @@
 #!/usr/bin/env bash
 
-gsutil cp data/master.data gs://training_ffnns_bhh/master.data
+gsutil cp data/master.csv gs://masters-363209/master.csv
 
-bq rm --force=true masters-287321:raw.raw
+bq rm --force=true masters-363209:raw.raw
 
 bq mk --force=true \
-	--external_table_definition=id:STRING,dataset:STRING,heuristic:STRING,heuristic_pool:STRING,population:INTEGER,burn_in:INTEGER,replay:INTEGER,reselection:INTEGER,reanalysis:INTEGER,normalisation:BOOLEAN,credit:STRING,discounted_rewards:BOOLEAN,run:INTEGER,step:INTEGER,wall_time:FLOAT,tag:STRING,value:FLOAT@CSV=gs://training_ffnns_bhh/master.data \
-	masters-287321:raw.raw
+	--external_table_definition=id:STRING,dataset:STRING,heuristic:STRING,heuristic_pool:STRING,population:INTEGER,burn_in:INTEGER,replay:INTEGER,reselection:INTEGER,reanalysis:INTEGER,normalisation:BOOLEAN,credit:STRING,discounted_rewards:BOOLEAN,run:INTEGER,step:INTEGER,wall_time:FLOAT,tag:STRING,value:FLOAT@CSV=gs://masters-363209/master.csv \
+	masters-363209:raw.raw

### 2022-10-09 dissertation/chapters/01-introduction.tex
✨ (dissertation): Chapter 1 done

@@
 \begin{quotation}
-      \textit{``It is better to solve one problem five different ways, than to solve five problems one way.'' - George Polya}
+      \noindent ``It is better to solve one problem five different ways, than to solve five problems one way.''
 \end{quotation}
+\begin{flushright}
+      George Polya
+\end{flushright}
 
@@
 \ac{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \ac{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1 \cite{ref:san-hun:2016}.
-Furthermore, an improvement on AlphaGo, called AlphaZero, learned to play Go  \textit{tabula rasa} \footnote{Latin word meaning to learn from no prior knowledge.} and managed to beat AlphaGo, 100-1 \cite{ref:silver:2017}.
 
@@
 Learning gives rise to the ability to apply some form of decision making.
-This ability provides a wide-range of applications from healthcare to finance and yields great interest in the field.
-With the improvement of hardware came an influx of \ac{ML} researchers that focused their attention on the training of \acp{ANN}.
+Decision making as an ability provides a wide-range of applications from healthcare to finance and yields great interest in the field.
+With the improvement of hardware came an influx of \ac{ML} researchers that focused their attention on training of \acp{ANN}.
 
@@
 A search algorithm known as a \index{heuristic}\textit{heuristic} \cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.
+The research presented in this disseration focuses on the development of a specific type of heuristic, called a \acl{HH} to train \acp{FFNN} in a supervised learning approach.
 
-This dissertation focuses on the development of a specific type of heuristic, called a \acl{HH} to train \acp{FFNN} in a supervised learning approach.
-In particular, this chapter provides the reader with a brief overview of the problem domain and outlines the research problem, objectives and purpose.
-The remainder of the chapter is presented as follows:
+This chapter provides the reader with a brief overview of the problem domain and outlines the research problem, objectives and purpose. The remainder of the chapter is presented as follows.
 
 \begin{itemize}
-      \item \textbf{Section \ref{sec:introduction:summary_research_domain}} provides the reader with brief summary of the problem domain.
-This section also provides a review of the history that lead to related \ac{ANN} research.
+      \item \textbf{Section \ref{sec:introduction:summary_research_domain}} provides the reader with brief summary of the research domain.
 
-      \item \textbf{Section \ref{sec:introduction:problem}} outlines the research problem being addressed in this dissertation.
+      \item \textbf{Section \ref{sec:introduction:problem}} outlines the research problem being addressed.
 
-      \item \textbf{Section \ref{sec:introduction:motivation}} provides motivations as to why this research is important and valuable to the field.
+      \item \textbf{Section \ref{sec:introduction:motivation}} provides a motivation for this research.
 
-      \item \textbf{Section \ref{sec:introduction:objectives}} presents the reader with research objectives and outlines the goals of this dissertation.
+      \item \textbf{Section \ref{sec:introduction:objectives}} presents the reader with the research objectives and outlines the goals of this dissertation.
 
@@
 
-      \item Finally, a full dissertation outline is provided in \textbf{Section \ref{sec:introduction:outline}}.
+      \item \textbf{Section \ref{sec:introduction:outline}} provides a full dissertation outline.
 \end{itemize}
-
-The reader is presented with the summary of the research domain next.
 
@@
 
-In order to grasp all the concepts that are included in this disseration, it is important to briefly review the landscape of the research fields that form the basis for the research in this disseration.
-This section provides the reader with a brief summary of the research field and outlines key concepts that contribute to the topics addressed and discussed in this disseration.
-
-Historically, \ac{ML} models were built with a specific purpose in mind and revolved around specialised applications.
-A notable development was that of Deep Blue by IBM \cite{ref:keene:1996}, which managed to play chess at a grand master level.
-Deep Blue was able to finish 2-4 against the greatest chess player at the time, Gary Kasparov.
-Although Deep Blue lost the tournament, this was a major breakthrough in the field of \ac{AI}.
-However, Deep Blue was only able to play chess and could not be utilised for any other purposes \cite{ref:kelley:2010}.
-Today, DeepMind's \ac{RL} algorithm is capable of playing all of the original Atari games \cite{ref:mnih:2013}, but is still very limited to a small set of problems that it can solve.
-Although the computational requirements were lagging behind, these achievements where impressive at the time.
+This section provides the reader with a brief summary of the research field and outlines key concepts that contribute to the topics discussed in this disseration.
 
@@
 
-Generalisation of \acp{ANN} refer to the capabilities of the network to either perform well on unseen data or to be applied to other problem domains.
-Various attempts have been made to improve the generalisation capabilities of \acp{ANN}.
-Examples of techniques used include weight \index{dropout}dropout \cite{ref:srivastava:2014}, \index{weight decay}weight decay \cite{ref:krogh:1992}, \index{meta-learning}meta-learning of learning parameters such as the \index{learning rate}learning rate and \index{momentum}momentum of gradient-based heuristics \cite{ref:zeiler:2012, ref:lv:2017, ref:darken:1992}, and removing or postponing the use of outliers in the training data \cite{ref:reeves:1998}.
-Other techniques focus on improving generalisation through model design.
-Design configurations focus on the layout of the neurons and structure of the \acs{ANN} (architecture) and how neurons are connected to interact (topology).
-Examples of such techniques include learning of \ac{ANN} architectures through pruning techniques \cite{ref:cibas:1996, ref:engelbrecht:1996} or constructive techniques \cite{ref:hassibi:1994, ref:lecun:1990}, adaptive activation functions \cite{ref:engelbrecht:1995, ref:fletcher:1994}, and quantum methods \cite{ref:wan:2017, ref:ricks:2004}.
-
 The performance and capabilities of \acp{ANN} is largely influenced by the learning process used.
@@
 
-An example of dynamically balancing exploitation and exploration during the search process is by dynamically adjusting and learning the heuristic \index{hyper-parameters}\textit{hyper-parameters} as part of the learning process.
+Techniques exist to dynamically balance the trade-off between exploration and exploitation during the search process.
+An example of such a technique is to dynamically adjust and learn the heuristic \index{hyper-parameters}\textit{hyper-parameters} as part of the learning process.
 This field of study is known as \index{meta-learning}meta-learning \cite{ref:giraud:2004}.
@@
 
-The dynamic nature of the learning process leads towards the idea that \ac{ML} models could yield better generalisation capabilities if the learning process and learning mechanism applied are not statically defined, but rather dynamic and under the control of some mechanism.
-Furthermore, a learning technique that has at its disposal a more diverse set of learning behaviours from which it can dynamically select (when the need arises) could yield better generalisation capabilities \cite{ref:huang:2009}.
+The dynamic nature of the learning process leads towards the idea that \ac{ML} models could be trained in a way such that the learning process and learning mechanism applied are not statically defined, but rather dynamic and under the control of some mechanism.
 
@@
 This approach focuses on the hybridisation of learning paradigms.
-The main concept behind this paradigm is that the learning process is dynamic and differs from problem to problem.
+The main concept behind this paradigm is that the learning process is dynamic and problem specific.
 A particular learning technique might work well for one problem and not for another.
@@
 
-One such form of hybridisation of learning paradigms is referred to as \index{heterogeneous learning approaches}\textit{heterogeneous learning approaches}.
-Heterogeneous learning approaches make use of different search behaviours by selecting from a behaviour pool.
+One such form of hybridisation of learning paradigms is referred to as \textit{heterogeneous learning approaches}.
+Heterogeneous learning approaches make use of different \textit{search behaviours} by selecting from a behaviour pool.
 Heterogeneous approaches have shown to balance the trade-off between exploration and exploitation \cite{ref:nepomuceno:2013}.
 
-A step further in the concept of hybridisation of learning paradigms is that of hybridisation of different heuristics as they are applied to some optimisation problem \cite{ref:burke:2013}.
+A step further in the concept of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem \cite{ref:burke:2013}.
 These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic-space} to solve a specific problem.
-One such form of \ac{HH} is a population-based approach that guides the search process by automatically selecting heuristics from a heuristic-space to be applied to a collection of different candidate solutions in the solution-space.
+One such form of \ac{HH} is a population-based approach that guides the search process by automatically selecting heuristics from a heuristic-pool to be applied to a collection of different candidate solutions in the solution-space.
 This collection of candidate solutions are referred to as a \textit{population} of \textit{entities}, where each \textit{entity} is a single candidate solution to the problem being optimised.
+Population-based \acp{HH} implement a strategy where multiple heuristics work together to solve a problem.
+This technique requires a mechanism that selects a specific heuristic to be applied to a specific candidate solution.
 
-Population-based \acp{HH} implement the strategy of multiple heuristics working together to solve a problem.
-However, finding the best heuristic to use is non-trivial and some \textit{selection strategy} must be used to select the best heuristic.
+Finding the best heuristic to use is non-trivial and some \textit{selection strategy} must be used to select the best heuristic.
 \acp{HH} that implement such a selection strategy are referred to as \textit{selection} \acp{HH}.
@@
 
-These selection \acp{HH} can be further categorised based on what information they use in the selection strategy.
 One specific type of selection \ac{HH} is called a \index{multi-method populated-based meta-heuristic}\textit{multi-method population-based \index{meta-heuristic}meta-heuristic} \cite{ref:vanderstockt:2018}.
@@
 Finally, the term \index{meta-heuristic}\textit{meta-heuristics} refers to the \ac{HH} as a heuristic that does not have any domain knowledge and only makes use of information from the search process.
+
 \citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} mentioned that \acp{HH} have been shown to solve a number of problems including bin-packing, examination timetabling, production scheduling, the traveling salesman problem, vehicle routing problem and many more.
 
-The following section outlines the research problem that this dissertation aims to focus on and is followed by a discussion as to why this research endevour is important and valuable to the field.
+The following section outlines the research problem that this dissertation aims to address and is followed by a motivation for this research.
 
@@
 This process is often non-trivial and could be a time-consuming exercise.
-Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is very problem dependent \cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
+Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is problem dependent \cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
 
@@
 In this way, researchers were able to determine which heuristics and which hyper-parameters performed well for different problems.
-However, this approach is problematic, because it is time-consuming and tedious.
-
-The following section provides the authors' motivation for this research and outlines the value that this research brings to the field.
+However, this approach is problematic, because it is time-consuming and laborious.
 
 \section{Motivation}\label{sec:introduction:motivation}
-
-Section \ref{sec:introduction:problem} provides the reader with the research problem being addressed in this disseration.
-This section provides compelling arguments for why this research is important and valuable to the field.
 
@@
 The best heuristic might not be a single heuristic, but rather a hybridisation of heuristics \cite{ref:pillay:2015}.
-Therefore, careful consideration is required to include and select from a diverse set of heuristics that is capable of solving the given problem.
-Importantly, only heuristics that are known to have the potential to solve the problem are applicable and can be included in the set of heuristics to select from.
 
 In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
-Some notable examples include the \index{simulated annealing}simulated annealing-based \ac{HH} by \citeauthor{ref:dowsland:2007} \cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \ac{HH} of \citeauthor{ref:burke:2010} \cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by \citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} and work done by \citeauthor{ref:vanderstockt:2018} \cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based metaheuristics in real-valued dynamic optimization.
+Some notable examples include the \index{simulated annealing}simulated annealing-based \ac{HH} by \citeauthor{ref:dowsland:2007} \cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \ac{HH} of \citeauthor{ref:burke:2010} \cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by \citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} and work done by \citeauthor{ref:vanderstockt:2018} \cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based meta-heuristics in real-valued dynamic optimization.
 However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.
 \citeauthor{ref:nel:2021} \cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
-The shortage of research in this field certainly warrants more exploration.
 
@@
 \acp{HH} is a field of research aimed at the automated selection, combination, adaptation or generation of multiple lower-level heuristics to efficiently solve computational search problems.
-This implies that it should be possible to apply \acp{HH} in the context \acs{FFNN} training.
 
@@
 
-This research takes a particular interest in developing a high-level heuristic that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process.
+This research takes a particular interest in developing a selection \acs{HH} that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process.
 This research develops the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
-This selection probability distribution is the mechanism by which the \ac{HH} selects appropriate heuristics to train \acp{FFNN} during the training process (online learning).
+This selection probability distribution is the mechanism by which the \ac{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.
+This process takes place dynamically and during the training process (online learning).
 
@@
 The main objective of this research is focused on developing a novel \Ac{BHH} selection mechanism in a \ac{HH} framework that can be used to train \acp{FFNN}.
-In order to reach this objective, the following sub-objectives are defined:
+In order to reach this objective, the following sub-objectives are defined.
 
@@
       \item Conduct a literature study on different types of heuristics that have been used to train \acp{FFNN}.
-The literature study will provide the necessary background information to understand how these different heuristics can be used in the set of heuristics to be selected to train the \ac{FFNN}.
+The literature study will provide the necessary background information to understand how different heuristics can be used in the set of heuristics to be selected to train the \ac{FFNN}.
 
@@
 
-      \item Conduct an empirical study to investigate the behavioural characteristics of the \ac{BHH} as it is used to train \acp{FFNN} over a number of different datasets.
+      \item Conduct an empirical study to investigate the behavioural characteristics of the \ac{BHH} as it is used to train \acp{FFNN} on an example problem.
 
-      \item Conduct an empirical study and critically evaluate the performance of the developed \Ac{BHH} compared to individual heuristics in the heuristic-space as they are used to train \acp{FFNN} on different problems.
+      \item Conduct an empirical study and critically evaluate the performance of the developed \Ac{BHH} compared to individual heuristics in the heuristic-space as they are used to train \acp{FFNN} on a number of different problems.
 
@@
 
-The following section outlines the research contributions that this disseration yields.
+By achieving the objectives outlined above, a number of research contributions are made. These contributions are presented in this following section.
 
@@
 The results obtained from this research contribute to the field of study in the
-following ways:
+following ways.
 
@@
 
-      \item The results of the empirical study show that the \Ac{BHH} is able to select the best heuristic to train \ac{FFNN} in general, with statistical certainty.
+      \item The results of the empirical study show that the \Ac{BHH} is able to select the best heuristic to train \ac{FFNN} in general.
 This relieves researchers from the burden of having to do this selection process manually through trial and error.
@@
 
-The remainder of this dissertation is structured as follows:
+The remainder of this dissertation is structured as follows.
 
@@
       \item \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN} and the various components that make up an \acl{AN}.
-The focus is on the training of \acp{FFNN}.
-It is shown how the training of \acp{FFNN} is seen as an optimisation problem.
+The focus is on training of \acp{FFNN}.
+It is shown how training of \acp{FFNN} is seen as an optimisation problem.
 
@@
       \item \textbf{Chapter~\ref{chap:methodology}} presents a detailed description of the empirical process and the setup of each experiment.
-It discusses the datasets used, the \ac{FFNN} architecture and topology used, heuristics that are used, the configuration of hyper-parameters, initialisation techniques used, performance measures used and other smaller details of the implementation of each experiment.
+It discusses the datasets used, the \ac{FFNN} architecture and topology used, heuristics that are used, the configuration of hyper-parameters, initialisation techniques used and performance measures used.
 Finally, discussions follow on how the results are analysed.
@@
 
-      \item \textbf{Chapter~\ref{chap:results}} provides and discusses the results of the empirical study, in detail.
-A baseline comparison is done by comparing the performance of the \Ac{BHH} to that of all the individual lower-level heuristics on all the datasets.
+      \item \textbf{Chapter~\ref{chap:results}} provides and discusses the results of the empirical study in detail.
+A baseline comparison is done by comparing the performance of the \Ac{BHH} to that of all the individual lower-level heuristics on all datasets.
 These datasets include classification and regression problems of various sizes and complexity.
@@
 To best view the illustrations, tables and figures presented throughout this dissertation, it is recommended that the dissertation be viewed in colour.
-
-The following chapter provides the reader with the background information required on \acp{ANN}.

### 2022-10-09 dissertation/chapters/03-heuristics.tex
✨ (dissertation): Chapter 1 done

@@
                   v'_{ij}(t+1) & \text{if } |v'_{ij}(t+1)| < V_{max,j}   \\
-            -V_{maxj}   & \text{if } v'_{ij}(t+1) \leq -V_{max,j}\\
+                  -V_{maxj}    & \text{if } v'_{ij}(t+1) \leq -V_{max,j} \\
                   V_{maxj}     & \text{if } v'_{ij}(t+1) \geq V_{max,j}
@@
 However, \ac{DE} differs significantly in the sense that it makes use of distance and direction information from the current population to guide the search process \cite{ref:engelbrecht:2007}.
-Originally, \ac{DE} was focussed on multi-dimensional real-values optimisation problems, but unlike gradient-based heuristics, it does not require any gradient information.
+Originally, \ac{DE} was focused on multi-dimensional real-values optimisation problems, but unlike gradient-based heuristics, it does not require any gradient information.
 This means that \ac{DE} does not require the underlying optimisation problem to be differentiable, meaning that it can be applied to problems that are discrete, noisy and dynamic \cite{ref:rocca:2011}.
@@
 \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that crossover operators can be further classified based on their encoding/representation scheme.
-These include binary-specific operators used for binary representations and operators focussed on floating-point representations.
+These include binary-specific operators used for binary representations and operators focused on floating-point representations.
 Since the focus is put on training \acp{FFNN}, from this point on, floating-point representations are assumed.

### 2022-10-12 dissertation/chapters/01-introduction.tex
✨ (dissertation): Chapter 2 WIP

@@
 
+\noindent
 \Ac{ML} is one of the most popular fields of research in \ac{AI} studies today.
@@
 
+\noindent
 By achieving the objectives outlined above, a number of research contributions are made. These contributions are presented in this following section.
@@
 
+\noindent
 This dissertation is accompanied by a full index given at page~\pageref{index} along with the following appendices:
@@
 
+\noindent
 To best view the illustrations, tables and figures presented throughout this dissertation, it is recommended that the dissertation be viewed in colour.

### 2022-10-12 dissertation/chapters/02-artificial-neural-networks.tex
✨ (dissertation): Chapter 2 WIP

@@
 
-\begin{quote}
-    \textit{There are an estimated 100 billion neurons in the human brain. That
-        means that there are approximately as many neurons in the human brain as
-        there are stars in our galaxy. Every one of these neurons is highly
-        interconnected with other neurons, yielding a synapse count of 100
-        trillion. These neural structures are the result of millions of years
-        of evolution. It is with these neural structures that we are able to think,
-    learn and dream.}
-\end{quote}
+\begin{quotation}
+    \noindent ``Men ought to know that from the brain, and from the brain only, arise our pleasures, joy, laughter and jests, as well as our sorrows, pains, griefs, and tears.''
+\end{quotation}
+\begin{flushright}
+    Hippocrates
+\end{flushright}
 
-The human brain is by far one of the most complicated biological organs in
-nature. The human brain is what gives us the ability to think and learn. The
-field of \ac{ML} has taken a lot of inspiration from the biological brain which
-lead to the development of \acp{ANN} \cite{ref:rosenblatt:1958}. \acp{ANN}
-are used throughout this dissertation as the model to be trained using \acp{HH}.
-Understanding how \acp{ANN} work is an important component of this dissertation.
+\noindent
+The human brain is one of the most complicated biological organs in nature.
+It gives us the ability to think and learn.
+The field of \ac{ML} has taken a lot of inspiration from the biological brain which lead to the development of \acp{ANN} \cite{ref:rosenblatt:1958}.
+\acp{ANN} are used throughout this dissertation as the \textit{model} to be trained using \acp{HH}.
 
-The purpose of this chapter is to provide the necessary background information
-needed on \acp{ANN} and is thus structured into five main parts:
+The purpose of this chapter is to provide the necessary background information needed on \acp{ANN} and is thus structured into the following sections.
 
 \begin{itemize}
-    \item
-    \textbf{Section \ref{sec:anns:bn}} gives background information on the \ac{BN}.
+    \item \textbf{Section \ref{sec:anns:bn}} gives background information on the \ac{BN}.
 
-    \item
-    \textbf{Section \ref{sec:anns:an}} introduces the \ac{AN} and the various
-    components that it is made up of. Brief discussions follow on
-    input, \index{weights}weights, \index{net input
-    signal}net input signal, \index{biases}biases,
-    \index{activation functions}activation functions, and
-    output.
+    \item \textbf{Section \ref{sec:anns:an}} introduces the \ac{AN}.
+Brief discussions follow on input, \index{weights}weights, \index{biases}biases, \index{net input signal}net input signal, \index{activation functions}activation functions, and output.
 
-    \item
-    Discussions on the \ac{BN} and the \ac{AN} set the tone for the \ac{ANN}
-    which is discussed in detail in \textbf{Section \ref{sec:anns:ann}}. Brief
-    discussions follow on \ac{ANN} architecture, topology, and
-    \acp{FFNN}.
+    \item \textbf{Section \ref{sec:anns:ann}} introduces the \ac{ANN}. Brief discussions follow on \ac{ANN} architecture, topology, and \acp{FFNN}.
 
-    \item
-    \textbf{Section \ref{sec:anns:training}} gives details on the training process,
-    training sets, \index{supervised learning}supervised learning,
-    \index{error function}error functions, performance measures
-    and stopping conditions.
+    \item \textbf{Section \ref{sec:anns:training}} provides details on the training process, training sets, \index {supervised learning}supervised learning, \index{error function}error functions, performance measures and stopping conditions.
 
-    \item
-    Finally, a brief summary of the chapter is given in
-    \textbf{Section \ref{sec:anns:summary}}.
+    \item \textbf{Section \ref{sec:anns:summary}} provides a brief summary of the chapter.
 \end{itemize}
@@
 \index{Biological Neuron}
-\section{Biological Neuron}
-\label{sec:anns:bn}
+\section{Biological Neuron}\label{sec:anns:bn}
 
-This section introduces the \ac{BN} and provides the necessary background
-information in order to understand how it has inspired the development
-of the \ac{AN}.
+This section introduces the \ac{BN} and provides the necessary background information that show how the \ac{BN} has inspired the development of the \ac{AN}.
 
-The biological neural systems are made up of microscopic nerve cells called
-neurons \cite{ref:jain:1996}. Figure \ref{fig:biological_neuron} illustrates a
-single \ac{BN}.
+The biological neural systems are made up of microscopic nerve cells called neurons \cite{ref:jain:1996}. Figure \ref{fig:biological_neuron} illustrates a single \ac{BN}.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{biological_neuron.eps}
-    \caption[The \index{Biological Neuron}Biological Neuron]{An illustration of
-    the \index{Biological Neuron}Biological Neuron.}
+    \includegraphics[width=0.95\textwidth]{biological_neuron.pdf}
+    \caption[The \index{biological neuron}biological Neuron]{An illustration of the \index{biological neuron}biological Neuron.}
     \label{fig:biological_neuron}
@@
 
-The main parts of the \ac{BN} to focus on include the cell body, the
-\index{dendrites}\textit{dendrites} and the \index{axon}\textit{axon} because these
-components are directly modeled in the \ac{AN}. \Acp{NN} are formed by
-neurons that connect to each other. This is known as
-\index{synaptogenesis}\textit{synaptogenesis} \cite{ref:huttenlocher:1997}.
-Connections are made between the \index{axons}axons and
-\index{dendrites}dendrites of various neurons. Such a connection is referred to
-as a \index{synapse}\textit{synapse}. It is through \index{synapses}synapses
-that neurons communicate with each other. Communication takes place by
-electro-chemical pulse and is often referred to as an \textit{activation} or
-\textit{action potential}.  Communication signals propagate from the
-\index{dendrites}dendrites, through the cell body to the axon of a neuron,
-provoking a signal in the post-synaptic neuron \cite{ref:engelbrecht:2007}.
-Neurons like these are massively interconnected.  The greater the connection
-between two neurons, the stronger the communication.  Kennedy
-\cite{ref:kennedy:2016} defines stronger \index{Synapse}synapses as ones that
-contribute more depolarisation to the neural membrane upon activation than
-weaker ones. Stronger \index{Synapse}synapses have a higher probability of
-generating an action potential in the post-synaptic neuron. During activation,
-the pre-synaptic neuron release neurotransmitters that bind to the post-synaptic
-neuron \cite{ref:khanacademy:synapse}. The frequent release of these molecules
-cause the \index{synapse}synapse to grow. Connections that grow over time yield
-stronger signals, while connections that are weak propagate low intensity
-signals and vanish over time. This is how the human brain learns and forgets.
-Every time we reinforce a memory in our brains, we ``train'' the neuron and the
-connection becomes stronger. This is known as \index{synaptic
-plasticity}\textit{synaptic plasticity} \cite{ref:huttenlocher:1997}. this
-reinforcement of connections plays a pivotal role in the way we algorithmically
-train \acp{ANN}.
+\noindent
+The main components of the \ac{BN} include the cell body, \index{dendrites}\textit{dendrites} and the \index{axon}\textit{axon}.
+\Acp{NN} are formed through the connections between the \index{axons}axons and \index{dendrites}dendrites of various neurons.
+This is known as \index{synaptogenesis}\textit{synaptogenesis} \cite{ref:huttenlocher:1997}.
+Such a connection is referred to as a \index{synapse}\textit{synapse}.
+Communication takes place, through the synapse, by electro-chemical pulse and is often referred to as an \textit{activation} or \textit{action potential}.
+Communication signals propagate from the \index{dendrites}dendrites, through the cell body to the axon of a neuron, provoking a signal in the post-synaptic neuron \cite{ref:engelbrecht:2007}.
+The greater the connection between two neurons, the stronger the communication.
+Kennedy \cite{ref:kennedy:2016} defines stronger \index{synapse}synapses as ones that contribute more depolarisation to the neural membrane upon activation than weaker ones.
+Stronger \index{Synapse}synapses have a higher probability of generating an action potential in the post-synaptic neuron.
+During activation, the pre-synaptic neuron release neurotransmitters that bind to the post-synaptic neuron \cite{ref:khanacademy:synapse}.
+The frequent release of these molecules cause the \index{synapse}synapse to grow.
+Connections that grow over time yield stronger signals (learning), while connections that are weak propagate low intensity signals and vanish over time (forgetting).
+The ability of synapses to strengthen and weaken over time is known as \index{synaptic plasticity}\textit{synaptic plasticity} \cite{ref:huttenlocher:1997}.
 
 \index{Artificial Neuron}
-\section{Artificial Neuron}
-\label{sec:anns:an}
+\section{Artificial Neuron}\label{sec:anns:an}
 
-This section introduces the \ac{AN}. It is shown how the \ac{AN} is modeled
-after the \ac{BN} by providing a brief discussion on the various components that
-make up the \ac{AN}. Each component is discussed in more detail, including input
-modeling, weight modeling, \index{net input signal}net input signal modeling,
-biases modeling and output modeling in the \ac{AN}.
+This section introduces the \ac{AN}.
+Brief discussion follow on the various components that make up the \ac{AN}.
+These components include inputs, weights, biases, \index{net input signal}net input signal, and output of the \ac{AN}.
 
-\subsection{Components}
-\label{sec:anns:components}
+\subsection{Components}\label{sec:anns:components}
 
@@
 $\mathbb{R}^{T}$, usually in the ranges $[0,1]$ or $[-1,1]$, depending on the
-activation function used \cite{ref:engelbrecht:2007}. This mapping is given
-below:
+activation function used \cite{ref:engelbrecht:2007} and is given
+in Equation \eqref{eq:an_function_mapping} below.
 
@@
 \noindent
-where $f_{AN}$ is the function mapping produced by the \ac{AN}, $I$
-is the total number of dimensions of the input in real-number space $\mathbb{R}$,
-and $T$ is the total number of dimensions of the target (desired output) in
-real-number space.
+In Equation \eqref{eq:an_function_mapping} above, $f_{AN}$ is the mapping function produced by the \ac{AN}, $I$ is the total number of dimensions of the input in real-number space ($\mathbb{R}$), and $T$ is the total number of dimensions of the target (desired output) in real-number space.
 
-An illustration of the \ac{AN} is given is Figure \ref{fig:artificial_neuron}.
+The \ac{AN} implements various components and is illustrated in Figure \ref{fig:artificial_neuron}.
 
@@
     \centering
-  \includegraphics[width=\textwidth]{artificial_neuron.eps}
-  \caption[The \index{Artificial Neuron}Artificial Neuron]{An illustration of
-  the \index{Artificial Neuron}Artificial Neuron.}
+    \includegraphics[width=\textwidth]{artificial_neuron.pdf}
+    \caption[The \index{artificial neuron}artificial neuron]{An illustration of the \index{artificial neuron}artificial neuron.}
     \label{fig:artificial_neuron}
@@
 
-From Figure~\ref{fig:artificial_neuron}, one can see that the
-\ac{AN} is made up of the following components:
+\noindent
+Each of the components of the \ac{AN} is inspired by some element of the \ac{BN}. Brief descriptions of these are given as follows.
 
 \begin{itemize}
-    \item
-    \textbf{Input:} The input models the activations received from the pre-synaptic neuron
-    or from some environment sensor. Input is represented by the input vector
-    $\vec{x}$.
+    \item \textbf{Input:} The input models the activations received from the pre-synaptic neuron or from some environment sensor.
+Input is represented by the input vector $\vec{x}$, in Figure \ref{fig:artificial_neuron}.
 
-    \item
-    \textbf{Weights:} The weights model the \index{synapse}synapses and connection
-    strengths. Weights are represented by the weight vector, $\vec{v}$.
+    \item \textbf{Weights:} The weights model the \index{synapse}synapses and connection strengths. Weights are represented by the weight vector $\vec{v}$, in Figure \ref{fig:artificial_neuron}.
 
-    \item
-    \index{net input signal}\textbf{Net input signal:} The \index{net input signal}net input signal models
-    the net resulting activations from all connected pre-synaptic neurons or
-    environment sensors. The \index{net input signal}net input signal is
-    represented by $net$.
+    \item \index{net input signal}\textbf{Net input signal:} The \index{net input signal}net input signal models the net resulting activations from all connected pre-synaptic neurons or environment sensors.
+The \index{net input signal}net input signal is represented by $net$, in Figure \ref{fig:artificial_neuron}.
 
-    \item
-    \textbf{Biases:} The biases model a mechanism introduced to influence the strength of the
-    activation (output signal) of the \index{AN}\ac{AN}. The bias is
-    represented by $\theta$.
+    \item \textbf{Biases:} The biases model a mechanism introduced to influence the strength of the activation (output signal) of the \index{AN}\ac{AN}.
+The bias is represented by $\theta$, in Figure \ref{fig:artificial_neuron}.
 
-    \item
-    \index{activation function}\textbf{Activation function:} Models the action potential of the
-    \ac{BN}\index{BN} based on the net input signal. The \index{activation
-    function}activation function is
-    represented by $f$.
+    \item \index{activation function}\textbf{Activation function:} The activation function models the action potential of the \ac{BN}\index{BN} based on the net input signal.
+The \index{activation function}activation function is represented by $f$, in Figure \ref{fig:artificial_neuron}.
 
-    \item
-    \textbf{Output:} The output models the activation by the post-synaptic neuron. Output is
-    represented by the output vector $\vec{y}$.
+    \item \textbf{Output:} The output models the activation by the post-synaptic neuron. Output is represented by the output vector $\vec{y}$, in Figure \ref{fig:artificial_neuron}.
 \end{itemize}
 
-Each of the above mentioned components are discussed in detail in the following
-sections.
+\noindent
+The following sections provide a detailed discussion on each of the above mentioned components.
 
-\subsection{Input}
-\label{sec:anns:an:input}
+\subsection{Input}\label{sec:anns:an:input}
 
-Input signals are $I$-dimensional vectors of numerical values that are obtained
-either through some environment sensor or from other \acp{AN}. Input signals
-are often referred to as \index{features}\textit{features} or \index{independent
-variables}\textit{independent variables} \cite{ref:francis:2001}. In this
-dissertation, a single input vector is referred to as a pattern. Input data must first
-be pre-processed before it is presented to the \ac{AN}. Input pre-processing
-techniques are discussed next.
+Input signals are $I$-dimensional vectors of numerical values that are obtained either through some environment sensor or from other \acp{AN}.
+Input signals are often referred to as \index{features}\textit{features} or \index{independent variables}\textit{independent variables} \cite{ref:francis:2001}.
+Throughout this dissertation, a single input vector is referred to as a pattern.
+Input data must first be pre-processed before it is presented to the \ac{AN}.
+Input pre-processing techniques are presented in the following sections.
 
-\subsubsection{Input Pre-processing}
-\label{sec:anns:an:input:input_pre_processing}
+\subsubsection{Input Pre-Processing}\label{sec:anns:an:input:input_pre_processing}
 
-Input pre-processing can help improve the training process, but also plays an
-important role in determining the success of a practical application of the
-\ac{ANN} \cite{ref:kuzniar:2017}. The primary purpose of input
-pre-processing is to modify the input data so that it can better match predicted
-output.
-
-There are many techniques to consider when pre-processing input data. From
-scaling to the correct ranges to dealing with incomplete, invalid or even
-irrelevant data. For the purposes of this dissertation, only data encoding and
-normalisation is considered. These topics are now discussed in more detail.
+Input pre-processing improves the training process and contributes to the success of the practical application of the \ac{ANN} \cite{ref:kuzniar:2017}.
+The primary purpose of input pre-processing is to modify the input data so that it can better match predicted output data.
+There are many techniques to consider when pre-processing input data.
+These techniques includes methods to encode data to certain formats, to scale to the correct ranges and to deal with incomplete, invalid or irrelevant data.
+For the purposes of this dissertation, only \textit{data encoding} and \textit{normalisation} is considered.
 
 \index{Encoding}
-\subsubsection{Encoding}
-\label{sec:anns:an:input:encoding}
+\subsubsection{Encoding}\label{sec:anns:an:input:encoding}
 
-For qualitative data, such as class labels, the class labels have to be
-converted to numerical representations. In general, class labels are encoded as
-vectors \cite{ref:srinidhi:2018, ref:brownlee:2017:one-hot}. This dissertation makes
-use of \index{One-Hot Encoding}\textit{one-hot encoding} of class labels which
-yields a $K$-dimensional output vector $\vec{y}$ of $0$'s and a single $1$. Each
-element $y_k$ of $\vec{y}$ uniquely refers to a class. An activation, represented by a value
-of $1$ at a given index thus represents a given class. Harris and Harris
-\cite{ref:harris:2010} describe \index{One-Hot Encoding}one-hot encoding as a
-group of vector elements where the classes are represented
-with a single high element (represented by $1$) and all the others low
-(represented by $0$).
-
-Once data has been encoded into the right form, normalisation is required. This
-is discussed next.
+For qualitative data such as categories, the class labels have to be converted from textual to numerical representations.
+In general, class labels are encoded as numerical vectors \cite{ref:srinidhi:2018, ref:brownlee:2017:one-hot}.
+One such encoding technique is referred to as \index{one-hot encoding}\textit{one-hot encoding}.
+Harris and Harris \cite{ref:harris:2010} describe \index{One-Hot Encoding}one-hot encoding as a group of vector elements where the classes are represented with a single high element (represented by $1$) and all the others low (represented by $0$).
+Each element $y_k$, where $k$ is the $k$-th element of the encoded vector $\vec{y}$, uniquely refers to a class.
+An activation, represented by a value of $1$ at a given index thus represents a class associated with that index.
 
 \index{Normalisation}
-\subsubsection{Normalisation}
-\label{sec:anns:an:input:normalisation}
+\subsubsection{Normalisation}\label{sec:anns:an:input:normalisation}
 
-Input data must be normalised and scaled appropriately. In general, input data
-is normalised to a range that is appropriate for the \index{Activation
-Function}activation function being used. This yields input data in a range that
-is comparable to the output produced. For the purpose of this dissertation, the
-min-max scaler \cite{ref:al:2006} and standard score scaler \cite{ref:jain:2005}
-are normalisation techniques that are considered. These are discussed next.
+Numerical data must be normalised and scaled appropriately for the \ac{AN}.
+In general, input data is normalised to a range that is appropriate for the \index{activation function}activation function being used by the \ac{AN}.
+Normalisation and scaling yields input data that is comparable to the output produced by the \ac{AN}.
+For the purposes of this disseration, \index{min-max scaler}min-max scaler \cite{ref:al:2006} and \index{standard score scaler}standard score scaler \cite{ref:jain:2005} are considered.
 
 \index{Min-Max Scalar}
-\subsubsection{Min-Max Scaler}
-\label{sec:anns:an:input:min_max_scaler}
+\subsubsection{Min-Max Scaler}\label{sec:anns:an:input:min_max_scaler}
 
-The \index{Min-Max Scaler}min-max scaler scales all values into the range
-$[0,1]$. This is also called \index{Unity-based
-Normalisation}\textit{unity-based normalisation}. The
-\index{min-max scaler}min-max scaler is used as a pre-processing technique for
-target values when the \index{sigmoid}\textit{sigmoid} \index{activation
-function} activation function is used and is given below:
+The \index{min-max scaler}min-max scaler, also called \index{unity-based normalisation}\textit{unity-based normalisation}, scales values to the range $[0,1]$.
+The \index{min-max scaler}min-max scaler is used as a pre-processing technique for target values when the \index{sigmoid}\textit{sigmoid} \index{activation function} activation function is used.
+The \index{min-max scaler}min-max scaler is given in Equation \eqref{eq:min_max_scaler} below.
 
@@
 
-\noindent where $x_{i,p}^{'}$ is the normalised form of $x_{i,p}$, the $i$-th
-dimension of the input vector $\vec{x}_p$, $p \in \{1,2, \dots, P \}$, where $P$
-is the total number of input patterns. $x_{i_{min}}$ and $x_{i_{max}}$ are
-respectfully the minimum and maximum values of the $i$-th dimension for all
-input vectors $\vec{x}_p, p \in \{1,2, \dots, P\}$.
+\noindent
+In Equation \eqref{eq:min_max_scaler} above, $x_{i,p}^{'}$ is the normalised form of $x_{i,p}$, the $i$-th dimension of the input vector $\vec{x}_p$, $p \in \{1,2, \dots, P \}$, where $P$ is the total number of input patterns, $x_{i_{min}}$ and $x_{i_{max}}$ are respectfully the minimum and maximum values of the $i$-th dimension for all input vectors $\vec{x}_p$.
 
 \index{Standard Score Scalar}
-\subsubsection{Standard Score Scaler}
-\label{sec:anns:an:input:standard_score_scaler}
+\subsubsection{Standard Score Scaler}\label{sec:anns:an:input:standard_score_scaler}
 
-The \index{standard score scaler}standard score scaler, also known as the
-\index{z-score scaler}\textit{z-score scaler}, scales features by subtracting
-the mean and scaling to the unit variance of each dimension $i$ for all input
-patterns $\vec{x}_p, p \in \{1,2, \dots, P\}$. The \index{standard score
-scaler}standard score scaler is used as a pre-processing technique for target
-values when the \index{hyperbolic tangent}\textit{hyperbolic tangent}
-\index{activation function}activation function\index{activation function} is
-used. The normalised form of $x_{i,p}^{'}$ as determined by the \index{standard
-score scaler}standard score scaler is given in below:
+The \index{standard score scaler}standard score scaler, also known as the \index{z-score scaler}\textit{z-score scaler}, scales values by subtracting the mean and scaling to the unit variance of each dimension $i$ for all input patterns $\vec{x}_p, p \in \{1,2, \dots, P\}$.
+The \index{standard score scaler}standard score scaler is used as a pre-processing technique for target values when the \index{hyperbolic tangent}\textit{hyperbolic tangent} \index{activation function}activation function\index{activation function} is used.
+The \index{standard score scaler}standard score scaler is given in Equation \eqref{eq:standard_score_scaler} below.
 
@@
 
-\noindent where $\mu_i$ and $\sigma^2_i$ are respectfully the mean and unit
-variance of the $i$-th dimension of all input vectors $\vec{x}_p, p \in \{1,2,
-\dots, P\}$.
+\noindent
+In Equation \eqref{eq:standard_score_scaler} above, $\mu_i$ and $\sigma^2_i$ are respectfully the mean and unit variance of the $i$-th dimension of all input vectors $\vec{x}_p$.
 
-\subsection{Weights}
-\label{sec:anns:an:weights}
+\subsection{Weights}\label{sec:anns:an:weights}
 
-It was mentioned in Section~\ref{sec:anns:bn} that \index{synapses}synapses can
-have strong or weak connections. The connection strength is modeled in the
-\ac{AN} as weight vectors of numerical values associated with each dimension $i$
-of the input data. Weights can either dampen or strengthen the input data by
-some negative or positive numerical value. By changing the weight associated
-with a feature, the influence of that particular feature on the predicted output
-is changed. Finding the correct value for each weight, to yield optimal output,
-is an optimisation problem \cite{ref:thierens:1993}. The initial placement of
-these weight vectors in the search-space is very important. Research has shown
-that weight initialisation plays an important role in the efficient training of
-\acp{ANN} \cite{ref:thimm:1995}. Weight initialisation is discussed next,
-followed by some common weight initialisation techniques used.
+The connection strength that synapses in the \acs{BN} have is modeled in the \ac{AN} as weight vectors of numerical values associated with each dimension of the input.
+Weights can either dampen or strengthen the input by some negative or positive numerical value.
+Changes in the weight associated with a feature changes the influence that that particular feature has on the predicted output.
+Finding the correct value for each weight, such that the \ac{AN} yields optimal output, is an optimisation problem \cite{ref:thierens:1993}.
+Research has shown that weight initialisation plays an important role in the efficient training of \acp{ANN} \cite{ref:thimm:1995}.
 
 \index{Weight Initialisation}
-\subsubsection{Weight Initialisation}
-\label{sec:anns:an:weights:initialisation}
+\subsubsection{Weight Initialisation}\label{sec:anns:an:weights:initialisation}
 
-Weight initialisation is the process by which candidate solutions (represented
-by the weights of the \ac{AN}) to the problem are placed in the search-space.
-Weight initialisation influences the speed of convergence, the probability of
-convergence and the generalisation capabilities of \acp{ANN}
-\cite{ref:fernandez:2001}. Finding the optimal initialisation values for weights
-is non-trivial and can be seen as another optimisation problem. Extensive
-research on this topic has been done in the past \cite{ref:de:2016,
-ref:erdogmus:2003, ref:yam:2000}.
+Weight initialisation is the process by which candidate solutions (represented by the weights of the \ac{AN}) to the problem are ``placed'' in the search-space.
+Weight initialisation influences the speed of convergence, the probability of convergence and the generalisation capabilities of \acp{ANN} \cite{ref:fernandez:2001}.
+Finding the optimal initialisation values for weights is non-trivial and can be seen as another optimisation problem \cite{ref:de:2016, ref:erdogmus:2003, ref:yam:2000}.
 
-\index{Weight Initialisation}Weight initialisation is dependent on the
-\index{activation function}activation function used. If weights are initialised
-to values that are too small, the vanishing gradients problem can occur
-\cite{ref:hanin:2018}. If weights are initialised to values that are too big,
-output of the activation function would not be in the active range. This leads
-to unit saturation, and exploding gradients can occur
-\cite{ref:hanin:2018, ref:yadav:2018}.
+\index{Weight Initialisation}Weight initialisation is dependent on the \index{activation function}activation function used.
+If weights are initialised as values that are too small, the vanishing gradients problem can occur \cite{ref:hanin:2018}.
+If weights are initialised as values that are too big, output of the activation function would not be in the active range.
+This leads to unit saturation, and exploding gradients can occur \cite{ref:hanin:2018, ref:yadav:2018}.
 
-Research has presented many initialisation techniques \cite{ref:erdogmus:2003}.
-Some techniques have been developed to address the problems that are mentioned
-above \cite{ref:yadav:2018}. However, this dissertation will only focus on
-\index{random uniform sampling}random uniform sampling, \index{Glorot uniform
-sampling}\textit{Glorot uniform (Xavier)} sampling and \index{Glorot normal
-sampling}\textit{Glorot normal} sampling \cite{ref:glorot:2010}. These
-techniques are briefly discussed next.
+Many different weight initialisation techniques have been developed \cite{ref:erdogmus:2003}.
+Some techniques have been developed to address the problems that are mentioned above \cite{ref:yadav:2018}.
+For the purposes of this dissertation, focus is put on \index{random uniform sampling}random uniform sampling, \index{Glorot uniform sampling}\textit{Glorot uniform (Xavier)} sampling and \index{Glorot normal sampling}\textit{Glorot normal} sampling \cite{ref:glorot:2010}.
+Brief discussions on each of these weight initialisation techniques are presented as follows.
 
 \index{random uniform sampling}
-\subsubsection{Random Uniform Sampling}
-\label{sec:anns:an:weights:random_uniform_sampling}
+\subsubsection{Random Uniform Sampling}\label{sec:anns:an:weights:random_uniform_sampling}
 
-\index{random uniform sampling}Random uniform sampling initialises weights
-uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $w_{i} \sim
-\textit{U} (\omega_{min}, \omega_{max})$ where the $\omega_{min}$ and
-$\omega_{max}$ are respectfully the lower and upper bounds of the uniform
-distribution. Suggested parameter values are $(-1, 1)$ or $(-0.5, 0.5)$
-\cite{ref:nguyen:1990}.
+\index{random uniform sampling}Random uniform sampling initialises weights uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $w_{i} \sim \textit{U} (\omega_{min}, \omega_{max})$, where the $\omega_{min}$ and $\omega_{max}$ are respectfully the lower and upper bounds of the uniform distribution.
+Suggested parameter values are $(-1, 1)$ or $(-0.5, 0.5)$ \cite{ref:nguyen:1990}.
 
 \index{Glorot uniform sampling}
-\subsubsection{Glorot Uniform Sampling}
-\label{sec:anns:an:weights:glorot_uniform_sampling}
+\subsubsection{Glorot Uniform Sampling}\label{sec:anns:an:weights:glorot_uniform_sampling}
 
-\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of
-\index{random uniform sampling}random uniform sampling whereby $\omega =
-\sqrt{\frac{6}{fanin + fanout}}$ and \index{$fanin$}$fanin$ is the number of
-input neurons to the weight vector and \index{$fanout$}$fanout$ is the number of
-output neurons from the weight vector.
+\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of \index{random uniform sampling}random uniform sampling whereby $\omega = \sqrt{\frac{6}{fanin + fanout}}$ and \index{$fanin$}$fanin$ is the number of input neurons to the weight vector and \index{$fanout$}$fanout$ is the number of output neurons from the weight vector.
 
 \index{Glorot Normal Sampling}
-\subsubsection{Glorot Normal Sampling}
-\label{sec:anns:an:weights:glorot_normal_sampling}
+\subsubsection{Glorot Normal Sampling}\label{sec:anns:an:weights:glorot_normal_sampling}
 
-\index{Glorot normal sampling}Glorot normal sampling initialises weights by
-sampling from a truncated normal distribution centred on a mean of $0$ and with
-$\sigma = \sqrt{\frac{2}{I + K}}$, where $\sigma$ is the standard deviation of
-the distribution. $I$ and $K$ are respectfully the number of input and output
-units in the weight vector. \index{Glorot normal sampling}Glorot normal sampling
-has been shown to decrease training time \cite{ref:glorot:2010}.
+\index{Glorot normal sampling}Glorot normal sampling initialises weights by sampling from a truncated normal distribution centred on a mean of $0$ and with $\sigma = \sqrt{\frac{2}{I + K}}$, where $\sigma$ is the standard deviation of the distribution.
+$I$ and $K$ are respectfully the number of input and output units in the weight vector.
+\index{Glorot normal sampling}Glorot normal sampling has been shown to decrease training time \cite{ref:glorot:2010}.
 
 \index{net input signal}
-\subsection{Net Input Signal}
-\label{sec:anns:an:net_input}
+\subsection{Net Input Signal}\label{sec:anns:an:net_input}
 
-\acp{AN} accumulate the net resulting input signal from all input dimensions
-into a value called the \index{net input signal}\textit{net input signal},
-expressed as $net$. This signal is passed to the \index{Activation
-Function}activation function, which provokes an artificial action potential in
-the \ac{AN}.
+\acp{AN} accumulate the net resulting input signal from all input dimensions into a value called the \index{net input signal}\textit{net input signal}, expressed as $net$.
+This signal is passed to the \index{activation function}activation function, which provokes an artificial action potential in the \ac{AN}.
 
-The most common way by which the \index{net input signal}net input signal is
-calculated is by means of \acp{SU} \cite{ref:engelbrecht:2007}, which
-compute the \index{net input signal}net input signal as the weighted sum of all
-input signals as shown below:
+A common way by which the \index{net input signal}net input signal is calculated is by means of \acp{SU} \cite{ref:engelbrecht:2007}, which compute the \index{net input signal}net input signal as the weighted sum of all input signals as shown in Equation \eqref{eq:summation_units} below.
 
@@
 
-\noindent where $x_{i}$ is the $i$-th
-dimension of the input vector $\vec{x}$, and $v_{i}$ is the $i$-th dimension of
-the weight vector $\vec{v}$, associated with the given input dimension.
+\noindent
+In Equation \eqref{eq:summation_units} above, $x_{i}$ is the $i$-th dimension of the input vector $\vec{x}$, and $v_{i}$ is the $i$-th dimension of the weight vector $\vec{v}$, associated with the given input dimension.
 
-\subsection{Biases}
-\label{sec:anns:an:biases}
+\subsection{Biases}\label{sec:anns:an:biases}
 
-A bias/threshold term $\theta$ is introduced to help translate the output of the
-\index{activation function}activation function \cite{ref:benitez:1997}. The
-value of $\theta$ must be learned during the training process along with the
-weights of the \ac{ANN}. In order to simplify equations, augmented vectors are
-used in which input and hidden layers have an additional neuron/unit, called the
-\textit{bias unit} \cite{ref:engelbrecht:2007}. Augumented vectors that include
-the bias unit to the net input signal are presented next.
+A bias/threshold term $\theta$ is introduced to help translate the output of the \index{activation function}activation function \cite{ref:benitez:1997}.
+The value of $\theta$ can be learned during the training process along with the weights of the \ac{ANN}.
+In order to simplify equations, the input and weight vectors are augmented such that the input and hidden layers have an additional neuron/unit, called the \textit{bias unit} \cite{ref:engelbrecht:2007}.
+The net input signal can then be rewritten to consider the bias unit, leading to an augmented net input signal.
 
-\subsubsection{Augmented Net Input Signal}
-\label{sec:anns:an:biases:augmented_net_input_signal}
+\subsubsection{Augmented Net Input Signal}\label{sec:anns:an:biases:augmented_net_input_signal}
 
-Input layer $x_{I+1}$ has a net input signal $net^{'} = net - \theta$. The value
-for $\theta$ is learned along with the weights such that $\theta =
-x_{i+1}v_{i+1}$. If a constant value $x_{i+1} = -1$ is used, the equation for
-\acp{SU} as given in Equation~\eqref{eq:summation_units} is then completed by
-including $\theta$ as shown below:
+The augmented net input signal, that includes the bias unit, has the form $net^{'} = net - \theta$.
+The value of $\theta$ is learned along with the weights such that $\theta = x_{i+1}v_{i+1}$.
+A constant value $x_{i+1} = -1$ can be used.
+The net input signal as given in Equation \eqref{eq:summation_units} then changes as is shown in Equation \eqref{eq:augmented_vectors} below.
 
@@
 
-\noindent where $\textit{net}^{'}$ is the augmented net input signal that now
-includes the bias term $\theta$.
+\subsection{Activation Functions}\label{sec:anns:an:act_functions}
 
-\subsection{Activation Functions}
-\label{sec:anns:an:act_functions}
+An \index{activation function}activation function is used to model the action potential of the \index{AN}\ac{AN} \cite{ref:ziv:1994, ref:hodgkin:1952}.
+The \index{activation function}activation function takes as a parameter, the augmented \index{net input signal}net input signal.
+When the output produced by the activation function surpasses some threshold value $\tau$, we consider that neuron to have ``fired'' an output signal.
+\index{activation function}Activation functions thus model \textit{phase shift}.
+In the context of classification problems, \index{activation function}activation functions form decision boundaries between classes.
+In the context of regression problems, \index{activation function}activation functions try to approximate some function that maps the input data to some target data.
 
-An \index{activation function}activation function is used to model the action
-potential of the \index{AN}\ac{AN} \cite{ref:ziv:1994, ref:hodgkin:1952}, and is
-a function over the augmented \index{net input signal}net input signal. It is
-the mechanism that models whether an \index{AN}\ac{AN} fires or not. When the
-output produced by the activation function surpasses some threshold value
-$\theta$, we consider that neuron to have fired an output signal.
-\index{activation function}Activation functions model \textit{phase shift}. In
-the context of classification problems, these \index{activation
-function}activation functions form decision boundaries between classes. In the
-context of regression problems, these \index{activation function}activation
-functions try to approximate some function that maps the input data to some
-target data.
-
-In general, activation functions produce a non-linear mapping of
-$\mathbb{R}^{I}$ to the range $[0,1]$ or $[-1,1]$ as shown below:
+In general, activation functions produce a non-linear mapping of $\mathbb{R}^{I}$ to the range $[0,1]$ or $[-1,1]$ as shown in Equations \eqref{eq:an_function_mapping_0_1} and \eqref{eq:an_function_mapping_minus_1_1} below.
 
 \begin{equation}
-    f_{AN}: \mathbb{R}^{I} \rightarrow [0,1],
+    f_{AN}: \mathbb{R}^{I} \rightarrow [0,1]
     \label{eq:an_function_mapping_0_1}
@@
 
-\noindent or
-
 \begin{equation}
-    f_{AN}: \mathbb{R}^{I} \rightarrow [-1,1].
+    f_{AN}: \mathbb{R}^{I} \rightarrow [-1,1]
     \label{eq:an_function_mapping_minus_1_1}
@@
 
-\noindent Research in the past has presented many \index{activation
-function}activation functions \cite{ref:karlik:2011} of varying ranges. However,
-this dissertation focuses on the \ac{ReLU} \cite{ref:jarrett:2009, ref:nair:2010}, the
-\ac{LReLU} \cite{ref:maas:2013}, the \index{sigmoid}sigmoid \cite{ref:lecun:1988} and the
-\index{hyperbolic tangent}hyperbolic tangent \cite{ref:lin:2008} \index{activation
-function}activation functions. These \index{activation function}activation
-functions are presented next.
+\noindent
+Many different \index{activation function}activation functions have been developed \cite{ref:karlik:2011}.
+For the purposes of this dissertation, focus is put on the \acf{ReLU} \cite{ref:jarrett:2009, ref:nair:2010}, the \acf{LReLU} \cite{ref:maas:2013}, the \index{sigmoid}sigmoid \cite{ref:lecun:1988} and the \index{hyperbolic tangent}hyperbolic tangent \cite{ref:lin:2008} \index{activation function}activation functions.
 
-\subsubsection{Rectified Linear Unit}
-\label{sec:anns:an:act_functions:relu}
+\subsubsection{Rectified Linear Unit}\label{sec:anns:an:act_functions:relu}
 
-The \ac{ReLU} \index{activation function}activation function is an
-\index{activation function}activation function defined in the positive part of
-its argument. It is defined as:
+The \acf{ReLU} \index{activation function}activation function is an \index{activation function}activation function defined in the positive part of its argument and is given in Equation \eqref{eq:relu} below.
 
@@
 
-\noindent An advantage of \ac{ReLU} is that it is not susceptible to the
-\index{vanishing gradient problem}vanishing gradients problem \cite{ref:xu:2015,
-ref:maksutov:2018} which occurs when gradients in the first layers of a
-multi-layer \ac{ANN} approach zero, and have no effect on the training process.
+\noindent
+An advantage of \acs{ReLU} is that it is not susceptible to the \index{vanishing gradient problem}vanishing gradients problem \cite{ref:xu:2015, ref:maksutov:2018} which occurs when gradients in the first layers of a multi-layer \acs{ANN} approach zero, and have no effect on the training process.
 
-\subsubsection{Leaky Rectified Linear Unit}
-\label{sec:anns:an:act_functions:leaky_relu}
+\subsubsection{Leaky Rectified Linear Unit}\label{sec:anns:an:act_functions:leaky_relu}
 
-The \ac{LReLU} \index{activation function}activation function is a variant of
-the \ac{ReLU} \index{activation function}activation function \cite{ref:xu:2015}.
-Similar to \ac{ReLU}, it is not susceptible to the \index{vanishing gradients
-problem}vanishing gradients problem, and it does not suffer from the \index{dying
-ReLU problem}dying \ac{ReLU} problem \cite{ref:agarap:2018}, which occurs when
-the neurons that use \ac{ReLU} \index{activation functions}activation functions
-become \textit{inactive} and only output $0$ due to a negative net input signal.
-
-The \ac{LReLU} \index{activation function}activation function is defined as:
+The \acf{LReLU} \index{activation function}activation function is a variant of the \acs{ReLU} \index{activation function}activation function that avoids zero gradients in the negative part of its argument by introducing a scaling parameter, $\alpha > 0$ \cite{ref:xu:2015}.
+Similar to \acs{ReLU}, \acs{LReLU} is not susceptible to the \index{vanishing gradients problem}vanishing gradients problem.
+However, \acs{LReLU} does not suffer from the \index{dying ReLU problem}dying \acs{ReLU} problem \cite{ref:agarap:2018}, which occurs when the neurons that use \acs{ReLU} \index{activation functions}activation functions become \textit{inactive} and only output $0$ due to a negative net input signal.
+The \acs{LReLU} \index{activation function}activation function is defined in Equation \eqref{eq:leaky_relu} below.
 
@@
     \begin{cases}
-        net - \theta & \text{if $net \geq \theta $}\\
-        \alpha(net - \theta) & \text{otherwise}\\
+        net - \theta         & \text{if $net \geq \theta $} \\
+        \alpha(net - \theta) & \text{otherwise}             \\
     \end{cases}
@@
 \noindent
-By introducing a parameter $\alpha >
-0$, negative \index{Net Input Signals}net input signals will still yield
-non-zero activations, resulting in non-zero gradients and avoiding gradient
-saturation. Non-zero gradients are required by some heuristics such as
-\ac{SGD} in order to be able to effectively train \acp{ANN}
-\cite{ref:hanin:2018}.
-
-An illustration of the \ac{LReLU} with various values for $\alpha$ and $\theta =
-0$ is given in Figure \ref{fig:anns:activation_functions:leaky_relu}.
+By introducing a parameter $\alpha > 0$, negative \index{Net Input Signals}net input signals will still yield non-zero activations, resulting in non-zero gradients and avoiding gradient saturation.
+Non-zero gradients are required by some heuristics such as \ac{SGD} in order to be able to effectively train \acp{ANN} \cite{ref:hanin:2018}.
+An illustration of \acs{LReLU} with various values for $\alpha$ and $\theta = 0$ is given in Figure \ref{fig:anns:activation_functions:leaky_relu}.
 
@@
     \centering
-    \input{./plots/leaky_relu.tex}
-    \caption[The \ac{LReLU} \index{activation function}activation function]{An illustration of the
-    \acs{LReLU} \index{activation function}activation function.}
+    \includegraphics[width=0.8\textwidth]{lrelu.pdf}
+    \caption[The \ac{LReLU} \index{activation function}activation function]{An illustration of the \acs{LReLU} \index{activation function}activation function with various values for $\alpha$ and $\theta = 0$.}
     \label{fig:anns:activation_functions:leaky_relu}
@@
 
-\subsubsection{Sigmoid}
-\label{sec:anns:an:act_functions:sigmoid}
+\subsubsection{Sigmoid}\label{sec:anns:an:act_functions:sigmoid}
 
-\index{sigmoid}Sigmoid is a very popular \index{activation function}activation
-function, because it is a continuous differentiable approximation of the step function, which was used in the original perceptron model developed by \citeauthor{ref:rosenblatt:1957} \cite{ref:rosenblatt:1957}.
-The
-\index{sigmoid}sigmoid \index{activation function}activation function is defined
-as:
+The \index{sigmoid}sigmoid activation is the continuous differentiable approximation of the step function, which was used in the original perceptron model developed by \citeauthor{ref:rosenblatt:1957} \cite{ref:rosenblatt:1957}, and yields output in the range $(0, 1)$.
+The \index{sigmoid}sigmoid \index{activation function}activation function is defined in Equation \eqref{eq:sigmoid} below.
 
@@
 
-\noindent where $\lambda$ is a control parameter, which controls the steepness
-of the function and is usually set to $\lambda = 1$.  \noindent The
-\index{sigmoid}sigmoid \index{activation function}activation function is a
-continuous variant of the ramp function and yields $f_{AN} \in (0,1)$.
-
-An illustration of the \index{sigmoid}sigmoid \index{Activation
-Function}activation function with various values for $\lambda$ and $\theta = 0$
-is given in Figure \ref{fig:anns:activation_functions:sigmoid}.
+\noindent
+In Equation \eqref{eq:sigmoid} above, $\lambda$ is a control parameter, which controls the steepness of the sigmoid activation function and is usually set to $\lambda = 1$.
+An illustration of the \index{sigmoid}sigmoid \index{Activation Function}activation function with various values for $\lambda$ and $\theta = 0$ is given in Figure \ref{fig:anns:activation_functions:sigmoid}.
 
@@
     \centering
-    \resizebox{0.8\textwidth}{!}{\input{./plots/sigmoid.tex}}
-    \caption[The \index{sigmoid}sigmoid \index{activation function}activation
-    function]{An illustration of the \index{sigmoid}sigmoid \index{Activation
-    Function}activation function.}
+    \includegraphics[width=0.8\textwidth]{sigmoid.pdf}
+    \caption[The \index{sigmoid}sigmoid \index{activation function}activation function]{An illustration of the \index{sigmoid}sigmoid \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$.}
     \label{fig:anns:activation_functions:sigmoid}
@@
 
-\subsubsection{Hyperbolic Tangent}
-\label{sec:anns:an:act_functions:tanh}
+\subsubsection{Hyperbolic Tangent}\label{sec:anns:an:act_functions:tanh}
 
-The \index{hyperbolic tangent}hyperbolic tangent \index{activation
-function}activation function is similar to the \index{sigmoid}sigmoid
-\index{activation function}activation function, but yields output in the range
-$(-1, 1)$. The \index{hyperbolic tangent}hyperbolic tangent
-\index{activation function}activation function is defined as:
+The \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function has a similar shape to that of the \index{sigmoid}sigmoid \index{activation function}activation function, but yields output in the range $(-1, 1)$.
+The \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function is given in Equation \eqref{eq:hyperbolic_tangent} below.
 
@@
 
-\noindent The \index{hyperbolic tangent}hyperbolic tangent \index{activation
-function}activation function with various values for $\lambda$ and $\theta = 0$
-is given in Figure \ref{fig:anns:activation_functions:hyperbolic_tangent}.
+\noindent
+An illustration of the \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$ is given in Figure \ref{fig:anns:activation_functions:hyperbolic_tangent}.
 
@@
     \centering
-    \resizebox{0.8\textwidth}{!}{\input{./plots/tanh.tex}}
-    \vspace{10pt}
-    \caption[The \index{hyperbolic tangent}hyperbolic tangent \index{Activation
-        Function}activation function]{An illustration of the \index{Hyperbolic
-    Tangent}hyperbolic tangent \index{activation function}activation function.}
+    \includegraphics[width=0.8\textwidth]{tanh.pdf}
+    \caption[The \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function]{An illustration of the \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$.}
     \label{fig:anns:activation_functions:hyperbolic_tangent}
@@
 
-\subsection{Output}
-\label{sec:anns:an:output}
+\subsection{Output}\label{sec:anns:an:output}
 
-Output signals are $K$-dimensional vectors of numerical values that are produced
-by the \index{activation function}activation function. Output signals are often
-referred to as \textit{predictions}. If target pre-processing was applied, it is
-necessary to post-process the output data. A brief discussion on post-processing
-techniques follows.
+Output signals are numerical values that represent the output of the \acs{AN}'s \index{activation function}activation function.
+Output signals are often referred to as \textit{predictions}.
+Output values need to be post-processed to ensure the practical application of the \ac{AN}.
 
-\subsubsection{Output Post-Processing}
-\label{sec:anns:an:output:output_post_processing}
+\subsubsection{Output Post-Processing}\label{sec:anns:an:output:output_post_processing}
 
-Output post-processing is necessary in order to convert data back to their
-original ranges. The post-processing techniques that are applicable depend on
-the type of problem (regression or classification), input pre-processing
-techniques used, as well as the \index{activation function}activation function
-used. For the purposes of this dissertation, only data decoding, normalisation and
+Output post-processing converts output values to ranges that better match that of the target values.
+The post-processing techniques that are applicable depend on the type of problem (regression or classification), pre-processing techniques used, as well as the \index{activation function}activation function used.
+For the purposes of this dissertation, data decoding, normalisation and
 re-scaling techniques are considered.
 
-\subsubsection{Decoding}
-\label{sec:anns:an:output:decoding}
+\subsubsection{Decoding}\label{sec:anns:an:output:decoding}
 
-Data decoding is used to convert \index{One-Hot Encoding}one-hot encoded vectors
-as described in Section~\ref{sec:anns:an:input:encoding} back to class labels.
-This is relevant to classification problems where the predicted output is a
-\index{One-Hot Encoding}one-hot encoded vector representing a class label.
+Data decoding refers to the process of undoing the encoding process.
+For min-max scaling, data is converted back to the range $(x_{min}, x_{max})$.
+In the context of an \acs{AN}, binary logistic regression problems maps the output to the positive or negative class, usually separating the class decision boundary using a threshold value $\tau$.
+In the context of multiple \acp{AN}' output, the output is a vector of numerical values.
+The one-hot encoded output is then decoded by mapping the index of the output vector that yields the highest activation (argmax) to its associated class.
 
-The high value (represented by $1$) at $y_k$ is used to decode the
-\index{One-Hot Encoding}one-hot encoded output vector $\vec{y}$ back to its
-corresponding class label.
+\subsubsection{Softmax}\label{sec:anns:an:output:softmax}
 
-Normalisation of the output data is used to simplify the decoding process. This
-dissertation considers \index{softmax}\textit{softmax} and
-\index{Argmax}\textit{argmax} normalisation to assist the decoding process.
-
-\subsubsection{Softmax}
-\label{sec:anns:an:output:softmax}
-
-The \index{softmax}softmax function, also known as the
-\index{softargmax}\textit{softargmax} \cite[p.~184]{ref:goodfellow:2016} or
-\index{normalised exponential function}\textit{normalised exponential function}
-\cite{ref:bishop:2006} is a generalisation of the logistic function that
-converts the $K$-dimensional output vector $\vec{y}$ into a $K$-dimensional
-output vector $\vec{y^{'}}$ where each element $y^{'}_k$ is in the range $(0,1)$
-and all elements sum up to $1$. This is expressed as follows:
+The \index{softmax}softmax function, also known as the \index{softargmax}\textit{softargmax} \cite[p.~184]{ref:goodfellow:2016} or \index{normalised exponential function}\textit{normalised exponential function} \cite{ref:bishop:2006} is a generalisation of the logistic function that converts a $K$-dimensional output vector $\vec{y}$ into a $K$-dimensional output vector $\vec{y^{'}}$ where each element $y^{'}_k$ is in the range $(0,1)$ and all elements sum up to $1$ as is shown in Equation \eqref{eq:sum_after_softmax} below.
 
@@
 
-\noindent The softmax function is given as:
+\noindent
+The softmax function is then given in Equation \eqref{eq:softmax} below.
 
@@
 
-\subsubsection{Argmax}
-\label{sec:anns:an:output:argmax}
+\subsubsection{Argmax}\label{sec:anns:an:output:argmax}
 
-The \index{Argmax}argmax function is similar to the \index{softmax}softmax
-function, with the difference that the element $y_k, k \in \{1,2, \dots, K\}$
-with the highest output value is set to $1$ and the rest are set to $0$. This
-means that all elements still sum to $1$, but the activation is only observed at
-index $k$ where the activation is $1$.
-
-The \index{Argmax}argmax function is given as:
+The \index{Argmax}argmax function is similar to the \index{softmax}softmax function, with the difference that the element $y_k, k \in \{1,2, \dots, K\}$ with the highest output value is set to $1$ and the rest are set to $0$.
+All elements still sum to $1$, but the activation is only observed at index $k$ where the activation is $1$.
+The \index{Argmax}argmax function is given in Equation \eqref{eq:argmax} below.
 
@@
     \begin{cases}
-        1 & \text{if $y_k = \max(y_1, y_2, \dots, y_K)$}\\
+        1 & \text{if $y_k = \max(y_1, y_2, \dots, y_K)$} \\
         0 & \text{otherwise}
@@
 
-\noindent Figure \ref{fig:anns:activation_functions:softmax_argmax} illustrates the comparison of
-transformations of the output vector $\vec{y}$, where the
-\index{sigmoid}sigmoid, the \index{softmax}softmax and the \index{argmax}argmax
-\index{activation function}activation functions are used.
+\noindent
+Figure \ref{fig:anns:activation_functions:softmax_argmax} illustrates the comparison of transformations of the output vector $\vec{y}$, where the \index{sigmoid}sigmoid, the \index{softmax}softmax and the \index{argmax}argmax \index{activation function}activation functions are used.
 
@@
     \centering
-    \resizebox{0.8\textwidth}{!}{\input{./plots/output_modifiers.tex}}
-    \caption[The results of \index{softmax}softmax and \index{Argmax}argmax]{An
-        illustration of \index{softmax}softmax and \index{Argmax}argmax applied
-    after the \index{sigmoid}sigmoid \index{activation function}activation function.}
+    \includegraphics[width=0.75\textwidth]{output_modifiers.pdf}
+    \caption[The results of \index{softmax}softmax and \index{Argmax}argmax]{An illustration of \index{softmax}softmax and \index{Argmax}argmax applied after the \index{sigmoid}sigmoid \index{activation function}activation function.}
     \label{fig:anns:activation_functions:softmax_argmax}
@@
 
-\section{Artificial Neural Network}
-\label{sec:anns:ann}
+\section{Artificial Neural Network} \label{sec:anns:ann}
 
-This section presents \acp{ANN}. Discussions follow on their applications,
-architecture, and topologies. Finally, a specific type of \ac{ANN} called a
-\acl{FFNN} is discussed in detail.
+Multiple \acp{AN} can be organised and used together forming a ``network'' of \acp{AN} referred to as an \acf{ANN}.
+This section presents \acp{ANN} and discussions follow on their applications, architecture, and topologies.
+Specific reference is made to \acf{FFNN}, a specific type of \acs{AN} used in this dissertation.
 
-\subsection{Applications}
-\label{sec:anns:anns:applications}
+\subsection{Applications} \label{sec:anns:anns:applications}
 
-\acp{ANN} are modelled after our biological brains. The human brain is
-biologically and chemically incredibly sophisticated. Trying to model an entire
-brain is at this stage not computationally feasible. \citeauthor{ref:sandberg:2008}
-\cite{ref:sandberg:2008} approximates a computational requirement of 256 000
-terabytes/s to emulate the entire brain. Despite our shortage in hardware
-capabilities, \acp{ANN} have been successfully applied to a range of problem
-classes. \citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} summarises some common problems
-that are solved using \acp{ANN}. These include:
+\acp{ANN} are inspired by the biological brain.
+Our brains model biological neural networks with neuron counts in the hundreds of billions and synapse counts in the trillions.
+To emulate the computational capability of the human brain is not yet possible on modern day hardware.
+\citeauthor{ref:sandberg:2008} \cite{ref:sandberg:2008} approximates a computational requirement of 256 000 terabytes/s to emulate the entire brain.
+Despite our shortage in hardware capabilities, \acp{ANN} have been successfully applied to a range of problem classes.
+\citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} summarises some common problems that are solved using \acp{ANN} and can be listed as follows.
 
 \begin{itemize}
-    \item
-    \textbf{Classification}: Predicting the class of an input vector
-    \cite{ref:khan:2001}.
+    \item \textbf{Classification}: Predicting the class of an input vector \cite{ref:khan:2001}.
 
-    \item
-    \textbf{Pattern Matching}: Producing closely associated patterns based on an
-    input vector \cite{ref:cannady:1998, ref:kumar:1994}.
+    \item \textbf{Pattern Matching}: Producing closely associated patterns based on an input vector \cite{ref:cannady:1998, ref:kumar:1994}.
 
-    \item
-    \textbf{Pattern Completion}: Completing the missing parts of an input vector
-    \cite{ref:dayhoff:2001}.
+    \item \textbf{Pattern Completion}: Completing the missing parts of an input vector \cite{ref:dayhoff:2001}.
 
-    \item
-    \textbf{Optimisation}: Producing optimal values of parameters in a
-    optimisation problems \cite{ref:specht:1991}.
+    \item \textbf{Optimisation}: Producing optimal values of parameters in a optimisation problems \cite{ref:specht:1991}.
 
-    \item
-    \textbf{Data Mining}: Feature discovery in large datasets
-    \cite{ref:singh:2009}.
+    \item \textbf{Data Mining}: Feature discovery in large datasets \cite{ref:singh:2009}.
 \end{itemize}
 
-Different \acp{ANN} are built for different types of problems, however, most
-applications of \acp{ANN} include some layered architecture. Discussions follow
-on \ac{ANN} architecture and topologies.
+\noindent
+The composition of \acp{AN} in an \ac{ANN} is expressed as the \textit{architecture} and \textit{topology} of the \ac{AN}. The exact composition to use depends on the problem being solved.
 
-\subsection{Architecture}
-\label{sec:anns:anns:architecture}
+\subsection{Architecture} \label{sec:anns:anns:architecture}
 
-\acp{ANN} are collections of \acp{AN} that are organised together to form a
-connected network. The architecture of the \ac{ANN} refers to the way in which
-these \acp{AN} are organised together as well as the type of \index{Activation
-Function}activation function used.
+The architecture of the \ac{ANN} refers to the way in which \acp{AN} are organised.
+\acp{ANN} can be organised in layers where a single layer can contain multiple \acp{AN}.
+Generally, each layer makes use of the same \index{activation function}activation function.
+Output from one layer is propagated as input to the next layer.
+This dissertation focuses on the simplest architecture, containing three particular layers, including the input, hidden and output layers.
+\acp{ANN} with this type of architecture are usually referred to as \textit{shallow} \acp{NN}.
+A description of each layer is given as follows.
 
-\acp{ANN} are organised in layers where a single layer can contain multiple
-\acp{AN}. Generally, each layer makes use of the same \index{activation
-function}activation function, but this is not a requirement. Output from one
-layer is propagated as input to the next layer. This dissertation focuses on the
-simplest architecture, containing three particular layers, including the input,
-hidden and output layers. \acp{ANN} with this type of architecture are usually
-referred to as \textit{shallow} \acp{NN}. The input, hidden and output layers
-are discussed next.
+\subsubsection{Input Layer}\label{sec:anns:anns:architecture:input}
 
-The input layer contains the input data to the \ac{ANN}. Since the
-input layer simply provides the input data, some literature does not consider
-the input layer as a layer \cite{ref:engelbrecht:2007}.
+The input layer contains the input data to the \ac{ANN}.
+Since the input layer simply provides the input data, some literature do not consider the input layer as an actual part of the \ac{ANN} \cite{ref:engelbrecht:2007}.
 
-The hidden layer contains a collection of hidden \acp{AN}. These hidden \acp{AN}
-are referred to as \textit{hidden units} or \textit{nodes}. Hidden units are
-used if the target data is not linearly separable \cite{ref:engelbrecht:2007}.
-It has been shown that \acp{ANN} that incorporate monotonically increasing
-differentiable \index{activation function}activation functions can approximate
-any continuous function with just one hidden layer, given that the hidden layer
-has enough hidden units \cite{ref:hornik:1989}.
+\subsubsection{Hidden Layer}\label{sec:anns:anns:architecture:hidden}
 
-The output layer contains the activations or the predictions of the \ac{ANN}.
-This layer is used to analyse the accuracy of the prediction and thus the
-performance of the \ac{ANN}.
+The hidden layer contains a collection of ``hidden'' \acp{AN}, also referred to as \textit{hidden units} or \textit{nodes}.
+Hidden units are used if the target data is not linearly separable \cite{ref:engelbrecht:2007}.
+It has been shown that \acp{ANN} that incorporate monotonically increasing differentiable \index{activation function}activation functions can approximate any continuous function with just one hidden layer, given that the hidden layer has enough hidden units \cite{ref:hornik:1989}.
+
+\subsubsection{Output Layer}\label{sec:anns:anns:architecture:output}
+
+The output layer contains the activations or the predictions of the \ac{ANN} and is used to measure the accuracy of the predictions of the \ac{ANN}.
 
@@
 
-The topology of the \ac{ANN} refers to the way \acp{AN} are connected to each
-other. Since \acp{AN} are organised in layers, this connectivity is described
-layer by layer.
+The topology of the \ac{ANN} refers to the way that layers of \acp{AN} are connected to each other.
+There are many different topologies \cite{ref:miikkulainen:2010}.
+For the purposes of this dissertation focus is put on a \index{fully connected topology}\textit{fully connected} topology where each \ac{AN} in one layer is connected to all \acp{AN} in the next, without any cycles \cite{ref:zell:1994}.
 
-There are many different topologies \cite{ref:miikkulainen:2010}, however, this
-dissertation only focuses on a \index{fully connected topology}fully connected
-topology.
+\subsection{Feedforward Neural Networks}\label{sec:anns:anns:ffnns}
 
-The most common and simplest topology is where each \ac{AN} in one layer is
-connected to all \acp{AN} in the next. Fully connected topologies have no
-cycles \cite{ref:zell:1994}.
-
-\subsection{Feedforward Neural Networks}
-\label{sec:anns:anns:ffnns}
-
-There are many different types of \acp{ANN}. All \acp{ANN} can be described
-in terms of their architecture and topology. This research will focus on a
-particular \ac{ANN} called a \acl{FFNN} (\acs{FFNN}).
-
-\acp{FFNN} were the first and simplest \acp{ANN} developed
-\cite{ref:schmidhuber:2015}. \acp{FFNN} incorporate the basic layers (input,
-hidden and output layers) by arranging them in sequential order. In \acp{FFNN}
-information moves forward, in one direction, from the input nodes, through the
-hidden nodes and finally to the output nodes, and, depending on the optimisation
-algorith used, error correction information can be backpropagated through the
-network. It can be said that input is \textit{fed} forward, through the
-\ac{ANN}. The \index{activation function}activation function used is problem
-dependent. \acp{FFNN} incorporate fully connected topologies amongst the layers
-such that no cycles form \cite{ref:zell:1994}.
-
-An illustration of a \ac{FFNN} using a three-layered architecture and a fully
-connected topology is given in Figure \ref{fig:ffnn}.
+\acp{FFNN} were the first and simplest type of \acp{ANN} developed \cite{ref:schmidhuber:2015} and implement input, hidden and output layers by arranging them in sequential order.
+Furthermore, \acp{FFNN} implement \index{fully connected topology}fully connected topologies.
+In \acp{FFNN} , information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
+Depending on the optimisation algorithm used, error correction information can be ``backpropagated'' through the network.
+An illustration of a \ac{FFNN} is given in Figure \ref{fig:ffnn} below.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{feedforward_neural_network.eps}
-    \caption[A \index{Feedforward Neural Network}Feedforward neural network]{An
-    illustration of a \index{Feedforward Neural Network}feedforward neural network.}
+    \includegraphics[width=0.98\textwidth]{feedforward_neural_network.pdf}
+    \caption[A \index{feedforward neural network}Feedforward neural network]{An illustration of a \index{Feedforward Neural Network}feedforward neural network implementing input, hidden and output layers using a fully connected topology.}
     \label{fig:ffnn}
@@
 
-In Figure~\ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input
-vector $\vec{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer,
-$y_k$ refers to the $k$-th dimension in the output vector $\vec{y}$, $v_{i,j}$
-refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the
-output node $y_k$.
+In Figure \ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input vector $\vec{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer, $y_k$ refers to the $k$-th dimension in the output vector $\vec{y}$, $v_{i,j}$ refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the output node $y_k$.
 
-With the layered architecture and \index{fully connected topology}fully
-connected topology of \acp{FFNN}, and assuming the use of \acp{SU}, the output
-for the \ac{FFNN} at index $k$, denoted $y_k$, is calculated using:
+Assuming the use of \acp{SU} and bias weights, the output for the \ac{FFNN} at index $k$, denoted $y_k$, is calculated as is shown in Equation \eqref{eq:ffnn} below.
 
@@
 
-\noindent The remainder of this dissertation makes use of \acp{FFNN} as the \ac{ANN}
-of interest, sometimes referred to as \textit{the model}.
+\noindent
+The remainder of this dissertation makes use of \acp{FFNN} and is sometimes referred to as \textit{the model}.
 

### 2022-10-13 dissertation/chapters/01-introduction.tex
✨ (disseration): Chapter 2 - Done

@@
 A search algorithm known as a \index{heuristic}\textit{heuristic} \cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.
-The research presented in this disseration focuses on the development of a specific type of heuristic, called a \acl{HH} to train \acp{FFNN} in a supervised learning approach.
+The research presented in this disseration focuses on the development of a specific type of heuristic, called a \acf{HH} to train \acp{FFNN} in a supervised learning approach.
 
@@
 \acp{FFNN} training is seen as a computational search problem.
-\Acl{HH} as defined by Burke et al.
+\acf{HH} as defined by Burke et al.
 \cite{ref:burke:2010} is ``a search method or learning mechanism for selecting or generating heuristics to solve computational search problems''.
@@
       \item A novel heuristic selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acp{FFNN}.
-The resulting \ac{HH} is referred to as the \Acl{BHH}.
+The resulting \ac{HH} is referred to as the \acf{BHH}.
 
@@
 \begin{itemize}
-      \item \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN} and the various components that make up an \acl{AN}.
+      \item \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN} and the various components that make up an \acf{AN}.
 The focus is on training of \acp{FFNN}.

### 2022-10-13 dissertation/chapters/02-artificial-neural-networks.tex
✨ (disseration): Chapter 2 - Done

@@
 It gives us the ability to think and learn.
-The field of \ac{ML} has taken a lot of inspiration from the biological brain which lead to the development of \acp{ANN} \cite{ref:rosenblatt:1958}.
+The field of \acs{ML} has taken a lot of inspiration from the biological brain which lead to the development of \acp{ANN} \cite{ref:rosenblatt:1958}.
 \acp{ANN} are used throughout this dissertation as the \textit{model} to be trained using \acp{HH}.
 
-The purpose of this chapter is to provide the necessary background information needed on \acp{ANN} and is thus structured into the following sections.
+The purpose of this chapter is to provide the necessary background information needed on \acp{ANN} and is structured as follows.
 
 \begin{itemize}
-    \item \textbf{Section \ref{sec:anns:bn}} gives background information on the \ac{BN}.
+    \item \textbf{Section \ref{sec:anns:bn}} gives background information on the \acs{BN}.
 
-    \item \textbf{Section \ref{sec:anns:an}} introduces the \ac{AN}.
-Brief discussions follow on input, \index{weights}weights, \index{biases}biases, \index{net input signal}net input signal, \index{activation functions}activation functions, and output.
+    \item \textbf{Section \ref{sec:anns:an}} introduces the \acs{AN}.
+Brief discussions follow on input, \index{weights}weights and \index{biases}biases, \index{net input signal}net input signal, \index{activation function}activation functions, and output.
 
-    \item \textbf{Section \ref{sec:anns:ann}} introduces the \ac{ANN}. Brief discussions follow on \ac{ANN} architecture, topology, and \acp{FFNN}.
+    \item \textbf{Section \ref{sec:anns:ann}} introduces the \acs{ANN}. Brief discussions follow on \acs{ANN} architecture, topology, and \acp{FFNN}.
 
-    \item \textbf{Section \ref{sec:anns:training}} provides details on the training process, training sets, \index {supervised learning}supervised learning, \index{error function}error functions, performance measures and stopping conditions.
+    \item \textbf{Section \ref{sec:anns:training}} provides details on the training process, \index {supervised learning}supervised learning, training sets, stopping conditions, performance measures and \index{error function}error functions.
 
@@
 
-\index{Biological Neuron}
+\index{biological neuron}
 \section{Biological Neuron}\label{sec:anns:bn}
 
-This section introduces the \ac{BN} and provides the necessary background information that show how the \ac{BN} has inspired the development of the \ac{AN}.
-
-The biological neural systems are made up of microscopic nerve cells called neurons \cite{ref:jain:1996}. Figure \ref{fig:biological_neuron} illustrates a single \ac{BN}.
+This section introduces the \acs{BN} and provides the necessary background information that show how the \acs{BN} has inspired the development of the \acs{AN}.
 
@@
 \noindent
-The main components of the \ac{BN} include the cell body, \index{dendrites}\textit{dendrites} and the \index{axon}\textit{axon}.
-\Acp{NN} are formed through the connections between the \index{axons}axons and \index{dendrites}dendrites of various neurons.
+The biological neural systems are made up of microscopic nerve cells called neurons \cite{ref:jain:1996}.
+Figure \ref{fig:biological_neuron} illustrates a single \acs{BN}.
+The main components of the \acs{BN} include the cell body, \index{dendrites}\textit{dendrites} and the \index{axon}\textit{axon}.
+\Acp{NN} are formed through the connections between the \index{axon}axons and \index{dendrites}dendrites of various neurons.
 This is known as \index{synaptogenesis}\textit{synaptogenesis} \cite{ref:huttenlocher:1997}.
@@
 Kennedy \cite{ref:kennedy:2016} defines stronger \index{synapse}synapses as ones that contribute more depolarisation to the neural membrane upon activation than weaker ones.
-Stronger \index{Synapse}synapses have a higher probability of generating an action potential in the post-synaptic neuron.
+Stronger \index{synapse}synapses have a higher probability of generating an action potential in the post-synaptic neuron.
 During activation, the pre-synaptic neuron release neurotransmitters that bind to the post-synaptic neuron \cite{ref:khanacademy:synapse}.
@@
 
-\index{Artificial Neuron}
+\index{artificial neuron}
 \section{Artificial Neuron}\label{sec:anns:an}
 
-This section introduces the \ac{AN}.
-Brief discussion follow on the various components that make up the \ac{AN}.
-These components include inputs, weights, biases, \index{net input signal}net input signal, and output of the \ac{AN}.
+This section introduces the \acs{AN}. Brief discussion follow on the various components that make up the \acs{AN}.
 
-\subsection{Components}\label{sec:anns:components}
-
-The \ac{AN} implements a nonlinear mapping from $\mathbb{R}^{I}$ to
+The \acs{AN} implements a nonlinear mapping from $\mathbb{R}^{I}$ to
 $\mathbb{R}^{T}$, usually in the ranges $[0,1]$ or $[-1,1]$, depending on the
 activation function used \cite{ref:engelbrecht:2007} and is given
-in Equation \eqref{eq:an_function_mapping} below.
+in Equation~\eqref{eq:an_function_mapping} below.
 
@@
 \noindent
-In Equation \eqref{eq:an_function_mapping} above, $f_{AN}$ is the mapping function produced by the \ac{AN}, $I$ is the total number of dimensions of the input in real-number space ($\mathbb{R}$), and $T$ is the total number of dimensions of the target (desired output) in real-number space.
+In Equation~\eqref{eq:an_function_mapping} above, $f_{AN}$ is the mapping function produced by the \acs{AN}, $I$ is the total number of dimensions of the input in real-number space ($\mathbb{R}$), and $T$ is the total number of dimensions of the target (desired output) in real-number space.
 
-The \ac{AN} implements various components and is illustrated in Figure \ref{fig:artificial_neuron}.
+The \acs{AN} implements various components and is illustrated in Figure \ref{fig:artificial_neuron}.
 
@@
 \noindent
-Each of the components of the \ac{AN} is inspired by some element of the \ac{BN}. Brief descriptions of these are given as follows.
+Each of the components of the \acs{AN} is inspired by some element of the \acs{BN}. Brief descriptions of these are given as follows.
 
@@
 
-    \item \textbf{Biases:} The biases model a mechanism introduced to influence the strength of the activation (output signal) of the \index{AN}\ac{AN}.
+    \item \textbf{Biases:} The biases model a mechanism introduced to influence the strength of the activation (output signal) of the \acs{AN}.
 The bias is represented by $\theta$, in Figure \ref{fig:artificial_neuron}.
 
-    \item \index{activation function}\textbf{Activation function:} The activation function models the action potential of the \ac{BN}\index{BN} based on the net input signal.
+    \item \index{activation function}\textbf{Activation function:} The activation function models the action potential of the \acs{BN} and is based on the net input signal.
 The \index{activation function}activation function is represented by $f$, in Figure \ref{fig:artificial_neuron}.
@@
 Input signals are often referred to as \index{features}\textit{features} or \index{independent variables}\textit{independent variables} \cite{ref:francis:2001}.
-Throughout this dissertation, a single input vector is referred to as a pattern.
-Input data must first be pre-processed before it is presented to the \ac{AN}.
+Throughout this dissertation, a single input vector is referred to as a \textit{pattern}.
+Input data must first be pre-processed before it is presented to the \acs{AN}.
 Input pre-processing techniques are presented in the following sections.
@@
 
-Input pre-processing improves the training process and contributes to the success of the practical application of the \ac{ANN} \cite{ref:kuzniar:2017}.
+Input pre-processing improves the training process and contributes to the success of the practical application of the \acs{ANN} \cite{ref:kuzniar:2017}.
 The primary purpose of input pre-processing is to modify the input data so that it can better match predicted output data.
 There are many techniques to consider when pre-processing input data.
-These techniques includes methods to encode data to certain formats, to scale to the correct ranges and to deal with incomplete, invalid or irrelevant data.
-For the purposes of this dissertation, only \textit{data encoding} and \textit{normalisation} is considered.
+These techniques include methods to encode data to certain formats, to scale to the correct ranges and to deal with incomplete, invalid or irrelevant data.
+For the purposes of this dissertation, \textit{data encoding} and \textit{normalisation} techniques are considered.
 
-\index{Encoding}
+\index{encoding}
 \subsubsection{Encoding}\label{sec:anns:an:input:encoding}
 
-For qualitative data such as categories, the class labels have to be converted from textual to numerical representations.
+For qualitative data, the class labels have to be converted from textual to numerical representations.
 In general, class labels are encoded as numerical vectors \cite{ref:srinidhi:2018, ref:brownlee:2017:one-hot}.
 One such encoding technique is referred to as \index{one-hot encoding}\textit{one-hot encoding}.
-Harris and Harris \cite{ref:harris:2010} describe \index{One-Hot Encoding}one-hot encoding as a group of vector elements where the classes are represented with a single high element (represented by $1$) and all the others low (represented by $0$).
+Harris and Harris \cite{ref:harris:2010} describe \index{one-hot encoding}one-hot encoding as a group of vector elements where the classes are represented with a single high element (represented by $1$) and all the others low (represented by $0$).
 Each element $y_k$, where $k$ is the $k$-th element of the encoded vector $\vec{y}$, uniquely refers to a class.
@@
 
-\index{Normalisation}
+\index{normalisation}
 \subsubsection{Normalisation}\label{sec:anns:an:input:normalisation}
 
-Numerical data must be normalised and scaled appropriately for the \ac{AN}.
-In general, input data is normalised to a range that is appropriate for the \index{activation function}activation function being used by the \ac{AN}.
-Normalisation and scaling yields input data that is comparable to the output produced by the \ac{AN}.
-For the purposes of this disseration, \index{min-max scaler}min-max scaler \cite{ref:al:2006} and \index{standard score scaler}standard score scaler \cite{ref:jain:2005} are considered.
+Numerical data must be normalised and scaled appropriately for the \acs{AN}.
+In general, input data is normalised to a range that is appropriate for the \index{activation function}activation function being used by the \acs{AN}.
+Normalisation and scaling yields input data that is comparable to the output produced by the \acs{AN}.
+For the purposes of this disseration, the \index{min-max scaler}min-max scaler \cite{ref:al:2006} and the \index{standard score scaler}standard score scaler \cite{ref:jain:2005} are considered.
 
-\index{Min-Max Scalar}
+\index{min-max scaler}
 \subsubsection{Min-Max Scaler}\label{sec:anns:an:input:min_max_scaler}
@@
 The \index{min-max scaler}min-max scaler is used as a pre-processing technique for target values when the \index{sigmoid}\textit{sigmoid} \index{activation function} activation function is used.
-The \index{min-max scaler}min-max scaler is given in Equation \eqref{eq:min_max_scaler} below.
+The \index{min-max scaler}min-max scaler is given in Equation~\eqref{eq:min_max_scaler} below.
 
@@
 \noindent
-In Equation \eqref{eq:min_max_scaler} above, $x_{i,p}^{'}$ is the normalised form of $x_{i,p}$, the $i$-th dimension of the input vector $\vec{x}_p$, $p \in \{1,2, \dots, P \}$, where $P$ is the total number of input patterns, $x_{i_{min}}$ and $x_{i_{max}}$ are respectfully the minimum and maximum values of the $i$-th dimension for all input vectors $\vec{x}_p$.
+In Equation~\eqref{eq:min_max_scaler} above, $x_{i,p}^{'}$ is the normalised form of $x_{i,p}$, the $i$-th dimension of the input vector $\vec{x}_p$, $p \in \{1,2, \dots, P \}$, where $P$ is the total number of input patterns, $x_{i_{min}}$ and $x_{i_{max}}$ are respectfully the minimum and maximum values of the $i$-th dimension for all input vectors $\vec{x}_p$.
 
-\index{Standard Score Scalar}
+\index{standard score scaler}
 \subsubsection{Standard Score Scaler}\label{sec:anns:an:input:standard_score_scaler}
@@
 The \index{standard score scaler}standard score scaler is used as a pre-processing technique for target values when the \index{hyperbolic tangent}\textit{hyperbolic tangent} \index{activation function}activation function\index{activation function} is used.
-The \index{standard score scaler}standard score scaler is given in Equation \eqref{eq:standard_score_scaler} below.
+The \index{standard score scaler}standard score scaler is given in Equation~\eqref{eq:standard_score_scaler} below.
 
@@
 \noindent
-In Equation \eqref{eq:standard_score_scaler} above, $\mu_i$ and $\sigma^2_i$ are respectfully the mean and unit variance of the $i$-th dimension of all input vectors $\vec{x}_p$.
+In Equation~\eqref{eq:standard_score_scaler} above, $\mu_i$ and $\sigma^2_i$ are respectfully the mean and unit variance of the $i$-th dimension of all input vectors $\vec{x}_p$.
 
@@
 
-The connection strength that synapses in the \acs{BN} have is modeled in the \ac{AN} as weight vectors of numerical values associated with each dimension of the input.
+The connection strength that synapses in the \acs{BN} have is modeled in the \acs{AN} as weight vectors of numerical values associated with each dimension of the input.
 Weights can either dampen or strengthen the input by some negative or positive numerical value.
 Changes in the weight associated with a feature changes the influence that that particular feature has on the predicted output.
-Finding the correct value for each weight, such that the \ac{AN} yields optimal output, is an optimisation problem \cite{ref:thierens:1993}.
+Finding the correct value for each weight, such that the \acs{AN} yields optimal output, is an optimisation problem \cite{ref:thierens:1993}.
 Research has shown that weight initialisation plays an important role in the efficient training of \acp{ANN} \cite{ref:thimm:1995}.
 
-\index{Weight Initialisation}
 \subsubsection{Weight Initialisation}\label{sec:anns:an:weights:initialisation}
 
-Weight initialisation is the process by which candidate solutions (represented by the weights of the \ac{AN}) to the problem are ``placed'' in the search-space.
+Weight initialisation is the process by which candidate solutions (represented by the weights of the \acs{AN}) to the problem are ``placed'' in the search-space.
 Weight initialisation influences the speed of convergence, the probability of convergence and the generalisation capabilities of \acp{ANN} \cite{ref:fernandez:2001}.
@@
 
-\index{Weight Initialisation}Weight initialisation is dependent on the \index{activation function}activation function used.
+Weight initialisation is dependent on the \index{activation function}activation function used.
 If weights are initialised as values that are too small, the vanishing gradients problem can occur \cite{ref:hanin:2018}.
@@
 
-\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of \index{random uniform sampling}random uniform sampling whereby $\omega = \sqrt{\frac{6}{fanin + fanout}}$ and \index{$fanin$}$fanin$ is the number of input neurons to the weight vector and \index{$fanout$}$fanout$ is the number of output neurons from the weight vector.
+\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of \index{random uniform sampling}random uniform sampling, whereby $\omega = \sqrt{\frac{6}{fanin + fanout}}$ and $fanin$ is the number of input neurons to the weight vector and $fanout$ is the number of output neurons from the weight vector.
 
-\index{Glorot Normal Sampling}
+\index{Glorot normal sampling}
 \subsubsection{Glorot Normal Sampling}\label{sec:anns:an:weights:glorot_normal_sampling}
@@
 \acp{AN} accumulate the net resulting input signal from all input dimensions into a value called the \index{net input signal}\textit{net input signal}, expressed as $net$.
-This signal is passed to the \index{activation function}activation function, which provokes an artificial action potential in the \ac{AN}.
+This signal is passed to the \index{activation function}activation function, which provokes an artificial action potential in the \acs{AN}.
 
-A common way by which the \index{net input signal}net input signal is calculated is by means of \acp{SU} \cite{ref:engelbrecht:2007}, which compute the \index{net input signal}net input signal as the weighted sum of all input signals as shown in Equation \eqref{eq:summation_units} below.
+A common way by which the \index{net input signal}net input signal is calculated is by means of \acp{SU} \cite{ref:engelbrecht:2007}, which compute the \index{net input signal}net input signal as the weighted sum of all input signals as shown in Equation~\eqref{eq:summation_units} below.
 
@@
 \noindent
-In Equation \eqref{eq:summation_units} above, $x_{i}$ is the $i$-th dimension of the input vector $\vec{x}$, and $v_{i}$ is the $i$-th dimension of the weight vector $\vec{v}$, associated with the given input dimension.
+In Equation~\eqref{eq:summation_units} above, $x_{i}$ is the $i$-th dimension of the input vector $\vec{x}$, and $v_{i}$ is the $i$-th dimension of the weight vector $\vec{v}$, associated with the given input dimension.
 
@@
 A bias/threshold term $\theta$ is introduced to help translate the output of the \index{activation function}activation function \cite{ref:benitez:1997}.
-The value of $\theta$ can be learned during the training process along with the weights of the \ac{ANN}.
+The value of $\theta$ can be learned during the training process along with the weights of the \acs{ANN}.
 In order to simplify equations, the input and weight vectors are augmented such that the input and hidden layers have an additional neuron/unit, called the \textit{bias unit} \cite{ref:engelbrecht:2007}.
@@
 
-The augmented net input signal, that includes the bias unit, has the form $net^{'} = net - \theta$.
-The value of $\theta$ is learned along with the weights such that $\theta = x_{i+1}v_{i+1}$.
-A constant value $x_{i+1} = -1$ can be used.
-The net input signal as given in Equation \eqref{eq:summation_units} then changes as is shown in Equation \eqref{eq:augmented_vectors} below.
+The augmented net input signal, that includes the bias unit, has the form $net^{'} = net - \theta$, with $\theta = x_{i+1}v_{i+1}$.
+A constant value $x_{i+1} = -1$ can be used, meaning that the weight associated with the bias unit, $v_{i+1}$, is optimised along with the other weights during the optimisation process.
+The net input signal as given in Equation~\eqref{eq:summation_units} then changes as is shown in Equation~\eqref{eq:augmented_vectors} below.
 
@@
 
-An \index{activation function}activation function is used to model the action potential of the \index{AN}\ac{AN} \cite{ref:ziv:1994, ref:hodgkin:1952}.
+An \index{activation function}activation function is used to model the action potential of the \acs{AN} \cite{ref:ziv:1994, ref:hodgkin:1952}.
 The \index{activation function}activation function takes as a parameter, the augmented \index{net input signal}net input signal.
@@
 
-In general, activation functions produce a non-linear mapping of $\mathbb{R}^{I}$ to the range $[0,1]$ or $[-1,1]$ as shown in Equations \eqref{eq:an_function_mapping_0_1} and \eqref{eq:an_function_mapping_minus_1_1} below.
+In general, activation functions produce a non-linear mapping of $\mathbb{R}^{I}$ to the range $[0,1]$ or $[-1,1]$ as shown in Equations~\eqref{eq:an_function_mapping_0_1} and~\eqref{eq:an_function_mapping_minus_1_1} below.
 
@@
 
-The \acf{ReLU} \index{activation function}activation function is an \index{activation function}activation function defined in the positive part of its argument and is given in Equation \eqref{eq:relu} below.
+The \acf{ReLU} \index{activation function}activation function is an \index{activation function}activation function defined in the positive part of its argument and is given in Equation~\eqref{eq:relu} below.
 
@@
 \noindent
-An advantage of \acs{ReLU} is that it is not susceptible to the \index{vanishing gradient problem}vanishing gradients problem \cite{ref:xu:2015, ref:maksutov:2018} which occurs when gradients in the first layers of a multi-layer \acs{ANN} approach zero, and have no effect on the training process.
+An advantage of \acs{ReLU} is that it is not susceptible to the \index{vanishing gradients problem}vanishing gradients problem \cite{ref:xu:2015, ref:maksutov:2018} which occurs when gradients in the first layers of a multi-layer \acs{ANN} approach zero, and have no effect on the training process.
 
@@
 Similar to \acs{ReLU}, \acs{LReLU} is not susceptible to the \index{vanishing gradients problem}vanishing gradients problem.
-However, \acs{LReLU} does not suffer from the \index{dying ReLU problem}dying \acs{ReLU} problem \cite{ref:agarap:2018}, which occurs when the neurons that use \acs{ReLU} \index{activation functions}activation functions become \textit{inactive} and only output $0$ due to a negative net input signal.
-The \acs{LReLU} \index{activation function}activation function is defined in Equation \eqref{eq:leaky_relu} below.
+However, \acs{LReLU} does not suffer from the \index{dying ReLU problem}dying \acs{ReLU} problem \cite{ref:agarap:2018}, which occurs when the neurons that use \acs{ReLU} \index{activation function}activation functions become \textit{inactive} and only output $0$ due to a negative net input signal.
+The \acs{LReLU} \index{activation function}activation function is defined in Equation~\eqref{eq:leaky_relu} below.
 
@@
 \noindent
-By introducing a parameter $\alpha > 0$, negative \index{Net Input Signals}net input signals will still yield non-zero activations, resulting in non-zero gradients and avoiding gradient saturation.
-Non-zero gradients are required by some heuristics such as \ac{SGD} in order to be able to effectively train \acp{ANN} \cite{ref:hanin:2018}.
+By introducing a parameter $\alpha > 0$, negative \index{net input signal}net input signals will still yield non-zero activations, resulting in non-zero gradients and avoiding gradient saturation.
+Non-zero gradients are required by some heuristics such as \acs{SGD} in order to be able to effectively train \acp{ANN} \cite{ref:hanin:2018}.
 An illustration of \acs{LReLU} with various values for $\alpha$ and $\theta = 0$ is given in Figure \ref{fig:anns:activation_functions:leaky_relu}.
@@
     \includegraphics[width=0.8\textwidth]{lrelu.pdf}
-    \caption[The \ac{LReLU} \index{activation function}activation function]{An illustration of the \acs{LReLU} \index{activation function}activation function with various values for $\alpha$ and $\theta = 0$.}
+    \caption[The \acs{LReLU} \index{activation function}activation function]{An illustration of the \acs{LReLU} \index{activation function}activation function with various values for $\alpha$ and $\theta = 0$.}
     \label{fig:anns:activation_functions:leaky_relu}
@@
 The \index{sigmoid}sigmoid activation is the continuous differentiable approximation of the step function, which was used in the original perceptron model developed by \citeauthor{ref:rosenblatt:1957} \cite{ref:rosenblatt:1957}, and yields output in the range $(0, 1)$.
-The \index{sigmoid}sigmoid \index{activation function}activation function is defined in Equation \eqref{eq:sigmoid} below.
+The \index{sigmoid}sigmoid \index{activation function}activation function is defined in Equation~\eqref{eq:sigmoid} below.
 
@@
 \noindent
-In Equation \eqref{eq:sigmoid} above, $\lambda$ is a control parameter, which controls the steepness of the sigmoid activation function and is usually set to $\lambda = 1$.
-An illustration of the \index{sigmoid}sigmoid \index{Activation Function}activation function with various values for $\lambda$ and $\theta = 0$ is given in Figure \ref{fig:anns:activation_functions:sigmoid}.
+In Equation~\eqref{eq:sigmoid} above, $\lambda$ is a control parameter, which controls the steepness of the sigmoid activation function and is usually set to $\lambda = 1$.
+An illustration of the \index{sigmoid}sigmoid \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$ is given in Figure \ref{fig:anns:activation_functions:sigmoid}.
 
@@
 The \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function has a similar shape to that of the \index{sigmoid}sigmoid \index{activation function}activation function, but yields output in the range $(-1, 1)$.
-The \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function is given in Equation \eqref{eq:hyperbolic_tangent} below.
+The \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function is given in Equation~\eqref{eq:hyperbolic_tangent} below.
 
@@
 Output signals are often referred to as \textit{predictions}.
-Output values need to be post-processed to ensure the practical application of the \ac{AN}.
+Output values need to be post-processed to ensure the practical application of the \acs{AN}.
 
@@
 
-The \index{softmax}softmax function, also known as the \index{softargmax}\textit{softargmax} \cite[p.~184]{ref:goodfellow:2016} or \index{normalised exponential function}\textit{normalised exponential function} \cite{ref:bishop:2006} is a generalisation of the logistic function that converts a $K$-dimensional output vector $\vec{y}$ into a $K$-dimensional output vector $\vec{y^{'}}$ where each element $y^{'}_k$ is in the range $(0,1)$ and all elements sum up to $1$ as is shown in Equation \eqref{eq:sum_after_softmax} below.
+The \index{softmax}softmax function, also known as the \index{softargmax}\textit{softargmax} \cite[p.~184]{ref:goodfellow:2016} or \index{normalised exponential function}\textit{normalised exponential function} \cite{ref:bishop:2006} is a generalisation of the logistic function that converts a $K$-dimensional output vector $\vec{y}$ into a $K$-dimensional output vector $\vec{y^{'}}$ where each element $y^{'}_k$ is in the range $(0,1)$ and all elements sum up to $1$ as is shown in Equation~\eqref{eq:sum_after_softmax} below.
 
@@
 \noindent
-The softmax function is then given in Equation \eqref{eq:softmax} below.
+The softmax function is then given in Equation~\eqref{eq:softmax} below.
 
@@
 
-The \index{Argmax}argmax function is similar to the \index{softmax}softmax function, with the difference that the element $y_k, k \in \{1,2, \dots, K\}$ with the highest output value is set to $1$ and the rest are set to $0$.
+The \index{argmax}argmax function is similar to the \index{softmax}softmax function, with the difference that the element $y_k, k \in \{1,2, \dots, K\}$ with the highest output value is set to $1$ and the rest are set to $0$.
 All elements still sum to $1$, but the activation is only observed at index $k$ where the activation is $1$.
-The \index{Argmax}argmax function is given in Equation \eqref{eq:argmax} below.
+The \index{argmax}argmax function is given in Equation~\eqref{eq:argmax} below.
 
@@
     \includegraphics[width=0.75\textwidth]{output_modifiers.pdf}
-    \caption[The results of \index{softmax}softmax and \index{Argmax}argmax]{An illustration of \index{softmax}softmax and \index{Argmax}argmax applied after the \index{sigmoid}sigmoid \index{activation function}activation function.}
+    \caption[The results of \index{softmax}softmax and \index{argmax}argmax]{An illustration of \index{softmax}softmax and \index{argmax}argmax applied after the \index{sigmoid}sigmoid \index{activation function}activation function.}
     \label{fig:anns:activation_functions:softmax_argmax}
@@
 \noindent
-The composition of \acp{AN} in an \ac{ANN} is expressed as the \textit{architecture} and \textit{topology} of the \ac{AN}. The exact composition to use depends on the problem being solved.
+The composition of \acp{AN} in an \acs{ANN} is expressed as the \textit{architecture} and \textit{topology} of the \acs{AN}. The exact composition to use depends on the problem being solved.
 
@@
 
-The architecture of the \ac{ANN} refers to the way in which \acp{AN} are organised.
+The architecture of the \acs{ANN} refers to the way in which \acp{AN} are organised.
 \acp{ANN} can be organised in layers where a single layer can contain multiple \acp{AN}.
@@
 
-The input layer contains the input data to the \ac{ANN}.
-Since the input layer simply provides the input data, some literature do not consider the input layer as an actual part of the \ac{ANN} \cite{ref:engelbrecht:2007}.
+The input layer contains the input data to the \acs{ANN}.
+Since the input layer simply provides the input data, some literature do not consider the input layer as an actual part of the \acs{ANN} \cite{ref:engelbrecht:2007}.
 
@@
 
-The output layer contains the activations or the predictions of the \ac{ANN} and is used to measure the accuracy of the predictions of the \ac{ANN}.
+The output layer contains the final activations or the predictions of the \acs{ANN}. These outputs can be used to measure the performance of the \acs{ANN}.
 
@@
 
-The topology of the \ac{ANN} refers to the way that layers of \acp{AN} are connected to each other.
+The topology of the \acs{ANN} refers to the way that layers of \acp{AN} are connected to each other.
 There are many different topologies \cite{ref:miikkulainen:2010}.
-For the purposes of this dissertation focus is put on a \index{fully connected topology}\textit{fully connected} topology where each \ac{AN} in one layer is connected to all \acp{AN} in the next, without any cycles \cite{ref:zell:1994}.
+For the purposes of this dissertation focus is put on a \index{fully connected topology}\textit{fully connected} topology where each \acs{AN} in one layer is connected to all \acp{AN} in the next, without any cycles \cite{ref:zell:1994}.
 
@@
 Furthermore, \acp{FFNN} implement \index{fully connected topology}fully connected topologies.
-In \acp{FFNN} , information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
+In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
 Depending on the optimisation algorithm used, error correction information can be ``backpropagated'' through the network.
-An illustration of a \ac{FFNN} is given in Figure \ref{fig:ffnn} below.
+An illustration of a \acs{FFNN} is given in Figure \ref{fig:ffnn} below.
 
@@
     \includegraphics[width=0.98\textwidth]{feedforward_neural_network.pdf}
-    \caption[A \index{feedforward neural network}Feedforward neural network]{An illustration of a \index{Feedforward Neural Network}feedforward neural network implementing input, hidden and output layers using a fully connected topology.}
+    \caption[A \index{feedforward neural network}feedforward neural network]{An illustration of a \index{feedforward neural network}feedforward neural network implementing input, hidden and output layers using a fully connected topology.}
     \label{fig:ffnn}
@@
 
+\noindent
 In Figure \ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input vector $\vec{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer, $y_k$ refers to the $k$-th dimension in the output vector $\vec{y}$, $v_{i,j}$ refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the output node $y_k$.
 
-Assuming the use of \acp{SU} and bias weights, the output for the \ac{FFNN} at index $k$, denoted $y_k$, is calculated as is shown in Equation \eqref{eq:ffnn} below.
+Assuming the use of \acp{SU} and bias weights, the output for the \acs{FFNN} at index $k$, denoted $y_k$, is calculated as is shown in Equation~\eqref{eq:ffnn} below.
 
@@
 
-Section~\ref{sec:anns:an:weights} mentioned that changing the weight associated
-with a feature, changes the influence of that particular feature on the
-predicted output. \textit{Training} is the process whereby the weights of the
-\acp{FFNN} is systematically changed with the aim of improving performance.
+Details on the training of \acp{FFNN} are presented in this section along with
+detailed discussions on \index{supervised learning}supervised learning and loss functions.
 
-Finding the optimal weights that produce the best output is an optimisation
-problem and therefore, training of \acp{FFNN} is done using a search function
-called a \index{Heuristic}\textit{heuristic}. \index{Heuristic}Heuristics search
-for possible solutions in the solution-space and make use of information from
-the search-space to guide to process. Heuristics are discussed in detail in
-Chapter~\ref{chap:heuristics}.
+\textit{Training} is the process whereby the weights of the \acs{FFNN} are systematically changed with the aim of improving the \textit{performance} of the \acs{FFNN}.
+During the training process, the \acs{FFNN} is exposed to data while trying to produce some target outcome.
 
-Details on the training of \acp{FFNN} are presented in this section along with
-brief discussions on the training process, generalisation capabilities, training
-sets, \index{Supervised Learning}supervised learning, error functions, and
-performance measurement.
+The degree to which the produced outcome differs from the target outcome is referred to as \textit{loss}.
+Since training of \acp{FFNN} is an optimisation problem, the goal of the training process is to minimise the loss of the \acp{FFNN} as it related to input and target data.
 
-\subsection{Training Process}
-\label{sec:anns:training:process}
-
-During the training process, the \ac{FFNN} is exposed to input data while
-trying to predict some expected outcome. From this prediction, a \textit{cost}
-is calculated based on the degree to which the predicted output differs from the
-expected outcome. This outcome could be predefined and static, or be the result
-of an action in a dynamic environment. This cost is used by some
-\index{Heuristic}heuristic as a guide to update the weights slightly such that
-the performance of the \ac{FFNN} improves over time.
-
-The training process is executed as follows: training data is retrieved and
-pre-processed. The pre-processed input data is then split into various datasets.
-A loss is calculated by exposing all patterns in the training data to the
-\ac{FFNN} and evaluating the  prediction in comparison to the expected or target
-output. Exposing the \ac{FFNN} to all training data once is referred to as an
-epoch. The \ac{FFNN} is trained for a maximum number of epochs, or until some
-stopping condition is reached. After training, the generalisation capabilities
-of the \ac{FFNN} is evaluated against never before seen data.
-
-Central to this dissertation is the topic of generalisation. Generalisation refers to
-the ability of a model to balance under- and overfitting of data. Training a
-\ac{FFNN} using a \ac{HH} aims to do exactly that. Overfitting and underfitting
-concepts are discussed next.
-
-\subsubsection{Overfitting}
-\label{sec:anns:training:overfitting}
-
-\index{Overfitting}Overfitting describes a scenario where the trained model
-performs well on training data, but does not generalise well to never before
-seen data. \cite{ref:tetko:1995, ref:geron:2017}. Geron \cite{ref:geron:2017}
-mentions that \index{overfitting}overfitting occurs when the model is too
-complex relative to the noisiness of the training data.
-
-\subsubsection{Underfitting}
-\label{sec:anns:training:generalisation_capabilities:underfitting}
-
-\index{underfitting}Underfitting is the opposite of
-\index{overfitting}overfitting. Geron \cite{ref:geron:2017} mentions that
-\index{underfitting}underfitting occurs when the model is too simple relative to
-the underlying structure of the training data.
-
-\subsection{Training Sets}
-\label{sec:anns:training:sets}
-
-The input data is split proportionally into a training and testing set. Data in
-the training set is used to train the \ac{FFNN} \cite{ref:james:2013}, while the
-generalisation capabilities of the \ac{FFNN} is evaluated over the performance
-of the trained model when exposed to never before seen data in the testing set.
-Some research propose a validation set whereby the trained model is evaluated on
-the validation data while hyper-parameters are tuned \cite{ref:brownlee:2017}.
+Finding the optimal weights that produce the best performance on a given task is an optimisation problem.
+The optimisation algorithm used to find the optimal weights is referred to as a \index{heuristic}\textit{heuristic}.
+\index{heuristic}Heuristics search for possible solutions in the solution-space and make use of information from the search-space to guide to process.
+Heuristics are discussed in detail in Chapter \ref{chap:heuristics}.
 
@@
 
-\index{supervised learning}Supervised learning is the process of learning where
-the training data that is presented to the \ac{FFNN} includes the desired
-solution \cite{ref:geron:2017}.  The \ac{FFNN} learns the mapping function from
-the input to the target output \cite{ref:brownlee:2016}. These desired solutions
-are referred to as \textit{labels}. \index{supervised learning}Supervised
-learning can be used for both classification and regression problems.
+\index{supervised learning}Supervised learning is the process of training where the data that is presented to the \acs{FFNN} during training, includes the desired solution \cite{ref:geron:2017}.
+The \acs{FFNN} learns the mapping function from the input to the target output \cite{ref:brownlee:2016}.
+The desired solutions are referred to as \textit{labels}.
+\index{supervised learning}Supervised learning can be used for both classification and regression problems.
 
-There are two types of supervised learning algorithms based on when weights are
-updated \cite{ref:engelbrecht:2007}. These include stochastic training and batch
-training and is discussed next.
+The training data that is used during supervised learning, is split proportionally into a \textit{training} and \textit{validation} set.
+Data in the training set is used to train the \acs{FFNN} \cite{ref:james:2013} and update the weights, while the validation dataset is used for hyper-parameter tuning, where the parameters of the training process are altered, but not the weights of the \acs{FFNN}.
 
-\subsubsection{Stochastic Training}
-\label{sec:anns:training:stochastic}
+Exposing the \acs{FFNN} to all training data once is referred to as an
+epoch.
+The \acs{FFNN} is trained until some stopping condition is reached.
+Once the stopping condition has been reached, the \textit{performance} of the \acs{FFNN} is evaluated.
+The performance is directly related to the loss of the \acs{FFNN} as it relates to a \textit{test dataset}.
+The test dataset is a collection of data that is not used during training and is used to determine the generalisation capabilities of the \acs{FFNN} as it relates to unseen data.
+Overfitting and underfitting describe two possible outcomes of the training process.
 
-\index{Stochastic Training}Stochastic training, also known as \index{Online
-    Learning}\textit{online learning}, is a \index{Supervised Learning}supervised
-learning variation whereby weights are adjusted after each training pattern is
-presented.
+\subsubsection{Overfitting}\label{sec:anns:training:process:overfitting}
 
-If \index{stochasting training}stochastic training is used to train the
-\ac{FFNN}, the training data must be shuffled before splitting into sets, in
-order to avoid overfitting or memorising the order in which patterns are
-presented in the training set \cite{ref:engelbrecht:2007}. It has been shown
-that shuffling the training data can speed up convergence
+\index{overfitting}Overfitting describes a scenario where the trained \acs{FFNN} performs well on training data, but does not generalise well to never before seen data from the test set \cite{ref:tetko:1995, ref:geron:2017}.
+Geron \cite{ref:geron:2017} describes \index{overfitting}overfitting as the case where \acs{FFNN} is too complex relative to the noisiness of the training data.
+
+\subsubsection{Underfitting}\label{sec:anns:training:process:underfitting}
+
+Underfitting describes a scenario where the \acs{FFNN} is not able to effectively learn the underlying structure of the training data \cite{ref:tetko:1995, ref:geron:2017}.
+Geron \cite{ref:geron:2017} describe underfitting as the case where the \acs{FFNN} is too simple relative to the underlying structure of the training data.\\
+\\
+\noindent
+There are two types of supervised learning algorithms based on when weights are updated \cite{ref:engelbrecht:2007}. These include stochastic training and batch
+training.
+
+\subsubsection{Stochastic Training}\label{sec:anns:training:stochastic}
+
+\index{stochastic training}Stochastic training, also known as \index{online learning}\textit{online learning}, is a \index{supervised learning}supervised learning variation whereby weights are adjusted after each training pattern presented.
+\index{stochastic training}Stochastic training benefits from shuffling data in the training dataset before presenting it to the \acs{FFNN}, in order to avoid overfitting or memorising the order in which patterns are presented \cite{ref:engelbrecht:2007}.
+It has been shown that shuffling the training data can speed up convergence
 \cite{ref:bengio:2012}.
 
-\subsubsection{Batch Training}
-\label{sec:anns:training:batch}
+\subsubsection{Batch Training}\label{sec:anns:training:batch}
 
-\index{Batch Training}Batch training, also known as \index{Offline
-    Learning}\textit{offline learning} is a supervised training variation whereby
-the weight changes are accumulated and used to adjust the weights once after all
-the training patterns have been presented.
+\index{batch training}Batch training, also known as \index{offline learning}\textit{offline learning}, is a supervised training variation whereby weight changes are accumulated and used to adjust the weights only once, after all the training patterns have been presented.
 
-\subsubsection{Mini-Batch Training}
-\label{sec:anns:training:mini_batch}
+\subsubsection{Mini-Batch Training}\label{sec:anns:training:mini_batch}
 
-Research suggests a trade-off between stochastic and batch training by making
-use of mini-batches \cite{ref:bengio:2012}. Mini-batch training is the same as
-batch training, however, weights are updated after $\beta$ patterns have been
-presented, where $\beta$ is the batch size.
+Research suggests a trade-off between stochastic and batch training by making use of mini-batches \cite{ref:bengio:2012}.
+Mini-batch training is similar to batch training, however weights are updated after $\beta$ patterns have been presented, where $\beta$ is the mini-batch size.\\
+\\
+\noindent
+Performance metrics are used during training on the training set and evaluation on the test set.
+There are many different performance measurements that can be used, however this dissertation focuses on performance measures related to loss.
+Loss is calculated using an error function.
+The following section presents the reader with more detail on the error functions that can be used during the training process.
 
-\subsection{Error Functions}
-\label{sec:anns:training:error_functions}
+\subsection{Error Functions}\label{sec:anns:training:error_functions}
 
-An error function, also known as a \index{Loss Function}\index{Cost
-    Function}\textit{loss/cost function} is used to
-evaluate the model's capability to approximate output data based on the input
-patterns presented. It measures the degree to which the model is capable of
-predicting the correct output data.  This error value is used by the
-\index{Heuristics}heuristic as a guide during the training process.
+This dissertation focuses on a number of error functions, including \acf{SSE}, \acf{MSE}, \acf{RMSE}, \acf{MAE}, \acf{BinXE}, \acf{CatXE} and \acf{SparseCatXE}.
 
-This dissertation focuses on the following error functions: \ac{SSE}, \ac{MSE},
-\ac{RMSE}, \ac{MAE}, \ac{BinXE}, \ac{CatXE} and \ac{SparseCatXE}. Each of these
-are discussed next.
+\subsubsection{Sum Squared Error}\label{sec:anns:training:error_functions:sse}
 
-\subsubsection{Sum Squared Error}
-\label{sec:anns:training:error_functions:sse}
-
-The \ac{SSE} is computed using:
+The \acs{SSE} is given in Equation~\eqref{eq:sse} below.
 
@@
 
-\noindent where $\hat{y}_{k,p}$ is $k$-th dimension of the target output of
-pattern $p$, $y_{k,p}$ is $k$-th dimension of the predicted output vector
-$\vec{y}_{p}$ for pattern $p$, $P$ is the number of patterns in the training
-set, and $K$ is the number of dimensions in the output vector $\vec{y}$.
+\noindent
+In Equation~\eqref{eq:sse} above, $\hat{y}_{k,p}$ is $k$-th dimension of the target output of pattern $p$, $y_{k,p}$ is $k$-th dimension of the predicted output vector $\vec{y}_{p}$ for pattern $p$, $P$ is the number of patterns in the mini-batch, and $K$ is the number of dimensions in the output vector $\vec{y}$.
 
-\subsubsection{Mean Squared Error}
-\label{sec:anns:training:error_functions:mse}
+\subsubsection{Mean Squared Error}\label{sec:anns:training:error_functions:mse}
 
-The \ac{MSE} is computed using:
+The \acs{MSE} is given in Equation~\eqref{eq:mse} below.
 
@@
 
-\subsubsection{Root Mean Squared Error}
-\label{sec:anns:training:error_functions:rmse}
+\subsubsection{Root Mean Squared Error}\label{sec:anns:training:error_functions:rmse}
 
-The \ac{RMSE} is computed using:
+The \acs{RMSE} is given in Equation~\eqref{eq:rmse} below.
 
@@
 
-\subsubsection{Mean Absolute Error}
-\label{sec:anns:training:error_functions:mae}
+\subsubsection{Mean Absolute Error}\label{sec:anns:training:error_functions:mae}
 
-The \ac{MAE} is computed using:
+The \acs{MAE} is given in Equation~\eqref{eq:mae} below.
 
@@
 
-\subsubsection{Binary Cross-Entropy}
-\label{sec:anns:training:error_functions:bin_xe}
+\subsubsection{Binary Cross-Entropy}\label{sec:anns:training:error_functions:bin_xe}
 
-\noindent The \ac{BinXE} is computed using:
+\acs{BinXE} is used in classification problems, where there are only two classes in the target output data. \acs{BinXE} is given in Equation~\eqref{eq:bin_xe} below.
 
@@
 
-\noindent \ac{BinXE} is used in classification problems, where there are only
-two classes in the target output data.
+\noindent
 
@@
 
-The \ac{CatXE} is computed using:
+\acs{CatXE} is used in classification problems where the target output or \textit{label} is a one-hot encoded vector. \acs{CatXE} is given in Equation~\eqref{eq:cat_xe} below.
 
@@
 
-\noindent where $\mathbbm{1}$ is the indicator function that the $k$-th index observation
-belongs to the $c$-th class. $C$ is the total number of unique class labels. If
-$C = 2$, then \ac{BinXE} can be used instead.
+\noindent
+In Equation~\eqref{eq:cat_xe} above, $\mathbbm{1}$ is the indicator function that the $k$-th index observation belongs to the $c$-th class.
+$C$ is the total number of unique class labels.
+If $C = 2$, then \acs{BinXE} can be used instead.
 
-\ac{CatXE} is used in classification problems where the target
-output or \textit{label} is a one-hot encoded vector.
+\subsubsection{Sparse Categorical Cross-Entropy}\label{sec:anns:training:error_functions:sparse_cat_xe}
 
-\subsubsection{Sparse Categorical Cross-Entropy}
-\label{sec:anns:training:error_functions:sparse_cat_xe}
-
-The \ac{SparseCatXE} error function is the same as \ac{CatXE} with the only
-difference being that the target output or label is a one-hot
-embedding of a class represented as an integer, $c \in \{1,2, \dots, C\}$.
-
-\subsection{Performance Measures}
-\label{sec:anns:training:performance_measures}
-
-Performance measures play an important role in understanding how well a
-\ac{FFNN} has been trained to predict target output. Performance metrics are
-used during training on the training set and evaluation on the test set. These
-performance metrics provide a mechanism by which different implementations of
-\acp{FFNN} and training processes can be compared.
-
-There are many different mechanisms that can be used to measure the performance
-of a \ac{FFNN}, however this dissertation only focuses on measures of cost such as
-loss and speed. Brief discussions follow on loss and speed as performance
-measures.
-
-\subsubsection{Loss/Cost}
-\label{sec:anns:training:performance_measure:loss_cost}
-
-A measure of cost indicates how well the \ac{FFNN} is able to predict target
-output and often include a metric over some distance between the predicted
-output and target output. This metric is calculated using an error function as
-described in Section~\ref{sec:anns:training:error_functions}.
-
-In the case of classification problems, the loss/cost can be expressed in terms
-of \textit{accuracy}. Accuracy refers to the percentage of patterns for which
-the \ac{FFNN} was able to successfully predict the target output.
-
-\subsubsection{Speed}
-\label{sec:anns:training:performance_measure:speed}
-
-Speed is a performance measure which calculates how fast a \ac{FFNN} can reach
-some target goal. Speed is often expressed relative to another performance
-measurement metric e.g how many epochs of training is necessary for a \ac{FFNN}
-to reach a certain lost/cost threshold.
-
-For this dissertation, speed is a measure of performance relative to training
-\textit{steps} or \textit{mini-batch} steps.
-
-\subsection{Stopping Conditions}
-\label{sec:anns:training:stopping_conditions}
-
-Stopping conditions are required to stop the training process. The goal of the
-stopping condition is to try and stop the training process to avoid unnecessary
-computational cost or to set a comparible timeframe in which \acp{FFNN} are
-trained. Stopping conditions include:
-
-\begin{itemize}
-    \item
-          \textbf{Max Epochs}: Stop when a maximum number of epochs has been reached.
-
-    \item
-          \textbf{Performance Measurement Threshold}: Stop the training when the
-          performance measurement metric has reached some acceptable threshold.
-
-    \item
-          \textbf{Stagnation}: Stop the training process if no improvements in the
-          performance of the model is observed over a window of epochs.
-
-    \item
-          \textbf{Overfit}: Stop the training process if the generalisation on the
-          test set indicates that the \ac{FFNN} is overfitting the data.
-\end{itemize}
+\acs{SparseCatXE} error function is similar to \acs{CatXE} with the only difference being that the target output or label is a one-hot embedding of a class represented as an integer, $c \in \{1,2, \dots, C\}$.
 
@@
 
-This chapter presented background information on the \ac{BN} and it was shown
-how neurons connect to each other. Emphasis was put on \index{Synapse}synapses
-and how communication happens between neurons. The \ac{AN} was introduced in
-Section~\ref{sec:anns:an} and it was shown how the brain inspired the
-development of \acp{AN}. Brief discussions followed on the various components
-that make up the \ac{AN}. Details on input, weights, \index{net input signal}net
-input signal, biases, \index{activation function}activation functions, and
-output were provided.  Section~\ref{sec:anns:ann} introduced \acp{ANN}. It was
-shown how \acp{AN} are connected together to form networks. \ac{ANN} design was
-described in terms of architecture and topologies. Special emphasis was put on
-\acp{FFNN} as the model being used throughout the rest of the dissertation.
-Section~\ref{sec:anns:training} provided the necessary background information
-required on the training of \acp{FFNN}. It is emphasised that the training of an
-\ac{ANN} is an optimisation problem where optimal values for weights and biases
-are sought such that a given cost function is minimised. The training process
-was explained and details on training sets was provided. A variant of learning,
-called \index{Supervised Learning}supervised learning was presented and led to
-the discussion on error functions, performance measures, and stopping
-conditions.
-
-Chapter~\ref{chap:heuristics} introduces background information on optimisation
-and heuristics.
+This chapter presented background information on the \acs{BN}.
+The \acs{AN} was introduced and discussions followed on the various components that make up the \acs{AN}.
+Details on input, weights and biases, \index{net input signal}net input signal, \index{activation function}activation functions, and output were provided.
+The \acs{ANN} was introduced.
+\acs{ANN} design was described in terms of architecture and topologies.
+Special emphasis was put on \acp{FFNN}.
+Background information on the training of \acp{FFNN} was presented.
+A variant of training, called \index{supervised learning}supervised learning was presented and led to the discussion on datasets, performance measures and training outcomes.
+The chapter concluded with a number or error functions that can be used to calculate the loss in the context of supervised learning.

### 2022-10-13 dissertation/preamble/abstract.tex
✨ (dissertation): Chapter 1 done
✨ (disseration): Chapter 2 - Done

@@
 \end{center}
-
+\noindent
 Many different heuristics have been developed and used to train \acfp{FFNN}.  However, selection of the best heuristic to train
@@
     \textbf{Keywords:} hyper-heuristics, meta-learning, feedforward neural
-    networks, supervised learning, Bayesian statistics.
+    networks, supervised learning, Bayesian statistics
 }

### 2022-10-22 dissertation/chapters/01-introduction.tex
🚧 (chapter3): WIP - Save point

@@
 \begin{itemize}
-      \item \textbf{Section \ref{sec:introduction:summary_research_domain}} provides the reader with brief summary of the research domain.
+      \item \textbf{Section~\ref{sec:introduction:summary_research_domain}} provides the reader with brief summary of the research domain.
 
-      \item \textbf{Section \ref{sec:introduction:problem}} outlines the research problem being addressed.
+      \item \textbf{Section~\ref{sec:introduction:problem}} outlines the research problem being addressed.
 
-      \item \textbf{Section \ref{sec:introduction:motivation}} provides a motivation for this research.
+      \item \textbf{Section~\ref{sec:introduction:motivation}} provides a motivation for this research.
 
-      \item \textbf{Section \ref{sec:introduction:objectives}} presents the reader with the research objectives and outlines the goals of this dissertation.
+      \item \textbf{Section~\ref{sec:introduction:objectives}} presents the reader with the research objectives and outlines the goals of this dissertation.
 
-      \item \textbf{Section \ref{sec:introduction:contributions}} outlines the contributions of this research to the field.
+      \item \textbf{Section~\ref{sec:introduction:contributions}} outlines the contributions of this research to the field.
 
-      \item \textbf{Section \ref{sec:introduction:outline}} provides a full dissertation outline.
+      \item \textbf{Section~\ref{sec:introduction:outline}} provides a full dissertation outline.
 \end{itemize}
@@
 
-In Section \ref{sec:introduction:problem} above, it is mentioned that finding the best heuristic to train \acp{FFNN} is a timely and tedious process.
+In Section~\ref{sec:introduction:problem} above, it is mentioned that finding the best heuristic to train \acp{FFNN} is a timely and tedious process.
 A modern approach is to use \acp{HH} to automate the process of selecting the best heuristic when applied to some optimisation problem.
@@
 \begin{itemize}
+      \item \textbf{Appendix~\ref{app:backpropagation}} provides a full breakdown of the \acf{BP} algorithm as presented by \citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007}.
+
+      \item \textbf{Appendix~\ref{app:symbols}} lists and defines the mathematical symbols used in this work, categorised according to the relevant chapter in which they appear.
+
+      \item \textbf{Appendix~\ref{app:acronyms}} provides a list of the important acronyms used or newly defined in the course of this work, as well as their associated definitions.
+
       \item \textbf{Appendix~\ref{app:datasets}} provides details on the datasets used for the empirical analysis.
@@
 
-      \item \textbf{Appendix~\ref{app:acronyms}} provides a list of the important acronyms used or newly defined in the course of this work, as well as their associated definitions.
-
       \item \textbf{Appendix~\ref{app:derived_publications}} lists the publications derived from this work.
-
-      \item \textbf{Appendix~\ref{app:symbols}} lists and defines the mathematical symbols used in this work, categorised according to the relevant chapter in which they appear.
 \end{itemize}

### 2022-10-22 dissertation/chapters/02-artificial-neural-networks.tex
🚧 (chapter3): WIP - Save point

@@
 \begin{itemize}
-    \item \textbf{Section \ref{sec:anns:bn}} gives background information on the \acs{BN}.
+    \item \textbf{Section~\ref{sec:anns:bn}} gives background information on the \acs{BN}.
 
-    \item \textbf{Section \ref{sec:anns:an}} introduces the \acs{AN}.
+    \item \textbf{Section~\ref{sec:anns:an}} introduces the \acs{AN}.
 Brief discussions follow on input, \index{weights}weights and \index{biases}biases, \index{net input signal}net input signal, \index{activation function}activation functions, and output.
 
-    \item \textbf{Section \ref{sec:anns:ann}} introduces the \acs{ANN}. Brief discussions follow on \acs{ANN} architecture, topology, and \acp{FFNN}.
+    \item \textbf{Section~\ref{sec:anns:ann}} introduces the \acs{ANN}. Brief discussions follow on \acs{ANN} architecture, topology, and \acp{FFNN}.
 
-    \item \textbf{Section \ref{sec:anns:training}} provides details on the training process, \index {supervised learning}supervised learning, training sets, stopping conditions, performance measures and \index{error function}error functions.
+    \item \textbf{Section~\ref{sec:anns:training}} provides details on the training process, \index {supervised learning}supervised learning, training sets, stopping conditions, performance measures and \index{error function}error functions.
 
-    \item \textbf{Section \ref{sec:anns:summary}} provides a brief summary of the chapter.
+    \item \textbf{Section~\ref{sec:anns:summary}} provides a brief summary of the chapter.
 \end{itemize}
@@
 The biological neural systems are made up of microscopic nerve cells called neurons \cite{ref:jain:1996}.
-Figure \ref{fig:biological_neuron} illustrates a single \acs{BN}.
+Figure~\ref{fig:biological_neuron} illustrates a single \acs{BN}.
 The main components of the \acs{BN} include the cell body, \index{dendrites}\textit{dendrites} and the \index{axon}\textit{axon}.
@@
 
-The \acs{AN} implements various components and is illustrated in Figure \ref{fig:artificial_neuron}.
+The \acs{AN} implements various components and is illustrated in Figure~\ref{fig:artificial_neuron}.
 
@@
     \item \textbf{Input:} The input models the activations received from the pre-synaptic neuron or from some environment sensor.
-Input is represented by the input vector $\vec{x}$, in Figure \ref{fig:artificial_neuron}.
+Input is represented by the input vector $\vec{x}$, in Figure~\ref{fig:artificial_neuron}.
 
-    \item \textbf{Weights:} The weights model the \index{synapse}synapses and connection strengths. Weights are represented by the weight vector $\vec{v}$, in Figure \ref{fig:artificial_neuron}.
+    \item \textbf{Weights:} The weights model the \index{synapse}synapses and connection strengths. Weights are represented by the weight vector $\vec{v}$, in Figure~\ref{fig:artificial_neuron}.
 
     \item \index{net input signal}\textbf{Net input signal:} The \index{net input signal}net input signal models the net resulting activations from all connected pre-synaptic neurons or environment sensors.
-The \index{net input signal}net input signal is represented by $net$, in Figure \ref{fig:artificial_neuron}.
+The \index{net input signal}net input signal is represented by $net$, in Figure~\ref{fig:artificial_neuron}.
 
     \item \textbf{Biases:} The biases model a mechanism introduced to influence the strength of the activation (output signal) of the \acs{AN}.
-The bias is represented by $\theta$, in Figure \ref{fig:artificial_neuron}.
+The bias is represented by $\theta$, in Figure~\ref{fig:artificial_neuron}.
 
     \item \index{activation function}\textbf{Activation function:} The activation function models the action potential of the \acs{BN} and is based on the net input signal.
-The \index{activation function}activation function is represented by $f$, in Figure \ref{fig:artificial_neuron}.
+The \index{activation function}activation function is represented by $f$, in Figure~\ref{fig:artificial_neuron}.
 
-    \item \textbf{Output:} The output models the activation by the post-synaptic neuron. Output is represented by the output vector $\vec{y}$, in Figure \ref{fig:artificial_neuron}.
+    \item \textbf{Output:} The output models the activation by the post-synaptic neuron. Output is represented by the output vector $\vec{y}$, in Figure~\ref{fig:artificial_neuron}.
 \end{itemize}
@@
 Non-zero gradients are required by some heuristics such as \acs{SGD} in order to be able to effectively train \acp{ANN} \cite{ref:hanin:2018}.
-An illustration of \acs{LReLU} with various values for $\alpha$ and $\theta = 0$ is given in Figure \ref{fig:anns:activation_functions:leaky_relu}.
+An illustration of \acs{LReLU} with various values for $\alpha$ and $\theta = 0$ is given in Figure~\ref{fig:anns:activation_functions:leaky_relu}.
 
@@
 In Equation~\eqref{eq:sigmoid} above, $\lambda$ is a control parameter, which controls the steepness of the sigmoid activation function and is usually set to $\lambda = 1$.
-An illustration of the \index{sigmoid}sigmoid \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$ is given in Figure \ref{fig:anns:activation_functions:sigmoid}.
+An illustration of the \index{sigmoid}sigmoid \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$ is given in Figure~\ref{fig:anns:activation_functions:sigmoid}.
 
@@
 \noindent
-An illustration of the \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$ is given in Figure \ref{fig:anns:activation_functions:hyperbolic_tangent}.
+An illustration of the \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$ is given in Figure~\ref{fig:anns:activation_functions:hyperbolic_tangent}.
 
@@
 \noindent
-Figure \ref{fig:anns:activation_functions:softmax_argmax} illustrates the comparison of transformations of the output vector $\vec{y}$, where the \index{sigmoid}sigmoid, the \index{softmax}softmax and the \index{argmax}argmax \index{activation function}activation functions are used.
+Figure~\ref{fig:anns:activation_functions:softmax_argmax} illustrates the comparison of transformations of the output vector $\vec{y}$, where the \index{sigmoid}sigmoid, the \index{softmax}softmax and the \index{argmax}argmax \index{activation function}activation functions are used.
 
@@
 Depending on the optimisation algorithm used, error correction information can be ``backpropagated'' through the network.
-An illustration of a \acs{FFNN} is given in Figure \ref{fig:ffnn} below.
+An illustration of a \acs{FFNN} is given in Figure~\ref{fig:ffnn} below.
 
@@
 \noindent
-In Figure \ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input vector $\vec{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer, $y_k$ refers to the $k$-th dimension in the output vector $\vec{y}$, $v_{i,j}$ refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the output node $y_k$.
+In Figure~\ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input vector $\vec{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer, $y_k$ refers to the $k$-th dimension in the output vector $\vec{y}$, $v_{i,j}$ refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the output node $y_k$.
 
@@
 \index{heuristic}Heuristics search for possible solutions in the solution-space and make use of information from the search-space to guide to process.
-Heuristics are discussed in detail in Chapter \ref{chap:heuristics}.
+Heuristics are discussed in detail in Chapter~\ref{chap:heuristics}.
 
@@
 
-\subsubsection{Categorical Cross-Entropy}
-\label{sec:anns:training:error_functions:cat_xe}
+\subsubsection{Categorical Cross-Entropy}\label{sec:anns:training:error_functions:cat_xe}
 
@@
 
-\section{Summary}
-\label{sec:anns:summary}
+\section{Summary}\label{sec:anns:summary}
 

### 2022-10-22 dissertation/chapters/03-heuristics.tex
🚧 (chapter3): WIP - Save point

@@
-\chapter{Heuristics}
-\label{chap:heuristics}
+\chapter{Heuristics}\label{chap:heuristics}
 
 \begin{quotation}
-      \textit{``It is not the strongest of the species that survives. It is also not the most intelligent that survives. It is the one that is the most adaptable to change.'' - Charles Darwin}
+      \noindent ``It is not the strongest of the species that survives. It is also not the most intelligent that survives. It is the one that is the most adaptable to change.''
 \end{quotation}
-
-So far the reader has been introduced to the detailed background information on \acp{ANN}.
-The training process was discussed without any reference to specific optimiser algorithms to execute the training process.
-Specific reference is made to supervised learning in the context of \ac{FFNN}.
-This chapter aims to extend to this information by providing the reader with a set of optimisers that have been widely used to train \acp{ANN}.
-In the context of \acp{HH}, standardisation of terminology is in order and therefore these optimisers fill the role of low-level heuristics and will be referred to as heuristics from this point on.
-
-Many different techniques have been used to train \acp{ANN} \cite{ref:kingma:2014}.
-At the time of writing, the majority of work that is published around \ac{ANN} training involves the use of some gradient-based technique \cite{ref:nel:2021}.
-However, research has shown that these gradient-based techniques do have their disadvantages such as slow-convergence or getting trapped in local optima \cite{ref:mingguang:2009}.
-Other techniques have also been shown to successfully train \acp{FFNN}.
-These include meta-heuristics such as  \ac{PSO} \cite{ref:rakitianskaia:2012}\cite{ref:vanwyk:2014}, \ac{DE} \cite{ref:espinal:2011} and \acp{GA} \cite{ref:gupta:1999}.
-Various heuristics are considered for training \acp{FFNN} as the best heuristic to use is shown to be problem dependent in many cases \cite{ref:kheiri:2017}.
-
-Although there are many different types of heuristics, the list of heuristics specified in this Chapter is by no means exhaustive.
-Broadly speaking this chapter focuses on two different groups of heuristics.
-These include classical gradient-based approaches and population-based meta-heuristics.
-Each technique is discussed in detail.
-Pseudo-code algorithms are provided and where possible and discussions follow on their advantages, disadvantages, capabilities and limitations.
-This subset of heuristics were selected for their characteristics and were deemed appropriate and sufficient for the problem at hand.
+\begin{flushright}
+      Charles Darwin
+\end{flushright}
+
+\noindent
+Many different techniques have been used to train \acp{FFNN} \cite{ref:kingma:2014}.
+Finding the best technique to use to train an \acs{FFNN} has been shown to be problem dependent in many cases \cite{ref:kheiri:2017}.
+Every technique has its characteristics, constraints, advantages and disadvantages.
+At the time of writing, the majority of work that is published around the training of \acp{FFNN}, involves the use of gradient-based techniques \cite{ref:nel:2021}.
+Gradient-based techniques are not without flaws and can, for example, yield slow convergence or get trapped in local optima \cite{ref:mingguang:2009}.
+Other techniques have also been used to successfully train \acp{FFNN}, including meta-heuristics such as \acf{PSO} \cite{ref:rakitianskaia:2012, ref:vanwyk:2014}, \acf{DE} \cite{ref:espinal:2011} and \acfp{GA} \cite{ref:gupta:1999}.
+
+Chapter~\ref{chap:anns} briefly introduced the reader to the concept of \index{heuristic}\index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
+This chapter presents more detailed background information on various different \index{heuristic}heuristics that have been used to train \acp{FFNN}.
+Broadly speaking, this chapter focuses on two different groups of \index{heuristic}heuristics, including classical gradient-based approaches and population-based \index{meta-heuristic}meta-heuristics.
+Each technique is presented and discussed in detail.
+Pseudo-code algorithms are provided for each technique and discussions follow on advantages, disadvantages, capabilities and limitations.
 The remainder of this chapter is structured as follows.
@@
 \begin{itemize}
-      \item \textbf{Section \ref{sec:heuristics:what_is_a_heuristic}} provides a high-level definition for heuristics.
-
-      \item \textbf{Section \ref{sec:heuristics:optimisation}} provides a brief overview of what optimisation is. It is also shown that \ac{FFNN} training is an optimisation problem.
-
-      \item \textbf{Section \ref{sec:heuristics:gd}} presents the reader with the concept of gradient-based heuristics.
-The basics of \ac{BP} is provided and detailed discussions follow on seven different gradient-based low-level heuristics.
-
-      \item \textbf{Section \ref{sec:heuristics:mh}} presents the reader with three different meta-heuristics that are show to train \acp{FFNN}.
-
-      \item Finally, a summary of the chapter is provided in \textbf{Section \ref{sec:heuristics:summary}}.
-\end{itemize}
-
-\section{What is a heuristic?}
-\label{sec:heuristics:what_is_a_heuristic}
-
-The term \textit{heuristic} comes from the Latin word \textit{heuristicus} which means ``to find out, discover''.
-\citeauthor{ref:romanycia:1985} \cite{ref:romanycia:1985} provides a complete study on the history and origins of the term \textit{heuristic}.
-From their research, a proposal was made to define heuristics in the context of
-\ac{AI}, as any device, be it a program, rule, piece of knowledge, which one is not entirely confident will be useful in providing a practical solution, but which one has reason to believe will be useful and which is added to a problem-solving system in expectation that on average the performance will improve.
-
-In the context of this dissertation, the above definition holds, but can be more clearly specified such that a heuristic refers to an algorithmic search technique that serves as a guide to a search process where some good-performing candidate solution to a optimisation problem is being sought out.
-Different heuristics make use of different information during the search process \cite{ref:kheiri:2017}.
-Heuristics such as gradient-based techniques make use of the derivatives obtained by evaluating the \ac{ANN} and thus it can be said that they make use of information directly from the \textit{search space}.
-On the contrary, heuristics such as meta-heuristics make use of meta-information obtained as a result of evaluating the \ac{FFNN} \cite{ref:blum:2003}.
-This could be the ranked-performance of a population of candidate solutions, referred to as \textit{entities}.
-Meta-heuristics are useful when there is imperfect information about the search space \cite{ref:bianchi:2009} and are generally less problem-specific than other heuristic techniques \cite{ref:blum:2003}.
-
-In order to understand the application of heuristics, consider first the concept of optimisation and how that relates to training \acp{FFNN}.
-
-\section{Optimisation}
-\label{sec:heuristics:optimisation}
+      \item \textbf{Section~\ref{sec:heuristics:optimisation}} provides a brief review of optimisation. It is shown that training of \acp{FFNN} is an optimisation problem.
+
+      \item \textbf{Section~\ref{sec:heuristics:what_is_a_heuristic}} provides background information on the origins and definition the term \index{heuristic}\textit{heuristic}.
+It is shown that \index{heuristic}heuristics are a class of algorithms that are used to solve optimisation problems.
+
+      \item \textbf{Section~\ref{sec:heuristics:gd}} presents the reader with seven low-level, gradient-based \index{heuristic}heuristics, including \acf{SGD}, \acf{Momentum}, \acf{NAG}, \acf{Adagrad}, \acf{RMSProp}, \acf{Adadelta} and \acf{Adam}.
+
+      \item \textbf{Section~\ref{sec:heuristics:mh}} presents the reader with three different population-baed \index{meta-heuristic}meta-heuristics, including \acf{PSO}, \acf{DE} and \acfp{GA}.
+
+      \item \textbf{Section~\ref{sec:heuristics:summary}} provides the reader with a brief summary of the chapter.
+\end{itemize}
+
+\section{Optimisation}\label{sec:heuristics:optimisation}
 
@@
 
-      \item A \textbf{set of unknowns or independent variables}: These affect the outcome of the objective function $f$ and is denoted as $x$.
-$f(x)$ is thus the quantification of the objective function over the unknowns $x$.
-
-      \item A \textbf{set of constraints}: These restrict and limit the values that can be assigned to the unknowns $x$.
-Optimisation problems that contain must adhere to a set of constraints are referred to as \acp{CSP}.
-\end{itemize}
-
-The goals of heuristics is to find a set of valid values for $x$ that optimises the objective function while adhering to a set of constraints.
-Heuristics thus search for solutions, referred to as candidate solutions, in a set of all possible and valid solutions, referred to as the \textit{feasible search space}.
-
-Optimisation problems come in a wide variety of forms.
-Mostly these functions are defined in terms of the number of variables used (uni- vs.
+      \item A \textbf{set of unknowns or independent variables}: Affects the outcome of the objective function $f$ and is denoted as $x$.
+$f(x)$ is thus the quantification of the objective function over the unknowns, represented by $x$.
+Note that $x$ could be a scalar value, a vector or a matrix and notation is left out for simplicity.
+
+      \item A \textbf{set of constraints}: Restrict and limit the values that can be assigned to the unknowns, represented by $x$.
+Optimisation problems that must adhere to a set of constraints are referred to as \acfp{CSP}.
+\end{itemize}
+
+\noindent
+Optimisation problems come in a wide variety, and can be defined in terms of the number of variables used (uni- vs.
 multivariate), the number of objective functions used (single- vs.
@@
 inseparable, discrete vs.
-continuous) and  the set of constraints that the solution has to adhere to (constrained vs unconstrained).
-
-Optima can be defined as local or global optima.
+continuous) and the set of constraints that the solution must adhere to (constrained vs unconstrained).
+
+Optima can be defined as \textit{local} or \textit{global} optima.
 Local optima is the best optimisation of $f(x)$ in a neighbourhood of solutions, while the global optima is the best optimisation of $f(x)$ over all solutions in the solution space.
 
-From the components of optimisation that was presented above, it can be said that the training process of an \ac{FFNN} is an optimisation problem.
-Consider the relationship between optimisation and supervised training of \acp{FFNN} as follows.
-During training, the \ac{FFNN} is evaluated by means of a loss/cost function as was presented in Chapter \ref{chap:anns}.
-In the context of optimisation, this loss/cost function is the object function to be minimised.
-For supervised learning specifically, it was mentioned that a training dataset is used to train the \ac{FFNN}.
-The inputs to the \ac{ANN} would be these training samples and thus serves the role of independent variables in the context of optimisation.
-The output of the \ac{ANN} is directly influenced by the \ac{ANN} model parameters, called the \textit{weights} of the network and is thus referred to as the dependent variables.
-Finally, the goal of training \acp{ANN} is to find the configuration of \textit{weights} such that the performance of the \ac{ANN} is optimal.
-
-The following sections present the various types of heuristics that are of concern to this dissertation and the implementation of the \ac{BHH}.
-
-\section{Gradient-Based Heuristics}
-\label{sec:heuristics:gd}
-
-Gradient-based techniques are optimisation technique that makes use of the evaluated gradients of a model in order to optimise the model.
-Specifically in the context of a minimisation problem, these techniques are called gradient-\textit{descent} heuristics as they minimise the loss/cost function.
-\Ac{GD} is generally attributed to Cauchy \cite{ref:lemarechal:2012}, who first suggested it in 1847.
+As stated in Chapter~\ref{chap:anns}, the training of an \acp{FFNN} is a particular type of optimisation problem, where the goal is to find the configuration of \textit{weights}, such that the \ac{FFNN} yields output that minimises some loss function.
+The mechanism by which the optimal weights for a \acs{FFNN} is sough out, is executed by an \index{optimisation algorithm}optimisation algorithm known as a \index{heuristic}heuristic.
+Discussions on the details of heuristics are presented in the following sections.
+
+\section{What is a heuristic?}\label{sec:heuristics:what_is_a_heuristic}
+
+The term \textit{heuristic} comes from the Latin word \textit{heuristicus} which means ``to find out or discover''.
+\citeauthor{ref:romanycia:1985} \cite{ref:romanycia:1985} provides a complete study on the history and origins of the term \index{heuristic}\textit{heuristic}.
+From their research, a proposal is made to define \index{heuristic}heuristics in the context of \ac{AI}, as any device, be it a program, rule, piece of knowledge, which is added to a problem-solving system, in expectation that on average, the performance will improve.
+
+In the context of this dissertation, a \index{heuristic}heuristic refers to an algorithmic search technique that serves as a guide to a search process where good solutions to a optimisation problem is being sought out.
+Different \index{heuristic}heuristics make use of different information during the search process \cite{ref:kheiri:2017}.
+During the training of \acp{FFNN}, \index{heuristic}heuristics such as gradient-based \index{heuristic}heuristics make use of the derivatives obtained by evaluating the \ac{FFNN}.
+It can thus be said that gradient-based \index{heuristic}heuristics make use of information directly from the \textit{search space}.
+On the contrary, \index{heuristic}heuristics such as \index{hmeta-euristic}meta-heuristics make use of meta-information obtained as a result of evaluating the \ac{FFNN} \cite{ref:blum:2003}.
+The meta-information that \index{meta-heuristic}meta-heuristics make use of could include ranked-performance of a population of candidate solutions, referred to as \textit{entities}.
+\index{meta-heuristic}Meta-heuristics are useful when there is imperfect information about the search space \cite{ref:bianchi:2009}, and are generally less problem-specific than other classes of \index{heuristic}heuristics \cite{ref:blum:2003}.
+This disseration takes a particular interest in gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
+Each of these are presented in detail in the following sections.
+
+\section{Gradient-Based Heuristics}\label{sec:heuristics:gd}
+
+Gradient-based \index{heuristic}heuristics are optimisation techniques that make use of derivates obtained from evaluating the model being optimised.
+Specifically, in the context of a minimisation problem, these techniques are called \acf{GD} heuristics as they \textit{minimise} some loss function.
+\Acs{GD} is generally attributed to Cauchy \cite{ref:lemarechal:2012}, who first suggested it in 1847.
 In 1907 Hadamard \cite{ref:hadamard:1908} independently proposed a similar method.
 
-Although \ac{GD} techniques where not the first techniques used to train \ac{FFNN}
-\cite{ref:engelbrecht:2007}, they are certainly the most popular.
-\Ac{GD} techniques have become increasingly popular partly due to their simplicity, but mostly due to their low computational overhead compared to other techniques such as meta-heuristics and other second-order derivative methods such as Newtons' method.
-There are many variants of this technique, however, they all fundamentally apply the same generic \ac{GD} framework called \acl{BP}.
-The \ac{BP} framework is provided next and all the other gradient-based techniques that follow are built upon this idea.
-
-\subsection{Backpropagation}
-\label{sec:heuristics:gd:backpropagation}
-
-\Ac{GD} techniques require the definition of some error function.
-In the context of training \acp{FFNN}, this error function is referred to as a loss/cost function.
-Consider the definition of the \ac{SSE} was given in Chapter\ref{algo:bhh} and is presented in Equation \ref{eq:heuristics:gd:sse} below for convenience.
-
-\begin{equation}
-      \label{eq:heuristics:gd:sse}
-      \epsilon = \sum^{P_{T}}_{p=1}(t_{p} - o_{p})^{2}
-\end{equation}
-
-In Equation \ref{eq:heuristics:gd:sse}, $t_{p}$ and $o_{p}$ denote the target and ground truth output for the $p$-th training sample/pattern.
-$P_{t}$ is the total number of input-target vector pairs in the training set \cite{ref:engelbrecht:2007}.
-
-The aim of \ac{GD} is then to find some candidate solution for the weights of the \ac{FFNN} that minimises the error $\epsilon$.
-\citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} states that this is done by calculating the gradient of $\epsilon$ in \textit{weight-space} and to move the weight vector along the negative gradient.
-An illustration of this is given in Figure \ref{fig:heuristics:gd:gd_illustration}.
+Although \acs{GD} \index{heuristic}heuristics where not the first \index{heuristic}heuristics used to train \ac{FFNN}
+\cite{ref:engelbrecht:2007}, they are certainly the most whidely used.
+\Acs{GD} heuristics have become increasingly popular partly due to their simplicity and low computational overhead compared to other \index{heuristic}heuristics such as \index{meta-heuristic}meta-heuristics and other second-order derivative methods such as Newtons' method.
+There are many variants of \acs{GD} \index{heuristic}heuristics, however, they all fundamentally apply the same generic \acs{GD} framework called \acl{BP}.
+
+\subsection{Backpropagation}\label{sec:heuristics:gd:backpropagation}
+
+Chapter~\ref{chap:anns} introduced the reader to \index {supervised learning}supervised learning and presented a number of loss functions.
+In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \ac{FFNN} and the desired output.
+When using \acs{GD} to train \acp{FFNN}, the \index{loss function}loss function is used to adjust the weights of the \ac{FFNN} in order to minimise the error \cite{ref:engelbrecht:2007}.
+\citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} states that training of \acp{FFNN} using \acs{GD}, is done by calculating the gradient of $\epsilon$ in \textit{weight-space}, and then moving the weight vector along the negative gradient.
+An illustration of \acs{GD} is given in Figure~\ref{fig:heuristics:gd:gd_illustration}.
 
 \begin{figure}[htbp]
-      \includegraphics[width=\textwidth]{images/gradient_descent.png}
-      \caption{An illustration of \ac{GD} over various timestep showing the minimisation of the error with regard to weight value.}
+      \centering
+      \includegraphics[width=0.85\textwidth]{images/gradient_descent.pdf}
+      \caption{An illustration of \ac{GD} over various timesteps showing the minimisation of the error with regards to weight value.}
       \label{fig:heuristics:gd:gd_illustration}
@@
 
-The update-step for \ac{GD} can then be formulated as is shown in Equations \ref{eq:heuristics:gd:update_step_part_1}-\ref{eq:heuristics:gd:update_step_part_3} below.
+\noindent
+The update step for \ac{GD} can be formulated as is shown in Equation~\eqref{eq:heuristics:gd:update_step_part_1} below.
 
@@
 
-where
+\noindent
+In Equation~\eqref{eq:heuristics:gd:update_step_part_1} above, the delta weight $\Delta w$, at index $i$ and timestep $t$ is given by Equation~\eqref{eq:heuristics:gd:update_step_part_2} below.
 
@@
 
-and
+\noindent
+In Equation~\eqref{eq:heuristics:gd:update_step_part_2} above, $\eta$ is the learning rate.
+The learning rate is an important hyper-parameter in gradient-based \index{heuristic}heuristic as it controls the step-size that is taken in the direction of the negative gradient at each timestep.
+Assuming the use of \acs{SSE} as the loss function, the partial derivative of $\epsilon$, relative to the weight $w$, at index $i$, is given by Equation~\eqref{eq:heuristics:gd:update_step_part_3} below.
 
@@
 
-In Equation \ref{eq:heuristics:gd:update_step_part_2}, $\eta$ is the learning rate.
-The learning rate is an important hyper-parameter in the \ac{GD} heuristic as it controls the step-size that is taken in the direction of the negative gradient at each timestep.
-
-In the context of \ac{FFNN} training, this error signal is propagated backwards in the network.
-This algorithm is known as \ac{BP} and was popularised by \citeauthor{ref:werbos:1994} \cite{ref:werbos:1994}.
-\citeauthor{ref:nel:2021} \cite{ref:nel:2021} states that \ac{BP} provides a procedure for updating the network weights by evaluating the derivatives of the error function $\epsilon$ with respect to the weights.
-\Ac{BP} consists out of the two phases \cite{ref:engelbrecht:2007}.
-These include:
-
-\begin{itemize}
-      \item \textbf{Feedforward Pass}: During this phase the the output values if calculcated for the \ac{FFNN} for each training pattern.
-      \item \textbf{Backward Propagation}: During this phase the error signal that is calculated as is shown above in Equations \ref{eq:heuristics:gd:update_step_part_1}-\ref{eq:heuristics:gd:update_step_part_3} is propagated backwards from the output layer to the input layer of the \ac{FFNN}.
+\noindent
+In the context of training \textit{shallow} \acp{FFNN} using \index{supervised learning}supervised learning, the error signal is propagated backwards in the network from the output layer, through the hidden layer.
+The algorithm that propagates the error signal backwardds is known as \acf{BP}.
+\Acs{BP} was popularised by \citeauthor{ref:werbos:1994} \cite{ref:werbos:1994}.
+\citeauthor{ref:nel:2021} \cite{ref:nel:2021} states that \acs{BP} provides a procedure for updating the network weights, layer by layer, by evaluating the derivatives of the error function $\epsilon$ with respect to the weights at each layer.
+\citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007}describes the \acs{BP} process in two steps:
+
+\begin{itemize}
+      \item \textbf{Feedforward Pass}: During this phase the output values of the \acs{FFNN} is calculcated for each training pattern.
+      \item \textbf{Backward Propagation}: During this phase the error signal that is calculated as is shown above in Equations~\eqref{eq:heuristics:gd:update_step_part_1}-~\eqref{eq:heuristics:gd:update_step_part_3} is propagated backwards from the output layer, through the hidden layer, to the input layer of the \ac{FFNN}.
 Weights are then adjusted as functions of the backpropagated error signal.
@@
 
-From the concepts mentioned above, the full \ac{BP} process for training \acp{FFNN} can be formulated.
-\citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} presents such an example and is given next.
-
-\subsubsection*{Backpropogation of Feedforward Neural Networks}
-
-In order to present the example for \ac{BP} as applied to \acp{FFNN}, a number of assumptions are made. These include:
-
-\begin{itemize}
-      \item The \ac{SSE} is used as the objective function.
-      \item The sigmoid activation function is used in both the input and output layers.
-      \item Biases are included through augmented vectors as was presented in Chapter \ref{chap:anns}
-      \item \Acp{SU} are used in the input and output layers.
-      \item Stochastic learning is used where a small subset of the training patterns, called a \textit{mini-batch}, is presented at a time (\ac{SGD} is discussed in further detail later in Section \ref{sec:heuristics:gd:sgd}).
-\end{itemize}
-
-Then, for each training pattern $z_{p}$ the output of the objective function is given in Equation \ref{eq:heuristics:gd:bp:sse} below.
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:sse}
-      \epsilon_{p} = \frac{1}{2}\left(\frac{\sum^{K}_{k=1}(t_{k,p} - o_{k,p})^{2}}{K}\right)
-\end{equation}
-
-In Equation \ref{eq:heuristics:gd:bp:sse}, $K$ represents the number of output units and $t_{k,p}$ and $o_{k,p}$ are respectively the target and output values of the $k$-th output unit.
-
-The rest of the derivations are presented only for a single pattern. The subscript $p$ is thus omitted for convenience. The output of each layer is given as
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:output_1}
-      o_{k} = f_{o_{k}}(net_{o_{k}}) = \frac{1}{1 + e^{-net_{o_{k}}}}
-\end{equation}
-
-and
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:output_2}
-      y_{k} = f_{y_{k}}(net_{y_{k}}) = \frac{1}{1 + e^{-net_{y_{k}}}}
-\end{equation}
-
-The weights of the \ac{FFNN} are then updated according to Equations \ref{eq:heuristics:gd:bp:output_hto} and \ref{eq:heuristics:gd:bp:output_ith} below.
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:output_hto}
-      w_{kj}(t) \hspace{3mm} += \hspace{3mm} \Delta w_{kj}(t) + \alpha \Delta w_{kj}(t - 1)
-\end{equation}
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:output_ith}
-      v_{ji}(t) \hspace{3mm} += \hspace{3mm} \Delta v_{ji}(t) + \alpha \Delta v_{ji}(t - 1)
-\end{equation}
-
-In Equations \ref{eq:heuristics:gd:bp:output_hto} and \ref{eq:heuristics:gd:bp:output_ith} $\alpha$ represents the \textit{momentum} and is discussed in more detail later in Section \ref{sec:heuristics:gd:momentum}.
-The remainder of the derivations are focused on calculating $\Delta w_{kj}(t)$ and $\Delta v_{ji}(t)$.
-As such, the reference to time $(t)$ is omitted for convenience.
-
-From Equation \ref{eq:heuristics:gd:bp:output_hto} it follows that
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:partial_output}
-      \frac{\partial o_{k}}{\partial net_{o_{k}}} = \frac{\partial f_{o_{k}}}{\partial net_{o_{k}}} = (1 - o_{k})o_{k} = f'_{o_{k}}
-\end{equation}
-
-and
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:partial_hidden}
-      \frac{\partial net_{o_{k}}}{\partial w_{kj}} = \frac{\partial}{\partial w_{jk}}\left( \sum^{J+1}_{j=1}w_{kj}y_{j}\right) = y_{j}
-\end{equation}
-
-In Equation \ref{eq:heuristics:gd:bp:partial_output} $f'_{o_{k}}$ represents the derivative of the corresponding activation function.
-From Equations \ref{eq:heuristics:gd:bp:partial_output} and \ref{eq:heuristics:gd:bp:partial_hidden}, using the chain-rule, it follows that
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:partial_output_hidden}
-      \begin{split}
-            \frac{\partial o_{k}}{\partial w_{kj}}
-            &= \frac{\partial o_{k}}{\partial net_{o_{k}}}\frac{\partial net_{o_{k}}}{\partial w_{kj}}\\
-            &= (1 - o_{k})o_{k}y_{j}\\
-            &= f'_{o_{k}}y_{j}
-      \end{split}
-\end{equation}
-
-From Equation \ref{eq:heuristics:gd:bp:sse} it follows that
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:partial_error}
-      \frac{\partial \epsilon}{\partial o_{k}} = \frac{\partial}{\partial o_{k}}\left( \frac{1}{2} \sum^{K}_{k=1}(t_{k} - o_{k})^{2} \right) = -(t_{k} - o_{k})
-\end{equation}
-
-Define the error signal that needs to be back-propagated as $\delta_{o_{k}} = \frac{\partial \epsilon}{\partial net_{o_{k}}}$.
-Then, from Equations \ref{eq:heuristics:gd:bp:partial_output} and \ref{eq:heuristics:gd:bp:partial_error} it follows that
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:delta_output}
-      \begin{split}
-            \delta_{o_{k}}
-            &= \frac{\partial \epsilon}{\partial net_{o_{k}}}\\
-            &= \frac{\partial \epsilon}{\partial o_{k}}\frac{\partial o_{k}}{\partial net_{o_{k}}}\\
-            &= -(t_{k} - o_{k})(1 - o_{k})o_{k}\\
-            &= -(t_{k} - o_{k})f'_{o_{k}}
-      \end{split}
-\end{equation}
-
-The changes in the hidden-to-output weights are then computed from Equations \ref{eq:heuristics:gd:bp:partial_output_hidden}, \ref{eq:heuristics:gd:bp:partial_error} and \ref{eq:heuristics:gd:bp:delta_output} as follows.
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:delta_hidden_to_output}
-      \begin{split}
-            \Delta w_{kj}
-            &= \eta \left( - \frac{\partial \epsilon}{\partial w_{kj}} \right)\\
-            &= -\eta \frac{\partial \epsilon}{\partial o_{k}}\frac{\partial o_{k}}{\partial w_{kj}}\\
-            &= -\eta \delta_{o_{k}}y_{j}
-      \end{split}
-\end{equation}
-
-Continuing on with the input-to-hidden weights as follows
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_1}
-      \begin{split}
-            \frac{\partial y_{j}}{\partial net_{y_{j}}}
-            &= \frac{\partial f_{y_{j}}}{\partial net_{y_{j}}}\\
-            &= (1 - y_{j})y_{j}\\
-            &= f'_{y_{j}}
-      \end{split}
-\end{equation}
-
-and
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_2}
-      \begin{split}
-            \frac{\partial net_{y_{j}}}{\partial v_{ji}}
-            &= \frac{\partial}{\partial v_{ji}}\left( \sum^{I+1}_{i=1}v_{ji}z_{i}\right)\\
-            &= z_{i}
-      \end{split}
-\end{equation}
-
-From Equations \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_1} and \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_2} it follows that
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_3}
-      \begin{split}
-            \frac{\partial y_{j}}{\partial v_{ji}}
-            &= \frac{\partial y_{j}}{\partial net_{y_{j}}}\frac{\partial net_{y_{j}}}{\partial v_{ji}}\\
-            &= (1 - y_{j})y_{j}z_{i}\\
-            &= f'_{y_{j}}z_{i}
-      \end{split}
-\end{equation}
-
-and
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_4}
-      \begin{split}
-            \frac{\partial net_{o_{k}}}{\partial y_{j}}
-            &= \frac{\partial}{\partial y_{j}}\left( \sum^{J+1}_{j=1}w_{kj}y_{j}\right)\\
-            &= w_{kj}
-      \end{split}
-\end{equation}
-
-From Equations \ref{eq:heuristics:gd:bp:delta_hidden_to_output} and \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_4} it follows that
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_5}
-      \begin{split}
-            \frac{\partial \epsilon}{\partial y_{j}}
-            &= \frac{\partial}{\partial y_{j}}\left( \frac{1}{2} \sum^{K}_{k=1} (t_{k} - o_{k})^{2} \right)\\
-            &= \sum^{K}_{k=1}\frac{}{} \frac{\partial \epsilon}{\partial o_{k}} \frac{\partial o_{k}}{\partial net_{o_{k}}} \frac{\partial net_{o_{k}}}{\partial y_{j}}\\
-            &= \sum^{K}_{k=1} \frac{\partial \epsilon}{\partial net_{o_{k}}} \frac{\partial net_{o_{k}}}{\partial y_{j}}\\
-            &= \sum^{K}_{k=1} \delta_{o_{k}}w_{kj}
-      \end{split}
-\end{equation}
-
-Define the hidden layer error which needs to be back-propagated from Equations \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_1} and \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_5} as
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:delta_hidden}
-      \begin{split}
-            \delta_{y_{j}}
-            &= \frac{\partial \epsilon}{\partial net_{y_{j}}}\\
-            &= \frac{\partial \epsilon}{\partial y_{j}} \frac{\partial y_{j}}{\partial net_{y_{j}}}\\
-            &= \sum^{K}_{k=1}\delta_{o_{k}}w_{kj}f'_{y_{j}}
-      \end{split}
-\end{equation}
-
-Finally, the changes to the input-to-hidden weights can then be calculated from Equations \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_3}, \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_5} and \ref{eq:heuristics:gd:bp:delta_hidden} as follows
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:delta_input_to_hidden}
-      \begin{split}
-            \Delta v_{ji}
-            &= \eta \left( - \frac{\partial \epsilon}{\partial v_{ji}} \right)\\
-            &= -\eta \frac{\partial \epsilon}{\partial y_{j}} \frac{\partial y_{j}}{\partial v_{ji}}\\
-            &= -\eta \delta_{y_{j}}z_{i}
-      \end{split}
-\end{equation}
-
-If the \ac{FFNN} include direct weights from the input to output layer, the following additional weight updates are required.
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:delta_input_to_output}
-      \begin{split}
-            \Delta u_{ki}
-            &= \eta \left( - \frac{\partial \epsilon}{\partial u_{ki}} \right)\\
-            &= -\eta \frac{\partial \epsilon}{\partial o_{k}} \frac{\partial o_{k}}{\partial u_{ki}}\\
-            &= -\eta \delta_{o_{k}}z_{i}
-      \end{split}
-\end{equation}
-
-In Equation \ref{eq:heuristics:gd:bp:delta_input_to_output} above, $u_{ki}$ is a weight from the $i$-th input unit to the $k$-th output unit.
-
-The derivations above assumed stochastic learning, however, if batch learning is applied, weight updates are given in Equations \ref{eq:heuristics:gd:bp:delta_hidden_to_output_batch_learning} and \ref{eq:heuristics:gd:bp:delta_input_to_hidden_batch_learning} below
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:delta_hidden_to_output_batch_learning}
-      \begin{split}
-            \Delta w_{kj}(t) = \sum^{P_{T}}_{p=1} \Delta w_{kj,p}(t)
-      \end{split}
-\end{equation}
-
-\begin{equation}
-      \label{eq:heuristics:gd:bp:delta_input_to_hidden_batch_learning}
-      \begin{split}
-            \Delta v_{kj}(t) = \sum^{P_{T}}_{p=1} \Delta v_{kj,p}(t)
-      \end{split}
-\end{equation}
-
-where $\Delta w_{kj}(t)$ and $\Delta v_{kj}(t)$ are weight updates for individual patterns $p$ and $P_{T}$ is the total number of patterns in the training set.
-
-Equations \ref{eq:heuristics:gd:bp:sse} through \ref{eq:heuristics:gd:bp:delta_input_to_hidden} provided the reader with the detailed derivations of the \ac{BP} weight-update components as it resolves from the error signal.
-The following sections provide the reader with variants of the \ac{BP} algorithm as presented in this section.
-
-\subsection{Stochastic Gradient Descent}
-\label{sec:heuristics:gd:sgd}
-
-Section \ref{sec:heuristics:gd:backpropagation} already assumed the use of stochastic learning and thus provided the detailed derivation of a specific variant of \ac{BP} called \acl{SGD}.
-Separation of theory and implementation is done such that the detail of the theory need not be repeated for each gradient-based variant.
+\subsection{Stochastic Gradient Descent}\label{sec:heuristics:gd:sgd}
+
 This section shines light on the algorithmic implementation of \ac{BP} with specific context to \ac{SGD}.
@@
 
-The pseudo-code implementation for the \ac{SGD} algorithm is taken from \cite{ref:engelbrecht:2007} and is presented in Algorithm \ref{algo:heuristics:gd:sgd} below.
+The pseudo-code implementation for the \ac{SGD} algorithm is taken from \cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:gd:sgd} below.
 
@@
 
-In Equation \ref{eq:heuristics:gd:sgd} $w$ refers to the weights of the \ac{FFNN}, $\eta$ refers to the learning rate as before and $\nabla_{w}\mathcal{E}(w)$ refers to the gradient of the loss/cost function w.r.t the output of the \ac{FFNN} as a result of its weights.
+In Equation~\ref{eq:heuristics:gd:sgd} $w$ refers to the weights of the \ac{FFNN}, $\eta$ refers to the learning rate as before and $\nabla_{w}\mathcal{E}(w)$ refers to the gradient of the loss/cost function w.r.t the output of the \ac{FFNN} as a result of its weights.
 Note that all subscripts w.r.t.
@@
 As such, weight updates are done with high variance and noise \cite{ref:ruder:2016}.
-An illustration of the the fluctuations caused by \ac{SGD} during training is given in Figure \ref{fig:heuristics:gd:sgd}.
+An illustration of the the fluctuations caused by \ac{SGD} during training is given in Figure~\ref{fig:heuristics:gd:sgd}.
 
@@
 As such, \ac{SGD} is shown to oscillate across the slopes of the ravine while only making minor progress towards the local minima.
-An illustration of this is given in Figure \ref{fig:heuristics:gd:sgd_with_and_without_momentum}.
+An illustration of this is given in Figure~\ref{fig:heuristics:gd:sgd_with_and_without_momentum}.
 
@@
 \cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$ of the weight update vector of the previous timestep to the current weight update vector.
-The accumulation of momentum is presented in Equation \ref{eq:heuristics:gd:momentum_part_1} while the update step is then amended in Equation \ref{eq:heuristics:gd:momentum_part_2} below.
+The accumulation of momentum is presented in Equation~\ref{eq:heuristics:gd:momentum_part_1} while the update step is then amended in Equation~\ref{eq:heuristics:gd:momentum_part_2} below.
 
@@
 In the \ac{NAG} heuristic, the gradient is not calculated w.r.t the current weights, but rather w.r.t the approximate future positions of the weights \cite{ref:ruder:2016}.
-An illustration of this is taken from Geoffrey Hinton's lecture on mini-batch \ac{GD} \cite{ref:hinton:2012} and is presented in Figure \ref{fig:heuristics:gd:nag} below.
+An illustration of this is taken from Geoffrey Hinton's lecture on mini-batch \ac{GD} \cite{ref:hinton:2012} and is presented in Figure~\ref{fig:heuristics:gd:nag} below.
 
@@
 \ac{Momentum} first computes the current gradient.
-This is seen by the small blue vector presented in Figure \ref{fig:heuristics:gd:nag}.
+This is seen by the small blue vector presented in Figure~\ref{fig:heuristics:gd:nag}.
 A large step is taken in the direction of the updated accumulated gradient, presented by the big blue vector.
@@
 By anticipating approximate future positions of the weights, the weight update step as defined by \ac{NAG} controls the optimisation process from from going too fast and results in increased responsiveness.
-The \ac{NAG} weight vector update steps are given in Equations \ref{eq:heuristics:gd:nag_part_1} and \ref{eq:heuristics:gd:nag_part_2} below.
+The \ac{NAG} weight vector update steps are given in Equations~\ref{eq:heuristics:gd:nag_part_1} and~\ref{eq:heuristics:gd:nag_part_2} below.
 
@@
 \Ac{Adagrad} uses a different learning rate for every weight $w_{i}$ at every timestep $t$.
-The weight update step as implemented by \ac{Adagrad} is presented in Equation \ref{eq:heuristics:gd:adagrad_part_1} below.
+The weight update step as implemented by \ac{Adagrad} is presented in Equation~\ref{eq:heuristics:gd:adagrad_part_1} below.
 
@@
 Since $G_{t}$ contains the sum of the squares of the gradients with respect to all parameters $w$ along its diagonal, the weight update step can be vectorised and updated using the matrix-vector product between $G_{t}$ and $\nabla_{w_{i}}\mathcal{E}(w_{i})$.
-This is presented in Equation \ref{eq:heuristics:gd:adagrad_part_2} below.
+This is presented in Equation~\ref{eq:heuristics:gd:adagrad_part_2} below.
 
@@
 
-In Section \ref{sec:heuristics:adagrad} it was mentioned that one of the main problems of \ac{Adagrad} is that it has an aggressively monotonically decreasing learning rate because of the accumulation of the sum of squared gradients in its denominator.
+In Section~\ref{sec:heuristics:adagrad} it was mentioned that one of the main problems of \ac{Adagrad} is that it has an aggressively monotonically decreasing learning rate because of the accumulation of the sum of squared gradients in its denominator.
 Zeiler \cite{ref:zeiler:2012} presents an improvement on \ac{Adagrad} that eliminates this problem.
@@
 In order to simplify the notation of update steps, let $g = \nabla_{w_{i}}\mathcal{E}(w_{t})$.
-The moving average update step for $E[g^{2}]_{t}$ is then presented in Equation \ref{eq:heuristics:gd:adadelta_part_1} below.
+The moving average update step for $E[g^{2}]_{t}$ is then presented in Equation~\ref{eq:heuristics:gd:adadelta_part_1} below.
 
@@
 For sake of clarity, the basic \ac{SGD} update step is rewritten in terms of the weight update vector $\Delta w_{t}$.
-This is presented in Equations \ref{eq:heuristics:gd:adadelta_part_2} and \ref{eq:heuristics:gd:adadelta_part_2} below.
+This is presented in Equations~\ref{eq:heuristics:gd:adadelta_part_2} and~\ref{eq:heuristics:gd:adadelta_part_2} below.
 
@@
 
-The weight update vector for \ac{Adagrad} as defined in Equation \ref{eq:heuristics:gd:adagrad_part_2} is then rewritten as
+The weight update vector for \ac{Adagrad} as defined in Equation~\ref{eq:heuristics:gd:adagrad_part_2} is then rewritten as
 
@@
 
-The diagonal matrix $G_{t}$ is then replaced with the decaying average over the past $W$ squared gradients as presented in Equation \ref{eq:heuristics:gd:adadelta_part_4} below.
+The diagonal matrix $G_{t}$ is then replaced with the decaying average over the past $W$ squared gradients as presented in Equation~\ref{eq:heuristics:gd:adadelta_part_4} below.
 
@@
 
-\citeauthor{ref:ruder:2016}\cite{ref:ruder:2016} highlights that the original authors \cite{ref:zeiler:2012} noted that the units of the update step as presented in Equation \ref{eq:heuristics:gd:adadelta_part_2} do not match i.e.
+\citeauthor{ref:ruder:2016}\cite{ref:ruder:2016} highlights that the original authors \cite{ref:zeiler:2012} noted that the units of the update step as presented in Equation~\ref{eq:heuristics:gd:adadelta_part_2} do not match i.e.
 the update vector should have the same hypothetical units as the weight vector.
-To realize this, another exponentially decaying average is defined in terms of squared weight updates as is presented in Equation \ref{eq:heuristics:gd:adadelta_part_6} below.
+To realize this, another exponentially decaying average is defined in terms of squared weight updates as is presented in Equation~\ref{eq:heuristics:gd:adadelta_part_6} below.
 
@@
 It is thus approximated with the \ac{RMS} of weight updates until the previous timestep.
-The learning rate in Equation \ref{eq:heuristics:gd:adadelta_part_5} is then replaced as follows.
+The learning rate in Equation~\ref{eq:heuristics:gd:adadelta_part_5} is then replaced as follows.
 
@@
 \citeauthor{ref:ruder:2016}\cite{ref:ruder:2016} mentions that \ac{RMSProp} is in fact the same as the first weight update vector as defined for \ac{Adadelta}.
-The update step for \ac{RMSProp} is then defined in terms of a decaying running average of gradients squared as is presented again for convenience in Equations \ref{eq:heuristics:gd:rmsprop_part_1} and \ref{eq:heuristics:gd:rmsprop_part_2} below.
+The update step for \ac{RMSProp} is then defined in terms of a decaying running average of gradients squared as is presented again for convenience in Equations~\ref{eq:heuristics:gd:rmsprop_part_1} and~\ref{eq:heuristics:gd:rmsprop_part_2} below.
 
@@
 
-The decaying averages for past gradients and past squared gradients is given in Equations \ref{eq:heuristics:gd:adam_part_1} and \ref{eq:heuristics:gd:adam_part_2} respectively.
+The decaying averages for past gradients and past squared gradients is given in Equations~\ref{eq:heuristics:gd:adam_part_1} and~\ref{eq:heuristics:gd:adam_part_2} respectively.
 
@@
 
-In Equations \ref{eq:heuristics:gd:adam_part_1} and \ref{eq:heuristics:gd:adam_part_2} above, $\beta_{1}$ and $\beta_{2}$ are decay rates, similar to $\alpha$ for \ac{Momentum}.
+In Equations~\ref{eq:heuristics:gd:adam_part_1} and~\ref{eq:heuristics:gd:adam_part_2} above, $\beta_{1}$ and $\beta_{2}$ are decay rates, similar to $\alpha$ for \ac{Momentum}.
 
@@
 These biases need to be corrected.
-The bias-corrected first and second moment estimates are presented in Equations \ref{eq:heuristics:gd:adam_bc_first_moment} and \ref{eq:heuristics:gd:adam_bc_second_moment} below.
+The bias-corrected first and second moment estimates are presented in Equations~\ref{eq:heuristics:gd:adam_bc_first_moment} and~\ref{eq:heuristics:gd:adam_bc_second_moment} below.
 
@@
 
-The \ac{Adam} update rule is then presented in Equation \ref{eq:heuristics:gd:adam} below.
+The \ac{Adam} update rule is then presented in Equation~\ref{eq:heuristics:gd:adam} below.
 
@@
 The particle's update step is then broken into two parts.
-These include a velocity update step presented in Equation \ref{eq:heuristics:pso:velocity} followed by a position update step as presented in Equation \ref{eq:heuristics:pso:position} below.
+These include a velocity update step presented in Equation~\ref{eq:heuristics:pso:velocity} followed by a position update step as presented in Equation~\ref{eq:heuristics:pso:position} below.
 
@@
 
-In Equations \ref{eq:heuristics:pso:velocity} and \ref{eq:heuristics:pso:position}, $i$ refers to the $i$-th particle in the swarm, $j$ refers to the $j$-th dimension of vectors with dimensionality $N$ defined by the optimisation problem.
+In Equations~\ref{eq:heuristics:pso:velocity} and~\ref{eq:heuristics:pso:position}, $i$ refers to the $i$-th particle in the swarm, $j$ refers to the $j$-th dimension of vectors with dimensionality $N$ defined by the optimisation problem.
 A breakdown of the components introduced above is required.
@@
 The idea behind velocity clamping is to restrict particle velocities to some $V_{max}$ threshold, in essence, modeling a form of terminal velocity.
-Velocity clamping is applied after the velocity update step and is given in Equation \ref{eq:heuristics:pso:velocity_clamping} below.
+Velocity clamping is applied after the velocity update step and is given in Equation~\ref{eq:heuristics:pso:velocity_clamping} below.
 
@@
 
-An example of the pseudo code implementation of the \textit{gbest} \ac{PSO} is taken from \cite{ref:engelbrecht:2007} and is given in Algorithm \ref{algo:heuristics:pso:gbest} below.
+An example of the pseudo code implementation of the \textit{gbest} \ac{PSO} is taken from \cite{ref:engelbrecht:2007} and is given in Algorithm~\ref{algo:heuristics:pso:gbest} below.
 
@@
 Importantly, all of these entities must be unique such that $i \neq i_{1} \neq i_{2} \neq i_{3}$ and $i_{2}, i_{3} \sim U(1, N_{s}$ where $N_{s}$ is the size of the swarm.
-      \item These individual entities are then used to calculate the trial vector by perturbing the target vector as presented in Equation \ref{eq:heuristics:de:mutation} below.
+      \item These individual entities are then used to calculate the trial vector by perturbing the target vector as presented in Equation~\ref{eq:heuristics:de:mutation} below.
 \end{itemize}
@@
 
-In Equation \ref{eq:heuristics:de:mutation} $\beta \in (0, \infty)$ is the scale factor and controls the amplification of the differential variation \cite{ref:engelbrecht:2007}.
+In Equation~\ref{eq:heuristics:de:mutation} $\beta \in (0, \infty)$ is the scale factor and controls the amplification of the differential variation \cite{ref:engelbrecht:2007}.
 Note that in the above steps, the selection strategy to select the target vector is not specified.
-Selection is discussed in Section \ref{sec:heuristics:mh:de:selection} below.
+Selection is discussed in Section~\ref{sec:heuristics:mh:de:selection} below.
 
@@
 The same applies to \ac{DE}.
-The \ac{DE} crossover operator implements a discrete recombination of the trial vector, $u_{i}(t)$ (as was generated in Section \ref{sec:heuristics:mh:de:mutation} above) and the parent vector $x_{i}(t)$ to produce new offspring $x'_{i}(t)$.
-The crossover operator is given in Equation \ref{eq:heuristics:de:crossover} below.
+The \ac{DE} crossover operator implements a discrete recombination of the trial vector, $u_{i}(t)$ (as was generated in Section~\ref{sec:heuristics:mh:de:mutation} above) and the parent vector $x_{i}(t)$ to produce new offspring $x'_{i}(t)$.
+The crossover operator is given in Equation~\ref{eq:heuristics:de:crossover} below.
 
@@
 
-In Equation \ref{eq:heuristics:de:crossover}, $x_{ij}(t)$ refers to the $j$-th element of the vector $x_{i}(t)$ and $\mathcal{J}$ refers to a set of crossover points or indices at which perturbation is done.
+In Equation~\ref{eq:heuristics:de:crossover}, $x_{ij}(t)$ refers to the $j$-th element of the vector $x_{i}(t)$ and $\mathcal{J}$ refers to a set of crossover points or indices at which perturbation is done.
 Different techniques for determining the set, $\mathcal{J}$ has been proposed \cite{ref:storn:1996}\cite{ref:storn:1997}.
@@
       \item \textbf{Binomial crossover}: A crossover mask is generated by randomly selecting indices from the set of possible crossover points $\{1,2,\dots,N_{x}$ where $N_{x}$ is the problem dimension.
-This techique is presented in Algorithm \ref{algo:heuristics:de:bin} below.
-In Algorithm \ref{algo:heuristics:de:bin} $p_{r}$ is the crossover probability.
+This techique is presented in Algorithm~\ref{algo:heuristics:de:bin} below.
+In Algorithm~\ref{algo:heuristics:de:bin} $p_{r}$ is the crossover probability.
 The higher the value of $p_{r}$, the more points will be included in the set $\mathcal{J}$.
-A \textit{Bernoulli} distribution (presented in Chapter \ref{chap:probability} can be used to generate the binomial crossover mask.
+A \textit{Bernoulli} distribution (presented in Chapter~\ref{chap:probability} can be used to generate the binomial crossover mask.
 Note that due to the probabilistic nature of this process, it is possible that no crossover points are selected.
@@
 $p_{r}$ is the same crossover probability as mentioned above for binomial crossover.
-The implementation of exponential crossover is given in Algorithm \ref{algo:heuristics:de:exp} below.
+The implementation of exponential crossover is given in Algorithm~\ref{algo:heuristics:de:exp} below.
 \end{itemize}
@@
 
-Selection refers to the technique that is used to determine which entities are included in the mutation operator to produce a trial vector \cite{ref:engelbrecht:2007} as was shown in Section \ref{sec:heuristics:mh:de:mutation} above.
+Selection refers to the technique that is used to determine which entities are included in the mutation operator to produce a trial vector \cite{ref:engelbrecht:2007} as was shown in Section~\ref{sec:heuristics:mh:de:mutation} above.
 Various selection operators have been suggested.
@@
 
-Algorithm \ref{algo:heuristics:de:general_de} is taken from \cite{ref:engelbrecht:2007} and presents the general \ac{DE} algorithm.
+Algorithm~\ref{algo:heuristics:de:general_de} is taken from \cite{ref:engelbrecht:2007} and presents the general \ac{DE} algorithm.
 The population is initialised by randomly placing entities in the search space such that the positions of the entities are confined to some search boundary.
@@
 These include \ac{PSO} and \ac{DE}.
-The \ac{DE} heuristic that was presented in Section \ref{sec:heuristics:mh:de} is one type of \ac{EC} algorithm.
+The \ac{DE} heuristic that was presented in Section~\ref{sec:heuristics:mh:de} is one type of \ac{EC} algorithm.
 This section introduces another population-based, nature-inspired optimisation \ac{EC} algorithm named \aclp{GA}.
@@
 This algorithm is also referred to as the canonical \ac{GA} (CGA) and was proposed by Holland \cite{ref:holland:1992}.
-The generic \ac{EC} algorithm is taken from \cite{ref:engelbrecht:2007} and is is presented in Algorithm \ref{algo:heuristics:ga:generic_ec} below.
+The generic \ac{EC} algorithm is taken from \cite{ref:engelbrecht:2007} and is is presented in Algorithm~\ref{algo:heuristics:ga:generic_ec} below.
 
@@
 
-From Algorithm \ref{algo:heuristics:ga:generic_ec} above it can be seen that a number of components influence the search process. These include:
+From Algorithm~\ref{algo:heuristics:ga:generic_ec} above it can be seen that a number of components influence the search process. These include:
 
@@
 During crossover, parents are selected using a selection operator.
-Selection operators are discussed later in Section \ref{sec:heuristics:mh:ga:selection}.
+Selection operators are discussed later in Section~\ref{sec:heuristics:mh:ga:selection}.
 As with \acp{DE}, recombination is applied probabilistically and thus, selection of a parent does not guarantee reproduction.
@@
 Uniform crossover refers to a crossover operator where an $N_{x}$-dimensional crossover mask is generated randomly \cite{ref:syswerda:1989}.
-Uniform crossover is illustrated in Figure \ref{fig:heuristics:mh:ga:uniform_crossover} below and the algorithm for uniform crossover is given in Algorithm \ref{algo:heuristics:mh:ga:uniform_crossover}.
+Uniform crossover is illustrated in Figure~\ref{fig:heuristics:mh:ga:uniform_crossover} below and the algorithm for uniform crossover is given in Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover}.
 
@@
 
-In Algorithm \ref{algo:heuristics:mh:ga:uniform_crossover} above, $p_{x}$ is the bitswapping probability.
+In Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover} above, $p_{x}$ is the bitswapping probability.
 
@@
 For the purposes of this dissertation, the application of the mutation operator on $x_{ij}(t)$ results in a small update step for that gene such that $x'_{ij}(t) = x_{ij}(t) + v_{ij}(t)$.
-In this case, $v_{ij}(t) \sim U(-limit, limit)$ and $limit = \sqrt{\frac{6}{fanin + fanout}}$ as presented for Glorot uniform sampling in \ref{chap:anns}.
-An adaptation of the uniform mutation operator is then provided in Algorithm \ref{algo:heuristics:mh:ga:uniform_mutation} below.
+In this case, $v_{ij}(t) \sim U(-limit, limit)$ and $limit = \sqrt{\frac{6}{fanin + fanout}}$ as presented for Glorot uniform sampling in~\ref{chap:anns}.
+An adaptation of the uniform mutation operator is then provided in Algorithm~\ref{algo:heuristics:mh:ga:uniform_mutation} below.
 
@@
 
-An illustration of the adapted uniform mutation operator is presented in Figure \ref{fig:heuristics:mh:ga:uniform_mutation} below.
+An illustration of the adapted uniform mutation operator is presented in Figure~\ref{fig:heuristics:mh:ga:uniform_mutation} below.
 
@@
 The more entities that survive to the next generation, the lower the diversity of the new population.
-It is later shown in \ref{chap:bhh} that the proposed \ac{BHH} can incorporate a form of elitism in its credit assignment strategy.
+It is later shown in~\ref{chap:bhh} that the proposed \ac{BHH} can incorporate a form of elitism in its credit assignment strategy.
 \end{itemize}

### 2022-10-22 dissertation/appendix/backpropagation.tex
🚧 WIP - Save point*

\chapter{Backpropagation}\label{app:backpropagation}

This appendix provides a full breakdown of the \acs{BP} algorithm as is provided by \citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007}.

In order to present the example for \ac{BP} as applied to \acp{FFNN}, a number of assumptions are made. These include:

\begin{itemize}
      \item The \ac{SSE} is used as the objective function.
      \item The sigmoid activation function is used in both the input and output layers.
      \item Biases are included through augmented vectors as was presented in Chapter \ref{chap:anns}
      \item \Acp{SU} are used in the input and output layers.
      \item Stochastic learning is used where a small subset of the training patterns, called a \textit{mini-batch}, is presented at a time (\ac{SGD} is discussed in further detail later in Section \ref{sec:heuristics:gd:sgd}).
\end{itemize}

Then, for each training pattern $z_{p}$ the output of the objective function is given in Equation \ref{eq:heuristics:gd:bp:sse} below.

\begin{equation}
      \label{eq:heuristics:gd:bp:sse}
      \epsilon_{p} = \frac{1}{2}\left(\frac{\sum^{K}_{k=1}(t_{k,p} - o_{k,p})^{2}}{K}\right)
\end{equation}

In Equation \ref{eq:heuristics:gd:bp:sse}, $K$ represents the number of output units and $t_{k,p}$ and $o_{k,p}$ are respectively the target and output values of the $k$-th output unit.

The rest of the derivations are presented only for a single pattern. The subscript $p$ is thus omitted for convenience. The output of each layer is given as

\begin{equation}
      \label{eq:heuristics:gd:bp:output_1}
      o_{k} = f_{o_{k}}(net_{o_{k}}) = \frac{1}{1 + e^{-net_{o_{k}}}}
\end{equation}

and

\begin{equation}
      \label{eq:heuristics:gd:bp:output_2}
      y_{k} = f_{y_{k}}(net_{y_{k}}) = \frac{1}{1 + e^{-net_{y_{k}}}}
\end{equation}

The weights of the \ac{FFNN} are then updated according to Equations \ref{eq:heuristics:gd:bp:output_hto} and \ref{eq:heuristics:gd:bp:output_ith} below.

\begin{equation}
      \label{eq:heuristics:gd:bp:output_hto}
      w_{kj}(t) \hspace{3mm} += \hspace{3mm} \Delta w_{kj}(t) + \alpha \Delta w_{kj}(t - 1)
\end{equation}

\begin{equation}
      \label{eq:heuristics:gd:bp:output_ith}
      v_{ji}(t) \hspace{3mm} += \hspace{3mm} \Delta v_{ji}(t) + \alpha \Delta v_{ji}(t - 1)
\end{equation}

In Equations \ref{eq:heuristics:gd:bp:output_hto} and \ref{eq:heuristics:gd:bp:output_ith} $\alpha$ represents the \textit{momentum} and is discussed in more detail later in Section \ref{sec:heuristics:gd:momentum}. The remainder of the derivations are focused on calculating $\Delta w_{kj}(t)$ and $\Delta v_{ji}(t)$. As such, the reference to time $(t)$ is omitted for convenience.

From Equation \ref{eq:heuristics:gd:bp:output_hto} it follows that

\begin{equation}
      \label{eq:heuristics:gd:bp:partial_output}
      \frac{\partial o_{k}}{\partial net_{o_{k}}} = \frac{\partial f_{o_{k}}}{\partial net_{o_{k}}} = (1 - o_{k})o_{k} = f'_{o_{k}}
\end{equation}

and

\begin{equation}
      \label{eq:heuristics:gd:bp:partial_hidden}
      \frac{\partial net_{o_{k}}}{\partial w_{kj}} = \frac{\partial}{\partial w_{jk}}\left( \sum^{J+1}_{j=1}w_{kj}y_{j}\right) = y_{j}
\end{equation}

In Equation \ref{eq:heuristics:gd:bp:partial_output} $f'_{o_{k}}$ represents the derivative of the corresponding activation function. From Equations \ref{eq:heuristics:gd:bp:partial_output} and \ref{eq:heuristics:gd:bp:partial_hidden}, using the chain-rule, it follows that

\begin{equation}
      \label{eq:heuristics:gd:bp:partial_output_hidden}
      \begin{split}
            \frac{\partial o_{k}}{\partial w_{kj}}
            &= \frac{\partial o_{k}}{\partial net_{o_{k}}}\frac{\partial net_{o_{k}}}{\partial w_{kj}}\\
            &= (1 - o_{k})o_{k}y_{j}\\
            &= f'_{o_{k}}y_{j}
      \end{split}
\end{equation}

From Equation \ref{eq:heuristics:gd:bp:sse} it follows that

\begin{equation}
      \label{eq:heuristics:gd:bp:partial_error}
      \frac{\partial \epsilon}{\partial o_{k}} = \frac{\partial}{\partial o_{k}}\left( \frac{1}{2} \sum^{K}_{k=1}(t_{k} - o_{k})^{2} \right) = -(t_{k} - o_{k})
\end{equation}

Define the error signal that needs to be back-propagated as $\delta_{o_{k}} = \frac{\partial \epsilon}{\partial net_{o_{k}}}$. Then, from Equations \ref{eq:heuristics:gd:bp:partial_output} and \ref{eq:heuristics:gd:bp:partial_error} it follows that

\begin{equation}
      \label{eq:heuristics:gd:bp:delta_output}
      \begin{split}
            \delta_{o_{k}}
            &= \frac{\partial \epsilon}{\partial net_{o_{k}}}\\
            &= \frac{\partial \epsilon}{\partial o_{k}}\frac{\partial o_{k}}{\partial net_{o_{k}}}\\
            &= -(t_{k} - o_{k})(1 - o_{k})o_{k}\\
            &= -(t_{k} - o_{k})f'_{o_{k}}
      \end{split}
\end{equation}

The changes in the hidden-to-output weights are then computed from Equations \ref{eq:heuristics:gd:bp:partial_output_hidden}, \ref{eq:heuristics:gd:bp:partial_error} and \ref{eq:heuristics:gd:bp:delta_output} as follows.

\begin{equation}
      \label{eq:heuristics:gd:bp:delta_hidden_to_output}
      \begin{split}
            \Delta w_{kj}
            &= \eta \left( - \frac{\partial \epsilon}{\partial w_{kj}} \right)\\
            &= -\eta \frac{\partial \epsilon}{\partial o_{k}}\frac{\partial o_{k}}{\partial w_{kj}}\\
            &= -\eta \delta_{o_{k}}y_{j}
      \end{split}
\end{equation}

Continuing on with the input-to-hidden weights as follows

\begin{equation}
      \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_1}
      \begin{split}
            \frac{\partial y_{j}}{\partial net_{y_{j}}}
            &= \frac{\partial f_{y_{j}}}{\partial net_{y_{j}}}\\
            &= (1 - y_{j})y_{j}\\
            &= f'_{y_{j}}
      \end{split}
\end{equation}

and

\begin{equation}
      \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_2}
      \begin{split}
            \frac{\partial net_{y_{j}}}{\partial v_{ji}}
            &= \frac{\partial}{\partial v_{ji}}\left( \sum^{I+1}_{i=1}v_{ji}z_{i}\right)\\
            &= z_{i}
      \end{split}
\end{equation}

From Equations \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_1} and \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_2} it follows that

\begin{equation}
      \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_3}
      \begin{split}
            \frac{\partial y_{j}}{\partial v_{ji}}
            &= \frac{\partial y_{j}}{\partial net_{y_{j}}}\frac{\partial net_{y_{j}}}{\partial v_{ji}}\\
            &= (1 - y_{j})y_{j}z_{i}\\
            &= f'_{y_{j}}z_{i}
      \end{split}
\end{equation}

and

\begin{equation}
      \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_4}
      \begin{split}
            \frac{\partial net_{o_{k}}}{\partial y_{j}}
            &= \frac{\partial}{\partial y_{j}}\left( \sum^{J+1}_{j=1}w_{kj}y_{j}\right)\\
            &= w_{kj}
      \end{split}
\end{equation}

From Equations \ref{eq:heuristics:gd:bp:delta_hidden_to_output} and \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_4} it follows that

\begin{equation}
      \label{eq:heuristics:gd:bp:partial_input_to_hidden_part_5}
      \begin{split}
            \frac{\partial \epsilon}{\partial y_{j}}
            &= \frac{\partial}{\partial y_{j}}\left( \frac{1}{2} \sum^{K}_{k=1} (t_{k} - o_{k})^{2} \right)\\
            &= \sum^{K}_{k=1}\frac{}{} \frac{\partial \epsilon}{\partial o_{k}} \frac{\partial o_{k}}{\partial net_{o_{k}}} \frac{\partial net_{o_{k}}}{\partial y_{j}}\\
            &= \sum^{K}_{k=1} \frac{\partial \epsilon}{\partial net_{o_{k}}} \frac{\partial net_{o_{k}}}{\partial y_{j}}\\
            &= \sum^{K}_{k=1} \delta_{o_{k}}w_{kj}
      \end{split}
\end{equation}

Define the hidden layer error which needs to be back-propagated from Equations \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_1} and \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_5} as

\begin{equation}
      \label{eq:heuristics:gd:bp:delta_hidden}
      \begin{split}
            \delta_{y_{j}}
            &= \frac{\partial \epsilon}{\partial net_{y_{j}}}\\
            &= \frac{\partial \epsilon}{\partial y_{j}} \frac{\partial y_{j}}{\partial net_{y_{j}}}\\
            &= \sum^{K}_{k=1}\delta_{o_{k}}w_{kj}f'_{y_{j}}
      \end{split}
\end{equation}

Finally, the changes to the input-to-hidden weights can then be calculated from Equations \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_3}, \ref{eq:heuristics:gd:bp:partial_input_to_hidden_part_5} and \ref{eq:heuristics:gd:bp:delta_hidden} as follows

\begin{equation}
      \label{eq:heuristics:gd:bp:delta_input_to_hidden}
      \begin{split}
            \Delta v_{ji}
            &= \eta \left( - \frac{\partial \epsilon}{\partial v_{ji}} \right)\\
            &= -\eta \frac{\partial \epsilon}{\partial y_{j}} \frac{\partial y_{j}}{\partial v_{ji}}\\
            &= -\eta \delta_{y_{j}}z_{i}
      \end{split}
\end{equation}

If the \ac{FFNN} include direct weights from the input to output layer, the following additional weight updates are required.

\begin{equation}
      \label{eq:heuristics:gd:bp:delta_input_to_output}
      \begin{split}
            \Delta u_{ki}
            &= \eta \left( - \frac{\partial \epsilon}{\partial u_{ki}} \right)\\
            &= -\eta \frac{\partial \epsilon}{\partial o_{k}} \frac{\partial o_{k}}{\partial u_{ki}}\\
            &= -\eta \delta_{o_{k}}z_{i}
      \end{split}
\end{equation}

In Equation \ref{eq:heuristics:gd:bp:delta_input_to_output} above, $u_{ki}$ is a weight from the $i$-th input unit to the $k$-th output unit.

The derivations above assumed stochastic learning, however, if batch learning is applied, weight updates are given in Equations \ref{eq:heuristics:gd:bp:delta_hidden_to_output_batch_learning} and \ref{eq:heuristics:gd:bp:delta_input_to_hidden_batch_learning} below

\begin{equation}
      \label{eq:heuristics:gd:bp:delta_hidden_to_output_batch_learning}
      \begin{split}
            \Delta w_{kj}(t) = \sum^{P_{T}}_{p=1} \Delta w_{kj,p}(t)
      \end{split}
\end{equation}

\begin{equation}
      \label{eq:heuristics:gd:bp:delta_input_to_hidden_batch_learning}
      \begin{split}
            \Delta v_{kj}(t) = \sum^{P_{T}}_{p=1} \Delta v_{kj,p}(t)
      \end{split}
\end{equation}

where $\Delta w_{kj}(t)$ and $\Delta v_{kj}(t)$ are weight updates for individual patterns $p$ and $P_{T}$ is the total number of patterns in the training set.

Equations \ref{eq:heuristics:gd:bp:sse} through \ref{eq:heuristics:gd:bp:delta_input_to_hidden} provided the reader with the detailed derivations of the \ac{BP} weight-update components as it resolves from the error signal. The following sections provide the reader with variants of the \ac{BP} algorithm as presented in this section.

### 2022-10-22 dissertation/chapters/01-introduction.tex
🚧 WIP - Save point*
🚧 WIP - Save point (compiles)

@@
 \noindent
-\Ac{ML} is one of the most popular fields of research in \ac{AI} studies today.
-In recent years, \ac{ML} research has seen some notable achievements in academia \cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large \cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.
-\ac{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \ac{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1 \cite{ref:san-hun:2016}.
+\Acf{ML} is one of the most popular fields of research in \acf{AI} studies today.
+In recent years, \acs{ML} research has seen some notable achievements in academia~\cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large~\cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.
+\acs{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \acs{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1~\cite{ref:san-hun:2016}.
 
-Over the past few years, modern hardware capabilities have improved to the point where workloads in the field of \ac{ML} that were previously computationally infeasible, are now possible.
-One such sub-field of \ac{ML} is \acp{ANN}.
-\acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain \cite{ref:engelbrecht:2007}.
+Over the past few years, modern hardware capabilities have improved to the point where workloads in the field of \acs{ML} that were previously computationally infeasible, are now possible.
+One such sub-field of \acs{ML} is \acp{ANN}.
+\acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain~\cite{ref:engelbrecht:2007}.
 \acp{ANN} can be trained, which is the equivalent of ``learning'' from data.
@@
 Decision making as an ability provides a wide-range of applications from healthcare to finance and yields great interest in the field.
-With the improvement of hardware came an influx of \ac{ML} researchers that focused their attention on training of \acp{ANN}.
+With the improvement of hardware came an influx of \acs{ML} researchers that focused their attention on training of \acp{ANN}.
 
-\Acfp{FFNN} are specific types of \acp{ANN} \cite{ref:reed:1999}.
+\Acfp{FFNN} are specific types of \acp{ANN}~\cite{ref:reed:1999}.
 A popular field of focus for studying \acp{ANN} is the process by which these models are trained.
@@
 Training of \acp{ANN} is seen as an optimisation problem.
-The \ac{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''.
-A search algorithm known as a \index{heuristic}\textit{heuristic} \cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised.
+The \acs{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''.
+A search algorithm known as a \index{heuristic}\textit{heuristic}~\cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \acs{ANN}, such that a specified objective function is minimised.
 The research presented in this disseration focuses on the development of a specific type of heuristic, called a \acf{HH} to train \acp{FFNN} in a supervised learning approach.
@@
 This means that a particular approach that works well for one domain or problem class, often does not necessarily work for another.
-This problem is known as the \ac{NFL} \cite{ref:wolpert:1997}.
+This problem is known as the \acf{NFL}~\cite{ref:wolpert:1997}.
 
@@
 An example of such a technique is to dynamically adjust and learn the heuristic \index{hyper-parameters}\textit{hyper-parameters} as part of the learning process.
-This field of study is known as \index{meta-learning}meta-learning \cite{ref:giraud:2004}.
-\index{meta-learning}Meta-learning of heuristic hyper-parameters as applied in the training of \acp{ANN} has shown to yield good generalisation results \cite{ref:hospedales:2020, ref:vilalta:2002}.
+This field of study is known as \index{meta-learning}meta-learning~\cite{ref:giraud:2004}.
+\index{meta-learning}Meta-learning of heuristic hyper-parameters as applied in the training of \acp{ANN} has shown to yield good generalisation results~\cite{ref:hospedales:2020, ref:vilalta:2002}.
 
-The dynamic nature of the learning process leads towards the idea that \ac{ML} models could be trained in a way such that the learning process and learning mechanism applied are not statically defined, but rather dynamic and under the control of some mechanism.
+The dynamic nature of the learning process leads towards the idea that \acs{ML} models could be trained in a way such that the learning process and learning mechanism applied are not statically defined, but rather dynamic and under the control of some mechanism.
 
@@
 Heterogeneous learning approaches make use of different \textit{search behaviours} by selecting from a behaviour pool.
-Heterogeneous approaches have shown to balance the trade-off between exploration and exploitation \cite{ref:nepomuceno:2013}.
+Heterogeneous approaches have shown to balance the trade-off between exploration and exploitation~\cite{ref:nepomuceno:2013}.
 
-A step further in the concept of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem \cite{ref:burke:2013}.
+A step further in the concept of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem~\cite{ref:burke:2013}.
 These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic-space} to solve a specific problem.
-One such form of \ac{HH} is a population-based approach that guides the search process by automatically selecting heuristics from a heuristic-pool to be applied to a collection of different candidate solutions in the solution-space.
+One such form of \acs{HH} is a population-based approach that guides the search process by automatically selecting heuristics from a heuristic-pool to be applied to a collection of different candidate solutions in the solution-space.
 This collection of candidate solutions are referred to as a \textit{population} of \textit{entities}, where each \textit{entity} is a single candidate solution to the problem being optimised.
@@
 \acp{HH} that implement such a selection strategy are referred to as \textit{selection} \acp{HH}.
-The term \textit{selection} refers to the ability of the \ac{HH} to select the best heuristic from a pool of low-level heuristics.
+The term \textit{selection} refers to the ability of the \acs{HH} to select the best heuristic from a pool of low-level heuristics.
 
-One specific type of selection \ac{HH} is called a \index{multi-method populated-based meta-heuristic}\textit{multi-method population-based \index{meta-heuristic}meta-heuristic} \cite{ref:vanderstockt:2018}.
+One specific type of selection \acs{HH} is called a \index{multi-method populated-based meta-heuristic}\textit{multi-method population-based \index{meta-heuristic}meta-heuristic}~\cite{ref:vanderstockt:2018}.
 The term \index{multi-method}\textit{multi-method} refers to the incorporation of different low-level heuristics, with different search behaviours, into the heuristic-space.
 The term \textit{population-based} refers to the utilisation of a population of entities that represent candidate solutions.
-Finally, the term \index{meta-heuristic}\textit{meta-heuristics} refers to the \ac{HH} as a heuristic that does not have any domain knowledge and only makes use of information from the search process.
+Finally, the term \index{meta-heuristic}\textit{meta-heuristics} refers to the \acs{HH} as a heuristic that does not have any domain knowledge and only makes use of information from the search process.
 
-\citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} mentioned that \acp{HH} have been shown to solve a number of problems including bin-packing, examination timetabling, production scheduling, the traveling salesman problem, vehicle routing problem and many more.
+\citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} mentioned that \acp{HH} have been shown to solve a number of problems including bin-packing, examination timetabling, production scheduling, the traveling salesman problem, vehicle routing problem and many more.
 
@@
 
-Many different heuristics have been developed and used to train \acp{FFNN} \cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
+Many different heuristics have been developed and used to train \acp{FFNN}~\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
 Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses.
-Finding the best heuristic to train the \ac{FFNN} is required in order to yield optimal results.
+Finding the best heuristic to train the \acs{FFNN} is required in order to yield optimal results.
 This process is often non-trivial and could be a time-consuming exercise.
-Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is problem dependent \cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
+Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is problem dependent~\cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
 
@@
 In the past, researchers selected the best heuristic by trail and error.
-A set of heuristics and carefully selected hyper-parameters would be implemented, followed by an empirical test to evaluate the performance of each heuristic for a given problem domain \cite{ref:pillay:2015}.
+A set of heuristics and carefully selected hyper-parameters would be implemented, followed by an empirical test to evaluate the performance of each heuristic for a given problem domain~\cite{ref:pillay:2015}.
 In this way, researchers were able to determine which heuristics and which hyper-parameters performed well for different problems.
@@
 A modern approach is to use \acp{HH} to automate the process of selecting the best heuristic when applied to some optimisation problem.
-The best heuristic might not be a single heuristic, but rather a hybridisation of heuristics \cite{ref:pillay:2015}.
+The best heuristic might not be a single heuristic, but rather a hybridisation of heuristics~\cite{ref:pillay:2015}.
 
 In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
-Some notable examples include the \index{simulated annealing}simulated annealing-based \ac{HH} by \citeauthor{ref:dowsland:2007} \cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \ac{HH} of \citeauthor{ref:burke:2010} \cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by \citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} and work done by \citeauthor{ref:vanderstockt:2018} \cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based meta-heuristics in real-valued dynamic optimization.
-However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.
-\citeauthor{ref:nel:2021} \cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
+Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based meta-heuristics in real-valued dynamic optimization.
+However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
 
 \acp{FFNN} training is seen as a computational search problem.
-\acf{HH} as defined by Burke et al.
-\cite{ref:burke:2010} is ``a search method or learning mechanism for selecting or generating heuristics to solve computational search problems''.
+\acf{HH} as defined by Burke et al.~\cite{ref:burke:2010} is ``a search method or learning mechanism for selecting or generating heuristics to solve computational search problems''.
 \acp{HH} is a field of research aimed at the automated selection, combination, adaptation or generation of multiple lower-level heuristics to efficiently solve computational search problems.
 
-\citeauthor{ref:grobler:2012} \cite{ref:grobler:2012} mention that the focus of \acp{HH} is on automating the development of the \textit{learning mechanism} used to find the best heuristic to obtain an appropriate solution to an optimisation problem.
-\citeauthor{ref:grobler:2012} explain that \acp{HH} employ a high-level heuristic that focuses on finding the best low-level heuristic in heuristic-space that could include \textit{single-method} and \textit{multi-method} optimisation algorithms (heuristics).
+\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} mention that the focus of \acp{HH} is on automating the development of the \textit{learning mechanism} used to find the best heuristic to obtain an appropriate solution to an optimisation problem.~\citeauthor{ref:grobler:2012} explain that \acp{HH} employ a high-level heuristic that focuses on finding the best low-level heuristic in heuristic-space that could include \textit{single-method} and \textit{multi-method} optimisation algorithms (heuristics).
 \acp{HH} relieve the burden of having to select the best heuristic to use by trial and error.
-Furthermore, \acp{HH} can generally be applied to multiple problems given that the set of low-level heuristics include heuristics that have the potential to solve the problem at hand \cite{ref:burke:2010}.
+Furthermore, \acp{HH} can generally be applied to multiple problems given that the set of low-level heuristics include heuristics that have the potential to solve the problem at hand~\cite{ref:burke:2010}.
 Automation of the heuristic selection process and the general application to a wider range of problems are characteristics of \acp{HH} that can be beneficial when applied in the context of \acp{FFNN} training.
 
-Note that training of \acp{FFNN} using \acp{HH} is not to be confused with the training of \acp{FFNN} using \index{ensemble networks}\textit{ensemble networks} or \index{query by committees}\textit{query by committees}.
-\citeauthor{ref:pappa:2014} \cite{ref:pappa:2014} describe \index{ensemble networks}ensemble networks as a combination method in \index{meta-learning}meta-learning whereby multiple \acp{ANN} are jointly used to solve a problem.
+Note that training of \acp{FFNN} using \acp{HH} is not to be confused with the training of \acp{FFNN} using \index{ensemble networks}\textit{ensemble networks} or \index{query by committees}\textit{query by committees}.~\citeauthor{ref:pappa:2014}~\cite{ref:pappa:2014} describe \index{ensemble networks}ensemble networks as a combination method in \index{meta-learning}meta-learning whereby multiple \acp{ANN} are jointly used to solve a problem.
 Each member network in the ensemble is trained using a specified heuristic, and generally this heuristic is applied to the same member throughout the training process.
-The results of all of the member networks are then joined together using some consensus mechanism \cite{ref:zhou:2002}.
+The results of all of the member networks are then joined together using some consensus mechanism~\cite{ref:zhou:2002}.
 This mechanism could be weighted averages, majority voting or weighted voting.
@@
 This research develops the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
-This selection probability distribution is the mechanism by which the \ac{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.
+This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.
 This process takes place dynamically and during the training process (online learning).
@@
 
-The main objective of this research is focused on developing a novel \Ac{BHH} selection mechanism in a \ac{HH} framework that can be used to train \acp{FFNN}.
+The main objective of this research is focused on developing a novel \Acf{BHH} selection mechanism in a \acs{HH} framework that can be used to train \acp{FFNN}.
 In order to reach this objective, the following sub-objectives are defined.
@@
 \begin{itemize}
-      \item Conduct a literature study on \acp{ANN} in order to provide the necessary background information of the \ac{AN}, \acp{FFNN} and the training process.
+      \item Conduct a literature study on \acp{ANN} in order to provide the necessary background information of the \acs{AN}, \acp{FFNN} and the training process.
 
       \item Conduct a literature study on different types of heuristics that have been used to train \acp{FFNN}.
-The literature study will provide the necessary background information to understand how different heuristics can be used in the set of heuristics to be selected to train the \ac{FFNN}.
+The literature study will provide the necessary background information to understand how different heuristics can be used in the set of heuristics to be selected to train the \acs{FFNN}.
 
@@
 
-      \item Develop a novel \Ac{BHH} selection mechanism for a \ac{HH} that makes use of Bayesian statistics to guide the \ac{HH} search process while training \acp{FFNN} on different problems.
+      \item Develop a novel \Acs{BHH} selection mechanism for a \acs{HH} that makes use of Bayesian statistics to guide the \acs{HH} search process while training \acp{FFNN} on different problems.
 
-      \item Conduct an empirical study to show that the developed \Ac{BHH} can effectively be used to train \acp{FFNN}.
+      \item Conduct an empirical study to show that the developed \Acs{BHH} can effectively be used to train \acp{FFNN}.
 
-      \item Conduct an empirical study to investigate the behavioural characteristics of the \ac{BHH} as it is used to train \acp{FFNN} on an example problem.
+      \item Conduct an empirical study to investigate the behavioural characteristics of the \Acs{BHH} as it is used to train \acp{FFNN} on an example problem.
 
-      \item Conduct an empirical study and critically evaluate the performance of the developed \Ac{BHH} compared to individual heuristics in the heuristic-space as they are used to train \acp{FFNN} on a number of different problems.
+      \item Conduct an empirical study and critically evaluate the performance of the developed \Acs{BHH} compared to individual heuristics in the heuristic-space as they are used to train \acp{FFNN} on a number of different problems.
 
-      \item Conduct an empirical study that investigates variations of the \Ac{BHH} and the effects of design decisions and hyper-parameters on the search process.
+      \item Conduct an empirical study that investigates variations of the \Acs{BHH} and the effects of design decisions and hyper-parameters on the search process.
 
@@
       \item A novel heuristic selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acp{FFNN}.
-The resulting \ac{HH} is referred to as the \acf{BHH}.
+The resulting \acs{HH} is referred to as the \acf{BHH}.
 
-      \item The results of the empirical study show with statistical significance and certainty that the \Ac{BHH} performs generally well on multiple problems.
-It is shown that, for each problem, the \Ac{BHH} performance is comparable to the best low-level heuristics (for the particular problem) included in the heuristic selection pool.
+      \item The results of the empirical study show with statistical significance and certainty that the \Acs{BHH} performs generally well on multiple problems.
+It is shown that, for each problem, the \Acs{BHH} performance is comparable to the best low-level heuristics (for the particular problem) included in the heuristic selection pool.
 
-      \item The results of the empirical study show that the \Ac{BHH} is able to select the best heuristic to train \ac{FFNN} in general.
+      \item The results of the empirical study show that the \Acs{BHH} is able to select the best heuristic to train \acp{FFNN} in general.
 This relieves researchers from the burden of having to do this selection process manually through trial and error.
 
-      \item The results of the empirical study show that the \Ac{BHH}, given a diverse set of lower-level heuristics, will generally produce good results when applied to multiple problems at the same time.
+      \item The results of the empirical study show that the \Acs{BHH}, given a diverse set of lower-level heuristics, will generally produce good results when applied to multiple problems at the same time.
 
-      \item Finally, the results of the empirical study show that the \Ac{BHH} is capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from what comes before''.} knowledge in which a predefined selection bias is used for heuristics that are known to be well suited for certain problems.
+      \item Finally, the results of the empirical study show that the \Acs{BHH} is capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from what comes before''.} knowledge in which a predefined selection bias is used for heuristics that are known to be well suited for certain problems.
 \end{itemize}
@@
       \item \textbf{Chapter~\ref{chap:hhs}} presents a literature study on the details of \acp{HH} and \index{meta-learning}meta-learning in general.
-A discussion follows on the current landscape of \ac{HH} research and a review of different selection approaches for \acp{HH} is conducted.
+A discussion follows on the current landscape of \acs{HH} research and a review of different selection approaches for \acp{HH} is conducted.
 It is shown how \acp{HH} are suitable for \acs{FFNN} training.
@@
 
-      \item \textbf{Chapter~\ref{chap:bhh}} presents the developed \Ac{BHH}.
-It is shown how the \Ac{BHH} is implemented as a selection mechanism in the context of a \ac{HH} framework.
-The \Ac{BHH} is shown to implement a \index{Na\"ive Bayes classifier}Na\"ive Bayes classifier.
+      \item \textbf{Chapter~\ref{chap:bhh}} presents the developed \Acs{BHH}.
+It is shown how the \Acs{BHH} is implemented as a selection mechanism in the context of a \acs{HH} framework.
+The \Acs{BHH} is shown to implement a \index{Na\"ive Bayes classifier}Na\"ive Bayes classifier.
 The probabilistic model that is implemented is derived and discussed in detail.
@@
 The update step (training step) for prior probability concentration parameters is derived and discussed in detail.
-The \Ac{BHH} algorithmic implementation, variants and suggested application are presented as well.
+The \Acs{BHH} algorithmic implementation, variants and suggested application are presented as well.
 
       \item \textbf{Chapter~\ref{chap:methodology}} presents a detailed description of the empirical process and the setup of each experiment.
-It discusses the datasets used, the \ac{FFNN} architecture and topology used, heuristics that are used, the configuration of hyper-parameters, initialisation techniques used and performance measures used.
+It discusses the datasets used, the \acs{FFNN} architecture and topology used, heuristics that are used, the configuration of hyper-parameters, initialisation techniques used and performance measures used.
 Finally, discussions follow on how the results are analysed.
@@
       \item \textbf{Chapter~\ref{chap:results}} provides and discusses the results of the empirical study in detail.
-A baseline comparison is done by comparing the performance of the \Ac{BHH} to that of all the individual lower-level heuristics on all datasets.
+A baseline comparison is done by comparing the performance of the \Acs{BHH} to that of all the individual lower-level heuristics on all datasets.
 These datasets include classification and regression problems of various sizes and complexity.
-Detailed results are presented on the performance of the \Ac{BHH} as a selection mechanism for \acp{HH} and a brief comparison is made to other selection mechanisms.
-Finally, results are presented on the effects of the hyper-parameters of the \Ac{BHH} on the training process.
-Discussions follow on how the \Ac{BHH} is shown to automate the selection of the best heuristic during the training of \acp{FFNN}, as applied to a range of problems, alleviating the burden on researchers to apply traditional trial and error approaches.
-The chapter is concluded with a brief argument in favor of the general applicability of the \Ac{BHH} to more problem domains.
+Detailed results are presented on the performance of the \Acs{BHH} as a selection mechanism for \acp{HH} and a brief comparison is made to other selection mechanisms.
+Finally, results are presented on the effects of the hyper-parameters of the \Acs{BHH} on the training process.
+Discussions follow on how the \Acs{BHH} is shown to automate the selection of the best heuristic during the training of \acp{FFNN}, as applied to a range of problems, alleviating the burden on researchers to apply traditional trial and error approaches.
+The chapter is concluded with a brief argument in favor of the general applicability of the \Acs{BHH} to more problem domains.
 
@@
 \begin{itemize}
-      \item \textbf{Appendix~\ref{app:backpropagation}} provides a full breakdown of the \acf{BP} algorithm as presented by \citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007}.
+      \item \textbf{Appendix~\ref{app:backpropagation}} provides a full breakdown of the \acf{BP} algorithm as presented by~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007}.
+
+      \item \textbf{Appendix~\ref{app:datasets}} provides details on the datasets used for the empirical analysis.
+
+      \item \textbf{Appendix~\ref{app:statistical_analysis}} provides details on the outcomes of the statistical analyses.
 
@@
       \item \textbf{Appendix~\ref{app:acronyms}} provides a list of the important acronyms used or newly defined in the course of this work, as well as their associated definitions.
-
-      \item \textbf{Appendix~\ref{app:datasets}} provides details on the datasets used for the empirical analysis.
-
-      \item \textbf{Appendix~\ref{app:statistical_analysis}} provides details on the outcomes of the statistical analyses.
 

### 2022-10-22 dissertation/chapters/02-artificial-neural-networks.tex
🚧 WIP - Save point (compiles)

@@
 It gives us the ability to think and learn.
-The field of \acs{ML} has taken a lot of inspiration from the biological brain which lead to the development of \acp{ANN} \cite{ref:rosenblatt:1958}.
+The field of \acs{ML} has taken a lot of inspiration from the biological brain which lead to the development of \acp{ANN}~\cite{ref:rosenblatt:1958}.
 \acp{ANN} are used throughout this dissertation as the \textit{model} to be trained using \acp{HH}.
@@
 \noindent
-The biological neural systems are made up of microscopic nerve cells called neurons \cite{ref:jain:1996}.
+The biological neural systems are made up of microscopic nerve cells called neurons~\cite{ref:jain:1996}.
 Figure~\ref{fig:biological_neuron} illustrates a single \acs{BN}.
@@
 \Acp{NN} are formed through the connections between the \index{axon}axons and \index{dendrites}dendrites of various neurons.
-This is known as \index{synaptogenesis}\textit{synaptogenesis} \cite{ref:huttenlocher:1997}.
+This is known as \index{synaptogenesis}\textit{synaptogenesis}~\cite{ref:huttenlocher:1997}.
 Such a connection is referred to as a \index{synapse}\textit{synapse}.
 Communication takes place, through the synapse, by electro-chemical pulse and is often referred to as an \textit{activation} or \textit{action potential}.
-Communication signals propagate from the \index{dendrites}dendrites, through the cell body to the axon of a neuron, provoking a signal in the post-synaptic neuron \cite{ref:engelbrecht:2007}.
+Communication signals propagate from the \index{dendrites}dendrites, through the cell body to the axon of a neuron, provoking a signal in the post-synaptic neuron~\cite{ref:engelbrecht:2007}.
 The greater the connection between two neurons, the stronger the communication.
-Kennedy \cite{ref:kennedy:2016} defines stronger \index{synapse}synapses as ones that contribute more depolarisation to the neural membrane upon activation than weaker ones.
+Kennedy~\cite{ref:kennedy:2016} defines stronger \index{synapse}synapses as ones that contribute more depolarisation to the neural membrane upon activation than weaker ones.
 Stronger \index{synapse}synapses have a higher probability of generating an action potential in the post-synaptic neuron.
-During activation, the pre-synaptic neuron release neurotransmitters that bind to the post-synaptic neuron \cite{ref:khanacademy:synapse}.
+During activation, the pre-synaptic neuron release neurotransmitters that bind to the post-synaptic neuron~\cite{ref:khanacademy:synapse}.
 The frequent release of these molecules cause the \index{synapse}synapse to grow.
 Connections that grow over time yield stronger signals (learning), while connections that are weak propagate low intensity signals and vanish over time (forgetting).
-The ability of synapses to strengthen and weaken over time is known as \index{synaptic plasticity}\textit{synaptic plasticity} \cite{ref:huttenlocher:1997}.
+The ability of synapses to strengthen and weaken over time is known as \index{synaptic plasticity}\textit{synaptic plasticity}~\cite{ref:huttenlocher:1997}.
 
@@
 $\mathbb{R}^{T}$, usually in the ranges $[0,1]$ or $[-1,1]$, depending on the
-activation function used \cite{ref:engelbrecht:2007} and is given
+activation function used~\cite{ref:engelbrecht:2007} and is given
 in Equation~\eqref{eq:an_function_mapping} below.
@@
 Input signals are $I$-dimensional vectors of numerical values that are obtained either through some environment sensor or from other \acp{AN}.
-Input signals are often referred to as \index{features}\textit{features} or \index{independent variables}\textit{independent variables} \cite{ref:francis:2001}.
+Input signals are often referred to as \index{features}\textit{features} or \index{independent variables}\textit{independent variables}~\cite{ref:francis:2001}.
 Throughout this dissertation, a single input vector is referred to as a \textit{pattern}.
@@
 
-Input pre-processing improves the training process and contributes to the success of the practical application of the \acs{ANN} \cite{ref:kuzniar:2017}.
+Input pre-processing improves the training process and contributes to the success of the practical application of the \acs{ANN}~\cite{ref:kuzniar:2017}.
 The primary purpose of input pre-processing is to modify the input data so that it can better match predicted output data.
@@
 For qualitative data, the class labels have to be converted from textual to numerical representations.
-In general, class labels are encoded as numerical vectors \cite{ref:srinidhi:2018, ref:brownlee:2017:one-hot}.
+In general, class labels are encoded as numerical vectors~\cite{ref:srinidhi:2018, ref:brownlee:2017:one-hot}.
 One such encoding technique is referred to as \index{one-hot encoding}\textit{one-hot encoding}.
-Harris and Harris \cite{ref:harris:2010} describe \index{one-hot encoding}one-hot encoding as a group of vector elements where the classes are represented with a single high element (represented by $1$) and all the others low (represented by $0$).
+Harris and Harris~\cite{ref:harris:2010} describe \index{one-hot encoding}one-hot encoding as a group of vector elements where the classes are represented with a single high element (represented by $1$) and all the others low (represented by $0$).
 Each element $y_k$, where $k$ is the $k$-th element of the encoded vector $\vec{y}$, uniquely refers to a class.
@@
 Normalisation and scaling yields input data that is comparable to the output produced by the \acs{AN}.
-For the purposes of this disseration, the \index{min-max scaler}min-max scaler \cite{ref:al:2006} and the \index{standard score scaler}standard score scaler \cite{ref:jain:2005} are considered.
+For the purposes of this disseration, the \index{min-max scaler}min-max scaler~\cite{ref:al:2006} and the \index{standard score scaler}standard score scaler~\cite{ref:jain:2005} are considered.
 
@@
 Changes in the weight associated with a feature changes the influence that that particular feature has on the predicted output.
-Finding the correct value for each weight, such that the \acs{AN} yields optimal output, is an optimisation problem \cite{ref:thierens:1993}.
-Research has shown that weight initialisation plays an important role in the efficient training of \acp{ANN} \cite{ref:thimm:1995}.
+Finding the correct value for each weight, such that the \acs{AN} yields optimal output, is an optimisation problem~\cite{ref:thierens:1993}.
+Research has shown that weight initialisation plays an important role in the efficient training of \acp{ANN}~\cite{ref:thimm:1995}.
 
@@
 Weight initialisation is the process by which candidate solutions (represented by the weights of the \acs{AN}) to the problem are ``placed'' in the search-space.
-Weight initialisation influences the speed of convergence, the probability of convergence and the generalisation capabilities of \acp{ANN} \cite{ref:fernandez:2001}.
-Finding the optimal initialisation values for weights is non-trivial and can be seen as another optimisation problem \cite{ref:de:2016, ref:erdogmus:2003, ref:yam:2000}.
+Weight initialisation influences the speed of convergence, the probability of convergence and the generalisation capabilities of \acp{ANN}~\cite{ref:fernandez:2001}.
+Finding the optimal initialisation values for weights is non-trivial and can be seen as another optimisation problem~\cite{ref:de:2016, ref:erdogmus:2003, ref:yam:2000}.
 
 Weight initialisation is dependent on the \index{activation function}activation function used.
-If weights are initialised as values that are too small, the vanishing gradients problem can occur \cite{ref:hanin:2018}.
+If weights are initialised as values that are too small, the vanishing gradients problem can occur~\cite{ref:hanin:2018}.
 If weights are initialised as values that are too big, output of the activation function would not be in the active range.
-This leads to unit saturation, and exploding gradients can occur \cite{ref:hanin:2018, ref:yadav:2018}.
+This leads to unit saturation, and exploding gradients can occur~\cite{ref:hanin:2018, ref:yadav:2018}.
 
-Many different weight initialisation techniques have been developed \cite{ref:erdogmus:2003}.
-Some techniques have been developed to address the problems that are mentioned above \cite{ref:yadav:2018}.
-For the purposes of this dissertation, focus is put on \index{random uniform sampling}random uniform sampling, \index{Glorot uniform sampling}\textit{Glorot uniform (Xavier)} sampling and \index{Glorot normal sampling}\textit{Glorot normal} sampling \cite{ref:glorot:2010}.
+Many different weight initialisation techniques have been developed~\cite{ref:erdogmus:2003}.
+Some techniques have been developed to address the problems that are mentioned above~\cite{ref:yadav:2018}.
+For the purposes of this dissertation, focus is put on \index{random uniform sampling}random uniform sampling, \index{Glorot uniform sampling}\textit{Glorot uniform (Xavier)} sampling and \index{Glorot normal sampling}\textit{Glorot normal} sampling~\cite{ref:glorot:2010}.
 Brief discussions on each of these weight initialisation techniques are presented as follows.
@@
 \index{random uniform sampling}Random uniform sampling initialises weights uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $w_{i} \sim \textit{U} (\omega_{min}, \omega_{max})$, where the $\omega_{min}$ and $\omega_{max}$ are respectfully the lower and upper bounds of the uniform distribution.
-Suggested parameter values are $(-1, 1)$ or $(-0.5, 0.5)$ \cite{ref:nguyen:1990}.
+Suggested parameter values are $(-1, 1)$ or $(-0.5, 0.5)$~\cite{ref:nguyen:1990}.
 
@@
 $I$ and $K$ are respectfully the number of input and output units in the weight vector.
-\index{Glorot normal sampling}Glorot normal sampling has been shown to decrease training time \cite{ref:glorot:2010}.
+\index{Glorot normal sampling}Glorot normal sampling has been shown to decrease training time~\cite{ref:glorot:2010}.
 
@@
 
-A common way by which the \index{net input signal}net input signal is calculated is by means of \acp{SU} \cite{ref:engelbrecht:2007}, which compute the \index{net input signal}net input signal as the weighted sum of all input signals as shown in Equation~\eqref{eq:summation_units} below.
+A common way by which the \index{net input signal}net input signal is calculated is by means of \acp{SU}~\cite{ref:engelbrecht:2007}, which compute the \index{net input signal}net input signal as the weighted sum of all input signals as shown in Equation~\eqref{eq:summation_units} below.
 
@@
 
-A bias/threshold term $\theta$ is introduced to help translate the output of the \index{activation function}activation function \cite{ref:benitez:1997}.
+A bias/threshold term $\theta$ is introduced to help translate the output of the \index{activation function}activation function~\cite{ref:benitez:1997}.
 The value of $\theta$ can be learned during the training process along with the weights of the \acs{ANN}.
-In order to simplify equations, the input and weight vectors are augmented such that the input and hidden layers have an additional neuron/unit, called the \textit{bias unit} \cite{ref:engelbrecht:2007}.
+In order to simplify equations, the input and weight vectors are augmented such that the input and hidden layers have an additional neuron/unit, called the \textit{bias unit}~\cite{ref:engelbrecht:2007}.
 The net input signal can then be rewritten to consider the bias unit, leading to an augmented net input signal.
@@
 
-An \index{activation function}activation function is used to model the action potential of the \acs{AN} \cite{ref:ziv:1994, ref:hodgkin:1952}.
+An \index{activation function}activation function is used to model the action potential of the \acs{AN}~\cite{ref:ziv:1994, ref:hodgkin:1952}.
 The \index{activation function}activation function takes as a parameter, the augmented \index{net input signal}net input signal.
@@
 \noindent
-Many different \index{activation function}activation functions have been developed \cite{ref:karlik:2011}.
-For the purposes of this dissertation, focus is put on the \acf{ReLU} \cite{ref:jarrett:2009, ref:nair:2010}, the \acf{LReLU} \cite{ref:maas:2013}, the \index{sigmoid}sigmoid \cite{ref:lecun:1988} and the \index{hyperbolic tangent}hyperbolic tangent \cite{ref:lin:2008} \index{activation function}activation functions.
+Many different \index{activation function}activation functions have been developed~\cite{ref:karlik:2011}.
+For the purposes of this dissertation, focus is put on the \acf{ReLU}~\cite{ref:jarrett:2009, ref:nair:2010}, the \acf{LReLU}~\cite{ref:maas:2013}, the \index{sigmoid}sigmoid~\cite{ref:lecun:1988} and the \index{hyperbolic tangent}hyperbolic tangent~\cite{ref:lin:2008} \index{activation function}activation functions.
 
@@
 \noindent
-An advantage of \acs{ReLU} is that it is not susceptible to the \index{vanishing gradients problem}vanishing gradients problem \cite{ref:xu:2015, ref:maksutov:2018} which occurs when gradients in the first layers of a multi-layer \acs{ANN} approach zero, and have no effect on the training process.
+An advantage of \acs{ReLU} is that it is not susceptible to the \index{vanishing gradients problem}vanishing gradients problem~\cite{ref:xu:2015, ref:maksutov:2018} which occurs when gradients in the first layers of a multi-layer \acs{ANN} approach zero, and have no effect on the training process.
 
@@
 
-The \acf{LReLU} \index{activation function}activation function is a variant of the \acs{ReLU} \index{activation function}activation function that avoids zero gradients in the negative part of its argument by introducing a scaling parameter, $\alpha > 0$ \cite{ref:xu:2015}.
+The \acf{LReLU} \index{activation function}activation function is a variant of the \acs{ReLU} \index{activation function}activation function that avoids zero gradients in the negative part of its argument by introducing a scaling parameter, $\alpha > 0$~\cite{ref:xu:2015}.
 Similar to \acs{ReLU}, \acs{LReLU} is not susceptible to the \index{vanishing gradients problem}vanishing gradients problem.
-However, \acs{LReLU} does not suffer from the \index{dying ReLU problem}dying \acs{ReLU} problem \cite{ref:agarap:2018}, which occurs when the neurons that use \acs{ReLU} \index{activation function}activation functions become \textit{inactive} and only output $0$ due to a negative net input signal.
+However, \acs{LReLU} does not suffer from the \index{dying ReLU problem}dying \acs{ReLU} problem~\cite{ref:agarap:2018}, which occurs when the neurons that use \acs{ReLU} \index{activation function}activation functions become \textit{inactive} and only output $0$ due to a negative net input signal.
 The \acs{LReLU} \index{activation function}activation function is defined in Equation~\eqref{eq:leaky_relu} below.
@@
 By introducing a parameter $\alpha > 0$, negative \index{net input signal}net input signals will still yield non-zero activations, resulting in non-zero gradients and avoiding gradient saturation.
-Non-zero gradients are required by some heuristics such as \acs{SGD} in order to be able to effectively train \acp{ANN} \cite{ref:hanin:2018}.
+Non-zero gradients are required by some heuristics such as \acs{SGD} in order to be able to effectively train \acp{ANN}~\cite{ref:hanin:2018}.
 An illustration of \acs{LReLU} with various values for $\alpha$ and $\theta = 0$ is given in Figure~\ref{fig:anns:activation_functions:leaky_relu}.
@@
 
-The \index{sigmoid}sigmoid activation is the continuous differentiable approximation of the step function, which was used in the original perceptron model developed by \citeauthor{ref:rosenblatt:1957} \cite{ref:rosenblatt:1957}, and yields output in the range $(0, 1)$.
+The \index{sigmoid}sigmoid activation is the continuous differentiable approximation of the step function, which was used in the original perceptron model developed by~\citeauthor{ref:rosenblatt:1957}~\cite{ref:rosenblatt:1957}, and yields output in the range $(0, 1)$.
 The \index{sigmoid}sigmoid \index{activation function}activation function is defined in Equation~\eqref{eq:sigmoid} below.
@@
 
-The \index{softmax}softmax function, also known as the \index{softargmax}\textit{softargmax} \cite[p.~184]{ref:goodfellow:2016} or \index{normalised exponential function}\textit{normalised exponential function} \cite{ref:bishop:2006} is a generalisation of the logistic function that converts a $K$-dimensional output vector $\vec{y}$ into a $K$-dimensional output vector $\vec{y^{'}}$ where each element $y^{'}_k$ is in the range $(0,1)$ and all elements sum up to $1$ as is shown in Equation~\eqref{eq:sum_after_softmax} below.
+The \index{softmax}softmax function, also known as the \index{softargmax}\textit{softargmax}~\cite[p.~184]{ref:goodfellow:2016} or \index{normalised exponential function}\textit{normalised exponential function}~\cite{ref:bishop:2006} is a generalisation of the logistic function that converts a $K$-dimensional output vector $\vec{y}$ into a $K$-dimensional output vector $\vec{y^{'}}$ where each element $y^{'}_k$ is in the range $(0,1)$ and all elements sum up to $1$ as is shown in Equation~\eqref{eq:sum_after_softmax} below.
 
@@
 Our brains model biological neural networks with neuron counts in the hundreds of billions and synapse counts in the trillions.
-To emulate the computational capability of the human brain is not yet possible on modern day hardware.
-\citeauthor{ref:sandberg:2008} \cite{ref:sandberg:2008} approximates a computational requirement of 256 000 terabytes/s to emulate the entire brain.
-Despite our shortage in hardware capabilities, \acp{ANN} have been successfully applied to a range of problem classes.
-\citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} summarises some common problems that are solved using \acp{ANN} and can be listed as follows.
+To emulate the computational capability of the human brain is not yet possible on modern day hardware.~\citeauthor{ref:sandberg:2008}~\cite{ref:sandberg:2008} approximates a computational requirement of 256 000 terabytes/s to emulate the entire brain.
+Despite our shortage in hardware capabilities, \acp{ANN} have been successfully applied to a range of problem classes.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} summarises some common problems that are solved using \acp{ANN} and can be listed as follows.
 
 \begin{itemize}
-    \item \textbf{Classification}: Predicting the class of an input vector \cite{ref:khan:2001}.
+      \item \textbf{Classification}: Predicting the class of an input vector~\cite{ref:khan:2001}.
 
-    \item \textbf{Pattern Matching}: Producing closely associated patterns based on an input vector \cite{ref:cannady:1998, ref:kumar:1994}.
+      \item \textbf{Pattern Matching}: Producing closely associated patterns based on an input vector~\cite{ref:cannady:1998, ref:kumar:1994}.
 
-    \item \textbf{Pattern Completion}: Completing the missing parts of an input vector \cite{ref:dayhoff:2001}.
+      \item \textbf{Pattern Completion}: Completing the missing parts of an input vector~\cite{ref:dayhoff:2001}.
 
-    \item \textbf{Optimisation}: Producing optimal values of parameters in a optimisation problems \cite{ref:specht:1991}.
+      \item \textbf{Optimisation}: Producing optimal values of parameters in a optimisation problems~\cite{ref:specht:1991}.
 
-    \item \textbf{Data Mining}: Feature discovery in large datasets \cite{ref:singh:2009}.
+      \item \textbf{Data Mining}: Feature discovery in large datasets~\cite{ref:singh:2009}.
 \end{itemize}
@@
 The input layer contains the input data to the \acs{ANN}.
-Since the input layer simply provides the input data, some literature do not consider the input layer as an actual part of the \acs{ANN} \cite{ref:engelbrecht:2007}.
+Since the input layer simply provides the input data, some literature do not consider the input layer as an actual part of the \acs{ANN}~\cite{ref:engelbrecht:2007}.
 
@@
 The hidden layer contains a collection of ``hidden'' \acp{AN}, also referred to as \textit{hidden units} or \textit{nodes}.
-Hidden units are used if the target data is not linearly separable \cite{ref:engelbrecht:2007}.
-It has been shown that \acp{ANN} that incorporate monotonically increasing differentiable \index{activation function}activation functions can approximate any continuous function with just one hidden layer, given that the hidden layer has enough hidden units \cite{ref:hornik:1989}.
+Hidden units are used if the target data is not linearly separable~\cite{ref:engelbrecht:2007}.
+It has been shown that \acp{ANN} that incorporate monotonically increasing differentiable \index{activation function}activation functions can approximate any continuous function with just one hidden layer, given that the hidden layer has enough hidden units~\cite{ref:hornik:1989}.
 
@@
 The topology of the \acs{ANN} refers to the way that layers of \acp{AN} are connected to each other.
-There are many different topologies \cite{ref:miikkulainen:2010}.
-For the purposes of this dissertation focus is put on a \index{fully connected topology}\textit{fully connected} topology where each \acs{AN} in one layer is connected to all \acp{AN} in the next, without any cycles \cite{ref:zell:1994}.
+There are many different topologies~\cite{ref:miikkulainen:2010}.
+For the purposes of this dissertation focus is put on a \index{fully connected topology}\textit{fully connected} topology where each \acs{AN} in one layer is connected to all \acp{AN} in the next, without any cycles~\cite{ref:zell:1994}.
 
@@
 
-\acp{FFNN} were the first and simplest type of \acp{ANN} developed \cite{ref:schmidhuber:2015} and implement input, hidden and output layers by arranging them in sequential order.
+\acp{FFNN} were the first and simplest type of \acp{ANN} developed~\cite{ref:schmidhuber:2015} and implement input, hidden and output layers by arranging them in sequential order.
 Furthermore, \acp{FFNN} implement \index{fully connected topology}fully connected topologies.
@@
 
-\index{supervised learning}Supervised learning is the process of training where the data that is presented to the \acs{FFNN} during training, includes the desired solution \cite{ref:geron:2017}.
-The \acs{FFNN} learns the mapping function from the input to the target output \cite{ref:brownlee:2016}.
+\index{supervised learning}Supervised learning is the process of training where the data that is presented to the \acs{FFNN} during training, includes the desired solution~\cite{ref:geron:2017}.
+The \acs{FFNN} learns the mapping function from the input to the target output~\cite{ref:brownlee:2016}.
 The desired solutions are referred to as \textit{labels}.
@@
 The training data that is used during supervised learning, is split proportionally into a \textit{training} and \textit{validation} set.
-Data in the training set is used to train the \acs{FFNN} \cite{ref:james:2013} and update the weights, while the validation dataset is used for hyper-parameter tuning, where the parameters of the training process are altered, but not the weights of the \acs{FFNN}.
+Data in the training set is used to train the \acs{FFNN}~\cite{ref:james:2013} and update the weights, while the validation dataset is used for hyper-parameter tuning, where the parameters of the training process are altered, but not the weights of the \acs{FFNN}.
 
@@
 
-\index{overfitting}Overfitting describes a scenario where the trained \acs{FFNN} performs well on training data, but does not generalise well to never before seen data from the test set \cite{ref:tetko:1995, ref:geron:2017}.
-Geron \cite{ref:geron:2017} describes \index{overfitting}overfitting as the case where \acs{FFNN} is too complex relative to the noisiness of the training data.
+\index{overfitting}Overfitting describes a scenario where the trained \acs{FFNN} performs well on training data, but does not generalise well to never before seen data from the test set~\cite{ref:tetko:1995, ref:geron:2017}.
+Geron~\cite{ref:geron:2017} describes \index{overfitting}overfitting as the case where \acs{FFNN} is too complex relative to the noisiness of the training data.
 
@@
 
-Underfitting describes a scenario where the \acs{FFNN} is not able to effectively learn the underlying structure of the training data \cite{ref:tetko:1995, ref:geron:2017}.
-Geron \cite{ref:geron:2017} describe underfitting as the case where the \acs{FFNN} is too simple relative to the underlying structure of the training data.\\
+Underfitting describes a scenario where the \acs{FFNN} is not able to effectively learn the underlying structure of the training data~\cite{ref:tetko:1995, ref:geron:2017}.
+Geron~\cite{ref:geron:2017} describe underfitting as the case where the \acs{FFNN} is too simple relative to the underlying structure of the training data.\\
 \\
 \noindent
-There are two types of supervised learning algorithms based on when weights are updated \cite{ref:engelbrecht:2007}. These include stochastic training and batch
+There are two types of supervised learning algorithms based on when weights are updated~\cite{ref:engelbrecht:2007}. These include stochastic training and batch
 training.
@@
 \index{stochastic training}Stochastic training, also known as \index{online learning}\textit{online learning}, is a \index{supervised learning}supervised learning variation whereby weights are adjusted after each training pattern presented.
-\index{stochastic training}Stochastic training benefits from shuffling data in the training dataset before presenting it to the \acs{FFNN}, in order to avoid overfitting or memorising the order in which patterns are presented \cite{ref:engelbrecht:2007}.
+\index{stochastic training}Stochastic training benefits from shuffling data in the training dataset before presenting it to the \acs{FFNN}, in order to avoid overfitting or memorising the order in which patterns are presented~\cite{ref:engelbrecht:2007}.
 It has been shown that shuffling the training data can speed up convergence
@@
 
-Research suggests a trade-off between stochastic and batch training by making use of mini-batches \cite{ref:bengio:2012}.
+Research suggests a trade-off between stochastic and batch training by making use of mini-batches~\cite{ref:bengio:2012}.
 Mini-batch training is similar to batch training, however weights are updated after $\beta$ patterns have been presented, where $\beta$ is the mini-batch size.\\

### 2022-10-22 dissertation/chapters/03-heuristics.tex
🚧 WIP - Save point (compiles)

@@
 \noindent
-Many different techniques have been used to train \acp{FFNN} \cite{ref:kingma:2014}.
-Finding the best technique to use to train an \acs{FFNN} has been shown to be problem dependent in many cases \cite{ref:kheiri:2017}.
+Many different techniques have been used to train \acp{FFNN}~\cite{ref:kingma:2014}.
+Finding the best technique to use to train an \acs{FFNN} has been shown to be problem dependent in many cases~\cite{ref:kheiri:2017}.
 Every technique has its characteristics, constraints, advantages and disadvantages.
-At the time of writing, the majority of work that is published around the training of \acp{FFNN}, involves the use of gradient-based techniques \cite{ref:nel:2021}.
-Gradient-based techniques are not without flaws and can, for example, yield slow convergence or get trapped in local optima \cite{ref:mingguang:2009}.
-Other techniques have also been used to successfully train \acp{FFNN}, including meta-heuristics such as \acf{PSO} \cite{ref:rakitianskaia:2012, ref:vanwyk:2014}, \acf{DE} \cite{ref:espinal:2011} and \acfp{GA} \cite{ref:gupta:1999}.
+At the time of writing, the majority of work that is published around the training of \acp{FFNN}, involves the use of gradient-based techniques~\cite{ref:nel:2021}.
+Gradient-based techniques are not without flaws and can, for example, yield slow convergence or get trapped in local optima~\cite{ref:mingguang:2009}.
+Other techniques have also been used to successfully train \acp{FFNN}, including meta-heuristics such as \acf{PSO}~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}, \acf{DE}~\cite{ref:espinal:2011} and \acfp{GA}~\cite{ref:gupta:1999}.
 
@@
 Optimisation is the task of finding a solution to a given problem that is better than alternative solutions.
-Better stated by Oldewage \cite{ref:oldewage:2017}, optimisation is the task of finding values for a set of variables such that some measure of optimality is satisfied given a set of constraints.
-Engelbrecht \cite{ref:engelbrecht:2007} breaks optimisations problems down into three components:
+Better stated by Oldewage~\cite{ref:oldewage:2017}, optimisation is the task of finding values for a set of variables such that some measure of optimality is satisfied given a set of constraints.
+Engelbrecht~\cite{ref:engelbrecht:2007} breaks optimisations problems down into three components:
 
@@
 
-As stated in Chapter~\ref{chap:anns}, the training of an \acp{FFNN} is a particular type of optimisation problem, where the goal is to find the configuration of \textit{weights}, such that the \ac{FFNN} yields output that minimises some loss function.
+As stated in Chapter~\ref{chap:anns}, the training of an \acp{FFNN} is a particular type of optimisation problem, where the goal is to find the configuration of \textit{weights}, such that the \acs{FFNN} yields output that minimises some loss function.
 The mechanism by which the optimal weights for a \acs{FFNN} is sough out, is executed by an \index{optimisation algorithm}optimisation algorithm known as a \index{heuristic}heuristic.
@@
 
-The term \textit{heuristic} comes from the Latin word \textit{heuristicus} which means ``to find out or discover''.
-\citeauthor{ref:romanycia:1985} \cite{ref:romanycia:1985} provides a complete study on the history and origins of the term \index{heuristic}\textit{heuristic}.
-From their research, a proposal is made to define \index{heuristic}heuristics in the context of \ac{AI}, as any device, be it a program, rule, piece of knowledge, which is added to a problem-solving system, in expectation that on average, the performance will improve.
+The term \textit{heuristic} comes from the Latin word \textit{heuristicus} which means ``to find out or discover''.~\citeauthor{ref:romanycia:1985}~\cite{ref:romanycia:1985} provides a complete study on the history and origins of the term \index{heuristic}\textit{heuristic}.
+From their research, a proposal is made to define \index{heuristic}heuristics in the context of \acf{AI}, as any device, be it a program, rule, piece of knowledge, which is added to a problem-solving system, in expectation that on average, the performance will improve.
 
 In the context of this dissertation, a \index{heuristic}heuristic refers to an algorithmic search technique that serves as a guide to a search process where good solutions to a optimisation problem is being sought out.
-Different \index{heuristic}heuristics make use of different information during the search process \cite{ref:kheiri:2017}.
-During the training of \acp{FFNN}, \index{heuristic}heuristics such as gradient-based \index{heuristic}heuristics make use of the derivatives obtained by evaluating the \ac{FFNN}.
+Different \index{heuristic}heuristics make use of different information during the search process~\cite{ref:kheiri:2017}.
+During the training of \acp{FFNN}, \index{heuristic}heuristics such as gradient-based \index{heuristic}heuristics make use of the derivatives obtained by evaluating the \acs{FFNN}.
 It can thus be said that gradient-based \index{heuristic}heuristics make use of information directly from the \textit{search space}.
-On the contrary, \index{heuristic}heuristics such as \index{hmeta-euristic}meta-heuristics make use of meta-information obtained as a result of evaluating the \ac{FFNN} \cite{ref:blum:2003}.
+On the contrary, \index{heuristic}heuristics such as \index{hmeta-euristic}meta-heuristics make use of meta-information obtained as a result of evaluating the \acs{FFNN}~\cite{ref:blum:2003}.
 The meta-information that \index{meta-heuristic}meta-heuristics make use of could include ranked-performance of a population of candidate solutions, referred to as \textit{entities}.
-\index{meta-heuristic}Meta-heuristics are useful when there is imperfect information about the search space \cite{ref:bianchi:2009}, and are generally less problem-specific than other classes of \index{heuristic}heuristics \cite{ref:blum:2003}.
+\index{meta-heuristic}Meta-heuristics are useful when there is imperfect information about the search space~\cite{ref:bianchi:2009}, and are generally less problem-specific than other classes of \index{heuristic}heuristics~\cite{ref:blum:2003}.
 This disseration takes a particular interest in gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
@@
 Specifically, in the context of a minimisation problem, these techniques are called \acf{GD} heuristics as they \textit{minimise} some loss function.
-\Acs{GD} is generally attributed to Cauchy \cite{ref:lemarechal:2012}, who first suggested it in 1847.
-In 1907 Hadamard \cite{ref:hadamard:1908} independently proposed a similar method.
-
-Although \acs{GD} \index{heuristic}heuristics where not the first \index{heuristic}heuristics used to train \ac{FFNN}
+\Acs{GD} is generally attributed to Cauchy~\cite{ref:lemarechal:2012}, who first suggested it in 1847.
+In 1907 Hadamard~\cite{ref:hadamard:1908} independently proposed a similar method.
+
+Although \acs{GD} \index{heuristic}heuristics where not the first \index{heuristic}heuristics used to train \acp{FFNN}
 \cite{ref:engelbrecht:2007}, they are certainly the most whidely used.
@@
 Chapter~\ref{chap:anns} introduced the reader to \index {supervised learning}supervised learning and presented a number of loss functions.
-In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \ac{FFNN} and the desired output.
-When using \acs{GD} to train \acp{FFNN}, the \index{loss function}loss function is used to adjust the weights of the \ac{FFNN} in order to minimise the error \cite{ref:engelbrecht:2007}.
-\citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} states that training of \acp{FFNN} using \acs{GD}, is done by calculating the gradient of $\epsilon$ in \textit{weight-space}, and then moving the weight vector along the negative gradient.
+In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{FFNN} and the desired output.
+When using \acs{GD} to train \acp{FFNN}, the \index{loss function}loss function is used to adjust the weights of the \acs{FFNN} in order to minimise the error~\cite{ref:engelbrecht:2007}.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} states that training of \acp{FFNN} using \acs{GD}, is done by calculating the gradient of $\epsilon$ in \textit{weight-space}, and then moving the weight vector along the negative gradient.
 An illustration of \acs{GD} is given in Figure~\ref{fig:heuristics:gd:gd_illustration}.
@@
       \includegraphics[width=0.85\textwidth]{images/gradient_descent.pdf}
-      \caption{An illustration of \ac{GD} over various timesteps showing the minimisation of the error with regards to weight value.}
+      \caption{An illustration of \acs{GD} over various timesteps showing the minimisation of the error with regards to weight value.}
       \label{fig:heuristics:gd:gd_illustration}
@@
 \noindent
-The update step for \ac{GD} can be formulated as is shown in Equation~\eqref{eq:heuristics:gd:update_step_part_1} below.
+The update step for \acs{GD} can be formulated as is shown in Equation~\eqref{eq:heuristics:gd:update_step_part_1} below.
 
@@
 The algorithm that propagates the error signal backwardds is known as \acf{BP}.
-\Acs{BP} was popularised by \citeauthor{ref:werbos:1994} \cite{ref:werbos:1994}.
-\citeauthor{ref:nel:2021} \cite{ref:nel:2021} states that \acs{BP} provides a procedure for updating the network weights, layer by layer, by evaluating the derivatives of the error function $\epsilon$ with respect to the weights at each layer.
-\citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007}describes the \acs{BP} process in two steps:
+\Acs{BP} was popularised by~\citeauthor{ref:werbos:1994}~\cite{ref:werbos:1994}.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} states that \acs{BP} provides a procedure for updating the network weights, layer by layer, by evaluating the derivatives of the error function $\epsilon$ with respect to the weights at each layer.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007}describes the \acs{BP} process in two steps:
 
@@
       \item \textbf{Feedforward Pass}: During this phase the output values of the \acs{FFNN} is calculcated for each training pattern.
-      \item \textbf{Backward Propagation}: During this phase the error signal that is calculated as is shown above in Equations~\eqref{eq:heuristics:gd:update_step_part_1}-~\eqref{eq:heuristics:gd:update_step_part_3} is propagated backwards from the output layer, through the hidden layer, to the input layer of the \ac{FFNN}.
+      \item \textbf{Backward Propagation}: During this phase the error signal that is calculated as is shown above in Equations~\eqref{eq:heuristics:gd:update_step_part_1}-~\eqref{eq:heuristics:gd:update_step_part_3} is propagated backwards from the output layer, through the hidden layer, to the input layer of the \acs{FFNN}.
 Weights are then adjusted as functions of the backpropagated error signal.
@@
 
-The pseudo-code implementation for the \ac{SGD} algorithm is taken from \cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:gd:sgd} below.
+The pseudo-code implementation for the \acs{SGD} algorithm is taken from~\cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:gd:sgd} below.
 
 \begin{algorithm}[H]
-      \caption{The pseudo code algorithm for the \ac{SGD} heuristic.}
+      \caption{The pseudo code algorithm for the \acs{SGD} heuristic.}
       \label{algo:heuristics:gd:sgd}
@@
 
-In order to provide a simplified frame of reference from which the gradient-based heuristics are compared, consider a simplification of the update-step for the weights of the \ac{FFNN} as is done using \ac{SGD} below.
+In order to provide a simplified frame of reference from which the gradient-based heuristics are compared, consider a simplification of the update-step for the weights of the \acs{FFNN} as is done using \ac{SGD} below.
 
@@
 
-In Equation~\ref{eq:heuristics:gd:sgd} $w$ refers to the weights of the \ac{FFNN}, $\eta$ refers to the learning rate as before and $\nabla_{w}\mathcal{E}(w)$ refers to the gradient of the loss/cost function w.r.t the output of the \ac{FFNN} as a result of its weights.
+In Equation~\ref{eq:heuristics:gd:sgd} $w$ refers to the weights of the \acs{FFNN}, $\eta$ refers to the learning rate as before and $\nabla_{w}\mathcal{E}(w)$ refers to the gradient of the loss/cost function w.r.t the output of the \acs{FFNN} as a result of its weights.
 Note that all subscripts w.r.t.
@@
 
-So far detailed mathematical descriptions have been provided to illustrate the concept of \ac{GD} and how it applies to the \ac{SGD} heuristic as applied to \ac{FFNN} training.
+So far detailed mathematical descriptions have been provided to illustrate the concept of \ac{GD} and how it applies to the \acs{SGD} heuristic as applied to \ac{FFNN} training.
 It was mentioned that \ac{SGD} was one of the first widely used heuristics to train \ac{FFNN}, however, it is not without flaws.
 With stochastic learning, only one training pattern is presented at each iteration.
-As such, weight updates are done with high variance and noise \cite{ref:ruder:2016}.
+As such, weight updates are done with high variance and noise~\cite{ref:ruder:2016}.
 An illustration of the the fluctuations caused by \ac{SGD} during training is given in Figure~\ref{fig:heuristics:gd:sgd}.
@@
       \includegraphics[width=\textwidth]{images/sgd.png}
-      \caption{An illustration of \ac{SGD} fluctuations during training as taken from \cite{ref:sgd:2006}.}
+      \caption{An illustration of \ac{SGD} fluctuations during training as taken from~\cite{ref:sgd:2006}.}
       \label{fig:heuristics:gd:sgd}
@@
 
-With batch learning, all the training patterns are presented at once and the \ac{FFNN} converges to the minimum of the loss/cost function w.r.t $w$.
+With batch learning, all the training patterns are presented at once and the \acs{FFNN} converges to the minimum of the loss/cost function w.r.t $w$.
 However, this is computationally expensive and intractable to implement in many situations.
-While \ac{SGD} is able to jump out of local minima into new, potentially better local minima \cite{ref:ruder:2016}, it does at first this seems advantageous.
+While \ac{SGD} is able to jump out of local minima into new, potentially better local minima~\cite{ref:ruder:2016}, it does at first this seems advantageous.
 However, this complicates convergence to the exact minima as \ac{SGD} can potentially keep overshooting better minima.
 It is shown that a slow decrease in the learning rate $\eta$ will lead to the same convergence behaviour as with batch learning, almost certainly converging to local or global minima for non-convex and convex optimisation respectively.
-A compromise to this problem is to include mini-batches of training patterns where a small number of training patterns are presented to the \ac{FFNN} at once.
+A compromise to this problem is to include mini-batches of training patterns where a small number of training patterns are presented to the \acs{FFNN} at once.
 This means that the input patterns from mini-batches are just approximations of the total population of training patterns.
-According to \citeauthor{ref:ruder:2016} \cite{ref:ruder:2016} this has two main advantages
+According to~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} this has two main advantages
 
@@
 
-      \item Learning rate schedules \cite{ref:robbins:1951} can be introduced to dynamically change the learning rate throughout the training process, however, these schedules and their parameters have to be defined a priori and are thus problem specific \cite{ref:darken:1992}.
+      \item Learning rate schedules~\cite{ref:robbins:1951} can be introduced to dynamically change the learning rate throughout the training process, however, these schedules and their parameters have to be defined a priori and are thus problem specific~\cite{ref:darken:1992}.
 
@@
 Larger weight updates are required for less frequently occurring features.
-This problem eludes to the credit assignment problem \cite{ref:rumelhart:1986} common to these \ac{GD} variants.
-
-      \item It is difficult to avoid getting trapped in local minima, especially for highly non-convex loss/cost functions used for \ac{ANN} training.
-\cite{ref:dauphin:2014} argues that this difficulty arises not from local minima, but from sadle points.
-Sadle points are points at which one dimensions slopes upwards while another dimension slopes downwards.
-\cite{ref:ruder:2016} mentions that these sadle points are usually surrounded by plateaus of the same error, leading to gradients that are close to zero in all dimensions.
+This problem eludes to the credit assignment problem~\cite{ref:rumelhart:1986} common to these \ac{GD} variants.
+
+      \item It is difficult to avoid getting trapped in local minima, especially for highly non-convex loss/cost functions used for \ac{ANN} training.~\cite{ref:dauphin:2014} argues that this difficulty arises not from local minima, but from sadle points.
+Sadle points are points at which one dimensions slopes upwards while another dimension slopes downwards.~\cite{ref:ruder:2016} mentions that these sadle points are usually surrounded by plateaus of the same error, leading to gradients that are close to zero in all dimensions.
 \end{itemize}
@@
 Research shows that \ac{SGD} has difficulty navigating ravines i.e.
-areas where the surface curves much more steeply in one dimension than in another \cite{ref:sutton:1986}.
+areas where the surface curves much more steeply in one dimension than in another~\cite{ref:sutton:1986}.
 These ravines are common around local minima.
@@
       \includegraphics[width=\textwidth]{images/sgd_with_and_without_momentum.png}
-      \caption{An illustration of \ac{SGD} with and without momentum taken from \cite{ref:du:2019}.}
+      \caption{An illustration of \ac{SGD} with and without momentum taken from~\cite{ref:du:2019}.}
       \label{fig:heuristics:gd:sgd_with_and_without_momentum}
@@
 
-Momentum \cite{ref:qian:1999} is a variant of the \ac{SGD} that helps accelerate \ac{SGD} in the relevant direction, dampening oscillations.
-\cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$ of the weight update vector of the previous timestep to the current weight update vector.
+Momentum~\cite{ref:qian:1999} is a variant of the \acs{SGD} that helps accelerate \ac{SGD} in the relevant direction, dampening oscillations.~\cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$ of the weight update vector of the previous timestep to the current weight update vector.
 The accumulation of momentum is presented in Equation~\ref{eq:heuristics:gd:momentum_part_1} while the update step is then amended in Equation~\ref{eq:heuristics:gd:momentum_part_2} below.
@@
 
-By redefining the \ac{SGD} update steps as shown above, the \ac{Momentum} heuristic allows for the increase of momentum for dimensions whose gradients point in the same direction, while simultaneously reducing momentum for dimensions whose gradients change direction, leading to faster convergence and less oscillation.
-The momentum term $\alpha$ is usually set to 0.9 \cite{ref:engelbrecht:2007}\cite{ref:ruder:2016}.
+By redefining the \acs{SGD} update steps as shown above, the \acs{Momentum} heuristic allows for the increase of momentum for dimensions whose gradients point in the same direction, while simultaneously reducing momentum for dimensions whose gradients change direction, leading to faster convergence and less oscillation.
+The momentum term $\alpha$ is usually set to 0.9~\cite{ref:engelbrecht:2007}\cite{ref:ruder:2016}.
 
@@
 
-\Acl{NAG} is a variant of the \ac{Momentum} heuristics developed by Ilya Sutskever \cite{ref:sutskever:2013-2} and is inspired from Yurii Nesterov's \cite{ref:nesterov:1983} work on optimising convex functions.
+\Acl{NAG} is a variant of the \acs{Momentum} heuristics developed by Ilya Sutskever~\cite{ref:sutskever:2013-2} and is inspired from Yurii Nesterov's~\cite{ref:nesterov:1983} work on optimising convex functions.
 \ac{NAG} provides an improvement to the momentum accumulation term by providing a look-ahead term that better refines the weight update step.
-In the \ac{NAG} heuristic, the gradient is not calculated w.r.t the current weights, but rather w.r.t the approximate future positions of the weights \cite{ref:ruder:2016}.
-An illustration of this is taken from Geoffrey Hinton's lecture on mini-batch \ac{GD} \cite{ref:hinton:2012} and is presented in Figure~\ref{fig:heuristics:gd:nag} below.
+In the \acs{NAG} heuristic, the gradient is not calculated w.r.t the current weights, but rather w.r.t the approximate future positions of the weights~\cite{ref:ruder:2016}.
+An illustration of this is taken from Geoffrey Hinton's lecture on mini-batch \ac{GD}~\cite{ref:hinton:2012} and is presented in Figure~\ref{fig:heuristics:gd:nag} below.
 
@@
       \includegraphics[width=\textwidth]{images/nag.png}
-      \caption{An illustration of the weight update vector for \ac{NAG} taken from \cite{ref:hinton:2012}.}
+      \caption{An illustration of the weight update vector for \ac{NAG} taken from~\cite{ref:hinton:2012}.}
       \label{fig:heuristics:gd:nag}
@@
 
-\citeauthor{ref:ruder:2016} \cite{ref:ruder:2016} explains the update step as is done by \ac{NAG} is follows.
+\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} explains the update step as is done by \ac{NAG} is follows.
 \ac{Momentum} first computes the current gradient.
@@
 
-\Acl{Adagrad} is an adaptation of \ac{SGD} which implements a learning rate for every parameter in the weight vector and is developed by Duchi et al.
-\cite{ref:duchi:2011}.
-\citeauthor{ref:ruder:2016} \cite{ref:ruder:2016} mentions that \Ac{Adagrad} adapts the learning rate to the weights, performing small updates (i.e.
+\Acl{Adagrad} is an adaptation of \ac{SGD} which implements a learning rate for every parameter in the weight vector and is developed by Duchi et al.~\cite{ref:duchi:2011}.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that \Ac{Adagrad} adapts the learning rate to the weights, performing small updates (i.e.
 low learning rates) for weights associated with frequently occurring features and larger updates (i.e.
@@
 
-In the \ac{GD} variants presented thus far, the weight updates have been applied to all weights at once using the same learning rate $\eta$ for all dimensions of the weight update vector.
+In the \acs{GD} variants presented thus far, the weight updates have been applied to all weights at once using the same learning rate $\eta$ for all dimensions of the weight update vector.
 \Ac{Adagrad} uses a different learning rate for every weight $w_{i}$ at every timestep $t$.
@@
 where $w_{i}$ is the $i$-th dimension of the weight vector, $G_{ii} \in \mathbb{R}^{d \times d}$ is a diagonal matrix where each diagonal element $i,i$ is the sum of the squared of the gradients w.r.t.
-$w_{i}$ up to timestep $t$ and $\epsilon$ is a smoothing term that avoids division by zero, usually set in the order of $1 \times 10^{-8}$ \cite{ref:ruder:2016}.
+$w_{i}$ up to timestep $t$ and $\epsilon$ is a smoothing term that avoids division by zero, usually set in the order of $1 \times 10^{-8}$~\cite{ref:ruder:2016}.
 Since $G_{t}$ contains the sum of the squares of the gradients with respect to all parameters $w$ along its diagonal, the weight update step can be vectorised and updated using the matrix-vector product between $G_{t}$ and $\nabla_{w_{i}}\mathcal{E}(w_{i})$.
@@
 In Section~\ref{sec:heuristics:adagrad} it was mentioned that one of the main problems of \ac{Adagrad} is that it has an aggressively monotonically decreasing learning rate because of the accumulation of the sum of squared gradients in its denominator.
-Zeiler \cite{ref:zeiler:2012} presents an improvement on \ac{Adagrad} that eliminates this problem.
-\citeauthor{ref:ruder:2016} \cite{ref:ruder:2016} mentions that instead of accumulating all past squared gradients as in the case of \ac{Adagrad}, \ac{Adadelta} restricts the window of accumulation to a window with a fixed size $W$.
+Zeiler~\cite{ref:zeiler:2012} presents an improvement on \ac{Adagrad} that eliminates this problem.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that instead of accumulating all past squared gradients as in the case of \ac{Adagrad}, \ac{Adadelta} restricts the window of accumulation to a window with a fixed size $W$.
 However, storing $W$ previous squared gradients is very inefficient.
@@
 
-Since the denominator is the \ac{RMS} error criterion of the gradient, the criteria short-hand notation is used as follows.
+Since the denominator is the \acs{RMS} error criterion of the gradient, the criteria short-hand notation is used as follows.
 
@@
 
-\citeauthor{ref:ruder:2016}\cite{ref:ruder:2016} highlights that the original authors \cite{ref:zeiler:2012} noted that the units of the update step as presented in Equation~\ref{eq:heuristics:gd:adadelta_part_2} do not match i.e.
+\citeauthor{ref:ruder:2016}\cite{ref:ruder:2016} highlights that the original authors~\cite{ref:zeiler:2012} noted that the units of the update step as presented in Equation~\ref{eq:heuristics:gd:adadelta_part_2} do not match i.e.
 the update vector should have the same hypothetical units as the weight vector.
@@
 Note that $RMS[\Delta w]_{t}$ is unknown at timestep $t$.
-It is thus approximated with the \ac{RMS} of weight updates until the previous timestep.
+It is thus approximated with the \acs{RMS} of weight updates until the previous timestep.
 The learning rate in Equation~\ref{eq:heuristics:gd:adadelta_part_5} is then replaced as follows.
@@
 
-\Ac{RMSProp} is a similar heuristic to \ac{Adadelta} presented by Geoffrey Hinton \cite{ref:hinton:2012} and was developed independently around the same time.
-\citeauthor{ref:ruder:2016}\cite{ref:ruder:2016} mentions that \ac{RMSProp} is in fact the same as the first weight update vector as defined for \ac{Adadelta}.
+\Ac{RMSProp} is a similar heuristic to \ac{Adadelta} presented by Geoffrey Hinton~\cite{ref:hinton:2012} and was developed independently around the same time.~\citeauthor{ref:ruder:2016}\cite{ref:ruder:2016} mentions that \ac{RMSProp} is in fact the same as the first weight update vector as defined for \ac{Adadelta}.
 The update step for \ac{RMSProp} is then defined in terms of a decaying running average of gradients squared as is presented again for convenience in Equations~\ref{eq:heuristics:gd:rmsprop_part_1} and~\ref{eq:heuristics:gd:rmsprop_part_2} below.
@@
 This is one of the disadvantages of \ac{RMSProp}.
-Hinton suggests $\alpha$ be set to 0.9 and $\eta$ be set to $0.001$ \cite{ref:hinton:2012}.
+Hinton suggests $\alpha$ be set to 0.9 and $\eta$ be set to $0.001$~\cite{ref:hinton:2012}.
 
@@
 \Ac{Adam} is another variant of \ac{SGD} that includes adaptive learning rates and is presented by Kingma et.
-al \cite{ref:kingma:2014}.
-However, in addition to storing an exponentially decaying average of past squared gradients like \ac{Adadelta} and \ac{RMSProp}, \ac{Adam} also stores an exponentially decaying average of past gradients $v_{t}$, similar to \ac{Momentum} \cite{ref:ruder:2016}.
-\citeauthor{ref:heusel:2017} \cite{ref:heusel:2017} uses the analogy that \ac{Momentum} can be seen as a ball running down a slope, while \ac{Adam} behaves like a heavy ball with friction, which thus prefers flat minima in the error surface.
+al~\cite{ref:kingma:2014}.
+However, in addition to storing an exponentially decaying average of past squared gradients like \ac{Adadelta} and \ac{RMSProp}, \ac{Adam} also stores an exponentially decaying average of past gradients $v_{t}$, similar to \ac{Momentum}~\cite{ref:ruder:2016}.~\citeauthor{ref:heusel:2017}~\cite{ref:heusel:2017} uses the analogy that \ac{Momentum} can be seen as a ball running down a slope, while \ac{Adam} behaves like a heavy ball with friction, which thus prefers flat minima in the error surface.
 
@@
 
-\citeauthor{ref:ruder:2016} \cite{ref:ruder:2016} mentions that $v_{t}$ and $w_{t}$ presented above are estimates of the first moment (the mean) and the second moment (the uncentered variance) of the gradients respectively.
-It is from these moment terms that the name \acl{Adam} is derived.
-\citeauthor{ref:kingma:2014} \cite{ref:kingma:2014} mentions that because $v_{t}$ and $w_{t}$ is initialised to be vectors of 0's, they are biased towards 0.
+\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that $v_{t}$ and $w_{t}$ presented above are estimates of the first moment (the mean) and the second moment (the uncentered variance) of the gradients respectively.
+It is from these moment terms that the name \acl{Adam} is derived.~\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} mentions that because $v_{t}$ and $w_{t}$ is initialised to be vectors of 0's, they are biased towards 0.
 This is especially true during the initial timesteps and/or when the decay rates $\beta_{1}$ and $\beta_{2}$ are small (i.e.
@@
 
-\citeauthor{ref:kingma:2014} \cite{ref:kingma:2014} suggest default values $B_{1}=0.9$, $B_{2}=0.999$ and $\epsilon = 1 \times 10^{-8}$.
+\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} suggest default values $B_{1}=0.9$, $B_{2}=0.999$ and $\epsilon = 1 \times 10^{-8}$.
 This section provided the reader with a collection of gradient-based heuristics.
@@
 
-Gradient-based methods are sensitive to the type of problem that they it applied to, with hyper-parameter selection often dominating the research focus \cite{ref:bengio:2000}\cite{ref:feurer:2019}.
+Gradient-based methods are sensitive to the type of problem that they it applied to, with hyper-parameter selection often dominating the research focus~\cite{ref:bengio:2000}\cite{ref:feurer:2019}.
 In the context of \acp{HH}, it is important to consider a diverse set of low-level heuristics to select from.
-Apart from gradient-based methods, alternative heuristics must thus be considered.
-\cite{ref:blum:2003} mentions since the 1980's, a new kind of approximate algorithm has emerged which basically tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
+Apart from gradient-based methods, alternative heuristics must thus be considered.~\cite{ref:blum:2003} mentions since the 1980's, a new kind of approximate algorithm has emerged which basically tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
 These methods referred to as metaheuristics.
@@
 Each of these have been shown to train \ac{FFNN}.
-These meta-heuristics include \ac{PSO}, \ac{DE} and \acp{GA}.
-\cite{ref:carvalho:2006} compared various \ac{PSO} variants for training \acp{FFNN}.
-\cite{ref:espinal:2011} compared \ac{DE} and \ac{PSO} when applied to \ac{FFNN} training and \cite{ref:gupta:1999} compared \ac{BP} to a \ac{GA} for training \acp{FFNN}.
+These meta-heuristics include \ac{PSO}, \ac{DE} and \acp{GA}.~\cite{ref:carvalho:2006} compared various \ac{PSO} variants for training \acp{FFNN}.~\cite{ref:espinal:2011} compared \ac{DE} and \ac{PSO} when applied to \ac{FFNN} training and~\cite{ref:gupta:1999} compared \ac{BP} to a \ac{GA} for training \acp{FFNN}.
 
 A formal definition for meta-heuristics is required.
-The term \aclp{MH} was first introduced by \citeauthor{ref:glover:1986}\cite{ref:glover:1986} in 1986.
+The term \aclp{MH} was first introduced by~\citeauthor{ref:glover:1986}\cite{ref:glover:1986} in 1986.
 The world derives from the composition of two Greek words.
@@
 The suffix, \textit{meta} means ``beyond, in an upper level''.
-Before this term was widely adopted, \acp{MH} were often called \textit{modern heuristics} \cite{ref:reeves:1993}.
-\cite{ref:blum:2003} mentions that there is a debate as to what the formal defintion of \acp{MH} is and suggests the definition of \acp{MH} to be high level strategies for exploring search spaces by using different methods.
-\citeauthor{ref:blum:2003} \cite{ref:blum:2003} provides characterists of meta-heuristics.
+Before this term was widely adopted, \acp{MH} were often called \textit{modern heuristics}~\cite{ref:reeves:1993}.~\cite{ref:blum:2003} mentions that there is a debate as to what the formal defintion of \acp{MH} is and suggests the definition of \acp{MH} to be high level strategies for exploring search spaces by using different methods.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} provides characterists of meta-heuristics.
 These characterists are given as follows.
@@
 
-\citeauthor{ref:blum:2003} \cite{ref:blum:2003} proposes the classification of heuristics as follows:
+\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} proposes the classification of heuristics as follows:
 
@@
 
-\Ac{PSO} is a stochastic population-based search algorithm based on the social behaviour of birds in a flock \cite{ref:kennedy:1995}.
-By definition, the \ac{PSO} heuristic is nature-inspired.
-\Acp{PSO} were first presented  by \citeauthor{ref:kennedy:1995}\cite{ref:kennedy:1995}.
-It was also Kennedy and Eberhart that first applied \acp{PSO} to train of \acp{FFNN} \cite{ref:eberhart:1995}\cite{ref:kennedy:1997}.
-The application of \acp{PSO} in the context of training \ac{FFNN} have been widely studied \cite{ref:rakitianskaia:2012}\cite{ref:vanwyk:2014} and it has been found to perform well.
+\Ac{PSO} is a stochastic population-based search algorithm based on the social behaviour of birds in a flock~\cite{ref:kennedy:1995}.
+By definition, the \acs{PSO} heuristic is nature-inspired.
+\Acp{PSO} were first presented  by~\citeauthor{ref:kennedy:1995}\cite{ref:kennedy:1995}.
+It was also Kennedy and Eberhart that first applied \acp{PSO} to train of \acp{FFNN}~\cite{ref:eberhart:1995}\cite{ref:kennedy:1997}.
+The application of \acp{PSO} in the context of training \ac{FFNN} have been widely studied~\cite{ref:rakitianskaia:2012}\cite{ref:vanwyk:2014} and it has been found to perform well.
 This section aims to provide the reader with the detail of \ac{PSO} implementation.
 
-In general, this dissertation uses the term \textit{entity} for candidate solutions and a \textit{population} for a collection of entities.
-\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that in \acp{PSO} individual candidate solutions are referred to as \textit{particles} and the population is referred to as a \textit{swarm}.
+In general, this dissertation uses the term \textit{entity} for candidate solutions and a \textit{population} for a collection of entities.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that in \acp{PSO} individual candidate solutions are referred to as \textit{particles} and the population is referred to as a \textit{swarm}.
 These particles are ``flown'' through a hyperdimensional space.
@@
 These are referred to as \textit{Local best (lbest)} \ac{PSO} and \textit{global best (gbest)} \ac{PSO}.
-There are two main differences between the two approaches in terms of their convergence characteristics \cite{ref:eberhart:1996}.
+There are two main differences between the two approaches in terms of their convergence characteristics~\cite{ref:eberhart:1996}.
 These include:
@@
 \begin{itemize}
-      \item Due to the larger particle interconnectivity of \textit{gbest} \ac{PSO}, the heuristic converges faster than with \textit{lbest} \ac{PSO}.
-\cite{ref:engelbrecht:2007} mentions that faster convergence comes at a cost of less diversity.
+      \item Due to the larger particle interconnectivity of \textit{gbest} \ac{PSO}, the heuristic converges faster than with \textit{lbest} \ac{PSO}.~\cite{ref:engelbrecht:2007} mentions that faster convergence comes at a cost of less diversity.
       \item As a consequence of larger diversity, the \textit{lbest} \ac{PSO} is less susceptible to getting trapped in local minima.
@@
 
-\citeauthor{ref:shi:1998}\cite{ref:shi:1998} proposed a modification of the original \ac{PSO} as was presented by \citeauthor{ref:kennedy:1995}.
+\citeauthor{ref:shi:1998}\cite{ref:shi:1998} proposed a modification of the original \ac{PSO} as was presented by~\citeauthor{ref:kennedy:1995}.
 Their implementation focuses on the \textit{gbest} \ac{PSO} with \textit{inertia} weights.
@@
 
-The particles in this configuration has a number of properties associated with them \cite{ref:vanwyk:2014}. These include:
+The particles in this configuration has a number of properties associated with them~\cite{ref:vanwyk:2014}. These include:
 
@@
       \item \textbf{Previous Velocity}: Denoted by the term $wv_{ij}(t)$.
-This term represents the particle's momentum and is used to formulate an update step for the particle in the search space.
-\citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that it forces the particle to maintain a consistent direction, preventing drastic changes in terms of update steps.
+This term represents the particle's momentum and is used to formulate an update step for the particle in the search space.~\citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that it forces the particle to maintain a consistent direction, preventing drastic changes in terms of update steps.
 This term is then scaled by the \textit{inertia} weight control parameter, denoted $w$.
-Inertia weight was introduced by \citeauthor{ref:shi:1998}\cite{ref:shi:1998} as a mechanism to control the exploration and exploitation abilities of the swarm.
+Inertia weight was introduced by~\citeauthor{ref:shi:1998}\cite{ref:shi:1998} as a mechanism to control the exploration and exploitation abilities of the swarm.
 It was also introduced as a mechanism to eliminate velocity clamping (discussed later in the section).
-The introduction of inertia weight was successful in addressing the first objective, however did not quite provide a way to totally eliminate velocity clamping \cite{ref:shi:2001}.
+The introduction of inertia weight was successful in addressing the first objective, however did not quite provide a way to totally eliminate velocity clamping~\cite{ref:shi:2001}.
 
@@
 
-A concept known as \textit{velocity clamping} is mentioned above.
-\citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that when \acp{PSO} where first developed, it was possible for particle velocities to become inappropriately large during optimisation leading to situations where particles fly out of the feasible search space.
+A concept known as \textit{velocity clamping} is mentioned above.~\citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that when \acp{PSO} where first developed, it was possible for particle velocities to become inappropriately large during optimisation leading to situations where particles fly out of the feasible search space.
 This is known as \textit{swarm explosion} and occurs when there are frequent changes in the global best position.
-In order to address this issues, the concept of \textit{velocity clamping} was introduced \cite{ref:eberhart:1996}.
+In order to address this issues, the concept of \textit{velocity clamping} was introduced~\cite{ref:eberhart:1996}.
 The idea behind velocity clamping is to restrict particle velocities to some $V_{max}$ threshold, in essence, modeling a form of terminal velocity.
@@
 Appropriate values $V_{max}$ may prevent swarm explosion, but also has an effect on the exploration and exploitation of the heuristic.
-If $V_{max}$ is small, particle update steps are small, resulting in exploitation \cite{ref:eberhart:1996}.
+If $V_{max}$ is small, particle update steps are small, resulting in exploitation~\cite{ref:eberhart:1996}.
 If $V_{max}$ is big, it allows for larger update steps, promoting more exploration.
 A balance is needed between exploration and exploitation.
-Similar to other strategies, such as learning rate schedules for gradient-based heuristics, adaptive strategies such as those proposed in \cite{ref:fan:2002} have been developed, but are beyond the scope of this dissertation.
-
-It should be noted that the choice of control parameter play a vital role on the behaviour and characteristics of the \ac{PSO}.
-Van den Berg and Engelbrecht \cite{ref:vandenberg:2007}\cite{ref:vandenberg:2006} have done extensive work on the effects of different values for control parameters.
-For the purposes of this dissertation, the $c_{1}$ and $c_{2}$ control parameter are set to $1.496180$ and the inertia weight $w$ is set to $0.0729844$ as these correspond to values used in \cite{ref:eberhart:2000} and have been shown to be appropriate for a number of problems.
-
-An example of the pseudo code implementation of the \textit{gbest} \ac{PSO} is taken from \cite{ref:engelbrecht:2007} and is given in Algorithm~\ref{algo:heuristics:pso:gbest} below.
+Similar to other strategies, such as learning rate schedules for gradient-based heuristics, adaptive strategies such as those proposed in~\cite{ref:fan:2002} have been developed, but are beyond the scope of this dissertation.
+
+It should be noted that the choice of control parameter play a vital role on the behaviour and characteristics of the \acs{PSO}.
+Van den Berg and Engelbrecht~\cite{ref:vandenberg:2007}\cite{ref:vandenberg:2006} have done extensive work on the effects of different values for control parameters.
+For the purposes of this dissertation, the $c_{1}$ and $c_{2}$ control parameter are set to $1.496180$ and the inertia weight $w$ is set to $0.0729844$ as these correspond to values used in~\cite{ref:eberhart:2000} and have been shown to be appropriate for a number of problems.
+
+An example of the pseudo code implementation of the \textit{gbest} \ac{PSO} is taken from~\cite{ref:engelbrecht:2007} and is given in Algorithm~\ref{algo:heuristics:pso:gbest} below.
 
@@
 
-This section provided the reader with the implementation details of the \ac{PSO} heuristic.
+This section provided the reader with the implementation details of the \acs{PSO} heuristic.
 It was mentioned that \ac{PSO} have been used to train \acp{FFNN} on many occasions with successful outcomes.
@@
 This section aims to introduce the reader to the next population-based \ac{MH} called \acl{DE}.
-Similar to \ac{PSO}, \Ac{DE} is a stochastic population-based search strategy developed by Storm and Price \cite{ref:price:2006} in 1995.
+Similar to \ac{PSO}, \Ac{DE} is a stochastic population-based search strategy developed by Storm and Price~\cite{ref:price:2006} in 1995.
 \Ac{DE} shares a lot of similarities with other evolutionary \ac{MH} paradigms such as \acp{PSO} and \acp{GA}.
-However, \ac{DE} differs significantly in the sense that it makes use of distance and direction information from the current population to guide the search process \cite{ref:engelbrecht:2007}.
+However, \ac{DE} differs significantly in the sense that it makes use of distance and direction information from the current population to guide the search process~\cite{ref:engelbrecht:2007}.
 Originally, \ac{DE} was focused on multi-dimensional real-values optimisation problems, but unlike gradient-based heuristics, it does not require any gradient information.
-This means that \ac{DE} does not require the underlying optimisation problem to be differentiable, meaning that it can be applied to problems that are discrete, noisy and dynamic \cite{ref:rocca:2011}.
+This means that \ac{DE} does not require the underlying optimisation problem to be differentiable, meaning that it can be applied to problems that are discrete, noisy and dynamic~\cite{ref:rocca:2011}.
 
 Lots of research has been done on using \ac{DE} to train \acp{FFNN}.
-Some notable work include \cite{ref:ilonen:2003}\cite{ref:slowik:2008}\cite{ref:mingguang:2009}.
+Some notable work include~\cite{ref:ilonen:2003}\cite{ref:slowik:2008}\cite{ref:mingguang:2009}.
 In these works, the authors often highlight the low computational complexity and simplicity of implementation for \ac{DE}.
@@
 Similar to other \acp{EA}, variation from one generation to the next is achieved through the application of crossover and mutation operators.
-Engelbrecht \cite{ref:engelbrecht:2007} mentions that for other \acp{EA} if both these operators are used, crossover is applied first after which the generated offspring is mutated.
+Engelbrecht~\cite{ref:engelbrecht:2007} mentions that for other \acp{EA} if both these operators are used, crossover is applied first after which the generated offspring is mutated.
 For other \acp{EA} mutation step sizes are sampled from some probability distribution.
@@
 \ac{DE} aims to exploit this concept in order to find optimal solutions.
-There are three main components to the \ac{DE} heuristic.
-These include mutation, crossover and selection operators \cite{ref:price:2006}.
+There are three main components to the \acs{DE} heuristic.
+These include mutation, crossover and selection operators~\cite{ref:price:2006}.
 Each of these are presented briefly next.
@@
 
-The purpose of the mutation operator is to produce a trial vector for each entity in the current population by mutating a target vector with a weighted differential \cite{ref:engelbrecht:2007}.
+The purpose of the mutation operator is to produce a trial vector for each entity in the current population by mutating a target vector with a weighted differential~\cite{ref:engelbrecht:2007}.
 This trial vector is used in the crossover operator (discussed next) to produce offspring.
@@
 
-In Equation~\ref{eq:heuristics:de:mutation} $\beta \in (0, \infty)$ is the scale factor and controls the amplification of the differential variation \cite{ref:engelbrecht:2007}.
+In Equation~\ref{eq:heuristics:de:mutation} $\beta \in (0, \infty)$ is the scale factor and controls the amplification of the differential variation~\cite{ref:engelbrecht:2007}.
 Note that in the above steps, the selection strategy to select the target vector is not specified.
@@
 In Equation~\ref{eq:heuristics:de:crossover}, $x_{ij}(t)$ refers to the $j$-th element of the vector $x_{i}(t)$ and $\mathcal{J}$ refers to a set of crossover points or indices at which perturbation is done.
-Different techniques for determining the set, $\mathcal{J}$ has been proposed \cite{ref:storn:1996}\cite{ref:storn:1997}.
+Different techniques for determining the set, $\mathcal{J}$ has been proposed~\cite{ref:storn:1996}\cite{ref:storn:1997}.
 These include:
@@
 To counteract this situation, a randomly selected crossover point $j^{*}$ is included in the set $\mathcal{J}$ such that $\mathcal{J} \neq \emptyset$ where $\emptyset$ is the empty set.
-      \item \textbf{Exponential crossover}: \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} states that with exponential crossover a sequence of adjacent crossover points are selected start from some randomly selected crossover index.
+      \item \textbf{Exponential crossover}:~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} states that with exponential crossover a sequence of adjacent crossover points are selected start from some randomly selected crossover index.
 This means that the set of possible crossover points $\mathcal{J}$ is a circular array in indices.
@@
 
-Selection refers to the technique that is used to determine which entities are included in the mutation operator to produce a trial vector \cite{ref:engelbrecht:2007} as was shown in Section~\ref{sec:heuristics:mh:de:mutation} above.
+Selection refers to the technique that is used to determine which entities are included in the mutation operator to produce a trial vector~\cite{ref:engelbrecht:2007} as was shown in Section~\ref{sec:heuristics:mh:de:mutation} above.
 Various selection operators have been suggested.
@@
 To construct the population for the next generation, deterministic selection is used.
-As such, a parent is replaced if the offspring produces a better solution that the parent such that $f(x'_{i}(t)) \leq f(x_{i}(t))$.
-\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} states that this is to ensure the average fitness of the population does not deteriorate.
+As such, a parent is replaced if the offspring produces a better solution that the parent such that $f(x'_{i}(t)) \leq f(x_{i}(t))$.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} states that this is to ensure the average fitness of the population does not deteriorate.
 
@@
 
-Algorithm~\ref{algo:heuristics:de:general_de} is taken from \cite{ref:engelbrecht:2007} and presents the general \ac{DE} algorithm.
+Algorithm~\ref{algo:heuristics:de:general_de} is taken from~\cite{ref:engelbrecht:2007} and presents the general \ac{DE} algorithm.
 The population is initialised by randomly placing entities in the search space such that the positions of the entities are confined to some search boundary.
@@
 \begin{itemize}
-      \item \textbf{Population size:} The population size has a direct influence on the exploration ability of the \ac{DE} heuristic \cite{ref:engelbrecht:2007}.
+      \item \textbf{Population size:} The population size has a direct influence on the exploration ability of the \acs{DE} heuristic~\cite{ref:engelbrecht:2007}.
 The larger the population size, the more differential vectors are available and thus, more directions can be explored.
@@
 
-      \item \textbf{Recombination Probability:} The probability of recombination, $p_{r}$ has a direct influence on the diversity of the \ac{DE} heuristic \cite{ref:engelbrecht:2007}.
+      \item \textbf{Recombination Probability:} The probability of recombination, $p_{r}$ has a direct influence on the diversity of the \acs{DE} heuristic~\cite{ref:engelbrecht:2007}.
 This parameter controls the number of elements that are included during crossover.
@@
 
-Many variants of \ac{DE} have been created and researched \cite{ref:mezura:2006}.
-A general notation for \ac{DE} heuristic variants have been developed by Storn et al.
-\cite{ref:storn:1996}\cite{ref:storn:1997}.
+Many variants of \ac{DE} have been created and researched~\cite{ref:mezura:2006}.
+A general notation for \ac{DE} heuristic variants have been developed by Storn et al.~\cite{ref:storn:1996}\cite{ref:storn:1997}.
 The notation follows the form \textit{DE/$x$/$y$/$z$} where $x$,$y$ and $z$ refer to the components that are used by the particular \ac{DE}.
@@
 For this dissertation, \textit{random} and \textit{best entity} selection, a single difference vector and binomial and exponential crossover is considered.
-This results in the \ac{DE} notations as follows.
+This results in the \acs{DE} notations as follows.
 
@@
 
-This section provided the reader with the details around the implementation of the \ac{DE} heuristic. The last population-based \ac{MH} is presented next.
+This section provided the reader with the details around the implementation of the \acs{DE} heuristic. The last population-based \ac{MH} is presented next.
 
@@
 
-\Ac{EC} refers to a collection of nature-inspired optimisation algorithms that lend their foundation to biological evolution.
-\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that \ac{EC} refers to computer-based problem solving systems that use computational models of evolutionary processes such as natural selection, survival of the fittest and reproduction.
-It was Charles Darwin's theory of \textit{natural selection} that became the foundation of biological evolution \cite{ref:darwin:1987}.
-\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} summarises the Darwinian theory of evolution \cite{ref:darwin:2012} as follows.
+\Ac{EC} refers to a collection of nature-inspired optimisation algorithms that lend their foundation to biological evolution.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that \ac{EC} refers to computer-based problem solving systems that use computational models of evolutionary processes such as natural selection, survival of the fittest and reproduction.
+It was Charles Darwin's theory of \textit{natural selection} that became the foundation of biological evolution~\cite{ref:darwin:1987}.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} summarises the Darwinian theory of evolution~\cite{ref:darwin:2012} as follows.
 In a world with limited resources and stable populations, each individual competes with others for survival.
@@
 Evolution via natural selection of a randomly chosen population of entities can be seen as a search through the space of possible chromosome values.
-This makes the \ac{EC} search process a stochastic search for an optimal solution to the given problem.
+This makes the \acs{EC} search process a stochastic search for an optimal solution to the given problem.
 
@@
 Importantly, the application of \acp{GA} is presented in the context of training \acp{FFNN}.
-\acp{GA} have been widely used to train \acp{FFNN} \cite{ref:montana:1989}\cite{ref:siddique:2001}\cite{ref:miller:1989}.
+\acp{GA} have been widely used to train \acp{FFNN}~\cite{ref:montana:1989}\cite{ref:siddique:2001}\cite{ref:miller:1989}.
 This section shines light on how this is done.
 
-\Acp{GA} where first proposed by Fraser \cite{ref:fraser:1957} and later by Bremermann \cite{ref:bremermann:1962} and Reed et al.
-\cite{ref:reed:1967}.
-However, Holland \cite{ref:holland:1992} is widely regarded as the father of \acp{GA}.
+\Acp{GA} where first proposed by Fraser~\cite{ref:fraser:1957} and later by Bremermann~\cite{ref:bremermann:1962} and Reed et al.~\cite{ref:reed:1967}.
+However, Holland~\cite{ref:holland:1992} is widely regarded as the father of \acp{GA}.
 Similar to \acp{DE}, \acp{GA} are also nature-inspired population-based \acp{MH} and model genetic evolution of entities in a hypothetical population.
@@
 However, it is necessary to first provide the reader with the generic \ac{EC} algorithm.
-This algorithm is also referred to as the canonical \ac{GA} (CGA) and was proposed by Holland \cite{ref:holland:1992}.
-The generic \ac{EC} algorithm is taken from \cite{ref:engelbrecht:2007} and is is presented in Algorithm~\ref{algo:heuristics:ga:generic_ec} below.
+This algorithm is also referred to as the canonical \ac{GA} (CGA) and was proposed by Holland~\cite{ref:holland:1992}.
+The generic \ac{EC} algorithm is taken from~\cite{ref:engelbrecht:2007} and is is presented in Algorithm~\ref{algo:heuristics:ga:generic_ec} below.
 
@@
 As with \ac{DE}, crossover operators model the reproduction of entities in the population.
-Broadly speaking, the crossover operators can be divided into three main categories \cite{ref:engelbrecht:2007} and are based on arity of the operator i.e.
+Broadly speaking, the crossover operators can be divided into three main categories~\cite{ref:engelbrecht:2007} and are based on arity of the operator i.e.
 the number of parents used for reproduction.
@@
 Each parent has a probability $p_{c}$ of producing offspring.
-Usually a high crossover probability is used \cite{ref:engelbrecht:2007}.
+Usually a high crossover probability is used~\cite{ref:engelbrecht:2007}.
 In addition to recombination, \acp{GA} implement a replacement policy where fit offspring can replace weaker parents in the population.
@@
 Specifically, in the context of this dissertation, focus is put on \textit{uniform} crossover.
-Uniform crossover refers to a crossover operator where an $N_{x}$-dimensional crossover mask is generated randomly \cite{ref:syswerda:1989}.
+Uniform crossover refers to a crossover operator where an $N_{x}$-dimensional crossover mask is generated randomly~\cite{ref:syswerda:1989}.
 Uniform crossover is illustrated in Figure~\ref{fig:heuristics:mh:ga:uniform_crossover} below and the algorithm for uniform crossover is given in Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover}.
@@
 
-The mutation operator is applied in order to introduce new genetic material into an existing entity \cite{ref:engelbrecht:2007}.
+The mutation operator is applied in order to introduce new genetic material into an existing entity~\cite{ref:engelbrecht:2007}.
 In doing so, diversity is added into the genetic characteristics of the population.
-Mutation is applied at a certain mutation probability $p_{m}$ to each gene of the offspring $x_{i}(t)$ to produce mutated offspring $x'_{i}(t)$.
-\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that the mutation probability, also referred to as the mutation rate is usually small such that $p_{m} \in [0,1]$ to ensure that good solutions are not distorted too much.
+Mutation is applied at a certain mutation probability $p_{m}$ to each gene of the offspring $x_{i}(t)$ to produce mutated offspring $x'_{i}(t)$.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that the mutation probability, also referred to as the mutation rate is usually small such that $p_{m} \in [0,1]$ to ensure that good solutions are not distorted too much.
 
@@
 Selection is a widely used concept in all \acp{EA} and models survival of the fittest in the evolutionary context.
-The main idea behind the selection operator is to emphasise better solutions \cite{ref:engelbrecht:2007}.
+The main idea behind the selection operator is to emphasise better solutions~\cite{ref:engelbrecht:2007}.
 This is done in two of the main components of \acp{EA}.
@@
 \citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that selection operators are characterised by their \textit{selective pressure}.
-Selective pressure is defined as the speed at which the best entity's solution will occupy the entire population by repeated application of the selection operator alone \cite{ref:back:1994}.
+Selective pressure is defined as the speed at which the best entity's solution will occupy the entire population by repeated application of the selection operator alone~\cite{ref:back:1994}.
 A selection operator with a high selective pressure rapidly decreases the diversity in the population.
@@
 The performance of the selected $N_{ts}$ entities are then compared and the best entities from this group is selected and returned by the operator.
-It should be mentioned that for sexual crossover of two parents, tournament selection is applied twice, first for the first parent and the again for the second parent.
-\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that tournament selection prevents the best entities from dominating provided that $N_{ts}$ is not too large.
+It should be mentioned that for sexual crossover of two parents, tournament selection is applied twice, first for the first parent and the again for the second parent.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that tournament selection prevents the best entities from dominating provided that $N_{ts}$ is not too large.
 This results in a lower selective pressure.
@@
       \item \textbf{Rank-based Selection: } Rank-based selection uses the rank-ordered fitness values to determine the probability of selection and not the absolute fitness value.
-It can therefore be said that selection is independent of actual fitness values.
-\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that the advantage of this approach is that the best entities will not dominate the selection process.
+It can therefore be said that selection is independent of actual fitness values.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that the advantage of this approach is that the best entities will not dominate the selection process.
 Non-deterministic linear sampling selects an entity $x_{i}(t)$ such that $i \sim U(0, U(0, N_{s} - 1))$.
@@
 
-Throughout this section a number of control parameters have been provided that affect the performance of the \ac{GA}.
-These include the population size $N$, the crossover rate $p_{c}$ and the mutation rate $p_{m}$.
-\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that these values are usually kept static.
-However, it is widely accepted that these parameters have a significant impact on the performance of the \ac{GA}.
+Throughout this section a number of control parameters have been provided that affect the performance of the \acs{GA}.
+These include the population size $N$, the crossover rate $p_{c}$ and the mutation rate $p_{m}$.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that these values are usually kept static.
+However, it is widely accepted that these parameters have a significant impact on the performance of the \acs{GA}.
 Finding optimal values for $p_{c}$ and  $p_{m}$ empirically can be a time consuming process.

### 2022-10-22 dissertation/chapters/04-hyper-heuristics.tex
🚧 WIP - Save point (compiles)

@@
 This is the nature of \acp{HH}.
-This is different from \textit{ensemble} \cite{ref:dietterich:2002} approaches in the sense that \acp{HH} provide a single solution, where as \textit{ensembles} make use of the combination of solutions that undergo a net weighted transformation in order to produce a final solution.
+This is different from \textit{ensemble}~\cite{ref:dietterich:2002} approaches in the sense that \acp{HH} provide a single solution, where as \textit{ensembles} make use of the combination of solutions that undergo a net weighted transformation in order to produce a final solution.
 
@@
 Meta learning is a branch of metacognition and is concerned with learning about the learning processes.
-Meta-learning studies how learning systems can increase in efficiency through experience and is broadly defined as the learning process concerned with the concept of \textit{learning to learn} \cite{ref:vilalta:2002}.
+Meta-learning studies how learning systems can increase in efficiency through experience and is broadly defined as the learning process concerned with the concept of \textit{learning to learn}~\cite{ref:vilalta:2002}.
 The goal of meta-learning is to understand if learning itself can become flexible to the problem domain or task under consideration.
 
-\citeauthor{ref:vilalta:2002} \cite{ref:vilalta:2002} mentions that meta-learning differs from base-learning in the scope of the level of adaptation.
+\citeauthor{ref:vilalta:2002}~\cite{ref:vilalta:2002} mentions that meta-learning differs from base-learning in the scope of the level of adaptation.
 Meta-learning is concerned with learning how to choosing the right configuration and biases dynamically.
@@
 
-The term \acl{HH} was first used in 1997 \cite{ref:burke:2010} and was used to describe a protocol that combines several \ac{AI} methods in the context of automated theorem proving.
-The term was independently used in 2000 \cite{ref:cowling:2000} to describe ``heuristics to choose heuristics''.
+The term \acl{HH} was first used in 1997~\cite{ref:burke:2010} and was used to describe a protocol that combines several \ac{AI} methods in the context of automated theorem proving.
+The term was independently used in 2000~\cite{ref:cowling:2000} to describe ``heuristics to choose heuristics''.
 
-Formal definition of \acp{HH} is required.
-\citeauthor{ref:burke:2010}\cite{ref:burke:2010} defines \acp{HH} as search methods or learning mechanism for selecting or generating heuristics to solve computational search problems.
-Burke goes on to say that \ac{HH} is a high-level approach that, given a particular problem instance and a number of low-level heuristics, can select and apply an appropriate low-level heuristic at each decision point \cite{ref:burke2003}.
+Formal definition of \acp{HH} is required.~\citeauthor{ref:burke:2010}\cite{ref:burke:2010} defines \acp{HH} as search methods or learning mechanism for selecting or generating heuristics to solve computational search problems.
+Burke goes on to say that \ac{HH} is a high-level approach that, given a particular problem instance and a number of low-level heuristics, can select and apply an appropriate low-level heuristic at each decision point~\cite{ref:burke2003}.
 
-\citeauthor{ref:grobler:2015} \cite{ref:grobler:2015} states that \acp{HH} promote the design of more generally applicable search methodologies and tend to performing relatively well on a large set of different problems.
+\citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} states that \acp{HH} promote the design of more generally applicable search methodologies and tend to performing relatively well on a large set of different problems.
 This is in contrast to specialised algorithms which typically focus on outperforming the state-of-the-art for a single application.
@@
 Secondly, there is significant potential to improve search methodologies by the incorporation of learning mechanisms that can adaptively guide the search.
-These two fundamental ideas have inspired different types of hyper-heuristics \cite{ref:burke:2010}.
+These two fundamental ideas have inspired different types of hyper-heuristics~\cite{ref:burke:2010}.
 
@@
 These include the nature of the heuristic search space and the source of feedback during learning.
-Figure \ref{fig:heuristics:hh:classification} was taken from \cite{ref:burke:2010} and summarises the classification scheme for \ac{HH}.
+Figure \ref{fig:heuristics:hh:classification} was taken from~\cite{ref:burke:2010} and summarises the classification scheme for \ac{HH}.
 
@@
 
-According to the classification proposed by \cite{ref:burke:2010}, the first dimension of classification involves the nature of the search space.
+According to the classification proposed by~\cite{ref:burke:2010}, the first dimension of classification involves the nature of the search space.
 Distinction is made between heuristic selection and heuristic generation.
@@
 
-Selection mechanisms can include probabilistic methods as is introduced in this dissertation or even some high level \ac{MH}. For generation mechanisms, \ac{EA} are often used \cite{ref:burke:2010}.
+Selection mechanisms can include probabilistic methods as is introduced in this dissertation or even some high level \ac{MH}. For generation mechanisms, \ac{EA} are often used~\cite{ref:burke:2010}.
 
@@
 Consider first construction heuristics.
-According to \citeauthor{ref:burke:2010}\cite{ref:burke:2010}, these approaches build a solution incrementally.
+According to~\citeauthor{ref:burke:2010}\cite{ref:burke:2010}, these approaches build a solution incrementally.
 Starting with an empty solution, the goal is to intelligently select and use construction heuristics to gradually build a complete solution.
@@
 Heuristic selection can be done in a \textit{non-adaptive} or simple way.
-This is done either randomly or along a cycle and is based on a prefixed heuristic ordering \cite{ref:cowling:2000}.
+This is done either randomly or along a cycle and is based on a prefixed heuristic ordering~\cite{ref:cowling:2000}.
 No learning is involved in these approaches.
-As an alternative, heuristic selection may incorporate an \textit{adaptive}, \textit{online learning}) mechanism based on the probabilistic weighting of the low-level heuristics \cite{ref:burke:2003} or some type of performance statistics \cite{ref:cowling:2000}.
+As an alternative, heuristic selection may incorporate an \textit{adaptive}, \textit{online learning}) mechanism based on the probabilistic weighting of the low-level heuristics~\cite{ref:burke:2003} or some type of performance statistics~\cite{ref:cowling:2000}.
 It will later be shown that the proposed \ac{BHH} implements this adaptive selection, perturbation strategy.
 
-The acceptance strategy is an important component of any local search heuristic.
-\cite{ref:burke:2003} mentions that many acceptance strategies have been explored within \acp{HH}.
+The acceptance strategy is an important component of any local search heuristic.~\cite{ref:burke:2003} mentions that many acceptance strategies have been explored within \acp{HH}.
 Move acceptance strategies can be divided into two categories.
@@
 However, a different outcome is possible if a non-deterministic approach is used.
-If the move acceptance test involves other parameters, such as the current time, then these strategies are referred to as non-deterministic strategies \cite{ref:burke:2003}.
+If the move acceptance test involves other parameters, such as the current time, then these strategies are referred to as non-deterministic strategies~\cite{ref:burke:2003}.
 
@@
 However, at the time of writing, only two examples of published work where found where \ac{HH} are used for training \ac{FFNN}.
-These include the works of Nel \cite{ref:nel:2021} and Ul et al.
-\cite{ref:ul:2018}
+These include the works of Nel~\cite{ref:nel:2021} and Ul et al.~\cite{ref:ul:2018}
 

### 2022-10-22 dissertation/chapters/05-probability.tex
🚧 WIP - Save point (compiles)

@@
 Probability theory and statistics can be traced back to as early as the 17th century.
-In 1718, \citeauthor{ref:demoivre:1718} \cite{ref:demoivre:1718} published the \textit{Doctrine of of Chance}; a book that is widely seen as the first published book on probability theory.
-In 1763, Thomas Bayes \cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of Bayes' Theorem was introduced.
+In 1718,~\citeauthor{ref:demoivre:1718}~\cite{ref:demoivre:1718} published the \textit{Doctrine of of Chance}; a book that is widely seen as the first published book on probability theory.
+In 1763, Thomas Bayes~\cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of Bayes' Theorem was introduced.
 It is from this theorem that the \ac{BHH} was named after.
@@
 There are many examples of how these two fields overlap.
-In 1991, \citeauthor{ref:denker:1991}, \cite{ref:denker:1991} proposed a way to transform \ac{ANN} outputs to probability distributions.
+In 1991,~\citeauthor{ref:denker:1991},~\cite{ref:denker:1991} proposed a way to transform \ac{ANN} outputs to probability distributions.
 In 1993,
-\citeauthor{ref:neal:1993} \cite{ref:neal:1993} developed the first \ac{MCMC} sampling algorithm for Bayesian \acp{NN}.
+\citeauthor{ref:neal:1993}~\cite{ref:neal:1993} developed the first \ac{MCMC} sampling algorithm for Bayesian \acp{NN}.
 These are just a  few examples of how the fields of probability theory, statistics and \ac{ML} overlap.
@@
 
-In everyday conversation, the term \textit{probability} is a measure of one's belief in the occurrence of a future event \cite{ref:wackerly:2014}.
+In everyday conversation, the term \textit{probability} is a measure of one's belief in the occurrence of a future event~\cite{ref:wackerly:2014}.
 Probability is a necessary tool used in many fields including physics, biology, chemistry and computer science.
-These fields contain many cases that generate observations that can not be predicted with absolute certainty \cite{ref:wackerly:2014}.
+These fields contain many cases that generate observations that can not be predicted with absolute certainty~\cite{ref:wackerly:2014}.
 Probability can be be inferred and confirmed through past events.
@@
 The probability of such an event occurring is $0.0009765625$.
-The \ac{CLT} shows that the normalised sum of events tends toward a normal distribution with a mean value of $0.5$ if the number of events observed $N$, is large \cite{ref:wackerly:2014}.
+The \ac{CLT} shows that the normalised sum of events tends toward a normal distribution with a mean value of $0.5$ if the number of events observed $N$, is large~\cite{ref:wackerly:2014}.
 The larger the value of $N$, the higher the confidence of mean probability and relative frequency of the event.
-The stable long-term relative frequency by which a random event occurs provides an intuitive and meaningful measure of belief that a certain event will occur again at some point in the future \cite{ref:wackerly:2014}.
+The stable long-term relative frequency by which a random event occurs provides an intuitive and meaningful measure of belief that a certain event will occur again at some point in the future~\cite{ref:wackerly:2014}.
 The belief that a random event would occur again sometime in the future, at an expected relative frequency could be useful for decision making.
@@
 On the contrary, the \textit{unconditional} probability is the probability of an event, not dependent on any other.
-The conditional probability of $A$ given $B$ can be expressed as is given in Definition \ref{eq:probability:cond_probability} below \cite{ref:wackerly:2014}.
+The conditional probability of $A$ given $B$ can be expressed as is given in Definition \ref{eq:probability:cond_probability} below~\cite{ref:wackerly:2014}.
 
@@
 From this concept, two laws of probability can be formulated.
-These are referred to as the \textit{multiplicative} and \textit{additive} laws of probability \cite{ref:wackerly:2014} and is given below in Theorems \ref{th:probability:multiple_events:multiplicative} and \ref{th:probability:multiple_events:additive} respectively.
+These are referred to as the \textit{multiplicative} and \textit{additive} laws of probability~\cite{ref:wackerly:2014} and is given below in Theorems \ref{th:probability:multiple_events:multiplicative} and \ref{th:probability:multiple_events:additive} respectively.
 
@@
 
-Bayes' Theorem, named after Thomas Bayes, describes the probability of an event $A$, based on prior knowledge of conditions that might be related to $A$ \cite{ref:zalta:2015}.
-On order to derive the formal theorem and proof, first consider Definition \ref{def:probability:bayes_theorem:partition} below \cite{ref:zalta:2015}.
+Bayes' Theorem, named after Thomas Bayes, describes the probability of an event $A$, based on prior knowledge of conditions that might be related to $A$~\cite{ref:zalta:2015}.
+On order to derive the formal theorem and proof, first consider Definition \ref{def:probability:bayes_theorem:partition} below~\cite{ref:zalta:2015}.
 
@@
 It will later be shown how the proposed \ac{BHH} makes extensive use of probability distributions and sampling to formulate its selection mechanism.
-The theory and equations presented in the following sections where all taken from \citeauthor{ref:wackerly:2014} \cite{ref:wackerly:2014}.
+The theory and equations presented in the following sections where all taken from~\citeauthor{ref:wackerly:2014}~\cite{ref:wackerly:2014}.
 
@@
 
-The Beta distribution is a family of univariate continuous probability distributions over some $x$, with support on the interval $[0,1]$ \cite{ref:wackerly:2014}.
+The Beta distribution is a family of univariate continuous probability distributions over some $x$, with support on the interval $[0,1]$~\cite{ref:wackerly:2014}.
 It is parameterised by two shape parameters $\alpha > 0$, $\alpha \in \mathbb{R}$ and $\beta > 0$, $\beta \in \mathbb{R}$.
@@
       \par\bigskip
-    \caption{An illustration of the Beta distribution (left) \cite{ref:beta:2014} as well as the cumulative Beta distribution (right) \cite{ref:cumulativebeta:2014} for various values of $\alpha$ and $\beta$ .}
+      \caption{An illustration of the Beta distribution (left)~\cite{ref:beta:2014} as well as the cumulative Beta distribution (right)~\cite{ref:cumulativebeta:2014} for various values of $\alpha$ and $\beta$ .}
       \label{fig:probability:probability_distributions:beta}
@@
 
-The Dirichlet distribution is a family of multivariate continuous probability distributions over some $x$ in $K$ dimensions  \cite{ref:wackerly:2014}.
+The Dirichlet distribution is a family of multivariate continuous probability distributions over some $x$ in $K$ dimensions ~\cite{ref:wackerly:2014}.
 The Dirichlet distribution is the multivariate generalization of the Beta distribution and is thus sometimes referred to by its alternative name, the Multivariate Beta Distribution.
@@
 The values of $\alpha$ are set to (1.5, 1.5, 1.5), (5, 5, 5), (1, 2, 2), and (2, 4, 8) respectively, read from top to bottom, left to right.
-The values of the \ac{PDF} are shown by the color maps with contour lines at equal values as indicated in the color bars \cite{ref:dirichlet:2020}.}
+The values of the \ac{PDF} are shown by the color maps with contour lines at equal values as indicated in the color bars~\cite{ref:dirichlet:2020}.}
       \label{fig:probability:probability_distributions:dirichlet}
@@
 
-The Bernoulli distribution is a discrete probability distribution over some random variable $x$ that takes the value of $1$ with probability $\theta$ and $0$ with probability $1-\theta$  \cite{ref:wackerly:2014}.
+The Bernoulli distribution is a discrete probability distribution over some random variable $x$ that takes the value of $1$ with probability $\theta$ and $0$ with probability $1-\theta$ ~\cite{ref:wackerly:2014}.
 It is denoted as $Ber(\theta)$ with support $x \in \{0, 1\}$.
@@
 
-The mean of the Bernoulli distribution approaches $\theta$ over many samples according to the \ac{CLT} \cite{ref:grinstead:1997}.
+The mean of the Bernoulli distribution approaches $\theta$ over many samples according to the \ac{CLT}~\cite{ref:grinstead:1997}.
 Figure \ref{fig:probability:probability_distributions:bernoulli:coin} shows a simulation of a fair-coin flipping simulation.
@@
 
-The Binomial distribution is a discrete probability distribution over a random variable $x$ taking on a number of successes in $N$ sequential independent experiments that each ask a \textit{yes-no} question \cite{ref:wackerly:2014}.
+The Binomial distribution is a discrete probability distribution over a random variable $x$ taking on a number of successes in $N$ sequential independent experiments that each ask a \textit{yes-no} question~\cite{ref:wackerly:2014}.
 The probability of a single independent experiment yielding a success is given as $\theta$ and the Binomial distribution is denoted as $Bin(N, \theta)$ with support $x \in \{0, 1, \dots, N\}$.
@@
 
-The Categorical distribution is a discrete probability distribution over some random variable $x$, taking on any one of $K$ possible categories \cite{ref:wackerly:2014}.
+The Categorical distribution is a discrete probability distribution over some random variable $x$, taking on any one of $K$ possible categories~\cite{ref:wackerly:2014}.
 There is no innate underlying ordering to these categories and therefore, for simplicity, each category is assigned a numerical representative value such that $k = (1, \dots, K)$.
@@
 The Categorical distribution, denoted $Cat(\theta)$ is the generalization of the Bernoulli distribution and is sometimes referred to it by its alternative names, the generalised Bernoulli Distribution or the Multinoulli distribution.
-In probability theory, the Categorical distribution is often used to explain the outcome of a single experiment with more than two possible outcomes such as rolling a die \cite{ref:wackerly:2014}.
+In probability theory, the Categorical distribution is often used to explain the outcome of a single experiment with more than two possible outcomes such as rolling a die~\cite{ref:wackerly:2014}.
 The \ac{PMF} of the Categorical distribution is given in Equation \ref{eq:probability:probability_distributions:categorical:pmf} below.
@@
 
-where $[x = k]$ is the Iversion Bracket \cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
+where $[x = k]$ is the Iversion Bracket~\cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
 From this, one can conclude that for a given class $k$, the categorical distribution simply yields $\theta_{k}$ as is shown in Equation \ref{eq:probability:probability_distributions:categorical:pmf_k} below.
@@
 
-The Multinomial distribution is a discrete probability distribution over some random variable $x = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials \cite{ref:wackerly:2014}.
+The Multinomial distribution is a discrete probability distribution over some random variable $x = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials~\cite{ref:wackerly:2014}.
 The probabilities for all possible outcomes in a single trial is given by the probability vector $\theta = (\theta_{1}, \dots, \theta_{K})$.
@@
 
-The conjugate prior to a Categorical and Multinomail distribution is the Dirichlet distribution \cite{ref:wackerly:2014}.
+The conjugate prior to a Categorical and Multinomail distribution is the Dirichlet distribution~\cite{ref:wackerly:2014}.
 Similar to the proof of the conjugate prior for the Bernoulli distribution as shown in Section \ref{eq:probability:conjugate_priors:binom_likelihood:posterior} above, this means that the posterior distribution must have the same functional form $\mathcal{A}(v)$ as the prior distribution.
@@
 Naturally, Bayesian statistics is based on Bayes' Theorem as was presented in Section \ref{sec:probability:bayes_theorem}.
-Bayesian statistics describe the probability of an event in terms of some belief based on previous knowledge of the event and the conditions under which the event happens \cite{ref:hackenberger:2019}.
+Bayesian statistics describe the probability of an event in terms of some belief based on previous knowledge of the event and the conditions under which the event happens~\cite{ref:hackenberger:2019}.
 To introduce the concept of Bayesian inference and analysis, one first need to understand the difference between these two approaches.
-Bayesian statistics out-date the frequentist approach, but lacked interest in the early days partly because of the limited applications where the conjugate priors where known \cite{ref:hackenberger:2019}.
+Bayesian statistics out-date the frequentist approach, but lacked interest in the early days partly because of the limited applications where the conjugate priors where known~\cite{ref:hackenberger:2019}.
 More recent advancements in mathematical methods popularised the Bayesian approach again.
 A notable contribution to this switch was the invention of \ac{MCMC} in the 1950's.
-This family of algorithms allowed for the construction of random sampling algorithms from a probability distribution which allows for the calculation of Bayesian hierarchical models \cite{ref:hackenberger:2019}.
-Soon after followed one of the earliest papers that use Bayesian statistics in the field of medicine in 1982 \cite{ref:ashby:2006}.
+This family of algorithms allowed for the construction of random sampling algorithms from a probability distribution which allows for the calculation of Bayesian hierarchical models~\cite{ref:hackenberger:2019}.
+Soon after followed one of the earliest papers that use Bayesian statistics in the field of medicine in 1982~\cite{ref:ashby:2006}.
 
-The difference between the frequentist approach and the Bayesian approach can be illustrated using an example.
-\citeauthor{ref:hackenberger:2019} \cite{ref:hackenberger:2019} suggests an experiment that investigates whether the sex ration in some hypothetical mice population is $1:1$.
+The difference between the frequentist approach and the Bayesian approach can be illustrated using an example.~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} suggests an experiment that investigates whether the sex ration in some hypothetical mice population is $1:1$.
 Two experiments can be designed.
@@
 Consider the $P$-value for each of these experiments.
-The P-value is the probability of obtaining results at least as extreme as the observed results of a statistical hypothesis test \cite{ref:beers:2022}.
+The P-value is the probability of obtaining results at least as extreme as the observed results of a statistical hypothesis test~\cite{ref:beers:2022}.
 For the first experiment, the $P$-value is $0.031$ and for the second experiment, the $P$-value is $0.227$.
@@
       \includegraphics[width=\textwidth]{images/mouse_experiment_outcome.jpg}
-    \caption{The experimental outcomes for the mice-population experiments as was taken from \cite{ref:hackenberger:2019} .}
+      \caption{The experimental outcomes for the mice-population experiments as was taken from~\cite{ref:hackenberger:2019} .}
       \label{fig:probability:bayesian_statistics:mouse_experiment_outcome}
@@
 The process by which this is done is shown later in this section.
-The $Beta$ distribution was presented in Section \ref{sec:probability:probability_distributions:beta}.
-\citeauthor{ref:hackenberger:2019} \cite{ref:hackenberger:2019} mentions that the $Beta$ distribution can be seen as a probability distribution of the occurrence of specific parameters.
+The $Beta$ distribution was presented in Section \ref{sec:probability:probability_distributions:beta}.~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} mentions that the $Beta$ distribution can be seen as a probability distribution of the occurrence of specific parameters.
 From the information that is now known about the $Beta$ distribution, it is possible to calculate the probability that the sex ratio in this mice population is not 1:1 with the $Beta$ distribution as a prior, yielding a $P$-value of $0.92$.
@@
       \includegraphics[width=\textwidth]{images/mouse_experiment_distributions.jpg}
-    \caption{An illustration of the prior and posterior probability distributions for the outcomes of the mice-population experiment, using a $Beta$ prior, as was taken from \cite{ref:hackenberger:2019}.}
+      \caption{An illustration of the prior and posterior probability distributions for the outcomes of the mice-population experiment, using a $Beta$ prior, as was taken from~\cite{ref:hackenberger:2019}.}
       \label{fig:probability:bayesian_statistics:mouse_distributions}
@@
 Bayesian analysis is the process by which prior beliefs are updated as a result of observing new data/evidence.
-Similar to the approaches followed above to explain Bayesian statistics, a proposal is made to explain Bayesian analysis by means of an example taken from \cite{ref:wackerly:2014}.
+Similar to the approaches followed above to explain Bayesian statistics, a proposal is made to explain Bayesian analysis by means of an example taken from~\cite{ref:wackerly:2014}.
 Let $Y_{1}, Y_{2}, \dots, Y_{N}$ denote the random variable that is observed over a sample size of $N$.
@@
 Consider now how Bayesian analysis can used to update the priors on $\theta$ based on newly observed data.
-As with the example above, the below is taken from \cite{ref:wackerly:2014}.
+As with the example above, the below is taken from~\cite{ref:wackerly:2014}.
 

### 2022-10-22 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 WIP - Save point (compiles)

@@
 Formal classification of the \Ac{BHH} is needed.
-Burke et al.
-\cite{ref:burke:2010} proposed a classification mechanism that was discussed in detail in Chapter \ref{chap:hhs}.
+Burke et al.~\cite{ref:burke:2010} proposed a classification mechanism that was discussed in detail in Chapter \ref{chap:hhs}.
 The same classification mechanism is used to classify the \ac{BHH}.
@@
 Furthermore, the \ac{BHH} is also classified as a population-based approach that includes meta-heuristics.
-Burke et al.
-\cite{ref:burke:2010} further proposed the classification of \acp{HH} according to the source of the feedback used during learning.
+Burke et al.~\cite{ref:burke:2010} further proposed the classification of \acp{HH} according to the source of the feedback used during learning.
 It can thus be said that the \ac{BHH} employs online learning according to this criteria, classifying it as an \textit{adaptive} \ac{HH}.
@@
 This section aims to present the reader with all the high level components in the architecture of the \Ac{BHH}.
-Burke et al.
-\cite{ref:burke:2010} proposed an initial framework for \acp{HH} and Grobler \cite{ref:grobler:2015} further proposed a framework for a heterogeneous meta-\ac{HH}.
+Burke et al.~\cite{ref:burke:2010} proposed an initial framework for \acp{HH} and Grobler~\cite{ref:grobler:2015} further proposed a framework for a heterogeneous meta-\ac{HH}.
 These frameworks have been adapted for the implementation of the \Ac{BHH}.
@@
       \centering
-    \includegraphics[width=0.4\textwidth]{shallow_ffnn.png}
+      \includegraphics[width=0.4\textwidth]{shallow_ffnn.pdf}
       \caption[Shallow \index{Feedforward Neural Network}Feedforward Neural Network]{An illustration of
@@
 Notice that the \ac{BHH} uses this performance information and no information from the solution space itself.
-Furthermore, the \ac{BHH} maps this loss to a credit assignment problem as is mentioned by Burke et al.
-\cite{ref:burke:2010}.
+Furthermore, the \ac{BHH} maps this loss to a credit assignment problem as is mentioned by Burke et al.~\cite{ref:burke:2010}.
 The \ac{BHH} at a high level, is not aware of the actual candidate solution that is represented by the entity, but rather just that there is a candidate solution with a unique identifier that, together with a heuristic, produced a certain level of performance.
 The domain barrier is a feature that occurs in al \acp{HH}.
-Burke et al.
-\cite{ref:burke:2010} states that the \ac{HH} collects domain-independent information from the domain barrier.
+Burke et al.~\cite{ref:burke:2010} states that the \ac{HH} collects domain-independent information from the domain barrier.
 A number of examples of domain independent information is given, these include the number of heuristics, the changes in evaluation function, whether a new solution was found or generated, the distance between two solutions, whether it has become stuck.
@@
 The credit assignment strategy is an implementation that maps a continuous performance metric into a discrete credit metric.
-This component implements the ``move acceptance'' process as proposed by Özcan et al.
-\cite{ref:ozcan:2006,ref:ozcan:2008}.
+This component implements the ``move acceptance'' process as proposed by Özcan et al.~\cite{ref:ozcan:2006,ref:ozcan:2008}.
 It determines if a given performance is deemed good or not.
-This simple discrete transformation is subject to the credit assignment problem as discussed by Burke et al.
-\cite{ref:burke:2010}.
+This simple discrete transformation is subject to the credit assignment problem as discussed by Burke et al.~\cite{ref:burke:2010}.
 A good credit assignment strategy will correctly allocate credit to the appropriate heuristic-entity combination.
@@
 It is later shown in Section \ref{sec:bhh:selection_mechanism:naive_bayes} that the \ac{BHH} implements a Naïve Bayes classifier.
-Domingos et al.
-\cite{ref:domingos:1997} mentions that although Bayesian classifiers’ probability estimates are only optimal under quadratic loss if the independence assumption holds, the classifier itself can be optimal under zero-one loss (misclassification rate) even when this assumption is violated by a wide margin.
+Domingos et al.~\cite{ref:domingos:1997} mentions that although Bayesian classifiers’ probability estimates are only optimal under quadratic loss if the independence assumption holds, the classifier itself can be optimal under zero-one loss (misclassification rate) even when this assumption is violated by a wide margin.
 This means that independence can be assumed when the probabilistic model is used as a classifier and not to get real probabilities.
@@
 Naturely, an assumption is made that a larger population could lead to better results, assuming that entities are initialised to be spread uniformly across the solution search space.
-Oldewage \cite{ref:oldewage:2017} mentions that a large number of particles (entities) may be able to traverse a greater portion of the search space as every particle provides additional information about the search space.
+Oldewage~\cite{ref:oldewage:2017} mentions that a large number of particles (entities) may be able to traverse a greater portion of the search space as every particle provides additional information about the search space.
 However, it is to be determined if this is indeed the case for the \ac{BHH}.

### 2022-10-22 dissertation/chapters/07-methodology.tex
🚧 WIP - Save point (compiles)

@@
 This section provides the detail around the different datasets that are used throughout the empirical process.
-These datasets originate from the UCI Machine Learning Repository \cite{ref:uci:2022}.
+These datasets originate from the UCI Machine Learning Repository~\cite{ref:uci:2022}.
 Datasets are grouped by problem type and include 8 classification and 7 regression datasets.
@@
                   \midrule
-            iris  & multivariate & real  & 4     & 3     & 150   & 16    & 10    & \cite{ref:fisher:1936} \\
-            car   & multivariate & categorical & 6     & 4     & 1728  & 128   & 14    & \cite{ref:bohanec:1988} \\
-            abalone & multivariate & categorical, integer, real & 8     & 28    & 4177  & 256   & 17    & \cite{ref:waugh:1995} \\
-            mushroom & multivariate & categorical & 22    & 2     & 8214  & 512   & 17    & \cite{ref:schlimmer:1987} \\
-            wine\_quality & multivariate & real  & 12    & 11    & 4898  & 256   & 20    & \cite{ref:cortez:2009} \\
-            bank  & multivariate & real  & 17    & 2     & 45211 & 512   & 89    & \cite{ref:moro:2014} \\
-            diabetic & multivariate & integer & 55    & 3     & 100000 & 1024  & 98    & \cite{ref:strack:2014} \\
-            adult & multivariate & categorical, integer & 14    & 2     & 48842 & 256   & 191   & \cite{ref:kohavi:1996} \\
+                  iris             & multivariate    & real                       & 4                   & 3                & 150                & 16             & 10             & ~\cite{ref:fisher:1936}    \\
+                  car              & multivariate    & categorical                & 6                   & 4                & 1728               & 128            & 14             & ~\cite{ref:bohanec:1988}   \\
+                  abalone          & multivariate    & categorical, integer, real & 8                   & 28               & 4177               & 256            & 17             & ~\cite{ref:waugh:1995}     \\
+                  mushroom         & multivariate    & categorical                & 22                  & 2                & 8214               & 512            & 17             & ~\cite{ref:schlimmer:1987} \\
+                  wine\_quality    & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & ~\cite{ref:cortez:2009}    \\
+                  bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & ~\cite{ref:moro:2014}      \\
+                  diabetic         & multivariate    & integer                    & 55                  & 3                & 100000             & 1024           & 98             & ~\cite{ref:strack:2014}    \\
+                  adult            & multivariate    & categorical, integer       & 14                  & 2                & 48842              & 256            & 191            & ~\cite{ref:kohavi:1996}    \\
             \end{tabular}%
@@
                   \midrule
-            fish\_toxicity & multivariate & real  & 7     & 908   & 64    & 15    & \cite{ref:cassotti:2015} \\
-            housing & univariate & real  & 13    & 506   & 32    & 16    & \cite{ref:harrison:1978} \\
-            forest\_fires & multivariate & real  & 13    & 517   & 32    & 17    & \cite{ref:cortez:2007} \\
-            student\_performance & multivariate & integer & 33    & 649   & 32    & 21    & \cite{ref:cortez:2008} \\
-            parkinsons & multivariate & integer, real & 26    & 5875  & 256   & 23    & \cite{ref:tsanas:2009} \\
-            air\_quality & multivariate, timeseries & real  & 15    & 9358  & 256   & 37    & \cite{ref:de:2008} \\
-            bike  & univariate & integer, real & 16    & 17389 & 256   & 68    & \cite{ref:fanaee:2014} \\
+                  fish\_toxicity       & multivariate             & real           & 7                   & 908                & 64             & 15             & ~\cite{ref:cassotti:2015} \\
+                  housing              & univariate               & real           & 13                  & 506                & 32             & 16             & ~\cite{ref:harrison:1978} \\
+                  forest\_fires        & multivariate             & real           & 13                  & 517                & 32             & 17             & ~\cite{ref:cortez:2007}   \\
+                  student\_performance & multivariate             & integer        & 33                  & 649                & 32             & 21             & ~\cite{ref:cortez:2008}   \\
+                  parkinsons           & multivariate             & integer, real  & 26                  & 5875               & 256            & 23             & ~\cite{ref:tsanas:2009}   \\
+                  air\_quality         & multivariate, timeseries & real           & 15                  & 9358               & 256            & 37             & ~\cite{ref:de:2008}       \\
+                  bike                 & univariate               & integer, real  & 16                  & 17389              & 256            & 68             & ~\cite{ref:fanaee:2014}   \\
             \end{tabular}%
@@
                   \midrule
-            sgd   & learning\_rate & 0.1**0.01 & \cite{ref:sutskever:2013} \\
-            momentum & learning\_rate & 0.1**0.01 & \cite{ref:sutskever:2013} \\
+                  sgd                & learning\_rate            & 0.1**0.01      & ~\cite{ref:sutskever:2013} \\
+                  momentum           & learning\_rate            & 0.1**0.01      & ~\cite{ref:sutskever:2013} \\
                                      & momentum                  & 0.9            &                            \\
-            nag   & learning\_rate & 0.1**0.01 & \cite{ref:sutskever:2013} \\
+                  nag                & learning\_rate            & 0.1**0.01      & ~\cite{ref:sutskever:2013} \\
                                      & momentum                  & 0.9            &                            \\
-            adagrad & learning\_rate & 0.1**0.01 & \cite{ref:duchi:2011} \\
+                  adagrad            & learning\_rate            & 0.1**0.01      & ~\cite{ref:duchi:2011}     \\
                                      & epsilon                   & 1E-07          &                            \\
-            rmsprop & learning\_rate & 0.1**0.01 & \cite{ref:hinton:2012} \\
+                  rmsprop            & learning\_rate            & 0.1**0.01      & ~\cite{ref:hinton:2012}    \\
                                      & rho                       & 0.95           &                            \\
                                      & epsilon                   & 1E-07          &                            \\
-            adadelta & learning\_rate & 1.0**0.95 & \cite{ref:zeiler:2012} \\
+                  adadelta           & learning\_rate            & 1.0**0.95      & ~\cite{ref:zeiler:2012}    \\
                                      & rho                       & 0.95           &                            \\
                                      & epsilon                   & 0.0000001      &                            \\
-            adam  & learning\_rate & 0.1**0.01 & \cite{ref:kingma:2014} \\
+                  adam               & learning\_rate            & 0.1**0.01      & ~\cite{ref:kingma:2014}    \\
                                      & beta1                     & 0.9            &                            \\
@@
                                      & epsilon                   & 1E-07          &                            \\
-            pso   & population\_size & 10    & \cite{ref:van:2010} \\
+                  pso                & population\_size          & 10             & ~\cite{ref:van:2010}       \\
                                      & learning\_rate            & 0.1**0.01      &                            \\
@@
                                      & velocity\_clip\_max       & 1.0            &                            \\
-            de    & population\_size & 10    & \cite{ref:mezura:2006} \\
+                  de                 & population\_size          & 10             & ~\cite{ref:mezura:2006}    \\
                                      & selection\_strategy       & best           &                            \\
@@
                                      & beta                      & 2.0**0.1       &                            \\
-            ga    & population\_size & 10    & \cite{ref:lambora:2019} \\
+                  ga                 & population\_size          & 10             & ~\cite{ref:lambora:2019}   \\
                                      & selection\_strategy       & rand           &                            \\
@@
 
-Two different configurations of the \ac{BHH} baseline is trained using the iris dataset \cite{ref:fisher:1936}.
+Two different configurations of the \ac{BHH} baseline is trained using the iris dataset~\cite{ref:fisher:1936}.
 These configurations include a replay window size of 10 (short memory) and a high replay window size of 250 (long memory).

### 2022-10-22 dissertation/chapters/03-heuristics.tex
✨ (chapter3): WIP - GB heuristics review done

@@
       \includegraphics[width=0.85\textwidth]{images/gradient_descent.pdf}
-      \caption{An illustration of \acs{GD} over various timesteps showing the minimisation of the error with regards to weight value.}
+      \caption{An illustration of \acf{GD} over various timesteps showing the minimisation of the error with regards to weight value.}
       \label{fig:heuristics:gd:gd_illustration}
@@
 \noindent
-In the context of training \textit{shallow} \acp{FFNN} using \index{supervised learning}supervised learning, the error signal is propagated backwards in the network from the output layer, through the hidden layer.
+In the context of training \textit{shallow} \acp{FFNN}, using \index{supervised learning}supervised learning, the error signal is propagated backwards in the network from the output layer, through the hidden layer.
 The algorithm that propagates the error signal backwardds is known as \acf{BP}.
@@
       \item \textbf{Feedforward Pass}: During this phase the output values of the \acs{FFNN} is calculcated for each training pattern.
-      \item \textbf{Backward Propagation}: During this phase the error signal that is calculated as is shown above in Equations~\eqref{eq:heuristics:gd:update_step_part_1}-~\eqref{eq:heuristics:gd:update_step_part_3} is propagated backwards from the output layer, through the hidden layer, to the input layer of the \acs{FFNN}.
+
+      \item \textbf{Backward Propagation}: During this phase the error signal that is calculated as is shown above in Equations~\eqref{eq:heuristics:gd:update_step_part_1}, ~\eqref{eq:heuristics:gd:update_step_part_2} and~\eqref{eq:heuristics:gd:update_step_part_3} is propagated backwards from the output layer, through the hidden layer, to the input layer of the \acs{FFNN}.
 Weights are then adjusted as functions of the backpropagated error signal.
@@
 
-\subsection{Stochastic Gradient Descent}\label{sec:heuristics:gd:sgd}
-
-This section shines light on the algorithmic implementation of \ac{BP} with specific context to \ac{SGD}.
-The algorithm is provided followed by a simplification of the update-step that provides the basis for the next gradient-based heuristics that follow.
-
-The pseudo-code implementation for the \acs{SGD} algorithm is taken from~\cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:gd:sgd} below.
+\noindent
+The pseudo-code implementation for the generic \acs{GD} algorithm is taken from~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:gd:gd} below.
 
 \begin{algorithm}[H]
-      \caption{The pseudo code algorithm for the \acs{SGD} heuristic.}
-      \label{algo:heuristics:gd:sgd}
+      \caption{The pseudo code algorithm for the generic \acf{GD} heuristic.}
+      \label{algo:heuristics:gd:gd}
       \begin{algorithmic}
-            \State Initialise weights, $\eta$, $\alpha$ and the number of epochs $t=0$;
-            \While{stopping condition not met}
-            let $\epsilon_{T} = 0$
+            \State Initialise the \acs{FFNN} weights and biases, the learning rate $\eta$ and the timestep/epoch $T=0$;
+            \While{stopping conditions are not met}
+            \State Let $\epsilon_{T} = 0$;
             \For{each training pattern p}
-            \State Do the feedforward pass phase to calculate $y_{j,p}$ ($\forall j = 1, \dots, J$) and $o_{k,p}$ ($\forall k = 1, \dots, K$);
+            \State Do the feedforward pass phase to calculate the output of the hidden layer $y_{j,p}$ ($\forall j = 1, \dots, J$), and the output of the output layer $o_{k,p}$ ($\forall k = 1, \dots, K$);
             \State Compute the output error signals $\delta_{o_{k,p}}$ and the hidden layer error signals $\delta_{y_{j,p}}$;
-            \State Adjust the weights $w_{kj}$ and $v_{ji}$ (backpropagation of errors);
-            \State $\epsilon_{T}$ += $[\epsilon_{p} = \sum^{K}_{k=1}(t_{k,p} - o_{k,p})^{2}]$;
+            \State Adjust the weights of the output layer $w_{kj}$, and the weights of the hidden layer $v_{ji}$ (backpropagation of errors);
+            \State $\epsilon_{T}$ += $[\epsilon_{T_{p}} = \sum^{K}_{k=1}(t_{k,p} - o_{k,p})^{2}]$; (assuming the use of \acs{SSE} as the loss function)
             \EndFor
-            \State $t = t + 1$;
+            \State $T += 1$;
             \EndWhile
@@
 
-In order to provide a simplified frame of reference from which the gradient-based heuristics are compared, consider a simplification of the update-step for the weights of the \acs{FFNN} as is done using \ac{SGD} below.
+\noindent
+In order to provide a simplified frame of reference from which the gradient-based heuristics are compared, consider a simplification of the update-step for \acs{SGD} as presented in Equation~\eqref{eq:heuristics:gd:update_step_part_1}.
+This simplification is depicted in Equation~\eqref{eq:heuristics:gd:sgd} below.
 
@@
 
-In Equation~\ref{eq:heuristics:gd:sgd} $w$ refers to the weights of the \acs{FFNN}, $\eta$ refers to the learning rate as before and $\nabla_{w}\mathcal{E}(w)$ refers to the gradient of the loss/cost function w.r.t the output of the \acs{FFNN} as a result of its weights.
+\noindent
+In Equation~\eqref{eq:heuristics:gd:sgd} above, $w$ refers to the weights of the \acs{FFNN}, $\eta$ refers to the learning rate as before and $\nabla_{w}\mathcal{E}(w)$ refers to the gradient of the loss function $\mathcal{E}$, w.r.t the output of the \acs{FFNN} as a result of its weights.
 Note that all subscripts w.r.t.
@@
 
-So far detailed mathematical descriptions have been provided to illustrate the concept of \ac{GD} and how it applies to the \acs{SGD} heuristic as applied to \ac{FFNN} training.
-It was mentioned that \ac{SGD} was one of the first widely used heuristics to train \ac{FFNN}, however, it is not without flaws.
-With stochastic learning, only one training pattern is presented at each iteration.
+\subsection{Stochastic vs. Batch Training}\label{sec:heuristics:gd:sgd}
+
+This section shines light on the algorithmic implementation of \ac{BP} with specific context to stochastic and batch training.
+The implementation of \acs{GD} using stochastic training is referred to as \acf{SGD}.
+
+\acs{SGD} was one of the first widely used heuristics to train \ac{FFNN}, however, it is not without flaws.
+With stochastic training, only one training pattern is presented at each iteration/epoch.
 As such, weight updates are done with high variance and noise~\cite{ref:ruder:2016}.
@@
 \begin{figure}[htbp]
-      \includegraphics[width=\textwidth]{images/sgd.png}
-      \caption{An illustration of \ac{SGD} fluctuations during training as taken from~\cite{ref:sgd:2006}.}
+      \centering
+      \includegraphics[width=0.9\textwidth]{images/sgd.png}
+      \caption{An illustration of \acf{SGD} fluctuations during training as taken from~\cite{ref:sgd:2006}.}
       \label{fig:heuristics:gd:sgd}
@@
 
-With batch learning, all the training patterns are presented at once and the \acs{FFNN} converges to the minimum of the loss/cost function w.r.t $w$.
-However, this is computationally expensive and intractable to implement in many situations.
-While \ac{SGD} is able to jump out of local minima into new, potentially better local minima~\cite{ref:ruder:2016}, it does at first this seems advantageous.
-However, this complicates convergence to the exact minima as \ac{SGD} can potentially keep overshooting better minima.
-It is shown that a slow decrease in the learning rate $\eta$ will lead to the same convergence behaviour as with batch learning, almost certainly converging to local or global minima for non-convex and convex optimisation respectively.
-A compromise to this problem is to include mini-batches of training patterns where a small number of training patterns are presented to the \acs{FFNN} at once.
-This means that the input patterns from mini-batches are just approximations of the total population of training patterns.
-According to~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} this has two main advantages
-
-\begin{itemize}
-      \item Reduces the high variance of weight updates which leads to better convergence
-      \item Allows for the implementation of \ac{SGD} using highly optimised matrix operations, common to the state-of-the-art \ac{ML} libraries used today.
-\end{itemize}
-
-In the context of this dissertation, \ac{SGD} refers to the mini-batch learning implementation.
-Although mini-batch \ac{SGD} does provide a compromise between single-pattern and batch learning there are still a number of challenges posed by this approach.
+\noindent
+With batch training, all the training patterns are presented at once and the \acs{FFNN} converges to the global minimum of the loss function w.r.t $w$ (assuming the loss function is convex).
+However, this is computationally expensive and impractical to implement in many situations.
+While \acs{SGD} is able to jump out of local minima into new, potentially better local minima~\cite{ref:ruder:2016}, \acs{SGD} complicates convergence to the minima as \acs{SGD} can potentially keep overshooting better minima.
+By slowly decreasing the learning rate $\eta$ during training, the same convergence behaviour is achieved as with batch training.
+
+A compromise to overshooting minima that \acs{SGD} suffers from, is to include mini-batches of training patterns where a small number of training patterns are presented to the \acs{FFNN} at once.
+This is referred to as \textit{mini-batch} training.
+Input patterns from mini-batches are approximations of the total population of training patterns.
+According to~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} this has two main advantages:
+
+\begin{itemize}
+      \item Mini-batch training reduces the high variance of weight updates as observed for \acs{SGD}, which leads to better convergence.
+
+      \item Mini-batch training allows for the implementation of \acs{GD} using highly optimised matrix operations, common to the state-of-the-art \acs{ML} libraries used today.
+\end{itemize}
+
+\noindent
+In the context of this dissertation, the implementation of \acs{SGD} refers to the mini-batch training implementation of \acs{GD}.
+Although mini-batch training does provide a compromise between stochastic and batch training, there are still a number of challenges faced by mini-batch training.
 These include:
@@
 
-      \item The learning rate that has been introduced so far is applied to all weight updates.
-If the training data is sparse and the features have very different frequencies an equal update to all weights is inefficient.
+      \item The learning rate that has been introduced so far is applied to all elements of the weight vector updates.
+If the training data is sparse and the features have very different frequencies, an equal update to all weights elements is inefficient.
 Larger weight updates are required for less frequently occurring features.
-This problem eludes to the credit assignment problem~\cite{ref:rumelhart:1986} common to these \ac{GD} variants.
-
-      \item It is difficult to avoid getting trapped in local minima, especially for highly non-convex loss/cost functions used for \ac{ANN} training.~\cite{ref:dauphin:2014} argues that this difficulty arises not from local minima, but from sadle points.
-Sadle points are points at which one dimensions slopes upwards while another dimension slopes downwards.~\cite{ref:ruder:2016} mentions that these sadle points are usually surrounded by plateaus of the same error, leading to gradients that are close to zero in all dimensions.
-\end{itemize}
-
-Alternative methods have been proposed that lead to better control over the convergence characteristics caused by \ac{GD} variants. The first of these include \ac{Momentum} and is presented next.
-
-\subsection{Momentum}
-\label{sec:heuristics:gd:momentum}
-
-Research shows that \ac{SGD} has difficulty navigating ravines i.e.
-areas where the surface curves much more steeply in one dimension than in another~\cite{ref:sutton:1986}.
+Inefficient updates of all elements in the weight vectors contribute to the credit assignment problem~\cite{ref:rumelhart:1986}, common to \acs{GD} variants.
+
+      \item It is difficult to avoid getting trapped in local minima, especially for highly non-convex loss functions used for training \acp{FFNN}.
+\citeauthor{ref:dauphin:2014}~\cite{ref:dauphin:2014} mentions the role of sadle points in getting trapped in local minima.
+Sadle points are points at which one dimensions slopes upwards, while another dimension slopes downwards.
+\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that these sadle points are usually surrounded by plateaus of the same error, leading to gradients that are close to zero in all dimensions.
+\end{itemize}
+
+\noindent
+Alternative variants have been proposed that lead to better control over the convergence characteristics caused by \acs{GD}.
+The first of these \acs{GD} variants include \acs{Momentum} and is presented in the following section.
+
+\subsection{Momentum}\label{sec:heuristics:gd:momentum}
+
+Research shows that \ac{SGD} has difficulty navigating ravines~\cite{ref:sutton:1986}.
+Ravines are areas where the surface curves much more steeply in one dimension than in another.
 These ravines are common around local minima.
-As such, \ac{SGD} is shown to oscillate across the slopes of the ravine while only making minor progress towards the local minima.
-An illustration of this is given in Figure~\ref{fig:heuristics:gd:sgd_with_and_without_momentum}.
+As such, \acs{SGD} is shown to oscillate across the slopes of the ravine while only making minor progress towards the local minima.
+
+\Acs{Momentum} ~\cite{ref:qian:1999} is a variant of the \acs{SGD} that helps accelerate \ac{SGD} in the relevant direction, dampening oscillations.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$, of the weight update vector of the previous timestep to the current weight update vector.
+An illustration of \acs{SGD} with and without momentum is given in Figure~\ref{fig:heuristics:gd:sgd_with_and_without_momentum}.
 
 \begin{figure}[htbp]
-      \includegraphics[width=\textwidth]{images/sgd_with_and_without_momentum.png}
-      \caption{An illustration of \ac{SGD} with and without momentum taken from~\cite{ref:du:2019}.}
+      \centering
+      \includegraphics[width=0.99\textwidth]{images/sgd_with_and_without_momentum.pdf}
+      \caption{An illustration of \acf{SGD} with and without momentum taken from~\cite{ref:du:2019}.}
       \label{fig:heuristics:gd:sgd_with_and_without_momentum}
@@
 
-Momentum~\cite{ref:qian:1999} is a variant of the \acs{SGD} that helps accelerate \ac{SGD} in the relevant direction, dampening oscillations.~\cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$ of the weight update vector of the previous timestep to the current weight update vector.
-The accumulation of momentum is presented in Equation~\ref{eq:heuristics:gd:momentum_part_1} while the update step is then amended in Equation~\ref{eq:heuristics:gd:momentum_part_2} below.
+\noindent
+The accumulation of momentum is presented in Equation~\eqref{eq:heuristics:gd:momentum_part_1} below, while the update step is then amended in Equation~\ref{eq:heuristics:gd:momentum_part_2} below.
 
@@
 
-By redefining the \acs{SGD} update steps as shown above, the \acs{Momentum} heuristic allows for the increase of momentum for dimensions whose gradients point in the same direction, while simultaneously reducing momentum for dimensions whose gradients change direction, leading to faster convergence and less oscillation.
-The momentum term $\alpha$ is usually set to 0.9~\cite{ref:engelbrecht:2007}\cite{ref:ruder:2016}.
-
-\subsection{Nesterov Accelerated Gradients}
-\label{sec:heuristics:nag}
-
-\Acl{NAG} is a variant of the \acs{Momentum} heuristics developed by Ilya Sutskever~\cite{ref:sutskever:2013-2} and is inspired from Yurii Nesterov's~\cite{ref:nesterov:1983} work on optimising convex functions.
+\noindent
+By redefining the \acs{SGD} update steps as shown above in Equations~\eqref{eq:heuristics:gd:momentum_part_1} and~\eqref{eq:heuristics:gd:momentum_part_2}, the \acs{Momentum} heuristic allows for the increase of momentum for dimensions whose gradients point in the same direction, while simultaneously reducing momentum for dimensions whose gradients change direction, leading to faster convergence and less oscillation.
+The momentum term $\alpha$ is usually set to 0.9~\cite{ref:engelbrecht:2007, ref:ruder:2016}.
+
+\subsection{Nesterov Accelerated Gradients}\label{sec:heuristics:nag}
+
+\Acf{NAG} is a variant of the \acs{Momentum} heuristic developed by~\citeauthor{ref:sutskever:2013-2}~\cite{ref:sutskever:2013-2} and is inspired from~\citeauthor{ref:nesterov:1983}~\cite{ref:nesterov:1983} work on optimising convex functions.
 \ac{NAG} provides an improvement to the momentum accumulation term by providing a look-ahead term that better refines the weight update step.
-In the \acs{NAG} heuristic, the gradient is not calculated w.r.t the current weights, but rather w.r.t the approximate future positions of the weights~\cite{ref:ruder:2016}.
-An illustration of this is taken from Geoffrey Hinton's lecture on mini-batch \ac{GD}~\cite{ref:hinton:2012} and is presented in Figure~\ref{fig:heuristics:gd:nag} below.
+
+In the \acs{NAG} heuristic, the gradient is not calculated w.r.t the current weights, but rather w.r.t the approximate future positions of the weights~\cite{ref:sutskever:2013-2, ref:ruder:2016}.
+An illustration of the weight update vector using \acs{NAG} is taken from Geoffrey Hinton's lecture on mini-batch \acs{GD}~\cite{ref:hinton:2012} and is presented in Figure~\ref{fig:heuristics:gd:nag} below.
 
 \begin{figure}[htbp]
-      \includegraphics[width=\textwidth]{images/nag.png}
-      \caption{An illustration of the weight update vector for \ac{NAG} taken from~\cite{ref:hinton:2012}.}
+      \centering
+      \includegraphics[width=0.95\textwidth]{images/nag.pdf}
+      \caption{An illustration of the weight update vector for \acf{NAG} taken from~\cite{ref:hinton:2012}.}
       \label{fig:heuristics:gd:nag}
@@
 
-\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} explains the update step as is done by \ac{NAG} is follows.
-\ac{Momentum} first computes the current gradient.
-This is seen by the small blue vector presented in Figure~\ref{fig:heuristics:gd:nag}.
-A large step is taken in the direction of the updated accumulated gradient, presented by the big blue vector.
-\ac{NAG} then first takes a big step in the direction of the previous accumulated gradient presented by the brown vector.
-At this point the gradient is measured and \ac{NAG} then makes a correction (red vector), which results in the complete NAG update (green vector).
-By anticipating approximate future positions of the weights, the weight update step as defined by \ac{NAG} controls the optimisation process from from going too fast and results in increased responsiveness.
-The \ac{NAG} weight vector update steps are given in Equations~\ref{eq:heuristics:gd:nag_part_1} and~\ref{eq:heuristics:gd:nag_part_2} below.
+\noindent
+The difference in the update step for \acs{Momentum} and the update step for \ac{NAG} as developed by~\citeauthor{ref:sutskever:2013-2}~\cite{ref:sutskever:2013-2} is described by~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} as follows.
+\ac{Momentum} first calculates the current gradient, represented by the small blue vector in Figure~\ref{fig:heuristics:gd:nag} and then takes a large step in the direction of the updated accumulated gradient, presented by the big blue vector.
+In contrast, \acs{NAG} first takes a big step in the direction of the previous accumulated gradient presented by the brown vector.
+At this point the gradient is measured and \acs{NAG} makes a correction represented by the red vector.
+The complete update step is represented by the green vector.
+By anticipating approximate future positions of the weights, the weight update step as defined by \ac{NAG} controls the optimisation process from going too fast and results in increased responsiveness~\cite{ref:bengio:2013}.
+The \acs{NAG} update steps are given in Equations~\eqref{eq:heuristics:gd:nag_part_1} and~\eqref{eq:heuristics:gd:nag_part_2} below.
 
@@
 
-The next logical step in the improvement of the weight vector update step is to tailor the update steps for each weight parameter controlling the magnitude of the update step based on the relevance and importance for that dimension.
-
-\subsection{Adaptive Gradients}
-\label{sec:heuristics:adagrad}
-
-\Acl{Adagrad} is an adaptation of \ac{SGD} which implements a learning rate for every parameter in the weight vector and is developed by Duchi et al.~\cite{ref:duchi:2011}.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that \Ac{Adagrad} adapts the learning rate to the weights, performing small updates (i.e.
+\subsection{Adaptive Gradients}\label{sec:heuristics:adagrad}
+
+\Acf{Adagrad} is an adaptation of \ac{SGD} which implements a learning rate for every element in the weight vector and is developed by Duchi et al.~\cite{ref:duchi:2011}.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that \acs{Adagrad} adapts the learning rate to the elements of the weight vector, by  performing small updates (i.e.
 low learning rates) for weights associated with frequently occurring features and larger updates (i.e.
 high learning rates) for weights associated with infrequent features.
-For this reason \ac{Adagrad} is well suited for dealing with situations with very sparse training data.
-
-In the \acs{GD} variants presented thus far, the weight updates have been applied to all weights at once using the same learning rate $\eta$ for all dimensions of the weight update vector.
-\Ac{Adagrad} uses a different learning rate for every weight $w_{i}$ at every timestep $t$.
-The weight update step as implemented by \ac{Adagrad} is presented in Equation~\ref{eq:heuristics:gd:adagrad_part_1} below.
+For this reason, \acs{Adagrad} is well suited for dealing with situations where training data is sparse.
+
+In the \acs{GD} variants presented thus far, the weight updates have been applied by making use of the same learning rate $\eta$ for all elements of the weight update vector.
+\Acs{Adagrad} uses a different learning rate for every weight element $w_{i}$, at every timestep $t$.
+The weight update step is presented in Equation~\eqref{eq:heuristics:gd:adagrad_part_1} below.
 
@@
 
-where $w_{i}$ is the $i$-th dimension of the weight vector, $G_{ii} \in \mathbb{R}^{d \times d}$ is a diagonal matrix where each diagonal element $i,i$ is the sum of the squared of the gradients w.r.t.
-$w_{i}$ up to timestep $t$ and $\epsilon$ is a smoothing term that avoids division by zero, usually set in the order of $1 \times 10^{-8}$~\cite{ref:ruder:2016}.
-Since $G_{t}$ contains the sum of the squares of the gradients with respect to all parameters $w$ along its diagonal, the weight update step can be vectorised and updated using the matrix-vector product between $G_{t}$ and $\nabla_{w_{i}}\mathcal{E}(w_{i})$.
-This is presented in Equation~\ref{eq:heuristics:gd:adagrad_part_2} below.
+\noindent
+In Equation~\eqref{eq:heuristics:gd:adagrad_part_1} above, $w_{i}$ is the $i$-th element of the weight vector, $G_{t,ii} \in \mathbb{R}^{d \times d}$ is a diagonal matrix where each diagonal element $i,i$ is the sum of the squared gradients w.r.t.
+$w_{i}$, up to timestep $t$ and $\epsilon$ is a smoothing term that avoids division by zero and is set to an insignificant value such as $1 \times 10^{-8}$.
+Since $G_{t}$ contains the sum of the squares of the gradients along its diagonal, the weight update step can be vectorised and updated using the matrix-vector product, represented by $\odot$, between $G_{t}$ and $\nabla_{w_{i}}\mathcal{E}(w_{i})$.
+The simplified update step as implemented by \acs{Adagrad} is given in Equation~\eqref{eq:heuristics:gd:adagrad_part_2} below.
 
@@
 
-\Ac{Adagrad}'s main benefit is that it does not require the need to manually tune the learning rate.
-However, a problem with \ac{Adagrad} is the accumulation of the sums of squared gradients in the denominator.
-Since every term that is added is positive, this number keeps growing, leading to a situation where the learning rate shrinks to the point that the heuristic is no longer able to learn.
-\acl{Adadelta} aims to improve on this problem.
-
-\subsection{Adaptive Learning Rate}
-\label{sec:heuristics:adadelta}
-
-In Section~\ref{sec:heuristics:adagrad} it was mentioned that one of the main problems of \ac{Adagrad} is that it has an aggressively monotonically decreasing learning rate because of the accumulation of the sum of squared gradients in its denominator.
-Zeiler~\cite{ref:zeiler:2012} presents an improvement on \ac{Adagrad} that eliminates this problem.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that instead of accumulating all past squared gradients as in the case of \ac{Adagrad}, \ac{Adadelta} restricts the window of accumulation to a window with a fixed size $W$.
+\noindent
+\Ac{Adagrad}'s main benefit is that it does not require manual tuning of the learning rate $\eta$.
+However, a problem with \ac{Adagrad} is in the accumulation of squared gradients in the denominator, represented by $G_{t}$.
+Since every term that is added is positive, $G_{t}$ keeps growing, leading to a situation where the learning rate shrinks to the point that the heuristic is no longer able to learn.
+
+\subsection{Adaptive Learning Rate}\label{sec:heuristics:adadelta}
+
+Zeiler~\cite{ref:zeiler:2012} presents \ac{Adadelta}, an improvement of \acs{Adagrad} that eliminates the accumulation of squared gradients in the denominator.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that instead of accumulating all past squared gradients as in the case of \ac{Adagrad}, \ac{Adadelta} restricts the window of accumulation to a window with a fixed size $W$.
 However, storing $W$ previous squared gradients is very inefficient.
-Instead, the accumulation of the sum of gradients over $W$ steps is defined recursively as a decaying average of all past squared gradients.
-The moving average $E[g^{2}]_{t}$ at timestep $t$ then depends only a fraction $\alpha$ of the previous average and current gradient, similar to the update step for \ac{Momentum}.
-In order to simplify the notation of update steps, let $g = \nabla_{w_{i}}\mathcal{E}(w_{t})$.
-The moving average update step for $E[g^{2}]_{t}$ is then presented in Equation~\ref{eq:heuristics:gd:adadelta_part_1} below.
+Instead, the accumulation of gradients over $W$ steps is defined recursively as a decaying average of all past squared gradients.
+In order to simplify the notation of update steps, let $g_{t} = \nabla_{w_{i}}\mathcal{E}(w_{t})$.
+The moving average of squared gradients at timestep $t$, denoted by $E[g^{2}]_{t}$  depends on a fraction $\alpha$ of the previous average of squared gradients and the current gradient, similar to the update step for \acs{Momentum}.
+Similar to \acs{Momentum}, $\alpha$ is set to 0.9.
+The update step for $E[g^{2}]_{t}$ is presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_1} below.
 
@@
 
-The value for $\alpha$ is set to a similar value, 0.9, as was done with \ac{Momentum}.
-For sake of clarity, the basic \ac{SGD} update step is rewritten in terms of the weight update vector $\Delta w_{t}$.
-This is presented in Equations~\ref{eq:heuristics:gd:adadelta_part_2} and~\ref{eq:heuristics:gd:adadelta_part_2} below.
+\noindent
+To illustrate the difference between \acs{Adagrad} and \acs{Adadelta}, the \ac{SGD} update step as presented in~\eqref{eq:heuristics:gd:sgd} is rewritten in terms of the weight update vector $\Delta w_{t}$ and gradient $g_{t}$ and is presented in Equations~\ref{eq:heuristics:gd:adadelta_part_2} and~\eqref{eq:heuristics:gd:adadelta_part_2} below.
 
@@
 
-The weight update vector for \ac{Adagrad} as defined in Equation~\ref{eq:heuristics:gd:adagrad_part_2} is then rewritten as
+\noindent
+The weight update vector for \ac{Adagrad} is then redefined in Equation~\eqref{eq:heuristics:gd:adagrad_part_2} below.
 
@@
 
-The diagonal matrix $G_{t}$ is then replaced with the decaying average over the past $W$ squared gradients as presented in Equation~\ref{eq:heuristics:gd:adadelta_part_4} below.
+\noindent
+The diagonal matrix $G_{t}$, implemented by \ac{Adagrad}, is then replaced with the moving average of squared gradients as presented in Equation~\ref{eq:heuristics:gd:adadelta_part_4} below.
 
@@
 
-Since the denominator is the \acs{RMS} error criterion of the gradient, the criteria short-hand notation is used as follows.
+\noindent
+Since the denominator is the \acf{RMS} error criterion of the gradient, the criteria short-hand notation is used as is depicted in Equation~\eqref{eq:heuristics:gd:adadelta_part_5} below.
 
@@
 
-\citeauthor{ref:ruder:2016}\cite{ref:ruder:2016} highlights that the original authors~\cite{ref:zeiler:2012} noted that the units of the update step as presented in Equation~\ref{eq:heuristics:gd:adadelta_part_2} do not match i.e.
-the update vector should have the same hypothetical units as the weight vector.
-To realize this, another exponentially decaying average is defined in terms of squared weight updates as is presented in Equation~\ref{eq:heuristics:gd:adadelta_part_6} below.
+\noindent
+~\citeauthor{ref:zeiler:2012}~\cite{ref:zeiler:2012} noted that the units of the update step as presented in Equation~\ref{eq:heuristics:gd:adadelta_part_5} do not match.
+The weight update vector should have the same hypothetical units as the weight vector.
+To fix the aforemention problem, another exponentially decaying average is defined in terms of squared weight updates as is presented in Equation~\ref{eq:heuristics:gd:adadelta_part_6} below.
 
@@
       \begin{split}
-            E[\Delta w^{2}]_{t} = \alpha E[\Delta w^{2}]_{t - 1} + (1 - \alpha)\Delta w^{2}
-      \end{split}
-\end{equation}
-
-The \ac{RMS} error of weight updates is thus
+            E[\Delta w^{2}]_{t} = \alpha E[\Delta w^{2}]_{t - 1} + (1 - \alpha)\Delta w_{t}^{2}
+      \end{split}
+\end{equation}
+
+\noindent
+The \acf{RMS} error of weight updates is given in Equation~\ref{eq:heuristics:gd:adadelta_part_7} below.
 
@@
 
+\noindent
 Note that $RMS[\Delta w]_{t}$ is unknown at timestep $t$.
-It is thus approximated with the \acs{RMS} of weight updates until the previous timestep.
-The learning rate in Equation~\ref{eq:heuristics:gd:adadelta_part_5} is then replaced as follows.
+$RMS[\Delta w]_{t}$ is approximated with the \acf{RMS} of weight updates until the previous timestep.
+The learning rate in Equation~\eqref{eq:heuristics:gd:adadelta_part_5} is then replaced.
+The weight update step for \acs{Adadelta} is then concluded in Equation~\eqref{eq:heuristics:gd:adadelta_part_8} below.
 
@@
 
-Finally, the weight update step for \ac{Adadelta} is concluded as follows.
-
-\begin{equation}
-      \label{eq:heuristics:gd:adadelta_part_9}
-      \begin{split}
-            w_{t+1} = w_{t} + \Delta w_{t}
-      \end{split}
-\end{equation}
-
-The main advantage of \ac{Adadelta} is that one does not have to provide a default learning rate a priori as it is no longer included in the weight update step.
-
-\subsection{Root Mean Squared Error Propagation}
-\label{sec:heuristics:rmsprop}
-
-\Ac{RMSProp} is a similar heuristic to \ac{Adadelta} presented by Geoffrey Hinton~\cite{ref:hinton:2012} and was developed independently around the same time.~\citeauthor{ref:ruder:2016}\cite{ref:ruder:2016} mentions that \ac{RMSProp} is in fact the same as the first weight update vector as defined for \ac{Adadelta}.
-The update step for \ac{RMSProp} is then defined in terms of a decaying running average of gradients squared as is presented again for convenience in Equations~\ref{eq:heuristics:gd:rmsprop_part_1} and~\ref{eq:heuristics:gd:rmsprop_part_2} below.
-
-\begin{equation}
-      \label{eq:heuristics:gd:rmsprop_part_1}
-      \begin{split}
-            E[g^{2}]_{t} = \alpha E[g^{2}]_{t - 1} + (1 - \alpha)g_{t}^{2}
-      \end{split}
-\end{equation}
-
-\begin{equation}
-      \label{eq:heuristics:gd:rmsprop_part_2}
-      \begin{split}
-            w_{t+1} = w_{t} - \frac{\eta}{\sqrt{E[g^{2}]_{t} + \epsilon}} g_{t}
-      \end{split}
-\end{equation}
-
-Note that \ac{RMSProp} still includes the learning rate term $\eta$ meaning that a default learning rate is required a priori.
-This is one of the disadvantages of \ac{RMSProp}.
-Hinton suggests $\alpha$ be set to 0.9 and $\eta$ be set to $0.001$~\cite{ref:hinton:2012}.
-
-\subsection{Adaptive Moments Estimation}
-\label{sec:heuristics:adam}
-
-\Ac{Adam} is another variant of \ac{SGD} that includes adaptive learning rates and is presented by Kingma et.
-al~\cite{ref:kingma:2014}.
-However, in addition to storing an exponentially decaying average of past squared gradients like \ac{Adadelta} and \ac{RMSProp}, \ac{Adam} also stores an exponentially decaying average of past gradients $v_{t}$, similar to \ac{Momentum}~\cite{ref:ruder:2016}.~\citeauthor{ref:heusel:2017}~\cite{ref:heusel:2017} uses the analogy that \ac{Momentum} can be seen as a ball running down a slope, while \ac{Adam} behaves like a heavy ball with friction, which thus prefers flat minima in the error surface.
-
+\noindent
+The main advantage of \ac{Adadelta} is in removing the need for a learning rate.
+
+\subsection{Root Mean Squared Error Propagation}\label{sec:heuristics:rmsprop}
+
+\Acf{RMSProp}, presented by~\citeauthor{ref:hinton:2012}~\cite{ref:hinton:2012} is similar to \acs{Adadelta}  and was developed independently around the same time.
+\ac{RMSProp} is the same as the first weight update vector for \ac{Adadelta}, presented in~\eqref{eq:heuristics:gd:adadelta_part_4}.
+A disadvantage of \acs{RMSProp} is that it still includes the learning rate term $\eta$ that needs to be tuned.
+For \acs{RMSProp},~\citeauthor{ref:hinton:2012}~\cite{ref:hinton:2012} suggests $\alpha$ be set to 0.9 and $\eta$ be set to $0.001$.
+
+\subsection{Adaptive Moments Estimation}\label{sec:heuristics:adam}
+
+\Acf{Adam} is another variant of \ac{SGD} that includes adaptive learning rates and is presented by~\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014}.
+In addition to storing an exponentially decaying average of past squared gradients like \acs{Adadelta} and \acs{RMSProp}, \acs{Adam} also stores an exponentially decaying average of past gradients, similar to \ac{Momentum}~\cite{ref:ruder:2016}.~\citeauthor{ref:heusel:2017}~\cite{ref:heusel:2017} uses the analogy that, if \acs{Momentum} can be seen as a ball running down a slope, then \acs{Adam} behaves like a heavy ball with friction, which prefers flat minima in the error surface.
 The decaying averages for past gradients and past squared gradients is given in Equations~\ref{eq:heuristics:gd:adam_part_1} and~\ref{eq:heuristics:gd:adam_part_2} respectively.
@@
 
+\noindent
 In Equations~\ref{eq:heuristics:gd:adam_part_1} and~\ref{eq:heuristics:gd:adam_part_2} above, $\beta_{1}$ and $\beta_{2}$ are decay rates, similar to $\alpha$ for \ac{Momentum}.
-
-\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that $v_{t}$ and $w_{t}$ presented above are estimates of the first moment (the mean) and the second moment (the uncentered variance) of the gradients respectively.
-It is from these moment terms that the name \acl{Adam} is derived.~\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} mentions that because $v_{t}$ and $w_{t}$ is initialised to be vectors of 0's, they are biased towards 0.
-This is especially true during the initial timesteps and/or when the decay rates $\beta_{1}$ and $\beta_{2}$ are small (i.e.
-$\beta_{1}$ and $\beta_{2}$ is close to 1).
+\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} suggest default values $B_{1}=0.9$, $B_{2}=0.999$ and $\epsilon = 1 \times 10^{-8}$.
+
+\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that $m_{t}$ and $v_{t}$ presented above are estimates of the first moment (the mean) and the second moment (the uncentered variance) of the gradients respectively.
+~\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} mentions that because $m_{t}$ and $v_{t}$ are initialised to be vectors of 0's, they are biased towards 0.
+The aforementioned bias is especially prominent during the initial timesteps and/or when the decay rates $\beta_{1}$ and $\beta_{2}$ are small ($\beta_{1}$ and $\beta_{2}$ are close to 1).
 These biases need to be corrected.
@@
 
-The \ac{Adam} update rule is then presented in Equation~\ref{eq:heuristics:gd:adam} below.
+\noindent
+The \acs{Adam} update rule is then presented in Equation~\ref{eq:heuristics:gd:adam} below.
 
@@
 
-\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} suggest default values $B_{1}=0.9$, $B_{2}=0.999$ and $\epsilon = 1 \times 10^{-8}$.
-This section provided the reader with a collection of gradient-based heuristics.
-The next section introduces meta-heuristics.
+\noindent
+This section provided the reader with a collection of gradient-based \index{heuristic}heuristics. The next section presents the reader with \index{meta-heuristic}meta-heuristics.
 

### 2022-10-24 dissertation/chapters/03-heuristics.tex
🚧 (chapter 3): Just before DE

@@
 
-      \item \textbf{Section~\ref{sec:heuristics:what_is_a_heuristic}} provides background information on the origins and definition the term \index{heuristic}\textit{heuristic}.
+      \item \textbf{Section~\ref{sec:heuristics:what_is_a_heuristic}} provides background information on the origins and definition of the term \index{heuristic}\textit{heuristic}.
 It is shown that \index{heuristic}heuristics are a class of algorithms that are used to solve optimisation problems.
@@
 The term \textit{heuristic} comes from the Latin word \textit{heuristicus} which means ``to find out or discover''.~\citeauthor{ref:romanycia:1985}~\cite{ref:romanycia:1985} provides a complete study on the history and origins of the term \index{heuristic}\textit{heuristic}.
-From their research, a proposal is made to define \index{heuristic}heuristics in the context of \acf{AI}, as any device, be it a program, rule, piece of knowledge, which is added to a problem-solving system, in expectation that on average, the performance will improve.
+From their research, a proposal is made to define \index{heuristic}heuristics in the context of \acf{AI}, as any device, be it a program, rule, piece of knowledge, which is added to a problem-solving system, in expectation that, on average, the performance will improve.
 
@@
 It can thus be said that gradient-based \index{heuristic}heuristics make use of information directly from the \textit{search space}.
-On the contrary, \index{heuristic}heuristics such as \index{hmeta-euristic}meta-heuristics make use of meta-information obtained as a result of evaluating the \acs{FFNN}~\cite{ref:blum:2003}.
+On the contrary, \index{heuristic}heuristics such as \index{meta-heuristic}meta-heuristics make use of meta-information obtained as a result of evaluating the \acs{FFNN}~\cite{ref:blum:2003}.
 The meta-information that \index{meta-heuristic}meta-heuristics make use of could include ranked-performance of a population of candidate solutions, referred to as \textit{entities}.
@@
 
-Although \acs{GD} \index{heuristic}heuristics where not the first \index{heuristic}heuristics used to train \acp{FFNN}
-\cite{ref:engelbrecht:2007}, they are certainly the most whidely used.
-\Acs{GD} heuristics have become increasingly popular partly due to their simplicity and low computational overhead compared to other \index{heuristic}heuristics such as \index{meta-heuristic}meta-heuristics and other second-order derivative methods such as Newtons' method.
-There are many variants of \acs{GD} \index{heuristic}heuristics, however, they all fundamentally apply the same generic \acs{GD} framework called \acl{BP}.
+Although gradient-based \index{heuristic}heuristics where not the first \index{heuristic}heuristics used to train \acp{FFNN}
+\cite{ref:engelbrecht:2007}, they are certainly the most widely used.
+Gradient-based heuristics have become increasingly popular partly due to their simplicity and low computational overhead compared to other \index{heuristic}heuristics such as \index{meta-heuristic}meta-heuristics and other second-order derivative methods such as Newtons' method.
+There are many variants of gradient-based \index{heuristic}heuristics, however, they all fundamentally apply the same generic \acs{GD} framework called \acf{BP}.
 
@@
 \noindent
-The update step for \acs{GD} can be formulated as is shown in Equation~\eqref{eq:heuristics:gd:update_step_part_1} below.
+In the context of training \textit{shallow} \acp{FFNN} using \index{supervised learning}supervised learning, the error signal is propagated backwards in the network from the output layer, through the hidden layer to the input layer, updating the weights at the output and hidden layers.
+The algorithm that propagates the error signal backwards is known as \acf{BP}.
+\Acs{BP} was popularised by~\citeauthor{ref:werbos:1994}~\cite{ref:werbos:1994}.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} states that \acs{BP} provides a procedure for updating the network weights, layer by layer, by evaluating the derivatives of the error function $\mathcal{E}$, with respect to the weights at each layer.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} describes the \acs{BP} process in two steps:
+
+\begin{itemize}
+      \item \textbf{Feedforward Pass}: During this phase the output values of the \acs{FFNN} is calculcated for each training pattern.
+
+      \item \textbf{Backward Propagation}: During this phase the error signal is propagated backwards from the output layer, through the hidden layer, to the input layer of the \acs{FFNN}.
+Weights at the output and hidden layers are then adjusted as functions of the backpropagated error signal.
+\end{itemize}
+
+\noindent
+The update step for \acs{GD} by means of \acs{BP} can be formulated as is shown in Equations~\eqref{eq:heuristics:gd:update_step_part_1}-\eqref{eq:heuristics:gd:update_step_part_3} below.
 
@@
 \noindent
-In Equation~\eqref{eq:heuristics:gd:update_step_part_1} above, the delta weight $\Delta w$, at index $i$ and timestep $t$ is given by Equation~\eqref{eq:heuristics:gd:update_step_part_2} below.
+In Equation~\eqref{eq:heuristics:gd:update_step_part_1} above, $w_{i}$ is the weight value at index $i$, $t$ is the timestep, $\Delta w_{i}(t)$ is the weight update vector at index $i$ and timestep $t$.
+$\Delta w_{i}(t)$ is specified by Equation~\eqref{eq:heuristics:gd:update_step_part_2} below.
 
@@
 \noindent
-In Equation~\eqref{eq:heuristics:gd:update_step_part_2} above, $\eta$ is the learning rate.
-The learning rate is an important hyper-parameter in gradient-based \index{heuristic}heuristic as it controls the step-size that is taken in the direction of the negative gradient at each timestep.
+In Equation~\eqref{eq:heuristics:gd:update_step_part_2} above, $\eta$ is the learning rate and $\frac{\partial \epsilon}{\partial w_{i}}$ is the \textit{gradient} of the error, as a result of a loss function, relative to the weight at index $i$.
+The learning rate is an important hyper-parameter in gradient-based \index{heuristic}heuristics as it controls the step-size that is taken in the direction of the negative gradient at each timestep.
 Assuming the use of \acs{SSE} as the loss function, the partial derivative of $\epsilon$, relative to the weight $w$, at index $i$, is given by Equation~\eqref{eq:heuristics:gd:update_step_part_3} below.
@@
 \noindent
-In the context of training \textit{shallow} \acp{FFNN}, using \index{supervised learning}supervised learning, the error signal is propagated backwards in the network from the output layer, through the hidden layer.
-The algorithm that propagates the error signal backwardds is known as \acf{BP}.
-\Acs{BP} was popularised by~\citeauthor{ref:werbos:1994}~\cite{ref:werbos:1994}.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} states that \acs{BP} provides a procedure for updating the network weights, layer by layer, by evaluating the derivatives of the error function $\epsilon$ with respect to the weights at each layer.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007}describes the \acs{BP} process in two steps:
-
-\begin{itemize}
-      \item \textbf{Feedforward Pass}: During this phase the output values of the \acs{FFNN} is calculcated for each training pattern.
-
-      \item \textbf{Backward Propagation}: During this phase the error signal that is calculated as is shown above in Equations~\eqref{eq:heuristics:gd:update_step_part_1}, ~\eqref{eq:heuristics:gd:update_step_part_2} and~\eqref{eq:heuristics:gd:update_step_part_3} is propagated backwards from the output layer, through the hidden layer, to the input layer of the \acs{FFNN}.
-Weights are then adjusted as functions of the backpropagated error signal.
-\end{itemize}
-
-\noindent
-The pseudo-code implementation for the generic \acs{GD} algorithm is taken from~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:gd:gd} below.
+In Equation~\eqref{eq:heuristics:gd:update_step_part_3} above, $t_{p}$ refers to the target value for pattern $p$, $o_{p}$ refers to the output value for pattern $p$, $f$ refers to the \index{activation function}activation function, $net_{p}$ refers to the \index{net input signal}net input signal for pattern $p$, and $z_{i,p}$ refers to the input value at index $i$ for pattern $p$.
+
+Finally, assuming the use of \index{sigmoid}sigmoid activation function, the partial derivative of the activation function, relative to the net input signal is given in Equation~\eqref{eq:heuristics:gd:update_step_part_4} below.
+
+\begin{equation}
+      \label{eq:heuristics:gd:update_step_part_4}
+      \frac{\partial f}{\partial net_{p}} = o_p(1 - o_{p})
+\end{equation}
+
+\noindent
+Again, assuming the use of \acs{SSE} as the loss function, the pseudo-code implementation for the generic \acs{GD} algorithm is taken from~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:gd:gd} below.
 
@@
             \For{each training pattern p}
-            \State Do the feedforward pass phase to calculate the output of the hidden layer $y_{j,p}$ ($\forall j = 1, \dots, J$), and the output of the output layer $o_{k,p}$ ($\forall k = 1, \dots, K$);
-            \State Compute the output error signals $\delta_{o_{k,p}}$ and the hidden layer error signals $\delta_{y_{j,p}}$;
-            \State Adjust the weights of the output layer $w_{kj}$, and the weights of the hidden layer $v_{ji}$ (backpropagation of errors);
-            \State $\epsilon_{T}$ += $[\epsilon_{T_{p}} = \sum^{K}_{k=1}(t_{k,p} - o_{k,p})^{2}]$; (assuming the use of \acs{SSE} as the loss function)
+            \State Calculate the output of the hidden and output layers (feedforward);
+            \State Compute the error signals of the hidden and output layers;
+            \State Adjust the weights of the output and hidden layers (backpropagate);
+            \State $\epsilon_{T}$ += $[\epsilon_{T_{p}} = \sum^{K}_{k=1}(t_{k,p} - o_{k,p})^{2}]$;
             \EndFor
@@
 \noindent
-In order to provide a simplified frame of reference from which the gradient-based heuristics are compared, consider a simplification of the update-step for \acs{SGD} as presented in Equation~\eqref{eq:heuristics:gd:update_step_part_1}.
-This simplification is depicted in Equation~\eqref{eq:heuristics:gd:sgd} below.
+A simplified notation is proposed from which the gradient-based heuristics can be compared.
+Consider a simplification of the update-step for \acs{SGD} as presented in Equations~\eqref{eq:heuristics:gd:update_step_part_1} and~\eqref{eq:heuristics:gd:update_step_part_2} where $\frac{\partial \epsilon}{\partial w_{i}}$ is simply represented as the gradient term $g$, resulting in a simplified weight update step as is shown in Equation~\eqref{eq:heuristics:gd:sgd} below.
 
@@
       \begin{split}
-            w = w - \eta \nabla_{w}\mathcal{E}(w)
-      \end{split}
-\end{equation}
-
-\noindent
-In Equation~\eqref{eq:heuristics:gd:sgd} above, $w$ refers to the weights of the \acs{FFNN}, $\eta$ refers to the learning rate as before and $\nabla_{w}\mathcal{E}(w)$ refers to the gradient of the loss function $\mathcal{E}$, w.r.t the output of the \acs{FFNN} as a result of its weights.
-Note that all subscripts w.r.t.
-layers and training patterns are omitted for convenience.
+            w = w - \eta g
+      \end{split}
+\end{equation}
+
+\noindent
+In Equation~\eqref{eq:heuristics:gd:sgd} above, $w$ refers to the weight vector, $\eta$ refers to the learning rate as before and $g$ refers to the gradient of the error function relative to weight vector.
+Note that, vector notation and some subscripts related to layers, indices, timesteps and training patterns are omitted for convenience.
 
@@
 
-This section shines light on the algorithmic implementation of \ac{BP} with specific context to stochastic and batch training.
+This section shines light on the algorithmic implementation of \acs{BP} with specific context to stochastic and batch training.
 The implementation of \acs{GD} using stochastic training is referred to as \acf{SGD}.
 
-\acs{SGD} was one of the first widely used heuristics to train \ac{FFNN}, however, it is not without flaws.
+\acs{SGD} was one of the first widely used heuristics to train \acs{FFNN}, however, it is not without flaws.
 With stochastic training, only one training pattern is presented at each iteration/epoch.
 As such, weight updates are done with high variance and noise~\cite{ref:ruder:2016}.
-An illustration of the the fluctuations caused by \ac{SGD} during training is given in Figure~\ref{fig:heuristics:gd:sgd}.
+An illustration of the the fluctuations caused by \acs{SGD} during training is given in Figure~\ref{fig:heuristics:gd:sgd}.
 
@@
 
-A compromise to overshooting minima that \acs{SGD} suffers from, is to include mini-batches of training patterns where a small number of training patterns are presented to the \acs{FFNN} at once.
+A compromise to overshooting minima that \acs{SGD} suffers from, is to make use of mini-batches of training patterns where a small number of training patterns are presented to the \acs{FFNN} at once.
 This is referred to as \textit{mini-batch} training.
@@
 
-      \item The learning rate that has been introduced so far is applied to all elements of the weight vector updates.
-If the training data is sparse and the features have very different frequencies, an equal update to all weights elements is inefficient.
+      \item The learning rate that has been introduced so far is applied to all elements of the weight update vector.
+If the training data is sparse and the features have varying frequencies, an equal update to all weight elements is inefficient.
 Larger weight updates are required for less frequently occurring features.
@@
 
-Research shows that \ac{SGD} has difficulty navigating ravines~\cite{ref:sutton:1986}.
+Research shows that \acs{SGD} has difficulty navigating ravines~\cite{ref:sutton:1986}.
 Ravines are areas where the surface curves much more steeply in one dimension than in another.
@@
 
-\Acs{Momentum} ~\cite{ref:qian:1999} is a variant of the \acs{SGD} that helps accelerate \ac{SGD} in the relevant direction, dampening oscillations.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$, of the weight update vector of the previous timestep to the current weight update vector.
+\Acs{Momentum} ~\cite{ref:qian:1999} is a variant of the \acs{SGD} that helps accelerate \acs{SGD} in the relevant direction, dampening oscillations.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$, of the weight update vector of the previous timestep to the current weight update vector.
 An illustration of \acs{SGD} with and without momentum is given in Figure~\ref{fig:heuristics:gd:sgd_with_and_without_momentum}.
@@
 \noindent
-The accumulation of momentum is presented in Equation~\eqref{eq:heuristics:gd:momentum_part_1} below, while the update step is then amended in Equation~\ref{eq:heuristics:gd:momentum_part_2} below.
+The accumulation of momentum is presented in Equation~\eqref{eq:heuristics:gd:momentum_part_1} below, while the update step is then amended in Equation~\eqref{eq:heuristics:gd:momentum_part_2} below.
 
@@
       \begin{split}
-            v_{t} = \alpha v_{t-1} + \eta \nabla_{w}\mathcal{E}(w)
+            v = \alpha v - \eta g
       \end{split}
@@
       \begin{split}
-            w = w - v_{t}
+            w = w + v
       \end{split}
@@
 
-\Acf{NAG} is a variant of the \acs{Momentum} heuristic developed by~\citeauthor{ref:sutskever:2013-2}~\cite{ref:sutskever:2013-2} and is inspired from~\citeauthor{ref:nesterov:1983}~\cite{ref:nesterov:1983} work on optimising convex functions.
-\ac{NAG} provides an improvement to the momentum accumulation term by providing a look-ahead term that better refines the weight update step.
+\Acf{NAG} is a variant of the \acs{Momentum} heuristic developed by~\citeauthor{ref:sutskever:2013-2}~\cite{ref:sutskever:2013-2} and is inspired by~\citeauthor{ref:nesterov:1983}'s~\cite{ref:nesterov:1983} work on optimising convex functions.
+\acs{NAG} provides an improvement to the momentum accumulation term by providing a look-ahead term that better refines the weight update step.
 
@@
 \noindent
-The difference in the update step for \acs{Momentum} and the update step for \ac{NAG} as developed by~\citeauthor{ref:sutskever:2013-2}~\cite{ref:sutskever:2013-2} is described by~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} as follows.
-\ac{Momentum} first calculates the current gradient, represented by the small blue vector in Figure~\ref{fig:heuristics:gd:nag} and then takes a large step in the direction of the updated accumulated gradient, presented by the big blue vector.
+The difference in the update step for \acs{Momentum} and the update step for \acs{NAG} as developed by~\citeauthor{ref:sutskever:2013-2}~\cite{ref:sutskever:2013-2} is described by~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} as follows.
+\acs{Momentum} first calculates the current gradient, represented by the small blue vector in Figure~\ref{fig:heuristics:gd:nag} and then takes a large step in the direction of the updated accumulated gradient, presented by the big blue vector.
 In contrast, \acs{NAG} first takes a big step in the direction of the previous accumulated gradient presented by the brown vector.
@@
 The complete update step is represented by the green vector.
-By anticipating approximate future positions of the weights, the weight update step as defined by \ac{NAG} controls the optimisation process from going too fast and results in increased responsiveness~\cite{ref:bengio:2013}.
-The \acs{NAG} update steps are given in Equations~\eqref{eq:heuristics:gd:nag_part_1} and~\eqref{eq:heuristics:gd:nag_part_2} below.
-
-\begin{equation}
-      \label{eq:heuristics:gd:nag_part_1}
-      \begin{split}
-            v_{t} = \alpha v_{t-1} + \eta \nabla_{w}\mathcal{E}(w - \alpha v_{t-1})
-      \end{split}
-\end{equation}
+By anticipating approximate future positions of the weights, the weight update step as defined by \acs{NAG} controls the optimisation process from going too fast and results in increased responsiveness~\cite{ref:bengio:2013}.
+Along with the same velocity update step for \acs{Momentum}, as presented in Equation~\eqref{eq:heuristics:gd:momentum_part_1}, the \acs{NAG} weight update step is given in Equation~\eqref{eq:heuristics:gd:nag_part_2} below.
 
@@
       \begin{split}
-            w = w - v_{t}
+            w = w + \alpha v - \eta g
       \end{split}
@@
 
-\Acf{Adagrad} is an adaptation of \ac{SGD} which implements a learning rate for every element in the weight vector and is developed by Duchi et al.~\cite{ref:duchi:2011}.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that \acs{Adagrad} adapts the learning rate to the elements of the weight vector, by  performing small updates (i.e.
+\Acf{Adagrad} is an adaptation of \acs{SGD} which implements a learning rate for every element in the weight vector and is developed by Duchi et al.~\cite{ref:duchi:2011}.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that \acs{Adagrad} adapts the learning rate to the elements of the weight vector, by  performing small updates (i.e.
 low learning rates) for weights associated with frequently occurring features and larger updates (i.e.
@@
 
-In the \acs{GD} variants presented thus far, the weight updates have been applied by making use of the same learning rate $\eta$ for all elements of the weight update vector.
+In the \acs{GD} variants presented thus far, the weight updates have been applied by making use of the same learning rate $\eta$, for all elements of the weight update vector.
 \Acs{Adagrad} uses a different learning rate for every weight element $w_{i}$, at every timestep $t$.
-The weight update step is presented in Equation~\eqref{eq:heuristics:gd:adagrad_part_1} below.
+The weight update step for \acs{Adagrad} is presented in Equation~\eqref{eq:heuristics:gd:adagrad_part_1} below.
 
@@
       \begin{split}
-            w_{t+1,i} = w_{t,i} - \frac{\eta}{\sqrt{G_{t,ii} + \epsilon}}.\nabla_{w_{i}}\mathcal{E}(w_{t,i})
-      \end{split}
-\end{equation}
-
-\noindent
-In Equation~\eqref{eq:heuristics:gd:adagrad_part_1} above, $w_{i}$ is the $i$-th element of the weight vector, $G_{t,ii} \in \mathbb{R}^{d \times d}$ is a diagonal matrix where each diagonal element $i,i$ is the sum of the squared gradients w.r.t.
+            w_{t+1,i} = w_{t,i} - \frac{\eta}{\sqrt{G_{t,ii} + \epsilon}}.g_{t,i}
+      \end{split}
+\end{equation}
+
+\noindent
+In Equation~\eqref{eq:heuristics:gd:adagrad_part_1} above, $w_{i}$ is the $i$-th element of the weight vector, $G_{t,ii} \in \mathbb{R}^{d \times d}$ is a diagonal matrix where each diagonal element $i,i$, is the sum of the squared gradients w.r.t.
 $w_{i}$, up to timestep $t$ and $\epsilon$ is a smoothing term that avoids division by zero and is set to an insignificant value such as $1 \times 10^{-8}$.
-Since $G_{t}$ contains the sum of the squares of the gradients along its diagonal, the weight update step can be vectorised and updated using the matrix-vector product, represented by $\odot$, between $G_{t}$ and $\nabla_{w_{i}}\mathcal{E}(w_{i})$.
+Since $G_{t}$ contains the sum of the squares of the gradients along its diagonal, the weight update step can be vectorised and updated using the matrix-vector product, represented by $\odot$, between $G_{t}$ and $g_{t,i}$.
 The simplified update step as implemented by \acs{Adagrad} is given in Equation~\eqref{eq:heuristics:gd:adagrad_part_2} below.
@@
       \begin{split}
-            w_{t+1} = w_{t} - \frac{\eta}{\sqrt{G_{t} + \epsilon}} \odot \nabla_{w_{i}}\mathcal{E}(w_{t})
+            w_{t+1} = w_{t} - \frac{\eta}{\sqrt{G_{t} + \epsilon}} \odot g_{t,i}
       \end{split}
@@
 \Ac{Adagrad}'s main benefit is that it does not require manual tuning of the learning rate $\eta$.
-However, a problem with \ac{Adagrad} is in the accumulation of squared gradients in the denominator, represented by $G_{t}$.
+However, a problem with \acs{Adagrad} is in the accumulation of squared gradients in the denominator, represented by $G_{t}$.
 Since every term that is added is positive, $G_{t}$ keeps growing, leading to a situation where the learning rate shrinks to the point that the heuristic is no longer able to learn.
@@
 
-Zeiler~\cite{ref:zeiler:2012} presents \ac{Adadelta}, an improvement of \acs{Adagrad} that eliminates the accumulation of squared gradients in the denominator.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that instead of accumulating all past squared gradients as in the case of \ac{Adagrad}, \ac{Adadelta} restricts the window of accumulation to a window with a fixed size $W$.
+Zeiler~\cite{ref:zeiler:2012} presents \acs{Adadelta}, an improvement of \acs{Adagrad} that eliminates the accumulation of squared gradients in the denominator.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that instead of accumulating all past squared gradients as in the case of \acs{Adagrad}, \acs{Adadelta} restricts the window of accumulation to a window with a fixed size $W$.
 However, storing $W$ previous squared gradients is very inefficient.
 Instead, the accumulation of gradients over $W$ steps is defined recursively as a decaying average of all past squared gradients.
-In order to simplify the notation of update steps, let $g_{t} = \nabla_{w_{i}}\mathcal{E}(w_{t})$.
 The moving average of squared gradients at timestep $t$, denoted by $E[g^{2}]_{t}$  depends on a fraction $\alpha$ of the previous average of squared gradients and the current gradient, similar to the update step for \acs{Momentum}.
-Similar to \acs{Momentum}, $\alpha$ is set to 0.9.
+Also similar to \acs{Momentum}, $\alpha$ is set to 0.9.
 The update step for $E[g^{2}]_{t}$ is presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_1} below.
@@
 \noindent
-To illustrate the difference between \acs{Adagrad} and \acs{Adadelta}, the \ac{SGD} update step as presented in~\eqref{eq:heuristics:gd:sgd} is rewritten in terms of the weight update vector $\Delta w_{t}$ and gradient $g_{t}$ and is presented in Equations~\ref{eq:heuristics:gd:adadelta_part_2} and~\eqref{eq:heuristics:gd:adadelta_part_2} below.
+To illustrate the difference between \acs{Adagrad} and \acs{Adadelta}, the \acs{SGD} weight update step for \acs{Adagrad}, as presented in~\eqref{eq:heuristics:gd:adagrad_part_2} is rewritten such that the diagonal matrix $G_{t}$, is replaced with the moving average of squared gradients as presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_2} below.
 
@@
       \begin{split}
-            \Delta w_{t} = -\eta g_{t,i}
-      \end{split}
-\end{equation}
+            w_{t+1} = w_{t} - \frac{\eta}{\sqrt{E[g^{2}]_{t} + \epsilon}} g_{t}
+      \end{split}
+\end{equation}
+
+\noindent
+Since the denominator is the \acf{RMS} error criterion of the gradient, the criteria short-hand notation is used as is depicted in Equation~\eqref{eq:heuristics:gd:adadelta_part_3} below.
 
@@
       \begin{split}
-            w_{t+1} = w_{t} + \Delta w_{t}
-      \end{split}
-\end{equation}
-
-\noindent
-The weight update vector for \ac{Adagrad} is then redefined in Equation~\eqref{eq:heuristics:gd:adagrad_part_2} below.
-
-\begin{equation}
-      \label{eq:heuristics:gd:adagrad_part_2_new}
-      \begin{split}
-            \Delta w_{t} = - \frac{\eta}{\sqrt{G_{t} + \epsilon}} \odot g_{t}
-      \end{split}
-\end{equation}
-
-\noindent
-The diagonal matrix $G_{t}$, implemented by \ac{Adagrad}, is then replaced with the moving average of squared gradients as presented in Equation~\ref{eq:heuristics:gd:adadelta_part_4} below.
+            w_{t+1} = w_{t} - \frac{\eta}{RMS[g]_{t}} g_{t}
+      \end{split}
+\end{equation}
+
+\noindent
+~\citeauthor{ref:zeiler:2012}~\cite{ref:zeiler:2012} noted that the units of the update step as presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_3} do not match.
+The weight update vector should have the same hypothetical units as the weight vector.
+To fix the aforemention problem, another exponentially decaying average is defined in terms of squared weight updates as is presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_4} below.
 
@@
       \begin{split}
-            \Delta w_{t} = - \frac{\eta}{\sqrt{E[g^{2}]_{t} + \epsilon}} g_{t}
-      \end{split}
-\end{equation}
-
-\noindent
-Since the denominator is the \acf{RMS} error criterion of the gradient, the criteria short-hand notation is used as is depicted in Equation~\eqref{eq:heuristics:gd:adadelta_part_5} below.
+            E[\Delta w^{2}]_{t} = \alpha E[\Delta w^{2}]_{t - 1} + (1 - \alpha)\Delta w_{t}^{2}
+      \end{split}
+\end{equation}
+
+\noindent
+The \acf{RMS} error of weight updates is given in Equation~\eqref{eq:heuristics:gd:adadelta_part_5} below.
 
@@
       \label{eq:heuristics:gd:adadelta_part_5}
-      \begin{split}
-            \Delta w_{t} = - \frac{\eta}{RMS[g]_{t}} g_{t}
-      \end{split}
-\end{equation}
-
-\noindent
-~\citeauthor{ref:zeiler:2012}~\cite{ref:zeiler:2012} noted that the units of the update step as presented in Equation~\ref{eq:heuristics:gd:adadelta_part_5} do not match.
-The weight update vector should have the same hypothetical units as the weight vector.
-To fix the aforemention problem, another exponentially decaying average is defined in terms of squared weight updates as is presented in Equation~\ref{eq:heuristics:gd:adadelta_part_6} below.
-
-\begin{equation}
-      \label{eq:heuristics:gd:adadelta_part_6}
-      \begin{split}
-            E[\Delta w^{2}]_{t} = \alpha E[\Delta w^{2}]_{t - 1} + (1 - \alpha)\Delta w_{t}^{2}
-      \end{split}
-\end{equation}
-
-\noindent
-The \acf{RMS} error of weight updates is given in Equation~\ref{eq:heuristics:gd:adadelta_part_7} below.
-
-\begin{equation}
-      \label{eq:heuristics:gd:adadelta_part_7}
       \begin{split}
@@
 $RMS[\Delta w]_{t}$ is approximated with the \acf{RMS} of weight updates until the previous timestep.
-The learning rate in Equation~\eqref{eq:heuristics:gd:adadelta_part_5} is then replaced.
-The weight update step for \acs{Adadelta} is then concluded in Equation~\eqref{eq:heuristics:gd:adadelta_part_8} below.
-
-\begin{equation}
-      \label{eq:heuristics:gd:adadelta_part_8}
-      \begin{split}
-            \Delta w_{t} = - \frac{RMS[\Delta w]_{t-1}}{RMS[g]_{t}} g_{t}
-      \end{split}
-\end{equation}
-
-\noindent
-The main advantage of \ac{Adadelta} is in removing the need for a learning rate.
+The learning rate in Equation~\eqref{eq:heuristics:gd:adadelta_part_3} is then replaced.
+The weight update step for \acs{Adadelta} is then concluded in Equation~\eqref{eq:heuristics:gd:adadelta_part_6} below.
+
+\begin{equation}
+      \label{eq:heuristics:gd:adadelta_part_6}
+      \begin{split}
+            w_{t+1} = w_{t} - \frac{RMS[\Delta w]_{t-1}}{RMS[g]_{t}} g_{t}
+      \end{split}
+\end{equation}
+
+\noindent
+The main advantage of \acs{Adadelta} is in removing the learning rate, which eliminates the need for hyper-parameter tuning of the learning rate.
 
@@
 \Acf{RMSProp}, presented by~\citeauthor{ref:hinton:2012}~\cite{ref:hinton:2012} is similar to \acs{Adadelta}  and was developed independently around the same time.
-\ac{RMSProp} is the same as the first weight update vector for \ac{Adadelta}, presented in~\eqref{eq:heuristics:gd:adadelta_part_4}.
+\acs{RMSProp} is the same as the first weight update vector for \acs{Adadelta}, presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_2}.
 A disadvantage of \acs{RMSProp} is that it still includes the learning rate term $\eta$ that needs to be tuned.
@@
 
-\Acf{Adam} is another variant of \ac{SGD} that includes adaptive learning rates and is presented by~\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014}.
-In addition to storing an exponentially decaying average of past squared gradients like \acs{Adadelta} and \acs{RMSProp}, \acs{Adam} also stores an exponentially decaying average of past gradients, similar to \ac{Momentum}~\cite{ref:ruder:2016}.~\citeauthor{ref:heusel:2017}~\cite{ref:heusel:2017} uses the analogy that, if \acs{Momentum} can be seen as a ball running down a slope, then \acs{Adam} behaves like a heavy ball with friction, which prefers flat minima in the error surface.
-The decaying averages for past gradients and past squared gradients is given in Equations~\ref{eq:heuristics:gd:adam_part_1} and~\ref{eq:heuristics:gd:adam_part_2} respectively.
+\Acf{Adam} is another variant of \acs{SGD} that includes adaptive learning rates and is presented by~\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014}.
+In addition to storing an exponentially decaying average of past squared gradients like \acs{Adadelta} and \acs{RMSProp}, \acs{Adam} also stores an exponentially decaying average of past gradients, similar to \acs{Momentum}~\cite{ref:ruder:2016}.~\citeauthor{ref:heusel:2017}~\cite{ref:heusel:2017} uses the analogy that, if \acs{Momentum} can be seen as a ball running down a slope, then \acs{Adam} behaves like a heavy ball with friction, which prefers flat minima in the error surface.
+The decaying averages for past gradients and past squared gradients is given in Equations~\eqref{eq:heuristics:gd:adam_part_1} and~\eqref{eq:heuristics:gd:adam_part_2} respectively.
 
@@
 \noindent
-In Equations~\ref{eq:heuristics:gd:adam_part_1} and~\ref{eq:heuristics:gd:adam_part_2} above, $\beta_{1}$ and $\beta_{2}$ are decay rates, similar to $\alpha$ for \ac{Momentum}.
+In Equations~\eqref{eq:heuristics:gd:adam_part_1} and~\eqref{eq:heuristics:gd:adam_part_2} above, $\beta_{1}$ and $\beta_{2}$ are decay rates, similar to $\alpha$ for \acs{Momentum}.
 \citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} suggest default values $B_{1}=0.9$, $B_{2}=0.999$ and $\epsilon = 1 \times 10^{-8}$.
@@
 These biases need to be corrected.
-The bias-corrected first and second moment estimates are presented in Equations~\ref{eq:heuristics:gd:adam_bc_first_moment} and~\ref{eq:heuristics:gd:adam_bc_second_moment} below.
+The bias-corrected first and second moment estimates are presented in Equations~\eqref{eq:heuristics:gd:adam_bc_first_moment} and~\eqref{eq:heuristics:gd:adam_bc_second_moment} below.
 
@@
 \noindent
-The \acs{Adam} update rule is then presented in Equation~\ref{eq:heuristics:gd:adam} below.
+The \acs{Adam} weight update rule is then presented in Equation~\eqref{eq:heuristics:gd:adam} below.
 
@@
 
-Gradient-based methods are sensitive to the type of problem that they it applied to, with hyper-parameter selection often dominating the research focus~\cite{ref:bengio:2000}\cite{ref:feurer:2019}.
-In the context of \acp{HH}, it is important to consider a diverse set of low-level heuristics to select from.
-Apart from gradient-based methods, alternative heuristics must thus be considered.~\cite{ref:blum:2003} mentions since the 1980's, a new kind of approximate algorithm has emerged which basically tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
-These methods referred to as metaheuristics.
-This section aims to introduce the reader to the concept of meta-heuristics.
-Specifically, this section focuses on population-based meta-heuristics.
-Three well known meta-heuristics are presented.
-Each of these have been shown to train \ac{FFNN}.
-These meta-heuristics include \ac{PSO}, \ac{DE} and \acp{GA}.~\cite{ref:carvalho:2006} compared various \ac{PSO} variants for training \acp{FFNN}.~\cite{ref:espinal:2011} compared \ac{DE} and \ac{PSO} when applied to \ac{FFNN} training and~\cite{ref:gupta:1999} compared \ac{BP} to a \ac{GA} for training \acp{FFNN}.
-
-A formal definition for meta-heuristics is required.
-The term \aclp{MH} was first introduced by~\citeauthor{ref:glover:1986}\cite{ref:glover:1986} in 1986.
-The world derives from the composition of two Greek words.
-Heuristic derives from the verb \textit{heuriskein} which means ``to find''.
-The suffix, \textit{meta} means ``beyond, in an upper level''.
-Before this term was widely adopted, \acp{MH} were often called \textit{modern heuristics}~\cite{ref:reeves:1993}.~\cite{ref:blum:2003} mentions that there is a debate as to what the formal defintion of \acp{MH} is and suggests the definition of \acp{MH} to be high level strategies for exploring search spaces by using different methods.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} provides characterists of meta-heuristics.
-These characterists are given as follows.
-
-\begin{itemize}
-      \item \ac{MH} are strategies to guide the search process.
-
-      \item The goal of \acp{MH} is to efficiently explore the search space in order to find (near) optimal solutions.
-
-      \item Techniques that constitute \ac{MH} algorithms range from simple local search to complex learning processes.
-
-      \item \ac{MH} algorithms are approximate and usually non-deterministic.
-
-      \item \acp{MH} may incorporate some mechanism to avoid getting trapped in local minima.
-
-      \item The basic concept of \acp{MH} permit an abstract level description.
-
-      \item \acp{MH} are not problem-specific.
-
-      \item \acp{MH} may make use of domain-specific knowledge  in the form of heuristics that are controlled by the upper level strategy.
-
-      \item Today's more advanced \acp{MH} use search experience (embodied in some form of memory) to guide the search/optimisation process.
-\end{itemize}
-
-\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} proposes the classification of heuristics as follows:
-
-\begin{itemize}
-      \item Nature inspired vs. non-nature inspired.
-      \item Population-based vs. single point search.
-      \item Dynamic vs. statis objective functions.
-      \item One vs. various neighbourhood structures.
-      \item Memory usage vs. memory-less methods.
-\end{itemize}
-
-The first of these \ac{MH} algorithms that are relevant to this dissertation include \ac{PSO}. The concept of \acp{PSO} is presented and discussed next.
+Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus~\cite{ref:bengio:2000, ref:feurer:2019}.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} mentions that since the 1980's, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
+These methods are referred to as \index{meta-heuristic}\textit{meta-heuristics}.
+
+This section aims to introduce the reader to the concept of \index{meta-heuristic}meta-heuristics, with focus on population-based meta-heuristics.
+Three well known \index{meta-heuristic}meta-heuristics, that have been shown to train \acs{FFNN}, are presented.
+These meta-heuristics include \acf{PSO}, \acf{DE} and \acfp{GA}.~\citeauthor{ref:carvalho:2006}~\cite{ref:carvalho:2006} compared various \acs{PSO} variants for training \acp{FFNN}.~\citeauthor{ref:espinal:2011}~\cite{ref:espinal:2011} compared \acs{DE} and \acs{PSO} when applied to \acs{FFNN} training and~\citeauthor{ref:gupta:1999}~\cite{ref:gupta:1999} compared \acs{BP} to a \acs{GA} for training \acp{FFNN}.
+
+The term \acf{MH} was first introduced by~\citeauthor{ref:glover:1986}~\cite{ref:glover:1986} in 1986 and is derived from the composition of two Greek words.
+\index{heuristic}Heuristic derives from the verb \textit{heuriskein} which means ``to find''.
+The prefix, \textit{meta}, means ``beyond, in an upper level''.
+\Acp{MH} were often called \textit{modern heuristics}~\cite{ref:reeves:1993}.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} mentions that there is a debate as to what the formal defintion of \acp{MH} is and suggests the definition of \acp{MH} to be ``high level strategies for exploring search spaces by using different methods''.
+
+The biggest difference between \index{meta-heuristic}meta-heuristics and gradient-bases heuristics is that
+\index{meta-heuristic}meta-heuristics make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search-space~\cite{ref:blum:2003}.
 
@@
 \Acp{PSO} were first presented  by~\citeauthor{ref:kennedy:1995}\cite{ref:kennedy:1995}.
-It was also Kennedy and Eberhart that first applied \acp{PSO} to train of \acp{FFNN}~\cite{ref:eberhart:1995}\cite{ref:kennedy:1997}.
-The application of \acp{PSO} in the context of training \ac{FFNN} have been widely studied~\cite{ref:rakitianskaia:2012}\cite{ref:vanwyk:2014} and it has been found to perform well.
-This section aims to provide the reader with the detail of \ac{PSO} implementation.
+Kennedy and Eberhart first applied \acp{PSO} to train of \acp{FFNN}~\cite{ref:eberhart:1995, ref:kennedy:1997}.
+The application of \acp{PSO} in the context of training \acs{FFNN} have been widely studied~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}.
+This section aims to provide the reader with the detail of \acs{PSO} implementation.
 
@@
 The changes in the particle position are then influenced by the experience or knowledge of the particle's neighbours.
-It can be said that the position of a particle is thus influenced by the positions of other particles in the swarm resulting in a symbiotic cooperative heuristic.
 The social behaviour of particles is modeled such that they stochastically return to previously successful regions in the search space.
 
-\citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that the swarm is usually arranged in a predefined structure, called a \textit{neighbourhood topology} that governs the communication between particles.
-Two different configurations of neighbourhood topologies exists.
-These are referred to as \textit{Local best (lbest)} \ac{PSO} and \textit{global best (gbest)} \ac{PSO}.
+\citeauthor{ref:vanwyk:2014}~\cite{ref:vanwyk:2014} mentions that the swarm is usually arranged in a predefined structure, called a \textit{neighbourhood topology} that governs the communication between particles.
+Two specific configurations of neighbourhood topologies that exists are referred to as \textit{local best (lbest)} \acs{PSO} and \textit{global best (gbest)} \acs{PSO}.
 There are two main differences between the two approaches in terms of their convergence characteristics~\cite{ref:eberhart:1996}.
@@
 \begin{itemize}
-      \item Due to the larger particle interconnectivity of \textit{gbest} \ac{PSO}, the heuristic converges faster than with \textit{lbest} \ac{PSO}.~\cite{ref:engelbrecht:2007} mentions that faster convergence comes at a cost of less diversity.
-      \item As a consequence of larger diversity, the \textit{lbest} \ac{PSO} is less susceptible to getting trapped in local minima.
-\end{itemize}
-
-\citeauthor{ref:shi:1998}\cite{ref:shi:1998} proposed a modification of the original \ac{PSO} as was presented by~\citeauthor{ref:kennedy:1995}.
-Their implementation focuses on the \textit{gbest} \ac{PSO} with \textit{inertia} weights.
-This dissertation focuses on their implementation of \textit{global best} \ac{PSO} and is discussed next.
-
-The particles in this configuration has a number of properties associated with them~\cite{ref:vanwyk:2014}. These include:
+      \item Due to the larger particle interconnectivity of \textit{gbest} \acs{PSO}, the heuristic converges faster than with \textit{lbest} \acs{PSO}.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that faster convergence comes at a cost of less diversity.
+
+      \item As a consequence of larger diversity, the \textit{lbest} \acs{PSO} is less susceptible to getting trapped in local minima.
+\end{itemize}
+
+\noindent
+\citeauthor{ref:shi:1998}~\cite{ref:shi:1998} proposed a modification of the original \acs{PSO} as was presented by~\citeauthor{ref:kennedy:1995}~\cite{ref:kennedy:1995}.
+Their implementation focuses on the \textit{gbest} \acs{PSO} with \textit{inertia} weights.
+This dissertation focuses on the \citeauthor{ref:shi:1998}~\cite{ref:shi:1998} implementation of \textit{global best} \acs{PSO}.
+The particles in this configuration has a number of properties associated with them~\cite{ref:vanwyk:2014}.
+These include:
 
@@
 Let the current position of particle $i$ at timestep $t$ be denoted by $x_{i}(t)$ and let $N$ be the search space dimensionality.
+
       \item \textbf{Velocity}: Represents a step size for the particle in the search space. The velocity vector of particle $i$ at timestep $t$ is denoted $v_{i}(t)$.
+
       \item \textbf{Solution Quality}: Refers to the evaluation of the particle's position with respect to the objective function.
 Let $f(x_{i}(t)$ denote the quality of the solution represented by the particle's position.
-      \item \textbf{Personal Best Position}: Refers to a cognitive memory construct where each particle keeps track of their personal best position found during optimisation thus far.
+
+      \item \textbf{Personal Best Position}: Refers to a cognitive memory construct, where each particle keeps track of their personal best position found during optimisation thus far.
 The personal best position is denoted $y_{i}(t)$.
-      \item \textbf{Global Best Position}: Refers to a social memory construct where the each particle has a reference to the best solution found in the particle's neighbourhood thus far.
-In the case of \text{gbest} \ac{PSO}, the global best position is the best position of the entire swarm.
+
+      \item \textbf{Global Best Position}: Refers to a social memory construct, where the each particle has a reference to the best solution found in the particle's neighbourhood thus far.
+In the case of \text{gbest} \acs{PSO}, the global best position is the best position of the entire swarm.
 The personal best position is denoted $\hat{y}_{i}(t)$.
@@
 
-During initialisation particles are randomly places within the search space by sampling from a uniform distribution such that $x_{i} \sim U(x_{min}, x_{max})$ and the velocity is set to vector of 0 such that $v_{i} = 0$.
+\noindent
+During initialisation, particles are randomly places within the search space by sampling from a uniform distribution such that $x_{i} \sim U(x_{min}, x_{max})$ and the velocity is set to 0.
 At timestep 0, the particle's initial position is set to be the particle's personal best solution such that $y_{i}(0) = x_{i}(0)$.
 The particle's update step is then broken into two parts.
-These include a velocity update step presented in Equation~\ref{eq:heuristics:pso:velocity} followed by a position update step as presented in Equation~\ref{eq:heuristics:pso:position} below.
+These include a velocity update step presented in Equation~\eqref{eq:heuristics:pso:velocity} followed by a position update step as presented in Equation~\eqref{eq:heuristics:pso:position} below.
 
@@
 
-In Equations~\ref{eq:heuristics:pso:velocity} and~\ref{eq:heuristics:pso:position}, $i$ refers to the $i$-th particle in the swarm, $j$ refers to the $j$-th dimension of vectors with dimensionality $N$ defined by the optimisation problem.
+\noindent
+In Equations~\eqref{eq:heuristics:pso:velocity} and~\eqref{eq:heuristics:pso:position} above, $i$ refers to the $i$-th particle in the swarm and $j$ refers to the $j$-th dimension of  the particle's position.
 A breakdown of the components introduced above is required.
@@
 \begin{itemize}
-      \item \textbf{Previous Velocity}: Denoted by the term $wv_{ij}(t)$.
-This term represents the particle's momentum and is used to formulate an update step for the particle in the search space.~\citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that it forces the particle to maintain a consistent direction, preventing drastic changes in terms of update steps.
+      \item \textbf{Previous Velocity}: Denoted by the term $v_{ij}(t)$.
+This term represents the particle's momentum and is used to formulate an update step for the particle in the search space.~\citeauthor{ref:vanwyk:2014}~\cite{ref:vanwyk:2014} mentions that it forces the particle to maintain a consistent direction, preventing drastic changes in terms of update steps.
 This term is then scaled by the \textit{inertia} weight control parameter, denoted $w$.
-Inertia weight was introduced by~\citeauthor{ref:shi:1998}\cite{ref:shi:1998} as a mechanism to control the exploration and exploitation abilities of the swarm.
-It was also introduced as a mechanism to eliminate velocity clamping (discussed later in the section).
-The introduction of inertia weight was successful in addressing the first objective, however did not quite provide a way to totally eliminate velocity clamping~\cite{ref:shi:2001}.
+Inertia weight was introduced by~\citeauthor{ref:shi:1998}~\cite{ref:shi:1998} as a mechanism to control the exploration and exploitation abilities of the swarm.
 
@@
 
-A concept known as \textit{velocity clamping} is mentioned above.~\citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that when \acp{PSO} where first developed, it was possible for particle velocities to become inappropriately large during optimisation leading to situations where particles fly out of the feasible search space.
+\noindent
+~\citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that when \acp{PSO} where first developed, it was possible for particle velocities to become inappropriately large during optimisation, leading to situations where particles fly out of the feasible search space.
 This is known as \textit{swarm explosion} and occurs when there are frequent changes in the global best position.
@@
 The idea behind velocity clamping is to restrict particle velocities to some $V_{max}$ threshold, in essence, modeling a form of terminal velocity.
-Velocity clamping is applied after the velocity update step and is given in Equation~\ref{eq:heuristics:pso:velocity_clamping} below.
+Velocity clamping is applied after the velocity update step and is given in Equation~\eqref{eq:heuristics:pso:velocity_clamping} below.
 
@@
 
+\noindent
 $V_{max}$ then becomes another hyper-parameter that must be defined a priori.
-Appropriate values $V_{max}$ may prevent swarm explosion, but also has an effect on the exploration and exploitation of the heuristic.
+Appropriate values for $V_{max}$ may prevent swarm explosion, but also has an effect on the exploration and exploitation of the heuristic.
 If $V_{max}$ is small, particle update steps are small, resulting in exploitation~\cite{ref:eberhart:1996}.
 If $V_{max}$ is big, it allows for larger update steps, promoting more exploration.
-A balance is needed between exploration and exploitation.
-Similar to other strategies, such as learning rate schedules for gradient-based heuristics, adaptive strategies such as those proposed in~\cite{ref:fan:2002} have been developed, but are beyond the scope of this dissertation.
-
-It should be noted that the choice of control parameter play a vital role on the behaviour and characteristics of the \acs{PSO}.
-Van den Berg and Engelbrecht~\cite{ref:vandenberg:2007}\cite{ref:vandenberg:2006} have done extensive work on the effects of different values for control parameters.
+
+It should be noted that the choice of control parameters play a vital role in the behaviour and characteristics of the \acs{PSO}.
+Van den Berg and Engelbrecht~\cite{ref:vandenberg:2007, ref:vandenberg:2006} have done extensive work on the effects of different values for control parameters.
 For the purposes of this dissertation, the $c_{1}$ and $c_{2}$ control parameter are set to $1.496180$ and the inertia weight $w$ is set to $0.0729844$ as these correspond to values used in~\cite{ref:eberhart:2000} and have been shown to be appropriate for a number of problems.
 
-An example of the pseudo code implementation of the \textit{gbest} \ac{PSO} is taken from~\cite{ref:engelbrecht:2007} and is given in Algorithm~\ref{algo:heuristics:pso:gbest} below.
+An example of the pseudo code implementation of the \textit{gbest} \acs{PSO} is taken from~\cite{ref:engelbrecht:2007} and is given in Algorithm~\ref{algo:heuristics:pso:gbest} below.
 
 \begin{algorithm}[H]
-      \caption{The pseudo code algorithm for the gbest \ac{PSO} heuristic.}
+      \caption{The pseudo code algorithm for the gbest \acs{PSO} heuristic.}
       \label{algo:heuristics:pso:gbest}
@@
 
-This section provided the reader with the implementation details of the \acs{PSO} heuristic.
-It was mentioned that \ac{PSO} have been used to train \acp{FFNN} on many occasions with successful outcomes.
-The following section presents the reader with the next population-based \ac{MH} that is considered.
-
 \subsection{Differential Evolution}
@@
 
-This section aims to introduce the reader to the next population-based \ac{MH} called \acl{DE}.
-Similar to \ac{PSO}, \Ac{DE} is a stochastic population-based search strategy developed by Storm and Price~\cite{ref:price:2006} in 1995.
-\Ac{DE} shares a lot of similarities with other evolutionary \ac{MH} paradigms such as \acp{PSO} and \acp{GA}.
-However, \ac{DE} differs significantly in the sense that it makes use of distance and direction information from the current population to guide the search process~\cite{ref:engelbrecht:2007}.
-Originally, \ac{DE} was focused on multi-dimensional real-values optimisation problems, but unlike gradient-based heuristics, it does not require any gradient information.
-This means that \ac{DE} does not require the underlying optimisation problem to be differentiable, meaning that it can be applied to problems that are discrete, noisy and dynamic~\cite{ref:rocca:2011}.
-
-Lots of research has been done on using \ac{DE} to train \acp{FFNN}.
+This section aims to introduce the reader to the next population-based \acs{MH} called \acl{DE}.
+Similar to \acs{PSO}, \Ac{DE} is a stochastic population-based search strategy developed by Storm and Price~\cite{ref:price:2006} in 1995.
+\Ac{DE} shares a lot of similarities with other evolutionary \acs{MH} paradigms such as \acp{PSO} and \acp{GA}.
+However, \acs{DE} differs significantly in the sense that it makes use of distance and direction information from the current population to guide the search process~\cite{ref:engelbrecht:2007}.
+Originally, \acs{DE} was focused on multi-dimensional real-values optimisation problems, but unlike gradient-based heuristics, it does not require any gradient information.
+This means that \acs{DE} does not require the underlying optimisation problem to be differentiable, meaning that it can be applied to problems that are discrete, noisy and dynamic~\cite{ref:rocca:2011}.
+
+Lots of research has been done on using \acs{DE} to train \acp{FFNN}.
 Some notable work include~\cite{ref:ilonen:2003}\cite{ref:slowik:2008}\cite{ref:mingguang:2009}.
-In these works, the authors often highlight the low computational complexity and simplicity of implementation for \ac{DE}.
+In these works, the authors often highlight the low computational complexity and simplicity of implementation for \acs{DE}.
 
@@
 For other \acp{EA} mutation step sizes are sampled from some probability distribution.
-\ac{DE} differs from these implementations in that
+\acs{DE} differs from these implementations in that
 
@@
 
-In \ac{DE} mutation step sizes are influenced by the differences in positions of different entities in the current population.
+In \acs{DE} mutation step sizes are influenced by the differences in positions of different entities in the current population.
 The positions of entities in the population provide valuable information about the fitness landscape.
 This is under the assumption that entities are initially uniformly placed in the search space.
-\ac{DE} aims to exploit this concept in order to find optimal solutions.
+\acs{DE} aims to exploit this concept in order to find optimal solutions.
 There are three main components to the \acs{DE} heuristic.
@@
 Importantly, all of these entities must be unique such that $i \neq i_{1} \neq i_{2} \neq i_{3}$ and $i_{2}, i_{3} \sim U(1, N_{s}$ where $N_{s}$ is the size of the swarm.
-      \item These individual entities are then used to calculate the trial vector by perturbing the target vector as presented in Equation~\ref{eq:heuristics:de:mutation} below.
+      \item These individual entities are then used to calculate the trial vector by perturbing the target vector as presented in Equation~\eqref{eq:heuristics:de:mutation} below.
 \end{itemize}
@@
 
-In Equation~\ref{eq:heuristics:de:mutation} $\beta \in (0, \infty)$ is the scale factor and controls the amplification of the differential variation~\cite{ref:engelbrecht:2007}.
+In Equation~\eqref{eq:heuristics:de:mutation} $\beta \in (0, \infty)$ is the scale factor and controls the amplification of the differential variation~\cite{ref:engelbrecht:2007}.
 Note that in the above steps, the selection strategy to select the target vector is not specified.
@@
 In the context of \acp{EA}, reproduction and recombination is done through the crossover operation.
-The same applies to \ac{DE}.
-The \ac{DE} crossover operator implements a discrete recombination of the trial vector, $u_{i}(t)$ (as was generated in Section~\ref{sec:heuristics:mh:de:mutation} above) and the parent vector $x_{i}(t)$ to produce new offspring $x'_{i}(t)$.
-The crossover operator is given in Equation~\ref{eq:heuristics:de:crossover} below.
+The same applies to \acs{DE}.
+The \acs{DE} crossover operator implements a discrete recombination of the trial vector, $u_{i}(t)$ (as was generated in Section~\ref{sec:heuristics:mh:de:mutation} above) and the parent vector $x_{i}(t)$ to produce new offspring $x'_{i}(t)$.
+The crossover operator is given in Equation~\eqref{eq:heuristics:de:crossover} below.
 
@@
 
-In Equation~\ref{eq:heuristics:de:crossover}, $x_{ij}(t)$ refers to the $j$-th element of the vector $x_{i}(t)$ and $\mathcal{J}$ refers to a set of crossover points or indices at which perturbation is done.
+In Equation~\eqref{eq:heuristics:de:crossover}, $x_{ij}(t)$ refers to the $j$-th element of the vector $x_{i}(t)$ and $\mathcal{J}$ refers to a set of crossover points or indices at which perturbation is done.
 Different techniques for determining the set, $\mathcal{J}$ has been proposed~\cite{ref:storn:1996}\cite{ref:storn:1997}.
@@
 \begin{algorithm}[H]
-      \caption{The pseudo code algorithm for the binomial crossover technique for \ac{DE}.}
+      \caption{The pseudo code algorithm for the binomial crossover technique for \acs{DE}.}
       \label{algo:heuristics:de:bin}
@@
 \begin{algorithm}[H]
-      \caption{The pseudo code algorithm for the exponential crossover technique for \ac{DE}.}
+      \caption{The pseudo code algorithm for the exponential crossover technique for \acs{DE}.}
       \label{algo:heuristics:de:exp}
@@
 Various selection operators have been suggested.
-With reference to the mutation operator, most \ac{DE} implementations make use of random selection or the best entity is used as the target vector $x_{i_{1}}(t)$.
+With reference to the mutation operator, most \acs{DE} implementations make use of random selection or the best entity is used as the target vector $x_{i_{1}}(t)$.
 To construct the population for the next generation, deterministic selection is used.
@@
 
-Algorithm~\ref{algo:heuristics:de:general_de} is taken from~\cite{ref:engelbrecht:2007} and presents the general \ac{DE} algorithm.
+Algorithm~\ref{algo:heuristics:de:general_de} is taken from~\cite{ref:engelbrecht:2007} and presents the general \acs{DE} algorithm.
 The population is initialised by randomly placing entities in the search space such that the positions of the entities are confined to some search boundary.
@@
 \begin{algorithm}[H]
-      \caption{The pseudo code for the general \ac{DE} heuristic.}
+      \caption{The pseudo code for the general \acs{DE} heuristic.}
       \label{algo:heuristics:de:general_de}
@@
 
-As with other heuristics, \ac{DE} also contains a set of control parameters. These include:
+As with other heuristics, \acs{DE} also contains a set of control parameters. These include:
 
@@
 
-Many variants of \ac{DE} have been created and researched~\cite{ref:mezura:2006}.
-A general notation for \ac{DE} heuristic variants have been developed by Storn et al.~\cite{ref:storn:1996}\cite{ref:storn:1997}.
-The notation follows the form \textit{DE/$x$/$y$/$z$} where $x$,$y$ and $z$ refer to the components that are used by the particular \ac{DE}.
+Many variants of \acs{DE} have been created and researched~\cite{ref:mezura:2006}.
+A general notation for \acs{DE} heuristic variants have been developed by Storn et al.~\cite{ref:storn:1996}\cite{ref:storn:1997}.
+The notation follows the form \textit{DE/$x$/$y$/$z$} where $x$,$y$ and $z$ refer to the components that are used by the particular \acs{DE}.
 A breakdown of this notation is provided as follows.
@@
 
-This section provided the reader with the details around the implementation of the \acs{DE} heuristic. The last population-based \ac{MH} is presented next.
+This section provided the reader with the details around the implementation of the \acs{DE} heuristic. The last population-based \acs{MH} is presented next.
 
@@
 
-\Ac{EC} refers to a collection of nature-inspired optimisation algorithms that lend their foundation to biological evolution.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that \ac{EC} refers to computer-based problem solving systems that use computational models of evolutionary processes such as natural selection, survival of the fittest and reproduction.
+\Ac{EC} refers to a collection of nature-inspired optimisation algorithms that lend their foundation to biological evolution.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that \acs{EC} refers to computer-based problem solving systems that use computational models of evolutionary processes such as natural selection, survival of the fittest and reproduction.
 It was Charles Darwin's theory of \textit{natural selection} that became the foundation of biological evolution~\cite{ref:darwin:1987}.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} summarises the Darwinian theory of evolution~\cite{ref:darwin:2012} as follows.
@@
 So far the reader has been introduced to two population-based \acp{MH}.
-These include \ac{PSO} and \ac{DE}.
-The \ac{DE} heuristic that was presented in Section~\ref{sec:heuristics:mh:de} is one type of \ac{EC} algorithm.
-This section introduces another population-based, nature-inspired optimisation \ac{EC} algorithm named \aclp{GA}.
+These include \acs{PSO} and \acs{DE}.
+The \acs{DE} heuristic that was presented in Section~\ref{sec:heuristics:mh:de} is one type of \acs{EC} algorithm.
+This section introduces another population-based, nature-inspired optimisation \acs{EC} algorithm named \aclp{GA}.
 The detail of the implementation of \acp{GA} is given in this section.
@@
 Primarily, \acp{GA} implement selection, modeling survival of the fittest and crossover, modeling reproduction.
-The remainder of this section follows the same approach as was done with \ac{DE} where the different operators are discussed.
-However, it is necessary to first provide the reader with the generic \ac{EC} algorithm.
-This algorithm is also referred to as the canonical \ac{GA} (CGA) and was proposed by Holland~\cite{ref:holland:1992}.
-The generic \ac{EC} algorithm is taken from~\cite{ref:engelbrecht:2007} and is is presented in Algorithm~\ref{algo:heuristics:ga:generic_ec} below.
+The remainder of this section follows the same approach as was done with \acs{DE} where the different operators are discussed.
+However, it is necessary to first provide the reader with the generic \acs{EC} algorithm.
+This algorithm is also referred to as the canonical \acs{GA} (CGA) and was proposed by Holland~\cite{ref:holland:1992}.
+The generic \acs{EC} algorithm is taken from~\cite{ref:engelbrecht:2007} and is is presented in Algorithm~\ref{algo:heuristics:ga:generic_ec} below.
 
 \begin{algorithm}[H]
-      \caption{The pseudo code for the generic \ac{EC} heuristic.}
+      \caption{The pseudo code for the generic \acs{EC} heuristic.}
       \label{algo:heuristics:ga:generic_ec}
@@
 
-Note that the initial implementations of \ac{EC} heuristics such as \acp{GA} did not contain a mutation operator as this was only introduced later.
+Note that the initial implementations of \acs{EC} heuristics such as \acp{GA} did not contain a mutation operator as this was only introduced later.
 The following sections provide the crossover, mutation and selection operators for \acp{GA}.
@@
 
-As with \ac{DE}, crossover operators model the reproduction of entities in the population.
+As with \acs{DE}, crossover operators model the reproduction of entities in the population.
 Broadly speaking, the crossover operators can be divided into three main categories~\cite{ref:engelbrecht:2007} and are based on arity of the operator i.e.
@@
 The more entities that survive to the next generation, the lower the diversity of the new population.
-It is later shown in~\ref{chap:bhh} that the proposed \ac{BHH} can incorporate a form of elitism in its credit assignment strategy.
+It is later shown in~\ref{chap:bhh} that the proposed \acs{BHH} can incorporate a form of elitism in its credit assignment strategy.
 \end{itemize}

### 2022-10-24 dissertation/chapters/05-probability.tex
🚧 (chapter 3): Just before DE

@@
 The Beta distribution is denoted as $Beta(\alpha, \beta)$.
-The \ac{PDF} of the Beta distribution is given below in Equation \ref{eq:probability:probability_distributions:beta:pdf}.
+The \ac{PDF} of the Beta distribution is given below in Equation~\eqref{eq:probability:probability_distributions:beta:pdf}.
 
@@
 
-where the normalising constant $B(\alpha, \beta)$ is defined below in Equation \ref{eq:probability:probability_distributions:beta:norm_const}.
+where the normalising constant $B(\alpha, \beta)$ is defined below in Equation~\eqref{eq:probability:probability_distributions:beta:norm_const}.
 
@@
 
-and $\Gamma$ is the Gamma function as defined below in Equation \ref{eq:probability:probability_distributions:beta:gamma_func}.
+and $\Gamma$ is the Gamma function as defined below in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func}.
 
@@
 
-it should be noted that the Gamma function can also be written as shown in Equation \ref{eq:probability:probability_distributions:beta:gamma_func_alt} below.
+it should be noted that the Gamma function can also be written as shown in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func_alt} below.
 
@@
 
-The expected value of $x$ is given below in Equation \ref{eq:probability:probability_distributions:beta:expected_value}.
+The expected value of $x$ is given below in Equation~\eqref{eq:probability:probability_distributions:beta:expected_value}.
 
@@
 
-Similarly, the expected value of the natural logarithm of $x$ can be calculated as shown below in Equation \ref{eq:probability:probability_distributions:beta:expected_value_ln}.
+Similarly, the expected value of the natural logarithm of $x$ can be calculated as shown below in Equation~\eqref{eq:probability:probability_distributions:beta:expected_value_ln}.
 
@@
 where $\psi$ is the logarithmic derivative of the Gamma function, called the \textit{Digamma} function.
-The Digamma function is given below in Equation \ref{eq:probability:probability_distributions:beta:digamma}.
+The Digamma function is given below in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}.
 
@@
 
-Finally, the mode of the distribution is given in Equation \ref{eq:probability:probability_distributions:beta:mode} below.
+Finally, the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:beta:mode} below.
 
@@
 It is later shown in Chapter \ref{chap:bhh} that this parameter plays a vital role in the optimisation process of the \ac{BHH}.
-The Dirichlet distribution of order $K \geq 2$ with parameters $\alpha$, denoted $Dir(\alpha)$, has a \ac{PDF} as given in Equation \ref{eq:probability:probability_distributions:dirichlet:pdf} below.
+The Dirichlet distribution of order $K \geq 2$ with parameters $\alpha$, denoted $Dir(\alpha)$, has a \ac{PDF} as given in Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} below.
 
@@
 
-where the normalising constant $B(\alpha)$ is defined in Equation \ref{eq:probability:probability_distributions:dirichlet:norm_cost}.
+where the normalising constant $B(\alpha)$ is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:norm_cost}.
 
@@
 
-and $\alpha_{0}$ is defined in Equation \ref{eq:probability:probability_distributions:dirichlet:alpha_0} below.
+and $\alpha_{0}$ is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:alpha_0} below.
 
@@
 
-The expected value of $x$ can be calculated as shown in Equation \ref{eq:probability:probability_distributions:dirichlet:expected_value} below.
+The expected value of $x$ can be calculated as shown in Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value} below.
 
@@
 
-Similarly, the expected value of the natural logarithm of $x_{k}$ can be calculated as defined in Equation \ref{eq:probability:probability_distributions:dirichlet:expected_value_ln} below.
+Similarly, the expected value of the natural logarithm of $x_{k}$ can be calculated as defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value_ln} below.
 
@@
 
-where $\psi$ is the Digamma function as defined in Equation \ref{eq:probability:probability_distributions:beta:digamma}.
-Finally, the mode of the distribution is given in Equation \ref{eq:probability:probability_distributions:dirichlet:mode} below.
+where $\psi$ is the Digamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}.
+Finally, the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:dirichlet:mode} below.
 
@@
 The outcome of such an experiment is a boolean value.
-The Bernoulli distribution has a \ac{PMF} as given below in Equation \ref{eq:probability:probability_distributions:bernoulli:pmf}.
+The Bernoulli distribution has a \ac{PMF} as given below in Equation~\eqref{eq:probability:probability_distributions:bernoulli:pmf}.
 
@@
 
-The above equation can also be expressed as show in Equation \ref{eq:probability:probability_distributions:bernoulli:alt} below.
+The above equation can also be expressed as show in Equation~\eqref{eq:probability:probability_distributions:bernoulli:alt} below.
 
@@
 
-The expected value of the distribution is thus given according to Equation \ref{eq:probability:probability_distributions:bernoulli:expected_value} below.
+The expected value of the distribution is thus given according to Equation~\eqref{eq:probability:probability_distributions:bernoulli:expected_value} below.
 
@@
 
-while the mode of the distribution is given in Equation \ref{eq:probability:probability_distributions:bernoulli:mode} below.
+while the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:bernoulli:mode} below.
 
@@
 When $N > 1$, the sequence of outcomes is referred to as a Bernoulli process.
-The \ac{PMF} of the Binomial distribution is given in Equation \ref{eq:probability:probability_distributions:binomial:pmf} below.
+The \ac{PMF} of the Binomial distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:pmf} below.
 
@@
 Similar to the Bernoulli distribution, the mean of the Binomial distribution is $N\theta$ given the \ac{CLT} as was shown in Figure \ref{fig:probability:probability_distributions:bernoulli:coin}.
-The expected value of the Binomial distribution is thus given in Equation \ref{eq:probability:probability_distributions:binomial:expected_value} below.
+The expected value of the Binomial distribution is thus given in Equation~\eqref{eq:probability:probability_distributions:binomial:expected_value} below.
 
@@
 
-The mode of the distribution is given in Equation \ref{eq:probability:probability_distributions:binomial:mode} below.
+The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:mode} below.
 
@@
 In probability theory, the Categorical distribution is often used to explain the outcome of a single experiment with more than two possible outcomes such as rolling a die~\cite{ref:wackerly:2014}.
-The \ac{PMF} of the Categorical distribution is given in Equation \ref{eq:probability:probability_distributions:categorical:pmf} below.
+The \ac{PMF} of the Categorical distribution is given in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf} below.
 
@@
 where $[x = k]$ is the Iversion Bracket~\cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
-From this, one can conclude that for a given class $k$, the categorical distribution simply yields $\theta_{k}$ as is shown in Equation \ref{eq:probability:probability_distributions:categorical:pmf_k} below.
+From this, one can conclude that for a given class $k$, the categorical distribution simply yields $\theta_{k}$ as is shown in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf_k} below.
 
@@
 Importantly, if the outcome of the random event is of category $k$, then $x_{k} = 1$ and $\forall_{j=1}^{K} x_{j} = 0, j \neq k$ so that the standard $K-1$ probability simplex $S$ still holds.
-The \ac{PMF} of the Categorical distribution can then be rewritten as follows in Equation \ref{eq:probability:probability_distributions:categorical:pmf_alt} below.
+The \ac{PMF} of the Categorical distribution can then be rewritten as follows in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf_alt} below.
 
@@
 Since there is no innate order to the underlying categories, the mean of the distribution does not yield any relevant information.
-The mode of the distribution is given in Equation \ref{eq:probability:probability_distributions:categorical:mode} below.
+The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:categorical:mode} below.
 
@@
 
-The support for the Multinomial is $\forall_{i=1}^{K} x_{k} \in \{1, \dots, N\}, \sum_{k=1}^{K}x_{k} = N$ and the \ac{PMF} for the Multinomial distribution is given below in Equation \ref{eq:probability:probability_distributions:multinomial:pmf}.
+The support for the Multinomial is $\forall_{i=1}^{K} x_{k} \in \{1, \dots, N\}, \sum_{k=1}^{K}x_{k} = N$ and the \ac{PMF} for the Multinomial distribution is given below in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf}.
 
@@
 The support is then given as $X \in \{0, 1\}^{N \times K}, \forall_{i=1}^{N}\sum_{k=1}^{K} x_{i,k} = 1$ so that the standard $K-1$ probability simplex $S$ still holds for each trial.
-The \ac{PMF} of the Multinomial distribution can then be rewritten as is presented in Equation \ref{eq:probability:probability_distributions:multinomial:pmf_alt}
+The \ac{PMF} of the Multinomial distribution can then be rewritten as is presented in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt}
 
@@
 
-The Bernoulli likelihood is then given in Equation \ref{eq:probability:conjugate_priors:binom_likelihood:likelihood} below.
+The Bernoulli likelihood is then given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:likelihood} below.
 
@@
 
-By Bayes Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation \ref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.
+By Bayes Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.
 
@@
 
-Since the denominator sums to $1$, one could get rid of the denominator and constants for the Bernoulli likelihood and the Beta prior, by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation \ref{eq:probability:conjugate_priors:binom_likelihood:posterior_propto} below.
+Since the denominator sums to $1$, one could get rid of the denominator and constants for the Bernoulli likelihood and the Beta prior, by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior_propto} below.
 
@@
 
-The likelihood of the Categorical and Multinomial distributions is then given in Equation \ref{eq:probability:conjugate_priors:mult_likelihood:likelihood} below.
+The likelihood of the Categorical and Multinomial distributions is then given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:likelihood} below.
 
@@
 
-By Bayes Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation \ref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.
+By Bayes Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.
 
@@
 
-Since the denominator sums to $1$, one could get rid of the denominator and constants for the Dirichlet prior,by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation \ref{eq:probability:conjugate_priors:mult_likelihood:posterior_propto} below.
+Since the denominator sums to $1$, one could get rid of the denominator and constants for the Dirichlet prior,by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior_propto} below.
 
@@
 Assume that the parameter $\theta$ has a continuous distribution with density $g(\theta)$ that has no unknown parameters.
-Considering the likelihood of the data and the prior on $\theta$, then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ is given in Equation \ref{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood} below.
+Considering the likelihood of the data and the prior on $\theta$, then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood} below.
 
@@
 
-The marginal density or mass function of $Y_{1}, Y_{2}, \dots, Y_{N}$ is given in Equation \ref{eq:probability:bayesian_statistic:bayesian_analysis:marginal_density} below.
+The marginal density or mass function of $Y_{1}, Y_{2}, \dots, Y_{N}$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:marginal_density} below.
 
@@
 
-Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$ according to Bayes' Theorem is given in Equation \ref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.
+Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$ according to Bayes' Theorem is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.
 

### 2022-10-24 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 (chapter 3): Just before DE

@@
 Section \ref{sec:bhh:selection_mechanism:random_events} presented the reader with the random events that are observed by the \ac{BHH} and Section \ref{sec:bhh:selection_mechanism:independence} provided an argument for independence between events.
-Chapter \ref{chap:probability} presented Bayes Theorem, but for convenience, it is given again in Equation \ref{eq:bhh:selection_mechanism:bayes_theorem} below.
+Chapter \ref{chap:probability} presented Bayes Theorem, but for convenience, it is given again in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} below.
 
@@
 
-As was indicated in Section \ref{sec:bhh:selection_mechanism:independence}, Equation \ref{eq:bhh:selection_mechanism:bayes_theorem} can be evaluated for proportionality since the \ac{BHH} is not concerned with actual accurate selection probabilities, but rather implements a Bayesian classifier.
-The resulting proportionality is expressed in Equation \ref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} below
+As was indicated in Section \ref{sec:bhh:selection_mechanism:independence}, Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} can be evaluated for proportionality since the \ac{BHH} is not concerned with actual accurate selection probabilities, but rather implements a Bayesian classifier.
+The resulting proportionality is expressed in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} below
 
@@
 
-Notice how the Equation \ref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} implements a Bayesian conditionally.
+Notice how the Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} implements a Bayesian conditionally.
 This conditionality can be extended to include multiple criteria.
@@
 
-The parameterised predictive model, as derived from Bayes theorem presented in Equation \ref{eq:bhh:selection_mechanism:bayes_theorem} is then given in Equation \ref{eq:bhh:selection_mechanism:predictive_model} below.
+The parameterised predictive model, as derived from Bayes theorem presented in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} is then given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model} below.
 
@@
 The calculation in the denominator can be intractable as has been previously indicated.
-However, in order to derive the posterior distribution as given in Equation \ref{eq:bhh:selection_mechanism:bayes_theorem}), one only has to evaluate to proportionality as is given in Equation \ref{eq:bhh:selection_mechanism:predictive_model_prop_to} below.
+However, in order to derive the posterior distribution as given in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem}), one only has to evaluate to proportionality as is given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} below.
 
@@
 
-The independence between events for the class label $H$ simply yields the \ac{PMF} of the Multinomial distribution as presented in Equation \ref{eq:bhh:selection_mechanism:naive_bayes:h_pmf} below.
+The independence between events for the class label $H$ simply yields the \ac{PMF} of the Multinomial distribution as presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf} below.
 
@@
 conditional to the occurrence of heuristic $k$ and model parameter $\phi$ as
-presented in Equation \ref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} below.
+presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} below.
 
@@
 label $H$ is denoted by the likelihood of $C$ conditional to the occurrence of
-heuristic $k$ and model parameter $\psi$ as given in Equation \ref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} below.
+heuristic $k$ and model parameter $\psi$ as given in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} below.
 
@@
 
-Where $N_{k}$ is the summary variable as described for Equation \ref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above.
+Where $N_{k}$ is the summary variable as described for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above.
 $N_{1,k}$ is a summary variable such that $N_{1,k} = \sum_{i=1}^{I}
@@
 
-Given the assumptions of the naïve Bayes classifier, one could supplement Equations \ref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}, \ref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} and \ref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above into the proportional evaluation of the predictive model as given in Equation \ref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
-This is presented in Equation \ref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} below.
+Given the assumptions of the naïve Bayes classifier, one could supplement Equations \ref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}, \ref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} and \ref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above into the proportional evaluation of the predictive model as given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
+This is presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} below.
 
@@
 
-Computationally the equation presented in Equation \ref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} will underflow if the resulting probabilities are very small.
+Computationally the equation presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} will underflow if the resulting probabilities are very small.
 
@@
 
-When evaluating for Equation \ref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf}, the numerical stability is shown to underflow if the resulting probabilities from its parts are very small.
+When evaluating for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf}, the numerical stability is shown to underflow if the resulting probabilities from its parts are very small.
 Multiplying multiple fractional parameters leads to an even smaller fractional number.
@@
 A solution to this problem is to apply the \textit{log-sum-exp trick}, parameterising distributions no longer using logits rather than probabilities.
-The transformation of Equation \ref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} using the log-sum-exp trick is given below in Equation \ref{eq:bhh:selection_mechanism:numerical_stability:log_sum_exp}.
+The transformation of Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} using the log-sum-exp trick is given below in Equation~\eqref{eq:bhh:selection_mechanism:numerical_stability:log_sum_exp}.
 
@@
 $\hat{\psi}_{k}$ are now presented. The log likelihood of $\hat{\theta}$, $\hat{\phi}$ and $\hat{\psi}$ as derived
-from the Equation \ref{eq:bhh:selection_mechanism:predictive_model_prop_to} is given in Equation \ref{eq:bhh:optimisation_step:mle:log_likelihood_all} below.
+from the Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} is given in Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} below.
 
@@
 
-Equation \ref{eq:bhh:optimisation_step:mle:log_likelihood_all} can be broken down into each of its factors.
-Consider the log likelihood of $\psi$  as denoted by Equation \ref{eq:bhh:optimisation_step:mle:log_likelihood_psi} below.
+Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} can be broken down into each of its factors.
+Consider the log likelihood of $\psi$  as denoted by Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_psi} below.
 
@@
 
-The MLE for $\hat{\psi_{k}} $ can be calculated by taking the derivative of Equation \ref{eq:bhh:optimisation_step:mle:log_likelihood_psi} with respect to $\psi_{k}$ and equating to zero as presented in Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_psi} as follows.
+The MLE for $\hat{\psi_{k}} $ can be calculated by taking the derivative of Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_psi} with respect to $\psi_{k}$ and equating to zero as presented in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_psi} as follows.
 
@@
 However, one has to compensate for the $K-1$ simplex $S$ by adding error factor $\epsilon$ to correct values for  $\theta$ where $\sum_{k}^{K} \theta_{k} \neq 1$.
-The new log likelihood function is then given in Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_1} below.
+The new log likelihood function is then given in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_1} below.
 
@@
 
-Solving first for $\epsilon$ yields Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_2} below.
+Solving first for $\epsilon$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_2} below.
 
@@
 
-Then solving for $\theta_{k}$ yields Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} as presented below.
+Then solving for $\theta_{k}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} as presented below.
 
@@
 
-Substituting back into the Equation yields Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_4} below.
+Substituting back into the Equation yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_4} below.
 
@@
 To compensate for the $K-1$ simplex $S$ an error factor $\lambda = (\lambda_{1}, \dots, \lambda_{J})$ is added.
-This follows in Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_1} as is presented below.
+This follows in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_1} as is presented below.
 
@@
 
-Solving first for $\lambda_{j}$ yields Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_2} as is given below.
+Solving first for $\lambda_{j}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_2} as is given below.
 
@@
 
-Then solving for $\phi_{j,k}$ yields Equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} below.
+Then solving for $\phi_{j,k}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} below.
 
@@
 
-The likelihood is presented in Equation \ref{eq:bhh:optimisation_step:map:bayesian_analysis_lamens} above.
+The likelihood is presented in Equation~\eqref{eq:bhh:optimisation_step:map:bayesian_analysis_lamens} above.
 The event $H$ is a multinomial distribution with parameter $\theta$.
 It is known that the conjugate prior to a multinomial distribution is a Dirichlet distribution (see Chapter \ref{chap:probability}.
-The \textit{prior} probability distribution for  $\theta_{k}$ is thus presented in Equation \ref{eq:bhh:optimisation_step:map:map_theta_prior} below.
+The \textit{prior} probability distribution for  $\theta_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_theta_prior} below.
 
@@
 Furthermore, the event $E$ is also a multinomial distribution with parameter $\phi$.
-The \textit{prior} probability distribution for $\phi_{j,k}$ is thus presented in Equation \ref{eq:bhh:optimisation_step:map:map_phi_prior} below.
+The \textit{prior} probability distribution for $\phi_{j,k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_phi_prior} below.
 
@@
 It is known that the conjugate prior to a binomial distribution is a Beta distribution (see Chapter \ref{chap:probability}).
-The prior probability distribution for $\psi_{k}$ is thus presented in Equation \ref{eq:bhh:optimisation_step:map:map_psi_prior} below.
+The prior probability distribution for $\psi_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.
 
@@
 
-Putting the likelihood and priors together yields the posterior distribution as given in Equation \ref{eq:bhh:optimisation_step:map:map_psi_prior} below.
+Putting the likelihood and priors together yields the posterior distribution as given in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.
 
@@
 
-From Equation \ref{eq:bhh:optimisation_step:map:posterior} above, it can be seen that the posterior distribution has the same form $\mathcal{A}(v)$ as the prior distribution.
+From Equation~\eqref{eq:bhh:optimisation_step:map:posterior} above, it can be seen that the posterior distribution has the same form $\mathcal{A}(v)$ as the prior distribution.
 The concentration update operations can then be given in equations \ref{eq:bhh:optimisation_step:map:alpha_update_operation}, \ref{eq:bhh:optimisation_step:map:beta_update_operation}, \ref{eq:bhh:optimisation_step:map:gamma1_update_operation} and \ref{eq:bhh:optimisation_step:map:gamma2_update_operation} below.

### 2022-10-25 dissertation/chapters/01-introduction.tex
✨ (Chapter 3): PSO review done

@@
 A step further in the concept of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem~\cite{ref:burke:2013}.
-These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic-space} to solve a specific problem.
+These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.
 One such form of \acs{HH} is a population-based approach that guides the search process by automatically selecting heuristics from a heuristic-pool to be applied to a collection of different candidate solutions in the solution-space.
@@
 One specific type of selection \acs{HH} is called a \index{multi-method populated-based meta-heuristic}\textit{multi-method population-based \index{meta-heuristic}meta-heuristic}~\cite{ref:vanderstockt:2018}.
-The term \index{multi-method}\textit{multi-method} refers to the incorporation of different low-level heuristics, with different search behaviours, into the heuristic-space.
+The term \index{multi-method}\textit{multi-method} refers to the incorporation of different low-level heuristics, with different search behaviours, into the heuristic space.
 The term \textit{population-based} refers to the utilisation of a population of entities that represent candidate solutions.
@@
 
-\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} mention that the focus of \acp{HH} is on automating the development of the \textit{learning mechanism} used to find the best heuristic to obtain an appropriate solution to an optimisation problem.~\citeauthor{ref:grobler:2012} explain that \acp{HH} employ a high-level heuristic that focuses on finding the best low-level heuristic in heuristic-space that could include \textit{single-method} and \textit{multi-method} optimisation algorithms (heuristics).
+\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} mention that the focus of \acp{HH} is on automating the development of the \textit{learning mechanism} used to find the best heuristic to obtain an appropriate solution to an optimisation problem.~\citeauthor{ref:grobler:2012} explain that \acp{HH} employ a high-level heuristic that focuses on finding the best low-level heuristic in heuristic space that could include \textit{single-method} and \textit{multi-method} optimisation algorithms (heuristics).
 \acp{HH} relieve the burden of having to select the best heuristic to use by trial and error.
@@
 
-      \item Conduct an empirical study and critically evaluate the performance of the developed \Acs{BHH} compared to individual heuristics in the heuristic-space as they are used to train \acp{FFNN} on a number of different problems.
+      \item Conduct an empirical study and critically evaluate the performance of the developed \Acs{BHH} compared to individual heuristics in the heuristic space as they are used to train \acp{FFNN} on a number of different problems.
 

### 2022-10-25 dissertation/chapters/02-artificial-neural-networks.tex
✨ (Chapter 3): PSO review done

@@
 
-Weight initialisation is the process by which candidate solutions (represented by the weights of the \acs{AN}) to the problem are ``placed'' in the search-space.
+Weight initialisation is the process by which candidate solutions (represented by the weights of the \acs{AN}) to the problem are ``placed'' in the search space.
 Weight initialisation influences the speed of convergence, the probability of convergence and the generalisation capabilities of \acp{ANN}~\cite{ref:fernandez:2001}.
@@
 The optimisation algorithm used to find the optimal weights is referred to as a \index{heuristic}\textit{heuristic}.
-\index{heuristic}Heuristics search for possible solutions in the solution-space and make use of information from the search-space to guide to process.
+\index{heuristic}Heuristics search for possible solutions in the solution-space and make use of information from the search space to guide to process.
 Heuristics are discussed in detail in Chapter~\ref{chap:heuristics}.

### 2022-10-25 dissertation/chapters/03-heuristics.tex
✨ (Chapter 3): PSO review done

@@
 The biggest difference between \index{meta-heuristic}meta-heuristics and gradient-bases heuristics is that
-\index{meta-heuristic}meta-heuristics make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search-space~\cite{ref:blum:2003}.
+\index{meta-heuristic}meta-heuristics make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space~\cite{ref:blum:2003}.
 
@@
 
-\Ac{PSO} is a stochastic population-based search algorithm based on the social behaviour of birds in a flock~\cite{ref:kennedy:1995}.
+\Acf{PSO} is a stochastic population-based search algorithm based on the social behaviour of birds in a flock~\cite{ref:kennedy:1995}.
 By definition, the \acs{PSO} heuristic is nature-inspired.
@@
 
-In general, this dissertation uses the term \textit{entity} for candidate solutions and a \textit{population} for a collection of entities.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that in \acp{PSO} individual candidate solutions are referred to as \textit{particles} and the population is referred to as a \textit{swarm}.
-These particles are ``flown'' through a hyperdimensional space.
+This dissertation uses the term \textit{entity} for candidate solutions and a \textit{population} for a collection of entities, in the general context of population-based \index{meta-heuristic}meta-heuristics.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that in \acp{PSO} individual candidate solutions are referred to as \textit{particles} and the population is referred to as a \textit{swarm}.
+These particles are ``flown'' through a hyperdimensional search space.
 Changes in particle position is due to social-psychological tendencies of individuals to emulate the success of other individuals.
@@
 Their implementation focuses on the \textit{gbest} \acs{PSO} with \textit{inertia} weights.
-This dissertation focuses on the \citeauthor{ref:shi:1998}~\cite{ref:shi:1998} implementation of \textit{global best} \acs{PSO}.
-The particles in this configuration has a number of properties associated with them~\cite{ref:vanwyk:2014}.
+This dissertation focuses on the \citeauthor{ref:shi:1998}~\cite{ref:shi:1998} implementation of \textit{global best} \acs{PSO} and particles in this specific implementation has a number of properties associated with them~\cite{ref:vanwyk:2014}.
 These include:
@@
       \item \textbf{Position}: Refers to the candidate solution that is represented by the particle and defines the particle position within the optimisation problem's hyper-dimensional solution space.
-Let the current position of particle $i$ at timestep $t$ be denoted by $x_{i}(t)$ and let $N$ be the search space dimensionality.
+Let the current position of particle $i$ at timestep $t$ be denoted by $x_{i}(t)$ and let $J$ be the search space dimensionality.
 
@@
       \item \textbf{Solution Quality}: Refers to the evaluation of the particle's position with respect to the objective function.
-Let $f(x_{i}(t)$ denote the quality of the solution represented by the particle's position.
+Let $f(x_{i}(t))$ denote the quality of the solution represented by the particle's position.
 
@@
 At timestep 0, the particle's initial position is set to be the particle's personal best solution such that $y_{i}(0) = x_{i}(0)$.
-The particle's update step is then broken into two parts.
-These include a velocity update step presented in Equation~\eqref{eq:heuristics:pso:velocity} followed by a position update step as presented in Equation~\eqref{eq:heuristics:pso:position} below.
+The particle's update step is then broken into two parts, including a velocity update step presented in Equation~\eqref{eq:heuristics:pso:velocity} followed by a position update step as presented in Equation~\eqref{eq:heuristics:pso:position} below.
 
@@
       \begin{split}
-            v_{ij}(t+1) = wv_{ij}(t) + c_{1}r_{1}(t)[y_{ij}(t) - x_{ij}(t)] + c_{2}r_{2}(t)[\hat{y}_{ij}(t) - x_{ij}(t)]
+            v_{ij}(t+1) = wv_{ij}(t) + c_{1}r_{1_{j}}(t)[y_{ij}(t) - x_{ij}(t)] + c_{2}r_{2_{j}}(t)[\hat{y}_{ij}(t) - x_{ij}(t)]
       \end{split}
@@
 
-      \item \textbf{Cognitive Component}: Denoted by the term $c_{1}r_{1}(t)[y_{ij} - x_{ij}(t)]$.
+      \item \textbf{Cognitive Component}: Denoted by the term $c_{1}r_{1_{j}}(t)[y_{ij} - x_{ij}(t)]$.
 This component represents the particle's personal  experience.
 It introduces an attractor to the particle's personal best position so far.
-The cognitive component is stochastically scaled with random numbers $r{1} \sim U(0,1)^N$ and the cognitive acceleration coefficient $c_{1}$ is used to control the influence of the cognitive attractor.
-
-      \item \textbf{Social Component}: Denoted by the term $c_{2}r_{2}(t)[\hat{y}_{ij} - x_{ij}(t)]$.
+The cognitive component is stochastically scaled with random numbers $r_{1} \sim U(0,1)^J$ and the cognitive acceleration coefficient $c_{1}$ is used to control the influence of the cognitive attractor.
+
+      \item \textbf{Social Component}: Denoted by the term $c_{2}r_{2+{j}}(t)[\hat{y}_{ij} - x_{ij}(t)]$.
 This component represents the particle's social  experience.
 It introduces an attractor to the swarm's best position so far.
-The social component is also stochastically scaled with random numbers $r{2} \sim U(0,1)^N$, while also introducing the social acceleration coefficient $c_{2}$ that is used to control the influence of the social attractor.
+The social component is also stochastically scaled with random numbers $r_{2} \sim U(0,1)^J$, while also introducing the social acceleration coefficient $c_{2}$ that is used to control the influence of the social attractor.
 \end{itemize}
@@
       \begin{algorithmic}
-            \State Create and initialise an $N_{x}$ dimensional swarm;
-            \While{stopping condition not met}
-            \For{each particle $i = 1, \dots, N_{s}$}
+            \State Create swarm of $N$ entities, each with $J$ dimensions;
+            \While{stopping condition are not met}
+            \For{each particle $i = 1, \dots, N$}
             \State // Set the personal best position;
@@
 
-            \For{each particle $i = 1, \dots, N_{s}$}
+            \For{each particle $i = 1, \dots, N$}
+            \For{each dimension $j = 1, \dots, J$}
             \State // Perform velocity update step;
-            \State $v_{ij} = wv_{ij} + c_{1}r_{1}[y_{ij} - x_{ij}] + c_{2}r_{2}[\hat{y}_{ij} - x_{ij}]$
+            \State $v_{ij} = wv_{ij} + c_{1}r_{1_{j}}[y_{ij} - x_{ij}] + c_{2}r_{2_{j}}[\hat{y}_{ij} - x_{ij}]$
             \State // Perform position update step;
             \State $x_{ij} = x_{ij} + v_{ij}$
+            \EndFor
             \EndFor

### 2022-10-25 dissertation/chapters/04-hyper-heuristics.tex
✨ (Chapter 3): PSO review done

@@
 
-Importantly, \ac{HH} are concerned with finding the best heuristic in heuristic-space, while the underlying low-level heuristics find solutions in the feasible search space.
+Importantly, \ac{HH} are concerned with finding the best heuristic in heuristic space, while the underlying low-level heuristics find solutions in the feasible search space.
 This level of abstraction is illustrated in Figure \ref{fig:heuristics:hh:hh_algorithm} below.

### 2022-10-25 dissertation/chapters/06-bayesian-hyper-heuristic.tex
✨ (Chapter 3): PSO review done

@@
       \item \textbf{Online Learning:} Refers to the source of the feedback used during training.
-The \ac{BHH} optimises, at a higher level, the selection and application of the \index{heuristic-space}\textit{heuristic-space} while low-level heuristics optimise entities' solution to the underlying model, in this case a \ac{FFNN}.
+The \ac{BHH} optimises, at a higher level, the selection and application of the \index{heuristic space}\textit{heuristic space} while low-level heuristics optimise entities' solution to the underlying model, in this case a \ac{FFNN}.
 This happens during training time, yielding the classification of utilising \textit{online} learning.

### 2022-10-25 dissertation/chapters/08-results.tex
🚧 WIP - Save point (compiles)
✨ (Chapter 3): PSO review done

@@
 To some extent this does make sense, since the proxied update step operations for these heuristics do not map as well between meta-heuristics as they do with gradient-based heuristics and thus an update step that occurs when switching from a \acs{PSO} to a \acs{GA} for example might maintain a state of momentum in a certain direction and then as a result of cross-over end up in a totally opposite direction, resulting in the entity vastly overshooting any optima.
-Van Wyk \cite{ref:vanwyk:2014} did a detailed analysis of overfitting that occurs when training \acp{FFNN} using \acp{PSO}.
+Van Wyk~\cite{ref:vanwyk:2014} did a detailed analysis of overfitting that occurs when training \acp{FFNN} using \acp{PSO}.
 Although the same velocity clamping techniques were used as suggested in Van Wyk's work, they are not guaranteed to avoid overfitting.
@@
 If a large dataset is presented, that means that the majority of training takes place in a small number of epochs.
-This leaves a very small window for the \Ac{BHH} to actually learn relevant and useful information from the \index{heuristic}heuristic-space.
+This leaves a very small window for the \Ac{BHH} to actually learn relevant and useful information from the \index{heuristic}heuristic space.
 
@@
 
-	\item Section \ref{sec:results:population} presented an empirical test to evaluate the effect of population size on the \Ac{BHH}. It was found that population size is shown to be problem-dependent.
+      \item Section \ref{sec:results:population} presented an empirical test to evaluate the effect of population size on the \Ac{BHH}.
+It was found that population size is shown to be problem-dependent.
 

### 2022-10-27 dissertation/chapters/03-heuristics.tex
✨ (chapter3): Review Done

@@
 Many different techniques have been used to train \acp{FFNN}~\cite{ref:kingma:2014}.
-Finding the best technique to use to train an \acs{FFNN} has been shown to be problem dependent in many cases~\cite{ref:kheiri:2017}.
+Finding the best technique to use to train a \acs{FFNN} has been shown to be problem dependent in many cases~\cite{ref:kheiri:2017}.
 Every technique has its characteristics, constraints, advantages and disadvantages.
@@
 
-Chapter~\ref{chap:anns} briefly introduced the reader to the concept of \index{heuristic}\index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
+Chapter~\ref{chap:anns} briefly introduced the reader to the concept of \index{heuristic}\index{heuristic}heuristics and \acfp{MH}s.
 This chapter presents more detailed background information on various different \index{heuristic}heuristics that have been used to train \acp{FFNN}.
-Broadly speaking, this chapter focuses on two different groups of \index{heuristic}heuristics, including classical gradient-based approaches and population-based \index{meta-heuristic}meta-heuristics.
+Broadly speaking, this chapter focuses on two different groups of \index{heuristic}heuristics, including classical gradient-based approaches and population-based \acp{MH}.
 Each technique is presented and discussed in detail.
@@
 
-      \item \textbf{Section~\ref{sec:heuristics:mh}} presents the reader with three different population-baed \index{meta-heuristic}meta-heuristics, including \acf{PSO}, \acf{DE} and \acfp{GA}.
+      \item \textbf{Section~\ref{sec:heuristics:mh}} presents the reader with three different population-baed \acp{MH}, including \acf{PSO}, \acf{DE} and \acfp{GA}.
 
@@
 It can thus be said that gradient-based \index{heuristic}heuristics make use of information directly from the \textit{search space}.
-On the contrary, \index{heuristic}heuristics such as \index{meta-heuristic}meta-heuristics make use of meta-information obtained as a result of evaluating the \acs{FFNN}~\cite{ref:blum:2003}.
-The meta-information that \index{meta-heuristic}meta-heuristics make use of could include ranked-performance of a population of candidate solutions, referred to as \textit{entities}.
+On the contrary, \index{heuristic}heuristics such as \acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN}~\cite{ref:blum:2003}.
+The meta-information that \acp{MH} make use of could include ranked-performance of a population of candidate solutions, referred to as \textit{entities}.
 \index{meta-heuristic}Meta-heuristics are useful when there is imperfect information about the search space~\cite{ref:bianchi:2009}, and are generally less problem-specific than other classes of \index{heuristic}heuristics~\cite{ref:blum:2003}.
-This disseration takes a particular interest in gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
+This disseration takes a particular interest in gradient-based \index{heuristic}heuristics and \acp{MH}.
 Each of these are presented in detail in the following sections.
@@
 \cite{ref:engelbrecht:2007}, they are certainly the most widely used.
-Gradient-based heuristics have become increasingly popular partly due to their simplicity and low computational overhead compared to other \index{heuristic}heuristics such as \index{meta-heuristic}meta-heuristics and other second-order derivative methods such as Newtons' method.
-There are many variants of gradient-based \index{heuristic}heuristics, however, they all fundamentally apply the same generic \acs{GD} framework called \acf{BP}.
+Gradient-based heuristics have become increasingly popular partly due to their simplicity and low computational overhead compared to other \index{heuristic}heuristics such as \acp{MH} and other second-order derivative methods such as Newtons' method.
+There are many variants of gradient-based \index{heuristic}heuristics, however, they all fundamentally apply the same generic \acf{GD} framework called \acf{BP}.
 
@@
 \noindent
-In Equation~\eqref{eq:heuristics:gd:update_step_part_2} above, $\eta$ is the learning rate and $\frac{\partial \epsilon}{\partial w_{i}}$ is the \textit{gradient} of the error, as a result of a loss function, relative to the weight at index $i$.
-The learning rate is an important hyper-parameter in gradient-based \index{heuristic}heuristics as it controls the step-size that is taken in the direction of the negative gradient at each timestep.
+In Equation~\eqref{eq:heuristics:gd:update_step_part_2} above, $\eta$ is the learning rate and $\frac{\partial \epsilon}{\partial w_{i}}$ is the \textit{gradient} of the error, as a result of a loss function $\mathcal{E}$, relative to the weight at index $i$.
+The learning rate controls the step-size that is taken in the direction of the negative gradient at each timestep.
 Assuming the use of \acs{SSE} as the loss function, the partial derivative of $\epsilon$, relative to the weight $w$, at index $i$, is given by Equation~\eqref{eq:heuristics:gd:update_step_part_3} below.
@@
 \noindent
+A more detailed breakdown of the steps for \acs{BP}, as presented by ~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007}, is given in Appendix~\ref{app:backpropagation}.
+
 A simplified notation is proposed from which the gradient-based heuristics can be compared.
@@
       \centering
-      \includegraphics[width=0.9\textwidth]{images/sgd.png}
+      \includegraphics[width=0.9\textwidth]{images/sgd.pdf}
       \caption{An illustration of \acf{SGD} fluctuations during training as taken from~\cite{ref:sgd:2006}.}
@@
 \begin{itemize}
-      \item The appropriate value to use for the learning rate $\eta$ is difficult to determine and is often problem-specific.
+      \item The appropriate value to use for the learning rate $\eta$, is difficult to determine and is often problem-specific.
 A learning rate that is too small causes premature exploitation, leading to slow and bad convergence.
@@
 
-      \item Learning rate schedules~\cite{ref:robbins:1951} can be introduced to dynamically change the learning rate throughout the training process, however, these schedules and their parameters have to be defined a priori and are thus problem specific~\cite{ref:darken:1992}.
+      \item Learning rate schedules~\cite{ref:robbins:1951} can be introduced to dynamically change the learning rate throughout the training process, however, these schedules and their parameters have to be defined a priori and are often problem specific~\cite{ref:darken:1992}.
 
@@
 The aforementioned bias is especially prominent during the initial timesteps and/or when the decay rates $\beta_{1}$ and $\beta_{2}$ are small ($\beta_{1}$ and $\beta_{2}$ are close to 1).
-These biases need to be corrected.
 The bias-corrected first and second moment estimates are presented in Equations~\eqref{eq:heuristics:gd:adam_bc_first_moment} and~\eqref{eq:heuristics:gd:adam_bc_second_moment} below.
@@
 \noindent
-This section provided the reader with a collection of gradient-based \index{heuristic}heuristics. The next section presents the reader with \index{meta-heuristic}meta-heuristics.
-
-\section{Meta-Heuristics}
-\label{sec:heuristics:mh}
+This section provided the reader with a collection of gradient-based \index{heuristic}heuristics. The next section presents the reader with \acp{MH}.
+
+\section{Meta-Heuristics}\label{sec:heuristics:mh}
 
@@
 
-This section aims to introduce the reader to the concept of \index{meta-heuristic}meta-heuristics, with focus on population-based meta-heuristics.
-Three well known \index{meta-heuristic}meta-heuristics, that have been shown to train \acs{FFNN}, are presented.
+This section aims to introduce the reader to the concept of \acp{MH}, with focus on population-based meta-heuristics.
+Three well known \acp{MH}, that have been shown to train \acs{FFNN}, are presented.
 These meta-heuristics include \acf{PSO}, \acf{DE} and \acfp{GA}.~\citeauthor{ref:carvalho:2006}~\cite{ref:carvalho:2006} compared various \acs{PSO} variants for training \acp{FFNN}.~\citeauthor{ref:espinal:2011}~\cite{ref:espinal:2011} compared \acs{DE} and \acs{PSO} when applied to \acs{FFNN} training and~\citeauthor{ref:gupta:1999}~\cite{ref:gupta:1999} compared \acs{BP} to a \acs{GA} for training \acp{FFNN}.
@@
 
-The biggest difference between \index{meta-heuristic}meta-heuristics and gradient-bases heuristics is that
-\index{meta-heuristic}meta-heuristics make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space~\cite{ref:blum:2003}.
-
-\subsection{Particle Swarm Optimisation}
-\label{sec:heuristics:mh:pso}
+The biggest difference between \acp{MH} and gradient-bases heuristics is that
+\acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space~\cite{ref:blum:2003}.
+
+\subsection{Particle Swarm Optimisation}\label{sec:heuristics:mh:pso}
 
@@
 The application of \acp{PSO} in the context of training \acs{FFNN} have been widely studied~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}.
-This section aims to provide the reader with the detail of \acs{PSO} implementation.
-
-This dissertation uses the term \textit{entity} for candidate solutions and a \textit{population} for a collection of entities, in the general context of population-based \index{meta-heuristic}meta-heuristics.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that in \acp{PSO} individual candidate solutions are referred to as \textit{particles} and the population is referred to as a \textit{swarm}.
+This section aims to provide the reader with the details of \acs{PSO} implementation.
+
+This dissertation uses the term \textit{entity} for candidate solutions and a \textit{population} for a collection of entities, in the general context of population-based \acp{MH}.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that in \acp{PSO} individual candidate solutions are referred to as \textit{particles} and the population is referred to as a \textit{swarm}.
 These particles are ``flown'' through a hyperdimensional search space.
@@
 
-      \item \textbf{Global Best Position}: Refers to a social memory construct, where the each particle has a reference to the best solution found in the particle's neighbourhood thus far.
+      \item \textbf{Global Best Position}: Refers to a social memory construct, where each particle has a reference to the best solution found in the particle's neighbourhood thus far.
 In the case of \text{gbest} \acs{PSO}, the global best position is the best position of the entire swarm.
@@
 \noindent
-During initialisation, particles are randomly places within the search space by sampling from a uniform distribution such that $x_{i} \sim U(x_{min}, x_{max})$ and the velocity is set to 0.
+During initialisation, particles are randomly placed within the search space by sampling from a uniform distribution such that $x_{i} \sim U(x_{min}, x_{max})$ and the velocity is set to 0.
 At timestep 0, the particle's initial position is set to be the particle's personal best solution such that $y_{i}(0) = x_{i}(0)$.
@@
 In Equations~\eqref{eq:heuristics:pso:velocity} and~\eqref{eq:heuristics:pso:position} above, $i$ refers to the $i$-th particle in the swarm and $j$ refers to the $j$-th dimension of  the particle's position.
-A breakdown of the components introduced above is required.
 The velocity update step consists of:
@@
 
-      \item \textbf{Social Component}: Denoted by the term $c_{2}r_{2+{j}}(t)[\hat{y}_{ij} - x_{ij}(t)]$.
+      \item \textbf{Social Component}: Denoted by the term $c_{2}r_{2_{j}}(t)[\hat{y}_{ij} - x_{ij}(t)]$.
 This component represents the particle's social  experience.
@@
 In order to address this issues, the concept of \textit{velocity clamping} was introduced~\cite{ref:eberhart:1996}.
-The idea behind velocity clamping is to restrict particle velocities to some $V_{max}$ threshold, in essence, modeling a form of terminal velocity.
+The idea behind velocity clamping is to restrict particle velocities to some $V_{max}$ threshold, modeling a form of terminal velocity.
 Velocity clamping is applied after the velocity update step and is given in Equation~\eqref{eq:heuristics:pso:velocity_clamping} below.
@@
             \begin{cases}
-                  v'_{ij}(t+1) & \text{if } |v'_{ij}(t+1)| < V_{max,j}   \\
+                  v'_{ij}(t+1) & \text{if } -V_{max,j} < v'_{ij}(t+1) < V_{max,j} \\
                   -V_{maxj}    & \text{if } v'_{ij}(t+1) \leq -V_{max,j}          \\
@@
 \noindent
-$V_{max}$ then becomes another hyper-parameter that must be defined a priori.
+$V_{max}$ is another hyper-parameter that must be defined a priori.
 Appropriate values for $V_{max}$ may prevent swarm explosion, but also has an effect on the exploration and exploitation of the heuristic.
@@
 
-\subsection{Differential Evolution}
-\label{sec:heuristics:mh:de}
-
-This section aims to introduce the reader to the next population-based \acs{MH} called \acl{DE}.
-Similar to \acs{PSO}, \Ac{DE} is a stochastic population-based search strategy developed by Storm and Price~\cite{ref:price:2006} in 1995.
+\subsection{Differential Evolution}\label{sec:heuristics:mh:de}
+
+This section aims to introduce the reader to the next population-based \acs{MH} called \acf{DE}.
+Similar to \acs{PSO}, \acs{DE} is a stochastic population-based search strategy developed by Storm and Price~\cite{ref:price:2006} in 1995.
 \Ac{DE} shares a lot of similarities with other evolutionary \acs{MH} paradigms such as \acp{PSO} and \acp{GA}.
-However, \acs{DE} differs significantly in the sense that it makes use of distance and direction information from the current population to guide the search process~\cite{ref:engelbrecht:2007}.
-Originally, \acs{DE} was focused on multi-dimensional real-values optimisation problems, but unlike gradient-based heuristics, it does not require any gradient information.
-This means that \acs{DE} does not require the underlying optimisation problem to be differentiable, meaning that it can be applied to problems that are discrete, noisy and dynamic~\cite{ref:rocca:2011}.
+However, \acs{DE} differs significantly in how distance and direction information from the current population is used to guide the search process~\cite{ref:engelbrecht:2007}.
+Originally, \acs{DE} was focused on multi-dimensional real-valued optimisation problems, but unlike gradient-based heuristics, it does not require any gradient information.
+\acs{DE} does not require the underlying optimisation problem to be differentiable and can thus be applied to problems that are discrete, noisy and dynamic~\cite{ref:rocca:2011}.
 
 Lots of research has been done on using \acs{DE} to train \acp{FFNN}.
-Some notable work include~\cite{ref:ilonen:2003}\cite{ref:slowik:2008}\cite{ref:mingguang:2009}.
+Some notable work include~\cite{ref:ilonen:2003, ref:slowik:2008, ref:mingguang:2009}.
 In these works, the authors often highlight the low computational complexity and simplicity of implementation for \acs{DE}.
 
-Similar to other \acp{EA}, variation from one generation to the next is achieved through the application of crossover and mutation operators.
-Engelbrecht~\cite{ref:engelbrecht:2007} mentions that for other \acp{EA} if both these operators are used, crossover is applied first after which the generated offspring is mutated.
-For other \acp{EA} mutation step sizes are sampled from some probability distribution.
-\acs{DE} differs from these implementations in that
-
-\begin{itemize}
-      \item mutation is applied first to generate a \textit{trial vector}, which is then used within the crossover operator to produce one offspring and
-      \item mutation step sizes are not sampled from prior known probability distributions.
-\end{itemize}
-
-In \acs{DE} mutation step sizes are influenced by the differences in positions of different entities in the current population.
-The positions of entities in the population provide valuable information about the fitness landscape.
-This is under the assumption that entities are initially uniformly placed in the search space.
-\acs{DE} aims to exploit this concept in order to find optimal solutions.
+Similar to other \acp{EA}, variation from one generation to the next is achieved through the application of \index{crossover}crossover and \index{mutation}mutation operators.
+Engelbrecht~\cite{ref:engelbrecht:2007} mentions that for other \acp{EA}, if both \index{crossover}crossover and \index{mutation}mutation operators are used, \index{crossover}crossover is applied first, after which the generated offspring is mutated.
+Furthermore, other \acp{EA} sample \index{mutation}mutation step sizes from some probability distribution.
+\acs{DE} differs from the aforementioned \acp{EA} in two ways.
+Firstly, \index{mutation}mutation is applied first to generate a \textit{trial vector}, which is then used within the \index{crossover}crossover operator to produce one offspring.
+Secondly, \index{mutation}mutation step sizes are not sampled from prior known probability distributions.
+
+In \acs{DE}, \index{mutation}mutation step sizes are influenced by the differences in positions of different entities in the current population.
+The positions of entities in the population provide valuable information about the fitness landscape, a concept \acs{DE} aims to exploit in order to find optimal solutions.
 There are three main components to the \acs{DE} heuristic.
-These include mutation, crossover and selection operators~\cite{ref:price:2006}.
-Each of these are presented briefly next.
-
-\subsubsection{Mutation}
-\label{sec:heuristics:mh:de:mutation}
-
-The purpose of the mutation operator is to produce a trial vector for each entity in the current population by mutating a target vector with a weighted differential~\cite{ref:engelbrecht:2007}.
-This trial vector is used in the crossover operator (discussed next) to produce offspring.
-The mutation process then follows as such.
+These include \index{mutation}mutation, \index{crossover}crossover and selection operators~\cite{ref:price:2006}.
+Each of these are presented in detail in the following sections.
+
+\subsubsection{Mutation}\label{sec:heuristics:mh:de:mutation}
+
+The purpose of the \index{mutation}mutation operator is to produce a trial vector for each entity in the current population by mutating a \textit{target} vector with a \textit{weighted differential}~\cite{ref:engelbrecht:2007}.
+The trial vector is used in the \index{crossover}crossover operator to produce offspring.
+The \index{mutation}mutation process then follows as such.
 For each each parent $x_{i}(t)$ generate a trial vector $u_{i}(t)$ as follows.
@@
 \begin{itemize}
-      \item Select a target vector, $x_{i_{1}}(t)$ from the population the is not the same as the parent i.e. $i \neq i_{1}$.
-      \item This is followed by randomly selecting two other individuals $x_{i_{2}}(t)$ and $x_{i_{3}}(t)$.
-Importantly, all of these entities must be unique such that $i \neq i_{1} \neq i_{2} \neq i_{3}$ and $i_{2}, i_{3} \sim U(1, N_{s}$ where $N_{s}$ is the size of the swarm.
-      \item These individual entities are then used to calculate the trial vector by perturbing the target vector as presented in Equation~\eqref{eq:heuristics:de:mutation} below.
+      \item Select a target vector, $x_{i_{1}}(t)$ from the population that is not the same as the parent i.e.
+$i \neq i_{1}$.
+Various different selection strategies can be used to select the target vector.
+
+      \item Randomly select two other individuals $x_{i_{2}}(t)$ and $x_{i_{3}}(t)$.
+Importantly, all of these entities must be unique such that $i \neq i_{1} \neq i_{2} \neq i_{3}$ and $i_{2}, i_{3} \sim U(1, N)$ where $N$ is the size of the swarm/population.
+
+      \item Selected individual entities are then used to calculate the trial vector by perturbing the target vector as presented in Equation~\eqref{eq:heuristics:de:mutation} below.
 \end{itemize}
@@
 
+\noindent
 In Equation~\eqref{eq:heuristics:de:mutation} $\beta \in (0, \infty)$ is the scale factor and controls the amplification of the differential variation~\cite{ref:engelbrecht:2007}.
-Note that in the above steps, the selection strategy to select the target vector is not specified.
-Selection is discussed in Section~\ref{sec:heuristics:mh:de:selection} below.
-
-\subsubsection{Crossover}
-\label{sec:heuristics:mh:de:crossover}
-
-In the context of \acp{EA}, reproduction and recombination is done through the crossover operation.
+
+\subsubsection{Crossover}\label{sec:heuristics:mh:de:crossover}
+
+In the context of \acp{EA}, reproduction and recombination is done through the \index{crossover}crossover operation.
 The same applies to \acs{DE}.
-The \acs{DE} crossover operator implements a discrete recombination of the trial vector, $u_{i}(t)$ (as was generated in Section~\ref{sec:heuristics:mh:de:mutation} above) and the parent vector $x_{i}(t)$ to produce new offspring $x'_{i}(t)$.
-The crossover operator is given in Equation~\eqref{eq:heuristics:de:crossover} below.
+The \acs{DE} \index{crossover}crossover operator implements a discrete recombination of the trial vector, $u_{i}(t)$, as was generated in Equation~\eqref{eq:heuristics:de:mutation} above, and the parent vector $x_{i}(t)$ to produce new offspring $x'_{i}(t)$.
+The \index{crossover}crossover operator is given in Equation~\eqref{eq:heuristics:de:crossover} below.
 
@@
 
-In Equation~\eqref{eq:heuristics:de:crossover}, $x_{ij}(t)$ refers to the $j$-th element of the vector $x_{i}(t)$ and $\mathcal{J}$ refers to a set of crossover points or indices at which perturbation is done.
-Different techniques for determining the set, $\mathcal{J}$ has been proposed~\cite{ref:storn:1996}\cite{ref:storn:1997}.
+\noindent
+In Equation~\eqref{eq:heuristics:de:crossover}, $x_{ij}(t)$ refers to the $j$-th element of the vector $x_{i}(t)$ and $\mathcal{J}$ refers to a set of \index{crossover}crossover points or indices at which perturbation is done.
+Different techniques for determining the set $\mathcal{J}$, has been proposed~\cite{ref:storn:1996, ref:storn:1997}.
 These include:
@@
 \begin{itemize}
-      \item \textbf{Binomial crossover}: A crossover mask is generated by randomly selecting indices from the set of possible crossover points $\{1,2,\dots,N_{x}$ where $N_{x}$ is the problem dimension.
-This techique is presented in Algorithm~\ref{algo:heuristics:de:bin} below.
-In Algorithm~\ref{algo:heuristics:de:bin} $p_{r}$ is the crossover probability.
+      \item \textbf{Binomial \index{crossover}crossover}: A \index{crossover}crossover mask is generated by randomly selecting indices from the set of possible \index{crossover}crossover points $\{1,2,\dots,J\}$ where $J$ is the problem dimension.
+Binomial \index{crossover}crossover is presented in Algorithm~\ref{algo:heuristics:de:bin}.
+In Algorithm~\ref{algo:heuristics:de:bin}, $p_{r}$ is the \index{crossover}crossover probability.
 The higher the value of $p_{r}$, the more points will be included in the set $\mathcal{J}$.
-A \textit{Bernoulli} distribution (presented in Chapter~\ref{chap:probability} can be used to generate the binomial crossover mask.
-Note that due to the probabilistic nature of this process, it is possible that no crossover points are selected.
-To counteract this situation, a randomly selected crossover point $j^{*}$ is included in the set $\mathcal{J}$ such that $\mathcal{J} \neq \emptyset$ where $\emptyset$ is the empty set.
-      \item \textbf{Exponential crossover}:~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} states that with exponential crossover a sequence of adjacent crossover points are selected start from some randomly selected crossover index.
-This means that the set of possible crossover points $\mathcal{J}$ is a circular array in indices.
-This technique does not require the selection of an additional crossover point $j^{*}$ as this technique includes at the very least one index, which is the starting index that is randomly selected.
-From this point, the next index is selected until $U(0,1) \geq p_{r}$ or $|\mathcal{J}| = N_{x}$.
-$p_{r}$ is the same crossover probability as mentioned above for binomial crossover.
-The implementation of exponential crossover is given in Algorithm~\ref{algo:heuristics:de:exp} below.
+A \textit{Bernoulli} distribution can be used to generate the binomial \index{crossover}crossover mask.
+Note that due to the probabilistic nature of this process, it is possible that no \index{crossover}crossover points are selected.
+To counteract this situation, a randomly selected \index{crossover}crossover point $j^{*}$ is included in the set $\mathcal{J}$ such that $\mathcal{J} \neq \emptyset$ where $\emptyset$ is the empty set.
+
+      \item \textbf{Exponential \index{crossover}crossover}:~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} states that with exponential \index{crossover}crossover, a sequence of adjacent \index{crossover}crossover points are selected from some randomly selected \index{crossover}crossover index.
+This means that the set of possible \index{crossover}crossover points $\mathcal{J}$ is a circular array in indices.
+Exponential \index{crossover}crossover does not require the selection of an additional \index{crossover}crossover point $j^{*}$ as this technique includes at the very least one index, which is the starting index that is randomly selected.
+From the starting index, the next index is selected until $U(0,1) \geq p_{r}$ or $|\mathcal{J}| = N$.
+$p_{r}$ is the same \index{crossover}crossover probability as mentioned above for binomial \index{crossover}crossover.
+The implementation of exponential \index{crossover}crossover is given in Algorithm~\ref{algo:heuristics:de:exp} below.
 \end{itemize}
@@
 \begin{algorithm}[H]
-      \caption{The pseudo code algorithm for the binomial crossover technique for \acs{DE}.}
+      \caption{The pseudo code algorithm for the binomial \index{crossover}crossover technique for \acs{DE}.}
       \label{algo:heuristics:de:bin}
       \begin{algorithmic}
-            \State $j^{*} \sim U(1,N_{x})$;
+            \State $j^{*} \sim U(1,N)$;
             \State $\mathcal{J} \gets \mathcal{J} \cup \{j^{*}\}$;
-            \For{each $j \in \{1, \dots, N_{x}\}$}
+            \For{each $j \in \{1, \dots, N\}$}
             \If{$U(0,1) < p_{r}$ and $j \neq j^{*}$ }
@@
 \begin{algorithm}[H]
-      \caption{The pseudo code algorithm for the exponential crossover technique for \acs{DE}.}
+      \caption{The pseudo code algorithm for the exponential \index{crossover}crossover technique for \acs{DE}.}
       \label{algo:heuristics:de:exp}
@@
             \State $\mathcal{J} \gets \{\}$;
-            \State $j \sim U(0,N_{x} - 1)$;
+            \State $j \sim U(0,N - 1)$;
             \Repeat
             \State $\mathcal{J} \gets \mathcal{J} \cup \{j + 1 \}$;
-            \State $j = (j+1) \mod N_{x}$
-            \Until{ $U(0,1) \geq p_{r}$ or $|\mathcal{J} = N_{x}$;}
+            \State $j = (j+1) \mod N$
+            \Until{ $U(0,1) \geq p_{r}$ or $|\mathcal{J}| = N$;}
       \end{algorithmic}
@@
 
-\subsubsection{Selection}
-\label{sec:heuristics:mh:de:selection}
-
-Selection refers to the technique that is used to determine which entities are included in the mutation operator to produce a trial vector~\cite{ref:engelbrecht:2007} as was shown in Section~\ref{sec:heuristics:mh:de:mutation} above.
-Various selection operators have been suggested.
-With reference to the mutation operator, most \acs{DE} implementations make use of random selection or the best entity is used as the target vector $x_{i_{1}}(t)$.
+\subsubsection{Selection}\label{sec:heuristics:mh:de:selection}
+
+Selection refers to the technique that is used to determine which entities are included in the \index{mutation}mutation operator to produce a trial vector~\cite{ref:engelbrecht:2007}.
+Various selection operators have been suggested~\cite{ref:storn:1996, ref:storn:1997}.
+With reference to the \index{mutation}mutation operator, most \acs{DE} implementations make use of random selection or the best entity is used as the target vector $x_{i_{1}}(t)$.
 To construct the population for the next generation, deterministic selection is used.
-As such, a parent is replaced if the offspring produces a better solution that the parent such that $f(x'_{i}(t)) \leq f(x_{i}(t))$.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} states that this is to ensure the average fitness of the population does not deteriorate.
+As such, a parent is replaced if the offspring produces a better solution than the parent such that $f(x'_{i}(t)) \leq f(x_{i}(t))$.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} states that deterministic selection for the next generation ensures the average fitness of the population does not deteriorate.
 
@@
 
-Algorithm~\ref{algo:heuristics:de:general_de} is taken from~\cite{ref:engelbrecht:2007} and presents the general \acs{DE} algorithm.
+Algorithm~\ref{algo:heuristics:de:general_de} is taken from~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} and presents the general \acs{DE} algorithm.
 The population is initialised by randomly placing entities in the search space such that the positions of the entities are confined to some search boundary.
@@
 
+\noindent
 As with other heuristics, \acs{DE} also contains a set of control parameters. These include:
@@
 Larger values facilitate exploration, but could cause the algorithm to overshoot.
-Similar to other heuristics, adaptive mechanisms can be used to dynamically alter the scaling factor throughout the optimisation process, however this is beyond the scope of this dissertation.
+Similar to other heuristics, adaptive mechanisms can be used to dynamically alter the scaling factor throughout the optimisation process.
 
       \item \textbf{Recombination Probability:} The probability of recombination, $p_{r}$ has a direct influence on the diversity of the \acs{DE} heuristic~\cite{ref:engelbrecht:2007}.
-This parameter controls the number of elements that are included during crossover.
+This parameter controls the number of elements that are included during \index{crossover}crossover.
 The higher the probability of recombination, the more variation is introduced in the new population.
-Similar to the scaling factor, dynamic techniques can be used to adjust this value dynamically during optimisation.
+Similar to the scaling factor, dynamic techniques can be used to adjust this the recombination probability during optimisation.
 \end{itemize}
@@
 Many variants of \acs{DE} have been created and researched~\cite{ref:mezura:2006}.
-A general notation for \acs{DE} heuristic variants have been developed by Storn et al.~\cite{ref:storn:1996}\cite{ref:storn:1997}.
+A general notation for \acs{DE} heuristic variants have been developed by Storn et al.~\cite{ref:storn:1996, ref:storn:1997}.
 The notation follows the form \textit{DE/$x$/$y$/$z$} where $x$,$y$ and $z$ refer to the components that are used by the particular \acs{DE}.
@@
       \item \textbf{$y$:} The number of difference vectors to include.
-      \item \textbf{$z$:} The type of crossover operator used.
-\end{itemize}
-
-For this dissertation, \textit{random} and \textit{best entity} selection, a single difference vector and binomial and exponential crossover is considered.
+      \item \textbf{$z$:} The type of \index{crossover}crossover operator used.
+\end{itemize}
+
+\noindent
+For this dissertation, \textit{random} and \textit{best entity} selection, a single difference vector and binomial and exponential \index{crossover}crossover are considered.
 This results in the \acs{DE} notations as follows.
@@
 
+\noindent
 This section provided the reader with the details around the implementation of the \acs{DE} heuristic. The last population-based \acs{MH} is presented next.
 
-\subsection{Genetic Algorithms}
-\label{sec:heuristics:mh:ga}
-
-\Ac{EC} refers to a collection of nature-inspired optimisation algorithms that lend their foundation to biological evolution.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that \acs{EC} refers to computer-based problem solving systems that use computational models of evolutionary processes such as natural selection, survival of the fittest and reproduction.
-It was Charles Darwin's theory of \textit{natural selection} that became the foundation of biological evolution~\cite{ref:darwin:1987}.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} summarises the Darwinian theory of evolution~\cite{ref:darwin:2012} as follows.
+\subsection{Genetic Algorithms}\label{sec:heuristics:mh:ga}
+
+\Ac{EC} refers to a collection of nature-inspired optimisation algorithms that lend their foundation to biological evolution.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that \acs{EC} refers to computer-based problem solving systems that use computational models of evolutionary processes such as natural selection, survival of the fittest and reproduction.
+Charles Darwin's theory of \textit{natural selection}~\cite{ref:darwin:2012} became the foundation of biological evolution~\cite{ref:darwin:1987}.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} summarises the Darwinian theory of evolution as follows.
 In a world with limited resources and stable populations, each individual competes with others for survival.
@@
 The \acs{DE} heuristic that was presented in Section~\ref{sec:heuristics:mh:de} is one type of \acs{EC} algorithm.
-This section introduces another population-based, nature-inspired optimisation \acs{EC} algorithm named \aclp{GA}.
-The detail of the implementation of \acp{GA} is given in this section.
-Importantly, the application of \acp{GA} is presented in the context of training \acp{FFNN}.
-\acp{GA} have been widely used to train \acp{FFNN}~\cite{ref:montana:1989}\cite{ref:siddique:2001}\cite{ref:miller:1989}.
-This section shines light on how this is done.
+This section introduces another population-based, nature-inspired optimisation \acs{EC} algorithm, referred to as \acfp{GA}.
+The details of the implementation of \acp{GA} is given in this section.
+\acp{GA} have been widely used to train \acp{FFNN}~\cite{ref:montana:1989, ref:siddique:2001, ref:miller:1989}.
 
@@
 As with other \acp{EA}, \acp{GA} implement a number of operators that drive the optimisation process.
-Primarily, \acp{GA} implement selection, modeling survival of the fittest and crossover, modeling reproduction.
-The remainder of this section follows the same approach as was done with \acs{DE} where the different operators are discussed.
-However, it is necessary to first provide the reader with the generic \acs{EC} algorithm.
-This algorithm is also referred to as the canonical \acs{GA} (CGA) and was proposed by Holland~\cite{ref:holland:1992}.
+Primarily, \acp{GA} implement selection, modeling survival of the fittest and \index{crossover}crossover, modeling reproduction.
+The remainder of this section presents the aforementioned operators in more detail.
+
+For sake of clarity, a generic \acs{EC} algorithm is presented first, as a frame of reference.
+The generic \acs{EC} algorithm is referred to as the canonical \acs{GA} (CGA) and was proposed by Holland~\cite{ref:holland:1992}.
 The generic \acs{EC} algorithm is taken from~\cite{ref:engelbrecht:2007} and is is presented in Algorithm~\ref{algo:heuristics:ga:generic_ec} below.
@@
             \State Let $t = 0$ be the generation counter;
-            \State Create an initialise an $N_{x}$-dimensional population, $\mathcal{C}(0)$, to consist of $N_{s}$ individuals;
+            \State Create an initialise a $J$-dimensional population $\mathcal{C}(0)$, to consist of $N$ individuals;
             \While{stopping condition not met}
@@
 
-From Algorithm~\ref{algo:heuristics:ga:generic_ec} above it can be seen that a number of components influence the search process. These include:
-
-\begin{itemize}
-      \item \textbf{Encoding}: Refers to the representation of a candidate solution to some optimisation problem as the chromosomes of some entity.
+\noindent
+From Algorithm~\ref{algo:heuristics:ga:generic_ec} above, it can be seen that a number of components influence the search process. These include:
+
+\begin{itemize}
+      \item \textbf{Encoding}: Refers to the representation of a candidate solution to some optimisation problem as the \index{chromosomes} of some entity.
+Every element in the chromosomes is referred to as a \textit{gene} or \textit{allele}.
 
@@
 
-      \item \textbf{Selection}: Refers to the techniques that are used to select entities for reproduction and generation of the new population as well as the selection of genes for mutation.
+      \item \textbf{Selection}: Refers to the techniques that are used to select entities for reproduction and generation of the new population as well as the selection of genes for \index{mutation}mutation.
 Selection is implemented through selection operators.
 
-      \item \textbf{Reproduction}: Refers to the generation of the next population and is implemented through crossover operators.
-\end{itemize}
-
-Note that the initial implementations of \acs{EC} heuristics such as \acp{GA} did not contain a mutation operator as this was only introduced later.
-The following sections provide the crossover, mutation and selection operators for \acp{GA}.
-
-\subsubsection{Crossover}
-\label{sec:heuristics:mh:ga:crossover}
-
-As with \acs{DE}, crossover operators model the reproduction of entities in the population.
-Broadly speaking, the crossover operators can be divided into three main categories~\cite{ref:engelbrecht:2007} and are based on arity of the operator i.e.
+      \item \textbf{Reproduction}: Refers to the generation of the next population and is implemented through \index{crossover}crossover operators.
+\end{itemize}
+
+\noindent
+The initial implementations of \acs{EC} heuristics such as \acp{GA} did not contain a \index{mutation}mutation operator as it was only introduced later~\cite{ref:engelbrecht:2007}.
+The following sections provide the \index{crossover}crossover, \index{mutation}mutation and selection operators for \acp{GA}.
+
+\subsubsection{Crossover}\label{sec:heuristics:mh:ga:crossover}
+
+As with \acs{DE}, \index{crossover}crossover operators model the reproduction of entities in the population.
+Broadly speaking, the \index{crossover}crossover operators can be divided into three main categories~\cite{ref:engelbrecht:2007} and are based on arity of the operator i.e.
 the number of parents used for reproduction.
@@
 \begin{itemize}
-      \item \textbf{Asexual: } Offspring is generated from one parent.
-
-      \item \textbf{Sexual: } Offspring is generated from two parents and can produce one or two offspring.
-
-      \item \textbf{Multi-recombination: } Offspring is generated from more than two parents and can produce one or more offspring.
-\end{itemize}
-
-\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that crossover operators can be further classified based on their encoding/representation scheme.
+      \item \textbf{Asexual:} Offspring is generated from one parent.
+
+      \item \textbf{Sexual:} Offspring is generated from two parents and can produce one or two offspring.
+
+      \item \textbf{Multi-recombination:} Offspring is generated from more than two parents and can produce one or more offspring.
+\end{itemize}
+
+\noindent
+\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that \index{crossover}crossover operators can be further classified based on their encoding/representation scheme.
 These include binary-specific operators used for binary representations and operators focused on floating-point representations.
@@
 
-During crossover, parents are selected using a selection operator.
-Selection operators are discussed later in Section~\ref{sec:heuristics:mh:ga:selection}.
+During \index{crossover}crossover, parents are selected using a selection operator.
 As with \acp{DE}, recombination is applied probabilistically and thus, selection of a parent does not guarantee reproduction.
 Each parent has a probability $p_{c}$ of producing offspring.
-Usually a high crossover probability is used~\cite{ref:engelbrecht:2007}.
+Usually a high \index{crossover}crossover probability is used~\cite{ref:engelbrecht:2007}.
 In addition to recombination, \acp{GA} implement a replacement policy where fit offspring can replace weaker parents in the population.
 
-Although floating-point representations of chromosomes are assumed, binary crossover operators can also be used since they produce a mask that defines how parents are recombined.
-Specifically, in the context of this dissertation, focus is put on \textit{uniform} crossover.
-Uniform crossover refers to a crossover operator where an $N_{x}$-dimensional crossover mask is generated randomly~\cite{ref:syswerda:1989}.
-Uniform crossover is illustrated in Figure~\ref{fig:heuristics:mh:ga:uniform_crossover} below and the algorithm for uniform crossover is given in Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover}.
+Although floating-point representations of chromosomes are assumed, binary \index{crossover}crossover operators can also be used, since they produce a mask that defines how parents are recombined.
+Specifically, in the context of this dissertation, focus is put on \textit{uniform} \index{crossover}crossover.
+Uniform \index{crossover}crossover refers to a \index{crossover}crossover operator where an $J$-dimensional \index{crossover}crossover mask is generated randomly~\cite{ref:syswerda:1989}.
+Uniform \index{crossover}crossover is illustrated in Figure~\ref{fig:heuristics:mh:ga:uniform_crossover} below and the algorithm for uniform \index{crossover}crossover is given in Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover}.
+In Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover}, $p_{x}$ is the bitswapping probability.
 
 \begin{figure}[htbp]
-      \includegraphics[width=\textwidth]{images/uniform_crossover.png}
-      \caption{An illustration of the uniform crossover operator as it applies to sexual recombination, resulting in two new offspring.}
+      \centering
+      \includegraphics[width=0.8\textwidth]{images/uniform_crossover.pdf}
+      \caption{An illustration of the uniform \index{crossover}crossover operator as it applies to sexual recombination, resulting in two new offspring.}
       \label{fig:heuristics:mh:ga:uniform_crossover}
@@
 \begin{algorithm}[H]
-      \caption{The pseudo code for the uniform crossover operator as used by \acp{GA}.}
+      \caption{The pseudo code for the uniform \index{crossover}crossover operator as used by \acp{GA}.}
       \label{algo:heuristics:mh:ga:uniform_crossover}
       \begin{algorithmic}
-            \State Initialise the mask, $m_{j}(t) = 0 \forall j = 1, \dots, N_{x}$;
-            \For{$j = 1$ to $N_{x}$}
+            \State Initialise the mask, $m_{j}(t) = 0, \forall j = 1, \dots, J$;
+            \For{$j = 1$ to $J$}
             \If{$U(0,1) \leq p_{x}$}
@@
 
-In Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover} above, $p_{x}$ is the bitswapping probability.
-
-\subsubsection{Mutation}
-\label{sec:heuristics:mh:ga:mutation}
-
-The mutation operator is applied in order to introduce new genetic material into an existing entity~\cite{ref:engelbrecht:2007}.
+\subsubsection{Mutation}\label{sec:heuristics:mh:ga:mutation}
+
+The \index{mutation}mutation operator is applied in order to introduce new genetic material into an existing entity~\cite{ref:engelbrecht:2007}.
 In doing so, diversity is added into the genetic characteristics of the population.
-Mutation is applied at a certain mutation probability $p_{m}$ to each gene of the offspring $x_{i}(t)$ to produce mutated offspring $x'_{i}(t)$.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that the mutation probability, also referred to as the mutation rate is usually small such that $p_{m} \in [0,1]$ to ensure that good solutions are not distorted too much.
-
-Similar to the crossover operator, mutation operators can be classified according to the representation scheme used. In the context of training
-\acp{FFNN}, binary crossover operators such as the \textit{uniform} mutation operator can be used to generate a mutation mask that specifies which genes are mutated.
-For the purposes of this dissertation, the application of the mutation operator on $x_{ij}(t)$ results in a small update step for that gene such that $x'_{ij}(t) = x_{ij}(t) + v_{ij}(t)$.
-In this case, $v_{ij}(t) \sim U(-limit, limit)$ and $limit = \sqrt{\frac{6}{fanin + fanout}}$ as presented for Glorot uniform sampling in~\ref{chap:anns}.
-An adaptation of the uniform mutation operator is then provided in Algorithm~\ref{algo:heuristics:mh:ga:uniform_mutation} below.
+Mutation is applied at a certain \index{mutation}mutation probability $p_{m}$, to each gene of the offspring $x_{i}(t)$ to produce mutated offspring $x'_{i}(t)$.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that the \index{mutation}mutation probability, also referred to as the \index{mutation}mutation rate, is usually small such that $p_{m} \in [0,1]$ to ensure that good solutions are not distorted too much.
+
+Similar to the \index{crossover}crossover operator, \index{mutation}mutation operators can be classified according to the representation scheme used. In the context of training
+\acp{FFNN}, binary \index{crossover}crossover operators such as the \textit{uniform} \index{mutation}mutation operator can be used to generate a \index{mutation}mutation mask that specifies which genes are mutated.
+For the purposes of this dissertation, the application of the \index{mutation}mutation operator on $x_{ij}(t)$ results in a small update step for that gene such that $x'_{ij}(t) = x_{ij}(t) + v_{ij}(t)$.
+In this case, $v_{ij}(t)$ is sampled using \index{Glorot uniform sampling}Glorot uniform sampling within the bounds $(-limit, limit)$, as was presented in Chapter~\ref{chap:anns}.
+An adaptation of the uniform \index{mutation}mutation operator is provided in Algorithm~\ref{algo:heuristics:mh:ga:uniform_mutation} below.
 
 \begin{algorithm}[H]
-      \caption{The pseudo code for the uniform mutation operator as used by \acp{GA}.}
+      \caption{The pseudo code for the uniform \index{mutation}mutation operator as used by \acp{GA}.}
       \label{algo:heuristics:mh:ga:uniform_mutation}
       \begin{algorithmic}
-            \For{$j = 1$ to $N_{x}$}
+            \For{$i = 1$ to $N$}
+            \For{$j = 1$ to $J$}
             \If{$U(0,1) \leq p_{m}$}
@@
             \EndFor
+            \EndFor
             \State
@@
 
-An illustration of the adapted uniform mutation operator is presented in Figure~\ref{fig:heuristics:mh:ga:uniform_mutation} below.
+\noindent
+An illustration of the adapted uniform \index{mutation}mutation operator is presented in Figure~\ref{fig:heuristics:mh:ga:uniform_mutation} below.
 
 \begin{figure}[htbp]
-      \includegraphics[width=\textwidth]{images/uniform_mutation.png}
-      \caption{An illustration of the adapted uniform mutation operator as it applies to mutated offspring.}
+      \centering
+      \includegraphics[width=0.8\textwidth]{images/uniform_mutation.pdf}
+      \caption{An illustration of the adapted uniform \index{mutation}mutation operator as it applies to mutated offspring.}
       \label{fig:heuristics:mh:ga:uniform_mutation}
@@
 The main idea behind the selection operator is to emphasise better solutions~\cite{ref:engelbrecht:2007}.
-This is done in two of the main components of \acp{EA}.
-These include
-
-\begin{itemize}
-      \item \textbf{Selection of the new population: } A new population of candidate solutions are is selected at the end of each generation to serve as the population for the next generation.
+Selection is applied in two of the main steps of \acp{EA}.
+These include:
+
+\begin{itemize}
+      \item \textbf{Selection of the new population:} A new population of candidate solutions are selected at the end of each generation to serve as the population for the next generation.
 The new population can be selected from both the parents and offspring.
@@
 
-      \item \textbf{Reproduction: } Offspring is created through the crossover and/or the mutation operators.
-In terms of crossover, good solutions should have a high probability of reproducing to ensure that offspring contain genetic material of the best entities.
-In terms of mutation, selection mechanisms should focus on weaker entities.
+      \item \textbf{Reproduction:} Offspring is created through the \index{crossover}crossover and/or the \index{mutation}mutation operators.
+In terms of \index{crossover}crossover, good solutions should have a high probability of reproducing to ensure that offspring contain genetic material of the best entities.
+In terms of \index{mutation}mutation, selection mechanisms should focus on weaker entities.
 By mutating weak entities, the hope is to introduce better traits, increasing their chance to survive.
@@
 
-\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that selection operators are characterised by their \textit{selective pressure}.
+\noindent
+\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that selection operators are characterised by their \textit{selective pressure}.
 Selective pressure is defined as the speed at which the best entity's solution will occupy the entire population by repeated application of the selection operator alone~\cite{ref:back:1994}.
-A selection operator with a high selective pressure rapidly decreases the diversity in the population.
-This could lead to premature convergence.
+A selection operator with a high selective pressure rapidly decreases the diversity in the population, possibly leading to premature convergence.
 A high selective pressure limits the exploration abilities of the population.
-Similar to other components and operators presented in this chapter, selection mechanisms should maintain a balance between exploration and exploitation.
+Selection operators should maintain a balance between exploration and exploitation.
 
@@
 \begin{itemize}
-      \item \textbf{Tournament Selection: } Tournament selection selects a group of $N_{ts}$ entities randomly from the population such that $N_{ts} < N_{s}$, where $N_{s}$ is the population size.
-The performance of the selected $N_{ts}$ entities are then compared and the best entities from this group is selected and returned by the operator.
-It should be mentioned that for sexual crossover of two parents, tournament selection is applied twice, first for the first parent and the again for the second parent.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that tournament selection prevents the best entities from dominating provided that $N_{ts}$ is not too large.
+      \item \textbf{Tournament Selection:} Tournament selection selects a group of $N_{t}$ entities randomly from the population such that $N_{t} < N$, where $N$ is the population size.
+The performance of the selected $N_{t}$ entities are then compared and the best entities from this group are selected and returned by the operator.
+It should be mentioned that for sexual \index{crossover}crossover of two parents, tournament selection is applied twice, first for the first parent and then again for the second parent.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that tournament selection prevents the best entities from dominating, provided that $N_{t}$ is not too large.
 This results in a lower selective pressure.
-If $N_{ts}$ is too small, the chances that bad entities will be selected increase.
-
-      \item \textbf{Rank-based Selection: } Rank-based selection uses the rank-ordered fitness values to determine the probability of selection and not the absolute fitness value.
-It can therefore be said that selection is independent of actual fitness values.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that the advantage of this approach is that the best entities will not dominate the selection process.
-Non-deterministic linear sampling selects an entity $x_{i}(t)$ such that $i \sim U(0, U(0, N_{s} - 1))$.
-Importantly, in the context of a minimisation problem, entities are first sorted in decreasing order of fitness value, assuming that the best heuristic is then contained at index 0, while the worst entity is contained at index $N_{s} - 1$.
-
-      \item \textbf{Elitism: } Elitism refers to the process of ensuring that the best entities from the current population survive to the next generation.
-The best entities are simply passed on to the next generation without mutation.
+If $N_{t}$ is too small, the chances that bad entities will be selected increase.
+
+      \item \textbf{Rank-based Selection:} Rank-based selection uses the rank-ordered fitness values to determine the probability of selection and not the absolute fitness value.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that the advantage of this approach is that the best entities will not dominate the selection process.
+Non-deterministic linear sampling selects an entity $x_{i}(t)$ such that $i \sim U(0, U(0, N - 1))$.
+Importantly, in the context of a minimisation problem, entities are first sorted in decreasing order of fitness value, assuming that the best heuristic is then contained at index 0, while the worst entity is contained at index $N - 1$.
+
+      \item \textbf{Elitism:} \index{elitism}Elitism refers to the process of ensuring that the best entities from the current population survive to the next generation.
+The best entities are simply passed on to the next generation without \index{mutation}mutation.
 The more entities that survive to the next generation, the lower the diversity of the new population.
-It is later shown in~\ref{chap:bhh} that the proposed \acs{BHH} can incorporate a form of elitism in its credit assignment strategy.
-\end{itemize}
-
-\subsubsection{Control Parameters}
-\label{sec:heuristics:mh:ga:control_parameters}
-
-Throughout this section a number of control parameters have been provided that affect the performance of the \acs{GA}.
-These include the population size $N$, the crossover rate $p_{c}$ and the mutation rate $p_{m}$.~\citeauthor{ref:engelbrecht:2007}\cite{ref:engelbrecht:2007} mentions that these values are usually kept static.
-However, it is widely accepted that these parameters have a significant impact on the performance of the \acs{GA}.
-Finding optimal values for $p_{c}$ and  $p_{m}$ empirically can be a time consuming process.
-As such, dynamic parameter values can be introduced, however, this is beyond the scope of this dissertation.
+\end{itemize}
 
@@
 
-This chapter provided the reader with detailed background information on different heuristics that have been shown to be able to train \acp{FFNN}.
-Two main groups of heuristics where discussed.
-These include gradient-based heuristics and \aclp{MH}.
-For each of these groups a number of different variants have been discussed.
-A total of ten different heuristics have been introduced and where possible, their advantages, disadvantages and characteristics have been discussed.
-
-The next chapter aims to build on the foundations provided in this chapter by putting focus on \acp{HH}.
-It is shown that \acp{MH} implement a heuristic pool of lower-level heuristics such as those presented in this chapter.
+This chapter provided the reader with detailed background information on \index{heuristic}heuristics.
+Different heuristics were presented that have been shown to be able to train \acp{FFNN}.
+Two main groups of \index{heuristic}heuristics where presented and discussed in detail.
+These include gradient-based \index{heuristic}heuristics and \acfp{MH}.
+A number of different variants for each group have been presented and discussed in detail.
+
+The following chapter aims to build on the foundations provided in this chapter and introduces the reader to \acfp{HH}.

### 2022-10-29 dissertation/chapters/04-hyper-heuristics.tex
✨ (chapter4): Review Done

@@
-\chapter{Hyper-Heuristics}
-\label{chap:hhs}
+\chapter{Hyper-Heuristics}\label{chap:hhs}
 
 \begin{quotation}
-      \textit{``Live as if you were to die tomorrow. Learn as if you were to live forever.'' - Mahatma Gandhi}
+      \noindent ``The capacity to learn is a gift; the ability to learn is a skill; the willingness to learn is a choice.''
 \end{quotation}
+\begin{flushright}
+      - Brian Herbert
+\end{flushright}
 
-One of the biggest challenges for any \ac{ML} researcher is that it is hard to find optimal configurations.
-These configurations often include the selection of appropriate models, heuristics and hyper-parameters.
-The optimal configuration is more often than not, problem-specific and it is difficult to find general approaches that can be applied to many situations.
+\noindent
+Chapter \ref{chap:heuristics} introduced the concept of a \index{heuristic}heuristic as an optimisation algorithm that is used in a search process that seeks out optimal solutions to an optimisation problem.
+Finding the best \index{heuristic}heuristic to use for a given optimisation problem is non-trivial.
+Furthermore, finding optimal solutions is often dependent on using the appropriate configurations.
+In the context of training \acp{FFNN}, these configurations could include \index{heuristic}heuristic hyper-parameters and model architecture.
+It is often the case that the application of a specific configuration only applies to a specific problem and does not necessarily translate or generalise to other problems~\cite{ref:kheiri:2017}.
+
+The optimal configuration of \index{heuristic}heuristics to use, along with hyper-parameters and model architecture, lies in some hyper-dimensional \textit{configuration space} yielding yet again, another optimisation problem on its own.
 Traditionally, if multiple configurations are to be considered, an empirical process of trial and error is executed.
-Trial and error approaches are time consuming and illustrates a problem of generalisation of solutions.
-A modern approach to this problem is to automate this process.
-Automation of this process can be done by brute force where many different configurations are considered iteratively, sweeping over different configurations one after the other.
-Only after all configurations have been considered, can an optimal configuration be identified.
+Trial and error approaches are time consuming and laborious.
 
-A different approach is to find optimal configurations by means of a search process.
-This means that a higher level optimisation process can be defined where the optimal configurations can be found as part of a search process.
-It is important to note that this search process is separate from the underlying problem to be solved.
-A measure of abstraction comes into play.
-In the context of training \acp{FFNN}, this is equivalent to finding the appropriate heuristic and hyper-parameters at various timesteps throughout the training process.
+One particular approach to the configuration optimisation problem mentioned above, is to try and automate the process to find the best configuration.
+One such automated process involves considering many different configurations in an iterative fashion, sweeping over different configurations parameters within the configuration space.
+Techniques such as \acf{DoE}, proposed by~\citeauthor{ref:fisher:1937}~\cite{ref:fisher:1937}, follow an iterative approach, where a configuration space is defined in terms of its extremities, while retrieving candidate configurations by interpolating over the configuration space.
+Iterative approaches implement a form of \index{offline learning}offline learning where the optimisation of configuration only happens after all configurations have been considered and evaluated.
 
-Automation alone is not enough.
-It is often the case that a single configuration is not sufficient.
-A modern suggestion is to include a hybridisation approach where multiple configurations are considered together.
-This is the nature of \acp{HH}.
-This is different from \textit{ensemble}~\cite{ref:dietterich:2002} approaches in the sense that \acp{HH} provide a single solution, where as \textit{ensembles} make use of the combination of solutions that undergo a net weighted transformation in order to produce a final solution.
+More modern techniques automate the search for optimal configuration as part of the underlying search process itself, resulting in a form of \index{online learning}online learning.
+An example of such a technique is to dynamically adjust and learn the heuristic \index{hyper-parameters}\textit{hyper-parameters} as part of the optimisation process.
+This field of study is known as \index{meta-learning}meta-learning~\cite{ref:giraud:2004}.
 
-So far the reader has been presented with background information on \acp{ANN} and heuristics.
-This chapter aims to provide the reader with the necessary background information on \acp{HH}.
-It should be noted that this is a short chapter as the foundations of heuristics have already been presented in Chapter \ref{chap:heuristics}.
-The remainder of the chapter is structured as follows:
+A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the \index{heuristic}heuristic used throughout the training process and not just the \index{heuristic}heuristic hyper-parameters.
+This approach focuses on the hybridisation of learning paradigms.
+By dynamically combining the best of different learning paradigms throughout the learning process, a trade-off can be made between focussing on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during training.
+The dynamic trade-off between exploration and exploitation could also be seen as a dynamic trade-off between the strengths and weaknesses of different heuristics during the search process.
+
+One such form of hybridisation of learning paradigms is referred to as \textit{heterogeneous learning approaches}.
+Heterogeneous learning approaches make use of different \textit{search behaviours} by selecting from a behaviour pool.
+Heterogeneous approaches have shown to balance the trade-off between exploration and exploitation~\cite{ref:nepomuceno:2013}.
+
+Another form of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem~\cite{ref:burke:2013}.
+These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.
+This dissertation takes a particular interest in developing a novel selection \acs{HH} that can be used to train \acp{FFNN}.
+This chapter provides the reader with the necessary background information of \index{meta-learning}meta-learning and \acp{HH}.
+The remainder of the chapter is structured as follows.
 
@@
 
-      \item \textbf{Section \ref{sec:hh:what_is_a_hh}} presents the concept of a \ac{HH} and a formal definition is provided.
+      \item \textbf{Section \ref{sec:hh:what_is_a_hh}} presents the concept of a \acs{HH} and a formal definition is provided.
+It is shown how \acp{HH} implement a form of \index{meta-learning}meta-learning.
 
       \item \textbf{Section \ref{sec:hh:classification}} provides a detailed discussion on the classification and types of \acp{HH}.
+Distinction is made between online and offline learning mechanisms.
+Discussions follow on selection and generation \acp{HH}, and constructive and generative mechanisms.
 
-      \item \textbf{Section \ref{sec:hh:application_to_nn_training}} sheds light on the applications of \acp{HH} in the context of training \acp{NN}.
-
-      \item Finally, a summary of the chapter is provided in \textbf{Section \ref{sec:hh:summary}}.
+      \item \textbf{Section \ref{sec:hh:summary}} provides a summary of the chapter.
 \end{itemize}
 
-\section{Meta-Learning}
-\label{sec:hh:meta_learning}
+\section{Meta-Learning}\label{sec:hh:meta_learning}
 
-Meta learning is a branch of metacognition and is concerned with learning about the learning processes.
-Meta-learning studies how learning systems can increase in efficiency through experience and is broadly defined as the learning process concerned with the concept of \textit{learning to learn}~\cite{ref:vilalta:2002}.
-The goal of meta-learning is to understand if learning itself can become flexible to the problem domain or task under consideration.
+\index{meta-learning}Meta-learning is inspired by a branch of meta-cognition that is concerned with learning about \textit{learning processes}.
+Meta-learning studies how learning systems can increase efficiency through experience~\cite{ref:vilalta:2002} and is broadly defined as the learning process concerned with the concept of \textit{learning to learn}~\cite{ref:thrun:1998}.
+The goal of meta-learning is to provide a learning/optimisation process that is flexible to the problem domain or task under consideration.
 
 \citeauthor{ref:vilalta:2002}~\cite{ref:vilalta:2002} mentions that meta-learning differs from base-learning in the scope of the level of adaptation.
-Meta-learning is concerned with learning how to choosing the right configuration and biases dynamically.
+Meta-learning is concerned with learning how to choose the right configuration and biases dynamically.
 On the contrary, for \textit{base}-learning, biases and configurations are predefined and fixed a priori.
+\citeauthor{ref:thrun:1998}~\cite{ref:thrun:1998} mentions that meta-learning aims at discovering ways to dynamically search for the best learning strategy as the number of tasks increases, implying some form of generalisation of the learning process to other problems.
+
+In the context of training \acp{FFNN}, \index{meta-learning}meta-learning could be applied to dynamically adjust the hyper-parameters of a \index{heuristic}heuristic during the training process.
+$K$-fold cross-validation is a common technique that applies dynamic adjustment of hyper-parameters during the training process~\cite{ref:allen:1974}.
+$K$-fold cross-validation is based on the idea that the optimal hyper-parameters for a given problem can be found by evaluating the performance of the heuristic on a subset of the training data.
+
+Dynamic adjustment of hyper-parameters might not be enough.
+Different search behaviours or techniques might be needed to balance the trade-off between exploration and exploitation.
+The following section provides a brief introduction to the concept of a \acf{HH}, a modern approach that builds on the foundations of \index{meta-learning}meta-learning.
 
@@
 
-The term \acl{HH} was first used in 1997~\cite{ref:burke:2010} and was used to describe a protocol that combines several \ac{AI} methods in the context of automated theorem proving.
-The term was independently used in 2000~\cite{ref:cowling:2000} to describe ``heuristics to choose heuristics''.
+The term \acf{HH} was first used in 1997 by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} and was used to describe a protocol that combines several \acs{AI} methods in the context of automated theorem proving.
+The term was independently used in 2000 by~\citeauthor{ref:cowling:2000}~\cite{ref:cowling:2000} to describe ``heuristics to choose heuristics''.
 
-Formal definition of \acp{HH} is required.~\citeauthor{ref:burke:2010}\cite{ref:burke:2010} defines \acp{HH} as search methods or learning mechanism for selecting or generating heuristics to solve computational search problems.
-Burke goes on to say that \ac{HH} is a high-level approach that, given a particular problem instance and a number of low-level heuristics, can select and apply an appropriate low-level heuristic at each decision point~\cite{ref:burke2003}.
+~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} define \acp{HH} as search methods or learning mechanism for selecting or generating heuristics to solve computational search problems.~\citeauthor{ref:burke:2003}~\cite{ref:burke:2003} mentions that a \acs{HH} is a high-level approach that, given a particular problem instance and a number of low-level heuristics, can select and apply an appropriate low-level heuristic at each decision point.
 
-\citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} states that \acp{HH} promote the design of more generally applicable search methodologies and tend to performing relatively well on a large set of different problems.
-This is in contrast to specialised algorithms which typically focus on outperforming the state-of-the-art for a single application.
+\citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} states that \acp{HH} promote the design of more generally applicable search methodologies and tend to perform relatively well on a large set of different problems, in contrast to specialised algorithms, which typically focus on outperforming the state-of-the-art for a single application.
 
-Importantly, \ac{HH} are concerned with finding the best heuristic in heuristic space, while the underlying low-level heuristics find solutions in the feasible search space.
-This level of abstraction is illustrated in Figure \ref{fig:heuristics:hh:hh_algorithm} below.
+\acp{HH} implement a form of \index{meta-learning}meta-learning that is concerned with the selection of the best heuristic from a pool of heuristics, to solve a given problem.
+In the context of population-based \acp{HH}, an entity pool exists that represent a pool of candidate solutions to the given problem.
+Each entity in the entity pool is assigned its own low-level \index{heuristic}heuristic from the heuristic pool.
+
+The selection of the best heuristic to apply to a candidate solution, is based on the performance of the heuristic relative to that particular candidate solution at a particular point in the search process.
+It can be said that \acp{HH} are concerned with finding the best \index{heuristic}heuristic in \textit{heuristic space}, while the underlying low-level \index{heuristic}heuristics find solutions in the feasible \textit{search/solution space}.
+\acp{HH}, introduce a domain barrier that separates the information that the high-level \index{heuristic}heuristic and low-level \index{heuristic}heuristics use during the search process and is illustrated in Figure \ref{fig:heuristics:hh:hh_algorithm} below.
 
@@
       \begin{centering}
-            \includegraphics[width=0.8\textwidth]{images/hh_high_level.png}
-            \caption{An illustration of abstraction introduced by \acp{HH}.}
+            \centering
+            \includegraphics[width=0.65\textwidth]{images/hh_domain_barrier.pdf}
+            \caption{An illustration of the domain barrier that exists as a result of the separation between the low-level \index{heuristic}heuristics and the high-level \index{heuristic}heuristic as introduced by \acp{HH}.}
             \label{fig:heuristics:hh:hh_algorithm}
@@
 
-One can clearly see from Figure \ref{fig:heuristics:hh:hh_algorithm} the abstraction of the heuristic search process.
-The two large elliptical figures highlight the entity and heuristic pools, each of these are concerned with their own optimisation process.
-Note, that at the higher level abstraction, \acp{HH} do not make use of domain specific information such as an entity's position or gradient in the search space.
+\noindent
+Figure \ref{fig:heuristics:hh:hh_algorithm} shows the separation of information that is accessible to the entity pool and heuristic pool.
+At a higher level abstraction, the high level heuristic implemented by \acp{HH}, do not make use of domain specific information such as an entity's position or gradient from the search space.
 
-\citeauthor{ref:grobler:2015}\cite{ref:grobler:2015} mentions that two fundamental ideas behind the notion of \ac{HH} can be identified.
+To summarise, \citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} highlights two fundamental ideas behind \acp{HH}.
 Firstly, the recognition that the process of selecting or designing efficient hybrid and/or cooperative heuristics can be regarded as a computational search problem in itself.
@@
 
-\section{Classification of Hyper-Heuristics}
-\label{sec:hh:classification}
+In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
+Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based meta-heuristics in real-valued dynamic optimization.
+Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
+The following section provides a framework for \acs{HH} classification.
 
-\citeauthor{ref:burke:2010}\cite{ref:burke:2010} proposed a modern classification scheme used to classify \acp{HH}.
+\section{Classification of Hyper-Heuristics}\label{sec:hh:classification}
+
+\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} proposed a modern classification scheme used to classify \acp{HH}.
 According to the proposed classification scheme, \acp{HH} are classified in two dimensions.
-These include the nature of the heuristic search space and the source of feedback during learning.
-Figure \ref{fig:heuristics:hh:classification} was taken from~\cite{ref:burke:2010} and summarises the classification scheme for \ac{HH}.
+These include the \textit{source of feedback} used during learning and the nature of the \textit{heuristic search space}.
+Figure \ref{fig:heuristics:hh:classification} presents the classification scheme as proposed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}.
 
 \begin{figure}[htbp]
-      \includegraphics[width=\textwidth]{images/hh_classification.png}
-      \caption{A classification of \ac{HH} approaches, according to two dimensions: (i) the nature of the heuristic search space, and (ii) the source of feedback during learning.}
+      \centering
+      \includegraphics[width=\textwidth]{images/hh_classification.pdf}
+      \caption{A classification of \acs{HH} approaches, according to two dimensions: (i) the source of feedback used during learning, and (ii) the nature of the heuristic search space.}
       \label{fig:heuristics:hh:classification}
@@
 
-Each of these groups are briefly discussed next.
+\subsection{Source of Feedback}
 
-\subsection{Selection vs. Generation}
+A \acs{HH} is considered to be a learning algorithm when it uses feedback from the search process to adapt and guide the search process.
+Learning \acp{HH} can implement a form of \index{online learning}\textit{online learning} or \index{offline learning}\textit{offline learning}.
 
-According to the classification proposed by~\cite{ref:burke:2010}, the first dimension of classification involves the nature of the search space.
-Distinction is made between heuristic selection and heuristic generation.
-For heuristic selection \acp{HH}, methodologies are implemented for choosing or selecting existing low-level heuristics.
-On the contrary, for heuristic generation \acp{HH}, methodologies  are implemented for generating new heuristics from components of existing heuristics.
+\acp{HH} that implement \index{online learning}online learning, implement a form of learning that continues to takes place while the algorithm is solving an instance of the underlying optimisation problem.
+Task-dependent, local properties can be used by the high-level \index{heuristic}heuristic to determine the appropriate low-level heuristic to apply at various points in the search process.
+Examples of \index{online learning}online learning approaches within \acp{HH} include the use of \acf{RL} and \acfp{MH} as high-level search strategies.
 
-Selection mechanisms can include probabilistic methods as is introduced in this dissertation or even some high level \ac{MH}. For generation mechanisms, \ac{EA} are often used~\cite{ref:burke:2010}.
+\acp{HH} that implement \index{offline learning}offline learning, implement a form of learning where knowledge, in the form of rules or programs, is gathered from a set of training instances and is then applied independently from the search process itself.
+Examples of offline learning approaches within hyper-heuristics include \textit{learning classifier systems}, \textit{case-based reasoning} and \acf{GP}.
 
-\subsection{Construction vs. Perturbation}
+\subsection{Heuristic Search Space}
+According to the classification proposed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the second dimension of classification involves the nature of the \index{heuristic}heuristic search space.
+Distinction is made between \index{heuristic}heuristic \textit{selection} and heuristic \textit{generation}.
 
-The second dimension of classification distinguishes between construction heuristics and perturbation heuristics.
-Consider first construction heuristics.
-According to~\citeauthor{ref:burke:2010}\cite{ref:burke:2010}, these approaches build a solution incrementally.
+\subsubsection{Selection vs. Generation}
+
+Selection \acp{HH} implement a high-level search mechanism that is used to determine which heuristic to apply to the underlying optimisation problem at a given point in the optimisation process.
+Selection mechanisms can include probabilistic approaches or high level \acfp{MH}.
+On the contrary, \index{heuristic}heuristic generation methodologies implement a mechanism that generate new heuristics from a pool of \textit{components} of various heuristics.
+Generation \acp{HH} often make use of \acfp{EA}~\cite{ref:burke:2010}.
+
+Selection \acp{HH} consists of two components, including a low-level \index{heuristic}heuristic selection strategy and a move acceptance strategy.
+Low-level \index{heuristic}heuristic selection can be done in a simple, \textit{non-adaptive} way.
+No learning is involved in these approaches.
+For non-adaptive techniques, heuristic selection is based on a predefined heuristic ordering that is generated either randomly or in a ordered cycle that is repeated throughout the optimisation process~\cite{ref:cowling:2000}.
+As an alternative, heuristic selection may incorporate an \textit{adaptive} (\index{online learning)}\textit{online learning}) mechanism, based on the probabilistic weighting of the low-level heuristics~\cite{ref:burke:2003} or some type of performance statistics~\cite{ref:cowling:2000}.
+
+A move acceptance strategy is the mechanism by which the application of a low-level \index{heuristic}heuristic is either accepted or rejected.
+In general, a move is accepted or rejected based on the quality of the move and the current solution during a single point search.~\citeauthor{ref:burke:2003}~\cite{ref:burke:2003} mentions that many move acceptance strategies have been explored within \acp{HH}.
+
+Move acceptance strategies can be divided into two categories.
+These include \textit{deterministic} and \textit{non-deterministic} move acceptance strategies.
+Deterministic move acceptance strategies generate the same result for the same candidate solution(s) used for the move acceptance test.
+Non-deterministic move acceptance strategies can involve other parameters, such as the current time, or a sampling operation that yields possibly different outcomes when repeated for the move acceptance test~\cite{ref:burke:2003}.
+
+\subsubsection{Construction vs. Perturbation}
+
+Selection and generation \acp{HH} can be further classified in terms of \textit{construction} and \textit{perturbation} mechanisms.
+According to~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, construction approaches build a solution incrementally.
 Starting with an empty solution, the goal is to intelligently select and use construction heuristics to gradually build a complete solution.
-As such, the \ac{HH} framework is provided with a set of pre-existing construction heuristics.
-These heuristics are generally problem specific and the challenge is to select the heuristic that is somehow the most suitable for the current problem state.
-This process is repeated until some final state such as a complete solution, is obtained.
+As such, the \acs{HH} framework is provided with a set of pre-existing construction heuristics.
 
-Perturbation heuristics refer to approaches that start with a complete solution, generated either randomly or using simple construction heuristics.
+Perturbation  approaches refer to approaches that start with a complete solution, generated either randomly or using simple construction heuristics.
 Perturbation heuristics try to iteratively improve the current solution.
 As such, the hyper-heuristic framework is provided with a set of neighbourhood structures and/or simple local searchers.
-The goal here it to iteratively select and apply them to the current complete solution.
-This process continues until a stopping condition has been met.
-Notice that these approaches do not have a natural termination condition.
-This is one of the biggest differences between construction and perturbation heuristics.
-
-\begin{itemize}
-      \item (i) low-level heuristic selection, and
-      \item (ii) move acceptance strategy.
-\end{itemize}
-
-Heuristic selection can be done in a \textit{non-adaptive} or simple way.
-This is done either randomly or along a cycle and is based on a prefixed heuristic ordering~\cite{ref:cowling:2000}.
-No learning is involved in these approaches.
-As an alternative, heuristic selection may incorporate an \textit{adaptive}, \textit{online learning}) mechanism based on the probabilistic weighting of the low-level heuristics~\cite{ref:burke:2003} or some type of performance statistics~\cite{ref:cowling:2000}.
-It will later be shown that the proposed \ac{BHH} implements this adaptive selection, perturbation strategy.
-
-The acceptance strategy is an important component of any local search heuristic.~\cite{ref:burke:2003} mentions that many acceptance strategies have been explored within \acp{HH}.
-Move acceptance strategies can be divided into two categories.
-These include \textit{deterministic} and \textit{non-deterministic}.
-In general, a move is accepted or rejected, based on the quality of the move and the current solution during a single point search.
-At any point in the search, deterministic move acceptance methods generate the same result for the same candidate solution(s) used for the acceptance test.
-However, a different outcome is possible if a non-deterministic approach is used.
-If the move acceptance test involves other parameters, such as the current time, then these strategies are referred to as non-deterministic strategies~\cite{ref:burke:2003}.
-
-\subsection{Online Learning vs. Offline Learning vs. No Learning}
-
-A \ac{HH} is considered to be a learning algorithm when it uses some feedback from the search process. Therefore, non-learning hyper-heuristics are those that do not use any feedback.
-
-With online learning \acp{HH}, learning continues to takes place while the algorithm is solving an instance of the underlying optimisation problem.
-Task-dependent local properties can be used by the high-level strategy to determine the appropriate low-level heuristic to apply.
-Examples of online learning approaches within hyper-heuristics include the use of reinforcement learning for heuristic selection and, generally, the use of \acp{MH} as high-level search strategies across a search space of heuristics.
-
-W.r.t offline learning \acp{HH} algorithms, the idea is to gather knowledge in the form of rules or programs, from a set of training instances.
-The hope is that it would generalise to the process of solving unseen instances.
-Examples of offline learning approaches within hyper-heuristics include \textit{learning classifier systems}, \textit{case-based reasoning} and \textit{genetic programming}.
-
-\section{Application to Neural Network Training}
-\label{sec:hh:application_to_nn_training}
-
-Training of \ac{FFNN} is notorious for being sensitive to configurations made beforehand.
-\acp{HH} provide a dynamic framework to train \ac{FFNN}.
-However, at the time of writing, only two examples of published work where found where \ac{HH} are used for training \ac{FFNN}.
-These include the works of Nel~\cite{ref:nel:2021} and Ul et al.~\cite{ref:ul:2018}
 
@@
 
-This chapter provided the reader with the necessary background information on \acp{HH}.
-A discussion on meta-learning is provided.
-The definition of a \ac{HH} is given and modern classifications of \ac{HH} types was discussed in detail.
-It was shown that \ac{HH} can be used to train \acp{FFNN}.
+This chapter provided the reader with the necessary background information on \index{meta-learning}meta-learning and \acp{HH}.
+Formal definitions were given, followed by detailed discussions.
+A modern classification scheme for \acs{HH} as proposed by ~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} was presented in detail.
+Distinction is made between the source of feedback information used during learning and the nature of the heuristic search space.
+Detailed discussions on selection and generation heuristics are provided, followed by a further classification of construction and perturbation mechanisms.
 
-This chapter then concludes the background information of heuristics in general.
-The next chapter aims to provide the reader with the necessary background information on statistics and probability theory.
-These concepts are required in order to formulate the proposed \ac{BHH}.
+This chapter concludes the background information of \index{heuristic}heuristics in general.
+The following chapter aims to provide the reader with the necessary background information on statistics and probability theory.

### 2022-10-29 dissertation/chapters/04-hyper-heuristics.tex
✨ (chapter4): Small fixes

@@
 Distinction is made between online and offline learning mechanisms.
-Discussions follow on selection and generation \acp{HH}, and constructive and generative mechanisms.
+Discussions follow on selection and generation \acp{HH}, and construction and perturbation mechanisms.
 
-      \item \textbf{Section \ref{sec:hh:summary}} provides a summary of the chapter.
+      \item \textbf{Section \ref{sec:hh:summary}} provides a brief summary of the chapter.
 \end{itemize}
@@
 For non-adaptive techniques, heuristic selection is based on a predefined heuristic ordering that is generated either randomly or in a ordered cycle that is repeated throughout the optimisation process~\cite{ref:cowling:2000}.
-As an alternative, heuristic selection may incorporate an \textit{adaptive} (\index{online learning)}\textit{online learning}) mechanism, based on the probabilistic weighting of the low-level heuristics~\cite{ref:burke:2003} or some type of performance statistics~\cite{ref:cowling:2000}.
+As an alternative, heuristic selection may incorporate an \textit{adaptive} (\index{online learning}\textit{online learning}) mechanism, based on the probabilistic weighting of the low-level heuristics~\cite{ref:burke:2003} or some type of performance statistics~\cite{ref:cowling:2000}.
 
@@
 
-\section{Summary}
-\label{sec:hh:summary}
+\section{Summary}\label{sec:hh:summary}
 

### 2022-10-29 dissertation/chapters/05-probability.tex
🚧 (chapter5): Save point

@@
 \begin{quotation}
-      \textit{``Probability theory is nothing but common sense reduced to calculation.'' - Pierre-Simon Laplace}
+      \noindent ``Probability theory is nothing but common sense reduced to calculation.''
 \end{quotation}
+\begin{flushright}
+      - Pierre-Simon Laplace
+\end{flushright}
 
-Probability theory and statistics can be traced back to as early as the 17th century.
+\noindent
+Probability theory and statistics can be traced back to as early as the 18th century.
 In 1718,~\citeauthor{ref:demoivre:1718}~\cite{ref:demoivre:1718} published the \textit{Doctrine of of Chance}; a book that is widely seen as the first published book on probability theory.
 In 1763, Thomas Bayes~\cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of Bayes' Theorem was introduced.
-It is from this theorem that the \ac{BHH} was named after.
 
-Probability theory and statistics play a vital role in the \ac{ML} space.
-A lot of constructs that arise in \ac{ML} originate from the fields of statistics and probability theory.
-There are many examples of how these two fields overlap.
-In 1991,~\citeauthor{ref:denker:1991},~\cite{ref:denker:1991} proposed a way to transform \ac{ANN} outputs to probability distributions.
-In 1993,
-\citeauthor{ref:neal:1993}~\cite{ref:neal:1993} developed the first \ac{MCMC} sampling algorithm for Bayesian \acp{NN}.
-These are just a  few examples of how the fields of probability theory, statistics and \ac{ML} overlap.
+Probability theory, statistics and \acf{ML} are transdisciplinary fields with many shared concepts.
+There are many examples of how probability theory has been incorporated into \acs{ML} research.
+In 1991,~\citeauthor{ref:denker:1991},~\cite{ref:denker:1991} proposed a way to transform \acf{ANN} outputs to probability distributions.
+In 1993, \citeauthor{ref:neal:1993}~\cite{ref:neal:1993} developed a \acf{MCMC} sampling algorithm for Bayesian \acp{NN}.
+These are but a few examples of the role that probability theory has played in \acs{ML} research in the past.
 
-So far the reader has been provided with the problem statement and goals of this dissertation in Chapter \ref{chap:introduction} and a detailed literature study and background information on \acp{ANN} was provided in Chapter \ref{chap:anns}.
+Chapter \ref{chap:hhs} provided the reader with the concept of a \acf{HH}.
+This dissertation aims to develop a selection \acs{HH} that makes use of probability theory to select the best \ac{HH} to solve a given problem.
 This chapter aims to provide the reader with the necessary background information on probability theory and statistics.
-These are big fields and focus is put on the elements that are required to formulate the proposed \ac{BHH}.
+These are big fields and focus is put on the elements that are required to formulate the proposed \acf{BHH}.
 The remainder of the chapter is structured as follows.
@@
 
-      \item \textbf{Section \ref{sec:probability:bayes_theorem}} introduces Bayes' Theorem, the fundamental theorem upon which the \ac{BHH} is built.
+      \item \textbf{Section \ref{sec:probability:bayes_theorem}} introduces Bayes' Theorem, the fundamental theorem upon which the \acs{BHH} is built.
 
-      \item \textbf{Section \ref{sec:probability:probability_distributions}} presents relevant probability distributions.
+      \item \textbf{Section \ref{sec:probability:probability_distributions}} presents the reader with the details of some relevant probability distributions.
 
-      \item \textbf{Section \ref{sec:probability:conjugate_priors}} presents the conjugate prior probability distributions for the probability distributions provided in Section \ref{sec:probability:probability_distributions}.
+      \item \textbf{Section \ref{sec:probability:conjugate_priors}} presents the reader with relevant conjugate prior probability distributions.
 
@@
 Brief discussions follow on the \textit{frequentist} view and \textit{Bayesian} view of probability.
-It is shown how Bayes' Theorem can be used to apply Bayesian statistics a alternative mechanism to do inference.
 Detailed discussions follow on \index{Bayesian optimisation}Bayesian optimisation methods such as \index{Bayesian analysis}\textit{Bayesian analysis}.
 
-      \item Finally, a summary of the elements discussed in this chapter is provided in \textbf{Section \ref{sec:probability:summary}}.
+      \item \textbf{Section \ref{sec:probability:summary}} provides a brief summary of the chapter.
 \end{itemize}
 
-\section{Overview}
-\label{sec:probability:overview}
+\section{Overview of Probability}\label{sec:probability:overview}
 
@@
 Although these random events cannot be predicted with absolute certainty, the relative frequency with which they occur over many trials if often remarkably stable.
+
 Consider flipping an unbiased, fair coin.
@@
 From this, one can conclude that each side has a $\frac{1}{2}$ or $50\%$ chance of occurring.
-In statistics, the decimal probability notation is used where $0 <= P(A) <= 1$.
+In statistics, the decimal probability notation is used, where $0 <= P(A) <= 1$.
 Suppose the fair coin is thrown 10 times, one is not guaranteed to observe $0.5$ heads and $0.5$ tails.
-There is is some probability, although small, that the coin might fall on heads $0/10$ times.
+There is some probability (although small) that the coin might fall on heads $0/10$ times.
 The probability of such an event occurring is $0.0009765625$.
@@
 The larger the value of $N$, the higher the confidence of mean probability and relative frequency of the event.
-The stable long-term relative frequency by which a random event occurs provides an intuitive and meaningful measure of belief that a certain event will occur again at some point in the future~\cite{ref:wackerly:2014}.
-The belief that a random event would occur again sometime in the future, at an expected relative frequency could be useful for decision making.
-It will later be shown that the proposed \ac{BHH} implements a probabilistic selection mechanism that continuously updates its beliefs such that it learns what the relative frequency by which a heuristic is selected should be.
+The stable long-term relative frequency by which a random event occurs, provides an intuitive and meaningful measure of belief that a certain event will occur again at some point in the future~\cite{ref:wackerly:2014}.
 
 Probability can also be expressed over multiple random events.
-For example, consider flipping a fair, unbiased coin and 6-sided dice together.
-One could then consider the probability of observing a certain outcome for the coin together with a certain outcome for the dice.
+For example, again consider flipping a fair, unbiased coin, but this time with a fair, unbiased 6-sided dice.
+One could consider the probability of observing a certain outcome for the coin together with a certain outcome for the dice.
 Multiple random events can be considered together, dependently or conditionally.
@@
 
-\section{Conditional Probability and Independence}
-\label{sec:probability:cond_probability}
+\section{Conditional Probability and Independence}\label{sec:probability:cond_probability}
 
@@
 In the field of medicine, an example of this is to calculate the probability of a certain diagnosis of a sick patient given his/her symptoms.
-This is referred to as the conditional probability between two events.
+The aforementioned dependence is referred to as the conditional probability between two events.
 The conditional probability is expressed as $P(A \vert B)$ and is read \textit{the probability of $A$ given $B$}.
@@
 
-      \begin{equation*}
+      \begin{equation}
+            \label{eq:probability:overview:conditional}
             P(A \vert B) = \frac{P(A \cap B)}{P(B)}
-      \end{equation*}
+      \end{equation}
 \end{definition}
 
-where $P(B) > 0$.
-Notice that conditional probability does not suggest causation.
+\noindent
+In Equation~\eqref{eq:probability:overview:conditional} above, $P(B) > 0$.
+Note that conditional probability does not suggest causation.
 If an event $A$ has a high probability of occurring after observing event $B$, it does not necessarily mean that $A$ is caused by $B$.
@@
 
+\noindent
 Events can also be considered together. The laws of probability for multiple events are presented next.
 
-\section{Two Laws of Probability for Multiple Events}
-\label{sec:probability:multiple_events}
+\section{Two Laws of Probability for Multiple Events}\label{sec:probability:multiple_events}
 
-Often times probabilities are calculated by considering multiple random events together.
 Suppose there are two random events $A$ and $B$, then one can calculate the probability of the union and intersection of these events.
-From this concept, two laws of probability can be formulated.
+From the aforementioned concept, two laws of probability can be formulated.
 These are referred to as the \textit{multiplicative} and \textit{additive} laws of probability~\cite{ref:wackerly:2014} and is given below in Theorems \ref{th:probability:multiple_events:multiplicative} and \ref{th:probability:multiple_events:additive} respectively.
@@
 
+      \noindent
       If $A$ and $B$ are independent, then
@@
 \begin{proof}
-      The proof of the additive law of probability is supported by the Venn Diagram presented in Figure \ref{fig:probability:multiple_events:additive} below.
-Notice that $A \cup B = A \cup ( \bar{A} \cap B)$, where $A$ and $\bar{A} \cap B$ are mutually exclusive events.
+      The geometric proof of the additive law of probability is given by the Venn Diagram presented in Figure \ref{fig:probability:multiple_events:additive}.
+Note that $A \cup B = A \cup ( \bar{A} \cap B)$, where $A$ and $\bar{A} \cap B$ are mutually exclusive events.
 Furthermore, consider that $B = (\bar{A} \cap B) \cup (A \cap B)$, where $\bar{A} \cap B$ and $A \cap B$ are mutually exclusive.
@@
 \begin{figure}[htbp]
-      \includegraphics[width=\textwidth]{images/additive_law_of_probability_proof.png}
+      \centering
+      \includegraphics[width=0.7\textwidth]{images/additive_law_of_probability_proof.png}
       \caption{A Venn-Diagram showing the proof of the additive law of probability for multiple events.}
@@
 
-The next section presents Bayes' Theorem and it is shown how it is related to conditional probability.
-
-\section{Bayes' Theorem}
-\label{sec:probability:bayes_theorem}
+\section{Bayes' Theorem}\label{sec:probability:bayes_theorem}
 
 Bayes' Theorem, named after Thomas Bayes, describes the probability of an event $A$, based on prior knowledge of conditions that might be related to $A$~\cite{ref:zalta:2015}.
-On order to derive the formal theorem and proof, first consider Definition \ref{def:probability:bayes_theorem:partition} below~\cite{ref:zalta:2015}.
+In order to derive the formal theorem and proof, first consider Definition \ref{def:probability:bayes_theorem:partition} below~\cite{ref:zalta:2015}.
 
@@
       \label{def:probability:bayes_theorem:partition}
-      For some positive integer, $k$, let the sets $B_{1}, B_{2}, \dots, B_{k}$ be such that
+      For some positive integer, $K$, let the sets $B_{1}, B_{2}, \dots, B_{K}$ be such that
 
       \begin{enumerate}
-            \item $S = B_{1} \cup B_{2} \cup \dots \cup B_{k}$
-            \item $B_{i} \cap B_{j} = \emptyset, for i \neq j$
+            \item $S = B_{1} \cup B_{2} \cup \dots \cup B_{K}$
+            \item $B_{i} \cap B_{j} = \emptyset$, for $i \neq j$
       \end{enumerate}
 
-      Then the collection of sets [$B_{1}$, $B_{2}$, $\dots$, $B_{k}$] is said to be a partition of S.
+      \noindent
+      Then the collection of sets [$B_{1}$, $B_{2}$, $\dots$, $B_{K}$] is said to be a partition of S.
 \end{definition}
-
-Bayes Theorem is then presented in Theorem \ref{th:probability:bayes_theorem:theorem} below.
 
@@
       \label{th:probability:bayes_theorem:theorem}
-      Assume that $[B_{1}, B_{2}, \dots, B_{k}]$ is a partition of $S$ such that $P(B_{i}) > 0$, for $i = 1,2, \dots, k$ then
+      Assume that $[B_{1}, B_{2}, \dots, B_{K}]$ is a partition of $S$ such that $P(B_{k}) > 0$, for $k = 1,2, \dots, K$ then\\
+      \\
       \begin{equation*}
-            P(B_{j} \vert A) = \frac{P(A \vert B_{j})P(B_{j})}{\sum_{i=1}^{k} P(A \vert B_{i})P(B_{i})}
+            P(B_{k} \vert A) = \frac{P(A \vert B_{k})P(B_{k})}{\sum_{k=1}^{K} P(A \vert B_{k})P(B_{k})}
       \end{equation*}
@@
 \begin{proof}
-      The proof follows directly from the definition of of conditional probability as was discussed in \ref{sec:probability:cond_probability}. This is shown below
+      The proof follows directly from the definition of conditional probability as was presented in \ref{sec:probability:cond_probability}. This is shown below
 
@@
             \begin{split}
-                  P(B_{j} \vert A)
-                  &= \frac{P(A \cap B_{j})}{P(A)}\\
-                  &= \frac{P(A \vert B_{j})P(B_{j})}{\sum_{i=1}^{k} P(A \vert B_{i})P(B_{i})}
+                  P(B_{k} \vert A)
+                  &= \frac{P(A \cap B_{k})}{P(A)}\\
+                  &= \frac{P(A \vert B_{k})P(B_{k})}{\sum_{k=1}^{K} P(A \vert B_{k})P(B_{k})}
             \end{split}
@@
 
+\noindent
 One of the many applications of Bayes' Theorem is to do statistical inference.
-This is referred to as Bayesian inference.
-The theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
+Bayes' Theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
 
-Bayesian inference is fundamental to Bayesian statistics.
-Section \ref{sec:probability:bayesian_statistics} presents the detail around Bayesian statistics.
-However, a brief detour is required to present to the user, a number of probability distributions.
-These probability distributions are presented next.
-Consider now a number of probability distributions as they are implemented.
-
-\section{Probability Distributions}
-\label{sec:probability:probability_distributions}
+\section{Probability Distributions}\label{sec:probability:probability_distributions}
 
 Probability distributions are mathematical functions that give the probabilities of the occurrences of different possible outcomes in the experiment.
-They play a crucial role in the architecture and design of the \ac{BHH}.
-It will later be shown how the proposed \ac{BHH} makes extensive use of probability distributions and sampling to formulate its selection mechanism.
 The theory and equations presented in the following sections where all taken from~\citeauthor{ref:wackerly:2014}~\cite{ref:wackerly:2014}.
 
-\subsection{Beta Distribution}
-\label{sec:probability:probability_distributions:beta}
+\subsection{Beta Distribution}\label{sec:probability:probability_distributions:beta}
 
-The Beta distribution is a family of univariate continuous probability distributions over some $x$, with support on the interval $[0,1]$~\cite{ref:wackerly:2014}.
+The Beta distribution is a family of univariate, continuous, probability distributions over some $x$, with support on the interval $[0,1]$~\cite{ref:wackerly:2014}.
 It is parameterised by two shape parameters $\alpha > 0$, $\alpha \in \mathbb{R}$ and $\beta > 0$, $\beta \in \mathbb{R}$.
 The Beta distribution is denoted as $Beta(\alpha, \beta)$.
-The \ac{PDF} of the Beta distribution is given below in Equation~\eqref{eq:probability:probability_distributions:beta:pdf}.
+The \ac{PDF} of the Beta distribution is given in Equation~\eqref{eq:probability:probability_distributions:beta:pdf} below.
 
@@
 
-where the normalising constant $B(\alpha, \beta)$ is defined below in Equation~\eqref{eq:probability:probability_distributions:beta:norm_const}.
+\noindent
+From Equation~\eqref{eq:probability:probability_distributions:beta:pdf} above, the normalising constant $B(\alpha, \beta)$, is defined below in Equation~\eqref{eq:probability:probability_distributions:beta:norm_const}.
 
@@
 
-and $\Gamma$ is the Gamma function as defined below in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func}.
+\noindent
+In Equation~\eqref{eq:probability:probability_distributions:beta:norm_const}, $\Gamma$ is the Gamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func} below.
 
@@
 
-it should be noted that the Gamma function can also be written as shown in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func_alt} below.
+\noindent
+It should be noted that the Gamma function can also be written as shown in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func_alt} below.
 
@@
 
-It should be noted that $\alpha$ and $\beta$ determine the shape of the distribution.
+\noindent
+The control parameters $\alpha$ and $\beta$, determine the shape of the distribution.
 There exists a special case where $\alpha = \beta$.
@@
 In the case where $\alpha = \beta = 1$ the distribution is equivalent to the uniform distribution over all points in its support.
-The Beta distribution for various values of $\alpha$ and $\beta$, including the symmetric version is presented below in Figure \ref{fig:probability:probability_distributions:beta}.
+The Beta distribution for various values of $\alpha$ and $\beta$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:beta}.
 
@@
       \begin{subfigure}{0.49\textwidth}
-            \includegraphics[width=\textwidth]{images/beta_various.png}
+            \centering
+            \includegraphics[width=\textwidth]{images/beta_various.pdf}
             \caption{Beta distribution}
@@
       \begin{subfigure}{0.49\textwidth}
-            \includegraphics[width=\textwidth]{images/beta_cumulative.png}
+            \centering
+            \includegraphics[width=\textwidth]{images/beta_cumulative.pdf}
             \caption{Cumulative Beta distribution}
@@
 
+\noindent
 The expected value of $x$ is given below in Equation~\eqref{eq:probability:probability_distributions:beta:expected_value}.
@@
 
-Similarly, the expected value of the natural logarithm of $x$ can be calculated as shown below in Equation~\eqref{eq:probability:probability_distributions:beta:expected_value_ln}.
+\noindent
+Similarly, the expected value of the natural logarithm of $x$ can be calculated as is shown below in Equation~\eqref{eq:probability:probability_distributions:beta:expected_value_ln}.
 
@@
 
-where $\psi$ is the logarithmic derivative of the Gamma function, called the \textit{Digamma} function.
+\noindent
+In Equation~\eqref{eq:probability:probability_distributions:beta:expected_value_ln} above, $\psi$ is the logarithmic derivative of the Gamma function, called the \textit{Digamma} function.
 The Digamma function is given below in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}.
@@
 
+\noindent
 Finally, the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:beta:mode} below.
@@
 $\alpha$ is referred to as the concentration parameter.
-It is later shown in Chapter \ref{chap:bhh} that this parameter plays a vital role in the optimisation process of the \ac{BHH}.
 The Dirichlet distribution of order $K \geq 2$ with parameters $\alpha$, denoted $Dir(\alpha)$, has a \ac{PDF} as given in Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} below.
@@
 
-where the normalising constant $B(\alpha)$ is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:norm_cost}.
+\noindent
+In Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} above, the normalising constant $B(\alpha)$, is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:norm_cost}.
 
@@
 
-and $\alpha_{0}$ is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:alpha_0} below.
+\noindent
+In Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} above, $\alpha_{0}$ is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:alpha_0} below.
 
@@
 
+\noindent
 Importantly, the set $\{x_{k}\}_{k=1}^{K}$ belongs to the standard $K-1$ probability simplex $S$, meaning that $x_{K} = 1 - \sum_{k=1}^{K-1}x_{k}$ with support $\forall_{k=1}^{K} x \in [0,1]$.
@@
 In the case where $c = 1$, the distribution is referred to as a \textit{flat} distribution and yields the uniform distribution over all points in $S$.
-The Dirichlet distribution of order $K = 3$, for various values of $\alpha$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:dirichlet} below.
+The Dirichlet distribution of order $K = 3$, for various values of $\alpha$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:dirichlet}.
 
 \begin{figure}[htbp]
-      \includegraphics[width=\textwidth]{images/dirichlet.jpg}
-      \caption{The \acp{PDF} for the Dirichlet distribution over the 2-simplex.
+      \centering
+      \includegraphics[width=0.8\textwidth]{images/dirichlet.pdf}
+      \caption{The \acfp{PDF} for the Dirichlet distribution over the 2-simplex.
 The concentration parameter $\alpha$ is varied.
-The values of $\alpha$ are set to (1.5, 1.5, 1.5), (5, 5, 5), (1, 2, 2), and (2, 4, 8) respectively, read from top to bottom, left to right.
-The values of the \ac{PDF} are shown by the color maps with contour lines at equal values as indicated in the color bars~\cite{ref:dirichlet:2020}.}
+The values of the \acs{PDF} are shown by the color maps with contour lines at equal values as indicated in the color bars~\cite{ref:dirichlet:2020}.}
       \label{fig:probability:probability_distributions:dirichlet}
@@
 
+\noindent
 The expected value of $x$ can be calculated as shown in Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value} below.
@@
 
+\noindent
 Similarly, the expected value of the natural logarithm of $x_{k}$ can be calculated as defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value_ln} below.
@@
 
-where $\psi$ is the Digamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}.
+\noindent
+In Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value_ln} above, $\psi$ is the Digamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}.
 Finally, the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:dirichlet:mode} below.

### 2022-10-30 dissertation/chapters/05-probability.tex
🚧 (chapter5): Conjugates review done

@@
 Chapter \ref{chap:hhs} provided the reader with the concept of a \acf{HH}.
-This dissertation aims to develop a selection \acs{HH} that makes use of probability theory to select the best \ac{HH} to solve a given problem.
+This dissertation aims to develop a selection \acs{HH} that makes use of probability theory to select the best \acs{HH} to solve a given problem.
 This chapter aims to provide the reader with the necessary background information on probability theory and statistics.
@@
 Probability is a necessary tool used in many fields including physics, biology, chemistry and computer science.
-These fields contain many cases that generate observations that can not be predicted with absolute certainty~\cite{ref:wackerly:2014}.
+These fields contain many cases that generate observations that cannot be predicted with absolute certainty~\cite{ref:wackerly:2014}.
 Probability can be be inferred and confirmed through past events.
@@
 The probability that a certain event $A$ might occur is denoted $P(A)$.
-Although these random events cannot be predicted with absolute certainty, the relative frequency with which they occur over many trials if often remarkably stable.
+Although these random events cannot be predicted with absolute certainty, the relative frequency with which they occur over many trials, is often remarkably stable.
 
@@
 The probability of such an event occurring is $0.0009765625$.
-The \ac{CLT} shows that the normalised sum of events tends toward a normal distribution with a mean value of $0.5$ if the number of events observed $N$, is large~\cite{ref:wackerly:2014}.
+In the coin flip example, the \acf{CLT} shows that the normalised sum of events tends toward a normal distribution with a mean value of $0.5$ if the number of events observed $N$, is large~\cite{ref:wackerly:2014}.
 The larger the value of $N$, the higher the confidence of mean probability and relative frequency of the event.
@@
 Probability can also be expressed over multiple random events.
-For example, again consider flipping a fair, unbiased coin, but this time with a fair, unbiased 6-sided dice.
-One could consider the probability of observing a certain outcome for the coin together with a certain outcome for the dice.
 Multiple random events can be considered together, dependently or conditionally.
-The following sections provides insight into conditional and joints probabilities.
+The following sections provides insight into conditional and joints probabilities of multiple random events.
 
@@
 
-The occurrence of a given random event $A$ can often be dependent on the occurrence of another event $B$.
+The occurrence of a given random event $A$ can often be conditional on the occurrence of another event $B$.
 In the field of medicine, an example of this is to calculate the probability of a certain diagnosis of a sick patient given his/her symptoms.
-The aforementioned dependence is referred to as the conditional probability between two events.
+The aforementioned relationship between events is referred to as the conditional probability between two events.
 The conditional probability is expressed as $P(A \vert B)$ and is read \textit{the probability of $A$ given $B$}.
@@
       \label{def:probability:cond_probability:independence}
-      Two events, $A$ and $B$ are said to be independent of each other if, and only if the following criteria holds:
+      Two events, $A$ and $B$ are said to be independent of each other if, and only if the following criteria hold:
 
@@
 
+      \noindent
       otherwise events $A$ and $B$ are said to be \textit{dependent} random events.
 \end{definition}
-
-\noindent
-Events can also be considered together. The laws of probability for multiple events are presented next.
 
@@
 
-      \begin{equation*}
+      \begin{equation}
             \begin{split}
@@
             \end{split}
-      \end{equation*}
+      \end{equation}
 
@@
 
-      \begin{equation*}
+      \begin{equation}
             P(A \cap B) = P(A)P(B)
-      \end{equation*}
+      \end{equation}
 \end{theorem}
@@
 
-      \begin{equation*}
+      \begin{equation}
             P(A \cup B) = P(A) + P(B) - P(B \cap A)
-      \end{equation*}
+      \end{equation}
 \end{theorem}
@@
       \centering
-      \includegraphics[width=0.7\textwidth]{images/additive_law_of_probability_proof.png}
+      \includegraphics[width=0.7\textwidth]{images/additive_law_of_probability_proof.pdf}
       \caption{A Venn-Diagram showing the proof of the additive law of probability for multiple events.}
@@
       \noindent
-      Then the collection of sets [$B_{1}$, $B_{2}$, $\dots$, $B_{K}$] is said to be a partition of S.
+      Then the collection of sets $\{B_{1}$, $B_{2}$, $\dots$, $B_{K}\}$ is said to be a partition of S, the union of mutually exclusive subsets.
 \end{definition}
@@
       \label{th:probability:bayes_theorem:theorem}
-      Assume that $[B_{1}, B_{2}, \dots, B_{K}]$ is a partition of $S$ such that $P(B_{k}) > 0$, for $k = 1,2, \dots, K$ then\\
+      Assume that $[B_{1}, B_{2}, \dots, B_{K}]$ is a partition of $S$ such that $P(B_{i}) > 0$, for $i = 1,2, \dots, K$ then\\
       \\
-      \begin{equation*}
-            P(B_{k} \vert A) = \frac{P(A \vert B_{k})P(B_{k})}{\sum_{k=1}^{K} P(A \vert B_{k})P(B_{k})}
-      \end{equation*}
+      \begin{equation}
+            P(B_{j} \vert A) = \frac{P(A \vert B_{j})P(B_{j})}{\sum_{i=1}^{K} P(A \vert B_{i})P(B_{i})}
+      \end{equation}
 \end{theorem}
@@
 \begin{proof}
-      The proof follows directly from the definition of conditional probability as was presented in \ref{sec:probability:cond_probability}. This is shown below
+      The proof follows from the definition of conditional probability as was presented in \ref{sec:probability:cond_probability}.
 
-      \begin{equation*}
+      \begin{equation}
             \begin{split}
-                  P(B_{k} \vert A)
-                  &= \frac{P(A \cap B_{k})}{P(A)}\\
-                  &= \frac{P(A \vert B_{k})P(B_{k})}{\sum_{k=1}^{K} P(A \vert B_{k})P(B_{k})}
+                  P(B_{j} \vert A)
+                  &= \frac{P(A \cap B_{j})}{P(A)}\\
+                  &= \frac{P(A \vert B_{j})P(B_{j})}{\sum_{i=1}^{K} P(A \vert B_{i})P(B_{i})}
             \end{split}
-      \end{equation*}
+      \end{equation}
 \end{proof}
@@
 
-\subsection{Beta Distribution}\label{sec:probability:probability_distributions:beta}
+\subsection{Beta probability distribution}\label{sec:probability:probability_distributions:beta}
 
-The Beta distribution is a family of univariate, continuous, probability distributions over some $x$, with support on the interval $[0,1]$~\cite{ref:wackerly:2014}.
+The \index{Beta probability distribution}Beta probability distribution is a family of univariate, continuous, probability distributions over some $x$, with support on the interval $[0,1]$~\cite{ref:wackerly:2014}.
 It is parameterised by two shape parameters $\alpha > 0$, $\alpha \in \mathbb{R}$ and $\beta > 0$, $\beta \in \mathbb{R}$.
-The Beta distribution is denoted as $Beta(\alpha, \beta)$.
-The \ac{PDF} of the Beta distribution is given in Equation~\eqref{eq:probability:probability_distributions:beta:pdf} below.
+The \index{Beta probability distribution}Beta probability distribution is denoted as $Beta(\alpha, \beta)$.
+The \acf{PDF} of the \index{Beta probability distribution}Beta probability distribution is given in Equation~\eqref{eq:probability:probability_distributions:beta:pdf} below.
 
@@
 There exists a special case where $\alpha = \beta$.
-This is referred to as the \textit{symmetric} Beta distribution.
+This is referred to as the \textit{symmetric} \index{Beta probability distribution}Beta probability distribution.
 In the case where $\alpha = \beta = 1$ the distribution is equivalent to the uniform distribution over all points in its support.
-The Beta distribution for various values of $\alpha$ and $\beta$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:beta}.
+The \index{Beta probability distribution}Beta probability distribution for various values of $\alpha$ and $\beta$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:beta}.
 
@@
             \includegraphics[width=\textwidth]{images/beta_various.pdf}
-            \caption{Beta distribution}
+            \caption{\index{Beta probability distribution}Beta probability distribution}
             \label{fig:probability:probability_distributions:beta_normal}
@@
             \includegraphics[width=\textwidth]{images/beta_cumulative.pdf}
-            \caption{Cumulative Beta distribution}
+            \caption{Cumulative \index{Beta probability distribution}Beta probability distribution}
             \label{fig:probability:probability_distributions:beta_cumulative}
@@
       \par\bigskip
-      \caption{An illustration of the Beta distribution (left)~\cite{ref:beta:2014} as well as the cumulative Beta distribution (right)~\cite{ref:cumulativebeta:2014} for various values of $\alpha$ and $\beta$ .}
+      \caption{An illustration of the \index{Beta probability distribution}Beta probability distribution (left)~\cite{ref:beta:2014} as well as the cumulative \index{Beta probability distribution}Beta probability distribution (right)~\cite{ref:cumulativebeta:2014} for various values of $\alpha$ and $\beta$ .}
       \label{fig:probability:probability_distributions:beta}
@@
 
-\subsection{Dirichlet Distribution}
-\label{sec:probability:probability_distributions:dirichlet}
+\subsection{Dirichlet probability distribution}\label{sec:probability:probability_distributions:dirichlet}
 
-The Dirichlet distribution is a family of multivariate continuous probability distributions over some $x$ in $K$ dimensions ~\cite{ref:wackerly:2014}.
-The Dirichlet distribution is the multivariate generalization of the Beta distribution and is thus sometimes referred to by its alternative name, the Multivariate Beta Distribution.
-The Dirichlet distribution is parameterised by some vector $\alpha = (\alpha_{1}$,  $\dots, \alpha_{K})$ $\forall_{k=1}^{K} \alpha_{k} > 0$, $\alpha_{k} \in \mathbb{R}$.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution is a family of multivariate continuous probability distributions over some $x$ in $K$ dimensions~\cite{ref:wackerly:2014}.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution is the multivariate generalization of the \index{Beta probability distribution}Beta probability distribution and is thus sometimes referred to by its alternative name, the multivariate Beta probability distribution.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution is parameterised by some vector $\vec{\alpha} = (\alpha_{1}$,  $\dots, \alpha_{K})$ $\forall_{k=1}^{K} \alpha_{k} > 0$, $\alpha_{k} \in \mathbb{R}$.
 $\alpha$ is referred to as the concentration parameter.
-The Dirichlet distribution of order $K \geq 2$ with parameters $\alpha$, denoted $Dir(\alpha)$, has a \ac{PDF} as given in Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} below.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K \geq 2$ with parameters $\alpha$, denoted $Dir(\alpha)$, has a \acs{PDF} as is given in Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} below.
 
@@
 Importantly, the set $\{x_{k}\}_{k=1}^{K}$ belongs to the standard $K-1$ probability simplex $S$, meaning that $x_{K} = 1 - \sum_{k=1}^{K-1}x_{k}$ with support $\forall_{k=1}^{K} x \in [0,1]$.
-Under the simplex $S$, this means that the sum over all values of the vector $x$ must be 1.
+Under the simplex $S$, this means that the sum over all values of the vector $\vec{x}$ must be 1.
 The simplex can thus be rewritten as $\sum_{k=1}^{K}x_{k} = 1$.
 
-Similar to the Beta distribution, $\alpha$ determines the shape of the distribution in $K$ dimensions and thus, there also exist a special case, referred to as the \textit{symmetric} distribution when $\forall_{k=1}^{K} \alpha_{k} = c$, where $c$ is some constant.
+Similar to the \index{Beta probability distribution}Beta probability distribution, $\alpha$ determines the shape of the distribution in $K$ dimensions and thus, there also exist a special case, referred to as the \textit{symmetric} distribution when $\forall_{k=1}^{K} \alpha_{k} = c$, where $c$ is some constant.
 In the case where $c = 1$, the distribution is referred to as a \textit{flat} distribution and yields the uniform distribution over all points in $S$.
-The Dirichlet distribution of order $K = 3$, for various values of $\alpha$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:dirichlet}.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K = 3$, for various values of $\alpha$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:dirichlet}.
 
-\begin{figure}[htbp]
+\begin{figure}[htb]
       \centering
-      \includegraphics[width=0.8\textwidth]{images/dirichlet.pdf}
-      \caption{The \acfp{PDF} for the Dirichlet distribution over the 2-simplex.
+      \includegraphics[width=0.9\textwidth]{images/dirichlet.pdf}
+      \caption{The \acfp{PDF} for the \index{Dirichlet probability distribution}Dirichlet probability distribution over the 2-simplex.
 The concentration parameter $\alpha$ is varied.
@@
 
-\subsection{Bernoulli Distribution}
-\label{sec:probability:probability_distributions:bernoulli}
+\subsection{Bernoulli probability distribution}\label{sec:probability:probability_distributions:bernoulli}
 
-The Bernoulli distribution is a discrete probability distribution over some random variable $x$ that takes the value of $1$ with probability $\theta$ and $0$ with probability $1-\theta$ ~\cite{ref:wackerly:2014}.
-It is denoted as $Ber(\theta)$ with support $x \in \{0, 1\}$.
-In probability theory, the Bernoulli distribution is often used to explain the possible outcomes of a single experiment that asks a \textit{yes-no} question such as flipping a coin.
+The \index{Bernoulli probability distribution}Bernoulli probability distribution is a discrete probability distribution over some random variable $x$ that takes the value of $1$ with probability $\theta$ and $0$ with probability $1-\theta$ ~\cite{ref:wackerly:2014}.
+The \index{Bernoulli probability distribution}Bernoulli probability distribution is denoted as $Ber(\theta)$ with support $x \in \{0, 1\}$.
+In probability theory, the \index{Bernoulli probability distribution}Bernoulli probability distribution is often used to explain the possible outcomes of a single experiment that asks a \textit{yes-no} question such as flipping a coin.
 The outcome of such an experiment is a boolean value.
-The Bernoulli distribution has a \ac{PMF} as given below in Equation~\eqref{eq:probability:probability_distributions:bernoulli:pmf}.
+The \index{Bernoulli probability distribution}Bernoulli probability distribution has a \acf{PMF} as given below in Equation~\eqref{eq:probability:probability_distributions:bernoulli:pmf}.
 
@@
 
-The above equation can also be expressed as show in Equation~\eqref{eq:probability:probability_distributions:bernoulli:alt} below.
+\noindent
+Equation~\eqref{eq:probability:probability_distributions:bernoulli:pmf} above, can also be expressed as show in Equation~\eqref{eq:probability:probability_distributions:bernoulli:alt} below.
 
@@
 
-The mean of the Bernoulli distribution approaches $\theta$ over many samples according to the \ac{CLT}~\cite{ref:grinstead:1997}.
+\noindent
+The mean of the \index{Bernoulli probability distribution}Bernoulli probability distribution approaches $\theta$ over many samples according to the \acs{CLT}~\cite{ref:grinstead:1997}.
 Figure \ref{fig:probability:probability_distributions:bernoulli:coin} shows a simulation of a fair-coin flipping simulation.
-One can see how the mean converges to 0.5 for various sample sizes.
+The mean converges to 0.5 for various sample sizes.
 
 \begin{figure}[htbp]
+      \centering
       \begin{subfigure}{0.49\textwidth}
-            \includegraphics[width=\textwidth]{images/coin_flip_samples_100.png}
+            \centering
+            \includegraphics[width=\textwidth]{images/coin_flip_samples_100.pdf}
             \caption{100 Samples}
@@
       \begin{subfigure}{0.49\textwidth}
-            \includegraphics[width=\textwidth]{images/coin_flip_samples_10000.png}
-            \caption{1000 Samples}
-            \label{fig:probability:probability_distributions:bernoulli:coin_1000}
+            \centering
+            \includegraphics[width=\textwidth]{images/coin_flip_samples_10000.pdf}
+            \caption{10000 Samples}
+            \label{fig:probability:probability_distributions:bernoulli:coin_10000}
       \end{subfigure}
       \par\bigskip
-      \caption{An illustration of the the coin flip situation for different sample sizes that show the convergence of the mean as per the \ac{CLT}.}
+      \caption{An illustration of the the coin flip situation for different sample sizes that show the convergence of the mean as per the \acf{CLT}.}
       \label{fig:probability:probability_distributions:bernoulli:coin}
@@
 
+\noindent
 The expected value of the distribution is thus given according to Equation~\eqref{eq:probability:probability_distributions:bernoulli:expected_value} below.
@@
 
+\noindent
 while the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:bernoulli:mode} below.
@@
 
-\subsection{Binomial Distribution}
-\label{sec:probability:probability_distributions:bin}
+\subsection{Binomial Distribution}\label{sec:probability:probability_distributions:bin}
 
-The Binomial distribution is a discrete probability distribution over a random variable $x$ taking on a number of successes in $N$ sequential independent experiments that each ask a \textit{yes-no} question~\cite{ref:wackerly:2014}.
-The probability of a single independent experiment yielding a success is given as $\theta$ and the Binomial distribution is denoted as $Bin(N, \theta)$ with support $x \in \{0, 1, \dots, N\}$.
-It should be noted that the Binomial distribution is the extension of the Bernoulli distribution over $N$ independent sequential experiments and thus, each experiment also yields some boolean outcome.
-When $N=1$, the experiment is referred to as a Bernoulli trial and the distribution is just a Bernoulli distribution.
+The \index{Binomial distribution}Binomial distribution is a discrete probability distribution over a random variable $x$ taking on a number of successes in $N$ sequential independent experiments that each ask a \textit{yes-no} question~\cite{ref:wackerly:2014}.
+The probability of a single independent experiment yielding a success, is given as $\theta$ and the \index{Binomial distribution}Binomial distribution is denoted as $Bin(N, \theta)$ with support $x \in \{0, 1, \dots, N\}$.
+It should be noted that the \index{Binomial distribution}Binomial distribution is the extension of the \index{Bernoulli probability distribution}Bernoulli probability distribution over $N$ independent sequential experiments and thus, each experiment also yields some boolean outcome.
+When $N=1$, the experiment is referred to as a Bernoulli trial and the distribution is just a \index{Bernoulli probability distribution}Bernoulli probability distribution.
 When $N > 1$, the sequence of outcomes is referred to as a Bernoulli process.
-The \ac{PMF} of the Binomial distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:pmf} below.
+The \acf{PMF} of the \index{Binomial distribution}Binomial distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:pmf} below.
 
@@
 
-Similar to the Bernoulli distribution, the mean of the Binomial distribution is $N\theta$ given the \ac{CLT} as was shown in Figure \ref{fig:probability:probability_distributions:bernoulli:coin}.
-The expected value of the Binomial distribution is thus given in Equation~\eqref{eq:probability:probability_distributions:binomial:expected_value} below.
+\noindent
+Similar to the \index{Bernoulli probability distribution}Bernoulli probability distribution, the mean of the \index{Binomial distribution}Binomial distribution is $N\theta$ given the \acs{CLT} as was shown in Figure \ref{fig:probability:probability_distributions:bernoulli:coin}.
+The expected value of the \index{Binomial distribution}Binomial distribution is thus given in Equation~\eqref{eq:probability:probability_distributions:binomial:expected_value} below.
 
@@
 
+\noindent
 The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:mode} below.
@@
 
-\subsection{Categorical Distribution}
-\label{sec:probability:probability_distributions:categorical}
+\subsection{Categorical Probability Distribution}\label{sec:probability:probability_distributions:categorical}
 
-The Categorical distribution is a discrete probability distribution over some random variable $x$, taking on any one of $K$ possible categories~\cite{ref:wackerly:2014}.
-There is no innate underlying ordering to these categories and therefore, for simplicity, each category is assigned a numerical representative value such that $k = (1, \dots, K)$.
-The probabilities for all outcomes is given by the probability vector $\theta = (\theta_{1}, \dots, \theta_{K})$.
-This means that the probability $P(x=k)=\theta_{k}$ has support $x \in \{1, \dots, K\}$.
-The Categorical distribution, denoted $Cat(\theta)$ is the generalization of the Bernoulli distribution and is sometimes referred to it by its alternative names, the generalised Bernoulli Distribution or the Multinoulli distribution.
-In probability theory, the Categorical distribution is often used to explain the outcome of a single experiment with more than two possible outcomes such as rolling a die~\cite{ref:wackerly:2014}.
-The \ac{PMF} of the Categorical distribution is given in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf} below.
+The \index{Categorical probability distribution}Categorical probability distribution is a discrete probability distribution over some random variable $x$, taking on any one of $K$ possible categories~\cite{ref:wackerly:2014}.
+There is no ordering to these categories and therefore, for simplicity, each category is assigned a numerical representative value such that $k = (1, 2, \dots, K)$.
+The probabilities for all outcomes is given by the probability vector $\vec{\theta} = (\theta_{1}, \dots, \theta_{K})$.
+This means that the probability $P(x=k)=\theta_{k}$, has support $x \in \{1, \dots, K\}$.
+The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\theta)$, is the generalization of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, the generalised \index{Bernoulli probability distribution}Bernoulli probability distribution or the Multinoulli probability distribution.
+In probability theory, the \index{Categorical probability distribution}Categorical probability distribution is often used to explain the outcome of a single experiment with more than two possible outcomes such as rolling a die~\cite{ref:wackerly:2014}.
+The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution is given in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf} below.
 
@@
 
-where $[x = k]$ is the Iversion Bracket~\cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
-From this, one can conclude that for a given class $k$, the categorical distribution simply yields $\theta_{k}$ as is shown in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf_k} below.
+\noindent
+In Equation~\eqref{eq:probability:probability_distributions:categorical:pmf} above, $[x = k]$ is the \textit{Iversion Bracket}~\cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
+Given class $k$, the categorical distribution simply yields $\theta_{k}$ as is shown in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf_k} below.
 
@@
 
-The random variable $x$ can also be encoded in binary format, yielding a vector $x = (x_{1}, \dots, x_{K})$ of Bernoulli distributions such that the support is $\forall_{k=1}^{K} x_{k} \in \{0, 1\}$.
+\noindent
+The random variable $x$ can also be encoded in binary format, yielding a vector $\vec{x} = (x_{1}, \dots, x_{K})$ of \index{Bernoulli probability distribution}Bernoulli probability distributions such that the support is $\forall_{k=1}^{K} x_{k} \in \{0, 1\}$.
 Importantly, if the outcome of the random event is of category $k$, then $x_{k} = 1$ and $\forall_{j=1}^{K} x_{j} = 0, j \neq k$ so that the standard $K-1$ probability simplex $S$ still holds.
-The \ac{PMF} of the Categorical distribution can then be rewritten as follows in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf_alt} below.
+The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution can then be rewritten as follows in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf_alt} below.
 
@@
 
-where $\mathbbm{1}(x_{k})$ is the \textit{indicator function}, yielding 1 if $x_{k} = 1$ and 0 otherwise.
+\noindent
+In Equation \ref{eq:probability:probability_distributions:categorical:pmf_alt} above, $\mathbbm{1}(x_{k})$ is the \textit{indicator function}, yielding 1 if $x_{k} = 1$ and 0 otherwise.
 
-Since there is no innate order to the underlying categories, the mean of the distribution does not yield any relevant information.
+Since there is no order to the underlying categories, the mean of the distribution does not yield any relevant information.
 The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:categorical:mode} below.
@@
 
-The Multinomial distribution is a discrete probability distribution over some random variable $x = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials~\cite{ref:wackerly:2014}.
-The probabilities for all possible outcomes in a single trial is given by the probability vector $\theta = (\theta_{1}, \dots, \theta_{K})$.
-The Multinomial distribution, denoted $Mul(N, K, \theta)$, is thus the generalization of the Binomial distribution to $K$ dimensions.
+The \index{Multinomial probability distribution}Multinomial probability distribution is a discrete probability distribution over some random variable $x = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials~\cite{ref:wackerly:2014}.
+The probabilities for all possible outcomes in a single trial is given by the probability vector $\vec{\theta} = (\theta_{1}, \dots, \theta_{K})$.
+The \index{Multinomial probability distribution}Multinomial probability distribution, denoted $Mul(N, K, \theta)$, is thus the generalization of the \index{Binomial distribution}Binomial distribution to $K$ dimensions.
 Consider the following special cases.
@@
 \begin{itemize}
-      \item When $K$ is 2 and $N = 1$, the Multinomial distribution is the Bernoulli distribution.
-      \item When $K$ is 2 and $N > 1$, the Multinomial distribution is the Binomial distribution.
-      \item When $K > 2$ and $N = 1$, the Multinomial distribution is the Categorical distribution.
+      \item When $K$ is 2 and $N = 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Bernoulli probability distribution}Bernoulli probability distribution.
+      \item When $K$ is 2 and $N > 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Binomial distribution}Binomial distribution.
+      \item When $K > 2$ and $N = 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Categorical probability distribution}Categorical probability distribution.
 \end{itemize}
 
-The support for the Multinomial is $\forall_{i=1}^{K} x_{k} \in \{1, \dots, N\}, \sum_{k=1}^{K}x_{k} = N$ and the \ac{PMF} for the Multinomial distribution is given below in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf}.
+\noindent
+The support for the Multinomial is $\forall_{i=1}^{K} x_{k} \in \{1, \dots, N\}, \sum_{k=1}^{K}x_{k} = N$ and the \acs{PMF} for the \index{Multinomial probability distribution}Multinomial probability distribution is given below in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf}.
 
@@
 
-Similar to the Categorical distribution, the random variable $x$ can also be encoded in binary format, yielding an $N \times K$ matrix $X$ of Bernoulli distributions.
+\noindent
+Similar to the \index{Categorical probability distribution}Categorical probability distribution, the random variable $x$ can also be encoded in binary format, yielding an $N \times K$ matrix $X$ of \index{Bernoulli probability distribution}Bernoulli probability distributions.
 The support is then given as $X \in \{0, 1\}^{N \times K}, \forall_{i=1}^{N}\sum_{k=1}^{K} x_{i,k} = 1$ so that the standard $K-1$ probability simplex $S$ still holds for each trial.
-The \ac{PMF} of the Multinomial distribution can then be rewritten as is presented in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt}
+The \acs{PMF} of the \index{Multinomial probability distribution}Multinomial probability distribution can then be rewritten as is presented in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt}
 
@@
 
-where $N_{k}$ is a summary variable denoting the number of times a category $k$ occurs over all trials in $N$.
+\noindent
+In Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt} above, $N_{k}$ is a summary variable denoting the number of times a category $k$ occurs over all trials in $N$.
 
-The reason why the Categorical and Multinomial distributions are presented as binary encoded vectors is to simplify the proof of their conjugate priors as will be shown next.
-This is further supported by the fact that \acp{NN} often use binary encoding of feature vectors.
-The combination of these probabilistic methods and \acp{NN} forms the basic of this dissertation.
+The \index{Categorical probability distribution}Categorical and \index{Multinomial probability distribution}Multinomial probability distributions are presented as binary encoded vectors in order to simplify the proof of their conjugate priors as is shown in the following section.
 
-\section{Conjugate Priors}
-\label{sec:probability:conjugate_priors}
+\section{Conjugate Priors}\label{sec:probability:conjugate_priors}
 
@@
 This section considers the conjugate priors for the Binomial likelihood and Categorical/Multinomial likelihood.
-Each of these are presented next.
 
-\subsection{Binomial Likelihood}
-\label{sec:probability:conjugate_priors:binom_likelihood}
+\subsection{Binomial Likelihood}\label{sec:probability:conjugate_priors:binom_likelihood}
 
-The conjugate prior to a Bernoulli distribution is the Beta distribution
+The conjugate prior to a \index{Bernoulli probability distribution}Bernoulli probability distribution is the \index{Beta probability distribution}Beta probability distribution
 \cite{ref:wackerly:2014}. This is shown by demonstrating that the posterior distribution has the
@@
 
-      \item Let $\alpha \in \mathbb{R}, \alpha > 0$ and $\beta \in \mathbb{R}, \beta >0$ be the shape parameters to the Beta distribution.
+      \item Let $\alpha \in \mathbb{R}, \alpha > 0$ and $\beta \in \mathbb{R}, \beta >0$ be the shape parameters to the \index{Beta probability distribution}Beta probability distribution.
 
@@
 
+\noindent
 The Bernoulli likelihood is then given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:likelihood} below.
@@
 
-By Bayes Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.
+\noindent
+By Bayes' Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.
 
@@
 
+\noindent
 Since the denominator sums to $1$, one could get rid of the denominator and constants for the Bernoulli likelihood and the Beta prior, by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior_propto} below.
@@
 
-It is show that the posterior distribution is of the same functional form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N_{1} + \alpha$ and $\beta' = N_{0} + \beta$.
-This shows that the Beta distribution is the conjugate prior to the Bernoulli likelihood.
+\noindent
+The posterior distribution has the same functional form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N_{1} + \alpha$ and $\beta' = N_{0} + \beta$.
+This shows that the \index{Beta probability distribution}Beta probability distribution is the conjugate prior to the Bernoulli likelihood.
 
@@
 
-The conjugate prior to a Categorical and Multinomail distribution is the Dirichlet distribution~\cite{ref:wackerly:2014}.
-Similar to the proof of the conjugate prior for the Bernoulli distribution as shown in Section \ref{eq:probability:conjugate_priors:binom_likelihood:posterior} above, this means that the posterior distribution must have the same functional form $\mathcal{A}(v)$ as the prior distribution.
-This is shown as follows.
+The conjugate prior to a \index{Categorical probability distribution}Categorical and \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Dirichlet probability distribution}Dirichlet probability distribution~\cite{ref:wackerly:2014}.
+The proof of the conjugate prior for the \index{Bernoulli probability distribution}Bernoulli probability distribution is similar to the proof presented in Section \ref{sec:probability:conjugate_priors:binom_likelihood} above.This means that the posterior distribution must have the same functional form $\mathcal{A}(v)$ as the prior distribution.
+The proof is shown as follows.
 \\\\
@@
 
-      \item Let $\alpha = (\alpha_{1}, \dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} \in \mathbb{R}, \alpha_{k} > 0$ be the concentration parameters to the Dirichlet distribution.
+      \item Let $\alpha = (\alpha_{1}, \dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} \in \mathbb{R}, \alpha_{k} > 0$ be the concentration parameters to the \index{Dirichlet probability distribution}Dirichlet probability distribution.
 
@@
 
-The likelihood of the Categorical and Multinomial distributions is then given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:likelihood} below.
+\noindent
+The likelihood of the Categorical and \index{Multinomial probability distribution}Multinomial probability distributions is then given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:likelihood} below.
 
@@
 
-By Bayes Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.
+\noindent
+By Bayes' Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.
 
@@
 
-Since the denominator sums to $1$, one could get rid of the denominator and constants for the Dirichlet prior,by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior_propto} below.
+\noindent
+Since the denominator sums to $1$, one could get rid of the denominator and constants for the \index{Dirichlet probability distribution}Dirichlet prior, by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior_propto} below.
 
@@
 
-Is it shown that the posterior distribution is of the same form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N + \alpha$.
-This shows that the Dirichlet distribution is the conjugate prior to the Categorical and Multinomial likelihood.
+\noindent
+The posterior distribution has the same form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N + \alpha$.
+This shows that the \index{Dirichlet probability distribution}Dirichlet probability distribution is the conjugate prior to the Categorical and Multinomial likelihood.
 
-The next section aims to provide the reader with the concept of Bayesian statistics and it is shown how Bayesian inference and Bayesian analysis can be used to to train a \ac{HH}.
+The next section aims to provide the reader with the concept of Bayesian statistics and it is shown how Bayesian inference and Bayesian analysis can be used to to train a \acs{HH}.
 
@@
 More recent advancements in mathematical methods popularised the Bayesian approach again.
-A notable contribution to this switch was the invention of \ac{MCMC} in the 1950's.
+A notable contribution to this switch was the invention of \acs{MCMC} in the 1950's.
 This family of algorithms allowed for the construction of random sampling algorithms from a probability distribution which allows for the calculation of Bayesian hierarchical models~\cite{ref:hackenberger:2019}.
@@
 If Bayesian statistics is used then the experimental design that was chosen does not matter.
-In Bayesian statistics it is common to use a Beta distribution as a prior distribution.
+In Bayesian statistics it is common to use a \index{Beta probability distribution}Beta probability distribution as a prior distribution.
 If the prior distribution is sampled from $Beta(3,3)$ then using Bayesian analysis, the posterior distribution, according to the outcomes of this experiment, would yield $Beta(9,4)$.
@@
 
-Let $Y_{1}, Y_{2}, \dots, Y_{N}$ denote a random sample from a $Bernoulli$ distribution where $P(Y_{i} = 1) = \theta$ and $P(Y_{i} = 0) = 1 - \theta$ and the prior distribution for $\theta$ is $Beta(\alpha, \beta)$.
+Let $Y_{1}, Y_{2}, \dots, Y_{N}$ denote a random sample from a \index{Bernoulli probability distribution}Bernoulli probability distribution where $P(Y_{i} = 1) = \theta$ and $P(Y_{i} = 0) = 1 - \theta$ and the prior distribution for $\theta$ is $Beta(\alpha, \beta)$.
 The formulation of the posterior distribution for $p$ is then shown as follows.
-Since the $Bernoulli$ probability function can be written as
+Since the Bernoulli probability function can be written as
 
@@
 
-This chapter provided the reader with all the necessary background on probability theory and statistics that is required to formulate the \ac{BHH}.
+This chapter provided the reader with all the necessary background on probability theory and statistics that is required to formulate the \acs{BHH}.
 Detailed mathematical descriptions have been provided on probability distributions and proofs of conjugate priors are provided with detailed mathematical descriptions.
 Bayesian statistics have been presented in detailed and finally, it has been shown how Bayesian analysis works.
-The formulation of the \ac{BHH} is provided in the next chapter.
+The formulation of the \acs{BHH} is provided in the next chapter.

### 2022-10-30 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 (chapter5): Conjugates review done

@@
 
-      \item $\theta \vert \alpha \sim Dir(\alpha; K)$: Denote the heuristic probability distribution, implementing a Dirchlet probability distribution parameterised by $\alpha$ and $K$.
+      \item $\theta \vert \alpha \sim Dir(\alpha; K)$: Denote the heuristic probability distribution, implementing a Dirichlet probability distribution parameterised by $\alpha$ and $K$.
 Heuristic selection probabilities are sampled from this distribution.
-      \item $\phi \vert \beta \sim Dir(\beta; K)^{J}$: Denote the entity-heuristic probability distribution, implementing a Dirchlet probability distribution parameterised by $\beta$ and $K$ for each entity in the entity pool with population size $J$.
+      \item $\phi \vert \beta \sim Dir(\beta; K)^{J}$: Denote the entity-heuristic probability distribution, implementing a Dirichlet probability distribution parameterised by $\beta$ and $K$ for each entity in the entity pool with population size $J$.
 Entity-heuristic probabilities are sampled from this distribution.
@@
 The event $H$ is a multinomial distribution with parameter $\theta$.
-It is known that the conjugate prior to a multinomial distribution is a Dirichlet distribution (see Chapter \ref{chap:probability}.
+It is known that the conjugate prior to a multinomial distribution is a Dirichlet probability distribution (see Chapter \ref{chap:probability}.
 The \textit{prior} probability distribution for  $\theta_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_theta_prior} below.
@@
 Finally, the event $C$ is a binomial distribution with parameter $\psi$.
-It is known that the conjugate prior to a binomial distribution is a Beta distribution (see Chapter \ref{chap:probability}).
+It is known that the conjugate prior to a binomial distribution is a Beta probability distribution (see Chapter \ref{chap:probability}).
 The prior probability distribution for $\psi_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.
@@
 Normalisation is a hyper-parameter that aims to provide a mechanism of control for the degree to which exploration is allowed.
-Figure \ref{sec:bhh:hyper_parameters:discounted_rewards:normalisation} shows the effect of different concentrations ($\alpha$ and $\beta$) on the Beta distribution.
+Figure \ref{sec:bhh:hyper_parameters:discounted_rewards:normalisation} shows the effect of different concentrations ($\alpha$ and $\beta$) on the Beta probability distribution.
 By normalising the concentration parameters for the \ac{BHH} ($\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$), the variance of the selection probability distributions increase, allowing for sampled probabilities further from the mean and thus allowing for more exploration.
@@
       \par\bigskip
-      \caption{Beta distribution with varying $\alpha$ and $\beta$ values.}
+      \caption{Beta probability distribution with varying $\alpha$ and $\beta$ values.}
       \label{sec:bhh:hyper_parameters:discounted_rewards:normalisation}

### 2022-10-30 dissertation/chapters/09-conclusion.tex
🚧 WIP - Save point (compiles)
🚧 (chapter5): Conjugates review done

@@
 Though there exists many applications of \acp{HH} there are little to no published work on using \acp{HH} to train \acp{FFNN}.
-The only work that was found include the work by \citeauthor{ref:nel:2021} \cite{ref:nel:2021}.
+The only work that was found include the work by~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021}.
 
@@
 Credit assignment in the context of this dissertation was has 2 outcomes, true and false.
-Therefore, credit assignment and by definition performance evaluation is modeled as a \index{binomial distribution} distribution with a \index{beta probability distribution}beta probability distribution as a prior probability distribution.
+Therefore, credit assignment and by definition performance evaluation is modeled as a \index{binomial distribution} distribution with a \index{Beta probability distribution}Beta probability distribution as a prior probability distribution.
 Heuristic selection has multiple possible outcomes, yielding a index associated with a heuristic.

### 2022-10-30 dissertation/chapters/05-probability.tex
✨ (chapter5): Review Done

@@
 
-      \item \textbf{Section \ref{sec:probability:probability_distributions}} presents the reader with the details of some relevant probability distributions.
+      \item \textbf{Section \ref{sec:probability:probability_distributions}} presents the reader with relevant probability distributions.
 
@@
 Brief discussions follow on the \textit{frequentist} view and \textit{Bayesian} view of probability.
-Detailed discussions follow on \index{Bayesian optimisation}Bayesian optimisation methods such as \index{Bayesian analysis}\textit{Bayesian analysis}.
+Detailed discussions follow on Bayesian optimisation methods such as \index{Bayesian analysis}\textit{Bayesian analysis}.
 
@@
 These events are referred to as \textit{random} or \textit{stochastic} events.
-The probability that a certain event $A$ might occur is denoted $P(A)$.
+The probability that a certain event $A$ might occur, is denoted $P(A)$.
 Although these random events cannot be predicted with absolute certainty, the relative frequency with which they occur over many trials, is often remarkably stable.
@@
 The coin has two possible outcomes.
-From this, one can conclude that each side has a $\frac{1}{2}$ or $50\%$ chance of occurring.
+It can conclude that each side has a $\frac{1}{2}$ or $50\%$ chance of occurring.
 In statistics, the decimal probability notation is used, where $0 <= P(A) <= 1$.
@@
 The conditional probability of $A$ given $B$ can be expressed as is given in Definition \ref{eq:probability:cond_probability} below~\cite{ref:wackerly:2014}.
-
+\\
 \begin{definition}[\textbf{Conditional Probability}]
@@
 The independence between two events are expressed in Definition \ref{def:probability:cond_probability:independence} below.
-
+\\
 \begin{definition}[\textbf{Independence of Events}]
@@
       \noindent
-      otherwise events $A$ and $B$ are said to be \textit{dependent} random events.
+      otherwise, events $A$ and $B$ are said to be \textit{dependent} random events.
 \end{definition}
@@
 From the aforementioned concept, two laws of probability can be formulated.
-These are referred to as the \textit{multiplicative} and \textit{additive} laws of probability~\cite{ref:wackerly:2014} and is given below in Theorems \ref{th:probability:multiple_events:multiplicative} and \ref{th:probability:multiple_events:additive} respectively.
+These are referred to as the \textit{multiplicative} and \textit{additive} laws of probability~\cite{ref:wackerly:2014} and is given below in Theorems \ref{th:probability:multiple_events:multiplicative} and \ref{th:probability:multiple_events:additive} respectively.\\
 
@@
 \end{proof}
+\vspace*{0.5cm}
 
@@
 In order to derive the formal theorem and proof, first consider Definition \ref{def:probability:bayes_theorem:partition} below~\cite{ref:zalta:2015}.
-
+\\
 \begin{definition}
@@
 \end{definition}
+\vspace*{0.5cm}
 
@@
 \begin{proof}
-      The proof follows from the definition of conditional probability as was presented in \ref{sec:probability:cond_probability}.
+      The proof follows from the definition of conditional probability as was presented in Section~\ref{sec:probability:cond_probability}.
 
@@
 The \index{Dirichlet probability distribution}Dirichlet probability distribution is parameterised by some vector $\vec{\alpha} = (\alpha_{1}$,  $\dots, \alpha_{K})$ $\forall_{k=1}^{K} \alpha_{k} > 0$, $\alpha_{k} \in \mathbb{R}$.
+Throughout this chapter, the vector notation is dropped for simplicity and readability.
 $\alpha$ is referred to as the concentration parameter.
@@
 \noindent
-while the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:bernoulli:mode} below.
+The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:bernoulli:mode} below.
 
@@
 
-\subsection{Binomial Distribution}\label{sec:probability:probability_distributions:bin}
+\subsection{Binomial probability distribution}\label{sec:probability:probability_distributions:bin}
 
-The \index{Binomial distribution}Binomial distribution is a discrete probability distribution over a random variable $x$ taking on a number of successes in $N$ sequential independent experiments that each ask a \textit{yes-no} question~\cite{ref:wackerly:2014}.
-The probability of a single independent experiment yielding a success, is given as $\theta$ and the \index{Binomial distribution}Binomial distribution is denoted as $Bin(N, \theta)$ with support $x \in \{0, 1, \dots, N\}$.
-It should be noted that the \index{Binomial distribution}Binomial distribution is the extension of the \index{Bernoulli probability distribution}Bernoulli probability distribution over $N$ independent sequential experiments and thus, each experiment also yields some boolean outcome.
-When $N=1$, the experiment is referred to as a Bernoulli trial and the distribution is just a \index{Bernoulli probability distribution}Bernoulli probability distribution.
+The \index{Binomial probability distribution}Binomial probability distribution is a discrete probability distribution over a random variable $x$ taking on a number of successes in $N$ sequential independent experiments that each ask a \textit{yes-no} question~\cite{ref:wackerly:2014}.
+The probability of a single independent experiment yielding a success, is given as $\theta$ and the \index{Binomial probability distribution}Binomial probability distribution is denoted as $Bin(N, \theta)$ with support $x \in \{0, 1, \dots, N\}$.
+It should be noted that the \index{Binomial probability distribution}Binomial probability distribution is the extension of the \index{Bernoulli probability distribution}Bernoulli probability distribution over $N$ independent sequential experiments and thus, each experiment also yields some boolean outcome.
+When $N=1$, the experiment is referred to as a Bernoulli trial, and the distribution is just a \index{Bernoulli probability distribution}Bernoulli probability distribution.
 When $N > 1$, the sequence of outcomes is referred to as a Bernoulli process.
-The \acf{PMF} of the \index{Binomial distribution}Binomial distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:pmf} below.
+The \acf{PMF} of the \index{Binomial probability distribution}Binomial probability distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:pmf} below.
 
@@
 \noindent
-Similar to the \index{Bernoulli probability distribution}Bernoulli probability distribution, the mean of the \index{Binomial distribution}Binomial distribution is $N\theta$ given the \acs{CLT} as was shown in Figure \ref{fig:probability:probability_distributions:bernoulli:coin}.
-The expected value of the \index{Binomial distribution}Binomial distribution is thus given in Equation~\eqref{eq:probability:probability_distributions:binomial:expected_value} below.
+Similar to the \index{Bernoulli probability distribution}Bernoulli probability distribution, the mean of the \index{Binomial probability distribution}Binomial probability distribution is $N\theta$ given the \acs{CLT} as was shown in Figure \ref{fig:probability:probability_distributions:bernoulli:coin}.
+The expected value of the \index{Binomial probability distribution}Binomial probability distribution is thus given in Equation~\eqref{eq:probability:probability_distributions:binomial:expected_value} below.
 
@@
 The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\theta)$, is the generalization of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, the generalised \index{Bernoulli probability distribution}Bernoulli probability distribution or the Multinoulli probability distribution.
-In probability theory, the \index{Categorical probability distribution}Categorical probability distribution is often used to explain the outcome of a single experiment with more than two possible outcomes such as rolling a die~\cite{ref:wackerly:2014}.
+In probability theory, the \index{Categorical probability distribution}Categorical probability distribution is often used to explain the outcome of a single experiment with more than two possible outcomes, such as rolling a six-sided die~\cite{ref:wackerly:2014}.
 The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution is given in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf} below.
@@
 The probabilities for all possible outcomes in a single trial is given by the probability vector $\vec{\theta} = (\theta_{1}, \dots, \theta_{K})$.
-The \index{Multinomial probability distribution}Multinomial probability distribution, denoted $Mul(N, K, \theta)$, is thus the generalization of the \index{Binomial distribution}Binomial distribution to $K$ dimensions.
+The \index{Multinomial probability distribution}Multinomial probability distribution, denoted $Mul(N, K, \theta)$, is thus the generalization of the \index{Binomial probability distribution}Binomial probability distribution to $K$ dimensions.
 Consider the following special cases.
@@
       \item When $K$ is 2 and $N = 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Bernoulli probability distribution}Bernoulli probability distribution.
-      \item When $K$ is 2 and $N > 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Binomial distribution}Binomial distribution.
+      \item When $K$ is 2 and $N > 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Binomial probability distribution}Binomial probability distribution.
       \item When $K > 2$ and $N = 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Categorical probability distribution}Categorical probability distribution.
@@
 The support is then given as $X \in \{0, 1\}^{N \times K}, \forall_{i=1}^{N}\sum_{k=1}^{K} x_{i,k} = 1$ so that the standard $K-1$ probability simplex $S$ still holds for each trial.
-The \acs{PMF} of the \index{Multinomial probability distribution}Multinomial probability distribution can then be rewritten as is presented in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt}
+The \acs{PMF} of the \index{Multinomial probability distribution}Multinomial probability distribution can then be rewritten as is presented in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt} below.
 
@@
 \noindent
-In Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt} above, $N_{k}$ is a summary variable denoting the number of times a category $k$ occurs over all trials in $N$.
+In Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt} above, $N_{k}$ is a summary variable, denoting the number of times a category $k$ occurs over all trials in $N$.
 
@@
 \citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} states that conjugate priors are prior probability distributions that results in posterior distributions that are of the same functional form $\mathcal{A}(v)$ as the prior, but with different parameter values.
-This section considers the conjugate priors for the Binomial likelihood and Categorical/Multinomial likelihood.
+This section considers the conjugate priors that are used with the Binomial likelihood and Categorical/Multinomial likelihood.
 
@@
       \item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with boolean outcome.
-That is $x_{i} | \theta \overset{\text{iid}}{\sim} Ber(\theta)$ and thus $\mathcal{L}(x_{i} \vert \theta)$ is the Bernoulli likelihood.
+That is $x_{i} | \theta \overset{\text{iid}}{\sim} Ber(\theta)$ and $\mathcal{L}(x_{i} \vert \theta)$ is the Bernoulli likelihood.
 
@@
 \noindent
-The Bernoulli likelihood is then given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:likelihood} below.
+The Bernoulli likelihood is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:likelihood} below.
 
@@
 The posterior distribution has the same functional form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N_{1} + \alpha$ and $\beta' = N_{0} + \beta$.
-This shows that the \index{Beta probability distribution}Beta probability distribution is the conjugate prior to the Bernoulli likelihood.
+This shows that the \index{Beta probability distribution}Beta probability distribution is the conjugate prior used with the Bernoulli likelihood.
 
@@
 The conjugate prior to a \index{Categorical probability distribution}Categorical and \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Dirichlet probability distribution}Dirichlet probability distribution~\cite{ref:wackerly:2014}.
-The proof of the conjugate prior for the \index{Bernoulli probability distribution}Bernoulli probability distribution is similar to the proof presented in Section \ref{sec:probability:conjugate_priors:binom_likelihood} above.This means that the posterior distribution must have the same functional form $\mathcal{A}(v)$ as the prior distribution.
+The proof of the conjugate prior for the \index{Bernoulli probability distribution}Bernoulli probability distribution is similar to the proof presented in Section \ref{sec:probability:conjugate_priors:binom_likelihood} above.
+This means that the posterior distribution must have the same functional form $\mathcal{A}(v)$ as the prior distribution.
 The proof is shown as follows.
@@
       \item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with $K$ possible outcomes.
-That is $x_{i} | \theta \overset{\text{iid}}{\sim} Cat(\theta)$ and thus $\mathcal{L}(x_{i} \vert \theta)$ is the Categorical likelihood.
+That is $x_{i} | \theta \overset{\text{iid}}{\sim} Cat(\theta)$ and $\mathcal{L}(x_{i} \vert \theta)$ is the Categorical likelihood.
 
@@
 \noindent
-The likelihood of the Categorical and \index{Multinomial probability distribution}Multinomial probability distributions is then given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:likelihood} below.
+The likelihood of the Categorical and \index{Multinomial probability distribution}Multinomial probability distributions is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:likelihood} below.
 
@@
 The posterior distribution has the same form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N + \alpha$.
-This shows that the \index{Dirichlet probability distribution}Dirichlet probability distribution is the conjugate prior to the Categorical and Multinomial likelihood.
+This shows that the \index{Dirichlet probability distribution}Dirichlet probability distribution is the conjugate prior used with the Categorical/Multinomial likelihood.
 
@@
 Naturally, Bayesian statistics is based on Bayes' Theorem as was presented in Section \ref{sec:probability:bayes_theorem}.
-Bayesian statistics describe the probability of an event in terms of some belief based on previous knowledge of the event and the conditions under which the event happens~\cite{ref:hackenberger:2019}.
+Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event, and the conditions under which the event happens~\cite{ref:hackenberger:2019}.
 To introduce the concept of Bayesian inference and analysis, one first need to understand the difference between these two approaches.
-Bayesian statistics out-date the frequentist approach, but lacked interest in the early days partly because of the limited applications where the conjugate priors where known~\cite{ref:hackenberger:2019}.
+Bayesian statistics out-date the frequentist approach, but lacked interest in the early days, partly because of the limited applications where the conjugate priors where known~\cite{ref:hackenberger:2019}.
 More recent advancements in mathematical methods popularised the Bayesian approach again.
-A notable contribution to this switch was the invention of \acs{MCMC} in the 1950's.
-This family of algorithms allowed for the construction of random sampling algorithms from a probability distribution which allows for the calculation of Bayesian hierarchical models~\cite{ref:hackenberger:2019}.
+A notable contribution to this switch, was the development of \acf{MCMC} in the 1950's.
+This family of algorithms allowed for the construction of random sampling algorithms from a probability distribution, which allows for the calculation of Bayesian hierarchical models~\cite{ref:hackenberger:2019}.
 Soon after followed one of the earliest papers that use Bayesian statistics in the field of medicine in 1982~\cite{ref:ashby:2006}.
@@
 For the first experiment, the $P$-value is $0.031$ and for the second experiment, the $P$-value is $0.227$.
-Using a confidence level of $\alpha = 0.05$, one would conclude opposite outcomes for these two experiments when it comes to rejecting the null hypothesis, despite using the same data.
-The reason for this difference is because of the difference in their null distributions.
-The first approach uses a geometrical approach and the second used a binomial approach as is illustrated on Figure \ref{fig:probability:bayesian_statistics:mouse_experiment_outcome} below.
+Using a confidence level of $\alpha = 0.05$, one would conclude opposite outcomes for these two experiments, when it comes to rejecting the null hypothesis, despite using the same data.
+The reason for the difference in outcomes, is due to the difference in their null distributions.
+The first approach uses a geometrical approach, and the second used a binomial approach as is illustrated on Figure \ref{fig:probability:bayesian_statistics:mouse_experiment_outcome} below.
 
 \begin{figure}[htbp]
-      \includegraphics[width=\textwidth]{images/mouse_experiment_outcome.jpg}
+      \centering
+      \includegraphics[width=0.6\textwidth]{images/mouse_experiment_outcome.pdf}
       \caption{The experimental outcomes for the mice-population experiments as was taken from~\cite{ref:hackenberger:2019} .}
@@
 
-If Bayesian statistics is used then the experimental design that was chosen does not matter.
+\noindent
+If Bayesian statistics is used, the experimental design that was chosen does not matter.
 In Bayesian statistics it is common to use a \index{Beta probability distribution}Beta probability distribution as a prior distribution.
 If the prior distribution is sampled from $Beta(3,3)$ then using Bayesian analysis, the posterior distribution, according to the outcomes of this experiment, would yield $Beta(9,4)$.
-The process by which this is done is shown later in this section.
-The $Beta$ distribution was presented in Section \ref{sec:probability:probability_distributions:beta}.~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} mentions that the $Beta$ distribution can be seen as a probability distribution of the occurrence of specific parameters.
-From the information that is now known about the $Beta$ distribution, it is possible to calculate the probability that the sex ratio in this mice population is not 1:1 with the $Beta$ distribution as a prior, yielding a $P$-value of $0.92$.
-This means that there is a probability of $92\%$ that the mice population is not 1:1, regardless of experiment design.
-This is illustrated in Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} below.
+
+~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} mentions that the $Beta$ distribution can be seen as a probability distribution of the occurrence of specific parameters.
+From the information that is now known about the $Beta$ distribution, it is possible to calculate the probability that the sex ratio in this mice population is not $1:1$, with the $Beta$ distribution as a prior, yielding a $P$-value of $0.92$.
+This means that there is a probability of $92\%$ that the mice population is not $1:1$, regardless of experiment design.
+An illustration of this is given in Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} below.
 
 \begin{figure}[htbp]
-      \includegraphics[width=\textwidth]{images/mouse_experiment_distributions.jpg}
+      \centering
+      \includegraphics[width=0.6\textwidth]{images/mouse_experiment_distributions.pdf}
       \caption{An illustration of the prior and posterior probability distributions for the outcomes of the mice-population experiment, using a $Beta$ prior, as was taken from~\cite{ref:hackenberger:2019}.}
@@
 
-One can see from Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} how the posterior distribution differs from the prior distribution.
-This is the nature of Bayesian analysis and is presented in more detail next.
+\noindent
+It can be seen from Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} how the posterior distribution differs from the prior distribution.
+This is the nature of Bayesian analysis and is presented in more detail in the following section.
 
@@
 Similar to the approaches followed above to explain Bayesian statistics, a proposal is made to explain Bayesian analysis by means of an example taken from~\cite{ref:wackerly:2014}.
-Let $Y_{1}, Y_{2}, \dots, Y_{N}$ denote the random variable that is observed over a sample size of $N$.
+Let $Y = Y_{1}, Y_{2}, \dots, Y_{N}$ denote the random variable that is observed over a sample size of $N$.
 Then the likelihood of the sample is given as $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$.
-In the discrete case this function is defined to be the joint probability $P(Y_{1} = y_{1}, Y_{2} = y_{2}, \dots, Y_{N} = y_{n})$ and the continuous case yields the joint density of $Y_{1}, Y_{2}, \dots, Y_{N}$, evaluated at $y_{1}, y_{2}, \dots, y_{n}$.
-The Bayesian view models the parameter $\theta$ as a random variable with a probability distribution.
-This probability distribution is referred to as the prior distribution of $\theta$.
-The symbol $\theta$ is included in the notation of $\mathcal{L}$ as an argument to illustrate that this function is dependent explicitly on the value of $\theta$.
-Importantly, this prior distribution is specified before any data is collected and represents the theoretical prior knowledge about $\theta$.
+In the discrete case the likelihood function is defined to be the joint probability $P(Y_{1} = y_{1}, Y_{2} = y_{2}, \dots, Y_{N} = y_{n})$ and the continuous case yields the joint density of $Y_{1}, Y_{2}, \dots, Y_{N}$, evaluated at $y_{1}, y_{2}, \dots, y_{n}$.
+The Bayesian view models the parameter $\theta$ as a random variable with a probability distribution, referred to as the prior distribution of $\theta$.
+The symbol $\theta$, is included in the notation of $\mathcal{L}$ as an argument to illustrate that this function is dependent, explicitly, on the value of $\theta$.
+Importantly, prior distribution is specified before any data is collected and represents the theoretical prior knowledge about $\theta$.
 Assume that the parameter $\theta$ has a continuous distribution with density $g(\theta)$ that has no unknown parameters.
@@
 
+\noindent
 The marginal density or mass function of $Y_{1}, Y_{2}, \dots, Y_{N}$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:marginal_density} below.
@@
 
-Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$ according to Bayes' Theorem is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.
+\noindent
+Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$, according to Bayes' Theorem, is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.
 
@@
 
-\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} mentions that the posterior density summarises all the pertinent information about the parameter $\theta$ by making use of the information contained in the prior for $\theta$ as well as the information in the observed data/evidence.
-Consider now how Bayesian analysis can used to update the priors on $\theta$ based on newly observed data.
+\noindent
+\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} mentions that the posterior density summarises all the pertinent information about the parameter $\theta$ by making use of the information contained in the prior for $\theta$, as well as the information in the observed data/evidence.
+
+Consider now how Bayesian analysis can be used to update the priors on $\theta$ based on newly observed data.
 As with the example above, the below is taken from~\cite{ref:wackerly:2014}.
+Let $Y_{1}, Y_{2}, \dots, Y_{N}$ denote a random sample from a \index{Bernoulli probability distribution}Bernoulli probability distribution, where $P(Y_{i} = 1) = \theta$ and $P(Y_{i} = 0) = 1 - \theta$ and the prior distribution for $\theta$ is $Beta(\alpha, \beta)$.
+The posterior distribution for $\theta$ can be formulated as follows.
+The Bernoulli probability function can be written as is shown in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_1} below.
 
-Let $Y_{1}, Y_{2}, \dots, Y_{N}$ denote a random sample from a \index{Bernoulli probability distribution}Bernoulli probability distribution where $P(Y_{i} = 1) = \theta$ and $P(Y_{i} = 0) = 1 - \theta$ and the prior distribution for $\theta$ is $Beta(\alpha, \beta)$.
-The formulation of the posterior distribution for $p$ is then shown as follows.
-Since the Bernoulli probability function can be written as
+\begin{equation}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:step_1}
+      P(y_{i} \vert \theta) = \theta^{y_{i}}(1 - \theta)^{1-y_{i}}
+\end{equation}
 
-\begin{equation*}
-      P(y_{i} \vert \theta) = \theta^{y_{i}}(1 - \theta)^{1-y_{i}}
-\end{equation*}
+\noindent
+In Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_1} above, $y_{i} = \{0,1\}$ and $0 < \theta < 1$.
+The likelihood $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$ is presented in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_2} below.
 
-where $y_{i} = \{0,1\}$ and $0 < \theta < 1$. The likelihood $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$ is
-
-\begin{equation*}
+\begin{equation}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:step_2}
       \begin{split}
@@
       \end{split}
-\end{equation*}
+\end{equation}
 
-Then
+\noindent
+Then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ from Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood} can be formulated as in shown in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_3} below.
 
-\begin{equation*}
+\begin{equation}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:step_3}
       \begin{split}
@@
       \end{split}
-\end{equation*}
+\end{equation}
 
-The marginal density of $Y_{1}, Y_{2}, \dots Y_{N}$ is then given as
+\noindent
+The marginal density of $Y_{1}, Y_{2}, \dots Y_{N}$ is then given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_4} below.
 
-\begin{equation*}
+\begin{equation}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:step_4}
       \begin{split}
@@
       \end{split}
-\end{equation*}
+\end{equation}
 
-Finally, the posterior density of $\theta$ is given as
+\noindent
+Finally, the posterior density of $\theta$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_5} below.
 
-\begin{equation*}
+\begin{equation}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:step_5}
       \begin{split}
@@
       \end{split}
-\end{equation*}
+\end{equation}
 
-From the above, one can see that the posterior density has the same functional shape $\mathcal{A}(v)$ as the prior, yielding the update on prior parameters as $\alpha^{*} = \sum y_{i} + \alpha$ and $\beta^{*} = n - \sum y_{i} + \beta$.
+\noindent
+The posterior density has the same functional shape $\mathcal{A}(v)$ as the prior, yielding the update on prior parameters as $\alpha^{*} = \sum y_{i} + \alpha$ and $\beta^{*} = n - \sum y_{i} + \beta$.
 
-\section{Summary}
-\label{sec:probability:summary}
+\section{Summary}\label{sec:probability:summary}
 
-This chapter provided the reader with all the necessary background on probability theory and statistics that is required to formulate the \acs{BHH}.
-Detailed mathematical descriptions have been provided on probability distributions and proofs of conjugate priors are provided with detailed mathematical descriptions.
-Bayesian statistics have been presented in detailed and finally, it has been shown how Bayesian analysis works.
-The formulation of the \acs{BHH} is provided in the next chapter.
+This chapter provided the reader with all the necessary background information on probability theory and statistics.
+The origins of statistical analysis was discussed and the differences between the frequentist and Bayesian view of statistics were discussed in detail.
+Probability distributions and proofs of conjugate priors were provided with detailed mathematical descriptions.
+Finally, a detailed description of Bayesian analysis was provided with detailed mathematical descriptions.
+
+This chapter concludes all the relevant background information that is needed to formulate the \acs{BHH}. The proposed \acs{BHH} is presented in the following chapter.

### 2022-10-30 dissertation/chapters/06-bayesian-hyper-heuristic.tex
✨ (chapter5): Review Done

@@
       \item $E \vert \phi \sim Mult(\phi; I, K)^{J}$: Denote the distribution of entity-heuristic combinations (event $E$), implementing a Multinomial distribution, parameterised by the sampled entity-heuristic selection probability $\phi$, the heuristic pool size $K$ and maximum number of instances $I$, for each entity in $J$.
-      \item $C \vert \psi \sim Bin(\psi, I)$: Denote the distribution of credit-heuristic combinations (event $C$), implementing a Binomial distribution, parameterised by the sampled credit-heuristic selection probability $\psi$ and the maximum number of instances $I$.
+      \item $C \vert \psi \sim Bin(\psi, I)$: Denote the distribution of credit-heuristic combinations (event $C$), implementing a\index{Binomial probability distribution}Binomial probability distribution, parameterised by the sampled credit-heuristic selection probability $\psi$ and the maximum number of instances $I$.
 \end{itemize}
@@
 
-Finally, the event $C$ is a binomial distribution with parameter $\psi$.
-It is known that the conjugate prior to a binomial distribution is a Beta probability distribution (see Chapter \ref{chap:probability}).
+Finally, the event $C$ is a\index{Binomial probability distribution}Binomial probability distribution with parameter $\psi$.
+It is known that the conjugate prior to a\index{Binomial probability distribution}Binomial probability distribution is a Beta probability distribution (see Chapter \ref{chap:probability}).
 The prior probability distribution for $\psi_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.

### 2022-10-30 dissertation/chapters/09-conclusion.tex
✨ (chapter5): Review Done

@@
 Credit assignment in the context of this dissertation was has 2 outcomes, true and false.
-Therefore, credit assignment and by definition performance evaluation is modeled as a \index{binomial distribution} distribution with a \index{Beta probability distribution}Beta probability distribution as a prior probability distribution.
+Therefore, credit assignment and by definition performance evaluation is modeled as a \index{Binomial probability distribution} distribution with a \index{Beta probability distribution}Beta probability distribution as a prior probability distribution.
 Heuristic selection has multiple possible outcomes, yielding a index associated with a heuristic.
 Therefore, heuristic selection is modeled as a \index{multionomial}multinomial/\index{categorical}categorical with a dirichlet probability distribution as a prior probability distribution.
-Since the dirichlet-multinomial distributions are the multivariate extensions of the beta-binomial distributions, it show be possible to extend credit assignment to a multivariate version.
+Since the dirichlet-multinomial distributions are the multivariate extensions of the beta-Binomial probability distributions, it show be possible to extend credit assignment to a multivariate version.
 A suggestion then is to learn which credit assignment to select.

### 2022-11-05 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 (chapter6): Review in progress

@@
-\chapter{Bayesian Hyper-Heuristic}
-\label{chap:bhh}
-
-\begin{quote}
-      \textit{
-            ``The result is a posterior distribution which the agent may use as its new prior in the next step.'' - Pedro Domingos, The Master Algorithm: How the Quest for the Ultimate Learning Machine Will Remake Our World.
-      }
-\end{quote}
-
-The above quote was the inspiration for the development of a novel \ac{HH} that uses \index{Bayesian}\textit{Bayesian} probability concepts as a selection mechanism to drive the heuristic selection process.
-Thus far the reader was presented with all of the necessary background information on \acp{ANN} in Chapter \ref{chap:anns}, low-level \index{heuristic}heuristics/\index{Optimiser}optimisers in Chapter \ref{chap:heuristics}, \acp{HH} in Chapter \ref{chap:hhs}  and lastly, \index{probability theory}probability theory in Chapter \ref{chap:probability}.
-These elements form the fundamental components that make up the proposed \Ac{BHH}.
-A detailed specification on the \Ac{BHH} can now be formulated.
-This chapter provides the detail around the theory, concept and implementation of the \Ac{BHH} and explains how it used to train \acp{ANN}.
-It is shown throughout this chapter that the \Ac{BHH} implements a probabilistic optimisation technique that implements and biases a \index{Gaussian Process}\textit{Gaussian process} towards good optimisation and performance.
-The remainder of the chapter is structured as follows:
-
-\begin{itemize}
-      \item \textbf{Section \ref{sec:bhh:overview}} provides a brief overview of the \Ac{BHH} optimiser.
-
-      \item \textbf{Section \ref{sec:bhh:architecture}} presents the general architecture, \Ac{HH} framework and the various components that make up the \index{Optimiser}optimiser.
-
-      \item \textbf{Section \ref{sec:bhh:heuristic_pool}} discusses the collection of low-level \index{heuristic}heuristics, referred to as the \index{heuristic}\textit{heuristic pool} and puts emphasis on the importance of a diverse set of low-level \index{heuristic}heuristics.
-
-      \item \textbf{Section \ref{sec:bhh:entity_pool}} discusses the detail of the \index{Population}population and its \index{entity}entities, with specific detail provided on entity (local) and population (global) state and memory.
-
-      \item \textbf{Section \ref{sec:bhh:initialisation_step}} presents the initialisation strategy in detail.
-
-      \item \textbf{Section \ref{sec:bhh:selection_mechanism}} presents the \index{Bayesian}\textit{Bayesian} probabilistic model that is used as a selection mechanism.
-
-      \item \textbf{Section \ref{sec:bhh:heuristic_entity_selections}} discusses heuristic-entity selections and how these two concepts are utilised together.
-
-      \item \textbf{Section\ref{sec:bhh:model}} discusses the models that can be optimised using the \Ac{BHH}, specifically referring to its application to training \acp{FFNN}.
-
-      \item \textbf{Section \ref{sec:bhh:train_test_datasets}} briefly discussed the role of the train and test datasets during training.
-
-      \item \textbf{Section \ref{sec:bhh:loss_function}} discusses model evaluation and the role of the loss/cost function.
-
-      \item \textbf{Section \ref{sec:bhh:domain_barrier}} discusses the domain barrier that exists between the high-level \ac{BHH} and low-level heuristics in the \index{heuristic pool}heuristic pool.
-
-      \item \textbf{Section \ref{sec:bhh:performance_log}} presents the performance log and discusses performance measurement in more detail.
-
-      \item \textbf{Section \ref{sec:bhh:credit_assignment_strategy}} discussed credit assignment and move acceptance strategies in detail.
+\chapter{Bayesian Hyper-Heuristic}\label{chap:bhh}
+
+\begin{quotation}
+      \noindent ``The result is a posterior distribution, which the agent may use as its new prior in the next step.''
+\end{quotation}
+\begin{flushright}
+      - Pedro Domingos, The Master Algorithm
+\end{flushright}
+
+\noindent
+The above quote was the inspiration for the development of a novel \acf{HH} that uses Bayesian probability concepts as a selection mechanism to drive the heuristic selection process.
+Thus far the reader has been presented with all of the necessary background information on \acp{ANN} (Chapter \ref{chap:anns}), low-level \index{heuristic}heuristics (Chapter \ref{chap:heuristics}), \acp{HH} (Chapter \ref{chap:hhs}) and lastly, probability theory(Chapter \ref{chap:probability}).
+These elements form the fundamental components of the proposed \Acf{BHH}.
+This chapter provides the details around the implementation of the \Ac{BHH} and explains how it used to train \acp{FFNN}.
+The remainder of the chapter is structured as follows.
+
+\begin{itemize}
+      \item \textbf{Section \ref{sec:bhh:overview}} provides a brief overview of the \Acs{BHH}.
+
+      \item \textbf{Section \ref{sec:bhh:architecture}} provides the general architecture and \Ac{HH} framework implemented by the \Acs{BHH}.
+
+      \item \textbf{Section \ref{sec:bhh:heuristic_pool}} presents the \index{heuristic}\textit{heuristic pool}, a collection of low-level \index{heuristic}heuristics.
+Discussions follow on the importance of diversity amoungst heuristics in the \index{heuristic pool}heuristic pool.
+
+      \item \textbf{Section \ref{sec:bhh:entity_pool}} presents details on entity (local) and population (global) memory (state).
+
+      \item \textbf{Section \ref{sec:bhh:heuristic_entity_selections}} presents discussions on heuristic-entity selections.
+
+      \item \textbf{Section \ref{sec:bhh:model}} presents the models that can be optimised using the \Acs{BHH}, specifically referring to the training of \acp{FFNN}.
+
+      \item \textbf{Section \ref{sec:bhh:train_test_datasets}} presents a brief discussion on the role of datasets for training and testing.
+
+      \item \textbf{Section \ref{sec:bhh:loss_function}} presents discussions on model evaluation and the role of the loss function.
+
+      \item \textbf{Section \ref{sec:bhh:domain_barrier}} presents discussions on the domain barrier, an information barrier that exists between the high-level \acs{BHH} and low-level heuristics in the \index{heuristic pool}heuristic pool.
+
+      \item \textbf{Section \ref{sec:bhh:performance_log}} presents detailed discussions on performance measurement. The \textit{performance log}, implemented by the \acs{BHH}, is presented.
+
+      \item \textbf{Section \ref{sec:bhh:credit_assignment_strategy}} presents detailed discussions on credit assignment and move acceptance strategies.
+
+      \item \textbf{Section \ref{sec:bhh:selection_mechanism}} presents the Bayesian probabilistic model that is used as the heuristic selection mechanism.
+
+      \item \textbf{Section \ref{sec:bhh:initialisation_step}} presents the initialisation strategy.
 
@@
 
-      \item The pseudo-code algorithm for the \ac{BHH} is given in \textbf{Section \ref{sec:bhh:algorithm}}.
-
-      \item Finally, a summary of the chapter is provide in \textbf{Section \ref{sec:bhh:summary}}.
-\end{itemize}
-
-\section{Overview}
-\label{sec:bhh:overview}
-
-This section provides an overview of the workings of the \Ac{BHH}. To start the discussion, consider the following analogy:\\
-\\
-\textit{
-      Bob is a teacher at a high school.
-Every year his students perform really well and he wins the prize for best teacher, evaluated by student performance.
-He is able to do this not just because he is a good teacher, but he understands that each student has a learning technique that works best for him/her.
-He exploits this concept by tailoring the teaching process to each students such that the result is an optimum mark for that student and by definition, the whole class.
-Bob knows that it is too timely to get to know each student, so he devises a model that does the allocations for him.
-This model uses a process of observation.
-With each evaluation opportunity he experiments by allocating different learning techniques to different students.
-He evaluates the student for the given opportunity and keeps a log of which learning technique he assigned to the student as well as the outcome.
-With each evaluation opportunity he updates his model by biasing the assignment process such that students generally get assigned learning techniques that yield the best performance for them.
-}\\
-\\
-The key take-out from the analogy above is the concept that Bob can maximise student performance by updating his beliefs, over time, about which learning technique to assign to which (type of) student.
-He does this by biasing selection/assignment towards the best combinations of student, learning technique
-and evaluation opportunity.
-This is the basic nature of the \Ac{BHH}.
-The students are analogous to a population of entities.
-The learning techniques are analogous to heuristics/optimisers.
-Evaluation opportunities are analogous to optimisation problems to be optimised.
-Student performance is analogous to optimisation capability and performance measurement.
-The general goal of the \ac{BHH} can be summarised as aiming to select and managing the appropriate  heuristic/optimiser and update step for each entity, at each optimisation step, while optimising some underlying model, which for this dissertation, is to train \acp{FFNN}.
-
-Formal classification of the \Ac{BHH} is needed.
-Burke et al.~\cite{ref:burke:2010} proposed a classification mechanism that was discussed in detail in Chapter \ref{chap:hhs}.
-The same classification mechanism is used to classify the \ac{BHH}.
-For the first dimension of the classification, the authors propose that the \Ac{BHH} be classified as a \textit{selection} \ac{HH}.
-For the second dimension of the classification proposed, the authors propose that the \Ac{BHH} be classified as utilising \textit{perturbation} low-level heuristics.
-Furthermore, the \ac{BHH} is also classified as a population-based approach that includes meta-heuristics.
-Burke et al.~\cite{ref:burke:2010} further proposed the classification of \acp{HH} according to the source of the feedback used during learning.
-It can thus be said that the \ac{BHH} employs online learning according to this criteria, classifying it as an \textit{adaptive} \ac{HH}.
-A \textit{population-based, selection, meta-hyper-heuristic that utilised perturbation of low-level heuristics and online learning} seems like an mouthful, but technically, that is it's full and formal classification.
-A breakdown and motivation of these classifications is given below:
-
-\begin{itemize}
-      \item \textbf{Population-Based:} The \ac{BHH} follows a population-based approach where a number of different \index{candidate solution}candidate solutions, referred to as \index{entity}\textit{entities} work together to yield a global best solution.
-There is also the concept of a shared global state or memory.
-
-      \item \textbf{Selection:} The \ac{BHH} implements a \index{heuristic}heuristic selection mechanism that selects from a collection of lower level \index{heuristic}heuristics' in a so-called \index{heuristic hool}\textit{heuristic pool}.
-There is also a measure of acceptance criteria through credit assignment strategies.
-
-      \item \textbf{Meta:} Incorporates the classical/analytical gradient-based low level \index{heuristic}heuristics (typically from the \ac{ML} research space) as well as meta-heuristics such as other population-based \index{Meta-Heuristic}meta-heuristics (typically \ac{EC} research space).
-
-      \item \textbf{Hyper-Heuristic:} There exists a domain barrier where the \ac{BHH} searches through the \textit{heuristic space} while lower level heuristics search through the \textit{solution space}.
-
-      \item \textbf{Perturbation of Low-Level Heuristics:} Refers to the iterative optimisation approach followed by the \ac{BHH}.
-The \ac{BHH} considers a number of randomly initialised candidate solutions in the form of entities in a population.
-It is applied in an iterative manner, during the training process.
-It generally employs the two main processes of \acp{HH} with perturbation of heuristics.
-These include a \textit{selection step} that selects from low-level heuristics and applies them to entities/candidate solutions.
-It also includes an \textit{acceptance strategy}.
-The \ac{BHH} maintains entity and population state through update step operations that proxy update steps from different heuristics.
-More details on this concept is given later in Section \ref{sec:bhh:heuristic:proxies}.
-
-      \item \textbf{Online Learning:} Refers to the source of the feedback used during training.
-The \ac{BHH} optimises, at a higher level, the selection and application of the \index{heuristic space}\textit{heuristic space} while low-level heuristics optimise entities' solution to the underlying model, in this case a \ac{FFNN}.
-This happens during training time, yielding the classification of utilising \textit{online} learning.
-\end{itemize}
-
-More detailed consideration of these elements are required. The following sections break down the \Ac{BHH} into its various parts, starting with a discussion on the high-level architecture next.
-
-\index{Architecture}
-\section{Architecture}
-\label{sec:bhh:architecture}
-
-This section aims to present the reader with all the high level components in the architecture of the \Ac{BHH}.
+      \item \textbf{Section \ref{sec:bhh:algorithm}} provides the pseudo-code algorithm for the \ac{BHH}.
+
+      \item \textbf{Section \ref{sec:bhh:summary}} provides a brief summary of the chapter.
+\end{itemize}
+
+\section{Overview}\label{sec:bhh:overview}
+
+This section provides an overview of the workings of the \Acf{BHH}.
+The general concept of the \acs{BHH} can be summarised as follows.
+The \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic, from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and \acs{FFNN} training process.
+The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process.
+These probabilities are then used as heuristic selection probabilities in the next step of the training process.
+
+Formal classification of the \Acs{BHH} is needed.
+Chapter \ref{chap:hhs} presented the reader with a proposed classification scheme for \acp{HH} by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}.
+According to the aforementioned classification scheme, the \Acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.
+A breakdown of the classification is given as follows.
+
+\begin{itemize}
+      \item \textbf{Population-Based:} The \ac{BHH} implements a population-based approach, where a collection of different candidate solutions, referred to as \textit{entities}, work together to yield a global best solution.
+
+      \item \textbf{Meta-Hyper-Heuristic:} There exists a domain barrier, where the \ac{BHH} searches through the \textit{heuristic space}, using only \index{heuristic}heuristic performance information, while lower level heuristics search through the \textit{solution space} using information from the search domain itself.
+Furthermore, the \index{heuristic pool}heuristic pool implemented by the \acs{BHH} supports both gradient-based low level \index{heuristic}heuristics, as well as meta-heuristics.
+
+      \item \textbf{Selection and Perturbation of Low-Level Heuristics:} The \acs{BHH} implements a \index{heuristic}heuristic selection mechanism that selects from a collection of lower level \index{heuristic}heuristics, called a \index{heuristic pool}\textit{heuristic pool}.
+Selection is biased towards good performing heuristics.
+A credit assignment strategy is used to \textit{reward} good heuristic performance.
+The \acs{BHH} maintains entity and population state through operations that \textit{proxy} update steps from different heuristics (perturbation), as is required.
+These proxy operations ensure that heuristic requirements are satisfied even when different heuristics are used for different entities throughout the training process.
+
+      \item \textbf{Online Learning:} The \acs{BHH} applies learning, at specified intervals, throughout the \acs{FFNN} training process.
+\end{itemize}
+
+\noindent
+The following sections presents the reader with more detail on the implementation of the \acs{BHH}.
+Discussions lead with the \acs{BHH} architecture and general \acs{HH} framework in the following section.
+
+\section{Architecture}\label{sec:bhh:architecture}
+
+This section aims to present the reader with all the high level components in the architecture of the \Acs{BHH}.
 Burke et al.~\cite{ref:burke:2010} proposed an initial framework for \acp{HH} and Grobler~\cite{ref:grobler:2015} further proposed a framework for a heterogeneous meta-\ac{HH}.
-These frameworks have been adapted for the implementation of the \Ac{BHH}.
-An illustration of the high-level architecture of the \Ac{BHH} is given in Figure \ref{fig:bhh_architecture} below.
-
-\begin{figure}[H]
+The aforementioned frameworks are adapted for the implementation of the \Acs{BHH}.
+An illustration of the high-level architecture of the \Acs{BHH} is given in Figure \ref{fig:bhh_architecture}.
+
+\begin{figure}[htbp]
       \centering
-      \includegraphics[width=1.0\textwidth]{bhh_architecture.png}
-      \caption[The \index{Bayesian Hyper-Heuristics}Bayesian Hyper-Heuristic Architecture]{An illustration of
-            the architecture and high level components of the \index{Bayesian Hyper-Heuristics}Bayesian Hyper-Heuristic.}
+      \includegraphics[width=1.0\textwidth]{bhh_architecture.pdf}
+      \caption[An illustration of
+            the architecture and high level components of the \acf{BHH}.]{An illustration of
+            the architecture and high level components of the \acf{BHH}.}
       \label{fig:bhh_architecture}
@@
 
-At a high level, the architecture presented in Figure \ref{fig:bhh_architecture} above, presents the following main components:
-
-\begin{itemize}
-      \item \textbf{Heuristic Pool}: Contains a collection of low-level \index{heuristic}heuristics/\index{optimiser}optimisers.
-This is the \index{heuristic space}\textit{heuristic} space.
-Each heuristic has a proxy that is used to relay heuristic state update operations.
-
-      \item \textbf{Entity Pool}: A collection of \index{entity}entities in a \index{population}population.
-These entities represent candidate solutions to the model.
-Each entity has its own state, but there is also a shared global population state.
-
-      \item \textbf{Initialisation Step}: This is the execution of some initialisation strategy that determines how the entities in the entity pool (population) and the heuristics in the heuristic pool are initialised.
-
-      \item \textbf{Selection Mechanism}: This is the implementation of the selection mechanism of selection \acp{HH}.
-In the case of the \ac{BHH}, the selection mechanism is a Bayesian probabilistic model.
-
-      \item \textbf{Heuristic-Entity Selections}: This is the results of the selection mechanism.
-Heuristics are sampled/selected for each entity.
-Each entity's state will thus be manipulated by that particular heuristic's proxy methods.
-
-      \item \textbf{Model}: The \index{model}model to be optimised.
-This forms the problem domain.
-In the case of this dissertation, the model is a \ac{FFNN}.Technically the model here simply refers to the architectural structure of the model, while entities represent that candidate solution (weights) to the model.
+\noindent
+With reference to Figure \ref{fig:bhh_architecture}, the components are briefly given below in the order of information flow during the \acs{FFNN} training process steps.
+
+\begin{itemize}
+      \item \textbf{Initialisation Step}: The initialisation step refers to the initialisation strategy implemented by the \acs{BHH}.
+
+      \item \textbf{Heuristic Pool}: The \index{heuristic pool}heuristic pool contains a collection of low-level \index{heuristic}heuristics.
+
+      \item \textbf{Entity Pool}: The \index{entity pool}entity pool represents a collection of candidate solutions for the underlying \acs{FFNN}, referred to as entities in a population.
+
+      \item \textbf{Selection Mechanism}: The selection mechanism refers to the Bayesian probabilistic model.
+
+      \item \textbf{Heuristic-Entity Selections}: Every entity in the \index{entity pool}entity pool gets assigned a selected heuristic.
 
@@
 
-      \item \textbf{Loss/Cost Function}: The loss/cost function is the metric  by which the model is evaluated.
-In the case of supervised learning, the loss/cost function is a measure of distance between predicted output and the ground truth.
-
-      \item \textbf{Domain Barrier}: A constraint on information flow, prohibiting high level components in the \index{heuristic space}\textit{heuristic} space from interacting and relaying information related to the \index{solution space}\textit{solution} space.
+      \item \textbf{Model}: The underlying \acs{FFNN} to be trained.
+
+      \item \textbf{Low-Level Heuristics Update Step}: The low-level heuristics' update step as it applies to its allocated entity.
+
+      \item \textbf{Loss Function}: In supervised learning, the loss function is a measure of distance between predicted output and the ground truth, and is the mechanism used to evaluate the model's performance.
+
+      \item \textbf{Domain Barrier}: The domain barrier is the logical separation of information available in the heuristic space and the solution space.
+The \acs{BHH} searches in the heuristic space, while low-level heuristics search in the solution space.
 
@@
 
-      \item \textbf{Credit Assignment Strategy}: Implements a specific strategy to determine if the performance of an entity-heuristic combination is better than others or not.
-
-      \item \textbf{Update Step}: The high level heuristic update step. This involves the mechanism by with the \ac{BHH} is optimised.
-\end{itemize}
-
-The above components are not described in enough detailed to properly illustrate their role in the \Ac{BHH}.
-To ensure proper clarity is given to each of these elements, a detailed discussion on each of these elements are presented next.
-
-\index{Heuristic Pool}
-\section{Heuristic Pool}
-\label{sec:bhh:heuristic_pool}
-
-This section discusses the concept of the heuristic pool, as implemented by the \ac{BHH}.
-Generally speaking, they heuristic pool is just a collection of low-level heuristics and make up the set of possible heuristics to select from.
-This is referred to as \text{heuristic space}.
-Importantly, since \acp{HH} optimise in heuristic space, it is from these lower-level heuristics that the \ac{BHH} must select and apply.
-The heuristic pool can then be defined in terms of size and/or heuristics that are included in the pool.
-These two aspects pose very important design choices.
-Both of these concepts can be empirically tested, however, one could argue the choice of design.
-Fundamentally, these design choices are about diversity.
-A brief discussion is given next on the trade-offs between exploration, exploitation and capability.
-
-\index{Exploration}
-\index{Exploitation}
-\subsection{Diversity: Exploration, Exploitation and Capability}
-\label{sec:bhh:heuristic_pool:diversity}
-
-As with all \acp{HH}, the heuristics to be included in the heuristic pool is of great importance and should be carefully decided upon.
-A heuristic's eligibility for inclusion is determined by the following factors:
-
-\begin{itemize}
-      \item \textbf{Capability}: Certain heuristics are only capable of solving or optimising for certain problem types and domains.
-Examples include continuous vs.
-discrete, differentiable vs.
-non-differentiable or static vs.
-dynamic problems.
-
-      \item \textbf{Exploration and Exploitation Trade-off}: Some heuristics explore or exploit more than others.
-This could be due to the nature of the implementation or due to some hyper-parameter such as a learning rate.
-\end{itemize}
-
-An argument for diversity must thus be made.
-One of the benefits of \acp{HH} in general is that it will learn which heuristics to apply and when.
-The trade-off between exploration and exploitation should thus be outsourced to the \ac{BHH} itself.
-By including a diverse set of heuristics, based on the criteria mentioned above, the \ac{BHH} will learn to select and apply the appropriate heuristic at the appropriate time throughout the training process, naturally balancing a trade-off between exploration and exploitation.
-Heuristics that initially explore a lot should be selected when exploration is needed and heuristics that exploit a lot should be selected accordingly.
-
-Notice however that diversity can not be achieved by simply including many different heuristics.
-The \ac{BHH} is still constraint by heuristic pool size.
-Consider that for every heuristic that is included, the demand for samples size required to learn with statistical certainty exponentially increases.
-Not only does a large heuristic pool drastically complicate the learning that is required by the \ac{BHH}, but it also drastically complicates the process of maintaining state.
-The next section provides the concept of heuristic update step proxies, an important component of the \ac{BHH}.
-
-\index{Proxies}
-\subsection{Proxies}
-\label{sec:bhh:heuristic:proxies}
-
-The concept of proxies arise from the sparsity of state as maintained by different heuristics.
-Since heuristics maintain different states, there is an uncertainty of state transition when switching between heuristics.
-Consider an example where the heuristic pool consists of just two heuristics.
-One heuristic is a gradient-based heuristic that maintains momentum such as \ac{Adam}.
-The other is a meta-heuristic that does not require a gradient at all such as \ac{PSO}.
-Both these heuristics track different parameters in their state.
-For \ac{Adam}, the expected gradient mean and variance is maintained, while the \ac{PSO} maintains record of the gbest and pbest solutions all of entities.
-A solution to this is to proxy heuristic state update operations.
-This allows us to maintain state in two parts:
-
-\begin{itemize}
-      \item \textbf{Primary State}: This refers to state the is originally maintained by a heuristic. The selected heuristic simply applies the normal state update operations to its state.
-
-      \item \textbf{Proxied State}: This refers to state that is not directly maintained by the current selected heuristic, but can be updated by outsourcing the required state update operation to another heuristic.
-\end{itemize}
-
-Effectively this means that both primary and proxied state elements must be maintained together.
-Since entities represent candidate solutions, which are a form of state, entities are ideal components to store these state parameters.
-Thus, entities are extended to include the primary state elements of all the underlying low-level heuristics as well as the candidate solution (weights) for the model.
+      \item \textbf{Credit Assignment Strategy}: The strategy used to assign credit to heuristics for their performance.
+
+      \item \textbf{Update Step}: The high-level heuristic update step as implemented by the \acs{BHH}.
+\end{itemize}
+
+\noindent
+Each of the components in Figure \ref{fig:bhh_architecture} is discussed in detail in the following sections.
+
+\index{heuristic pool}
+\section{Heuristic Pool}\label{sec:bhh:heuristic_pool}
+
+Generally speaking, the \index{heuristic pool}heuristic pool is a collection of low-level heuristics under consideration by the \acs{BHH}.
+The \index{heuristic pool}heuristic pool contains the set of low-level \index{heuristic}heuristics that, together with their performance information, make up the \text{heuristic space}.
+Importantly, the \acs{BHH} searches in \index{heuristic}heuristic space.
+The \index{heuristic pool}heuristic pool is defined in terms of the diversity of heuristics, as well as the amount of heuristics in the \index{heuristic pool}heuristic pool.
+Each of these are discussed in the following sections.
+
+\subsection{Heuristic Diversity}\label{sec:bhh:heuristic_pool:diversity}
+
+A \index{heuristic}heuristic's eligibility for inclusion in the \index{heuristic}heuristic pool, is determined by its ability to solve to underlying problem and its search behaviour and characteristics.
+The \index{heuristic pool}heuristic pool should contain a variety of different heuristics that have different search behaviours, so that a trade-off can be made by between exploration and exploitation of solutions, as is required during the training process.
+Heuristics that explore a lot, should be selected when exploration is needed, and heuristics that exploit a lot should be selected accordingly.
+The trade-off between exploration and exploitation is managed by the high-level heuristic.
+The \acs{BHH} will learn to select and apply the appropriate heuristic, at the appropriate points, throughout the training process.
+In doing so, a balance is achieved between exploration and exploitation.
+
+\subsection{Heuristic Pool Size}\label{sec:bhh:heuristic_pool:pool_size}
+
+Another design decision in the heuristic pool is heuristic pool size.
+Since the \acs{BHH} is a \textit{learning} \acs{HH}, every heuristic that is included in the heuristic pool increases the requirement of more statistical evidence of heuristic performance.
+Not only does a large \index{heuristic pool}heuristic pool drastically complicate the learning process that is required by the \ac{BHH}, but it also drastically complicates the process of maintaining \textit{state}.
+State is the term used to describe data that is relevant to the training process, and is maintained between training steps.
+An example of \textit{local} state is an entity's position, while an example of \textit{global} state is the global best solution found thus far.
+The following section presents the concept of \textit{proxies} and their role in maintaining state.
+
+\subsection{Proxies}\label{sec:bhh:heuristic:proxies}
+
+The concept of proxies arise from the sparsity of state as maintained by different \index{heuristic}heuristics.
+Since \index{heuristic}heuristics maintain (possibly) different states, there is an uncertainty of state transition when switching between \index{heuristic}heuristics.
+Consider an example where the \index{heuristic pool}heuristic pool consists of just two \index{heuristic}heuristics.
+One heuristic is a gradient-based heuristic that maintains momentum such as \acs{Adam}.
+The other is a \index{meta-heuristic}meta-heuristic that does not require a gradient, such as \acs{PSO}.
+Both these \index{heuristic}heuristics track different parameters in their state.
+For \acs{Adam}, the expected gradient mean and variance is maintained, while the \ac{PSO} maintains record of the gbest and pbest solutions of all of entities.
+A solution to state indifference, is to proxy heuristic state update operations.
+State is then maintained in two parts:
+
+\begin{itemize}
+      \item \textbf{Primary State}: Refers to the state that is originally maintained by a heuristic. The selected heuristic simply applies the normal state update operations to its state.
+
+      \item \textbf{Proxied State}: Refers to the state that is not directly maintained by the heuristic, but can be updated by outsourcing the required state update operation to another heuristic.
+\end{itemize}
+
+\noindent
+Primary and proxied state parameters must be maintained together.
+Since entities represent candidate solutions, which are forms of state, entities are ideal candidates to store and maintain these state parameters.
+Entities are extended to include the primary state elements of \textit{all} the underlying low-level heuristics, as well as the candidate solution (weights) for the \acs{FFNN}.
 At each heuristic-entity application step, all state elements per entity are updated either by primary method or by proxied method.
-The \ac{BHH} thus incorporates a state update operation proxy mapping as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.
+The \ac{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.
 
@@
       \centering
-      \caption{State update operation proxy mapping example.}
+      \caption{An example of mapping of proxied state update operation maintained by the \acs{BHH}.}
       \label{tab:bhh:heuristic_pool:proxy_mapping_example}%
@@
 
-From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when heuristic A is selected, it will outsource state update operations from heuristic B, for state parameter 2.
-Heuristic B will outsource from heuristic A, for state parameter 3.
-Finally, heuristic C will outsource from heuristic A and B, for state parameters 2 and 3 respectively.
-In this way, all heuristics maintain all the state parameters.
-
-Notice however that this is a simple concept in principle, but requires detailed decomposition of the heuristics included in the heuristic pool.
-Overlapping and unique state parameters must be identified so that a proxy mapping such as the one given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} can be constructed.
+\noindent
+From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when \index{heuristic}heuristic A is selected, it will outsource state update operations from \index{heuristic}heuristic B, for state parameter 2.
+Heuristic B will outsource from \index{heuristic}heuristic A, for state parameter 3.
+Finally, \index{heuristic}heuristic C will outsource from \index{heuristic}heuristic A and B, for state parameters 2 and 3 respectively.
+In this way, all \index{heuristic}heuristics maintain all the state parameters.
+
+Proxied state update operations is a simple concept in principle, but requires detailed decomposition of the \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool.
+Overlapping and unique state parameters must be identified so that a proxy mapping, such as the one given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, can be constructed.
 A suggestion to simplify this process is to borrow concepts from the equations of motion from physics.
 These include \textit{position}, \textit{velocity}, \textit{acceleration} and \textit{momentum}.
-Expressing heuristic update steps according to these parameters drastically simplify the process.
-However, it is possible that heuristics implement unique state parameters that do not overlap, these have to be catered for in the proxy mapping.
-
-These state parameters and update operations should not be considered in isolation.
-An example of this is position and velocity.
-Consider for example heuristics such as \acl{DE} and \aclp{GA}.
-These heuristics recombine entities.
-In this case, the concept of an equation of motion does not entirely make sense, since the displacement of its position is not a result of maintaining velocity or momentum, but rather by pure displacement through recombination.
-In this particular case, a solution to this is to apply the recombination operation to all secondary state parameters as well or to nullify secondary state parameters.
-Unfortunately there is no general solution and each heuristic must be carefully considered.
-The \ac{BHH} incorporates both of these approaches.
-The next section provides the reader with details around the entity pool.
-
-\index{Entity Pool}
-\section{Entity Pool}
-\label{sec:bhh:entity_pool}
-
-This section presents the details around the \index{entity pool}\textit{entity pool}.
-The \index{entity pool}entity pool refers to a collection of so-called individual \index{entity}\textit{entities}.
+Expressing \index{heuristic}heuristic update steps according to these parameters drastically simplify the process.
+However, it is possible that \index{heuristic}heuristics implement unique state parameters that do not overlap, these have to be catered for in the proxy mapping.
+
+State parameters and update operations should not be considered in isolation.
+An example is \textit{position} and \textit{velocity}.
+Consider, for example, \index{heuristic}heuristics such as \acf{DE} and \acfp{GA}.
+These \index{heuristic}heuristics recombine entities.
+In the aforementioned case, the concept of an equation of motion does not entirely make sense, since the displacement of its position is not a result of maintaining velocity or momentum, but rather by displacement through recombination.
+In this particular case, a solution is to apply the recombination operation to \textit{all} applicable state parameters as well, or to nullify the necessary state parameters.
+Unfortunately there is no general, automated solution to formulate these heuristic state overlaps.
+Each \index{heuristic}heuristic must be carefully considered.
+More details on the \index{entity pool}entity pool and entity state are presented in the following section.
+
+\index{entity pool}
+\section{Entity Pool}\label{sec:bhh:entity_pool}
+
+The \index{entity pool}entity pool refers to a collection of \textit{entities} that each represent a candidate solution to the underlying \acs{FFNN} being trained.
+The entities contain information of the solution space.
 A common naming convention for such a collection is a \textit{population} of entities.
-Similar to the heuristic pool that was described in Section \ref{sec:bhh:heuristic_pool} above, the entity pool size is an important design choice.
-The correct population size is thus a hyper-parameter that can be empirically evaluated.
-
-The entity pool maintains two different types of state. These include entity (local) and population (global) state. Each of these are discussed in more detail next.
-
-\index{Entity State}
-\subsection{Entity State}
-\label{sec:bhh:entity_pool:entity_state}
-
-\index{entity}Entities represent \index{candidate solution}candidate solutions to the \index{model}model's trainable parameters (weights) and other heuristic-specific state parameters as was just discussed above in Section \ref{sec:bhh:heuristic:proxies}.
+The \acs{BHH} is a population-based \acs{HH} and as such, the \index{entity pool}entity pool size or population size is an important design choice.
+The population size is defined as a hyper-parameter of the \acs{BHH} and can be empirically evaluated.
+
+The \index{entity pool}entity pool maintains two different types of state. These include entity (local) and population (global) state. Each of these are discussed in more detail next.
+
+\subsection{Entity State}\label{sec:bhh:entity_pool:entity_state}
+
+Entities represent candidate solutions to the model's trainable parameters (weights) and other heuristic-specific state parameters, as was discussed in Section \ref{sec:bhh:heuristic:proxies}.
 It can be said that entities implement \textit{local} state.
-It was mentioned that these \index{entity}entities can be treated as physical \index{particle}\textit{particles} in a hyper-dimensional physical environment.
-This means that these \index{entity}entities model concepts from physics.
-For example, the candidate solution is represented as the \index{entity}entity's \textit{position} and an \index{entity}entity's velocity and acceleration, is analogous to the gradient and momentum of an \index{entity}entity respectfully.
-Examples of \index{Entity State}entity state parameters as derived from various low-level heuristics is given as follows:
+It was mentioned that these entities can be treated as physical \index{particle}\textit{particles} in a hyper-dimensional search environment.
+Entities model concepts from physics.
+For example, the candidate solution is represented as the entity's position, and an entity's velocity and acceleration is analogous to the gradient and momentum of the entity respectfully.
+Examples of \index{Entity State}entity state parameters, as derived from various low-level heuristics, is given as follows.
 
@@
 
-      \item \textbf{velocity}: Directly implemented by heuristics such as \acp{PSO} can be derived proportionally from the gradient for gradient-based heuristics such as \ac{Momentum}.
-
-      \item \textbf{gradient}: The last know gradient as derived from gradient-based heuristics.
+      \item \textbf{velocity}: Directly implemented by heuristics such as \acp{PSO} and is analogous to the gradient for gradient-based heuristics such as \ac{Momentum}.
+
+      \item \textbf{gradient}: The last known gradient, as derived from gradient-based heuristics.
 
@@
 
-      \item \textbf{sum of the gradients squared}: As required and maintained by heuristics such as \ac{Adagrad}.
-
-      \item \textbf{expected position delta variance}: As required and maintained by heuristics such as \ac{Adadelta}.
-
-      \item \textbf{expected gradient mean}: As required and maintained by heuristics such as \ac{Momentum}, \ac{NAG} and \ac{Adam}.
-
-      \item \textbf{expected gradient variance}: As required and maintained by heuristics such as \ac{RMSProp}, \ac{Adadelta} and \ac{Adam}.
-
-      \item \textbf{personal best position}: Parameter that tracks that best known position by the entity thus far. As required and maintained by heuristics such as \ac{PSO}.
-
-      \item \textbf{personal best loss}: Parameter that tracks that best known loss by the entity thus far. As required and maintained by heuristics such as \ac{PSO}.
-
-      \item \textbf{loss}: General parameter that tracks the loss as achieved by the the entity throughout training.
-\end{itemize}
-
-From the list above it should become clear that entity state becomes increasingly complicated as the number of distinct heuristics included in the heuristic pool increases.
-Consider next the global state that is maintained.
-
-\index{Population State}
-\subsection{Population State}
-\label{sec:bhh:entity_pool:population_state}
-
-The \index{Population State}\textit{population state} refers to a collection of parameters that are shared between the \index{entity}entities in the population.
-This state is also referred to as \index{global state}\textit{global} state and represents the entity pool's memory of the population.
-The \index{population state}population state generally contains state parameters that are of importance to multiple heuristics and usually track the state of the population as a whole and not individual heuristic states.
-Some examples of population state that can arise from different heuristics is given below:
-
-\begin{itemize}
-      \item \textbf{\textit{entities}}: Naturally, the population state contains the list of entities in the population.
-List size determined by \index{Population Size}population size.
-Naturally this list contains multiple entities as with population based approaches such as \acp{PSO} and \acp{GA}.
-
-      \item \textbf{\textit{ibest}} and \textbf{\textit{ibest loss}}: Refers to the best position and loss achieved by the population for the current iteration/step.
+      \item \textbf{sum of the gradients squared}: As required and maintained by heuristics such as \acs{Adagrad}.
+
+      \item \textbf{expected position delta variance}: As required and maintained by heuristics such as \acs{Adadelta}.
+
+      \item \textbf{expected gradient mean}: As required and maintained by heuristics such as \acs{Momentum}, \acs{NAG} and \acs{Adam}.
+
+      \item \textbf{expected gradient variance}: As required and maintained by heuristics such as \acs{RMSProp}, \acs{Adadelta} and \acs{Adam}.
+
+      \item \textbf{personal best position}: Parameter that tracks that best known position by the entity thus far. As required and maintained by heuristics such as \acs{PSO}.
+
+      \item \textbf{personal best loss}: Parameter that tracks that best known loss by the entity thus far. As required and maintained by heuristics such as \acs{PSO}.
+
+      \item \textbf{loss}: Parameter that tracks the loss as achieved by the the entity throughout training.
+\end{itemize}
+
+\noindent
+From the list above, it should be clear that entity state becomes increasingly complicated as the number of distinct \index{heuristic}heuristics, included in the \index{heuristic pool}heuristic pool, increases.
+
+\subsection{Population State}\label{sec:bhh:entity_pool:population_state}
+
+The population state refers to a collection of parameters that are shared between the entities in the population.
+Population state is also referred to as \textit{global} state and represents the population's memory.
+The population state generally contains state parameters that are of importance to multiple \index{heuristic}heuristics, and usually tracks the state of the population and not individual heuristic.
+Some examples of population state that can arise from different \index{heuristic}heuristics is given below:
+
+\begin{itemize}
+      \item \textbf{entities}: Naturally, the population state contains the list of entities in the population.
+
+      \item \textbf{ibest} and \textbf{ibest loss}: Refers to the best position and loss achieved by the population for the current iteration/step.
 This parameter is introduced by the \ac{BHH} itself through the requirements of the \textit{ibest} credit assignment strategy.
 
-      \item \textbf{\textit{rbest}} and \textbf{\textit{rbest loss}}: Refers to the best position and loss achieved by the population for the current replay buffer/window size.
+      \item \textbf{rbest} and \textbf{rbest loss}: Refers to the best position and loss achieved by the population for the current replay buffer/window size.
 This parameter is introduced by the \ac{BHH} itself through the requirements of the \textit{rbest} credit assignment strategy.
 
-      \item \textbf{\textit{gbest}} and \textbf{\textit{gbest loss}}: Refers to the overall/global best position and loss achieved by the population for the entire training process.
-This parameter is introduced by heuristics such as \acp{PSO} and is also introduced by the \ac{BHH} itself through the requirements of the \textit{gbest} credit assignment strategy.
-\end{itemize}
-
-The reader was now introduced to both the heuristic pool and entity pool.
-The next section considers how the \ac{BHH} is initialised and makes specific reference to how these two pools of elements are initialised.
+      \item \textbf{gbest} and \textbf{gbest loss}: Refers to the overall/global best position and loss achieved by the population for the entire training process.
+This parameter is introduced by heuristics such as \acp{PSO}, and is also introduced by the \ac{BHH} itself through the requirements of the \textit{gbest} credit assignment strategy.
+\end{itemize}
+
+\noindent
+Entities in the entity pool are each assigned an associated \index{heuristic}heuristic. The following section provides details around the heuristic-entity selection process.
 
@@
 
-The \ac{BHH} selects from the heuristic pool a low-level heuristic to be applied to an entity.
+The \ac{BHH} selects from the \index{heuristic pool}heuristic pool a low-level heuristic to be applied to an entity.
 The outcome of this selection process is a table that tracks which heuristic has been selected for which entity.
@@
 
-The \index{Model}model refers to the target \index{model}model to be optimised and is usually expressed as a complex mathematical function.
+The \index{Model}model refers to the target model to be optimised and is usually expressed as a complex mathematical function.
 For this dissertation, the authors focused specifically on shallow \acp{FFNN} (only one hidden layer).
@@
 
-\begin{figure}[H]
+\begin{figure}[htbp]
       \centering
@@
       \item $I$: Denote the maximum number of instances in the replay window.
-      \item $J$: Denote the entity pool (population) size.
-      \item $K$: Denote the heuristic pool size.
+      \item $J$: Denote the \index{entity pool}entity pool (population) size.
+      \item $K$: Denote the \index{heuristic pool}heuristic pool size.
       \item $L$: Denote the number of credit assignment output classes. Since the output of credit assignment is boolean, $L = 2$.
@@
 Heuristic selection probabilities are sampled from this distribution.
-      \item $\phi \vert \beta \sim Dir(\beta; K)^{J}$: Denote the entity-heuristic probability distribution, implementing a Dirichlet probability distribution parameterised by $\beta$ and $K$ for each entity in the entity pool with population size $J$.
+      \item $\phi \vert \beta \sim Dir(\beta; K)^{J}$: Denote the entity-heuristic probability distribution, implementing a Dirichlet probability distribution parameterised by $\beta$ and $K$ for each entity in the \index{entity pool}entity pool with population size $J$.
 Entity-heuristic probabilities are sampled from this distribution.
@@
 
-      \item $H \vert \theta \sim Mult(\theta; I, K)$: Denote the distribution of heuristics (event $H$), implementing a Multinomial distribution, parameterised by the sampled heuristic selection probability $\theta$, the heuristic pool size $K$ and maximum number of instances $I$.
-      \item $E \vert \phi \sim Mult(\phi; I, K)^{J}$: Denote the distribution of entity-heuristic combinations (event $E$), implementing a Multinomial distribution, parameterised by the sampled entity-heuristic selection probability $\phi$, the heuristic pool size $K$ and maximum number of instances $I$, for each entity in $J$.
+      \item $H \vert \theta \sim Mult(\theta; I, K)$: Denote the distribution of heuristics (event $H$), implementing a Multinomial distribution, parameterised by the sampled heuristic selection probability $\theta$, the \index{heuristic pool}heuristic pool size $K$ and maximum number of instances $I$.
+      \item $E \vert \phi \sim Mult(\phi; I, K)^{J}$: Denote the distribution of entity-heuristic combinations (event $E$), implementing a Multinomial distribution, parameterised by the sampled entity-heuristic selection probability $\phi$, the \index{heuristic pool}heuristic pool size $K$ and maximum number of instances $I$, for each entity in $J$.
       \item $C \vert \psi \sim Bin(\psi, I)$: Denote the distribution of credit-heuristic combinations (event $C$), implementing a\index{Binomial probability distribution}Binomial probability distribution, parameterised by the sampled credit-heuristic selection probability $\psi$ and the maximum number of instances $I$.
@@
 
-This section sheds light into the initialisation of the \ac{BHH} and how it applies to the heuristic and entity pools.
-Since the heuristic pool is a collection of stateless heuristic proxy operations, there is no explicit initialisation that is applied to the heuristic pool itself.
-On the contrary, the entity pool is stateful and maintain candidate solutions.
+This section sheds light into the initialisation of the \ac{BHH} and how it applies to the heuristic and \index{entity pool}entity pools.
+Since the \index{heuristic pool}heuristic pool is a collection of stateless heuristic proxy operations, there is no explicit initialisation that is applied to the \index{heuristic pool}heuristic pool itself.
+On the contrary, the \index{entity pool}entity pool is stateful and maintain candidate solutions.
 Chapter \ref{chap:anns} presented various initialisation strategies to randomly place candidate solutions in the solution space.
@@
 
-Section \ref{sec:bhh:heuristic_pool} provided the reader with the context and detail of the heuristic pool as it is included in the architecture of the \ac{BHH}.
+Section \ref{sec:bhh:heuristic_pool} provided the reader with the context and detail of the \index{heuristic pool}heuristic pool as it is included in the architecture of the \ac{BHH}.
 A detailed discussion was given around the importance of diversity and balancing exploration and exploitation capabilities.
-The heuristic pool hyper-parameter refers to the heuristic-pool configuration that is used.
+The \index{heuristic pool}heuristic pool hyper-parameter refers to the heuristic-pool configuration that is used.
 This configuration should account for the following factors.
@@
 \begin{itemize}
-      \item The type of low-level heuristics to include in the heuristic pool. This dissertation investigates two main groups including gradient-based and meta-heuristics.
+      \item The type of low-level heuristics to include in the \index{heuristic pool}heuristic pool. This dissertation investigates two main groups including gradient-based and meta-heuristics.
       \item The low-level heuristic's hyper-parameters. At a lower-level, each of these heuristics have their own set of hyper-parameters.
-      \item The heuristic pool size. This refers to the number of heuristics in the heuristic pool.
+      \item The \index{heuristic pool}heuristic pool size. This refers to the number of heuristics in the \index{heuristic pool}heuristic pool.
 \end{itemize}
@@
 Take note that it has not been established yet if this is to the benefit or detriment of \ac{BHH}.
-These configurations increase the heuristic pool size and could also counteract eachother.
+These configurations increase the \index{heuristic pool}heuristic pool size and could also counteract eachother.
 It is thus still important to include relevant heuristics that is appropriate to the underlying problem being solved.
@@
 
-\index{Population Size}
 \subsection{Population Size}
@@
 
-\index{Population Size}\textit{Population size} refers to the number of \index{entity}entities included in the \index{Entity Pool}entity pool/\index{Population}population.
-The exact \index{Population Size}population size to use is to be determined empirically.
+\textit{Population size} refers to the number of entities included in the \index{entity pool}entity pool/population.
+The exact population size to use is to be determined empirically.
 Naturely, an assumption is made that a larger population could lead to better results, assuming that entities are initialised to be spread uniformly across the solution search space.
@@
 This means that a set of default low-level parameters must be allocated specifically for these proxies.
-Consider a scenario where two instances of \ac{Adam} is included in the heuristic pool.
+Consider a scenario where two instances of \ac{Adam} is included in the \index{heuristic pool}heuristic pool.
 Each has its own set of hyper-parameters that (should) differ from each other.

### 2022-11-05 dissertation/chapters/05-probability.tex
🚧 (chapter6): Save point

@@
 In 1718,~\citeauthor{ref:demoivre:1718}~\cite{ref:demoivre:1718} published the \textit{Doctrine of of Chance}; a book that is widely seen as the first published book on probability theory.
-In 1763, Thomas Bayes~\cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of Bayes' Theorem was introduced.
+In 1763, Thomas Bayes~\cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of \index{Bayes' Theorem}Bayes' Theorem was introduced.
 
@@
 
-      \item \textbf{Section \ref{sec:probability:bayes_theorem}} introduces Bayes' Theorem, the fundamental theorem upon which the \acs{BHH} is built.
+      \item \textbf{Section \ref{sec:probability:bayes_theorem}} introduces \index{Bayes' Theorem}Bayes' Theorem, the fundamental theorem upon which the \acs{BHH} is built.
 
@@
 
+\index{Bayes Theorem}
 \section{Bayes' Theorem}\label{sec:probability:bayes_theorem}
 
-Bayes' Theorem, named after Thomas Bayes, describes the probability of an event $A$, based on prior knowledge of conditions that might be related to $A$~\cite{ref:zalta:2015}.
+\index{Bayes' Theorem}Bayes' Theorem, named after Thomas Bayes, describes the probability of an event $A$, based on prior knowledge of conditions that might be related to $A$~\cite{ref:zalta:2015}.
 In order to derive the formal theorem and proof, first consider Definition \ref{def:probability:bayes_theorem:partition} below~\cite{ref:zalta:2015}.
@@
 
+\index{Bayes Theorem}
 \begin{theorem}[\textbf{Bayes' Theorem}]
@@
 \noindent
-One of the many applications of Bayes' Theorem is to do statistical inference.
-Bayes' Theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
+One of the many applications of \index{Bayes' Theorem}Bayes' Theorem is to do statistical inference.
+\index{Bayes' Theorem}Bayes' Theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
 
@@
 \noindent
-By Bayes' Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.
+By \index{Bayes' Theorem}Bayes' Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.
 
@@
 \noindent
-By Bayes' Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.
+By \index{Bayes' Theorem}Bayes' Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.
 
@@
 These include the \textit{frequentist} and the \textit{Bayesian} view of statistics.
-Naturally, Bayesian statistics is based on Bayes' Theorem as was presented in Section \ref{sec:probability:bayes_theorem}.
+Naturally, Bayesian statistics is based on \index{Bayes' Theorem}Bayes' Theorem as was presented in Section \ref{sec:probability:bayes_theorem}.
 Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event, and the conditions under which the event happens~\cite{ref:hackenberger:2019}.
@@
 \noindent
-Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$, according to Bayes' Theorem, is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.
+Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$, according to \index{Bayes' Theorem}Bayes' Theorem, is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.
 

### 2022-11-05 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 (chapter6): Save point

@@
 
-      \item \textbf{Section \ref{sec:bhh:heuristic_entity_selections}} presents discussions on heuristic-entity selections.
-
-      \item \textbf{Section \ref{sec:bhh:model}} presents the models that can be optimised using the \Acs{BHH}, specifically referring to the training of \acp{FFNN}.
-
-      \item \textbf{Section \ref{sec:bhh:train_test_datasets}} presents a brief discussion on the role of datasets for training and testing.
-
-      \item \textbf{Section \ref{sec:bhh:loss_function}} presents discussions on model evaluation and the role of the loss function.
-
-      \item \textbf{Section \ref{sec:bhh:domain_barrier}} presents discussions on the domain barrier, an information barrier that exists between the high-level \acs{BHH} and low-level heuristics in the \index{heuristic pool}heuristic pool.
-
       \item \textbf{Section \ref{sec:bhh:performance_log}} presents detailed discussions on performance measurement. The \textit{performance log}, implemented by the \acs{BHH}, is presented.
@@
 
-      \item \textbf{Section \ref{sec:bhh:initialisation_step}} presents the initialisation strategy.
-
       \item \textbf{Section \ref{sec:bhh:optimisation_step}} presents the learning mechanisms by which the probabilistic model can be optimised.
@@
 
-      \item \textbf{Section \ref{sec:bhh:algorithm}} provides the pseudo-code algorithm for the \ac{BHH}.
+      \item \textbf{Section \ref{sec:bhh:algorithm}} provides the pseudo-code algorithm for the \acs{BHH}.
 
@@
 \begin{itemize}
-      \item \textbf{Population-Based:} The \ac{BHH} implements a population-based approach, where a collection of different candidate solutions, referred to as \textit{entities}, work together to yield a global best solution.
-
-      \item \textbf{Meta-Hyper-Heuristic:} There exists a domain barrier, where the \ac{BHH} searches through the \textit{heuristic space}, using only \index{heuristic}heuristic performance information, while lower level heuristics search through the \textit{solution space} using information from the search domain itself.
+      \item \textbf{Population-Based:} The \acs{BHH} implements a population-based approach, where a collection of different candidate solutions, referred to as \textit{entities}, work together to yield a global best solution.
+
+      \item \textbf{Meta-Hyper-Heuristic:} There exists a domain barrier, where the \acs{BHH} searches through the \textit{heuristic space}, using only \index{heuristic}heuristic performance information, while lower level heuristics search through the \textit{solution space} using information from the search domain itself.
 Furthermore, the \index{heuristic pool}heuristic pool implemented by the \acs{BHH} supports both gradient-based low level \index{heuristic}heuristics, as well as meta-heuristics.
@@
 Since the \acs{BHH} is a \textit{learning} \acs{HH}, every heuristic that is included in the heuristic pool increases the requirement of more statistical evidence of heuristic performance.
-Not only does a large \index{heuristic pool}heuristic pool drastically complicate the learning process that is required by the \ac{BHH}, but it also drastically complicates the process of maintaining \textit{state}.
+Not only does a large \index{heuristic pool}heuristic pool drastically complicate the learning process that is required by the \acs{BHH}, but it also drastically complicates the process of maintaining \textit{state}.
 State is the term used to describe data that is relevant to the training process, and is maintained between training steps.
@@
 At each heuristic-entity application step, all state elements per entity are updated either by primary method or by proxied method.
-The \ac{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.
+The \acs{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.
 
@@
 
-Entities represent candidate solutions to the model's trainable parameters (weights) and other heuristic-specific state parameters, as was discussed in Section \ref{sec:bhh:heuristic:proxies}.
+Entities represent candidate solutions to the model's trainable parameters (weights) and other \index{heuristic}heuristic-specific state parameters, as was discussed in Section \ref{sec:bhh:heuristic:proxies}.
 It can be said that entities implement \textit{local} state.
-It was mentioned that these entities can be treated as physical \index{particle}\textit{particles} in a hyper-dimensional search environment.
+It was mentioned that these entities can be treated as physical \textit{particles} in a hyper-dimensional search environment.
 Entities model concepts from physics.
 For example, the candidate solution is represented as the entity's position, and an entity's velocity and acceleration is analogous to the gradient and momentum of the entity respectfully.
-Examples of \index{Entity State}entity state parameters, as derived from various low-level heuristics, is given as follows.
-
-\begin{itemize}
-      \item \textbf{position}: General parameter that represents the actual candidate solution and is thus a primary state parameter for all heuristics.
-
-      \item \textbf{velocity}: Directly implemented by heuristics such as \acp{PSO} and is analogous to the gradient for gradient-based heuristics such as \ac{Momentum}.
-
-      \item \textbf{gradient}: The last known gradient, as derived from gradient-based heuristics.
+Examples of entity state parameters, as derived from various low-level \index{heuristic}heuristics, is given as follows.
+
+\begin{itemize}
+      \item \textbf{position}: General parameter that represents the actual candidate solution and is thus a primary state parameter for all \index{heuristic}heuristics.
+
+      \item \textbf{velocity}: Directly implemented by \index{heuristic}heuristics such as \acp{PSO} and is analogous to the gradient for gradient-based \index{heuristic}heuristics such as \ac{Momentum}.
+
+      \item \textbf{gradient}: The last known gradient, as derived from gradient-based \index{heuristic}heuristics.
 
@@
 
-      \item \textbf{sum of the gradients squared}: As required and maintained by heuristics such as \acs{Adagrad}.
-
-      \item \textbf{expected position delta variance}: As required and maintained by heuristics such as \acs{Adadelta}.
-
-      \item \textbf{expected gradient mean}: As required and maintained by heuristics such as \acs{Momentum}, \acs{NAG} and \acs{Adam}.
-
-      \item \textbf{expected gradient variance}: As required and maintained by heuristics such as \acs{RMSProp}, \acs{Adadelta} and \acs{Adam}.
-
-      \item \textbf{personal best position}: Parameter that tracks that best known position by the entity thus far. As required and maintained by heuristics such as \acs{PSO}.
-
-      \item \textbf{personal best loss}: Parameter that tracks that best known loss by the entity thus far. As required and maintained by heuristics such as \acs{PSO}.
+      \item \textbf{sum of the gradients squared}: As required and maintained by \index{heuristic}heuristics such as \acs{Adagrad}.
+
+      \item \textbf{expected position delta variance}: As required and maintained by \index{heuristic}heuristics such as \acs{Adadelta}.
+
+      \item \textbf{expected gradient mean}: As required and maintained by \index{heuristic}heuristics such as \acs{Momentum}, \acs{NAG} and \acs{Adam}.
+
+      \item \textbf{expected gradient variance}: As required and maintained by \index{heuristic}heuristics such as \acs{RMSProp}, \acs{Adadelta} and \acs{Adam}.
+
+      \item \textbf{personal best position}: Parameter that tracks that best known position by the entity thus far. As required and maintained by \index{heuristic}heuristics such as \acs{PSO}.
+
+      \item \textbf{personal best loss}: Parameter that tracks that best known loss by the entity thus far. As required and maintained by \index{heuristic}heuristics such as \acs{PSO}.
 
@@
 \noindent
-From the list above, it should be clear that entity state becomes increasingly complicated as the number of distinct \index{heuristic}heuristics, included in the \index{heuristic pool}heuristic pool, increases.
+From the list above, it should be clear that entity state becomes increasingly complicated with the increase of the number of distinct \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool with unique state parameters.
 
@@
 Population state is also referred to as \textit{global} state and represents the population's memory.
-The population state generally contains state parameters that are of importance to multiple \index{heuristic}heuristics, and usually tracks the state of the population and not individual heuristic.
-Some examples of population state that can arise from different \index{heuristic}heuristics is given below:
+The population state generally contains state parameters that are of importance to multiple \index{heuristic}heuristics, and usually tracks the state of the population and not individual \index{heuristic}heuristic.
+Some examples of population state that can arise from different \index{heuristic}heuristics is given below.
 
@@
       \item \textbf{ibest} and \textbf{ibest loss}: Refers to the best position and loss achieved by the population for the current iteration/step.
-This parameter is introduced by the \ac{BHH} itself through the requirements of the \textit{ibest} credit assignment strategy.
 
       \item \textbf{rbest} and \textbf{rbest loss}: Refers to the best position and loss achieved by the population for the current replay buffer/window size.
-This parameter is introduced by the \ac{BHH} itself through the requirements of the \textit{rbest} credit assignment strategy.
 
       \item \textbf{gbest} and \textbf{gbest loss}: Refers to the overall/global best position and loss achieved by the population for the entire training process.
-This parameter is introduced by heuristics such as \acp{PSO}, and is also introduced by the \ac{BHH} itself through the requirements of the \textit{gbest} credit assignment strategy.
-\end{itemize}
-
-\noindent
-Entities in the entity pool are each assigned an associated \index{heuristic}heuristic. The following section provides details around the heuristic-entity selection process.
-
-\section{Heuristic-Entity Selections}
-\label{sec:bhh:heuristic_entity_selections}
-
-The \ac{BHH} selects from the \index{heuristic pool}heuristic pool a low-level heuristic to be applied to an entity.
-The outcome of this selection process is a table that tracks which heuristic has been selected for which entity.
-The selection process is executed by the selection mechanism of the \ac{BHH} and is discussed later in Section \ref{sec:bhh:selection_mechanism}.
-These heuristic-entity combinations are applied to an underlying model.
-The next section provides clarity on the model component from the architecture of the \ac{BHH}.
-
-\index{Model}
-\section{Model}
-\label{sec:bhh:model}
-
-The \index{Model}model refers to the target model to be optimised and is usually expressed as a complex mathematical function.
-For this dissertation, the authors focused specifically on shallow \acp{FFNN} (only one hidden layer).
-Figure \ref{fig:shallow_ffnn} below presents such a shallow \acp{FFNN}.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=0.4\textwidth]{shallow_ffnn.pdf}
-      \caption[Shallow \index{Feedforward Neural Network}Feedforward Neural Network]{An illustration of
-            a shallow \index{Feedforward Neural Network}Feedforward Neural Network.}
-      \label{fig:shallow_ffnn}
-\end{figure}
-
-\section{Train and Test Datasets}
-\label{sec:bhh:train_test_datasets}
-
-The training of \ac{FFNN} is a supervised learning problem as was highlighted in Chapter \ref{chap:anns}.
-Therefore, the \ac{BHH} trains the model on training data from the training set, while is reserves an unseen set of test data in the test dataset for evaluation.
-It should be mentioned that the goal of the \ac{BHH} is to generalise well to the test set across a number of problem domains.
-As was previously mentioned, the test set should be sufficiently large to truly evaluate for generalisation capabilities.
-For the \ac{BHH}, it is proposed to have a 80-20\% split between the training and test set.
-
-\section{Loss/Cost Function}
-\label{sec:bhh:loss_function}
-
-Chapter \ref{chap:anns} presented the concept of a loss/cost function that is used to evaluate the performance of \acp{ANN}.
-The \ac{BHH} uses this loss/cost function to evaluate the performance of a heuristic-entity combination.
-For classification problems, generally some entropy loss is used.
-For classification problems with 2 classes, \ac{BinXE} is used and for classification problems with more than 2 classes, the \ac{SparseCatXE} is used.
-For regression problems it is recommended to use some mean error measurement such as \ac{MSE} or \ac{RMSE}.
-
-The loss/cost function is very important as this metric is used to evaluate model performance as a result of the application of a heuristic to an entity's candidate solution.
-The \ac{BHH} used this performance metric to bias towards good heuristic-entity combinations.
-The continuous valued cost/loss function is translated into a discrete valued representation through a credit assignment strategy that is implemented in the \ac{BHH}.
-The credit assignment strategies is discussed in Section \ref{sec:bhh:credit_assignment_strategy}.
-
-\section{Domain Barrier}
-\label{sec:bhh:domain_barrier}
-
-The domain barrier presents the boundary of information flow between the heuristic space and the solution space.
-It is mentioned in Section \ref{sec:bhh:loss_function} that the heuristic-entity loss is used by the \ac{BHH}.
-Notice that the \ac{BHH} uses this performance information and no information from the solution space itself.
-Furthermore, the \ac{BHH} maps this loss to a credit assignment problem as is mentioned by Burke et al.~\cite{ref:burke:2010}.
-The \ac{BHH} at a high level, is not aware of the actual candidate solution that is represented by the entity, but rather just that there is a candidate solution with a unique identifier that, together with a heuristic, produced a certain level of performance.
-The domain barrier is a feature that occurs in al \acp{HH}.
-Burke et al.~\cite{ref:burke:2010} states that the \ac{HH} collects domain-independent information from the domain barrier.
-A number of examples of domain independent information is given, these include the number of heuristics, the changes in evaluation function, whether a new solution was found or generated, the distance between two solutions, whether it has become stuck.
-
-\index{Performance Log}
-\section{Performance Log}
-\label{sec:bhh:performance_log}
-
-Recall that the \ac{BHH} incorporates a Bayesian probabilistic implementation.
-Evidence is required to train the \ac{BHH}.
-The performance log is used to keep memory of a slice of the performance history.
-The performance log is simply a tabular implementation that tracks random events.
-The \ac{BHH} suggests the following metrics to keep track of in the performance log:
+This parameter is introduced by \index{heuristic}heuristics such as \acp{PSO}.
+\end{itemize}
+
+\noindent
+Entities in the entity pool are each assigned an associated \index{heuristic}heuristic.
+The \acs{BHH} selects from the \index{heuristic pool}heuristic pool a low-level \index{heuristic}heuristic to be applied to an individual entity.
+The outcome of this selection process is a mapping table that tracks which \index{heuristic}heuristic has been selected for which entity.
+The selection process is executed by the selection mechanism of the \acs{BHH}.
+These \index{heuristic}heuristic-entity combinations are applied to the underlying \acs{FFNN}.
+The \acs{BHH} tracks the performance of each of these combinations throughout the training process in a performance log.
+The performance log is presented in the following section.
+
+\section{Performance Log}\label{sec:bhh:performance_log}
+
+The \acs{BHH} incorporates a form of probabilistic modeling in its selection mechanism.
+Probability is calculated based on \index{heuristic}heuristic-entity performance over time.
+Evidence of \index{heuristic}heuristic-entity performance is thus required for the \acs{BHH} to learn.
+Since the performance log can become very big, only a sliding window of the performance history is maintained at each step in the learning process.
+The sliding window is also referred to as a \textit{replay} buffer, a term borrowed from the field of \acf{RL}.
+The replay window size is defined as a hyper-parameter of the \acs{BHH}.
+The performance log is then simply a table of events and metrics.
+The \acs{BHH} tracks the following metrics in the performance log.
 
@@
 
-      \item \textbf{heuristic}: The selected heuristics' index.
-
-      \item \textbf{entity}: The applied entity's index.
-
-      \item \textbf{loss}: The heuristic-entity performance metric.
-
-      \item \textbf{ibest loss}: Keeps track of the \textit{iteration} best loss. Thus, the best loss value achieved by all all entity-heuristic combinations for a single mini-batch step.
+      \item \textbf{\index{heuristic}heuristic}: The selected heuristic's index.
+
+      \item \textbf{entity}: The entity's index to whom the \index{heuristic}heuristic is applied.
+
+      \item \textbf{loss}: The \index{heuristic}heuristic-entity performance metric. The loss is retrieved from the loss function.
+
+      \item \textbf{ibest loss}: Keeps track of the \textit{iteration} best loss.
+Thus, the best loss value achieved by all entity-\index{heuristic}heuristic combinations, for a single mini-batch step.
 
       \item \textbf{rbest loss}:  Keeps track of the \textit{replay} best loss.
-Thus, the best loss value achieved by all all entity-heuristic combinations over all mini-batch steps currently in the performance log.
-
-      \item \textbf{gbest loss}:  Keeps track of the \textit{global} best loss. Thus, the best loss value achieved by all all entity-heuristic combinations over all mini-batch steps thus far.
-\end{itemize}
-
-The performance log as implemented by the \ac{BHH} is given in Table \ref{tab:bhh:performance_log:performance_log_example} below.
+Thus, the best loss value achieved by all entity-\index{heuristic}heuristic combinations, over all mini-batch steps currently in the performance log/replay buffer.
+
+      \item \textbf{gbest loss}:  Keeps track of the \textit{global} best loss.
+Thus, the best loss value achieved by all entity-\index{heuristic}heuristic combinations over all mini-batch steps thus far.
+\end{itemize}
+
+\noindent
+An example of the performance log implemented by the \acs{BHH} is given in Table \ref{tab:bhh:performance_log:performance_log_example} below.
 
@@
       \centering
-      \caption{Performance log example showing the first 5 entity's selected heuristics for step 1 and their resulting performance measurements.}
+      \caption{An example of the performance log implemented by the \acs{BHH}, showing the first 5 entities, their allocated \index{heuristic}heuristics and their resulting performance measurements for step 1 of the training process.}
       \label{tab:bhh:performance_log:performance_log_example}%
@@
             \begin{tabular}{cccccccc}
-                  \textbf{step} & \textbf{entity} & \textbf{heuristic} & \textbf{loss} & \textbf{ibest loss} & \textbf{pbest Loss} & \textbf{rbest loss} & \textbf{gbest loss} \\
+                  \textbf{step} & \textbf{entity} & \textbf{heuristic} & \textbf{loss} & \textbf{ibest loss} & \textbf{pbest loss} & \textbf{rbest loss} & \textbf{gbest loss} \\
                   \midrule
@@
 
-The performance log itself introduces a number of design considerations as well. Since the log contains a slice of memory, there should exists a trade-off between the following parameters:
-
-\begin{itemize}
-      \item \textbf{performance log size}: The larger the performance log, the longer memory is retained.The performance log size controls the recency of evidence from which new beliefs must be derived.
-This parameter is called the \textit{replay} window size, a term borrowed from \ac{RL} and should be empirically tested.
-If the replay window size is too small, it does not accumulate enough samples/evidence to really statistically make accurate classifications.
-If the replay window size is too back, the \ac{BHH} might remember too much of past performance and it could be that past performance is not indicative of future performance during the training process.
-Notice then that the performance log must be pruned to maintain a fixed replay window size.
-Dynamic replay window sizes is left as a research component for the future.
-
-      \item \textbf{performance log reanalysis}: Consider the temporal nature of the performance log.
-Since it tracks all random events across all steps in the training process, it is needed to reanalyse the performance log appropriately in order to update the past information in the performance log with newly added data.
-An example of this is when a new rbest value has been found.
-Then the entire performance log's rbest loss must be updated.
-\end{itemize}
-
-The performance log should be considered along with the selection of credit assignment strategy used. These are discussed next.
-
-\index{Credit Assignment Strategy}
+\noindent
+The performance log itself introduces a number of design considerations as well.
+The larger the performance log, the longer memory is retained throughout the training process.
+The performance log size, referred to as the \textit{replay window size}, controls the recency of evidence from which the \acs{BHH} must learn.
+If the replay window size is too small, it does not accumulate enough samples/evidence to statistically make accurate selections.
+If the replay window size is too big, a bias could exist for selecting \index{heuristic}heuristics that performed well in the past.
+Furthermore, it is not guaranteed that past performance is indicative of future performance during the training process.
+The performance log should be considered along with the selection of a credit assignment strategy.
+Credit assignment strategies are presented in the following section.
+
 \section{Credit Assignment Strategy}
@@
 
-The credit assignment strategy is an implementation that maps a continuous performance metric into a discrete credit metric.
-This component implements the ``move acceptance'' process as proposed by Özcan et al.~\cite{ref:ozcan:2006,ref:ozcan:2008}.
-It determines if a given performance is deemed good or not.
-This simple discrete transformation is subject to the credit assignment problem as discussed by Burke et al.~\cite{ref:burke:2010}.
-A good credit assignment strategy will correctly allocate credit to the appropriate heuristic-entity combination.
-THe magnitude of this credit is to be empirically tested.
-It is later shown how these credit metrics are used to accumulate ``pseudo counts'' which concentrates/biases heuristic selection towards good performing heuristics.
-The \ac{BHH} propose the following initial credit assignment strategies.
-
-\begin{itemize}
-      \item \textbf{ibest}: Credit is assigned to the heuristic-entity combination that set the \textit{ibest} loss value, meaning that it is the entity-heuristic combination that achieved the best performance in the current mini-batch iteration.
-
-      \item \textbf{pbest}: Credit is assigned to the heuristic-entity combination that set the \textit{pbest} loss value, meaning that it is the entity-heuristic combination that was able to improve on it's personal best past performance loss.
-
-      \item \textbf{rbest}: Credit is assigned to the heuristic-entity combination that set the \textit{rbest} loss value, meaning that it is the entity-heuristic combination that achieved the best performance in the current replay window.
-
-      \item \textbf{gbest}: Credit is assigned to the heuristic-entity combination that set the \textit{gbest} loss value, meaning that it is the entity-heuristic combination that achieved the overall best performance so far.
-
-      \item \textbf{symmetric}: A credit assignment strategy that gives credit to all entity-heuristic combinations regardless of performance.
-This credit assignment strategy suggests that ``symmetric'' credit assignment be given.
-As a result, any bias that arise from uncertainty or as a result of an untrained \ac{BHH} model, in the beginning, is maintained and further strengthened throughout the training process .
-Notice that this credit assignment strategy does not randomly assign credit, it simply assigns credit to the all events that are a result of random selection, which could be possibly be biased.
-\end{itemize}
-
-The implementation of a credit assignment strategy is a pure, stateless function that translates input $P$ from the performance log into output $C$ as is given in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example} below.
+The credit assignment strategy is a mechanism that assigns a discrete credit indicator to \index{heuristic}heuristics that perform well, based on their performance metrics such as loss.
+The credit assignment strategy implements the ``move acceptance'' process as proposed by~\citeauthor{ref:ozcan:2006}~\cite{ref:ozcan:2006,ref:ozcan:2008} and addresses the credit assignment problem as discussed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}.
+A good credit assignment strategy will correctly allocate credit to the appropriate \index{heuristic}heuristic-entity combination.
+The credit assignment strategy to use is defined as a hyper-parameter.
+The \acs{BHH} implements the following credit assignment strategies to choose from.
+
+\begin{itemize}
+      \item \textbf{ibest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{ibest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that achieved the best performance in the current mini-batch iteration.
+
+      \item \textbf{pbest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{pbest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that was able to improve on its personal best past performance loss.
+
+      \item \textbf{rbest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{rbest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that achieved the best performance in the current replay window.
+
+      \item \textbf{gbest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{gbest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that achieved the overall best performance so far.
+
+      \item \textbf{symmetric}: Credit is assigned to all entity-\index{heuristic}heuristic combinations, regardless of their performance.
+The symmetric credit assignment strategy does not randomly assign credit, but rather assigns credit to all events.
+In effect, no learning and performance-bias is achieved with the symmetric credit assignment strategy and thus, the symmetric credit assignment strategy is implemented as a basis for comparison.
+Comparing a credit assignment staretegy to the symmetric credit assignment indicates the ability of the other credit assignment strategy to have an effect on the learning process and performance of the \acs{BHH}.
+\end{itemize}
+
+\noindent
+The implementation of a credit assignment strategy is simply a function that translates the performance log from Table \ref{tab:bhh:performance_log:performance_log_example}, into Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example} below.
 
@@
       \centering
-      \caption{Credit assignment strategy output table showing \textit{ibest} credit assignment for the first 5 entity's and their selected heuristics for step 1 of the training process.}
+      \caption{Credit assignment strategy output table showing \textit{ibest} credit assignment for the first 5 entities and their selected heuristics, for step 1 of the training process.}
       \label{tab:bhh:credit_assignment_strategy:credit_assignment_example}%
@@
 
-Credit assignment is a key component of the \ac{BHH} is it will later be shown in Section \ref{sec:bhh:optimisation_step} how these credit assignments are used to optimise the \ac{BHH}.
-First, it is necessary to present the selection mechanism.
-
-\index{Selection Mechanism}
-\section{Selection Mechanism}
-\label{sec:bhh:selection_mechanism}
-
-This section aims to provide the reader with the detail around the selection mechanism as it is implemented by the \ac{BHH}.
-It is mentioned throughout this document that the \ac{BHH} implements a predictive model based on Bayesian probabilistic concepts.
+\noindent
+Credit is used by the selection mechanism of the \acs{BHH}. The selection mechanism is presented in the following section.
+
+\section{Selection Mechanism}\label{sec:bhh:selection_mechanism}
+
+This section aims to provide the reader with the detail around the selection mechanism as it is implemented by the \acs{BHH}.
+It is mentioned throughout this document that the \acs{BHH} implements a predictive model based on Bayesian probabilistic concepts.
 In probabilistic modeling it is necessary to identify all the random events that can occur.
 
-\index{Random Events}
 \subsection{Random Events}
@@
 
-Observation of random events is treated as evidence. In the context of a Bayesian approach, this evidence is used to update prior beliefs. The \ac{BHH} distinguishes between the following events:
+Observation of random events is treated as evidence. In the context of a Bayesian approach, this evidence is used to update prior beliefs. The \acs{BHH} distinguishes between the following events.
 
@@
       \item \textbf{$E$}: The event of observing \textit{entities}.
-      \item \textbf{$C$}: The event of observing \textit{credit assignments}.
-\end{itemize}
-
-It should be noted that this information is observed direclty from the performance log presented in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example} above.
-From the above list, the event $C$ is dependent on the occurrence of $H$ and $E$.
-However, for simplification, an argument for independence can be made.
-
-\index{Independence}
-\subsection{Independence}
-\label{sec:bhh:selection_mechanism:independence}
-
-The dependence between random events can have a drastic impact on the probabilistic model that is implemented.
-For simplicity, the \ac{BHH} assumes independence between events, although the event $C$ is clearly dependent on the occurrence of $H$ and $E$.
-Notice that the \ac{BHH} is fundamentally a classifier, classifying which heuristic to select given an entity and performance criteria.
-It is later shown in Section \ref{sec:bhh:selection_mechanism:naive_bayes} that the \ac{BHH} implements a Naïve Bayes classifier.
-Domingos et al.~\cite{ref:domingos:1997} mentions that although Bayesian classifiers’ probability estimates are only optimal under quadratic loss if the independence assumption holds, the classifier itself can be optimal under zero-one loss (misclassification rate) even when this assumption is violated by a wide margin.
-This means that independence can be assumed when the probabilistic model is used as a classifier and not to get real probabilities.
-Evaluating for proportionality and not precision allows for the assumption of independence.
+      \item \textbf{$C$}: The event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} is met.
+\end{itemize}
+
+\noindent
+It should be noted that event information is stored and observed direclty from the performance log as presented in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}.
+From the above list of events, the event $C$ is dependent on the occurrence of $H$ and $E$ and a credit assignment strategy.
+
+\subsection{Independence}\label{sec:bhh:selection_mechanism:independence}
+
+The dependence between random events can have an impact on the probabilistic model that is implemented.
+For simplicity, the \acs{BHH} assumes independence between events, although the event $C$ is clearly dependent on the occurrence of $H$ and $E$.
+Furthermore, the \acs{BHH} assumes independence between steps  and treats each training step as if training has restarted.
+The \acs{BHH} implements a form of Naïve Bayes classifier, where the appropriate heuristic to assign to an entity is a classification problem.
+\citeauthor{ref:domingos:1997}~\cite{ref:domingos:1997} mentions that although Bayesian classifiers’ probability estimates are only optimal under quadratic loss if the independence assumption holds, the classifier itself can still be optimal under zero-one loss (misclassification rate), even when this assumption is violated by a wide margin.
+This means that independence can be assumed when the probabilistic model is used as a classifier.
 
 \index{Bayes' Theorem}
-\subsection{Bayes' Theorem}
-\label{sec:bhh:selection_mechanism:bayes_theorem}
-
-Section \ref{sec:bhh:selection_mechanism:random_events} presented the reader with the random events that are observed by the \ac{BHH} and Section \ref{sec:bhh:selection_mechanism:independence} provided an argument for independence between events.
-Chapter \ref{chap:probability} presented Bayes Theorem, but for convenience, it is given again in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} below.
+\subsection{Bayes' Theorem}\label{sec:bhh:selection_mechanism:bayes_theorem}
+
+Chapter \ref{chap:probability} presented \index{Bayes' Theorem}Bayes' Theorem, but for convenience, it is given again in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} below.
 
@@
 
-As was indicated in Section \ref{sec:bhh:selection_mechanism:independence}, Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} can be evaluated for proportionality since the \ac{BHH} is not concerned with actual accurate selection probabilities, but rather implements a Bayesian classifier.
-The resulting proportionality is expressed in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} below
+\noindent
+Since the \acs{BHH} implements a Bayesian classifier, the \acs{BHH} is not concerned with actual probabilities.
+Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} can thus be evaluated for proportionality.
+The resulting proportionality is expressed in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} below.
 
@@
 
-Notice how the Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} implements a Bayesian conditionally.
-This conditionality can be extended to include multiple criteria.
-The next section shows how the Bayesian classifier is implemented by providing the detail around the implemented predictive model.
-
-\subsection{Predictive Model}
-\label{sec:bhh:selection_mechanism:predictive_model}
-
-Finally the reader is presented with the underlying predictive model as implemented by the \ac{BHH}.
-This component is arguably the most important component of the entire \ac{BHH} as it fundamentally drives the output of the \ac{BHH}.
-Bayes Theorem as was shown again in Section \ref{sec:bhh:selection_mechanism:bayes_theorem} above can be used to implement a predictive model to predict which heuristic to select, given the conditionality of a particular entity and a particular credit assignment criteria is met.
-Consider the following setup.
+\noindent
+The conditionality implemented by \index{Bayes' Theorem}Bayes' Theorem can be extended to include multiple criteria.
+\index{Bayes' Theorem}Bayes' Theorem is used by the selection mechanism of the \acs{BHH}.
+The predictive model that is used by the selection mechanism of the \acs{BHH} is presented in the following section.
+
+\subsection{Predictive Model}\label{sec:bhh:selection_mechanism:predictive_model}
+
+This section presents the predictive model as implemented by the selection mechanism of the \acs{BHH}.
+The predictive model is arguably the most important component of the \acs{BHH}, as it drives heuristic selection process.
+The \acs{BHH} implements a predictive model that predicts which heuristic to select, given the conditionality that a particular entity is used and a particular credit assignment criteria is met.
+The predictive model can be derived as follows.\\\\
+\textbf{Setup}:
+\\
+\noindent
 Let
@@
 
-      \item $\theta \vert \alpha \sim Dir(\alpha; K)$: Denote the heuristic probability distribution, implementing a Dirichlet probability distribution parameterised by $\alpha$ and $K$.
+      \item $\theta \vert \alpha \sim Dir(\alpha; K)$: Denote the heuristic probability distribution, implementing a \index{Dirichlet probability distribution}Dirichlet probability distribution parameterised by $\alpha$ and $K$.
 Heuristic selection probabilities are sampled from this distribution.
-      \item $\phi \vert \beta \sim Dir(\beta; K)^{J}$: Denote the entity-heuristic probability distribution, implementing a Dirichlet probability distribution parameterised by $\beta$ and $K$ for each entity in the \index{entity pool}entity pool with population size $J$.
+
+      \item $\phi \vert \beta \sim Dir(\beta; K)^{J}$: Denote the entity-heuristic probability distribution, implementing a \index{Dirichlet probability distribution}Dirichlet probability distribution parameterised by $\beta$ and $K$ for each entity in the \index{entity pool}entity pool with population size $J$.
 Entity-heuristic probabilities are sampled from this distribution.
+
       \item $\psi \vert \gamma_{1}, \gamma_{0}  \sim Beta(\gamma_{1}, \gamma_{0})$: Denote the credit-heuristic probability distribution, implementing a Beta probability distribution parameterised by $\gamma_{1}$ and $\gamma_{0}$.
@@
 
-      \item $H \vert \theta \sim Mult(\theta; I, K)$: Denote the distribution of heuristics (event $H$), implementing a Multinomial distribution, parameterised by the sampled heuristic selection probability $\theta$, the \index{heuristic pool}heuristic pool size $K$ and maximum number of instances $I$.
-      \item $E \vert \phi \sim Mult(\phi; I, K)^{J}$: Denote the distribution of entity-heuristic combinations (event $E$), implementing a Multinomial distribution, parameterised by the sampled entity-heuristic selection probability $\phi$, the \index{heuristic pool}heuristic pool size $K$ and maximum number of instances $I$, for each entity in $J$.
-      \item $C \vert \psi \sim Bin(\psi, I)$: Denote the distribution of credit-heuristic combinations (event $C$), implementing a\index{Binomial probability distribution}Binomial probability distribution, parameterised by the sampled credit-heuristic selection probability $\psi$ and the maximum number of instances $I$.
-\end{itemize}
-
-The parameterised predictive model, as derived from Bayes theorem presented in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} is then given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model} below.
+      \item $H \vert \theta \sim Mult(\theta; I, K)$: Denote the distribution of heuristics (event $H$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled heuristic selection probability $\theta$, the \index{heuristic pool}heuristic pool size $K$ and maximum number of instances $I$.
+
+      \item $E \vert \phi \sim Mult(\phi; I, K)^{J}$: Denote the distribution of entity-heuristic combinations (event $E$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled entity-heuristic selection probability $\phi$, the \index{heuristic pool}heuristic pool size $K$ and maximum number of instances $I$, for each entity in $J$.
+
+      \item $C \vert \psi \sim Bin(\psi, I)$: Denote the distribution of credit-heuristic combinations (event $C$), implementing a \index{Binomial probability distribution}Binomial probability distribution, parameterised by the sampled credit-heuristic selection probability $\psi$ and the maximum number of instances $I$.
+\end{itemize}
+
+\noindent
+Vector notation is dropped for sake of convenience, simplicity and readability.
+The parameterised predictive model, as derived from \index{Bayes' Theorem}Bayes' theorem, is then given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model} below.
 
@@
             }{
-                  \left[ \sum_{k}^{K} P(E, H=k \vert \theta, \psi) \right] \left[ \sum_{k}^{K}  P(C, H=k \vert \theta, \phi) \right]
+                  \left[ \sum_{k}^{K} P(E, H=k \vert \theta, \phi) \right] \left[ \sum_{k}^{K}  P(C, H=k \vert \theta, \psi) \right]
             } \\
@@
             }{
-                  \left[ \sum_{k}^{K} P(E \vert H=k \vert \phi) P(H=k \vert \theta) \right] \left[ \sum_{k}^{K} P(C \vert H=k \vert \psi) P(H=k \vert \theta) \right]
+                  \left[ \sum_{k}^{K} P(E \vert H=k, \phi) P(H=k \vert \theta) \right] \left[ \sum_{k}^{K} P(C \vert H=k, \psi) P(H=k \vert \theta) \right]
             }
@@
 
-Notice the joint probability over events $E$ and $C$ given the selection of a heuristic $H$ denoted by the sums of the products of the separate parts, for $E$ and $C$, in the denominator.
-The calculation in the denominator can be intractable as has been previously indicated.
-However, in order to derive the posterior distribution as given in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem}), one only has to evaluate to proportionality as is given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} below.
+\noindent
+Notice the joint probability over events $E$ and $C$, given the selection of a heuristic $H$, denoted by the sums of the products of the separate parts, for $E$ and $C$, in the denominator.
+The calculation in the denominator can be intractable.
+Since the \acs{BHH} selection mechanism uses the predictive model as a classifier, the posterior distribution as given in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem}), can be evaluated for proportionality, as is given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} below.
 
@@
 
+\noindent
 The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $H$, given allocation to entity $E$ and credit $C$, parameterised by sampled $\theta$, $\phi$ and $\psi$.
-These parameters are in turn parameterised by concentrations $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$ which denote the prior beliefs of the \ac{BHH}.
+These parameters are in turn parameterised by concentrations $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$, which denote the prior beliefs of the \acs{BHH}.
 
 \index{Naïve Bayes}
-\subsection{Naïve Bayes}
-\label{sec:bhh:selection_mechanism:naive_bayes}
-
-This section aims to dissect the probabilistic model that is presented in Equestion \ref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
-It has been established in Section \ref{sec:bhh:selection_mechanism:independence} that for \index{Naïve Bayes} naïve Bayes classifiers, independence between events can be assumed.
-The following derived \acp{PMF} are provided as fundamental building blocks that are later shown to be used in the optimisation process of the \ac{BHH} as is shown in Section \ref{sec:bhh:optimisation_step}.
-
-The independence between events for the class label $H$ simply yields the \ac{PMF} of the Multinomial distribution as presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf} below.
+\subsection{Naïve Bayes}\label{sec:bhh:selection_mechanism:naive_bayes}
+
+This section aims to dissect the probabilistic model that is presented in Equestion~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
+The \acs{BHH} implements a form of Naïve Bayes classifier and thus, independence between events can be assumed.
+The following derived \acp{PMF} are provided as fundamental building blocks to show the mechanism by which the \acs{BHH} learns.
+
+The independence between events for class label $H$, simply yields the \ac{PMF} of the \index{Multinomial probability distribution}Multinomial distribution as presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf} below.
 
@@
 
-Where $N_{k}$ is a summary variable such that $N_{k} = \sum_{i=i}^{I}
-      \mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the event
-$h_{i}$ taking on class $k$, i.e. the count of occurrences of heuristic $k$ in
-$I$ independent, identical runs.
-
-The independence between events $E$ given class label $H$ is denoted by the likelihood of $E$
-conditional to the occurrence of heuristic $k$ and model parameter $\phi$ as
-presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} below.
+\noindent
+In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf} above, $N_{k}$ is a summary variable such that $N_{k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the event $h_{i}$ taking on class $k$ in $I$ independent, identical runs.
+
+The independence between events $E$, given class label $H$, is denoted by the likelihood of $E$,
+conditional to the occurrence of heuristic $k$ and model parameter $\phi$ as is given in in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} below.
 
@@
 
-Where $N_{j,k}$ is a summary variable such that $N_{j,k} = \sum_{i=i}^{I}
-      \mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of
-occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on
-class $k$, i.e. the count of occurrences of both entity entity $e$ and heuristic
-$k$ occurring together in $I$ independent, identical runs.
-
-Finally, the independence between events for the performance criteria feature $C$ given class
-label $H$ is denoted by the likelihood of $C$ conditional to the occurrence of
-heuristic $k$ and model parameter $\psi$ as given in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} below.
+\noindent
+In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} above, $N_{j,k}$ is a summary variable such that $N_{j,k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on class $k$, i.e.
+the count of occurrences of both entity entity $e$ and heuristic $k$ occurring together in $I$ independent, identical runs.
+
+Finally, the independence between events for the performance criteria $C$, given class label $H$, is denoted by the likelihood of $C$, conditional to the occurrence of heuristic $k$ and model parameter $\psi$ as given in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} below.
 
@@
 
-Where $N_{k}$ is the summary variable as described for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above.
-$N_{1,k}$ is a summary variable such that $N_{1,k} = \sum_{i=1}^{I}
-      \mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of
-occurrences of the events $c_{i}$ taking on a success $(c_{i}=1)$ and $h_{i}$
-taking on class $k$, i.e. the count of occurrences of both succeeding in the
-performance criteria and heuristic $k$ occurring together in $I$ independent,
-identical runs. Similarly $N_{0,k} = N_{k} - N_{1,k}$ would denote the count of
-occurrences of the events $c_{i}$ taking on a failure $(c_{i}=0)$ and $h_{i}$
+\noindent
+In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above, $N_{k}$ is the same summary variable as described for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}.
+$N_{1,k}$ is a summary variable such that $N_{1,k} = \sum_{i=1}^{I} \mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $c_{i}$ taking on a success $(c_{i}=1)$ and $h_{i}$ taking on class $k$, i.e.
+the count of occurrences of both succeeding in the performance criteria and heuristic $k$ occurring together in $I$ independent, identical runs.
+Similarly $N_{0,k} = N_{k} - N_{1,k}$ would denote the count of occurrences of the events $c_{i}$ taking on a failure $(c_{i}=0)$ and $h_{i}$
 taking on class $k$.
 
-Given the assumptions of the naïve Bayes classifier, one could supplement Equations \ref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}, \ref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} and \ref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above into the proportional evaluation of the predictive model as given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
-This is presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} below.
+Equations~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}, \eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} and \eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} can be supplemented into the proportional evaluation of the predictive model as given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} and is given in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} below.
 
@@
 
-Computationally the equation presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} will underflow if the resulting probabilities are very small.
-
-\index{Numerical Stability}
-\subsection{Numerical Stability}
-\label{sec:bhh:selection_mechanism:numerical_stability}
+\noindent
+Consider the practical implementation of the predictive model as shown in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} above.
+Computationally the equation presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} will underflow on a real computer if the resulting probabilities are very small.
+Discussions follow on numerical stability as it relates to practical implementation.
+
+\subsection{Numerical Stability}\label{sec:bhh:selection_mechanism:numerical_stability}
 
@@
 Consider an example where training has stagnated, effectively leading to a scenario where a credit assignment strategy never fulfills a credit assignment, yielding an extremely small probability for $\psi$.
-A solution to this problem is to apply the \textit{log-sum-exp trick}, parameterising distributions no longer using logits rather than probabilities.
+A solution to the aforementioned problem is to apply the \textit{log-sum-exp} trick.
 The transformation of Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} using the log-sum-exp trick is given below in Equation~\eqref{eq:bhh:selection_mechanism:numerical_stability:log_sum_exp}.
@@
 
+\noindent
 The log-sum-exp trick as shown above caters for very small probabilities, however, there might be a situation where  a random event is never seen, purely by chance.
@@
 
-\index{Mode Collapse}
-\subsection{Mode Collapse}
-\label{sec:bhh:selection_mechanism:mode_collapse}
-
-Mode collapse is the situation that occurs where the selective pressure towards a heuristic is close to zero, as a results of random sampling, low initial bias or bad performance.
-This leads to a situation where to probabilistic model continually decrease the selective pressure until the selection probability of that heuristic is 0, yielding no further observations of that particular random event.
-This could be problematic and should be addressed.
-
-The \ac{BHH} addresses this issue by:
+\subsection{Mode Collapse}\label{sec:bhh:selection_mechanism:mode_collapse}
+
+Mode collapse is the situation that occurs where the selective pressure towards a heuristic is close to zero as a results of random sampling, low initial bias or bad performance.
+This leads to a situation where the probabilistic model continually decreases the selective pressure, until the selection probability of that heuristic is 0, yielding no further observations of that particular random event.
+The \acs{BHH} addresses the aforementioned issue by:
 
@@
 
+\noindent
 Another suggestion is to ensure that at least one of every heuristic is always selected during training.
-The \ac{BHH} does not incorporate this model as this could result in a situation where a bad choice of heuristic is continually used throughout the training process, possibly resulting in bad update steps/selections.
-Instead the \ac{BHH} relies on the underlying learning process to control the selective pressure according to performance and nothing else.
-If this leads to a situation where mode collapse occurs, the \ac{BHH} accepts this outcome.
-
-This section briefly touched on parameter initialisation. The next section discusses the initialisation process of the \ac{BHH} in detail.
-
-\section{Initialisation Step}
-\label{sec:bhh:initialisation_step}
-
-This section sheds light into the initialisation of the \ac{BHH} and how it applies to the heuristic and \index{entity pool}entity pools.
-Since the \index{heuristic pool}heuristic pool is a collection of stateless heuristic proxy operations, there is no explicit initialisation that is applied to the \index{heuristic pool}heuristic pool itself.
-On the contrary, the \index{entity pool}entity pool is stateful and maintain candidate solutions.
-Chapter \ref{chap:anns} presented various initialisation strategies to randomly place candidate solutions in the solution space.
-The \ac{BHH} can make use of any of these initialisation strategies and as such, by default makes use of \index{Glorot uniform sampling}Glorot uniform sampling.
-All other entity state parameters are initialised to be zero.
-
-The selection mechanism also requires initialisation.
-Section \ref{sec:bhh:selection_mechanism:predictive_model} introduces the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$.
-These parameters \textit{symmetrically} initialised, meaning that they are all initialised to the value of one in all dimensions.
-Section \ref{sec:bhh:optimisation_step:a_priori_bias} shows that these concentration parameters can be used to introduce \textit{a priori} biases based on expert knowledge.
-The next section provides the detail around the selection mechanism that is implemented by the \ac{BHH}.
-
-\section{Optimisation Step}
-\label{sec:bhh:optimisation_step}
-
-Thus far the reader has been presented with all the fundamental components of the \ac{BHH}.
-The final step that is missing is to present the optimisation step by which the optimisation process takes place.
-This section aims to provide a solid  mathematical explanation to show exactly how the \ac{BHH} is able to learn.
-
-The \ac{BHH} is an adaptive \ac{HH}, meaning that it implements online learning.
-Online learning refers to the continuous learning process that is executed by the \ac{BHH} while training is taking place.
-Throughout the training process, concentration parameters are updated strategically to guide the selection mechanism towards heuristics that perform well.
-The learning capability of the \ac{BHH} lies in the careful updating of these concentration parameters.
-
-Generally there are two different techniques that are used to train naïve Bayes classifiers.
-The frequentist approach implements \ac{MLE} and the Bayesian approach implements \ac{MAP}.
-These methods are provided in Sections \ref{sec:bhh:optimisation_step:mle} and \ref{sec:bhh:optimisation_step:map} respectively.
-It should be mentioned that the \ac{BHH} makes use of \ac{MAP} to optimise the underlying model, however, the authors deem it necessary to provide the details of \ac{MLE} as it contains fundamental mathematical building blocks that are required to understand \ac{MAP}.
-
-It has been established that the \ac{BHH} is a selective \ac{HH} that biases heuristic selection towards a certain performance bias. The concept of performance biases is discussed next.
-
-\index{Performance Bias}
-\subsection{Performance Bias}
-\label{sec:bhh:optimisation_step:performance_bias}
-
-The intent of the \ac{BHH} is to gather evidence that is can use to update its prior beliefs about which heuristics perform well during training.
+The \acs{BHH} does not incorporate this model as this could result in a situation where a bad choice of heuristic is continually used throughout the training process, possibly resulting in bad update steps/selections.
+Instead, the \acs{BHH} relies on the underlying learning process to control the selective pressure according to performance and nothing else.
+If this leads to a situation where mode collapse occurs, the \acs{BHH} accepts the outcome.
+
+\section{Optimisation Step}\label{sec:bhh:optimisation_step}
+
+Thus far all the fundamental components of the \acs{BHH} has been presented.
+The final step that is missing is to present the optimisation step by which the learning process takes place.
+This section aims to provide a solid mathematical explanation to show exactly how the \acs{BHH} is able to learn.
+
+The intent of the \acs{BHH} is to gather evidence that can be use to update prior beliefs about which heuristics perform well during training.
 These beliefs are represented by the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$.
 A change in prior beliefs is represented by a change in these concentration parameters.
-Sections \ref{sec:bhh:optimisation_step:mle} and \ref{sec:bhh:optimisation_step:map} show how the concentration parameters are updated throughout the training process, yielding the mechanism by which optimisation takes place.
-
-Specifically, it can be said, that the optimisation process employed by the \ac{BHH} updates \textit{pseudo counts} of events that it observes in its performance logs.
+Specifically, it can be said, that the optimisation process implemented by the \acs{BHH}, updates \textit{pseudo counts} of events that are observed in the performance logs.
 These pseudo counts track the occurrence of a heuristic, an entity and resulting performance of these two elements.
-Through the credit assignment strategy that was discussed in Section \ref{sec:bhh:credit_assignment_strategy}, these pseudo counts are biased towards entity-heuristic combinations that meet credit requirements and yield credit allocations i.e.
-credit pseudo counts.
-It is through this concept that the \ac{BHH} is able to bias selection towards performance.
-
-The above mentioned concepts discuss heuristic selection bias by means of online learning.
+Through the credit assignment strategy, these pseudo counts are biased towards entity-heuristic combinations that meet performance requirements and yield credit allocations.
+
+The \acs{BHH} is an adaptive \ac{HH}, meaning that it implements online learning.
+Online learning refers to a process where learning happens during the training process.
+Throughout the training process, concentration parameters are updated strategically to guide the selection mechanism towards heuristics that perform well.
+The learning capability of the \acs{BHH} lies in carefully updating these concentration parameters.
 Another possibility is to introduce \textit{a priori} information in the form of expert knowledge.
-This concept is discussed next.
-
-\index{A Priori Bias}
-\subsection{A Priori Bias}
-\label{sec:bhh:optimisation_step:a_priori_bias}
-
-Section \ref{sec:bhh:optimisation_step:performance_bias} above discusses the role of concentration parameters on the \ac{BHH}.
-It is further mentioned in Section \ref{sec:bhh:initialisation_step} that these concentration parameters are symmetrically initialised.
-This simply means that they are uniformly initialised to all have the value of one in all dimensions.
-
-Consider that the intent of the \ac{BHH} is to learn which heuristics to select during training.
-An expert can inject expert knowledge into the \ac{BHH} by means of these concentration parameters.
-An example of this is given as follows.
-It might be well known that a particular heuristic will perform well on a given problem domain.
-This could be through empirical analysis, part experiences, logical reasoning and deduction or simply by nature of the heuristic itself.
-A slight bias can be introduced to this heuristic before training starts but slightly scaling the initialised concentration parameter for that particular heuristic so that is more than the other concentration parameters.
-The \ac{BHH} interprets this encoded concentration parameter as a prior belief and aims to update this parameter as new evidence is collected.
-The next section introduces the mathematics behind \ac{MLE}.
-
-\index{Maximum Likelihood Estimation}
-\subsection{Maximum Likelihood Estimation}
-\label{sec:bhh:optimisation_step:mle}
-
-In probability theory and statistics, \ac{MLE} is a method that estimates the parameters of some assumed prior probability distribution given newly observed data and evidence.
-This section shows that the values for $\theta$, $\phi$ and $\psi$ can be estimated by \ac{MLE} to yield equations \ref{eq:bhh:optimisation_step:mle:theta}, \ref{eq:bhh:optimisation_step:mle:phi} and \ref{eq:bhh:optimisation_step:mle:psi} below.
+A priori biases can be introduced by carefully setting the concentration parameters to values that are known to be good.
+
+Generally, there are two different techniques that are used to train Naïve Bayes classifiers.
+The frequentist approach implements \acf{MLE} and the Bayesian approach implements \acf{MAP}.
+These methods are provided in Sections \ref{sec:bhh:optimisation_step:mle} and \ref{sec:bhh:optimisation_step:map} respectively and show how the concentration parameters are updated throughout the training process, yielding the mechanism by which optimisation and learning takes place.
+It should be mentioned that the \acs{BHH} makes use of \acs{MAP} to optimise the predictive model.
+However, the details of \acs{MLE} is provided as well as it contains fundamental mathematical building blocks that are required to present \acs{MAP}.
+
+\index{maximum likelihood estimation}
+\subsection{Maximum Likelihood Estimation}\label{sec:bhh:optimisation_step:mle}
+
+In probability theory and statistics, \acf{MLE} is a method that estimates the parameters of a prior probability distribution given newly observed data and evidence.
+This section shows that the values for $\theta$, $\phi$ and $\psi$ can be estimated by \ac{MLE} and is given in Equations \eqref{eq:bhh:optimisation_step:mle:theta}, \eqref{eq:bhh:optimisation_step:mle:phi} and \eqref{eq:bhh:optimisation_step:mle:psi} below.
 
@@
 
-The calculations of the \ac{MLE} for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and
-$\hat{\psi}_{k}$ are now presented. The log likelihood of $\hat{\theta}$, $\hat{\phi}$ and $\hat{\psi}$ as derived
-from the Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} is given in Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} below.
+\noindent
+The derivations of the \acs{MLE} for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and
+$\hat{\psi}_{k}$ are presented as follows.
+The log likelihood of $\hat{\theta}$, $\hat{\phi}$ and $\hat{\psi}$ as derived from the Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} is given in Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} below.
 
@@
 
-Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} can be broken down into each of its factors.
+\noindent
+Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} can be broken down into each of its components.
 Consider the log likelihood of $\psi$ as denoted by Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_psi} below.
@@
 
-The MLE for $\hat{\psi_{k}} $ can be calculated by taking the derivative of Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_psi} with respect to $\psi_{k}$ and equating to zero as presented in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_psi} as follows.
+\noindent
+The \acs{MLE} for $\hat{\psi_{k}} $ can be calculated by taking the partial derivative of Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_psi} with respect to $\psi_{k}$ and equating to zero as presented in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_psi} as follows.
 
@@
 
-The value for $\hat{\theta_{k}} $ can be calculated similarly.
-However, one has to compensate for the $K-1$ simplex $S$ by adding error factor $\epsilon$ to correct values for  $\theta$ where $\sum_{k}^{K} \theta_{k} \neq 1$.
+\noindent
+The \acs{MLE} for $\hat{\theta_{k}} $ can be calculated similarly.
+However, one has to compensate for the $K-1$ simplex $S$ by adding error factor $\epsilon$, to correct values for $\theta$, where $\sum_{k}^{K} \theta_{k} \neq 1$.
 The new log likelihood function is then given in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_1} below.
@@
 
+\noindent
 Solving first for $\epsilon$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_2} below.
@@
 
+\noindent
 Then solving for $\theta_{k}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} as presented below.
@@
 
-Substituting back into the Equation yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_4} below.
+\noindent
+Substituting $N = \epsilon$ back into Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_4} below.
 
@@
 
-The value for $\hat{\phi}_{j, k} $ is calculated very similarly.
-To compensate for the $K-1$ simplex $S$ an error factor $\lambda = (\lambda_{1}, \dots, \lambda_{J})$ is added.
-This follows in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_1} as is presented below.
+\noindent
+The \acs{MLE} for $\hat{\phi}_{j, k} $ is calculated similarly.
+To compensate for the $K-1$ simplex $S$ an error $\lambda = (\lambda_{1}, \dots, \lambda_{J})$ is added as is shown in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_1} below.
 
@@
 
+\noindent
 Solving first for $\lambda_{j}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_2} as is given below.
@@
 
+\noindent
 Then solving for $\phi_{j,k}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} below.
@@
 
-Substituting back into the Equation yields equation \ref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_4} below.
+\noindent
+Substituting $N_{j} = \lambda_{j}$ back into Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_4} below.
 
@@
 
-This section provided the mathematical derivations of the MLE equations for $\theta$, $\phi$ and $\psi$.
-The next section provides the detail around \ac{MAP}, the optimisation process utilised by the \ac{BHH}.
-
-\index{Maximum a Posteriori Estimation}
-\subsection{Maximum a Posteriori Estimation}
-\label{sec:bhh:optimisation_step:map}
+\index{maximum a posteriori estimation}
+\subsection{Maximum A Posteriori Estimation}\label{sec:bhh:optimisation_step:map}
 
@@
 This process is referred to as \index{Bayesian analysis}\textit{Bayesian analysis}.
-This section provides the mathematical details of the Bayesian analysis and \ac{MAP} as it is implemented by the \ac{BHH}.
-
-Bayesian analysis makes use of the \textit{posterior} probability distribution. The posterior distribution is simply expressed as:
-
-\begin{equation*}
+This section provides the mathematical details of Bayesian analysis and \acf{MAP} as it is implemented by the \acs{BHH}.
+
+Bayesian analysis makes use of the \textit{posterior} probability distribution. The posterior distribution is simply expressed proportionally as follows.
+
+\begin{equation}
       \label{eq:bhh:optimisation_step:map:bayesian_analysis_lamens}
@@
       \end{split}
-\end{equation*}
-
-The likelihood is presented in Equation~\eqref{eq:bhh:optimisation_step:map:bayesian_analysis_lamens} above.
-The event $H$ is a multinomial distribution with parameter $\theta$.
-It is known that the conjugate prior to a multinomial distribution is a Dirichlet probability distribution (see Chapter \ref{chap:probability}.
+\end{equation}
+
+\noindent
+The event $H$ is a multinomial distribution with probability parameter $\theta$.
+It is known that the conjugate prior to a multinomial distribution is a \index{Dirichlet probability distribution}Dirichlet probability distribution.
 The \textit{prior} probability distribution for $\theta_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_theta_prior} below.
@@
 
+\noindent
 Furthermore, the event $E$ is also a multinomial distribution with parameter $\phi$.
@@
 
-Finally, the event $C$ is a\index{Binomial probability distribution}Binomial probability distribution with parameter $\psi$.
-It is known that the conjugate prior to a\index{Binomial probability distribution}Binomial probability distribution is a Beta probability distribution (see Chapter \ref{chap:probability}).
+\noindent
+Finally, the event $C$ is a \index{Binomial probability distribution}Binomial probability distribution with probability parameter $\psi$.
+It is known that the conjugate prior to a\index{Binomial probability distribution}Binomial probability distribution is a Beta probability distribution.
 The prior probability distribution for $\psi_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.
@@
 
+\noindent
 Putting the likelihood and priors together yields the posterior distribution as given in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.
@@
       \begin{split}
-            & P(\theta, \phi, \psi \vert H, E, C;  \alpha, \beta, \gamma_{1}, \gamma_{0}) \\
+            P(\theta, \phi, \psi \vert H, E, C;  \alpha, \beta, \gamma_{1}, \gamma_{0})
             &\propto P(H \vert E, C; \theta, \phi, \psi)P(\theta, \phi, \psi \vert \alpha, \beta, \gamma_{1}, \gamma_{0}) \\
-            &\propto P(E \vert H; \phi) P(C \vert H; \psi) P(H \vert \theta) P(\phi \vert \beta) P(\psi \vert \gamma_{1}, \gamma_{0}) P(\theta \vert \alpha)  \\
-            &\propto \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right] \\
-            &\times \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{\beta_{j,k} - 1} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{\gamma_{1,k} - 1} (1 - \psi_{k})^{\gamma_{2,k} - 1} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} - 1} \right] \\
-            &\propto \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{(N_{j,k} + \beta_{j,k}) - 1} \right] \\
+            &= P(E \vert H; \phi) P(C \vert H; \psi) P(H \vert \theta) P(\phi \vert \beta) \\
+            &\times P(\psi \vert \gamma_{1}, \gamma_{0}) P(\theta \vert \alpha)  \\
+            &= \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right] \\
+            &\times \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{\beta_{j,k} - 1} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{\gamma_{1,k} - 1} (1 - \psi_{k})^{\gamma_{2,k} - 1} \right] \\
+            &\times \left[ \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} - 1} \right] \\
+            &= \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{(N_{j,k} + \beta_{j,k}) - 1} \right] \\
             &\times \left[ \prod_{k=1}^{K} \psi_{k}^{(N_{1,k} + \gamma_{1,k}) - 1} (1 - \psi_{k})^{(N_{0,k} + \gamma_{2,k} )- 1} \right] \\
@@
 
+\noindent
 From Equation~\eqref{eq:bhh:optimisation_step:map:posterior} above, it can be seen that the posterior distribution has the same form $\mathcal{A}(v)$ as the prior distribution.
-The concentration update operations can then be given in equations \ref{eq:bhh:optimisation_step:map:alpha_update_operation}, \ref{eq:bhh:optimisation_step:map:beta_update_operation}, \ref{eq:bhh:optimisation_step:map:gamma1_update_operation} and \ref{eq:bhh:optimisation_step:map:gamma2_update_operation} below.
+The concentration update operations can then be given in Equations \eqref{eq:bhh:optimisation_step:map:alpha_update_operation}, \eqref{eq:bhh:optimisation_step:map:beta_update_operation}, \eqref{eq:bhh:optimisation_step:map:gamma1_update_operation} and \eqref{eq:bhh:optimisation_step:map:gamma2_update_operation} below.
 
@@
 
+\noindent
 It can be seen that the prior and posterior probability distributions are of the same shape $\mathcal{A}(v)$.
-It can therefore be said that the \ac{BHH} implements a Gaussian process.
-Since the reselection of heuristics happen at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration.
-It can thus be said that the \ac{BHH} implements a \ac{HMM}.
-
-The section concludes the optimisation process that is implemented by the \ac{BHH}.
-Throughout this chapter a number of hyper-parameters have been identified.
-These are summarised and discussed in the next section.
-
-\index{Hyper-Parameters}
-\section{Hyper-Parameters}
-\label{sec:bhh:hyper_parameters}
-
-This section provides the reader with a breakdown of all the hyper-parameters that were identified and briefly mentioned in this chapter.
+It can therefore be said that the \acs{BHH} implements a Gaussian process.
+Since the reselection of heuristics happen at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acf{HMM}.
+
+Throughout this chapter a number of hyper-parameters have been identified. These are summarised and discussed in the next section.
+
+\section{Hyper-Parameters}\label{sec:bhh:hyper_parameters}
+
+This section provides a breakdown of all the hyper-parameters that were identified and briefly mentioned in this chapter.
 Some logical arguments can be made as to what their values should be, however it is still up to empirical analysis to determine the effects of certain hyper-parameter design decisions.
 Were possible, a range of possible values is provided.
-Each of the hyper-parameters are discussed in their own sections next.
-
-\index{Heuristic Pool}
-\subsection{Heuristic Pool}
-\label{sec:bhh:hyper_parameters:heuristic_pool}
-
-Section \ref{sec:bhh:heuristic_pool} provided the reader with the context and detail of the \index{heuristic pool}heuristic pool as it is included in the architecture of the \ac{BHH}.
+
+\index{heuristic pool}
+\subsection{Heuristic Pool}\label{sec:bhh:hyper_parameters:heuristic_pool}
+
+Section \ref{sec:bhh:heuristic_pool} provided the reader with the context and detail of the \index{heuristic pool}heuristic pool as it is included in the architecture of the \acs{BHH}.
 A detailed discussion was given around the importance of diversity and balancing exploration and exploitation capabilities.
 The \index{heuristic pool}heuristic pool hyper-parameter refers to the heuristic-pool configuration that is used.
-This configuration should account for the following factors.
-
-\begin{itemize}
-      \item The type of low-level heuristics to include in the \index{heuristic pool}heuristic pool. This dissertation investigates two main groups including gradient-based and meta-heuristics.
-      \item The low-level heuristic's hyper-parameters. At a lower-level, each of these heuristics have their own set of hyper-parameters.
+The configuration of the \index{heuristic pool}heuristic pool should account for the following factors.
+
+\begin{itemize}
+      \item The type of low-level heuristics to include in the \index{heuristic pool}heuristic pool.
+This dissertation investigates two main groups, including gradient-based \index{heuristic}heuristics and meta-heuristics.
+
+      \item The low-level heuristics' hyper-parameters. At a lower-level, each of these heuristics have their own set of hyper-parameters.
+
       \item The \index{heuristic pool}heuristic pool size. This refers to the number of heuristics in the \index{heuristic pool}heuristic pool.
@@
 
-The granularity of design choices at a high level is not as strict for the \ac{BHH} as it is for low-level heuristics.
-If one is unsure as to which low-level hyper-parameters to use, one could simply include multiple configurations of that low-level heuristic, each just with its own unique hyper-parameter configurations.
-Take note that it has not been established yet if this is to the benefit or detriment of \ac{BHH}.
-These configurations increase the \index{heuristic pool}heuristic pool size and could also counteract eachother.
-It is thus still important to include relevant heuristics that is appropriate to the underlying problem being solved.
-These heuristics should contain a balance between exploration and exploitation, either through the nature of their implementation or through careful hyper-parameter selection.
-Often times hyper-parameter schedules are used.
-This is also possible with the \ac{BHH}.
-
-\subsection{Population Size}
-\label{sec:bhh:hyper_parameters:population_size}
-
-\textit{Population size} refers to the number of entities included in the \index{entity pool}entity pool/population.
-The exact population size to use is to be determined empirically.
-Naturely, an assumption is made that a larger population could lead to better results, assuming that entities are initialised to be spread uniformly across the solution search space.
-Oldewage~\cite{ref:oldewage:2017} mentions that a large number of particles (entities) may be able to traverse a greater portion of the search space as every particle provides additional information about the search space.
-However, it is to be determined if this is indeed the case for the \ac{BHH}.
-The authors propose the following considerations when picking a \index{population size}population size:
-
-\begin{itemize}
-      \item When considering the lower bound of possible \index{population size}population sizes, take into account the highest, minimum \index{population size}population size required by all low-level \index{heuristic}heuristics.
-For example, if one includes \Ac{DE} into the \index{heuristic}heuristic pool, one needs a \index{population size}population size of at least 4.
-For \acp{PSO}, the minimum population size is 3.
-      \item When considering the upper bound of possible \index{population size}population sizes, take into account that the bigger the \index{population size}population size, the more computationally expensive it is to execute the training process.
-Furthermore, there could exists a point of \index{diminishing returns}\textit{diminishing returns} where an increase in \index{population size}population size does not yield any better outcome.
-Once again, this is to be empirically tested.
-To extend on this, consider that the \Ac{BHH} is a \Ac{HH} that utilises a \index{Bayesian}Bayesian probabilistic approach in it's selection mechanism.
-This means that a larger observed sample size (of entity and heuristic selection events) is needed to statistically and reliably update the selection mechanism's trainable parameters.
-\end{itemize}
-
-\subsection{Credit}
-\label{sec:bhh:hyper_parameters:credit}
+\noindent
+The granularity of design choices at a high level is not as strict for the \acs{BHH} as it is for low-level heuristics.
+If one is unsure as to which low-level hyper-parameters to use, one could simply include multiple configurations of a low-level heuristic, each with its own unique hyper-parameter configurations.
+
+\subsection{Population Size}\label{sec:bhh:hyper_parameters:population_size}
+
+Population size refers to the number of entities included in the \index{entity pool}entity pool.
+The population size to use is to be determined empirically.
+Naturely, an assumption is made that a larger population could lead to better results, assuming that entities are initialised uniformly across the solution search space.
+\citeauthor{ref:oldewage:2017}~\cite{ref:oldewage:2017} mentions that a large number of particles (entities) may be able to traverse a greater portion of the search space as every particle provides additional information about the search space.
+However, it is to be determined if this is indeed the case for the \acs{BHH}.
+The following factors need to be considered when picking a population size.
+
+\begin{itemize}
+      \item When considering the lower bound of possible population sizes, take into account the highest, minimum population size required by all low-level \index{heuristic}heuristics.
+For example, if one includes \Acs{DE} into the \index{heuristic}heuristic pool, one needs a population size of at least 4.
+For \acs{PSO}, the minimum population size is 3.
+
+      \item When considering the upper bound of possible population sizes, take into account that a bigger population size results in a more computationally expensive training process.
+Furthermore, there could exists a point of \textit{diminishing returns} where an increase in population size does not yield any better outcome.
+\end{itemize}
+
+\subsection{Credit}\label{sec:bhh:hyper_parameters:credit}
 
@@
 The choice of credit assignment is assumed to be problem-dependent, however, this is to be empirically tested.
-Apart from the credit assignment strategy itself, one has to consider the following components related to credit assignment:
-
-\begin{itemize}
-      \item When to apply credit?
-      \item What should the credit assignment score be (default = 1)
-      \item To what degree should credit assignment be allocated to past results in the performance log
-\end{itemize}
-
-It should be noted that this dissertation proposed an initial set of credit assignment strategies that are discrete in outcome.
-Perhaps an alternative is to include some measure of success, not just an indicator of success.
-This allows for the implementation of continuous valued outcomes from the credit assignment strategies.
-Take into account that this could also drastically increase the complexity of the underlying predictive model implemented by the \ac{BHH}.
-
-A number of other hyper-parameters are specifically included to address the above challenges.
-These include \textit{reselection}, \textit{replay} and \textit{reanalysis window sizes} along with \textit{burn in}, \textit{discounted rewards} and \textit{normalisation}.
-These are discussed next.
-
-\index{Reselection}
-\subsection{Reselection}
-\label{sec:bhh:hyper_parameters:reselection}
-
-The reselection window size is a hyper-parameter that controls how often heuristic selections are resampled from the heuristic distribution, parameterised by the heuristic selection probability that is learnt as was discussed in Section \ref{sec:bhh:selection_mechanism:predictive_model}.
+Along from the credit assignment strategy itself, the following factors related to the credit assignment strategy should be considered.
+
+\begin{itemize}
+      \item When to apply credit assignment during the training process.
+      \item What should the credit assignment score/value be (default = 1).
+      \item To what degree should credit assignment be allocated to past results in the performance log.
+\end{itemize}
+
+\noindent
+A number of other hyper-parameters are specifically included to address the list of considerations as given above.
+These include \textit{reselection}, \textit{replay} and \textit{reanalysis window sizes},\textit{burn in}, \textit{discounted rewards} and \textit{normalisation}.
+Each of these are presented next.
+
+\subsection{Reselection}\label{sec:bhh:hyper_parameters:reselection}
+
+The reselection window size is a hyper-parameter that controls how often heuristic selections are resampled from the heuristic distribution, parameterised by the heuristic selection probability that is learnt.
 The choice of reselection should be influenced by the following considerations.
-If reselection happens too frequently, it does not allow heuristics sufficient time to smooth out update steps which could be detrimental to the outcomes of the \ac{BHH}.
-If reselection happens too infrequently, it does not allow for sufficient room to collect samples/evidence from which learning is done.
+If reselection happens too frequently, it does not allow heuristics sufficient time to achieve their goals and smooth out update steps.
+If reselection happens too infrequently, it does not allow for sufficient collection of samples/evidence from which learning is done.
 Naturally, the correct reselection window size to use is to be determined empirically.
 
-\index{Replay}
-\subsection{Replay}
-\label{sec:bhh:hyper_parameters:replay}
-
-The replay window size is a hyper-parameter that controls how much historical performance information is kept in memory for the \ac{BHH} to learn from.
-This is a parameter that is borrowed from \ac{RL} and aims to control the effect that past performances has on the \ac{BHH}.
-An assumption is made that the correct replay window size  to use could be problem dependent.
-However, logical arguments can be deduced.
-A replay window size that is too small includes little to no memory.
-This results in a situation where the \ac{BHH} simply looks at the most recent evidence that is collected and nothing more.
-This could be a beneficial or detrimental to the \ac{BHH}.
-On the contrary, if the replay window size is big, then the \ac{BHH} tracks a longer history of past performances.
-Once again, the this could be beneficial or detrimental to the \ac{BHH}.
-
-\index{Reanalysis}
-\subsection{Reanalysis}
-\label{sec:bhh:hyper_parameters:reanalysis}
-
-The reanalysis window size is a hyper-parameter that controls how often the \ac{BHH} updates its past beliefs (priors).
-Consider that this parameter goes hand in hand with the reselection and replay window sizes.
-If the reanalysis window is too small, the \ac{BHH} prematurely updates its priors.
+\subsection{Replay}\label{sec:bhh:hyper_parameters:replay}
+
+The replay window size is a hyper-parameter that controls how much historical performance information is kept in the performance log for the \acs{BHH} to learn from and was introduced in Section \ref{sec:bhh:performance_log}.
+The replay window size is a parameter that is borrowed from \acf{RL} and aims to control the effect that past performances have on the \acs{BHH}.
+A replay window size that is too small includes little to no memory, resulting in a situation where the \acs{BHH} simply looks at the most recent evidence that is collected and nothing more.
+On the contrary, if the replay window size is big, the \acs{BHH} tracks a longer history of past performances, leading to a situation where previously well-performing heuristics that are not relevant later in the training process is still selected often.
+
+\subsection{Reanalysis}\label{sec:bhh:hyper_parameters:reanalysis}
+
+The reanalysis window size is a hyper-parameter that controls how often the \acs{BHH} updates its past beliefs (priors).
+The reanalysis window size goes hand in hand with the reselection and replay window sizes.
+If the reanalysis window is too small, the \acs{BHH} prematurely updates its priors.
 Similar to other hyper-parameters discussed thus far, the correct value to use for the reanalysis window size is to be determined empirically.
 However, some logical exclusions can be made.
-A reanalysis window size that is smaller than the reselection window size does not make sense, since the effects of reanalysis is only realised during reselection.
-A reanalysis window size that is too big could lead to a situation where the delay in updating priors could be detrimental to the outcomes of the \ac{BHH}.
-
-\index{Burn In}
-\subsection{Burn In}
-\label{sec:bhh:hyper_parameters:burn_in}
-
-Burn in is a hyper-parameter that is borrowed from \ac{MCMC} and aims to delay the learning process of the \ac{BHH}.
-The intent of this hyper-parameter is to determine if heuristics need time to execute before reselection starts.
+A reanalysis window size that is smaller than the reselection window size does not make sense, since the effects of reanalysis are only realised during reselection.
+A reanalysis window size that is too big could lead to a situation where the delay in updating priors could be detrimental to the outcomes of the \acs{BHH}.
+
+\subsection{Burn In}\label{sec:bhh:hyper_parameters:burn_in}
+
+Burn in is a hyper-parameter that is borrowed from \acf{MCMC} and aims to delay the learning process of the \acs{BHH}.
+The intent of the burn in hyper-parameter is to determine if heuristics need time to execute before reselection starts.
 Notice that a delay in the learning process does not mean that reselection doesn't occur or performance information is not collected in the replay window.
 Therefore, it should be noted that the burn in window size, reselection window size and replay window size should be considered together.
-If the replay size is smaller than the burn in window size, no performance information is accumulated and the \ac{BHH} essentially starts with a prior that is no better than the initial symmetric initialisation that was done.
-
-\index{Discounted Rewards}
-\subsection{Discounted Rewards}
-\label{sec:bhh:hyper_parameters:discounted_rewards}
-
-Discounted rewards is another hyper-parameter that is borrowed from \ac{RL}.
-This hyper-parameter is a flag that determines if discounted rewards is enabled or not.
-Discounted rewards refers to an operation where the credit assignments for past performance is exponentially decreased further into the past.
-An exponential decay factor or 0.5 is proposed.
-The intent of the discounted rewards flag is to scale the effect of past performances that are further back into the performance log such that they have a smaller impact than more recent evidence on the performance achieved by the \ac{BHH}.
-
-\index{Normalisation}
-\subsection{Normalisation}
-\label{sec:bhh:hyper_parameters:normalisation}
+If the replay window size is smaller than the burn in window size, performance information is discarded and an opportunity to learn is lost.
+
+\index{discounted rewards}
+\subsection{Discounted Rewards}\label{sec:bhh:hyper_parameters:discounted_rewards}
+
+\index{discounted rewards}Discounted rewards is another hyper-parameter that is borrowed from \acs{RL} and is a flag that determines if discounted rewards are applied or not.
+\index{discounted rewards}Discounted rewards refers to an implementation where credit assignments for past performances are exponentially decreased further into the past.
+An exponential decay factor of 0.5 is proposed.
+The intent of the discounted rewards flag is to scale the effect of past performances that are further back in the performance log, such that they have a smaller impact than more recent evidence on the learning process of the \acs{BHH}.
+
+\subsection{Normalisation}\label{sec:bhh:hyper_parameters:normalisation}
 
@@
 Figure \ref{sec:bhh:hyper_parameters:discounted_rewards:normalisation} shows the effect of different concentrations ($\alpha$ and $\beta$) on the Beta probability distribution.
-By normalising the concentration parameters for the \ac{BHH} ($\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$), the variance of the selection probability distributions increase, allowing for sampled probabilities further from the mean and thus allowing for more exploration.
+By normalising the concentration parameters for the \acs{BHH} ($\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$), the variance of the selection probability distributions increases, allowing for sampled probabilities further from the mean and thus allowing for more exploration.
 
 \begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \includegraphics[width=\textwidth]{images/beta_1_1.png}
+      \begin{subfigure}{0.49\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{images/beta_1_1.pdf}
             \caption{$\alpha=1$, $\beta=1$}
@@
       \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \includegraphics[width=\textwidth]{images/beta_5_5.png}
+      \begin{subfigure}{0.49\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{images/beta_5_5.pdf}
             \caption{$\alpha=5$, $\beta=5$}
@@
       \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
+      \begin{subfigure}{0.49\textwidth}
             \centering
-            \includegraphics[width=\textwidth]{images/beta_20_20.png}
+            \centering
+            \includegraphics[width=\textwidth]{images/beta_20_20.pdf}
             \caption{$\alpha=20$, $\beta=20$}
@@
       \par\bigskip
-      \caption{Beta probability distribution with varying $\alpha$ and $\beta$ values.}
+      \caption{The \index{Beta probability distribution}Beta probability distribution with varying $\alpha$ and $\beta$ values.}
       \label{sec:bhh:hyper_parameters:discounted_rewards:normalisation}
@@
 
-This concludes the hyper-parameters that are used by the \ac{BHH}. The following section discusses the default value for proxied update step operations.
+\noindent
+The following section discusses the default values for proxied update step operations.
 
@@
 As was mentioned in Section \ref{sec:bhh:hyper_parameters:heuristic_pool}, low-level heuristics each have their own set of hyper-parameters as well.
-This means that a set of default low-level parameters must be allocated specifically for these proxies.
-Consider a scenario where two instances of \ac{Adam} is included in the \index{heuristic pool}heuristic pool.
-Each has its own set of hyper-parameters that (should) differ from each other.
-In the case of \ac{Adam}, there are 4 hyper-parameters that include learning rate, $\beta1$, $\beta2$ and $\epsilon$.
-If another heuristic needs to proxy \ac{Adam}'s ``expected gradient mean operation'', a default $\beta1$ parameter must be supplied.
-Notice that this is only the case where multiple instances of a heuristic is included and there is uncertainty about which instance's hyper-parameters to use for the proxied heuristic update steps.
+A set of default low-level parameters must be allocated specifically for these proxies.
+Consider a scenario where two instances of \acs{Adam} is included in the \index{heuristic pool}heuristic pool.
+Each has its own set of hyper-parameters that differ from each other.
+In the case of \acs{Adam}, there are 4 hyper-parameters that include learning rate, $\beta1$, $\beta2$ and $\epsilon$.
+If another heuristic needs to proxy \acs{Adam}'s expected gradient mean operation, a default $\beta1$ parameter must be supplied that is applied by the proxy mechanism.
+This is only the case when multiple instances of a heuristic is included and there is uncertainty about which instance's hyper-parameters to use for the proxied heuristic update steps.
 If there is only one instance of a particular heuristic, that instance's hyper-parameters are used.
-The next section provides the reader with the pseudo-code algorithm for the \ac{BHH}.
+
+The next section provides the reader with the pseudo-code algorithm for the \acs{BHH}.
 
@@
 
-This section provides the reader with a high level pseudo-code implementation of the \ac{BHH}. This is given in Algorithm \ref{algo:bhh} below.
+The high level pseudo-code implementation of the \acs{BHH} is given in Algorithm \ref{algo:bhh}.
 
 \begin{algorithm}[H]
-      \caption{The pseudo code for the \index{Bayesian Hyper-Heuristic} Bayesian Hyper-Heuristic optimiser}
+      \caption{The pseudo-code for the implementation of the \acf{BHH}}
       \label{algo:bhh}
@@
             \State update population state
-            \State log performance to performance log
+            \State log performance metrics to performance log
 
@@
 
-This chapter provided the reader with extensive detail on the inner workings and design of the \ac{BHH}.
-The \ac{BHH} was formally classified and the details around various components of the \ac{BHH}'s architecture was presented.
+This chapter provided extensive detail on the inner workings and design of the \acs{BHH}.
+The \acs{BHH} was formally classified and the details around various components of the \acs{BHH}'s architecture was presented.
 Formal mathematical descriptions of the Bayesian selection method have been provided.
-The optimisation process, by means of Bayesian analysis has been presented and a pseudo code implementation of the \ac{BHH} was presented.
-
-This concludes the background information and literature studies that is required to propose a methodology for an empirical process. This methodology is provided in the next chapter.
+The selection mechanism was presented as a probabilistic, predictive classifier.
+The optimisation process, by means of Bayesian analysis, has also been presented.
+Hyper-parameters were discussed in detail and a pseudo code implementation of the \acs{BHH} was presented.
+
+This methodology for the empirical process is provided in the following chapter.

### 2022-11-05 dissertation/chapters/06-bayesian-hyper-heuristic.tex
✨ (chapter6): Review Done

@@
 The above quote was the inspiration for the development of a novel \acf{HH} that uses Bayesian probability concepts as a selection mechanism to drive the heuristic selection process.
-Thus far the reader has been presented with all of the necessary background information on \acp{ANN} (Chapter \ref{chap:anns}), low-level \index{heuristic}heuristics (Chapter \ref{chap:heuristics}), \acp{HH} (Chapter \ref{chap:hhs}) and lastly, probability theory(Chapter \ref{chap:probability}).
+Thus far the reader has been presented with all of the necessary background information on \acp{ANN} (Chapter \ref{chap:anns}), low-level \index{heuristic}heuristics (Chapter \ref{chap:heuristics}), \acp{HH} (Chapter \ref{chap:hhs}) and lastly, probability theory (Chapter \ref{chap:probability}).
 These elements form the fundamental components of the proposed \Acf{BHH}.
@@
 Entities are extended to include the primary state elements of \textit{all} the underlying low-level heuristics, as well as the candidate solution (weights) for the \acs{FFNN}.
-At each heuristic-entity application step, all state elements per entity are updated either by primary method or by proxied method.
+At each heuristic-entity application step, all state parameters, per entity, are updated either by primary method or by proxied method.
 The \acs{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.
@@
 \noindent
-The implementation of a credit assignment strategy is simply a function that translates the performance log from Table \ref{tab:bhh:performance_log:performance_log_example}, into Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example} below.
+The implementation of a credit assignment strategy is simply a function that translates the performance log from Table \ref{tab:bhh:performance_log:performance_log_example}, into Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}.
 
@@
 \noindent
-It should be noted that event information is stored and observed direclty from the performance log as presented in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}.
+It should be noted that event information is stored and observed directly from the performance log as presented in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}.
 From the above list of events, the event $C$ is dependent on the occurrence of $H$ and $E$ and a credit assignment strategy.
@@
 This section presents the predictive model as implemented by the selection mechanism of the \acs{BHH}.
-The predictive model is arguably the most important component of the \acs{BHH}, as it drives heuristic selection process.
+The predictive model is arguably the most important component of the \acs{BHH}, as it drives the heuristic selection process.
 The \acs{BHH} implements a predictive model that predicts which heuristic to select, given the conditionality that a particular entity is used and a particular credit assignment criteria is met.
@@
 \noindent
-Notice the joint probability over events $E$ and $C$, given the selection of a heuristic $H$, denoted by the sums of the products of the separate parts, for $E$ and $C$, in the denominator.
+Notice the joint probability over events $E$ and $C$, given the selection of a heuristic $H$, denoted by the product of the sums of the separate parts for $E$ and $C$, in the denominator.
 The calculation in the denominator can be intractable.
-Since the \acs{BHH} selection mechanism uses the predictive model as a classifier, the posterior distribution as given in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem}), can be evaluated for proportionality, as is given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} below.
+Since the \acs{BHH} selection mechanism uses the predictive model as a classifier, the posterior distribution as given in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem}, can be evaluated for proportionality, as is given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} below.
 
@@
 In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} above, $N_{j,k}$ is a summary variable such that $N_{j,k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on class $k$, i.e.
-the count of occurrences of both entity entity $e$ and heuristic $k$ occurring together in $I$ independent, identical runs.
+the count of occurrences of both entity $e$ and heuristic $k$ occurring together in $I$ independent, identical runs.
 
@@
 
-Mode collapse is the situation that occurs where the selective pressure towards a heuristic is close to zero as a results of random sampling, low initial bias or bad performance.
+Mode collapse is the situation that occurs where the selective pressure towards a heuristic is close to zero as a result of random sampling, low initial bias or bad performance.
 This leads to a situation where the probabilistic model continually decreases the selective pressure, until the selection probability of that heuristic is 0, yielding no further observations of that particular random event.
@@
 Another suggestion is to ensure that at least one of every heuristic is always selected during training.
-The \acs{BHH} does not incorporate this model as this could result in a situation where a bad choice of heuristic is continually used throughout the training process, possibly resulting in bad update steps/selections.
+The \acs{BHH} does not incorporate this approach as this could result in a situation where a bad choice of heuristic is continually used throughout the training process, possibly resulting in bad update steps/selections.
 Instead, the \acs{BHH} relies on the underlying learning process to control the selective pressure according to performance and nothing else.
@@
 The \acs{MLE} for $\hat{\phi}_{j, k} $ is calculated similarly.
-To compensate for the $K-1$ simplex $S$ an error $\lambda = (\lambda_{1}, \dots, \lambda_{J})$ is added as is shown in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_1} below.
+To compensate for the $K-1$ simplex $S$, an error $\lambda = (\lambda_{1}, \dots, \lambda_{J})$ is added as is shown in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_1} below.
 
@@
 Finally, the event $C$ is a \index{Binomial probability distribution}Binomial probability distribution with probability parameter $\psi$.
-It is known that the conjugate prior to a\index{Binomial probability distribution}Binomial probability distribution is a Beta probability distribution.
+It is known that the conjugate prior to a \index{Binomial probability distribution}Binomial probability distribution is a Beta probability distribution.
 The prior probability distribution for $\psi_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.
@@
 \noindent
-It can be seen that the prior and posterior probability distributions are of the same shape $\mathcal{A}(v)$.
+It can be seen that the prior and posterior probability distributions are of the same form, $\mathcal{A}(v)$.
 It can therefore be said that the \acs{BHH} implements a Gaussian process.
-Since the reselection of heuristics happen at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acf{HMM}.
+Since the reselection of heuristics happens at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acf{HMM}.
 
@@
 \noindent
-The granularity of design choices at a high level is not as strict for the \acs{BHH} as it is for low-level heuristics.
+The design choices at a high level is not as strict for the \acs{BHH} as it is for low-level heuristics.
 If one is unsure as to which low-level hyper-parameters to use, one could simply include multiple configurations of a low-level heuristic, each with its own unique hyper-parameter configurations.
@@
 This dissertation proposed 5 different credit assignment strategies that were presented in Section \ref{sec:bhh:credit_assignment_strategy}.
-The choice of credit assignment is assumed to be problem-dependent, however, this is to be empirically tested.
-Along from the credit assignment strategy itself, the following factors related to the credit assignment strategy should be considered.
+The choice of credit assignment is assumed to be problem-dependent, however, this is to be  tested empirically.
+Along with the credit assignment strategy itself, the following factors related to the credit assignment strategy should be considered.
 
@@
 A number of other hyper-parameters are specifically included to address the list of considerations as given above.
-These include \textit{reselection}, \textit{replay} and \textit{reanalysis window sizes},\textit{burn in}, \textit{discounted rewards} and \textit{normalisation}.
+These include \textit{reselection}, \textit{replay} and \textit{reanalysis window sizes}, \textit{burn in}, \textit{discounted rewards} and \textit{normalisation}.
 Each of these are presented next.
@@
 A replay window size that is too small includes little to no memory, resulting in a situation where the \acs{BHH} simply looks at the most recent evidence that is collected and nothing more.
-On the contrary, if the replay window size is big, the \acs{BHH} tracks a longer history of past performances, leading to a situation where previously well-performing heuristics that are not relevant later in the training process is still selected often.
+On the contrary, if the replay window size is big, the \acs{BHH} tracks a longer history of past performances, leading to a situation where previously well-performing heuristics that are not relevant later in the training process, is still selected often.
 
@@
 Burn in is a hyper-parameter that is borrowed from \acf{MCMC} and aims to delay the learning process of the \acs{BHH}.
-The intent of the burn in hyper-parameter is to determine if heuristics need time to execute before reselection starts.
+The intent of the burn in hyper-parameter is to determine if heuristics need time to execute before reanalysis starts.
 Notice that a delay in the learning process does not mean that reselection doesn't occur or performance information is not collected in the replay window.
@@
 \index{discounted rewards}Discounted rewards is another hyper-parameter that is borrowed from \acs{RL} and is a flag that determines if discounted rewards are applied or not.
-\index{discounted rewards}Discounted rewards refers to an implementation where credit assignments for past performances are exponentially decreased further into the past.
+\index{discounted rewards}Discounted rewards refer to an implementation where credit assignments for past performances are exponentially decreased further into the past.
 An exponential decay factor of 0.5 is proposed.

### 2022-11-06 dissertation/chapters/07-methodology.tex
🚧 (chapter7): Review WIP

@@
-\chapter{Methodology}
-\label{chap:methodology}
+\chapter{Methodology}\label{chap:methodology}
 
-\begin{quote}
-      \textit{Observation, reason and experimentation make up what we call the scientific method. $\sim$ Richard P. Feynman}
-\end{quote}
+\begin{quotation}
+      \noindent ``Observation, reason and experimentation make up what we call the scientific method.''
+\end{quotation}
+\begin{flushright}
+      - Richard P. Feynman
+\end{flushright}
 
-Chapter \ref{chap:introduction} set out the objectives of the dissertation.
-These objectives can broadly be split between background information and an empirical component.
-So far, chapters \ref{chap:introduction}-\ref{chap:bhh} provided the necessary background information.
-This chapter now provides the detailed specification of the methodology that is followed for the empirical process and the analysis of the results.
-The remainder of the chapter is structured as follows:
+\noindent
+So far this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acf{HH} and probability theory in Chapters \ref{chap:anns}-\ref{chap:probability}.
+Chapter \ref{chap:bhh} provided the detail of the implementation of the proposed \acs{BHH} with all its components and hyper-parameters.
+Scientific experimentation can now be established.
+Chapter \ref{chap:introduction} identified goals for this dissertation.
+The goals of this dissertation include an empirical evaluation of the \acs{BHH}, its behaviour and performance, and comparison to state of the art low-level heuristics.
+This chapter provides the detailed specification of the methodology that is followed for the empirical process.
+Details are provided on the implementation of experiments, datasets, selection of hyper-parameters and design decisions.
+The process by which the results are statistically analysed are also presented.
+The remainder of the chapter is structured as follows.
 
 \begin{itemize}
-      \item \textbf{Section \ref{sec:methodology:overview}} provides a brief overview of the entire empirical process, leaving the detail to subsequent sections.
+      \item \textbf{Section \ref{sec:methodology:overview}} provides a brief overview of the overall empirical process.
 
@@
 
-      \item \textbf{Section \ref{sec:methodology:model}} provides the details of the models (\acs{FFNN}s) that are being trained.
+      \item \textbf{Section \ref{sec:methodology:model}} provides the details of the models (\acs{FFNN}s) that are trained.
 
@@
 
-      \item \textbf{Section \ref{sec:methodology:experiments}} presents the different experimental groups that is executed.
+      \item \textbf{Section \ref{sec:methodology:experiments}} presents the different experimental groups that are executed.
 
-      \item \textbf{Section \ref{sec:methodology:implementation}} sheds some light as to the implementation and execution of the empirical process.
+      \item \textbf{Section \ref{sec:methodology:implementation}} sheds light on the implementation and execution of the empirical process.
 
-      \item \textbf{Section \ref{sec:methodology:statistical_analysis}} presents the procedures that are followed in during the statistical analysis of the results.
+      \item \textbf{Section \ref{sec:methodology:statistical_analysis}} presents the procedures that are followed for the statistical analysis of the results.
 
-      \item Finally, a summary of the chapter is provided in \textbf{Section \ref{sec:methodology:summary}}
+      \item \textbf{Section \ref{sec:methodology:summary}} presents a brief summary of the chapter.
 \end{itemize}
 
-\section{Overview of Empirical Process}
-\label{sec:methodology:overview}
+\section{Overview of Empirical Process}\label{sec:methodology:overview}
 
-The purpose of the empirical process is to present and execute a carefully crafted experiment/test that produces data that can be used to reject of verify some hypothesis about the element under investigation.
-This dissertation has outlined a set of 3 objectives that require such empirical processes to evaluate the \ac{BHH}.
-This section outlines what these empirical processes entail.
+The purpose of the empirical process is to conduct a carefully crafted set of experiments that produce data that can be used to reject of verify a hypothesis about the element under investigation.
+Chapter \ref{chap:introduction} identified a number of empirical tests to execute.
+These include:
 
-Each empirical test sets out some configuration of elements to be evaluated.
-These generally include a set of parameters that are altered between experiments.
+\begin{itemize}
+      \item An empirical study to show that the \Acs{BHH} can effectively be used to train \acp{FFNN}.
+
+      \item An empirical study to investigate the behavioural characteristics of the \Acs{BHH} as it is used to train \acp{FFNN} on an example problem.
+
+      \item An empirical study to critically evaluate the performance of the \Acs{BHH} compared to individual low-level heuristics in the heuristic space as they are used to train \acp{FFNN} on a number of different problems.
+\end{itemize}
+
+\noindent
+These empirical tests represent a set of questions, related to the \acs{BHH}, that need to be answered.
+The empirical process is designed to answer these questions.
+The empirical process is structured as follows.
+
+Each empirical tests starts with a question to be answered.
+A hypothesis is formulated for the outcome of the empirical test.
+The empirical tests are then designed around the implementation of the components under evaluation.
+Each empirical test defines the configuration of elements and generally include a set of parameters that are altered between experiments.
 Each experiment is evaluated by means of a performance measurement.
-In the context of training \acp{FFNN}, the underlying model (\ac{NN}) is trained across a number of datasets.
+In the context of training \acp{FFNN}, the underlying model is trained across a number of datasets.
 Each dataset is split into a training and test set.
-The training set is used to train the model, while the test set is used to evaluate the model.
+The training set is used to train the model, while the test set is used to evaluate the model's performance on unseen data.
 Training epochs are split into mini-batch iterations, with each dataset containing a specified mini-batch size.
 Evaluation takes place at every mini-batch step.
-These experiments contain a number of components, each with a set of paramaters.
-Due to the stochastic nature of the experiments, each experiment is repeated over a number of runs to provide sufficient sample for statistical certainty.
-Each run contains a different random seed.
-Each evaluation's results are analysed for statistical significance.
-It is from these statistical analyses that findings and conclusions are then made.
+Due to the stochastic nature of the experiments, each experiment is repeated over a number of runs to provide sufficient sample for statistical certainty about the outcome of the results.
+Each run contains a different random seed, such that each run is unique.
+The evaluation data forms the results of the empirical test.
+These results are analysed for statistical significance, from which findings and conclusions are then made.
+The null hypothesis is then either rejected or verified based on these findings.
 
-Detail around each of these elements are now provided, starting with the datasets that are used.
+Details around each of these elements are provided in the following sections and lead with discussions around the datasets that are used.
 
@@
                   mushroom         & multivariate    & categorical                & 22                  & 2                & 8214               & 512            & 17             & ~\cite{ref:schlimmer:1987} \\
-                  wine\_quality    & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & ~\cite{ref:cortez:2009}    \\
+                  wine quality     & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & ~\cite{ref:cortez:2009}    \\
                   bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & ~\cite{ref:moro:2014}      \\
@@
                   \midrule
-                  fish\_toxicity       & multivariate             & real           & 7                   & 908                & 64             & 15             & ~\cite{ref:cassotti:2015} \\
+                  fish toxicity       & multivariate             & real           & 7                   & 908                & 64             & 15             & ~\cite{ref:cassotti:2015} \\
                   housing             & univariate               & real           & 13                  & 506                & 32             & 16             & ~\cite{ref:harrison:1978} \\
-                  forest\_fires        & multivariate             & real           & 13                  & 517                & 32             & 17             & ~\cite{ref:cortez:2007}   \\
-                  student\_performance & multivariate             & integer        & 33                  & 649                & 32             & 21             & ~\cite{ref:cortez:2008}   \\
+                  forest fires        & multivariate             & real           & 13                  & 517                & 32             & 17             & ~\cite{ref:cortez:2007}   \\
+                  student performance & multivariate             & integer        & 33                  & 649                & 32             & 21             & ~\cite{ref:cortez:2008}   \\
                   parkinsons          & multivariate             & integer, real  & 26                  & 5875               & 256            & 23             & ~\cite{ref:tsanas:2009}   \\
-                  air\_quality         & multivariate, timeseries & real           & 15                  & 9358               & 256            & 37             & ~\cite{ref:de:2008}       \\
+                  air quality         & multivariate, timeseries & real           & 15                  & 9358               & 256            & 37             & ~\cite{ref:de:2008}       \\
                   bike                & univariate               & integer, real  & 16                  & 17389              & 256            & 68             & ~\cite{ref:fanaee:2014}   \\
@@
 
+\noindent
 Details on how the datasets where preprocessed and prepared is given in Appendix \ref{app:datasets}. The concept of class balancing is briefly discussed next.
@@
 
-A number of classification datasets as given in Table \ref{tab:methodology:datasets:classification} above contain unbalanced classes.
-A decision was made to not make use of class balancing.
-This was simply to eliminate as many variables adn factors in the empirical process as possible, as it is already a complicated process.
-It is therefore suggested that the \ac{BHH} first be studied under the assumption of balanced classes and then only apply class balancing.
+A number of classification datasets given in Table \ref{tab:methodology:datasets:classification} contain an unbalanced representation of classes.
+The empirical process defined in this dissertation does not apply mechanisms to cater for class balancing, in order to eliminate as many variables and factors in the empirical process as possible, as it is already a complicated process.
+It is therefore suggested that the \ac{BHH} first be studied under the assumption of balanced classes, before applying class balancing techniques.
 In future research opportunities, class balancing should be utilised.
 
-The next section presents the models and the configurations that are used.
+The next section presents the \acp{FFNN}/models and the configurations that are used in the empirical process.
 
-\section{Models}
-\label{sec:methodology:model}
+\section{Models}\label{sec:methodology:model}
 
-As the title of the dissertation suggests, these empirical process are focused on the training of \acp{FFNN}.
-In theory, one should be able to swap these \acp{FFNN} out for any other mathematical model that can be optimised.
-All models that are trained in this dissertation are shallow \acp{NN}, meaning they only have one hidden layer.
-The architecture of a model is dependent on the dataset being trained on, the type of problem it is (classification or regression), the number of input dimensions and the number of output dimensions.
-The models and their configuration, as it is used for each dataset, is given below in Table \ref{tab:methodology:models:configurations}
+All models that are trained in this dissertation follow implementations of shallow \acp{FFNN}, meaning they only have one hidden layer.
+The architecture of a model is dependent on the dataset being trained on, the type of optimisation problem, the number of input dimensions and the number of output dimensions.
+Models' initial weights are initialised by means of \index{Glorot uniform sampling}Glorot uniform sampling.
+The models and their configuration, as it is used for each dataset, is given in Table \ref{tab:methodology:models:configurations} below.
 
@@
                   \midrule
-                  fish\_toxicity       & 6               & 3               & 1               & yes             & 25                  & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+                  fish toxicity       & 6               & 3               & 1               & yes             & 25                  & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
                   iris                & 4               & 5               & 3               & yes             & 43                  & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  air\_quality         & 12              & 8               & 1               & yes             & 113                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+                  air quality         & 12              & 8               & 1               & yes             & 113                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
                   housing             & 13              & 8               & 1               & yes             & 121                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  wine\_quality        & 13              & 10              & 7               & yes             & 217                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+                  wine quality        & 13              & 10              & 7               & yes             & 217                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
                   parkinsons          & 21              & 10              & 1               & yes             & 231                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
                   car                 & 21              & 10              & 4               & yes             & 264                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  forest\_fires        & 43              & 16              & 1               & yes             & 721                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+                  forest fires        & 43              & 16              & 1               & yes             & 721                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
                   abalone             & 10              & 36              & 28              & yes             & 1432                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
@@
                   bike                & 61              & 32              & 1               & yes             & 2017                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  student\_performance & 99              & 32              & 1               & yes             & 3233                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+                  student performance & 99              & 32              & 1               & yes             & 3233                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
                   adult               & 108             & 64              & 1               & yes             & 7041                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
@@
 
-It should be noted that for the classification problems, the \index{softmax}softmax activation is not actually part of the model.
-It is just added for predictive output and is not needed during evaluation.
-The loss functions (\ac{SparseCatXE} and \ac{BinXE}) that are used contains a \index{softmax}softmax function.
-Models' initial weights are initialised by means of \index{Glorot uniform sampling}Glorot uniform sampling.
+\noindent
+For the classification problems presented in Tables \ref{tab:methodology:datasets:classification} and \ref{tab:methodology:models:configurations}, the softmax activation function is added after training and is not included in the model during training.
+The loss functions, \acf{SparseCatXE} and \acf{BinXE}, that are used, contain a \index{softmax}softmax function.
 
-\section{Heuristics/Optimisers}
-\label{sec:methodology:heuristics}
+\index{heuristic}
+\section{Heuristics}\label{sec:methodology:heuristics}
 
-This section provides the details of the standalone \index{heuristic}heuristics/optimisers that are used in the empirical process.
-
-Table \ref{tab:methodology:heuristics} contain a list of all the standalone \index{heuristic}heuristics that are used as well as their hyper-parameter configuration.
+This section provides the details of the low-level \index{heuristic}heuristics that are used in the empirical process.
+Each of these low-level heuristics are implemented as standalone heuristics and are also included in the heuristic pool of the \acs{BHH}.
+Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level \index{heuristic}heuristics that are used as well as their hyper-parameter configuration.
 
@@
       \centering
-      \caption{Heuristics/optimisers and their hyper-parameter configuration of their}
+      \caption{Low-level \index{heuristic}heuristics and their hyper-parameter configuration.}
       \label{tab:methodology:heuristics}%
       \par\bigskip
-      \resizebox{0.8\textwidth}{!}{
+      \resizebox{0.7\textwidth}{!}{
 
@@
                   \midrule
-                  sgd                & learning\_rate            & 0.1**0.01      & ~\cite{ref:sutskever:2013} \\
-                  momentum           & learning\_rate            & 0.1**0.01      & ~\cite{ref:sutskever:2013} \\
+                  sgd                & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
+                  momentum           & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
                                      & momentum                  & 0.9            &                            \\
-                  nag                & learning\_rate            & 0.1**0.01      & ~\cite{ref:sutskever:2013} \\
+                  nag                & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
                                      & momentum                  & 0.9            &                            \\
-                  adagrad            & learning\_rate            & 0.1**0.01      & ~\cite{ref:duchi:2011}     \\
+                  adagrad            & learning rate             & 0.1 (0.01)     & ~\cite{ref:duchi:2011}     \\
                                      & epsilon                   & 1E-07          &                            \\
-                  rmsprop            & learning\_rate            & 0.1**0.01      & ~\cite{ref:hinton:2012}    \\
+                  rmsprop            & learning rate             & 0.1 (0.01)     & ~\cite{ref:hinton:2012}    \\
                                      & rho                       & 0.95           &                            \\
                                      & epsilon                   & 1E-07          &                            \\
-                  adadelta           & learning\_rate            & 1.0**0.95      & ~\cite{ref:zeiler:2012}    \\
+                  adadelta           & learning rate             & 1.0 (0.95)     & ~\cite{ref:zeiler:2012}    \\
                                      & rho                       & 0.95           &                            \\
                                      & epsilon                   & 0.0000001      &                            \\
-                  adam               & learning\_rate            & 0.1**0.01      & ~\cite{ref:kingma:2014}    \\
+                  adam               & learning rate             & 0.1 (0.01)     & ~\cite{ref:kingma:2014}    \\
                                      & beta1                     & 0.9            &                            \\
@@
                                      & epsilon                   & 1E-07          &                            \\
-                  pso                & population\_size          & 10             & ~\cite{ref:van:2010}       \\
-                                     & learning\_rate            & 0.1**0.01      &                            \\
-                                     & inertia\_weight (w)       & 0.729844       &                            \\
-                                     & cognitive\_control (c1)   & 1.49618        &                            \\
-                                     & social\_control (c2)      & 1.49618        &                            \\
-                                     & velocity\_clip\_min       & -1.0           &                            \\
-                                     & velocity\_clip\_max       & 1.0            &                            \\
-                  de                 & population\_size          & 10             & ~\cite{ref:mezura:2006}    \\
-                                     & selection\_strategy       & best           &                            \\
-                                     & xo\_strategy              & exp            &                            \\
-                                     & recombination probability & 0.9**0.1       &                            \\
-                                     & beta                      & 2.0**0.1       &                            \\
-                  ga                 & population\_size          & 10             & ~\cite{ref:lambora:2019}   \\
-                                     & selection\_strategy       & rand           &                            \\
-                                     & xo\_strategy              & bin            &                            \\
-                                     & mutation\_rate            & 0.2**0.05      &                            \\
+                  pso                & population size           & 10             & ~\cite{ref:van:2010}       \\
+                                     & learning rate             & 0.1 (0.01)     &                            \\
+                                     & inertia weight (w)        & 0.729844       &                            \\
+                                     & cognitive control (c1)    & 1.49618        &                            \\
+                                     & social control (c2)       & 1.49618        &                            \\
+                                     & velocity clip min         & -1.0           &                            \\
+                                     & velocity clip max         & 1.0            &                            \\
+                  de                 & population size           & 10             & ~\cite{ref:mezura:2006}    \\
+                                     & selection strategy        & best           &                            \\
+                                     & xo strategy               & exp            &                            \\
+                                     & recombination probability & 0.9 (0.1)      &                            \\
+                                     & beta                      & 2.0 (0.1)      &                            \\
+                  ga                 & population size           & 10             & ~\cite{ref:lambora:2019}   \\
+                                     & selection strategy        & rand           &                            \\
+                                     & xo strategy               & bin            &                            \\
+                                     & mutation rate             & 0.2 (0.05)     &                            \\
             \end{tabular}%
@@
 
-Take note that for Table \ref{tab:methodology:heuristics}, values that contains an asterisk ($*$) are configured on a schedule with the initial value depicted first and the decay rate is depicted last.
-The number of steps is the total number of steps for that particular dataset it is being applied to.
+\noindent
+Note that from Table \ref{tab:methodology:heuristics}, values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it.
+The number of steps is the total number of mini-batch training steps that are executed for that particular dataset.
 
-Also take note that a learning rate was added to the \ac{PSO} as an attempt to avoid overshooting solutions later in the training process.
-This parameter does not traditionally form part of the \ac{PSO}, but it was found to work sufficiently here.
+Furthermore, it should be noted that a learning rate was added to \acs{PSO} as an attempt to avoid overshooting solutions later in the training process.
+This parameter does not traditionally form part of the \ac{PSO}, but was found to be useful.
 
-The next section provides the details around the \ac{BHH} baseline.
+Section \ref{sec:bhh:heuristic:proxies} presented the concept of a mapping of proxied heuristic state update operations.
+The mapping of proxied heuristic state update operations, implemented by the \acs{BHH} in the empirical process, is given in Figure \ref{fig:methodology:heuristics:proxies}.
 
-TODO: Proxy Mapping Table
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=0.95\textwidth]{images/bhh_heuristic_proxies.pdf}
+      \caption{Mapping of proxied heuristic state update operations as implemented by the \acs{BHH}}
+      \label{fig:methodology:heuristics:proxies}%
+\end{figure}
 
-\section{BHH Baseline}
-\label{sec:methodology:baseline_bhh}
+\noindent
+In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x}, indicate that the associated heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
+The required mapping of proxied heuristic state operations is then implemented as a lookup of the table presented in Figure \ref{fig:methodology:heuristics:proxies}.
 
-The \ac{BHH} baseline is a name given to a specific configuration of the \ac{BHH}, which during development, has been found to provide reasonable performance.
-It was decided that this configuration will be the cornerstone configuration from which all other \index{heuristic}heuristics and their configurations are evaluated.
-The \ac{BHH} baseline represents the main component that is evaluated in this dissertation.
-The configuration for the \ac{BHH} baseline is given in Table \ref{tab:methodology:bhh_baseline_configuration} below:
+The following section provides the details around the \acs{BHH} baseline configuration.
+
+\section{BHH Baseline}\label{sec:methodology:baseline_bhh}
+
+The \acs{BHH} baseline is a name given to a specific configuration of the \ac{BHH} which, during development, has been found to provide a reasonable baseline performance.
+The baseline configuration is used as the cornerstone configuration from which all other \index{heuristic}heuristics and their configurations are evaluated.
+The \acs{BHH} baseline is also used for the behavioural study of the \acs{BHH}.
+The \acs{BHH} baseline configuration is given in Table \ref{tab:methodology:bhh_baseline_configuration}.
 
@@
       \centering
-      \caption{BHH baseline configurations}
+      \caption{The \acs{BHH} baseline configurations as used in the empirical study.}
       \label{tab:methodology:bhh_baseline_configuration}%
       \par\bigskip
-      \resizebox{0.8\textwidth}{!}{
+      \resizebox{0.65\textwidth}{!}{
             \begin{tabular}{rrcc}
@@
                   \midrule
-                  \multicolumn{1}{l}{bhh}                      & \multicolumn{1}{l}{baseline}         & heuristic\_pool        & all            \\
+                  \multicolumn{1}{l}{bhh}                      & \multicolumn{1}{l}{baseline}         & heuristic pool         & all            \\
                                                                &                                      & population             & 5              \\
@@
                                                                &                                      & normalise              & false          \\
-                                                               &                                      & discounted\_rewards    & false          \\
+                                                               &                                      & discounted rewards     & false          \\
             \end{tabular}%
@@
 
-Table \ref{tab:methodology:bhh_baseline_configuration} refers to the \index{heuristic}heuristic pool that is used as \textit{all}.
-This refers to a configuration where the heuristic pool contains all the low-level heuristics as presented in Section \ref{sec:methodology:heuristics}.
-This list of low-level \index{heuristic}heuristics naturally also then form the list of standalone heuristics/optimisers to which the \ac{BHH} is compared and analysed as is described later in  Section \ref{sec:methodology:experiments:standalone_optimisers}.
-Specifically the finer details of the implementation of the \ac{BHH}, the low-level \index{heuristic}heuristic pool and how it is used is given in Chapter \ref{chap:bhh}.
+\noindent
+In Table \ref{tab:methodology:bhh_baseline_configuration}, the \index{heuristic}heuristic pool configuration that is used, is referred to as \textit{all}.
+The \textit{all} configuration refers to a configuration where the \index{heuristicpool}heuristic pool contains all the low-level \index{heuristic}heuristics as presented in Section \ref{sec:methodology:heuristics}, including all gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
 
-\section{Performance Measures}
-\label{sec:methodology:performance_measures}
+The following section provides the performance measurements that are implemented.
+
+\section{Performance Measures}\label{sec:methodology:performance_measures}
 

### 2022-11-06 dissertation/chapters/07-methodology.tex
✨ (chapter7): Review Done

@@
 \noindent
-So far this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acf{HH} and probability theory in Chapters \ref{chap:anns}-\ref{chap:probability}.
+So far, this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acf{HH} and probability theory in Chapters \ref{chap:anns}-\ref{chap:probability}.
 Chapter \ref{chap:bhh} provided the detail of the implementation of the proposed \acs{BHH} with all its components and hyper-parameters.
-Scientific experimentation can now be established.
-Chapter \ref{chap:introduction} identified goals for this dissertation.
-The goals of this dissertation include an empirical evaluation of the \acs{BHH}, its behaviour and performance, and comparison to state of the art low-level heuristics.
+Scientific experimentation can now be conducted.
+Chapter \ref{chap:introduction} identified a set of empirical goals for this dissertation.
+The goals of this dissertation include an empirical evaluation of the \acs{BHH}, its behaviour and performance, and a comparison to state of the art low-level \index{heuristic}heuristics.
 This chapter provides the detailed specification of the methodology that is followed for the empirical process.
@@
 
-      \item An empirical study to critically evaluate the performance of the \Acs{BHH} compared to individual low-level heuristics in the heuristic space as they are used to train \acp{FFNN} on a number of different problems.
+      \item An empirical study to critically evaluate the performance of the \Acs{BHH} compared to individual low-level \index{heuristic}heuristics in the \index{heuristic}heuristic space as they are used to train \acp{FFNN} on a number of different problems.
 \end{itemize}
@@
 The training set is used to train the model, while the test set is used to evaluate the model's performance on unseen data.
-Training epochs are split into mini-batch iterations, with each dataset containing a specified mini-batch size.
+Training epochs are split into mini-batch iterations with a specified mini-batch size.
 Evaluation takes place at every mini-batch step.
@@
                   abalone          & multivariate    & categorical, integer, real & 8                   & 28               & 4177               & 256            & 17             & ~\cite{ref:waugh:1995}     \\
+                  wine quality     & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & ~\cite{ref:cortez:2009}    \\
                   mushroom         & multivariate    & categorical                & 22                  & 2                & 8214               & 512            & 17             & ~\cite{ref:schlimmer:1987} \\
-                  wine quality     & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & ~\cite{ref:cortez:2009}    \\
                   bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & ~\cite{ref:moro:2014}      \\
+                  adult            & multivariate    & categorical, integer       & 14                  & 2                & 48842              & 256            & 191            & ~\cite{ref:kohavi:1996}    \\
                   diabetic         & multivariate    & integer                    & 55                  & 3                & 100000             & 1024           & 98             & ~\cite{ref:strack:2014}    \\
-                  adult            & multivariate    & categorical, integer       & 14                  & 2                & 48842              & 256            & 191            & ~\cite{ref:kohavi:1996}    \\
             \end{tabular}%
@@
 The empirical process defined in this dissertation does not apply mechanisms to cater for class balancing, in order to eliminate as many variables and factors in the empirical process as possible, as it is already a complicated process.
-It is therefore suggested that the \ac{BHH} first be studied under the assumption of balanced classes, before applying class balancing techniques.
+It is therefore suggested that the \acs{BHH} first be studied under the assumption of balanced classes, before applying class balancing techniques.
 In future research opportunities, class balancing should be utilised.
@@
 This section provides the details of the low-level \index{heuristic}heuristics that are used in the empirical process.
-Each of these low-level heuristics are implemented as standalone heuristics and are also included in the heuristic pool of the \acs{BHH}.
+Each of these low-level \index{heuristic}heuristics are implemented as standalone \index{heuristic}heuristics and are also included in the \index{heuristic pool}heuristic pool of the \acs{BHH}.
 Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level \index{heuristic}heuristics that are used as well as their hyper-parameter configuration.
@@
 Furthermore, it should be noted that a learning rate was added to \acs{PSO} as an attempt to avoid overshooting solutions later in the training process.
-This parameter does not traditionally form part of the \ac{PSO}, but was found to be useful.
+This parameter does not traditionally form part of \acs{PSO}, but was found to be useful.
 
-Section \ref{sec:bhh:heuristic:proxies} presented the concept of a mapping of proxied heuristic state update operations.
-The mapping of proxied heuristic state update operations, implemented by the \acs{BHH} in the empirical process, is given in Figure \ref{fig:methodology:heuristics:proxies}.
+Section \ref{sec:bhh:heuristic:proxies} presented the concept of a mapping of proxied \index{heuristic}heuristic state update operations.
+The mapping of proxied \index{heuristic}heuristic state update operations, implemented by the \acs{BHH} in the empirical process, is given in Figure \ref{fig:methodology:heuristics:proxies}.
 
@@
 \noindent
-In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x}, indicate that the associated heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
-The required mapping of proxied heuristic state operations is then implemented as a lookup of the table presented in Figure \ref{fig:methodology:heuristics:proxies}.
+In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x}, indicate that the associated \index{heuristic}heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
+The required mapping of proxied \index{heuristic}heuristic state operations is then implemented as a lookup of the table presented in Figure \ref{fig:methodology:heuristics:proxies}.
 
@@
 
-The \acs{BHH} baseline is a name given to a specific configuration of the \ac{BHH} which, during development, has been found to provide a reasonable baseline performance.
+The \acs{BHH} baseline is a name given to a specific configuration of the \acs{BHH} which, during development, has been found to provide a reasonable baseline performance.
 The baseline configuration is used as the cornerstone configuration from which all other \index{heuristic}heuristics and their configurations are evaluated.
@@
       \centering
-      \caption{The \acs{BHH} baseline configurations as used in the empirical study.}
+      \caption{The \acs{BHH} baseline configuration as it is used in the empirical study.}
       \label{tab:methodology:bhh_baseline_configuration}%
@@
                                                                &                                      & credit                 & ibest          \\
+                                                               &                                      & burn in                & 0              \\
                                                                &                                      & reselection            & 10             \\
@@
 In Table \ref{tab:methodology:bhh_baseline_configuration}, the \index{heuristic}heuristic pool configuration that is used, is referred to as \textit{all}.
-The \textit{all} configuration refers to a configuration where the \index{heuristicpool}heuristic pool contains all the low-level \index{heuristic}heuristics as presented in Section \ref{sec:methodology:heuristics}, including all gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
+The \textit{all} configuration refers to a configuration where the \index{heuristic pool}heuristic pool contains all the low-level \index{heuristic}heuristics as presented in Section \ref{sec:methodology:heuristics}, including all gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
 
@@
 
-This section sheds light into the performance measures that are used to evaluate the different experimental runs.
+This section provides the performance measures that are used to evaluate the different experimental runs during the empirical process.
+Chapter \ref{chap:anns} provided a number of loss functions.
+These loss functions are used to measure the performance of the \acp{FFNN} being trained.
+In this dissertation, \acf{BinXE} is used for classification problems with two classes and \acf{SparseCatXE} is used for classification problems with more than two classes.
+For the classifications problems accuracy is also measured.
+Accuracy refers to the proportion of correct classifications.
+For regression problems, the \acf{RMSE} is used as a performance metric.
 
-Chapter \ref{chap:anns} provided the reader with a number of techniques that are used to evaluate \ac{FFNN} performance during training.
-Broadly these techniques measure the output of some loss/cost function and accuracy for classification problems.
-For the classifications problems, the loss metrics used included \ac{SparseCatXE} and \ac{BinXE}.
-Their accuracy equivalent metrics are then also used.
-For regression problems, \ac{RMSE} is used as a loss metric.
+After training has been completed, the \textit{average rank}, based on test loss, for all configurations, is calculated at each mini-batch step across all runs.
+The test loss metric and average rank are statistically analysed and used to derive findings and conclusions.
 
-As mentioned in the preceding sections, datasets are split into a training set and a test dataset.
-The training set is used to train the model and the test set is used to test the model.
-Evaluation takes place at the end of each mini-batch iteration.
-Loss and accuracy is measured for both training and test datasets and is captured at each mini-batch iteration.
+The following section provides the stopping conditions that are used.
 
-Post processing of the results yield a average rank (by test loss metric) between configurations at each mini-batch step across all runs.
-This test loss metric and rank then form experimental results that are then statistically analysed.
+\section{Stopping Conditions}\label{sec:methodology:stopping_conditions}
 
-\section{Stopping Conditions}
-\label{sec:methodology:stopping_conditions}
+This section provides the stopping conditions that are used during the empirical process.
+For this dissertation, the \textit{maximum epoch} stopping condition is used, where a fixed, maximum number of training steps and epochs are executed and training is not haulted until the maximum number of epochs have been reached.
+Early stopping is a technique where training is stopped when the \index{heuristic}heuristic is not able to improve the performance of the \acs{FFNN} for a number of steps.
+If the performance has not improved, the training is halted and the last known best model weights are restored.
+Early stopping is not implemented for the empirical process in this dissertation.
+This design decision is made so that the behaviour of the \acs{BHH} can be studied beyond the point of optimal results.
 
-This section sheds light on the stopping conditions that are used.
-
-Early stopping is a technique where training is prematurely stopped due to training saturation.
-A popular technique for early stopping includes a check to see if the validation/test loss has improved in the last $k$ steps.
-If the loss has not improved, the training is halted and the last best model weights are used.
-
-It was decided not to use early stopping in this empirical process.
-Since the \ac{BHH} is a novel \ac{HH}, there are lots of uncertainty around its performance.
-It is unsure as to how the \ac{BHH} will behave, should overfitting take place.
-By eliminating early stop, the \ac{BHH} is evaluated until a maximum number of epochs (30) is reached.
-It is recommended that future research make use of early stopping.
-
-The different experimental groups are given next.
+The following sections provide the various experimental groups that are formulated and empirically tested.
 
@@
 
-This section presents the experimental groups that form part of the empirical process.
-There are broadly 3 main groups.
-These include a behavioural case study, a critical evaluation of the \ac{BHH} baseline's performance compared to other standalone low-level \index{heuristic}heuristics and finally an analysis of different \ac{BHH} variants is done by analysing the effects of different parameter values on the outcomes of the \ac{BHH}.
-Each of these sections are discussed in more detail below.
+This section presents the experimental groups that are executed in the empirical process.
+Three main experimental groups are formulated.
+These include a behavioural case study of the \acs{BHH} as it relates to an example problem, a critical evaluation of the \acs{BHH}'s baseline performance in comparison to other standalone low-level \index{heuristic}heuristics, and finally an analysis of different \acs{BHH} variants is done by analysing the effects of different hyper-parameter values on the outcomes of the \acs{BHH}.
+Each of these are discussed in more detail in the following sections.
 
@@
 
-This experimental group is concerned with objectively studying the behaviour of the \ac{BHH} baseline across a number of runs.
-This is meant to be an introductory analysis of the \ac{BHH} and includes analysis of the selection mechanism as well as the perturbative nature of the \ac{BHH}.
-It is important to mention that this experimental group is not meant to be statistically analysed, but to rather provide a detailed visual analysis of a number of hand-picked example runs, to determine if the \ac{BHH} is behaving as expected.
-It also provides a gentle introduction to the \ac{BHH}'s inner workings.
-From these observations, it is determined if the \ac{BHH} is learning and that selection is indeed biasing towards better performance.
-It also provides an opportunity to determine the outcome of the perturbative component of the \ac{BHH} which includes proxied \index{heuristic}heuristic update step operations.
+The behavioural case study is concerned with studying the behaviour of the \acs{BHH} baseline configuration as it relates to an example problem dataset, across a number of runs.
+The example problem dataset is the iris dataset, presented in Table \ref{tab:methodology:datasets:classification}.
+The behavioural case study is meant to provide an introductory analysis of the inner workings of the \acs{BHH} and includes analysis of the selection mechanism, as well as the perturbative nature of the \acs{BHH}.
+The behavioural case study is not meant to be statistically analysed, but to rather provide a detailed visual analysis of a number of hand-picked example runs, to determine if the \acs{BHH} is behaving as expected.
+From these observations, it is determined if the \acs{BHH} is learning and that selection is indeed biasing towards better performance.
+These observations also provide an opportunity to observe the outcome of the perturbative nature of the \acs{BHH}, which includes proxied \index{heuristic}heuristic update step operations.
 
-Two different configurations of the \ac{BHH} baseline is trained using the iris dataset~\cite{ref:fisher:1936}.
-These configurations include a replay window size of 10 (short memory) and a high replay window size of 250 (long memory).
-Each configuration is repeat 3 times.
-Finally these configurations are compared to a run that is purely random.
+The behavioural case study provides an implementation of the \acs{BHH} baseline which, by default, has a replay window size of 10.
+The baseline configuration is provided and compared to an implementation of a \acs{BHH} configuration where the replay window size is large (250), as well as an implementation of the \acs{BHH} using the \textit{symmetric} credit assignment strategy.
+The large replay window size configuration is to used to show the behaviour of the \acs{BHH} when it has access to a large number of performance log samples, which increases the statistical certainty of the learning outcome.
+The \acs{BHH} configuration that uses the \textit{symmetric} credit assignment strategy is used to illustrate the behaviour of the \acs{BHH} where no performance bias takes place and thus, no learning occurs.
 
-The analysis is primarily done by dissecting the output of various parameters and studying the plots of their values. From these plots, conclusions about the \ac{BHH}'s behaviour is made.
-
-\subsection{Standalone Optimisers}
+\subsection{Standalone Heuristics}
 \label{sec:methodology:experiments:standalone_optimisers}
 
-THis section presents the details with the experimental group that focuses on evaluating the performance of the \ac{BHH} with that of standalone \index{heuristics}/optimisers.
+For the standalone \index{heuristic}heuristics experimental group, the \index{heuristic}heuristics, as presented in Section \ref{sec:methodology:heuristics}, are used along with their specified hyper-parameters.
+Each of these standalone low-level \index{heuristic}heuristics are compared to that of the \acs{BHH} baseline configuration, across all datasets.
 
-For this experimental group, the heuristics and optimisers as presented in Section \ref{sec:methodology:heuristics} are used, along with their specified parameters.
-Each of these are then compared to that of the \ac{BHH} baseline configuration which is presented in Section \ref{sec:methodology:baseline_bhh}.
+The intent of the standalone \index{heuristic}heuristics experimental group is to determine if the \acs{BHH} baseline configuration can generalise to multiple problems in comparison to individual low-level \index{heuristic}heuristics.
 
-The next section provides the details around different \ac{BHH} variants that are evaluated.
+Additional to the \acs{BHH} baseline configuration, two more \acs{BHH} configurations are included.
+These include \acs{BHH} configurations where the \index{heuristic pool}heuristic pool only makes use of gradient-based \index{heuristic}heuristics, and a configuration where the \index{heuristic pool}heuristic pool only makes use of meta-heuristics.
+The intent behind the inclusion of these configurations is to determine the effectiveness of multi-method approaches in the \index{heuristic pool}heuristic pool as it applies to training \acp{FFNN}.
 
@@
 
-This section provides the details of the experimental group that focuses on \ac{BHH} variants and the effect that different hyper-parameter configurations can have on the outcome of the \ac{BHH}.
-
-The different variants and their possible configurations is given in Table \ref{tab:methodology:experiments:bhh_variants} below.
+This section provides the details of the experimental group that focuses on \acs{BHH} variants and the effect that different hyper-parameter configurations can have on the outcome of the \acs{BHH}.
+The different variants of the \acs{BHH} and their possible configurations are given in Table \ref{tab:methodology:experiments:bhh_variants}.
 
@@
                   \midrule
-                  \multicolumn{1}{l}{bhh}                      & heuristic\_pool     & all,gd,mh                         \\
-                                                               & population          & 5,10,15,20,25                     \\
-                                                               & credit              & ibest,pbest,rbest,gbest,symmetric \\
-                                                               & reselection         & 1,5,10,15,20                      \\
-                                                               & replay              & 1,5,10,15,20                      \\
-                                                               & reanalysis          & 1,5,10,15,20                      \\
-                                                               & burn\_in            & 0,5,10,15,20                      \\
-                                                               & normalise           & false,true                        \\
-                                                               & discounted\_rewards & false,true                        \\
+                  \multicolumn{1}{l}{bhh}                      & heuristic pool     & all, gd, mh                           \\
+                                                               & population         & 5, 10, 15, 20, 25                     \\
+                                                               & credit             & ibest, pbest, rbest, gbest, symmetric \\
+                                                               & reselection        & 1, 5, 10, 15, 20                      \\
+                                                               & replay             & 1, 5, 10, 15, 20                      \\
+                                                               & reanalysis         & 1, 5, 10, 15, 20                      \\
+                                                               & burn in            & 0, 5, 10, 15, 20                      \\
+                                                               & normalise          & false, true                           \\
+                                                               & discounted rewards & false, true                           \\
             \end{tabular}%
@@
 
-Take note that the \index{heuristics}heuristic pool options \textit{gd} and \textit{mh} refers to the \index{heuristics}heuristic pool configurations where the heuristic pools contain only gradient-descent heuristics or only \{index{meta-heuristics}meta-heuristics  respectively.
+\noindent
+In Table \ref{tab:methodology:experiments:bhh_variants}, the \index{heuristic pool}heuristic pool configuration \textit{gd} refers to the \index{heuristic pool}heuristic pool configuration where only gradient-based \index{heuristic}heuristics are included, and \textit{mh} refers to the \index{heuristic pool}heuristic pool configuration where only meta-heuristics are included.
 
-The next section explains in detail how the results are statistically analysed.
+The next section presents the method that is followed for statistical analysis.
 
@@
 
-Various experimental groups and the details of the configuration is given in the preceding sections.
-Each of these experimental groups are statistically analysed on their own.
-To ensure there is statistically sufficient sample, each experimental group and configuration is trained for 30 epochs, repeated over 30 runs.
-As it is mentioned above, the results contain performance evaluation data in the form of training and testing, loss and accuracy measurements.
-Each experimental run is then ranked by these metrics.
-Each run is executed using a unique seeding value such such that each run is identical in its setup and configuration (apart from seeding values) and independent of the other runs.
+Various experimental groups and configurations have been presented in Sections \ref{sec:methodology:experiments:case_study}, \ref{sec:methodology:experiments:standalone_optimisers} and \ref{sec:methodology:experiments:bhh_variants}.
+The results from each of these experimental groups are statistically analysed.
+To ensure that there are sufficient samples for statistical analysis, each experiment and configuration is trained for 30 epochs and is repeated over 30 runs, for each of the 15 datasets.
+The experimental results contain performance evaluation data for the training and testing datasets, and includes loss and accuracy measurements.
+Statistical analysis is executed on the results from the testing datasets.
+An average rank is calculated across all 30 runs, for all experimental groups and configurations, at each step, for every epoch of training.
+Each run is executed using a unique random seed, such that each run is identical in its setup and configuration, but unique between runs.
 
-Each experimental group goes through a set of steps that are followed during the statistical analysis process.
-First, the descriptive analysis is done to ensure that each experiment has the required data it needs.
-This includes 30 runs per configuration, across 15 datasets, across the applicable number of experimental configurations set up by that particular experimental group.
-The spread of the data is analysed to evaluate for overfit and outliers are identified.
-The skewness of the results is evaluated per dataset and the \index{Shapiro-Wilk}Shapiro-Wilk test for normality ($\alpha$ = 0.001) is used to determine in the results are normally distributed.
-The full statistical analysis reports are presented in Appendix \ref{app:statistical_analysis} and provides descriptive plots of the data's distribution.
+The evaluation of outcome is based on the aggregated statistical results as mentioned above.
+A descriptive analysis is executed on the spread of the data.
+The results are analysed and checked for overfitting and outliers are identified.
+The skewness of the results is evaluated per dataset and the \index{Shapiro-Wilk}Shapiro-Wilk test for normality ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
 Furthermore, the \index{Levene}Levene's test for equality of variance ($\alpha$ = 0.001) is used.
+The output of the full statistical analysis is presented in Appendix \ref{app:statistical_analysis}.
 
 Dependent on the outcomes of the above statistical tests, the appropriate statistical significance test is then executed.
-For configurations of independent variables where there are only 2 classes, the Mann-Whitney U\index{Mann-Whitney U} independent samples t-Test ($\alpha$ = 0.001) is executed and for configurations of 3 or more configuration classes, the \ac{ANOVA} statistical test ($\alpha$ = 0.001) is used.
+For experiments where there are only two configurations, the Mann-Whitney U\index{Mann-Whitney U} independent samples t-Test ($\alpha$ = 0.001) is executed.
+For experiments with three or more configurations, the \acf{ANOVA} statistical test ($\alpha$ = 0.001) is used.
 The\index{Kruskal-Wallis} Kruskal-Wallis ranked non-parametric test for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
 
-As mentioned earlier in the chapter, results are analysed for statistical significance over all the steps during the training process across all runs.
-This helps determine if there is statistical difference in the execution of various experimental configurations, throughout the entire training process, but also to cater for overfitting, which is to be studied as well.
+Regardless of the statistical test that is used, a post-hoc Tukey honest significant difference test ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
+Descriptive and critical difference plots are then retrieved from these results to provide visual aid.
 
-Regardless of the statistical test that is used, a post-hoc Tukey honest significant difference test ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
-Descriptive and critical difference plots are then retrieved from these results to provide visual aid, but all conclusions are made from statistically analysed data as mentioned above.
+\section{Implementation and Execution}\label{sec:methodology:implementation}
 
-\section{Implementation and Execution}
-\label{sec:methodology:implementation}
+All implementations are done from first principles in Python 3.9 using Tensorflow 2.7 and Tensorflow Probability 0.15.0.
+Most underlying mathematical functions are reused from the Tensorflow library, however, all \index{heuristic}heuristics are implemented from first principles to fit the \acs{HH} framework that was developed.
+The source code and data for this dissertation is provided and made public at \url{https://github.com/arneschreuder/masters.ai}.
 
-This section sheds some light as to the details of the implementation and execution of the empircal process.
+It should be noted that this implementation makes heavy use of CPU processing, due to flattening of the \acs{FFNN} weights by the \index{heuristic}heuristics.
+For this reason, execution is much more timely and costly than with GPU training.
 
-All implementation is done from first principles in Python 3.9 using Tensorflow 2.7 and Tensorflow Probability 0.15.0.
-Most underlying function are reused from the Tensorflow library, however, all heuristics/optimisers are implemented from first principles to fit the \ac{HH} framework that was developed.
-All source code and data is provided is resources in this dissertation.
-
-It should be noted that this implementation makes heavy use of CPU processing, due to the nature of modeling flattening for the \index{heuristic}heuristics.
-For this reason, execution is much more timely and costly than with GPU training.
-The authors hope that as the \ac{BHH} evolves, that better GPU implementations may speed up execution times.
-
-With regards to the computational power that was used the execute this empirical process.
-All experiments were run on the CHPC's cluster.
-This included 14 servers each running 24-56 cores and 256GB memory each.
+All experiments were run on the Centre for High Performance Computing (CHPC) cluster.
+A total of 14 different server were used, each running 24-56 cores and 256GB of memory.
 The entire empirical process took 6 days.
 
-\section{Summary}
-\label{sec:methodology:summary}
+\section{Summary}\label{sec:methodology:summary}
 
 This chapter provided the detail around the methodology that is used to execute the empirical process.
-The datasets, models and heuristics that are used during the empirical process have been presented in detail.
-A baseline \ac{BHH} has been formulated.
-The empirical process was defined in terms of a number of different experiments and finally, the process of statistical analysis of the results was provided.
+The datasets, \acp{FFNN} and \index{heuristic}heuristics that are used during the empirical process have been presented in detail, along with details around various \acs{BHH} configurations.
+A baseline \acs{BHH} has been formulated.
+The empirical process was defined in terms of a number of different experimental groups and finally, the process of statistical analysis of the results was provided.
 

### 2022-11-10 dissertation/chapters/08-results-old.tex
🚧 (results): WIP - Re-plotting case study

--- 2022-10-25 dissertation/chapters/08-results.tex
@@
 Figure \ref{fig:results:case_study:iris:p_HgEC} shows the resulting output of the predictive model for each of the five entities in the heuristic pool.
-This predicted heuristic selection probability is used to parameterise a new categorical distribution from which the heuristics are finally sampled and (re)selected.
+This predicted heuristic selection probability is used to parameterise a new Categorical distribution from which the heuristics are finally sampled and (re)selected.
 

### 2022-11-10 dissertation/chapters/08-results.tex
🚧 (results): WIP - Re-plotting case study

@@
 
-\begin{quote}
-      \textit{
-            ``Without data, you are just another person with an opinion.'' - W. Edwards Deming
-      }
-\end{quote}
+\begin{quotation}
+      \noindent ``Without data, you are just another person with an opinion.''
+\end{quotation}
+\begin{flushright}
+      - W. Edwards Deming
+\end{flushright}
 
-The last step in the scientific process requires the presentation and objective discussion of empirical findings with good statistical backing.
-From the problem statements and motivations made in Chapter \ref{chap:introduction}, goals have been defined that broadly include literature studies and a sound empirical process.
-Thus far, the reader has been provided with a vast scope of background information relevant to the development of the \Acs{BHH}.
-Chapters \ref{chap:introduction} - \ref{chap:probability} provided the background information, literature studies and existing landscape of research for \acp{ANN}, \index{heuristic}heuristics/\index{optimiser}optimisers, \acp{HH} and probability theory.
-These elements all share common elements that are required to understand the proposed \Acp{BHH} which was presented in Chapter \ref{chap:bhh}.
-The details around the empirical process was formally proposed in the methodology as presented in Chapter \ref{chap:methodology}.
-Finally, the results for the empirical process can be presented and this chapter aims to provide these results.
+\noindent
+All the required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}.
+The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}.
+The methodology presented a number of experiments to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level heuristics.
+The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.
 
-As a reminder, the empirical process is split into two main experimental groups.
-These include a behavioural case study and set of comparative studies.
-This chapter is organised into the same logical pattern.
-Each of these experimental groups is provided as its own section for detailed analysis and discussion of findings.
-The remainder of the chapter is structured as follows:
+Finally, this chapter provides the outcome of these empirical processes and provides results on all the experiments that have been conducted.
+Detailed discussions follow on the outcomes of each experiment.
+Discussions are accompanied by figures and plots to help provide visual aid for the discussions.
+All experiments and discussions also provide the outcome of the statistical analysis of the results.
+The remainder of the chapter is structured as follows.
 
 \begin{itemize}
-      \item \textbf{Section \ref{sec:results:overview}} provides a brief overview of the general empirical process, high level discussion points and a brief discussion on results interpretation.
+      \item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}.
+Illustrations are provided to show the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.
 
-      \item \textbf{Section \ref{sec:results:case_study}} provides a detailed analysis of the behaviour of the \Acs{BHH} over a few example runs during training and testing and is meant to introduce the analysis of the \Acs{BHH} from a behavioural characteristic point of view.
-In this section, focus is put on the learning process itself and to determine what happens during training.
-It aims to provide insight into ``how'' and ``when'' the \Acs{BHH} learning happens.
+      \item \textbf{Section \ref{sec:results:bhh_vs_low_level_heuristics}} provides the results of the performance of the \acs{BHH} compared to individual low-level heuristics as it relates to all datasets.
+Three variants of the \acs{BHH} are included in these results.
+These include the baseline configuration, as well as a configuration that only includes gradient-based heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.
 
-      \item \textbf{Section \ref{sec:results:standalone}} provides the first of a series of comparative studies.
-This section presents the comparative analysis that studies the performance capabilities of the baseline configuration of the \Acs{BHH} to that of standalone/individual low level \index{heuristic}heuristics/\index{optimiser}optimisers.
-The sections that follow focus on the effect of various parameters on the \Acs{BHH}.
+      \item \textbf{Section \ref{sec:results:bhh_variant_hp}} provides the results for the experimental group that analyses the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the outcomes of the \acs{BHH}.
 
-      \item \textbf{Sections \ref{sec:results:heuristic_pool}} - \ref{sec:results:discounted_rewards} capture the results of these empirical processes and focus on the configuration of the \textit{heuristic pool}, the \textit{population size}, \textit{credit assignment strategies}, \textit{reselection} window size, \textit{replay} window size, \textit{reanalysis} window size, \textit{burn in}, \textit{normalisation} and \textit{discounted rewards}, respectfully.
+      \item \textbf{Section \ref{sec:results:bhh_variant_population}} provides the results for the experimental group that analyses the effects of the \textit{population size} hyper-parameter on the outcomes of the \acs{BHH}.
 
-      \item \textbf{Section \ref{sec:results:computational_requirements}} contains a brief discussion on the computational requirements.
+      \item \textbf{Section \ref{sec:results:bhh_variant_burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.
 
-      \item \textbf{Section \ref{sec:results:overfitting}} provides a brief discussion on overfitting.
+      \item \textbf{Section \ref{sec:results:bhh_variant_credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.
 
-      \item Finally, a summary of the findings is given in \textbf{Section \ref{sec:results:summary}}.
+      \item \textbf{Section \ref{sec:results:bhh_variant_replay}} provides the results for the experimental group that analyses the effects of the \textit{replay window size} hyper-parameter on the outcomes of the \acs{BHH}.
+
+      \item \textbf{Section \ref{sec:results:bhh_variant_reanalysis}} provides the results for the experimental group that analyses the effects of the \textit{reanalysis interval} hyper-parameter on the outcomes of the \acs{BHH}.
+
+      \item \textbf{Section \ref{sec:results:bhh_variant_reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.
+
+      \item \textbf{Section \ref{sec:results:bhh_variant_normalise}} provides the results for the experimental group that analyses the effects of the \textit{normalisation} hyper-parameter on the outcomes of the \acs{BHH}.
+
+      \item \textbf{Section \ref{sec:results:bhh_variant_discounted_rewards}} provides the results for the experimental group that analyses the effects of the \textit{discounted rewards} hyper-parameter on the outcomes of the \acs{BHH}.
+
+      \item \textbf{Section \ref{sec:results:overfitting}} provides a brief discussion on overfitting as it is observed for some of the empirical tests.
+
+      \item \textbf{Section \ref{sec:results:computational_req}} provides a brief discussion on the practical application of the \acs{BHH} to real-world problems.
+
+      \item \textbf{Section \ref{sec:results:overview}} provides an overview of all the results for all the empirical tests, followed by a brief discussion on the overall performance of the \acs{BHH}.
+
+      \item \textbf{Section \ref{sec:results:overview}} provides a brief summary of the chapter.
 \end{itemize}
-
-\section{Overview}
-\label{sec:results:overview}
-
-This section aims to provide a general high level discussion on the outcomes of the empirical process as an introduction to the more detailed discussions to follow.
-Consider again the goals that have been defined in \ref{chap:introduction}.
-The empirical component addresses three different angles of analysis:
-
-\begin{enumerate}
-      \item Analysing the behaviour of the \Acs{BHH} during training and testing to determine if the the concept works and that the \Acs{BHH} is indeed learning.
-This component looks at the \Acs{BHH} in isolation and simply evaluates the outcomes of its behaviour over a few example runs and repeats this process for two groups of \Acs{BHH} variants based on \textit{replay} window size.
-
-      \item Comparing the performance capabilities of the \Acs{BHH} to that of well-known low-level \index{heuristic}heuristics that are well researched and understood.
-This component looks at how the \Acs{BHH} performs given a frame of reference to compare to.
-Careful consideration of results interpretation must be given here and is discussed in more detail below.
-
-      \item Analysing the effects of various configurations of hyper-parameters for the \Acs{BHH}.
-This component looks at which parameters have a statistically significant impact on the outcomes of the \Acs{BHH}.
-\end{enumerate}
-
-It is important to briefly discuss how results should be interpreted.
-Traditionally, for typical low-level heuristic training, evaluation of performance is done at a chosen point in time and based on a particular dependent variable.
-This could be a fixed number of training steps/epochs, early stopped conditions or any other stopping condition.
-The metric of interest could be a loss value, an accuracy or a rank.
-Algorithms/heuristics in question are then logically ranked/organised according to their final solution and conclusions are made based on these findings.
-However, the following arguments suggest an alternative approach for this empirical study:
-
-\begin{itemize}
-      \item
-            Since there does not exist any research on this specific implementation of \acp{HH} and its application to \acs{FFNN} training, there is no clear point at which it is known that the learning of the \acs{BHH} becomes detrimental to the training process.
-For example, there exists a currently unknown point during training where the performance bias towards the ``best'' \index{heuristic}heuristic no longer yield improved training or test generalisation outcomes.
-To cater for this, a fixed maximum number of training epochs have been chosen that empirically have been shown to be sufficient to notice diminishing returns in the outcome.
-\index{Early stopping}Early stopping was considered, but purposefully not implemented.
-This is to allow the study of the behaviour and capabilities of the \Acs{BHH} up to and beyond the point of diminishing returns.
-
-      \item
-            The training process is to some degree analogous and comparable to a dynamic optimisation problem as previously discussed.
-This means that the performance of \index{heuristic}heuristics, and thus the \Acs{BHH}, vary at different times during the training process.
-This hints to the hypothesis that was set in Chapter \ref{chap:introduction} and suggests that there is no single \index{heuristic}heuristic that is always the best \index{heuristic}heuristic to use during all of training.
-Rather, there exists an applicable, relevant \index{heuristic}heuristic (or combination of \index{heuristic}heuristics) to use at a given point in time during the training process and can change as the process continues.
-This means the selected \index{heuristic}heuristic at time step $t$ is not necessarily the best heuristic to select at timestamp $t+1$.
-This argument is further supported by the fact that these experiments are trained on mini-batches, resulting in a lot of noise during training.
-This noise can cause the \Ac{BHH} to want to "correct" a certain learnt belief.
-This introduces the same challenges as with \Ac{RL}: Consider delayed rewards, size of rewards, unlearning behaviour that is no longer required, all of which affect the training process throughout and not just at the point of stopping.
-\end{itemize}
-
-Based on the points made above, each experimental group is to be evaluated in isolation and has a specific area of focus.
-For all experimental groups, heuristics are evaluated during \textbf{all} the steps of the training and testing process.
-For this reason, ranking \index{heuristic}heuristic should not necessarily lead to the conclusion that one heuristic is \textit{better} than another, but rather, that there is a statistically significant difference between the outcomes of heuristics, relative to the entire training and testing process for a given experimental group.
-The authors suggest further research to include early stopping conditions for the ranking to make entirely sense.
-However, that does not mean the ranking approach is useless.
-It still provides a measure of comparison and is indeed indicative of statistically significant outcomes.
-
-The points that have been discussed above have been observed during the empirical process.
-It is shown in the succeeding sections that the \Acs{BHH} is capable of training \Acp{FFNN} and that it does so relatively well.
-It is shown that the \Acs{BHH} is generally capable of providing good test generalisations when compared to existing low-level \index{heuristic}heuristics.
-However, it is shown that the majority of the influence of the \Acs{BHH} occurs during the first few epochs of the training process.
-Initially uniformly randomised candidate solutions has more room to learn in the initial phases of training in comparison to later phases where learning has become stagnated.
-It is also shown that this pivotal point of diminishing return is problem specific.
-Further to this pivotal point, it is shown that the \Acs{BHH} is subject to over-fitting, quite drastically.
-There are various conclusions that can be made from this point, but the detail is left to the relevant sections to follow.
-
-The following section provides the results and findings for a behavioural case study of the \Acp{BHH} on the iris dataset.
-
-\section{Case Study}
-\label{sec:results:case_study}
-
-This section provides a study on the behaviour of the \Acs{BHH} during training and testing.
-It is important to mention that this experimental group does not necessarily focus on the exact metrics, but rather on the general behaviour of the \Ac{BHH}.
-This means that statistical analysis and statistical certainty as is not required.
-Instead, a number of example runs have been executed purely for the intent of analysing behaviour.
-Furthermore, this behavioural case study is executed on a very small, but well-known toy dataset called \textit{iris}.
-Iris is not usually considered for full empirical processes due to its size and simplicity.
-Although there are fourteen other datasets to choose from, iris provides a very simple, relevant and relate-able case study that illustrate the necessary points sufficiently.
-
-Figure \ref{fig:results:case_study:iris:metric_plots} illustrate these runs during training and testing.
-Take note of the legend as provided in Figure \ref{fig:results:case_study:iris:legend}.
-There are two variants of the \Acs{BHH} included here, each with three repeated runs, seeded according to run number:
-
-\begin{itemize}
-      \item \Acp{BHH} with a very \textbf{short memory}, i.e. replay windows size = 10
-      \item \Acp{BHH} with a very \textbf{long memory}, i.e. replay windows size = 250
-\end{itemize}
-
-These two groups have been chosen as their parameters have been shown to provide drastically different outcomes from each other during training and forms a good basis for behavioural analysis.
-For more details on replay window size, see Section \ref{sec:results:replay}.
-
-A breakdown of the run notation as provided in Figure \ref{fig:results:case_study:iris:legend} is then given as follows:
-
-\begin{itemize}
-      \item \textbf{iris} - The dataset in question
-      \item \textbf{bhh} - The heuristic in question
-      \item \textbf{hp:all} - The heuristic pool (hp) in question.
-``All'' refers to all the implemented lower-level heuristics including both classical gradient-based heuristics/optimisers as well as meta-heuristics.
-      \item \textbf{ps:5} - The population size (ps) in question. In this case, population size = 5.
-      \item \textbf{bi:0} - The burn in window size (bi) in question. In this case, burn in window size = 0.
-      \item \textbf{rp:10} - The replay window size (rp) in question. In this case, replay window size = 10.
-      \item \textbf{rs:10} - The reselection window size (rp) in question. In this case, reselection window size = 10.
-      \item \textbf{ra:10} - The reanalysis window size (rp) in question. In this case, reanalysis window size = 10.
-      \item \textbf{nm:False} - The normalisation flag (nm) in question. In this case, normalisation is disabled.
-      \item \textbf{ct:ibest} - The credit assignment strategy (ct) in question. In this case, the credit assignment strategy used is \textit{ibest}.
-      \item \textbf{dr:False} - The discounted rewards flag (dr) in question. In this case, discounted rewards is disabled.
-\end{itemize}
-
-From figure \ref{fig:results:case_study:iris:metric_plots} it is shown that the \Acs{BHH} exhibit similar behaviours to that of lower-level heuristics.
-Figures \ref{fig:results:case_study:iris:train:loss} and \ref{fig:results:case_study:iris:train:accuracy} illustrates a smooth training process, converging to a well-known minimum loss for the iris dataset.
-In Figures \ref{fig:results:case_study:iris:test:loss} and \ref{fig:results:case_study:iris:test:accuracy} it is shown that the \Acs{BHH} generalised well on the test set.
-Generalisation improved up to about epoch 10 before overfitting starts occurring.
-From this, it can be concluded that most of the learning, for this particular dataset, takes place in the first 10 epochs of the training process.
-From this point onwards, the \Acs{BHH} tries to undo ``bad'' selections made earlier.
-It is interesting to notice that despite overfitting, the \Acs{BHH} was able to ``correct'' itself to some degree (up to epoch 20), but never really converged back on the minimum it reached up to epoch 10.
-Early stopping should prohibit this from happening, but this is left for further research.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.49\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/train_loss.png}
-            \caption{Train loss}
-            \label{fig:results:case_study:iris:train:loss}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/test_loss.png}
-            \caption{Test loss}
-            \label{fig:results:case_study:iris:test:loss}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.49\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/train_accuracy.png}
-            \caption{Train accuracy}
-            \label{fig:results:case_study:iris:train:accuracy}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/test_accuracy.png}
-            \caption{Test accuracy}
-            \label{fig:results:case_study:iris:test:accuracy}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{\textwidth}
-            \centering
-            \includegraphics[width=0.35\textwidth]{bhh_case_study/iris/legend.png}
-            \caption{Legend}
-            \label{fig:results:case_study:iris:legend}
-      \end{subfigure}
-      \par\bigskip
-      \caption{Train and test behaviour of the \Ac{BHH} baseline for different configurations of replay window size}
-      \label{fig:results:case_study:iris:metric_plots}
-\end{figure}
-
-A high level view of the train and test metric plots is good for drawing high level conclusions, but more detail is required.
-Figure \ref{fig:results:case_study:iris:alpha} aims to provide more detail as to what is happening during training and plots the value of $\alpha$ during training.
-Each sub-figure represents the value of $\alpha$ for a particular index, representing a particular \index{heuristic}heuristic.
-From sub-figures \ref{fig:results:case_study:iris:alpha:0}, \ref{fig:results:case_study:iris:alpha:2} and \ref{fig:results:case_study:iris:alpha:6}, the effect of a larger replay value is clear.
-Although a more detailed discussed on replay window sizes is left for Section \ref{sec:results:replay}, one can clearly see the accumulation of ``knowledge''/``evidence'' in the concentration parameter $\alpha$.
-It should be noticeable then from these sub-figures how $\alpha$ changes over time for runs with lower replay window sizes and is indicative of the learning capabilities of the \Ac{BHH}.
-From these changes, one can formulate a prediction of which \index{heuristic}heuristics are then likely to be selected in the next steps.
-
-Figures \ref{fig:results:case_study:iris:alpha:5} and \ref{fig:results:case_study:iris:alpha:9} contain a run in orange that shows how the concentration for a particular heuristic (\Acs{Adadelta} and \Acs{DE}) and can change over time.
-This suggests that the \Acs{BHH} has the ability to dynamically switch between heuristics as the need requires.
-This concept bears similarities to dynamic optimisation algorithms.
-It can thus be said that an observation is made that the \Acs{BHH} is able to learn (to some degree) to balance exploration and exploitation by dynamically changing the heuristic of interest at that point in time.
-Notice that it has not yet been established if the attempt to balance leads to good or bad outcomes.
-However, this is a still a useful feature of the \Acs{BHH} and warrants further discussion and reasoning.
-These statements further support the hypothesis that there might not be a no single specific heuristic that is the best heuristic to train the \Acs{FFNN} during the entire training process.
-In the succeeding sections, it is shown how this statement is further supported as the behaviour of the \Acs{BHH} is shown to be problem-dependent.
-
-A clear distinction between Figures \ref{fig:results:case_study:iris:metric_plots} and \ref{fig:results:case_study:iris:alpha} should be pointed out.
-Figures \ref{fig:results:case_study:iris:metric_plots} plot metrics for every epoch, while Figure \ref{fig:results:case_study:iris:alpha} plot metrics for every mini-batch iteration.
-This is a subtle difference in visualisation, but nonetheless important.
-A more fine-grained visualisation illustrates the learning opportunities better since it is clear that a single step of learning happens on a single mini-batch iteration.
-This is important to keep in mind for various different sizes of datasets.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[0].png}
-            \caption{$\alpha_{0}$ - \Acs{SGD}}
-            \label{fig:results:case_study:iris:alpha:0}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[1].png}
-            \caption{$\alpha_{1}$ - \Acs{Momentum}}
-            \label{fig:results:case_study:iris:alpha:1}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[2].png}
-            \caption{$\alpha_{2}$ - \Acs{NAG}}
-            \label{fig:results:case_study:iris:alpha:2}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[3].png}
-            \caption{$\alpha_{3}$ - \Acs{Adagrad}}
-            \label{fig:results:case_study:iris:alpha:3}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[4].png}
-            \caption{$\alpha_{4}$ - \Acs{RMSProp}}
-            \label{fig:results:case_study:iris:alpha:4}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[5].png}
-            \caption{$\alpha_{5}$ - \Acs{Adadelta}}
-            \label{fig:results:case_study:iris:alpha:5}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[6].png}
-            \caption{$\alpha_{6}$ - \Acs{Adam}}
-            \label{fig:results:case_study:iris:alpha:6}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[7].png}
-            \caption{$\alpha_{7}$ - \Acs{PSO}}
-            \label{fig:results:case_study:iris:alpha:7}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[8].png}
-            \caption{$\alpha_{8}$ - \Acs{GA}}
-            \label{fig:results:case_study:iris:alpha:8}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[9].png}
-            \caption{$\alpha_{9}$ - \Acs{DE}}
-            \label{fig:results:case_study:iris:alpha:9}
-      \end{subfigure}
-      \par\bigskip
-      \caption{Change in the concentration of $\alpha$ during training for various heuristics}
-      \label{fig:results:case_study:iris:alpha}
-\end{figure}
-
-Due to the Bayesian nature of the \Acs{BHH}, one can expect the plots from figure \ref{fig:results:case_study:iris:alpha} to drive the plots presented in \ref{fig:results:case_study:iris:p_theta} as these two parameters are related.
-The parameter $\alpha$ is the concentration parameter for the Dirichlet probability distribution represented by $\theta$.
-The reader is now urged to consider Figures \ref{fig:results:case_study:iris:alpha:6} and \ref{fig:results:case_study:iris:p_theta:6} together.
-These two figures illustrate the above mentioned Bayesian concepts well.
-It should be noted that as $\alpha$ changes, $\theta$ will change.
-More specifically, the longer the ``memory'' of the \Acs{BHH} the greater the magnitude of $\alpha$ resulting in a sampled selection probability $\theta$ that converges to the ``learnt'' expected selection probability ($E\left[\theta\right]$).
-The impact of this concept (retained memory) is addressed in Sections \ref{sec:results:replay}.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[0].png}
-            \caption{$P(\theta_{0} | \alpha)$ - \Acs{SGD}}
-            \label{fig:results:case_study:iris:p_theta:0}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[1].png}
-            \caption{$P(\theta_{1} | \alpha)$ - \Acs{Momentum}}
-            \label{fig:results:case_study:iris:p_theta:1}
-      \end{subfigure}
-      \par\medskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[2].png}
-            \caption{$P(\theta_{2} | \alpha)$ - \Acs{NAG}}
-            \label{fig:results:case_study:iris:p_theta:2}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[3].png}
-            \caption{$P(\theta_{3} | \alpha)$ - \Acs{Adagrad}}
-            \label{fig:results:case_study:iris:p_theta:3}
-      \end{subfigure}
-      \par\medskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[4].png}
-            \caption{$P(\theta_{4} | \alpha)$ - \Acs{RMSProp}}
-            \label{fig:results:case_study:iris:p_theta:4}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[5].png}
-            \caption{$P(\theta_{5} | \alpha)$ - \Acs{Adadelta}}
-            \label{fig:results:case_study:iris:p_theta:5}
-      \end{subfigure}
-      \par\medskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[6].png}
-            \caption{$P(\theta_{6} | \alpha)$ - \Acs{Adam}}
-            \label{fig:results:case_study:iris:p_theta:6}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[7].png}
-            \caption{$P(\theta_{7} | \alpha)$ - \Acs{PSO}}
-            \label{fig:results:case_study:iris:p_theta:7}
-      \end{subfigure}
-      \par\medskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[8].png}
-            \caption{$P(\theta_{8} | \alpha)$ - \Acs{GA}}
-            \label{fig:results:case_study:iris:p_theta:8}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[9].png}
-            \caption{$P(\theta_{9} | \alpha)$ - \Acs{DE}}
-            \label{fig:results:case_study:iris:p_theta:9}
-      \end{subfigure}
-      \par\medskip
-      \caption{Change in the sampled selection probability of $\theta$ during training for various heuristics}
-      \label{fig:results:case_study:iris:p_theta}
-\end{figure}
-
-Another observation that can be made from Figures \ref{fig:results:case_study:iris:alpha} and \ref{fig:results:case_study:iris:p_theta} is that none of the runs are the same.
-This is of course due to the stochastic nature of the \Acs{BHH} and the noise caused by using mini-batches.
-However, it highlights the fact that the learning process for the \Acs{BHH} has to be adaptive from run to run.
-This is evident in the plots presented in Figure \ref{fig:results:case_study:iris:p_H} as one can see how the \index{heuristic}heuristic selection probability changes over time.
-This is proof that the \Ac{BHH} is learning something, but it is yet to be established what exactly it is learning.
-It is said that the \Acs{BHH} updates its \textit{beliefs} (prior knowledge) about which heuristic to select by biasing selection towards \index{heuristic}heuristic performance.
-It can therefore be concluded that any learning that is done, is done as a result of learning from performance.
-Since the performance criteria mechanism for the \Ac{BHH}, called the \textit{credit assignment strategy} marks a successful event as one meeting the performance criteria.
-Although this event is very much a local event, the continuous application of it over all runs means that learning does account for positive learning towards the overall performance goals.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[0].png}
-            \caption{$P\left(h_{0} | \theta \right)$ - \Acs{SGD}}
-            \label{fig:results:case_study:iris:p_H:0}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[1].png}
-            \caption{$P\left(h_{1} | \theta \right)$ - \Acs{Momentum}}
-            \label{fig:results:case_study:iris:p_H:1}
-      \end{subfigure}
-      \par\medskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[2].png}
-            \caption{$P\left(h_{2} | \theta \right)$ - \Acs{NAG}}
-            \label{fig:results:case_study:iris:p_H:2}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[3].png}
-            \caption{$P\left(h_{3} | \theta \right)$ - \Acs{Adagrad}}
-            \label{fig:results:case_study:iris:p_H:3}
-      \end{subfigure}
-      \par\medskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[4].png}
-            \caption{$P\left(h_{4} | \theta \right)$ - \Acs{RMSProp}}
-            \label{fig:results:case_study:iris:p_H:4}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[5].png}
-            \caption{$P\left(h_{5} | \theta \right)$ - \Acs{Adadelta}}
-            \label{fig:results:case_study:iris:p_H:5}
-      \end{subfigure}
-      \par\medskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[6].png}
-            \caption{$P\left(h_{6} | \theta \right)$ - \Acs{Adam}}
-            \label{fig:results:case_study:iris:p_H:6}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[7].png}
-            \caption{$P\left(h_{7} | \theta \right)$ - \Acs{PSO}}
-            \label{fig:results:case_study:iris:p_H:7}
-      \end{subfigure}
-      \par\medskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[8].png}
-            \caption{$P\left(h_{8} | \theta \right)$ - \Acs{GA}}
-            \label{fig:results:case_study:iris:p_H:8}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[9].png}
-            \caption{$P\left(h_{9} | \theta \right)$ - \Acs{DE}}
-            \label{fig:results:case_study:iris:p_H:9}
-      \end{subfigure}
-      \par\medskip
-      \caption{Change in the prior heuristic selection probability $P\left(H\right | \theta )$ as the \Ac{BHH} learns during training}
-      \label{fig:results:case_study:iris:p_H}
-\end{figure}
-
-Consider now Figure \ref{fig:results:case_study:iris:p_theta:6} again, but this time include a configuration of the \Acs{BHH} where no \index{Bayesian Analysis}Bayesian Analysis takes place, resulting in a purely random \index{heuristic}heuristic selection probability throughout.
-Such an configuration is given in Figure \ref{fig:results:case_study:iris:no_learn:metrics} below for the sampled \index{heuristic}heuristic selection probability for \Acs{Adam} (gray).
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/no_learning_theta.png}
-            \caption{$P(\theta_{6} | \alpha)$}
-            \label{fig:results:case_study:iris:no_learn:p_theta}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/no_learning_test_loss.png}
-            \caption{Test loss}
-            \label{fig:results:case_study:iris:no_learn:test:loss}
-      \end{subfigure}
-      \par\bigskip
-      \caption{Comparing baseline \Acp{BHH} to that of a \Ac{BHH} with pure random selection.}
-      \label{fig:results:case_study:iris:no_learn:metrics}
-\end{figure}
-
-One can see that the random configuration (gray) illustrated almost a fixed pattern behaviour, from which we can draw the following conclusions:
-
-\begin{itemize}
-      \item Despite a completely random heuristic selection probability, the underlying \Acs{BHH} was still able to learn and perform relatively well.
-If the ability to learn is then purely based on the \textit{perturbative} components of the \Acs{BHH} it can be concluded that the proxied heuristic step operations are successful.
-
-      \item This shows that the \Acs{BHH} selection mechanism is indeed facilitating a learning process and since \Acs{Adam} is known to perform well on the iris dataset, it can be concluded that the learning process is successful and beneficial to the outcome of the \Acs{BHH}.
-\end{itemize}
-
-The statements made above conclude the successful working of the \Acs{BHH}.
-Both the perturbative element (through proxied heuristic update steps) and the selection mechanism (through Bayesian analysis) is shown to work successfully.
-Figure \ref{fig:results:case_study:iris:p_HgEC} shows the resulting output of the predictive model for each of the five entities in the heuristic pool.
-This predicted heuristic selection probability is used to parameterise a new categorical distribution from which the heuristics are finally sampled and (re)selected.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[0][6].png}
-            \caption{$P\left(h_{6}|e_{0},c_{1}\right)$ - entity 0 + \Acs{Adam} }
-            \label{fig:results:case_study:iris:p_HgEC:0:6}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[1][6].png}
-            \caption{$P\left(h_{6}|e_{1},c_{1}\right)$ - entity 1 + \Acs{Adam} }
-            \label{fig:results:case_study:iris:p_HgEC:1:6}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[2][6].png}
-            \caption{$P\left(h_{6}|e_{2},c_{1}\right)$ - entity 2 + \Acs{Adam} }
-            \label{fig:results:case_study:iris:p_HgEC:2:6}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[3][6].png}
-            \caption{$P\left(h_{6}|e_{3},c_{1}\right)$ - entity 3 + \Acs{Adam} }
-            \label{fig:results:case_study:iris:p_HgEC:3:6}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{\textwidth}
-            \centering
-            \includegraphics[width=0.5\textwidth]{bhh_case_study/iris/p_HgEC[4][6].png}
-            \caption{$P\left(h_{6}|e_{4},c_{1}\right)$ - entity 4 + \Acs{Adam} }
-            \label{fig:results:case_study:iris:p_HgEC:4:6}
-      \end{subfigure}
-      \par\bigskip
-      \caption{Change in the realised output of the predictive model $P\left(H|E,C;\theta,\phi,\psi \right)$ showcasing the selection of the \Acs{Adam} optimiser/low-level heuristic as an example}
-      \label{fig:results:case_study:iris:p_HgEC}
-\end{figure}
-
-Figure \ref{fig:results:case_study:iris:HgEC} show the resulting selected \index{heuristic}heuristic, per entity, over time.
-From these plots, one can see how convergence on \Acs{Adam} occurs at least at some point during training for the majority of the entities.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[0].png}
-            \caption{HgEC\lbrack0\rbrack - entity 0}
-            \label{fig:results:case_study:iris:HgEC:0}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[1].png}
-            \caption{HgEC\lbrack1\rbrack - entity 1}
-            \label{fig:results:case_study:iris:HgEC:1}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[2].png}
-            \caption{HgEC\lbrack2\rbrack - entity 2}
-            \label{fig:results:case_study:iris:HgEC:2}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[3].png}
-            \caption{HgEC\lbrack3\rbrack - entity 3}
-            \label{fig:results:case_study:iris:HgEC:3}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{\textwidth}
-            \centering
-            \includegraphics[width=0.5\textwidth]{bhh_case_study/iris/HgEC[4].png}
-            \caption{HgEC\lbrack4\rbrack - entity 4}
-            \label{fig:results:case_study:iris:HgEC:4}
-      \end{subfigure}
-      \par\bigskip
-      \caption{Change in selected heuristics (HgEC) during training for various entities}
-      \label{fig:results:case_study:iris:HgEC}
-\end{figure}
-
-Finally, Figure \ref{fig:results:case_study:iris:adam:HgEC} below shows all of the probabilistic components involved in the selection mechanism of the \Ac{BHH}.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[6].png}
-            \caption{$\alpha_{6}$ - \Acs{Adam}}
-            \label{fig:results:case_study:iris:adam:alpha:6}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/theta[6].png}
-            \caption{$P(\theta_{6} | \alpha)$ - \Acs{Adam}}
-            \label{fig:results:case_study:iris:adam:p_theta:6}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[6].png}
-            \caption{$P\left(h_{6} | \theta \right)$ - \Acs{Adam}}
-            \label{fig:results:case_study:iris:adam:p_H:6}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[1][6].png}
-            \caption{$P\left(h_{6}|e_{1},c_{1}\right)$ - entity 1 + \Acs{Adam} }
-            \label{fig:results:case_study:iris:adam:p_HgEC:1:6}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{\textwidth}
-            \centering
-            \includegraphics[width=0.5\textwidth]{bhh_case_study/iris/HgEC[1].png}
-            \caption{HgEC\lbrack1\rbrack - entity 1}
-            \label{fig:results:case_study:iris:adam:HgEC:1}
-      \end{subfigure}
-      \par\bigskip
-      \caption{An illustration that shows the effects of learning as for \Acs{Adam}}
-      \label{fig:results:case_study:iris:adam:HgEC}
-\end{figure}
-
-The behaviour of the \Ac{BHH} has been studied and it is found to be successful in its intent to learn which \index{heuristic}heuristics to use throughout the training process.
-It has also been shown that the training of the \acp{FFNN} with \Acp{BHH} is done by means of a \index{heuristic}heuristic selection mechanism and proxied \index{heuristic}heuristic update steps, both which have been shown to attribute to the successful training of the \acp{FFNN}.
-
-Although these observations are good, these are still high level and not based on any statistical data.
-It is purely based on observation over a few runs.
-The following section aims to provide the first set of conclusions based on a statistically certain comparison of the \Ac{BHH}'s performance to that of standalone low-level \index{heuristic}heuristics.
-
-\section{Standalone vs BHH Baseline}
-\label{sec:results:standalone}
-
-This section provides the empirical results of the experiment group that compare the performance of the \Ac{BHH} to that of well-known, standalone, low-level heuristics.
-Table \ref{tab:results:standalone:metrics} below shows the count, average and standard deviation of the ranks achieved by die various heuristics for all timestamps, across all datasets.
-Furthermore, the table orders the \index{heuristic}heuristics by a normalised overall rank.
-
-\begin{table}[htbp]
-      \centering
-      \caption{Empirical results showcasing rank statistics for different standalone \index{heuristic}heuristics compared to the baseline \acs{BHH} across multiple datasets}
-      \label{tab:results:standalone:metrics}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{rcccccccccccc}
-                  \textbf{step}                      & \multicolumn{1}{l}{\textbf{(All)}}     &                                                                                    &                                                                           &                                                                           &                                                                           &                                               &                                             &                                                &                                                &                                                &                                                &                                                \\
-                  \cmidrule{1-2}                     &                                        &                                                                                    &                                                                           &                                                                           &                                                                           &                                               &                                             &                                                &                                                &                                                &                                                &                                                \\
-                                                     &                                        & \multicolumn{1}{l}{\textbf{heuristic}}                                             &                                                                           &                                                                           &                                                                           &                                               &                                             &                                                &                                                &                                                &                                                &                                                \\
-                  \cmidrule{3-3}    \textbf{dataset} & \multicolumn{1}{l}{\textbf{statistic}} & \textbf{adagrad}                                                                   & \textbf{adam}                                                             & \textbf{nag}                                                              & \textbf{rmsprop}                                                          & \textbf{bhh}                                  & \textbf{adadelta}                           & \textbf{ga}                                    & \textbf{sgd}                                   & \textbf{pso}                                   & \textbf{momentum}                              & \textbf{de}                                    \\
-                  \midrule
-                  abalone                            & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.0323}          & 2.2086                                                                    & 3.8108                                                                    & 4.0849                                                                    & 5.1430                                        & 4.7151                                      & 9.1839                                         & 6.9043                                         & 9.3914                                         & 7.9441                                         & 10.5817                                        \\
-                                                     & std                                    & 1.3436                                                                             & 1.5671                                                                    & 1.2760                                                                    & 2.2093                                                                    & 1.9327                                        & 1.1671                                      & 0.9030                                         & 0.7740                                         & 1.5268                                         & 0.9717                                         & 1.1291                                         \\
-                  adult                              & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 5.1570                                                                             & 6.3559                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4914} & 5.6968                                                                    & 10.1710                                       & 2.4720                                      & 7.7688                                         & 2.8237                                         & 9.6043                                         & 3.6688                                         & 9.0140                                         \\
-                                                     & std                                    & 1.2838                                                                             & 1.4823                                                                    & 0.6870                                                                    & 1.4006                                                                    & 2.2688                                        & 1.2974                                      & 1.3461                                         & 1.1988                                         & 1.6718                                         & 1.3834                                         & 1.5614                                         \\
-                  air\_quality                       & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 3.0688                                                                             & 4.4849                                                                    & 3.2527                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9269} & 5.4989                                        & 4.4204                                      & 6.3785                                         & 8.7548                                         & 8.1151                                         & 9.8301                                         & 9.2688                                         \\
-                                                     & std                                    & 1.8148                                                                             & 2.0087                                                                    & 1.7266                                                                    & 2.0466                                                                    & 2.5018                                        & 2.5575                                      & 1.7707                                         & 1.4074                                         & 1.9775                                         & 1.3046                                         & 1.9578                                         \\
-                  bank                               & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 2.4161                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9882} & 3.8516                                                                    & 3.1591                                                                    & 5.4688                                        & 5.0108                                      & 9.0505                                         & 7.2301                                         & 9.9043                                         & 7.3892                                         & 10.5312                                        \\
-                                                     & std                                    & 1.3873                                                                             & 1.3985                                                                    & 1.4056                                                                    & 1.8653                                                                    & 1.7489                                        & 0.9864                                      & 0.9955                                         & 0.9144                                         & 1.2374                                         & 0.8907                                         & 1.0445                                         \\
-                  bike                               & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6710}          & 3.2559                                                                    & 5.4247                                                                    & 5.4140                                                                    & 3.5903                                        & 4.3774                                      & 7.2591                                         & 8.3656                                         & 7.4000                                         & 8.7441                                         & 10.4978                                        \\
-                                                     & std                                    & 1.1854                                                                             & 3.2580                                                                    & 0.9310                                                                    & 3.7231                                                                    & 1.0534                                        & 1.0684                                      & 1.0992                                         & 1.3163                                         & 1.6037                                         & 1.2745                                         & 1.2717                                         \\
-                  car                                & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 3.8591                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5022} & 5.0839                                                                    & 2.0946                                                                    & 2.9720                                        & 6.5903                                      & 8.9301                                         & 8.4108                                         & 7.0118                                         & 9.0731                                         & 10.4720                                        \\
-                                                     & std                                    & 0.8054                                                                             & 1.1602                                                                    & 0.6925                                                                    & 1.1095                                                                    & 1.0151                                        & 1.4439                                      & 1.2877                                         & 1.2333                                         & 1.2970                                         & 1.1743                                         & 1.2916                                         \\
-                  diabetic                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 2.6129                                                                             & 6.0634                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7473} & 5.8387                                                                    & 7.9452                                        & 2.5129                                      & 9.2409                                         & 5.1968                                         & 8.7527                                         & 5.5516                                         & 10.5376                                        \\
-                                                     & std                                    & 1.3914                                                                             & 1.6944                                                                    & 1.2492                                                                    & 2.0128                                                                    & 2.4141                                        & 1.3843                                      & 1.2206                                         & 1.2711                                         & 0.9424                                         & 1.3025                                         & 1.0607                                         \\
-                  fish\_toxicity                     & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 3.6032                                                                             & 3.0742                                                                    & 4.8742                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.0462} & 4.8387                                        & 6.5785                                      & 5.5419                                         & 9.6462                                         & 6.2484                                         & 10.2731                                        & 8.2753                                         \\
-                                                     & std                                    & 2.0999                                                                             & 2.0463                                                                    & 2.2127                                                                    & 1.8158                                                                    & 2.2145                                        & 2.7393                                      & 2.2031                                         & 1.2726                                         & 2.4357                                         & 1.1959                                         & 2.0085                                         \\
-                  forest\_fires                      & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 4.1269                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.4634} & 4.6075                                                                    & 4.0860                                                                    & 4.4172                                        & 5.2011                                      & 5.8978                                         & 8.8591                                         & 5.2172                                         & 9.7538                                         & 10.3699                                        \\
-                                                     & std                                    & 2.4170                                                                             & 2.2577                                                                    & 1.7329                                                                    & 2.4576                                                                    & 2.5304                                        & 2.5924                                      & 1.9010                                         & 1.0073                                         & 2.6924                                         & 1.0954                                         & 1.7882                                         \\
-                  housing                            & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 3.0043                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9484} & 3.9495                                                                    & 3.2505                                                                    & 3.7720                                        & 6.2290                                      & 6.4538                                         & 9.4570                                         & 8.1570                                         & 9.3140                                         & 9.4645                                         \\
-                                                     & std                                    & 1.6877                                                                             & 1.5719                                                                    & 2.0695                                                                    & 1.7785                                                                    & 1.9772                                        & 2.1729                                      & 1.6569                                         & 1.3649                                         & 1.9825                                         & 1.3537                                         & 1.8465                                         \\
-                  iris                               & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 5.1613                                                                             & 3.0269                                                                    & 3.0462                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3925} & 4.3624                                        & 9.4419                                      & 6.6667                                         & 8.4839                                         & 6.9333                                         & 9.1344                                         & 7.3505                                         \\
-                                                     & std                                    & 1.2630                                                                             & 1.9064                                                                    & 1.6829                                                                    & 1.5569                                                                    & 2.4400                                        & 1.6211                                      & 1.4704                                         & 1.2011                                         & 3.6375                                         & 1.2817                                         & 2.7492                                         \\
-                  mushroom                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 3.6548                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8935} & 5.3484                                                                    & 2.2183                                                                    & 3.1484                                        & 5.5613                                      & 9.6634                                         & 7.9290                                         & 6.7774                                         & 9.0559                                         & 10.7495                                        \\
-                                                     & std                                    & 0.8854                                                                             & 1.5571                                                                    & 0.8150                                                                    & 1.1594                                                                    & 2.0245                                        & 0.9914                                      & 0.9675                                         & 0.8373                                         & 0.7826                                         & 0.9205                                         & 1.2513                                         \\
-                  parkinsons                         & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 2.2925                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.0376} & 6.2882                                                                    & 3.1634                                                                    & 3.8269                                        & 5.5226                                      & 6.5172                                         & 9.7839                                         & 7.0301                                         & 10.5785                                        & 8.9591                                         \\
-                                                     & std                                    & 1.2860                                                                             & 1.4103                                                                    & 1.1341                                                                    & 1.9798                                                                    & 1.4677                                        & 1.8893                                      & 1.3465                                         & 0.9741                                         & 1.4772                                         & 1.1491                                         & 1.1386                                         \\
-                  student\_performance               & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495}          & 9.6022                                                                    & 2.7731                                                                    & 10.5204                                                                   & 4.8806                                        & 2.8742                                      & 5.9376                                         & 5.6280                                         & 9.1957                                         & 5.6731                                         & 6.6656                                         \\
-                                                     & std                                    & 1.5171                                                                             & 1.8140                                                                    & 1.7252                                                                    & 1.1290                                                                    & 2.5544                                        & 1.5612                                      & 1.5940                                         & 1.7346                                         & 0.8806                                         & 1.6999                                         & 1.4815                                         \\
-                  wine\_quality                      & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                                                       & 930                                           & 930                                         & 930                                            & 930                                            & 930                                            & 930                                            & 930                                            \\
-                                                     & avg                                    & 2.9774                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9634} & 3.7194                                                                    & 3.2624                                                                    & 4.6140                                        & 5.2989                                      & 8.6882                                         & 7.3806                                         & 9.3785                                         & 8.0796                                         & 10.6376                                        \\
-                                                     & std                                    & 1.7194                                                                             & 1.4491                                                                    & 1.6072                                                                    & 1.4218                                                                    & 1.5987                                        & 1.9742                                      & 1.2730                                         & 0.9310                                         & 1.4409                                         & 1.0672                                         & 1.1360                                         \\
-                  \midrule
-                  \textbf{overall}                   & \textbf{avg}                           & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{3.1925}} & \textbf{3.5913}                                                           & \textbf{3.9513}                                                           & \textbf{4.0770}                                                           & \textbf{4.9766}                               & \textbf{5.1204}                             & \textbf{7.5452}                                & \textbf{7.6569}                                & \textbf{7.9411}                                & \textbf{8.2709}                                & \textbf{9.5584}                                \\
-                  \textbf{normalised}                & \textbf{rank}                          & \cellcolor[rgb]{ .388,  .745,  .482}\textbf{1}                                     & \cellcolor[rgb]{ .51,  .78,  .486}\textbf{2}                              & \cellcolor[rgb]{ .631,  .816,  .494}\textbf{3}                            & \cellcolor[rgb]{ .753,  .851,  .502}\textbf{4}                            & \cellcolor[rgb]{ .875,  .886,  .51}\textbf{5} & \cellcolor[rgb]{ 1,  .922,  .518}\textbf{6} & \cellcolor[rgb]{ .996,  .824,  .502}\textbf{7} & \cellcolor[rgb]{ .992,  .722,  .482}\textbf{8} & \cellcolor[rgb]{ .984,  .616,  .459}\textbf{9} & \cellcolor[rgb]{ .98,  .514,  .439}\textbf{10} & \cellcolor[rgb]{ .973,  .412,  .42}\textbf{11} \\
-            \end{tabular}%
-      }
-\end{table}%
-
-From Table \ref{tab:results:standalone:metrics} it can be seen that \index{heuristic}heuristic performance is problem/dataset specific.
-Despite this fact, it can be seen that the \Ac{BHH} managed to perform fairly well across almost all datasets (apart from the adult dataset for which discussions follow later) and achieved a normalised overall rank of 5 out of 12.
-As mentioned before, the rank should be taken with a pinch of salt, however, it does show the general capabilities of the \Ac{BHH}.
-It is expected that the performance of the \Ac{BHH} should be close to that of the best \index{heuristic}heuristic for that particular dataset.
-Both the rank and test loss metrics are indicative of this.
-Table \ref{tab:results:standalone:anova} shows the results of the ANOVA statistical test and it shows that the results are statistically significant between the heuristics.
-
-\begin{table}[htbp]
-      \centering
-      \caption{ANOVA - Rank - Standalone vs BHH Baseline}
-      \label{tab:results:standalone:anova}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrr}
-                  \toprule
-                  Cases               & Sum of Squares & df       & Mean Square & F           & p        \\
-                  \cmidrule[0.4pt]{1-6}
-                  dataset             & $248.990$      & $14$     & $17.785$    & $6.515$     & $<$ .001 \\
-                  heuristic           & $699163.514$   & $10$     & $69916.351$ & $25612.484$ & $<$ .001 \\
-                  dataset * heuristic & $421571.950$   & $140$    & $3011.228$  & $1103.104$  & $<$ .001 \\
-                  Residuals           & $418433.761$   & $153285$ & $2.730$     &             &          \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
-            \end{tabular}
-      }
-\end{table}
-
-\begin{table}[htbp]
-      \centering
-      \caption{Post Hoc Comparisons - Standalone vs BHH Baseline}
-      \label{tab:results:standalone:post_hoc}%
-      \par\bigskip
-      \resizebox{0.7\textwidth}{!}{
-            \begin{tabular}{lrrrrrrr}
-                  \toprule
-                  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}               \\
-                  \cline{4-5}
-                  $ $                  & $ $                  & Mean Difference      & Lower                                           & Upper                & SE                   & t                    & p$_{tukey}$ \\
-                  \cmidrule[0.4pt]{1-8}
-                  adadelta             & adagrad              & $1.928$              & $1.864$                                         & $1.992$              & $0.020$              & $97.455$             & $<$ .001    \\
-                  $ $                  & adam                 & $1.529$              & $1.466$                                         & $1.593$              & $0.020$              & $77.298$             & $<$ .001    \\
-                                       & bhh                  & $0.144$              & $0.080$                                         & $0.207$              & $0.020$              & $7.269$              & $<$ .001    \\
-                                       & de                   & $-4.438$             & $-4.502$                                        & $-4.374$             & $0.020$              & $-224.330$           & $<$ .001    \\
-                                       & ga                   & $-2.425$             & $-2.488$                                        & $-2.361$             & $0.020$              & $-122.570$           & $<$ .001    \\
-                                       & momentum             & $-3.150$             & $-3.214$                                        & $-3.087$             & $0.020$              & $-159.251$           & $<$ .001    \\
-                                       & nag                  & $1.169$              & $1.106$                                         & $1.233$              & $0.020$              & $59.100$             & $<$ .001    \\
-                                       & pso                  & $-2.821$             & $-2.884$                                        & $-2.757$             & $0.020$              & $-142.583$           & $<$ .001    \\
-                                       & rmsprop              & $1.043$              & $0.980$                                         & $1.107$              & $0.020$              & $52.744$             & $<$ .001    \\
-                                       & sgd                  & $-2.536$             & $-2.600$                                        & $-2.473$             & $0.020$              & $-128.216$           & $<$ .001    \\
-                  adagrad              & adam                 & $-0.399$             & $-0.462$                                        & $-0.335$             & $0.020$              & $-20.158$            & $<$ .001    \\
-                  $ $                  & bhh                  & $-1.784$             & $-1.848$                                        & $-1.720$             & $0.020$              & $-90.187$            & $<$ .001    \\
-                                       & de                   & $-6.366$             & $-6.430$                                        & $-6.302$             & $0.020$              & $-321.786$           & $<$ .001    \\
-                                       & ga                   & $-4.353$             & $-4.416$                                        & $-4.289$             & $0.020$              & $-220.026$           & $<$ .001    \\
-                                       & momentum             & $-5.078$             & $-5.142$                                        & $-5.015$             & $0.020$              & $-256.707$           & $<$ .001    \\
-                                       & nag                  & $-0.759$             & $-0.822$                                        & $-0.695$             & $0.020$              & $-38.355$            & $<$ .001    \\
-                                       & pso                  & $-4.749$             & $-4.812$                                        & $-4.685$             & $0.020$              & $-240.039$           & $<$ .001    \\
-                                       & rmsprop              & $-0.885$             & $-0.948$                                        & $-0.821$             & $0.020$              & $-44.711$            & $<$ .001    \\
-                                       & sgd                  & $-4.464$             & $-4.528$                                        & $-4.401$             & $0.020$              & $-225.671$           & $<$ .001    \\
-                  adam                 & bhh                  & $-1.385$             & $-1.449$                                        & $-1.322$             & $0.020$              & $-70.029$            & $<$ .001    \\
-                  $ $                  & de                   & $-5.967$             & $-6.031$                                        & $-5.903$             & $0.020$              & $-301.628$           & $<$ .001    \\
-                                       & ga                   & $-3.954$             & $-4.018$                                        & $-3.890$             & $0.020$              & $-199.868$           & $<$ .001    \\
-                                       & momentum             & $-4.680$             & $-4.743$                                        & $-4.616$             & $0.020$              & $-236.549$           & $<$ .001    \\
-                                       & nag                  & $-0.360$             & $-0.424$                                        & $-0.296$             & $0.020$              & $-18.197$            & $<$ .001    \\
-                                       & pso                  & $-4.350$             & $-4.414$                                        & $-4.286$             & $0.020$              & $-219.881$           & $<$ .001    \\
-                                       & rmsprop              & $-0.486$             & $-0.549$                                        & $-0.422$             & $0.020$              & $-24.553$            & $<$ .001    \\
-                                       & sgd                  & $-4.066$             & $-4.129$                                        & $-4.002$             & $0.020$              & $-205.513$           & $<$ .001    \\
-                  bhh                  & de                   & $-4.582$             & $-4.645$                                        & $-4.518$             & $0.020$              & $-231.599$           & $<$ .001    \\
-                  $ $                  & ga                   & $-2.569$             & $-2.632$                                        & $-2.505$             & $0.020$              & $-129.839$           & $<$ .001    \\
-                                       & momentum             & $-3.294$             & $-3.358$                                        & $-3.231$             & $0.020$              & $-166.520$           & $<$ .001    \\
-                                       & nag                  & $1.025$              & $0.962$                                         & $1.089$              & $0.020$              & $51.831$             & $<$ .001    \\
-                                       & pso                  & $-2.965$             & $-3.028$                                        & $-2.901$             & $0.020$              & $-149.852$           & $<$ .001    \\
-                                       & rmsprop              & $0.900$              & $0.836$                                         & $0.963$              & $0.020$              & $45.476$             & $<$ .001    \\
-                                       & sgd                  & $-2.680$             & $-2.744$                                        & $-2.617$             & $0.020$              & $-135.485$           & $<$ .001    \\
-                  de                   & ga                   & $2.013$              & $1.949$                                         & $2.077$              & $0.020$              & $101.760$            & $<$ .001    \\
-                  $ $                  & momentum             & $1.287$              & $1.224$                                         & $1.351$              & $0.020$              & $65.079$             & $<$ .001    \\
-                                       & nag                  & $5.607$              & $5.543$                                         & $5.671$              & $0.020$              & $283.431$            & $<$ .001    \\
-                                       & pso                  & $1.617$              & $1.554$                                         & $1.681$              & $0.020$              & $81.747$             & $<$ .001    \\
-                                       & rmsprop              & $5.481$              & $5.418$                                         & $5.545$              & $0.020$              & $277.075$            & $<$ .001    \\
-                                       & sgd                  & $1.901$              & $1.838$                                         & $1.965$              & $0.020$              & $96.115$             & $<$ .001    \\
-                  ga                   & momentum             & $-0.726$             & $-0.789$                                        & $-0.662$             & $0.020$              & $-36.681$            & $<$ .001    \\
-                  $ $                  & nag                  & $3.594$              & $3.530$                                         & $3.658$              & $0.020$              & $181.670$            & $<$ .001    \\
-                                       & pso                  & $-0.396$             & $-0.460$                                        & $-0.332$             & $0.020$              & $-20.013$            & $<$ .001    \\
-                                       & rmsprop              & $3.468$              & $3.405$                                         & $3.532$              & $0.020$              & $175.315$            & $<$ .001    \\
-                                       & sgd                  & $-0.112$             & $-0.175$                                        & $-0.048$             & $0.020$              & $-5.645$             & $<$ .001    \\
-                  momentum             & nag                  & $4.320$              & $4.256$                                         & $4.383$              & $0.020$              & $218.352$            & $<$ .001    \\
-                  $ $                  & pso                  & $0.330$              & $0.266$                                         & $0.393$              & $0.020$              & $16.668$             & $<$ .001    \\
-                                       & rmsprop              & $4.194$              & $4.130$                                         & $4.258$              & $0.020$              & $211.996$            & $<$ .001    \\
-                                       & sgd                  & $0.614$              & $0.550$                                         & $0.678$              & $0.020$              & $31.036$             & $<$ .001    \\
-                  nag                  & pso                  & $-3.990$             & $-4.054$                                        & $-3.926$             & $0.020$              & $-201.683$           & $<$ .001    \\
-                  $ $                  & rmsprop              & $-0.126$             & $-0.189$                                        & $-0.062$             & $0.020$              & $-6.356$             & $<$ .001    \\
-                                       & sgd                  & $-3.706$             & $-3.769$                                        & $-3.642$             & $0.020$              & $-187.316$           & $<$ .001    \\
-                  pso                  & rmsprop              & $3.864$              & $3.800$                                         & $3.928$              & $0.020$              & $195.328$            & $<$ .001    \\
-                  $ $                  & sgd                  & $0.284$              & $0.221$                                         & $0.348$              & $0.020$              & $14.367$             & $<$ .001    \\
-                  rmsprop              & sgd                  & $-3.580$             & $-3.644$                                        & $-3.516$             & $0.020$              & $-180.960$           & $<$ .001    \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 11 estimates (confidence intervals corrected using the tukey method).} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
-            \end{tabular}
-      }
-\end{table}
-
-Table \ref{tab:results:standalone:post_hoc} presents the results of the Post Hoc Tukey test and Figure \ref{fig:results:standalone:descriptive:descriptive} provides a descriptive plot that provides an alternative visualisation to see how the performance of the \Ac{BHH} compares across datasets and how it compares to other low-level heuristics.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.png}
-      \caption{Descriptive plots between the average ranks of standalone heuristics compared to the baseline \Acs{BHH} per dataset, across all runs and steps.}
-      \label{fig:results:standalone:descriptive:descriptive}
-\end{figure}
-
-Figure \ref{fig:results:standalone:descriptive:cd} provides the critical difference plots for the average ranks of the heuristics across all datasets.
-From this one can see five statistically significant groups of heuristics, with the \Ac{BHH} falling in the middle in group three.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
-      \caption{Critical difference plots between the average ranks of standalone heuristics compared to the baseline \Acs{BHH}, across all datasets, runs and steps.}
-      \label{fig:results:standalone:descriptive:cd}
-\end{figure}
-
-Figure \ref{fig:results:standalone:figures:car} provides example training and test loss and accuracy plots for all heuristics for the car dataset and Figure \ref{fig:results:standalone:figures:iris} provides the same plots, but for the iris dataset.
-These plots are provided to visualise the training and test outcomes over time.
-Figure \ref{fig:results:standalone:figures:loss:test:iris} was included to show how drastic the overfitting can become if early stopping is not employed.
-One can see that most of the gradient-based heuristics performed as expected, by the population-based approaches really struggle after learning has become stagnated.
-This is an important concept, because one has to remember that the \Ac{BHH} might ``try-out'' a certain heuristic and in a single step could cause the heuristic to generalise badly on the test set.
-Once again, the noise of mini-batches plays a large role here.
-
-Finally, a collection of test loss plots for various datasets is given in Figures \ref{fig:results:standalone:figures:test:loss:various1} and \ref{fig:results:standalone:figures:test:loss:various2}.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
-            \caption{Train loss}
-            \label{fig:results:standalone:figures:loss:train:car}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
-            \caption{Test loss}
-            \label{fig:results:standalone:figures:loss:test:car}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
-            \caption{Train accuracy}
-            \label{fig:results:standalone:figures:accuracy:train:car}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
-            \caption{Test accuracy}
-            \label{fig:results:standalone:figures:accuracy:test:car}
-      \end{subfigure}
-      \par\bigskip
-      \caption{Standalone vs. \Acs{BHH} baseline - train, test loss and accuracy - dataset: car}
-      \label{fig:results:standalone:figures:car}
-\end{figure}
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/train/loss/iris.pdf}
-            \caption{Train loss}
-            \label{fig:results:standalone:figures:loss:train:iris}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/loss/iris.pdf}
-            \caption{Test loss}
-            \label{fig:results:standalone:figures:loss:test:iris}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/train/accuracy/iris.pdf}
-            \caption{Train accuracy}
-            \label{fig:results:standalone:figures:accuracy:train:iris}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/accuracy/iris.pdf}
-            \caption{Test accuracy}
-            \label{fig:results:standalone:figures:accuracy:test:iris}
-      \end{subfigure}
-      \par\bigskip
-      \caption{Standalone vs. \Acs{BHH} baseline - train, test loss and accuracy - dataset: iris}
-      \label{fig:results:standalone:figures:iris}
-\end{figure}
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.48\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/loss/air_quality.pdf}
-            \caption{air\_quality}
-            \label{fig:results:standalone:figures:test:loss:air_quality}
-      \end{subfigure}
-      \begin{subfigure}{0.48\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/loss/bank.pdf}
-            \caption{bank}
-            \label{fig:results:standalone:figures:test:loss:bank}
-      \end{subfigure}
-      \begin{subfigure}{0.48\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/loss/bike.pdf}
-            \caption{bike}
-            \label{fig:results:standalone:figures:test:loss:bike}
-      \end{subfigure}
-      \begin{subfigure}{0.48\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/loss/fish_toxicity.pdf}
-            \caption{fish\_toxicity}
-            \label{fig:results:standalone:figures:test:loss:fish_toxicity}
-      \end{subfigure}
-      \caption{Standalone vs. \Acs{BHH} baseline - test loss across different datasets part 1}
-      \label{fig:results:standalone:figures:test:loss:various1}
-\end{figure}
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.48\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/loss/forest_fires.pdf}
-            \caption{forest\_fires}
-            \label{fig:results:standalone:figures:test:loss:forest_fires}
-      \end{subfigure}
-      \begin{subfigure}{0.48\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/loss/housing.pdf}
-            \caption{housing}
-            \label{fig:results:standalone:figures:test:loss:housing}
-      \end{subfigure}
-      \begin{subfigure}{0.48\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/loss/parkinsons.pdf}
-            \caption{parkinsons}
-            \label{fig:results:standalone:figures:test:loss:parkinsons}
-      \end{subfigure}
-      \begin{subfigure}{0.48\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{standalone/figures/test/loss/wine_quality.pdf}
-            \caption{wine\_quality}
-            \label{fig:results:standalone:figures:test:loss:wine_quality}
-      \end{subfigure}
-      \caption{Standalone vs. \Acs{BHH} baseline - test loss across different datasets part 2}
-      \label{fig:results:standalone:figures:test:loss:various2}
-\end{figure}
-
-From this experimental group it was shown that the \Ac{BHH} was able to perform relatively well, but was not able to outperform the best \index{heuristic}heuristics.
-This is understandable as there is a lot of noise that makes the learning process imperfect.
-Although learning was shown to be successful, there are many suggestions that could lead to better outcomes.
-One such a suggestion is to add a validation step, similar to that of \ac{MCMC} (ref???), before concentration parameters are accepted and updated.
-Another is to provide the \Ac{BHH} with expert knowledge in its priors.
-For example: if it is known that a certain heuristic works well for a certain dataset, one could bias the priors by biasing the value of  $\alpha$, the concentration parameter for the prior probability distribution, to have an higher initial selection probability (compared to uniform/symmetric selection) for \Ac{Adam}.
-This is a major advantage that the \Ac{BHH} has above other heuristics, the ability to provide expert prior knowledge if needed.
-
-The experiment is deemed successful and the results show promise for the field of \Acp{HH} in general, but specifically in training \Acp{FFNN}.
-The following sections delve into the hyper-parameters of the \Ac{BHH} and how it impacts its performance.
-
-\section{Heuristic Pool}
-\label{sec:results:heuristic_pool}
-
-This section provides the empirical results for an experimental group where the heuristic pool configuration is studied in comparison to the baseline \Ac{BHH}.
-As a reminder to the reader, the heuristic pool refers to the collection of low-level heuristics from which the \Ac{BHH} can select.
-The baseline \Ac{BHH} has a heuristic pool configuration that includes all ten of the low-level heuristics including gradient-based heuristics and meta-heuristics.
-Two alternative heuristic pools are then considered for investigation.
-These includes a configuration where the heuristic pool only consist out of gradient-based low-level heuristics and the other configuration includes only meta-heuristics.
-Table \ref{tab:results:heuristic_pool:metrics} presents the results of the average ranks, per heuristic, per dataset, across all runs, similar to what has been done for other experiments in this chapter.
-
-\begin{table}[htbp]
-      \centering
-      \caption{Empirical results showcasing rank statistics for different heuristic pool configurations used by the \acs{BHH} across multiple datasets}
-      \label{tab:results:heuristic_pool:metrics}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{rccccccccc}
-                  \textbf{step}                       & \multicolumn{1}{l}{\textbf{(All)}} &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
-                  \cmidrule{1-2}                      &                                    &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
-                                                      & \multicolumn{1}{l}{\textbf{pool}}  & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                &                                                                                    &                 &                &                 &                 \\
-                  \cmidrule{2-3}                      & \textbf{all}                       &                                                                           &                 & \textbf{gd}    &                                                                                    &                 & \textbf{mh}    &                 &                 \\
-                  \cmidrule{2-10}    \textbf{dataset} & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count} & \textbf{avg}    & \textbf{std}    \\
-                  \midrule
-                  abalone                             & 930                                & 1.7946                                                                    & 0.6411          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3828}          & 0.5604          & 930            & 2.8226          & 0.4198          \\
-                  adult                               & 930                                & 2.8484                                                                    & 0.5058          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.1559}          & 0.4077          & 930            & 1.8989          & 0.4104          \\
-                  air\_quality                        & 930                                & 2.1871                                                                    & 0.8153          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6828}          & 0.7506          & 930            & 2.1301          & 0.7883          \\
-                  bank                                & 930                                & 1.7731                                                                    & 0.5617          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3215}          & 0.4920          & 930            & 2.9054          & 0.3341          \\
-                  bike                                & 930                                & 1.6247                                                                    & 0.5529          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4387}          & 0.5321          & 930            & 2.9366          & 0.2808          \\
-                  car                                 & 930                                & 1.5903                                                                    & 0.5113          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4409}          & 0.5180          & 930            & 2.9688          & 0.2275          \\
-                  diabetic                            & 930                                & 2.4516                                                                    & 0.7353          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.2806}          & 0.5756          & 930            & 2.2677          & 0.5798          \\
-                  fish\_toxicity                      & 930                                & 1.9903                                                                    & 0.8485          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8344}          & 0.7684          & 930            & 2.1753          & 0.7959          \\
-                  forest\_fires                       & 930                                & 2.0667                                                                    & 0.8338          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8269}          & 0.7813          & 930            & 2.1065          & 0.8066          \\
-                  housing                             & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6043} & 0.6869          & 930            & 1.6602                                                                             & 0.6648          & 930            & 2.7355          & 0.5238          \\
-                  iris                                & 930                                & 1.8581                                                                    & 0.8005          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7806}          & 0.7272          & 930            & 2.3613          & 0.7960          \\
-                  mushroom                            & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5204} & 0.5815          & 930            & 1.5484                                                                             & 0.5273          & 930            & 2.9312          & 0.2890          \\
-                  parkinsons                          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5570} & 0.6238          & 930            & 1.6011                                                                             & 0.5915          & 930            & 2.8419          & 0.4448          \\
-                  student\_performance                & 930                                & 1.9828                                                                    & 0.8220          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7903}          & 0.8480          & 930            & 2.2269          & 0.7152          \\
-                  wine\_quality                       & 930                                & 1.5785                                                                    & 0.5498          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5630          & 930            & 2.9280          & 0.2938          \\
-                  \midrule
-                  \textbf{overall}                    & \textbf{13950}                     & \textbf{1.8952}                                                           & \textbf{0.7730} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.5492}} & \textbf{0.6651} & \textbf{13950} & \textbf{2.5491} & \textbf{0.6684} \\
-            \end{tabular}%
-      }
-\end{table}%
-
-As one would expect, the \index{heuristic pool}heuristic pool for gradient-based-only \index{heuristic}heuristics consistently do significantly better than the baseline and the meta-heuristic configurations.
-This is to be expected for the following reasons:
-
-\begin{itemize}
-      \item Gradient-based approaches are currently the state-of-the art in \Ac{FFNN} training and is the standard approach for doing so. (Ref???)
-
-      \item Switching between gradient-based approaches are easier as they require very little proxied state operations.
-Where they do require proxied state operations, almost all of them borrow from \Ac{Adam}, one of the best gradient-based heuristics at the time of writing.
-
-      \item All the meta-heuristics included are population-based. Since an entire population can be updated at once, the impact of a wrong selection is much larger.
-\end{itemize}
-
-Although it is quite intuitive that the gradient-based \index{heuristic}heuristics would perform well, it does place a constraint on the \Ac{BHH} that the correct heuristics have to be included in the heuristic pool for the \Ac{BHH} to perform similar to the best heuristics.
-However, if a general pool of heuristics with a wide set of capabilities and characteristics is included, the \Ac{BHH} should perform reasonably well and generalise well on the test set.
-From the results presented throughout this section, it is shown that the performance of the \Ac{BHH} is itself problem-dependent.
-Therefore, one can not expect the \Ac{BHH} to perform equally well on all datasets.
-Earlier in Figure \ref{tab:results:standalone:metrics} it was shown that the \Ac{BHH} performed well on all datasets except for adult dataset.
-This is due to overfitting chaos early-on as will be shown later.
-However, if the gradient-only heuristic pool configuration was used, the \Ac{BHH} would've performed much better.
-As a reminder to the reader, the goal of this dissertation is not to develop a universal best heuristic, but rather one that could automate the tedious process of heuristic and parameter search, saving a lot of time.
-
-Table \ref{tab:results:heuristic_pool:anova} provides the results of the ANOVA statistical test and one can see the statistical significance of the results.
-
-\begin{table}[htbp]
-      \centering
-      \caption{ANOVA - Rank - BHH Variant: Heuristic Pool}
-      \label{tab:results:heuristic_pool:anova}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrr}
-                  \toprule
-                  Cases                     & Sum of Squares & df      & Mean Square & F          & p        \\
-                  \cmidrule[0.4pt]{1-6}
-                  dataset                   & $2.710$        & $14$    & $0.194$     & $0.495$    & $0.938$  \\
-                  heuristic\_pool           & $7193.497$     & $2$     & $3596.749$  & $9192.243$ & $<$ .001 \\
-                  dataset * heuristic\_pool & $4376.103$     & $28$    & $156.289$   & $399.430$  & $<$ .001 \\
-                  Residuals                 & $16357.497$    & $41805$ & $0.391$     &            &          \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
-            \end{tabular}
-      }
-\end{table}
-
-Similar to the analysis for other experimental groups, the post hoc tukey test results are given in Table \ref{tab:results:heuristic_pool:post_hoc} below.
-From this table one can see how statistically different the gradient-based heuristic pool performs from the other configurations.
-
-\begin{table}[htbp]
-      \centering
-      \caption{Post Hoc Comparisons - BHH Variant: Heuristic Pool}
-      \label{tab:results:heuristic_pool:post_hoc}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}
-      {
-            \begin{tabular}{lrrrrrrr}
-                  \toprule
-                  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}               \\
-                  \cline{4-5}
-                  $ $                  & $ $                  & Mean Difference      & Lower                                           & Upper                & SE                   & t                    & p$_{tukey}$ \\
-                  \cmidrule[0.4pt]{1-8}
-                  all                  & gd                   & $0.346$              & $0.328$                                         & $0.364$              & $0.007$              & $46.189$             & $<$ .001    \\
-                  $ $                  & mh                   & $-0.654$             & $-0.671$                                        & $-0.636$             & $0.007$              & $-87.306$            & $<$ .001    \\
-                  gd                   & mh                   & $-1.000$             & $-1.017$                                        & $-0.982$             & $0.007$              & $-133.495$           & $<$ .001    \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 3 estimates (confidence intervals corrected using the tukey method).} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
-            \end{tabular}
-      }
-\end{table}
-
-Figure \ref{fig:results:heuristic_pool:descriptive:descriptive} provides the descriptive plots for this experimental group.
-It shows the average rank achieved by heuristics across different datasets.
-Once again, we can see how the performance of the heuristics are problem-dependent.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.png}
-      \caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying heuristic pools per dataset, across all runs and steps.}
-      \label{fig:results:heuristic_pool:descriptive:descriptive}
-\end{figure}
-
-As with the other sections, figure \ref{fig:results:heuristic_pool:descriptive:cd} provides the critical difference plots and finally, example test loss plots are given in Figure \ref{fig:results:heuristic_pool:figures:loss}.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying heuristic pools across all datasets, runs and steps.}
-      \label{fig:results:heuristic_pool:descriptive:cd}
-\end{figure}
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/abalone.pdf}
-            \caption{abalone}
-            \label{fig:results:heuristic_pool:figures:loss1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/wine_quality.pdf}
-            \caption{wine\_quality}
-            \label{fig:results:heuristic_pool:figures:loss2}
-      \end{subfigure}
-      \caption{\Acs{BHH} Heuristic Pool - example test loss plots for varying heuristic pools}
-      \label{fig:results:heuristic_pool:figures:loss}
-\end{figure}
-
-In this section it was established that the choice of heuristic pool has a significant impact on the outcome of the \Ac{BHH}.
-It was shown that the gradient-only pool significantly performs better than the baseline configuration that includes all the heuristics and the meta-heuristic-only pool.
-
-The following section presents the empirical results for the experimental group that focuses on studying the effects of population size on the \Ac{BHH}.
-
-\section{Population}
-\label{sec:results:population}
-
-This section investigates the effects of population size on the \Ac{BHH}.
-Initially the expectation was that a larger population size would perform best as this is the general consensus for population-based \index{heuristic}heuristics (ref ????).
-However, it has been found that population size is largely problem-dependent with some datasets preferring a small population size and others a large population size.
-Table \ref{tab:results:population:metrics} presents these empirical results.
-
-\begin{table}[htbp]
-      \centering
-      \caption{Empirical results showcasing rank statistics for different population size values used by the \acs{BHH} across multiple datasets}
-      \label{tab:results:population:metrics}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{rccccccccccccccc}
-                  \textbf{step}                       & \multicolumn{1}{l}{\textbf{(All)}}      &                                                                                    &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-                  \cmidrule{1-2}                      &                                         &                                                                                    &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-                                                      & \multicolumn{1}{l}{\textbf{population}} & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-                  \cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{5}}          &                                                                                    &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{15}} &                 &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{25}} &                                                                           &                 \\
-                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                          & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    \\
-                  \midrule
-                  abalone                             & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4387}          & 1.3396          & 930                             & 2.7452                                                                    & 1.3922          & 930                             & 3.0129          & 1.3865          & 930                             & 3.4065                                                                    & 1.3513          & 930                             & 3.3968                                                                    & 1.3514          \\
-                  adult                               & 930                                     & 3.5720                                                                             & 1.4693          & 930                             & 3.2828                                                                    & 1.3751          & 930                             & 2.8108          & 1.3625          & 930                             & 2.6484                                                                    & 1.3222          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3634} & 1.3063          \\
-                  air\_quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7527}          & 1.4283          & 930                             & 2.9258                                                                    & 1.3904          & 930                             & 2.9656          & 1.3791          & 930                             & 3.3140                                                                    & 1.3789          & 930                             & 3.0419                                                                    & 1.4374          \\
-                  bank                                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8129}          & 1.4102          & 930                             & 3.1591                                                                    & 1.4348          & 930                             & 2.9989          & 1.4199          & 930                             & 3.0505                                                                    & 1.4438          & 930                             & 2.9785                                                                    & 1.3414          \\
-                  bike                                & 930                                     & 3.8957                                                                             & 1.3355          & 930                             & 2.8688                                                                    & 1.2850          & 930                             & 2.9645          & 1.3447          & 930                             & 2.7430                                                                    & 1.3762          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5280} & 1.3278          \\
-                  car                                 & 930                                     & 3.1892                                                                             & 1.3915          & 930                             & 3.0409                                                                    & 1.3945          & 930                             & 3.0398          & 1.4523          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8559} & 1.3938          & 930                             & 2.8742                                                                    & 1.4151          \\
-                  diabetic                            & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7978}          & 1.5078          & 930                             & 2.9387                                                                    & 1.4133          & 930                             & 3.2129          & 1.4525          & 930                             & 2.9613                                                                    & 1.3036          & 930                             & 3.0892                                                                    & 1.3534          \\
-                  fish\_toxicity                      & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8151}          & 1.4249          & 930                             & 3.0409                                                                    & 1.4288          & 930                             & 3.0925          & 1.3230          & 930                             & 3.1280                                                                    & 1.4073          & 930                             & 2.9237                                                                    & 1.4634          \\
-                  forest\_fires                       & 930                                     & 3.0172                                                                             & 1.4026          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9215} & 1.3800          & 930                             & 2.9806          & 1.3833          & 930                             & 3.0968                                                                    & 1.4124          & 930                             & 2.9839                                                                    & 1.4879          \\
-                  housing                             & 930                                     & 2.8366                                                                             & 1.4040          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8258} & 1.3802          & 930                             & 2.9753          & 1.4393          & 930                             & 2.9849                                                                    & 1.4111          & 930                             & 3.3774                                                                    & 1.3680          \\
-                  iris                                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301}          & 1.3038          & 930                             & 2.8731                                                                    & 1.3970          & 930                             & 3.0505          & 1.4129          & 930                             & 3.1860                                                                    & 1.4251          & 930                             & 3.0602                                                                    & 1.4987          \\
-                  mushroom                            & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7989}          & 1.2052          & 930                             & 2.9441                                                                    & 1.3250          & 930                             & 3.0462          & 1.4521          & 930                             & 3.1366                                                                    & 1.4940          & 930                             & 3.0538                                                                    & 1.5664          \\
-                  parkinsons                          & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6645}          & 1.4411          & 930                             & 3.1065                                                                    & 1.3272          & 930                             & 3.0247          & 1.4265          & 930                             & 3.0495                                                                    & 1.4420          & 930                             & 3.1548                                                                    & 1.3810          \\
-                  student\_performance                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6376}          & 1.4357          & 930                             & 2.8645                                                                    & 1.4108          & 930                             & 3.1548          & 1.4042          & 930                             & 3.2387                                                                    & 1.3970          & 930                             & 3.1043                                                                    & 1.3395          \\
-                  wine\_quality                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5505}          & 1.3165          & 930                             & 2.7817                                                                    & 1.4152          & 930                             & 3.1581          & 1.3841          & 930                             & 3.1806                                                                    & 1.3941          & 930                             & 3.3290                                                                    & 1.4140          \\
-                  \midrule
-                  \textbf{overall}                    & \textbf{13950}                          & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9073}} & \textbf{1.4377} & \textbf{13950}                  & \textbf{2.9546}                                                           & \textbf{1.3904} & \textbf{13950}                  & \textbf{3.0325} & \textbf{1.4045} & \textbf{13950}                  & \textbf{3.0654}                                                           & \textbf{1.4108} & \textbf{13950}                  & \textbf{3.0173}                                                           & \textbf{1.4306} \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Tables \ref{tab:results:population:anova} presents the ANOVA statistical test results and Table \ref{tab:results:population:post_hoc} presents the post hoc Tukey test results.
-Both these tables present the results as statistically significant.
-
-\begin{table}[htbp]
-      \centering
-      \caption{ANOVA - Rank - BHH Variant: Population}
-      \label{tab:results:population:anova}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrr}
-                  \toprule
-                  Cases                & Sum of Squares & df      & Mean Square & F        & p        \\
-                  \cmidrule[0.4pt]{1-6}
-                  dataset              & $17.974$       & $14$    & $1.284$     & $0.659$  & $0.816$  \\
-                  population           & $225.672$      & $4$     & $56.418$    & $28.961$ & $<$ .001 \\
-                  dataset * population & $3879.662$     & $56$    & $69.280$    & $35.564$ & $<$ .001 \\
-                  Residuals            & $135730.233$   & $69675$ & $1.948$     &          &          \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
-            \end{tabular}
-      }
-
-\end{table}
-
-\begin{table}[htbp]
-      \centering
-      \caption{Post Hoc Comparisons - BHH Variant: Population}
-      \label{tab:results:population:post_hoc}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrrrr}
-                  \toprule
-                  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}               \\
-                  \cline{4-5}
-                  $ $                  & $ $                  & Mean Difference      & Lower                                           & Upper                & SE                   & t                    & p$_{tukey}$ \\
-                  \cmidrule[0.4pt]{1-8}
-                  $5$                  & $10$                 & $-0.047$             & $-0.093$                                        & $-0.002$             & $0.017$              & $-2.831$             & $0.037$     \\
-                  $ $                  & $15$                 & $-0.125$             & $-0.171$                                        & $-0.080$             & $0.017$              & $-7.494$             & $<$ .001    \\
-                                       & $20$                 & $-0.158$             & $-0.204$                                        & $-0.112$             & $0.017$              & $-9.458$             & $<$ .001    \\
-                                       & $25$                 & $-0.110$             & $-0.156$                                        & $-0.064$             & $0.017$              & $-6.580$             & $<$ .001    \\
-                  $10$                 & $15$                 & $-0.078$             & $-0.124$                                        & $-0.032$             & $0.017$              & $-4.663$             & $<$ .001    \\
-                  $ $                  & $20$                 & $-0.111$             & $-0.156$                                        & $-0.065$             & $0.017$              & $-6.627$             & $<$ .001    \\
-                                       & $25$                 & $-0.063$             & $-0.108$                                        & $-0.017$             & $0.017$              & $-3.749$             & $0.002$     \\
-                  $15$                 & $20$                 & $-0.033$             & $-0.078$                                        & $0.013$              & $0.017$              & $-1.965$             & $0.283$     \\
-                  $ $                  & $25$                 & $0.015$              & $-0.030$                                        & $0.061$              & $0.017$              & $0.914$              & $0.892$     \\
-                  $20$                 & $25$                 & $0.048$              & $0.003$                                         & $0.094$              & $0.017$              & $2.878$              & $0.033$     \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{$ $ * p $<$ .05, ** p < .01, *** p < .001} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{* $$} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{** $$} \\
-            \end{tabular}
-      }
-\end{table}
-
-From the descriptive plots given in Figure \ref{fig:results:population:descriptive:descriptive} one can see how radically different the outcomes are for each dataset.
-This clearly shows that population size, in most cases prefer a small population size, but there are multiple cases where a larger population size is preferred.
-Consider the plots for the abalone and adult datasets in this figure.
-They exhibit opposite outcomes for population size.
-Abalone prefers a small population size, while adult prefers larger population sizes.
-This makes the population size relatively problem dependent with a general tendency to prefer smaller population sizes.
-
-Another interesting observation to make is that for many of the descriptive plots such as for student\_performance, fish\_toxicity, iris, mushroom and bank, the average rank and population size is not linearly correlated which suggests an interesting opportunity for further investigation.
-
-Postulate for a moment why in some cases a smaller population size could be preferred.
-A larger population size means more combinations of heuristics and entities.
-Statistically these require many more samples to be able to achieve the same level of learning as with smaller populations.
-Since the nature of the \Ac{BHH} is in statistical and probabilistic components it makes sense that a larger sample leads to a harder learning and training process.
-As a reminder to the reader, the \ac{BHH} selection mechanism is a posterior probability distribution that is dependent on an entity and performance criteria.
-The larger the number of entities, the bigger the number of combinations in which this posterior distribution can be realises.
-Furthermore, with larger population sizes, the difficulty of managing and maintaining consistent entity state from iteration to iteration, between the switching of heuristics, increases drastically.
-This means that invalid selections and bad state update operations are more likely to propagate throughout the population.
-This argument is yet to be determined empirically, but it could be that the outcome of population size could be determined by the difference in importance between the selection mechanism's influence on the outcome or the perturbative mechanism's influence.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_population/figures/descriptive/descriptive.png}
-      \caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying population sizes per dataset, across all runs and steps.}
-      \label{fig:results:population:descriptive:descriptive}
-\end{figure}
-
-As with the other experimental groups, the critical difference plot for the various population sizes over all datasets is given in Figure \ref{fig:results:population:descriptive:cd}.
-The plot here shows just exactly how problem-depenent the population size is.
-This is evident from the insignificance between population sizes is you consider their performance over all datasets, yet the descriptive plots from Figure \ref{fig:results:population:descriptive:descriptive} clearly show statistically significant results for each configuration of population size for each dataset.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_population/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying population sizes across all datasets, runs and steps.}
-      \label{fig:results:population:descriptive:cd}
-\end{figure}
-
-Typically, as with the other sections, Figure \ref{fig:results:population:figures:loss} presents some example test loss plots for the bike and housing datasets.
-Here one can clearly see the differences in the runs for the various population size configurations.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_population/figures/test/loss/bike.pdf}
-            \caption{bike}
-            \label{fig:results:population:figures:loss1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_population/figures/test/loss/housing.pdf}
-            \caption{housing}
-            \label{fig:results:population:figures:loss2}
-      \end{subfigure}
-      \caption{\Acs{BHH} Population - example test loss plots for \Acsp{BHH} with varying population sizes}
-      \label{fig:results:population:figures:loss}
-\end{figure}
-
-Alternative to the test loss plots is Figure \ref{fig:results:population:figures:loss} which was carefully selected.
-This figure plots the test accuracy for adult, the dataset for which the \Ac{BHH} performed worst compared to standalone heuristics as was shown in Section \ref{sec:results:standalone}.
-One can see that early stopping measures would've stopped the training process early ($< 5$ epochs), but since there is no early stopping, overfitting takes place in drastic effect.
-Notice how all population size configurations suffer from this problem.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_population/figures/test/accuracy/adult.pdf}
-            \caption{adult}
-            \label{fig:results:population:figures:accuracy1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_population/figures/test/accuracy/car.pdf}
-            \caption{car}
-            \label{fig:results:population:figures:accuracy2}
-      \end{subfigure}
-      \caption{\Acs{BHH} Population - example test accuracy plots for \Acsp{BHH} with varying population sizes}
-      \label{fig:results:population:figures:accuracy}
-\end{figure}
-
-Another suggestion for investigation could be the relationship between entity population size and heuristic pool size.
-As a reminder, the baseline \ac{BHH} has a default population size of 5.
-From the results, we can see that this was also the population size that performed well.
-In fact, it is the only case where population size $<$ heuristic pool size (10).
-There could thus exists some relationship between these parameters, perhaps such that population size $ < $ heuristic pool size.
-Thus certainly warrants for further investigation in the future.
-
-In this section it was found that population size does have a significant impact on the outcomes of the \Ac{BHH} and surprisingly, it was found that a smaller population size is preferred instead of large ones.
-The following section provides a detailed analysis of the credit assignment strategies.
-
-\section{Credit}
-\label{sec:results:credit}
-
-This section provides the empirical results for the experimental group that focuses on studying the effects of different credit assignment strategies on the outcomes of the \Ac{BHH}.
-As a reminder to the reader, the \Ac{BHH} baseline makes use of the \textit{ibest} credit assignment strategy.
-The empirical results are presented in Table \ref{tab:results:credit:metrics} below.
-At first glance, it should be noticed that the selection of the correct credit assignment strategy to use is very problem-dependent.
-
-\begin{table}[htbp]
-      \centering
-      \caption{Empirical results showcasing rank statistics for different \index{credit}credit assignment strategies used by the \acs{BHH} across multiple datasets}
-      \label{tab:results:credit:metrics}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{rccccccccccccccc}
-                  \textbf{step}                       & \multicolumn{1}{l}{\textbf{(All)}}  &                                                                           &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
-                  \cmidrule{1-2}                      &                                     &                                                                           &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
-                                                      & \multicolumn{1}{l}{\textbf{credit}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
-                  \cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{ibest}}  &                                                                           &                 & \multicolumn{1}{l}{\textbf{pbest}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{rbest}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{gbest}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{symmetric}} &                                                                           &                 \\
-                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                      & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                         & \textbf{avg}                                                              & \textbf{std}    \\
-                  \midrule
-                  abalone                             & 930                                 & 3.1677                                                                    & 1.3188          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613}          & 1.4588          & 930                                & 2.9968                                                                    & 1.3993          & 930                                & 2.9667                                                                    & 1.4547          & 930                                    & 3.0075                                                                    & 1.4214          \\
-                  adult                               & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                & 2.6763                                                                             & 1.5019          & 930                                & 2.8065                                                                    & 1.5003          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                    & 3.3538                                                                    & 1.5682          \\
-                  air\_quality                        & 930                                 & 3.1312                                                                    & 1.3472          & 930                                & 3.0376                                                                             & 1.3566          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5914} & 1.4646          & 930                                & 3.1280                                                                    & 1.3358          & 930                                    & 3.1118                                                                    & 1.4871          \\
-                  bank                                & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8591} & 1.3442          & 930                                & 2.9903                                                                             & 1.4320          & 930                                & 2.8882                                                                    & 1.4098          & 930                                & 3.0441                                                                    & 1.4154          & 930                                    & 3.2183                                                                    & 1.4424          \\
-                  bike                                & 930                                 & 3.0527                                                                    & 1.3401          & 930                                & 3.0086                                                                             & 1.3935          & 930                                & 3.0667                                                                    & 1.4825          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3393          & 930                                    & 2.9978                                                                    & 1.5028          \\
-                  car                                 & 930                                 & 3.1151                                                                    & 1.3562          & 930                                & 3.0312                                                                             & 1.4826          & 930                                & 3.2516                                                                    & 1.4024          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6892} & 1.3540          & 930                                    & 2.9129                                                                    & 1.4111          \\
-                  diabetic                            & 930                                 & 2.8914                                                                    & 1.3488          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6269}          & 1.4171          & 930                                & 3.4151                                                                    & 1.3653          & 930                                & 2.8925                                                                    & 1.3620          & 930                                    & 3.1742                                                                    & 1.4487          \\
-                  fish\_toxicity                      & 930                                 & 3.1516                                                                    & 1.4360          & 930                                & 2.9903                                                                             & 1.4521          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.4748          & 930                                & 3.2043                                                                    & 1.2988          & 930                                    & 2.8957                                                                    & 1.3579          \\
-                  forest\_fires                       & 930                                 & 3.0968                                                                    & 1.2771          & 930                                & 3.1806                                                                             & 1.3040          & 930                                & 2.8559                                                                    & 1.3562          & 930                                & 3.1215                                                                    & 1.5018          & 930                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7452} & 1.5627          \\
-                  housing                             & 930                                 & 2.9011                                                                    & 1.4938          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8527}          & 1.3168          & 930                                & 2.9022                                                                    & 1.3974          & 930                                & 3.3108                                                                    & 1.3243          & 930                                    & 3.0333                                                                    & 1.4833          \\
-                  iris                                & 930                                 & 3.1892                                                                    & 1.4281          & 930                                & 3.0839                                                                             & 1.4412          & 930                                & 3.0591                                                                    & 1.3755          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8237} & 1.4085          & 930                                    & 2.8441                                                                    & 1.3844          \\
-                  mushroom                            & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8075} & 1.4594          & 930                                & 3.0183                                                                             & 1.4107          & 930                                & 2.8957                                                                    & 1.3985          & 930                                & 3.0839                                                                    & 1.4178          & 930                                    & 3.1720                                                                    & 1.3813          \\
-                  parkinsons                          & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5645} & 1.4835          & 930                                & 2.8925                                                                             & 1.3429          & 930                                & 3.5065                                                                    & 1.2190          & 930                                & 3.0796                                                                    & 1.3920          & 930                                    & 2.9570                                                                    & 1.4548          \\
-                  student\_performance                & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6624} & 1.3124          & 930                                & 3.0290                                                                             & 1.4067          & 930                                & 3.1892                                                                    & 1.3821          & 930                                & 2.7978                                                                    & 1.4702          & 930                                    & 3.3215                                                                    & 1.3938          \\
-                  wine\_quality                       & 930                                 & 3.1871                                                                    & 1.3080          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366}          & 1.4706          & 930                                & 3.0140                                                                    & 1.3712          & 930                                & 2.9419                                                                    & 1.4115          & 930                                    & 3.2204                                                                    & 1.4300          \\
-                  \midrule
-                  \textbf{overall}                    & \textbf{13950}                      & \textbf{2.9475}                                                           & \textbf{1.3805} & \textbf{13950}                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9277}} & \textbf{1.4222} & \textbf{13950}                     & \textbf{3.0131}                                                           & \textbf{1.4209} & \textbf{13950}                     & \textbf{2.9596}                                                           & \textbf{1.3921} & \textbf{13950}                         & \textbf{3.0644}                                                           & \textbf{1.4594} \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Table \ref{tab:results:credit:anova} provides the ANOVA statistical test results and it can be seen that these credit assignment strategies are indeed statistically signficant from each other.
-Table \ref{tab:results:credit:post_hoc} provides the post hoc Tukey test results.
-
-\begin{table}[htbp]
-      \centering
-      \caption{ANOVA - Rank - BHH Variant: Credit}
-      \label{tab:results:credit:anova}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            %----- Requires booktabs package -----%
-            \begin{tabular}{lrrrrr}
-                  \toprule
-                  Cases            & Sum of Squares & df      & Mean Square & F        & p        \\
-                  \cmidrule[0.4pt]{1-6}
-                  dataset          & $289.361$      & $14$    & $20.669$    & $10.532$ & $<$ .001 \\
-                  credit           & $172.812$      & $4$     & $43.203$    & $22.015$ & $<$ .001 \\
-                  dataset * credit & $2680.102$     & $56$    & $47.859$    & $24.387$ & $<$ .001 \\
-                  Residuals        & $136733.281$   & $69675$ & $1.962$     &          &          \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
-            \end{tabular}
-      }
-\end{table}
-
-\begin{table}[htbp]
-      \centering
-      \caption{Post Hoc Comparisons - BHH Variant: Credit}
-      \label{tab:results:credit:post_hoc}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrrrr}
-                  \toprule
-                  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}               \\
-                  \cline{4-5}
-                  $ $                  & $ $                  & Mean Difference      & Lower                                           & Upper                & SE                   & t                    & p$_{tukey}$ \\
-                  \cmidrule[0.4pt]{1-8}
-                  gbest                & ibest                & $0.012$              & $-0.034$                                        & $0.058$              & $0.017$              & $0.718$              & $0.952$     \\
-                  $ $                  & pbest                & $0.032$              & $-0.014$                                        & $0.078$              & $0.017$              & $1.898$              & $0.319$     \\
-                                       & rbest                & $-0.054$             & $-0.099$                                        & $-0.008$             & $0.017$              & $-3.192$             & $0.012$     \\
-                                       & symmetric            & $-0.105$             & $-0.151$                                        & $-0.059$             & $0.017$              & $-6.248$             & $<$ .001    \\
-                  ibest                & pbest                & $0.020$              & $-0.026$                                        & $0.066$              & $0.017$              & $1.180$              & $0.763$     \\
-                  $ $                  & rbest                & $-0.066$             & $-0.111$                                        & $-0.020$             & $0.017$              & $-3.910$             & $<$ .001    \\
-                                       & symmetric            & $-0.117$             & $-0.163$                                        & $-0.071$             & $0.017$              & $-6.966$             & $<$ .001    \\
-                  pbest                & rbest                & $-0.085$             & $-0.131$                                        & $-0.040$             & $0.017$              & $-5.090$             & $<$ .001    \\
-                  $ $                  & symmetric            & $-0.137$             & $-0.182$                                        & $-0.091$             & $0.017$              & $-8.146$             & $<$ .001    \\
-                  rbest                & symmetric            & $-0.051$             & $-0.097$                                        & $-0.005$             & $0.017$              & $-3.056$             & $0.019$     \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{$ $ * p $<$ .05, ** p < .01, *** p < .001} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{* $$} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{** $$} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
-            \end{tabular}
-      }
-\end{table}
-
-The descriptive plots as presented in Figure \ref{fig:results:credit:descriptive:descriptive} shows how different credit assignment strategies are prefered for different datasets.
-Interestingly, for the forest fires dataset, the preferred credit assignment strategy is statistically the \textit{symmetric} credit assignment strategy.
-As a reminder to the reader, the symmetric credit assignment strategy marks all performance outcomes as successful and thus as a result, no performance bias occurs, rendering the selection mechanism for the \Ac{BHH} useless since priors will never be updated.
-Notice that this does not necessarily make the symmetric credit assignment strategy completely random.
-With the random strategy, a single heuristic is selected and gets a successful count, where with symmetric credit assignment strategy gives a successful count for all selected heuristics.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_credit/figures/descriptive/descriptive.png}
-      \caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying credit assignment strategies per dataset, across all runs and steps.}
-      \label{fig:results:credit:descriptive:descriptive}
-\end{figure}
-
-The critical difference provided in Figure \ref{fig:results:credit:descriptive:cd} supports the statement that the selection of the credit assignment strategy to use is problem-dependent.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_credit/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying credit assignment strategies across all datasets, runs and steps.}
-      \label{fig:results:credit:descriptive:cd}
-\end{figure}
-
-Figure \ref{fig:results:credit:figures:accuracy} provides good example test accuracy plots as for the car and iris datasets and Figure \ref{fig:results:credit:figures:loss} provides example test loss plots as for the abalone and student\_performance datasets.
-Figure \ref{fig:results:credit:figures:loss2} have been included to show the effects of the credit assignment stategies after overfitting has started.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_credit/figures/test/accuracy/car.pdf}
-            \caption{car}
-            \label{fig:results:credit:figures:accuracy1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_credit/figures/test/accuracy/iris.pdf}
-            \caption{iris}
-            \label{fig:results:credit:figures:accuracy2}
-      \end{subfigure}
-      \caption{\Acs{BHH} Credit - example test accuracy plots for varying credit assignment strategies}
-      \label{fig:results:credit:figures:accuracy}
-\end{figure}
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/abalone.pdf}
-            \caption{abalone}
-            \label{fig:results:credit:figures:loss1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/student_performance.pdf}
-            \caption{student\_performance}
-            \label{fig:results:credit:figures:loss2}
-      \end{subfigure}
-      \caption{\Acs{BHH} Credit - example test loss plots for varying credit assignment strategies}
-      \label{fig:results:credit:figures:loss}
-\end{figure}
-
-This section has shown that there is a statistical difference between the outcomes of different credit assignment strategies per dataset.
-However, the choice of credit assignment strategy to use is shown to be problem-dependent.
-
-The following section presents the findings for an experimental group which includes different reselection configurations.
-
-\section{Reselection}
-\label{sec:results:reselection}
-
-This section provides the results for the next experimental group, which focuses on different reselection window sizes.
-As a reminder to the reader, the reselection window is the parameter that controls how often new \index{heuristic}heuristics are selected.
-The baseline \Ac{BHH} makes use of a reselection window size of 10.
-
-Table \ref{tab:results:reselection:metrics} provides the empirical results for this experimental group.
-From these results it can be seen that a larger reselection window size is generally preferred.
-From a statistical point of view this makes sense.
-By lowering the frequency by which reselections happen, the \Ac{BHH} accumulates more information per entity, \index{heuristic}heuristic and credit combination.
-Since the \Ac{BHH} makes use of a probabilistic model, the bigger the sample size the better.
-However, this parameter can not be considered in isolation.
-Consider the replay window size and the reanalysis window size.
-These two parameters put constraints on the window of information that is considered for learning.
-If reselection is large, it does not make sense for the replay size to be low since the \Ac{BHH} will just forget information before reselection has occured.
-Furthermore, as mentioned before, there is inherently a trade-off between exploration and exploitation that is required, even at a \ac{HH} level.
-Admittidly, it is difficult to balance the trade-off between exploration and exploitation.
-Further research could investigate dynamic techniques such as parameter schedules.
-
-Another possibility to consider is that larger reselection window sizes could be required because of noise.
-Perhaps there are too many noisy elements between iterations such that the \Ac{BHH} then requires a more stable configuration to learn sufficiently.
-Much more investigations is required here to confirm if this is the case, however, this was out of the scope for this dissertation.
-However, from a argumentative side it does make sense.
-Every time reselection occurs, state update operations also change due to the perturbative nature of the \Ac{BHH}.
-This could lead to many invalid selections, which in turn leads to bad state updates and ultimately affect the learning process negatively.
-Allowing selected low-level \index{heuristic}heuristic more time to run and learn allows for more consistent state update operations between iterations, catering best for noise introduced through mini-batch iterations and invalid selections.
-Such investigation should pair well with early stopping and the suggestion that was made in \ref{sec:results:standalone} to add a validation step before a state update operations occur.
-This should insure that the update step operations only occur when needed and when valid.
-Nonetheless, an interesting result.
-The remainder of this section simply provides the results in similar fashion to the sections before.
-
-\begin{table}[htbp]
-      \centering
-      \caption{Empirical results showcasing rank statistics for different reselection values used by the \acs{BHH} across multiple datasets}
-      \label{tab:results:reselection:metrics}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{rccccccccccccccc}
-                  \textbf{step}                       & \multicolumn{1}{l}{\textbf{(All)}}       &                                                                           &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
-                  \cmidrule{1-2}                      &                                          &                                                                           &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
-                                                      & \multicolumn{1}{l}{\textbf{reselection}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
-                  \cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}           &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                 &                 & \multicolumn{1}{l}{\textbf{10}} &                 &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                                    &                 \\
-                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                           & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                                       & \textbf{std}    \\
-                  \midrule
-                  abalone                             & 930                                      & 4.3548                                                                    & 0.9760          & 930                            & 2.8473          & 1.2885          & 930                             & 2.7505          & 1.2622          & 930                             & 2.5602                                                                    & 1.2988          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4871}          & 1.3182          \\
-                  adult                               & 930                                      & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7097} & 1.2671          & 930                            & 4.4559          & 1.0052          & 930                             & 3.4398          & 1.0453          & 930                             & 2.7656                                                                    & 0.9837          & 930                             & 2.3065                                                                             & 1.0670          \\
-                  air\_quality                        & 930                                      & 3.7355                                                                    & 1.4046          & 930                            & 3.4075          & 1.3790          & 930                             & 2.9688          & 1.2783          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4237} & 1.2281          & 930                             & 2.4645                                                                             & 1.2906          \\
-                  bank                                & 930                                      & 4.5677                                                                    & 0.7039          & 930                            & 3.6323          & 1.1271          & 930                             & 2.4237          & 1.1333          & 930                             & 2.2462                                                                    & 1.1139          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1301}          & 1.0957          \\
-                  bike                                & 930                                      & 4.7935                                                                    & 0.6124          & 930                            & 3.9204          & 0.6480          & 930                             & 2.5161          & 0.8632          & 930                             & 2.0763                                                                    & 0.9007          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6935}          & 0.8911          \\
-                  car                                 & 930                                      & 4.6409                                                                    & 0.7847          & 930                            & 2.9527          & 1.1581          & 930                             & 2.6548          & 1.1748          & 930                             & 2.5312                                                                    & 1.2440          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2204}          & 1.2169          \\
-                  diabetic                            & 930                                      & 3.0129                                                                    & 1.0478          & 930                            & 4.4624          & 0.8688          & 930                             & 2.7957          & 1.1753          & 930                             & 2.6065                                                                    & 1.4391          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1226}          & 1.2639          \\
-                  fish\_toxicity                      & 930                                      & 3.7484                                                                    & 1.2377          & 930                            & 3.1376          & 1.3174          & 930                             & 3.0344          & 1.4062          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4656} & 1.3039          & 930                             & 2.6140                                                                             & 1.4318          \\
-                  forest\_fires                       & 930                                      & 3.8194                                                                    & 1.4330          & 930                            & 3.2720          & 1.2477          & 930                             & 2.8656          & 1.3464          & 930                             & 2.8194                                                                    & 1.3048          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2237}          & 1.2186          \\
-                  housing                             & 930                                      & 4.1892                                                                    & 1.0993          & 930                            & 3.0172          & 1.2882          & 930                             & 2.5871          & 1.3541          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5312} & 1.2654          & 930                             & 2.6753                                                                             & 1.3399          \\
-                  iris                                & 930                                      & 2.9839                                                                    & 1.4244          & 930                            & 2.9710          & 1.3165          & 930                             & 3.3462          & 1.4182          & 930                             & 3.0140                                                                    & 1.4054          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6849}          & 1.4289          \\
-                  mushroom                            & 930                                      & 4.2065                                                                    & 1.2356          & 930                            & 2.9688          & 1.2992          & 930                             & 2.5860          & 1.2336          & 930                             & 2.7882                                                                    & 1.3397          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4505}          & 1.2259          \\
-                  parkinsons                          & 930                                      & 4.7645                                                                    & 0.7563          & 930                            & 3.1882          & 1.0208          & 930                             & 2.2957          & 1.2089          & 930                             & 2.4968                                                                    & 1.1282          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2548}          & 1.0973          \\
-                  student\_performance                & 930                                      & 3.9710                                                                    & 1.0942          & 930                            & 4.0226          & 1.1196          & 930                             & 2.4774          & 1.2206          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495} & 1.2002          & 930                             & 2.2796                                                                             & 1.1324          \\
-                  wine\_quality                       & 930                                      & 4.0688                                                                    & 1.1220          & 930                            & 2.9204          & 1.2934          & 930                             & 2.9559          & 1.3831          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4032} & 1.3779          & 930                             & 2.6516                                                                             & 1.2796          \\
-                  \midrule
-                  \textbf{overall}                    & \textbf{13950}                           & \textbf{3.9044}                                                           & \textbf{1.3641} & \textbf{13950}                 & \textbf{3.4118} & \textbf{1.2914} & \textbf{13950}                  & \textbf{2.7799} & \textbf{1.2811} & \textbf{13950}                  & \textbf{2.5318}                                                           & \textbf{1.2660} & \textbf{13950}                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.3506}} & \textbf{1.2541} \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Table \ref{tab:results:reselection:anova} provides the ANOVA statistical test results where one can see the statistical significance of the results.
-As with the other sections, Table \ref{tab:results:reselection:post_hoc} provides the post hoc Tukey test results.
-From this table, one can see the statistical significance that exists between all the different reselection window sizes.
-
-\begin{table}[htbp]
-      \centering
-      \caption{ANOVA - Rank - BHH Variant: Reselection}
-      \label{tab:results:reselection:anova}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrr}
-                  \toprule
-                  Cases                 & Sum of Squares & df      & Mean Square & F          & p        \\
-                  \cmidrule[0.4pt]{1-6}
-                  dataset               & $18.065$       & $14$    & $1.290$     & $0.895$    & $0.564$  \\
-                  reselection           & $23391.735$    & $4$     & $5847.934$  & $4055.181$ & $<$ .001 \\
-                  dataset * reselection & $15911.336$    & $56$    & $284.131$   & $197.027$  & $<$ .001 \\
-                  Residuals             & $100477.574$   & $69675$ & $1.442$     &            &          \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
-            \end{tabular}
-      }
-\end{table}
-
-\begin{table}[htbp]
-      \centering
-      \caption{Post Hoc Comparisons - BHH Variant: Reselection}
-      \label{tab:results:reselection:post_hoc}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrrrr}
-                  \toprule
-                  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}               \\
-                  \cline{4-5}
-                  $ $                  & $ $                  & Mean Difference      & Lower                                           & Upper                & SE                   & t                    & p$_{tukey}$ \\
-                  \cmidrule[0.4pt]{1-8}
-                  $1$                  & $5$                  & $0.493$              & $0.453$                                         & $0.532$              & $0.014$              & $34.265$             & $<$ .001    \\
-                  $ $                  & $10$                 & $1.125$              & $1.085$                                         & $1.164$              & $0.014$              & $78.211$             & $<$ .001    \\
-                                       & $15$                 & $1.373$              & $1.333$                                         & $1.412$              & $0.014$              & $95.461$             & $<$ .001    \\
-                                       & $20$                 & $1.554$              & $1.515$                                         & $1.593$              & $0.014$              & $108.064$            & $<$ .001    \\
-                  $5$                  & $10$                 & $0.632$              & $0.593$                                         & $0.671$              & $0.014$              & $43.946$             & $<$ .001    \\
-                  $ $                  & $15$                 & $0.880$              & $0.841$                                         & $0.919$              & $0.014$              & $61.196$             & $<$ .001    \\
-                                       & $20$                 & $1.061$              & $1.022$                                         & $1.100$              & $0.014$              & $73.799$             & $<$ .001    \\
-                  $10$                 & $15$                 & $0.248$              & $0.209$                                         & $0.287$              & $0.014$              & $17.250$             & $<$ .001    \\
-                  $ $                  & $20$                 & $0.429$              & $0.390$                                         & $0.468$              & $0.014$              & $29.853$             & $<$ .001    \\
-                  $15$                 & $20$                 & $0.181$              & $0.142$                                         & $0.220$              & $0.014$              & $12.603$             & $<$ .001    \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
-            \end{tabular}
-      }
-\end{table}
-
-The outcome of this experimental group is best illustrated in Figure \ref{fig:results:reselection:descriptive:descriptive} which provides the reader with descriptive plots of the reselection window size.
-For this experimental group, even though the outcomes are slightly different per dataset, it can be seen that there is a general pattern here that suggests larger selection window sizes across all datasets.
-The only real exception to this is the adult dataset, for which it has already been establish that the \Ac{BHH} overfits drastically.
-There is a slight difference in outcome in the diabetic dataset and that could also be for the same reason.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.png}
-      \caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying reselection values per dataset, across all runs and steps.}
-      \label{fig:results:reselection:descriptive:descriptive}
-\end{figure}
-
-The critical difference plot as presented in \ref{fig:results:reselection:descriptive:cd} visually illustrates the statistical significance between average ranks achieved by the baseline \Ac{BHH} with various reselection windows size values.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_reselection/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying reselection values across all datasets, runs and steps.}
-      \label{fig:results:reselection:descriptive:cd}
-\end{figure}
-
-Finally, Figure \ref{fig:results:reselection:figures:loss} provide example test loss plots for car and housing datasets where one can clearly see the difference in test loss outcomes with the larger reselection windows sizes is seen to perform best.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/car.pdf}
-            \caption{car}
-            \label{fig:results:reselection:figures:loss1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/housing.pdf}
-            \caption{housing}
-            \label{fig:results:reselection:figures:loss2}
-      \end{subfigure}
-      \caption{\Acs{BHH} Selection - example test loss plots for \Acsp{BHH} with varying reselection window sizes}
-      \label{fig:results:reselection:figures:loss}
-\end{figure}
-
-The section has shown that a longer reselection window size is generally preferred.
-However, it has been identified that this component requires more investigation as to why this is the case.
-The next sections are closely related to reselection window sizes as they also influence the intervals between learning/selection.
-The next sections provides the results for the experimental group that focuses on the effects of different replay windows sizes and reanalysis window sizes.
-
-\section{Replay}
-\label{sec:results:replay}
-
-In the previous section it was mentioned how the reselection windows size parameter is closely related to the replay window size and these parameters do have an impact on each other.
-This section provides the empirical results for the experimental group that focuses on the effects of different replay window sizes on the \Ac{BHH}.
-As a reminder to the reader, the replay window is the size of the \Ac{BHH}'s memory buffer i.e.
-how much information is kept in the performance log.
-If this number is low the \Ac{BHH} quickly forgets and if the number is too high it remembers information that is no longer applicable.
-Similar to some of the other parameters discussed in this chapter, it is then clear that this parameter is also subject to a balance between exploration and exploitation.
-The same recommendations that was made for reselection window sizes also account for replay window size.
-
-Table \ref{tab:results:replay:metrics} present the empirical results for this experimental group.
-It can be seen that the best value for the replay window size overall is 5, which is slightly smaller than the \Ac{BHH} baseline, but this value is clearly problem-dependent.
-This is further supported by the results presented in the ANOVA statistical test in Table \ref{tab:results:replay:anova} as well as the post hoc Tykey test presented in Table \ref{tab:results:replay:post_hoc}.
-
-\begin{table}[htbp]
-      \centering
-      \caption{Empirical results showcasing rank statistics for different replay window sizes used by the \acs{BHH} across multiple datasets}
-      \label{tab:results:replay:metrics}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{rccccccccccccccc}
-                  \textbf{step}                       & \multicolumn{1}{l}{\textbf{(All)}}  &                                                                           &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
-                  \cmidrule{1-2}                      &                                     &                                                                           &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
-                                                      & \multicolumn{1}{l}{\textbf{replay}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
-                  \cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}      &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                 &                 \\
-                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                      & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    \\
-                  \midrule
-                  abalone                             & 930                                 & 3.0258                                                                    & 1.3816          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6785}          & 1.4551          & 930                             & 3.1968                                                                    & 1.3460          & 930                             & 3.0903                                                                    & 1.3851          & 930                             & 3.0086          & 1.4503          \\
-                  adult                               & 930                                 & 2.8785                                                                    & 1.3824          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8269}          & 1.3595          & 930                             & 2.9430                                                                    & 1.4804          & 930                             & 3.0538                                                                    & 1.3714          & 930                             & 2.9645          & 1.5686          \\
-                  air\_quality                        & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3851          & 930                            & 3.0151                                                                             & 1.4970          & 930                             & 2.9978                                                                    & 1.4294          & 930                             & 2.9505                                                                    & 1.2966          & 930                             & 3.1624          & 1.4430          \\
-                  bank                                & 930                                 & 2.9484                                                                    & 1.4597          & 930                            & 3.0570                                                                             & 1.4731          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8602} & 1.3439          & 930                             & 3.0172                                                                    & 1.4202          & 930                             & 3.1172          & 1.3592          \\
-                  bike                                & 930                                 & 2.9602                                                                    & 1.2739          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7366}          & 1.3401          & 930                             & 3.1452                                                                    & 1.4478          & 930                             & 2.9226                                                                    & 1.4174          & 930                             & 3.2355          & 1.5274          \\
-                  car                                 & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7054} & 1.3572          & 930                            & 2.8376                                                                             & 1.3898          & 930                             & 3.0763                                                                    & 1.3723          & 930                             & 3.3269                                                                    & 1.4631          & 930                             & 3.0538          & 1.4086          \\
-                  diabetic                            & 930                                 & 3.2473                                                                    & 1.3690          & 930                            & 3.3247                                                                             & 1.4058          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5935} & 1.3719          & 930                             & 2.8075                                                                    & 1.3844          & 930                             & 3.0269          & 1.4113          \\
-                  fish\_toxicity                      & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7269} & 1.4190          & 930                            & 3.0785                                                                             & 1.4896          & 930                             & 3.1774                                                                    & 1.3980          & 930                             & 2.9892                                                                    & 1.3865          & 930                             & 3.0280          & 1.3373          \\
-                  forest\_fires                       & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8054} & 1.4926          & 930                            & 2.9151                                                                             & 1.3812          & 930                             & 2.9914                                                                    & 1.4081          & 930                             & 3.0591                                                                    & 1.4111          & 930                             & 3.2290          & 1.3416          \\
-                  housing                             & 930                                 & 3.1548                                                                    & 1.3007          & 930                            & 2.9774                                                                             & 1.4068          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8548} & 1.4501          & 930                             & 3.0355                                                                    & 1.4898          & 930                             & 2.9774          & 1.4037          \\
-                  iris                                & 930                                 & 3.0720                                                                    & 1.3757          & 930                            & 3.1581                                                                             & 1.4187          & 930                             & 3.2204                                                                    & 1.3919          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6183} & 1.3964          & 930                             & 2.9312          & 1.4102          \\
-                  mushroom                            & 930                                 & 3.0538                                                                    & 1.3243          & 930                            & 3.1430                                                                             & 1.4369          & 930                             & 3.0419                                                                    & 1.4140          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613} & 1.3823          & 930                             & 2.8957          & 1.4966          \\
-                  parkinsons                          & 930                                 & 3.1720                                                                    & 1.3719          & 930                            & 2.8430                                                                             & 1.2437          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6731} & 1.4535          & 930                             & 3.1172                                                                    & 1.4189          & 930                             & 3.1946          & 1.4977          \\
-                  student\_performance                & 930                                 & 3.0398                                                                    & 1.3684          & 930                            & 2.9226                                                                             & 1.4106          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6548} & 1.4028          & 930                             & 3.0935                                                                    & 1.3225          & 930                             & 3.2892          & 1.4874          \\
-                  wine\_quality                       & 930                                 & 3.1742                                                                    & 1.4300          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7323}          & 1.4556          & 930                             & 3.1581                                                                    & 1.4179          & 930                             & 3.0419                                                                    & 1.3565          & 930                             & 2.8935          & 1.3624          \\
-                  \midrule
-                  \textbf{overall}                    & \textbf{13950}                      & \textbf{2.9892}                                                           & \textbf{1.3892} & \textbf{13950}                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9497}} & \textbf{1.4224} & \textbf{13950}                  & \textbf{2.9723}                                                           & \textbf{1.4224} & \textbf{13950}                  & \textbf{2.9990}                                                           & \textbf{1.4021} & \textbf{13950}                  & \textbf{3.0672} & \textbf{1.4400} \\
-            \end{tabular}%
-      }
-\end{table}%
-
-\begin{table}[htbp]
-      \centering
-      \caption{ANOVA - Rank - BHH Variant: Replay}
-      \label{tab:results:replay:anova}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrr}
-                  \toprule
-                  Cases            & Sum of Squares & df      & Mean Square & F        & p        \\
-                  \cmidrule[0.4pt]{1-6}
-                  dataset          & $19.257$       & $14$    & $1.375$     & $0.695$  & $0.781$  \\
-                  replay           & $109.057$      & $4$     & $27.264$    & $13.784$ & $<$ .001 \\
-                  dataset * replay & $1876.507$     & $56$    & $33.509$    & $16.941$ & $<$ .001 \\
-                  Residuals        & $137815.766$   & $69675$ & $1.978$     &          &          \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
-            \end{tabular}
-      }
-\end{table}
-
-\begin{table}[htbp]
-      \centering
-      \caption{Post Hoc Comparisons - BHH Variant: Replay}
-      \label{tab:results:replay:post_hoc}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrrrr}
-                  \toprule
-                  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}               \\
-                  \cline{4-5}
-                  $ $                  & $ $                  & Mean Difference      & Lower                                           & Upper                & SE                   & t                    & p$_{tukey}$ \\
-                  \cmidrule[0.4pt]{1-8}
-                  $1$                  & $5$                  & $0.039$              & $-0.006$                                        & $0.085$              & $0.017$              & $2.346$              & $0.131$     \\
-                  $ $                  & $10$                 & $0.017$              & $-0.029$                                        & $0.063$              & $0.017$              & $1.005$              & $0.853$     \\
-                                       & $15$                 & $-0.010$             & $-0.056$                                        & $0.036$              & $0.017$              & $-0.579$             & $0.978$     \\
-                                       & $20$                 & $-0.078$             & $-0.124$                                        & $-0.032$             & $0.017$              & $-4.627$             & $<$ .001    \\
-                  $5$                  & $10$                 & $-0.023$             & $-0.069$                                        & $0.023$              & $0.017$              & $-1.341$             & $0.666$     \\
-                  $ $                  & $15$                 & $-0.049$             & $-0.095$                                        & $-0.003$             & $0.017$              & $-2.924$             & $0.028$     \\
-                                       & $20$                 & $-0.117$             & $-0.163$                                        & $-0.071$             & $0.017$              & $-6.973$             & $<$ .001    \\
-                  $10$                 & $15$                 & $-0.027$             & $-0.073$                                        & $0.019$              & $0.017$              & $-1.584$             & $0.508$     \\
-                  $ $                  & $20$                 & $-0.095$             & $-0.141$                                        & $-0.049$             & $0.017$              & $-5.632$             & $<$ .001    \\
-                  $15$                 & $20$                 & $-0.068$             & $-0.114$                                        & $-0.022$             & $0.017$              & $-4.048$             & $<$ .001    \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{$ $ * p $<$ .05, ** p < .01, *** p < .001} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{* $$} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{** $$} \\
-            \end{tabular}
-      }
-\end{table}
-
-The descriptive plots presented in Figure \ref{fig:results:replay:descriptive:cd} show the effect of different replay window sizes per dataset.
-The reader is reminded that the baseline \Ac{BHH} has a replay window size of 10.
-This value seems to be the best replay window size for the parkinsons and student performance datasets.
-There is no clear patterns between datasets.
-This makes sense, since each dataset has different training requirements, error landscapes and search spaces.
-In some situations a short memory is required to explore more and in other situations a longer memory is needed.
-An interesting opportunity for further research is to investigate how this value changes at different steps in the training process.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_replay/figures/descriptive/descriptive.png}
-      \caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying replay window sizes per dataset, across all runs and steps.}
-      \label{fig:results:replay:descriptive:descriptive}
-\end{figure}
-
-The critical difference plots show insignificant differences between overall average rank across all datasets.
-This is visual confirmation how the best value for the replay window size is problem dependent.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_replay/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying replay window sizes across all datasets, runs and steps.}
-      \label{fig:results:replay:descriptive:cd}
-\end{figure}
-
-As with the other experimental groups, Figure \ref{fig:results:replay:figures:loss} provide example test loss plots for the car and student performance datasets.
-These two datasets have been carefully selected to showcase a successful case where no overfitting took place(car dataset), while also showing the results of a case where overfitting is clear (student performance dataset).
-This highlight the extent of overfitting that can occur, supporting the idea to use early stop as suggested before.
-Furthermore, the overfit plot is show to illustrate the effects of invalid selections and the effect is has along with noise.
-Consider the large variance that occurs between runs at the point of overfitting in Figure \ref{fig:results:replay:figures:loss} as for the student performance dataset.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/car.pdf}
-            \caption{car}
-            \label{fig:results:replay:figures:loss1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/student_performance.pdf}
-            \caption{student\_performance}
-            \label{fig:results:replay:figures:loss2}
-      \end{subfigure}
-      \caption{\Acs{BHH} Replay - example test loss plots for \Acsp{BHH} with varying replay window sizes}
-      \label{fig:results:replay:figures:loss}
-\end{figure}
-
-In this section it was shown that replay window size configurations are problem-dependent.The replay window size was shown to be related to the reselection window size.
-The next section provides the empirical results for the the next related hyper-parameter, the reanalysis window size.
-
-\section{Reanalysis}
-\label{sec:results:reanalysis}
-
-This section provides the empirical results for the experimental group that focuses on the reanalysis window size and the effect it has on the outcomes of the \Ac{BHH}.
-As a reminder to the reader, the reanalsysis window size is another hyper-parameter which aims to provide a balance between exploration and exploitation by delaying or accelerating the update of beliefs/priors in the \Ac{BHH}.
-This parameter is related to the reselection window size as well as the replay window size.
-The configuration of these three parameters determine how often reselection occurs and if reselection occurs, what data should be considered.
-The reanalysis window size delays or acceleration the addition or removal or information from the performance log, while the replay window size controls how much data is kept in the performance log.
-The baseline \Ac{BHH} uses a reanalysis value that is equal to the reselection value, which is 10.
-
-Table \ref{tab:results:reanalysis:metrics} as before provides the empirical results for this experimental group.
-The results show that in general, the baseline reanalysis window size of 10 yielded the best outcomes overall.
-However, similar to the outcomes of the replay window size, one can clearly see that the best value for the reanalysis window size is also largely problem dependent.
-
-\begin{table}[htbp]
-      \centering
-      \caption{Empirical results showcasing rank statistics for different reanalysis values used by the \acs{BHH} across multiple datasets}
-      \label{tab:results:reanalysis:metrics}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{\begin{tabular}{rccccccccccccccc}
-                  \textbf{step}                       & \multicolumn{1}{l}{\textbf{(All)}}      &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-                  \cmidrule{1-2}                      &                                         &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-                                                      & \multicolumn{1}{l}{\textbf{reanalysis}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-                  \cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}          &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                           &                 \\
-                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                          & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    \\
-                  \midrule
-                  abalone                             & 930                                     & 2.9849                                                                    & 1.3965          & 930                            & 3.0699                                                                    & 1.4423          & 930                             & 3.1710                                                                             & 1.3205          & 930                             & 2.9441                                                                    & 1.4447          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301} & 1.4433          \\
-                  adult                               & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860}          & 0.8523          & 930                             & 2.7914                                                                    & 1.7091          & 930                             & 3.0151                                                                    & 1.7236          \\
-                  air\_quality                        & 930                                     & 2.9613                                                                    & 1.3442          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8387} & 1.4383          & 930                             & 3.2559                                                                             & 1.4024          & 930                             & 3.0538                                                                    & 1.4200          & 930                             & 2.8903                                                                    & 1.4297          \\
-                  bank                                & 930                                     & 3.1161                                                                    & 1.4322          & 930                            & 3.0452                                                                    & 1.3827          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7355}          & 1.3985          & 930                             & 2.9280                                                                    & 1.4028          & 930                             & 3.1753                                                                    & 1.4151          \\
-                  bike                                & 930                                     & 3.1409                                                                    & 1.2581          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.3914          & 930                             & 3.1946                                                                             & 1.3653          & 930                             & 3.0978                                                                    & 1.4978          & 930                             & 2.8086                                                                    & 1.4905          \\
-                  car                                 & 930                                     & 3.1237                                                                    & 1.4229          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7237} & 1.3575          & 930                             & 2.8763                                                                             & 1.2987          & 930                             & 3.1538                                                                    & 1.3846          & 930                             & 3.1226                                                                    & 1.5473          \\
-                  diabetic                            & 930                                     & 3.2452                                                                    & 1.3050          & 930                            & 3.0720                                                                    & 1.3913          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7785}          & 1.4067          & 930                             & 3.0290                                                                    & 1.4249          & 930                             & 2.8753                                                                    & 1.4940          \\
-                  fish\_toxicity                      & 930                                     & 3.1452                                                                    & 1.3620          & 930                            & 3.0032                                                                    & 1.4455          & 930                             & 3.2172                                                                             & 1.3639          & 930                             & 3.1000                                                                    & 1.4088          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5344} & 1.3879          \\
-                  forest\_fires                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8398} & 1.3690          & 930                            & 3.1215                                                                    & 1.4707          & 930                             & 3.0043                                                                             & 1.3181          & 930                             & 2.8860                                                                    & 1.3535          & 930                             & 3.1484                                                                    & 1.5261          \\
-                  housing                             & 930                                     & 3.3129                                                                    & 1.3107          & 930                            & 2.9892                                                                    & 1.3927          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6871}          & 1.4833          & 930                             & 2.6968                                                                    & 1.4965          & 930                             & 3.3140                                                                    & 1.2356          \\
-                  iris                                & 930                                     & 3.1204                                                                    & 1.3010          & 930                            & 3.0968                                                                    & 1.3909          & 930                             & 3.1269                                                                             & 1.4320          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366} & 1.4492          & 930                             & 3.0194                                                                    & 1.4352          \\
-                  mushroom                            & 930                                     & 2.9312                                                                    & 1.3794          & 930                            & 3.1538                                                                    & 1.4031          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8473}          & 1.3836          & 930                             & 3.1215                                                                    & 1.4530          & 930                             & 2.9032                                                                    & 1.4714          \\
-                  parkinsons                          & 930                                     & 2.9688                                                                    & 1.3850          & 930                            & 3.0086                                                                    & 1.3559          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6129}          & 1.4814          & 930                             & 3.1032                                                                    & 1.3804          & 930                             & 3.3065                                                                    & 1.3778          \\
-                  student\_performance                & 930                                     & 2.9409                                                                    & 1.4118          & 930                            & 3.1849                                                                    & 1.3804          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710}          & 1.4097          & 930                             & 3.1258                                                                    & 1.3655          & 930                             & 2.9774                                                                    & 1.4675          \\
-                  wine\_quality                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8032} & 1.4440          & 930                            & 2.9204                                                                    & 1.3042          & 930                             & 3.2022                                                                             & 1.4104          & 930                             & 2.9247                                                                    & 1.3491          & 930                             & 3.1495                                                                    & 1.5171          \\
-                  \midrule
-                  \textbf{overall}                    & \textbf{13950}                          & \textbf{2.9747}                                                           & \textbf{1.3710} & \textbf{13950}                 & \textbf{2.9315}                                                           & \textbf{1.3960} & \textbf{13950}                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.8978}} & \textbf{1.3999} & \textbf{13950}                  & \textbf{2.9728}                                                           & \textbf{1.4464} & \textbf{13950}                  & \textbf{3.0047}                                                           & \textbf{1.4805} \\
-            \end{tabular}%
-      }
-
-\end{table}%
-
-Tables \ref{tab:results:reanalysis:anova} and \ref{tab:results:reanalysis:post_hoc} provide the ANOVA and post hoc Tukey statistical test results respectively.
-From these results one can see the statistical certainty of the results, with the post hoc Tukey test indicating statistical significant differences between individual reanalysis window size configurations.
-
-\begin{table}[htbp]
-      \centering
-      \caption{ANOVA - Rank - BHH Variant: Reanalysis}
-      \label{tab:results:reanalysis:anova}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrr}
-                  \toprule
-                  Cases                & Sum of Squares & df      & Mean Square & F        & p        \\
-                  \cmidrule[0.4pt]{1-6}
-                  dataset              & $1814.177$     & $14$    & $129.584$   & $66.508$ & $<$ .001 \\
-                  reanalysis           & $97.535$       & $4$     & $24.384$    & $12.515$ & $<$ .001 \\
-                  dataset * reanalysis & $2924.722$     & $56$    & $52.227$    & $26.805$ & $<$ .001 \\
-                  Residuals            & $135755.285$   & $69675$ & $1.948$     &          &          \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
-            \end{tabular}
-      }
-\end{table}
-
-\begin{table}[htbp]
-      \centering
-      \caption{Post Hoc Comparisons - BHH Variant: Reanalysis}
-      \label{tab:results:reanalysis:post_hoc}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrrrr}
-                  \toprule
-                  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}               \\
-                  \cline{4-5}
-                  $ $                  & $ $                  & Mean Difference      & Lower                                           & Upper                & SE                   & t                    & p$_{tukey}$ \\
-                  \cmidrule[0.4pt]{1-8}
-                  $1$                  & $5$                  & $0.043$              & $-0.002$                                        & $0.089$              & $0.017$              & $2.586$              & $0.073$     \\
-                  $ $                  & $10$                 & $0.077$              & $0.031$                                         & $0.123$              & $0.017$              & $4.602$              & $<$ .001    \\
-                                       & $15$                 & $0.002$              & $-0.044$                                        & $0.047$              & $0.017$              & $0.112$              & $1.000$     \\
-                                       & $20$                 & $-0.030$             & $-0.076$                                        & $0.016$              & $0.017$              & $-1.793$             & $0.378$     \\
-                  $5$                  & $10$                 & $0.034$              & $-0.012$                                        & $0.079$              & $0.017$              & $2.016$              & $0.258$     \\
-                  $ $                  & $15$                 & $-0.041$             & $-0.087$                                        & $0.004$              & $0.017$              & $-2.475$             & $0.096$     \\
-                                       & $20$                 & $-0.073$             & $-0.119$                                        & $-0.028$             & $0.017$              & $-4.379$             & $<$ .001    \\
-                  $10$                 & $15$                 & $-0.075$             & $-0.121$                                        & $-0.029$             & $0.017$              & $-4.491$             & $<$ .001    \\
-                  $ $                  & $20$                 & $-0.107$             & $-0.152$                                        & $-0.061$             & $0.017$              & $-6.395$             & $<$ .001    \\
-                  $15$                 & $20$                 & $-0.032$             & $-0.077$                                        & $0.014$              & $0.017$              & $-1.904$             & $0.315$     \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
-            \end{tabular}
-      }
-\end{table}
-
-It can be seen from Figure \ref{fig:results:reanalysis:descriptive:descriptive} for all datasets that a pivot point exists in the results at reanalysis window size 10.
-More specifically, it should be stated that a pivot point exists at the configuration points where the reanalsysis window is equal to the reselection window.
-Since the baseline \Ac{BHH} has reselection and reanalys window sizes of 10, this pivot point can be seen at reanalysis window size 10 for all datasets.
-At this point, the performance either reach a minimum or a maximum for almost all the different configurations.
-From this, it can be concluded that the reanalysis window size is also problem dependent and that the relationship between the reselection, replay and reanalysis window sizes is clear.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_reanalysis/figures/descriptive/descriptive.png}
-      \caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying reanalysis window sizes per dataset, across all runs and steps.}
-      \label{fig:results:reanalysis:descriptive:descriptive}
-\end{figure}
-
-The critical difference plots beyween the outcomes of different reanalysis window states on the \Ac{BHH} is given in Figure \ref{fig:results:reanalysis:descriptive:cd} from which we can see there is no statistically significant diference between the outcomes overall across all datasets.
-This further supports the statement that the reanalysis window size is also problem dependent.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_reanalysis/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying reanalysis window sizes across all datasets, runs and steps.}
-      \label{fig:results:reanalysis:descriptive:cd}
-\end{figure}
-
-Finally, Figure \ref{fig:results:reanalysis:figures:loss} provides some example test loss plots for the forest fires and parkinsons datasets.
-These figures showcase how the majority of progress in training and learning is made within the first five epochs.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/forest_fires.pdf}
-            \caption{forest\_fires}
-            \label{fig:results:reanalysis:figures:loss1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/parkinsons.pdf}
-            \caption{parkinsons}
-            \label{fig:results:reanalysis:figures:loss2}
-      \end{subfigure}
-      \caption{\Acs{BHH} Reanalysis - example test loss plots for \Acsp{BHH} with varying reanalysis window sizes}
-      \label{fig:results:reanalysis:figures:loss}
-\end{figure}
-
-This section has shown that the reanalysis window size is largely problem dependent.
-A relationship between the reselection, replay and reanalysis window sizes has been identified and it has been concluded that in general a good configuration of reanalysis window size is one where the reanalysis size is equal to the reselection window size, similar to the baseline \Ac{BHH}.
-Given the relationship between the reselection, replay and reanalysis window sizes, a suggestion can be made to eliminate a hyper-parameter by removing the notion of reanalysis and simply making use of the  reselection window size, since these two parameters work best when they are equal.
-The next section provides the reader with the empirical results for burn in window size.
-
-\section{Burn In}
-\label{sec:results:burn_in}
-
-So far a handful of hyper-parameters have been investigated.
-It should be noted that a large overarching goal of all these parameters is to get a better understanding of their effects on exploration and exploitation and how that impacts the \Ac{BHH}.
-So far the results have all shown to yield statistically significant results, with a lot of parameters being shown to be problem-dependent.
-This section aims to further to the investigation by considering the experimental group that focuses on different burn in window sizes and the effects it has on the \Ac{BHH}.
-As a reminder to the reader, the burn in window size is a hyper-parameter that defines a delay in the \Ac{BHH} before any learning starts happening.
-This means that selection, replay and reanalysis window sizes still affect when and how often learning occurs, but burn in controls when learning starts.
-
-As with the other experimental groups, Table \ref{tab:results:burn_in:metrics} provide the empirical results.
-The empirical results indicate a relationship between the burn in window size and the average rank outcome.
-It can be seen that a lower burn in rate leads to better results.
-Infact, the results show on most occasions that no burn in is the best configuration.
-This outcome makes sense since it has already been established that most of the progress and learning is happening in the initial steps of training.
-If a burn in value is big, it causes the \Ac{BHH} to miss this opportunity to learn.
-Take note, even without learning anything before the burn in, the underlying heuristics are still all good and would still lead to decent results.
-Afterall, this is proof that the proxied state update operations work well
-
-\begin{table}[htbp]
-      \centering
-      \caption{Empirical results showcasing rank statistics for different \index{burn in}burn in values used by the \acs{BHH} across multiple datasets}
-      \label{tab:results:burn_in:metrics}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{rccccccccccccccc}
-                  \textbf{step}                       & \multicolumn{1}{l}{(All)}             &                                                                                    &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
-                  \cmidrule{1-2}                      &                                       &                                                                                    &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
-                                                      & \multicolumn{1}{l}{\textbf{burn\_in}} & \multicolumn{1}{l}{\textbf{results}}                                               &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
-                  \cmidrule{2-3}                      & \textbf{0}                            &                                                                                    &                 & \textbf{5}     &                                                                           &                 & \textbf{10}    &                                                                           &                 & \textbf{15}    &                                                                           &                 & \textbf{20}    &                 &                 \\
-                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                        & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}    & \textbf{std}    \\
-                  \midrule
-                  abalone                             & 930                                   & 2.9151                                                                             & 1.3952          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6935} & 1.3934          & 930            & 2.9172                                                                    & 1.3837          & 930            & 2.8398                                                                    & 1.3524          & 930            & 3.6344          & 1.3574          \\
-                  adult                               & 930                                   & 2.7366                                                                             & 1.4475          & 930            & 2.6430                                                                    & 1.3817          & 930            & 2.9892                                                                    & 1.4111          & 930            & 3.1731                                                                    & 1.4477          & 930            & 3.1355          & 1.4130          \\
-                  air\_quality                        & 930                                   & 2.9097                                                                             & 1.4408          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6817} & 1.4270          & 930            & 2.7699                                                                    & 1.3443          & 930            & 3.3720                                                                    & 1.3137          & 930            & 3.2667          & 1.4119          \\
-                  bike                                & 930                                   & 1.9237                                                                             & 0.9808          & 930            & 2.1806                                                                    & 1.0238          & 930            & 2.9237                                                                    & 1.2739          & 930            & 3.5054                                                                    & 1.1859          & 930            & 4.4667          & 0.8514          \\
-                  car                                 & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3624}          & 1.2315          & 930            & 2.5882                                                                    & 1.4246          & 930            & 3.2978                                                                    & 1.3922          & 930            & 3.3796                                                                    & 1.2711          & 930            & 3.3720          & 1.4009          \\
-                  fish\_toxicity                      & 930                                   & 3.0634                                                                             & 1.4589          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7935} & 1.4021          & 930            & 2.8204                                                                    & 1.5131          & 930            & 3.1022                                                                    & 1.3461          & 930            & 3.2204          & 1.2949          \\
-                  forest\_fires                       & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8161}          & 1.3301          & 930            & 2.8495                                                                    & 1.3830          & 930            & 2.8645                                                                    & 1.4092          & 930            & 3.3774                                                                    & 1.3976          & 930            & 3.0925          & 1.4709          \\
-                  housing                             & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6903}          & 1.3837          & 930            & 2.9516                                                                    & 1.3176          & 930            & 2.9968                                                                    & 1.4425          & 930            & 3.0581                                                                    & 1.3435          & 930            & 3.3032          & 1.5101          \\
-                  iris                                & 930                                   & 2.9473                                                                             & 1.4608          & 930            & 2.9720                                                                    & 1.3675          & 930            & 3.1903                                                                    & 1.4493          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710} & 1.3694          & 930            & 3.1194          & 1.3872          \\
-                  mushroom                            & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2065}          & 1.2486          & 930            & 2.9376                                                                    & 1.2977          & 930            & 3.1613                                                                    & 1.2966          & 930            & 3.1441                                                                    & 1.4015          & 930            & 3.5226          & 1.5006          \\
-                  parkinsons                          & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2796}          & 1.2822          & 930            & 2.8892                                                                    & 1.2474          & 930            & 2.7065                                                                    & 1.3143          & 930            & 3.3968                                                                    & 1.4175          & 930            & 3.7280          & 1.3295          \\
-                  student\_performance                & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1452}          & 1.2052          & 930            & 2.6946                                                                    & 1.4032          & 930            & 3.0968                                                                    & 1.3525          & 930            & 3.4581                                                                    & 1.3539          & 930            & 3.6054          & 1.2312          \\
-                  wine\_quality                       & 930                                   & 2.9699                                                                             & 1.4373          & 930            & 3.0108                                                                    & 1.3041          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6634} & 1.4186          & 930            & 3.1247                                                                    & 1.3980          & 930            & 3.2312          & 1.4471          \\
-                  bank                                & 930                                   & 2.7301                                                                             & 1.3210          & 930            & 2.8194                                                                    & 1.3350          & 930            & 2.8570                                                                    & 1.4848          & 930            & 2.9312                                                                    & 1.3841          & 930            & 3.6624          & 1.3391          \\
-                  \midrule
-                  \textbf{overall}                    & \textbf{13020}                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.6211}} & \textbf{1.3814} & \textbf{13020} & \textbf{2.7647}                                                           & \textbf{1.3553} & \textbf{13020} & \textbf{2.9468}                                                           & \textbf{1.4045} & \textbf{13020} & \textbf{3.1881}                                                           & \textbf{1.3754} & \textbf{13020} & \textbf{3.4543} & \textbf{1.4061} \\
-            \end{tabular}%
-      }
-\end{table}%
-
-As before, Tables \ref{tab:results:burn_in:anova} and \ref{tab:results:burn_in:post_hoc} provide the ANOVA and post hoc Tukey test results respectively.
-These tables show the statistical significance of the results.
-
-\begin{table}[htbp]
-      \centering
-      \caption{ANOVA - Rank - BHH Variant: Burn In}
-      \label{tab:results:burn_in:anova}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrr}
-                  \toprule
-                  Cases              & Sum of Squares & df      & Mean Square & F         & p        \\
-                  \cmidrule[0.4pt]{1-6}
-                  dataset            & $17.977$       & $14$    & $1.284$     & $0.696$   & $0.781$  \\
-                  burn\_in           & $6332.995$     & $4$     & $1583.249$  & $858.000$ & $<$ .001 \\
-                  dataset * burn\_in & $4955.754$     & $56$    & $88.496$    & $47.958$  & $<$ .001 \\
-                  Residuals          & $128569.751$   & $69675$ & $1.845$     &           &          \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
-            \end{tabular}
-      }
-\end{table}
-
-\begin{table}[htbp]
-      \centering
-      \caption{Post Hoc Comparisons - BHH Variant: Burn In}
-      \label{tab:results:burn_in:post_hoc}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}
-      {
-            \begin{tabular}{lrrrrrrr}
-                  \toprule
-                  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}               \\
-                  \cline{4-5}
-                  $ $                  & $ $                  & Mean Difference      & Lower                                           & Upper                & SE                   & t                    & p$_{tukey}$ \\
-                  \cmidrule[0.4pt]{1-8}
-                  $0$                  & $5$                  & $-0.154$             & $-0.198$                                        & $-0.109$             & $0.016$              & $-9.449$             & $<$ .001    \\
-                  $ $                  & $10$                 & $-0.360$             & $-0.404$                                        & $-0.315$             & $0.016$              & $-22.107$            & $<$ .001    \\
-                                       & $15$                 & $-0.584$             & $-0.629$                                        & $-0.540$             & $0.016$              & $-35.923$            & $<$ .001    \\
-                                       & $20$                 & $-0.845$             & $-0.890$                                        & $-0.801$             & $0.016$              & $-51.975$            & $<$ .001    \\
-                  $5$                  & $10$                 & $-0.206$             & $-0.250$                                        & $-0.162$             & $0.016$              & $-12.658$            & $<$ .001    \\
-                  $ $                  & $15$                 & $-0.431$             & $-0.475$                                        & $-0.386$             & $0.016$              & $-26.474$            & $<$ .001    \\
-                                       & $20$                 & $-0.692$             & $-0.736$                                        & $-0.647$             & $0.016$              & $-42.525$            & $<$ .001    \\
-                  $10$                 & $15$                 & $-0.225$             & $-0.269$                                        & $-0.180$             & $0.016$              & $-13.817$            & $<$ .001    \\
-                  $ $                  & $20$                 & $-0.486$             & $-0.530$                                        & $-0.441$             & $0.016$              & $-29.868$            & $<$ .001    \\
-                  $15$                 & $20$                 & $-0.261$             & $-0.305$                                        & $-0.217$             & $0.016$              & $-16.051$            & $<$ .001    \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} P-value and confidence intervals adjusted for comparing a family of 5 estimates (confidence intervals corrected using the tukey method).} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
-            \end{tabular}
-      }
-\end{table}
-
-The best illustration of the relationship between the burn in value and the average rank is best shown in Figure \ref{fig:results:burn_in:descriptive:descriptive} which provides a descriptive plot showing the difference in outcome by burn in window size and dataset.
-From these plots one can see that there is some problem dependence, but in general, there is a pattern that snows that lower burn in window sizes are best.
-There are cases where absolutely no burn in is also not the best, but rather a small, non-zero burn in window size is preferable.
-See the descriptive plots for fish toxicity, abalone, adult and air quality datasets in Figure \ref{fig:results:burn_in:descriptive:descriptive}.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_burn_in/figures/descriptive/descriptive.png}
-      \caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying burn in values per dataset, across all runs and steps.}
-      \label{fig:results:burn_in:descriptive:descriptive}
-\end{figure}
-
-The critical difference plot as presented in Figure \ref{fig:results:burn_in:descriptive:cd} shows the statistical significance between burn in window sizes overall, across all datasets.
-One can clearly see from this plot that little to no burn in is preferred in most of the cases.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_burn_in/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of \Acsp{BHH} with varying burn in values across all datasets, runs and steps.}
-      \label{fig:results:burn_in:descriptive:cd}
-\end{figure}
-
-Figure \ref{fig:results:burn_in:figures:loss} provides the test loss plots for different burn in window sizes for the bike and student performance datasets.
-Once again, an example is given of no overfitting (bike dataset) and another of drastic overfitting (student performance dataset).
-It should be clear from Figure \ref{fig:results:burn_in:figures:loss2} how a larger burn in window size has a greater effect on the overfitting.
-This makes sense, since the \Ac{BHH} only starts to try to learn when most of the progress in \ac{FFNN} training has already been achieved at that point.
-At this point, almost no heuristic, no matter how good, is yielding any positive outcomes, resulting in the \Ac{BHH} learning to make bad selections.
-After this point it has been shown to be difficult for the \Ac{BHH} to recover.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/bike.pdf}
-            \caption{bike}
-            \label{fig:results:burn_in:figures:loss1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/student_performance.pdf}
-            \caption{student\_performance}
-            \label{fig:results:burn_in:figures:loss2}
-      \end{subfigure}
-      \caption{\Acs{BHH} Burn In - example test loss plots for varying burn in values}
-      \label{fig:results:burn_in:figures:loss}
-\end{figure}
-
-This section provided the empirical results for the experimental group that focuses on burn in window sizes.
-It has been show that, in general, a lower burn in window size is preferred.
-The next sections provide investigation into the normalisation and discounted rewards hyper-parameter flags.
-
-\section{Normalise}
-\label{sec:results:normalise}
-
-This section presents the empirical results for the experimental group that focuses on normalisation of pseudo counts and the effects it has on the outcomes of the \Ac{BHH}.
-As a reminder to the reader this normalisation effect aims to promote exploration since it rescales the metric by which priors are updated.
-It could happen that the \Ac{BHH} gets stuck in some local optima and simply picks the same \index{heuristic}heursistic over and over again, resulting in other heuristics not being selected at all.
-This is referred to as \textit{mode-collapse} and is discussed in Chapter \ref{chap:methodology}.
-Normalisation is an attempt to then reset beliefs proportionally back to the initial symmetric starting concentration of 1.
-
-Table \ref{tab:results:normalise:metrics} present the empirical results for this experimental group.
-From the table one can see that in general, no normalisation yields the best results, however, it should be pointed out that this parameter is problem-dependent, yielding better results for the bank, fish toxicity, forest fires, iris and wine quality datasets when normalisation is enabled.
-
-\begin{table}[htbp]
-      \centering
-      \caption{Empirical results showcasing rank statistics for \index{normalisation}normalisation toggled by the \acs{BHH} across multiple datasets}
-      \label{tab:results:normalise:metrics}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{rcccccc}
-                  \textbf{step}                      & \multicolumn{1}{l}{\textbf{(All)}}         &                                                                                    &                 &                                   &                                                                           &                 \\
-                  \cmidrule{1-2}                     &                                            &                                                                                    &                 &                                   &                                                                           &                 \\
-                                                     & \multicolumn{1}{l}{\textbf{normalisation}} & \multicolumn{1}{l}{\textbf{metric}}                                                &                 &                                   &                                                                           &                 \\
-                  \cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{FALSE}}         &                                                                                    &                 & \multicolumn{1}{l}{\textbf{TRUE}} &                                                                           &                 \\
-                  \cmidrule{2-7}    \textbf{dataset} & \textbf{count}                             & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
-                  \midrule
-                  abalone                            & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5002          & 930                               & 1.5065                                                                    & 0.5002          \\
-                  adult                              & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4710}          & 0.4994          & 930                               & 1.4968                                                                    & 0.5003          \\
-                  air\_quality                       & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4892}          & 0.5002          & 930                               & 1.5108                                                                    & 0.5002          \\
-                  bank                               & 930                                        & 1.5484                                                                             & 0.4979          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4516} & 0.4979          \\
-                  bike                               & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4978}          & 0.5003          & 930                               & 1.5022                                                                    & 0.5003          \\
-                  car                                & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4258}          & 0.4947          & 930                               & 1.5742                                                                    & 0.4947          \\
-                  diabetic                           & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4753}          & 0.4997          & 930                               & 1.5247                                                                    & 0.4997          \\
-                  fish\_toxicity                     & 930                                        & 1.5505                                                                             & 0.4977          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4495} & 0.4977          \\
-                  forest\_fires                      & 930                                        & 1.5054                                                                             & 0.5002          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4946} & 0.5002          \\
-                  housing                            & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4720}          & 0.4995          & 930                               & 1.5280                                                                    & 0.4995          \\
-                  iris                               & 930                                        & 1.5645                                                                             & 0.4961          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4355} & 0.4961          \\
-                  mushroom                           & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4323}          & 0.4957          & 930                               & 1.5667                                                                    & 0.4958          \\
-                  parkinsons                         & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4000}          & 0.4902          & 930                               & 1.6000                                                                    & 0.4902          \\
-                  student\_performance               & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3892}          & 0.4878          & 930                               & 1.6108                                                                    & 0.4878          \\
-                  wine\_quality                      & 930                                        & 1.5473                                                                             & 0.4980          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4527} & 0.4980          \\
-                  \midrule
-                  \textbf{overall}                   & \textbf{13950}                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4842}} & \textbf{0.4998} & \textbf{13950}                    & \textbf{1.5136}                                                           & \textbf{0.4998} \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Similar to the other experimental groups, Tables \ref{tab:results:normalise:anova} and \ref{tab:results:normalise:post_hoc} provide the ANOVA and post hoc Tukey statistical test results.
-These tables show that the results are indeed statistical significance.
-
-\begin{table}[htbp]
-      \centering
-      \caption{ANOVA - Rank - BHH Variant: Normalise}
-      \label{tab:results:normalise:anova}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrr}
-                  \toprule
-                  Cases                   & Sum of Squares & df      & Mean Square & F        & p        \\
-                  \cmidrule[0.4pt]{1-6}
-                  dataset                 & $0.450$        & $14$    & $0.032$     & $0.130$  & $1.000$  \\
-                  normalisation           & $6.055$        & $1$     & $6.055$     & $24.490$ & $<$ .001 \\
-                  dataset * normalisation & $78.266$       & $14$    & $5.590$     & $22.613$ & $<$ .001 \\
-                  Residuals               & $6890.195$     & $27870$ & $0.247$     &          &          \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
-            \end{tabular}
-      }
-
-\end{table}
-
-\begin{table}[htbp]
-      \centering
-      \caption{Post Hoc Comparisons - BHH Variant: Normalise}
-      \label{tab:results:normalise:post_hoc}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrrrr}
-                  \toprule
-                  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}               \\
-                  \cline{4-5}
-                  $ $                  & $ $                  & Mean Difference      & Lower                                           & Upper                & SE                   & t                    & p$_{tukey}$ \\
-                  \cmidrule[0.4pt]{1-8}
-                  False                & True                 & $-0.029$             & $-0.041$                                        & $-0.018$             & $0.006$              & $-4.949$             & $<$ .001    \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
-            \end{tabular}
-      }
-\end{table}
-
-From the descriptive plots provided in Figure \ref{fig:results:normalise:descriptive:descriptive}, one can see how normalisation is problem dependent and in many cases, normalisation provides not statistically significant difference.
-This is further evident in Figure \ref{fig:results:normalise:descriptive:cd} which shows no statistically significant difference overall across all datasets.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_normalise/figures/descriptive/descriptive.png}
-      \caption{Descriptive plots between the average ranks of \Acsp{BHH} with normalisation toggled per dataset, across all runs and steps.}
-      \label{fig:results:normalise:descriptive:descriptive}
-\end{figure}
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_normalise/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of \Acsp{BHH} with normalisation toggled across all datasets, runs and steps.}
-      \label{fig:results:normalise:descriptive:cd}
-\end{figure}
-
-As with the other experimental groups, Figure \ref{fig:results:normalise:figures:loss} provides example test loss plots with normalisation enabled and disabled for the bank and housing datasets.
-For these particular plots, there is no real clear distinction between the outcomes of normalisation.
-Since the effect of this parameter is neglibly small, the authors do not deem this parameter as important as the others although it has been shown to provide some statistically significant differences for some datasets.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/bank.pdf}
-            \caption{bank}
-            \label{fig:results:normalise:figures:loss1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/housing.pdf}
-            \caption{housing}
-            \label{fig:results:normalise:figures:loss2}
-      \end{subfigure}
-      \caption{\Acs{BHH} Normalise - example test loss plots for \Acs{BHH} with normalisation toggled}
-      \label{fig:results:normalise:figures:loss}
-\end{figure}
-
-This section provided the empirical results for the experimental group that focuses on the effects of normalisation of pseudo counts on the \Ac{BHH}.
-Although it has been shown to yield interesting results with normalisation not being required in general, while normalisation is preferred for other datasets, the authors conclude that the importance of this parameter is of such nature that it does not have such a significant impact on the \Ac{BHH} as with the other parameters.
-
-The next section considers the empirical results for an experimental group that focus on an alternative strategy to the normalisation approach by providing a discounted rewards flag on the pseudo counts.
-
-\section{Discounted Rewards}
-\label{sec:results:discounted_rewards}
-
-This section presents the empirical results for an experimental group that focuses on the effects of discounted rewards on the \Ac{BHH}.
-As a reminder to the reader, discounted rewards is an strategy that attempts to exponentially decrease the impact of evidence in the performance log for evidence that is further back in history.
-This concept is borrowed from \Ac{RL} (ref???).
-The intent of the discounted rewards approach is to determine if a longer memory can be used where importance is placed on more recent evidence.
-Similar to other parameters discussed so far, this parameter also attempts to provide a mechanism to balance exploration and exploitation.
-
-Table \ref{tab:results:discounted_rewards:metrics} provides the empirical results for this experimental group.
-One can see from the results that the outcomes bear resemblance to the outcomes of the normalisation experimental group.
-It is found that discounted rewards are generally not required while there are some cases that do benefit from it.
-This means that the effect of discounted rewards is also problem-dependent.
-
-\begin{table}[htbp]
-      \centering
-      \caption{Empirical results showcasing rank statistics for \index{discounted rewards}discounted rewards toggled by the \acs{BHH} across multiple datasets}
-      \label{tab:results:discounted_rewards:metrics}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{rcccccc}
-                  step                               & \multicolumn{1}{l}{(All)}          &                                                                                    &                 &                                   &                                                                           &                 \\
-                  \cmidrule{1-2}                     &                                    &                                                                                    &                 &                                   &                                                                           &                 \\
-                                                     & \multicolumn{1}{l}{\textbf{dr}}    & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                   &                                                                           &                 \\
-                  \cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{FALSE}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{TRUE}} &                                                                           &                 \\
-                  \cmidrule{2-7}    \textbf{dataset} & \textbf{count}                     & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
-                  \midrule
-                  abalone                            & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4914}          & 0.5002          & 930                               & 1.5086                                                                    & 0.5002          \\
-                  adult                              & 930                                & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4645} & 0.4990          \\
-                  air\_quality                       & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4613}          & 0.4988          & 930                               & 1.5387                                                                    & 0.4988          \\
-                  bank                               & 930                                & 1.5161                                                                             & 0.5000          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4839} & 0.5000          \\
-                  bike                               & 930                                & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
-                  car                                & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4280}          & 0.4950          & 930                               & 1.5720                                                                    & 0.4950          \\
-                  diabetic                           & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4699}          & 0.4994          & 930                               & 1.5301                                                                    & 0.4994          \\
-                  fish\_toxicity                     & 930                                & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
-                  forest\_fires                      & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4742}          & 0.4996          & 930                               & 1.5258                                                                    & 0.4996          \\
-                  housing                            & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4237}          & 0.4944          & 930                               & 1.5763                                                                    & 0.4944          \\
-                  iris                               & 930                                & 1.5903                                                                             & 0.4920          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4097} & 0.4920          \\
-                  mushroom                           & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3946}          & 0.4890          & 930                               & 1.5806                                                                    & 0.4937          \\
-                  parkinsons                         & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3710}          & 0.4833          & 930                               & 1.6290                                                                    & 0.4833          \\
-                  student\_performance               & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4398}          & 0.4966          & 930                               & 1.5602                                                                    & 0.4966          \\
-                  wine\_quality                      & 930                                & 1.5570                                                                             & 0.4970          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4430} & 0.4970          \\
-                  \midrule
-                  \textbf{overall}                   & \textbf{13950}                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4747}} & \textbf{0.4994} & \textbf{13950}                    & \textbf{1.5214}                                                           & \textbf{0.4996} \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Tables \ref{tab:results:discounted_rewards:anova} and \ref{tab:results:discounted_rewards:post_hoc} provide the ANOVA and post hoc Tukey statistical test results from which it can be seen that the results are statistically significant.
-
-\begin{table}[htbp]
-      \centering
-      \caption{ANOVA - Rank - BHH Variant: Discounted Rewards}
-      \label{tab:results:discounted_rewards:anova}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrr}
-                  \toprule
-                  Cases                         & Sum of Squares & df      & Mean Square & F        & p        \\
-                  \cmidrule[0.4pt]{1-6}
-                  dataset                       & $0.727$        & $14$    & $0.052$     & $0.210$  & $0.999$  \\
-                  discounted\_rewards           & $15.190$       & $1$     & $15.190$    & $61.607$ & $<$ .001 \\
-                  dataset * discounted\_rewards & $87.282$       & $14$    & $6.234$     & $25.285$ & $<$ .001 \\
-                  Residuals                     & $6871.694$     & $27870$ & $0.247$     & $ $      & $ $      \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{6}{p{0.5\linewidth}}{\textit{Note.} Type III Sum of Squares} \\
-            \end{tabular}
-      }
-\end{table}
-
-\begin{table}[htbp]
-      \centering
-      \caption{Post Hoc Comparisons - BHH Variant: Discounted Rewards}
-      \label{tab:results:discounted_rewards:post_hoc}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{lrrrrrrr}
-                  \toprule
-                  \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{95\% CI for Mean Difference} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}               \\
-                  \cline{4-5}
-                  $ $                  & $ $                  & Mean Difference      & Lower                                           & Upper                & SE                   & t                    & p$_{tukey}$ \\
-                  \cmidrule[0.4pt]{1-8}
-                  False                & True                 & $-0.047$             & $-0.058$                                        & $-0.035$             & $0.006$              & $-7.849$             & $<$ .001    \\
-                  \bottomrule
-                  % \addlinespace[1ex]
-                  % \multicolumn{8}{p{0.5\linewidth}}{\textit{Note.} Results are averaged over the levels of: dataset} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{$ $ *** p $<$ .001} \\
-                  % \multicolumn{8}{p{0.5\linewidth}}{*** $$} \\
-            \end{tabular}
-      }
-\end{table}
-
-The descriptive plots as presented in Figure \ref{fig:results:discounted_rewards:descriptive:descriptive} shows how some datasets benefit from discounted rewards while others do not.
-This makes sense, since some datasets might have different training requirements that require long memory of state, the error landscapes could vastly differ or simply contain more noise due to mini-batch training.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/descriptive/descriptive.png}
-      \caption{Descriptive plots between the average ranks of \Acsp{BHH} with discounted rewards toggled per datasets, across all runs and steps.}
-      \label{fig:results:discounted_rewards:descriptive:descriptive}
-\end{figure}
-
-The critical difference plot as presented in Figure \ref{fig:results:discounted_rewards:descriptive:cd} shows that there is not statistically significant difference between enabling and disabling discounted rewards overall, across all datasets, once again suggesting problem-dependence.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of \Acsp{BHH} with discounted rewards toggled across all datasets, runs and steps.}
-      \label{fig:results:discounted_rewards:descriptive:cd}
-\end{figure}
-
-Figure \ref{fig:results:discounted_rewards:figures:loss} provides example plots of test loss when discounted rewards is enabled and disabled for the air quality and fish toxity datasets.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/air_quality.pdf}
-            \caption{air\_quality}
-            \label{fig:results:discounted_rewards:figures:loss1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/fish_toxicity.pdf}
-            \caption{fish\_toxicity}
-            \label{fig:results:discounted_rewards:figures:loss2}
-      \end{subfigure}
-      \caption{\Acs{BHH} Discounted Rewards - example test loss plots for discounted rewards toggled on and off}
-      \label{fig:results:discounted_rewards:figures:loss}
-\end{figure}
-
-This section presented the finding and results for the experimental group that focuses on discounted rewards of evidence in the performance log.
-It has been shown that the outcome of this parameter on the \Ac{BHH} is problem dependent.
-However, the authors deem this parameter to be less important than the other hyper-parameters since their influence is much bigger on the outcome of the \Ac{BHH} than that of discounted rewards.
-
-This concludes the formal experimental groups and empirical aspects to be evaluated. The next section aims to provide more insight into overfitting that occurs with the \Ac{BHH}.
-
-\section{Overfitting}
-\label{sec:results:overfitting}
-
-Throughout this chapter the topic of overfitting was raised on multiple occasions.
-The authors deem it necessary to dedicate a section to specifically discuss and summarise the effects of overfitting on the \Ac{BHH}.
-Take note of the fact that overfitting could be the results of many aspects.
-Overfitting is often the result of noise caused by mini-batch iterations.
-Overfitting could be the result of training and test sets that do not have the same approximate distributions.
-Investigation into the data is required.
-Consider again the experimental group that focused on \index{heuristic}heuristic pool configurations.
-Three different configurations were considered of which the gradient-only \index{heuristic}heuristics pool performed best.
-It should be observed that overfitting occurs much less frequently when the \index{heuristic}heuristics pool contains only the gradient-based low-level \index{heuristic}heuristics.
-Figure !!!!!!!!FIXME!!!!!!!!!!
-below contains the only case where overfitting occurs when the gradient-only heuristic pool is used.
-
-% TOOD: OLD REFERENCE
-% \ref{fig:results:overfitting:figures:gd-overfit}
-
-% TODO: REPLACE THIS
-% \begin{figure}[htbp]
-% 	\centering
-%     \includegraphics[width=\textwidth]{overfitting/student_performance.png}
-%     \caption{Example test loss plot where the \Ac{BHH}-gd is shown to overfit }
-%     \label{fig:results:overfitting:figures:gd-overfit}
-% \end{figure}
-
-One can then conclude that most of the overfitting occurs as a result of the inclusion of the meta-heuristics.
-To some extent this does make sense, since the proxied update step operations for these heuristics do not map as well between meta-heuristics as they do with gradient-based heuristics and thus an update step that occurs when switching from a \acs{PSO} to a \acs{GA} for example might maintain a state of momentum in a certain direction and then as a result of cross-over end up in a totally opposite direction, resulting in the entity vastly overshooting any optima.
-Van Wyk~\cite{ref:vanwyk:2014} did a detailed analysis of overfitting that occurs when training \acp{FFNN} using \acp{PSO}.
-Although the same velocity clamping techniques were used as suggested in Van Wyk's work, they are not guaranteed to avoid overfitting.
-Another technique would be to nullify and reset velocites and momentum, but this could then be detrimental to the other heuristics.
-Since the \Ac{BHH} includes a \acs{PSO} in the heuristic pool, one could expect similar results.
-
-Another aspect to remember is that when overfitting starts, the \Ac{BHH} has no notion of negative progress, since it merely maps the best of the evidence it observes.
-A strategy of picking the ``lesser of two evils''.
-It will then continue to bias toward the best of the heuristics even though the underlying entities have vastly overshot good solutions.
-
-Credit should however be given to the \Ac{BHH} for its ability to learn positively in such a short timespan.
-It has been indicated that the update step for the \Ac{BHH} happens at each mini-batch iteration.
-If a large dataset is presented, that means that the majority of training takes place in a small number of epochs.
-This leaves a very small window for the \Ac{BHH} to actually learn relevant and useful information from the \index{heuristic}heuristic space.
-
-Once overfitting has occurred, it is difficult to undo.
-Therefore the best recommendation is to just use early stopping criteria.
-A suggestion is to simply stop training after $k$-iterations have not yielded better test set generalisation results.
-
-As a last example, Figure \ref{fig:results:overfitting:figures:loss} shows two examples where overfitting is very obviously noticable.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/student_performance.pdf}
-            \caption{student\_performance}
-            \label{fig:results:overfitting:figures:loss1}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/adult.pdf}
-            \caption{adult}
-            \label{fig:results:overfitting:figures:loss2}
-      \end{subfigure}
-      \caption{\Acs{BHH} overfitting behaviour for varying selection window sizes and datasets}
-      \label{fig:results:overfitting:figures:loss}
-\end{figure}
-
-The natural steps that follow on this empirical process is to apply early stopping conditions and plot for every mini-batch iteration.
-This is left for future research.
-The following section briefly talks about the practical implications for the \Ac{BHH}.
-
-\section{Computational Requirements}
-\label{sec:results:computational_requirements}
-
-This section shines some light into the practical applications of the \Ac{BHH}.
-All population-based approach are generally more computationally expensive than individual candidate solution approaches.
-This is because of the number of function evaluations they have to do.
-This is even worse for \acp{HH} since some \acp{HH} require multiple runs, re-evaluations and some have very large memory footprints.
-This notion is further emphasised when training \acp{FFNN}, since training a single \ac{NN} is already computationally expensive, let alone a whole population.
-
-Specifically, the \Ac{BHH} admittedly has quite a high computational overhead and a relatively large memory footprint. Consider the following aspects that attribute to this fact:
-
-\begin{itemize}
-      \item The \Ac{BHH} contains a population of entities.
-      \item Each entity maintains a set of state variable that represent all the underlying states of various low-level \index{heuristic}heuristics in its \index{heuristic}heuristic pool.
-      \item The \Ac{BHH} sometimes have to re-evaluate heuristics. Some heuristics evaluate after the update step while others first step and then evaluate.
-      \item The \Ac{BHH} maintains a global population state.
-      \item The \Ac{BHH} maintains a performance log of variable length that needs to be maintained.
-      \item The \Ac{BHH} has to apply credit assignment strategies multiple times during a single step to ensure that the correct performance state is maintained.
-      \item Thrashing between CPU and GPU execution, such as training the \Acs{FFNN} and then updating the performance log, drastically slows down the training process and calls for rethinking of  implementation.
-\end{itemize}
-
-There are many suggestions that could be made as to how the \ac{BHH} can be improved upon, but those concepts are left for future research.
-It should just be noted since there is a trade-off involved here.
-In Chapter \ref{chap:introduction} it is mentioned that the intent of a \ac{HH} is to eliminate the need for a tedious process of trial and error to find a heuristic that can train a \ac{FFNN} sufficiently.
-The gain in computational time should still be less than the time it would need to follow the trial and error approach for the use of the \Ac{BHH} to be justified.
-
-The next section captures a summary of all of the results.
-
-\section{Summary of Results}
-\label{sec:results:summary}
-
-This section aims to provide a brief summary of the results before conclusions are made in the next chapter. This chapter was split into multiple experimental groups and their findings are given as:
-
-\begin{itemize}
-      \item Section \ref{sec:results:case_study} presented a case study that was done on the behavour of the \Ac{BHH} during training and testing.
-It was shown to be able to train \acp{FFNN} well.
-Detailed analysis was done and it was shown that the \Ac{BHH} does indeed learn and that the general learning is positive towards the overall goals.
-Both the selection mechanism as well as the perturbative component was shown to work well.
-
-      \item Section \ref{sec:results:standalone} presented an empirical test that was executed to compare the \Ac{BHH}'s performance to that of standalone low-level heuristics.
-It was found that the \Ac{BHH} performed reasonably well and is able to generalise well on the test set especially considering overfitting conditions that can be avoided in future work.
-Although the \Ac{BHH} was able to generalise well to the test set, it was not able to perform better than the absolute best low-level heuristic on all occasions.
-It was mentioned here that the \Ac{BHH} has the advantage to bias prior knowledge towards well known heuristics to aid in the learning process.
-
-      \item Section \ref{sec:results:heuristic_pool} presented an empirical test to compare different heuristic pool configurations. It was found that the gradient-only heuristic pool performed best.
-
-      \item Section \ref{sec:results:population} presented an empirical test to evaluate the effect of population size on the \Ac{BHH}.
-It was found that population size is shown to be problem-dependent.
-
-      \item Section \ref{sec:results:credit} presented an empirical test to evaluate credit assignment strategies and it was found that the choice of credit assignment strategy to use is problem-dependent.
-
-      \item Section \ref{sec:results:reselection} presented an empirical test to evaluate different reselection window sizes.
-It was found that the the \Ac{BHH} prefers larger reselection window sizes to give it more time to gather evidence.
-
-      \item Section \ref{sec:results:replay} presented an empirical test to evaluate different replay window sizes and it was found that the choice of replay window size is problem dependent.
-
-      \item Section \ref{sec:results:reanalysis} presented an empirical test to evaluate different reanalysis window sizes and it was also found to be problem dependent.
-
-      \item Section \ref{sec:results:burn_in} presented an empirical test to evaluate different burn in window sizes.
-In general it was found that limited to no burn in was preferred, giving the \Ac{BHH} the opportunity to start learning as soon as possible.
-
-      \item Sections \ref{sec:results:normalise} investigated the impacts of normalising pseudo counts for the concentration parameter updates before they are updated.
-It was found that the choice to enable normalisation or not is problem dependent but generally showed not to be necessary.
-For that reason the authors deem the impact of this parameter to be negligibly small.
-Small enough to consider for removal in future work.
-
-      \item Sections \ref{sec:results:discounted_rewards} investigated the impacts of discounted rewards in the performance logs for events further back in history.
-Similar outcomes to that of the normalisation flag parameter was found.
-In future work, this parameter can be removed.
-\end{itemize}
-
-This chapter presented various angles of analysis to ensure that the \Ac{BHH} is properly analysed and studied.
-As far as was required, all empirical test were analysed for statistical significance and the results of these tests have been provided.
-Various example plots and figures have been provided as visual aid to try better illustrate the outcomes of the empirical process.
-Deeper insight into all of the parameters have been given as far as possible.
-In general, the outcome of the entire empirical process is deemed successful and the \Ac{BHH} shows potential for future research work.
-The following chapter provides a conclusion of the entire dissertation and the work that is presented here.

### 2022-11-10 scripts/analyse.py

@@ -304,10 +304,10 @@ def main():
 	create_cd_plots_per_dataset()
 	create_cd_plots_overall()
 	setup_seaborn()
-	# plot(train=True,accuracy=False)
-	# plot(train=True,accuracy=True)
-	# plot(train=False,accuracy=False)
-	# plot(train=False,accuracy=True)
+	plot(train=True,accuracy=False)
+	plot(train=True,accuracy=True)
+	plot(train=False,accuracy=False)
+	plot(train=False,accuracy=True)
 
 if __name__ == '__main__':
 	main()

### 2022-11-10 scripts/export_case_study.py

@@ -30,6 +30,7 @@ COLUMNS = [
 	'tag',
 	'value'
 ]
+ALLOWED_TAGS = r'(^alpha\[\d\]$|^theta\[\d\]$|^train_accuracy$|^train_loss$|^test_accuracy$|^test_loss$|^p_H\[\d\]$|^p_HgEC\[0\]\[\d\]$|^HgEC\[\d\]$)'
 DATA_DIR = None
 PATH = None
 
@@ -39,7 +40,7 @@ def parse_arguments():
 
 	# Parser
 	parser = argparse.ArgumentParser(
-			description="Export experiments TensorBoard data to csv"
+			description="Export case study TensorBoard data to csv"
 	)
 
 	# Basic Params
@@ -58,7 +59,7 @@ def print_banner():
 
     print("")
     print("====================================================================")
-    print("Export experiments TensorBoard data to csv")
+    print("Export case study TensorBoard data to csv")
     print("====================================================================")
     print("Data Directory: {}".format(DATA_DIR))
     print("====================================================================")
@@ -69,7 +70,9 @@ def my_summary_iterator(path):
 		yield event_pb2.Event.FromString(r)
 
 def export_events(path):
+	global DATA_DIR
 	global COLUMNS
+	global ALLOWED_TAGS
 
 	directory = os.path.abspath(os.path.join(path, os.pardir))
 	filename = os.path.basename(path)
@@ -77,9 +80,8 @@ def export_events(path):
 
 	if os.path.isfile(data_filepath):
 		print("Skipped: {}".format(data_filepath))
-		return
 
-	experiment = str(directory).replace(os.getcwd() + '/data/', '')
+	experiment = str(directory).replace(os.getcwd() + f"/{DATA_DIR}/", '')
 	experiment_parts = experiment.split('/')
 	dataset = experiment_parts[0]
 	heuristic = experiment_parts[1]
@@ -119,31 +121,32 @@ def export_events(path):
 		for data in event.summary.value:
 			id = cuid.cuid()
 			tag = data.tag
-			value = tensor_util.MakeNdarray(data.tensor)
 
-			row = {
-				'id': id,
-				'dataset': dataset,
-				'heuristic': heuristic,
-				'heuristic_pool': heuristic_pool,
-				'population': population,
-				'burn_in': burn_in,
-				'replay': replay,
-				'reselection': reselection,
-				'reanalysis': reanalysis,
[…]

### 2022-11-10 scripts/upload_master_data_case_study.sh

@@ -1,0 +1,9 @@
+#!/usr/bin/env bash
+
+gsutil cp logs/master_case_study.csv gs://masters-363209/master_case_study.csv
+
+bq rm --force=true masters-363209:raw_case_study.raw
+
+bq mk --force=true \
+	--external_table_definition=id:STRING,dataset:STRING,heuristic:STRING,heuristic_pool:STRING,population:INTEGER,burn_in:INTEGER,replay:INTEGER,reselection:INTEGER,reanalysis:INTEGER,normalisation:BOOLEAN,credit:STRING,discounted_rewards:BOOLEAN,run:INTEGER,step:INTEGER,wall_time:FLOAT,tag:STRING,value:FLOAT@CSV=gs://masters-363209/master_case_study.csv \
+	masters-363209:raw_case_study.raw

### 2022-11-11 dissertation/appendix/case-study-additional.tex
🚧 (results): Replotting figures

\chapter{Datasets}
\label{app:case_study_additional}

THIS STILL NEEEDS TO BE ADDED TO CHAPTER 1

Appendices follow exactly the same structure as chapters. They are used to
describe aspects that are not central to the dissertation (for example, an
algorithm that you benchmark against, but do not focus on in the main text, or a
discussion on the sample datasets you test your algorithm on).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS ALPHAS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[1].pdf}
	\caption{The average value of the concentration parameter $\alpha_{1}$ (\acs{Momentum}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:alpha:1}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[2].pdf}
	\caption{The average value of the concentration parameter $\alpha_{2}$ (\acs{NAG}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:alpha:2}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[3].pdf}
	\caption{The average value of the concentration parameter $\alpha_{3}$ (\acs{Adagrad}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:alpha:3}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[4].pdf}
	\caption{The average value of the concentration parameter $\alpha_{4}$ (\acs{RMSProp}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:alpha:4}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[5].pdf}
	\caption{The average value of the concentration parameter $\alpha_{5}$ (\acs{Adadelta}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:alpha:5}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[9].pdf}
	\caption{The average value of the concentration parameter $\alpha_{9}$ (\acs{DE}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:alpha:9}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS THETAS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[1].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{1}$ (\acs{Momentum}), given concentration parameter $\alpha_{1}$, sampled from the probability distribution $P(\theta_{1} \vert \alpha_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:theta:1}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[2].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{2}$ (\acs{NAG}), given concentration parameter $\alpha_{2}$, sampled from the probability distribution $P(\theta_{2} \vert \alpha_{2})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:theta:2}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[3].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{3}$ (\acs{Adagrad}), given concentration parameter $\alpha_{3}$, sampled from the probability distribution $P(\theta_{3} \vert \alpha_{3})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:theta:3}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[4].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{4}$ (\acs{RMSProp}), given concentration parameter $\alpha_{4}$, sampled from the probability distribution $P(\theta_{4} \vert \alpha_{4})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:theta:4}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[5].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{5}$ (\acs{Adadelta}), given concentration parameter $\alpha_{5}$, sampled from the probability distribution $P(\theta_{5} \vert \alpha_{5})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:theta:5}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[9].pdf}
	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{9}$ (\acs{DE}), given concentration parameter $\alpha_{9}$, sampled from the probability distribution $P(\theta_{9} \vert \alpha_{9})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:theta:9}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS P_H (Priors)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[1].pdf}
	\caption{The average unnormalised sampled prior selection probability for heuristic $h_{1}$ (\acs{Momentum}), given the probability of the selection probability, denoted by $\theta_{1}$, sampled from the prior selection probability distribution $P(h_{1} \vert \theta_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_H:1}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[2].pdf}
	\caption{The average unnormalised sampled prior selection probability for heuristic $h_{2}$ (\acs{NAG}), given the probability of the selection probability, denoted by $\theta_{2}$, sampled from the prior selection probability distribution $P(h_{2} \vert \theta_{2})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_H:2}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[3].pdf}
	\caption{The average unnormalised sampled prior selection probability for heuristic $h_{3}$ (\acs{Adagrad}), given the probability of the selection probability, denoted by $\theta_{3}$, sampled from the prior selection probability distribution $P(h_{3} \vert \theta_{3})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_H:3}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[4].pdf}
	\caption{The average unnormalised sampled prior selection probability for heuristic $h_{4}$ (\acs{RMSProp}), given the probability of the selection probability, denoted by $\theta_{4}$, sampled from the prior selection probability distribution $P(h_{4} \vert \theta_{4})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_H:4}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[5].pdf}
	\caption{The average unnormalised sampled prior selection probability for heuristic $h_{5}$ (\acs{Adadelta}), given the probability of the selection probability, denoted by $\theta_{5}$, sampled from the prior selection probability distribution $P(h_{5} \vert \theta_{5})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_H:5}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[9].pdf}
	\caption{The average unnormalised sampled prior selection probability for heuristic $h_{9}$ (\acs{DE}), given the probability of the selection probability, denoted by $\theta_{9}$, sampled from the prior selection probability distribution $P(h_{9} \vert \theta_{9})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_H:9}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PARAMS P_HgEC (Posterior)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][1].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{1}$ (\acs{Momentum}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{1} \vert \theta_{1} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:1}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][2].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{2}$ (\acs{NAG}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{2} \vert \theta_{2} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:2}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][3].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{3}$ (\acs{Adagrad}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{3} \vert \theta_{3} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:3}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][4].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{4}$ (\acs{RMSProp}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{4} \vert \theta_{4} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:4}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][5].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{5}$ (\acs{Adadelta}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{5} \vert \theta_{5} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:5}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][9].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{9}$ (\acs{DE}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{9} \vert \theta_{9} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:9}
\end{figure}

\section{Summary}
\label{app:case_study_additional:summary}

### 2022-11-11 dissertation/chapters/08-results.tex
🚧 (results): Replotting figures

@@
 The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}.
-The methodology presented a number of experiments to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level heuristics.
+The methodology presented a number of experiments to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics.
 The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.
@@
 Discussions are accompanied by figures and plots to help provide visual aid for the discussions.
-All experiments and discussions also provide the outcome of the statistical analysis of the results.
+The output of the statistical analysis that yielded the results presented in the chapter is provided in Appendix~\ref{app:statistical_analysis}.
 The remainder of the chapter is structured as follows.
@@
 
-      \item \textbf{Section \ref{sec:results:bhh_vs_low_level_heuristics}} provides the results of the performance of the \acs{BHH} compared to individual low-level heuristics as it relates to all datasets.
+      \item \textbf{Section \ref{sec:results:bhh_vs_low_level_heuristics}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics as it relates to all datasets.
 Three variants of the \acs{BHH} are included in these results.
-These include the baseline configuration, as well as a configuration that only includes gradient-based heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.
+These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.
 
@@
 
-      \item \textbf{Section \ref{sec:results:bhh_variant_burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.
+      \item \textbf{Section \ref{sec:results:bhh_variant_credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.
 
-      \item \textbf{Section \ref{sec:results:bhh_variant_credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.
+      \item \textbf{Section \ref{sec:results:bhh_variant_reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.
 
@@
 
-      \item \textbf{Section \ref{sec:results:bhh_variant_reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.
+      \item \textbf{Section \ref{sec:results:bhh_variant_burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.
 
@@
 
-      \item \textbf{Section \ref{sec:results:computational_req}} provides a brief discussion on the practical application of the \acs{BHH} to real-world problems.
+      \item \textbf{Section \ref{sec:results:practical_applications}} provides a brief discussion on the practical application of the \acs{BHH} to real-world problems.
 
-      \item \textbf{Section \ref{sec:results:overview}} provides an overview of all the results for all the empirical tests, followed by a brief discussion on the overall performance of the \acs{BHH}.
+      \item \textbf{Section \ref{sec:results:summary}} provides a brief summary of the chapter.
+\end{itemize}
 
-      \item \textbf{Section \ref{sec:results:overview}} provides a brief summary of the chapter.
-\end{itemize}
+\section{Behavioural Case Study}\label{sec:results:case_study}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% METRICS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
+      \caption{The average training loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:train_loss}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
+      \caption{The average test loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:test_loss}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
+      \caption{The average training accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:train_accuracy}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
+      \caption{The average test accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:test_accuracy}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PARAMS ALPHAS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
+      \caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:alpha:0}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
+      \caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:alpha:6}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
+      \caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:alpha:7}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
+      \caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:alpha:8}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PARAMS THETAS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
+      \caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$, sampled from the probability distribution $P(\theta_{0} \vert \alpha_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:theta:0}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
+      \caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$, sampled from the probability distribution $P(\theta_{6} \vert \alpha_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:theta:6}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
+      \caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$, sampled from the probability distribution $P(\theta_{7} \vert \alpha_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:theta:7}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
+      \caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$, sampled from the probability distribution $P(\theta_{8} \vert \alpha_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:theta:8}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PARAMS P_H (Priors)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
+      \caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$, sampled from the prior selection probability distribution $P(h_{0} \vert \theta_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:p_H:0}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
+      \caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$, sampled from the prior selection probability distribution $P(h_{6} \vert \theta_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:p_H:6}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
+      \caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$, sampled from the prior selection probability distribution $P(h_{7} \vert \theta_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:p_H:7}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
+      \caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$, sampled from the prior selection probability distribution $P(h_{8} \vert \theta_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:p_H:8}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PARAMS P_HgEC (Posterior)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
+      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert \theta_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:p_HgEC:0:0}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
+      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert \theta_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:p_HgEC:0:6}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
+      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert \theta_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:p_HgEC:0:7}
+\end{figure}
+
+\begin{figure}[htpb]
+      \centering
+      \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
+      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert \theta_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+      \label{fig:results:case_study:p_HgEC:0:8}
+\end{figure}
+
+\section{BHH vs. Low-Level Heuristics}\label{sec:results:bhh_vs_low_level_heuristics}
+
+% Table generated by Excel2LaTeX from sheet 'results - test - loss'
+\begin{table}[htbp]
+      \centering
+      \caption{Empirical results showcasing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
+      \label{tab:results:standalone:metrics:test_loss}%
+      \par\bigskip
+      \resizebox{\textwidth}{!}{
+            \begin{tabular}{rlccc|c|c|c|c|c|ccccc}
+                  epoch                                                                          & 30                 &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
+                                                                                                 &                    &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
+                                                                                                 &                    & \multicolumn{1}{l}{\textbf{heuristic}}                                         &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
+                  \cmidrule{3-3}\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}    \textbf{dataset} & \textbf{statistic} & \textbf{adagrad}                                                               & \textbf{adam}                                                                  & \textbf{nag}                                                                   & \textbf{bhh\_gd}                                & \textbf{rmsprop}                                                               & \textbf{bhh\_all}                               & \textbf{adadelta}                                                              & \textbf{bhh\_mh}                                & \textbf{ga}                                     & \textbf{sgd}                                    & \textbf{pso}                                    & \textbf{momentum}                               & \textbf{de}                                     \\
+                  \midrule
+                  abalone                                                                        & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .506,  .776,  .486}1.967785                                   & \cellcolor[rgb]{ .494,  .773,  .486}1.965134827                                & \cellcolor[rgb]{ .765,  .851,  .502}2.0156043                                  & \cellcolor[rgb]{ .749,  .847,  .502}2.012517173 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{1.94553315}  & \cellcolor[rgb]{ 1,  .922,  .518}2.058704583    & \cellcolor[rgb]{ .788,  .859,  .502}2.019921077                                & \cellcolor[rgb]{ .996,  .827,  .502}2.29420573  & \cellcolor[rgb]{ .984,  .612,  .459}2.81545685  & \cellcolor[rgb]{ .992,  .773,  .49}2.42804241   & \cellcolor[rgb]{ .98,  .522,  .443}3.038417873  & \cellcolor[rgb]{ .992,  .745,  .486}2.494169393 & \cellcolor[rgb]{ .973,  .412,  .42}3.295858177  \\
+                                                                                                 & std                & 0.031577789                                                                    & 0.034949967                                                                    & 0.034657443                                                                    & 0.068121366                                     & 0.035183664                                                                    & 0.087594488                                     & 0.034405331                                                                    & 0.055085207                                     & 0.055148148                                     & 0.028810924                                     & 0.293755503                                     & 0.029086341                                     & 0.016489872                                     \\
+                  adult                                                                          & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ 1,  .922,  .518}0.346737798                                   & \cellcolor[rgb]{ 1,  .922,  .518}0.38233353                                    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.313320884} & \cellcolor[rgb]{ .788,  .859,  .502}0.335180995 & \cellcolor[rgb]{ .933,  .902,  .514}0.343292783                                & \cellcolor[rgb]{ .973,  .412,  .42}586.2065996  & \cellcolor[rgb]{ .467,  .765,  .486}0.317677033                                & \cellcolor[rgb]{ 1,  .922,  .518}0.363543899    & \cellcolor[rgb]{ 1,  .922,  .518}0.392047161    & \cellcolor[rgb]{ .388,  .745,  .482}0.313329677 & \cellcolor[rgb]{ 1,  .922,  .518}1.217724345    & \cellcolor[rgb]{ .388,  .745,  .482}0.313444396 & \cellcolor[rgb]{ 1,  .922,  .518}0.639695856    \\
+                                                                                                 & std                & 0.003704238                                                                    & 0.018067239                                                                    & 0.000510377                                                                    & 0.043628962                                     & 0.014659665                                                                    & 1261.204704                                     & 0.005277776                                                                    & 0.020803371                                     & 0.020086997                                     & 0.000411017                                     & 0.496591684                                     & 0.0003947                                       & 0.042558869                                     \\
+                  air quality                                                                    & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .651,  .82,  .494}0.256871193                                 & \cellcolor[rgb]{ .827,  .871,  .506}0.260623969                                & \cellcolor[rgb]{ .647,  .82,  .494}0.256829053                                 & \cellcolor[rgb]{ 1,  .922,  .518}0.264177871    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.251334045} & \cellcolor[rgb]{ .996,  .827,  .502}0.272859303 & \cellcolor[rgb]{ .647,  .82,  .494}0.256781683                                 & \cellcolor[rgb]{ .976,  .914,  .514}0.263703859 & \cellcolor[rgb]{ .996,  .792,  .494}0.275862527 & \cellcolor[rgb]{ .988,  .69,  .475}0.285172782  & \cellcolor[rgb]{ .984,  .608,  .459}0.292264593 & \cellcolor[rgb]{ .984,  .604,  .459}0.292851261 & \cellcolor[rgb]{ .973,  .412,  .42}0.309698115  \\
+                                                                                                 & std                & 0.007475522                                                                    & 0.008912099                                                                    & 0.005955119                                                                    & 0.011452365                                     & 0.007814891                                                                    & 0.016310047                                     & 0.00630808                                                                     & 0.007306605                                     & 0.008162884                                     & 0.014769128                                     & 0.022648597                                     & 0.016417541                                     & 0.017044223                                     \\
+                  bank                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .459,  .765,  .486}0.209641222                                & \cellcolor[rgb]{ .4,  .745,  .482}0.206461621                                  & \cellcolor[rgb]{ .588,  .8,  .49}0.2164275                                     & \cellcolor[rgb]{ .588,  .8,  .49}0.21643132     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.205779476} & \cellcolor[rgb]{ 1,  .886,  .514}0.245610465    & \cellcolor[rgb]{ .627,  .812,  .494}0.218599386                                & \cellcolor[rgb]{ .996,  .839,  .502}0.256171151 & \cellcolor[rgb]{ .988,  .686,  .475}0.28813827  & \cellcolor[rgb]{ 1,  .922,  .518}0.238179998    & \cellcolor[rgb]{ .973,  .412,  .42}0.345448185  & \cellcolor[rgb]{ 1,  .922,  .518}0.238550439    & \cellcolor[rgb]{ .976,  .424,  .424}0.343699166 \\
+                                                                                                 & std                & 0.004750498                                                                    & 0.004040969                                                                    & 0.005944898                                                                    & 0.004889433                                     & 0.005654034                                                                    & 0.064531685                                     & 0.003821749                                                                    & 0.010550504                                     & 0.012801143                                     & 0.005568018                                     & 0.033990143                                     & 0.004820977                                     & 0.028120079                                     \\
+                  bike                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.045805387} & \cellcolor[rgb]{ .592,  .804,  .494}0.068179412                                & \cellcolor[rgb]{ .882,  .886,  .51}0.099539486                                 & \cellcolor[rgb]{ .467,  .765,  .486}0.054496914 & \cellcolor[rgb]{ 1,  .922,  .518}0.112259627                                   & \cellcolor[rgb]{ .565,  .796,  .49}0.065136647  & \cellcolor[rgb]{ .588,  .8,  .49}0.06793708                                    & \cellcolor[rgb]{ 1,  .902,  .514}0.11787523     & \cellcolor[rgb]{ .992,  .761,  .486}0.153095534 & \cellcolor[rgb]{ .992,  .733,  .482}0.159868436 & \cellcolor[rgb]{ .992,  .773,  .49}0.150273084  & \cellcolor[rgb]{ .992,  .725,  .482}0.161397393 & \cellcolor[rgb]{ .973,  .412,  .42}0.239867227  \\
+                                                                                                 & std                & 0.001725608                                                                    & 0.068117237                                                                    & 0.001754469                                                                    & 0.005239285                                     & 0.103490928                                                                    & 0.019626763                                     & 0.002076596                                                                    & 0.005954748                                     & 0.005079692                                     & 0.002759                                        & 0.025177188                                     & 0.003354245                                     & 0.039791214                                     \\
+                  car                                                                            & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .729,  .843,  .502}0.202726327                                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.09724452}  & \cellcolor[rgb]{ .867,  .882,  .51}0.245363623                                 & \cellcolor[rgb]{ .62,  .812,  .494}0.16895294   & \cellcolor[rgb]{ .408,  .749,  .482}0.103937737                                & \cellcolor[rgb]{ .58,  .8,  .49}0.15718728      & \cellcolor[rgb]{ 1,  .922,  .518}0.285888989                                   & \cellcolor[rgb]{ .992,  .733,  .482}0.489062582 & \cellcolor[rgb]{ .98,  .502,  .439}0.737354357  & \cellcolor[rgb]{ .98,  .533,  .443}0.703539757  & \cellcolor[rgb]{ .988,  .667,  .471}0.563173207 & \cellcolor[rgb]{ .98,  .506,  .439}0.73217904   & \cellcolor[rgb]{ .973,  .412,  .42}0.833160108  \\
+                                                                                                 & std                & 0.018356416                                                                    & 0.023870777                                                                    & 0.028744869                                                                    & 0.025441117                                     & 0.031133074                                                                    & 0.033710554                                     & 0.027353972                                                                    & 0.076505599                                     & 0.062600847                                     & 0.052091474                                     & 0.157928484                                     & 0.042705727                                     & 0.074182791                                     \\
+                  diabetic                                                                       & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .694,  .831,  .498}0.889537739                                & \cellcolor[rgb]{ 1,  .898,  .514}0.919339482                                   & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.880898965} & \cellcolor[rgb]{ .98,  .914,  .514}0.897587026  & \cellcolor[rgb]{ .918,  .894,  .51}0.895749019                                 & \cellcolor[rgb]{ .973,  .412,  .42}1.298319185  & \cellcolor[rgb]{ .49,  .773,  .486}0.883864405                                 & \cellcolor[rgb]{ 1,  .902,  .518}0.913694494    & \cellcolor[rgb]{ .996,  .843,  .506}0.961291775 & \cellcolor[rgb]{ .976,  .914,  .514}0.897429714 & \cellcolor[rgb]{ .996,  .835,  .502}0.966103049 & \cellcolor[rgb]{ 1,  .922,  .518}0.898038783    & \cellcolor[rgb]{ .988,  .694,  .475}1.077362637 \\
+                                                                                                 & std                & 0.004272255                                                                    & 0.00981794                                                                     & 0.003758597                                                                    & 0.010748722                                     & 0.004045488                                                                    & 0.659754133                                     & 0.004759234                                                                    & 0.008388702                                     & 0.00657199                                      & 0.003551413                                     & 0.016450474                                     & 0.002801135                                     & 0.0391395                                       \\
+                  fish toxicity                                                                  & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .588,  .8,  .49}0.09908239                                    & \cellcolor[rgb]{ .451,  .761,  .482}0.097196901                                & \cellcolor[rgb]{ .831,  .871,  .506}0.10233624                                 & \cellcolor[rgb]{ 1,  .91,  .518}0.105584544     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.096326802} & \cellcolor[rgb]{ 1,  .922,  .518}0.104598099    & \cellcolor[rgb]{ .773,  .855,  .502}0.101567158                                & \cellcolor[rgb]{ .976,  .914,  .514}0.104293618 & \cellcolor[rgb]{ 1,  .863,  .506}0.109342435    & \cellcolor[rgb]{ .976,  .475,  .435}0.139280655 & \cellcolor[rgb]{ 1,  .855,  .506}0.109946059    & \cellcolor[rgb]{ .973,  .412,  .42}0.144088336  & \cellcolor[rgb]{ .992,  .733,  .482}0.119344204 \\
+                                                                                                 & std                & 0.008463336                                                                    & 0.006948088                                                                    & 0.007611236                                                                    & 0.008228438                                     & 0.008021585                                                                    & 0.008136956                                     & 0.008882708                                                                    & 0.00895412                                      & 0.008990894                                     & 0.012326524                                     & 0.012481736                                     & 0.012407706                                     & 0.0130782                                       \\
+                  forest fires                                                                   & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ 1,  .922,  .518}0.064321917                                   & \cellcolor[rgb]{ .557,  .792,  .49}0.052658676                                 & \cellcolor[rgb]{ .851,  .878,  .506}0.05923886                                 & \cellcolor[rgb]{ .824,  .871,  .506}0.058617148 & \cellcolor[rgb]{ 1,  .922,  .518}0.062552555                                   & \cellcolor[rgb]{ 1,  .89,  .514}0.080966845     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.048831474} & \cellcolor[rgb]{ .976,  .914,  .514}0.06209696  & \cellcolor[rgb]{ .553,  .792,  .49}0.05260701   & \cellcolor[rgb]{ .992,  .722,  .482}0.180571383 & \cellcolor[rgb]{ 1,  .914,  .518}0.069210426    & \cellcolor[rgb]{ .992,  .706,  .478}0.188476672 & \cellcolor[rgb]{ .973,  .412,  .42}0.359831599  \\
+                                                                                                 & std                & 0.039911806                                                                    & 0.039243672                                                                    & 0.031685801                                                                    & 0.034163415                                     & 0.039170629                                                                    & 0.069099845                                     & 0.032095867                                                                    & 0.038470671                                     & 0.025957821                                     & 0.008365929                                     & 0.047244856                                     & 0.010081381                                     & 0.089999905                                     \\
+                  housing                                                                        & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .518,  .78,  .486}0.088925893                                 & \cellcolor[rgb]{ .404,  .749,  .482}0.08481865                                 & \cellcolor[rgb]{ .612,  .808,  .494}0.092269667                                & \cellcolor[rgb]{ .69,  .831,  .498}0.095072459  & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.08422333}  & \cellcolor[rgb]{ .663,  .824,  .498}0.094078934 & \cellcolor[rgb]{ 1,  .922,  .518}0.105999965                                   & \cellcolor[rgb]{ 1,  .867,  .51}0.116883814     & \cellcolor[rgb]{ .996,  .812,  .498}0.127851649 & \cellcolor[rgb]{ .984,  .576,  .455}0.173521216 & \cellcolor[rgb]{ .992,  .722,  .482}0.145240159 & \cellcolor[rgb]{ .984,  .588,  .455}0.171302372 & \cellcolor[rgb]{ .973,  .412,  .42}0.205724786  \\
+                                                                                                 & std                & 0.012490666                                                                    & 0.011213172                                                                    & 0.015551947                                                                    & 0.014823695                                     & 0.014924594                                                                    & 0.017302471                                     & 0.018700331                                                                    & 0.019460369                                     & 0.020192262                                     & 0.022837541                                     & 0.029813905                                     & 0.017916976                                     & 0.036445189                                     \\
+                  iris                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .788,  .859,  .502}0.216138929                                & \cellcolor[rgb]{ .514,  .78,  .486}0.120305813                                 & \cellcolor[rgb]{ .416,  .753,  .482}0.084967127                                & \cellcolor[rgb]{ 1,  .855,  .506}0.372908547    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.075287772} & \cellcolor[rgb]{ .859,  .878,  .506}0.241094806 & \cellcolor[rgb]{ .996,  .808,  .498}0.426015649                                & \cellcolor[rgb]{ .686,  .831,  .498}0.180917533 & \cellcolor[rgb]{ 1,  .922,  .518}0.289495446    & \cellcolor[rgb]{ .992,  .773,  .49}0.469415404  & \cellcolor[rgb]{ .973,  .412,  .42}0.896458149  & \cellcolor[rgb]{ .992,  .745,  .486}0.502796506 & \cellcolor[rgb]{ .98,  .494,  .435}0.802733988  \\
+                                                                                                 & std                & 0.059156887                                                                    & 0.097731271                                                                    & 0.041820159                                                                    & 1.119111663                                     & 0.045657899                                                                    & 0.295227964                                     & 0.071608458                                                                    & 0.163729792                                     & 0.117435582                                     & 0.087556703                                     & 0.844445785                                     & 0.072001841                                     & 0.684394699                                     \\
+                  mushroom                                                                       & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .549,  .792,  .49}0.002577835                                 & \cellcolor[rgb]{ .467,  .765,  .486}0.001321295                                & \cellcolor[rgb]{ 1,  .922,  .518}0.009417256                                   & \cellcolor[rgb]{ .439,  .757,  .482}0.000906998 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{8.30695E-05} & \cellcolor[rgb]{ .718,  .839,  .498}0.005152476 & \cellcolor[rgb]{ .655,  .82,  .494}0.00417499                                  & \cellcolor[rgb]{ 1,  .871,  .51}0.077415858     & \cellcolor[rgb]{ .984,  .561,  .451}0.489160105 & \cellcolor[rgb]{ .996,  .796,  .494}0.179705445 & \cellcolor[rgb]{ 1,  .886,  .514}0.061137885    & \cellcolor[rgb]{ .992,  .749,  .486}0.241811308 & \cellcolor[rgb]{ .973,  .412,  .42}0.687017333  \\
+                                                                                                 & std                & 0.000662841                                                                    & 0.004905902                                                                    & 0.002279151                                                                    & 0.001259819                                     & 6.96496E-05                                                                    & 0.012039998                                     & 0.000905097                                                                    & 0.019865901                                     & 0.024593143                                     & 0.009208458                                     & 0.06033175                                      & 0.012790223                                     & 0.01638976                                      \\
+                  parkinsons                                                                     & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .51,  .776,  .486}0.056277858                                 & \cellcolor[rgb]{ .412,  .749,  .482}0.054480758                                & \cellcolor[rgb]{ 1,  .922,  .518}0.065451464                                   & \cellcolor[rgb]{ .639,  .816,  .494}0.058737776 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.053985977} & \cellcolor[rgb]{ .639,  .816,  .494}0.05873821  & \cellcolor[rgb]{ .69,  .831,  .498}0.05967759                                  & \cellcolor[rgb]{ 1,  .918,  .518}0.065774264    & \cellcolor[rgb]{ 1,  .898,  .514}0.066854953    & \cellcolor[rgb]{ .976,  .467,  .431}0.092323864 & \cellcolor[rgb]{ 1,  .894,  .514}0.067066667    & \cellcolor[rgb]{ .973,  .412,  .42}0.095371925  & \cellcolor[rgb]{ .984,  .604,  .459}0.084321583 \\
+                                                                                                 & std                & 0.001432862                                                                    & 0.001998668                                                                    & 0.002301839                                                                    & 0.002859752                                     & 0.001547989                                                                    & 0.002811075                                     & 0.001691389                                                                    & 0.002548177                                     & 0.003281185                                     & 0.008302374                                     & 0.005043049                                     & 0.009431099                                     & 0.008978517                                     \\
+                  student performance                                                            & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.165552792} & \cellcolor[rgb]{ .98,  .522,  .443}0.492891063                                 & \cellcolor[rgb]{ .471,  .769,  .486}0.169715979                                & \cellcolor[rgb]{ 1,  .855,  .506}0.245419875    & \cellcolor[rgb]{ .973,  .412,  .42}0.572439541                                 & \cellcolor[rgb]{ 1,  .871,  .51}0.235942235     & \cellcolor[rgb]{ .49,  .773,  .486}0.170794263                                 & \cellcolor[rgb]{ .969,  .91,  .514}0.194664435  & \cellcolor[rgb]{ 1,  .922,  .518}0.196187948    & \cellcolor[rgb]{ .933,  .902,  .514}0.193041307 & \cellcolor[rgb]{ .984,  .573,  .451}0.456490052 & \cellcolor[rgb]{ .925,  .898,  .51}0.192542094  & \cellcolor[rgb]{ 1,  .918,  .518}0.201390878    \\
+                                                                                                 & std                & 0.011258528                                                                    & 0.105388532                                                                    & 0.010966961                                                                    & 0.133694251                                     & 0.05360667                                                                     & 0.10249181                                      & 0.010377173                                                                    & 0.014024256                                     & 0.009798773                                     & 0.011295962                                     & 0.049033016                                     & 0.011402763                                     & 0.011757846                                     \\
+                  wine quality                                                                   & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+                                                                                                 & avg                & \cellcolor[rgb]{ .631,  .816,  .494}1.06505343                                 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{1.039511785} & \cellcolor[rgb]{ .698,  .831,  .498}1.07178488                                 & \cellcolor[rgb]{ 1,  .922,  .518}1.102805083    & \cellcolor[rgb]{ .502,  .776,  .486}1.051442793                                & \cellcolor[rgb]{ .804,  .863,  .506}1.082728853 & \cellcolor[rgb]{ .788,  .859,  .502}1.080905303                                & \cellcolor[rgb]{ .996,  .839,  .502}1.166586247 & \cellcolor[rgb]{ .992,  .725,  .482}1.251597837 & \cellcolor[rgb]{ .996,  .843,  .502}1.16477848  & \cellcolor[rgb]{ .988,  .659,  .467}1.3045869   & \cellcolor[rgb]{ .996,  .824,  .502}1.17741444  & \cellcolor[rgb]{ .973,  .412,  .42}1.489554557  \\
+                                                                                                 & std                & 0.023560192                                                                    & 0.018361143                                                                    & 0.024922811                                                                    & 0.039250798                                     & 0.020795097                                                                    & 0.026483778                                     & 0.021109916                                                                    & 0.030251195                                     & 0.045716819                                     & 0.022984412                                     & 0.114260845                                     & 0.01919043                                      & 0.092922599                                     \\
+                  \bottomrule
+            \end{tabular}%
+      }
+\end{table}%
+
+% Table generated by Excel2LaTeX from sheet 'results - test - rank'
+\begin{table}[htbp]
+      \centering
+      \caption{Empirical results showcasing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}
+      \label{tab:results:standalone:metrics:rank}%
+      \par\bigskip
+      \resizebox{\textwidth}{!}{
+            \begin{tabular}{rcccc|c|c|c|c|c|ccccc}
+                  epoch                                                                          & \multicolumn{1}{l}{(all)}              &                                                                                    &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
+                                                                                                 &                                        &                                                                                    &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
+                                                                                                 &                                        & \multicolumn{1}{l}{\textbf{heuristic}}                                             &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
+                  \cmidrule{3-3}\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}    \textbf{dataset} & \multicolumn{1}{l}{\textbf{statistic}} & \textbf{adagrad}                                                                   & \textbf{adam}                                                             & \textbf{nag}                                                              & \textbf{bhh\_gd}                               & \textbf{rmsprop}                                                          & \textbf{bhh\_all}                            & \textbf{adadelta}                           & \textbf{bhh\_mh}                               & \textbf{ga}                                    & \textbf{sgd}                                    & \textbf{pso}                                    & \textbf{momentum}                              & \textbf{de}                                    \\
+                  \midrule
+                  abalone                                                                        & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2215}          & 2.3989                                                                    & 4.2731                                                                    & 4.7032                                         & 4.6172                                                                    & 5.9376                                       & 5.3129                                      & 8.1882                                         & 11.1108                                        & 8.6280                                          & 11.2559                                         & 9.8151                                         & 12.5376                                        \\
+                                                                                                 & std                                    & 1.5913                                                                             & 1.8873                                                                    & 1.5419                                                                    & 2.1080                                         & 2.6504                                                                    & 2.3994                                       & 1.4782                                      & 1.1947                                         & 1.1017                                         & 1.0193                                          & 1.8265                                          & 1.1601                                         & 1.3291                                         \\
+                  adult                                                                          & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 5.8978                                                                             & 7.6258                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5140} & 5.3258                                         & 6.6892                                                                    & 12.0194                                      & 2.5258                                      & 7.9409                                         & 9.5860                                         & 3.0065                                          & 11.5344                                         & 3.8699                                         & 10.9462                                        \\
+                                                                                                 & std                                    & 1.6171                                                                             & 2.0293                                                                    & 0.7250                                                                    & 1.8985                                         & 1.8347                                                                    & 2.7430                                       & 1.3543                                      & 1.6391                                         & 1.7015                                         & 1.4999                                          & 2.0122                                          & 1.7090                                         & 1.8965                                         \\
+                  air quality                                                                    & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 3.6409                                                                             & 5.4312                                                                    & 3.8194                                                                    & 5.0817                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.4452} & 6.6860                                       & 5.2441                                      & 6.3570                                         & 7.8204                                         & 10.6613                                         & 9.9151                                          & 11.7559                                        & 11.1419                                        \\
+                                                                                                 & std                                    & 2.2588                                                                             & 2.6198                                                                    & 2.2285                                                                    & 2.7618                                         & 2.5704                                                                    & 3.0613                                       & 3.1622                                      & 2.3031                                         & 2.2652                                         & 1.6061                                          & 2.2882                                          & 1.4730                                         & 2.2361                                         \\
+                  bank                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 2.5495                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.0796} & 4.2871                                                                    & 4.8828                                         & 3.4645                                                                    & 6.2419                                       & 5.6720                                      & 9.7495                                         & 10.9817                                        & 8.2774                                          & 11.8376                                         & 8.4774                                         & 12.4989                                        \\
+                                                                                                 & std                                    & 1.5980                                                                             & 1.5871                                                                    & 1.7325                                                                    & 1.7017                                         & 2.2090                                                                    & 2.1571                                       & 1.2411                                      & 1.0482                                         & 1.2165                                         & 1.0304                                          & 1.4638                                          & 1.0682                                         & 1.2243                                         \\
+                  bike                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7204}          & 3.6925                                                                    & 6.4516                                                                    & 3.8441                                         & 6.2624                                                                    & 4.2151                                       & 5.3602                                      & 7.4108                                         & 9.2269                                         & 10.3355                                         & 9.3086                                          & 10.7086                                        & 12.4634                                        \\
+                                                                                                 & std                                    & 1.3839                                                                             & 4.0038                                                                    & 1.0199                                                                    & 1.3983                                         & 4.5803                                                                    & 1.3611                                       & 1.1555                                      & 1.0076                                         & 1.1835                                         & 1.4193                                          & 1.7615                                          & 1.4233                                         & 1.4648                                         \\
+                  car                                                                            & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 4.7634                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6226} & 6.0785                                                                    & 3.3473                                         & 2.3269                                                                    & 3.5624                                       & 7.7344                                      & 8.8505                                         & 10.7763                                        & 10.2452                                         & 8.3613                                          & 10.9226                                        & 12.4086                                        \\
+                                                                                                 & std                                    & 0.9383                                                                             & 1.4053                                                                    & 0.7991                                                                    & 1.3499                                         & 1.4091                                                                    & 1.3152                                       & 1.7464                                      & 1.4128                                         & 1.4715                                         & 1.4474                                          & 1.6222                                          & 1.3489                                         & 1.4915                                         \\
+                  diabetic                                                                       & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 2.7796                                                                             & 7.1484                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8118} & 5.2269                                         & 6.7376                                                                    & 9.3968                                       & 2.6753                                      & 8.5570                                         & 11.2011                                        & 5.9215                                          & 10.7022                                         & 6.3355                                         & 12.5065                                        \\
+                                                                                                 & std                                    & 1.6587                                                                             & 2.2265                                                                    & 1.4127                                                                    & 2.1860                                         & 2.5767                                                                    & 3.0221                                       & 1.6286                                      & 1.1699                                         & 1.4132                                         & 1.5421                                          & 1.0674                                          & 1.6118                                         & 1.2417                                         \\
+                  fish toxicity                                                                  & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 4.2645                                                                             & 3.6022                                                                    & 5.8914                                                                    & 5.4118                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.5946} & 5.8290                                       & 7.9140                                      & 6.3849                                         & 6.7043                                         & 11.5785                                         & 7.5731                                          & 12.2301                                        & 10.0215                                        \\
+                                                                                                 & std                                    & 2.6142                                                                             & 2.4453                                                                    & 2.6288                                                                    & 2.6649                                         & 2.3292                                                                    & 2.8557                                       & 3.4287                                      & 2.9437                                         & 2.8200                                         & 1.4587                                          & 2.9817                                          & 1.3822                                         & 2.3585                                         \\
+                  forest fires                                                                   & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 5.1559                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{4.2688} & 5.6882                                                                    & 4.6935                                         & 5.0355                                                                    & 5.4839                                       & 6.5161                                      & 5.4591                                         & 7.3667                                         & 10.8129                                         & 6.4796                                          & 11.7065                                        & 12.3333                                        \\
+                                                                                                 & std                                    & 2.9217                                                                             & 2.9841                                                                    & 2.2149                                                                    & 2.7594                                         & 3.1431                                                                    & 3.1070                                       & 3.0823                                      & 2.6680                                         & 2.3704                                         & 1.2070                                          & 3.3539                                          & 1.3250                                         & 1.9228                                         \\
+                  housing                                                                        & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 3.4484                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.3344} & 4.6839                                                                    & 4.4742                                         & 3.6946                                                                    & 4.3763                                       & 7.5903                                      & 7.5441                                         & 7.8839                                         & 11.4075                                         & 9.9409                                          & 11.2731                                        & 11.3484                                        \\
+                                                                                                 & std                                    & 2.0251                                                                             & 1.8193                                                                    & 2.6579                                                                    & 2.3125                                         & 2.1662                                                                    & 2.4377                                       & 2.7475                                      & 1.7363                                         & 2.0991                                         & 1.5278                                          & 2.3166                                          & 1.5059                                         & 2.0965                                         \\
+                  iris                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 6.3946                                                                             & 3.5839                                                                    & 3.5548                                                                    & 4.7473                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6968} & 5.2204                                       & 11.3527                                     & 6.6075                                         & 8.2473                                         & 10.3796                                         & 8.2731                                          & 11.0548                                        & 8.8871                                         \\
+                                                                                                 & std                                    & 1.6000                                                                             & 2.5111                                                                    & 2.1247                                                                    & 2.2749                                         & 1.9121                                                                    & 3.0415                                       & 1.7791                                      & 2.5553                                         & 1.7647                                         & 1.2938                                          & 4.3840                                          & 1.4090                                         & 3.2511                                         \\
+                  mushroom                                                                       & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 4.4656                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1344} & 6.3323                                                                    & 3.4484                                         & 2.4656                                                                    & 3.6688                                       & 6.5538                                      & 9.0452                                         & 11.5731                                        & 9.7527                                          & 7.8720                                          & 10.9785                                        & 12.7097                                        \\
+                                                                                                 & std                                    & 1.0527                                                                             & 1.8831                                                                    & 0.8915                                                                    & 1.6019                                         & 1.3589                                                                    & 2.4687                                       & 1.0711                                      & 1.0931                                         & 1.1927                                         & 1.0828                                          & 0.9197                                          & 1.1075                                         & 1.4781                                         \\
+                  parkinsons                                                                     & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 2.4677                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2333} & 7.5355                                                                    & 4.5720                                         & 3.5656                                                                    & 4.3839                                       & 6.4720                                      & 8.3161                                         & 7.7968                                         & 11.7516                                         & 8.4892                                          & 12.5419                                        & 10.8742                                        \\
+                                                                                                 & std                                    & 1.4969                                                                             & 1.7418                                                                    & 1.4396                                                                    & 1.9337                                         & 2.4919                                                                    & 1.8612                                       & 2.4229                                      & 1.6441                                         & 1.7188                                         & 1.1551                                          & 1.9008                                          & 1.3515                                         & 1.3174                                         \\
+                  student performance                                                            & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5634}          & 11.3978                                                                   & 3.1935                                                                    & 5.6624                                         & 12.4312                                                                   & 5.8634                                       & 3.4194                                      & 6.9333                                         & 7.1032                                         & 6.6366                                          & 11.0624                                         & 6.7011                                         & 8.0323                                         \\
+                                                                                                 & std                                    & 1.9122                                                                             & 2.1780                                                                    & 2.1205                                                                    & 3.5703                                         & 1.3400                                                                    & 3.1588                                       & 2.0060                                      & 2.4398                                         & 1.9887                                         & 2.0233                                          & 1.0674                                          & 2.2423                                         & 1.9346                                         \\
+                  wine quality                                                                   & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+                                                                                                 & avg                                    & 3.2806                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1118} & 4.1505                                                                    & 4.7882                                         & 3.6301                                                                    & 5.1925                                       & 6.0011                                      & 9.5935                                         & 10.3387                                        & 8.6344                                          & 11.1602                                         & 9.5269                                         & 12.5903                                        \\
+                                                                                                 & std                                    & 1.9309                                                                             & 1.6660                                                                    & 1.9156                                                                    & 2.1052                                         & 1.7314                                                                    & 1.9506                                       & 2.4040                                      & 1.4943                                         & 1.6201                                         & 1.1801                                          & 1.7732                                          & 1.3407                                         & 1.3515                                         \\
+                  \midrule
+                  \textbf{overall}                                                               & \textbf{avg}                           & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{3.7076}} & \textbf{4.1777}                                                           & \textbf{4.6177}                                                           & \textbf{4.6806}                                & \textbf{4.7105}                                                           & \textbf{5.8718}                              & \textbf{6.0229}                             & \textbf{7.7958}                                & \textbf{9.1811}                                & \textbf{9.2019}                                 & \textbf{9.5844}                                 & \textbf{9.8599}                                & \textbf{11.4200}                               \\
+                  \textbf{normalised}                                                            & \textbf{rank}                          & \cellcolor[rgb]{ .388,  .745,  .482}\textbf{1}                                     & \cellcolor[rgb]{ .49,  .773,  .486}\textbf{2}                             & \cellcolor[rgb]{ .592,  .804,  .494}\textbf{3}                            & \cellcolor[rgb]{ .694,  .831,  .498}\textbf{4} & \cellcolor[rgb]{ .796,  .863,  .506}\textbf{5}                            & \cellcolor[rgb]{ .898,  .89,  .51}\textbf{6} & \cellcolor[rgb]{ 1,  .922,  .518}\textbf{7} & \cellcolor[rgb]{ .996,  .839,  .502}\textbf{8} & \cellcolor[rgb]{ .992,  .753,  .486}\textbf{9} & \cellcolor[rgb]{ .988,  .667,  .471}\textbf{10} & \cellcolor[rgb]{ .984,  .584,  .455}\textbf{11} & \cellcolor[rgb]{ .98,  .498,  .439}\textbf{12} & \cellcolor[rgb]{ .973,  .412,  .42}\textbf{13} \\
+                  \cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}\end{tabular}%
+      }
+\end{table}%
+
+\begin{sidewaysfigure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
+      \caption{Descriptive plots between the average ranks of all low-level heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \Acs{BHH} per dataset, across all runs and steps.}
+      \label{fig:results:standalone:descriptive:descriptive}
+\end{sidewaysfigure}
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
+      \caption{Critical difference plots between the average ranks of all low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and steps.}
+      \label{fig:results:standalone:descriptive:cd}
+\end{figure}
+
+\section{Heuristic Pool}\label{sec:results:bhh_variant_hp}
+
+\begin{table}[htbp]
+      \centering
+      \caption{Empirical results showcasing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+      \label{tab:results:heuristic_pool:metrics}%
+      \par\bigskip
+      \resizebox{\textwidth}{!}{
+            \begin{tabular}{rccccccccc}
+                  \textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}} &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
+                  \cmidrule{1-2}                      &                                    &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
+                                                      & \multicolumn{1}{l}{\textbf{pool}}  & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                &                                                                                    &                 &                &                 &                 \\
+                  \cmidrule{2-3}                      & \textbf{all}                       &                                                                           &                 & \textbf{gd}    &                                                                                    &                 & \textbf{mh}    &                 &                 \\
+                  \cmidrule{2-10}    \textbf{dataset} & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count} & \textbf{avg}    & \textbf{std}    \\
+                  \midrule
+                  abalone                             & 930                                & 1.7946                                                                    & 0.6411          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3828}          & 0.5604          & 930            & 2.8226          & 0.4198          \\
+                  adult                               & 930                                & 2.8484                                                                    & 0.5058          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.1559}          & 0.4077          & 930            & 1.8989          & 0.4104          \\
+                  air\_quality                        & 930                                & 2.1871                                                                    & 0.8153          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6828}          & 0.7506          & 930            & 2.1301          & 0.7883          \\
+                  bank                                & 930                                & 1.7731                                                                    & 0.5617          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3215}          & 0.4920          & 930            & 2.9054          & 0.3341          \\
+                  bike                                & 930                                & 1.6247                                                                    & 0.5529          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4387}          & 0.5321          & 930            & 2.9366          & 0.2808          \\
+                  car                                 & 930                                & 1.5903                                                                    & 0.5113          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4409}          & 0.5180          & 930            & 2.9688          & 0.2275          \\
+                  diabetic                            & 930                                & 2.4516                                                                    & 0.7353          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.2806}          & 0.5756          & 930            & 2.2677          & 0.5798          \\
+                  fish\_toxicity                      & 930                                & 1.9903                                                                    & 0.8485          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8344}          & 0.7684          & 930            & 2.1753          & 0.7959          \\
+                  forest\_fires                       & 930                                & 2.0667                                                                    & 0.8338          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8269}          & 0.7813          & 930            & 2.1065          & 0.8066          \\
+                  housing                             & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6043} & 0.6869          & 930            & 1.6602                                                                             & 0.6648          & 930            & 2.7355          & 0.5238          \\
+                  iris                                & 930                                & 1.8581                                                                    & 0.8005          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7806}          & 0.7272          & 930            & 2.3613          & 0.7960          \\
+                  mushroom                            & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5204} & 0.5815          & 930            & 1.5484                                                                             & 0.5273          & 930            & 2.9312          & 0.2890          \\
+                  parkinsons                          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5570} & 0.6238          & 930            & 1.6011                                                                             & 0.5915          & 930            & 2.8419          & 0.4448          \\
+                  student\_performance                & 930                                & 1.9828                                                                    & 0.8220          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7903}          & 0.8480          & 930            & 2.2269          & 0.7152          \\
+                  wine\_quality                       & 930                                & 1.5785                                                                    & 0.5498          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5630          & 930            & 2.9280          & 0.2938          \\
+                  \midrule
+                  \textbf{overall}                    & \textbf{13950}                     & \textbf{1.8952}                                                           & \textbf{0.7730} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.5492}} & \textbf{0.6651} & \textbf{13950} & \textbf{2.5491} & \textbf{0.6684} \\
+            \end{tabular}%
+      }
+\end{table}%
+
+\begin{sidewaysfigure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.pdf}
+      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying heuristic pools per dataset, across all runs and steps.}
+      \label{fig:results:heuristic_pool:descriptive:descriptive}
+\end{sidewaysfigure}
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/cd/overall.pdf}
+      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying heuristic pools across all datasets, runs and steps.}
+      \label{fig:results:heuristic_pool:descriptive:cd}
+\end{figure}
+
+\section{Population Size}\label{sec:results:bhh_variant_population}
+
+\begin{table}[htbp]
+      \centering
+      \caption{Empirical results showcasing average rank and statistics for different population size values used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}
+      \label{tab:results:population:metrics}%
+      \par\bigskip
+      \resizebox{\textwidth}{!}{
+            \begin{tabular}{rccccccccccccccc}
+                  \textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}      &                                                                                    &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+                  \cmidrule{1-2}                      &                                         &                                                                                    &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+                                                      & \multicolumn{1}{l}{\textbf{population}} & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+                  \cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{5}}          &                                                                                    &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{15}} &                 &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{25}} &                                                                           &                 \\
+                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                          & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    \\
+                  \midrule
+                  abalone                             & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4387}          & 1.3396          & 930                             & 2.7452                                                                    & 1.3922          & 930                             & 3.0129          & 1.3865          & 930                             & 3.4065                                                                    & 1.3513          & 930                             & 3.3968                                                                    & 1.3514          \\
+                  adult                               & 930                                     & 3.5720                                                                             & 1.4693          & 930                             & 3.2828                                                                    & 1.3751          & 930                             & 2.8108          & 1.3625          & 930                             & 2.6484                                                                    & 1.3222          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3634} & 1.3063          \\
+                  air\_quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7527}          & 1.4283          & 930                             & 2.9258                                                                    & 1.3904          & 930                             & 2.9656          & 1.3791          & 930                             & 3.3140                                                                    & 1.3789          & 930                             & 3.0419                                                                    & 1.4374          \\
+                  bank                                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8129}          & 1.4102          & 930                             & 3.1591                                                                    & 1.4348          & 930                             & 2.9989          & 1.4199          & 930                             & 3.0505                                                                    & 1.4438          & 930                             & 2.9785                                                                    & 1.3414          \\
+                  bike                                & 930                                     & 3.8957                                                                             & 1.3355          & 930                             & 2.8688                                                                    & 1.2850          & 930                             & 2.9645          & 1.3447          & 930                             & 2.7430                                                                    & 1.3762          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5280} & 1.3278          \\
+                  car                                 & 930                                     & 3.1892                                                                             & 1.3915          & 930                             & 3.0409                                                                    & 1.3945          & 930                             & 3.0398          & 1.4523          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8559} & 1.3938          & 930                             & 2.8742                                                                    & 1.4151          \\
+                  diabetic                            & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7978}          & 1.5078          & 930                             & 2.9387                                                                    & 1.4133          & 930                             & 3.2129          & 1.4525          & 930                             & 2.9613                                                                    & 1.3036          & 930                             & 3.0892                                                                    & 1.3534          \\
+                  fish\_toxicity                      & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8151}          & 1.4249          & 930                             & 3.0409                                                                    & 1.4288          & 930                             & 3.0925          & 1.3230          & 930                             & 3.1280                                                                    & 1.4073          & 930                             & 2.9237                                                                    & 1.4634          \\
+                  forest\_fires                       & 930                                     & 3.0172                                                                             & 1.4026          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9215} & 1.3800          & 930                             & 2.9806          & 1.3833          & 930                             & 3.0968                                                                    & 1.4124          & 930                             & 2.9839                                                                    & 1.4879          \\
+                  housing                             & 930                                     & 2.8366                                                                             & 1.4040          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8258} & 1.3802          & 930                             & 2.9753          & 1.4393          & 930                             & 2.9849                                                                    & 1.4111          & 930                             & 3.3774                                                                    & 1.3680          \\
+                  iris                                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301}          & 1.3038          & 930                             & 2.8731                                                                    & 1.3970          & 930                             & 3.0505          & 1.4129          & 930                             & 3.1860                                                                    & 1.4251          & 930                             & 3.0602                                                                    & 1.4987          \\
+                  mushroom                            & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7989}          & 1.2052          & 930                             & 2.9441                                                                    & 1.3250          & 930                             & 3.0462          & 1.4521          & 930                             & 3.1366                                                                    & 1.4940          & 930                             & 3.0538                                                                    & 1.5664          \\
+                  parkinsons                          & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6645}          & 1.4411          & 930                             & 3.1065                                                                    & 1.3272          & 930                             & 3.0247          & 1.4265          & 930                             & 3.0495                                                                    & 1.4420          & 930                             & 3.1548                                                                    & 1.3810          \\
+                  student\_performance                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6376}          & 1.4357          & 930                             & 2.8645                                                                    & 1.4108          & 930                             & 3.1548          & 1.4042          & 930                             & 3.2387                                                                    & 1.3970          & 930                             & 3.1043                                                                    & 1.3395          \\
+                  wine\_quality                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5505}          & 1.3165          & 930                             & 2.7817                                                                    & 1.4152          & 930                             & 3.1581          & 1.3841          & 930                             & 3.1806                                                                    & 1.3941          & 930                             & 3.3290                                                                    & 1.4140          \\
+                  \midrule
+                  \textbf{overall}                    & \textbf{13950}                          & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9073}} & \textbf{1.4377} & \textbf{13950}                  & \textbf{2.9546}                                                           & \textbf{1.3904} & \textbf{13950}                  & \textbf{3.0325} & \textbf{1.4045} & \textbf{13950}                  & \textbf{3.0654}                                                           & \textbf{1.4108} & \textbf{13950}                  & \textbf{3.0173}                                                           & \textbf{1.4306} \\
+            \end{tabular}%
+      }
+\end{table}%
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_population/figures/descriptive/descriptive.pdf}
+      \caption{Descriptive plots between the average ranks of \acs{BHH} with varying population sizes per dataset, across all runs and epochs.}
+      \label{fig:results:population:descriptive:descriptive}
+\end{figure}
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_population/figures/cd/overall.pdf}
+      \caption{Critical Difference plots between the average ranks of \acs{BHH} with varying population sizes across all datasets, runs and epochs.}
+      \label{fig:results:population:descriptive:cd}
+\end{figure}
+
+\section{Credit Assignment Strategy}\label{sec:results:bhh_variant_credit}
+
+\begin{table}[htbp]
+      \centering
+      \caption{Empirical results showcasing average rank and statistics for different \index{credit}credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+      \label{tab:results:credit:metrics}%
+      \par\bigskip
+      \resizebox{\textwidth}{!}{
+            \begin{tabular}{rccccccccccccccc}
+                  \textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}  &                                                                           &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
+                  \cmidrule{1-2}                      &                                     &                                                                           &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
+                                                      & \multicolumn{1}{l}{\textbf{credit}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
+                  \cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{ibest}}  &                                                                           &                 & \multicolumn{1}{l}{\textbf{pbest}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{rbest}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{gbest}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{symmetric}} &                                                                           &                 \\
+                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                      & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                         & \textbf{avg}                                                              & \textbf{std}    \\
+                  \midrule
+                  abalone                             & 930                                 & 3.1677                                                                    & 1.3188          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613}          & 1.4588          & 930                                & 2.9968                                                                    & 1.3993          & 930                                & 2.9667                                                                    & 1.4547          & 930                                    & 3.0075                                                                    & 1.4214          \\
+                  adult                               & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                & 2.6763                                                                             & 1.5019          & 930                                & 2.8065                                                                    & 1.5003          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                    & 3.3538                                                                    & 1.5682          \\
+                  air\_quality                        & 930                                 & 3.1312                                                                    & 1.3472          & 930                                & 3.0376                                                                             & 1.3566          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5914} & 1.4646          & 930                                & 3.1280                                                                    & 1.3358          & 930                                    & 3.1118                                                                    & 1.4871          \\
+                  bank                                & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8591} & 1.3442          & 930                                & 2.9903                                                                             & 1.4320          & 930                                & 2.8882                                                                    & 1.4098          & 930                                & 3.0441                                                                    & 1.4154          & 930                                    & 3.2183                                                                    & 1.4424          \\
+                  bike                                & 930                                 & 3.0527                                                                    & 1.3401          & 930                                & 3.0086                                                                             & 1.3935          & 930                                & 3.0667                                                                    & 1.4825          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3393          & 930                                    & 2.9978                                                                    & 1.5028          \\
+                  car                                 & 930                                 & 3.1151                                                                    & 1.3562          & 930                                & 3.0312                                                                             & 1.4826          & 930                                & 3.2516                                                                    & 1.4024          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6892} & 1.3540          & 930                                    & 2.9129                                                                    & 1.4111          \\
+                  diabetic                            & 930                                 & 2.8914                                                                    & 1.3488          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6269}          & 1.4171          & 930                                & 3.4151                                                                    & 1.3653          & 930                                & 2.8925                                                                    & 1.3620          & 930                                    & 3.1742                                                                    & 1.4487          \\
+                  fish\_toxicity                      & 930                                 & 3.1516                                                                    & 1.4360          & 930                                & 2.9903                                                                             & 1.4521          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.4748          & 930                                & 3.2043                                                                    & 1.2988          & 930                                    & 2.8957                                                                    & 1.3579          \\
+                  forest\_fires                       & 930                                 & 3.0968                                                                    & 1.2771          & 930                                & 3.1806                                                                             & 1.3040          & 930                                & 2.8559                                                                    & 1.3562          & 930                                & 3.1215                                                                    & 1.5018          & 930                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7452} & 1.5627          \\
+                  housing                             & 930                                 & 2.9011                                                                    & 1.4938          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8527}          & 1.3168          & 930                                & 2.9022                                                                    & 1.3974          & 930                                & 3.3108                                                                    & 1.3243          & 930                                    & 3.0333                                                                    & 1.4833          \\
+                  iris                                & 930                                 & 3.1892                                                                    & 1.4281          & 930                                & 3.0839                                                                             & 1.4412          & 930                                & 3.0591                                                                    & 1.3755          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8237} & 1.4085          & 930                                    & 2.8441                                                                    & 1.3844          \\
+                  mushroom                            & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8075} & 1.4594          & 930                                & 3.0183                                                                             & 1.4107          & 930                                & 2.8957                                                                    & 1.3985          & 930                                & 3.0839                                                                    & 1.4178          & 930                                    & 3.1720                                                                    & 1.3813          \\
+                  parkinsons                          & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5645} & 1.4835          & 930                                & 2.8925                                                                             & 1.3429          & 930                                & 3.5065                                                                    & 1.2190          & 930                                & 3.0796                                                                    & 1.3920          & 930                                    & 2.9570                                                                    & 1.4548          \\
+                  student\_performance                & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6624} & 1.3124          & 930                                & 3.0290                                                                             & 1.4067          & 930                                & 3.1892                                                                    & 1.3821          & 930                                & 2.7978                                                                    & 1.4702          & 930                                    & 3.3215                                                                    & 1.3938          \\
+                  wine\_quality                       & 930                                 & 3.1871                                                                    & 1.3080          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366}          & 1.4706          & 930                                & 3.0140                                                                    & 1.3712          & 930                                & 2.9419                                                                    & 1.4115          & 930                                    & 3.2204                                                                    & 1.4300          \\
+                  \midrule
+                  \textbf{overall}                    & \textbf{13950}                      & \textbf{2.9475}                                                           & \textbf{1.3805} & \textbf{13950}                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9277}} & \textbf{1.4222} & \textbf{13950}                     & \textbf{3.0131}                                                           & \textbf{1.4209} & \textbf{13950}                     & \textbf{2.9596}                                                           & \textbf{1.3921} & \textbf{13950}                         & \textbf{3.0644}                                                           & \textbf{1.4594} \\
+            \end{tabular}%
+      }
+\end{table}%
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_credit/figures/descriptive/descriptive.pdf}
+      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying credit assignment strategies per dataset, across all runs and epochs.}
+      \label{fig:results:credit:descriptive:descriptive}
+\end{figure}
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_credit/figures/cd/overall.pdf}
+      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying credit assignment strategies across all datasets, runs and epochs.}
+      \label{fig:results:credit:descriptive:cd}
+\end{figure}
+
+\section{Reselection Interval}\label{sec:results:bhh_variant_reselection}
+
+\begin{table}[htbp]
+      \centering
+      \caption{Empirical results showcasing average rank and statistics for different reselection values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+      \label{tab:results:reselection:metrics}%
+      \par\bigskip
+      \resizebox{\textwidth}{!}{
+            \begin{tabular}{rccccccccccccccc}
+                  \textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}       &                                                                           &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
+                  \cmidrule{1-2}                      &                                          &                                                                           &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
+                                                      & \multicolumn{1}{l}{\textbf{reselection}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
+                  \cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}           &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                 &                 & \multicolumn{1}{l}{\textbf{10}} &                 &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                                    &                 \\
+                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                           & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                                       & \textbf{std}    \\
+                  \midrule
+                  abalone                             & 930                                      & 4.3548                                                                    & 0.9760          & 930                            & 2.8473          & 1.2885          & 930                             & 2.7505          & 1.2622          & 930                             & 2.5602                                                                    & 1.2988          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4871}          & 1.3182          \\
+                  adult                               & 930                                      & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7097} & 1.2671          & 930                            & 4.4559          & 1.0052          & 930                             & 3.4398          & 1.0453          & 930                             & 2.7656                                                                    & 0.9837          & 930                             & 2.3065                                                                             & 1.0670          \\
+                  air\_quality                        & 930                                      & 3.7355                                                                    & 1.4046          & 930                            & 3.4075          & 1.3790          & 930                             & 2.9688          & 1.2783          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4237} & 1.2281          & 930                             & 2.4645                                                                             & 1.2906          \\
+                  bank                                & 930                                      & 4.5677                                                                    & 0.7039          & 930                            & 3.6323          & 1.1271          & 930                             & 2.4237          & 1.1333          & 930                             & 2.2462                                                                    & 1.1139          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1301}          & 1.0957          \\
+                  bike                                & 930                                      & 4.7935                                                                    & 0.6124          & 930                            & 3.9204          & 0.6480          & 930                             & 2.5161          & 0.8632          & 930                             & 2.0763                                                                    & 0.9007          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6935}          & 0.8911          \\
+                  car                                 & 930                                      & 4.6409                                                                    & 0.7847          & 930                            & 2.9527          & 1.1581          & 930                             & 2.6548          & 1.1748          & 930                             & 2.5312                                                                    & 1.2440          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2204}          & 1.2169          \\
+                  diabetic                            & 930                                      & 3.0129                                                                    & 1.0478          & 930                            & 4.4624          & 0.8688          & 930                             & 2.7957          & 1.1753          & 930                             & 2.6065                                                                    & 1.4391          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1226}          & 1.2639          \\
+                  fish\_toxicity                      & 930                                      & 3.7484                                                                    & 1.2377          & 930                            & 3.1376          & 1.3174          & 930                             & 3.0344          & 1.4062          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4656} & 1.3039          & 930                             & 2.6140                                                                             & 1.4318          \\
+                  forest\_fires                       & 930                                      & 3.8194                                                                    & 1.4330          & 930                            & 3.2720          & 1.2477          & 930                             & 2.8656          & 1.3464          & 930                             & 2.8194                                                                    & 1.3048          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2237}          & 1.2186          \\
+                  housing                             & 930                                      & 4.1892                                                                    & 1.0993          & 930                            & 3.0172          & 1.2882          & 930                             & 2.5871          & 1.3541          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5312} & 1.2654          & 930                             & 2.6753                                                                             & 1.3399          \\
+                  iris                                & 930                                      & 2.9839                                                                    & 1.4244          & 930                            & 2.9710          & 1.3165          & 930                             & 3.3462          & 1.4182          & 930                             & 3.0140                                                                    & 1.4054          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6849}          & 1.4289          \\
+                  mushroom                            & 930                                      & 4.2065                                                                    & 1.2356          & 930                            & 2.9688          & 1.2992          & 930                             & 2.5860          & 1.2336          & 930                             & 2.7882                                                                    & 1.3397          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4505}          & 1.2259          \\
+                  parkinsons                          & 930                                      & 4.7645                                                                    & 0.7563          & 930                            & 3.1882          & 1.0208          & 930                             & 2.2957          & 1.2089          & 930                             & 2.4968                                                                    & 1.1282          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2548}          & 1.0973          \\
+                  student\_performance                & 930                                      & 3.9710                                                                    & 1.0942          & 930                            & 4.0226          & 1.1196          & 930                             & 2.4774          & 1.2206          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495} & 1.2002          & 930                             & 2.2796                                                                             & 1.1324          \\
+                  wine\_quality                       & 930                                      & 4.0688                                                                    & 1.1220          & 930                            & 2.9204          & 1.2934          & 930                             & 2.9559          & 1.3831          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4032} & 1.3779          & 930                             & 2.6516                                                                             & 1.2796          \\
+                  \midrule
+                  \textbf{overall}                    & \textbf{13950}                           & \textbf{3.9044}                                                           & \textbf{1.3641} & \textbf{13950}                 & \textbf{3.4118} & \textbf{1.2914} & \textbf{13950}                  & \textbf{2.7799} & \textbf{1.2811} & \textbf{13950}                  & \textbf{2.5318}                                                           & \textbf{1.2660} & \textbf{13950}                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.3506}} & \textbf{1.2541} \\
+            \end{tabular}%
+      }
+\end{table}%
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.pdf}
+      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying reselection values per dataset, across all runs and epochs.}
+      \label{fig:results:reselection:descriptive:descriptive}
+\end{figure}
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_reselection/figures/cd/overall.pdf}
+      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying reselection values across all datasets, runs and epochs.}
+      \label{fig:results:reselection:descriptive:cd}
+\end{figure}
+
+\section{Replay Window Size}\label{sec:results:bhh_variant_replay}
+
+\begin{table}[htbp]
+      \centering
+      \caption{Empirical results showcasing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+      \label{tab:results:replay:metrics}%
+      \par\bigskip
+      \resizebox{\textwidth}{!}{
+            \begin{tabular}{rccccccccccccccc}
+                  \textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}  &                                                                           &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
+                  \cmidrule{1-2}                      &                                     &                                                                           &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
+                                                      & \multicolumn{1}{l}{\textbf{replay}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
+                  \cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}      &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                 &                 \\
+                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                      & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    \\
+                  \midrule
+                  abalone                             & 930                                 & 3.0258                                                                    & 1.3816          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6785}          & 1.4551          & 930                             & 3.1968                                                                    & 1.3460          & 930                             & 3.0903                                                                    & 1.3851          & 930                             & 3.0086          & 1.4503          \\
+                  adult                               & 930                                 & 2.8785                                                                    & 1.3824          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8269}          & 1.3595          & 930                             & 2.9430                                                                    & 1.4804          & 930                             & 3.0538                                                                    & 1.3714          & 930                             & 2.9645          & 1.5686          \\
+                  air\_quality                        & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3851          & 930                            & 3.0151                                                                             & 1.4970          & 930                             & 2.9978                                                                    & 1.4294          & 930                             & 2.9505                                                                    & 1.2966          & 930                             & 3.1624          & 1.4430          \\
+                  bank                                & 930                                 & 2.9484                                                                    & 1.4597          & 930                            & 3.0570                                                                             & 1.4731          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8602} & 1.3439          & 930                             & 3.0172                                                                    & 1.4202          & 930                             & 3.1172          & 1.3592          \\
+                  bike                                & 930                                 & 2.9602                                                                    & 1.2739          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7366}          & 1.3401          & 930                             & 3.1452                                                                    & 1.4478          & 930                             & 2.9226                                                                    & 1.4174          & 930                             & 3.2355          & 1.5274          \\
+                  car                                 & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7054} & 1.3572          & 930                            & 2.8376                                                                             & 1.3898          & 930                             & 3.0763                                                                    & 1.3723          & 930                             & 3.3269                                                                    & 1.4631          & 930                             & 3.0538          & 1.4086          \\
+                  diabetic                            & 930                                 & 3.2473                                                                    & 1.3690          & 930                            & 3.3247                                                                             & 1.4058          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5935} & 1.3719          & 930                             & 2.8075                                                                    & 1.3844          & 930                             & 3.0269          & 1.4113          \\
+                  fish\_toxicity                      & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7269} & 1.4190          & 930                            & 3.0785                                                                             & 1.4896          & 930                             & 3.1774                                                                    & 1.3980          & 930                             & 2.9892                                                                    & 1.3865          & 930                             & 3.0280          & 1.3373          \\
+                  forest\_fires                       & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8054} & 1.4926          & 930                            & 2.9151                                                                             & 1.3812          & 930                             & 2.9914                                                                    & 1.4081          & 930                             & 3.0591                                                                    & 1.4111          & 930                             & 3.2290          & 1.3416          \\
+                  housing                             & 930                                 & 3.1548                                                                    & 1.3007          & 930                            & 2.9774                                                                             & 1.4068          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8548} & 1.4501          & 930                             & 3.0355                                                                    & 1.4898          & 930                             & 2.9774          & 1.4037          \\
+                  iris                                & 930                                 & 3.0720                                                                    & 1.3757          & 930                            & 3.1581                                                                             & 1.4187          & 930                             & 3.2204                                                                    & 1.3919          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6183} & 1.3964          & 930                             & 2.9312          & 1.4102          \\
+                  mushroom                            & 930                                 & 3.0538                                                                    & 1.3243          & 930                            & 3.1430                                                                             & 1.4369          & 930                             & 3.0419                                                                    & 1.4140          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613} & 1.3823          & 930                             & 2.8957          & 1.4966          \\
+                  parkinsons                          & 930                                 & 3.1720                                                                    & 1.3719          & 930                            & 2.8430                                                                             & 1.2437          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6731} & 1.4535          & 930                             & 3.1172                                                                    & 1.4189          & 930                             & 3.1946          & 1.4977          \\
+                  student\_performance                & 930                                 & 3.0398                                                                    & 1.3684          & 930                            & 2.9226                                                                             & 1.4106          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6548} & 1.4028          & 930                             & 3.0935                                                                    & 1.3225          & 930                             & 3.2892          & 1.4874          \\
+                  wine\_quality                       & 930                                 & 3.1742                                                                    & 1.4300          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7323}          & 1.4556          & 930                             & 3.1581                                                                    & 1.4179          & 930                             & 3.0419                                                                    & 1.3565          & 930                             & 2.8935          & 1.3624          \\
+                  \midrule
+                  \textbf{overall}                    & \textbf{13950}                      & \textbf{2.9892}                                                           & \textbf{1.3892} & \textbf{13950}                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9497}} & \textbf{1.4224} & \textbf{13950}                  & \textbf{2.9723}                                                           & \textbf{1.4224} & \textbf{13950}                  & \textbf{2.9990}                                                           & \textbf{1.4021} & \textbf{13950}                  & \textbf{3.0672} & \textbf{1.4400} \\
+            \end{tabular}%
+      }
+\end{table}%
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_replay/figures/descriptive/descriptive.pdf}
+      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying replay window sizes per dataset, across all runs and epochs.}
+      \label{fig:results:replay:descriptive:descriptive}
+\end{figure}
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_replay/figures/cd/overall.pdf}
+      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying replay window sizes across all datasets, runs and epochs.}
+      \label{fig:results:replay:descriptive:cd}
+\end{figure}
+
+\section{Reanalysis Interval}\label{sec:results:bhh_variant_reanalysis}
+
+\begin{table}[htbp]
+      \centering
+      \caption{Empirical results showcasing average rank and statistics for different reanalysis values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+      \label{tab:results:reanalysis:metrics}%
+      \par\bigskip
+      \resizebox{\textwidth}{!}{\begin{tabular}{rccccccccccccccc}
+                  \textbf{step}                       & \multicolumn{1}{l}{\textbf{(all)}}      &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+                  \cmidrule{1-2}                      &                                         &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+                                                      & \multicolumn{1}{l}{\textbf{reanalysis}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+                  \cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}          &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                           &                 \\
+                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                          & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    \\
+                  \midrule
+                  abalone                             & 930                                     & 2.9849                                                                    & 1.3965          & 930                            & 3.0699                                                                    & 1.4423          & 930                             & 3.1710                                                                             & 1.3205          & 930                             & 2.9441                                                                    & 1.4447          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301} & 1.4433          \\
+                  adult                               & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860}          & 0.8523          & 930                             & 2.7914                                                                    & 1.7091          & 930                             & 3.0151                                                                    & 1.7236          \\
+                  air\_quality                        & 930                                     & 2.9613                                                                    & 1.3442          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8387} & 1.4383          & 930                             & 3.2559                                                                             & 1.4024          & 930                             & 3.0538                                                                    & 1.4200          & 930                             & 2.8903                                                                    & 1.4297          \\
+                  bank                                & 930                                     & 3.1161                                                                    & 1.4322          & 930                            & 3.0452                                                                    & 1.3827          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7355}          & 1.3985          & 930                             & 2.9280                                                                    & 1.4028          & 930                             & 3.1753                                                                    & 1.4151          \\
+                  bike                                & 930                                     & 3.1409                                                                    & 1.2581          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.3914          & 930                             & 3.1946                                                                             & 1.3653          & 930                             & 3.0978                                                                    & 1.4978          & 930                             & 2.8086                                                                    & 1.4905          \\
+                  car                                 & 930                                     & 3.1237                                                                    & 1.4229          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7237} & 1.3575          & 930                             & 2.8763                                                                             & 1.2987          & 930                             & 3.1538                                                                    & 1.3846          & 930                             & 3.1226                                                                    & 1.5473          \\
+                  diabetic                            & 930                                     & 3.2452                                                                    & 1.3050          & 930                            & 3.0720                                                                    & 1.3913          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7785}          & 1.4067          & 930                             & 3.0290                                                                    & 1.4249          & 930                             & 2.8753                                                                    & 1.4940          \\
+                  fish\_toxicity                      & 930                                     & 3.1452                                                                    & 1.3620          & 930                            & 3.0032                                                                    & 1.4455          & 930                             & 3.2172                                                                             & 1.3639          & 930                             & 3.1000                                                                    & 1.4088          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5344} & 1.3879          \\
+                  forest\_fires                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8398} & 1.3690          & 930                            & 3.1215                                                                    & 1.4707          & 930                             & 3.0043                                                                             & 1.3181          & 930                             & 2.8860                                                                    & 1.3535          & 930                             & 3.1484                                                                    & 1.5261          \\
+                  housing                             & 930                                     & 3.3129                                                                    & 1.3107          & 930                            & 2.9892                                                                    & 1.3927          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6871}          & 1.4833          & 930                             & 2.6968                                                                    & 1.4965          & 930                             & 3.3140                                                                    & 1.2356          \\
+                  iris                                & 930                                     & 3.1204                                                                    & 1.3010          & 930                            & 3.0968                                                                    & 1.3909          & 930                             & 3.1269                                                                             & 1.4320          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366} & 1.4492          & 930                             & 3.0194                                                                    & 1.4352          \\
+                  mushroom                            & 930                                     & 2.9312                                                                    & 1.3794          & 930                            & 3.1538                                                                    & 1.4031          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8473}          & 1.3836          & 930                             & 3.1215                                                                    & 1.4530          & 930                             & 2.9032                                                                    & 1.4714          \\
+                  parkinsons                          & 930                                     & 2.9688                                                                    & 1.3850          & 930                            & 3.0086                                                                    & 1.3559          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6129}          & 1.4814          & 930                             & 3.1032                                                                    & 1.3804          & 930                             & 3.3065                                                                    & 1.3778          \\
+                  student\_performance                & 930                                     & 2.9409                                                                    & 1.4118          & 930                            & 3.1849                                                                    & 1.3804          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710}          & 1.4097          & 930                             & 3.1258                                                                    & 1.3655          & 930                             & 2.9774                                                                    & 1.4675          \\
+                  wine\_quality                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8032} & 1.4440          & 930                            & 2.9204                                                                    & 1.3042          & 930                             & 3.2022                                                                             & 1.4104          & 930                             & 2.9247                                                                    & 1.3491          & 930                             & 3.1495                                                                    & 1.5171          \\
+                  \midrule
+                  \textbf{overall}                    & \textbf{13950}                          & \textbf{2.9747}                                                           & \textbf{1.3710} & \textbf{13950}                 & \textbf{2.9315}                                                           & \textbf{1.3960} & \textbf{13950}                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.8978}} & \textbf{1.3999} & \textbf{13950}                  & \textbf{2.9728}                                                           & \textbf{1.4464} & \textbf{13950}                  & \textbf{3.0047}                                                           & \textbf{1.4805} \\
+            \end{tabular}%
+      }
+
+\end{table}%
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_reanalysis/figures/descriptive/descriptive.pdf}
+      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying reanalysis window sizes per dataset, across all runs and epochs.}
+      \label{fig:results:reanalysis:descriptive:descriptive}
+\end{figure}
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_reanalysis/figures/cd/overall.pdf}
+      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying reanalysis window sizes across all datasets, runs and epochs.}
+      \label{fig:results:reanalysis:descriptive:cd}
+\end{figure}
+
+\section{Burn In}\label{sec:results:bhh_variant_burn_in}
+
+\begin{table}[htbp]
+      \centering
+      \caption{Empirical results showcasing average rank and statistics for different \index{burn in}burn in values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+      \label{tab:results:burn_in:metrics}%
+      \par\bigskip
+      \resizebox{\textwidth}{!}{
+            \begin{tabular}{rccccccccccccccc}
+                  \textbf{epoch}                      & \multicolumn{1}{l}{(all)}             &                                                                                    &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
+                  \cmidrule{1-2}                      &                                       &                                                                                    &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
+                                                      & \multicolumn{1}{l}{\textbf{burn\_in}} & \multicolumn{1}{l}{\textbf{results}}                                               &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
+                  \cmidrule{2-3}                      & \textbf{0}                            &                                                                                    &                 & \textbf{5}     &                                                                           &                 & \textbf{10}    &                                                                           &                 & \textbf{15}    &                                                                           &                 & \textbf{20}    &                 &                 \\
+                  \cmidrule{2-16}    \textbf{dataset} & \textbf{count}                        & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}    & \textbf{std}    \\
+                  \midrule
+                  abalone                             & 930                                   & 2.9151                                                                             & 1.3952          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6935} & 1.3934          & 930            & 2.9172                                                                    & 1.3837          & 930            & 2.8398                                                                    & 1.3524          & 930            & 3.6344          & 1.3574          \\
+                  adult                               & 930                                   & 2.7366                                                                             & 1.4475          & 930            & 2.6430                                                                    & 1.3817          & 930            & 2.9892                                                                    & 1.4111          & 930            & 3.1731                                                                    & 1.4477          & 930            & 3.1355          & 1.4130          \\
+                  air\_quality                        & 930                                   & 2.9097                                                                             & 1.4408          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6817} & 1.4270          & 930            & 2.7699                                                                    & 1.3443          & 930            & 3.3720                                                                    & 1.3137          & 930            & 3.2667          & 1.4119          \\
+                  bike                                & 930                                   & 1.9237                                                                             & 0.9808          & 930            & 2.1806                                                                    & 1.0238          & 930            & 2.9237                                                                    & 1.2739          & 930            & 3.5054                                                                    & 1.1859          & 930            & 4.4667          & 0.8514          \\
+                  car                                 & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3624}          & 1.2315          & 930            & 2.5882                                                                    & 1.4246          & 930            & 3.2978                                                                    & 1.3922          & 930            & 3.3796                                                                    & 1.2711          & 930            & 3.3720          & 1.4009          \\
+                  fish\_toxicity                      & 930                                   & 3.0634                                                                             & 1.4589          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7935} & 1.4021          & 930            & 2.8204                                                                    & 1.5131          & 930            & 3.1022                                                                    & 1.3461          & 930            & 3.2204          & 1.2949          \\
+                  forest\_fires                       & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8161}          & 1.3301          & 930            & 2.8495                                                                    & 1.3830          & 930            & 2.8645                                                                    & 1.4092          & 930            & 3.3774                                                                    & 1.3976          & 930            & 3.0925          & 1.4709          \\
+                  housing                             & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6903}          & 1.3837          & 930            & 2.9516                                                                    & 1.3176          & 930            & 2.9968                                                                    & 1.4425          & 930            & 3.0581                                                                    & 1.3435          & 930            & 3.3032          & 1.5101          \\
+                  iris                                & 930                                   & 2.9473                                                                             & 1.4608          & 930            & 2.9720                                                                    & 1.3675          & 930            & 3.1903                                                                    & 1.4493          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710} & 1.3694          & 930            & 3.1194          & 1.3872          \\
+                  mushroom                            & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2065}          & 1.2486          & 930            & 2.9376                                                                    & 1.2977          & 930            & 3.1613                                                                    & 1.2966          & 930            & 3.1441                                                                    & 1.4015          & 930            & 3.5226          & 1.5006          \\
+                  parkinsons                          & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2796}          & 1.2822          & 930            & 2.8892                                                                    & 1.2474          & 930            & 2.7065                                                                    & 1.3143          & 930            & 3.3968                                                                    & 1.4175          & 930            & 3.7280          & 1.3295          \\
+                  student\_performance                & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1452}          & 1.2052          & 930            & 2.6946                                                                    & 1.4032          & 930            & 3.0968                                                                    & 1.3525          & 930            & 3.4581                                                                    & 1.3539          & 930            & 3.6054          & 1.2312          \\
+                  wine\_quality                       & 930                                   & 2.9699                                                                             & 1.4373          & 930            & 3.0108                                                                    & 1.3041          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6634} & 1.4186          & 930            & 3.1247                                                                    & 1.3980          & 930            & 3.2312          & 1.4471          \\
+                  bank                                & 930                                   & 2.7301                                                                             & 1.3210          & 930            & 2.8194                                                                    & 1.3350          & 930            & 2.8570                                                                    & 1.4848          & 930            & 2.9312                                                                    & 1.3841          & 930            & 3.6624          & 1.3391          \\
+                  \midrule
+                  \textbf{overall}                    & \textbf{13020}                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.6211}} & \textbf{1.3814} & \textbf{13020} & \textbf{2.7647}                                                           & \textbf{1.3553} & \textbf{13020} & \textbf{2.9468}                                                           & \textbf{1.4045} & \textbf{13020} & \textbf{3.1881}                                                           & \textbf{1.3754} & \textbf{13020} & \textbf{3.4543} & \textbf{1.4061} \\
+            \end{tabular}%
+      }
+\end{table}%
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_burn_in/figures/descriptive/descriptive.pdf}
+      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying burn in values per dataset, across all runs and epochs.}
+      \label{fig:results:burn_in:descriptive:descriptive}
+\end{figure}
+
+The critical difference plot as presented in Figure \ref{fig:results:burn_in:descriptive:cd} shows the statistical significance between burn in window sizes overall, across all datasets.
+One can clearly see from this plot that little to no burn in is preferred in most of the cases.
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_burn_in/figures/cd/overall.pdf}
+      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying burn in values across all datasets, runs and epochs.}
+      \label{fig:results:burn_in:descriptive:cd}
+\end{figure}
+
+\section{Normalisation}\label{sec:results:bhh_variant_normalise}
+
+\begin{table}[htbp]
+      \centering
+      \caption{Empirical results showcasing average rank and statistics for \index{normalisation}normalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+      \label{tab:results:normalise:metrics}%
+      \par\bigskip
+      \resizebox{\textwidth}{!}{
+            \begin{tabular}{rcccccc}
+                  \textbf{epoch}                     & \multicolumn{1}{l}{\textbf{(all)}}         &                                                                                    &                 &                                   &                                                                           &                 \\
+                  \cmidrule{1-2}                     &                                            &                                                                                    &                 &                                   &                                                                           &                 \\
+                                                     & \multicolumn{1}{l}{\textbf{normalisation}} & \multicolumn{1}{l}{\textbf{metric}}                                                &                 &                                   &                                                                           &                 \\
+                  \cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{FALSE}}         &                                                                                    &                 & \multicolumn{1}{l}{\textbf{TRUE}} &                                                                           &                 \\
+                  \cmidrule{2-7}    \textbf{dataset} & \textbf{count}                             & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
+                  \midrule
+                  abalone                            & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5002          & 930                               & 1.5065                                                                    & 0.5002          \\
+                  adult                              & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4710}          & 0.4994          & 930                               & 1.4968                                                                    & 0.5003          \\
+                  air\_quality                       & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4892}          & 0.5002          & 930                               & 1.5108                                                                    & 0.5002          \\
+                  bank                               & 930                                        & 1.5484                                                                             & 0.4979          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4516} & 0.4979          \\
+                  bike                               & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4978}          & 0.5003          & 930                               & 1.5022                                                                    & 0.5003          \\
+                  car                                & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4258}          & 0.4947          & 930                               & 1.5742                                                                    & 0.4947          \\
+                  diabetic                           & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4753}          & 0.4997          & 930                               & 1.5247                                                                    & 0.4997          \\
+                  fish\_toxicity                     & 930                                        & 1.5505                                                                             & 0.4977          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4495} & 0.4977          \\
+                  forest\_fires                      & 930                                        & 1.5054                                                                             & 0.5002          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4946} & 0.5002          \\
+                  housing                            & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4720}          & 0.4995          & 930                               & 1.5280                                                                    & 0.4995          \\
+                  iris                               & 930                                        & 1.5645                                                                             & 0.4961          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4355} & 0.4961          \\
+                  mushroom                           & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4323}          & 0.4957          & 930                               & 1.5667                                                                    & 0.4958          \\
+                  parkinsons                         & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4000}          & 0.4902          & 930                               & 1.6000                                                                    & 0.4902          \\
+                  student\_performance               & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3892}          & 0.4878          & 930                               & 1.6108                                                                    & 0.4878          \\
+                  wine\_quality                      & 930                                        & 1.5473                                                                             & 0.4980          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4527} & 0.4980          \\
+                  \midrule
+                  \textbf{overall}                   & \textbf{13950}                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4842}} & \textbf{0.4998} & \textbf{13950}                    & \textbf{1.5136}                                                           & \textbf{0.4998} \\
+            \end{tabular}%
+      }
+\end{table}%
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_normalise/figures/descriptive/descriptive.pdf}
+      \caption{Descriptive plots between the average ranks of the \acs{BHH} with normalisation toggled per dataset, across all runs and epochs.}
+      \label{fig:results:normalise:descriptive:descriptive}
+\end{figure}
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_normalise/figures/cd/overall.pdf}
+      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with normalisation toggled across all datasets, runs and epochs.}
+      \label{fig:results:normalise:descriptive:cd}
+\end{figure}
+
+\section{Discounted Rewards}\label{sec:results:bhh_variant_discounted_rewards}
+
+\begin{table}[htbp]
+      \centering
+      \caption{Empirical results showcasing average rank and statistics for \index{discounted rewards}discounted rewards toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+      \label{tab:results:discounted_rewards:metrics}%
+      \par\bigskip
+      \resizebox{\textwidth}{!}{
+            \begin{tabular}{rcccccc}
+                  epoch                              & \multicolumn{1}{l}{(all)}          &                                                                                    &                 &                                   &                                                                           &                 \\
+                  \cmidrule{1-2}                     &                                    &                                                                                    &                 &                                   &                                                                           &                 \\
+                                                     & \multicolumn{1}{l}{\textbf{dr}}    & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                   &                                                                           &                 \\
+                  \cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{FALSE}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{TRUE}} &                                                                           &                 \\
+                  \cmidrule{2-7}    \textbf{dataset} & \textbf{count}                     & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
+                  \midrule
+                  abalone                            & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4914}          & 0.5002          & 930                               & 1.5086                                                                    & 0.5002          \\
+                  adult                              & 930                                & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4645} & 0.4990          \\
+                  air\_quality                       & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4613}          & 0.4988          & 930                               & 1.5387                                                                    & 0.4988          \\
+                  bank                               & 930                                & 1.5161                                                                             & 0.5000          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4839} & 0.5000          \\
+                  bike                               & 930                                & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
+                  car                                & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4280}          & 0.4950          & 930                               & 1.5720                                                                    & 0.4950          \\
+                  diabetic                           & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4699}          & 0.4994          & 930                               & 1.5301                                                                    & 0.4994          \\
+                  fish\_toxicity                     & 930                                & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
+                  forest\_fires                      & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4742}          & 0.4996          & 930                               & 1.5258                                                                    & 0.4996          \\
+                  housing                            & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4237}          & 0.4944          & 930                               & 1.5763                                                                    & 0.4944          \\
+                  iris                               & 930                                & 1.5903                                                                             & 0.4920          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4097} & 0.4920          \\
+                  mushroom                           & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3946}          & 0.4890          & 930                               & 1.5806                                                                    & 0.4937          \\
+                  parkinsons                         & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3710}          & 0.4833          & 930                               & 1.6290                                                                    & 0.4833          \\
+                  student\_performance               & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4398}          & 0.4966          & 930                               & 1.5602                                                                    & 0.4966          \\
+                  wine\_quality                      & 930                                & 1.5570                                                                             & 0.4970          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4430} & 0.4970          \\
+                  \midrule
+                  \textbf{overall}                   & \textbf{13950}                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4747}} & \textbf{0.4994} & \textbf{13950}                    & \textbf{1.5214}                                                           & \textbf{0.4996} \\
+            \end{tabular}%
+      }
+\end{table}%
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/descriptive/descriptive.pdf}
+      \caption{Descriptive plots between the average ranks of the \acs{BHH} with discounted rewards toggled per datasets, across all runs and epochs.}
+      \label{fig:results:discounted_rewards:descriptive:descriptive}
+\end{figure}
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/cd/overall.pdf}
+      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with discounted rewards toggled across all datasets, runs and epochs.}
+      \label{fig:results:discounted_rewards:descriptive:cd}
+\end{figure}
+
+\section{Overfitting}\label{sec:results:overfitting}
+
+\section{Practical Applications}\label{sec:results:practical_applications}
+
+\section{Summary}\label{sec:results:summary}

### 2022-11-11 scripts/analyse_case_study.py
✨ (results): New plots with tight bounding boxes

@@ -242,7 +242,7 @@ def plot_params():
 				plot.set_yscale('log') # Logarithmic plot
 
 				OUTPUT = os.path.join(ANALYSIS_PATH, 'figures/{}/{}.pdf'.format(param_group, param))
-				fig.savefig(OUTPUT, transparent=True)
+				fig.savefig(OUTPUT, transparent=True, bbox_inches='tight')
 				plt.close()
 			except Exception as e:
 				print(e)

### 2022-11-11 dissertation/appendix/case-study-additional.tex
✨ (results): Recolored plots

@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][1].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{1}$ (\acs{Momentum}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{1} \vert \theta_{1} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{1}$ (\acs{Momentum}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{1} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
 	\label{fig:app:case_study_additional:p_HgEC:0:1}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][2].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{2}$ (\acs{NAG}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{2} \vert \theta_{2} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{2}$ (\acs{NAG}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{2} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
 	\label{fig:app:case_study_additional:p_HgEC:0:2}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][3].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{3}$ (\acs{Adagrad}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{3} \vert \theta_{3} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{3}$ (\acs{Adagrad}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{3} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
 	\label{fig:app:case_study_additional:p_HgEC:0:3}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][4].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{4}$ (\acs{RMSProp}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{4} \vert \theta_{4} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{4}$ (\acs{RMSProp}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{4} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
 	\label{fig:app:case_study_additional:p_HgEC:0:4}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][5].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{5}$ (\acs{Adadelta}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{5} \vert \theta_{5} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{5}$ (\acs{Adadelta}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{5} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
 	\label{fig:app:case_study_additional:p_HgEC:0:5}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][9].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{9}$ (\acs{DE}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{9} \vert \theta_{9} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{9}$ (\acs{DE}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{9} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
 	\label{fig:app:case_study_additional:p_HgEC:0:9}

### 2022-11-11 dissertation/chapters/08-results.tex
✨ (results): New plots with tight bounding boxes
✨ (results): Recolored plots

@@
 \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
-      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert \theta_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
-      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert \theta_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
-      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert \theta_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
-      \caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert \theta_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:8}
@@
 	\centering
-      \caption{Empirical results showcasing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
+	\caption{Empirical results showing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
 	\label{tab:results:standalone:metrics:test_loss}%
@@
 	\centering
-      \caption{Empirical results showcasing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:standalone:metrics:rank}%
@@
 
-\begin{sidewaysfigure}[htbp]
+\begin{figure}[htbp]
 	\centering
 	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots between the average ranks of all low-level heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \Acs{BHH} per dataset, across all runs and steps.}
+	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \Acs{BHH} per dataset, across all runs and epochs.}
 	\label{fig:results:standalone:descriptive:descriptive}
-\end{sidewaysfigure}
+\end{figure}
 
@@
 	\includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
-      \caption{Critical difference plots between the average ranks of all low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and steps.}
+	\caption{Critical difference plots for the average ranks of all low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
 	\label{fig:results:standalone:descriptive:cd}
@@
 	\centering
-      \caption{Empirical results showcasing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:heuristic_pool:metrics}%
@@
 			\cmidrule{1-2}                      &                                             &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
-                                                      & \multicolumn{1}{l}{\textbf{pool}}  & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                &                                                                                    &                 &                &                 &                 \\
+			                                    & \multicolumn{1}{l}{\textbf{heuristic pool}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                &                                                                                    &                 &                &                 &                 \\
 			\cmidrule{2-3}                      & \textbf{all}                                &                                                                           &                 & \textbf{gd}    &                                                                                    &                 & \textbf{mh}    &                 &                 \\
@@
 			adult                               & 930                                         & 2.8484                                                                    & 0.5058          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.1559}          & 0.4077          & 930            & 1.8989          & 0.4104          \\
-                  air\_quality                        & 930                                & 2.1871                                                                    & 0.8153          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6828}          & 0.7506          & 930            & 2.1301          & 0.7883          \\
+			air quality                         & 930                                         & 2.1871                                                                    & 0.8153          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6828}          & 0.7506          & 930            & 2.1301          & 0.7883          \\
 			bank                                & 930                                         & 1.7731                                                                    & 0.5617          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3215}          & 0.4920          & 930            & 2.9054          & 0.3341          \\
@@
 			diabetic                            & 930                                         & 2.4516                                                                    & 0.7353          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.2806}          & 0.5756          & 930            & 2.2677          & 0.5798          \\
-                  fish\_toxicity                      & 930                                & 1.9903                                                                    & 0.8485          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8344}          & 0.7684          & 930            & 2.1753          & 0.7959          \\
-                  forest\_fires                       & 930                                & 2.0667                                                                    & 0.8338          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8269}          & 0.7813          & 930            & 2.1065          & 0.8066          \\
+			fish toxicity                       & 930                                         & 1.9903                                                                    & 0.8485          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8344}          & 0.7684          & 930            & 2.1753          & 0.7959          \\
+			forest fires                        & 930                                         & 2.0667                                                                    & 0.8338          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8269}          & 0.7813          & 930            & 2.1065          & 0.8066          \\
 			housing                             & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6043} & 0.6869          & 930            & 1.6602                                                                             & 0.6648          & 930            & 2.7355          & 0.5238          \\
@@
 			parkinsons                          & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5570} & 0.6238          & 930            & 1.6011                                                                             & 0.5915          & 930            & 2.8419          & 0.4448          \\
-                  student\_performance                & 930                                & 1.9828                                                                    & 0.8220          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7903}          & 0.8480          & 930            & 2.2269          & 0.7152          \\
-                  wine\_quality                       & 930                                & 1.5785                                                                    & 0.5498          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5630          & 930            & 2.9280          & 0.2938          \\
+			student performance                 & 930                                         & 1.9828                                                                    & 0.8220          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7903}          & 0.8480          & 930            & 2.2269          & 0.7152          \\
+			wine quality                        & 930                                         & 1.5785                                                                    & 0.5498          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5630          & 930            & 2.9280          & 0.2938          \\
 			\midrule
@@
 
-\begin{sidewaysfigure}[htbp]
+\begin{figure}[htbp]
 	\centering
 	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying heuristic pools per dataset, across all runs and steps.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying heuristic pools per dataset, across all runs and epochs.}
 	\label{fig:results:heuristic_pool:descriptive:descriptive}
-\end{sidewaysfigure}
+\end{figure}
 
@@
 	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying heuristic pools across all datasets, runs and steps.}
+	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying heuristic pools across all datasets, runs and epochs.}
 	\label{fig:results:heuristic_pool:descriptive:cd}
@@
 	\centering
-      \caption{Empirical results showcasing average rank and statistics for different population size values used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}
+	\caption{Empirical results showing average rank and statistics for different population size values used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}
 	\label{tab:results:population:metrics}%
@@
 			adult                               & 930                                     & 3.5720                                                                             & 1.4693          & 930                             & 3.2828                                                                    & 1.3751          & 930                             & 2.8108          & 1.3625          & 930                             & 2.6484                                                                    & 1.3222          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3634} & 1.3063          \\
-                  air\_quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7527}          & 1.4283          & 930                             & 2.9258                                                                    & 1.3904          & 930                             & 2.9656          & 1.3791          & 930                             & 3.3140                                                                    & 1.3789          & 930                             & 3.0419                                                                    & 1.4374          \\
+			air quality                         & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7527}          & 1.4283          & 930                             & 2.9258                                                                    & 1.3904          & 930                             & 2.9656          & 1.3791          & 930                             & 3.3140                                                                    & 1.3789          & 930                             & 3.0419                                                                    & 1.4374          \\
 			bank                                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8129}          & 1.4102          & 930                             & 3.1591                                                                    & 1.4348          & 930                             & 2.9989          & 1.4199          & 930                             & 3.0505                                                                    & 1.4438          & 930                             & 2.9785                                                                    & 1.3414          \\
@@
 			diabetic                            & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7978}          & 1.5078          & 930                             & 2.9387                                                                    & 1.4133          & 930                             & 3.2129          & 1.4525          & 930                             & 2.9613                                                                    & 1.3036          & 930                             & 3.0892                                                                    & 1.3534          \\
-                  fish\_toxicity                      & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8151}          & 1.4249          & 930                             & 3.0409                                                                    & 1.4288          & 930                             & 3.0925          & 1.3230          & 930                             & 3.1280                                                                    & 1.4073          & 930                             & 2.9237                                                                    & 1.4634          \\
-                  forest\_fires                       & 930                                     & 3.0172                                                                             & 1.4026          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9215} & 1.3800          & 930                             & 2.9806          & 1.3833          & 930                             & 3.0968                                                                    & 1.4124          & 930                             & 2.9839                                                                    & 1.4879          \\
+			fish toxicity                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8151}          & 1.4249          & 930                             & 3.0409                                                                    & 1.4288          & 930                             & 3.0925          & 1.3230          & 930                             & 3.1280                                                                    & 1.4073          & 930                             & 2.9237                                                                    & 1.4634          \\
+			forest fires                        & 930                                     & 3.0172                                                                             & 1.4026          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9215} & 1.3800          & 930                             & 2.9806          & 1.3833          & 930                             & 3.0968                                                                    & 1.4124          & 930                             & 2.9839                                                                    & 1.4879          \\
 			housing                             & 930                                     & 2.8366                                                                             & 1.4040          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8258} & 1.3802          & 930                             & 2.9753          & 1.4393          & 930                             & 2.9849                                                                    & 1.4111          & 930                             & 3.3774                                                                    & 1.3680          \\
@@
 			parkinsons                          & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6645}          & 1.4411          & 930                             & 3.1065                                                                    & 1.3272          & 930                             & 3.0247          & 1.4265          & 930                             & 3.0495                                                                    & 1.4420          & 930                             & 3.1548                                                                    & 1.3810          \\
-                  student\_performance                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6376}          & 1.4357          & 930                             & 2.8645                                                                    & 1.4108          & 930                             & 3.1548          & 1.4042          & 930                             & 3.2387                                                                    & 1.3970          & 930                             & 3.1043                                                                    & 1.3395          \\
-                  wine\_quality                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5505}          & 1.3165          & 930                             & 2.7817                                                                    & 1.4152          & 930                             & 3.1581          & 1.3841          & 930                             & 3.1806                                                                    & 1.3941          & 930                             & 3.3290                                                                    & 1.4140          \\
+			student performance                 & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6376}          & 1.4357          & 930                             & 2.8645                                                                    & 1.4108          & 930                             & 3.1548          & 1.4042          & 930                             & 3.2387                                                                    & 1.3970          & 930                             & 3.1043                                                                    & 1.3395          \\
+			wine quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5505}          & 1.3165          & 930                             & 2.7817                                                                    & 1.4152          & 930                             & 3.1581          & 1.3841          & 930                             & 3.1806                                                                    & 1.3941          & 930                             & 3.3290                                                                    & 1.4140          \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_population/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots between the average ranks of \acs{BHH} with varying population sizes per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of \acs{BHH} with varying population sizes per dataset, across all runs and epochs.}
 	\label{fig:results:population:descriptive:descriptive}
@@
 	\includegraphics[width=\textwidth]{bhh_population/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of \acs{BHH} with varying population sizes across all datasets, runs and epochs.}
+	\caption{Critical difference plots for the average ranks of \acs{BHH} with varying population sizes across all datasets, runs and epochs.}
 	\label{fig:results:population:descriptive:cd}
@@
 	\centering
-      \caption{Empirical results showcasing average rank and statistics for different \index{credit}credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different \index{credit}credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:credit:metrics}%
@@
 			adult                               & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                & 2.6763                                                                             & 1.5019          & 930                                & 2.8065                                                                    & 1.5003          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                    & 3.3538                                                                    & 1.5682          \\
-                  air\_quality                        & 930                                 & 3.1312                                                                    & 1.3472          & 930                                & 3.0376                                                                             & 1.3566          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5914} & 1.4646          & 930                                & 3.1280                                                                    & 1.3358          & 930                                    & 3.1118                                                                    & 1.4871          \\
+			air quality                         & 930                                 & 3.1312                                                                    & 1.3472          & 930                                & 3.0376                                                                             & 1.3566          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5914} & 1.4646          & 930                                & 3.1280                                                                    & 1.3358          & 930                                    & 3.1118                                                                    & 1.4871          \\
 			bank                                & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8591} & 1.3442          & 930                                & 2.9903                                                                             & 1.4320          & 930                                & 2.8882                                                                    & 1.4098          & 930                                & 3.0441                                                                    & 1.4154          & 930                                    & 3.2183                                                                    & 1.4424          \\
@@
 			diabetic                            & 930                                 & 2.8914                                                                    & 1.3488          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6269}          & 1.4171          & 930                                & 3.4151                                                                    & 1.3653          & 930                                & 2.8925                                                                    & 1.3620          & 930                                    & 3.1742                                                                    & 1.4487          \\
-                  fish\_toxicity                      & 930                                 & 3.1516                                                                    & 1.4360          & 930                                & 2.9903                                                                             & 1.4521          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.4748          & 930                                & 3.2043                                                                    & 1.2988          & 930                                    & 2.8957                                                                    & 1.3579          \\
-                  forest\_fires                       & 930                                 & 3.0968                                                                    & 1.2771          & 930                                & 3.1806                                                                             & 1.3040          & 930                                & 2.8559                                                                    & 1.3562          & 930                                & 3.1215                                                                    & 1.5018          & 930                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7452} & 1.5627          \\
+			fish toxicity                       & 930                                 & 3.1516                                                                    & 1.4360          & 930                                & 2.9903                                                                             & 1.4521          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.4748          & 930                                & 3.2043                                                                    & 1.2988          & 930                                    & 2.8957                                                                    & 1.3579          \\
+			forest fires                        & 930                                 & 3.0968                                                                    & 1.2771          & 930                                & 3.1806                                                                             & 1.3040          & 930                                & 2.8559                                                                    & 1.3562          & 930                                & 3.1215                                                                    & 1.5018          & 930                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7452} & 1.5627          \\
 			housing                             & 930                                 & 2.9011                                                                    & 1.4938          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8527}          & 1.3168          & 930                                & 2.9022                                                                    & 1.3974          & 930                                & 3.3108                                                                    & 1.3243          & 930                                    & 3.0333                                                                    & 1.4833          \\
@@
 			parkinsons                          & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5645} & 1.4835          & 930                                & 2.8925                                                                             & 1.3429          & 930                                & 3.5065                                                                    & 1.2190          & 930                                & 3.0796                                                                    & 1.3920          & 930                                    & 2.9570                                                                    & 1.4548          \\
-                  student\_performance                & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6624} & 1.3124          & 930                                & 3.0290                                                                             & 1.4067          & 930                                & 3.1892                                                                    & 1.3821          & 930                                & 2.7978                                                                    & 1.4702          & 930                                    & 3.3215                                                                    & 1.3938          \\
-                  wine\_quality                       & 930                                 & 3.1871                                                                    & 1.3080          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366}          & 1.4706          & 930                                & 3.0140                                                                    & 1.3712          & 930                                & 2.9419                                                                    & 1.4115          & 930                                    & 3.2204                                                                    & 1.4300          \\
+			student performance                 & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6624} & 1.3124          & 930                                & 3.0290                                                                             & 1.4067          & 930                                & 3.1892                                                                    & 1.3821          & 930                                & 2.7978                                                                    & 1.4702          & 930                                    & 3.3215                                                                    & 1.3938          \\
+			wine quality                        & 930                                 & 3.1871                                                                    & 1.3080          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366}          & 1.4706          & 930                                & 3.0140                                                                    & 1.3712          & 930                                & 2.9419                                                                    & 1.4115          & 930                                    & 3.2204                                                                    & 1.4300          \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_credit/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying credit assignment strategies per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying credit assignment strategies per dataset, across all runs and epochs.}
 	\label{fig:results:credit:descriptive:descriptive}
@@
 	\includegraphics[width=\textwidth]{bhh_credit/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying credit assignment strategies across all datasets, runs and epochs.}
+	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying credit assignment strategies across all datasets, runs and epochs.}
 	\label{fig:results:credit:descriptive:cd}
@@
 	\centering
-      \caption{Empirical results showcasing average rank and statistics for different reselection values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different reselection values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:reselection:metrics}%
@@
 			adult                               & 930                                      & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7097} & 1.2671          & 930                            & 4.4559          & 1.0052          & 930                             & 3.4398          & 1.0453          & 930                             & 2.7656                                                                    & 0.9837          & 930                             & 2.3065                                                                             & 1.0670          \\
-                  air\_quality                        & 930                                      & 3.7355                                                                    & 1.4046          & 930                            & 3.4075          & 1.3790          & 930                             & 2.9688          & 1.2783          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4237} & 1.2281          & 930                             & 2.4645                                                                             & 1.2906          \\
+			air quality                         & 930                                      & 3.7355                                                                    & 1.4046          & 930                            & 3.4075          & 1.3790          & 930                             & 2.9688          & 1.2783          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4237} & 1.2281          & 930                             & 2.4645                                                                             & 1.2906          \\
 			bank                                & 930                                      & 4.5677                                                                    & 0.7039          & 930                            & 3.6323          & 1.1271          & 930                             & 2.4237          & 1.1333          & 930                             & 2.2462                                                                    & 1.1139          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1301}          & 1.0957          \\
@@
 			diabetic                            & 930                                      & 3.0129                                                                    & 1.0478          & 930                            & 4.4624          & 0.8688          & 930                             & 2.7957          & 1.1753          & 930                             & 2.6065                                                                    & 1.4391          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1226}          & 1.2639          \\
-                  fish\_toxicity                      & 930                                      & 3.7484                                                                    & 1.2377          & 930                            & 3.1376          & 1.3174          & 930                             & 3.0344          & 1.4062          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4656} & 1.3039          & 930                             & 2.6140                                                                             & 1.4318          \\
-                  forest\_fires                       & 930                                      & 3.8194                                                                    & 1.4330          & 930                            & 3.2720          & 1.2477          & 930                             & 2.8656          & 1.3464          & 930                             & 2.8194                                                                    & 1.3048          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2237}          & 1.2186          \\
+			fish toxicity                       & 930                                      & 3.7484                                                                    & 1.2377          & 930                            & 3.1376          & 1.3174          & 930                             & 3.0344          & 1.4062          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4656} & 1.3039          & 930                             & 2.6140                                                                             & 1.4318          \\
+			forest fires                        & 930                                      & 3.8194                                                                    & 1.4330          & 930                            & 3.2720          & 1.2477          & 930                             & 2.8656          & 1.3464          & 930                             & 2.8194                                                                    & 1.3048          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2237}          & 1.2186          \\
 			housing                             & 930                                      & 4.1892                                                                    & 1.0993          & 930                            & 3.0172          & 1.2882          & 930                             & 2.5871          & 1.3541          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5312} & 1.2654          & 930                             & 2.6753                                                                             & 1.3399          \\
@@
 			parkinsons                          & 930                                      & 4.7645                                                                    & 0.7563          & 930                            & 3.1882          & 1.0208          & 930                             & 2.2957          & 1.2089          & 930                             & 2.4968                                                                    & 1.1282          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2548}          & 1.0973          \\
-                  student\_performance                & 930                                      & 3.9710                                                                    & 1.0942          & 930                            & 4.0226          & 1.1196          & 930                             & 2.4774          & 1.2206          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495} & 1.2002          & 930                             & 2.2796                                                                             & 1.1324          \\
-                  wine\_quality                       & 930                                      & 4.0688                                                                    & 1.1220          & 930                            & 2.9204          & 1.2934          & 930                             & 2.9559          & 1.3831          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4032} & 1.3779          & 930                             & 2.6516                                                                             & 1.2796          \\
+			student performance                 & 930                                      & 3.9710                                                                    & 1.0942          & 930                            & 4.0226          & 1.1196          & 930                             & 2.4774          & 1.2206          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495} & 1.2002          & 930                             & 2.2796                                                                             & 1.1324          \\
+			wine quality                        & 930                                      & 4.0688                                                                    & 1.1220          & 930                            & 2.9204          & 1.2934          & 930                             & 2.9559          & 1.3831          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4032} & 1.3779          & 930                             & 2.6516                                                                             & 1.2796          \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying reselection values per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reselection values per dataset, across all runs and epochs.}
 	\label{fig:results:reselection:descriptive:descriptive}
@@
 	\includegraphics[width=\textwidth]{bhh_reselection/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying reselection values across all datasets, runs and epochs.}
+	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reselection values across all datasets, runs and epochs.}
 	\label{fig:results:reselection:descriptive:cd}
@@
 	\centering
-      \caption{Empirical results showcasing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:replay:metrics}%
@@
 			adult                               & 930                                 & 2.8785                                                                    & 1.3824          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8269}          & 1.3595          & 930                             & 2.9430                                                                    & 1.4804          & 930                             & 3.0538                                                                    & 1.3714          & 930                             & 2.9645          & 1.5686          \\
-                  air\_quality                        & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3851          & 930                            & 3.0151                                                                             & 1.4970          & 930                             & 2.9978                                                                    & 1.4294          & 930                             & 2.9505                                                                    & 1.2966          & 930                             & 3.1624          & 1.4430          \\
+			air quality                         & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3851          & 930                            & 3.0151                                                                             & 1.4970          & 930                             & 2.9978                                                                    & 1.4294          & 930                             & 2.9505                                                                    & 1.2966          & 930                             & 3.1624          & 1.4430          \\
 			bank                                & 930                                 & 2.9484                                                                    & 1.4597          & 930                            & 3.0570                                                                             & 1.4731          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8602} & 1.3439          & 930                             & 3.0172                                                                    & 1.4202          & 930                             & 3.1172          & 1.3592          \\
@@
 			diabetic                            & 930                                 & 3.2473                                                                    & 1.3690          & 930                            & 3.3247                                                                             & 1.4058          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5935} & 1.3719          & 930                             & 2.8075                                                                    & 1.3844          & 930                             & 3.0269          & 1.4113          \\
-                  fish\_toxicity                      & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7269} & 1.4190          & 930                            & 3.0785                                                                             & 1.4896          & 930                             & 3.1774                                                                    & 1.3980          & 930                             & 2.9892                                                                    & 1.3865          & 930                             & 3.0280          & 1.3373          \\
-                  forest\_fires                       & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8054} & 1.4926          & 930                            & 2.9151                                                                             & 1.3812          & 930                             & 2.9914                                                                    & 1.4081          & 930                             & 3.0591                                                                    & 1.4111          & 930                             & 3.2290          & 1.3416          \\
+			fish toxicity                       & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7269} & 1.4190          & 930                            & 3.0785                                                                             & 1.4896          & 930                             & 3.1774                                                                    & 1.3980          & 930                             & 2.9892                                                                    & 1.3865          & 930                             & 3.0280          & 1.3373          \\
+			forest fires                        & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8054} & 1.4926          & 930                            & 2.9151                                                                             & 1.3812          & 930                             & 2.9914                                                                    & 1.4081          & 930                             & 3.0591                                                                    & 1.4111          & 930                             & 3.2290          & 1.3416          \\
 			housing                             & 930                                 & 3.1548                                                                    & 1.3007          & 930                            & 2.9774                                                                             & 1.4068          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8548} & 1.4501          & 930                             & 3.0355                                                                    & 1.4898          & 930                             & 2.9774          & 1.4037          \\
@@
 			parkinsons                          & 930                                 & 3.1720                                                                    & 1.3719          & 930                            & 2.8430                                                                             & 1.2437          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6731} & 1.4535          & 930                             & 3.1172                                                                    & 1.4189          & 930                             & 3.1946          & 1.4977          \\
-                  student\_performance                & 930                                 & 3.0398                                                                    & 1.3684          & 930                            & 2.9226                                                                             & 1.4106          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6548} & 1.4028          & 930                             & 3.0935                                                                    & 1.3225          & 930                             & 3.2892          & 1.4874          \\
-                  wine\_quality                       & 930                                 & 3.1742                                                                    & 1.4300          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7323}          & 1.4556          & 930                             & 3.1581                                                                    & 1.4179          & 930                             & 3.0419                                                                    & 1.3565          & 930                             & 2.8935          & 1.3624          \\
+			student performance                 & 930                                 & 3.0398                                                                    & 1.3684          & 930                            & 2.9226                                                                             & 1.4106          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6548} & 1.4028          & 930                             & 3.0935                                                                    & 1.3225          & 930                             & 3.2892          & 1.4874          \\
+			wine quality                        & 930                                 & 3.1742                                                                    & 1.4300          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7323}          & 1.4556          & 930                             & 3.1581                                                                    & 1.4179          & 930                             & 3.0419                                                                    & 1.3565          & 930                             & 2.8935          & 1.3624          \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_replay/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying replay window sizes per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying replay window sizes per dataset, across all runs and epochs.}
 	\label{fig:results:replay:descriptive:descriptive}
@@
 	\includegraphics[width=\textwidth]{bhh_replay/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying replay window sizes across all datasets, runs and epochs.}
+	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying replay window sizes across all datasets, runs and epochs.}
 	\label{fig:results:replay:descriptive:cd}
@@
 	\centering
-      \caption{Empirical results showcasing average rank and statistics for different reanalysis values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different reanalysis values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:reanalysis:metrics}%
@@
 	\resizebox{\textwidth}{!}{\begin{tabular}{rccccccccccccccc}
-                  \textbf{step}                       & \multicolumn{1}{l}{\textbf{(all)}}      &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}      &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
 			\cmidrule{1-2}                      &                                         &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
@@
 			adult                               & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860}          & 0.8523          & 930                             & 2.7914                                                                    & 1.7091          & 930                             & 3.0151                                                                    & 1.7236          \\
-                  air\_quality                        & 930                                     & 2.9613                                                                    & 1.3442          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8387} & 1.4383          & 930                             & 3.2559                                                                             & 1.4024          & 930                             & 3.0538                                                                    & 1.4200          & 930                             & 2.8903                                                                    & 1.4297          \\
+			air quality                         & 930                                     & 2.9613                                                                    & 1.3442          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8387} & 1.4383          & 930                             & 3.2559                                                                             & 1.4024          & 930                             & 3.0538                                                                    & 1.4200          & 930                             & 2.8903                                                                    & 1.4297          \\
 			bank                                & 930                                     & 3.1161                                                                    & 1.4322          & 930                            & 3.0452                                                                    & 1.3827          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7355}          & 1.3985          & 930                             & 2.9280                                                                    & 1.4028          & 930                             & 3.1753                                                                    & 1.4151          \\
@@
 			diabetic                            & 930                                     & 3.2452                                                                    & 1.3050          & 930                            & 3.0720                                                                    & 1.3913          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7785}          & 1.4067          & 930                             & 3.0290                                                                    & 1.4249          & 930                             & 2.8753                                                                    & 1.4940          \\
-                  fish\_toxicity                      & 930                                     & 3.1452                                                                    & 1.3620          & 930                            & 3.0032                                                                    & 1.4455          & 930                             & 3.2172                                                                             & 1.3639          & 930                             & 3.1000                                                                    & 1.4088          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5344} & 1.3879          \\
-                  forest\_fires                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8398} & 1.3690          & 930                            & 3.1215                                                                    & 1.4707          & 930                             & 3.0043                                                                             & 1.3181          & 930                             & 2.8860                                                                    & 1.3535          & 930                             & 3.1484                                                                    & 1.5261          \\
+			fish toxicity                       & 930                                     & 3.1452                                                                    & 1.3620          & 930                            & 3.0032                                                                    & 1.4455          & 930                             & 3.2172                                                                             & 1.3639          & 930                             & 3.1000                                                                    & 1.4088          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5344} & 1.3879          \\
+			forest fires                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8398} & 1.3690          & 930                            & 3.1215                                                                    & 1.4707          & 930                             & 3.0043                                                                             & 1.3181          & 930                             & 2.8860                                                                    & 1.3535          & 930                             & 3.1484                                                                    & 1.5261          \\
 			housing                             & 930                                     & 3.3129                                                                    & 1.3107          & 930                            & 2.9892                                                                    & 1.3927          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6871}          & 1.4833          & 930                             & 2.6968                                                                    & 1.4965          & 930                             & 3.3140                                                                    & 1.2356          \\
@@
 			parkinsons                          & 930                                     & 2.9688                                                                    & 1.3850          & 930                            & 3.0086                                                                    & 1.3559          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6129}          & 1.4814          & 930                             & 3.1032                                                                    & 1.3804          & 930                             & 3.3065                                                                    & 1.3778          \\
-                  student\_performance                & 930                                     & 2.9409                                                                    & 1.4118          & 930                            & 3.1849                                                                    & 1.3804          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710}          & 1.4097          & 930                             & 3.1258                                                                    & 1.3655          & 930                             & 2.9774                                                                    & 1.4675          \\
-                  wine\_quality                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8032} & 1.4440          & 930                            & 2.9204                                                                    & 1.3042          & 930                             & 3.2022                                                                             & 1.4104          & 930                             & 2.9247                                                                    & 1.3491          & 930                             & 3.1495                                                                    & 1.5171          \\
+			student performance                 & 930                                     & 2.9409                                                                    & 1.4118          & 930                            & 3.1849                                                                    & 1.3804          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710}          & 1.4097          & 930                             & 3.1258                                                                    & 1.3655          & 930                             & 2.9774                                                                    & 1.4675          \\
+			wine quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8032} & 1.4440          & 930                            & 2.9204                                                                    & 1.3042          & 930                             & 3.2022                                                                             & 1.4104          & 930                             & 2.9247                                                                    & 1.3491          & 930                             & 3.1495                                                                    & 1.5171          \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying reanalysis window sizes per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reanalysis window sizes per dataset, across all runs and epochs.}
 	\label{fig:results:reanalysis:descriptive:descriptive}
@@
 	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying reanalysis window sizes across all datasets, runs and epochs.}
+	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reanalysis window sizes across all datasets, runs and epochs.}
 	\label{fig:results:reanalysis:descriptive:cd}
@@
 	\centering
-      \caption{Empirical results showcasing average rank and statistics for different \index{burn in}burn in values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different \index{burn in}burn in values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:burn_in:metrics}%
@@
 			\cmidrule{1-2}                      &                                      &                                                                                    &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
-                                                      & \multicolumn{1}{l}{\textbf{burn\_in}} & \multicolumn{1}{l}{\textbf{results}}                                               &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
+			                                    & \multicolumn{1}{l}{\textbf{burn in}} & \multicolumn{1}{l}{\textbf{results}}                                               &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
 			\cmidrule{2-3}                      & \textbf{0}                           &                                                                                    &                 & \textbf{5}     &                                                                           &                 & \textbf{10}    &                                                                           &                 & \textbf{15}    &                                                                           &                 & \textbf{20}    &                 &                 \\
@@
 			adult                               & 930                                  & 2.7366                                                                             & 1.4475          & 930            & 2.6430                                                                    & 1.3817          & 930            & 2.9892                                                                    & 1.4111          & 930            & 3.1731                                                                    & 1.4477          & 930            & 3.1355          & 1.4130          \\
-                  air\_quality                        & 930                                   & 2.9097                                                                             & 1.4408          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6817} & 1.4270          & 930            & 2.7699                                                                    & 1.3443          & 930            & 3.3720                                                                    & 1.3137          & 930            & 3.2667          & 1.4119          \\
+			air quality                         & 930                                  & 2.9097                                                                             & 1.4408          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6817} & 1.4270          & 930            & 2.7699                                                                    & 1.3443          & 930            & 3.3720                                                                    & 1.3137          & 930            & 3.2667          & 1.4119          \\
 			bike                                & 930                                  & 1.9237                                                                             & 0.9808          & 930            & 2.1806                                                                    & 1.0238          & 930            & 2.9237                                                                    & 1.2739          & 930            & 3.5054                                                                    & 1.1859          & 930            & 4.4667          & 0.8514          \\
 			car                                 & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3624}          & 1.2315          & 930            & 2.5882                                                                    & 1.4246          & 930            & 3.2978                                                                    & 1.3922          & 930            & 3.3796                                                                    & 1.2711          & 930            & 3.3720          & 1.4009          \\
-                  fish\_toxicity                      & 930                                   & 3.0634                                                                             & 1.4589          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7935} & 1.4021          & 930            & 2.8204                                                                    & 1.5131          & 930            & 3.1022                                                                    & 1.3461          & 930            & 3.2204          & 1.2949          \\
-                  forest\_fires                       & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8161}          & 1.3301          & 930            & 2.8495                                                                    & 1.3830          & 930            & 2.8645                                                                    & 1.4092          & 930            & 3.3774                                                                    & 1.3976          & 930            & 3.0925          & 1.4709          \\
+			fish toxicity                       & 930                                  & 3.0634                                                                             & 1.4589          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7935} & 1.4021          & 930            & 2.8204                                                                    & 1.5131          & 930            & 3.1022                                                                    & 1.3461          & 930            & 3.2204          & 1.2949          \\
+			forest fires                        & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8161}          & 1.3301          & 930            & 2.8495                                                                    & 1.3830          & 930            & 2.8645                                                                    & 1.4092          & 930            & 3.3774                                                                    & 1.3976          & 930            & 3.0925          & 1.4709          \\
 			housing                             & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6903}          & 1.3837          & 930            & 2.9516                                                                    & 1.3176          & 930            & 2.9968                                                                    & 1.4425          & 930            & 3.0581                                                                    & 1.3435          & 930            & 3.3032          & 1.5101          \\
@@
 			parkinsons                          & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2796}          & 1.2822          & 930            & 2.8892                                                                    & 1.2474          & 930            & 2.7065                                                                    & 1.3143          & 930            & 3.3968                                                                    & 1.4175          & 930            & 3.7280          & 1.3295          \\
-                  student\_performance                & 930                                   & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1452}          & 1.2052          & 930            & 2.6946                                                                    & 1.4032          & 930            & 3.0968                                                                    & 1.3525          & 930            & 3.4581                                                                    & 1.3539          & 930            & 3.6054          & 1.2312          \\
-                  wine\_quality                       & 930                                   & 2.9699                                                                             & 1.4373          & 930            & 3.0108                                                                    & 1.3041          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6634} & 1.4186          & 930            & 3.1247                                                                    & 1.3980          & 930            & 3.2312          & 1.4471          \\
+			student performance                 & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1452}          & 1.2052          & 930            & 2.6946                                                                    & 1.4032          & 930            & 3.0968                                                                    & 1.3525          & 930            & 3.4581                                                                    & 1.3539          & 930            & 3.6054          & 1.2312          \\
+			wine quality                        & 930                                  & 2.9699                                                                             & 1.4373          & 930            & 3.0108                                                                    & 1.3041          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6634} & 1.4186          & 930            & 3.1247                                                                    & 1.3980          & 930            & 3.2312          & 1.4471          \\
 			bank                                & 930                                  & 2.7301                                                                             & 1.3210          & 930            & 2.8194                                                                    & 1.3350          & 930            & 2.8570                                                                    & 1.4848          & 930            & 2.9312                                                                    & 1.3841          & 930            & 3.6624          & 1.3391          \\
@@
 	\includegraphics[width=\textwidth]{bhh_burn_in/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots between the average ranks of the \acs{BHH} with varying burn in values per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying burn in values per dataset, across all runs and epochs.}
 	\label{fig:results:burn_in:descriptive:descriptive}
@@
 	\includegraphics[width=\textwidth]{bhh_burn_in/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with varying burn in values across all datasets, runs and epochs.}
+	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying burn in values across all datasets, runs and epochs.}
 	\label{fig:results:burn_in:descriptive:cd}
@@
 	\centering
-      \caption{Empirical results showcasing average rank and statistics for \index{normalisation}normalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for \index{normalisation}normalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:normalise:metrics}%
 	\par\bigskip
-      \resizebox{\textwidth}{!}{
+	\resizebox{0.75\textwidth}{!}{
 		\begin{tabular}{rcccccc}
@@
 			                                   & \multicolumn{1}{l}{\textbf{normalisation}} & \multicolumn{1}{l}{\textbf{metric}}                                                &                 &                                   &                                                                           &                 \\
-                  \cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{FALSE}}         &                                                                                    &                 & \multicolumn{1}{l}{\textbf{TRUE}} &                                                                           &                 \\
+			\cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{false}}         &                                                                                    &                 & \multicolumn{1}{l}{\textbf{true}} &                                                                           &                 \\
 			\cmidrule{2-7}    \textbf{dataset} & \textbf{count}                             & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
@@
 			adult                              & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4710}          & 0.4994          & 930                               & 1.4968                                                                    & 0.5003          \\
-                  air\_quality                       & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4892}          & 0.5002          & 930                               & 1.5108                                                                    & 0.5002          \\
+			air quality                        & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4892}          & 0.5002          & 930                               & 1.5108                                                                    & 0.5002          \\
 			bank                               & 930                                        & 1.5484                                                                             & 0.4979          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4516} & 0.4979          \\
@@
 			diabetic                           & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4753}          & 0.4997          & 930                               & 1.5247                                                                    & 0.4997          \\
-                  fish\_toxicity                     & 930                                        & 1.5505                                                                             & 0.4977          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4495} & 0.4977          \\
-                  forest\_fires                      & 930                                        & 1.5054                                                                             & 0.5002          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4946} & 0.5002          \\
+			fish toxicity                      & 930                                        & 1.5505                                                                             & 0.4977          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4495} & 0.4977          \\
+			forest fires                       & 930                                        & 1.5054                                                                             & 0.5002          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4946} & 0.5002          \\
 			housing                            & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4720}          & 0.4995          & 930                               & 1.5280                                                                    & 0.4995          \\
@@
 			parkinsons                         & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4000}          & 0.4902          & 930                               & 1.6000                                                                    & 0.4902          \\
-                  student\_performance               & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3892}          & 0.4878          & 930                               & 1.6108                                                                    & 0.4878          \\
-                  wine\_quality                      & 930                                        & 1.5473                                                                             & 0.4980          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4527} & 0.4980          \\
+			student performance                & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3892}          & 0.4878          & 930                               & 1.6108                                                                    & 0.4878          \\
+			wine quality                       & 930                                        & 1.5473                                                                             & 0.4980          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4527} & 0.4980          \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_normalise/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots between the average ranks of the \acs{BHH} with normalisation toggled per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with normalisation toggled per dataset, across all runs and epochs.}
 	\label{fig:results:normalise:descriptive:descriptive}
@@
 	\includegraphics[width=\textwidth]{bhh_normalise/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with normalisation toggled across all datasets, runs and epochs.}
+	\caption{Critical difference plots for the average ranks of the \acs{BHH} with normalisation toggled across all datasets, runs and epochs.}
 	\label{fig:results:normalise:descriptive:cd}
@@
 	\centering
-      \caption{Empirical results showcasing average rank and statistics for \index{discounted rewards}discounted rewards toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for \index{discounted rewards}discounted rewards toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:discounted_rewards:metrics}%
 	\par\bigskip
-      \resizebox{\textwidth}{!}{
+	\resizebox{0.85\textwidth}{!}{
 		\begin{tabular}{rcccccc}
@@
 			\cmidrule{1-2}                     &                                                 &                                                                                    &                 &                                   &                                                                           &                 \\
-                                                     & \multicolumn{1}{l}{\textbf{dr}}    & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                   &                                                                           &                 \\
+			                                   & \multicolumn{1}{l}{\textbf{discounted rewards}} & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                   &                                                                           &                 \\
 			\cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{FALSE}}              &                                                                                    &                 & \multicolumn{1}{l}{\textbf{TRUE}} &                                                                           &                 \\
@@
 			adult                              & 930                                             & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4645} & 0.4990          \\
-                  air\_quality                       & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4613}          & 0.4988          & 930                               & 1.5387                                                                    & 0.4988          \\
+			air quality                        & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4613}          & 0.4988          & 930                               & 1.5387                                                                    & 0.4988          \\
 			bank                               & 930                                             & 1.5161                                                                             & 0.5000          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4839} & 0.5000          \\
@@
 			diabetic                           & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4699}          & 0.4994          & 930                               & 1.5301                                                                    & 0.4994          \\
-                  fish\_toxicity                     & 930                                & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
-                  forest\_fires                      & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4742}          & 0.4996          & 930                               & 1.5258                                                                    & 0.4996          \\
+			fish toxicity                      & 930                                             & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
+			forest fires                       & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4742}          & 0.4996          & 930                               & 1.5258                                                                    & 0.4996          \\
 			housing                            & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4237}          & 0.4944          & 930                               & 1.5763                                                                    & 0.4944          \\
@@
 			parkinsons                         & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3710}          & 0.4833          & 930                               & 1.6290                                                                    & 0.4833          \\
-                  student\_performance               & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4398}          & 0.4966          & 930                               & 1.5602                                                                    & 0.4966          \\
-                  wine\_quality                      & 930                                & 1.5570                                                                             & 0.4970          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4430} & 0.4970          \\
+			student performance                & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4398}          & 0.4966          & 930                               & 1.5602                                                                    & 0.4966          \\
+			wine quality                       & 930                                             & 1.5570                                                                             & 0.4970          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4430} & 0.4970          \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots between the average ranks of the \acs{BHH} with discounted rewards toggled per datasets, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with discounted rewards toggled per datasets, across all runs and epochs.}
 	\label{fig:results:discounted_rewards:descriptive:descriptive}
@@
 	\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/cd/overall.pdf}
-      \caption{Critical Difference plots between the average ranks of the \acs{BHH} with discounted rewards toggled across all datasets, runs and epochs.}
+	\caption{Critical difference plots for the average ranks of the \acs{BHH} with discounted rewards toggled across all datasets, runs and epochs.}
 	\label{fig:results:discounted_rewards:descriptive:cd}

### 2022-11-11 scripts/analyse.py

@@ -268,9 +268,10 @@ def setup_seaborn():
 	global PALETTE
 	global PARAM_COUNT
 	# Setup Plots
-	sns.set_context('paper',  font_scale=1.5, rc={'lines.linewidth': 2, 'lines.markersize': 5})
+	sns.set_context('paper',  font_scale=1.5, rc={'lines.linewidth': 1, 'lines.markersize': 3})
+	PALETTE = sns.color_palette('hls', PARAM_COUNT)
 	# PALETTE = sns.color_palette('viridis', PARAM_COUNT)
-	PALETTE = sns.color_palette('mako_r', PARAM_COUNT)
+	# PALETTE = sns.color_palette('mako_r', PARAM_COUNT)
 
 def plot(train: bool = False, accuracy = False):
 	global DATA
@@ -306,10 +307,11 @@ def plot(train: bool = False, accuracy = False):
 				hue=COLUMN,
 				style_order=ORDER,
 				style=COLUMN,
-				markers=False,
+				markers=True,
 				dashes=False,
 				ax=ax,
-				palette=PALETTE
+				palette=PALETTE,
+				markeredgecolor=None
 			)
 
 			plot.set_xlabel("Epoch")

### 2022-11-11 dissertation/chapters/08-results.tex
✏️ (results): Fixing header of plots

@@
 
-	\item \textbf{Section \ref{sec:results:bhh_vs_low_level_heuristics}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics as it relates to all datasets.
+	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics as it relates to all datasets.
 Three variants of the \acs{BHH} are included in these results.
@@
 
-	\item \textbf{Section \ref{sec:results:bhh_variant_hp}} provides the results for the experimental group that analyses the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_population}} provides the results for the experimental group that analyses the effects of the \textit{population size} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_replay}} provides the results for the experimental group that analyses the effects of the \textit{replay window size} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_reanalysis}} provides the results for the experimental group that analyses the effects of the \textit{reanalysis interval} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_normalise}} provides the results for the experimental group that analyses the effects of the \textit{normalisation} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_discounted_rewards}} provides the results for the experimental group that analyses the effects of the \textit{discounted rewards} hyper-parameter on the outcomes of the \acs{BHH}.
+	\item \textbf{Section \ref{sec:results:heuristic_pool}} provides the results for the experimental group that analyses the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:population}} provides the results for the experimental group that analyses the effects of the \textit{population size} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:replay}} provides the results for the experimental group that analyses the effects of the \textit{replay window size} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:reanalysis}} provides the results for the experimental group that analyses the effects of the \textit{reanalysis interval} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:normalise}} provides the results for the experimental group that analyses the effects of the \textit{normalisation} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:discounted_rewards}} provides the results for the experimental group that analyses the effects of the \textit{discounted rewards} hyper-parameter on the outcomes of the \acs{BHH}.
 
@@
 	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
-	\caption{The average training loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average training loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:train_loss}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
-	\caption{The average test loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average test loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:test_loss}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
-	\caption{The average training accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average training accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:train_accuracy}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
-	\caption{The average test accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average test accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:test_accuracy}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:8}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$, sampled from the probability distribution $P(\theta_{0} \vert \alpha_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$, sampled from the probability distribution $P(\theta_{0} \vert \alpha_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$, sampled from the probability distribution $P(\theta_{6} \vert \alpha_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$, sampled from the probability distribution $P(\theta_{6} \vert \alpha_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$, sampled from the probability distribution $P(\theta_{7} \vert \alpha_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$, sampled from the probability distribution $P(\theta_{7} \vert \alpha_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$, sampled from the probability distribution $P(\theta_{8} \vert \alpha_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$, sampled from the probability distribution $P(\theta_{8} \vert \alpha_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:8}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$, sampled from the prior selection probability distribution $P(h_{0} \vert \theta_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$, sampled from the prior selection probability distribution $P(h_{0} \vert \theta_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$, sampled from the prior selection probability distribution $P(h_{6} \vert \theta_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$, sampled from the prior selection probability distribution $P(h_{6} \vert \theta_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$, sampled from the prior selection probability distribution $P(h_{7} \vert \theta_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$, sampled from the prior selection probability distribution $P(h_{7} \vert \theta_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$, sampled from the prior selection probability distribution $P(h_{8} \vert \theta_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$, sampled from the prior selection probability distribution $P(h_{8} \vert \theta_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:8}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:8}
@@
 
-\section{BHH vs. Low-Level Heuristics}\label{sec:results:bhh_vs_low_level_heuristics}
+\section{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
 
@@
 
-\section{Heuristic Pool}\label{sec:results:bhh_variant_hp}
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/train/loss/iris.pdf}
+		\caption{Train log loss}
+		\label{fig:results:standalone:figures:loss:train:iris}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/iris.pdf}
+		\caption{Test log loss}
+		\label{fig:results:standalone:figures:loss:test:iris}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/iris.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:standalone:figures:accuracy:train:iris}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/iris.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:standalone:figures:accuracy:test:iris}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:standalone:figures:iris}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/train/loss/bank.pdf}
+		\caption{Train log loss}
+		\label{fig:results:standalone:figures:loss:train:bank}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/bank.pdf}
+		\caption{Test log loss}
+		\label{fig:results:standalone:figures:loss:test:bank}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/bank.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:standalone:figures:accuracy:train:bank}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/bank.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:standalone:figures:accuracy:test:bank}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:standalone:figures:bank}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
+		\caption{Train log loss}
+		\label{fig:results:standalone:figures:loss:train:car}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
+		\caption{Test log loss}
+		\label{fig:results:standalone:figures:loss:test:car}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:standalone:figures:accuracy:train:car}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:standalone:figures:accuracy:test:car}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the car dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:standalone:figures:car}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/train/loss/fish_toxicity.pdf}
+		\caption{Train log loss}
+		\label{fig:results:standalone:figures:loss:train:fish_toxicity}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/fish_toxicity.pdf}
+		\caption{Test log loss}
+		\label{fig:results:standalone:figures:loss:test:fish_toxicity}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test loss plot for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:standalone:figures:fish_toxicity}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/train/loss/parkinsons.pdf}
+		\caption{Train log loss}
+		\label{fig:results:standalone:figures:loss:train:parkinsons}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/parkinsons.pdf}
+		\caption{Test log loss}
+		\label{fig:results:standalone:figures:loss:test:parkinsons}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test loss plot for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:standalone:figures:parkinsons}
+\end{figure}
+
+\section{Heuristic Pool}\label{sec:results:heuristic_pool}
 
@@
 
-\section{Population Size}\label{sec:results:bhh_variant_population}
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/loss/abalone.pdf}
+		\caption{Train log loss}
+		\label{fig:results:heuristic_pool:figures:loss:train:abalone}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/abalone.pdf}
+		\caption{Test log loss}
+		\label{fig:results:heuristic_pool:figures:loss:test:abalone}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/accuracy/abalone.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:heuristic_pool:figures:accuracy:train:abalone}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/accuracy/abalone.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:heuristic_pool:figures:accuracy:test:abalone}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the abalone dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:heuristic_pool:figures:abalone}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/loss/forest_fires.pdf}
+		\caption{Train log loss}
+		\label{fig:results:heuristic_pool:figures:loss:train:forest_fires}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/forest_fires.pdf}
+		\caption{Test log loss}
+		\label{fig:results:heuristic_pool:figures:loss:test:forest_fires}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test loss plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the forest fires dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:heuristic_pool:figures:forest_fires}
+\end{figure}
+
+\section{Population Size}\label{sec:results:population}
 
@@
 
-\section{Credit Assignment Strategy}\label{sec:results:bhh_variant_credit}
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_population/figures/train/loss/mushroom.pdf}
+		\caption{Train log loss}
+		\label{fig:results:population:figures:loss:train:mushroom}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/mushroom.pdf}
+		\caption{Test log loss}
+		\label{fig:results:population:figures:loss:test:mushroom}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_population/figures/train/accuracy/mushroom.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:population:figures:accuracy:train:mushroom}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_population/figures/test/accuracy/mushroom.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:population:figures:accuracy:test:mushroom}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:population:figures:mushroom}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_population/figures/train/loss/student_performance.pdf}
+		\caption{Train log loss}
+		\label{fig:results:population:figures:loss:train:student_performance}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/student_performance.pdf}
+		\caption{Test log loss}
+		\label{fig:results:population:figures:loss:test:student_performance}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the student performance dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:population:figures:student_performance}
+\end{figure}
+
+\section{Credit Assignment Strategy}\label{sec:results:credit}
 
@@
 
-\section{Reselection Interval}\label{sec:results:bhh_variant_reselection}
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/bank.pdf}
+		\caption{Train log loss}
+		\label{fig:results:credit:figures:loss:train:bank}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/bank.pdf}
+		\caption{Test log loss}
+		\label{fig:results:credit:figures:loss:test:bank}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_credit/figures/train/accuracy/bank.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:credit:figures:accuracy:train:bank}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_credit/figures/test/accuracy/bank.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:credit:figures:accuracy:test:bank}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the bank dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:credit:figures:bank}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/housing.pdf}
+		\caption{Train log loss}
+		\label{fig:results:credit:figures:loss:train:housing}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/housing.pdf}
+		\caption{Test log loss}
+		\label{fig:results:credit:figures:loss:test:housing}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the housing dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:credit:figures:housing}
+\end{figure}
+
+\section{Reselection Interval}\label{sec:results:reselection}
 
@@
 
-\section{Replay Window Size}\label{sec:results:bhh_variant_replay}
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/car.pdf}
+		\caption{Train log loss}
+		\label{fig:results:reselection:figures:loss:train:car}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/car.pdf}
+		\caption{Test log loss}
+		\label{fig:results:reselection:figures:loss:test:car}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/accuracy/car.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:reselection:figures:accuracy:train:car}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/accuracy/car.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:reselection:figures:accuracy:test:car}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the car dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:reselection:figures:car}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/bike.pdf}
+		\caption{Train log loss}
+		\label{fig:results:reselection:figures:loss:train:bike}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/bike.pdf}
+		\caption{Test log loss}
+		\label{fig:results:reselection:figures:loss:test:bike}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the bike dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:reselection:figures:bike}
+\end{figure}
+
+\section{Replay Window Size}\label{sec:results:replay}
 
@@
 
-\section{Reanalysis Interval}\label{sec:results:bhh_variant_reanalysis}
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/diabetic.pdf}
+		\caption{Train log loss}
+		\label{fig:results:replay:figures:loss:train:diabetic}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/diabetic.pdf}
+		\caption{Test log loss}
+		\label{fig:results:replay:figures:loss:test:diabetic}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_replay/figures/train/accuracy/diabetic.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:replay:figures:accuracy:train:diabetic}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_replay/figures/test/accuracy/diabetic.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:replay:figures:accuracy:test:diabetic}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:replay:figures:diabetic}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/fish_toxicity.pdf}
+		\caption{Train log loss}
+		\label{fig:results:replay:figures:loss:train:fish_toxicity}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/fish_toxicity.pdf}
+		\caption{Test log loss}
+		\label{fig:results:replay:figures:loss:test:fish_toxicity}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:replay:figures:fish_toxicity}
+\end{figure}
+
+\section{Reanalysis Interval}\label{sec:results:reanalysis}
 
@@
 
-\section{Burn In}\label{sec:results:bhh_variant_burn_in}
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/mushroom.pdf}
+		\caption{Train log loss}
+		\label{fig:results:reanalysis:figures:loss:train:mushroom}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/mushroom.pdf}
+		\caption{Test log loss}
+		\label{fig:results:reanalysis:figures:loss:test:mushroom}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/accuracy/mushroom.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:reanalysis:figures:accuracy:train:mushroom}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/accuracy/mushroom.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:reanalysis:figures:accuracy:test:mushroom}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:reanalysis:figures:mushroom}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/parkinsons.pdf}
+		\caption{Train log loss}
+		\label{fig:results:reanalysis:figures:loss:train:parkinsons}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/parkinsons.pdf}
+		\caption{Test log loss}
+		\label{fig:results:reanalysis:figures:loss:test:parkinsons}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:reanalysis:figures:parkinsons}
+\end{figure}
+
+\section{Burn In}\label{sec:results:burn_in}
 
@@
 
-The critical difference plot as presented in Figure \ref{fig:results:burn_in:descriptive:cd} shows the statistical significance between burn in window sizes overall, across all datasets.
-One can clearly see from this plot that little to no burn in is preferred in most of the cases.
-
 \begin{figure}[htbp]
@@
 
-\section{Normalisation}\label{sec:results:bhh_variant_normalise}
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_burn_in/figures/train/loss/mushroom.pdf}
+		\caption{Train log loss}
+		\label{fig:results:burn_in:figures:loss:train:mushroom}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/mushroom.pdf}
+		\caption{Test log loss}
+		\label{fig:results:burn_in:figures:loss:test:mushroom}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_burn_in/figures/train/accuracy/mushroom.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:burn_in:figures:accuracy:train:mushroom}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_burn_in/figures/test/accuracy/mushroom.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:burn_in:figures:accuracy:test:mushroom}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:burn_in:figures:mushroom}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_burn_in/figures/train/loss/parkinsons.pdf}
+		\caption{Train log loss}
+		\label{fig:results:burn_in:figures:loss:train:parkinsons}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/parkinsons.pdf}
+		\caption{Test log loss}
+		\label{fig:results:burn_in:figures:loss:test:parkinsons}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:burn_in:figures:parkinsons}
+\end{figure}
+
+\section{Normalisation}\label{sec:results:normalise}
 
@@
 
-\section{Discounted Rewards}\label{sec:results:bhh_variant_discounted_rewards}
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_normalise/figures/train/loss/abalone.pdf}
+		\caption{Train log loss}
+		\label{fig:results:normalise:figures:loss:train:abalone}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/abalone.pdf}
+		\caption{Test log loss}
+		\label{fig:results:normalise:figures:loss:test:abalone}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_normalise/figures/train/accuracy/abalone.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:normalise:figures:accuracy:train:abalone}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_normalise/figures/test/accuracy/abalone.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:normalise:figures:accuracy:test:abalone}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the abalone dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:normalise:figures:abalone}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_normalise/figures/train/loss/bike.pdf}
+		\caption{Train log loss}
+		\label{fig:results:normalise:figures:loss:train:bike}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/bike.pdf}
+		\caption{Test log loss}
+		\label{fig:results:normalise:figures:loss:test:bike}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the bike dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:normalise:figures:bike}
+\end{figure}
+
+\section{Discounted Rewards}\label{sec:results:discounted_rewards}
 
@@
 
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/loss/wine_quality.pdf}
+		\caption{Train log loss}
+		\label{fig:results:discounted_rewards:figures:loss:train:wine_quality}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/wine_quality.pdf}
+		\caption{Test log loss}
+		\label{fig:results:discounted_rewards:figures:loss:test:wine_quality}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/accuracy/wine_quality.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:discounted_rewards:figures:accuracy:train:wine_quality}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/accuracy/wine_quality.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:discounted_rewards:figures:accuracy:test:wine_quality}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the wine quality dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:discounted_rewards:figures:wine_quality}
+\end{figure}
+
+\begin{figure}[htbp]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/loss/housing.pdf}
+		\caption{Train log loss}
+		\label{fig:results:discounted_rewards:figures:loss:train:housing}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/housing.pdf}
+		\caption{Test log loss}
+		\label{fig:results:discounted_rewards:figures:loss:test:housing}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the housing dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:discounted_rewards:figures:housing}
+\end{figure}
+
 \section{Overfitting}\label{sec:results:overfitting}

### 2022-11-14 dissertation/chapters/08-results.tex
🚧 (results): WIP writing up findings

--- 2022-11-11 dissertation/chapters/08-results.tex
@@
 
-\noindent
-All the required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}.
+The required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}.
 The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}.
-The methodology presented a number of experiments to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics.
+The methodology presented a number of experimental groups to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics.
 The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.
@@
 Discussions are accompanied by figures and plots to help provide visual aid for the discussions.
-The output of the statistical analysis that yielded the results presented in the chapter is provided in Appendix~\ref{app:statistical_analysis}.
+The output of the statistical analysis that yielded the results that is presented in the chapter is provided in Appendix~\ref{app:statistical_analysis}.
 The remainder of the chapter is structured as follows.
@@
 	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}.
-Illustrations are provided to show the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.
-
-	\item \textbf{Section \ref{sec:results:bhh_vs_low_level_heuristics}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics as it relates to all datasets.
+Illustrations are provided to show the change in parameter values to illustrate the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.
+
+	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics as it relates to all datasets.
 Three variants of the \acs{BHH} are included in these results.
@@
 
-	\item \textbf{Section \ref{sec:results:bhh_variant_hp}} provides the results for the experimental group that analyses the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_population}} provides the results for the experimental group that analyses the effects of the \textit{population size} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_replay}} provides the results for the experimental group that analyses the effects of the \textit{replay window size} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_reanalysis}} provides the results for the experimental group that analyses the effects of the \textit{reanalysis interval} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_normalise}} provides the results for the experimental group that analyses the effects of the \textit{normalisation} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:bhh_variant_discounted_rewards}} provides the results for the experimental group that analyses the effects of the \textit{discounted rewards} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:overfitting}} provides a brief discussion on overfitting as it is observed for some of the empirical tests.
+	\item \textbf{Section \ref{sec:results:heuristic_pool}} provides the results for the experimental group that analyses the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:population}} provides the results for the experimental group that analyses the effects of the \textit{population size} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:replay}} provides the results for the experimental group that analyses the effects of the \textit{replay window size} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:reanalysis}} provides the results for the experimental group that analyses the effects of the \textit{reanalysis interval} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:normalise}} provides the results for the experimental group that analyses the effects of the \textit{normalisation} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:discounted_rewards}} provides the results for the experimental group that analyses the effects of the \textit{discounted rewards} hyper-parameter on the outcomes of the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:divergence}} provides a brief discussion on divergence as it is observed for some of the empirical tests.
 
@@
 \section{Behavioural Case Study}\label{sec:results:case_study}
+
+This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset.
+As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records.
+The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process.
+Some noisiness can be expected as mini-batch training is executed with batch sizes of 30.
+The results that are presented are averaged over 30 independent runs.
+
+Furthermore, the case study focuses on three different variants of the \acs{BHH}.
+These include the baseline configuration as was provided in Chapter~\ref{chap:bhh}, as well as a configuration that includes a ``long memory'' by setting the replay window size to 250, and a configuration that makes use of the \textit{symmetric} credit assignment strategy.
+These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment is chosen to illustrate a case where there \acs{BHH} does not reward good performance and does not yield a bias towards \index{heuristic}heuristics that perform well.
+This section is structured as follows.
+
+\begin{itemize}
+	\item \textbf{Section \ref{sec:results:case_study:performance_metrics}} provides illustrations and discussions around the outcomes of the performance metrics as obtained by the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:case_study:concentration_parameters}} provides illustrations and discussions around the changes in concentration parameter values as a result of the learning process implemented by the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probabilities of \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:case_study:prior_selec_prob}} provides illustrations and discussions around the changes in the \textit{prior \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:case_study:posterior_selec_prob}} provides illustrations and discussions around the changes in the \textit{posterior \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.
+
+\end{itemize}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Performance metrics}\label{sec:results:case_study:performance_metrics}
+
+Figures~\ref{fig:results:case_study:train_loss}-\ref{fig:results:case_study:test_accuracy} provide illustrations of the train and test, loss and accuracy plots over 30 epochs and is illustrated in log scale.
+The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}.
+The noisiness that results from mini-batch training can be observed in Figure~\ref{fig:results:case_study:test_loss}.
+Figures~\ref{fig:results:case_study:train_accuracy} and~\ref{fig:results:case_study:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%.
+Although the \acs{BHH} was able to succesfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.
+However, it should be noted from epochs 5 and onwards presented in Figure~\ref{fig:results:case_study:test_accuracy} that all the configurations of the \acs{BHH} was able to ``undo'' selections that yielded worse test loss results in the previous epoch.
+The sporadic, oscillating nature of the results later in the training process is simply a result of momentum that is maintained between low-level \index{heuristic}heuristics.
+For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions.
+The \acs{BHH} does not incorporate a \textit{move acceptance} strategy, whereby a heuristic's outcome is rejected if it does not improve on previous results, yielding a possibly worse loss measurement.
+A move acceptance strategy can be utilised on a validation set as a mechanism to approve or reject heuristic progressions from one step to the other.
+
+Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figures~\ref{fig:results:case_study:train_loss}-\ref{fig:results:case_study:test_accuracy} only provide the outcomes of performance metrics at the end of each epoch.
+Further investigation is required at a mini-batch step level.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PARAMS ALPHAS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % PARAMS ALPHAS
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}
+
+To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
+Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, from which prior \textit{probabilities of selection probabilities} are sampled.
+Figures~\ref{fig:results:case_study:alpha:0}-\ref{fig:results:case_study:alpha:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, 8 respectively.
+Index 0, 6, 7, 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively and only represent a subset of the concentration parameters in $\boldsymbol{\alpha}$ and the \index{heuristic pool}heuristic pool.
+Simular illustrations for the other indices in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
 
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:8}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PARAMS THETAS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The first logical observation to be made from Figures~\ref{fig:results:case_study:alpha:0}-\ref{fig:results:case_study:alpha:8} is the step-wise increasing nature of $\boldsymbol{\alpha}$ for the long memory configuration (denoted \textit{bhh\_replay\_250}), illustrated in green.
+Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics.
+The values in $\boldsymbol{\alpha}$ is never reset to its initial value of 1, and thus $\boldsymbol{\alpha}$ continues to increase throughout the training process.
+However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$.
+The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}.
+Heuristics that perform will will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.
+
+The next observation that can be made is for the baseline configuration (denoted \textit{bhh\_baseline}) in red, and the symmetric credit assignment strategy configuration (denoted \textit{bhh\_credit\_symmetric}) in blue.
+Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1 as regular intervals.
+This interval is represented by the \textit{reanalysis} window size.
+The reanalysis window size dictates the frequency at which Bayesian analysis is conducated on the performance log, mainted by the \acs{BHH}.
+Bayesian analysis is used to update $\boldsymbol{\alpha}$.
+As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.
+Notice that $\boldsymbol{\alpha} \geq 1$ for multiple indices, even after reanalysis.
+This is because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1 at the corresponding index in $\boldsymbol{\alpha}$ through the Bayesian analysis process.
+In a case where all 5 entities in the entity pool are allocated the same heuristic, for all 10 steps in the reanalysis windown, $\boldsymbol{\alpha} = 50$.
+
+Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning.
+The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurance} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
+\index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the probabilistic sampling nature of the \acs{BHH}.
+Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % PARAMS THETAS
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Probabilities of Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
+
+This section provides a detailed investigation into the \textit{probabilities of selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process.
+As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves.
+The probability distribution of \index{heuristic}heuristic selection probabilities is denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
+
+Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8} provide illustrations of the probabilities of the selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
+These illustrations are presented in log scale.
+Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at index 0, 6, 7, 8 represent the probabilities of selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and the \index{heuristic pool}heuristic pool.
+Once again, simular illustrations for the other indices in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
+
+From the illustrations presented in Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8}, a clearer picture off the learning process of the \acs{BHH} is formed.
+The first important observation to make is for the bhh\_replay\_250 configuration, presented in green.
+As a reminder, 10 low-level \index{heuristic}heuristics are included in the heuristic pool, yielding a probability of selection probability of 0.1 for each \index{heuristic}heuristic by the frequentist view of probabilistic modeling.
+Towards the end of the training process, the probability of selection probability converges back to the symmetrical, uniform probability distribution, yielding a probability of selection probability of 0.1 per \index{heuristic}heuristic.
+This can be explained as follows: most of the training progress is made in the early stages of the training process, and training stagnates towards the end of the training process.
+Since training stagnates, all heuristics, no matter their past performances, struggle to yield better solutions towards the end of the training process.
+As a result of stagnation, heuristics then struggle to yield credit allocations by means of the credit assignment strategy.
+In the case study experimental group, both the bhh\_baseline and bhh\_replay\_250 configurations make use of the \textit{ibest} credit assignment strategy.
+The \textit{ibest} credit assignment strategy allocates credit to the heuristic that provided the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
+However, since the bhh\_baseline has a short reanalysis interval, the concentration parameter $\boldsymbol{\alpha}$ gets reset to its default value of 1 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is less narrow and thus explaining the larger variance of $\boldsymbol{\theta}$ throughout.
+
+Another observation to make occurs in the first 30 steps of the training process.
+Notice how all three configurations mostly yield the same probabilities of selection probabilities in these first 30 steps.
+This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same runs.
+This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches.
+This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.
+It should be noted that, despite using the same random seed across configurations for the same runs, after about 30 steps, the behavioural changes between the configurations start the show.
+As a reminder, the bhh\_credit\_symmetric configuration, does not bias towards best performing \index{heuristic}heuristics and thus, where the bhh\_baseline and bhh\_replay\_250 configurations diverge from the behaviour of the bhh\_credit\_symmetric configuration, the difference in behaviour is proof of the effect of performance bias.
+
+Finally, despite divergence in behaviour, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar sporadic behaviour, much more so than with the bhh\_replay\_250 configuration.
+This can be attributed to a very small reanalysis window that contains very few samples to learn from (N=10).
+A small reanalysis window allows for more exploration, but can also yield greater variance of the probabilities of selection probabilities.
+Once again, any differences then in the behaviour of the  bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations.
 
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$, sampled from the probability distribution $P(\theta_{0} \vert \alpha_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$.
+The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{0} \vert \alpha_{0})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$, sampled from the probability distribution $P(\theta_{6} \vert \alpha_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$.
+The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{6} \vert \alpha_{6})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$, sampled from the probability distribution $P(\theta_{7} \vert \alpha_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$.
+The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{7} \vert \alpha_{7})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$, sampled from the probability distribution $P(\theta_{8} \vert \alpha_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$.
+The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{8} \vert \alpha_{8})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:8}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PARAMS P_H (Priors)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % PARAMS P_H (Priors)
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Prior Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}
+
+This section provides a brief investigation into the \textit{prior selection probabilities}, that results from the probabilistic model implemented by the \acs{BHH}.
+The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
+
+Figures~\ref{fig:results:case_study:p_H:0}-\ref{fig:results:case_study:p_H:8} provide illustrations of the \index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$ throughout the training process, and averaged over all 30 runs.
+Similar to before, these illustrations are also presented in log scale.
+The main observation to make from these figures is that they are much less sporafic than the figures presented for the probabilities of selection probabilities.
+This is because of the \textit{reselection} interval hyper-parameter.
+A reselection interval hyper-parameter is introduces to control the frequency by which new heuristics are allocated to each entity.
+Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10.
+These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8} for the probabilities of selection probabilities.
+As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
+
+Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of \index{heuristic}heuristic performances.
+Since these prior selection probabilities change over time, it can be concludes that the change in prior selection probabilities is a result of the learning mechanism of the \acs{BHH}.
+Furthermore, these prior selection probability distributions provide an opportunity to utilise prior knowledge by some expert to inject heuristic selection biases, even before training starts.
 
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$, sampled from the prior selection probability distribution $P(h_{0} \vert \theta_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$.
+The prior selection probability is sampled from the prior selection probability distribution, denoted $P(h_{0} \vert \theta_{0})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$, sampled from the prior selection probability distribution $P(h_{6} \vert \theta_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$.
+The prior selection probability is sampled from the prior selection probability distribution, denoted $P(h_{6} \vert \theta_{6})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$, sampled from the prior selection probability distribution $P(h_{7} \vert \theta_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$.
+The prior selection probability is sampled from the prior selection probability distribution, denoted $P(h_{7} \vert \theta_{7})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$, sampled from the prior selection probability distribution $P(h_{8} \vert \theta_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$.
+The prior selection probability is sampled from the prior selection probability distribution, denoted $P(h_{8} \vert \theta_{8})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:8}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PARAMS P_HgEC (Posterior)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % PARAMS P_HgEC (Posterior)
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Posterior Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}
+
+TODO
 
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
+The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{0} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
+The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{6} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
+The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{7} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
+	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
+The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{8} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:8}
@@
 
-\section{BHH vs. Low-Level Heuristics}\label{sec:results:bhh_vs_low_level_heuristics}
-
-% Table generated by Excel2LaTeX from sheet 'results - test - loss'
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
-	\label{tab:results:standalone:metrics:test_loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rlccc|c|c|c|c|c|ccccc}
-			epoch                                                                          & 30                 &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
-			                                                                               &                    &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
-			                                                                               &                    & \multicolumn{1}{l}{\textbf{heuristic}}                                         &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
-			\cmidrule{3-3}\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}    \textbf{dataset} & \textbf{statistic} & \textbf{adagrad}                                                               & \textbf{adam}                                                                  & \textbf{nag}                                                                   & \textbf{bhh\_gd}                                & \textbf{rmsprop}                                                               & \textbf{bhh\_all}                               & \textbf{adadelta}                                                              & \textbf{bhh\_mh}                                & \textbf{ga}                                     & \textbf{sgd}                                    & \textbf{pso}                                    & \textbf{momentum}                               & \textbf{de}                                     \\
-			\midrule
-			abalone                                                                        & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .506,  .776,  .486}1.967785                                   & \cellcolor[rgb]{ .494,  .773,  .486}1.965134827                                & \cellcolor[rgb]{ .765,  .851,  .502}2.0156043                                  & \cellcolor[rgb]{ .749,  .847,  .502}2.012517173 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{1.94553315}  & \cellcolor[rgb]{ 1,  .922,  .518}2.058704583    & \cellcolor[rgb]{ .788,  .859,  .502}2.019921077                                & \cellcolor[rgb]{ .996,  .827,  .502}2.29420573  & \cellcolor[rgb]{ .984,  .612,  .459}2.81545685  & \cellcolor[rgb]{ .992,  .773,  .49}2.42804241   & \cellcolor[rgb]{ .98,  .522,  .443}3.038417873  & \cellcolor[rgb]{ .992,  .745,  .486}2.494169393 & \cellcolor[rgb]{ .973,  .412,  .42}3.295858177  \\
-			                                                                               & std                & 0.031577789                                                                    & 0.034949967                                                                    & 0.034657443                                                                    & 0.068121366                                     & 0.035183664                                                                    & 0.087594488                                     & 0.034405331                                                                    & 0.055085207                                     & 0.055148148                                     & 0.028810924                                     & 0.293755503                                     & 0.029086341                                     & 0.016489872                                     \\
-			adult                                                                          & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ 1,  .922,  .518}0.346737798                                   & \cellcolor[rgb]{ 1,  .922,  .518}0.38233353                                    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.313320884} & \cellcolor[rgb]{ .788,  .859,  .502}0.335180995 & \cellcolor[rgb]{ .933,  .902,  .514}0.343292783                                & \cellcolor[rgb]{ .973,  .412,  .42}586.2065996  & \cellcolor[rgb]{ .467,  .765,  .486}0.317677033                                & \cellcolor[rgb]{ 1,  .922,  .518}0.363543899    & \cellcolor[rgb]{ 1,  .922,  .518}0.392047161    & \cellcolor[rgb]{ .388,  .745,  .482}0.313329677 & \cellcolor[rgb]{ 1,  .922,  .518}1.217724345    & \cellcolor[rgb]{ .388,  .745,  .482}0.313444396 & \cellcolor[rgb]{ 1,  .922,  .518}0.639695856    \\
-			                                                                               & std                & 0.003704238                                                                    & 0.018067239                                                                    & 0.000510377                                                                    & 0.043628962                                     & 0.014659665                                                                    & 1261.204704                                     & 0.005277776                                                                    & 0.020803371                                     & 0.020086997                                     & 0.000411017                                     & 0.496591684                                     & 0.0003947                                       & 0.042558869                                     \\
-			air quality                                                                    & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .651,  .82,  .494}0.256871193                                 & \cellcolor[rgb]{ .827,  .871,  .506}0.260623969                                & \cellcolor[rgb]{ .647,  .82,  .494}0.256829053                                 & \cellcolor[rgb]{ 1,  .922,  .518}0.264177871    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.251334045} & \cellcolor[rgb]{ .996,  .827,  .502}0.272859303 & \cellcolor[rgb]{ .647,  .82,  .494}0.256781683                                 & \cellcolor[rgb]{ .976,  .914,  .514}0.263703859 & \cellcolor[rgb]{ .996,  .792,  .494}0.275862527 & \cellcolor[rgb]{ .988,  .69,  .475}0.285172782  & \cellcolor[rgb]{ .984,  .608,  .459}0.292264593 & \cellcolor[rgb]{ .984,  .604,  .459}0.292851261 & \cellcolor[rgb]{ .973,  .412,  .42}0.309698115  \\
-			                                                                               & std                & 0.007475522                                                                    & 0.008912099                                                                    & 0.005955119                                                                    & 0.011452365                                     & 0.007814891                                                                    & 0.016310047                                     & 0.00630808                                                                     & 0.007306605                                     & 0.008162884                                     & 0.014769128                                     & 0.022648597                                     & 0.016417541                                     & 0.017044223                                     \\
-			bank                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .459,  .765,  .486}0.209641222                                & \cellcolor[rgb]{ .4,  .745,  .482}0.206461621                                  & \cellcolor[rgb]{ .588,  .8,  .49}0.2164275                                     & \cellcolor[rgb]{ .588,  .8,  .49}0.21643132     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.205779476} & \cellcolor[rgb]{ 1,  .886,  .514}0.245610465    & \cellcolor[rgb]{ .627,  .812,  .494}0.218599386                                & \cellcolor[rgb]{ .996,  .839,  .502}0.256171151 & \cellcolor[rgb]{ .988,  .686,  .475}0.28813827  & \cellcolor[rgb]{ 1,  .922,  .518}0.238179998    & \cellcolor[rgb]{ .973,  .412,  .42}0.345448185  & \cellcolor[rgb]{ 1,  .922,  .518}0.238550439    & \cellcolor[rgb]{ .976,  .424,  .424}0.343699166 \\
-			                                                                               & std                & 0.004750498                                                                    & 0.004040969                                                                    & 0.005944898                                                                    & 0.004889433                                     & 0.005654034                                                                    & 0.064531685                                     & 0.003821749                                                                    & 0.010550504                                     & 0.012801143                                     & 0.005568018                                     & 0.033990143                                     & 0.004820977                                     & 0.028120079                                     \\
-			bike                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.045805387} & \cellcolor[rgb]{ .592,  .804,  .494}0.068179412                                & \cellcolor[rgb]{ .882,  .886,  .51}0.099539486                                 & \cellcolor[rgb]{ .467,  .765,  .486}0.054496914 & \cellcolor[rgb]{ 1,  .922,  .518}0.112259627                                   & \cellcolor[rgb]{ .565,  .796,  .49}0.065136647  & \cellcolor[rgb]{ .588,  .8,  .49}0.06793708                                    & \cellcolor[rgb]{ 1,  .902,  .514}0.11787523     & \cellcolor[rgb]{ .992,  .761,  .486}0.153095534 & \cellcolor[rgb]{ .992,  .733,  .482}0.159868436 & \cellcolor[rgb]{ .992,  .773,  .49}0.150273084  & \cellcolor[rgb]{ .992,  .725,  .482}0.161397393 & \cellcolor[rgb]{ .973,  .412,  .42}0.239867227  \\
-			                                                                               & std                & 0.001725608                                                                    & 0.068117237                                                                    & 0.001754469                                                                    & 0.005239285                                     & 0.103490928                                                                    & 0.019626763                                     & 0.002076596                                                                    & 0.005954748                                     & 0.005079692                                     & 0.002759                                        & 0.025177188                                     & 0.003354245                                     & 0.039791214                                     \\
-			car                                                                            & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .729,  .843,  .502}0.202726327                                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.09724452}  & \cellcolor[rgb]{ .867,  .882,  .51}0.245363623                                 & \cellcolor[rgb]{ .62,  .812,  .494}0.16895294   & \cellcolor[rgb]{ .408,  .749,  .482}0.103937737                                & \cellcolor[rgb]{ .58,  .8,  .49}0.15718728      & \cellcolor[rgb]{ 1,  .922,  .518}0.285888989                                   & \cellcolor[rgb]{ .992,  .733,  .482}0.489062582 & \cellcolor[rgb]{ .98,  .502,  .439}0.737354357  & \cellcolor[rgb]{ .98,  .533,  .443}0.703539757  & \cellcolor[rgb]{ .988,  .667,  .471}0.563173207 & \cellcolor[rgb]{ .98,  .506,  .439}0.73217904   & \cellcolor[rgb]{ .973,  .412,  .42}0.833160108  \\
-			                                                                               & std                & 0.018356416                                                                    & 0.023870777                                                                    & 0.028744869                                                                    & 0.025441117                                     & 0.031133074                                                                    & 0.033710554                                     & 0.027353972                                                                    & 0.076505599                                     & 0.062600847                                     & 0.052091474                                     & 0.157928484                                     & 0.042705727                                     & 0.074182791                                     \\
-			diabetic                                                                       & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .694,  .831,  .498}0.889537739                                & \cellcolor[rgb]{ 1,  .898,  .514}0.919339482                                   & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.880898965} & \cellcolor[rgb]{ .98,  .914,  .514}0.897587026  & \cellcolor[rgb]{ .918,  .894,  .51}0.895749019                                 & \cellcolor[rgb]{ .973,  .412,  .42}1.298319185  & \cellcolor[rgb]{ .49,  .773,  .486}0.883864405                                 & \cellcolor[rgb]{ 1,  .902,  .518}0.913694494    & \cellcolor[rgb]{ .996,  .843,  .506}0.961291775 & \cellcolor[rgb]{ .976,  .914,  .514}0.897429714 & \cellcolor[rgb]{ .996,  .835,  .502}0.966103049 & \cellcolor[rgb]{ 1,  .922,  .518}0.898038783    & \cellcolor[rgb]{ .988,  .694,  .475}1.077362637 \\
-			                                                                               & std                & 0.004272255                                                                    & 0.00981794                                                                     & 0.003758597                                                                    & 0.010748722                                     & 0.004045488                                                                    & 0.659754133                                     & 0.004759234                                                                    & 0.008388702                                     & 0.00657199                                      & 0.003551413                                     & 0.016450474                                     & 0.002801135                                     & 0.0391395                                       \\
-			fish toxicity                                                                  & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .588,  .8,  .49}0.09908239                                    & \cellcolor[rgb]{ .451,  .761,  .482}0.097196901                                & \cellcolor[rgb]{ .831,  .871,  .506}0.10233624                                 & \cellcolor[rgb]{ 1,  .91,  .518}0.105584544     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.096326802} & \cellcolor[rgb]{ 1,  .922,  .518}0.104598099    & \cellcolor[rgb]{ .773,  .855,  .502}0.101567158                                & \cellcolor[rgb]{ .976,  .914,  .514}0.104293618 & \cellcolor[rgb]{ 1,  .863,  .506}0.109342435    & \cellcolor[rgb]{ .976,  .475,  .435}0.139280655 & \cellcolor[rgb]{ 1,  .855,  .506}0.109946059    & \cellcolor[rgb]{ .973,  .412,  .42}0.144088336  & \cellcolor[rgb]{ .992,  .733,  .482}0.119344204 \\
-			                                                                               & std                & 0.008463336                                                                    & 0.006948088                                                                    & 0.007611236                                                                    & 0.008228438                                     & 0.008021585                                                                    & 0.008136956                                     & 0.008882708                                                                    & 0.00895412                                      & 0.008990894                                     & 0.012326524                                     & 0.012481736                                     & 0.012407706                                     & 0.0130782                                       \\
-			forest fires                                                                   & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ 1,  .922,  .518}0.064321917                                   & \cellcolor[rgb]{ .557,  .792,  .49}0.052658676                                 & \cellcolor[rgb]{ .851,  .878,  .506}0.05923886                                 & \cellcolor[rgb]{ .824,  .871,  .506}0.058617148 & \cellcolor[rgb]{ 1,  .922,  .518}0.062552555                                   & \cellcolor[rgb]{ 1,  .89,  .514}0.080966845     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.048831474} & \cellcolor[rgb]{ .976,  .914,  .514}0.06209696  & \cellcolor[rgb]{ .553,  .792,  .49}0.05260701   & \cellcolor[rgb]{ .992,  .722,  .482}0.180571383 & \cellcolor[rgb]{ 1,  .914,  .518}0.069210426    & \cellcolor[rgb]{ .992,  .706,  .478}0.188476672 & \cellcolor[rgb]{ .973,  .412,  .42}0.359831599  \\
-			                                                                               & std                & 0.039911806                                                                    & 0.039243672                                                                    & 0.031685801                                                                    & 0.034163415                                     & 0.039170629                                                                    & 0.069099845                                     & 0.032095867                                                                    & 0.038470671                                     & 0.025957821                                     & 0.008365929                                     & 0.047244856                                     & 0.010081381                                     & 0.089999905                                     \\
-			housing                                                                        & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .518,  .78,  .486}0.088925893                                 & \cellcolor[rgb]{ .404,  .749,  .482}0.08481865                                 & \cellcolor[rgb]{ .612,  .808,  .494}0.092269667                                & \cellcolor[rgb]{ .69,  .831,  .498}0.095072459  & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.08422333}  & \cellcolor[rgb]{ .663,  .824,  .498}0.094078934 & \cellcolor[rgb]{ 1,  .922,  .518}0.105999965                                   & \cellcolor[rgb]{ 1,  .867,  .51}0.116883814     & \cellcolor[rgb]{ .996,  .812,  .498}0.127851649 & \cellcolor[rgb]{ .984,  .576,  .455}0.173521216 & \cellcolor[rgb]{ .992,  .722,  .482}0.145240159 & \cellcolor[rgb]{ .984,  .588,  .455}0.171302372 & \cellcolor[rgb]{ .973,  .412,  .42}0.205724786  \\
-			                                                                               & std                & 0.012490666                                                                    & 0.011213172                                                                    & 0.015551947                                                                    & 0.014823695                                     & 0.014924594                                                                    & 0.017302471                                     & 0.018700331                                                                    & 0.019460369                                     & 0.020192262                                     & 0.022837541                                     & 0.029813905                                     & 0.017916976                                     & 0.036445189                                     \\
-			iris                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .788,  .859,  .502}0.216138929                                & \cellcolor[rgb]{ .514,  .78,  .486}0.120305813                                 & \cellcolor[rgb]{ .416,  .753,  .482}0.084967127                                & \cellcolor[rgb]{ 1,  .855,  .506}0.372908547    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.075287772} & \cellcolor[rgb]{ .859,  .878,  .506}0.241094806 & \cellcolor[rgb]{ .996,  .808,  .498}0.426015649                                & \cellcolor[rgb]{ .686,  .831,  .498}0.180917533 & \cellcolor[rgb]{ 1,  .922,  .518}0.289495446    & \cellcolor[rgb]{ .992,  .773,  .49}0.469415404  & \cellcolor[rgb]{ .973,  .412,  .42}0.896458149  & \cellcolor[rgb]{ .992,  .745,  .486}0.502796506 & \cellcolor[rgb]{ .98,  .494,  .435}0.802733988  \\
-			                                                                               & std                & 0.059156887                                                                    & 0.097731271                                                                    & 0.041820159                                                                    & 1.119111663                                     & 0.045657899                                                                    & 0.295227964                                     & 0.071608458                                                                    & 0.163729792                                     & 0.117435582                                     & 0.087556703                                     & 0.844445785                                     & 0.072001841                                     & 0.684394699                                     \\
-			mushroom                                                                       & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .549,  .792,  .49}0.002577835                                 & \cellcolor[rgb]{ .467,  .765,  .486}0.001321295                                & \cellcolor[rgb]{ 1,  .922,  .518}0.009417256                                   & \cellcolor[rgb]{ .439,  .757,  .482}0.000906998 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{8.30695E-05} & \cellcolor[rgb]{ .718,  .839,  .498}0.005152476 & \cellcolor[rgb]{ .655,  .82,  .494}0.00417499                                  & \cellcolor[rgb]{ 1,  .871,  .51}0.077415858     & \cellcolor[rgb]{ .984,  .561,  .451}0.489160105 & \cellcolor[rgb]{ .996,  .796,  .494}0.179705445 & \cellcolor[rgb]{ 1,  .886,  .514}0.061137885    & \cellcolor[rgb]{ .992,  .749,  .486}0.241811308 & \cellcolor[rgb]{ .973,  .412,  .42}0.687017333  \\
-			                                                                               & std                & 0.000662841                                                                    & 0.004905902                                                                    & 0.002279151                                                                    & 0.001259819                                     & 6.96496E-05                                                                    & 0.012039998                                     & 0.000905097                                                                    & 0.019865901                                     & 0.024593143                                     & 0.009208458                                     & 0.06033175                                      & 0.012790223                                     & 0.01638976                                      \\
-			parkinsons                                                                     & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .51,  .776,  .486}0.056277858                                 & \cellcolor[rgb]{ .412,  .749,  .482}0.054480758                                & \cellcolor[rgb]{ 1,  .922,  .518}0.065451464                                   & \cellcolor[rgb]{ .639,  .816,  .494}0.058737776 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.053985977} & \cellcolor[rgb]{ .639,  .816,  .494}0.05873821  & \cellcolor[rgb]{ .69,  .831,  .498}0.05967759                                  & \cellcolor[rgb]{ 1,  .918,  .518}0.065774264    & \cellcolor[rgb]{ 1,  .898,  .514}0.066854953    & \cellcolor[rgb]{ .976,  .467,  .431}0.092323864 & \cellcolor[rgb]{ 1,  .894,  .514}0.067066667    & \cellcolor[rgb]{ .973,  .412,  .42}0.095371925  & \cellcolor[rgb]{ .984,  .604,  .459}0.084321583 \\
-			                                                                               & std                & 0.001432862                                                                    & 0.001998668                                                                    & 0.002301839                                                                    & 0.002859752                                     & 0.001547989                                                                    & 0.002811075                                     & 0.001691389                                                                    & 0.002548177                                     & 0.003281185                                     & 0.008302374                                     & 0.005043049                                     & 0.009431099                                     & 0.008978517                                     \\
-			student performance                                                            & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.165552792} & \cellcolor[rgb]{ .98,  .522,  .443}0.492891063                                 & \cellcolor[rgb]{ .471,  .769,  .486}0.169715979                                & \cellcolor[rgb]{ 1,  .855,  .506}0.245419875    & \cellcolor[rgb]{ .973,  .412,  .42}0.572439541                                 & \cellcolor[rgb]{ 1,  .871,  .51}0.235942235     & \cellcolor[rgb]{ .49,  .773,  .486}0.170794263                                 & \cellcolor[rgb]{ .969,  .91,  .514}0.194664435  & \cellcolor[rgb]{ 1,  .922,  .518}0.196187948    & \cellcolor[rgb]{ .933,  .902,  .514}0.193041307 & \cellcolor[rgb]{ .984,  .573,  .451}0.456490052 & \cellcolor[rgb]{ .925,  .898,  .51}0.192542094  & \cellcolor[rgb]{ 1,  .918,  .518}0.201390878    \\
-			                                                                               & std                & 0.011258528                                                                    & 0.105388532                                                                    & 0.010966961                                                                    & 0.133694251                                     & 0.05360667                                                                     & 0.10249181                                      & 0.010377173                                                                    & 0.014024256                                     & 0.009798773                                     & 0.011295962                                     & 0.049033016                                     & 0.011402763                                     & 0.011757846                                     \\
-			wine quality                                                                   & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .631,  .816,  .494}1.06505343                                 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{1.039511785} & \cellcolor[rgb]{ .698,  .831,  .498}1.07178488                                 & \cellcolor[rgb]{ 1,  .922,  .518}1.102805083    & \cellcolor[rgb]{ .502,  .776,  .486}1.051442793                                & \cellcolor[rgb]{ .804,  .863,  .506}1.082728853 & \cellcolor[rgb]{ .788,  .859,  .502}1.080905303                                & \cellcolor[rgb]{ .996,  .839,  .502}1.166586247 & \cellcolor[rgb]{ .992,  .725,  .482}1.251597837 & \cellcolor[rgb]{ .996,  .843,  .502}1.16477848  & \cellcolor[rgb]{ .988,  .659,  .467}1.3045869   & \cellcolor[rgb]{ .996,  .824,  .502}1.17741444  & \cellcolor[rgb]{ .973,  .412,  .42}1.489554557  \\
-			                                                                               & std                & 0.023560192                                                                    & 0.018361143                                                                    & 0.024922811                                                                    & 0.039250798                                     & 0.020795097                                                                    & 0.026483778                                     & 0.021109916                                                                    & 0.030251195                                     & 0.045716819                                     & 0.022984412                                     & 0.114260845                                     & 0.01919043                                      & 0.092922599                                     \\
-			\bottomrule
-		\end{tabular}%
-	}
-\end{table}%
-
-% Table generated by Excel2LaTeX from sheet 'results - test - rank'
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:standalone:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rcccc|c|c|c|c|c|ccccc}
-			epoch                                                                          & \multicolumn{1}{l}{(all)}              &                                                                                    &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
-			                                                                               &                                        &                                                                                    &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
-			                                                                               &                                        & \multicolumn{1}{l}{\textbf{heuristic}}                                             &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
-			\cmidrule{3-3}\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}    \textbf{dataset} & \multicolumn{1}{l}{\textbf{statistic}} & \textbf{adagrad}                                                                   & \textbf{adam}                                                             & \textbf{nag}                                                              & \textbf{bhh\_gd}                               & \textbf{rmsprop}                                                          & \textbf{bhh\_all}                            & \textbf{adadelta}                           & \textbf{bhh\_mh}                               & \textbf{ga}                                    & \textbf{sgd}                                    & \textbf{pso}                                    & \textbf{momentum}                              & \textbf{de}                                    \\
-			\midrule
-			abalone                                                                        & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2215}          & 2.3989                                                                    & 4.2731                                                                    & 4.7032                                         & 4.6172                                                                    & 5.9376                                       & 5.3129                                      & 8.1882                                         & 11.1108                                        & 8.6280                                          & 11.2559                                         & 9.8151                                         & 12.5376                                        \\
-			                                                                               & std                                    & 1.5913                                                                             & 1.8873                                                                    & 1.5419                                                                    & 2.1080                                         & 2.6504                                                                    & 2.3994                                       & 1.4782                                      & 1.1947                                         & 1.1017                                         & 1.0193                                          & 1.8265                                          & 1.1601                                         & 1.3291                                         \\
-			adult                                                                          & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 5.8978                                                                             & 7.6258                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5140} & 5.3258                                         & 6.6892                                                                    & 12.0194                                      & 2.5258                                      & 7.9409                                         & 9.5860                                         & 3.0065                                          & 11.5344                                         & 3.8699                                         & 10.9462                                        \\
-			                                                                               & std                                    & 1.6171                                                                             & 2.0293                                                                    & 0.7250                                                                    & 1.8985                                         & 1.8347                                                                    & 2.7430                                       & 1.3543                                      & 1.6391                                         & 1.7015                                         & 1.4999                                          & 2.0122                                          & 1.7090                                         & 1.8965                                         \\
-			air quality                                                                    & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 3.6409                                                                             & 5.4312                                                                    & 3.8194                                                                    & 5.0817                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.4452} & 6.6860                                       & 5.2441                                      & 6.3570                                         & 7.8204                                         & 10.6613                                         & 9.9151                                          & 11.7559                                        & 11.1419                                        \\
-			                                                                               & std                                    & 2.2588                                                                             & 2.6198                                                                    & 2.2285                                                                    & 2.7618                                         & 2.5704                                                                    & 3.0613                                       & 3.1622                                      & 2.3031                                         & 2.2652                                         & 1.6061                                          & 2.2882                                          & 1.4730                                         & 2.2361                                         \\
-			bank                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 2.5495                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.0796} & 4.2871                                                                    & 4.8828                                         & 3.4645                                                                    & 6.2419                                       & 5.6720                                      & 9.7495                                         & 10.9817                                        & 8.2774                                          & 11.8376                                         & 8.4774                                         & 12.4989                                        \\
-			                                                                               & std                                    & 1.5980                                                                             & 1.5871                                                                    & 1.7325                                                                    & 1.7017                                         & 2.2090                                                                    & 2.1571                                       & 1.2411                                      & 1.0482                                         & 1.2165                                         & 1.0304                                          & 1.4638                                          & 1.0682                                         & 1.2243                                         \\
-			bike                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7204}          & 3.6925                                                                    & 6.4516                                                                    & 3.8441                                         & 6.2624                                                                    & 4.2151                                       & 5.3602                                      & 7.4108                                         & 9.2269                                         & 10.3355                                         & 9.3086                                          & 10.7086                                        & 12.4634                                        \\
-			                                                                               & std                                    & 1.3839                                                                             & 4.0038                                                                    & 1.0199                                                                    & 1.3983                                         & 4.5803                                                                    & 1.3611                                       & 1.1555                                      & 1.0076                                         & 1.1835                                         & 1.4193                                          & 1.7615                                          & 1.4233                                         & 1.4648                                         \\
-			car                                                                            & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 4.7634                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6226} & 6.0785                                                                    & 3.3473                                         & 2.3269                                                                    & 3.5624                                       & 7.7344                                      & 8.8505                                         & 10.7763                                        & 10.2452                                         & 8.3613                                          & 10.9226                                        & 12.4086                                        \\
-			                                                                               & std                                    & 0.9383                                                                             & 1.4053                                                                    & 0.7991                                                                    & 1.3499                                         & 1.4091                                                                    & 1.3152                                       & 1.7464                                      & 1.4128                                         & 1.4715                                         & 1.4474                                          & 1.6222                                          & 1.3489                                         & 1.4915                                         \\
-			diabetic                                                                       & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 2.7796                                                                             & 7.1484                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8118} & 5.2269                                         & 6.7376                                                                    & 9.3968                                       & 2.6753                                      & 8.5570                                         & 11.2011                                        & 5.9215                                          & 10.7022                                         & 6.3355                                         & 12.5065                                        \\
-			                                                                               & std                                    & 1.6587                                                                             & 2.2265                                                                    & 1.4127                                                                    & 2.1860                                         & 2.5767                                                                    & 3.0221                                       & 1.6286                                      & 1.1699                                         & 1.4132                                         & 1.5421                                          & 1.0674                                          & 1.6118                                         & 1.2417                                         \\
-			fish toxicity                                                                  & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 4.2645                                                                             & 3.6022                                                                    & 5.8914                                                                    & 5.4118                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.5946} & 5.8290                                       & 7.9140                                      & 6.3849                                         & 6.7043                                         & 11.5785                                         & 7.5731                                          & 12.2301                                        & 10.0215                                        \\
-			                                                                               & std                                    & 2.6142                                                                             & 2.4453                                                                    & 2.6288                                                                    & 2.6649                                         & 2.3292                                                                    & 2.8557                                       & 3.4287                                      & 2.9437                                         & 2.8200                                         & 1.4587                                          & 2.9817                                          & 1.3822                                         & 2.3585                                         \\
-			forest fires                                                                   & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 5.1559                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{4.2688} & 5.6882                                                                    & 4.6935                                         & 5.0355                                                                    & 5.4839                                       & 6.5161                                      & 5.4591                                         & 7.3667                                         & 10.8129                                         & 6.4796                                          & 11.7065                                        & 12.3333                                        \\
-			                                                                               & std                                    & 2.9217                                                                             & 2.9841                                                                    & 2.2149                                                                    & 2.7594                                         & 3.1431                                                                    & 3.1070                                       & 3.0823                                      & 2.6680                                         & 2.3704                                         & 1.2070                                          & 3.3539                                          & 1.3250                                         & 1.9228                                         \\
-			housing                                                                        & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 3.4484                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.3344} & 4.6839                                                                    & 4.4742                                         & 3.6946                                                                    & 4.3763                                       & 7.5903                                      & 7.5441                                         & 7.8839                                         & 11.4075                                         & 9.9409                                          & 11.2731                                        & 11.3484                                        \\
-			                                                                               & std                                    & 2.0251                                                                             & 1.8193                                                                    & 2.6579                                                                    & 2.3125                                         & 2.1662                                                                    & 2.4377                                       & 2.7475                                      & 1.7363                                         & 2.0991                                         & 1.5278                                          & 2.3166                                          & 1.5059                                         & 2.0965                                         \\
-			iris                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 6.3946                                                                             & 3.5839                                                                    & 3.5548                                                                    & 4.7473                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6968} & 5.2204                                       & 11.3527                                     & 6.6075                                         & 8.2473                                         & 10.3796                                         & 8.2731                                          & 11.0548                                        & 8.8871                                         \\
-			                                                                               & std                                    & 1.6000                                                                             & 2.5111                                                                    & 2.1247                                                                    & 2.2749                                         & 1.9121                                                                    & 3.0415                                       & 1.7791                                      & 2.5553                                         & 1.7647                                         & 1.2938                                          & 4.3840                                          & 1.4090                                         & 3.2511                                         \\
-			mushroom                                                                       & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 4.4656                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1344} & 6.3323                                                                    & 3.4484                                         & 2.4656                                                                    & 3.6688                                       & 6.5538                                      & 9.0452                                         & 11.5731                                        & 9.7527                                          & 7.8720                                          & 10.9785                                        & 12.7097                                        \\
-			                                                                               & std                                    & 1.0527                                                                             & 1.8831                                                                    & 0.8915                                                                    & 1.6019                                         & 1.3589                                                                    & 2.4687                                       & 1.0711                                      & 1.0931                                         & 1.1927                                         & 1.0828                                          & 0.9197                                          & 1.1075                                         & 1.4781                                         \\
-			parkinsons                                                                     & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 2.4677                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2333} & 7.5355                                                                    & 4.5720                                         & 3.5656                                                                    & 4.3839                                       & 6.4720                                      & 8.3161                                         & 7.7968                                         & 11.7516                                         & 8.4892                                          & 12.5419                                        & 10.8742                                        \\
-			                                                                               & std                                    & 1.4969                                                                             & 1.7418                                                                    & 1.4396                                                                    & 1.9337                                         & 2.4919                                                                    & 1.8612                                       & 2.4229                                      & 1.6441                                         & 1.7188                                         & 1.1551                                          & 1.9008                                          & 1.3515                                         & 1.3174                                         \\
-			student performance                                                            & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5634}          & 11.3978                                                                   & 3.1935                                                                    & 5.6624                                         & 12.4312                                                                   & 5.8634                                       & 3.4194                                      & 6.9333                                         & 7.1032                                         & 6.6366                                          & 11.0624                                         & 6.7011                                         & 8.0323                                         \\
-			                                                                               & std                                    & 1.9122                                                                             & 2.1780                                                                    & 2.1205                                                                    & 3.5703                                         & 1.3400                                                                    & 3.1588                                       & 2.0060                                      & 2.4398                                         & 1.9887                                         & 2.0233                                          & 1.0674                                          & 2.2423                                         & 1.9346                                         \\
-			wine quality                                                                   & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 3.2806                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1118} & 4.1505                                                                    & 4.7882                                         & 3.6301                                                                    & 5.1925                                       & 6.0011                                      & 9.5935                                         & 10.3387                                        & 8.6344                                          & 11.1602                                         & 9.5269                                         & 12.5903                                        \\
-			                                                                               & std                                    & 1.9309                                                                             & 1.6660                                                                    & 1.9156                                                                    & 2.1052                                         & 1.7314                                                                    & 1.9506                                       & 2.4040                                      & 1.4943                                         & 1.6201                                         & 1.1801                                          & 1.7732                                          & 1.3407                                         & 1.3515                                         \\
-			\midrule
-			\textbf{overall}                                                               & \textbf{avg}                           & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{3.7076}} & \textbf{4.1777}                                                           & \textbf{4.6177}                                                           & \textbf{4.6806}                                & \textbf{4.7105}                                                           & \textbf{5.8718}                              & \textbf{6.0229}                             & \textbf{7.7958}                                & \textbf{9.1811}                                & \textbf{9.2019}                                 & \textbf{9.5844}                                 & \textbf{9.8599}                                & \textbf{11.4200}                               \\
-			\textbf{normalised}                                                            & \textbf{rank}                          & \cellcolor[rgb]{ .388,  .745,  .482}\textbf{1}                                     & \cellcolor[rgb]{ .49,  .773,  .486}\textbf{2}                             & \cellcolor[rgb]{ .592,  .804,  .494}\textbf{3}                            & \cellcolor[rgb]{ .694,  .831,  .498}\textbf{4} & \cellcolor[rgb]{ .796,  .863,  .506}\textbf{5}                            & \cellcolor[rgb]{ .898,  .89,  .51}\textbf{6} & \cellcolor[rgb]{ 1,  .922,  .518}\textbf{7} & \cellcolor[rgb]{ .996,  .839,  .502}\textbf{8} & \cellcolor[rgb]{ .992,  .753,  .486}\textbf{9} & \cellcolor[rgb]{ .988,  .667,  .471}\textbf{10} & \cellcolor[rgb]{ .984,  .584,  .455}\textbf{11} & \cellcolor[rgb]{ .98,  .498,  .439}\textbf{12} & \cellcolor[rgb]{ .973,  .412,  .42}\textbf{13} \\
-			\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}\end{tabular}%
-	}
-\end{table}%
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \Acs{BHH} per dataset, across all runs and epochs.}
-	\label{fig:results:standalone:descriptive:descriptive}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of all low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
-	\label{fig:results:standalone:descriptive:cd}
-\end{figure}
-
-\section{Heuristic Pool}\label{sec:results:bhh_variant_hp}
-
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:heuristic_pool:metrics}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}          &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
-			\cmidrule{1-2}                      &                                             &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{heuristic pool}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                &                                                                                    &                 &                &                 &                 \\
-			\cmidrule{2-3}                      & \textbf{all}                                &                                                                           &                 & \textbf{gd}    &                                                                                    &                 & \textbf{mh}    &                 &                 \\
-			\cmidrule{2-10}    \textbf{dataset} & \textbf{count}                              & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count} & \textbf{avg}    & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                         & 1.7946                                                                    & 0.6411          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3828}          & 0.5604          & 930            & 2.8226          & 0.4198          \\
-			adult                               & 930                                         & 2.8484                                                                    & 0.5058          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.1559}          & 0.4077          & 930            & 1.8989          & 0.4104          \\
-			air quality                         & 930                                         & 2.1871                                                                    & 0.8153          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6828}          & 0.7506          & 930            & 2.1301          & 0.7883          \\
-			bank                                & 930                                         & 1.7731                                                                    & 0.5617          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3215}          & 0.4920          & 930            & 2.9054          & 0.3341          \\
-			bike                                & 930                                         & 1.6247                                                                    & 0.5529          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4387}          & 0.5321          & 930            & 2.9366          & 0.2808          \\
-			car                                 & 930                                         & 1.5903                                                                    & 0.5113          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4409}          & 0.5180          & 930            & 2.9688          & 0.2275          \\
-			diabetic                            & 930                                         & 2.4516                                                                    & 0.7353          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.2806}          & 0.5756          & 930            & 2.2677          & 0.5798          \\
-			fish toxicity                       & 930                                         & 1.9903                                                                    & 0.8485          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8344}          & 0.7684          & 930            & 2.1753          & 0.7959          \\
-			forest fires                        & 930                                         & 2.0667                                                                    & 0.8338          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8269}          & 0.7813          & 930            & 2.1065          & 0.8066          \\
-			housing                             & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6043} & 0.6869          & 930            & 1.6602                                                                             & 0.6648          & 930            & 2.7355          & 0.5238          \\
-			iris                                & 930                                         & 1.8581                                                                    & 0.8005          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7806}          & 0.7272          & 930            & 2.3613          & 0.7960          \\
-			mushroom                            & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5204} & 0.5815          & 930            & 1.5484                                                                             & 0.5273          & 930            & 2.9312          & 0.2890          \\
-			parkinsons                          & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5570} & 0.6238          & 930            & 1.6011                                                                             & 0.5915          & 930            & 2.8419          & 0.4448          \\
-			student performance                 & 930                                         & 1.9828                                                                    & 0.8220          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7903}          & 0.8480          & 930            & 2.2269          & 0.7152          \\
-			wine quality                        & 930                                         & 1.5785                                                                    & 0.5498          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5630          & 930            & 2.9280          & 0.2938          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                              & \textbf{1.8952}                                                           & \textbf{0.7730} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.5492}} & \textbf{0.6651} & \textbf{13950} & \textbf{2.5491} & \textbf{0.6684} \\
-		\end{tabular}%
-	}
-\end{table}%
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying heuristic pools per dataset, across all runs and epochs.}
-	\label{fig:results:heuristic_pool:descriptive:descriptive}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying heuristic pools across all datasets, runs and epochs.}
-	\label{fig:results:heuristic_pool:descriptive:cd}
-\end{figure}
-
-\section{Population Size}\label{sec:results:bhh_variant_population}
-
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different population size values used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}
-	\label{tab:results:population:metrics}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}      &                                                                                    &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			\cmidrule{1-2}                      &                                         &                                                                                    &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{population}} & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{5}}          &                                                                                    &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{15}} &                 &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{25}} &                                                                           &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                          & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4387}          & 1.3396          & 930                             & 2.7452                                                                    & 1.3922          & 930                             & 3.0129          & 1.3865          & 930                             & 3.4065                                                                    & 1.3513          & 930                             & 3.3968                                                                    & 1.3514          \\
-			adult                               & 930                                     & 3.5720                                                                             & 1.4693          & 930                             & 3.2828                                                                    & 1.3751          & 930                             & 2.8108          & 1.3625          & 930                             & 2.6484                                                                    & 1.3222          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3634} & 1.3063          \\
-			air quality                         & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7527}          & 1.4283          & 930                             & 2.9258                                                                    & 1.3904          & 930                             & 2.9656          & 1.3791          & 930                             & 3.3140                                                                    & 1.3789          & 930                             & 3.0419                                                                    & 1.4374          \\
-			bank                                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8129}          & 1.4102          & 930                             & 3.1591                                                                    & 1.4348          & 930                             & 2.9989          & 1.4199          & 930                             & 3.0505                                                                    & 1.4438          & 930                             & 2.9785                                                                    & 1.3414          \\
-			bike                                & 930                                     & 3.8957                                                                             & 1.3355          & 930                             & 2.8688                                                                    & 1.2850          & 930                             & 2.9645          & 1.3447          & 930                             & 2.7430                                                                    & 1.3762          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5280} & 1.3278          \\
-			car                                 & 930                                     & 3.1892                                                                             & 1.3915          & 930                             & 3.0409                                                                    & 1.3945          & 930                             & 3.0398          & 1.4523          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8559} & 1.3938          & 930                             & 2.8742                                                                    & 1.4151          \\
-			diabetic                            & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7978}          & 1.5078          & 930                             & 2.9387                                                                    & 1.4133          & 930                             & 3.2129          & 1.4525          & 930                             & 2.9613                                                                    & 1.3036          & 930                             & 3.0892                                                                    & 1.3534          \\
-			fish toxicity                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8151}          & 1.4249          & 930                             & 3.0409                                                                    & 1.4288          & 930                             & 3.0925          & 1.3230          & 930                             & 3.1280                                                                    & 1.4073          & 930                             & 2.9237                                                                    & 1.4634          \\
-			forest fires                        & 930                                     & 3.0172                                                                             & 1.4026          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9215} & 1.3800          & 930                             & 2.9806          & 1.3833          & 930                             & 3.0968                                                                    & 1.4124          & 930                             & 2.9839                                                                    & 1.4879          \\
-			housing                             & 930                                     & 2.8366                                                                             & 1.4040          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8258} & 1.3802          & 930                             & 2.9753          & 1.4393          & 930                             & 2.9849                                                                    & 1.4111          & 930                             & 3.3774                                                                    & 1.3680          \\
-			iris                                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301}          & 1.3038          & 930                             & 2.8731                                                                    & 1.3970          & 930                             & 3.0505          & 1.4129          & 930                             & 3.1860                                                                    & 1.4251          & 930                             & 3.0602                                                                    & 1.4987          \\
-			mushroom                            & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7989}          & 1.2052          & 930                             & 2.9441                                                                    & 1.3250          & 930                             & 3.0462          & 1.4521          & 930                             & 3.1366                                                                    & 1.4940          & 930                             & 3.0538                                                                    & 1.5664          \\
-			parkinsons                          & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6645}          & 1.4411          & 930                             & 3.1065                                                                    & 1.3272          & 930                             & 3.0247          & 1.4265          & 930                             & 3.0495                                                                    & 1.4420          & 930                             & 3.1548                                                                    & 1.3810          \\
-			student performance                 & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6376}          & 1.4357          & 930                             & 2.8645                                                                    & 1.4108          & 930                             & 3.1548          & 1.4042          & 930                             & 3.2387                                                                    & 1.3970          & 930                             & 3.1043                                                                    & 1.3395          \\
-			wine quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5505}          & 1.3165          & 930                             & 2.7817                                                                    & 1.4152          & 930                             & 3.1581          & 1.3841          & 930                             & 3.1806                                                                    & 1.3941          & 930                             & 3.3290                                                                    & 1.4140          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                          & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9073}} & \textbf{1.4377} & \textbf{13950}                  & \textbf{2.9546}                                                           & \textbf{1.3904} & \textbf{13950}                  & \textbf{3.0325} & \textbf{1.4045} & \textbf{13950}                  & \textbf{3.0654}                                                           & \textbf{1.4108} & \textbf{13950}                  & \textbf{3.0173}                                                           & \textbf{1.4306} \\
-		\end{tabular}%
-	}
-\end{table}%
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_population/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of \acs{BHH} with varying population sizes per dataset, across all runs and epochs.}
-	\label{fig:results:population:descriptive:descriptive}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_population/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of \acs{BHH} with varying population sizes across all datasets, runs and epochs.}
-	\label{fig:results:population:descriptive:cd}
-\end{figure}
-
-\section{Credit Assignment Strategy}\label{sec:results:bhh_variant_credit}
-
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different \index{credit}credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:credit:metrics}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}  &                                                                           &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
-			\cmidrule{1-2}                      &                                     &                                                                           &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{credit}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
-			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{ibest}}  &                                                                           &                 & \multicolumn{1}{l}{\textbf{pbest}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{rbest}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{gbest}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{symmetric}} &                                                                           &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                      & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                         & \textbf{avg}                                                              & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                 & 3.1677                                                                    & 1.3188          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613}          & 1.4588          & 930                                & 2.9968                                                                    & 1.3993          & 930                                & 2.9667                                                                    & 1.4547          & 930                                    & 3.0075                                                                    & 1.4214          \\
-			adult                               & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                & 2.6763                                                                             & 1.5019          & 930                                & 2.8065                                                                    & 1.5003          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                    & 3.3538                                                                    & 1.5682          \\
-			air quality                         & 930                                 & 3.1312                                                                    & 1.3472          & 930                                & 3.0376                                                                             & 1.3566          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5914} & 1.4646          & 930                                & 3.1280                                                                    & 1.3358          & 930                                    & 3.1118                                                                    & 1.4871          \\
-			bank                                & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8591} & 1.3442          & 930                                & 2.9903                                                                             & 1.4320          & 930                                & 2.8882                                                                    & 1.4098          & 930                                & 3.0441                                                                    & 1.4154          & 930                                    & 3.2183                                                                    & 1.4424          \\
-			bike                                & 930                                 & 3.0527                                                                    & 1.3401          & 930                                & 3.0086                                                                             & 1.3935          & 930                                & 3.0667                                                                    & 1.4825          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3393          & 930                                    & 2.9978                                                                    & 1.5028          \\
-			car                                 & 930                                 & 3.1151                                                                    & 1.3562          & 930                                & 3.0312                                                                             & 1.4826          & 930                                & 3.2516                                                                    & 1.4024          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6892} & 1.3540          & 930                                    & 2.9129                                                                    & 1.4111          \\
-			diabetic                            & 930                                 & 2.8914                                                                    & 1.3488          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6269}          & 1.4171          & 930                                & 3.4151                                                                    & 1.3653          & 930                                & 2.8925                                                                    & 1.3620          & 930                                    & 3.1742                                                                    & 1.4487          \\
-			fish toxicity                       & 930                                 & 3.1516                                                                    & 1.4360          & 930                                & 2.9903                                                                             & 1.4521          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.4748          & 930                                & 3.2043                                                                    & 1.2988          & 930                                    & 2.8957                                                                    & 1.3579          \\
-			forest fires                        & 930                                 & 3.0968                                                                    & 1.2771          & 930                                & 3.1806                                                                             & 1.3040          & 930                                & 2.8559                                                                    & 1.3562          & 930                                & 3.1215                                                                    & 1.5018          & 930                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7452} & 1.5627          \\
-			housing                             & 930                                 & 2.9011                                                                    & 1.4938          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8527}          & 1.3168          & 930                                & 2.9022                                                                    & 1.3974          & 930                                & 3.3108                                                                    & 1.3243          & 930                                    & 3.0333                                                                    & 1.4833          \\
-			iris                                & 930                                 & 3.1892                                                                    & 1.4281          & 930                                & 3.0839                                                                             & 1.4412          & 930                                & 3.0591                                                                    & 1.3755          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8237} & 1.4085          & 930                                    & 2.8441                                                                    & 1.3844          \\
-			mushroom                            & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8075} & 1.4594          & 930                                & 3.0183                                                                             & 1.4107          & 930                                & 2.8957                                                                    & 1.3985          & 930                                & 3.0839                                                                    & 1.4178          & 930                                    & 3.1720                                                                    & 1.3813          \\
-			parkinsons                          & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5645} & 1.4835          & 930                                & 2.8925                                                                             & 1.3429          & 930                                & 3.5065                                                                    & 1.2190          & 930                                & 3.0796                                                                    & 1.3920          & 930                                    & 2.9570                                                                    & 1.4548          \\
-			student performance                 & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6624} & 1.3124          & 930                                & 3.0290                                                                             & 1.4067          & 930                                & 3.1892                                                                    & 1.3821          & 930                                & 2.7978                                                                    & 1.4702          & 930                                    & 3.3215                                                                    & 1.3938          \\
-			wine quality                        & 930                                 & 3.1871                                                                    & 1.3080          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366}          & 1.4706          & 930                                & 3.0140                                                                    & 1.3712          & 930                                & 2.9419                                                                    & 1.4115          & 930                                    & 3.2204                                                                    & 1.4300          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                      & \textbf{2.9475}                                                           & \textbf{1.3805} & \textbf{13950}                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9277}} & \textbf{1.4222} & \textbf{13950}                     & \textbf{3.0131}                                                           & \textbf{1.4209} & \textbf{13950}                     & \textbf{2.9596}                                                           & \textbf{1.3921} & \textbf{13950}                         & \textbf{3.0644}                                                           & \textbf{1.4594} \\
-		\end{tabular}%
-	}
-\end{table}%
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_credit/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying credit assignment strategies per dataset, across all runs and epochs.}
-	\label{fig:results:credit:descriptive:descriptive}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_credit/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying credit assignment strategies across all datasets, runs and epochs.}
-	\label{fig:results:credit:descriptive:cd}
-\end{figure}
-
-\section{Reselection Interval}\label{sec:results:bhh_variant_reselection}
-
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different reselection values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:reselection:metrics}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}       &                                                                           &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
-			\cmidrule{1-2}                      &                                          &                                                                           &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{reselection}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
-			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}           &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                 &                 & \multicolumn{1}{l}{\textbf{10}} &                 &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                                    &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                           & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                                       & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                      & 4.3548                                                                    & 0.9760          & 930                            & 2.8473          & 1.2885          & 930                             & 2.7505          & 1.2622          & 930                             & 2.5602                                                                    & 1.2988          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4871}          & 1.3182          \\
-			adult                               & 930                                      & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7097} & 1.2671          & 930                            & 4.4559          & 1.0052          & 930                             & 3.4398          & 1.0453          & 930                             & 2.7656                                                                    & 0.9837          & 930                             & 2.3065                                                                             & 1.0670          \\
-			air quality                         & 930                                      & 3.7355                                                                    & 1.4046          & 930                            & 3.4075          & 1.3790          & 930                             & 2.9688          & 1.2783          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4237} & 1.2281          & 930                             & 2.4645                                                                             & 1.2906          \\
-			bank                                & 930                                      & 4.5677                                                                    & 0.7039          & 930                            & 3.6323          & 1.1271          & 930                             & 2.4237          & 1.1333          & 930                             & 2.2462                                                                    & 1.1139          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1301}          & 1.0957          \\
-			bike                                & 930                                      & 4.7935                                                                    & 0.6124          & 930                            & 3.9204          & 0.6480          & 930                             & 2.5161          & 0.8632          & 930                             & 2.0763                                                                    & 0.9007          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6935}          & 0.8911          \\
-			car                                 & 930                                      & 4.6409                                                                    & 0.7847          & 930                            & 2.9527          & 1.1581          & 930                             & 2.6548          & 1.1748          & 930                             & 2.5312                                                                    & 1.2440          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2204}          & 1.2169          \\
-			diabetic                            & 930                                      & 3.0129                                                                    & 1.0478          & 930                            & 4.4624          & 0.8688          & 930                             & 2.7957          & 1.1753          & 930                             & 2.6065                                                                    & 1.4391          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1226}          & 1.2639          \\
-			fish toxicity                       & 930                                      & 3.7484                                                                    & 1.2377          & 930                            & 3.1376          & 1.3174          & 930                             & 3.0344          & 1.4062          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4656} & 1.3039          & 930                             & 2.6140                                                                             & 1.4318          \\
-			forest fires                        & 930                                      & 3.8194                                                                    & 1.4330          & 930                            & 3.2720          & 1.2477          & 930                             & 2.8656          & 1.3464          & 930                             & 2.8194                                                                    & 1.3048          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2237}          & 1.2186          \\
-			housing                             & 930                                      & 4.1892                                                                    & 1.0993          & 930                            & 3.0172          & 1.2882          & 930                             & 2.5871          & 1.3541          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5312} & 1.2654          & 930                             & 2.6753                                                                             & 1.3399          \\
-			iris                                & 930                                      & 2.9839                                                                    & 1.4244          & 930                            & 2.9710          & 1.3165          & 930                             & 3.3462          & 1.4182          & 930                             & 3.0140                                                                    & 1.4054          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6849}          & 1.4289          \\
-			mushroom                            & 930                                      & 4.2065                                                                    & 1.2356          & 930                            & 2.9688          & 1.2992          & 930                             & 2.5860          & 1.2336          & 930                             & 2.7882                                                                    & 1.3397          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4505}          & 1.2259          \\
-			parkinsons                          & 930                                      & 4.7645                                                                    & 0.7563          & 930                            & 3.1882          & 1.0208          & 930                             & 2.2957          & 1.2089          & 930                             & 2.4968                                                                    & 1.1282          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2548}          & 1.0973          \\
-			student performance                 & 930                                      & 3.9710                                                                    & 1.0942          & 930                            & 4.0226          & 1.1196          & 930                             & 2.4774          & 1.2206          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495} & 1.2002          & 930                             & 2.2796                                                                             & 1.1324          \\
-			wine quality                        & 930                                      & 4.0688                                                                    & 1.1220          & 930                            & 2.9204          & 1.2934          & 930                             & 2.9559          & 1.3831          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4032} & 1.3779          & 930                             & 2.6516                                                                             & 1.2796          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                           & \textbf{3.9044}                                                           & \textbf{1.3641} & \textbf{13950}                 & \textbf{3.4118} & \textbf{1.2914} & \textbf{13950}                  & \textbf{2.7799} & \textbf{1.2811} & \textbf{13950}                  & \textbf{2.5318}                                                           & \textbf{1.2660} & \textbf{13950}                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.3506}} & \textbf{1.2541} \\
-		\end{tabular}%
-	}
-\end{table}%
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reselection values per dataset, across all runs and epochs.}
-	\label{fig:results:reselection:descriptive:descriptive}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_reselection/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reselection values across all datasets, runs and epochs.}
-	\label{fig:results:reselection:descriptive:cd}
-\end{figure}
-
-\section{Replay Window Size}\label{sec:results:bhh_variant_replay}
-
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:replay:metrics}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}  &                                                                           &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
-			\cmidrule{1-2}                      &                                     &                                                                           &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{replay}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
-			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}      &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                 &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                      & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                 & 3.0258                                                                    & 1.3816          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6785}          & 1.4551          & 930                             & 3.1968                                                                    & 1.3460          & 930                             & 3.0903                                                                    & 1.3851          & 930                             & 3.0086          & 1.4503          \\
-			adult                               & 930                                 & 2.8785                                                                    & 1.3824          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8269}          & 1.3595          & 930                             & 2.9430                                                                    & 1.4804          & 930                             & 3.0538                                                                    & 1.3714          & 930                             & 2.9645          & 1.5686          \\
-			air quality                         & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3851          & 930                            & 3.0151                                                                             & 1.4970          & 930                             & 2.9978                                                                    & 1.4294          & 930                             & 2.9505                                                                    & 1.2966          & 930                             & 3.1624          & 1.4430          \\
-			bank                                & 930                                 & 2.9484                                                                    & 1.4597          & 930                            & 3.0570                                                                             & 1.4731          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8602} & 1.3439          & 930                             & 3.0172                                                                    & 1.4202          & 930                             & 3.1172          & 1.3592          \\
-			bike                                & 930                                 & 2.9602                                                                    & 1.2739          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7366}          & 1.3401          & 930                             & 3.1452                                                                    & 1.4478          & 930                             & 2.9226                                                                    & 1.4174          & 930                             & 3.2355          & 1.5274          \\
-			car                                 & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7054} & 1.3572          & 930                            & 2.8376                                                                             & 1.3898          & 930                             & 3.0763                                                                    & 1.3723          & 930                             & 3.3269                                                                    & 1.4631          & 930                             & 3.0538          & 1.4086          \\
-			diabetic                            & 930                                 & 3.2473                                                                    & 1.3690          & 930                            & 3.3247                                                                             & 1.4058          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5935} & 1.3719          & 930                             & 2.8075                                                                    & 1.3844          & 930                             & 3.0269          & 1.4113          \\
-			fish toxicity                       & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7269} & 1.4190          & 930                            & 3.0785                                                                             & 1.4896          & 930                             & 3.1774                                                                    & 1.3980          & 930                             & 2.9892                                                                    & 1.3865          & 930                             & 3.0280          & 1.3373          \\
-			forest fires                        & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8054} & 1.4926          & 930                            & 2.9151                                                                             & 1.3812          & 930                             & 2.9914                                                                    & 1.4081          & 930                             & 3.0591                                                                    & 1.4111          & 930                             & 3.2290          & 1.3416          \\
-			housing                             & 930                                 & 3.1548                                                                    & 1.3007          & 930                            & 2.9774                                                                             & 1.4068          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8548} & 1.4501          & 930                             & 3.0355                                                                    & 1.4898          & 930                             & 2.9774          & 1.4037          \\
-			iris                                & 930                                 & 3.0720                                                                    & 1.3757          & 930                            & 3.1581                                                                             & 1.4187          & 930                             & 3.2204                                                                    & 1.3919          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6183} & 1.3964          & 930                             & 2.9312          & 1.4102          \\
-			mushroom                            & 930                                 & 3.0538                                                                    & 1.3243          & 930                            & 3.1430                                                                             & 1.4369          & 930                             & 3.0419                                                                    & 1.4140          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613} & 1.3823          & 930                             & 2.8957          & 1.4966          \\
-			parkinsons                          & 930                                 & 3.1720                                                                    & 1.3719          & 930                            & 2.8430                                                                             & 1.2437          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6731} & 1.4535          & 930                             & 3.1172                                                                    & 1.4189          & 930                             & 3.1946          & 1.4977          \\
-			student performance                 & 930                                 & 3.0398                                                                    & 1.3684          & 930                            & 2.9226                                                                             & 1.4106          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6548} & 1.4028          & 930                             & 3.0935                                                                    & 1.3225          & 930                             & 3.2892          & 1.4874          \\
-			wine quality                        & 930                                 & 3.1742                                                                    & 1.4300          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7323}          & 1.4556          & 930                             & 3.1581                                                                    & 1.4179          & 930                             & 3.0419                                                                    & 1.3565          & 930                             & 2.8935          & 1.3624          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                      & \textbf{2.9892}                                                           & \textbf{1.3892} & \textbf{13950}                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9497}} & \textbf{1.4224} & \textbf{13950}                  & \textbf{2.9723}                                                           & \textbf{1.4224} & \textbf{13950}                  & \textbf{2.9990}                                                           & \textbf{1.4021} & \textbf{13950}                  & \textbf{3.0672} & \textbf{1.4400} \\
-		\end{tabular}%
-	}
-\end{table}%
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_replay/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying replay window sizes per dataset, across all runs and epochs.}
-	\label{fig:results:replay:descriptive:descriptive}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_replay/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying replay window sizes across all datasets, runs and epochs.}
-	\label{fig:results:replay:descriptive:cd}
-\end{figure}
-
-\section{Reanalysis Interval}\label{sec:results:bhh_variant_reanalysis}
-
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different reanalysis values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:reanalysis:metrics}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}      &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			\cmidrule{1-2}                      &                                         &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{reanalysis}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}          &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                           &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                          & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                     & 2.9849                                                                    & 1.3965          & 930                            & 3.0699                                                                    & 1.4423          & 930                             & 3.1710                                                                             & 1.3205          & 930                             & 2.9441                                                                    & 1.4447          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301} & 1.4433          \\
-			adult                               & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860}          & 0.8523          & 930                             & 2.7914                                                                    & 1.7091          & 930                             & 3.0151                                                                    & 1.7236          \\
-			air quality                         & 930                                     & 2.9613                                                                    & 1.3442          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8387} & 1.4383          & 930                             & 3.2559                                                                             & 1.4024          & 930                             & 3.0538                                                                    & 1.4200          & 930                             & 2.8903                                                                    & 1.4297          \\
-			bank                                & 930                                     & 3.1161                                                                    & 1.4322          & 930                            & 3.0452                                                                    & 1.3827          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7355}          & 1.3985          & 930                             & 2.9280                                                                    & 1.4028          & 930                             & 3.1753                                                                    & 1.4151          \\
-			bike                                & 930                                     & 3.1409                                                                    & 1.2581          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.3914          & 930                             & 3.1946                                                                             & 1.3653          & 930                             & 3.0978                                                                    & 1.4978          & 930                             & 2.8086                                                                    & 1.4905          \\
-			car                                 & 930                                     & 3.1237                                                                    & 1.4229          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7237} & 1.3575          & 930                             & 2.8763                                                                             & 1.2987          & 930                             & 3.1538                                                                    & 1.3846          & 930                             & 3.1226                                                                    & 1.5473          \\
-			diabetic                            & 930                                     & 3.2452                                                                    & 1.3050          & 930                            & 3.0720                                                                    & 1.3913          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7785}          & 1.4067          & 930                             & 3.0290                                                                    & 1.4249          & 930                             & 2.8753                                                                    & 1.4940          \\
-			fish toxicity                       & 930                                     & 3.1452                                                                    & 1.3620          & 930                            & 3.0032                                                                    & 1.4455          & 930                             & 3.2172                                                                             & 1.3639          & 930                             & 3.1000                                                                    & 1.4088          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5344} & 1.3879          \\
-			forest fires                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8398} & 1.3690          & 930                            & 3.1215                                                                    & 1.4707          & 930                             & 3.0043                                                                             & 1.3181          & 930                             & 2.8860                                                                    & 1.3535          & 930                             & 3.1484                                                                    & 1.5261          \\
-			housing                             & 930                                     & 3.3129                                                                    & 1.3107          & 930                            & 2.9892                                                                    & 1.3927          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6871}          & 1.4833          & 930                             & 2.6968                                                                    & 1.4965          & 930                             & 3.3140                                                                    & 1.2356          \\
-			iris                                & 930                                     & 3.1204                                                                    & 1.3010          & 930                            & 3.0968                                                                    & 1.3909          & 930                             & 3.1269                                                                             & 1.4320          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366} & 1.4492          & 930                             & 3.0194                                                                    & 1.4352          \\
-			mushroom                            & 930                                     & 2.9312                                                                    & 1.3794          & 930                            & 3.1538                                                                    & 1.4031          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8473}          & 1.3836          & 930                             & 3.1215                                                                    & 1.4530          & 930                             & 2.9032                                                                    & 1.4714          \\
-			parkinsons                          & 930                                     & 2.9688                                                                    & 1.3850          & 930                            & 3.0086                                                                    & 1.3559          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6129}          & 1.4814          & 930                             & 3.1032                                                                    & 1.3804          & 930                             & 3.3065                                                                    & 1.3778          \\
-			student performance                 & 930                                     & 2.9409                                                                    & 1.4118          & 930                            & 3.1849                                                                    & 1.3804          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710}          & 1.4097          & 930                             & 3.1258                                                                    & 1.3655          & 930                             & 2.9774                                                                    & 1.4675          \\
-			wine quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8032} & 1.4440          & 930                            & 2.9204                                                                    & 1.3042          & 930                             & 3.2022                                                                             & 1.4104          & 930                             & 2.9247                                                                    & 1.3491          & 930                             & 3.1495                                                                    & 1.5171          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                          & \textbf{2.9747}                                                           & \textbf{1.3710} & \textbf{13950}                 & \textbf{2.9315}                                                           & \textbf{1.3960} & \textbf{13950}                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.8978}} & \textbf{1.3999} & \textbf{13950}                  & \textbf{2.9728}                                                           & \textbf{1.4464} & \textbf{13950}                  & \textbf{3.0047}                                                           & \textbf{1.4805} \\
-		\end{tabular}%
-	}
-
-\end{table}%
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reanalysis window sizes per dataset, across all runs and epochs.}
-	\label{fig:results:reanalysis:descriptive:descriptive}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reanalysis window sizes across all datasets, runs and epochs.}
-	\label{fig:results:reanalysis:descriptive:cd}
-\end{figure}
-
-\section{Burn In}\label{sec:results:bhh_variant_burn_in}
-
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different \index{burn in}burn in values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:burn_in:metrics}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{(all)}            &                                                                                    &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
-			\cmidrule{1-2}                      &                                      &                                                                                    &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{burn in}} & \multicolumn{1}{l}{\textbf{results}}                                               &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
-			\cmidrule{2-3}                      & \textbf{0}                           &                                                                                    &                 & \textbf{5}     &                                                                           &                 & \textbf{10}    &                                                                           &                 & \textbf{15}    &                                                                           &                 & \textbf{20}    &                 &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                       & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}    & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                  & 2.9151                                                                             & 1.3952          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6935} & 1.3934          & 930            & 2.9172                                                                    & 1.3837          & 930            & 2.8398                                                                    & 1.3524          & 930            & 3.6344          & 1.3574          \\
-			adult                               & 930                                  & 2.7366                                                                             & 1.4475          & 930            & 2.6430                                                                    & 1.3817          & 930            & 2.9892                                                                    & 1.4111          & 930            & 3.1731                                                                    & 1.4477          & 930            & 3.1355          & 1.4130          \\
-			air quality                         & 930                                  & 2.9097                                                                             & 1.4408          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6817} & 1.4270          & 930            & 2.7699                                                                    & 1.3443          & 930            & 3.3720                                                                    & 1.3137          & 930            & 3.2667          & 1.4119          \\
-			bike                                & 930                                  & 1.9237                                                                             & 0.9808          & 930            & 2.1806                                                                    & 1.0238          & 930            & 2.9237                                                                    & 1.2739          & 930            & 3.5054                                                                    & 1.1859          & 930            & 4.4667          & 0.8514          \\
-			car                                 & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3624}          & 1.2315          & 930            & 2.5882                                                                    & 1.4246          & 930            & 3.2978                                                                    & 1.3922          & 930            & 3.3796                                                                    & 1.2711          & 930            & 3.3720          & 1.4009          \\
-			fish toxicity                       & 930                                  & 3.0634                                                                             & 1.4589          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7935} & 1.4021          & 930            & 2.8204                                                                    & 1.5131          & 930            & 3.1022                                                                    & 1.3461          & 930            & 3.2204          & 1.2949          \\
-			forest fires                        & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8161}          & 1.3301          & 930            & 2.8495                                                                    & 1.3830          & 930            & 2.8645                                                                    & 1.4092          & 930            & 3.3774                                                                    & 1.3976          & 930            & 3.0925          & 1.4709          \\
-			housing                             & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6903}          & 1.3837          & 930            & 2.9516                                                                    & 1.3176          & 930            & 2.9968                                                                    & 1.4425          & 930            & 3.0581                                                                    & 1.3435          & 930            & 3.3032          & 1.5101          \\
-			iris                                & 930                                  & 2.9473                                                                             & 1.4608          & 930            & 2.9720                                                                    & 1.3675          & 930            & 3.1903                                                                    & 1.4493          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710} & 1.3694          & 930            & 3.1194          & 1.3872          \\
-			mushroom                            & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2065}          & 1.2486          & 930            & 2.9376                                                                    & 1.2977          & 930            & 3.1613                                                                    & 1.2966          & 930            & 3.1441                                                                    & 1.4015          & 930            & 3.5226          & 1.5006          \\
-			parkinsons                          & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2796}          & 1.2822          & 930            & 2.8892                                                                    & 1.2474          & 930            & 2.7065                                                                    & 1.3143          & 930            & 3.3968                                                                    & 1.4175          & 930            & 3.7280          & 1.3295          \\
-			student performance                 & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1452}          & 1.2052          & 930            & 2.6946                                                                    & 1.4032          & 930            & 3.0968                                                                    & 1.3525          & 930            & 3.4581                                                                    & 1.3539          & 930            & 3.6054          & 1.2312          \\
-			wine quality                        & 930                                  & 2.9699                                                                             & 1.4373          & 930            & 3.0108                                                                    & 1.3041          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6634} & 1.4186          & 930            & 3.1247                                                                    & 1.3980          & 930            & 3.2312          & 1.4471          \\
-			bank                                & 930                                  & 2.7301                                                                             & 1.3210          & 930            & 2.8194                                                                    & 1.3350          & 930            & 2.8570                                                                    & 1.4848          & 930            & 2.9312                                                                    & 1.3841          & 930            & 3.6624          & 1.3391          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13020}                       & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.6211}} & \textbf{1.3814} & \textbf{13020} & \textbf{2.7647}                                                           & \textbf{1.3553} & \textbf{13020} & \textbf{2.9468}                                                           & \textbf{1.4045} & \textbf{13020} & \textbf{3.1881}                                                           & \textbf{1.3754} & \textbf{13020} & \textbf{3.4543} & \textbf{1.4061} \\
-		\end{tabular}%
-	}
-\end{table}%
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_burn_in/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying burn in values per dataset, across all runs and epochs.}
-	\label{fig:results:burn_in:descriptive:descriptive}
-\end{figure}
-
-The critical difference plot as presented in Figure \ref{fig:results:burn_in:descriptive:cd} shows the statistical significance between burn in window sizes overall, across all datasets.
-One can clearly see from this plot that little to no burn in is preferred in most of the cases.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_burn_in/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying burn in values across all datasets, runs and epochs.}
-	\label{fig:results:burn_in:descriptive:cd}
-\end{figure}
-
-\section{Normalisation}\label{sec:results:bhh_variant_normalise}
-
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for \index{normalisation}normalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:normalise:metrics}%
-	\par\bigskip
-	\resizebox{0.75\textwidth}{!}{
-		\begin{tabular}{rcccccc}
-			\textbf{epoch}                     & \multicolumn{1}{l}{\textbf{(all)}}         &                                                                                    &                 &                                   &                                                                           &                 \\
-			\cmidrule{1-2}                     &                                            &                                                                                    &                 &                                   &                                                                           &                 \\
-			                                   & \multicolumn{1}{l}{\textbf{normalisation}} & \multicolumn{1}{l}{\textbf{metric}}                                                &                 &                                   &                                                                           &                 \\
-			\cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{false}}         &                                                                                    &                 & \multicolumn{1}{l}{\textbf{true}} &                                                                           &                 \\
-			\cmidrule{2-7}    \textbf{dataset} & \textbf{count}                             & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
-			\midrule
-			abalone                            & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5002          & 930                               & 1.5065                                                                    & 0.5002          \\
-			adult                              & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4710}          & 0.4994          & 930                               & 1.4968                                                                    & 0.5003          \\
-			air quality                        & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4892}          & 0.5002          & 930                               & 1.5108                                                                    & 0.5002          \\
-			bank                               & 930                                        & 1.5484                                                                             & 0.4979          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4516} & 0.4979          \\
-			bike                               & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4978}          & 0.5003          & 930                               & 1.5022                                                                    & 0.5003          \\
-			car                                & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4258}          & 0.4947          & 930                               & 1.5742                                                                    & 0.4947          \\
-			diabetic                           & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4753}          & 0.4997          & 930                               & 1.5247                                                                    & 0.4997          \\
-			fish toxicity                      & 930                                        & 1.5505                                                                             & 0.4977          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4495} & 0.4977          \\
-			forest fires                       & 930                                        & 1.5054                                                                             & 0.5002          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4946} & 0.5002          \\
-			housing                            & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4720}          & 0.4995          & 930                               & 1.5280                                                                    & 0.4995          \\
-			iris                               & 930                                        & 1.5645                                                                             & 0.4961          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4355} & 0.4961          \\
-			mushroom                           & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4323}          & 0.4957          & 930                               & 1.5667                                                                    & 0.4958          \\
-			parkinsons                         & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4000}          & 0.4902          & 930                               & 1.6000                                                                    & 0.4902          \\
-			student performance                & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3892}          & 0.4878          & 930                               & 1.6108                                                                    & 0.4878          \\
-			wine quality                       & 930                                        & 1.5473                                                                             & 0.4980          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4527} & 0.4980          \\
-			\midrule
-			\textbf{overall}                   & \textbf{13950}                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4842}} & \textbf{0.4998} & \textbf{13950}                    & \textbf{1.5136}                                                           & \textbf{0.4998} \\
-		\end{tabular}%
-	}
-\end{table}%
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_normalise/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with normalisation toggled per dataset, across all runs and epochs.}
-	\label{fig:results:normalise:descriptive:descriptive}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_normalise/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with normalisation toggled across all datasets, runs and epochs.}
-	\label{fig:results:normalise:descriptive:cd}
-\end{figure}
-
-\section{Discounted Rewards}\label{sec:results:bhh_variant_discounted_rewards}
-
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for \index{discounted rewards}discounted rewards toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:discounted_rewards:metrics}%
-	\par\bigskip
-	\resizebox{0.85\textwidth}{!}{
-		\begin{tabular}{rcccccc}
-			epoch                              & \multicolumn{1}{l}{(all)}                       &                                                                                    &                 &                                   &                                                                           &                 \\
-			\cmidrule{1-2}                     &                                                 &                                                                                    &                 &                                   &                                                                           &                 \\
-			                                   & \multicolumn{1}{l}{\textbf{discounted rewards}} & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                   &                                                                           &                 \\
-			\cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{FALSE}}              &                                                                                    &                 & \multicolumn{1}{l}{\textbf{TRUE}} &                                                                           &                 \\
-			\cmidrule{2-7}    \textbf{dataset} & \textbf{count}                                  & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
-			\midrule
-			abalone                            & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4914}          & 0.5002          & 930                               & 1.5086                                                                    & 0.5002          \\
-			adult                              & 930                                             & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4645} & 0.4990          \\
-			air quality                        & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4613}          & 0.4988          & 930                               & 1.5387                                                                    & 0.4988          \\
-			bank                               & 930                                             & 1.5161                                                                             & 0.5000          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4839} & 0.5000          \\
-			bike                               & 930                                             & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
-			car                                & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4280}          & 0.4950          & 930                               & 1.5720                                                                    & 0.4950          \\
-			diabetic                           & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4699}          & 0.4994          & 930                               & 1.5301                                                                    & 0.4994          \\
-			fish toxicity                      & 930                                             & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
-			forest fires                       & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4742}          & 0.4996          & 930                               & 1.5258                                                                    & 0.4996          \\
-			housing                            & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4237}          & 0.4944          & 930                               & 1.5763                                                                    & 0.4944          \\
-			iris                               & 930                                             & 1.5903                                                                             & 0.4920          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4097} & 0.4920          \\
-			mushroom                           & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3946}          & 0.4890          & 930                               & 1.5806                                                                    & 0.4937          \\
-			parkinsons                         & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3710}          & 0.4833          & 930                               & 1.6290                                                                    & 0.4833          \\
-			student performance                & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4398}          & 0.4966          & 930                               & 1.5602                                                                    & 0.4966          \\
-			wine quality                       & 930                                             & 1.5570                                                                             & 0.4970          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4430} & 0.4970          \\
-			\midrule
-			\textbf{overall}                   & \textbf{13950}                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4747}} & \textbf{0.4994} & \textbf{13950}                    & \textbf{1.5214}                                                           & \textbf{0.4996} \\
-		\end{tabular}%
-	}
-\end{table}%
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with discounted rewards toggled per datasets, across all runs and epochs.}
-	\label{fig:results:discounted_rewards:descriptive:descriptive}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with discounted rewards toggled across all datasets, runs and epochs.}
-	\label{fig:results:discounted_rewards:descriptive:cd}
-\end{figure}
-
-\section{Overfitting}\label{sec:results:overfitting}
-
-\section{Practical Applications}\label{sec:results:practical_applications}
-
-\section{Summary}\label{sec:results:summary}
+% \section{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
+
+% % Table generated by Excel2LaTeX from sheet 'results - test - loss'
+% \begin{table}[htbp]
+% 	\centering
+% 	\caption{Empirical results showing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
+% 	\label{tab:results:standalone:metrics:test_loss}%
+% 	\par\bigskip
+% 	\resizebox{\textwidth}{!}{
+% 		\begin{tabular}{rlccc|c|c|c|c|c|ccccc}
+% 			epoch                                                                          & 30                 &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
+% 			                                                                               &                    &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
+% 			                                                                               &                    & \multicolumn{1}{l}{\textbf{heuristic}}                                         &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
+% 			\cmidrule{3-3}\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}    \textbf{dataset} & \textbf{statistic} & \textbf{adagrad}                                                               & \textbf{adam}                                                                  & \textbf{nag}                                                                   & \textbf{bhh\_gd}                                & \textbf{rmsprop}                                                               & \textbf{bhh\_all}                               & \textbf{adadelta}                                                              & \textbf{bhh\_mh}                                & \textbf{ga}                                     & \textbf{sgd}                                    & \textbf{pso}                                    & \textbf{momentum}                               & \textbf{de}                                     \\
+% 			\midrule
+% 			abalone                                                                        & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .506,  .776,  .486}1.967785                                   & \cellcolor[rgb]{ .494,  .773,  .486}1.965134827                                & \cellcolor[rgb]{ .765,  .851,  .502}2.0156043                                  & \cellcolor[rgb]{ .749,  .847,  .502}2.012517173 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{1.94553315}  & \cellcolor[rgb]{ 1,  .922,  .518}2.058704583    & \cellcolor[rgb]{ .788,  .859,  .502}2.019921077                                & \cellcolor[rgb]{ .996,  .827,  .502}2.29420573  & \cellcolor[rgb]{ .984,  .612,  .459}2.81545685  & \cellcolor[rgb]{ .992,  .773,  .49}2.42804241   & \cellcolor[rgb]{ .98,  .522,  .443}3.038417873  & \cellcolor[rgb]{ .992,  .745,  .486}2.494169393 & \cellcolor[rgb]{ .973,  .412,  .42}3.295858177  \\
+% 			                                                                               & std                & 0.031577789                                                                    & 0.034949967                                                                    & 0.034657443                                                                    & 0.068121366                                     & 0.035183664                                                                    & 0.087594488                                     & 0.034405331                                                                    & 0.055085207                                     & 0.055148148                                     & 0.028810924                                     & 0.293755503                                     & 0.029086341                                     & 0.016489872                                     \\
+% 			adult                                                                          & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ 1,  .922,  .518}0.346737798                                   & \cellcolor[rgb]{ 1,  .922,  .518}0.38233353                                    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.313320884} & \cellcolor[rgb]{ .788,  .859,  .502}0.335180995 & \cellcolor[rgb]{ .933,  .902,  .514}0.343292783                                & \cellcolor[rgb]{ .973,  .412,  .42}586.2065996  & \cellcolor[rgb]{ .467,  .765,  .486}0.317677033                                & \cellcolor[rgb]{ 1,  .922,  .518}0.363543899    & \cellcolor[rgb]{ 1,  .922,  .518}0.392047161    & \cellcolor[rgb]{ .388,  .745,  .482}0.313329677 & \cellcolor[rgb]{ 1,  .922,  .518}1.217724345    & \cellcolor[rgb]{ .388,  .745,  .482}0.313444396 & \cellcolor[rgb]{ 1,  .922,  .518}0.639695856    \\
+% 			                                                                               & std                & 0.003704238                                                                    & 0.018067239                                                                    & 0.000510377                                                                    & 0.043628962                                     & 0.014659665                                                                    & 1261.204704                                     & 0.005277776                                                                    & 0.020803371                                     & 0.020086997                                     & 0.000411017                                     & 0.496591684                                     & 0.0003947                                       & 0.042558869                                     \\
+% 			air quality                                                                    & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .651,  .82,  .494}0.256871193                                 & \cellcolor[rgb]{ .827,  .871,  .506}0.260623969                                & \cellcolor[rgb]{ .647,  .82,  .494}0.256829053                                 & \cellcolor[rgb]{ 1,  .922,  .518}0.264177871    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.251334045} & \cellcolor[rgb]{ .996,  .827,  .502}0.272859303 & \cellcolor[rgb]{ .647,  .82,  .494}0.256781683                                 & \cellcolor[rgb]{ .976,  .914,  .514}0.263703859 & \cellcolor[rgb]{ .996,  .792,  .494}0.275862527 & \cellcolor[rgb]{ .988,  .69,  .475}0.285172782  & \cellcolor[rgb]{ .984,  .608,  .459}0.292264593 & \cellcolor[rgb]{ .984,  .604,  .459}0.292851261 & \cellcolor[rgb]{ .973,  .412,  .42}0.309698115  \\
+% 			                                                                               & std                & 0.007475522                                                                    & 0.008912099                                                                    & 0.005955119                                                                    & 0.011452365                                     & 0.007814891                                                                    & 0.016310047                                     & 0.00630808                                                                     & 0.007306605                                     & 0.008162884                                     & 0.014769128                                     & 0.022648597                                     & 0.016417541                                     & 0.017044223                                     \\
+% 			bank                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .459,  .765,  .486}0.209641222                                & \cellcolor[rgb]{ .4,  .745,  .482}0.206461621                                  & \cellcolor[rgb]{ .588,  .8,  .49}0.2164275                                     & \cellcolor[rgb]{ .588,  .8,  .49}0.21643132     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.205779476} & \cellcolor[rgb]{ 1,  .886,  .514}0.245610465    & \cellcolor[rgb]{ .627,  .812,  .494}0.218599386                                & \cellcolor[rgb]{ .996,  .839,  .502}0.256171151 & \cellcolor[rgb]{ .988,  .686,  .475}0.28813827  & \cellcolor[rgb]{ 1,  .922,  .518}0.238179998    & \cellcolor[rgb]{ .973,  .412,  .42}0.345448185  & \cellcolor[rgb]{ 1,  .922,  .518}0.238550439    & \cellcolor[rgb]{ .976,  .424,  .424}0.343699166 \\
+% 			                                                                               & std                & 0.004750498                                                                    & 0.004040969                                                                    & 0.005944898                                                                    & 0.004889433                                     & 0.005654034                                                                    & 0.064531685                                     & 0.003821749                                                                    & 0.010550504                                     & 0.012801143                                     & 0.005568018                                     & 0.033990143                                     & 0.004820977                                     & 0.028120079                                     \\
+% 			bike                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.045805387} & \cellcolor[rgb]{ .592,  .804,  .494}0.068179412                                & \cellcolor[rgb]{ .882,  .886,  .51}0.099539486                                 & \cellcolor[rgb]{ .467,  .765,  .486}0.054496914 & \cellcolor[rgb]{ 1,  .922,  .518}0.112259627                                   & \cellcolor[rgb]{ .565,  .796,  .49}0.065136647  & \cellcolor[rgb]{ .588,  .8,  .49}0.06793708                                    & \cellcolor[rgb]{ 1,  .902,  .514}0.11787523     & \cellcolor[rgb]{ .992,  .761,  .486}0.153095534 & \cellcolor[rgb]{ .992,  .733,  .482}0.159868436 & \cellcolor[rgb]{ .992,  .773,  .49}0.150273084  & \cellcolor[rgb]{ .992,  .725,  .482}0.161397393 & \cellcolor[rgb]{ .973,  .412,  .42}0.239867227  \\
+% 			                                                                               & std                & 0.001725608                                                                    & 0.068117237                                                                    & 0.001754469                                                                    & 0.005239285                                     & 0.103490928                                                                    & 0.019626763                                     & 0.002076596                                                                    & 0.005954748                                     & 0.005079692                                     & 0.002759                                        & 0.025177188                                     & 0.003354245                                     & 0.039791214                                     \\
+% 			car                                                                            & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .729,  .843,  .502}0.202726327                                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.09724452}  & \cellcolor[rgb]{ .867,  .882,  .51}0.245363623                                 & \cellcolor[rgb]{ .62,  .812,  .494}0.16895294   & \cellcolor[rgb]{ .408,  .749,  .482}0.103937737                                & \cellcolor[rgb]{ .58,  .8,  .49}0.15718728      & \cellcolor[rgb]{ 1,  .922,  .518}0.285888989                                   & \cellcolor[rgb]{ .992,  .733,  .482}0.489062582 & \cellcolor[rgb]{ .98,  .502,  .439}0.737354357  & \cellcolor[rgb]{ .98,  .533,  .443}0.703539757  & \cellcolor[rgb]{ .988,  .667,  .471}0.563173207 & \cellcolor[rgb]{ .98,  .506,  .439}0.73217904   & \cellcolor[rgb]{ .973,  .412,  .42}0.833160108  \\
+% 			                                                                               & std                & 0.018356416                                                                    & 0.023870777                                                                    & 0.028744869                                                                    & 0.025441117                                     & 0.031133074                                                                    & 0.033710554                                     & 0.027353972                                                                    & 0.076505599                                     & 0.062600847                                     & 0.052091474                                     & 0.157928484                                     & 0.042705727                                     & 0.074182791                                     \\
+% 			diabetic                                                                       & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .694,  .831,  .498}0.889537739                                & \cellcolor[rgb]{ 1,  .898,  .514}0.919339482                                   & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.880898965} & \cellcolor[rgb]{ .98,  .914,  .514}0.897587026  & \cellcolor[rgb]{ .918,  .894,  .51}0.895749019                                 & \cellcolor[rgb]{ .973,  .412,  .42}1.298319185  & \cellcolor[rgb]{ .49,  .773,  .486}0.883864405                                 & \cellcolor[rgb]{ 1,  .902,  .518}0.913694494    & \cellcolor[rgb]{ .996,  .843,  .506}0.961291775 & \cellcolor[rgb]{ .976,  .914,  .514}0.897429714 & \cellcolor[rgb]{ .996,  .835,  .502}0.966103049 & \cellcolor[rgb]{ 1,  .922,  .518}0.898038783    & \cellcolor[rgb]{ .988,  .694,  .475}1.077362637 \\
+% 			                                                                               & std                & 0.004272255                                                                    & 0.00981794                                                                     & 0.003758597                                                                    & 0.010748722                                     & 0.004045488                                                                    & 0.659754133                                     & 0.004759234                                                                    & 0.008388702                                     & 0.00657199                                      & 0.003551413                                     & 0.016450474                                     & 0.002801135                                     & 0.0391395                                       \\
+% 			fish toxicity                                                                  & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .588,  .8,  .49}0.09908239                                    & \cellcolor[rgb]{ .451,  .761,  .482}0.097196901                                & \cellcolor[rgb]{ .831,  .871,  .506}0.10233624                                 & \cellcolor[rgb]{ 1,  .91,  .518}0.105584544     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.096326802} & \cellcolor[rgb]{ 1,  .922,  .518}0.104598099    & \cellcolor[rgb]{ .773,  .855,  .502}0.101567158                                & \cellcolor[rgb]{ .976,  .914,  .514}0.104293618 & \cellcolor[rgb]{ 1,  .863,  .506}0.109342435    & \cellcolor[rgb]{ .976,  .475,  .435}0.139280655 & \cellcolor[rgb]{ 1,  .855,  .506}0.109946059    & \cellcolor[rgb]{ .973,  .412,  .42}0.144088336  & \cellcolor[rgb]{ .992,  .733,  .482}0.119344204 \\
+% 			                                                                               & std                & 0.008463336                                                                    & 0.006948088                                                                    & 0.007611236                                                                    & 0.008228438                                     & 0.008021585                                                                    & 0.008136956                                     & 0.008882708                                                                    & 0.00895412                                      & 0.008990894                                     & 0.012326524                                     & 0.012481736                                     & 0.012407706                                     & 0.0130782                                       \\
+% 			forest fires                                                                   & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ 1,  .922,  .518}0.064321917                                   & \cellcolor[rgb]{ .557,  .792,  .49}0.052658676                                 & \cellcolor[rgb]{ .851,  .878,  .506}0.05923886                                 & \cellcolor[rgb]{ .824,  .871,  .506}0.058617148 & \cellcolor[rgb]{ 1,  .922,  .518}0.062552555                                   & \cellcolor[rgb]{ 1,  .89,  .514}0.080966845     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.048831474} & \cellcolor[rgb]{ .976,  .914,  .514}0.06209696  & \cellcolor[rgb]{ .553,  .792,  .49}0.05260701   & \cellcolor[rgb]{ .992,  .722,  .482}0.180571383 & \cellcolor[rgb]{ 1,  .914,  .518}0.069210426    & \cellcolor[rgb]{ .992,  .706,  .478}0.188476672 & \cellcolor[rgb]{ .973,  .412,  .42}0.359831599  \\
+% 			                                                                               & std                & 0.039911806                                                                    & 0.039243672                                                                    & 0.031685801                                                                    & 0.034163415                                     & 0.039170629                                                                    & 0.069099845                                     & 0.032095867                                                                    & 0.038470671                                     & 0.025957821                                     & 0.008365929                                     & 0.047244856                                     & 0.010081381                                     & 0.089999905                                     \\
+% 			housing                                                                        & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .518,  .78,  .486}0.088925893                                 & \cellcolor[rgb]{ .404,  .749,  .482}0.08481865                                 & \cellcolor[rgb]{ .612,  .808,  .494}0.092269667                                & \cellcolor[rgb]{ .69,  .831,  .498}0.095072459  & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.08422333}  & \cellcolor[rgb]{ .663,  .824,  .498}0.094078934 & \cellcolor[rgb]{ 1,  .922,  .518}0.105999965                                   & \cellcolor[rgb]{ 1,  .867,  .51}0.116883814     & \cellcolor[rgb]{ .996,  .812,  .498}0.127851649 & \cellcolor[rgb]{ .984,  .576,  .455}0.173521216 & \cellcolor[rgb]{ .992,  .722,  .482}0.145240159 & \cellcolor[rgb]{ .984,  .588,  .455}0.171302372 & \cellcolor[rgb]{ .973,  .412,  .42}0.205724786  \\
+% 			                                                                               & std                & 0.012490666                                                                    & 0.011213172                                                                    & 0.015551947                                                                    & 0.014823695                                     & 0.014924594                                                                    & 0.017302471                                     & 0.018700331                                                                    & 0.019460369                                     & 0.020192262                                     & 0.022837541                                     & 0.029813905                                     & 0.017916976                                     & 0.036445189                                     \\
+% 			iris                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .788,  .859,  .502}0.216138929                                & \cellcolor[rgb]{ .514,  .78,  .486}0.120305813                                 & \cellcolor[rgb]{ .416,  .753,  .482}0.084967127                                & \cellcolor[rgb]{ 1,  .855,  .506}0.372908547    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.075287772} & \cellcolor[rgb]{ .859,  .878,  .506}0.241094806 & \cellcolor[rgb]{ .996,  .808,  .498}0.426015649                                & \cellcolor[rgb]{ .686,  .831,  .498}0.180917533 & \cellcolor[rgb]{ 1,  .922,  .518}0.289495446    & \cellcolor[rgb]{ .992,  .773,  .49}0.469415404  & \cellcolor[rgb]{ .973,  .412,  .42}0.896458149  & \cellcolor[rgb]{ .992,  .745,  .486}0.502796506 & \cellcolor[rgb]{ .98,  .494,  .435}0.802733988  \\
+% 			                                                                               & std                & 0.059156887                                                                    & 0.097731271                                                                    & 0.041820159                                                                    & 1.119111663                                     & 0.045657899                                                                    & 0.295227964                                     & 0.071608458                                                                    & 0.163729792                                     & 0.117435582                                     & 0.087556703                                     & 0.844445785                                     & 0.072001841                                     & 0.684394699                                     \\
+% 			mushroom                                                                       & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .549,  .792,  .49}0.002577835                                 & \cellcolor[rgb]{ .467,  .765,  .486}0.001321295                                & \cellcolor[rgb]{ 1,  .922,  .518}0.009417256                                   & \cellcolor[rgb]{ .439,  .757,  .482}0.000906998 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{8.30695E-05} & \cellcolor[rgb]{ .718,  .839,  .498}0.005152476 & \cellcolor[rgb]{ .655,  .82,  .494}0.00417499                                  & \cellcolor[rgb]{ 1,  .871,  .51}0.077415858     & \cellcolor[rgb]{ .984,  .561,  .451}0.489160105 & \cellcolor[rgb]{ .996,  .796,  .494}0.179705445 & \cellcolor[rgb]{ 1,  .886,  .514}0.061137885    & \cellcolor[rgb]{ .992,  .749,  .486}0.241811308 & \cellcolor[rgb]{ .973,  .412,  .42}0.687017333  \\
+% 			                                                                               & std                & 0.000662841                                                                    & 0.004905902                                                                    & 0.002279151                                                                    & 0.001259819                                     & 6.96496E-05                                                                    & 0.012039998                                     & 0.000905097                                                                    & 0.019865901                                     & 0.024593143                                     & 0.009208458                                     & 0.06033175                                      & 0.012790223                                     & 0.01638976                                      \\
+% 			parkinsons                                                                     & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .51,  .776,  .486}0.056277858                                 & \cellcolor[rgb]{ .412,  .749,  .482}0.054480758                                & \cellcolor[rgb]{ 1,  .922,  .518}0.065451464                                   & \cellcolor[rgb]{ .639,  .816,  .494}0.058737776 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.053985977} & \cellcolor[rgb]{ .639,  .816,  .494}0.05873821  & \cellcolor[rgb]{ .69,  .831,  .498}0.05967759                                  & \cellcolor[rgb]{ 1,  .918,  .518}0.065774264    & \cellcolor[rgb]{ 1,  .898,  .514}0.066854953    & \cellcolor[rgb]{ .976,  .467,  .431}0.092323864 & \cellcolor[rgb]{ 1,  .894,  .514}0.067066667    & \cellcolor[rgb]{ .973,  .412,  .42}0.095371925  & \cellcolor[rgb]{ .984,  .604,  .459}0.084321583 \\
+% 			                                                                               & std                & 0.001432862                                                                    & 0.001998668                                                                    & 0.002301839                                                                    & 0.002859752                                     & 0.001547989                                                                    & 0.002811075                                     & 0.001691389                                                                    & 0.002548177                                     & 0.003281185                                     & 0.008302374                                     & 0.005043049                                     & 0.009431099                                     & 0.008978517                                     \\
+% 			student performance                                                            & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.165552792} & \cellcolor[rgb]{ .98,  .522,  .443}0.492891063                                 & \cellcolor[rgb]{ .471,  .769,  .486}0.169715979                                & \cellcolor[rgb]{ 1,  .855,  .506}0.245419875    & \cellcolor[rgb]{ .973,  .412,  .42}0.572439541                                 & \cellcolor[rgb]{ 1,  .871,  .51}0.235942235     & \cellcolor[rgb]{ .49,  .773,  .486}0.170794263                                 & \cellcolor[rgb]{ .969,  .91,  .514}0.194664435  & \cellcolor[rgb]{ 1,  .922,  .518}0.196187948    & \cellcolor[rgb]{ .933,  .902,  .514}0.193041307 & \cellcolor[rgb]{ .984,  .573,  .451}0.456490052 & \cellcolor[rgb]{ .925,  .898,  .51}0.192542094  & \cellcolor[rgb]{ 1,  .918,  .518}0.201390878    \\
+% 			                                                                               & std                & 0.011258528                                                                    & 0.105388532                                                                    & 0.010966961                                                                    & 0.133694251                                     & 0.05360667                                                                     & 0.10249181                                      & 0.010377173                                                                    & 0.014024256                                     & 0.009798773                                     & 0.011295962                                     & 0.049033016                                     & 0.011402763                                     & 0.011757846                                     \\
+% 			wine quality                                                                   & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
+% 			                                                                               & avg                & \cellcolor[rgb]{ .631,  .816,  .494}1.06505343                                 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{1.039511785} & \cellcolor[rgb]{ .698,  .831,  .498}1.07178488                                 & \cellcolor[rgb]{ 1,  .922,  .518}1.102805083    & \cellcolor[rgb]{ .502,  .776,  .486}1.051442793                                & \cellcolor[rgb]{ .804,  .863,  .506}1.082728853 & \cellcolor[rgb]{ .788,  .859,  .502}1.080905303                                & \cellcolor[rgb]{ .996,  .839,  .502}1.166586247 & \cellcolor[rgb]{ .992,  .725,  .482}1.251597837 & \cellcolor[rgb]{ .996,  .843,  .502}1.16477848  & \cellcolor[rgb]{ .988,  .659,  .467}1.3045869   & \cellcolor[rgb]{ .996,  .824,  .502}1.17741444  & \cellcolor[rgb]{ .973,  .412,  .42}1.489554557  \\
+% 			                                                                               & std                & 0.023560192                                                                    & 0.018361143                                                                    & 0.024922811                                                                    & 0.039250798                                     & 0.020795097                                                                    & 0.026483778                                     & 0.021109916                                                                    & 0.030251195                                     & 0.045716819                                     & 0.022984412                                     & 0.114260845                                     & 0.01919043                                      & 0.092922599                                     \\
+% 			\bottomrule
+% 		\end{tabular}%
+% 	}
+% \end{table}%
+
+% % Table generated by Excel2LaTeX from sheet 'results - test - rank'
+% \begin{table}[htbp]
+% 	\centering
+% 	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}
+% 	\label{tab:results:standalone:metrics:rank}%
+% 	\par\bigskip
+% 	\resizebox{\textwidth}{!}{
+% 		\begin{tabular}{rcccc|c|c|c|c|c|ccccc}
+% 			epoch                                                                          & \multicolumn{1}{l}{(all)}              &                                                                                    &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
+% 			                                                                               &                                        &                                                                                    &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
+% 			                                                                               &                                        & \multicolumn{1}{l}{\textbf{heuristic}}                                             &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
+% 			\cmidrule{3-3}\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}    \textbf{dataset} & \multicolumn{1}{l}{\textbf{statistic}} & \textbf{adagrad}                                                                   & \textbf{adam}                                                             & \textbf{nag}                                                              & \textbf{bhh\_gd}                               & \textbf{rmsprop}                                                          & \textbf{bhh\_all}                            & \textbf{adadelta}                           & \textbf{bhh\_mh}                               & \textbf{ga}                                    & \textbf{sgd}                                    & \textbf{pso}                                    & \textbf{momentum}                              & \textbf{de}                                    \\
+% 			\midrule
+% 			abalone                                                                        & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2215}          & 2.3989                                                                    & 4.2731                                                                    & 4.7032                                         & 4.6172                                                                    & 5.9376                                       & 5.3129                                      & 8.1882                                         & 11.1108                                        & 8.6280                                          & 11.2559                                         & 9.8151                                         & 12.5376                                        \\
+% 			                                                                               & std                                    & 1.5913                                                                             & 1.8873                                                                    & 1.5419                                                                    & 2.1080                                         & 2.6504                                                                    & 2.3994                                       & 1.4782                                      & 1.1947                                         & 1.1017                                         & 1.0193                                          & 1.8265                                          & 1.1601                                         & 1.3291                                         \\
+% 			adult                                                                          & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 5.8978                                                                             & 7.6258                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5140} & 5.3258                                         & 6.6892                                                                    & 12.0194                                      & 2.5258                                      & 7.9409                                         & 9.5860                                         & 3.0065                                          & 11.5344                                         & 3.8699                                         & 10.9462                                        \\
+% 			                                                                               & std                                    & 1.6171                                                                             & 2.0293                                                                    & 0.7250                                                                    & 1.8985                                         & 1.8347                                                                    & 2.7430                                       & 1.3543                                      & 1.6391                                         & 1.7015                                         & 1.4999                                          & 2.0122                                          & 1.7090                                         & 1.8965                                         \\
+% 			air quality                                                                    & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 3.6409                                                                             & 5.4312                                                                    & 3.8194                                                                    & 5.0817                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.4452} & 6.6860                                       & 5.2441                                      & 6.3570                                         & 7.8204                                         & 10.6613                                         & 9.9151                                          & 11.7559                                        & 11.1419                                        \\
+% 			                                                                               & std                                    & 2.2588                                                                             & 2.6198                                                                    & 2.2285                                                                    & 2.7618                                         & 2.5704                                                                    & 3.0613                                       & 3.1622                                      & 2.3031                                         & 2.2652                                         & 1.6061                                          & 2.2882                                          & 1.4730                                         & 2.2361                                         \\
+% 			bank                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 2.5495                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.0796} & 4.2871                                                                    & 4.8828                                         & 3.4645                                                                    & 6.2419                                       & 5.6720                                      & 9.7495                                         & 10.9817                                        & 8.2774                                          & 11.8376                                         & 8.4774                                         & 12.4989                                        \\
+% 			                                                                               & std                                    & 1.5980                                                                             & 1.5871                                                                    & 1.7325                                                                    & 1.7017                                         & 2.2090                                                                    & 2.1571                                       & 1.2411                                      & 1.0482                                         & 1.2165                                         & 1.0304                                          & 1.4638                                          & 1.0682                                         & 1.2243                                         \\
+% 			bike                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7204}          & 3.6925                                                                    & 6.4516                                                                    & 3.8441                                         & 6.2624                                                                    & 4.2151                                       & 5.3602                                      & 7.4108                                         & 9.2269                                         & 10.3355                                         & 9.3086                                          & 10.7086                                        & 12.4634                                        \\
+% 			                                                                               & std                                    & 1.3839                                                                             & 4.0038                                                                    & 1.0199                                                                    & 1.3983                                         & 4.5803                                                                    & 1.3611                                       & 1.1555                                      & 1.0076                                         & 1.1835                                         & 1.4193                                          & 1.7615                                          & 1.4233                                         & 1.4648                                         \\
+% 			car                                                                            & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 4.7634                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6226} & 6.0785                                                                    & 3.3473                                         & 2.3269                                                                    & 3.5624                                       & 7.7344                                      & 8.8505                                         & 10.7763                                        & 10.2452                                         & 8.3613                                          & 10.9226                                        & 12.4086                                        \\
+% 			                                                                               & std                                    & 0.9383                                                                             & 1.4053                                                                    & 0.7991                                                                    & 1.3499                                         & 1.4091                                                                    & 1.3152                                       & 1.7464                                      & 1.4128                                         & 1.4715                                         & 1.4474                                          & 1.6222                                          & 1.3489                                         & 1.4915                                         \\
+% 			diabetic                                                                       & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 2.7796                                                                             & 7.1484                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8118} & 5.2269                                         & 6.7376                                                                    & 9.3968                                       & 2.6753                                      & 8.5570                                         & 11.2011                                        & 5.9215                                          & 10.7022                                         & 6.3355                                         & 12.5065                                        \\
+% 			                                                                               & std                                    & 1.6587                                                                             & 2.2265                                                                    & 1.4127                                                                    & 2.1860                                         & 2.5767                                                                    & 3.0221                                       & 1.6286                                      & 1.1699                                         & 1.4132                                         & 1.5421                                          & 1.0674                                          & 1.6118                                         & 1.2417                                         \\
+% 			fish toxicity                                                                  & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 4.2645                                                                             & 3.6022                                                                    & 5.8914                                                                    & 5.4118                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.5946} & 5.8290                                       & 7.9140                                      & 6.3849                                         & 6.7043                                         & 11.5785                                         & 7.5731                                          & 12.2301                                        & 10.0215                                        \\
+% 			                                                                               & std                                    & 2.6142                                                                             & 2.4453                                                                    & 2.6288                                                                    & 2.6649                                         & 2.3292                                                                    & 2.8557                                       & 3.4287                                      & 2.9437                                         & 2.8200                                         & 1.4587                                          & 2.9817                                          & 1.3822                                         & 2.3585                                         \\
+% 			forest fires                                                                   & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 5.1559                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{4.2688} & 5.6882                                                                    & 4.6935                                         & 5.0355                                                                    & 5.4839                                       & 6.5161                                      & 5.4591                                         & 7.3667                                         & 10.8129                                         & 6.4796                                          & 11.7065                                        & 12.3333                                        \\
+% 			                                                                               & std                                    & 2.9217                                                                             & 2.9841                                                                    & 2.2149                                                                    & 2.7594                                         & 3.1431                                                                    & 3.1070                                       & 3.0823                                      & 2.6680                                         & 2.3704                                         & 1.2070                                          & 3.3539                                          & 1.3250                                         & 1.9228                                         \\
+% 			housing                                                                        & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 3.4484                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.3344} & 4.6839                                                                    & 4.4742                                         & 3.6946                                                                    & 4.3763                                       & 7.5903                                      & 7.5441                                         & 7.8839                                         & 11.4075                                         & 9.9409                                          & 11.2731                                        & 11.3484                                        \\
+% 			                                                                               & std                                    & 2.0251                                                                             & 1.8193                                                                    & 2.6579                                                                    & 2.3125                                         & 2.1662                                                                    & 2.4377                                       & 2.7475                                      & 1.7363                                         & 2.0991                                         & 1.5278                                          & 2.3166                                          & 1.5059                                         & 2.0965                                         \\
+% 			iris                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 6.3946                                                                             & 3.5839                                                                    & 3.5548                                                                    & 4.7473                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6968} & 5.2204                                       & 11.3527                                     & 6.6075                                         & 8.2473                                         & 10.3796                                         & 8.2731                                          & 11.0548                                        & 8.8871                                         \\
+% 			                                                                               & std                                    & 1.6000                                                                             & 2.5111                                                                    & 2.1247                                                                    & 2.2749                                         & 1.9121                                                                    & 3.0415                                       & 1.7791                                      & 2.5553                                         & 1.7647                                         & 1.2938                                          & 4.3840                                          & 1.4090                                         & 3.2511                                         \\
+% 			mushroom                                                                       & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 4.4656                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1344} & 6.3323                                                                    & 3.4484                                         & 2.4656                                                                    & 3.6688                                       & 6.5538                                      & 9.0452                                         & 11.5731                                        & 9.7527                                          & 7.8720                                          & 10.9785                                        & 12.7097                                        \\
+% 			                                                                               & std                                    & 1.0527                                                                             & 1.8831                                                                    & 0.8915                                                                    & 1.6019                                         & 1.3589                                                                    & 2.4687                                       & 1.0711                                      & 1.0931                                         & 1.1927                                         & 1.0828                                          & 0.9197                                          & 1.1075                                         & 1.4781                                         \\
+% 			parkinsons                                                                     & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 2.4677                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2333} & 7.5355                                                                    & 4.5720                                         & 3.5656                                                                    & 4.3839                                       & 6.4720                                      & 8.3161                                         & 7.7968                                         & 11.7516                                         & 8.4892                                          & 12.5419                                        & 10.8742                                        \\
+% 			                                                                               & std                                    & 1.4969                                                                             & 1.7418                                                                    & 1.4396                                                                    & 1.9337                                         & 2.4919                                                                    & 1.8612                                       & 2.4229                                      & 1.6441                                         & 1.7188                                         & 1.1551                                          & 1.9008                                          & 1.3515                                         & 1.3174                                         \\
+% 			student performance                                                            & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5634}          & 11.3978                                                                   & 3.1935                                                                    & 5.6624                                         & 12.4312                                                                   & 5.8634                                       & 3.4194                                      & 6.9333                                         & 7.1032                                         & 6.6366                                          & 11.0624                                         & 6.7011                                         & 8.0323                                         \\
+% 			                                                                               & std                                    & 1.9122                                                                             & 2.1780                                                                    & 2.1205                                                                    & 3.5703                                         & 1.3400                                                                    & 3.1588                                       & 2.0060                                      & 2.4398                                         & 1.9887                                         & 2.0233                                          & 1.0674                                          & 2.2423                                         & 1.9346                                         \\
+% 			wine quality                                                                   & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
+% 			                                                                               & avg                                    & 3.2806                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1118} & 4.1505                                                                    & 4.7882                                         & 3.6301                                                                    & 5.1925                                       & 6.0011                                      & 9.5935                                         & 10.3387                                        & 8.6344                                          & 11.1602                                         & 9.5269                                         & 12.5903                                        \\
+% 			                                                                               & std                                    & 1.9309                                                                             & 1.6660                                                                    & 1.9156                                                                    & 2.1052                                         & 1.7314                                                                    & 1.9506                                       & 2.4040                                      & 1.4943                                         & 1.6201                                         & 1.1801                                          & 1.7732                                          & 1.3407                                         & 1.3515                                         \\
+% 			\midrule
+% 			\textbf{overall}                                                               & \textbf{avg}                           & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{3.7076}} & \textbf{4.1777}                                                           & \textbf{4.6177}                                                           & \textbf{4.6806}                                & \textbf{4.7105}                                                           & \textbf{5.8718}                              & \textbf{6.0229}                             & \textbf{7.7958}                                & \textbf{9.1811}                                & \textbf{9.2019}                                 & \textbf{9.5844}                                 & \textbf{9.8599}                                & \textbf{11.4200}                               \\
+% 			\textbf{normalised}                                                            & \textbf{rank}                          & \cellcolor[rgb]{ .388,  .745,  .482}\textbf{1}                                     & \cellcolor[rgb]{ .49,  .773,  .486}\textbf{2}                             & \cellcolor[rgb]{ .592,  .804,  .494}\textbf{3}                            & \cellcolor[rgb]{ .694,  .831,  .498}\textbf{4} & \cellcolor[rgb]{ .796,  .863,  .506}\textbf{5}                            & \cellcolor[rgb]{ .898,  .89,  .51}\textbf{6} & \cellcolor[rgb]{ 1,  .922,  .518}\textbf{7} & \cellcolor[rgb]{ .996,  .839,  .502}\textbf{8} & \cellcolor[rgb]{ .992,  .753,  .486}\textbf{9} & \cellcolor[rgb]{ .988,  .667,  .471}\textbf{10} & \cellcolor[rgb]{ .984,  .584,  .455}\textbf{11} & \cellcolor[rgb]{ .98,  .498,  .439}\textbf{12} & \cellcolor[rgb]{ .973,  .412,  .42}\textbf{13} \\
+% 			\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}\end{tabular}%
+% 	}
+% \end{table}%
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
+% 	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \Acs{BHH} per dataset, across all runs and epochs.}
+% 	\label{fig:results:standalone:descriptive:descriptive}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
+% 	\caption{Critical difference plots for the average ranks of all low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
+% 	\label{fig:results:standalone:descriptive:cd}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/train/loss/iris.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:standalone:figures:loss:train:iris}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/test/loss/iris.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:standalone:figures:loss:test:iris}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/iris.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:standalone:figures:accuracy:train:iris}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/iris.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:standalone:figures:accuracy:test:iris}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:standalone:figures:iris}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/train/loss/bank.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:standalone:figures:loss:train:bank}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/test/loss/bank.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:standalone:figures:loss:test:bank}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/bank.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:standalone:figures:accuracy:train:bank}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/bank.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:standalone:figures:accuracy:test:bank}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:standalone:figures:bank}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:standalone:figures:loss:train:car}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:standalone:figures:loss:test:car}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:standalone:figures:accuracy:train:car}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:standalone:figures:accuracy:test:car}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the car dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:standalone:figures:car}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/train/loss/fish_toxicity.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:standalone:figures:loss:train:fish_toxicity}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/test/loss/fish_toxicity.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:standalone:figures:loss:test:fish_toxicity}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:standalone:figures:fish_toxicity}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/train/loss/parkinsons.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:standalone:figures:loss:train:parkinsons}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/test/loss/parkinsons.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:standalone:figures:loss:test:parkinsons}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:standalone:figures:parkinsons}
+% \end{figure}
+
+% \section{Heuristic Pool}\label{sec:results:heuristic_pool}
+
+% \begin{table}[htbp]
+% 	\centering
+% 	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+% 	\label{tab:results:heuristic_pool:metrics}%
+% 	\par\bigskip
+% 	\resizebox{\textwidth}{!}{
+% 		\begin{tabular}{rccccccccc}
+% 			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}          &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
+% 			\cmidrule{1-2}                      &                                             &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
+% 			                                    & \multicolumn{1}{l}{\textbf{heuristic pool}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                &                                                                                    &                 &                &                 &                 \\
+% 			\cmidrule{2-3}                      & \textbf{all}                                &                                                                           &                 & \textbf{gd}    &                                                                                    &                 & \textbf{mh}    &                 &                 \\
+% 			\cmidrule{2-10}    \textbf{dataset} & \textbf{count}                              & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count} & \textbf{avg}    & \textbf{std}    \\
+% 			\midrule
+% 			abalone                             & 930                                         & 1.7946                                                                    & 0.6411          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3828}          & 0.5604          & 930            & 2.8226          & 0.4198          \\
+% 			adult                               & 930                                         & 2.8484                                                                    & 0.5058          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.1559}          & 0.4077          & 930            & 1.8989          & 0.4104          \\
+% 			air quality                         & 930                                         & 2.1871                                                                    & 0.8153          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6828}          & 0.7506          & 930            & 2.1301          & 0.7883          \\
+% 			bank                                & 930                                         & 1.7731                                                                    & 0.5617          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3215}          & 0.4920          & 930            & 2.9054          & 0.3341          \\
+% 			bike                                & 930                                         & 1.6247                                                                    & 0.5529          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4387}          & 0.5321          & 930            & 2.9366          & 0.2808          \\
+% 			car                                 & 930                                         & 1.5903                                                                    & 0.5113          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4409}          & 0.5180          & 930            & 2.9688          & 0.2275          \\
+% 			diabetic                            & 930                                         & 2.4516                                                                    & 0.7353          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.2806}          & 0.5756          & 930            & 2.2677          & 0.5798          \\
+% 			fish toxicity                       & 930                                         & 1.9903                                                                    & 0.8485          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8344}          & 0.7684          & 930            & 2.1753          & 0.7959          \\
+% 			forest fires                        & 930                                         & 2.0667                                                                    & 0.8338          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8269}          & 0.7813          & 930            & 2.1065          & 0.8066          \\
+% 			housing                             & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6043} & 0.6869          & 930            & 1.6602                                                                             & 0.6648          & 930            & 2.7355          & 0.5238          \\
+% 			iris                                & 930                                         & 1.8581                                                                    & 0.8005          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7806}          & 0.7272          & 930            & 2.3613          & 0.7960          \\
+% 			mushroom                            & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5204} & 0.5815          & 930            & 1.5484                                                                             & 0.5273          & 930            & 2.9312          & 0.2890          \\
+% 			parkinsons                          & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5570} & 0.6238          & 930            & 1.6011                                                                             & 0.5915          & 930            & 2.8419          & 0.4448          \\
+% 			student performance                 & 930                                         & 1.9828                                                                    & 0.8220          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7903}          & 0.8480          & 930            & 2.2269          & 0.7152          \\
+% 			wine quality                        & 930                                         & 1.5785                                                                    & 0.5498          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5630          & 930            & 2.9280          & 0.2938          \\
+% 			\midrule
+% 			\textbf{overall}                    & \textbf{13950}                              & \textbf{1.8952}                                                           & \textbf{0.7730} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.5492}} & \textbf{0.6651} & \textbf{13950} & \textbf{2.5491} & \textbf{0.6684} \\
+% 		\end{tabular}%
+% 	}
+% \end{table}%
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.pdf}
+% 	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying heuristic pools per dataset, across all runs and epochs.}
+% 	\label{fig:results:heuristic_pool:descriptive:descriptive}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/cd/overall.pdf}
+% 	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying heuristic pools across all datasets, runs and epochs.}
+% 	\label{fig:results:heuristic_pool:descriptive:cd}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/loss/abalone.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:heuristic_pool:figures:loss:train:abalone}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/abalone.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:heuristic_pool:figures:loss:test:abalone}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/accuracy/abalone.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:heuristic_pool:figures:accuracy:train:abalone}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/accuracy/abalone.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:heuristic_pool:figures:accuracy:test:abalone}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the abalone dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:heuristic_pool:figures:abalone}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/loss/forest_fires.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:heuristic_pool:figures:loss:train:forest_fires}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/forest_fires.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:heuristic_pool:figures:loss:test:forest_fires}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the forest fires dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:heuristic_pool:figures:forest_fires}
+% \end{figure}
+
+% \section{Population Size}\label{sec:results:population}
+
+% \begin{table}[htbp]
+% 	\centering
+% 	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}
+% 	\label{tab:results:population:metrics}%
+% 	\par\bigskip
+% 	\resizebox{\textwidth}{!}{
+% 		\begin{tabular}{rccccccccccccccc}
+% 			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}      &                                                                                    &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+% 			\cmidrule{1-2}                      &                                         &                                                                                    &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+% 			                                    & \multicolumn{1}{l}{\textbf{population}} & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+% 			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{5}}          &                                                                                    &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{15}} &                 &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{25}} &                                                                           &                 \\
+% 			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                          & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    \\
+% 			\midrule
+% 			abalone                             & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4387}          & 1.3396          & 930                             & 2.7452                                                                    & 1.3922          & 930                             & 3.0129          & 1.3865          & 930                             & 3.4065                                                                    & 1.3513          & 930                             & 3.3968                                                                    & 1.3514          \\
+% 			adult                               & 930                                     & 3.5720                                                                             & 1.4693          & 930                             & 3.2828                                                                    & 1.3751          & 930                             & 2.8108          & 1.3625          & 930                             & 2.6484                                                                    & 1.3222          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3634} & 1.3063          \\
+% 			air quality                         & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7527}          & 1.4283          & 930                             & 2.9258                                                                    & 1.3904          & 930                             & 2.9656          & 1.3791          & 930                             & 3.3140                                                                    & 1.3789          & 930                             & 3.0419                                                                    & 1.4374          \\
+% 			bank                                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8129}          & 1.4102          & 930                             & 3.1591                                                                    & 1.4348          & 930                             & 2.9989          & 1.4199          & 930                             & 3.0505                                                                    & 1.4438          & 930                             & 2.9785                                                                    & 1.3414          \\
+% 			bike                                & 930                                     & 3.8957                                                                             & 1.3355          & 930                             & 2.8688                                                                    & 1.2850          & 930                             & 2.9645          & 1.3447          & 930                             & 2.7430                                                                    & 1.3762          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5280} & 1.3278          \\
+% 			car                                 & 930                                     & 3.1892                                                                             & 1.3915          & 930                             & 3.0409                                                                    & 1.3945          & 930                             & 3.0398          & 1.4523          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8559} & 1.3938          & 930                             & 2.8742                                                                    & 1.4151          \\
+% 			diabetic                            & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7978}          & 1.5078          & 930                             & 2.9387                                                                    & 1.4133          & 930                             & 3.2129          & 1.4525          & 930                             & 2.9613                                                                    & 1.3036          & 930                             & 3.0892                                                                    & 1.3534          \\
+% 			fish toxicity                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8151}          & 1.4249          & 930                             & 3.0409                                                                    & 1.4288          & 930                             & 3.0925          & 1.3230          & 930                             & 3.1280                                                                    & 1.4073          & 930                             & 2.9237                                                                    & 1.4634          \\
+% 			forest fires                        & 930                                     & 3.0172                                                                             & 1.4026          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9215} & 1.3800          & 930                             & 2.9806          & 1.3833          & 930                             & 3.0968                                                                    & 1.4124          & 930                             & 2.9839                                                                    & 1.4879          \\
+% 			housing                             & 930                                     & 2.8366                                                                             & 1.4040          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8258} & 1.3802          & 930                             & 2.9753          & 1.4393          & 930                             & 2.9849                                                                    & 1.4111          & 930                             & 3.3774                                                                    & 1.3680          \\
+% 			iris                                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301}          & 1.3038          & 930                             & 2.8731                                                                    & 1.3970          & 930                             & 3.0505          & 1.4129          & 930                             & 3.1860                                                                    & 1.4251          & 930                             & 3.0602                                                                    & 1.4987          \\
+% 			mushroom                            & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7989}          & 1.2052          & 930                             & 2.9441                                                                    & 1.3250          & 930                             & 3.0462          & 1.4521          & 930                             & 3.1366                                                                    & 1.4940          & 930                             & 3.0538                                                                    & 1.5664          \\
+% 			parkinsons                          & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6645}          & 1.4411          & 930                             & 3.1065                                                                    & 1.3272          & 930                             & 3.0247          & 1.4265          & 930                             & 3.0495                                                                    & 1.4420          & 930                             & 3.1548                                                                    & 1.3810          \\
+% 			student performance                 & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6376}          & 1.4357          & 930                             & 2.8645                                                                    & 1.4108          & 930                             & 3.1548          & 1.4042          & 930                             & 3.2387                                                                    & 1.3970          & 930                             & 3.1043                                                                    & 1.3395          \\
+% 			wine quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5505}          & 1.3165          & 930                             & 2.7817                                                                    & 1.4152          & 930                             & 3.1581          & 1.3841          & 930                             & 3.1806                                                                    & 1.3941          & 930                             & 3.3290                                                                    & 1.4140          \\
+% 			\midrule
+% 			\textbf{overall}                    & \textbf{13950}                          & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9073}} & \textbf{1.4377} & \textbf{13950}                  & \textbf{2.9546}                                                           & \textbf{1.3904} & \textbf{13950}                  & \textbf{3.0325} & \textbf{1.4045} & \textbf{13950}                  & \textbf{3.0654}                                                           & \textbf{1.4108} & \textbf{13950}                  & \textbf{3.0173}                                                           & \textbf{1.4306} \\
+% 		\end{tabular}%
+% 	}
+% \end{table}%
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_population/figures/descriptive/descriptive.pdf}
+% 	\caption{Descriptive plots for the average ranks of \acs{BHH} with varying population sizes per dataset, across all runs and epochs.}
+% 	\label{fig:results:population:descriptive:descriptive}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_population/figures/cd/overall.pdf}
+% 	\caption{Critical difference plots for the average ranks of \acs{BHH} with varying population sizes across all datasets, runs and epochs.}
+% 	\label{fig:results:population:descriptive:cd}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_population/figures/train/loss/mushroom.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:population:figures:loss:train:mushroom}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/mushroom.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:population:figures:loss:test:mushroom}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_population/figures/train/accuracy/mushroom.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:population:figures:accuracy:train:mushroom}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_population/figures/test/accuracy/mushroom.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:population:figures:accuracy:test:mushroom}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:population:figures:mushroom}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_population/figures/train/loss/student_performance.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:population:figures:loss:train:student_performance}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/student_performance.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:population:figures:loss:test:student_performance}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the student performance dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:population:figures:student_performance}
+% \end{figure}
+
+% \section{Credit Assignment Strategy}\label{sec:results:credit}
+
+% \begin{table}[htbp]
+% 	\centering
+% 	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+% 	\label{tab:results:credit:metrics}%
+% 	\par\bigskip
+% 	\resizebox{\textwidth}{!}{
+% 		\begin{tabular}{rccccccccccccccc}
+% 			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}  &                                                                           &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
+% 			\cmidrule{1-2}                      &                                     &                                                                           &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
+% 			                                    & \multicolumn{1}{l}{\textbf{credit}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
+% 			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{ibest}}  &                                                                           &                 & \multicolumn{1}{l}{\textbf{pbest}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{rbest}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{gbest}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{symmetric}} &                                                                           &                 \\
+% 			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                      & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                         & \textbf{avg}                                                              & \textbf{std}    \\
+% 			\midrule
+% 			abalone                             & 930                                 & 3.1677                                                                    & 1.3188          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613}          & 1.4588          & 930                                & 2.9968                                                                    & 1.3993          & 930                                & 2.9667                                                                    & 1.4547          & 930                                    & 3.0075                                                                    & 1.4214          \\
+% 			adult                               & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                & 2.6763                                                                             & 1.5019          & 930                                & 2.8065                                                                    & 1.5003          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                    & 3.3538                                                                    & 1.5682          \\
+% 			air quality                         & 930                                 & 3.1312                                                                    & 1.3472          & 930                                & 3.0376                                                                             & 1.3566          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5914} & 1.4646          & 930                                & 3.1280                                                                    & 1.3358          & 930                                    & 3.1118                                                                    & 1.4871          \\
+% 			bank                                & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8591} & 1.3442          & 930                                & 2.9903                                                                             & 1.4320          & 930                                & 2.8882                                                                    & 1.4098          & 930                                & 3.0441                                                                    & 1.4154          & 930                                    & 3.2183                                                                    & 1.4424          \\
+% 			bike                                & 930                                 & 3.0527                                                                    & 1.3401          & 930                                & 3.0086                                                                             & 1.3935          & 930                                & 3.0667                                                                    & 1.4825          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3393          & 930                                    & 2.9978                                                                    & 1.5028          \\
+% 			car                                 & 930                                 & 3.1151                                                                    & 1.3562          & 930                                & 3.0312                                                                             & 1.4826          & 930                                & 3.2516                                                                    & 1.4024          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6892} & 1.3540          & 930                                    & 2.9129                                                                    & 1.4111          \\
+% 			diabetic                            & 930                                 & 2.8914                                                                    & 1.3488          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6269}          & 1.4171          & 930                                & 3.4151                                                                    & 1.3653          & 930                                & 2.8925                                                                    & 1.3620          & 930                                    & 3.1742                                                                    & 1.4487          \\
+% 			fish toxicity                       & 930                                 & 3.1516                                                                    & 1.4360          & 930                                & 2.9903                                                                             & 1.4521          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.4748          & 930                                & 3.2043                                                                    & 1.2988          & 930                                    & 2.8957                                                                    & 1.3579          \\
+% 			forest fires                        & 930                                 & 3.0968                                                                    & 1.2771          & 930                                & 3.1806                                                                             & 1.3040          & 930                                & 2.8559                                                                    & 1.3562          & 930                                & 3.1215                                                                    & 1.5018          & 930                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7452} & 1.5627          \\
+% 			housing                             & 930                                 & 2.9011                                                                    & 1.4938          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8527}          & 1.3168          & 930                                & 2.9022                                                                    & 1.3974          & 930                                & 3.3108                                                                    & 1.3243          & 930                                    & 3.0333                                                                    & 1.4833          \\
+% 			iris                                & 930                                 & 3.1892                                                                    & 1.4281          & 930                                & 3.0839                                                                             & 1.4412          & 930                                & 3.0591                                                                    & 1.3755          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8237} & 1.4085          & 930                                    & 2.8441                                                                    & 1.3844          \\
+% 			mushroom                            & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8075} & 1.4594          & 930                                & 3.0183                                                                             & 1.4107          & 930                                & 2.8957                                                                    & 1.3985          & 930                                & 3.0839                                                                    & 1.4178          & 930                                    & 3.1720                                                                    & 1.3813          \\
+% 			parkinsons                          & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5645} & 1.4835          & 930                                & 2.8925                                                                             & 1.3429          & 930                                & 3.5065                                                                    & 1.2190          & 930                                & 3.0796                                                                    & 1.3920          & 930                                    & 2.9570                                                                    & 1.4548          \\
+% 			student performance                 & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6624} & 1.3124          & 930                                & 3.0290                                                                             & 1.4067          & 930                                & 3.1892                                                                    & 1.3821          & 930                                & 2.7978                                                                    & 1.4702          & 930                                    & 3.3215                                                                    & 1.3938          \\
+% 			wine quality                        & 930                                 & 3.1871                                                                    & 1.3080          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366}          & 1.4706          & 930                                & 3.0140                                                                    & 1.3712          & 930                                & 2.9419                                                                    & 1.4115          & 930                                    & 3.2204                                                                    & 1.4300          \\
+% 			\midrule
+% 			\textbf{overall}                    & \textbf{13950}                      & \textbf{2.9475}                                                           & \textbf{1.3805} & \textbf{13950}                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9277}} & \textbf{1.4222} & \textbf{13950}                     & \textbf{3.0131}                                                           & \textbf{1.4209} & \textbf{13950}                     & \textbf{2.9596}                                                           & \textbf{1.3921} & \textbf{13950}                         & \textbf{3.0644}                                                           & \textbf{1.4594} \\
+% 		\end{tabular}%
+% 	}
+% \end{table}%
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_credit/figures/descriptive/descriptive.pdf}
+% 	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying credit assignment strategies per dataset, across all runs and epochs.}
+% 	\label{fig:results:credit:descriptive:descriptive}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_credit/figures/cd/overall.pdf}
+% 	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying credit assignment strategies across all datasets, runs and epochs.}
+% 	\label{fig:results:credit:descriptive:cd}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/bank.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:credit:figures:loss:train:bank}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/bank.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:credit:figures:loss:test:bank}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_credit/figures/train/accuracy/bank.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:credit:figures:accuracy:train:bank}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_credit/figures/test/accuracy/bank.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:credit:figures:accuracy:test:bank}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the bank dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:credit:figures:bank}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/housing.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:credit:figures:loss:train:housing}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/housing.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:credit:figures:loss:test:housing}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the housing dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:credit:figures:housing}
+% \end{figure}
+
+% \section{Reselection Interval}\label{sec:results:reselection}
+
+% \begin{table}[htbp]
+% 	\centering
+% 	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+% 	\label{tab:results:reselection:metrics}%
+% 	\par\bigskip
+% 	\resizebox{\textwidth}{!}{
+% 		\begin{tabular}{rccccccccccccccc}
+% 			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}       &                                                                           &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
+% 			\cmidrule{1-2}                      &                                          &                                                                           &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
+% 			                                    & \multicolumn{1}{l}{\textbf{reselection}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
+% 			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}           &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                 &                 & \multicolumn{1}{l}{\textbf{10}} &                 &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                                    &                 \\
+% 			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                           & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                                       & \textbf{std}    \\
+% 			\midrule
+% 			abalone                             & 930                                      & 4.3548                                                                    & 0.9760          & 930                            & 2.8473          & 1.2885          & 930                             & 2.7505          & 1.2622          & 930                             & 2.5602                                                                    & 1.2988          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4871}          & 1.3182          \\
+% 			adult                               & 930                                      & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7097} & 1.2671          & 930                            & 4.4559          & 1.0052          & 930                             & 3.4398          & 1.0453          & 930                             & 2.7656                                                                    & 0.9837          & 930                             & 2.3065                                                                             & 1.0670          \\
+% 			air quality                         & 930                                      & 3.7355                                                                    & 1.4046          & 930                            & 3.4075          & 1.3790          & 930                             & 2.9688          & 1.2783          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4237} & 1.2281          & 930                             & 2.4645                                                                             & 1.2906          \\
+% 			bank                                & 930                                      & 4.5677                                                                    & 0.7039          & 930                            & 3.6323          & 1.1271          & 930                             & 2.4237          & 1.1333          & 930                             & 2.2462                                                                    & 1.1139          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1301}          & 1.0957          \\
+% 			bike                                & 930                                      & 4.7935                                                                    & 0.6124          & 930                            & 3.9204          & 0.6480          & 930                             & 2.5161          & 0.8632          & 930                             & 2.0763                                                                    & 0.9007          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6935}          & 0.8911          \\
+% 			car                                 & 930                                      & 4.6409                                                                    & 0.7847          & 930                            & 2.9527          & 1.1581          & 930                             & 2.6548          & 1.1748          & 930                             & 2.5312                                                                    & 1.2440          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2204}          & 1.2169          \\
+% 			diabetic                            & 930                                      & 3.0129                                                                    & 1.0478          & 930                            & 4.4624          & 0.8688          & 930                             & 2.7957          & 1.1753          & 930                             & 2.6065                                                                    & 1.4391          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1226}          & 1.2639          \\
+% 			fish toxicity                       & 930                                      & 3.7484                                                                    & 1.2377          & 930                            & 3.1376          & 1.3174          & 930                             & 3.0344          & 1.4062          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4656} & 1.3039          & 930                             & 2.6140                                                                             & 1.4318          \\
+% 			forest fires                        & 930                                      & 3.8194                                                                    & 1.4330          & 930                            & 3.2720          & 1.2477          & 930                             & 2.8656          & 1.3464          & 930                             & 2.8194                                                                    & 1.3048          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2237}          & 1.2186          \\
+% 			housing                             & 930                                      & 4.1892                                                                    & 1.0993          & 930                            & 3.0172          & 1.2882          & 930                             & 2.5871          & 1.3541          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5312} & 1.2654          & 930                             & 2.6753                                                                             & 1.3399          \\
+% 			iris                                & 930                                      & 2.9839                                                                    & 1.4244          & 930                            & 2.9710          & 1.3165          & 930                             & 3.3462          & 1.4182          & 930                             & 3.0140                                                                    & 1.4054          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6849}          & 1.4289          \\
+% 			mushroom                            & 930                                      & 4.2065                                                                    & 1.2356          & 930                            & 2.9688          & 1.2992          & 930                             & 2.5860          & 1.2336          & 930                             & 2.7882                                                                    & 1.3397          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4505}          & 1.2259          \\
+% 			parkinsons                          & 930                                      & 4.7645                                                                    & 0.7563          & 930                            & 3.1882          & 1.0208          & 930                             & 2.2957          & 1.2089          & 930                             & 2.4968                                                                    & 1.1282          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2548}          & 1.0973          \\
+% 			student performance                 & 930                                      & 3.9710                                                                    & 1.0942          & 930                            & 4.0226          & 1.1196          & 930                             & 2.4774          & 1.2206          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495} & 1.2002          & 930                             & 2.2796                                                                             & 1.1324          \\
+% 			wine quality                        & 930                                      & 4.0688                                                                    & 1.1220          & 930                            & 2.9204          & 1.2934          & 930                             & 2.9559          & 1.3831          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4032} & 1.3779          & 930                             & 2.6516                                                                             & 1.2796          \\
+% 			\midrule
+% 			\textbf{overall}                    & \textbf{13950}                           & \textbf{3.9044}                                                           & \textbf{1.3641} & \textbf{13950}                 & \textbf{3.4118} & \textbf{1.2914} & \textbf{13950}                  & \textbf{2.7799} & \textbf{1.2811} & \textbf{13950}                  & \textbf{2.5318}                                                           & \textbf{1.2660} & \textbf{13950}                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.3506}} & \textbf{1.2541} \\
+% 		\end{tabular}%
+% 	}
+% \end{table}%
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.pdf}
+% 	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reselection values per dataset, across all runs and epochs.}
+% 	\label{fig:results:reselection:descriptive:descriptive}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_reselection/figures/cd/overall.pdf}
+% 	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reselection values across all datasets, runs and epochs.}
+% 	\label{fig:results:reselection:descriptive:cd}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/car.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:reselection:figures:loss:train:car}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/car.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:reselection:figures:loss:test:car}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/accuracy/car.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:reselection:figures:accuracy:train:car}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/accuracy/car.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:reselection:figures:accuracy:test:car}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the car dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:reselection:figures:car}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/bike.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:reselection:figures:loss:train:bike}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/bike.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:reselection:figures:loss:test:bike}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the bike dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:reselection:figures:bike}
+% \end{figure}
+
+% \section{Replay Window Size}\label{sec:results:replay}
+
+% \begin{table}[htbp]
+% 	\centering
+% 	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+% 	\label{tab:results:replay:metrics}%
+% 	\par\bigskip
+% 	\resizebox{\textwidth}{!}{
+% 		\begin{tabular}{rccccccccccccccc}
+% 			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}  &                                                                           &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
+% 			\cmidrule{1-2}                      &                                     &                                                                           &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
+% 			                                    & \multicolumn{1}{l}{\textbf{replay}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
+% 			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}      &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                 &                 \\
+% 			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                      & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    \\
+% 			\midrule
+% 			abalone                             & 930                                 & 3.0258                                                                    & 1.3816          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6785}          & 1.4551          & 930                             & 3.1968                                                                    & 1.3460          & 930                             & 3.0903                                                                    & 1.3851          & 930                             & 3.0086          & 1.4503          \\
+% 			adult                               & 930                                 & 2.8785                                                                    & 1.3824          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8269}          & 1.3595          & 930                             & 2.9430                                                                    & 1.4804          & 930                             & 3.0538                                                                    & 1.3714          & 930                             & 2.9645          & 1.5686          \\
+% 			air quality                         & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3851          & 930                            & 3.0151                                                                             & 1.4970          & 930                             & 2.9978                                                                    & 1.4294          & 930                             & 2.9505                                                                    & 1.2966          & 930                             & 3.1624          & 1.4430          \\
+% 			bank                                & 930                                 & 2.9484                                                                    & 1.4597          & 930                            & 3.0570                                                                             & 1.4731          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8602} & 1.3439          & 930                             & 3.0172                                                                    & 1.4202          & 930                             & 3.1172          & 1.3592          \\
+% 			bike                                & 930                                 & 2.9602                                                                    & 1.2739          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7366}          & 1.3401          & 930                             & 3.1452                                                                    & 1.4478          & 930                             & 2.9226                                                                    & 1.4174          & 930                             & 3.2355          & 1.5274          \\
+% 			car                                 & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7054} & 1.3572          & 930                            & 2.8376                                                                             & 1.3898          & 930                             & 3.0763                                                                    & 1.3723          & 930                             & 3.3269                                                                    & 1.4631          & 930                             & 3.0538          & 1.4086          \\
+% 			diabetic                            & 930                                 & 3.2473                                                                    & 1.3690          & 930                            & 3.3247                                                                             & 1.4058          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5935} & 1.3719          & 930                             & 2.8075                                                                    & 1.3844          & 930                             & 3.0269          & 1.4113          \\
+% 			fish toxicity                       & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7269} & 1.4190          & 930                            & 3.0785                                                                             & 1.4896          & 930                             & 3.1774                                                                    & 1.3980          & 930                             & 2.9892                                                                    & 1.3865          & 930                             & 3.0280          & 1.3373          \\
+% 			forest fires                        & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8054} & 1.4926          & 930                            & 2.9151                                                                             & 1.3812          & 930                             & 2.9914                                                                    & 1.4081          & 930                             & 3.0591                                                                    & 1.4111          & 930                             & 3.2290          & 1.3416          \\
+% 			housing                             & 930                                 & 3.1548                                                                    & 1.3007          & 930                            & 2.9774                                                                             & 1.4068          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8548} & 1.4501          & 930                             & 3.0355                                                                    & 1.4898          & 930                             & 2.9774          & 1.4037          \\
+% 			iris                                & 930                                 & 3.0720                                                                    & 1.3757          & 930                            & 3.1581                                                                             & 1.4187          & 930                             & 3.2204                                                                    & 1.3919          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6183} & 1.3964          & 930                             & 2.9312          & 1.4102          \\
+% 			mushroom                            & 930                                 & 3.0538                                                                    & 1.3243          & 930                            & 3.1430                                                                             & 1.4369          & 930                             & 3.0419                                                                    & 1.4140          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613} & 1.3823          & 930                             & 2.8957          & 1.4966          \\
+% 			parkinsons                          & 930                                 & 3.1720                                                                    & 1.3719          & 930                            & 2.8430                                                                             & 1.2437          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6731} & 1.4535          & 930                             & 3.1172                                                                    & 1.4189          & 930                             & 3.1946          & 1.4977          \\
+% 			student performance                 & 930                                 & 3.0398                                                                    & 1.3684          & 930                            & 2.9226                                                                             & 1.4106          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6548} & 1.4028          & 930                             & 3.0935                                                                    & 1.3225          & 930                             & 3.2892          & 1.4874          \\
+% 			wine quality                        & 930                                 & 3.1742                                                                    & 1.4300          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7323}          & 1.4556          & 930                             & 3.1581                                                                    & 1.4179          & 930                             & 3.0419                                                                    & 1.3565          & 930                             & 2.8935          & 1.3624          \\
+% 			\midrule
+% 			\textbf{overall}                    & \textbf{13950}                      & \textbf{2.9892}                                                           & \textbf{1.3892} & \textbf{13950}                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9497}} & \textbf{1.4224} & \textbf{13950}                  & \textbf{2.9723}                                                           & \textbf{1.4224} & \textbf{13950}                  & \textbf{2.9990}                                                           & \textbf{1.4021} & \textbf{13950}                  & \textbf{3.0672} & \textbf{1.4400} \\
+% 		\end{tabular}%
+% 	}
+% \end{table}%
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_replay/figures/descriptive/descriptive.pdf}
+% 	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying replay window sizes per dataset, across all runs and epochs.}
+% 	\label{fig:results:replay:descriptive:descriptive}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_replay/figures/cd/overall.pdf}
+% 	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying replay window sizes across all datasets, runs and epochs.}
+% 	\label{fig:results:replay:descriptive:cd}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/diabetic.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:replay:figures:loss:train:diabetic}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/diabetic.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:replay:figures:loss:test:diabetic}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_replay/figures/train/accuracy/diabetic.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:replay:figures:accuracy:train:diabetic}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_replay/figures/test/accuracy/diabetic.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:replay:figures:accuracy:test:diabetic}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:replay:figures:diabetic}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/fish_toxicity.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:replay:figures:loss:train:fish_toxicity}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/fish_toxicity.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:replay:figures:loss:test:fish_toxicity}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:replay:figures:fish_toxicity}
+% \end{figure}
+
+% \section{Reanalysis Interval}\label{sec:results:reanalysis}
+
+% \begin{table}[htbp]
+% 	\centering
+% 	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+% 	\label{tab:results:reanalysis:metrics}%
+% 	\par\bigskip
+% 	\resizebox{\textwidth}{!}{\begin{tabular}{rccccccccccccccc}
+% 			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}      &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+% 			\cmidrule{1-2}                      &                                         &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+% 			                                    & \multicolumn{1}{l}{\textbf{reanalysis}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
+% 			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}          &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                           &                 \\
+% 			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                          & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    \\
+% 			\midrule
+% 			abalone                             & 930                                     & 2.9849                                                                    & 1.3965          & 930                            & 3.0699                                                                    & 1.4423          & 930                             & 3.1710                                                                             & 1.3205          & 930                             & 2.9441                                                                    & 1.4447          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301} & 1.4433          \\
+% 			adult                               & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860}          & 0.8523          & 930                             & 2.7914                                                                    & 1.7091          & 930                             & 3.0151                                                                    & 1.7236          \\
+% 			air quality                         & 930                                     & 2.9613                                                                    & 1.3442          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8387} & 1.4383          & 930                             & 3.2559                                                                             & 1.4024          & 930                             & 3.0538                                                                    & 1.4200          & 930                             & 2.8903                                                                    & 1.4297          \\
+% 			bank                                & 930                                     & 3.1161                                                                    & 1.4322          & 930                            & 3.0452                                                                    & 1.3827          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7355}          & 1.3985          & 930                             & 2.9280                                                                    & 1.4028          & 930                             & 3.1753                                                                    & 1.4151          \\
+% 			bike                                & 930                                     & 3.1409                                                                    & 1.2581          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.3914          & 930                             & 3.1946                                                                             & 1.3653          & 930                             & 3.0978                                                                    & 1.4978          & 930                             & 2.8086                                                                    & 1.4905          \\
+% 			car                                 & 930                                     & 3.1237                                                                    & 1.4229          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7237} & 1.3575          & 930                             & 2.8763                                                                             & 1.2987          & 930                             & 3.1538                                                                    & 1.3846          & 930                             & 3.1226                                                                    & 1.5473          \\
+% 			diabetic                            & 930                                     & 3.2452                                                                    & 1.3050          & 930                            & 3.0720                                                                    & 1.3913          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7785}          & 1.4067          & 930                             & 3.0290                                                                    & 1.4249          & 930                             & 2.8753                                                                    & 1.4940          \\
+% 			fish toxicity                       & 930                                     & 3.1452                                                                    & 1.3620          & 930                            & 3.0032                                                                    & 1.4455          & 930                             & 3.2172                                                                             & 1.3639          & 930                             & 3.1000                                                                    & 1.4088          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5344} & 1.3879          \\
+% 			forest fires                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8398} & 1.3690          & 930                            & 3.1215                                                                    & 1.4707          & 930                             & 3.0043                                                                             & 1.3181          & 930                             & 2.8860                                                                    & 1.3535          & 930                             & 3.1484                                                                    & 1.5261          \\
+% 			housing                             & 930                                     & 3.3129                                                                    & 1.3107          & 930                            & 2.9892                                                                    & 1.3927          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6871}          & 1.4833          & 930                             & 2.6968                                                                    & 1.4965          & 930                             & 3.3140                                                                    & 1.2356          \\
+% 			iris                                & 930                                     & 3.1204                                                                    & 1.3010          & 930                            & 3.0968                                                                    & 1.3909          & 930                             & 3.1269                                                                             & 1.4320          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366} & 1.4492          & 930                             & 3.0194                                                                    & 1.4352          \\
+% 			mushroom                            & 930                                     & 2.9312                                                                    & 1.3794          & 930                            & 3.1538                                                                    & 1.4031          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8473}          & 1.3836          & 930                             & 3.1215                                                                    & 1.4530          & 930                             & 2.9032                                                                    & 1.4714          \\
+% 			parkinsons                          & 930                                     & 2.9688                                                                    & 1.3850          & 930                            & 3.0086                                                                    & 1.3559          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6129}          & 1.4814          & 930                             & 3.1032                                                                    & 1.3804          & 930                             & 3.3065                                                                    & 1.3778          \\
+% 			student performance                 & 930                                     & 2.9409                                                                    & 1.4118          & 930                            & 3.1849                                                                    & 1.3804          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710}          & 1.4097          & 930                             & 3.1258                                                                    & 1.3655          & 930                             & 2.9774                                                                    & 1.4675          \\
+% 			wine quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8032} & 1.4440          & 930                            & 2.9204                                                                    & 1.3042          & 930                             & 3.2022                                                                             & 1.4104          & 930                             & 2.9247                                                                    & 1.3491          & 930                             & 3.1495                                                                    & 1.5171          \\
+% 			\midrule
+% 			\textbf{overall}                    & \textbf{13950}                          & \textbf{2.9747}                                                           & \textbf{1.3710} & \textbf{13950}                 & \textbf{2.9315}                                                           & \textbf{1.3960} & \textbf{13950}                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.8978}} & \textbf{1.3999} & \textbf{13950}                  & \textbf{2.9728}                                                           & \textbf{1.4464} & \textbf{13950}                  & \textbf{3.0047}                                                           & \textbf{1.4805} \\
+% 		\end{tabular}%
+% 	}
+
+% \end{table}%
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/descriptive/descriptive.pdf}
+% 	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reanalysis window sizes per dataset, across all runs and epochs.}
+% 	\label{fig:results:reanalysis:descriptive:descriptive}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/cd/overall.pdf}
+% 	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reanalysis window sizes across all datasets, runs and epochs.}
+% 	\label{fig:results:reanalysis:descriptive:cd}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/mushroom.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:reanalysis:figures:loss:train:mushroom}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/mushroom.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:reanalysis:figures:loss:test:mushroom}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/accuracy/mushroom.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:reanalysis:figures:accuracy:train:mushroom}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/accuracy/mushroom.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:reanalysis:figures:accuracy:test:mushroom}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:reanalysis:figures:mushroom}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/parkinsons.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:reanalysis:figures:loss:train:parkinsons}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/parkinsons.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:reanalysis:figures:loss:test:parkinsons}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:reanalysis:figures:parkinsons}
+% \end{figure}
+
+% \section{Burn In}\label{sec:results:burn_in}
+
+% \begin{table}[htbp]
+% 	\centering
+% 	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+% 	\label{tab:results:burn_in:metrics}%
+% 	\par\bigskip
+% 	\resizebox{\textwidth}{!}{
+% 		\begin{tabular}{rccccccccccccccc}
+% 			\textbf{epoch}                      & \multicolumn{1}{l}{(all)}            &                                                                                    &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
+% 			\cmidrule{1-2}                      &                                      &                                                                                    &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
+% 			                                    & \multicolumn{1}{l}{\textbf{burn in}} & \multicolumn{1}{l}{\textbf{results}}                                               &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
+% 			\cmidrule{2-3}                      & \textbf{0}                           &                                                                                    &                 & \textbf{5}     &                                                                           &                 & \textbf{10}    &                                                                           &                 & \textbf{15}    &                                                                           &                 & \textbf{20}    &                 &                 \\
+% 			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                       & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}    & \textbf{std}    \\
+% 			\midrule
+% 			abalone                             & 930                                  & 2.9151                                                                             & 1.3952          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6935} & 1.3934          & 930            & 2.9172                                                                    & 1.3837          & 930            & 2.8398                                                                    & 1.3524          & 930            & 3.6344          & 1.3574          \\
+% 			adult                               & 930                                  & 2.7366                                                                             & 1.4475          & 930            & 2.6430                                                                    & 1.3817          & 930            & 2.9892                                                                    & 1.4111          & 930            & 3.1731                                                                    & 1.4477          & 930            & 3.1355          & 1.4130          \\
+% 			air quality                         & 930                                  & 2.9097                                                                             & 1.4408          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6817} & 1.4270          & 930            & 2.7699                                                                    & 1.3443          & 930            & 3.3720                                                                    & 1.3137          & 930            & 3.2667          & 1.4119          \\
+% 			bike                                & 930                                  & 1.9237                                                                             & 0.9808          & 930            & 2.1806                                                                    & 1.0238          & 930            & 2.9237                                                                    & 1.2739          & 930            & 3.5054                                                                    & 1.1859          & 930            & 4.4667          & 0.8514          \\
+% 			car                                 & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3624}          & 1.2315          & 930            & 2.5882                                                                    & 1.4246          & 930            & 3.2978                                                                    & 1.3922          & 930            & 3.3796                                                                    & 1.2711          & 930            & 3.3720          & 1.4009          \\
+% 			fish toxicity                       & 930                                  & 3.0634                                                                             & 1.4589          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7935} & 1.4021          & 930            & 2.8204                                                                    & 1.5131          & 930            & 3.1022                                                                    & 1.3461          & 930            & 3.2204          & 1.2949          \\
+% 			forest fires                        & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8161}          & 1.3301          & 930            & 2.8495                                                                    & 1.3830          & 930            & 2.8645                                                                    & 1.4092          & 930            & 3.3774                                                                    & 1.3976          & 930            & 3.0925          & 1.4709          \\
+% 			housing                             & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6903}          & 1.3837          & 930            & 2.9516                                                                    & 1.3176          & 930            & 2.9968                                                                    & 1.4425          & 930            & 3.0581                                                                    & 1.3435          & 930            & 3.3032          & 1.5101          \\
+% 			iris                                & 930                                  & 2.9473                                                                             & 1.4608          & 930            & 2.9720                                                                    & 1.3675          & 930            & 3.1903                                                                    & 1.4493          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710} & 1.3694          & 930            & 3.1194          & 1.3872          \\
+% 			mushroom                            & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2065}          & 1.2486          & 930            & 2.9376                                                                    & 1.2977          & 930            & 3.1613                                                                    & 1.2966          & 930            & 3.1441                                                                    & 1.4015          & 930            & 3.5226          & 1.5006          \\
+% 			parkinsons                          & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2796}          & 1.2822          & 930            & 2.8892                                                                    & 1.2474          & 930            & 2.7065                                                                    & 1.3143          & 930            & 3.3968                                                                    & 1.4175          & 930            & 3.7280          & 1.3295          \\
+% 			student performance                 & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1452}          & 1.2052          & 930            & 2.6946                                                                    & 1.4032          & 930            & 3.0968                                                                    & 1.3525          & 930            & 3.4581                                                                    & 1.3539          & 930            & 3.6054          & 1.2312          \\
+% 			wine quality                        & 930                                  & 2.9699                                                                             & 1.4373          & 930            & 3.0108                                                                    & 1.3041          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6634} & 1.4186          & 930            & 3.1247                                                                    & 1.3980          & 930            & 3.2312          & 1.4471          \\
+% 			bank                                & 930                                  & 2.7301                                                                             & 1.3210          & 930            & 2.8194                                                                    & 1.3350          & 930            & 2.8570                                                                    & 1.4848          & 930            & 2.9312                                                                    & 1.3841          & 930            & 3.6624          & 1.3391          \\
+% 			\midrule
+% 			\textbf{overall}                    & \textbf{13020}                       & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.6211}} & \textbf{1.3814} & \textbf{13020} & \textbf{2.7647}                                                           & \textbf{1.3553} & \textbf{13020} & \textbf{2.9468}                                                           & \textbf{1.4045} & \textbf{13020} & \textbf{3.1881}                                                           & \textbf{1.3754} & \textbf{13020} & \textbf{3.4543} & \textbf{1.4061} \\
+% 		\end{tabular}%
+% 	}
+% \end{table}%
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_burn_in/figures/descriptive/descriptive.pdf}
+% 	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying burn in values per dataset, across all runs and epochs.}
+% 	\label{fig:results:burn_in:descriptive:descriptive}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_burn_in/figures/cd/overall.pdf}
+% 	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying burn in values across all datasets, runs and epochs.}
+% 	\label{fig:results:burn_in:descriptive:cd}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_burn_in/figures/train/loss/mushroom.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:burn_in:figures:loss:train:mushroom}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/mushroom.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:burn_in:figures:loss:test:mushroom}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_burn_in/figures/train/accuracy/mushroom.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:burn_in:figures:accuracy:train:mushroom}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_burn_in/figures/test/accuracy/mushroom.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:burn_in:figures:accuracy:test:mushroom}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:burn_in:figures:mushroom}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_burn_in/figures/train/loss/parkinsons.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:burn_in:figures:loss:train:parkinsons}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/parkinsons.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:burn_in:figures:loss:test:parkinsons}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:burn_in:figures:parkinsons}
+% \end{figure}
+
+% \section{Normalisation}\label{sec:results:normalise}
+
+% \begin{table}[htbp]
+% 	\centering
+% 	\caption{Empirical results showing average rank and statistics for normalisationnormalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+% 	\label{tab:results:normalise:metrics}%
+% 	\par\bigskip
+% 	\resizebox{0.75\textwidth}{!}{
+% 		\begin{tabular}{rcccccc}
+% 			\textbf{epoch}                     & \multicolumn{1}{l}{\textbf{(all)}}         &                                                                                    &                 &                                   &                                                                           &                 \\
+% 			\cmidrule{1-2}                     &                                            &                                                                                    &                 &                                   &                                                                           &                 \\
+% 			                                   & \multicolumn{1}{l}{\textbf{normalisation}} & \multicolumn{1}{l}{\textbf{metric}}                                                &                 &                                   &                                                                           &                 \\
+% 			\cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{false}}         &                                                                                    &                 & \multicolumn{1}{l}{\textbf{true}} &                                                                           &                 \\
+% 			\cmidrule{2-7}    \textbf{dataset} & \textbf{count}                             & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
+% 			\midrule
+% 			abalone                            & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5002          & 930                               & 1.5065                                                                    & 0.5002          \\
+% 			adult                              & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4710}          & 0.4994          & 930                               & 1.4968                                                                    & 0.5003          \\
+% 			air quality                        & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4892}          & 0.5002          & 930                               & 1.5108                                                                    & 0.5002          \\
+% 			bank                               & 930                                        & 1.5484                                                                             & 0.4979          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4516} & 0.4979          \\
+% 			bike                               & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4978}          & 0.5003          & 930                               & 1.5022                                                                    & 0.5003          \\
+% 			car                                & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4258}          & 0.4947          & 930                               & 1.5742                                                                    & 0.4947          \\
+% 			diabetic                           & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4753}          & 0.4997          & 930                               & 1.5247                                                                    & 0.4997          \\
+% 			fish toxicity                      & 930                                        & 1.5505                                                                             & 0.4977          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4495} & 0.4977          \\
+% 			forest fires                       & 930                                        & 1.5054                                                                             & 0.5002          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4946} & 0.5002          \\
+% 			housing                            & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4720}          & 0.4995          & 930                               & 1.5280                                                                    & 0.4995          \\
+% 			iris                               & 930                                        & 1.5645                                                                             & 0.4961          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4355} & 0.4961          \\
+% 			mushroom                           & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4323}          & 0.4957          & 930                               & 1.5667                                                                    & 0.4958          \\
+% 			parkinsons                         & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4000}          & 0.4902          & 930                               & 1.6000                                                                    & 0.4902          \\
+% 			student performance                & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3892}          & 0.4878          & 930                               & 1.6108                                                                    & 0.4878          \\
+% 			wine quality                       & 930                                        & 1.5473                                                                             & 0.4980          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4527} & 0.4980          \\
+% 			\midrule
+% 			\textbf{overall}                   & \textbf{13950}                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4842}} & \textbf{0.4998} & \textbf{13950}                    & \textbf{1.5136}                                                           & \textbf{0.4998} \\
+% 		\end{tabular}%
+% 	}
+% \end{table}%
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_normalise/figures/descriptive/descriptive.pdf}
+% 	\caption{Descriptive plots for the average ranks of the \acs{BHH} with normalisation toggled per dataset, across all runs and epochs.}
+% 	\label{fig:results:normalise:descriptive:descriptive}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_normalise/figures/cd/overall.pdf}
+% 	\caption{Critical difference plots for the average ranks of the \acs{BHH} with normalisation toggled across all datasets, runs and epochs.}
+% 	\label{fig:results:normalise:descriptive:cd}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_normalise/figures/train/loss/abalone.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:normalise:figures:loss:train:abalone}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/abalone.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:normalise:figures:loss:test:abalone}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_normalise/figures/train/accuracy/abalone.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:normalise:figures:accuracy:train:abalone}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_normalise/figures/test/accuracy/abalone.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:normalise:figures:accuracy:test:abalone}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the abalone dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:normalise:figures:abalone}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_normalise/figures/train/loss/bike.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:normalise:figures:loss:train:bike}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/bike.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:normalise:figures:loss:test:bike}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the bike dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:normalise:figures:bike}
+% \end{figure}
+
+% \section{Discounted Rewards}\label{sec:results:discounted_rewards}
+
+% \begin{table}[htbp]
+% 	\centering
+% 	\caption{Empirical results showing average rank and statistics for discounted rewardsdiscounted rewards toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+% 	\label{tab:results:discounted_rewards:metrics}%
+% 	\par\bigskip
+% 	\resizebox{0.85\textwidth}{!}{
+% 		\begin{tabular}{rcccccc}
+% 			epoch                              & \multicolumn{1}{l}{(all)}                       &                                                                                    &                 &                                   &                                                                           &                 \\
+% 			\cmidrule{1-2}                     &                                                 &                                                                                    &                 &                                   &                                                                           &                 \\
+% 			                                   & \multicolumn{1}{l}{\textbf{discounted rewards}} & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                   &                                                                           &                 \\
+% 			\cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{FALSE}}              &                                                                                    &                 & \multicolumn{1}{l}{\textbf{TRUE}} &                                                                           &                 \\
+% 			\cmidrule{2-7}    \textbf{dataset} & \textbf{count}                                  & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
+% 			\midrule
+% 			abalone                            & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4914}          & 0.5002          & 930                               & 1.5086                                                                    & 0.5002          \\
+% 			adult                              & 930                                             & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4645} & 0.4990          \\
+% 			air quality                        & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4613}          & 0.4988          & 930                               & 1.5387                                                                    & 0.4988          \\
+% 			bank                               & 930                                             & 1.5161                                                                             & 0.5000          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4839} & 0.5000          \\
+% 			bike                               & 930                                             & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
+% 			car                                & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4280}          & 0.4950          & 930                               & 1.5720                                                                    & 0.4950          \\
+% 			diabetic                           & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4699}          & 0.4994          & 930                               & 1.5301                                                                    & 0.4994          \\
+% 			fish toxicity                      & 930                                             & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
+% 			forest fires                       & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4742}          & 0.4996          & 930                               & 1.5258                                                                    & 0.4996          \\
+% 			housing                            & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4237}          & 0.4944          & 930                               & 1.5763                                                                    & 0.4944          \\
+% 			iris                               & 930                                             & 1.5903                                                                             & 0.4920          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4097} & 0.4920          \\
+% 			mushroom                           & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3946}          & 0.4890          & 930                               & 1.5806                                                                    & 0.4937          \\
+% 			parkinsons                         & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3710}          & 0.4833          & 930                               & 1.6290                                                                    & 0.4833          \\
+% 			student performance                & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4398}          & 0.4966          & 930                               & 1.5602                                                                    & 0.4966          \\
+% 			wine quality                       & 930                                             & 1.5570                                                                             & 0.4970          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4430} & 0.4970          \\
+% 			\midrule
+% 			\textbf{overall}                   & \textbf{13950}                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4747}} & \textbf{0.4994} & \textbf{13950}                    & \textbf{1.5214}                                                           & \textbf{0.4996} \\
+% 		\end{tabular}%
+% 	}
+% \end{table}%
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/descriptive/descriptive.pdf}
+% 	\caption{Descriptive plots for the average ranks of the \acs{BHH} with discounted rewards toggled per datasets, across all runs and epochs.}
+% 	\label{fig:results:discounted_rewards:descriptive:descriptive}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/cd/overall.pdf}
+% 	\caption{Critical difference plots for the average ranks of the \acs{BHH} with discounted rewards toggled across all datasets, runs and epochs.}
+% 	\label{fig:results:discounted_rewards:descriptive:cd}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/loss/wine_quality.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:discounted_rewards:figures:loss:train:wine_quality}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/wine_quality.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:discounted_rewards:figures:loss:test:wine_quality}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/accuracy/wine_quality.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:discounted_rewards:figures:accuracy:train:wine_quality}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/accuracy/wine_quality.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:discounted_rewards:figures:accuracy:test:wine_quality}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the wine quality dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:discounted_rewards:figures:wine_quality}
+% \end{figure}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/loss/housing.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:discounted_rewards:figures:loss:train:housing}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/housing.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:discounted_rewards:figures:loss:test:housing}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the housing dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:discounted_rewards:figures:housing}
+% \end{figure}
+
+% \section{Divergence}\label{sec:results:divergence}
+
+% \begin{figure}[htbp]
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/train/loss/adult.pdf}
+% 		\caption{Train log loss}
+% 		\label{fig:results:divergence:figures:loss:train:adult}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/test/loss/adult.pdf}
+% 		\caption{Test log loss}
+% 		\label{fig:results:divergence:figures:loss:test:adult}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/adult.pdf}
+% 		\caption{Train log accuracy}
+% 		\label{fig:results:divergence:figures:accuracy:train:adult}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/adult.pdf}
+% 		\caption{Test log accuracy}
+% 		\label{fig:results:divergence:figures:accuracy:test:adult}
+% 	\end{subfigure}
+% 	\par\bigskip
+% 	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the adult dataset over 30 epochs, illustrated in log scale.}
+% 	\label{fig:results:divergence:figures:adult}
+% \end{figure}
+
+% \section{Practical Applications}\label{sec:results:practical_applications}
+
+% \section{Summary}\label{sec:results:summary}

### 2022-11-14 dissertation/chapters/08-results.tex
🚧 (results): WIP case study done

@@
 
-This section provides a brief investigation into the \textit{prior selection probabilities}, that results from the probabilistic model implemented by the \acs{BHH}.
+This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities}, that results from the probabilistic model implemented by the \acs{BHH}.
 The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
 
-Figures~\ref{fig:results:case_study:p_H:0}-\ref{fig:results:case_study:p_H:8} provide illustrations of the \index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$ throughout the training process, and averaged over all 30 runs.
+Figures~\ref{fig:results:case_study:p_H:0}-\ref{fig:results:case_study:p_H:8} provide illustrations of the prior\index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$ throughout the training process, and averaged over all 30 runs.
 Similar to before, these illustrations are also presented in log scale.
-The main observation to make from these figures is that they are much less sporafic than the figures presented for the probabilities of selection probabilities.
+The main observation to make from these figures is that they are much less sporadic than the figures presented for the probabilities of selection probabilities.
 This is because of the \textit{reselection} interval hyper-parameter.
@@
 Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of \index{heuristic}heuristic performances.
-Since these prior selection probabilities change over time, it can be concludes that the change in prior selection probabilities is a result of the learning mechanism of the \acs{BHH}.
-Furthermore, these prior selection probability distributions provide an opportunity to utilise prior knowledge by some expert to inject heuristic selection biases, even before training starts.
+Since these prior \index{heuristic}heuristic selection probabilities change over time, it can be concludes that the change in prior \index{heuristic}heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}.
+Furthermore, these prior \index{heuristic}heuristic selection probability distributions provide an opportunity to utilise prior knowledge by some expert to inject heuristic selection biases, even before training starts.
 
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
-	\caption{The average sampled prior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$.
-The prior selection probability is sampled from the prior selection probability distribution, denoted $P(h_{0} \vert \theta_{0})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$.
+The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{0} \vert \theta_{0})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
-	\caption{The average sampled prior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$.
-The prior selection probability is sampled from the prior selection probability distribution, denoted $P(h_{6} \vert \theta_{6})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$.
+The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{6} \vert \theta_{6})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
-	\caption{The average sampled prior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$.
-The prior selection probability is sampled from the prior selection probability distribution, denoted $P(h_{7} \vert \theta_{7})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$.
+The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{7} \vert \theta_{7})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
-	\caption{The average sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$.
-The prior selection probability is sampled from the prior selection probability distribution, denoted $P(h_{8} \vert \theta_{8})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$.
+The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{8} \vert \theta_{8})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:8}
@@
 
-TODO
+This section provides a brief investigation into the outcomes of the \textit{posterior heuristic selection probabilities} that forms the probabilistic model implemented by the \acs{BHH} from which new \index{heuristic}heuristics selections are sampled.
+The posterior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector representing the entities in the entity pool, and $\boldsymbol{C}$ represents the vector of performance criteria outcomes as implemented by the credit assignment strategy.
+Furthermore $\boldsymbol{\theta}, \boldsymbol{\phi}$ represent the probabilities of selection probabilities for the heuristics and entities respectively, and $\boldsymbol{\psi}$ represents the probability of observing a succesful credit allocation from the credit assignment strategy.
+
+Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities, throughout the training process, and averaged over all 30 runs.
+Similar to before, these illustrations are also presented in log scale.
+The main observation to make from these figures is that these values do not actually yield probabilities.
+The reasons for this is because the probablistic model, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, is evaluated for proportionality i.e.
+they are not normalised, and the log-sum-exp trick is used in order to maintain numerical stability.
+Instead, these values are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
+
+The first noteworthy observation to make is for the bhh\_replay\_250 configuration.
+From Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8}, it can be seen that the posterior heuristic selection probabilities stagnate.
+As previously mentioned, this is a result of training stagnation later in the training process.
+As a result, fewer and fewer improvements to the current best solutions are found, thus yielding a case where heuristic selection bias is based mostly on past performances obtained from a large reanalysis window.
+
+Furthermore, the posterior heuristic selection probability distribution is conditional on the occurance of a specific entity that the potential \index{heuristic}heuristic will be applied to, as well as a specific performance criteria enforced by a specific credit assignment strategy.
+This means that \index{heuristic}heuristic selection is specific to each entity.
+A particular \index{heuristic}heuristic might be good for one entity, but not for another.
+This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct \index{heuristic}heuristic to the correct entity at the correct point in the training process.
+
+Finally, the posterior heuristic selection probabilities oscillate much less and are much less sporadic than their prior heuristic selection probability equivalents.
+This is a result of the information that is added by the conditionality on entity and performance criteria.
 
@@
 
-% \section{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
+From the observations made in Sections~\ref{sec:results:case_study:performance_metrics}-\ref{sec:results:case_study:posterior_selec_prob}, it can be concluded that the \acs{BHH} is able to succesfully train the underlying \acs{FFNN}.
+Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases and thus, the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+% BHH vs. Low-Level Heuristics
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\section{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
 

### 2022-11-15 dissertation/chapters/08-results.tex
🚧 (results): Save point before removing adult dataset

--- 2022-11-11 dissertation/chapters/08-results.tex
@@
 	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}.
-Illustrations are provided to show the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.
+Illustrations are provided to show the change in parameter values to illustrate the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.
 
@@
 
-	\item \textbf{Section \ref{sec:results:overfitting}} provides a brief discussion on overfitting as it is observed for some of the empirical tests.
-
 	\item \textbf{Section \ref{sec:results:practical_applications}} provides a brief discussion on the practical application of the \acs{BHH} to real-world problems.
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 250 training steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:alpha:8}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PARAMS THETAS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The first logical observation to be made from Figures~\ref{fig:results:case_study:alpha:0}-\ref{fig:results:case_study:alpha:8} is the step-wise increasing nature of $\boldsymbol{\alpha}$ for the long memory configuration (denoted \textit{bhh\_replay\_250}), illustrated in green.
+Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics.
+The values in $\boldsymbol{\alpha}$ is never reset to its initial value of 1, and thus $\boldsymbol{\alpha}$ continues to increase throughout the training process.
+However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$.
+The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}.
+Heuristics that perform will will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.
+
+The next observation that can be made is for the baseline configuration (denoted \textit{bhh\_baseline}) in red, and the symmetric credit assignment strategy configuration (denoted \textit{bhh\_credit\_symmetric}) in blue.
+Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1 as regular intervals.
+This interval is represented by the \textit{reanalysis} window size.
+The reanalysis interval dictates the frequency at which Bayesian analysis is conducated on the performance log, mainted by the \acs{BHH}.
+Bayesian analysis is used to update $\boldsymbol{\alpha}$.
+As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.
+Notice that $\boldsymbol{\alpha} \geq 1$ for multiple indices, even after reanalysis.
+This is because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1 at the corresponding index in $\boldsymbol{\alpha}$ through the Bayesian analysis process.
+In a case where all 5 entities in the entity pool are allocated the same heuristic, for all 10 steps in the reanalysis windown, $\boldsymbol{\alpha} = 50$.
+
+Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning.
+The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurance} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
+\index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the probabilistic sampling nature of the \acs{BHH}.
+Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % PARAMS THETAS
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Probabilities of Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
+
+This section provides a detailed investigation into the \textit{probabilities of selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process.
+As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves.
+The probability distribution of \index{heuristic}heuristic selection probabilities is denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
+
+Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8} provide illustrations of the probabilities of the selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
+These illustrations are presented in log scale.
+Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at index 0, 6, 7, 8 represent the probabilities of selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and the \index{heuristic pool}heuristic pool.
+Once again, simular illustrations for the other indices in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
+
+From the illustrations presented in Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8}, a clearer picture off the learning process of the \acs{BHH} is formed.
+The first important observation to make is for the bhh\_replay\_250 configuration, presented in green.
+As a reminder, 10 low-level \index{heuristic}heuristics are included in the heuristic pool, yielding a probability of selection probability of 0.1 for each \index{heuristic}heuristic by the frequentist view of probabilistic modeling.
+Towards the end of the training process, the probability of selection probability converges back to the symmetrical, uniform probability distribution, yielding a probability of selection probability of 0.1 per \index{heuristic}heuristic.
+This can be explained as follows: most of the training progress is made in the early stages of the training process, and training stagnates towards the end of the training process.
+Since training stagnates, all heuristics, no matter their past performances, struggle to yield better solutions towards the end of the training process.
+As a result of stagnation, heuristics then struggle to yield credit allocations by means of the credit assignment strategy.
+In the case study experimental group, both the bhh\_baseline and bhh\_replay\_250 configurations make use of the \textit{ibest} credit assignment strategy.
+The \textit{ibest} credit assignment strategy allocates credit to the heuristic that provided the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
+However, since the bhh\_baseline has a short reanalysis interval, the concentration parameter $\boldsymbol{\alpha}$ gets reset to its default value of 1 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is less narrow and thus explaining the larger variance of $\boldsymbol{\theta}$ throughout.
+
+Another observation to make occurs in the first 30 steps of the training process.
+Notice how all three configurations mostly yield the same probabilities of selection probabilities in these first 30 steps.
+This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same runs.
+This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches.
+This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.
+It should be noted that, despite using the same random seed across configurations for the same runs, after about 30 steps, the behavioural changes between the configurations start the show.
+As a reminder, the bhh\_credit\_symmetric configuration, does not bias towards best performing \index{heuristic}heuristics and thus, where the bhh\_baseline and bhh\_replay\_250 configurations diverge from the behaviour of the bhh\_credit\_symmetric configuration, the difference in behaviour is proof of the effect of performance bias.
+
+Finally, despite divergence in behaviour, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar sporadic behaviour, much more so than with the bhh\_replay\_250 configuration.
+This can be attributed to a very small reanalysis window that contains very few samples to learn from (N=10).
+A small reanalysis window allows for more exploration, but can also yield greater variance of the probabilities of selection probabilities.
+Once again, any differences then in the behaviour of the  bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations.
 
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$, sampled from the probability distribution $P(\theta_{0} \vert \alpha_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$.
+The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{0} \vert \alpha_{0})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$, sampled from the probability distribution $P(\theta_{6} \vert \alpha_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$.
+The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{6} \vert \alpha_{6})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$, sampled from the probability distribution $P(\theta_{7} \vert \alpha_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$.
+The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{7} \vert \alpha_{7})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
-	\caption{The average unnormalised sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$, sampled from the probability distribution $P(\theta_{8} \vert \alpha_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$.
+The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{8} \vert \alpha_{8})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:theta:8}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PARAMS P_H (Priors)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % PARAMS P_H (Priors)
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Prior Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}
+
+This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities}, that results from the probabilistic model implemented by the \acs{BHH}.
+The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
+
+Figures~\ref{fig:results:case_study:p_H:0}-\ref{fig:results:case_study:p_H:8} provide illustrations of the prior\index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$ throughout the training process, and averaged over all 30 runs.
+Similar to before, these illustrations are also presented in log scale.
+The main observation to make from these figures is that they are much less sporadic than the figures presented for the probabilities of selection probabilities.
+This is because of the \textit{reselection} interval hyper-parameter.
+A reselection interval hyper-parameter is introduces to control the frequency by which new heuristics are allocated to each entity.
+Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10.
+These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8} for the probabilities of selection probabilities.
+As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
+
+Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of \index{heuristic}heuristic performances.
+Since these prior \index{heuristic}heuristic selection probabilities change over time, it can be concludes that the change in prior \index{heuristic}heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}.
+Furthermore, these prior \index{heuristic}heuristic selection probability distributions provide an opportunity to utilise prior knowledge by some expert to inject heuristic selection biases, even before training starts.
 
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$, sampled from the prior selection probability distribution $P(h_{0} \vert \theta_{0})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$.
+The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{0} \vert \theta_{0})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$, sampled from the prior selection probability distribution $P(h_{6} \vert \theta_{6})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$.
+The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{6} \vert \theta_{6})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$, sampled from the prior selection probability distribution $P(h_{7} \vert \theta_{7})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$.
+The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{7} \vert \theta_{7})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
-	\caption{The average unnormalised sampled prior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$, sampled from the prior selection probability distribution $P(h_{8} \vert \theta_{8})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$.
+The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{8} \vert \theta_{8})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H:8}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PARAMS P_HgEC (Posterior)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % PARAMS P_HgEC (Posterior)
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Posterior Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}
+
+This section provides a brief investigation into the outcomes of the \textit{posterior heuristic selection probabilities} that forms the probabilistic model implemented by the \acs{BHH} from which new \index{heuristic}heuristics selections are sampled.
+The posterior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector representing the entities in the entity pool, and $\boldsymbol{C}$ represents the vector of performance criteria outcomes as implemented by the credit assignment strategy.
+Furthermore $\boldsymbol{\theta}, \boldsymbol{\phi}$ represent the probabilities of selection probabilities for the heuristics and entities respectively, and $\boldsymbol{\psi}$ represents the probability of observing a succesful credit allocation from the credit assignment strategy.
+
+Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities, throughout the training process, and averaged over all 30 runs.
+Similar to before, these illustrations are also presented in log scale.
+The main observation to make from these figures is that these values do not actually yield probabilities.
+The reasons for this is because the probablistic model, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, is evaluated for proportionality i.e.
+they are not normalised, and the log-sum-exp trick is used in order to maintain numerical stability.
+Instead, these values are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
+
+The first noteworthy observation to make is for the bhh\_replay\_250 configuration.
+From Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8}, it can be seen that the posterior heuristic selection probabilities stagnate.
+As previously mentioned, this is a result of training stagnation later in the training process.
+As a result, fewer and fewer improvements to the current best solutions are found, thus yielding a case where heuristic selection bias is based mostly on past performances obtained from a large reanalysis window.
+
+Furthermore, the posterior heuristic selection probability distribution is conditional on the occurance of a specific entity that the potential \index{heuristic}heuristic will be applied to, as well as a specific performance criteria enforced by a specific credit assignment strategy.
+This means that \index{heuristic}heuristic selection is specific to each entity.
+A particular \index{heuristic}heuristic might be good for one entity, but not for another.
+This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct \index{heuristic}heuristic to the correct entity at the correct point in the training process.
+
+Finally, the posterior heuristic selection probabilities oscillate much less and are much less sporadic than their prior heuristic selection probability equivalents.
+This is a result of the information that is added by the conditionality on entity and performance criteria.
 
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{0} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
+The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{0} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:0}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{6} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
+The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{6} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:6}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{7} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
+The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{7} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:7}
@@
 	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
-	\caption{The average unnormalised sampled posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{8} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
+The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{8} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0:8}
@@
 
+From the observations made in Sections~\ref{sec:results:case_study:performance_metrics}-\ref{sec:results:case_study:posterior_selec_prob}, it can be concluded that the \acs{BHH} is able to succesfully train the underlying \acs{FFNN}.
+Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases and thus, the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+% BHH vs. Low-Level Heuristics
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 \section{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
 
+This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics.
+Detailed discussions and illustrations follow.
+As a reminder, the set of low-level heuristics include a number of gradient-based heuristics and a number of meta-heuristics.
+Three different variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics (denoted bhh\_gd), and finally, a \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics (denoted bhh\_mh).
+
+Table~\ref{tab:results:standalone:metrics:test_loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented.
+The test loss that is reported in Table~\ref{tab:results:standalone:metrics:test_loss} reflects on the test loss achieved at the last epoch of training, across all datasets, averaged over all independent runs.
+
 % Table generated by Excel2LaTeX from sheet 'results - test - loss'
-\begin{table}[htbp]
+\begin{table}[H]
 	\centering
@@
 
+From Table~\ref{tab:results:standalone:metrics:test_loss} it can be seen that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
+The bhh\_gd configuration managed to produced results comparable to the best heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.
+One exception stands out, and that is for the for bhh\_all configuration.
+The bhh\_all configuration produced bad results for the adult dataset, yielding an average loss far greater than any of the other implementations.
+More detailed discussions on this specific case is provided later in the Chapter.
+
+Table~\ref{tab:results:standalone:metrics:rank} provides the empirical results in ranking format.
+The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, for all datasets, over all runs and all training epochs.
+The average rank across all epochs produce a view on the performance of the \index{heuristic}heuristics as it relates to the entire training process.
+Finally, a normalised average rank is provided for the overall performance of all \index{heuristic}heuristics at the bottom of the table.
+From the normalised average ranks, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and 8th amongst all thirteen \index{heuristic}heuristic implementations respectively.
+
 % Table generated by Excel2LaTeX from sheet 'results - test - rank'
-\begin{table}[htbp]
+\begin{table}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks across all runs for each \index{heuristic}heuristic, per dataset.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic}heuristic as it relates to all datasets, across all runs.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all \index{heuristic}heuristics is very small.
+Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, was statistically only outperformed overall by \acs{Adagrad}, yielding statistically comparable results than \acs{Adam}, \acs{NAG} and \acs{RMSProp}.
+It should be noted that the standalone low-level \index{heuristic} \index{heuristic}heuristics already produce good results in general across all datasets.
+In this particular case, producing better performance outcomes can be hard to achieve.
+However, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.
+
+Another observation that can be made is that the gradient-based \index{heuristic}heuristics generally performed much better than the \index{meta-heuristic}meta-heuristics on all datasets.
+State of the art methods for training \acp{FFNN} such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions~\cite{ref:kingma:2014}.
+Exploration of the \index{heuristic}heuristic space leads the \acs{BHH} to consider other \index{heuristic}heuristics during the training process, which could possibly result in worse performances at times.
+As previously mentioned, a suggestion to improve on these results is to include a move-acceptance strategy, where heuristic progressions are discarded if they fail to produce better results.
+
+Figures~\ref{fig:results:standalone:figures:iris}-\ref{fig:results:standalone:figures:car} provide illustrations of the train and test, loss and accuracy plots for each heuristics as it relates to a selection of classification datasets.
+The train and test, loss and accuracy plots provided are illustrated in log scale.
+The other classification datasets are left out for brevity as they produce similar illustrations.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 	\par\bigskip
-	\caption{The train and test loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:standalone:figures:iris}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 	\par\bigskip
-	\caption{The train and test loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:standalone:figures:bank}
@@
 	\par\bigskip
-	\caption{The train and test loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the car dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the car dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:standalone:figures:car}
@@
 
-\begin{figure}[htbp]
+Figures~\ref{fig:results:standalone:figures:fish_toxicity}-\ref{fig:results:standalone:figures:parkinsons} provide illustrations of the train and test loss plots for each heuristics as it relates to a selection of regression datasets.
+The train and test loss plots provided are illustrated in log scale.
+Similar to before, the other regression datasets are left out for brevity as they produce similar illustrations.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 	\par\bigskip
-	\caption{The train and test loss plot for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:standalone:figures:fish_toxicity}
@@
 	\par\bigskip
-	\caption{The train and test loss plot for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:standalone:figures:parkinsons}
@@
 
-\begin{table}[htbp]
+This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \index{heuristic pool}\textit{heuristic pool} hyper-parameter.
+Brief discussions follow and illustrations are provided for visual aid.
+This experimental group utilises the same three variants of the \acs{BHH} as was utilised in Section \ref{sec:results:standalone}, but provides an opportunity to look at the \acs{BHH} \index{heuristic pool}heuristic pool hyper-parameter in more depth.
+
+Table \ref{tab:results:heuristic_pool:metrics} provides the ranked performance, per dataset, of each of the \acs{BHH} \index{heuristic pool}heuristic pool configurations.
+Similar to before, the performance rank is calculated as the average rank produced by each \index{heuristic pool}heuristic pool configuration, for all datasets, over all runs and all training epochs.
+
+\begin{table}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Similar to the outcomes provided in Section \ref{sec:results:standalone}, it is found that the bhh\_gd configuration yielded the best overall performance compared to the bhh\_all and bhh\_mh configurations.
+Figure~\ref{fig:results:heuristic_pool:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different \index{heuristic pool}heuristic pool configurations, per dataset.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:heuristic_pool:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic pool}heuristic pool configuration as it relates to all datasets, across all runs.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+From Figures~\ref{fig:results:heuristic_pool:descriptive:descriptive} and Figure~\ref{fig:results:heuristic_pool:descriptive:cd}, it is clear that the bhh\_gd configuration performs best overall, with statistically insignificant exceptions for the parkinsons and housing datasets.
+
+From the results show in Section \ref{sec:results:standalone}, the gradient-based methods outperformed the \index{meta-heuristic}meta-heuristics in all cases.
+It then logically makes sense that the bhh\_gd configuration yields the best performance.
+However, the inclusion of \index{meta-heuristic}meta-heuristics is done as an attempt to provide a mechanism that could provide even better performance, as well as generalisation capabilities to other datasets.
+The benefits of a generalisation capability is not realised in this dissertation, since the gradient-based \index{heuristic}heuristics provided the best performance across datasets and overall.
+Furthermore, the gradient-based \index{heuristic}heuristics already produce good performance results, and improvement on those results are hard.
+Faster convergence is also difficult to achieve, since the \acs{BHH} needs sufficient time to explore the heuristic space.
+The benefit that the \acs{BHH} then brings is that it provides a mechanism where prior expert knowledge can be injected, before training starts.
+Since gradient-based \index{heuristic}heuristics perform well, future research can exploit this knowledge and provide a significant bias towards these gradient-based \index{heuristic}heuristics through the initialisation of the concentration parameters as is mentioned previously.
+
+Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides the train and test, loss and accuracy plot for an example classification dataset (abalone) as it relates to the heuristic pool experimental group.
+As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 	\par\bigskip
-	\caption{The train and test loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the abalone dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the abalone dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:heuristic_pool:figures:abalone}
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:heuristic_pool:figures:forest_fires} provides the train and test loss plot for an example regression dataset (forest fires) as it relates to the heuristic pool experimental group.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 	\par\bigskip
-	\caption{The train and test loss plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the forest fires dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the forest fires dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:heuristic_pool:figures:forest_fires}
@@
 
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different population size values used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}
+This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{population size} hyper-parameter.
+Brief discussions follow and illustrations are provided for visual aid.
+As a reminder, five different population sizes are considered.
+These include population sizes of 5, 10, 15, 20, and 25.
+
+Table \ref{tab:results:population:metrics} provides the ranked performance, per dataset, of each of the \acs{BHH} population size configurations.
+Similar to before, the performance rank is calculated as the average rank produced by each population size configuration, for all datasets, over all runs and all training epochs.
+
+\begin{table}[H]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}
 	\label{tab:results:population:metrics}%
@@
 
-\begin{figure}[htbp]
+Table \ref{tab:results:population:metrics} show that that a smaller population size mostly produces the best results, with statistically significant differences on the adult, bike and car datasets.
+A population size of 10, slightly higher than the default of 5 is preferred for the forest fires and housing datasets.
+
+Figure~\ref{fig:results:population:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different population size configurations, per dataset.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:population:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each population size configuration as it relates to all datasets, across all runs.
+It is shown that there is no overall statistical significant difference between population sizes and the population size hyper-parameter is problem specific.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Similar to before, Figure~\ref{fig:results:population:figures:mushroom} provides the train and test, loss and accuracy plot for an example classification dataset (mushroom) as it relates to the population size experimental group.
+As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{figure}[htbp]
+As a reminder, the experimental group for population sizes only varies the population size hyper-parameter and all other hyper-parameters remain the same between configurations.
+As such, all population size configurations make use of the \index{heuristic pool}heuristic pool configuration that includes all the low-level heuristics, including gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
+This explains the sporadic results in Figure \ref{fig:results:population:figures:loss:test:mushroom}.
+Note that the accuracy is almost 100\% and that these sporadic results are simply a result of an attempt to further improve performance even more, by exploring the heuristic space more.
+Since there is not much room for more improvement, the \acs{BHH} is bound to try different heuristic that yield sub-optimal results.
+
+Figure~\ref{fig:results:population:figures:student_performance} provides the train and test loss plot for an example regression dataset (student performance) as it relates to the population size experimental group.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
+From Figure~\ref{fig:results:population:figures:loss:train:student_performance} it can be seen that the \acs{BHH} with a small population size of 5 starts to diverge away from optimal results as it explores more options in attempt to provide better solutions.
+Divergence can be eliminated by means of an early stopping strategy.
+
 \section{Credit Assignment Strategy}\label{sec:results:credit}
 
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different \index{credit}credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{credit assignment strategy} hyper-parameter.
+Brief discussions follow and illustrations are provided for visual aid.
+As a reminder, five different credit assignment strategies are considered.
+These include the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies as presented in Chapter \ref{chap:bhh}.
+
+Table \ref{tab:results:credit:metrics} provides the ranked performance, per dataset, of each of the \acs{BHH} credit assignment strategy configurations.
+Similar to before, the performance rank is calculated as the average rank produced by each credit assignment strategy configuration, for all datasets, over all runs and all training epochs.
+
+\begin{table}[H]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:credit:metrics}%
@@
 
-\begin{figure}[htbp]
+Table \ref{tab:results:credit:metrics} show that different credit assignment strategies perform best for different datasets, from which it can be concluded that the credit assignment strategy hyper-parameter is problem specific.
+It should be noted that the symmetric credit assignment strategy yielded the best results for the forest fires dataset.
+This does not necessarily suggest that random search in the heuristic space yields the best performance for this dataset.
+Instead, it could be the case that the initial selection of heuristics is good enough and that it is difficult to find a performance bias that results in better performance, as all \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool provide good results.
+For all other datasets, it is found that a particular non-symmetric credit assignment strategy yields better results than random search.
+
+Figure~\ref{fig:results:credit:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different credit assignment strategy configurations, per dataset.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:credit:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each credit assignment strategy configuration as it relates to all datasets, across all runs.
+It is shown that there is no overall statistical significant difference between credit assignment strategies and that the credit assignment strategy hyper-parameter is problem specific.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Similar to before, Figure~\ref{fig:results:credit:figures:bank} provides the train and test, loss and accuracy plot for an example classification dataset (bank) as it relates to the credit assignment strategy experimental group.
+As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{figure}[htbp]
+From Figure~\ref{fig:results:credit:figures:bank} it can be seen that the \textit{pbest} credit assignment strategy (green) diverged away from the current best solution, but was able to return to the current best solution.
+Since the solution found by the \acs{BHH} with the \textit{pbest} credit assignment strategy was already optimal before divergence, it stands to reason that this divergence is a result of the \acs{BHH} exploring other solutions in the heuristic space that yield sub-optimal solutions.
+As mentioned before, a move-acceptance strategy can be incorporated to counteract this effect.
+
+Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plot for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different reselection values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{reselection interval} hyper-parameter.
+Detailed discussions follow and illustrations are provided for visual aid.
+As a reminder, five different reselection intervals are considered.
+These include reselection intervals of 1, 5, 10, 15, and 20.
+
+Table \ref{tab:results:reselection:metrics} provides the ranked performance, per dataset, of each of the \acs{BHH} reselection interval configurations.
+Similar to before, the performance rank is calculated as the average rank produced by reselection interval configuration, for all datasets, over all runs and all training epochs.
+
+\begin{table}[H]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:reselection:metrics}%
@@
 
-\begin{figure}[htbp]
+Table \ref{tab:results:reselection:metrics} show that larger reselection intervals are mostly preferred, with the exception of the adult dataset.
+This outcome can be explained as follows.
+A larger reselection interval gives the low-level \index{heuristic}heuristics more time to execute, resulting in smoother update steps.
+This is further supported by the findings from Sections \ref{sec:results:standalone} and \ref{sec:results:heuristic_pool}, that show that gradient-based \index{heuristic}heuristics generally yield the best performance.
+Gradient-based \index{heuristic}heuristics rely on exponentially averaged state parameters in order to produce smooth update steps.
+If reselection occurs too frequently these exponentially averaged state parameters do not yield smooth update steps.
+Finally, it should be noted that the default reanalysis interval is 10.
+At every reanalysis interval, the concentrations for low-level \index{heuristic}heuristics is reset to the default, symmetrical value of 1.
+As such, \acs{BHH} configurations with reselection intervals that are larger than the reanalysis interval only consider performance samples from the last reanalysis window size.
+This suggests that exploitation of low-level \index{heuristic}heuristics is more important than exploration of low-level \index{heuristic}heuristics.
+
+Figure~\ref{fig:results:credit:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reselection interval configurations, per dataset.
+
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reselection values per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reselection interval values per dataset, across all runs and epochs.}
 	\label{fig:results:reselection:descriptive:descriptive}
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:reselection:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reselection interval configuration as it relates to all datasets, across all runs.
+
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=\textwidth]{bhh_reselection/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reselection values across all datasets, runs and epochs.}
+	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reselection interval values across all datasets, runs and epochs.}
 	\label{fig:results:reselection:descriptive:cd}
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:reselection:descriptive:cd} shows the statistically significant difference in results for the various reselection intervals.
+It can be seen that larger reselection intervals statistically perform better than smaller reselection intervals.
+
+Similar to before, Figure~\ref{fig:results:reselection:figures:car} provides the train and test, loss and accuracy plot for an example classification dataset (car) as it relates to the reselection interval experimental group.
+As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plot for an example regression dataset (bike) as it relates to the reselection interval experimental group.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
+Figures~\ref{fig:results:reselection:figures:loss:train:car} and ~\ref{fig:results:reselection:figures:loss:train:bike} both show a smooth decline in training loss for all reselection interval configurations of the \acs{BHH}, but larger reselection interval configurations are able to provide better results than smaller reselection intervals.
+This further supports the suggestion that exploitation of low-level \index{heuristic}heuristics is more important than exploration of low-level \index{heuristic}heuristics in this particular case.
+
 \section{Replay Window Size}\label{sec:results:replay}
 
-\begin{table}[htbp]
+This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{replay window size} hyper-parameter.
+Brief discussions follow and illustrations are provided for visual aid.
+As a reminder, five different replay window sizes are considered.
+These include replay window sizes of 1, 5, 10, 15, and 20.
+
+Table \ref{tab:results:replay:metrics} provides the ranked performance, per dataset, for each of the \acs{BHH} replay window size configurations.
+Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all runs and all training epochs.
+
+\begin{table}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Table \ref{tab:results:replay:metrics} shows that there is no clear best performing replay window size configuration of the \acs{BHH} for all datasets.
+A replay window size of 1 is best for the air quality, car, fish toxity and forest fires datasets.
+A replay window size of 5 is best for the abalone, adult, bike and wine quality datasets.
+A replay window size of 10 is best for the bank, diabetic, housing, parkinsons and student performance datasets.
+A replay window size of 15 is best for the iris and mushroom datasets.
+Finally, the largest replay window size of 20 did not provide the best outcome for any dataset, but provided results very close to that of the other configurations.
+From these observations it can be concluded that the replay window size is problem specific.
+This means that some problem sets require a shorter replay window size, while others require a larger replay window size.
+
+Furthermore, it can be concluded that some problem sets require more exploration of the \index{heuristic}heuristic space, while other problem sets require more exploitation of low-level \index{heuristic}heuristics.
+
+Figure~\ref{fig:results:replay:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different replay window size configurations, per dataset.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:replay:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each replay window size configuration as it relates to all datasets, across all runs.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:replay:descriptive:cd} shows no statistically significant difference in results for the various replay window size configurations as it relates to all datasets.
+
+Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test, loss and accuracy plot for an example classification dataset (diabetic) as it relates to the replay window size experimental group.
+As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plot for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different reanalysis values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{reanalysis interval} hyper-parameter.
+Brief discussions follow and illustrations are provided for visual aid.
+As a reminder, five different reanalysis intervals are considered.
+These include reanalysis intervals of 1, 5, 10, 15, and 20.
+
+Table \ref{tab:results:reanalysis:metrics} provides the ranked performance, per dataset, for each of the \acs{BHH} reanalysis interval configurations.
+Similar to before, the performance rank is calculated as the average rank produced by the reanalysis interval configurations, for all datasets, over all runs and all training epochs.
+
+\begin{table}[H]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:reanalysis:metrics}%
@@
 
-\begin{figure}[htbp]
+Table \ref{tab:results:reanalysis:metrics} shows that there is no clear best performing reanalysis interval configuration of the \acs{BHH} for all datasets.
+A reanalysis interval of 1 is best for the adult, forest fires and wine quality datasets.
+A reanalysis interval of 5 is best for the adult, air quality, bike and car datasets.
+A reanalysis interval of 10 is best for the adult, bank, diabetic, housing, mushroom, parkinsons and wine quality datasets.
+A reanalysis interval of 15 is best for the iris dataset.
+Finally, the largest reanalysis interval of 20 is best for the abalone and fish toxicity datasets.
+
+It should be noted that the configuration and results for the reanalysis interval configurations should be considered along with the reselection interval configurations as reselection is based on the outcome of the reanalysis step.
+For the \acs{BHH} baseline configuration, both the reselection and reanalysis interval hyper-parameters have default value of 10.
+Furthermore, the smaller the reanalysis interval, the more frequently the \acs{BHH} resets concentration parameters.
+A reanalysis interval of 1 provides a case where only the last executed step is considered for reanalysis and thus provides a shortsighted view on the relevance of past performance, and thus, reselection is based only on the most recent performance of each selected \index{heuristic}heuristic.
+
+Figure~\ref{fig:results:reanalysis:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reanalysis interval configurations, per dataset.
+
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reanalysis window sizes per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reanalysis intervals per dataset, across all runs and epochs.}
 	\label{fig:results:reanalysis:descriptive:descriptive}
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:reanalysis:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reanalysis interval configuration as it relates to all datasets, across all runs.
+
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reanalysis window sizes across all datasets, runs and epochs.}
+	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reanalysis intervals across all datasets, runs and epochs.}
 	\label{fig:results:reanalysis:descriptive:cd}
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:reanalysis:descriptive:cd} shows no statistically significant difference in results for the various reanalysis interval configurations as it relates to all datasets.
+
+Similar to before, Figure~\ref{fig:results:reanalysis:figures:mushroom} provides the train and test, loss and accuracy plot for an example classification dataset (mushroom) as it relates to the reanalysis interval experimental group.
+As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plot for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different \index{burn in}burn in values used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{burn in} hyper-parameter.
+Brief discussions follow and illustrations are provided for visual aid.
+As a reminder, five different burn ins are considered.
+These include burn ins of 0, 5, 10, 15, and 20.
+
+Table \ref{tab:results:burn_in:metrics} provides the ranked performance, per dataset, for each of the \acs{BHH} burn in configurations.
+Similar to before, the performance rank is calculated as the average rank produced by the burn in configurations, for all datasets, over all runs and all training epochs.
+
+\begin{table}[H]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:burn_in:metrics}%
@@
 
-\begin{figure}[htbp]
+Table \ref{tab:results:burn_in:metrics} shows that, in general, a configuration where there is no burn in produces the best results.
+This can be explains from the fact that most of the training progress that is made is done early in the training process.
+The faster the \acs{BHH} is able to start learning, the better.
+Note that reselection still occurs during a burn in window, but burn in overrides the reanalysis interval is the burn in window size is larger than the reanalysis window.
+
+Figure~\ref{fig:results:burn_in:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the burn in window size configurations, per dataset.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:burn_in:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reanalysis interval configuration as it relates to all datasets, across all runs.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:burn_in:descriptive:cd} shows with statistical certainty that a small burn in configuration of the \acs{BHH} (burn in values 0 and 5) generally produce better results than larger burn in configurations.
+
+Similar to before, Figure~\ref{fig:results:burn_in:figures:mushroom} provides the train and test, loss and accuracy plot for an example classification dataset (mushroom) as it relates to the burn in window  size experimental group.
+As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:burn_in:figures:parkinsons} provides the train and test loss plot for an example regression dataset (parkinsons) as it relates to the burn in window size experimental group.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for \index{normalisation}normalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{normalisation} hyper-parameter.
+Brief discussions follow and illustrations are provided for visual aid.
+As a reminder, the normalisation hyper-parameter is a flag that enables or disables normalisation of the concentration parameters in an attempt to provide more exploration in the \index{heuristic}heuristic space.
+
+Table \ref{tab:results:normalise:metrics} provides the ranked performance, per dataset, with normalisation enabled and disabled.
+Similar to before, the performance rank is calculated as the average rank produced by the normalisation configurations, for all datasets, over all runs and all training epochs.
+
+\begin{table}[H]
+	\centering
+	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:normalise:metrics}%
@@
 
-\begin{figure}[htbp]
+Table \ref{tab:results:normalise:metrics} shows that, in general, there is no obvious difference in the outcomes of the \acs{BHH} when normalisation is enabled or disabled.
+For some datasets such as bank, fish toxicity, forest fires, iris, and wine quality, enabling normalisation provided the best results, while disabling of the normalisation flag provided the best results for the other datasets.
+This suggests that the normalisation flag is problem specific.
+Since the normalisation hyper-parameter provides a mechanism for the \acs{BHH} to explore more in the \index{heuristic}heuristic space, with the intent of finding better solutions, it can be concluded that some datasets require more exploration, while others require more exploitation.
+
+Figure~\ref{fig:results:normalise:descriptive:descriptive} provides a illustration of the descriptive plots for the \acs{BHH} configurations with the normalisation hyper-parameter enabled and disabled, per dataset.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:normalise:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for normalisation configurations that are enabled and disabled, as it relates to all datasets, across all runs.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:normalise:descriptive:descriptive} shows no statistical difference in the outcomes of the normalisation configurations of the \acs{BHH}.
+This further supports the suggestion that the use of the normalisation hyper-parameter is problem specific.
+
+Similar to before, Figure~\ref{fig:results:normalise:figures:abalone} provides the train and test, loss and accuracy plot for an example classification dataset (abalone) as it relates to the normalisation experimental group.
+As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:normalise:figures:bike} provides the train and test loss plot for an example regression dataset (bike) as it relates to the normalisation experimental group.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% DISCOUNTED REWARDS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Discounted Rewards}\label{sec:results:discounted_rewards}
 
-\begin{table}[htbp]
-	\centering
-	\caption{Empirical results showing average rank and statistics for \index{discounted rewards}discounted rewards toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{discounted rewards} hyper-parameter.
+Brief discussions follow and illustrations are provided for visual aid.
+As a reminder, the discounted rewards hyper-parameter is a flag that enables or disables discounted rewards of the pseudo counts that are added to concentration parameters in an attempt to provide control over the effects of past performances of the low-level \index{heuristic}heuristics.
+
+Table \ref{tab:results:discounted_rewards:metrics} provides the ranked performance, per dataset, with discounted rewards enabled and disabled.
+Similar to before, the performance rank is calculated as the average rank produced by the discounted rewards configurations, for all datasets, over all runs and all training epochs.
+
+\begin{table}[H]
+	\centering
+	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
 	\label{tab:results:discounted_rewards:metrics}%
@@
 			                                   & \multicolumn{1}{l}{\textbf{discounted rewards}} & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                   &                                                                           &                 \\
-			\cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{FALSE}}              &                                                                                    &                 & \multicolumn{1}{l}{\textbf{TRUE}} &                                                                           &                 \\
+			\cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{false}}              &                                                                                    &                 & \multicolumn{1}{l}{\textbf{true}} &                                                                           &                 \\
 			\cmidrule{2-7}    \textbf{dataset} & \textbf{count}                                  & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
@@
 
-\begin{figure}[htbp]
+Table \ref{tab:results:discounted_rewards:metrics} shows that, in general, there is no obvious difference in the outcomes of the \acs{BHH} when discounted rewards is enabled or disabled.
+
+Figure~\ref{fig:results:discounted_rewards:descriptive:descriptive} provides a illustration of the descriptive plots for the \acs{BHH} configurations with the discounted rewards hyper-parameter enabled and disabled, per dataset.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:discounted_rewards:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for discounted rewards configurations that are enabled and disabled, as it relates to all datasets, across all runs.
+
+\begin{figure}[H]
 	\centering
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:discounted_rewards:descriptive:descriptive} shows no statistical difference in the outcomes of the discounted rewards configurations of the \acs{BHH}.
+This further supports the suggestion that the use of the discounted rewards hyper-parameter is problem specific.
+
+Similar to before, Figure~\ref{fig:results:discounted_rewards:figures:wine_quality} provides the train and test, loss and accuracy plot for an example classification dataset (wine quality) as it relates to the discounted rewards experimental group.
+As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{figure}[htbp]
+Figure~\ref{fig:results:discounted_rewards:figures:housing} provides the train and test loss plot for an example regression dataset (housing) as it relates to the discounted rewards experimental group.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\section{Overfitting}\label{sec:results:overfitting}
-
-\section{Practical Applications}\label{sec:results:practical_applications}
-
 \section{Summary}\label{sec:results:summary}
+
+TODO

### 2022-11-15 dissertation/chapters/08-results.tex
🚧 (results): WIP replotting tables

@@
 
-% Table generated by Excel2LaTeX from sheet 'results - test - loss'
-\begin{table}[H]
-	\centering
-	\caption{Empirical results showing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
-	\label{tab:results:standalone:metrics:test_loss}%
+\begin{sidewaystable}[htbp]
+	\centering
+	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\label{tab:results:standalone:metrics:rank}%
 	\par\bigskip
 	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rlccc|c|c|c|c|c|ccccc}
-			epoch                                                                          & 30                 &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
-			                                                                               &                    &                                                                                &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
-			                                                                               &                    & \multicolumn{1}{l}{\textbf{heuristic}}                                         &                                                                                & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            & \multicolumn{1}{r}{}                                                           & \multicolumn{1}{r}{}                            &                                                 &                                                 &                                                 &                                                 &                                                 \\
-			\cmidrule{3-3}\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}    \textbf{dataset} & \textbf{statistic} & \textbf{adagrad}                                                               & \textbf{adam}                                                                  & \textbf{nag}                                                                   & \textbf{bhh\_gd}                                & \textbf{rmsprop}                                                               & \textbf{bhh\_all}                               & \textbf{adadelta}                                                              & \textbf{bhh\_mh}                                & \textbf{ga}                                     & \textbf{sgd}                                    & \textbf{pso}                                    & \textbf{momentum}                               & \textbf{de}                                     \\
-			\midrule
-			abalone                                                                        & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .506,  .776,  .486}1.967785                                   & \cellcolor[rgb]{ .494,  .773,  .486}1.965134827                                & \cellcolor[rgb]{ .765,  .851,  .502}2.0156043                                  & \cellcolor[rgb]{ .749,  .847,  .502}2.012517173 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{1.94553315}  & \cellcolor[rgb]{ 1,  .922,  .518}2.058704583    & \cellcolor[rgb]{ .788,  .859,  .502}2.019921077                                & \cellcolor[rgb]{ .996,  .827,  .502}2.29420573  & \cellcolor[rgb]{ .984,  .612,  .459}2.81545685  & \cellcolor[rgb]{ .992,  .773,  .49}2.42804241   & \cellcolor[rgb]{ .98,  .522,  .443}3.038417873  & \cellcolor[rgb]{ .992,  .745,  .486}2.494169393 & \cellcolor[rgb]{ .973,  .412,  .42}3.295858177  \\
-			                                                                               & std                & 0.031577789                                                                    & 0.034949967                                                                    & 0.034657443                                                                    & 0.068121366                                     & 0.035183664                                                                    & 0.087594488                                     & 0.034405331                                                                    & 0.055085207                                     & 0.055148148                                     & 0.028810924                                     & 0.293755503                                     & 0.029086341                                     & 0.016489872                                     \\
-			adult                                                                          & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ 1,  .922,  .518}0.346737798                                   & \cellcolor[rgb]{ 1,  .922,  .518}0.38233353                                    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.313320884} & \cellcolor[rgb]{ .788,  .859,  .502}0.335180995 & \cellcolor[rgb]{ .933,  .902,  .514}0.343292783                                & \cellcolor[rgb]{ .973,  .412,  .42}586.2065996  & \cellcolor[rgb]{ .467,  .765,  .486}0.317677033                                & \cellcolor[rgb]{ 1,  .922,  .518}0.363543899    & \cellcolor[rgb]{ 1,  .922,  .518}0.392047161    & \cellcolor[rgb]{ .388,  .745,  .482}0.313329677 & \cellcolor[rgb]{ 1,  .922,  .518}1.217724345    & \cellcolor[rgb]{ .388,  .745,  .482}0.313444396 & \cellcolor[rgb]{ 1,  .922,  .518}0.639695856    \\
-			                                                                               & std                & 0.003704238                                                                    & 0.018067239                                                                    & 0.000510377                                                                    & 0.043628962                                     & 0.014659665                                                                    & 1261.204704                                     & 0.005277776                                                                    & 0.020803371                                     & 0.020086997                                     & 0.000411017                                     & 0.496591684                                     & 0.0003947                                       & 0.042558869                                     \\
-			air quality                                                                    & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .651,  .82,  .494}0.256871193                                 & \cellcolor[rgb]{ .827,  .871,  .506}0.260623969                                & \cellcolor[rgb]{ .647,  .82,  .494}0.256829053                                 & \cellcolor[rgb]{ 1,  .922,  .518}0.264177871    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.251334045} & \cellcolor[rgb]{ .996,  .827,  .502}0.272859303 & \cellcolor[rgb]{ .647,  .82,  .494}0.256781683                                 & \cellcolor[rgb]{ .976,  .914,  .514}0.263703859 & \cellcolor[rgb]{ .996,  .792,  .494}0.275862527 & \cellcolor[rgb]{ .988,  .69,  .475}0.285172782  & \cellcolor[rgb]{ .984,  .608,  .459}0.292264593 & \cellcolor[rgb]{ .984,  .604,  .459}0.292851261 & \cellcolor[rgb]{ .973,  .412,  .42}0.309698115  \\
-			                                                                               & std                & 0.007475522                                                                    & 0.008912099                                                                    & 0.005955119                                                                    & 0.011452365                                     & 0.007814891                                                                    & 0.016310047                                     & 0.00630808                                                                     & 0.007306605                                     & 0.008162884                                     & 0.014769128                                     & 0.022648597                                     & 0.016417541                                     & 0.017044223                                     \\
-			bank                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .459,  .765,  .486}0.209641222                                & \cellcolor[rgb]{ .4,  .745,  .482}0.206461621                                  & \cellcolor[rgb]{ .588,  .8,  .49}0.2164275                                     & \cellcolor[rgb]{ .588,  .8,  .49}0.21643132     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.205779476} & \cellcolor[rgb]{ 1,  .886,  .514}0.245610465    & \cellcolor[rgb]{ .627,  .812,  .494}0.218599386                                & \cellcolor[rgb]{ .996,  .839,  .502}0.256171151 & \cellcolor[rgb]{ .988,  .686,  .475}0.28813827  & \cellcolor[rgb]{ 1,  .922,  .518}0.238179998    & \cellcolor[rgb]{ .973,  .412,  .42}0.345448185  & \cellcolor[rgb]{ 1,  .922,  .518}0.238550439    & \cellcolor[rgb]{ .976,  .424,  .424}0.343699166 \\
-			                                                                               & std                & 0.004750498                                                                    & 0.004040969                                                                    & 0.005944898                                                                    & 0.004889433                                     & 0.005654034                                                                    & 0.064531685                                     & 0.003821749                                                                    & 0.010550504                                     & 0.012801143                                     & 0.005568018                                     & 0.033990143                                     & 0.004820977                                     & 0.028120079                                     \\
-			bike                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.045805387} & \cellcolor[rgb]{ .592,  .804,  .494}0.068179412                                & \cellcolor[rgb]{ .882,  .886,  .51}0.099539486                                 & \cellcolor[rgb]{ .467,  .765,  .486}0.054496914 & \cellcolor[rgb]{ 1,  .922,  .518}0.112259627                                   & \cellcolor[rgb]{ .565,  .796,  .49}0.065136647  & \cellcolor[rgb]{ .588,  .8,  .49}0.06793708                                    & \cellcolor[rgb]{ 1,  .902,  .514}0.11787523     & \cellcolor[rgb]{ .992,  .761,  .486}0.153095534 & \cellcolor[rgb]{ .992,  .733,  .482}0.159868436 & \cellcolor[rgb]{ .992,  .773,  .49}0.150273084  & \cellcolor[rgb]{ .992,  .725,  .482}0.161397393 & \cellcolor[rgb]{ .973,  .412,  .42}0.239867227  \\
-			                                                                               & std                & 0.001725608                                                                    & 0.068117237                                                                    & 0.001754469                                                                    & 0.005239285                                     & 0.103490928                                                                    & 0.019626763                                     & 0.002076596                                                                    & 0.005954748                                     & 0.005079692                                     & 0.002759                                        & 0.025177188                                     & 0.003354245                                     & 0.039791214                                     \\
-			car                                                                            & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .729,  .843,  .502}0.202726327                                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.09724452}  & \cellcolor[rgb]{ .867,  .882,  .51}0.245363623                                 & \cellcolor[rgb]{ .62,  .812,  .494}0.16895294   & \cellcolor[rgb]{ .408,  .749,  .482}0.103937737                                & \cellcolor[rgb]{ .58,  .8,  .49}0.15718728      & \cellcolor[rgb]{ 1,  .922,  .518}0.285888989                                   & \cellcolor[rgb]{ .992,  .733,  .482}0.489062582 & \cellcolor[rgb]{ .98,  .502,  .439}0.737354357  & \cellcolor[rgb]{ .98,  .533,  .443}0.703539757  & \cellcolor[rgb]{ .988,  .667,  .471}0.563173207 & \cellcolor[rgb]{ .98,  .506,  .439}0.73217904   & \cellcolor[rgb]{ .973,  .412,  .42}0.833160108  \\
-			                                                                               & std                & 0.018356416                                                                    & 0.023870777                                                                    & 0.028744869                                                                    & 0.025441117                                     & 0.031133074                                                                    & 0.033710554                                     & 0.027353972                                                                    & 0.076505599                                     & 0.062600847                                     & 0.052091474                                     & 0.157928484                                     & 0.042705727                                     & 0.074182791                                     \\
-			diabetic                                                                       & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .694,  .831,  .498}0.889537739                                & \cellcolor[rgb]{ 1,  .898,  .514}0.919339482                                   & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.880898965} & \cellcolor[rgb]{ .98,  .914,  .514}0.897587026  & \cellcolor[rgb]{ .918,  .894,  .51}0.895749019                                 & \cellcolor[rgb]{ .973,  .412,  .42}1.298319185  & \cellcolor[rgb]{ .49,  .773,  .486}0.883864405                                 & \cellcolor[rgb]{ 1,  .902,  .518}0.913694494    & \cellcolor[rgb]{ .996,  .843,  .506}0.961291775 & \cellcolor[rgb]{ .976,  .914,  .514}0.897429714 & \cellcolor[rgb]{ .996,  .835,  .502}0.966103049 & \cellcolor[rgb]{ 1,  .922,  .518}0.898038783    & \cellcolor[rgb]{ .988,  .694,  .475}1.077362637 \\
-			                                                                               & std                & 0.004272255                                                                    & 0.00981794                                                                     & 0.003758597                                                                    & 0.010748722                                     & 0.004045488                                                                    & 0.659754133                                     & 0.004759234                                                                    & 0.008388702                                     & 0.00657199                                      & 0.003551413                                     & 0.016450474                                     & 0.002801135                                     & 0.0391395                                       \\
-			fish toxicity                                                                  & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .588,  .8,  .49}0.09908239                                    & \cellcolor[rgb]{ .451,  .761,  .482}0.097196901                                & \cellcolor[rgb]{ .831,  .871,  .506}0.10233624                                 & \cellcolor[rgb]{ 1,  .91,  .518}0.105584544     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.096326802} & \cellcolor[rgb]{ 1,  .922,  .518}0.104598099    & \cellcolor[rgb]{ .773,  .855,  .502}0.101567158                                & \cellcolor[rgb]{ .976,  .914,  .514}0.104293618 & \cellcolor[rgb]{ 1,  .863,  .506}0.109342435    & \cellcolor[rgb]{ .976,  .475,  .435}0.139280655 & \cellcolor[rgb]{ 1,  .855,  .506}0.109946059    & \cellcolor[rgb]{ .973,  .412,  .42}0.144088336  & \cellcolor[rgb]{ .992,  .733,  .482}0.119344204 \\
-			                                                                               & std                & 0.008463336                                                                    & 0.006948088                                                                    & 0.007611236                                                                    & 0.008228438                                     & 0.008021585                                                                    & 0.008136956                                     & 0.008882708                                                                    & 0.00895412                                      & 0.008990894                                     & 0.012326524                                     & 0.012481736                                     & 0.012407706                                     & 0.0130782                                       \\
-			forest fires                                                                   & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ 1,  .922,  .518}0.064321917                                   & \cellcolor[rgb]{ .557,  .792,  .49}0.052658676                                 & \cellcolor[rgb]{ .851,  .878,  .506}0.05923886                                 & \cellcolor[rgb]{ .824,  .871,  .506}0.058617148 & \cellcolor[rgb]{ 1,  .922,  .518}0.062552555                                   & \cellcolor[rgb]{ 1,  .89,  .514}0.080966845     & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.048831474} & \cellcolor[rgb]{ .976,  .914,  .514}0.06209696  & \cellcolor[rgb]{ .553,  .792,  .49}0.05260701   & \cellcolor[rgb]{ .992,  .722,  .482}0.180571383 & \cellcolor[rgb]{ 1,  .914,  .518}0.069210426    & \cellcolor[rgb]{ .992,  .706,  .478}0.188476672 & \cellcolor[rgb]{ .973,  .412,  .42}0.359831599  \\
-			                                                                               & std                & 0.039911806                                                                    & 0.039243672                                                                    & 0.031685801                                                                    & 0.034163415                                     & 0.039170629                                                                    & 0.069099845                                     & 0.032095867                                                                    & 0.038470671                                     & 0.025957821                                     & 0.008365929                                     & 0.047244856                                     & 0.010081381                                     & 0.089999905                                     \\
-			housing                                                                        & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .518,  .78,  .486}0.088925893                                 & \cellcolor[rgb]{ .404,  .749,  .482}0.08481865                                 & \cellcolor[rgb]{ .612,  .808,  .494}0.092269667                                & \cellcolor[rgb]{ .69,  .831,  .498}0.095072459  & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.08422333}  & \cellcolor[rgb]{ .663,  .824,  .498}0.094078934 & \cellcolor[rgb]{ 1,  .922,  .518}0.105999965                                   & \cellcolor[rgb]{ 1,  .867,  .51}0.116883814     & \cellcolor[rgb]{ .996,  .812,  .498}0.127851649 & \cellcolor[rgb]{ .984,  .576,  .455}0.173521216 & \cellcolor[rgb]{ .992,  .722,  .482}0.145240159 & \cellcolor[rgb]{ .984,  .588,  .455}0.171302372 & \cellcolor[rgb]{ .973,  .412,  .42}0.205724786  \\
-			                                                                               & std                & 0.012490666                                                                    & 0.011213172                                                                    & 0.015551947                                                                    & 0.014823695                                     & 0.014924594                                                                    & 0.017302471                                     & 0.018700331                                                                    & 0.019460369                                     & 0.020192262                                     & 0.022837541                                     & 0.029813905                                     & 0.017916976                                     & 0.036445189                                     \\
-			iris                                                                           & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .788,  .859,  .502}0.216138929                                & \cellcolor[rgb]{ .514,  .78,  .486}0.120305813                                 & \cellcolor[rgb]{ .416,  .753,  .482}0.084967127                                & \cellcolor[rgb]{ 1,  .855,  .506}0.372908547    & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.075287772} & \cellcolor[rgb]{ .859,  .878,  .506}0.241094806 & \cellcolor[rgb]{ .996,  .808,  .498}0.426015649                                & \cellcolor[rgb]{ .686,  .831,  .498}0.180917533 & \cellcolor[rgb]{ 1,  .922,  .518}0.289495446    & \cellcolor[rgb]{ .992,  .773,  .49}0.469415404  & \cellcolor[rgb]{ .973,  .412,  .42}0.896458149  & \cellcolor[rgb]{ .992,  .745,  .486}0.502796506 & \cellcolor[rgb]{ .98,  .494,  .435}0.802733988  \\
-			                                                                               & std                & 0.059156887                                                                    & 0.097731271                                                                    & 0.041820159                                                                    & 1.119111663                                     & 0.045657899                                                                    & 0.295227964                                     & 0.071608458                                                                    & 0.163729792                                     & 0.117435582                                     & 0.087556703                                     & 0.844445785                                     & 0.072001841                                     & 0.684394699                                     \\
-			mushroom                                                                       & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .549,  .792,  .49}0.002577835                                 & \cellcolor[rgb]{ .467,  .765,  .486}0.001321295                                & \cellcolor[rgb]{ 1,  .922,  .518}0.009417256                                   & \cellcolor[rgb]{ .439,  .757,  .482}0.000906998 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{8.30695E-05} & \cellcolor[rgb]{ .718,  .839,  .498}0.005152476 & \cellcolor[rgb]{ .655,  .82,  .494}0.00417499                                  & \cellcolor[rgb]{ 1,  .871,  .51}0.077415858     & \cellcolor[rgb]{ .984,  .561,  .451}0.489160105 & \cellcolor[rgb]{ .996,  .796,  .494}0.179705445 & \cellcolor[rgb]{ 1,  .886,  .514}0.061137885    & \cellcolor[rgb]{ .992,  .749,  .486}0.241811308 & \cellcolor[rgb]{ .973,  .412,  .42}0.687017333  \\
-			                                                                               & std                & 0.000662841                                                                    & 0.004905902                                                                    & 0.002279151                                                                    & 0.001259819                                     & 6.96496E-05                                                                    & 0.012039998                                     & 0.000905097                                                                    & 0.019865901                                     & 0.024593143                                     & 0.009208458                                     & 0.06033175                                      & 0.012790223                                     & 0.01638976                                      \\
-			parkinsons                                                                     & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .51,  .776,  .486}0.056277858                                 & \cellcolor[rgb]{ .412,  .749,  .482}0.054480758                                & \cellcolor[rgb]{ 1,  .922,  .518}0.065451464                                   & \cellcolor[rgb]{ .639,  .816,  .494}0.058737776 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.053985977} & \cellcolor[rgb]{ .639,  .816,  .494}0.05873821  & \cellcolor[rgb]{ .69,  .831,  .498}0.05967759                                  & \cellcolor[rgb]{ 1,  .918,  .518}0.065774264    & \cellcolor[rgb]{ 1,  .898,  .514}0.066854953    & \cellcolor[rgb]{ .976,  .467,  .431}0.092323864 & \cellcolor[rgb]{ 1,  .894,  .514}0.067066667    & \cellcolor[rgb]{ .973,  .412,  .42}0.095371925  & \cellcolor[rgb]{ .984,  .604,  .459}0.084321583 \\
-			                                                                               & std                & 0.001432862                                                                    & 0.001998668                                                                    & 0.002301839                                                                    & 0.002859752                                     & 0.001547989                                                                    & 0.002811075                                     & 0.001691389                                                                    & 0.002548177                                     & 0.003281185                                     & 0.008302374                                     & 0.005043049                                     & 0.009431099                                     & 0.008978517                                     \\
-			student performance                                                            & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{0.165552792} & \cellcolor[rgb]{ .98,  .522,  .443}0.492891063                                 & \cellcolor[rgb]{ .471,  .769,  .486}0.169715979                                & \cellcolor[rgb]{ 1,  .855,  .506}0.245419875    & \cellcolor[rgb]{ .973,  .412,  .42}0.572439541                                 & \cellcolor[rgb]{ 1,  .871,  .51}0.235942235     & \cellcolor[rgb]{ .49,  .773,  .486}0.170794263                                 & \cellcolor[rgb]{ .969,  .91,  .514}0.194664435  & \cellcolor[rgb]{ 1,  .922,  .518}0.196187948    & \cellcolor[rgb]{ .933,  .902,  .514}0.193041307 & \cellcolor[rgb]{ .984,  .573,  .451}0.456490052 & \cellcolor[rgb]{ .925,  .898,  .51}0.192542094  & \cellcolor[rgb]{ 1,  .918,  .518}0.201390878    \\
-			                                                                               & std                & 0.011258528                                                                    & 0.105388532                                                                    & 0.010966961                                                                    & 0.133694251                                     & 0.05360667                                                                     & 0.10249181                                      & 0.010377173                                                                    & 0.014024256                                     & 0.009798773                                     & 0.011295962                                     & 0.049033016                                     & 0.011402763                                     & 0.011757846                                     \\
-			wine quality                                                                   & count              & 30                                                                             & 30                                                                             & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                                                             & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              & 30                                              \\
-			                                                                               & avg                & \cellcolor[rgb]{ .631,  .816,  .494}1.06505343                                 & \cellcolor[rgb]{ .388,  .745,  .482}\textcolor[rgb]{ 0,  .38,  0}{1.039511785} & \cellcolor[rgb]{ .698,  .831,  .498}1.07178488                                 & \cellcolor[rgb]{ 1,  .922,  .518}1.102805083    & \cellcolor[rgb]{ .502,  .776,  .486}1.051442793                                & \cellcolor[rgb]{ .804,  .863,  .506}1.082728853 & \cellcolor[rgb]{ .788,  .859,  .502}1.080905303                                & \cellcolor[rgb]{ .996,  .839,  .502}1.166586247 & \cellcolor[rgb]{ .992,  .725,  .482}1.251597837 & \cellcolor[rgb]{ .996,  .843,  .502}1.16477848  & \cellcolor[rgb]{ .988,  .659,  .467}1.3045869   & \cellcolor[rgb]{ .996,  .824,  .502}1.17741444  & \cellcolor[rgb]{ .973,  .412,  .42}1.489554557  \\
-			                                                                               & std                & 0.023560192                                                                    & 0.018361143                                                                    & 0.024922811                                                                    & 0.039250798                                     & 0.020795097                                                                    & 0.026483778                                     & 0.021109916                                                                    & 0.030251195                                     & 0.045716819                                     & 0.022984412                                     & 0.114260845                                     & 0.01919043                                      & 0.092922599                                     \\
-			\bottomrule
-		\end{tabular}%
+		\begin{tabular}{r|ccc|c|c|c|c|c|ccccc}
+			                              & \multicolumn{13}{c}{\textbf{BHH vs.
+Low-Level Heuristics - Average Rank}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\
+			\textbf{dataset}              & \textbf{adagrad}                                                          & \textbf{adam}                                           & \textbf{rmsprop}                                        & \textbf{bhh\_gd}                                        & \textbf{nag}                                            & \textbf{bhh\_all}                                       & \textbf{adadelta}                                       & \textbf{bhh\_mh}                                        & \textbf{ga}                                              & \textbf{pso}                                             & \textbf{sgd}                                             & \textbf{momentum}                                        & \textbf{de}                                              \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .388,  .745,  .482}2.2215 ($\pm$1.591)                   & \cellcolor[rgb]{ .416,  .753,  .482}2.3989 ($\pm$1.887) & \cellcolor[rgb]{ .78,  .859,  .502}4.6172 ($\pm$2.65)   & \cellcolor[rgb]{ .796,  .863,  .506}4.7032 ($\pm$2.108) & \cellcolor[rgb]{ .725,  .839,  .498}4.2731 ($\pm$1.542) & \cellcolor[rgb]{ 1,  .922,  .518}5.9376 ($\pm$2.399)    & \cellcolor[rgb]{ .894,  .89,  .51}5.3129 ($\pm$1.478)   & \cellcolor[rgb]{ .992,  .749,  .486}8.1882 ($\pm$1.195) & \cellcolor[rgb]{ .98,  .525,  .443}11.1108 ($\pm$1.102)  & \cellcolor[rgb]{ .98,  .514,  .439}11.2559 ($\pm$1.826)  & \cellcolor[rgb]{ .992,  .718,  .478}8.628 ($\pm$1.019)   & \cellcolor[rgb]{ .984,  .624,  .463}9.8151 ($\pm$1.16)   & \cellcolor[rgb]{ .973,  .412,  .42}12.5376 ($\pm$1.329)  \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                   & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\
+			\textbf{bank}                 & \cellcolor[rgb]{ .455,  .765,  .486}2.5495 ($\pm$1.598)                   & \cellcolor[rgb]{ .388,  .745,  .482}2.0796 ($\pm$1.587) & \cellcolor[rgb]{ .588,  .8,  .49}3.4645 ($\pm$2.209)    & \cellcolor[rgb]{ .8,  .863,  .506}4.8828 ($\pm$1.702)   & \cellcolor[rgb]{ .71,  .835,  .498}4.2871 ($\pm$1.732)  & \cellcolor[rgb]{ 1,  .922,  .518}6.2419 ($\pm$2.157)    & \cellcolor[rgb]{ .914,  .894,  .51}5.672 ($\pm$1.241)   & \cellcolor[rgb]{ .988,  .639,  .463}9.7495 ($\pm$1.048) & \cellcolor[rgb]{ .98,  .537,  .447}10.9817 ($\pm$1.216)  & \cellcolor[rgb]{ .976,  .467,  .431}11.8376 ($\pm$1.464) & \cellcolor[rgb]{ .992,  .757,  .486}8.2774 ($\pm$1.03)   & \cellcolor[rgb]{ .992,  .741,  .486}8.4774 ($\pm$1.068)  & \cellcolor[rgb]{ .973,  .412,  .42}12.4989 ($\pm$1.224)  \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.7204 ($\pm$1.384)                   & \cellcolor[rgb]{ .643,  .816,  .494}3.6925 ($\pm$4.004) & \cellcolor[rgb]{ .973,  .914,  .514}6.2624 ($\pm$4.58)  & \cellcolor[rgb]{ .663,  .824,  .498}3.8441 ($\pm$1.398) & \cellcolor[rgb]{ 1,  .922,  .518}6.4516 ($\pm$1.02)     & \cellcolor[rgb]{ .71,  .835,  .498}4.2151 ($\pm$1.361)  & \cellcolor[rgb]{ .859,  .878,  .506}5.3602 ($\pm$1.155) & \cellcolor[rgb]{ .996,  .843,  .506}7.4108 ($\pm$1.008) & \cellcolor[rgb]{ .988,  .686,  .475}9.2269 ($\pm$1.183)  & \cellcolor[rgb]{ .988,  .682,  .475}9.3086 ($\pm$1.761)  & \cellcolor[rgb]{ .984,  .596,  .455}10.3355 ($\pm$1.419) & \cellcolor[rgb]{ .984,  .561,  .451}10.7086 ($\pm$1.423) & \cellcolor[rgb]{ .973,  .412,  .42}12.4634 ($\pm$1.465)  \\
+			\textbf{car}                  & \cellcolor[rgb]{ .702,  .835,  .498}4.7634 ($\pm$0.938)                   & \cellcolor[rgb]{ .388,  .745,  .482}1.6226 ($\pm$1.405) & \cellcolor[rgb]{ .455,  .765,  .486}2.3269 ($\pm$1.409) & \cellcolor[rgb]{ .561,  .792,  .49}3.3473 ($\pm$1.35)   & \cellcolor[rgb]{ .831,  .871,  .506}6.0785 ($\pm$0.799) & \cellcolor[rgb]{ .58,  .8,  .49}3.5624 ($\pm$1.315)     & \cellcolor[rgb]{ 1,  .922,  .518}7.7344 ($\pm$1.746)    & \cellcolor[rgb]{ .996,  .8,  .498}8.8505 ($\pm$1.413)   & \cellcolor[rgb]{ .984,  .592,  .455}10.7763 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .855,  .506}8.3613 ($\pm$1.622)     & \cellcolor[rgb]{ .988,  .651,  .467}10.2452 ($\pm$1.447) & \cellcolor[rgb]{ .984,  .576,  .451}10.9226 ($\pm$1.349) & \cellcolor[rgb]{ .973,  .412,  .42}12.4086 ($\pm$1.492)  \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .506,  .776,  .486}2.7796 ($\pm$1.659)                   & \cellcolor[rgb]{ 1,  .886,  .514}7.1484 ($\pm$2.227)    & \cellcolor[rgb]{ 1,  .922,  .518}6.7376 ($\pm$2.577)    & \cellcolor[rgb]{ .812,  .867,  .506}5.2269 ($\pm$2.186) & \cellcolor[rgb]{ .388,  .745,  .482}1.8118 ($\pm$1.413) & \cellcolor[rgb]{ .988,  .69,  .475}9.3968 ($\pm$3.022)  & \cellcolor[rgb]{ .494,  .773,  .486}2.6753 ($\pm$1.629) & \cellcolor[rgb]{ .992,  .765,  .49}8.557 ($\pm$1.17)    & \cellcolor[rgb]{ .98,  .529,  .443}11.2011 ($\pm$1.413)  & \cellcolor[rgb]{ .984,  .573,  .451}10.7022 ($\pm$1.067) & \cellcolor[rgb]{ .898,  .89,  .51}5.9215 ($\pm$1.542)    & \cellcolor[rgb]{ .949,  .906,  .514}6.3355 ($\pm$1.612)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5065 ($\pm$1.242)  \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                    & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                   & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\
+			\textbf{housing}              & \cellcolor[rgb]{ .404,  .749,  .482}3.4484 ($\pm$2.025)                   & \cellcolor[rgb]{ .388,  .745,  .482}3.3344 ($\pm$1.819) & \cellcolor[rgb]{ .439,  .757,  .482}3.6946 ($\pm$2.166) & \cellcolor[rgb]{ .553,  .792,  .49}4.4742 ($\pm$2.312)  & \cellcolor[rgb]{ .584,  .8,  .49}4.6839 ($\pm$2.658)    & \cellcolor[rgb]{ .537,  .788,  .49}4.3763 ($\pm$2.438)  & \cellcolor[rgb]{ 1,  .918,  .518}7.5903 ($\pm$2.748)    & \cellcolor[rgb]{ 1,  .922,  .518}7.5441 ($\pm$1.736)    & \cellcolor[rgb]{ 1,  .878,  .51}7.8839 ($\pm$2.099)      & \cellcolor[rgb]{ .984,  .608,  .459}9.9409 ($\pm$2.317)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4075 ($\pm$1.528)  & \cellcolor[rgb]{ .976,  .431,  .424}11.2731 ($\pm$1.506) & \cellcolor[rgb]{ .976,  .42,  .424}11.3484 ($\pm$2.096)  \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .965,  .91,  .514}6.3946 ($\pm$1.6)                      & \cellcolor[rgb]{ .525,  .784,  .49}3.5839 ($\pm$2.511)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6968 ($\pm$1.912) & \cellcolor[rgb]{ .706,  .835,  .498}4.7473 ($\pm$2.275) & \cellcolor[rgb]{ .522,  .78,  .486}3.5548 ($\pm$2.125)  & \cellcolor[rgb]{ .78,  .859,  .502}5.2204 ($\pm$3.041)  & \cellcolor[rgb]{ .973,  .412,  .42}11.3527 ($\pm$1.779) & \cellcolor[rgb]{ 1,  .922,  .518}6.6075 ($\pm$2.555)    & \cellcolor[rgb]{ .992,  .749,  .486}8.2473 ($\pm$1.765)  & \cellcolor[rgb]{ .992,  .745,  .486}8.2731 ($\pm$4.384)  & \cellcolor[rgb]{ .98,  .518,  .443}10.3796 ($\pm$1.294)  & \cellcolor[rgb]{ .976,  .447,  .427}11.0548 ($\pm$1.409) & \cellcolor[rgb]{ .988,  .678,  .471}8.8871 ($\pm$3.251)  \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ .71,  .835,  .498}4.4656 ($\pm$1.053)                    & \cellcolor[rgb]{ .388,  .745,  .482}2.1344 ($\pm$1.883) & \cellcolor[rgb]{ .431,  .757,  .482}2.4656 ($\pm$1.359) & \cellcolor[rgb]{ .569,  .796,  .49}3.4484 ($\pm$1.602)  & \cellcolor[rgb]{ .969,  .91,  .514}6.3323 ($\pm$0.891)  & \cellcolor[rgb]{ .6,  .804,  .494}3.6688 ($\pm$2.469)   & \cellcolor[rgb]{ 1,  .922,  .518}6.5538 ($\pm$1.071)    & \cellcolor[rgb]{ .992,  .718,  .478}9.0452 ($\pm$1.093) & \cellcolor[rgb]{ .98,  .51,  .439}11.5731 ($\pm$1.193)   & \cellcolor[rgb]{ .996,  .816,  .498}7.872 ($\pm$0.92)    & \cellcolor[rgb]{ .988,  .659,  .471}9.7527 ($\pm$1.083)  & \cellcolor[rgb]{ .98,  .557,  .451}10.9785 ($\pm$1.108)  & \cellcolor[rgb]{ .973,  .412,  .42}12.7097 ($\pm$1.478)  \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .412,  .749,  .482}2.4677 ($\pm$1.497)                   & \cellcolor[rgb]{ .388,  .745,  .482}2.2333 ($\pm$1.742) & \cellcolor[rgb]{ .541,  .788,  .49}3.5656 ($\pm$2.492)  & \cellcolor[rgb]{ .655,  .82,  .494}4.572 ($\pm$1.934)   & \cellcolor[rgb]{ 1,  .922,  .518}7.5355 ($\pm$1.44)     & \cellcolor[rgb]{ .635,  .816,  .494}4.3839 ($\pm$1.861) & \cellcolor[rgb]{ .875,  .882,  .51}6.472 ($\pm$2.423)   & \cellcolor[rgb]{ .996,  .843,  .506}8.3161 ($\pm$1.644) & \cellcolor[rgb]{ 1,  .898,  .514}7.7968 ($\pm$1.719)     & \cellcolor[rgb]{ .996,  .827,  .502}8.4892 ($\pm$1.901)  & \cellcolor[rgb]{ .98,  .494,  .435}11.7516 ($\pm$1.155)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5419 ($\pm$1.351)  & \cellcolor[rgb]{ .984,  .584,  .455}10.8742 ($\pm$1.317) \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                   & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                    & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\
+			\midrule
+			\textbf{avg rank}             & \cellcolor[rgb]{ .388,  .745,  .482}3.5512 ($\pm$2.25)                    & \cellcolor[rgb]{ .471,  .769,  .486}3.9314 ($\pm$3.423) & \cellcolor[rgb]{ .616,  .808,  .494}4.5691 ($\pm$3.517) & \cellcolor[rgb]{ .631,  .812,  .494}4.6346 ($\pm$2.364) & \cellcolor[rgb]{ .675,  .827,  .498}4.8394 ($\pm$2.384) & \cellcolor[rgb]{ .808,  .867,  .506}5.4327 ($\pm$2.9)   & \cellcolor[rgb]{ 1,  .922,  .518}6.2727 ($\pm$3.004)    & \cellcolor[rgb]{ .992,  .776,  .49}7.7855 ($\pm$2.271)  & \cellcolor[rgb]{ .988,  .639,  .467}9.1522 ($\pm$2.48)   & \cellcolor[rgb]{ .984,  .612,  .459}9.4451 ($\pm$2.75)   & \cellcolor[rgb]{ .984,  .592,  .455}9.6445 ($\pm$2.214)  & \cellcolor[rgb]{ .98,  .529,  .443}10.2877 ($\pm$2.346)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4538 ($\pm$2.354)  \\
+			\midrule
+			\textbf{normalised avg rank}  & \cellcolor[rgb]{ .388,  .745,  .482}1                                     & \cellcolor[rgb]{ .49,  .773,  .486}2                    & \cellcolor[rgb]{ .592,  .804,  .494}3                   & \cellcolor[rgb]{ .694,  .831,  .498}4                   & \cellcolor[rgb]{ .796,  .863,  .506}5                   & \cellcolor[rgb]{ .898,  .89,  .51}6                     & \cellcolor[rgb]{ 1,  .922,  .518}7                      & \cellcolor[rgb]{ .996,  .839,  .502}8                   & \cellcolor[rgb]{ .992,  .753,  .486}9                    & \cellcolor[rgb]{ .988,  .667,  .471}10                   & \cellcolor[rgb]{ .984,  .584,  .455}11                   & \cellcolor[rgb]{ .98,  .498,  .439}12                    & \cellcolor[rgb]{ .973,  .412,  .42}13                    \\
+			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
+
 	}
-\end{table}%
+\end{sidewaystable}%
 
@@
 
-% Table generated by Excel2LaTeX from sheet 'results - test - rank'
-\begin{table}[H]
-	\centering
-	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:standalone:metrics:rank}%
+\begin{sidewaystable}[htbp]
+	\centering
+	\caption{Empirical results showing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
+	\label{tab:results:standalone:metrics:test_loss}%
 	\par\bigskip
 	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rcccc|c|c|c|c|c|ccccc}
-			epoch                                                                          & \multicolumn{1}{l}{(all)}              &                                                                                    &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
-			                                                                               &                                        &                                                                                    &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
-			                                                                               &                                        & \multicolumn{1}{l}{\textbf{heuristic}}                                             &                                                                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                           & \multicolumn{1}{r}{}                                                      & \multicolumn{1}{r}{}                         & \multicolumn{1}{r}{}                        & \multicolumn{1}{r}{}                           &                                                &                                                 &                                                 &                                                &                                                \\
-			\cmidrule{3-3}\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}    \textbf{dataset} & \multicolumn{1}{l}{\textbf{statistic}} & \textbf{adagrad}                                                                   & \textbf{adam}                                                             & \textbf{nag}                                                              & \textbf{bhh\_gd}                               & \textbf{rmsprop}                                                          & \textbf{bhh\_all}                            & \textbf{adadelta}                           & \textbf{bhh\_mh}                               & \textbf{ga}                                    & \textbf{sgd}                                    & \textbf{pso}                                    & \textbf{momentum}                              & \textbf{de}                                    \\
-			\midrule
-			abalone                                                                        & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2215}          & 2.3989                                                                    & 4.2731                                                                    & 4.7032                                         & 4.6172                                                                    & 5.9376                                       & 5.3129                                      & 8.1882                                         & 11.1108                                        & 8.6280                                          & 11.2559                                         & 9.8151                                         & 12.5376                                        \\
-			                                                                               & std                                    & 1.5913                                                                             & 1.8873                                                                    & 1.5419                                                                    & 2.1080                                         & 2.6504                                                                    & 2.3994                                       & 1.4782                                      & 1.1947                                         & 1.1017                                         & 1.0193                                          & 1.8265                                          & 1.1601                                         & 1.3291                                         \\
-			adult                                                                          & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 5.8978                                                                             & 7.6258                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5140} & 5.3258                                         & 6.6892                                                                    & 12.0194                                      & 2.5258                                      & 7.9409                                         & 9.5860                                         & 3.0065                                          & 11.5344                                         & 3.8699                                         & 10.9462                                        \\
-			                                                                               & std                                    & 1.6171                                                                             & 2.0293                                                                    & 0.7250                                                                    & 1.8985                                         & 1.8347                                                                    & 2.7430                                       & 1.3543                                      & 1.6391                                         & 1.7015                                         & 1.4999                                          & 2.0122                                          & 1.7090                                         & 1.8965                                         \\
-			air quality                                                                    & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 3.6409                                                                             & 5.4312                                                                    & 3.8194                                                                    & 5.0817                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.4452} & 6.6860                                       & 5.2441                                      & 6.3570                                         & 7.8204                                         & 10.6613                                         & 9.9151                                          & 11.7559                                        & 11.1419                                        \\
-			                                                                               & std                                    & 2.2588                                                                             & 2.6198                                                                    & 2.2285                                                                    & 2.7618                                         & 2.5704                                                                    & 3.0613                                       & 3.1622                                      & 2.3031                                         & 2.2652                                         & 1.6061                                          & 2.2882                                          & 1.4730                                         & 2.2361                                         \\
-			bank                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 2.5495                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.0796} & 4.2871                                                                    & 4.8828                                         & 3.4645                                                                    & 6.2419                                       & 5.6720                                      & 9.7495                                         & 10.9817                                        & 8.2774                                          & 11.8376                                         & 8.4774                                         & 12.4989                                        \\
-			                                                                               & std                                    & 1.5980                                                                             & 1.5871                                                                    & 1.7325                                                                    & 1.7017                                         & 2.2090                                                                    & 2.1571                                       & 1.2411                                      & 1.0482                                         & 1.2165                                         & 1.0304                                          & 1.4638                                          & 1.0682                                         & 1.2243                                         \\
-			bike                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7204}          & 3.6925                                                                    & 6.4516                                                                    & 3.8441                                         & 6.2624                                                                    & 4.2151                                       & 5.3602                                      & 7.4108                                         & 9.2269                                         & 10.3355                                         & 9.3086                                          & 10.7086                                        & 12.4634                                        \\
-			                                                                               & std                                    & 1.3839                                                                             & 4.0038                                                                    & 1.0199                                                                    & 1.3983                                         & 4.5803                                                                    & 1.3611                                       & 1.1555                                      & 1.0076                                         & 1.1835                                         & 1.4193                                          & 1.7615                                          & 1.4233                                         & 1.4648                                         \\
-			car                                                                            & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 4.7634                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6226} & 6.0785                                                                    & 3.3473                                         & 2.3269                                                                    & 3.5624                                       & 7.7344                                      & 8.8505                                         & 10.7763                                        & 10.2452                                         & 8.3613                                          & 10.9226                                        & 12.4086                                        \\
-			                                                                               & std                                    & 0.9383                                                                             & 1.4053                                                                    & 0.7991                                                                    & 1.3499                                         & 1.4091                                                                    & 1.3152                                       & 1.7464                                      & 1.4128                                         & 1.4715                                         & 1.4474                                          & 1.6222                                          & 1.3489                                         & 1.4915                                         \\
-			diabetic                                                                       & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 2.7796                                                                             & 7.1484                                                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8118} & 5.2269                                         & 6.7376                                                                    & 9.3968                                       & 2.6753                                      & 8.5570                                         & 11.2011                                        & 5.9215                                          & 10.7022                                         & 6.3355                                         & 12.5065                                        \\
-			                                                                               & std                                    & 1.6587                                                                             & 2.2265                                                                    & 1.4127                                                                    & 2.1860                                         & 2.5767                                                                    & 3.0221                                       & 1.6286                                      & 1.1699                                         & 1.4132                                         & 1.5421                                          & 1.0674                                          & 1.6118                                         & 1.2417                                         \\
-			fish toxicity                                                                  & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 4.2645                                                                             & 3.6022                                                                    & 5.8914                                                                    & 5.4118                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.5946} & 5.8290                                       & 7.9140                                      & 6.3849                                         & 6.7043                                         & 11.5785                                         & 7.5731                                          & 12.2301                                        & 10.0215                                        \\
-			                                                                               & std                                    & 2.6142                                                                             & 2.4453                                                                    & 2.6288                                                                    & 2.6649                                         & 2.3292                                                                    & 2.8557                                       & 3.4287                                      & 2.9437                                         & 2.8200                                         & 1.4587                                          & 2.9817                                          & 1.3822                                         & 2.3585                                         \\
-			forest fires                                                                   & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 5.1559                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{4.2688} & 5.6882                                                                    & 4.6935                                         & 5.0355                                                                    & 5.4839                                       & 6.5161                                      & 5.4591                                         & 7.3667                                         & 10.8129                                         & 6.4796                                          & 11.7065                                        & 12.3333                                        \\
-			                                                                               & std                                    & 2.9217                                                                             & 2.9841                                                                    & 2.2149                                                                    & 2.7594                                         & 3.1431                                                                    & 3.1070                                       & 3.0823                                      & 2.6680                                         & 2.3704                                         & 1.2070                                          & 3.3539                                          & 1.3250                                         & 1.9228                                         \\
-			housing                                                                        & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 3.4484                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{3.3344} & 4.6839                                                                    & 4.4742                                         & 3.6946                                                                    & 4.3763                                       & 7.5903                                      & 7.5441                                         & 7.8839                                         & 11.4075                                         & 9.9409                                          & 11.2731                                        & 11.3484                                        \\
-			                                                                               & std                                    & 2.0251                                                                             & 1.8193                                                                    & 2.6579                                                                    & 2.3125                                         & 2.1662                                                                    & 2.4377                                       & 2.7475                                      & 1.7363                                         & 2.0991                                         & 1.5278                                          & 2.3166                                          & 1.5059                                         & 2.0965                                         \\
-			iris                                                                           & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 6.3946                                                                             & 3.5839                                                                    & 3.5548                                                                    & 4.7473                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6968} & 5.2204                                       & 11.3527                                     & 6.6075                                         & 8.2473                                         & 10.3796                                         & 8.2731                                          & 11.0548                                        & 8.8871                                         \\
-			                                                                               & std                                    & 1.6000                                                                             & 2.5111                                                                    & 2.1247                                                                    & 2.2749                                         & 1.9121                                                                    & 3.0415                                       & 1.7791                                      & 2.5553                                         & 1.7647                                         & 1.2938                                          & 4.3840                                          & 1.4090                                         & 3.2511                                         \\
-			mushroom                                                                       & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 4.4656                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1344} & 6.3323                                                                    & 3.4484                                         & 2.4656                                                                    & 3.6688                                       & 6.5538                                      & 9.0452                                         & 11.5731                                        & 9.7527                                          & 7.8720                                          & 10.9785                                        & 12.7097                                        \\
-			                                                                               & std                                    & 1.0527                                                                             & 1.8831                                                                    & 0.8915                                                                    & 1.6019                                         & 1.3589                                                                    & 2.4687                                       & 1.0711                                      & 1.0931                                         & 1.1927                                         & 1.0828                                          & 0.9197                                          & 1.1075                                         & 1.4781                                         \\
-			parkinsons                                                                     & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 2.4677                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2333} & 7.5355                                                                    & 4.5720                                         & 3.5656                                                                    & 4.3839                                       & 6.4720                                      & 8.3161                                         & 7.7968                                         & 11.7516                                         & 8.4892                                          & 12.5419                                        & 10.8742                                        \\
-			                                                                               & std                                    & 1.4969                                                                             & 1.7418                                                                    & 1.4396                                                                    & 1.9337                                         & 2.4919                                                                    & 1.8612                                       & 2.4229                                      & 1.6441                                         & 1.7188                                         & 1.1551                                          & 1.9008                                          & 1.3515                                         & 1.3174                                         \\
-			student performance                                                            & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5634}          & 11.3978                                                                   & 3.1935                                                                    & 5.6624                                         & 12.4312                                                                   & 5.8634                                       & 3.4194                                      & 6.9333                                         & 7.1032                                         & 6.6366                                          & 11.0624                                         & 6.7011                                         & 8.0323                                         \\
-			                                                                               & std                                    & 1.9122                                                                             & 2.1780                                                                    & 2.1205                                                                    & 3.5703                                         & 1.3400                                                                    & 3.1588                                       & 2.0060                                      & 2.4398                                         & 1.9887                                         & 2.0233                                          & 1.0674                                          & 2.2423                                         & 1.9346                                         \\
-			wine quality                                                                   & count                                  & 930                                                                                & 930                                                                       & 930                                                                       & 930                                            & 930                                                                       & 930                                          & 930                                         & 930                                            & 930                                            & 930                                             & 930                                             & 930                                            & 930                                            \\
-			                                                                               & avg                                    & 3.2806                                                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1118} & 4.1505                                                                    & 4.7882                                         & 3.6301                                                                    & 5.1925                                       & 6.0011                                      & 9.5935                                         & 10.3387                                        & 8.6344                                          & 11.1602                                         & 9.5269                                         & 12.5903                                        \\
-			                                                                               & std                                    & 1.9309                                                                             & 1.6660                                                                    & 1.9156                                                                    & 2.1052                                         & 1.7314                                                                    & 1.9506                                       & 2.4040                                      & 1.4943                                         & 1.6201                                         & 1.1801                                          & 1.7732                                          & 1.3407                                         & 1.3515                                         \\
-			\midrule
-			\textbf{overall}                                                               & \textbf{avg}                           & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{3.7076}} & \textbf{4.1777}                                                           & \textbf{4.6177}                                                           & \textbf{4.6806}                                & \textbf{4.7105}                                                           & \textbf{5.8718}                              & \textbf{6.0229}                             & \textbf{7.7958}                                & \textbf{9.1811}                                & \textbf{9.2019}                                 & \textbf{9.5844}                                 & \textbf{9.8599}                                & \textbf{11.4200}                               \\
-			\textbf{normalised}                                                            & \textbf{rank}                          & \cellcolor[rgb]{ .388,  .745,  .482}\textbf{1}                                     & \cellcolor[rgb]{ .49,  .773,  .486}\textbf{2}                             & \cellcolor[rgb]{ .592,  .804,  .494}\textbf{3}                            & \cellcolor[rgb]{ .694,  .831,  .498}\textbf{4} & \cellcolor[rgb]{ .796,  .863,  .506}\textbf{5}                            & \cellcolor[rgb]{ .898,  .89,  .51}\textbf{6} & \cellcolor[rgb]{ 1,  .922,  .518}\textbf{7} & \cellcolor[rgb]{ .996,  .839,  .502}\textbf{8} & \cellcolor[rgb]{ .992,  .753,  .486}\textbf{9} & \cellcolor[rgb]{ .988,  .667,  .471}\textbf{10} & \cellcolor[rgb]{ .984,  .584,  .455}\textbf{11} & \cellcolor[rgb]{ .98,  .498,  .439}\textbf{12} & \cellcolor[rgb]{ .973,  .412,  .42}\textbf{13} \\
-			\cmidrule{6-6}\cmidrule{8-8}\cmidrule{10-10}\end{tabular}%
+		% Table generated by Excel2LaTeX from sheet 'loss'
+		\begin{tabular}{r|lll|l|l|l|l|l|lllll}
+			                                    & \multicolumn{13}{c}{\textbf{BHH vs.
+Low-Level Heuristics - Average Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
+			\cmidrule{2-14}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                      & \multicolumn{1}{c}{\textbf{adam}}                       & \multicolumn{1}{c|}{\textbf{rmsprop}}                   & \multicolumn{1}{c|}{\textbf{bhh\_gd}}                   & \multicolumn{1}{c|}{\textbf{nag}}                       & \multicolumn{1}{c|}{\textbf{bhh\_all}}                  & \multicolumn{1}{c|}{\textbf{adadelta}}                  & \multicolumn{1}{c|}{\textbf{bhh\_mh}}                   & \multicolumn{1}{c}{\textbf{ga}}                         & \multicolumn{1}{c}{\textbf{pso}}                        & \multicolumn{1}{c}{\textbf{sgd}}                        & \multicolumn{1}{c}{\textbf{momentum}}                   & \multicolumn{1}{c}{\textbf{de}}                         \\
+			\midrule
+			\textbf{abalone}                    & \cellcolor[rgb]{ .506,  .776,  .486}1.9678 ($\pm$0.032)                   & \cellcolor[rgb]{ .494,  .773,  .486}1.9651 ($\pm$0.035) & \cellcolor[rgb]{ .388,  .745,  .482}1.9455 ($\pm$0.035) & \cellcolor[rgb]{ .749,  .847,  .502}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .765,  .851,  .502}2.0156 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .788,  .859,  .502}2.0199 ($\pm$0.034) & \cellcolor[rgb]{ .996,  .827,  .502}2.2942 ($\pm$0.055) & \cellcolor[rgb]{ .984,  .612,  .459}2.8155 ($\pm$0.055) & \cellcolor[rgb]{ .98,  .522,  .443}3.0384 ($\pm$0.294)  & \cellcolor[rgb]{ .992,  .773,  .49}2.428 ($\pm$0.029)   & \cellcolor[rgb]{ .992,  .745,  .486}2.4942 ($\pm$0.029) & \cellcolor[rgb]{ .973,  .412,  .42}3.2959 ($\pm$0.016)  \\
+			\textbf{air\_quality}               & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                    & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\
+			\textbf{bank}                       & \cellcolor[rgb]{ .459,  .765,  .486}0.2096 ($\pm$0.005)                   & \cellcolor[rgb]{ .4,  .745,  .482}0.2065 ($\pm$0.004)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2058 ($\pm$0.006) & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.005)    & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .886,  .514}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .627,  .812,  .494}0.2186 ($\pm$0.004) & \cellcolor[rgb]{ .996,  .839,  .502}0.2562 ($\pm$0.011) & \cellcolor[rgb]{ .988,  .686,  .475}0.2881 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.3454 ($\pm$0.034)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2382 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2386 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .424,  .424}0.3437 ($\pm$0.028) \\
+			\textbf{bike}                       & \cellcolor[rgb]{ .388,  .745,  .482}0.0458 ($\pm$0.002)                   & \cellcolor[rgb]{ .592,  .804,  .494}0.0682 ($\pm$0.068) & \cellcolor[rgb]{ 1,  .922,  .518}0.1123 ($\pm$0.103)    & \cellcolor[rgb]{ .467,  .765,  .486}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .882,  .886,  .51}0.0995 ($\pm$0.002)  & \cellcolor[rgb]{ .565,  .796,  .49}0.0651 ($\pm$0.02)   & \cellcolor[rgb]{ .588,  .8,  .49}0.0679 ($\pm$0.002)    & \cellcolor[rgb]{ 1,  .902,  .514}0.1179 ($\pm$0.006)    & \cellcolor[rgb]{ .992,  .761,  .486}0.1531 ($\pm$0.005) & \cellcolor[rgb]{ .992,  .773,  .49}0.1503 ($\pm$0.025)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1599 ($\pm$0.003) & \cellcolor[rgb]{ .992,  .725,  .482}0.1614 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.2399 ($\pm$0.04)   \\
+			\textbf{car}                        & \cellcolor[rgb]{ .729,  .843,  .502}0.2027 ($\pm$0.018)                   & \cellcolor[rgb]{ .388,  .745,  .482}0.0972 ($\pm$0.024) & \cellcolor[rgb]{ .408,  .749,  .482}0.1039 ($\pm$0.031) & \cellcolor[rgb]{ .62,  .812,  .494}0.169 ($\pm$0.025)   & \cellcolor[rgb]{ .867,  .882,  .51}0.2454 ($\pm$0.029)  & \cellcolor[rgb]{ .58,  .8,  .49}0.1572 ($\pm$0.034)     & \cellcolor[rgb]{ 1,  .922,  .518}0.2859 ($\pm$0.027)    & \cellcolor[rgb]{ .992,  .733,  .482}0.4891 ($\pm$0.077) & \cellcolor[rgb]{ .98,  .502,  .439}0.7374 ($\pm$0.063)  & \cellcolor[rgb]{ .988,  .667,  .471}0.5632 ($\pm$0.158) & \cellcolor[rgb]{ .98,  .533,  .443}0.7035 ($\pm$0.052)  & \cellcolor[rgb]{ .98,  .506,  .439}0.7322 ($\pm$0.043)  & \cellcolor[rgb]{ .973,  .412,  .42}0.8332 ($\pm$0.074)  \\
+			\textbf{diabetic}                   & \cellcolor[rgb]{ .694,  .831,  .498}0.8895 ($\pm$0.004)                   & \cellcolor[rgb]{ 1,  .898,  .514}0.9193 ($\pm$0.01)     & \cellcolor[rgb]{ .918,  .894,  .51}0.8957 ($\pm$0.004)  & \cellcolor[rgb]{ .98,  .914,  .514}0.8976 ($\pm$0.011)  & \cellcolor[rgb]{ .388,  .745,  .482}0.8809 ($\pm$0.004) & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)   & \cellcolor[rgb]{ .49,  .773,  .486}0.8839 ($\pm$0.005)  & \cellcolor[rgb]{ 1,  .902,  .518}0.9137 ($\pm$0.008)    & \cellcolor[rgb]{ .996,  .843,  .506}0.9613 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .835,  .502}0.9661 ($\pm$0.016) & \cellcolor[rgb]{ .976,  .914,  .514}0.8974 ($\pm$0.004) & \cellcolor[rgb]{ 1,  .922,  .518}0.898 ($\pm$0.003)     & \cellcolor[rgb]{ .988,  .694,  .475}1.0774 ($\pm$0.039) \\
+			\textbf{fish\_toxicity}             & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                      & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
+			\textbf{forest\_fires}              & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                       & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\
+			\textbf{housing}                    & \cellcolor[rgb]{ .518,  .78,  .486}0.0889 ($\pm$0.012)                    & \cellcolor[rgb]{ .404,  .749,  .482}0.0848 ($\pm$0.011) & \cellcolor[rgb]{ .388,  .745,  .482}0.0842 ($\pm$0.015) & \cellcolor[rgb]{ .69,  .831,  .498}0.0951 ($\pm$0.015)  & \cellcolor[rgb]{ .612,  .808,  .494}0.0923 ($\pm$0.016) & \cellcolor[rgb]{ .663,  .824,  .498}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.106 ($\pm$0.019)     & \cellcolor[rgb]{ 1,  .867,  .51}0.1169 ($\pm$0.019)     & \cellcolor[rgb]{ .996,  .812,  .498}0.1279 ($\pm$0.02)  & \cellcolor[rgb]{ .992,  .722,  .482}0.1452 ($\pm$0.03)  & \cellcolor[rgb]{ .984,  .576,  .455}0.1735 ($\pm$0.023) & \cellcolor[rgb]{ .984,  .588,  .455}0.1713 ($\pm$0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.2057 ($\pm$0.036)  \\
+			\textbf{iris}                       & \cellcolor[rgb]{ .788,  .859,  .502}0.2161 ($\pm$0.059)                   & \cellcolor[rgb]{ .514,  .78,  .486}0.1203 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0753 ($\pm$0.046) & \cellcolor[rgb]{ 1,  .855,  .506}0.3729 ($\pm$1.119)    & \cellcolor[rgb]{ .416,  .753,  .482}0.085 ($\pm$0.042)  & \cellcolor[rgb]{ .859,  .878,  .506}0.2411 ($\pm$0.295) & \cellcolor[rgb]{ .996,  .808,  .498}0.426 ($\pm$0.072)  & \cellcolor[rgb]{ .686,  .831,  .498}0.1809 ($\pm$0.164) & \cellcolor[rgb]{ 1,  .922,  .518}0.2895 ($\pm$0.117)    & \cellcolor[rgb]{ .973,  .412,  .42}0.8965 ($\pm$0.844)  & \cellcolor[rgb]{ .992,  .773,  .49}0.4694 ($\pm$0.088)  & \cellcolor[rgb]{ .992,  .745,  .486}0.5028 ($\pm$0.072) & \cellcolor[rgb]{ .98,  .494,  .435}0.8027 ($\pm$0.684)  \\
+			\textbf{mushroom}                   & \cellcolor[rgb]{ .549,  .792,  .49}0.0026 ($\pm$0.001)                    & \cellcolor[rgb]{ .467,  .765,  .486}0.0013 ($\pm$0.005) & \cellcolor[rgb]{ .388,  .745,  .482}0.0001 ($\pm$0)     & \cellcolor[rgb]{ .439,  .757,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ 1,  .922,  .518}0.0094 ($\pm$0.002)    & \cellcolor[rgb]{ .718,  .839,  .498}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ .655,  .82,  .494}0.0042 ($\pm$0.001)  & \cellcolor[rgb]{ 1,  .871,  .51}0.0774 ($\pm$0.02)      & \cellcolor[rgb]{ .984,  .561,  .451}0.4892 ($\pm$0.025) & \cellcolor[rgb]{ 1,  .886,  .514}0.0611 ($\pm$0.06)     & \cellcolor[rgb]{ .996,  .796,  .494}0.1797 ($\pm$0.009) & \cellcolor[rgb]{ .992,  .749,  .486}0.2418 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.687 ($\pm$0.016)   \\
+			\textbf{parkinsons}                 & \cellcolor[rgb]{ .51,  .776,  .486}0.0563 ($\pm$0.001)                    & \cellcolor[rgb]{ .412,  .749,  .482}0.0545 ($\pm$0.002) & \cellcolor[rgb]{ .388,  .745,  .482}0.054 ($\pm$0.002)  & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0655 ($\pm$0.002)    & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .69,  .831,  .498}0.0597 ($\pm$0.002)  & \cellcolor[rgb]{ 1,  .918,  .518}0.0658 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .898,  .514}0.0669 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .894,  .514}0.0671 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .467,  .431}0.0923 ($\pm$0.008) & \cellcolor[rgb]{ .973,  .412,  .42}0.0954 ($\pm$0.009)  & \cellcolor[rgb]{ .984,  .604,  .459}0.0843 ($\pm$0.009) \\
+			\textbf{student\_performance}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1656 ($\pm$0.011)                   & \cellcolor[rgb]{ .98,  .522,  .443}0.4929 ($\pm$0.105)  & \cellcolor[rgb]{ .973,  .412,  .42}0.5724 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .855,  .506}0.2454 ($\pm$0.134)    & \cellcolor[rgb]{ .471,  .769,  .486}0.1697 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .871,  .51}0.2359 ($\pm$0.102)     & \cellcolor[rgb]{ .49,  .773,  .486}0.1708 ($\pm$0.01)   & \cellcolor[rgb]{ .969,  .91,  .514}0.1947 ($\pm$0.014)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1962 ($\pm$0.01)     & \cellcolor[rgb]{ .984,  .573,  .451}0.4565 ($\pm$0.049) & \cellcolor[rgb]{ .933,  .902,  .514}0.193 ($\pm$0.011)  & \cellcolor[rgb]{ .925,  .898,  .51}0.1925 ($\pm$0.011)  & \cellcolor[rgb]{ 1,  .918,  .518}0.2014 ($\pm$0.012)    \\
+			\textbf{wine\_quality}              & \cellcolor[rgb]{ .631,  .816,  .494}1.0651 ($\pm$0.024)                   & \cellcolor[rgb]{ .388,  .745,  .482}1.0395 ($\pm$0.018) & \cellcolor[rgb]{ .502,  .776,  .486}1.0514 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .698,  .831,  .498}1.0718 ($\pm$0.025) & \cellcolor[rgb]{ .804,  .863,  .506}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .788,  .859,  .502}1.0809 ($\pm$0.021) & \cellcolor[rgb]{ .996,  .839,  .502}1.1666 ($\pm$0.03)  & \cellcolor[rgb]{ .992,  .725,  .482}1.2516 ($\pm$0.046) & \cellcolor[rgb]{ .988,  .659,  .467}1.3046 ($\pm$0.114) & \cellcolor[rgb]{ .996,  .843,  .502}1.1648 ($\pm$0.023) & \cellcolor[rgb]{ .996,  .824,  .502}1.1774 ($\pm$0.019) & \cellcolor[rgb]{ .973,  .412,  .42}1.4896 ($\pm$0.093)  \\
+			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
+
 	}
-\end{table}%
+\end{sidewaystable}%
 
@@
 
-\begin{figure}[H]
+\begin{figure}[htbp]
 	\centering
@@
 
-\begin{figure}[H]
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{table}[H]
+\begin{table}[htbp]
 	\centering
@@
 
-\begin{table}[H]
+\begin{table}[htbp]
 	\centering
 	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}
-	\label{tab:results:population:metrics}%
+	\label{tab:results:population:metrics:rank}%
 	\par\bigskip
 	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}      &                                                                                    &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			\cmidrule{1-2}                      &                                         &                                                                                    &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{population}} & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                 &                                                                           &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{5}}          &                                                                                    &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{15}} &                 &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{25}} &                                                                           &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                          & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4387}          & 1.3396          & 930                             & 2.7452                                                                    & 1.3922          & 930                             & 3.0129          & 1.3865          & 930                             & 3.4065                                                                    & 1.3513          & 930                             & 3.3968                                                                    & 1.3514          \\
-			adult                               & 930                                     & 3.5720                                                                             & 1.4693          & 930                             & 3.2828                                                                    & 1.3751          & 930                             & 2.8108          & 1.3625          & 930                             & 2.6484                                                                    & 1.3222          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3634} & 1.3063          \\
-			air quality                         & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7527}          & 1.4283          & 930                             & 2.9258                                                                    & 1.3904          & 930                             & 2.9656          & 1.3791          & 930                             & 3.3140                                                                    & 1.3789          & 930                             & 3.0419                                                                    & 1.4374          \\
-			bank                                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8129}          & 1.4102          & 930                             & 3.1591                                                                    & 1.4348          & 930                             & 2.9989          & 1.4199          & 930                             & 3.0505                                                                    & 1.4438          & 930                             & 2.9785                                                                    & 1.3414          \\
-			bike                                & 930                                     & 3.8957                                                                             & 1.3355          & 930                             & 2.8688                                                                    & 1.2850          & 930                             & 2.9645          & 1.3447          & 930                             & 2.7430                                                                    & 1.3762          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5280} & 1.3278          \\
-			car                                 & 930                                     & 3.1892                                                                             & 1.3915          & 930                             & 3.0409                                                                    & 1.3945          & 930                             & 3.0398          & 1.4523          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8559} & 1.3938          & 930                             & 2.8742                                                                    & 1.4151          \\
-			diabetic                            & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7978}          & 1.5078          & 930                             & 2.9387                                                                    & 1.4133          & 930                             & 3.2129          & 1.4525          & 930                             & 2.9613                                                                    & 1.3036          & 930                             & 3.0892                                                                    & 1.3534          \\
-			fish toxicity                       & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8151}          & 1.4249          & 930                             & 3.0409                                                                    & 1.4288          & 930                             & 3.0925          & 1.3230          & 930                             & 3.1280                                                                    & 1.4073          & 930                             & 2.9237                                                                    & 1.4634          \\
-			forest fires                        & 930                                     & 3.0172                                                                             & 1.4026          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.9215} & 1.3800          & 930                             & 2.9806          & 1.3833          & 930                             & 3.0968                                                                    & 1.4124          & 930                             & 2.9839                                                                    & 1.4879          \\
-			housing                             & 930                                     & 2.8366                                                                             & 1.4040          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8258} & 1.3802          & 930                             & 2.9753          & 1.4393          & 930                             & 2.9849                                                                    & 1.4111          & 930                             & 3.3774                                                                    & 1.3680          \\
-			iris                                & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301}          & 1.3038          & 930                             & 2.8731                                                                    & 1.3970          & 930                             & 3.0505          & 1.4129          & 930                             & 3.1860                                                                    & 1.4251          & 930                             & 3.0602                                                                    & 1.4987          \\
-			mushroom                            & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7989}          & 1.2052          & 930                             & 2.9441                                                                    & 1.3250          & 930                             & 3.0462          & 1.4521          & 930                             & 3.1366                                                                    & 1.4940          & 930                             & 3.0538                                                                    & 1.5664          \\
-			parkinsons                          & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6645}          & 1.4411          & 930                             & 3.1065                                                                    & 1.3272          & 930                             & 3.0247          & 1.4265          & 930                             & 3.0495                                                                    & 1.4420          & 930                             & 3.1548                                                                    & 1.3810          \\
-			student performance                 & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6376}          & 1.4357          & 930                             & 2.8645                                                                    & 1.4108          & 930                             & 3.1548          & 1.4042          & 930                             & 3.2387                                                                    & 1.3970          & 930                             & 3.1043                                                                    & 1.3395          \\
-			wine quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5505}          & 1.3165          & 930                             & 2.7817                                                                    & 1.4152          & 930                             & 3.1581          & 1.3841          & 930                             & 3.1806                                                                    & 1.3941          & 930                             & 3.3290                                                                    & 1.4140          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                          & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9073}} & \textbf{1.4377} & \textbf{13950}                  & \textbf{2.9546}                                                           & \textbf{1.3904} & \textbf{13950}                  & \textbf{3.0325} & \textbf{1.4045} & \textbf{13950}                  & \textbf{3.0654}                                                           & \textbf{1.4108} & \textbf{13950}                  & \textbf{3.0173}                                                           & \textbf{1.4306} \\
+		\begin{tabular}{r|ccccc}
+			                              & \multicolumn{5}{c}{\textbf{Population - Average Rank}}                                                                                                                                                                                                                                          \\
+			\midrule
+			\textbf{dataset}              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             & \textbf{25}                                             \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .388,  .745,  .482}2.4387 ($\pm$1.34)  & \cellcolor[rgb]{ .714,  .839,  .498}2.7452 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}3.0129 ($\pm$1.386)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4065 ($\pm$1.351)  & \cellcolor[rgb]{ .976,  .427,  .424}3.3968 ($\pm$1.351) \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.7527 ($\pm$1.428) & \cellcolor[rgb]{ .882,  .886,  .51}2.9258 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9656 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.379)   & \cellcolor[rgb]{ .996,  .812,  .498}3.0419 ($\pm$1.437) \\
+			\textbf{bank}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.8129 ($\pm$1.41)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1591 ($\pm$1.435)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9989 ($\pm$1.42)     & \cellcolor[rgb]{ .992,  .761,  .486}3.0505 ($\pm$1.444) & \cellcolor[rgb]{ .929,  .902,  .514}2.9785 ($\pm$1.341) \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .973,  .412,  .42}3.8957 ($\pm$1.335)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8688 ($\pm$1.285)    & \cellcolor[rgb]{ 1,  .875,  .51}2.9645 ($\pm$1.345)     & \cellcolor[rgb]{ .773,  .855,  .502}2.743 ($\pm$1.376)  & \cellcolor[rgb]{ .388,  .745,  .482}2.528 ($\pm$1.328)  \\
+			\textbf{car}                  & \cellcolor[rgb]{ .973,  .412,  .42}3.1892 ($\pm$1.391)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.394)    & \cellcolor[rgb]{ 1,  .922,  .518}3.0398 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8559 ($\pm$1.394) & \cellcolor[rgb]{ .447,  .761,  .482}2.8742 ($\pm$1.415) \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .388,  .745,  .482}2.7978 ($\pm$1.508) & \cellcolor[rgb]{ .914,  .894,  .51}2.9387 ($\pm$1.413)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2129 ($\pm$1.452)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9613 ($\pm$1.304)    & \cellcolor[rgb]{ .988,  .663,  .471}3.0892 ($\pm$1.353) \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.8151 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.429)    & \cellcolor[rgb]{ .984,  .62,  .463}3.0925 ($\pm$1.323)  & \cellcolor[rgb]{ .973,  .412,  .42}3.128 ($\pm$1.407)   & \cellcolor[rgb]{ .682,  .827,  .498}2.9237 ($\pm$1.463) \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ .992,  .773,  .49}3.0172 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9215 ($\pm$1.38)  & \cellcolor[rgb]{ .965,  .91,  .514}2.9806 ($\pm$1.383)  & \cellcolor[rgb]{ .973,  .412,  .42}3.0968 ($\pm$1.412)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.488)    \\
+			\textbf{housing}              & \cellcolor[rgb]{ .431,  .757,  .482}2.8366 ($\pm$1.404) & \cellcolor[rgb]{ .388,  .745,  .482}2.8258 ($\pm$1.38)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9753 ($\pm$1.439)    & \cellcolor[rgb]{ 1,  .91,  .518}2.9849 ($\pm$1.411)     & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.368)  \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.8301 ($\pm$1.304) & \cellcolor[rgb]{ .506,  .776,  .486}2.8731 ($\pm$1.397) & \cellcolor[rgb]{ 1,  .922,  .518}3.0505 ($\pm$1.413)    & \cellcolor[rgb]{ .973,  .412,  .42}3.186 ($\pm$1.425)   & \cellcolor[rgb]{ 1,  .886,  .514}3.0602 ($\pm$1.499)    \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ .388,  .745,  .482}2.7989 ($\pm$1.205) & \cellcolor[rgb]{ .745,  .847,  .502}2.9441 ($\pm$1.325) & \cellcolor[rgb]{ 1,  .922,  .518}3.0462 ($\pm$1.452)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1366 ($\pm$1.494)  & \cellcolor[rgb]{ 1,  .882,  .51}3.0538 ($\pm$1.566)     \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .388,  .745,  .482}2.6645 ($\pm$1.441) & \cellcolor[rgb]{ .988,  .647,  .467}3.1065 ($\pm$1.327) & \cellcolor[rgb]{ .957,  .91,  .514}3.0247 ($\pm$1.427)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0495 ($\pm$1.442)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1548 ($\pm$1.381)  \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6376 ($\pm$1.436) & \cellcolor[rgb]{ .682,  .827,  .498}2.8645 ($\pm$1.411) & \cellcolor[rgb]{ .992,  .733,  .482}3.1548 ($\pm$1.404) & \cellcolor[rgb]{ .973,  .412,  .42}3.2387 ($\pm$1.397)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1043 ($\pm$1.34)     \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.5505 ($\pm$1.317) & \cellcolor[rgb]{ .62,  .812,  .494}2.7817 ($\pm$1.415)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1581 ($\pm$1.384)    & \cellcolor[rgb]{ 1,  .855,  .506}3.1806 ($\pm$1.394)    & \cellcolor[rgb]{ .973,  .412,  .42}3.329 ($\pm$1.414)   \\
+			\midrule
+			\textbf{avg rank}             & \cellcolor[rgb]{ .388,  .745,  .482}2.8598 ($\pm$1.424) & \cellcolor[rgb]{ .62,  .812,  .494}2.9312 ($\pm$1.389)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0484 ($\pm$1.406)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0952 ($\pm$1.412)  & \cellcolor[rgb]{ .992,  .753,  .486}3.064 ($\pm$1.428)  \\
+			\midrule
+			\textbf{normalised avg rank}  & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ .988,  .667,  .471}4                   \\
 		\end{tabular}%
+
 	}
@@
 
+\begin{table}[htbp]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}
+	\label{tab:results:population:metrics:loss}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccccc}
+			                              & \multicolumn{5}{c}{\textbf{Population - Average Loss}}                                                                                                                                                                                                                                         \\
+			\midrule
+			\textbf{dataset}              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                            & \textbf{25}                                             \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088) & \cellcolor[rgb]{ .612,  .808,  .494}2.1592 ($\pm$0.278) & \cellcolor[rgb]{ 1,  .922,  .518}2.3321 ($\pm$0.446)    & \cellcolor[rgb]{ 1,  .91,  .518}2.3345 ($\pm$0.357)    & \cellcolor[rgb]{ .973,  .412,  .42}2.4188 ($\pm$0.473)  \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 ($\pm$0.016)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2701 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .878,  .51}0.2736 ($\pm$0.014)     & \cellcolor[rgb]{ .973,  .412,  .42}0.2808 ($\pm$0.026) & \cellcolor[rgb]{ .702,  .835,  .498}0.2715 ($\pm$0.011) \\
+			\textbf{bank}                 & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)  & \cellcolor[rgb]{ .992,  .729,  .482}0.2356 ($\pm$0.029) & \cellcolor[rgb]{ .388,  .745,  .482}0.2268 ($\pm$0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.2294 ($\pm$0.019)   & \cellcolor[rgb]{ .608,  .808,  .494}0.2278 ($\pm$0.012) \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .973,  .412,  .42}0.0651 ($\pm$0.02)   & \cellcolor[rgb]{ .388,  .745,  .482}0.0527 ($\pm$0.002) & \cellcolor[rgb]{ .988,  .918,  .514}0.0535 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .898,  .514}0.0541 ($\pm$0.003)   & \cellcolor[rgb]{ 1,  .922,  .518}0.0535 ($\pm$0.003)    \\
+			\textbf{car}                  & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034) & \cellcolor[rgb]{ .757,  .851,  .502}0.1595 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}0.161 ($\pm$0.039)     & \cellcolor[rgb]{ .992,  .773,  .49}0.1636 ($\pm$0.04)  & \cellcolor[rgb]{ .973,  .412,  .42}0.17 ($\pm$0.048)    \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)   & \cellcolor[rgb]{ 1,  .922,  .518}0.9954 ($\pm$0.103)    & \cellcolor[rgb]{ .992,  .776,  .49}1.0826 ($\pm$0.3)    & \cellcolor[rgb]{ .525,  .784,  .49}0.9893 ($\pm$0.105) & \cellcolor[rgb]{ .388,  .745,  .482}0.9875 ($\pm$0.078) \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1046 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1077 ($\pm$0.009)    & \cellcolor[rgb]{ .882,  .886,  .51}0.1071 ($\pm$0.011)  & \cellcolor[rgb]{ .973,  .412,  .42}0.1104 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .886,  .514}0.1079 ($\pm$0.008)    \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ 1,  .922,  .518}0.081 ($\pm$0.069)     & \cellcolor[rgb]{ .388,  .745,  .482}0.0694 ($\pm$0.059) & \cellcolor[rgb]{ .737,  .843,  .502}0.0761 ($\pm$0.056) & \cellcolor[rgb]{ .984,  .569,  .451}0.084 ($\pm$0.07)  & \cellcolor[rgb]{ .973,  .412,  .42}0.0854 ($\pm$0.065)  \\
+			\textbf{housing}              & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.0985 ($\pm$0.026)    & \cellcolor[rgb]{ .412,  .749,  .482}0.0943 ($\pm$0.016) & \cellcolor[rgb]{ 1,  .906,  .518}0.0987 ($\pm$0.017)   & \cellcolor[rgb]{ .973,  .412,  .42}0.1038 ($\pm$0.017)  \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.2411 ($\pm$0.295) & \cellcolor[rgb]{ .992,  .741,  .486}0.4212 ($\pm$0.671) & \cellcolor[rgb]{ .973,  .412,  .42}0.5905 ($\pm$1.043)  & \cellcolor[rgb]{ .651,  .82,  .494}0.2784 ($\pm$0.261) & \cellcolor[rgb]{ 1,  .922,  .518}0.327 ($\pm$0.381)     \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}1.9037 ($\pm$10.345) & \cellcolor[rgb]{ 1,  .898,  .514}0.3366 ($\pm$1.559)    & \cellcolor[rgb]{ .69,  .831,  .498}0.1311 ($\pm$0.486) & \cellcolor[rgb]{ 1,  .922,  .518}0.2602 ($\pm$1.115)    \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .82,  .867,  .506}0.0598 ($\pm$0.003)  & \cellcolor[rgb]{ .988,  .694,  .475}0.0606 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0602 ($\pm$0.003)   & \cellcolor[rgb]{ .973,  .412,  .42}0.0612 ($\pm$0.003)  \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .973,  .412,  .42}0.2359 ($\pm$0.102)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2007 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .922,  .518}0.2092 ($\pm$0.039)    & \cellcolor[rgb]{ .573,  .796,  .49}0.2033 ($\pm$0.037) & \cellcolor[rgb]{ 1,  .922,  .518}0.2091 ($\pm$0.054)    \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .553,  .792,  .49}1.0864 ($\pm$0.034)  & \cellcolor[rgb]{ .973,  .412,  .42}1.1083 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .922,  .518}1.0961 ($\pm$0.027)   & \cellcolor[rgb]{ .976,  .463,  .431}1.1071 ($\pm$0.039) \\
+		\end{tabular}%
+
+	}
+\end{table}%
+
 Table \ref{tab:results:population:metrics} show that that a smaller population size mostly produces the best results, with statistically significant differences on the adult, bike and car datasets.
@@
 
-\begin{table}[H]
+\begin{table}[htbp]
 	\centering
 	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:credit:metrics}%
+	\label{tab:results:credit:metrics:rank}%
 	\par\bigskip
 	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}  &                                                                           &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
-			\cmidrule{1-2}                      &                                     &                                                                           &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{credit}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                    &                                                                                    &                 &                                    &                                                                           &                 &                                    &                                                                           &                 &                                        &                                                                           &                 \\
-			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{ibest}}  &                                                                           &                 & \multicolumn{1}{l}{\textbf{pbest}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{rbest}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{gbest}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{symmetric}} &                                                                           &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                      & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                     & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                         & \textbf{avg}                                                              & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                 & 3.1677                                                                    & 1.3188          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613}          & 1.4588          & 930                                & 2.9968                                                                    & 1.3993          & 930                                & 2.9667                                                                    & 1.4547          & 930                                    & 3.0075                                                                    & 1.4214          \\
-			adult                               & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                & 2.6763                                                                             & 1.5019          & 930                                & 2.8065                                                                    & 1.5003          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4355} & 1.1177          & 930                                    & 3.3538                                                                    & 1.5682          \\
-			air quality                         & 930                                 & 3.1312                                                                    & 1.3472          & 930                                & 3.0376                                                                             & 1.3566          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5914} & 1.4646          & 930                                & 3.1280                                                                    & 1.3358          & 930                                    & 3.1118                                                                    & 1.4871          \\
-			bank                                & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8591} & 1.3442          & 930                                & 2.9903                                                                             & 1.4320          & 930                                & 2.8882                                                                    & 1.4098          & 930                                & 3.0441                                                                    & 1.4154          & 930                                    & 3.2183                                                                    & 1.4424          \\
-			bike                                & 930                                 & 3.0527                                                                    & 1.3401          & 930                                & 3.0086                                                                             & 1.3935          & 930                                & 3.0667                                                                    & 1.4825          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3393          & 930                                    & 2.9978                                                                    & 1.5028          \\
-			car                                 & 930                                 & 3.1151                                                                    & 1.3562          & 930                                & 3.0312                                                                             & 1.4826          & 930                                & 3.2516                                                                    & 1.4024          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6892} & 1.3540          & 930                                    & 2.9129                                                                    & 1.4111          \\
-			diabetic                            & 930                                 & 2.8914                                                                    & 1.3488          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6269}          & 1.4171          & 930                                & 3.4151                                                                    & 1.3653          & 930                                & 2.8925                                                                    & 1.3620          & 930                                    & 3.1742                                                                    & 1.4487          \\
-			fish toxicity                       & 930                                 & 3.1516                                                                    & 1.4360          & 930                                & 2.9903                                                                             & 1.4521          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.4748          & 930                                & 3.2043                                                                    & 1.2988          & 930                                    & 2.8957                                                                    & 1.3579          \\
-			forest fires                        & 930                                 & 3.0968                                                                    & 1.2771          & 930                                & 3.1806                                                                             & 1.3040          & 930                                & 2.8559                                                                    & 1.3562          & 930                                & 3.1215                                                                    & 1.5018          & 930                                    & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7452} & 1.5627          \\
-			housing                             & 930                                 & 2.9011                                                                    & 1.4938          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8527}          & 1.3168          & 930                                & 2.9022                                                                    & 1.3974          & 930                                & 3.3108                                                                    & 1.3243          & 930                                    & 3.0333                                                                    & 1.4833          \\
-			iris                                & 930                                 & 3.1892                                                                    & 1.4281          & 930                                & 3.0839                                                                             & 1.4412          & 930                                & 3.0591                                                                    & 1.3755          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8237} & 1.4085          & 930                                    & 2.8441                                                                    & 1.3844          \\
-			mushroom                            & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8075} & 1.4594          & 930                                & 3.0183                                                                             & 1.4107          & 930                                & 2.8957                                                                    & 1.3985          & 930                                & 3.0839                                                                    & 1.4178          & 930                                    & 3.1720                                                                    & 1.3813          \\
-			parkinsons                          & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5645} & 1.4835          & 930                                & 2.8925                                                                             & 1.3429          & 930                                & 3.5065                                                                    & 1.2190          & 930                                & 3.0796                                                                    & 1.3920          & 930                                    & 2.9570                                                                    & 1.4548          \\
-			student performance                 & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6624} & 1.3124          & 930                                & 3.0290                                                                             & 1.4067          & 930                                & 3.1892                                                                    & 1.3821          & 930                                & 2.7978                                                                    & 1.4702          & 930                                    & 3.3215                                                                    & 1.3938          \\
-			wine quality                        & 930                                 & 3.1871                                                                    & 1.3080          & 930                                & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366}          & 1.4706          & 930                                & 3.0140                                                                    & 1.3712          & 930                                & 2.9419                                                                    & 1.4115          & 930                                    & 3.2204                                                                    & 1.4300          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                      & \textbf{2.9475}                                                           & \textbf{1.3805} & \textbf{13950}                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9277}} & \textbf{1.4222} & \textbf{13950}                     & \textbf{3.0131}                                                           & \textbf{1.4209} & \textbf{13950}                     & \textbf{2.9596}                                                           & \textbf{1.3921} & \textbf{13950}                         & \textbf{3.0644}                                                           & \textbf{1.4594} \\
+		\begin{tabular}{r|ccccc}
+			                              & \multicolumn{5}{c}{\textbf{Credit - Average Rank}}                                                                                                                                                                                                                                              \\
+			\midrule
+			\textbf{dataset}              & \textbf{ibest}                                          & \textbf{pbest}                                          & \textbf{rbest}                                          & \textbf{gbest}                                          & \textbf{symmetric}                                      \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .973,  .412,  .42}3.1677 ($\pm$1.319)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8613 ($\pm$1.459) & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.399)    & \cellcolor[rgb]{ .863,  .882,  .51}2.9667 ($\pm$1.455)  & \cellcolor[rgb]{ 1,  .89,  .514}3.0075 ($\pm$1.421)     \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.1312 ($\pm$1.347)  & \cellcolor[rgb]{ .91,  .894,  .51}3.0376 ($\pm$1.357)   & \cellcolor[rgb]{ .388,  .745,  .482}2.5914 ($\pm$1.465) & \cellcolor[rgb]{ .98,  .498,  .439}3.128 ($\pm$1.336)   & \cellcolor[rgb]{ 1,  .922,  .518}3.1118 ($\pm$1.487)    \\
+			\textbf{bank}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.8591 ($\pm$1.344) & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.432)    & \cellcolor[rgb]{ .522,  .78,  .486}2.8882 ($\pm$1.41)   & \cellcolor[rgb]{ .996,  .804,  .498}3.0441 ($\pm$1.415) & \cellcolor[rgb]{ .973,  .412,  .42}3.2183 ($\pm$1.442)  \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .98,  .537,  .447}3.0527 ($\pm$1.34)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0086 ($\pm$1.393)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0667 ($\pm$1.483)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8742 ($\pm$1.339) & \cellcolor[rgb]{ .949,  .906,  .514}2.9978 ($\pm$1.503) \\
+			\textbf{car}                  & \cellcolor[rgb]{ .992,  .729,  .482}3.1151 ($\pm$1.356) & \cellcolor[rgb]{ 1,  .922,  .518}3.0312 ($\pm$1.483)    & \cellcolor[rgb]{ .973,  .412,  .42}3.2516 ($\pm$1.402)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6892 ($\pm$1.354) & \cellcolor[rgb]{ .788,  .859,  .502}2.9129 ($\pm$1.411) \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .996,  .918,  .514}2.8914 ($\pm$1.349) & \cellcolor[rgb]{ .388,  .745,  .482}2.6269 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.4151 ($\pm$1.365)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8925 ($\pm$1.362)    & \cellcolor[rgb]{ .988,  .647,  .467}3.1742 ($\pm$1.449) \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .98,  .541,  .447}3.1516 ($\pm$1.436)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.475) & \cellcolor[rgb]{ .973,  .412,  .42}3.2043 ($\pm$1.299)  & \cellcolor[rgb]{ .749,  .847,  .502}2.8957 ($\pm$1.358) \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.277)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1806 ($\pm$1.304)  & \cellcolor[rgb]{ .58,  .8,  .49}2.8559 ($\pm$1.356)     & \cellcolor[rgb]{ .992,  .773,  .49}3.1215 ($\pm$1.502)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7452 ($\pm$1.563) \\
+			\textbf{housing}              & \cellcolor[rgb]{ .984,  .918,  .514}2.9011 ($\pm$1.494) & \cellcolor[rgb]{ .388,  .745,  .482}2.8527 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}2.9022 ($\pm$1.397)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3108 ($\pm$1.324)  & \cellcolor[rgb]{ .992,  .761,  .486}3.0333 ($\pm$1.483) \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .973,  .412,  .42}3.1892 ($\pm$1.428)  & \cellcolor[rgb]{ .996,  .827,  .502}3.0839 ($\pm$1.441) & \cellcolor[rgb]{ 1,  .922,  .518}3.0591 ($\pm$1.376)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8237 ($\pm$1.409) & \cellcolor[rgb]{ .439,  .757,  .482}2.8441 ($\pm$1.384) \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ .388,  .745,  .482}2.8075 ($\pm$1.459) & \cellcolor[rgb]{ 1,  .922,  .518}3.0183 ($\pm$1.411)    & \cellcolor[rgb]{ .643,  .816,  .494}2.8957 ($\pm$1.398) & \cellcolor[rgb]{ .992,  .706,  .478}3.0839 ($\pm$1.418) & \cellcolor[rgb]{ .973,  .412,  .42}3.172 ($\pm$1.381)   \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .388,  .745,  .482}2.5645 ($\pm$1.484) & \cellcolor[rgb]{ .898,  .89,  .51}2.8925 ($\pm$1.343)   & \cellcolor[rgb]{ .973,  .412,  .42}3.5065 ($\pm$1.219)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0796 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}2.957 ($\pm$1.455)     \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6624 ($\pm$1.312) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.407)     & \cellcolor[rgb]{ .988,  .643,  .467}3.1892 ($\pm$1.382) & \cellcolor[rgb]{ .612,  .808,  .494}2.7978 ($\pm$1.47)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3215 ($\pm$1.394)  \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ .98,  .494,  .439}3.1871 ($\pm$1.308)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .922,  .518}3.014 ($\pm$1.371)     & \cellcolor[rgb]{ .882,  .886,  .51}2.9419 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.43)   \\
+			\midrule
+			\textbf{avg rank}             & \cellcolor[rgb]{ .843,  .875,  .506}2.9841 ($\pm$1.39)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9457 ($\pm$1.415) & \cellcolor[rgb]{ .984,  .588,  .455}3.0279 ($\pm$1.414) & \cellcolor[rgb]{ 1,  .922,  .518}2.997 ($\pm$1.402)     & \cellcolor[rgb]{ .973,  .412,  .42}3.0437 ($\pm$1.449)  \\
+			\midrule
+			\textbf{normalised avg rank}  & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
 		\end{tabular}%
+
+	}
+\end{table}%
+
+\begin{table}[htbp]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\label{tab:results:credit:metrics:loss}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccccc}
+			                              & \multicolumn{5}{c}{\textbf{Credit - Average Loss}}                                                                                                                                                                                                                               \\
+			\midrule
+			\textbf{dataset}              & \textbf{ibest}                                       & \textbf{pbest}                                       & \textbf{rbest}                                       & \textbf{gbest}                                       & \textbf{symmetric}                                   \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .631,  .816,  .494}2.0587 (+-0.088) & \cellcolor[rgb]{ .388,  .745,  .482}2.0422 (+-0.094) & \cellcolor[rgb]{ .996,  .792,  .494}2.0922 (+-0.152) & \cellcolor[rgb]{ 1,  .922,  .518}2.0833 (+-0.136)    & \cellcolor[rgb]{ .973,  .412,  .42}2.1177 (+-0.259)  \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 (+-0.016)  & \cellcolor[rgb]{ .902,  .89,  .51}0.2678 (+-0.015)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2644 (+-0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.2684 (+-0.013)    & \cellcolor[rgb]{ 1,  .882,  .51}0.2688 (+-0.017)     \\
+			\textbf{bank}                 & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 (+-0.065)    & \cellcolor[rgb]{ .973,  .412,  .42}0.2645 (+-0.171)  & \cellcolor[rgb]{ .51,  .78,  .486}0.238 (+-0.047)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2361 (+-0.031) & \cellcolor[rgb]{ .996,  .812,  .498}0.2498 (+-0.047) \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .988,  .647,  .467}0.0651 (+-0.02)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0634 (+-0.023)    & \cellcolor[rgb]{ .871,  .882,  .51}0.0633 (+-0.02)   & \cellcolor[rgb]{ .388,  .745,  .482}0.063 (+-0.021)  & \cellcolor[rgb]{ .973,  .412,  .42}0.0666 (+-0.021)  \\
+			\textbf{car}                  & \cellcolor[rgb]{ 1,  .91,  .518}0.1572 (+-0.034)     & \cellcolor[rgb]{ 1,  .922,  .518}0.1569 (+-0.029)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1665 (+-0.03)   & \cellcolor[rgb]{ .388,  .745,  .482}0.1504 (+-0.03)  & \cellcolor[rgb]{ .945,  .906,  .514}0.1564 (+-0.037) \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .878,  .886,  .51}1.2983 (+-0.66)   & \cellcolor[rgb]{ .988,  .651,  .467}1.4981 (+-2.41)  & \cellcolor[rgb]{ .973,  .412,  .42}1.6172 (+-1.527)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0347 (+-0.231) & \cellcolor[rgb]{ 1,  .922,  .518}1.3627 (+-1.145)    \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .988,  .647,  .467}0.1046 (+-0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1028 (+-0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1024 (+-0.009) & \cellcolor[rgb]{ .973,  .412,  .42}0.1061 (+-0.009)  & \cellcolor[rgb]{ .643,  .816,  .494}0.1026 (+-0.009) \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ .973,  .914,  .514}0.081 (+-0.069)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0819 (+-0.062)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0591 (+-0.046) & \cellcolor[rgb]{ .973,  .412,  .42}0.0845 (+-0.077)  & \cellcolor[rgb]{ 1,  .867,  .51}0.0822 (+-0.07)      \\
+			\textbf{housing}              & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 (+-0.017) & \cellcolor[rgb]{ .996,  .82,  .498}0.0974 (+-0.021)  & \cellcolor[rgb]{ .835,  .875,  .506}0.0961 (+-0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.0995 (+-0.016)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0969 (+-0.018)    \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 (+-0.295)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1441 (+-0.131) & \cellcolor[rgb]{ 1,  .922,  .518}0.1547 (+-0.111)    & \cellcolor[rgb]{ 1,  .882,  .51}0.1616 (+-0.187)     & \cellcolor[rgb]{ .765,  .851,  .502}0.1507 (+-0.142) \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ .404,  .749,  .482}0.0052 (+-0.012) & \cellcolor[rgb]{ 1,  .922,  .518}0.0289 (+-0.107)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0044 (+-0.011) & \cellcolor[rgb]{ 1,  .91,  .518}0.1835 (+-0.949)     & \cellcolor[rgb]{ .973,  .412,  .42}5.3926 (+-29.503) \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 (+-0.003) & \cellcolor[rgb]{ 1,  .867,  .51}0.0594 (+-0.002)     & \cellcolor[rgb]{ .973,  .412,  .42}0.0602 (+-0.002)  & \cellcolor[rgb]{ .898,  .89,  .51}0.0592 (+-0.002)   & \cellcolor[rgb]{ 1,  .922,  .518}0.0593 (+-0.003)    \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 (+-0.102)    & \cellcolor[rgb]{ .678,  .827,  .498}0.2303 (+-0.095) & \cellcolor[rgb]{ .988,  .69,  .475}0.2551 (+-0.109)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2251 (+-0.088) & \cellcolor[rgb]{ .973,  .412,  .42}0.2777 (+-0.116)  \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ .98,  .525,  .443}1.0827 (+-0.026)  & \cellcolor[rgb]{ 1,  .922,  .518}1.0799 (+-0.031)    & \cellcolor[rgb]{ .925,  .898,  .51}1.0794 (+-0.021)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0757 (+-0.027) & \cellcolor[rgb]{ .973,  .412,  .42}1.0835 (+-0.029)  \\
+		\end{tabular}%
+
 	}
@@
 
-\begin{table}[H]
+\begin{table}[htbp]
 	\centering
 	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:reselection:metrics}%
+	\label{tab:results:reselection:metrics:rank}%
 	\par\bigskip
 	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}       &                                                                           &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
-			\cmidrule{1-2}                      &                                          &                                                                           &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{reselection}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                 &                 &                                 &                 &                 &                                 &                                                                           &                 &                                 &                                                                                    &                 \\
-			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}           &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                 &                 & \multicolumn{1}{l}{\textbf{10}} &                 &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                                    &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                           & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                                       & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                      & 4.3548                                                                    & 0.9760          & 930                            & 2.8473          & 1.2885          & 930                             & 2.7505          & 1.2622          & 930                             & 2.5602                                                                    & 1.2988          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4871}          & 1.3182          \\
-			adult                               & 930                                      & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7097} & 1.2671          & 930                            & 4.4559          & 1.0052          & 930                             & 3.4398          & 1.0453          & 930                             & 2.7656                                                                    & 0.9837          & 930                             & 2.3065                                                                             & 1.0670          \\
-			air quality                         & 930                                      & 3.7355                                                                    & 1.4046          & 930                            & 3.4075          & 1.3790          & 930                             & 2.9688          & 1.2783          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4237} & 1.2281          & 930                             & 2.4645                                                                             & 1.2906          \\
-			bank                                & 930                                      & 4.5677                                                                    & 0.7039          & 930                            & 3.6323          & 1.1271          & 930                             & 2.4237          & 1.1333          & 930                             & 2.2462                                                                    & 1.1139          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1301}          & 1.0957          \\
-			bike                                & 930                                      & 4.7935                                                                    & 0.6124          & 930                            & 3.9204          & 0.6480          & 930                             & 2.5161          & 0.8632          & 930                             & 2.0763                                                                    & 0.9007          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6935}          & 0.8911          \\
-			car                                 & 930                                      & 4.6409                                                                    & 0.7847          & 930                            & 2.9527          & 1.1581          & 930                             & 2.6548          & 1.1748          & 930                             & 2.5312                                                                    & 1.2440          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2204}          & 1.2169          \\
-			diabetic                            & 930                                      & 3.0129                                                                    & 1.0478          & 930                            & 4.4624          & 0.8688          & 930                             & 2.7957          & 1.1753          & 930                             & 2.6065                                                                    & 1.4391          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1226}          & 1.2639          \\
-			fish toxicity                       & 930                                      & 3.7484                                                                    & 1.2377          & 930                            & 3.1376          & 1.3174          & 930                             & 3.0344          & 1.4062          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4656} & 1.3039          & 930                             & 2.6140                                                                             & 1.4318          \\
-			forest fires                        & 930                                      & 3.8194                                                                    & 1.4330          & 930                            & 3.2720          & 1.2477          & 930                             & 2.8656          & 1.3464          & 930                             & 2.8194                                                                    & 1.3048          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2237}          & 1.2186          \\
-			housing                             & 930                                      & 4.1892                                                                    & 1.0993          & 930                            & 3.0172          & 1.2882          & 930                             & 2.5871          & 1.3541          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5312} & 1.2654          & 930                             & 2.6753                                                                             & 1.3399          \\
-			iris                                & 930                                      & 2.9839                                                                    & 1.4244          & 930                            & 2.9710          & 1.3165          & 930                             & 3.3462          & 1.4182          & 930                             & 3.0140                                                                    & 1.4054          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6849}          & 1.4289          \\
-			mushroom                            & 930                                      & 4.2065                                                                    & 1.2356          & 930                            & 2.9688          & 1.2992          & 930                             & 2.5860          & 1.2336          & 930                             & 2.7882                                                                    & 1.3397          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4505}          & 1.2259          \\
-			parkinsons                          & 930                                      & 4.7645                                                                    & 0.7563          & 930                            & 3.1882          & 1.0208          & 930                             & 2.2957          & 1.2089          & 930                             & 2.4968                                                                    & 1.1282          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2548}          & 1.0973          \\
-			student performance                 & 930                                      & 3.9710                                                                    & 1.0942          & 930                            & 4.0226          & 1.1196          & 930                             & 2.4774          & 1.2206          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2495} & 1.2002          & 930                             & 2.2796                                                                             & 1.1324          \\
-			wine quality                        & 930                                      & 4.0688                                                                    & 1.1220          & 930                            & 2.9204          & 1.2934          & 930                             & 2.9559          & 1.3831          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.4032} & 1.3779          & 930                             & 2.6516                                                                             & 1.2796          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                           & \textbf{3.9044}                                                           & \textbf{1.3641} & \textbf{13950}                 & \textbf{3.4118} & \textbf{1.2914} & \textbf{13950}                  & \textbf{2.7799} & \textbf{1.2811} & \textbf{13950}                  & \textbf{2.5318}                                                           & \textbf{1.2660} & \textbf{13950}                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.3506}} & \textbf{1.2541} \\
+		\begin{tabular}{r|ccccc}
+			                              & \multicolumn{5}{c}{\textbf{Reselection - Average Rank}}                                                                                                                                                                                                                                         \\
+			\midrule
+			\textbf{dataset}              & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .973,  .412,  .42}4.3548 ($\pm$0.976)  & \cellcolor[rgb]{ 1,  .894,  .514}2.8473 ($\pm$1.288)    & \cellcolor[rgb]{ 1,  .922,  .518}2.7505 ($\pm$1.262)    & \cellcolor[rgb]{ .557,  .792,  .49}2.5602 ($\pm$1.299)  & \cellcolor[rgb]{ .388,  .745,  .482}2.4871 ($\pm$1.318) \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.7355 ($\pm$1.405)  & \cellcolor[rgb]{ .984,  .631,  .463}3.4075 ($\pm$1.379) & \cellcolor[rgb]{ 1,  .922,  .518}2.9688 ($\pm$1.278)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4237 ($\pm$1.228) & \cellcolor[rgb]{ .431,  .757,  .482}2.4645 ($\pm$1.291) \\
+			\textbf{bank}                 & \cellcolor[rgb]{ .973,  .412,  .42}4.5677 ($\pm$0.704)  & \cellcolor[rgb]{ .988,  .635,  .463}3.6323 ($\pm$1.127) & \cellcolor[rgb]{ 1,  .922,  .518}2.4237 ($\pm$1.133)    & \cellcolor[rgb]{ .627,  .812,  .494}2.2462 ($\pm$1.114) & \cellcolor[rgb]{ .388,  .745,  .482}2.1301 ($\pm$1.096) \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .973,  .412,  .42}4.7935 ($\pm$0.612)  & \cellcolor[rgb]{ .984,  .608,  .459}3.9204 ($\pm$0.648) & \cellcolor[rgb]{ 1,  .922,  .518}2.5161 ($\pm$0.863)    & \cellcolor[rgb]{ .671,  .824,  .498}2.0763 ($\pm$0.901) & \cellcolor[rgb]{ .388,  .745,  .482}1.6935 ($\pm$0.891) \\
+			\textbf{car}                  & \cellcolor[rgb]{ .973,  .412,  .42}4.6409 ($\pm$0.785)  & \cellcolor[rgb]{ .996,  .847,  .506}2.9527 ($\pm$1.158) & \cellcolor[rgb]{ 1,  .922,  .518}2.6548 ($\pm$1.175)    & \cellcolor[rgb]{ .824,  .871,  .506}2.5312 ($\pm$1.244) & \cellcolor[rgb]{ .388,  .745,  .482}2.2204 ($\pm$1.217) \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ 1,  .859,  .506}3.0129 ($\pm$1.048)    & \cellcolor[rgb]{ .973,  .412,  .42}4.4624 ($\pm$0.869)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7957 ($\pm$1.175)    & \cellcolor[rgb]{ .827,  .871,  .506}2.6065 ($\pm$1.439) & \cellcolor[rgb]{ .388,  .745,  .482}2.1226 ($\pm$1.264) \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}3.7484 ($\pm$1.238)  & \cellcolor[rgb]{ .996,  .851,  .506}3.1376 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}3.0344 ($\pm$1.406)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4656 ($\pm$1.304) & \cellcolor[rgb]{ .545,  .788,  .49}2.614 ($\pm$1.432)   \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ .973,  .412,  .42}3.8194 ($\pm$1.433)  & \cellcolor[rgb]{ .992,  .706,  .478}3.272 ($\pm$1.248)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8656 ($\pm$1.346)    & \cellcolor[rgb]{ .953,  .906,  .514}2.8194 ($\pm$1.305) & \cellcolor[rgb]{ .388,  .745,  .482}2.2237 ($\pm$1.219) \\
+			\textbf{housing}              & \cellcolor[rgb]{ .973,  .412,  .42}4.1892 ($\pm$1.099)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0172 ($\pm$1.288) & \cellcolor[rgb]{ .624,  .812,  .494}2.5871 ($\pm$1.354) & \cellcolor[rgb]{ .388,  .745,  .482}2.5312 ($\pm$1.265) & \cellcolor[rgb]{ 1,  .922,  .518}2.6753 ($\pm$1.34)     \\
+			\textbf{iris}                 & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.424)    & \cellcolor[rgb]{ .973,  .914,  .514}2.971 ($\pm$1.317)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3462 ($\pm$1.418)  & \cellcolor[rgb]{ 1,  .882,  .51}3.014 ($\pm$1.405)      & \cellcolor[rgb]{ .388,  .745,  .482}2.6849 ($\pm$1.429) \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ .973,  .412,  .42}4.2065 ($\pm$1.236)  & \cellcolor[rgb]{ 1,  .859,  .506}2.9688 ($\pm$1.299)    & \cellcolor[rgb]{ .631,  .816,  .494}2.586 ($\pm$1.234)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7882 ($\pm$1.34)     & \cellcolor[rgb]{ .388,  .745,  .482}2.4505 ($\pm$1.226) \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .973,  .412,  .42}4.7645 ($\pm$0.756)  & \cellcolor[rgb]{ .992,  .769,  .49}3.1882 ($\pm$1.021)  & \cellcolor[rgb]{ .49,  .773,  .486}2.2957 ($\pm$1.209)  & \cellcolor[rgb]{ 1,  .922,  .518}2.4968 ($\pm$1.128)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2548 ($\pm$1.097) \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .976,  .431,  .424}3.971 ($\pm$1.094)  & \cellcolor[rgb]{ .973,  .412,  .42}4.0226 ($\pm$1.12)   & \cellcolor[rgb]{ 1,  .922,  .518}2.4774 ($\pm$1.221)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2495 ($\pm$1.2)   & \cellcolor[rgb]{ .467,  .765,  .486}2.2796 ($\pm$1.132) \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ .973,  .412,  .42}4.0688 ($\pm$1.122)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9204 ($\pm$1.293)    & \cellcolor[rgb]{ 1,  .906,  .518}2.9559 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4032 ($\pm$1.378) & \cellcolor[rgb]{ .678,  .827,  .498}2.6516 ($\pm$1.28)  \\
+			\midrule
+			\textbf{avg rank}             & \cellcolor[rgb]{ .973,  .412,  .42}4.0612 ($\pm$1.229)  & \cellcolor[rgb]{ .988,  .69,  .475}3.3372 ($\pm$1.277)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7327 ($\pm$1.283)    & \cellcolor[rgb]{ .647,  .82,  .494}2.5151 ($\pm$1.282)  & \cellcolor[rgb]{ .388,  .745,  .482}2.3538 ($\pm$1.266) \\
+			\midrule
+			\textbf{normalised avg rank}  & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   \\
 		\end{tabular}%
+
+	}
+\end{table}%
+
+\begin{table}[htbp]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\label{tab:results:reselection:metrics:loss}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccccc}
+			                              & \multicolumn{5}{c}{\textbf{Reselection - Average Loss}}                                                                                                                                                                                                                                         \\
+			\midrule
+			\textbf{dataset}              & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .973,  .412,  .42}2.737 ($\pm$0.507)   & \cellcolor[rgb]{ 1,  .922,  .518}2.0907 ($\pm$0.113)    & \cellcolor[rgb]{ .545,  .788,  .49}2.0587 ($\pm$0.088)  & \cellcolor[rgb]{ .388,  .745,  .482}2.0475 ($\pm$0.103) & \cellcolor[rgb]{ 1,  .906,  .518}2.1139 ($\pm$0.336)    \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.3003 ($\pm$0.046)  & \cellcolor[rgb]{ .992,  .725,  .482}0.2835 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 ($\pm$0.016)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2619 ($\pm$0.013) & \cellcolor[rgb]{ .486,  .773,  .486}0.2637 ($\pm$0.016) \\
+			\textbf{bank}                 & \cellcolor[rgb]{ .984,  .596,  .455}0.2933 ($\pm$0.033) & \cellcolor[rgb]{ .973,  .412,  .42}0.3198 ($\pm$0.18)   & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .553,  .792,  .49}0.2299 ($\pm$0.032)  & \cellcolor[rgb]{ .388,  .745,  .482}0.224 ($\pm$0.018)  \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .973,  .412,  .42}0.1524 ($\pm$0.023)  & \cellcolor[rgb]{ .988,  .671,  .471}0.1084 ($\pm$0.025) & \cellcolor[rgb]{ 1,  .922,  .518}0.0651 ($\pm$0.02)     & \cellcolor[rgb]{ .6,  .804,  .494}0.0566 ($\pm$0.01)    & \cellcolor[rgb]{ .388,  .745,  .482}0.052 ($\pm$0.004)  \\
+			\textbf{car}                  & \cellcolor[rgb]{ .973,  .412,  .42}0.2157 ($\pm$0.031)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1591 ($\pm$0.026)    & \cellcolor[rgb]{ .91,  .894,  .51}0.1572 ($\pm$0.034)   & \cellcolor[rgb]{ 1,  .863,  .51}0.1659 ($\pm$0.064)     & \cellcolor[rgb]{ .388,  .745,  .482}0.1456 ($\pm$0.03)  \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .388,  .745,  .482}0.9624 ($\pm$0.043) & \cellcolor[rgb]{ .973,  .412,  .42}3.7821 ($\pm$4.993)  & \cellcolor[rgb]{ 1,  .914,  .518}1.2983 ($\pm$0.66)     & \cellcolor[rgb]{ 1,  .922,  .518}1.2541 ($\pm$0.868)    & \cellcolor[rgb]{ .482,  .773,  .486}1.0085 ($\pm$0.251) \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}0.1091 ($\pm$0.01)   & \cellcolor[rgb]{ 1,  .922,  .518}0.1043 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .894,  .514}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1013 ($\pm$0.008) & \cellcolor[rgb]{ .549,  .792,  .49}0.1021 ($\pm$0.008)  \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.1253 ($\pm$0.087)  & \cellcolor[rgb]{ .988,  .702,  .478}0.1002 ($\pm$0.064) & \cellcolor[rgb]{ 1,  .922,  .518}0.081 ($\pm$0.069)     & \cellcolor[rgb]{ .647,  .82,  .494}0.0681 ($\pm$0.055)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.056) \\
+			\textbf{housing}              & \cellcolor[rgb]{ .973,  .412,  .42}0.1268 ($\pm$0.025)  & \cellcolor[rgb]{ 1,  .902,  .514}0.0974 ($\pm$0.017)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.0961 ($\pm$0.026)    & \cellcolor[rgb]{ .729,  .843,  .502}0.0952 ($\pm$0.02)  \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .714,  .839,  .498}0.1633 ($\pm$0.135) & \cellcolor[rgb]{ .388,  .745,  .482}0.1376 ($\pm$0.138) & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 ($\pm$0.295)  & \cellcolor[rgb]{ .976,  .447,  .427}0.2373 ($\pm$0.361) & \cellcolor[rgb]{ 1,  .922,  .518}0.1853 ($\pm$0.235)    \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ .973,  .412,  .42}1.8461 ($\pm$5.829)  & \cellcolor[rgb]{ .886,  .886,  .51}0.0283 ($\pm$0.099)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ 1,  .922,  .518}0.0388 ($\pm$0.111)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0335 ($\pm$0.158)    \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .973,  .412,  .42}0.0872 ($\pm$0.018)  & \cellcolor[rgb]{ 1,  .886,  .514}0.0609 ($\pm$0.004)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0587 ($\pm$0.003)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0584 ($\pm$0.002) & \cellcolor[rgb]{ .482,  .769,  .486}0.0585 ($\pm$0.003) \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .973,  .412,  .42}0.4376 ($\pm$0.108)  & \cellcolor[rgb]{ .98,  .518,  .443}0.397 ($\pm$0.13)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)    & \cellcolor[rgb]{ .784,  .859,  .502}0.223 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1991 ($\pm$0.064) \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ .973,  .412,  .42}1.1183 ($\pm$0.031)  & \cellcolor[rgb]{ 1,  .922,  .518}1.081 ($\pm$0.023)     & \cellcolor[rgb]{ 1,  .898,  .514}1.0827 ($\pm$0.026)    & \cellcolor[rgb]{ .388,  .745,  .482}1.0711 ($\pm$0.028) & \cellcolor[rgb]{ .498,  .776,  .486}1.0729 ($\pm$0.022) \\
+		\end{tabular}%
+
 	}
@@
 
-\begin{table}[H]
+\begin{table}[htbp]
 	\centering
 	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:burn_in:metrics}%
+	\label{tab:results:burn_in:metrics:rank}%
 	\par\bigskip
 	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{(all)}            &                                                                                    &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
-			\cmidrule{1-2}                      &                                      &                                                                                    &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{burn in}} & \multicolumn{1}{l}{\textbf{results}}                                               &                 &                &                                                                           &                 &                &                                                                           &                 &                &                                                                           &                 &                &                 &                 \\
-			\cmidrule{2-3}                      & \textbf{0}                           &                                                                                    &                 & \textbf{5}     &                                                                           &                 & \textbf{10}    &                                                                           &                 & \textbf{15}    &                                                                           &                 & \textbf{20}    &                 &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                       & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}    & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                  & 2.9151                                                                             & 1.3952          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6935} & 1.3934          & 930            & 2.9172                                                                    & 1.3837          & 930            & 2.8398                                                                    & 1.3524          & 930            & 3.6344          & 1.3574          \\
-			adult                               & 930                                  & 2.7366                                                                             & 1.4475          & 930            & 2.6430                                                                    & 1.3817          & 930            & 2.9892                                                                    & 1.4111          & 930            & 3.1731                                                                    & 1.4477          & 930            & 3.1355          & 1.4130          \\
-			air quality                         & 930                                  & 2.9097                                                                             & 1.4408          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6817} & 1.4270          & 930            & 2.7699                                                                    & 1.3443          & 930            & 3.3720                                                                    & 1.3137          & 930            & 3.2667          & 1.4119          \\
-			bike                                & 930                                  & 1.9237                                                                             & 0.9808          & 930            & 2.1806                                                                    & 1.0238          & 930            & 2.9237                                                                    & 1.2739          & 930            & 3.5054                                                                    & 1.1859          & 930            & 4.4667          & 0.8514          \\
-			car                                 & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.3624}          & 1.2315          & 930            & 2.5882                                                                    & 1.4246          & 930            & 3.2978                                                                    & 1.3922          & 930            & 3.3796                                                                    & 1.2711          & 930            & 3.3720          & 1.4009          \\
-			fish toxicity                       & 930                                  & 3.0634                                                                             & 1.4589          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7935} & 1.4021          & 930            & 2.8204                                                                    & 1.5131          & 930            & 3.1022                                                                    & 1.3461          & 930            & 3.2204          & 1.2949          \\
-			forest fires                        & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8161}          & 1.3301          & 930            & 2.8495                                                                    & 1.3830          & 930            & 2.8645                                                                    & 1.4092          & 930            & 3.3774                                                                    & 1.3976          & 930            & 3.0925          & 1.4709          \\
-			housing                             & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6903}          & 1.3837          & 930            & 2.9516                                                                    & 1.3176          & 930            & 2.9968                                                                    & 1.4425          & 930            & 3.0581                                                                    & 1.3435          & 930            & 3.3032          & 1.5101          \\
-			iris                                & 930                                  & 2.9473                                                                             & 1.4608          & 930            & 2.9720                                                                    & 1.3675          & 930            & 3.1903                                                                    & 1.4493          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710} & 1.3694          & 930            & 3.1194          & 1.3872          \\
-			mushroom                            & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2065}          & 1.2486          & 930            & 2.9376                                                                    & 1.2977          & 930            & 3.1613                                                                    & 1.2966          & 930            & 3.1441                                                                    & 1.4015          & 930            & 3.5226          & 1.5006          \\
-			parkinsons                          & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.2796}          & 1.2822          & 930            & 2.8892                                                                    & 1.2474          & 930            & 2.7065                                                                    & 1.3143          & 930            & 3.3968                                                                    & 1.4175          & 930            & 3.7280          & 1.3295          \\
-			student performance                 & 930                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.1452}          & 1.2052          & 930            & 2.6946                                                                    & 1.4032          & 930            & 3.0968                                                                    & 1.3525          & 930            & 3.4581                                                                    & 1.3539          & 930            & 3.6054          & 1.2312          \\
-			wine quality                        & 930                                  & 2.9699                                                                             & 1.4373          & 930            & 3.0108                                                                    & 1.3041          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6634} & 1.4186          & 930            & 3.1247                                                                    & 1.3980          & 930            & 3.2312          & 1.4471          \\
-			bank                                & 930                                  & 2.7301                                                                             & 1.3210          & 930            & 2.8194                                                                    & 1.3350          & 930            & 2.8570                                                                    & 1.4848          & 930            & 2.9312                                                                    & 1.3841          & 930            & 3.6624          & 1.3391          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13020}                       & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.6211}} & \textbf{1.3814} & \textbf{13020} & \textbf{2.7647}                                                           & \textbf{1.3553} & \textbf{13020} & \textbf{2.9468}                                                           & \textbf{1.4045} & \textbf{13020} & \textbf{3.1881}                                                           & \textbf{1.3754} & \textbf{13020} & \textbf{3.4543} & \textbf{1.4061} \\
+		% Table generated by Excel2LaTeX from sheet 'rank'
+		\begin{tabular}{r|ccccc}
+			                              & \multicolumn{5}{c}{\textbf{Burn In - Average Rank}}                                                                                                                                                                                                                                             \\
+			\midrule
+			\textbf{dataset}              & \textbf{0}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ 1,  .922,  .518}2.9151 ($\pm$1.395)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6935 ($\pm$1.393) & \cellcolor[rgb]{ 1,  .922,  .518}2.9172 ($\pm$1.384)    & \cellcolor[rgb]{ .788,  .859,  .502}2.8398 ($\pm$1.352) & \cellcolor[rgb]{ .973,  .412,  .42}3.6344 ($\pm$1.357)  \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9097 ($\pm$1.441)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6817 ($\pm$1.427) & \cellcolor[rgb]{ .624,  .812,  .494}2.7699 ($\pm$1.344) & \cellcolor[rgb]{ .973,  .412,  .42}3.372 ($\pm$1.314)   & \cellcolor[rgb]{ .98,  .529,  .443}3.2667 ($\pm$1.412)  \\
+			\textbf{bank}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.7301 ($\pm$1.321) & \cellcolor[rgb]{ .816,  .867,  .506}2.8194 ($\pm$1.335) & \cellcolor[rgb]{ 1,  .922,  .518}2.857 ($\pm$1.485)     & \cellcolor[rgb]{ 1,  .878,  .51}2.9312 ($\pm$1.384)     & \cellcolor[rgb]{ .973,  .412,  .42}3.6624 ($\pm$1.339)  \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.9237 ($\pm$0.981) & \cellcolor[rgb]{ .545,  .788,  .49}2.1806 ($\pm$1.024)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9237 ($\pm$1.274)    & \cellcolor[rgb]{ .992,  .729,  .482}3.5054 ($\pm$1.186) & \cellcolor[rgb]{ .973,  .412,  .42}4.4667 ($\pm$0.851)  \\
+			\textbf{car}                  & \cellcolor[rgb]{ .388,  .745,  .482}2.3624 ($\pm$1.231) & \cellcolor[rgb]{ .533,  .784,  .49}2.5882 ($\pm$1.425)  & \cellcolor[rgb]{ 1,  .922,  .518}3.2978 ($\pm$1.392)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3796 ($\pm$1.271)  & \cellcolor[rgb]{ .976,  .459,  .431}3.372 ($\pm$1.401)  \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .388,  .745,  .482}2.4054 ($\pm$1.358) & \cellcolor[rgb]{ .604,  .808,  .494}2.7011 ($\pm$1.358) & \cellcolor[rgb]{ 1,  .902,  .518}3.2398 ($\pm$1.372)    & \cellcolor[rgb]{ 1,  .922,  .518}3.2323 ($\pm$1.326)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4215 ($\pm$1.396)  \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}3.0634 ($\pm$1.459)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7935 ($\pm$1.402) & \cellcolor[rgb]{ .447,  .761,  .482}2.8204 ($\pm$1.513) & \cellcolor[rgb]{ .996,  .796,  .494}3.1022 ($\pm$1.346) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.295)  \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8161 ($\pm$1.33)  & \cellcolor[rgb]{ .808,  .867,  .506}2.8495 ($\pm$1.383) & \cellcolor[rgb]{ 1,  .922,  .518}2.8645 ($\pm$1.409)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.398)  & \cellcolor[rgb]{ .988,  .698,  .475}3.0925 ($\pm$1.471) \\
+			\textbf{housing}              & \cellcolor[rgb]{ .388,  .745,  .482}2.6903 ($\pm$1.384) & \cellcolor[rgb]{ .91,  .894,  .51}2.9516 ($\pm$1.318)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.442)    & \cellcolor[rgb]{ .996,  .82,  .498}3.0581 ($\pm$1.344)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3032 ($\pm$1.51)   \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .922,  .898,  .51}2.9473 ($\pm$1.461)  & \cellcolor[rgb]{ 1,  .922,  .518}2.972 ($\pm$1.367)     & \cellcolor[rgb]{ .973,  .412,  .42}3.1903 ($\pm$1.449)  & \cellcolor[rgb]{ .388,  .745,  .482}2.771 ($\pm$1.369)  & \cellcolor[rgb]{ .984,  .58,  .455}3.1194 ($\pm$1.387)  \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ .388,  .745,  .482}2.2065 ($\pm$1.249) & \cellcolor[rgb]{ .863,  .882,  .51}2.9376 ($\pm$1.298)  & \cellcolor[rgb]{ 1,  .902,  .514}3.1613 ($\pm$1.297)    & \cellcolor[rgb]{ 1,  .922,  .518}3.1441 ($\pm$1.401)    & \cellcolor[rgb]{ .973,  .412,  .42}3.5226 ($\pm$1.501)  \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .388,  .745,  .482}2.2796 ($\pm$1.282) & \cellcolor[rgb]{ 1,  .922,  .518}2.8892 ($\pm$1.247)    & \cellcolor[rgb]{ .816,  .867,  .506}2.7065 ($\pm$1.314) & \cellcolor[rgb]{ .984,  .616,  .459}3.3968 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.728 ($\pm$1.33)    \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.1452 ($\pm$1.205) & \cellcolor[rgb]{ .741,  .843,  .502}2.6946 ($\pm$1.403) & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.352)    & \cellcolor[rgb]{ .984,  .561,  .451}3.4581 ($\pm$1.354) & \cellcolor[rgb]{ .973,  .412,  .42}3.6054 ($\pm$1.231)  \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ .925,  .898,  .51}2.9699 ($\pm$1.437)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0108 ($\pm$1.304)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6634 ($\pm$1.419) & \cellcolor[rgb]{ .988,  .659,  .471}3.1247 ($\pm$1.398) & \cellcolor[rgb]{ .973,  .412,  .42}3.2312 ($\pm$1.447)  \\
+			\midrule
+			\textbf{avg rank}             & \cellcolor[rgb]{ .388,  .745,  .482}2.5975 ($\pm$1.376) & \cellcolor[rgb]{ .671,  .824,  .498}2.7688 ($\pm$1.353) & \cellcolor[rgb]{ 1,  .922,  .518}2.9647 ($\pm$1.404)    & \cellcolor[rgb]{ .988,  .694,  .475}3.1923 ($\pm$1.367) & \cellcolor[rgb]{ .973,  .412,  .42}3.4747 ($\pm$1.402)  \\
+			\midrule
+			\textbf{normalised avg rank}  & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
 		\end{tabular}%
+
+	}
+\end{table}%
+
+\begin{table}[htbp]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\label{tab:results:burn_in:metrics:loss}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccccc}
+			                              & \multicolumn{5}{c}{\textbf{Burn In - Average Loss}}                                                                                                                                                                                                                              \\
+			\midrule
+			\textbf{dataset}              & \textbf{0}                                           & \textbf{5}                                           & \textbf{10}                                          & \textbf{15}                                          & \textbf{20}                                          \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .392,  .745,  .482}2.0587 (+-0.088) & \cellcolor[rgb]{ .388,  .745,  .482}2.0583 (+-0.181) & \cellcolor[rgb]{ 1,  .922,  .518}2.0961 (+-0.168)    & \cellcolor[rgb]{ 1,  .878,  .51}2.1454 (+-0.365)     & \cellcolor[rgb]{ .973,  .412,  .42}2.6753 (+-2.18)   \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 (+-0.016)    & \cellcolor[rgb]{ .851,  .878,  .506}0.2719 (+-0.02)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2688 (+-0.014) & \cellcolor[rgb]{ .988,  .694,  .475}0.2784 (+-0.017) & \cellcolor[rgb]{ .973,  .412,  .42}0.2851 (+-0.029)  \\
+			\textbf{bank}                 & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 (+-0.065)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2373 (+-0.033) & \cellcolor[rgb]{ .996,  .804,  .498}0.2514 (+-0.109) & \cellcolor[rgb]{ .784,  .859,  .502}0.2427 (+-0.033) & \cellcolor[rgb]{ .973,  .412,  .42}0.2703 (+-0.056)  \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.0651 (+-0.02)  & \cellcolor[rgb]{ .443,  .761,  .482}0.0678 (+-0.024) & \cellcolor[rgb]{ 1,  .922,  .518}0.0929 (+-0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1109 (+-0.043) & \cellcolor[rgb]{ .973,  .412,  .42}0.1383 (+-0.034)  \\
+			\textbf{car}                  & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 (+-0.034) & \cellcolor[rgb]{ .627,  .812,  .494}0.164 (+-0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1745 (+-0.037)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1883 (+-0.067)  & \cellcolor[rgb]{ .992,  .71,  .478}0.1803 (+-0.039)  \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .698,  .831,  .498}1.2983 (+-0.66)  & \cellcolor[rgb]{ .388,  .745,  .482}1.1216 (+-0.582) & \cellcolor[rgb]{ 1,  .922,  .518}1.4701 (+-1.161)    & \cellcolor[rgb]{ .984,  .604,  .459}1.9918 (+-3.645) & \cellcolor[rgb]{ .973,  .412,  .42}2.2996 (+-3.589)  \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .992,  .765,  .49}0.1046 (+-0.008)  & \cellcolor[rgb]{ .69,  .831,  .498}0.1026 (+-0.009)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1009 (+-0.01)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1043 (+-0.007)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1052 (+-0.009)  \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ 1,  .922,  .518}0.081 (+-0.069)     & \cellcolor[rgb]{ .753,  .851,  .502}0.0772 (+-0.057) & \cellcolor[rgb]{ .388,  .745,  .482}0.0714 (+-0.045) & \cellcolor[rgb]{ .973,  .412,  .42}0.1136 (+-0.059)  & \cellcolor[rgb]{ .98,  .557,  .451}0.1044 (+-0.093)  \\
+			\textbf{housing}              & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 (+-0.017) & \cellcolor[rgb]{ .596,  .804,  .494}0.096 (+-0.015)  & \cellcolor[rgb]{ .992,  .757,  .486}0.1036 (+-0.037) & \cellcolor[rgb]{ 1,  .922,  .518}0.0997 (+-0.021)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1116 (+-0.034)  \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .996,  .78,  .49}0.2411 (+-0.295)   & \cellcolor[rgb]{ .388,  .745,  .482}0.1472 (+-0.134) & \cellcolor[rgb]{ .973,  .412,  .42}0.2717 (+-0.462)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2291 (+-0.376)    & \cellcolor[rgb]{ .663,  .824,  .498}0.1842 (+-0.189) \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 (+-0.012) & \cellcolor[rgb]{ .976,  .42,  .424}0.1068 (+-0.3)    & \cellcolor[rgb]{ .616,  .808,  .494}0.0262 (+-0.057) & \cellcolor[rgb]{ .973,  .412,  .42}0.1075 (+-0.256)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0612 (+-0.108)    \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 (+-0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0599 (+-0.003)    & \cellcolor[rgb]{ .745,  .847,  .502}0.0594 (+-0.003) & \cellcolor[rgb]{ .984,  .627,  .463}0.0644 (+-0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.0676 (+-0.015)  \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 (+-0.102) & \cellcolor[rgb]{ .733,  .843,  .502}0.2801 (+-0.127) & \cellcolor[rgb]{ 1,  .922,  .518}0.314 (+-0.137)     & \cellcolor[rgb]{ .988,  .631,  .463}0.3623 (+-0.139) & \cellcolor[rgb]{ .973,  .412,  .42}0.3988 (+-0.133)  \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ 1,  .922,  .518}1.0827 (+-0.026)    & \cellcolor[rgb]{ .396,  .745,  .482}1.0791 (+-0.021) & \cellcolor[rgb]{ .388,  .745,  .482}1.079 (+-0.03)   & \cellcolor[rgb]{ .988,  .686,  .475}1.086 (+-0.029)  & \cellcolor[rgb]{ .973,  .412,  .42}1.0897 (+-0.034)  \\
+		\end{tabular}%
+
 	}

### 2022-11-15 dissertation/chapters/08-results.tex
🚧 (results): New CD plots and tables

@@
 			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.2215 ($\pm$1.591)                   & \cellcolor[rgb]{ .416,  .753,  .482}2.3989 ($\pm$1.887) & \cellcolor[rgb]{ .78,  .859,  .502}4.6172 ($\pm$2.65)   & \cellcolor[rgb]{ .796,  .863,  .506}4.7032 ($\pm$2.108) & \cellcolor[rgb]{ .725,  .839,  .498}4.2731 ($\pm$1.542) & \cellcolor[rgb]{ 1,  .922,  .518}5.9376 ($\pm$2.399)    & \cellcolor[rgb]{ .894,  .89,  .51}5.3129 ($\pm$1.478)   & \cellcolor[rgb]{ .992,  .749,  .486}8.1882 ($\pm$1.195) & \cellcolor[rgb]{ .98,  .525,  .443}11.1108 ($\pm$1.102)  & \cellcolor[rgb]{ .98,  .514,  .439}11.2559 ($\pm$1.826)  & \cellcolor[rgb]{ .992,  .718,  .478}8.628 ($\pm$1.019)   & \cellcolor[rgb]{ .984,  .624,  .463}9.8151 ($\pm$1.16)   & \cellcolor[rgb]{ .973,  .412,  .42}12.5376 ($\pm$1.329)  \\
-			\textbf{air\_quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                   & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                   & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\
 			\textbf{bank}                & \cellcolor[rgb]{ .455,  .765,  .486}2.5495 ($\pm$1.598)                   & \cellcolor[rgb]{ .388,  .745,  .482}2.0796 ($\pm$1.587) & \cellcolor[rgb]{ .588,  .8,  .49}3.4645 ($\pm$2.209)    & \cellcolor[rgb]{ .8,  .863,  .506}4.8828 ($\pm$1.702)   & \cellcolor[rgb]{ .71,  .835,  .498}4.2871 ($\pm$1.732)  & \cellcolor[rgb]{ 1,  .922,  .518}6.2419 ($\pm$2.157)    & \cellcolor[rgb]{ .914,  .894,  .51}5.672 ($\pm$1.241)   & \cellcolor[rgb]{ .988,  .639,  .463}9.7495 ($\pm$1.048) & \cellcolor[rgb]{ .98,  .537,  .447}10.9817 ($\pm$1.216)  & \cellcolor[rgb]{ .976,  .467,  .431}11.8376 ($\pm$1.464) & \cellcolor[rgb]{ .992,  .757,  .486}8.2774 ($\pm$1.03)   & \cellcolor[rgb]{ .992,  .741,  .486}8.4774 ($\pm$1.068)  & \cellcolor[rgb]{ .973,  .412,  .42}12.4989 ($\pm$1.224)  \\
@@
 			\textbf{diabetic}            & \cellcolor[rgb]{ .506,  .776,  .486}2.7796 ($\pm$1.659)                   & \cellcolor[rgb]{ 1,  .886,  .514}7.1484 ($\pm$2.227)    & \cellcolor[rgb]{ 1,  .922,  .518}6.7376 ($\pm$2.577)    & \cellcolor[rgb]{ .812,  .867,  .506}5.2269 ($\pm$2.186) & \cellcolor[rgb]{ .388,  .745,  .482}1.8118 ($\pm$1.413) & \cellcolor[rgb]{ .988,  .69,  .475}9.3968 ($\pm$3.022)  & \cellcolor[rgb]{ .494,  .773,  .486}2.6753 ($\pm$1.629) & \cellcolor[rgb]{ .992,  .765,  .49}8.557 ($\pm$1.17)    & \cellcolor[rgb]{ .98,  .529,  .443}11.2011 ($\pm$1.413)  & \cellcolor[rgb]{ .984,  .573,  .451}10.7022 ($\pm$1.067) & \cellcolor[rgb]{ .898,  .89,  .51}5.9215 ($\pm$1.542)    & \cellcolor[rgb]{ .949,  .906,  .514}6.3355 ($\pm$1.612)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5065 ($\pm$1.242)  \\
-			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                    & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
-			\textbf{forest\_fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                   & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                    & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                   & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\
 			\textbf{housing}             & \cellcolor[rgb]{ .404,  .749,  .482}3.4484 ($\pm$2.025)                   & \cellcolor[rgb]{ .388,  .745,  .482}3.3344 ($\pm$1.819) & \cellcolor[rgb]{ .439,  .757,  .482}3.6946 ($\pm$2.166) & \cellcolor[rgb]{ .553,  .792,  .49}4.4742 ($\pm$2.312)  & \cellcolor[rgb]{ .584,  .8,  .49}4.6839 ($\pm$2.658)    & \cellcolor[rgb]{ .537,  .788,  .49}4.3763 ($\pm$2.438)  & \cellcolor[rgb]{ 1,  .918,  .518}7.5903 ($\pm$2.748)    & \cellcolor[rgb]{ 1,  .922,  .518}7.5441 ($\pm$1.736)    & \cellcolor[rgb]{ 1,  .878,  .51}7.8839 ($\pm$2.099)      & \cellcolor[rgb]{ .984,  .608,  .459}9.9409 ($\pm$2.317)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4075 ($\pm$1.528)  & \cellcolor[rgb]{ .976,  .431,  .424}11.2731 ($\pm$1.506) & \cellcolor[rgb]{ .976,  .42,  .424}11.3484 ($\pm$2.096)  \\
@@
 			\textbf{parkinsons}          & \cellcolor[rgb]{ .412,  .749,  .482}2.4677 ($\pm$1.497)                   & \cellcolor[rgb]{ .388,  .745,  .482}2.2333 ($\pm$1.742) & \cellcolor[rgb]{ .541,  .788,  .49}3.5656 ($\pm$2.492)  & \cellcolor[rgb]{ .655,  .82,  .494}4.572 ($\pm$1.934)   & \cellcolor[rgb]{ 1,  .922,  .518}7.5355 ($\pm$1.44)     & \cellcolor[rgb]{ .635,  .816,  .494}4.3839 ($\pm$1.861) & \cellcolor[rgb]{ .875,  .882,  .51}6.472 ($\pm$2.423)   & \cellcolor[rgb]{ .996,  .843,  .506}8.3161 ($\pm$1.644) & \cellcolor[rgb]{ 1,  .898,  .514}7.7968 ($\pm$1.719)     & \cellcolor[rgb]{ .996,  .827,  .502}8.4892 ($\pm$1.901)  & \cellcolor[rgb]{ .98,  .494,  .435}11.7516 ($\pm$1.155)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5419 ($\pm$1.351)  & \cellcolor[rgb]{ .984,  .584,  .455}10.8742 ($\pm$1.317) \\
-			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                   & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
-			\textbf{wine\_quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                    & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                   & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                    & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\
 			\midrule
@@
 			\textbf{abalone}                    & \cellcolor[rgb]{ .506,  .776,  .486}1.9678 ($\pm$0.032)                   & \cellcolor[rgb]{ .494,  .773,  .486}1.9651 ($\pm$0.035) & \cellcolor[rgb]{ .388,  .745,  .482}1.9455 ($\pm$0.035) & \cellcolor[rgb]{ .749,  .847,  .502}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .765,  .851,  .502}2.0156 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .788,  .859,  .502}2.0199 ($\pm$0.034) & \cellcolor[rgb]{ .996,  .827,  .502}2.2942 ($\pm$0.055) & \cellcolor[rgb]{ .984,  .612,  .459}2.8155 ($\pm$0.055) & \cellcolor[rgb]{ .98,  .522,  .443}3.0384 ($\pm$0.294)  & \cellcolor[rgb]{ .992,  .773,  .49}2.428 ($\pm$0.029)   & \cellcolor[rgb]{ .992,  .745,  .486}2.4942 ($\pm$0.029) & \cellcolor[rgb]{ .973,  .412,  .42}3.2959 ($\pm$0.016)  \\
-			\textbf{air\_quality}               & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                    & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\
+			\textbf{air quality}                & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                    & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\
 			\textbf{bank}                       & \cellcolor[rgb]{ .459,  .765,  .486}0.2096 ($\pm$0.005)                   & \cellcolor[rgb]{ .4,  .745,  .482}0.2065 ($\pm$0.004)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2058 ($\pm$0.006) & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.005)    & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .886,  .514}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .627,  .812,  .494}0.2186 ($\pm$0.004) & \cellcolor[rgb]{ .996,  .839,  .502}0.2562 ($\pm$0.011) & \cellcolor[rgb]{ .988,  .686,  .475}0.2881 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.3454 ($\pm$0.034)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2382 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2386 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .424,  .424}0.3437 ($\pm$0.028) \\
@@
 			\textbf{diabetic}                   & \cellcolor[rgb]{ .694,  .831,  .498}0.8895 ($\pm$0.004)                   & \cellcolor[rgb]{ 1,  .898,  .514}0.9193 ($\pm$0.01)     & \cellcolor[rgb]{ .918,  .894,  .51}0.8957 ($\pm$0.004)  & \cellcolor[rgb]{ .98,  .914,  .514}0.8976 ($\pm$0.011)  & \cellcolor[rgb]{ .388,  .745,  .482}0.8809 ($\pm$0.004) & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)   & \cellcolor[rgb]{ .49,  .773,  .486}0.8839 ($\pm$0.005)  & \cellcolor[rgb]{ 1,  .902,  .518}0.9137 ($\pm$0.008)    & \cellcolor[rgb]{ .996,  .843,  .506}0.9613 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .835,  .502}0.9661 ($\pm$0.016) & \cellcolor[rgb]{ .976,  .914,  .514}0.8974 ($\pm$0.004) & \cellcolor[rgb]{ 1,  .922,  .518}0.898 ($\pm$0.003)     & \cellcolor[rgb]{ .988,  .694,  .475}1.0774 ($\pm$0.039) \\
-			\textbf{fish\_toxicity}             & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                      & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
-			\textbf{forest\_fires}              & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                       & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\
+			\textbf{fish toxicity}              & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                      & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
+			\textbf{forest fires}               & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                       & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\
 			\textbf{housing}                    & \cellcolor[rgb]{ .518,  .78,  .486}0.0889 ($\pm$0.012)                    & \cellcolor[rgb]{ .404,  .749,  .482}0.0848 ($\pm$0.011) & \cellcolor[rgb]{ .388,  .745,  .482}0.0842 ($\pm$0.015) & \cellcolor[rgb]{ .69,  .831,  .498}0.0951 ($\pm$0.015)  & \cellcolor[rgb]{ .612,  .808,  .494}0.0923 ($\pm$0.016) & \cellcolor[rgb]{ .663,  .824,  .498}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.106 ($\pm$0.019)     & \cellcolor[rgb]{ 1,  .867,  .51}0.1169 ($\pm$0.019)     & \cellcolor[rgb]{ .996,  .812,  .498}0.1279 ($\pm$0.02)  & \cellcolor[rgb]{ .992,  .722,  .482}0.1452 ($\pm$0.03)  & \cellcolor[rgb]{ .984,  .576,  .455}0.1735 ($\pm$0.023) & \cellcolor[rgb]{ .984,  .588,  .455}0.1713 ($\pm$0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.2057 ($\pm$0.036)  \\
@@
 			\textbf{parkinsons}                 & \cellcolor[rgb]{ .51,  .776,  .486}0.0563 ($\pm$0.001)                    & \cellcolor[rgb]{ .412,  .749,  .482}0.0545 ($\pm$0.002) & \cellcolor[rgb]{ .388,  .745,  .482}0.054 ($\pm$0.002)  & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0655 ($\pm$0.002)    & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .69,  .831,  .498}0.0597 ($\pm$0.002)  & \cellcolor[rgb]{ 1,  .918,  .518}0.0658 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .898,  .514}0.0669 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .894,  .514}0.0671 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .467,  .431}0.0923 ($\pm$0.008) & \cellcolor[rgb]{ .973,  .412,  .42}0.0954 ($\pm$0.009)  & \cellcolor[rgb]{ .984,  .604,  .459}0.0843 ($\pm$0.009) \\
-			\textbf{student\_performance}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1656 ($\pm$0.011)                   & \cellcolor[rgb]{ .98,  .522,  .443}0.4929 ($\pm$0.105)  & \cellcolor[rgb]{ .973,  .412,  .42}0.5724 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .855,  .506}0.2454 ($\pm$0.134)    & \cellcolor[rgb]{ .471,  .769,  .486}0.1697 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .871,  .51}0.2359 ($\pm$0.102)     & \cellcolor[rgb]{ .49,  .773,  .486}0.1708 ($\pm$0.01)   & \cellcolor[rgb]{ .969,  .91,  .514}0.1947 ($\pm$0.014)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1962 ($\pm$0.01)     & \cellcolor[rgb]{ .984,  .573,  .451}0.4565 ($\pm$0.049) & \cellcolor[rgb]{ .933,  .902,  .514}0.193 ($\pm$0.011)  & \cellcolor[rgb]{ .925,  .898,  .51}0.1925 ($\pm$0.011)  & \cellcolor[rgb]{ 1,  .918,  .518}0.2014 ($\pm$0.012)    \\
-			\textbf{wine\_quality}              & \cellcolor[rgb]{ .631,  .816,  .494}1.0651 ($\pm$0.024)                   & \cellcolor[rgb]{ .388,  .745,  .482}1.0395 ($\pm$0.018) & \cellcolor[rgb]{ .502,  .776,  .486}1.0514 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .698,  .831,  .498}1.0718 ($\pm$0.025) & \cellcolor[rgb]{ .804,  .863,  .506}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .788,  .859,  .502}1.0809 ($\pm$0.021) & \cellcolor[rgb]{ .996,  .839,  .502}1.1666 ($\pm$0.03)  & \cellcolor[rgb]{ .992,  .725,  .482}1.2516 ($\pm$0.046) & \cellcolor[rgb]{ .988,  .659,  .467}1.3046 ($\pm$0.114) & \cellcolor[rgb]{ .996,  .843,  .502}1.1648 ($\pm$0.023) & \cellcolor[rgb]{ .996,  .824,  .502}1.1774 ($\pm$0.019) & \cellcolor[rgb]{ .973,  .412,  .42}1.4896 ($\pm$0.093)  \\
+			\textbf{student performance}        & \cellcolor[rgb]{ .388,  .745,  .482}0.1656 ($\pm$0.011)                   & \cellcolor[rgb]{ .98,  .522,  .443}0.4929 ($\pm$0.105)  & \cellcolor[rgb]{ .973,  .412,  .42}0.5724 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .855,  .506}0.2454 ($\pm$0.134)    & \cellcolor[rgb]{ .471,  .769,  .486}0.1697 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .871,  .51}0.2359 ($\pm$0.102)     & \cellcolor[rgb]{ .49,  .773,  .486}0.1708 ($\pm$0.01)   & \cellcolor[rgb]{ .969,  .91,  .514}0.1947 ($\pm$0.014)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1962 ($\pm$0.01)     & \cellcolor[rgb]{ .984,  .573,  .451}0.4565 ($\pm$0.049) & \cellcolor[rgb]{ .933,  .902,  .514}0.193 ($\pm$0.011)  & \cellcolor[rgb]{ .925,  .898,  .51}0.1925 ($\pm$0.011)  & \cellcolor[rgb]{ 1,  .918,  .518}0.2014 ($\pm$0.012)    \\
+			\textbf{wine quality}               & \cellcolor[rgb]{ .631,  .816,  .494}1.0651 ($\pm$0.024)                   & \cellcolor[rgb]{ .388,  .745,  .482}1.0395 ($\pm$0.018) & \cellcolor[rgb]{ .502,  .776,  .486}1.0514 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .698,  .831,  .498}1.0718 ($\pm$0.025) & \cellcolor[rgb]{ .804,  .863,  .506}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .788,  .859,  .502}1.0809 ($\pm$0.021) & \cellcolor[rgb]{ .996,  .839,  .502}1.1666 ($\pm$0.03)  & \cellcolor[rgb]{ .992,  .725,  .482}1.2516 ($\pm$0.046) & \cellcolor[rgb]{ .988,  .659,  .467}1.3046 ($\pm$0.114) & \cellcolor[rgb]{ .996,  .843,  .502}1.1648 ($\pm$0.023) & \cellcolor[rgb]{ .996,  .824,  .502}1.1774 ($\pm$0.019) & \cellcolor[rgb]{ .973,  .412,  .42}1.4896 ($\pm$0.093)  \\
 			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
@@
 	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:heuristic_pool:metrics}%
+	\label{tab:results:heuristic_pool:metrics:rank}%
 	\par\bigskip
 	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}          &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
-			\cmidrule{1-2}                      &                                             &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{heuristic pool}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                &                                                                                    &                 &                &                 &                 \\
-			\cmidrule{2-3}                      & \textbf{all}                                &                                                                           &                 & \textbf{gd}    &                                                                                    &                 & \textbf{mh}    &                 &                 \\
-			\cmidrule{2-10}    \textbf{dataset} & \textbf{count}                              & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count} & \textbf{avg}    & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                         & 1.7946                                                                    & 0.6411          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3828}          & 0.5604          & 930            & 2.8226          & 0.4198          \\
-			adult                               & 930                                         & 2.8484                                                                    & 0.5058          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.1559}          & 0.4077          & 930            & 1.8989          & 0.4104          \\
-			air quality                         & 930                                         & 2.1871                                                                    & 0.8153          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6828}          & 0.7506          & 930            & 2.1301          & 0.7883          \\
-			bank                                & 930                                         & 1.7731                                                                    & 0.5617          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3215}          & 0.4920          & 930            & 2.9054          & 0.3341          \\
-			bike                                & 930                                         & 1.6247                                                                    & 0.5529          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4387}          & 0.5321          & 930            & 2.9366          & 0.2808          \\
-			car                                 & 930                                         & 1.5903                                                                    & 0.5113          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4409}          & 0.5180          & 930            & 2.9688          & 0.2275          \\
-			diabetic                            & 930                                         & 2.4516                                                                    & 0.7353          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.2806}          & 0.5756          & 930            & 2.2677          & 0.5798          \\
-			fish toxicity                       & 930                                         & 1.9903                                                                    & 0.8485          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8344}          & 0.7684          & 930            & 2.1753          & 0.7959          \\
-			forest fires                        & 930                                         & 2.0667                                                                    & 0.8338          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8269}          & 0.7813          & 930            & 2.1065          & 0.8066          \\
-			housing                             & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6043} & 0.6869          & 930            & 1.6602                                                                             & 0.6648          & 930            & 2.7355          & 0.5238          \\
-			iris                                & 930                                         & 1.8581                                                                    & 0.8005          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7806}          & 0.7272          & 930            & 2.3613          & 0.7960          \\
-			mushroom                            & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5204} & 0.5815          & 930            & 1.5484                                                                             & 0.5273          & 930            & 2.9312          & 0.2890          \\
-			parkinsons                          & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5570} & 0.6238          & 930            & 1.6011                                                                             & 0.5915          & 930            & 2.8419          & 0.4448          \\
-			student performance                 & 930                                         & 1.9828                                                                    & 0.8220          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7903}          & 0.8480          & 930            & 2.2269          & 0.7152          \\
-			wine quality                        & 930                                         & 1.5785                                                                    & 0.5498          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5630          & 930            & 2.9280          & 0.2938          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                              & \textbf{1.8952}                                                           & \textbf{0.7730} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.5492}} & \textbf{0.6651} & \textbf{13950} & \textbf{2.5491} & \textbf{0.6684} \\
+		\begin{tabular}{r|ccc}
+			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Rank}}                                                                                                                    \\
+			\midrule
+			\textbf{dataset}             & \textbf{all}                                               & \textbf{gd}                                             & \textbf{mh}                                            \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}1.7946 ($\pm$0.641)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3828 ($\pm$0.56)  & \cellcolor[rgb]{ .973,  .412,  .42}2.8226 ($\pm$0.42)  \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}2.1871 ($\pm$0.815)     & \cellcolor[rgb]{ .388,  .745,  .482}1.6828 ($\pm$0.751) & \cellcolor[rgb]{ 1,  .922,  .518}2.1301 ($\pm$0.788)   \\
+			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}1.7731 ($\pm$0.562)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3215 ($\pm$0.492) & \cellcolor[rgb]{ .973,  .412,  .42}2.9054 ($\pm$0.334) \\
+			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}1.6247 ($\pm$0.553)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4387 ($\pm$0.532) & \cellcolor[rgb]{ .973,  .412,  .42}2.9366 ($\pm$0.281) \\
+			\textbf{car}                 & \cellcolor[rgb]{ 1,  .922,  .518}1.5903 ($\pm$0.511)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4409 ($\pm$0.518) & \cellcolor[rgb]{ .973,  .412,  .42}2.9688 ($\pm$0.228) \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}2.4516 ($\pm$0.735)     & \cellcolor[rgb]{ .388,  .745,  .482}1.2806 ($\pm$0.576) & \cellcolor[rgb]{ 1,  .922,  .518}2.2677 ($\pm$0.58)    \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}1.9903 ($\pm$0.849)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8344 ($\pm$0.768) & \cellcolor[rgb]{ .973,  .412,  .42}2.1753 ($\pm$0.796) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}2.0667 ($\pm$0.834)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8269 ($\pm$0.781) & \cellcolor[rgb]{ .973,  .412,  .42}2.1065 ($\pm$0.807) \\
+			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}1.6043 ($\pm$0.687)    & \cellcolor[rgb]{ 1,  .922,  .518}1.6602 ($\pm$0.665)    & \cellcolor[rgb]{ .973,  .412,  .42}2.7355 ($\pm$0.524) \\
+			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}1.8581 ($\pm$0.8)         & \cellcolor[rgb]{ .388,  .745,  .482}1.7806 ($\pm$0.727) & \cellcolor[rgb]{ .973,  .412,  .42}2.3613 ($\pm$0.796) \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}1.5204 ($\pm$0.581)    & \cellcolor[rgb]{ 1,  .922,  .518}1.5484 ($\pm$0.527)    & \cellcolor[rgb]{ .973,  .412,  .42}2.9312 ($\pm$0.289) \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}1.557 ($\pm$0.624)     & \cellcolor[rgb]{ 1,  .922,  .518}1.6011 ($\pm$0.591)    & \cellcolor[rgb]{ .973,  .412,  .42}2.8419 ($\pm$0.445) \\
+			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}1.9828 ($\pm$0.822)       & \cellcolor[rgb]{ .388,  .745,  .482}1.7903 ($\pm$0.848) & \cellcolor[rgb]{ .973,  .412,  .42}2.2269 ($\pm$0.715) \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ 1,  .922,  .518}1.5785 ($\pm$0.55)        & \cellcolor[rgb]{ .388,  .745,  .482}1.4935 ($\pm$0.563) & \cellcolor[rgb]{ .973,  .412,  .42}2.928 ($\pm$0.294)  \\
+			\midrule
+			\textbf{avg rank}            & \cellcolor[rgb]{ 1,  .922,  .518}1.8271 ($\pm$0.743)       & \cellcolor[rgb]{ .388,  .745,  .482}1.5773 ($\pm$0.671) & \cellcolor[rgb]{ .973,  .412,  .42}2.5955 ($\pm$0.659) \\
+			\midrule
+			\textbf{normalised avg rank} & \cellcolor[rgb]{ 1,  .922,  .518}2                         & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .973,  .412,  .42}3                   \\
 		\end{tabular}%
+	}
+\end{table}%
+
+\begin{table}[htbp]
+	\centering
+	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\label{tab:results:heuristic_pool:metrics:loss}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|lll}
+			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Loss}}                                                                                                                     \\
+			\midrule
+			\textbf{dataset}             & \multicolumn{1}{c}{\textbf{all}}                           & \multicolumn{1}{c}{\textbf{gd}}                         & \multicolumn{1}{c}{\textbf{mh}}                         \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)       & \cellcolor[rgb]{ .388,  .745,  .482}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .973,  .412,  .42}2.2942 ($\pm$0.055)  \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)     & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2637 ($\pm$0.007) \\
+			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)       & \cellcolor[rgb]{ .388,  .745,  .482}0.2164 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.2562 ($\pm$0.011)  \\
+			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}0.0651 ($\pm$0.02)        & \cellcolor[rgb]{ .388,  .745,  .482}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.1179 ($\pm$0.006)  \\
+			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)    & \cellcolor[rgb]{ 1,  .922,  .518}0.169 ($\pm$0.025)     & \cellcolor[rgb]{ .973,  .412,  .42}0.4891 ($\pm$0.077)  \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)      & \cellcolor[rgb]{ .388,  .745,  .482}0.8976 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .922,  .518}0.9137 ($\pm$0.008)    \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)       & \cellcolor[rgb]{ .973,  .412,  .42}0.1056 ($\pm$0.008)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1043 ($\pm$0.009) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ 1,  .922,  .518}0.0621 ($\pm$0.038)    \\
+			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0951 ($\pm$0.015)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1169 ($\pm$0.019)  \\
+			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2411 ($\pm$0.295)       & \cellcolor[rgb]{ .973,  .412,  .42}0.3729 ($\pm$1.119)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1809 ($\pm$0.164) \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}0.0052 ($\pm$0.012)       & \cellcolor[rgb]{ .388,  .745,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ .973,  .412,  .42}0.0774 ($\pm$0.02)   \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ 1,  .922,  .518}0.0587 ($\pm$0.003)       & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.0658 ($\pm$0.003)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)       & \cellcolor[rgb]{ .973,  .412,  .42}0.2454 ($\pm$0.134)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1947 ($\pm$0.014) \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)    & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .973,  .412,  .42}1.1666 ($\pm$0.03)   \\
+		\end{tabular}%
+
 	}
@@
 			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.4387 ($\pm$1.34)  & \cellcolor[rgb]{ .714,  .839,  .498}2.7452 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}3.0129 ($\pm$1.386)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4065 ($\pm$1.351)  & \cellcolor[rgb]{ .976,  .427,  .424}3.3968 ($\pm$1.351) \\
-			\textbf{air\_quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.7527 ($\pm$1.428) & \cellcolor[rgb]{ .882,  .886,  .51}2.9258 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9656 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.379)   & \cellcolor[rgb]{ .996,  .812,  .498}3.0419 ($\pm$1.437) \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.7527 ($\pm$1.428) & \cellcolor[rgb]{ .882,  .886,  .51}2.9258 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9656 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.379)   & \cellcolor[rgb]{ .996,  .812,  .498}3.0419 ($\pm$1.437) \\
 			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8129 ($\pm$1.41)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1591 ($\pm$1.435)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9989 ($\pm$1.42)     & \cellcolor[rgb]{ .992,  .761,  .486}3.0505 ($\pm$1.444) & \cellcolor[rgb]{ .929,  .902,  .514}2.9785 ($\pm$1.341) \\
@@
 			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}2.7978 ($\pm$1.508) & \cellcolor[rgb]{ .914,  .894,  .51}2.9387 ($\pm$1.413)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2129 ($\pm$1.452)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9613 ($\pm$1.304)    & \cellcolor[rgb]{ .988,  .663,  .471}3.0892 ($\pm$1.353) \\
-			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.8151 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.429)    & \cellcolor[rgb]{ .984,  .62,  .463}3.0925 ($\pm$1.323)  & \cellcolor[rgb]{ .973,  .412,  .42}3.128 ($\pm$1.407)   & \cellcolor[rgb]{ .682,  .827,  .498}2.9237 ($\pm$1.463) \\
-			\textbf{forest\_fires}        & \cellcolor[rgb]{ .992,  .773,  .49}3.0172 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9215 ($\pm$1.38)  & \cellcolor[rgb]{ .965,  .91,  .514}2.9806 ($\pm$1.383)  & \cellcolor[rgb]{ .973,  .412,  .42}3.0968 ($\pm$1.412)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.488)    \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.8151 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.429)    & \cellcolor[rgb]{ .984,  .62,  .463}3.0925 ($\pm$1.323)  & \cellcolor[rgb]{ .973,  .412,  .42}3.128 ($\pm$1.407)   & \cellcolor[rgb]{ .682,  .827,  .498}2.9237 ($\pm$1.463) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .992,  .773,  .49}3.0172 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9215 ($\pm$1.38)  & \cellcolor[rgb]{ .965,  .91,  .514}2.9806 ($\pm$1.383)  & \cellcolor[rgb]{ .973,  .412,  .42}3.0968 ($\pm$1.412)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.488)    \\
 			\textbf{housing}             & \cellcolor[rgb]{ .431,  .757,  .482}2.8366 ($\pm$1.404) & \cellcolor[rgb]{ .388,  .745,  .482}2.8258 ($\pm$1.38)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9753 ($\pm$1.439)    & \cellcolor[rgb]{ 1,  .91,  .518}2.9849 ($\pm$1.411)     & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.368)  \\
@@
 			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.6645 ($\pm$1.441) & \cellcolor[rgb]{ .988,  .647,  .467}3.1065 ($\pm$1.327) & \cellcolor[rgb]{ .957,  .91,  .514}3.0247 ($\pm$1.427)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0495 ($\pm$1.442)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1548 ($\pm$1.381)  \\
-			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6376 ($\pm$1.436) & \cellcolor[rgb]{ .682,  .827,  .498}2.8645 ($\pm$1.411) & \cellcolor[rgb]{ .992,  .733,  .482}3.1548 ($\pm$1.404) & \cellcolor[rgb]{ .973,  .412,  .42}3.2387 ($\pm$1.397)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1043 ($\pm$1.34)     \\
-			\textbf{wine\_quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.5505 ($\pm$1.317) & \cellcolor[rgb]{ .62,  .812,  .494}2.7817 ($\pm$1.415)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1581 ($\pm$1.384)    & \cellcolor[rgb]{ 1,  .855,  .506}3.1806 ($\pm$1.394)    & \cellcolor[rgb]{ .973,  .412,  .42}3.329 ($\pm$1.414)   \\
+			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6376 ($\pm$1.436) & \cellcolor[rgb]{ .682,  .827,  .498}2.8645 ($\pm$1.411) & \cellcolor[rgb]{ .992,  .733,  .482}3.1548 ($\pm$1.404) & \cellcolor[rgb]{ .973,  .412,  .42}3.2387 ($\pm$1.397)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1043 ($\pm$1.34)     \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.5505 ($\pm$1.317) & \cellcolor[rgb]{ .62,  .812,  .494}2.7817 ($\pm$1.415)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1581 ($\pm$1.384)    & \cellcolor[rgb]{ 1,  .855,  .506}3.1806 ($\pm$1.394)    & \cellcolor[rgb]{ .973,  .412,  .42}3.329 ($\pm$1.414)   \\
 			\midrule
@@
 			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088) & \cellcolor[rgb]{ .612,  .808,  .494}2.1592 ($\pm$0.278) & \cellcolor[rgb]{ 1,  .922,  .518}2.3321 ($\pm$0.446)    & \cellcolor[rgb]{ 1,  .91,  .518}2.3345 ($\pm$0.357)    & \cellcolor[rgb]{ .973,  .412,  .42}2.4188 ($\pm$0.473)  \\
-			\textbf{air\_quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 ($\pm$0.016)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2701 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .878,  .51}0.2736 ($\pm$0.014)     & \cellcolor[rgb]{ .973,  .412,  .42}0.2808 ($\pm$0.026) & \cellcolor[rgb]{ .702,  .835,  .498}0.2715 ($\pm$0.011) \\
+			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 ($\pm$0.016)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2701 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .878,  .51}0.2736 ($\pm$0.014)     & \cellcolor[rgb]{ .973,  .412,  .42}0.2808 ($\pm$0.026) & \cellcolor[rgb]{ .702,  .835,  .498}0.2715 ($\pm$0.011) \\
 			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)  & \cellcolor[rgb]{ .992,  .729,  .482}0.2356 ($\pm$0.029) & \cellcolor[rgb]{ .388,  .745,  .482}0.2268 ($\pm$0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.2294 ($\pm$0.019)   & \cellcolor[rgb]{ .608,  .808,  .494}0.2278 ($\pm$0.012) \\
@@
 			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)   & \cellcolor[rgb]{ 1,  .922,  .518}0.9954 ($\pm$0.103)    & \cellcolor[rgb]{ .992,  .776,  .49}1.0826 ($\pm$0.3)    & \cellcolor[rgb]{ .525,  .784,  .49}0.9893 ($\pm$0.105) & \cellcolor[rgb]{ .388,  .745,  .482}0.9875 ($\pm$0.078) \\
-			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1046 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1077 ($\pm$0.009)    & \cellcolor[rgb]{ .882,  .886,  .51}0.1071 ($\pm$0.011)  & \cellcolor[rgb]{ .973,  .412,  .42}0.1104 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .886,  .514}0.1079 ($\pm$0.008)    \\
-			\textbf{forest\_fires}        & \cellcolor[rgb]{ 1,  .922,  .518}0.081 ($\pm$0.069)     & \cellcolor[rgb]{ .388,  .745,  .482}0.0694 ($\pm$0.059) & \cellcolor[rgb]{ .737,  .843,  .502}0.0761 ($\pm$0.056) & \cellcolor[rgb]{ .984,  .569,  .451}0.084 ($\pm$0.07)  & \cellcolor[rgb]{ .973,  .412,  .42}0.0854 ($\pm$0.065)  \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1046 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1077 ($\pm$0.009)    & \cellcolor[rgb]{ .882,  .886,  .51}0.1071 ($\pm$0.011)  & \cellcolor[rgb]{ .973,  .412,  .42}0.1104 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .886,  .514}0.1079 ($\pm$0.008)    \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}0.081 ($\pm$0.069)     & \cellcolor[rgb]{ .388,  .745,  .482}0.0694 ($\pm$0.059) & \cellcolor[rgb]{ .737,  .843,  .502}0.0761 ($\pm$0.056) & \cellcolor[rgb]{ .984,  .569,  .451}0.084 ($\pm$0.07)  & \cellcolor[rgb]{ .973,  .412,  .42}0.0854 ($\pm$0.065)  \\
 			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.0985 ($\pm$0.026)    & \cellcolor[rgb]{ .412,  .749,  .482}0.0943 ($\pm$0.016) & \cellcolor[rgb]{ 1,  .906,  .518}0.0987 ($\pm$0.017)   & \cellcolor[rgb]{ .973,  .412,  .42}0.1038 ($\pm$0.017)  \\
@@
 			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .82,  .867,  .506}0.0598 ($\pm$0.003)  & \cellcolor[rgb]{ .988,  .694,  .475}0.0606 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0602 ($\pm$0.003)   & \cellcolor[rgb]{ .973,  .412,  .42}0.0612 ($\pm$0.003)  \\
-			\textbf{student\_performance} & \cellcolor[rgb]{ .973,  .412,  .42}0.2359 ($\pm$0.102)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2007 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .922,  .518}0.2092 ($\pm$0.039)    & \cellcolor[rgb]{ .573,  .796,  .49}0.2033 ($\pm$0.037) & \cellcolor[rgb]{ 1,  .922,  .518}0.2091 ($\pm$0.054)    \\
-			\textbf{wine\_quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .553,  .792,  .49}1.0864 ($\pm$0.034)  & \cellcolor[rgb]{ .973,  .412,  .42}1.1083 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .922,  .518}1.0961 ($\pm$0.027)   & \cellcolor[rgb]{ .976,  .463,  .431}1.1071 ($\pm$0.039) \\
+			\textbf{student performance} & \cellcolor[rgb]{ .973,  .412,  .42}0.2359 ($\pm$0.102)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2007 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .922,  .518}0.2092 ($\pm$0.039)    & \cellcolor[rgb]{ .573,  .796,  .49}0.2033 ($\pm$0.037) & \cellcolor[rgb]{ 1,  .922,  .518}0.2091 ($\pm$0.054)    \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .553,  .792,  .49}1.0864 ($\pm$0.034)  & \cellcolor[rgb]{ .973,  .412,  .42}1.1083 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .922,  .518}1.0961 ($\pm$0.027)   & \cellcolor[rgb]{ .976,  .463,  .431}1.1071 ($\pm$0.039) \\
 		\end{tabular}%
@@
 			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}3.1677 ($\pm$1.319)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8613 ($\pm$1.459) & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.399)    & \cellcolor[rgb]{ .863,  .882,  .51}2.9667 ($\pm$1.455)  & \cellcolor[rgb]{ 1,  .89,  .514}3.0075 ($\pm$1.421)     \\
-			\textbf{air\_quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.1312 ($\pm$1.347)  & \cellcolor[rgb]{ .91,  .894,  .51}3.0376 ($\pm$1.357)   & \cellcolor[rgb]{ .388,  .745,  .482}2.5914 ($\pm$1.465) & \cellcolor[rgb]{ .98,  .498,  .439}3.128 ($\pm$1.336)   & \cellcolor[rgb]{ 1,  .922,  .518}3.1118 ($\pm$1.487)    \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.1312 ($\pm$1.347)  & \cellcolor[rgb]{ .91,  .894,  .51}3.0376 ($\pm$1.357)   & \cellcolor[rgb]{ .388,  .745,  .482}2.5914 ($\pm$1.465) & \cellcolor[rgb]{ .98,  .498,  .439}3.128 ($\pm$1.336)   & \cellcolor[rgb]{ 1,  .922,  .518}3.1118 ($\pm$1.487)    \\
 			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8591 ($\pm$1.344) & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.432)    & \cellcolor[rgb]{ .522,  .78,  .486}2.8882 ($\pm$1.41)   & \cellcolor[rgb]{ .996,  .804,  .498}3.0441 ($\pm$1.415) & \cellcolor[rgb]{ .973,  .412,  .42}3.2183 ($\pm$1.442)  \\
@@
 			\textbf{diabetic}            & \cellcolor[rgb]{ .996,  .918,  .514}2.8914 ($\pm$1.349) & \cellcolor[rgb]{ .388,  .745,  .482}2.6269 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.4151 ($\pm$1.365)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8925 ($\pm$1.362)    & \cellcolor[rgb]{ .988,  .647,  .467}3.1742 ($\pm$1.449) \\
-			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .98,  .541,  .447}3.1516 ($\pm$1.436)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.475) & \cellcolor[rgb]{ .973,  .412,  .42}3.2043 ($\pm$1.299)  & \cellcolor[rgb]{ .749,  .847,  .502}2.8957 ($\pm$1.358) \\
-			\textbf{forest\_fires}        & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.277)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1806 ($\pm$1.304)  & \cellcolor[rgb]{ .58,  .8,  .49}2.8559 ($\pm$1.356)     & \cellcolor[rgb]{ .992,  .773,  .49}3.1215 ($\pm$1.502)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7452 ($\pm$1.563) \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .98,  .541,  .447}3.1516 ($\pm$1.436)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.475) & \cellcolor[rgb]{ .973,  .412,  .42}3.2043 ($\pm$1.299)  & \cellcolor[rgb]{ .749,  .847,  .502}2.8957 ($\pm$1.358) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.277)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1806 ($\pm$1.304)  & \cellcolor[rgb]{ .58,  .8,  .49}2.8559 ($\pm$1.356)     & \cellcolor[rgb]{ .992,  .773,  .49}3.1215 ($\pm$1.502)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7452 ($\pm$1.563) \\
 			\textbf{housing}             & \cellcolor[rgb]{ .984,  .918,  .514}2.9011 ($\pm$1.494) & \cellcolor[rgb]{ .388,  .745,  .482}2.8527 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}2.9022 ($\pm$1.397)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3108 ($\pm$1.324)  & \cellcolor[rgb]{ .992,  .761,  .486}3.0333 ($\pm$1.483) \\
@@
 			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.5645 ($\pm$1.484) & \cellcolor[rgb]{ .898,  .89,  .51}2.8925 ($\pm$1.343)   & \cellcolor[rgb]{ .973,  .412,  .42}3.5065 ($\pm$1.219)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0796 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}2.957 ($\pm$1.455)     \\
-			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6624 ($\pm$1.312) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.407)     & \cellcolor[rgb]{ .988,  .643,  .467}3.1892 ($\pm$1.382) & \cellcolor[rgb]{ .612,  .808,  .494}2.7978 ($\pm$1.47)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3215 ($\pm$1.394)  \\
-			\textbf{wine\_quality}        & \cellcolor[rgb]{ .98,  .494,  .439}3.1871 ($\pm$1.308)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .922,  .518}3.014 ($\pm$1.371)     & \cellcolor[rgb]{ .882,  .886,  .51}2.9419 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.43)   \\
+			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6624 ($\pm$1.312) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.407)     & \cellcolor[rgb]{ .988,  .643,  .467}3.1892 ($\pm$1.382) & \cellcolor[rgb]{ .612,  .808,  .494}2.7978 ($\pm$1.47)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3215 ($\pm$1.394)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .98,  .494,  .439}3.1871 ($\pm$1.308)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .922,  .518}3.014 ($\pm$1.371)     & \cellcolor[rgb]{ .882,  .886,  .51}2.9419 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.43)   \\
 			\midrule
@@
 			\textbf{abalone}             & \cellcolor[rgb]{ .631,  .816,  .494}2.0587 (+-0.088) & \cellcolor[rgb]{ .388,  .745,  .482}2.0422 (+-0.094) & \cellcolor[rgb]{ .996,  .792,  .494}2.0922 (+-0.152) & \cellcolor[rgb]{ 1,  .922,  .518}2.0833 (+-0.136)    & \cellcolor[rgb]{ .973,  .412,  .42}2.1177 (+-0.259)  \\
-			\textbf{air\_quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 (+-0.016)  & \cellcolor[rgb]{ .902,  .89,  .51}0.2678 (+-0.015)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2644 (+-0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.2684 (+-0.013)    & \cellcolor[rgb]{ 1,  .882,  .51}0.2688 (+-0.017)     \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 (+-0.016)  & \cellcolor[rgb]{ .902,  .89,  .51}0.2678 (+-0.015)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2644 (+-0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.2684 (+-0.013)    & \cellcolor[rgb]{ 1,  .882,  .51}0.2688 (+-0.017)     \\
 			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 (+-0.065)    & \cellcolor[rgb]{ .973,  .412,  .42}0.2645 (+-0.171)  & \cellcolor[rgb]{ .51,  .78,  .486}0.238 (+-0.047)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2361 (+-0.031) & \cellcolor[rgb]{ .996,  .812,  .498}0.2498 (+-0.047) \\
@@
 			\textbf{diabetic}            & \cellcolor[rgb]{ .878,  .886,  .51}1.2983 (+-0.66)   & \cellcolor[rgb]{ .988,  .651,  .467}1.4981 (+-2.41)  & \cellcolor[rgb]{ .973,  .412,  .42}1.6172 (+-1.527)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0347 (+-0.231) & \cellcolor[rgb]{ 1,  .922,  .518}1.3627 (+-1.145)    \\
-			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .988,  .647,  .467}0.1046 (+-0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1028 (+-0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1024 (+-0.009) & \cellcolor[rgb]{ .973,  .412,  .42}0.1061 (+-0.009)  & \cellcolor[rgb]{ .643,  .816,  .494}0.1026 (+-0.009) \\
-			\textbf{forest\_fires}        & \cellcolor[rgb]{ .973,  .914,  .514}0.081 (+-0.069)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0819 (+-0.062)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0591 (+-0.046) & \cellcolor[rgb]{ .973,  .412,  .42}0.0845 (+-0.077)  & \cellcolor[rgb]{ 1,  .867,  .51}0.0822 (+-0.07)      \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .988,  .647,  .467}0.1046 (+-0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1028 (+-0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1024 (+-0.009) & \cellcolor[rgb]{ .973,  .412,  .42}0.1061 (+-0.009)  & \cellcolor[rgb]{ .643,  .816,  .494}0.1026 (+-0.009) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .914,  .514}0.081 (+-0.069)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0819 (+-0.062)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0591 (+-0.046) & \cellcolor[rgb]{ .973,  .412,  .42}0.0845 (+-0.077)  & \cellcolor[rgb]{ 1,  .867,  .51}0.0822 (+-0.07)      \\
 			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 (+-0.017) & \cellcolor[rgb]{ .996,  .82,  .498}0.0974 (+-0.021)  & \cellcolor[rgb]{ .835,  .875,  .506}0.0961 (+-0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.0995 (+-0.016)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0969 (+-0.018)    \\
@@
 			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 (+-0.003) & \cellcolor[rgb]{ 1,  .867,  .51}0.0594 (+-0.002)     & \cellcolor[rgb]{ .973,  .412,  .42}0.0602 (+-0.002)  & \cellcolor[rgb]{ .898,  .89,  .51}0.0592 (+-0.002)   & \cellcolor[rgb]{ 1,  .922,  .518}0.0593 (+-0.003)    \\
-			\textbf{student\_performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 (+-0.102)    & \cellcolor[rgb]{ .678,  .827,  .498}0.2303 (+-0.095) & \cellcolor[rgb]{ .988,  .69,  .475}0.2551 (+-0.109)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2251 (+-0.088) & \cellcolor[rgb]{ .973,  .412,  .42}0.2777 (+-0.116)  \\
-			\textbf{wine\_quality}        & \cellcolor[rgb]{ .98,  .525,  .443}1.0827 (+-0.026)  & \cellcolor[rgb]{ 1,  .922,  .518}1.0799 (+-0.031)    & \cellcolor[rgb]{ .925,  .898,  .51}1.0794 (+-0.021)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0757 (+-0.027) & \cellcolor[rgb]{ .973,  .412,  .42}1.0835 (+-0.029)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 (+-0.102)    & \cellcolor[rgb]{ .678,  .827,  .498}0.2303 (+-0.095) & \cellcolor[rgb]{ .988,  .69,  .475}0.2551 (+-0.109)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2251 (+-0.088) & \cellcolor[rgb]{ .973,  .412,  .42}0.2777 (+-0.116)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .98,  .525,  .443}1.0827 (+-0.026)  & \cellcolor[rgb]{ 1,  .922,  .518}1.0799 (+-0.031)    & \cellcolor[rgb]{ .925,  .898,  .51}1.0794 (+-0.021)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0757 (+-0.027) & \cellcolor[rgb]{ .973,  .412,  .42}1.0835 (+-0.029)  \\
 		\end{tabular}%
@@
 			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}4.3548 ($\pm$0.976)  & \cellcolor[rgb]{ 1,  .894,  .514}2.8473 ($\pm$1.288)    & \cellcolor[rgb]{ 1,  .922,  .518}2.7505 ($\pm$1.262)    & \cellcolor[rgb]{ .557,  .792,  .49}2.5602 ($\pm$1.299)  & \cellcolor[rgb]{ .388,  .745,  .482}2.4871 ($\pm$1.318) \\
-			\textbf{air\_quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.7355 ($\pm$1.405)  & \cellcolor[rgb]{ .984,  .631,  .463}3.4075 ($\pm$1.379) & \cellcolor[rgb]{ 1,  .922,  .518}2.9688 ($\pm$1.278)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4237 ($\pm$1.228) & \cellcolor[rgb]{ .431,  .757,  .482}2.4645 ($\pm$1.291) \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.7355 ($\pm$1.405)  & \cellcolor[rgb]{ .984,  .631,  .463}3.4075 ($\pm$1.379) & \cellcolor[rgb]{ 1,  .922,  .518}2.9688 ($\pm$1.278)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4237 ($\pm$1.228) & \cellcolor[rgb]{ .431,  .757,  .482}2.4645 ($\pm$1.291) \\
 			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}4.5677 ($\pm$0.704)  & \cellcolor[rgb]{ .988,  .635,  .463}3.6323 ($\pm$1.127) & \cellcolor[rgb]{ 1,  .922,  .518}2.4237 ($\pm$1.133)    & \cellcolor[rgb]{ .627,  .812,  .494}2.2462 ($\pm$1.114) & \cellcolor[rgb]{ .388,  .745,  .482}2.1301 ($\pm$1.096) \\
@@
 			\textbf{diabetic}            & \cellcolor[rgb]{ 1,  .859,  .506}3.0129 ($\pm$1.048)    & \cellcolor[rgb]{ .973,  .412,  .42}4.4624 ($\pm$0.869)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7957 ($\pm$1.175)    & \cellcolor[rgb]{ .827,  .871,  .506}2.6065 ($\pm$1.439) & \cellcolor[rgb]{ .388,  .745,  .482}2.1226 ($\pm$1.264) \\
-			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}3.7484 ($\pm$1.238)  & \cellcolor[rgb]{ .996,  .851,  .506}3.1376 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}3.0344 ($\pm$1.406)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4656 ($\pm$1.304) & \cellcolor[rgb]{ .545,  .788,  .49}2.614 ($\pm$1.432)   \\
-			\textbf{forest\_fires}        & \cellcolor[rgb]{ .973,  .412,  .42}3.8194 ($\pm$1.433)  & \cellcolor[rgb]{ .992,  .706,  .478}3.272 ($\pm$1.248)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8656 ($\pm$1.346)    & \cellcolor[rgb]{ .953,  .906,  .514}2.8194 ($\pm$1.305) & \cellcolor[rgb]{ .388,  .745,  .482}2.2237 ($\pm$1.219) \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}3.7484 ($\pm$1.238)  & \cellcolor[rgb]{ .996,  .851,  .506}3.1376 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}3.0344 ($\pm$1.406)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4656 ($\pm$1.304) & \cellcolor[rgb]{ .545,  .788,  .49}2.614 ($\pm$1.432)   \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}3.8194 ($\pm$1.433)  & \cellcolor[rgb]{ .992,  .706,  .478}3.272 ($\pm$1.248)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8656 ($\pm$1.346)    & \cellcolor[rgb]{ .953,  .906,  .514}2.8194 ($\pm$1.305) & \cellcolor[rgb]{ .388,  .745,  .482}2.2237 ($\pm$1.219) \\
 			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}4.1892 ($\pm$1.099)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0172 ($\pm$1.288) & \cellcolor[rgb]{ .624,  .812,  .494}2.5871 ($\pm$1.354) & \cellcolor[rgb]{ .388,  .745,  .482}2.5312 ($\pm$1.265) & \cellcolor[rgb]{ 1,  .922,  .518}2.6753 ($\pm$1.34)     \\
@@
 			\textbf{parkinsons}          & \cellcolor[rgb]{ .973,  .412,  .42}4.7645 ($\pm$0.756)  & \cellcolor[rgb]{ .992,  .769,  .49}3.1882 ($\pm$1.021)  & \cellcolor[rgb]{ .49,  .773,  .486}2.2957 ($\pm$1.209)  & \cellcolor[rgb]{ 1,  .922,  .518}2.4968 ($\pm$1.128)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2548 ($\pm$1.097) \\
-			\textbf{student\_performance} & \cellcolor[rgb]{ .976,  .431,  .424}3.971 ($\pm$1.094)  & \cellcolor[rgb]{ .973,  .412,  .42}4.0226 ($\pm$1.12)   & \cellcolor[rgb]{ 1,  .922,  .518}2.4774 ($\pm$1.221)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2495 ($\pm$1.2)   & \cellcolor[rgb]{ .467,  .765,  .486}2.2796 ($\pm$1.132) \\
-			\textbf{wine\_quality}        & \cellcolor[rgb]{ .973,  .412,  .42}4.0688 ($\pm$1.122)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9204 ($\pm$1.293)    & \cellcolor[rgb]{ 1,  .906,  .518}2.9559 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4032 ($\pm$1.378) & \cellcolor[rgb]{ .678,  .827,  .498}2.6516 ($\pm$1.28)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ .976,  .431,  .424}3.971 ($\pm$1.094)  & \cellcolor[rgb]{ .973,  .412,  .42}4.0226 ($\pm$1.12)   & \cellcolor[rgb]{ 1,  .922,  .518}2.4774 ($\pm$1.221)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2495 ($\pm$1.2)   & \cellcolor[rgb]{ .467,  .765,  .486}2.2796 ($\pm$1.132) \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}4.0688 ($\pm$1.122)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9204 ($\pm$1.293)    & \cellcolor[rgb]{ 1,  .906,  .518}2.9559 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4032 ($\pm$1.378) & \cellcolor[rgb]{ .678,  .827,  .498}2.6516 ($\pm$1.28)  \\
 			\midrule
@@
 			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}2.737 ($\pm$0.507)   & \cellcolor[rgb]{ 1,  .922,  .518}2.0907 ($\pm$0.113)    & \cellcolor[rgb]{ .545,  .788,  .49}2.0587 ($\pm$0.088)  & \cellcolor[rgb]{ .388,  .745,  .482}2.0475 ($\pm$0.103) & \cellcolor[rgb]{ 1,  .906,  .518}2.1139 ($\pm$0.336)    \\
-			\textbf{air\_quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.3003 ($\pm$0.046)  & \cellcolor[rgb]{ .992,  .725,  .482}0.2835 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 ($\pm$0.016)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2619 ($\pm$0.013) & \cellcolor[rgb]{ .486,  .773,  .486}0.2637 ($\pm$0.016) \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.3003 ($\pm$0.046)  & \cellcolor[rgb]{ .992,  .725,  .482}0.2835 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 ($\pm$0.016)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2619 ($\pm$0.013) & \cellcolor[rgb]{ .486,  .773,  .486}0.2637 ($\pm$0.016) \\
 			\textbf{bank}                & \cellcolor[rgb]{ .984,  .596,  .455}0.2933 ($\pm$0.033) & \cellcolor[rgb]{ .973,  .412,  .42}0.3198 ($\pm$0.18)   & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .553,  .792,  .49}0.2299 ($\pm$0.032)  & \cellcolor[rgb]{ .388,  .745,  .482}0.224 ($\pm$0.018)  \\
@@
 			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}0.9624 ($\pm$0.043) & \cellcolor[rgb]{ .973,  .412,  .42}3.7821 ($\pm$4.993)  & \cellcolor[rgb]{ 1,  .914,  .518}1.2983 ($\pm$0.66)     & \cellcolor[rgb]{ 1,  .922,  .518}1.2541 ($\pm$0.868)    & \cellcolor[rgb]{ .482,  .773,  .486}1.0085 ($\pm$0.251) \\
-			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}0.1091 ($\pm$0.01)   & \cellcolor[rgb]{ 1,  .922,  .518}0.1043 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .894,  .514}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1013 ($\pm$0.008) & \cellcolor[rgb]{ .549,  .792,  .49}0.1021 ($\pm$0.008)  \\
-			\textbf{forest\_fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.1253 ($\pm$0.087)  & \cellcolor[rgb]{ .988,  .702,  .478}0.1002 ($\pm$0.064) & \cellcolor[rgb]{ 1,  .922,  .518}0.081 ($\pm$0.069)     & \cellcolor[rgb]{ .647,  .82,  .494}0.0681 ($\pm$0.055)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.056) \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}0.1091 ($\pm$0.01)   & \cellcolor[rgb]{ 1,  .922,  .518}0.1043 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .894,  .514}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1013 ($\pm$0.008) & \cellcolor[rgb]{ .549,  .792,  .49}0.1021 ($\pm$0.008)  \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.1253 ($\pm$0.087)  & \cellcolor[rgb]{ .988,  .702,  .478}0.1002 ($\pm$0.064) & \cellcolor[rgb]{ 1,  .922,  .518}0.081 ($\pm$0.069)     & \cellcolor[rgb]{ .647,  .82,  .494}0.0681 ($\pm$0.055)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.056) \\
 			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}0.1268 ($\pm$0.025)  & \cellcolor[rgb]{ 1,  .902,  .514}0.0974 ($\pm$0.017)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.0961 ($\pm$0.026)    & \cellcolor[rgb]{ .729,  .843,  .502}0.0952 ($\pm$0.02)  \\
@@
 			\textbf{parkinsons}          & \cellcolor[rgb]{ .973,  .412,  .42}0.0872 ($\pm$0.018)  & \cellcolor[rgb]{ 1,  .886,  .514}0.0609 ($\pm$0.004)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0587 ($\pm$0.003)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0584 ($\pm$0.002) & \cellcolor[rgb]{ .482,  .769,  .486}0.0585 ($\pm$0.003) \\
-			\textbf{student\_performance} & \cellcolor[rgb]{ .973,  .412,  .42}0.4376 ($\pm$0.108)  & \cellcolor[rgb]{ .98,  .518,  .443}0.397 ($\pm$0.13)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)    & \cellcolor[rgb]{ .784,  .859,  .502}0.223 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1991 ($\pm$0.064) \\
-			\textbf{wine\_quality}        & \cellcolor[rgb]{ .973,  .412,  .42}1.1183 ($\pm$0.031)  & \cellcolor[rgb]{ 1,  .922,  .518}1.081 ($\pm$0.023)     & \cellcolor[rgb]{ 1,  .898,  .514}1.0827 ($\pm$0.026)    & \cellcolor[rgb]{ .388,  .745,  .482}1.0711 ($\pm$0.028) & \cellcolor[rgb]{ .498,  .776,  .486}1.0729 ($\pm$0.022) \\
+			\textbf{student performance} & \cellcolor[rgb]{ .973,  .412,  .42}0.4376 ($\pm$0.108)  & \cellcolor[rgb]{ .98,  .518,  .443}0.397 ($\pm$0.13)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)    & \cellcolor[rgb]{ .784,  .859,  .502}0.223 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1991 ($\pm$0.064) \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}1.1183 ($\pm$0.031)  & \cellcolor[rgb]{ 1,  .922,  .518}1.081 ($\pm$0.023)     & \cellcolor[rgb]{ 1,  .898,  .514}1.0827 ($\pm$0.026)    & \cellcolor[rgb]{ .388,  .745,  .482}1.0711 ($\pm$0.028) & \cellcolor[rgb]{ .498,  .776,  .486}1.0729 ($\pm$0.022) \\
 		\end{tabular}%
@@
 	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:replay:metrics}%
+	\label{tab:results:replay:metrics:rank}%
 	\par\bigskip
 	\resizebox{\textwidth}{!}{
-		\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}  &                                                                           &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
-			\cmidrule{1-2}                      &                                     &                                                                           &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{replay}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 &                                 &                 &                 \\
-			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}      &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                 &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                      & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}    & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                 & 3.0258                                                                    & 1.3816          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6785}          & 1.4551          & 930                             & 3.1968                                                                    & 1.3460          & 930                             & 3.0903                                                                    & 1.3851          & 930                             & 3.0086          & 1.4503          \\
-			adult                               & 930                                 & 2.8785                                                                    & 1.3824          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8269}          & 1.3595          & 930                             & 2.9430                                                                    & 1.4804          & 930                             & 3.0538                                                                    & 1.3714          & 930                             & 2.9645          & 1.5686          \\
-			air quality                         & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8742} & 1.3851          & 930                            & 3.0151                                                                             & 1.4970          & 930                             & 2.9978                                                                    & 1.4294          & 930                             & 2.9505                                                                    & 1.2966          & 930                             & 3.1624          & 1.4430          \\
-			bank                                & 930                                 & 2.9484                                                                    & 1.4597          & 930                            & 3.0570                                                                             & 1.4731          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8602} & 1.3439          & 930                             & 3.0172                                                                    & 1.4202          & 930                             & 3.1172          & 1.3592          \\
-			bike                                & 930                                 & 2.9602                                                                    & 1.2739          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7366}          & 1.3401          & 930                             & 3.1452                                                                    & 1.4478          & 930                             & 2.9226                                                                    & 1.4174          & 930                             & 3.2355          & 1.5274          \\
-			car                                 & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7054} & 1.3572          & 930                            & 2.8376                                                                             & 1.3898          & 930                             & 3.0763                                                                    & 1.3723          & 930                             & 3.3269                                                                    & 1.4631          & 930                             & 3.0538          & 1.4086          \\
-			diabetic                            & 930                                 & 3.2473                                                                    & 1.3690          & 930                            & 3.3247                                                                             & 1.4058          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5935} & 1.3719          & 930                             & 2.8075                                                                    & 1.3844          & 930                             & 3.0269          & 1.4113          \\
-			fish toxicity                       & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7269} & 1.4190          & 930                            & 3.0785                                                                             & 1.4896          & 930                             & 3.1774                                                                    & 1.3980          & 930                             & 2.9892                                                                    & 1.3865          & 930                             & 3.0280          & 1.3373          \\
-			forest fires                        & 930                                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8054} & 1.4926          & 930                            & 2.9151                                                                             & 1.3812          & 930                             & 2.9914                                                                    & 1.4081          & 930                             & 3.0591                                                                    & 1.4111          & 930                             & 3.2290          & 1.3416          \\
-			housing                             & 930                                 & 3.1548                                                                    & 1.3007          & 930                            & 2.9774                                                                             & 1.4068          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8548} & 1.4501          & 930                             & 3.0355                                                                    & 1.4898          & 930                             & 2.9774          & 1.4037          \\
-			iris                                & 930                                 & 3.0720                                                                    & 1.3757          & 930                            & 3.1581                                                                             & 1.4187          & 930                             & 3.2204                                                                    & 1.3919          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6183} & 1.3964          & 930                             & 2.9312          & 1.4102          \\
-			mushroom                            & 930                                 & 3.0538                                                                    & 1.3243          & 930                            & 3.1430                                                                             & 1.4369          & 930                             & 3.0419                                                                    & 1.4140          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8613} & 1.3823          & 930                             & 2.8957          & 1.4966          \\
-			parkinsons                          & 930                                 & 3.1720                                                                    & 1.3719          & 930                            & 2.8430                                                                             & 1.2437          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6731} & 1.4535          & 930                             & 3.1172                                                                    & 1.4189          & 930                             & 3.1946          & 1.4977          \\
-			student performance                 & 930                                 & 3.0398                                                                    & 1.3684          & 930                            & 2.9226                                                                             & 1.4106          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6548} & 1.4028          & 930                             & 3.0935                                                                    & 1.3225          & 930                             & 3.2892          & 1.4874          \\
-			wine quality                        & 930                                 & 3.1742                                                                    & 1.4300          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7323}          & 1.4556          & 930                             & 3.1581                                                                    & 1.4179          & 930                             & 3.0419                                                                    & 1.3565          & 930                             & 2.8935          & 1.3624          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                      & \textbf{2.9892}                                                           & \textbf{1.3892} & \textbf{13950}                 & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.9497}} & \textbf{1.4224} & \textbf{13950}                  & \textbf{2.9723}                                                           & \textbf{1.4224} & \textbf{13950}                  & \textbf{2.9990}                                                           & \textbf{1.4021} & \textbf{13950}                  & \textbf{3.0672} & \textbf{1.4400} \\
+		\begin{tabular}{r|ccccc}
+			                             & \multicolumn{5}{c}{\textbf{Replay - Average Rank}}                                                                                                                                                                                                                                              \\
+			\midrule
+			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}3.0258 ($\pm$1.382)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6785 ($\pm$1.455) & \cellcolor[rgb]{ .973,  .412,  .42}3.1968 ($\pm$1.346)  & \cellcolor[rgb]{ .992,  .729,  .482}3.0903 ($\pm$1.385) & \cellcolor[rgb]{ .969,  .91,  .514}3.0086 ($\pm$1.45)   \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.8742 ($\pm$1.385) & \cellcolor[rgb]{ 1,  .871,  .51}3.0151 ($\pm$1.497)     & \cellcolor[rgb]{ 1,  .922,  .518}2.9978 ($\pm$1.429)    & \cellcolor[rgb]{ .765,  .851,  .502}2.9505 ($\pm$1.297) & \cellcolor[rgb]{ .973,  .412,  .42}3.1624 ($\pm$1.443)  \\
+			\textbf{bank}                & \cellcolor[rgb]{ .729,  .843,  .502}2.9484 ($\pm$1.46)  & \cellcolor[rgb]{ .992,  .722,  .482}3.057 ($\pm$1.473)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8602 ($\pm$1.344) & \cellcolor[rgb]{ 1,  .922,  .518}3.0172 ($\pm$1.42)     & \cellcolor[rgb]{ .973,  .412,  .42}3.1172 ($\pm$1.359)  \\
+			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}2.9602 ($\pm$1.274)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7366 ($\pm$1.34)  & \cellcolor[rgb]{ .984,  .58,  .455}3.1452 ($\pm$1.448)  & \cellcolor[rgb]{ .894,  .89,  .51}2.9226 ($\pm$1.417)   & \cellcolor[rgb]{ .973,  .412,  .42}3.2355 ($\pm$1.527)  \\
+			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.7054 ($\pm$1.357) & \cellcolor[rgb]{ .62,  .812,  .494}2.8376 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .882,  .51}3.0763 ($\pm$1.372)     & \cellcolor[rgb]{ .973,  .412,  .42}3.3269 ($\pm$1.463)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0538 ($\pm$1.409)    \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .98,  .545,  .447}3.2473 ($\pm$1.369)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3247 ($\pm$1.406)  & \cellcolor[rgb]{ .388,  .745,  .482}2.5935 ($\pm$1.372) & \cellcolor[rgb]{ .69,  .831,  .498}2.8075 ($\pm$1.384)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0269 ($\pm$1.411)    \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.7269 ($\pm$1.419) & \cellcolor[rgb]{ .992,  .753,  .486}3.0785 ($\pm$1.49)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1774 ($\pm$1.398)  & \cellcolor[rgb]{ .918,  .898,  .51}2.9892 ($\pm$1.386)  & \cellcolor[rgb]{ 1,  .922,  .518}3.028 ($\pm$1.337)     \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8054 ($\pm$1.493) & \cellcolor[rgb]{ .745,  .847,  .502}2.9151 ($\pm$1.381) & \cellcolor[rgb]{ 1,  .922,  .518}2.9914 ($\pm$1.408)    & \cellcolor[rgb]{ .996,  .776,  .49}3.0591 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.229 ($\pm$1.342)   \\
+			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}3.1548 ($\pm$1.301)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.407)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8548 ($\pm$1.45)  & \cellcolor[rgb]{ .992,  .757,  .486}3.0355 ($\pm$1.49)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.404)    \\
+			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}3.072 ($\pm$1.376)     & \cellcolor[rgb]{ .984,  .627,  .463}3.1581 ($\pm$1.419) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.392)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6183 ($\pm$1.396) & \cellcolor[rgb]{ .808,  .867,  .506}2.9312 ($\pm$1.41)  \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .863,  .51}3.0538 ($\pm$1.324)     & \cellcolor[rgb]{ .973,  .412,  .42}3.143 ($\pm$1.437)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0419 ($\pm$1.414)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8613 ($\pm$1.382) & \cellcolor[rgb]{ .502,  .776,  .486}2.8957 ($\pm$1.497) \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .984,  .561,  .451}3.172 ($\pm$1.372)  & \cellcolor[rgb]{ .62,  .812,  .494}2.843 ($\pm$1.244)   & \cellcolor[rgb]{ .388,  .745,  .482}2.6731 ($\pm$1.453) & \cellcolor[rgb]{ 1,  .922,  .518}3.1172 ($\pm$1.419)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1946 ($\pm$1.498)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}3.0398 ($\pm$1.368)    & \cellcolor[rgb]{ .812,  .867,  .506}2.9226 ($\pm$1.411) & \cellcolor[rgb]{ .388,  .745,  .482}2.6548 ($\pm$1.403) & \cellcolor[rgb]{ .996,  .812,  .498}3.0935 ($\pm$1.323) & \cellcolor[rgb]{ .973,  .412,  .42}3.2892 ($\pm$1.487)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}3.1742 ($\pm$1.43)   & \cellcolor[rgb]{ .388,  .745,  .482}2.7323 ($\pm$1.456) & \cellcolor[rgb]{ .976,  .475,  .435}3.1581 ($\pm$1.418) & \cellcolor[rgb]{ 1,  .922,  .518}3.0419 ($\pm$1.356)    & \cellcolor[rgb]{ .706,  .835,  .498}2.8935 ($\pm$1.362) \\
+			\midrule
+			\textbf{avg rank}            & \cellcolor[rgb]{ 1,  .91,  .518}2.9972 ($\pm$1.389)     & \cellcolor[rgb]{ .388,  .745,  .482}2.9585 ($\pm$1.426) & \cellcolor[rgb]{ .651,  .82,  .494}2.9744 ($\pm$1.418)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9951 ($\pm$1.404)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0745 ($\pm$1.43)   \\
+			\midrule
+			\textbf{normalised avg rank} & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
+		\end{tabular}%
+
+	}
+\end{table}%
+
+\begin{table}[htbp]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\label{tab:results:replay:metrics:loss}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccccc}
+			                             & \multicolumn{5}{c}{\textbf{Replay - Average Loss}}                                                                                                                                                                                                                                              \\
+			\midrule
+			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}2.136 ($\pm$0.088)   & \cellcolor[rgb]{ .388,  .745,  .482}2.0424 ($\pm$0.47)  & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.135)    & \cellcolor[rgb]{ .863,  .878,  .506}2.0551 ($\pm$0.159) & \cellcolor[rgb]{ .976,  .455,  .427}2.1299 ($\pm$0.292) \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .525,  .784,  .49}0.2676 ($\pm$0.016)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2687 ($\pm$0.014)    & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)  & \cellcolor[rgb]{ .992,  .722,  .482}0.2703 ($\pm$0.015) & \cellcolor[rgb]{ .388,  .745,  .482}0.2673 ($\pm$0.011) \\
+			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2358 ($\pm$0.065)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2347 ($\pm$0.022) & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.019)  & \cellcolor[rgb]{ .996,  .839,  .502}0.2374 ($\pm$0.037) & \cellcolor[rgb]{ .965,  .91,  .514}0.2358 ($\pm$0.025)  \\
+			\textbf{bike}                & \cellcolor[rgb]{ .522,  .78,  .486}0.0568 ($\pm$0.02)   & \cellcolor[rgb]{ .388,  .745,  .482}0.0552 ($\pm$0.007) & \cellcolor[rgb]{ .973,  .412,  .42}0.0651 ($\pm$0.004)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0625 ($\pm$0.019)    & \cellcolor[rgb]{ .976,  .443,  .427}0.065 ($\pm$0.018)  \\
+			\textbf{car}                 & \cellcolor[rgb]{ 1,  .878,  .51}0.1605 ($\pm$0.034)     & \cellcolor[rgb]{ .388,  .745,  .482}0.1537 ($\pm$0.05)  & \cellcolor[rgb]{ .733,  .843,  .502}0.1572 ($\pm$0.026) & \cellcolor[rgb]{ .973,  .412,  .42}0.1671 ($\pm$0.056)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1599 ($\pm$0.028)    \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .996,  .8,  .494}1.3315 ($\pm$0.66)    & \cellcolor[rgb]{ .918,  .894,  .51}1.2672 ($\pm$0.691)  & \cellcolor[rgb]{ 1,  .922,  .518}1.2983 ($\pm$0.534)    & \cellcolor[rgb]{ .388,  .745,  .482}1.0647 ($\pm$0.22)  & \cellcolor[rgb]{ .973,  .412,  .42}1.4342 ($\pm$1.399)  \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1028 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .749,  .486}0.1055 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.012)    & \cellcolor[rgb]{ .604,  .808,  .494}0.1034 ($\pm$0.011) & \cellcolor[rgb]{ .973,  .412,  .42}0.1074 ($\pm$0.012)  \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .988,  .663,  .471}0.0935 ($\pm$0.069) & \cellcolor[rgb]{ 1,  .922,  .518}0.0814 ($\pm$0.078)    & \cellcolor[rgb]{ .863,  .882,  .51}0.081 ($\pm$0.073)   & \cellcolor[rgb]{ .388,  .745,  .482}0.0794 ($\pm$0.063) & \cellcolor[rgb]{ .973,  .412,  .42}0.105 ($\pm$0.068)   \\
+			\textbf{housing}             & \cellcolor[rgb]{ .992,  .745,  .486}0.0979 ($\pm$0.017) & \cellcolor[rgb]{ .467,  .769,  .486}0.0944 ($\pm$0.015) & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.0967 ($\pm$0.022)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1002 ($\pm$0.024)  \\
+			\textbf{iris}                & \cellcolor[rgb]{ .443,  .761,  .482}0.1577 ($\pm$0.295) & \cellcolor[rgb]{ .973,  .412,  .42}0.295 ($\pm$0.16)    & \cellcolor[rgb]{ .996,  .784,  .494}0.2411 ($\pm$0.546) & \cellcolor[rgb]{ .388,  .745,  .482}0.1514 ($\pm$0.192) & \cellcolor[rgb]{ 1,  .922,  .518}0.2208 ($\pm$0.349)    \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ .722,  .839,  .498}0.0504 ($\pm$0.012) & \cellcolor[rgb]{ 1,  .922,  .518}0.0881 ($\pm$0.239)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.336) & \cellcolor[rgb]{ .973,  .412,  .42}0.4733 ($\pm$2.385)  & \cellcolor[rgb]{ 1,  .855,  .506}0.139 ($\pm$0.62)      \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .973,  .412,  .42}0.0596 ($\pm$0.003)  & \cellcolor[rgb]{ .576,  .8,  .49}0.0589 ($\pm$0.003)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .976,  .424,  .424}0.0596 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0594 ($\pm$0.003)    \\
+			\textbf{student performance} & \cellcolor[rgb]{ .996,  .792,  .494}0.2529 ($\pm$0.102) & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.103)    & \cellcolor[rgb]{ .42,  .753,  .482}0.2359 ($\pm$0.093)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2354 ($\pm$0.083) & \cellcolor[rgb]{ .973,  .412,  .42}0.2739 ($\pm$0.126)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}1.0876 ($\pm$0.026)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0756 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}1.0827 ($\pm$0.022)    & \cellcolor[rgb]{ .98,  .522,  .443}1.0866 ($\pm$0.039)  & \cellcolor[rgb]{ .482,  .773,  .486}1.0767 ($\pm$0.022) \\
 		\end{tabular}%
@@
 	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:reanalysis:metrics}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{\begin{tabular}{rccccccccccccccc}
-			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}      &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			\cmidrule{1-2}                      &                                         &                                                                           &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			                                    & \multicolumn{1}{l}{\textbf{reanalysis}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                                &                                                                           &                 &                                 &                                                                                    &                 &                                 &                                                                           &                 &                                 &                                                                           &                 \\
-			\cmidrule{2-3}                      & \multicolumn{1}{l}{\textbf{1}}          &                                                                           &                 & \multicolumn{1}{l}{\textbf{5}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{10}} &                                                                                    &                 & \multicolumn{1}{l}{\textbf{15}} &                                                                           &                 & \multicolumn{1}{l}{\textbf{20}} &                                                                           &                 \\
-			\cmidrule{2-16}    \textbf{dataset} & \textbf{count}                          & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                 & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    & \textbf{count}                  & \textbf{avg}                                                              & \textbf{std}    \\
-			\midrule
-			abalone                             & 930                                     & 2.9849                                                                    & 1.3965          & 930                            & 3.0699                                                                    & 1.4423          & 930                             & 3.1710                                                                             & 1.3205          & 930                             & 2.9441                                                                    & 1.4447          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8301} & 1.4433          \\
-			adult                               & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860} & 0.8523          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.9860}          & 0.8523          & 930                             & 2.7914                                                                    & 1.7091          & 930                             & 3.0151                                                                    & 1.7236          \\
-			air quality                         & 930                                     & 2.9613                                                                    & 1.3442          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8387} & 1.4383          & 930                             & 3.2559                                                                             & 1.4024          & 930                             & 3.0538                                                                    & 1.4200          & 930                             & 2.8903                                                                    & 1.4297          \\
-			bank                                & 930                                     & 3.1161                                                                    & 1.4322          & 930                            & 3.0452                                                                    & 1.3827          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7355}          & 1.3985          & 930                             & 2.9280                                                                    & 1.4028          & 930                             & 3.1753                                                                    & 1.4151          \\
-			bike                                & 930                                     & 3.1409                                                                    & 1.2581          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7581} & 1.3914          & 930                             & 3.1946                                                                             & 1.3653          & 930                             & 3.0978                                                                    & 1.4978          & 930                             & 2.8086                                                                    & 1.4905          \\
-			car                                 & 930                                     & 3.1237                                                                    & 1.4229          & 930                            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7237} & 1.3575          & 930                             & 2.8763                                                                             & 1.2987          & 930                             & 3.1538                                                                    & 1.3846          & 930                             & 3.1226                                                                    & 1.5473          \\
-			diabetic                            & 930                                     & 3.2452                                                                    & 1.3050          & 930                            & 3.0720                                                                    & 1.3913          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7785}          & 1.4067          & 930                             & 3.0290                                                                    & 1.4249          & 930                             & 2.8753                                                                    & 1.4940          \\
-			fish toxicity                       & 930                                     & 3.1452                                                                    & 1.3620          & 930                            & 3.0032                                                                    & 1.4455          & 930                             & 3.2172                                                                             & 1.3639          & 930                             & 3.1000                                                                    & 1.4088          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.5344} & 1.3879          \\
-			forest fires                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8398} & 1.3690          & 930                            & 3.1215                                                                    & 1.4707          & 930                             & 3.0043                                                                             & 1.3181          & 930                             & 2.8860                                                                    & 1.3535          & 930                             & 3.1484                                                                    & 1.5261          \\
-			housing                             & 930                                     & 3.3129                                                                    & 1.3107          & 930                            & 2.9892                                                                    & 1.3927          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6871}          & 1.4833          & 930                             & 2.6968                                                                    & 1.4965          & 930                             & 3.3140                                                                    & 1.2356          \\
-			iris                                & 930                                     & 3.1204                                                                    & 1.3010          & 930                            & 3.0968                                                                    & 1.3909          & 930                             & 3.1269                                                                             & 1.4320          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6366} & 1.4492          & 930                             & 3.0194                                                                    & 1.4352          \\
-			mushroom                            & 930                                     & 2.9312                                                                    & 1.3794          & 930                            & 3.1538                                                                    & 1.4031          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8473}          & 1.3836          & 930                             & 3.1215                                                                    & 1.4530          & 930                             & 2.9032                                                                    & 1.4714          \\
-			parkinsons                          & 930                                     & 2.9688                                                                    & 1.3850          & 930                            & 3.0086                                                                    & 1.3559          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.6129}          & 1.4814          & 930                             & 3.1032                                                                    & 1.3804          & 930                             & 3.3065                                                                    & 1.3778          \\
-			student performance                 & 930                                     & 2.9409                                                                    & 1.4118          & 930                            & 3.1849                                                                    & 1.3804          & 930                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.7710}          & 1.4097          & 930                             & 3.1258                                                                    & 1.3655          & 930                             & 2.9774                                                                    & 1.4675          \\
-			wine quality                        & 930                                     & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{2.8032} & 1.4440          & 930                            & 2.9204                                                                    & 1.3042          & 930                             & 3.2022                                                                             & 1.4104          & 930                             & 2.9247                                                                    & 1.3491          & 930                             & 3.1495                                                                    & 1.5171          \\
-			\midrule
-			\textbf{overall}                    & \textbf{13950}                          & \textbf{2.9747}                                                           & \textbf{1.3710} & \textbf{13950}                 & \textbf{2.9315}                                                           & \textbf{1.3960} & \textbf{13950}                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{2.8978}} & \textbf{1.3999} & \textbf{13950}                  & \textbf{2.9728}                                                           & \textbf{1.4464} & \textbf{13950}                  & \textbf{3.0047}                                                           & \textbf{1.4805} \\
+	\label{tab:results:reanalysis:metrics:rank}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccccc}
+			                             & \multicolumn{5}{c}{\textbf{Reanalysis - Average Rank}}                                                                                                                                                                                                                                          \\
+			\midrule
+			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.9849 ($\pm$1.397)    & \cellcolor[rgb]{ .988,  .69,  .475}3.0699 ($\pm$1.442)  & \cellcolor[rgb]{ .973,  .412,  .42}3.171 ($\pm$1.32)    & \cellcolor[rgb]{ .835,  .875,  .506}2.9441 ($\pm$1.445) & \cellcolor[rgb]{ .388,  .745,  .482}2.8301 ($\pm$1.443) \\
+			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9613 ($\pm$1.344)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8387 ($\pm$1.438) & \cellcolor[rgb]{ .973,  .412,  .42}3.2559 ($\pm$1.402)  & \cellcolor[rgb]{ .992,  .765,  .49}3.0538 ($\pm$1.42)   & \cellcolor[rgb]{ .643,  .816,  .494}2.8903 ($\pm$1.43)  \\
+			\textbf{bank}                & \cellcolor[rgb]{ .988,  .647,  .467}3.1161 ($\pm$1.432) & \cellcolor[rgb]{ 1,  .922,  .518}3.0452 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7355 ($\pm$1.398) & \cellcolor[rgb]{ .765,  .851,  .502}2.928 ($\pm$1.403)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1753 ($\pm$1.415)  \\
+			\textbf{bike}                & \cellcolor[rgb]{ .988,  .698,  .475}3.1409 ($\pm$1.258) & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.391) & \cellcolor[rgb]{ .973,  .412,  .42}3.1946 ($\pm$1.365)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0978 ($\pm$1.498)    & \cellcolor[rgb]{ .478,  .769,  .486}2.8086 ($\pm$1.491) \\
+			\textbf{car}                 & \cellcolor[rgb]{ 1,  .906,  .518}3.1237 ($\pm$1.423)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7237 ($\pm$1.358) & \cellcolor[rgb]{ .62,  .812,  .494}2.8763 ($\pm$1.299)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1538 ($\pm$1.385)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1226 ($\pm$1.547)    \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}3.2452 ($\pm$1.305)  & \cellcolor[rgb]{ .996,  .824,  .502}3.072 ($\pm$1.391)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7785 ($\pm$1.407) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.425)     & \cellcolor[rgb]{ .624,  .812,  .494}2.8753 ($\pm$1.494) \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .992,  .725,  .482}3.1452 ($\pm$1.362) & \cellcolor[rgb]{ .894,  .89,  .51}3.0032 ($\pm$1.445)   & \cellcolor[rgb]{ .973,  .412,  .42}3.2172 ($\pm$1.364)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1 ($\pm$1.409)       & \cellcolor[rgb]{ .388,  .745,  .482}2.5344 ($\pm$1.388) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8398 ($\pm$1.369) & \cellcolor[rgb]{ .98,  .51,  .439}3.1215 ($\pm$1.471)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0043 ($\pm$1.318)    & \cellcolor[rgb]{ .557,  .792,  .49}2.886 ($\pm$1.354)   & \cellcolor[rgb]{ .973,  .412,  .42}3.1484 ($\pm$1.526)  \\
+			\textbf{housing}             & \cellcolor[rgb]{ .976,  .416,  .424}3.3129 ($\pm$1.311) & \cellcolor[rgb]{ 1,  .922,  .518}2.9892 ($\pm$1.393)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6871 ($\pm$1.483) & \cellcolor[rgb]{ .404,  .749,  .482}2.6968 ($\pm$1.496) & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.236)   \\
+			\textbf{iris}                & \cellcolor[rgb]{ .98,  .522,  .443}3.1204 ($\pm$1.301)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.391)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1269 ($\pm$1.432)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.449) & \cellcolor[rgb]{ .894,  .89,  .51}3.0194 ($\pm$1.435)   \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}2.9312 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1538 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8473 ($\pm$1.384) & \cellcolor[rgb]{ .98,  .486,  .435}3.1215 ($\pm$1.453)  & \cellcolor[rgb]{ .796,  .863,  .506}2.9032 ($\pm$1.471) \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .937,  .902,  .514}2.9688 ($\pm$1.385) & \cellcolor[rgb]{ 1,  .922,  .518}3.0086 ($\pm$1.356)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6129 ($\pm$1.481) & \cellcolor[rgb]{ .992,  .761,  .49}3.1032 ($\pm$1.38)   & \cellcolor[rgb]{ .973,  .412,  .42}3.3065 ($\pm$1.378)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ .89,  .89,  .51}2.9409 ($\pm$1.412)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1849 ($\pm$1.38)   & \cellcolor[rgb]{ .388,  .745,  .482}2.771 ($\pm$1.41)   & \cellcolor[rgb]{ .98,  .561,  .451}3.1258 ($\pm$1.366)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.467)    \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8032 ($\pm$1.444) & \cellcolor[rgb]{ .976,  .914,  .514}2.9204 ($\pm$1.304) & \cellcolor[rgb]{ .973,  .412,  .42}3.2022 ($\pm$1.41)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9247 ($\pm$1.349)    & \cellcolor[rgb]{ .98,  .51,  .439}3.1495 ($\pm$1.517)   \\
+			\midrule
+			\textbf{avg rank}            & \cellcolor[rgb]{ .973,  .412,  .42}3.0453 ($\pm$1.374)  & \cellcolor[rgb]{ 1,  .922,  .518}2.999 ($\pm$1.403)     & \cellcolor[rgb]{ .388,  .745,  .482}2.9629 ($\pm$1.409) & \cellcolor[rgb]{ .773,  .855,  .502}2.9858 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .871,  .51}3.0039 ($\pm$1.462)     \\
+			\midrule
+			\textbf{normalised avg rank} & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .988,  .667,  .471}4                   \\
 		\end{tabular}%
+
+	}
+
+\end{table}%
+
+\begin{table}[htbp]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\label{tab:results:reanalysis:metrics:loss}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|lllll}
+			                             & \multicolumn{5}{c}{\textbf{Reanalysis - Average Loss}}                                                                                                                                                                                                                                         \\
+			\midrule
+			\textbf{dataset}             & \multicolumn{1}{c}{\textbf{1}}                          & \multicolumn{1}{c}{\textbf{5}}                          & \multicolumn{1}{c}{\textbf{10}}                         & \multicolumn{1}{c}{\textbf{15}}                        & \multicolumn{1}{c}{\textbf{20}}                         \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.0571 ($\pm$0.102)    & \cellcolor[rgb]{ .388,  .745,  .482}2.0424 ($\pm$0.071) & \cellcolor[rgb]{ 1,  .898,  .514}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .973,  .412,  .42}2.0879 ($\pm$0.226) & \cellcolor[rgb]{ .518,  .78,  .486}2.0456 ($\pm$0.079)  \\
+			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2682 ($\pm$0.014)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2637 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)  & \cellcolor[rgb]{ .98,  .525,  .443}0.2718 ($\pm$0.019) & \cellcolor[rgb]{ .584,  .8,  .49}0.2651 ($\pm$0.012)    \\
+			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2599 ($\pm$0.114)  & \cellcolor[rgb]{ .698,  .831,  .498}0.2406 ($\pm$0.023) & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .984,  .624,  .463}0.254 ($\pm$0.047) & \cellcolor[rgb]{ .388,  .745,  .482}0.2353 ($\pm$0.025) \\
+			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0621 ($\pm$0.016) & \cellcolor[rgb]{ 1,  .922,  .518}0.0627 ($\pm$0.021)    & \cellcolor[rgb]{ .984,  .584,  .455}0.0651 ($\pm$0.02)  & \cellcolor[rgb]{ .973,  .412,  .42}0.0663 ($\pm$0.023) & \cellcolor[rgb]{ .765,  .851,  .502}0.0625 ($\pm$0.02)  \\
+			\textbf{car}                 & \cellcolor[rgb]{ 1,  .922,  .518}0.1597 ($\pm$0.042)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1535 ($\pm$0.038) & \cellcolor[rgb]{ .749,  .847,  .502}0.1572 ($\pm$0.034) & \cellcolor[rgb]{ .973,  .412,  .42}0.1667 ($\pm$0.036) & \cellcolor[rgb]{ .984,  .58,  .455}0.1644 ($\pm$0.04)   \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.482 ($\pm$1.563)   & \cellcolor[rgb]{ .984,  .62,  .463}1.4074 ($\pm$1.558)  & \cellcolor[rgb]{ 1,  .922,  .518}1.2983 ($\pm$0.66)     & \cellcolor[rgb]{ .388,  .745,  .482}1.222 ($\pm$0.6)   & \cellcolor[rgb]{ .969,  .91,  .514}1.2944 ($\pm$0.832)  \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .961,  .91,  .514}0.1031 ($\pm$0.01)   & \cellcolor[rgb]{ 1,  .922,  .518}0.1033 ($\pm$0.008)    & \cellcolor[rgb]{ .988,  .694,  .475}0.1046 ($\pm$0.008) & \cellcolor[rgb]{ .973,  .412,  .42}0.1062 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.1004 ($\pm$0.009) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.1083 ($\pm$0.1)    & \cellcolor[rgb]{ .988,  .675,  .471}0.1003 ($\pm$0.069) & \cellcolor[rgb]{ .388,  .745,  .482}0.081 ($\pm$0.069)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0927 ($\pm$0.069)   & \cellcolor[rgb]{ .451,  .761,  .482}0.0822 ($\pm$0.059) \\
+			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}0.0998 ($\pm$0.017)  & \cellcolor[rgb]{ .745,  .847,  .502}0.0953 ($\pm$0.017) & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .918,  .518}0.0963 ($\pm$0.029)   & \cellcolor[rgb]{ 1,  .922,  .518}0.0962 ($\pm$0.011)    \\
+			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.582 ($\pm$2.084)   & \cellcolor[rgb]{ .604,  .804,  .494}0.164 ($\pm$0.154)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2411 ($\pm$0.295)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1218 ($\pm$0.11) & \cellcolor[rgb]{ 1,  .882,  .514}0.2674 ($\pm$0.545)    \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ .996,  .796,  .494}0.0548 ($\pm$0.241) & \cellcolor[rgb]{ .973,  .412,  .42}0.1165 ($\pm$0.597)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ 1,  .922,  .518}0.0344 ($\pm$0.102)   & \cellcolor[rgb]{ .655,  .82,  .494}0.0181 ($\pm$0.059)  \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ 1,  .922,  .518}0.0597 ($\pm$0.003)    & \cellcolor[rgb]{ .769,  .855,  .502}0.0593 ($\pm$0.002) & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.06 ($\pm$0.004)   & \cellcolor[rgb]{ 1,  .918,  .518}0.0597 ($\pm$0.003)    \\
+			\textbf{student performance} & \cellcolor[rgb]{ .992,  .741,  .486}0.2331 ($\pm$0.083) & \cellcolor[rgb]{ .725,  .839,  .498}0.2297 ($\pm$0.09)  & \cellcolor[rgb]{ .973,  .412,  .42}0.2359 ($\pm$0.102)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2315 ($\pm$0.063)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2274 ($\pm$0.098) \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0728 ($\pm$0.026) & \cellcolor[rgb]{ 1,  .922,  .518}1.0818 ($\pm$0.028)    & \cellcolor[rgb]{ 1,  .871,  .51}1.0827 ($\pm$0.026)     & \cellcolor[rgb]{ .514,  .78,  .486}1.0747 ($\pm$0.026) & \cellcolor[rgb]{ .973,  .412,  .42}1.0909 ($\pm$0.042)  \\
+		\end{tabular}%
+
 	}
@@
 			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.9151 ($\pm$1.395)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6935 ($\pm$1.393) & \cellcolor[rgb]{ 1,  .922,  .518}2.9172 ($\pm$1.384)    & \cellcolor[rgb]{ .788,  .859,  .502}2.8398 ($\pm$1.352) & \cellcolor[rgb]{ .973,  .412,  .42}3.6344 ($\pm$1.357)  \\
-			\textbf{air\_quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9097 ($\pm$1.441)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6817 ($\pm$1.427) & \cellcolor[rgb]{ .624,  .812,  .494}2.7699 ($\pm$1.344) & \cellcolor[rgb]{ .973,  .412,  .42}3.372 ($\pm$1.314)   & \cellcolor[rgb]{ .98,  .529,  .443}3.2667 ($\pm$1.412)  \\
+			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9097 ($\pm$1.441)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6817 ($\pm$1.427) & \cellcolor[rgb]{ .624,  .812,  .494}2.7699 ($\pm$1.344) & \cellcolor[rgb]{ .973,  .412,  .42}3.372 ($\pm$1.314)   & \cellcolor[rgb]{ .98,  .529,  .443}3.2667 ($\pm$1.412)  \\
 			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.7301 ($\pm$1.321) & \cellcolor[rgb]{ .816,  .867,  .506}2.8194 ($\pm$1.335) & \cellcolor[rgb]{ 1,  .922,  .518}2.857 ($\pm$1.485)     & \cellcolor[rgb]{ 1,  .878,  .51}2.9312 ($\pm$1.384)     & \cellcolor[rgb]{ .973,  .412,  .42}3.6624 ($\pm$1.339)  \\
@@
 			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}2.4054 ($\pm$1.358) & \cellcolor[rgb]{ .604,  .808,  .494}2.7011 ($\pm$1.358) & \cellcolor[rgb]{ 1,  .902,  .518}3.2398 ($\pm$1.372)    & \cellcolor[rgb]{ 1,  .922,  .518}3.2323 ($\pm$1.326)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4215 ($\pm$1.396)  \\
-			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}3.0634 ($\pm$1.459)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7935 ($\pm$1.402) & \cellcolor[rgb]{ .447,  .761,  .482}2.8204 ($\pm$1.513) & \cellcolor[rgb]{ .996,  .796,  .494}3.1022 ($\pm$1.346) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.295)  \\
-			\textbf{forest\_fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8161 ($\pm$1.33)  & \cellcolor[rgb]{ .808,  .867,  .506}2.8495 ($\pm$1.383) & \cellcolor[rgb]{ 1,  .922,  .518}2.8645 ($\pm$1.409)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.398)  & \cellcolor[rgb]{ .988,  .698,  .475}3.0925 ($\pm$1.471) \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}3.0634 ($\pm$1.459)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7935 ($\pm$1.402) & \cellcolor[rgb]{ .447,  .761,  .482}2.8204 ($\pm$1.513) & \cellcolor[rgb]{ .996,  .796,  .494}3.1022 ($\pm$1.346) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.295)  \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8161 ($\pm$1.33)  & \cellcolor[rgb]{ .808,  .867,  .506}2.8495 ($\pm$1.383) & \cellcolor[rgb]{ 1,  .922,  .518}2.8645 ($\pm$1.409)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.398)  & \cellcolor[rgb]{ .988,  .698,  .475}3.0925 ($\pm$1.471) \\
 			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}2.6903 ($\pm$1.384) & \cellcolor[rgb]{ .91,  .894,  .51}2.9516 ($\pm$1.318)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.442)    & \cellcolor[rgb]{ .996,  .82,  .498}3.0581 ($\pm$1.344)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3032 ($\pm$1.51)   \\
@@
 			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.2796 ($\pm$1.282) & \cellcolor[rgb]{ 1,  .922,  .518}2.8892 ($\pm$1.247)    & \cellcolor[rgb]{ .816,  .867,  .506}2.7065 ($\pm$1.314) & \cellcolor[rgb]{ .984,  .616,  .459}3.3968 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.728 ($\pm$1.33)    \\
-			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.1452 ($\pm$1.205) & \cellcolor[rgb]{ .741,  .843,  .502}2.6946 ($\pm$1.403) & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.352)    & \cellcolor[rgb]{ .984,  .561,  .451}3.4581 ($\pm$1.354) & \cellcolor[rgb]{ .973,  .412,  .42}3.6054 ($\pm$1.231)  \\
-			\textbf{wine\_quality}        & \cellcolor[rgb]{ .925,  .898,  .51}2.9699 ($\pm$1.437)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0108 ($\pm$1.304)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6634 ($\pm$1.419) & \cellcolor[rgb]{ .988,  .659,  .471}3.1247 ($\pm$1.398) & \cellcolor[rgb]{ .973,  .412,  .42}3.2312 ($\pm$1.447)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.1452 ($\pm$1.205) & \cellcolor[rgb]{ .741,  .843,  .502}2.6946 ($\pm$1.403) & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.352)    & \cellcolor[rgb]{ .984,  .561,  .451}3.4581 ($\pm$1.354) & \cellcolor[rgb]{ .973,  .412,  .42}3.6054 ($\pm$1.231)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .925,  .898,  .51}2.9699 ($\pm$1.437)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0108 ($\pm$1.304)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6634 ($\pm$1.419) & \cellcolor[rgb]{ .988,  .659,  .471}3.1247 ($\pm$1.398) & \cellcolor[rgb]{ .973,  .412,  .42}3.2312 ($\pm$1.447)  \\
 			\midrule
@@
 			\textbf{abalone}             & \cellcolor[rgb]{ .392,  .745,  .482}2.0587 (+-0.088) & \cellcolor[rgb]{ .388,  .745,  .482}2.0583 (+-0.181) & \cellcolor[rgb]{ 1,  .922,  .518}2.0961 (+-0.168)    & \cellcolor[rgb]{ 1,  .878,  .51}2.1454 (+-0.365)     & \cellcolor[rgb]{ .973,  .412,  .42}2.6753 (+-2.18)   \\
-			\textbf{air\_quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 (+-0.016)    & \cellcolor[rgb]{ .851,  .878,  .506}0.2719 (+-0.02)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2688 (+-0.014) & \cellcolor[rgb]{ .988,  .694,  .475}0.2784 (+-0.017) & \cellcolor[rgb]{ .973,  .412,  .42}0.2851 (+-0.029)  \\
+			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 (+-0.016)    & \cellcolor[rgb]{ .851,  .878,  .506}0.2719 (+-0.02)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2688 (+-0.014) & \cellcolor[rgb]{ .988,  .694,  .475}0.2784 (+-0.017) & \cellcolor[rgb]{ .973,  .412,  .42}0.2851 (+-0.029)  \\
 			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 (+-0.065)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2373 (+-0.033) & \cellcolor[rgb]{ .996,  .804,  .498}0.2514 (+-0.109) & \cellcolor[rgb]{ .784,  .859,  .502}0.2427 (+-0.033) & \cellcolor[rgb]{ .973,  .412,  .42}0.2703 (+-0.056)  \\
@@
 			\textbf{diabetic}            & \cellcolor[rgb]{ .698,  .831,  .498}1.2983 (+-0.66)  & \cellcolor[rgb]{ .388,  .745,  .482}1.1216 (+-0.582) & \cellcolor[rgb]{ 1,  .922,  .518}1.4701 (+-1.161)    & \cellcolor[rgb]{ .984,  .604,  .459}1.9918 (+-3.645) & \cellcolor[rgb]{ .973,  .412,  .42}2.2996 (+-3.589)  \\
-			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .992,  .765,  .49}0.1046 (+-0.008)  & \cellcolor[rgb]{ .69,  .831,  .498}0.1026 (+-0.009)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1009 (+-0.01)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1043 (+-0.007)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1052 (+-0.009)  \\
-			\textbf{forest\_fires}        & \cellcolor[rgb]{ 1,  .922,  .518}0.081 (+-0.069)     & \cellcolor[rgb]{ .753,  .851,  .502}0.0772 (+-0.057) & \cellcolor[rgb]{ .388,  .745,  .482}0.0714 (+-0.045) & \cellcolor[rgb]{ .973,  .412,  .42}0.1136 (+-0.059)  & \cellcolor[rgb]{ .98,  .557,  .451}0.1044 (+-0.093)  \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .992,  .765,  .49}0.1046 (+-0.008)  & \cellcolor[rgb]{ .69,  .831,  .498}0.1026 (+-0.009)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1009 (+-0.01)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1043 (+-0.007)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1052 (+-0.009)  \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}0.081 (+-0.069)     & \cellcolor[rgb]{ .753,  .851,  .502}0.0772 (+-0.057) & \cellcolor[rgb]{ .388,  .745,  .482}0.0714 (+-0.045) & \cellcolor[rgb]{ .973,  .412,  .42}0.1136 (+-0.059)  & \cellcolor[rgb]{ .98,  .557,  .451}0.1044 (+-0.093)  \\
 			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 (+-0.017) & \cellcolor[rgb]{ .596,  .804,  .494}0.096 (+-0.015)  & \cellcolor[rgb]{ .992,  .757,  .486}0.1036 (+-0.037) & \cellcolor[rgb]{ 1,  .922,  .518}0.0997 (+-0.021)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1116 (+-0.034)  \\
@@
 			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 (+-0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0599 (+-0.003)    & \cellcolor[rgb]{ .745,  .847,  .502}0.0594 (+-0.003) & \cellcolor[rgb]{ .984,  .627,  .463}0.0644 (+-0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.0676 (+-0.015)  \\
-			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 (+-0.102) & \cellcolor[rgb]{ .733,  .843,  .502}0.2801 (+-0.127) & \cellcolor[rgb]{ 1,  .922,  .518}0.314 (+-0.137)     & \cellcolor[rgb]{ .988,  .631,  .463}0.3623 (+-0.139) & \cellcolor[rgb]{ .973,  .412,  .42}0.3988 (+-0.133)  \\
-			\textbf{wine\_quality}        & \cellcolor[rgb]{ 1,  .922,  .518}1.0827 (+-0.026)    & \cellcolor[rgb]{ .396,  .745,  .482}1.0791 (+-0.021) & \cellcolor[rgb]{ .388,  .745,  .482}1.079 (+-0.03)   & \cellcolor[rgb]{ .988,  .686,  .475}1.086 (+-0.029)  & \cellcolor[rgb]{ .973,  .412,  .42}1.0897 (+-0.034)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 (+-0.102) & \cellcolor[rgb]{ .733,  .843,  .502}0.2801 (+-0.127) & \cellcolor[rgb]{ 1,  .922,  .518}0.314 (+-0.137)     & \cellcolor[rgb]{ .988,  .631,  .463}0.3623 (+-0.139) & \cellcolor[rgb]{ .973,  .412,  .42}0.3988 (+-0.133)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ 1,  .922,  .518}1.0827 (+-0.026)    & \cellcolor[rgb]{ .396,  .745,  .482}1.0791 (+-0.021) & \cellcolor[rgb]{ .388,  .745,  .482}1.079 (+-0.03)   & \cellcolor[rgb]{ .988,  .686,  .475}1.086 (+-0.029)  & \cellcolor[rgb]{ .973,  .412,  .42}1.0897 (+-0.034)  \\
 		\end{tabular}%
@@
 	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:normalise:metrics}%
-	\par\bigskip
-	\resizebox{0.75\textwidth}{!}{
-		\begin{tabular}{rcccccc}
-			\textbf{epoch}                     & \multicolumn{1}{l}{\textbf{(all)}}         &                                                                                    &                 &                                   &                                                                           &                 \\
-			\cmidrule{1-2}                     &                                            &                                                                                    &                 &                                   &                                                                           &                 \\
-			                                   & \multicolumn{1}{l}{\textbf{normalisation}} & \multicolumn{1}{l}{\textbf{metric}}                                                &                 &                                   &                                                                           &                 \\
-			\cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{false}}         &                                                                                    &                 & \multicolumn{1}{l}{\textbf{true}} &                                                                           &                 \\
-			\cmidrule{2-7}    \textbf{dataset} & \textbf{count}                             & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
-			\midrule
-			abalone                            & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5002          & 930                               & 1.5065                                                                    & 0.5002          \\
-			adult                              & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4710}          & 0.4994          & 930                               & 1.4968                                                                    & 0.5003          \\
-			air quality                        & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4892}          & 0.5002          & 930                               & 1.5108                                                                    & 0.5002          \\
-			bank                               & 930                                        & 1.5484                                                                             & 0.4979          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4516} & 0.4979          \\
-			bike                               & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4978}          & 0.5003          & 930                               & 1.5022                                                                    & 0.5003          \\
-			car                                & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4258}          & 0.4947          & 930                               & 1.5742                                                                    & 0.4947          \\
-			diabetic                           & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4753}          & 0.4997          & 930                               & 1.5247                                                                    & 0.4997          \\
-			fish toxicity                      & 930                                        & 1.5505                                                                             & 0.4977          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4495} & 0.4977          \\
-			forest fires                       & 930                                        & 1.5054                                                                             & 0.5002          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4946} & 0.5002          \\
-			housing                            & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4720}          & 0.4995          & 930                               & 1.5280                                                                    & 0.4995          \\
-			iris                               & 930                                        & 1.5645                                                                             & 0.4961          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4355} & 0.4961          \\
-			mushroom                           & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4323}          & 0.4957          & 930                               & 1.5667                                                                    & 0.4958          \\
-			parkinsons                         & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4000}          & 0.4902          & 930                               & 1.6000                                                                    & 0.4902          \\
-			student performance                & 930                                        & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3892}          & 0.4878          & 930                               & 1.6108                                                                    & 0.4878          \\
-			wine quality                       & 930                                        & 1.5473                                                                             & 0.4980          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4527} & 0.4980          \\
-			\midrule
-			\textbf{overall}                   & \textbf{13950}                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4842}} & \textbf{0.4998} & \textbf{13950}                    & \textbf{1.5136}                                                           & \textbf{0.4998} \\
+	\label{tab:results:normalise:metrics:rank}%
+	\par\bigskip
+	\resizebox{0.6\textwidth}{!}{
+		\begin{tabular}{rcc}
+			\multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Normalisation - Average Rank}}                                                           \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                            & \textbf{true}                                           \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4935 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5065 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4892 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5108 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5484 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4516 ($\pm$0.498) \\
+			\multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .388,  .745,  .482}1.4978 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5022 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.4258 ($\pm$0.495)   & \cellcolor[rgb]{ .973,  .412,  .42}1.5742 ($\pm$0.495)  \\
+			\multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4753 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5247 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5505 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4495 ($\pm$0.498) \\
+			\multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.5054 ($\pm$0.5)      & \cellcolor[rgb]{ .388,  .745,  .482}1.4946 ($\pm$0.5)   \\
+			\multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.472 ($\pm$0.499)    & \cellcolor[rgb]{ .973,  .412,  .42}1.528 ($\pm$0.499)   \\
+			\multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5645 ($\pm$0.496)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4355 ($\pm$0.496) \\
+			\multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4323 ($\pm$0.496)   & \cellcolor[rgb]{ .973,  .412,  .42}1.5667 ($\pm$0.496)  \\
+			\multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.4 ($\pm$0.49)       & \cellcolor[rgb]{ .973,  .412,  .42}1.6 ($\pm$0.49)      \\
+			\multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.3892 ($\pm$0.488)   & \cellcolor[rgb]{ .973,  .412,  .42}1.6108 ($\pm$0.488)  \\
+			\multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.5473 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4527 ($\pm$0.498) \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4851 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5148 ($\pm$0.5)    \\
+			\midrule
+			\textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                     & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\
+		\end{tabular}%
+
+	}
+\end{table}%
+
+\begin{table}[htbp]
+	\centering
+	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\label{tab:results:normalise:metrics:loss}%
+	\par\bigskip
+	\resizebox{0.6\textwidth}{!}{
+		\begin{tabular}{r|cc}
+			                             & \multicolumn{2}{c}{\textbf{Normalisation - Average Loss}}                                                           \\
+			\midrule
+			\textbf{dataset}             & \textbf{false}                                            & \textbf{true}                                           \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088)   & \cellcolor[rgb]{ .973,  .412,  .42}2.0936 ($\pm$0.231)  \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2704 ($\pm$0.017) \\
+			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2374 ($\pm$0.042) \\
+			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0651 ($\pm$0.02)    & \cellcolor[rgb]{ .973,  .412,  .42}0.0689 ($\pm$0.03)   \\
+			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)   & \cellcolor[rgb]{ .973,  .412,  .42}0.1721 ($\pm$0.038)  \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}1.2983 ($\pm$0.66)    & \cellcolor[rgb]{ .973,  .412,  .42}1.5051 ($\pm$1.93)   \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1021 ($\pm$0.009) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}0.081 ($\pm$0.069)    & \cellcolor[rgb]{ .973,  .412,  .42}0.0868 ($\pm$0.069)  \\
+			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}0.0941 ($\pm$0.017)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0931 ($\pm$0.019) \\
+			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 ($\pm$0.295)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2358 ($\pm$0.333) \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012)   & \cellcolor[rgb]{ .973,  .412,  .42}0.0455 ($\pm$0.216)  \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003)   & \cellcolor[rgb]{ .973,  .412,  .42}0.0598 ($\pm$0.004)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 ($\pm$0.102)   & \cellcolor[rgb]{ .973,  .412,  .42}0.2522 ($\pm$0.098)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)   & \cellcolor[rgb]{ .973,  .412,  .42}1.0831 ($\pm$0.045)  \\
 		\end{tabular}%
@@
 	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:discounted_rewards:metrics}%
-	\par\bigskip
-	\resizebox{0.85\textwidth}{!}{
-		\begin{tabular}{rcccccc}
-			epoch                              & \multicolumn{1}{l}{(all)}                       &                                                                                    &                 &                                   &                                                                           &                 \\
-			\cmidrule{1-2}                     &                                                 &                                                                                    &                 &                                   &                                                                           &                 \\
-			                                   & \multicolumn{1}{l}{\textbf{discounted rewards}} & \multicolumn{1}{l}{\textbf{metrics}}                                               &                 &                                   &                                                                           &                 \\
-			\cmidrule{2-3}                     & \multicolumn{1}{l}{\textbf{false}}              &                                                                                    &                 & \multicolumn{1}{l}{\textbf{true}} &                                                                           &                 \\
-			\cmidrule{2-7}    \textbf{dataset} & \textbf{count}                                  & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count}                    & \textbf{avg}                                                              & \textbf{std}    \\
-			\midrule
-			abalone                            & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4914}          & 0.5002          & 930                               & 1.5086                                                                    & 0.5002          \\
-			adult                              & 930                                             & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4645} & 0.4990          \\
-			air quality                        & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4613}          & 0.4988          & 930                               & 1.5387                                                                    & 0.4988          \\
-			bank                               & 930                                             & 1.5161                                                                             & 0.5000          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4839} & 0.5000          \\
-			bike                               & 930                                             & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
-			car                                & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4280}          & 0.4950          & 930                               & 1.5720                                                                    & 0.4950          \\
-			diabetic                           & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4699}          & 0.4994          & 930                               & 1.5301                                                                    & 0.4994          \\
-			fish toxicity                      & 930                                             & 1.5011                                                                             & 0.5003          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4989} & 0.5003          \\
-			forest fires                       & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4742}          & 0.4996          & 930                               & 1.5258                                                                    & 0.4996          \\
-			housing                            & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4237}          & 0.4944          & 930                               & 1.5763                                                                    & 0.4944          \\
-			iris                               & 930                                             & 1.5903                                                                             & 0.4920          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4097} & 0.4920          \\
-			mushroom                           & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3946}          & 0.4890          & 930                               & 1.5806                                                                    & 0.4937          \\
-			parkinsons                         & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3710}          & 0.4833          & 930                               & 1.6290                                                                    & 0.4833          \\
-			student performance                & 930                                             & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4398}          & 0.4966          & 930                               & 1.5602                                                                    & 0.4966          \\
-			wine quality                       & 930                                             & 1.5570                                                                             & 0.4970          & 930                               & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4430} & 0.4970          \\
-			\midrule
-			\textbf{overall}                   & \textbf{13950}                                  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.4747}} & \textbf{0.4994} & \textbf{13950}                    & \textbf{1.5214}                                                           & \textbf{0.4996} \\
+	\label{tab:results:discounted_rewards:metrics:rank}%
+	\par\bigskip
+	\resizebox{0.6\textwidth}{!}{
+		\begin{tabular}{rcc}
+			\multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Rank}}                                                           \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                                 & \textbf{true}                                           \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4914 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5086 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4613 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5387 ($\pm$0.499)  \\
+			\multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5161 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4839 ($\pm$0.5)   \\
+			\multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
+			\multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.428 ($\pm$0.495)         & \cellcolor[rgb]{ .973,  .412,  .42}1.572 ($\pm$0.495)   \\
+			\multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4699 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5301 ($\pm$0.499)  \\
+			\multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
+			\multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .388,  .745,  .482}1.4742 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5258 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4237 ($\pm$0.494)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5763 ($\pm$0.494)  \\
+			\multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5903 ($\pm$0.492)         & \cellcolor[rgb]{ .388,  .745,  .482}1.4097 ($\pm$0.492) \\
+			\multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.3946 ($\pm$0.489)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5806 ($\pm$0.494)  \\
+			\multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.371 ($\pm$0.483)         & \cellcolor[rgb]{ .973,  .412,  .42}1.629 ($\pm$0.483)   \\
+			\multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.4398 ($\pm$0.497)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5602 ($\pm$0.497)  \\
+			\multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.557 ($\pm$0.497)          & \cellcolor[rgb]{ .388,  .745,  .482}1.443 ($\pm$0.497)  \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4728 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5254 ($\pm$0.499)  \\
+			\midrule
+			\textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                          & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\
 		\end{tabular}%
+
+	}
+\end{table}%
+
+\begin{table}[htbp]
+	\centering
+	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\label{tab:results:discounted_rewards:metrics:loss}%
+	\par\bigskip
+	\resizebox{0.6\textwidth}{!}{
+		\begin{tabular}{r|cc}
+			                             & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Loss}}                                                           \\
+			\midrule
+			\textbf{dataset}             & \textbf{false}                                                 & \textbf{true}                                           \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088)        & \cellcolor[rgb]{ .973,  .412,  .42}2.0789 ($\pm$0.102)  \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)         & \cellcolor[rgb]{ .388,  .745,  .482}0.2693 ($\pm$0.011) \\
+			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)         & \cellcolor[rgb]{ .388,  .745,  .482}0.2349 ($\pm$0.041) \\
+			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0651 ($\pm$0.02)         & \cellcolor[rgb]{ .973,  .412,  .42}0.0676 ($\pm$0.027)  \\
+			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)        & \cellcolor[rgb]{ .973,  .412,  .42}0.1672 ($\pm$0.037)  \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}1.2983 ($\pm$0.66)         & \cellcolor[rgb]{ .973,  .412,  .42}1.3457 ($\pm$1.419)  \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1046 ($\pm$0.008)        & \cellcolor[rgb]{ .973,  .412,  .42}0.1053 ($\pm$0.008)  \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}0.081 ($\pm$0.069)         & \cellcolor[rgb]{ .973,  .412,  .42}0.0928 ($\pm$0.079)  \\
+			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)        & \cellcolor[rgb]{ .973,  .412,  .42}0.0972 ($\pm$0.017)  \\
+			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 ($\pm$0.295)         & \cellcolor[rgb]{ .388,  .745,  .482}0.1833 ($\pm$0.259) \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012)        & \cellcolor[rgb]{ .973,  .412,  .42}0.0479 ($\pm$0.203)  \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003)        & \cellcolor[rgb]{ .973,  .412,  .42}0.06 ($\pm$0.002)    \\
+			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 ($\pm$0.102)        & \cellcolor[rgb]{ .973,  .412,  .42}0.2408 ($\pm$0.086)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}1.0827 ($\pm$0.026)         & \cellcolor[rgb]{ .388,  .745,  .482}1.0792 ($\pm$0.039) \\
+		\end{tabular}%
+
 	}

### 2022-11-19 dissertation/chapters/08-results.tex
🚧 (results): Bigger font sizes

@@
 
-The required background information on all the elements relevant to the empirical process have been presented in Chapters~\ref{chap:anns}-\ref{chap:probability}.
-The proposed \acf{BHH} was presented in Chapter~\ref{chap:bhh} and the design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}.
-The methodology presented a number of experimental groups to conduct, including a case study on the behaviour of the \acs{BHH} during training, and a comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics.
-The methodology also defined a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.
-
-Finally, this chapter provides the outcome of these empirical processes and provides results on all the experiments that have been conducted.
+The last step in the scientific process requires the presentation of the outcomes of the empirical process.
+Objective discussions based on statistical analysis of the findings is required.
+The design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}.
+The methodology presented a number of experimental groups to conduct.
+The experimental groups that were identified include a case study on the behaviour of the \acs{BHH} during training, an empirical comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics, and a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.
+
+This chapter provides the outcomes of the empirical processes and provides results on all the experiments that have been conducted.
 Detailed discussions follow on the outcomes of each experiment.
-Discussions are accompanied by figures and plots to help provide visual aid for the discussions.
-The output of the statistical analysis that yielded the results that is presented in the chapter is provided in Appendix~\ref{app:statistical_analysis}.
+Discussions are accompanied by figures and plots to help provide visual aid for discussions.
+The output of the statistical analysis that yielded the results is provided in Appendix~\ref{app:statistical_analysis}.
 The remainder of the chapter is structured as follows.
@@
 \begin{itemize}
+	\item \textbf{Section \ref{sec:results:overview}} provides a brief overview of the outcomes of the empirical process and highlights key aspects to observe in the results.
+
 	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}.
@@
 
-	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics as it relates to all datasets.
+	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics on all datasets.
 Three variants of the \acs{BHH} are included in these results.
@@
 
-	\item \textbf{Section \ref{sec:results:practical_applications}} provides a brief discussion on the practical application of the \acs{BHH} to real-world problems.
-
 	\item \textbf{Section \ref{sec:results:summary}} provides a brief summary of the chapter.
 \end{itemize}
+
+\section{Overview}\label{sec:results:overview}
+
+This section provides a brief discussion on the general outcome of the empirical process as a whole.
+Overall the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets.
+In general, the \acs{BHH} performs well and the empirical process provides key insights into the workings of the \acs{BHH}.
+Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.
+
+Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results.
+The \acs{BHH} applies a form of \index{online learning}online learning.
+As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process.
+The training process is not repeated iteratively.
+All experiments conducted are executed for 30 epochs.
+The number of training steps executed is dependent on the batch size applied for each dataset.
+
+All of the underlying \acp{FFNN} trained in the empirical process are relatively small.
+As such, most of the training progress is observed to occur withing the first five epochs.
+As a result, the \acs{BHH} should apply most learning at the early stages of the training process.
+After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point.
+Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the \index{heuristic}heuristic space beyond the five epoch mark.
+
+The \acs{BHH} does not implement a move acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution.
+In some cases the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.
+
+Given the stochastic nature of the \index{heuristic}heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn.
+This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}.
+The probabilistic model implements \textit{probabilities of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.
+
+The \textit{reanalysis interval} defines intervals at which the \acs{BHH} reanalyses the performance log, in effect, resetting the concentration parameters to their default values and reapplying the underlying Bayesian analysis process on the performance log.
+Furthermore, the \textit{replay window size} defines the amount of performance evidence in the performance log.
+By default, the \acs{BHH} baseline configuration has a reanalysis interval of 10, and a replay window size of 10, which is a small window to learn from.
+Despite the small reanalysis interval and the small replay window size, it should be observed that the \acs{BHH} exploits small performance biases regardless and does find small performance gains throughout.
 
@@
 The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process.
-Some noisiness can be expected as mini-batch training is executed with batch sizes of 30.
+Mini-batch training is executed with a batch size of 30.
 The results that are presented are averaged over 30 independent runs.
 
-Furthermore, the case study focuses on three different variants of the \acs{BHH}.
-These include the baseline configuration as was provided in Chapter~\ref{chap:bhh}, as well as a configuration that includes a ``long memory'' by setting the replay window size to 250, and a configuration that makes use of the \textit{symmetric} credit assignment strategy.
-These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment is chosen to illustrate a case where there \acs{BHH} does not reward good performance and does not yield a bias towards \index{heuristic}heuristics that perform well.
+Furthermore, the case study focuses on three variants of the \acs{BHH}.
+These include the baseline configuration, as was provided in Chapter~\ref{chap:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}).
+Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}).
+Finally, the case study includes a configuration that makes use of the \textit{symmetric} credit assignment strategy hyper-parameter, and is denoted as bhh\_credit\_symmetric (illustrated throughout in \textcolor{blue}{blue}).
+
+These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all.
 This section is structured as follows.
@@
 
-	\item \textbf{Section \ref{sec:results:case_study:concentration_parameters}} provides illustrations and discussions around the changes in concentration parameter values as a result of the learning process implemented by the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probabilities of \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:case_study:prior_selec_prob}} provides illustrations and discussions around the changes in the \textit{prior \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:case_study:posterior_selec_prob}} provides illustrations and discussions around the changes in the \textit{posterior \index{heuristic}heuristic selection probabilities} as a result of the learning process implemented by the \acs{BHH}.
+	\item \textbf{Section \ref{sec:results:case_study:concentration_parameters}} provides illustrations and discussions around the changes in concentration parameter values as a result of the learning mechanism implemented by the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probabilities of \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:case_study:prior_selec_prob}} provides illustrations and discussions around the changes in the \textit{prior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.
+
+	\item \textbf{Section \ref{sec:results:case_study:posterior_selec_prob}} provides illustrations and discussions around the changes in the \textit{posterior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Performance metrics}\label{sec:results:case_study:performance_metrics}
-
-Figures~\ref{fig:results:case_study:train_loss}-\ref{fig:results:case_study:test_accuracy} provide illustrations of the train and test, loss and accuracy plots over 30 epochs and is illustrated in log scale.
-The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}.
-The noisiness that results from mini-batch training can be observed in Figure~\ref{fig:results:case_study:test_loss}.
-Figures~\ref{fig:results:case_study:train_accuracy} and~\ref{fig:results:case_study:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%.
-Although the \acs{BHH} was able to succesfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.
-However, it should be noted from epochs 5 and onwards presented in Figure~\ref{fig:results:case_study:test_accuracy} that all the configurations of the \acs{BHH} was able to ``undo'' selections that yielded worse test loss results in the previous epoch.
-The sporadic, oscillating nature of the results later in the training process is simply a result of momentum that is maintained between low-level \index{heuristic}heuristics.
+\subsection{Performance Metrics}\label{sec:results:case_study:performance_metrics}
+
+This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}.
+Figures~\ref{fig:results:case_study:metrics:train_loss}-\ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test, loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
+
+\begin{figure}[htb]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
+		\caption{Train log loss}
+		\label{fig:results:case_study:metrics:train_loss}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
+		\caption{Test log loss}
+		\label{fig:results:case_study:metrics:test_loss}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:case_study:metrics:train_accuracy}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:case_study:metrics:test_accuracy}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The average train and test, loss and accuracy plots over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\label{fig:results:case_study:metrics}
+\end{figure}
+
+The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}, observed by the convergence of the training process, yielding good results.
+Figures~\ref{fig:results:case_study:metrics:train_accuracy} and~\ref{fig:results:case_study:metrics:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%.
+
+Although the different configurations of the \acs{BHH} are all able to succesfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.
+
+The volatility observed in Figure~\ref{fig:results:case_study:metrics:test_loss} is due to overfitting and partly due to the noisiness that results from mini-batch training.
+Early stopping can be applied to the training process to hault training before the model overfits on the training data.
+The training dataset is also very small, with just 120 samples.
+As such, overfitting can be expected.
+
+From Figure~\ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed.
+This could simply be a result of momentum that is maintained when switching between low-level \index{heuristic}heuristics in an attempt to find better solutions.
 For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions.
-The \acs{BHH} does not incorporate a \textit{move acceptance} strategy, whereby a heuristic's outcome is rejected if it does not improve on previous results, yielding a possibly worse loss measurement.
-A move acceptance strategy can be utilised on a validation set as a mechanism to approve or reject heuristic progressions from one step to the other.
-
-Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figures~\ref{fig:results:case_study:train_loss}-\ref{fig:results:case_study:test_accuracy} only provide the outcomes of performance metrics at the end of each epoch.
-Further investigation is required at a mini-batch step level.
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
-	\caption{The average training loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:train_loss}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
-	\caption{The average test loss over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:test_loss}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
-	\caption{The average training accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:train_accuracy}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
-	\caption{The average test accuracy over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:test_accuracy}
-\end{figure}
+The \acs{BHH} does not incorporate a \textit{move acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set.
+A move acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.
+
+Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figure~\ref{fig:results:case_study:metrics} only provides the outcomes of performance metrics at the end of each epoch.
+Further investigation is required at a mini-batch step level and is provided in the following sections.
 
@@
 To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
-Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, from which prior \textit{probabilities of selection probabilities} are sampled.
-Figures~\ref{fig:results:case_study:alpha:0}-\ref{fig:results:case_study:alpha:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, 8 respectively.
-Index 0, 6, 7, 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively and only represent a subset of the concentration parameters in $\boldsymbol{\alpha}$ and the \index{heuristic pool}heuristic pool.
-Simular illustrations for the other indices in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
-
-\begin{figure}[htpb]
+Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
+The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of selection probabilities}.
+Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at index 0, 6, 7, and 8 respectively.
+Index 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool.
+Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
+
+\begin{figure}[htb]
+	\begin{subfigure}{0.5\textwidth}
 		\centering
 		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{0}$ (\acs{SGD}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:alpha:0}
-\end{figure}
-
-\begin{figure}[htpb]
+		\caption{$\alpha_{0}$ - \acs{SGD}}
+		\label{fig:results:case_study:alphas:0}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
 		\centering
 		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{6}$ (\acs{Adam}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:alpha:6}
-\end{figure}
-
-\begin{figure}[htpb]
+		\caption{$\alpha_{6}$ - \acs{Adam}}
+		\label{fig:results:case_study:alphas:6}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
 		\centering
 		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{7}$ (\acs{PSO}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:alpha:7}
-\end{figure}
-
-\begin{figure}[htpb]
+		\caption{$\alpha_{7}$ - \acs{PSO}}
+		\label{fig:results:case_study:alphas:7}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
 		\centering
 		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
-	\caption{The average value of the concentration parameter $\alpha_{8}$ (\acs{GA}) over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:alpha:8}
-\end{figure}
-
-The first logical observation to be made from Figures~\ref{fig:results:case_study:alpha:0}-\ref{fig:results:case_study:alpha:8} is the step-wise increasing nature of $\boldsymbol{\alpha}$ for the long memory configuration (denoted \textit{bhh\_replay\_250}), illustrated in green.
-Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics.
-The values in $\boldsymbol{\alpha}$ is never reset to its initial value of 1, and thus $\boldsymbol{\alpha}$ continues to increase throughout the training process.
+		\caption{$\alpha_{8}$ - \acs{GA}}
+		\label{fig:results:case_study:alphas:8}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0,6,7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\label{fig:results:case_study:alphas}
+\end{figure}
+
+The first logical observation to be made from Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
+Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
+The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process.
 However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$.
 The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}.
-Heuristics that perform will will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.
-
-The next observation that can be made is for the baseline configuration (denoted \textit{bhh\_baseline}) in red, and the symmetric credit assignment strategy configuration (denoted \textit{bhh\_credit\_symmetric}) in blue.
-Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1 as regular intervals.
-This interval is represented by the \textit{reanalysis} window size.
+Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.
+
+The next observations that can be made are for the bhh\_baseline configuration, illustrated in \textcolor{red}{red}, and the bhh\_credit\_symmetric configuration in \textcolor{blue}{blue}.
+Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1.0 as regular intervals.
+This interval is defined by the \textit{reanalysis interval} hyper-parameter.
 The reanalysis interval dictates the frequency at which Bayesian analysis is conducated on the performance log, mainted by the \acs{BHH}.
-Bayesian analysis is used to update $\boldsymbol{\alpha}$.
+Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval.
 As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.
-Notice that $\boldsymbol{\alpha} \geq 1$ for multiple indices, even after reanalysis.
-This is because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1 at the corresponding index in $\boldsymbol{\alpha}$ through the Bayesian analysis process.
-In a case where all 5 entities in the entity pool are allocated the same heuristic, for all 10 steps in the reanalysis windown, $\boldsymbol{\alpha} = 50$.
+
+Notice from Figure~\ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements.
+This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process.
+Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process.
+In a case where all five entities in the entity pool are allocated the same heuristic, for all ten samples defined in the performance log, defined by the replay window size, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.
 
@@
 The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurance} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
-\index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the probabilistic sampling nature of the \acs{BHH}.
+\index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
 Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.
@@
 As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves.
-The probability distribution of \index{heuristic}heuristic selection probabilities is denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
-
-Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8} provide illustrations of the probabilities of the selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
+The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
+
+Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of the \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
 These illustrations are presented in log scale.
-Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at index 0, 6, 7, 8 represent the probabilities of selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and the \index{heuristic pool}heuristic pool.
-Once again, simular illustrations for the other indices in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
-
-From the illustrations presented in Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8}, a clearer picture off the learning process of the \acs{BHH} is formed.
-The first important observation to make is for the bhh\_replay\_250 configuration, presented in green.
-As a reminder, 10 low-level \index{heuristic}heuristics are included in the heuristic pool, yielding a probability of selection probability of 0.1 for each \index{heuristic}heuristic by the frequentist view of probabilistic modeling.
-Towards the end of the training process, the probability of selection probability converges back to the symmetrical, uniform probability distribution, yielding a probability of selection probability of 0.1 per \index{heuristic}heuristic.
-This can be explained as follows: most of the training progress is made in the early stages of the training process, and training stagnates towards the end of the training process.
-Since training stagnates, all heuristics, no matter their past performances, struggle to yield better solutions towards the end of the training process.
-As a result of stagnation, heuristics then struggle to yield credit allocations by means of the credit assignment strategy.
-In the case study experimental group, both the bhh\_baseline and bhh\_replay\_250 configurations make use of the \textit{ibest} credit assignment strategy.
-The \textit{ibest} credit assignment strategy allocates credit to the heuristic that provided the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
-However, since the bhh\_baseline has a short reanalysis interval, the concentration parameter $\boldsymbol{\alpha}$ gets reset to its default value of 1 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is less narrow and thus explaining the larger variance of $\boldsymbol{\theta}$ throughout.
+Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at index 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool.
+Once again, simular illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
+
+\begin{figure}[htb]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
+		\caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
+		\label{fig:results:case_study:thetas:0}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
+		\caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
+		\label{fig:results:case_study:thetas:6}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
+		\caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
+		\label{fig:results:case_study:thetas:7}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
+		\caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
+		\label{fig:results:case_study:thetas:8}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The average sampled probabilities of \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
+The probabilities of the \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\label{fig:results:case_study:thetas}
+\end{figure}
+
+From the illustrations presented in Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8}, a clearer picture off the learning process of the \acs{BHH} is formed.
+The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}.
+As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected probability of \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modeling.
+
+Towards the end of the training process, the probability of \index{heuristic}heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a probability of \index{heuristic}heuristic selection probability of 0.1, for all \index{heuristic}heuristics.
+This can be explained as follows: most of the training progress is made in the early stages of the training process, and training converges towards the end of the training process.
+Since training converges, all heuristics, no matter their past performances, fail to yield better solutions towards the end of the training process.
+As a result of training convergence, heuristics then fail to meet the performance criteria and credit allocations by means of the credit assignment strategy.
+
+Both the bhh\_baseline (\textcolor{red}{red}) and the bhh\_replay\_250 (\textcolor{green}{green}) configurations make use of the \textit{ibest} credit assignment strategy.
+The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yield the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
+However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ gets reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.
 
 Another observation to make occurs in the first 30 steps of the training process.
-Notice how all three configurations mostly yield the same probabilities of selection probabilities in these first 30 steps.
-This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same runs.
+In Figure~\ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same probabilities of \index{heuristic}heuristic selection probabilities in these first 30 steps.
+This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number.
 This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches.
 This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.
-It should be noted that, despite using the same random seed across configurations for the same runs, after about 30 steps, the behavioural changes between the configurations start the show.
-As a reminder, the bhh\_credit\_symmetric configuration, does not bias towards best performing \index{heuristic}heuristics and thus, where the bhh\_baseline and bhh\_replay\_250 configurations diverge from the behaviour of the bhh\_credit\_symmetric configuration, the difference in behaviour is proof of the effect of performance bias.
-
-Finally, despite divergence in behaviour, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar sporadic behaviour, much more so than with the bhh\_replay\_250 configuration.
-This can be attributed to a very small reanalysis window that contains very few samples to learn from (N=10).
-A small reanalysis window allows for more exploration, but can also yield greater variance of the probabilities of selection probabilities.
-Once again, any differences then in the behaviour of the  bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations.
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
-	\caption{The average sampled probability of the selection probability, denoted $\theta_{0}$ (\acs{SGD}), given concentration parameter $\alpha_{0}$.
-The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{0} \vert \alpha_{0})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:theta:0}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
-	\caption{The average sampled probability of the selection probability, denoted $\theta_{6}$ (\acs{Adam}), given concentration parameter $\alpha_{6}$.
-The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{6} \vert \alpha_{6})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:theta:6}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
-	\caption{The average sampled probability of the selection probability, denoted $\theta_{7}$ (\acs{PSO}), given concentration parameter $\alpha_{7}$.
-The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{7} \vert \alpha_{7})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:theta:7}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
-	\caption{The average sampled probability of the selection probability, denoted $\theta_{8}$ (\acs{GA}), given concentration parameter $\alpha_{8}$.
-The probability of the selection probability is sampled from the probability distribution, denoted $P(\theta_{8} \vert \alpha_{8})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:theta:8}
-\end{figure}
+
+It should be noted that, despite using the same random seed across configurations for the same run number, after about 30 steps, the behavioural changes between the configurations start the show.
+As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing \index{heuristic}heuristics and thus, where the bhh\_baseline and bhh\_replay\_250 configurations diverge from the behaviour of the bhh\_credit\_symmetric configuration.
+The difference in behaviour is proof of the effect of performance bias.
+
+Furthermore, the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, with means not equal to the expected probabilities of \index{heuristic}heuristic selection probabilities of 0.1, observed for small windows, at various steps for multiple runs, is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations.
+This is also true for the bhh\_credit\_symmetric configuration, as the bhh\_credit\_symmetric configuration biases towards heuristics that happen to be sampled, despite not biasing towards good performance.
+
+Finally, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar volatile behaviour, much more so than with the bhh\_replay\_250 configuration.
+This can be attributed to a very small reanalysis window combined with a small replay window size of 10, that contains very few samples to learn from.
+A small reanalysis interval and a small replay window size allows for more exploration of the \index{heuristic}heuristic space, but can also yield greater variance of the probabilities of \index{heuristic}heuristic selection probabilities.
+Once again, any differences then in the behaviour of the bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations and biases by the bhh\_baseline configuration.
 
@@
 
-\subsection{Prior Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}
-
-This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities}, that results from the probabilistic model implemented by the \acs{BHH}.
+\subsection{Prior Heuristic Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}
+
+This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities}, that result from the probabilistic model implemented by the \acs{BHH}.
 The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
 
-Figures~\ref{fig:results:case_study:p_H:0}-\ref{fig:results:case_study:p_H:8} provide illustrations of the prior\index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$ throughout the training process, and averaged over all 30 runs.
+Figures~\ref{fig:results:case_study:p_H:0}-\ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at index 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
 Similar to before, these illustrations are also presented in log scale.
-The main observation to make from these figures is that they are much less sporadic than the figures presented for the probabilities of selection probabilities.
+
+\begin{figure}[htb]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
+		\caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
+		\label{fig:results:case_study:p_H:0}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
+		\caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
+		\label{fig:results:case_study:p_H:6}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
+		\caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
+		\label{fig:results:case_study:p_H:7}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
+		\caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
+		\label{fig:results:case_study:p_H:8}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The average sampled prior \index{heuristic}heuristic selection probabilities, given the probabilities of \index{heuristic}heuristic selection probabilities, denoted by $\boldsymbol{H}$, at indices 0, 6, 7, and 8.
+The prior \index{heuristic}heuristic selection probabilities are sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(\boldsymbol{H} \vert \theta)$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\label{fig:results:case_study:p_H}
+\end{figure}
+
+The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the probabilities of \index{heuristic}heuristic selection probabilities presented in the previous section in Figure~\ref{fig:results:case_study:thetas}.
 This is because of the \textit{reselection} interval hyper-parameter.
-A reselection interval hyper-parameter is introduces to control the frequency by which new heuristics are allocated to each entity.
+The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity.
 Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10.
-These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:theta:0}-\ref{fig:results:case_study:theta:8} for the probabilities of selection probabilities.
+These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8} for the probabilities of \index{heuristic}heuristic selection probabilities.
 As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
@@
 Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of \index{heuristic}heuristic performances.
-Since these prior \index{heuristic}heuristic selection probabilities change over time, it can be concludes that the change in prior \index{heuristic}heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}.
-Furthermore, these prior \index{heuristic}heuristic selection probability distributions provide an opportunity to utilise prior knowledge by some expert to inject heuristic selection biases, even before training starts.
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
-	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the probability of the selection probability, denoted by $\theta_{0}$.
-The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{0} \vert \theta_{0})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_H:0}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
-	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the probability of the selection probability, denoted by $\theta_{6}$.
-The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{6} \vert \theta_{6})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_H:6}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
-	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the probability of the selection probability, denoted by $\theta_{7}$.
-The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{7} \vert \theta_{7})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_H:7}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
-	\caption{The average sampled prior \index{heuristic}heuristic selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the probability of the selection probability, denoted by $\theta_{8}$.
-The prior \index{heuristic}heuristic selection probability is sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(h_{8} \vert \theta_{8})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_H:8}
-\end{figure}
+Since these prior \index{heuristic}heuristic selection probabilities change over time, it can be concluded that the change in prior \index{heuristic}heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}.
+Furthermore, the prior \index{heuristic}heuristic selection probability distribution provides an opportunity to utilise prior knowledge by some expert before training starts, by injecting heuristic selection biases, by means of the initial values for the concentration parameter $\boldsymbol{\alpha}$.
 
@@
 
-\subsection{Posterior Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}
-
-This section provides a brief investigation into the outcomes of the \textit{posterior heuristic selection probabilities} that forms the probabilistic model implemented by the \acs{BHH} from which new \index{heuristic}heuristics selections are sampled.
-The posterior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector representing the entities in the entity pool, and $\boldsymbol{C}$ represents the vector of performance criteria outcomes as implemented by the credit assignment strategy.
-Furthermore $\boldsymbol{\theta}, \boldsymbol{\phi}$ represent the probabilities of selection probabilities for the heuristics and entities respectively, and $\boldsymbol{\psi}$ represents the probability of observing a succesful credit allocation from the credit assignment strategy.
-
-Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities, throughout the training process, and averaged over all 30 runs.
+\subsection{Posterior Heuristic Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}
+
+This section provides a detailed discussion on the outcomes of the \textit{posterior heuristic selection probabilities}.
+These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}.
+The posterior \index{heuristic}heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the generalised vector of credit allocation outcomes as implemented by the credit assignment strategy.
+Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probabilities of \index{heuristic}heuristic selection probabilities and probabilities of entity selection probabilities respectively.
+Finally, $\boldsymbol{\psi}$ represents the generalised form of the probabilities of successful credit allocation probabilities.
+Since this dissertation implements credit allocation operations that yield discrete, binary outcomes, $\boldsymbol{\psi}$ can be used interchangeably by $\gamma_{0}$ and $\gamma_{1}$, where $\gamma_{0}$ represents the probabilities of failed credit allocation probabilities and $\gamma_{1}$ represents the probabilities of successful credit allocation probabilities.
+
+Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities at index 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
 Similar to before, these illustrations are also presented in log scale.
-The main observation to make from these figures is that these values do not actually yield probabilities.
-The reasons for this is because the probablistic model, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, is evaluated for proportionality i.e.
-they are not normalised, and the log-sum-exp trick is used in order to maintain numerical stability.
-Instead, these values are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
-
-The first noteworthy observation to make is for the bhh\_replay\_250 configuration.
-From Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8}, it can be seen that the posterior heuristic selection probabilities stagnate.
-As previously mentioned, this is a result of training stagnation later in the training process.
-As a result, fewer and fewer improvements to the current best solutions are found, thus yielding a case where heuristic selection bias is based mostly on past performances obtained from a large reanalysis window.
+As before, illustrations for the other indices are left out for brevity as they yield simular illustrations.
+
+\begin{figure}[htb]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
+		\caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
+		\label{fig:results:case_study:p_HgEC:0:0}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
+		\caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
+		\label{fig:results:case_study:p_HgEC:0:6}
+	\end{subfigure}
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
+		\caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
+		\label{fig:results:case_study:p_HgEC:0:7}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
+		\caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
+		\label{fig:results:case_study:p_HgEC:0:8}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The average proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at index 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
+The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\label{fig:results:case_study:p_HgEC:0}
+\end{figure}
+
+The main observation to make from Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8}, is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
+The reasons for the aforementioned, is because the probablistic model, is evaluated proportionaly as was discussed in Chapter~\ref{chap:bhh}.
+As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
+
+Another observation to make, is for the bhh\_replay\_250 configuration $(\textcolor{green}{green})$.
+From Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8}, it can be seen that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities, later in the training stages.
+The aforementioned suggests that the \acs{BHH} is not able to find anymore performance biases and can not exploit better solutions.
+At this point, the \acs{BHH} starts to explore more as the concentration parameters are reanalysed more uniformly, resolving more and more to a random search in attempt to find better solutions.
 
@@
 A particular \index{heuristic}heuristic might be good for one entity, but not for another.
-This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct \index{heuristic}heuristic to the correct entity at the correct point in the training process.
-
-Finally, the posterior heuristic selection probabilities oscillate much less and are much less sporadic than their prior heuristic selection probability equivalents.
-This is a result of the information that is added by the conditionality on entity and performance criteria.
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
-	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{0}$ (\acs{SGD}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
-The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{0} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_HgEC:0:0}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
-	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{6}$ (\acs{Adam}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
-The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{6} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_HgEC:0:6}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
-	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{7}$ (\acs{PSO}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
-The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{7} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_HgEC:0:7}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
-	\caption{The average proportional posterior selection probability for \index{heuristic}heuristic $h_{8}$ (\acs{GA}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
-The proportional posterior selection probability is calculated from the probabilistic model, denoted $P(h_{8} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_HgEC:0:8}
-\end{figure}
-
-From the observations made in Sections~\ref{sec:results:case_study:performance_metrics}-\ref{sec:results:case_study:posterior_selec_prob}, it can be concluded that the \acs{BHH} is able to succesfully train the underlying \acs{FFNN}.
+This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct \index{heuristic}heuristic to the correct entity at the correct time in the training process.
+
+Finally, the posterior heuristic selection probabilities are much less volatile than their prior heuristic selection probability equivalents.
+This is a result of the information that is added in the performance log by tracking the entity and credit allocation as well.
+
+From the observations made in Sections~\ref{sec:results:case_study:performance_metrics}-\ref{sec:results:case_study:posterior_selec_prob}, it can be concluded that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset.
 Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases and thus, the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.
@@
 
-From Table~\ref{tab:results:standalone:metrics:test_loss} it can be seen that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
-The bhh\_gd configuration managed to produced results comparable to the best heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.
-One exception stands out, and that is for the for bhh\_all configuration.
-The bhh\_all configuration produced bad results for the adult dataset, yielding an average loss far greater than any of the other implementations.
-More detailed discussions on this specific case is provided later in the Chapter.
-
-Table~\ref{tab:results:standalone:metrics:rank} provides the empirical results in ranking format.
-The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, for all datasets, over all runs and all training epochs.
-The average rank across all epochs produce a view on the performance of the \index{heuristic}heuristics as it relates to the entire training process.
-Finally, a normalised average rank is provided for the overall performance of all \index{heuristic}heuristics at the bottom of the table.
-From the normalised average ranks, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and 8th amongst all thirteen \index{heuristic}heuristic implementations respectively.
-
 \begin{sidewaystable}[htbp]
 	\centering
-	\caption{Empirical results showing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
-	\label{tab:results:standalone:metrics:test_loss}%
+	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\label{tab:results:standalone:metrics:loss}%
 	\par\bigskip
 	\resizebox{\textwidth}{!}{
-		% Table generated by Excel2LaTeX from sheet 'loss'
 		\begin{tabular}{r|lll|l|l|l|l|l|lllll}
@@
 
+From Table~\ref{tab:results:standalone:metrics:test_loss} it can be seen that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
+The bhh\_gd configuration managed to produced results comparable to the best heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.
+One exception stands out, and that is for the for bhh\_all configuration.
+The bhh\_all configuration produced bad results for the adult dataset, yielding an average loss far greater than any of the other implementations.
+More detailed discussions on this specific case is provided later in the Chapter.
+
+Table~\ref{tab:results:standalone:metrics:rank} provides the empirical results in ranking format.
+The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, for all datasets, over all runs and all training epochs.
+The average rank across all epochs produce a view on the performance of the \index{heuristic}heuristics as it relates to the entire training process.
+Finally, a normalised average rank is provided for the overall performance of all \index{heuristic}heuristics at the bottom of the table.
+From the normalised average ranks, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and 8th amongst all thirteen \index{heuristic}heuristic implementations respectively.
+
+\begin{sidewaystable}[htbp]
+	\centering
+	\caption{Empirical results showing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
+	\label{tab:results:standalone:metrics:test_loss}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		% Table generated by Excel2LaTeX from sheet 'loss'
+		\begin{tabular}{r|lll|l|l|l|l|l|lllll}
+			                                    & \multicolumn{13}{c}{\textbf{BHH vs.
+Low-Level Heuristics - Average Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
+			\cmidrule{2-14}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                      & \multicolumn{1}{c}{\textbf{adam}}                       & \multicolumn{1}{c|}{\textbf{rmsprop}}                   & \multicolumn{1}{c|}{\textbf{bhh\_gd}}                   & \multicolumn{1}{c|}{\textbf{nag}}                       & \multicolumn{1}{c|}{\textbf{bhh\_all}}                  & \multicolumn{1}{c|}{\textbf{adadelta}}                  & \multicolumn{1}{c|}{\textbf{bhh\_mh}}                   & \multicolumn{1}{c}{\textbf{ga}}                         & \multicolumn{1}{c}{\textbf{pso}}                        & \multicolumn{1}{c}{\textbf{sgd}}                        & \multicolumn{1}{c}{\textbf{momentum}}                   & \multicolumn{1}{c}{\textbf{de}}                         \\
+			\midrule
+			\textbf{abalone}                    & \cellcolor[rgb]{ .506,  .776,  .486}1.9678 ($\pm$0.032)                   & \cellcolor[rgb]{ .494,  .773,  .486}1.9651 ($\pm$0.035) & \cellcolor[rgb]{ .388,  .745,  .482}1.9455 ($\pm$0.035) & \cellcolor[rgb]{ .749,  .847,  .502}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .765,  .851,  .502}2.0156 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .788,  .859,  .502}2.0199 ($\pm$0.034) & \cellcolor[rgb]{ .996,  .827,  .502}2.2942 ($\pm$0.055) & \cellcolor[rgb]{ .984,  .612,  .459}2.8155 ($\pm$0.055) & \cellcolor[rgb]{ .98,  .522,  .443}3.0384 ($\pm$0.294)  & \cellcolor[rgb]{ .992,  .773,  .49}2.428 ($\pm$0.029)   & \cellcolor[rgb]{ .992,  .745,  .486}2.4942 ($\pm$0.029) & \cellcolor[rgb]{ .973,  .412,  .42}3.2959 ($\pm$0.016)  \\
+			\textbf{air quality}                & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                    & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\
+			\textbf{bank}                       & \cellcolor[rgb]{ .459,  .765,  .486}0.2096 ($\pm$0.005)                   & \cellcolor[rgb]{ .4,  .745,  .482}0.2065 ($\pm$0.004)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2058 ($\pm$0.006) & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.005)    & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .886,  .514}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .627,  .812,  .494}0.2186 ($\pm$0.004) & \cellcolor[rgb]{ .996,  .839,  .502}0.2562 ($\pm$0.011) & \cellcolor[rgb]{ .988,  .686,  .475}0.2881 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.3454 ($\pm$0.034)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2382 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2386 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .424,  .424}0.3437 ($\pm$0.028) \\
+			\textbf{bike}                       & \cellcolor[rgb]{ .388,  .745,  .482}0.0458 ($\pm$0.002)                   & \cellcolor[rgb]{ .592,  .804,  .494}0.0682 ($\pm$0.068) & \cellcolor[rgb]{ 1,  .922,  .518}0.1123 ($\pm$0.103)    & \cellcolor[rgb]{ .467,  .765,  .486}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .882,  .886,  .51}0.0995 ($\pm$0.002)  & \cellcolor[rgb]{ .565,  .796,  .49}0.0651 ($\pm$0.02)   & \cellcolor[rgb]{ .588,  .8,  .49}0.0679 ($\pm$0.002)    & \cellcolor[rgb]{ 1,  .902,  .514}0.1179 ($\pm$0.006)    & \cellcolor[rgb]{ .992,  .761,  .486}0.1531 ($\pm$0.005) & \cellcolor[rgb]{ .992,  .773,  .49}0.1503 ($\pm$0.025)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1599 ($\pm$0.003) & \cellcolor[rgb]{ .992,  .725,  .482}0.1614 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.2399 ($\pm$0.04)   \\
+			\textbf{car}                        & \cellcolor[rgb]{ .729,  .843,  .502}0.2027 ($\pm$0.018)                   & \cellcolor[rgb]{ .388,  .745,  .482}0.0972 ($\pm$0.024) & \cellcolor[rgb]{ .408,  .749,  .482}0.1039 ($\pm$0.031) & \cellcolor[rgb]{ .62,  .812,  .494}0.169 ($\pm$0.025)   & \cellcolor[rgb]{ .867,  .882,  .51}0.2454 ($\pm$0.029)  & \cellcolor[rgb]{ .58,  .8,  .49}0.1572 ($\pm$0.034)     & \cellcolor[rgb]{ 1,  .922,  .518}0.2859 ($\pm$0.027)    & \cellcolor[rgb]{ .992,  .733,  .482}0.4891 ($\pm$0.077) & \cellcolor[rgb]{ .98,  .502,  .439}0.7374 ($\pm$0.063)  & \cellcolor[rgb]{ .988,  .667,  .471}0.5632 ($\pm$0.158) & \cellcolor[rgb]{ .98,  .533,  .443}0.7035 ($\pm$0.052)  & \cellcolor[rgb]{ .98,  .506,  .439}0.7322 ($\pm$0.043)  & \cellcolor[rgb]{ .973,  .412,  .42}0.8332 ($\pm$0.074)  \\
+			\textbf{diabetic}                   & \cellcolor[rgb]{ .694,  .831,  .498}0.8895 ($\pm$0.004)                   & \cellcolor[rgb]{ 1,  .898,  .514}0.9193 ($\pm$0.01)     & \cellcolor[rgb]{ .918,  .894,  .51}0.8957 ($\pm$0.004)  & \cellcolor[rgb]{ .98,  .914,  .514}0.8976 ($\pm$0.011)  & \cellcolor[rgb]{ .388,  .745,  .482}0.8809 ($\pm$0.004) & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)   & \cellcolor[rgb]{ .49,  .773,  .486}0.8839 ($\pm$0.005)  & \cellcolor[rgb]{ 1,  .902,  .518}0.9137 ($\pm$0.008)    & \cellcolor[rgb]{ .996,  .843,  .506}0.9613 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .835,  .502}0.9661 ($\pm$0.016) & \cellcolor[rgb]{ .976,  .914,  .514}0.8974 ($\pm$0.004) & \cellcolor[rgb]{ 1,  .922,  .518}0.898 ($\pm$0.003)     & \cellcolor[rgb]{ .988,  .694,  .475}1.0774 ($\pm$0.039) \\
+			\textbf{fish toxicity}              & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                      & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
+			\textbf{forest fires}               & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                       & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\
+			\textbf{housing}                    & \cellcolor[rgb]{ .518,  .78,  .486}0.0889 ($\pm$0.012)                    & \cellcolor[rgb]{ .404,  .749,  .482}0.0848 ($\pm$0.011) & \cellcolor[rgb]{ .388,  .745,  .482}0.0842 ($\pm$0.015) & \cellcolor[rgb]{ .69,  .831,  .498}0.0951 ($\pm$0.015)  & \cellcolor[rgb]{ .612,  .808,  .494}0.0923 ($\pm$0.016) & \cellcolor[rgb]{ .663,  .824,  .498}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.106 ($\pm$0.019)     & \cellcolor[rgb]{ 1,  .867,  .51}0.1169 ($\pm$0.019)     & \cellcolor[rgb]{ .996,  .812,  .498}0.1279 ($\pm$0.02)  & \cellcolor[rgb]{ .992,  .722,  .482}0.1452 ($\pm$0.03)  & \cellcolor[rgb]{ .984,  .576,  .455}0.1735 ($\pm$0.023) & \cellcolor[rgb]{ .984,  .588,  .455}0.1713 ($\pm$0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.2057 ($\pm$0.036)  \\
+			\textbf{iris}                       & \cellcolor[rgb]{ .788,  .859,  .502}0.2161 ($\pm$0.059)                   & \cellcolor[rgb]{ .514,  .78,  .486}0.1203 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0753 ($\pm$0.046) & \cellcolor[rgb]{ 1,  .855,  .506}0.3729 ($\pm$1.119)    & \cellcolor[rgb]{ .416,  .753,  .482}0.085 ($\pm$0.042)  & \cellcolor[rgb]{ .859,  .878,  .506}0.2411 ($\pm$0.295) & \cellcolor[rgb]{ .996,  .808,  .498}0.426 ($\pm$0.072)  & \cellcolor[rgb]{ .686,  .831,  .498}0.1809 ($\pm$0.164) & \cellcolor[rgb]{ 1,  .922,  .518}0.2895 ($\pm$0.117)    & \cellcolor[rgb]{ .973,  .412,  .42}0.8965 ($\pm$0.844)  & \cellcolor[rgb]{ .992,  .773,  .49}0.4694 ($\pm$0.088)  & \cellcolor[rgb]{ .992,  .745,  .486}0.5028 ($\pm$0.072) & \cellcolor[rgb]{ .98,  .494,  .435}0.8027 ($\pm$0.684)  \\
+			\textbf{mushroom}                   & \cellcolor[rgb]{ .549,  .792,  .49}0.0026 ($\pm$0.001)                    & \cellcolor[rgb]{ .467,  .765,  .486}0.0013 ($\pm$0.005) & \cellcolor[rgb]{ .388,  .745,  .482}0.0001 ($\pm$0)     & \cellcolor[rgb]{ .439,  .757,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ 1,  .922,  .518}0.0094 ($\pm$0.002)    & \cellcolor[rgb]{ .718,  .839,  .498}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ .655,  .82,  .494}0.0042 ($\pm$0.001)  & \cellcolor[rgb]{ 1,  .871,  .51}0.0774 ($\pm$0.02)      & \cellcolor[rgb]{ .984,  .561,  .451}0.4892 ($\pm$0.025) & \cellcolor[rgb]{ 1,  .886,  .514}0.0611 ($\pm$0.06)     & \cellcolor[rgb]{ .996,  .796,  .494}0.1797 ($\pm$0.009) & \cellcolor[rgb]{ .992,  .749,  .486}0.2418 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.687 ($\pm$0.016)   \\
+			\textbf{parkinsons}                 & \cellcolor[rgb]{ .51,  .776,  .486}0.0563 ($\pm$0.001)                    & \cellcolor[rgb]{ .412,  .749,  .482}0.0545 ($\pm$0.002) & \cellcolor[rgb]{ .388,  .745,  .482}0.054 ($\pm$0.002)  & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0655 ($\pm$0.002)    & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .69,  .831,  .498}0.0597 ($\pm$0.002)  & \cellcolor[rgb]{ 1,  .918,  .518}0.0658 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .898,  .514}0.0669 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .894,  .514}0.0671 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .467,  .431}0.0923 ($\pm$0.008) & \cellcolor[rgb]{ .973,  .412,  .42}0.0954 ($\pm$0.009)  & \cellcolor[rgb]{ .984,  .604,  .459}0.0843 ($\pm$0.009) \\
+			\textbf{student performance}        & \cellcolor[rgb]{ .388,  .745,  .482}0.1656 ($\pm$0.011)                   & \cellcolor[rgb]{ .98,  .522,  .443}0.4929 ($\pm$0.105)  & \cellcolor[rgb]{ .973,  .412,  .42}0.5724 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .855,  .506}0.2454 ($\pm$0.134)    & \cellcolor[rgb]{ .471,  .769,  .486}0.1697 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .871,  .51}0.2359 ($\pm$0.102)     & \cellcolor[rgb]{ .49,  .773,  .486}0.1708 ($\pm$0.01)   & \cellcolor[rgb]{ .969,  .91,  .514}0.1947 ($\pm$0.014)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1962 ($\pm$0.01)     & \cellcolor[rgb]{ .984,  .573,  .451}0.4565 ($\pm$0.049) & \cellcolor[rgb]{ .933,  .902,  .514}0.193 ($\pm$0.011)  & \cellcolor[rgb]{ .925,  .898,  .51}0.1925 ($\pm$0.011)  & \cellcolor[rgb]{ 1,  .918,  .518}0.2014 ($\pm$0.012)    \\
+			\textbf{wine quality}               & \cellcolor[rgb]{ .631,  .816,  .494}1.0651 ($\pm$0.024)                   & \cellcolor[rgb]{ .388,  .745,  .482}1.0395 ($\pm$0.018) & \cellcolor[rgb]{ .502,  .776,  .486}1.0514 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .698,  .831,  .498}1.0718 ($\pm$0.025) & \cellcolor[rgb]{ .804,  .863,  .506}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .788,  .859,  .502}1.0809 ($\pm$0.021) & \cellcolor[rgb]{ .996,  .839,  .502}1.1666 ($\pm$0.03)  & \cellcolor[rgb]{ .992,  .725,  .482}1.2516 ($\pm$0.046) & \cellcolor[rgb]{ .988,  .659,  .467}1.3046 ($\pm$0.114) & \cellcolor[rgb]{ .996,  .843,  .502}1.1648 ($\pm$0.023) & \cellcolor[rgb]{ .996,  .824,  .502}1.1774 ($\pm$0.019) & \cellcolor[rgb]{ .973,  .412,  .42}1.4896 ($\pm$0.093)  \\
+			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
+
+	}
+\end{sidewaystable}%
+
 Figure~\ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks across all runs for each \index{heuristic}heuristic, per dataset.
 
-\begin{figure}[htbp]
+\begin{figure}[htb]
 	\centering
@@
 
-\begin{figure}[htbp]
+\begin{figure}[htb]
 	\centering
@@
 
-\begin{figure}[htbp]
+\begin{figure}[htb]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{table}[htbp]
+\begin{table}[htb]
 	\centering

### 2022-11-19 scripts/analyse.py

@@ -98,6 +98,7 @@ ANALYSIS_CONFIG = {
 		'column': 'heuristic',
 		'param_count': 13,
 		'order': ['adam', 'adadelta', 'adagrad', 'bhh_all', 'bhh_gd', 'bhh_mh', 'de', 'ga', 'momentum','nag', 'pso', 'rmsprop', 'sgd'],
+		# 'order': ['adagrad', 'adam', 'rmsprop', 'bhh_gd', 'nag', 'bhh_all', 'adadelta', 'bhh_mh', 'ga', 'pso', 'sgd', 'momentum', 'de'],
 		'fig_size_x': 12,
 		'fig_size_y': 9,
 	},
@@ -266,8 +267,19 @@ def setup_seaborn():
 	global PALETTE
 	global PARAM_COUNT
 	# Setup Plots
-	sns.set_context('paper',  font_scale=1.5, rc={'lines.linewidth': 1, 'lines.markersize': 3})
-	PALETTE = sns.color_palette('hls', PARAM_COUNT)
+	rc_config = {
+		'figure.titlesize': 24,
+		'axes.labelsize': 20,
+		'axes.titlesize': 20,
+		'xtick.labelsize': 20,
+		'ytick.labelsize': 20,
+		'legend.fontsize': 12,
+		'lines.linewidth': 2,
+		'lines.markersize': 7,
+	}
+	sns.set_context('paper', rc=rc_config)
+	PALETTE = sns.color_palette('husl', PARAM_COUNT)
+	# PALETTE = sns.color_palette('hls', PARAM_COUNT)
 	# PALETTE = sns.color_palette('viridis', PARAM_COUNT)
 	# PALETTE = sns.color_palette('mako_r', PARAM_COUNT)
 
@@ -295,7 +307,7 @@ def plot(train: bool = False, accuracy = False):
 			subset = DATA.query(query)
 
 			fig, ax = plt.subplots(figsize=(FIG_SIZE_X,FIG_SIZE_Y))
-			fig.suptitle('BHH {} - {} {} - Dataset: {}'.format(FRIENDLY, DS, TYPE, dataset))
+			fig.suptitle('BHH {} - {} {} - Dataset: {}'.format(FRIENDLY, DS, TYPE, dataset), fontsize=24)
 
 			plot = sns.lineplot(
 				data=subset,
@@ -331,11 +343,11 @@ def main():
 	read_data_from_csv()
 	create_cd_plots_per_dataset()
 	create_cd_plots_overall()
[…]

### 2022-11-19 dissertation/chapters/08-results.tex
🚧 (results): BHH vs Low Level Heuristics

@@
 Detailed discussions and illustrations follow.
-As a reminder, the set of low-level heuristics include a number of gradient-based heuristics and a number of meta-heuristics.
-Three different variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics (denoted bhh\_gd), and finally, a \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics (denoted bhh\_mh).
-
-Table~\ref{tab:results:standalone:metrics:test_loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented.
-The test loss that is reported in Table~\ref{tab:results:standalone:metrics:test_loss} reflects on the test loss achieved at the last epoch of training, across all datasets, averaged over all independent runs.
+As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of meta-heuristics.
+Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics (denoted bhh\_mh).
+
+Table~\ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented.
+The test loss is measured at the last epoch for each dataset, over all indepedent runs.
 
@@
 	\centering
-	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}
-	\label{tab:results:standalone:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccc|c|c|c|c|c|ccccc}
-			                             & \multicolumn{13}{c}{\textbf{BHH vs.
-Low-Level Heuristics - Average Rank}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\
-			\textbf{dataset}             & \textbf{adagrad}                                                          & \textbf{adam}                                           & \textbf{rmsprop}                                        & \textbf{bhh\_gd}                                        & \textbf{nag}                                            & \textbf{bhh\_all}                                       & \textbf{adadelta}                                       & \textbf{bhh\_mh}                                        & \textbf{ga}                                              & \textbf{pso}                                             & \textbf{sgd}                                             & \textbf{momentum}                                        & \textbf{de}                                              \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.2215 ($\pm$1.591)                   & \cellcolor[rgb]{ .416,  .753,  .482}2.3989 ($\pm$1.887) & \cellcolor[rgb]{ .78,  .859,  .502}4.6172 ($\pm$2.65)   & \cellcolor[rgb]{ .796,  .863,  .506}4.7032 ($\pm$2.108) & \cellcolor[rgb]{ .725,  .839,  .498}4.2731 ($\pm$1.542) & \cellcolor[rgb]{ 1,  .922,  .518}5.9376 ($\pm$2.399)    & \cellcolor[rgb]{ .894,  .89,  .51}5.3129 ($\pm$1.478)   & \cellcolor[rgb]{ .992,  .749,  .486}8.1882 ($\pm$1.195) & \cellcolor[rgb]{ .98,  .525,  .443}11.1108 ($\pm$1.102)  & \cellcolor[rgb]{ .98,  .514,  .439}11.2559 ($\pm$1.826)  & \cellcolor[rgb]{ .992,  .718,  .478}8.628 ($\pm$1.019)   & \cellcolor[rgb]{ .984,  .624,  .463}9.8151 ($\pm$1.16)   & \cellcolor[rgb]{ .973,  .412,  .42}12.5376 ($\pm$1.329)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                   & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .455,  .765,  .486}2.5495 ($\pm$1.598)                   & \cellcolor[rgb]{ .388,  .745,  .482}2.0796 ($\pm$1.587) & \cellcolor[rgb]{ .588,  .8,  .49}3.4645 ($\pm$2.209)    & \cellcolor[rgb]{ .8,  .863,  .506}4.8828 ($\pm$1.702)   & \cellcolor[rgb]{ .71,  .835,  .498}4.2871 ($\pm$1.732)  & \cellcolor[rgb]{ 1,  .922,  .518}6.2419 ($\pm$2.157)    & \cellcolor[rgb]{ .914,  .894,  .51}5.672 ($\pm$1.241)   & \cellcolor[rgb]{ .988,  .639,  .463}9.7495 ($\pm$1.048) & \cellcolor[rgb]{ .98,  .537,  .447}10.9817 ($\pm$1.216)  & \cellcolor[rgb]{ .976,  .467,  .431}11.8376 ($\pm$1.464) & \cellcolor[rgb]{ .992,  .757,  .486}8.2774 ($\pm$1.03)   & \cellcolor[rgb]{ .992,  .741,  .486}8.4774 ($\pm$1.068)  & \cellcolor[rgb]{ .973,  .412,  .42}12.4989 ($\pm$1.224)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}1.7204 ($\pm$1.384)                   & \cellcolor[rgb]{ .643,  .816,  .494}3.6925 ($\pm$4.004) & \cellcolor[rgb]{ .973,  .914,  .514}6.2624 ($\pm$4.58)  & \cellcolor[rgb]{ .663,  .824,  .498}3.8441 ($\pm$1.398) & \cellcolor[rgb]{ 1,  .922,  .518}6.4516 ($\pm$1.02)     & \cellcolor[rgb]{ .71,  .835,  .498}4.2151 ($\pm$1.361)  & \cellcolor[rgb]{ .859,  .878,  .506}5.3602 ($\pm$1.155) & \cellcolor[rgb]{ .996,  .843,  .506}7.4108 ($\pm$1.008) & \cellcolor[rgb]{ .988,  .686,  .475}9.2269 ($\pm$1.183)  & \cellcolor[rgb]{ .988,  .682,  .475}9.3086 ($\pm$1.761)  & \cellcolor[rgb]{ .984,  .596,  .455}10.3355 ($\pm$1.419) & \cellcolor[rgb]{ .984,  .561,  .451}10.7086 ($\pm$1.423) & \cellcolor[rgb]{ .973,  .412,  .42}12.4634 ($\pm$1.465)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .702,  .835,  .498}4.7634 ($\pm$0.938)                   & \cellcolor[rgb]{ .388,  .745,  .482}1.6226 ($\pm$1.405) & \cellcolor[rgb]{ .455,  .765,  .486}2.3269 ($\pm$1.409) & \cellcolor[rgb]{ .561,  .792,  .49}3.3473 ($\pm$1.35)   & \cellcolor[rgb]{ .831,  .871,  .506}6.0785 ($\pm$0.799) & \cellcolor[rgb]{ .58,  .8,  .49}3.5624 ($\pm$1.315)     & \cellcolor[rgb]{ 1,  .922,  .518}7.7344 ($\pm$1.746)    & \cellcolor[rgb]{ .996,  .8,  .498}8.8505 ($\pm$1.413)   & \cellcolor[rgb]{ .984,  .592,  .455}10.7763 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .855,  .506}8.3613 ($\pm$1.622)     & \cellcolor[rgb]{ .988,  .651,  .467}10.2452 ($\pm$1.447) & \cellcolor[rgb]{ .984,  .576,  .451}10.9226 ($\pm$1.349) & \cellcolor[rgb]{ .973,  .412,  .42}12.4086 ($\pm$1.492)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .506,  .776,  .486}2.7796 ($\pm$1.659)                   & \cellcolor[rgb]{ 1,  .886,  .514}7.1484 ($\pm$2.227)    & \cellcolor[rgb]{ 1,  .922,  .518}6.7376 ($\pm$2.577)    & \cellcolor[rgb]{ .812,  .867,  .506}5.2269 ($\pm$2.186) & \cellcolor[rgb]{ .388,  .745,  .482}1.8118 ($\pm$1.413) & \cellcolor[rgb]{ .988,  .69,  .475}9.3968 ($\pm$3.022)  & \cellcolor[rgb]{ .494,  .773,  .486}2.6753 ($\pm$1.629) & \cellcolor[rgb]{ .992,  .765,  .49}8.557 ($\pm$1.17)    & \cellcolor[rgb]{ .98,  .529,  .443}11.2011 ($\pm$1.413)  & \cellcolor[rgb]{ .984,  .573,  .451}10.7022 ($\pm$1.067) & \cellcolor[rgb]{ .898,  .89,  .51}5.9215 ($\pm$1.542)    & \cellcolor[rgb]{ .949,  .906,  .514}6.3355 ($\pm$1.612)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5065 ($\pm$1.242)  \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                    & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                   & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\
-			\textbf{housing}             & \cellcolor[rgb]{ .404,  .749,  .482}3.4484 ($\pm$2.025)                   & \cellcolor[rgb]{ .388,  .745,  .482}3.3344 ($\pm$1.819) & \cellcolor[rgb]{ .439,  .757,  .482}3.6946 ($\pm$2.166) & \cellcolor[rgb]{ .553,  .792,  .49}4.4742 ($\pm$2.312)  & \cellcolor[rgb]{ .584,  .8,  .49}4.6839 ($\pm$2.658)    & \cellcolor[rgb]{ .537,  .788,  .49}4.3763 ($\pm$2.438)  & \cellcolor[rgb]{ 1,  .918,  .518}7.5903 ($\pm$2.748)    & \cellcolor[rgb]{ 1,  .922,  .518}7.5441 ($\pm$1.736)    & \cellcolor[rgb]{ 1,  .878,  .51}7.8839 ($\pm$2.099)      & \cellcolor[rgb]{ .984,  .608,  .459}9.9409 ($\pm$2.317)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4075 ($\pm$1.528)  & \cellcolor[rgb]{ .976,  .431,  .424}11.2731 ($\pm$1.506) & \cellcolor[rgb]{ .976,  .42,  .424}11.3484 ($\pm$2.096)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .965,  .91,  .514}6.3946 ($\pm$1.6)                      & \cellcolor[rgb]{ .525,  .784,  .49}3.5839 ($\pm$2.511)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6968 ($\pm$1.912) & \cellcolor[rgb]{ .706,  .835,  .498}4.7473 ($\pm$2.275) & \cellcolor[rgb]{ .522,  .78,  .486}3.5548 ($\pm$2.125)  & \cellcolor[rgb]{ .78,  .859,  .502}5.2204 ($\pm$3.041)  & \cellcolor[rgb]{ .973,  .412,  .42}11.3527 ($\pm$1.779) & \cellcolor[rgb]{ 1,  .922,  .518}6.6075 ($\pm$2.555)    & \cellcolor[rgb]{ .992,  .749,  .486}8.2473 ($\pm$1.765)  & \cellcolor[rgb]{ .992,  .745,  .486}8.2731 ($\pm$4.384)  & \cellcolor[rgb]{ .98,  .518,  .443}10.3796 ($\pm$1.294)  & \cellcolor[rgb]{ .976,  .447,  .427}11.0548 ($\pm$1.409) & \cellcolor[rgb]{ .988,  .678,  .471}8.8871 ($\pm$3.251)  \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .71,  .835,  .498}4.4656 ($\pm$1.053)                    & \cellcolor[rgb]{ .388,  .745,  .482}2.1344 ($\pm$1.883) & \cellcolor[rgb]{ .431,  .757,  .482}2.4656 ($\pm$1.359) & \cellcolor[rgb]{ .569,  .796,  .49}3.4484 ($\pm$1.602)  & \cellcolor[rgb]{ .969,  .91,  .514}6.3323 ($\pm$0.891)  & \cellcolor[rgb]{ .6,  .804,  .494}3.6688 ($\pm$2.469)   & \cellcolor[rgb]{ 1,  .922,  .518}6.5538 ($\pm$1.071)    & \cellcolor[rgb]{ .992,  .718,  .478}9.0452 ($\pm$1.093) & \cellcolor[rgb]{ .98,  .51,  .439}11.5731 ($\pm$1.193)   & \cellcolor[rgb]{ .996,  .816,  .498}7.872 ($\pm$0.92)    & \cellcolor[rgb]{ .988,  .659,  .471}9.7527 ($\pm$1.083)  & \cellcolor[rgb]{ .98,  .557,  .451}10.9785 ($\pm$1.108)  & \cellcolor[rgb]{ .973,  .412,  .42}12.7097 ($\pm$1.478)  \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .412,  .749,  .482}2.4677 ($\pm$1.497)                   & \cellcolor[rgb]{ .388,  .745,  .482}2.2333 ($\pm$1.742) & \cellcolor[rgb]{ .541,  .788,  .49}3.5656 ($\pm$2.492)  & \cellcolor[rgb]{ .655,  .82,  .494}4.572 ($\pm$1.934)   & \cellcolor[rgb]{ 1,  .922,  .518}7.5355 ($\pm$1.44)     & \cellcolor[rgb]{ .635,  .816,  .494}4.3839 ($\pm$1.861) & \cellcolor[rgb]{ .875,  .882,  .51}6.472 ($\pm$2.423)   & \cellcolor[rgb]{ .996,  .843,  .506}8.3161 ($\pm$1.644) & \cellcolor[rgb]{ 1,  .898,  .514}7.7968 ($\pm$1.719)     & \cellcolor[rgb]{ .996,  .827,  .502}8.4892 ($\pm$1.901)  & \cellcolor[rgb]{ .98,  .494,  .435}11.7516 ($\pm$1.155)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5419 ($\pm$1.351)  & \cellcolor[rgb]{ .984,  .584,  .455}10.8742 ($\pm$1.317) \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                   & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                    & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}3.5512 ($\pm$2.25)                    & \cellcolor[rgb]{ .471,  .769,  .486}3.9314 ($\pm$3.423) & \cellcolor[rgb]{ .616,  .808,  .494}4.5691 ($\pm$3.517) & \cellcolor[rgb]{ .631,  .812,  .494}4.6346 ($\pm$2.364) & \cellcolor[rgb]{ .675,  .827,  .498}4.8394 ($\pm$2.384) & \cellcolor[rgb]{ .808,  .867,  .506}5.4327 ($\pm$2.9)   & \cellcolor[rgb]{ 1,  .922,  .518}6.2727 ($\pm$3.004)    & \cellcolor[rgb]{ .992,  .776,  .49}7.7855 ($\pm$2.271)  & \cellcolor[rgb]{ .988,  .639,  .467}9.1522 ($\pm$2.48)   & \cellcolor[rgb]{ .984,  .612,  .459}9.4451 ($\pm$2.75)   & \cellcolor[rgb]{ .984,  .592,  .455}9.6445 ($\pm$2.214)  & \cellcolor[rgb]{ .98,  .529,  .443}10.2877 ($\pm$2.346)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4538 ($\pm$2.354)  \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                                     & \cellcolor[rgb]{ .49,  .773,  .486}2                    & \cellcolor[rgb]{ .592,  .804,  .494}3                   & \cellcolor[rgb]{ .694,  .831,  .498}4                   & \cellcolor[rgb]{ .796,  .863,  .506}5                   & \cellcolor[rgb]{ .898,  .89,  .51}6                     & \cellcolor[rgb]{ 1,  .922,  .518}7                      & \cellcolor[rgb]{ .996,  .839,  .502}8                   & \cellcolor[rgb]{ .992,  .753,  .486}9                    & \cellcolor[rgb]{ .988,  .667,  .471}10                   & \cellcolor[rgb]{ .984,  .584,  .455}11                   & \cellcolor[rgb]{ .98,  .498,  .439}12                    & \cellcolor[rgb]{ .973,  .412,  .42}13                    \\
-			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
-
-	}
-\end{sidewaystable}%
-
-\begin{sidewaystable}[htbp]
-	\centering
-	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing test loss and statistics for different low-level \index{heuristic}heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs, measured at the last epoch.}
 	\label{tab:results:standalone:metrics:loss}%
@@
 			                                    & \multicolumn{13}{c}{\textbf{BHH vs.
-Low-Level Heuristics - Average Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
+Low-Level Heuristics - Average Test Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
 			\cmidrule{2-14}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                           & \multicolumn{1}{c}{\textbf{adam}}                       & \multicolumn{1}{c|}{\textbf{rmsprop}}                   & \multicolumn{1}{c|}{\textbf{bhh\_gd}}                   & \multicolumn{1}{c|}{\textbf{nag}}                       & \multicolumn{1}{c|}{\textbf{bhh\_all}}                  & \multicolumn{1}{c|}{\textbf{adadelta}}                  & \multicolumn{1}{c|}{\textbf{bhh\_mh}}                   & \multicolumn{1}{c}{\textbf{ga}}                         & \multicolumn{1}{c}{\textbf{pso}}                        & \multicolumn{1}{c}{\textbf{sgd}}                        & \multicolumn{1}{c}{\textbf{momentum}}                   & \multicolumn{1}{c}{\textbf{de}}                         \\
@@
 			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
-
 	}
@@
 
-From Table~\ref{tab:results:standalone:metrics:test_loss} it can be seen that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
-The bhh\_gd configuration managed to produced results comparable to the best heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.
-One exception stands out, and that is for the for bhh\_all configuration.
-The bhh\_all configuration produced bad results for the adult dataset, yielding an average loss far greater than any of the other implementations.
-More detailed discussions on this specific case is provided later in the Chapter.
-
-Table~\ref{tab:results:standalone:metrics:rank} provides the empirical results in ranking format.
-The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, for all datasets, over all runs and all training epochs.
-The average rank across all epochs produce a view on the performance of the \index{heuristic}heuristics as it relates to the entire training process.
+From Table~\ref{tab:results:standalone:metrics:loss} it can be seen that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
+The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.
+
+Table~\ref{tab:results:standalone:metrics:rank} provides the empirical results from Table~\ref{tab:results:standalone:metrics:loss} in ranked format.
+The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, across all datasets, for all indepented runs and all epochs.
+The average rank across all epochs produces a view on the performance of the \index{heuristic}heuristics as it relates to the entire training process.
 Finally, a normalised average rank is provided for the overall performance of all \index{heuristic}heuristics at the bottom of the table.
-From the normalised average ranks, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and 8th amongst all thirteen \index{heuristic}heuristic implementations respectively.
+The normalised average rank is calculated as a discrete normalisation of the average rank achieved across all datasets, for all independent runs and epochs.
 
@@
 	\centering
-	\caption{Empirical results showing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
-	\label{tab:results:standalone:metrics:test_loss}%
+	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:standalone:metrics:rank}%
 	\par\bigskip
 	\resizebox{\textwidth}{!}{
-		% Table generated by Excel2LaTeX from sheet 'loss'
-		\begin{tabular}{r|lll|l|l|l|l|l|lllll}
+		\begin{tabular}{r|ccc|c|c|c|c|c|ccccc}
 			                             & \multicolumn{13}{c}{\textbf{BHH vs.
-Low-Level Heuristics - Average Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
-			\cmidrule{2-14}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                      & \multicolumn{1}{c}{\textbf{adam}}                       & \multicolumn{1}{c|}{\textbf{rmsprop}}                   & \multicolumn{1}{c|}{\textbf{bhh\_gd}}                   & \multicolumn{1}{c|}{\textbf{nag}}                       & \multicolumn{1}{c|}{\textbf{bhh\_all}}                  & \multicolumn{1}{c|}{\textbf{adadelta}}                  & \multicolumn{1}{c|}{\textbf{bhh\_mh}}                   & \multicolumn{1}{c}{\textbf{ga}}                         & \multicolumn{1}{c}{\textbf{pso}}                        & \multicolumn{1}{c}{\textbf{sgd}}                        & \multicolumn{1}{c}{\textbf{momentum}}                   & \multicolumn{1}{c}{\textbf{de}}                         \\
-			\midrule
-			\textbf{abalone}                    & \cellcolor[rgb]{ .506,  .776,  .486}1.9678 ($\pm$0.032)                   & \cellcolor[rgb]{ .494,  .773,  .486}1.9651 ($\pm$0.035) & \cellcolor[rgb]{ .388,  .745,  .482}1.9455 ($\pm$0.035) & \cellcolor[rgb]{ .749,  .847,  .502}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .765,  .851,  .502}2.0156 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .788,  .859,  .502}2.0199 ($\pm$0.034) & \cellcolor[rgb]{ .996,  .827,  .502}2.2942 ($\pm$0.055) & \cellcolor[rgb]{ .984,  .612,  .459}2.8155 ($\pm$0.055) & \cellcolor[rgb]{ .98,  .522,  .443}3.0384 ($\pm$0.294)  & \cellcolor[rgb]{ .992,  .773,  .49}2.428 ($\pm$0.029)   & \cellcolor[rgb]{ .992,  .745,  .486}2.4942 ($\pm$0.029) & \cellcolor[rgb]{ .973,  .412,  .42}3.2959 ($\pm$0.016)  \\
-			\textbf{air quality}                & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                    & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\
-			\textbf{bank}                       & \cellcolor[rgb]{ .459,  .765,  .486}0.2096 ($\pm$0.005)                   & \cellcolor[rgb]{ .4,  .745,  .482}0.2065 ($\pm$0.004)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2058 ($\pm$0.006) & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.005)    & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .886,  .514}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .627,  .812,  .494}0.2186 ($\pm$0.004) & \cellcolor[rgb]{ .996,  .839,  .502}0.2562 ($\pm$0.011) & \cellcolor[rgb]{ .988,  .686,  .475}0.2881 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.3454 ($\pm$0.034)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2382 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2386 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .424,  .424}0.3437 ($\pm$0.028) \\
-			\textbf{bike}                       & \cellcolor[rgb]{ .388,  .745,  .482}0.0458 ($\pm$0.002)                   & \cellcolor[rgb]{ .592,  .804,  .494}0.0682 ($\pm$0.068) & \cellcolor[rgb]{ 1,  .922,  .518}0.1123 ($\pm$0.103)    & \cellcolor[rgb]{ .467,  .765,  .486}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .882,  .886,  .51}0.0995 ($\pm$0.002)  & \cellcolor[rgb]{ .565,  .796,  .49}0.0651 ($\pm$0.02)   & \cellcolor[rgb]{ .588,  .8,  .49}0.0679 ($\pm$0.002)    & \cellcolor[rgb]{ 1,  .902,  .514}0.1179 ($\pm$0.006)    & \cellcolor[rgb]{ .992,  .761,  .486}0.1531 ($\pm$0.005) & \cellcolor[rgb]{ .992,  .773,  .49}0.1503 ($\pm$0.025)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1599 ($\pm$0.003) & \cellcolor[rgb]{ .992,  .725,  .482}0.1614 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.2399 ($\pm$0.04)   \\
-			\textbf{car}                        & \cellcolor[rgb]{ .729,  .843,  .502}0.2027 ($\pm$0.018)                   & \cellcolor[rgb]{ .388,  .745,  .482}0.0972 ($\pm$0.024) & \cellcolor[rgb]{ .408,  .749,  .482}0.1039 ($\pm$0.031) & \cellcolor[rgb]{ .62,  .812,  .494}0.169 ($\pm$0.025)   & \cellcolor[rgb]{ .867,  .882,  .51}0.2454 ($\pm$0.029)  & \cellcolor[rgb]{ .58,  .8,  .49}0.1572 ($\pm$0.034)     & \cellcolor[rgb]{ 1,  .922,  .518}0.2859 ($\pm$0.027)    & \cellcolor[rgb]{ .992,  .733,  .482}0.4891 ($\pm$0.077) & \cellcolor[rgb]{ .98,  .502,  .439}0.7374 ($\pm$0.063)  & \cellcolor[rgb]{ .988,  .667,  .471}0.5632 ($\pm$0.158) & \cellcolor[rgb]{ .98,  .533,  .443}0.7035 ($\pm$0.052)  & \cellcolor[rgb]{ .98,  .506,  .439}0.7322 ($\pm$0.043)  & \cellcolor[rgb]{ .973,  .412,  .42}0.8332 ($\pm$0.074)  \\
-			\textbf{diabetic}                   & \cellcolor[rgb]{ .694,  .831,  .498}0.8895 ($\pm$0.004)                   & \cellcolor[rgb]{ 1,  .898,  .514}0.9193 ($\pm$0.01)     & \cellcolor[rgb]{ .918,  .894,  .51}0.8957 ($\pm$0.004)  & \cellcolor[rgb]{ .98,  .914,  .514}0.8976 ($\pm$0.011)  & \cellcolor[rgb]{ .388,  .745,  .482}0.8809 ($\pm$0.004) & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)   & \cellcolor[rgb]{ .49,  .773,  .486}0.8839 ($\pm$0.005)  & \cellcolor[rgb]{ 1,  .902,  .518}0.9137 ($\pm$0.008)    & \cellcolor[rgb]{ .996,  .843,  .506}0.9613 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .835,  .502}0.9661 ($\pm$0.016) & \cellcolor[rgb]{ .976,  .914,  .514}0.8974 ($\pm$0.004) & \cellcolor[rgb]{ 1,  .922,  .518}0.898 ($\pm$0.003)     & \cellcolor[rgb]{ .988,  .694,  .475}1.0774 ($\pm$0.039) \\
-			\textbf{fish toxicity}              & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                      & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
-			\textbf{forest fires}               & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                       & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\
-			\textbf{housing}                    & \cellcolor[rgb]{ .518,  .78,  .486}0.0889 ($\pm$0.012)                    & \cellcolor[rgb]{ .404,  .749,  .482}0.0848 ($\pm$0.011) & \cellcolor[rgb]{ .388,  .745,  .482}0.0842 ($\pm$0.015) & \cellcolor[rgb]{ .69,  .831,  .498}0.0951 ($\pm$0.015)  & \cellcolor[rgb]{ .612,  .808,  .494}0.0923 ($\pm$0.016) & \cellcolor[rgb]{ .663,  .824,  .498}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.106 ($\pm$0.019)     & \cellcolor[rgb]{ 1,  .867,  .51}0.1169 ($\pm$0.019)     & \cellcolor[rgb]{ .996,  .812,  .498}0.1279 ($\pm$0.02)  & \cellcolor[rgb]{ .992,  .722,  .482}0.1452 ($\pm$0.03)  & \cellcolor[rgb]{ .984,  .576,  .455}0.1735 ($\pm$0.023) & \cellcolor[rgb]{ .984,  .588,  .455}0.1713 ($\pm$0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.2057 ($\pm$0.036)  \\
-			\textbf{iris}                       & \cellcolor[rgb]{ .788,  .859,  .502}0.2161 ($\pm$0.059)                   & \cellcolor[rgb]{ .514,  .78,  .486}0.1203 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0753 ($\pm$0.046) & \cellcolor[rgb]{ 1,  .855,  .506}0.3729 ($\pm$1.119)    & \cellcolor[rgb]{ .416,  .753,  .482}0.085 ($\pm$0.042)  & \cellcolor[rgb]{ .859,  .878,  .506}0.2411 ($\pm$0.295) & \cellcolor[rgb]{ .996,  .808,  .498}0.426 ($\pm$0.072)  & \cellcolor[rgb]{ .686,  .831,  .498}0.1809 ($\pm$0.164) & \cellcolor[rgb]{ 1,  .922,  .518}0.2895 ($\pm$0.117)    & \cellcolor[rgb]{ .973,  .412,  .42}0.8965 ($\pm$0.844)  & \cellcolor[rgb]{ .992,  .773,  .49}0.4694 ($\pm$0.088)  & \cellcolor[rgb]{ .992,  .745,  .486}0.5028 ($\pm$0.072) & \cellcolor[rgb]{ .98,  .494,  .435}0.8027 ($\pm$0.684)  \\
-			\textbf{mushroom}                   & \cellcolor[rgb]{ .549,  .792,  .49}0.0026 ($\pm$0.001)                    & \cellcolor[rgb]{ .467,  .765,  .486}0.0013 ($\pm$0.005) & \cellcolor[rgb]{ .388,  .745,  .482}0.0001 ($\pm$0)     & \cellcolor[rgb]{ .439,  .757,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ 1,  .922,  .518}0.0094 ($\pm$0.002)    & \cellcolor[rgb]{ .718,  .839,  .498}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ .655,  .82,  .494}0.0042 ($\pm$0.001)  & \cellcolor[rgb]{ 1,  .871,  .51}0.0774 ($\pm$0.02)      & \cellcolor[rgb]{ .984,  .561,  .451}0.4892 ($\pm$0.025) & \cellcolor[rgb]{ 1,  .886,  .514}0.0611 ($\pm$0.06)     & \cellcolor[rgb]{ .996,  .796,  .494}0.1797 ($\pm$0.009) & \cellcolor[rgb]{ .992,  .749,  .486}0.2418 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.687 ($\pm$0.016)   \\
-			\textbf{parkinsons}                 & \cellcolor[rgb]{ .51,  .776,  .486}0.0563 ($\pm$0.001)                    & \cellcolor[rgb]{ .412,  .749,  .482}0.0545 ($\pm$0.002) & \cellcolor[rgb]{ .388,  .745,  .482}0.054 ($\pm$0.002)  & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0655 ($\pm$0.002)    & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .69,  .831,  .498}0.0597 ($\pm$0.002)  & \cellcolor[rgb]{ 1,  .918,  .518}0.0658 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .898,  .514}0.0669 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .894,  .514}0.0671 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .467,  .431}0.0923 ($\pm$0.008) & \cellcolor[rgb]{ .973,  .412,  .42}0.0954 ($\pm$0.009)  & \cellcolor[rgb]{ .984,  .604,  .459}0.0843 ($\pm$0.009) \\
-			\textbf{student performance}        & \cellcolor[rgb]{ .388,  .745,  .482}0.1656 ($\pm$0.011)                   & \cellcolor[rgb]{ .98,  .522,  .443}0.4929 ($\pm$0.105)  & \cellcolor[rgb]{ .973,  .412,  .42}0.5724 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .855,  .506}0.2454 ($\pm$0.134)    & \cellcolor[rgb]{ .471,  .769,  .486}0.1697 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .871,  .51}0.2359 ($\pm$0.102)     & \cellcolor[rgb]{ .49,  .773,  .486}0.1708 ($\pm$0.01)   & \cellcolor[rgb]{ .969,  .91,  .514}0.1947 ($\pm$0.014)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1962 ($\pm$0.01)     & \cellcolor[rgb]{ .984,  .573,  .451}0.4565 ($\pm$0.049) & \cellcolor[rgb]{ .933,  .902,  .514}0.193 ($\pm$0.011)  & \cellcolor[rgb]{ .925,  .898,  .51}0.1925 ($\pm$0.011)  & \cellcolor[rgb]{ 1,  .918,  .518}0.2014 ($\pm$0.012)    \\
-			\textbf{wine quality}               & \cellcolor[rgb]{ .631,  .816,  .494}1.0651 ($\pm$0.024)                   & \cellcolor[rgb]{ .388,  .745,  .482}1.0395 ($\pm$0.018) & \cellcolor[rgb]{ .502,  .776,  .486}1.0514 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .698,  .831,  .498}1.0718 ($\pm$0.025) & \cellcolor[rgb]{ .804,  .863,  .506}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .788,  .859,  .502}1.0809 ($\pm$0.021) & \cellcolor[rgb]{ .996,  .839,  .502}1.1666 ($\pm$0.03)  & \cellcolor[rgb]{ .992,  .725,  .482}1.2516 ($\pm$0.046) & \cellcolor[rgb]{ .988,  .659,  .467}1.3046 ($\pm$0.114) & \cellcolor[rgb]{ .996,  .843,  .502}1.1648 ($\pm$0.023) & \cellcolor[rgb]{ .996,  .824,  .502}1.1774 ($\pm$0.019) & \cellcolor[rgb]{ .973,  .412,  .42}1.4896 ($\pm$0.093)  \\
+Low-Level Heuristics - Average Rank (Based on Test Loss)}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\
+			\textbf{dataset}             & \textbf{adagrad}                                                                               & \textbf{adam}                                           & \textbf{rmsprop}                                        & \textbf{bhh\_gd}                                        & \textbf{nag}                                            & \textbf{bhh\_all}                                       & \textbf{adadelta}                                       & \textbf{bhh\_mh}                                        & \textbf{ga}                                              & \textbf{pso}                                             & \textbf{sgd}                                             & \textbf{momentum}                                        & \textbf{de}                                              \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.2215 ($\pm$1.591)                                        & \cellcolor[rgb]{ .416,  .753,  .482}2.3989 ($\pm$1.887) & \cellcolor[rgb]{ .78,  .859,  .502}4.6172 ($\pm$2.65)   & \cellcolor[rgb]{ .796,  .863,  .506}4.7032 ($\pm$2.108) & \cellcolor[rgb]{ .725,  .839,  .498}4.2731 ($\pm$1.542) & \cellcolor[rgb]{ 1,  .922,  .518}5.9376 ($\pm$2.399)    & \cellcolor[rgb]{ .894,  .89,  .51}5.3129 ($\pm$1.478)   & \cellcolor[rgb]{ .992,  .749,  .486}8.1882 ($\pm$1.195) & \cellcolor[rgb]{ .98,  .525,  .443}11.1108 ($\pm$1.102)  & \cellcolor[rgb]{ .98,  .514,  .439}11.2559 ($\pm$1.826)  & \cellcolor[rgb]{ .992,  .718,  .478}8.628 ($\pm$1.019)   & \cellcolor[rgb]{ .984,  .624,  .463}9.8151 ($\pm$1.16)   & \cellcolor[rgb]{ .973,  .412,  .42}12.5376 ($\pm$1.329)  \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                                        & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\
+			\textbf{bank}                & \cellcolor[rgb]{ .455,  .765,  .486}2.5495 ($\pm$1.598)                                        & \cellcolor[rgb]{ .388,  .745,  .482}2.0796 ($\pm$1.587) & \cellcolor[rgb]{ .588,  .8,  .49}3.4645 ($\pm$2.209)    & \cellcolor[rgb]{ .8,  .863,  .506}4.8828 ($\pm$1.702)   & \cellcolor[rgb]{ .71,  .835,  .498}4.2871 ($\pm$1.732)  & \cellcolor[rgb]{ 1,  .922,  .518}6.2419 ($\pm$2.157)    & \cellcolor[rgb]{ .914,  .894,  .51}5.672 ($\pm$1.241)   & \cellcolor[rgb]{ .988,  .639,  .463}9.7495 ($\pm$1.048) & \cellcolor[rgb]{ .98,  .537,  .447}10.9817 ($\pm$1.216)  & \cellcolor[rgb]{ .976,  .467,  .431}11.8376 ($\pm$1.464) & \cellcolor[rgb]{ .992,  .757,  .486}8.2774 ($\pm$1.03)   & \cellcolor[rgb]{ .992,  .741,  .486}8.4774 ($\pm$1.068)  & \cellcolor[rgb]{ .973,  .412,  .42}12.4989 ($\pm$1.224)  \\
+			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}1.7204 ($\pm$1.384)                                        & \cellcolor[rgb]{ .643,  .816,  .494}3.6925 ($\pm$4.004) & \cellcolor[rgb]{ .973,  .914,  .514}6.2624 ($\pm$4.58)  & \cellcolor[rgb]{ .663,  .824,  .498}3.8441 ($\pm$1.398) & \cellcolor[rgb]{ 1,  .922,  .518}6.4516 ($\pm$1.02)     & \cellcolor[rgb]{ .71,  .835,  .498}4.2151 ($\pm$1.361)  & \cellcolor[rgb]{ .859,  .878,  .506}5.3602 ($\pm$1.155) & \cellcolor[rgb]{ .996,  .843,  .506}7.4108 ($\pm$1.008) & \cellcolor[rgb]{ .988,  .686,  .475}9.2269 ($\pm$1.183)  & \cellcolor[rgb]{ .988,  .682,  .475}9.3086 ($\pm$1.761)  & \cellcolor[rgb]{ .984,  .596,  .455}10.3355 ($\pm$1.419) & \cellcolor[rgb]{ .984,  .561,  .451}10.7086 ($\pm$1.423) & \cellcolor[rgb]{ .973,  .412,  .42}12.4634 ($\pm$1.465)  \\
+			\textbf{car}                 & \cellcolor[rgb]{ .702,  .835,  .498}4.7634 ($\pm$0.938)                                        & \cellcolor[rgb]{ .388,  .745,  .482}1.6226 ($\pm$1.405) & \cellcolor[rgb]{ .455,  .765,  .486}2.3269 ($\pm$1.409) & \cellcolor[rgb]{ .561,  .792,  .49}3.3473 ($\pm$1.35)   & \cellcolor[rgb]{ .831,  .871,  .506}6.0785 ($\pm$0.799) & \cellcolor[rgb]{ .58,  .8,  .49}3.5624 ($\pm$1.315)     & \cellcolor[rgb]{ 1,  .922,  .518}7.7344 ($\pm$1.746)    & \cellcolor[rgb]{ .996,  .8,  .498}8.8505 ($\pm$1.413)   & \cellcolor[rgb]{ .984,  .592,  .455}10.7763 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .855,  .506}8.3613 ($\pm$1.622)     & \cellcolor[rgb]{ .988,  .651,  .467}10.2452 ($\pm$1.447) & \cellcolor[rgb]{ .984,  .576,  .451}10.9226 ($\pm$1.349) & \cellcolor[rgb]{ .973,  .412,  .42}12.4086 ($\pm$1.492)  \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .506,  .776,  .486}2.7796 ($\pm$1.659)                                        & \cellcolor[rgb]{ 1,  .886,  .514}7.1484 ($\pm$2.227)    & \cellcolor[rgb]{ 1,  .922,  .518}6.7376 ($\pm$2.577)    & \cellcolor[rgb]{ .812,  .867,  .506}5.2269 ($\pm$2.186) & \cellcolor[rgb]{ .388,  .745,  .482}1.8118 ($\pm$1.413) & \cellcolor[rgb]{ .988,  .69,  .475}9.3968 ($\pm$3.022)  & \cellcolor[rgb]{ .494,  .773,  .486}2.6753 ($\pm$1.629) & \cellcolor[rgb]{ .992,  .765,  .49}8.557 ($\pm$1.17)    & \cellcolor[rgb]{ .98,  .529,  .443}11.2011 ($\pm$1.413)  & \cellcolor[rgb]{ .984,  .573,  .451}10.7022 ($\pm$1.067) & \cellcolor[rgb]{ .898,  .89,  .51}5.9215 ($\pm$1.542)    & \cellcolor[rgb]{ .949,  .906,  .514}6.3355 ($\pm$1.612)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5065 ($\pm$1.242)  \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                                         & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                                        & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\
+			\textbf{housing}             & \cellcolor[rgb]{ .404,  .749,  .482}3.4484 ($\pm$2.025)                                        & \cellcolor[rgb]{ .388,  .745,  .482}3.3344 ($\pm$1.819) & \cellcolor[rgb]{ .439,  .757,  .482}3.6946 ($\pm$2.166) & \cellcolor[rgb]{ .553,  .792,  .49}4.4742 ($\pm$2.312)  & \cellcolor[rgb]{ .584,  .8,  .49}4.6839 ($\pm$2.658)    & \cellcolor[rgb]{ .537,  .788,  .49}4.3763 ($\pm$2.438)  & \cellcolor[rgb]{ 1,  .918,  .518}7.5903 ($\pm$2.748)    & \cellcolor[rgb]{ 1,  .922,  .518}7.5441 ($\pm$1.736)    & \cellcolor[rgb]{ 1,  .878,  .51}7.8839 ($\pm$2.099)      & \cellcolor[rgb]{ .984,  .608,  .459}9.9409 ($\pm$2.317)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4075 ($\pm$1.528)  & \cellcolor[rgb]{ .976,  .431,  .424}11.2731 ($\pm$1.506) & \cellcolor[rgb]{ .976,  .42,  .424}11.3484 ($\pm$2.096)  \\
+			\textbf{iris}                & \cellcolor[rgb]{ .965,  .91,  .514}6.3946 ($\pm$1.6)                                           & \cellcolor[rgb]{ .525,  .784,  .49}3.5839 ($\pm$2.511)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6968 ($\pm$1.912) & \cellcolor[rgb]{ .706,  .835,  .498}4.7473 ($\pm$2.275) & \cellcolor[rgb]{ .522,  .78,  .486}3.5548 ($\pm$2.125)  & \cellcolor[rgb]{ .78,  .859,  .502}5.2204 ($\pm$3.041)  & \cellcolor[rgb]{ .973,  .412,  .42}11.3527 ($\pm$1.779) & \cellcolor[rgb]{ 1,  .922,  .518}6.6075 ($\pm$2.555)    & \cellcolor[rgb]{ .992,  .749,  .486}8.2473 ($\pm$1.765)  & \cellcolor[rgb]{ .992,  .745,  .486}8.2731 ($\pm$4.384)  & \cellcolor[rgb]{ .98,  .518,  .443}10.3796 ($\pm$1.294)  & \cellcolor[rgb]{ .976,  .447,  .427}11.0548 ($\pm$1.409) & \cellcolor[rgb]{ .988,  .678,  .471}8.8871 ($\pm$3.251)  \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ .71,  .835,  .498}4.4656 ($\pm$1.053)                                         & \cellcolor[rgb]{ .388,  .745,  .482}2.1344 ($\pm$1.883) & \cellcolor[rgb]{ .431,  .757,  .482}2.4656 ($\pm$1.359) & \cellcolor[rgb]{ .569,  .796,  .49}3.4484 ($\pm$1.602)  & \cellcolor[rgb]{ .969,  .91,  .514}6.3323 ($\pm$0.891)  & \cellcolor[rgb]{ .6,  .804,  .494}3.6688 ($\pm$2.469)   & \cellcolor[rgb]{ 1,  .922,  .518}6.5538 ($\pm$1.071)    & \cellcolor[rgb]{ .992,  .718,  .478}9.0452 ($\pm$1.093) & \cellcolor[rgb]{ .98,  .51,  .439}11.5731 ($\pm$1.193)   & \cellcolor[rgb]{ .996,  .816,  .498}7.872 ($\pm$0.92)    & \cellcolor[rgb]{ .988,  .659,  .471}9.7527 ($\pm$1.083)  & \cellcolor[rgb]{ .98,  .557,  .451}10.9785 ($\pm$1.108)  & \cellcolor[rgb]{ .973,  .412,  .42}12.7097 ($\pm$1.478)  \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .412,  .749,  .482}2.4677 ($\pm$1.497)                                        & \cellcolor[rgb]{ .388,  .745,  .482}2.2333 ($\pm$1.742) & \cellcolor[rgb]{ .541,  .788,  .49}3.5656 ($\pm$2.492)  & \cellcolor[rgb]{ .655,  .82,  .494}4.572 ($\pm$1.934)   & \cellcolor[rgb]{ 1,  .922,  .518}7.5355 ($\pm$1.44)     & \cellcolor[rgb]{ .635,  .816,  .494}4.3839 ($\pm$1.861) & \cellcolor[rgb]{ .875,  .882,  .51}6.472 ($\pm$2.423)   & \cellcolor[rgb]{ .996,  .843,  .506}8.3161 ($\pm$1.644) & \cellcolor[rgb]{ 1,  .898,  .514}7.7968 ($\pm$1.719)     & \cellcolor[rgb]{ .996,  .827,  .502}8.4892 ($\pm$1.901)  & \cellcolor[rgb]{ .98,  .494,  .435}11.7516 ($\pm$1.155)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5419 ($\pm$1.351)  & \cellcolor[rgb]{ .984,  .584,  .455}10.8742 ($\pm$1.317) \\
+			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                                        & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                                         & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\
+			\midrule
+			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}3.5512 ($\pm$2.25)                                         & \cellcolor[rgb]{ .471,  .769,  .486}3.9314 ($\pm$3.423) & \cellcolor[rgb]{ .616,  .808,  .494}4.5691 ($\pm$3.517) & \cellcolor[rgb]{ .631,  .812,  .494}4.6346 ($\pm$2.364) & \cellcolor[rgb]{ .675,  .827,  .498}4.8394 ($\pm$2.384) & \cellcolor[rgb]{ .808,  .867,  .506}5.4327 ($\pm$2.9)   & \cellcolor[rgb]{ 1,  .922,  .518}6.2727 ($\pm$3.004)    & \cellcolor[rgb]{ .992,  .776,  .49}7.7855 ($\pm$2.271)  & \cellcolor[rgb]{ .988,  .639,  .467}9.1522 ($\pm$2.48)   & \cellcolor[rgb]{ .984,  .612,  .459}9.4451 ($\pm$2.75)   & \cellcolor[rgb]{ .984,  .592,  .455}9.6445 ($\pm$2.214)  & \cellcolor[rgb]{ .98,  .529,  .443}10.2877 ($\pm$2.346)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4538 ($\pm$2.354)  \\
+			\midrule
+			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                                                          & \cellcolor[rgb]{ .49,  .773,  .486}2                    & \cellcolor[rgb]{ .592,  .804,  .494}3                   & \cellcolor[rgb]{ .694,  .831,  .498}4                   & \cellcolor[rgb]{ .796,  .863,  .506}5                   & \cellcolor[rgb]{ .898,  .89,  .51}6                     & \cellcolor[rgb]{ 1,  .922,  .518}7                      & \cellcolor[rgb]{ .996,  .839,  .502}8                   & \cellcolor[rgb]{ .992,  .753,  .486}9                    & \cellcolor[rgb]{ .988,  .667,  .471}10                   & \cellcolor[rgb]{ .984,  .584,  .455}11                   & \cellcolor[rgb]{ .98,  .498,  .439}12                    & \cellcolor[rgb]{ .973,  .412,  .42}13                    \\
 			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
@@
 
-Figure~\ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks across all runs for each \index{heuristic}heuristic, per dataset.
+From the normalised average ranks provided in Table~\ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eigth amongst all thirteen \index{heuristic}heuristic implementations respectively.
+These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.
+
+Figure~\ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each \index{heuristic}heuristic, per dataset.
+The heuristics are ordered according to the normalised ranks presented in Table~\ref{tab:results:standalone:metrics:rank}.
 
@@
 	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \Acs{BHH} per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all runs and epochs.}
 	\label{fig:results:standalone:descriptive:descriptive}
 \end{figure}
+
+From Figure~\ref{fig:results:standalone:descriptive:descriptive} a few observations can be made.
+Firstly, both \acs{Adam} and \acs{RMSProp} achieved radically different average ranks for the student performance dataset, compared to the other datasets.
+This can also be see in Table~\ref{tab:results:standalone:metrics:rank}.
+Further investigation into the reasons for this is required as both these heuristics perform well on all other datasets, and the other heuristics perform well for the student performance dataset.
+A suggestions then leads to the possibility that an invalid learning rate or learning rate schedule leads to a scenario where good solutions are overshot, causing \acs{Adam} and \acs{RMSProp} to struggle to resolve back to good solutions.
+Furthermore, the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
+The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.
 
@@
 Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all \index{heuristic}heuristics is very small.
-Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, was statistically only outperformed overall by \acs{Adagrad}, yielding statistically comparable results than \acs{Adam}, \acs{NAG} and \acs{RMSProp}.
+Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, was statistically only outperformed overall by \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}.
 It should be noted that the standalone low-level \index{heuristic} \index{heuristic}heuristics already produce good results in general across all datasets.
 In this particular case, producing better performance outcomes can be hard to achieve.
-However, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.
+However, as mentioned previously, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.
 
 Another observation that can be made is that the gradient-based \index{heuristic}heuristics generally performed much better than the \index{meta-heuristic}meta-heuristics on all datasets.
-State of the art methods for training \acp{FFNN} such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions~\cite{ref:kingma:2014}.
+State of the art methods for training \acp{FFNN}, such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions~\cite{ref:kingma:2014}.
 Exploration of the \index{heuristic}heuristic space leads the \acs{BHH} to consider other \index{heuristic}heuristics during the training process, which could possibly result in worse performances at times.
@@
 
-Figures~\ref{fig:results:standalone:figures:iris}-\ref{fig:results:standalone:figures:car} provide illustrations of the train and test, loss and accuracy plots for each heuristics as it relates to a selection of classification datasets.
+Figures~\ref{fig:results:standalone:figures:iris}-\ref{fig:results:standalone:figures:bank} provide example illustrations of the train and test, loss and accuracy plots for each heuristic as it relates to a selection of classification datasets.
 The train and test, loss and accuracy plots provided are illustrated in log scale.
@@
 
-\begin{figure}[htb]
+\begin{figure}[htpb]
 	\begin{subfigure}{0.5\textwidth}
@@
 	\end{subfigure}
+	\par\bigskip
 	\par\bigskip
@@
 
-\begin{figure}[htb]
+\begin{figure}[htpb]
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
+		\caption{Train log loss}
+		\label{fig:results:standalone:figures:loss:train:car}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
+		\caption{Test log loss}
+		\label{fig:results:standalone:figures:loss:test:car}
+	\end{subfigure}
+	\par\bigskip
+	\par\bigskip
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
+		\caption{Train log accuracy}
+		\label{fig:results:standalone:figures:accuracy:train:car}
+	\end{subfigure}
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
+		\caption{Test log accuracy}
+		\label{fig:results:standalone:figures:accuracy:test:car}
+	\end{subfigure}
+	\par\bigskip
+	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the car dataset over 30 epochs, illustrated in log scale.}
+	\label{fig:results:standalone:figures:car}
+\end{figure}
+
+\begin{figure}[htpb]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the car dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:car}
-\end{figure}
-
-Figures~\ref{fig:results:standalone:figures:fish_toxicity}-\ref{fig:results:standalone:figures:parkinsons} provide illustrations of the train and test loss plots for each heuristics as it relates to a selection of regression datasets.
+Figures~\ref{fig:results:standalone:figures:fish_toxicity}-\ref{fig:results:standalone:figures:parkinsons} provide example illustrations of the train and test loss plots for each heuristic as it relates to a selection of regression datasets.
 The train and test loss plots provided are illustrated in log scale.
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:heuristic_pool:metrics:rank}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:heuristic_pool:metrics:loss}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}
+	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all independent runs and all epochs.}
 	\label{tab:results:population:metrics:rank}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}
+	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all independent runs and all epochs.}
 	\label{tab:results:population:metrics:loss}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:credit:metrics:rank}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:credit:metrics:loss}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:reselection:metrics:rank}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:reselection:metrics:loss}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:replay:metrics:rank}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:replay:metrics:loss}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:reanalysis:metrics:rank}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:reanalysis:metrics:loss}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:burn_in:metrics:rank}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:burn_in:metrics:loss}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:normalise:metrics:rank}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:normalise:metrics:loss}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:discounted_rewards:metrics:rank}%
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
+	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:discounted_rewards:metrics:loss}%

### 2022-11-19 dissertation/chapters/08-results.tex
🚧 (results): Heuristic pools

@@
 Table~\ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all indepedent runs.
+The test loss is measured at the last epoch for each dataset, over all independent runs.
 
@@
 This experimental group utilises the same three variants of the \acs{BHH} as was utilised in Section \ref{sec:results:standalone}, but provides an opportunity to look at the \acs{BHH} \index{heuristic pool}heuristic pool hyper-parameter in more depth.
-
-Table \ref{tab:results:heuristic_pool:metrics} provides the ranked performance, per dataset, of each of the \acs{BHH} \index{heuristic pool}heuristic pool configurations.
-Similar to before, the performance rank is calculated as the average rank produced by each \index{heuristic pool}heuristic pool configuration, for all datasets, over all runs and all training epochs.
+These variants are denoted as follows.
+The \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics is denoted as \textit{all}, the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics is denoted as \textit{gd}, and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics is denoted as \textit{mh}.
+
+Table~\ref{tab:results:heuristic_pool:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the heuristic pool variants of the \acs{BHH} that was implemented.
+The test loss is measured at the last epoch for each dataset, over all independent runs.
 
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:heuristic_pool:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccc}
-			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Rank}}                                                                                                                    \\
-			\midrule
-			\textbf{dataset}             & \textbf{all}                                               & \textbf{gd}                                             & \textbf{mh}                                            \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}1.7946 ($\pm$0.641)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3828 ($\pm$0.56)  & \cellcolor[rgb]{ .973,  .412,  .42}2.8226 ($\pm$0.42)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}2.1871 ($\pm$0.815)     & \cellcolor[rgb]{ .388,  .745,  .482}1.6828 ($\pm$0.751) & \cellcolor[rgb]{ 1,  .922,  .518}2.1301 ($\pm$0.788)   \\
-			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}1.7731 ($\pm$0.562)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3215 ($\pm$0.492) & \cellcolor[rgb]{ .973,  .412,  .42}2.9054 ($\pm$0.334) \\
-			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}1.6247 ($\pm$0.553)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4387 ($\pm$0.532) & \cellcolor[rgb]{ .973,  .412,  .42}2.9366 ($\pm$0.281) \\
-			\textbf{car}                 & \cellcolor[rgb]{ 1,  .922,  .518}1.5903 ($\pm$0.511)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4409 ($\pm$0.518) & \cellcolor[rgb]{ .973,  .412,  .42}2.9688 ($\pm$0.228) \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}2.4516 ($\pm$0.735)     & \cellcolor[rgb]{ .388,  .745,  .482}1.2806 ($\pm$0.576) & \cellcolor[rgb]{ 1,  .922,  .518}2.2677 ($\pm$0.58)    \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}1.9903 ($\pm$0.849)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8344 ($\pm$0.768) & \cellcolor[rgb]{ .973,  .412,  .42}2.1753 ($\pm$0.796) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}2.0667 ($\pm$0.834)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8269 ($\pm$0.781) & \cellcolor[rgb]{ .973,  .412,  .42}2.1065 ($\pm$0.807) \\
-			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}1.6043 ($\pm$0.687)    & \cellcolor[rgb]{ 1,  .922,  .518}1.6602 ($\pm$0.665)    & \cellcolor[rgb]{ .973,  .412,  .42}2.7355 ($\pm$0.524) \\
-			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}1.8581 ($\pm$0.8)         & \cellcolor[rgb]{ .388,  .745,  .482}1.7806 ($\pm$0.727) & \cellcolor[rgb]{ .973,  .412,  .42}2.3613 ($\pm$0.796) \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}1.5204 ($\pm$0.581)    & \cellcolor[rgb]{ 1,  .922,  .518}1.5484 ($\pm$0.527)    & \cellcolor[rgb]{ .973,  .412,  .42}2.9312 ($\pm$0.289) \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}1.557 ($\pm$0.624)     & \cellcolor[rgb]{ 1,  .922,  .518}1.6011 ($\pm$0.591)    & \cellcolor[rgb]{ .973,  .412,  .42}2.8419 ($\pm$0.445) \\
-			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}1.9828 ($\pm$0.822)       & \cellcolor[rgb]{ .388,  .745,  .482}1.7903 ($\pm$0.848) & \cellcolor[rgb]{ .973,  .412,  .42}2.2269 ($\pm$0.715) \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ 1,  .922,  .518}1.5785 ($\pm$0.55)        & \cellcolor[rgb]{ .388,  .745,  .482}1.4935 ($\pm$0.563) & \cellcolor[rgb]{ .973,  .412,  .42}2.928 ($\pm$0.294)  \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ 1,  .922,  .518}1.8271 ($\pm$0.743)       & \cellcolor[rgb]{ .388,  .745,  .482}1.5773 ($\pm$0.671) & \cellcolor[rgb]{ .973,  .412,  .42}2.5955 ($\pm$0.659) \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ 1,  .922,  .518}2                         & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .973,  .412,  .42}3                   \\
-		\end{tabular}%
-	}
-\end{table}%
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\caption{Empirical results showing average test loss and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
 	\label{tab:results:heuristic_pool:metrics:loss}%
 	\par\bigskip
-	\resizebox{\textwidth}{!}{
+	\resizebox{0.8\textwidth}{!}{
 		\begin{tabular}{r|lll}
@@
 
-Similar to the outcomes provided in Section \ref{sec:results:standalone}, it is found that the bhh\_gd configuration yielded the best overall performance compared to the bhh\_all and bhh\_mh configurations.
-Figure~\ref{fig:results:heuristic_pool:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different \index{heuristic pool}heuristic pool configurations, per dataset.
+Similar to before, Table \ref{tab:results:heuristic_pool:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} \index{heuristic pool}heuristic pool configurations.
+The performance rank is calculated as the average rank produced by each \index{heuristic pool}heuristic pool configuration, for all datasets, over all runs and all epochs.
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:heuristic_pool:metrics:rank}%
+	\par\bigskip
+	\resizebox{0.8\textwidth}{!}{
+		\begin{tabular}{r|ccc}
+			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Rank}}                                                                                                                    \\
+			\midrule
+			\textbf{dataset}             & \textbf{all}                                               & \textbf{gd}                                             & \textbf{mh}                                            \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}1.7946 ($\pm$0.641)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3828 ($\pm$0.56)  & \cellcolor[rgb]{ .973,  .412,  .42}2.8226 ($\pm$0.42)  \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}2.1871 ($\pm$0.815)     & \cellcolor[rgb]{ .388,  .745,  .482}1.6828 ($\pm$0.751) & \cellcolor[rgb]{ 1,  .922,  .518}2.1301 ($\pm$0.788)   \\
+			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}1.7731 ($\pm$0.562)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3215 ($\pm$0.492) & \cellcolor[rgb]{ .973,  .412,  .42}2.9054 ($\pm$0.334) \\
+			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}1.6247 ($\pm$0.553)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4387 ($\pm$0.532) & \cellcolor[rgb]{ .973,  .412,  .42}2.9366 ($\pm$0.281) \\
+			\textbf{car}                 & \cellcolor[rgb]{ 1,  .922,  .518}1.5903 ($\pm$0.511)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4409 ($\pm$0.518) & \cellcolor[rgb]{ .973,  .412,  .42}2.9688 ($\pm$0.228) \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}2.4516 ($\pm$0.735)     & \cellcolor[rgb]{ .388,  .745,  .482}1.2806 ($\pm$0.576) & \cellcolor[rgb]{ 1,  .922,  .518}2.2677 ($\pm$0.58)    \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}1.9903 ($\pm$0.849)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8344 ($\pm$0.768) & \cellcolor[rgb]{ .973,  .412,  .42}2.1753 ($\pm$0.796) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}2.0667 ($\pm$0.834)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8269 ($\pm$0.781) & \cellcolor[rgb]{ .973,  .412,  .42}2.1065 ($\pm$0.807) \\
+			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}1.6043 ($\pm$0.687)    & \cellcolor[rgb]{ 1,  .922,  .518}1.6602 ($\pm$0.665)    & \cellcolor[rgb]{ .973,  .412,  .42}2.7355 ($\pm$0.524) \\
+			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}1.8581 ($\pm$0.8)         & \cellcolor[rgb]{ .388,  .745,  .482}1.7806 ($\pm$0.727) & \cellcolor[rgb]{ .973,  .412,  .42}2.3613 ($\pm$0.796) \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}1.5204 ($\pm$0.581)    & \cellcolor[rgb]{ 1,  .922,  .518}1.5484 ($\pm$0.527)    & \cellcolor[rgb]{ .973,  .412,  .42}2.9312 ($\pm$0.289) \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}1.557 ($\pm$0.624)     & \cellcolor[rgb]{ 1,  .922,  .518}1.6011 ($\pm$0.591)    & \cellcolor[rgb]{ .973,  .412,  .42}2.8419 ($\pm$0.445) \\
+			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}1.9828 ($\pm$0.822)       & \cellcolor[rgb]{ .388,  .745,  .482}1.7903 ($\pm$0.848) & \cellcolor[rgb]{ .973,  .412,  .42}2.2269 ($\pm$0.715) \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ 1,  .922,  .518}1.5785 ($\pm$0.55)        & \cellcolor[rgb]{ .388,  .745,  .482}1.4935 ($\pm$0.563) & \cellcolor[rgb]{ .973,  .412,  .42}2.928 ($\pm$0.294)  \\
+			\midrule
+			\textbf{avg rank}            & \cellcolor[rgb]{ 1,  .922,  .518}1.8271 ($\pm$0.743)       & \cellcolor[rgb]{ .388,  .745,  .482}1.5773 ($\pm$0.671) & \cellcolor[rgb]{ .973,  .412,  .42}2.5955 ($\pm$0.659) \\
+			\midrule
+			\textbf{normalised avg rank} & \cellcolor[rgb]{ 1,  .922,  .518}2                         & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .973,  .412,  .42}3                   \\
+		\end{tabular}%
+	}
+\end{table}%
+
+Similar to the outcomes provided in Section \ref{sec:results:standalone}, by ranked performance over all epochs, it is found that the \textit{gd} configuration yielded the best overall performance compared to the \textit{all} and \textit{mh} configurations.
+However, when considering the test loss measured at the last epoch, there is no clear difference in performance overall.
+This illustrates the reasoning behind the use of the rank metric over all epochs to evaluate the overall training process, as the test loss outcome differs at different epochs and early stopping of the training process was not used.
+
+Figure~\ref{fig:results:heuristic_pool:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different \index{heuristic pool}heuristic pool configurations, per dataset.
+From this illustration it can clearly be seen that, by ranked performance, the \textit{gd} configuration produced better results overall, considering the entire training process.
 
@@
 
-Figure~\ref{fig:results:heuristic_pool:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic pool}heuristic pool configuration as it relates to all datasets, across all runs.
+Figure~\ref{fig:results:heuristic_pool:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic pool}heuristic pool configuration as it relates to all datasets, across all independent runs and epochs.
 
@@
 
-From Figures~\ref{fig:results:heuristic_pool:descriptive:descriptive} and Figure~\ref{fig:results:heuristic_pool:descriptive:cd}, it is clear that the bhh\_gd configuration performs best overall, with statistically insignificant exceptions for the parkinsons and housing datasets.
-
-From the results show in Section \ref{sec:results:standalone}, the gradient-based methods outperformed the \index{meta-heuristic}meta-heuristics in all cases.
-It then logically makes sense that the bhh\_gd configuration yields the best performance.
-However, the inclusion of \index{meta-heuristic}meta-heuristics is done as an attempt to provide a mechanism that could provide even better performance, as well as generalisation capabilities to other datasets.
-The benefits of a generalisation capability is not realised in this dissertation, since the gradient-based \index{heuristic}heuristics provided the best performance across datasets and overall.
-Furthermore, the gradient-based \index{heuristic}heuristics already produce good performance results, and improvement on those results are hard.
+From Figures~\ref{fig:results:heuristic_pool:descriptive:descriptive} and~\ref{fig:results:heuristic_pool:descriptive:cd}, it is clear that the \textit{gd} configuration configuration performs best overall, with exceptions to the parkinsons and housing datasets, where the \textit{all} and \textit{gd} configurations performed equally well with statistically insignificant differences in their outcomes.
+
+From the results shown in this section and Section \ref{sec:results:standalone}, the gradient-based \index{heuristic}heuristics outperformed the \index{meta-heuristic}meta-heuristics in almost all cases.
+It can then logically be concluded that the \acs{BHH} baseline configuration with only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool yields the best performance.
+The inclusion of \index{meta-heuristic}meta-heuristics is done as an attempt to provide a mechanism that could provide even better performance, as well as generalisation capabilities to other datasets.
+The benefits of using \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool is not realised in this dissertation, since the gradient-based \index{heuristic}heuristics provided the best overall performance across  all datasets.
+Furthermore, the standalone gradient-based \index{heuristic}heuristics already produce good performance results, and improvement on those results are hard.
 Faster convergence is also difficult to achieve, since the \acs{BHH} needs sufficient time to explore the heuristic space.
-The benefit that the \acs{BHH} then brings is that it provides a mechanism where prior expert knowledge can be injected, before training starts.
-Since gradient-based \index{heuristic}heuristics perform well, future research can exploit this knowledge and provide a significant bias towards these gradient-based \index{heuristic}heuristics through the initialisation of the concentration parameters as is mentioned previously.
-
-Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides the train and test, loss and accuracy plot for an example classification dataset (abalone) as it relates to the heuristic pool experimental group.
-As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+The benefit that the \acs{BHH} then brings is that it provides a mechanism whereby prior expert knowledge can be injected, before training starts.
+Since gradient-based \index{heuristic}heuristics perform well, future research can exploit this knowledge and provide a significant bias towards these gradient-based \index{heuristic}heuristics through the initialisation of the concentration parameters related to these \index{heuristic}heuristics as mentioned previously.
+
+Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides an illustration of the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the \index{heuristic pool}heuristic pool experimental group.
+As before, the illustration is provided in log scale and illustrations for the other classification datasets are left out for brevity as they yield similar illustrations.
 
@@
 Figure~\ref{fig:results:heuristic_pool:figures:forest_fires} provides the train and test loss plot for an example regression dataset (forest fires) as it relates to the heuristic pool experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+As before, the illustration is provided in log scale and illustrations for the other regression datasets are left out for brevity.
 
@@
 
-Figure~\ref{fig:results:population:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different population size configurations, per dataset.
+Figure~\ref{fig:results:population:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different population size configurations, per dataset.
 
@@
 Figure~\ref{fig:results:population:figures:student_performance} provides the train and test loss plot for an example regression dataset (student performance) as it relates to the population size experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 
-Figure~\ref{fig:results:credit:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different credit assignment strategy configurations, per dataset.
+Figure~\ref{fig:results:credit:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different credit assignment strategy configurations, per dataset.
 
@@
 Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plot for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 
-Figure~\ref{fig:results:credit:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reselection interval configurations, per dataset.
+Figure~\ref{fig:results:credit:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reselection interval configurations, per dataset.
 
@@
 Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plot for an example regression dataset (bike) as it relates to the reselection interval experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 
-Figure~\ref{fig:results:replay:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different replay window size configurations, per dataset.
+Figure~\ref{fig:results:replay:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different replay window size configurations, per dataset.
 
@@
 Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plot for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 
-Figure~\ref{fig:results:reanalysis:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reanalysis interval configurations, per dataset.
+Figure~\ref{fig:results:reanalysis:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reanalysis interval configurations, per dataset.
 
@@
 Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plot for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 
-Figure~\ref{fig:results:burn_in:descriptive:descriptive} provides a illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the burn in window size configurations, per dataset.
+Figure~\ref{fig:results:burn_in:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the burn in window size configurations, per dataset.
 
@@
 Figure~\ref{fig:results:burn_in:figures:parkinsons} provides the train and test loss plot for an example regression dataset (parkinsons) as it relates to the burn in window size experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 
-Figure~\ref{fig:results:normalise:descriptive:descriptive} provides a illustration of the descriptive plots for the \acs{BHH} configurations with the normalisation hyper-parameter enabled and disabled, per dataset.
+Figure~\ref{fig:results:normalise:descriptive:descriptive} provides an illustration of the descriptive plots for the \acs{BHH} configurations with the normalisation hyper-parameter enabled and disabled, per dataset.
 
@@
 Figure~\ref{fig:results:normalise:figures:bike} provides the train and test loss plot for an example regression dataset (bike) as it relates to the normalisation experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 
-Figure~\ref{fig:results:discounted_rewards:descriptive:descriptive} provides a illustration of the descriptive plots for the \acs{BHH} configurations with the discounted rewards hyper-parameter enabled and disabled, per dataset.
+Figure~\ref{fig:results:discounted_rewards:descriptive:descriptive} provides an illustration of the descriptive plots for the \acs{BHH} configurations with the discounted rewards hyper-parameter enabled and disabled, per dataset.
 
@@
 Figure~\ref{fig:results:discounted_rewards:figures:housing} provides the train and test loss plot for an example regression dataset (housing) as it relates to the discounted rewards experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression databases are left out for brevity.
+As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 

### 2022-11-20 dissertation/chapters/08-results.tex
🚧 (results): Population size

@@
 Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides an illustration of the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the \index{heuristic pool}heuristic pool experimental group.
-As before, the illustration is provided in log scale and illustrations for the other classification datasets are left out for brevity as they yield similar illustrations.
+As before, the illustrations are provided in log scale and illustrations for the other classification datasets are left out for brevity as they yield similar illustrations.
 
@@
 
-Figure~\ref{fig:results:heuristic_pool:figures:forest_fires} provides the train and test loss plot for an example regression dataset (forest fires) as it relates to the heuristic pool experimental group.
-As before, the illustration is provided in log scale and illustrations for the other regression datasets are left out for brevity.
+Figure~\ref{fig:results:heuristic_pool:figures:forest_fires} provides the train and test loss plots for an example regression dataset (forest fires) as it relates to the heuristic pool experimental group.
+As before, the illustrations are provided in log scale and illustrations for the other regression datasets are left out for brevity.
 
@@
 As a reminder, five different population sizes are considered.
-These include population sizes of 5, 10, 15, 20, and 25.
-
-Table \ref{tab:results:population:metrics} provides the ranked performance, per dataset, of each of the \acs{BHH} population size configurations.
-Similar to before, the performance rank is calculated as the average rank produced by each population size configuration, for all datasets, over all runs and all training epochs.
+These include population sizes of 5, 10, 15, 20, and 25, and experiments are denoted as such.
+
+Table~\ref{tab:results:population:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the population size variants of the \acs{BHH} that was implemented.
+Similar to before, the test loss is measured at the last epoch for each dataset, over all independent runs.
 
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all independent runs and all epochs.}
-	\label{tab:results:population:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Population - Average Rank}}                                                                                                                                                                                                                                          \\
-			\midrule
-			\textbf{dataset}             & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             & \textbf{25}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.4387 ($\pm$1.34)  & \cellcolor[rgb]{ .714,  .839,  .498}2.7452 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}3.0129 ($\pm$1.386)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4065 ($\pm$1.351)  & \cellcolor[rgb]{ .976,  .427,  .424}3.3968 ($\pm$1.351) \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.7527 ($\pm$1.428) & \cellcolor[rgb]{ .882,  .886,  .51}2.9258 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9656 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.379)   & \cellcolor[rgb]{ .996,  .812,  .498}3.0419 ($\pm$1.437) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8129 ($\pm$1.41)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1591 ($\pm$1.435)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9989 ($\pm$1.42)     & \cellcolor[rgb]{ .992,  .761,  .486}3.0505 ($\pm$1.444) & \cellcolor[rgb]{ .929,  .902,  .514}2.9785 ($\pm$1.341) \\
-			\textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}3.8957 ($\pm$1.335)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8688 ($\pm$1.285)    & \cellcolor[rgb]{ 1,  .875,  .51}2.9645 ($\pm$1.345)     & \cellcolor[rgb]{ .773,  .855,  .502}2.743 ($\pm$1.376)  & \cellcolor[rgb]{ .388,  .745,  .482}2.528 ($\pm$1.328)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .973,  .412,  .42}3.1892 ($\pm$1.391)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.394)    & \cellcolor[rgb]{ 1,  .922,  .518}3.0398 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8559 ($\pm$1.394) & \cellcolor[rgb]{ .447,  .761,  .482}2.8742 ($\pm$1.415) \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}2.7978 ($\pm$1.508) & \cellcolor[rgb]{ .914,  .894,  .51}2.9387 ($\pm$1.413)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2129 ($\pm$1.452)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9613 ($\pm$1.304)    & \cellcolor[rgb]{ .988,  .663,  .471}3.0892 ($\pm$1.353) \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.8151 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.429)    & \cellcolor[rgb]{ .984,  .62,  .463}3.0925 ($\pm$1.323)  & \cellcolor[rgb]{ .973,  .412,  .42}3.128 ($\pm$1.407)   & \cellcolor[rgb]{ .682,  .827,  .498}2.9237 ($\pm$1.463) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .992,  .773,  .49}3.0172 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9215 ($\pm$1.38)  & \cellcolor[rgb]{ .965,  .91,  .514}2.9806 ($\pm$1.383)  & \cellcolor[rgb]{ .973,  .412,  .42}3.0968 ($\pm$1.412)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.488)    \\
-			\textbf{housing}             & \cellcolor[rgb]{ .431,  .757,  .482}2.8366 ($\pm$1.404) & \cellcolor[rgb]{ .388,  .745,  .482}2.8258 ($\pm$1.38)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9753 ($\pm$1.439)    & \cellcolor[rgb]{ 1,  .91,  .518}2.9849 ($\pm$1.411)     & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.368)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8301 ($\pm$1.304) & \cellcolor[rgb]{ .506,  .776,  .486}2.8731 ($\pm$1.397) & \cellcolor[rgb]{ 1,  .922,  .518}3.0505 ($\pm$1.413)    & \cellcolor[rgb]{ .973,  .412,  .42}3.186 ($\pm$1.425)   & \cellcolor[rgb]{ 1,  .886,  .514}3.0602 ($\pm$1.499)    \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.7989 ($\pm$1.205) & \cellcolor[rgb]{ .745,  .847,  .502}2.9441 ($\pm$1.325) & \cellcolor[rgb]{ 1,  .922,  .518}3.0462 ($\pm$1.452)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1366 ($\pm$1.494)  & \cellcolor[rgb]{ 1,  .882,  .51}3.0538 ($\pm$1.566)     \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.6645 ($\pm$1.441) & \cellcolor[rgb]{ .988,  .647,  .467}3.1065 ($\pm$1.327) & \cellcolor[rgb]{ .957,  .91,  .514}3.0247 ($\pm$1.427)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0495 ($\pm$1.442)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1548 ($\pm$1.381)  \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6376 ($\pm$1.436) & \cellcolor[rgb]{ .682,  .827,  .498}2.8645 ($\pm$1.411) & \cellcolor[rgb]{ .992,  .733,  .482}3.1548 ($\pm$1.404) & \cellcolor[rgb]{ .973,  .412,  .42}3.2387 ($\pm$1.397)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1043 ($\pm$1.34)     \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.5505 ($\pm$1.317) & \cellcolor[rgb]{ .62,  .812,  .494}2.7817 ($\pm$1.415)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1581 ($\pm$1.384)    & \cellcolor[rgb]{ 1,  .855,  .506}3.1806 ($\pm$1.394)    & \cellcolor[rgb]{ .973,  .412,  .42}3.329 ($\pm$1.414)   \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}2.8598 ($\pm$1.424) & \cellcolor[rgb]{ .62,  .812,  .494}2.9312 ($\pm$1.389)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0484 ($\pm$1.406)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0952 ($\pm$1.412)  & \cellcolor[rgb]{ .992,  .753,  .486}3.064 ($\pm$1.428)  \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ .988,  .667,  .471}4                   \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all independent runs and all epochs.}
+	\caption{Empirical results showing average test loss and statistics for all population size configurations used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
 	\label{tab:results:population:metrics:loss}%
@@
 
-Table \ref{tab:results:population:metrics} show that that a smaller population size mostly produces the best results, with statistically significant differences on the adult, bike and car datasets.
-A population size of 10, slightly higher than the default of 5 is preferred for the forest fires and housing datasets.
+From Table \ref{tab:results:population:metrics:loss} it can be seen that the lowest population size produced mostly the best performance outcomes, yielding the best average test loss for eight of the fourteen datasets.
+However, the lowest population size also produced the worst performance outcomes for four of the fourteen datasets.
+From the empirical results that show the average test loss, measured at the last epoch, it is not clear which population size configuration produced the overall best results.
+
+As before, the performance of the different \acs{BHH} population size configurations need to be considered for the entire training process.
+As such, Table \ref{tab:results:population:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} population size configurations.
+Similar to before, the performance rank is calculated as the average rank produced by each population size configuration, for all datasets, over all runs and all training epochs.
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all independent runs and all epochs.}
+	\label{tab:results:population:metrics:rank}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccccc}
+			                             & \multicolumn{5}{c}{\textbf{Population - Average Rank}}                                                                                                                                                                                                                                          \\
+			\midrule
+			\textbf{dataset}             & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             & \textbf{25}                                             \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.4387 ($\pm$1.34)  & \cellcolor[rgb]{ .714,  .839,  .498}2.7452 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}3.0129 ($\pm$1.386)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4065 ($\pm$1.351)  & \cellcolor[rgb]{ .976,  .427,  .424}3.3968 ($\pm$1.351) \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.7527 ($\pm$1.428) & \cellcolor[rgb]{ .882,  .886,  .51}2.9258 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9656 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.379)   & \cellcolor[rgb]{ .996,  .812,  .498}3.0419 ($\pm$1.437) \\
+			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8129 ($\pm$1.41)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1591 ($\pm$1.435)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9989 ($\pm$1.42)     & \cellcolor[rgb]{ .992,  .761,  .486}3.0505 ($\pm$1.444) & \cellcolor[rgb]{ .929,  .902,  .514}2.9785 ($\pm$1.341) \\
+			\textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}3.8957 ($\pm$1.335)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8688 ($\pm$1.285)    & \cellcolor[rgb]{ 1,  .875,  .51}2.9645 ($\pm$1.345)     & \cellcolor[rgb]{ .773,  .855,  .502}2.743 ($\pm$1.376)  & \cellcolor[rgb]{ .388,  .745,  .482}2.528 ($\pm$1.328)  \\
+			\textbf{car}                 & \cellcolor[rgb]{ .973,  .412,  .42}3.1892 ($\pm$1.391)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.394)    & \cellcolor[rgb]{ 1,  .922,  .518}3.0398 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8559 ($\pm$1.394) & \cellcolor[rgb]{ .447,  .761,  .482}2.8742 ($\pm$1.415) \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}2.7978 ($\pm$1.508) & \cellcolor[rgb]{ .914,  .894,  .51}2.9387 ($\pm$1.413)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2129 ($\pm$1.452)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9613 ($\pm$1.304)    & \cellcolor[rgb]{ .988,  .663,  .471}3.0892 ($\pm$1.353) \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.8151 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.429)    & \cellcolor[rgb]{ .984,  .62,  .463}3.0925 ($\pm$1.323)  & \cellcolor[rgb]{ .973,  .412,  .42}3.128 ($\pm$1.407)   & \cellcolor[rgb]{ .682,  .827,  .498}2.9237 ($\pm$1.463) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .992,  .773,  .49}3.0172 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9215 ($\pm$1.38)  & \cellcolor[rgb]{ .965,  .91,  .514}2.9806 ($\pm$1.383)  & \cellcolor[rgb]{ .973,  .412,  .42}3.0968 ($\pm$1.412)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.488)    \\
+			\textbf{housing}             & \cellcolor[rgb]{ .431,  .757,  .482}2.8366 ($\pm$1.404) & \cellcolor[rgb]{ .388,  .745,  .482}2.8258 ($\pm$1.38)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9753 ($\pm$1.439)    & \cellcolor[rgb]{ 1,  .91,  .518}2.9849 ($\pm$1.411)     & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.368)  \\
+			\textbf{iris}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8301 ($\pm$1.304) & \cellcolor[rgb]{ .506,  .776,  .486}2.8731 ($\pm$1.397) & \cellcolor[rgb]{ 1,  .922,  .518}3.0505 ($\pm$1.413)    & \cellcolor[rgb]{ .973,  .412,  .42}3.186 ($\pm$1.425)   & \cellcolor[rgb]{ 1,  .886,  .514}3.0602 ($\pm$1.499)    \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.7989 ($\pm$1.205) & \cellcolor[rgb]{ .745,  .847,  .502}2.9441 ($\pm$1.325) & \cellcolor[rgb]{ 1,  .922,  .518}3.0462 ($\pm$1.452)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1366 ($\pm$1.494)  & \cellcolor[rgb]{ 1,  .882,  .51}3.0538 ($\pm$1.566)     \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.6645 ($\pm$1.441) & \cellcolor[rgb]{ .988,  .647,  .467}3.1065 ($\pm$1.327) & \cellcolor[rgb]{ .957,  .91,  .514}3.0247 ($\pm$1.427)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0495 ($\pm$1.442)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1548 ($\pm$1.381)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6376 ($\pm$1.436) & \cellcolor[rgb]{ .682,  .827,  .498}2.8645 ($\pm$1.411) & \cellcolor[rgb]{ .992,  .733,  .482}3.1548 ($\pm$1.404) & \cellcolor[rgb]{ .973,  .412,  .42}3.2387 ($\pm$1.397)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1043 ($\pm$1.34)     \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.5505 ($\pm$1.317) & \cellcolor[rgb]{ .62,  .812,  .494}2.7817 ($\pm$1.415)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1581 ($\pm$1.384)    & \cellcolor[rgb]{ 1,  .855,  .506}3.1806 ($\pm$1.394)    & \cellcolor[rgb]{ .973,  .412,  .42}3.329 ($\pm$1.414)   \\
+			\midrule
+			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}2.8598 ($\pm$1.424) & \cellcolor[rgb]{ .62,  .812,  .494}2.9312 ($\pm$1.389)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0484 ($\pm$1.406)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0952 ($\pm$1.412)  & \cellcolor[rgb]{ .992,  .753,  .486}3.064 ($\pm$1.428)  \\
+			\midrule
+			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ .988,  .667,  .471}4                   \\
+		\end{tabular}%
+
+	}
+\end{table}%
+
+From Table \ref{tab:results:population:metrics:rank} it can be seen that a lower population size of five, mostly produced the best results, with exception to the bike and car datasets, for which the lowest population size configuration produced the worst performance, yielding statistically significant differences in outcomes from the other datasets.
+A larger population size configuration is prefered for the bike and car datasets.
+Furthermore, a population size configuration of ten, slightly higher than the default of five, is preferred for the forest fires and housing datasets.
+Finally, the overall normalised average rank is provided at the bottom of the table, showing that a population size of five produced the best performance outcome across all datasets on average.
 
@@
 
-Figure~\ref{fig:results:population:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each population size configuration as it relates to all datasets, across all runs.
-It is shown that there is no overall statistical significant difference between population sizes and the population size hyper-parameter is problem specific.
+Figure~\ref{fig:results:population:descriptive:descriptive}, shows the correlation of performance with population size for each dataset.
+From these illustrations, it can be seen that the correlation between the population size configuration and performance is different for each dataset, suggesting that the population size hyper-parameter is problem specific.
+However, the overall performance related to each population configuration, across all datasets is not clear from these illustrations.
+
+Figure~\ref{fig:results:population:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each population size configuration as it relates to all datasets, across all runs and epochs.
+It is shown that there is no overall statistical significant difference between population sizes and thus, it can be concluded that the population size hyper-parameter is problem specific.
 
@@
 
-Similar to before, Figure~\ref{fig:results:population:figures:mushroom} provides the train and test, loss and accuracy plot for an example classification dataset (mushroom) as it relates to the population size experimental group.
-As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
+Similar to before, Figure~\ref{fig:results:population:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the population size experimental group.
+As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:population:figures:mushroom}
@@
 As such, all population size configurations make use of the \index{heuristic pool}heuristic pool configuration that includes all the low-level heuristics, including gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
-This explains the sporadic results in Figure \ref{fig:results:population:figures:loss:test:mushroom}.
-Note that the accuracy is almost 100\% and that these sporadic results are simply a result of an attempt to further improve performance even more, by exploring the heuristic space more.
-Since there is not much room for more improvement, the \acs{BHH} is bound to try different heuristic that yield sub-optimal results.
-
-Figure~\ref{fig:results:population:figures:student_performance} provides the train and test loss plot for an example regression dataset (student performance) as it relates to the population size experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
-
-\begin{figure}[htb]
+
+Divergence of the training loss can be observed in Figure \ref{fig:results:population:figures:loss:test:mushroom}.
+Note that, despite the divergence of training loss, the accuracy is still almost 100\% and that these divergent behaviours are simply a result of an attempt to further improve performance, by exploring the heuristic space more.
+For example, heuristics could have momentum as a result of good training progression thus far, but then overshoot good solutions after \index{heuristic}heuristic reselection.
+Overshooting good solutions then causes the \index{heuristic}heuristics to struggle to converge back to good solutions, especially if many different \index{heuristic}heuristics are selected in quick succession.
+A suggestion to this problem is to implement a move-acceptance strategy as was mentioned before.
+At the nineth epoch, the \acs{BHH} fails to produce better solutions on the training set.
+Since there is not much room for more improvement, the \acs{BHH} is bound to try different \index{heuristic}heuristics that yield sub-optimal results.
+From this point onwards, the \acs{BHH} finds slightly better results on the train set, and as a result, produces volatile performance on the test set.
+
+Figure~\ref{fig:results:population:figures:student_performance} provides the train and test loss plots for an example regression dataset (student performance) as it relates to the population size experimental group.
+As before, the illustrations are provided in log scale and illustration of train and test loss plots for the other regression datasets are left out for brevity.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the student performance dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the student performance dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:population:figures:student_performance}
@@
 
-From Figure~\ref{fig:results:population:figures:loss:train:student_performance} it can be seen that the \acs{BHH} with a small population size of 5 starts to diverge away from optimal results as it explores more options in attempt to provide better solutions.
-Divergence can be eliminated by means of an early stopping strategy.
+From Figure~\ref{fig:results:population:figures:loss:train:student_performance} it can be seen that the \acs{BHH} with a low population size of five starts to diverge away from optimal results as it explores different \index{heuristic}heuristics in an attempt to provide better solutions.
+Divergence can be eliminated by means of an early stopping strategy as well as a move-acceptance strategy as mentioned before.
 
@@
 
-Similar to before, Figure~\ref{fig:results:credit:figures:bank} provides the train and test, loss and accuracy plot for an example classification dataset (bank) as it relates to the credit assignment strategy experimental group.
-As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+Similar to before, Figure~\ref{fig:results:credit:figures:bank} provides the train and test, loss and accuracy plots for an example classification dataset (bank) as it relates to the credit assignment strategy experimental group.
+As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the bank dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the bank dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:credit:figures:bank}
@@
 
-Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plot for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plots for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group.
+As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the housing dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the housing dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:credit:figures:housing}
@@
 
-Similar to before, Figure~\ref{fig:results:reselection:figures:car} provides the train and test, loss and accuracy plot for an example classification dataset (car) as it relates to the reselection interval experimental group.
-As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+Similar to before, Figure~\ref{fig:results:reselection:figures:car} provides the train and test, loss and accuracy plots for an example classification dataset (car) as it relates to the reselection interval experimental group.
+As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the car dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the car dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:reselection:figures:car}
@@
 
-Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plot for an example regression dataset (bike) as it relates to the reselection interval experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plots for an example regression dataset (bike) as it relates to the reselection interval experimental group.
+As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the bike dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the bike dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:reselection:figures:bike}
@@
 
-Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test, loss and accuracy plot for an example classification dataset (diabetic) as it relates to the replay window size experimental group.
-As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test, loss and accuracy plots for an example classification dataset (diabetic) as it relates to the replay window size experimental group.
+As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:replay:figures:diabetic}
@@
 
-Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plot for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plots for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group.
+As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:replay:figures:fish_toxicity}
@@
 
-Similar to before, Figure~\ref{fig:results:reanalysis:figures:mushroom} provides the train and test, loss and accuracy plot for an example classification dataset (mushroom) as it relates to the reanalysis interval experimental group.
-As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+Similar to before, Figure~\ref{fig:results:reanalysis:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the reanalysis interval experimental group.
+As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:reanalysis:figures:mushroom}
@@
 
-Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plot for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group.
+As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:reanalysis:figures:parkinsons}
@@
 
-Similar to before, Figure~\ref{fig:results:burn_in:figures:mushroom} provides the train and test, loss and accuracy plot for an example classification dataset (mushroom) as it relates to the burn in window  size experimental group.
-As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+Similar to before, Figure~\ref{fig:results:burn_in:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the burn in window  size experimental group.
+As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:burn_in:figures:mushroom}
@@
 
-Figure~\ref{fig:results:burn_in:figures:parkinsons} provides the train and test loss plot for an example regression dataset (parkinsons) as it relates to the burn in window size experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+Figure~\ref{fig:results:burn_in:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the burn in window size experimental group.
+As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:burn_in:figures:parkinsons}
@@
 
-Similar to before, Figure~\ref{fig:results:normalise:figures:abalone} provides the train and test, loss and accuracy plot for an example classification dataset (abalone) as it relates to the normalisation experimental group.
-As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+Similar to before, Figure~\ref{fig:results:normalise:figures:abalone} provides the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the normalisation experimental group.
+As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the abalone dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the abalone dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:normalise:figures:abalone}
@@
 
-Figure~\ref{fig:results:normalise:figures:bike} provides the train and test loss plot for an example regression dataset (bike) as it relates to the normalisation experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+Figure~\ref{fig:results:normalise:figures:bike} provides the train and test loss plots for an example regression dataset (bike) as it relates to the normalisation experimental group.
+As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the bike dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the bike dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:normalise:figures:bike}
@@
 
-Similar to before, Figure~\ref{fig:results:discounted_rewards:figures:wine_quality} provides the train and test, loss and accuracy plot for an example classification dataset (wine quality) as it relates to the discounted rewards experimental group.
-As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+Similar to before, Figure~\ref{fig:results:discounted_rewards:figures:wine_quality} provides the train and test, loss and accuracy plots for an example classification dataset (wine quality) as it relates to the discounted rewards experimental group.
+As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the wine quality dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the wine quality dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:discounted_rewards:figures:wine_quality}
@@
 
-Figure~\ref{fig:results:discounted_rewards:figures:housing} provides the train and test loss plot for an example regression dataset (housing) as it relates to the discounted rewards experimental group.
-As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+Figure~\ref{fig:results:discounted_rewards:figures:housing} provides the train and test loss plots for an example regression dataset (housing) as it relates to the discounted rewards experimental group.
+As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
 
@@
 	\par\bigskip
-	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the housing dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the housing dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:discounted_rewards:figures:housing}

### 2022-11-20 dissertation/chapters/08-results.tex
🚧 (results): Credit

@@
 Similar to before, Figure~\ref{fig:results:population:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the population size experimental group.
-As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
 
@@
 Figure~\ref{fig:results:population:figures:student_performance} provides the train and test loss plots for an example regression dataset (student performance) as it relates to the population size experimental group.
-As before, the illustrations are provided in log scale and illustration of train and test loss plots for the other regression datasets are left out for brevity.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
 
@@
 As a reminder, five different credit assignment strategies are considered.
-These include the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies as presented in Chapter \ref{chap:bhh}.
-
-Table \ref{tab:results:credit:metrics} provides the ranked performance, per dataset, of each of the \acs{BHH} credit assignment strategy configurations.
-Similar to before, the performance rank is calculated as the average rank produced by each credit assignment strategy configuration, for all datasets, over all runs and all training epochs.
+These include the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies as presented in Chapter \ref{chap:bhh} and experiments are denoted as such.
+
+Table~\ref{tab:results:credit:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the credit assignment strategy variants of the \acs{BHH} that was implemented.
+As before, the test loss is measured at the last epoch for each dataset, over all independent runs.
 
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:credit:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Credit - Average Rank}}                                                                                                                                                                                                                                              \\
-			\midrule
-			\textbf{dataset}             & \textbf{ibest}                                          & \textbf{pbest}                                          & \textbf{rbest}                                          & \textbf{gbest}                                          & \textbf{symmetric}                                      \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}3.1677 ($\pm$1.319)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8613 ($\pm$1.459) & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.399)    & \cellcolor[rgb]{ .863,  .882,  .51}2.9667 ($\pm$1.455)  & \cellcolor[rgb]{ 1,  .89,  .514}3.0075 ($\pm$1.421)     \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.1312 ($\pm$1.347)  & \cellcolor[rgb]{ .91,  .894,  .51}3.0376 ($\pm$1.357)   & \cellcolor[rgb]{ .388,  .745,  .482}2.5914 ($\pm$1.465) & \cellcolor[rgb]{ .98,  .498,  .439}3.128 ($\pm$1.336)   & \cellcolor[rgb]{ 1,  .922,  .518}3.1118 ($\pm$1.487)    \\
-			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8591 ($\pm$1.344) & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.432)    & \cellcolor[rgb]{ .522,  .78,  .486}2.8882 ($\pm$1.41)   & \cellcolor[rgb]{ .996,  .804,  .498}3.0441 ($\pm$1.415) & \cellcolor[rgb]{ .973,  .412,  .42}3.2183 ($\pm$1.442)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .98,  .537,  .447}3.0527 ($\pm$1.34)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0086 ($\pm$1.393)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0667 ($\pm$1.483)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8742 ($\pm$1.339) & \cellcolor[rgb]{ .949,  .906,  .514}2.9978 ($\pm$1.503) \\
-			\textbf{car}                 & \cellcolor[rgb]{ .992,  .729,  .482}3.1151 ($\pm$1.356) & \cellcolor[rgb]{ 1,  .922,  .518}3.0312 ($\pm$1.483)    & \cellcolor[rgb]{ .973,  .412,  .42}3.2516 ($\pm$1.402)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6892 ($\pm$1.354) & \cellcolor[rgb]{ .788,  .859,  .502}2.9129 ($\pm$1.411) \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .996,  .918,  .514}2.8914 ($\pm$1.349) & \cellcolor[rgb]{ .388,  .745,  .482}2.6269 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.4151 ($\pm$1.365)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8925 ($\pm$1.362)    & \cellcolor[rgb]{ .988,  .647,  .467}3.1742 ($\pm$1.449) \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .98,  .541,  .447}3.1516 ($\pm$1.436)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.475) & \cellcolor[rgb]{ .973,  .412,  .42}3.2043 ($\pm$1.299)  & \cellcolor[rgb]{ .749,  .847,  .502}2.8957 ($\pm$1.358) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.277)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1806 ($\pm$1.304)  & \cellcolor[rgb]{ .58,  .8,  .49}2.8559 ($\pm$1.356)     & \cellcolor[rgb]{ .992,  .773,  .49}3.1215 ($\pm$1.502)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7452 ($\pm$1.563) \\
-			\textbf{housing}             & \cellcolor[rgb]{ .984,  .918,  .514}2.9011 ($\pm$1.494) & \cellcolor[rgb]{ .388,  .745,  .482}2.8527 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}2.9022 ($\pm$1.397)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3108 ($\pm$1.324)  & \cellcolor[rgb]{ .992,  .761,  .486}3.0333 ($\pm$1.483) \\
-			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}3.1892 ($\pm$1.428)  & \cellcolor[rgb]{ .996,  .827,  .502}3.0839 ($\pm$1.441) & \cellcolor[rgb]{ 1,  .922,  .518}3.0591 ($\pm$1.376)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8237 ($\pm$1.409) & \cellcolor[rgb]{ .439,  .757,  .482}2.8441 ($\pm$1.384) \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.8075 ($\pm$1.459) & \cellcolor[rgb]{ 1,  .922,  .518}3.0183 ($\pm$1.411)    & \cellcolor[rgb]{ .643,  .816,  .494}2.8957 ($\pm$1.398) & \cellcolor[rgb]{ .992,  .706,  .478}3.0839 ($\pm$1.418) & \cellcolor[rgb]{ .973,  .412,  .42}3.172 ($\pm$1.381)   \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.5645 ($\pm$1.484) & \cellcolor[rgb]{ .898,  .89,  .51}2.8925 ($\pm$1.343)   & \cellcolor[rgb]{ .973,  .412,  .42}3.5065 ($\pm$1.219)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0796 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}2.957 ($\pm$1.455)     \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6624 ($\pm$1.312) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.407)     & \cellcolor[rgb]{ .988,  .643,  .467}3.1892 ($\pm$1.382) & \cellcolor[rgb]{ .612,  .808,  .494}2.7978 ($\pm$1.47)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3215 ($\pm$1.394)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .98,  .494,  .439}3.1871 ($\pm$1.308)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .922,  .518}3.014 ($\pm$1.371)     & \cellcolor[rgb]{ .882,  .886,  .51}2.9419 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.43)   \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .843,  .875,  .506}2.9841 ($\pm$1.39)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9457 ($\pm$1.415) & \cellcolor[rgb]{ .984,  .588,  .455}3.0279 ($\pm$1.414) & \cellcolor[rgb]{ 1,  .922,  .518}2.997 ($\pm$1.402)     & \cellcolor[rgb]{ .973,  .412,  .42}3.0437 ($\pm$1.449)  \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\caption{Empirical results showing average test loss and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
 	\label{tab:results:credit:metrics:loss}%
@@
 		\end{tabular}%
-
 	}
@@
 
-Table \ref{tab:results:credit:metrics} show that different credit assignment strategies perform best for different datasets, from which it can be concluded that the credit assignment strategy hyper-parameter is problem specific.
-It should be noted that the symmetric credit assignment strategy yielded the best results for the forest fires dataset.
+From Table~\ref{tab:results:credit:metrics:loss}, it is not clear which credit assignment strategy yields the best performance for the entire training process.
+As such, Table \ref{tab:results:credit:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} credit assignment strategy configurations.
+Similar to before, the performance rank is calculated as the average rank produced by each credit assignment strategy configuration, for all datasets, over all runs and all training epochs.
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:credit:metrics:rank}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccccc}
+			                             & \multicolumn{5}{c}{\textbf{Credit - Average Rank}}                                                                                                                                                                                                                                              \\
+			\midrule
+			\textbf{dataset}             & \textbf{ibest}                                          & \textbf{pbest}                                          & \textbf{rbest}                                          & \textbf{gbest}                                          & \textbf{symmetric}                                      \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}3.1677 ($\pm$1.319)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8613 ($\pm$1.459) & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.399)    & \cellcolor[rgb]{ .863,  .882,  .51}2.9667 ($\pm$1.455)  & \cellcolor[rgb]{ 1,  .89,  .514}3.0075 ($\pm$1.421)     \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.1312 ($\pm$1.347)  & \cellcolor[rgb]{ .91,  .894,  .51}3.0376 ($\pm$1.357)   & \cellcolor[rgb]{ .388,  .745,  .482}2.5914 ($\pm$1.465) & \cellcolor[rgb]{ .98,  .498,  .439}3.128 ($\pm$1.336)   & \cellcolor[rgb]{ 1,  .922,  .518}3.1118 ($\pm$1.487)    \\
+			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8591 ($\pm$1.344) & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.432)    & \cellcolor[rgb]{ .522,  .78,  .486}2.8882 ($\pm$1.41)   & \cellcolor[rgb]{ .996,  .804,  .498}3.0441 ($\pm$1.415) & \cellcolor[rgb]{ .973,  .412,  .42}3.2183 ($\pm$1.442)  \\
+			\textbf{bike}                & \cellcolor[rgb]{ .98,  .537,  .447}3.0527 ($\pm$1.34)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0086 ($\pm$1.393)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0667 ($\pm$1.483)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8742 ($\pm$1.339) & \cellcolor[rgb]{ .949,  .906,  .514}2.9978 ($\pm$1.503) \\
+			\textbf{car}                 & \cellcolor[rgb]{ .992,  .729,  .482}3.1151 ($\pm$1.356) & \cellcolor[rgb]{ 1,  .922,  .518}3.0312 ($\pm$1.483)    & \cellcolor[rgb]{ .973,  .412,  .42}3.2516 ($\pm$1.402)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6892 ($\pm$1.354) & \cellcolor[rgb]{ .788,  .859,  .502}2.9129 ($\pm$1.411) \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .996,  .918,  .514}2.8914 ($\pm$1.349) & \cellcolor[rgb]{ .388,  .745,  .482}2.6269 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.4151 ($\pm$1.365)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8925 ($\pm$1.362)    & \cellcolor[rgb]{ .988,  .647,  .467}3.1742 ($\pm$1.449) \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .98,  .541,  .447}3.1516 ($\pm$1.436)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.475) & \cellcolor[rgb]{ .973,  .412,  .42}3.2043 ($\pm$1.299)  & \cellcolor[rgb]{ .749,  .847,  .502}2.8957 ($\pm$1.358) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.277)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1806 ($\pm$1.304)  & \cellcolor[rgb]{ .58,  .8,  .49}2.8559 ($\pm$1.356)     & \cellcolor[rgb]{ .992,  .773,  .49}3.1215 ($\pm$1.502)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7452 ($\pm$1.563) \\
+			\textbf{housing}             & \cellcolor[rgb]{ .984,  .918,  .514}2.9011 ($\pm$1.494) & \cellcolor[rgb]{ .388,  .745,  .482}2.8527 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}2.9022 ($\pm$1.397)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3108 ($\pm$1.324)  & \cellcolor[rgb]{ .992,  .761,  .486}3.0333 ($\pm$1.483) \\
+			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}3.1892 ($\pm$1.428)  & \cellcolor[rgb]{ .996,  .827,  .502}3.0839 ($\pm$1.441) & \cellcolor[rgb]{ 1,  .922,  .518}3.0591 ($\pm$1.376)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8237 ($\pm$1.409) & \cellcolor[rgb]{ .439,  .757,  .482}2.8441 ($\pm$1.384) \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.8075 ($\pm$1.459) & \cellcolor[rgb]{ 1,  .922,  .518}3.0183 ($\pm$1.411)    & \cellcolor[rgb]{ .643,  .816,  .494}2.8957 ($\pm$1.398) & \cellcolor[rgb]{ .992,  .706,  .478}3.0839 ($\pm$1.418) & \cellcolor[rgb]{ .973,  .412,  .42}3.172 ($\pm$1.381)   \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.5645 ($\pm$1.484) & \cellcolor[rgb]{ .898,  .89,  .51}2.8925 ($\pm$1.343)   & \cellcolor[rgb]{ .973,  .412,  .42}3.5065 ($\pm$1.219)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0796 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}2.957 ($\pm$1.455)     \\
+			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6624 ($\pm$1.312) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.407)     & \cellcolor[rgb]{ .988,  .643,  .467}3.1892 ($\pm$1.382) & \cellcolor[rgb]{ .612,  .808,  .494}2.7978 ($\pm$1.47)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3215 ($\pm$1.394)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .98,  .494,  .439}3.1871 ($\pm$1.308)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .922,  .518}3.014 ($\pm$1.371)     & \cellcolor[rgb]{ .882,  .886,  .51}2.9419 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.43)   \\
+			\midrule
+			\textbf{avg rank}            & \cellcolor[rgb]{ .843,  .875,  .506}2.9841 ($\pm$1.39)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9457 ($\pm$1.415) & \cellcolor[rgb]{ .984,  .588,  .455}3.0279 ($\pm$1.414) & \cellcolor[rgb]{ 1,  .922,  .518}2.997 ($\pm$1.402)     & \cellcolor[rgb]{ .973,  .412,  .42}3.0437 ($\pm$1.449)  \\
+			\midrule
+			\textbf{normalised avg rank} & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
+		\end{tabular}%
+
+	}
+\end{table}%
+
+Table \ref{tab:results:credit:metrics:rank} shows that different credit assignment strategies perform best for different datasets, from which it can be concluded that the credit assignment strategy hyper-parameter is problem specific.
+Furthermore, the overall normalised average rank across all datasets is provided at the bottom of the table.
+It should be noted that the \textit{symmetric} credit assignment strategy yielded the best results for the forest fires dataset.
 This does not necessarily suggest that random search in the heuristic space yields the best performance for this dataset.
-Instead, it could be the case that the initial selection of heuristics is good enough and that it is difficult to find a performance bias that results in better performance, as all \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool provide good results.
-For all other datasets, it is found that a particular non-symmetric credit assignment strategy yields better results than random search.
+As a reminder, the \textit{symmetric} credit assignment strategy does not bias towards performance, but rather uniformly assigns credit to any heuristic that happens to be selected.
+For the particular case where the \textit{symmetric} credit assignment strategy yielded the best results, it could be the case that the initial selection of heuristics is good enough and that it is difficult to find a performance bias that results in better performance, as all \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool provide good results.
+For all other datasets, it is found that a particular non-\textit{symmetric} credit assignment strategy yields better results.
 
@@
 It is shown that there is no overall statistical significant difference between credit assignment strategies and that the credit assignment strategy hyper-parameter is problem specific.
+At this point it should be mentioned that the credit assignment strategies implemented in this dissertation yield a discrete credit value and that future research should consider a continuous credit value in an attempt to provide a more fine grained indicator of performance, which should be easier to exploit.
 
@@
 Similar to before, Figure~\ref{fig:results:credit:figures:bank} provides the train and test, loss and accuracy plots for an example classification dataset (bank) as it relates to the credit assignment strategy experimental group.
-As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-From Figure~\ref{fig:results:credit:figures:bank} it can be seen that the \textit{pbest} credit assignment strategy (green) diverged away from the current best solution, but was able to return to the current best solution.
-Since the solution found by the \acs{BHH} with the \textit{pbest} credit assignment strategy was already optimal before divergence, it stands to reason that this divergence is a result of the \acs{BHH} exploring other solutions in the heuristic space that yield sub-optimal solutions.
-As mentioned before, a move-acceptance strategy can be incorporated to counteract this effect.
-
-Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plots for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group.
-As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
-
-\begin{figure}[htb]
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 \end{figure}
+
+From Figure~\ref{fig:results:credit:figures:bank} it can be seen that the \textit{pbest} credit assignment strategy diverged away from the current best solution, but was able to return to the current best solution.
+Since the solution found by the \acs{BHH} with the \textit{pbest} credit assignment strategy was already optimal before divergence, it stands to reason that this divergence is a result of the \acs{BHH} exploring other \index{heuristic}heuristics in the heuristic space that yield sub-optimal solutions.
+As mentioned before, a move-acceptance strategy can be incorporated to counteract this effect.
+
+Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plots for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
 
@@
 Similar to before, Figure~\ref{fig:results:reselection:figures:car} provides the train and test, loss and accuracy plots for an example classification dataset (car) as it relates to the reselection interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plots for an example regression dataset (bike) as it relates to the reselection interval experimental group.
-As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
 
@@
 Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test, loss and accuracy plots for an example classification dataset (diabetic) as it relates to the replay window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plots for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group.
-As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
 
@@
 Similar to before, Figure~\ref{fig:results:reanalysis:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the reanalysis interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group.
-As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
 
@@
 Similar to before, Figure~\ref{fig:results:burn_in:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the burn in window  size experimental group.
-As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 Figure~\ref{fig:results:burn_in:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the burn in window size experimental group.
-As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
 
@@
 Similar to before, Figure~\ref{fig:results:normalise:figures:abalone} provides the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the normalisation experimental group.
-As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 Figure~\ref{fig:results:normalise:figures:bike} provides the train and test loss plots for an example regression dataset (bike) as it relates to the normalisation experimental group.
-As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
 
@@
 Similar to before, Figure~\ref{fig:results:discounted_rewards:figures:wine_quality} provides the train and test, loss and accuracy plots for an example classification dataset (wine quality) as it relates to the discounted rewards experimental group.
-As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
 
@@
 Figure~\ref{fig:results:discounted_rewards:figures:housing} provides the train and test loss plots for an example regression dataset (housing) as it relates to the discounted rewards experimental group.
-As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
 

### 2022-11-20 dissertation/chapters/08-results.tex
🚧 (results): Reselection

@@
 	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all independent runs and epochs.}
 	\label{fig:results:standalone:descriptive:descriptive}
@@
 
-Figure~\ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic}heuristic as it relates to all datasets, across all runs.
+Figure~\ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic}heuristic as it relates to all datasets, across all independent runs and epochs.
 
@@
 		\begin{tabular}{r|lll}
-			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Loss}}                                                                                                                     \\
+			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Test Loss}}                                                                                                                     \\
 			\midrule
@@
 Similar to before, Table \ref{tab:results:heuristic_pool:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} \index{heuristic pool}heuristic pool configurations.
-The performance rank is calculated as the average rank produced by each \index{heuristic pool}heuristic pool configuration, for all datasets, over all runs and all epochs.
+The performance rank is calculated as the average rank produced by each \index{heuristic pool}heuristic pool configuration, for all datasets, over all independent runs and epochs.
 
@@
 	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying heuristic pools per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying heuristic pools per dataset, across all independent runs and epochs.}
 	\label{fig:results:heuristic_pool:descriptive:descriptive}
@@
 		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Population - Average Loss}}                                                                                                                                                                                                                                         \\
+			                             & \multicolumn{5}{c}{\textbf{Population - Average Test Loss}}                                                                                                                                                                                                                                        \\
 			\midrule
@@
 As such, Table \ref{tab:results:population:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} population size configurations.
-Similar to before, the performance rank is calculated as the average rank produced by each population size configuration, for all datasets, over all runs and all training epochs.
+Similar to before, the performance rank is calculated as the average rank produced by each population size configuration, for all datasets, over all independent runs and epochs.
 
@@
 	\includegraphics[width=\textwidth]{bhh_population/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of \acs{BHH} with varying population sizes per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of \acs{BHH} with varying population sizes per dataset, across all independent runs and epochs.}
 	\label{fig:results:population:descriptive:descriptive}
@@
 
-Figure~\ref{fig:results:population:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each population size configuration as it relates to all datasets, across all runs and epochs.
+Figure~\ref{fig:results:population:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each population size configuration as it relates to all datasets, across all independent runs and epochs.
 It is shown that there is no overall statistical significant difference between population sizes and thus, it can be concluded that the population size hyper-parameter is problem specific.
@@
 		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Credit - Average Loss}}                                                                                                                                                                                                                               \\
+			                             & \multicolumn{5}{c}{\textbf{Credit - Average Test Loss}}                                                                                                                                                                                                                             \\
 			\midrule
@@
 As such, Table \ref{tab:results:credit:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} credit assignment strategy configurations.
-Similar to before, the performance rank is calculated as the average rank produced by each credit assignment strategy configuration, for all datasets, over all runs and all training epochs.
+Similar to before, the performance rank is calculated as the average rank produced by each credit assignment strategy configuration, for all datasets, over all independent runs and epochs.
 
@@
 	\includegraphics[width=\textwidth]{bhh_credit/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying credit assignment strategies per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying credit assignment strategies per dataset, across all independent runs and epochs.}
 	\label{fig:results:credit:descriptive:descriptive}
@@
 
-Figure~\ref{fig:results:credit:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each credit assignment strategy configuration as it relates to all datasets, across all runs.
+Figure~\ref{fig:results:credit:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each credit assignment strategy configuration as it relates to all datasets, across all independent runs and epochs.
 It is shown that there is no overall statistical significant difference between credit assignment strategies and that the credit assignment strategy hyper-parameter is problem specific.
@@
 These include reselection intervals of 1, 5, 10, 15, and 20.
-
-Table \ref{tab:results:reselection:metrics} provides the ranked performance, per dataset, of each of the \acs{BHH} reselection interval configurations.
-Similar to before, the performance rank is calculated as the average rank produced by reselection interval configuration, for all datasets, over all runs and all training epochs.
+Experiments are denoted as such.
+
+Table~\ref{tab:results:reselection:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the reselection interval variants of the \acs{BHH} that was implemented.
+The test loss is measured at the last epoch for each dataset, over all independent runs.
 
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:reselection:metrics:rank}%
+	\caption{Empirical results showing average test loss and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
+	\label{tab:results:reselection:metrics:loss}%
 	\par\bigskip
@@
 		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Reselection - Average Rank}}                                                                                                                                                                                                                                         \\
-			\midrule
-			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}4.3548 ($\pm$0.976)  & \cellcolor[rgb]{ 1,  .894,  .514}2.8473 ($\pm$1.288)    & \cellcolor[rgb]{ 1,  .922,  .518}2.7505 ($\pm$1.262)    & \cellcolor[rgb]{ .557,  .792,  .49}2.5602 ($\pm$1.299)  & \cellcolor[rgb]{ .388,  .745,  .482}2.4871 ($\pm$1.318) \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.7355 ($\pm$1.405)  & \cellcolor[rgb]{ .984,  .631,  .463}3.4075 ($\pm$1.379) & \cellcolor[rgb]{ 1,  .922,  .518}2.9688 ($\pm$1.278)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4237 ($\pm$1.228) & \cellcolor[rgb]{ .431,  .757,  .482}2.4645 ($\pm$1.291) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}4.5677 ($\pm$0.704)  & \cellcolor[rgb]{ .988,  .635,  .463}3.6323 ($\pm$1.127) & \cellcolor[rgb]{ 1,  .922,  .518}2.4237 ($\pm$1.133)    & \cellcolor[rgb]{ .627,  .812,  .494}2.2462 ($\pm$1.114) & \cellcolor[rgb]{ .388,  .745,  .482}2.1301 ($\pm$1.096) \\
-			\textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}4.7935 ($\pm$0.612)  & \cellcolor[rgb]{ .984,  .608,  .459}3.9204 ($\pm$0.648) & \cellcolor[rgb]{ 1,  .922,  .518}2.5161 ($\pm$0.863)    & \cellcolor[rgb]{ .671,  .824,  .498}2.0763 ($\pm$0.901) & \cellcolor[rgb]{ .388,  .745,  .482}1.6935 ($\pm$0.891) \\
-			\textbf{car}                 & \cellcolor[rgb]{ .973,  .412,  .42}4.6409 ($\pm$0.785)  & \cellcolor[rgb]{ .996,  .847,  .506}2.9527 ($\pm$1.158) & \cellcolor[rgb]{ 1,  .922,  .518}2.6548 ($\pm$1.175)    & \cellcolor[rgb]{ .824,  .871,  .506}2.5312 ($\pm$1.244) & \cellcolor[rgb]{ .388,  .745,  .482}2.2204 ($\pm$1.217) \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ 1,  .859,  .506}3.0129 ($\pm$1.048)    & \cellcolor[rgb]{ .973,  .412,  .42}4.4624 ($\pm$0.869)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7957 ($\pm$1.175)    & \cellcolor[rgb]{ .827,  .871,  .506}2.6065 ($\pm$1.439) & \cellcolor[rgb]{ .388,  .745,  .482}2.1226 ($\pm$1.264) \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}3.7484 ($\pm$1.238)  & \cellcolor[rgb]{ .996,  .851,  .506}3.1376 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}3.0344 ($\pm$1.406)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4656 ($\pm$1.304) & \cellcolor[rgb]{ .545,  .788,  .49}2.614 ($\pm$1.432)   \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}3.8194 ($\pm$1.433)  & \cellcolor[rgb]{ .992,  .706,  .478}3.272 ($\pm$1.248)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8656 ($\pm$1.346)    & \cellcolor[rgb]{ .953,  .906,  .514}2.8194 ($\pm$1.305) & \cellcolor[rgb]{ .388,  .745,  .482}2.2237 ($\pm$1.219) \\
-			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}4.1892 ($\pm$1.099)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0172 ($\pm$1.288) & \cellcolor[rgb]{ .624,  .812,  .494}2.5871 ($\pm$1.354) & \cellcolor[rgb]{ .388,  .745,  .482}2.5312 ($\pm$1.265) & \cellcolor[rgb]{ 1,  .922,  .518}2.6753 ($\pm$1.34)     \\
-			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.424)    & \cellcolor[rgb]{ .973,  .914,  .514}2.971 ($\pm$1.317)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3462 ($\pm$1.418)  & \cellcolor[rgb]{ 1,  .882,  .51}3.014 ($\pm$1.405)      & \cellcolor[rgb]{ .388,  .745,  .482}2.6849 ($\pm$1.429) \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .973,  .412,  .42}4.2065 ($\pm$1.236)  & \cellcolor[rgb]{ 1,  .859,  .506}2.9688 ($\pm$1.299)    & \cellcolor[rgb]{ .631,  .816,  .494}2.586 ($\pm$1.234)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7882 ($\pm$1.34)     & \cellcolor[rgb]{ .388,  .745,  .482}2.4505 ($\pm$1.226) \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .973,  .412,  .42}4.7645 ($\pm$0.756)  & \cellcolor[rgb]{ .992,  .769,  .49}3.1882 ($\pm$1.021)  & \cellcolor[rgb]{ .49,  .773,  .486}2.2957 ($\pm$1.209)  & \cellcolor[rgb]{ 1,  .922,  .518}2.4968 ($\pm$1.128)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2548 ($\pm$1.097) \\
-			\textbf{student performance} & \cellcolor[rgb]{ .976,  .431,  .424}3.971 ($\pm$1.094)  & \cellcolor[rgb]{ .973,  .412,  .42}4.0226 ($\pm$1.12)   & \cellcolor[rgb]{ 1,  .922,  .518}2.4774 ($\pm$1.221)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2495 ($\pm$1.2)   & \cellcolor[rgb]{ .467,  .765,  .486}2.2796 ($\pm$1.132) \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}4.0688 ($\pm$1.122)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9204 ($\pm$1.293)    & \cellcolor[rgb]{ 1,  .906,  .518}2.9559 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4032 ($\pm$1.378) & \cellcolor[rgb]{ .678,  .827,  .498}2.6516 ($\pm$1.28)  \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .973,  .412,  .42}4.0612 ($\pm$1.229)  & \cellcolor[rgb]{ .988,  .69,  .475}3.3372 ($\pm$1.277)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7327 ($\pm$1.283)    & \cellcolor[rgb]{ .647,  .82,  .494}2.5151 ($\pm$1.282)  & \cellcolor[rgb]{ .388,  .745,  .482}2.3538 ($\pm$1.266) \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:reselection:metrics:loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Reselection - Average Loss}}                                                                                                                                                                                                                                         \\
+			                             & \multicolumn{5}{c}{\textbf{Reselection - Average Test Loss}}                                                                                                                                                                                                                                         \\
 			\midrule
@@
 
-Table \ref{tab:results:reselection:metrics} show that larger reselection intervals are mostly preferred, with the exception of the adult dataset.
+From Table~\ref{tab:results:reselection:metrics:loss}, a clear pattern can be observed.
+The empirical results show that, in general, a larger reselection interval is preferred, with the largest reselection intervals yielding the best performance outcomes in the majority of cases, and the lowest reselection interval of one, yielding the worst performance in the majority of cases.
+
+To illustrate the effects of the reselection interval hyper-paramter on the entire trianing, process, Table \ref{tab:results:reselection:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} reselection interval configurations.
+Similar to before, the performance rank is calculated as the average rank produced by reselection interval configuration, for all datasets, over all independent runs and epochs.
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:reselection:metrics:rank}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccccc}
+			                             & \multicolumn{5}{c}{\textbf{Reselection - Average Rank}}                                                                                                                                                                                                                                         \\
+			\midrule
+			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}4.3548 ($\pm$0.976)  & \cellcolor[rgb]{ 1,  .894,  .514}2.8473 ($\pm$1.288)    & \cellcolor[rgb]{ 1,  .922,  .518}2.7505 ($\pm$1.262)    & \cellcolor[rgb]{ .557,  .792,  .49}2.5602 ($\pm$1.299)  & \cellcolor[rgb]{ .388,  .745,  .482}2.4871 ($\pm$1.318) \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.7355 ($\pm$1.405)  & \cellcolor[rgb]{ .984,  .631,  .463}3.4075 ($\pm$1.379) & \cellcolor[rgb]{ 1,  .922,  .518}2.9688 ($\pm$1.278)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4237 ($\pm$1.228) & \cellcolor[rgb]{ .431,  .757,  .482}2.4645 ($\pm$1.291) \\
+			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}4.5677 ($\pm$0.704)  & \cellcolor[rgb]{ .988,  .635,  .463}3.6323 ($\pm$1.127) & \cellcolor[rgb]{ 1,  .922,  .518}2.4237 ($\pm$1.133)    & \cellcolor[rgb]{ .627,  .812,  .494}2.2462 ($\pm$1.114) & \cellcolor[rgb]{ .388,  .745,  .482}2.1301 ($\pm$1.096) \\
+			\textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}4.7935 ($\pm$0.612)  & \cellcolor[rgb]{ .984,  .608,  .459}3.9204 ($\pm$0.648) & \cellcolor[rgb]{ 1,  .922,  .518}2.5161 ($\pm$0.863)    & \cellcolor[rgb]{ .671,  .824,  .498}2.0763 ($\pm$0.901) & \cellcolor[rgb]{ .388,  .745,  .482}1.6935 ($\pm$0.891) \\
+			\textbf{car}                 & \cellcolor[rgb]{ .973,  .412,  .42}4.6409 ($\pm$0.785)  & \cellcolor[rgb]{ .996,  .847,  .506}2.9527 ($\pm$1.158) & \cellcolor[rgb]{ 1,  .922,  .518}2.6548 ($\pm$1.175)    & \cellcolor[rgb]{ .824,  .871,  .506}2.5312 ($\pm$1.244) & \cellcolor[rgb]{ .388,  .745,  .482}2.2204 ($\pm$1.217) \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ 1,  .859,  .506}3.0129 ($\pm$1.048)    & \cellcolor[rgb]{ .973,  .412,  .42}4.4624 ($\pm$0.869)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7957 ($\pm$1.175)    & \cellcolor[rgb]{ .827,  .871,  .506}2.6065 ($\pm$1.439) & \cellcolor[rgb]{ .388,  .745,  .482}2.1226 ($\pm$1.264) \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}3.7484 ($\pm$1.238)  & \cellcolor[rgb]{ .996,  .851,  .506}3.1376 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}3.0344 ($\pm$1.406)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4656 ($\pm$1.304) & \cellcolor[rgb]{ .545,  .788,  .49}2.614 ($\pm$1.432)   \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}3.8194 ($\pm$1.433)  & \cellcolor[rgb]{ .992,  .706,  .478}3.272 ($\pm$1.248)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8656 ($\pm$1.346)    & \cellcolor[rgb]{ .953,  .906,  .514}2.8194 ($\pm$1.305) & \cellcolor[rgb]{ .388,  .745,  .482}2.2237 ($\pm$1.219) \\
+			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}4.1892 ($\pm$1.099)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0172 ($\pm$1.288) & \cellcolor[rgb]{ .624,  .812,  .494}2.5871 ($\pm$1.354) & \cellcolor[rgb]{ .388,  .745,  .482}2.5312 ($\pm$1.265) & \cellcolor[rgb]{ 1,  .922,  .518}2.6753 ($\pm$1.34)     \\
+			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.424)    & \cellcolor[rgb]{ .973,  .914,  .514}2.971 ($\pm$1.317)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3462 ($\pm$1.418)  & \cellcolor[rgb]{ 1,  .882,  .51}3.014 ($\pm$1.405)      & \cellcolor[rgb]{ .388,  .745,  .482}2.6849 ($\pm$1.429) \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ .973,  .412,  .42}4.2065 ($\pm$1.236)  & \cellcolor[rgb]{ 1,  .859,  .506}2.9688 ($\pm$1.299)    & \cellcolor[rgb]{ .631,  .816,  .494}2.586 ($\pm$1.234)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7882 ($\pm$1.34)     & \cellcolor[rgb]{ .388,  .745,  .482}2.4505 ($\pm$1.226) \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .973,  .412,  .42}4.7645 ($\pm$0.756)  & \cellcolor[rgb]{ .992,  .769,  .49}3.1882 ($\pm$1.021)  & \cellcolor[rgb]{ .49,  .773,  .486}2.2957 ($\pm$1.209)  & \cellcolor[rgb]{ 1,  .922,  .518}2.4968 ($\pm$1.128)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2548 ($\pm$1.097) \\
+			\textbf{student performance} & \cellcolor[rgb]{ .976,  .431,  .424}3.971 ($\pm$1.094)  & \cellcolor[rgb]{ .973,  .412,  .42}4.0226 ($\pm$1.12)   & \cellcolor[rgb]{ 1,  .922,  .518}2.4774 ($\pm$1.221)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2495 ($\pm$1.2)   & \cellcolor[rgb]{ .467,  .765,  .486}2.2796 ($\pm$1.132) \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}4.0688 ($\pm$1.122)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9204 ($\pm$1.293)    & \cellcolor[rgb]{ 1,  .906,  .518}2.9559 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4032 ($\pm$1.378) & \cellcolor[rgb]{ .678,  .827,  .498}2.6516 ($\pm$1.28)  \\
+			\midrule
+			\textbf{avg rank}            & \cellcolor[rgb]{ .973,  .412,  .42}4.0612 ($\pm$1.229)  & \cellcolor[rgb]{ .988,  .69,  .475}3.3372 ($\pm$1.277)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7327 ($\pm$1.283)    & \cellcolor[rgb]{ .647,  .82,  .494}2.5151 ($\pm$1.282)  & \cellcolor[rgb]{ .388,  .745,  .482}2.3538 ($\pm$1.266) \\
+			\midrule
+			\textbf{normalised avg rank} & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   \\
+		\end{tabular}%
+
+	}
+\end{table}%
+
+Table \ref{tab:results:reselection:metrics:rank} shows that larger reselection intervals are mostly preferred.
+The overall normalised average rank is given at the bottom of the table and supports this finding.
 This outcome can be explained as follows.
-A larger reselection interval gives the low-level \index{heuristic}heuristics more time to execute, resulting in smoother update steps.
+A larger reselection interval gives the low-level \index{heuristic}heuristics more time to execute, resulting in smoother update steps and provides an opportunity for the \acs{BHH} to gather more evidence of the current selection of \index{heuristic}heuristics' performance in the performance log.
+Both of these effects allow the \acs{BHH} to select better \index{heuristic}heuristics during training.
 This is further supported by the findings from Sections \ref{sec:results:standalone} and \ref{sec:results:heuristic_pool}, that show that gradient-based \index{heuristic}heuristics generally yield the best performance.
-Gradient-based \index{heuristic}heuristics rely on exponentially averaged state parameters in order to produce smooth update steps.
+Most of the gradient-based \index{heuristic}heuristics that are included in the \index{heuristic pool }heuristic pool implement exponentially averaged state parameters in order to produce smooth update steps.
 If reselection occurs too frequently these exponentially averaged state parameters do not yield smooth update steps.
-Finally, it should be noted that the default reanalysis interval is 10.
-At every reanalysis interval, the concentrations for low-level \index{heuristic}heuristics is reset to the default, symmetrical value of 1.
-As such, \acs{BHH} configurations with reselection intervals that are larger than the reanalysis interval only consider performance samples from the last reanalysis window size.
-This suggests that exploitation of low-level \index{heuristic}heuristics is more important than exploration of low-level \index{heuristic}heuristics.
+This is further supported by the inclusion of meta-heuristics such as \acp{GA} and \acs{DE}, which recombine state parameters.
+
+Finally, it should be noted that the default reanalysis interval is ten and the default replay window size is also ten.
+At every reanalysis interval, the concentrations for low-level \index{heuristic}heuristics are reset to the default, symmetrical value of 1.0.
+The replay window size then determines the number of samples in the performance log from which the reanalysis can be done.
+As such, \acs{BHH} configurations with reselection intervals that are larger than the replay window size, will only consider performance samples from the last replay window, which should contain less entries than the reselection interval.
+The reselection interval then directly influences what goes into the performance log.
+Since it is found that reselection intervals larger than the default reanalysis interval and replay window size yield better performance, it can be suggested that exploitation of low-level \index{heuristic}heuristics yields better results than exploration of low-level \index{heuristic}heuristics.
+
+Furthermore, early in the training process, a low reselection interval yields the highest variance of \index{heuristic}heuristic selection.
+Since the default population size is five and the default number of heuristics in the heuristic pool is thirteen, not all heuristics are represented at every training step, causing an unwanted bias towards the \index{heuristic}heuristics that happen to be             selected.
 
 Figure~\ref{fig:results:credit:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reselection interval configurations, per dataset.
+It can be seen that a general pattern occurs for almost all datasets that show an inverse correlation between performance and the reselection interval.
+Some exceptions of this relationship can be observed for the iris and diabetic datasets where an average reselection interval yielded the best results.
 
@@
 	\includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reselection interval values per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reselection interval values per dataset, across all independent runs and epochs.}
 	\label{fig:results:reselection:descriptive:descriptive}
@@
 
-Figure~\ref{fig:results:reselection:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reselection interval configuration as it relates to all datasets, across all runs.
+Figure~\ref{fig:results:reselection:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reselection interval configuration as it relates to all datasets, across all independent runs and epochs.
 
@@
 
-Figure~\ref{fig:results:reselection:descriptive:cd} shows the statistically significant difference in results for the various reselection intervals.
+Figure~\ref{fig:results:reselection:descriptive:cd} shows the statistically significant difference in overall results for the various reselection intervals across all datasets.
 It can be seen that larger reselection intervals statistically perform better than smaller reselection intervals.
+The largest reselection intervals (15 and 20) yielded the best overall results with statistically insignificant differences between them.
 
 Similar to before, Figure~\ref{fig:results:reselection:figures:car} provides the train and test, loss and accuracy plots for an example classification dataset (car) as it relates to the reselection interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plots for an example regression dataset (bike) as it relates to the reselection interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
-
-\begin{figure}[htb]
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-Figures~\ref{fig:results:reselection:figures:loss:train:car} and ~\ref{fig:results:reselection:figures:loss:train:bike} both show a smooth decline in training loss for all reselection interval configurations of the \acs{BHH}, but larger reselection interval configurations are able to provide better results than smaller reselection intervals.
+Figures~\ref{fig:results:reselection:figures:loss:train:car} and ~\ref{fig:results:reselection:figures:loss:train:bike} both show a smooth decline in training loss for all reselection interval configurations of the \acs{BHH}, but larger reselection interval configurations are able to provide better results than lower reselection intervals.
 This further supports the suggestion that exploitation of low-level \index{heuristic}heuristics is more important than exploration of low-level \index{heuristic}heuristics in this particular case.
@@
 Table \ref{tab:results:replay:metrics} provides the ranked performance, per dataset, for each of the \acs{BHH} replay window size configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all runs and all training epochs.
+Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all independent runs and all training epochs.
 
@@
 		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Replay - Average Loss}}                                                                                                                                                                                                                                              \\
+			                             & \multicolumn{5}{c}{\textbf{Replay - Average Test Loss}}                                                                                                                                                                                                                                         \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_replay/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying replay window sizes per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying replay window sizes per dataset, across all independent runs and epochs.}
 	\label{fig:results:replay:descriptive:descriptive}
@@
 
-Figure~\ref{fig:results:replay:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each replay window size configuration as it relates to all datasets, across all runs.
+Figure~\ref{fig:results:replay:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each replay window size configuration as it relates to all datasets, across all independent runs.
 
@@
 Table \ref{tab:results:reanalysis:metrics} provides the ranked performance, per dataset, for each of the \acs{BHH} reanalysis interval configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the reanalysis interval configurations, for all datasets, over all runs and all training epochs.
+Similar to before, the performance rank is calculated as the average rank produced by the reanalysis interval configurations, for all datasets, over all independent runs and all training epochs.
 
@@
 		\begin{tabular}{r|lllll}
-			                             & \multicolumn{5}{c}{\textbf{Reanalysis - Average Loss}}                                                                                                                                                                                                                                         \\
+			                             & \multicolumn{5}{c}{\textbf{Reanalysis - Average Test Loss}}                                                                                                                                                                                                                                        \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reanalysis intervals per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reanalysis intervals per dataset, across all independent runs and epochs.}
 	\label{fig:results:reanalysis:descriptive:descriptive}
@@
 
-Figure~\ref{fig:results:reanalysis:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reanalysis interval configuration as it relates to all datasets, across all runs.
+Figure~\ref{fig:results:reanalysis:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reanalysis interval configuration as it relates to all datasets, across all independent runs and epochs.
 
@@
 Table \ref{tab:results:burn_in:metrics} provides the ranked performance, per dataset, for each of the \acs{BHH} burn in configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the burn in configurations, for all datasets, over all runs and all training epochs.
+Similar to before, the performance rank is calculated as the average rank produced by the burn in configurations, for all datasets, over all independent runs and epochs.
 
@@
 		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Burn In - Average Loss}}                                                                                                                                                                                                                              \\
+			                             & \multicolumn{5}{c}{\textbf{Burn In - Average Test Loss}}                                                                                                                                                                                                                             \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_burn_in/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying burn in values per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying burn in values per dataset, across all independent runs and epochs.}
 	\label{fig:results:burn_in:descriptive:descriptive}
@@
 
-Figure~\ref{fig:results:burn_in:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reanalysis interval configuration as it relates to all datasets, across all runs.
+Figure~\ref{fig:results:burn_in:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reanalysis interval configuration as it relates to all datasets, across all independent runs and epochs.
 
@@
 Table \ref{tab:results:normalise:metrics} provides the ranked performance, per dataset, with normalisation enabled and disabled.
-Similar to before, the performance rank is calculated as the average rank produced by the normalisation configurations, for all datasets, over all runs and all training epochs.
+Similar to before, the performance rank is calculated as the average rank produced by the normalisation configurations, for all datasets, over all independent runs and epochs.
 
@@
 		\begin{tabular}{r|cc}
-			                             & \multicolumn{2}{c}{\textbf{Normalisation - Average Loss}}                                                           \\
+			                             & \multicolumn{2}{c}{\textbf{Normalisation - Average Test Loss}}                                                           \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_normalise/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with normalisation toggled per dataset, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with normalisation toggled per dataset, across all independent runs and epochs.}
 	\label{fig:results:normalise:descriptive:descriptive}
@@
 
-Figure~\ref{fig:results:normalise:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for normalisation configurations that are enabled and disabled, as it relates to all datasets, across all runs.
+Figure~\ref{fig:results:normalise:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for normalisation configurations that are enabled and disabled, as it relates to all datasets, across all independent runs and epochs.
 
@@
 Table \ref{tab:results:discounted_rewards:metrics} provides the ranked performance, per dataset, with discounted rewards enabled and disabled.
-Similar to before, the performance rank is calculated as the average rank produced by the discounted rewards configurations, for all datasets, over all runs and all training epochs.
+Similar to before, the performance rank is calculated as the average rank produced by the discounted rewards configurations, for all datasets, over all independent runs and epochs.
 
@@
 		\begin{tabular}{r|cc}
-			                             & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Loss}}                                                           \\
+			                             & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Test Loss}}                                                           \\
 			\midrule
@@
 	\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with discounted rewards toggled per datasets, across all runs and epochs.}
+	\caption{Descriptive plots for the average ranks of the \acs{BHH} with discounted rewards toggled per datasets, across all independent runs and epochs.}
 	\label{fig:results:discounted_rewards:descriptive:descriptive}
@@
 
-Figure~\ref{fig:results:discounted_rewards:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for discounted rewards configurations that are enabled and disabled, as it relates to all datasets, across all runs.
+Figure~\ref{fig:results:discounted_rewards:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for discounted rewards configurations that are enabled and disabled, as it relates to all datasets, across all independent runs and epochs.
 

### 2022-11-20 dissertation/chapters/08-results.tex
🚧 (results): Replay

@@
 These include replay window sizes of 1, 5, 10, 15, and 20.
-
-Table \ref{tab:results:replay:metrics} provides the ranked performance, per dataset, for each of the \acs{BHH} replay window size configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all independent runs and all training epochs.
+Experiments are denoted as such.
+
+As before, Table~\ref{tab:results:replay:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the replay window size variants of the \acs{BHH} that was implemented.
+The test loss is measured at the last epoch for each dataset, over all independent runs.
 
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:replay:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Replay - Average Rank}}                                                                                                                                                                                                                                              \\
-			\midrule
-			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}3.0258 ($\pm$1.382)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6785 ($\pm$1.455) & \cellcolor[rgb]{ .973,  .412,  .42}3.1968 ($\pm$1.346)  & \cellcolor[rgb]{ .992,  .729,  .482}3.0903 ($\pm$1.385) & \cellcolor[rgb]{ .969,  .91,  .514}3.0086 ($\pm$1.45)   \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.8742 ($\pm$1.385) & \cellcolor[rgb]{ 1,  .871,  .51}3.0151 ($\pm$1.497)     & \cellcolor[rgb]{ 1,  .922,  .518}2.9978 ($\pm$1.429)    & \cellcolor[rgb]{ .765,  .851,  .502}2.9505 ($\pm$1.297) & \cellcolor[rgb]{ .973,  .412,  .42}3.1624 ($\pm$1.443)  \\
-			\textbf{bank}                & \cellcolor[rgb]{ .729,  .843,  .502}2.9484 ($\pm$1.46)  & \cellcolor[rgb]{ .992,  .722,  .482}3.057 ($\pm$1.473)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8602 ($\pm$1.344) & \cellcolor[rgb]{ 1,  .922,  .518}3.0172 ($\pm$1.42)     & \cellcolor[rgb]{ .973,  .412,  .42}3.1172 ($\pm$1.359)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}2.9602 ($\pm$1.274)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7366 ($\pm$1.34)  & \cellcolor[rgb]{ .984,  .58,  .455}3.1452 ($\pm$1.448)  & \cellcolor[rgb]{ .894,  .89,  .51}2.9226 ($\pm$1.417)   & \cellcolor[rgb]{ .973,  .412,  .42}3.2355 ($\pm$1.527)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.7054 ($\pm$1.357) & \cellcolor[rgb]{ .62,  .812,  .494}2.8376 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .882,  .51}3.0763 ($\pm$1.372)     & \cellcolor[rgb]{ .973,  .412,  .42}3.3269 ($\pm$1.463)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0538 ($\pm$1.409)    \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .98,  .545,  .447}3.2473 ($\pm$1.369)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3247 ($\pm$1.406)  & \cellcolor[rgb]{ .388,  .745,  .482}2.5935 ($\pm$1.372) & \cellcolor[rgb]{ .69,  .831,  .498}2.8075 ($\pm$1.384)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0269 ($\pm$1.411)    \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.7269 ($\pm$1.419) & \cellcolor[rgb]{ .992,  .753,  .486}3.0785 ($\pm$1.49)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1774 ($\pm$1.398)  & \cellcolor[rgb]{ .918,  .898,  .51}2.9892 ($\pm$1.386)  & \cellcolor[rgb]{ 1,  .922,  .518}3.028 ($\pm$1.337)     \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8054 ($\pm$1.493) & \cellcolor[rgb]{ .745,  .847,  .502}2.9151 ($\pm$1.381) & \cellcolor[rgb]{ 1,  .922,  .518}2.9914 ($\pm$1.408)    & \cellcolor[rgb]{ .996,  .776,  .49}3.0591 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.229 ($\pm$1.342)   \\
-			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}3.1548 ($\pm$1.301)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.407)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8548 ($\pm$1.45)  & \cellcolor[rgb]{ .992,  .757,  .486}3.0355 ($\pm$1.49)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.404)    \\
-			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}3.072 ($\pm$1.376)     & \cellcolor[rgb]{ .984,  .627,  .463}3.1581 ($\pm$1.419) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.392)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6183 ($\pm$1.396) & \cellcolor[rgb]{ .808,  .867,  .506}2.9312 ($\pm$1.41)  \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .863,  .51}3.0538 ($\pm$1.324)     & \cellcolor[rgb]{ .973,  .412,  .42}3.143 ($\pm$1.437)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0419 ($\pm$1.414)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8613 ($\pm$1.382) & \cellcolor[rgb]{ .502,  .776,  .486}2.8957 ($\pm$1.497) \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .984,  .561,  .451}3.172 ($\pm$1.372)  & \cellcolor[rgb]{ .62,  .812,  .494}2.843 ($\pm$1.244)   & \cellcolor[rgb]{ .388,  .745,  .482}2.6731 ($\pm$1.453) & \cellcolor[rgb]{ 1,  .922,  .518}3.1172 ($\pm$1.419)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1946 ($\pm$1.498)  \\
-			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}3.0398 ($\pm$1.368)    & \cellcolor[rgb]{ .812,  .867,  .506}2.9226 ($\pm$1.411) & \cellcolor[rgb]{ .388,  .745,  .482}2.6548 ($\pm$1.403) & \cellcolor[rgb]{ .996,  .812,  .498}3.0935 ($\pm$1.323) & \cellcolor[rgb]{ .973,  .412,  .42}3.2892 ($\pm$1.487)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}3.1742 ($\pm$1.43)   & \cellcolor[rgb]{ .388,  .745,  .482}2.7323 ($\pm$1.456) & \cellcolor[rgb]{ .976,  .475,  .435}3.1581 ($\pm$1.418) & \cellcolor[rgb]{ 1,  .922,  .518}3.0419 ($\pm$1.356)    & \cellcolor[rgb]{ .706,  .835,  .498}2.8935 ($\pm$1.362) \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ 1,  .91,  .518}2.9972 ($\pm$1.389)     & \cellcolor[rgb]{ .388,  .745,  .482}2.9585 ($\pm$1.426) & \cellcolor[rgb]{ .651,  .82,  .494}2.9744 ($\pm$1.418)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9951 ($\pm$1.404)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0745 ($\pm$1.43)   \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\caption{Empirical results showing average test loss and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
 	\label{tab:results:replay:metrics:loss}%
@@
 
-Table \ref{tab:results:replay:metrics} shows that there is no clear best performing replay window size configuration of the \acs{BHH} for all datasets.
-A replay window size of 1 is best for the air quality, car, fish toxity and forest fires datasets.
-A replay window size of 5 is best for the abalone, adult, bike and wine quality datasets.
-A replay window size of 10 is best for the bank, diabetic, housing, parkinsons and student performance datasets.
-A replay window size of 15 is best for the iris and mushroom datasets.
-Finally, the largest replay window size of 20 did not provide the best outcome for any dataset, but provided results very close to that of the other configurations.
-From these observations it can be concluded that the replay window size is problem specific.
-This means that some problem sets require a shorter replay window size, while others require a larger replay window size.
-
-Furthermore, it can be concluded that some problem sets require more exploration of the \index{heuristic}heuristic space, while other problem sets require more exploitation of low-level \index{heuristic}heuristics.
+Table \ref{tab:results:replay:metrics:rank} provides the ranked performance, per dataset, for each of the \acs{BHH} replay window size configurations.
+Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all independent runs and all training epochs.
+The overall normalised average rank is provided at the end of the table.
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:replay:metrics:rank}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccccc}
+			                             & \multicolumn{5}{c}{\textbf{Replay - Average Rank}}                                                                                                                                                                                                                                              \\
+			\midrule
+			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}3.0258 ($\pm$1.382)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6785 ($\pm$1.455) & \cellcolor[rgb]{ .973,  .412,  .42}3.1968 ($\pm$1.346)  & \cellcolor[rgb]{ .992,  .729,  .482}3.0903 ($\pm$1.385) & \cellcolor[rgb]{ .969,  .91,  .514}3.0086 ($\pm$1.45)   \\
+			\textbf{air quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.8742 ($\pm$1.385) & \cellcolor[rgb]{ 1,  .871,  .51}3.0151 ($\pm$1.497)     & \cellcolor[rgb]{ 1,  .922,  .518}2.9978 ($\pm$1.429)    & \cellcolor[rgb]{ .765,  .851,  .502}2.9505 ($\pm$1.297) & \cellcolor[rgb]{ .973,  .412,  .42}3.1624 ($\pm$1.443)  \\
+			\textbf{bank}                & \cellcolor[rgb]{ .729,  .843,  .502}2.9484 ($\pm$1.46)  & \cellcolor[rgb]{ .992,  .722,  .482}3.057 ($\pm$1.473)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8602 ($\pm$1.344) & \cellcolor[rgb]{ 1,  .922,  .518}3.0172 ($\pm$1.42)     & \cellcolor[rgb]{ .973,  .412,  .42}3.1172 ($\pm$1.359)  \\
+			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}2.9602 ($\pm$1.274)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7366 ($\pm$1.34)  & \cellcolor[rgb]{ .984,  .58,  .455}3.1452 ($\pm$1.448)  & \cellcolor[rgb]{ .894,  .89,  .51}2.9226 ($\pm$1.417)   & \cellcolor[rgb]{ .973,  .412,  .42}3.2355 ($\pm$1.527)  \\
+			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.7054 ($\pm$1.357) & \cellcolor[rgb]{ .62,  .812,  .494}2.8376 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .882,  .51}3.0763 ($\pm$1.372)     & \cellcolor[rgb]{ .973,  .412,  .42}3.3269 ($\pm$1.463)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0538 ($\pm$1.409)    \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .98,  .545,  .447}3.2473 ($\pm$1.369)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3247 ($\pm$1.406)  & \cellcolor[rgb]{ .388,  .745,  .482}2.5935 ($\pm$1.372) & \cellcolor[rgb]{ .69,  .831,  .498}2.8075 ($\pm$1.384)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0269 ($\pm$1.411)    \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.7269 ($\pm$1.419) & \cellcolor[rgb]{ .992,  .753,  .486}3.0785 ($\pm$1.49)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1774 ($\pm$1.398)  & \cellcolor[rgb]{ .918,  .898,  .51}2.9892 ($\pm$1.386)  & \cellcolor[rgb]{ 1,  .922,  .518}3.028 ($\pm$1.337)     \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8054 ($\pm$1.493) & \cellcolor[rgb]{ .745,  .847,  .502}2.9151 ($\pm$1.381) & \cellcolor[rgb]{ 1,  .922,  .518}2.9914 ($\pm$1.408)    & \cellcolor[rgb]{ .996,  .776,  .49}3.0591 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.229 ($\pm$1.342)   \\
+			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}3.1548 ($\pm$1.301)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.407)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8548 ($\pm$1.45)  & \cellcolor[rgb]{ .992,  .757,  .486}3.0355 ($\pm$1.49)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.404)    \\
+			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}3.072 ($\pm$1.376)     & \cellcolor[rgb]{ .984,  .627,  .463}3.1581 ($\pm$1.419) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.392)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6183 ($\pm$1.396) & \cellcolor[rgb]{ .808,  .867,  .506}2.9312 ($\pm$1.41)  \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .863,  .51}3.0538 ($\pm$1.324)     & \cellcolor[rgb]{ .973,  .412,  .42}3.143 ($\pm$1.437)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0419 ($\pm$1.414)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8613 ($\pm$1.382) & \cellcolor[rgb]{ .502,  .776,  .486}2.8957 ($\pm$1.497) \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .984,  .561,  .451}3.172 ($\pm$1.372)  & \cellcolor[rgb]{ .62,  .812,  .494}2.843 ($\pm$1.244)   & \cellcolor[rgb]{ .388,  .745,  .482}2.6731 ($\pm$1.453) & \cellcolor[rgb]{ 1,  .922,  .518}3.1172 ($\pm$1.419)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1946 ($\pm$1.498)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}3.0398 ($\pm$1.368)    & \cellcolor[rgb]{ .812,  .867,  .506}2.9226 ($\pm$1.411) & \cellcolor[rgb]{ .388,  .745,  .482}2.6548 ($\pm$1.403) & \cellcolor[rgb]{ .996,  .812,  .498}3.0935 ($\pm$1.323) & \cellcolor[rgb]{ .973,  .412,  .42}3.2892 ($\pm$1.487)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}3.1742 ($\pm$1.43)   & \cellcolor[rgb]{ .388,  .745,  .482}2.7323 ($\pm$1.456) & \cellcolor[rgb]{ .976,  .475,  .435}3.1581 ($\pm$1.418) & \cellcolor[rgb]{ 1,  .922,  .518}3.0419 ($\pm$1.356)    & \cellcolor[rgb]{ .706,  .835,  .498}2.8935 ($\pm$1.362) \\
+			\midrule
+			\textbf{avg rank}            & \cellcolor[rgb]{ 1,  .91,  .518}2.9972 ($\pm$1.389)     & \cellcolor[rgb]{ .388,  .745,  .482}2.9585 ($\pm$1.426) & \cellcolor[rgb]{ .651,  .82,  .494}2.9744 ($\pm$1.418)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9951 ($\pm$1.404)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0745 ($\pm$1.43)   \\
+			\midrule
+			\textbf{normalised avg rank} & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
+		\end{tabular}%
+
+	}
+\end{table}%
+
+Tables \ref{tab:results:replay:metrics:loss} and \ref{tab:results:replay:metrics:rank} shows that there is no clear overall best performing replay window size configuration of the \acs{BHH}, for all datasets.
+In some cases, a replay window size of one yielded the best results.
+A replay window of one simply considers the last step in the training process.
+This means that memory of past performance actually had a negative impact on the training process in those particular cases.
+It should also be observed that the largest replay window size yielded the worst performance overall and also for the most datasets.
+This suggests that \index{heuristic}heuristic selection is more likely to benefit from short, recent observations in the training process.
+From these observations it can be concluded that past performances of the \index{heuristic}heuristics are not always beneficial to the training process, and that the replay window size is problem specific.
+Furthermore, it can be concluded that some problems require more exploration of the \index{heuristic}heuristic space, while other problem sets require more exploitation of low-level \index{heuristic}heuristics.
 
@@
 
-Figure~\ref{fig:results:replay:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each replay window size configuration as it relates to all datasets, across all independent runs.
+Figure~\ref{fig:results:replay:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each replay window size configuration as it relates to all datasets, across all independent runs and epochs.
 
@@
 
-Figure~\ref{fig:results:replay:descriptive:cd} shows no statistically significant difference in results for the various replay window size configurations as it relates to all datasets.
+Figure~\ref{fig:results:replay:descriptive:cd} shows no overall statistically significant difference in results for the various replay window size configurations as it relates to all datasets.
 
 Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test, loss and accuracy plots for an example classification dataset (diabetic) as it relates to the replay window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plots for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
-
-\begin{figure}[htb]
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 \end{figure}
+
+The divergence that can be seen in Figure~\ref{fig:results:replay:figures:loss:train:diabetic} and \ref{fig:results:replay:figures:loss:test:diabetic} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results, when an optimal solution has already been found.
+As mentioned before, an early stopping strategy as well as a move-acceptance strategy can be incorporated to avoid this effect.
 

### 2022-11-20 dissertation/chapters/08-results.tex
🚧 (results): Reanalysis

@@
 Table \ref{tab:results:replay:metrics:rank} provides the ranked performance, per dataset, for each of the \acs{BHH} replay window size configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all independent runs and all training epochs.
+Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all independent runs and epochs.
 The overall normalised average rank is provided at the end of the table.
@@
 These include reanalysis intervals of 1, 5, 10, 15, and 20.
-
-Table \ref{tab:results:reanalysis:metrics} provides the ranked performance, per dataset, for each of the \acs{BHH} reanalysis interval configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the reanalysis interval configurations, for all datasets, over all independent runs and all training epochs.
+Experiments are denoted as such.
+
+As before, Table~\ref{tab:results:reanalysis:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the reanalysis interval variants of the \acs{BHH} that was implemented.
+The test loss is measured at the last epoch for each dataset, over all independent runs.
 
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:reanalysis:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Reanalysis - Average Rank}}                                                                                                                                                                                                                                          \\
-			\midrule
-			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.9849 ($\pm$1.397)    & \cellcolor[rgb]{ .988,  .69,  .475}3.0699 ($\pm$1.442)  & \cellcolor[rgb]{ .973,  .412,  .42}3.171 ($\pm$1.32)    & \cellcolor[rgb]{ .835,  .875,  .506}2.9441 ($\pm$1.445) & \cellcolor[rgb]{ .388,  .745,  .482}2.8301 ($\pm$1.443) \\
-			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9613 ($\pm$1.344)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8387 ($\pm$1.438) & \cellcolor[rgb]{ .973,  .412,  .42}3.2559 ($\pm$1.402)  & \cellcolor[rgb]{ .992,  .765,  .49}3.0538 ($\pm$1.42)   & \cellcolor[rgb]{ .643,  .816,  .494}2.8903 ($\pm$1.43)  \\
-			\textbf{bank}                & \cellcolor[rgb]{ .988,  .647,  .467}3.1161 ($\pm$1.432) & \cellcolor[rgb]{ 1,  .922,  .518}3.0452 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7355 ($\pm$1.398) & \cellcolor[rgb]{ .765,  .851,  .502}2.928 ($\pm$1.403)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1753 ($\pm$1.415)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .988,  .698,  .475}3.1409 ($\pm$1.258) & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.391) & \cellcolor[rgb]{ .973,  .412,  .42}3.1946 ($\pm$1.365)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0978 ($\pm$1.498)    & \cellcolor[rgb]{ .478,  .769,  .486}2.8086 ($\pm$1.491) \\
-			\textbf{car}                 & \cellcolor[rgb]{ 1,  .906,  .518}3.1237 ($\pm$1.423)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7237 ($\pm$1.358) & \cellcolor[rgb]{ .62,  .812,  .494}2.8763 ($\pm$1.299)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1538 ($\pm$1.385)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1226 ($\pm$1.547)    \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}3.2452 ($\pm$1.305)  & \cellcolor[rgb]{ .996,  .824,  .502}3.072 ($\pm$1.391)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7785 ($\pm$1.407) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.425)     & \cellcolor[rgb]{ .624,  .812,  .494}2.8753 ($\pm$1.494) \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .992,  .725,  .482}3.1452 ($\pm$1.362) & \cellcolor[rgb]{ .894,  .89,  .51}3.0032 ($\pm$1.445)   & \cellcolor[rgb]{ .973,  .412,  .42}3.2172 ($\pm$1.364)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1 ($\pm$1.409)       & \cellcolor[rgb]{ .388,  .745,  .482}2.5344 ($\pm$1.388) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8398 ($\pm$1.369) & \cellcolor[rgb]{ .98,  .51,  .439}3.1215 ($\pm$1.471)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0043 ($\pm$1.318)    & \cellcolor[rgb]{ .557,  .792,  .49}2.886 ($\pm$1.354)   & \cellcolor[rgb]{ .973,  .412,  .42}3.1484 ($\pm$1.526)  \\
-			\textbf{housing}             & \cellcolor[rgb]{ .976,  .416,  .424}3.3129 ($\pm$1.311) & \cellcolor[rgb]{ 1,  .922,  .518}2.9892 ($\pm$1.393)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6871 ($\pm$1.483) & \cellcolor[rgb]{ .404,  .749,  .482}2.6968 ($\pm$1.496) & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.236)   \\
-			\textbf{iris}                & \cellcolor[rgb]{ .98,  .522,  .443}3.1204 ($\pm$1.301)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.391)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1269 ($\pm$1.432)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.449) & \cellcolor[rgb]{ .894,  .89,  .51}3.0194 ($\pm$1.435)   \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}2.9312 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1538 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8473 ($\pm$1.384) & \cellcolor[rgb]{ .98,  .486,  .435}3.1215 ($\pm$1.453)  & \cellcolor[rgb]{ .796,  .863,  .506}2.9032 ($\pm$1.471) \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .937,  .902,  .514}2.9688 ($\pm$1.385) & \cellcolor[rgb]{ 1,  .922,  .518}3.0086 ($\pm$1.356)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6129 ($\pm$1.481) & \cellcolor[rgb]{ .992,  .761,  .49}3.1032 ($\pm$1.38)   & \cellcolor[rgb]{ .973,  .412,  .42}3.3065 ($\pm$1.378)  \\
-			\textbf{student performance} & \cellcolor[rgb]{ .89,  .89,  .51}2.9409 ($\pm$1.412)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1849 ($\pm$1.38)   & \cellcolor[rgb]{ .388,  .745,  .482}2.771 ($\pm$1.41)   & \cellcolor[rgb]{ .98,  .561,  .451}3.1258 ($\pm$1.366)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.467)    \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8032 ($\pm$1.444) & \cellcolor[rgb]{ .976,  .914,  .514}2.9204 ($\pm$1.304) & \cellcolor[rgb]{ .973,  .412,  .42}3.2022 ($\pm$1.41)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9247 ($\pm$1.349)    & \cellcolor[rgb]{ .98,  .51,  .439}3.1495 ($\pm$1.517)   \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .973,  .412,  .42}3.0453 ($\pm$1.374)  & \cellcolor[rgb]{ 1,  .922,  .518}2.999 ($\pm$1.403)     & \cellcolor[rgb]{ .388,  .745,  .482}2.9629 ($\pm$1.409) & \cellcolor[rgb]{ .773,  .855,  .502}2.9858 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .871,  .51}3.0039 ($\pm$1.462)     \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .988,  .667,  .471}4                   \\
-		\end{tabular}%
-
-	}
-
-\end{table}%
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\caption{Empirical results showing average test loss and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
 	\label{tab:results:reanalysis:metrics:loss}%
@@
 		\end{tabular}%
-
 	}
-
 \end{table}%
 
-Table \ref{tab:results:reanalysis:metrics} shows that there is no clear best performing reanalysis interval configuration of the \acs{BHH} for all datasets.
-A reanalysis interval of 1 is best for the adult, forest fires and wine quality datasets.
-A reanalysis interval of 5 is best for the adult, air quality, bike and car datasets.
-A reanalysis interval of 10 is best for the adult, bank, diabetic, housing, mushroom, parkinsons and wine quality datasets.
-A reanalysis interval of 15 is best for the iris dataset.
-Finally, the largest reanalysis interval of 20 is best for the abalone and fish toxicity datasets.
+Table \ref{tab:results:reanalysis:metrics:rank} provides the ranked performance, per dataset, for each of the \acs{BHH} reanalysis interval configurations.
+Similar to before, the performance rank is calculated as the average rank produced by the reanalysis interval configurations, for all datasets, over all independent runs and epochs.
+The overall normalised average ranks are provided at the bottom of the table.
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:reanalysis:metrics:rank}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccccc}
+			                             & \multicolumn{5}{c}{\textbf{Reanalysis - Average Rank}}                                                                                                                                                                                                                                          \\
+			\midrule
+			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.9849 ($\pm$1.397)    & \cellcolor[rgb]{ .988,  .69,  .475}3.0699 ($\pm$1.442)  & \cellcolor[rgb]{ .973,  .412,  .42}3.171 ($\pm$1.32)    & \cellcolor[rgb]{ .835,  .875,  .506}2.9441 ($\pm$1.445) & \cellcolor[rgb]{ .388,  .745,  .482}2.8301 ($\pm$1.443) \\
+			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9613 ($\pm$1.344)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8387 ($\pm$1.438) & \cellcolor[rgb]{ .973,  .412,  .42}3.2559 ($\pm$1.402)  & \cellcolor[rgb]{ .992,  .765,  .49}3.0538 ($\pm$1.42)   & \cellcolor[rgb]{ .643,  .816,  .494}2.8903 ($\pm$1.43)  \\
+			\textbf{bank}                & \cellcolor[rgb]{ .988,  .647,  .467}3.1161 ($\pm$1.432) & \cellcolor[rgb]{ 1,  .922,  .518}3.0452 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7355 ($\pm$1.398) & \cellcolor[rgb]{ .765,  .851,  .502}2.928 ($\pm$1.403)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1753 ($\pm$1.415)  \\
+			\textbf{bike}                & \cellcolor[rgb]{ .988,  .698,  .475}3.1409 ($\pm$1.258) & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.391) & \cellcolor[rgb]{ .973,  .412,  .42}3.1946 ($\pm$1.365)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0978 ($\pm$1.498)    & \cellcolor[rgb]{ .478,  .769,  .486}2.8086 ($\pm$1.491) \\
+			\textbf{car}                 & \cellcolor[rgb]{ 1,  .906,  .518}3.1237 ($\pm$1.423)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7237 ($\pm$1.358) & \cellcolor[rgb]{ .62,  .812,  .494}2.8763 ($\pm$1.299)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1538 ($\pm$1.385)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1226 ($\pm$1.547)    \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}3.2452 ($\pm$1.305)  & \cellcolor[rgb]{ .996,  .824,  .502}3.072 ($\pm$1.391)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7785 ($\pm$1.407) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.425)     & \cellcolor[rgb]{ .624,  .812,  .494}2.8753 ($\pm$1.494) \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ .992,  .725,  .482}3.1452 ($\pm$1.362) & \cellcolor[rgb]{ .894,  .89,  .51}3.0032 ($\pm$1.445)   & \cellcolor[rgb]{ .973,  .412,  .42}3.2172 ($\pm$1.364)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1 ($\pm$1.409)       & \cellcolor[rgb]{ .388,  .745,  .482}2.5344 ($\pm$1.388) \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8398 ($\pm$1.369) & \cellcolor[rgb]{ .98,  .51,  .439}3.1215 ($\pm$1.471)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0043 ($\pm$1.318)    & \cellcolor[rgb]{ .557,  .792,  .49}2.886 ($\pm$1.354)   & \cellcolor[rgb]{ .973,  .412,  .42}3.1484 ($\pm$1.526)  \\
+			\textbf{housing}             & \cellcolor[rgb]{ .976,  .416,  .424}3.3129 ($\pm$1.311) & \cellcolor[rgb]{ 1,  .922,  .518}2.9892 ($\pm$1.393)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6871 ($\pm$1.483) & \cellcolor[rgb]{ .404,  .749,  .482}2.6968 ($\pm$1.496) & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.236)   \\
+			\textbf{iris}                & \cellcolor[rgb]{ .98,  .522,  .443}3.1204 ($\pm$1.301)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.391)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1269 ($\pm$1.432)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.449) & \cellcolor[rgb]{ .894,  .89,  .51}3.0194 ($\pm$1.435)   \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}2.9312 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1538 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8473 ($\pm$1.384) & \cellcolor[rgb]{ .98,  .486,  .435}3.1215 ($\pm$1.453)  & \cellcolor[rgb]{ .796,  .863,  .506}2.9032 ($\pm$1.471) \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .937,  .902,  .514}2.9688 ($\pm$1.385) & \cellcolor[rgb]{ 1,  .922,  .518}3.0086 ($\pm$1.356)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6129 ($\pm$1.481) & \cellcolor[rgb]{ .992,  .761,  .49}3.1032 ($\pm$1.38)   & \cellcolor[rgb]{ .973,  .412,  .42}3.3065 ($\pm$1.378)  \\
+			\textbf{student performance} & \cellcolor[rgb]{ .89,  .89,  .51}2.9409 ($\pm$1.412)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1849 ($\pm$1.38)   & \cellcolor[rgb]{ .388,  .745,  .482}2.771 ($\pm$1.41)   & \cellcolor[rgb]{ .98,  .561,  .451}3.1258 ($\pm$1.366)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.467)    \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8032 ($\pm$1.444) & \cellcolor[rgb]{ .976,  .914,  .514}2.9204 ($\pm$1.304) & \cellcolor[rgb]{ .973,  .412,  .42}3.2022 ($\pm$1.41)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9247 ($\pm$1.349)    & \cellcolor[rgb]{ .98,  .51,  .439}3.1495 ($\pm$1.517)   \\
+			\midrule
+			\textbf{avg rank}            & \cellcolor[rgb]{ .973,  .412,  .42}3.0453 ($\pm$1.374)  & \cellcolor[rgb]{ 1,  .922,  .518}2.999 ($\pm$1.403)     & \cellcolor[rgb]{ .388,  .745,  .482}2.9629 ($\pm$1.409) & \cellcolor[rgb]{ .773,  .855,  .502}2.9858 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .871,  .51}3.0039 ($\pm$1.462)     \\
+			\midrule
+			\textbf{normalised avg rank} & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .988,  .667,  .471}4                   \\
+		\end{tabular}%
+	}
+\end{table}%
+
+Tables \ref{tab:results:reanalysis:metrics:loss} and \ref{tab:results:reanalysis:metrics:rank} shows that there is no clear overall best performing reanalysis interval configuration of the \acs{BHH} for all datasets.
 
 It should be noted that the configuration and results for the reanalysis interval configurations should be considered along with the reselection interval configurations as reselection is based on the outcome of the reanalysis step.
-For the \acs{BHH} baseline configuration, both the reselection and reanalysis interval hyper-parameters have default value of 10.
+Furthermore, the reanalysis interval configurations should also be considered along with the replay window size, as the replay window size determines the number of performance log samples to reanalyse.
+For the \acs{BHH} baseline configuration, the reselection and reanalysis interval hyper-parameters have default values of ten, and the replay window size also has a default value of ten.
+These values are deliberately chosen so that there is a balance between the different hyper-parameters from which empirical conclusions can be made.
+
 Furthermore, the smaller the reanalysis interval, the more frequently the \acs{BHH} resets concentration parameters.
-A reanalysis interval of 1 provides a case where only the last executed step is considered for reanalysis and thus provides a shortsighted view on the relevance of past performance, and thus, reselection is based only on the most recent performance of each selected \index{heuristic}heuristic.
+The smaller the replay window size, the less performance samples in the performance log are considered for reanalysis.
+A replay window size of one yields a case where only the last executed step is considered for reanalysis and thus provides a shortsighted view on the relevance of past performance.
+As such, reselection is based only on the most recent performance of each selected \index{heuristic}heuristic.
+However, if the reanalysis interval is larger than the replay window size, the \acs{BHH} does not update its beliefs fast enough, and as a result, \index{heuristic}heuristic performance evidence is lost.
 
@@
 Figure~\ref{fig:results:reanalysis:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reanalysis interval configuration as it relates to all datasets, across all independent runs and epochs.
+From Figure~\ref{fig:results:reanalysis:descriptive:cd}, it can be concluded that the best reanalysis interval is problem specific.
 
@@
 
-Figure~\ref{fig:results:reanalysis:descriptive:cd} shows no statistically significant difference in results for the various reanalysis interval configurations as it relates to all datasets.
+Figure~\ref{fig:results:reanalysis:descriptive:cd} shows no overall statistically significant difference in results for the various reanalysis interval configurations as it relates to all datasets.
 
 Similar to before, Figure~\ref{fig:results:reanalysis:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the reanalysis interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
-
-\begin{figure}[htb]
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 \end{figure}
+
+The divergence that can be seen in Figure~\ref{fig:results:reanalysis:figures:loss:train:mushroom} and \ref{fig:results:reanalysis:figures:loss:test:mushroom} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results, when an optimal solution has already been found.
+As mentioned before, an early stopping strategy as well as a move-acceptance strategy can be incorporated to avoid this effect.
 

### 2022-11-20 dissertation/chapters/08-results.tex
🚧 (result): Burn In

@@
 
-Similar to before, Table \ref{tab:results:heuristic_pool:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} \index{heuristic pool}heuristic pool configurations.
+Similar to before, Table \ref{tab:results:heuristic_pool:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} \index{heuristic pool}heuristic pool configurations.
 The performance rank is calculated as the average rank produced by each \index{heuristic pool}heuristic pool configuration, for all datasets, over all independent runs and epochs.
@@
 As before, the performance of the different \acs{BHH} population size configurations need to be considered for the entire training process.
-As such, Table \ref{tab:results:population:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} population size configurations.
+As such, Table \ref{tab:results:population:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} population size configurations.
 Similar to before, the performance rank is calculated as the average rank produced by each population size configuration, for all datasets, over all independent runs and epochs.
@@
 From Table~\ref{tab:results:credit:metrics:loss}, it is not clear which credit assignment strategy yields the best performance for the entire training process.
-As such, Table \ref{tab:results:credit:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} credit assignment strategy configurations.
+As such, Table \ref{tab:results:credit:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} credit assignment strategy configurations.
 Similar to before, the performance rank is calculated as the average rank produced by each credit assignment strategy configuration, for all datasets, over all independent runs and epochs.
@@
 
-To illustrate the effects of the reselection interval hyper-paramter on the entire trianing, process, Table \ref{tab:results:reselection:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} reselection interval configurations.
+To illustrate the effects of the reselection interval hyper-paramter on the entire trianing, process, Table \ref{tab:results:reselection:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} reselection interval configurations.
 Similar to before, the performance rank is calculated as the average rank produced by reselection interval configuration, for all datasets, over all independent runs and epochs.
@@
 
-Table \ref{tab:results:replay:metrics:rank} provides the ranked performance, per dataset, for each of the \acs{BHH} replay window size configurations.
+Table \ref{tab:results:replay:metrics:rank} provides the average ranked performance, per dataset, for each of the \acs{BHH} replay window size configurations.
 Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all independent runs and epochs.
@@
 
-Table \ref{tab:results:reanalysis:metrics:rank} provides the ranked performance, per dataset, for each of the \acs{BHH} reanalysis interval configurations.
+Table \ref{tab:results:reanalysis:metrics:rank} provides the average ranked performance, per dataset, for each of the \acs{BHH} reanalysis interval configurations.
 Similar to before, the performance rank is calculated as the average rank produced by the reanalysis interval configurations, for all datasets, over all independent runs and epochs.
@@
 
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{burn in} hyper-parameter.
+This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{burn in} window size hyper-parameter.
 Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, five different burn ins are considered.
-These include burn ins of 0, 5, 10, 15, and 20.
-
-Table \ref{tab:results:burn_in:metrics} provides the ranked performance, per dataset, for each of the \acs{BHH} burn in configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the burn in configurations, for all datasets, over all independent runs and epochs.
+Five different burn in window sizes are considered.
+These include burn in window sizes of 0, 5, 10, 15, and 20.
+Experiments are denoted as such.
+
+As a reminder, the burn in window size is a hyper-parameter that is borrowed from the \acs{MCMC} algorithm, and provides a window whereby exploration is encouraged in order to obtain sufficient samples of \index{heuristic}heuristic performance evidence for statistical inference.
+
+As before, Table~\ref{tab:results:burn_in:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the burn in window size variants of the \acs{BHH} that was implemented.
+The test loss is measured at the last epoch for each dataset, over all independent runs and epochs.
 
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:burn_in:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		% Table generated by Excel2LaTeX from sheet 'rank'
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Burn In - Average Rank}}                                                                                                                                                                                                                                             \\
-			\midrule
-			\textbf{dataset}             & \textbf{0}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.9151 ($\pm$1.395)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6935 ($\pm$1.393) & \cellcolor[rgb]{ 1,  .922,  .518}2.9172 ($\pm$1.384)    & \cellcolor[rgb]{ .788,  .859,  .502}2.8398 ($\pm$1.352) & \cellcolor[rgb]{ .973,  .412,  .42}3.6344 ($\pm$1.357)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9097 ($\pm$1.441)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6817 ($\pm$1.427) & \cellcolor[rgb]{ .624,  .812,  .494}2.7699 ($\pm$1.344) & \cellcolor[rgb]{ .973,  .412,  .42}3.372 ($\pm$1.314)   & \cellcolor[rgb]{ .98,  .529,  .443}3.2667 ($\pm$1.412)  \\
-			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.7301 ($\pm$1.321) & \cellcolor[rgb]{ .816,  .867,  .506}2.8194 ($\pm$1.335) & \cellcolor[rgb]{ 1,  .922,  .518}2.857 ($\pm$1.485)     & \cellcolor[rgb]{ 1,  .878,  .51}2.9312 ($\pm$1.384)     & \cellcolor[rgb]{ .973,  .412,  .42}3.6624 ($\pm$1.339)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}1.9237 ($\pm$0.981) & \cellcolor[rgb]{ .545,  .788,  .49}2.1806 ($\pm$1.024)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9237 ($\pm$1.274)    & \cellcolor[rgb]{ .992,  .729,  .482}3.5054 ($\pm$1.186) & \cellcolor[rgb]{ .973,  .412,  .42}4.4667 ($\pm$0.851)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.3624 ($\pm$1.231) & \cellcolor[rgb]{ .533,  .784,  .49}2.5882 ($\pm$1.425)  & \cellcolor[rgb]{ 1,  .922,  .518}3.2978 ($\pm$1.392)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3796 ($\pm$1.271)  & \cellcolor[rgb]{ .976,  .459,  .431}3.372 ($\pm$1.401)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}2.4054 ($\pm$1.358) & \cellcolor[rgb]{ .604,  .808,  .494}2.7011 ($\pm$1.358) & \cellcolor[rgb]{ 1,  .902,  .518}3.2398 ($\pm$1.372)    & \cellcolor[rgb]{ 1,  .922,  .518}3.2323 ($\pm$1.326)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4215 ($\pm$1.396)  \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}3.0634 ($\pm$1.459)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7935 ($\pm$1.402) & \cellcolor[rgb]{ .447,  .761,  .482}2.8204 ($\pm$1.513) & \cellcolor[rgb]{ .996,  .796,  .494}3.1022 ($\pm$1.346) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.295)  \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8161 ($\pm$1.33)  & \cellcolor[rgb]{ .808,  .867,  .506}2.8495 ($\pm$1.383) & \cellcolor[rgb]{ 1,  .922,  .518}2.8645 ($\pm$1.409)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.398)  & \cellcolor[rgb]{ .988,  .698,  .475}3.0925 ($\pm$1.471) \\
-			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}2.6903 ($\pm$1.384) & \cellcolor[rgb]{ .91,  .894,  .51}2.9516 ($\pm$1.318)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.442)    & \cellcolor[rgb]{ .996,  .82,  .498}3.0581 ($\pm$1.344)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3032 ($\pm$1.51)   \\
-			\textbf{iris}                & \cellcolor[rgb]{ .922,  .898,  .51}2.9473 ($\pm$1.461)  & \cellcolor[rgb]{ 1,  .922,  .518}2.972 ($\pm$1.367)     & \cellcolor[rgb]{ .973,  .412,  .42}3.1903 ($\pm$1.449)  & \cellcolor[rgb]{ .388,  .745,  .482}2.771 ($\pm$1.369)  & \cellcolor[rgb]{ .984,  .58,  .455}3.1194 ($\pm$1.387)  \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.2065 ($\pm$1.249) & \cellcolor[rgb]{ .863,  .882,  .51}2.9376 ($\pm$1.298)  & \cellcolor[rgb]{ 1,  .902,  .514}3.1613 ($\pm$1.297)    & \cellcolor[rgb]{ 1,  .922,  .518}3.1441 ($\pm$1.401)    & \cellcolor[rgb]{ .973,  .412,  .42}3.5226 ($\pm$1.501)  \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.2796 ($\pm$1.282) & \cellcolor[rgb]{ 1,  .922,  .518}2.8892 ($\pm$1.247)    & \cellcolor[rgb]{ .816,  .867,  .506}2.7065 ($\pm$1.314) & \cellcolor[rgb]{ .984,  .616,  .459}3.3968 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.728 ($\pm$1.33)    \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.1452 ($\pm$1.205) & \cellcolor[rgb]{ .741,  .843,  .502}2.6946 ($\pm$1.403) & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.352)    & \cellcolor[rgb]{ .984,  .561,  .451}3.4581 ($\pm$1.354) & \cellcolor[rgb]{ .973,  .412,  .42}3.6054 ($\pm$1.231)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .925,  .898,  .51}2.9699 ($\pm$1.437)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0108 ($\pm$1.304)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6634 ($\pm$1.419) & \cellcolor[rgb]{ .988,  .659,  .471}3.1247 ($\pm$1.398) & \cellcolor[rgb]{ .973,  .412,  .42}3.2312 ($\pm$1.447)  \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}2.5975 ($\pm$1.376) & \cellcolor[rgb]{ .671,  .824,  .498}2.7688 ($\pm$1.353) & \cellcolor[rgb]{ 1,  .922,  .518}2.9647 ($\pm$1.404)    & \cellcolor[rgb]{ .988,  .694,  .475}3.1923 ($\pm$1.367) & \cellcolor[rgb]{ .973,  .412,  .42}3.4747 ($\pm$1.402)  \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\caption{Empirical results showing average test loss and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
 	\label{tab:results:burn_in:metrics:loss}%
@@
 
-Table \ref{tab:results:burn_in:metrics} shows that, in general, a configuration where there is no burn in produces the best results.
-This can be explains from the fact that most of the training progress that is made is done early in the training process.
-The faster the \acs{BHH} is able to start learning, the better.
-Note that reselection still occurs during a burn in window, but burn in overrides the reanalysis interval is the burn in window size is larger than the reanalysis window.
+From Table \ref{tab:results:burn_in:metrics:loss} a noticeable pattern can be observed.
+Generally it is found that a small burn in window size produces better results than larger burn in window sizes.
+The largest burn in window size of 20 produced the worst results in nine out of thirteen datasets.
+Some exceptions include the mushroom and the iris datasets.
+Notice that burn in window sizes smaller than the default reanalysis interval, reselection interval and replay window size of ten, generally produced the best results.
+However, Table \ref{tab:results:burn_in:metrics:loss} does not provide a clear view of the overall performance produced by different burn in window size configurations for the entire training process.
+
+In order to obtain a better view of the overall performance produced by different burn in window size configurations for the entire training process, Table \ref{tab:results:burn_in:metrics:rank} provides the average ranked performance, per dataset, for each of the \acs{BHH} burn in configurations.
+Similar to before, the performance rank is calculated as the average rank produced by the burn in window size configurations, for all datasets, over all independent runs and epochs.
+The overall normalised average rank is provided at the bottom of the table.
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:burn_in:metrics:rank}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		% Table generated by Excel2LaTeX from sheet 'rank'
+		\begin{tabular}{r|ccccc}
+			                             & \multicolumn{5}{c}{\textbf{Burn In - Average Rank}}                                                                                                                                                                                                                                             \\
+			\midrule
+			\textbf{dataset}             & \textbf{0}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
+			\midrule
+			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.9151 ($\pm$1.395)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6935 ($\pm$1.393) & \cellcolor[rgb]{ 1,  .922,  .518}2.9172 ($\pm$1.384)    & \cellcolor[rgb]{ .788,  .859,  .502}2.8398 ($\pm$1.352) & \cellcolor[rgb]{ .973,  .412,  .42}3.6344 ($\pm$1.357)  \\
+			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9097 ($\pm$1.441)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6817 ($\pm$1.427) & \cellcolor[rgb]{ .624,  .812,  .494}2.7699 ($\pm$1.344) & \cellcolor[rgb]{ .973,  .412,  .42}3.372 ($\pm$1.314)   & \cellcolor[rgb]{ .98,  .529,  .443}3.2667 ($\pm$1.412)  \\
+			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.7301 ($\pm$1.321) & \cellcolor[rgb]{ .816,  .867,  .506}2.8194 ($\pm$1.335) & \cellcolor[rgb]{ 1,  .922,  .518}2.857 ($\pm$1.485)     & \cellcolor[rgb]{ 1,  .878,  .51}2.9312 ($\pm$1.384)     & \cellcolor[rgb]{ .973,  .412,  .42}3.6624 ($\pm$1.339)  \\
+			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}1.9237 ($\pm$0.981) & \cellcolor[rgb]{ .545,  .788,  .49}2.1806 ($\pm$1.024)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9237 ($\pm$1.274)    & \cellcolor[rgb]{ .992,  .729,  .482}3.5054 ($\pm$1.186) & \cellcolor[rgb]{ .973,  .412,  .42}4.4667 ($\pm$0.851)  \\
+			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.3624 ($\pm$1.231) & \cellcolor[rgb]{ .533,  .784,  .49}2.5882 ($\pm$1.425)  & \cellcolor[rgb]{ 1,  .922,  .518}3.2978 ($\pm$1.392)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3796 ($\pm$1.271)  & \cellcolor[rgb]{ .976,  .459,  .431}3.372 ($\pm$1.401)  \\
+			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}2.4054 ($\pm$1.358) & \cellcolor[rgb]{ .604,  .808,  .494}2.7011 ($\pm$1.358) & \cellcolor[rgb]{ 1,  .902,  .518}3.2398 ($\pm$1.372)    & \cellcolor[rgb]{ 1,  .922,  .518}3.2323 ($\pm$1.326)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4215 ($\pm$1.396)  \\
+			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}3.0634 ($\pm$1.459)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7935 ($\pm$1.402) & \cellcolor[rgb]{ .447,  .761,  .482}2.8204 ($\pm$1.513) & \cellcolor[rgb]{ .996,  .796,  .494}3.1022 ($\pm$1.346) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.295)  \\
+			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8161 ($\pm$1.33)  & \cellcolor[rgb]{ .808,  .867,  .506}2.8495 ($\pm$1.383) & \cellcolor[rgb]{ 1,  .922,  .518}2.8645 ($\pm$1.409)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.398)  & \cellcolor[rgb]{ .988,  .698,  .475}3.0925 ($\pm$1.471) \\
+			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}2.6903 ($\pm$1.384) & \cellcolor[rgb]{ .91,  .894,  .51}2.9516 ($\pm$1.318)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.442)    & \cellcolor[rgb]{ .996,  .82,  .498}3.0581 ($\pm$1.344)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3032 ($\pm$1.51)   \\
+			\textbf{iris}                & \cellcolor[rgb]{ .922,  .898,  .51}2.9473 ($\pm$1.461)  & \cellcolor[rgb]{ 1,  .922,  .518}2.972 ($\pm$1.367)     & \cellcolor[rgb]{ .973,  .412,  .42}3.1903 ($\pm$1.449)  & \cellcolor[rgb]{ .388,  .745,  .482}2.771 ($\pm$1.369)  & \cellcolor[rgb]{ .984,  .58,  .455}3.1194 ($\pm$1.387)  \\
+			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.2065 ($\pm$1.249) & \cellcolor[rgb]{ .863,  .882,  .51}2.9376 ($\pm$1.298)  & \cellcolor[rgb]{ 1,  .902,  .514}3.1613 ($\pm$1.297)    & \cellcolor[rgb]{ 1,  .922,  .518}3.1441 ($\pm$1.401)    & \cellcolor[rgb]{ .973,  .412,  .42}3.5226 ($\pm$1.501)  \\
+			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.2796 ($\pm$1.282) & \cellcolor[rgb]{ 1,  .922,  .518}2.8892 ($\pm$1.247)    & \cellcolor[rgb]{ .816,  .867,  .506}2.7065 ($\pm$1.314) & \cellcolor[rgb]{ .984,  .616,  .459}3.3968 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.728 ($\pm$1.33)    \\
+			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.1452 ($\pm$1.205) & \cellcolor[rgb]{ .741,  .843,  .502}2.6946 ($\pm$1.403) & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.352)    & \cellcolor[rgb]{ .984,  .561,  .451}3.4581 ($\pm$1.354) & \cellcolor[rgb]{ .973,  .412,  .42}3.6054 ($\pm$1.231)  \\
+			\textbf{wine quality}        & \cellcolor[rgb]{ .925,  .898,  .51}2.9699 ($\pm$1.437)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0108 ($\pm$1.304)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6634 ($\pm$1.419) & \cellcolor[rgb]{ .988,  .659,  .471}3.1247 ($\pm$1.398) & \cellcolor[rgb]{ .973,  .412,  .42}3.2312 ($\pm$1.447)  \\
+			\midrule
+			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}2.5975 ($\pm$1.376) & \cellcolor[rgb]{ .671,  .824,  .498}2.7688 ($\pm$1.353) & \cellcolor[rgb]{ 1,  .922,  .518}2.9647 ($\pm$1.404)    & \cellcolor[rgb]{ .988,  .694,  .475}3.1923 ($\pm$1.367) & \cellcolor[rgb]{ .973,  .412,  .42}3.4747 ($\pm$1.402)  \\
+			\midrule
+			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
+		\end{tabular}%
+	}
+\end{table}%
+
+Table \ref{tab:results:burn_in:metrics:rank} shows that, in general, a configuration where there is no burn in produces the overall best ranked performance across all datasets.
+Furthermore, it can be observed that performance degrades with larger burn in window sizes.
+This can be explained from the fact that most of the training progress that is made, is done early in the training process.
+The faster the \acs{BHH} is able to start learning and exploiting \index{heuristic}heuristics and solutions, the better.
+
+Note that the \acs{BHH} is configured with a reselection interval of one, until the burn in window has been exhausted, after which the actual reselection interval applies.
+That means that reselection occurs at each step during the burn in window, but the reanalysis interval and replay window size remain intact.
+This observation agrees with previous results, where the \acs{BHH} prefers to start exploiting \index{heuristic}heuristics and solutions as soon as possible.
+Furthermore, this agrees with previous results, where large reselection intervals are found to produce the best results, giving \index{heuristic}heuristics sufficient time to progress and smooth out training steps.
+
+Recall that the gradient-based \index{heuristic}heuristics generally produce the best results overall.
+Most of the gradient-based \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool implement some form of momentum and exponentially average state parameters.
+When reselection occurs frequently in succession, these gradient-based \index{heuristic}heuristics struggle to produce smooth update steps.
+As a result, the \acs{BHH} can produce delayed convergence and thus leads to worse performance when considering the entire training process.
 
 Figure~\ref{fig:results:burn_in:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the burn in window size configurations, per dataset.
+From Figure~\ref{fig:results:burn_in:descriptive:descriptive} is can be seen that there is mostly a linear correlation between performance results and burn in window sizes, with minor exceptions to some datasets.
 
@@
 
-Figure~\ref{fig:results:burn_in:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reanalysis interval configuration as it relates to all datasets, across all independent runs and epochs.
+Figure~\ref{fig:results:burn_in:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each burn in window size configuration as it relates to all datasets, across all independent runs and epochs.
 
@@
 
-Figure~\ref{fig:results:burn_in:descriptive:cd} shows with statistical certainty that a small burn in configuration of the \acs{BHH} (burn in values 0 and 5) generally produce better results than larger burn in configurations.
+Figure~\ref{fig:results:burn_in:descriptive:cd} shows with statistical certainty that a small burn in configuration of the \acs{BHH} generally produce overall better results than larger burn in configurations, as it relates to all datasets,
 
 Similar to before, Figure~\ref{fig:results:burn_in:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the burn in window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 Figure~\ref{fig:results:burn_in:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the burn in window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
-
-\begin{figure}[htb]
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 \end{figure}
+
+The divergence that can be seen in Figures~\ref{fig:results:burn_in:figures:loss:train:mushroom} and \ref{fig:results:burn_in:figures:loss:test:mushroom} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results, when an optimal solution has already been found.
+As mentioned before, an early stopping strategy as well as a move-acceptance strategy can be incorporated to avoid this effect.
 
@@
 
-Table \ref{tab:results:normalise:metrics} provides the ranked performance, per dataset, with normalisation enabled and disabled.
+Table \ref{tab:results:normalise:metrics} provides the average ranked performance, per dataset, with normalisation enabled and disabled.
 Similar to before, the performance rank is calculated as the average rank produced by the normalisation configurations, for all datasets, over all independent runs and epochs.
@@
 
-Table \ref{tab:results:discounted_rewards:metrics} provides the ranked performance, per dataset, with discounted rewards enabled and disabled.
+Table \ref{tab:results:discounted_rewards:metrics} provides the average ranked performance, per dataset, with discounted rewards enabled and disabled.
 Similar to before, the performance rank is calculated as the average rank produced by the discounted rewards configurations, for all datasets, over all independent runs and epochs.

### 2022-11-20 dissertation/chapters/08-results.tex
🚧 (results): Normalisation

@@
 As before, Table~\ref{tab:results:burn_in:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the burn in window size variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs and epochs.
+The test loss is measured at the last epoch for each dataset, over all independent runs.
 
@@
 As a reminder, the normalisation hyper-parameter is a flag that enables or disables normalisation of the concentration parameters in an attempt to provide more exploration in the \index{heuristic}heuristic space.
-
-Table \ref{tab:results:normalise:metrics} provides the average ranked performance, per dataset, with normalisation enabled and disabled.
-Similar to before, the performance rank is calculated as the average rank produced by the normalisation configurations, for all datasets, over all independent runs and epochs.
+The experiments are denoted as \textit{true} where normalisation is enabled, and \textit{false} where normalisation is disabled.
+
+As before, Table~\ref{tab:results:normalise:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for variants of the \acs{BHH} that was implemented where normalisation is enabled and disabled.
+The test loss is measured at the last epoch for each dataset, over all independent runs.
 
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:normalise:metrics:rank}%
-	\par\bigskip
-	\resizebox{0.6\textwidth}{!}{
-		\begin{tabular}{rcc}
-			\multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Normalisation - Average Rank}}                                                           \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                            & \textbf{true}                                           \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4935 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5065 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4892 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5108 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5484 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4516 ($\pm$0.498) \\
-			\multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .388,  .745,  .482}1.4978 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5022 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.4258 ($\pm$0.495)   & \cellcolor[rgb]{ .973,  .412,  .42}1.5742 ($\pm$0.495)  \\
-			\multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4753 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5247 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5505 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4495 ($\pm$0.498) \\
-			\multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.5054 ($\pm$0.5)      & \cellcolor[rgb]{ .388,  .745,  .482}1.4946 ($\pm$0.5)   \\
-			\multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.472 ($\pm$0.499)    & \cellcolor[rgb]{ .973,  .412,  .42}1.528 ($\pm$0.499)   \\
-			\multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5645 ($\pm$0.496)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4355 ($\pm$0.496) \\
-			\multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4323 ($\pm$0.496)   & \cellcolor[rgb]{ .973,  .412,  .42}1.5667 ($\pm$0.496)  \\
-			\multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.4 ($\pm$0.49)       & \cellcolor[rgb]{ .973,  .412,  .42}1.6 ($\pm$0.49)      \\
-			\multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.3892 ($\pm$0.488)   & \cellcolor[rgb]{ .973,  .412,  .42}1.6108 ($\pm$0.488)  \\
-			\multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.5473 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4527 ($\pm$0.498) \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4851 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5148 ($\pm$0.5)    \\
-			\midrule
-			\textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                     & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\caption{Empirical results showing average test loss and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
 	\label{tab:results:normalise:metrics:loss}%
@@
 
-Table \ref{tab:results:normalise:metrics} shows that, in general, there is no obvious difference in the outcomes of the \acs{BHH} when normalisation is enabled or disabled.
-For some datasets such as bank, fish toxicity, forest fires, iris, and wine quality, enabling normalisation provided the best results, while disabling of the normalisation flag provided the best results for the other datasets.
+Table \ref{tab:results:normalise:metrics:rank} provides the average ranked performance, per dataset, with normalisation enabled and disabled.
+Similar to before, the performance rank is calculated as the average rank produced by the normalisation configurations, for all datasets, over all independent runs and epochs.
+The overall normalised average ranks are provided at the bottom of the table.
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:normalise:metrics:rank}%
+	\par\bigskip
+	\resizebox{0.6\textwidth}{!}{
+		\begin{tabular}{rcc}
+			\multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Normalisation - Average Rank}}                                                           \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                            & \textbf{true}                                           \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4935 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5065 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4892 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5108 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5484 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4516 ($\pm$0.498) \\
+			\multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .388,  .745,  .482}1.4978 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5022 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.4258 ($\pm$0.495)   & \cellcolor[rgb]{ .973,  .412,  .42}1.5742 ($\pm$0.495)  \\
+			\multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4753 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5247 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5505 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4495 ($\pm$0.498) \\
+			\multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.5054 ($\pm$0.5)      & \cellcolor[rgb]{ .388,  .745,  .482}1.4946 ($\pm$0.5)   \\
+			\multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.472 ($\pm$0.499)    & \cellcolor[rgb]{ .973,  .412,  .42}1.528 ($\pm$0.499)   \\
+			\multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5645 ($\pm$0.496)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4355 ($\pm$0.496) \\
+			\multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4323 ($\pm$0.496)   & \cellcolor[rgb]{ .973,  .412,  .42}1.5667 ($\pm$0.496)  \\
+			\multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.4 ($\pm$0.49)       & \cellcolor[rgb]{ .973,  .412,  .42}1.6 ($\pm$0.49)      \\
+			\multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.3892 ($\pm$0.488)   & \cellcolor[rgb]{ .973,  .412,  .42}1.6108 ($\pm$0.488)  \\
+			\multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.5473 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4527 ($\pm$0.498) \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4851 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5148 ($\pm$0.5)    \\
+			\midrule
+			\textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                     & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\
+		\end{tabular}%
+
+	}
+\end{table}%
+
+Table \ref{tab:results:normalise:metrics:rank} shows that, in general, there is no obvious difference in the outcomes of the \acs{BHH} when normalisation is enabled or disabled.
 This suggests that the normalisation flag is problem specific.
 Since the normalisation hyper-parameter provides a mechanism for the \acs{BHH} to explore more in the \index{heuristic}heuristic space, with the intent of finding better solutions, it can be concluded that some datasets require more exploration, while others require more exploitation.
+However, a better suggestion can be made from the observation of previous results.
+The \acs{BHH} has a default replay window size of ten, yielding a small window of memory to maintain \index{heuristic}heuristic performance evidence in the performance log.
+Normalisation of the concentration parameters then yield an insignificant difference in the outcome as the concentration parameters never reach high values.
+Furthermore, previous results have shown that the best results are obtained from exploitation of \index{heuristic}heuristics and solutions, in comparison to exploration.
 
@@
 
-Figure~\ref{fig:results:normalise:descriptive:descriptive} shows no statistical difference in the outcomes of the normalisation configurations of the \acs{BHH}.
-This further supports the suggestion that the use of the normalisation hyper-parameter is problem specific.
+Figure~\ref{fig:results:normalise:descriptive:cd} shows no statistical difference in the outcomes of the normalisation configurations of the \acs{BHH}.
+This further supports the suggestion that the use of the normalisation hyper-parameter is problem specific or that the effects of the normalisation hyper-parameter is not realised for small replay window sizes.
 
 Similar to before, Figure~\ref{fig:results:normalise:figures:abalone} provides the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the normalisation experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
+As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 Figure~\ref{fig:results:normalise:figures:bike} provides the train and test loss plots for an example regression dataset (bike) as it relates to the normalisation experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
-
-\begin{figure}[htb]
+As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
+
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}

### 2022-11-20 dissertation/chapters/08-results.tex
✨ (results): Done

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% DISCOUNTED REWARDS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Discounted Rewards}\label{sec:results:discounted_rewards}
@@
 
-Table \ref{tab:results:discounted_rewards:metrics} provides the average ranked performance, per dataset, with discounted rewards enabled and disabled.
-Similar to before, the performance rank is calculated as the average rank produced by the discounted rewards configurations, for all datasets, over all independent runs and epochs.
+As a reminder, the discounted rewards mechanism is implemented such that pseudo counts for past performances that achieved successful credit allocations are exponentially decayed into the past.
+The default discounted rewards decay rate is set to 0.5.
+
+As before, Table~\ref{tab:results:discounted_rewards:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for variants of the \acs{BHH} that was implemented where discounted rewards is enabled and disabled.
+The test loss is measured at the last epoch for each dataset, over all independent runs.
 
@@
 	\centering
-	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:discounted_rewards:metrics:rank}%
-	\par\bigskip
-	\resizebox{0.6\textwidth}{!}{
-		\begin{tabular}{rcc}
-			\multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Rank}}                                                           \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                                 & \textbf{true}                                           \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4914 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5086 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4613 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5387 ($\pm$0.499)  \\
-			\multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5161 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4839 ($\pm$0.5)   \\
-			\multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
-			\multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.428 ($\pm$0.495)         & \cellcolor[rgb]{ .973,  .412,  .42}1.572 ($\pm$0.495)   \\
-			\multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4699 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5301 ($\pm$0.499)  \\
-			\multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
-			\multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .388,  .745,  .482}1.4742 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5258 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4237 ($\pm$0.494)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5763 ($\pm$0.494)  \\
-			\multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5903 ($\pm$0.492)         & \cellcolor[rgb]{ .388,  .745,  .482}1.4097 ($\pm$0.492) \\
-			\multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.3946 ($\pm$0.489)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5806 ($\pm$0.494)  \\
-			\multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.371 ($\pm$0.483)         & \cellcolor[rgb]{ .973,  .412,  .42}1.629 ($\pm$0.483)   \\
-			\multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.4398 ($\pm$0.497)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5602 ($\pm$0.497)  \\
-			\multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.557 ($\pm$0.497)          & \cellcolor[rgb]{ .388,  .745,  .482}1.443 ($\pm$0.497)  \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4728 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5254 ($\pm$0.499)  \\
-			\midrule
-			\textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                          & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\caption{Empirical results showing average test loss and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
 	\label{tab:results:discounted_rewards:metrics:loss}%
 	\par\bigskip
-	\resizebox{0.6\textwidth}{!}{
+	\resizebox{0.7\textwidth}{!}{
 		\begin{tabular}{r|cc}
@@
 
-Table \ref{tab:results:discounted_rewards:metrics} shows that, in general, there is no obvious difference in the outcomes of the \acs{BHH} when discounted rewards is enabled or disabled.
+Table \ref{tab:results:discounted_rewards:metrics:rank} provides the average ranked performance, per dataset, with discounted rewards enabled and disabled.
+Similar to before, the performance rank is calculated as the average rank produced by the discounted rewards configurations, for all datasets, over all independent runs and epochs.
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:discounted_rewards:metrics:rank}%
+	\par\bigskip
+	\resizebox{0.7\textwidth}{!}{
+		\begin{tabular}{rcc}
+			\multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Rank}}                                                           \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                                 & \textbf{true}                                           \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4914 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5086 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4613 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5387 ($\pm$0.499)  \\
+			\multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5161 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4839 ($\pm$0.5)   \\
+			\multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
+			\multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.428 ($\pm$0.495)         & \cellcolor[rgb]{ .973,  .412,  .42}1.572 ($\pm$0.495)   \\
+			\multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4699 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5301 ($\pm$0.499)  \\
+			\multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
+			\multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .388,  .745,  .482}1.4742 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5258 ($\pm$0.5)    \\
+			\multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4237 ($\pm$0.494)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5763 ($\pm$0.494)  \\
+			\multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5903 ($\pm$0.492)         & \cellcolor[rgb]{ .388,  .745,  .482}1.4097 ($\pm$0.492) \\
+			\multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.3946 ($\pm$0.489)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5806 ($\pm$0.494)  \\
+			\multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.371 ($\pm$0.483)         & \cellcolor[rgb]{ .973,  .412,  .42}1.629 ($\pm$0.483)   \\
+			\multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.4398 ($\pm$0.497)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5602 ($\pm$0.497)  \\
+			\multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.557 ($\pm$0.497)          & \cellcolor[rgb]{ .388,  .745,  .482}1.443 ($\pm$0.497)  \\
+			\midrule
+			\multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4728 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5254 ($\pm$0.499)  \\
+			\midrule
+			\textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                          & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\
+		\end{tabular}%
+	}
+\end{table}%
+
+Table \ref{tab:results:discounted_rewards:metrics:rank} shows that, in general, there is no obvious difference in the outcomes of the \acs{BHH} when discounted rewards is enabled or disabled.
+Although this could suggestion that the discounted rewards hyper-parameter is problem specific, a better suggestion supports the findings from Section \ref{sec:results:normalise} that suggest that manipulation of the outcomes of the concentration parameters yield insignificant differences in the outcomes of performance, as a small replay window size of ten, is used by default.
+
+In general, it is found that the online learning approach, followed by the \acs{BHH} yields very little room to learn from.
+This is supported by the fact that most of the significant performance gains are made in the early stages of training after which exploitation of \index{heuristic}heuristics and solutions later in the training process is shown to produce the best results.
 
@@
 
-Figure~\ref{fig:results:discounted_rewards:descriptive:descriptive} shows no statistical difference in the outcomes of the discounted rewards configurations of the \acs{BHH}.
-This further supports the suggestion that the use of the discounted rewards hyper-parameter is problem specific.
+Figure~\ref{fig:results:discounted_rewards:descriptive:cd} shows no statistically significant difference in the outcomes of the discounted rewards configurations of the \acs{BHH}.
+This further supports the suggestion that the effects of discounted rewards is not realised for small replay window sizes.
 
@@
 
-\begin{figure}[htb]
+\begin{figure}[htbp]
 	\begin{subfigure}{0.5\textwidth}
@@
 
-TODO
+This section provided the results of the empirical process that was described in Chapter \ref{chap:methodology}.
+Three experimental groups were designed.
+These experimental groups include a case study on the behaviour of the \acs{BHH} as it relates to an example dataset (iris).
+Furthermore, an experimental group that compares the performance of the \acs{BHH} to standalone, low-level \index{heuristic}heuristics was included, and finally, an experimental group that compares the effects of various hyper-parameters on the outcomes of the \acs{BHH} was also included.
+The empirical results for each of these experimental groups were presented in detail.
+
+In general, it was found that the \acs{BHH} is able to successfully train the underlying \acp{FFNN}.
+Detailed analysis and discussions of the empirical results were provided along with illustrations for visual aid.
+Where possible, detailed discussions were presented that explain the reasons behind the outcomes that were produced.
+Throughout, various suggestions were made to improve on the implementations made in this dissertation.
+
+Finally, all results that were presented were retrieved from statistical analysis which yield statistical certainty in the results and outcomes observed.

### 2022-11-22 dissertation/chapters/09-conclusion.tex
✨ (conclusion): Done

--- 2022-10-30 dissertation/chapters/09-conclusion.tex
@@
 
-\begin{quote}
-      \textit{
-            I am sorry to have made such a long speech, but I did not have time to make a shorter one. - Winston Churchill
-      }
-\end{quote}
+\begin{quotation}
+      \noindent ``I am sorry to have made such a long speech, but I did not have time to make a shorter one.''
+\end{quotation}
+\begin{flushright}
+      - Winston Churchill
+\end{flushright}
 
-Finally, the research objectives that have been set out in this dissertation must be concluded. This chapter provides a summary of the research that has been done.
-
-The remainder of the chapter is structured as follows:
+This chapter provides a summary of the research that is done in this dissertation.
+The research objectives were set out in Chapter \ref{chap:introduction} and are concluded in this chapter.
+Furthermore, this chapter provides a summary of the results and findings from the empirical process and provides future research opportunities.
+The remainder of the chapter is structured as follows.
 
 \begin{itemize}
-      \item \textbf{Section \ref{sec:conclusion:research_goals}} provides a review of the problem statement, objectives and motivations behind the research.
+      \item \textbf{Section \ref{sec:conclusion:research_goals}} provides a summary of the research intent and provides a review of the problem statement, objectives and motivations behind the research.
 
@@
 
-      \item \textbf{Section \ref{sec:conclusion:bhh}} provides a brief recap of the \ac{BHH} and its implementation.
+      \item \textbf{Section \ref{sec:conclusion:bhh}} provides a brief summary of the \ac{BHH} and its implementation.
 
-      \item \textbf{Section \ref{sec:conclusion:methodology}} provides a brief recap of the methodology and the empirical process that was followed.
+      \item \textbf{Section \ref{sec:conclusion:methodology}} provides a brief summary of the methodology and the empirical process that was followed.
 
-      \item \textbf{Section \ref{sec:conclusion:results}} summarises the research findings.
+      \item \textbf{Section \ref{sec:conclusion:results}} summarises the research findings. This section is broken down into the various experimental groups that were executed.
 
-      \item \textbf{Section \ref{sec:conclusion:further_research}} discuss further research opportunities.
+      \item \textbf{Section \ref{sec:conclusion:further_research}} presents future research opportunities.
 
-      \item \textbf{Section \ref{sec:conclusion:documentation_and_data}} briefly discusses some supplementary and supporting material related to the research, as made available by the authors either as external sources or in the appendices of this dissertation.
+      \item \textbf{Section \ref{sec:conclusion:documentation_and_data}} provides a brief discussion on supporting material related to the research, as made available by the authors.
 
-      \item Finally, \textbf{Section \ref{sec:conclusion:closing_statements}} provides the closing statements of the dissertation.
+      \item \textbf{Section \ref{sec:conclusion:summary}} provides a brief summary of the chapter.
 \end{itemize}
 
-\section{Reviewing Research Objectives}
+\section{Summary of Research Intent}
 \label{sec:conclusion:research_goals}
@@
 
-The main area of focus for this research stems from the problem statement which identified the difficult and tedious problem of heuristic selection for \ac{FFNN} training.
-Often times this process is non-trivial and very time-consuming.
-It has been identified that there is no easy way to know which heuristic to select to train \acp{FFNN}.
+\subsection{Review of Problem Statement}
+\label{sec:conclusion:research_goals:problem_statement}
+
+The main area of focus for the research done in this dissertation stems from the problem statement, which identified the difficult and tedious problem of selecting the best \index{heuristic}heuristic for training \acp{FFNN}.
+This process is often non-trivial and time-consuming.
+There is no easy way to know which \index{heuristic}heuristic to select to train \acp{FFNN}.
 Traditionally, an iterative approach of trial-and-error was followed.
-This process involves a tedious process of careful consideration and selection, often at the expense of the researcher's resources.
-This research has identified the possibility of using a relatively new approach, referred to as \acp{HH} to automate this selection process.
-\ac{HH} has been shown to provide a general solution to this problem.
-The consequences of such approach being successful could provide a mechanism that saves a lot of time and could provide a more generalised solution to heuristic selection.
+This process involves a tedious process of carefully considering and selecting candidate \index{heuristic}heuristics, whereby each candidate \index{heuristic}heuristic is then empirically tested and evaluated.
+This process is often executed at the expense of the researcher's resources.
+
+\subsection{Review of Research Motivation}
+\label{sec:conclusion:research_goals:motivations}
+
+The research presented in this disseration identified the possibility of using a different approach, referred to as \acp{HH}, to automate the \index{heuristic}heuristic selection process.
+\acp{HH} are high-level search algorithms that search in the \index{heuristic}heuristic space, whereby low-level \index{heuristic}heuristics search in the solution space.
+\acp{HH} have been shown to provide a general solution to the \index{heuristic}heuristic selection process.
+The benefit that such an approach provides, is that it automates the \index{heuristic}heuristic selection process.
+This approach saves researchers time and potentially produce a solution that could generalise to multiple problems.
 
 Investigation was done into the landscapes of existing solutions to train \acp{FFNN} as well as \acp{HH}.
-Though there exists many applications of \acp{HH} there are little to no published work on using \acp{HH} to train \acp{FFNN}.
+Though there exists many applications where \acp{HH} are used for optimisation, there are little to no published work on using \acp{HH} to train \acp{FFNN}.
 The only work that was found include the work by~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021}.
 
-Other existing techniques from other problem domains were investigated.
-\ac{RL}, meta-learning, online, one-shot and probabilistic learning approached were considered.
-Bayesian probability theory showed promise and the \Ac{BHH} was conceptualised.
+\subsection{Review of Research Objectives}
+\label{sec:conclusion:research_goals:research_objectives}
 
-The research objectives were defined and are summarised as follows:
+Existing techniques from other problem domains were considered.
+\acs{RL}, meta-learning and probabilistic learning approached were considered.
+Bayesian probability theory showed promise.
+This research then set out to develop a novel high-level \index{heuristic}heuristic that utilises probability theory in an online learning setting to drive the automatic \index{heuristic}heuristic selection process.
+As such, the \acs{BHH} was conceptualised.
+The research objectives were defined and are summarised as follows.
 
 \begin{itemize}
-      \item Conduct literature studies on all related topics that are relevant to the development of the \ac{BHH}.
-These include \ac{ANN}, \index{heuristic}heuristics/optimisers, meta-learning, \acp{HH}, probability theory and Bayesian statistics.
+      \item Conduct literature studies on all related topics that are relevant to the development of the \acs{BHH}.
+These include \acs{ANN}, existing low-level \index{heuristic}heuristics, meta-learning, \acp{HH}, probability theory and Bayesian statistics.
 
-      \item Develop a novel \ac{BHH} that has both a selective and perturbative element.
-For the selection mechanism, Bayesian statistics and \ac{MAP} is used.
-For the perturbative element, proxied low-level \index{heuristic}heuristic update steps are used.
+      \item Develop a novel \acs{BHH} that can be used to automate the \index{heuristic}heuristic selection process.
+The \acs{BHH} follows an approach that includes a selective and perturbative element in an online learning setting.
+Bayesian statistics and \acs{MAP} is used as the optimisation technique.
+Furthermore, the \acs{BHH} implements a mapping for proxied \index{heuristic}heuristic state update operations, whereby \index{heuristic}heuristic state is maintained by outsourcing state opertations to relevant low-level \index{heuristic}heuristics.
 
@@
 
-      \item Conduct an empirical study to study the behavioural characteristics of the \ac{BHH}.
+      \item Conduct an empirical study to study the behavioural characteristics of the \acs{BHH}.
 
-      \item Conduct an empirical study to critically evaluate the performance of the \ac{BHH} to those of traditional, low-level \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.
+      \item Conduct an empirical study to critically evaluate the performance of the \acs{BHH} compared to traditional, low-level, standalone \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.
 
-      \item Conduct an empirical study to evaluate variants of the \ac{BHH} to study the impacts of various design decisions on the outcomes of the \ac{BHH}.
+      \item Conduct an empirical study to evaluate variants of the \acs{BHH} to study the impact of various hyper-parameters on the outcomes of the \ac{BHH}.
 
-      \item Provide a statistically sound evaluation of outcomes with statistical significance tests driving the conclusions of the outcomes.
+      \item Provide and discuss the findings of the results produced by the empirical process. The results are analysed for statistical significance.
 \end{itemize}
 
-As one can see, the research set out to do in this dissertation was quite extensive and also identifies many different opportunities for future research.
-
-The next sections aim to provide brief summaries of the work that was done, followed by a conclusion of the outcomes of each.
+The research objectives set out in this dissertation are extensive.
+Each of these research objectives have been successfully executed.
+From the findings made in this dissertation, many different opportunities for future research are identified.
 
@@
 
-Chapters \ref{chap:introduction} - \ref{chap:probability} provided the reader with background information that is necessary to understand the components that are discussed and developed in this work.
-These chapters respectively provided background information, literature reviews and landscape analyses into \acp{ANN}, \index{heuristic}heuristics/optimisers, \acp{HH} and meta-learning, probability theory and Bayesian statistics.
+Chapters \ref{chap:anns}-\ref{chap:probability} provided the reader with the relevant background information that is necessary to develop the novel \acs{BHH}.
+Chapter~\ref{chap:anns} provided background information on \acp{ANN}.
+All the components that make up the \acs{AN} were provided and is followed by discussions on \acp{FFNN}.
+Chapter~\ref{chap:heuristics} provided background information on various low-level heuristics that are designed to train \acp{FFNN}.
+A number of gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics were presented in detail.
+Chapter~\ref{chap:hhs} provided background information and literature reviews on \acp{HH}.
+Meta-learning is discussed and a \acs{HH} classification scheme, developed by \citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, was discussed in detail.
+Chapter~\ref{chap:probability} provided background information and mathematical derivations on probability theory and Bayesian statistics.
+Various probability distributions were provided along with their conjugate priors.
+\acs{MLE} and \acs{MAP} were presented in detail along with mathematical breakdowns.
 
-It should be mentioned that there are many resources available on the above mentioned topics in their own right.
-However, the intersection of these topics, especially \acp{ANN} and \acp{HH} are close to non-existent and calls for much more research and publication.
-This dissertation aims to provide a manifesto of these topics and how they are bring together to show that \acp{HH} can be used to train \acp{FFNN}.
+From the aforementioned chapters, it can be concluded that the necessary background information was provided as set out in the research objectives of this dissertation.
 
-From these topics, it can be concluded that the necessary background information that was provisioned for in the objectives for the dissertation have been provided.
-The next section gives a summary of the novel \ac{BHH} that was developed.
-
-\section{Summary of Bayesian Hyper-Heuristics}
+\section{Summary of The Bayesian Hyper-Heuristic}
 \label{sec:conclusion:bhh}
 
-The main takeaway point from this dissertation is the development of a novel \ac{BHH}.
-Chapter \ref{chap:bhh} provides the details and implementation of the \ac{BHH} and provides the reader with various design decisions that could control/affect the outcomes of the \ac{BHH}.
+The main contribution from this dissertation is the development of a novel \acf{BHH}.
+Chapter \ref{chap:bhh} provided the details on the concept and implementation of the \ac{BHH}.
+Various design decisions and hyper-parameters that could affect the outcomes of the \ac{BHH} were presented.
 
-It was shown how the \ac{BHH} implements a Bayesian probabilistic model and makes use of online learning to select \index{heuristic}heuristics dynamically throughout the training process.
-This probabilistic model forms the selection mechanism for the \ac{BHH}.
+It was shown that the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level \index{heuristic}heuristics in an online learning fashion.
+\index{heuristic}Heuristics are selected for each entity in a population of entities that each implement a candidate solution to the underlying \acs{FFNN}.
+The \acs{BHH} uses a Bayesian probabilistic model to drive the \index{heuristic}heuristic selection process.
+\acs{MAP} was derived for the probabilistic model and is used as the mechanism by which the \acs{BHH} is optimised, yielding the learning capability of the \acs{BHH}.
 
-Furthermore, it is shown that selection alone is not enough and that a measure of transition between \index{heuristic}heuristics is needed.
+Furthermore, it is shown that \index{heuristic}heuristic selection alone is not sufficient and that a mechanism of transition between \index{heuristic}heuristics is needed as they are selected for each entity in the population.
 Entity and \index{heuristic}heuristic state and state-manipulation formed the cornerstone of this topic.
-A technique that deconstructs \index{heuristic}heuristics into their initialisation and update steps is proposed.
-This technique then allows for the proxying of update step operations as they are required by different \index{heuristic}heuristics.
-Though this solves the transition problem between \index{heuristic}heuristics, is has been indicated that does not guarantee stable search processes.
-This does raise opportunities for further research which is summarised below in Section \ref{sec:conclusion:further_research}.
+Perturbation of \index{heuristic}heuristics and solutions is achieved through a technique that deconstructs \index{heuristic}heuristics into their initialisation and update steps.
+The update operations for each heuristic was derived as movement equations borrowed from the field of physics.
+This technique allows for the proxying of update step operations as they are required by different \index{heuristic}heuristics.
 
-The simplicity of the \ac{BHH} and various challenges related to it have been highlighted. Of these challenge include:
+Detailed discussions were provided on a number of hyper-parameters that each contribute to the trade-off between \index{heuristic}heuristic and solution exploration and exploitation.
+These hyper-parameters include the \index{heuristic pool}\textit{heuristic pool} configuration, the \textit{population size}, the \textit{credit assignment strategy} used, the \textit{reselection interval}, the \textit{replay window size}, the \textit{reanalysis interval}, the \textit{burn in window size}, \textit{normalisation} of concentration parameters and \textit{discounted rewards} as assigned by the credit assignment strategy.
+A \acs{BHH} baseline configuration was identified with default values for each of the hyper-parameters.
 
-\begin{itemize}
-      \item Catering for overfitting by early stopping conditions.
-      \item Catering for invalid selections.
-      \item Catering for invalid or stale entity and \index{heuristic}heuristic states.
-      \item Catering for mode-collapse where a \index{heuristic}heuristic is either always selected or never selected.
-      \item Catering for a trade-off between exploration and exploitation.
-\end{itemize}
-
-After the development of the \ac{BHH}, the authors presented the methodology used to execute the empirical process. The details of which is summarised in the next section.
+It was mentioned that the \acs{BHH}, implemented in this dissertation, does not implement a move-acceptance strategy that rejects heuristic progressions if they do not improve on the current best solution.
+Throughout the presentation of empirical results, it is recommended that this technique be investigated and implemented in further research.
 
@@
 
-As discussed above, the research objectives defined a number of empirical tests to be executed.
+The research objectives defined a number of empirical tests to be executed.
 Each one of the empirical tests is referred to as an experimental group.
-Various experimental groups have been identified and is listed below:
+Various experimental groups have been identified and are listed below.
 
 \begin{itemize}
-      \item A case-study on the behaviour of the \ac{BHH} during training and testing to understand the workings of the \ac{BHH} and to see if the \ac{BHH} is able to train \acp{FFNN}.
-      \item A comparative analysis between the performance of standalone \index{heuristic}heuristics and the baseline \ac{BHH} when training \acp{FFNN}.
-      \item A comparative analysis between variants of the \ac{BHH} that include:
+      \item An experimental group that provides a case-study on the behaviour of the \ac{BHH} as it relates to training of a \acs{FFNN} on an example dataset (iris), in order to understand the workings of the \acs{BHH}, and to determine if the \acs{BHH} is able to successfully train \acp{FFNN}.
+Three different configurations of the \acs{BHH} configuration was implemented.
+This includes the default \acs{BHH} baseline configuration, the \acs{BHH} baseline configuration where the replay window size is set to 250, and the \acs{BHH} baseline configuration which utilises the \textit{symmetric} credit assignment strategy.
+
+      \item An experimental group that provides a comparative analysis between the performance of the \acs{BHH} baseline configuration and low-level, standalone \index{heuristic}heuristics when training \acp{FFNN} on a number of datasets.
+
+      \item An experimental group that provides a comparative analysis between variants of the \ac{BHH} that investigate the effects of various hyper-parameters on the outcomes of the \acs{BHH}.
+These variants include:
+
             \begin{itemize}
-                  \item Different \index{heuristic}heuristic pool configurations.
-                  \item Different population sizes.
-                  \item Different credit assignment strategies.
-                  \item Different reselection window sizes.
-                  \item Different replay window sizes.
-                  \item Different reanalysis window sizes.
-                  \item Different burn in window sizes.
-                  \item Enabling and disabling normalisation of pseudo counts in the performance log.
-                  \item Enabling and disabling discounted rewards of pseudo counts in the performance log.
+                  \item The \acs{BHH} baseline configuration with different \index{heuristic pool}heuristic pool configurations.
+Three different \index{heuristic pool}heuristic pool configurations were implemented.
+These configurations include a configuration with all the low-level \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool, a configuration with only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration with only \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool.
+
+                  \item The \acs{BHH} baseline configuration with different population sizes. Five different population sizes were implemented including 5, 10, 15, 20, and 25.
+
+                  \item The \acs{BHH} baseline configuration with different credit assignment strategies.
+Five different credit assignment strategies were implemented including the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies.
+
+                  \item The \acs{BHH} baseline configuration with different reselection intervals. Five different reselection intervals were implemented including 1, 5, 10, 15, and 20.
+
+                  \item The \acs{BHH} baseline configuration with different reanalysis window sizes. Five different reanalysis intervals were implemented including 1, 5, 10, 15, and 20.
+
+                  \item The \acs{BHH} baseline configuration with different replay window sizes. Five different replay window sizes were implemented including 1, 5, 10, 15, and 20.
+
+                  \item The \acs{BHH} baseline configuration with different burn in window sizes. Five different burn in window sizes were implemented including 0, 5, 10, 15, and 20.
+
+                  \item The \acs{BHH} baseline configuration where normalisation of pseudo counts for concentration parameters, as derived from credit allocations in the performance log, are enabled and disabled.
+
+                  \item The \acs{BHH} baseline configuration where discounted rewards of pseudo counts for concentration parameters, as derived from credit allocations in the performance log, are enabled and disabled.
             \end{itemize}
@@
 
-Each experimental group is run against a set of 15 datasets, consisting of regression and classification problems, split between uni- and multimodal problems.
-Each experimental group is repeated over 30 runs for statistical certainty.
-The statistical analysis process was discussed and ANOVA, post hoc Tukey, independent T-test and Kruskal-Wallis formed part of the statistical test repertoir.
+Each experimental group was executed against a set of fourteen datasets, consisting of regression and classification problems, split between uni- and multimodal problems.
+Each experimental group was repeated over 30 runs for statistical certainty.
+The statistical analysis process was discussed and the ANOVA, post hoc Tukey, independent T-test and Kruskal-Wallis statistical tests formed part of the statistical tests that were conducted.
 
-In order to allow for the studying of the \ac{BHH} even after training has saturated and overfitting has occured, all experimental groups are run for 30 epochs, way more than what has been empirically found to be necessary.
-This also meant that no early stopping conditions were used.
-
-The next section provides a summary of all the results, findings and conclusions related to the empirical process is given next.
+All experimental groups were run for a maximum of 30 epochs in order to allow for the studying of the \ac{BHH} even after training has converged and overfitting has occured.
+The maximum epoch strategy yielded a training process that is longer than what was empirically found to be necessary.
+This also meant that no early stopping strategy was used.
+Future research opportunities should incorporate an early stopping strategy of the training process.
 
@@
 
-All empirical tests where successfully executed and statistically evaluate as described in the methodology presented in Chapter \ref{chap:methodology}.
-From these evaluations a number of conclusions are made, each described briefly in the sub-sections below:
+This section provides a summary of the results obtained from each of the experimental groups that were executed. This section is structured as follows.
 
-\subsection{\ac{BHH} behavioural case study}
+\begin{itemize}
+      \item \textbf{Section \ref{sec:conclusion:results:summary:case_study}} provides a summary of the results for the experimental group that executed a case study on the behaviour of the \acs{BHH} on an example dataset.
+
+      \item \textbf{Section \ref{sec:conclusion:results:summary:standalone}} provides a summary of the results for the experimental group that compares the performance of the \acs{BHH} baseline configuration with low-level, standalone \index{heuristic}heuristics, across all datasets.
+
+      \item \textbf{Section \ref{sec:conclusion:results:summary:heuristic_pool}} provides a summary of the results for the experimental group that investigates the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the \acs{BHH}, across all datasets.
+
+      \item \textbf{Section \ref{sec:conclusion:results:summary:population_size}} provides a summary of the results for the experimental group that investigates the effects of the \textit{population size} hyper-parameter on the \acs{BHH}, across all datasets.
+
+      \item \textbf{Section \ref{sec:conclusion:results:summary:credit}} provides a summary of the results for the experimental group that investigates the effects of the \textit{credit assignment strategy} hyper-parameter on the \acs{BHH}, across all datasets.
+
+      \item \textbf{Section \ref{sec:conclusion:results:summary:reselection}} provides a summary of the results for the experimental group that investigates the effects of the \textit{reselection interval} hyper-parameter on the \acs{BHH}, across all datasets.
+
+      \item \textbf{Section \ref{sec:conclusion:results:summary:replay}} provides a summary of the results for the experimental group that investigates the effects of the \textit{replay window size} hyper-parameter on the \acs{BHH}, across all datasets.
+
+      \item \textbf{Section \ref{sec:conclusion:results:summary:reanalysis}} provides a summary of the results for the experimental group that investigates the effects of the \textit{reanalysis interval} hyper-parameter on the \acs{BHH}, across all datasets.
+
+      \item \textbf{Section \ref{sec:conclusion:results:summary:burn_in}} provides a summary of the results for the experimental group that investigates the effects of the \textit{burn in window size} hyper-parameter on the \acs{BHH}, across all datasets.
+
+      \item \textbf{Section \ref{sec:conclusion:results:summary:normalise}} provides a summary of the results for the experimental group that investigates the effects of the \textit{normalisation} hyper-parameter on the \acs{BHH}, across all datasets.
+
+      \item \textbf{Section \ref{sec:conclusion:results:summary:discounted_rewards}} provides a summary of the results for the experimental group that investigates the effects of the \textit{discounted rewards} hyper-parameter on the \acs{BHH}, across all datasets.
+\end{itemize}
+
+\subsection{Behavioural Case Study}
 \label{sec:conclusion:results:summary:case_study}
 
-For this experimental group it was found that the \ac{BHH} is able to train \acp{FFNN} relatively well.
-It was shown how the \ac{BHH} is able to learn and that the learning is in a positive direction towards the overall objectives of the \ac{BHH}.
-Furthermore, it was shown in isolation that both the selection mechanism as well as the perturbative component of the \ac{BHH} was successful in their own rights, resulting in a \ac{HH} that is able to select and combine \index{heuristic}heuristics as needed.
+For this experimental group it was found that the \ac{BHH} is able to train a \acf{FFNN} relatively well.
+Detailed analysis was provided for various state parameters maintained by the \acs{BHH}.
+These include the concentration parameters for different heuristics, probabilities of \index{heuristic}heuristic selection probabilities, prior heuristic selection probabilities and posterior heuristic selection probabilities.
+It was shown that the \ac{BHH} is able to learn and that the \acs{BHH} is able to exploit small performance biases as it relates to \index{heuristic}heuristic selection.
+This enables the \acs{BHH} to select the correct \index{heuristic}heuristics to apply to the correct entities at the correct time in the training process.
 
-It was shown how the \ac{BHH} drastically overfits at some point during training for a number of datasets.
-Although it is known that early stopping conditions would prohibit this from happening, other solutions have also been proposed.
-These include:
+Various illustrations of the train and test loss plots, as it relates to training of a \acs{FFNN} on the the iris dataset, have been provided.
+Furthermore, various illustrations on the changes of the \acs{BHH} state parameters were provided for visual aid.
 
-\begin{itemize}
-      \item \index{heuristic}Heuristic selection acceptance criteria: where a selection is only deemed valid if it does indeed improve on performance.
+The main findings that were made for this experimental group are given as follows.
+Most of the training progression is made in the early stages of the training process.
+That leads to the conclusion that the \acs{BHH} has a small window from which it should learn and gain the most in the training process.
+After training has converged, the \acs{BHH} resets its concentration parameters and heuristic selection returns to the symmetric heuristic selection case.
+As such, the \acs{BHH} explores other heuristics in an attempt to further improve on the current best solution found.
+The test set was used as a validation set during training.
+Some overfitting can be observed as the \acs{BHH} tried finding better solutions on the train set, but at the cost of generalisation on the test set.
+Minor divergence of the training loss is observed as the \acs{BHH} explores other heuristics in an attempt to improve performance.
+Since no move-acceptance strategy, and no early stopping stategy was used, the \acs{BHH} could select heuristics that are sub-optimal.
+Future research opportunities should incorporate these aforementioned strategies.
 
-      \item State reset: to avoid overshooting solutions due to momentum.
-
-      \item Various techniques to balance exploration and exploitation.
-\end{itemize}
-
-Various example plots on training and test datasets have been provided and detailed plots of the inner-workings of the \ac{BHH} have been presented to support the findings and arguments.
-
-\subsection{Standalone vs. \ac{BHH} Baseline}
+\subsection{\acs{BHH} Baseline vs. Low-Level Heuristics}
 \label{sec:conclusion:results:summary:standalone}
 
-For this experimental group the baseline \ac{BHH} was found to perform relatively well in comparison to the standalone low-level \index{heuristic}heuristics.
-Overall the \ac{BHH} ranked 5th out of 11 with performances close to that of the best \index{heuristic}heuristics.
-Unfortunately, the \ac{BHH} was not entirely able to beat the best heuristics on all occasions, but did perform comparatively well in all cases.
-The empirical results, statistical tests, descriptive plots and plots of example runs are given to support findings and conclusions.
+For this experimental group, three different configurations of the \acs{BHH} baseline configuration were implemented.
+These configurations vary in the type of \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool.
+The \textit{bhh\_all} configuration included all low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool.
+The \textit{bhh\_gd} configuration included only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the \textit{bhh\_mh} configuration included only \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool.
 
-\subsection{\ac{BHH} Variant: Heuristic pool}
+Overall the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen \index{heuristic}heuristics that were implemented and executed on fourteen datasets.
+The \textit{bhh\_gd} configuration produced performance results close to that of the best low-level \index{heuristic}heuristics and was only statistically outperformed by the top two low-level \index{heuristic}heuristics.
+The \textit{bhh\_all} configuration achieved an overall rank of sixth and the \textit{bhh\_mh} achieved an overall rank of eighth.
+
+Although the \textit{bhh\_gd} configuration produced performance results comparable to the best low-level heuristics, the \textit{bhh\_all} and \textit{bhh\_mh} configurations produced average results.
+It was found that, in general, gradient-based heuristics produced the best results, as such, it it understandable that the \textit{bhh\_gd}  yielded the best performance outcomes between the different \acs{BHH} variants that were implemented.
+Although the \acs{BHH} variants were not able to produce better results than the top low-level \index{heuristic}heuristics, the \acs{BHH} variants still effectively trained the underlying \acp{FFNN} and produced good training outcomes overall.
+
+It was shown that the \textit{bhh\_gd} configuration produced the lowest variance in rank between datasets out of all of the \index{heuristic}heuristics implemented, giving the \acs{BHH} the ability to generalise well to other problems.
+
+Furthermore, it was shown that the \acs{BHH} provides a mechanism whereby prior expert knowledge can be injected, before training starts.
+Future research can exploit this knowledge and provide a significant bias towards \index{heuristic}heuristics that are known to perform well on particular problem types.
+
+\subsection{Heuristic pool}
 \label{sec:conclusion:results:summary:heuristic_pool}
 
-For this experimental group, different configurations of \index{heuristic}heuristic pools were considered.
-Three different configurations were evaluated.
-It was found that the gradient-only \ac{BHH} variant performed significantly better than the configurations that included all of the heuristics and one that included only the meta-heuristics.
-It was shown that the inclusion of meta-heuristics cause the \ac{BHH} to overfit much more drastically due to the nature of their update step operations.
+For this experimental group, the same three \index{heuristic pool}heuristical pool variants, as outlined for the \acs{BHH} behavioural case study, was implemented.
+These variants are denoted as \textit{all}, \textit{gd}, and \textit{mh}.
+This experimental group then provided an opportunity to look at the effects of the \index{heuristic pool}heuristic pool hyper-parameter in more detail.
 
-\subsection{\ac{BHH} Variant: Population Size}
+As with the experimental group that compares the performance of the \acs{BHH} baseline configuration with low-level, standalone \index{heuristic}heuristics, it was found that the \textit{gd} configuration performed significantly better than the \textit{all} and \textit{mh} configurations overall, across all datasets.
+
+The benefits of using meta-heuristics in the heuristic pool was not realised in this dissertation, since the gradient-based low-level \index{heuristic}heuristics, as well as the \textit{gd} configuration produced the best overall performance, across all datasets.
+
+\subsection{Population Size}
 \label{sec:conclusion:results:summary:population_size}
 
-For this experimental group, various different population sizes are evaluated.
-It was found that the population size is largely problem-dependent.
-An interesting observation was made where some cases where shown where the relationship between population size and performance is not linear, but rather parabolic or even polynomial in some cases.
-This warrants for further investigation and could serve as a good opportunity for future research.
+For this experimental group, five different population sizes were evaluated.
+These included population sizes of 5, 10, 15, 20, and 25.
+It was found that lower population sizes yielded better results on the majority of datasets, while only some datasets prefer larger population sizes.
+However, overall it was shown that the population size hyper-parameter is problem specific.
+Illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
+Some divergence in training loss was observed and was attributed to selection of \index{heuristic}heuristics that yield sub-optimal results after an optimal solution has already been found.
+As before, a move acceptance strategy and an early stopping strategy can be incorporated to avoid this effect.
 
-\subsection{\ac{BHH} Variant: Credit}
+\subsection{Credit Assignment Strategy}
 \label{sec:conclusion:results:summary:credit}
 
-For this experimental group, various different credit assignment strategies were evaluated.
-It was found that the choice of credit assignment strategy to use is largely problem-dependent.
-Two cases were highlighted where symmetric credit assignment was preferred, which suggests that for that dataset \index{heuristic}heuristic selection doesn't matter, only the proxied update step operations are sufficient.
+For this experimental group, five different credit assignment strategies were evaluated.
+These included the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies.
+No clear overall difference in performance was observed for the various credit assignment strategies.
+In the majority of cases, a particular non-symmetric credit assignment strategy yielded the best performance, while the \textit{symmetric} credit assignment strategy yielded the best performance results in one case.
+It can therefore be concluded that the credit assignment strategy is problem specific.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-\subsection{\ac{BHH} Variant: Reselection}
+\subsection{Reselection Interval}
 \label{sec:conclusion:results:summary:reselection}
 
-For this experimental group different reselection window sizes were evaluated.
-It was found that a larger reselection size is generally preferred.
-A bigger reselection window sizes lead to a longer timeframe to learn before reselection has to occur.
-The increase in number of samples of evidence, per entity-heuristic combination in the performance log is argued to be the reason for this.
-However, that means that the reselection and replay window size parameter are related.
-If the reselection window size is large, the replay window size should be large as well.
+For this experimental group, five different reselection intervals were evaluated.
+These included reselection intervals of 1, 5, 10, 15, and 20.
+Overall, with statistical significance, it was found that a larger reselection interval is generally preferred.
+It was found that larger reselection intervals lead to longer timeframes for the low-level heuristics to progress, smoothing out update steps.
+Larger reselection intervals also allow the \acs{BHH} to collect more samples of \index{heuristic}heuristic performance evidence from which it can learn.
+Therefore, a conclusion that can be made is that \index{heuristic}heuristic and solution exploitation is preferred over exploration.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-\subsection{\ac{BHH} Variant: Replay}
+\subsection{Replay}
 \label{sec:conclusion:results:summary:replay}
 
-For this experimental group, different replay windows sizes were evaluated.
-It was found that the replay window is problem-dependent with some dataset preferring short memory and other preferring long memory.
-Take note of the relationship between the reselection, replay and reanalysis window sizes.
-The value of the one does influence the value of other and should be carefully selection together.
+For this experimental group, five different replay windows sizes were evaluated.
+These included replay window sizes of 1, 5, 10, 15, and 20.
+Overall, no statistically significant difference was found for the performance of the replay window size configurations, and thus, it was concluded that the replay window size is problem specific, with some datasets preferring short memory and other preferring long memory.
+The relationship between the reselection interval, replay window size and reanalysis interval was discussed, and it was shown that these hyper-parameters should be considered together.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-\subsection{\ac{BHH} Variant: Reanalysis}
+\subsection{Reanalysis Interval}
 \label{sec:conclusion:results:summary:reanalysis}
 
-For this experimental group different reanalysis window sizes were evaluated.
-It was also found that the reanalysis window size is problem-dependent.
-Given the relationship between the reselection, replay and reanalysis window sizes, a suggestion to eliminate hyper-parameters is to remove the notion of reanalysis and merge with reselection.
-Reselection is shown to correlate with reanalysis and thus can be removed by just setting the reanalysis window size equal to the reselection size.
+For this experimental group, five different reanalysis intervals were evaluated.
+These included reanalysis intervals of 1, 5, 10, 15, and 20.
+Overall, no statistically significant difference was found for the performance of the reanalysis intervals across all datasets, and thus, it was concluded that the reanalysis interval is problem specific.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-\subsection{\ac{BHH} Variant: Burn In}
+\subsection{Burn In}
 \label{sec:conclusion:results:summary:burn_in}
 
-For this experimental group different burn in window sizes were evaluated.
-It was found that in general no burn in is preferred, but some exceptions preferring just a very small burn in.
-In general is was shown that large burn in values are not good.
+For this experimental group, five different burn in window sizes were evaluated.
+These included burn in window sizes of 1, 5, 10, 15, and 20.
+Overall, it was found with statistical significance, that lower burn in window sizes are generally preferred.
+The lower burn in window sizes generally produced the best results in the majority of cases, with some exceptions that prefer average burn in window sizes.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-\subsection{\ac{BHH} Variant: Normalise}
+\subsection{Normalisation}
 \label{sec:conclusion:results:summary:normalise}
 
-For this experimental group an empirical test was conducted to determine the effects of normalisation of pseudo counts in the performance log.
-The choice of this parameter was shown to be problem depedent.
+For this experimental group an empirical test was conducted to determine the effects of normalisation of pseudo counts allocated by the credit assignment strategy in the performance log.
+A configuration is included with normalisation enabled and a configuration is included with normalisation disabled.
+It was concluded that the default replay window size of ten is too small to yield a significant difference in performance outcome for when normalisation is enabled compared to when normalisation is disabled.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-\subsection{\ac{BHH} Variant: Discounted Rewards}
+\subsection{Discounted Rewards}
 \label{sec:conclusion:results:summary:discounted_rewards}
 
-It can be concluded that the outcomes of the empirical process were successful and that the scientific process has been followed accordingly.
-From this, it can be concluded that all of the objective of the dissertation have been met and that the research can be concluded.
-The next section provides a brief discussion of further research opportunities that stem from this work.
+For this experimental group an empirical test was conducted to determine the effects of discounted rewards of pseudo counts allocated by the credit assignment strategy in the performance log.
+A configuration is included with discounted rewards enabled and a configuration is included with discounted rewards disabled.
+Similar to the findings for the experimental group investigating the effects of the normalisation hyper-parameter, it was concluded that the default replay window size of ten is too small to yield a significant difference in performance outcome for when discounted rewards is enabled compared to when discounted rewards is disabled.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-\section{Further Research}
+\section{Future Research Opportunities}
 \label{sec:conclusion:further_research}
 
-Throughout this dissertation, many different opportunities have been identified for future research. This section contains a summmary of these topics.
+Throughout this dissertation, many different opportunities have been identified for future research. This section contains a summary of each of these topics.
 
-\subsubsection{Prior Knowledge}
+\subsubsection{A Priori Biases}
+\label{sec:conclusion:further_research:a_priori_biases}
 
-The \ac{BHH} initialises the concentrations for its distributions symmetrically (a value of 1 for all indices).
-Symmetric initialisation contains no prior bias and assumes uniform sampling at first.
-It has been identified that expert knowledge can be incorporated into the \ac{BHH} by carefully providing the initial concentration for the distributions.
-This research would then evaluate if such prior information has a positive impact on the outcomes of the \ac{BHH}.
+By default, the \acs{BHH} initialises the values for the concentration parameters, related to each \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool, symmetrically with an initial value of 1.0.
+This yields an initial probability distribution of the \index{heuristic}heuristic selection probabilities that is uniform.
+Symmetric initialisation contains no a priori \index{heuristic}heuristic selection bias and assumes uniform sampling at first.
+It has been identified that expert knowledge can be incorporated into the \acs{BHH} by carefully providing the initial concentrations for the each \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.
+Such research would then evaluate if such prior \index{heuristic}heuristic selection biases have a positive impact on the outcomes of the \acs{BHH}.
 
-\subsubsection{Early Stopping}
+\subsubsection{Move Acceptance Strategies}
+\label{sec:conclusion:further_research:move_acceptance}
 
-It has been shown that the \ac{BHH} suffers drastically from overfitting as the majority of learning happens during the first few epochs (large datasets have more mini-batch iterations per epoch) resulting in the majority of the training process, which span 30 epochs, to try recover from overfitting.
-Early stop was purposefully not utilised in this research in order to see how the \ac{BHH} would behave after training has saturated.
-Early stopping could provide valuable insight into the actual ranked performance of the \ac{BHH} since overfitting would then no longer be present and a ranked performance evaluation can be done at some point in time.
+Throughout the presentation of the empirical results, it is mentioned that a move-acceptance strategy can be incorporated to reject \index{heuristic}heuristic progressions that do not improve on the current best solution found.
+This would eliminate any divergence in the training process as a result of selecting sub-optimal \index{heuristic}heuristics.
+Various different move-acceptance strategies can be developed and empirically tested.
+
+\subsubsection{Early Stopping Strategies}
+\label{sec:conclusion:further_research:early_stopping}
+
+Similar to the move-acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to hault the training process if the performance does not improve for a number of steps.
+In this dissertation, a number of examples were presented where divergence of training loss occurred.
+Furthermore, a number of examples were presented where overfitting occurred.
+An early stopping strategy can help prevent such outcomes.
 
 \subsubsection{Entity Search}
+\label{sec:conclusion:further_research:entity_search}
+For this dissertation, even though the predictive model implemented by the \acs{BHH} includes entity consideration, it does not sample from an entity pool.
+The \acs{BHH} keeps the entire entity pool fixed, and just reselects heuristics for each entity.
+The \acs{BHH}, as is, can be used to learn which entities to select as well.
+The hypothesis is that this would result in better combinations of entities and heuristics, which should have a positive effect on the outcomes of the \acs{BHH}.
 
-For this dissertation, even though the predictive model implemented by the \ac{BHH} includes entity consideration, it does not sample from an entity pool, but rather keeps the entire entity pool and just switch allocated heuristics.
-The \ac{BHH}, as is, can be used to learn which entities to select as well.
-The hypothesis is that this would result in better combinations of entities and heuristics, more often, which should have a positive effect on the outcomes of the \ac{BHH}
+\subsubsection{Continuous Valued Credit Allocation}
+\label{sec:conclusion:further_research:continuous_credit}
+
+Credit assignment in the context of this dissertation yields a discrete credit allocation value.
+More specifically, the credit allocation is binary, yielding a zero or a one.
+Future research can investigate different credit allocation strategies that yield continuous valued outcomes.
+This should provide more fine-grained indicators of \index{heuristic}heuristic performance which the \acs{BHH} can exploit easier.
+
+\subsubsection{Credit Search}
+\label{sec:conclusion:further_research:credit_search}
+
+Similar to entity search, the \acs{BHH}, as is, can be used to learn which credit assignment strategies to use.
+This can then be combined with heuristic and entity selection so that the correct heuristic is selected for the correct entity, by means of the correct credit allocation strategy that is applicable, at the correct time in the training process.
+For example, a particular heuristic-entity combination might benefit from a \textit{pbest} credit allocation, while another heuristic-entity combination might benefit from a \textit{ibest} credit allocation at the same time in the training process.
 
 \subsubsection{Models}
+\label{sec:conclusion:further_research:models}
 
 For this dissertation, focus was put on training \acp{FFNN}.
-However, in theory one should be able to swap out \acp{FFNN} for any other mathematical model that can be optimised.
-Suggestions include \acp{DNN}, \acp{RNN} and dynamic optimisation problems.
+However, in theory, other models can also be used.
+Suggestions include \acp{DNN} and \acp{RNN}.
+Furthermore, future research can attempt to use the \acs{BHH} for dynamic optimisation problems.
 
-\subsubsection{Credit Search}
+\subsubsection{Dynamic Hyper-Parameter Values}
+\label{sec:conclusion:further_research:dynamic_hyper_parameters}
 
-Credit assignment in the context of this dissertation was has 2 outcomes, true and false.
-Therefore, credit assignment and by definition performance evaluation is modeled as a \index{binomial distribution} distribution with a \index{Beta probability distribution}Beta probability distribution as a prior probability distribution.
-Heuristic selection has multiple possible outcomes, yielding a index associated with a heuristic.
-Therefore, heuristic selection is modeled as a \index{multionomial}multinomial/\index{categorical}categorical with a dirichlet probability distribution as a prior probability distribution.
-Since the dirichlet-multinomial distributions are the multivariate extensions of the beta-binomial distributions, it show be possible to extend credit assignment to a multivariate version.
-A suggestion then is to learn which credit assignment to select.
-The results of this have show that credit assignment is problem-dependent.
-Therefore, include credit selection as part of the selection pool implemented by the \ac{BHH}.
-One could then include multiple strategies, each with varying exploration-exploitation trade-off.
-
-\subsubsection{Selection Validation}
-
-The intent behind a selection validation mechanism is to confirm that selections are successful before they are utilised.
-In other words, a small verification window where it is decided whether the outcomes of a selection mechanism was beneficial to the learning outcomes or not.
-These selection validations are based on an ``acceptance criterion'' that a selection has to pass before it is validated.
-Inclusion of a selection validation mechanism for the \ac{BHH} could yield interesting outcomes.
-
-\subsubsection{Dynamic Reselection Window Size Strategies}
-
-It was shown that generally larger reselection window sizes are required.
-It was shown that there is a relationship between the reselection, replay and reanalysis window sizes.
-There is an inherent trade-off between exploration and exploitation and therefore, investigation into dynamic sizing strategies could be prove to yield interesting outcomes.
+It was shown that larger reselection intervals are generally preferred.
+It was shown that there is a relationship between the reselection interval, the replay window size and the reanalysis interval.
+These hyper-parameters provide an mechanism for trade-off between exploration and exploitation and therefore, investigation into dynamic selection of hyper-parameter values can be considered in future research.
 
 \subsubsection{Heuristic Pools}
+\label{sec:conclusion:further_research:heuristic_pools}
 
-This dissertation only considered 3 different configurations of the heuristic pool. The following alternative  configurations could be considered:
-
-\begin{itemize}
-      \item Multiple of the same heuristic, but with different hyper-parameter values.
-      \item Very large or very small heuristic pool sizes.
-      \item Inclusion of black-box optimisers such as CMA-ES.
-      \item Ensemble pools where the heuristic selection is a selection of a ensemble configuration.
-\end{itemize}
+This dissertation only considered three different types of \index{heuristic pool}heuristic pool configurations.
+The following alternative configurations could be considered.
+A \index{heuristic pool}heuristic pool could be considered where multiple instances of the same \index{heuristic}heuristic is included, but with different hyper-parameter values, effectively implementing dynamic hyper-parameter optimisation.
+Empirical testing can be done to determine the effects of various \index{heuristic pool}heuristic pool sizes.
+Different types of heuristics can be considered for inclusion in the \index{heuristic pool}heuristic pool.
+A suggestion is to include black-box optimisers such as \acs{CMA-ES}.
+Finally, \index{heuristic}heuristic ensemble pools could be considered, where the \index{heuristic}heuristic selection is a selection of an ensemble of \index{heuristic}heuristics.
 
 \subsubsection{Parameter Pools}
+\label{sec:conclusion:further_research:parameter_pools}
 
-Throughout this dissertation, many of the findings have been said to be "problem-dependent".
-A possible solution to this is to apply the \ac{BHH} then for all parameters, not just heuristics.
-This means to include hyper-parameters such as learning rate, which can be "learnt" during training.
-This eliminates a lot of the burden to tediously fine-tune and optimise hyper-params.
-
-This could also provide opportunity to investigate other \ac{FFNN} paradigms such as neural architecture search (ref ???) by including various parameters, that describe the \ac{NN} architecture.
-The \ac{BHH} slection mechanism can then include these elements for learning as well.
-
-\subsubsection{Models}
-
-This dissertation focused on \acp{FFNN} as the underlying model to be trained. However, other models can also be considered.
+A suggestion for future research is to apply the \acs{BHH} to a multitude of parameter types.
+These could be hyper-parameters of the low-level \index{heuristic}heuristics, the parameters for the topology and architecture of models (similar to neural architecture search) or the hyper-parameters of the \acs{BHH} itself.
 
@@
 
-All data, source code, logs, configurations, scripts and analysis is hosted at: \url{https://github.com/arneschreuder/masters.ai} with raw empirical data made available on Google Cloud project id: masters-363209.
+All the source code, data, logs and analyses that were used in this dissertation, as well as the dissertation source itself, can be found at \url{https://github.com/arneschreuder/masters.ai}.
+The raw empirical data is made available on Google Cloud's BigQuery platform, under the project id \textit{masters-363209}.
 
-\section{Closing Statements}
-\label{sec:conclusion:closing_statements}
+\section{Summary}
+\label{sec:conclusion:summary}
 
-The research that is presented in this dissertation included the development and detailed analysis of a novel \ac{BHH}.
-This chapter presented a review of the research objectives.
-In conclusion it is found that all of the research objectives have been met.
-The empirical process was sound and the research outcome have been shown to be statistically significant.
-This concludes the research presented in this document
+This chapter concludes the research that is done in this dissertation.
+This chapter provided a summary of the research intent, providing a brief review of the research problem, motivations and objectives defined for this dissertation.
+A brief summary of the background information that is covered in this dissertation is provided.
+A brief summary on the concept and implementation of the novel \acs{BHH} is provided, followed by a brief summary of the methodology that is used for the empirical process.
+This chapter also provided brief summaries of the results and findings for each of the experimental groups that were executed in the empirical process.
+Future research opportunities were identified and reference is made to materials and assets used in this dissertation that are made available online.

### 2022-11-24 dissertation/chapters/01-introduction.tex
✨ (chapter4): Review Done
✨ (final-review): Done up till chapter 1

@@
 \begin{flushright}
-      George Polya
+      - George Polya
 \end{flushright}
 
-\noindent
 \Acf{ML} is one of the most popular fields of research in \acf{AI} studies today.
@@
 A popular field of focus for studying \acp{ANN} is the process by which these models are trained.
-The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input and comparing the produced output to that of predefined target data.
+The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input data and comparing the produced output data to that of predefined target data.
 Training of \acp{ANN} is seen as an optimisation problem.
@@
 
-The following section outlines the research problem that this dissertation aims to address and is followed by a motivation for this research.
-
 \section{Problem Statement}\label{sec:introduction:problem}
@@
 This process is often non-trivial and could be a time-consuming exercise.
-Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is problem dependent~\cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
+Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is problem specific~\cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
 
@@
 
-\acp{FFNN} training is seen as a computational search problem.
-\acf{HH} as defined by Burke et al.~\cite{ref:burke:2010} is ``a search method or learning mechanism for selecting or generating heuristics to solve computational search problems''.
+Training of \acp{FFNN} is seen as a computational search problem.
+A \acf{HH}, as defined by Burke et al.~\cite{ref:burke:2010}, is ``a search method or learning mechanism for selecting or generating heuristics to solve computational search problems''.
 \acp{HH} is a field of research aimed at the automated selection, combination, adaptation or generation of multiple lower-level heuristics to efficiently solve computational search problems.
@@
 Furthermore, \acp{HH} can generally be applied to multiple problems given that the set of low-level heuristics include heuristics that have the potential to solve the problem at hand~\cite{ref:burke:2010}.
-Automation of the heuristic selection process and the general application to a wider range of problems are characteristics of \acp{HH} that can be beneficial when applied in the context of \acp{FFNN} training.
+Automation of the heuristic selection process and the general application to a wider range of problems are characteristics of \acp{HH} that can be beneficial when applied in the context of training \acp{FFNN}.
 
@@
 
-      \item Provide a statistically sound analysis of the results obtained from the empirical study.
+      \item Provide a statistical analysis of the results obtained from the empirical study.
 \end{itemize}
-
-\noindent
-By achieving the objectives outlined above, a number of research contributions are made. These contributions are presented in this following section.
 
@@
       \item The results of the empirical study show with statistical significance and certainty that the \Acs{BHH} performs generally well on multiple problems.
-It is shown that, for each problem, the \Acs{BHH} performance is comparable to the best low-level heuristics (for the particular problem) included in the heuristic selection pool.
+It is shown that, for each problem, the \Acs{BHH} performance is comparable to the best low-level heuristics included in the heuristic selection pool.
 
@@
 Discussions follow on how the \Acs{BHH} is shown to automate the selection of the best heuristic during the training of \acp{FFNN}, as applied to a range of problems, alleviating the burden on researchers to apply traditional trial and error approaches.
-The chapter is concluded with a brief argument in favor of the general applicability of the \Acs{BHH} to more problem domains.
 
@@
 
-\noindent
 This dissertation is accompanied by a full index given at page~\pageref{index} along with the following appendices:
@@
 \begin{itemize}
-      \item \textbf{Appendix~\ref{app:backpropagation}} provides a full breakdown of the \acf{BP} algorithm as presented by~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007}.
-
       \item \textbf{Appendix~\ref{app:datasets}} provides details on the datasets used for the empirical analysis.
@@
 
-\noindent
 To best view the illustrations, tables and figures presented throughout this dissertation, it is recommended that the dissertation be viewed in colour.

### 2022-11-24 dissertation/preamble/abstract.tex
✨ (final-review): Done up till chapter 1

@@
 \noindent
-Many different heuristics have been developed and used to train \acfp{FFNN}.  However, selection of the best heuristic to train
-\acsp{FFNN} is a time consuming and non-trivial exercise. Careful, systematic
-selection is thus required to ensure that the best heuristic is used to train the \acsp{FFNN}. In the past, selection
-was done by trial and error. A modern approach is to automate the heuristic selection
-process. Often it is found that a single approach is not sufficient. Research has
-proposed the use of hybridisation of heuristics. One such approach is referred to
-as \acfp{HH}. \acsp{HH} focus on dynamically finding the best heuristic or combinations of heuristics in
-heuristic-space by making use of heuristic performance information during training time. One such
-implementation of a \acs{HH} is a population-based approach that guides the search process by
-dynamically selecting heuristics from a heuristic-pool to be applied to
-different entities that represent candidate solutions to the problem-space and
-work together to find good solutions. This dissertation introduces a novel population-based \Acf{BHH}. An empirical study is done by
-using the \acs{BHH} to train \acsp{FFNN}. An in-depth behaviour analysis is done and the performance of the \acs{BHH} is compared to that of ten popular low-level heuristics each with different search
-behaviours.
+Many different heuristics have been developed and used to train \acfp{FFNN}.
+However, selection of the best heuristic to train \acp{FFNN} is a time consuming and non-trivial exercise.
+Careful, systematic selection is required to ensure that the best heuristic is used to train \acp{FFNN}.
+In the past, selection was done by trial and error.
+A modern approach is to automate the heuristic selection process.
+Often it is found that a single approach is not sufficient.
+Research has proposed the use of hybridisation of heuristics.
+One such approach is referred to as \acfp{HH}.
+\acsp{HH} focus on dynamically finding the best heuristic or combinations of heuristics in heuristic-space by making use of heuristic performance information.
+One such implementation of a \acs{HH} is a population-based approach that guides the search process by dynamically selecting heuristics from a heuristic-pool to be applied to different entities that represent candidate solutions to the problem-space, and work together to find good solutions.
+This dissertation introduces a novel population-based \Acf{BHH}.
+An empirical study is done by using the \acs{BHH} to train \acsp{FFNN}.
+An in-depth behaviour analysis is done and the performance of the \acs{BHH} is compared to that of ten popular low-level heuristics each with different search behaviours.
 The chosen heuristic pool consists out of classic gradient-based heuristics as well as meta-heuristics.
-The empirical process was executed on fifteen datasets consisting of classification and regression problems
-with varying characteristics.
+The empirical process is executed on fourteen datasets consisting of classification and regression problems with varying characteristics.
 Results are analysed for statistical significance and the \acs{BHH} is shown to be able to train \acsp{FFNN} well and provide an automated method for finding the best heuristic to train the \acsp{FFNN} at various stages of the training process.\\*[1cm]
@@
 \parbox{\textwidth}{
-    \textbf{Keywords:} hyper-heuristics, meta-learning, feedforward neural
-    networks, supervised learning, Bayesian statistics
+    \textbf{Keywords:} hyper-heuristics, meta-learning, feedforward neural networks, supervised learning, Bayesian statistics
 }

### 2022-11-24 bhh.py

@@ -78,7 +78,6 @@ def parse_bhh_arguments():
         required=True,
         choices=[
             "abalone",
-            "adult",
             "air_quality",
             "bank",
             "bike",
@@ -93,7 +92,7 @@ def parse_bhh_arguments():
             "student_performance",
             "wine_quality",
         ],
-        help="The dataset to use"
+        help="The dataset to use",
     )
     parser.add_argument("--seed", type=int, help="The seed to use")
     parser.add_argument("--log-level", type=int, help="The log level to use")
@@ -108,85 +107,54 @@ def parse_bhh_arguments():
             "gd",
             "mh",
         ],
-        help="The BHH heuristic pool to use"
+        help="The BHH heuristic pool to use",
     )
     parser.add_argument(
         "--population-size",
         type=int,
         required=False,
-        choices=[
-            5,
-            10,
-            15,
-            20,
-            25
-        ],
+        choices=[5, 10, 15, 20, 25],
         default=5,
-        help="The population size to use"
+        help="The population size to use",
     )
     parser.add_argument(
         "--burn_in",
         type=int,
         required=False,
-        choices=[
-            0,
-            5,
-            10,
-            15,
-            20
-        ],
+        choices=[0, 5, 10, 15, 20],
         default=0,
-        help="The burn-in to use"
+        help="The burn-in to use",
     )
     parser.add_argument(
         "--replay",
         type=int,
         required=False,
-        choices=[
-            1,
-            5,
-            10,
-            15,
-            20,
-            250 # Special case
-        ],
+        choices=[1, 5, 10, 15, 20, 250],  # Special case
         default=10,
-        help="The replay buffer size to use"
+        help="The replay buffer size to use",
     )
     parser.add_argument(
         "--reselection",
         type=int,
         required=False,
-        choices=[
-            1,
-            5,
-            10,
-            15,
-            20
-        ],
+        choices=[1, 5, 10, 15, 20],
         default=10,
-        help="The reselection interval to use"
+        help="The reselection interval to use",
     )
     parser.add_argument(
         "--reanalysis",
         type=int,
[…]

### 2022-11-24 dissertation/chapters/02-artificial-neural-networks.tex
✨ (chapter4): Review Done
✨ (final-review): Done up till chapter 2

@@
 \begin{quotation}
-      \noindent ``Men ought to know that from the brain, and from the brain only, arise our pleasures, joy, laughter and jests, as well as our sorrows, pains, griefs, and tears.''
+      ``Men ought to know that from the brain, and from the brain only, arise our pleasures, joy, laughter and jests, as well as our sorrows, pains, griefs, and tears.''
 \end{quotation}
 \begin{flushright}
-      Hippocrates
+      - Hippocrates
 \end{flushright}
 
-\noindent
 The human brain is one of the most complicated biological organs in nature.
@@
 \acp{ANN} are used throughout this dissertation as the \textit{model} to be trained using \acp{HH}.
-
 The purpose of this chapter is to provide the necessary background information needed on \acp{ANN} and is structured as follows.
@@
 
-\begin{figure}[htpb]
+\begin{figure}[htb]
       \centering
@@
 
-\noindent
 The biological neural systems are made up of microscopic nerve cells called neurons~\cite{ref:jain:1996}.
@@
 activation function used~\cite{ref:engelbrecht:2007} and is given
-in Equation~\eqref{eq:an_function_mapping} below.
+as
 
@@
 
-\noindent
-In Equation~\eqref{eq:an_function_mapping} above, $f_{AN}$ is the mapping function produced by the \acs{AN}, $I$ is the total number of dimensions of the input in real-number space ($\mathbb{R}$), and $T$ is the total number of dimensions of the target (desired output) in real-number space.
+where $f_{AN}$ is the mapping function produced by the \acs{AN}, $I$ is the total number of dimensions of the input in real-number space ($\mathbb{R}$), and $T$ is the total number of dimensions of the target (desired output) in real-number space.
 
@@
 
-\noindent
-Each of the components of the \acs{AN} is inspired by some element of the \acs{BN}. Brief descriptions of these are given as follows.
+Each of the components of the \acs{AN} is inspired by some element of the \acs{BN}. Brief descriptions of these are given as follows:
 
@@
       \item \textbf{Input:} The input models the activations received from the pre-synaptic neuron or from some environment sensor.
-Input is represented by the input vector $\vec{x}$, in Figure~\ref{fig:artificial_neuron}.
+Input is represented by the input vector $\boldsymbol{x}$, in Figure~\ref{fig:artificial_neuron}.
 
-      \item \textbf{Weights:} The weights model the \index{synapse}synapses and connection strengths. Weights are represented by the weight vector $\vec{v}$, in Figure~\ref{fig:artificial_neuron}.
+      \item \textbf{Weights:} The weights model the \index{synapse}synapses and connection strengths.
+Weights are represented by the weight vector $\boldsymbol{v}$, in Figure~\ref{fig:artificial_neuron}.
 
@@
 
-      \item \textbf{Output:} The output models the activation by the post-synaptic neuron. Output is represented by the output vector $\vec{y}$, in Figure~\ref{fig:artificial_neuron}.
+      \item \textbf{Output:} The output models the activation by the post-synaptic neuron. Output is represented by the output vector $\boldsymbol{y}$, in Figure~\ref{fig:artificial_neuron}.
 \end{itemize}
 
-\noindent
 The following sections provide a detailed discussion on each of the above mentioned components.
@@
 Harris and Harris~\cite{ref:harris:2010} describe \index{one-hot encoding}one-hot encoding as a group of vector elements where the classes are represented with a single high element (represented by $1$) and all the others low (represented by $0$).
-Each element $y_k$, where $k$ is the $k$-th element of the encoded vector $\vec{y}$, uniquely refers to a class.
+Each element $y_k$, where $k$ is the $k$-th element of the encoded vector $\boldsymbol{y}$, uniquely refers to a class.
 An activation, represented by a value of $1$ at a given index thus represents a class associated with that index.
@@
 The \index{min-max scaler}min-max scaler is used as a pre-processing technique for target values when the \index{sigmoid}\textit{sigmoid} \index{activation function} activation function is used.
-The \index{min-max scaler}min-max scaler is given in Equation~\eqref{eq:min_max_scaler} below.
+The \index{min-max scaler}min-max scaler is given as
 
@@
 
-\noindent
-In Equation~\eqref{eq:min_max_scaler} above, $x_{i,p}^{'}$ is the normalised form of $x_{i,p}$, the $i$-th dimension of the input vector $\vec{x}_p$, $p \in \{1,2, \dots, P \}$, where $P$ is the total number of input patterns, $x_{i_{min}}$ and $x_{i_{max}}$ are respectfully the minimum and maximum values of the $i$-th dimension for all input vectors $\vec{x}_p$.
+where $x_{i,p}^{'}$ is the normalised form of $x_{i,p}$, the $i$-th dimension of the input vector $\boldsymbol{x}_p$, $p \in \{1,2, \dots, P \}$, where $P$ is the total number of input patterns, $x_{i_{min}}$ and $x_{i_{max}}$ are respectfully the minimum and maximum values of the $i$-th dimension for all input vectors $\boldsymbol{x}_p$.
 
@@
 
-The \index{standard score scaler}standard score scaler, also known as the \index{z-score scaler}\textit{z-score scaler}, scales values by subtracting the mean and scaling to the unit variance of each dimension $i$ for all input patterns $\vec{x}_p, p \in \{1,2, \dots, P\}$.
+The \index{standard score scaler}standard score scaler, also known as the \index{z-score scaler}\textit{z-score scaler}, scales values by subtracting the mean and scaling to the unit variance of each dimension $i$ for all input patterns $\boldsymbol{x}_p, p \in \{1,2, \dots, P\}$.
 The \index{standard score scaler}standard score scaler is used as a pre-processing technique for target values when the \index{hyperbolic tangent}\textit{hyperbolic tangent} \index{activation function}activation function\index{activation function} is used.
-The \index{standard score scaler}standard score scaler is given in Equation~\eqref{eq:standard_score_scaler} below.
+The \index{standard score scaler}standard score scaler is given as
 
@@
 
-\noindent
-In Equation~\eqref{eq:standard_score_scaler} above, $\mu_i$ and $\sigma^2_i$ are respectfully the mean and unit variance of the $i$-th dimension of all input vectors $\vec{x}_p$.
+where $\mu_i$ and $\sigma^2_i$ are respectfully the mean and unit variance of the $i$-th dimension of all input vectors $\boldsymbol{x}_p$.
 
@@
 
-A common way by which the \index{net input signal}net input signal is calculated is by means of \acp{SU}~\cite{ref:engelbrecht:2007}, which compute the \index{net input signal}net input signal as the weighted sum of all input signals as shown in Equation~\eqref{eq:summation_units} below.
+A common way by which the \index{net input signal}net input signal is calculated is by means of \acp{SU}~\cite{ref:engelbrecht:2007}, which compute the \index{net input signal}net input signal as the weighted sum of all input signals and is given as
 
@@
 
-\noindent
-In Equation~\eqref{eq:summation_units} above, $x_{i}$ is the $i$-th dimension of the input vector $\vec{x}$, and $v_{i}$ is the $i$-th dimension of the weight vector $\vec{v}$, associated with the given input dimension.
+where $x_{i}$ is the $i$-th dimension of the input vector $\boldsymbol{x}$, and $v_{i}$ is the $i$-th dimension of the weight vector $\boldsymbol{v}$, associated with the given input dimension.
 
@@
 A constant value $x_{i+1} = -1$ can be used, meaning that the weight associated with the bias unit, $v_{i+1}$, is optimised along with the other weights during the optimisation process.
-The net input signal as given in Equation~\eqref{eq:summation_units} then changes as is shown in Equation~\eqref{eq:augmented_vectors} below.
+The net input signal, as given in Equation~\eqref{eq:summation_units}, then changes as
 
@@
 
-\noindent
 Many different \index{activation function}activation functions have been developed~\cite{ref:karlik:2011}.
@@
 
-The \acf{ReLU} \index{activation function}activation function is an \index{activation function}activation function defined in the positive part of its argument and is given in Equation~\eqref{eq:relu} below.
+The \acf{ReLU} \index{activation function}activation function is an \index{activation function}activation function defined in the positive part of its argument and is given as
 
@@
 
-\noindent
 An advantage of \acs{ReLU} is that it is not susceptible to the \index{vanishing gradients problem}vanishing gradients problem~\cite{ref:xu:2015, ref:maksutov:2018} which occurs when gradients in the first layers of a multi-layer \acs{ANN} approach zero, and have no effect on the training process.
@@
 However, \acs{LReLU} does not suffer from the \index{dying ReLU problem}dying \acs{ReLU} problem~\cite{ref:agarap:2018}, which occurs when the neurons that use \acs{ReLU} \index{activation function}activation functions become \textit{inactive} and only output $0$ due to a negative net input signal.
-The \acs{LReLU} \index{activation function}activation function is defined in Equation~\eqref{eq:leaky_relu} below.
+The \acs{LReLU} \index{activation function}activation function is given as
 
@@
 
-\noindent
 By introducing a parameter $\alpha > 0$, negative \index{net input signal}net input signals will still yield non-zero activations, resulting in non-zero gradients and avoiding gradient saturation.
@@
 
-\begin{figure}[htpb]
+\begin{figure}[htb]
       \centering
-      \includegraphics[width=0.8\textwidth]{lrelu.pdf}
+      \includegraphics[width=0.75\textwidth]{lrelu.pdf}
       \caption[The \acs{LReLU} \index{activation function}activation function]{An illustration of the \acs{LReLU} \index{activation function}activation function with various values for $\alpha$ and $\theta = 0$.}
@@
 The \index{sigmoid}sigmoid activation is the continuous differentiable approximation of the step function, which was used in the original perceptron model developed by~\citeauthor{ref:rosenblatt:1957}~\cite{ref:rosenblatt:1957}, and yields output in the range $(0, 1)$.
-The \index{sigmoid}sigmoid \index{activation function}activation function is defined in Equation~\eqref{eq:sigmoid} below.
+The \index{sigmoid}sigmoid \index{activation function}activation function is given as
 
@@
 
-\noindent
-In Equation~\eqref{eq:sigmoid} above, $\lambda$ is a control parameter, which controls the steepness of the sigmoid activation function and is usually set to $\lambda = 1$.
+where $\lambda$ is a control parameter that controls the steepness of the sigmoid activation function and is usually set to $\lambda = 1$.
 An illustration of the \index{sigmoid}sigmoid \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$ is given in Figure~\ref{fig:anns:activation_functions:sigmoid}.
 
-\begin{figure}[htpb]
+\begin{figure}[htb]
       \centering
-      \includegraphics[width=0.8\textwidth]{sigmoid.pdf}
+      \includegraphics[width=0.75\textwidth]{sigmoid.pdf}
       \caption[The \index{sigmoid}sigmoid \index{activation function}activation function]{An illustration of the \index{sigmoid}sigmoid \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$.}
@@
 The \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function has a similar shape to that of the \index{sigmoid}sigmoid \index{activation function}activation function, but yields output in the range $(-1, 1)$.
-The \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function is given in Equation~\eqref{eq:hyperbolic_tangent} below.
+The \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function is given as
 
@@
 
-\noindent
 An illustration of the \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$ is given in Figure~\ref{fig:anns:activation_functions:hyperbolic_tangent}.
 
-\begin{figure}[htpb]
+\begin{figure}[htb]
       \centering
-      \includegraphics[width=0.8\textwidth]{tanh.pdf}
+      \includegraphics[width=0.75\textwidth]{tanh.pdf}
       \caption[The \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function]{An illustration of the \index{hyperbolic tangent}hyperbolic tangent \index{activation function}activation function with various values for $\lambda$ and $\theta = 0$.}
@@
 For min-max scaling, data is converted back to the range $(x_{min}, x_{max})$.
-In the context of an \acs{AN}, binary logistic regression problems maps the output to the positive or negative class, usually separating the class decision boundary using a threshold value $\tau$.
+In the context of an \acs{AN}, binary logistic regression problems map the output to the positive or negative class, usually separating the class decision boundary using a threshold value $\tau$.
 In the context of multiple \acp{AN}' output, the output is a vector of numerical values.
@@
 
-The \index{softmax}softmax function, also known as the \index{softargmax}\textit{softargmax}~\cite[p.~184]{ref:goodfellow:2016} or \index{normalised exponential function}\textit{normalised exponential function}~\cite{ref:bishop:2006} is a generalisation of the logistic function that converts a $K$-dimensional output vector $\vec{y}$ into a $K$-dimensional output vector $\vec{y^{'}}$ where each element $y^{'}_k$ is in the range $(0,1)$ and all elements sum up to $1$ as is shown in Equation~\eqref{eq:sum_after_softmax} below.
+The \index{softmax}softmax function, also known as the \index{softargmax}\textit{softargmax}~\cite[p.~184]{ref:goodfellow:2016} or \index{normalised exponential function}\textit{normalised exponential function}~\cite{ref:bishop:2006} is a generalisation of the logistic function that converts a $K$-dimensional output vector $\boldsymbol{y}$ into a $K$-dimensional output vector $\boldsymbol{y^{'}}$ where each element $y^{'}_k$ is in the range $(0,1)$ and all elements sum up to $1$ as is shown in Equation~\eqref{eq:sum_after_softmax} below.
 
 \begin{equation}
-      \vec{y^{'}} \colon \mathbb{R}^{K} \to \left\{\vec{y^{'}} \in \mathbb{R}^{K} \vert y^{'}_k \in (0,1), \sum_{k=1}^{K} y_k = 1\right\}
+      \boldsymbol{y^{'}} \colon \mathbb{R}^{K} \to \left\{\boldsymbol{y^{'}} \in \mathbb{R}^{K} \vert y^{'}_k \in (0,1), \sum_{k=1}^{K} y_k = 1\right\}
       \label{eq:sum_after_softmax}
@@
 
-\noindent
-The softmax function is then given in Equation~\eqref{eq:softmax} below.
+The softmax function is then given as
 
@@
 All elements still sum to $1$, but the activation is only observed at index $k$ where the activation is $1$.
-The \index{argmax}argmax function is given in Equation~\eqref{eq:argmax} below.
+The \index{argmax}argmax function is given as
 
@@
 
-\noindent
-Figure~\ref{fig:anns:activation_functions:softmax_argmax} illustrates the comparison of transformations of the output vector $\vec{y}$, where the \index{sigmoid}sigmoid, the \index{softmax}softmax and the \index{argmax}argmax \index{activation function}activation functions are used.
+Figure~\ref{fig:anns:activation_functions:softmax_argmax} illustrates the comparison of transformations of the output vector $\boldsymbol{y}$, where the \index{sigmoid}sigmoid, the \index{softmax}softmax and the \index{argmax}argmax \index{activation function}activation functions are used.
 
-\begin{figure}[htpb]
+\begin{figure}[htb]
       \centering
-      \includegraphics[width=0.75\textwidth]{output_modifiers.pdf}
+      \includegraphics[width=0.65\textwidth]{output_modifiers.pdf}
       \caption[The results of \index{softmax}softmax and \index{argmax}argmax]{An illustration of \index{softmax}softmax and \index{argmax}argmax applied after the \index{sigmoid}sigmoid \index{activation function}activation function.}
@@
 
-\noindent
 The composition of \acp{AN} in an \acs{ANN} is expressed as the \textit{architecture} and \textit{topology} of the \acs{AN}. The exact composition to use depends on the problem being solved.
@@
 
-\noindent
-In Figure~\ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input vector $\vec{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer, $y_k$ refers to the $k$-th dimension in the output vector $\vec{y}$, $v_{i,j}$ refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the output node $y_k$.
+In Figure~\ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input vector $\boldsymbol{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer, $y_k$ refers to the $k$-th dimension in the output vector $\boldsymbol{y}$, $v_{i,j}$ refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the output node $y_k$.
 
-Assuming the use of \acp{SU} and bias weights, the output for the \acs{FFNN} at index $k$, denoted $y_k$, is calculated as is shown in Equation~\eqref{eq:ffnn} below.
+Assuming the use of \acp{SU} and bias weights, the output for the \acs{FFNN} at index $k$, denoted $y_k$, is calculated as
 
@@
 
-\noindent
 The remainder of this dissertation makes use of \acp{FFNN} and is sometimes referred to as \textit{the model}.
@@
 \index{heuristic}Heuristics search for possible solutions in the solution-space and make use of information from the search space to guide to process.
-Heuristics are discussed in detail in Chapter~\ref{chap:heuristics}.
 
@@
 \\
-\noindent
 There are two types of supervised learning algorithms based on when weights are updated~\cite{ref:engelbrecht:2007}. These include stochastic training and batch
@@
 \\
-\noindent
 Performance metrics are used during training on the training set and evaluation on the test set.
@@
 
-The \acs{SSE} is given in Equation~\eqref{eq:sse} below.
+The \acs{SSE} is given as
 
@@
 
-\noindent
-In Equation~\eqref{eq:sse} above, $\hat{y}_{k,p}$ is $k$-th dimension of the target output of pattern $p$, $y_{k,p}$ is $k$-th dimension of the predicted output vector $\vec{y}_{p}$ for pattern $p$, $P$ is the number of patterns in the mini-batch, and $K$ is the number of dimensions in the output vector $\vec{y}$.
+where $\hat{y}_{k,p}$ is $k$-th dimension of the target output of pattern $p$, $y_{k,p}$ is $k$-th dimension of the predicted output vector $\boldsymbol{y}_{p}$ for pattern $p$, $P$ is the number of patterns in the mini-batch, and $K$ is the number of dimensions in the output vector $\boldsymbol{y}$.
 
@@
 
-The \acs{MSE} is given in Equation~\eqref{eq:mse} below.
+The \acs{MSE} is given as
 
@@
 
-The \acs{RMSE} is given in Equation~\eqref{eq:rmse} below.
+The \acs{RMSE} is given as
 
@@
 
-The \acs{MAE} is given in Equation~\eqref{eq:mae} below.
+The \acs{MAE} is given as
 
@@
 
-\acs{BinXE} is used in classification problems, where there are only two classes in the target output data. \acs{BinXE} is given in Equation~\eqref{eq:bin_xe} below.
+\acs{BinXE} is used in classification problems, where there are only two classes in the target output data. \acs{BinXE} is given as
 
@@
 
-\noindent
-
 \subsubsection{Categorical Cross-Entropy}\label{sec:anns:training:error_functions:cat_xe}
 
-\acs{CatXE} is used in classification problems where the target output or \textit{label} is a one-hot encoded vector. \acs{CatXE} is given in Equation~\eqref{eq:cat_xe} below.
+\acs{CatXE} is used in classification problems where the target output or \textit{label} is a one-hot encoded vector. \acs{CatXE} is given as
 
@@
 \end{equation}
-
-\noindent
-In Equation~\eqref{eq:cat_xe} above, $\mathbbm{1}$ is the indicator function that the $k$-th index observation belongs to the $c$-th class.
+where $\mathbbm{1}$ is the indicator function that the $k$-th index observation belongs to the $c$-th class.
 $C$ is the total number of unique class labels.
@@
 Background information on the training of \acp{FFNN} was presented.
-A variant of training, called \index{supervised learning}supervised learning was presented and led to the discussion on datasets, performance measures and training outcomes.
+A variant of training, called \index{supervised learning}supervised learning was presented and led to discussions on datasets, performance measures and training outcomes.
 The chapter concluded with a number or error functions that can be used to calculate the loss in the context of supervised learning.

### 2022-11-24 dissertation/chapters/03-heuristics.tex
✨ (chapter4): Review Done
✨ (final-review): Done up to chapter 3

@@
 \begin{quotation}
-      \noindent ``It is not the strongest of the species that survives. It is also not the most intelligent that survives. It is the one that is the most adaptable to change.''
+      ``It is not the strongest of the species that survives. It is also not the most intelligent that survives. It is the one that is the most adaptable to change.''
 \end{quotation}
 \begin{flushright}
-      Charles Darwin
+      - Charles Darwin
 \end{flushright}
 
-\noindent
 Many different techniques have been used to train \acp{FFNN}~\cite{ref:kingma:2014}.
@@
 
-      \item \textbf{Section~\ref{sec:heuristics:gd}} presents the reader with seven low-level, gradient-based \index{heuristic}heuristics, including \acf{SGD}, \acf{Momentum}, \acf{NAG}, \acf{Adagrad}, \acf{RMSProp}, \acf{Adadelta} and \acf{Adam}.
-
-      \item \textbf{Section~\ref{sec:heuristics:mh}} presents the reader with three different population-baed \acp{MH}, including \acf{PSO}, \acf{DE} and \acfp{GA}.
-
-      \item \textbf{Section~\ref{sec:heuristics:summary}} provides the reader with a brief summary of the chapter.
+      \item \textbf{Section~\ref{sec:heuristics:gd}} presents seven low-level, gradient-based \index{heuristic}heuristics, including \acf{SGD}, \acf{Momentum}, \acf{NAG}, \acf{Adagrad}, \acf{RMSProp}, \acf{Adadelta} and \acf{Adam}.
+
+      \item \textbf{Section~\ref{sec:heuristics:mh}} presents three different population-based \acp{MH}, including \acf{PSO}, \acf{DE} and \acfp{GA}.
+
+      \item \textbf{Section~\ref{sec:heuristics:summary}} provides a brief summary of the chapter.
 \end{itemize}
@@
 
-\noindent
 Optimisation problems come in a wide variety, and can be defined in terms of the number of variables used (uni- vs.
@@
 The mechanism by which the optimal weights for a \acs{FFNN} is sough out, is executed by an \index{optimisation algorithm}optimisation algorithm known as a \index{heuristic}heuristic.
-Discussions on the details of heuristics are presented in the following sections.
 
@@
 
-The term \textit{heuristic} comes from the Latin word \textit{heuristicus} which means ``to find out or discover''.~\citeauthor{ref:romanycia:1985}~\cite{ref:romanycia:1985} provides a complete study on the history and origins of the term \index{heuristic}\textit{heuristic}.
+The term \textit{heuristic} comes from the Latin word \textit{heuristicus} which means ``to find out or discover''.~\citeauthor{ref:romanycia:1985}~\cite{ref:romanycia:1985} provide a complete study on the history and origins of the term \index{heuristic}\textit{heuristic}.
 From their research, a proposal is made to define \index{heuristic}heuristics in the context of \acf{AI}, as any device, be it a program, rule, piece of knowledge, which is added to a problem-solving system, in expectation that, on average, the performance will improve.
@@
 Different \index{heuristic}heuristics make use of different information during the search process~\cite{ref:kheiri:2017}.
-During the training of \acp{FFNN}, \index{heuristic}heuristics such as gradient-based \index{heuristic}heuristics make use of the derivatives obtained by evaluating the \acs{FFNN}.
+During training of \acp{FFNN}, \index{heuristic}heuristics such as gradient-based \index{heuristic}heuristics make use of the derivatives obtained by evaluating the \acs{FFNN}.
 It can thus be said that gradient-based \index{heuristic}heuristics make use of information directly from the \textit{search space}.
@@
 This disseration takes a particular interest in gradient-based \index{heuristic}heuristics and \acp{MH}.
-Each of these are presented in detail in the following sections.
 
@@
 
-Chapter~\ref{chap:anns} introduced the reader to \index {supervised learning}supervised learning and presented a number of loss functions.
+Chapter~\ref{chap:anns} introduced \index {supervised learning}supervised learning and presented a number of loss functions.
 In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{FFNN} and the desired output.
@@
       \centering
-      \includegraphics[width=0.85\textwidth]{images/gradient_descent.pdf}
+      \includegraphics[width=0.75\textwidth]{images/gradient_descent.pdf}
       \caption{An illustration of \acf{GD} over various timesteps showing the minimisation of the error with regards to weight value.}
@@
 
-\noindent
 In the context of training \textit{shallow} \acp{FFNN} using \index{supervised learning}supervised learning, the error signal is propagated backwards in the network from the output layer, through the hidden layer to the input layer, updating the weights at the output and hidden layers.
@@
 
-\noindent
-The update step for \acs{GD} by means of \acs{BP} can be formulated as is shown in Equations~\eqref{eq:heuristics:gd:update_step_part_1}-\eqref{eq:heuristics:gd:update_step_part_3} below.
+The update step for \acs{GD} by means of \acs{BP} can be formulated as is shown in Equations~\eqref{eq:heuristics:gd:update_step_part_1}-\eqref{eq:heuristics:gd:update_step_part_4}.
+The general weight update step is given as
 
@@
 
-\noindent
-In Equation~\eqref{eq:heuristics:gd:update_step_part_1} above, $w_{i}$ is the weight value at index $i$, $t$ is the timestep, $\Delta w_{i}(t)$ is the weight update vector at index $i$ and timestep $t$.
-$\Delta w_{i}(t)$ is specified by Equation~\eqref{eq:heuristics:gd:update_step_part_2} below.
+where $w_{i}$ is the weight value at index $i$, $t$ is the timestep, $\Delta w_{i}(t)$ is the weight update vector at index $i$ and timestep $t$. The delta weight term $\Delta w_{i}(t)$, is given as
 
@@
 
-\noindent
-In Equation~\eqref{eq:heuristics:gd:update_step_part_2} above, $\eta$ is the learning rate and $\frac{\partial \epsilon}{\partial w_{i}}$ is the \textit{gradient} of the error, as a result of a loss function $\mathcal{E}$, relative to the weight at index $i$.
+where $\eta$ is the learning rate and $\frac{\partial \epsilon}{\partial w_{i}}$ is the \textit{gradient} of the error, as a result of a loss function $\mathcal{E}$, relative to the weight at index $i$.
 The learning rate controls the step-size that is taken in the direction of the negative gradient at each timestep.
-Assuming the use of \acs{SSE} as the loss function, the partial derivative of $\epsilon$, relative to the weight $w$, at index $i$, is given by Equation~\eqref{eq:heuristics:gd:update_step_part_3} below.
+Assuming the use of \acs{SSE} as the loss function, the partial derivative of $\epsilon$, relative to the weight $w$, at index $i$, is given as
 
@@
 
-\noindent
-In Equation~\eqref{eq:heuristics:gd:update_step_part_3} above, $t_{p}$ refers to the target value for pattern $p$, $o_{p}$ refers to the output value for pattern $p$, $f$ refers to the \index{activation function}activation function, $net_{p}$ refers to the \index{net input signal}net input signal for pattern $p$, and $z_{i,p}$ refers to the input value at index $i$ for pattern $p$.
-
-Finally, assuming the use of \index{sigmoid}sigmoid activation function, the partial derivative of the activation function, relative to the net input signal is given in Equation~\eqref{eq:heuristics:gd:update_step_part_4} below.
+where $t_{p}$ refers to the target value for pattern $p$, $o_{p}$ refers to the output value for pattern $p$, $f$ refers to the \index{activation function}activation function, $net_{p}$ refers to the \index{net input signal}net input signal for pattern $p$, and $z_{i,p}$ refers to the input value at index $i$ for pattern $p$.
+
+Finally, assuming the use of the \index{sigmoid}sigmoid activation function, the partial derivative of the activation function, relative to the net input signal is given as
 
@@
 
-\noindent
 Again, assuming the use of \acs{SSE} as the loss function, the pseudo-code implementation for the generic \acs{GD} algorithm is taken from~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:gd:gd} below.
@@
 
-\noindent
-A more detailed breakdown of the steps for \acs{BP}, as presented by ~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007}, is given in Appendix~\ref{app:backpropagation}.
-
 A simplified notation is proposed from which the gradient-based heuristics can be compared.
-Consider a simplification of the update-step for \acs{SGD} as presented in Equations~\eqref{eq:heuristics:gd:update_step_part_1} and~\eqref{eq:heuristics:gd:update_step_part_2} where $\frac{\partial \epsilon}{\partial w_{i}}$ is simply represented as the gradient term $g$, resulting in a simplified weight update step as is shown in Equation~\eqref{eq:heuristics:gd:sgd} below.
+Consider a simplification of the update-step for \acs{SGD} as presented in Equations~\eqref{eq:heuristics:gd:update_step_part_1} and~\eqref{eq:heuristics:gd:update_step_part_2} where $\frac{\partial \epsilon}{\partial w_{i}}$ is simply represented as the gradient term $g$, resulting in a simplified weight update step and is given as
 
@@
       \begin{split}
-            w = w - \eta g
-      \end{split}
-\end{equation}
-
-\noindent
-In Equation~\eqref{eq:heuristics:gd:sgd} above, $w$ refers to the weight vector, $\eta$ refers to the learning rate as before and $g$ refers to the gradient of the error function relative to weight vector.
-Note that, vector notation and some subscripts related to layers, indices, timesteps and training patterns are omitted for convenience.
+            \boldsymbol{w} = \boldsymbol{w} - \eta \boldsymbol{g}
+      \end{split}
+\end{equation}
+
+where $\boldsymbol{w}$ refers to the weight vector, $\eta$ refers to the learning rate as before and $\boldsymbol{g}$ refers to the gradient of the error function relative to weight vector.
+Note that some subscripts related to layers, indices, timesteps and training patterns are omitted for convenience.
 
@@
       \centering
-      \includegraphics[width=0.9\textwidth]{images/sgd.pdf}
+      \includegraphics[width=0.8\textwidth]{images/sgd.pdf}
       \caption{An illustration of \acf{SGD} fluctuations during training as taken from~\cite{ref:sgd:2006}.}
@@
 
-\noindent
-With batch training, all the training patterns are presented at once and the \acs{FFNN} converges to the global minimum of the loss function w.r.t $w$ (assuming the loss function is convex).
+With batch training, all the training patterns are presented at once and the \acs{FFNN} converges to the global minimum of the loss function w.r.t $\boldsymbol{w}$ (assuming the loss function is convex).
 However, this is computationally expensive and impractical to implement in many situations.
@@
 
-A compromise to overshooting minima that \acs{SGD} suffers from, is to make use of mini-batches of training patterns where a small number of training patterns are presented to the \acs{FFNN} at once.
+A compromise is to make use of mini-batches of training patterns, where a small number of training patterns are presented to the \acs{FFNN} at once.
 This is referred to as \textit{mini-batch} training.
@@
 
-\noindent
 In the context of this dissertation, the implementation of \acs{SGD} refers to the mini-batch training implementation of \acs{GD}.
@@
 
-\noindent
-Alternative variants have been proposed that lead to better control over the convergence characteristics caused by \acs{GD}.
-The first of these \acs{GD} variants include \acs{Momentum} and is presented in the following section.
+Alternative variants have been proposed that lead to better control over the convergence characteristics caused by \acs{GD}. The first of these \acs{GD} variants include \acs{Momentum}.
 
@@
 
-\Acs{Momentum} ~\cite{ref:qian:1999} is a variant of the \acs{SGD} that helps accelerate \acs{SGD} in the relevant direction, dampening oscillations.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$, of the weight update vector of the previous timestep to the current weight update vector.
+\Acs{Momentum} ~\cite{ref:qian:1999} is a variant of \acs{SGD} that helps accelerate \acs{SGD} in the relevant direction, dampening oscillations.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$, of the weight update vector of the previous timestep to the current weight update vector.
 An illustration of \acs{SGD} with and without momentum is given in Figure~\ref{fig:heuristics:gd:sgd_with_and_without_momentum}.
@@
 
-\noindent
-The accumulation of momentum is presented in Equation~\eqref{eq:heuristics:gd:momentum_part_1} below, while the update step is then amended in Equation~\eqref{eq:heuristics:gd:momentum_part_2} below.
+The accumulation of momentum is presented in Equation~\eqref{eq:heuristics:gd:momentum_part_1}, while the update step is then amended in Equation~\eqref{eq:heuristics:gd:momentum_part_2}.
 
@@
       \begin{split}
-            v = \alpha v - \eta g
+            \boldsymbol{v} = \alpha \boldsymbol{v} - \eta \boldsymbol{g}
       \end{split}
@@
       \begin{split}
-            w = w + v
-      \end{split}
-\end{equation}
-
-\noindent
+            \boldsymbol{w} = \boldsymbol{w} + \boldsymbol{v}
+      \end{split}
+\end{equation}
+
 By redefining the \acs{SGD} update steps as shown above in Equations~\eqref{eq:heuristics:gd:momentum_part_1} and~\eqref{eq:heuristics:gd:momentum_part_2}, the \acs{Momentum} heuristic allows for the increase of momentum for dimensions whose gradients point in the same direction, while simultaneously reducing momentum for dimensions whose gradients change direction, leading to faster convergence and less oscillation.
@@
 
-\noindent
 The difference in the update step for \acs{Momentum} and the update step for \acs{NAG} as developed by~\citeauthor{ref:sutskever:2013-2}~\cite{ref:sutskever:2013-2} is described by~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} as follows.
-\acs{Momentum} first calculates the current gradient, represented by the small blue vector in Figure~\ref{fig:heuristics:gd:nag} and then takes a large step in the direction of the updated accumulated gradient, presented by the big blue vector.
-In contrast, \acs{NAG} first takes a big step in the direction of the previous accumulated gradient presented by the brown vector.
-At this point the gradient is measured and \acs{NAG} makes a correction represented by the red vector.
+\acs{Momentum} first calculates the current gradient, represented by the small \textcolor{blue}{blue} vector in Figure~\ref{fig:heuristics:gd:nag} and then takes a large step in the direction of the updated accumulated gradient, presented by the big \textcolor{blue}{blue} vector.
+In contrast, \acs{NAG} first takes a big step in the direction of the previous accumulated gradient presented by the \textcolor{brown}{brown} vector.
+At this point the gradient is measured and \acs{NAG} makes a correction represented by the \textcolor{red}{red} vector.
 The complete update step is represented by the green vector.
 By anticipating approximate future positions of the weights, the weight update step as defined by \acs{NAG} controls the optimisation process from going too fast and results in increased responsiveness~\cite{ref:bengio:2013}.
-Along with the same velocity update step for \acs{Momentum}, as presented in Equation~\eqref{eq:heuristics:gd:momentum_part_1}, the \acs{NAG} weight update step is given in Equation~\eqref{eq:heuristics:gd:nag_part_2} below.
+Along with the same velocity update step for \acs{Momentum}, as presented in Equation~\eqref{eq:heuristics:gd:momentum_part_1}, the \acs{NAG} weight update step is given as
 
@@
       \begin{split}
-            w = w + \alpha v - \eta g
+            \boldsymbol{w} = \boldsymbol{w} + \alpha \boldsymbol{v} - \eta \boldsymbol{g}
       \end{split}
@@
 
-\Acf{Adagrad} is an adaptation of \acs{SGD} which implements a learning rate for every element in the weight vector and is developed by Duchi et al.~\cite{ref:duchi:2011}.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that \acs{Adagrad} adapts the learning rate to the elements of the weight vector, by  performing small updates (i.e.
+\Acf{Adagrad} is an adaptation of \acs{SGD} that implements a learning rate for every element in the weight vector and is developed by Duchi et al.~\cite{ref:duchi:2011}.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that \acs{Adagrad} adapts the learning rate to the elements of the weight vector, by  performing small updates (i.e.
 low learning rates) for weights associated with frequently occurring features and larger updates (i.e.
@@
 \Acs{Adagrad} uses a different learning rate for every weight element $w_{i}$, at every timestep $t$.
-The weight update step for \acs{Adagrad} is presented in Equation~\eqref{eq:heuristics:gd:adagrad_part_1} below.
+The weight update step for \acs{Adagrad} is given as
 
@@
 
-\noindent
-In Equation~\eqref{eq:heuristics:gd:adagrad_part_1} above, $w_{i}$ is the $i$-th element of the weight vector, $G_{t,ii} \in \mathbb{R}^{d \times d}$ is a diagonal matrix where each diagonal element $i,i$, is the sum of the squared gradients w.r.t.
+where $w_{i}$ is the $i$-th element of the weight vector, $G_{t,ii} \in \mathbb{R}^{d \times d}$ is a diagonal matrix where each diagonal element $i,i$, is the sum of the squared gradients w.r.t.
 $w_{i}$, up to timestep $t$ and $\epsilon$ is a smoothing term that avoids division by zero and is set to an insignificant value such as $1 \times 10^{-8}$.
-Since $G_{t}$ contains the sum of the squares of the gradients along its diagonal, the weight update step can be vectorised and updated using the matrix-vector product, represented by $\odot$, between $G_{t}$ and $g_{t,i}$.
-The simplified update step as implemented by \acs{Adagrad} is given in Equation~\eqref{eq:heuristics:gd:adagrad_part_2} below.
+Since $\boldsymbol{G_{t}}$ contains the sum of the squares of the gradients along its diagonal, the weight update step can be vectorised and updated using the matrix-vector product, represented by $\odot$, between $G_{t,i}$ and $g_{t,i}$.
+The simplified update step as implemented by \acs{Adagrad} is given as
 
@@
       \begin{split}
-            w_{t+1} = w_{t} - \frac{\eta}{\sqrt{G_{t} + \epsilon}} \odot g_{t,i}
-      \end{split}
-\end{equation}
-
-\noindent
+            w_{t+1} = w_{t} - \frac{\eta}{\sqrt{G_{t,i} + \epsilon}} \odot g_{t,i}
+      \end{split}
+\end{equation}
+
 \Ac{Adagrad}'s main benefit is that it does not require manual tuning of the learning rate $\eta$.
-However, a problem with \acs{Adagrad} is in the accumulation of squared gradients in the denominator, represented by $G_{t}$.
-Since every term that is added is positive, $G_{t}$ keeps growing, leading to a situation where the learning rate shrinks to the point that the heuristic is no longer able to learn.
+However, a problem with \acs{Adagrad} is in the accumulation of squared gradients in the denominator, represented by $\boldsymbol{G_{t}}$.
+Since every term that is added is positive, $\boldsymbol{G_{t}}$ keeps growing, leading to a situation where the learning rate shrinks to the point that the heuristic is no longer able to learn.
 
@@
 Instead, the accumulation of gradients over $W$ steps is defined recursively as a decaying average of all past squared gradients.
-The moving average of squared gradients at timestep $t$, denoted by $E[g^{2}]_{t}$  depends on a fraction $\alpha$ of the previous average of squared gradients and the current gradient, similar to the update step for \acs{Momentum}.
+The moving average of squared gradients at timestep $t$, denoted by $E[\boldsymbol{g}^{2}]_{t}$  depends on a fraction $\alpha$ of the previous average of squared gradients and the current gradient, similar to the update step for \acs{Momentum}.
 Also similar to \acs{Momentum}, $\alpha$ is set to 0.9.
-The update step for $E[g^{2}]_{t}$ is presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_1} below.
+The update step for $E[\boldsymbol{g}^{2}]_{t}$ is given as
 
@@
       \begin{split}
-            E[g^{2}]_{t} = \alpha E[g^{2}]_{t - 1} + (1 - \alpha)g_{t}^{2}
-      \end{split}
-\end{equation}
-
-\noindent
-To illustrate the difference between \acs{Adagrad} and \acs{Adadelta}, the \acs{SGD} weight update step for \acs{Adagrad}, as presented in~\eqref{eq:heuristics:gd:adagrad_part_2} is rewritten such that the diagonal matrix $G_{t}$, is replaced with the moving average of squared gradients as presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_2} below.
+            E[\boldsymbol{g}^{2}]_{t} = \alpha E[\boldsymbol{g}^{2}]_{t - 1} + (1 - \alpha)\boldsymbol{g}_{t}^{2}
+      \end{split}
+\end{equation}
+
+To illustrate the difference between \acs{Adagrad} and \acs{Adadelta}, the \acs{SGD} weight update step for \acs{Adagrad}, as presented in~\eqref{eq:heuristics:gd:adagrad_part_2} is rewritten such that the diagonal matrix $\boldsymbol{G_{t}}$, is replaced with the moving average of squared gradients and is given as
 
@@
       \begin{split}
-            w_{t+1} = w_{t} - \frac{\eta}{\sqrt{E[g^{2}]_{t} + \epsilon}} g_{t}
-      \end{split}
-\end{equation}
-
-\noindent
-Since the denominator is the \acf{RMS} error criterion of the gradient, the criteria short-hand notation is used as is depicted in Equation~\eqref{eq:heuristics:gd:adadelta_part_3} below.
+            \boldsymbol{w}_{t+1} = \boldsymbol{w}_{t} - \frac{\eta}{\sqrt{E[\boldsymbol{g}^{2}]_{t} + \epsilon}} \boldsymbol{g}_{t}
+      \end{split}
+\end{equation}
+
+Since the denominator is the \acf{RMS} error criterion of the gradient, the criteria short-hand notation is used and is given as
 
@@
       \begin{split}
-            w_{t+1} = w_{t} - \frac{\eta}{RMS[g]_{t}} g_{t}
-      \end{split}
-\end{equation}
-
-\noindent
+            \boldsymbol{w}_{t+1} = \boldsymbol{w}_{t} - \frac{\eta}{RMS[\boldsymbol{g}]_{t}} \boldsymbol{g}_{t}
+      \end{split}
+\end{equation}
+
 ~\citeauthor{ref:zeiler:2012}~\cite{ref:zeiler:2012} noted that the units of the update step as presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_3} do not match.
 The weight update vector should have the same hypothetical units as the weight vector.
-To fix the aforemention problem, another exponentially decaying average is defined in terms of squared weight updates as is presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_4} below.
+To fix the aforemention problem, another exponentially decaying average is defined in terms of squared weight updates and is given as
 
@@
       \begin{split}
-            E[\Delta w^{2}]_{t} = \alpha E[\Delta w^{2}]_{t - 1} + (1 - \alpha)\Delta w_{t}^{2}
-      \end{split}
-\end{equation}
-
-\noindent
-The \acf{RMS} error of weight updates is given in Equation~\eqref{eq:heuristics:gd:adadelta_part_5} below.
+            E[\Delta \boldsymbol{w}^{2}]_{t} = \alpha E[\Delta \boldsymbol{w}^{2}]_{t - 1} + (1 - \alpha)\Delta \boldsymbol{w}_{t}^{2}
+      \end{split}
+\end{equation}
+
+The \acf{RMS} error of weight updates is given as
 
@@
       \begin{split}
-            RMS[\Delta w]_{t} = \sqrt{E[\Delta w^{2}]_{t} + \epsilon}
-      \end{split}
-\end{equation}
-
-\noindent
-Note that $RMS[\Delta w]_{t}$ is unknown at timestep $t$.
-$RMS[\Delta w]_{t}$ is approximated with the \acf{RMS} of weight updates until the previous timestep.
+            RMS[\Delta \boldsymbol{w}]_{t} = \sqrt{E[\Delta \boldsymbol{w}^{2}]_{t} + \epsilon}
+      \end{split}
+\end{equation}
+
+Note that $RMS[\Delta \boldsymbol{w}]_{t}$ is unknown at timestep $t$.
+$RMS[\Delta \boldsymbol{w}]_{t}$ is approximated with the \acf{RMS} of weight updates until the previous timestep.
 The learning rate in Equation~\eqref{eq:heuristics:gd:adadelta_part_3} is then replaced.
-The weight update step for \acs{Adadelta} is then concluded in Equation~\eqref{eq:heuristics:gd:adadelta_part_6} below.
+The weight update step for \acs{Adadelta} is then concluded and is given as
 
@@
       \begin{split}
-            w_{t+1} = w_{t} - \frac{RMS[\Delta w]_{t-1}}{RMS[g]_{t}} g_{t}
-      \end{split}
-\end{equation}
-
-\noindent
+            \boldsymbol{w}_{t+1} = \boldsymbol{w}_{t} - \frac{RMS[\Delta \boldsymbol{w}]_{t-1}}{RMS[\boldsymbol{g}]_{t}} \boldsymbol{g}_{t}
+      \end{split}
+\end{equation}
+
 The main advantage of \acs{Adadelta} is in removing the learning rate, which eliminates the need for hyper-parameter tuning of the learning rate.
@@
       \begin{split}
-            m_{t+1} = \beta_{1}m_{t} + (1 - \beta_{1})g_{t}
+            \boldsymbol{m}_{t+1} = \beta_{1}\boldsymbol{m}_{t} + (1 - \beta_{1})\boldsymbol{g}_{t}
       \end{split}
@@
       \begin{split}
-            v_{t+1} = \beta_{2}v_{t} + (1 - \beta_{2})g^{2}_{t}
-      \end{split}
-\end{equation}
-
-\noindent
+            \boldsymbol{v}_{t+1} = \beta_{2}\boldsymbol{v}_{t} + (1 - \beta_{2})\boldsymbol{g}^{2}_{t}
+      \end{split}
+\end{equation}
+
 In Equations~\eqref{eq:heuristics:gd:adam_part_1} and~\eqref{eq:heuristics:gd:adam_part_2} above, $\beta_{1}$ and $\beta_{2}$ are decay rates, similar to $\alpha$ for \acs{Momentum}.
@@
 
-\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that $m_{t}$ and $v_{t}$ presented above are estimates of the first moment (the mean) and the second moment (the uncentered variance) of the gradients respectively.
-~\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} mentions that because $m_{t}$ and $v_{t}$ are initialised to be vectors of 0's, they are biased towards 0.
+\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that $\boldsymbol{m}_{t}$ and $\boldsymbol{v}_{t}$ presented above are estimates of the first moment (the mean) and the second moment (the uncentered variance) of the gradients respectively.
+~\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} mentions that because $\boldsymbol{m}_{t}$ and $\boldsymbol{v}_{t}$ are initialised to be vectors of 0's, they are biased towards 0.
 The aforementioned bias is especially prominent during the initial timesteps and/or when the decay rates $\beta_{1}$ and $\beta_{2}$ are small ($\beta_{1}$ and $\beta_{2}$ are close to 1).
-The bias-corrected first and second moment estimates are presented in Equations~\eqref{eq:heuristics:gd:adam_bc_first_moment} and~\eqref{eq:heuristics:gd:adam_bc_second_moment} below.
+The bias-corrected first and second moment estimates are presented in Equations~\eqref{eq:heuristics:gd:adam_bc_first_moment} and~\eqref{eq:heuristics:gd:adam_bc_second_moment} respectively.
 
@@
       \begin{split}
-            \hat{m}_{t} = \frac{m_{t}}{1 - \beta^{t}_{1}}
+            \hat{\boldsymbol{m}}_{t} = \frac{\boldsymbol{m}_{t}}{1 - \beta^{t}_{1}}
       \end{split}
@@
       \begin{split}
-            \hat{v}_{t} = \frac{v_{t}}{1 - \beta^{t}_{2}}
-      \end{split}
-\end{equation}
-
-\noindent
-The \acs{Adam} weight update rule is then presented in Equation~\eqref{eq:heuristics:gd:adam} below.
+            \hat{\boldsymbol{v}}_{t} = \frac{\boldsymbol{v}_{t}}{1 - \beta^{t}_{2}}
+      \end{split}
+\end{equation}
+
+The \acs{Adam} weight update rule is then given as
 
@@
       \begin{split}
-            w_{t+1} = w_{t} - \frac{\eta}{\sqrt{\hat{v}_{t}} + \epsilon}\hat{m}_{t}
-      \end{split}
-\end{equation}
-
-\noindent
-This section provided the reader with a collection of gradient-based \index{heuristic}heuristics. The next section presents the reader with \acp{MH}.
+            \boldsymbol{w}_{t+1} = \boldsymbol{w}_{t} - \frac{\eta}{\sqrt{\hat{\boldsymbol{v}}_{t}} + \epsilon}\hat{\boldsymbol{m}}_{t}
+      \end{split}
+\end{equation}
 
@@
 
-Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus~\cite{ref:bengio:2000, ref:feurer:2019}.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} mentions that since the 1980's, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
+Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus~\cite{ref:bengio:2000, ref:feurer:2019}.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} mention that since the 1980's, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
 These methods are referred to as \index{meta-heuristic}\textit{meta-heuristics}.
 
-This section aims to introduce the reader to the concept of \acp{MH}, with focus on population-based meta-heuristics.
+This section aims to introduce the concept of \acp{MH}, with focus on population-based meta-heuristics.
 Three well known \acp{MH}, that have been shown to train \acs{FFNN}, are presented.
@@
 The prefix, \textit{meta}, means ``beyond, in an upper level''.
-\Acp{MH} were often called \textit{modern heuristics}~\cite{ref:reeves:1993}.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} mentions that there is a debate as to what the formal defintion of \acp{MH} is and suggests the definition of \acp{MH} to be ``high level strategies for exploring search spaces by using different methods''.
+\Acp{MH} were often called \textit{modern heuristics}~\cite{ref:reeves:1993}.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} mention that there is a debate as to what the formal defintion of \acp{MH} is and suggests the definition of \acp{MH} to be ``high level strategies for exploring search spaces by using different methods''.
 
@@
 The application of \acp{PSO} in the context of training \acs{FFNN} have been widely studied~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}.
-This section aims to provide the reader with the details of \acs{PSO} implementation.
+This section aims to provide the details of \acs{PSO} implementation.
 
@@
 
-\noindent
 \citeauthor{ref:shi:1998}~\cite{ref:shi:1998} proposed a modification of the original \acs{PSO} as was presented by~\citeauthor{ref:kennedy:1995}~\cite{ref:kennedy:1995}.
@@
       \item \textbf{Position}: Refers to the candidate solution that is represented by the particle and defines the particle position within the optimisation problem's hyper-dimensional solution space.
-Let the current position of particle $i$ at timestep $t$ be denoted by $x_{i}(t)$ and let $J$ be the search space dimensionality.
-
-      \item \textbf{Velocity}: Represents a step size for the particle in the search space. The velocity vector of particle $i$ at timestep $t$ is denoted $v_{i}(t)$.
+Let the current position vector, for particle $i$, at timestep $t$ be denoted by $\boldsymbol{x}_{i}(t)$.
+Let $I$ denoted the population size and $J$ denote the search space dimensionality.
+
+      \item \textbf{Velocity}: Represents a step size for the particle in the search space. The velocity at vector, for particle $i$, at timestep $t$ is denoted $\boldsymbol{v}_{i}(t)$.
 
       \item \textbf{Solution Quality}: Refers to the evaluation of the particle's position with respect to the objective function.
-Let $f(x_{i}(t))$ denote the quality of the solution represented by the particle's position.
+Let $f(\boldsymbol{x}_{i}(t))$ denote the quality of the solution represented by the particle's position.
 
       \item \textbf{Personal Best Position}: Refers to a cognitive memory construct, where each particle keeps track of their personal best position found during optimisation thus far.
-The personal best position is denoted $y_{i}(t)$.
+The personal best position is denoted $\boldsymbol{y}_{i}(t)$.
 
@@
 In the case of \text{gbest} \acs{PSO}, the global best position is the best position of the entire swarm.
-The personal best position is denoted $\hat{y}_{i}(t)$.
-\end{itemize}
-
-\noindent
-During initialisation, particles are randomly placed within the search space by sampling from a uniform distribution such that $x_{i} \sim U(x_{min}, x_{max})$ and the velocity is set to 0.
-At timestep 0, the particle's initial position is set to be the particle's personal best solution such that $y_{i}(0) = x_{i}(0)$.
-The particle's update step is then broken into two parts, including a velocity update step presented in Equation~\eqref{eq:heuristics:pso:velocity} followed by a position update step as presented in Equation~\eqref{eq:heuristics:pso:position} below.
+The global best position is denoted $\boldsymbol{\hat{y}}_{i}(t)$.
+\end{itemize}
+
+During initialisation, particles are randomly placed within the search space by sampling from a uniform distribution such that $\boldsymbol{x}_{i} \sim U(x_{min}, x_{max})$ and the velocity is set to 0.
+At timestep 0, the particle's initial position is set to be the particle's personal best solution such that $\boldsymbol{y}_{i}(0) = \boldsymbol{x}_{i}(0)$.
+The particle's update step is then broken into two parts, including a velocity update step presented in Equation~\eqref{eq:heuristics:pso:velocity} followed by a position update step as presented in Equation~\eqref{eq:heuristics:pso:position}.
 
@@
 
-\noindent
 In Equations~\eqref{eq:heuristics:pso:velocity} and~\eqref{eq:heuristics:pso:position} above, $i$ refers to the $i$-th particle in the swarm and $j$ refers to the $j$-th dimension of  the particle's position.
@@
       \item \textbf{Previous Velocity}: Denoted by the term $v_{ij}(t)$.
-This term represents the particle's momentum and is used to formulate an update step for the particle in the search space.~\citeauthor{ref:vanwyk:2014}~\cite{ref:vanwyk:2014} mentions that it forces the particle to maintain a consistent direction, preventing drastic changes in terms of update steps.
+This term represents the particle's momentum at index j and is used to formulate an update step for the particle in the search space.~\citeauthor{ref:vanwyk:2014}~\cite{ref:vanwyk:2014} mentions that it forces the particle to maintain a consistent direction, preventing drastic changes in terms of update steps.
 This term is then scaled by the \textit{inertia} weight control parameter, denoted $w$.
@@
       \item \textbf{Cognitive Component}: Denoted by the term $c_{1}r_{1_{j}}(t)[y_{ij} - x_{ij}(t)]$.
-This component represents the particle's personal  experience.
+This component represents the particle's personal experience at index j.
 It introduces an attractor to the particle's personal best position so far.
-The cognitive component is stochastically scaled with random numbers $r_{1} \sim U(0,1)^J$ and the cognitive acceleration coefficient $c_{1}$ is used to control the influence of the cognitive attractor.
+The cognitive component is stochastically scaled with random numbers $\boldsymbol{r}_{1} \sim U(0,1)^J$ and the cognitive acceleration coefficient $c_{1}$ is used to control the influence of the cognitive attractor.
 
       \item \textbf{Social Component}: Denoted by the term $c_{2}r_{2_{j}}(t)[\hat{y}_{ij} - x_{ij}(t)]$.
-This component represents the particle's social  experience.
+This component represents the particle's social experience at index j.
 It introduces an attractor to the swarm's best position so far.
-The social component is also stochastically scaled with random numbers $r_{2} \sim U(0,1)^J$, while also introducing the social acceleration coefficient $c_{2}$ that is used to control the influence of the social attractor.
-\end{itemize}
-
-\noindent
+The social component is also stochastically scaled with random numbers $\boldsymbol{r}_{2} \sim U(0,1)^J$, while also introducing the social acceleration coefficient $c_{2}$ that is used to control the influence of the social attractor.
+\end{itemize}
+
 ~\citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that when \acp{PSO} where first developed, it was possible for particle velocities to become inappropriately large during optimisation, leading to situations where particles fly out of the feasible search space.
@@
 
-\noindent
-$V_{max}$ is another hyper-parameter that must be defined a priori.
-Appropriate values for $V_{max}$ may prevent swarm explosion, but also has an effect on the exploration and exploitation of the heuristic.
-If $V_{max}$ is small, particle update steps are small, resulting in exploitation~\cite{ref:eberhart:1996}.
-If $V_{max}$ is big, it allows for larger update steps, promoting more exploration.
+$\boldsymbol{V}_{max}$ is another hyper-parameter that must be defined a priori.
+Appropriate values for $\boldsymbol{V}_{max}$ may prevent swarm explosion, but also has an effect on the exploration and exploitation of the heuristic.
+If $\boldsymbol{V}_{max}$ is small, particle update steps are small, resulting in exploitation~\cite{ref:eberhart:1996}.
+If $\boldsymbol{V}_{max}$ is big, it allows for larger update steps, promoting more exploration.
 
@@
 
-An example of the pseudo code implementation of the \textit{gbest} \acs{PSO} is taken from~\cite{ref:engelbrecht:2007} and is given in Algorithm~\ref{algo:heuristics:pso:gbest} below.
+An example of the pseudo code implementation of the \textit{gbest} \acs{PSO} is taken from~\cite{ref:engelbrecht:2007} and is given in Algorithm~\ref{algo:heuristics:pso:gbest}.
 
@@
 
-This section aims to introduce the reader to the next population-based \acs{MH} called \acf{DE}.
+This section aims to introduce the next population-based \acs{MH}, called \acf{DE}.
 Similar to \acs{PSO}, \acs{DE} is a stochastic population-based search strategy developed by Storm and Price~\cite{ref:price:2006} in 1995.
@@
 The \index{mutation}mutation process then follows as such.
-For each each parent $x_{i}(t)$ generate a trial vector $u_{i}(t)$ as follows.
-
-\begin{itemize}
-      \item Select a target vector, $x_{i_{1}}(t)$ from the population that is not the same as the parent i.e.
+For each each parent $\boldsymbol{x}_{i}(t)$ generate a trial vector $\boldsymbol{u}_{i}(t)$ as follows.
+
+\begin{itemize}
+      \item Select a target vector, $\boldsymbol{x}_{i_{1}}(t)$ from the population that is not the same as the parent i.e.
 $i \neq i_{1}$.
@@
 
-      \item Randomly select two other individuals $x_{i_{2}}(t)$ and $x_{i_{3}}(t)$.
+      \item Randomly select two other individuals $\boldsymbol{x}_{i_{2}}(t)$ and $\boldsymbol{x}_{i_{3}}(t)$.
 Importantly, all of these entities must be unique such that $i \neq i_{1} \neq i_{2} \neq i_{3}$ and $i_{2}, i_{3} \sim U(1, N)$ where $N$ is the size of the swarm/population.
@@
       \begin{split}
-            u_{i}(t) = x_{i_{1}} + \beta(x_{i_{2}}(t) - x_{i_{3}}(t))
-      \end{split}
-\end{equation}
-
-\noindent
+            \boldsymbol{u}_{i}(t) = \boldsymbol{x}_{i_{1}} + \beta(\boldsymbol{x}_{i_{2}}(t) - \boldsymbol{x}_{i_{3}}(t))
+      \end{split}
+\end{equation}
+
 In Equation~\eqref{eq:heuristics:de:mutation} $\beta \in (0, \infty)$ is the scale factor and controls the amplification of the differential variation~\cite{ref:engelbrecht:2007}.
@@
 The same applies to \acs{DE}.
-The \acs{DE} \index{crossover}crossover operator implements a discrete recombination of the trial vector, $u_{i}(t)$, as was generated in Equation~\eqref{eq:heuristics:de:mutation} above, and the parent vector $x_{i}(t)$ to produce new offspring $x'_{i}(t)$.
+The \acs{DE} \index{crossover}crossover operator implements a discrete recombination of the trial vector, $\boldsymbol{u}_{i}(t)$, as was generated in Equation~\eqref{eq:heuristics:de:mutation} above, and the parent vector $\boldsymbol{x}_{i}(t)$ to produce new offspring $\boldsymbol{x}'_{i}(t)$.
 The \index{crossover}crossover operator is given in Equation~\eqref{eq:heuristics:de:crossover} below.
@@
 
-\noindent
-In Equation~\eqref{eq:heuristics:de:crossover}, $x_{ij}(t)$ refers to the $j$-th element of the vector $x_{i}(t)$ and $\mathcal{J}$ refers to a set of \index{crossover}crossover points or indices at which perturbation is done.
+In Equation~\eqref{eq:heuristics:de:crossover}, $x_{ij}(t)$ refers to the $j$-th element of the vector $\boldsymbol{x}_{i}(t)$ and $\mathcal{J}$ refers to a set of \index{crossover}crossover points or indices at which perturbation is done.
 Different techniques for determining the set $\mathcal{J}$, has been proposed~\cite{ref:storn:1996, ref:storn:1997}.
@@
 Exponential \index{crossover}crossover does not require the selection of an additional \index{crossover}crossover point $j^{*}$ as this technique includes at the very least one index, which is the starting index that is randomly selected.
-From the starting index, the next index is selected until $U(0,1) \geq p_{r}$ or $|\mathcal{J}| = N$.
-$p_{r}$ is the same \index{crossover}crossover probability as mentioned above for binomial \index{crossover}crossover.
-The implementation of exponential \index{crossover}crossover is given in Algorithm~\ref{algo:heuristics:de:exp} below.
+From the starting index, the next index is selected until $U(0,1) \geq p_{r}$ or $|\mathcal{J}| = N$, and $p_{r}$ is the same \index{crossover}crossover probability as mentioned above for binomial \index{crossover}crossover.
+The implementation of exponential \index{crossover}crossover is given in Algorithm~\ref{algo:heuristics:de:exp}.
 \end{itemize}
@@
 Various selection operators have been suggested~\cite{ref:storn:1996, ref:storn:1997}.
-With reference to the \index{mutation}mutation operator, most \acs{DE} implementations make use of random selection or the best entity is used as the target vector $x_{i_{1}}(t)$.
+With reference to the \index{mutation}mutation operator, most \acs{DE} implementations make use of random selection or the best entity is used as the target vector $\boldsymbol{x}_{i_{1}}(t)$.
 To construct the population for the next generation, deterministic selection is used.
-As such, a parent is replaced if the offspring produces a better solution than the parent such that $f(x'_{i}(t)) \leq f(x_{i}(t))$.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} states that deterministic selection for the next generation ensures the average fitness of the population does not deteriorate.
+As such, a parent is replaced if the offspring produces a better solution than the parent such that $f(\boldsymbol{x}'_{i}(t)) \leq f(\boldsymbol{x}_{i}(t))$.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} states that deterministic selection for the next generation ensures the average fitness of the population does not deteriorate.
 
@@
             \While{stopping condition not met}
-            \For{each entity $x_{i}(t) \in \mathcal{C}(t)$ }
-            \State Evaluate the fitness, $f(x_{i}(t))$;
-            \State Create the trial vector, $u_{i}(t)$ by applying the mutation operator;
-            \State Create an offspring, $x'_{i}(t)$ by applying the crossover operator;
-            \If{$f(x'_{i}(t))$ is better than $f(x_{i}(t))$ }
-            \State Add $x'_{i}(t)$ to $\mathcal{C}(t+1)$;
+            \For{each entity $\boldsymbol{x}_{i}(t) \in \mathcal{C}(t)$ }
+            \State Evaluate the fitness, $f(\boldsymbol{x}_{i}(t))$;
+            \State Create the trial vector, $\boldsymbol{u}_{i}(t)$ by applying the mutation operator;
+            \State Create an offspring, $\boldsymbol{x}'_{i}(t)$ by applying the crossover operator;
+            \If{$f(\boldsymbol{x}'_{i}(t))$ is better than $f(\boldsymbol{x}_{i}(t))$ }
+            \State Add $\boldsymbol{x}'_{i}(t)$ to $\mathcal{C}(t+1)$;
             \Else
-            \State Add $x_{i}(t)$ to $\mathcal{C}(t+1)$;
+            \State Add $\boldsymbol{x}_{i}(t)$ to $\mathcal{C}(t+1)$;
             \EndIf
@@
 
-\noindent
 As with other heuristics, \acs{DE} also contains a set of control parameters. These include:
@@
 
-      \item \textbf{Scaling Factor:} The scaling factor, $\beta \in (0, \infty)$ controls the amplification of the differential variations $(x_{i_{2}}(t) - x_{i_{3}}(t))$.
+      \item \textbf{Scaling Factor:} The scaling factor, $\beta \in (0, \infty)$ controls the amplification of the differential variations $(\boldsymbol{x}_{i_{2}}(t) - \boldsymbol{x}_{i_{3}}(t))$.
 A lower scaling factor leads to smaller step sizes and as a result, convergence will take longer.
@@
 A general notation for \acs{DE} heuristic variants have been developed by Storn et al.~\cite{ref:storn:1996, ref:storn:1997}.
-The notation follows the form \textit{DE/$x$/$y$/$z$} where $x$,$y$ and $z$ refer to the components that are used by the particular \acs{DE}.
-A breakdown of this notation is provided as follows.
+The notation follows the form \textit{DE/$x$/$y$/$z$} where $x$, $y$ and $z$ refer to the components that are used by the particular \acs{DE}.
+A breakdown of this notation is provided as follows:
 
@@
 
-\noindent
 For this dissertation, \textit{random} and \textit{best entity} selection, a single difference vector and binomial and exponential \index{crossover}crossover are considered.
-This results in the \acs{DE} notations as follows.
+This results in the \acs{DE} notations as follows:
 
@@
 \end{itemize}
-
-\noindent
-This section provided the reader with the details around the implementation of the \acs{DE} heuristic. The last population-based \acs{MH} is presented next.
 
@@
 
-So far the reader has been introduced to two population-based \acp{MH}.
+So far, two population-based \acp{MH} have been introduces.
 These include \acs{PSO} and \acs{DE}.
@@
             \While{stopping condition not met}
-            \State Evaluate the fitness, $f(x_{i}(t))$ of each individual $x_{i}(t)$;
+            \State Evaluate the fitness, $f(\boldsymbol{x}_{i}(t))$ of each individual $\boldsymbol{x}_{i}(t)$;
             \State Perform reproduction to create offspring;
@@
 
-\noindent
 From Algorithm~\ref{algo:heuristics:ga:generic_ec} above, it can be seen that a number of components influence the search process. These include:
@@
 
-\noindent
 The initial implementations of \acs{EC} heuristics such as \acp{GA} did not contain a \index{mutation}mutation operator as it was only introduced later~\cite{ref:engelbrecht:2007}.
@@
 \begin{itemize}
-      \item \textbf{Asexual:} Offspring is generated from one parent.
-
-      \item \textbf{Sexual:} Offspring is generated from two parents and can produce one or two offspring.
-
-      \item \textbf{Multi-recombination:} Offspring is generated from more than two parents and can produce one or more offspring.
-\end{itemize}
-
-\noindent
+      \item \textbf{Asexual:} Offspring are generated from one parent.
+
+      \item \textbf{Sexual:} Offspring are generated from two parents and can produce one or two offspring.
+
+      \item \textbf{Multi-recombination:} Offspring are generated from more than two parents and can produce one or more offspring.
+\end{itemize}
+
 \citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that \index{crossover}crossover operators can be further classified based on their encoding/representation scheme.
@@
 In doing so, diversity is added into the genetic characteristics of the population.
-Mutation is applied at a certain \index{mutation}mutation probability $p_{m}$, to each gene of the offspring $x_{i}(t)$ to produce mutated offspring $x'_{i}(t)$.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that the \index{mutation}mutation probability, also referred to as the \index{mutation}mutation rate, is usually small such that $p_{m} \in [0,1]$ to ensure that good solutions are not distorted too much.
+Mutation is applied at a certain \index{mutation}mutation probability $p_{m}$, to each gene of the offspring $\boldsymbol{x}_{i}(t)$ to produce mutated offspring $\boldsymbol{x}'_{i}(t)$.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that the \index{mutation}mutation probability, also referred to as the \index{mutation}mutation rate, is usually small such that $p_{m} \in [0,1]$ to ensure that good solutions are not distorted too much.
 
@@
 
-\noindent
 An illustration of the adapted uniform \index{mutation}mutation operator is presented in Figure~\ref{fig:heuristics:mh:ga:uniform_mutation} below.
@@
 
-\noindent
 \citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that selection operators are characterised by their \textit{selective pressure}.
@@
       \item \textbf{Rank-based Selection:} Rank-based selection uses the rank-ordered fitness values to determine the probability of selection and not the absolute fitness value.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that the advantage of this approach is that the best entities will not dominate the selection process.
-Non-deterministic linear sampling selects an entity $x_{i}(t)$ such that $i \sim U(0, U(0, N - 1))$.
+Non-deterministic linear sampling selects an entity $\boldsymbol{x}_{i}(t)$ such that $i \sim U(0, U(0, N - 1))$.
 Importantly, in the context of a minimisation problem, entities are first sorted in decreasing order of fitness value, assuming that the best heuristic is then contained at index 0, while the worst entity is contained at index $N - 1$.
@@
 
-This chapter provided the reader with detailed background information on \index{heuristic}heuristics.
+This chapter provided detailed background information on \index{heuristic}heuristics.
 Different heuristics were presented that have been shown to be able to train \acp{FFNN}.
@@
 These include gradient-based \index{heuristic}heuristics and \acfp{MH}.
-A number of different variants for each group have been presented and discussed in detail.
-
-The following chapter aims to build on the foundations provided in this chapter and introduces the reader to \acfp{HH}.
+A number of different variants for each group have been presented and was discussed in detail.

### 2022-11-24 dissertation/chapters/01-introduction.tex
✨ (final-review): Up to chapter 4

@@
 \begin{quotation}
-      \noindent ``It is better to solve one problem five different ways, than to solve five problems one way.''
+      ``It is better to solve one problem five different ways, than to solve five problems one way.''
 \end{quotation}
@@
 
-This chapter provides the reader with a brief overview of the problem domain and outlines the research problem, objectives and purpose. The remainder of the chapter is presented as follows.
+This chapter provides the reader with a brief overview of the problem domain and outlines the research problem, objectives and purpose. The remainder of the chapter is presented as follows:
 
@@
 
-The remainder of this dissertation is structured as follows.
+The remainder of this dissertation is structured as follows:
 

### 2022-11-24 dissertation/chapters/02-artificial-neural-networks.tex
✨ (final-review): Up to chapter 4

@@
 \acp{ANN} are used throughout this dissertation as the \textit{model} to be trained using \acp{HH}.
-The purpose of this chapter is to provide the necessary background information needed on \acp{ANN} and is structured as follows.
+The purpose of this chapter is to provide the necessary background information needed on \acp{ANN} and is structured as follows:
 
@@
 To emulate the computational capability of the human brain is not yet possible on modern day hardware.~\citeauthor{ref:sandberg:2008}~\cite{ref:sandberg:2008} approximates a computational requirement of 256 000 terabytes/s to emulate the entire brain.
-Despite our shortage in hardware capabilities, \acp{ANN} have been successfully applied to a range of problem classes.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} summarises some common problems that are solved using \acp{ANN} and can be listed as follows.
+Despite our shortage in hardware capabilities, \acp{ANN} have been successfully applied to a range of problem classes.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} summarises some common problems that are solved using \acp{ANN} and can be listed as follows:
 

### 2022-11-24 dissertation/chapters/03-heuristics.tex
✨ (final-review): Up to chapter 4

@@
 Pseudo-code algorithms are provided for each technique and discussions follow on advantages, disadvantages, capabilities and limitations.
-The remainder of this chapter is structured as follows.
+The remainder of this chapter is structured as follows:
 
@@
 The \index{mutation}mutation process then follows as such.
-For each each parent $\boldsymbol{x}_{i}(t)$ generate a trial vector $\boldsymbol{u}_{i}(t)$ as follows.
+For each each parent $\boldsymbol{x}_{i}(t)$ generate a trial vector $\boldsymbol{u}_{i}(t)$ as follows:
 

### 2022-11-24 dissertation/chapters/04-hyper-heuristics.tex
✨ (final-review): Up to chapter 4

@@
 \begin{quotation}
-      \noindent ``The capacity to learn is a gift; the ability to learn is a skill; the willingness to learn is a choice.''
+      ``The capacity to learn is a gift; the ability to learn is a skill; the willingness to learn is a choice.''
 \end{quotation}
@@
 
-\noindent
 Chapter \ref{chap:heuristics} introduced the concept of a \index{heuristic}heuristic as an optimisation algorithm that is used in a search process that seeks out optimal solutions to an optimisation problem.
@@
 
-More modern techniques automate the search for optimal configuration as part of the underlying search process itself, resulting in a form of \index{online learning}online learning.
-An example of such a technique is to dynamically adjust and learn the heuristic \index{hyper-parameters}\textit{hyper-parameters} as part of the optimisation process.
+More modern techniques automate the search for optimal configuration as part of the underlying search process itself, resulting in a form of dynamic configuration during the search process.
+An example of such a technique is to dynamically adjust the heuristic \index{hyper-parameters}\textit{hyper-parameters} as part of the optimisation process.
 This field of study is known as \index{meta-learning}meta-learning~\cite{ref:giraud:2004}.
+The term \textit{learning} refers to the optimisation of the configuration and \index{hyper-parameters}hyper-parameters.
 
-A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the \index{heuristic}heuristic used throughout the training process and not just the \index{heuristic}heuristic hyper-parameters.
-This approach focuses on the hybridisation of learning paradigms.
-By dynamically combining the best of different learning paradigms throughout the learning process, a trade-off can be made between focussing on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during training.
-The dynamic trade-off between exploration and exploitation could also be seen as a dynamic trade-off between the strengths and weaknesses of different heuristics during the search process.
+A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the \index{heuristic}heuristic characteristics and heaviours used throughout the search process and not just the \index{heuristic}heuristic hyper-parameters.
+This approach focuses on the hybridisation of \index{heuristic}heuristic paradigms.
+By dynamically combining the best of different \index{heuristic} paradigms throughout the learning process, a trade-off can be made between focussing on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during the search process.
+The dynamic trade-off between exploration and exploitation could also be seen as a dynamic trade-off between the strengths and weaknesses of different \index{heuristic}heuristics during the search process.
 
-One such form of hybridisation of learning paradigms is referred to as \textit{heterogeneous learning approaches}.
-Heterogeneous learning approaches make use of different \textit{search behaviours} by selecting from a behaviour pool.
+One such form of hybridisation of \index{heuristic}heuristic paradigms is referred to as \textit{heterogeneous approaches}.
+Heterogeneous approaches make use of different \textit{search behaviours} by selecting from a behaviour pool.
 Heterogeneous approaches have shown to balance the trade-off between exploration and exploitation~\cite{ref:nepomuceno:2013}.
 
-Another form of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem~\cite{ref:burke:2013}.
+Another form of hybridisation of \index{heuristic}heuristic paradigms is that of hybridisation of different \textit{heuristics} that are applied to some optimisation problem~\cite{ref:burke:2013}.
 These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.
@@
 This chapter provides the reader with the necessary background information of \index{meta-learning}meta-learning and \acp{HH}.
-The remainder of the chapter is structured as follows.
+The remainder of the chapter is structured as follows:
 
@@
 
-\citeauthor{ref:vilalta:2002}~\cite{ref:vilalta:2002} mentions that meta-learning differs from base-learning in the scope of the level of adaptation.
+\citeauthor{ref:vilalta:2002}~\cite{ref:vilalta:2002} mention that meta-learning differs from base-learning in the scope of the level of adaptation.
 Meta-learning is concerned with learning how to choose the right configuration and biases dynamically.
 On the contrary, for \textit{base}-learning, biases and configurations are predefined and fixed a priori.
-\citeauthor{ref:thrun:1998}~\cite{ref:thrun:1998} mentions that meta-learning aims at discovering ways to dynamically search for the best learning strategy as the number of tasks increases, implying some form of generalisation of the learning process to other problems.
+\citeauthor{ref:thrun:1998}~\cite{ref:thrun:1998} mention that meta-learning aims at discovering ways to dynamically search for the best learning strategy as the number of tasks increase, implying some form of generalisation of the learning process to other problems.
 
@@
 
-\acp{HH} implement a form of \index{meta-learning}meta-learning that is concerned with the selection of the best heuristic from a pool of heuristics, to solve a given problem.
+\acp{HH} implement a form of \index{meta-learning}meta-learning that is concerned with the selection of the best heuristic from a pool of heuristics to solve a given problem.
 In the context of population-based \acp{HH}, an entity pool exists that represent a pool of candidate solutions to the given problem.
@@
 
-\noindent
 Figure \ref{fig:heuristics:hh:hh_algorithm} shows the separation of information that is accessible to the entity pool and heuristic pool.
@@
 
-A \acs{HH} is considered to be a learning algorithm when it uses feedback from the search process to adapt and guide the search process.
+\acp{HH} make use of feedback from the search process to adapt and guide the search process.
+Some \acp{HH} implement a learning mechanism that utilises this feedback.
 Learning \acp{HH} can implement a form of \index{online learning}\textit{online learning} or \index{offline learning}\textit{offline learning}.
@@
 \acp{HH} that implement \index{offline learning}offline learning, implement a form of learning where knowledge, in the form of rules or programs, is gathered from a set of training instances and is then applied independently from the search process itself.
-Examples of offline learning approaches within hyper-heuristics include \textit{learning classifier systems}, \textit{case-based reasoning} and \acf{GP}.
+Examples of offline learning approaches within hyper-heuristics include \textit{learning classifier systems} and \textit{case-based reasoning}.
 
@@
 
-Selection \acp{HH} consists of two components, including a low-level \index{heuristic}heuristic selection strategy and a move acceptance strategy.
+Selection \acp{HH} consist of two components, including a low-level \index{heuristic}heuristic selection strategy and a move acceptance strategy.
 Low-level \index{heuristic}heuristic selection can be done in a simple, \textit{non-adaptive} way.
@@
 A move acceptance strategy is the mechanism by which the application of a low-level \index{heuristic}heuristic is either accepted or rejected.
-In general, a move is accepted or rejected based on the quality of the move and the current solution during a single point search.~\citeauthor{ref:burke:2003}~\cite{ref:burke:2003} mentions that many move acceptance strategies have been explored within \acp{HH}.
+In general, a move is accepted or rejected based on the quality of the move and the current solution during a single point search.~\citeauthor{ref:burke:2003}~\cite{ref:burke:2003} mention that many move acceptance strategies have been explored within \acp{HH}.
 
@@
 Formal definitions were given, followed by detailed discussions.
-A modern classification scheme for \acs{HH} as proposed by ~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} was presented in detail.
+A modern classification scheme for \acs{HH} as proposed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} was presented in detail.
 Distinction is made between the source of feedback information used during learning and the nature of the heuristic search space.

### 2022-11-24 dissertation/chapters/05-probability.tex
✨ (final-review): Up to chapter 4

@@
 \begin{quotation}
-      \noindent ``Probability theory is nothing but common sense reduced to calculation.''
+      ``Probability theory is nothing but common sense reduced to calculation.''
 \end{quotation}
@@
 
-\noindent
 Probability theory and statistics can be traced back to as early as the 18th century.
@@
 These are big fields and focus is put on the elements that are required to formulate the proposed \acf{BHH}.
-The remainder of the chapter is structured as follows.
+The remainder of the chapter is structured as follows:
 
@@
 
-\noindent
 In Equation~\eqref{eq:probability:overview:conditional} above, $P(B) > 0$.
@@
 
-      \noindent
       otherwise, events $A$ and $B$ are said to be \textit{dependent} random events.
@@
 
-      \noindent
       If $A$ and $B$ are independent, then
@@
 
-      \noindent
       Then the collection of sets $\{B_{1}$, $B_{2}$, $\dots$, $B_{K}\}$ is said to be a partition of S, the union of mutually exclusive subsets.
@@
 
-\noindent
 One of the many applications of \index{Bayes' Theorem}Bayes' Theorem is to do statistical inference.
@@
 
-\noindent
 From Equation~\eqref{eq:probability:probability_distributions:beta:pdf} above, the normalising constant $B(\alpha, \beta)$, is defined below in Equation~\eqref{eq:probability:probability_distributions:beta:norm_const}.
@@
 
-\noindent
 In Equation~\eqref{eq:probability:probability_distributions:beta:norm_const}, $\Gamma$ is the Gamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func} below.
@@
 
-\noindent
 It should be noted that the Gamma function can also be written as shown in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func_alt} below.
@@
 
-\noindent
 The control parameters $\alpha$ and $\beta$, determine the shape of the distribution.
@@
 
-\noindent
 The expected value of $x$ is given below in Equation~\eqref{eq:probability:probability_distributions:beta:expected_value}.
@@
 
-\noindent
 Similarly, the expected value of the natural logarithm of $x$ can be calculated as is shown below in Equation~\eqref{eq:probability:probability_distributions:beta:expected_value_ln}.
@@
 
-\noindent
 In Equation~\eqref{eq:probability:probability_distributions:beta:expected_value_ln} above, $\psi$ is the logarithmic derivative of the Gamma function, called the \textit{Digamma} function.
@@
 
-\noindent
 Finally, the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:beta:mode} below.
@@
 
-\noindent
 In Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} above, the normalising constant $B(\alpha)$, is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:norm_cost}.
@@
 
-\noindent
 In Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} above, $\alpha_{0}$ is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:alpha_0} below.
@@
 
-\noindent
 Importantly, the set $\{x_{k}\}_{k=1}^{K}$ belongs to the standard $K-1$ probability simplex $S$, meaning that $x_{K} = 1 - \sum_{k=1}^{K-1}x_{k}$ with support $\forall_{k=1}^{K} x \in [0,1]$.
@@
 
-\noindent
 The expected value of $x$ can be calculated as shown in Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value} below.
@@
 
-\noindent
 Similarly, the expected value of the natural logarithm of $x_{k}$ can be calculated as defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value_ln} below.
@@
 
-\noindent
 In Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value_ln} above, $\psi$ is the Digamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}.
@@
 
-\noindent
 Equation~\eqref{eq:probability:probability_distributions:bernoulli:pmf} above, can also be expressed as show in Equation~\eqref{eq:probability:probability_distributions:bernoulli:alt} below.
@@
 
-\noindent
 The mean of the \index{Bernoulli probability distribution}Bernoulli probability distribution approaches $\theta$ over many samples according to the \acs{CLT}~\cite{ref:grinstead:1997}.
@@
 
-\noindent
 The expected value of the distribution is thus given according to Equation~\eqref{eq:probability:probability_distributions:bernoulli:expected_value} below.
@@
 
-\noindent
 The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:bernoulli:mode} below.
@@
 
-\noindent
 Similar to the \index{Bernoulli probability distribution}Bernoulli probability distribution, the mean of the \index{Binomial probability distribution}Binomial probability distribution is $N\theta$ given the \acs{CLT} as was shown in Figure \ref{fig:probability:probability_distributions:bernoulli:coin}.
@@
 
-\noindent
 The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:mode} below.
@@
 
-\noindent
 In Equation~\eqref{eq:probability:probability_distributions:categorical:pmf} above, $[x = k]$ is the \textit{Iversion Bracket}~\cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
@@
 
-\noindent
 The random variable $x$ can also be encoded in binary format, yielding a vector $\vec{x} = (x_{1}, \dots, x_{K})$ of \index{Bernoulli probability distribution}Bernoulli probability distributions such that the support is $\forall_{k=1}^{K} x_{k} \in \{0, 1\}$.
@@
 
-\noindent
 In Equation \ref{eq:probability:probability_distributions:categorical:pmf_alt} above, $\mathbbm{1}(x_{k})$ is the \textit{indicator function}, yielding 1 if $x_{k} = 1$ and 0 otherwise.
@@
 
-\noindent
 The support for the Multinomial is $\forall_{i=1}^{K} x_{k} \in \{1, \dots, N\}, \sum_{k=1}^{K}x_{k} = N$ and the \acs{PMF} for the \index{Multinomial probability distribution}Multinomial probability distribution is given below in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf}.
@@
 
-\noindent
 Similar to the \index{Categorical probability distribution}Categorical probability distribution, the random variable $x$ can also be encoded in binary format, yielding an $N \times K$ matrix $X$ of \index{Bernoulli probability distribution}Bernoulli probability distributions.
@@
 
-\noindent
 In Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt} above, $N_{k}$ is a summary variable, denoting the number of times a category $k$ occurs over all trials in $N$.
@@
 
-\noindent
 The Bernoulli likelihood is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:likelihood} below.
@@
 
-\noindent
 By \index{Bayes' Theorem}Bayes' Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.
@@
 
-\noindent
 Since the denominator sums to $1$, one could get rid of the denominator and constants for the Bernoulli likelihood and the Beta prior, by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior_propto} below.
@@
 
-\noindent
 The posterior distribution has the same functional form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N_{1} + \alpha$ and $\beta' = N_{0} + \beta$.
@@
 
-\noindent
 The likelihood of the Categorical and \index{Multinomial probability distribution}Multinomial probability distributions is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:likelihood} below.
@@
 
-\noindent
 By \index{Bayes' Theorem}Bayes' Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.
@@
 
-\noindent
 Since the denominator sums to $1$, one could get rid of the denominator and constants for the \index{Dirichlet probability distribution}Dirichlet prior, by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior_propto} below.
@@
 
-\noindent
 The posterior distribution has the same form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N + \alpha$.
@@
 
-\noindent
 If Bayesian statistics is used, the experimental design that was chosen does not matter.
@@
 
-\noindent
 It can be seen from Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} how the posterior distribution differs from the prior distribution.
@@
 
-\noindent
 The marginal density or mass function of $Y_{1}, Y_{2}, \dots, Y_{N}$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:marginal_density} below.
@@
 
-\noindent
 Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$, according to \index{Bayes' Theorem}Bayes' Theorem, is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.
@@
 
-\noindent
 \citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} mentions that the posterior density summarises all the pertinent information about the parameter $\theta$ by making use of the information contained in the prior for $\theta$, as well as the information in the observed data/evidence.
@@
 
-\noindent
 In Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_1} above, $y_{i} = \{0,1\}$ and $0 < \theta < 1$.
@@
 
-\noindent
 Then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ from Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood} can be formulated as in shown in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_3} below.
@@
 
-\noindent
 The marginal density of $Y_{1}, Y_{2}, \dots Y_{N}$ is then given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_4} below.
@@
 
-\noindent
 Finally, the posterior density of $\theta$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_5} below.
@@
 
-\noindent
 The posterior density has the same functional shape $\mathcal{A}(v)$ as the prior, yielding the update on prior parameters as $\alpha^{*} = \sum y_{i} + \alpha$ and $\beta^{*} = n - \sum y_{i} + \beta$.

### 2022-11-24 dissertation/chapters/06-bayesian-hyper-heuristic.tex
✨ (final-review): Up to chapter 4

@@
 \begin{quotation}
-      \noindent ``The result is a posterior distribution, which the agent may use as its new prior in the next step.''
+      ``The result is a posterior distribution, which the agent may use as its new prior in the next step.''
 \end{quotation}
@@
 
-\noindent
 The above quote was the inspiration for the development of a novel \acf{HH} that uses Bayesian probability concepts as a selection mechanism to drive the heuristic selection process.
@@
 This chapter provides the details around the implementation of the \Ac{BHH} and explains how it used to train \acp{FFNN}.
-The remainder of the chapter is structured as follows.
+The remainder of the chapter is structured as follows:
 
@@
 According to the aforementioned classification scheme, the \Acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.
-A breakdown of the classification is given as follows.
+A breakdown of the classification is given as follows:
 
@@
 
-\noindent
 The following sections presents the reader with more detail on the implementation of the \acs{BHH}.
@@
 
-\noindent
 With reference to Figure \ref{fig:bhh_architecture}, the components are briefly given below in the order of information flow during the \acs{FFNN} training process steps.
@@
 
-\noindent
 Each of the components in Figure \ref{fig:bhh_architecture} is discussed in detail in the following sections.
@@
 
-\noindent
 Primary and proxied state parameters must be maintained together.
@@
 
-\noindent
 From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when \index{heuristic}heuristic A is selected, it will outsource state update operations from \index{heuristic}heuristic B, for state parameter 2.
@@
 
-\noindent
 From the list above, it should be clear that entity state becomes increasingly complicated with the increase of the number of distinct \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool with unique state parameters.
@@
 
-\noindent
 Entities in the entity pool are each assigned an associated \index{heuristic}heuristic.
@@
 
-\noindent
 An example of the performance log implemented by the \acs{BHH} is given in Table \ref{tab:bhh:performance_log:performance_log_example} below.
@@
 
-\noindent
 The performance log itself introduces a number of design considerations as well.
@@
 
-\noindent
 The implementation of a credit assignment strategy is simply a function that translates the performance log from Table \ref{tab:bhh:performance_log:performance_log_example}, into Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}.
@@
 
-\noindent
 Credit is used by the selection mechanism of the \acs{BHH}. The selection mechanism is presented in the following section.
@@
 
-\noindent
 It should be noted that event information is stored and observed directly from the performance log as presented in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}.
@@
 
-\noindent
 Since the \acs{BHH} implements a Bayesian classifier, the \acs{BHH} is not concerned with actual probabilities.
@@
 
-\noindent
 The conditionality implemented by \index{Bayes' Theorem}Bayes' Theorem can be extended to include multiple criteria.
@@
 \\
-\noindent
 Let
@@
 
-\noindent
 Vector notation is dropped for sake of convenience, simplicity and readability.
@@
 
-\noindent
 Notice the joint probability over events $E$ and $C$, given the selection of a heuristic $H$, denoted by the product of the sums of the separate parts for $E$ and $C$, in the denominator.
@@
 
-\noindent
 The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $H$, given allocation to entity $E$ and credit $C$, parameterised by sampled $\theta$, $\phi$ and $\psi$.
@@
 
-\noindent
 In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf} above, $N_{k}$ is a summary variable such that $N_{k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the event $h_{i}$ taking on class $k$ in $I$ independent, identical runs.
@@
 
-\noindent
 In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} above, $N_{j,k}$ is a summary variable such that $N_{j,k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on class $k$, i.e.
@@
 
-\noindent
 In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above, $N_{k}$ is the same summary variable as described for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}.
@@
 
-\noindent
 Consider the practical implementation of the predictive model as shown in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} above.
@@
 
-\noindent
 The log-sum-exp trick as shown above caters for very small probabilities, however, there might be a situation where  a random event is never seen, purely by chance.
@@
 
-\noindent
 Another suggestion is to ensure that at least one of every heuristic is always selected during training.
@@
 
-\noindent
 The derivations of the \acs{MLE} for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and
@@
 
-\noindent
 Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} can be broken down into each of its components.
@@
 
-\noindent
 The \acs{MLE} for $\hat{\psi_{k}} $ can be calculated by taking the partial derivative of Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_psi} with respect to $\psi_{k}$ and equating to zero as presented in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_psi} as follows.
@@
 
-\noindent
 The \acs{MLE} for $\hat{\theta_{k}} $ can be calculated similarly.
@@
 
-\noindent
 Solving first for $\epsilon$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_2} below.
@@
 
-\noindent
 Then solving for $\theta_{k}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} as presented below.
@@
 
-\noindent
 Substituting $N = \epsilon$ back into Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_4} below.
@@
 
-\noindent
 The \acs{MLE} for $\hat{\phi}_{j, k} $ is calculated similarly.
@@
 
-\noindent
 Solving first for $\lambda_{j}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_2} as is given below.
@@
 
-\noindent
 Then solving for $\phi_{j,k}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} below.
@@
 
-\noindent
 Substituting $N_{j} = \lambda_{j}$ back into Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_4} below.
@@
 
-\noindent
 The event $H$ is a multinomial distribution with probability parameter $\theta$.
@@
 
-\noindent
 Furthermore, the event $E$ is also a multinomial distribution with parameter $\phi$.
@@
 
-\noindent
 Finally, the event $C$ is a \index{Binomial probability distribution}Binomial probability distribution with probability parameter $\psi$.
@@
 
-\noindent
 Putting the likelihood and priors together yields the posterior distribution as given in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.
@@
 
-\noindent
 From Equation~\eqref{eq:bhh:optimisation_step:map:posterior} above, it can be seen that the posterior distribution has the same form $\mathcal{A}(v)$ as the prior distribution.
@@
 
-\noindent
 It can be seen that the prior and posterior probability distributions are of the same form, $\mathcal{A}(v)$.
@@
 
-\noindent
 The design choices at a high level is not as strict for the \acs{BHH} as it is for low-level heuristics.
@@
 
-\noindent
 A number of other hyper-parameters are specifically included to address the list of considerations as given above.
@@
 
-\noindent
 The following section discusses the default values for proxied update step operations.

### 2022-11-24 dissertation/chapters/07-methodology.tex
✨ (final-review): Up to chapter 4

@@
 \begin{quotation}
-      \noindent ``Observation, reason and experimentation make up what we call the scientific method.''
+      ``Observation, reason and experimentation make up what we call the scientific method.''
 \end{quotation}
@@
 
-\noindent
 So far, this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acf{HH} and probability theory in Chapters \ref{chap:anns}-\ref{chap:probability}.
@@
 The process by which the results are statistically analysed are also presented.
-The remainder of the chapter is structured as follows.
+The remainder of the chapter is structured as follows:
 
@@
 
-\noindent
 These empirical tests represent a set of questions, related to the \acs{BHH}, that need to be answered.
@@
 
-\noindent
 Details on how the datasets where preprocessed and prepared is given in Appendix \ref{app:datasets}. The concept of class balancing is briefly discussed next.
@@
 
-\noindent
 For the classification problems presented in Tables \ref{tab:methodology:datasets:classification} and \ref{tab:methodology:models:configurations}, the softmax activation function is added after training and is not included in the model during training.
@@
 
-\noindent
 Note that from Table \ref{tab:methodology:heuristics}, values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it.
@@
 
-\noindent
 In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x}, indicate that the associated \index{heuristic}heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
@@
 
-\noindent
 In Table \ref{tab:methodology:bhh_baseline_configuration}, the \index{heuristic}heuristic pool configuration that is used, is referred to as \textit{all}.
@@
 
-\noindent
 In Table \ref{tab:methodology:experiments:bhh_variants}, the \index{heuristic pool}heuristic pool configuration \textit{gd} refers to the \index{heuristic pool}heuristic pool configuration where only gradient-based \index{heuristic}heuristics are included, and \textit{mh} refers to the \index{heuristic pool}heuristic pool configuration where only meta-heuristics are included.

### 2022-11-24 dissertation/chapters/08-results.tex
✨ (final-review): Up to chapter 4

--- 2022-11-20 dissertation/chapters/08-results.tex
@@
-\chapter{Results}
-\label{chap:results}
+\chapter{Conclusion}
+\label{chap:conclusion}
 
 \begin{quotation}
-	\noindent ``Without data, you are just another person with an opinion.''
+      ``I am sorry to have made such a long speech, but I did not have time to make a shorter one.''
 \end{quotation}
 \begin{flushright}
-	- W. Edwards Deming
+      - Winston Churchill
 \end{flushright}
 
-The last step in the scientific process requires the presentation of the outcomes of the empirical process.
-Objective discussions based on statistical analysis of the findings is required.
-The design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}.
-The methodology presented a number of experimental groups to conduct.
-The experimental groups that were identified include a case study on the behaviour of the \acs{BHH} during training, an empirical comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics, and a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.
-
-This chapter provides the outcomes of the empirical processes and provides results on all the experiments that have been conducted.
-Detailed discussions follow on the outcomes of each experiment.
-Discussions are accompanied by figures and plots to help provide visual aid for discussions.
-The output of the statistical analysis that yielded the results is provided in Appendix~\ref{app:statistical_analysis}.
-The remainder of the chapter is structured as follows.
+This chapter provides a summary of the research that is done in this dissertation.
+The research objectives were set out in Chapter \ref{chap:introduction} and are concluded in this chapter.
+Furthermore, this chapter provides a summary of the results and findings from the empirical process and provides future research opportunities.
+The remainder of the chapter is structured as follows:
 
 \begin{itemize}
-	\item \textbf{Section \ref{sec:results:overview}} provides a brief overview of the outcomes of the empirical process and highlights key aspects to observe in the results.
+      \item \textbf{Section \ref{sec:conclusion:research_goals}} provides a summary of the research intent and provides a review of the problem statement, objectives and motivations behind the research.
 
-	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}.
-Illustrations are provided to show the change in parameter values to illustrate the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.
+      \item \textbf{Section \ref{sec:conclusion:background_info}} summarises the background information that was covered.
 
-	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics on all datasets.
-Three variants of the \acs{BHH} are included in these results.
-These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.
+      \item \textbf{Section \ref{sec:conclusion:bhh}} provides a brief summary of the \ac{BHH} and its implementation.
 
-	\item \textbf{Section \ref{sec:results:heuristic_pool}} provides the results for the experimental group that analyses the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the outcomes of the \acs{BHH}.
+      \item \textbf{Section \ref{sec:conclusion:methodology}} provides a brief summary of the methodology and the empirical process that was followed.
 
-	\item \textbf{Section \ref{sec:results:population}} provides the results for the experimental group that analyses the effects of the \textit{population size} hyper-parameter on the outcomes of the \acs{BHH}.
+      \item \textbf{Section \ref{sec:conclusion:results}} summarises the research findings. This section is broken down into the various experimental groups that were executed.
 
-	\item \textbf{Section \ref{sec:results:credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.
+      \item \textbf{Section \ref{sec:conclusion:further_research}} presents future research opportunities.
 
-	\item \textbf{Section \ref{sec:results:reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.
+      \item \textbf{Section \ref{sec:conclusion:documentation_and_data}} provides a brief discussion on supporting material related to the research, as made available by the authors.
 
-	\item \textbf{Section \ref{sec:results:replay}} provides the results for the experimental group that analyses the effects of the \textit{replay window size} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:reanalysis}} provides the results for the experimental group that analyses the effects of the \textit{reanalysis interval} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:normalise}} provides the results for the experimental group that analyses the effects of the \textit{normalisation} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:discounted_rewards}} provides the results for the experimental group that analyses the effects of the \textit{discounted rewards} hyper-parameter on the outcomes of the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:summary}} provides a brief summary of the chapter.
+      \item \textbf{Section \ref{sec:conclusion:summary}} provides a brief summary of the chapter.
 \end{itemize}
 
-\section{Overview}\label{sec:results:overview}
+\section{Summary of Research Intent}
+\label{sec:conclusion:research_goals}
 
-This section provides a brief discussion on the general outcome of the empirical process as a whole.
-Overall the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets.
-In general, the \acs{BHH} performs well and the empirical process provides key insights into the workings of the \acs{BHH}.
-Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.
+This section briefly reviews the problem statement, motivations and research objectives that was set out in Chapter \ref{chap:introduction} of this dissertation.
 
-Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results.
-The \acs{BHH} applies a form of \index{online learning}online learning.
-As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process.
-The training process is not repeated iteratively.
-All experiments conducted are executed for 30 epochs.
-The number of training steps executed is dependent on the batch size applied for each dataset.
+\subsection{Review of Problem Statement}
+\label{sec:conclusion:research_goals:problem_statement}
 
-All of the underlying \acp{FFNN} trained in the empirical process are relatively small.
-As such, most of the training progress is observed to occur withing the first five epochs.
-As a result, the \acs{BHH} should apply most learning at the early stages of the training process.
-After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point.
-Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the \index{heuristic}heuristic space beyond the five epoch mark.
+The main area of focus for the research done in this dissertation stems from the problem statement, which identified the difficult and tedious problem of selecting the best \index{heuristic}heuristic for training \acp{FFNN}.
+This process is often non-trivial and time-consuming.
+There is no easy way to know which \index{heuristic}heuristic to select to train \acp{FFNN}.
+Traditionally, an iterative approach of trial-and-error was followed.
+This process involves a tedious process of carefully considering and selecting candidate \index{heuristic}heuristics, whereby each candidate \index{heuristic}heuristic is then empirically tested and evaluated.
+This process is often executed at the expense of the researcher's resources.
 
-The \acs{BHH} does not implement a move acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution.
-In some cases the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.
+\subsection{Review of Research Motivation}
+\label{sec:conclusion:research_goals:motivations}
 
-Given the stochastic nature of the \index{heuristic}heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn.
-This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}.
-The probabilistic model implements \textit{probabilities of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.
+The research presented in this disseration identified the possibility of using a different approach, referred to as \acp{HH}, to automate the \index{heuristic}heuristic selection process.
+\acp{HH} are high-level search algorithms that search in the \index{heuristic}heuristic space, whereby low-level \index{heuristic}heuristics search in the solution space.
+\acp{HH} have been shown to provide a general solution to the \index{heuristic}heuristic selection process.
+The benefit that such an approach provides, is that it automates the \index{heuristic}heuristic selection process.
+This approach saves researchers time and potentially produce a solution that could generalise to multiple problems.
 
-The \textit{reanalysis interval} defines intervals at which the \acs{BHH} reanalyses the performance log, in effect, resetting the concentration parameters to their default values and reapplying the underlying Bayesian analysis process on the performance log.
-Furthermore, the \textit{replay window size} defines the amount of performance evidence in the performance log.
-By default, the \acs{BHH} baseline configuration has a reanalysis interval of 10, and a replay window size of 10, which is a small window to learn from.
-Despite the small reanalysis interval and the small replay window size, it should be observed that the \acs{BHH} exploits small performance biases regardless and does find small performance gains throughout.
+Investigation was done into the landscapes of existing solutions to train \acp{FFNN} as well as \acp{HH}.
+Though there exists many applications where \acp{HH} are used for optimisation, there are little to no published work on using \acp{HH} to train \acp{FFNN}.
+The only work that was found include the work by~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021}.
 
-\section{Behavioural Case Study}\label{sec:results:case_study}
+\subsection{Review of Research Objectives}
+\label{sec:conclusion:research_goals:research_objectives}
 
-This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset.
-As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records.
-The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process.
-Mini-batch training is executed with a batch size of 30.
-The results that are presented are averaged over 30 independent runs.
-
-Furthermore, the case study focuses on three variants of the \acs{BHH}.
-These include the baseline configuration, as was provided in Chapter~\ref{chap:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}).
-Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}).
-Finally, the case study includes a configuration that makes use of the \textit{symmetric} credit assignment strategy hyper-parameter, and is denoted as bhh\_credit\_symmetric (illustrated throughout in \textcolor{blue}{blue}).
-
-These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all.
-This section is structured as follows.
+Existing techniques from other problem domains were considered.
+\acs{RL}, meta-learning and probabilistic learning approached were considered.
+Bayesian probability theory showed promise.
+This research then set out to develop a novel high-level \index{heuristic}heuristic that utilises probability theory in an online learning setting to drive the automatic \index{heuristic}heuristic selection process.
+As such, the \acs{BHH} was conceptualised.
+The research objectives were defined and are summarised as follows:
 
 \begin{itemize}
-	\item \textbf{Section \ref{sec:results:case_study:performance_metrics}} provides illustrations and discussions around the outcomes of the performance metrics as obtained by the \acs{BHH}.
+      \item Conduct literature studies on all related topics that are relevant to the development of the \acs{BHH}.
+These include \acs{ANN}, existing low-level \index{heuristic}heuristics, meta-learning, \acp{HH}, probability theory and Bayesian statistics.
 
-	\item \textbf{Section \ref{sec:results:case_study:concentration_parameters}} provides illustrations and discussions around the changes in concentration parameter values as a result of the learning mechanism implemented by the \acs{BHH}.
+      \item Develop a novel \acs{BHH} that can be used to automate the \index{heuristic}heuristic selection process.
+The \acs{BHH} follows an approach that includes a selective and perturbative element in an online learning setting.
+Bayesian statistics and \acs{MAP} is used as the optimisation technique.
+Furthermore, the \acs{BHH} implements a mapping for proxied \index{heuristic}heuristic state update operations, whereby \index{heuristic}heuristic state is maintained by outsourcing state opertations to relevant low-level \index{heuristic}heuristics.
 
-	\item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probabilities of \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.
+      \item Conduct an empirical study to show that the \ac{BHH} is able to train \acp{FFNN} effectively on a number of different datasets.
 
-	\item \textbf{Section \ref{sec:results:case_study:prior_selec_prob}} provides illustrations and discussions around the changes in the \textit{prior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.
+      \item Conduct an empirical study to study the behavioural characteristics of the \acs{BHH}.
 
-	\item \textbf{Section \ref{sec:results:case_study:posterior_selec_prob}} provides illustrations and discussions around the changes in the \textit{posterior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.
+      \item Conduct an empirical study to critically evaluate the performance of the \acs{BHH} compared to traditional, low-level, standalone \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.
 
+      \item Conduct an empirical study to evaluate variants of the \acs{BHH} to study the impact of various hyper-parameters on the outcomes of the \ac{BHH}.
+
+      \item Provide and discuss the findings of the results produced by the empirical process. The results are analysed for statistical significance.
 \end{itemize}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% METRICS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Performance Metrics}\label{sec:results:case_study:performance_metrics}
+The research objectives set out in this dissertation are extensive.
+Each of these research objectives have been successfully executed.
+From the findings made in this dissertation, many different opportunities for future research are identified.
 
-This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}.
-Figures~\ref{fig:results:case_study:metrics:train_loss}-\ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test, loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
+\section{Summary of Background Information}
+\label{sec:conclusion:background_info}
 
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
-		\caption{Train log loss}
-		\label{fig:results:case_study:metrics:train_loss}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
-		\caption{Test log loss}
-		\label{fig:results:case_study:metrics:test_loss}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:case_study:metrics:train_accuracy}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:case_study:metrics:test_accuracy}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average train and test, loss and accuracy plots over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:metrics}
-\end{figure}
+Chapters \ref{chap:anns}-\ref{chap:probability} provided the reader with the relevant background information that is necessary to develop the novel \acs{BHH}.
+Chapter~\ref{chap:anns} provided background information on \acp{ANN}.
+All the components that make up the \acs{AN} were provided and is followed by discussions on \acp{FFNN}.
+Chapter~\ref{chap:heuristics} provided background information on various low-level heuristics that are designed to train \acp{FFNN}.
+A number of gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics were presented in detail.
+Chapter~\ref{chap:hhs} provided background information and literature reviews on \acp{HH}.
+Meta-learning is discussed and a \acs{HH} classification scheme, developed by \citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, was discussed in detail.
+Chapter~\ref{chap:probability} provided background information and mathematical derivations on probability theory and Bayesian statistics.
+Various probability distributions were provided along with their conjugate priors.
+\acs{MLE} and \acs{MAP} were presented in detail along with mathematical breakdowns.
 
-The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}, observed by the convergence of the training process, yielding good results.
-Figures~\ref{fig:results:case_study:metrics:train_accuracy} and~\ref{fig:results:case_study:metrics:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%.
+From the aforementioned chapters, it can be concluded that the necessary background information was provided as set out in the research objectives of this dissertation.
 
-Although the different configurations of the \acs{BHH} are all able to succesfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.
+\section{Summary of The Bayesian Hyper-Heuristic}
+\label{sec:conclusion:bhh}
 
-The volatility observed in Figure~\ref{fig:results:case_study:metrics:test_loss} is due to overfitting and partly due to the noisiness that results from mini-batch training.
-Early stopping can be applied to the training process to hault training before the model overfits on the training data.
-The training dataset is also very small, with just 120 samples.
-As such, overfitting can be expected.
+The main contribution from this dissertation is the development of a novel \acf{BHH}.
+Chapter \ref{chap:bhh} provided the details on the concept and implementation of the \ac{BHH}.
+Various design decisions and hyper-parameters that could affect the outcomes of the \ac{BHH} were presented.
 
-From Figure~\ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed.
-This could simply be a result of momentum that is maintained when switching between low-level \index{heuristic}heuristics in an attempt to find better solutions.
-For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions.
-The \acs{BHH} does not incorporate a \textit{move acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set.
-A move acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.
+It was shown that the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level \index{heuristic}heuristics in an online learning fashion.
+\index{heuristic}Heuristics are selected for each entity in a population of entities that each implement a candidate solution to the underlying \acs{FFNN}.
+The \acs{BHH} uses a Bayesian probabilistic model to drive the \index{heuristic}heuristic selection process.
+\acs{MAP} was derived for the probabilistic model and is used as the mechanism by which the \acs{BHH} is optimised, yielding the learning capability of the \acs{BHH}.
 
-Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figure~\ref{fig:results:case_study:metrics} only provides the outcomes of performance metrics at the end of each epoch.
-Further investigation is required at a mini-batch step level and is provided in the following sections.
+Furthermore, it is shown that \index{heuristic}heuristic selection alone is not sufficient and that a mechanism of transition between \index{heuristic}heuristics is needed as they are selected for each entity in the population.
+Entity and \index{heuristic}heuristic state and state-manipulation formed the cornerstone of this topic.
+Perturbation of \index{heuristic}heuristics and solutions is achieved through a technique that deconstructs \index{heuristic}heuristics into their initialisation and update steps.
+The update operations for each heuristic was derived as movement equations borrowed from the field of physics.
+This technique allows for the proxying of update step operations as they are required by different \index{heuristic}heuristics.
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS ALPHAS
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Detailed discussions were provided on a number of hyper-parameters that each contribute to the trade-off between \index{heuristic}heuristic and solution exploration and exploitation.
+These hyper-parameters include the \index{heuristic pool}\textit{heuristic pool} configuration, the \textit{population size}, the \textit{credit assignment strategy} used, the \textit{reselection interval}, the \textit{replay window size}, the \textit{reanalysis interval}, the \textit{burn in window size}, \textit{normalisation} of concentration parameters and \textit{discounted rewards} as assigned by the credit assignment strategy.
+A \acs{BHH} baseline configuration was identified with default values for each of the hyper-parameters.
 
-\subsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}
+It was mentioned that the \acs{BHH}, implemented in this dissertation, does not implement a move acceptance strategy that rejects heuristic progressions if they do not improve on the current best solution.
+Throughout the presentation of empirical results, it is recommended that this technique be investigated and implemented in further research.
 
-To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
-Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
-The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of selection probabilities}.
-Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at index 0, 6, 7, and 8 respectively.
-Index 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool.
-Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
+\section{Summary of Methodology}
+\label{sec:conclusion:methodology}
 
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
-		\caption{$\alpha_{0}$ - \acs{SGD}}
-		\label{fig:results:case_study:alphas:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
-		\caption{$\alpha_{6}$ - \acs{Adam}}
-		\label{fig:results:case_study:alphas:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
-		\caption{$\alpha_{7}$ - \acs{PSO}}
-		\label{fig:results:case_study:alphas:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
-		\caption{$\alpha_{8}$ - \acs{GA}}
-		\label{fig:results:case_study:alphas:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0,6,7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:alphas}
-\end{figure}
+The research objectives defined a number of empirical tests to be executed.
+Each one of the empirical tests is referred to as an experimental group.
+Various experimental groups have been identified and are listed below.
 
-The first logical observation to be made from Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
-Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
-The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process.
-However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$.
-The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}.
-Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.
+\begin{itemize}
+      \item An experimental group that provides a case-study on the behaviour of the \ac{BHH} as it relates to training of a \acs{FFNN} on an example dataset (iris), in order to understand the workings of the \acs{BHH}, and to determine if the \acs{BHH} is able to successfully train \acp{FFNN}.
+Three different configurations of the \acs{BHH} configuration was implemented.
+This includes the default \acs{BHH} baseline configuration, the \acs{BHH} baseline configuration where the replay window size is set to 250, and the \acs{BHH} baseline configuration which utilises the \textit{symmetric} credit assignment strategy.
 
-The next observations that can be made are for the bhh\_baseline configuration, illustrated in \textcolor{red}{red}, and the bhh\_credit\_symmetric configuration in \textcolor{blue}{blue}.
-Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1.0 as regular intervals.
-This interval is defined by the \textit{reanalysis interval} hyper-parameter.
-The reanalysis interval dictates the frequency at which Bayesian analysis is conducated on the performance log, mainted by the \acs{BHH}.
-Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval.
-As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.
+      \item An experimental group that provides a comparative analysis between the performance of the \acs{BHH} baseline configuration and low-level, standalone \index{heuristic}heuristics when training \acp{FFNN} on a number of datasets.
 
-Notice from Figure~\ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements.
-This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process.
-Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process.
-In a case where all five entities in the entity pool are allocated the same heuristic, for all ten samples defined in the performance log, defined by the replay window size, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.
+      \item An experimental group that provides a comparative analysis between variants of the \ac{BHH} that investigate the effects of various hyper-parameters on the outcomes of the \acs{BHH}.
+These variants include:
 
-Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning.
-The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurance} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
-\index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
-Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.
+            \begin{itemize}
+                  \item The \acs{BHH} baseline configuration with different \index{heuristic pool}heuristic pool configurations.
+Three different \index{heuristic pool}heuristic pool configurations were implemented.
+These configurations include a configuration with all the low-level \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool, a configuration with only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration with only \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool.
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS THETAS
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+                  \item The \acs{BHH} baseline configuration with different population sizes. Five different population sizes were implemented including 5, 10, 15, 20, and 25.
 
-\subsection{Probabilities of Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
+                  \item The \acs{BHH} baseline configuration with different credit assignment strategies.
+Five different credit assignment strategies were implemented including the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies.
 
-This section provides a detailed investigation into the \textit{probabilities of selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process.
-As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves.
-The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
+                  \item The \acs{BHH} baseline configuration with different reselection intervals. Five different reselection intervals were implemented including 1, 5, 10, 15, and 20.
 
-Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of the \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
-These illustrations are presented in log scale.
-Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at index 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool.
-Once again, simular illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
+                  \item The \acs{BHH} baseline configuration with different reanalysis window sizes. Five different reanalysis intervals were implemented including 1, 5, 10, 15, and 20.
 
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
-		\caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
-		\label{fig:results:case_study:thetas:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
-		\caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
-		\label{fig:results:case_study:thetas:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
-		\caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
-		\label{fig:results:case_study:thetas:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
-		\caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
-		\label{fig:results:case_study:thetas:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average sampled probabilities of \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
-The probabilities of the \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:thetas}
-\end{figure}
+                  \item The \acs{BHH} baseline configuration with different replay window sizes. Five different replay window sizes were implemented including 1, 5, 10, 15, and 20.
 
-From the illustrations presented in Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8}, a clearer picture off the learning process of the \acs{BHH} is formed.
-The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}.
-As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected probability of \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modeling.
+                  \item The \acs{BHH} baseline configuration with different burn in window sizes. Five different burn in window sizes were implemented including 0, 5, 10, 15, and 20.
 
-Towards the end of the training process, the probability of \index{heuristic}heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a probability of \index{heuristic}heuristic selection probability of 0.1, for all \index{heuristic}heuristics.
-This can be explained as follows: most of the training progress is made in the early stages of the training process, and training converges towards the end of the training process.
-Since training converges, all heuristics, no matter their past performances, fail to yield better solutions towards the end of the training process.
-As a result of training convergence, heuristics then fail to meet the performance criteria and credit allocations by means of the credit assignment strategy.
+                  \item The \acs{BHH} baseline configuration where normalisation of pseudo counts for concentration parameters, as derived from credit allocations in the performance log, are enabled and disabled.
 
-Both the bhh\_baseline (\textcolor{red}{red}) and the bhh\_replay\_250 (\textcolor{green}{green}) configurations make use of the \textit{ibest} credit assignment strategy.
-The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yield the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
-However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ gets reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.
+                  \item The \acs{BHH} baseline configuration where discounted rewards of pseudo counts for concentration parameters, as derived from credit allocations in the performance log, are enabled and disabled.
+            \end{itemize}
+\end{itemize}
 
-Another observation to make occurs in the first 30 steps of the training process.
-In Figure~\ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same probabilities of \index{heuristic}heuristic selection probabilities in these first 30 steps.
-This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number.
-This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches.
-This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.
+Each experimental group was executed against a set of fourteen datasets, consisting of regression and classification problems, split between uni- and multimodal problems.
+Each experimental group was repeated over 30 runs for statistical certainty.
+The statistical analysis process was discussed and the ANOVA, post hoc Tukey, independent T-test and Kruskal-Wallis statistical tests formed part of the statistical tests that were conducted.
 
-It should be noted that, despite using the same random seed across configurations for the same run number, after about 30 steps, the behavioural changes between the configurations start the show.
-As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing \index{heuristic}heuristics and thus, where the bhh\_baseline and bhh\_replay\_250 configurations diverge from the behaviour of the bhh\_credit\_symmetric configuration.
-The difference in behaviour is proof of the effect of performance bias.
+All experimental groups were run for a maximum of 30 epochs in order to allow for the studying of the \ac{BHH} even after training has converged and overfitting has occured.
+The maximum epoch strategy yielded a training process that is longer than what was empirically found to be necessary.
+This also meant that no early stopping strategy was used.
+Future research opportunities should incorporate an early stopping strategy of the training process.
 
-Furthermore, the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, with means not equal to the expected probabilities of \index{heuristic}heuristic selection probabilities of 0.1, observed for small windows, at various steps for multiple runs, is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations.
-This is also true for the bhh\_credit\_symmetric configuration, as the bhh\_credit\_symmetric configuration biases towards heuristics that happen to be sampled, despite not biasing towards good performance.
+\section{Summary of Results}
+\label{sec:conclusion:results}
 
-Finally, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar volatile behaviour, much more so than with the bhh\_replay\_250 configuration.
-This can be attributed to a very small reanalysis window combined with a small replay window size of 10, that contains very few samples to learn from.
-A small reanalysis interval and a small replay window size allows for more exploration of the \index{heuristic}heuristic space, but can also yield greater variance of the probabilities of \index{heuristic}heuristic selection probabilities.
-Once again, any differences then in the behaviour of the bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations and biases by the bhh\_baseline configuration.
+This section provides a summary of the results obtained from each of the experimental groups that were executed. This section is structured as follows.
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS P_H (Priors)
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{itemize}
+      \item \textbf{Section \ref{sec:conclusion:results:summary:case_study}} provides a summary of the results for the experimental group that executed a case study on the behaviour of the \acs{BHH} on an example dataset.
 
-\subsection{Prior Heuristic Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}
+      \item \textbf{Section \ref{sec:conclusion:results:summary:standalone}} provides a summary of the results for the experimental group that compares the performance of the \acs{BHH} baseline configuration with low-level, standalone \index{heuristic}heuristics, across all datasets.
 
-This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities}, that result from the probabilistic model implemented by the \acs{BHH}.
-The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
+      \item \textbf{Section \ref{sec:conclusion:results:summary:heuristic_pool}} provides a summary of the results for the experimental group that investigates the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the \acs{BHH}, across all datasets.
 
-Figures~\ref{fig:results:case_study:p_H:0}-\ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at index 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
-Similar to before, these illustrations are also presented in log scale.
+      \item \textbf{Section \ref{sec:conclusion:results:summary:population_size}} provides a summary of the results for the experimental group that investigates the effects of the \textit{population size} hyper-parameter on the \acs{BHH}, across all datasets.
 
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
-		\caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
-		\label{fig:results:case_study:p_H:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
-		\caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
-		\label{fig:results:case_study:p_H:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
-		\caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
-		\label{fig:results:case_study:p_H:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
-		\caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
-		\label{fig:results:case_study:p_H:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average sampled prior \index{heuristic}heuristic selection probabilities, given the probabilities of \index{heuristic}heuristic selection probabilities, denoted by $\boldsymbol{H}$, at indices 0, 6, 7, and 8.
-The prior \index{heuristic}heuristic selection probabilities are sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(\boldsymbol{H} \vert \theta)$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_H}
-\end{figure}
+      \item \textbf{Section \ref{sec:conclusion:results:summary:credit}} provides a summary of the results for the experimental group that investigates the effects of the \textit{credit assignment strategy} hyper-parameter on the \acs{BHH}, across all datasets.
 
-The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the probabilities of \index{heuristic}heuristic selection probabilities presented in the previous section in Figure~\ref{fig:results:case_study:thetas}.
-This is because of the \textit{reselection} interval hyper-parameter.
-The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity.
-Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10.
-These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8} for the probabilities of \index{heuristic}heuristic selection probabilities.
-As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
+      \item \textbf{Section \ref{sec:conclusion:results:summary:reselection}} provides a summary of the results for the experimental group that investigates the effects of the \textit{reselection interval} hyper-parameter on the \acs{BHH}, across all datasets.
 
-Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of \index{heuristic}heuristic performances.
-Since these prior \index{heuristic}heuristic selection probabilities change over time, it can be concluded that the change in prior \index{heuristic}heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}.
-Furthermore, the prior \index{heuristic}heuristic selection probability distribution provides an opportunity to utilise prior knowledge by some expert before training starts, by injecting heuristic selection biases, by means of the initial values for the concentration parameter $\boldsymbol{\alpha}$.
+      \item \textbf{Section \ref{sec:conclusion:results:summary:replay}} provides a summary of the results for the experimental group that investigates the effects of the \textit{replay window size} hyper-parameter on the \acs{BHH}, across all datasets.
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS P_HgEC (Posterior)
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+      \item \textbf{Section \ref{sec:conclusion:results:summary:reanalysis}} provides a summary of the results for the experimental group that investigates the effects of the \textit{reanalysis interval} hyper-parameter on the \acs{BHH}, across all datasets.
 
-\subsection{Posterior Heuristic Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}
+      \item \textbf{Section \ref{sec:conclusion:results:summary:burn_in}} provides a summary of the results for the experimental group that investigates the effects of the \textit{burn in window size} hyper-parameter on the \acs{BHH}, across all datasets.
 
-This section provides a detailed discussion on the outcomes of the \textit{posterior heuristic selection probabilities}.
-These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}.
-The posterior \index{heuristic}heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the generalised vector of credit allocation outcomes as implemented by the credit assignment strategy.
-Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probabilities of \index{heuristic}heuristic selection probabilities and probabilities of entity selection probabilities respectively.
-Finally, $\boldsymbol{\psi}$ represents the generalised form of the probabilities of successful credit allocation probabilities.
-Since this dissertation implements credit allocation operations that yield discrete, binary outcomes, $\boldsymbol{\psi}$ can be used interchangeably by $\gamma_{0}$ and $\gamma_{1}$, where $\gamma_{0}$ represents the probabilities of failed credit allocation probabilities and $\gamma_{1}$ represents the probabilities of successful credit allocation probabilities.
+      \item \textbf{Section \ref{sec:conclusion:results:summary:normalise}} provides a summary of the results for the experimental group that investigates the effects of the \textit{normalisation} hyper-parameter on the \acs{BHH}, across all datasets.
 
-Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities at index 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
-Similar to before, these illustrations are also presented in log scale.
-As before, illustrations for the other indices are left out for brevity as they yield simular illustrations.
+      \item \textbf{Section \ref{sec:conclusion:results:summary:discounted_rewards}} provides a summary of the results for the experimental group that investigates the effects of the \textit{discounted rewards} hyper-parameter on the \acs{BHH}, across all datasets.
+\end{itemize}
 
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
-		\caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
-		\label{fig:results:case_study:p_HgEC:0:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
-		\caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
-		\label{fig:results:case_study:p_HgEC:0:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
-		\caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
-		\label{fig:results:case_study:p_HgEC:0:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
-		\caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
-		\label{fig:results:case_study:p_HgEC:0:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at index 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
-The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_HgEC:0}
-\end{figure}
+\subsection{Behavioural Case Study}
+\label{sec:conclusion:results:summary:case_study}
 
-The main observation to make from Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8}, is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
-The reasons for the aforementioned, is because the probablistic model, is evaluated proportionaly as was discussed in Chapter~\ref{chap:bhh}.
-As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
+For this experimental group it was found that the \ac{BHH} is able to train a \acf{FFNN} relatively well.
+Detailed analysis was provided for various state parameters maintained by the \acs{BHH}.
+These include the concentration parameters for different heuristics, probabilities of \index{heuristic}heuristic selection probabilities, prior heuristic selection probabilities and posterior heuristic selection probabilities.
+It was shown that the \ac{BHH} is able to learn and that the \acs{BHH} is able to exploit small performance biases as it relates to \index{heuristic}heuristic selection.
+This enables the \acs{BHH} to select the correct \index{heuristic}heuristics to apply to the correct entities at the correct time in the training process.
 
-Another observation to make, is for the bhh\_replay\_250 configuration $(\textcolor{green}{green})$.
-From Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8}, it can be seen that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities, later in the training stages.
-The aforementioned suggests that the \acs{BHH} is not able to find anymore performance biases and can not exploit better solutions.
-At this point, the \acs{BHH} starts to explore more as the concentration parameters are reanalysed more uniformly, resolving more and more to a random search in attempt to find better solutions.
+Various illustrations of the train and test loss plots, as it relates to training of a \acs{FFNN} on the the iris dataset, have been provided.
+Furthermore, various illustrations on the changes of the \acs{BHH} state parameters were provided for visual aid.
 
-Furthermore, the posterior heuristic selection probability distribution is conditional on the occurance of a specific entity that the potential \index{heuristic}heuristic will be applied to, as well as a specific performance criteria enforced by a specific credit assignment strategy.
-This means that \index{heuristic}heuristic selection is specific to each entity.
-A particular \index{heuristic}heuristic might be good for one entity, but not for another.
-This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct \index{heuristic}heuristic to the correct entity at the correct time in the training process.
+The main findings that were made for this experimental group are given as follows.
+Most of the training progression is made in the early stages of the training process.
+That leads to the conclusion that the \acs{BHH} has a small window from which it should learn and gain the most in the training process.
+After training has converged, the \acs{BHH} resets its concentration parameters and heuristic selection returns to the symmetric heuristic selection case.
+As such, the \acs{BHH} explores other heuristics in an attempt to further improve on the current best solution found.
+The test set was used as a validation set during training.
+Some overfitting can be observed as the \acs{BHH} tried finding better solutions on the train set, but at the cost of generalisation on the test set.
+Minor divergence of the training loss is observed as the \acs{BHH} explores other heuristics in an attempt to improve performance.
+Since no move acceptance strategy, and no early stopping stategy was used, the \acs{BHH} could select heuristics that are sub-optimal.
+Future research opportunities should incorporate these aforementioned strategies.
 
-Finally, the posterior heuristic selection probabilities are much less volatile than their prior heuristic selection probability equivalents.
-This is a result of the information that is added in the performance log by tracking the entity and credit allocation as well.
+\subsection{\acs{BHH} Baseline vs. Low-Level Heuristics}
+\label{sec:conclusion:results:summary:standalone}
 
-From the observations made in Sections~\ref{sec:results:case_study:performance_metrics}-\ref{sec:results:case_study:posterior_selec_prob}, it can be concluded that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset.
-Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases and thus, the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.
+For this experimental group, three different configurations of the \acs{BHH} baseline configuration were implemented.
+These configurations vary in the type of \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool.
+The \textit{bhh\_all} configuration included all low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool.
+The \textit{bhh\_gd} configuration included only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the \textit{bhh\_mh} configuration included only \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-% BHH vs. Low-Level Heuristics
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\section{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
+Overall the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen \index{heuristic}heuristics that were implemented and executed on fourteen datasets.
+The \textit{bhh\_gd} configuration produced performance results close to that of the best low-level \index{heuristic}heuristics and was only statistically outperformed by the top two low-level \index{heuristic}heuristics.
+The \textit{bhh\_all} configuration achieved an overall rank of sixth and the \textit{bhh\_mh} achieved an overall rank of eighth.
 
-This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics.
-Detailed discussions and illustrations follow.
-As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of meta-heuristics.
-Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics (denoted bhh\_mh).
+Although the \textit{bhh\_gd} configuration produced performance results comparable to the best low-level heuristics, the \textit{bhh\_all} and \textit{bhh\_mh} configurations produced average results.
+It was found that, in general, gradient-based heuristics produced the best results, as such, it it understandable that the \textit{bhh\_gd}  yielded the best performance outcomes between the different \acs{BHH} variants that were implemented.
+Although the \acs{BHH} variants were not able to produce better results than the top low-level \index{heuristic}heuristics, the \acs{BHH} variants still effectively trained the underlying \acp{FFNN} and produced good training outcomes overall.
 
-Table~\ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
+It was shown that the \textit{bhh\_gd} configuration produced the lowest variance in rank between datasets out of all of the \index{heuristic}heuristics implemented, giving the \acs{BHH} the ability to generalise well to other problems.
 
-\begin{sidewaystable}[htbp]
-	\centering
-	\caption{Empirical results showing test loss and statistics for different low-level \index{heuristic}heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs, measured at the last epoch.}
-	\label{tab:results:standalone:metrics:loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|lll|l|l|l|l|l|lllll}
-			                                    & \multicolumn{13}{c}{\textbf{BHH vs.
-Low-Level Heuristics - Average Test Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
-			\cmidrule{2-14}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                           & \multicolumn{1}{c}{\textbf{adam}}                       & \multicolumn{1}{c|}{\textbf{rmsprop}}                   & \multicolumn{1}{c|}{\textbf{bhh\_gd}}                   & \multicolumn{1}{c|}{\textbf{nag}}                       & \multicolumn{1}{c|}{\textbf{bhh\_all}}                  & \multicolumn{1}{c|}{\textbf{adadelta}}                  & \multicolumn{1}{c|}{\textbf{bhh\_mh}}                   & \multicolumn{1}{c}{\textbf{ga}}                         & \multicolumn{1}{c}{\textbf{pso}}                        & \multicolumn{1}{c}{\textbf{sgd}}                        & \multicolumn{1}{c}{\textbf{momentum}}                   & \multicolumn{1}{c}{\textbf{de}}                         \\
-			\midrule
-			\textbf{abalone}                    & \cellcolor[rgb]{ .506,  .776,  .486}1.9678 ($\pm$0.032)                        & \cellcolor[rgb]{ .494,  .773,  .486}1.9651 ($\pm$0.035) & \cellcolor[rgb]{ .388,  .745,  .482}1.9455 ($\pm$0.035) & \cellcolor[rgb]{ .749,  .847,  .502}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .765,  .851,  .502}2.0156 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .788,  .859,  .502}2.0199 ($\pm$0.034) & \cellcolor[rgb]{ .996,  .827,  .502}2.2942 ($\pm$0.055) & \cellcolor[rgb]{ .984,  .612,  .459}2.8155 ($\pm$0.055) & \cellcolor[rgb]{ .98,  .522,  .443}3.0384 ($\pm$0.294)  & \cellcolor[rgb]{ .992,  .773,  .49}2.428 ($\pm$0.029)   & \cellcolor[rgb]{ .992,  .745,  .486}2.4942 ($\pm$0.029) & \cellcolor[rgb]{ .973,  .412,  .42}3.2959 ($\pm$0.016)  \\
-			\textbf{air quality}                & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                         & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\
-			\textbf{bank}                       & \cellcolor[rgb]{ .459,  .765,  .486}0.2096 ($\pm$0.005)                        & \cellcolor[rgb]{ .4,  .745,  .482}0.2065 ($\pm$0.004)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2058 ($\pm$0.006) & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.005)    & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .886,  .514}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .627,  .812,  .494}0.2186 ($\pm$0.004) & \cellcolor[rgb]{ .996,  .839,  .502}0.2562 ($\pm$0.011) & \cellcolor[rgb]{ .988,  .686,  .475}0.2881 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.3454 ($\pm$0.034)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2382 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2386 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .424,  .424}0.3437 ($\pm$0.028) \\
-			\textbf{bike}                       & \cellcolor[rgb]{ .388,  .745,  .482}0.0458 ($\pm$0.002)                        & \cellcolor[rgb]{ .592,  .804,  .494}0.0682 ($\pm$0.068) & \cellcolor[rgb]{ 1,  .922,  .518}0.1123 ($\pm$0.103)    & \cellcolor[rgb]{ .467,  .765,  .486}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .882,  .886,  .51}0.0995 ($\pm$0.002)  & \cellcolor[rgb]{ .565,  .796,  .49}0.0651 ($\pm$0.02)   & \cellcolor[rgb]{ .588,  .8,  .49}0.0679 ($\pm$0.002)    & \cellcolor[rgb]{ 1,  .902,  .514}0.1179 ($\pm$0.006)    & \cellcolor[rgb]{ .992,  .761,  .486}0.1531 ($\pm$0.005) & \cellcolor[rgb]{ .992,  .773,  .49}0.1503 ($\pm$0.025)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1599 ($\pm$0.003) & \cellcolor[rgb]{ .992,  .725,  .482}0.1614 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.2399 ($\pm$0.04)   \\
-			\textbf{car}                        & \cellcolor[rgb]{ .729,  .843,  .502}0.2027 ($\pm$0.018)                        & \cellcolor[rgb]{ .388,  .745,  .482}0.0972 ($\pm$0.024) & \cellcolor[rgb]{ .408,  .749,  .482}0.1039 ($\pm$0.031) & \cellcolor[rgb]{ .62,  .812,  .494}0.169 ($\pm$0.025)   & \cellcolor[rgb]{ .867,  .882,  .51}0.2454 ($\pm$0.029)  & \cellcolor[rgb]{ .58,  .8,  .49}0.1572 ($\pm$0.034)     & \cellcolor[rgb]{ 1,  .922,  .518}0.2859 ($\pm$0.027)    & \cellcolor[rgb]{ .992,  .733,  .482}0.4891 ($\pm$0.077) & \cellcolor[rgb]{ .98,  .502,  .439}0.7374 ($\pm$0.063)  & \cellcolor[rgb]{ .988,  .667,  .471}0.5632 ($\pm$0.158) & \cellcolor[rgb]{ .98,  .533,  .443}0.7035 ($\pm$0.052)  & \cellcolor[rgb]{ .98,  .506,  .439}0.7322 ($\pm$0.043)  & \cellcolor[rgb]{ .973,  .412,  .42}0.8332 ($\pm$0.074)  \\
-			\textbf{diabetic}                   & \cellcolor[rgb]{ .694,  .831,  .498}0.8895 ($\pm$0.004)                        & \cellcolor[rgb]{ 1,  .898,  .514}0.9193 ($\pm$0.01)     & \cellcolor[rgb]{ .918,  .894,  .51}0.8957 ($\pm$0.004)  & \cellcolor[rgb]{ .98,  .914,  .514}0.8976 ($\pm$0.011)  & \cellcolor[rgb]{ .388,  .745,  .482}0.8809 ($\pm$0.004) & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)   & \cellcolor[rgb]{ .49,  .773,  .486}0.8839 ($\pm$0.005)  & \cellcolor[rgb]{ 1,  .902,  .518}0.9137 ($\pm$0.008)    & \cellcolor[rgb]{ .996,  .843,  .506}0.9613 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .835,  .502}0.9661 ($\pm$0.016) & \cellcolor[rgb]{ .976,  .914,  .514}0.8974 ($\pm$0.004) & \cellcolor[rgb]{ 1,  .922,  .518}0.898 ($\pm$0.003)     & \cellcolor[rgb]{ .988,  .694,  .475}1.0774 ($\pm$0.039) \\
-			\textbf{fish toxicity}              & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                           & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
-			\textbf{forest fires}               & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                            & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\
-			\textbf{housing}                    & \cellcolor[rgb]{ .518,  .78,  .486}0.0889 ($\pm$0.012)                         & \cellcolor[rgb]{ .404,  .749,  .482}0.0848 ($\pm$0.011) & \cellcolor[rgb]{ .388,  .745,  .482}0.0842 ($\pm$0.015) & \cellcolor[rgb]{ .69,  .831,  .498}0.0951 ($\pm$0.015)  & \cellcolor[rgb]{ .612,  .808,  .494}0.0923 ($\pm$0.016) & \cellcolor[rgb]{ .663,  .824,  .498}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.106 ($\pm$0.019)     & \cellcolor[rgb]{ 1,  .867,  .51}0.1169 ($\pm$0.019)     & \cellcolor[rgb]{ .996,  .812,  .498}0.1279 ($\pm$0.02)  & \cellcolor[rgb]{ .992,  .722,  .482}0.1452 ($\pm$0.03)  & \cellcolor[rgb]{ .984,  .576,  .455}0.1735 ($\pm$0.023) & \cellcolor[rgb]{ .984,  .588,  .455}0.1713 ($\pm$0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.2057 ($\pm$0.036)  \\
-			\textbf{iris}                       & \cellcolor[rgb]{ .788,  .859,  .502}0.2161 ($\pm$0.059)                        & \cellcolor[rgb]{ .514,  .78,  .486}0.1203 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0753 ($\pm$0.046) & \cellcolor[rgb]{ 1,  .855,  .506}0.3729 ($\pm$1.119)    & \cellcolor[rgb]{ .416,  .753,  .482}0.085 ($\pm$0.042)  & \cellcolor[rgb]{ .859,  .878,  .506}0.2411 ($\pm$0.295) & \cellcolor[rgb]{ .996,  .808,  .498}0.426 ($\pm$0.072)  & \cellcolor[rgb]{ .686,  .831,  .498}0.1809 ($\pm$0.164) & \cellcolor[rgb]{ 1,  .922,  .518}0.2895 ($\pm$0.117)    & \cellcolor[rgb]{ .973,  .412,  .42}0.8965 ($\pm$0.844)  & \cellcolor[rgb]{ .992,  .773,  .49}0.4694 ($\pm$0.088)  & \cellcolor[rgb]{ .992,  .745,  .486}0.5028 ($\pm$0.072) & \cellcolor[rgb]{ .98,  .494,  .435}0.8027 ($\pm$0.684)  \\
-			\textbf{mushroom}                   & \cellcolor[rgb]{ .549,  .792,  .49}0.0026 ($\pm$0.001)                         & \cellcolor[rgb]{ .467,  .765,  .486}0.0013 ($\pm$0.005) & \cellcolor[rgb]{ .388,  .745,  .482}0.0001 ($\pm$0)     & \cellcolor[rgb]{ .439,  .757,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ 1,  .922,  .518}0.0094 ($\pm$0.002)    & \cellcolor[rgb]{ .718,  .839,  .498}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ .655,  .82,  .494}0.0042 ($\pm$0.001)  & \cellcolor[rgb]{ 1,  .871,  .51}0.0774 ($\pm$0.02)      & \cellcolor[rgb]{ .984,  .561,  .451}0.4892 ($\pm$0.025) & \cellcolor[rgb]{ 1,  .886,  .514}0.0611 ($\pm$0.06)     & \cellcolor[rgb]{ .996,  .796,  .494}0.1797 ($\pm$0.009) & \cellcolor[rgb]{ .992,  .749,  .486}0.2418 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.687 ($\pm$0.016)   \\
-			\textbf{parkinsons}                 & \cellcolor[rgb]{ .51,  .776,  .486}0.0563 ($\pm$0.001)                         & \cellcolor[rgb]{ .412,  .749,  .482}0.0545 ($\pm$0.002) & \cellcolor[rgb]{ .388,  .745,  .482}0.054 ($\pm$0.002)  & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0655 ($\pm$0.002)    & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .69,  .831,  .498}0.0597 ($\pm$0.002)  & \cellcolor[rgb]{ 1,  .918,  .518}0.0658 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .898,  .514}0.0669 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .894,  .514}0.0671 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .467,  .431}0.0923 ($\pm$0.008) & \cellcolor[rgb]{ .973,  .412,  .42}0.0954 ($\pm$0.009)  & \cellcolor[rgb]{ .984,  .604,  .459}0.0843 ($\pm$0.009) \\
-			\textbf{student performance}        & \cellcolor[rgb]{ .388,  .745,  .482}0.1656 ($\pm$0.011)                        & \cellcolor[rgb]{ .98,  .522,  .443}0.4929 ($\pm$0.105)  & \cellcolor[rgb]{ .973,  .412,  .42}0.5724 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .855,  .506}0.2454 ($\pm$0.134)    & \cellcolor[rgb]{ .471,  .769,  .486}0.1697 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .871,  .51}0.2359 ($\pm$0.102)     & \cellcolor[rgb]{ .49,  .773,  .486}0.1708 ($\pm$0.01)   & \cellcolor[rgb]{ .969,  .91,  .514}0.1947 ($\pm$0.014)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1962 ($\pm$0.01)     & \cellcolor[rgb]{ .984,  .573,  .451}0.4565 ($\pm$0.049) & \cellcolor[rgb]{ .933,  .902,  .514}0.193 ($\pm$0.011)  & \cellcolor[rgb]{ .925,  .898,  .51}0.1925 ($\pm$0.011)  & \cellcolor[rgb]{ 1,  .918,  .518}0.2014 ($\pm$0.012)    \\
-			\textbf{wine quality}               & \cellcolor[rgb]{ .631,  .816,  .494}1.0651 ($\pm$0.024)                        & \cellcolor[rgb]{ .388,  .745,  .482}1.0395 ($\pm$0.018) & \cellcolor[rgb]{ .502,  .776,  .486}1.0514 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .698,  .831,  .498}1.0718 ($\pm$0.025) & \cellcolor[rgb]{ .804,  .863,  .506}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .788,  .859,  .502}1.0809 ($\pm$0.021) & \cellcolor[rgb]{ .996,  .839,  .502}1.1666 ($\pm$0.03)  & \cellcolor[rgb]{ .992,  .725,  .482}1.2516 ($\pm$0.046) & \cellcolor[rgb]{ .988,  .659,  .467}1.3046 ($\pm$0.114) & \cellcolor[rgb]{ .996,  .843,  .502}1.1648 ($\pm$0.023) & \cellcolor[rgb]{ .996,  .824,  .502}1.1774 ($\pm$0.019) & \cellcolor[rgb]{ .973,  .412,  .42}1.4896 ($\pm$0.093)  \\
-			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
-	}
-\end{sidewaystable}%
+Furthermore, it was shown that the \acs{BHH} provides a mechanism whereby prior expert knowledge can be injected, before training starts.
+Future research can exploit this knowledge and provide a significant bias towards \index{heuristic}heuristics that are known to perform well on particular problem types.
 
-From Table~\ref{tab:results:standalone:metrics:loss} it can be seen that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
-The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.
+\subsection{Heuristic pool}
+\label{sec:conclusion:results:summary:heuristic_pool}
 
-Table~\ref{tab:results:standalone:metrics:rank} provides the empirical results from Table~\ref{tab:results:standalone:metrics:loss} in ranked format.
-The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, across all datasets, for all indepented runs and all epochs.
-The average rank across all epochs produces a view on the performance of the \index{heuristic}heuristics as it relates to the entire training process.
-Finally, a normalised average rank is provided for the overall performance of all \index{heuristic}heuristics at the bottom of the table.
-The normalised average rank is calculated as a discrete normalisation of the average rank achieved across all datasets, for all independent runs and epochs.
+For this experimental group, the same three \index{heuristic pool}heuristical pool variants, as outlined for the \acs{BHH} behavioural case study, was implemented.
+These variants are denoted as \textit{all}, \textit{gd}, and \textit{mh}.
+This experimental group then provided an opportunity to look at the effects of the \index{heuristic pool}heuristic pool hyper-parameter in more detail.
 
-\begin{sidewaystable}[htbp]
-	\centering
-	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:standalone:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccc|c|c|c|c|c|ccccc}
-			                             & \multicolumn{13}{c}{\textbf{BHH vs.
-Low-Level Heuristics - Average Rank (Based on Test Loss)}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\
-			\textbf{dataset}             & \textbf{adagrad}                                                                               & \textbf{adam}                                           & \textbf{rmsprop}                                        & \textbf{bhh\_gd}                                        & \textbf{nag}                                            & \textbf{bhh\_all}                                       & \textbf{adadelta}                                       & \textbf{bhh\_mh}                                        & \textbf{ga}                                              & \textbf{pso}                                             & \textbf{sgd}                                             & \textbf{momentum}                                        & \textbf{de}                                              \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.2215 ($\pm$1.591)                                        & \cellcolor[rgb]{ .416,  .753,  .482}2.3989 ($\pm$1.887) & \cellcolor[rgb]{ .78,  .859,  .502}4.6172 ($\pm$2.65)   & \cellcolor[rgb]{ .796,  .863,  .506}4.7032 ($\pm$2.108) & \cellcolor[rgb]{ .725,  .839,  .498}4.2731 ($\pm$1.542) & \cellcolor[rgb]{ 1,  .922,  .518}5.9376 ($\pm$2.399)    & \cellcolor[rgb]{ .894,  .89,  .51}5.3129 ($\pm$1.478)   & \cellcolor[rgb]{ .992,  .749,  .486}8.1882 ($\pm$1.195) & \cellcolor[rgb]{ .98,  .525,  .443}11.1108 ($\pm$1.102)  & \cellcolor[rgb]{ .98,  .514,  .439}11.2559 ($\pm$1.826)  & \cellcolor[rgb]{ .992,  .718,  .478}8.628 ($\pm$1.019)   & \cellcolor[rgb]{ .984,  .624,  .463}9.8151 ($\pm$1.16)   & \cellcolor[rgb]{ .973,  .412,  .42}12.5376 ($\pm$1.329)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                                        & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .455,  .765,  .486}2.5495 ($\pm$1.598)                                        & \cellcolor[rgb]{ .388,  .745,  .482}2.0796 ($\pm$1.587) & \cellcolor[rgb]{ .588,  .8,  .49}3.4645 ($\pm$2.209)    & \cellcolor[rgb]{ .8,  .863,  .506}4.8828 ($\pm$1.702)   & \cellcolor[rgb]{ .71,  .835,  .498}4.2871 ($\pm$1.732)  & \cellcolor[rgb]{ 1,  .922,  .518}6.2419 ($\pm$2.157)    & \cellcolor[rgb]{ .914,  .894,  .51}5.672 ($\pm$1.241)   & \cellcolor[rgb]{ .988,  .639,  .463}9.7495 ($\pm$1.048) & \cellcolor[rgb]{ .98,  .537,  .447}10.9817 ($\pm$1.216)  & \cellcolor[rgb]{ .976,  .467,  .431}11.8376 ($\pm$1.464) & \cellcolor[rgb]{ .992,  .757,  .486}8.2774 ($\pm$1.03)   & \cellcolor[rgb]{ .992,  .741,  .486}8.4774 ($\pm$1.068)  & \cellcolor[rgb]{ .973,  .412,  .42}12.4989 ($\pm$1.224)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}1.7204 ($\pm$1.384)                                        & \cellcolor[rgb]{ .643,  .816,  .494}3.6925 ($\pm$4.004) & \cellcolor[rgb]{ .973,  .914,  .514}6.2624 ($\pm$4.58)  & \cellcolor[rgb]{ .663,  .824,  .498}3.8441 ($\pm$1.398) & \cellcolor[rgb]{ 1,  .922,  .518}6.4516 ($\pm$1.02)     & \cellcolor[rgb]{ .71,  .835,  .498}4.2151 ($\pm$1.361)  & \cellcolor[rgb]{ .859,  .878,  .506}5.3602 ($\pm$1.155) & \cellcolor[rgb]{ .996,  .843,  .506}7.4108 ($\pm$1.008) & \cellcolor[rgb]{ .988,  .686,  .475}9.2269 ($\pm$1.183)  & \cellcolor[rgb]{ .988,  .682,  .475}9.3086 ($\pm$1.761)  & \cellcolor[rgb]{ .984,  .596,  .455}10.3355 ($\pm$1.419) & \cellcolor[rgb]{ .984,  .561,  .451}10.7086 ($\pm$1.423) & \cellcolor[rgb]{ .973,  .412,  .42}12.4634 ($\pm$1.465)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .702,  .835,  .498}4.7634 ($\pm$0.938)                                        & \cellcolor[rgb]{ .388,  .745,  .482}1.6226 ($\pm$1.405) & \cellcolor[rgb]{ .455,  .765,  .486}2.3269 ($\pm$1.409) & \cellcolor[rgb]{ .561,  .792,  .49}3.3473 ($\pm$1.35)   & \cellcolor[rgb]{ .831,  .871,  .506}6.0785 ($\pm$0.799) & \cellcolor[rgb]{ .58,  .8,  .49}3.5624 ($\pm$1.315)     & \cellcolor[rgb]{ 1,  .922,  .518}7.7344 ($\pm$1.746)    & \cellcolor[rgb]{ .996,  .8,  .498}8.8505 ($\pm$1.413)   & \cellcolor[rgb]{ .984,  .592,  .455}10.7763 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .855,  .506}8.3613 ($\pm$1.622)     & \cellcolor[rgb]{ .988,  .651,  .467}10.2452 ($\pm$1.447) & \cellcolor[rgb]{ .984,  .576,  .451}10.9226 ($\pm$1.349) & \cellcolor[rgb]{ .973,  .412,  .42}12.4086 ($\pm$1.492)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .506,  .776,  .486}2.7796 ($\pm$1.659)                                        & \cellcolor[rgb]{ 1,  .886,  .514}7.1484 ($\pm$2.227)    & \cellcolor[rgb]{ 1,  .922,  .518}6.7376 ($\pm$2.577)    & \cellcolor[rgb]{ .812,  .867,  .506}5.2269 ($\pm$2.186) & \cellcolor[rgb]{ .388,  .745,  .482}1.8118 ($\pm$1.413) & \cellcolor[rgb]{ .988,  .69,  .475}9.3968 ($\pm$3.022)  & \cellcolor[rgb]{ .494,  .773,  .486}2.6753 ($\pm$1.629) & \cellcolor[rgb]{ .992,  .765,  .49}8.557 ($\pm$1.17)    & \cellcolor[rgb]{ .98,  .529,  .443}11.2011 ($\pm$1.413)  & \cellcolor[rgb]{ .984,  .573,  .451}10.7022 ($\pm$1.067) & \cellcolor[rgb]{ .898,  .89,  .51}5.9215 ($\pm$1.542)    & \cellcolor[rgb]{ .949,  .906,  .514}6.3355 ($\pm$1.612)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5065 ($\pm$1.242)  \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                                         & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                                        & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\
-			\textbf{housing}             & \cellcolor[rgb]{ .404,  .749,  .482}3.4484 ($\pm$2.025)                                        & \cellcolor[rgb]{ .388,  .745,  .482}3.3344 ($\pm$1.819) & \cellcolor[rgb]{ .439,  .757,  .482}3.6946 ($\pm$2.166) & \cellcolor[rgb]{ .553,  .792,  .49}4.4742 ($\pm$2.312)  & \cellcolor[rgb]{ .584,  .8,  .49}4.6839 ($\pm$2.658)    & \cellcolor[rgb]{ .537,  .788,  .49}4.3763 ($\pm$2.438)  & \cellcolor[rgb]{ 1,  .918,  .518}7.5903 ($\pm$2.748)    & \cellcolor[rgb]{ 1,  .922,  .518}7.5441 ($\pm$1.736)    & \cellcolor[rgb]{ 1,  .878,  .51}7.8839 ($\pm$2.099)      & \cellcolor[rgb]{ .984,  .608,  .459}9.9409 ($\pm$2.317)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4075 ($\pm$1.528)  & \cellcolor[rgb]{ .976,  .431,  .424}11.2731 ($\pm$1.506) & \cellcolor[rgb]{ .976,  .42,  .424}11.3484 ($\pm$2.096)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .965,  .91,  .514}6.3946 ($\pm$1.6)                                           & \cellcolor[rgb]{ .525,  .784,  .49}3.5839 ($\pm$2.511)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6968 ($\pm$1.912) & \cellcolor[rgb]{ .706,  .835,  .498}4.7473 ($\pm$2.275) & \cellcolor[rgb]{ .522,  .78,  .486}3.5548 ($\pm$2.125)  & \cellcolor[rgb]{ .78,  .859,  .502}5.2204 ($\pm$3.041)  & \cellcolor[rgb]{ .973,  .412,  .42}11.3527 ($\pm$1.779) & \cellcolor[rgb]{ 1,  .922,  .518}6.6075 ($\pm$2.555)    & \cellcolor[rgb]{ .992,  .749,  .486}8.2473 ($\pm$1.765)  & \cellcolor[rgb]{ .992,  .745,  .486}8.2731 ($\pm$4.384)  & \cellcolor[rgb]{ .98,  .518,  .443}10.3796 ($\pm$1.294)  & \cellcolor[rgb]{ .976,  .447,  .427}11.0548 ($\pm$1.409) & \cellcolor[rgb]{ .988,  .678,  .471}8.8871 ($\pm$3.251)  \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .71,  .835,  .498}4.4656 ($\pm$1.053)                                         & \cellcolor[rgb]{ .388,  .745,  .482}2.1344 ($\pm$1.883) & \cellcolor[rgb]{ .431,  .757,  .482}2.4656 ($\pm$1.359) & \cellcolor[rgb]{ .569,  .796,  .49}3.4484 ($\pm$1.602)  & \cellcolor[rgb]{ .969,  .91,  .514}6.3323 ($\pm$0.891)  & \cellcolor[rgb]{ .6,  .804,  .494}3.6688 ($\pm$2.469)   & \cellcolor[rgb]{ 1,  .922,  .518}6.5538 ($\pm$1.071)    & \cellcolor[rgb]{ .992,  .718,  .478}9.0452 ($\pm$1.093) & \cellcolor[rgb]{ .98,  .51,  .439}11.5731 ($\pm$1.193)   & \cellcolor[rgb]{ .996,  .816,  .498}7.872 ($\pm$0.92)    & \cellcolor[rgb]{ .988,  .659,  .471}9.7527 ($\pm$1.083)  & \cellcolor[rgb]{ .98,  .557,  .451}10.9785 ($\pm$1.108)  & \cellcolor[rgb]{ .973,  .412,  .42}12.7097 ($\pm$1.478)  \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .412,  .749,  .482}2.4677 ($\pm$1.497)                                        & \cellcolor[rgb]{ .388,  .745,  .482}2.2333 ($\pm$1.742) & \cellcolor[rgb]{ .541,  .788,  .49}3.5656 ($\pm$2.492)  & \cellcolor[rgb]{ .655,  .82,  .494}4.572 ($\pm$1.934)   & \cellcolor[rgb]{ 1,  .922,  .518}7.5355 ($\pm$1.44)     & \cellcolor[rgb]{ .635,  .816,  .494}4.3839 ($\pm$1.861) & \cellcolor[rgb]{ .875,  .882,  .51}6.472 ($\pm$2.423)   & \cellcolor[rgb]{ .996,  .843,  .506}8.3161 ($\pm$1.644) & \cellcolor[rgb]{ 1,  .898,  .514}7.7968 ($\pm$1.719)     & \cellcolor[rgb]{ .996,  .827,  .502}8.4892 ($\pm$1.901)  & \cellcolor[rgb]{ .98,  .494,  .435}11.7516 ($\pm$1.155)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5419 ($\pm$1.351)  & \cellcolor[rgb]{ .984,  .584,  .455}10.8742 ($\pm$1.317) \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                                        & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                                         & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}3.5512 ($\pm$2.25)                                         & \cellcolor[rgb]{ .471,  .769,  .486}3.9314 ($\pm$3.423) & \cellcolor[rgb]{ .616,  .808,  .494}4.5691 ($\pm$3.517) & \cellcolor[rgb]{ .631,  .812,  .494}4.6346 ($\pm$2.364) & \cellcolor[rgb]{ .675,  .827,  .498}4.8394 ($\pm$2.384) & \cellcolor[rgb]{ .808,  .867,  .506}5.4327 ($\pm$2.9)   & \cellcolor[rgb]{ 1,  .922,  .518}6.2727 ($\pm$3.004)    & \cellcolor[rgb]{ .992,  .776,  .49}7.7855 ($\pm$2.271)  & \cellcolor[rgb]{ .988,  .639,  .467}9.1522 ($\pm$2.48)   & \cellcolor[rgb]{ .984,  .612,  .459}9.4451 ($\pm$2.75)   & \cellcolor[rgb]{ .984,  .592,  .455}9.6445 ($\pm$2.214)  & \cellcolor[rgb]{ .98,  .529,  .443}10.2877 ($\pm$2.346)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4538 ($\pm$2.354)  \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                                                          & \cellcolor[rgb]{ .49,  .773,  .486}2                    & \cellcolor[rgb]{ .592,  .804,  .494}3                   & \cellcolor[rgb]{ .694,  .831,  .498}4                   & \cellcolor[rgb]{ .796,  .863,  .506}5                   & \cellcolor[rgb]{ .898,  .89,  .51}6                     & \cellcolor[rgb]{ 1,  .922,  .518}7                      & \cellcolor[rgb]{ .996,  .839,  .502}8                   & \cellcolor[rgb]{ .992,  .753,  .486}9                    & \cellcolor[rgb]{ .988,  .667,  .471}10                   & \cellcolor[rgb]{ .984,  .584,  .455}11                   & \cellcolor[rgb]{ .98,  .498,  .439}12                    & \cellcolor[rgb]{ .973,  .412,  .42}13                    \\
-			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
+As with the experimental group that compares the performance of the \acs{BHH} baseline configuration with low-level, standalone \index{heuristic}heuristics, it was found that the \textit{gd} configuration performed significantly better than the \textit{all} and \textit{mh} configurations overall, across all datasets.
 
-	}
-\end{sidewaystable}%
+The benefits of using meta-heuristics in the heuristic pool was not realised in this dissertation, since the gradient-based low-level \index{heuristic}heuristics, as well as the \textit{gd} configuration produced the best overall performance, across all datasets.
 
-From the normalised average ranks provided in Table~\ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eigth amongst all thirteen \index{heuristic}heuristic implementations respectively.
-These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.
+\subsection{Population Size}
+\label{sec:conclusion:results:summary:population_size}
 
-Figure~\ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each \index{heuristic}heuristic, per dataset.
-The heuristics are ordered according to the normalised ranks presented in Table~\ref{tab:results:standalone:metrics:rank}.
+For this experimental group, five different population sizes were evaluated.
+These included population sizes of 5, 10, 15, 20, and 25.
+It was found that lower population sizes yielded better results on the majority of datasets, while only some datasets prefer larger population sizes.
+However, overall it was shown that the population size hyper-parameter is problem specific.
+Illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
+Some divergence in training loss was observed and was attributed to selection of \index{heuristic}heuristics that yield sub-optimal results after an optimal solution has already been found.
+As before, a move acceptance strategy and an early stopping strategy can be incorporated to avoid this effect.
 
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all independent runs and epochs.}
-	\label{fig:results:standalone:descriptive:descriptive}
-\end{figure}
+\subsection{Credit Assignment Strategy}
+\label{sec:conclusion:results:summary:credit}
 
-From Figure~\ref{fig:results:standalone:descriptive:descriptive} a few observations can be made.
-Firstly, both \acs{Adam} and \acs{RMSProp} achieved radically different average ranks for the student performance dataset, compared to the other datasets.
-This can also be see in Table~\ref{tab:results:standalone:metrics:rank}.
-Further investigation into the reasons for this is required as both these heuristics perform well on all other datasets, and the other heuristics perform well for the student performance dataset.
-A suggestions then leads to the possibility that an invalid learning rate or learning rate schedule leads to a scenario where good solutions are overshot, causing \acs{Adam} and \acs{RMSProp} to struggle to resolve back to good solutions.
-Furthermore, the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
-The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.
+For this experimental group, five different credit assignment strategies were evaluated.
+These included the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies.
+No clear overall difference in performance was observed for the various credit assignment strategies.
+In the majority of cases, a particular non-symmetric credit assignment strategy yielded the best performance, while the \textit{symmetric} credit assignment strategy yielded the best performance results in one case.
+It can therefore be concluded that the credit assignment strategy is problem specific.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-Figure~\ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic}heuristic as it relates to all datasets, across all independent runs and epochs.
+\subsection{Reselection Interval}
+\label{sec:conclusion:results:summary:reselection}
 
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of all low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
-	\label{fig:results:standalone:descriptive:cd}
-\end{figure}
+For this experimental group, five different reselection intervals were evaluated.
+These included reselection intervals of 1, 5, 10, 15, and 20.
+Overall, with statistical significance, it was found that a larger reselection interval is generally preferred.
+It was found that larger reselection intervals lead to longer timeframes for the low-level heuristics to progress, smoothing out update steps.
+Larger reselection intervals also allow the \acs{BHH} to collect more samples of \index{heuristic}heuristic performance evidence from which it can learn.
+Therefore, a conclusion that can be made is that \index{heuristic}heuristic and solution exploitation is preferred over exploration.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all \index{heuristic}heuristics is very small.
-Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, was statistically only outperformed overall by \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}.
-It should be noted that the standalone low-level \index{heuristic} \index{heuristic}heuristics already produce good results in general across all datasets.
-In this particular case, producing better performance outcomes can be hard to achieve.
-However, as mentioned previously, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.
+\subsection{Replay}
+\label{sec:conclusion:results:summary:replay}
 
-Another observation that can be made is that the gradient-based \index{heuristic}heuristics generally performed much better than the \index{meta-heuristic}meta-heuristics on all datasets.
-State of the art methods for training \acp{FFNN}, such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions~\cite{ref:kingma:2014}.
-Exploration of the \index{heuristic}heuristic space leads the \acs{BHH} to consider other \index{heuristic}heuristics during the training process, which could possibly result in worse performances at times.
-As previously mentioned, a suggestion to improve on these results is to include a move-acceptance strategy, where heuristic progressions are discarded if they fail to produce better results.
+For this experimental group, five different replay windows sizes were evaluated.
+These included replay window sizes of 1, 5, 10, 15, and 20.
+Overall, no statistically significant difference was found for the performance of the replay window size configurations, and thus, it was concluded that the replay window size is problem specific, with some datasets preferring short memory and other preferring long memory.
+The relationship between the reselection interval, replay window size and reanalysis interval was discussed, and it was shown that these hyper-parameters should be considered together.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-Figures~\ref{fig:results:standalone:figures:iris}-\ref{fig:results:standalone:figures:bank} provide example illustrations of the train and test, loss and accuracy plots for each heuristic as it relates to a selection of classification datasets.
-The train and test, loss and accuracy plots provided are illustrated in log scale.
-The other classification datasets are left out for brevity as they produce similar illustrations.
+\subsection{Reanalysis Interval}
+\label{sec:conclusion:results:summary:reanalysis}
 
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/iris.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:iris}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/iris.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:iris}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/iris.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:iris}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/iris.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:iris}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:iris}
-\end{figure}
+For this experimental group, five different reanalysis intervals were evaluated.
+These included reanalysis intervals of 1, 5, 10, 15, and 20.
+Overall, no statistically significant difference was found for the performance of the reanalysis intervals across all datasets, and thus, it was concluded that the reanalysis interval is problem specific.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the car dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:car}
-\end{figure}
+\subsection{Burn In}
+\label{sec:conclusion:results:summary:burn_in}
 
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/bank.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/bank.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/bank.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/bank.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:bank}
-\end{figure}
+For this experimental group, five different burn in window sizes were evaluated.
+These included burn in window sizes of 1, 5, 10, 15, and 20.
+Overall, it was found with statistical significance, that lower burn in window sizes are generally preferred.
+The lower burn in window sizes generally produced the best results in the majority of cases, with some exceptions that prefer average burn in window sizes.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-Figures~\ref{fig:results:standalone:figures:fish_toxicity}-\ref{fig:results:standalone:figures:parkinsons} provide example illustrations of the train and test loss plots for each heuristic as it relates to a selection of regression datasets.
-The train and test loss plots provided are illustrated in log scale.
-Similar to before, the other regression datasets are left out for brevity as they produce similar illustrations.
+\subsection{Normalisation}
+\label{sec:conclusion:results:summary:normalise}
 
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/fish_toxicity.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:fish_toxicity}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/fish_toxicity.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:fish_toxicity}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:fish_toxicity}
-\end{figure}
+For this experimental group an empirical test was conducted to determine the effects of normalisation of pseudo counts allocated by the credit assignment strategy in the performance log.
+A configuration is included with normalisation enabled and a configuration is included with normalisation disabled.
+It was concluded that the default replay window size of ten is too small to yield a significant difference in performance outcome for when normalisation is enabled compared to when normalisation is disabled.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/parkinsons.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:parkinsons}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/parkinsons.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:parkinsons}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:parkinsons}
-\end{figure}
+\subsection{Discounted Rewards}
+\label{sec:conclusion:results:summary:discounted_rewards}
 
-\section{Heuristic Pool}\label{sec:results:heuristic_pool}
+For this experimental group an empirical test was conducted to determine the effects of discounted rewards of pseudo counts allocated by the credit assignment strategy in the performance log.
+A configuration is included with discounted rewards enabled and a configuration is included with discounted rewards disabled.
+Similar to the findings for the experimental group investigating the effects of the normalisation hyper-parameter, it was concluded that the default replay window size of ten is too small to yield a significant difference in performance outcome for when discounted rewards is enabled compared to when discounted rewards is disabled.
+As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
 
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \index{heuristic pool}\textit{heuristic pool} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-This experimental group utilises the same three variants of the \acs{BHH} as was utilised in Section \ref{sec:results:standalone}, but provides an opportunity to look at the \acs{BHH} \index{heuristic pool}heuristic pool hyper-parameter in more depth.
-These variants are denoted as follows.
-The \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics is denoted as \textit{all}, the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics is denoted as \textit{gd}, and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics is denoted as \textit{mh}.
+\section{Future Research Opportunities}
+\label{sec:conclusion:further_research}
 
-Table~\ref{tab:results:heuristic_pool:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the heuristic pool variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
+Throughout this dissertation, many different opportunities have been identified for future research. This section contains a summary of each of these topics.
 
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average test loss and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-	\label{tab:results:heuristic_pool:metrics:loss}%
-	\par\bigskip
-	\resizebox{0.8\textwidth}{!}{
-		\begin{tabular}{r|lll}
-			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Test Loss}}                                                                                                                     \\
-			\midrule
-			\textbf{dataset}             & \multicolumn{1}{c}{\textbf{all}}                                & \multicolumn{1}{c}{\textbf{gd}}                         & \multicolumn{1}{c}{\textbf{mh}}                         \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)            & \cellcolor[rgb]{ .388,  .745,  .482}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .973,  .412,  .42}2.2942 ($\pm$0.055)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)          & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2637 ($\pm$0.007) \\
-			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)            & \cellcolor[rgb]{ .388,  .745,  .482}0.2164 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.2562 ($\pm$0.011)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}0.0651 ($\pm$0.02)             & \cellcolor[rgb]{ .388,  .745,  .482}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.1179 ($\pm$0.006)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)         & \cellcolor[rgb]{ 1,  .922,  .518}0.169 ($\pm$0.025)     & \cellcolor[rgb]{ .973,  .412,  .42}0.4891 ($\pm$0.077)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)           & \cellcolor[rgb]{ .388,  .745,  .482}0.8976 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .922,  .518}0.9137 ($\pm$0.008)    \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)            & \cellcolor[rgb]{ .973,  .412,  .42}0.1056 ($\pm$0.008)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1043 ($\pm$0.009) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.081 ($\pm$0.069)           & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ 1,  .922,  .518}0.0621 ($\pm$0.038)    \\
-			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)         & \cellcolor[rgb]{ 1,  .922,  .518}0.0951 ($\pm$0.015)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1169 ($\pm$0.019)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2411 ($\pm$0.295)            & \cellcolor[rgb]{ .973,  .412,  .42}0.3729 ($\pm$1.119)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1809 ($\pm$0.164) \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}0.0052 ($\pm$0.012)            & \cellcolor[rgb]{ .388,  .745,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ .973,  .412,  .42}0.0774 ($\pm$0.02)   \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ 1,  .922,  .518}0.0587 ($\pm$0.003)            & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.0658 ($\pm$0.003)  \\
-			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)            & \cellcolor[rgb]{ .973,  .412,  .42}0.2454 ($\pm$0.134)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1947 ($\pm$0.014) \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)         & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .973,  .412,  .42}1.1666 ($\pm$0.03)   \\
-		\end{tabular}%
+\subsubsection{A Priori Biases}
+\label{sec:conclusion:further_research:a_priori_biases}
 
-	}
-\end{table}%
+By default, the \acs{BHH} initialises the values for the concentration parameters, related to each \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool, symmetrically with an initial value of 1.0.
+This yields an initial probability distribution of the \index{heuristic}heuristic selection probabilities that is uniform.
+Symmetric initialisation contains no a priori \index{heuristic}heuristic selection bias and assumes uniform sampling at first.
+It has been identified that expert knowledge can be incorporated into the \acs{BHH} by carefully providing the initial concentrations for the each \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.
+Such research would then evaluate if such prior \index{heuristic}heuristic selection biases have a positive impact on the outcomes of the \acs{BHH}.
 
-Similar to before, Table \ref{tab:results:heuristic_pool:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} \index{heuristic pool}heuristic pool configurations.
-The performance rank is calculated as the average rank produced by each \index{heuristic pool}heuristic pool configuration, for all datasets, over all independent runs and epochs.
+\subsubsection{Move Acceptance Strategies}
+\label{sec:conclusion:further_research:move_acceptance}
 
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:heuristic_pool:metrics:rank}%
-	\par\bigskip
-	\resizebox{0.8\textwidth}{!}{
-		\begin{tabular}{r|ccc}
-			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Rank}}                                                                                                                    \\
-			\midrule
-			\textbf{dataset}             & \textbf{all}                                               & \textbf{gd}                                             & \textbf{mh}                                            \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}1.7946 ($\pm$0.641)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3828 ($\pm$0.56)  & \cellcolor[rgb]{ .973,  .412,  .42}2.8226 ($\pm$0.42)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}2.1871 ($\pm$0.815)     & \cellcolor[rgb]{ .388,  .745,  .482}1.6828 ($\pm$0.751) & \cellcolor[rgb]{ 1,  .922,  .518}2.1301 ($\pm$0.788)   \\
-			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}1.7731 ($\pm$0.562)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3215 ($\pm$0.492) & \cellcolor[rgb]{ .973,  .412,  .42}2.9054 ($\pm$0.334) \\
-			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}1.6247 ($\pm$0.553)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4387 ($\pm$0.532) & \cellcolor[rgb]{ .973,  .412,  .42}2.9366 ($\pm$0.281) \\
-			\textbf{car}                 & \cellcolor[rgb]{ 1,  .922,  .518}1.5903 ($\pm$0.511)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4409 ($\pm$0.518) & \cellcolor[rgb]{ .973,  .412,  .42}2.9688 ($\pm$0.228) \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}2.4516 ($\pm$0.735)     & \cellcolor[rgb]{ .388,  .745,  .482}1.2806 ($\pm$0.576) & \cellcolor[rgb]{ 1,  .922,  .518}2.2677 ($\pm$0.58)    \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}1.9903 ($\pm$0.849)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8344 ($\pm$0.768) & \cellcolor[rgb]{ .973,  .412,  .42}2.1753 ($\pm$0.796) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}2.0667 ($\pm$0.834)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8269 ($\pm$0.781) & \cellcolor[rgb]{ .973,  .412,  .42}2.1065 ($\pm$0.807) \\
-			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}1.6043 ($\pm$0.687)    & \cellcolor[rgb]{ 1,  .922,  .518}1.6602 ($\pm$0.665)    & \cellcolor[rgb]{ .973,  .412,  .42}2.7355 ($\pm$0.524) \\
-			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}1.8581 ($\pm$0.8)         & \cellcolor[rgb]{ .388,  .745,  .482}1.7806 ($\pm$0.727) & \cellcolor[rgb]{ .973,  .412,  .42}2.3613 ($\pm$0.796) \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}1.5204 ($\pm$0.581)    & \cellcolor[rgb]{ 1,  .922,  .518}1.5484 ($\pm$0.527)    & \cellcolor[rgb]{ .973,  .412,  .42}2.9312 ($\pm$0.289) \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}1.557 ($\pm$0.624)     & \cellcolor[rgb]{ 1,  .922,  .518}1.6011 ($\pm$0.591)    & \cellcolor[rgb]{ .973,  .412,  .42}2.8419 ($\pm$0.445) \\
-			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}1.9828 ($\pm$0.822)       & \cellcolor[rgb]{ .388,  .745,  .482}1.7903 ($\pm$0.848) & \cellcolor[rgb]{ .973,  .412,  .42}2.2269 ($\pm$0.715) \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ 1,  .922,  .518}1.5785 ($\pm$0.55)        & \cellcolor[rgb]{ .388,  .745,  .482}1.4935 ($\pm$0.563) & \cellcolor[rgb]{ .973,  .412,  .42}2.928 ($\pm$0.294)  \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ 1,  .922,  .518}1.8271 ($\pm$0.743)       & \cellcolor[rgb]{ .388,  .745,  .482}1.5773 ($\pm$0.671) & \cellcolor[rgb]{ .973,  .412,  .42}2.5955 ($\pm$0.659) \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ 1,  .922,  .518}2                         & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .973,  .412,  .42}3                   \\
-		\end{tabular}%
-	}
-\end{table}%
+Throughout the presentation of the empirical results, it is mentioned that a move acceptance strategy can be incorporated to reject \index{heuristic}heuristic progressions that do not improve on the current best solution found.
+This would eliminate any divergence in the training process as a result of selecting sub-optimal \index{heuristic}heuristics.
+Various different move acceptance strategies can be developed and empirically tested.
 
-Similar to the outcomes provided in Section \ref{sec:results:standalone}, by ranked performance over all epochs, it is found that the \textit{gd} configuration yielded the best overall performance compared to the \textit{all} and \textit{mh} configurations.
-However, when considering the test loss measured at the last epoch, there is no clear difference in performance overall.
-This illustrates the reasoning behind the use of the rank metric over all epochs to evaluate the overall training process, as the test loss outcome differs at different epochs and early stopping of the training process was not used.
+\subsubsection{Early Stopping Strategies}
+\label{sec:conclusion:further_research:early_stopping}
 
-Figure~\ref{fig:results:heuristic_pool:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different \index{heuristic pool}heuristic pool configurations, per dataset.
-From this illustration it can clearly be seen that, by ranked performance, the \textit{gd} configuration produced better results overall, considering the entire training process.
+Similar to the move acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to hault the training process if the performance does not improve for a number of steps.
+In this dissertation, a number of examples were presented where divergence of training loss occurred.
+Furthermore, a number of examples were presented where overfitting occurred.
+An early stopping strategy can help prevent such outcomes.
 
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying heuristic pools per dataset, across all independent runs and epochs.}
-	\label{fig:results:heuristic_pool:descriptive:descriptive}
-\end{figure}
+\subsubsection{Entity Search}
+\label{sec:conclusion:further_research:entity_search}
+For this dissertation, even though the predictive model implemented by the \acs{BHH} includes entity consideration, it does not sample from an entity pool.
+The \acs{BHH} keeps the entire entity pool fixed, and just reselects heuristics for each entity.
+The \acs{BHH}, as is, can be used to learn which entities to select as well.
+The hypothesis is that this would result in better combinations of entities and heuristics, which should have a positive effect on the outcomes of the \acs{BHH}.
 
-Figure~\ref{fig:results:heuristic_pool:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic pool}heuristic pool configuration as it relates to all datasets, across all independent runs and epochs.
+\subsubsection{Continuous Valued Credit Allocation}
+\label{sec:conclusion:further_research:continuous_credit}
 
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying heuristic pools across all datasets, runs and epochs.}
-	\label{fig:results:heuristic_pool:descriptive:cd}
-\end{figure}
+Credit assignment in the context of this dissertation yields a discrete credit allocation value.
+More specifically, the credit allocation is binary, yielding a zero or a one.
+Future research can investigate different credit allocation strategies that yield continuous valued outcomes.
+This should provide more fine-grained indicators of \index{heuristic}heuristic performance which the \acs{BHH} can exploit easier.
 
-From Figures~\ref{fig:results:heuristic_pool:descriptive:descriptive} and~\ref{fig:results:heuristic_pool:descriptive:cd}, it is clear that the \textit{gd} configuration configuration performs best overall, with exceptions to the parkinsons and housing datasets, where the \textit{all} and \textit{gd} configurations performed equally well with statistically insignificant differences in their outcomes.
+\subsubsection{Credit Search}
+\label{sec:conclusion:further_research:credit_search}
 
-From the results shown in this section and Section \ref{sec:results:standalone}, the gradient-based \index{heuristic}heuristics outperformed the \index{meta-heuristic}meta-heuristics in almost all cases.
-It can then logically be concluded that the \acs{BHH} baseline configuration with only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool yields the best performance.
-The inclusion of \index{meta-heuristic}meta-heuristics is done as an attempt to provide a mechanism that could provide even better performance, as well as generalisation capabilities to other datasets.
-The benefits of using \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool is not realised in this dissertation, since the gradient-based \index{heuristic}heuristics provided the best overall performance across  all datasets.
-Furthermore, the standalone gradient-based \index{heuristic}heuristics already produce good performance results, and improvement on those results are hard.
-Faster convergence is also difficult to achieve, since the \acs{BHH} needs sufficient time to explore the heuristic space.
-The benefit that the \acs{BHH} then brings is that it provides a mechanism whereby prior expert knowledge can be injected, before training starts.
-Since gradient-based \index{heuristic}heuristics perform well, future research can exploit this knowledge and provide a significant bias towards these gradient-based \index{heuristic}heuristics through the initialisation of the concentration parameters related to these \index{heuristic}heuristics as mentioned previously.
+Similar to entity search, the \acs{BHH}, as is, can be used to learn which credit assignment strategies to use.
+This can then be combined with heuristic and entity selection so that the correct heuristic is selected for the correct entity, by means of the correct credit allocation strategy that is applicable, at the correct time in the training process.
+For example, a particular heuristic-entity combination might benefit from a \textit{pbest} credit allocation, while another heuristic-entity combination might benefit from a \textit{ibest} credit allocation at the same time in the training process.
 
-Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides an illustration of the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the \index{heuristic pool}heuristic pool experimental group.
-As before, the illustrations are provided in log scale and illustrations for the other classification datasets are left out for brevity as they yield similar illustrations.
+\subsubsection{Models}
+\label{sec:conclusion:further_research:models}
 
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/loss/abalone.pdf}
-		\caption{Train log loss}
-		\label{fig:results:heuristic_pool:figures:loss:train:abalone}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/abalone.pdf}
-		\caption{Test log loss}
-		\label{fig:results:heuristic_pool:figures:loss:test:abalone}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/accuracy/abalone.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:heuristic_pool:figures:accuracy:train:abalone}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/accuracy/abalone.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:heuristic_pool:figures:accuracy:test:abalone}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the abalone dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:heuristic_pool:figures:abalone}
-\end{figure}
+For this dissertation, focus was put on training \acp{FFNN}.
+However, in theory, other models can also be used.
+Suggestions include \acp{DNN} and \acp{RNN}.
+Furthermore, future research can attempt to use the \acs{BHH} for dynamic optimisation problems.
 
-Figure~\ref{fig:results:heuristic_pool:figures:forest_fires} provides the train and test loss plots for an example regression dataset (forest fires) as it relates to the heuristic pool experimental group.
-As before, the illustrations are provided in log scale and illustrations for the other regression datasets are left out for brevity.
+\subsubsection{Dynamic Hyper-Parameter Values}
+\label{sec:conclusion:further_research:dynamic_hyper_parameters}
 
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/loss/forest_fires.pdf}
-		\caption{Train log loss}
-		\label{fig:results:heuristic_pool:figures:loss:train:forest_fires}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/forest_fires.pdf}
-		\caption{Test log loss}
-		\label{fig:results:heuristic_pool:figures:loss:test:forest_fires}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the forest fires dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:heuristic_pool:figures:forest_fires}
-\end{figure}
+It was shown that larger reselection intervals are generally preferred.
+It was shown that there is a relationship between the reselection interval, the replay window size and the reanalysis interval.
+These hyper-parameters provide an mechanism for trade-off between exploration and exploitation and therefore, investigation into dynamic selection of hyper-parameter values can be considered in future research.
 
-\section{Population Size}\label{sec:results:population}
+\subsubsection{Heuristic Pools}
+\label{sec:conclusion:further_research:heuristic_pools}
 
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{population size} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, five different population sizes are considered.
-These include population sizes of 5, 10, 15, 20, and 25, and experiments are denoted as such.
+This dissertation only considered three different types of \index{heuristic pool}heuristic pool configurations.
+The following alternative configurations could be considered.
+A \index{heuristic pool}heuristic pool could be considered where multiple instances of the same \index{heuristic}heuristic is included, but with different hyper-parameter values, effectively implementing dynamic hyper-parameter optimisation.
+Empirical testing can be done to determine the effects of various \index{heuristic pool}heuristic pool sizes.
+Different types of heuristics can be considered for inclusion in the \index{heuristic pool}heuristic pool.
+A suggestion is to include black-box optimisers such as \acs{CMA-ES}.
+Finally, \index{heuristic}heuristic ensemble pools could be considered, where the \index{heuristic}heuristic selection is a selection of an ensemble of \index{heuristic}heuristics.
 
-Table~\ref{tab:results:population:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the population size variants of the \acs{BHH} that was implemented.
-Similar to before, the test loss is measured at the last epoch for each dataset, over all independent runs.
+\subsubsection{Parameter Pools}
+\label{sec:conclusion:further_research:parameter_pools}
 
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average test loss and statistics for all population size configurations used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-	\label{tab:results:population:metrics:loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Population - Average Test Loss}}                                                                                                                                                                                                                                        \\
-			\midrule
-			\textbf{dataset}             & \textbf{5}                                                  & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                            & \textbf{25}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088)     & \cellcolor[rgb]{ .612,  .808,  .494}2.1592 ($\pm$0.278) & \cellcolor[rgb]{ 1,  .922,  .518}2.3321 ($\pm$0.446)    & \cellcolor[rgb]{ 1,  .91,  .518}2.3345 ($\pm$0.357)    & \cellcolor[rgb]{ .973,  .412,  .42}2.4188 ($\pm$0.473)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 ($\pm$0.016)        & \cellcolor[rgb]{ .388,  .745,  .482}0.2701 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .878,  .51}0.2736 ($\pm$0.014)     & \cellcolor[rgb]{ .973,  .412,  .42}0.2808 ($\pm$0.026) & \cellcolor[rgb]{ .702,  .835,  .498}0.2715 ($\pm$0.011) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)      & \cellcolor[rgb]{ .992,  .729,  .482}0.2356 ($\pm$0.029) & \cellcolor[rgb]{ .388,  .745,  .482}0.2268 ($\pm$0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.2294 ($\pm$0.019)   & \cellcolor[rgb]{ .608,  .808,  .494}0.2278 ($\pm$0.012) \\
-			\textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}0.0651 ($\pm$0.02)       & \cellcolor[rgb]{ .388,  .745,  .482}0.0527 ($\pm$0.002) & \cellcolor[rgb]{ .988,  .918,  .514}0.0535 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .898,  .514}0.0541 ($\pm$0.003)   & \cellcolor[rgb]{ 1,  .922,  .518}0.0535 ($\pm$0.003)    \\
-			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)     & \cellcolor[rgb]{ .757,  .851,  .502}0.1595 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}0.161 ($\pm$0.039)     & \cellcolor[rgb]{ .992,  .773,  .49}0.1636 ($\pm$0.04)  & \cellcolor[rgb]{ .973,  .412,  .42}0.17 ($\pm$0.048)    \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)       & \cellcolor[rgb]{ 1,  .922,  .518}0.9954 ($\pm$0.103)    & \cellcolor[rgb]{ .992,  .776,  .49}1.0826 ($\pm$0.3)    & \cellcolor[rgb]{ .525,  .784,  .49}0.9893 ($\pm$0.105) & \cellcolor[rgb]{ .388,  .745,  .482}0.9875 ($\pm$0.078) \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1046 ($\pm$0.008)     & \cellcolor[rgb]{ 1,  .922,  .518}0.1077 ($\pm$0.009)    & \cellcolor[rgb]{ .882,  .886,  .51}0.1071 ($\pm$0.011)  & \cellcolor[rgb]{ .973,  .412,  .42}0.1104 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .886,  .514}0.1079 ($\pm$0.008)    \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}0.081 ($\pm$0.069)         & \cellcolor[rgb]{ .388,  .745,  .482}0.0694 ($\pm$0.059) & \cellcolor[rgb]{ .737,  .843,  .502}0.0761 ($\pm$0.056) & \cellcolor[rgb]{ .984,  .569,  .451}0.084 ($\pm$0.07)  & \cellcolor[rgb]{ .973,  .412,  .42}0.0854 ($\pm$0.065)  \\
-			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)     & \cellcolor[rgb]{ 1,  .922,  .518}0.0985 ($\pm$0.026)    & \cellcolor[rgb]{ .412,  .749,  .482}0.0943 ($\pm$0.016) & \cellcolor[rgb]{ 1,  .906,  .518}0.0987 ($\pm$0.017)   & \cellcolor[rgb]{ .973,  .412,  .42}0.1038 ($\pm$0.017)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .388,  .745,  .482}0.2411 ($\pm$0.295)     & \cellcolor[rgb]{ .992,  .741,  .486}0.4212 ($\pm$0.671) & \cellcolor[rgb]{ .973,  .412,  .42}0.5905 ($\pm$1.043)  & \cellcolor[rgb]{ .651,  .82,  .494}0.2784 ($\pm$0.261) & \cellcolor[rgb]{ 1,  .922,  .518}0.327 ($\pm$0.381)     \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012)     & \cellcolor[rgb]{ .973,  .412,  .42}1.9037 ($\pm$10.345) & \cellcolor[rgb]{ 1,  .898,  .514}0.3366 ($\pm$1.559)    & \cellcolor[rgb]{ .69,  .831,  .498}0.1311 ($\pm$0.486) & \cellcolor[rgb]{ 1,  .922,  .518}0.2602 ($\pm$1.115)    \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003)     & \cellcolor[rgb]{ .82,  .867,  .506}0.0598 ($\pm$0.003)  & \cellcolor[rgb]{ .988,  .694,  .475}0.0606 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0602 ($\pm$0.003)   & \cellcolor[rgb]{ .973,  .412,  .42}0.0612 ($\pm$0.003)  \\
-			\textbf{student performance} & \cellcolor[rgb]{ .973,  .412,  .42}0.2359 ($\pm$0.102)      & \cellcolor[rgb]{ .388,  .745,  .482}0.2007 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .922,  .518}0.2092 ($\pm$0.039)    & \cellcolor[rgb]{ .573,  .796,  .49}0.2033 ($\pm$0.037) & \cellcolor[rgb]{ 1,  .922,  .518}0.2091 ($\pm$0.054)    \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)     & \cellcolor[rgb]{ .553,  .792,  .49}1.0864 ($\pm$0.034)  & \cellcolor[rgb]{ .973,  .412,  .42}1.1083 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .922,  .518}1.0961 ($\pm$0.027)   & \cellcolor[rgb]{ .976,  .463,  .431}1.1071 ($\pm$0.039) \\
-		\end{tabular}%
+A suggestion for future research is to apply the \acs{BHH} to a multitude of parameter types.
+These could be hyper-parameters of the low-level \index{heuristic}heuristics, the parameters for the topology and architecture of models (similar to neural architecture search) or the hyper-parameters of the \acs{BHH} itself.
 
-	}
-\end{table}%
+\section{Documentation and Data}
+\label{sec:conclusion:documentation_and_data}
 
-From Table \ref{tab:results:population:metrics:loss} it can be seen that the lowest population size produced mostly the best performance outcomes, yielding the best average test loss for eight of the fourteen datasets.
-However, the lowest population size also produced the worst performance outcomes for four of the fourteen datasets.
-From the empirical results that show the average test loss, measured at the last epoch, it is not clear which population size configuration produced the overall best results.
+All the source code, data, logs and analyses that were used in this dissertation, as well as the dissertation source itself, can be found at \url{https://github.com/arneschreuder/masters.ai}.
+The raw empirical data is made available on Google Cloud's BigQuery platform, under the project id \textit{masters-363209}.
 
-As before, the performance of the different \acs{BHH} population size configurations need to be considered for the entire training process.
-As such, Table \ref{tab:results:population:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} population size configurations.
-Similar to before, the performance rank is calculated as the average rank produced by each population size configuration, for all datasets, over all independent runs and epochs.
+\section{Summary}
+\label{sec:conclusion:summary}
 
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all independent runs and all epochs.}
-	\label{tab:results:population:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Population - Average Rank}}                                                                                                                                                                                                                                          \\
-			\midrule
-			\textbf{dataset}             & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             & \textbf{25}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.4387 ($\pm$1.34)  & \cellcolor[rgb]{ .714,  .839,  .498}2.7452 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}3.0129 ($\pm$1.386)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4065 ($\pm$1.351)  & \cellcolor[rgb]{ .976,  .427,  .424}3.3968 ($\pm$1.351) \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.7527 ($\pm$1.428) & \cellcolor[rgb]{ .882,  .886,  .51}2.9258 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9656 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.379)   & \cellcolor[rgb]{ .996,  .812,  .498}3.0419 ($\pm$1.437) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8129 ($\pm$1.41)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1591 ($\pm$1.435)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9989 ($\pm$1.42)     & \cellcolor[rgb]{ .992,  .761,  .486}3.0505 ($\pm$1.444) & \cellcolor[rgb]{ .929,  .902,  .514}2.9785 ($\pm$1.341) \\
-			\textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}3.8957 ($\pm$1.335)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8688 ($\pm$1.285)    & \cellcolor[rgb]{ 1,  .875,  .51}2.9645 ($\pm$1.345)     & \cellcolor[rgb]{ .773,  .855,  .502}2.743 ($\pm$1.376)  & \cellcolor[rgb]{ .388,  .745,  .482}2.528 ($\pm$1.328)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .973,  .412,  .42}3.1892 ($\pm$1.391)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.394)    & \cellcolor[rgb]{ 1,  .922,  .518}3.0398 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8559 ($\pm$1.394) & \cellcolor[rgb]{ .447,  .761,  .482}2.8742 ($\pm$1.415) \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}2.7978 ($\pm$1.508) & \cellcolor[rgb]{ .914,  .894,  .51}2.9387 ($\pm$1.413)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2129 ($\pm$1.452)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9613 ($\pm$1.304)    & \cellcolor[rgb]{ .988,  .663,  .471}3.0892 ($\pm$1.353) \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.8151 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.429)    & \cellcolor[rgb]{ .984,  .62,  .463}3.0925 ($\pm$1.323)  & \cellcolor[rgb]{ .973,  .412,  .42}3.128 ($\pm$1.407)   & \cellcolor[rgb]{ .682,  .827,  .498}2.9237 ($\pm$1.463) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .992,  .773,  .49}3.0172 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9215 ($\pm$1.38)  & \cellcolor[rgb]{ .965,  .91,  .514}2.9806 ($\pm$1.383)  & \cellcolor[rgb]{ .973,  .412,  .42}3.0968 ($\pm$1.412)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.488)    \\
-			\textbf{housing}             & \cellcolor[rgb]{ .431,  .757,  .482}2.8366 ($\pm$1.404) & \cellcolor[rgb]{ .388,  .745,  .482}2.8258 ($\pm$1.38)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9753 ($\pm$1.439)    & \cellcolor[rgb]{ 1,  .91,  .518}2.9849 ($\pm$1.411)     & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.368)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8301 ($\pm$1.304) & \cellcolor[rgb]{ .506,  .776,  .486}2.8731 ($\pm$1.397) & \cellcolor[rgb]{ 1,  .922,  .518}3.0505 ($\pm$1.413)    & \cellcolor[rgb]{ .973,  .412,  .42}3.186 ($\pm$1.425)   & \cellcolor[rgb]{ 1,  .886,  .514}3.0602 ($\pm$1.499)    \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.7989 ($\pm$1.205) & \cellcolor[rgb]{ .745,  .847,  .502}2.9441 ($\pm$1.325) & \cellcolor[rgb]{ 1,  .922,  .518}3.0462 ($\pm$1.452)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1366 ($\pm$1.494)  & \cellcolor[rgb]{ 1,  .882,  .51}3.0538 ($\pm$1.566)     \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.6645 ($\pm$1.441) & \cellcolor[rgb]{ .988,  .647,  .467}3.1065 ($\pm$1.327) & \cellcolor[rgb]{ .957,  .91,  .514}3.0247 ($\pm$1.427)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0495 ($\pm$1.442)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1548 ($\pm$1.381)  \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6376 ($\pm$1.436) & \cellcolor[rgb]{ .682,  .827,  .498}2.8645 ($\pm$1.411) & \cellcolor[rgb]{ .992,  .733,  .482}3.1548 ($\pm$1.404) & \cellcolor[rgb]{ .973,  .412,  .42}3.2387 ($\pm$1.397)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1043 ($\pm$1.34)     \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.5505 ($\pm$1.317) & \cellcolor[rgb]{ .62,  .812,  .494}2.7817 ($\pm$1.415)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1581 ($\pm$1.384)    & \cellcolor[rgb]{ 1,  .855,  .506}3.1806 ($\pm$1.394)    & \cellcolor[rgb]{ .973,  .412,  .42}3.329 ($\pm$1.414)   \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}2.8598 ($\pm$1.424) & \cellcolor[rgb]{ .62,  .812,  .494}2.9312 ($\pm$1.389)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0484 ($\pm$1.406)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0952 ($\pm$1.412)  & \cellcolor[rgb]{ .992,  .753,  .486}3.064 ($\pm$1.428)  \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ .988,  .667,  .471}4                   \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-From Table \ref{tab:results:population:metrics:rank} it can be seen that a lower population size of five, mostly produced the best results, with exception to the bike and car datasets, for which the lowest population size configuration produced the worst performance, yielding statistically significant differences in outcomes from the other datasets.
-A larger population size configuration is prefered for the bike and car datasets.
-Furthermore, a population size configuration of ten, slightly higher than the default of five, is preferred for the forest fires and housing datasets.
-Finally, the overall normalised average rank is provided at the bottom of the table, showing that a population size of five produced the best performance outcome across all datasets on average.
-
-Figure~\ref{fig:results:population:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different population size configurations, per dataset.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_population/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of \acs{BHH} with varying population sizes per dataset, across all independent runs and epochs.}
-	\label{fig:results:population:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:population:descriptive:descriptive}, shows the correlation of performance with population size for each dataset.
-From these illustrations, it can be seen that the correlation between the population size configuration and performance is different for each dataset, suggesting that the population size hyper-parameter is problem specific.
-However, the overall performance related to each population configuration, across all datasets is not clear from these illustrations.
-
-Figure~\ref{fig:results:population:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each population size configuration as it relates to all datasets, across all independent runs and epochs.
-It is shown that there is no overall statistical significant difference between population sizes and thus, it can be concluded that the population size hyper-parameter is problem specific.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_population/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of \acs{BHH} with varying population sizes across all datasets, runs and epochs.}
-	\label{fig:results:population:descriptive:cd}
-\end{figure}
-
-Similar to before, Figure~\ref{fig:results:population:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the population size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_population/figures/train/loss/mushroom.pdf}
-		\caption{Train log loss}
-		\label{fig:results:population:figures:loss:train:mushroom}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/mushroom.pdf}
-		\caption{Test log loss}
-		\label{fig:results:population:figures:loss:test:mushroom}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_population/figures/train/accuracy/mushroom.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:population:figures:accuracy:train:mushroom}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_population/figures/test/accuracy/mushroom.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:population:figures:accuracy:test:mushroom}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:population:figures:mushroom}
-\end{figure}
-
-As a reminder, the experimental group for population sizes only varies the population size hyper-parameter and all other hyper-parameters remain the same between configurations.
-As such, all population size configurations make use of the \index{heuristic pool}heuristic pool configuration that includes all the low-level heuristics, including gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
-
-Divergence of the training loss can be observed in Figure \ref{fig:results:population:figures:loss:test:mushroom}.
-Note that, despite the divergence of training loss, the accuracy is still almost 100\% and that these divergent behaviours are simply a result of an attempt to further improve performance, by exploring the heuristic space more.
-For example, heuristics could have momentum as a result of good training progression thus far, but then overshoot good solutions after \index{heuristic}heuristic reselection.
-Overshooting good solutions then causes the \index{heuristic}heuristics to struggle to converge back to good solutions, especially if many different \index{heuristic}heuristics are selected in quick succession.
-A suggestion to this problem is to implement a move-acceptance strategy as was mentioned before.
-At the nineth epoch, the \acs{BHH} fails to produce better solutions on the training set.
-Since there is not much room for more improvement, the \acs{BHH} is bound to try different \index{heuristic}heuristics that yield sub-optimal results.
-From this point onwards, the \acs{BHH} finds slightly better results on the train set, and as a result, produces volatile performance on the test set.
-
-Figure~\ref{fig:results:population:figures:student_performance} provides the train and test loss plots for an example regression dataset (student performance) as it relates to the population size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_population/figures/train/loss/student_performance.pdf}
-		\caption{Train log loss}
-		\label{fig:results:population:figures:loss:train:student_performance}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/student_performance.pdf}
-		\caption{Test log loss}
-		\label{fig:results:population:figures:loss:test:student_performance}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the student performance dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:population:figures:student_performance}
-\end{figure}
-
-From Figure~\ref{fig:results:population:figures:loss:train:student_performance} it can be seen that the \acs{BHH} with a low population size of five starts to diverge away from optimal results as it explores different \index{heuristic}heuristics in an attempt to provide better solutions.
-Divergence can be eliminated by means of an early stopping strategy as well as a move-acceptance strategy as mentioned before.
-
-\section{Credit Assignment Strategy}\label{sec:results:credit}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{credit assignment strategy} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, five different credit assignment strategies are considered.
-These include the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies as presented in Chapter \ref{chap:bhh} and experiments are denoted as such.
-
-Table~\ref{tab:results:credit:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the credit assignment strategy variants of the \acs{BHH} that was implemented.
-As before, the test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average test loss and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-	\label{tab:results:credit:metrics:loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Credit - Average Test Loss}}                                                                                                                                                                                                                             \\
-			\midrule
-			\textbf{dataset}             & \textbf{ibest}                                          & \textbf{pbest}                                       & \textbf{rbest}                                       & \textbf{gbest}                                       & \textbf{symmetric}                                   \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .631,  .816,  .494}2.0587 (+-0.088)    & \cellcolor[rgb]{ .388,  .745,  .482}2.0422 (+-0.094) & \cellcolor[rgb]{ .996,  .792,  .494}2.0922 (+-0.152) & \cellcolor[rgb]{ 1,  .922,  .518}2.0833 (+-0.136)    & \cellcolor[rgb]{ .973,  .412,  .42}2.1177 (+-0.259)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 (+-0.016)     & \cellcolor[rgb]{ .902,  .89,  .51}0.2678 (+-0.015)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2644 (+-0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.2684 (+-0.013)    & \cellcolor[rgb]{ 1,  .882,  .51}0.2688 (+-0.017)     \\
-			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 (+-0.065)       & \cellcolor[rgb]{ .973,  .412,  .42}0.2645 (+-0.171)  & \cellcolor[rgb]{ .51,  .78,  .486}0.238 (+-0.047)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2361 (+-0.031) & \cellcolor[rgb]{ .996,  .812,  .498}0.2498 (+-0.047) \\
-			\textbf{bike}                & \cellcolor[rgb]{ .988,  .647,  .467}0.0651 (+-0.02)     & \cellcolor[rgb]{ 1,  .922,  .518}0.0634 (+-0.023)    & \cellcolor[rgb]{ .871,  .882,  .51}0.0633 (+-0.02)   & \cellcolor[rgb]{ .388,  .745,  .482}0.063 (+-0.021)  & \cellcolor[rgb]{ .973,  .412,  .42}0.0666 (+-0.021)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ 1,  .91,  .518}0.1572 (+-0.034)        & \cellcolor[rgb]{ 1,  .922,  .518}0.1569 (+-0.029)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1665 (+-0.03)   & \cellcolor[rgb]{ .388,  .745,  .482}0.1504 (+-0.03)  & \cellcolor[rgb]{ .945,  .906,  .514}0.1564 (+-0.037) \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .878,  .886,  .51}1.2983 (+-0.66)      & \cellcolor[rgb]{ .988,  .651,  .467}1.4981 (+-2.41)  & \cellcolor[rgb]{ .973,  .412,  .42}1.6172 (+-1.527)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0347 (+-0.231) & \cellcolor[rgb]{ 1,  .922,  .518}1.3627 (+-1.145)    \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .988,  .647,  .467}0.1046 (+-0.008)    & \cellcolor[rgb]{ 1,  .922,  .518}0.1028 (+-0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1024 (+-0.009) & \cellcolor[rgb]{ .973,  .412,  .42}0.1061 (+-0.009)  & \cellcolor[rgb]{ .643,  .816,  .494}0.1026 (+-0.009) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .914,  .514}0.081 (+-0.069)     & \cellcolor[rgb]{ 1,  .922,  .518}0.0819 (+-0.062)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0591 (+-0.046) & \cellcolor[rgb]{ .973,  .412,  .42}0.0845 (+-0.077)  & \cellcolor[rgb]{ 1,  .867,  .51}0.0822 (+-0.07)      \\
-			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 (+-0.017)    & \cellcolor[rgb]{ .996,  .82,  .498}0.0974 (+-0.021)  & \cellcolor[rgb]{ .835,  .875,  .506}0.0961 (+-0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.0995 (+-0.016)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0969 (+-0.018)    \\
-			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 (+-0.295)     & \cellcolor[rgb]{ .388,  .745,  .482}0.1441 (+-0.131) & \cellcolor[rgb]{ 1,  .922,  .518}0.1547 (+-0.111)    & \cellcolor[rgb]{ 1,  .882,  .51}0.1616 (+-0.187)     & \cellcolor[rgb]{ .765,  .851,  .502}0.1507 (+-0.142) \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .404,  .749,  .482}0.0052 (+-0.012)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0289 (+-0.107)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0044 (+-0.011) & \cellcolor[rgb]{ 1,  .91,  .518}0.1835 (+-0.949)     & \cellcolor[rgb]{ .973,  .412,  .42}5.3926 (+-29.503) \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 (+-0.003)    & \cellcolor[rgb]{ 1,  .867,  .51}0.0594 (+-0.002)     & \cellcolor[rgb]{ .973,  .412,  .42}0.0602 (+-0.002)  & \cellcolor[rgb]{ .898,  .89,  .51}0.0592 (+-0.002)   & \cellcolor[rgb]{ 1,  .922,  .518}0.0593 (+-0.003)    \\
-			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 (+-0.102)       & \cellcolor[rgb]{ .678,  .827,  .498}0.2303 (+-0.095) & \cellcolor[rgb]{ .988,  .69,  .475}0.2551 (+-0.109)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2251 (+-0.088) & \cellcolor[rgb]{ .973,  .412,  .42}0.2777 (+-0.116)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .98,  .525,  .443}1.0827 (+-0.026)     & \cellcolor[rgb]{ 1,  .922,  .518}1.0799 (+-0.031)    & \cellcolor[rgb]{ .925,  .898,  .51}1.0794 (+-0.021)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0757 (+-0.027) & \cellcolor[rgb]{ .973,  .412,  .42}1.0835 (+-0.029)  \\
-		\end{tabular}%
-	}
-\end{table}%
-
-From Table~\ref{tab:results:credit:metrics:loss}, it is not clear which credit assignment strategy yields the best performance for the entire training process.
-As such, Table \ref{tab:results:credit:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} credit assignment strategy configurations.
-Similar to before, the performance rank is calculated as the average rank produced by each credit assignment strategy configuration, for all datasets, over all independent runs and epochs.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:credit:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Credit - Average Rank}}                                                                                                                                                                                                                                              \\
-			\midrule
-			\textbf{dataset}             & \textbf{ibest}                                          & \textbf{pbest}                                          & \textbf{rbest}                                          & \textbf{gbest}                                          & \textbf{symmetric}                                      \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}3.1677 ($\pm$1.319)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8613 ($\pm$1.459) & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.399)    & \cellcolor[rgb]{ .863,  .882,  .51}2.9667 ($\pm$1.455)  & \cellcolor[rgb]{ 1,  .89,  .514}3.0075 ($\pm$1.421)     \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.1312 ($\pm$1.347)  & \cellcolor[rgb]{ .91,  .894,  .51}3.0376 ($\pm$1.357)   & \cellcolor[rgb]{ .388,  .745,  .482}2.5914 ($\pm$1.465) & \cellcolor[rgb]{ .98,  .498,  .439}3.128 ($\pm$1.336)   & \cellcolor[rgb]{ 1,  .922,  .518}3.1118 ($\pm$1.487)    \\
-			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8591 ($\pm$1.344) & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.432)    & \cellcolor[rgb]{ .522,  .78,  .486}2.8882 ($\pm$1.41)   & \cellcolor[rgb]{ .996,  .804,  .498}3.0441 ($\pm$1.415) & \cellcolor[rgb]{ .973,  .412,  .42}3.2183 ($\pm$1.442)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .98,  .537,  .447}3.0527 ($\pm$1.34)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0086 ($\pm$1.393)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0667 ($\pm$1.483)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8742 ($\pm$1.339) & \cellcolor[rgb]{ .949,  .906,  .514}2.9978 ($\pm$1.503) \\
-			\textbf{car}                 & \cellcolor[rgb]{ .992,  .729,  .482}3.1151 ($\pm$1.356) & \cellcolor[rgb]{ 1,  .922,  .518}3.0312 ($\pm$1.483)    & \cellcolor[rgb]{ .973,  .412,  .42}3.2516 ($\pm$1.402)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6892 ($\pm$1.354) & \cellcolor[rgb]{ .788,  .859,  .502}2.9129 ($\pm$1.411) \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .996,  .918,  .514}2.8914 ($\pm$1.349) & \cellcolor[rgb]{ .388,  .745,  .482}2.6269 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.4151 ($\pm$1.365)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8925 ($\pm$1.362)    & \cellcolor[rgb]{ .988,  .647,  .467}3.1742 ($\pm$1.449) \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .98,  .541,  .447}3.1516 ($\pm$1.436)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.475) & \cellcolor[rgb]{ .973,  .412,  .42}3.2043 ($\pm$1.299)  & \cellcolor[rgb]{ .749,  .847,  .502}2.8957 ($\pm$1.358) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.277)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1806 ($\pm$1.304)  & \cellcolor[rgb]{ .58,  .8,  .49}2.8559 ($\pm$1.356)     & \cellcolor[rgb]{ .992,  .773,  .49}3.1215 ($\pm$1.502)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7452 ($\pm$1.563) \\
-			\textbf{housing}             & \cellcolor[rgb]{ .984,  .918,  .514}2.9011 ($\pm$1.494) & \cellcolor[rgb]{ .388,  .745,  .482}2.8527 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}2.9022 ($\pm$1.397)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3108 ($\pm$1.324)  & \cellcolor[rgb]{ .992,  .761,  .486}3.0333 ($\pm$1.483) \\
-			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}3.1892 ($\pm$1.428)  & \cellcolor[rgb]{ .996,  .827,  .502}3.0839 ($\pm$1.441) & \cellcolor[rgb]{ 1,  .922,  .518}3.0591 ($\pm$1.376)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8237 ($\pm$1.409) & \cellcolor[rgb]{ .439,  .757,  .482}2.8441 ($\pm$1.384) \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.8075 ($\pm$1.459) & \cellcolor[rgb]{ 1,  .922,  .518}3.0183 ($\pm$1.411)    & \cellcolor[rgb]{ .643,  .816,  .494}2.8957 ($\pm$1.398) & \cellcolor[rgb]{ .992,  .706,  .478}3.0839 ($\pm$1.418) & \cellcolor[rgb]{ .973,  .412,  .42}3.172 ($\pm$1.381)   \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.5645 ($\pm$1.484) & \cellcolor[rgb]{ .898,  .89,  .51}2.8925 ($\pm$1.343)   & \cellcolor[rgb]{ .973,  .412,  .42}3.5065 ($\pm$1.219)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0796 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}2.957 ($\pm$1.455)     \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6624 ($\pm$1.312) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.407)     & \cellcolor[rgb]{ .988,  .643,  .467}3.1892 ($\pm$1.382) & \cellcolor[rgb]{ .612,  .808,  .494}2.7978 ($\pm$1.47)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3215 ($\pm$1.394)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .98,  .494,  .439}3.1871 ($\pm$1.308)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .922,  .518}3.014 ($\pm$1.371)     & \cellcolor[rgb]{ .882,  .886,  .51}2.9419 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.43)   \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .843,  .875,  .506}2.9841 ($\pm$1.39)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9457 ($\pm$1.415) & \cellcolor[rgb]{ .984,  .588,  .455}3.0279 ($\pm$1.414) & \cellcolor[rgb]{ 1,  .922,  .518}2.997 ($\pm$1.402)     & \cellcolor[rgb]{ .973,  .412,  .42}3.0437 ($\pm$1.449)  \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-Table \ref{tab:results:credit:metrics:rank} shows that different credit assignment strategies perform best for different datasets, from which it can be concluded that the credit assignment strategy hyper-parameter is problem specific.
-Furthermore, the overall normalised average rank across all datasets is provided at the bottom of the table.
-It should be noted that the \textit{symmetric} credit assignment strategy yielded the best results for the forest fires dataset.
-This does not necessarily suggest that random search in the heuristic space yields the best performance for this dataset.
-As a reminder, the \textit{symmetric} credit assignment strategy does not bias towards performance, but rather uniformly assigns credit to any heuristic that happens to be selected.
-For the particular case where the \textit{symmetric} credit assignment strategy yielded the best results, it could be the case that the initial selection of heuristics is good enough and that it is difficult to find a performance bias that results in better performance, as all \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool provide good results.
-For all other datasets, it is found that a particular non-\textit{symmetric} credit assignment strategy yields better results.
-
-Figure~\ref{fig:results:credit:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different credit assignment strategy configurations, per dataset.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_credit/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying credit assignment strategies per dataset, across all independent runs and epochs.}
-	\label{fig:results:credit:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:credit:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each credit assignment strategy configuration as it relates to all datasets, across all independent runs and epochs.
-It is shown that there is no overall statistical significant difference between credit assignment strategies and that the credit assignment strategy hyper-parameter is problem specific.
-At this point it should be mentioned that the credit assignment strategies implemented in this dissertation yield a discrete credit value and that future research should consider a continuous credit value in an attempt to provide a more fine grained indicator of performance, which should be easier to exploit.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_credit/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying credit assignment strategies across all datasets, runs and epochs.}
-	\label{fig:results:credit:descriptive:cd}
-\end{figure}
-
-Similar to before, Figure~\ref{fig:results:credit:figures:bank} provides the train and test, loss and accuracy plots for an example classification dataset (bank) as it relates to the credit assignment strategy experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/bank.pdf}
-		\caption{Train log loss}
-		\label{fig:results:credit:figures:loss:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/bank.pdf}
-		\caption{Test log loss}
-		\label{fig:results:credit:figures:loss:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_credit/figures/train/accuracy/bank.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:credit:figures:accuracy:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_credit/figures/test/accuracy/bank.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:credit:figures:accuracy:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the bank dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:credit:figures:bank}
-\end{figure}
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/housing.pdf}
-		\caption{Train log loss}
-		\label{fig:results:credit:figures:loss:train:housing}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/housing.pdf}
-		\caption{Test log loss}
-		\label{fig:results:credit:figures:loss:test:housing}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the housing dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:credit:figures:housing}
-\end{figure}
-
-From Figure~\ref{fig:results:credit:figures:bank} it can be seen that the \textit{pbest} credit assignment strategy diverged away from the current best solution, but was able to return to the current best solution.
-Since the solution found by the \acs{BHH} with the \textit{pbest} credit assignment strategy was already optimal before divergence, it stands to reason that this divergence is a result of the \acs{BHH} exploring other \index{heuristic}heuristics in the heuristic space that yield sub-optimal solutions.
-As mentioned before, a move-acceptance strategy can be incorporated to counteract this effect.
-
-Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plots for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\section{Reselection Interval}\label{sec:results:reselection}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{reselection interval} hyper-parameter.
-Detailed discussions follow and illustrations are provided for visual aid.
-As a reminder, five different reselection intervals are considered.
-These include reselection intervals of 1, 5, 10, 15, and 20.
-Experiments are denoted as such.
-
-Table~\ref{tab:results:reselection:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the reselection interval variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average test loss and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-	\label{tab:results:reselection:metrics:loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Reselection - Average Test Loss}}                                                                                                                                                                                                                                         \\
-			\midrule
-			\textbf{dataset}             & \textbf{1}                                                   & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}2.737 ($\pm$0.507)        & \cellcolor[rgb]{ 1,  .922,  .518}2.0907 ($\pm$0.113)    & \cellcolor[rgb]{ .545,  .788,  .49}2.0587 ($\pm$0.088)  & \cellcolor[rgb]{ .388,  .745,  .482}2.0475 ($\pm$0.103) & \cellcolor[rgb]{ 1,  .906,  .518}2.1139 ($\pm$0.336)    \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.3003 ($\pm$0.046)       & \cellcolor[rgb]{ .992,  .725,  .482}0.2835 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 ($\pm$0.016)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2619 ($\pm$0.013) & \cellcolor[rgb]{ .486,  .773,  .486}0.2637 ($\pm$0.016) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .984,  .596,  .455}0.2933 ($\pm$0.033)      & \cellcolor[rgb]{ .973,  .412,  .42}0.3198 ($\pm$0.18)   & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .553,  .792,  .49}0.2299 ($\pm$0.032)  & \cellcolor[rgb]{ .388,  .745,  .482}0.224 ($\pm$0.018)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}0.1524 ($\pm$0.023)       & \cellcolor[rgb]{ .988,  .671,  .471}0.1084 ($\pm$0.025) & \cellcolor[rgb]{ 1,  .922,  .518}0.0651 ($\pm$0.02)     & \cellcolor[rgb]{ .6,  .804,  .494}0.0566 ($\pm$0.01)    & \cellcolor[rgb]{ .388,  .745,  .482}0.052 ($\pm$0.004)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .973,  .412,  .42}0.2157 ($\pm$0.031)       & \cellcolor[rgb]{ 1,  .922,  .518}0.1591 ($\pm$0.026)    & \cellcolor[rgb]{ .91,  .894,  .51}0.1572 ($\pm$0.034)   & \cellcolor[rgb]{ 1,  .863,  .51}0.1659 ($\pm$0.064)     & \cellcolor[rgb]{ .388,  .745,  .482}0.1456 ($\pm$0.03)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}0.9624 ($\pm$0.043)      & \cellcolor[rgb]{ .973,  .412,  .42}3.7821 ($\pm$4.993)  & \cellcolor[rgb]{ 1,  .914,  .518}1.2983 ($\pm$0.66)     & \cellcolor[rgb]{ 1,  .922,  .518}1.2541 ($\pm$0.868)    & \cellcolor[rgb]{ .482,  .773,  .486}1.0085 ($\pm$0.251) \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}0.1091 ($\pm$0.01)        & \cellcolor[rgb]{ 1,  .922,  .518}0.1043 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .894,  .514}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1013 ($\pm$0.008) & \cellcolor[rgb]{ .549,  .792,  .49}0.1021 ($\pm$0.008)  \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.1253 ($\pm$0.087)       & \cellcolor[rgb]{ .988,  .702,  .478}0.1002 ($\pm$0.064) & \cellcolor[rgb]{ 1,  .922,  .518}0.081 ($\pm$0.069)     & \cellcolor[rgb]{ .647,  .82,  .494}0.0681 ($\pm$0.055)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.056) \\
-			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}0.1268 ($\pm$0.025)       & \cellcolor[rgb]{ 1,  .902,  .514}0.0974 ($\pm$0.017)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.0961 ($\pm$0.026)    & \cellcolor[rgb]{ .729,  .843,  .502}0.0952 ($\pm$0.02)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .714,  .839,  .498}0.1633 ($\pm$0.135)      & \cellcolor[rgb]{ .388,  .745,  .482}0.1376 ($\pm$0.138) & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 ($\pm$0.295)  & \cellcolor[rgb]{ .976,  .447,  .427}0.2373 ($\pm$0.361) & \cellcolor[rgb]{ 1,  .922,  .518}0.1853 ($\pm$0.235)    \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .973,  .412,  .42}1.8461 ($\pm$5.829)       & \cellcolor[rgb]{ .886,  .886,  .51}0.0283 ($\pm$0.099)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ 1,  .922,  .518}0.0388 ($\pm$0.111)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0335 ($\pm$0.158)    \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .973,  .412,  .42}0.0872 ($\pm$0.018)       & \cellcolor[rgb]{ 1,  .886,  .514}0.0609 ($\pm$0.004)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0587 ($\pm$0.003)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0584 ($\pm$0.002) & \cellcolor[rgb]{ .482,  .769,  .486}0.0585 ($\pm$0.003) \\
-			\textbf{student performance} & \cellcolor[rgb]{ .973,  .412,  .42}0.4376 ($\pm$0.108)       & \cellcolor[rgb]{ .98,  .518,  .443}0.397 ($\pm$0.13)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)    & \cellcolor[rgb]{ .784,  .859,  .502}0.223 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1991 ($\pm$0.064) \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}1.1183 ($\pm$0.031)       & \cellcolor[rgb]{ 1,  .922,  .518}1.081 ($\pm$0.023)     & \cellcolor[rgb]{ 1,  .898,  .514}1.0827 ($\pm$0.026)    & \cellcolor[rgb]{ .388,  .745,  .482}1.0711 ($\pm$0.028) & \cellcolor[rgb]{ .498,  .776,  .486}1.0729 ($\pm$0.022) \\
-		\end{tabular}%
-	}
-\end{table}%
-
-From Table~\ref{tab:results:reselection:metrics:loss}, a clear pattern can be observed.
-The empirical results show that, in general, a larger reselection interval is preferred, with the largest reselection intervals yielding the best performance outcomes in the majority of cases, and the lowest reselection interval of one, yielding the worst performance in the majority of cases.
-
-To illustrate the effects of the reselection interval hyper-paramter on the entire trianing, process, Table \ref{tab:results:reselection:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} reselection interval configurations.
-Similar to before, the performance rank is calculated as the average rank produced by reselection interval configuration, for all datasets, over all independent runs and epochs.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:reselection:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Reselection - Average Rank}}                                                                                                                                                                                                                                         \\
-			\midrule
-			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}4.3548 ($\pm$0.976)  & \cellcolor[rgb]{ 1,  .894,  .514}2.8473 ($\pm$1.288)    & \cellcolor[rgb]{ 1,  .922,  .518}2.7505 ($\pm$1.262)    & \cellcolor[rgb]{ .557,  .792,  .49}2.5602 ($\pm$1.299)  & \cellcolor[rgb]{ .388,  .745,  .482}2.4871 ($\pm$1.318) \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.7355 ($\pm$1.405)  & \cellcolor[rgb]{ .984,  .631,  .463}3.4075 ($\pm$1.379) & \cellcolor[rgb]{ 1,  .922,  .518}2.9688 ($\pm$1.278)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4237 ($\pm$1.228) & \cellcolor[rgb]{ .431,  .757,  .482}2.4645 ($\pm$1.291) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}4.5677 ($\pm$0.704)  & \cellcolor[rgb]{ .988,  .635,  .463}3.6323 ($\pm$1.127) & \cellcolor[rgb]{ 1,  .922,  .518}2.4237 ($\pm$1.133)    & \cellcolor[rgb]{ .627,  .812,  .494}2.2462 ($\pm$1.114) & \cellcolor[rgb]{ .388,  .745,  .482}2.1301 ($\pm$1.096) \\
-			\textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}4.7935 ($\pm$0.612)  & \cellcolor[rgb]{ .984,  .608,  .459}3.9204 ($\pm$0.648) & \cellcolor[rgb]{ 1,  .922,  .518}2.5161 ($\pm$0.863)    & \cellcolor[rgb]{ .671,  .824,  .498}2.0763 ($\pm$0.901) & \cellcolor[rgb]{ .388,  .745,  .482}1.6935 ($\pm$0.891) \\
-			\textbf{car}                 & \cellcolor[rgb]{ .973,  .412,  .42}4.6409 ($\pm$0.785)  & \cellcolor[rgb]{ .996,  .847,  .506}2.9527 ($\pm$1.158) & \cellcolor[rgb]{ 1,  .922,  .518}2.6548 ($\pm$1.175)    & \cellcolor[rgb]{ .824,  .871,  .506}2.5312 ($\pm$1.244) & \cellcolor[rgb]{ .388,  .745,  .482}2.2204 ($\pm$1.217) \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ 1,  .859,  .506}3.0129 ($\pm$1.048)    & \cellcolor[rgb]{ .973,  .412,  .42}4.4624 ($\pm$0.869)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7957 ($\pm$1.175)    & \cellcolor[rgb]{ .827,  .871,  .506}2.6065 ($\pm$1.439) & \cellcolor[rgb]{ .388,  .745,  .482}2.1226 ($\pm$1.264) \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}3.7484 ($\pm$1.238)  & \cellcolor[rgb]{ .996,  .851,  .506}3.1376 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}3.0344 ($\pm$1.406)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4656 ($\pm$1.304) & \cellcolor[rgb]{ .545,  .788,  .49}2.614 ($\pm$1.432)   \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}3.8194 ($\pm$1.433)  & \cellcolor[rgb]{ .992,  .706,  .478}3.272 ($\pm$1.248)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8656 ($\pm$1.346)    & \cellcolor[rgb]{ .953,  .906,  .514}2.8194 ($\pm$1.305) & \cellcolor[rgb]{ .388,  .745,  .482}2.2237 ($\pm$1.219) \\
-			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}4.1892 ($\pm$1.099)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0172 ($\pm$1.288) & \cellcolor[rgb]{ .624,  .812,  .494}2.5871 ($\pm$1.354) & \cellcolor[rgb]{ .388,  .745,  .482}2.5312 ($\pm$1.265) & \cellcolor[rgb]{ 1,  .922,  .518}2.6753 ($\pm$1.34)     \\
-			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.424)    & \cellcolor[rgb]{ .973,  .914,  .514}2.971 ($\pm$1.317)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3462 ($\pm$1.418)  & \cellcolor[rgb]{ 1,  .882,  .51}3.014 ($\pm$1.405)      & \cellcolor[rgb]{ .388,  .745,  .482}2.6849 ($\pm$1.429) \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .973,  .412,  .42}4.2065 ($\pm$1.236)  & \cellcolor[rgb]{ 1,  .859,  .506}2.9688 ($\pm$1.299)    & \cellcolor[rgb]{ .631,  .816,  .494}2.586 ($\pm$1.234)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7882 ($\pm$1.34)     & \cellcolor[rgb]{ .388,  .745,  .482}2.4505 ($\pm$1.226) \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .973,  .412,  .42}4.7645 ($\pm$0.756)  & \cellcolor[rgb]{ .992,  .769,  .49}3.1882 ($\pm$1.021)  & \cellcolor[rgb]{ .49,  .773,  .486}2.2957 ($\pm$1.209)  & \cellcolor[rgb]{ 1,  .922,  .518}2.4968 ($\pm$1.128)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2548 ($\pm$1.097) \\
-			\textbf{student performance} & \cellcolor[rgb]{ .976,  .431,  .424}3.971 ($\pm$1.094)  & \cellcolor[rgb]{ .973,  .412,  .42}4.0226 ($\pm$1.12)   & \cellcolor[rgb]{ 1,  .922,  .518}2.4774 ($\pm$1.221)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2495 ($\pm$1.2)   & \cellcolor[rgb]{ .467,  .765,  .486}2.2796 ($\pm$1.132) \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}4.0688 ($\pm$1.122)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9204 ($\pm$1.293)    & \cellcolor[rgb]{ 1,  .906,  .518}2.9559 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4032 ($\pm$1.378) & \cellcolor[rgb]{ .678,  .827,  .498}2.6516 ($\pm$1.28)  \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .973,  .412,  .42}4.0612 ($\pm$1.229)  & \cellcolor[rgb]{ .988,  .69,  .475}3.3372 ($\pm$1.277)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7327 ($\pm$1.283)    & \cellcolor[rgb]{ .647,  .82,  .494}2.5151 ($\pm$1.282)  & \cellcolor[rgb]{ .388,  .745,  .482}2.3538 ($\pm$1.266) \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-Table \ref{tab:results:reselection:metrics:rank} shows that larger reselection intervals are mostly preferred.
-The overall normalised average rank is given at the bottom of the table and supports this finding.
-This outcome can be explained as follows.
-A larger reselection interval gives the low-level \index{heuristic}heuristics more time to execute, resulting in smoother update steps and provides an opportunity for the \acs{BHH} to gather more evidence of the current selection of \index{heuristic}heuristics' performance in the performance log.
-Both of these effects allow the \acs{BHH} to select better \index{heuristic}heuristics during training.
-This is further supported by the findings from Sections \ref{sec:results:standalone} and \ref{sec:results:heuristic_pool}, that show that gradient-based \index{heuristic}heuristics generally yield the best performance.
-Most of the gradient-based \index{heuristic}heuristics that are included in the \index{heuristic pool }heuristic pool implement exponentially averaged state parameters in order to produce smooth update steps.
-If reselection occurs too frequently these exponentially averaged state parameters do not yield smooth update steps.
-This is further supported by the inclusion of meta-heuristics such as \acp{GA} and \acs{DE}, which recombine state parameters.
-
-Finally, it should be noted that the default reanalysis interval is ten and the default replay window size is also ten.
-At every reanalysis interval, the concentrations for low-level \index{heuristic}heuristics are reset to the default, symmetrical value of 1.0.
-The replay window size then determines the number of samples in the performance log from which the reanalysis can be done.
-As such, \acs{BHH} configurations with reselection intervals that are larger than the replay window size, will only consider performance samples from the last replay window, which should contain less entries than the reselection interval.
-The reselection interval then directly influences what goes into the performance log.
-Since it is found that reselection intervals larger than the default reanalysis interval and replay window size yield better performance, it can be suggested that exploitation of low-level \index{heuristic}heuristics yields better results than exploration of low-level \index{heuristic}heuristics.
-
-Furthermore, early in the training process, a low reselection interval yields the highest variance of \index{heuristic}heuristic selection.
-Since the default population size is five and the default number of heuristics in the heuristic pool is thirteen, not all heuristics are represented at every training step, causing an unwanted bias towards the \index{heuristic}heuristics that happen to be             selected.
-
-Figure~\ref{fig:results:credit:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reselection interval configurations, per dataset.
-It can be seen that a general pattern occurs for almost all datasets that show an inverse correlation between performance and the reselection interval.
-Some exceptions of this relationship can be observed for the iris and diabetic datasets where an average reselection interval yielded the best results.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reselection interval values per dataset, across all independent runs and epochs.}
-	\label{fig:results:reselection:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:reselection:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reselection interval configuration as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_reselection/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reselection interval values across all datasets, runs and epochs.}
-	\label{fig:results:reselection:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:reselection:descriptive:cd} shows the statistically significant difference in overall results for the various reselection intervals across all datasets.
-It can be seen that larger reselection intervals statistically perform better than smaller reselection intervals.
-The largest reselection intervals (15 and 20) yielded the best overall results with statistically insignificant differences between them.
-
-Similar to before, Figure~\ref{fig:results:reselection:figures:car} provides the train and test, loss and accuracy plots for an example classification dataset (car) as it relates to the reselection interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/car.pdf}
-		\caption{Train log loss}
-		\label{fig:results:reselection:figures:loss:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/car.pdf}
-		\caption{Test log loss}
-		\label{fig:results:reselection:figures:loss:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/accuracy/car.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:reselection:figures:accuracy:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/accuracy/car.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:reselection:figures:accuracy:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the car dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:reselection:figures:car}
-\end{figure}
-
-Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plots for an example regression dataset (bike) as it relates to the reselection interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/bike.pdf}
-		\caption{Train log loss}
-		\label{fig:results:reselection:figures:loss:train:bike}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/bike.pdf}
-		\caption{Test log loss}
-		\label{fig:results:reselection:figures:loss:test:bike}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the bike dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:reselection:figures:bike}
-\end{figure}
-
-Figures~\ref{fig:results:reselection:figures:loss:train:car} and ~\ref{fig:results:reselection:figures:loss:train:bike} both show a smooth decline in training loss for all reselection interval configurations of the \acs{BHH}, but larger reselection interval configurations are able to provide better results than lower reselection intervals.
-This further supports the suggestion that exploitation of low-level \index{heuristic}heuristics is more important than exploration of low-level \index{heuristic}heuristics in this particular case.
-
-\section{Replay Window Size}\label{sec:results:replay}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{replay window size} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, five different replay window sizes are considered.
-These include replay window sizes of 1, 5, 10, 15, and 20.
-Experiments are denoted as such.
-
-As before, Table~\ref{tab:results:replay:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the replay window size variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average test loss and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-	\label{tab:results:replay:metrics:loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Replay - Average Test Loss}}                                                                                                                                                                                                                                         \\
-			\midrule
-			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}2.136 ($\pm$0.088)   & \cellcolor[rgb]{ .388,  .745,  .482}2.0424 ($\pm$0.47)  & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.135)    & \cellcolor[rgb]{ .863,  .878,  .506}2.0551 ($\pm$0.159) & \cellcolor[rgb]{ .976,  .455,  .427}2.1299 ($\pm$0.292) \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .525,  .784,  .49}0.2676 ($\pm$0.016)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2687 ($\pm$0.014)    & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)  & \cellcolor[rgb]{ .992,  .722,  .482}0.2703 ($\pm$0.015) & \cellcolor[rgb]{ .388,  .745,  .482}0.2673 ($\pm$0.011) \\
-			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2358 ($\pm$0.065)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2347 ($\pm$0.022) & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.019)  & \cellcolor[rgb]{ .996,  .839,  .502}0.2374 ($\pm$0.037) & \cellcolor[rgb]{ .965,  .91,  .514}0.2358 ($\pm$0.025)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .522,  .78,  .486}0.0568 ($\pm$0.02)   & \cellcolor[rgb]{ .388,  .745,  .482}0.0552 ($\pm$0.007) & \cellcolor[rgb]{ .973,  .412,  .42}0.0651 ($\pm$0.004)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0625 ($\pm$0.019)    & \cellcolor[rgb]{ .976,  .443,  .427}0.065 ($\pm$0.018)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ 1,  .878,  .51}0.1605 ($\pm$0.034)     & \cellcolor[rgb]{ .388,  .745,  .482}0.1537 ($\pm$0.05)  & \cellcolor[rgb]{ .733,  .843,  .502}0.1572 ($\pm$0.026) & \cellcolor[rgb]{ .973,  .412,  .42}0.1671 ($\pm$0.056)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1599 ($\pm$0.028)    \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .996,  .8,  .494}1.3315 ($\pm$0.66)    & \cellcolor[rgb]{ .918,  .894,  .51}1.2672 ($\pm$0.691)  & \cellcolor[rgb]{ 1,  .922,  .518}1.2983 ($\pm$0.534)    & \cellcolor[rgb]{ .388,  .745,  .482}1.0647 ($\pm$0.22)  & \cellcolor[rgb]{ .973,  .412,  .42}1.4342 ($\pm$1.399)  \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1028 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .749,  .486}0.1055 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.012)    & \cellcolor[rgb]{ .604,  .808,  .494}0.1034 ($\pm$0.011) & \cellcolor[rgb]{ .973,  .412,  .42}0.1074 ($\pm$0.012)  \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .988,  .663,  .471}0.0935 ($\pm$0.069) & \cellcolor[rgb]{ 1,  .922,  .518}0.0814 ($\pm$0.078)    & \cellcolor[rgb]{ .863,  .882,  .51}0.081 ($\pm$0.073)   & \cellcolor[rgb]{ .388,  .745,  .482}0.0794 ($\pm$0.063) & \cellcolor[rgb]{ .973,  .412,  .42}0.105 ($\pm$0.068)   \\
-			\textbf{housing}             & \cellcolor[rgb]{ .992,  .745,  .486}0.0979 ($\pm$0.017) & \cellcolor[rgb]{ .467,  .769,  .486}0.0944 ($\pm$0.015) & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.0967 ($\pm$0.022)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1002 ($\pm$0.024)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .443,  .761,  .482}0.1577 ($\pm$0.295) & \cellcolor[rgb]{ .973,  .412,  .42}0.295 ($\pm$0.16)    & \cellcolor[rgb]{ .996,  .784,  .494}0.2411 ($\pm$0.546) & \cellcolor[rgb]{ .388,  .745,  .482}0.1514 ($\pm$0.192) & \cellcolor[rgb]{ 1,  .922,  .518}0.2208 ($\pm$0.349)    \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .722,  .839,  .498}0.0504 ($\pm$0.012) & \cellcolor[rgb]{ 1,  .922,  .518}0.0881 ($\pm$0.239)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.336) & \cellcolor[rgb]{ .973,  .412,  .42}0.4733 ($\pm$2.385)  & \cellcolor[rgb]{ 1,  .855,  .506}0.139 ($\pm$0.62)      \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .973,  .412,  .42}0.0596 ($\pm$0.003)  & \cellcolor[rgb]{ .576,  .8,  .49}0.0589 ($\pm$0.003)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .976,  .424,  .424}0.0596 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0594 ($\pm$0.003)    \\
-			\textbf{student performance} & \cellcolor[rgb]{ .996,  .792,  .494}0.2529 ($\pm$0.102) & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.103)    & \cellcolor[rgb]{ .42,  .753,  .482}0.2359 ($\pm$0.093)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2354 ($\pm$0.083) & \cellcolor[rgb]{ .973,  .412,  .42}0.2739 ($\pm$0.126)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}1.0876 ($\pm$0.026)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0756 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}1.0827 ($\pm$0.022)    & \cellcolor[rgb]{ .98,  .522,  .443}1.0866 ($\pm$0.039)  & \cellcolor[rgb]{ .482,  .773,  .486}1.0767 ($\pm$0.022) \\
-		\end{tabular}%
-	}
-\end{table}%
-
-Table \ref{tab:results:replay:metrics:rank} provides the average ranked performance, per dataset, for each of the \acs{BHH} replay window size configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all independent runs and epochs.
-The overall normalised average rank is provided at the end of the table.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:replay:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Replay - Average Rank}}                                                                                                                                                                                                                                              \\
-			\midrule
-			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}3.0258 ($\pm$1.382)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6785 ($\pm$1.455) & \cellcolor[rgb]{ .973,  .412,  .42}3.1968 ($\pm$1.346)  & \cellcolor[rgb]{ .992,  .729,  .482}3.0903 ($\pm$1.385) & \cellcolor[rgb]{ .969,  .91,  .514}3.0086 ($\pm$1.45)   \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.8742 ($\pm$1.385) & \cellcolor[rgb]{ 1,  .871,  .51}3.0151 ($\pm$1.497)     & \cellcolor[rgb]{ 1,  .922,  .518}2.9978 ($\pm$1.429)    & \cellcolor[rgb]{ .765,  .851,  .502}2.9505 ($\pm$1.297) & \cellcolor[rgb]{ .973,  .412,  .42}3.1624 ($\pm$1.443)  \\
-			\textbf{bank}                & \cellcolor[rgb]{ .729,  .843,  .502}2.9484 ($\pm$1.46)  & \cellcolor[rgb]{ .992,  .722,  .482}3.057 ($\pm$1.473)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8602 ($\pm$1.344) & \cellcolor[rgb]{ 1,  .922,  .518}3.0172 ($\pm$1.42)     & \cellcolor[rgb]{ .973,  .412,  .42}3.1172 ($\pm$1.359)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}2.9602 ($\pm$1.274)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7366 ($\pm$1.34)  & \cellcolor[rgb]{ .984,  .58,  .455}3.1452 ($\pm$1.448)  & \cellcolor[rgb]{ .894,  .89,  .51}2.9226 ($\pm$1.417)   & \cellcolor[rgb]{ .973,  .412,  .42}3.2355 ($\pm$1.527)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.7054 ($\pm$1.357) & \cellcolor[rgb]{ .62,  .812,  .494}2.8376 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .882,  .51}3.0763 ($\pm$1.372)     & \cellcolor[rgb]{ .973,  .412,  .42}3.3269 ($\pm$1.463)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0538 ($\pm$1.409)    \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .98,  .545,  .447}3.2473 ($\pm$1.369)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3247 ($\pm$1.406)  & \cellcolor[rgb]{ .388,  .745,  .482}2.5935 ($\pm$1.372) & \cellcolor[rgb]{ .69,  .831,  .498}2.8075 ($\pm$1.384)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0269 ($\pm$1.411)    \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.7269 ($\pm$1.419) & \cellcolor[rgb]{ .992,  .753,  .486}3.0785 ($\pm$1.49)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1774 ($\pm$1.398)  & \cellcolor[rgb]{ .918,  .898,  .51}2.9892 ($\pm$1.386)  & \cellcolor[rgb]{ 1,  .922,  .518}3.028 ($\pm$1.337)     \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8054 ($\pm$1.493) & \cellcolor[rgb]{ .745,  .847,  .502}2.9151 ($\pm$1.381) & \cellcolor[rgb]{ 1,  .922,  .518}2.9914 ($\pm$1.408)    & \cellcolor[rgb]{ .996,  .776,  .49}3.0591 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.229 ($\pm$1.342)   \\
-			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}3.1548 ($\pm$1.301)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.407)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8548 ($\pm$1.45)  & \cellcolor[rgb]{ .992,  .757,  .486}3.0355 ($\pm$1.49)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.404)    \\
-			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}3.072 ($\pm$1.376)     & \cellcolor[rgb]{ .984,  .627,  .463}3.1581 ($\pm$1.419) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.392)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6183 ($\pm$1.396) & \cellcolor[rgb]{ .808,  .867,  .506}2.9312 ($\pm$1.41)  \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .863,  .51}3.0538 ($\pm$1.324)     & \cellcolor[rgb]{ .973,  .412,  .42}3.143 ($\pm$1.437)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0419 ($\pm$1.414)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8613 ($\pm$1.382) & \cellcolor[rgb]{ .502,  .776,  .486}2.8957 ($\pm$1.497) \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .984,  .561,  .451}3.172 ($\pm$1.372)  & \cellcolor[rgb]{ .62,  .812,  .494}2.843 ($\pm$1.244)   & \cellcolor[rgb]{ .388,  .745,  .482}2.6731 ($\pm$1.453) & \cellcolor[rgb]{ 1,  .922,  .518}3.1172 ($\pm$1.419)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1946 ($\pm$1.498)  \\
-			\textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}3.0398 ($\pm$1.368)    & \cellcolor[rgb]{ .812,  .867,  .506}2.9226 ($\pm$1.411) & \cellcolor[rgb]{ .388,  .745,  .482}2.6548 ($\pm$1.403) & \cellcolor[rgb]{ .996,  .812,  .498}3.0935 ($\pm$1.323) & \cellcolor[rgb]{ .973,  .412,  .42}3.2892 ($\pm$1.487)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}3.1742 ($\pm$1.43)   & \cellcolor[rgb]{ .388,  .745,  .482}2.7323 ($\pm$1.456) & \cellcolor[rgb]{ .976,  .475,  .435}3.1581 ($\pm$1.418) & \cellcolor[rgb]{ 1,  .922,  .518}3.0419 ($\pm$1.356)    & \cellcolor[rgb]{ .706,  .835,  .498}2.8935 ($\pm$1.362) \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ 1,  .91,  .518}2.9972 ($\pm$1.389)     & \cellcolor[rgb]{ .388,  .745,  .482}2.9585 ($\pm$1.426) & \cellcolor[rgb]{ .651,  .82,  .494}2.9744 ($\pm$1.418)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9951 ($\pm$1.404)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0745 ($\pm$1.43)   \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-Tables \ref{tab:results:replay:metrics:loss} and \ref{tab:results:replay:metrics:rank} shows that there is no clear overall best performing replay window size configuration of the \acs{BHH}, for all datasets.
-In some cases, a replay window size of one yielded the best results.
-A replay window of one simply considers the last step in the training process.
-This means that memory of past performance actually had a negative impact on the training process in those particular cases.
-It should also be observed that the largest replay window size yielded the worst performance overall and also for the most datasets.
-This suggests that \index{heuristic}heuristic selection is more likely to benefit from short, recent observations in the training process.
-From these observations it can be concluded that past performances of the \index{heuristic}heuristics are not always beneficial to the training process, and that the replay window size is problem specific.
-Furthermore, it can be concluded that some problems require more exploration of the \index{heuristic}heuristic space, while other problem sets require more exploitation of low-level \index{heuristic}heuristics.
-
-Figure~\ref{fig:results:replay:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different replay window size configurations, per dataset.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_replay/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying replay window sizes per dataset, across all independent runs and epochs.}
-	\label{fig:results:replay:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:replay:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each replay window size configuration as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_replay/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying replay window sizes across all datasets, runs and epochs.}
-	\label{fig:results:replay:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:replay:descriptive:cd} shows no overall statistically significant difference in results for the various replay window size configurations as it relates to all datasets.
-
-Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test, loss and accuracy plots for an example classification dataset (diabetic) as it relates to the replay window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/diabetic.pdf}
-		\caption{Train log loss}
-		\label{fig:results:replay:figures:loss:train:diabetic}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/diabetic.pdf}
-		\caption{Test log loss}
-		\label{fig:results:replay:figures:loss:test:diabetic}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_replay/figures/train/accuracy/diabetic.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:replay:figures:accuracy:train:diabetic}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_replay/figures/test/accuracy/diabetic.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:replay:figures:accuracy:test:diabetic}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:replay:figures:diabetic}
-\end{figure}
-
-Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plots for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/fish_toxicity.pdf}
-		\caption{Train log loss}
-		\label{fig:results:replay:figures:loss:train:fish_toxicity}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/fish_toxicity.pdf}
-		\caption{Test log loss}
-		\label{fig:results:replay:figures:loss:test:fish_toxicity}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:replay:figures:fish_toxicity}
-\end{figure}
-
-The divergence that can be seen in Figure~\ref{fig:results:replay:figures:loss:train:diabetic} and \ref{fig:results:replay:figures:loss:test:diabetic} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results, when an optimal solution has already been found.
-As mentioned before, an early stopping strategy as well as a move-acceptance strategy can be incorporated to avoid this effect.
-
-\section{Reanalysis Interval}\label{sec:results:reanalysis}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{reanalysis interval} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, five different reanalysis intervals are considered.
-These include reanalysis intervals of 1, 5, 10, 15, and 20.
-Experiments are denoted as such.
-
-As before, Table~\ref{tab:results:reanalysis:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the reanalysis interval variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average test loss and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-	\label{tab:results:reanalysis:metrics:loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|lllll}
-			                             & \multicolumn{5}{c}{\textbf{Reanalysis - Average Test Loss}}                                                                                                                                                                                                                                        \\
-			\midrule
-			\textbf{dataset}             & \multicolumn{1}{c}{\textbf{1}}                              & \multicolumn{1}{c}{\textbf{5}}                          & \multicolumn{1}{c}{\textbf{10}}                         & \multicolumn{1}{c}{\textbf{15}}                        & \multicolumn{1}{c}{\textbf{20}}                         \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.0571 ($\pm$0.102)        & \cellcolor[rgb]{ .388,  .745,  .482}2.0424 ($\pm$0.071) & \cellcolor[rgb]{ 1,  .898,  .514}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .973,  .412,  .42}2.0879 ($\pm$0.226) & \cellcolor[rgb]{ .518,  .78,  .486}2.0456 ($\pm$0.079)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2682 ($\pm$0.014)        & \cellcolor[rgb]{ .388,  .745,  .482}0.2637 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)  & \cellcolor[rgb]{ .98,  .525,  .443}0.2718 ($\pm$0.019) & \cellcolor[rgb]{ .584,  .8,  .49}0.2651 ($\pm$0.012)    \\
-			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2599 ($\pm$0.114)      & \cellcolor[rgb]{ .698,  .831,  .498}0.2406 ($\pm$0.023) & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .984,  .624,  .463}0.254 ($\pm$0.047) & \cellcolor[rgb]{ .388,  .745,  .482}0.2353 ($\pm$0.025) \\
-			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0621 ($\pm$0.016)     & \cellcolor[rgb]{ 1,  .922,  .518}0.0627 ($\pm$0.021)    & \cellcolor[rgb]{ .984,  .584,  .455}0.0651 ($\pm$0.02)  & \cellcolor[rgb]{ .973,  .412,  .42}0.0663 ($\pm$0.023) & \cellcolor[rgb]{ .765,  .851,  .502}0.0625 ($\pm$0.02)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ 1,  .922,  .518}0.1597 ($\pm$0.042)        & \cellcolor[rgb]{ .388,  .745,  .482}0.1535 ($\pm$0.038) & \cellcolor[rgb]{ .749,  .847,  .502}0.1572 ($\pm$0.034) & \cellcolor[rgb]{ .973,  .412,  .42}0.1667 ($\pm$0.036) & \cellcolor[rgb]{ .984,  .58,  .455}0.1644 ($\pm$0.04)   \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.482 ($\pm$1.563)       & \cellcolor[rgb]{ .984,  .62,  .463}1.4074 ($\pm$1.558)  & \cellcolor[rgb]{ 1,  .922,  .518}1.2983 ($\pm$0.66)     & \cellcolor[rgb]{ .388,  .745,  .482}1.222 ($\pm$0.6)   & \cellcolor[rgb]{ .969,  .91,  .514}1.2944 ($\pm$0.832)  \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .961,  .91,  .514}0.1031 ($\pm$0.01)       & \cellcolor[rgb]{ 1,  .922,  .518}0.1033 ($\pm$0.008)    & \cellcolor[rgb]{ .988,  .694,  .475}0.1046 ($\pm$0.008) & \cellcolor[rgb]{ .973,  .412,  .42}0.1062 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.1004 ($\pm$0.009) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.1083 ($\pm$0.1)        & \cellcolor[rgb]{ .988,  .675,  .471}0.1003 ($\pm$0.069) & \cellcolor[rgb]{ .388,  .745,  .482}0.081 ($\pm$0.069)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0927 ($\pm$0.069)   & \cellcolor[rgb]{ .451,  .761,  .482}0.0822 ($\pm$0.059) \\
-			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}0.0998 ($\pm$0.017)      & \cellcolor[rgb]{ .745,  .847,  .502}0.0953 ($\pm$0.017) & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .918,  .518}0.0963 ($\pm$0.029)   & \cellcolor[rgb]{ 1,  .922,  .518}0.0962 ($\pm$0.011)    \\
-			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.582 ($\pm$2.084)       & \cellcolor[rgb]{ .604,  .804,  .494}0.164 ($\pm$0.154)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2411 ($\pm$0.295)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1218 ($\pm$0.11) & \cellcolor[rgb]{ 1,  .882,  .514}0.2674 ($\pm$0.545)    \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .996,  .796,  .494}0.0548 ($\pm$0.241)     & \cellcolor[rgb]{ .973,  .412,  .42}0.1165 ($\pm$0.597)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ 1,  .922,  .518}0.0344 ($\pm$0.102)   & \cellcolor[rgb]{ .655,  .82,  .494}0.0181 ($\pm$0.059)  \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ 1,  .922,  .518}0.0597 ($\pm$0.003)        & \cellcolor[rgb]{ .769,  .855,  .502}0.0593 ($\pm$0.002) & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.06 ($\pm$0.004)   & \cellcolor[rgb]{ 1,  .918,  .518}0.0597 ($\pm$0.003)    \\
-			\textbf{student performance} & \cellcolor[rgb]{ .992,  .741,  .486}0.2331 ($\pm$0.083)     & \cellcolor[rgb]{ .725,  .839,  .498}0.2297 ($\pm$0.09)  & \cellcolor[rgb]{ .973,  .412,  .42}0.2359 ($\pm$0.102)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2315 ($\pm$0.063)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2274 ($\pm$0.098) \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0728 ($\pm$0.026)     & \cellcolor[rgb]{ 1,  .922,  .518}1.0818 ($\pm$0.028)    & \cellcolor[rgb]{ 1,  .871,  .51}1.0827 ($\pm$0.026)     & \cellcolor[rgb]{ .514,  .78,  .486}1.0747 ($\pm$0.026) & \cellcolor[rgb]{ .973,  .412,  .42}1.0909 ($\pm$0.042)  \\
-		\end{tabular}%
-	}
-\end{table}%
-
-Table \ref{tab:results:reanalysis:metrics:rank} provides the average ranked performance, per dataset, for each of the \acs{BHH} reanalysis interval configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the reanalysis interval configurations, for all datasets, over all independent runs and epochs.
-The overall normalised average ranks are provided at the bottom of the table.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:reanalysis:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Reanalysis - Average Rank}}                                                                                                                                                                                                                                          \\
-			\midrule
-			\textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.9849 ($\pm$1.397)    & \cellcolor[rgb]{ .988,  .69,  .475}3.0699 ($\pm$1.442)  & \cellcolor[rgb]{ .973,  .412,  .42}3.171 ($\pm$1.32)    & \cellcolor[rgb]{ .835,  .875,  .506}2.9441 ($\pm$1.445) & \cellcolor[rgb]{ .388,  .745,  .482}2.8301 ($\pm$1.443) \\
-			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9613 ($\pm$1.344)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8387 ($\pm$1.438) & \cellcolor[rgb]{ .973,  .412,  .42}3.2559 ($\pm$1.402)  & \cellcolor[rgb]{ .992,  .765,  .49}3.0538 ($\pm$1.42)   & \cellcolor[rgb]{ .643,  .816,  .494}2.8903 ($\pm$1.43)  \\
-			\textbf{bank}                & \cellcolor[rgb]{ .988,  .647,  .467}3.1161 ($\pm$1.432) & \cellcolor[rgb]{ 1,  .922,  .518}3.0452 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7355 ($\pm$1.398) & \cellcolor[rgb]{ .765,  .851,  .502}2.928 ($\pm$1.403)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1753 ($\pm$1.415)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .988,  .698,  .475}3.1409 ($\pm$1.258) & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.391) & \cellcolor[rgb]{ .973,  .412,  .42}3.1946 ($\pm$1.365)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0978 ($\pm$1.498)    & \cellcolor[rgb]{ .478,  .769,  .486}2.8086 ($\pm$1.491) \\
-			\textbf{car}                 & \cellcolor[rgb]{ 1,  .906,  .518}3.1237 ($\pm$1.423)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7237 ($\pm$1.358) & \cellcolor[rgb]{ .62,  .812,  .494}2.8763 ($\pm$1.299)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1538 ($\pm$1.385)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1226 ($\pm$1.547)    \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}3.2452 ($\pm$1.305)  & \cellcolor[rgb]{ .996,  .824,  .502}3.072 ($\pm$1.391)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7785 ($\pm$1.407) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.425)     & \cellcolor[rgb]{ .624,  .812,  .494}2.8753 ($\pm$1.494) \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .992,  .725,  .482}3.1452 ($\pm$1.362) & \cellcolor[rgb]{ .894,  .89,  .51}3.0032 ($\pm$1.445)   & \cellcolor[rgb]{ .973,  .412,  .42}3.2172 ($\pm$1.364)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1 ($\pm$1.409)       & \cellcolor[rgb]{ .388,  .745,  .482}2.5344 ($\pm$1.388) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8398 ($\pm$1.369) & \cellcolor[rgb]{ .98,  .51,  .439}3.1215 ($\pm$1.471)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0043 ($\pm$1.318)    & \cellcolor[rgb]{ .557,  .792,  .49}2.886 ($\pm$1.354)   & \cellcolor[rgb]{ .973,  .412,  .42}3.1484 ($\pm$1.526)  \\
-			\textbf{housing}             & \cellcolor[rgb]{ .976,  .416,  .424}3.3129 ($\pm$1.311) & \cellcolor[rgb]{ 1,  .922,  .518}2.9892 ($\pm$1.393)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6871 ($\pm$1.483) & \cellcolor[rgb]{ .404,  .749,  .482}2.6968 ($\pm$1.496) & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.236)   \\
-			\textbf{iris}                & \cellcolor[rgb]{ .98,  .522,  .443}3.1204 ($\pm$1.301)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.391)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1269 ($\pm$1.432)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.449) & \cellcolor[rgb]{ .894,  .89,  .51}3.0194 ($\pm$1.435)   \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}2.9312 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1538 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8473 ($\pm$1.384) & \cellcolor[rgb]{ .98,  .486,  .435}3.1215 ($\pm$1.453)  & \cellcolor[rgb]{ .796,  .863,  .506}2.9032 ($\pm$1.471) \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .937,  .902,  .514}2.9688 ($\pm$1.385) & \cellcolor[rgb]{ 1,  .922,  .518}3.0086 ($\pm$1.356)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6129 ($\pm$1.481) & \cellcolor[rgb]{ .992,  .761,  .49}3.1032 ($\pm$1.38)   & \cellcolor[rgb]{ .973,  .412,  .42}3.3065 ($\pm$1.378)  \\
-			\textbf{student performance} & \cellcolor[rgb]{ .89,  .89,  .51}2.9409 ($\pm$1.412)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1849 ($\pm$1.38)   & \cellcolor[rgb]{ .388,  .745,  .482}2.771 ($\pm$1.41)   & \cellcolor[rgb]{ .98,  .561,  .451}3.1258 ($\pm$1.366)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.467)    \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8032 ($\pm$1.444) & \cellcolor[rgb]{ .976,  .914,  .514}2.9204 ($\pm$1.304) & \cellcolor[rgb]{ .973,  .412,  .42}3.2022 ($\pm$1.41)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9247 ($\pm$1.349)    & \cellcolor[rgb]{ .98,  .51,  .439}3.1495 ($\pm$1.517)   \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .973,  .412,  .42}3.0453 ($\pm$1.374)  & \cellcolor[rgb]{ 1,  .922,  .518}2.999 ($\pm$1.403)     & \cellcolor[rgb]{ .388,  .745,  .482}2.9629 ($\pm$1.409) & \cellcolor[rgb]{ .773,  .855,  .502}2.9858 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .871,  .51}3.0039 ($\pm$1.462)     \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .988,  .667,  .471}4                   \\
-		\end{tabular}%
-	}
-\end{table}%
-
-Tables \ref{tab:results:reanalysis:metrics:loss} and \ref{tab:results:reanalysis:metrics:rank} shows that there is no clear overall best performing reanalysis interval configuration of the \acs{BHH} for all datasets.
-
-It should be noted that the configuration and results for the reanalysis interval configurations should be considered along with the reselection interval configurations as reselection is based on the outcome of the reanalysis step.
-Furthermore, the reanalysis interval configurations should also be considered along with the replay window size, as the replay window size determines the number of performance log samples to reanalyse.
-For the \acs{BHH} baseline configuration, the reselection and reanalysis interval hyper-parameters have default values of ten, and the replay window size also has a default value of ten.
-These values are deliberately chosen so that there is a balance between the different hyper-parameters from which empirical conclusions can be made.
-
-Furthermore, the smaller the reanalysis interval, the more frequently the \acs{BHH} resets concentration parameters.
-The smaller the replay window size, the less performance samples in the performance log are considered for reanalysis.
-A replay window size of one yields a case where only the last executed step is considered for reanalysis and thus provides a shortsighted view on the relevance of past performance.
-As such, reselection is based only on the most recent performance of each selected \index{heuristic}heuristic.
-However, if the reanalysis interval is larger than the replay window size, the \acs{BHH} does not update its beliefs fast enough, and as a result, \index{heuristic}heuristic performance evidence is lost.
-
-Figure~\ref{fig:results:reanalysis:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reanalysis interval configurations, per dataset.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reanalysis intervals per dataset, across all independent runs and epochs.}
-	\label{fig:results:reanalysis:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:reanalysis:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reanalysis interval configuration as it relates to all datasets, across all independent runs and epochs.
-From Figure~\ref{fig:results:reanalysis:descriptive:cd}, it can be concluded that the best reanalysis interval is problem specific.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_reanalysis/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reanalysis intervals across all datasets, runs and epochs.}
-	\label{fig:results:reanalysis:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:reanalysis:descriptive:cd} shows no overall statistically significant difference in results for the various reanalysis interval configurations as it relates to all datasets.
-
-Similar to before, Figure~\ref{fig:results:reanalysis:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the reanalysis interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/mushroom.pdf}
-		\caption{Train log loss}
-		\label{fig:results:reanalysis:figures:loss:train:mushroom}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/mushroom.pdf}
-		\caption{Test log loss}
-		\label{fig:results:reanalysis:figures:loss:test:mushroom}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/accuracy/mushroom.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:reanalysis:figures:accuracy:train:mushroom}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/accuracy/mushroom.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:reanalysis:figures:accuracy:test:mushroom}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:reanalysis:figures:mushroom}
-\end{figure}
-
-Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/parkinsons.pdf}
-		\caption{Train log loss}
-		\label{fig:results:reanalysis:figures:loss:train:parkinsons}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/parkinsons.pdf}
-		\caption{Test log loss}
-		\label{fig:results:reanalysis:figures:loss:test:parkinsons}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:reanalysis:figures:parkinsons}
-\end{figure}
-
-The divergence that can be seen in Figure~\ref{fig:results:reanalysis:figures:loss:train:mushroom} and \ref{fig:results:reanalysis:figures:loss:test:mushroom} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results, when an optimal solution has already been found.
-As mentioned before, an early stopping strategy as well as a move-acceptance strategy can be incorporated to avoid this effect.
-
-\section{Burn In}\label{sec:results:burn_in}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{burn in} window size hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-Five different burn in window sizes are considered.
-These include burn in window sizes of 0, 5, 10, 15, and 20.
-Experiments are denoted as such.
-
-As a reminder, the burn in window size is a hyper-parameter that is borrowed from the \acs{MCMC} algorithm, and provides a window whereby exploration is encouraged in order to obtain sufficient samples of \index{heuristic}heuristic performance evidence for statistical inference.
-
-As before, Table~\ref{tab:results:burn_in:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the burn in window size variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs and epochs.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average test loss and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-	\label{tab:results:burn_in:metrics:loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Burn In - Average Test Loss}}                                                                                                                                                                                                                             \\
-			\midrule
-			\textbf{dataset}             & \textbf{0}                                               & \textbf{5}                                           & \textbf{10}                                          & \textbf{15}                                          & \textbf{20}                                          \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .392,  .745,  .482}2.0587 (+-0.088)     & \cellcolor[rgb]{ .388,  .745,  .482}2.0583 (+-0.181) & \cellcolor[rgb]{ 1,  .922,  .518}2.0961 (+-0.168)    & \cellcolor[rgb]{ 1,  .878,  .51}2.1454 (+-0.365)     & \cellcolor[rgb]{ .973,  .412,  .42}2.6753 (+-2.18)   \\
-			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 (+-0.016)        & \cellcolor[rgb]{ .851,  .878,  .506}0.2719 (+-0.02)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2688 (+-0.014) & \cellcolor[rgb]{ .988,  .694,  .475}0.2784 (+-0.017) & \cellcolor[rgb]{ .973,  .412,  .42}0.2851 (+-0.029)  \\
-			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 (+-0.065)        & \cellcolor[rgb]{ .388,  .745,  .482}0.2373 (+-0.033) & \cellcolor[rgb]{ .996,  .804,  .498}0.2514 (+-0.109) & \cellcolor[rgb]{ .784,  .859,  .502}0.2427 (+-0.033) & \cellcolor[rgb]{ .973,  .412,  .42}0.2703 (+-0.056)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0651 (+-0.02)      & \cellcolor[rgb]{ .443,  .761,  .482}0.0678 (+-0.024) & \cellcolor[rgb]{ 1,  .922,  .518}0.0929 (+-0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1109 (+-0.043) & \cellcolor[rgb]{ .973,  .412,  .42}0.1383 (+-0.034)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 (+-0.034)     & \cellcolor[rgb]{ .627,  .812,  .494}0.164 (+-0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1745 (+-0.037)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1883 (+-0.067)  & \cellcolor[rgb]{ .992,  .71,  .478}0.1803 (+-0.039)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .698,  .831,  .498}1.2983 (+-0.66)      & \cellcolor[rgb]{ .388,  .745,  .482}1.1216 (+-0.582) & \cellcolor[rgb]{ 1,  .922,  .518}1.4701 (+-1.161)    & \cellcolor[rgb]{ .984,  .604,  .459}1.9918 (+-3.645) & \cellcolor[rgb]{ .973,  .412,  .42}2.2996 (+-3.589)  \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .992,  .765,  .49}0.1046 (+-0.008)      & \cellcolor[rgb]{ .69,  .831,  .498}0.1026 (+-0.009)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1009 (+-0.01)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1043 (+-0.007)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1052 (+-0.009)  \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}0.081 (+-0.069)         & \cellcolor[rgb]{ .753,  .851,  .502}0.0772 (+-0.057) & \cellcolor[rgb]{ .388,  .745,  .482}0.0714 (+-0.045) & \cellcolor[rgb]{ .973,  .412,  .42}0.1136 (+-0.059)  & \cellcolor[rgb]{ .98,  .557,  .451}0.1044 (+-0.093)  \\
-			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 (+-0.017)     & \cellcolor[rgb]{ .596,  .804,  .494}0.096 (+-0.015)  & \cellcolor[rgb]{ .992,  .757,  .486}0.1036 (+-0.037) & \cellcolor[rgb]{ 1,  .922,  .518}0.0997 (+-0.021)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1116 (+-0.034)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .996,  .78,  .49}0.2411 (+-0.295)       & \cellcolor[rgb]{ .388,  .745,  .482}0.1472 (+-0.134) & \cellcolor[rgb]{ .973,  .412,  .42}0.2717 (+-0.462)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2291 (+-0.376)    & \cellcolor[rgb]{ .663,  .824,  .498}0.1842 (+-0.189) \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 (+-0.012)     & \cellcolor[rgb]{ .976,  .42,  .424}0.1068 (+-0.3)    & \cellcolor[rgb]{ .616,  .808,  .494}0.0262 (+-0.057) & \cellcolor[rgb]{ .973,  .412,  .42}0.1075 (+-0.256)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0612 (+-0.108)    \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 (+-0.003)     & \cellcolor[rgb]{ 1,  .922,  .518}0.0599 (+-0.003)    & \cellcolor[rgb]{ .745,  .847,  .502}0.0594 (+-0.003) & \cellcolor[rgb]{ .984,  .627,  .463}0.0644 (+-0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.0676 (+-0.015)  \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 (+-0.102)     & \cellcolor[rgb]{ .733,  .843,  .502}0.2801 (+-0.127) & \cellcolor[rgb]{ 1,  .922,  .518}0.314 (+-0.137)     & \cellcolor[rgb]{ .988,  .631,  .463}0.3623 (+-0.139) & \cellcolor[rgb]{ .973,  .412,  .42}0.3988 (+-0.133)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ 1,  .922,  .518}1.0827 (+-0.026)        & \cellcolor[rgb]{ .396,  .745,  .482}1.0791 (+-0.021) & \cellcolor[rgb]{ .388,  .745,  .482}1.079 (+-0.03)   & \cellcolor[rgb]{ .988,  .686,  .475}1.086 (+-0.029)  & \cellcolor[rgb]{ .973,  .412,  .42}1.0897 (+-0.034)  \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-From Table \ref{tab:results:burn_in:metrics:loss} a noticeable pattern can be observed.
-Generally it is found that a small burn in window size produces better results than larger burn in window sizes.
-The largest burn in window size of 20 produced the worst results in nine out of thirteen datasets.
-Some exceptions include the mushroom and the iris datasets.
-Notice that burn in window sizes smaller than the default reanalysis interval, reselection interval and replay window size of ten, generally produced the best results.
-However, Table \ref{tab:results:burn_in:metrics:loss} does not provide a clear view of the overall performance produced by different burn in window size configurations for the entire training process.
-
-In order to obtain a better view of the overall performance produced by different burn in window size configurations for the entire training process, Table \ref{tab:results:burn_in:metrics:rank} provides the average ranked performance, per dataset, for each of the \acs{BHH} burn in configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the burn in window size configurations, for all datasets, over all independent runs and epochs.
-The overall normalised average rank is provided at the bottom of the table.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:burn_in:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		% Table generated by Excel2LaTeX from sheet 'rank'
-		\begin{tabular}{r|ccccc}
-			                             & \multicolumn{5}{c}{\textbf{Burn In - Average Rank}}                                                                                                                                                                                                                                             \\
-			\midrule
-			\textbf{dataset}             & \textbf{0}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.9151 ($\pm$1.395)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6935 ($\pm$1.393) & \cellcolor[rgb]{ 1,  .922,  .518}2.9172 ($\pm$1.384)    & \cellcolor[rgb]{ .788,  .859,  .502}2.8398 ($\pm$1.352) & \cellcolor[rgb]{ .973,  .412,  .42}3.6344 ($\pm$1.357)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9097 ($\pm$1.441)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6817 ($\pm$1.427) & \cellcolor[rgb]{ .624,  .812,  .494}2.7699 ($\pm$1.344) & \cellcolor[rgb]{ .973,  .412,  .42}3.372 ($\pm$1.314)   & \cellcolor[rgb]{ .98,  .529,  .443}3.2667 ($\pm$1.412)  \\
-			\textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.7301 ($\pm$1.321) & \cellcolor[rgb]{ .816,  .867,  .506}2.8194 ($\pm$1.335) & \cellcolor[rgb]{ 1,  .922,  .518}2.857 ($\pm$1.485)     & \cellcolor[rgb]{ 1,  .878,  .51}2.9312 ($\pm$1.384)     & \cellcolor[rgb]{ .973,  .412,  .42}3.6624 ($\pm$1.339)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}1.9237 ($\pm$0.981) & \cellcolor[rgb]{ .545,  .788,  .49}2.1806 ($\pm$1.024)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9237 ($\pm$1.274)    & \cellcolor[rgb]{ .992,  .729,  .482}3.5054 ($\pm$1.186) & \cellcolor[rgb]{ .973,  .412,  .42}4.4667 ($\pm$0.851)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.3624 ($\pm$1.231) & \cellcolor[rgb]{ .533,  .784,  .49}2.5882 ($\pm$1.425)  & \cellcolor[rgb]{ 1,  .922,  .518}3.2978 ($\pm$1.392)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3796 ($\pm$1.271)  & \cellcolor[rgb]{ .976,  .459,  .431}3.372 ($\pm$1.401)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}2.4054 ($\pm$1.358) & \cellcolor[rgb]{ .604,  .808,  .494}2.7011 ($\pm$1.358) & \cellcolor[rgb]{ 1,  .902,  .518}3.2398 ($\pm$1.372)    & \cellcolor[rgb]{ 1,  .922,  .518}3.2323 ($\pm$1.326)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4215 ($\pm$1.396)  \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}3.0634 ($\pm$1.459)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7935 ($\pm$1.402) & \cellcolor[rgb]{ .447,  .761,  .482}2.8204 ($\pm$1.513) & \cellcolor[rgb]{ .996,  .796,  .494}3.1022 ($\pm$1.346) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.295)  \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8161 ($\pm$1.33)  & \cellcolor[rgb]{ .808,  .867,  .506}2.8495 ($\pm$1.383) & \cellcolor[rgb]{ 1,  .922,  .518}2.8645 ($\pm$1.409)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.398)  & \cellcolor[rgb]{ .988,  .698,  .475}3.0925 ($\pm$1.471) \\
-			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}2.6903 ($\pm$1.384) & \cellcolor[rgb]{ .91,  .894,  .51}2.9516 ($\pm$1.318)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.442)    & \cellcolor[rgb]{ .996,  .82,  .498}3.0581 ($\pm$1.344)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3032 ($\pm$1.51)   \\
-			\textbf{iris}                & \cellcolor[rgb]{ .922,  .898,  .51}2.9473 ($\pm$1.461)  & \cellcolor[rgb]{ 1,  .922,  .518}2.972 ($\pm$1.367)     & \cellcolor[rgb]{ .973,  .412,  .42}3.1903 ($\pm$1.449)  & \cellcolor[rgb]{ .388,  .745,  .482}2.771 ($\pm$1.369)  & \cellcolor[rgb]{ .984,  .58,  .455}3.1194 ($\pm$1.387)  \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.2065 ($\pm$1.249) & \cellcolor[rgb]{ .863,  .882,  .51}2.9376 ($\pm$1.298)  & \cellcolor[rgb]{ 1,  .902,  .514}3.1613 ($\pm$1.297)    & \cellcolor[rgb]{ 1,  .922,  .518}3.1441 ($\pm$1.401)    & \cellcolor[rgb]{ .973,  .412,  .42}3.5226 ($\pm$1.501)  \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.2796 ($\pm$1.282) & \cellcolor[rgb]{ 1,  .922,  .518}2.8892 ($\pm$1.247)    & \cellcolor[rgb]{ .816,  .867,  .506}2.7065 ($\pm$1.314) & \cellcolor[rgb]{ .984,  .616,  .459}3.3968 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.728 ($\pm$1.33)    \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.1452 ($\pm$1.205) & \cellcolor[rgb]{ .741,  .843,  .502}2.6946 ($\pm$1.403) & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.352)    & \cellcolor[rgb]{ .984,  .561,  .451}3.4581 ($\pm$1.354) & \cellcolor[rgb]{ .973,  .412,  .42}3.6054 ($\pm$1.231)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .925,  .898,  .51}2.9699 ($\pm$1.437)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0108 ($\pm$1.304)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6634 ($\pm$1.419) & \cellcolor[rgb]{ .988,  .659,  .471}3.1247 ($\pm$1.398) & \cellcolor[rgb]{ .973,  .412,  .42}3.2312 ($\pm$1.447)  \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}2.5975 ($\pm$1.376) & \cellcolor[rgb]{ .671,  .824,  .498}2.7688 ($\pm$1.353) & \cellcolor[rgb]{ 1,  .922,  .518}2.9647 ($\pm$1.404)    & \cellcolor[rgb]{ .988,  .694,  .475}3.1923 ($\pm$1.367) & \cellcolor[rgb]{ .973,  .412,  .42}3.4747 ($\pm$1.402)  \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
-		\end{tabular}%
-	}
-\end{table}%
-
-Table \ref{tab:results:burn_in:metrics:rank} shows that, in general, a configuration where there is no burn in produces the overall best ranked performance across all datasets.
-Furthermore, it can be observed that performance degrades with larger burn in window sizes.
-This can be explained from the fact that most of the training progress that is made, is done early in the training process.
-The faster the \acs{BHH} is able to start learning and exploiting \index{heuristic}heuristics and solutions, the better.
-
-Note that the \acs{BHH} is configured with a reselection interval of one, until the burn in window has been exhausted, after which the actual reselection interval applies.
-That means that reselection occurs at each step during the burn in window, but the reanalysis interval and replay window size remain intact.
-This observation agrees with previous results, where the \acs{BHH} prefers to start exploiting \index{heuristic}heuristics and solutions as soon as possible.
-Furthermore, this agrees with previous results, where large reselection intervals are found to produce the best results, giving \index{heuristic}heuristics sufficient time to progress and smooth out training steps.
-
-Recall that the gradient-based \index{heuristic}heuristics generally produce the best results overall.
-Most of the gradient-based \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool implement some form of momentum and exponentially average state parameters.
-When reselection occurs frequently in succession, these gradient-based \index{heuristic}heuristics struggle to produce smooth update steps.
-As a result, the \acs{BHH} can produce delayed convergence and thus leads to worse performance when considering the entire training process.
-
-Figure~\ref{fig:results:burn_in:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the burn in window size configurations, per dataset.
-From Figure~\ref{fig:results:burn_in:descriptive:descriptive} is can be seen that there is mostly a linear correlation between performance results and burn in window sizes, with minor exceptions to some datasets.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_burn_in/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with varying burn in values per dataset, across all independent runs and epochs.}
-	\label{fig:results:burn_in:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:burn_in:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each burn in window size configuration as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_burn_in/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with varying burn in values across all datasets, runs and epochs.}
-	\label{fig:results:burn_in:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:burn_in:descriptive:cd} shows with statistical certainty that a small burn in configuration of the \acs{BHH} generally produce overall better results than larger burn in configurations, as it relates to all datasets,
-
-Similar to before, Figure~\ref{fig:results:burn_in:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the burn in window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_burn_in/figures/train/loss/mushroom.pdf}
-		\caption{Train log loss}
-		\label{fig:results:burn_in:figures:loss:train:mushroom}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/mushroom.pdf}
-		\caption{Test log loss}
-		\label{fig:results:burn_in:figures:loss:test:mushroom}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_burn_in/figures/train/accuracy/mushroom.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:burn_in:figures:accuracy:train:mushroom}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_burn_in/figures/test/accuracy/mushroom.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:burn_in:figures:accuracy:test:mushroom}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:burn_in:figures:mushroom}
-\end{figure}
-
-Figure~\ref{fig:results:burn_in:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the burn in window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\begin{figure}[htbp]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_burn_in/figures/train/loss/parkinsons.pdf}
-		\caption{Train log loss}
-		\label{fig:results:burn_in:figures:loss:train:parkinsons}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/parkinsons.pdf}
-		\caption{Test log loss}
-		\label{fig:results:burn_in:figures:loss:test:parkinsons}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:burn_in:figures:parkinsons}
-\end{figure}
-
-The divergence that can be seen in Figures~\ref{fig:results:burn_in:figures:loss:train:mushroom} and \ref{fig:results:burn_in:figures:loss:test:mushroom} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results, when an optimal solution has already been found.
-As mentioned before, an early stopping strategy as well as a move-acceptance strategy can be incorporated to avoid this effect.
-
-\section{Normalisation}\label{sec:results:normalise}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{normalisation} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, the normalisation hyper-parameter is a flag that enables or disables normalisation of the concentration parameters in an attempt to provide more exploration in the \index{heuristic}heuristic space.
-
-Table \ref{tab:results:normalise:metrics} provides the average ranked performance, per dataset, with normalisation enabled and disabled.
-Similar to before, the performance rank is calculated as the average rank produced by the normalisation configurations, for all datasets, over all independent runs and epochs.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:normalise:metrics:rank}%
-	\par\bigskip
-	\resizebox{0.6\textwidth}{!}{
-		\begin{tabular}{rcc}
-			\multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Normalisation - Average Rank}}                                                           \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                            & \textbf{true}                                           \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4935 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5065 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4892 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5108 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5484 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4516 ($\pm$0.498) \\
-			\multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .388,  .745,  .482}1.4978 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5022 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.4258 ($\pm$0.495)   & \cellcolor[rgb]{ .973,  .412,  .42}1.5742 ($\pm$0.495)  \\
-			\multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4753 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5247 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5505 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4495 ($\pm$0.498) \\
-			\multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.5054 ($\pm$0.5)      & \cellcolor[rgb]{ .388,  .745,  .482}1.4946 ($\pm$0.5)   \\
-			\multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.472 ($\pm$0.499)    & \cellcolor[rgb]{ .973,  .412,  .42}1.528 ($\pm$0.499)   \\
-			\multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5645 ($\pm$0.496)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4355 ($\pm$0.496) \\
-			\multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4323 ($\pm$0.496)   & \cellcolor[rgb]{ .973,  .412,  .42}1.5667 ($\pm$0.496)  \\
-			\multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.4 ($\pm$0.49)       & \cellcolor[rgb]{ .973,  .412,  .42}1.6 ($\pm$0.49)      \\
-			\multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.3892 ($\pm$0.488)   & \cellcolor[rgb]{ .973,  .412,  .42}1.6108 ($\pm$0.488)  \\
-			\multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.5473 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4527 ($\pm$0.498) \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4851 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5148 ($\pm$0.5)    \\
-			\midrule
-			\textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                     & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:normalise:metrics:loss}%
-	\par\bigskip
-	\resizebox{0.6\textwidth}{!}{
-		\begin{tabular}{r|cc}
-			                             & \multicolumn{2}{c}{\textbf{Normalisation - Average Test Loss}}                                                           \\
-			\midrule
-			\textbf{dataset}             & \textbf{false}                                                 & \textbf{true}                                           \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088)        & \cellcolor[rgb]{ .973,  .412,  .42}2.0936 ($\pm$0.231)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)         & \cellcolor[rgb]{ .388,  .745,  .482}0.2704 ($\pm$0.017) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)         & \cellcolor[rgb]{ .388,  .745,  .482}0.2374 ($\pm$0.042) \\
-			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0651 ($\pm$0.02)         & \cellcolor[rgb]{ .973,  .412,  .42}0.0689 ($\pm$0.03)   \\
-			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)        & \cellcolor[rgb]{ .973,  .412,  .42}0.1721 ($\pm$0.038)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}1.2983 ($\pm$0.66)         & \cellcolor[rgb]{ .973,  .412,  .42}1.5051 ($\pm$1.93)   \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}0.1046 ($\pm$0.008)         & \cellcolor[rgb]{ .388,  .745,  .482}0.1021 ($\pm$0.009) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}0.081 ($\pm$0.069)         & \cellcolor[rgb]{ .973,  .412,  .42}0.0868 ($\pm$0.069)  \\
-			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}0.0941 ($\pm$0.017)         & \cellcolor[rgb]{ .388,  .745,  .482}0.0931 ($\pm$0.019) \\
-			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 ($\pm$0.295)         & \cellcolor[rgb]{ .388,  .745,  .482}0.2358 ($\pm$0.333) \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012)        & \cellcolor[rgb]{ .973,  .412,  .42}0.0455 ($\pm$0.216)  \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003)        & \cellcolor[rgb]{ .973,  .412,  .42}0.0598 ($\pm$0.004)  \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 ($\pm$0.102)        & \cellcolor[rgb]{ .973,  .412,  .42}0.2522 ($\pm$0.098)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)        & \cellcolor[rgb]{ .973,  .412,  .42}1.0831 ($\pm$0.045)  \\
-		\end{tabular}%
-	}
-\end{table}%
-
-Table \ref{tab:results:normalise:metrics} shows that, in general, there is no obvious difference in the outcomes of the \acs{BHH} when normalisation is enabled or disabled.
-For some datasets such as bank, fish toxicity, forest fires, iris, and wine quality, enabling normalisation provided the best results, while disabling of the normalisation flag provided the best results for the other datasets.
-This suggests that the normalisation flag is problem specific.
-Since the normalisation hyper-parameter provides a mechanism for the \acs{BHH} to explore more in the \index{heuristic}heuristic space, with the intent of finding better solutions, it can be concluded that some datasets require more exploration, while others require more exploitation.
-
-Figure~\ref{fig:results:normalise:descriptive:descriptive} provides an illustration of the descriptive plots for the \acs{BHH} configurations with the normalisation hyper-parameter enabled and disabled, per dataset.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_normalise/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with normalisation toggled per dataset, across all independent runs and epochs.}
-	\label{fig:results:normalise:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:normalise:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for normalisation configurations that are enabled and disabled, as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_normalise/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with normalisation toggled across all datasets, runs and epochs.}
-	\label{fig:results:normalise:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:normalise:descriptive:descriptive} shows no statistical difference in the outcomes of the normalisation configurations of the \acs{BHH}.
-This further supports the suggestion that the use of the normalisation hyper-parameter is problem specific.
-
-Similar to before, Figure~\ref{fig:results:normalise:figures:abalone} provides the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the normalisation experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_normalise/figures/train/loss/abalone.pdf}
-		\caption{Train log loss}
-		\label{fig:results:normalise:figures:loss:train:abalone}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/abalone.pdf}
-		\caption{Test log loss}
-		\label{fig:results:normalise:figures:loss:test:abalone}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_normalise/figures/train/accuracy/abalone.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:normalise:figures:accuracy:train:abalone}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_normalise/figures/test/accuracy/abalone.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:normalise:figures:accuracy:test:abalone}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the abalone dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:normalise:figures:abalone}
-\end{figure}
-
-Figure~\ref{fig:results:normalise:figures:bike} provides the train and test loss plots for an example regression dataset (bike) as it relates to the normalisation experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_normalise/figures/train/loss/bike.pdf}
-		\caption{Train log loss}
-		\label{fig:results:normalise:figures:loss:train:bike}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/bike.pdf}
-		\caption{Test log loss}
-		\label{fig:results:normalise:figures:loss:test:bike}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the bike dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:normalise:figures:bike}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% DISCOUNTED REWARDS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discounted Rewards}\label{sec:results:discounted_rewards}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{discounted rewards} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, the discounted rewards hyper-parameter is a flag that enables or disables discounted rewards of the pseudo counts that are added to concentration parameters in an attempt to provide control over the effects of past performances of the low-level \index{heuristic}heuristics.
-
-Table \ref{tab:results:discounted_rewards:metrics} provides the average ranked performance, per dataset, with discounted rewards enabled and disabled.
-Similar to before, the performance rank is calculated as the average rank produced by the discounted rewards configurations, for all datasets, over all independent runs and epochs.
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:discounted_rewards:metrics:rank}%
-	\par\bigskip
-	\resizebox{0.6\textwidth}{!}{
-		\begin{tabular}{rcc}
-			\multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Rank}}                                                           \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                                 & \textbf{true}                                           \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4914 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5086 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4613 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5387 ($\pm$0.499)  \\
-			\multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5161 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4839 ($\pm$0.5)   \\
-			\multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
-			\multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.428 ($\pm$0.495)         & \cellcolor[rgb]{ .973,  .412,  .42}1.572 ($\pm$0.495)   \\
-			\multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4699 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5301 ($\pm$0.499)  \\
-			\multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
-			\multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .388,  .745,  .482}1.4742 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5258 ($\pm$0.5)    \\
-			\multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4237 ($\pm$0.494)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5763 ($\pm$0.494)  \\
-			\multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5903 ($\pm$0.492)         & \cellcolor[rgb]{ .388,  .745,  .482}1.4097 ($\pm$0.492) \\
-			\multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.3946 ($\pm$0.489)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5806 ($\pm$0.494)  \\
-			\multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.371 ($\pm$0.483)         & \cellcolor[rgb]{ .973,  .412,  .42}1.629 ($\pm$0.483)   \\
-			\multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.4398 ($\pm$0.497)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5602 ($\pm$0.497)  \\
-			\multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.557 ($\pm$0.497)          & \cellcolor[rgb]{ .388,  .745,  .482}1.443 ($\pm$0.497)  \\
-			\midrule
-			\multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4728 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5254 ($\pm$0.499)  \\
-			\midrule
-			\textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                          & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-\begin{table}[htb]
-	\centering
-	\caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:discounted_rewards:metrics:loss}%
-	\par\bigskip
-	\resizebox{0.6\textwidth}{!}{
-		\begin{tabular}{r|cc}
-			                             & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Test Loss}}                                                           \\
-			\midrule
-			\textbf{dataset}             & \textbf{false}                                                      & \textbf{true}                                           \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088)             & \cellcolor[rgb]{ .973,  .412,  .42}2.0789 ($\pm$0.102)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)              & \cellcolor[rgb]{ .388,  .745,  .482}0.2693 ($\pm$0.011) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)              & \cellcolor[rgb]{ .388,  .745,  .482}0.2349 ($\pm$0.041) \\
-			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0651 ($\pm$0.02)              & \cellcolor[rgb]{ .973,  .412,  .42}0.0676 ($\pm$0.027)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)             & \cellcolor[rgb]{ .973,  .412,  .42}0.1672 ($\pm$0.037)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}1.2983 ($\pm$0.66)              & \cellcolor[rgb]{ .973,  .412,  .42}1.3457 ($\pm$1.419)  \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1046 ($\pm$0.008)             & \cellcolor[rgb]{ .973,  .412,  .42}0.1053 ($\pm$0.008)  \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}0.081 ($\pm$0.069)              & \cellcolor[rgb]{ .973,  .412,  .42}0.0928 ($\pm$0.079)  \\
-			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)             & \cellcolor[rgb]{ .973,  .412,  .42}0.0972 ($\pm$0.017)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 ($\pm$0.295)              & \cellcolor[rgb]{ .388,  .745,  .482}0.1833 ($\pm$0.259) \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012)             & \cellcolor[rgb]{ .973,  .412,  .42}0.0479 ($\pm$0.203)  \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003)             & \cellcolor[rgb]{ .973,  .412,  .42}0.06 ($\pm$0.002)    \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 ($\pm$0.102)             & \cellcolor[rgb]{ .973,  .412,  .42}0.2408 ($\pm$0.086)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}1.0827 ($\pm$0.026)              & \cellcolor[rgb]{ .388,  .745,  .482}1.0792 ($\pm$0.039) \\
-		\end{tabular}%
-
-	}
-\end{table}%
-
-Table \ref{tab:results:discounted_rewards:metrics} shows that, in general, there is no obvious difference in the outcomes of the \acs{BHH} when discounted rewards is enabled or disabled.
-
-Figure~\ref{fig:results:discounted_rewards:descriptive:descriptive} provides an illustration of the descriptive plots for the \acs{BHH} configurations with the discounted rewards hyper-parameter enabled and disabled, per dataset.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of the \acs{BHH} with discounted rewards toggled per datasets, across all independent runs and epochs.}
-	\label{fig:results:discounted_rewards:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:discounted_rewards:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for discounted rewards configurations that are enabled and disabled, as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of the \acs{BHH} with discounted rewards toggled across all datasets, runs and epochs.}
-	\label{fig:results:discounted_rewards:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:discounted_rewards:descriptive:descriptive} shows no statistical difference in the outcomes of the discounted rewards configurations of the \acs{BHH}.
-This further supports the suggestion that the use of the discounted rewards hyper-parameter is problem specific.
-
-Similar to before, Figure~\ref{fig:results:discounted_rewards:figures:wine_quality} provides the train and test, loss and accuracy plots for an example classification dataset (wine quality) as it relates to the discounted rewards experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/loss/wine_quality.pdf}
-		\caption{Train log loss}
-		\label{fig:results:discounted_rewards:figures:loss:train:wine_quality}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/wine_quality.pdf}
-		\caption{Test log loss}
-		\label{fig:results:discounted_rewards:figures:loss:test:wine_quality}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/accuracy/wine_quality.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:discounted_rewards:figures:accuracy:train:wine_quality}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/accuracy/wine_quality.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:discounted_rewards:figures:accuracy:test:wine_quality}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the wine quality dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:discounted_rewards:figures:wine_quality}
-\end{figure}
-
-Figure~\ref{fig:results:discounted_rewards:figures:housing} provides the train and test loss plots for an example regression dataset (housing) as it relates to the discounted rewards experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/loss/housing.pdf}
-		\caption{Train log loss}
-		\label{fig:results:discounted_rewards:figures:loss:train:housing}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/housing.pdf}
-		\caption{Test log loss}
-		\label{fig:results:discounted_rewards:figures:loss:test:housing}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the housing dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:discounted_rewards:figures:housing}
-\end{figure}
-
-\section{Summary}\label{sec:results:summary}
-
-TODO
+This chapter concludes the research that is done in this dissertation.
+This chapter provided a summary of the research intent, providing a brief review of the research problem, motivations and objectives defined for this dissertation.
+A brief summary of the background information that is covered in this dissertation is provided.
+A brief summary on the concept and implementation of the novel \acs{BHH} is provided, followed by a brief summary of the methodology that is used for the empirical process.
+This chapter also provided brief summaries of the results and findings for each of the experimental groups that were executed in the empirical process.
+Future research opportunities were identified and reference is made to materials and assets used in this dissertation that are made available online.

### 2022-11-26 dissertation/chapters/05-probability.tex
🚧 (final-review): Chapter 5 WIP

@@
 In 1718,~\citeauthor{ref:demoivre:1718}~\cite{ref:demoivre:1718} published the \textit{Doctrine of of Chance}; a book that is widely seen as the first published book on probability theory.
-In 1763, Thomas Bayes~\cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of \index{Bayes' Theorem}Bayes' Theorem was introduced.
+In 1763, Thomas Bayes~\cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of \index{Bayes' theorem}Bayes' theorem was introduced.
 
@@
 In 1991,~\citeauthor{ref:denker:1991},~\cite{ref:denker:1991} proposed a way to transform \acf{ANN} outputs to probability distributions.
-In 1993, \citeauthor{ref:neal:1993}~\cite{ref:neal:1993} developed a \acf{MCMC} sampling algorithm for Bayesian \acp{NN}.
+In 1993, \citeauthor{ref:neal:1993}~\cite{ref:neal:1993} developed a \acf{MCMC} sampling algorithm for \acfp{BNN}.
 These are but a few examples of the role that probability theory has played in \acs{ML} research in the past.
@@
 This chapter aims to provide the reader with the necessary background information on probability theory and statistics.
-These are big fields and focus is put on the elements that are required to formulate the proposed \acf{BHH}.
+These are large fields and focus is put on the elements that are required to formulate the proposed \acf{BHH}.
 The remainder of the chapter is structured as follows:
@@
 
-      \item \textbf{Section \ref{sec:probability:bayes_theorem}} introduces \index{Bayes' Theorem}Bayes' Theorem, the fundamental theorem upon which the \acs{BHH} is built.
+      \item \textbf{Section \ref{sec:probability:bayes_theorem}} introduces \index{Bayes' theorem}Bayes' theorem, the fundamental theorem upon which the \acs{BHH} is built.
 
@@
 
-In everyday conversation, the term \textit{probability} is a measure of one's belief in the occurrence of a future event~\cite{ref:wackerly:2014}.
+In everyday conversation, the term \textit{probability} is a measure of belief in the occurrence of a future event~\cite{ref:wackerly:2014}.
 Probability is a necessary tool used in many fields including physics, biology, chemistry and computer science.
@@
 These events are referred to as \textit{random} or \textit{stochastic} events.
-The probability that a certain event $A$ might occur, is denoted $P(A)$.
+The probability that a certain event, $A$ might occur is denoted by $P(A)$.
 Although these random events cannot be predicted with absolute certainty, the relative frequency with which they occur over many trials, is often remarkably stable.
@@
 In statistics, the decimal probability notation is used, where $0 <= P(A) <= 1$.
-Suppose the fair coin is thrown 10 times, one is not guaranteed to observe $0.5$ heads and $0.5$ tails.
+Suppose the fair coin is thrown 10 times, there is not guarantee of observing $0.5$ heads and $0.5$ tails.
 There is some probability (although small) that the coin might fall on heads $0/10$ times.
@@
 Multiple random events can be considered together, dependently or conditionally.
-The following sections provides insight into conditional and joints probabilities of multiple random events.
+The following sections provide insight into conditional and joint probabilities of multiple random events.
 
@@
 
-The occurrence of a given random event $A$ can often be conditional on the occurrence of another event $B$.
+The occurrence of a given random event, $A$ can often be conditional on the occurrence of another event, $B$.
 In the field of medicine, an example of this is to calculate the probability of a certain diagnosis of a sick patient given his/her symptoms.
@@
       \label{def:probability:cond_probability:independence}
-      Two events, $A$ and $B$ are said to be independent of each other if, and only if the following criteria hold:
+      Two events, $A$ and $B$, are said to be independent of each other if, and only if the following criteria hold:
 
@@
 
-      otherwise, events $A$ and $B$ are said to be \textit{dependent} random events.
+      Otherwise, events $A$ and $B$ are said to be \textit{dependent} random events.
 \end{definition}
@@
 \begin{proof}
-      Proof is given from Definition \ref{eq:probability:cond_probability} above.
+      Proof is given from Definition \ref{eq:probability:cond_probability}.
 \end{proof}
@@
 The equality on the right implies that $P(\bar{A} \cap B) = P(B) - P(A \cap B)$.
-By substituting the expression for $P(\bar{A} \cap B)$ into the expression for $P(A \cup B)$, one can obtain the result $P(A \cup B) = P(A) + P(B) - P(A \cap B)$.
+By substituting the expression for $P(\bar{A} \cap B)$ into the expression for $P(A \cup B)$, the resulting expression $P(A \cup B) = P(A) + P(B) - P(A \cap B)$ is obtained.
 \end{proof}
@@
 
-\index{Bayes' Theorem}Bayes' Theorem, named after Thomas Bayes, describes the probability of an event $A$, based on prior knowledge of conditions that might be related to $A$~\cite{ref:zalta:2015}.
+\index{Bayes' theorem}Bayes' theorem, named after Thomas Bayes, describes the probability of an event, $A$, based on prior knowledge of conditions that might be related to $A$~\cite{ref:zalta:2015}.
 In order to derive the formal theorem and proof, first consider Definition \ref{def:probability:bayes_theorem:partition} below~\cite{ref:zalta:2015}.
@@
 \index{Bayes Theorem}
-\begin{theorem}[\textbf{Bayes' Theorem}]
+\begin{theorem}[\textbf{Bayes' theorem}]
       \label{th:probability:bayes_theorem:theorem}
-      Assume that $[B_{1}, B_{2}, \dots, B_{K}]$ is a partition of $S$ such that $P(B_{i}) > 0$, for $i = 1,2, \dots, K$ then\\
+      Assume that $\{B_{1}, B_{2}, \dots, B_{K}\}$ is a partition of $S$ such that $P(B_{i}) > 0$, for $i = 1,2, \dots, K$ then\\
       \\
@@
 \begin{proof}
-      The proof follows from the definition of conditional probability as was presented in Section~\ref{sec:probability:cond_probability}.
+      The proof follows from the definition of conditional probability as was presented in Section~\ref{sec:probability:cond_probability}:
 
@@
 
-One of the many applications of \index{Bayes' Theorem}Bayes' Theorem is to do statistical inference.
-\index{Bayes' Theorem}Bayes' Theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
+One of the many applications of \index{Bayes' theorem}Bayes' theorem is to do statistical inference.
+\index{Bayes' theorem}Bayes' theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
 
@@
 The \index{Beta probability distribution}Beta probability distribution is denoted as $Beta(\alpha, \beta)$.
-The \acf{PDF} of the \index{Beta probability distribution}Beta probability distribution is given in Equation~\eqref{eq:probability:probability_distributions:beta:pdf} below.
+The \acf{PDF} of the \index{Beta probability distribution}Beta probability distribution is given as
 
@@
 
-From Equation~\eqref{eq:probability:probability_distributions:beta:pdf} above, the normalising constant $B(\alpha, \beta)$, is defined below in Equation~\eqref{eq:probability:probability_distributions:beta:norm_const}.
+The normalising constant, $B(\alpha, \beta)$, is defined as
 
@@
 
-In Equation~\eqref{eq:probability:probability_distributions:beta:norm_const}, $\Gamma$ is the Gamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func} below.
+where $\Gamma$ is the Gamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func} below.
 
@@
 In probability theory, the \index{Bernoulli probability distribution}Bernoulli probability distribution is often used to explain the possible outcomes of a single experiment that asks a \textit{yes-no} question such as flipping a coin.
-The outcome of such an experiment is a boolean value.
-The \index{Bernoulli probability distribution}Bernoulli probability distribution has a \acf{PMF} as given below in Equation~\eqref{eq:probability:probability_distributions:bernoulli:pmf}.
+The outcome of such an experiment is a Boolean value.
+The \index{Bernoulli probability distribution}Bernoulli probability distribution has a \acf{PMF}, given as
 
@@
 
-Equation~\eqref{eq:probability:probability_distributions:bernoulli:pmf} above, can also be expressed as show in Equation~\eqref{eq:probability:probability_distributions:bernoulli:alt} below.
+Equation~\eqref{eq:probability:probability_distributions:bernoulli:pmf} can also be expressed as
 
@@
 The mean of the \index{Bernoulli probability distribution}Bernoulli probability distribution approaches $\theta$ over many samples according to the \acs{CLT}~\cite{ref:grinstead:1997}.
-Figure \ref{fig:probability:probability_distributions:bernoulli:coin} shows a simulation of a fair-coin flipping simulation.
+Figure \ref{fig:probability:probability_distributions:bernoulli:coin} illustrates a simulation of a fair-coin flipping simulation.
 The mean converges to 0.5 for various sample sizes.
@@
 
-The expected value of the distribution is thus given according to Equation~\eqref{eq:probability:probability_distributions:bernoulli:expected_value} below.
+The expected value of the distribution is thus given as
 
@@
 
-The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:bernoulli:mode} below.
+The mode of the distribution is given as
 
@@
       \label{eq:probability:probability_distributions:bernoulli:mode}
-      M[x_{k}] =
+      M[x] =
       \begin{cases}
@@
 The \index{Binomial probability distribution}Binomial probability distribution is a discrete probability distribution over a random variable $x$ taking on a number of successes in $N$ sequential independent experiments that each ask a \textit{yes-no} question~\cite{ref:wackerly:2014}.
-The probability of a single independent experiment yielding a success, is given as $\theta$ and the \index{Binomial probability distribution}Binomial probability distribution is denoted as $Bin(N, \theta)$ with support $x \in \{0, 1, \dots, N\}$.
-It should be noted that the \index{Binomial probability distribution}Binomial probability distribution is the extension of the \index{Bernoulli probability distribution}Bernoulli probability distribution over $N$ independent sequential experiments and thus, each experiment also yields some boolean outcome.
+The probability of a single independent experiment yielding a success is given as $\theta$ and the \index{Binomial probability distribution}Binomial probability distribution is denoted as $Bin(N, \theta)$, with support $x \in \{0, 1, \dots, N\}$.
+It should be noted that the \index{Binomial probability distribution}Binomial probability distribution is an extension of the \index{Bernoulli probability distribution}Bernoulli probability distribution over $N$ independent sequential experiments, and thus each experiment also yields some Boolean outcome.
 When $N=1$, the experiment is referred to as a Bernoulli trial, and the distribution is just a \index{Bernoulli probability distribution}Bernoulli probability distribution.
 When $N > 1$, the sequence of outcomes is referred to as a Bernoulli process.
-The \acf{PMF} of the \index{Binomial probability distribution}Binomial probability distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:pmf} below.
+The \acf{PMF} of the \index{Binomial probability distribution}Binomial probability distribution is given as
 
@@
 Similar to the \index{Bernoulli probability distribution}Bernoulli probability distribution, the mean of the \index{Binomial probability distribution}Binomial probability distribution is $N\theta$ given the \acs{CLT} as was shown in Figure \ref{fig:probability:probability_distributions:bernoulli:coin}.
-The expected value of the \index{Binomial probability distribution}Binomial probability distribution is thus given in Equation~\eqref{eq:probability:probability_distributions:binomial:expected_value} below.
+The expected value of the \index{Binomial probability distribution}Binomial probability distribution is thus given as
 
@@
 
-The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:mode} below.
+The mode of the distribution is given as
 
@@
       \begin{split}
-            M[x_{k}] &= E[x] + \theta \\
+            M[x] &= E[x] + \theta \\
             &= N\theta  + \theta \\
@@
 
-The \index{Categorical probability distribution}Categorical probability distribution is a discrete probability distribution over some random variable $x$, taking on any one of $K$ possible categories~\cite{ref:wackerly:2014}.
-There is no ordering to these categories and therefore, for simplicity, each category is assigned a numerical representative value such that $k = (1, 2, \dots, K)$.
+The \index{Categorical probability distribution}Categorical probability distribution is a discrete probability distribution over some random variable, $x$, taking on any one of $K$ possible categories~\cite{ref:wackerly:2014}.
+There is no ordering to these categories and therefore, for simplicity, each category is assigned a numerical representative value such that $k \in \{1, 2, \dots, K\}$.
 The probabilities for all outcomes is given by the probability vector $\vec{\theta} = (\theta_{1}, \dots, \theta_{K})$.
-This means that the probability $P(x=k)=\theta_{k}$, has support $x \in \{1, \dots, K\}$.
-The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\theta)$, is the generalization of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, the generalised \index{Bernoulli probability distribution}Bernoulli probability distribution or the Multinoulli probability distribution.
+This means that the probability $P(x=k)=\theta_{k}$ has support $x \in \{1, \dots, K\}$.
+The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\theta)$, is a generalization of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, i.e.
+the generalised \index{Bernoulli probability distribution}Bernoulli probability distribution or the Multinoulli probability distribution.
 In probability theory, the \index{Categorical probability distribution}Categorical probability distribution is often used to explain the outcome of a single experiment with more than two possible outcomes, such as rolling a six-sided die~\cite{ref:wackerly:2014}.
-The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution is given in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf} below.
+The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution is given as
 
@@
 
-In Equation~\eqref{eq:probability:probability_distributions:categorical:pmf} above, $[x = k]$ is the \textit{Iversion Bracket}~\cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
-Given class $k$, the categorical distribution simply yields $\theta_{k}$ as is shown in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf_k} below.
+where the term $[x = k]$ is the \textit{Iversion Bracket}~\cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
+Given class $k$, the categorical distribution simply yields $\theta_{k}$ as is follows:
 
@@
       \label{eq:probability:probability_distributions:categorical:pmf_k}
-      f_{Cat}(x=k; K, \theta) = \theta_{k}
+      f_{Cat}(x=k; K, \boldsymbol{\theta}) = \theta_{k}
 \end{equation}
 
-The random variable $x$ can also be encoded in binary format, yielding a vector $\vec{x} = (x_{1}, \dots, x_{K})$ of \index{Bernoulli probability distribution}Bernoulli probability distributions such that the support is $\forall_{k=1}^{K} x_{k} \in \{0, 1\}$.
+The random variable $x$ can also be encoded in binary format, yielding a vector $\boldsymbol{x} = (x_{1}, \dots, x_{K})$ of \index{Bernoulli probability distribution}Bernoulli probability distributions such that the support is $\forall_{k=1}^{K} x_{k} \in \{0, 1\}$.
 Importantly, if the outcome of the random event is of category $k$, then $x_{k} = 1$ and $\forall_{j=1}^{K} x_{j} = 0, j \neq k$ so that the standard $K-1$ probability simplex $S$ still holds.
-The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution can then be rewritten as follows in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf_alt} below.
+The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution is rewritten as
 
@@
       \label{eq:probability:probability_distributions:categorical:pmf_alt}
-      f_{Cat}(x; K, \theta) = \prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{k})}
+      f_{Cat}(\boldsymbol{x}; K, \boldsymbol{\theta}) = \prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{k})}
 \end{equation}
 
-In Equation \ref{eq:probability:probability_distributions:categorical:pmf_alt} above, $\mathbbm{1}(x_{k})$ is the \textit{indicator function}, yielding 1 if $x_{k} = 1$ and 0 otherwise.
+where $\mathbbm{1}(x_{k})$ is the \textit{indicator function}, yielding 1 if $x_{k} = 1$ and 0 otherwise.
 
-Since there is no order to the underlying categories, the mean of the distribution does not yield any relevant information.
-The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:categorical:mode} below.
+Since there is no order to the underlying categories, the mean of the distribution does not yield any relevant information. The mode of the distribution is given as
 
@@
 
-      \item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with boolean outcome.
+      \item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with Boolean outcome.
 That is $x_{i} | \theta \overset{\text{iid}}{\sim} Ber(\theta)$ and $\mathcal{L}(x_{i} \vert \theta)$ is the Bernoulli likelihood.
@@
 
-By \index{Bayes' Theorem}Bayes' Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.
+By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.
 
@@
 
-By \index{Bayes' Theorem}Bayes' Theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.
+By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.
 
@@
 These include the \textit{frequentist} and the \textit{Bayesian} view of statistics.
-Naturally, Bayesian statistics is based on \index{Bayes' Theorem}Bayes' Theorem as was presented in Section \ref{sec:probability:bayes_theorem}.
+Naturally, Bayesian statistics is based on \index{Bayes' theorem}Bayes' theorem as was presented in Section \ref{sec:probability:bayes_theorem}.
 Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event, and the conditions under which the event happens~\cite{ref:hackenberger:2019}.
@@
 
-Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$, according to \index{Bayes' Theorem}Bayes' Theorem, is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.
+Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$, according to \index{Bayes' theorem}Bayes' theorem, is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.
 

### 2022-11-26 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 (final-review): Chapter 5 WIP

@@
-\chapter{Bayesian Hyper-Heuristic}\label{chap:bhh}
+\chapter{Probability}
+\label{chap:probability}
 
 \begin{quotation}
-      ``The result is a posterior distribution, which the agent may use as its new prior in the next step.''
+      ``Probability theory is nothing but common sense reduced to calculation.''
 \end{quotation}
 \begin{flushright}
-      - Pedro Domingos, The Master Algorithm
+      - Pierre-Simon Laplace
 \end{flushright}
 
-The above quote was the inspiration for the development of a novel \acf{HH} that uses Bayesian probability concepts as a selection mechanism to drive the heuristic selection process.
-Thus far the reader has been presented with all of the necessary background information on \acp{ANN} (Chapter \ref{chap:anns}), low-level \index{heuristic}heuristics (Chapter \ref{chap:heuristics}), \acp{HH} (Chapter \ref{chap:hhs}) and lastly, probability theory (Chapter \ref{chap:probability}).
-These elements form the fundamental components of the proposed \Acf{BHH}.
-This chapter provides the details around the implementation of the \Ac{BHH} and explains how it used to train \acp{FFNN}.
+Probability theory and statistics can be traced back to as early as the 18th century.
+In 1718,~\citeauthor{ref:demoivre:1718}~\cite{ref:demoivre:1718} published the \textit{Doctrine of of Chance}; a book that is widely seen as the first published book on probability theory.
+In 1763, Thomas Bayes~\cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of \index{Bayes' theorem}Bayes' theorem was introduced.
+
+Probability theory, statistics and \acf{ML} are transdisciplinary fields with many shared concepts.
+There are many examples of how probability theory has been incorporated into \acs{ML} research.
+In 1991,~\citeauthor{ref:denker:1991},~\cite{ref:denker:1991} proposed a way to transform \acf{ANN} outputs to probability distributions.
+In 1993, \citeauthor{ref:neal:1993}~\cite{ref:neal:1993} developed a \acf{MCMC} sampling algorithm for Bayesian \acp{NN}.
+These are but a few examples of the role that probability theory has played in \acs{ML} research in the past.
+
+Chapter \ref{chap:hhs} provided the reader with the concept of a \acf{HH}.
+This dissertation aims to develop a selection \acs{HH} that makes use of probability theory to select the best \acs{HH} to solve a given problem.
+This chapter aims to provide the reader with the necessary background information on probability theory and statistics.
+These are big fields and focus is put on the elements that are required to formulate the proposed \acf{BHH}.
 The remainder of the chapter is structured as follows:
@@
 \begin{itemize}
-      \item \textbf{Section \ref{sec:bhh:overview}} provides a brief overview of the \Acs{BHH}.
+      \item \textbf{Section \ref{sec:probability:overview}} gives a brief overview of what probability is and how it is used.
 
-      \item \textbf{Section \ref{sec:bhh:architecture}} provides the general architecture and \Ac{HH} framework implemented by the \Acs{BHH}.
+      \item \textbf{Section \ref{sec:probability:multiple_events}} presents the concept of conditional probability.
 
-      \item \textbf{Section \ref{sec:bhh:heuristic_pool}} presents the \index{heuristic}\textit{heuristic pool}, a collection of low-level \index{heuristic}heuristics.
-Discussions follow on the importance of diversity amoungst heuristics in the \index{heuristic pool}heuristic pool.
+      \item \textbf{Section \ref{sec:probability:multiple_events}} presents the two laws of probability related to the intersection and union of multiple events.
 
-      \item \textbf{Section \ref{sec:bhh:entity_pool}} presents details on entity (local) and population (global) memory (state).
+      \item \textbf{Section \ref{sec:probability:cond_probability}} introduces conditional probability.
 
-      \item \textbf{Section \ref{sec:bhh:performance_log}} presents detailed discussions on performance measurement. The \textit{performance log}, implemented by the \acs{BHH}, is presented.
+      \item \textbf{Section \ref{sec:probability:bayes_theorem}} introduces \index{Bayes' theorem}Bayes' theorem, the fundamental theorem upon which the \acs{BHH} is built.
 
-      \item \textbf{Section \ref{sec:bhh:credit_assignment_strategy}} presents detailed discussions on credit assignment and move acceptance strategies.
+      \item \textbf{Section \ref{sec:probability:probability_distributions}} presents the reader with relevant probability distributions.
 
-      \item \textbf{Section \ref{sec:bhh:selection_mechanism}} presents the Bayesian probabilistic model that is used as the heuristic selection mechanism.
+      \item \textbf{Section \ref{sec:probability:conjugate_priors}} presents the reader with relevant conjugate prior probability distributions.
 
-      \item \textbf{Section \ref{sec:bhh:optimisation_step}} presents the learning mechanisms by which the probabilistic model can be optimised.
+      \item \textbf{Section \ref{sec:probability:bayesian_statistics}} presents \textit{Bayesian} statistics.
+Brief discussions follow on the \textit{frequentist} view and \textit{Bayesian} view of probability.
+Detailed discussions follow on Bayesian optimisation methods such as \index{Bayesian analysis}\textit{Bayesian analysis}.
 
-      \item \textbf{Section \ref{sec:bhh:hyper_parameters}} summarises and discusses the associated \index{hyper-parameters}hyper-parameters and default values.
-
-      \item \textbf{Section \ref{sec:bhh:algorithm}} provides the pseudo-code algorithm for the \acs{BHH}.
-
-      \item \textbf{Section \ref{sec:bhh:summary}} provides a brief summary of the chapter.
+      \item \textbf{Section \ref{sec:probability:summary}} provides a brief summary of the chapter.
 \end{itemize}
 
-\section{Overview}\label{sec:bhh:overview}
+\section{Overview of Probability}\label{sec:probability:overview}
 
-This section provides an overview of the workings of the \Acf{BHH}.
-The general concept of the \acs{BHH} can be summarised as follows.
-The \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic, from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and \acs{FFNN} training process.
-The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process.
-These probabilities are then used as heuristic selection probabilities in the next step of the training process.
+In everyday conversation, the term \textit{probability} is a measure of one's belief in the occurrence of a future event~\cite{ref:wackerly:2014}.
+Probability is a necessary tool used in many fields including physics, biology, chemistry and computer science.
+These fields contain many cases that generate observations that cannot be predicted with absolute certainty~\cite{ref:wackerly:2014}.
+Probability can be be inferred and confirmed through past events.
+These events are referred to as \textit{random} or \textit{stochastic} events.
+The probability that a certain event $A$ might occur, is denoted $P(A)$.
+Although these random events cannot be predicted with absolute certainty, the relative frequency with which they occur over many trials, is often remarkably stable.
 
-Formal classification of the \Acs{BHH} is needed.
-Chapter \ref{chap:hhs} presented the reader with a proposed classification scheme for \acp{HH} by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}.
-According to the aforementioned classification scheme, the \Acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.
-A breakdown of the classification is given as follows:
+Consider flipping an unbiased, fair coin.
+The coin has two possible outcomes.
+It can conclude that each side has a $\frac{1}{2}$ or $50\%$ chance of occurring.
+In statistics, the decimal probability notation is used, where $0 <= P(A) <= 1$.
+Suppose the fair coin is thrown 10 times, one is not guaranteed to observe $0.5$ heads and $0.5$ tails.
+There is some probability (although small) that the coin might fall on heads $0/10$ times.
+The probability of such an event occurring is $0.0009765625$.
+In the coin flip example, the \acf{CLT} shows that the normalised sum of events tends toward a normal distribution with a mean value of $0.5$ if the number of events observed $N$, is large~\cite{ref:wackerly:2014}.
+The larger the value of $N$, the higher the confidence of mean probability and relative frequency of the event.
+The stable long-term relative frequency by which a random event occurs, provides an intuitive and meaningful measure of belief that a certain event will occur again at some point in the future~\cite{ref:wackerly:2014}.
+
+Probability can also be expressed over multiple random events.
+Multiple random events can be considered together, dependently or conditionally.
+The following sections provides insight into conditional and joints probabilities of multiple random events.
+
+\section{Conditional Probability and Independence}\label{sec:probability:cond_probability}
+
+The occurrence of a given random event $A$ can often be conditional on the occurrence of another event $B$.
+In the field of medicine, an example of this is to calculate the probability of a certain diagnosis of a sick patient given his/her symptoms.
+The aforementioned relationship between events is referred to as the conditional probability between two events.
+The conditional probability is expressed as $P(A \vert B)$ and is read \textit{the probability of $A$ given $B$}.
+On the contrary, the \textit{unconditional} probability is the probability of an event, not dependent on any other.
+The conditional probability of $A$ given $B$ can be expressed as is given in Definition \ref{eq:probability:cond_probability} below~\cite{ref:wackerly:2014}.
+\\
+\begin{definition}[\textbf{Conditional Probability}]
+      \label{eq:probability:cond_probability}
+      The conditional probability of an event $A$, subject to the occurrence of event $B$ is expressed as
+
+      \begin{equation}
+            \label{eq:probability:overview:conditional}
+            P(A \vert B) = \frac{P(A \cap B)}{P(B)}
+      \end{equation}
+\end{definition}
+
+In Equation~\eqref{eq:probability:overview:conditional} above, $P(B) > 0$.
+Note that conditional probability does not suggest causation.
+If an event $A$ has a high probability of occurring after observing event $B$, it does not necessarily mean that $A$ is caused by $B$.
+Conditional probability simply expresses the dependence amongst events.
+
+It could also be the case that the outcome of observing event $A$ is not affected by the occurrence of $B$.
+In this case, it is said that events $A$ and $B$ are independent.
+The independence between two events are expressed in Definition \ref{def:probability:cond_probability:independence} below.
+\\
+\begin{definition}[\textbf{Independence of Events}]
+      \label{def:probability:cond_probability:independence}
+      Two events, $A$ and $B$ are said to be independent of each other if, and only if the following criteria hold:
 
       \begin{itemize}
-      \item \textbf{Population-Based:} The \acs{BHH} implements a population-based approach, where a collection of different candidate solutions, referred to as \textit{entities}, work together to yield a global best solution.
-
-      \item \textbf{Meta-Hyper-Heuristic:} There exists a domain barrier, where the \acs{BHH} searches through the \textit{heuristic space}, using only \index{heuristic}heuristic performance information, while lower level heuristics search through the \textit{solution space} using information from the search domain itself.
-Furthermore, the \index{heuristic pool}heuristic pool implemented by the \acs{BHH} supports both gradient-based low level \index{heuristic}heuristics, as well as meta-heuristics.
-
-      \item \textbf{Selection and Perturbation of Low-Level Heuristics:} The \acs{BHH} implements a \index{heuristic}heuristic selection mechanism that selects from a collection of lower level \index{heuristic}heuristics, called a \index{heuristic pool}\textit{heuristic pool}.
-Selection is biased towards good performing heuristics.
-A credit assignment strategy is used to \textit{reward} good heuristic performance.
-The \acs{BHH} maintains entity and population state through operations that \textit{proxy} update steps from different heuristics (perturbation), as is required.
-These proxy operations ensure that heuristic requirements are satisfied even when different heuristics are used for different entities throughout the training process.
-
-      \item \textbf{Online Learning:} The \acs{BHH} applies learning, at specified intervals, throughout the \acs{FFNN} training process.
+            \item $P(A \vert B) = P(A)$
+            \item $P(B \vert A) = P(B)$
+            \item $P(A \cap B) = P(A)P(B)$
       \end{itemize}
 
-The following sections presents the reader with more detail on the implementation of the \acs{BHH}.
-Discussions lead with the \acs{BHH} architecture and general \acs{HH} framework in the following section.
+      otherwise, events $A$ and $B$ are said to be \textit{dependent} random events.
+\end{definition}
 
-\section{Architecture}\label{sec:bhh:architecture}
+\section{Two Laws of Probability for Multiple Events}\label{sec:probability:multiple_events}
 
-This section aims to present the reader with all the high level components in the architecture of the \Acs{BHH}.
-Burke et al.~\cite{ref:burke:2010} proposed an initial framework for \acp{HH} and Grobler~\cite{ref:grobler:2015} further proposed a framework for a heterogeneous meta-\ac{HH}.
-The aforementioned frameworks are adapted for the implementation of the \Acs{BHH}.
-An illustration of the high-level architecture of the \Acs{BHH} is given in Figure \ref{fig:bhh_architecture}.
+Suppose there are two random events $A$ and $B$, then one can calculate the probability of the union and intersection of these events.
+From the aforementioned concept, two laws of probability can be formulated.
+These are referred to as the \textit{multiplicative} and \textit{additive} laws of probability~\cite{ref:wackerly:2014} and is given below in Theorems \ref{th:probability:multiple_events:multiplicative} and \ref{th:probability:multiple_events:additive} respectively.\\
+
+\begin{theorem}[\textbf{The Multiplicative Law of Probability}]
+      \label{th:probability:multiple_events:multiplicative}
+      The probability of the intersection of two events $A$ and $B$ is given as
+
+      \begin{equation}
+            \begin{split}
+                  P(A \cap B)
+                  &= P(A)P(B \vert A) \\
+                  &= P(B)P(A \vert B)
+            \end{split}
+      \end{equation}
+
+      If $A$ and $B$ are independent, then
+
+      \begin{equation}
+            P(A \cap B) = P(A)P(B)
+      \end{equation}
+\end{theorem}
+
+\begin{proof}
+      Proof is given from Definition \ref{eq:probability:cond_probability} above.
+\end{proof}
+\vspace*{0.5cm}
+
+\begin{theorem}[\textbf{The Additive Law of Probability}]
+      \label{th:probability:multiple_events:additive}
+      The probability of the union of two events $A$ and $B$ is given as
+
+      \begin{equation}
+            P(A \cup B) = P(A) + P(B) - P(B \cap A)
+      \end{equation}
+\end{theorem}
+
+\begin{proof}
+      The geometric proof of the additive law of probability is given by the Venn Diagram presented in Figure \ref{fig:probability:multiple_events:additive}.
+Note that $A \cup B = A \cup ( \bar{A} \cap B)$, where $A$ and $\bar{A} \cap B$ are mutually exclusive events.
+Furthermore, consider that $B = (\bar{A} \cap B) \cup (A \cap B)$, where $\bar{A} \cap B$ and $A \cap B$ are mutually exclusive.
+Then $P(A \cup B) = P(A) + P(\bar{A} \cap B)$ and $P(B) = P(\bar{A} \cap B) + P(A \cap B)$.
+The equality on the right implies that $P(\bar{A} \cap B) = P(B) - P(A \cap B)$.
+By substituting the expression for $P(\bar{A} \cap B)$ into the expression for $P(A \cup B)$, one can obtain the result $P(A \cup B) = P(A) + P(B) - P(A \cap B)$.
+\end{proof}
 
@@
       \centering
-      \includegraphics[width=1.0\textwidth]{bhh_architecture.pdf}
-      \caption[An illustration of
-            the architecture and high level components of the \acf{BHH}.]{An illustration of
-            the architecture and high level components of the \acf{BHH}.}
-      \label{fig:bhh_architecture}
+      \includegraphics[width=0.7\textwidth]{images/additive_law_of_probability_proof.pdf}
+      \caption{A Venn-Diagram showing the proof of the additive law of probability for multiple events.}
+      \label{fig:probability:multiple_events:additive}
 \end{figure}
 
-With reference to Figure \ref{fig:bhh_architecture}, the components are briefly given below in the order of information flow during the \acs{FFNN} training process steps.
+\index{Bayes Theorem}
+\section{Bayes' Theorem}\label{sec:probability:bayes_theorem}
 
-\begin{itemize}
-      \item \textbf{Initialisation Step}: The initialisation step refers to the initialisation strategy implemented by the \acs{BHH}.
+\index{Bayes' theorem}Bayes' theorem, named after Thomas Bayes, describes the probability of an event $A$, based on prior knowledge of conditions that might be related to $A$~\cite{ref:zalta:2015}.
+In order to derive the formal theorem and proof, first consider Definition \ref{def:probability:bayes_theorem:partition} below~\cite{ref:zalta:2015}.
+\\
+\begin{definition}
+      \label{def:probability:bayes_theorem:partition}
+      For some positive integer, $K$, let the sets $B_{1}, B_{2}, \dots, B_{K}$ be such that
 
-      \item \textbf{Heuristic Pool}: The \index{heuristic pool}heuristic pool contains a collection of low-level \index{heuristic}heuristics.
+      \begin{enumerate}
+            \item $S = B_{1} \cup B_{2} \cup \dots \cup B_{K}$
+            \item $B_{i} \cap B_{j} = \emptyset$, for $i \neq j$
+      \end{enumerate}
 
-      \item \textbf{Entity Pool}: The \index{entity pool}entity pool represents a collection of candidate solutions for the underlying \acs{FFNN}, referred to as entities in a population.
+      Then the collection of sets $\{B_{1}$, $B_{2}$, $\dots$, $B_{K}\}$ is said to be a partition of S, the union of mutually exclusive subsets.
+\end{definition}
+\vspace*{0.5cm}
 
-      \item \textbf{Selection Mechanism}: The selection mechanism refers to the Bayesian probabilistic model.
+\index{Bayes Theorem}
+\begin{theorem}[\textbf{Bayes' theorem}]
+      \label{th:probability:bayes_theorem:theorem}
+      Assume that $[B_{1}, B_{2}, \dots, B_{K}]$ is a partition of $S$ such that $P(B_{i}) > 0$, for $i = 1,2, \dots, K$ then\\
+      \\
+      \begin{equation}
+            P(B_{j} \vert A) = \frac{P(A \vert B_{j})P(B_{j})}{\sum_{i=1}^{K} P(A \vert B_{i})P(B_{i})}
+      \end{equation}
+\end{theorem}
 
-      \item \textbf{Heuristic-Entity Selections}: Every entity in the \index{entity pool}entity pool gets assigned a selected heuristic.
-
-      \item \textbf{Train and Test Datasets}: The training set is used to train the model while the test set is used to evaluate the model's generalisation capabilities.
-
-      \item \textbf{Model}: The underlying \acs{FFNN} to be trained.
-
-      \item \textbf{Low-Level Heuristics Update Step}: The low-level heuristics' update step as it applies to its allocated entity.
-
-      \item \textbf{Loss Function}: In supervised learning, the loss function is a measure of distance between predicted output and the ground truth, and is the mechanism used to evaluate the model's performance.
-
-      \item \textbf{Domain Barrier}: The domain barrier is the logical separation of information available in the heuristic space and the solution space.
-The \acs{BHH} searches in the heuristic space, while low-level heuristics search in the solution space.
-
-      \item \textbf{Performance Log}: Contains a record of heuristic-entity performance at each step of the training process.
-
-      \item \textbf{Credit Assignment Strategy}: The strategy used to assign credit to heuristics for their performance.
-
-      \item \textbf{Update Step}: The high-level heuristic update step as implemented by the \acs{BHH}.
-\end{itemize}
-
-Each of the components in Figure \ref{fig:bhh_architecture} is discussed in detail in the following sections.
-
-\index{heuristic pool}
-\section{Heuristic Pool}\label{sec:bhh:heuristic_pool}
-
-Generally speaking, the \index{heuristic pool}heuristic pool is a collection of low-level heuristics under consideration by the \acs{BHH}.
-The \index{heuristic pool}heuristic pool contains the set of low-level \index{heuristic}heuristics that, together with their performance information, make up the \text{heuristic space}.
-Importantly, the \acs{BHH} searches in \index{heuristic}heuristic space.
-The \index{heuristic pool}heuristic pool is defined in terms of the diversity of heuristics, as well as the amount of heuristics in the \index{heuristic pool}heuristic pool.
-Each of these are discussed in the following sections.
-
-\subsection{Heuristic Diversity}\label{sec:bhh:heuristic_pool:diversity}
-
-A \index{heuristic}heuristic's eligibility for inclusion in the \index{heuristic}heuristic pool, is determined by its ability to solve to underlying problem and its search behaviour and characteristics.
-The \index{heuristic pool}heuristic pool should contain a variety of different heuristics that have different search behaviours, so that a trade-off can be made by between exploration and exploitation of solutions, as is required during the training process.
-Heuristics that explore a lot, should be selected when exploration is needed, and heuristics that exploit a lot should be selected accordingly.
-The trade-off between exploration and exploitation is managed by the high-level heuristic.
-The \acs{BHH} will learn to select and apply the appropriate heuristic, at the appropriate points, throughout the training process.
-In doing so, a balance is achieved between exploration and exploitation.
-
-\subsection{Heuristic Pool Size}\label{sec:bhh:heuristic_pool:pool_size}
-
-Another design decision in the heuristic pool is heuristic pool size.
-Since the \acs{BHH} is a \textit{learning} \acs{HH}, every heuristic that is included in the heuristic pool increases the requirement of more statistical evidence of heuristic performance.
-Not only does a large \index{heuristic pool}heuristic pool drastically complicate the learning process that is required by the \acs{BHH}, but it also drastically complicates the process of maintaining \textit{state}.
-State is the term used to describe data that is relevant to the training process, and is maintained between training steps.
-An example of \textit{local} state is an entity's position, while an example of \textit{global} state is the global best solution found thus far.
-The following section presents the concept of \textit{proxies} and their role in maintaining state.
-
-\subsection{Proxies}\label{sec:bhh:heuristic:proxies}
-
-The concept of proxies arise from the sparsity of state as maintained by different \index{heuristic}heuristics.
-Since \index{heuristic}heuristics maintain (possibly) different states, there is an uncertainty of state transition when switching between \index{heuristic}heuristics.
-Consider an example where the \index{heuristic pool}heuristic pool consists of just two \index{heuristic}heuristics.
-One heuristic is a gradient-based heuristic that maintains momentum such as \acs{Adam}.
-The other is a \index{meta-heuristic}meta-heuristic that does not require a gradient, such as \acs{PSO}.
-Both these \index{heuristic}heuristics track different parameters in their state.
-For \acs{Adam}, the expected gradient mean and variance is maintained, while the \ac{PSO} maintains record of the gbest and pbest solutions of all of entities.
-A solution to state indifference, is to proxy heuristic state update operations.
-State is then maintained in two parts:
-
-\begin{itemize}
-      \item \textbf{Primary State}: Refers to the state that is originally maintained by a heuristic. The selected heuristic simply applies the normal state update operations to its state.
-
-      \item \textbf{Proxied State}: Refers to the state that is not directly maintained by the heuristic, but can be updated by outsourcing the required state update operation to another heuristic.
-\end{itemize}
-
-Primary and proxied state parameters must be maintained together.
-Since entities represent candidate solutions, which are forms of state, entities are ideal candidates to store and maintain these state parameters.
-Entities are extended to include the primary state elements of \textit{all} the underlying low-level heuristics, as well as the candidate solution (weights) for the \acs{FFNN}.
-At each heuristic-entity application step, all state parameters, per entity, are updated either by primary method or by proxied method.
-The \acs{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.
-
-\begin{table}[htbp]
-      \centering
-      \caption{An example of mapping of proxied state update operation maintained by the \acs{BHH}.}
-      \label{tab:bhh:heuristic_pool:proxy_mapping_example}%
-      \par\bigskip
-      \resizebox{0.5\textwidth}{!}{
-            \begin{tabular}{ccccc}
-                                                                  &   & \multicolumn{3}{c}{State Parameter}                                                                                                                                                                                      \\
-                  \cmidrule{3-5}                                  &   & 1                                                                      & 2                                                                      & 3                                                                      \\
-                  \cmidrule{3-5}    \multirow{3}[1]{*}{Heuristic} & A & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} \\
-                                                                  & B & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
-                                                                  & C & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
-            \end{tabular}%
-      }
-\end{table}%
-
-From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when \index{heuristic}heuristic A is selected, it will outsource state update operations from \index{heuristic}heuristic B, for state parameter 2.
-Heuristic B will outsource from \index{heuristic}heuristic A, for state parameter 3.
-Finally, \index{heuristic}heuristic C will outsource from \index{heuristic}heuristic A and B, for state parameters 2 and 3 respectively.
-In this way, all \index{heuristic}heuristics maintain all the state parameters.
-
-Proxied state update operations is a simple concept in principle, but requires detailed decomposition of the \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool.
-Overlapping and unique state parameters must be identified so that a proxy mapping, such as the one given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, can be constructed.
-A suggestion to simplify this process is to borrow concepts from the equations of motion from physics.
-These include \textit{position}, \textit{velocity}, \textit{acceleration} and \textit{momentum}.
-Expressing \index{heuristic}heuristic update steps according to these parameters drastically simplify the process.
-However, it is possible that \index{heuristic}heuristics implement unique state parameters that do not overlap, these have to be catered for in the proxy mapping.
-
-State parameters and update operations should not be considered in isolation.
-An example is \textit{position} and \textit{velocity}.
-Consider, for example, \index{heuristic}heuristics such as \acf{DE} and \acfp{GA}.
-These \index{heuristic}heuristics recombine entities.
-In the aforementioned case, the concept of an equation of motion does not entirely make sense, since the displacement of its position is not a result of maintaining velocity or momentum, but rather by displacement through recombination.
-In this particular case, a solution is to apply the recombination operation to \textit{all} applicable state parameters as well, or to nullify the necessary state parameters.
-Unfortunately there is no general, automated solution to formulate these heuristic state overlaps.
-Each \index{heuristic}heuristic must be carefully considered.
-More details on the \index{entity pool}entity pool and entity state are presented in the following section.
-
-\index{entity pool}
-\section{Entity Pool}\label{sec:bhh:entity_pool}
-
-The \index{entity pool}entity pool refers to a collection of \textit{entities} that each represent a candidate solution to the underlying \acs{FFNN} being trained.
-The entities contain information of the solution space.
-A common naming convention for such a collection is a \textit{population} of entities.
-The \acs{BHH} is a population-based \acs{HH} and as such, the \index{entity pool}entity pool size or population size is an important design choice.
-The population size is defined as a hyper-parameter of the \acs{BHH} and can be empirically evaluated.
-
-The \index{entity pool}entity pool maintains two different types of state. These include entity (local) and population (global) state. Each of these are discussed in more detail next.
-
-\subsection{Entity State}\label{sec:bhh:entity_pool:entity_state}
-
-Entities represent candidate solutions to the model's trainable parameters (weights) and other \index{heuristic}heuristic-specific state parameters, as was discussed in Section \ref{sec:bhh:heuristic:proxies}.
-It can be said that entities implement \textit{local} state.
-It was mentioned that these entities can be treated as physical \textit{particles} in a hyper-dimensional search environment.
-Entities model concepts from physics.
-For example, the candidate solution is represented as the entity's position, and an entity's velocity and acceleration is analogous to the gradient and momentum of the entity respectfully.
-Examples of entity state parameters, as derived from various low-level \index{heuristic}heuristics, is given as follows.
-
-\begin{itemize}
-      \item \textbf{position}: General parameter that represents the actual candidate solution and is thus a primary state parameter for all \index{heuristic}heuristics.
-
-      \item \textbf{velocity}: Directly implemented by \index{heuristic}heuristics such as \acp{PSO} and is analogous to the gradient for gradient-based \index{heuristic}heuristics such as \ac{Momentum}.
-
-      \item \textbf{gradient}: The last known gradient, as derived from gradient-based \index{heuristic}heuristics.
-
-      \item \textbf{position delta}: The last computed position delta between the current timestep and the previous timestep.
-
-      \item \textbf{sum of the gradients squared}: As required and maintained by \index{heuristic}heuristics such as \acs{Adagrad}.
-
-      \item \textbf{expected position delta variance}: As required and maintained by \index{heuristic}heuristics such as \acs{Adadelta}.
-
-      \item \textbf{expected gradient mean}: As required and maintained by \index{heuristic}heuristics such as \acs{Momentum}, \acs{NAG} and \acs{Adam}.
-
-      \item \textbf{expected gradient variance}: As required and maintained by \index{heuristic}heuristics such as \acs{RMSProp}, \acs{Adadelta} and \acs{Adam}.
-
-      \item \textbf{personal best position}: Parameter that tracks that best known position by the entity thus far. As required and maintained by \index{heuristic}heuristics such as \acs{PSO}.
-
-      \item \textbf{personal best loss}: Parameter that tracks that best known loss by the entity thus far. As required and maintained by \index{heuristic}heuristics such as \acs{PSO}.
-
-      \item \textbf{loss}: Parameter that tracks the loss as achieved by the the entity throughout training.
-\end{itemize}
-
-From the list above, it should be clear that entity state becomes increasingly complicated with the increase of the number of distinct \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool with unique state parameters.
-
-\subsection{Population State}\label{sec:bhh:entity_pool:population_state}
-
-The population state refers to a collection of parameters that are shared between the entities in the population.
-Population state is also referred to as \textit{global} state and represents the population's memory.
-The population state generally contains state parameters that are of importance to multiple \index{heuristic}heuristics, and usually tracks the state of the population and not individual \index{heuristic}heuristic.
-Some examples of population state that can arise from different \index{heuristic}heuristics is given below.
-
-\begin{itemize}
-      \item \textbf{entities}: Naturally, the population state contains the list of entities in the population.
-
-      \item \textbf{ibest} and \textbf{ibest loss}: Refers to the best position and loss achieved by the population for the current iteration/step.
-
-      \item \textbf{rbest} and \textbf{rbest loss}: Refers to the best position and loss achieved by the population for the current replay buffer/window size.
-
-      \item \textbf{gbest} and \textbf{gbest loss}: Refers to the overall/global best position and loss achieved by the population for the entire training process.
-This parameter is introduced by \index{heuristic}heuristics such as \acp{PSO}.
-\end{itemize}
-
-Entities in the entity pool are each assigned an associated \index{heuristic}heuristic.
-The \acs{BHH} selects from the \index{heuristic pool}heuristic pool a low-level \index{heuristic}heuristic to be applied to an individual entity.
-The outcome of this selection process is a mapping table that tracks which \index{heuristic}heuristic has been selected for which entity.
-The selection process is executed by the selection mechanism of the \acs{BHH}.
-These \index{heuristic}heuristic-entity combinations are applied to the underlying \acs{FFNN}.
-The \acs{BHH} tracks the performance of each of these combinations throughout the training process in a performance log.
-The performance log is presented in the following section.
-
-\section{Performance Log}\label{sec:bhh:performance_log}
-
-The \acs{BHH} incorporates a form of probabilistic modeling in its selection mechanism.
-Probability is calculated based on \index{heuristic}heuristic-entity performance over time.
-Evidence of \index{heuristic}heuristic-entity performance is thus required for the \acs{BHH} to learn.
-Since the performance log can become very big, only a sliding window of the performance history is maintained at each step in the learning process.
-The sliding window is also referred to as a \textit{replay} buffer, a term borrowed from the field of \acf{RL}.
-The replay window size is defined as a hyper-parameter of the \acs{BHH}.
-The performance log is then simply a table of events and metrics.
-The \acs{BHH} tracks the following metrics in the performance log.
-
-\begin{itemize}
-      \item \textbf{step}: The current mini-batch step.
-
-      \item \textbf{\index{heuristic}heuristic}: The selected heuristic's index.
-
-      \item \textbf{entity}: The entity's index to whom the \index{heuristic}heuristic is applied.
-
-      \item \textbf{loss}: The \index{heuristic}heuristic-entity performance metric. The loss is retrieved from the loss function.
-
-      \item \textbf{ibest loss}: Keeps track of the \textit{iteration} best loss.
-Thus, the best loss value achieved by all entity-\index{heuristic}heuristic combinations, for a single mini-batch step.
-
-      \item \textbf{rbest loss}:  Keeps track of the \textit{replay} best loss.
-Thus, the best loss value achieved by all entity-\index{heuristic}heuristic combinations, over all mini-batch steps currently in the performance log/replay buffer.
-
-      \item \textbf{gbest loss}:  Keeps track of the \textit{global} best loss.
-Thus, the best loss value achieved by all entity-\index{heuristic}heuristic combinations over all mini-batch steps thus far.
-\end{itemize}
-
-An example of the performance log implemented by the \acs{BHH} is given in Table \ref{tab:bhh:performance_log:performance_log_example} below.
-
-\begin{table}[htbp]
-      \centering
-      \caption{An example of the performance log implemented by the \acs{BHH}, showing the first 5 entities, their allocated \index{heuristic}heuristics and their resulting performance measurements for step 1 of the training process.}
-      \label{tab:bhh:performance_log:performance_log_example}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{cccccccc}
-                  \textbf{step} & \textbf{entity} & \textbf{heuristic} & \textbf{loss} & \textbf{ibest loss} & \textbf{pbest loss} & \textbf{rbest loss} & \textbf{gbest loss} \\
-                  \midrule
-                  1             & 1               & 1                  & 0.016444      & 0.016444            & 0.016444            & 0.016444            & 0.016444            \\
-                  1             & 2               & 2                  & 0.337965      & 0.016444            & 0.337965            & 0.016444            & 0.016444            \\
-                  1             & 3               & 1                  & 0.134781      & 0.016444            & 0.134781            & 0.016444            & 0.016444            \\
-                  1             & 4               & 1                  & 0.998719      & 0.016444            & 0.998719            & 0.016444            & 0.016444            \\
-                  1             & 5               & 3                  & 0.708702      & 0.016444            & 0.708702            & 0.016444            & 0.016444            \\
-            \end{tabular}%
-      }
-\end{table}%
-
-The performance log itself introduces a number of design considerations as well.
-The larger the performance log, the longer memory is retained throughout the training process.
-The performance log size, referred to as the \textit{replay window size}, controls the recency of evidence from which the \acs{BHH} must learn.
-If the replay window size is too small, it does not accumulate enough samples/evidence to statistically make accurate selections.
-If the replay window size is too big, a bias could exist for selecting \index{heuristic}heuristics that performed well in the past.
-Furthermore, it is not guaranteed that past performance is indicative of future performance during the training process.
-The performance log should be considered along with the selection of a credit assignment strategy.
-Credit assignment strategies are presented in the following section.
-
-\section{Credit Assignment Strategy}
-\label{sec:bhh:credit_assignment_strategy}
-
-The credit assignment strategy is a mechanism that assigns a discrete credit indicator to \index{heuristic}heuristics that perform well, based on their performance metrics such as loss.
-The credit assignment strategy implements the ``move acceptance'' process as proposed by~\citeauthor{ref:ozcan:2006}~\cite{ref:ozcan:2006,ref:ozcan:2008} and addresses the credit assignment problem as discussed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}.
-A good credit assignment strategy will correctly allocate credit to the appropriate \index{heuristic}heuristic-entity combination.
-The credit assignment strategy to use is defined as a hyper-parameter.
-The \acs{BHH} implements the following credit assignment strategies to choose from.
-
-\begin{itemize}
-      \item \textbf{ibest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{ibest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that achieved the best performance in the current mini-batch iteration.
-
-      \item \textbf{pbest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{pbest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that was able to improve on its personal best past performance loss.
-
-      \item \textbf{rbest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{rbest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that achieved the best performance in the current replay window.
-
-      \item \textbf{gbest}: Credit is assigned to the \index{heuristic}heuristic-entity combination that set the \textit{gbest} loss value, meaning that it is the entity-\index{heuristic}heuristic combination that achieved the overall best performance so far.
-
-      \item \textbf{symmetric}: Credit is assigned to all entity-\index{heuristic}heuristic combinations, regardless of their performance.
-The symmetric credit assignment strategy does not randomly assign credit, but rather assigns credit to all events.
-In effect, no learning and performance-bias is achieved with the symmetric credit assignment strategy and thus, the symmetric credit assignment strategy is implemented as a basis for comparison.
-Comparing a credit assignment staretegy to the symmetric credit assignment indicates the ability of the other credit assignment strategy to have an effect on the learning process and performance of the \acs{BHH}.
-\end{itemize}
-
-The implementation of a credit assignment strategy is simply a function that translates the performance log from Table \ref{tab:bhh:performance_log:performance_log_example}, into Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}.
-
-\begin{table}[htbp]
-      \centering
-      \caption{Credit assignment strategy output table showing \textit{ibest} credit assignment for the first 5 entities and their selected heuristics, for step 1 of the training process.}
-      \label{tab:bhh:credit_assignment_strategy:credit_assignment_example}%
-      \par\bigskip
-      \resizebox{0.4\textwidth}{!}{
-            \begin{tabular}{cccc}
-                  \textbf{step} & \textbf{entity} & \textbf{heuristic} & \textbf{credit} \\
-                  \midrule
-                  1             & 1               & 1                  & true            \\
-                  1             & 2               & 2                  & false           \\
-                  1             & 3               & 1                  & false           \\
-                  1             & 4               & 1                  & false           \\
-                  1             & 5               & 3                  & false           \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Credit is used by the selection mechanism of the \acs{BHH}. The selection mechanism is presented in the following section.
-
-\section{Selection Mechanism}\label{sec:bhh:selection_mechanism}
-
-This section aims to provide the reader with the detail around the selection mechanism as it is implemented by the \acs{BHH}.
-It is mentioned throughout this document that the \acs{BHH} implements a predictive model based on Bayesian probabilistic concepts.
-In probabilistic modeling it is necessary to identify all the random events that can occur.
-
-\subsection{Random Events}
-\label{sec:bhh:selection_mechanism:random_events}
-
-Observation of random events is treated as evidence. In the context of a Bayesian approach, this evidence is used to update prior beliefs. The \acs{BHH} distinguishes between the following events.
-
-\begin{itemize}
-      \item \textbf{$H$}: The event of observing \textit{heuristics}.
-      \item \textbf{$E$}: The event of observing \textit{entities}.
-      \item \textbf{$C$}: The event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} is met.
-\end{itemize}
-
-It should be noted that event information is stored and observed directly from the performance log as presented in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}.
-From the above list of events, the event $C$ is dependent on the occurrence of $H$ and $E$ and a credit assignment strategy.
-
-\subsection{Independence}\label{sec:bhh:selection_mechanism:independence}
-
-The dependence between random events can have an impact on the probabilistic model that is implemented.
-For simplicity, the \acs{BHH} assumes independence between events, although the event $C$ is clearly dependent on the occurrence of $H$ and $E$.
-Furthermore, the \acs{BHH} assumes independence between steps  and treats each training step as if training has restarted.
-The \acs{BHH} implements a form of Naïve Bayes classifier, where the appropriate heuristic to assign to an entity is a classification problem.
-\citeauthor{ref:domingos:1997}~\cite{ref:domingos:1997} mentions that although Bayesian classifiers’ probability estimates are only optimal under quadratic loss if the independence assumption holds, the classifier itself can still be optimal under zero-one loss (misclassification rate), even when this assumption is violated by a wide margin.
-This means that independence can be assumed when the probabilistic model is used as a classifier.
-
-\index{Bayes' Theorem}
-\subsection{Bayes' Theorem}\label{sec:bhh:selection_mechanism:bayes_theorem}
-
-Chapter \ref{chap:probability} presented \index{Bayes' Theorem}Bayes' Theorem, but for convenience, it is given again in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} below.
+\begin{proof}
+      The proof follows from the definition of conditional probability as was presented in Section~\ref{sec:probability:cond_probability}.
 
       \begin{equation}
-      \label{eq:bhh:selection_mechanism:bayes_theorem}
-      P(A \vert B) = \frac{P(B \vert A)P(A)}{P(B)}
+            \begin{split}
+                  P(B_{j} \vert A)
+                  &= \frac{P(A \cap B_{j})}{P(A)}\\
+                  &= \frac{P(A \vert B_{j})P(B_{j})}{\sum_{i=1}^{K} P(A \vert B_{i})P(B_{i})}
+            \end{split}
+      \end{equation}
+\end{proof}
+
+One of the many applications of \index{Bayes' theorem}Bayes' theorem is to do statistical inference.
+\index{Bayes' theorem}Bayes' theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
+
+\section{Probability Distributions}\label{sec:probability:probability_distributions}
+
+Probability distributions are mathematical functions that give the probabilities of the occurrences of different possible outcomes in the experiment.
+The theory and equations presented in the following sections where all taken from~\citeauthor{ref:wackerly:2014}~\cite{ref:wackerly:2014}.
+
+\subsection{Beta probability distribution}\label{sec:probability:probability_distributions:beta}
+
+The \index{Beta probability distribution}Beta probability distribution is a family of univariate, continuous, probability distributions over some $x$, with support on the interval $[0,1]$~\cite{ref:wackerly:2014}.
+It is parameterised by two shape parameters $\alpha > 0$, $\alpha \in \mathbb{R}$ and $\beta > 0$, $\beta \in \mathbb{R}$.
+The \index{Beta probability distribution}Beta probability distribution is denoted as $Beta(\alpha, \beta)$.
+The \acf{PDF} of the \index{Beta probability distribution}Beta probability distribution is given in Equation~\eqref{eq:probability:probability_distributions:beta:pdf} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:beta:pdf}
+      P(x \vert \alpha, \beta) = f_{Beta}(x; \alpha, \beta) = \frac{1}{B(\alpha, \beta)} x^{\alpha - 1} (1 - x)^{\beta - 1}
 \end{equation}
 
-Since the \acs{BHH} implements a Bayesian classifier, the \acs{BHH} is not concerned with actual probabilities.
-Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} can thus be evaluated for proportionality.
-The resulting proportionality is expressed in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} below.
+From Equation~\eqref{eq:probability:probability_distributions:beta:pdf} above, the normalising constant $B(\alpha, \beta)$, is defined below in Equation~\eqref{eq:probability:probability_distributions:beta:norm_const}.
 
 \begin{equation}
-      \label{eq:bhh:selection_mechanism:bayes_theorem_prop_to}
-      P(A \vert B) \propto P(B \vert A)P(A)
+      \label{eq:probability:probability_distributions:beta:norm_const}
+      B(\alpha, \beta) = \frac{\Gamma(\alpha)\Gamma(\beta)}{\Gamma(\alpha + \beta)}
 \end{equation}
 
-The conditionality implemented by \index{Bayes' Theorem}Bayes' Theorem can be extended to include multiple criteria.
-\index{Bayes' Theorem}Bayes' Theorem is used by the selection mechanism of the \acs{BHH}.
-The predictive model that is used by the selection mechanism of the \acs{BHH} is presented in the following section.
-
-\subsection{Predictive Model}\label{sec:bhh:selection_mechanism:predictive_model}
-
-This section presents the predictive model as implemented by the selection mechanism of the \acs{BHH}.
-The predictive model is arguably the most important component of the \acs{BHH}, as it drives the heuristic selection process.
-The \acs{BHH} implements a predictive model that predicts which heuristic to select, given the conditionality that a particular entity is used and a particular credit assignment criteria is met.
-The predictive model can be derived as follows.\\\\
-\textbf{Setup}:
-\\
-Let
-
-\begin{itemize}
-      \item $I$: Denote the maximum number of instances in the replay window.
-      \item $J$: Denote the \index{entity pool}entity pool (population) size.
-      \item $K$: Denote the \index{heuristic pool}heuristic pool size.
-      \item $L$: Denote the number of credit assignment output classes. Since the output of credit assignment is boolean, $L = 2$.
-
-      \item $\alpha = (\alpha_{1}, \dots, \alpha_{K})$: Denote the concentration parameters for the heuristic probability distribution.
-      \item $\beta = (\beta_{1}, \dots, \beta_{K})^{J}$: Denote the concentration parameters for the entity-heuristic probability distributions.
-      \item $\gamma = (\gamma_{1}, \dots, \gamma_{K})^{L}$: Denote the concentration parameters for the credit-heuristic probability distribution.
-
-      \item $\theta \vert \alpha \sim Dir(\alpha; K)$: Denote the heuristic probability distribution, implementing a \index{Dirichlet probability distribution}Dirichlet probability distribution parameterised by $\alpha$ and $K$.
-Heuristic selection probabilities are sampled from this distribution.
-
-      \item $\phi \vert \beta \sim Dir(\beta; K)^{J}$: Denote the entity-heuristic probability distribution, implementing a \index{Dirichlet probability distribution}Dirichlet probability distribution parameterised by $\beta$ and $K$ for each entity in the \index{entity pool}entity pool with population size $J$.
-Entity-heuristic probabilities are sampled from this distribution.
-
-      \item $\psi \vert \gamma_{1}, \gamma_{0}  \sim Beta(\gamma_{1}, \gamma_{0})$: Denote the credit-heuristic probability distribution, implementing a Beta probability distribution parameterised by $\gamma_{1}$ and $\gamma_{0}$.
-Credit-heuristic probabilities are sampled from this distribution.
-
-      \item $H \vert \theta \sim Mult(\theta; I, K)$: Denote the distribution of heuristics (event $H$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled heuristic selection probability $\theta$, the \index{heuristic pool}heuristic pool size $K$ and maximum number of instances $I$.
-
-      \item $E \vert \phi \sim Mult(\phi; I, K)^{J}$: Denote the distribution of entity-heuristic combinations (event $E$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled entity-heuristic selection probability $\phi$, the \index{heuristic pool}heuristic pool size $K$ and maximum number of instances $I$, for each entity in $J$.
-
-      \item $C \vert \psi \sim Bin(\psi, I)$: Denote the distribution of credit-heuristic combinations (event $C$), implementing a \index{Binomial probability distribution}Binomial probability distribution, parameterised by the sampled credit-heuristic selection probability $\psi$ and the maximum number of instances $I$.
-\end{itemize}
-
-Vector notation is dropped for sake of convenience, simplicity and readability.
-The parameterised predictive model, as derived from \index{Bayes' Theorem}Bayes' theorem, is then given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model} below.
+In Equation~\eqref{eq:probability:probability_distributions:beta:norm_const}, $\Gamma$ is the Gamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func} below.
 
 \begin{equation}
-      \label{eq:bhh:selection_mechanism:predictive_model}
+      \label{eq:probability:probability_distributions:beta:gamma_func}
+      \Gamma(n) = ( n - 1)!
+\end{equation}
+
+It should be noted that the Gamma function can also be written as shown in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func_alt} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:beta:gamma_func_alt}
+      \Gamma(n+1) = n!
+\end{equation}
+
+The control parameters $\alpha$ and $\beta$, determine the shape of the distribution.
+There exists a special case where $\alpha = \beta$.
+This is referred to as the \textit{symmetric} \index{Beta probability distribution}Beta probability distribution.
+In the case where $\alpha = \beta = 1$ the distribution is equivalent to the uniform distribution over all points in its support.
+The \index{Beta probability distribution}Beta probability distribution for various values of $\alpha$ and $\beta$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:beta}.
+
+\begin{figure}[htbp]
+      \begin{subfigure}{0.49\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{images/beta_various.pdf}
+            \caption{\index{Beta probability distribution}Beta probability distribution}
+            \label{fig:probability:probability_distributions:beta_normal}
+      \end{subfigure}
+      \begin{subfigure}{0.49\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{images/beta_cumulative.pdf}
+            \caption{Cumulative \index{Beta probability distribution}Beta probability distribution}
+            \label{fig:probability:probability_distributions:beta_cumulative}
+      \end{subfigure}
+      \par\bigskip
+      \caption{An illustration of the \index{Beta probability distribution}Beta probability distribution (left)~\cite{ref:beta:2014} as well as the cumulative \index{Beta probability distribution}Beta probability distribution (right)~\cite{ref:cumulativebeta:2014} for various values of $\alpha$ and $\beta$ .}
+      \label{fig:probability:probability_distributions:beta}
+\end{figure}
+
+The expected value of $x$ is given below in Equation~\eqref{eq:probability:probability_distributions:beta:expected_value}.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:beta:expected_value}
+      E[x] = \frac{\alpha}{\alpha + \beta}
+\end{equation}
+
+Similarly, the expected value of the natural logarithm of $x$ can be calculated as is shown below in Equation~\eqref{eq:probability:probability_distributions:beta:expected_value_ln}.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:beta:expected_value_ln}
+      E[\ln(x)] = \psi({\alpha}) - \psi(\alpha + \beta)
+\end{equation}
+
+In Equation~\eqref{eq:probability:probability_distributions:beta:expected_value_ln} above, $\psi$ is the logarithmic derivative of the Gamma function, called the \textit{Digamma} function.
+The Digamma function is given below in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:beta:digamma}
+      \psi(n) = \frac{d}{dn}\ln(\Gamma(n)) = \frac{\Gamma'(n)}{\Gamma(n)}
+\end{equation}
+
+Finally, the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:beta:mode} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:beta:mode}
+      M[x] = E[x] - 1 = \frac{\alpha - 1}{\alpha + \beta - 1}
+\end{equation}
+
+\subsection{Dirichlet probability distribution}\label{sec:probability:probability_distributions:dirichlet}
+
+The \index{Dirichlet probability distribution}Dirichlet probability distribution is a family of multivariate continuous probability distributions over some $x$ in $K$ dimensions~\cite{ref:wackerly:2014}.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution is the multivariate generalization of the \index{Beta probability distribution}Beta probability distribution and is thus sometimes referred to by its alternative name, the multivariate Beta probability distribution.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution is parameterised by some vector $\vec{\alpha} = (\alpha_{1}$,  $\dots, \alpha_{K})$ $\forall_{k=1}^{K} \alpha_{k} > 0$, $\alpha_{k} \in \mathbb{R}$.
+Throughout this chapter, the vector notation is dropped for simplicity and readability.
+$\alpha$ is referred to as the concentration parameter.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K \geq 2$ with parameters $\alpha$, denoted $Dir(\alpha)$, has a \acs{PDF} as is given in Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:dirichlet:pdf}
+      P(x \vert \alpha) =  f_{Dir}(x; K, \alpha) = \frac{1}{B(\alpha)}  \prod_{k=1}^{K} x_{k}^{\alpha_{k} - 1}
+\end{equation}
+
+In Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} above, the normalising constant $B(\alpha)$, is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:norm_cost}.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:dirichlet:norm_cost}
+      B(\alpha) = \frac{\prod_{k=1}^{K} \Gamma(\alpha_{k})}{\Gamma(\alpha_{0})}
+\end{equation}
+
+In Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} above, $\alpha_{0}$ is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:alpha_0} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:dirichlet:alpha_0}
+      \alpha_{0} = \sum_{k=1}^{K}\alpha_{k}
+\end{equation}
+
+Importantly, the set $\{x_{k}\}_{k=1}^{K}$ belongs to the standard $K-1$ probability simplex $S$, meaning that $x_{K} = 1 - \sum_{k=1}^{K-1}x_{k}$ with support $\forall_{k=1}^{K} x \in [0,1]$.
+Under the simplex $S$, this means that the sum over all values of the vector $\vec{x}$ must be 1.
+The simplex can thus be rewritten as $\sum_{k=1}^{K}x_{k} = 1$.
+
+Similar to the \index{Beta probability distribution}Beta probability distribution, $\alpha$ determines the shape of the distribution in $K$ dimensions and thus, there also exist a special case, referred to as the \textit{symmetric} distribution when $\forall_{k=1}^{K} \alpha_{k} = c$, where $c$ is some constant.
+In the case where $c = 1$, the distribution is referred to as a \textit{flat} distribution and yields the uniform distribution over all points in $S$.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K = 3$, for various values of $\alpha$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:dirichlet}.
+
+\begin{figure}[htb]
+      \centering
+      \includegraphics[width=0.9\textwidth]{images/dirichlet.pdf}
+      \caption{The \acfp{PDF} for the \index{Dirichlet probability distribution}Dirichlet probability distribution over the 2-simplex.
+The concentration parameter $\alpha$ is varied.
+The values of the \acs{PDF} are shown by the color maps with contour lines at equal values as indicated in the color bars~\cite{ref:dirichlet:2020}.}
+      \label{fig:probability:probability_distributions:dirichlet}
+\end{figure}
+
+The expected value of $x$ can be calculated as shown in Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:dirichlet:expected_value}
+      E[x_{k}] = \frac{\alpha_{k}}{\alpha_{0}}
+\end{equation}
+
+Similarly, the expected value of the natural logarithm of $x_{k}$ can be calculated as defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value_ln} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:dirichlet:expected_value_ln}
+      E[\ln(x_{k})] = \psi({\alpha_{k}}) - \psi(\alpha_{0})
+\end{equation}
+
+In Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value_ln} above, $\psi$ is the Digamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}.
+Finally, the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:dirichlet:mode} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:dirichlet:mode}
       \begin{split}
-            P(H \vert E, C;  \theta, \phi, \psi)
-            &= \frac{
-                  P(E, C \vert H;  \phi, \psi)  P(H \vert \theta)
-            }{
-                  P(E, C \vert \theta, \phi, \psi)
-            } \\
-            &= \frac{
-                  P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
-            }{
-                  P(E \vert \theta, \psi) P(C \vert \theta, \phi)
-            } \\
-            &= \frac{
-                  P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
-            }{
-                  \left[ \sum_{k}^{K} P(E, H=k \vert \theta, \phi) \right] \left[ \sum_{k}^{K}  P(C, H=k \vert \theta, \psi) \right]
-            } \\
-            &= \frac{
-                  P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
-            }{
-                  \left[ \sum_{k}^{K} P(E \vert H=k, \phi) P(H=k \vert \theta) \right] \left[ \sum_{k}^{K} P(C \vert H=k, \psi) P(H=k \vert \theta) \right]
-            }
+            M[x_{k}] &= E[{x_{k}] -K^{-1}} \\
+            &=  \frac{\alpha_{k} - 1}{\alpha_{0} - K}
       \end{split}
@@
 
-Notice the joint probability over events $E$ and $C$, given the selection of a heuristic $H$, denoted by the product of the sums of the separate parts for $E$ and $C$, in the denominator.
-The calculation in the denominator can be intractable.
-Since the \acs{BHH} selection mechanism uses the predictive model as a classifier, the posterior distribution as given in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem}, can be evaluated for proportionality, as is given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} below.
+\subsection{Bernoulli probability distribution}\label{sec:probability:probability_distributions:bernoulli}
+
+The \index{Bernoulli probability distribution}Bernoulli probability distribution is a discrete probability distribution over some random variable $x$ that takes the value of $1$ with probability $\theta$ and $0$ with probability $1-\theta$ ~\cite{ref:wackerly:2014}.
+The \index{Bernoulli probability distribution}Bernoulli probability distribution is denoted as $Ber(\theta)$ with support $x \in \{0, 1\}$.
+In probability theory, the \index{Bernoulli probability distribution}Bernoulli probability distribution is often used to explain the possible outcomes of a single experiment that asks a \textit{yes-no} question such as flipping a coin.
+The outcome of such an experiment is a Boolean value.
+The \index{Bernoulli probability distribution}Bernoulli probability distribution has a \acf{PMF} as given below in Equation~\eqref{eq:probability:probability_distributions:bernoulli:pmf}.
 
 \begin{equation}
-      \label{eq:bhh:selection_mechanism:predictive_model_prop_to}
+      \label{eq:probability:probability_distributions:bernoulli:pmf}
+      P(x \vert \theta) = f_{Ber}(x; \theta) =
+      \begin{cases}
+            \theta     & \text{if}\ x=1 \\
+            1 - \theta & \text{if}\ x=0
+      \end{cases}
+\end{equation}
+
+Equation~\eqref{eq:probability:probability_distributions:bernoulli:pmf} above, can also be expressed as show in Equation~\eqref{eq:probability:probability_distributions:bernoulli:alt} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:bernoulli:alt}
+      f_{Ber}(x; \theta) = \theta^{x}(1-\theta)^{1-x}
+\end{equation}
+
+The mean of the \index{Bernoulli probability distribution}Bernoulli probability distribution approaches $\theta$ over many samples according to the \acs{CLT}~\cite{ref:grinstead:1997}.
+Figure \ref{fig:probability:probability_distributions:bernoulli:coin} shows a simulation of a fair-coin flipping simulation.
+The mean converges to 0.5 for various sample sizes.
+
+\begin{figure}[htbp]
+      \centering
+      \begin{subfigure}{0.49\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{images/coin_flip_samples_100.pdf}
+            \caption{100 Samples}
+            \label{fig:probability:probability_distributions:bernoulli:coin_100}
+      \end{subfigure}
+      \begin{subfigure}{0.49\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{images/coin_flip_samples_10000.pdf}
+            \caption{10000 Samples}
+            \label{fig:probability:probability_distributions:bernoulli:coin_10000}
+      \end{subfigure}
+      \par\bigskip
+      \caption{An illustration of the the coin flip situation for different sample sizes that show the convergence of the mean as per the \acf{CLT}.}
+      \label{fig:probability:probability_distributions:bernoulli:coin}
+\end{figure}
+
+The expected value of the distribution is thus given according to Equation~\eqref{eq:probability:probability_distributions:bernoulli:expected_value} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:bernoulli:expected_value}
+      E[x] = \theta
+\end{equation}
+
+The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:bernoulli:mode} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:bernoulli:mode}
+      M[x_{k}] =
+      \begin{cases}
+            0   & \text{if}\ \theta < 0.5 \\
+            0,1 & \text{if}\ \theta = 0.5 \\
+            1   & \text{if}\ \theta > 0.5 \\
+      \end{cases}
+\end{equation}
+
+\subsection{Binomial probability distribution}\label{sec:probability:probability_distributions:bin}
+
+The \index{Binomial probability distribution}Binomial probability distribution is a discrete probability distribution over a random variable $x$ taking on a number of successes in $N$ sequential independent experiments that each ask a \textit{yes-no} question~\cite{ref:wackerly:2014}.
+The probability of a single independent experiment yielding a success, is given as $\theta$ and the \index{Binomial probability distribution}Binomial probability distribution is denoted as $Bin(N, \theta)$ with support $x \in \{0, 1, \dots, N\}$.
+It should be noted that the \index{Binomial probability distribution}Binomial probability distribution is the extension of the \index{Bernoulli probability distribution}Bernoulli probability distribution over $N$ independent sequential experiments and thus, each experiment also yields some Boolean outcome.
+When $N=1$, the experiment is referred to as a Bernoulli trial, and the distribution is just a \index{Bernoulli probability distribution}Bernoulli probability distribution.
+When $N > 1$, the sequence of outcomes is referred to as a Bernoulli process.
+The \acf{PMF} of the \index{Binomial probability distribution}Binomial probability distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:pmf} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:binomial:pmf}
+      P(x \vert \theta; N) = f_{Bin}(x; N, \theta) = \binom{N}{x} \theta^{x}(1-\theta)^{1-x}
+\end{equation}
+
+Similar to the \index{Bernoulli probability distribution}Bernoulli probability distribution, the mean of the \index{Binomial probability distribution}Binomial probability distribution is $N\theta$ given the \acs{CLT} as was shown in Figure \ref{fig:probability:probability_distributions:bernoulli:coin}.
+The expected value of the \index{Binomial probability distribution}Binomial probability distribution is thus given in Equation~\eqref{eq:probability:probability_distributions:binomial:expected_value} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:binomial:expected_value}
+      E[x] = N\theta
+\end{equation}
+
+The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:binomial:mode} below.
+
+\begin{align}
+      \label{eq:probability:probability_distributions:binomial:mode}
       \begin{split}
-            P(H \vert E, C;  \theta, \phi, \psi) &\propto P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
+            M[x_{k}] &= E[x] + \theta \\
+            &= N\theta  + \theta \\
+            &= (N  + 1)\theta
+      \end{split}
+\end{align}
+
+\subsection{Categorical Probability Distribution}\label{sec:probability:probability_distributions:categorical}
+
+The \index{Categorical probability distribution}Categorical probability distribution is a discrete probability distribution over some random variable $x$, taking on any one of $K$ possible categories~\cite{ref:wackerly:2014}.
+There is no ordering to these categories and therefore, for simplicity, each category is assigned a numerical representative value such that $k = (1, 2, \dots, K)$.
+The probabilities for all outcomes is given by the probability vector $\vec{\theta} = (\theta_{1}, \dots, \theta_{K})$.
+This means that the probability $P(x=k)=\theta_{k}$, has support $x \in \{1, \dots, K\}$.
+The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\theta)$, is the generalization of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, the generalised \index{Bernoulli probability distribution}Bernoulli probability distribution or the Multinoulli probability distribution.
+In probability theory, the \index{Categorical probability distribution}Categorical probability distribution is often used to explain the outcome of a single experiment with more than two possible outcomes, such as rolling a six-sided die~\cite{ref:wackerly:2014}.
+The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution is given in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:categorical:pmf}
+      P(x \vert \theta; K) = f_{Cat}(x; K, \theta) = \prod_{k=1}^{K}\theta_{k}^{[x = k]}
+\end{equation}
+
+In Equation~\eqref{eq:probability:probability_distributions:categorical:pmf} above, $[x = k]$ is the \textit{Iversion Bracket}~\cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
+Given class $k$, the categorical distribution simply yields $\theta_{k}$ as is shown in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf_k} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:categorical:pmf_k}
+      f_{Cat}(x=k; K, \theta) = \theta_{k}
+\end{equation}
+
+The random variable $x$ can also be encoded in binary format, yielding a vector $\vec{x} = (x_{1}, \dots, x_{K})$ of \index{Bernoulli probability distribution}Bernoulli probability distributions such that the support is $\forall_{k=1}^{K} x_{k} \in \{0, 1\}$.
+Importantly, if the outcome of the random event is of category $k$, then $x_{k} = 1$ and $\forall_{j=1}^{K} x_{j} = 0, j \neq k$ so that the standard $K-1$ probability simplex $S$ still holds.
+The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution can then be rewritten as follows in Equation~\eqref{eq:probability:probability_distributions:categorical:pmf_alt} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:categorical:pmf_alt}
+      f_{Cat}(x; K, \theta) = \prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{k})}
+\end{equation}
+
+In Equation \ref{eq:probability:probability_distributions:categorical:pmf_alt} above, $\mathbbm{1}(x_{k})$ is the \textit{indicator function}, yielding 1 if $x_{k} = 1$ and 0 otherwise.
+
+Since there is no order to the underlying categories, the mean of the distribution does not yield any relevant information.
+The mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:categorical:mode} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:categorical:mode}
+      M[x] = \argmax_{k}(\theta_{1}, \dots, \theta_{K})
+\end{equation}
+
+\subsection{Multinomial Distribution}
+\label{sec:probability:probability_distributions:multinomial}
+
+The \index{Multinomial probability distribution}Multinomial probability distribution is a discrete probability distribution over some random variable $x = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials~\cite{ref:wackerly:2014}.
+The probabilities for all possible outcomes in a single trial is given by the probability vector $\vec{\theta} = (\theta_{1}, \dots, \theta_{K})$.
+The \index{Multinomial probability distribution}Multinomial probability distribution, denoted $Mul(N, K, \theta)$, is thus the generalization of the \index{Binomial probability distribution}Binomial probability distribution to $K$ dimensions.
+Consider the following special cases.
+
+\begin{itemize}
+      \item When $K$ is 2 and $N = 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Bernoulli probability distribution}Bernoulli probability distribution.
+      \item When $K$ is 2 and $N > 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Binomial probability distribution}Binomial probability distribution.
+      \item When $K > 2$ and $N = 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Categorical probability distribution}Categorical probability distribution.
+\end{itemize}
+
+The support for the Multinomial is $\forall_{i=1}^{K} x_{k} \in \{1, \dots, N\}, \sum_{k=1}^{K}x_{k} = N$ and the \acs{PMF} for the \index{Multinomial probability distribution}Multinomial probability distribution is given below in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf}.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:multinomial:pmf}
+      P(x \vert \theta; N; K) = f_{Mul}(x; N, K, \theta) = \frac{N!}{\prod_{k=1}^{K}x_{k}!} \prod_{k=1}^{K}\theta_{k}^{x_{k}}
+\end{equation}
+
+Similar to the \index{Categorical probability distribution}Categorical probability distribution, the random variable $x$ can also be encoded in binary format, yielding an $N \times K$ matrix $X$ of \index{Bernoulli probability distribution}Bernoulli probability distributions.
+The support is then given as $X \in \{0, 1\}^{N \times K}, \forall_{i=1}^{N}\sum_{k=1}^{K} x_{i,k} = 1$ so that the standard $K-1$ probability simplex $S$ still holds for each trial.
+The \acs{PMF} of the \index{Multinomial probability distribution}Multinomial probability distribution can then be rewritten as is presented in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt} below.
+
+\begin{equation}
+      \label{eq:probability:probability_distributions:multinomial:pmf_alt}
+      \begin{split}
+            f_{Mul}(x; N, K, \theta) &= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!}\prod_{i=1}^{N}\prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{i,k})} \\
+            &= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!} \prod_{k=1}^{K}\theta_{k}^{\sum_{i=1}^{N}\mathbbm{1}_{1}(x_{i,k})} \\
+            &= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!} \prod_{k=1}^{K}\theta_{k}^{N_{k}} \\
       \end{split}
@@
 
-The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $H$, given allocation to entity $E$ and credit $C$, parameterised by sampled $\theta$, $\phi$ and $\psi$.
-These parameters are in turn parameterised by concentrations $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$, which denote the prior beliefs of the \acs{BHH}.
+In Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt} above, $N_{k}$ is a summary variable, denoting the number of times a category $k$ occurs over all trials in $N$.
 
-\index{Naïve Bayes}
-\subsection{Naïve Bayes}\label{sec:bhh:selection_mechanism:naive_bayes}
+The \index{Categorical probability distribution}Categorical and \index{Multinomial probability distribution}Multinomial probability distributions are presented as binary encoded vectors in order to simplify the proof of their conjugate priors as is shown in the following section.
 
-This section aims to dissect the probabilistic model that is presented in Equestion~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
-The \acs{BHH} implements a form of Naïve Bayes classifier and thus, independence between events can be assumed.
-The following derived \acp{PMF} are provided as fundamental building blocks to show the mechanism by which the \acs{BHH} learns.
+\section{Conjugate Priors}\label{sec:probability:conjugate_priors}
 
-The independence between events for class label $H$, simply yields the \ac{PMF} of the \index{Multinomial probability distribution}Multinomial distribution as presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf} below.
+\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} states that conjugate priors are prior probability distributions that results in posterior distributions that are of the same functional form $\mathcal{A}(v)$ as the prior, but with different parameter values.
+This section considers the conjugate priors that are used with the Binomial likelihood and Categorical/Multinomial likelihood.
+
+\subsection{Binomial Likelihood}\label{sec:probability:conjugate_priors:binom_likelihood}
+
+The conjugate prior to a \index{Bernoulli probability distribution}Bernoulli probability distribution is the \index{Beta probability distribution}Beta probability distribution
+\cite{ref:wackerly:2014}. This is shown by demonstrating that the posterior distribution has the
+same functional form $\mathcal{A}(v)$ as the prior distribution as follows. \\\\
+\textbf{Setup}:
+
+\begin{itemize}
+      \item Let $I$ be a number of independent, identical  (iid) random events.
+
+      \item Let $\alpha \in \mathbb{R}, \alpha > 0$ and $\beta \in \mathbb{R}, \beta >0$ be the shape parameters to the \index{Beta probability distribution}Beta probability distribution.
+
+      \item Let $\theta$ be the probability of a success. With $\theta | \alpha, \beta \sim Beta(\alpha, \beta)$.
+
+      \item $P(\theta)$ is the prior probability distribution with the functional form $\mathcal{A}(v)$.
+
+      \item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with Boolean outcome.
+That is $x_{i} | \theta \overset{\text{iid}}{\sim} Ber(\theta)$ and $\mathcal{L}(x_{i} \vert \theta)$ is the Bernoulli likelihood.
+
+      \item Let $\mathcal{D}$ denote all the prior data $X$, parameterised by $\alpha$, $\beta$.
+
+      \item Let $N_{1} = \sum_{i=1}^{I} \mathbbm{1}(x_{i} = 1)$ and $N_{0} = \sum_{i=1}^{I} \mathbbm{1}(x_{i} = 0)$.
+\end{itemize}
+
+The Bernoulli likelihood is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:likelihood} below.
 
 \begin{equation}
-      \label{eq:bhh:selection_mechanism:naive_bayes:h_pmf}
+      \label{eq:probability:conjugate_priors:binom_likelihood:likelihood}
       \begin{split}
-            P(H \vert \theta)
-            &\propto \prod_{i=1}^{I} \prod_{k=1}^{K} P(h_{i,k} \vert \theta_{k}) \\
-            &\propto \prod_{i=1}^{I} \prod_{k=1}^{K} \theta_{k}^{\mathbbm{1}_{1}(h_{i,k})} \\
-            &\propto \prod_{k=1}^{K} \theta_{k}^{\sum_{i=1}^{I} \mathbbm{1}_{1}(h_{i,k})} \\
+            \mathcal{L}(\mathcal{D}) &=  P(\mathcal{D} | \theta) \\
+            &\propto \theta^{N_{1}}(1-\theta)^{N_{0}}
+      \end{split}
+\end{equation}
+
+By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.
+
+\begin{equation}
+      \begin{split}
+            \label{eq:probability:conjugate_priors:binom_likelihood:posterior}
+            P(\theta \vert \mathcal{D}) &= \frac{P(\mathcal{D} | \theta) P(\theta)}{P(\mathcal{D})}
+      \end{split}
+\end{equation}
+
+Since the denominator sums to $1$, one could get rid of the denominator and constants for the Bernoulli likelihood and the Beta prior, by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior_propto} below.
+
+\begin{equation}
+      \label{eq:probability:conjugate_priors:binom_likelihood:posterior_propto}
+      \begin{split}
+            P(\theta | \mathcal{D}) &\propto \left[\theta^{N_{1}}(1-\theta)^{N_{0}}\right] \left[\theta^{\alpha - 1} (1 - \theta)^{\beta - 1}\right] \\
+            &\propto \theta^{(N_{1} + \alpha) - 1}(1-\theta)^{(N_{0} + \beta) - 1} \\
+            &\propto Beta(N_{1} + \alpha, N_{0} + \beta)
+      \end{split}
+\end{equation}
+
+The posterior distribution has the same functional form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N_{1} + \alpha$ and $\beta' = N_{0} + \beta$.
+This shows that the \index{Beta probability distribution}Beta probability distribution is the conjugate prior used with the Bernoulli likelihood.
+
+\subsection{Categorical and Multinomial Likelihood}
+\label{sec:probability:conjugate_priors:cat_mult_likelihood}
+
+The conjugate prior to a \index{Categorical probability distribution}Categorical and \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Dirichlet probability distribution}Dirichlet probability distribution~\cite{ref:wackerly:2014}.
+The proof of the conjugate prior for the \index{Bernoulli probability distribution}Bernoulli probability distribution is similar to the proof presented in Section \ref{sec:probability:conjugate_priors:binom_likelihood} above.
+This means that the posterior distribution must have the same functional form $\mathcal{A}(v)$ as the prior distribution.
+The proof is shown as follows.
+\\\\
+\textbf{Setup}:
+
+\begin{itemize}
+      \item Let $I$ be a number of independent, identical (iid) random events.
+
+      \item Let $K$ be a number of possible outcomes for each event, with $K \geq 2$.
+
+      \item Let $\alpha = (\alpha_{1}, \dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} \in \mathbb{R}, \alpha_{k} > 0$ be the concentration parameters to the \index{Dirichlet probability distribution}Dirichlet probability distribution.
+
+      \item Let $\theta = (\theta_{1}, \dots, \theta_{K}), \forall_{k=1}^{K} \theta{k} \in (0,1), \sum_{k}^{K} \theta{k} = 1$ be the probability of each class in $K$ and $\theta$ belongs to the standard $K-1$ probability simplex $S$.
+With $\theta | \alpha \sim Dir(K, \alpha)$.
+
+      \item $P(\theta)$ is the prior probability distribution with the functional form $\mathcal{A}(v)$.
+
+      \item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with $K$ possible outcomes.
+That is $x_{i} | \theta \overset{\text{iid}}{\sim} Cat(\theta)$ and $\mathcal{L}(x_{i} \vert \theta)$ is the Categorical likelihood.
+
+      \item Let $\mathcal{D}$ denote all the prior data $X$, parameterised by $\alpha$.
+
+      \item Let $N = (N_{1}, \dots, N_{K}), N_{k} = \sum_{i=1}^{I} \mathbbm{1}(x_{i,k} = 1)$, denote the counts for each occurrence of a class $k$.
+\end{itemize}
+
+The likelihood of the Categorical and \index{Multinomial probability distribution}Multinomial probability distributions is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:likelihood} below.
+
+\begin{equation}
+      \label{eq:probability:conjugate_priors:mult_likelihood:likelihood}
+      \begin{split}
+            \mathcal{L}(\mathcal{D}) &=  P(\mathcal{D} | \theta) \\
             &\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}}
@@
 
-In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf} above, $N_{k}$ is a summary variable such that $N_{k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the event $h_{i}$ taking on class $k$ in $I$ independent, identical runs.
-
-The independence between events $E$, given class label $H$, is denoted by the likelihood of $E$,
-conditional to the occurrence of heuristic $k$ and model parameter $\phi$ as is given in in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} below.
+By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.
 
 \begin{equation}
-      \label{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf}
+      \label{eq:probability:conjugate_priors:mult_likelihood:posterior}
       \begin{split}
-            P(E \vert H;  \phi)
-            &\propto \prod_{i=1}^{I} \prod_{j=1}^{J} \prod_{k=1}^{K} P(e_{i,j,k} \vert h_{i,k} ; \phi_{j,k})  \\
-            &\propto \prod_{i=1}^{I} \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{\mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})} \\
-            &\propto \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{ \sum_{i}^{I} \left[ \mathbbm{1}_{1}(e_{i,j,k}) \mathbbm{1}_{1}(h_{i,k}) \right]} \\
-            &\propto \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}}
+            P(\theta \vert \mathcal{D}) &= \frac{P(\mathcal{D} \vert \theta) P(\theta)}{P(\mathcal{D})}
       \end{split}
@@
 
-In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} above, $N_{j,k}$ is a summary variable such that $N_{j,k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on class $k$, i.e.
-the count of occurrences of both entity $e$ and heuristic $k$ occurring together in $I$ independent, identical runs.
-
-Finally, the independence between events for the performance criteria $C$, given class label $H$, is denoted by the likelihood of $C$, conditional to the occurrence of heuristic $k$ and model parameter $\psi$ as given in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} below.
+Since the denominator sums to $1$, one could get rid of the denominator and constants for the \index{Dirichlet probability distribution}Dirichlet prior, by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior_propto} below.
 
 \begin{equation}
-      \label{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf}
+      \label{eq:probability:conjugate_priors:mult_likelihood:posterior_propto}
       \begin{split}
-            P(C\vert H;  \psi)
-            &\propto\prod_{i=1}^{I} \prod_{k=1}^{K} P(c_{i,k} \vert h_{i,k} ; \psi_{k})  \\
-            &\propto \prod_{i=1}^{I} \prod_{k=1}^{K} \psi_{k}^{\mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})} (1 - \psi_{k})^{\mathbbm{1}_{0}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})}\\
-            &\propto \prod_{k=1}^{K} \psi_{k}^{\sum_{i=1}^{I} \mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})} (1 - \psi_{k})^{\sum_{i=1}^{I} \mathbbm{1}_{0}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})}\\
-            &\propto \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{N_{0,k}} \\
-            &\propto \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})}
+            P(\theta \vert \mathcal{D}) &\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}} \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} - 1}\\
+            &\propto \prod_{k=1}^{K} \theta_{k}^{(N_{k} + \alpha_{k}) - 1} \\
+            &\propto Dir(K, N + \alpha)
       \end{split}
@@
 
-In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above, $N_{k}$ is the same summary variable as described for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}.
-$N_{1,k}$ is a summary variable such that $N_{1,k} = \sum_{i=1}^{I} \mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $c_{i}$ taking on a success $(c_{i}=1)$ and $h_{i}$ taking on class $k$, i.e.
-the count of occurrences of both succeeding in the performance criteria and heuristic $k$ occurring together in $I$ independent, identical runs.
-Similarly $N_{0,k} = N_{k} - N_{1,k}$ would denote the count of occurrences of the events $c_{i}$ taking on a failure $(c_{i}=0)$ and $h_{i}$
-taking on class $k$.
+The posterior distribution has the same form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N + \alpha$.
+This shows that the \index{Dirichlet probability distribution}Dirichlet probability distribution is the conjugate prior used with the Categorical/Multinomial likelihood.
 
-Equations~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}, \eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} and \eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} can be supplemented into the proportional evaluation of the predictive model as given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} and is given in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} below.
+The next section aims to provide the reader with the concept of Bayesian statistics and it is shown how Bayesian inference and Bayesian analysis can be used to to train a \acs{HH}.
+
+\section{Bayesian Statistics}
+\label{sec:probability:bayesian_statistics}
+
+In general, there are two main views to probability and statistics.
+These include the \textit{frequentist} and the \textit{Bayesian} view of statistics.
+Naturally, Bayesian statistics is based on \index{Bayes' theorem}Bayes' theorem as was presented in Section \ref{sec:probability:bayes_theorem}.
+Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event, and the conditions under which the event happens~\cite{ref:hackenberger:2019}.
+To introduce the concept of Bayesian inference and analysis, one first need to understand the difference between these two approaches.
+Bayesian statistics out-date the frequentist approach, but lacked interest in the early days, partly because of the limited applications where the conjugate priors where known~\cite{ref:hackenberger:2019}.
+More recent advancements in mathematical methods popularised the Bayesian approach again.
+A notable contribution to this switch, was the development of \acf{MCMC} in the 1950's.
+This family of algorithms allowed for the construction of random sampling algorithms from a probability distribution, which allows for the calculation of Bayesian hierarchical models~\cite{ref:hackenberger:2019}.
+Soon after followed one of the earliest papers that use Bayesian statistics in the field of medicine in 1982~\cite{ref:ashby:2006}.
+
+The difference between the frequentist approach and the Bayesian approach can be illustrated using an example.~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} suggests an experiment that investigates whether the sex ration in some hypothetical mice population is $1:1$.
+Two experiments can be designed.
+In the first experiment, mice are randomly selected until the first male is chosen.
+The result in this experiment will then be the total number of mice chosen by sex.
+For the second experiment, exactly seven mice are randomly selected.
+The result of the second experiment would be the number of males and females in a sample of seven.
+Suppose the outcome of the experiment was $FFFFFFM$, where $F$ represents a female and $M$ represents a male.
+If the experimental design is not known ahead of time, the result is useless.
+Consider the $P$-value for each of these experiments.
+The P-value is the probability of obtaining results at least as extreme as the observed results of a statistical hypothesis test~\cite{ref:beers:2022}.
+For the first experiment, the $P$-value is $0.031$ and for the second experiment, the $P$-value is $0.227$.
+Using a confidence level of $\alpha = 0.05$, one would conclude opposite outcomes for these two experiments, when it comes to rejecting the null hypothesis, despite using the same data.
+The reason for the difference in outcomes, is due to the difference in their null distributions.
+The first approach uses a geometrical approach, and the second used a binomial approach as is illustrated on Figure \ref{fig:probability:bayesian_statistics:mouse_experiment_outcome} below.
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=0.6\textwidth]{images/mouse_experiment_outcome.pdf}
+      \caption{The experimental outcomes for the mice-population experiments as was taken from~\cite{ref:hackenberger:2019} .}
+      \label{fig:probability:bayesian_statistics:mouse_experiment_outcome}
+\end{figure}
+
+If Bayesian statistics is used, the experimental design that was chosen does not matter.
+In Bayesian statistics it is common to use a \index{Beta probability distribution}Beta probability distribution as a prior distribution.
+If the prior distribution is sampled from $Beta(3,3)$ then using Bayesian analysis, the posterior distribution, according to the outcomes of this experiment, would yield $Beta(9,4)$.
+
+~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} mentions that the $Beta$ distribution can be seen as a probability distribution of the occurrence of specific parameters.
+From the information that is now known about the $Beta$ distribution, it is possible to calculate the probability that the sex ratio in this mice population is not $1:1$, with the $Beta$ distribution as a prior, yielding a $P$-value of $0.92$.
+This means that there is a probability of $92\%$ that the mice population is not $1:1$, regardless of experiment design.
+An illustration of this is given in Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} below.
+
+\begin{figure}[htbp]
+      \centering
+      \includegraphics[width=0.6\textwidth]{images/mouse_experiment_distributions.pdf}
+      \caption{An illustration of the prior and posterior probability distributions for the outcomes of the mice-population experiment, using a $Beta$ prior, as was taken from~\cite{ref:hackenberger:2019}.}
+      \label{fig:probability:bayesian_statistics:mouse_distributions}
+\end{figure}
+
+It can be seen from Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} how the posterior distribution differs from the prior distribution.
+This is the nature of Bayesian analysis and is presented in more detail in the following section.
+
+\subsection{Bayesian Analysis}
+\label{sec:probability:bayesian_statistics:bayesian_analysis}
+
+Bayesian analysis is the process by which prior beliefs are updated as a result of observing new data/evidence.
+Similar to the approaches followed above to explain Bayesian statistics, a proposal is made to explain Bayesian analysis by means of an example taken from~\cite{ref:wackerly:2014}.
+Let $Y = Y_{1}, Y_{2}, \dots, Y_{N}$ denote the random variable that is observed over a sample size of $N$.
+Then the likelihood of the sample is given as $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$.
+In the discrete case the likelihood function is defined to be the joint probability $P(Y_{1} = y_{1}, Y_{2} = y_{2}, \dots, Y_{N} = y_{n})$ and the continuous case yields the joint density of $Y_{1}, Y_{2}, \dots, Y_{N}$, evaluated at $y_{1}, y_{2}, \dots, y_{n}$.
+The Bayesian view models the parameter $\theta$ as a random variable with a probability distribution, referred to as the prior distribution of $\theta$.
+The symbol $\theta$, is included in the notation of $\mathcal{L}$ as an argument to illustrate that this function is dependent, explicitly, on the value of $\theta$.
+Importantly, prior distribution is specified before any data is collected and represents the theoretical prior knowledge about $\theta$.
+Assume that the parameter $\theta$ has a continuous distribution with density $g(\theta)$ that has no unknown parameters.
+Considering the likelihood of the data and the prior on $\theta$, then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood} below.
 
 \begin{equation}
-      \label{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood}
+      f(y_{1}, y_{2}, \dots, y_{n}, \theta) = \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)
+\end{equation}
+
+The marginal density or mass function of $Y_{1}, Y_{2}, \dots, Y_{N}$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:marginal_density} below.
+
+\begin{equation}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:marginal_density}
+      m(y_{1}, y_{2}, \dots, y_{n}) = \int_{-\infty}^{\infty} \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)d\theta
+\end{equation}
+
+Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$, according to \index{Bayes' theorem}Bayes' theorem, is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.
+
+\begin{equation}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density}
+      g^{*}(\theta \vert y_{1}, y_{2}, \dots, y_{n}) = \frac{\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)}{\int_{-\infty}^{\infty} \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)d\theta}
+\end{equation}
+
+\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} mentions that the posterior density summarises all the pertinent information about the parameter $\theta$ by making use of the information contained in the prior for $\theta$, as well as the information in the observed data/evidence.
+
+Consider now how Bayesian analysis can be used to update the priors on $\theta$ based on newly observed data.
+As with the example above, the below is taken from~\cite{ref:wackerly:2014}.
+Let $Y_{1}, Y_{2}, \dots, Y_{N}$ denote a random sample from a \index{Bernoulli probability distribution}Bernoulli probability distribution, where $P(Y_{i} = 1) = \theta$ and $P(Y_{i} = 0) = 1 - \theta$ and the prior distribution for $\theta$ is $Beta(\alpha, \beta)$.
+The posterior distribution for $\theta$ can be formulated as follows.
+The Bernoulli probability function can be written as is shown in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_1} below.
+
+\begin{equation}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:step_1}
+      P(y_{i} \vert \theta) = \theta^{y_{i}}(1 - \theta)^{1-y_{i}}
+\end{equation}
+
+In Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_1} above, $y_{i} = \{0,1\}$ and $0 < \theta < 1$.
+The likelihood $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$ is presented in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_2} below.
+
+\begin{equation}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:step_2}
       \begin{split}
-            P(H \vert E, C;  \theta, \phi, \psi)
-            &\propto P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)  \\
-            &\propto \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right]
+            \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)
+            &= P(y_{1}, y_{2}, \dots, y_{n} \vert \theta)\\
+            &= \theta^{y_{1}}(1-\theta)^{1 - y_{1}} \times \theta^{y_{2}}(1-\theta)^{1 - y_{2}} \times \dots \times \theta^{y_{n}}(1-\theta)^{1 - y_{n}}\\
+            &= \theta^{\sum y_{i}}(1-\theta)^{n-\sum y_{i}}
       \end{split}
@@
 
-Consider the practical implementation of the predictive model as shown in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} above.
-Computationally the equation presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} will underflow on a real computer if the resulting probabilities are very small.
-Discussions follow on numerical stability as it relates to practical implementation.
-
-\subsection{Numerical Stability}\label{sec:bhh:selection_mechanism:numerical_stability}
-
-When evaluating for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf}, the numerical stability is shown to underflow if the resulting probabilities from its parts are very small.
-Multiplying multiple fractional parameters leads to an even smaller fractional number.
-Probabilities might be very low at some points during training.
-Consider an example where training has stagnated, effectively leading to a scenario where a credit assignment strategy never fulfills a credit assignment, yielding an extremely small probability for $\psi$.
-A solution to the aforementioned problem is to apply the \textit{log-sum-exp} trick.
-The transformation of Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} using the log-sum-exp trick is given below in Equation~\eqref{eq:bhh:selection_mechanism:numerical_stability:log_sum_exp}.
+Then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ from Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood} can be formulated as in shown in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_3} below.
 
 \begin{equation}
-      \label{eq:bhh:selection_mechanism:numerical_stability:log_sum_exp}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:step_3}
       \begin{split}
-            LSE(P(h_{k} \vert e_{j}, c_{1};  \theta, \phi, \psi)) = \ln(\exp(\phi_{j,k}) +  \exp(\psi_{k}) + \exp(\theta_{k}))
+            f(y_{1}, y_{2}, \dots, y_{n}, \theta)
+            &= \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)\\
+            &= \theta^{\sum y_{i}}(1-\theta)^{n-\sum y_{i}} \times \frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\alpha - 1}(1 - \theta)^{\beta  - 1}\\
+            &= \frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}
       \end{split}
@@
 
-The log-sum-exp trick as shown above caters for very small probabilities, however, there might be a situation where  a random event is never seen, purely by chance.
-This results in a scenario referred to as \textit{mode collapse} and is discussed next.
-
-\subsection{Mode Collapse}\label{sec:bhh:selection_mechanism:mode_collapse}
-
-Mode collapse is the situation that occurs where the selective pressure towards a heuristic is close to zero as a result of random sampling, low initial bias or bad performance.
-This leads to a situation where the probabilistic model continually decreases the selective pressure, until the selection probability of that heuristic is 0, yielding no further observations of that particular random event.
-The \acs{BHH} addresses the aforementioned issue by:
-
-\begin{itemize}
-      \item Using \textit{symmetric} initialisation of the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$.
-
-      \item Setting the lower-bound of the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$ to 1, so that a selection probability of 0 is highly improbable.
-
-      \item Continuously resampling heuristics throughout the training process, before and after optimisation, eliminating mode collapse as a result of just random sampling.
-\end{itemize}
-
-Another suggestion is to ensure that at least one of every heuristic is always selected during training.
-The \acs{BHH} does not incorporate this approach as this could result in a situation where a bad choice of heuristic is continually used throughout the training process, possibly resulting in bad update steps/selections.
-Instead, the \acs{BHH} relies on the underlying learning process to control the selective pressure according to performance and nothing else.
-If this leads to a situation where mode collapse occurs, the \acs{BHH} accepts the outcome.
-
-\section{Optimisation Step}\label{sec:bhh:optimisation_step}
-
-Thus far all the fundamental components of the \acs{BHH} has been presented.
-The final step that is missing is to present the optimisation step by which the learning process takes place.
-This section aims to provide a solid mathematical explanation to show exactly how the \acs{BHH} is able to learn.
-
-The intent of the \acs{BHH} is to gather evidence that can be use to update prior beliefs about which heuristics perform well during training.
-These beliefs are represented by the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$.
-A change in prior beliefs is represented by a change in these concentration parameters.
-Specifically, it can be said, that the optimisation process implemented by the \acs{BHH}, updates \textit{pseudo counts} of events that are observed in the performance logs.
-These pseudo counts track the occurrence of a heuristic, an entity and resulting performance of these two elements.
-Through the credit assignment strategy, these pseudo counts are biased towards entity-heuristic combinations that meet performance requirements and yield credit allocations.
-
-The \acs{BHH} is an adaptive \ac{HH}, meaning that it implements online learning.
-Online learning refers to a process where learning happens during the training process.
-Throughout the training process, concentration parameters are updated strategically to guide the selection mechanism towards heuristics that perform well.
-The learning capability of the \acs{BHH} lies in carefully updating these concentration parameters.
-Another possibility is to introduce \textit{a priori} information in the form of expert knowledge.
-A priori biases can be introduced by carefully setting the concentration parameters to values that are known to be good.
-
-Generally, there are two different techniques that are used to train Naïve Bayes classifiers.
-The frequentist approach implements \acf{MLE} and the Bayesian approach implements \acf{MAP}.
-These methods are provided in Sections \ref{sec:bhh:optimisation_step:mle} and \ref{sec:bhh:optimisation_step:map} respectively and show how the concentration parameters are updated throughout the training process, yielding the mechanism by which optimisation and learning takes place.
-It should be mentioned that the \acs{BHH} makes use of \acs{MAP} to optimise the predictive model.
-However, the details of \acs{MLE} is provided as well as it contains fundamental mathematical building blocks that are required to present \acs{MAP}.
-
-\index{maximum likelihood estimation}
-\subsection{Maximum Likelihood Estimation}\label{sec:bhh:optimisation_step:mle}
-
-In probability theory and statistics, \acf{MLE} is a method that estimates the parameters of a prior probability distribution given newly observed data and evidence.
-This section shows that the values for $\theta$, $\phi$ and $\psi$ can be estimated by \ac{MLE} and is given in Equations \eqref{eq:bhh:optimisation_step:mle:theta}, \eqref{eq:bhh:optimisation_step:mle:phi} and \eqref{eq:bhh:optimisation_step:mle:psi} below.
+The marginal density of $Y_{1}, Y_{2}, \dots Y_{N}$ is then given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_4} below.
 
 \begin{equation}
-      \label{eq:bhh:optimisation_step:mle:theta}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:step_4}
       \begin{split}
-            \hat{\theta}_{k} = E[\theta_{k}] = \frac{N_{k}}{N}
+            m(y_{1}, y_{2}, \dots, y_{n})
+            &= \int_{0}^{1}\frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}d\theta\\
+            &= \frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\frac{\Gamma(\sum y_{i} + \alpha)\Gamma(n - \sum y_{i} + \beta)}{\Gamma(n + \alpha + \beta)}
       \end{split}
@@
 
+Finally, the posterior density of $\theta$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_5} below.
+
 \begin{equation}
-      \label{eq:bhh:optimisation_step:mle:phi}
+      \label{eq:probability:bayesian_statistic:bayesian_analysis:step_5}
       \begin{split}
-            \hat{\phi}_{j,k} = E[\phi_{j,k}] = \frac{N_{j,k}}{N_{j}}
+            g^{*}(\theta \vert y_{1}, y_{2}, \dots, y_{n})
+            &= \frac{\frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}}{\frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\frac{\Gamma(\sum y_{i} + \alpha)\Gamma(n - \sum y_{i} + \beta)}{\Gamma(n + \alpha + \beta)}}\\
+            &= \frac{\Gamma(n + \alpha + \beta)}{\Gamma(\sum y_{i} + \alpha)\Gamma(n - \sum y_{i} + \beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}
       \end{split}
@@
 
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:psi}
-      \begin{split}
-            \hat{\psi}_{k} = E[\psi_{k}] = \frac{N_{1,k}}{N_{k}}
-      \end{split}
-\end{equation}
+The posterior density has the same functional shape $\mathcal{A}(v)$ as the prior, yielding the update on prior parameters as $\alpha^{*} = \sum y_{i} + \alpha$ and $\beta^{*} = n - \sum y_{i} + \beta$.
 
-The derivations of the \acs{MLE} for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and
-$\hat{\psi}_{k}$ are presented as follows.
-The log likelihood of $\hat{\theta}$, $\hat{\phi}$ and $\hat{\psi}$ as derived from the Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} is given in Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} below.
+\section{Summary}\label{sec:probability:summary}
 
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:log_likelihood_all}
-      \begin{split}
-            & \mathcal{L}(\theta, \phi, \psi) \\
-            &= \ln\left(\left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right] \right) \\
-            &= \ln \left( \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right) +  \ln \left( \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right) + \ln \left( \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right) \\
-            &= \left( \sum_{j=1}^{J} \sum_{k=1}^{K} N_{j,k} \ ln \left( \phi_{j,k}
-            \right) \right) \\
-            &+ \left( \sum_{k=1}^{K} N_{1,k} \ln \left( \psi_{k} \right) + \left( N_{k} - N_{1,k} \right) \ln \left( 1 - \psi_{k} \right) \right) + \left( \sum_{k=1}^{K} N_{k} \ln \left( \theta_{k} \right) \right)
-      \end{split}
-\end{equation}
+This chapter provided the reader with all the necessary background information on probability theory and statistics.
+The origins of statistical analysis was discussed and the differences between the frequentist and Bayesian view of statistics were discussed in detail.
+Probability distributions and proofs of conjugate priors were provided with detailed mathematical descriptions.
+Finally, a detailed description of Bayesian analysis was provided with detailed mathematical descriptions.
 
-Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} can be broken down into each of its components.
-Consider the log likelihood of $\psi$ as denoted by Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_psi} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:log_likelihood_psi}
-      \begin{split}
-            \mathcal{L}(\psi) &=  \sum_{k=1}^{K} N_{1,k} \ln \left( \psi_{k} \right) + \left( N_{k} - N_{1,k} \right) \ln \left( 1 - \psi_{k} \right)
-      \end{split}
-\end{equation}
-
-The \acs{MLE} for $\hat{\psi_{k}} $ can be calculated by taking the partial derivative of Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_psi} with respect to $\psi_{k}$ and equating to zero as presented in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_psi} as follows.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_psi}
-      \begin{split}
-            \frac{\partial \mathcal{L}(\psi)}{\partial \psi_{k}} &= N_{1,k} \frac{1}{ \psi_{k}} + \left( N_{k} - N_{1,k} \right) \frac{-1}{ \left( 1 - \psi_{k} \right) } \\
-            0 &=  \frac{ N_{1,k} \left( 1 - \psi_{k} \right) +  \left( N_{1,k} - N_{k} \right) \psi_{k}}{ \psi_{k} \left( 1 - \psi_{k} \right) } \\
-            0 &=  N_{1,k} \left( 1 - \psi_{k} \right) +  \left( N_{1,k} - N_{k} \right) \psi_{k} \\
-            0 &=  N_{1,k} - N_{1,k} \psi_{k}  +  N_{1,k} \psi_{k} - N_{k}\psi_{k} \\
-            0 &=  N_{1,k} - N_{k}\psi_{k} \\
-            N_{k}\psi_{k} &=  N_{1,k} \\
-            \hat{\psi}_{k} &=  \frac{N_{1,k}}{N_{k}} \\
-      \end{split}
-\end{equation}
-
-The \acs{MLE} for $\hat{\theta_{k}} $ can be calculated similarly.
-However, one has to compensate for the $K-1$ simplex $S$ by adding error factor $\epsilon$, to correct values for $\theta$, where $\sum_{k}^{K} \theta_{k} \neq 1$.
-The new log likelihood function is then given in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_1} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_1}
-      \begin{split}
-            \mathcal{L}(\theta, \epsilon)
-            &=  \left( \sum_{k=1}^{K} N_{k} \ln \left( \theta_{k} \right) \right) + \epsilon \left( 1 - \sum_{k=1}^{K} \theta_{k} \right) \\
-            &=  \left( \sum_{k=1}^{K} N_{k} \ln \left( \theta_{k} \right) \right) + \left( \epsilon -  \epsilon \sum_{k=1}^{K} \theta_{k} \right)
-      \end{split}
-\end{equation}
-
-Solving first for $\epsilon$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_2} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_2}
-      \begin{split}
-            \frac{\partial \mathcal{L}(\theta, \epsilon)}{\partial \epsilon} &= 1 - \sum_{k=1}^{K} \theta_{k}  \\
-            \sum_{k=1}^{K} \theta_{k}  &= 1
-      \end{split}
-\end{equation}
-
-Then solving for $\theta_{k}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} as presented below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3}
-      \begin{split}
-            \frac{\partial \mathcal{L}(\theta, \epsilon)}{\partial \theta_{k}} &=  N_{k} \frac{1}{\theta_{k}}  + \epsilon(-1) \\
-            \frac{N_{k}}{\theta_{k}} &= \epsilon \\
-            N_{k} &= \theta_{k} \epsilon \\
-            \sum_{k=1}^{K} N_{k} &= \sum_{k=1}^{K} \theta_{k} \epsilon \\
-            N &= \epsilon \sum_{k=1}^{K} \theta_{k} \\
-            N &= \epsilon
-      \end{split}
-\end{equation}
-
-Substituting $N = \epsilon$ back into Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_4} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_4}
-      \begin{split}
-            N_{k} &= \theta_{k} \epsilon \\
-            N_{k} &= \theta_{k} N \\
-            \hat{\theta}_{k} &= \frac{N_{k}}{N}\\
-      \end{split}
-\end{equation}
-
-The \acs{MLE} for $\hat{\phi}_{j, k} $ is calculated similarly.
-To compensate for the $K-1$ simplex $S$, an error $\lambda = (\lambda_{1}, \dots, \lambda_{J})$ is added as is shown in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_1} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_1}
-      \begin{split}
-            \mathcal{L}(\phi, \lambda)
-            &=  \left( \sum_{j=1}^{J} \sum_{k=1}^{K} N_{j,k} \ ln \left( \phi_{j,k} \right) \right) + \sum_{j=1}^{J} \lambda_{j} \left( 1 - \sum_{k=1}^{K} \phi_{j,k} \right) \\
-            &=  \left( \sum_{j=1}^{J} \sum_{k=1}^{K} N_{j,k} \ ln \left( \phi_{j,k} \right) \right) + \sum_{j=1}^{J} \lambda_{j} - \sum_{j=1}^{J} \lambda_{j} \sum_{k=1}^{K} \phi_{j,k} \\
-      \end{split}
-\end{equation}
-
-Solving first for $\lambda_{j}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_2} as is given below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_2}
-      \begin{split}
-            \frac{\partial \mathcal{L}(\phi, \lambda)}{\partial \lambda_{j}} &= 1 - \sum_{k=1}^{K} \phi_{j,k}  \\
-            \sum_{k=1}^{K} \phi_{j,k}  &= 1
-      \end{split}
-\end{equation}
-
-Then solving for $\phi_{j,k}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3}
-      \begin{split}
-            \frac{\partial \mathcal{L}(\phi, \lambda)}{\partial \phi_{j,k}} &= N_{j,k} \frac{1}{\phi_{j,k}}  - \lambda_{j} \\
-            \frac{N_{j,k}}{\phi_{jk}} &= \lambda_{j} \\
-            N_{j,k} &= \phi_{j,k} \lambda_{j} \\
-            \sum_{k=1}^{K} N_{j,k} &= \sum_{k=1}^{K} \phi_{j,k} \lambda_{j} \\
-            N_{j} &= \lambda_{j} \sum_{k=1}^{K} \phi_{j,k} \\
-            N_{j} &= \lambda_{j}
-      \end{split}
-\end{equation}
-
-Substituting $N_{j} = \lambda_{j}$ back into Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_4} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_4}
-      \begin{split}
-            N_{j,k} &= \phi_{j,k} \lambda_{j} \\
-            N_{j,k} &= \phi_{j,k} N_{j} \\
-            \hat{\phi}_{j,k} &= \frac{N_{j,k}}{N_{j}}\\
-      \end{split}
-\end{equation}
-
-\index{maximum a posteriori estimation}
-\subsection{Maximum A Posteriori Estimation}\label{sec:bhh:optimisation_step:map}
-
-Another approach to optimising the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ is to optimise the parameters by their probability distributions' parameters.
-This process is referred to as \index{Bayesian analysis}\textit{Bayesian analysis}.
-This section provides the mathematical details of Bayesian analysis and \acf{MAP} as it is implemented by the \acs{BHH}.
-
-Bayesian analysis makes use of the \textit{posterior} probability distribution. The posterior distribution is simply expressed proportionally as follows.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:map:bayesian_analysis_lamens}
-      \begin{split}
-            POSTERIOR \propto LIKELIHOOD \times PRIOR
-      \end{split}
-\end{equation}
-
-The event $H$ is a multinomial distribution with probability parameter $\theta$.
-It is known that the conjugate prior to a multinomial distribution is a \index{Dirichlet probability distribution}Dirichlet probability distribution.
-The \textit{prior} probability distribution for $\theta_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_theta_prior} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:map:map_theta_prior}
-      \begin{split}
-            P(\theta | \alpha)
-            &\propto \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} -1}
-      \end{split}
-\end{equation}
-
-Furthermore, the event $E$ is also a multinomial distribution with parameter $\phi$.
-The \textit{prior} probability distribution for $\phi_{j,k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_phi_prior} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:map:map_phi_prior}
-      \begin{split}
-            P(\phi \vert \beta)
-            &\propto \prod_{j=1}^{J}  \prod_{k=1}^{K} \phi_{j,k}^{\beta_{j,k} -1}
-      \end{split}
-\end{equation}
-
-Finally, the event $C$ is a \index{Binomial probability distribution}Binomial probability distribution with probability parameter $\psi$.
-It is known that the conjugate prior to a \index{Binomial probability distribution}Binomial probability distribution is a Beta probability distribution.
-The prior probability distribution for $\psi_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:map:map_psi_prior}
-      \begin{split}
-            P(\psi | \gamma_{1}, \gamma_{0})
-            &\propto \prod_{k=1}^{K} \psi_{k}^{\gamma_{1,k}} (1- \psi_{k})^{\gamma_{2,k}}
-      \end{split}
-\end{equation}
-
-Putting the likelihood and priors together yields the posterior distribution as given in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:map:posterior}
-      \begin{split}
-            P(\theta, \phi, \psi \vert H, E, C;  \alpha, \beta, \gamma_{1}, \gamma_{0})
-            &\propto P(H \vert E, C; \theta, \phi, \psi)P(\theta, \phi, \psi \vert \alpha, \beta, \gamma_{1}, \gamma_{0}) \\
-            &= P(E \vert H; \phi) P(C \vert H; \psi) P(H \vert \theta) P(\phi \vert \beta) \\
-            &\times P(\psi \vert \gamma_{1}, \gamma_{0}) P(\theta \vert \alpha)  \\
-            &= \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right] \\
-            &\times \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{\beta_{j,k} - 1} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{\gamma_{1,k} - 1} (1 - \psi_{k})^{\gamma_{2,k} - 1} \right] \\
-            &\times \left[ \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} - 1} \right] \\
-            &= \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{(N_{j,k} + \beta_{j,k}) - 1} \right] \\
-            &\times \left[ \prod_{k=1}^{K} \psi_{k}^{(N_{1,k} + \gamma_{1,k}) - 1} (1 - \psi_{k})^{(N_{0,k} + \gamma_{2,k} )- 1} \right] \\
-            &\times \left[ \prod_{k=1}^{K} \theta_{k}^{(N_{k} + \alpha_{k}) - 1} \right]
-      \end{split}
-\end{equation}
-
-From Equation~\eqref{eq:bhh:optimisation_step:map:posterior} above, it can be seen that the posterior distribution has the same form $\mathcal{A}(v)$ as the prior distribution.
-The concentration update operations can then be given in Equations \eqref{eq:bhh:optimisation_step:map:alpha_update_operation}, \eqref{eq:bhh:optimisation_step:map:beta_update_operation}, \eqref{eq:bhh:optimisation_step:map:gamma1_update_operation} and \eqref{eq:bhh:optimisation_step:map:gamma2_update_operation} below.
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:map:alpha_update_operation}
-      \begin{split}
-            \alpha_{k}(t+1) = N_{k} + \alpha_{k}(t)
-      \end{split}
-\end{equation}
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:map:beta_update_operation}
-      \begin{split}
-            \beta_{j,k}(t+1) = N_{j,k} + \beta_{j,k}(t)
-      \end{split}
-\end{equation}
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:map:gamma1_update_operation}
-      \begin{split}
-            \gamma_{1,k}(t+1) = N_{1,k} + \gamma_{1,k}(t)
-      \end{split}
-\end{equation}
-
-\begin{equation}
-      \label{eq:bhh:optimisation_step:map:gamma2_update_operation}
-      \begin{split}
-            \gamma_{2,k}(t+1) = N_{0,k} + \gamma_{2,k}(t)
-      \end{split}
-\end{equation}
-
-It can be seen that the prior and posterior probability distributions are of the same form, $\mathcal{A}(v)$.
-It can therefore be said that the \acs{BHH} implements a Gaussian process.
-Since the reselection of heuristics happens at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acf{HMM}.
-
-Throughout this chapter a number of hyper-parameters have been identified. These are summarised and discussed in the next section.
-
-\section{Hyper-Parameters}\label{sec:bhh:hyper_parameters}
-
-This section provides a breakdown of all the hyper-parameters that were identified and briefly mentioned in this chapter.
-Some logical arguments can be made as to what their values should be, however it is still up to empirical analysis to determine the effects of certain hyper-parameter design decisions.
-Were possible, a range of possible values is provided.
-
-\index{heuristic pool}
-\subsection{Heuristic Pool}\label{sec:bhh:hyper_parameters:heuristic_pool}
-
-Section \ref{sec:bhh:heuristic_pool} provided the reader with the context and detail of the \index{heuristic pool}heuristic pool as it is included in the architecture of the \acs{BHH}.
-A detailed discussion was given around the importance of diversity and balancing exploration and exploitation capabilities.
-The \index{heuristic pool}heuristic pool hyper-parameter refers to the heuristic-pool configuration that is used.
-The configuration of the \index{heuristic pool}heuristic pool should account for the following factors.
-
-\begin{itemize}
-      \item The type of low-level heuristics to include in the \index{heuristic pool}heuristic pool.
-This dissertation investigates two main groups, including gradient-based \index{heuristic}heuristics and meta-heuristics.
-
-      \item The low-level heuristics' hyper-parameters. At a lower-level, each of these heuristics have their own set of hyper-parameters.
-
-      \item The \index{heuristic pool}heuristic pool size. This refers to the number of heuristics in the \index{heuristic pool}heuristic pool.
-\end{itemize}
-
-The design choices at a high level is not as strict for the \acs{BHH} as it is for low-level heuristics.
-If one is unsure as to which low-level hyper-parameters to use, one could simply include multiple configurations of a low-level heuristic, each with its own unique hyper-parameter configurations.
-
-\subsection{Population Size}\label{sec:bhh:hyper_parameters:population_size}
-
-Population size refers to the number of entities included in the \index{entity pool}entity pool.
-The population size to use is to be determined empirically.
-Naturely, an assumption is made that a larger population could lead to better results, assuming that entities are initialised uniformly across the solution search space.
-\citeauthor{ref:oldewage:2017}~\cite{ref:oldewage:2017} mentions that a large number of particles (entities) may be able to traverse a greater portion of the search space as every particle provides additional information about the search space.
-However, it is to be determined if this is indeed the case for the \acs{BHH}.
-The following factors need to be considered when picking a population size.
-
-\begin{itemize}
-      \item When considering the lower bound of possible population sizes, take into account the highest, minimum population size required by all low-level \index{heuristic}heuristics.
-For example, if one includes \Acs{DE} into the \index{heuristic}heuristic pool, one needs a population size of at least 4.
-For \acs{PSO}, the minimum population size is 3.
-
-      \item When considering the upper bound of possible population sizes, take into account that a bigger population size results in a more computationally expensive training process.
-Furthermore, there could exists a point of \textit{diminishing returns} where an increase in population size does not yield any better outcome.
-\end{itemize}
-
-\subsection{Credit}\label{sec:bhh:hyper_parameters:credit}
-
-The credit hyper-parameter refers to the credit assignment strategy that is used.
-This dissertation proposed 5 different credit assignment strategies that were presented in Section \ref{sec:bhh:credit_assignment_strategy}.
-The choice of credit assignment is assumed to be problem-dependent, however, this is to be  tested empirically.
-Along with the credit assignment strategy itself, the following factors related to the credit assignment strategy should be considered.
-
-\begin{itemize}
-      \item When to apply credit assignment during the training process.
-      \item What should the credit assignment score/value be (default = 1).
-      \item To what degree should credit assignment be allocated to past results in the performance log.
-\end{itemize}
-
-A number of other hyper-parameters are specifically included to address the list of considerations as given above.
-These include \textit{reselection}, \textit{replay} and \textit{reanalysis window sizes}, \textit{burn in}, \textit{discounted rewards} and \textit{normalisation}.
-Each of these are presented next.
-
-\subsection{Reselection}\label{sec:bhh:hyper_parameters:reselection}
-
-The reselection window size is a hyper-parameter that controls how often heuristic selections are resampled from the heuristic distribution, parameterised by the heuristic selection probability that is learnt.
-The choice of reselection should be influenced by the following considerations.
-If reselection happens too frequently, it does not allow heuristics sufficient time to achieve their goals and smooth out update steps.
-If reselection happens too infrequently, it does not allow for sufficient collection of samples/evidence from which learning is done.
-Naturally, the correct reselection window size to use is to be determined empirically.
-
-\subsection{Replay}\label{sec:bhh:hyper_parameters:replay}
-
-The replay window size is a hyper-parameter that controls how much historical performance information is kept in the performance log for the \acs{BHH} to learn from and was introduced in Section \ref{sec:bhh:performance_log}.
-The replay window size is a parameter that is borrowed from \acf{RL} and aims to control the effect that past performances have on the \acs{BHH}.
-A replay window size that is too small includes little to no memory, resulting in a situation where the \acs{BHH} simply looks at the most recent evidence that is collected and nothing more.
-On the contrary, if the replay window size is big, the \acs{BHH} tracks a longer history of past performances, leading to a situation where previously well-performing heuristics that are not relevant later in the training process, is still selected often.
-
-\subsection{Reanalysis}\label{sec:bhh:hyper_parameters:reanalysis}
-
-The reanalysis window size is a hyper-parameter that controls how often the \acs{BHH} updates its past beliefs (priors).
-The reanalysis window size goes hand in hand with the reselection and replay window sizes.
-If the reanalysis window is too small, the \acs{BHH} prematurely updates its priors.
-Similar to other hyper-parameters discussed thus far, the correct value to use for the reanalysis window size is to be determined empirically.
-However, some logical exclusions can be made.
-A reanalysis window size that is smaller than the reselection window size does not make sense, since the effects of reanalysis are only realised during reselection.
-A reanalysis window size that is too big could lead to a situation where the delay in updating priors could be detrimental to the outcomes of the \acs{BHH}.
-
-\subsection{Burn In}\label{sec:bhh:hyper_parameters:burn_in}
-
-Burn in is a hyper-parameter that is borrowed from \acf{MCMC} and aims to delay the learning process of the \acs{BHH}.
-The intent of the burn in hyper-parameter is to determine if heuristics need time to execute before reanalysis starts.
-Notice that a delay in the learning process does not mean that reselection doesn't occur or performance information is not collected in the replay window.
-Therefore, it should be noted that the burn in window size, reselection window size and replay window size should be considered together.
-If the replay window size is smaller than the burn in window size, performance information is discarded and an opportunity to learn is lost.
-
-\index{discounted rewards}
-\subsection{Discounted Rewards}\label{sec:bhh:hyper_parameters:discounted_rewards}
-
-\index{discounted rewards}Discounted rewards is another hyper-parameter that is borrowed from \acs{RL} and is a flag that determines if discounted rewards are applied or not.
-\index{discounted rewards}Discounted rewards refer to an implementation where credit assignments for past performances are exponentially decreased further into the past.
-An exponential decay factor of 0.5 is proposed.
-The intent of the discounted rewards flag is to scale the effect of past performances that are further back in the performance log, such that they have a smaller impact than more recent evidence on the learning process of the \acs{BHH}.
-
-\subsection{Normalisation}\label{sec:bhh:hyper_parameters:normalisation}
-
-Normalisation is a hyper-parameter that aims to provide a mechanism of control for the degree to which exploration is allowed.
-Figure \ref{sec:bhh:hyper_parameters:discounted_rewards:normalisation} shows the effect of different concentrations ($\alpha$ and $\beta$) on the Beta probability distribution.
-By normalising the concentration parameters for the \acs{BHH} ($\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$), the variance of the selection probability distributions increases, allowing for sampled probabilities further from the mean and thus allowing for more exploration.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.49\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{images/beta_1_1.pdf}
-            \caption{$\alpha=1$, $\beta=1$}
-            \label{sec:bhh:hyper_parameters:normalisation_beta_1_1}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{images/beta_5_5.pdf}
-            \caption{$\alpha=5$, $\beta=5$}
-            \label{sec:bhh:hyper_parameters:normalisation_beta_5_5}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.49\textwidth}
-            \centering
-            \centering
-            \includegraphics[width=\textwidth]{images/beta_20_20.pdf}
-            \caption{$\alpha=20$, $\beta=20$}
-            \label{sec:bhh:hyper_parameters:normalisation_beta_20_20}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The \index{Beta probability distribution}Beta probability distribution with varying $\alpha$ and $\beta$ values.}
-      \label{sec:bhh:hyper_parameters:discounted_rewards:normalisation}
-\end{figure}
-
-The following section discusses the default values for proxied update step operations.
-
-\subsection{Defaults}
-\label{sec:bhh:hyper_parameters:defaults}
-
-Section \ref{sec:bhh:heuristic:proxies} provided the reader with the concept of proxied heuristic update step operations.
-As was mentioned in Section \ref{sec:bhh:hyper_parameters:heuristic_pool}, low-level heuristics each have their own set of hyper-parameters as well.
-A set of default low-level parameters must be allocated specifically for these proxies.
-Consider a scenario where two instances of \acs{Adam} is included in the \index{heuristic pool}heuristic pool.
-Each has its own set of hyper-parameters that differ from each other.
-In the case of \acs{Adam}, there are 4 hyper-parameters that include learning rate, $\beta1$, $\beta2$ and $\epsilon$.
-If another heuristic needs to proxy \acs{Adam}'s expected gradient mean operation, a default $\beta1$ parameter must be supplied that is applied by the proxy mechanism.
-This is only the case when multiple instances of a heuristic is included and there is uncertainty about which instance's hyper-parameters to use for the proxied heuristic update steps.
-If there is only one instance of a particular heuristic, that instance's hyper-parameters are used.
-
-The next section provides the reader with the pseudo-code algorithm for the \acs{BHH}.
-
-\section{Algorithm}
-\label{sec:bhh:algorithm}
-
-The high level pseudo-code implementation of the \acs{BHH} is given in Algorithm \ref{algo:bhh}.
-
-\begin{algorithm}[H]
-      \caption{The pseudo-code for the implementation of the \acf{BHH}}
-      \label{algo:bhh}
-      \begin{algorithmic}
-            \State step $\gets 0$
-
-            \State select initial heuristics
-            \State initialise population and entities
-            \State evaluate entities' initial position
-            \State update population state
-
-            \While{stopping condition not met}
-            \For{all entities in entity pool}
-            \If{selected heuristic is gradient-based}
-            \State get gradients
-            \EndIf
-
-            \State apply low-level heuristic and proxy operations
-            \State update population state
-            \State log performance metrics to performance log
-
-            \If {step < burn-in window size}
-            \State select heuristic
-            \Else
-            \If {step $\mathbin{\%}$ reanalysis window size = 0}
-            \State apply Bayesian analysis
-            \EndIf
-
-            \If {step $\mathbin{\%}$ reselection window size = 0}
-            \State select heuristic
-            \EndIf
-
-            \If {step > replay window size}
-            \State prune performance log
-            \EndIf
-            \EndIf
-            \EndFor
-            \State step $\gets$ step + $1$
-            \EndWhile
-      \end{algorithmic}
-\end{algorithm}
-
-\section{Summary}
-\label{sec:bhh:summary}
-
-This chapter provided extensive detail on the inner workings and design of the \acs{BHH}.
-The \acs{BHH} was formally classified and the details around various components of the \acs{BHH}'s architecture was presented.
-Formal mathematical descriptions of the Bayesian selection method have been provided.
-The selection mechanism was presented as a probabilistic, predictive classifier.
-The optimisation process, by means of Bayesian analysis, has also been presented.
-Hyper-parameters were discussed in detail and a pseudo code implementation of the \acs{BHH} was presented.
-
-This methodology for the empirical process is provided in the following chapter.
+This chapter concludes all the relevant background information that is needed to formulate the \acs{BHH}. The proposed \acs{BHH} is presented in the following chapter.

### 2022-11-27 dissertation/chapters/05-probability.tex
🚧 (final-review): Chapter 5 WIP, just before conjugate priors

@@
 
-\subsection{Beta probability distribution}\label{sec:probability:probability_distributions:beta}
+\subsection{Beta Probability Distribution}\label{sec:probability:probability_distributions:beta}
 
@@
 
-where $\Gamma$ is the Gamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func} below.
+where $\Gamma$ is the Gamma function defined as
 
@@
 
-It should be noted that the Gamma function can also be written as shown in Equation~\eqref{eq:probability:probability_distributions:beta:gamma_func_alt} below.
+It should be noted that the Gamma function can also be written as
 
@@
 
-The control parameters $\alpha$ and $\beta$, determine the shape of the distribution.
+The control parameters $\alpha$ and $\beta$ determine the shape of the distribution.
 There exists a special case where $\alpha = \beta$.
@@
 In the case where $\alpha = \beta = 1$ the distribution is equivalent to the uniform distribution over all points in its support.
-The \index{Beta probability distribution}Beta probability distribution for various values of $\alpha$ and $\beta$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:beta}.
+The \index{Beta probability distribution}Beta probability distribution for various values of $\alpha$ and $\beta$, including the symmetric version is illustrated in Figure \ref{fig:probability:probability_distributions:beta}.
 
@@
 
-The expected value of $x$ is given below in Equation~\eqref{eq:probability:probability_distributions:beta:expected_value}.
+The expected value of $x$ is given as
 
@@
 
-Similarly, the expected value of the natural logarithm of $x$ can be calculated as is shown below in Equation~\eqref{eq:probability:probability_distributions:beta:expected_value_ln}.
+Similarly, the expected value of the natural logarithm of $x$ is calculated as
 
@@
 
-In Equation~\eqref{eq:probability:probability_distributions:beta:expected_value_ln} above, $\psi$ is the logarithmic derivative of the Gamma function, called the \textit{Digamma} function.
-The Digamma function is given below in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}.
+where $\psi$ is the logarithmic derivative of the Gamma function, called the \textit{Digamma} function. The Digamma function is given as
 
@@
 
-Finally, the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:beta:mode} below.
+Finally, the mode of the distribution is given as
 
@@
 
-\subsection{Dirichlet probability distribution}\label{sec:probability:probability_distributions:dirichlet}
+\subsection{Dirichlet Probability Distribution}\label{sec:probability:probability_distributions:dirichlet}
 
-The \index{Dirichlet probability distribution}Dirichlet probability distribution is a family of multivariate continuous probability distributions over some $x$ in $K$ dimensions~\cite{ref:wackerly:2014}.
-The \index{Dirichlet probability distribution}Dirichlet probability distribution is the multivariate generalization of the \index{Beta probability distribution}Beta probability distribution and is thus sometimes referred to by its alternative name, the multivariate Beta probability distribution.
-The \index{Dirichlet probability distribution}Dirichlet probability distribution is parameterised by some vector $\vec{\alpha} = (\alpha_{1}$,  $\dots, \alpha_{K})$ $\forall_{k=1}^{K} \alpha_{k} > 0$, $\alpha_{k} \in \mathbb{R}$.
-Throughout this chapter, the vector notation is dropped for simplicity and readability.
-$\alpha$ is referred to as the concentration parameter.
-The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K \geq 2$ with parameters $\alpha$, denoted $Dir(\alpha)$, has a \acs{PDF} as is given in Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} below.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution is a family of multivariate continuous probability distributions over some $\boldsymbol{x}$ in $K$ dimensions~\cite{ref:wackerly:2014}.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution is the multivariate generalization of the \index{Beta probability distribution}Beta probability distribution and is thus sometimes referred to by its alternative name, i.e.
+the multivariate Beta probability distribution.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution is parameterised by some vector $\boldsymbol{\alpha} = (\alpha_{1}$,  $\dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} > 0, \alpha_{k} \in \mathbb{R}$.
+The parameter, $\boldsymbol{\alpha}$, is referred to as the concentration parameter.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K \geq 2$ with parameter $\boldsymbol{\alpha}$, denoted $Dir(\boldsymbol{\alpha})$, has a \acs{PDF} given as
 
@@
       \label{eq:probability:probability_distributions:dirichlet:pdf}
-      P(x \vert \alpha) =  f_{Dir}(x; K, \alpha) = \frac{1}{B(\alpha)}  \prod_{k=1}^{K} x_{k}^{\alpha_{k} - 1}
+      P(\boldsymbol{x} \vert \boldsymbol{\alpha}) =  f_{Dir}(\boldsymbol{x}; K, \boldsymbol{\alpha}) = \frac{1}{B(\boldsymbol{\alpha})}  \prod_{k=1}^{K} x_{k}^{\alpha_{k} - 1}
 \end{equation}
 
-In Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} above, the normalising constant $B(\alpha)$, is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:norm_cost}.
+The normalising constant, $B(\boldsymbol{\alpha})$, is defined as
 
@@
       \label{eq:probability:probability_distributions:dirichlet:norm_cost}
-      B(\alpha) = \frac{\prod_{k=1}^{K} \Gamma(\alpha_{k})}{\Gamma(\alpha_{0})}
+      B(\boldsymbol{\alpha}) = \frac{\prod_{k=1}^{K} \Gamma(\alpha_{k})}{\Gamma(\alpha_{0})}
 \end{equation}
 
-In Equation~\eqref{eq:probability:probability_distributions:dirichlet:pdf} above, $\alpha_{0}$ is defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:alpha_0} below.
+where $\alpha_{0}$ is defined as
 
@@
 
-Importantly, the set $\{x_{k}\}_{k=1}^{K}$ belongs to the standard $K-1$ probability simplex $S$, meaning that $x_{K} = 1 - \sum_{k=1}^{K-1}x_{k}$ with support $\forall_{k=1}^{K} x \in [0,1]$.
-Under the simplex $S$, this means that the sum over all values of the vector $\vec{x}$ must be 1.
+Importantly, the set $\{x_{k}\}_{k=1}^{K}$ belongs to the standard $K-1$ probability simplex $S$, meaning that $x_{K} = 1 - \sum_{k=1}^{K-1}x_{k}$ with support $\forall_{k=1}^{K} x_{k} \in [0,1]$.
+Under the simplex $S$, this means that the sum over all values of the vector $\boldsymbol{x}$ must be 1.
 The simplex can thus be rewritten as $\sum_{k=1}^{K}x_{k} = 1$.
 
-Similar to the \index{Beta probability distribution}Beta probability distribution, $\alpha$ determines the shape of the distribution in $K$ dimensions and thus, there also exist a special case, referred to as the \textit{symmetric} distribution when $\forall_{k=1}^{K} \alpha_{k} = c$, where $c$ is some constant.
+Similar to the \index{Beta probability distribution}Beta probability distribution, $\boldsymbol{\alpha}$ determines the shape of the distribution in $K$ dimensions and thus, there also exist a special case, referred to as the \textit{symmetric} distribution when $\forall_{k=1}^{K} \alpha_{k} = c$, where $c$ is some constant.
 In the case where $c = 1$, the distribution is referred to as a \textit{flat} distribution and yields the uniform distribution over all points in $S$.
-The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K = 3$, for various values of $\alpha$, including the symmetric version is presented in Figure \ref{fig:probability:probability_distributions:dirichlet}.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K = 3$ for various values of $\boldsymbol{\alpha}$, including the symmetric version, is presented in Figure \ref{fig:probability:probability_distributions:dirichlet}.
 
@@
       \caption{The \acfp{PDF} for the \index{Dirichlet probability distribution}Dirichlet probability distribution over the 2-simplex.
-The concentration parameter $\alpha$ is varied.
+The concentration parameter $\boldsymbol{\alpha}$ is varied.
 The values of the \acs{PDF} are shown by the color maps with contour lines at equal values as indicated in the color bars~\cite{ref:dirichlet:2020}.}
@@
 
-The expected value of $x$ can be calculated as shown in Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value} below.
+The expected value of $x_{k}$ is calculated as
 
@@
 
-Similarly, the expected value of the natural logarithm of $x_{k}$ can be calculated as defined in Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value_ln} below.
+Similarly, the expected value of the natural logarithm of $x_{k}$ is calculated as
 
@@
 
-In Equation~\eqref{eq:probability:probability_distributions:dirichlet:expected_value_ln} above, $\psi$ is the Digamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}.
-Finally, the mode of the distribution is given in Equation~\eqref{eq:probability:probability_distributions:dirichlet:mode} below.
+where $\psi$ is the Digamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}. Finally, the mode of the distribution is given as
 
@@
 
-\subsection{Bernoulli probability distribution}\label{sec:probability:probability_distributions:bernoulli}
+\subsection{Bernoulli Probability Distribution}\label{sec:probability:probability_distributions:bernoulli}
 
@@
 The outcome of such an experiment is a Boolean value.
-The \index{Bernoulli probability distribution}Bernoulli probability distribution has a \acf{PMF}, given as
+The \index{Bernoulli probability distribution}Bernoulli probability distribution has a \acs{PMF}, given as
 
@@
 
-\subsection{Binomial probability distribution}\label{sec:probability:probability_distributions:bin}
+\subsection{Binomial Probability Distribution}\label{sec:probability:probability_distributions:bin}
 
@@
 When $N > 1$, the sequence of outcomes is referred to as a Bernoulli process.
-The \acf{PMF} of the \index{Binomial probability distribution}Binomial probability distribution is given as
+The \acs{PMF} of the \index{Binomial probability distribution}Binomial probability distribution is given as
 
@@
 There is no ordering to these categories and therefore, for simplicity, each category is assigned a numerical representative value such that $k \in \{1, 2, \dots, K\}$.
-The probabilities for all outcomes is given by the probability vector $\vec{\theta} = (\theta_{1}, \dots, \theta_{K})$.
+The probabilities for all outcomes is given by the probability vector $\boldsymbol{\theta} = (\theta_{1}, \dots, \theta_{K})$.
 This means that the probability $P(x=k)=\theta_{k}$ has support $x \in \{1, \dots, K\}$.
-The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\theta)$, is a generalization of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, i.e.
+The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\boldsymbol{\theta})$, is a generalization of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, i.e.
 the generalised \index{Bernoulli probability distribution}Bernoulli probability distribution or the Multinoulli probability distribution.
@@
       \label{eq:probability:probability_distributions:categorical:pmf}
-      P(x \vert \theta; K) = f_{Cat}(x; K, \theta) = \prod_{k=1}^{K}\theta_{k}^{[x = k]}
+      P(x \vert \boldsymbol{\theta}; K) = f_{Cat}(x; K, \boldsymbol{\theta}) = \prod_{k=1}^{K}\theta_{k}^{[x = k]}
 \end{equation}
 
-where the term $[x = k]$ is the \textit{Iversion Bracket}~\cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
-Given class $k$, the categorical distribution simply yields $\theta_{k}$ as is follows:
+where the term, $[x = k]$, is the \textit{Iversion Bracket}~\cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
+Given class $k$, the categorical distribution simply yields $\theta_{k}$ as follows:
 
@@
 
-The \index{Multinomial probability distribution}Multinomial probability distribution is a discrete probability distribution over some random variable $x = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials~\cite{ref:wackerly:2014}.
-The probabilities for all possible outcomes in a single trial is given by the probability vector $\vec{\theta} = (\theta_{1}, \dots, \theta_{K})$.
-The \index{Multinomial probability distribution}Multinomial probability distribution, denoted $Mul(N, K, \theta)$, is thus the generalization of the \index{Binomial probability distribution}Binomial probability distribution to $K$ dimensions.
-Consider the following special cases.
+The \index{Multinomial probability distribution}Multinomial probability distribution is a discrete probability distribution over some random variable $\boldsymbol{x} = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials~\cite{ref:wackerly:2014}.
+The probabilities for all possible outcomes in a single trial is given by the probability vector, $\boldsymbol{\theta} = (\theta_{1}, \dots, \theta_{K})$.
+The \index{Multinomial probability distribution}Multinomial probability distribution, denoted $Mul(N, K, \boldsymbol{\theta})$, is thus a generalization of the \index{Binomial probability distribution}Binomial probability distribution to $K$ dimensions.
+Consider the following special cases:
 
@@
 
-The support for the Multinomial is $\forall_{i=1}^{K} x_{k} \in \{1, \dots, N\}, \sum_{k=1}^{K}x_{k} = N$ and the \acs{PMF} for the \index{Multinomial probability distribution}Multinomial probability distribution is given below in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf}.
+The support for the Multinomial is $\forall_{i=1}^{K} x_{k} \in \{1, \dots, N\}, \sum_{k=1}^{K}x_{k} = N$ and the \acs{PMF} for the \index{Multinomial probability distribution}Multinomial probability distribution is given as
 
@@
       \label{eq:probability:probability_distributions:multinomial:pmf}
-      P(x \vert \theta; N; K) = f_{Mul}(x; N, K, \theta) = \frac{N!}{\prod_{k=1}^{K}x_{k}!} \prod_{k=1}^{K}\theta_{k}^{x_{k}}
+      P(\boldsymbol{x} \vert \boldsymbol{\theta}; N; K) = f_{Mul}(x; N, K, \boldsymbol{\theta}) = \frac{N!}{\prod_{k=1}^{K}x_{k}!} \prod_{k=1}^{K}\theta_{k}^{x_{k}}
 \end{equation}
@@
 Similar to the \index{Categorical probability distribution}Categorical probability distribution, the random variable $x$ can also be encoded in binary format, yielding an $N \times K$ matrix $X$ of \index{Bernoulli probability distribution}Bernoulli probability distributions.
-The support is then given as $X \in \{0, 1\}^{N \times K}, \forall_{i=1}^{N}\sum_{k=1}^{K} x_{i,k} = 1$ so that the standard $K-1$ probability simplex $S$ still holds for each trial.
-The \acs{PMF} of the \index{Multinomial probability distribution}Multinomial probability distribution can then be rewritten as is presented in Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt} below.
+The support is then given as $\boldsymbol{X} \in \{0, 1\}^{N \times K}, \forall_{i=1}^{N}\sum_{k=1}^{K} x_{i,k} = 1$ so that the standard $K-1$ probability simplex $S$ still holds for each trial.
+The \acs{PMF} of the \index{Multinomial probability distribution}Multinomial probability distribution is then rewritten as
 
@@
       \begin{split}
-            f_{Mul}(x; N, K, \theta) &= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!}\prod_{i=1}^{N}\prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{i,k})} \\
+            f_{Mul}(\boldsymbol{X}; N, K, \boldsymbol{\theta}) &= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!}\prod_{i=1}^{N}\prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{i,k})} \\
             &= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!} \prod_{k=1}^{K}\theta_{k}^{\sum_{i=1}^{N}\mathbbm{1}_{1}(x_{i,k})} \\
@@
 
-In Equation~\eqref{eq:probability:probability_distributions:multinomial:pmf_alt} above, $N_{k}$ is a summary variable, denoting the number of times a category $k$ occurs over all trials in $N$.
-
-The \index{Categorical probability distribution}Categorical and \index{Multinomial probability distribution}Multinomial probability distributions are presented as binary encoded vectors in order to simplify the proof of their conjugate priors as is shown in the following section.
+where $N_{k}$ is a summary variable, denoting the number of times a category $k$ occurs over all trials in $N$.
 

### 2022-11-27 dissertation/chapters/05-probability.tex
🚧 (final-review): Chapter 5, Bayesian Statistics WIP

@@
 
-\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} states that conjugate priors are prior probability distributions that results in posterior distributions that are of the same functional form $\mathcal{A}(v)$ as the prior, but with different parameter values.
+\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} state that conjugate priors are prior probability distributions that result in posterior distributions that are of the same functional form, $\mathcal{A}(v)$, as the prior, but with different parameter values.
 This section considers the conjugate priors that are used with the Binomial likelihood and Categorical/Multinomial likelihood.
@@
 \cite{ref:wackerly:2014}. This is shown by demonstrating that the posterior distribution has the
-same functional form $\mathcal{A}(v)$ as the prior distribution as follows. \\\\
+same functional form, $\mathcal{A}(v)$, as the prior distribution as follows. \\\\
 \textbf{Setup}:
@@
 
-      \item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with Boolean outcome.
+      \item Let $\boldsymbol{X} = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with Boolean outcome.
 That is $x_{i} | \theta \overset{\text{iid}}{\sim} Ber(\theta)$ and $\mathcal{L}(x_{i} \vert \theta)$ is the Bernoulli likelihood.
 
-      \item Let $\mathcal{D}$ denote all the prior data $X$, parameterised by $\alpha$, $\beta$.
+      \item Let $\boldsymbol{\mathcal{D}}$ denote all the prior data $\boldsymbol{X}$, parameterised by $\alpha$, $\beta$.
 
@@
 
-The Bernoulli likelihood is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:likelihood} below.
+The Bernoulli likelihood is given as
 
@@
       \begin{split}
-            \mathcal{L}(\mathcal{D}) &=  P(\mathcal{D} | \theta) \\
+            \mathcal{L}(\boldsymbol{\mathcal{D}}) &=  P(\boldsymbol{\mathcal{D}} | \theta) \\
             &\propto \theta^{N_{1}}(1-\theta)^{N_{0}}
@@
 
-By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior} below.
+By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\boldsymbol{\mathcal{D}}$ is given as
 
@@
             \label{eq:probability:conjugate_priors:binom_likelihood:posterior}
-            P(\theta \vert \mathcal{D}) &= \frac{P(\mathcal{D} | \theta) P(\theta)}{P(\mathcal{D})}
+            P(\theta \vert \boldsymbol{\mathcal{D}}) &= \frac{P(\boldsymbol{\mathcal{D}} | \theta) P(\theta)}{P(\boldsymbol{\mathcal{D}})}
       \end{split}
@@
 
-Since the denominator sums to $1$, one could get rid of the denominator and constants for the Bernoulli likelihood and the Beta prior, by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation~\eqref{eq:probability:conjugate_priors:binom_likelihood:posterior_propto} below.
+Since the denominator sums to $1$, the denominator and constants for the Bernoulli likelihood and the Beta prior can be removed by expressing the posterior as proportional to the likelihood times the prior as follows:
 
@@
       \begin{split}
-            P(\theta | \mathcal{D}) &\propto \left[\theta^{N_{1}}(1-\theta)^{N_{0}}\right] \left[\theta^{\alpha - 1} (1 - \theta)^{\beta - 1}\right] \\
+            P(\theta | \boldsymbol{\mathcal{D}}) &\propto \left[\theta^{N_{1}}(1-\theta)^{N_{0}}\right] \left[\theta^{\alpha - 1} (1 - \theta)^{\beta - 1}\right] \\
             &\propto \theta^{(N_{1} + \alpha) - 1}(1-\theta)^{(N_{0} + \beta) - 1} \\
@@
 
-The posterior distribution has the same functional form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N_{1} + \alpha$ and $\beta' = N_{0} + \beta$.
+The posterior distribution has the same functional form, $\mathcal{A}(v)$, as the prior, but with updated prior parameters $\alpha' = N_{1} + \alpha$ and $\beta' = N_{0} + \beta$.
 This shows that the \index{Beta probability distribution}Beta probability distribution is the conjugate prior used with the Bernoulli likelihood.
@@
 The conjugate prior to a \index{Categorical probability distribution}Categorical and \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Dirichlet probability distribution}Dirichlet probability distribution~\cite{ref:wackerly:2014}.
-The proof of the conjugate prior for the \index{Bernoulli probability distribution}Bernoulli probability distribution is similar to the proof presented in Section \ref{sec:probability:conjugate_priors:binom_likelihood} above.
-This means that the posterior distribution must have the same functional form $\mathcal{A}(v)$ as the prior distribution.
+The proof of the conjugate prior for the \index{Bernoulli probability distribution}Bernoulli probability distribution is similar to the proof presented in Section \ref{sec:probability:conjugate_priors:binom_likelihood}.
+This means that the posterior distribution must have the same functional form, $\mathcal{A}(v)$, as the prior distribution.
 The proof is shown as follows.
@@
 
-      \item Let $\alpha = (\alpha_{1}, \dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} \in \mathbb{R}, \alpha_{k} > 0$ be the concentration parameters to the \index{Dirichlet probability distribution}Dirichlet probability distribution.
+      \item Let $\boldsymbol{\alpha} = (\alpha_{1}, \dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} \in \mathbb{R}, \alpha_{k} > 0$ be the concentration parameters to the \index{Dirichlet probability distribution}Dirichlet probability distribution.
 
-      \item Let $\theta = (\theta_{1}, \dots, \theta_{K}), \forall_{k=1}^{K} \theta{k} \in (0,1), \sum_{k}^{K} \theta{k} = 1$ be the probability of each class in $K$ and $\theta$ belongs to the standard $K-1$ probability simplex $S$.
-With $\theta | \alpha \sim Dir(K, \alpha)$.
+      \item Let $\boldsymbol{\theta} = (\theta_{1}, \dots, \theta_{K}), \forall_{k=1}^{K} \theta_{k} \in (0,1), \sum_{k}^{K} \theta_{k} = 1$ be the probability of each class in $K$ and $\boldsymbol{\theta}$ belongs to the standard $K-1$ probability simplex $S$.
+With $\boldsymbol{\theta} | \boldsymbol{\alpha} \sim Dir(K, \boldsymbol{\alpha})$.
 
-      \item $P(\theta)$ is the prior probability distribution with the functional form $\mathcal{A}(v)$.
+      \item $P(\boldsymbol{\theta})$ is the prior probability distribution with the functional form $\mathcal{A}(v)$.
 
-      \item Let $X = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with $K$ possible outcomes.
-That is $x_{i} | \theta \overset{\text{iid}}{\sim} Cat(\theta)$ and $\mathcal{L}(x_{i} \vert \theta)$ is the Categorical likelihood.
+      \item Let $\boldsymbol{X} = (\boldsymbol{x_{1}}, \dots, \boldsymbol{x_{I}})$ be the outcomes of $I$ independent, identical random events, each with $K$ possible outcomes.
+That is $\boldsymbol{x_{i}} | \boldsymbol{\theta} \overset{\text{iid}}{\sim} Cat(\boldsymbol{\theta})$ and $\mathcal{L}(\boldsymbol{x_{i}} \vert \boldsymbol{\theta})$ is the Categorical likelihood.
 
-      \item Let $\mathcal{D}$ denote all the prior data $X$, parameterised by $\alpha$.
+      \item Let $\boldsymbol{\mathcal{D}}$ denote all the prior data $\boldsymbol{X}$, parameterised by $\boldsymbol{\alpha}$.
 
-      \item Let $N = (N_{1}, \dots, N_{K}), N_{k} = \sum_{i=1}^{I} \mathbbm{1}(x_{i,k} = 1)$, denote the counts for each occurrence of a class $k$.
+      \item Let $\boldsymbol{N} = (N_{1}, \dots, N_{K}), N_{k} = \sum_{i=1}^{I} \mathbbm{1}(x_{i,k} = 1)$, denote the counts for each occurrence of a class $k$.
 \end{itemize}
 
-The likelihood of the Categorical and \index{Multinomial probability distribution}Multinomial probability distributions is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:likelihood} below.
+The likelihood of the Categorical and \index{Multinomial probability distribution}Multinomial probability distributions is given as
 
@@
       \begin{split}
-            \mathcal{L}(\mathcal{D}) &=  P(\mathcal{D} | \theta) \\
+            \mathcal{L}(\boldsymbol{\mathcal{D}}) &=  P(\boldsymbol{\mathcal{D}} | \boldsymbol{\theta}) \\
             &\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}}
@@
 
-By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\mathcal{D}$ is given in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior} below.
+By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\mathcal{D}$ is given as
 
@@
       \begin{split}
-            P(\theta \vert \mathcal{D}) &= \frac{P(\mathcal{D} \vert \theta) P(\theta)}{P(\mathcal{D})}
+            P(\boldsymbol{\theta} \vert \boldsymbol{\mathcal{D}}) &= \frac{P(\boldsymbol{\mathcal{D}} \vert \boldsymbol{\theta}) P(\boldsymbol{\theta)}}{P(\boldsymbol{\mathcal{D}})}
       \end{split}
@@
 
-Since the denominator sums to $1$, one could get rid of the denominator and constants for the \index{Dirichlet probability distribution}Dirichlet prior, by expressing the posterior as proportional to the likelihood times the prior as is shown in Equation~\eqref{eq:probability:conjugate_priors:mult_likelihood:posterior_propto} below.
+Since the denominator sums to $1$, the denominator and constants for the \index{Dirichlet probability distribution}Dirichlet prior can be removed by expressing the posterior as proportional to the likelihood times the prior as follows:
 
@@
       \begin{split}
-            P(\theta \vert \mathcal{D}) &\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}} \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} - 1}\\
+            P(\boldsymbol{\theta} \vert \boldsymbol{\mathcal{D}}) &\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}} \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} - 1}\\
             &\propto \prod_{k=1}^{K} \theta_{k}^{(N_{k} + \alpha_{k}) - 1} \\
-            &\propto Dir(K, N + \alpha)
+            &\propto Dir(K, \boldsymbol{N} + \boldsymbol{\alpha})
       \end{split}
@@
 
-The posterior distribution has the same form $\mathcal{A}(v)$ as the prior, but with updated prior parameters $\alpha' = N + \alpha$.
+The posterior distribution has the same form, $\mathcal{A}(v)$, as the prior, but with updated prior parameters $\boldsymbol{\alpha'} = \boldsymbol{N} + \boldsymbol{\alpha}$.
 This shows that the \index{Dirichlet probability distribution}Dirichlet probability distribution is the conjugate prior used with the Categorical/Multinomial likelihood.
-
-The next section aims to provide the reader with the concept of Bayesian statistics and it is shown how Bayesian inference and Bayesian analysis can be used to to train a \acs{HH}.
 
@@
 Naturally, Bayesian statistics is based on \index{Bayes' theorem}Bayes' theorem as was presented in Section \ref{sec:probability:bayes_theorem}.
-Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event, and the conditions under which the event happens~\cite{ref:hackenberger:2019}.
-To introduce the concept of Bayesian inference and analysis, one first need to understand the difference between these two approaches.
+Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event and the conditions under which the event happened~\cite{ref:hackenberger:2019}.
+To introduce the concept of Bayesian inference and Bayesian analysis, a proposal is made to first understand the difference between these two approaches.
 Bayesian statistics out-date the frequentist approach, but lacked interest in the early days, partly because of the limited applications where the conjugate priors where known~\cite{ref:hackenberger:2019}.
 More recent advancements in mathematical methods popularised the Bayesian approach again.
-A notable contribution to this switch, was the development of \acf{MCMC} in the 1950's.
+A notable contribution to this switch was the development of the \acf{MCMC} algorithm in the 1950s.
 This family of algorithms allowed for the construction of random sampling algorithms from a probability distribution, which allows for the calculation of Bayesian hierarchical models~\cite{ref:hackenberger:2019}.
@@
 
-The difference between the frequentist approach and the Bayesian approach can be illustrated using an example.~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} suggests an experiment that investigates whether the sex ration in some hypothetical mice population is $1:1$.
-Two experiments can be designed.
+The difference between the frequentist approach and the Bayesian approach can be illustrated using an example.~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} suggests an experiment that investigates whether the gender ratio in some hypothetical mice population is $1:1$.
+Two experiments were designed.
 In the first experiment, mice are randomly selected until the first male is chosen.
-The result in this experiment will then be the total number of mice chosen by sex.
+The result in this experiment will then be the total number of mice chosen by gender.
 For the second experiment, exactly seven mice are randomly selected.
@@
 If the experimental design is not known ahead of time, the result is useless.
-Consider the $P$-value for each of these experiments.
-The P-value is the probability of obtaining results at least as extreme as the observed results of a statistical hypothesis test~\cite{ref:beers:2022}.
-For the first experiment, the $P$-value is $0.031$ and for the second experiment, the $P$-value is $0.227$.
-Using a confidence level of $\alpha = 0.05$, one would conclude opposite outcomes for these two experiments, when it comes to rejecting the null hypothesis, despite using the same data.
-The reason for the difference in outcomes, is due to the difference in their null distributions.
-The first approach uses a geometrical approach, and the second used a binomial approach as is illustrated on Figure \ref{fig:probability:bayesian_statistics:mouse_experiment_outcome} below.
+Consider the $p$-value for each of these experiments.
+The $p$-value is the probability of obtaining results at least as extreme as the observed results of a statistical hypothesis test~\cite{ref:beers:2022}.
+For the first experiment, the $p$-value is $0.031$ and for the second experiment, the $p$-value is $0.227$.
+Using a confidence level of $\alpha = 0.05$, opposite outcomes could be concluded for these two experiments when it comes to rejecting the null hypothesis, despite using the same data.
+The reason for the difference in outcomes, is due to the difference in their null distributions, which represent the probability distribution of the test statistic when the null hypothesis is true.
+The first approach uses a geometrical approach, and the second used a binomial approach as illustrated in Figure \ref{fig:probability:bayesian_statistics:mouse_experiment_outcome}.
 
-\begin{figure}[htbp]
+\begin{figure}[htb]
       \centering
@@
 In Bayesian statistics it is common to use a \index{Beta probability distribution}Beta probability distribution as a prior distribution.
-If the prior distribution is sampled from $Beta(3,3)$ then using Bayesian analysis, the posterior distribution, according to the outcomes of this experiment, would yield $Beta(9,4)$.
+If the prior distribution is sampled from $Beta(3,3)$, then using Bayesian analysis, the posterior distribution, according to the outcomes of this experiment, would yield $Beta(9,4)$.
 
 ~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} mentions that the $Beta$ distribution can be seen as a probability distribution of the occurrence of specific parameters.
-From the information that is now known about the $Beta$ distribution, it is possible to calculate the probability that the sex ratio in this mice population is not $1:1$, with the $Beta$ distribution as a prior, yielding a $P$-value of $0.92$.
+From the information that is now known about the $Beta$ distribution, it is possible to calculate the probability that the gender ratio in this mice population is not $1:1$, with the $Beta$ distribution as a prior, yielding a $p$-value of $0.92$.
 This means that there is a probability of $92\%$ that the mice population is not $1:1$, regardless of experiment design.

### 2022-11-27 dissertation/chapters/05-probability.tex
✨ (final-review): Chapter 5 Done

@@
 Probability theory and statistics can be traced back to as early as the 18th century.
-In 1718,~\citeauthor{ref:demoivre:1718}~\cite{ref:demoivre:1718} published the \textit{Doctrine of of Chance}; a book that is widely seen as the first published book on probability theory.
+In 1718,~\citeauthor{ref:demoivre:1718}~\cite{ref:demoivre:1718} published the \textit{Doctrine of of Chance}; a book that is widely regarded as the first published book on probability theory.
 In 1763, Thomas Bayes~\cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of \index{Bayes' theorem}Bayes' theorem was introduced.
@@
 There are many examples of how probability theory has been incorporated into \acs{ML} research.
-In 1991,~\citeauthor{ref:denker:1991},~\cite{ref:denker:1991} proposed a way to transform \acf{ANN} outputs to probability distributions.
+In 1991,~\citeauthor{ref:denker:1991}~\cite{ref:denker:1991} proposed a way to transform \acf{ANN} outputs to probability distributions.
 In 1993, \citeauthor{ref:neal:1993}~\cite{ref:neal:1993} developed a \acf{MCMC} sampling algorithm for \acfp{BNN}.
@@
 
-Chapter \ref{chap:hhs} provided the reader with the concept of a \acf{HH}.
+Chapter \ref{chap:hhs} provided the concept of a \acf{HH}.
 This dissertation aims to develop a selection \acs{HH} that makes use of probability theory to select the best \acs{HH} to solve a given problem.
-This chapter aims to provide the reader with the necessary background information on probability theory and statistics.
+This chapter aims to provide the necessary background information on probability theory and statistics.
 These are large fields and focus is put on the elements that are required to formulate the proposed \acf{BHH}.
@@
 \begin{itemize}
-      \item \textbf{Section \ref{sec:probability:overview}} gives a brief overview of what probability is and how it is used.
+      \item \textbf{Section \ref{sec:probability:overview}} provides a brief overview of what probability is and how it is used.
 
-      \item \textbf{Section \ref{sec:probability:multiple_events}} presents the concept of conditional probability.
+      \item \textbf{Section \ref{sec:probability:cond_probability}} presents the concept of conditional probability.
 
       \item \textbf{Section \ref{sec:probability:multiple_events}} presents the two laws of probability related to the intersection and union of multiple events.
-
-      \item \textbf{Section \ref{sec:probability:cond_probability}} introduces conditional probability.
 
@@
 These events are referred to as \textit{random} or \textit{stochastic} events.
-The probability that a certain event, $A$ might occur is denoted by $P(A)$.
+The probability that a certain event, $A$, might occur is denoted by $P(A)$.
 Although these random events cannot be predicted with absolute certainty, the relative frequency with which they occur over many trials, is often remarkably stable.
@@
 In statistics, the decimal probability notation is used, where $0 <= P(A) <= 1$.
-Suppose the fair coin is thrown 10 times, there is not guarantee of observing $0.5$ heads and $0.5$ tails.
+Suppose the fair coin is thrown 10 times, there is no guarantee of observing $0.5$ heads and $0.5$ tails.
 There is some probability (although small) that the coin might fall on heads $0/10$ times.
 The probability of such an event occurring is $0.0009765625$.
-In the coin flip example, the \acf{CLT} shows that the normalised sum of events tends toward a normal distribution with a mean value of $0.5$ if the number of events observed $N$, is large~\cite{ref:wackerly:2014}.
+In the coin flip example, the \acf{CLT} shows that the normalised sum of events tends toward a normal distribution with a mean value of $0.5$, if the number of events observed, $N$, is large~\cite{ref:wackerly:2014}.
 The larger the value of $N$, the higher the confidence of mean probability and relative frequency of the event.
@@
 
-The occurrence of a given random event, $A$ can often be conditional on the occurrence of another event, $B$.
+The occurrence of a given random event, $A$, can often be conditional on the occurrence of another event, $B$.
 In the field of medicine, an example of this is to calculate the probability of a certain diagnosis of a sick patient given his/her symptoms.
@@
 
-In Equation~\eqref{eq:probability:overview:conditional} above, $P(B) > 0$.
+where $P(B) > 0$.
 Note that conditional probability does not suggest causation.
@@
 
-Suppose there are two random events $A$ and $B$, then one can calculate the probability of the union and intersection of these events.
+Suppose there are two random events, $A$ and $B$, then one can calculate the probability of the union and intersection of these events.
 From the aforementioned concept, two laws of probability can be formulated.
@@
       \label{th:probability:multiple_events:multiplicative}
-      The probability of the intersection of two events $A$ and $B$ is given as
+      The probability of the intersection of two events, $A$ and $B$, is given as
 
@@
       \label{th:probability:multiple_events:additive}
-      The probability of the union of two events $A$ and $B$ is given as
+      The probability of the union of two events, $A$ and $B$, is given as
 
@@
 
-\index{Bayes Theorem}
+\index{Bayes' theorem}
 \section{Bayes' Theorem}\label{sec:probability:bayes_theorem}
@@
 
-\index{Bayes Theorem}
+\index{Bayes' theorem}
 \begin{theorem}[\textbf{Bayes' theorem}]
@@
 The \index{Dirichlet probability distribution}Dirichlet probability distribution is a family of multivariate continuous probability distributions over some $\boldsymbol{x}$ in $K$ dimensions~\cite{ref:wackerly:2014}.
-The \index{Dirichlet probability distribution}Dirichlet probability distribution is the multivariate generalization of the \index{Beta probability distribution}Beta probability distribution and is thus sometimes referred to by its alternative name, i.e.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution is a multivariate generalization of the \index{Beta probability distribution}Beta probability distribution and is thus sometimes referred to by its alternative name, i.e.
 the multivariate Beta probability distribution.
 The \index{Dirichlet probability distribution}Dirichlet probability distribution is parameterised by some vector $\boldsymbol{\alpha} = (\alpha_{1}$,  $\dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} > 0, \alpha_{k} \in \mathbb{R}$.
-The parameter, $\boldsymbol{\alpha}$, is referred to as the concentration parameter.
-The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K \geq 2$ with parameter $\boldsymbol{\alpha}$, denoted $Dir(\boldsymbol{\alpha})$, has a \acs{PDF} given as
+The parameters, $\boldsymbol{\alpha}$, are referred to as the concentration parameters.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K \geq 2$ with parameters $\boldsymbol{\alpha}$, denoted $Dir(\boldsymbol{\alpha})$, has a \acs{PDF} given as
 
@@
       \caption{The \acfp{PDF} for the \index{Dirichlet probability distribution}Dirichlet probability distribution over the 2-simplex.
-The concentration parameter $\boldsymbol{\alpha}$ is varied.
+The concentration parameters, $\boldsymbol{\alpha}$, are varied.
 The values of the \acs{PDF} are shown by the color maps with contour lines at equal values as indicated in the color bars~\cite{ref:dirichlet:2020}.}
@@
 The mean of the \index{Bernoulli probability distribution}Bernoulli probability distribution approaches $\theta$ over many samples according to the \acs{CLT}~\cite{ref:grinstead:1997}.
-Figure \ref{fig:probability:probability_distributions:bernoulli:coin} illustrates a simulation of a fair-coin flipping simulation.
+Figure \ref{fig:probability:probability_distributions:bernoulli:coin} illustrates a fair-coin flipping simulation.
 The mean converges to 0.5 for various sample sizes.
@@
       \par\bigskip
-      \caption{An illustration of the the coin flip situation for different sample sizes that show the convergence of the mean as per the \acf{CLT}.}
+      \caption{An illustration of the the coin-flip simulation for different sample sizes that show the convergence of the mean as per the \acf{CLT}.}
       \label{fig:probability:probability_distributions:bernoulli:coin}
@@
       \label{eq:probability:probability_distributions:multinomial:pmf}
-      P(\boldsymbol{x} \vert \boldsymbol{\theta}; N; K) = f_{Mul}(x; N, K, \boldsymbol{\theta}) = \frac{N!}{\prod_{k=1}^{K}x_{k}!} \prod_{k=1}^{K}\theta_{k}^{x_{k}}
+      P(\boldsymbol{x} \vert \boldsymbol{\theta}; N; K) = f_{Mul}(\boldsymbol{x}; N, K, \boldsymbol{\theta}) = \frac{N!}{\prod_{k=1}^{K}x_{k}!} \prod_{k=1}^{K}\theta_{k}^{x_{k}}
 \end{equation}
 
-Similar to the \index{Categorical probability distribution}Categorical probability distribution, the random variable $x$ can also be encoded in binary format, yielding an $N \times K$ matrix $X$ of \index{Bernoulli probability distribution}Bernoulli probability distributions.
+Similar to the \index{Categorical probability distribution}Categorical probability distribution, the random variable $x$ can also be encoded in binary format, yielding an $N \times K$ matrix $\boldsymbol{X}$ of \index{Bernoulli probability distribution}Bernoulli probability distributions.
 The support is then given as $\boldsymbol{X} \in \{0, 1\}^{N \times K}, \forall_{i=1}^{N}\sum_{k=1}^{K} x_{i,k} = 1$ so that the standard $K-1$ probability simplex $S$ still holds for each trial.
@@
 
-      \item Let $\boldsymbol{X} = (x_{1}, \dots, x_{I})$ be the outcomes of independent, identical random events, each with Boolean outcome.
+      \item Let $\boldsymbol{X} = (x_{1}, \dots, x_{I})$ be the outcomes of $I$ independent, identical random events, each with Boolean outcome.
 That is $x_{i} | \theta \overset{\text{iid}}{\sim} Ber(\theta)$ and $\mathcal{L}(x_{i} \vert \theta)$ is the Bernoulli likelihood.
 
-      \item Let $\boldsymbol{\mathcal{D}}$ denote all the prior data $\boldsymbol{X}$, parameterised by $\alpha$, $\beta$.
+      \item Let $\boldsymbol{\mathcal{D}}$ denote all the prior data of $\boldsymbol{X}$, parameterised by $\alpha$, $\beta$.
 
@@
 
-      \item Let $\boldsymbol{\mathcal{D}}$ denote all the prior data $\boldsymbol{X}$, parameterised by $\boldsymbol{\alpha}$.
+      \item Let $\boldsymbol{\mathcal{D}}$ denote all the prior data of $\boldsymbol{X}$, parameterised by $\boldsymbol{\alpha}$.
 
@@
 
-By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\mathcal{D}$ is given as
+By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\boldsymbol{\mathcal{D}}$ is given as
 
@@
 
+This section provides detailed discussions on various aspects related to Bayesian statistics and probability.
+Brief discussion follow on the frequentist and the Bayesian approach to statistics and probability.
+Finally, the concept of Bayesian analysis is presented in detail.
+
+\subsection{Frequentist vs. Bayesian Statistics}
+\label{sec:probability:bayesian_statistics:frequentist_vs_bayesian}
+
 In general, there are two main views to probability and statistics.
@@
 Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event and the conditions under which the event happened~\cite{ref:hackenberger:2019}.
-To introduce the concept of Bayesian inference and Bayesian analysis, a proposal is made to first understand the difference between these two approaches.
+To introduce the concept of Bayesian inference and Bayesian analysis, the differences between the frequentist and the Bayesian view of statistics need to be presented.
+
 Bayesian statistics out-date the frequentist approach, but lacked interest in the early days, partly because of the limited applications where the conjugate priors where known~\cite{ref:hackenberger:2019}.
@@
 
-~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} mentions that the $Beta$ distribution can be seen as a probability distribution of the occurrence of specific parameters.
-From the information that is now known about the $Beta$ distribution, it is possible to calculate the probability that the gender ratio in this mice population is not $1:1$, with the $Beta$ distribution as a prior, yielding a $p$-value of $0.92$.
-This means that there is a probability of $92\%$ that the mice population is not $1:1$, regardless of experiment design.
-An illustration of this is given in Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} below.
+~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} mentions that the $Beta$ probability distribution can be seen as a probability distribution of the occurrence of specific parameters.
+From the information that is now known about the $Beta$ probability distribution, it is possible to calculate the probability that the gender ratio in this mice population is not $1:1$, with the $Beta$ probability distribution as a prior, yielding a $p$-value of $0.92$.
+This means that there is a probability of $92\%$ that the mice population is not $1:1$, regardless of experimental design.
+An illustration of this is given in Figure \ref{fig:probability:bayesian_statistics:mouse_distributions}.
 
@@
 
-It can be seen from Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} how the posterior distribution differs from the prior distribution.
-This is the nature of Bayesian analysis and is presented in more detail in the following section.
+Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} shows how the posterior distribution differs from the prior distribution.
 
@@
 Similar to the approaches followed above to explain Bayesian statistics, a proposal is made to explain Bayesian analysis by means of an example taken from~\cite{ref:wackerly:2014}.
-Let $Y = Y_{1}, Y_{2}, \dots, Y_{N}$ denote the random variable that is observed over a sample size of $N$.
+Let $\boldsymbol{Y} = (Y_{1}, Y_{2}, \dots, Y_{N})$ denote the random variable that is observed over a sample size of $N$.
 Then the likelihood of the sample is given as $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$.
-In the discrete case the likelihood function is defined to be the joint probability $P(Y_{1} = y_{1}, Y_{2} = y_{2}, \dots, Y_{N} = y_{n})$ and the continuous case yields the joint density of $Y_{1}, Y_{2}, \dots, Y_{N}$, evaluated at $y_{1}, y_{2}, \dots, y_{n}$.
+In the discrete case, the likelihood function is defined to be the joint probability, $P(Y_{1} = y_{1}, Y_{2} = y_{2}, \dots, Y_{N} = y_{n})$, and for the continuous case, yields the joint density of $Y_{1}, Y_{2}, \dots, Y_{N}$, evaluated at $y_{1}, y_{2}, \dots, y_{n}$.
 The Bayesian view models the parameter $\theta$ as a random variable with a probability distribution, referred to as the prior distribution of $\theta$.
 The symbol $\theta$, is included in the notation of $\mathcal{L}$ as an argument to illustrate that this function is dependent, explicitly, on the value of $\theta$.
-Importantly, prior distribution is specified before any data is collected and represents the theoretical prior knowledge about $\theta$.
+Importantly, the prior distribution is specified before any data is collected and represents the theoretical prior knowledge about $\theta$.
 Assume that the parameter $\theta$ has a continuous distribution with density $g(\theta)$ that has no unknown parameters.
-Considering the likelihood of the data and the prior on $\theta$, then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood} below.
+Considering the likelihood of the data and the prior on $\theta$, then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ is given as
 
@@
 
-The marginal density or mass function of $Y_{1}, Y_{2}, \dots, Y_{N}$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:marginal_density} below.
+The marginal density or mass function of $Y_{1}, Y_{2}, \dots, Y_{N}$ is given as
 
@@
 
-Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$, according to \index{Bayes' theorem}Bayes' theorem, is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density} below.
+Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$ denoted by $g^{*}(\theta \vert y_{1}, y_{2}, \dots, y_{n})$, according to \index{Bayes' theorem}Bayes' theorem, is given as
 
@@
 
-\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} mentions that the posterior density summarises all the pertinent information about the parameter $\theta$ by making use of the information contained in the prior for $\theta$, as well as the information in the observed data/evidence.
+\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} mention that the posterior density summarises all the pertinent information about the parameter $\theta$ by making use of the information contained in the prior for $\theta$, as well as the information in the observed data/evidence.
 
 Consider now how Bayesian analysis can be used to update the priors on $\theta$ based on newly observed data.
-As with the example above, the below is taken from~\cite{ref:wackerly:2014}.
+As with the example above, the discussion below is taken from~\cite{ref:wackerly:2014}.
 Let $Y_{1}, Y_{2}, \dots, Y_{N}$ denote a random sample from a \index{Bernoulli probability distribution}Bernoulli probability distribution, where $P(Y_{i} = 1) = \theta$ and $P(Y_{i} = 0) = 1 - \theta$ and the prior distribution for $\theta$ is $Beta(\alpha, \beta)$.
 The posterior distribution for $\theta$ can be formulated as follows.
-The Bernoulli probability function can be written as is shown in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_1} below.
+The Bernoulli probability function is written as
 
@@
 
-In Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_1} above, $y_{i} = \{0,1\}$ and $0 < \theta < 1$.
-The likelihood $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$ is presented in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_2} below.
+where $y_{i} = \{0,1\}$ and $0 < \theta < 1$. The likelihood $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$ is presented as follows:
 
@@
 
-Then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ from Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood} can be formulated as in shown in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_3} below.
+Then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ from Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood} is formulated as
 
@@
 
-The marginal density of $Y_{1}, Y_{2}, \dots Y_{N}$ is then given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_4} below.
+The marginal density of $Y_{1}, Y_{2}, \dots Y_{N}$ is then given as
 
@@
 
-Finally, the posterior density of $\theta$ is given in Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:step_5} below.
+Finally, the posterior density of $\theta$, denoted by $g^{*}(\theta \vert y_{1}, y_{2}, \dots, y_{n})$, is given as
 
@@
 
-The posterior density has the same functional shape $\mathcal{A}(v)$ as the prior, yielding the update on prior parameters as $\alpha^{*} = \sum y_{i} + \alpha$ and $\beta^{*} = n - \sum y_{i} + \beta$.
+The posterior density has the same functional form, $\mathcal{A}(v)$, as the prior, yielding the update on prior parameters as $\alpha' = \sum y_{i} + \alpha$ and $\beta' = n - \sum y_{i} + \beta$.
 
@@
 
-This chapter provided the reader with all the necessary background information on probability theory and statistics.
-The origins of statistical analysis was discussed and the differences between the frequentist and Bayesian view of statistics were discussed in detail.
+This chapter provided all the necessary background information on probability theory and statistics.
+The origins of statistical analysis were discussed and the differences between the frequentist and Bayesian view of statistics were discussed in detail.
 Probability distributions and proofs of conjugate priors were provided with detailed mathematical descriptions.

### 2022-11-27 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 (final-review): Chapter 6 WIP

--- 2022-11-24 dissertation/chapters/06-bayesian-hyper-heuristic.tex
@@
 These elements form the fundamental components of the proposed \Acf{BHH}.
-This chapter provides the details around the implementation of the \Ac{BHH} and explains how it used to train \acp{FFNN}.
+This chapter provides the details around the implementation of the \Ac{BHH} and explains how it is used to train \acp{FFNN}.
 The remainder of the chapter is structured as follows:
@@
       \item \textbf{Section \ref{sec:bhh:heuristic_pool}} presents the \index{heuristic}\textit{heuristic pool}, a collection of low-level \index{heuristic}heuristics.
-Discussions follow on the importance of diversity amoungst heuristics in the \index{heuristic pool}heuristic pool.
+Discussions follow on the importance of diversity amongst heuristics in the \index{heuristic pool}heuristic pool.
 
@@
 
-The following sections presents the reader with more detail on the implementation of the \acs{BHH}.
-Discussions lead with the \acs{BHH} architecture and general \acs{HH} framework in the following section.
-
 \section{Architecture}\label{sec:bhh:architecture}
@@
 This section aims to present the reader with all the high level components in the architecture of the \Acs{BHH}.
-Burke et al.~\cite{ref:burke:2010} proposed an initial framework for \acp{HH} and Grobler~\cite{ref:grobler:2015} further proposed a framework for a heterogeneous meta-\ac{HH}.
+Burke et al.~\cite{ref:burke:2010} propose an initial framework for \acp{HH} and Grobler~\cite{ref:grobler:2015} further proposed a framework for a heterogeneous meta-\ac{HH}.
 The aforementioned frameworks are adapted for the implementation of the \Acs{BHH}.
@@
 
-With reference to Figure \ref{fig:bhh_architecture}, the components are briefly given below in the order of information flow during the \acs{FFNN} training process steps.
+With reference to Figure \ref{fig:bhh_architecture}, the components are briefly given below in the order of information flow during the \acs{FFNN} training process steps:
 
@@
 
-      \item \textbf{Heuristic-Entity Selections}: Every entity in the \index{entity pool}entity pool gets assigned a selected heuristic.
+      \item \textbf{Heuristic-Entity Selections}: Every entity in the \index{entity pool}entity pool is assigned a selected heuristic.
 
@@
 Importantly, the \acs{BHH} searches in \index{heuristic}heuristic space.
-The \index{heuristic pool}heuristic pool is defined in terms of the diversity of heuristics, as well as the amount of heuristics in the \index{heuristic pool}heuristic pool.
+The \index{heuristic pool}heuristic pool is defined in terms of the diversity of heuristics, as well as the number of heuristics in the \index{heuristic pool}heuristic pool.
 Each of these are discussed in the following sections.
@@
 
-A \index{heuristic}heuristic's eligibility for inclusion in the \index{heuristic}heuristic pool, is determined by its ability to solve to underlying problem and its search behaviour and characteristics.
-The \index{heuristic pool}heuristic pool should contain a variety of different heuristics that have different search behaviours, so that a trade-off can be made by between exploration and exploitation of solutions, as is required during the training process.
-Heuristics that explore a lot, should be selected when exploration is needed, and heuristics that exploit a lot should be selected accordingly.
+A \index{heuristic}heuristic's eligibility for inclusion in the \index{heuristic}heuristic pool is determined by its ability to solve the underlying problem and its search behaviour and characteristics.
+The \index{heuristic pool}heuristic pool should contain a variety of different heuristics that have different search behaviours, so that a trade-off can be made between exploration and exploitation of solutions, as is required during the training process.
+Heuristics that explore a lot should be selected when exploration is needed, and heuristics that exploit a lot should be selected accordingly.
 The trade-off between exploration and exploitation is managed by the high-level heuristic.
-The \acs{BHH} will learn to select and apply the appropriate heuristic, at the appropriate points, throughout the training process.
+The \acs{BHH} learns to select and apply the appropriate heuristic at the appropriate time, throughout the training process.
 In doing so, a balance is achieved between exploration and exploitation.
@@
 
-Another design decision in the heuristic pool is heuristic pool size.
+Another design decision with respect to the heuristic pool is heuristic pool size.
 Since the \acs{BHH} is a \textit{learning} \acs{HH}, every heuristic that is included in the heuristic pool increases the requirement of more statistical evidence of heuristic performance.
@@
 An example of \textit{local} state is an entity's position, while an example of \textit{global} state is the global best solution found thus far.
-The following section presents the concept of \textit{proxies} and their role in maintaining state.
 
@@
 Consider an example where the \index{heuristic pool}heuristic pool consists of just two \index{heuristic}heuristics.
-One heuristic is a gradient-based heuristic that maintains momentum such as \acs{Adam}.
-The other is a \index{meta-heuristic}meta-heuristic that does not require a gradient, such as \acs{PSO}.
+One heuristic is a gradient-based heuristic that maintains momentum, such as \acs{Adam}~\cite{ref:kingma:2014}.
+The other is a \index{meta-heuristic}meta-heuristic that does not require a gradient, such as \acs{PSO}~\cite{ref:shi:1998}.
 Both these \index{heuristic}heuristics track different parameters in their state.
 For \acs{Adam}, the expected gradient mean and variance is maintained, while the \ac{PSO} maintains record of the gbest and pbest solutions of all of entities.
-A solution to state indifference, is to proxy heuristic state update operations.
+A solution to state indifference is to proxy heuristic state update operations.
 State is then maintained in two parts:
@@
 At each heuristic-entity application step, all state parameters, per entity, are updated either by primary method or by proxied method.
-The \acs{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example} below.
+The \acs{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}.
 
@@
       \par\bigskip
-      \resizebox{0.5\textwidth}{!}{
+      \resizebox{0.38\textwidth}{!}{
             \begin{tabular}{ccccc}
@@
 
-From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when \index{heuristic}heuristic A is selected, it will outsource state update operations from \index{heuristic}heuristic B, for state parameter 2.
-Heuristic B will outsource from \index{heuristic}heuristic A, for state parameter 3.
-Finally, \index{heuristic}heuristic C will outsource from \index{heuristic}heuristic A and B, for state parameters 2 and 3 respectively.
+From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when \index{heuristic}heuristic A is selected, it will outsource state update operations from \index{heuristic}heuristic B for state parameter 2.
+Heuristic B will outsource from \index{heuristic}heuristic A for state parameter 3.
+Finally, \index{heuristic}heuristic C will outsource from \index{heuristic}heuristic A and B for state parameters 2 and 3 respectively.
 In this way, all \index{heuristic}heuristics maintain all the state parameters.
@@
 A suggestion to simplify this process is to borrow concepts from the equations of motion from physics.
-These include \textit{position}, \textit{velocity}, \textit{acceleration} and \textit{momentum}.
+These include \textit{position}, \textit{velocity}, \textit{acceleration}, and \textit{momentum}.
 Expressing \index{heuristic}heuristic update steps according to these parameters drastically simplify the process.
-However, it is possible that \index{heuristic}heuristics implement unique state parameters that do not overlap, these have to be catered for in the proxy mapping.
+However, it is possible that \index{heuristic}heuristics implement unique state parameters that do not overlap.
+These have to be catered for in the proxy mapping.
 
@@
 An example is \textit{position} and \textit{velocity}.
-Consider, for example, \index{heuristic}heuristics such as \acf{DE} and \acfp{GA}.
+Consider, for example, \index{heuristic}heuristics such as \acs{DE}~\cite{ref:price:2006} and \acp{GA}~\cite{ref:holland:1992}.
 These \index{heuristic}heuristics recombine entities.
@@
 In this particular case, a solution is to apply the recombination operation to \textit{all} applicable state parameters as well, or to nullify the necessary state parameters.
-Unfortunately there is no general, automated solution to formulate these heuristic state overlaps.
+Unfortunately, there is no general, automated solution to formulate these heuristic state overlaps.
 Each \index{heuristic}heuristic must be carefully considered.
-More details on the \index{entity pool}entity pool and entity state are presented in the following section.
 
@@
 For example, the candidate solution is represented as the entity's position, and an entity's velocity and acceleration is analogous to the gradient and momentum of the entity respectfully.
-Examples of entity state parameters, as derived from various low-level \index{heuristic}heuristics, is given as follows.
-
-\begin{itemize}
-      \item \textbf{position}: General parameter that represents the actual candidate solution and is thus a primary state parameter for all \index{heuristic}heuristics.
+Examples of entity state parameters, as derived from various low-level \index{heuristic}heuristics, is given as follows:
+
+\begin{itemize}
+      \item \textbf{position}: A general parameter that represents the actual candidate solution and is thus a primary state parameter for all \index{heuristic}heuristics.
 
@@
 
-      \item \textbf{personal best position}: Parameter that tracks that best known position by the entity thus far. As required and maintained by \index{heuristic}heuristics such as \acs{PSO}.
-
-      \item \textbf{personal best loss}: Parameter that tracks that best known loss by the entity thus far. As required and maintained by \index{heuristic}heuristics such as \acs{PSO}.
-
-      \item \textbf{loss}: Parameter that tracks the loss as achieved by the the entity throughout training.
+      \item \textbf{personal best position}: A parameter that tracks that best known position by the entity thus far, as required and maintained by \index{heuristic}heuristics such as \acs{PSO}.
+
+      \item \textbf{personal best loss}: A parameter that tracks that best known loss by the entity thus far, as required and maintained by \index{heuristic}heuristics such as \acs{PSO}.
+
+      \item \textbf{loss}: A parameter that tracks the loss as achieved by the the entity throughout training.
 \end{itemize}
@@
 The population state generally contains state parameters that are of importance to multiple \index{heuristic}heuristics, and usually tracks the state of the population and not individual \index{heuristic}heuristic.
-Some examples of population state that can arise from different \index{heuristic}heuristics is given below.
+Some examples of population state that can arise from different \index{heuristic}heuristics is given below:
 
@@
 
-      \item \textbf{rbest} and \textbf{rbest loss}: Refers to the best position and loss achieved by the population for the current replay buffer/window size.
+      \item \textbf{rbest} and \textbf{rbest loss}: Refers to the best position and loss achieved by the population for a number of steps, referred to as the replay window size.
+The replay window size defines a window of memory for tracking historical performance data of \index{heuristic}heuristics.
 
@@
 The \acs{BHH} tracks the performance of each of these combinations throughout the training process in a performance log.
-The performance log is presented in the following section.
 
@@
 The performance log is then simply a table of events and metrics.
-The \acs{BHH} tracks the following metrics in the performance log.
+The \acs{BHH} tracks the following metrics in the performance log:
 
@@
       \item \textbf{rbest loss}:  Keeps track of the \textit{replay} best loss.
-Thus, the best loss value achieved by all entity-\index{heuristic}heuristic combinations, over all mini-batch steps currently in the performance log/replay buffer.
+Thus, the best loss value achieved by all entity-\index{heuristic}heuristic combinations, over all mini-batch steps currently in the performance log/replay window.
 
@@
 
-An example of the performance log implemented by the \acs{BHH} is given in Table \ref{tab:bhh:performance_log:performance_log_example} below.
+An example of the performance log implemented by the \acs{BHH} is given in Table \ref{tab:bhh:performance_log:performance_log_example}.
 
@@
       \centering
-      \caption{An example of the performance log implemented by the \acs{BHH}, showing the first 5 entities, their allocated \index{heuristic}heuristics and their resulting performance measurements for step 1 of the training process.}
+      \caption{An example of the performance log implemented by the \acs{BHH}, showing the first five entities, their allocated \index{heuristic}heuristics and their resulting performance measurements for step 1 of the training process.}
       \label{tab:bhh:performance_log:performance_log_example}%
@@
 The performance log should be considered along with the selection of a credit assignment strategy.
-Credit assignment strategies are presented in the following section.
 
@@
 The credit assignment strategy to use is defined as a hyper-parameter.
-The \acs{BHH} implements the following credit assignment strategies to choose from.
+The \acs{BHH} implements the following credit assignment strategies to choose from:
 
@@
 The symmetric credit assignment strategy does not randomly assign credit, but rather assigns credit to all events.
-In effect, no learning and performance-bias is achieved with the symmetric credit assignment strategy and thus, the symmetric credit assignment strategy is implemented as a basis for comparison.
+In effect, no learning and performance-bias is achieved with the symmetric credit assignment strategy and thus the symmetric credit assignment strategy is implemented as a basis for comparison.
 Comparing a credit assignment staretegy to the symmetric credit assignment indicates the ability of the other credit assignment strategy to have an effect on the learning process and performance of the \acs{BHH}.
@@
 
-The implementation of a credit assignment strategy is simply a function that translates the performance log from Table \ref{tab:bhh:performance_log:performance_log_example}, into Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}.
+The implementation of a credit assignment strategy is simply a function that translates the performance log from Table \ref{tab:bhh:performance_log:performance_log_example} into Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}.
 
@@
       \centering
-      \caption{Credit assignment strategy output table showing \textit{ibest} credit assignment for the first 5 entities and their selected heuristics, for step 1 of the training process.}
+      \caption{Credit assignment strategy output table showing \textit{ibest} credit assignment for the first five entities and their selected heuristics for step 1 of the training process.}
       \label{tab:bhh:credit_assignment_strategy:credit_assignment_example}%
@@
 
-Credit is used by the selection mechanism of the \acs{BHH}. The selection mechanism is presented in the following section.
+Credit is used by the selection mechanism of the \acs{BHH}.
 
@@
 
-This section aims to provide the reader with the detail around the selection mechanism as it is implemented by the \acs{BHH}.
-It is mentioned throughout this document that the \acs{BHH} implements a predictive model based on Bayesian probabilistic concepts.
-In probabilistic modeling it is necessary to identify all the random events that can occur.
+This section provides the detail around the selection mechanism as it is implemented by the \acs{BHH}.
+Detail is provided around random events as observed by the \acs{BHH}.
+An argument for independence between random events is made.
+\index{Bayes' theorem}Bayes' theorem is briefly reviewed in the context of the \acs{BHH} implementation.
+It is shown how the \acs{BHH} implements a probabilistic, predictive model based on the fundamentals of the Na\"{\i}ve Bayes algorithm.
+Brief discussions follow on numerical stability and mode collapse.
 
@@
 
-Observation of random events is treated as evidence. In the context of a Bayesian approach, this evidence is used to update prior beliefs. The \acs{BHH} distinguishes between the following events.
+Observation of random events is treated as evidence. In the context of a Bayesian approach, this evidence is used to update prior beliefs. The \acs{BHH} distinguishes between the following events:
 
@@
       \item \textbf{$E$}: The event of observing \textit{entities}.
-      \item \textbf{$C$}: The event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} is met.
+      \item \textbf{$C$}: The event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} are met.
 \end{itemize}
@@
 The \acs{BHH} implements a form of Naïve Bayes classifier, where the appropriate heuristic to assign to an entity is a classification problem.
-\citeauthor{ref:domingos:1997}~\cite{ref:domingos:1997} mentions that although Bayesian classifiers’ probability estimates are only optimal under quadratic loss if the independence assumption holds, the classifier itself can still be optimal under zero-one loss (misclassification rate), even when this assumption is violated by a wide margin.
+\citeauthor{ref:domingos:1997}~\cite{ref:domingos:1997} mention that although the probability estimates of Bayesian classifiers are only optimal under quadratic loss if the independence assumption holds, the classifier itself can still be optimal under zero-one loss (misclassification rate), even when this assumption is violated by a wide margin.
 This means that independence can be assumed when the probabilistic model is used as a classifier.
 
-\index{Bayes' Theorem}
+\index{Bayes' theorem}
 \subsection{Bayes' Theorem}\label{sec:bhh:selection_mechanism:bayes_theorem}
 
-Chapter \ref{chap:probability} presented \index{Bayes' Theorem}Bayes' Theorem, but for convenience, it is given again in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} below.
+Chapter \ref{chap:probability} presented \index{Bayes' theorem}Bayes' theorem, but for convenience, it is given below:
 
@@
 Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} can thus be evaluated for proportionality.
-The resulting proportionality is expressed in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem_prop_to} below.
+The resulting proportionality is expressed as
 
@@
 
-The conditionality implemented by \index{Bayes' Theorem}Bayes' Theorem can be extended to include multiple criteria.
-\index{Bayes' Theorem}Bayes' Theorem is used by the selection mechanism of the \acs{BHH}.
-The predictive model that is used by the selection mechanism of the \acs{BHH} is presented in the following section.
+The conditionality implemented by \index{Bayes' theorem}Bayes' theorem can be extended to include multiple criteria.
+\index{Bayes' theorem}Bayes' theorem is used by the selection mechanism of the \acs{BHH}.
 
@@
 This section presents the predictive model as implemented by the selection mechanism of the \acs{BHH}.
-The predictive model is arguably the most important component of the \acs{BHH}, as it drives the heuristic selection process.
+The predictive model is arguably the most important component of the \acs{BHH}, because it drives the heuristic selection process.
 The \acs{BHH} implements a predictive model that predicts which heuristic to select, given the conditionality that a particular entity is used and a particular credit assignment criteria is met.
@@
 \begin{itemize}
-      \item $I$: Denote the maximum number of instances in the replay window.
-      \item $J$: Denote the \index{entity pool}entity pool (population) size.
-      \item $K$: Denote the \index{heuristic pool}heuristic pool size.
-      \item $L$: Denote the number of credit assignment output classes. Since the output of credit assignment is boolean, $L = 2$.
-
-      \item $\alpha = (\alpha_{1}, \dots, \alpha_{K})$: Denote the concentration parameters for the heuristic probability distribution.
-      \item $\beta = (\beta_{1}, \dots, \beta_{K})^{J}$: Denote the concentration parameters for the entity-heuristic probability distributions.
-      \item $\gamma = (\gamma_{1}, \dots, \gamma_{K})^{L}$: Denote the concentration parameters for the credit-heuristic probability distribution.
-
-      \item $\theta \vert \alpha \sim Dir(\alpha; K)$: Denote the heuristic probability distribution, implementing a \index{Dirichlet probability distribution}Dirichlet probability distribution parameterised by $\alpha$ and $K$.
+      \item $I$ denote the maximum number of instances in the replay window.
+      \item $J$ denote the \index{entity pool}entity pool (population) size.
+      \item $K$ denote the \index{heuristic pool}heuristic pool size.
+      \item $L$ denote the number of credit assignment output classes. Since the output of credit assignment is boolean, $L = 2$.
+
+      \item $\boldsymbol{\alpha} = (\alpha_{1}, \dots, \alpha_{K})$ denote the concentration parameters for the heuristic probability distribution.
+      \item $\boldsymbol{\beta} = (\beta_{1}, \dots, \beta_{K})^{J}$ denote the concentration parameters for the entity-heuristic probability distributions.
+      \item $\boldsymbol{\gamma} = (\gamma_{1}, \dots, \gamma_{K})^{L}$ denote the concentration parameters for the credit-heuristic probability distribution.
+
+      \item $\boldsymbol{\theta} \vert \boldsymbol{\alpha} \sim Dir(\boldsymbol{\alpha}; K)$ denote the heuristic probability distribution, implementing a \index{Dirichlet probability distribution}Dirichlet probability distribution parameterised by $\boldsymbol{\alpha}$ and $K$.
 Heuristic selection probabilities are sampled from this distribution.
 
-      \item $\phi \vert \beta \sim Dir(\beta; K)^{J}$: Denote the entity-heuristic probability distribution, implementing a \index{Dirichlet probability distribution}Dirichlet probability distribution parameterised by $\beta$ and $K$ for each entity in the \index{entity pool}entity pool with population size $J$.
+      \item $\boldsymbol{\phi} \vert \boldsymbol{\beta} \sim Dir(\boldsymbol{\beta}; K)^{J}$ denote the entity-heuristic probability distribution, implementing a \index{Dirichlet probability distribution}Dirichlet probability distribution parameterised by $\boldsymbol{\beta}$ and $K$ for each entity in the \index{entity pool}entity pool with population size $J$.
 Entity-heuristic probabilities are sampled from this distribution.
 
-      \item $\psi \vert \gamma_{1}, \gamma_{0}  \sim Beta(\gamma_{1}, \gamma_{0})$: Denote the credit-heuristic probability distribution, implementing a Beta probability distribution parameterised by $\gamma_{1}$ and $\gamma_{0}$.
+      \item $\boldsymbol{\psi} \vert \gamma_{1}, \gamma_{0}  \sim Beta(\gamma_{1}, \gamma_{0})$ denote the credit-heuristic probability distribution, implementing a Beta probability distribution parameterised by $\gamma_{1}$ and $\gamma_{0}$.
 Credit-heuristic probabilities are sampled from this distribution.
 
-      \item $H \vert \theta \sim Mult(\theta; I, K)$: Denote the distribution of heuristics (event $H$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled heuristic selection probability $\theta$, the \index{heuristic pool}heuristic pool size $K$ and maximum number of instances $I$.
-
-      \item $E \vert \phi \sim Mult(\phi; I, K)^{J}$: Denote the distribution of entity-heuristic combinations (event $E$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled entity-heuristic selection probability $\phi$, the \index{heuristic pool}heuristic pool size $K$ and maximum number of instances $I$, for each entity in $J$.
-
-      \item $C \vert \psi \sim Bin(\psi, I)$: Denote the distribution of credit-heuristic combinations (event $C$), implementing a \index{Binomial probability distribution}Binomial probability distribution, parameterised by the sampled credit-heuristic selection probability $\psi$ and the maximum number of instances $I$.
-\end{itemize}
-
-Vector notation is dropped for sake of convenience, simplicity and readability.
-The parameterised predictive model, as derived from \index{Bayes' Theorem}Bayes' theorem, is then given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model} below.
-
+      \item $\boldsymbol{H} \vert \boldsymbol{\theta} \sim Mult(\boldsymbol{\theta}; I, K)$ denote the distribution of heuristics (events $\boldsymbol{H}$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled heuristic selection probabilities $\boldsymbol{\theta}$, the \index{heuristic pool}heuristic pool size $K$, and maximum number of instances $I$.
+
+      \item $\boldsymbol{E} \vert \boldsymbol{\phi} \sim Mult(\boldsymbol{\phi}; I, K)^{J}$ denote the distribution of entity-heuristic combinations (events $\boldsymbol{E}$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled entity-heuristic selection probabilities $\boldsymbol{\phi}$, the \index{heuristic pool}heuristic pool size $K$, and maximum number of instances $I$ for each entity in $J$.
+
+      \item $\boldsymbol{C} \vert \boldsymbol{\psi} \sim Bin(\boldsymbol{\psi}, I)$ denote the distribution of credit-heuristic combinations (events $\boldsymbol{C}$), implementing a \index{Binomial probability distribution}Binomial probability distribution, parameterised by the sampled credit-heuristic selection probabilities $\boldsymbol{\psi}$ and the maximum number of instances $I$.
+\end{itemize}
+
+The parameterised predictive model, as derived from \index{Bayes' theorem}Bayes' theorem, is then given as
+
+\footnotesize
 \begin{equation}
@@
       \begin{split}
-            P(H \vert E, C;  \theta, \phi, \psi)
+            P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C};  \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})
             &= \frac{
-                  P(E, C \vert H;  \phi, \psi)  P(H \vert \theta)
+                  P(\boldsymbol{E}, \boldsymbol{C} \vert \boldsymbol{H};  \boldsymbol{\phi}, \boldsymbol{\psi})  P(\boldsymbol{H} \vert \boldsymbol{\theta})
             }{
-                  P(E, C \vert \theta, \phi, \psi)
+                  P(\boldsymbol{E}, \boldsymbol{C} \vert \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})
             } \\
             &= \frac{
-                  P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
+                  P(\boldsymbol{E} \vert \boldsymbol{H};  \boldsymbol{\phi})  P(\boldsymbol{C} \vert \boldsymbol{H};  \boldsymbol{\psi}) P(\boldsymbol{H} \vert \boldsymbol{\theta})
             }{
-                  P(E \vert \theta, \psi) P(C \vert \theta, \phi)
+                  P(\boldsymbol{E} \vert \boldsymbol{\theta}, \boldsymbol{\psi}) P(\boldsymbol{C} \vert \boldsymbol{\theta}, \boldsymbol{\phi})
             } \\
             &= \frac{
-                  P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
+                  P(\boldsymbol{E} \vert \boldsymbol{H};  \boldsymbol{\phi})  P(\boldsymbol{C} \vert \boldsymbol{H};  \boldsymbol{\psi}) P(\boldsymbol{H} \vert \boldsymbol{\theta})
             }{
-                  \left[ \sum_{k}^{K} P(E, H=k \vert \theta, \phi) \right] \left[ \sum_{k}^{K}  P(C, H=k \vert \theta, \psi) \right]
+                  \left[ \sum_{k}^{K} P(\boldsymbol{E}, \boldsymbol{H}=k \vert \boldsymbol{\theta}, \boldsymbol{\phi}) \right] \left[ \sum_{k}^{K}  P(\boldsymbol{C}, \boldsymbol{H}=k \vert \boldsymbol{\theta}, \boldsymbol{\psi}) \right]
             } \\
             &= \frac{
-                  P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
+                  P(\boldsymbol{E} \vert \boldsymbol{H};  \boldsymbol{\phi})  P(\boldsymbol{C} \vert \boldsymbol{H};  \boldsymbol{\psi}) P(\boldsymbol{H} \vert \boldsymbol{\theta})
             }{
-                  \left[ \sum_{k}^{K} P(E \vert H=k, \phi) P(H=k \vert \theta) \right] \left[ \sum_{k}^{K} P(C \vert H=k, \psi) P(H=k \vert \theta) \right]
+                  \left[ \sum_{k}^{K} P(\boldsymbol{E} \vert \boldsymbol{H}=k, \boldsymbol{\phi}) P(\boldsymbol{H}=k \vert \boldsymbol{\theta}) \right] \left[ \sum_{k}^{K} P(\boldsymbol{C} \vert \boldsymbol{H}=k, \boldsymbol{\psi}) P(\boldsymbol{H}=k \vert \boldsymbol{\theta}) \right]
             }
@@
 \end{equation}
-
-Notice the joint probability over events $E$ and $C$, given the selection of a heuristic $H$, denoted by the product of the sums of the separate parts for $E$ and $C$, in the denominator.
+\normalsize
+
+Notice the joint probability over events $\boldsymbol{E}$ and $\boldsymbol{C}$, given the selection of a heuristic $\boldsymbol{H}$, denoted by the product of the sums of the separate parts for $\boldsymbol{E}$ and $\boldsymbol{C}$, in the denominator.
 The calculation in the denominator can be intractable.
-Since the \acs{BHH} selection mechanism uses the predictive model as a classifier, the posterior distribution as given in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem}, can be evaluated for proportionality, as is given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} below.
+Since the \acs{BHH} selection mechanism uses the predictive model as a classifier, the posterior distribution as given in Equation~\eqref{eq:bhh:selection_mechanism:bayes_theorem} can be evaluated for proportionality as follows:
 
@@
       \begin{split}
-            P(H \vert E, C;  \theta, \phi, \psi) &\propto P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)
-      \end{split}
-\end{equation}
-
-The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $H$, given allocation to entity $E$ and credit $C$, parameterised by sampled $\theta$, $\phi$ and $\psi$.
-These parameters are in turn parameterised by concentrations $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$, which denote the prior beliefs of the \acs{BHH}.
+            P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C};  \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi}) &\propto P(\boldsymbol{E} \vert \boldsymbol{H};  \boldsymbol{\phi})  P(\boldsymbol{C} \vert \boldsymbol{H};  \boldsymbol{\psi}) P(\boldsymbol{H} \vert \boldsymbol{\theta})
+      \end{split}
+\end{equation}
+
+The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $\boldsymbol{H}$, given allocation to entity $\boldsymbol{E}$ and credit $\boldsymbol{C}$, parameterised by sampled $\boldsymbol{\theta}$, $\boldsymbol{\phi}$ and $\boldsymbol{\psi}$.
+These parameters are in turn parameterised by concentrations $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$, which denote the prior beliefs of the \acs{BHH}.
 
@@
 This section aims to dissect the probabilistic model that is presented in Equestion~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
-The \acs{BHH} implements a form of Naïve Bayes classifier and thus, independence between events can be assumed.
+The \acs{BHH} implements a form of Naïve Bayes classifier, and thus independence between events can be assumed.
 The following derived \acp{PMF} are provided as fundamental building blocks to show the mechanism by which the \acs{BHH} learns.
 
-The independence between events for class label $H$, simply yields the \ac{PMF} of the \index{Multinomial probability distribution}Multinomial distribution as presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf} below.
+The independence between events for class label $\boldsymbol{H}$, simply yields the \ac{PMF} of the \index{Multinomial probability distribution}Multinomial distribution as presented below:
 
@@
       \begin{split}
-            P(H \vert \theta)
+            P(\boldsymbol{H} \vert \boldsymbol{\theta})
             &\propto \prod_{i=1}^{I} \prod_{k=1}^{K} P(h_{i,k} \vert \theta_{k}) \\
@@
 
-In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf} above, $N_{k}$ is a summary variable such that $N_{k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the event $h_{i}$ taking on class $k$ in $I$ independent, identical runs.
-
-The independence between events $E$, given class label $H$, is denoted by the likelihood of $E$,
-conditional to the occurrence of heuristic $k$ and model parameter $\phi$ as is given in in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} below.
+where $N_{k}$ is a summary variable such that $N_{k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the event $h_{i}$ taking on class $k$ in $I$ independent, identical runs.
+
+The independence between events $\boldsymbol{E}$, given class label $\boldsymbol{H}$, is denoted by the likelihood of $\boldsymbol{E}$, conditional to the occurrence of heuristic $k$ and model parameter $\boldsymbol{\phi}$ as follows:
 
@@
       \begin{split}
-            P(E \vert H;  \phi)
+            P(\boldsymbol{E} \vert \boldsymbol{H};  \boldsymbol{\phi})
             &\propto \prod_{i=1}^{I} \prod_{j=1}^{J} \prod_{k=1}^{K} P(e_{i,j,k} \vert h_{i,k} ; \phi_{j,k})  \\
@@
 
-In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} above, $N_{j,k}$ is a summary variable such that $N_{j,k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on class $k$, i.e.
-the count of occurrences of both entity $e$ and heuristic $k$ occurring together in $I$ independent, identical runs.
-
-Finally, the independence between events for the performance criteria $C$, given class label $H$, is denoted by the likelihood of $C$, conditional to the occurrence of heuristic $k$ and model parameter $\psi$ as given in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} below.
+where $N_{j,k}$ is a summary variable such that $N_{j,k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on class $k$, i.e.
+the count of occurrences of both entity $j$ and heuristic $k$ occurring together in $I$ independent, identical runs.
+
+Finally, the independence between events for the performance criteria $\boldsymbol{C}$, given class label $\boldsymbol{H}$, is denoted by the likelihood of $\boldsymbol{C}$, conditional to the occurrence of heuristic $k$ and model parameter $\boldsymbol{\psi}$ as given below:
 
@@
       \begin{split}
-            P(C\vert H;  \psi)
+            P(\boldsymbol{C} \vert \boldsymbol{H}; \boldsymbol{\psi})
             &\propto\prod_{i=1}^{I} \prod_{k=1}^{K} P(c_{i,k} \vert h_{i,k} ; \psi_{k})  \\
@@
 
-In Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} above, $N_{k}$ is the same summary variable as described for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}.
-$N_{1,k}$ is a summary variable such that $N_{1,k} = \sum_{i=1}^{I} \mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $c_{i}$ taking on a success $(c_{i}=1)$ and $h_{i}$ taking on class $k$, i.e.
+where $N_{k}$ is the same summary variable as described for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}.
+$N_{1,k}$ is a summary variable such that $N_{1,k} = \sum_{i=1}^{I} \mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $c_{i}$ taking on a success (i.e.
+$c_{i}=1$) and $h_{i}$ taking on class $k$, i.e.
 the count of occurrences of both succeeding in the performance criteria and heuristic $k$ occurring together in $I$ independent, identical runs.
-Similarly $N_{0,k} = N_{k} - N_{1,k}$ would denote the count of occurrences of the events $c_{i}$ taking on a failure $(c_{i}=0)$ and $h_{i}$
-taking on class $k$.
-
-Equations~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}, \eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} and \eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} can be supplemented into the proportional evaluation of the predictive model as given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} and is given in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} below.
+Similarly, $N_{0,k} = N_{k} - N_{1,k}$ denotes the count of occurrences of the events $c_{i}$ taking on a failure (i.e.
+$c_{i}=0$) and $h_{i}$ taking on class $k$.
+
+Equations~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}, \eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} and \eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} can be substituded into the proportional evaluation of the predictive model as given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}, resulting in
 
@@
       \begin{split}
-            P(H \vert E, C;  \theta, \phi, \psi)
-            &\propto P(E \vert H;  \phi)  P(C \vert H;  \psi) P(H \vert \theta)  \\
+            P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C};  \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})
+            &\propto P(\boldsymbol{E} \vert \boldsymbol{H};  \boldsymbol{\phi})  P(\boldsymbol{C} \vert \boldsymbol{H}; \boldsymbol{\psi}) P(\boldsymbol{H} \vert \boldsymbol{\theta})  \\
             &\propto \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right]
@@
 
-Consider the practical implementation of the predictive model as shown in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} above.
-Computationally the equation presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} will underflow on a real computer if the resulting probabilities are very small.
-Discussions follow on numerical stability as it relates to practical implementation.
+Consider the practical implementation of the predictive model as shown in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf}.
+Computationally, the equation presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} will underflow on a real computer if the resulting probabilities are very small.
 
@@
 
-When evaluating for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf}, the numerical stability is shown to underflow if the resulting probabilities from its parts are very small.
-Multiplying multiple fractional parameters leads to an even smaller fractional number.
+When Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} is evaluated, the numerical stability is shown to underflow if the resulting probabilities from its parts are very small.
+Multiplication of multiple fractional parameters leads to an even smaller fractional number.
 Probabilities might be very low at some points during training.
@@
 A solution to the aforementioned problem is to apply the \textit{log-sum-exp} trick.
-The transformation of Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} using the log-sum-exp trick is given below in Equation~\eqref{eq:bhh:selection_mechanism:numerical_stability:log_sum_exp}.
+The transformation of Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} using the log-sum-exp trick is given as
 
@@
 
-The log-sum-exp trick as shown above caters for very small probabilities, however, there might be a situation where  a random event is never seen, purely by chance.
-This results in a scenario referred to as \textit{mode collapse} and is discussed next.
+The log-sum-exp trick as shown above caters for very small probabilities.
+However, there might be a situation where a random event is never seen, purely by chance.
+This results in a scenario referred to as \textit{mode collapse}.
 
@@
 
-Mode collapse is the situation that occurs where the selective pressure towards a heuristic is close to zero as a result of random sampling, low initial bias or bad performance.
+Mode collapse is the situation that occurs where the selective pressure towards a heuristic is close to zero as a result of random sampling, low initial bias, or bad performance.
 This leads to a situation where the probabilistic model continually decreases the selective pressure, until the selection probability of that heuristic is 0, yielding no further observations of that particular random event.
-The \acs{BHH} addresses the aforementioned issue by:
-
-\begin{itemize}
-      \item Using \textit{symmetric} initialisation of the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$.
-
-      \item Setting the lower-bound of the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$ to 1, so that a selection probability of 0 is highly improbable.
-
-      \item Continuously resampling heuristics throughout the training process, before and after optimisation, eliminating mode collapse as a result of just random sampling.
+The \acs{BHH} addresses the aforementioned issue by
+
+\begin{itemize}
+      \item using \textit{symmetric} initialisation of the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$;
+
+      \item setting the lower-bound of the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$ to 1, so that a selection probability of 0 is highly improbable; and
+
+      \item continuously resampling heuristics throughout the training process, before and after optimisation, eliminating mode collapse as a result of just random sampling.
 \end{itemize}
@@
 Another suggestion is to ensure that at least one of every heuristic is always selected during training.
-The \acs{BHH} does not incorporate this approach as this could result in a situation where a bad choice of heuristic is continually used throughout the training process, possibly resulting in bad update steps/selections.
+The \acs{BHH} does not incorporate this approach, because this could result in a situation where a bad choice of heuristic is continually used throughout the training process, possibly resulting in bad update steps/selections.
 Instead, the \acs{BHH} relies on the underlying learning process to control the selective pressure according to performance and nothing else.
@@
 
-Thus far all the fundamental components of the \acs{BHH} has been presented.
+Thus far all the fundamental components of the \acs{BHH} have been presented.
 The final step that is missing is to present the optimisation step by which the learning process takes place.
-This section aims to provide a solid mathematical explanation to show exactly how the \acs{BHH} is able to learn.
-
-The intent of the \acs{BHH} is to gather evidence that can be use to update prior beliefs about which heuristics perform well during training.
-These beliefs are represented by the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$.
+This section provides a solid mathematical explanation to show exactly how the \acs{BHH} is able to learn.
+This section provides a brief overview of the role of concentration parameters and pseudo counts.
+Detailed discussions and mathematical descriptions follow for two techniques, known as \acs{MLE} and \acs{MAP}, that are used to train Na\"{\i}ve Bayes classifiers.
+
+\subsection{Concentration Parameters and Pseudo Counts}\label{sec:bhh:optimisation_step:concentration_pseudo_counts}
+
+The intent of the \acs{BHH} is to gather evidence that can be used to update prior beliefs about which heuristics perform well during training.
+These beliefs are represented by the concentration parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$.
 A change in prior beliefs is represented by a change in these concentration parameters.
-Specifically, it can be said, that the optimisation process implemented by the \acs{BHH}, updates \textit{pseudo counts} of events that are observed in the performance logs.
-These pseudo counts track the occurrence of a heuristic, an entity and resulting performance of these two elements.
+Specifically, it can be said that the optimisation process implemented by the \acs{BHH} updates \textit{pseudo counts} of events that are observed in the performance logs.
+These pseudo counts track the occurrence of a heuristic, an entity, and resulting performance of these two elements.
 Through the credit assignment strategy, these pseudo counts are biased towards entity-heuristic combinations that meet performance requirements and yield credit allocations.
@@
 In probability theory and statistics, \acf{MLE} is a method that estimates the parameters of a prior probability distribution given newly observed data and evidence.
-This section shows that the values for $\theta$, $\phi$ and $\psi$ can be estimated by \ac{MLE} and is given in Equations \eqref{eq:bhh:optimisation_step:mle:theta}, \eqref{eq:bhh:optimisation_step:mle:phi} and \eqref{eq:bhh:optimisation_step:mle:psi} below.
+This section shows that the values for $\boldsymbol{\theta}$, $\boldsymbol{\phi}$ and $\boldsymbol{\psi}$ can be estimated by \acs{MLE} as follows:
 
@@
 The derivations of the \acs{MLE} for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and
-$\hat{\psi}_{k}$ are presented as follows.
-The log likelihood of $\hat{\theta}$, $\hat{\phi}$ and $\hat{\psi}$ as derived from the Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} is given in Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} below.
+$\hat{\psi}_{k}$ are presented as follows: The log likelihood of $\boldsymbol{\hat{\theta}}$, $\boldsymbol{\hat{\phi}}$ and $\boldsymbol{\hat{\psi}}$ as derived from the Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to} is given as
 
@@
       \begin{split}
-            & \mathcal{L}(\theta, \phi, \psi) \\
+            & \mathcal{L}(\boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi}) \\
             &= \ln\left(\left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right] \right) \\
@@
 
-Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} can be broken down into each of its components.
-Consider the log likelihood of $\psi$ as denoted by Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_psi} below.
+Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_all} is broken down into each of its components. Consider the log likelihood of $\boldsymbol{\psi}$ as denoted by
 
@@
       \begin{split}
-            \mathcal{L}(\psi) &=  \sum_{k=1}^{K} N_{1,k} \ln \left( \psi_{k} \right) + \left( N_{k} - N_{1,k} \right) \ln \left( 1 - \psi_{k} \right)
-      \end{split}
-\end{equation}
-
-The \acs{MLE} for $\hat{\psi_{k}} $ can be calculated by taking the partial derivative of Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_psi} with respect to $\psi_{k}$ and equating to zero as presented in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_psi} as follows.
+            \mathcal{L}(\boldsymbol{\psi}) &=  \sum_{k=1}^{K} N_{1,k} \ln \left( \psi_{k} \right) + \left( N_{k} - N_{1,k} \right) \ln \left( 1 - \psi_{k} \right)
+      \end{split}
+\end{equation}
+
+The \acs{MLE} for $\hat{\psi_{k}} $ is calculated by taking the partial derivative of Equation~\eqref{eq:bhh:optimisation_step:mle:log_likelihood_psi} with respect to $\psi_{k}$ and equating to zero as follows:
 
@@
       \begin{split}
-            \frac{\partial \mathcal{L}(\psi)}{\partial \psi_{k}} &= N_{1,k} \frac{1}{ \psi_{k}} + \left( N_{k} - N_{1,k} \right) \frac{-1}{ \left( 1 - \psi_{k} \right) } \\
-            0 &=  \frac{ N_{1,k} \left( 1 - \psi_{k} \right) +  \left( N_{1,k} - N_{k} \right) \psi_{k}}{ \psi_{k} \left( 1 - \psi_{k} \right) } \\
-            0 &=  N_{1,k} \left( 1 - \psi_{k} \right) +  \left( N_{1,k} - N_{k} \right) \psi_{k} \\
-            0 &=  N_{1,k} - N_{1,k} \psi_{k}  +  N_{1,k} \psi_{k} - N_{k}\psi_{k} \\
-            0 &=  N_{1,k} - N_{k}\psi_{k} \\
-            N_{k}\psi_{k} &=  N_{1,k} \\
-            \hat{\psi}_{k} &=  \frac{N_{1,k}}{N_{k}} \\
+            \frac{\partial \mathcal{L}(\boldsymbol{\psi})}{\partial \psi_{k}} &= N_{1,k} \frac{1}{ \psi_{k}} + \left( N_{k} - N_{1,k} \right) \frac{-1}{ \left( 1 - \psi_{k} \right) } \\
+            \therefore 0 &=  \frac{ N_{1,k} \left( 1 - \psi_{k} \right) +  \left( N_{1,k} - N_{k} \right) \psi_{k}}{ \psi_{k} \left( 1 - \psi_{k} \right) } \\
+            \therefore 0 &=  N_{1,k} \left( 1 - \psi_{k} \right) +  \left( N_{1,k} - N_{k} \right) \psi_{k} \\
+            \therefore 0 &=  N_{1,k} - N_{1,k} \psi_{k}  +  N_{1,k} \psi_{k} - N_{k}\psi_{k} \\
+            \therefore 0 &=  N_{1,k} - N_{k}\psi_{k} \\
+            \therefore N_{k}\psi_{k} &=  N_{1,k} \\
+            \therefore \hat{\psi}_{k} &=  \frac{N_{1,k}}{N_{k}} \\
       \end{split}
@@
 The \acs{MLE} for $\hat{\theta_{k}} $ can be calculated similarly.
-However, one has to compensate for the $K-1$ simplex $S$ by adding error factor $\epsilon$, to correct values for $\theta$, where $\sum_{k}^{K} \theta_{k} \neq 1$.
-The new log likelihood function is then given in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_1} below.
+However, the $K-1$ simplex $S$ has to be compensated for by adding error factor, $\epsilon$, to correct values for $\boldsymbol{\theta}$, where $\sum_{k}^{K} \theta_{k} \neq 1$.
+The new log likelihood function is then given as
 
@@
       \begin{split}
-            \mathcal{L}(\theta, \epsilon)
+            \mathcal{L}(\boldsymbol{\theta}, \epsilon)
             &=  \left( \sum_{k=1}^{K} N_{k} \ln \left( \theta_{k} \right) \right) + \epsilon \left( 1 - \sum_{k=1}^{K} \theta_{k} \right) \\
@@
 
-Solving first for $\epsilon$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_2} below.
+Solving first for $\epsilon$ yields
 
@@
       \begin{split}
-            \frac{\partial \mathcal{L}(\theta, \epsilon)}{\partial \epsilon} &= 1 - \sum_{k=1}^{K} \theta_{k}  \\
-            \sum_{k=1}^{K} \theta_{k}  &= 1
-      \end{split}
-\end{equation}
-
-Then solving for $\theta_{k}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} as presented below.
+            \frac{\partial \mathcal{L}(\boldsymbol{\theta}, \epsilon)}{\partial \epsilon} &= 1 - \sum_{k=1}^{K} \theta_{k}  \\
+            \therefore \sum_{k=1}^{K} \theta_{k}  &= 1
+      \end{split}
+\end{equation}
+
+Then solving for $\theta_{k}$ yields
 
@@
       \begin{split}
-            \frac{\partial \mathcal{L}(\theta, \epsilon)}{\partial \theta_{k}} &=  N_{k} \frac{1}{\theta_{k}}  + \epsilon(-1) \\
-            \frac{N_{k}}{\theta_{k}} &= \epsilon \\
-            N_{k} &= \theta_{k} \epsilon \\
-            \sum_{k=1}^{K} N_{k} &= \sum_{k=1}^{K} \theta_{k} \epsilon \\
-            N &= \epsilon \sum_{k=1}^{K} \theta_{k} \\
-            N &= \epsilon
-      \end{split}
-\end{equation}
-
-Substituting $N = \epsilon$ back into Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_4} below.
+            \frac{\partial \mathcal{L}(\boldsymbol{\theta}, \epsilon)}{\partial \theta_{k}} &=  N_{k} \frac{1}{\theta_{k}}  + \epsilon(-1) \\
+            \therefore \frac{N_{k}}{\theta_{k}} &= \epsilon \\
+            \therefore N_{k} &= \theta_{k} \epsilon \\
+            \therefore \sum_{k=1}^{K} N_{k} &= \sum_{k=1}^{K} \theta_{k} \epsilon \\
+            \therefore N &= \epsilon \sum_{k=1}^{K} \theta_{k} \\
+            \therefore N &= \epsilon
+      \end{split}
+\end{equation}
+
+Substitution of $N = \epsilon$ back into Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_theta_part_3} yields
 
@@
 
-The \acs{MLE} for $\hat{\phi}_{j, k} $ is calculated similarly.
-To compensate for the $K-1$ simplex $S$, an error $\lambda = (\lambda_{1}, \dots, \lambda_{J})$ is added as is shown in Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_1} below.
+The \acs{MLE} for $\hat{\phi}_{j, k} $ is calculated similarly. To compensate for the $K-1$ simplex $S$, an error, $\boldsymbol{\lambda} = (\lambda_{1}, \dots, \lambda_{J})$ is added as follows:
 
@@
       \begin{split}
-            \mathcal{L}(\phi, \lambda)
+            \mathcal{L}(\boldsymbol{\phi}, \boldsymbol{\lambda})
             &=  \left( \sum_{j=1}^{J} \sum_{k=1}^{K} N_{j,k} \ ln \left( \phi_{j,k} \right) \right) + \sum_{j=1}^{J} \lambda_{j} \left( 1 - \sum_{k=1}^{K} \phi_{j,k} \right) \\
@@
 
-Solving first for $\lambda_{j}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_2} as is given below.
+Solving first for $\lambda_{j}$ yields
 
@@
       \begin{split}
-            \frac{\partial \mathcal{L}(\phi, \lambda)}{\partial \lambda_{j}} &= 1 - \sum_{k=1}^{K} \phi_{j,k}  \\
-            \sum_{k=1}^{K} \phi_{j,k}  &= 1
-      \end{split}
-\end{equation}
-
-Then solving for $\phi_{j,k}$ yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} below.
+            \frac{\partial \mathcal{L}(\boldsymbol{\phi}, \boldsymbol{\lambda})}{\partial \lambda_{j}} &= 1 - \sum_{k=1}^{K} \phi_{j,k}  \\
+            \therefore \sum_{k=1}^{K} \phi_{j,k}  &= 1
+      \end{split}
+\end{equation}
+
+Then solving for $\phi_{j,k}$ yields
 
@@
       \begin{split}
-            \frac{\partial \mathcal{L}(\phi, \lambda)}{\partial \phi_{j,k}} &= N_{j,k} \frac{1}{\phi_{j,k}}  - \lambda_{j} \\
-            \frac{N_{j,k}}{\phi_{jk}} &= \lambda_{j} \\
-            N_{j,k} &= \phi_{j,k} \lambda_{j} \\
-            \sum_{k=1}^{K} N_{j,k} &= \sum_{k=1}^{K} \phi_{j,k} \lambda_{j} \\
-            N_{j} &= \lambda_{j} \sum_{k=1}^{K} \phi_{j,k} \\
-            N_{j} &= \lambda_{j}
-      \end{split}
-\end{equation}
-
-Substituting $N_{j} = \lambda_{j}$ back into Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} yields Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_4} below.
+            \frac{\partial \mathcal{L}(\boldsymbol{\phi}, \boldsymbol{\lambda})}{\partial \phi_{j,k}} &= N_{j,k} \frac{1}{\phi_{j,k}}  - \lambda_{j} \\
+            \therefore \frac{N_{j,k}}{\phi_{jk}} &= \lambda_{j} \\
+            \therefore N_{j,k} &= \phi_{j,k} \lambda_{j} \\
+            \therefore \sum_{k=1}^{K} N_{j,k} &= \sum_{k=1}^{K} \phi_{j,k} \lambda_{j} \\
+            \therefore N_{j} &= \lambda_{j} \sum_{k=1}^{K} \phi_{j,k} \\
+            \therefore N_{j} &= \lambda_{j}
+      \end{split}
+\end{equation}
+
+Substitution of $N_{j} = \lambda_{j}$ back into Equation~\eqref{eq:bhh:optimisation_step:mle:proof_log_likelihood_phi_part_3} yields
 
@@
 
-Another approach to optimising the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ is to optimise the parameters by their probability distributions' parameters.
+Another approach to optimise the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ is to optimise the parameters by their probability distributions' parameters.
 This process is referred to as \index{Bayesian analysis}\textit{Bayesian analysis}.
-This section provides the mathematical details of Bayesian analysis and \acf{MAP} as it is implemented by the \acs{BHH}.
-
-Bayesian analysis makes use of the \textit{posterior} probability distribution. The posterior distribution is simply expressed proportionally as follows.
+This section provides the mathematical details of Bayesian analysis and \acf{MAP} as it is implemented in the \acs{BHH}.
+
+Bayesian analysis makes use of the \textit{posterior} probability distribution. The posterior distribution is simply expressed proportionally as
 
@@
 
-The event $H$ is a multinomial distribution with probability parameter $\theta$.
+The events $\boldsymbol{H}$ is a multinomial distribution with probability parameter $\boldsymbol{\theta}$.
 It is known that the conjugate prior to a multinomial distribution is a \index{Dirichlet probability distribution}Dirichlet probability distribution.
-The \textit{prior} probability distribution for $\theta_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_theta_prior} below.
+The \textit{prior} probability distribution for $\boldsymbol{\theta}$ is thus presented as
 
@@
       \begin{split}
-            P(\theta | \alpha)
+            P(\boldsymbol{\theta} | \boldsymbol{\alpha})
             &\propto \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} -1}
@@
 
-Furthermore, the event $E$ is also a multinomial distribution with parameter $\phi$.
-The \textit{prior} probability distribution for $\phi_{j,k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_phi_prior} below.
+Furthermore, the events $\boldsymbol{E}$ is also a multinomial distribution with parameter $\boldsymbol{\phi}$. The \textit{prior} probability distribution for $\boldsymbol{\phi}$ is thus presented as
 
@@
       \begin{split}
-            P(\phi \vert \beta)
+            P(\boldsymbol{\phi} \vert \boldsymbol{\beta})
             &\propto \prod_{j=1}^{J}  \prod_{k=1}^{K} \phi_{j,k}^{\beta_{j,k} -1}
@@
 
-Finally, the event $C$ is a \index{Binomial probability distribution}Binomial probability distribution with probability parameter $\psi$.
+Finally, the events $\boldsymbol{C}$ is a \index{Binomial probability distribution}Binomial probability distribution with probability parameter $\boldsymbol{\psi}$.
 It is known that the conjugate prior to a \index{Binomial probability distribution}Binomial probability distribution is a Beta probability distribution.
-The prior probability distribution for $\psi_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.
+The prior probability distribution for $\boldsymbol{\psi}$ is thus presented as
 
@@
       \begin{split}
-            P(\psi | \gamma_{1}, \gamma_{0})
+            P(\boldsymbol{\psi} | \gamma_{1}, \gamma_{0})
             &\propto \prod_{k=1}^{K} \psi_{k}^{\gamma_{1,k}} (1- \psi_{k})^{\gamma_{2,k}}
@@
 
-Putting the likelihood and priors together yields the posterior distribution as given in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.
-
+Putting the likelihood and priors together yields the posterior distribution as given below:
+
+\footnotesize
 \begin{equation}
@@
       \begin{split}
-            P(\theta, \phi, \psi \vert H, E, C;  \alpha, \beta, \gamma_{1}, \gamma_{0})
-            &\propto P(H \vert E, C; \theta, \phi, \psi)P(\theta, \phi, \psi \vert \alpha, \beta, \gamma_{1}, \gamma_{0}) \\
-            &= P(E \vert H; \phi) P(C \vert H; \psi) P(H \vert \theta) P(\phi \vert \beta) \\
-            &\times P(\psi \vert \gamma_{1}, \gamma_{0}) P(\theta \vert \alpha)  \\
+            P(\boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi} \vert \boldsymbol{H}, \boldsymbol{E}, \boldsymbol{C};  \boldsymbol{\alpha}, \boldsymbol{\beta}, \gamma_{1}, \gamma_{0})
+            &\propto P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})P(\boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi} \vert \boldsymbol{\alpha}, \boldsymbol{\beta}, \gamma_{1}, \gamma_{0}) \\
+            &= P(\boldsymbol{E} \vert \boldsymbol{H}; \boldsymbol{\phi}) P(\boldsymbol{C} \vert \boldsymbol{H}; \boldsymbol{\psi}) P(\boldsymbol{H} \vert \boldsymbol{\theta}) P(\boldsymbol{\phi} \vert \boldsymbol{\beta}) P(\boldsymbol{\psi} \vert \gamma_{1}, \gamma_{0}) P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})  \\
             &= \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right] \\
@@
 \end{equation}
-
-From Equation~\eqref{eq:bhh:optimisation_step:map:posterior} above, it can be seen that the posterior distribution has the same form $\mathcal{A}(v)$ as the prior distribution.
-The concentration update operations can then be given in Equations \eqref{eq:bhh:optimisation_step:map:alpha_update_operation}, \eqref{eq:bhh:optimisation_step:map:beta_update_operation}, \eqref{eq:bhh:optimisation_step:map:gamma1_update_operation} and \eqref{eq:bhh:optimisation_step:map:gamma2_update_operation} below.
+\normalsize
+
+From Equation~\eqref{eq:bhh:optimisation_step:map:posterior} above, it can be seen that the posterior distribution has the same form, $\mathcal{A}(v)$, as the prior distribution.
+The concentration update operations are then be given as
 
@@
 It can be seen that the prior and posterior probability distributions are of the same form, $\mathcal{A}(v)$.
-It can therefore be said that the \acs{BHH} implements a Gaussian process.
-Since the reselection of heuristics happens at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acf{HMM}.
-
-Throughout this chapter a number of hyper-parameters have been identified. These are summarised and discussed in the next section.
+It can therefore be said that the \acs{BHH} implements a Gaussian process~\cite{ref:gortler:2019}.
+Since the reselection of heuristics happens at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acs{HMM}~\cite{ref:rabiner:1986}.
 
@@
 This section provides a breakdown of all the hyper-parameters that were identified and briefly mentioned in this chapter.
-Some logical arguments can be made as to what their values should be, however it is still up to empirical analysis to determine the effects of certain hyper-parameter design decisions.
+The following hyper-parameters are presented: \index{heuristic pool}\textit{heuristic pool}, \textit{population size}, \textit{credit assignment strategy}, \textit{reselection interval}, \textit{replay window size}, \textit{reanalysis interval}, \textit{burn in window size}, \textit{discounted rewards} and \textit{normalisation}.
+Some logical arguments can be made as to what their values should be.
+However it is still up to empirical analysis to determine the effects of certain hyper-parameter design decisions.
 Were possible, a range of possible values is provided.
@@
 The \index{heuristic pool}heuristic pool hyper-parameter refers to the heuristic-pool configuration that is used.
-The configuration of the \index{heuristic pool}heuristic pool should account for the following factors.
+The configuration of the \index{heuristic pool}heuristic pool should account for the following factors:
 
@@
 
-The design choices at a high level is not as strict for the \acs{BHH} as it is for low-level heuristics.
-If one is unsure as to which low-level hyper-parameters to use, one could simply include multiple configurations of a low-level heuristic, each with its own unique hyper-parameter configurations.
+The design choices at a high level are not as strict for the \acs{BHH} as it is for low-level heuristics.
+If the choice of hyper-parameters is uncertain, multiple configurations of a low-level heuristic, each with its own unique hyper-parameter configurations, can be included in the \index{heuristic pool}heuristic pool.
 
@@
 The population size to use is to be determined empirically.
-Naturely, an assumption is made that a larger population could lead to better results, assuming that entities are initialised uniformly across the solution search space.
-\citeauthor{ref:oldewage:2017}~\cite{ref:oldewage:2017} mentions that a large number of particles (entities) may be able to traverse a greater portion of the search space as every particle provides additional information about the search space.
+Naturally, an assumption is made that a larger population could lead to better results, assuming that entities are initialised uniformly across the solution search space.
+However, larger population sizes are computationally more expensive.
+\citeauthor{ref:oldewage:2017}~\cite{ref:oldewage:2017} mentions that a large number of particles (entities) may be able to traverse a greater portion of the search space, because every particle provides additional information about the search space.
 However, it is to be determined if this is indeed the case for the \acs{BHH}.
-The following factors need to be considered when picking a population size.
+The following factors need to be considered when picking a population size:
 
@@
       \item When considering the lower bound of possible population sizes, take into account the highest, minimum population size required by all low-level \index{heuristic}heuristics.
-For example, if one includes \Acs{DE} into the \index{heuristic}heuristic pool, one needs a population size of at least 4.
-For \acs{PSO}, the minimum population size is 3.
+For example, if \Acs{DE} is included into the \index{heuristic}heuristic pool, a population size of at least four is required.
+For \acs{PSO}, the minimum population size is three.
 
       \item When considering the upper bound of possible population sizes, take into account that a bigger population size results in a more computationally expensive training process.
-Furthermore, there could exists a point of \textit{diminishing returns} where an increase in population size does not yield any better outcome.
+Furthermore, there could exist a point of \textit{diminishing returns} where an increase in population size does not yield any better outcome.
 \end{itemize}
@@
 The credit hyper-parameter refers to the credit assignment strategy that is used.
-This dissertation proposed 5 different credit assignment strategies that were presented in Section \ref{sec:bhh:credit_assignment_strategy}.
-The choice of credit assignment is assumed to be problem-dependent, however, this is to be  tested empirically.
-Along with the credit assignment strategy itself, the following factors related to the credit assignment strategy should be considered.
+This dissertation proposed five different credit assignment strategies that were presented in Section \ref{sec:bhh:credit_assignment_strategy}.
+The choice of credit assignment is assumed to be problem-dependent.
+However, this is to be tested empirically.
+Along with the credit assignment strategy itself, the following factors related to the credit assignment strategy should be considered:
 
@@
 A number of other hyper-parameters are specifically included to address the list of considerations as given above.
-These include \textit{reselection}, \textit{replay} and \textit{reanalysis window sizes}, \textit{burn in}, \textit{discounted rewards} and \textit{normalisation}.
-Each of these are presented next.
-
-\subsection{Reselection}\label{sec:bhh:hyper_parameters:reselection}
-
-The reselection window size is a hyper-parameter that controls how often heuristic selections are resampled from the heuristic distribution, parameterised by the heuristic selection probability that is learnt.
-The choice of reselection should be influenced by the following considerations.
-If reselection happens too frequently, it does not allow heuristics sufficient time to achieve their goals and smooth out update steps.
+These include \textit{reselection interval}, \textit{replay window size} and \textit{reanalysis interval}, \textit{burn in window size}, \textit{discounted rewards} and \textit{normalisation}.
+
+\subsection{Reselection Interval}\label{sec:bhh:hyper_parameters:reselection}
+
+The reselection interval is a hyper-parameter that controls how often heuristic selections are resampled from the heuristic distribution, parameterised by the heuristic selection probability that is learnt.
+The choice of reselection should be influenced by the following considerations: If reselection happens too frequently, heuristics are not allowed sufficient time to achieve their goals and to smooth out update steps.
 If reselection happens too infrequently, it does not allow for sufficient collection of samples/evidence from which learning is done.
-Naturally, the correct reselection window size to use is to be determined empirically.
-
-\subsection{Replay}\label{sec:bhh:hyper_parameters:replay}
+Naturally, the correct reselection interval to use is to be determined empirically.
+
+\subsection{Replay Window Size}\label{sec:bhh:hyper_parameters:replay}
 
@@
 A replay window size that is too small includes little to no memory, resulting in a situation where the \acs{BHH} simply looks at the most recent evidence that is collected and nothing more.
-On the contrary, if the replay window size is big, the \acs{BHH} tracks a longer history of past performances, leading to a situation where previously well-performing heuristics that are not relevant later in the training process, is still selected often.
-
-\subsection{Reanalysis}\label{sec:bhh:hyper_parameters:reanalysis}
-
-The reanalysis window size is a hyper-parameter that controls how often the \acs{BHH} updates its past beliefs (priors).
-The reanalysis window size goes hand in hand with the reselection and replay window sizes.
+On the contrary, if the replay window size is large, the \acs{BHH} tracks a longer history of past performances, leading to a situation where previously well-performing heuristics that are not relevant later in the training process, is still selected often.
+
+\subsection{Reanalysis Interval}\label{sec:bhh:hyper_parameters:reanalysis}
+
+The reanalysis interval is a hyper-parameter that controls how often the \acs{BHH} updates its past beliefs (priors).
+The reanalysis interval goes hand in hand with the reselection interval and replay window size.
 If the reanalysis window is too small, the \acs{BHH} prematurely updates its priors.
-Similar to other hyper-parameters discussed thus far, the correct value to use for the reanalysis window size is to be determined empirically.
+Similar to other hyper-parameters discussed thus far, the correct value to use for the reanalysis interval is to be determined empirically.
 However, some logical exclusions can be made.
-A reanalysis window size that is smaller than the reselection window size does not make sense, since the effects of reanalysis are only realised during reselection.
-A reanalysis window size that is too big could lead to a situation where the delay in updating priors could be detrimental to the outcomes of the \acs{BHH}.
+A reanalysis interval that is smaller than the reselection interval does not make sense, since the effects of reanalysis are only realised during reselection.
+A reanalysis interval that is too big could lead to a situation where the delay in updating priors could be detrimental to the outcomes of the \acs{BHH}.
 
@@
 The intent of the burn in hyper-parameter is to determine if heuristics need time to execute before reanalysis starts.
-Notice that a delay in the learning process does not mean that reselection doesn't occur or performance information is not collected in the replay window.
-Therefore, it should be noted that the burn in window size, reselection window size and replay window size should be considered together.
+Notice that a delay in the learning process does not mean that reselection does not occur or that performance information is not collected in the replay window.
+Therefore, it should be noted that the burn in window size, reselection interval, and replay window size should be considered together.
 If the replay window size is smaller than the burn in window size, performance information is discarded and an opportunity to learn is lost.
@@
 
-The following section discusses the default values for proxied update step operations.
-
 \subsection{Defaults}
@@
 Each has its own set of hyper-parameters that differ from each other.
-In the case of \acs{Adam}, there are 4 hyper-parameters that include learning rate, $\beta1$, $\beta2$ and $\epsilon$.
-If another heuristic needs to proxy \acs{Adam}'s expected gradient mean operation, a default $\beta1$ parameter must be supplied that is applied by the proxy mechanism.
+In the case of \acs{Adam}, there are four hyper-parameters that include learning rate, $\beta_{1}$, $\beta_{2}$ and $\epsilon$.
+If another heuristic needs to proxy \acs{Adam}'s expected gradient mean operation, a default $\beta_{1}$ parameter must be supplied that is applied by the proxy mechanism.
 This is only the case when multiple instances of a heuristic is included and there is uncertainty about which instance's hyper-parameters to use for the proxied heuristic update steps.
@@
 
-The next section provides the reader with the pseudo-code algorithm for the \acs{BHH}.
-
-\section{Algorithm}
+\section{The \acs{BHH} Algorithm}
 \label{sec:bhh:algorithm}
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[htbp]
       \caption{The pseudo-code for the implementation of the \acf{BHH}}
@@
             \Else
-            \If {step $\mathbin{\%}$ reanalysis window size = 0}
+            \If {step $\mathbin{\%}$ reanalysis interval = 0}
             \State apply Bayesian analysis
@@
 
-            \If {step $\mathbin{\%}$ reselection window size = 0}
+            \If {step $\mathbin{\%}$ reselection interval = 0}
             \State select heuristic

### 2022-11-27 dissertation/chapters/06-bayesian-hyper-heuristic.tex
✨ (final-review): Chapter 6 Done

@@
 
-      \item \textbf{Section \ref{sec:bhh:credit_assignment_strategy}} presents detailed discussions on credit assignment and move acceptance strategies.
+      \item \textbf{Section \ref{sec:bhh:credit_assignment_strategy}} presents detailed discussions on credit assignment strategies.
 
@@
 This section provides an overview of the workings of the \Acf{BHH}.
-The general concept of the \acs{BHH} can be summarised as follows.
-The \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic, from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and \acs{FFNN} training process.
+The general concept of the \acs{BHH} can be summarised as follows: The \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and \acs{FFNN} training process.
 The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process.
@@
 This section aims to present the reader with all the high level components in the architecture of the \Acs{BHH}.
-Burke et al.~\cite{ref:burke:2010} propose an initial framework for \acp{HH} and Grobler~\cite{ref:grobler:2015} further proposed a framework for a heterogeneous meta-\ac{HH}.
+Burke et al.~\cite{ref:burke:2010} propose an initial framework for \acp{HH} and Grobler~\cite{ref:grobler:2015} further propose a framework for a heterogeneous meta-\ac{HH}.
 The aforementioned frameworks are adapted for the implementation of the \Acs{BHH}.
@@
 \end{itemize}
-
-Each of the components in Figure \ref{fig:bhh_architecture} is discussed in detail in the following sections.
 
@@
       \centering
-      \caption{An example of mapping of proxied state update operation maintained by the \acs{BHH}.}
+      \caption{An example of a mapping of proxied state update operation maintained by the \acs{BHH}.}
       \label{tab:bhh:heuristic_pool:proxy_mapping_example}%
@@
 The population state generally contains state parameters that are of importance to multiple \index{heuristic}heuristics, and usually tracks the state of the population and not individual \index{heuristic}heuristic.
-Some examples of population state that can arise from different \index{heuristic}heuristics is given below:
+Some examples of population state that can arise from different \index{heuristic}heuristics are given below:
 
@@
       \centering
-      \caption{An example of the performance log implemented by the \acs{BHH}, showing the first five entities, their allocated \index{heuristic}heuristics and their resulting performance measurements for step 1 of the training process.}
+      \caption{An example of the performance log implemented by the \acs{BHH}, showing the first five entities, their allocated \index{heuristic}heuristics and their resulting performance measurements for the first step of the training process.}
       \label{tab:bhh:performance_log:performance_log_example}%
@@
 \begin{itemize}
-      \item \textbf{$H$}: The event of observing \textit{heuristics}.
-      \item \textbf{$E$}: The event of observing \textit{entities}.
-      \item \textbf{$C$}: The event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} are met.
+      \item \textbf{$\boldsymbol{H}$}: The event of observing \textit{heuristics}.
+      \item \textbf{$\boldsymbol{E}$}: The event of observing \textit{entities}.
+      \item \textbf{$\boldsymbol{C}$}: The event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} are met.
 \end{itemize}
@@
 It should be noted that event information is stored and observed directly from the performance log as presented in Table \ref{tab:bhh:credit_assignment_strategy:credit_assignment_example}.
-From the above list of events, the event $C$ is dependent on the occurrence of $H$ and $E$ and a credit assignment strategy.
+From the above list of events, the event $\boldsymbol{C}$ is dependent on the occurrence of $\boldsymbol{H}$ and $\boldsymbol{E}$ and a credit assignment strategy.
 
@@
 The dependence between random events can have an impact on the probabilistic model that is implemented.
-For simplicity, the \acs{BHH} assumes independence between events, although the event $C$ is clearly dependent on the occurrence of $H$ and $E$.
+For simplicity, the \acs{BHH} assumes independence between events, although the event $\boldsymbol{C}$ is clearly dependent on the occurrence of $\boldsymbol{H}$ and $\boldsymbol{E}$.
 Furthermore, the \acs{BHH} assumes independence between steps  and treats each training step as if training has restarted.
@@
 
-      \item $\boldsymbol{H} \vert \boldsymbol{\theta} \sim Mult(\boldsymbol{\theta}; I, K)$ denote the distribution of heuristics (events $\boldsymbol{H}$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled heuristic selection probabilities $\boldsymbol{\theta}$, the \index{heuristic pool}heuristic pool size $K$, and maximum number of instances $I$.
-
-      \item $\boldsymbol{E} \vert \boldsymbol{\phi} \sim Mult(\boldsymbol{\phi}; I, K)^{J}$ denote the distribution of entity-heuristic combinations (events $\boldsymbol{E}$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled entity-heuristic selection probabilities $\boldsymbol{\phi}$, the \index{heuristic pool}heuristic pool size $K$, and maximum number of instances $I$ for each entity in $J$.
-
-      \item $\boldsymbol{C} \vert \boldsymbol{\psi} \sim Bin(\boldsymbol{\psi}, I)$ denote the distribution of credit-heuristic combinations (events $\boldsymbol{C}$), implementing a \index{Binomial probability distribution}Binomial probability distribution, parameterised by the sampled credit-heuristic selection probabilities $\boldsymbol{\psi}$ and the maximum number of instances $I$.
+      \item $\boldsymbol{H} \vert \boldsymbol{\theta} \sim Mult(\boldsymbol{\theta}; I, K)$ denote the distribution of heuristics (event $\boldsymbol{H}$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled heuristic selection probabilities $\boldsymbol{\theta}$, the \index{heuristic pool}heuristic pool size $K$, and maximum number of instances $I$.
+
+      \item $\boldsymbol{E} \vert \boldsymbol{\phi} \sim Mult(\boldsymbol{\phi}; I, K)^{J}$ denote the distribution of entity-heuristic combinations (event $\boldsymbol{E}$), implementing a \index{Multinomial probability distribution}Multinomial distribution, parameterised by the sampled entity-heuristic selection probabilities $\boldsymbol{\phi}$, the \index{heuristic pool}heuristic pool size $K$, and maximum number of instances $I$ for each entity in $J$.
+
+      \item $\boldsymbol{C} \vert \boldsymbol{\psi} \sim Bin(\boldsymbol{\psi}, I)$ denote the distribution of credit-heuristic combinations (event $\boldsymbol{C}$), implementing a \index{Binomial probability distribution}Binomial probability distribution, parameterised by the sampled credit-heuristic selection probabilities $\boldsymbol{\psi}$ and the maximum number of instances $I$.
 \end{itemize}
@@
 Probabilities might be very low at some points during training.
-Consider an example where training has stagnated, effectively leading to a scenario where a credit assignment strategy never fulfills a credit assignment, yielding an extremely small probability for $\psi$.
+Consider an example where training has stagnated, effectively leading to a scenario where a credit assignment strategy never fulfills a credit assignment, yielding an extremely small probability for $\boldsymbol{\psi}$.
 A solution to the aforementioned problem is to apply the \textit{log-sum-exp} trick.
@@
 
-      \item setting the lower-bound of the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$ to 1, so that a selection probability of 0 is highly improbable; and
+      \item setting the lower-bound of the concentration parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$ to 1, so that a selection probability of 0 is highly improbable; and
 
@@
 
-The events $\boldsymbol{H}$ is a multinomial distribution with probability parameter $\boldsymbol{\theta}$.
+The event $\boldsymbol{H}$ is a multinomial distribution with probability parameter $\boldsymbol{\theta}$.
 It is known that the conjugate prior to a multinomial distribution is a \index{Dirichlet probability distribution}Dirichlet probability distribution.
@@
 
-Furthermore, the events $\boldsymbol{E}$ is also a multinomial distribution with parameter $\boldsymbol{\phi}$. The \textit{prior} probability distribution for $\boldsymbol{\phi}$ is thus presented as
+Furthermore, the event $\boldsymbol{E}$ is also a multinomial distribution with parameter $\boldsymbol{\phi}$. The \textit{prior} probability distribution for $\boldsymbol{\phi}$ is thus presented as
 
@@
 
-Finally, the events $\boldsymbol{C}$ is a \index{Binomial probability distribution}Binomial probability distribution with probability parameter $\boldsymbol{\psi}$.
+Finally, the event $\boldsymbol{C}$ is a \index{Binomial probability distribution}Binomial probability distribution with probability parameter $\boldsymbol{\psi}$.
 It is known that the conjugate prior to a \index{Binomial probability distribution}Binomial probability distribution is a Beta probability distribution.
@@
 However it is still up to empirical analysis to determine the effects of certain hyper-parameter design decisions.
-Were possible, a range of possible values is provided.
+Where possible, a range of possible values are provided.
 
@@
       \item The type of low-level heuristics to include in the \index{heuristic pool}heuristic pool.
-This dissertation investigates two main groups, including gradient-based \index{heuristic}heuristics and meta-heuristics.
+This dissertation investigates two main groups, including gradient-based \index{heuristic}heuristics and \acp{MH}.
 
@@
 
-\subsection{Credit}\label{sec:bhh:hyper_parameters:credit}
-
-The credit hyper-parameter refers to the credit assignment strategy that is used.
-This dissertation proposed five different credit assignment strategies that were presented in Section \ref{sec:bhh:credit_assignment_strategy}.
-The choice of credit assignment is assumed to be problem-dependent.
+\subsection{Credit Assignment Strategy}\label{sec:bhh:hyper_parameters:credit}
+
+Five different credit assignment strategies were presented in Section \ref{sec:bhh:credit_assignment_strategy}.
+The choice of credit assignment is assumed to be problem dependent.
 However, this is to be tested empirically.
@@
 A number of other hyper-parameters are specifically included to address the list of considerations as given above.
-These include \textit{reselection interval}, \textit{replay window size} and \textit{reanalysis interval}, \textit{burn in window size}, \textit{discounted rewards} and \textit{normalisation}.
+These include the \textit{reselection interval}, \textit{replay window size} and \textit{reanalysis interval}, \textit{burn in window size}, \textit{discounted rewards} and \textit{normalisation}.
 
@@
 A replay window size that is too small includes little to no memory, resulting in a situation where the \acs{BHH} simply looks at the most recent evidence that is collected and nothing more.
-On the contrary, if the replay window size is large, the \acs{BHH} tracks a longer history of past performances, leading to a situation where previously well-performing heuristics that are not relevant later in the training process, is still selected often.
+On the contrary, if the replay window size is large, the \acs{BHH} tracks a longer history of past performances, leading to a situation where previously well-performing heuristics that are not relevant later in the training process, are still selected often.
 
@@
 The reanalysis interval goes hand in hand with the reselection interval and replay window size.
-If the reanalysis window is too small, the \acs{BHH} prematurely updates its priors.
+If the reanalysis interval is too small, the \acs{BHH} prematurely updates its priors.
 Similar to other hyper-parameters discussed thus far, the correct value to use for the reanalysis interval is to be determined empirically.
@@
 Notice that a delay in the learning process does not mean that reselection does not occur or that performance information is not collected in the replay window.
-Therefore, it should be noted that the burn in window size, reselection interval, and replay window size should be considered together.
+Therefore, it should be noted that the burn in window size, reselection interval, replay window size, and reanalysis interval should be considered together.
 If the replay window size is smaller than the burn in window size, performance information is discarded and an opportunity to learn is lost.
@@
 
-Normalisation is a hyper-parameter that aims to provide a mechanism of control for the degree to which exploration is allowed.
+Normalisation is a hyper-parameter that provides a mechanism of control for the degree to which exploration is allowed.
 Figure \ref{sec:bhh:hyper_parameters:discounted_rewards:normalisation} shows the effect of different concentrations ($\alpha$ and $\beta$) on the Beta probability distribution.
-By normalising the concentration parameters for the \acs{BHH} ($\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$), the variance of the selection probability distributions increases, allowing for sampled probabilities further from the mean and thus allowing for more exploration.
-
-\begin{figure}[htbp]
+By normalising the concentration parameters for the \acs{BHH} ($\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$), the variance of the selection probability distributions increases, allowing for sampled probabilities further from the mean and thus allowing for more exploration.
+
+\begin{figure}[htb]
       \begin{subfigure}{0.49\textwidth}
@@
 Each has its own set of hyper-parameters that differ from each other.
-In the case of \acs{Adam}, there are four hyper-parameters that include learning rate, $\beta_{1}$, $\beta_{2}$ and $\epsilon$.
+In the case of \acs{Adam}, there are four hyper-parameters that include learning rate, $\eta$, $\beta_{1}$, $\beta_{2}$ and $\epsilon$.
 If another heuristic needs to proxy \acs{Adam}'s expected gradient mean operation, a default $\beta_{1}$ parameter must be supplied that is applied by the proxy mechanism.
@@
 
-\begin{algorithm}[htbp]
+\begin{algorithm}[htb]
       \caption{The pseudo-code for the implementation of the \acf{BHH}}

### 2022-11-28 dissertation/chapters/07-methodology.tex
🗃️ (data): Removing old data

@@
 
-So far, this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acf{HH} and probability theory in Chapters \ref{chap:anns}-\ref{chap:probability}.
+So far, this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acp{HH} and probability theory in Chapters \ref{chap:anns} to \ref{chap:probability}.
 Chapter \ref{chap:bhh} provided the detail of the implementation of the proposed \acs{BHH} with all its components and hyper-parameters.

### 2022-11-28 dissertation/chapters/01-introduction.tex
🚧 (final-review): Chapter 7 WIP

@@
 In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
-Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based meta-heuristics in real-valued dynamic optimization.
+Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimization.
 However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
@@
 
-      \item \textbf{Chapter~\ref{chap:heuristics}} provides details on various types of heuristics and meta-heuristics that have been used to train \acp{FFNN}.
+      \item \textbf{Chapter~\ref{chap:heuristics}} provides details on various types of heuristics and \acp{MH} that have been used to train \acp{FFNN}.
 A literature study is done to provide details on the search behaviours, application and implementation of each heuristic in the context of training \acp{FFNN}.

### 2022-11-28 dissertation/chapters/03-heuristics.tex
🚧 (final-review): Chapter 7 WIP

@@
 Gradient-based techniques are not without flaws and can, for example, yield slow convergence or get trapped in local optima~\cite{ref:mingguang:2009}.
-Other techniques have also been used to successfully train \acp{FFNN}, including meta-heuristics such as \acf{PSO}~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}, \acf{DE}~\cite{ref:espinal:2011} and \acfp{GA}~\cite{ref:gupta:1999}.
+Other techniques have also been used to successfully train \acp{FFNN}, including \acp{MH} such as \acf{PSO}~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}, \acf{DE}~\cite{ref:espinal:2011} and \acfp{GA}~\cite{ref:gupta:1999}.
 
@@
 Three well known \acp{MH}, that have been shown to train \acs{FFNN}, are presented.
-These meta-heuristics include \acf{PSO}, \acf{DE} and \acfp{GA}.~\citeauthor{ref:carvalho:2006}~\cite{ref:carvalho:2006} compared various \acs{PSO} variants for training \acp{FFNN}.~\citeauthor{ref:espinal:2011}~\cite{ref:espinal:2011} compared \acs{DE} and \acs{PSO} when applied to \acs{FFNN} training and~\citeauthor{ref:gupta:1999}~\cite{ref:gupta:1999} compared \acs{BP} to a \acs{GA} for training \acp{FFNN}.
+These \acp{MH} include \acf{PSO}, \acf{DE} and \acfp{GA}.~\citeauthor{ref:carvalho:2006}~\cite{ref:carvalho:2006} compared various \acs{PSO} variants for training \acp{FFNN}.~\citeauthor{ref:espinal:2011}~\cite{ref:espinal:2011} compared \acs{DE} and \acs{PSO} when applied to \acs{FFNN} training and~\citeauthor{ref:gupta:1999}~\cite{ref:gupta:1999} compared \acs{BP} to a \acs{GA} for training \acp{FFNN}.
 

### 2022-11-28 dissertation/chapters/04-hyper-heuristics.tex
🚧 (final-review): Chapter 7 WIP

@@
 In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
-Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based meta-heuristics in real-valued dynamic optimization.
+Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimization.
 Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.

### 2022-11-28 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 (final-review): Chapter 7 WIP

@@
       \item \textbf{Meta-Hyper-Heuristic:} There exists a domain barrier, where the \acs{BHH} searches through the \textit{heuristic space}, using only \index{heuristic}heuristic performance information, while lower level heuristics search through the \textit{solution space} using information from the search domain itself.
-Furthermore, the \index{heuristic pool}heuristic pool implemented by the \acs{BHH} supports both gradient-based low level \index{heuristic}heuristics, as well as meta-heuristics.
+Furthermore, the \index{heuristic pool}heuristic pool implemented by the \acs{BHH} supports both gradient-based low level \index{heuristic}heuristics, as well as \acp{MH}.
 

### 2022-11-28 dissertation/chapters/07-methodology.tex
🚧 (final-review): Chapter 7 WIP

@@
 
-Each empirical tests starts with a question to be answered.
+Each empirical test starts with a question to be answered.
 A hypothesis is formulated for the outcome of the empirical test.
@@
 In the context of training \acp{FFNN}, the underlying model is trained across a number of datasets.
-Each dataset is split into a training and test set.
+Each dataset is split into a training set comprising of 80\% of the data, and a test set comprising of 20\% of the data.
 The training set is used to train the model, while the test set is used to evaluate the model's performance on unseen data.
-Training epochs are split into mini-batch iterations with a specified mini-batch size.
+Training epochs are split into mini-batch iterations with a specified mini-batch size per dataset.
 Evaluation takes place at every mini-batch step.
@@
 These datasets originate from the UCI Machine Learning Repository~\cite{ref:uci:2022}.
-Datasets are grouped by problem type and include 8 classification and 7 regression datasets.
+Datasets are grouped by problem type and include seven classification and seven regression datasets.
 The classification datasets are given in Table \ref{tab:methodology:datasets:classification} and the regression datasets are given in Table \ref{tab:methodology:datasets:regression} below.
 
-\begin{table}[htbp]
+\begin{table}[htb]
       \centering
@@
                   bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & ~\cite{ref:moro:2014}      \\
-                  adult            & multivariate    & categorical, integer       & 14                  & 2                & 48842              & 256            & 191            & ~\cite{ref:kohavi:1996}    \\
                   diabetic         & multivariate    & integer                    & 55                  & 3                & 100000             & 1024           & 98             & ~\cite{ref:strack:2014}    \\
@@
 
-\begin{table}[htbp]
+\begin{table}[htb]
       \centering
@@
 
-Details on how the datasets where preprocessed and prepared is given in Appendix \ref{app:datasets}. The concept of class balancing is briefly discussed next.
+Details on how the datasets where preprocessed and prepared is given in Appendix \ref{app:datasets}.
 
@@
 A number of classification datasets given in Table \ref{tab:methodology:datasets:classification} contain an unbalanced representation of classes.
-The empirical process defined in this dissertation does not apply mechanisms to cater for class balancing, in order to eliminate as many variables and factors in the empirical process as possible, as it is already a complicated process.
+The empirical process defined in this dissertation does not apply mechanisms to cater for class balancing, in order to eliminate as many variables and factors in the empirical process as possible.
 It is therefore suggested that the \acs{BHH} first be studied under the assumption of balanced classes, before applying class balancing techniques.
@@
 
-The next section presents the \acp{FFNN}/models and the configurations that are used in the empirical process.
-
 \section{Models}\label{sec:methodology:model}
 
-All models that are trained in this dissertation follow implementations of shallow \acp{FFNN}, meaning they only have one hidden layer.
+All models that are trained in this dissertation follow implementations of shallow \acp{FFNN}, meaning that they only have one hidden layer.
 The architecture of a model is dependent on the dataset being trained on, the type of optimisation problem, the number of input dimensions and the number of output dimensions.
-Models' initial weights are initialised by means of \index{Glorot uniform sampling}Glorot uniform sampling.
-The models and their configuration, as it is used for each dataset, is given in Table \ref{tab:methodology:models:configurations} below.
+The number of hidden layers were determined empirically.
+Weights are initialised by means of \index{Glorot uniform sampling}Glorot uniform sampling~\cite{ref:glorot:2010}.
+The models and their configuration, as it is used for each dataset, are given in Table \ref{tab:methodology:models:configurations}.
 
-% Table generated by Excel2LaTeX from sheet 'Model Configurations'
-\begin{table}[htbp]
+\begin{table}[htb]
       \centering
@@
                                      & rho                       & 0.95           &                            \\
-                                     & epsilon                   & 0.0000001      &                            \\
+                                     & epsilon                   & 1E-07          &                            \\
                   adam               & learning rate             & 0.1 (0.01)     & ~\cite{ref:kingma:2014}    \\
                                      & beta1                     & 0.9            &                            \\
-                                     & beta2                     & 0.95           &                            \\
+                                     & beta2                     & 0.999          &                            \\
                                      & epsilon                   & 1E-07          &                            \\
                   pso                & population size           & 10             & ~\cite{ref:van:2010}       \\
-                                     & learning rate             & 0.1 (0.01)     &                            \\
+                                     & learning rate             & 1.0 (0.9)      &                            \\
                                      & inertia weight (w)        & 0.729844       &                            \\
@@
 
-Note that from Table \ref{tab:methodology:heuristics}, values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it.
+Note from Table \ref{tab:methodology:heuristics} that values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it.
 The number of steps is the total number of mini-batch training steps that are executed for that particular dataset.
@@
 Furthermore, it should be noted that a learning rate was added to \acs{PSO} as an attempt to avoid overshooting solutions later in the training process.
-This parameter does not traditionally form part of \acs{PSO}, but was found to be useful.
+A learning rate parameter does not traditionally form part of \acs{PSO}, but was found to be useful.
+The position update step for \acs{PSO} using a learning rate is then defined as
+
+\begin{equation}
+      \label{eq:heuristics:pso:position_learning_rate}
+      \begin{split}
+            x_{ij}(t+1) = x_{ij}(t) + \eta v_{ij}(t+1)
+      \end{split}
+\end{equation}
+
+where $\eta$ is the added learning rate with $0 \leq \eta \leq 1, \eta \in \mathbb{R}$.
 
 Section \ref{sec:bhh:heuristic:proxies} presented the concept of a mapping of proxied \index{heuristic}heuristic state update operations.
-The mapping of proxied \index{heuristic}heuristic state update operations, implemented by the \acs{BHH} in the empirical process, is given in Figure \ref{fig:methodology:heuristics:proxies}.
+The mapping of proxied \index{heuristic}heuristic state update operations implemented by the \acs{BHH} in the empirical process is given in Figure \ref{fig:methodology:heuristics:proxies}.
 
@@
 
-In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x}, indicate that the associated \index{heuristic}heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
+In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x} indicate that the associated \index{heuristic}heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
 The required mapping of proxied \index{heuristic}heuristic state operations is then implemented as a lookup of the table presented in Figure \ref{fig:methodology:heuristics:proxies}.
-
-The following section provides the details around the \acs{BHH} baseline configuration.
 
@@
 % Table generated by Excel2LaTeX from sheet 'BHH Baseline'
-\begin{table}[htbp]
+\begin{table}[htb]
       \centering
@@
 
-The following section provides the performance measurements that are implemented.
-
 \section{Performance Measures}\label{sec:methodology:performance_measures}
@@
 
-After training has been completed, the \textit{average rank}, based on test loss, for all configurations, is calculated at each mini-batch step across all runs.
-The test loss metric and average rank are statistically analysed and used to derive findings and conclusions.
+The test set is used as a validation set during training.
+All performance metrics are measured for the training set as well as the test/validation set during training.
+As such, a divergence in performance metrics between the training and test/validation set is used to evaluate for overfitting during the training process.
 
-The following section provides the stopping conditions that are used.
+After training has been completed, the \textit{average rank}, based on test loss, for all configurations, is calculated at each mini-batch step.
+A total of 30 independent runs with different random seed configurations are executed for each empirical test.
+The test loss metric and average rank are then statistically analysed across all runs, and are used to derive findings and conclusions.
 
@@
 
-The following sections provide the various experimental groups that are formulated and empirically tested.
-
 \section{Experiments}
@@
 Three main experimental groups are formulated.
-These include a behavioural case study of the \acs{BHH} as it relates to an example problem, a critical evaluation of the \acs{BHH}'s baseline performance in comparison to other standalone low-level \index{heuristic}heuristics, and finally an analysis of different \acs{BHH} variants is done by analysing the effects of different hyper-parameter values on the outcomes of the \acs{BHH}.
 Each of these are discussed in more detail in the following sections.
@@
 
-The behavioural case study is concerned with studying the behaviour of the \acs{BHH} baseline configuration as it relates to an example problem dataset, across a number of runs.
+The behavioural case study analyses the behaviour of the \acs{BHH} baseline configuration as it relates to an example problem dataset, across 30 independent runs.
 The example problem dataset is the iris dataset, presented in Table \ref{tab:methodology:datasets:classification}.
@@
 Additional to the \acs{BHH} baseline configuration, two more \acs{BHH} configurations are included.
-These include \acs{BHH} configurations where the \index{heuristic pool}heuristic pool only makes use of gradient-based \index{heuristic}heuristics, and a configuration where the \index{heuristic pool}heuristic pool only makes use of meta-heuristics.
+These include \acs{BHH} configurations where the \index{heuristic pool}heuristic pool only makes use of gradient-based \index{heuristic}heuristics, and a configuration where the \index{heuristic pool}heuristic pool only makes use of \acp{MH}.
 The intent behind the inclusion of these configurations is to determine the effectiveness of multi-method approaches in the \index{heuristic pool}heuristic pool as it applies to training \acp{FFNN}.
@@
 
-In Table \ref{tab:methodology:experiments:bhh_variants}, the \index{heuristic pool}heuristic pool configuration \textit{gd} refers to the \index{heuristic pool}heuristic pool configuration where only gradient-based \index{heuristic}heuristics are included, and \textit{mh} refers to the \index{heuristic pool}heuristic pool configuration where only meta-heuristics are included.
-
-The next section presents the method that is followed for statistical analysis.
+In Table \ref{tab:methodology:experiments:bhh_variants}, the \index{heuristic pool}heuristic pool configuration \textit{gd} refers to the \index{heuristic pool}heuristic pool configuration where only gradient-based \index{heuristic}heuristics are included, and \textit{mh} refers to the \index{heuristic pool}heuristic pool configuration where only \acp{MH} are included.
 
@@
 The results are analysed and checked for overfitting and outliers are identified.
-The skewness of the results is evaluated per dataset and the \index{Shapiro-Wilk}Shapiro-Wilk test for normality ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
-Furthermore, the \index{Levene}Levene's test for equality of variance ($\alpha$ = 0.001) is used.
+The skewness of the results is evaluated per dataset and the \index{Shapiro-Wilk}Shapiro-Wilk test for normality~\cite{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
+Furthermore, the \index{Levene}Levene's test for equality of variance~\cite{ref:levene:1961} ($\alpha$ = 0.001) is used.
 The output of the full statistical analysis is presented in Appendix \ref{app:statistical_analysis}.
@@
 Dependent on the outcomes of the above statistical tests, the appropriate statistical significance test is then executed.
-For experiments where there are only two configurations, the Mann-Whitney U\index{Mann-Whitney U} independent samples t-Test ($\alpha$ = 0.001) is executed.
-For experiments with three or more configurations, the \acf{ANOVA} statistical test ($\alpha$ = 0.001) is used.
-The\index{Kruskal-Wallis} Kruskal-Wallis ranked non-parametric test for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
+For experiments where there are only two configurations, the Mann-Whitney U\index{Mann-Whitney U} independent samples t-Test~\cite{ref:mann:1947} ($\alpha$ = 0.001) is executed.
+For experiments with three or more configurations, the \acs{ANOVA} statistical test~\cite{ref:fisher:1921} ($\alpha$ = 0.001) is used.
+The\index{Kruskal-Wallis} Kruskal-Wallis ranked non-parametric test~\cite{ref:kruskal:1952} for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
 
-Regardless of the statistical test that is used, a post-hoc Tukey honest significant difference test ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
+Regardless of the statistical test that is used, a post-hoc Tukey honest significant difference test~\cite{ref:tukey:1949} ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
 Descriptive and critical difference plots are then retrieved from these results to provide visual aid.
@@
 Most underlying mathematical functions are reused from the Tensorflow library, however, all \index{heuristic}heuristics are implemented from first principles to fit the \acs{HH} framework that was developed.
-The source code and data for this dissertation is provided and made public at \url{https://github.com/arneschreuder/masters.ai}.
+The source code and data for this dissertation is provided and made public at \url{https://github.com/arneschreuder/masters}.
 
@@
 All experiments were run on the Centre for High Performance Computing (CHPC) cluster.
-A total of 14 different server were used, each running 24-56 cores and 256GB of memory.
-The entire empirical process took 6 days.
+A total of 14 different server were used, each running 24 to 56 cores and 256GB of memory.
+The entire empirical process took six days.
 
@@
 
-This chapter provided the detail around the methodology that is used to execute the empirical process.
+This chapter provided the detail around the methodology that was used to execute the empirical process.
 The datasets, \acp{FFNN} and \index{heuristic}heuristics that are used during the empirical process have been presented in detail, along with details around various \acs{BHH} configurations.

### 2022-11-28 dissertation/chapters/08-results.tex
♻️ (chapters 6 and 8): Restore
🚧 (final-review): Chapter 7 WIP

--- 2022-11-20 dissertation/chapters/08-results.tex
@@
 Three variants of the \acs{BHH} are included in these results.
-These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.
+These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes \acp{MH} in the \index{heuristic pool}heuristic pool.
 
@@
 Detailed discussions and illustrations follow.
-As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of meta-heuristics.
+As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of \acp{MH}.
 Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics (denoted bhh\_mh).
@@
 If reselection occurs too frequently these exponentially averaged state parameters do not yield smooth update steps.
-This is further supported by the inclusion of meta-heuristics such as \acp{GA} and \acs{DE}, which recombine state parameters.
+This is further supported by the inclusion of \acp{MH} such as \acp{GA} and \acs{DE}, which recombine state parameters.
 

### 2022-11-28 dissertation/chapters/09-conclusion.tex
🚧 (final-review): Chapter 7 WIP

@@
 \begin{quotation}
-      \noindent ``I am sorry to have made such a long speech, but I did not have time to make a shorter one.''
+      ``I am sorry to have made such a long speech, but I did not have time to make a shorter one.''
 \end{quotation}
@@
 Furthermore, this chapter provides a summary of the results and findings from the empirical process and provides future research opportunities.
-The remainder of the chapter is structured as follows.
+The remainder of the chapter is structured as follows:
 
@@
 As such, the \acs{BHH} was conceptualised.
-The research objectives were defined and are summarised as follows.
+The research objectives were defined and are summarised as follows:
 
@@
 
-It was mentioned that the \acs{BHH}, implemented in this dissertation, does not implement a move-acceptance strategy that rejects heuristic progressions if they do not improve on the current best solution.
+It was mentioned that the \acs{BHH}, implemented in this dissertation, does not implement a move acceptance strategy that rejects heuristic progressions if they do not improve on the current best solution.
 Throughout the presentation of empirical results, it is recommended that this technique be investigated and implemented in further research.
@@
 Minor divergence of the training loss is observed as the \acs{BHH} explores other heuristics in an attempt to improve performance.
-Since no move-acceptance strategy, and no early stopping stategy was used, the \acs{BHH} could select heuristics that are sub-optimal.
+Since no move acceptance strategy, and no early stopping stategy was used, the \acs{BHH} could select heuristics that are sub-optimal.
 Future research opportunities should incorporate these aforementioned strategies.
@@
 
-Throughout the presentation of the empirical results, it is mentioned that a move-acceptance strategy can be incorporated to reject \index{heuristic}heuristic progressions that do not improve on the current best solution found.
+Throughout the presentation of the empirical results, it is mentioned that a move acceptance strategy can be incorporated to reject \index{heuristic}heuristic progressions that do not improve on the current best solution found.
 This would eliminate any divergence in the training process as a result of selecting sub-optimal \index{heuristic}heuristics.
-Various different move-acceptance strategies can be developed and empirically tested.
+Various different move acceptance strategies can be developed and empirically tested.
 
@@
 
-Similar to the move-acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to hault the training process if the performance does not improve for a number of steps.
+Similar to the move acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to hault the training process if the performance does not improve for a number of steps.
 In this dissertation, a number of examples were presented where divergence of training loss occurred.
@@
 
-All the source code, data, logs and analyses that were used in this dissertation, as well as the dissertation source itself, can be found at \url{https://github.com/arneschreuder/masters.ai}.
+All the source code, data, logs and analyses that were used in this dissertation, as well as the dissertation source itself, can be found at \url{https://github.com/arneschreuder/masters}.
 The raw empirical data is made available on Google Cloud's BigQuery platform, under the project id \textit{masters-363209}.

### 2022-11-28 dissertation/chapters/07-methodology.tex
✨ (final-review): Chapter 7 Done

@@
 Evaluation takes place at every mini-batch step.
-Due to the stochastic nature of the experiments, each experiment is repeated over a number of runs to provide sufficient sample for statistical certainty about the outcome of the results.
+Due to the stochastic nature of the experiments, each experiment is repeated over 30 independent runs to provide sufficient sample for statistical certainty about the outcome of the results.
 Each run contains a different random seed, such that each run is unique.
@@
 These results are analysed for statistical significance, from which findings and conclusions are then made.
-The null hypothesis is then either rejected or verified based on these findings.
+The null hypothesis is then either rejected or accepted based on these findings.
 
-Details around each of these elements are provided in the following sections and lead with discussions around the datasets that are used.
+Details around each of these elements are provided in the following sections.
 
@@
 The architecture of a model is dependent on the dataset being trained on, the type of optimisation problem, the number of input dimensions and the number of output dimensions.
-The number of hidden layers were determined empirically.
+The number of hidden layers used were determined empirically.
 Weights are initialised by means of \index{Glorot uniform sampling}Glorot uniform sampling~\cite{ref:glorot:2010}.
@@
 Each of these low-level \index{heuristic}heuristics are implemented as standalone \index{heuristic}heuristics and are also included in the \index{heuristic pool}heuristic pool of the \acs{BHH}.
-Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level \index{heuristic}heuristics that are used as well as their hyper-parameter configuration.
+Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level \index{heuristic}heuristics that are used as well as their hyper-parameter configurations.
 
@@
       \centering
-      \caption{Low-level \index{heuristic}heuristics and their hyper-parameter configuration.}
+      \caption{Low-level \index{heuristic}heuristics and their hyper-parameter configurations.}
       \label{tab:methodology:heuristics}%
@@
 These loss functions are used to measure the performance of the \acp{FFNN} being trained.
-In this dissertation, \acf{BinXE} is used for classification problems with two classes and \acf{SparseCatXE} is used for classification problems with more than two classes.
-For the classifications problems accuracy is also measured.
+In this dissertation, \acs{BinXE} is used for classification problems with two classes and \acs{SparseCatXE} is used for classification problems with more than two classes.
+For the classification problems, accuracy is also measured.
 Accuracy refers to the proportion of correct classifications.
-For regression problems, the \acf{RMSE} is used as a performance metric.
+For regression problems, the \acs{RMSE} is used as a performance metric.
 
@@
 For this dissertation, the \textit{maximum epoch} stopping condition is used, where a fixed, maximum number of training steps and epochs are executed and training is not haulted until the maximum number of epochs have been reached.
+\acp{FFNN} are trained for a maximum of 30 epochs.
 Early stopping is a technique where training is stopped when the \index{heuristic}heuristic is not able to improve the performance of the \acs{FFNN} for a number of steps.
@@
 The behavioural case study is meant to provide an introductory analysis of the inner workings of the \acs{BHH} and includes analysis of the selection mechanism, as well as the perturbative nature of the \acs{BHH}.
-The behavioural case study is not meant to be statistically analysed, but to rather provide a detailed visual analysis of a number of hand-picked example runs, to determine if the \acs{BHH} is behaving as expected.
-From these observations, it is determined if the \acs{BHH} is learning and that selection is indeed biasing towards better performance.
+The behavioural case study is used to determine if the \acs{BHH} is learning and that selection is indeed biasing towards better performance.
 These observations also provide an opportunity to observe the outcome of the perturbative nature of the \acs{BHH}, which includes proxied \index{heuristic}heuristic update step operations.
@@
 The results from each of these experimental groups are statistically analysed.
-To ensure that there are sufficient samples for statistical analysis, each experiment and configuration is trained for 30 epochs and is repeated over 30 runs, for each of the 15 datasets.
+To ensure that there are sufficient samples for statistical analysis, each experiment and configuration is trained for 30 epochs and is repeated over 30 runs, for each of the fourteen datasets.
 The experimental results contain performance evaluation data for the training and testing datasets, and includes loss and accuracy measurements.

### 2022-11-29 dissertation/chapters/03-heuristics.tex
🚧 (final-review): Chapter 8 WIP

@@
 
-The update step for \acs{GD} by means of \acs{BP} can be formulated as is shown in Equations~\eqref{eq:heuristics:gd:update_step_part_1}-\eqref{eq:heuristics:gd:update_step_part_4}.
+The update step for \acs{GD} by means of \acs{BP} can be formulated as is shown in Equations~\eqref{eq:heuristics:gd:update_step_part_1} to \eqref{eq:heuristics:gd:update_step_part_4}.
 The general weight update step is given as

### 2022-11-29 dissertation/chapters/07-methodology.tex
🚧 (final-review): Chapter 8 WIP

@@
 This section provides the stopping conditions that are used during the empirical process.
-For this dissertation, the \textit{maximum epoch} stopping condition is used, where a fixed, maximum number of training steps and epochs are executed and training is not haulted until the maximum number of epochs have been reached.
+For this dissertation, the \textit{maximum epoch} stopping condition is used, where a fixed, maximum number of training steps and epochs are executed and training is not halted until the maximum number of epochs have been reached.
 \acp{FFNN} are trained for a maximum of 30 epochs.

### 2022-11-29 dissertation/chapters/08-results.tex
🚧 (final-review): Chapter 8 WIP

@@
 The last step in the scientific process requires the presentation of the outcomes of the empirical process.
-Objective discussions based on statistical analysis of the findings is required.
+Objective discussions based on statistical analysis of the findings are required.
 The design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}.
@@
 The output of the statistical analysis that yielded the results is provided in Appendix~\ref{app:statistical_analysis}.
-The remainder of the chapter is structured as follows.
+The remainder of the chapter is structured as follows:
 
@@
 This section provides a brief discussion on the general outcome of the empirical process as a whole.
-Overall the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets.
+Overall, the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets.
 In general, the \acs{BHH} performs well and the empirical process provides key insights into the workings of the \acs{BHH}.
@@
 All of the underlying \acp{FFNN} trained in the empirical process are relatively small.
-As such, most of the training progress is observed to occur withing the first five epochs.
+As such, most of the training progress is observed to occur within the first five epochs.
 As a result, the \acs{BHH} should apply most learning at the early stages of the training process.
@@
 These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all.
-This section is structured as follows.
+This section is structured as follows:
 
@@
 This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}.
-Figures~\ref{fig:results:case_study:metrics:train_loss}-\ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test, loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
+Figures~\ref{fig:results:case_study:metrics:train_loss} to \ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
 
@@
       \par\bigskip
-      \caption{The average train and test, loss and accuracy plots over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+      \caption{The average train and test loss and accuracy plots over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
       \label{fig:results:case_study:metrics}
@@
 
-The volatility observed in Figure~\ref{fig:results:case_study:metrics:test_loss} is due to overfitting and partly due to the noisiness that results from mini-batch training.
-Early stopping can be applied to the training process to hault training before the model overfits on the training data.
+The volatility and minor divergence of the test loss compared to the training loss, observed in Figure~\ref{fig:results:case_study:metrics:test_loss}, is due to overfitting and partly due to the noisiness that results from mini-batch training.
+Early stopping can be applied to the training process to halt training before the model overfits on the training data.
 The training dataset is also very small, with just 120 samples.
-As such, overfitting can be expected.
+Furthermore, a very small batch size of 16 is used.
+As such, noisiness and overfitting can be expected.
 
@@
 The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of selection probabilities}.
-Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at index 0, 6, 7, and 8 respectively.
-Index 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool.
+Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
+Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool.
 Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
@@
 
-The first logical observation to be made from Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
+The first logical observation to be made from Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
 Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
@@
 The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}.
-Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.
+Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly than other heuristics that do not perform well.
 
@@
 Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process.
-In a case where all five entities in the entity pool are allocated the same heuristic, for all ten samples defined in the performance log, defined by the replay window size, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.
+Consider a case where all five entities in the entity pool are allocated the same heuristic and that a the replay window size of 10 is used.
+For all ten samples defined in the performance log, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.
 
 Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning.
-The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurance} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
+The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
 \index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
@@
 
-Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of the \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
+Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of the \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
 These illustrations are presented in log scale.
-Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at index 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool.
+Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at indices 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool.
 Once again, simular illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
@@
 
-From the illustrations presented in Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8}, a clearer picture off the learning process of the \acs{BHH} is formed.
+From the illustrations presented in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed.
 The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}.
@@
 The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yield the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
-However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ gets reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.
+However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ is reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.
 
@@
 
-It should be noted that, despite using the same random seed across configurations for the same run number, after about 30 steps, the behavioural changes between the configurations start the show.
-As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing \index{heuristic}heuristics and thus, where the bhh\_baseline and bhh\_replay\_250 configurations diverge from the behaviour of the bhh\_credit\_symmetric configuration.
-The difference in behaviour is proof of the effect of performance bias.
+It should be noted that, despite using the same random seed across configurations for the same run number, the behavioural changes between the configurations start to show after about 30 steps.
+As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing \index{heuristic}heuristics.
+Where the bhh\_baseline and bhh\_replay\_250 configurations then diverge from the behaviour of the bhh\_credit\_symmetric configuration is proof of the effect of performance bias.
 
@@
 
-This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities}, that result from the probabilistic model implemented by the \acs{BHH}.
+This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}.
 The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
 
-Figures~\ref{fig:results:case_study:p_H:0}-\ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at index 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
+Figures~\ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
 Similar to before, these illustrations are also presented in log scale.
@@
 Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10.
-These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8} for the probabilities of \index{heuristic}heuristic selection probabilities.
+These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the probabilities of \index{heuristic}heuristic selection probabilities.
 As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
@@
 
-Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities at index 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
+Figures~\ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
 Similar to before, these illustrations are also presented in log scale.
@@
       \par\bigskip
-      \caption{The average proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at index 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
+      \caption{The average proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
 The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
@@
 
-The main observation to make from Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8}, is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
-The reasons for the aforementioned, is because the probablistic model, is evaluated proportionaly as was discussed in Chapter~\ref{chap:bhh}.
+The main observation to make from Figures~\ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
+The reasons for the aforementioned is because the probablistic model is evaluated proportionaly as was discussed in Chapter~\ref{chap:bhh}.
 As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
 
-Another observation to make, is for the bhh\_replay\_250 configuration $(\textcolor{green}{green})$.
-From Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8}, it can be seen that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities, later in the training stages.
-The aforementioned suggests that the \acs{BHH} is not able to find anymore performance biases and can not exploit better solutions.
+Another observation to make is for the bhh\_replay\_250 configuration $(\textcolor{green}{green})$.
+Figures~\ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} show that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities later in the training stages.
+The aforementioned suggests that the \acs{BHH} is not able to find anymore performance biases and cannot exploit better solutions.
 At this point, the \acs{BHH} starts to explore more as the concentration parameters are reanalysed more uniformly, resolving more and more to a random search in attempt to find better solutions.
 
-Furthermore, the posterior heuristic selection probability distribution is conditional on the occurance of a specific entity that the potential \index{heuristic}heuristic will be applied to, as well as a specific performance criteria enforced by a specific credit assignment strategy.
+Furthermore, the posterior heuristic selection probability distribution is conditional on the occurrence of a specific entity that the potential \index{heuristic}heuristic will be applied to, as well as a specific performance criterion enforced by a specific credit assignment strategy.
 This means that \index{heuristic}heuristic selection is specific to each entity.
@@
 
-From the observations made in Sections~\ref{sec:results:case_study:performance_metrics}-\ref{sec:results:case_study:posterior_selec_prob}, it can be concluded that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset.
-Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases and thus, the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.
+It can be concluded from Sections~\ref{sec:results:case_study:performance_metrics} to \ref{sec:results:case_study:posterior_selec_prob} that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset.
+Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases, and thus the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.
 
@@
 
-From Table~\ref{tab:results:standalone:metrics:loss} it can be seen that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
+Table~\ref{tab:results:standalone:metrics:loss} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
 The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.
@@
 Firstly, both \acs{Adam} and \acs{RMSProp} achieved radically different average ranks for the student performance dataset, compared to the other datasets.
-This can also be see in Table~\ref{tab:results:standalone:metrics:rank}.
+This can also be seen in Table~\ref{tab:results:standalone:metrics:rank}.
 Further investigation into the reasons for this is required as both these heuristics perform well on all other datasets, and the other heuristics perform well for the student performance dataset.
-A suggestions then leads to the possibility that an invalid learning rate or learning rate schedule leads to a scenario where good solutions are overshot, causing \acs{Adam} and \acs{RMSProp} to struggle to resolve back to good solutions.
+A suggestion is that an invalid learning rate or learning rate schedule leads to a scenario where good solutions are overshot, causing \acs{Adam} and \acs{RMSProp} to struggle to resolve back to good solutions.
 Furthermore, the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
@@
       \includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
-      \caption{Critical difference plots for the average ranks of all low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
+      \caption{Critical difference plots for the average ranks of all low-level \index{heuristic}heuristics compared to three \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
       \label{fig:results:standalone:descriptive:cd}
@@
 Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all \index{heuristic}heuristics is very small.
-Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, was statistically only outperformed overall by \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}.
+Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, is statistically only outperformed overall by \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}.
 It should be noted that the standalone low-level \index{heuristic} \index{heuristic}heuristics already produce good results in general across all datasets.
@@
 
-Figures~\ref{fig:results:standalone:figures:iris}-\ref{fig:results:standalone:figures:bank} provide example illustrations of the train and test, loss and accuracy plots for each heuristic as it relates to a selection of classification datasets.
-The train and test, loss and accuracy plots provided are illustrated in log scale.
+Figures~\ref{fig:results:standalone:figures:iris} to \ref{fig:results:standalone:figures:bank} provide example illustrations of the train and test loss and accuracy plots for each heuristic as it relates to a selection of classification datasets.
+The train and test loss and accuracy plots provided are illustrated in log scale.
 The other classification datasets are left out for brevity as they produce similar illustrations.
@@
 
-Figures~\ref{fig:results:standalone:figures:fish_toxicity}-\ref{fig:results:standalone:figures:parkinsons} provide example illustrations of the train and test loss plots for each heuristic as it relates to a selection of regression datasets.
+Figures~\ref{fig:results:standalone:figures:fish_toxicity} to \ref{fig:results:standalone:figures:parkinsons} provide example illustrations of the train and test loss plots for each heuristic as it relates to a selection of regression datasets.
 The train and test loss plots provided are illustrated in log scale.
@@
 
-Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides an illustration of the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the \index{heuristic pool}heuristic pool experimental group.
+Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides an illustration of the train and test loss and accuracy plots for an example classification dataset (abalone) as it relates to the \index{heuristic pool}heuristic pool experimental group.
 As before, the illustrations are provided in log scale and illustrations for the other classification datasets are left out for brevity as they yield similar illustrations.
@@
 
-Figure~\ref{fig:results:population:descriptive:descriptive}, shows the correlation of performance with population size for each dataset.
+Figure~\ref{fig:results:population:descriptive:descriptive} shows the correlation of performance with population size for each dataset.
 From these illustrations, it can be seen that the correlation between the population size configuration and performance is different for each dataset, suggesting that the population size hyper-parameter is problem specific.
@@
 Figure~\ref{fig:results:population:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each population size configuration as it relates to all datasets, across all independent runs and epochs.
-It is shown that there is no overall statistical significant difference between population sizes and thus, it can be concluded that the population size hyper-parameter is problem specific.
+It is shown that there is no overall statistical significant difference between population sizes, and thus it can be concluded that the population size hyper-parameter is problem specific.
 
@@
 
-Similar to before, Figure~\ref{fig:results:population:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the population size experimental group.
+Similar to before, Figure~\ref{fig:results:population:figures:mushroom} provides the train and test loss and accuracy plots for an example classification dataset (mushroom) as it relates to the population size experimental group.
 As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:population:figures:mushroom}
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the student performance dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the student performance dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:population:figures:student_performance}
@@
 
-Similar to before, Figure~\ref{fig:results:credit:figures:bank} provides the train and test, loss and accuracy plots for an example classification dataset (bank) as it relates to the credit assignment strategy experimental group.
+Similar to before, Figure~\ref{fig:results:credit:figures:bank} provides the train and test loss and accuracy plots for an example classification dataset (bank) as it relates to the credit assignment strategy experimental group.
 As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the bank dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the bank dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:credit:figures:bank}
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the housing dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the housing dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:credit:figures:housing}
@@
 Most of the gradient-based \index{heuristic}heuristics that are included in the \index{heuristic pool }heuristic pool implement exponentially averaged state parameters in order to produce smooth update steps.
-If reselection occurs too frequently these exponentially averaged state parameters do not yield smooth update steps.
+If reselection occurs too frequently, these exponentially averaged state parameters do not yield smooth update steps.
 This is further supported by the inclusion of \acp{MH} such as \acp{GA} and \acs{DE}, which recombine state parameters.
 
-Finally, it should be noted that the default reanalysis interval is ten and the default replay window size is also ten.
+Finally, it should be noted that the default reanalysis interval is 10 and the default replay window size is also ten.
 At every reanalysis interval, the concentrations for low-level \index{heuristic}heuristics are reset to the default, symmetrical value of 1.0.
@@
 It can be seen that a general pattern occurs for almost all datasets that show an inverse correlation between performance and the reselection interval.
-Some exceptions of this relationship can be observed for the iris and diabetic datasets where an average reselection interval yielded the best results.
+Some exceptions to this relationship can be observed for the iris and diabetic datasets where an average reselection interval yielded the best results.
 
@@
 
-Similar to before, Figure~\ref{fig:results:reselection:figures:car} provides the train and test, loss and accuracy plots for an example classification dataset (car) as it relates to the reselection interval experimental group.
+Similar to before, Figure~\ref{fig:results:reselection:figures:car} provides the train and test loss and accuracy plots for an example classification dataset (car) as it relates to the reselection interval experimental group.
 As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the car dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the car dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:reselection:figures:car}
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the bike dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the bike dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:reselection:figures:bike}
@@
 
-Tables \ref{tab:results:replay:metrics:loss} and \ref{tab:results:replay:metrics:rank} shows that there is no clear overall best performing replay window size configuration of the \acs{BHH}, for all datasets.
+Tables \ref{tab:results:replay:metrics:loss} and \ref{tab:results:replay:metrics:rank} show that there is no clear overall best performing replay window size configuration of the \acs{BHH} for all datasets.
 In some cases, a replay window size of one yielded the best results.
 A replay window of one simply considers the last step in the training process.
-This means that memory of past performance actually had a negative impact on the training process in those particular cases.
+This means that memory of past performance actually had a negative impact on the training process for those particular cases.
 It should also be observed that the largest replay window size yielded the worst performance overall and also for the most datasets.
@@
 
-Figure~\ref{fig:results:replay:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different replay window size configurations, per dataset.
+Figure~\ref{fig:results:replay:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different replay window size configurations per dataset.
 
@@
 
-Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test, loss and accuracy plots for an example classification dataset (diabetic) as it relates to the replay window size experimental group.
+Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test loss and accuracy plots for an example classification dataset (diabetic) as it relates to the replay window size experimental group.
 As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:replay:figures:diabetic}
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:replay:figures:fish_toxicity}
@@
 
-Tables \ref{tab:results:reanalysis:metrics:loss} and \ref{tab:results:reanalysis:metrics:rank} shows that there is no clear overall best performing reanalysis interval configuration of the \acs{BHH} for all datasets.
+Tables \ref{tab:results:reanalysis:metrics:loss} and \ref{tab:results:reanalysis:metrics:rank} show that there is no clear overall best performing reanalysis interval configuration of the \acs{BHH} for all datasets.
 
@@
 Furthermore, the reanalysis interval configurations should also be considered along with the replay window size, as the replay window size determines the number of performance log samples to reanalyse.
-For the \acs{BHH} baseline configuration, the reselection and reanalysis interval hyper-parameters have default values of ten, and the replay window size also has a default value of ten.
+For the \acs{BHH} baseline configuration, the reselection and reanalysis interval hyper-parameters have default values of 10, and the replay window size also has a default value of 10.
 These values are deliberately chosen so that there is a balance between the different hyper-parameters from which empirical conclusions can be made.
@@
 
-Similar to before, Figure~\ref{fig:results:reanalysis:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the reanalysis interval experimental group.
+Similar to before, Figure~\ref{fig:results:reanalysis:figures:mushroom} provides the train and test loss and accuracy plots for an example classification dataset (mushroom) as it relates to the reanalysis interval experimental group.
 As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:reanalysis:figures:mushroom}
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:reanalysis:figures:parkinsons}
@@
 
-The divergence that can be seen in Figure~\ref{fig:results:reanalysis:figures:loss:train:mushroom} and \ref{fig:results:reanalysis:figures:loss:test:mushroom} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results, when an optimal solution has already been found.
+The divergence that can be seen in Figure~\ref{fig:results:reanalysis:figures:loss:train:mushroom} and \ref{fig:results:reanalysis:figures:loss:test:mushroom} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results when an optimal solution has already been found.
 As mentioned before, an early stopping strategy as well as a move-acceptance strategy can be incorporated to avoid this effect.
@@
 From Table \ref{tab:results:burn_in:metrics:loss} a noticeable pattern can be observed.
-Generally it is found that a small burn in window size produces better results than larger burn in window sizes.
+Generally, it is found that a small burn in window size produces better results than larger burn in window sizes.
 The largest burn in window size of 20 produced the worst results in nine out of thirteen datasets.
 Some exceptions include the mushroom and the iris datasets.
-Notice that burn in window sizes smaller than the default reanalysis interval, reselection interval and replay window size of ten, generally produced the best results.
+Notice that burn in window sizes smaller than the default reanalysis interval, reselection interval and replay window size of 10, generally produced the best results.
 However, Table \ref{tab:results:burn_in:metrics:loss} does not provide a clear view of the overall performance produced by different burn in window size configurations for the entire training process.
@@
 Note that the \acs{BHH} is configured with a reselection interval of one, until the burn in window has been exhausted, after which the actual reselection interval applies.
-That means that reselection occurs at each step during the burn in window, but the reanalysis interval and replay window size remain intact.
+This means that reselection occurs at each step during the burn in window, but the reanalysis interval and replay window size remain intact.
 This observation agrees with previous results, where the \acs{BHH} prefers to start exploiting \index{heuristic}heuristics and solutions as soon as possible.
@@
 Figure~\ref{fig:results:burn_in:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the burn in window size configurations, per dataset.
-From Figure~\ref{fig:results:burn_in:descriptive:descriptive} is can be seen that there is mostly a linear correlation between performance results and burn in window sizes, with minor exceptions to some datasets.
+Figure~\ref{fig:results:burn_in:descriptive:descriptive} shows that there is mostly a linear correlation between performance results and burn in window sizes, with minor exceptions to some datasets.
 
@@
 
-Figure~\ref{fig:results:burn_in:descriptive:cd} shows with statistical certainty that a small burn in configuration of the \acs{BHH} generally produce overall better results than larger burn in configurations, as it relates to all datasets,
-
-Similar to before, Figure~\ref{fig:results:burn_in:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the burn in window size experimental group.
+Figure~\ref{fig:results:burn_in:descriptive:cd} shows with statistical certainty that a small burn in configuration of the \acs{BHH} generally produce overall better results than larger burn in configurations, as it relates to all datasets.
+
+Similar to before, Figure~\ref{fig:results:burn_in:figures:mushroom} provides the train and test loss and accuracy plots for an example classification dataset (mushroom) as it relates to the burn in window size experimental group.
 As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:burn_in:figures:mushroom}
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:burn_in:figures:parkinsons}
@@
 However, a better suggestion can be made from the observation of previous results.
-The \acs{BHH} has a default replay window size of ten, yielding a small window of memory to maintain \index{heuristic}heuristic performance evidence in the performance log.
+The \acs{BHH} has a default replay window size of 10, yielding a small window of memory to maintain \index{heuristic}heuristic performance evidence in the performance log.
 Normalisation of the concentration parameters then yield an insignificant difference in the outcome as the concentration parameters never reach high values.
@@
 
-Similar to before, Figure~\ref{fig:results:normalise:figures:abalone} provides the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the normalisation experimental group.
+Similar to before, Figure~\ref{fig:results:normalise:figures:abalone} provides the train and test loss and accuracy plots for an example classification dataset (abalone) as it relates to the normalisation experimental group.
 As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the abalone dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the abalone dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:normalise:figures:abalone}
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the bike dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the bike dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:normalise:figures:bike}
@@
 Table \ref{tab:results:discounted_rewards:metrics:rank} shows that, in general, there is no obvious difference in the outcomes of the \acs{BHH} when discounted rewards is enabled or disabled.
-Although this could suggestion that the discounted rewards hyper-parameter is problem specific, a better suggestion supports the findings from Section \ref{sec:results:normalise} that suggest that manipulation of the outcomes of the concentration parameters yield insignificant differences in the outcomes of performance, as a small replay window size of ten, is used by default.
+Although this could suggest that the discounted rewards hyper-parameter is problem specific, a better suggestion supports the findings from Section \ref{sec:results:normalise}.
+These findings suggest that manipulation of the concentration parameters yield insignificant differences in the outcomes of performance, as a small replay window size of 10 is used by default.
 
@@
 
-Similar to before, Figure~\ref{fig:results:discounted_rewards:figures:wine_quality} provides the train and test, loss and accuracy plots for an example classification dataset (wine quality) as it relates to the discounted rewards experimental group.
+Similar to before, Figure~\ref{fig:results:discounted_rewards:figures:wine_quality} provides the train and test loss and accuracy plots for an example classification dataset (wine quality) as it relates to the discounted rewards experimental group.
 As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the wine quality dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the wine quality dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:discounted_rewards:figures:wine_quality}
@@
       \par\bigskip
-      \caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the housing dataset over 30 epochs, illustrated in log scale.}
+      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the housing dataset over 30 epochs, illustrated in log scale.}
       \label{fig:results:discounted_rewards:figures:housing}

### 2022-11-29 dissertation/chapters/09-conclusion.tex
🚧 (final-review): Chapter 8 WIP

@@
 
-Chapters \ref{chap:anns}-\ref{chap:probability} provided the reader with the relevant background information that is necessary to develop the novel \acs{BHH}.
+Chapters \ref{chap:anns} to \ref{chap:probability} provided the reader with the relevant background information that is necessary to develop the novel \acs{BHH}.
 Chapter~\ref{chap:anns} provided background information on \acp{ANN}.
@@
 
-Similar to the move acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to hault the training process if the performance does not improve for a number of steps.
+Similar to the move acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to halt the training process if the performance does not improve for a number of steps.
 In this dissertation, a number of examples were presented where divergence of training loss occurred.

### 2022-11-29 dissertation/chapters/08-results.tex
🚧 (final-review): Chapter 8, before distribution changes
🚧 WIP

@@
 Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
-The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of selection probabilities}.
+The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of \index{heuristic}heuristic selection probabilities}.
 Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
@@
 
-\subsection{Probabilities of Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
-
-This section provides a detailed investigation into the \textit{probabilities of selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process.
+\subsection{Probabilities of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
+
+This section provides a detailed investigation into the \textit{probabilities of \index{heuristic}heuristic selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process.
 As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves.
@@
 
-Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of the \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
+Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
 These illustrations are presented in log scale.
-Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at indices 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool.
+Indices 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of \index{heuristic}heuristic selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool.
 Once again, simular illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
@@
       \caption{The average sampled probabilities of \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
-The probabilities of the \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+The probabilities of \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
       \label{fig:results:case_study:thetas}

### 2022-11-29 dissertation/chapters/08-results.tex
✨ (plots): Larger fonts
🚧  (final-review): Chapter 8  - almost done

@@
 This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}.
-The probabilistic model implements \textit{probabilities of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.
+The probabilistic model implements \textit{probability distributions of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.
 
@@
 
-      \item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probabilities of \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.
+      \item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probability distribution of \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.
 
@@
 
-\subsection{Probabilities of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
-
-This section provides a detailed investigation into the \textit{probabilities of \index{heuristic}heuristic selection probabilities}, denoted by $\boldsymbol{\theta}$, as it changes throughout the training process.
+\subsection{Probability Distribution of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
+
+This section provides a detailed investigation into the \textit{probability distribution of \index{heuristic}heuristic selection probabilities} as it changes throughout the training process.
 As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves.
-The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, and the prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
-
-Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
+The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.
+
+Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
 These illustrations are presented in log scale.
-Indices 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of \index{heuristic}heuristic selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool.
-Once again, simular illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
+Indices 0, 6, 7, and 8 represent the distribution of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of \index{heuristic}heuristic selection probabilities in $\boldsymbol{\theta}$.
+Similar illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
 
@@
       \par\bigskip
-      \caption{The average sampled probabilities of \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
-The probabilities of \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+      \caption{The average sampled \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
+The \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
       \label{fig:results:case_study:thetas}
@@
 The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}.
-As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected probability of \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modeling.
-
-Towards the end of the training process, the probability of \index{heuristic}heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a probability of \index{heuristic}heuristic selection probability of 0.1, for all \index{heuristic}heuristics.
+As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected mean \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modeling.
+
+Towards the end of the training process, the \index{heuristic}heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a \index{heuristic}heuristic selection probability of 0.1, for all \index{heuristic}heuristics.
 This can be explained as follows: most of the training progress is made in the early stages of the training process, and training converges towards the end of the training process.
@@
 Another observation to make occurs in the first 30 steps of the training process.
-In Figure~\ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same probabilities of \index{heuristic}heuristic selection probabilities in these first 30 steps.
+In Figure~\ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same \index{heuristic}heuristic selection probabilities in these first 30 steps.
 This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number.
@@
 
-Furthermore, the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, with means not equal to the expected probabilities of \index{heuristic}heuristic selection probabilities of 0.1, observed for small windows, at various steps for multiple runs, is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations.
+Furthermore, it can be observed for small windows, at various steps for multiple runs, that the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, do not yield means that are equal to the expected \index{heuristic}heuristic selection probabilities of 0.1.
+This is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations.
 This is also true for the bhh\_credit\_symmetric configuration, as the bhh\_credit\_symmetric configuration biases towards heuristics that happen to be sampled, despite not biasing towards good performance.
@@
 This can be attributed to a very small reanalysis window combined with a small replay window size of 10, that contains very few samples to learn from.
-A small reanalysis interval and a small replay window size allows for more exploration of the \index{heuristic}heuristic space, but can also yield greater variance of the probabilities of \index{heuristic}heuristic selection probabilities.
+A small reanalysis interval and a small replay window size allows for more exploration of the \index{heuristic}heuristic space, but can also yield greater variance of the \index{heuristic}heuristic selection probabilities.
 Once again, any differences then in the behaviour of the bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations and biases by the bhh\_baseline configuration.
@@
 The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
-
-Figures~\ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
+As such, $P(\boldsymbol{H} \vert \boldsymbol{\theta}) = \boldsymbol{\theta}$ and heuristics are initially sampled such that $\boldsymbol{H} \sim Cat(\boldsymbol{\theta})$.
+
+Figures~\ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
 Similar to before, these illustrations are also presented in log scale.
@@
       \par\bigskip
-      \caption{The average sampled prior \index{heuristic}heuristic selection probabilities, given the probabilities of \index{heuristic}heuristic selection probabilities, denoted by $\boldsymbol{H}$, at indices 0, 6, 7, and 8.
-The prior \index{heuristic}heuristic selection probabilities are sampled from the prior \index{heuristic}heuristic selection probability distribution, denoted $P(\boldsymbol{H} \vert \theta)$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+      \caption{The average prior \index{heuristic}heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8.
+The prior \index{heuristic}heuristic selection probabilities are sampled from the probability distribution of \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
       \label{fig:results:case_study:p_H}
@@
 
-The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the probabilities of \index{heuristic}heuristic selection probabilities presented in the previous section in Figure~\ref{fig:results:case_study:thetas}.
+The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure~\ref{fig:results:case_study:thetas}.
 This is because of the \textit{reselection} interval hyper-parameter.
@@
 Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10.
-These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the probabilities of \index{heuristic}heuristic selection probabilities.
+These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of \index{heuristic}heuristic selection probabilities.
 As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
@@
 These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}.
-The posterior \index{heuristic}heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the generalised vector of credit allocation outcomes as implemented by the credit assignment strategy.
-Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probabilities of \index{heuristic}heuristic selection probabilities and probabilities of entity selection probabilities respectively.
-Finally, $\boldsymbol{\psi}$ represents the generalised form of the probabilities of successful credit allocation probabilities.
-Since this dissertation implements credit allocation operations that yield discrete, binary outcomes, $\boldsymbol{\psi}$ can be used interchangeably by $\gamma_{0}$ and $\gamma_{1}$, where $\gamma_{0}$ represents the probabilities of failed credit allocation probabilities and $\gamma_{1}$ represents the probabilities of successful credit allocation probabilities.
+The posterior \index{heuristic}heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy.
+Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of \index{heuristic}heuristic selection probabilities and the entity selection probabilities respectively.
+Finally, $\boldsymbol{\psi}$ represents the probability distribution of successful credit allocation probabilities.
 
@@
       \par\bigskip
-      \caption{The average proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy.
-The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+      \caption{The average calculated proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, ($c_{1}$), from the \textit{ibest} credit assignment strategy.
+The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
       \label{fig:results:case_study:p_HgEC:0}

### 2022-11-29 dissertation/chapters/08-results.tex
✨ (final-review): Results Done

@@
 
-The \acs{BHH} does not implement a move acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution.
+The \acs{BHH} does not implement a move-acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution.
 In some cases the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.
@@
 For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions.
-The \acs{BHH} does not incorporate a \textit{move acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set.
-A move acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.
+The \acs{BHH} does not incorporate a \textit{move-acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set.
+A move-acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.
 
@@
 Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
-The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of \index{heuristic}heuristic selection probabilities}.
+The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{\index{heuristic}heuristic selection probabilities}.
 Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
@@
       \par\bigskip
-      \caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0,6,7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+      \caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
       \label{fig:results:case_study:alphas}
@@
 This interval is defined by the \textit{reanalysis interval} hyper-parameter.
-The reanalysis interval dictates the frequency at which Bayesian analysis is conducated on the performance log, mainted by the \acs{BHH}.
+The reanalysis interval dictates the frequency at which Bayesian analysis is conducted on the performance log, mainted by the \acs{BHH}.
 Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval.
@@
 Consider a case where all five entities in the entity pool are allocated the same heuristic and that a the replay window size of 10 is used.
-For all ten samples defined in the performance log, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.
+Then for all ten samples defined in the performance log, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.
 
@@
 Both the bhh\_baseline (\textcolor{red}{red}) and the bhh\_replay\_250 (\textcolor{green}{green}) configurations make use of the \textit{ibest} credit assignment strategy.
-The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yield the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
+The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yields the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
 However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ is reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.
@@
       \par\bigskip
-      \caption{The average calculated proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, ($c_{1}$), from the \textit{ibest} credit assignment strategy.
+      \caption{The average calculated proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, $c_{1}$, from the \textit{ibest} credit assignment strategy.
 The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
@@
 This experimental group utilises the same three variants of the \acs{BHH} as was utilised in Section \ref{sec:results:standalone}, but provides an opportunity to look at the \acs{BHH} \index{heuristic pool}heuristic pool hyper-parameter in more depth.
-These variants are denoted as follows.
-The \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics is denoted as \textit{all}, the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics is denoted as \textit{gd}, and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics is denoted as \textit{mh}.
+These variants are denoted as follows: The \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics is denoted as \textit{all}, the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics is denoted as \textit{gd}, and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics is denoted as \textit{mh}.
 
@@
 
-Figures~\ref{fig:results:reselection:figures:loss:train:car} and ~\ref{fig:results:reselection:figures:loss:train:bike} both show a smooth decline in training loss for all reselection interval configurations of the \acs{BHH}, but larger reselection interval configurations are able to provide better results than lower reselection intervals.
+Figures~\ref{fig:results:reselection:figures:loss:train:car} and \ref{fig:results:reselection:figures:loss:train:bike} both show a smooth decline in training loss for all reselection interval configurations of the \acs{BHH}, but larger reselection interval configurations are able to provide better results than lower reselection intervals.
 This further supports the suggestion that exploitation of low-level \index{heuristic}heuristics is more important than exploration of low-level \index{heuristic}heuristics in this particular case.
@@
 
-\begin{figure}[htbp]
+\begin{figure}[htb]
       \begin{subfigure}{0.5\textwidth}

### 2022-11-30 dissertation/chapters/09-conclusion.tex
✨ (final-review): Chapter 9 Done

--- 2022-11-22 dissertation/chapters/09-conclusion.tex
@@
 
-This chapter provides a summary of the research that is done in this dissertation.
+This chapter provides a summary of the research that was done in this dissertation.
 The research objectives were set out in Chapter \ref{chap:introduction} and are concluded in this chapter.
 Furthermore, this chapter provides a summary of the results and findings from the empirical process and provides future research opportunities.
-The remainder of the chapter is structured as follows.
+The remainder of the chapter is structured as follows:
 
 \begin{itemize}
-      \item \textbf{Section \ref{sec:conclusion:research_goals}} provides a summary of the research intent and provides a review of the problem statement, objectives and motivations behind the research.
+      \item \textbf{Section \ref{sec:conclusion:research_goals}} provides a summary of the research intent and provides a review of the problem statement, objectives, and motivations behind the research.
 
@@
 
-      \item \textbf{Section \ref{sec:conclusion:further_research}} presents future research opportunities.
+      \item \textbf{Section \ref{sec:conclusion:further_research}} provides suggestions for future research opportunities.
 
@@
 
-This section briefly reviews the problem statement, motivations and research objectives that was set out in Chapter \ref{chap:introduction} of this dissertation.
+This section briefly reviews the problem statement, motivations, and research objectives that was set out in Chapter \ref{chap:introduction} of this dissertation.
 
@@
 \acp{HH} have been shown to provide a general solution to the \index{heuristic}heuristic selection process.
-The benefit that such an approach provides, is that it automates the \index{heuristic}heuristic selection process.
+The benefit that such an approach provides is that it automates the \index{heuristic}heuristic selection process.
 This approach saves researchers time and potentially produce a solution that could generalise to multiple problems.
@@
 As such, the \acs{BHH} was conceptualised.
-The research objectives were defined and are summarised as follows.
+The research objectives were defined and were addressed as follows:
 
 \begin{itemize}
-      \item Conduct literature studies on all related topics that are relevant to the development of the \acs{BHH}.
-These include \acs{ANN}, existing low-level \index{heuristic}heuristics, meta-learning, \acp{HH}, probability theory and Bayesian statistics.
+      \item A literature study was conducted on all related topics that are relevant to the development of the \acs{BHH} and is provided in Chapters ~\ref{chap:anns} to \ref{chap:probability}.
+The literature study included background information on \acs{ANN}, existing low-level \index{heuristic}heuristics, meta-learning, \acp{HH}, probability theory, and Bayesian statistics.
+Detailed discussions were provided on every topic and was supported by visual illustrations and mathematical derivations.
 
-      \item Develop a novel \acs{BHH} that can be used to automate the \index{heuristic}heuristic selection process.
+      \item A novel \acs{BHH} that can be used to automate the \index{heuristic}heuristic selection process was proposed in detail and was implemented.
 The \acs{BHH} follows an approach that includes a selective and perturbative element in an online learning setting.
-Bayesian statistics and \acs{MAP} is used as the optimisation technique.
-Furthermore, the \acs{BHH} implements a mapping for proxied \index{heuristic}heuristic state update operations, whereby \index{heuristic}heuristic state is maintained by outsourcing state opertations to relevant low-level \index{heuristic}heuristics.
+Bayesian statistics and \acs{MAP} is used as the optimisation technique and detailed mathematical derivations of the optimisation process was provided.
+Detailed discussions were provided on the mapping of proxied \index{heuristic}heuristic state update operations.
+Finally, a \acs{BHH} baseline configuration was defined as a cornerstone reference for empirical analysis.
 
-      \item Conduct an empirical study to show that the \ac{BHH} is able to train \acp{FFNN} effectively on a number of different datasets.
+      \item An empirical process was desiged and the detail of the implementation for the empirical process and the \acs{BHH} was provided.
 
-      \item Conduct an empirical study to study the behavioural characteristics of the \acs{BHH}.
+      \item An empirical study was conducted to show that the \ac{BHH} is able to train \acp{FFNN} effectively on a number of different datasets.
 
-      \item Conduct an empirical study to critically evaluate the performance of the \acs{BHH} compared to traditional, low-level, standalone \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.
+      \item An empirical study was conducted to study the behavioural characteristics of the \acs{BHH}.
 
-      \item Conduct an empirical study to evaluate variants of the \acs{BHH} to study the impact of various hyper-parameters on the outcomes of the \ac{BHH}.
+      \item An empirical study was conducted to critically evaluate the performance of the \acs{BHH} compared to traditional, low-level, standalone \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.
 
-      \item Provide and discuss the findings of the results produced by the empirical process. The results are analysed for statistical significance.
+      \item An empirical study was conducted to evaluate variants of the \acs{BHH} to study the impact of various hyper-parameters on the outcomes of the \ac{BHH}.
+
+      \item Results from the empirical process were statistically analysed over multiple runs and provided statistical significance.
+These results were discussed in detail and was supported through visual illustrations.
 \end{itemize}
 
-The research objectives set out in this dissertation are extensive.
-Each of these research objectives have been successfully executed.
-From the findings made in this dissertation, many different opportunities for future research are identified.
+The research objectives set out in this dissertation were extensive.
+Each of these research objectives have been successfully executed as indicated in the list above.
+From the findings made in this dissertation, many different opportunities for future research were identified.
 
@@
 Chapter~\ref{chap:heuristics} provided background information on various low-level heuristics that are designed to train \acp{FFNN}.
-A number of gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics were presented in detail.
+A number of gradient-based \index{heuristic}heuristics and \acp{MH} were presented in detail.
 Chapter~\ref{chap:hhs} provided background information and literature reviews on \acp{HH}.
@@
 Entity and \index{heuristic}heuristic state and state-manipulation formed the cornerstone of this topic.
-Perturbation of \index{heuristic}heuristics and solutions is achieved through a technique that deconstructs \index{heuristic}heuristics into their initialisation and update steps.
-The update operations for each heuristic was derived as movement equations borrowed from the field of physics.
+Perturbation of \index{heuristic}heuristics and solutions are achieved through a technique that deconstructs \index{heuristic}heuristics into their initialisation and update steps.
+The update operations for each heuristic were derived as movement equations borrowed from the field of physics.
 This technique allows for the proxying of update step operations as they are required by different \index{heuristic}heuristics.
@@
 Each one of the empirical tests is referred to as an experimental group.
-Various experimental groups have been identified and are listed below.
+Various experimental groups have been identified and are listed below:
 
@@
       \item An experimental group that provides a case-study on the behaviour of the \ac{BHH} as it relates to training of a \acs{FFNN} on an example dataset (iris), in order to understand the workings of the \acs{BHH}, and to determine if the \acs{BHH} is able to successfully train \acp{FFNN}.
-Three different configurations of the \acs{BHH} configuration was implemented.
+Three different configurations of the \acs{BHH} configuration were implemented.
 This includes the default \acs{BHH} baseline configuration, the \acs{BHH} baseline configuration where the replay window size is set to 250, and the \acs{BHH} baseline configuration which utilises the \textit{symmetric} credit assignment strategy.
@@
 Three different \index{heuristic pool}heuristic pool configurations were implemented.
-These configurations include a configuration with all the low-level \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool, a configuration with only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration with only \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool.
+These configurations include a configuration with all the low-level \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool, a configuration with only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration with only \acp{MH} in the \index{heuristic pool}heuristic pool.
 
@@
 
-This section provides a summary of the results obtained from each of the experimental groups that were executed. This section is structured as follows.
+This section provides a summary of the results obtained from each of the experimental groups that were executed. This section is structured as follows:
 
@@
 Detailed analysis was provided for various state parameters maintained by the \acs{BHH}.
-These include the concentration parameters for different heuristics, probabilities of \index{heuristic}heuristic selection probabilities, prior heuristic selection probabilities and posterior heuristic selection probabilities.
+These include the concentration parameters for different heuristics, the probability distribution of \index{heuristic}heuristic selection probabilities, prior heuristic selection probabilities and posterior heuristic selection probabilities.
 It was shown that the \ac{BHH} is able to learn and that the \acs{BHH} is able to exploit small performance biases as it relates to \index{heuristic}heuristic selection.
@@
 
-The main findings that were made for this experimental group are given as follows.
-Most of the training progression is made in the early stages of the training process.
+The main findings that were made for this experimental group are given as follows: Most of the training progression is made in the early stages of the training process.
 That leads to the conclusion that the \acs{BHH} has a small window from which it should learn and gain the most in the training process.
@@
 The \textit{bhh\_all} configuration included all low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool.
-The \textit{bhh\_gd} configuration included only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the \textit{bhh\_mh} configuration included only \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool.
+The \textit{bhh\_gd} configuration included only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the \textit{bhh\_mh} configuration included only \acp{MH} in the \index{heuristic pool}heuristic pool.
 
-Overall the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen \index{heuristic}heuristics that were implemented and executed on fourteen datasets.
+Overall, the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen \index{heuristic}heuristics that were implemented and executed on fourteen datasets.
 The \textit{bhh\_gd} configuration produced performance results close to that of the best low-level \index{heuristic}heuristics and was only statistically outperformed by the top two low-level \index{heuristic}heuristics.
@@
 Although the \textit{bhh\_gd} configuration produced performance results comparable to the best low-level heuristics, the \textit{bhh\_all} and \textit{bhh\_mh} configurations produced average results.
-It was found that, in general, gradient-based heuristics produced the best results, as such, it it understandable that the \textit{bhh\_gd}  yielded the best performance outcomes between the different \acs{BHH} variants that were implemented.
+It was found that, in general, gradient-based heuristics produced the best results, as such, it is understandable that the \textit{bhh\_gd}  yielded the best performance outcomes between the different \acs{BHH} variants that were implemented.
 Although the \acs{BHH} variants were not able to produce better results than the top low-level \index{heuristic}heuristics, the \acs{BHH} variants still effectively trained the underlying \acp{FFNN} and produced good training outcomes overall.
@@
 
-For this experimental group, the same three \index{heuristic pool}heuristical pool variants, as outlined for the \acs{BHH} behavioural case study, was implemented.
+For this experimental group, the same three \index{heuristic pool}heuristical pool variants as outlined for the \acs{BHH} behavioural case study, was implemented.
 These variants are denoted as \textit{all}, \textit{gd}, and \textit{mh}.
@@
 However, overall it was shown that the population size hyper-parameter is problem specific.
-Illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
+Illustrations of the train and test loss and accuracy plots for some example datasets were provided.
 Some divergence in training loss was observed and was attributed to selection of \index{heuristic}heuristics that yield sub-optimal results after an optimal solution has already been found.
-As before, a move acceptance strategy and an early stopping strategy can be incorporated to avoid this effect.
+As before, a move-acceptance strategy and an early stopping strategy can be incorporated to avoid this effect.
 
@@
 No clear overall difference in performance was observed for the various credit assignment strategies.
-In the majority of cases, a particular non-symmetric credit assignment strategy yielded the best performance, while the \textit{symmetric} credit assignment strategy yielded the best performance results in one case.
+For the majority of cases, a particular non-symmetric credit assignment strategy yielded the best performance, while the \textit{symmetric} credit assignment strategy yielded the best performance results in one case.
 It can therefore be concluded that the credit assignment strategy is problem specific.
-As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
+As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
 
@@
 Therefore, a conclusion that can be made is that \index{heuristic}heuristic and solution exploitation is preferred over exploration.
-As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
+As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
 
@@
 The relationship between the reselection interval, replay window size and reanalysis interval was discussed, and it was shown that these hyper-parameters should be considered together.
-As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
+As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
 
@@
 Overall, no statistically significant difference was found for the performance of the reanalysis intervals across all datasets, and thus, it was concluded that the reanalysis interval is problem specific.
-As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
+As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
 
@@
 The lower burn in window sizes generally produced the best results in the majority of cases, with some exceptions that prefer average burn in window sizes.
-As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
+As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
 
@@
 A configuration is included with normalisation enabled and a configuration is included with normalisation disabled.
-It was concluded that the default replay window size of ten is too small to yield a significant difference in performance outcome for when normalisation is enabled compared to when normalisation is disabled.
-As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
+It was concluded that the default replay window size of 10 is too small to yield a significant difference in performance outcome for when normalisation is enabled compared to when normalisation is disabled.
+As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
 
@@
 A configuration is included with discounted rewards enabled and a configuration is included with discounted rewards disabled.
-Similar to the findings for the experimental group investigating the effects of the normalisation hyper-parameter, it was concluded that the default replay window size of ten is too small to yield a significant difference in performance outcome for when discounted rewards is enabled compared to when discounted rewards is disabled.
-As before, illustrations of the train and test, loss and accuracy plots for some example datasets were provided.
+Similar to the findings for the experimental group investigating the effects of the normalisation hyper-parameter, it was concluded that the default replay window size of 10 is too small to yield a significant difference in performance outcome for when discounted rewards is enabled compared to when discounted rewards is disabled.
+As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
 
@@
 
-\subsubsection{Move Acceptance Strategies}
+\subsubsection{Move-Acceptance Strategies}
 \label{sec:conclusion:further_research:move_acceptance}
@@
 
-Similar to the move-acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to hault the training process if the performance does not improve for a number of steps.
+Similar to the move-acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to halt the training process if the performance does not improve for a number of steps.
 In this dissertation, a number of examples were presented where divergence of training loss occurred.
@@
 
-\subsubsection{Continuous Valued Credit Allocation}
+\subsubsection{Continuous-Valued Credit Allocation}
 \label{sec:conclusion:further_research:continuous_credit}
@@
 It was shown that there is a relationship between the reselection interval, the replay window size and the reanalysis interval.
-These hyper-parameters provide an mechanism for trade-off between exploration and exploitation and therefore, investigation into dynamic selection of hyper-parameter values can be considered in future research.
+These hyper-parameters provide a mechanism for trade-off between exploration and exploitation and therefore, investigation into dynamic selection of hyper-parameter values can be considered in future research.
 
@@
 This chapter provided a summary of the research intent, providing a brief review of the research problem, motivations and objectives defined for this dissertation.
-A brief summary of the background information that is covered in this dissertation is provided.
-A brief summary on the concept and implementation of the novel \acs{BHH} is provided, followed by a brief summary of the methodology that is used for the empirical process.
+A brief summary of the background information that was covered in this dissertation was provided.
+A brief summary on the concept and implementation of the novel \acs{BHH} was provided, followed by a brief summary of the methodology that was used for the empirical process.
 This chapter also provided brief summaries of the results and findings for each of the experimental groups that were executed in the empirical process.
-Future research opportunities were identified and reference is made to materials and assets used in this dissertation that are made available online.
+Future research opportunities were identified and reference was made to materials and assets used in this dissertation that was made available online.

### 2022-11-30 dissertation/appendix/datasets.tex
💚 Dedicated to Taylah, Beané and Aleah

\chapter{Datasets}
\label{app:datasets}

This appendix provides insight into the preparation and usage of datasets that were used as part of the empirical process. The section is structured as follows:

\begin{itemize}
	\item \textbf{Section \ref{app:datasets:overview}} provides an overview of the data processing that was executed on each dataset.

	\item \textbf{Section \ref{app:datasets:example}} provides an example data processing script for the iris dataset. The same approach was followed for all datasets.
\end{itemize}

\section{Overview}\label{app:datasets:overview}

This section provides a brief overview of all the data processing operations that were executed on all datasets. The data processing tasks included:

\begin{itemize}
	\item Exploratory analysis and visualisation off data distribution.

	\item Dropping of rows that contain missing data in and standardisation of data types.

	\item Normalising all numerical features using the \index{standard score scaler}standard score scaler and one-hot encoding of all categorical features.

	\item Splitting the datasets into a training set (80\%) and a testing set (20\%) and then shuffling and batching of data.
\end{itemize}

\section{Example}\label{app:datasets:example}

This section provides an example data processing script that was used for the iris dataset. All the datasets used in this dissertation follow the same data processing principles.

\includepdf[pages=-]{attachments/iris.pdf}

### 2022-12-05 dissertation/chapters/08-results.tex
🐛 (derived-publications): Removed redundant entries and small technical fix

@@
 To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
-Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
+Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichlet probability distribution}Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
 The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{\index{heuristic}heuristic selection probabilities}.

### 2022-12-05 dissertation/appendix/datasets.tex
✨ (review): Spelling and grammar, derived publications fix

@@
 
-This appendix provides insight into the preparation and usage of datasets that were used as part of the empirical process. The section is structured as follows:
-
-\begin{itemize}
-	\item \textbf{Section \ref{app:datasets:overview}} provides an overview of the data processing that was executed on each dataset.
-
-	\item \textbf{Section \ref{app:datasets:example}} provides an example data processing script for the iris dataset. The same approach was followed for all datasets.
-\end{itemize}
+This appendix provides insight into the preparation and usage of datasets that were used as part of the empirical process.
+Section \ref{app:datasets:overview} provides an overview of the data processing that was executed on each dataset.
 
@@
 \end{itemize}
-
-\section{Example}\label{app:datasets:example}
-
-This section provides an example data processing script that was used for the iris dataset. All the datasets used in this dissertation follow the same data processing principles.
-
-\includepdf[pages=-]{attachments/iris.pdf}

### 2022-12-05 dissertation/chapters/01-introduction.tex
✨ (final-review): Chapter 9 Done
✨ (review): Spelling and grammar, derived publications fix

@@
 A search algorithm known as a \index{heuristic}\textit{heuristic}~\cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \acs{ANN}, such that a specified objective function is minimised.
-The research presented in this disseration focuses on the development of a specific type of heuristic, called a \acf{HH} to train \acp{FFNN} in a supervised learning approach.
+The research presented in this dissertation focuses on the development of a specific type of heuristic, called a \acf{HH} to train \acp{FFNN} in a supervised learning approach.
 
@@
 
-This section provides the reader with a brief summary of the research field and outlines key concepts that contribute to the topics discussed in this disseration.
+This section provides the reader with a brief summary of the research field and outlines key concepts that contribute to the topics discussed in this dissertation.
 
@@
 
-\citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} mentioned that \acp{HH} have been shown to solve a number of problems including bin-packing, examination timetabling, production scheduling, the traveling salesman problem, vehicle routing problem and many more.
+\citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} mentioned that \acp{HH} have been shown to solve a number of problems including bin-packing, examination timetabling, production scheduling, the travelling salesman problem, vehicle routing problem and many more.
 
@@
 Careful, systematic selection is thus required to find and select the best heuristic to train \acp{FFNN}.
-In the past, researchers selected the best heuristic by trail and error.
+In the past, researchers selected the best heuristic by trial and error.
 A set of heuristics and carefully selected hyper-parameters would be implemented, followed by an empirical test to evaluate the performance of each heuristic for a given problem domain~\cite{ref:pillay:2015}.
@@
 
-      \item \textbf{Appendix~\ref{app:symbols}} lists and defines the mathematical symbols used in this work, categorised according to the relevant chapter in which they appear.
-
       \item \textbf{Appendix~\ref{app:acronyms}} provides a list of the important acronyms used or newly defined in the course of this work, as well as their associated definitions.

### 2022-12-05 dissertation/chapters/02-artificial-neural-networks.tex
✨ (review): Spelling and grammar, derived publications fix

@@
 
-The \acs{AN} implements a nonlinear mapping from $\mathbb{R}^{I}$ to
+The \acs{AN} implements a non-linear mapping from $\mathbb{R}^{I}$ to
 $\mathbb{R}^{T}$, usually in the ranges $[0,1]$ or $[-1,1]$, depending on the
@@
 Normalisation and scaling yields input data that is comparable to the output produced by the \acs{AN}.
-For the purposes of this disseration, the \index{min-max scaler}min-max scaler~\cite{ref:al:2006} and the \index{standard score scaler}standard score scaler~\cite{ref:jain:2005} are considered.
+For the purposes of this dissertation, the \index{min-max scaler}min-max scaler~\cite{ref:al:2006} and the \index{standard score scaler}standard score scaler~\cite{ref:jain:2005} are considered.
 
@@
 
-The connection strength that synapses in the \acs{BN} have is modeled in the \acs{AN} as weight vectors of numerical values associated with each dimension of the input.
+The connection strength that synapses in the \acs{BN} have is modelled in the \acs{AN} as weight vectors of numerical values associated with each dimension of the input.
 Weights can either dampen or strengthen the input by some negative or positive numerical value.
@@
 In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
-Depending on the optimisation algorithm used, error correction information can be ``backpropagated'' through the network.
+Depending on the optimisation algorithm used, error correction information can be propagated backwards through the network.
 An illustration of a \acs{FFNN} is given in Figure~\ref{fig:ffnn} below.
@@
 \index{overfitting}Overfitting describes a scenario where the trained \acs{FFNN} performs well on training data, but does not generalise well to never before seen data from the test set~\cite{ref:tetko:1995, ref:geron:2017}.
-Geron~\cite{ref:geron:2017} describes \index{overfitting}overfitting as the case where \acs{FFNN} is too complex relative to the noisiness of the training data.
+\citeauthor{ref:geron:2017}~\cite{ref:geron:2017} describes \index{overfitting}overfitting as the case where \acs{FFNN} is too complex relative to the noisiness of the training data.
 
@@
 Underfitting describes a scenario where the \acs{FFNN} is not able to effectively learn the underlying structure of the training data~\cite{ref:tetko:1995, ref:geron:2017}.
-Geron~\cite{ref:geron:2017} describe underfitting as the case where the \acs{FFNN} is too simple relative to the underlying structure of the training data.\\
+\citeauthor{ref:geron:2017}~\cite{ref:geron:2017} describe underfitting as the case where the \acs{FFNN} is too simple relative to the underlying structure of the training data.\\
 \\

### 2022-12-05 dissertation/chapters/03-heuristics.tex
💚 Dedicated to Taylah, Beané and Aleah
✨ (review): Spelling and grammar, derived publications fix

@@
 Optimisation is the task of finding a solution to a given problem that is better than alternative solutions.
-Better stated by Oldewage~\cite{ref:oldewage:2017}, optimisation is the task of finding values for a set of variables such that some measure of optimality is satisfied given a set of constraints.
-Engelbrecht~\cite{ref:engelbrecht:2007} breaks optimisations problems down into three components:
+Better stated by \citeauthor{ref:oldewage:2017}~\cite{ref:oldewage:2017}, optimisation is the task of finding values for a set of variables such that some measure of optimality is satisfied given a set of constraints.
+\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} breaks optimisations problems down into three components:
 
@@
 As stated in Chapter~\ref{chap:anns}, the training of an \acp{FFNN} is a particular type of optimisation problem, where the goal is to find the configuration of \textit{weights}, such that the \acs{FFNN} yields output that minimises some loss function.
-The mechanism by which the optimal weights for a \acs{FFNN} is sough out, is executed by an \index{optimisation algorithm}optimisation algorithm known as a \index{heuristic}heuristic.
+The mechanism by which the optimal weights for a \acs{FFNN} is sought out, is executed by an \index{optimisation algorithm}optimisation algorithm known as a \index{heuristic}heuristic.
 
@@
 \index{meta-heuristic}Meta-heuristics are useful when there is imperfect information about the search space~\cite{ref:bianchi:2009}, and are generally less problem-specific than other classes of \index{heuristic}heuristics~\cite{ref:blum:2003}.
-This disseration takes a particular interest in gradient-based \index{heuristic}heuristics and \acp{MH}.
+This dissertation takes a particular interest in gradient-based \index{heuristic}heuristics and \acp{MH}.
 
@@
       \includegraphics[width=0.75\textwidth]{images/gradient_descent.pdf}
-      \caption{An illustration of \acf{GD} over various timesteps showing the minimisation of the error with regards to weight value.}
+      \caption{An illustration of \acf{GD} over various time steps showing the minimisation of the error with regards to weight value.}
       \label{fig:heuristics:gd:gd_illustration}
@@
 \begin{itemize}
-      \item \textbf{Feedforward Pass}: During this phase the output values of the \acs{FFNN} is calculcated for each training pattern.
+      \item \textbf{Feedforward Pass}: During this phase the output values of the \acs{FFNN} is calculated for each training pattern.
 
@@
 
-where $w_{i}$ is the weight value at index $i$, $t$ is the timestep, $\Delta w_{i}(t)$ is the weight update vector at index $i$ and timestep $t$. The delta weight term $\Delta w_{i}(t)$, is given as
+where $w_{i}$ is the weight value at index $i$, $t$ is the time step, $\Delta w_{i}(t)$ is the weight update vector at index $i$ and time step $t$. The delta weight term $\Delta w_{i}(t)$, is given as
 
@@
 where $\eta$ is the learning rate and $\frac{\partial \epsilon}{\partial w_{i}}$ is the \textit{gradient} of the error, as a result of a loss function $\mathcal{E}$, relative to the weight at index $i$.
-The learning rate controls the step-size that is taken in the direction of the negative gradient at each timestep.
+The learning rate controls the step-size that is taken in the direction of the negative gradient at each time step.
 Assuming the use of \acs{SSE} as the loss function, the partial derivative of $\epsilon$, relative to the weight $w$, at index $i$, is given as
@@
 
-\begin{algorithm}[H]
-      \caption{The pseudo code algorithm for the generic \acf{GD} heuristic.}
+\begin{algorithm}[htb]
+      \caption{The pseudo-code algorithm for the generic \acf{GD} heuristic.}
       \label{algo:heuristics:gd:gd}
       \begin{algorithmic}
-            \State Initialise the \acs{FFNN} weights and biases, the learning rate $\eta$ and the timestep/epoch $T=0$;
+            \State Initialise the \acs{FFNN} weights and biases, the learning rate $\eta$ and the time step/epoch $T=0$;
             \While{stopping conditions are not met}
@@
 where $\boldsymbol{w}$ refers to the weight vector, $\eta$ refers to the learning rate as before and $\boldsymbol{g}$ refers to the gradient of the error function relative to weight vector.
-Note that some subscripts related to layers, indices, timesteps and training patterns are omitted for convenience.
+Note that some subscripts related to layers, indices, time steps and training patterns are omitted for convenience.
 
@@
 As such, weight updates are done with high variance and noise~\cite{ref:ruder:2016}.
-An illustration of the the fluctuations caused by \acs{SGD} during training is given in Figure~\ref{fig:heuristics:gd:sgd}.
+An illustration of the fluctuations caused by \acs{SGD} during training is given in Figure~\ref{fig:heuristics:gd:sgd}.
 
@@
       \item It is difficult to avoid getting trapped in local minima, especially for highly non-convex loss functions used for training \acp{FFNN}.
-\citeauthor{ref:dauphin:2014}~\cite{ref:dauphin:2014} mentions the role of sadle points in getting trapped in local minima.
-Sadle points are points at which one dimensions slopes upwards, while another dimension slopes downwards.
-\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that these sadle points are usually surrounded by plateaus of the same error, leading to gradients that are close to zero in all dimensions.
+\citeauthor{ref:dauphin:2014}~\cite{ref:dauphin:2014} mentions the role of saddle points in getting trapped in local minima.
+Saddle points are points at which one dimensions slopes upwards, while another dimension slopes downwards.
+\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that these saddle points are usually surrounded by plateaus of the same error, leading to gradients that are close to zero in all dimensions.
 \end{itemize}
@@
 
-\Acs{Momentum} ~\cite{ref:qian:1999} is a variant of \acs{SGD} that helps accelerate \acs{SGD} in the relevant direction, dampening oscillations.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$, of the weight update vector of the previous timestep to the current weight update vector.
+\Acs{Momentum} ~\cite{ref:qian:1999} is a variant of \acs{SGD} that helps accelerate \acs{SGD} in the relevant direction, dampening oscillations.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$, of the weight update vector of the previous time step to the current weight update vector.
 An illustration of \acs{SGD} with and without momentum is given in Figure~\ref{fig:heuristics:gd:sgd_with_and_without_momentum}.
@@
 
-\Acf{Adagrad} is an adaptation of \acs{SGD} that implements a learning rate for every element in the weight vector and is developed by Duchi et al.~\cite{ref:duchi:2011}.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that \acs{Adagrad} adapts the learning rate to the elements of the weight vector, by  performing small updates (i.e.
+\Acf{Adagrad} is an adaptation of \acs{SGD} that implements a learning rate for every element in the weight vector and is developed by \citeauthor{ref:duchi:2011}~\cite{ref:duchi:2011}.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that \acs{Adagrad} adapts the learning rate to the elements of the weight vector, by  performing small updates (i.e.
 low learning rates) for weights associated with frequently occurring features and larger updates (i.e.
@@
 In the \acs{GD} variants presented thus far, the weight updates have been applied by making use of the same learning rate $\eta$, for all elements of the weight update vector.
-\Acs{Adagrad} uses a different learning rate for every weight element $w_{i}$, at every timestep $t$.
+\Acs{Adagrad} uses a different learning rate for every weight element $w_{i}$, at every time step $t$.
 The weight update step for \acs{Adagrad} is given as
@@
 where $w_{i}$ is the $i$-th element of the weight vector, $G_{t,ii} \in \mathbb{R}^{d \times d}$ is a diagonal matrix where each diagonal element $i,i$, is the sum of the squared gradients w.r.t.
-$w_{i}$, up to timestep $t$ and $\epsilon$ is a smoothing term that avoids division by zero and is set to an insignificant value such as $1 \times 10^{-8}$.
+$w_{i}$, up to time step $t$ and $\epsilon$ is a smoothing term that avoids division by zero and is set to an insignificant value such as $1 \times 10^{-8}$.
 Since $\boldsymbol{G_{t}}$ contains the sum of the squares of the gradients along its diagonal, the weight update step can be vectorised and updated using the matrix-vector product, represented by $\odot$, between $G_{t,i}$ and $g_{t,i}$.
@@
 
-Zeiler~\cite{ref:zeiler:2012} presents \acs{Adadelta}, an improvement of \acs{Adagrad} that eliminates the accumulation of squared gradients in the denominator.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that instead of accumulating all past squared gradients as in the case of \acs{Adagrad}, \acs{Adadelta} restricts the window of accumulation to a window with a fixed size $W$.
+\citeauthor{ref:zeiler:2012}~\cite{ref:zeiler:2012} presents \acs{Adadelta}, an improvement of \acs{Adagrad} that eliminates the accumulation of squared gradients in the denominator.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that instead of accumulating all past squared gradients as in the case of \acs{Adagrad}, \acs{Adadelta} restricts the window of accumulation to a window with a fixed size $W$.
 However, storing $W$ previous squared gradients is very inefficient.
 Instead, the accumulation of gradients over $W$ steps is defined recursively as a decaying average of all past squared gradients.
-The moving average of squared gradients at timestep $t$, denoted by $E[\boldsymbol{g}^{2}]_{t}$  depends on a fraction $\alpha$ of the previous average of squared gradients and the current gradient, similar to the update step for \acs{Momentum}.
+The moving average of squared gradients at time step $t$, denoted by $E[\boldsymbol{g}^{2}]_{t}$  depends on a fraction $\alpha$ of the previous average of squared gradients and the current gradient, similar to the update step for \acs{Momentum}.
 Also similar to \acs{Momentum}, $\alpha$ is set to 0.9.
@@
 The weight update vector should have the same hypothetical units as the weight vector.
-To fix the aforemention problem, another exponentially decaying average is defined in terms of squared weight updates and is given as
+To fix the aforementioned problem, another exponentially decaying average is defined in terms of squared weight updates and is given as
 
@@
 
-Note that $RMS[\Delta \boldsymbol{w}]_{t}$ is unknown at timestep $t$.
-$RMS[\Delta \boldsymbol{w}]_{t}$ is approximated with the \acf{RMS} of weight updates until the previous timestep.
+Note that $RMS[\Delta \boldsymbol{w}]_{t}$ is unknown at time step $t$.
+$RMS[\Delta \boldsymbol{w}]_{t}$ is approximated with the \acf{RMS} of weight updates until the previous time step.
 The learning rate in Equation~\eqref{eq:heuristics:gd:adadelta_part_3} is then replaced.
@@
 ~\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} mentions that because $\boldsymbol{m}_{t}$ and $\boldsymbol{v}_{t}$ are initialised to be vectors of 0's, they are biased towards 0.
-The aforementioned bias is especially prominent during the initial timesteps and/or when the decay rates $\beta_{1}$ and $\beta_{2}$ are small ($\beta_{1}$ and $\beta_{2}$ are close to 1).
+The aforementioned bias is especially prominent during the initial time steps and/or when the decay rates $\beta_{1}$ and $\beta_{2}$ are small ($\beta_{1}$ and $\beta_{2}$ are close to 1).
 The bias-corrected first and second moment estimates are presented in Equations~\eqref{eq:heuristics:gd:adam_bc_first_moment} and~\eqref{eq:heuristics:gd:adam_bc_second_moment} respectively.
@@
 The prefix, \textit{meta}, means ``beyond, in an upper level''.
-\Acp{MH} were often called \textit{modern heuristics}~\cite{ref:reeves:1993}.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} mention that there is a debate as to what the formal defintion of \acp{MH} is and suggests the definition of \acp{MH} to be ``high level strategies for exploring search spaces by using different methods''.
+\Acp{MH} were often called \textit{modern heuristics}~\cite{ref:reeves:1993}.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} mention that there is a debate as to what the formal definition of \acp{MH} is and suggests the definition of \acp{MH} to be ``high level strategies for exploring search spaces by using different methods''.
 
@@
 This dissertation uses the term \textit{entity} for candidate solutions and a \textit{population} for a collection of entities, in the general context of population-based \acp{MH}.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that in \acp{PSO} individual candidate solutions are referred to as \textit{particles} and the population is referred to as a \textit{swarm}.
-These particles are ``flown'' through a hyperdimensional search space.
+These particles are ``flown'' through a hyper-dimensional search space.
 Changes in particle position is due to social-psychological tendencies of individuals to emulate the success of other individuals.
 The changes in the particle position are then influenced by the experience or knowledge of the particle's neighbours.
-The social behaviour of particles is modeled such that they stochastically return to previously successful regions in the search space.
+The social behaviour of particles is modelled such that they stochastically return to previously successful regions in the search space.
 
@@
       \item \textbf{Position}: Refers to the candidate solution that is represented by the particle and defines the particle position within the optimisation problem's hyper-dimensional solution space.
-Let the current position vector, for particle $i$, at timestep $t$ be denoted by $\boldsymbol{x}_{i}(t)$.
+Let the current position vector, for particle $i$, at time step $t$ be denoted by $\boldsymbol{x}_{i}(t)$.
 Let $I$ denoted the population size and $J$ denote the search space dimensionality.
 
-      \item \textbf{Velocity}: Represents a step size for the particle in the search space. The velocity at vector, for particle $i$, at timestep $t$ is denoted $\boldsymbol{v}_{i}(t)$.
+      \item \textbf{Velocity}: Represents a step size for the particle in the search space. The velocity at vector, for particle $i$, at time step $t$ is denoted $\boldsymbol{v}_{i}(t)$.
 
@@
 During initialisation, particles are randomly placed within the search space by sampling from a uniform distribution such that $\boldsymbol{x}_{i} \sim U(x_{min}, x_{max})$ and the velocity is set to 0.
-At timestep 0, the particle's initial position is set to be the particle's personal best solution such that $\boldsymbol{y}_{i}(0) = \boldsymbol{x}_{i}(0)$.
+At time step 0, the particle's initial position is set to be the particle's personal best solution such that $\boldsymbol{y}_{i}(0) = \boldsymbol{x}_{i}(0)$.
 The particle's update step is then broken into two parts, including a velocity update step presented in Equation~\eqref{eq:heuristics:pso:velocity} followed by a position update step as presented in Equation~\eqref{eq:heuristics:pso:position}.
@@
 
-~\citeauthor{ref:vanwyk:2014}\cite{ref:vanwyk:2014} mentions that when \acp{PSO} where first developed, it was possible for particle velocities to become inappropriately large during optimisation, leading to situations where particles fly out of the feasible search space.
+\citeauthor{ref:vanwyk:2014}~\cite{ref:vanwyk:2014} mentions that when \acp{PSO} where first developed, it was possible for particle velocities to become inappropriately large during optimisation, leading to situations where particles fly out of the feasible search space.
 This is known as \textit{swarm explosion} and occurs when there are frequent changes in the global best position.
 In order to address this issues, the concept of \textit{velocity clamping} was introduced~\cite{ref:eberhart:1996}.
-The idea behind velocity clamping is to restrict particle velocities to some $V_{max}$ threshold, modeling a form of terminal velocity.
+The idea behind velocity clamping is to restrict particle velocities to some $V_{max}$ threshold, modelling a form of terminal velocity.
 Velocity clamping is applied after the velocity update step and is given in Equation~\eqref{eq:heuristics:pso:velocity_clamping} below.
@@
                   v'_{ij}(t+1) & \text{if } -V_{max,j} < v'_{ij}(t+1) < V_{max,j} \\
-                  -V_{maxj}    & \text{if } v'_{ij}(t+1) \leq -V_{max,j}          \\
-                  V_{maxj}     & \text{if } v'_{ij}(t+1) \geq V_{max,j}
+                  -V_{max,j}   & \text{if } v'_{ij}(t+1) \leq -V_{max,j}          \\
+                  V_{max,j}    & \text{if } v'_{ij}(t+1) \geq V_{max,j}
             \end{cases}
@@
 
-An example of the pseudo code implementation of the \textit{gbest} \acs{PSO} is taken from~\cite{ref:engelbrecht:2007} and is given in Algorithm~\ref{algo:heuristics:pso:gbest}.
-
-\begin{algorithm}[H]
-      \caption{The pseudo code algorithm for the gbest \acs{PSO} heuristic.}
+An example of the pseudo-code implementation of the \textit{gbest} \acs{PSO} is taken from~\cite{ref:engelbrecht:2007} and is given in Algorithm~\ref{algo:heuristics:pso:gbest}.
+
+\begin{algorithm}[htb]
+      \caption{The pseudo-code algorithm for the gbest \acs{PSO} heuristic.}
       \label{algo:heuristics:pso:gbest}
@@
 The \index{mutation}mutation process then follows as such.
-For each each parent $\boldsymbol{x}_{i}(t)$ generate a trial vector $\boldsymbol{u}_{i}(t)$ as follows:
+For each parent $\boldsymbol{x}_{i}(t)$ generate a trial vector $\boldsymbol{u}_{i}(t)$ as follows:
 
@@
 
-\begin{algorithm}[H]
-      \caption{The pseudo code algorithm for the binomial \index{crossover}crossover technique for \acs{DE}.}
+\begin{algorithm}[htb]
+      \caption{The pseudo-code algorithm for the binomial \index{crossover}crossover technique for \acs{DE}.}
       \label{algo:heuristics:de:bin}
@@
 
-\begin{algorithm}[H]
-      \caption{The pseudo code algorithm for the exponential \index{crossover}crossover technique for \acs{DE}.}
+\begin{algorithm}[htb]
+      \caption{The pseudo-code algorithm for the exponential \index{crossover}crossover technique for \acs{DE}.}
       \label{algo:heuristics:de:exp}
@@
 
-\begin{algorithm}[H]
-      \caption{The pseudo code for the general \acs{DE} heuristic.}
+\begin{algorithm}[htbp]
+      \caption{The pseudo-code for the general \acs{DE} heuristic.}
       \label{algo:heuristics:de:general_de}
@@
 Many variants of \acs{DE} have been created and researched~\cite{ref:mezura:2006}.
-A general notation for \acs{DE} heuristic variants have been developed by Storn et al.~\cite{ref:storn:1996, ref:storn:1997}.
+A general notation for \acs{DE} heuristic variants have been developed by \citeauthor{ref:storn:1996}~\cite{ref:storn:1996, ref:storn:1997}.
 The notation follows the form \textit{DE/$x$/$y$/$z$} where $x$, $y$ and $z$ refer to the components that are used by the particular \acs{DE}.
@@
 
-\Acp{GA} where first proposed by Fraser~\cite{ref:fraser:1957} and later by Bremermann~\cite{ref:bremermann:1962} and Reed et al.~\cite{ref:reed:1967}.
+\Acp{GA} where first proposed by \citeauthor{ref:fraser:1957}~\cite{ref:fraser:1957} and later by \citeauthor{ref:bremermann:1962}~\cite{ref:bremermann:1962} and \citeauthor{ref:reed:1967}~\cite{ref:reed:1967}.
 However, Holland~\cite{ref:holland:1992} is widely regarded as the father of \acp{GA}.
@@
 As with other \acp{EA}, \acp{GA} implement a number of operators that drive the optimisation process.
-Primarily, \acp{GA} implement selection, modeling survival of the fittest and \index{crossover}crossover, modeling reproduction.
+Primarily, \acp{GA} implement selection, modelling survival of the fittest and \index{crossover}crossover, modelling reproduction.
 The remainder of this section presents the aforementioned operators in more detail.
@@
 The generic \acs{EC} algorithm is referred to as the canonical \acs{GA} (CGA) and was proposed by Holland~\cite{ref:holland:1992}.
-The generic \acs{EC} algorithm is taken from~\cite{ref:engelbrecht:2007} and is is presented in Algorithm~\ref{algo:heuristics:ga:generic_ec} below.
-
-\begin{algorithm}[H]
-      \caption{The pseudo code for the generic \acs{EC} heuristic.}
+The generic \acs{EC} algorithm is taken from~\cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:ga:generic_ec} below.
+
+\begin{algorithm}[htb]
+      \caption{The pseudo-code for the generic \acs{EC} heuristic.}
       \label{algo:heuristics:ga:generic_ec}
@@
 Uniform \index{crossover}crossover is illustrated in Figure~\ref{fig:heuristics:mh:ga:uniform_crossover} below and the algorithm for uniform \index{crossover}crossover is given in Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover}.
-In Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover}, $p_{x}$ is the bitswapping probability.
+In Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover}, $p_{x}$ is the bit-swapping probability.
 
@@
 
-\begin{algorithm}[H]
-      \caption{The pseudo code for the uniform \index{crossover}crossover operator as used by \acp{GA}.}
+\begin{algorithm}[htb]
+      \caption{The pseudo-code for the uniform \index{crossover}crossover operator as used by \acp{GA}.}
       \label{algo:heuristics:mh:ga:uniform_crossover}
@@
 
-\begin{algorithm}[H]
-      \caption{The pseudo code for the uniform \index{mutation}mutation operator as used by \acp{GA}.}
+\begin{algorithm}[htb]
+      \caption{The pseudo-code for the uniform \index{mutation}mutation operator as used by \acp{GA}.}
       \label{algo:heuristics:mh:ga:uniform_mutation}

### 2022-12-05 dissertation/chapters/04-hyper-heuristics.tex
✨ (review): Spelling and grammar, derived publications fix

@@
 
-A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the \index{heuristic}heuristic characteristics and heaviours used throughout the search process and not just the \index{heuristic}heuristic hyper-parameters.
+A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the \index{heuristic}heuristic characteristics and behaviours used throughout the search process and not just the \index{heuristic}heuristic hyper-parameters.
 This approach focuses on the hybridisation of \index{heuristic}heuristic paradigms.

### 2022-12-05 dissertation/chapters/05-probability.tex
💚 Dedicated to Taylah, Beané and Aleah
✨ (review): Spelling and grammar, derived publications fix

@@
 Probability theory and statistics can be traced back to as early as the 18th century.
-In 1718,~\citeauthor{ref:demoivre:1718}~\cite{ref:demoivre:1718} published the \textit{Doctrine of of Chance}; a book that is widely regarded as the first published book on probability theory.
+In 1718,~\citeauthor{ref:demoivre:1718}~\cite{ref:demoivre:1718} published the \textit{Doctrine of Chance}; a book that is widely regarded as the first published book on probability theory.
 In 1763, Thomas Bayes~\cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of \index{Bayes' theorem}Bayes' theorem was introduced.
@@
 These fields contain many cases that generate observations that cannot be predicted with absolute certainty~\cite{ref:wackerly:2014}.
-Probability can be be inferred and confirmed through past events.
+Probability can be inferred and confirmed through past events.
 These events are referred to as \textit{random} or \textit{stochastic} events.
@@
 The concentration parameters, $\boldsymbol{\alpha}$, are varied.
-The values of the \acs{PDF} are shown by the color maps with contour lines at equal values as indicated in the color bars~\cite{ref:dirichlet:2020}.}
+The values of the \acs{PDF} are shown by the colour maps with contour lines at equal values as indicated in the colour bars~\cite{ref:dirichlet:2020}.}
       \label{fig:probability:probability_distributions:dirichlet}
@@
       \par\bigskip
-      \caption{An illustration of the the coin-flip simulation for different sample sizes that show the convergence of the mean as per the \acf{CLT}.}
+      \caption{An illustration of the coin-flip simulation for different sample sizes that show the convergence of the mean as per the \acf{CLT}.}
       \label{fig:probability:probability_distributions:bernoulli:coin}
@@
 
-\subsection{Multinomial Distribution}
+\subsection{Multinomial Probability Distribution}
 \label{sec:probability:probability_distributions:multinomial}

### 2022-12-05 dissertation/chapters/06-bayesian-hyper-heuristic.tex
✨ (review): Spelling and grammar, derived publications fix

@@
 
-      \item \textbf{position delta}: The last computed position delta between the current timestep and the previous timestep.
+      \item \textbf{position delta}: The last computed position delta between the current time step and the previous time step.
 
@@
 
-      \item \textbf{loss}: A parameter that tracks the loss as achieved by the the entity throughout training.
+      \item \textbf{loss}: A parameter that tracks the loss as achieved by the entity throughout training.
 \end{itemize}
@@
 
-The \acs{BHH} incorporates a form of probabilistic modeling in its selection mechanism.
+The \acs{BHH} incorporates a form of probabilistic modelling in its selection mechanism.
 Probability is calculated based on \index{heuristic}heuristic-entity performance over time.
@@
 In effect, no learning and performance-bias is achieved with the symmetric credit assignment strategy and thus the symmetric credit assignment strategy is implemented as a basis for comparison.
-Comparing a credit assignment staretegy to the symmetric credit assignment indicates the ability of the other credit assignment strategy to have an effect on the learning process and performance of the \acs{BHH}.
+Comparing a credit assignment strategy to the symmetric credit assignment indicates the ability of the other credit assignment strategy to have an effect on the learning process and performance of the \acs{BHH}.
 \end{itemize}
@@
       \item $K$ denote the \index{heuristic pool}heuristic pool size.
-      \item $L$ denote the number of credit assignment output classes. Since the output of credit assignment is boolean, $L = 2$.
+      \item $L$ denote the number of credit assignment output classes. Since the output of credit assignment is Boolean, $L = 2$.
 
@@
 
-This section aims to dissect the probabilistic model that is presented in Equestion~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
+This section aims to dissect the probabilistic model that is presented in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
 The \acs{BHH} implements a form of Naïve Bayes classifier, and thus independence between events can be assumed.
@@
 
-Equations~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}, \eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} and \eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} can be substituded into the proportional evaluation of the predictive model as given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}, resulting in
+Equations~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}, \eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} and \eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} can be substituted into the proportional evaluation of the predictive model as given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}, resulting in
 
@@
 Probabilities might be very low at some points during training.
-Consider an example where training has stagnated, effectively leading to a scenario where a credit assignment strategy never fulfills a credit assignment, yielding an extremely small probability for $\boldsymbol{\psi}$.
+Consider an example where training has stagnated, effectively leading to a scenario where a credit assignment strategy never fulfils a credit assignment, yielding an extremely small probability for $\boldsymbol{\psi}$.
 A solution to the aforementioned problem is to apply the \textit{log-sum-exp} trick.
@@
 The optimisation process, by means of Bayesian analysis, has also been presented.
-Hyper-parameters were discussed in detail and a pseudo code implementation of the \acs{BHH} was presented.
+Hyper-parameters were discussed in detail and a pseudo-code implementation of the \acs{BHH} was presented.
 

### 2022-12-05 dissertation/chapters/07-methodology.tex
✨ (review): Spelling and grammar, derived publications fix

@@
                   parkinsons          & multivariate              & integer, real  & 26                  & 5875               & 256            & 23             & ~\cite{ref:tsanas:2009}   \\
-                  air quality         & multivariate, timeseries & real           & 15                  & 9358               & 256            & 37             & ~\cite{ref:de:2008}       \\
+                  air quality         & multivariate, time series & real           & 15                  & 9358               & 256            & 37             & ~\cite{ref:de:2008}       \\
                   bike                & univariate                & integer, real  & 16                  & 17389              & 256            & 68             & ~\cite{ref:fanaee:2014}   \\
@@
 The baseline configuration is provided and compared to an implementation of a \acs{BHH} configuration where the replay window size is large (250), as well as an implementation of the \acs{BHH} using the \textit{symmetric} credit assignment strategy.
-The large replay window size configuration is to used to show the behaviour of the \acs{BHH} when it has access to a large number of performance log samples, which increases the statistical certainty of the learning outcome.
+The large replay window size configuration is used to show the behaviour of the \acs{BHH} when it has access to a large number of performance log samples, which increases the statistical certainty of the learning outcome.
 The \acs{BHH} configuration that uses the \textit{symmetric} credit assignment strategy is used to illustrate the behaviour of the \acs{BHH} where no performance bias takes place and thus, no learning occurs.

### 2022-12-05 dissertation/chapters/08-results.tex
✨ (review): Spelling and grammar, derived publications fix

@@
 
-Although the different configurations of the \acs{BHH} are all able to succesfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.
+Although the different configurations of the \acs{BHH} are all able to successfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.
 
@@
 The first logical observation to be made from Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
-Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
+Since the replay window size is sufficiently large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
 The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process.
@@
 This interval is defined by the \textit{reanalysis interval} hyper-parameter.
-The reanalysis interval dictates the frequency at which Bayesian analysis is conducted on the performance log, mainted by the \acs{BHH}.
+The reanalysis interval dictates the frequency at which Bayesian analysis is conducted on the performance log, maintained by the \acs{BHH}.
 Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval.
@@
 The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
-\index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
+\index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequently reselect these \index{heuristic}heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
 Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.
@@
 This section provides a detailed investigation into the \textit{probability distribution of \index{heuristic}heuristic selection probabilities} as it changes throughout the training process.
-As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modeling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probablistic distribution themselves.
+As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modelling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probabilistic distribution themselves.
 The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.
@@
 The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}.
-As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected mean \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modeling.
+As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected mean \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modelling.
 
@@
 Similar to before, these illustrations are also presented in log scale.
-As before, illustrations for the other indices are left out for brevity as they yield simular illustrations.
+As before, illustrations for the other indices are left out for brevity as they yield similar illustrations.
 
@@
 The main observation to make from Figures~\ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
-The reasons for the aforementioned is because the probablistic model is evaluated proportionaly as was discussed in Chapter~\ref{chap:bhh}.
+The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Chapter~\ref{chap:bhh}.
 As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
@@
 Figures~\ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} show that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities later in the training stages.
-The aforementioned suggests that the \acs{BHH} is not able to find anymore performance biases and cannot exploit better solutions.
+The aforementioned suggests that the \acs{BHH} is not able to find further performance biases and cannot exploit better solutions.
 At this point, the \acs{BHH} starts to explore more as the concentration parameters are reanalysed more uniformly, resolving more and more to a random search in attempt to find better solutions.
@@
 Table~\ref{tab:results:standalone:metrics:rank} provides the empirical results from Table~\ref{tab:results:standalone:metrics:loss} in ranked format.
-The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, across all datasets, for all indepented runs and all epochs.
+The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, across all datasets, for all independent runs and all epochs.
 The average rank across all epochs produces a view on the performance of the \index{heuristic}heuristics as it relates to the entire training process.
@@
 
-From the normalised average ranks provided in Table~\ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eigth amongst all thirteen \index{heuristic}heuristic implementations respectively.
+From the normalised average ranks provided in Table~\ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen \index{heuristic}heuristic implementations respectively.
 These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.
@@
 
-From Figures~\ref{fig:results:heuristic_pool:descriptive:descriptive} and~\ref{fig:results:heuristic_pool:descriptive:cd}, it is clear that the \textit{gd} configuration configuration performs best overall, with exceptions to the parkinsons and housing datasets, where the \textit{all} and \textit{gd} configurations performed equally well with statistically insignificant differences in their outcomes.
+From Figures~\ref{fig:results:heuristic_pool:descriptive:descriptive} and~\ref{fig:results:heuristic_pool:descriptive:cd}, it is clear that the \textit{gd} configuration performs best overall, with exceptions to the parkinsons and housing datasets, where the \textit{all} and \textit{gd} configurations performed equally well with statistically insignificant differences in their outcomes.
 
@@
 From Table \ref{tab:results:population:metrics:rank} it can be seen that a lower population size of five, mostly produced the best results, with exception to the bike and car datasets, for which the lowest population size configuration produced the worst performance, yielding statistically significant differences in outcomes from the other datasets.
-A larger population size configuration is prefered for the bike and car datasets.
+A larger population size configuration is preferred for the bike and car datasets.
 Furthermore, a population size configuration of ten, slightly higher than the default of five, is preferred for the forest fires and housing datasets.
@@
 A suggestion to this problem is to implement a move-acceptance strategy as was mentioned before.
-At the nineth epoch, the \acs{BHH} fails to produce better solutions on the training set.
+At the ninth epoch, the \acs{BHH} fails to produce better solutions on the training set.
 Since there is not much room for more improvement, the \acs{BHH} is bound to try different \index{heuristic}heuristics that yield sub-optimal results.
@@
 
-To illustrate the effects of the reselection interval hyper-paramter on the entire trianing, process, Table \ref{tab:results:reselection:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} reselection interval configurations.
+To illustrate the effects of the reselection interval hyper-parameter on the entire training, process, Table \ref{tab:results:reselection:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} reselection interval configurations.
 Similar to before, the performance rank is calculated as the average rank produced by reselection interval configuration, for all datasets, over all independent runs and epochs.
@@
 The smaller the replay window size, the less performance samples in the performance log are considered for reanalysis.
-A replay window size of one yields a case where only the last executed step is considered for reanalysis and thus provides a shortsighted view on the relevance of past performance.
+A replay window size of one yields a case where only the last executed step is considered for reanalysis and thus provides a short-sighted view on the relevance of past performance.
 As such, reselection is based only on the most recent performance of each selected \index{heuristic}heuristic.
@@
 
-Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group.
+Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the reanalysis interval experimental group.
 As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.

### 2022-12-05 dissertation/chapters/09-conclusion.tex
✨ (review): Spelling and grammar, derived publications fix

@@
 
-The research presented in this disseration identified the possibility of using a different approach, referred to as \acp{HH}, to automate the \index{heuristic}heuristic selection process.
+The research presented in this dissertation identified the possibility of using a different approach, referred to as \acp{HH}, to automate the \index{heuristic}heuristic selection process.
 \acp{HH} are high-level search algorithms that search in the \index{heuristic}heuristic space, whereby low-level \index{heuristic}heuristics search in the solution space.
@@
 
-      \item An empirical process was desiged and the detail of the implementation for the empirical process and the \acs{BHH} was provided.
+      \item An empirical process was designed and the detail of the implementation for the empirical process and the \acs{BHH} was provided.
 
@@
 
-All experimental groups were run for a maximum of 30 epochs in order to allow for the studying of the \ac{BHH} even after training has converged and overfitting has occured.
+All experimental groups were run for a maximum of 30 epochs in order to allow for the studying of the \ac{BHH} even after training has converged and overfitting has occurred.
 The maximum epoch strategy yielded a training process that is longer than what was empirically found to be necessary.
@@
 
-Various illustrations of the train and test loss plots, as it relates to training of a \acs{FFNN} on the the iris dataset, have been provided.
+Various illustrations of the train and test loss plots, as it relates to training of a \acs{FFNN} on the iris dataset, have been provided.
 Furthermore, various illustrations on the changes of the \acs{BHH} state parameters were provided for visual aid.
@@
 Minor divergence of the training loss is observed as the \acs{BHH} explores other heuristics in an attempt to improve performance.
-Since no move-acceptance strategy, and no early stopping stategy was used, the \acs{BHH} could select heuristics that are sub-optimal.
+Since no move-acceptance strategy, and no early stopping strategy was used, the \acs{BHH} could select heuristics that are sub-optimal.
 Future research opportunities should incorporate these aforementioned strategies.
@@
 
-For this experimental group, the same three \index{heuristic pool}heuristical pool variants as outlined for the \acs{BHH} behavioural case study, was implemented.
+For this experimental group, the same three \index{heuristic pool}heuristic pool variants as outlined for the \acs{BHH} behavioural case study, was implemented.
 These variants are denoted as \textit{all}, \textit{gd}, and \textit{mh}.
@@
 Overall, with statistical significance, it was found that a larger reselection interval is generally preferred.
-It was found that larger reselection intervals lead to longer timeframes for the low-level heuristics to progress, smoothing out update steps.
+It was found that larger reselection intervals lead to longer time frames for the low-level heuristics to progress, smoothing out update steps.
 Larger reselection intervals also allow the \acs{BHH} to collect more samples of \index{heuristic}heuristic performance evidence from which it can learn.

### 2022-12-06 dissertation/appendix/symbols.tex
✏️ (final-review): References, datasets, start of symbols.

--- 2022-01-07 thesis/appendex/c-symbols.tex
@@
 This appendix summarises the important symbols used throughout the dissertation.
-For each symbol, a short description is provided as well as the reference to the
-equation that makes use it. Symbols are divided according to the chapter in
-which they were introduced and are ordered alphabetically.
+For each symbol, a short description is provided as well as the reference to the equation that makes use it.
+Symbols are divided according to the chapter in which they were introduced and are ordered alphabetically.
+
+\section{Chapter~\ref{chap:introduction}: Introduction}
+\label{sec:symbols:introduction}
 
@@
 
-\todo[inline]{ref usage}
-
 \begin{description}
 	\item
-    [\parbox{1cm}{$\alpha$}] Control parameter for leaky ReLU that controls non-zero gradients.
+	      [\parbox{1cm}{$\alpha$}] Control parameter for leaky ReLU that controls non-zero gradients. (See Eq.~\eqref{eq:an_function_mapping} p.~\pageref{eq:an_function_mapping})
+\end{description}
 
-    \item
-    [\parbox{1cm}{$\beta$}] Batch size.
+\section{Chapter~\ref{chap:heuristics}: Heuristics}
+\label{sec:symbols:heuristics}
 
-    \item
-    [\parbox{1cm}{$c$}] Index for classes.
+\section{Chapter~\ref{chap:hhs}: Hyper-Heuristics}
+\label{sec:symbols:hhs}
 
-    \item
-    [\parbox{1cm}{$C$}] Total number of classes.
+\section{Chapter~\ref{chap:probability}: Probability}
+\label{sec:symbols:probability}
 
-    \item
-    [\parbox{1cm}{$E$}] Total number of epochs.
+\section{Chapter~\ref{chap:bhh}: Bayesian Hyper-Heuristic}
+\label{sec:symbols:bhh}
 
-    \item
-    [\parbox{1cm}{$\epsilon$}] Error value calculated from loss/cost function.
+\section{Chapter~\ref{chap:methodology}: Methodology}
+\label{sec:symbols:methodology}
 
-    \item
-    [\parbox{1cm}{$f$}] The activation function implemented by the \ac{AN}.
+\section{Chapter~\ref{chap:results}: Results}
+\label{sec:symbols:results}
 
-    \item
-    [\parbox{1cm}{$f_{AN}$}] The non-linear function represented by the \ac{AN}.
-
-    \item
-    [\parbox{1cm}{$\vec{h}$}] The vector representing the activations of the hidden units.
-
-    \item
-    [\parbox{1cm}{$h_j$}] The $j$-th hidden unit and thus its activation.
-
-    \item
-    [\parbox{1cm}{$i$}] Index for the input dimensions.
-
-    \item
-    [\parbox{1cm}{$I$}] Total number of dimensions on the input space.
-
-    \item
-    [\parbox{1cm}{$j$}] Index for the hidden layer.
-
-    \item
-    [\parbox{1cm}{$J$}] The total number of units in the hidden layer.
-
-    \item
-    [\parbox{1cm}{$k$}] Index for the output dimensions.
-
-    \item
-    [\parbox{1cm}{$K$}] The total number of dimensions in the output space.
-
-    \item
-    [\parbox{1cm}{$\lambda$}] Control parameter for the steepness of sigmoid and hyperbolic tangent activation functions.
-
-    \item
-    [\parbox{1cm}{$net$}] The net input signal.
-
-    \item
-    [\parbox{1cm}{$net'$}] The augmented net input signal which contains the bias term $\theta$.
-
-    \item
-    [\parbox{1cm}{$\mu_i$}] The mean over all input patterns at index $i$.
-
-    \item
-    [\parbox{1cm}{$p$}] Index used for patterns in the set of all training data.
-
-    \item
-    [\parbox{1cm}{$P$}] Total number of patterns in the training data.
-
-    \item
-    [\parbox{1cm}{$\omega_{min}$}] The lower bound of the range for random uniform sampling.
-
-    \item
-    [\parbox{1cm}{$\omega_{max}$}] The upper bound of the range for random uniform sampling.
-
-    \item
-    [\parbox{1cm}{$\mathbb{R}$}] The real number space.
-
-    \item
-    [\parbox{1cm}{$\sigma$}] The standard deviation.
-
-    \item
-    [\parbox{1cm}{$\sigma_i^2$}] Unit variance.
-
-    \item
-    [\parbox{1cm}{$T$}] The total number of dimensions in the target space.
-
-    \item
-    [\parbox{1cm}{$\theta$}] The bias or threshold term.
-
-    \item
-    [\parbox{1cm}{$\vec{v}$}] The vector of weights associated with the input.
-
-    \item
-    [\parbox{1cm}{$v_i$}] The $i$-th index of the weight vector associated with the input.
-
-    \item
-    [\parbox{1cm}{$v_{i,j}$}] The $i,j$-th index of the weight vector between the input and hidden layers.
-
-    \item
-    [\parbox{1cm}{$\vec{w}$}] The weight vector between the hidden and output layers.
-
-    \item
-    [\parbox{1cm}{$w_{j,k}$}] The $j,k$-th index of the weight vector between the hidden and output layers.
-
-    \item
-    [\parbox{1cm}{$\vec{x}$}] The input vector.
-
-    \item
-    [\parbox{1cm}{$\vec{x}_p$}] The input vector for pattern $p$.
-
-    \item
-    [\parbox{1cm}{$x_i$}] The $i$-th index of the input vector $\vec{x}$
-
-    \item
-    [\parbox{1cm}{$x_{i,p}$}] The $i$-th index of the input vector $\vec{x}$ for pattern $p$.
-
-    \item
-    [\parbox{1cm}{$x_{i,p}'$}] The pre-processed input at the $i$-th index of the input vector $\vec{x}$ for pattern $p$.
-
-    \item
-    [\parbox{1cm}{$x_{i_{min}}$}] The minimum value at the  $i$-th index of the input vector $\vec{x}$  for all patterns in $P$.
-
-    \item
-    [\parbox{1cm}{$x_{i_{max}}$}] The maximum value at the  $i$-th index of the input vector $\vec{x}$  for all patterns in $P$.
-
-    \item
-    [\parbox{1cm}{$\vec{y}$}] The output vector.
-
-    \item
-    [\parbox{1cm}{$\vec{y}_p$}] The output vector for pattern $p$.
-
-    \item
-    [\parbox{1cm}{$y_k$}] The $k$-th dimension of the output vector $\vec{y}$.
-
-    \item
-    [\parbox{1cm}{$y_{k}'$}] The post-processed output at the $k$-th dimension of the output vector $\vec{y}$.
-
-    \item
-    [\parbox{1cm}{$y_{k,p}$}] The $k$-th dimension of the output vector $\vec{y}$ for pattern $p$.
-
-    \item
-    [\parbox{1cm}{$y_{k,p}'$}] The post-processed output at the $k$-th dimension of the output vector $\vec{y}$ for pattern $p$.
-
-    \item
-    [\parbox{1cm}{$\hat{y}_{k,p}$}] The $k$-th dimension of the target output for pattern $p$. 
-\end{description}
+\section{Chapter~\ref{chap:conclusion}: Conclusion}
+\label{sec:symbols:conclusion}

### 2022-12-06 dissertation/chapters/01-introduction.tex
✏️ (final-review): References, datasets, start of symbols.

@@
 \Acf{ML} is one of the most popular fields of research in \acf{AI} studies today.
-In recent years, \acs{ML} research has seen some notable achievements in academia~\cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large~\cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.
-\acs{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \acs{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1~\cite{ref:san-hun:2016}.
+In recent years, \acs{ML} research has seen some notable achievements in academia~\cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:vaswani:2017}, as well as the industry at large~\cite{ref:silver:2016, ref:silver2017, ref:zoph:2017, ref:lewis:2017}.
+\acs{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \acs{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1~\cite{ref:silver:2017}.
 
@@
 This field of study is known as \index{meta-learning}meta-learning~\cite{ref:giraud:2004}.
-\index{meta-learning}Meta-learning of heuristic hyper-parameters as applied in the training of \acp{ANN} has shown to yield good generalisation results~\cite{ref:hospedales:2020, ref:vilalta:2002}.
+\index{meta-learning}Meta-learning of heuristic hyper-parameters as applied in the training of \acp{ANN} has shown to yield good generalisation results~\cite{ref:hospedales:2022, ref:vilalta:2002}.
 
@@
 \begin{itemize}
+      \item \textbf{Appendix~\ref{app:acronyms}} provides a list of the important acronyms used or newly defined in the course of this work, as well as their associated definitions.
+
+      \item \textbf{Appendix~\ref{app:symbols}} lists and defines the mathematical symbols used in this work, categorised according to the relevant chapter in which they appear.
+
       \item \textbf{Appendix~\ref{app:datasets}} provides details on the datasets used for the empirical analysis.
@@
       \item \textbf{Appendix~\ref{app:statistical_analysis}} provides details on the outcomes of the statistical analyses.
-
-      \item \textbf{Appendix~\ref{app:acronyms}} provides a list of the important acronyms used or newly defined in the course of this work, as well as their associated definitions.
 

### 2022-12-06 dissertation/chapters/02-artificial-neural-networks.tex
✏️ (final-review): References, datasets, start of symbols.

@@
 Stronger \index{synapse}synapses have a higher probability of generating an action potential in the post-synaptic neuron.
-During activation, the pre-synaptic neuron release neurotransmitters that bind to the post-synaptic neuron~\cite{ref:khanacademy:synapse}.
+During activation, the pre-synaptic neuron release neurotransmitters that bind to the post-synaptic neuron.
 The frequent release of these molecules cause the \index{synapse}synapse to grow.
@@
 For qualitative data, the class labels have to be converted from textual to numerical representations.
-In general, class labels are encoded as numerical vectors~\cite{ref:srinidhi:2018, ref:brownlee:2017:one-hot}.
+In general, class labels are encoded as numerical vectors~\cite{ref:brownlee:2017:one-hot}.
 One such encoding technique is referred to as \index{one-hot encoding}\textit{one-hot encoding}.
@@
 If weights are initialised as values that are too big, output of the activation function would not be in the active range.
-This leads to unit saturation, and exploding gradients can occur~\cite{ref:hanin:2018, ref:yadav:2018}.
+This leads to unit saturation, and exploding gradients can occur~\cite{ref:hanin:2018}.
 
 Many different weight initialisation techniques have been developed~\cite{ref:erdogmus:2003}.
-Some techniques have been developed to address the problems that are mentioned above~\cite{ref:yadav:2018}.
 For the purposes of this dissertation, focus is put on \index{random uniform sampling}random uniform sampling, \index{Glorot uniform sampling}\textit{Glorot uniform (Xavier)} sampling and \index{Glorot normal sampling}\textit{Glorot normal} sampling~\cite{ref:glorot:2010}.
@@
 
-An advantage of \acs{ReLU} is that it is not susceptible to the \index{vanishing gradients problem}vanishing gradients problem~\cite{ref:xu:2015, ref:maksutov:2018} which occurs when gradients in the first layers of a multi-layer \acs{ANN} approach zero, and have no effect on the training process.
+An advantage of \acs{ReLU} is that it is not susceptible to the \index{vanishing gradients problem}vanishing gradients problem~\cite{ref:xu:2015} which occurs when gradients in the first layers of a multi-layer \acs{ANN} approach zero, and have no effect on the training process.
 
@@
 Similar to \acs{ReLU}, \acs{LReLU} is not susceptible to the \index{vanishing gradients problem}vanishing gradients problem.
-However, \acs{LReLU} does not suffer from the \index{dying ReLU problem}dying \acs{ReLU} problem~\cite{ref:agarap:2018}, which occurs when the neurons that use \acs{ReLU} \index{activation function}activation functions become \textit{inactive} and only output $0$ due to a negative net input signal.
+However, \acs{LReLU} does not suffer from the \index{dying ReLU problem}dying \acs{ReLU} problem~\cite{ref:trottier:2017}, which occurs when the neurons that use \acs{ReLU} \index{activation function}activation functions become \textit{inactive} and only output $0$ due to a negative net input signal.
 The \acs{LReLU} \index{activation function}activation function is given as

### 2022-12-06 dissertation/chapters/03-heuristics.tex
✏️ (final-review): References, datasets, start of symbols.

@@
 
-\Acf{NAG} is a variant of the \acs{Momentum} heuristic developed by~\citeauthor{ref:sutskever:2013-2}~\cite{ref:sutskever:2013-2} and is inspired by~\citeauthor{ref:nesterov:1983}'s~\cite{ref:nesterov:1983} work on optimising convex functions.
+\Acf{NAG} is a variant of the \acs{Momentum} heuristic developed by~\citeauthor{ref:sutskever:2013}~\cite{ref:sutskever:2013} and is inspired by~\citeauthor{ref:nesterov:1983}'s~\cite{ref:nesterov:1983} work on optimising convex functions.
 \acs{NAG} provides an improvement to the momentum accumulation term by providing a look-ahead term that better refines the weight update step.
 
-In the \acs{NAG} heuristic, the gradient is not calculated w.r.t the current weights, but rather w.r.t the approximate future positions of the weights~\cite{ref:sutskever:2013-2, ref:ruder:2016}.
+In the \acs{NAG} heuristic, the gradient is not calculated w.r.t the current weights, but rather w.r.t the approximate future positions of the weights~\cite{ref:sutskever:2013, ref:ruder:2016}.
 An illustration of the weight update vector using \acs{NAG} is taken from Geoffrey Hinton's lecture on mini-batch \acs{GD}~\cite{ref:hinton:2012} and is presented in Figure~\ref{fig:heuristics:gd:nag} below.
@@
 
-The difference in the update step for \acs{Momentum} and the update step for \acs{NAG} as developed by~\citeauthor{ref:sutskever:2013-2}~\cite{ref:sutskever:2013-2} is described by~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} as follows.
+The difference in the update step for \acs{Momentum} and the update step for \acs{NAG} as developed by~\citeauthor{ref:sutskever:2013}~\cite{ref:sutskever:2013} is described by~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} as follows.
 \acs{Momentum} first calculates the current gradient, represented by the small \textcolor{blue}{blue} vector in Figure~\ref{fig:heuristics:gd:nag} and then takes a large step in the direction of the updated accumulated gradient, presented by the big \textcolor{blue}{blue} vector.

### 2022-12-06 dissertation/chapters/05-probability.tex
✏️ (final-review): References, datasets, start of symbols.

@@
 Consider the $p$-value for each of these experiments.
-The $p$-value is the probability of obtaining results at least as extreme as the observed results of a statistical hypothesis test~\cite{ref:beers:2022}.
+The $p$-value is the probability of obtaining results at least as extreme as the observed results of a statistical hypothesis test~\cite{ref:thisted:1998}.
 For the first experiment, the $p$-value is $0.031$ and for the second experiment, the $p$-value is $0.227$.

### 2022-12-09 dissertation/appendix/symbols.tex
✨ (symbols): Chapter 2 done

@@
 
-\section{Chapter~\ref{chap:introduction}: Introduction}
-\label{sec:symbols:introduction}
-
 \section{Chapter~\ref{chap:anns}: Artificial Neural Networks}
@@
 \begin{description}
-	\item
-	      [\parbox{1cm}{$\alpha$}] Control parameter for leaky ReLU that controls non-zero gradients. (See Eq.~\eqref{eq:an_function_mapping} p.~\pageref{eq:an_function_mapping})
+	% \item
+	%       [\parbox{1cm}{$EXAMPLE$}] THIS IS AN EXAMPLE DESCRIPTION. \lbrack Eq.~\eqref{eq:an_function_mapping} pg.~\pageref{eq:an_function_mapping} \rbrack
+
+	\item [\parbox{1cm}{$I$}] The input pattern's dimension size.
+	\item [\parbox{1cm}{$T$}] The target pattern's dimension size.
+	\item [\parbox{1cm}{$\mathbb{R}$}] The real-number space.
+	\item [\parbox{1cm}{$\mathbb{R}^{I}$}] The real-number space in I dimensions.
+	\item [\parbox{1cm}{$\mathbb{R}^{T}$}] The real-number space in T dimensions.
+	\item [\parbox{1cm}{$f_{AN}$}] The mapping function realised by the \acs{AN}.
+	\item [\parbox{1cm}{$\boldsymbol{x}$}] The input pattern/vector.
+	\item [\parbox{1cm}{$x_{i}$}] The $i$-th dimension of the input pattern/vector.
+	\item [\parbox{1cm}{$\theta$}] The bias unit.
+	\item [\parbox{1cm}{$\boldsymbol{v}$}] The weight vector.
+	\item [\parbox{1cm}{$v_{i}$}] The $i$-th dimension of the weight vector.
+	\item [\parbox{1cm}{$net$}] The net input signal to the \acs{AN}.
+	\item [\parbox{1cm}{$f(net)$}] The activation function over net input signal.
+	\item [\parbox{1cm}{$\boldsymbol{y}$}] The output vector.
+	\item [\parbox{1cm}{$\boldsymbol{y}_{p}$}] The output vector for pattern $p$.
+	\item [\parbox{1cm}{$k$}] Index for the output vector.
+	\item [\parbox{1cm}{$x_{i,p}^{'}$}] The normalised form of the input at dimension $i$, pattern $p$.
+	\item [\parbox{1cm}{$x_{i,p}$}] The original input at dimension $i$, pattern $p$.
+	\item [\parbox{1cm}{$x_{i_{min}}$}] The input's minimum value at dimension $i$.
+	\item [\parbox{1cm}{$x_{i_{max}}$}] The input's maximum value at dimension $i$.
+	\item [\parbox{1cm}{$p$}] Index for the input data patterns.
+	\item [\parbox{1cm}{$P$}] Total number of input data patterns.
+	\item [\parbox{1cm}{$\boldsymbol{x}_p$}] The $p$-th input vector/pattern.
+	\item [\parbox{1cm}{$\mu_i$}] The mean of the input at dimension $i$.
+	\item [\parbox{1cm}{$\sigma^2_i$}] The unit variance of the input at dimension $i$.
+	\item [\parbox{1cm}{$i$}] Index for the input vector.
+	\item [\parbox{1cm}{$\omega$}] The general weight vector used for normalisation.
+	\item [\parbox{1cm}{$\omega_{i}$}] The general weight vector used for normalisation at dimension $i$.
+	\item [\parbox{1cm}{$\omega_{min}$}] The lower bound of the uniform distribution used for weights initialisation.
+	\item [\parbox{1cm}{$\omega_{max}$}] The upper bound of the uniform distribution used for weights initialisation.
+	\item [\parbox{1cm}{\footnotesize{$fanin$}}] The number of input neurons to the weight vector.
+	\item [\parbox{1cm}{\footnotesize{$fanout$}}] The number of output neurons from the weight vector.
+	\item [\parbox{1cm}{$\sigma$}] The standard deviation of the truncated normal distribution used for weight initialisation.
+	\item [\parbox{1cm}{$K$}] Number of output units.
+	\item [\parbox{1cm}{$x_{i+1}$}] The $i+1$-th dimension of the input pattern/vector.
+	\item [\parbox{1cm}{$v_{i+1}$}] The $i+1$-th dimension of the weight vector.
+	\item [\parbox{1cm}{$net^{'}$}] The augmented net input signal that includes the bias term.
+	\item [\parbox{1cm}{$\tau$}] Phase shift threshold parameter.
+	\item [\parbox{1cm}{$f(x)$}] The function used to describe the \acs{LReLU} activation function.
+	\item [\parbox{1cm}{$f$}] A shorted form of the activation function.
+	\item [\parbox{1cm}{$x^{+}$}] The positive part of the input parameter's domain.
+	\item [\parbox{1cm}{$\alpha$}] Scaling parameter used by the \acs{LReLU} activation function.
+	\item [\parbox{1cm}{$\lambda$}] Scaling/control parameter used by the sigmoid and tanh activation functions.
+	\item [\parbox{1cm}{$x_{min}$}] The input's minimum value used by the min-max scaler.
+	\item [\parbox{1cm}{$x_{max}$}] The input's maximum value used by the min-max scaler.
+	\item [\parbox{1cm}{$\mathbb{R}^{K}$}] The real-number space in $K$ dimensions.
+	\item [\parbox{1cm}{$y_{k}$}] The $k$-th dimension of the output vector.
+	\item [\parbox{1cm}{$y^{'}_k$}] The softmax value of the output at dimension $k$.
+	\item [\parbox{1cm}{$\boldsymbol{y^{'}}$}] The softmax form of the output vector.
+	\item [\parbox{1cm}{$x_{i}$}] The $i$-th dimension of the input vector.
+	\item [\parbox{1cm}{$h_{j}$}] The $j$-th dimension of the hidden layer.
+	\item [\parbox{1cm}{$j$}] Index used for the hidden layer.
+	\item [\parbox{1cm}{$v_{i,j}$}] The weight associated with input node $x_{i}$ and the hidden node $h_{j}$.
+	\item [\parbox{1cm}{$w_{j,k}$}] The weight associated with hidden node $h_{j}$ and the output node $y_{k}$.
+	\item [\parbox{1cm}{$net_{i,h}$}] The net input signal at the hidden layer.
+	\item [\parbox{1cm}{$net_{h,y}$}] The net input signal at the output layer.
+	\item [\parbox{1cm}{$\epsilon$}] The cost/loss produced by the loss function.
+	\item [\parbox{1cm}{$y_{k,p}$}] The output produced by the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.
+	\item [\parbox{1cm}{$\hat{y}_{k,p}$}] The target output for the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.
+	\item [\parbox{1cm}{$\beta$}] Mini-batch size.
+	\item [\parbox{1cm}{$\mathbbm{1}$}] The indicator function.
+	\item [\parbox{1cm}{$c$}] Index used for $c$-th class.
+	\item [\parbox{1cm}{$C$}] Total number of classes.
+
 \end{description}
@@
 
+\begin{description}
+	\item [\parbox{1cm}{$\alpha$}]
+	\item [\parbox{1cm}{$\beta_{1}$}]
+	\item [\parbox{1cm}{$\beta_{2}$}]
+	\item [\parbox{1cm}{$\beta^{t}_{1}$}]
+	\item [\parbox{1cm}{$\beta^{t}_{2}$}]
+	\item [\parbox{1cm}{$\beta$}]
+	\item [\parbox{1cm}{$\boldsymbol{\hat{y}}_{i}(t)$}]
+	\item [\parbox{1cm}{$\boldsymbol{G_{t}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{g}_{t}^{2}$}]
+	\item [\parbox{1cm}{$\boldsymbol{g}_{t}$}]
+	\item [\parbox{1cm}{$\boldsymbol{g}^{2}_{t}$}]
+	\item [\parbox{1cm}{$\boldsymbol{g}$}]
+	\item [\parbox{1cm}{$\boldsymbol{m}_{t}$}]
+	\item [\parbox{1cm}{$\boldsymbol{m}_{t+1}$}]
+	\item [\parbox{1cm}{$\boldsymbol{r}_{1} \sim U(0,1)^J$}]
+	\item [\parbox{1cm}{$\boldsymbol{r}_{2} \sim U(0,1)^J$}]
+	\item [\parbox{1cm}{$\boldsymbol{u}_{i}(t)$}]
+	\item [\parbox{1cm}{$\boldsymbol{v}_{i}(t)$}]
+	\item [\parbox{1cm}{$\boldsymbol{V}_{max}$}]
+	\item [\parbox{1cm}{$\boldsymbol{v}_{t}$}]
+	\item [\parbox{1cm}{$\boldsymbol{v}_{t+1}$}]
+	\item [\parbox{1cm}{$\boldsymbol{v}$}]
+	\item [\parbox{1cm}{$\boldsymbol{w}_{t}^{2}$}]
+	\item [\parbox{1cm}{$\boldsymbol{w}_{t}$}]
+	\item [\parbox{1cm}{$\boldsymbol{w}_{t+1}$}]
+	\item [\parbox{1cm}{$\boldsymbol{w}$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{1}}(t)$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{1}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{2}}(t)$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{2}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{3}}(t)$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}_{i_{3}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}_{i} \sim U(x_{min}, x_{max})$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}_{i}(0)$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}_{i}(t) \in \mathcal{C}(t)$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}_{i}(t)$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}'_{i}(t)$}]
+	\item [\parbox{1cm}{$\boldsymbol{y}_{i}(0)$}]
+	\item [\parbox{1cm}{$\boldsymbol{y}_{i}(t)$}]
+	\item [\parbox{1cm}{$\Delta w_{i}(t)$}]
+	\item [\parbox{1cm}{$\Delta$}]
+	\item [\parbox{1cm}{$\emptyset$}]
+	\item [\parbox{1cm}{$\epsilon_{T_{p}}$}]
+	\item [\parbox{1cm}{$\epsilon_{T}$}]
+	\item [\parbox{1cm}{$\epsilon$}]
+	\item [\parbox{1cm}{$\eta$}]
+	\item [\parbox{1cm}{$\hat{\boldsymbol{m}}_{t}$}]
+	\item [\parbox{1cm}{$\hat{\boldsymbol{v}}_{t}$}]
+	\item [\parbox{1cm}{$\hat{y}_{ij}(t)$}]
+	\item [\parbox{1cm}{$\hat{y}_{ij}$}]
+	\item [\parbox{1cm}{$\hat{y}$}]
+	\item [\parbox{1cm}{$\mathcal{C}(0)$}]
+	\item [\parbox{1cm}{$\mathcal{C}(t+1)$}]
+	\item [\parbox{1cm}{$\mathcal{E}$}]
+	\item [\parbox{1cm}{$\mathcal{J}$}]
+	\item [\parbox{1cm}{$\odot$}]
+	\item [\parbox{1cm}{$c_{1}$}]
+	\item [\parbox{1cm}{$c_{2}$}]
+	\item [\parbox{1cm}{$E[\boldsymbol{g}^{2}]_{t - 1}$}]
+	\item [\parbox{1cm}{$E[\boldsymbol{g}^{2}]_{t}$}]
+	\item [\parbox{1cm}{$E[\Delta \boldsymbol{w}^{2}]_{t - 1}$}]
+	\item [\parbox{1cm}{$E[\Delta \boldsymbol{w}^{2}]_{t}$}]
+	\item [\parbox{1cm}{$f(\boldsymbol{x}_{i}(t))$}]
+	\item [\parbox{1cm}{$f(\boldsymbol{x}'_{i}(t))$}]
+	\item [\parbox{1cm}{$f(\hat{y})$}]
+	\item [\parbox{1cm}{$f(x_{i})$}]
+	\item [\parbox{1cm}{$f(x)$}]
+	\item [\parbox{1cm}{$f(y_{i})$}]
+	\item [\parbox{1cm}{$f$}]
+	\item [\parbox{1cm}{$g_{t,i}$}]
+	\item [\parbox{1cm}{$G_{t,i}$}]
+	\item [\parbox{1cm}{$G_{t,ii}$}]
+	\item [\parbox{1cm}{$g$}]
+	\item [\parbox{1cm}{$i_{1}$}]
+	\item [\parbox{1cm}{$i_{2}$}]
+	\item [\parbox{1cm}{$i_{3}$}]
+	\item [\parbox{1cm}{$i$}]
+	\item [\parbox{1cm}{$I$}]
+	\item [\parbox{1cm}{$j^{*}$}]
+	\item [\parbox{1cm}{$j$}]
+	\item [\parbox{1cm}{$J$}]
+	\item [\parbox{1cm}{$k$}]
+	\item [\parbox{1cm}{$m_{j}(t)$}]
+	\item [\parbox{1cm}{$mathcal{J}$}]
+	\item [\parbox{1cm}{$N_{t}$}]
+	\item [\parbox{1cm}{$N$}]
+	\item [\parbox{1cm}{$net_{p}$}]
+	\item [\parbox{1cm}{$o_{k,p}^{2}$}]
+	\item [\parbox{1cm}{$o_{p}$}]
+	\item [\parbox{1cm}{$o_p$}]
+	\item [\parbox{1cm}{$p_{c}$}]
+	\item [\parbox{1cm}{$p_{m}$}]
+	\item [\parbox{1cm}{$p_{r}$}]
+	\item [\parbox{1cm}{$p_{x}$}]
+	\item [\parbox{1cm}{$p$}]
+	\item [\parbox{1cm}{$r_{1_{j}}$}]
+	\item [\parbox{1cm}{$r_{2_{j}}$}]
+	\item [\parbox{1cm}{$RMS$}]
+	\item [\parbox{1cm}{$t_{k,p}$}]
+	\item [\parbox{1cm}{$t_{p}$}]
+	\item [\parbox{1cm}{$t$}]
+	\item [\parbox{1cm}{$T$}]
+	\item [\parbox{1cm}{$u_{ij}(t)$}]
+	\item [\parbox{1cm}{$v_{ij}(t)$}]
+	\item [\parbox{1cm}{$v_{ij}(t+1)$}]
+	\item [\parbox{1cm}{$v_{ij}$}]
+	\item [\parbox{1cm}{$V_{max,j}$}]
+	\item [\parbox{1cm}{$V_{max}$}]
+	\item [\parbox{1cm}{$v'_{ij}(t+1)$}]
+	\item [\parbox{1cm}{$w_{i}(t-1)$}]
+	\item [\parbox{1cm}{$w_{i}(t)$}]
+	\item [\parbox{1cm}{$w_{i}$}]
+	\item [\parbox{1cm}{$w_{i}$}]
+	\item [\parbox{1cm}{$w_{t,i}$}]
+	\item [\parbox{1cm}{$w_{t}$}]
+	\item [\parbox{1cm}{$w_{t+1,i}$}]
+	\item [\parbox{1cm}{$w_{t+1}$}]
+	\item [\parbox{1cm}{$w$}]
+	\item [\parbox{1cm}{$W$}]
+	\item [\parbox{1cm}{$wv_{ij}(t)$}]
+	\item [\parbox{1cm}{$wv_{ij}$}]
+	\item [\parbox{1cm}{$x_{i}$}]
+	\item [\parbox{1cm}{$x_{ij}(t)$}]
+	\item [\parbox{1cm}{$x_{ij}(t+1)$}]
+	\item [\parbox{1cm}{$x_{ij}$}]
+	\item [\parbox{1cm}{$x_{max,j}$}]
+	\item [\parbox{1cm}{$x_{min,j}$}]
+	\item [\parbox{1cm}{$x'_{ij}(t)$}]
+	\item [\parbox{1cm}{$x$}]
+	\item [\parbox{1cm}{$y_{i}$}]
+	\item [\parbox{1cm}{$y_{ij}(t)$}]
+	\item [\parbox{1cm}{$y_{ij}$}]
+	\item [\parbox{1cm}{$y$}]
+	\item [\parbox{1cm}{$z_{i,p}$}]
+	\item [\parbox{1cm}{$z$}]
+\end{description}
+
 \section{Chapter~\ref{chap:hhs}: Hyper-Heuristics}
 \label{sec:symbols:hhs}
+
+\begin{description}
+	\item [\parbox{1cm}{$K$}]
+\end{description}
 
@@
 
+\begin{description}
+	\item [\parbox{1cm}{$\alpha_{0}$}]
+	\item [\parbox{1cm}{$\alpha_{1}$}]
+	\item [\parbox{1cm}{$\alpha_{k}$}]
+	\item [\parbox{1cm}{$\alpha_{K}$}]
+	\item [\parbox{1cm}{$\alpha$}]
+	\item [\parbox{1cm}{$\bar{A}$}]
+	\item [\parbox{1cm}{$\beta'$ }]
+	\item [\parbox{1cm}{$\beta$}]
+	\item [\parbox{1cm}{$Bin$}]
+	\item [\parbox{1cm}{$\boldsymbol{\alpha'}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\alpha}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\mathcal{D}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\theta}$}]
+	\item [\parbox{1cm}{$\boldsymbol{N}$}]
+	\item [\parbox{1cm}{$\boldsymbol{x_{1}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{x_{i}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{x_{I}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{x}$}]
+	\item [\parbox{1cm}{$\boldsymbol{X}$}]
+	\item [\parbox{1cm}{$\boldsymbol{Y}$}]
+	\item [\parbox{1cm}{$\emptyset$}]
+	\item [\parbox{1cm}{$\Gamma'(n)$}]
+	\item [\parbox{1cm}{$\Gamma(n)$}]
+	\item [\parbox{1cm}{$\Gamma$}]
+	\item [\parbox{1cm}{$\mathbb{R}$}]
+	\item [\parbox{1cm}{$\mathbbm{1}$}]
+	\item [\parbox{1cm}{$\mathcal{A}$}]
+	\item [\parbox{1cm}{$\mathcal{L}$}]
+	\item [\parbox{1cm}{$\overset{\text{iid}}{\sim}$}]
+	\item [\parbox{1cm}{$\psi$}]
+	\item [\parbox{1cm}{$\theta_{1}$}]
+	\item [\parbox{1cm}{$\theta_{k}$}]
+	\item [\parbox{1cm}{$\theta_{K}$}]
+	\item [\parbox{1cm}{$\theta$}]
+	\item [\parbox{1cm}{$A$}]
+	\item [\parbox{1cm}{$B_{1}$}]
+	\item [\parbox{1cm}{$B_{2}$}]
+	\item [\parbox{1cm}{$B_{i}$}]
+	\item [\parbox{1cm}{$B_{j}$}]
+	\item [\parbox{1cm}{$B_{K}$}]
+	\item [\parbox{1cm}{$B(\boldsymbol{\alpha})$}]
+	\item [\parbox{1cm}{$B$}]
+	\item [\parbox{1cm}{$Ber(\theta)$}]
+	\item [\parbox{1cm}{$Beta$}]
+	\item [\parbox{1cm}{$Bin$}]
+	\item [\parbox{1cm}{$c$}]
+	\item [\parbox{1cm}{$Cat$}]
+	\item [\parbox{1cm}{$d$}]
+	\item [\parbox{1cm}{$Dir$}]
+	\item [\parbox{1cm}{$dn$}]
+	\item [\parbox{1cm}{$E[{x_{k}}]$}]
+	\item [\parbox{1cm}{$E[\ln(x_{k})]$}]
+	\item [\parbox{1cm}{$E[\ln(x)]$}]
+	\item [\parbox{1cm}{$E[x_{k}]$}]
+	\item [\parbox{1cm}{$E[x]$}]
+	\item [\parbox{1cm}{$f_{Ber}$}]
+	\item [\parbox{1cm}{$f_{Beta}$}]
+	\item [\parbox{1cm}{$f_{Bin}$}]
+	\item [\parbox{1cm}{$f_{Cat}$}]
+	\item [\parbox{1cm}{$f_{Dir}$}]
+	\item [\parbox{1cm}{$f_{Mul}$}]
+	\item [\parbox{1cm}{$f$}]
+	\item [\parbox{1cm}{$F$}]
+	\item [\parbox{1cm}{$g^{*}$}]
+	\item [\parbox{1cm}{$g$}]
+	\item [\parbox{1cm}{$i$}]
+	\item [\parbox{1cm}{$I$}]
+	\item [\parbox{1cm}{$j$}]
+	\item [\parbox{1cm}{$K$}]
+	\item [\parbox{1cm}{$k$}]
+	\item [\parbox{1cm}{$K$}]
+	\item [\parbox{1cm}{$M[x_{k}]$}]
+	\item [\parbox{1cm}{$M[x]$}]
+	\item [\parbox{1cm}{$m$}]
+	\item [\parbox{1cm}{$M$}]
+	\item [\parbox{1cm}{$Mul$}]
+	\item [\parbox{1cm}{$N_{0}$}]
+	\item [\parbox{1cm}{$N_{1}$}]
+	\item [\parbox{1cm}{$N_{k}$}]
+	\item [\parbox{1cm}{$N_{K}$}]
+	\item [\parbox{1cm}{$n$}]
+	\item [\parbox{1cm}{$N$}]
+	\item [\parbox{1cm}{$p$}]
+	\item [\parbox{1cm}{$S$}]
+	\item [\parbox{1cm}{$v$}]
+	\item [\parbox{1cm}{$x_{1}$}]
+	\item [\parbox{1cm}{$x_{i,k}$}]
+	\item [\parbox{1cm}{$x_{i}$}]
+	\item [\parbox{1cm}{$x_{I}$}]
+	\item [\parbox{1cm}{$x_{j}$}]
+	\item [\parbox{1cm}{$x_{k}$}]
+	\item [\parbox{1cm}{$x_{K}$}]
+	\item [\parbox{1cm}{$x$}]
+	\item [\parbox{1cm}{$y_{1}$}]
+	\item [\parbox{1cm}{$Y_{1}$}]
+	\item [\parbox{1cm}{$y_{2}$}]
+	\item [\parbox{1cm}{$Y_{2}$}]
+	\item [\parbox{1cm}{$y_{i}$}]
+	\item [\parbox{1cm}{$Y_{i}$}]
+	\item [\parbox{1cm}{$y_{n}$}]
+	\item [\parbox{1cm}{$Y_{N}$}]
+\end{description}
+
 \section{Chapter~\ref{chap:bhh}: Bayesian Hyper-Heuristic}
 \label{sec:symbols:bhh}
+
+\begin{description}
+	\item [\parbox{1cm}{$\alpha_{1}$}]
+	\item [\parbox{1cm}{$\alpha_{k}$}]
+	\item [\parbox{1cm}{$\alpha_{K}$}]
+	\item [\parbox{1cm}{$\alpha$}]
+	\item [\parbox{1cm}{$\beta_{1}$}]
+	\item [\parbox{1cm}{$\beta_{2}$}]
+	\item [\parbox{1cm}{$\beta_{j,k}$}]
+	\item [\parbox{1cm}{$\beta_{K}^{J}$}]
+	\item [\parbox{1cm}{$\beta$}]
+	\item [\parbox{1cm}{$\boldsymbol{\alpha}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\beta}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\gamma}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\hat{\phi}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\hat{\psi}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\hat{\theta}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\lambda}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\phi}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\psi}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\theta}$}]
+	\item [\parbox{1cm}{$\boldsymbol{C}$}]
+	\item [\parbox{1cm}{$\boldsymbol{E}$}]
+	\item [\parbox{1cm}{$\boldsymbol{H}$}]
+	\item [\parbox{1cm}{$\epsilon(-1)$}]
+	\item [\parbox{1cm}{$\epsilon$}]
+	\item [\parbox{1cm}{$\eta$}]
+	\item [\parbox{1cm}{$\gamma_{0}$}]
+	\item [\parbox{1cm}{$\gamma_{1,k}$}]
+	\item [\parbox{1cm}{$\gamma_{1}$}]
+	\item [\parbox{1cm}{$\gamma_{2,k}$}]
+	\item [\parbox{1cm}{$\gamma_{K}$}]
+	\item [\parbox{1cm}{$\hat{\phi}_{j,k}$}]
+	\item [\parbox{1cm}{$\hat{\psi_{k}}$}]
+	\item [\parbox{1cm}{$\hat{\psi}_{k}$}]
+	\item [\parbox{1cm}{$\hat{\theta_{k}}$}]
+	\item [\parbox{1cm}{$\hat{\theta}_{k}$}]
+	\item [\parbox{1cm}{$\lambda_{1}$}]
+	\item [\parbox{1cm}{$\lambda_{j}$}]
+	\item [\parbox{1cm}{$\lambda_{J}$}]
+	\item [\parbox{1cm}{$\mathbbm{1}_{0}$}]
+	\item [\parbox{1cm}{$\mathbbm{1}_{1}$}]
+	\item [\parbox{1cm}{$\mathbin{\%}$}]
+	\item [\parbox{1cm}{$\mathcal{A}(v)$}]
+	\item [\parbox{1cm}{$\mathcal{L}$}]
+	\item [\parbox{1cm}{$\phi_{j,k}$}]
+	\item [\parbox{1cm}{$\phi_{jk}$}]
+	\item [\parbox{1cm}{$\phi$}]
+	\item [\parbox{1cm}{$\psi_{k}$}]
+	\item [\parbox{1cm}{$\psi_{k}N_{k}$}]
+	\item [\parbox{1cm}{$\psi$}]
+	\item [\parbox{1cm}{$\theta_{k}$}]
+	\item [\parbox{1cm}{$\theta$}]
+	\item [\parbox{1cm}{$A$}]
+	\item [\parbox{1cm}{$B$}]
+	\item [\parbox{1cm}{$Beta$}]
+	\item [\parbox{1cm}{$Bin$}]
+	\item [\parbox{1cm}{$c_{1}$}]
+	\item [\parbox{1cm}{$c_{i,k}$}]
+	\item [\parbox{1cm}{$c_{i}$}]
+	\item [\parbox{1cm}{$Dir$}]
+	\item [\parbox{1cm}{$e_{i,j,k}$}]
+	\item [\parbox{1cm}{$e_{i}$}]
+	\item [\parbox{1cm}{$e_{j}$}]
+	\item [\parbox{1cm}{$E[\phi_{j,k}]$}]
+	\item [\parbox{1cm}{$E[\psi_{k}]$}]
+	\item [\parbox{1cm}{$E[\theta_{k}]$}]
+	\item [\parbox{1cm}{$h_{i,k}$}]
+	\item [\parbox{1cm}{$h_{i}$}]
+	\item [\parbox{1cm}{$h_{k}$}]
+	\item [\parbox{1cm}{$i$}]
+	\item [\parbox{1cm}{$I$}]
+	\item [\parbox{1cm}{$j$}]
+	\item [\parbox{1cm}{$J$}]
+	\item [\parbox{1cm}{$K-1$}]
+	\item [\parbox{1cm}{$k$}]
+	\item [\parbox{1cm}{$K$}]
+	\item [\parbox{1cm}{$L$}]
+	\item [\parbox{1cm}{$LSE$}]
+	\item [\parbox{1cm}{$Mult$}]
+	\item [\parbox{1cm}{$N_{0,k}$}]
+	\item [\parbox{1cm}{$N_{1,k}$}]
+	\item [\parbox{1cm}{$N_{j,k}$}]
+	\item [\parbox{1cm}{$N_{j}$}]
+	\item [\parbox{1cm}{$N_{k}$}]
+	\item [\parbox{1cm}{$N$}]
+	\item [\parbox{1cm}{$S$}]
+	\item [\parbox{1cm}{$t$}]
+\end{description}
 
@@
 
+\begin{description}
+	\item [\parbox{1cm}{$\alpha$}]
+	\item [\parbox{1cm}{$\eta$}]
+	\item [\parbox{1cm}{$\mathbb{R}$}]
+	\item [\parbox{1cm}{$v_{ij}$}]
+	\item [\parbox{1cm}{$x_{ij}$}]
+
+\end{description}
+
 \section{Chapter~\ref{chap:results}: Results}
@@
 
-\section{Chapter~\ref{chap:conclusion}: Conclusion}
-\label{sec:symbols:conclusion}
+\begin{description}
+	\item [\parbox{1cm}{$\alpha_{0}$}]
+	\item [\parbox{1cm}{$\alpha_{6}$}]
+	\item [\parbox{1cm}{$\alpha_{7}$}]
+	\item [\parbox{1cm}{$\alpha_{8}$}]
+	\item [\parbox{1cm}{$\alpha_{i} = 50$}]
+	\item [\parbox{1cm}{$\boldsymbol{{H}}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\alpha}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\phi}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\psi}$}]
+	\item [\parbox{1cm}{$\boldsymbol{\theta}$}]
+	\item [\parbox{1cm}{$\boldsymbol{C}$}]
+	\item [\parbox{1cm}{$\boldsymbol{E}$}]
+	\item [\parbox{1cm}{$\boldsymbol{H}$}]
+	\item [\parbox{1cm}{$\pm$}]
+	\item [\parbox{1cm}{$\theta_{0}$}]
+	\item [\parbox{1cm}{$\theta_{6}$}]
+	\item [\parbox{1cm}{$\theta_{7}$}]
+	\item [\parbox{1cm}{$\theta_{8}$}]
+	\item [\parbox{1cm}{$c_{1}$}]
+	\item [\parbox{1cm}{$Cat$}]
+	\item [\parbox{1cm}{$Dir$}]
+	\item [\parbox{1cm}{$e_{0}$}]
+	\item [\parbox{1cm}{$h_{0}$}]
+	\item [\parbox{1cm}{$h_{6}$}]
+	\item [\parbox{1cm}{$h_{7}$}]
+	\item [\parbox{1cm}{$h_{8}$}]
+	\item [\parbox{1cm}{$i$}]
+	\item [\parbox{1cm}{$K$}]
+\end{description}

### 2022-12-09 dissertation/chapters/02-artificial-neural-networks.tex
✨ (symbols): Chapter 2 done

@@
 
-\index{random uniform sampling}Random uniform sampling initialises weights uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $w_{i} \sim \textit{U} (\omega_{min}, \omega_{max})$, where the $\omega_{min}$ and $\omega_{max}$ are respectfully the lower and upper bounds of the uniform distribution.
+\index{random uniform sampling}Random uniform sampling initialises weights uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $omega_{i} \sim \textit{U} (\omega_{min}, \omega_{max})$, where the $\omega_{min}$ and $\omega_{max}$ are respectfully the lower and upper bounds of the uniform distribution.
 Suggested parameter values are $(-1, 1)$ or $(-0.5, 0.5)$~\cite{ref:nguyen:1990}.
@@
 
-\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of \index{random uniform sampling}random uniform sampling, whereby $\omega = \sqrt{\frac{6}{fanin + fanout}}$ and $fanin$ is the number of input neurons to the weight vector and $fanout$ is the number of output neurons from the weight vector.
+\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of \index{random uniform sampling}random uniform sampling, whereby $\omega_{i} = \sqrt{\frac{6}{fanin + fanout}}$ and $fanin$ is the number of input neurons to the weight vector and $fanout$ is the number of output neurons from the weight vector.
 

### 2022-12-09 dissertation/appendix/symbols.tex
✨ (symbols): Chapters 3,4,7 done

--- 2022-12-06 dissertation/appendix/symbols.tex
@@
 \begin{description}
-	\item
-	      [\parbox{1cm}{$\alpha$}] Control parameter for leaky ReLU that controls non-zero gradients. (See Eq.~\eqref{eq:an_function_mapping} p.~\pageref{eq:an_function_mapping})
+	% \item
+	%       [\parbox{2cm}{$EXAMPLE$}] THIS IS AN EXAMPLE DESCRIPTION. \lbrack Eq.~\eqref{eq:an_function_mapping} pg.~\pageref{eq:an_function_mapping} \rbrack
+
+	\item [\parbox{2cm}{$I$}] The input pattern's dimension size.
+	\item [\parbox{2cm}{$T$}] The target pattern's dimension size.
+	\item [\parbox{2cm}{$\mathbb{R}$}] The real-number space.
+	\item [\parbox{2cm}{$\mathbb{R}^{I}$}] The real-number space in I dimensions.
+	\item [\parbox{2cm}{$\mathbb{R}^{T}$}] The real-number space in T dimensions.
+	\item [\parbox{2cm}{$f_{AN}$}] The mapping function realised by the \acs{AN}.
+	\item [\parbox{2cm}{$\boldsymbol{x}$}] The input pattern/vector.
+	\item [\parbox{2cm}{$x_{i}$}] The $i$-th dimension of the input pattern/vector.
+	\item [\parbox{2cm}{$\theta$}] The bias unit.
+	\item [\parbox{2cm}{$\boldsymbol{v}$}] The weight vector.
+	\item [\parbox{2cm}{$v_{i}$}] The $i$-th dimension of the weight vector.
+	\item [\parbox{2cm}{$net$}] The net input signal to the \acs{AN}.
+	\item [\parbox{2cm}{$f(net)$}] The activation function over net input signal.
+	\item [\parbox{2cm}{$\boldsymbol{y}$}] The output vector.
+	\item [\parbox{2cm}{$\boldsymbol{y}_{p}$}] The output vector for pattern $p$.
+	\item [\parbox{2cm}{$k$}] Index for the output vector.
+	\item [\parbox{2cm}{$x_{i,p}^{'}$}] The normalised form of the input at dimension $i$, pattern $p$.
+	\item [\parbox{2cm}{$x_{i,p}$}] The original input at dimension $i$, pattern $p$.
+	\item [\parbox{2cm}{$x_{i_{min}}$}] The input's minimum value at dimension $i$.
+	\item [\parbox{2cm}{$x_{i_{max}}$}] The input's maximum value at dimension $i$.
+	\item [\parbox{2cm}{$p$}] Index for the input data patterns.
+	\item [\parbox{2cm}{$P$}] Total number of input data patterns.
+	\item [\parbox{2cm}{$\boldsymbol{x}_p$}] The $p$-th input vector/pattern.
+	\item [\parbox{2cm}{$\mu_i$}] The mean of the input at dimension $i$.
+	\item [\parbox{2cm}{$\sigma^2_i$}] The unit variance of the input at dimension $i$.
+	\item [\parbox{2cm}{$i$}] Index for the input vector.
+	\item [\parbox{2cm}{$\omega$}] The general weight vector used for normalisation.
+	\item [\parbox{2cm}{$\omega_{i}$}] The general weight vector used for normalisation at dimension $i$.
+	\item [\parbox{2cm}{$\omega_{min}$}] The lower bound of the uniform distribution used for weights initialisation.
+	\item [\parbox{2cm}{$\omega_{max}$}] The upper bound of the uniform distribution used for weights initialisation.
+	\item [\parbox{2cm}{$fanin$}] The number of input neurons to the weight vector.
+	\item [\parbox{2cm}{$fanout$}] The number of output neurons from the weight vector.
+	\item [\parbox{2cm}{$\sigma$}] The standard deviation of the truncated normal distribution used for weight initialisation.
+	\item [\parbox{2cm}{$K$}] Number of output units.
+	\item [\parbox{2cm}{$x_{i+1}$}] The $i+1$-th dimension of the input pattern/vector.
+	\item [\parbox{2cm}{$v_{i+1}$}] The $i+1$-th dimension of the weight vector.
+	\item [\parbox{2cm}{$net^{'}$}] The augmented net input signal that includes the bias term.
+	\item [\parbox{2cm}{$\tau$}] Phase shift threshold parameter.
+	\item [\parbox{2cm}{$f(x)$}] The function used to describe the \acs{LReLU} activation function.
+	\item [\parbox{2cm}{$f$}] A shorted form of the activation function.
+	\item [\parbox{2cm}{$x^{+}$}] The positive part of the input parameter's domain.
+	\item [\parbox{2cm}{$\alpha$}] Scaling parameter used by the \acs{LReLU} activation function.
+	\item [\parbox{2cm}{$\lambda$}] Scaling/control parameter used by the sigmoid and tanh activation functions.
+	\item [\parbox{2cm}{$x_{min}$}] The input's minimum value used by the min-max scaler.
+	\item [\parbox{2cm}{$x_{max}$}] The input's maximum value used by the min-max scaler.
+	\item [\parbox{2cm}{$\mathbb{R}^{K}$}] The real-number space in $K$ dimensions.
+	\item [\parbox{2cm}{$y_{k}$}] The $k$-th dimension of the output vector.
+	\item [\parbox{2cm}{$y^{'}_k$}] The softmax value of the output at dimension $k$.
+	\item [\parbox{2cm}{$\boldsymbol{y^{'}}$}] The softmax form of the output vector.
+	\item [\parbox{2cm}{$h_{j}$}] The $j$-th dimension of the hidden layer.
+	\item [\parbox{2cm}{$j$}] Index used for the hidden layer.
+	\item [\parbox{2cm}{$v_{i,j}$}] The weight associated with input node $x_{i}$ and the hidden node $h_{j}$.
+	\item [\parbox{2cm}{$w_{j,k}$}] The weight associated with hidden node $h_{j}$ and the output node $y_{k}$.
+	\item [\parbox{2cm}{$net_{i,h}$}] The net input signal at the hidden layer.
+	\item [\parbox{2cm}{$net_{h,y}$}] The net input signal at the output layer.
+	\item [\parbox{2cm}{$\epsilon$}] The cost/loss produced by the loss function.
+	\item [\parbox{2cm}{$y_{k,p}$}] The output produced by the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.
+	\item [\parbox{2cm}{$\hat{y}_{k,p}$}] The target output for the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.
+	\item [\parbox{2cm}{$\beta$}] Mini-batch size.
+	\item [\parbox{2cm}{$\mathbbm{1}$}] The indicator function.
+	\item [\parbox{2cm}{$c$}] Index used for $c$-th class.
+	\item [\parbox{2cm}{$C$}] Total number of classes.
+
 \end{description}
@@
 
+\begin{description}
+	\item [\parbox{2cm}{$f$}] A shortened form of the objective function being optimised.
+	\item [\parbox{2cm}{$x$}] The independent variables to the objective function. Also used in \acs{DE} notation to denote the selection mechanism for the trial vector.
+	\item [\parbox{2cm}{$f(x)$}] The objective function over $x$.
+	\item [\parbox{2cm}{$\epsilon$}] The error between the output of the \acs{FFNN} and the target pattern, produced by the loss function.
+Also used as a small error value used by heuristics to avoid division by 0.
+	\item [\parbox{2cm}{$\mathcal{E}$}] The error function.
+	\item [\parbox{2cm}{$w_{i}(t)$}] The $i$-th dimension of the weight vector at time step $t$.
+	\item [\parbox{2cm}{$w_{i}(t-1)$}] The $i$-th dimension of the weight vector at time step $t-1$.
+	\item [\parbox{2cm}{$\Delta w_{i}(t)$}] The change in the $i$-th dimension of the weight vector at time step $t$.
+	\item [\parbox{2cm}{$w_{i}$}] The $i$-th dimension of the weight vector.
+	\item [\parbox{2cm}{$i$}] Index used for the weight vector. Also used as the index for the $i$-th particle in the population, implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$\boldsymbol{w}$}] The weight vector.
+	\item [\parbox{2cm}{$p$}] Index used for input data patterns.
+	\item [\parbox{2cm}{$o_{i,p}$}] The $i$-th dimension of the output for pattern $p$.
+	\item [\parbox{2cm}{$t_{i,p}$}] The $i$-th dimension of the target for pattern $p$.
+	      item [\parbox{2cm}{$o_{k,p}$}] The $k$-th dimension of the output for pattern $p$.
+	\item [\parbox{2cm}{$t_{k,p}$}] The $k$-th dimension of the target for pattern $p$.
+	\item [\parbox{2cm}{$net_{p}$}] The net input signal for pattern $p$.
+	\item [\parbox{2cm}{$z_{i,p}$}] The input value at index $i$ for pattern $p$.
+	\item [\parbox{2cm}{$\boldsymbol{g}$}] General symbol used to represent the gradient vector, retrieved from the error function relative to the weight vector.
+	\item [\parbox{2cm}{$\boldsymbol{v}$}] The velocity vector resulting from \acs{Momentum}.
+	\item [\parbox{2cm}{$\boldsymbol{w}$}] General symbol used to represent the weight vector.
+	\item [\parbox{2cm}{$\epsilon_{T}$}] The error at time step $T$.
+	\item [\parbox{2cm}{$\epsilon_{T_{p}}$}] The error produced for pattern $p$ at time step $T$.
+	\item [\parbox{2cm}{$\eta$}] Learning rate.
+	\item [\parbox{2cm}{$k$}] Index used for the output layer.
+	\item [\parbox{2cm}{$K$}] Total number of output units.
+	\item [\parbox{2cm}{$t$}] Time step.
+	\item [\parbox{2cm}{$T$}] Time step.
+	\item [\parbox{2cm}{$\alpha$}] The momentum hyper-parameter.
+	\item [\parbox{2cm}{$w_{t,i}$}] The $i$-th dimension of the weight vector at time step $t$.
+	\item [\parbox{2cm}{$w_{t+1,i}$}] The $i$-th dimension of the weight vector at time step $t+1$.
+	\item [\parbox{2cm}{$G_{t,ii}$}] Diagonal matrix containing the sum of the squared gradients with regards to the $i$-th dimension of the weight vector.
+	\item [\parbox{2cm}{$g_{t,i}$}] The $i$-th dimension of the gradient vector at time step $t$.
+	\item [\parbox{2cm}{$\boldsymbol{G_{t}}$}] The sum of the squares of the gradients.
+	\item [\parbox{2cm}{$G_{t,i}$}] The sum of the squared gradients with regards to the $i$-th dimension of the weight vector.
+	\item [\parbox{2cm}{$\odot$}] The matrix-vector product.
+	\item [\parbox{2cm}{$W$}] Window size of previous squared gradients.
+	\item [\parbox{2cm}{$E[\boldsymbol{g}^{2}]_{t}$}] The expected value of the squared gradients at time step $t$.
+	\item [\parbox{2cm}{$E[\boldsymbol{g}^{2}]_{t - 1}$}] The expected value of the squared gradients at time step $t-1$.
+	\item [\parbox{2cm}{$\boldsymbol{g}^{2}_{t}$}] The squared gradient vector at time step $t$.
+	\item [\parbox{2cm}{$\boldsymbol{w}_{t+1}$}] The weight vector at time step $t+1$.
+	\item [\parbox{2cm}{$\boldsymbol{w}_{t}^{2}$}] The squared weight vector at time step $t$.
+	\item [\parbox{2cm}{$\boldsymbol{g}_{t}$}] The gradient vector at time step $t$.
+	\item [\parbox{2cm}{$RMS$}] The root mean squared error criterion.
+	\item [\parbox{2cm}{$E[\Delta \boldsymbol{w}^{2}]_{t}$}] The expected value of the delta of the squared weight vector at time step $t$.
+	\item [\parbox{2cm}{$E[\Delta \boldsymbol{w}^{2}]_{t - 1}$}] The expected value of the delta of the squared weight vector at time step $t-1$.
+	\item [\parbox{2cm}{$\Delta \boldsymbol{w}^{2}_{t}$}] The delta of the squared weight vector at time step $t$.
+	\item [\parbox{2cm}{$RMS[\Delta \boldsymbol{w}]_{t}$}] The root mean squared delta of the weight vector at time step $t$.
+	\item [\parbox{2cm}{$RMS[\Delta \boldsymbol{w}]_{t-1}$}] The root mean squared delta of the weight vector at time step $t-1$.
+	\item [\parbox{2cm}{$RMS[\boldsymbol{g}]_{t}$}] The root mean squared gradient vector at time step $t$.
+	\item [\parbox{2cm}{$\boldsymbol{g}_{t}$}] The gradient vector at time step $t$.
+	\item [\parbox{2cm}{$\boldsymbol{m}_{t}$}] The estimate of the first moment at time step $t$.
+	\item [\parbox{2cm}{$\boldsymbol{m}_{t+1}$}] The estimate of the first moment at time step $t+1$.
+	\item [\parbox{2cm}{$\boldsymbol{v}_{t}$}] The estimate of the second moment at time step $t$.
+	\item [\parbox{2cm}{$\boldsymbol{v}_{t+1}$}] The estimate of the second moment at time step $t+1$.
+	\item [\parbox{2cm}{$\beta_{1}$}] First decay rate parameter for \acs{Adam}.
+	\item [\parbox{2cm}{$\beta_{2}$}] Second decay rate parameter for \acs{Adam}.
+	\item [\parbox{2cm}{$\hat{\boldsymbol{m}}_{t}$}] The bias-corrected first moment at time step $t$.
+	\item [\parbox{2cm}{$\hat{\boldsymbol{v}}_{t}$}] The bias-corrected second moment at time step $t$.
+	\item [\parbox{2cm}{$\beta^{t}_{1}$}] First decay rate parameter for \acs{Adam} at time step $t$.
+	\item [\parbox{2cm}{$\beta^{t}_{2}$}] Second decay rate parameter for \acs{Adam} at time step $t$.
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i}$}] The $i$-th particle's position vector as implemented by \acs{PSO}. Also represents the $i$-th parent's position vector as implemented by \acs{DE}.
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i}(t)$}] The $i$-th particle's position vector at time step $t$ as implemented by \acs{PSO}.
+Also represents the $i$-th parent's position vector at time step $t$ as implemented by \acs{DE}.
+	\item [\parbox{2cm}{$\boldsymbol{v}_{i}(t)$}] The $i$-th particle's velocity vector at time step $t$ as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$f(x_{i})$}] The evaluation of the $i$-th particle's solution with respect to the objective function.
+	\item [\parbox{2cm}{$\boldsymbol{y}_{i}(t)$}] The $i$-th particle's personal best position vector at time step $t$ as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i}(0)$}] The $i$-th particle's position vector at time step $0$ as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$\boldsymbol{y}_{i}(0)$}] The $i$-th particle's personal best position vector at time step $0$ as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$\boldsymbol{\hat{y}}_{i}(t)$}] The $i$-th particle's global best position vector as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i}$}] The $i$-th particle's position vector as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$\boldsymbol{x}_{min}$}] The lower bound constraint vector of the position vector's values.
+	\item [\parbox{2cm}{$\boldsymbol{x}_{max}$}] The upper bound constraint vector of the position vector's values.
+	\item [\parbox{2cm}{$v_{ij}(t+1)$}] The $i$-th particle's $j$-th dimension of the velocity vector at time step $t+1$.
+	\item [\parbox{2cm}{$v_{ij}(t)$}] The $i$-th particle's $j$-th dimension of the velocity vector at time step $t$.
+Also used in the mutation operator for \acp{GA} to represent some sampled mutation update value.
+	\item [\parbox{2cm}{$w$}] The inertia weight hyper-parameter as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$c_{1}$}] The cognitive control parameter as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$c_{2}$}] The social control parameter as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$r_{1_{j}}(t)$}] The $j$-th dimension of the first stochastic scaling parameter at time step $t$ as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$r_{2_{j}}(t)$}] The $j$-th dimension of the second stochastic scaling parameter at time step $t$ as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$x_{ij}$}] The $i$-th particle's/entity's $j$-th dimension of the position vector.
+	\item [\parbox{2cm}{$x_{ij}(t)$}] The $i$-th particle's/entity's $j$-th dimension of the position vector at time step $t$.
+	\item [\parbox{2cm}{$y_{ij}$}] The $i$-th particle's $j$-th dimension of the personal best position vector.
+	\item [\parbox{2cm}{$y_{ij}(t)$}] The $i$-th particle's $j$-th dimension of the personal best position vector at time step $t$.
+	\item [\parbox{2cm}{$\boldsymbol{\hat{y}}$}] Short form of the global best position vector.
+	\item [\parbox{2cm}{$\hat{y}_{ij}$}] The $i$-th particle's $j$-th dimension of the global best position vector.
+	\item [\parbox{2cm}{$\hat{y}_{ij}(t)$}] The $i$-th particle's $j$-th dimension of the global best position vector at time step $t$.
+	\item [\parbox{2cm}{$f(\hat{y})$}] The evaluation of the global best position.
+	\item [\parbox{2cm}{$x_{ij}(t+1)$}] The $i$-th particle's $j$-th dimension of the position vector at time step $t+1$.
+	\item [\parbox{2cm}{$\boldsymbol{r}_{1}$}] The vector for the first stochastic scaling parameter as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$\boldsymbol{r}_{2}$}] The vector for the second stochastic scaling parameter as implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$I$}] The total number of particles in the swarm (particle swarm size).
+	\item [\parbox{2cm}{$N$}] An alternative to the particle swarm size.
+	\item [\parbox{2cm}{$j$}] Index used for the dimensions of candidate solutions.
+	\item [\parbox{2cm}{$J$}] The total number of dimensions in the position vector for particles in \acs{PSO}.
+	\item [\parbox{2cm}{$U$}] The uniform distribution.
+	\item [\parbox{2cm}{$v'_{ij}(t+1)$}] The $i$-th particle's $j$-th dimension of the clamped velocity vector at time step $t+1$.
+	\item [\parbox{2cm}{$\boldsymbol{V}_{max}$}] The upper bound of the velocity clamping vector.
+	\item [\parbox{2cm}{$V_{max,j}$}] The $j$-th dimension of the upper bound of the velocity clamping vector.
+	\item [\parbox{2cm}{$\boldsymbol{u}_{i}(t)$}] The $i$-th entity's trial vector at time step $t$ implemented by \acs{DE}.
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{1}}(t)$}] The $i$-th entity's target vector at time step $t$ implemented by \acs{DE}.
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{2}}(t)$}] The $i$-th entity's first selected individual's position vector at time step $t$ implemented by \acs{DE}.
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{3}}(t)$}] The $i$-th entity's second selected individual's position vector at time step $t$ implemented by \acs{DE}.
+	\item [\parbox{2cm}{$i_{1}$}] Index for the target vector in \acs{DE}.
+	\item [\parbox{2cm}{$i_{2}$}] Index for the first selected individual in \acs{DE}.
+	\item [\parbox{2cm}{$i_{3}$}] Index for the second selected individual in \acs{DE}.
+	\item [\parbox{2cm}{$\beta$}] Scale factor as implemented by \acs{DE}.
+	\item [\parbox{2cm}{$\boldsymbol{x}'_{i}(t)$}] The $i$-th offspring's position vector at time step $t$ as implemented by \acs{DE}.
+	\item [\parbox{2cm}{$x'_{ij}(t)$}] The $i$-th offspring's $j$-th dimension of the position vector at time step $t$.
+	\item [\parbox{2cm}{$u_{ij}(t)$}] The $j$-th dimension of the $i$-th entity's trial vector at time step $t$ implemented by \acs{DE}.
+	\item [\parbox{2cm}{$\mathcal{J}$}] The set of crossover points.
+	\item [\parbox{2cm}{$j^{*}$}] Randomly selected crossover point.
+	\item [\parbox{2cm}{$\emptyset$}] The empty set.
+	\item [\parbox{2cm}{$p_{r}$}] The crossover probability i.e. recombination probability.
+	\item [\parbox{2cm}{$f(\boldsymbol{x}_{i}(t))$}] The evaluation of the $i$-th entity's candidate solution at time step $t$.
+	\item [\parbox{2cm}{$f(\boldsymbol{x}'_{i}(t))$}] The evaluation of the $i$-th offspring's candidate solution at time step $t$.
+	\item [\parbox{2cm}{$f(\boldsymbol{y}_{i})$}] The evaluation of the $i$-th particle's personal best position.
+	\item [\parbox{2cm}{$f(\boldsymbol{\hat{y}})$}] The evaluation of the global best position.
+	\item [\parbox{2cm}{$x_{min,j}$}] The $j$-th dimension of the lower bound constraint for an entity's position.
+	\item [\parbox{2cm}{$x_{max,j}$}] The $j$-th dimension of the upper bound constraint for an entity's position.
+	\item [\parbox{2cm}{$\mathcal{C}$}] The set of entities in the population.
+	\item [\parbox{2cm}{$\mathcal{C}(0)$}] The set of entities in the population at time step $0$.
+	\item [\parbox{2cm}{$\mathcal{C}(t)$}] The set of entities in the population at time step $t$.
+	\item [\parbox{2cm}{$\mathcal{C}(t+1)$}] The set of entities in the population at time step $t+1$.
+	\item [\parbox{2cm}{$y$}] Used in \acs{DE} notation to denote the number of difference vectors to include.
+	\item [\parbox{2cm}{$z$}] Used in \acs{DE} notation to denote the type of crossover operator to use.
+	\item [\parbox{2cm}{$p_{c}$}] Probability of producing offspring.
+	\item [\parbox{2cm}{$p_{x}$}] Bitswapping probability.
+	\item [\parbox{2cm}{$m_{j}(t)$}] The $j$-th dimension of the crossover mask, $m$, at time step $t$.
+	\item [\parbox{2cm}{$p_{m}$}] The mutation probability.
+	\item [\parbox{2cm}{$N_{t}$}] Tournament selection size.
+\end{description}
+
 \section{Chapter~\ref{chap:hhs}: Hyper-Heuristics}
 \label{sec:symbols:hhs}
+
+\begin{description}
+	\item [\parbox{2cm}{$K$}] The number of folds to execute for $K$-fold crossover validation.
+\end{description}
 
@@
 
+\begin{description}
+	\item [\parbox{2cm}{$\alpha_{0}$}]
+	\item [\parbox{2cm}{$\alpha_{1}$}]
+	\item [\parbox{2cm}{$\alpha_{k}$}]
+	\item [\parbox{2cm}{$\alpha_{K}$}]
+	\item [\parbox{2cm}{$\alpha$}]
+	\item [\parbox{2cm}{$\bar{A}$}]
+	\item [\parbox{2cm}{$\beta'$ }]
+	\item [\parbox{2cm}{$\beta$}]
+	\item [\parbox{2cm}{$Bin$}]
+	\item [\parbox{2cm}{$\boldsymbol{\alpha'}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\mathcal{D}}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
+	\item [\parbox{2cm}{$\boldsymbol{N}$}]
+	\item [\parbox{2cm}{$\boldsymbol{x_{1}}$}]
+	\item [\parbox{2cm}{$\boldsymbol{x_{i}}$}]
+	\item [\parbox{2cm}{$\boldsymbol{x_{I}}$}]
+	\item [\parbox{2cm}{$\boldsymbol{x}$}]
+	\item [\parbox{2cm}{$\boldsymbol{X}$}]
+	\item [\parbox{2cm}{$\boldsymbol{Y}$}]
+	\item [\parbox{2cm}{$\emptyset$}]
+	\item [\parbox{2cm}{$\Gamma'(n)$}]
+	\item [\parbox{2cm}{$\Gamma(n)$}]
+	\item [\parbox{2cm}{$\Gamma$}]
+	\item [\parbox{2cm}{$\mathbb{R}$}]
+	\item [\parbox{2cm}{$\mathbbm{1}$}]
+	\item [\parbox{2cm}{$\mathcal{A}$}]
+	\item [\parbox{2cm}{$\mathcal{L}$}]
+	\item [\parbox{2cm}{$\overset{\text{iid}}{\sim}$}]
+	\item [\parbox{2cm}{$\psi$}]
+	\item [\parbox{2cm}{$\theta_{1}$}]
+	\item [\parbox{2cm}{$\theta_{k}$}]
+	\item [\parbox{2cm}{$\theta_{K}$}]
+	\item [\parbox{2cm}{$\theta$}]
+	\item [\parbox{2cm}{$A$}]
+	\item [\parbox{2cm}{$B_{1}$}]
+	\item [\parbox{2cm}{$B_{2}$}]
+	\item [\parbox{2cm}{$B_{i}$}]
+	\item [\parbox{2cm}{$B_{j}$}]
+	\item [\parbox{2cm}{$B_{K}$}]
+	\item [\parbox{2cm}{$B(\boldsymbol{\alpha})$}]
+	\item [\parbox{2cm}{$B$}]
+	\item [\parbox{2cm}{$Ber(\theta)$}]
+	\item [\parbox{2cm}{$Beta$}]
+	\item [\parbox{2cm}{$Bin$}]
+	\item [\parbox{2cm}{$c$}]
+	\item [\parbox{2cm}{$Cat$}]
+	\item [\parbox{2cm}{$d$}]
+	\item [\parbox{2cm}{$Dir$}]
+	\item [\parbox{2cm}{$dn$}]
+	\item [\parbox{2cm}{$E[{x_{k}}]$}]
+	\item [\parbox{2cm}{$E[\ln(x_{k})]$}]
+	\item [\parbox{2cm}{$E[\ln(x)]$}]
+	\item [\parbox{2cm}{$E[x_{k}]$}]
+	\item [\parbox{2cm}{$E[x]$}]
+	\item [\parbox{2cm}{$f_{Ber}$}]
+	\item [\parbox{2cm}{$f_{Beta}$}]
+	\item [\parbox{2cm}{$f_{Bin}$}]
+	\item [\parbox{2cm}{$f_{Cat}$}]
+	\item [\parbox{2cm}{$f_{Dir}$}]
+	\item [\parbox{2cm}{$f_{Mul}$}]
+	\item [\parbox{2cm}{$f$}]
+	\item [\parbox{2cm}{$F$}]
+	\item [\parbox{2cm}{$g^{*}$}]
+	\item [\parbox{2cm}{$g$}]
+	\item [\parbox{2cm}{$i$}]
+	\item [\parbox{2cm}{$I$}]
+	\item [\parbox{2cm}{$j$}]
+	\item [\parbox{2cm}{$K$}]
+	\item [\parbox{2cm}{$k$}]
+	\item [\parbox{2cm}{$K$}]
+	\item [\parbox{2cm}{$M[x_{k}]$}]
+	\item [\parbox{2cm}{$M[x]$}]
+	\item [\parbox{2cm}{$m$}]
+	\item [\parbox{2cm}{$M$}]
+	\item [\parbox{2cm}{$Mul$}]
+	\item [\parbox{2cm}{$N_{0}$}]
+	\item [\parbox{2cm}{$N_{1}$}]
+	\item [\parbox{2cm}{$N_{k}$}]
+	\item [\parbox{2cm}{$N_{K}$}]
+	\item [\parbox{2cm}{$n$}]
+	\item [\parbox{2cm}{$N$}]
+	\item [\parbox{2cm}{$p$}]
+	\item [\parbox{2cm}{$S$}]
+	\item [\parbox{2cm}{$v$}]
+	\item [\parbox{2cm}{$x_{1}$}]
+	\item [\parbox{2cm}{$x_{i,k}$}]
+	\item [\parbox{2cm}{$x_{i}$}]
+	\item [\parbox{2cm}{$x_{I}$}]
+	\item [\parbox{2cm}{$x_{j}$}]
+	\item [\parbox{2cm}{$x_{k}$}]
+	\item [\parbox{2cm}{$x_{K}$}]
+	\item [\parbox{2cm}{$x$}]
+	\item [\parbox{2cm}{$y_{1}$}]
+	\item [\parbox{2cm}{$Y_{1}$}]
+	\item [\parbox{2cm}{$y_{2}$}]
+	\item [\parbox{2cm}{$Y_{2}$}]
+	\item [\parbox{2cm}{$y_{i}$}]
+	\item [\parbox{2cm}{$Y_{i}$}]
+	\item [\parbox{2cm}{$y_{n}$}]
+	\item [\parbox{2cm}{$Y_{N}$}]
+\end{description}
+
 \section{Chapter~\ref{chap:bhh}: Bayesian Hyper-Heuristic}
 \label{sec:symbols:bhh}
+
+\begin{description}
+	\item [\parbox{2cm}{$\alpha_{1}$}]
+	\item [\parbox{2cm}{$\alpha_{k}$}]
+	\item [\parbox{2cm}{$\alpha_{K}$}]
+	\item [\parbox{2cm}{$\alpha$}]
+	\item [\parbox{2cm}{$\beta_{1}$}]
+	\item [\parbox{2cm}{$\beta_{2}$}]
+	\item [\parbox{2cm}{$\beta_{j,k}$}]
+	\item [\parbox{2cm}{$\beta_{K}^{J}$}]
+	\item [\parbox{2cm}{$\beta$}]
+	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\beta}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\gamma}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\hat{\phi}}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\hat{\psi}}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\hat{\theta}}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\lambda}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\phi}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\psi}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
+	\item [\parbox{2cm}{$\boldsymbol{C}$}]
+	\item [\parbox{2cm}{$\boldsymbol{E}$}]
+	\item [\parbox{2cm}{$\boldsymbol{H}$}]
+	\item [\parbox{2cm}{$\epsilon(-1)$}]
+	\item [\parbox{2cm}{$\epsilon$}]
+	\item [\parbox{2cm}{$\eta$}]
+	\item [\parbox{2cm}{$\gamma_{0}$}]
+	\item [\parbox{2cm}{$\gamma_{1,k}$}]
+	\item [\parbox{2cm}{$\gamma_{1}$}]
+	\item [\parbox{2cm}{$\gamma_{2,k}$}]
+	\item [\parbox{2cm}{$\gamma_{K}$}]
+	\item [\parbox{2cm}{$\hat{\phi}_{j,k}$}]
+	\item [\parbox{2cm}{$\hat{\psi_{k}}$}]
+	\item [\parbox{2cm}{$\hat{\psi}_{k}$}]
+	\item [\parbox{2cm}{$\hat{\theta_{k}}$}]
+	\item [\parbox{2cm}{$\hat{\theta}_{k}$}]
+	\item [\parbox{2cm}{$\lambda_{1}$}]
+	\item [\parbox{2cm}{$\lambda_{j}$}]
+	\item [\parbox{2cm}{$\lambda_{J}$}]
+	\item [\parbox{2cm}{$\mathbbm{1}_{0}$}]
+	\item [\parbox{2cm}{$\mathbbm{1}_{1}$}]
+	\item [\parbox{2cm}{$\mathbin{\%}$}]
+	\item [\parbox{2cm}{$\mathcal{A}(v)$}]
+	\item [\parbox{2cm}{$\mathcal{L}$}]
+	\item [\parbox{2cm}{$\phi_{j,k}$}]
+	\item [\parbox{2cm}{$\phi_{jk}$}]
+	\item [\parbox{2cm}{$\phi$}]
+	\item [\parbox{2cm}{$\psi_{k}$}]
+	\item [\parbox{2cm}{$\psi_{k}N_{k}$}]
+	\item [\parbox{2cm}{$\psi$}]
+	\item [\parbox{2cm}{$\theta_{k}$}]
+	\item [\parbox{2cm}{$\theta$}]
+	\item [\parbox{2cm}{$A$}]
+	\item [\parbox{2cm}{$B$}]
+	\item [\parbox{2cm}{$Beta$}]
+	\item [\parbox{2cm}{$Bin$}]
+	\item [\parbox{2cm}{$c_{1}$}]
+	\item [\parbox{2cm}{$c_{i,k}$}]
+	\item [\parbox{2cm}{$c_{i}$}]
+	\item [\parbox{2cm}{$Dir$}]
+	\item [\parbox{2cm}{$e_{i,j,k}$}]
+	\item [\parbox{2cm}{$e_{i}$}]
+	\item [\parbox{2cm}{$e_{j}$}]
+	\item [\parbox{2cm}{$E[\phi_{j,k}]$}]
+	\item [\parbox{2cm}{$E[\psi_{k}]$}]
+	\item [\parbox{2cm}{$E[\theta_{k}]$}]
+	\item [\parbox{2cm}{$h_{i,k}$}]
+	\item [\parbox{2cm}{$h_{i}$}]
+	\item [\parbox{2cm}{$h_{k}$}]
+	\item [\parbox{2cm}{$i$}]
+	\item [\parbox{2cm}{$I$}]
+	\item [\parbox{2cm}{$j$}]
+	\item [\parbox{2cm}{$J$}]
+	\item [\parbox{2cm}{$K-1$}]
+	\item [\parbox{2cm}{$k$}]
+	\item [\parbox{2cm}{$K$}]
+	\item [\parbox{2cm}{$L$}]
+	\item [\parbox{2cm}{$LSE$}]
+	\item [\parbox{2cm}{$Mult$}]
+	\item [\parbox{2cm}{$N_{0,k}$}]
+	\item [\parbox{2cm}{$N_{1,k}$}]
+	\item [\parbox{2cm}{$N_{j,k}$}]
+	\item [\parbox{2cm}{$N_{j}$}]
+	\item [\parbox{2cm}{$N_{k}$}]
+	\item [\parbox{2cm}{$N$}]
+	\item [\parbox{2cm}{$S$}]
+	\item [\parbox{2cm}{$t$}]
+\end{description}
 
@@
 
+\begin{description}
+	\item [\parbox{2cm}{$\alpha$}] Used as a scaling parameter for the \acs{LReLU} activation function. Also used as a threshold parameter for the statistical significance tests.
+	\item [\parbox{2cm}{$\eta$}] Learning rate.
+	\item [\parbox{2cm}{$\mathbb{R}$}] Real-number space.
+	\item [\parbox{2cm}{$v_{ij}$}] The $j$-th dimension of the velocity vector of the $i$-th particle in the population implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$x_{ij}$}] The $j$-th dimension of the position vector of the $i$-th particle in the population implemented by \acs{PSO}.
+\end{description}
+
 \section{Chapter~\ref{chap:results}: Results}
@@
 
-\section{Chapter~\ref{chap:conclusion}: Conclusion}
-\label{sec:symbols:conclusion}
+\begin{description}
+	\item [\parbox{2cm}{$\alpha_{0}$}]
+	\item [\parbox{2cm}{$\alpha_{6}$}]
+	\item [\parbox{2cm}{$\alpha_{7}$}]
+	\item [\parbox{2cm}{$\alpha_{8}$}]
+	\item [\parbox{2cm}{$\alpha_{i} = 50$}]
+	\item [\parbox{2cm}{$\boldsymbol{{H}}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\phi}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\psi}$}]
+	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
+	\item [\parbox{2cm}{$\boldsymbol{C}$}]
+	\item [\parbox{2cm}{$\boldsymbol{E}$}]
+	\item [\parbox{2cm}{$\boldsymbol{H}$}]
+	\item [\parbox{2cm}{$\pm$}]
+	\item [\parbox{2cm}{$\theta_{0}$}]
+	\item [\parbox{2cm}{$\theta_{6}$}]
+	\item [\parbox{2cm}{$\theta_{7}$}]
+	\item [\parbox{2cm}{$\theta_{8}$}]
+	\item [\parbox{2cm}{$c_{1}$}]
+	\item [\parbox{2cm}{$Cat$}]
+	\item [\parbox{2cm}{$Dir$}]
+	\item [\parbox{2cm}{$e_{0}$}]
+	\item [\parbox{2cm}{$h_{0}$}]
+	\item [\parbox{2cm}{$h_{6}$}]
+	\item [\parbox{2cm}{$h_{7}$}]
+	\item [\parbox{2cm}{$h_{8}$}]
+	\item [\parbox{2cm}{$i$}]
+	\item [\parbox{2cm}{$K$}]
+\end{description}

### 2022-12-09 dissertation/chapters/03-heuristics.tex
✨ (symbols): Chapter 2 done
✨ (symbols): Chapters 3,4,7 done

@@
 The learning rate controls the step-size that is taken in the direction of the negative gradient at each time step.
-Assuming the use of \acs{SSE} as the loss function, the partial derivative of $\epsilon$, relative to the weight $w$, at index $i$, is given as
+Assuming the use of \acs{SSE} as the loss function, the partial derivative of $\epsilon$, relative to the weight vector $\boldsymbol{w}$, at index $i$, is given as
 
@@
 	\label{eq:heuristics:gd:update_step_part_3}
-      \frac{\partial \epsilon}{\partial w_{i}} = -2(t_{p} - o_{p})\frac{\partial f}{\partial net_{p}}z_{i,p}
-\end{equation}
-
-where $t_{p}$ refers to the target value for pattern $p$, $o_{p}$ refers to the output value for pattern $p$, $f$ refers to the \index{activation function}activation function, $net_{p}$ refers to the \index{net input signal}net input signal for pattern $p$, and $z_{i,p}$ refers to the input value at index $i$ for pattern $p$.
+	\frac{\partial \epsilon}{\partial w_{i}} = -2(t_{i,p} - o_{i,p})\frac{\partial f}{\partial net_{p}}z_{i,p}
+\end{equation}
+
+where $t_{i,p}$ refers to the $i$-th element of the target value for pattern $p$, $o_{i,p}$ refers to the $i$-th element of the output value for pattern $p$, $f$ refers to the \index{activation function}activation function, $net_{p}$ refers to the \index{net input signal}net input signal for pattern $p$, and $z_{i,p}$ refers to the input value at index $i$ for pattern $p$.
 
@@
 A simplified notation is proposed from which the gradient-based heuristics can be compared.
-Consider a simplification of the update-step for \acs{SGD} as presented in Equations~\eqref{eq:heuristics:gd:update_step_part_1} and~\eqref{eq:heuristics:gd:update_step_part_2} where $\frac{\partial \epsilon}{\partial w_{i}}$ is simply represented as the gradient term $g$, resulting in a simplified weight update step and is given as
+Consider a simplification of the update-step for \acs{SGD} as presented in Equations~\eqref{eq:heuristics:gd:update_step_part_1} and~\eqref{eq:heuristics:gd:update_step_part_2} where $\frac{\partial \epsilon}{\partial w_{i}}$ is simply represented as the gradient term $\boldsymbol{g}$, resulting in a simplified weight update step and is given as
 
@@
 	\begin{split}
-            w_{t+1} = w_{t} - \frac{\eta}{\sqrt{G_{t,i} + \epsilon}} \odot g_{t,i}
+		w_{t+1,i} = w_{t,i} - \frac{\eta}{\sqrt{G_{t,i} + \epsilon}} \odot g_{t,i}
 	\end{split}
@@
 In Equations~\eqref{eq:heuristics:gd:adam_part_1} and~\eqref{eq:heuristics:gd:adam_part_2} above, $\beta_{1}$ and $\beta_{2}$ are decay rates, similar to $\alpha$ for \acs{Momentum}.
-\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} suggest default values $B_{1}=0.9$, $B_{2}=0.999$ and $\epsilon = 1 \times 10^{-8}$.
+\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} suggest default values $\beta_{1}=0.9$, $\beta_{2}=0.999$ and $\epsilon = 1 \times 10^{-8}$.
 
@@
 
-During initialisation, particles are randomly placed within the search space by sampling from a uniform distribution such that $\boldsymbol{x}_{i} \sim U(x_{min}, x_{max})$ and the velocity is set to 0.
+During initialisation, particles are randomly placed within the search space by sampling from a uniform distribution such that $\boldsymbol{x}_{i} \sim U(\boldsymbol{x}_{min}, \boldsymbol{x}_{max})$ and the velocity is set to 0.
 At time step 0, the particle's initial position is set to be the particle's personal best solution such that $\boldsymbol{y}_{i}(0) = \boldsymbol{x}_{i}(0)$.
@@
 In order to address this issues, the concept of \textit{velocity clamping} was introduced~\cite{ref:eberhart:1996}.
-The idea behind velocity clamping is to restrict particle velocities to some $V_{max}$ threshold, modelling a form of terminal velocity.
+The idea behind velocity clamping is to restrict particle velocities to some $\boldsymbol{V_{max}{}$ threshold, modelling a form of terminal velocity.
 Velocity clamping is applied after the velocity update step and is given in Equation~\eqref{eq:heuristics:pso:velocity_clamping} below.
@@
 		\State // Set the personal best position;
-            \If{$f(x_{i}) < f(y_{i})$ }
-            \State $y_{i} = x_{i}$;
+		\If{$f(\boldsymbol{x}_{i}) < f(\boldsymbol{y}_{i})$ }
+		\State $\boldsymbol{y}_{i} = \boldsymbol{x}_{i}$;
 		\EndIf
@@
 		\State // Set the global best position;
-            \If{$f(x_{i}) < f(\hat{y})$ }
-            \State $\hat{y} = x_{i}$;
+		\If{$f(\boldsymbol{x}_{i}) < f(\boldsymbol{\hat{y}})$ }
+		\State $\boldsymbol{\hat{y}} = \boldsymbol{x}_{i}$;
 		\EndIf
@@
 	\begin{split}
-            \boldsymbol{u}_{i}(t) = \boldsymbol{x}_{i_{1}} + \beta(\boldsymbol{x}_{i_{2}}(t) - \boldsymbol{x}_{i_{3}}(t))
+		\boldsymbol{u}_{i}(t) = \boldsymbol{x}_{i_{1}}(t) + \beta(\boldsymbol{x}_{i_{2}}(t) - \boldsymbol{x}_{i_{3}}(t))
 	\end{split}

### 2022-12-09 dissertation/appendix/symbols.tex
✨ (symbols): Chapter 5 done

@@
 \begin{description}
-	\item [\parbox{2cm}{$\alpha_{0}$}]
-	\item [\parbox{2cm}{$\alpha_{1}$}]
-	\item [\parbox{2cm}{$\alpha_{k}$}]
-	\item [\parbox{2cm}{$\alpha_{K}$}]
-	\item [\parbox{2cm}{$\alpha$}]
-	\item [\parbox{2cm}{$\bar{A}$}]
-	\item [\parbox{2cm}{$\beta'$ }]
-	\item [\parbox{2cm}{$\beta$}]
-	\item [\parbox{2cm}{$Bin$}]
-	\item [\parbox{2cm}{$\boldsymbol{\alpha'}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\mathcal{D}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
-	\item [\parbox{2cm}{$\boldsymbol{N}$}]
-	\item [\parbox{2cm}{$\boldsymbol{x_{1}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{x_{i}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{x_{I}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{x}$}]
-	\item [\parbox{2cm}{$\boldsymbol{X}$}]
-	\item [\parbox{2cm}{$\boldsymbol{Y}$}]
-	\item [\parbox{2cm}{$\emptyset$}]
-	\item [\parbox{2cm}{$\Gamma'(n)$}]
-	\item [\parbox{2cm}{$\Gamma(n)$}]
-	\item [\parbox{2cm}{$\Gamma$}]
-	\item [\parbox{2cm}{$\mathbb{R}$}]
-	\item [\parbox{2cm}{$\mathbbm{1}$}]
-	\item [\parbox{2cm}{$\mathcal{A}$}]
-	\item [\parbox{2cm}{$\mathcal{L}$}]
-	\item [\parbox{2cm}{$\overset{\text{iid}}{\sim}$}]
-	\item [\parbox{2cm}{$\psi$}]
-	\item [\parbox{2cm}{$\theta_{1}$}]
-	\item [\parbox{2cm}{$\theta_{k}$}]
-	\item [\parbox{2cm}{$\theta_{K}$}]
-	\item [\parbox{2cm}{$\theta$}]
-	\item [\parbox{2cm}{$A$}]
-	\item [\parbox{2cm}{$B_{1}$}]
-	\item [\parbox{2cm}{$B_{2}$}]
-	\item [\parbox{2cm}{$B_{i}$}]
-	\item [\parbox{2cm}{$B_{j}$}]
-	\item [\parbox{2cm}{$B_{K}$}]
-	\item [\parbox{2cm}{$B(\boldsymbol{\alpha})$}]
-	\item [\parbox{2cm}{$B$}]
-	\item [\parbox{2cm}{$Ber(\theta)$}]
-	\item [\parbox{2cm}{$Beta$}]
-	\item [\parbox{2cm}{$Bin$}]
-	\item [\parbox{2cm}{$c$}]
-	\item [\parbox{2cm}{$Cat$}]
-	\item [\parbox{2cm}{$d$}]
-	\item [\parbox{2cm}{$Dir$}]
-	\item [\parbox{2cm}{$dn$}]
-	\item [\parbox{2cm}{$E[{x_{k}}]$}]
-	\item [\parbox{2cm}{$E[\ln(x_{k})]$}]
-	\item [\parbox{2cm}{$E[\ln(x)]$}]
-	\item [\parbox{2cm}{$E[x_{k}]$}]
-	\item [\parbox{2cm}{$E[x]$}]
-	\item [\parbox{2cm}{$f_{Ber}$}]
-	\item [\parbox{2cm}{$f_{Beta}$}]
-	\item [\parbox{2cm}{$f_{Bin}$}]
-	\item [\parbox{2cm}{$f_{Cat}$}]
-	\item [\parbox{2cm}{$f_{Dir}$}]
-	\item [\parbox{2cm}{$f_{Mul}$}]
-	\item [\parbox{2cm}{$f$}]
-	\item [\parbox{2cm}{$F$}]
-	\item [\parbox{2cm}{$g^{*}$}]
-	\item [\parbox{2cm}{$g$}]
-	\item [\parbox{2cm}{$i$}]
-	\item [\parbox{2cm}{$I$}]
-	\item [\parbox{2cm}{$j$}]
-	\item [\parbox{2cm}{$K$}]
-	\item [\parbox{2cm}{$k$}]
-	\item [\parbox{2cm}{$K$}]
-	\item [\parbox{2cm}{$M[x_{k}]$}]
-	\item [\parbox{2cm}{$M[x]$}]
-	\item [\parbox{2cm}{$m$}]
-	\item [\parbox{2cm}{$M$}]
-	\item [\parbox{2cm}{$Mul$}]
-	\item [\parbox{2cm}{$N_{0}$}]
-	\item [\parbox{2cm}{$N_{1}$}]
-	\item [\parbox{2cm}{$N_{k}$}]
-	\item [\parbox{2cm}{$N_{K}$}]
-	\item [\parbox{2cm}{$n$}]
-	\item [\parbox{2cm}{$N$}]
-	\item [\parbox{2cm}{$p$}]
-	\item [\parbox{2cm}{$S$}]
-	\item [\parbox{2cm}{$v$}]
-	\item [\parbox{2cm}{$x_{1}$}]
-	\item [\parbox{2cm}{$x_{i,k}$}]
-	\item [\parbox{2cm}{$x_{i}$}]
-	\item [\parbox{2cm}{$x_{I}$}]
-	\item [\parbox{2cm}{$x_{j}$}]
-	\item [\parbox{2cm}{$x_{k}$}]
-	\item [\parbox{2cm}{$x_{K}$}]
-	\item [\parbox{2cm}{$x$}]
-	\item [\parbox{2cm}{$y_{1}$}]
-	\item [\parbox{2cm}{$Y_{1}$}]
-	\item [\parbox{2cm}{$y_{2}$}]
-	\item [\parbox{2cm}{$Y_{2}$}]
-	\item [\parbox{2cm}{$y_{i}$}]
-	\item [\parbox{2cm}{$Y_{i}$}]
-	\item [\parbox{2cm}{$y_{n}$}]
-	\item [\parbox{2cm}{$Y_{N}$}]
+	\item [\parbox{2cm}{$A$}] Random event.
+	\item [\parbox{2cm}{$P$}] The probability of some event.
+	\item [\parbox{2cm}{$N$}] The total number of events observed.
+	\item [\parbox{2cm}{$B$}] Random event.
+	\item [\parbox{2cm}{$\bar{A}$}] Not observing random event $A$.
+	\item [\parbox{2cm}{$B_{1}$}] The first set in the partition $S$.
+	\item [\parbox{2cm}{$B_{2}$}] The second set in the partition $S$.
+	\item [\parbox{2cm}{$B_{i}$}] The $i$-th set in the partition $S$.
+	\item [\parbox{2cm}{$B_{j}$}] The $j$-th set in the partition $S$.
+	\item [\parbox{2cm}{$B_{K}$}] The last set in the partition $S$.
+	\item [\parbox{2cm}{$S$}] The union of mutually exclusion subsets. Also referred to as the probability simplex.
+	\item [\parbox{2cm}{$\emptyset$}] The empty set.
+	\item [\parbox{2cm}{$i$}] Index to track sets in partition $S$. Also used as a general index in random variables in $I$ dimensions.
+	\item [\parbox{2cm}{$j$}] Index to track sets in partition $S$. Also used as a general index in random variables in $J$ dimensions.
+	\item [\parbox{2cm}{$k$}] Index used to denote class $k$ in $K$ classes. Also used as a general index in random variables in $K$ dimensions.
+	\item [\parbox{2cm}{$K$}] The total number of sets in the partition $S$. Also used to denote the number of classes in the Dirichlet probability distribution.
+	\item [\parbox{2cm}{$\alpha$}] Shape parameter for the Beta probability distribution. Also used for confidence levels for the statistical tests.
+	\item [\parbox{2cm}{$x$}] Random variable used by various probability distributions. Also referred to as a realisation of an event that occurred as a results of a random process $X$.
+	\item [\parbox{2cm}{$\beta$}] Shape parameter for the Beta probability distribution.
+	\item [\parbox{2cm}{$\mathbb{R}$}] The real-number space.
+	\item [\parbox{2cm}{$Beta$}] The Beta probability distribution.
+	\item [\parbox{2cm}{$f_{Beta}$}] The \acs{PDF} of the Beta probability distribution.
+	\item [\parbox{2cm}{$B(\alpha, \beta)$}] The normalising constant used in the \acs{PDF} of the Beta probability distribution.
+	\item [\parbox{2cm}{$\Gamma$}] The Gamma function.
+	\item [\parbox{2cm}{$n$}] Input parameter to the Gamma function.
+	\item [\parbox{2cm}{$E[x]$}] The expected value of the distribution of $x$.
+	\item [\parbox{2cm}{$E[\ln(x)]$}] The expected value of the natural logarithm of $x$.
+	\item [\parbox{2cm}{$\psi$}] The logarithmic derivative of the Gamma function, called the Digamma Function.
+	\item [\parbox{2cm}{$\Gamma(n)$}] The Gamma function over input $n$.
+	\item [\parbox{2cm}{$\Gamma'(n)$}] The first derivative of the Gamma function over input $n$.
+	\item [\parbox{2cm}{$M[x]$}] The mode of the distribution of $x$.
+	\item [\parbox{2cm}{$\boldsymbol{x}$}] The random variable for various probability distributions in multiple dimensions.
+	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}] The concentration parameter vector that parameterises the Dirichlet probability distribution.
+	\item [\parbox{2cm}{$\alpha_{1}$}] The first dimension of the concentration parameter $\boldsymbol{\alpha}$.
+	\item [\parbox{2cm}{$\alpha_{k}$}] The $k$-th dimension of the concentration parameter $\boldsymbol{\alpha}$.
+	\item [\parbox{2cm}{$\alpha_{K}$}] The last dimension of the concentration parameter $\boldsymbol{\alpha}$.
+	\item [\parbox{2cm}{$Dir$}] The Dirichlet probability distribution.
+	\item [\parbox{2cm}{$f_{Dir}$}] The \acs{PDF} of the Dirichlet probability distribution.
+	\item [\parbox{2cm}{$B(\boldsymbol{\alpha})$}] The normalising constant used in the \acs{PDF} of the Dirichlet probability distribution.
+	\item [\parbox{2cm}{$\alpha_{0}$}] The sum of all the values in each dimension of the concentration parameter $\boldsymbol{\alpha}$.
+	\item [\parbox{2cm}{$x_{1}$}] The first dimension of the random variable. Also used as the first random event.
+	\item [\parbox{2cm}{$x_{i}$}] The $i$-th dimension of the random variable. Also used as the $i$-th random event.
+	\item [\parbox{2cm}{$x_{j}$}] The $j$-th dimension of the random variable. Also used as the $j$-th random event.
+	\item [\parbox{2cm}{$x_{k}$}] The $k$-th dimension of the random variable. Also used as the $k$-th random event.
+	\item [\parbox{2cm}{$x_{I}$}] The last dimension of the random variable with $I$ dimensions. Also used as the last random event in $I$ random events.
+	\item [\parbox{2cm}{$x_{K}$}] The last dimension of the random variable with $K$ dimensions. Also used as the last random event in $K$ random events.
+	\item [\parbox{2cm}{$c$}] Symmetric distribution constant.
+	\item [\parbox{2cm}{$E[x_{k}]$}] The expected value of the $k$-th dimension of the random variable.
+	\item [\parbox{2cm}{$E[\ln(x_{k})]$}] The expected value of the natural logarithm of the $k$-th dimension of the random variable.
+	\item [\parbox{2cm}{$M[x_{k}]$}] The mode of the $k$-th dimension of the random variable.
+	\item [\parbox{2cm}{$\theta$}] Success probability for the Bernoulli probability distribution.
+	\item [\parbox{2cm}{$Ber$}] The Bernoulli probability distribution.
+	\item [\parbox{2cm}{$f_{Ber}$}] The \acs{PMF} for the Bernoulli probability distribution.
+	\item [\parbox{2cm}{$Bin$}] The Binomial probability distribution.
+	\item [\parbox{2cm}{$f_{Bin}$}] The \acs{PMF} for the Binomial probability distribution.
+	\item [\parbox{2cm}{$\boldsymbol{\theta}$}] The probability vector in multiple dimensions used by multiple probability distributions.
+	\item [\parbox{2cm}{$\theta_{1}$}] The first dimension of the probability vector $\boldsymbol{\theta}$.
+	\item [\parbox{2cm}{$\theta_{k}$}] The $k$-th dimension of the probability vector $\boldsymbol{\theta}$.
+	\item [\parbox{2cm}{$\theta_{K}$}] The last dimension of the probability vector $\boldsymbol{\theta}$.
+	\item [\parbox{2cm}{$Cat$}] The Categorical probability distribution.
+	\item [\parbox{2cm}{$f_{Cat}$}] The \acs{PMF} for the Categorical probability distribution.
+	\item [\parbox{2cm}{$\mathbbm{1}$}] Indicator function.
+	\item [\parbox{2cm}{$Mul$}] The Multinomial probability distribution.
+	\item [\parbox{2cm}{$f_{Mul}$}] The \acs{PMF} for the Multinomial probability distribution.
+	\item [\parbox{2cm}{$\boldsymbol{X}$}] Matrix of Bernoulli probability distributions. Also used to represent the outcomes of $I$ independent, identical (iid) random events.
+	\item [\parbox{2cm}{$x_{i,k}$}] The $k$-th dimension of the $i$-th random event vector $\boldsymbol{x}$.
+	\item [\parbox{2cm}{$N_{k}$}] is a summary variable, denoting the number of times a category $k$ occurs over all trials in $N$.
+	\item [\parbox{2cm}{$\boldsymbol{x_{1}}$}] The outcomes of the first random event in $I$ independent, identical (iid) events for $k$ categories.
+	\item [\parbox{2cm}{$\boldsymbol{x_{I}}$}] The outcomes of the last random event in $I$ independent, identical (iid) events for $k$ categories.
+	\item [\parbox{2cm}{$\boldsymbol{x_{i}}$}] The outcomes of the $i$-th random event in $I$ independent, identical (iid) events for $k$ categories.
+	\item [\parbox{2cm}{$\overset{\text{iid}}{\sim}$}] Independent, identical (iid) random events.
+	\item [\parbox{2cm}{$\boldsymbol{N}$}] The counts for each occurrence of a category $k$ over $I$ independent, identical (iid) events.
+	\item [\parbox{2cm}{$I$}] The total number of independent, identical (iid) random events.
+	\item [\parbox{2cm}{$\mathcal{A}(v)$}] Functional form of priors.
+	\item [\parbox{2cm}{$\mathbb{R}$}] Real-number space.
+	\item [\parbox{2cm}{$\mathcal{L}$}] The likelihood function.
+	\item [\parbox{2cm}{$\boldsymbol{\mathcal{D}}$}] All the prior data of $\boldsymbol{X}$
+	\item [\parbox{2cm}{$N_{0}$}] Summary variable tracking the number of unsuccessful Boolean outcomes.
+	\item [\parbox{2cm}{$N_{1}$}] Summary variable tracking the number of successful Boolean outcomes.
+	\item [\parbox{2cm}{$N_{K}$}] Summary variable denoting the number of times category $k$ occurs.
+	\item [\parbox{2cm}{$\alpha'$ }] The update form of the prior parameter, $\alpha$, for a Beta probability distribution.
+	\item [\parbox{2cm}{$\beta'$ }] The update form of the prior parameter, $\beta$, for a Beta probability distribution.
+	\item [\parbox{2cm}{$\boldsymbol{\alpha'}$}] Update form of the prior parameter, $\boldsymbol{\alpha}$, for a Dirichlet probability distribution.
+	\item [\parbox{2cm}{$p$}] The statistical $p$-value.
+	\item [\parbox{2cm}{$\boldsymbol{Y}$}] A vector of random events.
+	\item [\parbox{2cm}{$Y_{1}$}] The first random event in $\boldsymbol{Y}$.
+	\item [\parbox{2cm}{$Y_{2}$}] The second random event in $\boldsymbol{Y}$.
+	\item [\parbox{2cm}{$Y_{i}$}] The $i$-th random event in $\boldsymbol{Y}$.
+	\item [\parbox{2cm}{$Y_{N}$}] The last random event in $\boldsymbol{Y}$ with $N$ events.
+	\item [\parbox{2cm}{$y_{1}$}] The realisation of the first random event in $\boldsymbol{Y}$.
+	\item [\parbox{2cm}{$y_{2}$}] The realisation of the second random event in $\boldsymbol{Y}$.
+	\item [\parbox{2cm}{$y_{i}$}] The realisation of the $i$-th random event in $\boldsymbol{Y}$.
+	\item [\parbox{2cm}{$y_{n}$}] The realisation of the $n$-th random event in $\boldsymbol{Y}$ with $N$ events.
+	\item [\parbox{2cm}{$g$}] Prior density.
+	\item [\parbox{2cm}{$g^{*}$}] Posterior density.
+	\item [\parbox{2cm}{$f$}] General symbol used for functions. Used for likelihood functions, \acp{PMF} and \acp{PDF}.
+	\item [\parbox{2cm}{$m$}] The marginal density function.
+	\item [\parbox{2cm}{$M$}] The symbol used for a male outcome in the mice experiment.
+	\item [\parbox{2cm}{$F$}] The symbol used for a female outcome in the mice experiment.
 \end{description}

### 2022-12-09 dissertation/appendix/symbols.tex
Symbols done

@@
 \begin{description}
-	\item [\parbox{2cm}{$\alpha_{1}$}]
-	\item [\parbox{2cm}{$\alpha_{k}$}]
-	\item [\parbox{2cm}{$\alpha_{K}$}]
-	\item [\parbox{2cm}{$\alpha$}]
-	\item [\parbox{2cm}{$\beta_{1}$}]
-	\item [\parbox{2cm}{$\beta_{2}$}]
-	\item [\parbox{2cm}{$\beta_{j,k}$}]
-	\item [\parbox{2cm}{$\beta_{K}^{J}$}]
-	\item [\parbox{2cm}{$\beta$}]
-	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\beta}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\gamma}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\hat{\phi}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\hat{\psi}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\hat{\theta}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\lambda}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\phi}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\psi}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
-	\item [\parbox{2cm}{$\boldsymbol{C}$}]
-	\item [\parbox{2cm}{$\boldsymbol{E}$}]
-	\item [\parbox{2cm}{$\boldsymbol{H}$}]
-	\item [\parbox{2cm}{$\epsilon(-1)$}]
-	\item [\parbox{2cm}{$\epsilon$}]
-	\item [\parbox{2cm}{$\eta$}]
-	\item [\parbox{2cm}{$\gamma_{0}$}]
-	\item [\parbox{2cm}{$\gamma_{1,k}$}]
-	\item [\parbox{2cm}{$\gamma_{1}$}]
-	\item [\parbox{2cm}{$\gamma_{2,k}$}]
-	\item [\parbox{2cm}{$\gamma_{K}$}]
-	\item [\parbox{2cm}{$\hat{\phi}_{j,k}$}]
-	\item [\parbox{2cm}{$\hat{\psi_{k}}$}]
-	\item [\parbox{2cm}{$\hat{\psi}_{k}$}]
-	\item [\parbox{2cm}{$\hat{\theta_{k}}$}]
-	\item [\parbox{2cm}{$\hat{\theta}_{k}$}]
-	\item [\parbox{2cm}{$\lambda_{1}$}]
-	\item [\parbox{2cm}{$\lambda_{j}$}]
-	\item [\parbox{2cm}{$\lambda_{J}$}]
-	\item [\parbox{2cm}{$\mathbbm{1}_{0}$}]
-	\item [\parbox{2cm}{$\mathbbm{1}_{1}$}]
-	\item [\parbox{2cm}{$\mathbin{\%}$}]
-	\item [\parbox{2cm}{$\mathcal{A}(v)$}]
-	\item [\parbox{2cm}{$\mathcal{L}$}]
-	\item [\parbox{2cm}{$\phi_{j,k}$}]
-	\item [\parbox{2cm}{$\phi_{jk}$}]
-	\item [\parbox{2cm}{$\phi$}]
-	\item [\parbox{2cm}{$\psi_{k}$}]
-	\item [\parbox{2cm}{$\psi_{k}N_{k}$}]
-	\item [\parbox{2cm}{$\psi$}]
-	\item [\parbox{2cm}{$\theta_{k}$}]
-	\item [\parbox{2cm}{$\theta$}]
-	\item [\parbox{2cm}{$A$}]
-	\item [\parbox{2cm}{$B$}]
-	\item [\parbox{2cm}{$Beta$}]
-	\item [\parbox{2cm}{$Bin$}]
-	\item [\parbox{2cm}{$c_{1}$}]
-	\item [\parbox{2cm}{$c_{i,k}$}]
-	\item [\parbox{2cm}{$c_{i}$}]
-	\item [\parbox{2cm}{$Dir$}]
-	\item [\parbox{2cm}{$e_{i,j,k}$}]
-	\item [\parbox{2cm}{$e_{i}$}]
-	\item [\parbox{2cm}{$e_{j}$}]
-	\item [\parbox{2cm}{$E[\phi_{j,k}]$}]
-	\item [\parbox{2cm}{$E[\psi_{k}]$}]
-	\item [\parbox{2cm}{$E[\theta_{k}]$}]
-	\item [\parbox{2cm}{$h_{i,k}$}]
-	\item [\parbox{2cm}{$h_{i}$}]
-	\item [\parbox{2cm}{$h_{k}$}]
-	\item [\parbox{2cm}{$i$}]
-	\item [\parbox{2cm}{$I$}]
-	\item [\parbox{2cm}{$j$}]
-	\item [\parbox{2cm}{$J$}]
-	\item [\parbox{2cm}{$K-1$}]
-	\item [\parbox{2cm}{$k$}]
-	\item [\parbox{2cm}{$K$}]
-	\item [\parbox{2cm}{$L$}]
-	\item [\parbox{2cm}{$LSE$}]
-	\item [\parbox{2cm}{$Mult$}]
-	\item [\parbox{2cm}{$N_{0,k}$}]
-	\item [\parbox{2cm}{$N_{1,k}$}]
-	\item [\parbox{2cm}{$N_{j,k}$}]
-	\item [\parbox{2cm}{$N_{j}$}]
-	\item [\parbox{2cm}{$N_{k}$}]
-	\item [\parbox{2cm}{$N$}]
-	\item [\parbox{2cm}{$S$}]
-	\item [\parbox{2cm}{$t$}]
+	\item [\parbox{2cm}{$\boldsymbol{H}$}] The event of observing heuristics.
+	\item [\parbox{2cm}{$\boldsymbol{E}$}] The event of observing entities.
+	\item [\parbox{2cm}{$\boldsymbol{C}$}] The event of observing credit assignments upon meeting credit assignment criteria.
+	\item [\parbox{2cm}{$A$}] A random event.
+	\item [\parbox{2cm}{$B$}] A random event.
+	\item [\parbox{2cm}{$I$}] The maximum number of instances in the replay window.
+	\item [\parbox{2cm}{$N$}] The maximum number of random events observed.
+	\item [\parbox{2cm}{$J$}] The entity pool (population) size.
+	\item [\parbox{2cm}{$K$}] The heuristic pool size.
+	\item [\parbox{2cm}{$L$}] The number of credit assignment output classes.
+	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}] The concentration parameters for the heuristic probability distribution.
+	\item [\parbox{2cm}{$\alpha_{1}$}] The first dimension of the concentration parameter, $\boldsymbol{\alpha}$.
+	\item [\parbox{2cm}{$\alpha_{k}$}] The dimension of $\boldsymbol{\alpha}$ associated with class $k$.
+	\item [\parbox{2cm}{$\alpha_{K}$}] The $k$-th dimension of the concentration parameter, $\boldsymbol{\alpha}$.
+	\item [\parbox{2cm}{$\boldsymbol{\beta}$}] The concentration parameters for the entity-heuristic probability distributions.
+	\item [\parbox{2cm}{$\beta_{1}$}] The first dimension of the concentration parameter, $\boldsymbol{\beta}$.
+	\item [\parbox{2cm}{$\beta_{2}$}] The second dimension of the concentration parameter, $\boldsymbol{\beta}$.
+	\item [\parbox{2cm}{$\beta_{j,k}$}] The $j$-th entity's concentration parameter associated with heuristic $k$.
+	\item [\parbox{2cm}{$\boldsymbol{\gamma}$}] The concentration parameters for the credit-heuristic probability distribution.
+	\item [\parbox{2cm}{$\gamma_{0}$}] The zeroth dimension of the concentration parameter, $\boldsymbol{\gamma}$.
+	\item [\parbox{2cm}{$\gamma_{1}$}] The first dimension of the concentration parameter, $\boldsymbol{\gamma}$.
+	\item [\parbox{2cm}{$\gamma_{K}$}] The $k$-th dimension of the concentration parameter, $\boldsymbol{\gamma}$.
+	\item [\parbox{2cm}{$\boldsymbol{\theta}$}] The heuristic probability distribution.
+	\item [\parbox{2cm}{$\boldsymbol{\phi}$}] The entity-heuristic probability distribution.
+	\item [\parbox{2cm}{$Dir$}] The Dirichlet probability distribution.
+	\item [\parbox{2cm}{$\boldsymbol{\psi}$}] The credit-heuristic probability distribution.
+	\item [\parbox{2cm}{$Beta$}] The Beta probability distribution.
+	\item [\parbox{2cm}{$Mult$}] The Multinomial probability distribution.
+	\item [\parbox{2cm}{$Bin$}] The Binomial probability distribution.
+	\item [\parbox{2cm}{$h_{i,k}$}] The realisation of the $i$-th event of observing heuristic $k$.
+	\item [\parbox{2cm}{$\theta_{k}$}] The heuristic selection probability for heuristic $k$.
+	\item [\parbox{2cm}{$\mathbbm{1}_{0}$}] The indicator function yielding a failure/non-occurrence.
+	\item [\parbox{2cm}{$\mathbbm{1}_{1}$}] The indicator function yielding a success/occurrence.
+	\item [\parbox{2cm}{$N_{k}$}] A summary variable denoting the count of occurrences of the event $h_{i}$ taking on class $k$ in $I$ independent, identical runs.
+	\item [\parbox{2cm}{$e_{i,j,k}$}] The realisation of the $i$-th event of observing heuristic $k$ for selected for entity $j$.
+	\item [\parbox{2cm}{$\phi_{j,k}$}] The entity-heuristic selection probability for entity $j$ and heuristic $k$.
+	\item [\parbox{2cm}{$N_{j,k}$}] A summary variable denoting the count of occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on class $k$ in $I$ independent, identical runs.
+	\item [\parbox{2cm}{$k$}] Index generally associated to heuristic $k$.
+	\item [\parbox{2cm}{$j$}] Index generally associated to entity $j$.
+	\item [\parbox{2cm}{$i$}] Index generally associated to event/run $i$.
+	\item [\parbox{2cm}{$h_{i}$}] The $i$-th event of observing heuristics.
+	\item [\parbox{2cm}{$c_{i,k}$}] The realisation of the $i$-th event of observing a credit assignment $i$ to heuristic $k$.
+	\item [\parbox{2cm}{$\psi_{k}$}] The heuristic-credit-assignment probability for credit assignment success and heuristic $k$.
+	\item [\parbox{2cm}{$N_{0,k}$}] The count of occurrences of the events $c_{i}$ taking on a failure.
+	\item [\parbox{2cm}{$N_{1,k}$}] The count of occurrences of the events $c_{i}$ taking on a success.
+	\item [\parbox{2cm}{$c_{i}$}] The $i$-th event of observing credit assignments.
+	\item [\parbox{2cm}{$LSE$}] The log-sum-exp trick/function.
+	\item [\parbox{2cm}{$\hat{\theta}_{k}$}] The expected value of the probability of selecting heuristic $k$.
+	\item [\parbox{2cm}{$E[\theta_{k}]$}] The expected value of the probability of selecting heuristic $k$.
+	\item [\parbox{2cm}{$N_{j}$}] The count of the occurrences of observing entity $j$.
+	\item [\parbox{2cm}{$\hat{\phi}_{j,k}$}] The expected value of the probability of selecting heuristic $k$ for entity $j$.
+	\item [\parbox{2cm}{$E[\phi_{j,k}]$}] The expected value of the probability of selecting heuristic $k$ for entity $j$.
+	\item [\parbox{2cm}{$\hat{\psi}_{k}$}] The expected value of the probability of selecting heuristic $k$ and observing credit assignments.
+	\item [\parbox{2cm}{$E[\psi_{k}]$}] The expected value of the probability of selecting heuristic $k$ and observing credit assignments.
+	\item [\parbox{2cm}{$\boldsymbol{\hat{\theta}}$}] The expected value of the heuristic selection probabilities.
+	\item [\parbox{2cm}{$\boldsymbol{\hat{\phi}}$}] The expected value of the entity-heuristic probabilities.
+	\item [\parbox{2cm}{$\boldsymbol{\hat{\psi}}$}] The expected value of the heuristic-credit-assignment probabilities.
+	\item [\parbox{2cm}{$\mathcal{L}$}] The likelihood function.
+	\item [\parbox{2cm}{$\boldsymbol{\lambda}$}] Error vector.
+	\item \item [\parbox{2cm}{$\lambda_{1}$}] The first dimension of the error vector, $\boldsymbol{\lambda}$.
+	\item [\parbox{2cm}{$\lambda_{j}$}] The $j$-th dimension of the error vector, $\boldsymbol{\lambda}$.
+	\item [\parbox{2cm}{$\lambda_{J}$}] The last dimension of the error vector, $\boldsymbol{\lambda}$ in $J$ dimensions.
+	\item [\parbox{2cm}{$\epsilon$}] Error factor.
+	\item [\parbox{2cm}{$\gamma_{1,k}$}] The first dimension of the concentration parameter, $\boldsymbol{\gamma}$ associated with heuristic $k$.
+	\item [\parbox{2cm}{$\gamma_{2,k}$}] The second dimension of the concentration parameter, $\boldsymbol{\gamma}$ associated with heuristic $k$.
+	\item [\parbox{2cm}{$\alpha$}] Concentration parameter for the Beta probability distribution.
+	\item [\parbox{2cm}{$\beta$}] Concentration parameter for the Beta probability distribution.
+
+	\item [\parbox{2cm}{$\eta$}] Learning rate.
+	\item [\parbox{2cm}{$\mathcal{A}(v)$}] Functional form of priors.
+	\item [\parbox{2cm}{$\psi_{k}$}] The successful credit assignment probability for heuristic $k$.
+	\item [\parbox{2cm}{$c_{1}$}] Successful credit allocation.
+	\item [\parbox{2cm}{$e_{i}$}] The $i$-th event of observing entities.
+	\item [\parbox{2cm}{$e_{j}$}] The $j$-th entity.
+	\item [\parbox{2cm}{$h_{k}$}] The $k$-th heuristic.
+	\item [\parbox{2cm}{$S$}] The probability simplex.
+	\item [\parbox{2cm}{$t$}] Time step.
 \end{description}
@@
 \begin{description}
-	\item [\parbox{2cm}{$\alpha_{0}$}]
-	\item [\parbox{2cm}{$\alpha_{6}$}]
-	\item [\parbox{2cm}{$\alpha_{7}$}]
-	\item [\parbox{2cm}{$\alpha_{8}$}]
-	\item [\parbox{2cm}{$\alpha_{i} = 50$}]
-	\item [\parbox{2cm}{$\boldsymbol{{H}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\phi}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\psi}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
-	\item [\parbox{2cm}{$\boldsymbol{C}$}]
-	\item [\parbox{2cm}{$\boldsymbol{E}$}]
-	\item [\parbox{2cm}{$\boldsymbol{H}$}]
-	\item [\parbox{2cm}{$\pm$}]
-	\item [\parbox{2cm}{$\theta_{0}$}]
-	\item [\parbox{2cm}{$\theta_{6}$}]
-	\item [\parbox{2cm}{$\theta_{7}$}]
-	\item [\parbox{2cm}{$\theta_{8}$}]
-	\item [\parbox{2cm}{$c_{1}$}]
-	\item [\parbox{2cm}{$Cat$}]
-	\item [\parbox{2cm}{$Dir$}]
-	\item [\parbox{2cm}{$e_{0}$}]
-	\item [\parbox{2cm}{$h_{0}$}]
-	\item [\parbox{2cm}{$h_{6}$}]
-	\item [\parbox{2cm}{$h_{7}$}]
-	\item [\parbox{2cm}{$h_{8}$}]
-	\item [\parbox{2cm}{$i$}]
-	\item [\parbox{2cm}{$K$}]
+	\item [\parbox{2cm}{$\alpha_{0}$}] The zeroth dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $0$ (\acs{SGD}).
+	\item [\parbox{2cm}{$\alpha_{6}$}] The sixth dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $6$ (\acs{Adam}).
+	\item [\parbox{2cm}{$\alpha_{7}$}] The seventh dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $7$ (\acs{PSO}).
+	\item [\parbox{2cm}{$\alpha_{8}$}] The eight dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $8$ (\acs{GA}).
+	\item [\parbox{2cm}{$\alpha_{i}$}] The $i$-th dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $i$.
+	\item [\parbox{2cm}{$\boldsymbol{H}$}] The event of observing heuristics.
+	\item [\parbox{2cm}{$\boldsymbol{E}$}] The event of observing entities.
+	\item [\parbox{2cm}{$\boldsymbol{C}$}] The event of observing credit assignments upon meeting credit assignment criteria.
+	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}] The concentration parameters for the heuristic probability distribution.
+	\item [\parbox{2cm}{$\boldsymbol{\phi}$}] The entity-heuristic probability distribution.
+	\item [\parbox{2cm}{$\boldsymbol{\psi}$}] The credit-heuristic probability distribution.
+	\item [\parbox{2cm}{$\boldsymbol{\theta}$}] The heuristic probability distribution.
+	\item [\parbox{2cm}{$\theta_{0}$}] The zeroth dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $0$ (\acs{SGD}).
+	\item [\parbox{2cm}{$\theta_{6}$}] The sixth dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $6$ (\acs{Adam}).
+	\item [\parbox{2cm}{$\theta_{7}$}] The seventh dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $7$ (\acs{PSO}).
+	\item [\parbox{2cm}{$\theta_{8}$}] The eight dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $8$ (\acs{GA}).
+	\item [\parbox{2cm}{$c_{1}$}] Successful credit allocation.
+	\item [\parbox{2cm}{$Cat$}] The Categorical probability distribution.
+	\item [\parbox{2cm}{$Dir$}] The Dirichlet probability distribution.
+	\item [\parbox{2cm}{$e_{0}$}] Entity $0$.
+	\item [\parbox{2cm}{$h_{0}$}] Heuristic $0$ (\acs{SGD}).
+	\item [\parbox{2cm}{$h_{6}$}] Heuristic $6$ (\acs{Adam}).
+	\item [\parbox{2cm}{$h_{7}$}] Heuristic $7$ (\acs{PSO}).
+	\item [\parbox{2cm}{$h_{8}$}] Heuristic $8$ (\acs{GA}).
+	\item [\parbox{2cm}{$i$}] General index associated with event/run number.
+	\item [\parbox{2cm}{$K$}] Heuristic pool size.
 \end{description}

### 2022-12-10 dissertation/chapters/01-introduction.tex
Spacing configuration

@@
 \Acf{ML} is one of the most popular fields of research in \acf{AI} studies today.
-In recent years, \acs{ML} research has seen some notable achievements in academia~\cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:vaswani:2017}, as well as the industry at large~\cite{ref:silver:2016, ref:silver2017, ref:zoph:2017, ref:lewis:2017}.
+In recent years, \acs{ML} research has seen some notable achievements in academia~\cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:vaswani:2017}, as well as the industry at large~\cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.
 \acs{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \acs{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1~\cite{ref:silver:2017}.

### 2022-12-10 dissertation/chapters/02-artificial-neural-networks.tex
Spacing configuration

@@
 
-\index{random uniform sampling}Random uniform sampling initialises weights uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $omega_{i} \sim \textit{U} (\omega_{min}, \omega_{max})$, where the $\omega_{min}$ and $\omega_{max}$ are respectfully the lower and upper bounds of the uniform distribution.
+\index{random uniform sampling}Random uniform sampling initialises weights uniformly in the range $[\omega_{min}, \omega_{max}]$, written as $\omega_{i} \sim \textit{U} (\omega_{min}, \omega_{max})$, where the $\omega_{min}$ and $\omega_{max}$ are respectfully the lower and upper bounds of the uniform distribution.
 Suggested parameter values are $(-1, 1)$ or $(-0.5, 0.5)$~\cite{ref:nguyen:1990}.
@@
       \centering
-      \includegraphics[width=0.65\textwidth]{output_modifiers.pdf}
+      \includegraphics[width=0.75\textwidth]{output_modifiers.pdf}
       \caption[The results of \index{softmax}softmax and \index{argmax}argmax]{An illustration of \index{softmax}softmax and \index{argmax}argmax applied after the \index{sigmoid}sigmoid \index{activation function}activation function.}

### 2022-12-10 dissertation/chapters/03-heuristics.tex
Spacing configuration

@@
 
-The accumulation of momentum is presented in Equation~\eqref{eq:heuristics:gd:momentum_part_1}, while the update step is then amended in Equation~\eqref{eq:heuristics:gd:momentum_part_2}.
-
-\begin{equation}
+The accumulation of momentum is given as
+
+\begin{equation}
+	\boldsymbol{v} = \alpha \boldsymbol{v} - \eta \boldsymbol{g}
 	\label{eq:heuristics:gd:momentum_part_1}
-	\begin{split}
-		\boldsymbol{v} = \alpha \boldsymbol{v} - \eta \boldsymbol{g}
-	\end{split}
-\end{equation}
-
-\begin{equation}
+\end{equation}
+
+while the update step is then amended as
+
+\begin{equation}
+	\boldsymbol{w} = \boldsymbol{w} + \boldsymbol{v}
 	\label{eq:heuristics:gd:momentum_part_2}
-	\begin{split}
-		\boldsymbol{w} = \boldsymbol{w} + \boldsymbol{v}
-	\end{split}
 \end{equation}
@@
 In order to address this issues, the concept of \textit{velocity clamping} was introduced~\cite{ref:eberhart:1996}.
-The idea behind velocity clamping is to restrict particle velocities to some $\boldsymbol{V_{max}{}$ threshold, modelling a form of terminal velocity.
+The idea behind velocity clamping is to restrict particle velocities to some $\boldsymbol{V_{max}}$ threshold, modelling a form of terminal velocity.
 Velocity clamping is applied after the velocity update step and is given in Equation~\eqref{eq:heuristics:pso:velocity_clamping} below.

### 2022-12-10 dissertation/chapters/09-conclusion.tex
💚 Dedicated to Taylah, Beané & Aleah

@@
 \begin{itemize}
-      \item A literature study was conducted on all related topics that are relevant to the development of the \acs{BHH} and is provided in Chapters ~\ref{chap:anns} to \ref{chap:probability}.
+      \item A literature study was conducted on all related topics that are relevant to the development of the \acs{BHH} and is provided in Chapters \ref{chap:anns} to \ref{chap:probability}.
 The literature study included background information on \acs{ANN}, existing low-level \index{heuristic}heuristics, meta-learning, \acp{HH}, probability theory, and Bayesian statistics.

### 2023-01-09 article/main.tex
✨ (article): Initial setup

% \documentclass[preprint,12pt]{elsarticle}
%% Use the option review to obtain double line spacing
\documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

\journal{Information Sciences}

\usepackage{acro}

% Feedforward Neural Network
\DeclareAcronym{FFNN}{
      short = FFNN,
      short-plural-form = FFNNs,
      long = \textit{feedforward neural network},
      long-plural-form = \textit{feedforward neural networks}
}

% Hyper-Heuristic
\DeclareAcronym{HH}{
      short = HH,
      short-plural-form = HHs,
      long = \textit{hyper-heuristic},
      long-plural-form = \textit{hyper-heuristics}
}

% Bayesian Hyper-Heuristic
\DeclareAcronym{BHH}{
      short = BHH,
      short-plural-form = BHHs,
      long = \textit{Bayesian hyper-heuristic},
      long-plural-form = \textit{Bayesian hyper-heuristics}
}

\begin{document}

\begin{frontmatter}
  %% Title, authors and addresses

  %% use the tnoteref command within \title for footnotes;
  %% use the tnotetext command for theassociated footnote;
  %% use the fnref command within \author or \address for footnotes;
  %% use the fntext command for theassociated footnote;
  %% use the corref command within \author for corresponding author footnotes;
  %% use the cortext command for theassociated footnote;
  %% use the ead command for the email address,
  %% and the form \ead[url] for the home page:
  %% \title{Title\tnoteref{label1}}
  %% \tnotetext[label1]{}
  %% \author{Name\corref{cor1}\fnref{label2}}
  %% \ead{email address}
  %% \ead[url]{home page}
  %% \fntext[label2]{}
  %% \cortext[cor1]{}
  %% \affiliation{organization={},
  %%             addressline={},
  %%             city={},
  %%             postcode={},
  %%             state={},
  %%             country={}}
  %% \fntext[label3]{}

  \title{Bayesian Hyper-Heuristics}

  %% use optional labels to link authors explicitly to addresses:
  \author[aff:tuks]{A.N.~Schreuder}
  \author[aff:stellenbosch]{Prof.~A.P.~Engelbrecht}
  \author[aff:tuks]{Dr.~A.S.~Bosman}
  \author[aff:wits]{Prof.~C.W.~Cleghorn}

  \affiliation[aff:tuks]{
    organization={University of Pretoria},
    % addressline={Lynnwood Rd},
    city={Pretoria},
    postcode={0002},
    state={Gauteng},
    country={South Africa}
  }

  \affiliation[aff:stellenbosch]{
    organization={Stellenbosch University},
    % addressline={Ryneveld Street},
    city={Stellenbosch},
    postcode={7602},
    state={Western Cape},
    country={South Africa}
  }

  \affiliation[aff:wits]{
    organization={University of the Witwatersrand},
    % addressline={1 Jan Smuts Ave},
    city={Johannesburg},
    postcode={2000},
    state={Gauteng},
    country={South Africa}
  }

  \begin{abstract}

    This work introduces a novel population-based \Acf{BHH}. An empirical study is done by using the \acs{BHH} to train \acsp{FFNN}. An in-depth behaviour analysis is done and the performance of the \acs{BHH} is compared to that of ten popular low-level heuristics, each with different search behaviours. The chosen heuristic pool consists of classic gradient-based heuristics as well as meta-heuristics. The empirical process is executed on fourteen datasets consisting of classification and regression problems with varying characteristics. The \acs{BHH} is shown to be able to train \acsp{FFNN} well and provide an automated method for finding the best heuristic to train the \acsp{FFNN} at various stages of the training process.

  \end{abstract}

  %%Graphical abstract
  % \begin{graphicalabstract}
  % \includegraphics{grabs}
  % \end{graphicalabstract}

  %%Research highlights
  \begin{highlights}
    \item A novel heuristic selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acp{FFNN}. The resulting \acs{HH} is referred to as the \acf{BHH}.

    \item The results of the empirical study show with statistical significance and certainty that the \Acs{BHH} performs generally well on multiple problems. It is shown that, for each problem, the \Acs{BHH} performance is comparable to the best low-level heuristics included in the heuristic selection pool.

    \item The results of the empirical study show that the \Acs{BHH} is able to select the best heuristic to train \acp{FFNN} in general. This relieves researchers from the burden of having to do this selection process manually through trial and error.

    \item The results of the empirical study show that the \Acs{BHH}, given a diverse set of lower-level heuristics, will generally produce good results when applied to multiple problems at the same time.

    \item Finally, the results of the empirical study show that the \Acs{BHH} is capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from what comes before''.} knowledge in which a predefined selection bias is used for heuristics that are known to be well suited for certain problems.
  \end{highlights}

  \begin{keyword}

    hyper-heuristics \sep meta-learning \sep feedforward neural networks \sep supervised learning \sep Bayesian statistics

  \end{keyword}

\end{frontmatter}

\section{Introduction}
\label{sec:introduction}

\section{Artifical Neural Networks}
\label{sec:anns}

\section{Heuristics}
\label{sec:heuristics}

\section{Hyper-Heuristics}
\label{sec:hhs}

\section{Probability}
\label{sec:probability}

\section{Bayesian Hyper-Heuristics}
\label{sec:bhh}

\section{Methodology}
\label{sec:methodology}

\section{Results}
\label{sec:results}

\section{Conclusion}
\label{sec:conclusion}

\appendix

\section{Appendix A}
\label{app:appendix_a}

\section{Appendix B}
\label{app:appendix_b}

%% For citations use: 
%%       \citet{<label>} ==> Jones et al. [21]
%%       \citep{<label>} ==> [21]
%%

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num-names} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{00}

  %% \bibitem[Author(year)]{label}
  %% Text of bibliographic item

  \bibitem[ ()]{}

\end{thebibliography}
\end{document}

\endinput

### 2023-01-11 article/frontmatter/abstract.tex
✨ (article/introduction): Initial

--- 2023-01-09 article/main.tex
@@
-% \documentclass[preprint,12pt]{elsarticle}
-%% Use the option review to obtain double line spacing
-\documentclass[preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-\journal{Information Sciences}
-
-\usepackage{acro}
-
-% Feedforward Neural Network
-\DeclareAcronym{FFNN}{
-      short = FFNN,
-      short-plural-form = FFNNs,
-      long = \textit{feedforward neural network},
-      long-plural-form = \textit{feedforward neural networks}
-}
-
-% Hyper-Heuristic
-\DeclareAcronym{HH}{
-      short = HH,
-      short-plural-form = HHs,
-      long = \textit{hyper-heuristic},
-      long-plural-form = \textit{hyper-heuristics}
-}
-
-% Bayesian Hyper-Heuristic
-\DeclareAcronym{BHH}{
-      short = BHH,
-      short-plural-form = BHHs,
-      long = \textit{Bayesian hyper-heuristic},
-      long-plural-form = \textit{Bayesian hyper-heuristics}
-}
-
-\begin{document}
-
-\begin{frontmatter}
-  %% Title, authors and addresses
-
-  %% use the tnoteref command within \title for footnotes;
-  %% use the tnotetext command for theassociated footnote;
-  %% use the fnref command within \author or \address for footnotes;
-  %% use the fntext command for theassociated footnote;
-  %% use the corref command within \author for corresponding author footnotes;
-  %% use the cortext command for theassociated footnote;
-  %% use the ead command for the email address,
-  %% and the form \ead[url] for the home page:
-  %% \title{Title\tnoteref{label1}}
-  %% \tnotetext[label1]{}
-  %% \author{Name\corref{cor1}\fnref{label2}}
-  %% \ead{email address}
-  %% \ead[url]{home page}
-  %% \fntext[label2]{}
-  %% \cortext[cor1]{}
-  %% \affiliation{organization={},
-  %%             addressline={},
-  %%             city={},
-  %%             postcode={},
-  %%             state={},
-  %%             country={}}
-  %% \fntext[label3]{}
-
-  \title{Bayesian Hyper-Heuristics}
-
-  %% use optional labels to link authors explicitly to addresses:
-  \author[aff:tuks]{A.N.~Schreuder}
-  \author[aff:stellenbosch]{Prof.~A.P.~Engelbrecht}
-  \author[aff:tuks]{Dr.~A.S.~Bosman}
-  \author[aff:wits]{Prof.~C.W.~Cleghorn}
-
-  \affiliation[aff:tuks]{
-    organization={University of Pretoria},
-    % addressline={Lynnwood Rd},
-    city={Pretoria},
-    postcode={0002},
-    state={Gauteng},
-    country={South Africa}
-  }
-
-  \affiliation[aff:stellenbosch]{
-    organization={Stellenbosch University},
-    % addressline={Ryneveld Street},
-    city={Stellenbosch},
-    postcode={7602},
-    state={Western Cape},
-    country={South Africa}
-  }
-
-  \affiliation[aff:wits]{
-    organization={University of the Witwatersrand},
-    % addressline={1 Jan Smuts Ave},
-    city={Johannesburg},
-    postcode={2000},
-    state={Gauteng},
-    country={South Africa}
-  }
-
 \begin{abstract}
@@
 \end{abstract}
-
-  %%Graphical abstract
-  % \begin{graphicalabstract}
-  % \includegraphics{grabs}
-  % \end{graphicalabstract}
-
-  %%Research highlights
-  \begin{highlights}
-    \item A novel heuristic selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acp{FFNN}.
-The resulting \acs{HH} is referred to as the \acf{BHH}.
-
-    \item The results of the empirical study show with statistical significance and certainty that the \Acs{BHH} performs generally well on multiple problems.
-It is shown that, for each problem, the \Acs{BHH} performance is comparable to the best low-level heuristics included in the heuristic selection pool.
-
-    \item The results of the empirical study show that the \Acs{BHH} is able to select the best heuristic to train \acp{FFNN} in general.
-This relieves researchers from the burden of having to do this selection process manually through trial and error.
-
-    \item The results of the empirical study show that the \Acs{BHH}, given a diverse set of lower-level heuristics, will generally produce good results when applied to multiple problems at the same time.
-
-    \item Finally, the results of the empirical study show that the \Acs{BHH} is capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from what comes before''.} knowledge in which a predefined selection bias is used for heuristics that are known to be well suited for certain problems.
-  \end{highlights}
-
-  \begin{keyword}
-
-    hyper-heuristics \sep meta-learning \sep feedforward neural networks \sep supervised learning \sep Bayesian statistics
-
-  \end{keyword}
-
-\end{frontmatter}
-
-\section{Introduction}
-\label{sec:introduction}
-
-\section{Artifical Neural Networks}
-\label{sec:anns}
-
-\section{Heuristics}
-\label{sec:heuristics}
-
-\section{Hyper-Heuristics}
-\label{sec:hhs}
-
-\section{Probability}
-\label{sec:probability}
-
-\section{Bayesian Hyper-Heuristics}
-\label{sec:bhh}
-
-\section{Methodology}
-\label{sec:methodology}
-
-\section{Results}
-\label{sec:results}
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-\appendix
-
-\section{Appendix A}
-\label{app:appendix_a}
-
-\section{Appendix B}
-\label{app:appendix_b}
-
-%% For citations use: 
-%%       \citet{<label>} ==> Jones et al. [21]
-%%       \citep{<label>} ==> [21]
-%%
-
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
-%%  \bibliographystyle{elsarticle-num-names} 
-%%  \bibliography{<your bibdatabase>}
-
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
-
-\begin{thebibliography}{00}
-
-  %% \bibitem[Author(year)]{label}
-  %% Text of bibliographic item
-
-  \bibitem[ ()]{}
-
-\end{thebibliography}
-\end{document}
-
-\endinput

### 2023-01-11 article/frontmatter/highlights.tex
✨ (article/introduction): Initial

--- 2023-01-09 article/main.tex
@@
-% \documentclass[preprint,12pt]{elsarticle}
-%% Use the option review to obtain double line spacing
-\documentclass[preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-\journal{Information Sciences}
-
-\usepackage{acro}
-
-% Feedforward Neural Network
-\DeclareAcronym{FFNN}{
-      short = FFNN,
-      short-plural-form = FFNNs,
-      long = \textit{feedforward neural network},
-      long-plural-form = \textit{feedforward neural networks}
-}
-
-% Hyper-Heuristic
-\DeclareAcronym{HH}{
-      short = HH,
-      short-plural-form = HHs,
-      long = \textit{hyper-heuristic},
-      long-plural-form = \textit{hyper-heuristics}
-}
-
-% Bayesian Hyper-Heuristic
-\DeclareAcronym{BHH}{
-      short = BHH,
-      short-plural-form = BHHs,
-      long = \textit{Bayesian hyper-heuristic},
-      long-plural-form = \textit{Bayesian hyper-heuristics}
-}
-
-\begin{document}
-
-\begin{frontmatter}
-  %% Title, authors and addresses
-
-  %% use the tnoteref command within \title for footnotes;
-  %% use the tnotetext command for theassociated footnote;
-  %% use the fnref command within \author or \address for footnotes;
-  %% use the fntext command for theassociated footnote;
-  %% use the corref command within \author for corresponding author footnotes;
-  %% use the cortext command for theassociated footnote;
-  %% use the ead command for the email address,
-  %% and the form \ead[url] for the home page:
-  %% \title{Title\tnoteref{label1}}
-  %% \tnotetext[label1]{}
-  %% \author{Name\corref{cor1}\fnref{label2}}
-  %% \ead{email address}
-  %% \ead[url]{home page}
-  %% \fntext[label2]{}
-  %% \cortext[cor1]{}
-  %% \affiliation{organization={},
-  %%             addressline={},
-  %%             city={},
-  %%             postcode={},
-  %%             state={},
-  %%             country={}}
-  %% \fntext[label3]{}
-
-  \title{Bayesian Hyper-Heuristics}
-
-  %% use optional labels to link authors explicitly to addresses:
-  \author[aff:tuks]{A.N.~Schreuder}
-  \author[aff:stellenbosch]{Prof.~A.P.~Engelbrecht}
-  \author[aff:tuks]{Dr.~A.S.~Bosman}
-  \author[aff:wits]{Prof.~C.W.~Cleghorn}
-
-  \affiliation[aff:tuks]{
-    organization={University of Pretoria},
-    % addressline={Lynnwood Rd},
-    city={Pretoria},
-    postcode={0002},
-    state={Gauteng},
-    country={South Africa}
-  }
-
-  \affiliation[aff:stellenbosch]{
-    organization={Stellenbosch University},
-    % addressline={Ryneveld Street},
-    city={Stellenbosch},
-    postcode={7602},
-    state={Western Cape},
-    country={South Africa}
-  }
-
-  \affiliation[aff:wits]{
-    organization={University of the Witwatersrand},
-    % addressline={1 Jan Smuts Ave},
-    city={Johannesburg},
-    postcode={2000},
-    state={Gauteng},
-    country={South Africa}
-  }
-
-  \begin{abstract}
-
-    This work introduces a novel population-based \Acf{BHH}.
-An empirical study is done by using the \acs{BHH} to train \acsp{FFNN}.
-An in-depth behaviour analysis is done and the performance of the \acs{BHH} is compared to that of ten popular low-level heuristics, each with different search behaviours.
-The chosen heuristic pool consists of classic gradient-based heuristics as well as meta-heuristics.
-The empirical process is executed on fourteen datasets consisting of classification and regression problems with varying characteristics.
-The \acs{BHH} is shown to be able to train \acsp{FFNN} well and provide an automated method for finding the best heuristic to train the \acsp{FFNN} at various stages of the training process.
-
-  \end{abstract}
-
-  %%Graphical abstract
-  % \begin{graphicalabstract}
-  % \includegraphics{grabs}
-  % \end{graphicalabstract}
-
 %%Research highlights
@@
 \end{highlights}
-
-  \begin{keyword}
-
-    hyper-heuristics \sep meta-learning \sep feedforward neural networks \sep supervised learning \sep Bayesian statistics
-
-  \end{keyword}
-
-\end{frontmatter}
-
-\section{Introduction}
-\label{sec:introduction}
-
-\section{Artifical Neural Networks}
-\label{sec:anns}
-
-\section{Heuristics}
-\label{sec:heuristics}
-
-\section{Hyper-Heuristics}
-\label{sec:hhs}
-
-\section{Probability}
-\label{sec:probability}
-
-\section{Bayesian Hyper-Heuristics}
-\label{sec:bhh}
-
-\section{Methodology}
-\label{sec:methodology}
-
-\section{Results}
-\label{sec:results}
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-\appendix
-
-\section{Appendix A}
-\label{app:appendix_a}
-
-\section{Appendix B}
-\label{app:appendix_b}
-
-%% For citations use: 
-%%       \citet{<label>} ==> Jones et al. [21]
-%%       \citep{<label>} ==> [21]
-%%
-
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
-%%  \bibliographystyle{elsarticle-num-names} 
-%%  \bibliography{<your bibdatabase>}
-
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
-
-\begin{thebibliography}{00}
-
-  %% \bibitem[Author(year)]{label}
-  %% Text of bibliographic item
-
-  \bibitem[ ()]{}
-
-\end{thebibliography}
-\end{document}
-
-\endinput

### 2023-01-11 article/main.tex
✨ (article/introduction): Initial

@@
-% \documentclass[preprint,12pt]{elsarticle}
+\documentclass[preprint,12pt]{elsarticle}
 %% Use the option review to obtain double line spacing
-\documentclass[preprint,review,12pt]{elsarticle}
+% \documentclass[preprint,review,12pt]{elsarticle}
 
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+\input{journal/journal.tex}
 
-\journal{Information Sciences}
-
-\usepackage{acro}
-
-% Feedforward Neural Network
-\DeclareAcronym{FFNN}{
-      short = FFNN,
-      short-plural-form = FFNNs,
-      long = \textit{feedforward neural network},
-      long-plural-form = \textit{feedforward neural networks}
-}
-
-% Hyper-Heuristic
-\DeclareAcronym{HH}{
-      short = HH,
-      short-plural-form = HHs,
-      long = \textit{hyper-heuristic},
-      long-plural-form = \textit{hyper-heuristics}
-}
-
-% Bayesian Hyper-Heuristic
-\DeclareAcronym{BHH}{
-      short = BHH,
-      short-plural-form = BHHs,
-      long = \textit{Bayesian hyper-heuristic},
-      long-plural-form = \textit{Bayesian hyper-heuristics}
-}
+\input{packages/packages.tex}
+\input{acronyms/acronyms.tex}
 
@@
 
-\begin{frontmatter}
-  %% Title, authors and addresses
-
-  %% use the tnoteref command within \title for footnotes;
-  %% use the tnotetext command for theassociated footnote;
-  %% use the fnref command within \author or \address for footnotes;
-  %% use the fntext command for theassociated footnote;
-  %% use the corref command within \author for corresponding author footnotes;
-  %% use the cortext command for theassociated footnote;
-  %% use the ead command for the email address,
-  %% and the form \ead[url] for the home page:
-  %% \title{Title\tnoteref{label1}}
-  %% \tnotetext[label1]{}
-  %% \author{Name\corref{cor1}\fnref{label2}}
-  %% \ead{email address}
-  %% \ead[url]{home page}
-  %% \fntext[label2]{}
-  %% \cortext[cor1]{}
-  %% \affiliation{organization={},
-  %%             addressline={},
-  %%             city={},
-  %%             postcode={},
-  %%             state={},
-  %%             country={}}
-  %% \fntext[label3]{}
-
-  \title{Bayesian Hyper-Heuristics}
-
-  %% use optional labels to link authors explicitly to addresses:
-  \author[aff:tuks]{A.N.~Schreuder}
-  \author[aff:stellenbosch]{Prof.~A.P.~Engelbrecht}
-  \author[aff:tuks]{Dr.~A.S.~Bosman}
-  \author[aff:wits]{Prof.~C.W.~Cleghorn}
-
-  \affiliation[aff:tuks]{
-    organization={University of Pretoria},
-    % addressline={Lynnwood Rd},
-    city={Pretoria},
-    postcode={0002},
-    state={Gauteng},
-    country={South Africa}
-  }
-
-  \affiliation[aff:stellenbosch]{
-    organization={Stellenbosch University},
-    % addressline={Ryneveld Street},
-    city={Stellenbosch},
-    postcode={7602},
-    state={Western Cape},
-    country={South Africa}
-  }
-
-  \affiliation[aff:wits]{
-    organization={University of the Witwatersrand},
-    % addressline={1 Jan Smuts Ave},
-    city={Johannesburg},
-    postcode={2000},
-    state={Gauteng},
-    country={South Africa}
-  }
-
-  \begin{abstract}
-
-    This work introduces a novel population-based \Acf{BHH}.
-An empirical study is done by using the \acs{BHH} to train \acsp{FFNN}.
-An in-depth behaviour analysis is done and the performance of the \acs{BHH} is compared to that of ten popular low-level heuristics, each with different search behaviours.
-The chosen heuristic pool consists of classic gradient-based heuristics as well as meta-heuristics.
-The empirical process is executed on fourteen datasets consisting of classification and regression problems with varying characteristics.
-The \acs{BHH} is shown to be able to train \acsp{FFNN} well and provide an automated method for finding the best heuristic to train the \acsp{FFNN} at various stages of the training process.
-
-  \end{abstract}
-
-  %%Graphical abstract
-  % \begin{graphicalabstract}
-  % \includegraphics{grabs}
-  % \end{graphicalabstract}
-
-  %%Research highlights
-  \begin{highlights}
-    \item A novel heuristic selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acp{FFNN}.
-The resulting \acs{HH} is referred to as the \acf{BHH}.
-
-    \item The results of the empirical study show with statistical significance and certainty that the \Acs{BHH} performs generally well on multiple problems.
-It is shown that, for each problem, the \Acs{BHH} performance is comparable to the best low-level heuristics included in the heuristic selection pool.
-
-    \item The results of the empirical study show that the \Acs{BHH} is able to select the best heuristic to train \acp{FFNN} in general.
-This relieves researchers from the burden of having to do this selection process manually through trial and error.
-
-    \item The results of the empirical study show that the \Acs{BHH}, given a diverse set of lower-level heuristics, will generally produce good results when applied to multiple problems at the same time.
-
-    \item Finally, the results of the empirical study show that the \Acs{BHH} is capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from what comes before''.} knowledge in which a predefined selection bias is used for heuristics that are known to be well suited for certain problems.
-  \end{highlights}
-
-  \begin{keyword}
-
-    hyper-heuristics \sep meta-learning \sep feedforward neural networks \sep supervised learning \sep Bayesian statistics
-
-  \end{keyword}
-
-\end{frontmatter}
-
-\section{Introduction}
-\label{sec:introduction}
-
-\section{Artifical Neural Networks}
-\label{sec:anns}
-
-\section{Heuristics}
-\label{sec:heuristics}
-
-\section{Hyper-Heuristics}
-\label{sec:hhs}
-
-\section{Probability}
-\label{sec:probability}
-
-\section{Bayesian Hyper-Heuristics}
-\label{sec:bhh}
-
-\section{Methodology}
-\label{sec:methodology}
-
-\section{Results}
-\label{sec:results}
-
-\section{Conclusion}
-\label{sec:conclusion}
+\input{frontmatter/frontmatter.tex}
+\input{sections/01-introduction.tex}
+\input{sections/02-artificial-neural-networks.tex}
+\input{sections/03-heuristics.tex}
+\input{sections/04-hyper-heuristics.tex}
+\input{sections/05-probability.tex}
+\input{sections/06-bayesian-hyper-heuristics.tex}
+\input{sections/07-methodology.tex}
+\input{sections/08-results.tex}
+\input{sections/09-conclusion.tex}
 
@@
 
-\section{Appendix A}
-\label{app:appendix_a}
+\input{appendices/b.tex}
+\input{appendices/a.tex}
 
-\section{Appendix B}
-\label{app:appendix_b}
+\input{references/bibliography.tex}
 
-%% For citations use: 
-%%       \citet{<label>} ==> Jones et al. [21]
-%%       \citep{<label>} ==> [21]
-%%
-
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
-%%  \bibliographystyle{elsarticle-num-names} 
-%%  \bibliography{<your bibdatabase>}
-
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
-
-\begin{thebibliography}{00}
-
-  %% \bibitem[Author(year)]{label}
-  %% Text of bibliographic item
-
-  \bibitem[ ()]{}
-
-\end{thebibliography}
 \end{document}

### 2023-01-11 article/sections/01-introduction.tex
✨ (article/introduction): Initial

--- 2022-12-05 dissertation/chapters/01-introduction.tex
@@
-\chapter{Introduction}\label{chap:introduction}
-
-\begin{quotation}
-      ``It is better to solve one problem five different ways, than to solve five problems one way.''
-\end{quotation}
-\begin{flushright}
-      - George Polya
-\end{flushright}
-
-\Acf{ML} is one of the most popular fields of research in \acf{AI} studies today.
-In recent years, \acs{ML} research has seen some notable achievements in academia~\cite{ref:lecun:2015, ref:glorot:2010, ref:goodfellow:2014, ref:quoc:2017}, as well as the industry at large~\cite{ref:silver:2016, ref:silver:2017, ref:zoph:2017, ref:lewis:2017}.
-\acs{ML} research has grown tremendously over the past decade with successes like AlphaGo, which set new standards for \acs{AI} capabilities by beating the world's best Go player, Lee Sedol, 4-1~\cite{ref:san-hun:2016}.
-
-Over the past few years, modern hardware capabilities have improved to the point where workloads in the field of \acs{ML} that were previously computationally infeasible, are now possible.
-One such sub-field of \acs{ML} is \acp{ANN}.
-\acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain~\cite{ref:engelbrecht:2007}.
-\acp{ANN} can be trained, which is the equivalent of ``learning'' from data.
-Learning gives rise to the ability to apply some form of decision making.
-Decision making as an ability provides a wide-range of applications from healthcare to finance and yields great interest in the field.
-With the improvement of hardware came an influx of \acs{ML} researchers that focused their attention on training of \acp{ANN}.
-
-\Acfp{FFNN} are specific types of \acp{ANN}~\cite{ref:reed:1999}.
-A popular field of focus for studying \acp{ANN} is the process by which these models are trained.
-The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input data and comparing the produced output data to that of predefined target data.
-Training of \acp{ANN} is seen as an optimisation problem.
-The \acs{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''.
-A search algorithm known as a \index{heuristic}\textit{heuristic}~\cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \acs{ANN}, such that a specified objective function is minimised.
-The research presented in this dissertation focuses on the development of a specific type of heuristic, called a \acf{HH} to train \acp{FFNN} in a supervised learning approach.
-
-This chapter provides the reader with a brief overview of the problem domain and outlines the research problem, objectives and purpose. The remainder of the chapter is presented as follows:
-
-\begin{itemize}
-      \item \textbf{Section~\ref{sec:introduction:summary_research_domain}} provides the reader with brief summary of the research domain.
-
-      \item \textbf{Section~\ref{sec:introduction:problem}} outlines the research problem being addressed.
-
-      \item \textbf{Section~\ref{sec:introduction:motivation}} provides a motivation for this research.
-
-      \item \textbf{Section~\ref{sec:introduction:objectives}} presents the reader with the research objectives and outlines the goals of this dissertation.
-
-      \item \textbf{Section~\ref{sec:introduction:contributions}} outlines the contributions of this research to the field.
-
-      \item \textbf{Section~\ref{sec:introduction:outline}} provides a full dissertation outline.
-\end{itemize}
-
-\section{Summary of Research Domain}\label{sec:introduction:summary_research_domain}
-
-This section provides the reader with a brief summary of the research field and outlines key concepts that contribute to the topics discussed in this dissertation.
-
-Although the landscape of what can be solved using \acp{ANN} today is extensive, there still exists no single model that can be generalised to solving multiple problem classes, across multiple problem domains.
-\acs{ANN} training algorithms mostly yield problem specific solutions.
-This means that a particular approach that works well for one domain or problem class, often does not necessarily work for another.
-This problem is known as the \acf{NFL}~\cite{ref:wolpert:1997}.
+\section{Introduction}
+\label{sec:introduction}
 
 The performance and capabilities of \acp{ANN} is largely influenced by the learning process used.
+As such, a popular field of focus for studying \acp{FFNN} is the process by which these models are trained.
 The learning process consists of multiple components.
-These include the type of underlying optimisation algorithm used, how the model parameters are initialised, the hyper-parameters used and the constraints of learning such as allowed search space and boundaries.
 Each of these elements influence how much a particular learning technique might focus on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during training.
@@
 This field of study is known as \index{meta-learning}meta-learning~\cite{ref:giraud:2004}.
-\index{meta-learning}Meta-learning of heuristic hyper-parameters as applied in the training of \acp{ANN} has shown to yield good generalisation results~\cite{ref:hospedales:2020, ref:vilalta:2002}.
-
-The dynamic nature of the learning process leads towards the idea that \acs{ML} models could be trained in a way such that the learning process and learning mechanism applied are not statically defined, but rather dynamic and under the control of some mechanism.
 
@@
 This approach focuses on the hybridisation of learning paradigms.
-The main concept behind this paradigm is that the learning process is dynamic and problem specific.
-A particular learning technique might work well for one problem and not for another.
-At the same time, a particular learning technique might work well for a particular part of the search landscape, but not for another.
-By dynamically combining the best of different learning paradigms throughout the learning process, a trade-off can be made between exploration and exploitation as is required.
 
@@
 These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.
+
 One such form of \acs{HH} is a population-based approach that guides the search process by automatically selecting heuristics from a heuristic-pool to be applied to a collection of different candidate solutions in the solution-space.
@@
 
-One specific type of selection \acs{HH} is called a \index{multi-method populated-based meta-heuristic}\textit{multi-method population-based \index{meta-heuristic}meta-heuristic}~\cite{ref:vanderstockt:2018}.
-The term \index{multi-method}\textit{multi-method} refers to the incorporation of different low-level heuristics, with different search behaviours, into the heuristic space.
-The term \textit{population-based} refers to the utilisation of a population of entities that represent candidate solutions.
-Finally, the term \index{meta-heuristic}\textit{meta-heuristics} refers to the \acs{HH} as a heuristic that does not have any domain knowledge and only makes use of information from the search process.
-
-\citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} mentioned that \acp{HH} have been shown to solve a number of problems including bin-packing, examination timetabling, production scheduling, the travelling salesman problem, vehicle routing problem and many more.
-
-\section{Problem Statement}\label{sec:introduction:problem}
+\subsection{Problem Statement}\label{subsec:introduction:problem}
 
@@
 
-\section{Motivation}\label{sec:introduction:motivation}
+\subsection{Motivation}\label{subsec:introduction:motivation}
 
-A process is required to alleviate the burden of having to exhaustively test each implementation of heuristic and hyper-parameters, for every problem being optimised.
-
-In Section~\ref{sec:introduction:problem} above, it is mentioned that finding the best heuristic to train \acp{FFNN} is a timely and tedious process.
+It was previously mentioned that finding the best heuristic to train \acp{FFNN} is a timely and tedious process.
 A modern approach is to use \acp{HH} to automate the process of selecting the best heuristic when applied to some optimisation problem.
@@
 
-Training of \acp{FFNN} is seen as a computational search problem.
-A \acf{HH}, as defined by Burke et al.~\cite{ref:burke:2010}, is ``a search method or learning mechanism for selecting or generating heuristics to solve computational search problems''.
-\acp{HH} is a field of research aimed at the automated selection, combination, adaptation or generation of multiple lower-level heuristics to efficiently solve computational search problems.
-
-\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} mention that the focus of \acp{HH} is on automating the development of the \textit{learning mechanism} used to find the best heuristic to obtain an appropriate solution to an optimisation problem.~\citeauthor{ref:grobler:2012} explain that \acp{HH} employ a high-level heuristic that focuses on finding the best low-level heuristic in heuristic space that could include \textit{single-method} and \textit{multi-method} optimisation algorithms (heuristics).
-\acp{HH} relieve the burden of having to select the best heuristic to use by trial and error.
-Furthermore, \acp{HH} can generally be applied to multiple problems given that the set of low-level heuristics include heuristics that have the potential to solve the problem at hand~\cite{ref:burke:2010}.
-Automation of the heuristic selection process and the general application to a wider range of problems are characteristics of \acp{HH} that can be beneficial when applied in the context of training \acp{FFNN}.
-
-Note that training of \acp{FFNN} using \acp{HH} is not to be confused with the training of \acp{FFNN} using \index{ensemble networks}\textit{ensemble networks} or \index{query by committees}\textit{query by committees}.~\citeauthor{ref:pappa:2014}~\cite{ref:pappa:2014} describe \index{ensemble networks}ensemble networks as a combination method in \index{meta-learning}meta-learning whereby multiple \acp{ANN} are jointly used to solve a problem.
-Each member network in the ensemble is trained using a specified heuristic, and generally this heuristic is applied to the same member throughout the training process.
-The results of all of the member networks are then joined together using some consensus mechanism~\cite{ref:zhou:2002}.
-This mechanism could be weighted averages, majority voting or weighted voting.
-\index{ensemble networks}Ensemble networks do not search through the heuristic space to find the best training algorithm for each member, while \acp{HH} do.
-
 This research takes a particular interest in developing a selection \acs{HH} that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process.
@@
 
-\section{Objectives}\label{sec:introduction:objectives}
+\subsection{Outline}\label{subsec:introduction:outline}
 
-The main objective of this research is focused on developing a novel \Acf{BHH} selection mechanism in a \acs{HH} framework that can be used to train \acp{FFNN}.
-In order to reach this objective, the following sub-objectives are defined.
-
-\begin{itemize}
-      \item Conduct a literature study on \acp{ANN} in order to provide the necessary background information of the \acs{AN}, \acp{FFNN} and the training process.
-
-      \item Conduct a literature study on different types of heuristics that have been used to train \acp{FFNN}.
-The literature study will provide the necessary background information to understand how different heuristics can be used in the set of heuristics to be selected to train the \acs{FFNN}.
-
-      \item Conduct a literature study on \index{meta-learning}meta-learning and \acp{HH} in order to provide the required background information necessary to propose and develop a new high-level heuristic and selection mechanism.
-
-      \item Conduct a literature study on probability theory and Bayesian statistics such as Bayesian inference and Bayesian analysis to provide the necessary background information required to understand how Bayesian approaches can be used as a learning technique.
-
-      \item Develop a novel \Acs{BHH} selection mechanism for a \acs{HH} that makes use of Bayesian statistics to guide the \acs{HH} search process while training \acp{FFNN} on different problems.
-
-      \item Conduct an empirical study to show that the developed \Acs{BHH} can effectively be used to train \acp{FFNN}.
-
-      \item Conduct an empirical study to investigate the behavioural characteristics of the \Acs{BHH} as it is used to train \acp{FFNN} on an example problem.
-
-      \item Conduct an empirical study and critically evaluate the performance of the developed \Acs{BHH} compared to individual heuristics in the heuristic space as they are used to train \acp{FFNN} on a number of different problems.
-
-      \item Conduct an empirical study that investigates variations of the \Acs{BHH} and the effects of design decisions and hyper-parameters on the search process.
-
-      \item Provide a statistical analysis of the results obtained from the empirical study.
-\end{itemize}
-
-\section{Contributions}\label{sec:introduction:contributions}
-
-The results obtained from this research contribute to the field of study in the
-following ways.
-
-\begin{itemize}
-      \item A novel heuristic selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acp{FFNN}.
-The resulting \acs{HH} is referred to as the \acf{BHH}.
-
-      \item The results of the empirical study show with statistical significance and certainty that the \Acs{BHH} performs generally well on multiple problems.
-It is shown that, for each problem, the \Acs{BHH} performance is comparable to the best low-level heuristics included in the heuristic selection pool.
-
-      \item The results of the empirical study show that the \Acs{BHH} is able to select the best heuristic to train \acp{FFNN} in general.
-This relieves researchers from the burden of having to do this selection process manually through trial and error.
-
-      \item The results of the empirical study show that the \Acs{BHH}, given a diverse set of lower-level heuristics, will generally produce good results when applied to multiple problems at the same time.
-
-      \item Finally, the results of the empirical study show that the \Acs{BHH} is capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from what comes before''.} knowledge in which a predefined selection bias is used for heuristics that are known to be well suited for certain problems.
-\end{itemize}
-
-\section{Dissertation Outline}\label{sec:introduction:outline}
-
-The remainder of this dissertation is structured as follows:
-
-\begin{itemize}
-      \item \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN} and the various components that make up an \acf{AN}.
+The remainder of this article is structured as follows: Section~\ref{sec:anns} provides a literature study on \acp{ANN}.
 The focus is on training of \acp{FFNN}.
-It is shown how training of \acp{FFNN} is seen as an optimisation problem.
-
-      \item \textbf{Chapter~\ref{chap:heuristics}} provides details on various types of heuristics and \acp{MH} that have been used to train \acp{FFNN}.
-A literature study is done to provide details on the search behaviours, application and implementation of each heuristic in the context of training \acp{FFNN}.
-
-      \item \textbf{Chapter~\ref{chap:hhs}} presents a literature study on the details of \acp{HH} and \index{meta-learning}meta-learning in general.
-A discussion follows on the current landscape of \acs{HH} research and a review of different selection approaches for \acp{HH} is conducted.
-It is shown how \acp{HH} are suitable for \acs{FFNN} training.
-
-      \item \textbf{Chapter~\ref{chap:probability}} presents a literature study on probability theory.
-Probability distributions and conjugate priors are discussed in detail.
-The chapter concludes with a detailed discussion on Bayesian statistics, specifically focusing on Bayesian inference and analysis.
-
-      \item \textbf{Chapter~\ref{chap:bhh}} presents the developed \Acs{BHH}.
-It is shown how the \Acs{BHH} is implemented as a selection mechanism in the context of a \acs{HH} framework.
-The \Acs{BHH} is shown to implement a \index{Na\"ive Bayes classifier}Na\"ive Bayes classifier.
-The probabilistic model that is implemented is derived and discussed in detail.
-Finally, the chapter concludes with a detailed discussion on how \index{Bayesian analysis}Bayesian analysis is used to guide the heuristic selection process.
-The update step (training step) for prior probability concentration parameters is derived and discussed in detail.
-The \Acs{BHH} algorithmic implementation, variants and suggested application are presented as well.
-
-      \item \textbf{Chapter~\ref{chap:methodology}} presents a detailed description of the empirical process and the setup of each experiment.
-It discusses the datasets used, the \acs{FFNN} architecture and topology used, heuristics that are used, the configuration of hyper-parameters, initialisation techniques used and performance measures used.
-Finally, discussions follow on how the results are analysed.
-This includes a discussion on the method used to determine statistical significance.
-
-      \item \textbf{Chapter~\ref{chap:results}} provides and discusses the results of the empirical study in detail.
-A baseline comparison is done by comparing the performance of the \Acs{BHH} to that of all the individual lower-level heuristics on all datasets.
-These datasets include classification and regression problems of various sizes and complexity.
-Detailed results are presented on the performance of the \Acs{BHH} as a selection mechanism for \acp{HH} and a brief comparison is made to other selection mechanisms.
-Finally, results are presented on the effects of the hyper-parameters of the \Acs{BHH} on the training process.
-Discussions follow on how the \Acs{BHH} is shown to automate the selection of the best heuristic during the training of \acp{FFNN}, as applied to a range of problems, alleviating the burden on researchers to apply traditional trial and error approaches.
-
-      \item \textbf{Chapter~\ref{chap:conclusion}} summarises the research done in this dissertation along with a brief overview of the findings made throughout the research process.
-A review of the research goals are given and suggestions for future research are made.
-\end{itemize}
-
-This dissertation is accompanied by a full index given at page~\pageref{index} along with the following appendices:
-
-\begin{itemize}
-      \item \textbf{Appendix~\ref{app:datasets}} provides details on the datasets used for the empirical analysis.
-
-      \item \textbf{Appendix~\ref{app:statistical_analysis}} provides details on the outcomes of the statistical analyses.
-
-      \item \textbf{Appendix~\ref{app:acronyms}} provides a list of the important acronyms used or newly defined in the course of this work, as well as their associated definitions.
-
-      \item \textbf{Appendix~\ref{app:derived_publications}} lists the publications derived from this work.
-\end{itemize}
-
-To best view the illustrations, tables and figures presented throughout this dissertation, it is recommended that the dissertation be viewed in colour.
+Section~\ref{sec:heuristics} provides details on various types of heuristics and \acp{MH} that have been used to train \acp{FFNN}.
+Section~\ref{sec:hhs} presents a literature study on the details of \acp{HH} and \index{meta-learning}meta-learning in general.
+Section~\ref{sec:probability} presents a literature study on probability theory.
+Section~\ref{sec:bhh} presents the developed \Acs{BHH}.
+Section~\ref{sec:methodology} presents a detailed description of the empirical process and the setup of each experiment.
+Section~\ref{sec:results} provides and discusses the results of the empirical study in detail.
+Section~\ref{sec:conclusion} summarises the research done in this dissertation along with a brief overview of the findings made throughout the research process.

### 2023-01-11 article/sections/02-artificial-neural-networks.tex
✨ (article/introduction): Initial

\section{Artifical Neural Networks}
\label{sec:anns}

### 2023-01-11 article/sections/06-bayesian-hyper-heuristics.tex
✨ (article/introduction): Initial

\section{Bayesian Hyper-Heuristics}
\label{sec:bhh}

### 2023-01-12 article/sections/01-introduction.tex
✨ (article): Introduction Done

@@
 
+Over the past few years, modern hardware capabilities have improved to the point where workloads in the field of \acs{ML} that were previously computationally infeasible, are now possible.
+One such sub-field of \acs{ML} is \acp{ANN}.
+
 The performance and capabilities of \acp{ANN} is largely influenced by the learning process used.
 As such, a popular field of focus for studying \acp{FFNN} is the process by which these models are trained.
-The learning process consists of multiple components.
-Each of these elements influence how much a particular learning technique might focus on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during training.
-
-Techniques exist to dynamically balance the trade-off between exploration and exploitation during the search process.
-An example of such a technique is to dynamically adjust and learn the heuristic \index{hyper-parameters}\textit{hyper-parameters} as part of the learning process.
-This field of study is known as \index{meta-learning}meta-learning~\cite{ref:giraud:2004}.
-
-A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process.
-This approach focuses on the hybridisation of learning paradigms.
-
-One such form of hybridisation of learning paradigms is referred to as \textit{heterogeneous learning approaches}.
-Heterogeneous learning approaches make use of different \textit{search behaviours} by selecting from a behaviour pool.
-Heterogeneous approaches have shown to balance the trade-off between exploration and exploitation~\cite{ref:nepomuceno:2013}.
-
-A step further in the concept of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem~\cite{ref:burke:2013}.
-These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.
-
-One such form of \acs{HH} is a population-based approach that guides the search process by automatically selecting heuristics from a heuristic-pool to be applied to a collection of different candidate solutions in the solution-space.
-This collection of candidate solutions are referred to as a \textit{population} of \textit{entities}, where each \textit{entity} is a single candidate solution to the problem being optimised.
-Population-based \acp{HH} implement a strategy where multiple heuristics work together to solve a problem.
-This technique requires a mechanism that selects a specific heuristic to be applied to a specific candidate solution.
-
-Finding the best heuristic to use is non-trivial and some \textit{selection strategy} must be used to select the best heuristic.
-\acp{HH} that implement such a selection strategy are referred to as \textit{selection} \acp{HH}.
-The term \textit{selection} refers to the ability of the \acs{HH} to select the best heuristic from a pool of low-level heuristics.
-
-\subsection{Problem Statement}\label{subsec:introduction:problem}
+\acp{ANN} are trained by optimisation algorithms known as heuristics.
 
@@
 
-Careful, systematic selection is thus required to find and select the best heuristic to train \acp{FFNN}.
-In the past, researchers selected the best heuristic by trial and error.
-A set of heuristics and carefully selected hyper-parameters would be implemented, followed by an empirical test to evaluate the performance of each heuristic for a given problem domain~\cite{ref:pillay:2015}.
-In this way, researchers were able to determine which heuristics and which hyper-parameters performed well for different problems.
-However, this approach is problematic, because it is time-consuming and laborious.
+A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process.
+This approach focuses on the hybridisation of learning paradigms.
 
-\subsection{Motivation}\label{subsec:introduction:motivation}
-
-It was previously mentioned that finding the best heuristic to train \acp{FFNN} is a timely and tedious process.
-A modern approach is to use \acp{HH} to automate the process of selecting the best heuristic when applied to some optimisation problem.
-The best heuristic might not be a single heuristic, but rather a hybridisation of heuristics~\cite{ref:pillay:2015}.
+One such form of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem~\cite{ref:burke:2013}.
+These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.
 
@@
 
-This research takes a particular interest in developing a selection \acs{HH} that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process.
-This research develops the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
+This research takes a particular interest in developing a population-based, selection \acs{HH} that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process.
+This research presents the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
 This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.
@@
 
-\subsection{Outline}\label{subsec:introduction:outline}
-
-The remainder of this article is structured as follows: Section~\ref{sec:anns} provides a literature study on \acp{ANN}.
+The remainder of this article is structured as follows: Section~\ref{sec:anns} provides background information on \acp{ANN}.
 The focus is on training of \acp{FFNN}.
 Section~\ref{sec:heuristics} provides details on various types of heuristics and \acp{MH} that have been used to train \acp{FFNN}.
-Section~\ref{sec:hhs} presents a literature study on the details of \acp{HH} and \index{meta-learning}meta-learning in general.
-Section~\ref{sec:probability} presents a literature study on probability theory.
+Section~\ref{sec:hhs} presents background information on the details of \acp{HH} and \index{meta-learning}meta-learning in general.
+Section~\ref{sec:probability} presents background information on probability theory.
 Section~\ref{sec:bhh} presents the developed \Acs{BHH}.

### 2023-01-22 article/sections/01-introduction.tex
🚧 (article): Section 2 done, WIP

@@
 One such sub-field of \acs{ML} is \acp{ANN}.
-
 The performance and capabilities of \acp{ANN} is largely influenced by the learning process used.
-As such, a popular field of focus for studying \acp{FFNN} is the process by which these models are trained.
+As such, a popular field of focus for studying \acp{ANN} is the process by which these models are trained.
 \acp{ANN} are trained by optimisation algorithms known as heuristics.
 
-Many different heuristics have been developed and used to train \acp{FFNN}~\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
+Many different heuristics have been developed and used to train \acp{ANN}~\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
 Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses.
-Finding the best heuristic to train the \acs{FFNN} is required in order to yield optimal results.
+Finding the best heuristic to train the \acs{ANN} is required in order to yield optimal results.
 This process is often non-trivial and could be a time-consuming exercise.
-Consider that selection of the best heuristic as applied to optimisation problems, such as training \acp{FFNN}, is problem specific~\cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
+Selection of the best heuristic to train \acp{ANN}, is often problem specific~\cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
 
@@
 This approach focuses on the hybridisation of learning paradigms.
-
 One such form of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem~\cite{ref:burke:2013}.
@@
 In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
-Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimization.
-However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
+However, research on the application of \acp{HH} in the context of \acs{ANN} training is scarce.
+\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
 
@@
 The remainder of this article is structured as follows: Section~\ref{sec:anns} provides background information on \acp{ANN}.
-The focus is on training of \acp{FFNN}.
-Section~\ref{sec:heuristics} provides details on various types of heuristics and \acp{MH} that have been used to train \acp{FFNN}.
-Section~\ref{sec:hhs} presents background information on the details of \acp{HH} and \index{meta-learning}meta-learning in general.
+Section~\ref{sec:heuristics} provides details on various types of heuristics that have been used to train \acp{FFNN}.
+Section~\ref{sec:hhs} presents background information on \acp{HH} and \index{meta-learning}meta-learning.
 Section~\ref{sec:probability} presents background information on probability theory.
@@
 Section~\ref{sec:methodology} presents a detailed description of the empirical process and the setup of each experiment.
-Section~\ref{sec:results} provides and discusses the results of the empirical study in detail.
-Section~\ref{sec:conclusion} summarises the research done in this dissertation along with a brief overview of the findings made throughout the research process.
+Section~\ref{sec:results} provides and discusses the results of the empirical study.
+Section~\ref{sec:conclusion} summarises the research that is done along with a brief overview of the findings made throughout the research process.

### 2023-01-22 article/sections/02-artificial-neural-networks.tex
🚧 (article): Section 2 done, WIP

@@
 \label{sec:anns}
+
+\acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain~\cite{ref:engelbrecht:2007}.
+\acp{ANN} have been successfully applied to a range of problem classes.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} summarises some common problems that are solved using \acp{ANN}.
+These include classification~\cite{ref:khan:2001}, pattern matching~\cite{ref:cannady:1998, ref:kumar:1994}, pattern completion~\cite{ref:dayhoff:2001}, optimisation~\cite{ref:specht:1991} and data mining~\cite{ref:singh:2009}.
+
+\subsection{Artificial Neuron}
+\label{sec:anns:an}
+
+\Acp{AN} provide the fundamental building blocks for \acp{ANN}.
+The \acs{AN} implements a non-linear mapping from $\mathbb{R}^{I}$ to $\mathbb{R}^{T}$, usually in the ranges $[0,1]$ or $[-1,1]$, depending on the problem being solved ~\cite{ref:engelbrecht:2007}.
+$I$ is the total number of dimensions of the input in real-number space ($\mathbb{R}$), and $T$ is the total number of dimensions of the target (desired output) in real-number space.
+The \acs{AN} implements various components and is illustrated in Figure~\ref{fig:artificial_neuron}.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=\textwidth]{artificial_neuron.pdf}
+	\caption[The \index{artificial neuron}artificial neuron]{An illustration of the \index{artificial neuron}artificial neuron.}
+	\label{fig:artificial_neuron}
+\end{figure}
+
+Each of the components of the \acs{AN}, presented in Figure~\ref{fig:artificial_neuron}, is inspired by some element of the \acs{BN}.
+The input ($\boldsymbol{x}$) models the activations received from the pre-synaptic neuron.
+The weights ($\boldsymbol{v}$), model the \index{synapse}synapses and connection strengths.
+The \index{net input signal}net input signal ($net$) models the net resulting activations from all connected pre-synaptic neurons.
+The biases ($\theta$), model a mechanism introduced to influence the strength of the activation (output signal) of the \acs{AN}.
+The activation function ($f$) models the action potential of the \acs{BN} and is based on the net input signal.
+Finally, the output ($\boldsymbol{y}$) models the activation by the post-synaptic neuron.
+
+\subsection{Feedforward Neural Networks}
+\label{sec:anns:ffnn}
+
+Multiple \acp{AN} can be organised and used together forming a ``network'' of \acp{AN} referred to as an \acf{ANN}.
+The architecture of the \acs{ANN} refers to the way in which \acp{AN} are organised.
+\acp{ANN} can be organised in layers where a single layer can contain multiple \acp{AN}.
+Generally, each layer makes use of the same \index{activation function}activation function.
+Output from one layer is propagated as input to the next layer.
+The topology of the \acs{ANN} refers to the way that layers of \acp{AN} are connected to each other.
+There are many different topologies~\cite{ref:miikkulainen:2010}.
+
+This research focuses on a particular type of \acs{ANN}, referred to as \acp{FFNN}.
+\acp{FFNN} were the first and simplest type of \acp{ANN} developed~\cite{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order.
+Furthermore, \acp{FFNN} implement \index{fully connected topology}fully connected topologies, where each \acs{AN} in one layer is connected to all \acp{AN} in the next, without any cycles~\cite{ref:zell:1994}.
+
+In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
+An illustration of a \acs{FFNN} is given in Figure~\ref{fig:ffnn}.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.98\textwidth]{feedforward_neural_network.pdf}
+	\caption[A \index{feedforward neural network}feedforward neural network]{An illustration of a \index{feedforward neural network}feedforward neural network implementing input, hidden and output layers using a fully connected topology.}
+	\label{fig:ffnn}
+\end{figure}
+
+In Figure~\ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input vector $\boldsymbol{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer, $y_k$ refers to the $k$-th dimension in the output vector $\boldsymbol{y}$, $v_{i,j}$ refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the output node $y_k$.
+
+\subsection{Training}
+\label{sec:anns:training}
+
+\textit{Training} is the process whereby the weights of the \acs{FFNN} are systematically changed with the aim of improving the \textit{performance} of the \acs{FFNN}.
+Finding the optimal weights that produce the best performance on a given task is an optimisation problem.
+The optimisation algorithm used to find the optimal weights is referred to as a \index{heuristic}\textit{heuristic}.
+\index{heuristic}Heuristics search for possible solutions in the solution-space and make use of information from the search space to guide to process.
+
+During the training process, the \acs{FFNN} is exposed to data while trying to produce some target outcome.
+The degree to which the produced outcome differs from the target outcome is referred to as \textit{loss}.
+Since training of \acp{FFNN} is an optimisation problem, the goal of the training process is to minimise the loss.
+The loss is calculated using an error function.
+This research focuses on a number of error functions, including \acf{SSE}, \acf{MSE}, \acf{RMSE}, \acf{MAE}, \acf{BinXE}, \acf{CatXE} and \acf{SparseCatXE}.
+
+\index{supervised learning}Supervised learning is the process of training where the data that is presented to the \acs{FFNN} during training, includes the desired solution~\cite{ref:geron:2017}.
+The \acs{FFNN} learns the mapping function from the input to the target output~\cite{ref:brownlee:2016}.

### 2023-01-22 article/sections/03-heuristics.tex
🚧 (article): Section 2 done, WIP

--- 2022-12-10 dissertation/chapters/03-heuristics.tex
@@
-\chapter{Heuristics}\label{chap:heuristics}
+\section{Heuristics}
+\label{sec:heuristics}
 
-\begin{quotation}
-	``It is not the strongest of the species that survives. It is also not the most intelligent that survives. It is the one that is the most adaptable to change.''
-\end{quotation}
-\begin{flushright}
-	- Charles Darwin
-\end{flushright}
+A \index{heuristic}heuristic refers to an algorithmic search technique that serves as a guide to a search process where good solutions to a optimisation problem is being sought out.
+Many different techniques have been used to train \acp{FFNN}~\cite{ref:kingma:2014}.
+At the time of writing, the majority of work that is published around the training of \acp{FFNN}, involves the use of gradient-based techniques~\cite{ref:nel:2021}.
+However, other techniques have also been used to successfully train \acp{FFNN}, including \acp{MH} such as \acf{PSO}~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}, \acf{DE}~\cite{ref:espinal:2011} and \acfp{GA}~\cite{ref:gupta:1999}.
+This research takes a particular interest in both gradient-based heuristics as well as \acp{MH}.
 
-Many different techniques have been used to train \acp{FFNN}~\cite{ref:kingma:2014}.
-Finding the best technique to use to train a \acs{FFNN} has been shown to be problem dependent in many cases~\cite{ref:kheiri:2017}.
-Every technique has its characteristics, constraints, advantages and disadvantages.
-At the time of writing, the majority of work that is published around the training of \acp{FFNN}, involves the use of gradient-based techniques~\cite{ref:nel:2021}.
-Gradient-based techniques are not without flaws and can, for example, yield slow convergence or get trapped in local optima~\cite{ref:mingguang:2009}.
-Other techniques have also been used to successfully train \acp{FFNN}, including \acp{MH} such as \acf{PSO}~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}, \acf{DE}~\cite{ref:espinal:2011} and \acfp{GA}~\cite{ref:gupta:1999}.
-
-Chapter~\ref{chap:anns} briefly introduced the reader to the concept of \index{heuristic}\index{heuristic}heuristics and \acfp{MH}s.
-This chapter presents more detailed background information on various different \index{heuristic}heuristics that have been used to train \acp{FFNN}.
-Broadly speaking, this chapter focuses on two different groups of \index{heuristic}heuristics, including classical gradient-based approaches and population-based \acp{MH}.
-Each technique is presented and discussed in detail.
-Pseudo-code algorithms are provided for each technique and discussions follow on advantages, disadvantages, capabilities and limitations.
-The remainder of this chapter is structured as follows:
-
-\begin{itemize}
-	\item \textbf{Section~\ref{sec:heuristics:optimisation}} provides a brief review of optimisation. It is shown that training of \acp{FFNN} is an optimisation problem.
-
-	\item \textbf{Section~\ref{sec:heuristics:what_is_a_heuristic}} provides background information on the origins and definition of the term \index{heuristic}\textit{heuristic}.
-It is shown that \index{heuristic}heuristics are a class of algorithms that are used to solve optimisation problems.
-
-	\item \textbf{Section~\ref{sec:heuristics:gd}} presents seven low-level, gradient-based \index{heuristic}heuristics, including \acf{SGD}, \acf{Momentum}, \acf{NAG}, \acf{Adagrad}, \acf{RMSProp}, \acf{Adadelta} and \acf{Adam}.
-
-	\item \textbf{Section~\ref{sec:heuristics:mh}} presents three different population-based \acp{MH}, including \acf{PSO}, \acf{DE} and \acfp{GA}.
-
-	\item \textbf{Section~\ref{sec:heuristics:summary}} provides a brief summary of the chapter.
-\end{itemize}
-
-\section{Optimisation}\label{sec:heuristics:optimisation}
-
-Optimisation is the task of finding a solution to a given problem that is better than alternative solutions.
-Better stated by \citeauthor{ref:oldewage:2017}~\cite{ref:oldewage:2017}, optimisation is the task of finding values for a set of variables such that some measure of optimality is satisfied given a set of constraints.
-\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} breaks optimisations problems down into three components:
-
-\begin{itemize}
-	\item An \textbf{objective function}: Represents the quantity to be optimised and is used as the ``measure of optimality''.
-Optimisation can be defined in terms of the minimisation or maximisation of the objective function $f$.
-
-	\item A \textbf{set of unknowns or independent variables}: Affects the outcome of the objective function $f$ and is denoted as $x$.
-$f(x)$ is thus the quantification of the objective function over the unknowns, represented by $x$.
-Note that $x$ could be a scalar value, a vector or a matrix and notation is left out for simplicity.
-
-	\item A \textbf{set of constraints}: Restrict and limit the values that can be assigned to the unknowns, represented by $x$.
-Optimisation problems that must adhere to a set of constraints are referred to as \acfp{CSP}.
-\end{itemize}
-
-Optimisation problems come in a wide variety, and can be defined in terms of the number of variables used (uni- vs.
-multivariate), the number of objective functions used (single- vs.
-multi-objective), the degree of linearity (linear vs.
-quadratic/polynomial), the number of optima (uni- vs.
-multi-modal), the nature of the environment (static vs.
-dynamic), the types of variables used (separable vs.
-inseparable, discrete vs.
-continuous) and the set of constraints that the solution must adhere to (constrained vs unconstrained).
-
-Optima can be defined as \textit{local} or \textit{global} optima.
-Local optima is the best optimisation of $f(x)$ in a neighbourhood of solutions, while the global optima is the best optimisation of $f(x)$ over all solutions in the solution space.
-
-As stated in Chapter~\ref{chap:anns}, the training of an \acp{FFNN} is a particular type of optimisation problem, where the goal is to find the configuration of \textit{weights}, such that the \acs{FFNN} yields output that minimises some loss function.
-The mechanism by which the optimal weights for a \acs{FFNN} is sought out, is executed by an \index{optimisation algorithm}optimisation algorithm known as a \index{heuristic}heuristic.
-
-\section{What is a heuristic?}\label{sec:heuristics:what_is_a_heuristic}
-
-The term \textit{heuristic} comes from the Latin word \textit{heuristicus} which means ``to find out or discover''.~\citeauthor{ref:romanycia:1985}~\cite{ref:romanycia:1985} provide a complete study on the history and origins of the term \index{heuristic}\textit{heuristic}.
-From their research, a proposal is made to define \index{heuristic}heuristics in the context of \acf{AI}, as any device, be it a program, rule, piece of knowledge, which is added to a problem-solving system, in expectation that, on average, the performance will improve.
-
-In the context of this dissertation, a \index{heuristic}heuristic refers to an algorithmic search technique that serves as a guide to a search process where good solutions to a optimisation problem is being sought out.
-Different \index{heuristic}heuristics make use of different information during the search process~\cite{ref:kheiri:2017}.
-During training of \acp{FFNN}, \index{heuristic}heuristics such as gradient-based \index{heuristic}heuristics make use of the derivatives obtained by evaluating the \acs{FFNN}.
-It can thus be said that gradient-based \index{heuristic}heuristics make use of information directly from the \textit{search space}.
-On the contrary, \index{heuristic}heuristics such as \acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN}~\cite{ref:blum:2003}.
-The meta-information that \acp{MH} make use of could include ranked-performance of a population of candidate solutions, referred to as \textit{entities}.
-\index{meta-heuristic}Meta-heuristics are useful when there is imperfect information about the search space~\cite{ref:bianchi:2009}, and are generally less problem-specific than other classes of \index{heuristic}heuristics~\cite{ref:blum:2003}.
-This dissertation takes a particular interest in gradient-based \index{heuristic}heuristics and \acp{MH}.
-
-\section{Gradient-Based Heuristics}\label{sec:heuristics:gd}
+\subsection{Gradient-Based Heuristics}\label{sec:heuristics:gd}
 
 Gradient-based \index{heuristic}heuristics are optimisation techniques that make use of derivates obtained from evaluating the model being optimised.
-Specifically, in the context of a minimisation problem, these techniques are called \acf{GD} heuristics as they \textit{minimise} some loss function.
-\Acs{GD} is generally attributed to Cauchy~\cite{ref:lemarechal:2012}, who first suggested it in 1847.
-In 1907 Hadamard~\cite{ref:hadamard:1908} independently proposed a similar method.
-
-Although gradient-based \index{heuristic}heuristics where not the first \index{heuristic}heuristics used to train \acp{FFNN}
-\cite{ref:engelbrecht:2007}, they are certainly the most widely used.
-Gradient-based heuristics have become increasingly popular partly due to their simplicity and low computational overhead compared to other \index{heuristic}heuristics such as \acp{MH} and other second-order derivative methods such as Newtons' method.
 There are many variants of gradient-based \index{heuristic}heuristics, however, they all fundamentally apply the same generic \acf{GD} framework called \acf{BP}.
 
-\subsection{Backpropagation}\label{sec:heuristics:gd:backpropagation}
-
-Chapter~\ref{chap:anns} introduced \index {supervised learning}supervised learning and presented a number of loss functions.
 In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{FFNN} and the desired output.
 When using \acs{GD} to train \acp{FFNN}, the \index{loss function}loss function is used to adjust the weights of the \acs{FFNN} in order to minimise the error~\cite{ref:engelbrecht:2007}.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} states that training of \acp{FFNN} using \acs{GD}, is done by calculating the gradient of $\epsilon$ in \textit{weight-space}, and then moving the weight vector along the negative gradient.
-An illustration of \acs{GD} is given in Figure~\ref{fig:heuristics:gd:gd_illustration}.
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.75\textwidth]{images/gradient_descent.pdf}
-	\caption{An illustration of \acf{GD} over various time steps showing the minimisation of the error with regards to weight value.}
-	\label{fig:heuristics:gd:gd_illustration}
-\end{figure}
-
-In the context of training \textit{shallow} \acp{FFNN} using \index{supervised learning}supervised learning, the error signal is propagated backwards in the network from the output layer, through the hidden layer to the input layer, updating the weights at the output and hidden layers.
+In the context of training \acp{FFNN} using \index{supervised learning}supervised learning, the error signal is propagated backwards in the network from the output layer, through the hidden layer to the input layer, updating the weights at the output and hidden layers.
 The algorithm that propagates the error signal backwards is known as \acf{BP}.
@@
 
-The update step for \acs{GD} by means of \acs{BP} can be formulated as is shown in Equations~\eqref{eq:heuristics:gd:update_step_part_1} to \eqref{eq:heuristics:gd:update_step_part_4}.
+% The update step for \acs{GD} by means of \acs{BP} can be formulated as is shown in Equations~\eqref{eq:heuristics:gd:update_step_part_1} to \eqref{eq:heuristics:gd:update_step_part_4}.
 The general weight update step is given as
 
-\begin{equation}
-	\label{eq:heuristics:gd:update_step_part_1}
-	w_{i}(t) = w_{i}(t-1) + \Delta w_{i}(t)
-\end{equation}
+% \begin{equation}
+% 	\label{eq:heuristics:gd:update_step_part_1}
+% 	w_{i}(t) = w_{i}(t-1) + \Delta w_{i}(t)
+% \end{equation}
 
-where $w_{i}$ is the weight value at index $i$, $t$ is the time step, $\Delta w_{i}(t)$ is the weight update vector at index $i$ and time step $t$. The delta weight term $\Delta w_{i}(t)$, is given as
+% where $w_{i}$ is the weight value at index $i$, $t$ is the time step, $\Delta w_{i}(t)$ is the weight update vector at index $i$ and time step $t$.
+The delta weight term $\Delta w_{i}(t)$, is given as
 
-\begin{equation}
-	\label{eq:heuristics:gd:update_step_part_2}
-	\Delta w_{i}(t) = -\eta\frac{\partial \epsilon}{\partial w_{i}}
-\end{equation}
+% \begin{equation}
+% 	\label{eq:heuristics:gd:update_step_part_2}
+% 	\Delta w_{i}(t) = -\eta\frac{\partial \epsilon}{\partial w_{i}}
+% \end{equation}
 
-where $\eta$ is the learning rate and $\frac{\partial \epsilon}{\partial w_{i}}$ is the \textit{gradient} of the error, as a result of a loss function $\mathcal{E}$, relative to the weight at index $i$.
+% where $\eta$ is the learning rate and $\frac{\partial \epsilon}{\partial w_{i}}$ is the \textit{gradient} of the error, as a result of a loss function $\mathcal{E}$, relative to the weight at index $i$.
 The learning rate controls the step-size that is taken in the direction of the negative gradient at each time step.
@@
 
-\begin{equation}
-	\label{eq:heuristics:gd:update_step_part_3}
-	\frac{\partial \epsilon}{\partial w_{i}} = -2(t_{i,p} - o_{i,p})\frac{\partial f}{\partial net_{p}}z_{i,p}
-\end{equation}
+% \begin{equation}
+% 	\label{eq:heuristics:gd:update_step_part_3}
+% 	\frac{\partial \epsilon}{\partial w_{i}} = -2(t_{i,p} - o_{i,p})\frac{\partial f}{\partial net_{p}}z_{i,p}
+% \end{equation}
 
-where $t_{i,p}$ refers to the $i$-th element of the target value for pattern $p$, $o_{i,p}$ refers to the $i$-th element of the output value for pattern $p$, $f$ refers to the \index{activation function}activation function, $net_{p}$ refers to the \index{net input signal}net input signal for pattern $p$, and $z_{i,p}$ refers to the input value at index $i$ for pattern $p$.
+% where $t_{i,p}$ refers to the $i$-th element of the target value for pattern $p$, $o_{i,p}$ refers to the $i$-th element of the output value for pattern $p$, $f$ refers to the \index{activation function}activation function, $net_{p}$ refers to the \index{net input signal}net input signal for pattern $p$, and $z_{i,p}$ refers to the input value at index $i$ for pattern $p$.
 
-Finally, assuming the use of the \index{sigmoid}sigmoid activation function, the partial derivative of the activation function, relative to the net input signal is given as
+% Finally, assuming the use of the \index{sigmoid}sigmoid activation function, the partial derivative of the activation function, relative to the net input signal is given as
 
-\begin{equation}
-	\label{eq:heuristics:gd:update_step_part_4}
-	\frac{\partial f}{\partial net_{p}} = o_p(1 - o_{p})
-\end{equation}
+% \begin{equation}
+% 	\label{eq:heuristics:gd:update_step_part_4}
+% 	\frac{\partial f}{\partial net_{p}} = o_p(1 - o_{p})
+% \end{equation}
 
-Again, assuming the use of \acs{SSE} as the loss function, the pseudo-code implementation for the generic \acs{GD} algorithm is taken from~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:gd:gd} below.
+% Again, assuming the use of \acs{SSE} as the loss function, the pseudo-code implementation for the generic \acs{GD} algorithm is taken from~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:gd:gd} below.
 
-\begin{algorithm}[htb]
-	\caption{The pseudo-code algorithm for the generic \acf{GD} heuristic.}
-	\label{algo:heuristics:gd:gd}
-	\begin{algorithmic}
-		\State Initialise the \acs{FFNN} weights and biases, the learning rate $\eta$ and the time step/epoch $T=0$;
-		\While{stopping conditions are not met}
-		\State Let $\epsilon_{T} = 0$;
-		\For{each training pattern p}
-		\State Calculate the output of the hidden and output layers (feedforward);
-		\State Compute the error signals of the hidden and output layers;
-		\State Adjust the weights of the output and hidden layers (backpropagate);
-		\State $\epsilon_{T}$ += $[\epsilon_{T_{p}} = \sum^{K}_{k=1}(t_{k,p} - o_{k,p})^{2}]$;
-		\EndFor
-		\State $T += 1$;
-		\EndWhile
-	\end{algorithmic}
-\end{algorithm}
+% \begin{algorithm}[htb]
+% 	\caption{The pseudo-code algorithm for the generic \acf{GD} heuristic.}
+% 	\label{algo:heuristics:gd:gd}
+% 	\begin{algorithmic}
+% 		\State Initialise the \acs{FFNN} weights and biases, the learning rate $\eta$ and the time step/epoch $T=0$;
+% 		\While{stopping conditions are not met}
+% 		\State Let $\epsilon_{T} = 0$;
+% 		\For{each training pattern p}
+% 		\State Calculate the output of the hidden and output layers (feedforward);
+% 		\State Compute the error signals of the hidden and output layers;
+% 		\State Adjust the weights of the output and hidden layers (backpropagate);
+% 		\State $\epsilon_{T}$ += $[\epsilon_{T_{p}} = \sum^{K}_{k=1}(t_{k,p} - o_{k,p})^{2}]$;
+% 		\EndFor
+% 		\State $T += 1$;
+% 		\EndWhile
+% 	\end{algorithmic}
+% \end{algorithm}
 
@@
 Note that some subscripts related to layers, indices, time steps and training patterns are omitted for convenience.
-
-\subsection{Stochastic vs. Batch Training}\label{sec:heuristics:gd:sgd}
-
-This section shines light on the algorithmic implementation of \acs{BP} with specific context to stochastic and batch training.
-The implementation of \acs{GD} using stochastic training is referred to as \acf{SGD}.
-
-\acs{SGD} was one of the first widely used heuristics to train \acs{FFNN}, however, it is not without flaws.
-With stochastic training, only one training pattern is presented at each iteration/epoch.
-As such, weight updates are done with high variance and noise~\cite{ref:ruder:2016}.
-An illustration of the fluctuations caused by \acs{SGD} during training is given in Figure~\ref{fig:heuristics:gd:sgd}.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.8\textwidth]{images/sgd.pdf}
-	\caption{An illustration of \acf{SGD} fluctuations during training as taken from~\cite{ref:sgd:2006}.}
-	\label{fig:heuristics:gd:sgd}
-\end{figure}
-
-With batch training, all the training patterns are presented at once and the \acs{FFNN} converges to the global minimum of the loss function w.r.t $\boldsymbol{w}$ (assuming the loss function is convex).
-However, this is computationally expensive and impractical to implement in many situations.
-While \acs{SGD} is able to jump out of local minima into new, potentially better local minima~\cite{ref:ruder:2016}, \acs{SGD} complicates convergence to the minima as \acs{SGD} can potentially keep overshooting better minima.
-By slowly decreasing the learning rate $\eta$ during training, the same convergence behaviour is achieved as with batch training.
-
-A compromise is to make use of mini-batches of training patterns, where a small number of training patterns are presented to the \acs{FFNN} at once.
-This is referred to as \textit{mini-batch} training.
-Input patterns from mini-batches are approximations of the total population of training patterns.
-According to~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} this has two main advantages:
-
-\begin{itemize}
-	\item Mini-batch training reduces the high variance of weight updates as observed for \acs{SGD}, which leads to better convergence.
-
-	\item Mini-batch training allows for the implementation of \acs{GD} using highly optimised matrix operations, common to the state-of-the-art \acs{ML} libraries used today.
-\end{itemize}
 
@@
 
-\subsection{Momentum}\label{sec:heuristics:gd:momentum}
+\subsubsection{Momentum}\label{sec:heuristics:gd:momentum}
 
@@
 
-\subsection{Nesterov Accelerated Gradients}\label{sec:heuristics:nag}
+\subsubsection{Nesterov Accelerated Gradients}\label{sec:heuristics:nag}
 
@@
 
-\subsection{Adaptive Gradients}\label{sec:heuristics:adagrad}
+\subsubsection{Adaptive Gradients}\label{sec:heuristics:adagrad}
 
@@
 
-\subsection{Adaptive Learning Rate}\label{sec:heuristics:adadelta}
+\subsubsection{Adaptive Learning Rate}\label{sec:heuristics:adadelta}
 
@@
 
-\subsection{Root Mean Squared Error Propagation}\label{sec:heuristics:rmsprop}
+\subsubsection{Root Mean Squared Error Propagation}\label{sec:heuristics:rmsprop}
 
@@
 
-\subsection{Adaptive Moments Estimation}\label{sec:heuristics:adam}
+\subsubsection{Adaptive Moments Estimation}\label{sec:heuristics:adam}
 
@@
 
-\section{Meta-Heuristics}\label{sec:heuristics:mh}
+\subsection{Meta-Heuristics}\label{sec:heuristics:mh}
 
@@
 
-\subsection{Particle Swarm Optimisation}\label{sec:heuristics:mh:pso}
+\subsubsection{Particle Swarm Optimisation}\label{sec:heuristics:mh:pso}
 
@@
 
-\subsection{Differential Evolution}\label{sec:heuristics:mh:de}
+\subsubsection{Differential Evolution}\label{sec:heuristics:mh:de}
 
@@
 
-\subsection{Genetic Algorithms}\label{sec:heuristics:mh:ga}
+\subsubsection{Genetic Algorithms}\label{sec:heuristics:mh:ga}
 
@@
 \end{itemize}
-
-\section{Summary}
-\label{sec:heuristics:summary}
-
-This chapter provided detailed background information on \index{heuristic}heuristics.
-Different heuristics were presented that have been shown to be able to train \acp{FFNN}.
-Two main groups of \index{heuristic}heuristics where presented and discussed in detail.
-These include gradient-based \index{heuristic}heuristics and \acfp{MH}.
-A number of different variants for each group have been presented and was discussed in detail.

### 2023-01-22 article/sections/01-introduction.tex
✨ (article): Heuristics section done

@@
 
-Many different heuristics have been developed and used to train \acp{ANN}~\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
+Many different heuristics have been developed and used to train \acp{ANN}  \cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
 Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses.
@@
 This process is often non-trivial and could be a time-consuming exercise.
-Selection of the best heuristic to train \acp{ANN}, is often problem specific~\cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
+Selection of the best heuristic to train \acp{ANN}, is often problem specific  \cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
 
@@
 This approach focuses on the hybridisation of learning paradigms.
-One such form of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem~\cite{ref:burke:2013}.
+One such form of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem  \cite{ref:burke:2013}.
 These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.
@@
 However, research on the application of \acp{HH} in the context of \acs{ANN} training is scarce.
-\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
+\citeauthor{ref:nel:2021}  \cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
 
@@
 
-The remainder of this article is structured as follows: Section~\ref{sec:anns} provides background information on \acp{ANN}.
-Section~\ref{sec:heuristics} provides details on various types of heuristics that have been used to train \acp{FFNN}.
-Section~\ref{sec:hhs} presents background information on \acp{HH} and \index{meta-learning}meta-learning.
-Section~\ref{sec:probability} presents background information on probability theory.
-Section~\ref{sec:bhh} presents the developed \Acs{BHH}.
-Section~\ref{sec:methodology} presents a detailed description of the empirical process and the setup of each experiment.
-Section~\ref{sec:results} provides and discusses the results of the empirical study.
-Section~\ref{sec:conclusion} summarises the research that is done along with a brief overview of the findings made throughout the research process.
+The remainder of this article is structured as follows: Section  \ref{sec:anns} provides background information on \acp{ANN}.
+Section  \ref{sec:heuristics} provides details on various types of heuristics that have been used to train \acp{FFNN}.
+Section  \ref{sec:hhs} presents background information on \acp{HH} and \index{meta-learning}meta-learning.
+Section  \ref{sec:probability} presents background information on probability theory.
+Section  \ref{sec:bhh} presents the developed \Acs{BHH}.
+Section  \ref{sec:methodology} presents a detailed description of the empirical process and the setup of each experiment.
+Section  \ref{sec:results} provides and discusses the results of the empirical study.
+Section  \ref{sec:conclusion} summarises the research that is done along with a brief overview of the findings made throughout the research process.

### 2023-01-22 article/sections/02-artificial-neural-networks.tex
✨ (article): Heuristics section done

@@
 
-\acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain~\cite{ref:engelbrecht:2007}.
-\acp{ANN} have been successfully applied to a range of problem classes.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} summarises some common problems that are solved using \acp{ANN}.
-These include classification~\cite{ref:khan:2001}, pattern matching~\cite{ref:cannady:1998, ref:kumar:1994}, pattern completion~\cite{ref:dayhoff:2001}, optimisation~\cite{ref:specht:1991} and data mining~\cite{ref:singh:2009}.
+\acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain  \cite{ref:engelbrecht:2007}.
+\acp{ANN} have been successfully applied to a range of problem classes.
+\citeauthor{ref:engelbrecht:2007}  \cite{ref:engelbrecht:2007} summarises some common problems that are solved using \acp{ANN}.
+These include classification  \cite{ref:khan:2001}, pattern matching  \cite{ref:cannady:1998, ref:kumar:1994}, pattern completion  \cite{ref:dayhoff:2001}, optimisation  \cite{ref:specht:1991} and data mining  \cite{ref:singh:2009}.
+\Acp{AN} provide the fundamental building blocks for \acp{ANN}.
 
@@
 
-\Acp{AN} provide the fundamental building blocks for \acp{ANN}.
-The \acs{AN} implements a non-linear mapping from $\mathbb{R}^{I}$ to $\mathbb{R}^{T}$, usually in the ranges $[0,1]$ or $[-1,1]$, depending on the problem being solved ~\cite{ref:engelbrecht:2007}.
-$I$ is the total number of dimensions of the input in real-number space ($\mathbb{R}$), and $T$ is the total number of dimensions of the target (desired output) in real-number space.
-The \acs{AN} implements various components and is illustrated in Figure~\ref{fig:artificial_neuron}.
+The \acs{AN} implements a non-linear mapping from some $I$-dimensional, real-numbered input space to some $T$-dimensional, real-numbered output space.
+The output space is usually in the ranges $[0,1]$ or $[-1,1]$, depending on the problem being solved \cite{ref:engelbrecht:2007}.
+The \acs{AN} implements various components and is illustrated in Figure  \ref{fig:artificial_neuron}.
 
@@
 
-Each of the components of the \acs{AN}, presented in Figure~\ref{fig:artificial_neuron}, is inspired by some element of the \acs{BN}.
+Each of the components of the \acs{AN}, presented in Figure  \ref{fig:artificial_neuron}, is inspired by some element of the \acs{BN}.
 The input ($\boldsymbol{x}$) models the activations received from the pre-synaptic neuron.
@@
 The topology of the \acs{ANN} refers to the way that layers of \acp{AN} are connected to each other.
-There are many different topologies~\cite{ref:miikkulainen:2010}.
+There are many different topologies  \cite{ref:miikkulainen:2010}.
 
 This research focuses on a particular type of \acs{ANN}, referred to as \acp{FFNN}.
-\acp{FFNN} were the first and simplest type of \acp{ANN} developed~\cite{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order.
-Furthermore, \acp{FFNN} implement \index{fully connected topology}fully connected topologies, where each \acs{AN} in one layer is connected to all \acp{AN} in the next, without any cycles~\cite{ref:zell:1994}.
+\acp{FFNN} were the first and simplest type of \acp{ANN} developed  \cite{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order.
+Furthermore, \acp{FFNN} implement \index{fully connected topology}fully connected topologies, where each \acs{AN} in one layer is connected to all \acp{AN} in the next, without any cycles  \cite{ref:zell:1994}.
 
 In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
-An illustration of a \acs{FFNN} is given in Figure~\ref{fig:ffnn}.
+An illustration of a \acs{FFNN} is given in Figure  \ref{fig:ffnn}.
 
@@
 
-In Figure~\ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input vector $\boldsymbol{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer, $y_k$ refers to the $k$-th dimension in the output vector $\boldsymbol{y}$, $v_{i,j}$ refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the output node $y_k$.
+In Figure  \ref{fig:ffnn}, $x_i$ refers to the $i$-th dimension in the input vector $\boldsymbol{x}$, $h_j$ refers to the $j$-th dimension in the hidden layer, $y_k$ refers to the $k$-th dimension in the output vector $\boldsymbol{y}$, $v_{i,j}$ refers to the weight associated with input node $x_i$ and the hidden node $h_j$, and $w_{j,k}$ refers to the weight associated with hidden node $h_j$ and the output node $y_k$.
 
@@
 
-\index{supervised learning}Supervised learning is the process of training where the data that is presented to the \acs{FFNN} during training, includes the desired solution~\cite{ref:geron:2017}.
-The \acs{FFNN} learns the mapping function from the input to the target output~\cite{ref:brownlee:2016}.
+\index{supervised learning}Supervised learning is the process of training where the data that is presented to the \acs{FFNN} during training, includes the desired solution  \cite{ref:geron:2017}.
+The \acs{FFNN} learns the mapping function from the input to the target output  \cite{ref:brownlee:2016}.

### 2023-01-22 article/sections/03-heuristics.tex
✨ (article): Heuristics section done

@@
 A \index{heuristic}heuristic refers to an algorithmic search technique that serves as a guide to a search process where good solutions to a optimisation problem is being sought out.
-Many different techniques have been used to train \acp{FFNN}~\cite{ref:kingma:2014}.
-At the time of writing, the majority of work that is published around the training of \acp{FFNN}, involves the use of gradient-based techniques~\cite{ref:nel:2021}.
-However, other techniques have also been used to successfully train \acp{FFNN}, including \acp{MH} such as \acf{PSO}~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}, \acf{DE}~\cite{ref:espinal:2011} and \acfp{GA}~\cite{ref:gupta:1999}.
-This research takes a particular interest in both gradient-based heuristics as well as \acp{MH}.
+Many different techniques have been used to train \acp{FFNN} \cite{ref:kingma:2014}.
+At the time of writing, the majority of work that is published around the training of \acp{FFNN} involves the use of gradient-based techniques \cite{ref:nel:2021}.
 
@@
 
-Gradient-based \index{heuristic}heuristics are optimisation techniques that make use of derivates obtained from evaluating the model being optimised.
-There are many variants of gradient-based \index{heuristic}heuristics, however, they all fundamentally apply the same generic \acf{GD} framework called \acf{BP}.
+Gradient-based \index{heuristic}heuristics are optimisation techniques that make use of derivates obtained from evaluating the \acs{ANN} being trained.
+In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{ANN} and the desired output.
+When using \acs{GD} to train \acp{ANN}, the \index{loss function}loss function is used to adjust the weights of the \acs{ANN} in order to minimise the error \cite{ref:engelbrecht:2007}.
 
-In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{FFNN} and the desired output.
-When using \acs{GD} to train \acp{FFNN}, the \index{loss function}loss function is used to adjust the weights of the \acs{FFNN} in order to minimise the error~\cite{ref:engelbrecht:2007}.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} states that training of \acp{FFNN} using \acs{GD}, is done by calculating the gradient of $\epsilon$ in \textit{weight-space}, and then moving the weight vector along the negative gradient.
-
-In the context of training \acp{FFNN} using \index{supervised learning}supervised learning, the error signal is propagated backwards in the network from the output layer, through the hidden layer to the input layer, updating the weights at the output and hidden layers.
-The algorithm that propagates the error signal backwards is known as \acf{BP}.
-\Acs{BP} was popularised by~\citeauthor{ref:werbos:1994}~\cite{ref:werbos:1994}.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} states that \acs{BP} provides a procedure for updating the network weights, layer by layer, by evaluating the derivatives of the error function $\mathcal{E}$, with respect to the weights at each layer.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} describes the \acs{BP} process in two steps:
-
-\begin{itemize}
-	\item \textbf{Feedforward Pass}: During this phase the output values of the \acs{FFNN} is calculated for each training pattern.
-
-	\item \textbf{Backward Propagation}: During this phase the error signal is propagated backwards from the output layer, through the hidden layer, to the input layer of the \acs{FFNN}.
-Weights at the output and hidden layers are then adjusted as functions of the backpropagated error signal.
-\end{itemize}
-
-% The update step for \acs{GD} by means of \acs{BP} can be formulated as is shown in Equations~\eqref{eq:heuristics:gd:update_step_part_1} to \eqref{eq:heuristics:gd:update_step_part_4}.
-The general weight update step is given as
-
-% \begin{equation}
-% 	\label{eq:heuristics:gd:update_step_part_1}
-% 	w_{i}(t) = w_{i}(t-1) + \Delta w_{i}(t)
-% \end{equation}
-
-% where $w_{i}$ is the weight value at index $i$, $t$ is the time step, $\Delta w_{i}(t)$ is the weight update vector at index $i$ and time step $t$.
-The delta weight term $\Delta w_{i}(t)$, is given as
-
-% \begin{equation}
-% 	\label{eq:heuristics:gd:update_step_part_2}
-% 	\Delta w_{i}(t) = -\eta\frac{\partial \epsilon}{\partial w_{i}}
-% \end{equation}
-
-% where $\eta$ is the learning rate and $\frac{\partial \epsilon}{\partial w_{i}}$ is the \textit{gradient} of the error, as a result of a loss function $\mathcal{E}$, relative to the weight at index $i$.
-The learning rate controls the step-size that is taken in the direction of the negative gradient at each time step.
-Assuming the use of \acs{SSE} as the loss function, the partial derivative of $\epsilon$, relative to the weight vector $\boldsymbol{w}$, at index $i$, is given as
-
-% \begin{equation}
-% 	\label{eq:heuristics:gd:update_step_part_3}
-% 	\frac{\partial \epsilon}{\partial w_{i}} = -2(t_{i,p} - o_{i,p})\frac{\partial f}{\partial net_{p}}z_{i,p}
-% \end{equation}
-
-% where $t_{i,p}$ refers to the $i$-th element of the target value for pattern $p$, $o_{i,p}$ refers to the $i$-th element of the output value for pattern $p$, $f$ refers to the \index{activation function}activation function, $net_{p}$ refers to the \index{net input signal}net input signal for pattern $p$, and $z_{i,p}$ refers to the input value at index $i$ for pattern $p$.
-
-% Finally, assuming the use of the \index{sigmoid}sigmoid activation function, the partial derivative of the activation function, relative to the net input signal is given as
-
-% \begin{equation}
-% 	\label{eq:heuristics:gd:update_step_part_4}
-% 	\frac{\partial f}{\partial net_{p}} = o_p(1 - o_{p})
-% \end{equation}
-
-% Again, assuming the use of \acs{SSE} as the loss function, the pseudo-code implementation for the generic \acs{GD} algorithm is taken from~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:gd:gd} below.
-
-% \begin{algorithm}[htb]
-% 	\caption{The pseudo-code algorithm for the generic \acf{GD} heuristic.}
-% 	\label{algo:heuristics:gd:gd}
-% 	\begin{algorithmic}
-% 		\State Initialise the \acs{FFNN} weights and biases, the learning rate $\eta$ and the time step/epoch $T=0$;
-% 		\While{stopping conditions are not met}
-% 		\State Let $\epsilon_{T} = 0$;
-% 		\For{each training pattern p}
-% 		\State Calculate the output of the hidden and output layers (feedforward);
-% 		\State Compute the error signals of the hidden and output layers;
-% 		\State Adjust the weights of the output and hidden layers (backpropagate);
-% 		\State $\epsilon_{T}$ += $[\epsilon_{T_{p}} = \sum^{K}_{k=1}(t_{k,p} - o_{k,p})^{2}]$;
-% 		\EndFor
-% 		\State $T += 1$;
-% 		\EndWhile
-% 	\end{algorithmic}
-% \end{algorithm}
-
-A simplified notation is proposed from which the gradient-based heuristics can be compared.
-Consider a simplification of the update-step for \acs{SGD} as presented in Equations~\eqref{eq:heuristics:gd:update_step_part_1} and~\eqref{eq:heuristics:gd:update_step_part_2} where $\frac{\partial \epsilon}{\partial w_{i}}$ is simply represented as the gradient term $\boldsymbol{g}$, resulting in a simplified weight update step and is given as
+The simplest type of \acs{GD} algorithm is referred to as \acs{SGD}, which implements a gradient-based weight update step for each training pattern. The weight update step and is given as
 
@@
 
-where $\boldsymbol{w}$ refers to the weight vector, $\eta$ refers to the learning rate as before and $\boldsymbol{g}$ refers to the gradient of the error function relative to weight vector.
-Note that some subscripts related to layers, indices, time steps and training patterns are omitted for convenience.
+where $\boldsymbol{w}$ refers to the weight vector, $\eta$ refers to the learning rate, which controls the step size and $\boldsymbol{g}$ refers to the gradient of the error function relative to weight vector.
 
-In the context of this dissertation, the implementation of \acs{SGD} refers to the mini-batch training implementation of \acs{GD}.
-Although mini-batch training does provide a compromise between stochastic and batch training, there are still a number of challenges faced by mini-batch training.
-These include:
+There are many variants of gradient-based \index{heuristic}heuristics, however, they all fundamentally apply the same generic \acf{GD} framework that propagates the error signal backwards through the \acs{ANN}.
+This algorithm is known as \acf{BP}.
+\Acs{BP} was popularised by \citeauthor{ref:werbos:1994} \cite{ref:werbos:1994}.
+\citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} describes the \acs{BP} process in two steps.
+During the forward pass step, the output values of the \acs{FFNN} is calculated for each training pattern.
+Then, during the backward propogation step, the error signal is propagated backwards from the output layer, through the hidden layer, to the input layer of the \acs{FFNN}.
+Weights at the output and hidden layers are then adjusted as functions of the backpropagated error signal.
 
-\begin{itemize}
-	\item The appropriate value to use for the learning rate $\eta$, is difficult to determine and is often problem-specific.
-A learning rate that is too small causes premature exploitation, leading to slow and bad convergence.
-On the contrary, a learning rate that is too high may lead to bad learning outcomes as the heuristic keeps overshooting good minima.
+In the context of this research, the implementation of \acs{SGD} refers to the mini-batch training implementation of \acs{GD}, where a small batch of training patterns are fed to the \acs{FFNN} at once and the error function is aggregated across all training patterns.
 
-	\item Learning rate schedules~\cite{ref:robbins:1951} can be introduced to dynamically change the learning rate throughout the training process, however, these schedules and their parameters have to be defined a priori and are often problem specific~\cite{ref:darken:1992}.
-
-	\item The learning rate that has been introduced so far is applied to all elements of the weight update vector.
-If the training data is sparse and the features have varying frequencies, an equal update to all weight elements is inefficient.
-Larger weight updates are required for less frequently occurring features.
-Inefficient updates of all elements in the weight vectors contribute to the credit assignment problem~\cite{ref:rumelhart:1986}, common to \acs{GD} variants.
-
-	\item It is difficult to avoid getting trapped in local minima, especially for highly non-convex loss functions used for training \acp{FFNN}.
-\citeauthor{ref:dauphin:2014}~\cite{ref:dauphin:2014} mentions the role of saddle points in getting trapped in local minima.
-Saddle points are points at which one dimensions slopes upwards, while another dimension slopes downwards.
-\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that these saddle points are usually surrounded by plateaus of the same error, leading to gradients that are close to zero in all dimensions.
-\end{itemize}
-
-Alternative variants have been proposed that lead to better control over the convergence characteristics caused by \acs{GD}. The first of these \acs{GD} variants include \acs{Momentum}.
-
-\subsubsection{Momentum}\label{sec:heuristics:gd:momentum}
-
-Research shows that \acs{SGD} has difficulty navigating ravines~\cite{ref:sutton:1986}.
-Ravines are areas where the surface curves much more steeply in one dimension than in another.
-These ravines are common around local minima.
-As such, \acs{SGD} is shown to oscillate across the slopes of the ravine while only making minor progress towards the local minima.
-
-\Acs{Momentum} ~\cite{ref:qian:1999} is a variant of \acs{SGD} that helps accelerate \acs{SGD} in the relevant direction, dampening oscillations.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that this is done by adding a fraction $\alpha$, of the weight update vector of the previous time step to the current weight update vector.
-An illustration of \acs{SGD} with and without momentum is given in Figure~\ref{fig:heuristics:gd:sgd_with_and_without_momentum}.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.99\textwidth]{images/sgd_with_and_without_momentum.pdf}
-	\caption{An illustration of \acf{SGD} with and without momentum taken from~\cite{ref:du:2019}.}
-	\label{fig:heuristics:gd:sgd_with_and_without_momentum}
-\end{figure}
-
-The accumulation of momentum is given as
-
-\begin{equation}
-	\boldsymbol{v} = \alpha \boldsymbol{v} - \eta \boldsymbol{g}
-	\label{eq:heuristics:gd:momentum_part_1}
-\end{equation}
-
-while the update step is then amended as
-
-\begin{equation}
-	\boldsymbol{w} = \boldsymbol{w} + \boldsymbol{v}
-	\label{eq:heuristics:gd:momentum_part_2}
-\end{equation}
-
-By redefining the \acs{SGD} update steps as shown above in Equations~\eqref{eq:heuristics:gd:momentum_part_1} and~\eqref{eq:heuristics:gd:momentum_part_2}, the \acs{Momentum} heuristic allows for the increase of momentum for dimensions whose gradients point in the same direction, while simultaneously reducing momentum for dimensions whose gradients change direction, leading to faster convergence and less oscillation.
-The momentum term $\alpha$ is usually set to 0.9~\cite{ref:engelbrecht:2007, ref:ruder:2016}.
-
-\subsubsection{Nesterov Accelerated Gradients}\label{sec:heuristics:nag}
-
-\Acf{NAG} is a variant of the \acs{Momentum} heuristic developed by~\citeauthor{ref:sutskever:2013}~\cite{ref:sutskever:2013} and is inspired by~\citeauthor{ref:nesterov:1983}'s~\cite{ref:nesterov:1983} work on optimising convex functions.
-\acs{NAG} provides an improvement to the momentum accumulation term by providing a look-ahead term that better refines the weight update step.
-
-In the \acs{NAG} heuristic, the gradient is not calculated w.r.t the current weights, but rather w.r.t the approximate future positions of the weights~\cite{ref:sutskever:2013, ref:ruder:2016}.
-An illustration of the weight update vector using \acs{NAG} is taken from Geoffrey Hinton's lecture on mini-batch \acs{GD}~\cite{ref:hinton:2012} and is presented in Figure~\ref{fig:heuristics:gd:nag} below.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.95\textwidth]{images/nag.pdf}
-	\caption{An illustration of the weight update vector for \acf{NAG} taken from~\cite{ref:hinton:2012}.}
-	\label{fig:heuristics:gd:nag}
-\end{figure}
-
-The difference in the update step for \acs{Momentum} and the update step for \acs{NAG} as developed by~\citeauthor{ref:sutskever:2013}~\cite{ref:sutskever:2013} is described by~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} as follows.
-\acs{Momentum} first calculates the current gradient, represented by the small \textcolor{blue}{blue} vector in Figure~\ref{fig:heuristics:gd:nag} and then takes a large step in the direction of the updated accumulated gradient, presented by the big \textcolor{blue}{blue} vector.
-In contrast, \acs{NAG} first takes a big step in the direction of the previous accumulated gradient presented by the \textcolor{brown}{brown} vector.
-At this point the gradient is measured and \acs{NAG} makes a correction represented by the \textcolor{red}{red} vector.
-The complete update step is represented by the green vector.
-By anticipating approximate future positions of the weights, the weight update step as defined by \acs{NAG} controls the optimisation process from going too fast and results in increased responsiveness~\cite{ref:bengio:2013}.
-Along with the same velocity update step for \acs{Momentum}, as presented in Equation~\eqref{eq:heuristics:gd:momentum_part_1}, the \acs{NAG} weight update step is given as
-
-\begin{equation}
-	\label{eq:heuristics:gd:nag_part_2}
-	\begin{split}
-		\boldsymbol{w} = \boldsymbol{w} + \alpha \boldsymbol{v} - \eta \boldsymbol{g}
-	\end{split}
-\end{equation}
-
-\subsubsection{Adaptive Gradients}\label{sec:heuristics:adagrad}
-
-\Acf{Adagrad} is an adaptation of \acs{SGD} that implements a learning rate for every element in the weight vector and is developed by \citeauthor{ref:duchi:2011}~\cite{ref:duchi:2011}.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that \acs{Adagrad} adapts the learning rate to the elements of the weight vector, by  performing small updates (i.e.
-low learning rates) for weights associated with frequently occurring features and larger updates (i.e.
-high learning rates) for weights associated with infrequent features.
-For this reason, \acs{Adagrad} is well suited for dealing with situations where training data is sparse.
-
-In the \acs{GD} variants presented thus far, the weight updates have been applied by making use of the same learning rate $\eta$, for all elements of the weight update vector.
-\Acs{Adagrad} uses a different learning rate for every weight element $w_{i}$, at every time step $t$.
-The weight update step for \acs{Adagrad} is given as
-
-\begin{equation}
-	\label{eq:heuristics:gd:adagrad_part_1}
-	\begin{split}
-		w_{t+1,i} = w_{t,i} - \frac{\eta}{\sqrt{G_{t,ii} + \epsilon}}.g_{t,i}
-	\end{split}
-\end{equation}
-
-where $w_{i}$ is the $i$-th element of the weight vector, $G_{t,ii} \in \mathbb{R}^{d \times d}$ is a diagonal matrix where each diagonal element $i,i$, is the sum of the squared gradients w.r.t.
-$w_{i}$, up to time step $t$ and $\epsilon$ is a smoothing term that avoids division by zero and is set to an insignificant value such as $1 \times 10^{-8}$.
-Since $\boldsymbol{G_{t}}$ contains the sum of the squares of the gradients along its diagonal, the weight update step can be vectorised and updated using the matrix-vector product, represented by $\odot$, between $G_{t,i}$ and $g_{t,i}$.
-The simplified update step as implemented by \acs{Adagrad} is given as
-
-\begin{equation}
-	\label{eq:heuristics:gd:adagrad_part_2}
-	\begin{split}
-		w_{t+1,i} = w_{t,i} - \frac{\eta}{\sqrt{G_{t,i} + \epsilon}} \odot g_{t,i}
-	\end{split}
-\end{equation}
-
-\Ac{Adagrad}'s main benefit is that it does not require manual tuning of the learning rate $\eta$.
-However, a problem with \acs{Adagrad} is in the accumulation of squared gradients in the denominator, represented by $\boldsymbol{G_{t}}$.
-Since every term that is added is positive, $\boldsymbol{G_{t}}$ keeps growing, leading to a situation where the learning rate shrinks to the point that the heuristic is no longer able to learn.
-
-\subsubsection{Adaptive Learning Rate}\label{sec:heuristics:adadelta}
-
-\citeauthor{ref:zeiler:2012}~\cite{ref:zeiler:2012} presents \acs{Adadelta}, an improvement of \acs{Adagrad} that eliminates the accumulation of squared gradients in the denominator.~\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that instead of accumulating all past squared gradients as in the case of \acs{Adagrad}, \acs{Adadelta} restricts the window of accumulation to a window with a fixed size $W$.
-However, storing $W$ previous squared gradients is very inefficient.
-Instead, the accumulation of gradients over $W$ steps is defined recursively as a decaying average of all past squared gradients.
-The moving average of squared gradients at time step $t$, denoted by $E[\boldsymbol{g}^{2}]_{t}$  depends on a fraction $\alpha$ of the previous average of squared gradients and the current gradient, similar to the update step for \acs{Momentum}.
-Also similar to \acs{Momentum}, $\alpha$ is set to 0.9.
-The update step for $E[\boldsymbol{g}^{2}]_{t}$ is given as
-
-\begin{equation}
-	\label{eq:heuristics:gd:adadelta_part_1}
-	\begin{split}
-		E[\boldsymbol{g}^{2}]_{t} = \alpha E[\boldsymbol{g}^{2}]_{t - 1} + (1 - \alpha)\boldsymbol{g}_{t}^{2}
-	\end{split}
-\end{equation}
-
-To illustrate the difference between \acs{Adagrad} and \acs{Adadelta}, the \acs{SGD} weight update step for \acs{Adagrad}, as presented in~\eqref{eq:heuristics:gd:adagrad_part_2} is rewritten such that the diagonal matrix $\boldsymbol{G_{t}}$, is replaced with the moving average of squared gradients and is given as
-
-\begin{equation}
-	\label{eq:heuristics:gd:adadelta_part_2}
-	\begin{split}
-		\boldsymbol{w}_{t+1} = \boldsymbol{w}_{t} - \frac{\eta}{\sqrt{E[\boldsymbol{g}^{2}]_{t} + \epsilon}} \boldsymbol{g}_{t}
-	\end{split}
-\end{equation}
-
-Since the denominator is the \acf{RMS} error criterion of the gradient, the criteria short-hand notation is used and is given as
-
-\begin{equation}
-	\label{eq:heuristics:gd:adadelta_part_3}
-	\begin{split}
-		\boldsymbol{w}_{t+1} = \boldsymbol{w}_{t} - \frac{\eta}{RMS[\boldsymbol{g}]_{t}} \boldsymbol{g}_{t}
-	\end{split}
-\end{equation}
-
-~\citeauthor{ref:zeiler:2012}~\cite{ref:zeiler:2012} noted that the units of the update step as presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_3} do not match.
-The weight update vector should have the same hypothetical units as the weight vector.
-To fix the aforementioned problem, another exponentially decaying average is defined in terms of squared weight updates and is given as
-
-\begin{equation}
-	\label{eq:heuristics:gd:adadelta_part_4}
-	\begin{split}
-		E[\Delta \boldsymbol{w}^{2}]_{t} = \alpha E[\Delta \boldsymbol{w}^{2}]_{t - 1} + (1 - \alpha)\Delta \boldsymbol{w}_{t}^{2}
-	\end{split}
-\end{equation}
-
-The \acf{RMS} error of weight updates is given as
-
-\begin{equation}
-	\label{eq:heuristics:gd:adadelta_part_5}
-	\begin{split}
-		RMS[\Delta \boldsymbol{w}]_{t} = \sqrt{E[\Delta \boldsymbol{w}^{2}]_{t} + \epsilon}
-	\end{split}
-\end{equation}
-
-Note that $RMS[\Delta \boldsymbol{w}]_{t}$ is unknown at time step $t$.
-$RMS[\Delta \boldsymbol{w}]_{t}$ is approximated with the \acf{RMS} of weight updates until the previous time step.
-The learning rate in Equation~\eqref{eq:heuristics:gd:adadelta_part_3} is then replaced.
-The weight update step for \acs{Adadelta} is then concluded and is given as
-
-\begin{equation}
-	\label{eq:heuristics:gd:adadelta_part_6}
-	\begin{split}
-		\boldsymbol{w}_{t+1} = \boldsymbol{w}_{t} - \frac{RMS[\Delta \boldsymbol{w}]_{t-1}}{RMS[\boldsymbol{g}]_{t}} \boldsymbol{g}_{t}
-	\end{split}
-\end{equation}
-
-The main advantage of \acs{Adadelta} is in removing the learning rate, which eliminates the need for hyper-parameter tuning of the learning rate.
-
-\subsubsection{Root Mean Squared Error Propagation}\label{sec:heuristics:rmsprop}
-
-\Acf{RMSProp}, presented by~\citeauthor{ref:hinton:2012}~\cite{ref:hinton:2012} is similar to \acs{Adadelta}  and was developed independently around the same time.
-\acs{RMSProp} is the same as the first weight update vector for \acs{Adadelta}, presented in Equation~\eqref{eq:heuristics:gd:adadelta_part_2}.
-A disadvantage of \acs{RMSProp} is that it still includes the learning rate term $\eta$ that needs to be tuned.
-For \acs{RMSProp},~\citeauthor{ref:hinton:2012}~\cite{ref:hinton:2012} suggests $\alpha$ be set to 0.9 and $\eta$ be set to $0.001$.
-
-\subsubsection{Adaptive Moments Estimation}\label{sec:heuristics:adam}
-
-\Acf{Adam} is another variant of \acs{SGD} that includes adaptive learning rates and is presented by~\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014}.
-In addition to storing an exponentially decaying average of past squared gradients like \acs{Adadelta} and \acs{RMSProp}, \acs{Adam} also stores an exponentially decaying average of past gradients, similar to \acs{Momentum}~\cite{ref:ruder:2016}.~\citeauthor{ref:heusel:2017}~\cite{ref:heusel:2017} uses the analogy that, if \acs{Momentum} can be seen as a ball running down a slope, then \acs{Adam} behaves like a heavy ball with friction, which prefers flat minima in the error surface.
-The decaying averages for past gradients and past squared gradients is given in Equations~\eqref{eq:heuristics:gd:adam_part_1} and~\eqref{eq:heuristics:gd:adam_part_2} respectively.
-
-\begin{equation}
-	\label{eq:heuristics:gd:adam_part_1}
-	\begin{split}
-		\boldsymbol{m}_{t+1} = \beta_{1}\boldsymbol{m}_{t} + (1 - \beta_{1})\boldsymbol{g}_{t}
-	\end{split}
-\end{equation}
-
-\begin{equation}
-	\label{eq:heuristics:gd:adam_part_2}
-	\begin{split}
-		\boldsymbol{v}_{t+1} = \beta_{2}\boldsymbol{v}_{t} + (1 - \beta_{2})\boldsymbol{g}^{2}_{t}
-	\end{split}
-\end{equation}
-
-In Equations~\eqref{eq:heuristics:gd:adam_part_1} and~\eqref{eq:heuristics:gd:adam_part_2} above, $\beta_{1}$ and $\beta_{2}$ are decay rates, similar to $\alpha$ for \acs{Momentum}.
-\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} suggest default values $\beta_{1}=0.9$, $\beta_{2}=0.999$ and $\epsilon = 1 \times 10^{-8}$.
-
-\citeauthor{ref:ruder:2016}~\cite{ref:ruder:2016} mentions that $\boldsymbol{m}_{t}$ and $\boldsymbol{v}_{t}$ presented above are estimates of the first moment (the mean) and the second moment (the uncentered variance) of the gradients respectively.
-~\citeauthor{ref:kingma:2014}~\cite{ref:kingma:2014} mentions that because $\boldsymbol{m}_{t}$ and $\boldsymbol{v}_{t}$ are initialised to be vectors of 0's, they are biased towards 0.
-The aforementioned bias is especially prominent during the initial time steps and/or when the decay rates $\beta_{1}$ and $\beta_{2}$ are small ($\beta_{1}$ and $\beta_{2}$ are close to 1).
-The bias-corrected first and second moment estimates are presented in Equations~\eqref{eq:heuristics:gd:adam_bc_first_moment} and~\eqref{eq:heuristics:gd:adam_bc_second_moment} respectively.
-
-\begin{equation}
-	\label{eq:heuristics:gd:adam_bc_first_moment}
-	\begin{split}
-		\hat{\boldsymbol{m}}_{t} = \frac{\boldsymbol{m}_{t}}{1 - \beta^{t}_{1}}
-	\end{split}
-\end{equation}
-
-\begin{equation}
-	\label{eq:heuristics:gd:adam_bc_second_moment}
-	\begin{split}
-		\hat{\boldsymbol{v}}_{t} = \frac{\boldsymbol{v}_{t}}{1 - \beta^{t}_{2}}
-	\end{split}
-\end{equation}
-
-The \acs{Adam} weight update rule is then given as
-
-\begin{equation}
-	\label{eq:heuristics:gd:adam}
-	\begin{split}
-		\boldsymbol{w}_{t+1} = \boldsymbol{w}_{t} - \frac{\eta}{\sqrt{\hat{\boldsymbol{v}}_{t}} + \epsilon}\hat{\boldsymbol{m}}_{t}
-	\end{split}
-\end{equation}
+Alternative variants have been proposed that lead to better control over the convergence characteristics caused by \acs{SGD}.
+This research focusses on a number of these variants that include \Acs{Momentum} \cite{ref:qian:1999}, \Acf{NAG} \cite{ref:sutskever:2013}, \Acf{Adagrad} \cite{ref:duchi:2011}, \acs{Adadelta} \cite{ref:zeiler:2012}, \Acf{RMSProp} \cite{ref:hinton:2012} and \Acf{Adam} \cite{ref:kingma:2014}.
 
@@
 
-Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus~\cite{ref:bengio:2000, ref:feurer:2019}.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} mention that since the 1980's, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
+Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus \cite{ref:bengio:2000, ref:feurer:2019}.
+\citeauthor{ref:blum:2003} \cite{ref:blum:2003} mention that since the 1980's, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
 These methods are referred to as \index{meta-heuristic}\textit{meta-heuristics}.
 
-This section aims to introduce the concept of \acp{MH}, with focus on population-based meta-heuristics.
-Three well known \acp{MH}, that have been shown to train \acs{FFNN}, are presented.
-These \acp{MH} include \acf{PSO}, \acf{DE} and \acfp{GA}.~\citeauthor{ref:carvalho:2006}~\cite{ref:carvalho:2006} compared various \acs{PSO} variants for training \acp{FFNN}.~\citeauthor{ref:espinal:2011}~\cite{ref:espinal:2011} compared \acs{DE} and \acs{PSO} when applied to \acs{FFNN} training and~\citeauthor{ref:gupta:1999}~\cite{ref:gupta:1999} compared \acs{BP} to a \acs{GA} for training \acp{FFNN}.
-
-The term \acf{MH} was first introduced by~\citeauthor{ref:glover:1986}~\cite{ref:glover:1986} in 1986 and is derived from the composition of two Greek words.
-\index{heuristic}Heuristic derives from the verb \textit{heuriskein} which means ``to find''.
-The prefix, \textit{meta}, means ``beyond, in an upper level''.
-\Acp{MH} were often called \textit{modern heuristics}~\cite{ref:reeves:1993}.~\citeauthor{ref:blum:2003}~\cite{ref:blum:2003} mention that there is a debate as to what the formal definition of \acp{MH} is and suggests the definition of \acp{MH} to be ``high level strategies for exploring search spaces by using different methods''.
-
 The biggest difference between \acp{MH} and gradient-bases heuristics is that
-\acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space~\cite{ref:blum:2003}.
-
-\subsubsection{Particle Swarm Optimisation}\label{sec:heuristics:mh:pso}
-
-\Acf{PSO} is a stochastic population-based search algorithm based on the social behaviour of birds in a flock~\cite{ref:kennedy:1995}.
-By definition, the \acs{PSO} heuristic is nature-inspired.
-\Acp{PSO} were first presented  by~\citeauthor{ref:kennedy:1995}\cite{ref:kennedy:1995}.
-Kennedy and Eberhart first applied \acp{PSO} to train of \acp{FFNN}~\cite{ref:eberhart:1995, ref:kennedy:1997}.
-The application of \acp{PSO} in the context of training \acs{FFNN} have been widely studied~\cite{ref:rakitianskaia:2012, ref:vanwyk:2014}.
-This section aims to provide the details of \acs{PSO} implementation.
-
-This dissertation uses the term \textit{entity} for candidate solutions and a \textit{population} for a collection of entities, in the general context of population-based \acp{MH}.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that in \acp{PSO} individual candidate solutions are referred to as \textit{particles} and the population is referred to as a \textit{swarm}.
-These particles are ``flown'' through a hyper-dimensional search space.
-Changes in particle position is due to social-psychological tendencies of individuals to emulate the success of other individuals.
-The changes in the particle position are then influenced by the experience or knowledge of the particle's neighbours.
-The social behaviour of particles is modelled such that they stochastically return to previously successful regions in the search space.
-
-\citeauthor{ref:vanwyk:2014}~\cite{ref:vanwyk:2014} mentions that the swarm is usually arranged in a predefined structure, called a \textit{neighbourhood topology} that governs the communication between particles.
-Two specific configurations of neighbourhood topologies that exists are referred to as \textit{local best (lbest)} \acs{PSO} and \textit{global best (gbest)} \acs{PSO}.
-There are two main differences between the two approaches in terms of their convergence characteristics~\cite{ref:eberhart:1996}.
-These include:
-
-\begin{itemize}
-	\item Due to the larger particle interconnectivity of \textit{gbest} \acs{PSO}, the heuristic converges faster than with \textit{lbest} \acs{PSO}.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that faster convergence comes at a cost of less diversity.
-
-	\item As a consequence of larger diversity, the \textit{lbest} \acs{PSO} is less susceptible to getting trapped in local minima.
-\end{itemize}
-
-\citeauthor{ref:shi:1998}~\cite{ref:shi:1998} proposed a modification of the original \acs{PSO} as was presented by~\citeauthor{ref:kennedy:1995}~\cite{ref:kennedy:1995}.
-Their implementation focuses on the \textit{gbest} \acs{PSO} with \textit{inertia} weights.
-This dissertation focuses on the \citeauthor{ref:shi:1998}~\cite{ref:shi:1998} implementation of \textit{global best} \acs{PSO} and particles in this specific implementation has a number of properties associated with them~\cite{ref:vanwyk:2014}.
-These include:
-
-\begin{itemize}
-	\item \textbf{Position}: Refers to the candidate solution that is represented by the particle and defines the particle position within the optimisation problem's hyper-dimensional solution space.
-Let the current position vector, for particle $i$, at time step $t$ be denoted by $\boldsymbol{x}_{i}(t)$.
-Let $I$ denoted the population size and $J$ denote the search space dimensionality.
-
-	\item \textbf{Velocity}: Represents a step size for the particle in the search space. The velocity at vector, for particle $i$, at time step $t$ is denoted $\boldsymbol{v}_{i}(t)$.
-
-	\item \textbf{Solution Quality}: Refers to the evaluation of the particle's position with respect to the objective function.
-Let $f(\boldsymbol{x}_{i}(t))$ denote the quality of the solution represented by the particle's position.
-
-	\item \textbf{Personal Best Position}: Refers to a cognitive memory construct, where each particle keeps track of their personal best position found during optimisation thus far.
-The personal best position is denoted $\boldsymbol{y}_{i}(t)$.
-
-	\item \textbf{Global Best Position}: Refers to a social memory construct, where each particle has a reference to the best solution found in the particle's neighbourhood thus far.
-In the case of \text{gbest} \acs{PSO}, the global best position is the best position of the entire swarm.
-The global best position is denoted $\boldsymbol{\hat{y}}_{i}(t)$.
-\end{itemize}
-
-During initialisation, particles are randomly placed within the search space by sampling from a uniform distribution such that $\boldsymbol{x}_{i} \sim U(\boldsymbol{x}_{min}, \boldsymbol{x}_{max})$ and the velocity is set to 0.
-At time step 0, the particle's initial position is set to be the particle's personal best solution such that $\boldsymbol{y}_{i}(0) = \boldsymbol{x}_{i}(0)$.
-The particle's update step is then broken into two parts, including a velocity update step presented in Equation~\eqref{eq:heuristics:pso:velocity} followed by a position update step as presented in Equation~\eqref{eq:heuristics:pso:position}.
-
-\begin{equation}
-	\label{eq:heuristics:pso:velocity}
-	\begin{split}
-		v_{ij}(t+1) = wv_{ij}(t) + c_{1}r_{1_{j}}(t)[y_{ij}(t) - x_{ij}(t)] + c_{2}r_{2_{j}}(t)[\hat{y}_{ij}(t) - x_{ij}(t)]
-	\end{split}
-\end{equation}
-
-\begin{equation}
-	\label{eq:heuristics:pso:position}
-	\begin{split}
-		x_{ij}(t+1) = x_{ij}(t) + v_{ij}(t+1)
-	\end{split}
-\end{equation}
-
-In Equations~\eqref{eq:heuristics:pso:velocity} and~\eqref{eq:heuristics:pso:position} above, $i$ refers to the $i$-th particle in the swarm and $j$ refers to the $j$-th dimension of  the particle's position.
-The velocity update step consists of:
-
-\begin{itemize}
-	\item \textbf{Previous Velocity}: Denoted by the term $v_{ij}(t)$.
-This term represents the particle's momentum at index j and is used to formulate an update step for the particle in the search space.~\citeauthor{ref:vanwyk:2014}~\cite{ref:vanwyk:2014} mentions that it forces the particle to maintain a consistent direction, preventing drastic changes in terms of update steps.
-This term is then scaled by the \textit{inertia} weight control parameter, denoted $w$.
-Inertia weight was introduced by~\citeauthor{ref:shi:1998}~\cite{ref:shi:1998} as a mechanism to control the exploration and exploitation abilities of the swarm.
-
-	\item \textbf{Cognitive Component}: Denoted by the term $c_{1}r_{1_{j}}(t)[y_{ij} - x_{ij}(t)]$.
-This component represents the particle's personal experience at index j.
-It introduces an attractor to the particle's personal best position so far.
-The cognitive component is stochastically scaled with random numbers $\boldsymbol{r}_{1} \sim U(0,1)^J$ and the cognitive acceleration coefficient $c_{1}$ is used to control the influence of the cognitive attractor.
-
-	\item \textbf{Social Component}: Denoted by the term $c_{2}r_{2_{j}}(t)[\hat{y}_{ij} - x_{ij}(t)]$.
-This component represents the particle's social experience at index j.
-It introduces an attractor to the swarm's best position so far.
-The social component is also stochastically scaled with random numbers $\boldsymbol{r}_{2} \sim U(0,1)^J$, while also introducing the social acceleration coefficient $c_{2}$ that is used to control the influence of the social attractor.
-\end{itemize}
-
-\citeauthor{ref:vanwyk:2014}~\cite{ref:vanwyk:2014} mentions that when \acp{PSO} where first developed, it was possible for particle velocities to become inappropriately large during optimisation, leading to situations where particles fly out of the feasible search space.
-This is known as \textit{swarm explosion} and occurs when there are frequent changes in the global best position.
-In order to address this issues, the concept of \textit{velocity clamping} was introduced~\cite{ref:eberhart:1996}.
-The idea behind velocity clamping is to restrict particle velocities to some $\boldsymbol{V_{max}}$ threshold, modelling a form of terminal velocity.
-Velocity clamping is applied after the velocity update step and is given in Equation~\eqref{eq:heuristics:pso:velocity_clamping} below.
-
-\begin{equation}
-	\label{eq:heuristics:pso:velocity_clamping}
-	\begin{split}
-		v_{ij}(t+1)=
-		\begin{cases}
-			v'_{ij}(t+1) & \text{if } -V_{max,j} < v'_{ij}(t+1) < V_{max,j} \\
-			-V_{max,j}   & \text{if } v'_{ij}(t+1) \leq -V_{max,j}          \\
-			V_{max,j}    & \text{if } v'_{ij}(t+1) \geq V_{max,j}
-		\end{cases}
-	\end{split}
-\end{equation}
-
-$\boldsymbol{V}_{max}$ is another hyper-parameter that must be defined a priori.
-Appropriate values for $\boldsymbol{V}_{max}$ may prevent swarm explosion, but also has an effect on the exploration and exploitation of the heuristic.
-If $\boldsymbol{V}_{max}$ is small, particle update steps are small, resulting in exploitation~\cite{ref:eberhart:1996}.
-If $\boldsymbol{V}_{max}$ is big, it allows for larger update steps, promoting more exploration.
-
-It should be noted that the choice of control parameters play a vital role in the behaviour and characteristics of the \acs{PSO}.
-Van den Berg and Engelbrecht~\cite{ref:vandenberg:2007, ref:vandenberg:2006} have done extensive work on the effects of different values for control parameters.
-For the purposes of this dissertation, the $c_{1}$ and $c_{2}$ control parameter are set to $1.496180$ and the inertia weight $w$ is set to $0.0729844$ as these correspond to values used in~\cite{ref:eberhart:2000} and have been shown to be appropriate for a number of problems.
-
-An example of the pseudo-code implementation of the \textit{gbest} \acs{PSO} is taken from~\cite{ref:engelbrecht:2007} and is given in Algorithm~\ref{algo:heuristics:pso:gbest}.
-
-\begin{algorithm}[htb]
-	\caption{The pseudo-code algorithm for the gbest \acs{PSO} heuristic.}
-	\label{algo:heuristics:pso:gbest}
-	\begin{algorithmic}
-		\State Create swarm of $N$ entities, each with $J$ dimensions;
-		\While{stopping condition are not met}
-		\For{each particle $i = 1, \dots, N$}
-		\State // Set the personal best position;
-		\If{$f(\boldsymbol{x}_{i}) < f(\boldsymbol{y}_{i})$ }
-		\State $\boldsymbol{y}_{i} = \boldsymbol{x}_{i}$;
-		\EndIf
-
-		\State // Set the global best position;
-		\If{$f(\boldsymbol{x}_{i}) < f(\boldsymbol{\hat{y}})$ }
-		\State $\boldsymbol{\hat{y}} = \boldsymbol{x}_{i}$;
-		\EndIf
-		\EndFor
-
-		\For{each particle $i = 1, \dots, N$}
-		\For{each dimension $j = 1, \dots, J$}
-		\State // Perform velocity update step;
-		\State $v_{ij} = wv_{ij} + c_{1}r_{1_{j}}[y_{ij} - x_{ij}] + c_{2}r_{2_{j}}[\hat{y}_{ij} - x_{ij}]$
-		\State // Perform position update step;
-		\State $x_{ij} = x_{ij} + v_{ij}$
-		\EndFor
-		\EndFor
-		\EndWhile
-	\end{algorithmic}
-\end{algorithm}
-
-\subsubsection{Differential Evolution}\label{sec:heuristics:mh:de}
-
-This section aims to introduce the next population-based \acs{MH}, called \acf{DE}.
-Similar to \acs{PSO}, \acs{DE} is a stochastic population-based search strategy developed by Storm and Price~\cite{ref:price:2006} in 1995.
-\Ac{DE} shares a lot of similarities with other evolutionary \acs{MH} paradigms such as \acp{PSO} and \acp{GA}.
-However, \acs{DE} differs significantly in how distance and direction information from the current population is used to guide the search process~\cite{ref:engelbrecht:2007}.
-Originally, \acs{DE} was focused on multi-dimensional real-valued optimisation problems, but unlike gradient-based heuristics, it does not require any gradient information.
-\acs{DE} does not require the underlying optimisation problem to be differentiable and can thus be applied to problems that are discrete, noisy and dynamic~\cite{ref:rocca:2011}.
-
-Lots of research has been done on using \acs{DE} to train \acp{FFNN}.
-Some notable work include~\cite{ref:ilonen:2003, ref:slowik:2008, ref:mingguang:2009}.
-In these works, the authors often highlight the low computational complexity and simplicity of implementation for \acs{DE}.
-
-Similar to other \acp{EA}, variation from one generation to the next is achieved through the application of \index{crossover}crossover and \index{mutation}mutation operators.
-Engelbrecht~\cite{ref:engelbrecht:2007} mentions that for other \acp{EA}, if both \index{crossover}crossover and \index{mutation}mutation operators are used, \index{crossover}crossover is applied first, after which the generated offspring is mutated.
-Furthermore, other \acp{EA} sample \index{mutation}mutation step sizes from some probability distribution.
-\acs{DE} differs from the aforementioned \acp{EA} in two ways.
-Firstly, \index{mutation}mutation is applied first to generate a \textit{trial vector}, which is then used within the \index{crossover}crossover operator to produce one offspring.
-Secondly, \index{mutation}mutation step sizes are not sampled from prior known probability distributions.
-
-In \acs{DE}, \index{mutation}mutation step sizes are influenced by the differences in positions of different entities in the current population.
-The positions of entities in the population provide valuable information about the fitness landscape, a concept \acs{DE} aims to exploit in order to find optimal solutions.
-There are three main components to the \acs{DE} heuristic.
-These include \index{mutation}mutation, \index{crossover}crossover and selection operators~\cite{ref:price:2006}.
-Each of these are presented in detail in the following sections.
-
-\subsubsection{Mutation}\label{sec:heuristics:mh:de:mutation}
-
-The purpose of the \index{mutation}mutation operator is to produce a trial vector for each entity in the current population by mutating a \textit{target} vector with a \textit{weighted differential}~\cite{ref:engelbrecht:2007}.
-The trial vector is used in the \index{crossover}crossover operator to produce offspring.
-The \index{mutation}mutation process then follows as such.
-For each parent $\boldsymbol{x}_{i}(t)$ generate a trial vector $\boldsymbol{u}_{i}(t)$ as follows:
-
-\begin{itemize}
-	\item Select a target vector, $\boldsymbol{x}_{i_{1}}(t)$ from the population that is not the same as the parent i.e.
-$i \neq i_{1}$.
-Various different selection strategies can be used to select the target vector.
-
-	\item Randomly select two other individuals $\boldsymbol{x}_{i_{2}}(t)$ and $\boldsymbol{x}_{i_{3}}(t)$.
-Importantly, all of these entities must be unique such that $i \neq i_{1} \neq i_{2} \neq i_{3}$ and $i_{2}, i_{3} \sim U(1, N)$ where $N$ is the size of the swarm/population.
-
-	\item Selected individual entities are then used to calculate the trial vector by perturbing the target vector as presented in Equation~\eqref{eq:heuristics:de:mutation} below.
-\end{itemize}
-
-\begin{equation}
-	\label{eq:heuristics:de:mutation}
-	\begin{split}
-		\boldsymbol{u}_{i}(t) = \boldsymbol{x}_{i_{1}}(t) + \beta(\boldsymbol{x}_{i_{2}}(t) - \boldsymbol{x}_{i_{3}}(t))
-	\end{split}
-\end{equation}
-
-In Equation~\eqref{eq:heuristics:de:mutation} $\beta \in (0, \infty)$ is the scale factor and controls the amplification of the differential variation~\cite{ref:engelbrecht:2007}.
-
-\subsubsection{Crossover}\label{sec:heuristics:mh:de:crossover}
-
-In the context of \acp{EA}, reproduction and recombination is done through the \index{crossover}crossover operation.
-The same applies to \acs{DE}.
-The \acs{DE} \index{crossover}crossover operator implements a discrete recombination of the trial vector, $\boldsymbol{u}_{i}(t)$, as was generated in Equation~\eqref{eq:heuristics:de:mutation} above, and the parent vector $\boldsymbol{x}_{i}(t)$ to produce new offspring $\boldsymbol{x}'_{i}(t)$.
-The \index{crossover}crossover operator is given in Equation~\eqref{eq:heuristics:de:crossover} below.
-
-\begin{equation}
-	\label{eq:heuristics:de:crossover}
-	\begin{split}
-		x'_{ij}(t)=
-		\begin{cases}
-			u_{ij}(t) & \text{if } j \in \mathcal{J} \\
-			x_{ij}(t) & \text{otherwise }
-		\end{cases}
-	\end{split}
-\end{equation}
-
-In Equation~\eqref{eq:heuristics:de:crossover}, $x_{ij}(t)$ refers to the $j$-th element of the vector $\boldsymbol{x}_{i}(t)$ and $\mathcal{J}$ refers to a set of \index{crossover}crossover points or indices at which perturbation is done.
-Different techniques for determining the set $\mathcal{J}$, has been proposed~\cite{ref:storn:1996, ref:storn:1997}.
-These include:
-
-\begin{itemize}
-	\item \textbf{Binomial \index{crossover}crossover}: A \index{crossover}crossover mask is generated by randomly selecting indices from the set of possible \index{crossover}crossover points $\{1,2,\dots,J\}$ where $J$ is the problem dimension.
-Binomial \index{crossover}crossover is presented in Algorithm~\ref{algo:heuristics:de:bin}.
-In Algorithm~\ref{algo:heuristics:de:bin}, $p_{r}$ is the \index{crossover}crossover probability.
-The higher the value of $p_{r}$, the more points will be included in the set $\mathcal{J}$.
-A \textit{Bernoulli} distribution can be used to generate the binomial \index{crossover}crossover mask.
-Note that due to the probabilistic nature of this process, it is possible that no \index{crossover}crossover points are selected.
-To counteract this situation, a randomly selected \index{crossover}crossover point $j^{*}$ is included in the set $\mathcal{J}$ such that $\mathcal{J} \neq \emptyset$ where $\emptyset$ is the empty set.
-
-	\item \textbf{Exponential \index{crossover}crossover}:~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} states that with exponential \index{crossover}crossover, a sequence of adjacent \index{crossover}crossover points are selected from some randomly selected \index{crossover}crossover index.
-This means that the set of possible \index{crossover}crossover points $\mathcal{J}$ is a circular array in indices.
-Exponential \index{crossover}crossover does not require the selection of an additional \index{crossover}crossover point $j^{*}$ as this technique includes at the very least one index, which is the starting index that is randomly selected.
-From the starting index, the next index is selected until $U(0,1) \geq p_{r}$ or $|\mathcal{J}| = N$, and $p_{r}$ is the same \index{crossover}crossover probability as mentioned above for binomial \index{crossover}crossover.
-The implementation of exponential \index{crossover}crossover is given in Algorithm~\ref{algo:heuristics:de:exp}.
-\end{itemize}
-
-\begin{algorithm}[htb]
-	\caption{The pseudo-code algorithm for the binomial \index{crossover}crossover technique for \acs{DE}.}
-	\label{algo:heuristics:de:bin}
-	\begin{algorithmic}
-		\State $j^{*} \sim U(1,N)$;
-		\State $\mathcal{J} \gets \mathcal{J} \cup \{j^{*}\}$;
-		\For{each $j \in \{1, \dots, N\}$}
-		\If{$U(0,1) < p_{r}$ and $j \neq j^{*}$ }
-		\State $\mathcal{J} \gets \mathcal{J} \cup \{j\}$;
-		\EndIf
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[htb]
-	\caption{The pseudo-code algorithm for the exponential \index{crossover}crossover technique for \acs{DE}.}
-	\label{algo:heuristics:de:exp}
-	\begin{algorithmic}
-		\State $\mathcal{J} \gets \{\}$;
-		\State $j \sim U(0,N - 1)$;
-		\Repeat
-		\State $\mathcal{J} \gets \mathcal{J} \cup \{j + 1 \}$;
-		\State $j = (j+1) \mod N$
-		\Until{ $U(0,1) \geq p_{r}$ or $|\mathcal{J}| = N$;}
-	\end{algorithmic}
-\end{algorithm}
-
-\subsubsection{Selection}\label{sec:heuristics:mh:de:selection}
-
-Selection refers to the technique that is used to determine which entities are included in the \index{mutation}mutation operator to produce a trial vector~\cite{ref:engelbrecht:2007}.
-Various selection operators have been suggested~\cite{ref:storn:1996, ref:storn:1997}.
-With reference to the \index{mutation}mutation operator, most \acs{DE} implementations make use of random selection or the best entity is used as the target vector $\boldsymbol{x}_{i_{1}}(t)$.
-To construct the population for the next generation, deterministic selection is used.
-As such, a parent is replaced if the offspring produces a better solution than the parent such that $f(\boldsymbol{x}'_{i}(t)) \leq f(\boldsymbol{x}_{i}(t))$.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} states that deterministic selection for the next generation ensures the average fitness of the population does not deteriorate.
-
-\subsubsection{General Differential Evolution Algorithm}
-
-Algorithm~\ref{algo:heuristics:de:general_de} is taken from~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} and presents the general \acs{DE} algorithm.
-The population is initialised by randomly placing entities in the search space such that the positions of the entities are confined to some search boundary.
-As such, $x_{ij}(t) \sim U(x_{min,j}, x_{max,j})$, where $x_{min,j}$ and $x_{max,j}$ define the search boundaries.
-
-\begin{algorithm}[htbp]
-	\caption{The pseudo-code for the general \acs{DE} heuristic.}
-	\label{algo:heuristics:de:general_de}
-	\begin{algorithmic}
-		\State Set the generation counter, $t = 0$;
-		\State Initialise the control parameters, $\beta$ and $p_{r}$
-		\While{stopping condition not met}
-		\For{each entity $\boldsymbol{x}_{i}(t) \in \mathcal{C}(t)$ }
-		\State Evaluate the fitness, $f(\boldsymbol{x}_{i}(t))$;
-		\State Create the trial vector, $\boldsymbol{u}_{i}(t)$ by applying the mutation operator;
-		\State Create an offspring, $\boldsymbol{x}'_{i}(t)$ by applying the crossover operator;
-		\If{$f(\boldsymbol{x}'_{i}(t))$ is better than $f(\boldsymbol{x}_{i}(t))$ }
-		\State Add $\boldsymbol{x}'_{i}(t)$ to $\mathcal{C}(t+1)$;
-		\Else
-		\State Add $\boldsymbol{x}_{i}(t)$ to $\mathcal{C}(t+1)$;
-		\EndIf
-		\EndFor
-		\EndWhile
-		\State Return the individual with the best fitness as the solution;
-	\end{algorithmic}
-\end{algorithm}
-
-As with other heuristics, \acs{DE} also contains a set of control parameters. These include:
-
-\begin{itemize}
-	\item \textbf{Population size:} The population size has a direct influence on the exploration ability of the \acs{DE} heuristic~\cite{ref:engelbrecht:2007}.
-The larger the population size, the more differential vectors are available and thus, more directions can be explored.
-
-	\item \textbf{Scaling Factor:} The scaling factor, $\beta \in (0, \infty)$ controls the amplification of the differential variations $(\boldsymbol{x}_{i_{2}}(t) - \boldsymbol{x}_{i_{3}}(t))$.
-A lower scaling factor leads to smaller step sizes and as a result, convergence will take longer.
-Larger values facilitate exploration, but could cause the algorithm to overshoot.
-Similar to other heuristics, adaptive mechanisms can be used to dynamically alter the scaling factor throughout the optimisation process.
-
-	\item \textbf{Recombination Probability:} The probability of recombination, $p_{r}$ has a direct influence on the diversity of the \acs{DE} heuristic~\cite{ref:engelbrecht:2007}.
-This parameter controls the number of elements that are included during \index{crossover}crossover.
-The higher the probability of recombination, the more variation is introduced in the new population.
-Similar to the scaling factor, dynamic techniques can be used to adjust this the recombination probability during optimisation.
-\end{itemize}
-
-\subsubsection{DE/$x$/$y$/$z$ Notation}
-
-Many variants of \acs{DE} have been created and researched~\cite{ref:mezura:2006}.
-A general notation for \acs{DE} heuristic variants have been developed by \citeauthor{ref:storn:1996}~\cite{ref:storn:1996, ref:storn:1997}.
-The notation follows the form \textit{DE/$x$/$y$/$z$} where $x$, $y$ and $z$ refer to the components that are used by the particular \acs{DE}.
-A breakdown of this notation is provided as follows:
-
-\begin{itemize}
-	\item \textbf{$x$:} The selection mechanism for the target vector.
-	\item \textbf{$y$:} The number of difference vectors to include.
-	\item \textbf{$z$:} The type of \index{crossover}crossover operator used.
-\end{itemize}
-
-For this dissertation, \textit{random} and \textit{best entity} selection, a single difference vector and binomial and exponential \index{crossover}crossover are considered.
-This results in the \acs{DE} notations as follows:
-
-\begin{itemize}
-	\item DE/rand/1/bin
-	\item DE/best/1/bin
-	\item DE/rand/1/exp
-	\item DE/best/1/exp
-\end{itemize}
-
-\subsubsection{Genetic Algorithms}\label{sec:heuristics:mh:ga}
-
-\Ac{EC} refers to a collection of nature-inspired optimisation algorithms that lend their foundation to biological evolution.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that \acs{EC} refers to computer-based problem solving systems that use computational models of evolutionary processes such as natural selection, survival of the fittest and reproduction.
-Charles Darwin's theory of \textit{natural selection}~\cite{ref:darwin:2012} became the foundation of biological evolution~\cite{ref:darwin:1987}.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} summarises the Darwinian theory of evolution as follows.
-In a world with limited resources and stable populations, each individual competes with others for survival.
-Those individuals with the ``best'' characteristics (traits) are more likely to survive and to reproduce and those characteristics will be passed on to their offspring.
-These desirable characteristics are inherited by the following generations and (over time) become dominant among the population.
-Evolution via natural selection of a randomly chosen population of entities can be seen as a search through the space of possible chromosome values.
-This makes the \acs{EC} search process a stochastic search for an optimal solution to the given problem.
-
-So far, two population-based \acp{MH} have been introduces.
-These include \acs{PSO} and \acs{DE}.
-The \acs{DE} heuristic that was presented in Section~\ref{sec:heuristics:mh:de} is one type of \acs{EC} algorithm.
-This section introduces another population-based, nature-inspired optimisation \acs{EC} algorithm, referred to as \acfp{GA}.
-The details of the implementation of \acp{GA} is given in this section.
-\acp{GA} have been widely used to train \acp{FFNN}~\cite{ref:montana:1989, ref:siddique:2001, ref:miller:1989}.
-
-\Acp{GA} where first proposed by \citeauthor{ref:fraser:1957}~\cite{ref:fraser:1957} and later by \citeauthor{ref:bremermann:1962}~\cite{ref:bremermann:1962} and \citeauthor{ref:reed:1967}~\cite{ref:reed:1967}.
-However, Holland~\cite{ref:holland:1992} is widely regarded as the father of \acp{GA}.
-Similar to \acp{DE}, \acp{GA} are also nature-inspired population-based \acp{MH} and model genetic evolution of entities in a hypothetical population.
-As with other \acp{EA}, \acp{GA} implement a number of operators that drive the optimisation process.
-Primarily, \acp{GA} implement selection, modelling survival of the fittest and \index{crossover}crossover, modelling reproduction.
-The remainder of this section presents the aforementioned operators in more detail.
-
-For sake of clarity, a generic \acs{EC} algorithm is presented first, as a frame of reference.
-The generic \acs{EC} algorithm is referred to as the canonical \acs{GA} (CGA) and was proposed by Holland~\cite{ref:holland:1992}.
-The generic \acs{EC} algorithm is taken from~\cite{ref:engelbrecht:2007} and is presented in Algorithm~\ref{algo:heuristics:ga:generic_ec} below.
-
-\begin{algorithm}[htb]
-	\caption{The pseudo-code for the generic \acs{EC} heuristic.}
-	\label{algo:heuristics:ga:generic_ec}
-	\begin{algorithmic}
-		\State Let $t = 0$ be the generation counter;
-		\State Create an initialise a $J$-dimensional population $\mathcal{C}(0)$, to consist of $N$ individuals;
-		\While{stopping condition not met}
-		\State Evaluate the fitness, $f(\boldsymbol{x}_{i}(t))$ of each individual $\boldsymbol{x}_{i}(t)$;
-		\State Perform reproduction to create offspring;
-		\State Select the new population, $\mathcal{C}(t+1)$;
-		\State Advance to the new generation, i.e. $t = t + 1$
-		\EndWhile
-		\State
-	\end{algorithmic}
-\end{algorithm}
-
-From Algorithm~\ref{algo:heuristics:ga:generic_ec} above, it can be seen that a number of components influence the search process. These include:
-
-\begin{itemize}
-	\item \textbf{Encoding}: Refers to the representation of a candidate solution to some optimisation problem as the \index{chromosomes} of some entity.
-Every element in the chromosomes is referred to as a \textit{gene} or \textit{allele}.
-
-	\item \textbf{Fitness Function}: Refers to the objective function that measures the fitness of an entity.
-Fitness refers to the survivability of an entity and measures the strength of a candidate solution represented by the entity's chromosomes.
-
-	\item \textbf{Initialisation}: Refers to the initialisation strategy used to generate the initial population.
-Often entities' chromosomes are uniformly sampled in the feasible search space for the underlying optimisation problem.
-
-	\item \textbf{Selection}: Refers to the techniques that are used to select entities for reproduction and generation of the new population as well as the selection of genes for \index{mutation}mutation.
-Selection is implemented through selection operators.
-
-	\item \textbf{Reproduction}: Refers to the generation of the next population and is implemented through \index{crossover}crossover operators.
-\end{itemize}
-
-The initial implementations of \acs{EC} heuristics such as \acp{GA} did not contain a \index{mutation}mutation operator as it was only introduced later~\cite{ref:engelbrecht:2007}.
-The following sections provide the \index{crossover}crossover, \index{mutation}mutation and selection operators for \acp{GA}.
-
-\subsubsection{Crossover}\label{sec:heuristics:mh:ga:crossover}
-
-As with \acs{DE}, \index{crossover}crossover operators model the reproduction of entities in the population.
-Broadly speaking, the \index{crossover}crossover operators can be divided into three main categories~\cite{ref:engelbrecht:2007} and are based on arity of the operator i.e.
-the number of parents used for reproduction.
-
-\begin{itemize}
-	\item \textbf{Asexual:} Offspring are generated from one parent.
-
-	\item \textbf{Sexual:} Offspring are generated from two parents and can produce one or two offspring.
-
-	\item \textbf{Multi-recombination:} Offspring are generated from more than two parents and can produce one or more offspring.
-\end{itemize}
-
-\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that \index{crossover}crossover operators can be further classified based on their encoding/representation scheme.
-These include binary-specific operators used for binary representations and operators focused on floating-point representations.
-Since the focus is put on training \acp{FFNN}, from this point on, floating-point representations are assumed.
-
-During \index{crossover}crossover, parents are selected using a selection operator.
-As with \acp{DE}, recombination is applied probabilistically and thus, selection of a parent does not guarantee reproduction.
-Each parent has a probability $p_{c}$ of producing offspring.
-Usually a high \index{crossover}crossover probability is used~\cite{ref:engelbrecht:2007}.
-In addition to recombination, \acp{GA} implement a replacement policy where fit offspring can replace weaker parents in the population.
-
-Although floating-point representations of chromosomes are assumed, binary \index{crossover}crossover operators can also be used, since they produce a mask that defines how parents are recombined.
-Specifically, in the context of this dissertation, focus is put on \textit{uniform} \index{crossover}crossover.
-Uniform \index{crossover}crossover refers to a \index{crossover}crossover operator where an $J$-dimensional \index{crossover}crossover mask is generated randomly~\cite{ref:syswerda:1989}.
-Uniform \index{crossover}crossover is illustrated in Figure~\ref{fig:heuristics:mh:ga:uniform_crossover} below and the algorithm for uniform \index{crossover}crossover is given in Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover}.
-In Algorithm~\ref{algo:heuristics:mh:ga:uniform_crossover}, $p_{x}$ is the bit-swapping probability.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.8\textwidth]{images/uniform_crossover.pdf}
-	\caption{An illustration of the uniform \index{crossover}crossover operator as it applies to sexual recombination, resulting in two new offspring.}
-	\label{fig:heuristics:mh:ga:uniform_crossover}
-\end{figure}
-
-\begin{algorithm}[htb]
-	\caption{The pseudo-code for the uniform \index{crossover}crossover operator as used by \acp{GA}.}
-	\label{algo:heuristics:mh:ga:uniform_crossover}
-	\begin{algorithmic}
-		\State Initialise the mask, $m_{j}(t) = 0, \forall j = 1, \dots, J$;
-		\For{$j = 1$ to $J$}
-		\If{$U(0,1) \leq p_{x}$}
-		\State $m_{j}(t) = 1$;
-		\EndIf
-		\EndFor
-		\State
-	\end{algorithmic}
-\end{algorithm}
-
-\subsubsection{Mutation}\label{sec:heuristics:mh:ga:mutation}
-
-The \index{mutation}mutation operator is applied in order to introduce new genetic material into an existing entity~\cite{ref:engelbrecht:2007}.
-In doing so, diversity is added into the genetic characteristics of the population.
-Mutation is applied at a certain \index{mutation}mutation probability $p_{m}$, to each gene of the offspring $\boldsymbol{x}_{i}(t)$ to produce mutated offspring $\boldsymbol{x}'_{i}(t)$.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that the \index{mutation}mutation probability, also referred to as the \index{mutation}mutation rate, is usually small such that $p_{m} \in [0,1]$ to ensure that good solutions are not distorted too much.
-
-Similar to the \index{crossover}crossover operator, \index{mutation}mutation operators can be classified according to the representation scheme used. In the context of training
-\acp{FFNN}, binary \index{crossover}crossover operators such as the \textit{uniform} \index{mutation}mutation operator can be used to generate a \index{mutation}mutation mask that specifies which genes are mutated.
-For the purposes of this dissertation, the application of the \index{mutation}mutation operator on $x_{ij}(t)$ results in a small update step for that gene such that $x'_{ij}(t) = x_{ij}(t) + v_{ij}(t)$.
-In this case, $v_{ij}(t)$ is sampled using \index{Glorot uniform sampling}Glorot uniform sampling within the bounds $(-limit, limit)$, as was presented in Chapter~\ref{chap:anns}.
-An adaptation of the uniform \index{mutation}mutation operator is provided in Algorithm~\ref{algo:heuristics:mh:ga:uniform_mutation} below.
-
-\begin{algorithm}[htb]
-	\caption{The pseudo-code for the uniform \index{mutation}mutation operator as used by \acp{GA}.}
-	\label{algo:heuristics:mh:ga:uniform_mutation}
-	\begin{algorithmic}
-		\For{$i = 1$ to $N$}
-		\For{$j = 1$ to $J$}
-		\If{$U(0,1) \leq p_{m}$}
-		\State Sample update step $v_{ij}(t) \sim U(-limit, limit)$
-		\State $x'_{ij}(t) = x_{ij}(t) + v_{ij}(t)$;
-		\EndIf
-		\EndFor
-		\EndFor
-		\State
-	\end{algorithmic}
-\end{algorithm}
-
-An illustration of the adapted uniform \index{mutation}mutation operator is presented in Figure~\ref{fig:heuristics:mh:ga:uniform_mutation} below.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.8\textwidth]{images/uniform_mutation.pdf}
-	\caption{An illustration of the adapted uniform \index{mutation}mutation operator as it applies to mutated offspring.}
-	\label{fig:heuristics:mh:ga:uniform_mutation}
-\end{figure}
-
-\subsubsection{Selection}
-\label{sec:heuristics:mh:ga:selection}
-
-Selection is a widely used concept in all \acp{EA} and models survival of the fittest in the evolutionary context.
-The main idea behind the selection operator is to emphasise better solutions~\cite{ref:engelbrecht:2007}.
-Selection is applied in two of the main steps of \acp{EA}.
-These include:
-
-\begin{itemize}
-	\item \textbf{Selection of the new population:} A new population of candidate solutions are selected at the end of each generation to serve as the population for the next generation.
-The new population can be selected from both the parents and offspring.
-The selection operator is thus responsible for ensuring that good entities survive to the next generation.
-
-	\item \textbf{Reproduction:} Offspring is created through the \index{crossover}crossover and/or the \index{mutation}mutation operators.
-In terms of \index{crossover}crossover, good solutions should have a high probability of reproducing to ensure that offspring contain genetic material of the best entities.
-In terms of \index{mutation}mutation, selection mechanisms should focus on weaker entities.
-By mutating weak entities, the hope is to introduce better traits, increasing their chance to survive.
-\end{itemize}
-
-\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that selection operators are characterised by their \textit{selective pressure}.
-Selective pressure is defined as the speed at which the best entity's solution will occupy the entire population by repeated application of the selection operator alone~\cite{ref:back:1994}.
-A selection operator with a high selective pressure rapidly decreases the diversity in the population, possibly leading to premature convergence.
-A high selective pressure limits the exploration abilities of the population.
-Selection operators should maintain a balance between exploration and exploitation.
-
-Various selection mechanisms have been proposed. For the purposes of this dissertation, focus is put on the following selection mechanisms and concepts.
-
-\begin{itemize}
-	\item \textbf{Tournament Selection:} Tournament selection selects a group of $N_{t}$ entities randomly from the population such that $N_{t} < N$, where $N$ is the population size.
-The performance of the selected $N_{t}$ entities are then compared and the best entities from this group are selected and returned by the operator.
-It should be mentioned that for sexual \index{crossover}crossover of two parents, tournament selection is applied twice, first for the first parent and then again for the second parent.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that tournament selection prevents the best entities from dominating, provided that $N_{t}$ is not too large.
-This results in a lower selective pressure.
-If $N_{t}$ is too small, the chances that bad entities will be selected increase.
-
-	\item \textbf{Rank-based Selection:} Rank-based selection uses the rank-ordered fitness values to determine the probability of selection and not the absolute fitness value.~\citeauthor{ref:engelbrecht:2007}~\cite{ref:engelbrecht:2007} mentions that the advantage of this approach is that the best entities will not dominate the selection process.
-Non-deterministic linear sampling selects an entity $\boldsymbol{x}_{i}(t)$ such that $i \sim U(0, U(0, N - 1))$.
-Importantly, in the context of a minimisation problem, entities are first sorted in decreasing order of fitness value, assuming that the best heuristic is then contained at index 0, while the worst entity is contained at index $N - 1$.
-
-	\item \textbf{Elitism:} \index{elitism}Elitism refers to the process of ensuring that the best entities from the current population survive to the next generation.
-The best entities are simply passed on to the next generation without \index{mutation}mutation.
-The more entities that survive to the next generation, the lower the diversity of the new population.
-\end{itemize}
+\acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space \cite{ref:blum:2003}.
+Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \cite{ref:rakitianskaia:2012, ref:vanwyk:2014, ref:espinal:2011, ref:gupta:1999}.
+This research takes a particular interest in population-based \acp{MH} that have been used to successfully train \acp{FFNN}.
+These include \acp{PSO} \cite{ref:shi:1998}, \acf{DE} \cite{ref:price:2006} and \Acp{GA} \cite{ref:fraser:1957}.

### 2023-01-22 article/sections/08-results.tex
🚧 (article): Results, initial

--- 2022-12-05 dissertation/chapters/08-results.tex
@@
-\chapter{Results}
-\label{chap:results}
-
-\begin{quotation}
-      \noindent ``Without data, you are just another person with an opinion.''
-\end{quotation}
-\begin{flushright}
-      - W. Edwards Deming
-\end{flushright}
-
-The last step in the scientific process requires the presentation of the outcomes of the empirical process.
-Objective discussions based on statistical analysis of the findings are required.
-The design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}.
+\section{Results}
+\label{sec:results}
+
 The methodology presented a number of experimental groups to conduct.
-The experimental groups that were identified include a case study on the behaviour of the \acs{BHH} during training, an empirical comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics, and a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.
-
-This chapter provides the outcomes of the empirical processes and provides results on all the experiments that have been conducted.
+The experimental groups that were identified include a case study on the behaviour of the \acs{BHH} during training, and an empirical comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics.
+This section provides the outcomes of the empirical processes and provides results on all the experiments that have been conducted.
 Detailed discussions follow on the outcomes of each experiment.
 Discussions are accompanied by figures and plots to help provide visual aid for discussions.
-The output of the statistical analysis that yielded the results is provided in Appendix~\ref{app:statistical_analysis}.
+The output of the statistical analysis that yielded the results is provided in Appendix \ref{app:statistical_analysis}.
 The remainder of the chapter is structured as follows:
@@
 
-      \item \textbf{Section \ref{sec:results:heuristic_pool}} provides the results for the experimental group that analyses the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the outcomes of the \acs{BHH}.
-
-      \item \textbf{Section \ref{sec:results:population}} provides the results for the experimental group that analyses the effects of the \textit{population size} hyper-parameter on the outcomes of the \acs{BHH}.
-
-      \item \textbf{Section \ref{sec:results:credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.
-
-      \item \textbf{Section \ref{sec:results:reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.
-
-      \item \textbf{Section \ref{sec:results:replay}} provides the results for the experimental group that analyses the effects of the \textit{replay window size} hyper-parameter on the outcomes of the \acs{BHH}.
-
-      \item \textbf{Section \ref{sec:results:reanalysis}} provides the results for the experimental group that analyses the effects of the \textit{reanalysis interval} hyper-parameter on the outcomes of the \acs{BHH}.
-
-      \item \textbf{Section \ref{sec:results:burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.
-
-      \item \textbf{Section \ref{sec:results:normalise}} provides the results for the experimental group that analyses the effects of the \textit{normalisation} hyper-parameter on the outcomes of the \acs{BHH}.
-
-      \item \textbf{Section \ref{sec:results:discounted_rewards}} provides the results for the experimental group that analyses the effects of the \textit{discounted rewards} hyper-parameter on the outcomes of the \acs{BHH}.
-
-      \item \textbf{Section \ref{sec:results:summary}} provides a brief summary of the chapter.
 \end{itemize}
 
-\section{Overview}\label{sec:results:overview}
+\subsection{Overview}\label{sec:results:overview}
 
@@
 
-\section{Behavioural Case Study}\label{sec:results:case_study}
+\subsection{Behavioural Case Study}\label{sec:results:case_study}
 
@@
 Furthermore, the case study focuses on three variants of the \acs{BHH}.
-These include the baseline configuration, as was provided in Chapter~\ref{chap:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}).
+These include the baseline configuration, as was provided in Chapter \ref{chap:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}).
 Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}).
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Performance Metrics}\label{sec:results:case_study:performance_metrics}
+\subsubsection{Performance Metrics}\label{sec:results:case_study:performance_metrics}
 
 This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}.
-Figures~\ref{fig:results:case_study:metrics:train_loss} to \ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
+Figures \ref{fig:results:case_study:metrics:train_loss} to \ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
 
@@
 The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}, observed by the convergence of the training process, yielding good results.
-Figures~\ref{fig:results:case_study:metrics:train_accuracy} and~\ref{fig:results:case_study:metrics:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%.
+Figures \ref{fig:results:case_study:metrics:train_accuracy} and \ref{fig:results:case_study:metrics:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%.
 
@@
 
-The volatility and minor divergence of the test loss compared to the training loss, observed in Figure~\ref{fig:results:case_study:metrics:test_loss}, is due to overfitting and partly due to the noisiness that results from mini-batch training.
+The volatility and minor divergence of the test loss compared to the training loss, observed in Figure \ref{fig:results:case_study:metrics:test_loss}, is due to overfitting and partly due to the noisiness that results from mini-batch training.
 Early stopping can be applied to the training process to halt training before the model overfits on the training data.
@@
 
-From Figure~\ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed.
+From Figure \ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed.
 This could simply be a result of momentum that is maintained when switching between low-level \index{heuristic}heuristics in an attempt to find better solutions.
@@
 
-Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figure~\ref{fig:results:case_study:metrics} only provides the outcomes of performance metrics at the end of each epoch.
+Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figure \ref{fig:results:case_study:metrics} only provides the outcomes of performance metrics at the end of each epoch.
 Further investigation is required at a mini-batch step level and is provided in the following sections.
@@
 
-\subsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}
+\subsubsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}
 
@@
 The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{\index{heuristic}heuristic selection probabilities}.
-Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
+Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
 Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool.
@@
 
-The first logical observation to be made from Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
+The first logical observation to be made from Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
 Since the replay window size is sufficiently large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
@@
 
-Notice from Figure~\ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements.
+Notice from Figure \ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements.
 This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process.
@@
 
-\subsection{Probability Distribution of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
+\subsubsection{Probability Distribution of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
 
@@
 
-Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
+Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
 These illustrations are presented in log scale.
@@
 
-From the illustrations presented in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed.
+From the illustrations presented in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed.
 The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}.
@@
 Another observation to make occurs in the first 30 steps of the training process.
-In Figure~\ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same \index{heuristic}heuristic selection probabilities in these first 30 steps.
+In Figure \ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same \index{heuristic}heuristic selection probabilities in these first 30 steps.
 This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number.
@@
 
-\subsection{Prior Heuristic Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}
+\subsubsection{Prior Heuristic Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}
 
@@
 
-Figures~\ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
+Figures \ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
 Similar to before, these illustrations are also presented in log scale.
@@
 
-The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure~\ref{fig:results:case_study:thetas}.
+The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure \ref{fig:results:case_study:thetas}.
 This is because of the \textit{reselection} interval hyper-parameter.
@@
 Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10.
-These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of \index{heuristic}heuristic selection probabilities.
+These illustrations then simply yield rough approximations of the illustrations provided in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of \index{heuristic}heuristic selection probabilities.
 As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
@@
 
-\subsection{Posterior Heuristic Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}
+\subsubsection{Posterior Heuristic Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}
 
@@
 
-Figures~\ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
+Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
 Similar to before, these illustrations are also presented in log scale.
@@
 
-The main observation to make from Figures~\ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
-The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Chapter~\ref{chap:bhh}.
+The main observation to make from Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
+The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Chapter \ref{chap:bhh}.
 As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
@@
 Another observation to make is for the bhh\_replay\_250 configuration $(\textcolor{green}{green})$.
-Figures~\ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} show that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities later in the training stages.
+Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} show that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities later in the training stages.
 The aforementioned suggests that the \acs{BHH} is not able to find further performance biases and cannot exploit better solutions.
@@
 
-It can be concluded from Sections~\ref{sec:results:case_study:performance_metrics} to \ref{sec:results:case_study:posterior_selec_prob} that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset.
+It can be concluded from Sections \ref{sec:results:case_study:performance_metrics} to \ref{sec:results:case_study:posterior_selec_prob} that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset.
 Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases, and thus the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\section{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
+\subsection{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
 
@@
 
-Table~\ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented.
+Table \ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented.
 The test loss is measured at the last epoch for each dataset, over all independent runs.
@@
 
-Table~\ref{tab:results:standalone:metrics:loss} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
+Table \ref{tab:results:standalone:metrics:loss} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
 The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.
 
-Table~\ref{tab:results:standalone:metrics:rank} provides the empirical results from Table~\ref{tab:results:standalone:metrics:loss} in ranked format.
+Table \ref{tab:results:standalone:metrics:rank} provides the empirical results from Table \ref{tab:results:standalone:metrics:loss} in ranked format.
 The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, across all datasets, for all independent runs and all epochs.
@@
 
-From the normalised average ranks provided in Table~\ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen \index{heuristic}heuristic implementations respectively.
+From the normalised average ranks provided in Table \ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen \index{heuristic}heuristic implementations respectively.
 These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.
 
-Figure~\ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each \index{heuristic}heuristic, per dataset.
-The heuristics are ordered according to the normalised ranks presented in Table~\ref{tab:results:standalone:metrics:rank}.
+Figure \ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each \index{heuristic}heuristic, per dataset.
+The heuristics are ordered according to the normalised ranks presented in Table \ref{tab:results:standalone:metrics:rank}.
 
@@
 
-From Figure~\ref{fig:results:standalone:descriptive:descriptive} a few observations can be made.
+From Figure \ref{fig:results:standalone:descriptive:descriptive} a few observations can be made.
 Firstly, both \acs{Adam} and \acs{RMSProp} achieved radically different average ranks for the student performance dataset, compared to the other datasets.
-This can also be seen in Table~\ref{tab:results:standalone:metrics:rank}.
+This can also be seen in Table \ref{tab:results:standalone:metrics:rank}.
 Further investigation into the reasons for this is required as both these heuristics perform well on all other datasets, and the other heuristics perform well for the student performance dataset.
@@
 
-Figure~\ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic}heuristic as it relates to all datasets, across all independent runs and epochs.
+Figure \ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic}heuristic as it relates to all datasets, across all independent runs and epochs.
 
@@
 Another observation that can be made is that the gradient-based \index{heuristic}heuristics generally performed much better than the \index{meta-heuristic}meta-heuristics on all datasets.
-State of the art methods for training \acp{FFNN}, such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions~\cite{ref:kingma:2014}.
+State of the art methods for training \acp{FFNN}, such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions \cite{ref:kingma:2014}.
 Exploration of the \index{heuristic}heuristic space leads the \acs{BHH} to consider other \index{heuristic}heuristics during the training process, which could possibly result in worse performances at times.
@@
 
-Figures~\ref{fig:results:standalone:figures:iris} to \ref{fig:results:standalone:figures:bank} provide example illustrations of the train and test loss and accuracy plots for each heuristic as it relates to a selection of classification datasets.
+Figures \ref{fig:results:standalone:figures:iris} to \ref{fig:results:standalone:figures:bank} provide example illustrations of the train and test loss and accuracy plots for each heuristic as it relates to a selection of classification datasets.
 The train and test loss and accuracy plots provided are illustrated in log scale.
@@
 
-Figures~\ref{fig:results:standalone:figures:fish_toxicity} to \ref{fig:results:standalone:figures:parkinsons} provide example illustrations of the train and test loss plots for each heuristic as it relates to a selection of regression datasets.
+Figures \ref{fig:results:standalone:figures:fish_toxicity} to \ref{fig:results:standalone:figures:parkinsons} provide example illustrations of the train and test loss plots for each heuristic as it relates to a selection of regression datasets.
 The train and test loss plots provided are illustrated in log scale.
@@
 
-\section{Heuristic Pool}\label{sec:results:heuristic_pool}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \index{heuristic pool}\textit{heuristic pool} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-This experimental group utilises the same three variants of the \acs{BHH} as was utilised in Section \ref{sec:results:standalone}, but provides an opportunity to look at the \acs{BHH} \index{heuristic pool}heuristic pool hyper-parameter in more depth.
-These variants are denoted as follows: The \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics is denoted as \textit{all}, the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics is denoted as \textit{gd}, and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics is denoted as \textit{mh}.
-
-Table~\ref{tab:results:heuristic_pool:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the heuristic pool variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average test loss and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-      \label{tab:results:heuristic_pool:metrics:loss}%
-      \par\bigskip
-      \resizebox{0.8\textwidth}{!}{
-            \begin{tabular}{r|lll}
-                                               & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Test Loss}}                                                                                                                     \\
-                  \midrule
-                  \textbf{dataset}             & \multicolumn{1}{c}{\textbf{all}}                                & \multicolumn{1}{c}{\textbf{gd}}                         & \multicolumn{1}{c}{\textbf{mh}}                         \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)            & \cellcolor[rgb]{ .388,  .745,  .482}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .973,  .412,  .42}2.2942 ($\pm$0.055)  \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)          & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2637 ($\pm$0.007) \\
-                  \textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)            & \cellcolor[rgb]{ .388,  .745,  .482}0.2164 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.2562 ($\pm$0.011)  \\
-                  \textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}0.0651 ($\pm$0.02)             & \cellcolor[rgb]{ .388,  .745,  .482}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .973,  .412,  .42}0.1179 ($\pm$0.006)  \\
-                  \textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)         & \cellcolor[rgb]{ 1,  .922,  .518}0.169 ($\pm$0.025)     & \cellcolor[rgb]{ .973,  .412,  .42}0.4891 ($\pm$0.077)  \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)           & \cellcolor[rgb]{ .388,  .745,  .482}0.8976 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .922,  .518}0.9137 ($\pm$0.008)    \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)            & \cellcolor[rgb]{ .973,  .412,  .42}0.1056 ($\pm$0.008)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1043 ($\pm$0.009) \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.081 ($\pm$0.069)           & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ 1,  .922,  .518}0.0621 ($\pm$0.038)    \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)         & \cellcolor[rgb]{ 1,  .922,  .518}0.0951 ($\pm$0.015)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1169 ($\pm$0.019)  \\
-                  \textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2411 ($\pm$0.295)            & \cellcolor[rgb]{ .973,  .412,  .42}0.3729 ($\pm$1.119)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1809 ($\pm$0.164) \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}0.0052 ($\pm$0.012)            & \cellcolor[rgb]{ .388,  .745,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ .973,  .412,  .42}0.0774 ($\pm$0.02)   \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ 1,  .922,  .518}0.0587 ($\pm$0.003)            & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.0658 ($\pm$0.003)  \\
-                  \textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)            & \cellcolor[rgb]{ .973,  .412,  .42}0.2454 ($\pm$0.134)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1947 ($\pm$0.014) \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)         & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .973,  .412,  .42}1.1666 ($\pm$0.03)   \\
-            \end{tabular}%
-
-      }
-\end{table}%
-
-Similar to before, Table \ref{tab:results:heuristic_pool:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} \index{heuristic pool}heuristic pool configurations.
-The performance rank is calculated as the average rank produced by each \index{heuristic pool}heuristic pool configuration, for all datasets, over all independent runs and epochs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-      \label{tab:results:heuristic_pool:metrics:rank}%
-      \par\bigskip
-      \resizebox{0.8\textwidth}{!}{
-            \begin{tabular}{r|ccc}
-                                               & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Rank}}                                                                                                                    \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{all}                                               & \textbf{gd}                                             & \textbf{mh}                                            \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}1.7946 ($\pm$0.641)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3828 ($\pm$0.56)  & \cellcolor[rgb]{ .973,  .412,  .42}2.8226 ($\pm$0.42)  \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}2.1871 ($\pm$0.815)     & \cellcolor[rgb]{ .388,  .745,  .482}1.6828 ($\pm$0.751) & \cellcolor[rgb]{ 1,  .922,  .518}2.1301 ($\pm$0.788)   \\
-                  \textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}1.7731 ($\pm$0.562)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3215 ($\pm$0.492) & \cellcolor[rgb]{ .973,  .412,  .42}2.9054 ($\pm$0.334) \\
-                  \textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}1.6247 ($\pm$0.553)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4387 ($\pm$0.532) & \cellcolor[rgb]{ .973,  .412,  .42}2.9366 ($\pm$0.281) \\
-                  \textbf{car}                 & \cellcolor[rgb]{ 1,  .922,  .518}1.5903 ($\pm$0.511)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4409 ($\pm$0.518) & \cellcolor[rgb]{ .973,  .412,  .42}2.9688 ($\pm$0.228) \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}2.4516 ($\pm$0.735)     & \cellcolor[rgb]{ .388,  .745,  .482}1.2806 ($\pm$0.576) & \cellcolor[rgb]{ 1,  .922,  .518}2.2677 ($\pm$0.58)    \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}1.9903 ($\pm$0.849)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8344 ($\pm$0.768) & \cellcolor[rgb]{ .973,  .412,  .42}2.1753 ($\pm$0.796) \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}2.0667 ($\pm$0.834)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8269 ($\pm$0.781) & \cellcolor[rgb]{ .973,  .412,  .42}2.1065 ($\pm$0.807) \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}1.6043 ($\pm$0.687)    & \cellcolor[rgb]{ 1,  .922,  .518}1.6602 ($\pm$0.665)    & \cellcolor[rgb]{ .973,  .412,  .42}2.7355 ($\pm$0.524) \\
-                  \textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}1.8581 ($\pm$0.8)         & \cellcolor[rgb]{ .388,  .745,  .482}1.7806 ($\pm$0.727) & \cellcolor[rgb]{ .973,  .412,  .42}2.3613 ($\pm$0.796) \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}1.5204 ($\pm$0.581)    & \cellcolor[rgb]{ 1,  .922,  .518}1.5484 ($\pm$0.527)    & \cellcolor[rgb]{ .973,  .412,  .42}2.9312 ($\pm$0.289) \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}1.557 ($\pm$0.624)     & \cellcolor[rgb]{ 1,  .922,  .518}1.6011 ($\pm$0.591)    & \cellcolor[rgb]{ .973,  .412,  .42}2.8419 ($\pm$0.445) \\
-                  \textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}1.9828 ($\pm$0.822)       & \cellcolor[rgb]{ .388,  .745,  .482}1.7903 ($\pm$0.848) & \cellcolor[rgb]{ .973,  .412,  .42}2.2269 ($\pm$0.715) \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ 1,  .922,  .518}1.5785 ($\pm$0.55)        & \cellcolor[rgb]{ .388,  .745,  .482}1.4935 ($\pm$0.563) & \cellcolor[rgb]{ .973,  .412,  .42}2.928 ($\pm$0.294)  \\
-                  \midrule
-                  \textbf{avg rank}            & \cellcolor[rgb]{ 1,  .922,  .518}1.8271 ($\pm$0.743)       & \cellcolor[rgb]{ .388,  .745,  .482}1.5773 ($\pm$0.671) & \cellcolor[rgb]{ .973,  .412,  .42}2.5955 ($\pm$0.659) \\
-                  \midrule
-                  \textbf{normalised avg rank} & \cellcolor[rgb]{ 1,  .922,  .518}2                         & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .973,  .412,  .42}3                   \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Similar to the outcomes provided in Section \ref{sec:results:standalone}, by ranked performance over all epochs, it is found that the \textit{gd} configuration yielded the best overall performance compared to the \textit{all} and \textit{mh} configurations.
-However, when considering the test loss measured at the last epoch, there is no clear difference in performance overall.
-This illustrates the reasoning behind the use of the rank metric over all epochs to evaluate the overall training process, as the test loss outcome differs at different epochs and early stopping of the training process was not used.
-
-Figure~\ref{fig:results:heuristic_pool:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different \index{heuristic pool}heuristic pool configurations, per dataset.
-From this illustration it can clearly be seen that, by ranked performance, the \textit{gd} configuration produced better results overall, considering the entire training process.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots for the average ranks of the \acs{BHH} with varying heuristic pools per dataset, across all independent runs and epochs.}
-      \label{fig:results:heuristic_pool:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:heuristic_pool:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic pool}heuristic pool configuration as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/cd/overall.pdf}
-      \caption{Critical difference plots for the average ranks of the \acs{BHH} with varying heuristic pools across all datasets, runs and epochs.}
-      \label{fig:results:heuristic_pool:descriptive:cd}
-\end{figure}
-
-From Figures~\ref{fig:results:heuristic_pool:descriptive:descriptive} and~\ref{fig:results:heuristic_pool:descriptive:cd}, it is clear that the \textit{gd} configuration performs best overall, with exceptions to the parkinsons and housing datasets, where the \textit{all} and \textit{gd} configurations performed equally well with statistically insignificant differences in their outcomes.
-
-From the results shown in this section and Section \ref{sec:results:standalone}, the gradient-based \index{heuristic}heuristics outperformed the \index{meta-heuristic}meta-heuristics in almost all cases.
-It can then logically be concluded that the \acs{BHH} baseline configuration with only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool yields the best performance.
-The inclusion of \index{meta-heuristic}meta-heuristics is done as an attempt to provide a mechanism that could provide even better performance, as well as generalisation capabilities to other datasets.
-The benefits of using \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool is not realised in this dissertation, since the gradient-based \index{heuristic}heuristics provided the best overall performance across  all datasets.
-Furthermore, the standalone gradient-based \index{heuristic}heuristics already produce good performance results, and improvement on those results are hard.
-Faster convergence is also difficult to achieve, since the \acs{BHH} needs sufficient time to explore the heuristic space.
-The benefit that the \acs{BHH} then brings is that it provides a mechanism whereby prior expert knowledge can be injected, before training starts.
-Since gradient-based \index{heuristic}heuristics perform well, future research can exploit this knowledge and provide a significant bias towards these gradient-based \index{heuristic}heuristics through the initialisation of the concentration parameters related to these \index{heuristic}heuristics as mentioned previously.
-
-Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides an illustration of the train and test loss and accuracy plots for an example classification dataset (abalone) as it relates to the \index{heuristic pool}heuristic pool experimental group.
-As before, the illustrations are provided in log scale and illustrations for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/loss/abalone.pdf}
-            \caption{Train log loss}
-            \label{fig:results:heuristic_pool:figures:loss:train:abalone}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/abalone.pdf}
-            \caption{Test log loss}
-            \label{fig:results:heuristic_pool:figures:loss:test:abalone}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/accuracy/abalone.pdf}
-            \caption{Train log accuracy}
-            \label{fig:results:heuristic_pool:figures:accuracy:train:abalone}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/accuracy/abalone.pdf}
-            \caption{Test log accuracy}
-            \label{fig:results:heuristic_pool:figures:accuracy:test:abalone}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the abalone dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:heuristic_pool:figures:abalone}
-\end{figure}
-
-Figure~\ref{fig:results:heuristic_pool:figures:forest_fires} provides the train and test loss plots for an example regression dataset (forest fires) as it relates to the heuristic pool experimental group.
-As before, the illustrations are provided in log scale and illustrations for the other regression datasets are left out for brevity.
-
-\begin{figure}[htb]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/train/loss/forest_fires.pdf}
-            \caption{Train log loss}
-            \label{fig:results:heuristic_pool:figures:loss:train:forest_fires}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/test/loss/forest_fires.pdf}
-            \caption{Test log loss}
-            \label{fig:results:heuristic_pool:figures:loss:test:forest_fires}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the \index{heuristic pool}heuristic pool hyper-parameter on the forest fires dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:heuristic_pool:figures:forest_fires}
-\end{figure}
-
-\section{Population Size}\label{sec:results:population}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{population size} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, five different population sizes are considered.
-These include population sizes of 5, 10, 15, 20, and 25, and experiments are denoted as such.
-
-Table~\ref{tab:results:population:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the population size variants of the \acs{BHH} that was implemented.
-Similar to before, the test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average test loss and statistics for all population size configurations used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-      \label{tab:results:population:metrics:loss}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{r|ccccc}
-                                               & \multicolumn{5}{c}{\textbf{Population - Average Test Loss}}                                                                                                                                                                                                                                        \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{5}                                                  & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                            & \textbf{25}                                             \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088)     & \cellcolor[rgb]{ .612,  .808,  .494}2.1592 ($\pm$0.278) & \cellcolor[rgb]{ 1,  .922,  .518}2.3321 ($\pm$0.446)    & \cellcolor[rgb]{ 1,  .91,  .518}2.3345 ($\pm$0.357)    & \cellcolor[rgb]{ .973,  .412,  .42}2.4188 ($\pm$0.473)  \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 ($\pm$0.016)        & \cellcolor[rgb]{ .388,  .745,  .482}0.2701 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .878,  .51}0.2736 ($\pm$0.014)     & \cellcolor[rgb]{ .973,  .412,  .42}0.2808 ($\pm$0.026) & \cellcolor[rgb]{ .702,  .835,  .498}0.2715 ($\pm$0.011) \\
-                  \textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)      & \cellcolor[rgb]{ .992,  .729,  .482}0.2356 ($\pm$0.029) & \cellcolor[rgb]{ .388,  .745,  .482}0.2268 ($\pm$0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.2294 ($\pm$0.019)   & \cellcolor[rgb]{ .608,  .808,  .494}0.2278 ($\pm$0.012) \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}0.0651 ($\pm$0.02)       & \cellcolor[rgb]{ .388,  .745,  .482}0.0527 ($\pm$0.002) & \cellcolor[rgb]{ .988,  .918,  .514}0.0535 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .898,  .514}0.0541 ($\pm$0.003)   & \cellcolor[rgb]{ 1,  .922,  .518}0.0535 ($\pm$0.003)    \\
-                  \textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)     & \cellcolor[rgb]{ .757,  .851,  .502}0.1595 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}0.161 ($\pm$0.039)     & \cellcolor[rgb]{ .992,  .773,  .49}0.1636 ($\pm$0.04)  & \cellcolor[rgb]{ .973,  .412,  .42}0.17 ($\pm$0.048)    \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)       & \cellcolor[rgb]{ 1,  .922,  .518}0.9954 ($\pm$0.103)    & \cellcolor[rgb]{ .992,  .776,  .49}1.0826 ($\pm$0.3)    & \cellcolor[rgb]{ .525,  .784,  .49}0.9893 ($\pm$0.105) & \cellcolor[rgb]{ .388,  .745,  .482}0.9875 ($\pm$0.078) \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1046 ($\pm$0.008)     & \cellcolor[rgb]{ 1,  .922,  .518}0.1077 ($\pm$0.009)    & \cellcolor[rgb]{ .882,  .886,  .51}0.1071 ($\pm$0.011)  & \cellcolor[rgb]{ .973,  .412,  .42}0.1104 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .886,  .514}0.1079 ($\pm$0.008)    \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}0.081 ($\pm$0.069)         & \cellcolor[rgb]{ .388,  .745,  .482}0.0694 ($\pm$0.059) & \cellcolor[rgb]{ .737,  .843,  .502}0.0761 ($\pm$0.056) & \cellcolor[rgb]{ .984,  .569,  .451}0.084 ($\pm$0.07)  & \cellcolor[rgb]{ .973,  .412,  .42}0.0854 ($\pm$0.065)  \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)     & \cellcolor[rgb]{ 1,  .922,  .518}0.0985 ($\pm$0.026)    & \cellcolor[rgb]{ .412,  .749,  .482}0.0943 ($\pm$0.016) & \cellcolor[rgb]{ 1,  .906,  .518}0.0987 ($\pm$0.017)   & \cellcolor[rgb]{ .973,  .412,  .42}0.1038 ($\pm$0.017)  \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .388,  .745,  .482}0.2411 ($\pm$0.295)     & \cellcolor[rgb]{ .992,  .741,  .486}0.4212 ($\pm$0.671) & \cellcolor[rgb]{ .973,  .412,  .42}0.5905 ($\pm$1.043)  & \cellcolor[rgb]{ .651,  .82,  .494}0.2784 ($\pm$0.261) & \cellcolor[rgb]{ 1,  .922,  .518}0.327 ($\pm$0.381)     \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012)     & \cellcolor[rgb]{ .973,  .412,  .42}1.9037 ($\pm$10.345) & \cellcolor[rgb]{ 1,  .898,  .514}0.3366 ($\pm$1.559)    & \cellcolor[rgb]{ .69,  .831,  .498}0.1311 ($\pm$0.486) & \cellcolor[rgb]{ 1,  .922,  .518}0.2602 ($\pm$1.115)    \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003)     & \cellcolor[rgb]{ .82,  .867,  .506}0.0598 ($\pm$0.003)  & \cellcolor[rgb]{ .988,  .694,  .475}0.0606 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0602 ($\pm$0.003)   & \cellcolor[rgb]{ .973,  .412,  .42}0.0612 ($\pm$0.003)  \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .973,  .412,  .42}0.2359 ($\pm$0.102)      & \cellcolor[rgb]{ .388,  .745,  .482}0.2007 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .922,  .518}0.2092 ($\pm$0.039)    & \cellcolor[rgb]{ .573,  .796,  .49}0.2033 ($\pm$0.037) & \cellcolor[rgb]{ 1,  .922,  .518}0.2091 ($\pm$0.054)    \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)     & \cellcolor[rgb]{ .553,  .792,  .49}1.0864 ($\pm$0.034)  & \cellcolor[rgb]{ .973,  .412,  .42}1.1083 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .922,  .518}1.0961 ($\pm$0.027)   & \cellcolor[rgb]{ .976,  .463,  .431}1.1071 ($\pm$0.039) \\
-            \end{tabular}%
-
-      }
-\end{table}%
-
-From Table \ref{tab:results:population:metrics:loss} it can be seen that the lowest population size produced mostly the best performance outcomes, yielding the best average test loss for eight of the fourteen datasets.
-However, the lowest population size also produced the worst performance outcomes for four of the fourteen datasets.
-From the empirical results that show the average test loss, measured at the last epoch, it is not clear which population size configuration produced the overall best results.
-
-As before, the performance of the different \acs{BHH} population size configurations need to be considered for the entire training process.
-As such, Table \ref{tab:results:population:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} population size configurations.
-Similar to before, the performance rank is calculated as the average rank produced by each population size configuration, for all datasets, over all independent runs and epochs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all independent runs and all epochs.}
-      \label{tab:results:population:metrics:rank}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{r|ccccc}
-                                               & \multicolumn{5}{c}{\textbf{Population - Average Rank}}                                                                                                                                                                                                                                          \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             & \textbf{25}                                             \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.4387 ($\pm$1.34)  & \cellcolor[rgb]{ .714,  .839,  .498}2.7452 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}3.0129 ($\pm$1.386)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4065 ($\pm$1.351)  & \cellcolor[rgb]{ .976,  .427,  .424}3.3968 ($\pm$1.351) \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.7527 ($\pm$1.428) & \cellcolor[rgb]{ .882,  .886,  .51}2.9258 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9656 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.379)   & \cellcolor[rgb]{ .996,  .812,  .498}3.0419 ($\pm$1.437) \\
-                  \textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8129 ($\pm$1.41)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1591 ($\pm$1.435)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9989 ($\pm$1.42)     & \cellcolor[rgb]{ .992,  .761,  .486}3.0505 ($\pm$1.444) & \cellcolor[rgb]{ .929,  .902,  .514}2.9785 ($\pm$1.341) \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}3.8957 ($\pm$1.335)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8688 ($\pm$1.285)    & \cellcolor[rgb]{ 1,  .875,  .51}2.9645 ($\pm$1.345)     & \cellcolor[rgb]{ .773,  .855,  .502}2.743 ($\pm$1.376)  & \cellcolor[rgb]{ .388,  .745,  .482}2.528 ($\pm$1.328)  \\
-                  \textbf{car}                 & \cellcolor[rgb]{ .973,  .412,  .42}3.1892 ($\pm$1.391)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.394)    & \cellcolor[rgb]{ 1,  .922,  .518}3.0398 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8559 ($\pm$1.394) & \cellcolor[rgb]{ .447,  .761,  .482}2.8742 ($\pm$1.415) \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}2.7978 ($\pm$1.508) & \cellcolor[rgb]{ .914,  .894,  .51}2.9387 ($\pm$1.413)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2129 ($\pm$1.452)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9613 ($\pm$1.304)    & \cellcolor[rgb]{ .988,  .663,  .471}3.0892 ($\pm$1.353) \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.8151 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .922,  .518}3.0409 ($\pm$1.429)    & \cellcolor[rgb]{ .984,  .62,  .463}3.0925 ($\pm$1.323)  & \cellcolor[rgb]{ .973,  .412,  .42}3.128 ($\pm$1.407)   & \cellcolor[rgb]{ .682,  .827,  .498}2.9237 ($\pm$1.463) \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .992,  .773,  .49}3.0172 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9215 ($\pm$1.38)  & \cellcolor[rgb]{ .965,  .91,  .514}2.9806 ($\pm$1.383)  & \cellcolor[rgb]{ .973,  .412,  .42}3.0968 ($\pm$1.412)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.488)    \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .431,  .757,  .482}2.8366 ($\pm$1.404) & \cellcolor[rgb]{ .388,  .745,  .482}2.8258 ($\pm$1.38)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9753 ($\pm$1.439)    & \cellcolor[rgb]{ 1,  .91,  .518}2.9849 ($\pm$1.411)     & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.368)  \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8301 ($\pm$1.304) & \cellcolor[rgb]{ .506,  .776,  .486}2.8731 ($\pm$1.397) & \cellcolor[rgb]{ 1,  .922,  .518}3.0505 ($\pm$1.413)    & \cellcolor[rgb]{ .973,  .412,  .42}3.186 ($\pm$1.425)   & \cellcolor[rgb]{ 1,  .886,  .514}3.0602 ($\pm$1.499)    \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.7989 ($\pm$1.205) & \cellcolor[rgb]{ .745,  .847,  .502}2.9441 ($\pm$1.325) & \cellcolor[rgb]{ 1,  .922,  .518}3.0462 ($\pm$1.452)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1366 ($\pm$1.494)  & \cellcolor[rgb]{ 1,  .882,  .51}3.0538 ($\pm$1.566)     \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.6645 ($\pm$1.441) & \cellcolor[rgb]{ .988,  .647,  .467}3.1065 ($\pm$1.327) & \cellcolor[rgb]{ .957,  .91,  .514}3.0247 ($\pm$1.427)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0495 ($\pm$1.442)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1548 ($\pm$1.381)  \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6376 ($\pm$1.436) & \cellcolor[rgb]{ .682,  .827,  .498}2.8645 ($\pm$1.411) & \cellcolor[rgb]{ .992,  .733,  .482}3.1548 ($\pm$1.404) & \cellcolor[rgb]{ .973,  .412,  .42}3.2387 ($\pm$1.397)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1043 ($\pm$1.34)     \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.5505 ($\pm$1.317) & \cellcolor[rgb]{ .62,  .812,  .494}2.7817 ($\pm$1.415)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1581 ($\pm$1.384)    & \cellcolor[rgb]{ 1,  .855,  .506}3.1806 ($\pm$1.394)    & \cellcolor[rgb]{ .973,  .412,  .42}3.329 ($\pm$1.414)   \\
-                  \midrule
-                  \textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}2.8598 ($\pm$1.424) & \cellcolor[rgb]{ .62,  .812,  .494}2.9312 ($\pm$1.389)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0484 ($\pm$1.406)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0952 ($\pm$1.412)  & \cellcolor[rgb]{ .992,  .753,  .486}3.064 ($\pm$1.428)  \\
-                  \midrule
-                  \textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ .988,  .667,  .471}4                   \\
-            \end{tabular}%
-
-      }
-\end{table}%
-
-From Table \ref{tab:results:population:metrics:rank} it can be seen that a lower population size of five, mostly produced the best results, with exception to the bike and car datasets, for which the lowest population size configuration produced the worst performance, yielding statistically significant differences in outcomes from the other datasets.
-A larger population size configuration is preferred for the bike and car datasets.
-Furthermore, a population size configuration of ten, slightly higher than the default of five, is preferred for the forest fires and housing datasets.
-Finally, the overall normalised average rank is provided at the bottom of the table, showing that a population size of five produced the best performance outcome across all datasets on average.
-
-Figure~\ref{fig:results:population:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different population size configurations, per dataset.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_population/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots for the average ranks of \acs{BHH} with varying population sizes per dataset, across all independent runs and epochs.}
-      \label{fig:results:population:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:population:descriptive:descriptive} shows the correlation of performance with population size for each dataset.
-From these illustrations, it can be seen that the correlation between the population size configuration and performance is different for each dataset, suggesting that the population size hyper-parameter is problem specific.
-However, the overall performance related to each population configuration, across all datasets is not clear from these illustrations.
-
-Figure~\ref{fig:results:population:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each population size configuration as it relates to all datasets, across all independent runs and epochs.
-It is shown that there is no overall statistical significant difference between population sizes, and thus it can be concluded that the population size hyper-parameter is problem specific.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_population/figures/cd/overall.pdf}
-      \caption{Critical difference plots for the average ranks of \acs{BHH} with varying population sizes across all datasets, runs and epochs.}
-      \label{fig:results:population:descriptive:cd}
-\end{figure}
-
-Similar to before, Figure~\ref{fig:results:population:figures:mushroom} provides the train and test loss and accuracy plots for an example classification dataset (mushroom) as it relates to the population size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_population/figures/train/loss/mushroom.pdf}
-            \caption{Train log loss}
-            \label{fig:results:population:figures:loss:train:mushroom}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_population/figures/test/loss/mushroom.pdf}
-            \caption{Test log loss}
-            \label{fig:results:population:figures:loss:test:mushroom}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_population/figures/train/accuracy/mushroom.pdf}
-            \caption{Train log accuracy}
-            \label{fig:results:population:figures:accuracy:train:mushroom}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_population/figures/test/accuracy/mushroom.pdf}
-            \caption{Test log accuracy}
-            \label{fig:results:population:figures:accuracy:test:mushroom}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:population:figures:mushroom}
-\end{figure}
-
-As a reminder, the experimental group for population sizes only varies the population size hyper-parameter and all other hyper-parameters remain the same between configurations.
-As such, all population size configurations make use of the \index{heuristic pool}heuristic pool configuration that includes all the low-level heuristics, including gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
-
-Divergence of the training loss can be observed in Figure \ref{fig:results:population:figures:loss:test:mushroom}.
-Note that, despite the divergence of training loss, the accuracy is still almost 100\% and that these divergent behaviours are simply a result of an attempt to further improve performance, by exploring the heuristic space more.
-For example, heuristics could have momentum as a result of good training progression thus far, but then overshoot good solutions after \index{heuristic}heuristic reselection.
-Overshooting good solutions then causes the \index{heuristic}heuristics to struggle to converge back to good solutions, especially if many different \index{heuristic}heuristics are selected in quick succession.
-A suggestion to this problem is to implement a move-acceptance strategy as was mentioned before.
-At the ninth epoch, the \acs{BHH} fails to produce better solutions on the training set.
-Since there is not much room for more improvement, the \acs{BHH} is bound to try different \index{heuristic}heuristics that yield sub-optimal results.
-From this point onwards, the \acs{BHH} finds slightly better results on the train set, and as a result, produces volatile performance on the test set.
-
-Figure~\ref{fig:results:population:figures:student_performance} provides the train and test loss plots for an example regression dataset (student performance) as it relates to the population size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_population/figures/train/loss/student_performance.pdf}
-            \caption{Train log loss}
-            \label{fig:results:population:figures:loss:train:student_performance}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_population/figures/test/loss/student_performance.pdf}
-            \caption{Test log loss}
-            \label{fig:results:population:figures:loss:test:student_performance}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the student performance dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:population:figures:student_performance}
-\end{figure}
-
-From Figure~\ref{fig:results:population:figures:loss:train:student_performance} it can be seen that the \acs{BHH} with a low population size of five starts to diverge away from optimal results as it explores different \index{heuristic}heuristics in an attempt to provide better solutions.
-Divergence can be eliminated by means of an early stopping strategy as well as a move-acceptance strategy as mentioned before.
-
-\section{Credit Assignment Strategy}\label{sec:results:credit}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{credit assignment strategy} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, five different credit assignment strategies are considered.
-These include the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies as presented in Chapter \ref{chap:bhh} and experiments are denoted as such.
-
-Table~\ref{tab:results:credit:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the credit assignment strategy variants of the \acs{BHH} that was implemented.
-As before, the test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average test loss and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-      \label{tab:results:credit:metrics:loss}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{r|ccccc}
-                                               & \multicolumn{5}{c}{\textbf{Credit - Average Test Loss}}                                                                                                                                                                                                                             \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{ibest}                                          & \textbf{pbest}                                       & \textbf{rbest}                                       & \textbf{gbest}                                       & \textbf{symmetric}                                   \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ .631,  .816,  .494}2.0587 (+-0.088)    & \cellcolor[rgb]{ .388,  .745,  .482}2.0422 (+-0.094) & \cellcolor[rgb]{ .996,  .792,  .494}2.0922 (+-0.152) & \cellcolor[rgb]{ 1,  .922,  .518}2.0833 (+-0.136)    & \cellcolor[rgb]{ .973,  .412,  .42}2.1177 (+-0.259)  \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 (+-0.016)     & \cellcolor[rgb]{ .902,  .89,  .51}0.2678 (+-0.015)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2644 (+-0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.2684 (+-0.013)    & \cellcolor[rgb]{ 1,  .882,  .51}0.2688 (+-0.017)     \\
-                  \textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 (+-0.065)       & \cellcolor[rgb]{ .973,  .412,  .42}0.2645 (+-0.171)  & \cellcolor[rgb]{ .51,  .78,  .486}0.238 (+-0.047)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2361 (+-0.031) & \cellcolor[rgb]{ .996,  .812,  .498}0.2498 (+-0.047) \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .988,  .647,  .467}0.0651 (+-0.02)     & \cellcolor[rgb]{ 1,  .922,  .518}0.0634 (+-0.023)    & \cellcolor[rgb]{ .871,  .882,  .51}0.0633 (+-0.02)   & \cellcolor[rgb]{ .388,  .745,  .482}0.063 (+-0.021)  & \cellcolor[rgb]{ .973,  .412,  .42}0.0666 (+-0.021)  \\
-                  \textbf{car}                 & \cellcolor[rgb]{ 1,  .91,  .518}0.1572 (+-0.034)        & \cellcolor[rgb]{ 1,  .922,  .518}0.1569 (+-0.029)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1665 (+-0.03)   & \cellcolor[rgb]{ .388,  .745,  .482}0.1504 (+-0.03)  & \cellcolor[rgb]{ .945,  .906,  .514}0.1564 (+-0.037) \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .878,  .886,  .51}1.2983 (+-0.66)      & \cellcolor[rgb]{ .988,  .651,  .467}1.4981 (+-2.41)  & \cellcolor[rgb]{ .973,  .412,  .42}1.6172 (+-1.527)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0347 (+-0.231) & \cellcolor[rgb]{ 1,  .922,  .518}1.3627 (+-1.145)    \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .988,  .647,  .467}0.1046 (+-0.008)    & \cellcolor[rgb]{ 1,  .922,  .518}0.1028 (+-0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1024 (+-0.009) & \cellcolor[rgb]{ .973,  .412,  .42}0.1061 (+-0.009)  & \cellcolor[rgb]{ .643,  .816,  .494}0.1026 (+-0.009) \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .973,  .914,  .514}0.081 (+-0.069)     & \cellcolor[rgb]{ 1,  .922,  .518}0.0819 (+-0.062)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0591 (+-0.046) & \cellcolor[rgb]{ .973,  .412,  .42}0.0845 (+-0.077)  & \cellcolor[rgb]{ 1,  .867,  .51}0.0822 (+-0.07)      \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 (+-0.017)    & \cellcolor[rgb]{ .996,  .82,  .498}0.0974 (+-0.021)  & \cellcolor[rgb]{ .835,  .875,  .506}0.0961 (+-0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.0995 (+-0.016)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0969 (+-0.018)    \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 (+-0.295)     & \cellcolor[rgb]{ .388,  .745,  .482}0.1441 (+-0.131) & \cellcolor[rgb]{ 1,  .922,  .518}0.1547 (+-0.111)    & \cellcolor[rgb]{ 1,  .882,  .51}0.1616 (+-0.187)     & \cellcolor[rgb]{ .765,  .851,  .502}0.1507 (+-0.142) \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .404,  .749,  .482}0.0052 (+-0.012)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0289 (+-0.107)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0044 (+-0.011) & \cellcolor[rgb]{ 1,  .91,  .518}0.1835 (+-0.949)     & \cellcolor[rgb]{ .973,  .412,  .42}5.3926 (+-29.503) \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 (+-0.003)    & \cellcolor[rgb]{ 1,  .867,  .51}0.0594 (+-0.002)     & \cellcolor[rgb]{ .973,  .412,  .42}0.0602 (+-0.002)  & \cellcolor[rgb]{ .898,  .89,  .51}0.0592 (+-0.002)   & \cellcolor[rgb]{ 1,  .922,  .518}0.0593 (+-0.003)    \\
-                  \textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 (+-0.102)       & \cellcolor[rgb]{ .678,  .827,  .498}0.2303 (+-0.095) & \cellcolor[rgb]{ .988,  .69,  .475}0.2551 (+-0.109)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2251 (+-0.088) & \cellcolor[rgb]{ .973,  .412,  .42}0.2777 (+-0.116)  \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .98,  .525,  .443}1.0827 (+-0.026)     & \cellcolor[rgb]{ 1,  .922,  .518}1.0799 (+-0.031)    & \cellcolor[rgb]{ .925,  .898,  .51}1.0794 (+-0.021)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0757 (+-0.027) & \cellcolor[rgb]{ .973,  .412,  .42}1.0835 (+-0.029)  \\
-            \end{tabular}%
-      }
-\end{table}%
-
-From Table~\ref{tab:results:credit:metrics:loss}, it is not clear which credit assignment strategy yields the best performance for the entire training process.
-As such, Table \ref{tab:results:credit:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} credit assignment strategy configurations.
-Similar to before, the performance rank is calculated as the average rank produced by each credit assignment strategy configuration, for all datasets, over all independent runs and epochs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-      \label{tab:results:credit:metrics:rank}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{r|ccccc}
-                                               & \multicolumn{5}{c}{\textbf{Credit - Average Rank}}                                                                                                                                                                                                                                              \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{ibest}                                          & \textbf{pbest}                                          & \textbf{rbest}                                          & \textbf{gbest}                                          & \textbf{symmetric}                                      \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}3.1677 ($\pm$1.319)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8613 ($\pm$1.459) & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.399)    & \cellcolor[rgb]{ .863,  .882,  .51}2.9667 ($\pm$1.455)  & \cellcolor[rgb]{ 1,  .89,  .514}3.0075 ($\pm$1.421)     \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.1312 ($\pm$1.347)  & \cellcolor[rgb]{ .91,  .894,  .51}3.0376 ($\pm$1.357)   & \cellcolor[rgb]{ .388,  .745,  .482}2.5914 ($\pm$1.465) & \cellcolor[rgb]{ .98,  .498,  .439}3.128 ($\pm$1.336)   & \cellcolor[rgb]{ 1,  .922,  .518}3.1118 ($\pm$1.487)    \\
-                  \textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.8591 ($\pm$1.344) & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.432)    & \cellcolor[rgb]{ .522,  .78,  .486}2.8882 ($\pm$1.41)   & \cellcolor[rgb]{ .996,  .804,  .498}3.0441 ($\pm$1.415) & \cellcolor[rgb]{ .973,  .412,  .42}3.2183 ($\pm$1.442)  \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .98,  .537,  .447}3.0527 ($\pm$1.34)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0086 ($\pm$1.393)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0667 ($\pm$1.483)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8742 ($\pm$1.339) & \cellcolor[rgb]{ .949,  .906,  .514}2.9978 ($\pm$1.503) \\
-                  \textbf{car}                 & \cellcolor[rgb]{ .992,  .729,  .482}3.1151 ($\pm$1.356) & \cellcolor[rgb]{ 1,  .922,  .518}3.0312 ($\pm$1.483)    & \cellcolor[rgb]{ .973,  .412,  .42}3.2516 ($\pm$1.402)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6892 ($\pm$1.354) & \cellcolor[rgb]{ .788,  .859,  .502}2.9129 ($\pm$1.411) \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .996,  .918,  .514}2.8914 ($\pm$1.349) & \cellcolor[rgb]{ .388,  .745,  .482}2.6269 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.4151 ($\pm$1.365)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8925 ($\pm$1.362)    & \cellcolor[rgb]{ .988,  .647,  .467}3.1742 ($\pm$1.449) \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .98,  .541,  .447}3.1516 ($\pm$1.436)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9903 ($\pm$1.452)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.475) & \cellcolor[rgb]{ .973,  .412,  .42}3.2043 ($\pm$1.299)  & \cellcolor[rgb]{ .749,  .847,  .502}2.8957 ($\pm$1.358) \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.277)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1806 ($\pm$1.304)  & \cellcolor[rgb]{ .58,  .8,  .49}2.8559 ($\pm$1.356)     & \cellcolor[rgb]{ .992,  .773,  .49}3.1215 ($\pm$1.502)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7452 ($\pm$1.563) \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .984,  .918,  .514}2.9011 ($\pm$1.494) & \cellcolor[rgb]{ .388,  .745,  .482}2.8527 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}2.9022 ($\pm$1.397)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3108 ($\pm$1.324)  & \cellcolor[rgb]{ .992,  .761,  .486}3.0333 ($\pm$1.483) \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}3.1892 ($\pm$1.428)  & \cellcolor[rgb]{ .996,  .827,  .502}3.0839 ($\pm$1.441) & \cellcolor[rgb]{ 1,  .922,  .518}3.0591 ($\pm$1.376)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8237 ($\pm$1.409) & \cellcolor[rgb]{ .439,  .757,  .482}2.8441 ($\pm$1.384) \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.8075 ($\pm$1.459) & \cellcolor[rgb]{ 1,  .922,  .518}3.0183 ($\pm$1.411)    & \cellcolor[rgb]{ .643,  .816,  .494}2.8957 ($\pm$1.398) & \cellcolor[rgb]{ .992,  .706,  .478}3.0839 ($\pm$1.418) & \cellcolor[rgb]{ .973,  .412,  .42}3.172 ($\pm$1.381)   \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.5645 ($\pm$1.484) & \cellcolor[rgb]{ .898,  .89,  .51}2.8925 ($\pm$1.343)   & \cellcolor[rgb]{ .973,  .412,  .42}3.5065 ($\pm$1.219)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0796 ($\pm$1.392) & \cellcolor[rgb]{ 1,  .922,  .518}2.957 ($\pm$1.455)     \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.6624 ($\pm$1.312) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.407)     & \cellcolor[rgb]{ .988,  .643,  .467}3.1892 ($\pm$1.382) & \cellcolor[rgb]{ .612,  .808,  .494}2.7978 ($\pm$1.47)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3215 ($\pm$1.394)  \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .98,  .494,  .439}3.1871 ($\pm$1.308)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .922,  .518}3.014 ($\pm$1.371)     & \cellcolor[rgb]{ .882,  .886,  .51}2.9419 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.43)   \\
-                  \midrule
-                  \textbf{avg rank}            & \cellcolor[rgb]{ .843,  .875,  .506}2.9841 ($\pm$1.39)  & \cellcolor[rgb]{ .388,  .745,  .482}2.9457 ($\pm$1.415) & \cellcolor[rgb]{ .984,  .588,  .455}3.0279 ($\pm$1.414) & \cellcolor[rgb]{ 1,  .922,  .518}2.997 ($\pm$1.402)     & \cellcolor[rgb]{ .973,  .412,  .42}3.0437 ($\pm$1.449)  \\
-                  \midrule
-                  \textbf{normalised avg rank} & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
-            \end{tabular}%
-
-      }
-\end{table}%
-
-Table \ref{tab:results:credit:metrics:rank} shows that different credit assignment strategies perform best for different datasets, from which it can be concluded that the credit assignment strategy hyper-parameter is problem specific.
-Furthermore, the overall normalised average rank across all datasets is provided at the bottom of the table.
-It should be noted that the \textit{symmetric} credit assignment strategy yielded the best results for the forest fires dataset.
-This does not necessarily suggest that random search in the heuristic space yields the best performance for this dataset.
-As a reminder, the \textit{symmetric} credit assignment strategy does not bias towards performance, but rather uniformly assigns credit to any heuristic that happens to be selected.
-For the particular case where the \textit{symmetric} credit assignment strategy yielded the best results, it could be the case that the initial selection of heuristics is good enough and that it is difficult to find a performance bias that results in better performance, as all \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool provide good results.
-For all other datasets, it is found that a particular non-\textit{symmetric} credit assignment strategy yields better results.
-
-Figure~\ref{fig:results:credit:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of the different credit assignment strategy configurations, per dataset.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_credit/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots for the average ranks of the \acs{BHH} with varying credit assignment strategies per dataset, across all independent runs and epochs.}
-      \label{fig:results:credit:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:credit:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each credit assignment strategy configuration as it relates to all datasets, across all independent runs and epochs.
-It is shown that there is no overall statistical significant difference between credit assignment strategies and that the credit assignment strategy hyper-parameter is problem specific.
-At this point it should be mentioned that the credit assignment strategies implemented in this dissertation yield a discrete credit value and that future research should consider a continuous credit value in an attempt to provide a more fine grained indicator of performance, which should be easier to exploit.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_credit/figures/cd/overall.pdf}
-      \caption{Critical difference plots for the average ranks of the \acs{BHH} with varying credit assignment strategies across all datasets, runs and epochs.}
-      \label{fig:results:credit:descriptive:cd}
-\end{figure}
-
-Similar to before, Figure~\ref{fig:results:credit:figures:bank} provides the train and test loss and accuracy plots for an example classification dataset (bank) as it relates to the credit assignment strategy experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/bank.pdf}
-            \caption{Train log loss}
-            \label{fig:results:credit:figures:loss:train:bank}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/bank.pdf}
-            \caption{Test log loss}
-            \label{fig:results:credit:figures:loss:test:bank}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_credit/figures/train/accuracy/bank.pdf}
-            \caption{Train log accuracy}
-            \label{fig:results:credit:figures:accuracy:train:bank}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_credit/figures/test/accuracy/bank.pdf}
-            \caption{Test log accuracy}
-            \label{fig:results:credit:figures:accuracy:test:bank}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the bank dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:credit:figures:bank}
-\end{figure}
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/housing.pdf}
-            \caption{Train log loss}
-            \label{fig:results:credit:figures:loss:train:housing}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/housing.pdf}
-            \caption{Test log loss}
-            \label{fig:results:credit:figures:loss:test:housing}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the housing dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:credit:figures:housing}
-\end{figure}
-
-From Figure~\ref{fig:results:credit:figures:bank} it can be seen that the \textit{pbest} credit assignment strategy diverged away from the current best solution, but was able to return to the current best solution.
-Since the solution found by the \acs{BHH} with the \textit{pbest} credit assignment strategy was already optimal before divergence, it stands to reason that this divergence is a result of the \acs{BHH} exploring other \index{heuristic}heuristics in the heuristic space that yield sub-optimal solutions.
-As mentioned before, a move-acceptance strategy can be incorporated to counteract this effect.
-
-Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plots for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\section{Reselection Interval}\label{sec:results:reselection}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{reselection interval} hyper-parameter.
-Detailed discussions follow and illustrations are provided for visual aid.
-As a reminder, five different reselection intervals are considered.
-These include reselection intervals of 1, 5, 10, 15, and 20.
-Experiments are denoted as such.
-
-Table~\ref{tab:results:reselection:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the reselection interval variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average test loss and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-      \label{tab:results:reselection:metrics:loss}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{r|ccccc}
-                                               & \multicolumn{5}{c}{\textbf{Reselection - Average Test Loss}}                                                                                                                                                                                                                                         \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{1}                                                   & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}2.737 ($\pm$0.507)        & \cellcolor[rgb]{ 1,  .922,  .518}2.0907 ($\pm$0.113)    & \cellcolor[rgb]{ .545,  .788,  .49}2.0587 ($\pm$0.088)  & \cellcolor[rgb]{ .388,  .745,  .482}2.0475 ($\pm$0.103) & \cellcolor[rgb]{ 1,  .906,  .518}2.1139 ($\pm$0.336)    \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.3003 ($\pm$0.046)       & \cellcolor[rgb]{ .992,  .725,  .482}0.2835 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 ($\pm$0.016)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2619 ($\pm$0.013) & \cellcolor[rgb]{ .486,  .773,  .486}0.2637 ($\pm$0.016) \\
-                  \textbf{bank}                & \cellcolor[rgb]{ .984,  .596,  .455}0.2933 ($\pm$0.033)      & \cellcolor[rgb]{ .973,  .412,  .42}0.3198 ($\pm$0.18)   & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .553,  .792,  .49}0.2299 ($\pm$0.032)  & \cellcolor[rgb]{ .388,  .745,  .482}0.224 ($\pm$0.018)  \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}0.1524 ($\pm$0.023)       & \cellcolor[rgb]{ .988,  .671,  .471}0.1084 ($\pm$0.025) & \cellcolor[rgb]{ 1,  .922,  .518}0.0651 ($\pm$0.02)     & \cellcolor[rgb]{ .6,  .804,  .494}0.0566 ($\pm$0.01)    & \cellcolor[rgb]{ .388,  .745,  .482}0.052 ($\pm$0.004)  \\
-                  \textbf{car}                 & \cellcolor[rgb]{ .973,  .412,  .42}0.2157 ($\pm$0.031)       & \cellcolor[rgb]{ 1,  .922,  .518}0.1591 ($\pm$0.026)    & \cellcolor[rgb]{ .91,  .894,  .51}0.1572 ($\pm$0.034)   & \cellcolor[rgb]{ 1,  .863,  .51}0.1659 ($\pm$0.064)     & \cellcolor[rgb]{ .388,  .745,  .482}0.1456 ($\pm$0.03)  \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}0.9624 ($\pm$0.043)      & \cellcolor[rgb]{ .973,  .412,  .42}3.7821 ($\pm$4.993)  & \cellcolor[rgb]{ 1,  .914,  .518}1.2983 ($\pm$0.66)     & \cellcolor[rgb]{ 1,  .922,  .518}1.2541 ($\pm$0.868)    & \cellcolor[rgb]{ .482,  .773,  .486}1.0085 ($\pm$0.251) \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}0.1091 ($\pm$0.01)        & \cellcolor[rgb]{ 1,  .922,  .518}0.1043 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .894,  .514}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1013 ($\pm$0.008) & \cellcolor[rgb]{ .549,  .792,  .49}0.1021 ($\pm$0.008)  \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.1253 ($\pm$0.087)       & \cellcolor[rgb]{ .988,  .702,  .478}0.1002 ($\pm$0.064) & \cellcolor[rgb]{ 1,  .922,  .518}0.081 ($\pm$0.069)     & \cellcolor[rgb]{ .647,  .82,  .494}0.0681 ($\pm$0.055)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0586 ($\pm$0.056) \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}0.1268 ($\pm$0.025)       & \cellcolor[rgb]{ 1,  .902,  .514}0.0974 ($\pm$0.017)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.0961 ($\pm$0.026)    & \cellcolor[rgb]{ .729,  .843,  .502}0.0952 ($\pm$0.02)  \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .714,  .839,  .498}0.1633 ($\pm$0.135)      & \cellcolor[rgb]{ .388,  .745,  .482}0.1376 ($\pm$0.138) & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 ($\pm$0.295)  & \cellcolor[rgb]{ .976,  .447,  .427}0.2373 ($\pm$0.361) & \cellcolor[rgb]{ 1,  .922,  .518}0.1853 ($\pm$0.235)    \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .973,  .412,  .42}1.8461 ($\pm$5.829)       & \cellcolor[rgb]{ .886,  .886,  .51}0.0283 ($\pm$0.099)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ 1,  .922,  .518}0.0388 ($\pm$0.111)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0335 ($\pm$0.158)    \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .973,  .412,  .42}0.0872 ($\pm$0.018)       & \cellcolor[rgb]{ 1,  .886,  .514}0.0609 ($\pm$0.004)    & \cellcolor[rgb]{ 1,  .922,  .518}0.0587 ($\pm$0.003)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0584 ($\pm$0.002) & \cellcolor[rgb]{ .482,  .769,  .486}0.0585 ($\pm$0.003) \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .973,  .412,  .42}0.4376 ($\pm$0.108)       & \cellcolor[rgb]{ .98,  .518,  .443}0.397 ($\pm$0.13)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2359 ($\pm$0.102)    & \cellcolor[rgb]{ .784,  .859,  .502}0.223 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1991 ($\pm$0.064) \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}1.1183 ($\pm$0.031)       & \cellcolor[rgb]{ 1,  .922,  .518}1.081 ($\pm$0.023)     & \cellcolor[rgb]{ 1,  .898,  .514}1.0827 ($\pm$0.026)    & \cellcolor[rgb]{ .388,  .745,  .482}1.0711 ($\pm$0.028) & \cellcolor[rgb]{ .498,  .776,  .486}1.0729 ($\pm$0.022) \\
-            \end{tabular}%
-      }
-\end{table}%
-
-From Table~\ref{tab:results:reselection:metrics:loss}, a clear pattern can be observed.
-The empirical results show that, in general, a larger reselection interval is preferred, with the largest reselection intervals yielding the best performance outcomes in the majority of cases, and the lowest reselection interval of one, yielding the worst performance in the majority of cases.
-
-To illustrate the effects of the reselection interval hyper-parameter on the entire training, process, Table \ref{tab:results:reselection:metrics:rank} provides the average ranked performance, per dataset, of each of the \acs{BHH} reselection interval configurations.
-Similar to before, the performance rank is calculated as the average rank produced by reselection interval configuration, for all datasets, over all independent runs and epochs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-      \label{tab:results:reselection:metrics:rank}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{r|ccccc}
-                                               & \multicolumn{5}{c}{\textbf{Reselection - Average Rank}}                                                                                                                                                                                                                                         \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}4.3548 ($\pm$0.976)  & \cellcolor[rgb]{ 1,  .894,  .514}2.8473 ($\pm$1.288)    & \cellcolor[rgb]{ 1,  .922,  .518}2.7505 ($\pm$1.262)    & \cellcolor[rgb]{ .557,  .792,  .49}2.5602 ($\pm$1.299)  & \cellcolor[rgb]{ .388,  .745,  .482}2.4871 ($\pm$1.318) \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}3.7355 ($\pm$1.405)  & \cellcolor[rgb]{ .984,  .631,  .463}3.4075 ($\pm$1.379) & \cellcolor[rgb]{ 1,  .922,  .518}2.9688 ($\pm$1.278)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4237 ($\pm$1.228) & \cellcolor[rgb]{ .431,  .757,  .482}2.4645 ($\pm$1.291) \\
-                  \textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}4.5677 ($\pm$0.704)  & \cellcolor[rgb]{ .988,  .635,  .463}3.6323 ($\pm$1.127) & \cellcolor[rgb]{ 1,  .922,  .518}2.4237 ($\pm$1.133)    & \cellcolor[rgb]{ .627,  .812,  .494}2.2462 ($\pm$1.114) & \cellcolor[rgb]{ .388,  .745,  .482}2.1301 ($\pm$1.096) \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .973,  .412,  .42}4.7935 ($\pm$0.612)  & \cellcolor[rgb]{ .984,  .608,  .459}3.9204 ($\pm$0.648) & \cellcolor[rgb]{ 1,  .922,  .518}2.5161 ($\pm$0.863)    & \cellcolor[rgb]{ .671,  .824,  .498}2.0763 ($\pm$0.901) & \cellcolor[rgb]{ .388,  .745,  .482}1.6935 ($\pm$0.891) \\
-                  \textbf{car}                 & \cellcolor[rgb]{ .973,  .412,  .42}4.6409 ($\pm$0.785)  & \cellcolor[rgb]{ .996,  .847,  .506}2.9527 ($\pm$1.158) & \cellcolor[rgb]{ 1,  .922,  .518}2.6548 ($\pm$1.175)    & \cellcolor[rgb]{ .824,  .871,  .506}2.5312 ($\pm$1.244) & \cellcolor[rgb]{ .388,  .745,  .482}2.2204 ($\pm$1.217) \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ 1,  .859,  .506}3.0129 ($\pm$1.048)    & \cellcolor[rgb]{ .973,  .412,  .42}4.4624 ($\pm$0.869)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7957 ($\pm$1.175)    & \cellcolor[rgb]{ .827,  .871,  .506}2.6065 ($\pm$1.439) & \cellcolor[rgb]{ .388,  .745,  .482}2.1226 ($\pm$1.264) \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}3.7484 ($\pm$1.238)  & \cellcolor[rgb]{ .996,  .851,  .506}3.1376 ($\pm$1.317) & \cellcolor[rgb]{ 1,  .922,  .518}3.0344 ($\pm$1.406)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4656 ($\pm$1.304) & \cellcolor[rgb]{ .545,  .788,  .49}2.614 ($\pm$1.432)   \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}3.8194 ($\pm$1.433)  & \cellcolor[rgb]{ .992,  .706,  .478}3.272 ($\pm$1.248)  & \cellcolor[rgb]{ 1,  .922,  .518}2.8656 ($\pm$1.346)    & \cellcolor[rgb]{ .953,  .906,  .514}2.8194 ($\pm$1.305) & \cellcolor[rgb]{ .388,  .745,  .482}2.2237 ($\pm$1.219) \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}4.1892 ($\pm$1.099)  & \cellcolor[rgb]{ .996,  .808,  .498}3.0172 ($\pm$1.288) & \cellcolor[rgb]{ .624,  .812,  .494}2.5871 ($\pm$1.354) & \cellcolor[rgb]{ .388,  .745,  .482}2.5312 ($\pm$1.265) & \cellcolor[rgb]{ 1,  .922,  .518}2.6753 ($\pm$1.34)     \\
-                  \textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}2.9839 ($\pm$1.424)    & \cellcolor[rgb]{ .973,  .914,  .514}2.971 ($\pm$1.317)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3462 ($\pm$1.418)  & \cellcolor[rgb]{ 1,  .882,  .51}3.014 ($\pm$1.405)      & \cellcolor[rgb]{ .388,  .745,  .482}2.6849 ($\pm$1.429) \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .973,  .412,  .42}4.2065 ($\pm$1.236)  & \cellcolor[rgb]{ 1,  .859,  .506}2.9688 ($\pm$1.299)    & \cellcolor[rgb]{ .631,  .816,  .494}2.586 ($\pm$1.234)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7882 ($\pm$1.34)     & \cellcolor[rgb]{ .388,  .745,  .482}2.4505 ($\pm$1.226) \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .973,  .412,  .42}4.7645 ($\pm$0.756)  & \cellcolor[rgb]{ .992,  .769,  .49}3.1882 ($\pm$1.021)  & \cellcolor[rgb]{ .49,  .773,  .486}2.2957 ($\pm$1.209)  & \cellcolor[rgb]{ 1,  .922,  .518}2.4968 ($\pm$1.128)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2548 ($\pm$1.097) \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .976,  .431,  .424}3.971 ($\pm$1.094)  & \cellcolor[rgb]{ .973,  .412,  .42}4.0226 ($\pm$1.12)   & \cellcolor[rgb]{ 1,  .922,  .518}2.4774 ($\pm$1.221)    & \cellcolor[rgb]{ .388,  .745,  .482}2.2495 ($\pm$1.2)   & \cellcolor[rgb]{ .467,  .765,  .486}2.2796 ($\pm$1.132) \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}4.0688 ($\pm$1.122)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9204 ($\pm$1.293)    & \cellcolor[rgb]{ 1,  .906,  .518}2.9559 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.4032 ($\pm$1.378) & \cellcolor[rgb]{ .678,  .827,  .498}2.6516 ($\pm$1.28)  \\
-                  \midrule
-                  \textbf{avg rank}            & \cellcolor[rgb]{ .973,  .412,  .42}4.0612 ($\pm$1.229)  & \cellcolor[rgb]{ .988,  .69,  .475}3.3372 ($\pm$1.277)  & \cellcolor[rgb]{ 1,  .922,  .518}2.7327 ($\pm$1.283)    & \cellcolor[rgb]{ .647,  .82,  .494}2.5151 ($\pm$1.282)  & \cellcolor[rgb]{ .388,  .745,  .482}2.3538 ($\pm$1.266) \\
-                  \midrule
-                  \textbf{normalised avg rank} & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   \\
-            \end{tabular}%
-
-      }
-\end{table}%
-
-Table \ref{tab:results:reselection:metrics:rank} shows that larger reselection intervals are mostly preferred.
-The overall normalised average rank is given at the bottom of the table and supports this finding.
-This outcome can be explained as follows.
-A larger reselection interval gives the low-level \index{heuristic}heuristics more time to execute, resulting in smoother update steps and provides an opportunity for the \acs{BHH} to gather more evidence of the current selection of \index{heuristic}heuristics' performance in the performance log.
-Both of these effects allow the \acs{BHH} to select better \index{heuristic}heuristics during training.
-This is further supported by the findings from Sections \ref{sec:results:standalone} and \ref{sec:results:heuristic_pool}, that show that gradient-based \index{heuristic}heuristics generally yield the best performance.
-Most of the gradient-based \index{heuristic}heuristics that are included in the \index{heuristic pool }heuristic pool implement exponentially averaged state parameters in order to produce smooth update steps.
-If reselection occurs too frequently, these exponentially averaged state parameters do not yield smooth update steps.
-This is further supported by the inclusion of \acp{MH} such as \acp{GA} and \acs{DE}, which recombine state parameters.
-
-Finally, it should be noted that the default reanalysis interval is 10 and the default replay window size is also ten.
-At every reanalysis interval, the concentrations for low-level \index{heuristic}heuristics are reset to the default, symmetrical value of 1.0.
-The replay window size then determines the number of samples in the performance log from which the reanalysis can be done.
-As such, \acs{BHH} configurations with reselection intervals that are larger than the replay window size, will only consider performance samples from the last replay window, which should contain less entries than the reselection interval.
-The reselection interval then directly influences what goes into the performance log.
-Since it is found that reselection intervals larger than the default reanalysis interval and replay window size yield better performance, it can be suggested that exploitation of low-level \index{heuristic}heuristics yields better results than exploration of low-level \index{heuristic}heuristics.
-
-Furthermore, early in the training process, a low reselection interval yields the highest variance of \index{heuristic}heuristic selection.
-Since the default population size is five and the default number of heuristics in the heuristic pool is thirteen, not all heuristics are represented at every training step, causing an unwanted bias towards the \index{heuristic}heuristics that happen to be             selected.
-
-Figure~\ref{fig:results:credit:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reselection interval configurations, per dataset.
-It can be seen that a general pattern occurs for almost all datasets that show an inverse correlation between performance and the reselection interval.
-Some exceptions to this relationship can be observed for the iris and diabetic datasets where an average reselection interval yielded the best results.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_reselection/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reselection interval values per dataset, across all independent runs and epochs.}
-      \label{fig:results:reselection:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:reselection:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reselection interval configuration as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_reselection/figures/cd/overall.pdf}
-      \caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reselection interval values across all datasets, runs and epochs.}
-      \label{fig:results:reselection:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:reselection:descriptive:cd} shows the statistically significant difference in overall results for the various reselection intervals across all datasets.
-It can be seen that larger reselection intervals statistically perform better than smaller reselection intervals.
-The largest reselection intervals (15 and 20) yielded the best overall results with statistically insignificant differences between them.
-
-Similar to before, Figure~\ref{fig:results:reselection:figures:car} provides the train and test loss and accuracy plots for an example classification dataset (car) as it relates to the reselection interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/car.pdf}
-            \caption{Train log loss}
-            \label{fig:results:reselection:figures:loss:train:car}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/car.pdf}
-            \caption{Test log loss}
-            \label{fig:results:reselection:figures:loss:test:car}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reselection/figures/train/accuracy/car.pdf}
-            \caption{Train log accuracy}
-            \label{fig:results:reselection:figures:accuracy:train:car}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reselection/figures/test/accuracy/car.pdf}
-            \caption{Test log accuracy}
-            \label{fig:results:reselection:figures:accuracy:test:car}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the car dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:reselection:figures:car}
-\end{figure}
-
-Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plots for an example regression dataset (bike) as it relates to the reselection interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/bike.pdf}
-            \caption{Train log loss}
-            \label{fig:results:reselection:figures:loss:train:bike}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/bike.pdf}
-            \caption{Test log loss}
-            \label{fig:results:reselection:figures:loss:test:bike}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the bike dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:reselection:figures:bike}
-\end{figure}
-
-Figures~\ref{fig:results:reselection:figures:loss:train:car} and \ref{fig:results:reselection:figures:loss:train:bike} both show a smooth decline in training loss for all reselection interval configurations of the \acs{BHH}, but larger reselection interval configurations are able to provide better results than lower reselection intervals.
-This further supports the suggestion that exploitation of low-level \index{heuristic}heuristics is more important than exploration of low-level \index{heuristic}heuristics in this particular case.
-
-\section{Replay Window Size}\label{sec:results:replay}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{replay window size} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, five different replay window sizes are considered.
-These include replay window sizes of 1, 5, 10, 15, and 20.
-Experiments are denoted as such.
-
-As before, Table~\ref{tab:results:replay:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the replay window size variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average test loss and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-      \label{tab:results:replay:metrics:loss}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{r|ccccc}
-                                               & \multicolumn{5}{c}{\textbf{Replay - Average Test Loss}}                                                                                                                                                                                                                                         \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ .973,  .412,  .42}2.136 ($\pm$0.088)   & \cellcolor[rgb]{ .388,  .745,  .482}2.0424 ($\pm$0.47)  & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.135)    & \cellcolor[rgb]{ .863,  .878,  .506}2.0551 ($\pm$0.159) & \cellcolor[rgb]{ .976,  .455,  .427}2.1299 ($\pm$0.292) \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ .525,  .784,  .49}0.2676 ($\pm$0.016)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2687 ($\pm$0.014)    & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)  & \cellcolor[rgb]{ .992,  .722,  .482}0.2703 ($\pm$0.015) & \cellcolor[rgb]{ .388,  .745,  .482}0.2673 ($\pm$0.011) \\
-                  \textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2358 ($\pm$0.065)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2347 ($\pm$0.022) & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.019)  & \cellcolor[rgb]{ .996,  .839,  .502}0.2374 ($\pm$0.037) & \cellcolor[rgb]{ .965,  .91,  .514}0.2358 ($\pm$0.025)  \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .522,  .78,  .486}0.0568 ($\pm$0.02)   & \cellcolor[rgb]{ .388,  .745,  .482}0.0552 ($\pm$0.007) & \cellcolor[rgb]{ .973,  .412,  .42}0.0651 ($\pm$0.004)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0625 ($\pm$0.019)    & \cellcolor[rgb]{ .976,  .443,  .427}0.065 ($\pm$0.018)  \\
-                  \textbf{car}                 & \cellcolor[rgb]{ 1,  .878,  .51}0.1605 ($\pm$0.034)     & \cellcolor[rgb]{ .388,  .745,  .482}0.1537 ($\pm$0.05)  & \cellcolor[rgb]{ .733,  .843,  .502}0.1572 ($\pm$0.026) & \cellcolor[rgb]{ .973,  .412,  .42}0.1671 ($\pm$0.056)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1599 ($\pm$0.028)    \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .996,  .8,  .494}1.3315 ($\pm$0.66)    & \cellcolor[rgb]{ .918,  .894,  .51}1.2672 ($\pm$0.691)  & \cellcolor[rgb]{ 1,  .922,  .518}1.2983 ($\pm$0.534)    & \cellcolor[rgb]{ .388,  .745,  .482}1.0647 ($\pm$0.22)  & \cellcolor[rgb]{ .973,  .412,  .42}1.4342 ($\pm$1.399)  \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1028 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .749,  .486}0.1055 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.012)    & \cellcolor[rgb]{ .604,  .808,  .494}0.1034 ($\pm$0.011) & \cellcolor[rgb]{ .973,  .412,  .42}0.1074 ($\pm$0.012)  \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .988,  .663,  .471}0.0935 ($\pm$0.069) & \cellcolor[rgb]{ 1,  .922,  .518}0.0814 ($\pm$0.078)    & \cellcolor[rgb]{ .863,  .882,  .51}0.081 ($\pm$0.073)   & \cellcolor[rgb]{ .388,  .745,  .482}0.0794 ($\pm$0.063) & \cellcolor[rgb]{ .973,  .412,  .42}0.105 ($\pm$0.068)   \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .992,  .745,  .486}0.0979 ($\pm$0.017) & \cellcolor[rgb]{ .467,  .769,  .486}0.0944 ($\pm$0.015) & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.015) & \cellcolor[rgb]{ 1,  .922,  .518}0.0967 ($\pm$0.022)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1002 ($\pm$0.024)  \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .443,  .761,  .482}0.1577 ($\pm$0.295) & \cellcolor[rgb]{ .973,  .412,  .42}0.295 ($\pm$0.16)    & \cellcolor[rgb]{ .996,  .784,  .494}0.2411 ($\pm$0.546) & \cellcolor[rgb]{ .388,  .745,  .482}0.1514 ($\pm$0.192) & \cellcolor[rgb]{ 1,  .922,  .518}0.2208 ($\pm$0.349)    \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .722,  .839,  .498}0.0504 ($\pm$0.012) & \cellcolor[rgb]{ 1,  .922,  .518}0.0881 ($\pm$0.239)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.336) & \cellcolor[rgb]{ .973,  .412,  .42}0.4733 ($\pm$2.385)  & \cellcolor[rgb]{ 1,  .855,  .506}0.139 ($\pm$0.62)      \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .973,  .412,  .42}0.0596 ($\pm$0.003)  & \cellcolor[rgb]{ .576,  .8,  .49}0.0589 ($\pm$0.003)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .976,  .424,  .424}0.0596 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0594 ($\pm$0.003)    \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .996,  .792,  .494}0.2529 ($\pm$0.102) & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.103)    & \cellcolor[rgb]{ .42,  .753,  .482}0.2359 ($\pm$0.093)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2354 ($\pm$0.083) & \cellcolor[rgb]{ .973,  .412,  .42}0.2739 ($\pm$0.126)  \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}1.0876 ($\pm$0.026)  & \cellcolor[rgb]{ .388,  .745,  .482}1.0756 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}1.0827 ($\pm$0.022)    & \cellcolor[rgb]{ .98,  .522,  .443}1.0866 ($\pm$0.039)  & \cellcolor[rgb]{ .482,  .773,  .486}1.0767 ($\pm$0.022) \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Table \ref{tab:results:replay:metrics:rank} provides the average ranked performance, per dataset, for each of the \acs{BHH} replay window size configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all independent runs and epochs.
-The overall normalised average rank is provided at the end of the table.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-      \label{tab:results:replay:metrics:rank}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{r|ccccc}
-                                               & \multicolumn{5}{c}{\textbf{Replay - Average Rank}}                                                                                                                                                                                                                                              \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}3.0258 ($\pm$1.382)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6785 ($\pm$1.455) & \cellcolor[rgb]{ .973,  .412,  .42}3.1968 ($\pm$1.346)  & \cellcolor[rgb]{ .992,  .729,  .482}3.0903 ($\pm$1.385) & \cellcolor[rgb]{ .969,  .91,  .514}3.0086 ($\pm$1.45)   \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ .388,  .745,  .482}2.8742 ($\pm$1.385) & \cellcolor[rgb]{ 1,  .871,  .51}3.0151 ($\pm$1.497)     & \cellcolor[rgb]{ 1,  .922,  .518}2.9978 ($\pm$1.429)    & \cellcolor[rgb]{ .765,  .851,  .502}2.9505 ($\pm$1.297) & \cellcolor[rgb]{ .973,  .412,  .42}3.1624 ($\pm$1.443)  \\
-                  \textbf{bank}                & \cellcolor[rgb]{ .729,  .843,  .502}2.9484 ($\pm$1.46)  & \cellcolor[rgb]{ .992,  .722,  .482}3.057 ($\pm$1.473)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8602 ($\pm$1.344) & \cellcolor[rgb]{ 1,  .922,  .518}3.0172 ($\pm$1.42)     & \cellcolor[rgb]{ .973,  .412,  .42}3.1172 ($\pm$1.359)  \\
-                  \textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}2.9602 ($\pm$1.274)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7366 ($\pm$1.34)  & \cellcolor[rgb]{ .984,  .58,  .455}3.1452 ($\pm$1.448)  & \cellcolor[rgb]{ .894,  .89,  .51}2.9226 ($\pm$1.417)   & \cellcolor[rgb]{ .973,  .412,  .42}3.2355 ($\pm$1.527)  \\
-                  \textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.7054 ($\pm$1.357) & \cellcolor[rgb]{ .62,  .812,  .494}2.8376 ($\pm$1.39)   & \cellcolor[rgb]{ 1,  .882,  .51}3.0763 ($\pm$1.372)     & \cellcolor[rgb]{ .973,  .412,  .42}3.3269 ($\pm$1.463)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0538 ($\pm$1.409)    \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .98,  .545,  .447}3.2473 ($\pm$1.369)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3247 ($\pm$1.406)  & \cellcolor[rgb]{ .388,  .745,  .482}2.5935 ($\pm$1.372) & \cellcolor[rgb]{ .69,  .831,  .498}2.8075 ($\pm$1.384)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0269 ($\pm$1.411)    \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}2.7269 ($\pm$1.419) & \cellcolor[rgb]{ .992,  .753,  .486}3.0785 ($\pm$1.49)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1774 ($\pm$1.398)  & \cellcolor[rgb]{ .918,  .898,  .51}2.9892 ($\pm$1.386)  & \cellcolor[rgb]{ 1,  .922,  .518}3.028 ($\pm$1.337)     \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8054 ($\pm$1.493) & \cellcolor[rgb]{ .745,  .847,  .502}2.9151 ($\pm$1.381) & \cellcolor[rgb]{ 1,  .922,  .518}2.9914 ($\pm$1.408)    & \cellcolor[rgb]{ .996,  .776,  .49}3.0591 ($\pm$1.411)  & \cellcolor[rgb]{ .973,  .412,  .42}3.229 ($\pm$1.342)   \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}3.1548 ($\pm$1.301)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.407)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8548 ($\pm$1.45)  & \cellcolor[rgb]{ .992,  .757,  .486}3.0355 ($\pm$1.49)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.404)    \\
-                  \textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}3.072 ($\pm$1.376)     & \cellcolor[rgb]{ .984,  .627,  .463}3.1581 ($\pm$1.419) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.392)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6183 ($\pm$1.396) & \cellcolor[rgb]{ .808,  .867,  .506}2.9312 ($\pm$1.41)  \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ 1,  .863,  .51}3.0538 ($\pm$1.324)     & \cellcolor[rgb]{ .973,  .412,  .42}3.143 ($\pm$1.437)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0419 ($\pm$1.414)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8613 ($\pm$1.382) & \cellcolor[rgb]{ .502,  .776,  .486}2.8957 ($\pm$1.497) \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .984,  .561,  .451}3.172 ($\pm$1.372)  & \cellcolor[rgb]{ .62,  .812,  .494}2.843 ($\pm$1.244)   & \cellcolor[rgb]{ .388,  .745,  .482}2.6731 ($\pm$1.453) & \cellcolor[rgb]{ 1,  .922,  .518}3.1172 ($\pm$1.419)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1946 ($\pm$1.498)  \\
-                  \textbf{student performance} & \cellcolor[rgb]{ 1,  .922,  .518}3.0398 ($\pm$1.368)    & \cellcolor[rgb]{ .812,  .867,  .506}2.9226 ($\pm$1.411) & \cellcolor[rgb]{ .388,  .745,  .482}2.6548 ($\pm$1.403) & \cellcolor[rgb]{ .996,  .812,  .498}3.0935 ($\pm$1.323) & \cellcolor[rgb]{ .973,  .412,  .42}3.2892 ($\pm$1.487)  \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}3.1742 ($\pm$1.43)   & \cellcolor[rgb]{ .388,  .745,  .482}2.7323 ($\pm$1.456) & \cellcolor[rgb]{ .976,  .475,  .435}3.1581 ($\pm$1.418) & \cellcolor[rgb]{ 1,  .922,  .518}3.0419 ($\pm$1.356)    & \cellcolor[rgb]{ .706,  .835,  .498}2.8935 ($\pm$1.362) \\
-                  \midrule
-                  \textbf{avg rank}            & \cellcolor[rgb]{ 1,  .91,  .518}2.9972 ($\pm$1.389)     & \cellcolor[rgb]{ .388,  .745,  .482}2.9585 ($\pm$1.426) & \cellcolor[rgb]{ .651,  .82,  .494}2.9744 ($\pm$1.418)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9951 ($\pm$1.404)    & \cellcolor[rgb]{ .973,  .412,  .42}3.0745 ($\pm$1.43)   \\
-                  \midrule
-                  \textbf{normalised avg rank} & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
-            \end{tabular}%
-
-      }
-\end{table}%
-
-Tables \ref{tab:results:replay:metrics:loss} and \ref{tab:results:replay:metrics:rank} show that there is no clear overall best performing replay window size configuration of the \acs{BHH} for all datasets.
-In some cases, a replay window size of one yielded the best results.
-A replay window of one simply considers the last step in the training process.
-This means that memory of past performance actually had a negative impact on the training process for those particular cases.
-It should also be observed that the largest replay window size yielded the worst performance overall and also for the most datasets.
-This suggests that \index{heuristic}heuristic selection is more likely to benefit from short, recent observations in the training process.
-From these observations it can be concluded that past performances of the \index{heuristic}heuristics are not always beneficial to the training process, and that the replay window size is problem specific.
-Furthermore, it can be concluded that some problems require more exploration of the \index{heuristic}heuristic space, while other problem sets require more exploitation of low-level \index{heuristic}heuristics.
-
-Figure~\ref{fig:results:replay:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different replay window size configurations per dataset.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_replay/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots for the average ranks of the \acs{BHH} with varying replay window sizes per dataset, across all independent runs and epochs.}
-      \label{fig:results:replay:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:replay:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each replay window size configuration as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_replay/figures/cd/overall.pdf}
-      \caption{Critical difference plots for the average ranks of the \acs{BHH} with varying replay window sizes across all datasets, runs and epochs.}
-      \label{fig:results:replay:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:replay:descriptive:cd} shows no overall statistically significant difference in results for the various replay window size configurations as it relates to all datasets.
-
-Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test loss and accuracy plots for an example classification dataset (diabetic) as it relates to the replay window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/diabetic.pdf}
-            \caption{Train log loss}
-            \label{fig:results:replay:figures:loss:train:diabetic}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/diabetic.pdf}
-            \caption{Test log loss}
-            \label{fig:results:replay:figures:loss:test:diabetic}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_replay/figures/train/accuracy/diabetic.pdf}
-            \caption{Train log accuracy}
-            \label{fig:results:replay:figures:accuracy:train:diabetic}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_replay/figures/test/accuracy/diabetic.pdf}
-            \caption{Test log accuracy}
-            \label{fig:results:replay:figures:accuracy:test:diabetic}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:replay:figures:diabetic}
-\end{figure}
-
-Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plots for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/fish_toxicity.pdf}
-            \caption{Train log loss}
-            \label{fig:results:replay:figures:loss:train:fish_toxicity}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/fish_toxicity.pdf}
-            \caption{Test log loss}
-            \label{fig:results:replay:figures:loss:test:fish_toxicity}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:replay:figures:fish_toxicity}
-\end{figure}
-
-The divergence that can be seen in Figure~\ref{fig:results:replay:figures:loss:train:diabetic} and \ref{fig:results:replay:figures:loss:test:diabetic} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results, when an optimal solution has already been found.
-As mentioned before, an early stopping strategy as well as a move-acceptance strategy can be incorporated to avoid this effect.
-
-\section{Reanalysis Interval}\label{sec:results:reanalysis}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{reanalysis interval} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, five different reanalysis intervals are considered.
-These include reanalysis intervals of 1, 5, 10, 15, and 20.
-Experiments are denoted as such.
-
-As before, Table~\ref{tab:results:reanalysis:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the reanalysis interval variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average test loss and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-      \label{tab:results:reanalysis:metrics:loss}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{r|lllll}
-                                               & \multicolumn{5}{c}{\textbf{Reanalysis - Average Test Loss}}                                                                                                                                                                                                                                        \\
-                  \midrule
-                  \textbf{dataset}             & \multicolumn{1}{c}{\textbf{1}}                              & \multicolumn{1}{c}{\textbf{5}}                          & \multicolumn{1}{c}{\textbf{10}}                         & \multicolumn{1}{c}{\textbf{15}}                        & \multicolumn{1}{c}{\textbf{20}}                         \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.0571 ($\pm$0.102)        & \cellcolor[rgb]{ .388,  .745,  .482}2.0424 ($\pm$0.071) & \cellcolor[rgb]{ 1,  .898,  .514}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .973,  .412,  .42}2.0879 ($\pm$0.226) & \cellcolor[rgb]{ .518,  .78,  .486}2.0456 ($\pm$0.079)  \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2682 ($\pm$0.014)        & \cellcolor[rgb]{ .388,  .745,  .482}0.2637 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)  & \cellcolor[rgb]{ .98,  .525,  .443}0.2718 ($\pm$0.019) & \cellcolor[rgb]{ .584,  .8,  .49}0.2651 ($\pm$0.012)    \\
-                  \textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2599 ($\pm$0.114)      & \cellcolor[rgb]{ .698,  .831,  .498}0.2406 ($\pm$0.023) & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .984,  .624,  .463}0.254 ($\pm$0.047) & \cellcolor[rgb]{ .388,  .745,  .482}0.2353 ($\pm$0.025) \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0621 ($\pm$0.016)     & \cellcolor[rgb]{ 1,  .922,  .518}0.0627 ($\pm$0.021)    & \cellcolor[rgb]{ .984,  .584,  .455}0.0651 ($\pm$0.02)  & \cellcolor[rgb]{ .973,  .412,  .42}0.0663 ($\pm$0.023) & \cellcolor[rgb]{ .765,  .851,  .502}0.0625 ($\pm$0.02)  \\
-                  \textbf{car}                 & \cellcolor[rgb]{ 1,  .922,  .518}0.1597 ($\pm$0.042)        & \cellcolor[rgb]{ .388,  .745,  .482}0.1535 ($\pm$0.038) & \cellcolor[rgb]{ .749,  .847,  .502}0.1572 ($\pm$0.034) & \cellcolor[rgb]{ .973,  .412,  .42}0.1667 ($\pm$0.036) & \cellcolor[rgb]{ .984,  .58,  .455}0.1644 ($\pm$0.04)   \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}1.482 ($\pm$1.563)       & \cellcolor[rgb]{ .984,  .62,  .463}1.4074 ($\pm$1.558)  & \cellcolor[rgb]{ 1,  .922,  .518}1.2983 ($\pm$0.66)     & \cellcolor[rgb]{ .388,  .745,  .482}1.222 ($\pm$0.6)   & \cellcolor[rgb]{ .969,  .91,  .514}1.2944 ($\pm$0.832)  \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .961,  .91,  .514}0.1031 ($\pm$0.01)       & \cellcolor[rgb]{ 1,  .922,  .518}0.1033 ($\pm$0.008)    & \cellcolor[rgb]{ .988,  .694,  .475}0.1046 ($\pm$0.008) & \cellcolor[rgb]{ .973,  .412,  .42}0.1062 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.1004 ($\pm$0.009) \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .973,  .412,  .42}0.1083 ($\pm$0.1)        & \cellcolor[rgb]{ .988,  .675,  .471}0.1003 ($\pm$0.069) & \cellcolor[rgb]{ .388,  .745,  .482}0.081 ($\pm$0.069)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0927 ($\pm$0.069)   & \cellcolor[rgb]{ .451,  .761,  .482}0.0822 ($\pm$0.059) \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}0.0998 ($\pm$0.017)      & \cellcolor[rgb]{ .745,  .847,  .502}0.0953 ($\pm$0.017) & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .918,  .518}0.0963 ($\pm$0.029)   & \cellcolor[rgb]{ 1,  .922,  .518}0.0962 ($\pm$0.011)    \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.582 ($\pm$2.084)       & \cellcolor[rgb]{ .604,  .804,  .494}0.164 ($\pm$0.154)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2411 ($\pm$0.295)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1218 ($\pm$0.11) & \cellcolor[rgb]{ 1,  .882,  .514}0.2674 ($\pm$0.545)    \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .996,  .796,  .494}0.0548 ($\pm$0.241)     & \cellcolor[rgb]{ .973,  .412,  .42}0.1165 ($\pm$0.597)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ 1,  .922,  .518}0.0344 ($\pm$0.102)   & \cellcolor[rgb]{ .655,  .82,  .494}0.0181 ($\pm$0.059)  \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ 1,  .922,  .518}0.0597 ($\pm$0.003)        & \cellcolor[rgb]{ .769,  .855,  .502}0.0593 ($\pm$0.002) & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.06 ($\pm$0.004)   & \cellcolor[rgb]{ 1,  .918,  .518}0.0597 ($\pm$0.003)    \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .992,  .741,  .486}0.2331 ($\pm$0.083)     & \cellcolor[rgb]{ .725,  .839,  .498}0.2297 ($\pm$0.09)  & \cellcolor[rgb]{ .973,  .412,  .42}0.2359 ($\pm$0.102)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2315 ($\pm$0.063)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2274 ($\pm$0.098) \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0728 ($\pm$0.026)     & \cellcolor[rgb]{ 1,  .922,  .518}1.0818 ($\pm$0.028)    & \cellcolor[rgb]{ 1,  .871,  .51}1.0827 ($\pm$0.026)     & \cellcolor[rgb]{ .514,  .78,  .486}1.0747 ($\pm$0.026) & \cellcolor[rgb]{ .973,  .412,  .42}1.0909 ($\pm$0.042)  \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Table \ref{tab:results:reanalysis:metrics:rank} provides the average ranked performance, per dataset, for each of the \acs{BHH} reanalysis interval configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the reanalysis interval configurations, for all datasets, over all independent runs and epochs.
-The overall normalised average ranks are provided at the bottom of the table.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-      \label{tab:results:reanalysis:metrics:rank}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{r|ccccc}
-                                               & \multicolumn{5}{c}{\textbf{Reanalysis - Average Rank}}                                                                                                                                                                                                                                          \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{1}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.9849 ($\pm$1.397)    & \cellcolor[rgb]{ .988,  .69,  .475}3.0699 ($\pm$1.442)  & \cellcolor[rgb]{ .973,  .412,  .42}3.171 ($\pm$1.32)    & \cellcolor[rgb]{ .835,  .875,  .506}2.9441 ($\pm$1.445) & \cellcolor[rgb]{ .388,  .745,  .482}2.8301 ($\pm$1.443) \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9613 ($\pm$1.344)    & \cellcolor[rgb]{ .388,  .745,  .482}2.8387 ($\pm$1.438) & \cellcolor[rgb]{ .973,  .412,  .42}3.2559 ($\pm$1.402)  & \cellcolor[rgb]{ .992,  .765,  .49}3.0538 ($\pm$1.42)   & \cellcolor[rgb]{ .643,  .816,  .494}2.8903 ($\pm$1.43)  \\
-                  \textbf{bank}                & \cellcolor[rgb]{ .988,  .647,  .467}3.1161 ($\pm$1.432) & \cellcolor[rgb]{ 1,  .922,  .518}3.0452 ($\pm$1.383)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7355 ($\pm$1.398) & \cellcolor[rgb]{ .765,  .851,  .502}2.928 ($\pm$1.403)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1753 ($\pm$1.415)  \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .988,  .698,  .475}3.1409 ($\pm$1.258) & \cellcolor[rgb]{ .388,  .745,  .482}2.7581 ($\pm$1.391) & \cellcolor[rgb]{ .973,  .412,  .42}3.1946 ($\pm$1.365)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0978 ($\pm$1.498)    & \cellcolor[rgb]{ .478,  .769,  .486}2.8086 ($\pm$1.491) \\
-                  \textbf{car}                 & \cellcolor[rgb]{ 1,  .906,  .518}3.1237 ($\pm$1.423)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7237 ($\pm$1.358) & \cellcolor[rgb]{ .62,  .812,  .494}2.8763 ($\pm$1.299)  & \cellcolor[rgb]{ .973,  .412,  .42}3.1538 ($\pm$1.385)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1226 ($\pm$1.547)    \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}3.2452 ($\pm$1.305)  & \cellcolor[rgb]{ .996,  .824,  .502}3.072 ($\pm$1.391)  & \cellcolor[rgb]{ .388,  .745,  .482}2.7785 ($\pm$1.407) & \cellcolor[rgb]{ 1,  .922,  .518}3.029 ($\pm$1.425)     & \cellcolor[rgb]{ .624,  .812,  .494}2.8753 ($\pm$1.494) \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .992,  .725,  .482}3.1452 ($\pm$1.362) & \cellcolor[rgb]{ .894,  .89,  .51}3.0032 ($\pm$1.445)   & \cellcolor[rgb]{ .973,  .412,  .42}3.2172 ($\pm$1.364)  & \cellcolor[rgb]{ 1,  .922,  .518}3.1 ($\pm$1.409)       & \cellcolor[rgb]{ .388,  .745,  .482}2.5344 ($\pm$1.388) \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8398 ($\pm$1.369) & \cellcolor[rgb]{ .98,  .51,  .439}3.1215 ($\pm$1.471)   & \cellcolor[rgb]{ 1,  .922,  .518}3.0043 ($\pm$1.318)    & \cellcolor[rgb]{ .557,  .792,  .49}2.886 ($\pm$1.354)   & \cellcolor[rgb]{ .973,  .412,  .42}3.1484 ($\pm$1.526)  \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .976,  .416,  .424}3.3129 ($\pm$1.311) & \cellcolor[rgb]{ 1,  .922,  .518}2.9892 ($\pm$1.393)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6871 ($\pm$1.483) & \cellcolor[rgb]{ .404,  .749,  .482}2.6968 ($\pm$1.496) & \cellcolor[rgb]{ .973,  .412,  .42}3.314 ($\pm$1.236)   \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .98,  .522,  .443}3.1204 ($\pm$1.301)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.391)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1269 ($\pm$1.432)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6366 ($\pm$1.449) & \cellcolor[rgb]{ .894,  .89,  .51}3.0194 ($\pm$1.435)   \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ 1,  .922,  .518}2.9312 ($\pm$1.379)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1538 ($\pm$1.403)  & \cellcolor[rgb]{ .388,  .745,  .482}2.8473 ($\pm$1.384) & \cellcolor[rgb]{ .98,  .486,  .435}3.1215 ($\pm$1.453)  & \cellcolor[rgb]{ .796,  .863,  .506}2.9032 ($\pm$1.471) \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .937,  .902,  .514}2.9688 ($\pm$1.385) & \cellcolor[rgb]{ 1,  .922,  .518}3.0086 ($\pm$1.356)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6129 ($\pm$1.481) & \cellcolor[rgb]{ .992,  .761,  .49}3.1032 ($\pm$1.38)   & \cellcolor[rgb]{ .973,  .412,  .42}3.3065 ($\pm$1.378)  \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .89,  .89,  .51}2.9409 ($\pm$1.412)    & \cellcolor[rgb]{ .973,  .412,  .42}3.1849 ($\pm$1.38)   & \cellcolor[rgb]{ .388,  .745,  .482}2.771 ($\pm$1.41)   & \cellcolor[rgb]{ .98,  .561,  .451}3.1258 ($\pm$1.366)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9774 ($\pm$1.467)    \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8032 ($\pm$1.444) & \cellcolor[rgb]{ .976,  .914,  .514}2.9204 ($\pm$1.304) & \cellcolor[rgb]{ .973,  .412,  .42}3.2022 ($\pm$1.41)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9247 ($\pm$1.349)    & \cellcolor[rgb]{ .98,  .51,  .439}3.1495 ($\pm$1.517)   \\
-                  \midrule
-                  \textbf{avg rank}            & \cellcolor[rgb]{ .973,  .412,  .42}3.0453 ($\pm$1.374)  & \cellcolor[rgb]{ 1,  .922,  .518}2.999 ($\pm$1.403)     & \cellcolor[rgb]{ .388,  .745,  .482}2.9629 ($\pm$1.409) & \cellcolor[rgb]{ .773,  .855,  .502}2.9858 ($\pm$1.425) & \cellcolor[rgb]{ 1,  .871,  .51}3.0039 ($\pm$1.462)     \\
-                  \midrule
-                  \textbf{normalised avg rank} & \cellcolor[rgb]{ .973,  .412,  .42}5                    & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ .988,  .667,  .471}4                   \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Tables \ref{tab:results:reanalysis:metrics:loss} and \ref{tab:results:reanalysis:metrics:rank} show that there is no clear overall best performing reanalysis interval configuration of the \acs{BHH} for all datasets.
-
-It should be noted that the configuration and results for the reanalysis interval configurations should be considered along with the reselection interval configurations as reselection is based on the outcome of the reanalysis step.
-Furthermore, the reanalysis interval configurations should also be considered along with the replay window size, as the replay window size determines the number of performance log samples to reanalyse.
-For the \acs{BHH} baseline configuration, the reselection and reanalysis interval hyper-parameters have default values of 10, and the replay window size also has a default value of 10.
-These values are deliberately chosen so that there is a balance between the different hyper-parameters from which empirical conclusions can be made.
-
-Furthermore, the smaller the reanalysis interval, the more frequently the \acs{BHH} resets concentration parameters.
-The smaller the replay window size, the less performance samples in the performance log are considered for reanalysis.
-A replay window size of one yields a case where only the last executed step is considered for reanalysis and thus provides a short-sighted view on the relevance of past performance.
-As such, reselection is based only on the most recent performance of each selected \index{heuristic}heuristic.
-However, if the reanalysis interval is larger than the replay window size, the \acs{BHH} does not update its beliefs fast enough, and as a result, \index{heuristic}heuristic performance evidence is lost.
-
-Figure~\ref{fig:results:reanalysis:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the performance of different reanalysis interval configurations, per dataset.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_reanalysis/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots for the average ranks of the \acs{BHH} with varying reanalysis intervals per dataset, across all independent runs and epochs.}
-      \label{fig:results:reanalysis:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:reanalysis:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each reanalysis interval configuration as it relates to all datasets, across all independent runs and epochs.
-From Figure~\ref{fig:results:reanalysis:descriptive:cd}, it can be concluded that the best reanalysis interval is problem specific.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_reanalysis/figures/cd/overall.pdf}
-      \caption{Critical difference plots for the average ranks of the \acs{BHH} with varying reanalysis intervals across all datasets, runs and epochs.}
-      \label{fig:results:reanalysis:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:reanalysis:descriptive:cd} shows no overall statistically significant difference in results for the various reanalysis interval configurations as it relates to all datasets.
-
-Similar to before, Figure~\ref{fig:results:reanalysis:figures:mushroom} provides the train and test loss and accuracy plots for an example classification dataset (mushroom) as it relates to the reanalysis interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/mushroom.pdf}
-            \caption{Train log loss}
-            \label{fig:results:reanalysis:figures:loss:train:mushroom}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/mushroom.pdf}
-            \caption{Test log loss}
-            \label{fig:results:reanalysis:figures:loss:test:mushroom}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/accuracy/mushroom.pdf}
-            \caption{Train log accuracy}
-            \label{fig:results:reanalysis:figures:accuracy:train:mushroom}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/accuracy/mushroom.pdf}
-            \caption{Test log accuracy}
-            \label{fig:results:reanalysis:figures:accuracy:test:mushroom}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:reanalysis:figures:mushroom}
-\end{figure}
-
-Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the reanalysis interval experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\begin{figure}[htb]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/parkinsons.pdf}
-            \caption{Train log loss}
-            \label{fig:results:reanalysis:figures:loss:train:parkinsons}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/parkinsons.pdf}
-            \caption{Test log loss}
-            \label{fig:results:reanalysis:figures:loss:test:parkinsons}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:reanalysis:figures:parkinsons}
-\end{figure}
-
-The divergence that can be seen in Figure~\ref{fig:results:reanalysis:figures:loss:train:mushroom} and \ref{fig:results:reanalysis:figures:loss:test:mushroom} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results when an optimal solution has already been found.
-As mentioned before, an early stopping strategy as well as a move-acceptance strategy can be incorporated to avoid this effect.
-
-\section{Burn In}\label{sec:results:burn_in}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{burn in} window size hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-Five different burn in window sizes are considered.
-These include burn in window sizes of 0, 5, 10, 15, and 20.
-Experiments are denoted as such.
-
-As a reminder, the burn in window size is a hyper-parameter that is borrowed from the \acs{MCMC} algorithm, and provides a window whereby exploration is encouraged in order to obtain sufficient samples of \index{heuristic}heuristic performance evidence for statistical inference.
-
-As before, Table~\ref{tab:results:burn_in:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the burn in window size variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average test loss and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-      \label{tab:results:burn_in:metrics:loss}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{r|ccccc}
-                                               & \multicolumn{5}{c}{\textbf{Burn In - Average Test Loss}}                                                                                                                                                                                                                             \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{0}                                               & \textbf{5}                                           & \textbf{10}                                          & \textbf{15}                                          & \textbf{20}                                          \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ .392,  .745,  .482}2.0587 (+-0.088)     & \cellcolor[rgb]{ .388,  .745,  .482}2.0583 (+-0.181) & \cellcolor[rgb]{ 1,  .922,  .518}2.0961 (+-0.168)    & \cellcolor[rgb]{ 1,  .878,  .51}2.1454 (+-0.365)     & \cellcolor[rgb]{ .973,  .412,  .42}2.6753 (+-2.18)   \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}0.2729 (+-0.016)        & \cellcolor[rgb]{ .851,  .878,  .506}0.2719 (+-0.02)  & \cellcolor[rgb]{ .388,  .745,  .482}0.2688 (+-0.014) & \cellcolor[rgb]{ .988,  .694,  .475}0.2784 (+-0.017) & \cellcolor[rgb]{ .973,  .412,  .42}0.2851 (+-0.029)  \\
-                  \textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}0.2456 (+-0.065)        & \cellcolor[rgb]{ .388,  .745,  .482}0.2373 (+-0.033) & \cellcolor[rgb]{ .996,  .804,  .498}0.2514 (+-0.109) & \cellcolor[rgb]{ .784,  .859,  .502}0.2427 (+-0.033) & \cellcolor[rgb]{ .973,  .412,  .42}0.2703 (+-0.056)  \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0651 (+-0.02)      & \cellcolor[rgb]{ .443,  .761,  .482}0.0678 (+-0.024) & \cellcolor[rgb]{ 1,  .922,  .518}0.0929 (+-0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1109 (+-0.043) & \cellcolor[rgb]{ .973,  .412,  .42}0.1383 (+-0.034)  \\
-                  \textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 (+-0.034)     & \cellcolor[rgb]{ .627,  .812,  .494}0.164 (+-0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1745 (+-0.037)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1883 (+-0.067)  & \cellcolor[rgb]{ .992,  .71,  .478}0.1803 (+-0.039)  \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .698,  .831,  .498}1.2983 (+-0.66)      & \cellcolor[rgb]{ .388,  .745,  .482}1.1216 (+-0.582) & \cellcolor[rgb]{ 1,  .922,  .518}1.4701 (+-1.161)    & \cellcolor[rgb]{ .984,  .604,  .459}1.9918 (+-3.645) & \cellcolor[rgb]{ .973,  .412,  .42}2.2996 (+-3.589)  \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .992,  .765,  .49}0.1046 (+-0.008)      & \cellcolor[rgb]{ .69,  .831,  .498}0.1026 (+-0.009)  & \cellcolor[rgb]{ .388,  .745,  .482}0.1009 (+-0.01)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1043 (+-0.007)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1052 (+-0.009)  \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}0.081 (+-0.069)         & \cellcolor[rgb]{ .753,  .851,  .502}0.0772 (+-0.057) & \cellcolor[rgb]{ .388,  .745,  .482}0.0714 (+-0.045) & \cellcolor[rgb]{ .973,  .412,  .42}0.1136 (+-0.059)  & \cellcolor[rgb]{ .98,  .557,  .451}0.1044 (+-0.093)  \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 (+-0.017)     & \cellcolor[rgb]{ .596,  .804,  .494}0.096 (+-0.015)  & \cellcolor[rgb]{ .992,  .757,  .486}0.1036 (+-0.037) & \cellcolor[rgb]{ 1,  .922,  .518}0.0997 (+-0.021)    & \cellcolor[rgb]{ .973,  .412,  .42}0.1116 (+-0.034)  \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .996,  .78,  .49}0.2411 (+-0.295)       & \cellcolor[rgb]{ .388,  .745,  .482}0.1472 (+-0.134) & \cellcolor[rgb]{ .973,  .412,  .42}0.2717 (+-0.462)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2291 (+-0.376)    & \cellcolor[rgb]{ .663,  .824,  .498}0.1842 (+-0.189) \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 (+-0.012)     & \cellcolor[rgb]{ .976,  .42,  .424}0.1068 (+-0.3)    & \cellcolor[rgb]{ .616,  .808,  .494}0.0262 (+-0.057) & \cellcolor[rgb]{ .973,  .412,  .42}0.1075 (+-0.256)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0612 (+-0.108)    \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 (+-0.003)     & \cellcolor[rgb]{ 1,  .922,  .518}0.0599 (+-0.003)    & \cellcolor[rgb]{ .745,  .847,  .502}0.0594 (+-0.003) & \cellcolor[rgb]{ .984,  .627,  .463}0.0644 (+-0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.0676 (+-0.015)  \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 (+-0.102)     & \cellcolor[rgb]{ .733,  .843,  .502}0.2801 (+-0.127) & \cellcolor[rgb]{ 1,  .922,  .518}0.314 (+-0.137)     & \cellcolor[rgb]{ .988,  .631,  .463}0.3623 (+-0.139) & \cellcolor[rgb]{ .973,  .412,  .42}0.3988 (+-0.133)  \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ 1,  .922,  .518}1.0827 (+-0.026)        & \cellcolor[rgb]{ .396,  .745,  .482}1.0791 (+-0.021) & \cellcolor[rgb]{ .388,  .745,  .482}1.079 (+-0.03)   & \cellcolor[rgb]{ .988,  .686,  .475}1.086 (+-0.029)  & \cellcolor[rgb]{ .973,  .412,  .42}1.0897 (+-0.034)  \\
-            \end{tabular}%
-
-      }
-\end{table}%
-
-From Table \ref{tab:results:burn_in:metrics:loss} a noticeable pattern can be observed.
-Generally, it is found that a small burn in window size produces better results than larger burn in window sizes.
-The largest burn in window size of 20 produced the worst results in nine out of thirteen datasets.
-Some exceptions include the mushroom and the iris datasets.
-Notice that burn in window sizes smaller than the default reanalysis interval, reselection interval and replay window size of 10, generally produced the best results.
-However, Table \ref{tab:results:burn_in:metrics:loss} does not provide a clear view of the overall performance produced by different burn in window size configurations for the entire training process.
-
-In order to obtain a better view of the overall performance produced by different burn in window size configurations for the entire training process, Table \ref{tab:results:burn_in:metrics:rank} provides the average ranked performance, per dataset, for each of the \acs{BHH} burn in configurations.
-Similar to before, the performance rank is calculated as the average rank produced by the burn in window size configurations, for all datasets, over all independent runs and epochs.
-The overall normalised average rank is provided at the bottom of the table.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-      \label{tab:results:burn_in:metrics:rank}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            % Table generated by Excel2LaTeX from sheet 'rank'
-            \begin{tabular}{r|ccccc}
-                                               & \multicolumn{5}{c}{\textbf{Burn In - Average Rank}}                                                                                                                                                                                                                                             \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{0}                                              & \textbf{5}                                              & \textbf{10}                                             & \textbf{15}                                             & \textbf{20}                                             \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}2.9151 ($\pm$1.395)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6935 ($\pm$1.393) & \cellcolor[rgb]{ 1,  .922,  .518}2.9172 ($\pm$1.384)    & \cellcolor[rgb]{ .788,  .859,  .502}2.8398 ($\pm$1.352) & \cellcolor[rgb]{ .973,  .412,  .42}3.6344 ($\pm$1.357)  \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ 1,  .922,  .518}2.9097 ($\pm$1.441)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6817 ($\pm$1.427) & \cellcolor[rgb]{ .624,  .812,  .494}2.7699 ($\pm$1.344) & \cellcolor[rgb]{ .973,  .412,  .42}3.372 ($\pm$1.314)   & \cellcolor[rgb]{ .98,  .529,  .443}3.2667 ($\pm$1.412)  \\
-                  \textbf{bank}                & \cellcolor[rgb]{ .388,  .745,  .482}2.7301 ($\pm$1.321) & \cellcolor[rgb]{ .816,  .867,  .506}2.8194 ($\pm$1.335) & \cellcolor[rgb]{ 1,  .922,  .518}2.857 ($\pm$1.485)     & \cellcolor[rgb]{ 1,  .878,  .51}2.9312 ($\pm$1.384)     & \cellcolor[rgb]{ .973,  .412,  .42}3.6624 ($\pm$1.339)  \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}1.9237 ($\pm$0.981) & \cellcolor[rgb]{ .545,  .788,  .49}2.1806 ($\pm$1.024)  & \cellcolor[rgb]{ 1,  .922,  .518}2.9237 ($\pm$1.274)    & \cellcolor[rgb]{ .992,  .729,  .482}3.5054 ($\pm$1.186) & \cellcolor[rgb]{ .973,  .412,  .42}4.4667 ($\pm$0.851)  \\
-                  \textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}2.3624 ($\pm$1.231) & \cellcolor[rgb]{ .533,  .784,  .49}2.5882 ($\pm$1.425)  & \cellcolor[rgb]{ 1,  .922,  .518}3.2978 ($\pm$1.392)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3796 ($\pm$1.271)  & \cellcolor[rgb]{ .976,  .459,  .431}3.372 ($\pm$1.401)  \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}2.4054 ($\pm$1.358) & \cellcolor[rgb]{ .604,  .808,  .494}2.7011 ($\pm$1.358) & \cellcolor[rgb]{ 1,  .902,  .518}3.2398 ($\pm$1.372)    & \cellcolor[rgb]{ 1,  .922,  .518}3.2323 ($\pm$1.326)    & \cellcolor[rgb]{ .973,  .412,  .42}3.4215 ($\pm$1.396)  \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}3.0634 ($\pm$1.459)    & \cellcolor[rgb]{ .388,  .745,  .482}2.7935 ($\pm$1.402) & \cellcolor[rgb]{ .447,  .761,  .482}2.8204 ($\pm$1.513) & \cellcolor[rgb]{ .996,  .796,  .494}3.1022 ($\pm$1.346) & \cellcolor[rgb]{ .973,  .412,  .42}3.2204 ($\pm$1.295)  \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}2.8161 ($\pm$1.33)  & \cellcolor[rgb]{ .808,  .867,  .506}2.8495 ($\pm$1.383) & \cellcolor[rgb]{ 1,  .922,  .518}2.8645 ($\pm$1.409)    & \cellcolor[rgb]{ .973,  .412,  .42}3.3774 ($\pm$1.398)  & \cellcolor[rgb]{ .988,  .698,  .475}3.0925 ($\pm$1.471) \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}2.6903 ($\pm$1.384) & \cellcolor[rgb]{ .91,  .894,  .51}2.9516 ($\pm$1.318)   & \cellcolor[rgb]{ 1,  .922,  .518}2.9968 ($\pm$1.442)    & \cellcolor[rgb]{ .996,  .82,  .498}3.0581 ($\pm$1.344)  & \cellcolor[rgb]{ .973,  .412,  .42}3.3032 ($\pm$1.51)   \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .922,  .898,  .51}2.9473 ($\pm$1.461)  & \cellcolor[rgb]{ 1,  .922,  .518}2.972 ($\pm$1.367)     & \cellcolor[rgb]{ .973,  .412,  .42}3.1903 ($\pm$1.449)  & \cellcolor[rgb]{ .388,  .745,  .482}2.771 ($\pm$1.369)  & \cellcolor[rgb]{ .984,  .58,  .455}3.1194 ($\pm$1.387)  \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}2.2065 ($\pm$1.249) & \cellcolor[rgb]{ .863,  .882,  .51}2.9376 ($\pm$1.298)  & \cellcolor[rgb]{ 1,  .902,  .514}3.1613 ($\pm$1.297)    & \cellcolor[rgb]{ 1,  .922,  .518}3.1441 ($\pm$1.401)    & \cellcolor[rgb]{ .973,  .412,  .42}3.5226 ($\pm$1.501)  \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}2.2796 ($\pm$1.282) & \cellcolor[rgb]{ 1,  .922,  .518}2.8892 ($\pm$1.247)    & \cellcolor[rgb]{ .816,  .867,  .506}2.7065 ($\pm$1.314) & \cellcolor[rgb]{ .984,  .616,  .459}3.3968 ($\pm$1.417) & \cellcolor[rgb]{ .973,  .412,  .42}3.728 ($\pm$1.33)    \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.1452 ($\pm$1.205) & \cellcolor[rgb]{ .741,  .843,  .502}2.6946 ($\pm$1.403) & \cellcolor[rgb]{ 1,  .922,  .518}3.0968 ($\pm$1.352)    & \cellcolor[rgb]{ .984,  .561,  .451}3.4581 ($\pm$1.354) & \cellcolor[rgb]{ .973,  .412,  .42}3.6054 ($\pm$1.231)  \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .925,  .898,  .51}2.9699 ($\pm$1.437)  & \cellcolor[rgb]{ 1,  .922,  .518}3.0108 ($\pm$1.304)    & \cellcolor[rgb]{ .388,  .745,  .482}2.6634 ($\pm$1.419) & \cellcolor[rgb]{ .988,  .659,  .471}3.1247 ($\pm$1.398) & \cellcolor[rgb]{ .973,  .412,  .42}3.2312 ($\pm$1.447)  \\
-                  \midrule
-                  \textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}2.5975 ($\pm$1.376) & \cellcolor[rgb]{ .671,  .824,  .498}2.7688 ($\pm$1.353) & \cellcolor[rgb]{ 1,  .922,  .518}2.9647 ($\pm$1.404)    & \cellcolor[rgb]{ .988,  .694,  .475}3.1923 ($\pm$1.367) & \cellcolor[rgb]{ .973,  .412,  .42}3.4747 ($\pm$1.402)  \\
-                  \midrule
-                  \textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                   & \cellcolor[rgb]{ .694,  .831,  .498}2                   & \cellcolor[rgb]{ 1,  .922,  .518}3                      & \cellcolor[rgb]{ .988,  .667,  .471}4                   & \cellcolor[rgb]{ .973,  .412,  .42}5                    \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Table \ref{tab:results:burn_in:metrics:rank} shows that, in general, a configuration where there is no burn in produces the overall best ranked performance across all datasets.
-Furthermore, it can be observed that performance degrades with larger burn in window sizes.
-This can be explained from the fact that most of the training progress that is made, is done early in the training process.
-The faster the \acs{BHH} is able to start learning and exploiting \index{heuristic}heuristics and solutions, the better.
-
-Note that the \acs{BHH} is configured with a reselection interval of one, until the burn in window has been exhausted, after which the actual reselection interval applies.
-This means that reselection occurs at each step during the burn in window, but the reanalysis interval and replay window size remain intact.
-This observation agrees with previous results, where the \acs{BHH} prefers to start exploiting \index{heuristic}heuristics and solutions as soon as possible.
-Furthermore, this agrees with previous results, where large reselection intervals are found to produce the best results, giving \index{heuristic}heuristics sufficient time to progress and smooth out training steps.
-
-Recall that the gradient-based \index{heuristic}heuristics generally produce the best results overall.
-Most of the gradient-based \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool implement some form of momentum and exponentially average state parameters.
-When reselection occurs frequently in succession, these gradient-based \index{heuristic}heuristics struggle to produce smooth update steps.
-As a result, the \acs{BHH} can produce delayed convergence and thus leads to worse performance when considering the entire training process.
-
-Figure~\ref{fig:results:burn_in:descriptive:descriptive} provides an illustration of the descriptive plots for the different \acs{BHH} configurations as it relates to the burn in window size configurations, per dataset.
-Figure~\ref{fig:results:burn_in:descriptive:descriptive} shows that there is mostly a linear correlation between performance results and burn in window sizes, with minor exceptions to some datasets.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_burn_in/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots for the average ranks of the \acs{BHH} with varying burn in values per dataset, across all independent runs and epochs.}
-      \label{fig:results:burn_in:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:burn_in:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each burn in window size configuration as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_burn_in/figures/cd/overall.pdf}
-      \caption{Critical difference plots for the average ranks of the \acs{BHH} with varying burn in values across all datasets, runs and epochs.}
-      \label{fig:results:burn_in:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:burn_in:descriptive:cd} shows with statistical certainty that a small burn in configuration of the \acs{BHH} generally produce overall better results than larger burn in configurations, as it relates to all datasets.
-
-Similar to before, Figure~\ref{fig:results:burn_in:figures:mushroom} provides the train and test loss and accuracy plots for an example classification dataset (mushroom) as it relates to the burn in window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_burn_in/figures/train/loss/mushroom.pdf}
-            \caption{Train log loss}
-            \label{fig:results:burn_in:figures:loss:train:mushroom}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/mushroom.pdf}
-            \caption{Test log loss}
-            \label{fig:results:burn_in:figures:loss:test:mushroom}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_burn_in/figures/train/accuracy/mushroom.pdf}
-            \caption{Train log accuracy}
-            \label{fig:results:burn_in:figures:accuracy:train:mushroom}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_burn_in/figures/test/accuracy/mushroom.pdf}
-            \caption{Test log accuracy}
-            \label{fig:results:burn_in:figures:accuracy:test:mushroom}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:burn_in:figures:mushroom}
-\end{figure}
-
-Figure~\ref{fig:results:burn_in:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the burn in window size experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_burn_in/figures/train/loss/parkinsons.pdf}
-            \caption{Train log loss}
-            \label{fig:results:burn_in:figures:loss:train:parkinsons}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_burn_in/figures/test/loss/parkinsons.pdf}
-            \caption{Test log loss}
-            \label{fig:results:burn_in:figures:loss:test:parkinsons}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the burn in window size hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:burn_in:figures:parkinsons}
-\end{figure}
-
-The divergence that can be seen in Figures~\ref{fig:results:burn_in:figures:loss:train:mushroom} and \ref{fig:results:burn_in:figures:loss:test:mushroom} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results, when an optimal solution has already been found.
-As mentioned before, an early stopping strategy as well as a move-acceptance strategy can be incorporated to avoid this effect.
-
-\section{Normalisation}\label{sec:results:normalise}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{normalisation} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, the normalisation hyper-parameter is a flag that enables or disables normalisation of the concentration parameters in an attempt to provide more exploration in the \index{heuristic}heuristic space.
-The experiments are denoted as \textit{true} where normalisation is enabled, and \textit{false} where normalisation is disabled.
-
-As before, Table~\ref{tab:results:normalise:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for variants of the \acs{BHH} that was implemented where normalisation is enabled and disabled.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average test loss and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-      \label{tab:results:normalise:metrics:loss}%
-      \par\bigskip
-      \resizebox{0.6\textwidth}{!}{
-            \begin{tabular}{r|cc}
-                                               & \multicolumn{2}{c}{\textbf{Normalisation - Average Test Loss}}                                                           \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{false}                                                 & \textbf{true}                                           \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088)        & \cellcolor[rgb]{ .973,  .412,  .42}2.0936 ($\pm$0.231)  \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)         & \cellcolor[rgb]{ .388,  .745,  .482}0.2704 ($\pm$0.017) \\
-                  \textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)         & \cellcolor[rgb]{ .388,  .745,  .482}0.2374 ($\pm$0.042) \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0651 ($\pm$0.02)         & \cellcolor[rgb]{ .973,  .412,  .42}0.0689 ($\pm$0.03)   \\
-                  \textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)        & \cellcolor[rgb]{ .973,  .412,  .42}0.1721 ($\pm$0.038)  \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}1.2983 ($\pm$0.66)         & \cellcolor[rgb]{ .973,  .412,  .42}1.5051 ($\pm$1.93)   \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}0.1046 ($\pm$0.008)         & \cellcolor[rgb]{ .388,  .745,  .482}0.1021 ($\pm$0.009) \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}0.081 ($\pm$0.069)         & \cellcolor[rgb]{ .973,  .412,  .42}0.0868 ($\pm$0.069)  \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}0.0941 ($\pm$0.017)         & \cellcolor[rgb]{ .388,  .745,  .482}0.0931 ($\pm$0.019) \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 ($\pm$0.295)         & \cellcolor[rgb]{ .388,  .745,  .482}0.2358 ($\pm$0.333) \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012)        & \cellcolor[rgb]{ .973,  .412,  .42}0.0455 ($\pm$0.216)  \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003)        & \cellcolor[rgb]{ .973,  .412,  .42}0.0598 ($\pm$0.004)  \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 ($\pm$0.102)        & \cellcolor[rgb]{ .973,  .412,  .42}0.2522 ($\pm$0.098)  \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)        & \cellcolor[rgb]{ .973,  .412,  .42}1.0831 ($\pm$0.045)  \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Table \ref{tab:results:normalise:metrics:rank} provides the average ranked performance, per dataset, with normalisation enabled and disabled.
-Similar to before, the performance rank is calculated as the average rank produced by the normalisation configurations, for all datasets, over all independent runs and epochs.
-The overall normalised average ranks are provided at the bottom of the table.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-      \label{tab:results:normalise:metrics:rank}%
-      \par\bigskip
-      \resizebox{0.6\textwidth}{!}{
-            \begin{tabular}{rcc}
-                  \multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Normalisation - Average Rank}}                                                           \\
-                  \midrule
-                  \multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                            & \textbf{true}                                           \\
-                  \midrule
-                  \multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4935 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5065 ($\pm$0.5)    \\
-                  \multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4892 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5108 ($\pm$0.5)    \\
-                  \multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5484 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4516 ($\pm$0.498) \\
-                  \multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .388,  .745,  .482}1.4978 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5022 ($\pm$0.5)    \\
-                  \multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.4258 ($\pm$0.495)   & \cellcolor[rgb]{ .973,  .412,  .42}1.5742 ($\pm$0.495)  \\
-                  \multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4753 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5247 ($\pm$0.5)    \\
-                  \multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5505 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4495 ($\pm$0.498) \\
-                  \multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.5054 ($\pm$0.5)      & \cellcolor[rgb]{ .388,  .745,  .482}1.4946 ($\pm$0.5)   \\
-                  \multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.472 ($\pm$0.499)    & \cellcolor[rgb]{ .973,  .412,  .42}1.528 ($\pm$0.499)   \\
-                  \multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5645 ($\pm$0.496)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4355 ($\pm$0.496) \\
-                  \multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4323 ($\pm$0.496)   & \cellcolor[rgb]{ .973,  .412,  .42}1.5667 ($\pm$0.496)  \\
-                  \multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.4 ($\pm$0.49)       & \cellcolor[rgb]{ .973,  .412,  .42}1.6 ($\pm$0.49)      \\
-                  \multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.3892 ($\pm$0.488)   & \cellcolor[rgb]{ .973,  .412,  .42}1.6108 ($\pm$0.488)  \\
-                  \multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.5473 ($\pm$0.498)    & \cellcolor[rgb]{ .388,  .745,  .482}1.4527 ($\pm$0.498) \\
-                  \midrule
-                  \multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4851 ($\pm$0.5)     & \cellcolor[rgb]{ .973,  .412,  .42}1.5148 ($\pm$0.5)    \\
-                  \midrule
-                  \textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                     & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\
-            \end{tabular}%
-
-      }
-\end{table}%
-
-Table \ref{tab:results:normalise:metrics:rank} shows that, in general, there is no obvious difference in the outcomes of the \acs{BHH} when normalisation is enabled or disabled.
-This suggests that the normalisation flag is problem specific.
-Since the normalisation hyper-parameter provides a mechanism for the \acs{BHH} to explore more in the \index{heuristic}heuristic space, with the intent of finding better solutions, it can be concluded that some datasets require more exploration, while others require more exploitation.
-However, a better suggestion can be made from the observation of previous results.
-The \acs{BHH} has a default replay window size of 10, yielding a small window of memory to maintain \index{heuristic}heuristic performance evidence in the performance log.
-Normalisation of the concentration parameters then yield an insignificant difference in the outcome as the concentration parameters never reach high values.
-Furthermore, previous results have shown that the best results are obtained from exploitation of \index{heuristic}heuristics and solutions, in comparison to exploration.
-
-Figure~\ref{fig:results:normalise:descriptive:descriptive} provides an illustration of the descriptive plots for the \acs{BHH} configurations with the normalisation hyper-parameter enabled and disabled, per dataset.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_normalise/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots for the average ranks of the \acs{BHH} with normalisation toggled per dataset, across all independent runs and epochs.}
-      \label{fig:results:normalise:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:normalise:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for normalisation configurations that are enabled and disabled, as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_normalise/figures/cd/overall.pdf}
-      \caption{Critical difference plots for the average ranks of the \acs{BHH} with normalisation toggled across all datasets, runs and epochs.}
-      \label{fig:results:normalise:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:normalise:descriptive:cd} shows no statistical difference in the outcomes of the normalisation configurations of the \acs{BHH}.
-This further supports the suggestion that the use of the normalisation hyper-parameter is problem specific or that the effects of the normalisation hyper-parameter is not realised for small replay window sizes.
-
-Similar to before, Figure~\ref{fig:results:normalise:figures:abalone} provides the train and test loss and accuracy plots for an example classification dataset (abalone) as it relates to the normalisation experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_normalise/figures/train/loss/abalone.pdf}
-            \caption{Train log loss}
-            \label{fig:results:normalise:figures:loss:train:abalone}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/abalone.pdf}
-            \caption{Test log loss}
-            \label{fig:results:normalise:figures:loss:test:abalone}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_normalise/figures/train/accuracy/abalone.pdf}
-            \caption{Train log accuracy}
-            \label{fig:results:normalise:figures:accuracy:train:abalone}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_normalise/figures/test/accuracy/abalone.pdf}
-            \caption{Test log accuracy}
-            \label{fig:results:normalise:figures:accuracy:test:abalone}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the abalone dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:normalise:figures:abalone}
-\end{figure}
-
-Figure~\ref{fig:results:normalise:figures:bike} provides the train and test loss plots for an example regression dataset (bike) as it relates to the normalisation experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_normalise/figures/train/loss/bike.pdf}
-            \caption{Train log loss}
-            \label{fig:results:normalise:figures:loss:train:bike}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_normalise/figures/test/loss/bike.pdf}
-            \caption{Test log loss}
-            \label{fig:results:normalise:figures:loss:test:bike}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the normalisation hyper-parameter toggled on the bike dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:normalise:figures:bike}
-\end{figure}
-
-\section{Discounted Rewards}\label{sec:results:discounted_rewards}
-
-This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{discounted rewards} hyper-parameter.
-Brief discussions follow and illustrations are provided for visual aid.
-As a reminder, the discounted rewards hyper-parameter is a flag that enables or disables discounted rewards of the pseudo counts that are added to concentration parameters in an attempt to provide control over the effects of past performances of the low-level \index{heuristic}heuristics.
-
-As a reminder, the discounted rewards mechanism is implemented such that pseudo counts for past performances that achieved successful credit allocations are exponentially decayed into the past.
-The default discounted rewards decay rate is set to 0.5.
-
-As before, Table~\ref{tab:results:discounted_rewards:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for variants of the \acs{BHH} that was implemented where discounted rewards is enabled and disabled.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average test loss and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}
-      \label{tab:results:discounted_rewards:metrics:loss}%
-      \par\bigskip
-      \resizebox{0.7\textwidth}{!}{
-            \begin{tabular}{r|cc}
-                                               & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Test Loss}}                                                           \\
-                  \midrule
-                  \textbf{dataset}             & \textbf{false}                                                      & \textbf{true}                                           \\
-                  \midrule
-                  \textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088)             & \cellcolor[rgb]{ .973,  .412,  .42}2.0789 ($\pm$0.102)  \\
-                  \textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)              & \cellcolor[rgb]{ .388,  .745,  .482}0.2693 ($\pm$0.011) \\
-                  \textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)              & \cellcolor[rgb]{ .388,  .745,  .482}0.2349 ($\pm$0.041) \\
-                  \textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0651 ($\pm$0.02)              & \cellcolor[rgb]{ .973,  .412,  .42}0.0676 ($\pm$0.027)  \\
-                  \textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)             & \cellcolor[rgb]{ .973,  .412,  .42}0.1672 ($\pm$0.037)  \\
-                  \textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}1.2983 ($\pm$0.66)              & \cellcolor[rgb]{ .973,  .412,  .42}1.3457 ($\pm$1.419)  \\
-                  \textbf{fish toxicity}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1046 ($\pm$0.008)             & \cellcolor[rgb]{ .973,  .412,  .42}0.1053 ($\pm$0.008)  \\
-                  \textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}0.081 ($\pm$0.069)              & \cellcolor[rgb]{ .973,  .412,  .42}0.0928 ($\pm$0.079)  \\
-                  \textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}0.0941 ($\pm$0.017)             & \cellcolor[rgb]{ .973,  .412,  .42}0.0972 ($\pm$0.017)  \\
-                  \textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 ($\pm$0.295)              & \cellcolor[rgb]{ .388,  .745,  .482}0.1833 ($\pm$0.259) \\
-                  \textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012)             & \cellcolor[rgb]{ .973,  .412,  .42}0.0479 ($\pm$0.203)  \\
-                  \textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003)             & \cellcolor[rgb]{ .973,  .412,  .42}0.06 ($\pm$0.002)    \\
-                  \textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 ($\pm$0.102)             & \cellcolor[rgb]{ .973,  .412,  .42}0.2408 ($\pm$0.086)  \\
-                  \textbf{wine quality}        & \cellcolor[rgb]{ .973,  .412,  .42}1.0827 ($\pm$0.026)              & \cellcolor[rgb]{ .388,  .745,  .482}1.0792 ($\pm$0.039) \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Table \ref{tab:results:discounted_rewards:metrics:rank} provides the average ranked performance, per dataset, with discounted rewards enabled and disabled.
-Similar to before, the performance rank is calculated as the average rank produced by the discounted rewards configurations, for all datasets, over all independent runs and epochs.
-
-\begin{table}[htb]
-      \centering
-      \caption{Empirical results showing average rank and statistics for discounted rewards toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
-      \label{tab:results:discounted_rewards:metrics:rank}%
-      \par\bigskip
-      \resizebox{0.7\textwidth}{!}{
-            \begin{tabular}{rcc}
-                  \multicolumn{1}{r|}{}                             & \multicolumn{2}{c}{\textbf{Discounted Rewards - Average Rank}}                                                           \\
-                  \midrule
-                  \multicolumn{1}{r|}{\textbf{dataset}}             & \textbf{false}                                                 & \textbf{true}                                           \\
-                  \midrule
-                  \multicolumn{1}{r|}{\textbf{abalone}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4914 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5086 ($\pm$0.5)    \\
-                  \multicolumn{1}{r|}{\textbf{air quality}}         & \cellcolor[rgb]{ .388,  .745,  .482}1.4613 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5387 ($\pm$0.499)  \\
-                  \multicolumn{1}{r|}{\textbf{bank}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5161 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4839 ($\pm$0.5)   \\
-                  \multicolumn{1}{r|}{\textbf{bike}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
-                  \multicolumn{1}{r|}{\textbf{car}}                 & \cellcolor[rgb]{ .388,  .745,  .482}1.428 ($\pm$0.495)         & \cellcolor[rgb]{ .973,  .412,  .42}1.572 ($\pm$0.495)   \\
-                  \multicolumn{1}{r|}{\textbf{diabetic}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4699 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5301 ($\pm$0.499)  \\
-                  \multicolumn{1}{r|}{\textbf{fish toxicity}}       & \cellcolor[rgb]{ .973,  .412,  .42}1.5011 ($\pm$0.5)           & \cellcolor[rgb]{ .388,  .745,  .482}1.4989 ($\pm$0.5)   \\
-                  \multicolumn{1}{r|}{\textbf{forest fires}}        & \cellcolor[rgb]{ .388,  .745,  .482}1.4742 ($\pm$0.5)          & \cellcolor[rgb]{ .973,  .412,  .42}1.5258 ($\pm$0.5)    \\
-                  \multicolumn{1}{r|}{\textbf{housing}}             & \cellcolor[rgb]{ .388,  .745,  .482}1.4237 ($\pm$0.494)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5763 ($\pm$0.494)  \\
-                  \multicolumn{1}{r|}{\textbf{iris}}                & \cellcolor[rgb]{ .973,  .412,  .42}1.5903 ($\pm$0.492)         & \cellcolor[rgb]{ .388,  .745,  .482}1.4097 ($\pm$0.492) \\
-                  \multicolumn{1}{r|}{\textbf{mushroom}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.3946 ($\pm$0.489)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5806 ($\pm$0.494)  \\
-                  \multicolumn{1}{r|}{\textbf{parkinsons}}          & \cellcolor[rgb]{ .388,  .745,  .482}1.371 ($\pm$0.483)         & \cellcolor[rgb]{ .973,  .412,  .42}1.629 ($\pm$0.483)   \\
-                  \multicolumn{1}{r|}{\textbf{student performance}} & \cellcolor[rgb]{ .388,  .745,  .482}1.4398 ($\pm$0.497)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5602 ($\pm$0.497)  \\
-                  \multicolumn{1}{r|}{\textbf{wine quality}}        & \cellcolor[rgb]{ .973,  .412,  .42}1.557 ($\pm$0.497)          & \cellcolor[rgb]{ .388,  .745,  .482}1.443 ($\pm$0.497)  \\
-                  \midrule
-                  \multicolumn{1}{r|}{\textbf{avg rank}}            & \cellcolor[rgb]{ .388,  .745,  .482}1.4728 ($\pm$0.499)        & \cellcolor[rgb]{ .973,  .412,  .42}1.5254 ($\pm$0.499)  \\
-                  \midrule
-                  \textbf{normalised avg rank}                      & \cellcolor[rgb]{ .388,  .745,  .482}1                          & \cellcolor[rgb]{ .973,  .412,  .42}2                    \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Table \ref{tab:results:discounted_rewards:metrics:rank} shows that, in general, there is no obvious difference in the outcomes of the \acs{BHH} when discounted rewards is enabled or disabled.
-Although this could suggest that the discounted rewards hyper-parameter is problem specific, a better suggestion supports the findings from Section \ref{sec:results:normalise}.
-These findings suggest that manipulation of the concentration parameters yield insignificant differences in the outcomes of performance, as a small replay window size of 10 is used by default.
-
-In general, it is found that the online learning approach, followed by the \acs{BHH} yields very little room to learn from.
-This is supported by the fact that most of the significant performance gains are made in the early stages of training after which exploitation of \index{heuristic}heuristics and solutions later in the training process is shown to produce the best results.
-
-Figure~\ref{fig:results:discounted_rewards:descriptive:descriptive} provides an illustration of the descriptive plots for the \acs{BHH} configurations with the discounted rewards hyper-parameter enabled and disabled, per dataset.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/descriptive/descriptive.pdf}
-      \caption{Descriptive plots for the average ranks of the \acs{BHH} with discounted rewards toggled per datasets, across all independent runs and epochs.}
-      \label{fig:results:discounted_rewards:descriptive:descriptive}
-\end{figure}
-
-Figure~\ref{fig:results:discounted_rewards:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for discounted rewards configurations that are enabled and disabled, as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/cd/overall.pdf}
-      \caption{Critical difference plots for the average ranks of the \acs{BHH} with discounted rewards toggled across all datasets, runs and epochs.}
-      \label{fig:results:discounted_rewards:descriptive:cd}
-\end{figure}
-
-Figure~\ref{fig:results:discounted_rewards:descriptive:cd} shows no statistically significant difference in the outcomes of the discounted rewards configurations of the \acs{BHH}.
-This further supports the suggestion that the effects of discounted rewards is not realised for small replay window sizes.
-
-Similar to before, Figure~\ref{fig:results:discounted_rewards:figures:wine_quality} provides the train and test loss and accuracy plots for an example classification dataset (wine quality) as it relates to the discounted rewards experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/loss/wine_quality.pdf}
-            \caption{Train log loss}
-            \label{fig:results:discounted_rewards:figures:loss:train:wine_quality}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/wine_quality.pdf}
-            \caption{Test log loss}
-            \label{fig:results:discounted_rewards:figures:loss:test:wine_quality}
-      \end{subfigure}
-      \par\bigskip
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/accuracy/wine_quality.pdf}
-            \caption{Train log accuracy}
-            \label{fig:results:discounted_rewards:figures:accuracy:train:wine_quality}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/accuracy/wine_quality.pdf}
-            \caption{Test log accuracy}
-            \label{fig:results:discounted_rewards:figures:accuracy:test:wine_quality}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the wine quality dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:discounted_rewards:figures:wine_quality}
-\end{figure}
-
-Figure~\ref{fig:results:discounted_rewards:figures:housing} provides the train and test loss plots for an example regression dataset (housing) as it relates to the discounted rewards experimental group.
-As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/train/loss/housing.pdf}
-            \caption{Train log loss}
-            \label{fig:results:discounted_rewards:figures:loss:train:housing}
-      \end{subfigure}
-      \begin{subfigure}{0.5\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{bhh_discounted_rewards/figures/test/loss/housing.pdf}
-            \caption{Test log loss}
-            \label{fig:results:discounted_rewards:figures:loss:test:housing}
-      \end{subfigure}
-      \par\bigskip
-      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with the discounted rewards hyper-parameter toggled on the housing dataset over 30 epochs, illustrated in log scale.}
-      \label{fig:results:discounted_rewards:figures:housing}
-\end{figure}
-
-\section{Summary}\label{sec:results:summary}
+\subsection{Summary}\label{sec:results:summary}
 

### 2023-01-23 article/sections/08-results.tex
✨ (article): Conclusion done

@@
 
-The methodology presented a number of experimental groups to conduct.
-The experimental groups that were identified include a case study on the behaviour of the \acs{BHH} during training, and an empirical comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics.
-This section provides the outcomes of the empirical processes and provides results on all the experiments that have been conducted.
+This section provides the results of all the experiments that have been conducted.
 Detailed discussions follow on the outcomes of each experiment.
@@
 The output of the statistical analysis that yielded the results is provided in Appendix \ref{app:statistical_analysis}.
-The remainder of the chapter is structured as follows:
-
-\begin{itemize}
-	\item \textbf{Section \ref{sec:results:overview}} provides a brief overview of the outcomes of the empirical process and highlights key aspects to observe in the results.
-
-	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}.
-Illustrations are provided to show the change in parameter values to illustrate the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.
-
-	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics on all datasets.
-Three variants of the \acs{BHH} are included in these results.
-These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes \acp{MH} in the \index{heuristic pool}heuristic pool.
-
-\end{itemize}
 
@@
 
-Furthermore, the case study focuses on three variants of the \acs{BHH}.
-These include the baseline configuration, as was provided in Chapter \ref{chap:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}).
+The case study focuses on three variants of the \acs{BHH}.
+These include the baseline configuration, as was provided in Section \ref{sec:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}).
 Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}).
@@
 These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all.
-This section is structured as follows:
-
-\begin{itemize}
-	\item \textbf{Section \ref{sec:results:case_study:performance_metrics}} provides illustrations and discussions around the outcomes of the performance metrics as obtained by the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:case_study:concentration_parameters}} provides illustrations and discussions around the changes in concentration parameter values as a result of the learning mechanism implemented by the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probability distribution of \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:case_study:prior_selec_prob}} provides illustrations and discussions around the changes in the \textit{prior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.
-
-	\item \textbf{Section \ref{sec:results:case_study:posterior_selec_prob}} provides illustrations and discussions around the changes in the \textit{posterior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.
-
-\end{itemize}
 
@@
 Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process.
-Consider a case where all five entities in the entity pool are allocated the same heuristic and that a the replay window size of 10 is used.
-Then for all ten samples defined in the performance log, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.
 
@@
 The main observation to make from Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
-The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Chapter \ref{chap:bhh}.
+The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Section \ref{sec:bhh}.
 As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
@@
 \end{figure}
-
-\subsection{Summary}\label{sec:results:summary}
-
-This section provided the results of the empirical process that was described in Chapter \ref{chap:methodology}.
-Three experimental groups were designed.
-These experimental groups include a case study on the behaviour of the \acs{BHH} as it relates to an example dataset (iris).
-Furthermore, an experimental group that compares the performance of the \acs{BHH} to standalone, low-level \index{heuristic}heuristics was included, and finally, an experimental group that compares the effects of various hyper-parameters on the outcomes of the \acs{BHH} was also included.
-The empirical results for each of these experimental groups were presented in detail.
-
-In general, it was found that the \acs{BHH} is able to successfully train the underlying \acp{FFNN}.
-Detailed analysis and discussions of the empirical results were provided along with illustrations for visual aid.
-Where possible, detailed discussions were presented that explain the reasons behind the outcomes that were produced.
-Throughout, various suggestions were made to improve on the implementations made in this dissertation.
-
-Finally, all results that were presented were retrieved from statistical analysis which yield statistical certainty in the results and outcomes observed.

### 2023-01-23 article/sections/09-conclusion.tex
✨ (article): Conclusion done

--- 2022-12-10 dissertation/chapters/09-conclusion.tex
@@
-\chapter{Conclusion}
-\label{chap:conclusion}
-
-\begin{quotation}
-      ``I am sorry to have made such a long speech, but I did not have time to make a shorter one.''
-\end{quotation}
-\begin{flushright}
-      - Winston Churchill
-\end{flushright}
-
-This chapter provides a summary of the research that was done in this dissertation.
-The research objectives were set out in Chapter \ref{chap:introduction} and are concluded in this chapter.
-Furthermore, this chapter provides a summary of the results and findings from the empirical process and provides future research opportunities.
-The remainder of the chapter is structured as follows:
-
-\begin{itemize}
-      \item \textbf{Section \ref{sec:conclusion:research_goals}} provides a summary of the research intent and provides a review of the problem statement, objectives, and motivations behind the research.
-
-      \item \textbf{Section \ref{sec:conclusion:background_info}} summarises the background information that was covered.
-
-      \item \textbf{Section \ref{sec:conclusion:bhh}} provides a brief summary of the \ac{BHH} and its implementation.
-
-      \item \textbf{Section \ref{sec:conclusion:methodology}} provides a brief summary of the methodology and the empirical process that was followed.
-
-      \item \textbf{Section \ref{sec:conclusion:results}} summarises the research findings. This section is broken down into the various experimental groups that were executed.
-
-      \item \textbf{Section \ref{sec:conclusion:further_research}} provides suggestions for future research opportunities.
-
-      \item \textbf{Section \ref{sec:conclusion:documentation_and_data}} provides a brief discussion on supporting material related to the research, as made available by the authors.
-
-      \item \textbf{Section \ref{sec:conclusion:summary}} provides a brief summary of the chapter.
-\end{itemize}
-
-\section{Summary of Research Intent}
-\label{sec:conclusion:research_goals}
-
-This section briefly reviews the problem statement, motivations, and research objectives that was set out in Chapter \ref{chap:introduction} of this dissertation.
-
-\subsection{Review of Problem Statement}
-\label{sec:conclusion:research_goals:problem_statement}
+\section{Conclusion}
+\label{sec:conclusion}
 
 The main area of focus for the research done in this dissertation stems from the problem statement, which identified the difficult and tedious problem of selecting the best \index{heuristic}heuristic for training \acp{FFNN}.
-This process is often non-trivial and time-consuming.
-There is no easy way to know which \index{heuristic}heuristic to select to train \acp{FFNN}.
-Traditionally, an iterative approach of trial-and-error was followed.
-This process involves a tedious process of carefully considering and selecting candidate \index{heuristic}heuristics, whereby each candidate \index{heuristic}heuristic is then empirically tested and evaluated.
-This process is often executed at the expense of the researcher's resources.
+The research presented in this article identified the possibility of using a different approach, referred to as \acp{HH}, to automate the \index{heuristic}heuristic selection process.
 
-\subsection{Review of Research Motivation}
-\label{sec:conclusion:research_goals:motivations}
-
-The research presented in this dissertation identified the possibility of using a different approach, referred to as \acp{HH}, to automate the \index{heuristic}heuristic selection process.
-\acp{HH} are high-level search algorithms that search in the \index{heuristic}heuristic space, whereby low-level \index{heuristic}heuristics search in the solution space.
-\acp{HH} have been shown to provide a general solution to the \index{heuristic}heuristic selection process.
-The benefit that such an approach provides is that it automates the \index{heuristic}heuristic selection process.
-This approach saves researchers time and potentially produce a solution that could generalise to multiple problems.
-
-Investigation was done into the landscapes of existing solutions to train \acp{FFNN} as well as \acp{HH}.
-Though there exists many applications where \acp{HH} are used for optimisation, there are little to no published work on using \acp{HH} to train \acp{FFNN}.
-The only work that was found include the work by~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021}.
-
-\subsection{Review of Research Objectives}
-\label{sec:conclusion:research_goals:research_objectives}
-
-Existing techniques from other problem domains were considered.
-\acs{RL}, meta-learning and probabilistic learning approached were considered.
-Bayesian probability theory showed promise.
 This research then set out to develop a novel high-level \index{heuristic}heuristic that utilises probability theory in an online learning setting to drive the automatic \index{heuristic}heuristic selection process.
 As such, the \acs{BHH} was conceptualised.
-The research objectives were defined and were addressed as follows:
 
-\begin{itemize}
-      \item A literature study was conducted on all related topics that are relevant to the development of the \acs{BHH} and is provided in Chapters \ref{chap:anns} to \ref{chap:probability}.
+A literature study was conducted on all related topics that are relevant to the development of the \acs{BHH}.
 The literature study included background information on \acs{ANN}, existing low-level \index{heuristic}heuristics, meta-learning, \acp{HH}, probability theory, and Bayesian statistics.
-Detailed discussions were provided on every topic and was supported by visual illustrations and mathematical derivations.
 
-      \item A novel \acs{BHH} that can be used to automate the \index{heuristic}heuristic selection process was proposed in detail and was implemented.
+A novel \acs{BHH} that can be used to automate the \index{heuristic}heuristic selection process was proposed in detail and was implemented.
 The \acs{BHH} follows an approach that includes a selective and perturbative element in an online learning setting.
@@
 
-      \item An empirical process was designed and the detail of the implementation for the empirical process and the \acs{BHH} was provided.
+An empirical process was designed and the detail of the implementation for the empirical process and the \acs{BHH} was provided.
+An empirical study was conducted to show that the \ac{BHH} is able to train \acp{FFNN} effectively on a number of different datasets.
+An empirical study was conducted to study the behavioural characteristics of the \acs{BHH}.
+An empirical study was conducted to critically evaluate the performance of the \acs{BHH} compared to traditional, low-level, standalone \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.
 
-      \item An empirical study was conducted to show that the \ac{BHH} is able to train \acp{FFNN} effectively on a number of different datasets.
+Results from the empirical process were statistically analysed over multiple runs and provided statistical significance.
+These results were discussed in detail and was supported through visual illustrations.
 
-      \item An empirical study was conducted to study the behavioural characteristics of the \acs{BHH}.
-
-      \item An empirical study was conducted to critically evaluate the performance of the \acs{BHH} compared to traditional, low-level, standalone \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.
-
-      \item An empirical study was conducted to evaluate variants of the \acs{BHH} to study the impact of various hyper-parameters on the outcomes of the \ac{BHH}.
-
-      \item Results from the empirical process were statistically analysed over multiple runs and provided statistical significance.
-These results were discussed in detail and was supported through visual illustrations.
-\end{itemize}
-
-The research objectives set out in this dissertation were extensive.
-Each of these research objectives have been successfully executed as indicated in the list above.
-From the findings made in this dissertation, many different opportunities for future research were identified.
-
-\section{Summary of Background Information}
-\label{sec:conclusion:background_info}
-
-Chapters \ref{chap:anns} to \ref{chap:probability} provided the reader with the relevant background information that is necessary to develop the novel \acs{BHH}.
-Chapter~\ref{chap:anns} provided background information on \acp{ANN}.
-All the components that make up the \acs{AN} were provided and is followed by discussions on \acp{FFNN}.
-Chapter~\ref{chap:heuristics} provided background information on various low-level heuristics that are designed to train \acp{FFNN}.
-A number of gradient-based \index{heuristic}heuristics and \acp{MH} were presented in detail.
-Chapter~\ref{chap:hhs} provided background information and literature reviews on \acp{HH}.
-Meta-learning is discussed and a \acs{HH} classification scheme, developed by \citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, was discussed in detail.
-Chapter~\ref{chap:probability} provided background information and mathematical derivations on probability theory and Bayesian statistics.
-Various probability distributions were provided along with their conjugate priors.
-\acs{MLE} and \acs{MAP} were presented in detail along with mathematical breakdowns.
-
-From the aforementioned chapters, it can be concluded that the necessary background information was provided as set out in the research objectives of this dissertation.
-
-\section{Summary of The Bayesian Hyper-Heuristic}
-\label{sec:conclusion:bhh}
-
-The main contribution from this dissertation is the development of a novel \acf{BHH}.
-Chapter \ref{chap:bhh} provided the details on the concept and implementation of the \ac{BHH}.
-Various design decisions and hyper-parameters that could affect the outcomes of the \ac{BHH} were presented.
-
-It was shown that the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level \index{heuristic}heuristics in an online learning fashion.
-\index{heuristic}Heuristics are selected for each entity in a population of entities that each implement a candidate solution to the underlying \acs{FFNN}.
-The \acs{BHH} uses a Bayesian probabilistic model to drive the \index{heuristic}heuristic selection process.
-\acs{MAP} was derived for the probabilistic model and is used as the mechanism by which the \acs{BHH} is optimised, yielding the learning capability of the \acs{BHH}.
-
-Furthermore, it is shown that \index{heuristic}heuristic selection alone is not sufficient and that a mechanism of transition between \index{heuristic}heuristics is needed as they are selected for each entity in the population.
-Entity and \index{heuristic}heuristic state and state-manipulation formed the cornerstone of this topic.
-Perturbation of \index{heuristic}heuristics and solutions are achieved through a technique that deconstructs \index{heuristic}heuristics into their initialisation and update steps.
-The update operations for each heuristic were derived as movement equations borrowed from the field of physics.
-This technique allows for the proxying of update step operations as they are required by different \index{heuristic}heuristics.
-
-Detailed discussions were provided on a number of hyper-parameters that each contribute to the trade-off between \index{heuristic}heuristic and solution exploration and exploitation.
-These hyper-parameters include the \index{heuristic pool}\textit{heuristic pool} configuration, the \textit{population size}, the \textit{credit assignment strategy} used, the \textit{reselection interval}, the \textit{replay window size}, the \textit{reanalysis interval}, the \textit{burn in window size}, \textit{normalisation} of concentration parameters and \textit{discounted rewards} as assigned by the credit assignment strategy.
-A \acs{BHH} baseline configuration was identified with default values for each of the hyper-parameters.
-
-It was mentioned that the \acs{BHH}, implemented in this dissertation, does not implement a move-acceptance strategy that rejects heuristic progressions if they do not improve on the current best solution.
-Throughout the presentation of empirical results, it is recommended that this technique be investigated and implemented in further research.
-
-\section{Summary of Methodology}
-\label{sec:conclusion:methodology}
-
-The research objectives defined a number of empirical tests to be executed.
-Each one of the empirical tests is referred to as an experimental group.
-Various experimental groups have been identified and are listed below:
-
-\begin{itemize}
-      \item An experimental group that provides a case-study on the behaviour of the \ac{BHH} as it relates to training of a \acs{FFNN} on an example dataset (iris), in order to understand the workings of the \acs{BHH}, and to determine if the \acs{BHH} is able to successfully train \acp{FFNN}.
-Three different configurations of the \acs{BHH} configuration were implemented.
-This includes the default \acs{BHH} baseline configuration, the \acs{BHH} baseline configuration where the replay window size is set to 250, and the \acs{BHH} baseline configuration which utilises the \textit{symmetric} credit assignment strategy.
-
-      \item An experimental group that provides a comparative analysis between the performance of the \acs{BHH} baseline configuration and low-level, standalone \index{heuristic}heuristics when training \acp{FFNN} on a number of datasets.
-
-      \item An experimental group that provides a comparative analysis between variants of the \ac{BHH} that investigate the effects of various hyper-parameters on the outcomes of the \acs{BHH}.
-These variants include:
-
-            \begin{itemize}
-                  \item The \acs{BHH} baseline configuration with different \index{heuristic pool}heuristic pool configurations.
-Three different \index{heuristic pool}heuristic pool configurations were implemented.
-These configurations include a configuration with all the low-level \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool, a configuration with only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration with only \acp{MH} in the \index{heuristic pool}heuristic pool.
-
-                  \item The \acs{BHH} baseline configuration with different population sizes. Five different population sizes were implemented including 5, 10, 15, 20, and 25.
-
-                  \item The \acs{BHH} baseline configuration with different credit assignment strategies.
-Five different credit assignment strategies were implemented including the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies.
-
-                  \item The \acs{BHH} baseline configuration with different reselection intervals. Five different reselection intervals were implemented including 1, 5, 10, 15, and 20.
-
-                  \item The \acs{BHH} baseline configuration with different reanalysis window sizes. Five different reanalysis intervals were implemented including 1, 5, 10, 15, and 20.
-
-                  \item The \acs{BHH} baseline configuration with different replay window sizes. Five different replay window sizes were implemented including 1, 5, 10, 15, and 20.
-
-                  \item The \acs{BHH} baseline configuration with different burn in window sizes. Five different burn in window sizes were implemented including 0, 5, 10, 15, and 20.
-
-                  \item The \acs{BHH} baseline configuration where normalisation of pseudo counts for concentration parameters, as derived from credit allocations in the performance log, are enabled and disabled.
-
-                  \item The \acs{BHH} baseline configuration where discounted rewards of pseudo counts for concentration parameters, as derived from credit allocations in the performance log, are enabled and disabled.
-            \end{itemize}
-\end{itemize}
-
-Each experimental group was executed against a set of fourteen datasets, consisting of regression and classification problems, split between uni- and multimodal problems.
-Each experimental group was repeated over 30 runs for statistical certainty.
-The statistical analysis process was discussed and the ANOVA, post hoc Tukey, independent T-test and Kruskal-Wallis statistical tests formed part of the statistical tests that were conducted.
-
-All experimental groups were run for a maximum of 30 epochs in order to allow for the studying of the \ac{BHH} even after training has converged and overfitting has occurred.
-The maximum epoch strategy yielded a training process that is longer than what was empirically found to be necessary.
-This also meant that no early stopping strategy was used.
-Future research opportunities should incorporate an early stopping strategy of the training process.
-
-\section{Summary of Results}
+\subsection{Summary of Results}
 \label{sec:conclusion:results}
 
-This section provides a summary of the results obtained from each of the experimental groups that were executed. This section is structured as follows:
-
-\begin{itemize}
-      \item \textbf{Section \ref{sec:conclusion:results:summary:case_study}} provides a summary of the results for the experimental group that executed a case study on the behaviour of the \acs{BHH} on an example dataset.
-
-      \item \textbf{Section \ref{sec:conclusion:results:summary:standalone}} provides a summary of the results for the experimental group that compares the performance of the \acs{BHH} baseline configuration with low-level, standalone \index{heuristic}heuristics, across all datasets.
-
-      \item \textbf{Section \ref{sec:conclusion:results:summary:heuristic_pool}} provides a summary of the results for the experimental group that investigates the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the \acs{BHH}, across all datasets.
-
-      \item \textbf{Section \ref{sec:conclusion:results:summary:population_size}} provides a summary of the results for the experimental group that investigates the effects of the \textit{population size} hyper-parameter on the \acs{BHH}, across all datasets.
-
-      \item \textbf{Section \ref{sec:conclusion:results:summary:credit}} provides a summary of the results for the experimental group that investigates the effects of the \textit{credit assignment strategy} hyper-parameter on the \acs{BHH}, across all datasets.
-
-      \item \textbf{Section \ref{sec:conclusion:results:summary:reselection}} provides a summary of the results for the experimental group that investigates the effects of the \textit{reselection interval} hyper-parameter on the \acs{BHH}, across all datasets.
-
-      \item \textbf{Section \ref{sec:conclusion:results:summary:replay}} provides a summary of the results for the experimental group that investigates the effects of the \textit{replay window size} hyper-parameter on the \acs{BHH}, across all datasets.
-
-      \item \textbf{Section \ref{sec:conclusion:results:summary:reanalysis}} provides a summary of the results for the experimental group that investigates the effects of the \textit{reanalysis interval} hyper-parameter on the \acs{BHH}, across all datasets.
-
-      \item \textbf{Section \ref{sec:conclusion:results:summary:burn_in}} provides a summary of the results for the experimental group that investigates the effects of the \textit{burn in window size} hyper-parameter on the \acs{BHH}, across all datasets.
-
-      \item \textbf{Section \ref{sec:conclusion:results:summary:normalise}} provides a summary of the results for the experimental group that investigates the effects of the \textit{normalisation} hyper-parameter on the \acs{BHH}, across all datasets.
-
-      \item \textbf{Section \ref{sec:conclusion:results:summary:discounted_rewards}} provides a summary of the results for the experimental group that investigates the effects of the \textit{discounted rewards} hyper-parameter on the \acs{BHH}, across all datasets.
-\end{itemize}
-
-\subsection{Behavioural Case Study}
-\label{sec:conclusion:results:summary:case_study}
-
-For this experimental group it was found that the \ac{BHH} is able to train a \acf{FFNN} relatively well.
-Detailed analysis was provided for various state parameters maintained by the \acs{BHH}.
-These include the concentration parameters for different heuristics, the probability distribution of \index{heuristic}heuristic selection probabilities, prior heuristic selection probabilities and posterior heuristic selection probabilities.
+For the behavioural case study of the \acs{BHH} it was found that the \ac{BHH} is able to train a \acf{FFNN} relatively well.
 It was shown that the \ac{BHH} is able to learn and that the \acs{BHH} is able to exploit small performance biases as it relates to \index{heuristic}heuristic selection.
 This enables the \acs{BHH} to select the correct \index{heuristic}heuristics to apply to the correct entities at the correct time in the training process.
-
-Various illustrations of the train and test loss plots, as it relates to training of a \acs{FFNN} on the iris dataset, have been provided.
-Furthermore, various illustrations on the changes of the \acs{BHH} state parameters were provided for visual aid.
 
@@
 
-\subsection{\acs{BHH} Baseline vs. Low-Level Heuristics}
-\label{sec:conclusion:results:summary:standalone}
-
-For this experimental group, three different configurations of the \acs{BHH} baseline configuration were implemented.
+For the experimental group that compares the \acs{BHH} baseline with a number of  low-level heuristics, three different configurations of the \acs{BHH} baseline configuration were implemented.
 These configurations vary in the type of \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool.
-The \textit{bhh\_all} configuration included all low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool.
-The \textit{bhh\_gd} configuration included only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the \textit{bhh\_mh} configuration included only \acp{MH} in the \index{heuristic pool}heuristic pool.
 
@@
 
-Furthermore, it was shown that the \acs{BHH} provides a mechanism whereby prior expert knowledge can be injected, before training starts.
+Finally, it was shown that the \acs{BHH} provides a mechanism whereby prior expert knowledge can be injected, before training starts.
 Future research can exploit this knowledge and provide a significant bias towards \index{heuristic}heuristics that are known to perform well on particular problem types.
-
-\subsection{Heuristic pool}
-\label{sec:conclusion:results:summary:heuristic_pool}
-
-For this experimental group, the same three \index{heuristic pool}heuristic pool variants as outlined for the \acs{BHH} behavioural case study, was implemented.
-These variants are denoted as \textit{all}, \textit{gd}, and \textit{mh}.
-This experimental group then provided an opportunity to look at the effects of the \index{heuristic pool}heuristic pool hyper-parameter in more detail.
-
-As with the experimental group that compares the performance of the \acs{BHH} baseline configuration with low-level, standalone \index{heuristic}heuristics, it was found that the \textit{gd} configuration performed significantly better than the \textit{all} and \textit{mh} configurations overall, across all datasets.
-
-The benefits of using meta-heuristics in the heuristic pool was not realised in this dissertation, since the gradient-based low-level \index{heuristic}heuristics, as well as the \textit{gd} configuration produced the best overall performance, across all datasets.
-
-\subsection{Population Size}
-\label{sec:conclusion:results:summary:population_size}
-
-For this experimental group, five different population sizes were evaluated.
-These included population sizes of 5, 10, 15, 20, and 25.
-It was found that lower population sizes yielded better results on the majority of datasets, while only some datasets prefer larger population sizes.
-However, overall it was shown that the population size hyper-parameter is problem specific.
-Illustrations of the train and test loss and accuracy plots for some example datasets were provided.
-Some divergence in training loss was observed and was attributed to selection of \index{heuristic}heuristics that yield sub-optimal results after an optimal solution has already been found.
-As before, a move-acceptance strategy and an early stopping strategy can be incorporated to avoid this effect.
-
-\subsection{Credit Assignment Strategy}
-\label{sec:conclusion:results:summary:credit}
-
-For this experimental group, five different credit assignment strategies were evaluated.
-These included the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies.
-No clear overall difference in performance was observed for the various credit assignment strategies.
-For the majority of cases, a particular non-symmetric credit assignment strategy yielded the best performance, while the \textit{symmetric} credit assignment strategy yielded the best performance results in one case.
-It can therefore be concluded that the credit assignment strategy is problem specific.
-As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
-
-\subsection{Reselection Interval}
-\label{sec:conclusion:results:summary:reselection}
-
-For this experimental group, five different reselection intervals were evaluated.
-These included reselection intervals of 1, 5, 10, 15, and 20.
-Overall, with statistical significance, it was found that a larger reselection interval is generally preferred.
-It was found that larger reselection intervals lead to longer time frames for the low-level heuristics to progress, smoothing out update steps.
-Larger reselection intervals also allow the \acs{BHH} to collect more samples of \index{heuristic}heuristic performance evidence from which it can learn.
-Therefore, a conclusion that can be made is that \index{heuristic}heuristic and solution exploitation is preferred over exploration.
-As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
-
-\subsection{Replay}
-\label{sec:conclusion:results:summary:replay}
-
-For this experimental group, five different replay windows sizes were evaluated.
-These included replay window sizes of 1, 5, 10, 15, and 20.
-Overall, no statistically significant difference was found for the performance of the replay window size configurations, and thus, it was concluded that the replay window size is problem specific, with some datasets preferring short memory and other preferring long memory.
-The relationship between the reselection interval, replay window size and reanalysis interval was discussed, and it was shown that these hyper-parameters should be considered together.
-As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
-
-\subsection{Reanalysis Interval}
-\label{sec:conclusion:results:summary:reanalysis}
-
-For this experimental group, five different reanalysis intervals were evaluated.
-These included reanalysis intervals of 1, 5, 10, 15, and 20.
-Overall, no statistically significant difference was found for the performance of the reanalysis intervals across all datasets, and thus, it was concluded that the reanalysis interval is problem specific.
-As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
-
-\subsection{Burn In}
-\label{sec:conclusion:results:summary:burn_in}
-
-For this experimental group, five different burn in window sizes were evaluated.
-These included burn in window sizes of 1, 5, 10, 15, and 20.
-Overall, it was found with statistical significance, that lower burn in window sizes are generally preferred.
-The lower burn in window sizes generally produced the best results in the majority of cases, with some exceptions that prefer average burn in window sizes.
-As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
-
-\subsection{Normalisation}
-\label{sec:conclusion:results:summary:normalise}
-
-For this experimental group an empirical test was conducted to determine the effects of normalisation of pseudo counts allocated by the credit assignment strategy in the performance log.
-A configuration is included with normalisation enabled and a configuration is included with normalisation disabled.
-It was concluded that the default replay window size of 10 is too small to yield a significant difference in performance outcome for when normalisation is enabled compared to when normalisation is disabled.
-As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
-
-\subsection{Discounted Rewards}
-\label{sec:conclusion:results:summary:discounted_rewards}
-
-For this experimental group an empirical test was conducted to determine the effects of discounted rewards of pseudo counts allocated by the credit assignment strategy in the performance log.
-A configuration is included with discounted rewards enabled and a configuration is included with discounted rewards disabled.
-Similar to the findings for the experimental group investigating the effects of the normalisation hyper-parameter, it was concluded that the default replay window size of 10 is too small to yield a significant difference in performance outcome for when discounted rewards is enabled compared to when discounted rewards is disabled.
-As before, illustrations of the train and test loss and accuracy plots for some example datasets were provided.
-
-\section{Future Research Opportunities}
-\label{sec:conclusion:further_research}
-
-Throughout this dissertation, many different opportunities have been identified for future research. This section contains a summary of each of these topics.
-
-\subsubsection{A Priori Biases}
-\label{sec:conclusion:further_research:a_priori_biases}
-
-By default, the \acs{BHH} initialises the values for the concentration parameters, related to each \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool, symmetrically with an initial value of 1.0.
-This yields an initial probability distribution of the \index{heuristic}heuristic selection probabilities that is uniform.
-Symmetric initialisation contains no a priori \index{heuristic}heuristic selection bias and assumes uniform sampling at first.
-It has been identified that expert knowledge can be incorporated into the \acs{BHH} by carefully providing the initial concentrations for the each \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.
-Such research would then evaluate if such prior \index{heuristic}heuristic selection biases have a positive impact on the outcomes of the \acs{BHH}.
-
-\subsubsection{Move-Acceptance Strategies}
-\label{sec:conclusion:further_research:move_acceptance}
-
-Throughout the presentation of the empirical results, it is mentioned that a move-acceptance strategy can be incorporated to reject \index{heuristic}heuristic progressions that do not improve on the current best solution found.
-This would eliminate any divergence in the training process as a result of selecting sub-optimal \index{heuristic}heuristics.
-Various different move-acceptance strategies can be developed and empirically tested.
-
-\subsubsection{Early Stopping Strategies}
-\label{sec:conclusion:further_research:early_stopping}
-
-Similar to the move-acceptance strategy, throughout the presentation of the empirical results, it is mentioned that an early stopping strategy can be used to halt the training process if the performance does not improve for a number of steps.
-In this dissertation, a number of examples were presented where divergence of training loss occurred.
-Furthermore, a number of examples were presented where overfitting occurred.
-An early stopping strategy can help prevent such outcomes.
-
-\subsubsection{Entity Search}
-\label{sec:conclusion:further_research:entity_search}
-For this dissertation, even though the predictive model implemented by the \acs{BHH} includes entity consideration, it does not sample from an entity pool.
-The \acs{BHH} keeps the entire entity pool fixed, and just reselects heuristics for each entity.
-The \acs{BHH}, as is, can be used to learn which entities to select as well.
-The hypothesis is that this would result in better combinations of entities and heuristics, which should have a positive effect on the outcomes of the \acs{BHH}.
-
-\subsubsection{Continuous-Valued Credit Allocation}
-\label{sec:conclusion:further_research:continuous_credit}
-
-Credit assignment in the context of this dissertation yields a discrete credit allocation value.
-More specifically, the credit allocation is binary, yielding a zero or a one.
-Future research can investigate different credit allocation strategies that yield continuous valued outcomes.
-This should provide more fine-grained indicators of \index{heuristic}heuristic performance which the \acs{BHH} can exploit easier.
-
-\subsubsection{Credit Search}
-\label{sec:conclusion:further_research:credit_search}
-
-Similar to entity search, the \acs{BHH}, as is, can be used to learn which credit assignment strategies to use.
-This can then be combined with heuristic and entity selection so that the correct heuristic is selected for the correct entity, by means of the correct credit allocation strategy that is applicable, at the correct time in the training process.
-For example, a particular heuristic-entity combination might benefit from a \textit{pbest} credit allocation, while another heuristic-entity combination might benefit from a \textit{ibest} credit allocation at the same time in the training process.
-
-\subsubsection{Models}
-\label{sec:conclusion:further_research:models}
-
-For this dissertation, focus was put on training \acp{FFNN}.
-However, in theory, other models can also be used.
-Suggestions include \acp{DNN} and \acp{RNN}.
-Furthermore, future research can attempt to use the \acs{BHH} for dynamic optimisation problems.
-
-\subsubsection{Dynamic Hyper-Parameter Values}
-\label{sec:conclusion:further_research:dynamic_hyper_parameters}
-
-It was shown that larger reselection intervals are generally preferred.
-It was shown that there is a relationship between the reselection interval, the replay window size and the reanalysis interval.
-These hyper-parameters provide a mechanism for trade-off between exploration and exploitation and therefore, investigation into dynamic selection of hyper-parameter values can be considered in future research.
-
-\subsubsection{Heuristic Pools}
-\label{sec:conclusion:further_research:heuristic_pools}
-
-This dissertation only considered three different types of \index{heuristic pool}heuristic pool configurations.
-The following alternative configurations could be considered.
-A \index{heuristic pool}heuristic pool could be considered where multiple instances of the same \index{heuristic}heuristic is included, but with different hyper-parameter values, effectively implementing dynamic hyper-parameter optimisation.
-Empirical testing can be done to determine the effects of various \index{heuristic pool}heuristic pool sizes.
-Different types of heuristics can be considered for inclusion in the \index{heuristic pool}heuristic pool.
-A suggestion is to include black-box optimisers such as \acs{CMA-ES}.
-Finally, \index{heuristic}heuristic ensemble pools could be considered, where the \index{heuristic}heuristic selection is a selection of an ensemble of \index{heuristic}heuristics.
-
-\subsubsection{Parameter Pools}
-\label{sec:conclusion:further_research:parameter_pools}
-
-A suggestion for future research is to apply the \acs{BHH} to a multitude of parameter types.
-These could be hyper-parameters of the low-level \index{heuristic}heuristics, the parameters for the topology and architecture of models (similar to neural architecture search) or the hyper-parameters of the \acs{BHH} itself.
-
-\section{Documentation and Data}
-\label{sec:conclusion:documentation_and_data}
-
-All the source code, data, logs and analyses that were used in this dissertation, as well as the dissertation source itself, can be found at \url{https://github.com/arneschreuder/masters}.
-The raw empirical data is made available on Google Cloud's BigQuery platform, under the project id \textit{masters-363209}.
-
-\section{Summary}
-\label{sec:conclusion:summary}
-
-This chapter concludes the research that is done in this dissertation.
-This chapter provided a summary of the research intent, providing a brief review of the research problem, motivations and objectives defined for this dissertation.
-A brief summary of the background information that was covered in this dissertation was provided.
-A brief summary on the concept and implementation of the novel \acs{BHH} was provided, followed by a brief summary of the methodology that was used for the empirical process.
-This chapter also provided brief summaries of the results and findings for each of the experimental groups that were executed in the empirical process.
-Future research opportunities were identified and reference was made to materials and assets used in this dissertation that was made available online.

### 2023-01-23 article/sections/04-hyper-heuristics.tex
🚧  (article): Probability WIP

--- 2022-11-28 dissertation/chapters/04-hyper-heuristics.tex
@@
-\chapter{Hyper-Heuristics}\label{chap:hhs}
-
-\begin{quotation}
-      ``The capacity to learn is a gift; the ability to learn is a skill; the willingness to learn is a choice.''
-\end{quotation}
-\begin{flushright}
-      - Brian Herbert
-\end{flushright}
-
-Chapter \ref{chap:heuristics} introduced the concept of a \index{heuristic}heuristic as an optimisation algorithm that is used in a search process that seeks out optimal solutions to an optimisation problem.
-Finding the best \index{heuristic}heuristic to use for a given optimisation problem is non-trivial.
-Furthermore, finding optimal solutions is often dependent on using the appropriate configurations.
-In the context of training \acp{FFNN}, these configurations could include \index{heuristic}heuristic hyper-parameters and model architecture.
-It is often the case that the application of a specific configuration only applies to a specific problem and does not necessarily translate or generalise to other problems~\cite{ref:kheiri:2017}.
-
-The optimal configuration of \index{heuristic}heuristics to use, along with hyper-parameters and model architecture, lies in some hyper-dimensional \textit{configuration space} yielding yet again, another optimisation problem on its own.
-Traditionally, if multiple configurations are to be considered, an empirical process of trial and error is executed.
-Trial and error approaches are time consuming and laborious.
-
-One particular approach to the configuration optimisation problem mentioned above, is to try and automate the process to find the best configuration.
-One such automated process involves considering many different configurations in an iterative fashion, sweeping over different configurations parameters within the configuration space.
-Techniques such as \acf{DoE}, proposed by~\citeauthor{ref:fisher:1937}~\cite{ref:fisher:1937}, follow an iterative approach, where a configuration space is defined in terms of its extremities, while retrieving candidate configurations by interpolating over the configuration space.
-Iterative approaches implement a form of \index{offline learning}offline learning where the optimisation of configuration only happens after all configurations have been considered and evaluated.
-
-More modern techniques automate the search for optimal configuration as part of the underlying search process itself, resulting in a form of dynamic configuration during the search process.
-An example of such a technique is to dynamically adjust the heuristic \index{hyper-parameters}\textit{hyper-parameters} as part of the optimisation process.
-This field of study is known as \index{meta-learning}meta-learning~\cite{ref:giraud:2004}.
-The term \textit{learning} refers to the optimisation of the configuration and \index{hyper-parameters}hyper-parameters.
-
-A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the \index{heuristic}heuristic characteristics and heaviours used throughout the search process and not just the \index{heuristic}heuristic hyper-parameters.
-This approach focuses on the hybridisation of \index{heuristic}heuristic paradigms.
-By dynamically combining the best of different \index{heuristic} paradigms throughout the learning process, a trade-off can be made between focussing on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during the search process.
-The dynamic trade-off between exploration and exploitation could also be seen as a dynamic trade-off between the strengths and weaknesses of different \index{heuristic}heuristics during the search process.
-
-One such form of hybridisation of \index{heuristic}heuristic paradigms is referred to as \textit{heterogeneous approaches}.
-Heterogeneous approaches make use of different \textit{search behaviours} by selecting from a behaviour pool.
-Heterogeneous approaches have shown to balance the trade-off between exploration and exploitation~\cite{ref:nepomuceno:2013}.
-
-Another form of hybridisation of \index{heuristic}heuristic paradigms is that of hybridisation of different \textit{heuristics} that are applied to some optimisation problem~\cite{ref:burke:2013}.
-These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.
-This dissertation takes a particular interest in developing a novel selection \acs{HH} that can be used to train \acp{FFNN}.
-This chapter provides the reader with the necessary background information of \index{meta-learning}meta-learning and \acp{HH}.
-The remainder of the chapter is structured as follows:
-
-\begin{itemize}
-      \item \textbf{Section \ref{sec:hh:meta_learning}} provides the reader with a brief definition and discussion on meta-learning.
-
-      \item \textbf{Section \ref{sec:hh:what_is_a_hh}} presents the concept of a \acs{HH} and a formal definition is provided.
-It is shown how \acp{HH} implement a form of \index{meta-learning}meta-learning.
-
-      \item \textbf{Section \ref{sec:hh:classification}} provides a detailed discussion on the classification and types of \acp{HH}.
-Distinction is made between online and offline learning mechanisms.
-Discussions follow on selection and generation \acp{HH}, and construction and perturbation mechanisms.
-
-      \item \textbf{Section \ref{sec:hh:summary}} provides a brief summary of the chapter.
-\end{itemize}
-
-\section{Meta-Learning}\label{sec:hh:meta_learning}
-
-\index{meta-learning}Meta-learning is inspired by a branch of meta-cognition that is concerned with learning about \textit{learning processes}.
-Meta-learning studies how learning systems can increase efficiency through experience~\cite{ref:vilalta:2002} and is broadly defined as the learning process concerned with the concept of \textit{learning to learn}~\cite{ref:thrun:1998}.
-The goal of meta-learning is to provide a learning/optimisation process that is flexible to the problem domain or task under consideration.
-
-\citeauthor{ref:vilalta:2002}~\cite{ref:vilalta:2002} mention that meta-learning differs from base-learning in the scope of the level of adaptation.
-Meta-learning is concerned with learning how to choose the right configuration and biases dynamically.
-On the contrary, for \textit{base}-learning, biases and configurations are predefined and fixed a priori.
-\citeauthor{ref:thrun:1998}~\cite{ref:thrun:1998} mention that meta-learning aims at discovering ways to dynamically search for the best learning strategy as the number of tasks increase, implying some form of generalisation of the learning process to other problems.
-
-In the context of training \acp{FFNN}, \index{meta-learning}meta-learning could be applied to dynamically adjust the hyper-parameters of a \index{heuristic}heuristic during the training process.
-$K$-fold cross-validation is a common technique that applies dynamic adjustment of hyper-parameters during the training process~\cite{ref:allen:1974}.
-$K$-fold cross-validation is based on the idea that the optimal hyper-parameters for a given problem can be found by evaluating the performance of the heuristic on a subset of the training data.
-
-Dynamic adjustment of hyper-parameters might not be enough.
-Different search behaviours or techniques might be needed to balance the trade-off between exploration and exploitation.
-The following section provides a brief introduction to the concept of a \acf{HH}, a modern approach that builds on the foundations of \index{meta-learning}meta-learning.
-
-\section{What are Hyper-Heuristics?}
-\label{sec:hh:what_is_a_hh}
-
-The term \acf{HH} was first used in 1997 by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} and was used to describe a protocol that combines several \acs{AI} methods in the context of automated theorem proving.
-The term was independently used in 2000 by~\citeauthor{ref:cowling:2000}~\cite{ref:cowling:2000} to describe ``heuristics to choose heuristics''.
+\section{Hyper-Heuristics}
+\label{sec:hhs}
 
@@
 It can be said that \acp{HH} are concerned with finding the best \index{heuristic}heuristic in \textit{heuristic space}, while the underlying low-level \index{heuristic}heuristics find solutions in the feasible \textit{search/solution space}.
-\acp{HH}, introduce a domain barrier that separates the information that the high-level \index{heuristic}heuristic and low-level \index{heuristic}heuristics use during the search process and is illustrated in Figure \ref{fig:heuristics:hh:hh_algorithm} below.
 
-\begin{figure}[htbp]
-      \begin{centering}
-            \centering
-            \includegraphics[width=0.65\textwidth]{images/hh_domain_barrier.pdf}
-            \caption{An illustration of the domain barrier that exists as a result of the separation between the low-level \index{heuristic}heuristics and the high-level \index{heuristic}heuristic as introduced by \acp{HH}.}
-            \label{fig:heuristics:hh:hh_algorithm}
-      \end{centering}
-\end{figure}
-
-Figure \ref{fig:heuristics:hh:hh_algorithm} shows the separation of information that is accessible to the entity pool and heuristic pool.
-At a higher level abstraction, the high level heuristic implemented by \acp{HH}, do not make use of domain specific information such as an entity's position or gradient from the search space.
-
-To summarise, \citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} highlights two fundamental ideas behind \acp{HH}.
+\citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} highlights two fundamental ideas behind \acp{HH}.
 Firstly, the recognition that the process of selecting or designing efficient hybrid and/or cooperative heuristics can be regarded as a computational search problem in itself.
@@
 
-\section{Classification of Hyper-Heuristics}\label{sec:hh:classification}
+\subsection{Classification of Hyper-Heuristics}\label{sec:hh:classification}
 
@@
 	\centering
-      \includegraphics[width=\textwidth]{images/hh_classification.pdf}
+	\includegraphics[width=0.85\textwidth]{images/hh_classification.pdf}
 	\caption{A classification of \acs{HH} approaches, according to two dimensions: (i) the source of feedback used during learning, and (ii) the nature of the heuristic search space.}
@@
 
-\subsection{Source of Feedback}
+\subsubsection{Source of Feedback}
 
@@
 
-\subsection{Heuristic Search Space}
+\subsubsection{Heuristic Search Space}
 According to the classification proposed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the second dimension of classification involves the nature of the \index{heuristic}heuristic search space.
@@
 As such, the hyper-heuristic framework is provided with a set of neighbourhood structures and/or simple local searchers.
-
-\section{Summary}\label{sec:hh:summary}
-
-This chapter provided the reader with the necessary background information on \index{meta-learning}meta-learning and \acp{HH}.
-Formal definitions were given, followed by detailed discussions.
-A modern classification scheme for \acs{HH} as proposed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} was presented in detail.
-Distinction is made between the source of feedback information used during learning and the nature of the heuristic search space.
-Detailed discussions on selection and generation heuristics are provided, followed by a further classification of construction and perturbation mechanisms.
-
-This chapter concludes the background information of \index{heuristic}heuristics in general.
-The following chapter aims to provide the reader with the necessary background information on statistics and probability theory.

### 2023-01-23 article/sections/05-probability.tex
🚧  (article): Probability WIP

--- 2022-12-06 dissertation/chapters/05-probability.tex
@@
-\chapter{Probability}
-\label{chap:probability}
-
-\begin{quotation}
-      ``Probability theory is nothing but common sense reduced to calculation.''
-\end{quotation}
-\begin{flushright}
-      - Pierre-Simon Laplace
-\end{flushright}
+\section{Probability}
+\label{sec:probability}
 
@@
 These are large fields and focus is put on the elements that are required to formulate the proposed \acf{BHH}.
-The remainder of the chapter is structured as follows:
-
-\begin{itemize}
-      \item \textbf{Section \ref{sec:probability:overview}} provides a brief overview of what probability is and how it is used.
-
-      \item \textbf{Section \ref{sec:probability:cond_probability}} presents the concept of conditional probability.
-
-      \item \textbf{Section \ref{sec:probability:multiple_events}} presents the two laws of probability related to the intersection and union of multiple events.
-
-      \item \textbf{Section \ref{sec:probability:bayes_theorem}} introduces \index{Bayes' theorem}Bayes' theorem, the fundamental theorem upon which the \acs{BHH} is built.
-
-      \item \textbf{Section \ref{sec:probability:probability_distributions}} presents the reader with relevant probability distributions.
-
-      \item \textbf{Section \ref{sec:probability:conjugate_priors}} presents the reader with relevant conjugate prior probability distributions.
-
-      \item \textbf{Section \ref{sec:probability:bayesian_statistics}} presents \textit{Bayesian} statistics.
-Brief discussions follow on the \textit{frequentist} view and \textit{Bayesian} view of probability.
-Detailed discussions follow on Bayesian optimisation methods such as \index{Bayesian analysis}\textit{Bayesian analysis}.
-
-      \item \textbf{Section \ref{sec:probability:summary}} provides a brief summary of the chapter.
-\end{itemize}
 
@@
 
-\section{Conditional Probability and Independence}\label{sec:probability:cond_probability}
-
-The occurrence of a given random event, $A$, can often be conditional on the occurrence of another event, $B$.
-In the field of medicine, an example of this is to calculate the probability of a certain diagnosis of a sick patient given his/her symptoms.
-The aforementioned relationship between events is referred to as the conditional probability between two events.
-The conditional probability is expressed as $P(A \vert B)$ and is read \textit{the probability of $A$ given $B$}.
-On the contrary, the \textit{unconditional} probability is the probability of an event, not dependent on any other.
-The conditional probability of $A$ given $B$ can be expressed as is given in Definition \ref{eq:probability:cond_probability} below~\cite{ref:wackerly:2014}.
-\\
-\begin{definition}[\textbf{Conditional Probability}]
-      \label{eq:probability:cond_probability}
-      The conditional probability of an event $A$, subject to the occurrence of event $B$ is expressed as
-
-      \begin{equation}
-            \label{eq:probability:overview:conditional}
-            P(A \vert B) = \frac{P(A \cap B)}{P(B)}
-      \end{equation}
-\end{definition}
-
-where $P(B) > 0$.
-Note that conditional probability does not suggest causation.
-If an event $A$ has a high probability of occurring after observing event $B$, it does not necessarily mean that $A$ is caused by $B$.
-Conditional probability simply expresses the dependence amongst events.
-
-It could also be the case that the outcome of observing event $A$ is not affected by the occurrence of $B$.
-In this case, it is said that events $A$ and $B$ are independent.
-The independence between two events are expressed in Definition \ref{def:probability:cond_probability:independence} below.
-\\
-\begin{definition}[\textbf{Independence of Events}]
-      \label{def:probability:cond_probability:independence}
-      Two events, $A$ and $B$, are said to be independent of each other if, and only if the following criteria hold:
-
-      \begin{itemize}
-            \item $P(A \vert B) = P(A)$
-            \item $P(B \vert A) = P(B)$
-            \item $P(A \cap B) = P(A)P(B)$
-      \end{itemize}
-
-      Otherwise, events $A$ and $B$ are said to be \textit{dependent} random events.
-\end{definition}
-
-\section{Two Laws of Probability for Multiple Events}\label{sec:probability:multiple_events}
-
-Suppose there are two random events, $A$ and $B$, then one can calculate the probability of the union and intersection of these events.
-From the aforementioned concept, two laws of probability can be formulated.
-These are referred to as the \textit{multiplicative} and \textit{additive} laws of probability~\cite{ref:wackerly:2014} and is given below in Theorems \ref{th:probability:multiple_events:multiplicative} and \ref{th:probability:multiple_events:additive} respectively.\\
-
-\begin{theorem}[\textbf{The Multiplicative Law of Probability}]
-      \label{th:probability:multiple_events:multiplicative}
-      The probability of the intersection of two events, $A$ and $B$, is given as
-
-      \begin{equation}
-            \begin{split}
-                  P(A \cap B)
-                  &= P(A)P(B \vert A) \\
-                  &= P(B)P(A \vert B)
-            \end{split}
-      \end{equation}
-
-      If $A$ and $B$ are independent, then
-
-      \begin{equation}
-            P(A \cap B) = P(A)P(B)
-      \end{equation}
-\end{theorem}
-
-\begin{proof}
-      Proof is given from Definition \ref{eq:probability:cond_probability}.
-\end{proof}
-\vspace*{0.5cm}
-
-\begin{theorem}[\textbf{The Additive Law of Probability}]
-      \label{th:probability:multiple_events:additive}
-      The probability of the union of two events, $A$ and $B$, is given as
-
-      \begin{equation}
-            P(A \cup B) = P(A) + P(B) - P(B \cap A)
-      \end{equation}
-\end{theorem}
-
-\begin{proof}
-      The geometric proof of the additive law of probability is given by the Venn Diagram presented in Figure \ref{fig:probability:multiple_events:additive}.
-Note that $A \cup B = A \cup ( \bar{A} \cap B)$, where $A$ and $\bar{A} \cap B$ are mutually exclusive events.
-Furthermore, consider that $B = (\bar{A} \cap B) \cup (A \cap B)$, where $\bar{A} \cap B$ and $A \cap B$ are mutually exclusive.
-Then $P(A \cup B) = P(A) + P(\bar{A} \cap B)$ and $P(B) = P(\bar{A} \cap B) + P(A \cap B)$.
-The equality on the right implies that $P(\bar{A} \cap B) = P(B) - P(A \cap B)$.
-By substituting the expression for $P(\bar{A} \cap B)$ into the expression for $P(A \cup B)$, the resulting expression $P(A \cup B) = P(A) + P(B) - P(A \cap B)$ is obtained.
-\end{proof}
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=0.7\textwidth]{images/additive_law_of_probability_proof.pdf}
-      \caption{A Venn-Diagram showing the proof of the additive law of probability for multiple events.}
-      \label{fig:probability:multiple_events:additive}
-\end{figure}
-
-\index{Bayes' theorem}
-\section{Bayes' Theorem}\label{sec:probability:bayes_theorem}
-
-\index{Bayes' theorem}Bayes' theorem, named after Thomas Bayes, describes the probability of an event, $A$, based on prior knowledge of conditions that might be related to $A$~\cite{ref:zalta:2015}.
-In order to derive the formal theorem and proof, first consider Definition \ref{def:probability:bayes_theorem:partition} below~\cite{ref:zalta:2015}.
-\\
-\begin{definition}
-      \label{def:probability:bayes_theorem:partition}
-      For some positive integer, $K$, let the sets $B_{1}, B_{2}, \dots, B_{K}$ be such that
-
-      \begin{enumerate}
-            \item $S = B_{1} \cup B_{2} \cup \dots \cup B_{K}$
-            \item $B_{i} \cap B_{j} = \emptyset$, for $i \neq j$
-      \end{enumerate}
-
-      Then the collection of sets $\{B_{1}$, $B_{2}$, $\dots$, $B_{K}\}$ is said to be a partition of S, the union of mutually exclusive subsets.
-\end{definition}
-\vspace*{0.5cm}
-
 \index{Bayes' theorem}
@@
 \index{Bayes' theorem}Bayes' theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
-
-\section{Probability Distributions}\label{sec:probability:probability_distributions}
-
-Probability distributions are mathematical functions that give the probabilities of the occurrences of different possible outcomes in the experiment.
-The theory and equations presented in the following sections where all taken from~\citeauthor{ref:wackerly:2014}~\cite{ref:wackerly:2014}.
-
-\subsection{Beta Probability Distribution}\label{sec:probability:probability_distributions:beta}
-
-The \index{Beta probability distribution}Beta probability distribution is a family of univariate, continuous, probability distributions over some $x$, with support on the interval $[0,1]$~\cite{ref:wackerly:2014}.
-It is parameterised by two shape parameters $\alpha > 0$, $\alpha \in \mathbb{R}$ and $\beta > 0$, $\beta \in \mathbb{R}$.
-The \index{Beta probability distribution}Beta probability distribution is denoted as $Beta(\alpha, \beta)$.
-The \acf{PDF} of the \index{Beta probability distribution}Beta probability distribution is given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:beta:pdf}
-      P(x \vert \alpha, \beta) = f_{Beta}(x; \alpha, \beta) = \frac{1}{B(\alpha, \beta)} x^{\alpha - 1} (1 - x)^{\beta - 1}
-\end{equation}
-
-The normalising constant, $B(\alpha, \beta)$, is defined as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:beta:norm_const}
-      B(\alpha, \beta) = \frac{\Gamma(\alpha)\Gamma(\beta)}{\Gamma(\alpha + \beta)}
-\end{equation}
-
-where $\Gamma$ is the Gamma function defined as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:beta:gamma_func}
-      \Gamma(n) = ( n - 1)!
-\end{equation}
-
-It should be noted that the Gamma function can also be written as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:beta:gamma_func_alt}
-      \Gamma(n+1) = n!
-\end{equation}
-
-The control parameters $\alpha$ and $\beta$ determine the shape of the distribution.
-There exists a special case where $\alpha = \beta$.
-This is referred to as the \textit{symmetric} \index{Beta probability distribution}Beta probability distribution.
-In the case where $\alpha = \beta = 1$ the distribution is equivalent to the uniform distribution over all points in its support.
-The \index{Beta probability distribution}Beta probability distribution for various values of $\alpha$ and $\beta$, including the symmetric version is illustrated in Figure \ref{fig:probability:probability_distributions:beta}.
-
-\begin{figure}[htbp]
-      \begin{subfigure}{0.49\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{images/beta_various.pdf}
-            \caption{\index{Beta probability distribution}Beta probability distribution}
-            \label{fig:probability:probability_distributions:beta_normal}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{images/beta_cumulative.pdf}
-            \caption{Cumulative \index{Beta probability distribution}Beta probability distribution}
-            \label{fig:probability:probability_distributions:beta_cumulative}
-      \end{subfigure}
-      \par\bigskip
-      \caption{An illustration of the \index{Beta probability distribution}Beta probability distribution (left)~\cite{ref:beta:2014} as well as the cumulative \index{Beta probability distribution}Beta probability distribution (right)~\cite{ref:cumulativebeta:2014} for various values of $\alpha$ and $\beta$ .}
-      \label{fig:probability:probability_distributions:beta}
-\end{figure}
-
-The expected value of $x$ is given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:beta:expected_value}
-      E[x] = \frac{\alpha}{\alpha + \beta}
-\end{equation}
-
-Similarly, the expected value of the natural logarithm of $x$ is calculated as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:beta:expected_value_ln}
-      E[\ln(x)] = \psi({\alpha}) - \psi(\alpha + \beta)
-\end{equation}
-
-where $\psi$ is the logarithmic derivative of the Gamma function, called the \textit{Digamma} function. The Digamma function is given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:beta:digamma}
-      \psi(n) = \frac{d}{dn}\ln(\Gamma(n)) = \frac{\Gamma'(n)}{\Gamma(n)}
-\end{equation}
-
-Finally, the mode of the distribution is given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:beta:mode}
-      M[x] = E[x] - 1 = \frac{\alpha - 1}{\alpha + \beta - 1}
-\end{equation}
-
-\subsection{Dirichlet Probability Distribution}\label{sec:probability:probability_distributions:dirichlet}
-
-The \index{Dirichlet probability distribution}Dirichlet probability distribution is a family of multivariate continuous probability distributions over some $\boldsymbol{x}$ in $K$ dimensions~\cite{ref:wackerly:2014}.
-The \index{Dirichlet probability distribution}Dirichlet probability distribution is a multivariate generalization of the \index{Beta probability distribution}Beta probability distribution and is thus sometimes referred to by its alternative name, i.e.
-the multivariate Beta probability distribution.
-The \index{Dirichlet probability distribution}Dirichlet probability distribution is parameterised by some vector $\boldsymbol{\alpha} = (\alpha_{1}$,  $\dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} > 0, \alpha_{k} \in \mathbb{R}$.
-The parameters, $\boldsymbol{\alpha}$, are referred to as the concentration parameters.
-The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K \geq 2$ with parameters $\boldsymbol{\alpha}$, denoted $Dir(\boldsymbol{\alpha})$, has a \acs{PDF} given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:dirichlet:pdf}
-      P(\boldsymbol{x} \vert \boldsymbol{\alpha}) =  f_{Dir}(\boldsymbol{x}; K, \boldsymbol{\alpha}) = \frac{1}{B(\boldsymbol{\alpha})}  \prod_{k=1}^{K} x_{k}^{\alpha_{k} - 1}
-\end{equation}
-
-The normalising constant, $B(\boldsymbol{\alpha})$, is defined as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:dirichlet:norm_cost}
-      B(\boldsymbol{\alpha}) = \frac{\prod_{k=1}^{K} \Gamma(\alpha_{k})}{\Gamma(\alpha_{0})}
-\end{equation}
-
-where $\alpha_{0}$ is defined as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:dirichlet:alpha_0}
-      \alpha_{0} = \sum_{k=1}^{K}\alpha_{k}
-\end{equation}
-
-Importantly, the set $\{x_{k}\}_{k=1}^{K}$ belongs to the standard $K-1$ probability simplex $S$, meaning that $x_{K} = 1 - \sum_{k=1}^{K-1}x_{k}$ with support $\forall_{k=1}^{K} x_{k} \in [0,1]$.
-Under the simplex $S$, this means that the sum over all values of the vector $\boldsymbol{x}$ must be 1.
-The simplex can thus be rewritten as $\sum_{k=1}^{K}x_{k} = 1$.
-
-Similar to the \index{Beta probability distribution}Beta probability distribution, $\boldsymbol{\alpha}$ determines the shape of the distribution in $K$ dimensions and thus, there also exist a special case, referred to as the \textit{symmetric} distribution when $\forall_{k=1}^{K} \alpha_{k} = c$, where $c$ is some constant.
-In the case where $c = 1$, the distribution is referred to as a \textit{flat} distribution and yields the uniform distribution over all points in $S$.
-The \index{Dirichlet probability distribution}Dirichlet probability distribution of order $K = 3$ for various values of $\boldsymbol{\alpha}$, including the symmetric version, is presented in Figure \ref{fig:probability:probability_distributions:dirichlet}.
-
-\begin{figure}[htb]
-      \centering
-      \includegraphics[width=0.9\textwidth]{images/dirichlet.pdf}
-      \caption{The \acfp{PDF} for the \index{Dirichlet probability distribution}Dirichlet probability distribution over the 2-simplex.
-The concentration parameters, $\boldsymbol{\alpha}$, are varied.
-The values of the \acs{PDF} are shown by the colour maps with contour lines at equal values as indicated in the colour bars~\cite{ref:dirichlet:2020}.}
-      \label{fig:probability:probability_distributions:dirichlet}
-\end{figure}
-
-The expected value of $x_{k}$ is calculated as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:dirichlet:expected_value}
-      E[x_{k}] = \frac{\alpha_{k}}{\alpha_{0}}
-\end{equation}
-
-Similarly, the expected value of the natural logarithm of $x_{k}$ is calculated as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:dirichlet:expected_value_ln}
-      E[\ln(x_{k})] = \psi({\alpha_{k}}) - \psi(\alpha_{0})
-\end{equation}
-
-where $\psi$ is the Digamma function as defined in Equation~\eqref{eq:probability:probability_distributions:beta:digamma}. Finally, the mode of the distribution is given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:dirichlet:mode}
-      \begin{split}
-            M[x_{k}] &= E[{x_{k}] -K^{-1}} \\
-            &=  \frac{\alpha_{k} - 1}{\alpha_{0} - K}
-      \end{split}
-\end{equation}
-
-\subsection{Bernoulli Probability Distribution}\label{sec:probability:probability_distributions:bernoulli}
-
-The \index{Bernoulli probability distribution}Bernoulli probability distribution is a discrete probability distribution over some random variable $x$ that takes the value of $1$ with probability $\theta$ and $0$ with probability $1-\theta$ ~\cite{ref:wackerly:2014}.
-The \index{Bernoulli probability distribution}Bernoulli probability distribution is denoted as $Ber(\theta)$ with support $x \in \{0, 1\}$.
-In probability theory, the \index{Bernoulli probability distribution}Bernoulli probability distribution is often used to explain the possible outcomes of a single experiment that asks a \textit{yes-no} question such as flipping a coin.
-The outcome of such an experiment is a Boolean value.
-The \index{Bernoulli probability distribution}Bernoulli probability distribution has a \acs{PMF}, given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:bernoulli:pmf}
-      P(x \vert \theta) = f_{Ber}(x; \theta) =
-      \begin{cases}
-            \theta     & \text{if}\ x=1 \\
-            1 - \theta & \text{if}\ x=0
-      \end{cases}
-\end{equation}
-
-Equation~\eqref{eq:probability:probability_distributions:bernoulli:pmf} can also be expressed as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:bernoulli:alt}
-      f_{Ber}(x; \theta) = \theta^{x}(1-\theta)^{1-x}
-\end{equation}
-
-The mean of the \index{Bernoulli probability distribution}Bernoulli probability distribution approaches $\theta$ over many samples according to the \acs{CLT}~\cite{ref:grinstead:1997}.
-Figure \ref{fig:probability:probability_distributions:bernoulli:coin} illustrates a fair-coin flipping simulation.
-The mean converges to 0.5 for various sample sizes.
-
-\begin{figure}[htbp]
-      \centering
-      \begin{subfigure}{0.49\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{images/coin_flip_samples_100.pdf}
-            \caption{100 Samples}
-            \label{fig:probability:probability_distributions:bernoulli:coin_100}
-      \end{subfigure}
-      \begin{subfigure}{0.49\textwidth}
-            \centering
-            \includegraphics[width=\textwidth]{images/coin_flip_samples_10000.pdf}
-            \caption{10000 Samples}
-            \label{fig:probability:probability_distributions:bernoulli:coin_10000}
-      \end{subfigure}
-      \par\bigskip
-      \caption{An illustration of the coin-flip simulation for different sample sizes that show the convergence of the mean as per the \acf{CLT}.}
-      \label{fig:probability:probability_distributions:bernoulli:coin}
-\end{figure}
-
-The expected value of the distribution is thus given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:bernoulli:expected_value}
-      E[x] = \theta
-\end{equation}
-
-The mode of the distribution is given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:bernoulli:mode}
-      M[x] =
-      \begin{cases}
-            0   & \text{if}\ \theta < 0.5 \\
-            0,1 & \text{if}\ \theta = 0.5 \\
-            1   & \text{if}\ \theta > 0.5 \\
-      \end{cases}
-\end{equation}
-
-\subsection{Binomial Probability Distribution}\label{sec:probability:probability_distributions:bin}
-
-The \index{Binomial probability distribution}Binomial probability distribution is a discrete probability distribution over a random variable $x$ taking on a number of successes in $N$ sequential independent experiments that each ask a \textit{yes-no} question~\cite{ref:wackerly:2014}.
-The probability of a single independent experiment yielding a success is given as $\theta$ and the \index{Binomial probability distribution}Binomial probability distribution is denoted as $Bin(N, \theta)$, with support $x \in \{0, 1, \dots, N\}$.
-It should be noted that the \index{Binomial probability distribution}Binomial probability distribution is an extension of the \index{Bernoulli probability distribution}Bernoulli probability distribution over $N$ independent sequential experiments, and thus each experiment also yields some Boolean outcome.
-When $N=1$, the experiment is referred to as a Bernoulli trial, and the distribution is just a \index{Bernoulli probability distribution}Bernoulli probability distribution.
-When $N > 1$, the sequence of outcomes is referred to as a Bernoulli process.
-The \acs{PMF} of the \index{Binomial probability distribution}Binomial probability distribution is given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:binomial:pmf}
-      P(x \vert \theta; N) = f_{Bin}(x; N, \theta) = \binom{N}{x} \theta^{x}(1-\theta)^{1-x}
-\end{equation}
-
-Similar to the \index{Bernoulli probability distribution}Bernoulli probability distribution, the mean of the \index{Binomial probability distribution}Binomial probability distribution is $N\theta$ given the \acs{CLT} as was shown in Figure \ref{fig:probability:probability_distributions:bernoulli:coin}.
-The expected value of the \index{Binomial probability distribution}Binomial probability distribution is thus given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:binomial:expected_value}
-      E[x] = N\theta
-\end{equation}
-
-The mode of the distribution is given as
-
-\begin{align}
-      \label{eq:probability:probability_distributions:binomial:mode}
-      \begin{split}
-            M[x] &= E[x] + \theta \\
-            &= N\theta  + \theta \\
-            &= (N  + 1)\theta
-      \end{split}
-\end{align}
-
-\subsection{Categorical Probability Distribution}\label{sec:probability:probability_distributions:categorical}
-
-The \index{Categorical probability distribution}Categorical probability distribution is a discrete probability distribution over some random variable, $x$, taking on any one of $K$ possible categories~\cite{ref:wackerly:2014}.
-There is no ordering to these categories and therefore, for simplicity, each category is assigned a numerical representative value such that $k \in \{1, 2, \dots, K\}$.
-The probabilities for all outcomes is given by the probability vector $\boldsymbol{\theta} = (\theta_{1}, \dots, \theta_{K})$.
-This means that the probability $P(x=k)=\theta_{k}$ has support $x \in \{1, \dots, K\}$.
-The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\boldsymbol{\theta})$, is a generalization of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, i.e.
-the generalised \index{Bernoulli probability distribution}Bernoulli probability distribution or the Multinoulli probability distribution.
-In probability theory, the \index{Categorical probability distribution}Categorical probability distribution is often used to explain the outcome of a single experiment with more than two possible outcomes, such as rolling a six-sided die~\cite{ref:wackerly:2014}.
-The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution is given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:categorical:pmf}
-      P(x \vert \boldsymbol{\theta}; K) = f_{Cat}(x; K, \boldsymbol{\theta}) = \prod_{k=1}^{K}\theta_{k}^{[x = k]}
-\end{equation}
-
-where the term, $[x = k]$, is the \textit{Iversion Bracket}~\cite{ref:iverson:1962}, yielding 1 if $x = k$ and 0 otherwise.
-Given class $k$, the categorical distribution simply yields $\theta_{k}$ as follows:
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:categorical:pmf_k}
-      f_{Cat}(x=k; K, \boldsymbol{\theta}) = \theta_{k}
-\end{equation}
-
-The random variable $x$ can also be encoded in binary format, yielding a vector $\boldsymbol{x} = (x_{1}, \dots, x_{K})$ of \index{Bernoulli probability distribution}Bernoulli probability distributions such that the support is $\forall_{k=1}^{K} x_{k} \in \{0, 1\}$.
-Importantly, if the outcome of the random event is of category $k$, then $x_{k} = 1$ and $\forall_{j=1}^{K} x_{j} = 0, j \neq k$ so that the standard $K-1$ probability simplex $S$ still holds.
-The \acs{PMF} of the \index{Categorical probability distribution}Categorical probability distribution is rewritten as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:categorical:pmf_alt}
-      f_{Cat}(\boldsymbol{x}; K, \boldsymbol{\theta}) = \prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{k})}
-\end{equation}
-
-where $\mathbbm{1}(x_{k})$ is the \textit{indicator function}, yielding 1 if $x_{k} = 1$ and 0 otherwise.
-
-Since there is no order to the underlying categories, the mean of the distribution does not yield any relevant information. The mode of the distribution is given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:categorical:mode}
-      M[x] = \argmax_{k}(\theta_{1}, \dots, \theta_{K})
-\end{equation}
-
-\subsection{Multinomial Probability Distribution}
-\label{sec:probability:probability_distributions:multinomial}
-
-The \index{Multinomial probability distribution}Multinomial probability distribution is a discrete probability distribution over some random variable $\boldsymbol{x} = (x_{1}, \dots\, x_{K})$ that takes on the counts for each occurrence of $K$ possible classes in $N$ independent trials~\cite{ref:wackerly:2014}.
-The probabilities for all possible outcomes in a single trial is given by the probability vector, $\boldsymbol{\theta} = (\theta_{1}, \dots, \theta_{K})$.
-The \index{Multinomial probability distribution}Multinomial probability distribution, denoted $Mul(N, K, \boldsymbol{\theta})$, is thus a generalization of the \index{Binomial probability distribution}Binomial probability distribution to $K$ dimensions.
-Consider the following special cases:
-
-\begin{itemize}
-      \item When $K$ is 2 and $N = 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Bernoulli probability distribution}Bernoulli probability distribution.
-      \item When $K$ is 2 and $N > 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Binomial probability distribution}Binomial probability distribution.
-      \item When $K > 2$ and $N = 1$, the \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Categorical probability distribution}Categorical probability distribution.
-\end{itemize}
-
-The support for the Multinomial is $\forall_{i=1}^{K} x_{k} \in \{1, \dots, N\}, \sum_{k=1}^{K}x_{k} = N$ and the \acs{PMF} for the \index{Multinomial probability distribution}Multinomial probability distribution is given as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:multinomial:pmf}
-      P(\boldsymbol{x} \vert \boldsymbol{\theta}; N; K) = f_{Mul}(\boldsymbol{x}; N, K, \boldsymbol{\theta}) = \frac{N!}{\prod_{k=1}^{K}x_{k}!} \prod_{k=1}^{K}\theta_{k}^{x_{k}}
-\end{equation}
-
-Similar to the \index{Categorical probability distribution}Categorical probability distribution, the random variable $x$ can also be encoded in binary format, yielding an $N \times K$ matrix $\boldsymbol{X}$ of \index{Bernoulli probability distribution}Bernoulli probability distributions.
-The support is then given as $\boldsymbol{X} \in \{0, 1\}^{N \times K}, \forall_{i=1}^{N}\sum_{k=1}^{K} x_{i,k} = 1$ so that the standard $K-1$ probability simplex $S$ still holds for each trial.
-The \acs{PMF} of the \index{Multinomial probability distribution}Multinomial probability distribution is then rewritten as
-
-\begin{equation}
-      \label{eq:probability:probability_distributions:multinomial:pmf_alt}
-      \begin{split}
-            f_{Mul}(\boldsymbol{X}; N, K, \boldsymbol{\theta}) &= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!}\prod_{i=1}^{N}\prod_{k=1}^{K}\theta_{k}^{\mathbbm{1}_{1}(x_{i,k})} \\
-            &= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!} \prod_{k=1}^{K}\theta_{k}^{\sum_{i=1}^{N}\mathbbm{1}_{1}(x_{i,k})} \\
-            &= \frac{N!}{\prod_{k=1}(\sum_{i=1}^{N}x_{i, k})!} \prod_{k=1}^{K}\theta_{k}^{N_{k}} \\
-      \end{split}
-\end{equation}
-
-where $N_{k}$ is a summary variable, denoting the number of times a category $k$ occurs over all trials in $N$.
 
@@
 The posterior density has the same functional form, $\mathcal{A}(v)$, as the prior, yielding the update on prior parameters as $\alpha' = \sum y_{i} + \alpha$ and $\beta' = n - \sum y_{i} + \beta$.
-
-\section{Summary}\label{sec:probability:summary}
-
-This chapter provided all the necessary background information on probability theory and statistics.
-The origins of statistical analysis were discussed and the differences between the frequentist and Bayesian view of statistics were discussed in detail.
-Probability distributions and proofs of conjugate priors were provided with detailed mathematical descriptions.
-Finally, a detailed description of Bayesian analysis was provided with detailed mathematical descriptions.
-
-This chapter concludes all the relevant background information that is needed to formulate the \acs{BHH}. The proposed \acs{BHH} is presented in the following chapter.

### 2023-02-01 article/appendices/c-datasets.tex
🚧 (article): Save point, WIP

--- 2022-12-05 dissertation/chapters/07-methodology.tex
@@
-\chapter{Methodology}\label{chap:methodology}
+\section{Datasets}
+\label{app:appendix_datasets}
 
-\begin{quotation}
-      ``Observation, reason and experimentation make up what we call the scientific method.''
-\end{quotation}
-\begin{flushright}
-      - Richard P. Feynman
-\end{flushright}
-
-So far, this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acp{HH} and probability theory in Chapters \ref{chap:anns} to \ref{chap:probability}.
-Chapter \ref{chap:bhh} provided the detail of the implementation of the proposed \acs{BHH} with all its components and hyper-parameters.
-Scientific experimentation can now be conducted.
-Chapter \ref{chap:introduction} identified a set of empirical goals for this dissertation.
-The goals of this dissertation include an empirical evaluation of the \acs{BHH}, its behaviour and performance, and a comparison to state of the art low-level \index{heuristic}heuristics.
-This chapter provides the detailed specification of the methodology that is followed for the empirical process.
-Details are provided on the implementation of experiments, datasets, selection of hyper-parameters and design decisions.
-The process by which the results are statistically analysed are also presented.
-The remainder of the chapter is structured as follows:
-
-\begin{itemize}
-      \item \textbf{Section \ref{sec:methodology:overview}} provides a brief overview of the overall empirical process.
-
-      \item \textbf{Section \ref{sec:methodology:datasets}} presents the detail around the datasets that are used.
-
-      \item \textbf{Section \ref{sec:methodology:model}} provides the details of the models (\acs{FFNN}s) that are trained.
-
-      \item \textbf{Section \ref{sec:methodology:heuristics}} presents the detail around the different \index{heuristic}heuristics that are used along with their hyper-parameters.
-
-      \item \textbf{Section \ref{sec:methodology:baseline_bhh}} provides the detail of the configuration of the \acs{BHH} baseline.
-
-      \item \textbf{Section \ref{sec:methodology:performance_measures}} sheds light into the performance evaluation measures that are used.
-
-      \item \textbf{Section \ref{sec:methodology:stopping_conditions}} discusses the stopping conditions that are used.
-
-      \item \textbf{Section \ref{sec:methodology:experiments}} presents the different experimental groups that are executed.
-
-      \item \textbf{Section \ref{sec:methodology:implementation}} sheds light on the implementation and execution of the empirical process.
-
-      \item \textbf{Section \ref{sec:methodology:statistical_analysis}} presents the procedures that are followed for the statistical analysis of the results.
-
-      \item \textbf{Section \ref{sec:methodology:summary}} presents a brief summary of the chapter.
-\end{itemize}
-
-\section{Overview of Empirical Process}\label{sec:methodology:overview}
-
-The purpose of the empirical process is to conduct a carefully crafted set of experiments that produce data that can be used to reject of verify a hypothesis about the element under investigation.
-Chapter \ref{chap:introduction} identified a number of empirical tests to execute.
-These include:
-
-\begin{itemize}
-      \item An empirical study to show that the \Acs{BHH} can effectively be used to train \acp{FFNN}.
-
-      \item An empirical study to investigate the behavioural characteristics of the \Acs{BHH} as it is used to train \acp{FFNN} on an example problem.
-
-      \item An empirical study to critically evaluate the performance of the \Acs{BHH} compared to individual low-level \index{heuristic}heuristics in the \index{heuristic}heuristic space as they are used to train \acp{FFNN} on a number of different problems.
-\end{itemize}
-
-These empirical tests represent a set of questions, related to the \acs{BHH}, that need to be answered.
-The empirical process is designed to answer these questions.
-The empirical process is structured as follows.
-
-Each empirical test starts with a question to be answered.
-A hypothesis is formulated for the outcome of the empirical test.
-The empirical tests are then designed around the implementation of the components under evaluation.
-Each empirical test defines the configuration of elements and generally include a set of parameters that are altered between experiments.
-Each experiment is evaluated by means of a performance measurement.
-In the context of training \acp{FFNN}, the underlying model is trained across a number of datasets.
-Each dataset is split into a training set comprising of 80\% of the data, and a test set comprising of 20\% of the data.
-The training set is used to train the model, while the test set is used to evaluate the model's performance on unseen data.
-Training epochs are split into mini-batch iterations with a specified mini-batch size per dataset.
-Evaluation takes place at every mini-batch step.
-Due to the stochastic nature of the experiments, each experiment is repeated over 30 independent runs to provide sufficient sample for statistical certainty about the outcome of the results.
-Each run contains a different random seed, such that each run is unique.
-The evaluation data forms the results of the empirical test.
-These results are analysed for statistical significance, from which findings and conclusions are then made.
-The null hypothesis is then either rejected or accepted based on these findings.
-
-Details around each of these elements are provided in the following sections.
-
-\section{Datasets}
-\label{sec:methodology:datasets}
-
-This section provides the detail around the different datasets that are used throughout the empirical process.
-These datasets originate from the UCI Machine Learning Repository~\cite{ref:uci:2022}.
-Datasets are grouped by problem type and include seven classification and seven regression datasets.
-The classification datasets are given in Table \ref{tab:methodology:datasets:classification} and the regression datasets are given in Table \ref{tab:methodology:datasets:regression} below.
-
-\begin{table}[htb]
+\begin{table}[H]
 	\centering
@@
 
-\begin{table}[htb]
+\begin{table}[htbp]
 	\centering
@@
 \end{table}%
-
-Details on how the datasets where preprocessed and prepared is given in Appendix \ref{app:datasets}.
-
-\subsection{Class Balancing}
-
-A number of classification datasets given in Table \ref{tab:methodology:datasets:classification} contain an unbalanced representation of classes.
-The empirical process defined in this dissertation does not apply mechanisms to cater for class balancing, in order to eliminate as many variables and factors in the empirical process as possible.
-It is therefore suggested that the \acs{BHH} first be studied under the assumption of balanced classes, before applying class balancing techniques.
-In future research opportunities, class balancing should be utilised.
-
-\section{Models}\label{sec:methodology:model}
-
-All models that are trained in this dissertation follow implementations of shallow \acp{FFNN}, meaning that they only have one hidden layer.
-The architecture of a model is dependent on the dataset being trained on, the type of optimisation problem, the number of input dimensions and the number of output dimensions.
-The number of hidden layers used were determined empirically.
-Weights are initialised by means of \index{Glorot uniform sampling}Glorot uniform sampling~\cite{ref:glorot:2010}.
-The models and their configuration, as it is used for each dataset, are given in Table \ref{tab:methodology:models:configurations}.
-
-\begin{table}[htb]
-      \centering
-      \caption{Model configurations}
-      \label{tab:methodology:models:configurations}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{rcccccccc}
-                  \textbf{dataset}    & \textbf{inputs} & \textbf{hidden} & \textbf{output} & \textbf{biases} & \textbf{parameters} & \textbf{topology} & \textbf{l1 activation} & \textbf{l2 activation} \\
-                  \midrule
-                  fish toxicity       & 6               & 3               & 1               & yes             & 25                  & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  iris                & 4               & 5               & 3               & yes             & 43                  & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  air quality         & 12              & 8               & 1               & yes             & 113                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  housing             & 13              & 8               & 1               & yes             & 121                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  wine quality        & 13              & 10              & 7               & yes             & 217                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  parkinsons          & 21              & 10              & 1               & yes             & 231                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  car                 & 21              & 10              & 4               & yes             & 264                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  forest fires        & 43              & 16              & 1               & yes             & 721                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  abalone             & 10              & 36              & 28              & yes             & 1432                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  bank                & 51              & 32              & 1               & yes             & 1697                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  bike                & 61              & 32              & 1               & yes             & 2017                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  student performance & 99              & 32              & 1               & yes             & 3233                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  adult               & 108             & 64              & 1               & yes             & 7041                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  mushroom            & 117             & 64              & 1               & yes             & 7617                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  diabetic            & 2369            & 32              & 3               & yes             & 75939               & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-            \end{tabular}%
-      }
-\end{table}%
-
-For the classification problems presented in Tables \ref{tab:methodology:datasets:classification} and \ref{tab:methodology:models:configurations}, the softmax activation function is added after training and is not included in the model during training.
-The loss functions, \acf{SparseCatXE} and \acf{BinXE}, that are used, contain a \index{softmax}softmax function.
-
-\index{heuristic}
-\section{Heuristics}\label{sec:methodology:heuristics}
-
-This section provides the details of the low-level \index{heuristic}heuristics that are used in the empirical process.
-Each of these low-level \index{heuristic}heuristics are implemented as standalone \index{heuristic}heuristics and are also included in the \index{heuristic pool}heuristic pool of the \acs{BHH}.
-Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level \index{heuristic}heuristics that are used as well as their hyper-parameter configurations.
-
-% Table generated by Excel2LaTeX from sheet 'BHH Baseline'
-\begin{table}[htbp]
-      \centering
-      \caption{Low-level \index{heuristic}heuristics and their hyper-parameter configurations.}
-      \label{tab:methodology:heuristics}%
-      \par\bigskip
-      \resizebox{0.7\textwidth}{!}{
-
-            \begin{tabular}{llll}
-                  \textbf{heuristic} & \textbf{configuration}    & \textbf{value} & \textbf{citation}          \\
-                  \midrule
-                  sgd                & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
-                  momentum           & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
-                                     & momentum                  & 0.9            &                            \\
-                  nag                & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
-                                     & momentum                  & 0.9            &                            \\
-                  adagrad            & learning rate             & 0.1 (0.01)     & ~\cite{ref:duchi:2011}     \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  rmsprop            & learning rate             & 0.1 (0.01)     & ~\cite{ref:hinton:2012}    \\
-                                     & rho                       & 0.95           &                            \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  adadelta           & learning rate             & 1.0 (0.95)     & ~\cite{ref:zeiler:2012}    \\
-                                     & rho                       & 0.95           &                            \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  adam               & learning rate             & 0.1 (0.01)     & ~\cite{ref:kingma:2014}    \\
-                                     & beta1                     & 0.9            &                            \\
-                                     & beta2                     & 0.999          &                            \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  pso                & population size           & 10             & ~\cite{ref:van:2010}       \\
-                                     & learning rate             & 1.0 (0.9)      &                            \\
-                                     & inertia weight (w)        & 0.729844       &                            \\
-                                     & cognitive control (c1)    & 1.49618        &                            \\
-                                     & social control (c2)       & 1.49618        &                            \\
-                                     & velocity clip min         & -1.0           &                            \\
-                                     & velocity clip max         & 1.0            &                            \\
-                  de                 & population size           & 10             & ~\cite{ref:mezura:2006}    \\
-                                     & selection strategy        & best           &                            \\
-                                     & xo strategy               & exp            &                            \\
-                                     & recombination probability & 0.9 (0.1)      &                            \\
-                                     & beta                      & 2.0 (0.1)      &                            \\
-                  ga                 & population size           & 10             & ~\cite{ref:lambora:2019}   \\
-                                     & selection strategy        & rand           &                            \\
-                                     & xo strategy               & bin            &                            \\
-                                     & mutation rate             & 0.2 (0.05)     &                            \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Note from Table \ref{tab:methodology:heuristics} that values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it.
-The number of steps is the total number of mini-batch training steps that are executed for that particular dataset.
-
-Furthermore, it should be noted that a learning rate was added to \acs{PSO} as an attempt to avoid overshooting solutions later in the training process.
-A learning rate parameter does not traditionally form part of \acs{PSO}, but was found to be useful.
-The position update step for \acs{PSO} using a learning rate is then defined as
-
-\begin{equation}
-      \label{eq:heuristics:pso:position_learning_rate}
-      \begin{split}
-            x_{ij}(t+1) = x_{ij}(t) + \eta v_{ij}(t+1)
-      \end{split}
-\end{equation}
-
-where $\eta$ is the added learning rate with $0 \leq \eta \leq 1, \eta \in \mathbb{R}$.
-
-Section \ref{sec:bhh:heuristic:proxies} presented the concept of a mapping of proxied \index{heuristic}heuristic state update operations.
-The mapping of proxied \index{heuristic}heuristic state update operations implemented by the \acs{BHH} in the empirical process is given in Figure \ref{fig:methodology:heuristics:proxies}.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=0.95\textwidth]{images/bhh_heuristic_proxies.pdf}
-      \caption{Mapping of proxied heuristic state update operations as implemented by the \acs{BHH}}
-      \label{fig:methodology:heuristics:proxies}%
-\end{figure}
-
-In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x} indicate that the associated \index{heuristic}heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
-The required mapping of proxied \index{heuristic}heuristic state operations is then implemented as a lookup of the table presented in Figure \ref{fig:methodology:heuristics:proxies}.
-
-\section{BHH Baseline}\label{sec:methodology:baseline_bhh}
-
-The \acs{BHH} baseline is a name given to a specific configuration of the \acs{BHH} which, during development, has been found to provide a reasonable baseline performance.
-The baseline configuration is used as the cornerstone configuration from which all other \index{heuristic}heuristics and their configurations are evaluated.
-The \acs{BHH} baseline is also used for the behavioural study of the \acs{BHH}.
-The \acs{BHH} baseline configuration is given in Table \ref{tab:methodology:bhh_baseline_configuration}.
-
-% Table generated by Excel2LaTeX from sheet 'BHH Baseline'
-\begin{table}[htb]
-      \centering
-      \caption{The \acs{BHH} baseline configuration as it is used in the empirical study.}
-      \label{tab:methodology:bhh_baseline_configuration}%
-      \par\bigskip
-      \resizebox{0.65\textwidth}{!}{
-            \begin{tabular}{rrcc}
-                  \multicolumn{1}{c}{\textbf{hyper-heuristic}} & \multicolumn{1}{c}{\textbf{variant}} & \textbf{configuration} & \textbf{value} \\
-                  \midrule
-                  \multicolumn{1}{l}{bhh}                      & \multicolumn{1}{l}{baseline}         & heuristic pool         & all            \\
-                                                               &                                      & population             & 5              \\
-                                                               &                                      & credit                 & ibest          \\
-                                                               &                                      & burn in                & 0              \\
-                                                               &                                      & reselection            & 10             \\
-                                                               &                                      & replay                 & 10             \\
-                                                               &                                      & reanalysis             & 10             \\
-                                                               &                                      & normalise              & false          \\
-                                                               &                                      & discounted rewards     & false          \\
-            \end{tabular}%
-      }
-\end{table}%
-
-In Table \ref{tab:methodology:bhh_baseline_configuration}, the \index{heuristic}heuristic pool configuration that is used, is referred to as \textit{all}.
-The \textit{all} configuration refers to a configuration where the \index{heuristic pool}heuristic pool contains all the low-level \index{heuristic}heuristics as presented in Section \ref{sec:methodology:heuristics}, including all gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
-
-\section{Performance Measures}\label{sec:methodology:performance_measures}
-
-This section provides the performance measures that are used to evaluate the different experimental runs during the empirical process.
-Chapter \ref{chap:anns} provided a number of loss functions.
-These loss functions are used to measure the performance of the \acp{FFNN} being trained.
-In this dissertation, \acs{BinXE} is used for classification problems with two classes and \acs{SparseCatXE} is used for classification problems with more than two classes.
-For the classification problems, accuracy is also measured.
-Accuracy refers to the proportion of correct classifications.
-For regression problems, the \acs{RMSE} is used as a performance metric.
-
-The test set is used as a validation set during training.
-All performance metrics are measured for the training set as well as the test/validation set during training.
-As such, a divergence in performance metrics between the training and test/validation set is used to evaluate for overfitting during the training process.
-
-After training has been completed, the \textit{average rank}, based on test loss, for all configurations, is calculated at each mini-batch step.
-A total of 30 independent runs with different random seed configurations are executed for each empirical test.
-The test loss metric and average rank are then statistically analysed across all runs, and are used to derive findings and conclusions.
-
-\section{Stopping Conditions}\label{sec:methodology:stopping_conditions}
-
-This section provides the stopping conditions that are used during the empirical process.
-For this dissertation, the \textit{maximum epoch} stopping condition is used, where a fixed, maximum number of training steps and epochs are executed and training is not halted until the maximum number of epochs have been reached.
-\acp{FFNN} are trained for a maximum of 30 epochs.
-Early stopping is a technique where training is stopped when the \index{heuristic}heuristic is not able to improve the performance of the \acs{FFNN} for a number of steps.
-If the performance has not improved, the training is halted and the last known best model weights are restored.
-Early stopping is not implemented for the empirical process in this dissertation.
-This design decision is made so that the behaviour of the \acs{BHH} can be studied beyond the point of optimal results.
-
-\section{Experiments}
-\label{sec:methodology:experiments}
-
-This section presents the experimental groups that are executed in the empirical process.
-Three main experimental groups are formulated.
-Each of these are discussed in more detail in the following sections.
-
-\subsection{Behavioural Case Study}
-\label{sec:methodology:experiments:case_study}
-
-The behavioural case study analyses the behaviour of the \acs{BHH} baseline configuration as it relates to an example problem dataset, across 30 independent runs.
-The example problem dataset is the iris dataset, presented in Table \ref{tab:methodology:datasets:classification}.
-The behavioural case study is meant to provide an introductory analysis of the inner workings of the \acs{BHH} and includes analysis of the selection mechanism, as well as the perturbative nature of the \acs{BHH}.
-The behavioural case study is used to determine if the \acs{BHH} is learning and that selection is indeed biasing towards better performance.
-These observations also provide an opportunity to observe the outcome of the perturbative nature of the \acs{BHH}, which includes proxied \index{heuristic}heuristic update step operations.
-
-The behavioural case study provides an implementation of the \acs{BHH} baseline which, by default, has a replay window size of 10.
-The baseline configuration is provided and compared to an implementation of a \acs{BHH} configuration where the replay window size is large (250), as well as an implementation of the \acs{BHH} using the \textit{symmetric} credit assignment strategy.
-The large replay window size configuration is used to show the behaviour of the \acs{BHH} when it has access to a large number of performance log samples, which increases the statistical certainty of the learning outcome.
-The \acs{BHH} configuration that uses the \textit{symmetric} credit assignment strategy is used to illustrate the behaviour of the \acs{BHH} where no performance bias takes place and thus, no learning occurs.
-
-\subsection{Standalone Heuristics}
-\label{sec:methodology:experiments:standalone_optimisers}
-
-For the standalone \index{heuristic}heuristics experimental group, the \index{heuristic}heuristics, as presented in Section \ref{sec:methodology:heuristics}, are used along with their specified hyper-parameters.
-Each of these standalone low-level \index{heuristic}heuristics are compared to that of the \acs{BHH} baseline configuration, across all datasets.
-
-The intent of the standalone \index{heuristic}heuristics experimental group is to determine if the \acs{BHH} baseline configuration can generalise to multiple problems in comparison to individual low-level \index{heuristic}heuristics.
-
-Additional to the \acs{BHH} baseline configuration, two more \acs{BHH} configurations are included.
-These include \acs{BHH} configurations where the \index{heuristic pool}heuristic pool only makes use of gradient-based \index{heuristic}heuristics, and a configuration where the \index{heuristic pool}heuristic pool only makes use of \acp{MH}.
-The intent behind the inclusion of these configurations is to determine the effectiveness of multi-method approaches in the \index{heuristic pool}heuristic pool as it applies to training \acp{FFNN}.
-
-\subsection{BHH Variants}
-\label{sec:methodology:experiments:bhh_variants}
-
-This section provides the details of the experimental group that focuses on \acs{BHH} variants and the effect that different hyper-parameter configurations can have on the outcome of the \acs{BHH}.
-The different variants of the \acs{BHH} and their possible configurations are given in Table \ref{tab:methodology:experiments:bhh_variants}.
-
-\begin{table}[htb]
-      \centering
-      \caption{BHH variants and their configuration}
-      \label{tab:methodology:experiments:bhh_variants}%
-      \par\bigskip
-      \resizebox{0.9\textwidth}{!}{
-            \begin{tabular}{rcc}
-                  \multicolumn{1}{c}{\textbf{hyper-heuristic}} & \textbf{variant}   & \textbf{values}                       \\
-                  \midrule
-                  \multicolumn{1}{l}{bhh}                      & heuristic pool     & all, gd, mh                           \\
-                                                               & population         & 5, 10, 15, 20, 25                     \\
-                                                               & credit             & ibest, pbest, rbest, gbest, symmetric \\
-                                                               & reselection        & 1, 5, 10, 15, 20                      \\
-                                                               & replay             & 1, 5, 10, 15, 20                      \\
-                                                               & reanalysis         & 1, 5, 10, 15, 20                      \\
-                                                               & burn in            & 0, 5, 10, 15, 20                      \\
-                                                               & normalise          & false, true                           \\
-                                                               & discounted rewards & false, true                           \\
-            \end{tabular}%
-      }
-\end{table}%
-
-In Table \ref{tab:methodology:experiments:bhh_variants}, the \index{heuristic pool}heuristic pool configuration \textit{gd} refers to the \index{heuristic pool}heuristic pool configuration where only gradient-based \index{heuristic}heuristics are included, and \textit{mh} refers to the \index{heuristic pool}heuristic pool configuration where only \acp{MH} are included.
-
-\section{Statistical Analysis}
-\label{sec:methodology:statistical_analysis}
-
-This section provides the detail of the process that is used to execute the statistical analysis of the results.
-
-Various experimental groups and configurations have been presented in Sections \ref{sec:methodology:experiments:case_study}, \ref{sec:methodology:experiments:standalone_optimisers} and \ref{sec:methodology:experiments:bhh_variants}.
-The results from each of these experimental groups are statistically analysed.
-To ensure that there are sufficient samples for statistical analysis, each experiment and configuration is trained for 30 epochs and is repeated over 30 runs, for each of the fourteen datasets.
-The experimental results contain performance evaluation data for the training and testing datasets, and includes loss and accuracy measurements.
-Statistical analysis is executed on the results from the testing datasets.
-An average rank is calculated across all 30 runs, for all experimental groups and configurations, at each step, for every epoch of training.
-Each run is executed using a unique random seed, such that each run is identical in its setup and configuration, but unique between runs.
-
-The evaluation of outcome is based on the aggregated statistical results as mentioned above.
-A descriptive analysis is executed on the spread of the data.
-The results are analysed and checked for overfitting and outliers are identified.
-The skewness of the results is evaluated per dataset and the \index{Shapiro-Wilk}Shapiro-Wilk test for normality~\cite{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
-Furthermore, the \index{Levene}Levene's test for equality of variance~\cite{ref:levene:1961} ($\alpha$ = 0.001) is used.
-The output of the full statistical analysis is presented in Appendix \ref{app:statistical_analysis}.
-
-Dependent on the outcomes of the above statistical tests, the appropriate statistical significance test is then executed.
-For experiments where there are only two configurations, the Mann-Whitney U\index{Mann-Whitney U} independent samples t-Test~\cite{ref:mann:1947} ($\alpha$ = 0.001) is executed.
-For experiments with three or more configurations, the \acs{ANOVA} statistical test~\cite{ref:fisher:1921} ($\alpha$ = 0.001) is used.
-The\index{Kruskal-Wallis} Kruskal-Wallis ranked non-parametric test~\cite{ref:kruskal:1952} for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
-
-Regardless of the statistical test that is used, a post-hoc Tukey honest significant difference test~\cite{ref:tukey:1949} ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
-Descriptive and critical difference plots are then retrieved from these results to provide visual aid.
-
-\section{Implementation and Execution}\label{sec:methodology:implementation}
-
-All implementations are done from first principles in Python 3.9 using Tensorflow 2.7 and Tensorflow Probability 0.15.0.
-Most underlying mathematical functions are reused from the Tensorflow library, however, all \index{heuristic}heuristics are implemented from first principles to fit the \acs{HH} framework that was developed.
-The source code and data for this dissertation is provided and made public at \url{https://github.com/arneschreuder/masters}.
-
-It should be noted that this implementation makes heavy use of CPU processing, due to flattening of the \acs{FFNN} weights by the \index{heuristic}heuristics.
-For this reason, execution is much more timely and costly than with GPU training.
-
-All experiments were run on the Centre for High Performance Computing (CHPC) cluster.
-A total of 14 different server were used, each running 24 to 56 cores and 256GB of memory.
-The entire empirical process took six days.
-
-\section{Summary}\label{sec:methodology:summary}
-
-This chapter provided the detail around the methodology that was used to execute the empirical process.
-The datasets, \acp{FFNN} and \index{heuristic}heuristics that are used during the empirical process have been presented in detail, along with details around various \acs{BHH} configurations.
-A baseline \acs{BHH} has been formulated.
-The empirical process was defined in terms of a number of different experimental groups and finally, the process of statistical analysis of the results was provided.
-
-The results and findings of the empirical process are presented in the following chapter.

### 2023-02-01 article/appendices/d-models.tex
🚧 (article): Save point, WIP

--- 2022-12-05 dissertation/chapters/07-methodology.tex
@@
-\chapter{Methodology}\label{chap:methodology}
+\section{Models}
+\label{app:appendix_models}
 
-\begin{quotation}
-      ``Observation, reason and experimentation make up what we call the scientific method.''
-\end{quotation}
-\begin{flushright}
-      - Richard P. Feynman
-\end{flushright}
-
-So far, this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acp{HH} and probability theory in Chapters \ref{chap:anns} to \ref{chap:probability}.
-Chapter \ref{chap:bhh} provided the detail of the implementation of the proposed \acs{BHH} with all its components and hyper-parameters.
-Scientific experimentation can now be conducted.
-Chapter \ref{chap:introduction} identified a set of empirical goals for this dissertation.
-The goals of this dissertation include an empirical evaluation of the \acs{BHH}, its behaviour and performance, and a comparison to state of the art low-level \index{heuristic}heuristics.
-This chapter provides the detailed specification of the methodology that is followed for the empirical process.
-Details are provided on the implementation of experiments, datasets, selection of hyper-parameters and design decisions.
-The process by which the results are statistically analysed are also presented.
-The remainder of the chapter is structured as follows:
-
-\begin{itemize}
-      \item \textbf{Section \ref{sec:methodology:overview}} provides a brief overview of the overall empirical process.
-
-      \item \textbf{Section \ref{sec:methodology:datasets}} presents the detail around the datasets that are used.
-
-      \item \textbf{Section \ref{sec:methodology:model}} provides the details of the models (\acs{FFNN}s) that are trained.
-
-      \item \textbf{Section \ref{sec:methodology:heuristics}} presents the detail around the different \index{heuristic}heuristics that are used along with their hyper-parameters.
-
-      \item \textbf{Section \ref{sec:methodology:baseline_bhh}} provides the detail of the configuration of the \acs{BHH} baseline.
-
-      \item \textbf{Section \ref{sec:methodology:performance_measures}} sheds light into the performance evaluation measures that are used.
-
-      \item \textbf{Section \ref{sec:methodology:stopping_conditions}} discusses the stopping conditions that are used.
-
-      \item \textbf{Section \ref{sec:methodology:experiments}} presents the different experimental groups that are executed.
-
-      \item \textbf{Section \ref{sec:methodology:implementation}} sheds light on the implementation and execution of the empirical process.
-
-      \item \textbf{Section \ref{sec:methodology:statistical_analysis}} presents the procedures that are followed for the statistical analysis of the results.
-
-      \item \textbf{Section \ref{sec:methodology:summary}} presents a brief summary of the chapter.
-\end{itemize}
-
-\section{Overview of Empirical Process}\label{sec:methodology:overview}
-
-The purpose of the empirical process is to conduct a carefully crafted set of experiments that produce data that can be used to reject of verify a hypothesis about the element under investigation.
-Chapter \ref{chap:introduction} identified a number of empirical tests to execute.
-These include:
-
-\begin{itemize}
-      \item An empirical study to show that the \Acs{BHH} can effectively be used to train \acp{FFNN}.
-
-      \item An empirical study to investigate the behavioural characteristics of the \Acs{BHH} as it is used to train \acp{FFNN} on an example problem.
-
-      \item An empirical study to critically evaluate the performance of the \Acs{BHH} compared to individual low-level \index{heuristic}heuristics in the \index{heuristic}heuristic space as they are used to train \acp{FFNN} on a number of different problems.
-\end{itemize}
-
-These empirical tests represent a set of questions, related to the \acs{BHH}, that need to be answered.
-The empirical process is designed to answer these questions.
-The empirical process is structured as follows.
-
-Each empirical test starts with a question to be answered.
-A hypothesis is formulated for the outcome of the empirical test.
-The empirical tests are then designed around the implementation of the components under evaluation.
-Each empirical test defines the configuration of elements and generally include a set of parameters that are altered between experiments.
-Each experiment is evaluated by means of a performance measurement.
-In the context of training \acp{FFNN}, the underlying model is trained across a number of datasets.
-Each dataset is split into a training set comprising of 80\% of the data, and a test set comprising of 20\% of the data.
-The training set is used to train the model, while the test set is used to evaluate the model's performance on unseen data.
-Training epochs are split into mini-batch iterations with a specified mini-batch size per dataset.
-Evaluation takes place at every mini-batch step.
-Due to the stochastic nature of the experiments, each experiment is repeated over 30 independent runs to provide sufficient sample for statistical certainty about the outcome of the results.
-Each run contains a different random seed, such that each run is unique.
-The evaluation data forms the results of the empirical test.
-These results are analysed for statistical significance, from which findings and conclusions are then made.
-The null hypothesis is then either rejected or accepted based on these findings.
-
-Details around each of these elements are provided in the following sections.
-
-\section{Datasets}
-\label{sec:methodology:datasets}
-
-This section provides the detail around the different datasets that are used throughout the empirical process.
-These datasets originate from the UCI Machine Learning Repository~\cite{ref:uci:2022}.
-Datasets are grouped by problem type and include seven classification and seven regression datasets.
-The classification datasets are given in Table \ref{tab:methodology:datasets:classification} and the regression datasets are given in Table \ref{tab:methodology:datasets:regression} below.
-
-\begin{table}[htb]
-      \centering
-      \caption{Classification datasets}
-      \label{tab:methodology:datasets:classification}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{ccccccccc}
-                  \textbf{dataset} & \textbf{output} & \textbf{types}             & \textbf{attributes} & \textbf{classes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}          \\
-                  \midrule
-                  iris             & multivariate    & real                       & 4                   & 3                & 150                & 16             & 10             & ~\cite{ref:fisher:1936}    \\
-                  car              & multivariate    & categorical                & 6                   & 4                & 1728               & 128            & 14             & ~\cite{ref:bohanec:1988}   \\
-                  abalone          & multivariate    & categorical, integer, real & 8                   & 28               & 4177               & 256            & 17             & ~\cite{ref:waugh:1995}     \\
-                  wine quality     & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & ~\cite{ref:cortez:2009}    \\
-                  mushroom         & multivariate    & categorical                & 22                  & 2                & 8214               & 512            & 17             & ~\cite{ref:schlimmer:1987} \\
-                  bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & ~\cite{ref:moro:2014}      \\
-                  diabetic         & multivariate    & integer                    & 55                  & 3                & 100000             & 1024           & 98             & ~\cite{ref:strack:2014}    \\
-            \end{tabular}%
-      }
-\end{table}%
-
-\begin{table}[htb]
-      \centering
-      \caption{Regression datasets}
-      \label{tab:methodology:datasets:regression}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{cccccccc}
-                  \textbf{dataset}    & \textbf{output}           & \textbf{types} & \textbf{attributes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}         \\
-                  \midrule
-                  fish toxicity       & multivariate              & real           & 7                   & 908                & 64             & 15             & ~\cite{ref:cassotti:2015} \\
-                  housing             & univariate                & real           & 13                  & 506                & 32             & 16             & ~\cite{ref:harrison:1978} \\
-                  forest fires        & multivariate              & real           & 13                  & 517                & 32             & 17             & ~\cite{ref:cortez:2007}   \\
-                  student performance & multivariate              & integer        & 33                  & 649                & 32             & 21             & ~\cite{ref:cortez:2008}   \\
-                  parkinsons          & multivariate              & integer, real  & 26                  & 5875               & 256            & 23             & ~\cite{ref:tsanas:2009}   \\
-                  air quality         & multivariate, time series & real           & 15                  & 9358               & 256            & 37             & ~\cite{ref:de:2008}       \\
-                  bike                & univariate                & integer, real  & 16                  & 17389              & 256            & 68             & ~\cite{ref:fanaee:2014}   \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Details on how the datasets where preprocessed and prepared is given in Appendix \ref{app:datasets}.
-
-\subsection{Class Balancing}
-
-A number of classification datasets given in Table \ref{tab:methodology:datasets:classification} contain an unbalanced representation of classes.
-The empirical process defined in this dissertation does not apply mechanisms to cater for class balancing, in order to eliminate as many variables and factors in the empirical process as possible.
-It is therefore suggested that the \acs{BHH} first be studied under the assumption of balanced classes, before applying class balancing techniques.
-In future research opportunities, class balancing should be utilised.
-
-\section{Models}\label{sec:methodology:model}
-
-All models that are trained in this dissertation follow implementations of shallow \acp{FFNN}, meaning that they only have one hidden layer.
-The architecture of a model is dependent on the dataset being trained on, the type of optimisation problem, the number of input dimensions and the number of output dimensions.
-The number of hidden layers used were determined empirically.
-Weights are initialised by means of \index{Glorot uniform sampling}Glorot uniform sampling~\cite{ref:glorot:2010}.
-The models and their configuration, as it is used for each dataset, are given in Table \ref{tab:methodology:models:configurations}.
-
-\begin{table}[htb]
+\begin{table}[H]
 	\centering
@@
 \end{table}%
-
-For the classification problems presented in Tables \ref{tab:methodology:datasets:classification} and \ref{tab:methodology:models:configurations}, the softmax activation function is added after training and is not included in the model during training.
-The loss functions, \acf{SparseCatXE} and \acf{BinXE}, that are used, contain a \index{softmax}softmax function.
-
-\index{heuristic}
-\section{Heuristics}\label{sec:methodology:heuristics}
-
-This section provides the details of the low-level \index{heuristic}heuristics that are used in the empirical process.
-Each of these low-level \index{heuristic}heuristics are implemented as standalone \index{heuristic}heuristics and are also included in the \index{heuristic pool}heuristic pool of the \acs{BHH}.
-Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level \index{heuristic}heuristics that are used as well as their hyper-parameter configurations.
-
-% Table generated by Excel2LaTeX from sheet 'BHH Baseline'
-\begin{table}[htbp]
-      \centering
-      \caption{Low-level \index{heuristic}heuristics and their hyper-parameter configurations.}
-      \label{tab:methodology:heuristics}%
-      \par\bigskip
-      \resizebox{0.7\textwidth}{!}{
-
-            \begin{tabular}{llll}
-                  \textbf{heuristic} & \textbf{configuration}    & \textbf{value} & \textbf{citation}          \\
-                  \midrule
-                  sgd                & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
-                  momentum           & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
-                                     & momentum                  & 0.9            &                            \\
-                  nag                & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
-                                     & momentum                  & 0.9            &                            \\
-                  adagrad            & learning rate             & 0.1 (0.01)     & ~\cite{ref:duchi:2011}     \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  rmsprop            & learning rate             & 0.1 (0.01)     & ~\cite{ref:hinton:2012}    \\
-                                     & rho                       & 0.95           &                            \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  adadelta           & learning rate             & 1.0 (0.95)     & ~\cite{ref:zeiler:2012}    \\
-                                     & rho                       & 0.95           &                            \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  adam               & learning rate             & 0.1 (0.01)     & ~\cite{ref:kingma:2014}    \\
-                                     & beta1                     & 0.9            &                            \\
-                                     & beta2                     & 0.999          &                            \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  pso                & population size           & 10             & ~\cite{ref:van:2010}       \\
-                                     & learning rate             & 1.0 (0.9)      &                            \\
-                                     & inertia weight (w)        & 0.729844       &                            \\
-                                     & cognitive control (c1)    & 1.49618        &                            \\
-                                     & social control (c2)       & 1.49618        &                            \\
-                                     & velocity clip min         & -1.0           &                            \\
-                                     & velocity clip max         & 1.0            &                            \\
-                  de                 & population size           & 10             & ~\cite{ref:mezura:2006}    \\
-                                     & selection strategy        & best           &                            \\
-                                     & xo strategy               & exp            &                            \\
-                                     & recombination probability & 0.9 (0.1)      &                            \\
-                                     & beta                      & 2.0 (0.1)      &                            \\
-                  ga                 & population size           & 10             & ~\cite{ref:lambora:2019}   \\
-                                     & selection strategy        & rand           &                            \\
-                                     & xo strategy               & bin            &                            \\
-                                     & mutation rate             & 0.2 (0.05)     &                            \\
-            \end{tabular}%
-      }
-\end{table}%
-
-Note from Table \ref{tab:methodology:heuristics} that values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it.
-The number of steps is the total number of mini-batch training steps that are executed for that particular dataset.
-
-Furthermore, it should be noted that a learning rate was added to \acs{PSO} as an attempt to avoid overshooting solutions later in the training process.
-A learning rate parameter does not traditionally form part of \acs{PSO}, but was found to be useful.
-The position update step for \acs{PSO} using a learning rate is then defined as
-
-\begin{equation}
-      \label{eq:heuristics:pso:position_learning_rate}
-      \begin{split}
-            x_{ij}(t+1) = x_{ij}(t) + \eta v_{ij}(t+1)
-      \end{split}
-\end{equation}
-
-where $\eta$ is the added learning rate with $0 \leq \eta \leq 1, \eta \in \mathbb{R}$.
-
-Section \ref{sec:bhh:heuristic:proxies} presented the concept of a mapping of proxied \index{heuristic}heuristic state update operations.
-The mapping of proxied \index{heuristic}heuristic state update operations implemented by the \acs{BHH} in the empirical process is given in Figure \ref{fig:methodology:heuristics:proxies}.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=0.95\textwidth]{images/bhh_heuristic_proxies.pdf}
-      \caption{Mapping of proxied heuristic state update operations as implemented by the \acs{BHH}}
-      \label{fig:methodology:heuristics:proxies}%
-\end{figure}
-
-In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x} indicate that the associated \index{heuristic}heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
-The required mapping of proxied \index{heuristic}heuristic state operations is then implemented as a lookup of the table presented in Figure \ref{fig:methodology:heuristics:proxies}.
-
-\section{BHH Baseline}\label{sec:methodology:baseline_bhh}
-
-The \acs{BHH} baseline is a name given to a specific configuration of the \acs{BHH} which, during development, has been found to provide a reasonable baseline performance.
-The baseline configuration is used as the cornerstone configuration from which all other \index{heuristic}heuristics and their configurations are evaluated.
-The \acs{BHH} baseline is also used for the behavioural study of the \acs{BHH}.
-The \acs{BHH} baseline configuration is given in Table \ref{tab:methodology:bhh_baseline_configuration}.
-
-% Table generated by Excel2LaTeX from sheet 'BHH Baseline'
-\begin{table}[htb]
-      \centering
-      \caption{The \acs{BHH} baseline configuration as it is used in the empirical study.}
-      \label{tab:methodology:bhh_baseline_configuration}%
-      \par\bigskip
-      \resizebox{0.65\textwidth}{!}{
-            \begin{tabular}{rrcc}
-                  \multicolumn{1}{c}{\textbf{hyper-heuristic}} & \multicolumn{1}{c}{\textbf{variant}} & \textbf{configuration} & \textbf{value} \\
-                  \midrule
-                  \multicolumn{1}{l}{bhh}                      & \multicolumn{1}{l}{baseline}         & heuristic pool         & all            \\
-                                                               &                                      & population             & 5              \\
-                                                               &                                      & credit                 & ibest          \\
-                                                               &                                      & burn in                & 0              \\
-                                                               &                                      & reselection            & 10             \\
-                                                               &                                      & replay                 & 10             \\
-                                                               &                                      & reanalysis             & 10             \\
-                                                               &                                      & normalise              & false          \\
-                                                               &                                      & discounted rewards     & false          \\
-            \end{tabular}%
-      }
-\end{table}%
-
-In Table \ref{tab:methodology:bhh_baseline_configuration}, the \index{heuristic}heuristic pool configuration that is used, is referred to as \textit{all}.
-The \textit{all} configuration refers to a configuration where the \index{heuristic pool}heuristic pool contains all the low-level \index{heuristic}heuristics as presented in Section \ref{sec:methodology:heuristics}, including all gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
-
-\section{Performance Measures}\label{sec:methodology:performance_measures}
-
-This section provides the performance measures that are used to evaluate the different experimental runs during the empirical process.
-Chapter \ref{chap:anns} provided a number of loss functions.
-These loss functions are used to measure the performance of the \acp{FFNN} being trained.
-In this dissertation, \acs{BinXE} is used for classification problems with two classes and \acs{SparseCatXE} is used for classification problems with more than two classes.
-For the classification problems, accuracy is also measured.
-Accuracy refers to the proportion of correct classifications.
-For regression problems, the \acs{RMSE} is used as a performance metric.
-
-The test set is used as a validation set during training.
-All performance metrics are measured for the training set as well as the test/validation set during training.
-As such, a divergence in performance metrics between the training and test/validation set is used to evaluate for overfitting during the training process.
-
-After training has been completed, the \textit{average rank}, based on test loss, for all configurations, is calculated at each mini-batch step.
-A total of 30 independent runs with different random seed configurations are executed for each empirical test.
-The test loss metric and average rank are then statistically analysed across all runs, and are used to derive findings and conclusions.
-
-\section{Stopping Conditions}\label{sec:methodology:stopping_conditions}
-
-This section provides the stopping conditions that are used during the empirical process.
-For this dissertation, the \textit{maximum epoch} stopping condition is used, where a fixed, maximum number of training steps and epochs are executed and training is not halted until the maximum number of epochs have been reached.
-\acp{FFNN} are trained for a maximum of 30 epochs.
-Early stopping is a technique where training is stopped when the \index{heuristic}heuristic is not able to improve the performance of the \acs{FFNN} for a number of steps.
-If the performance has not improved, the training is halted and the last known best model weights are restored.
-Early stopping is not implemented for the empirical process in this dissertation.
-This design decision is made so that the behaviour of the \acs{BHH} can be studied beyond the point of optimal results.
-
-\section{Experiments}
-\label{sec:methodology:experiments}
-
-This section presents the experimental groups that are executed in the empirical process.
-Three main experimental groups are formulated.
-Each of these are discussed in more detail in the following sections.
-
-\subsection{Behavioural Case Study}
-\label{sec:methodology:experiments:case_study}
-
-The behavioural case study analyses the behaviour of the \acs{BHH} baseline configuration as it relates to an example problem dataset, across 30 independent runs.
-The example problem dataset is the iris dataset, presented in Table \ref{tab:methodology:datasets:classification}.
-The behavioural case study is meant to provide an introductory analysis of the inner workings of the \acs{BHH} and includes analysis of the selection mechanism, as well as the perturbative nature of the \acs{BHH}.
-The behavioural case study is used to determine if the \acs{BHH} is learning and that selection is indeed biasing towards better performance.
-These observations also provide an opportunity to observe the outcome of the perturbative nature of the \acs{BHH}, which includes proxied \index{heuristic}heuristic update step operations.
-
-The behavioural case study provides an implementation of the \acs{BHH} baseline which, by default, has a replay window size of 10.
-The baseline configuration is provided and compared to an implementation of a \acs{BHH} configuration where the replay window size is large (250), as well as an implementation of the \acs{BHH} using the \textit{symmetric} credit assignment strategy.
-The large replay window size configuration is used to show the behaviour of the \acs{BHH} when it has access to a large number of performance log samples, which increases the statistical certainty of the learning outcome.
-The \acs{BHH} configuration that uses the \textit{symmetric} credit assignment strategy is used to illustrate the behaviour of the \acs{BHH} where no performance bias takes place and thus, no learning occurs.
-
-\subsection{Standalone Heuristics}
-\label{sec:methodology:experiments:standalone_optimisers}
-
-For the standalone \index{heuristic}heuristics experimental group, the \index{heuristic}heuristics, as presented in Section \ref{sec:methodology:heuristics}, are used along with their specified hyper-parameters.
-Each of these standalone low-level \index{heuristic}heuristics are compared to that of the \acs{BHH} baseline configuration, across all datasets.
-
-The intent of the standalone \index{heuristic}heuristics experimental group is to determine if the \acs{BHH} baseline configuration can generalise to multiple problems in comparison to individual low-level \index{heuristic}heuristics.
-
-Additional to the \acs{BHH} baseline configuration, two more \acs{BHH} configurations are included.
-These include \acs{BHH} configurations where the \index{heuristic pool}heuristic pool only makes use of gradient-based \index{heuristic}heuristics, and a configuration where the \index{heuristic pool}heuristic pool only makes use of \acp{MH}.
-The intent behind the inclusion of these configurations is to determine the effectiveness of multi-method approaches in the \index{heuristic pool}heuristic pool as it applies to training \acp{FFNN}.
-
-\subsection{BHH Variants}
-\label{sec:methodology:experiments:bhh_variants}
-
-This section provides the details of the experimental group that focuses on \acs{BHH} variants and the effect that different hyper-parameter configurations can have on the outcome of the \acs{BHH}.
-The different variants of the \acs{BHH} and their possible configurations are given in Table \ref{tab:methodology:experiments:bhh_variants}.
-
-\begin{table}[htb]
-      \centering
-      \caption{BHH variants and their configuration}
-      \label{tab:methodology:experiments:bhh_variants}%
-      \par\bigskip
-      \resizebox{0.9\textwidth}{!}{
-            \begin{tabular}{rcc}
-                  \multicolumn{1}{c}{\textbf{hyper-heuristic}} & \textbf{variant}   & \textbf{values}                       \\
-                  \midrule
-                  \multicolumn{1}{l}{bhh}                      & heuristic pool     & all, gd, mh                           \\
-                                                               & population         & 5, 10, 15, 20, 25                     \\
-                                                               & credit             & ibest, pbest, rbest, gbest, symmetric \\
-                                                               & reselection        & 1, 5, 10, 15, 20                      \\
-                                                               & replay             & 1, 5, 10, 15, 20                      \\
-                                                               & reanalysis         & 1, 5, 10, 15, 20                      \\
-                                                               & burn in            & 0, 5, 10, 15, 20                      \\
-                                                               & normalise          & false, true                           \\
-                                                               & discounted rewards & false, true                           \\
-            \end{tabular}%
-      }
-\end{table}%
-
-In Table \ref{tab:methodology:experiments:bhh_variants}, the \index{heuristic pool}heuristic pool configuration \textit{gd} refers to the \index{heuristic pool}heuristic pool configuration where only gradient-based \index{heuristic}heuristics are included, and \textit{mh} refers to the \index{heuristic pool}heuristic pool configuration where only \acp{MH} are included.
-
-\section{Statistical Analysis}
-\label{sec:methodology:statistical_analysis}
-
-This section provides the detail of the process that is used to execute the statistical analysis of the results.
-
-Various experimental groups and configurations have been presented in Sections \ref{sec:methodology:experiments:case_study}, \ref{sec:methodology:experiments:standalone_optimisers} and \ref{sec:methodology:experiments:bhh_variants}.
-The results from each of these experimental groups are statistically analysed.
-To ensure that there are sufficient samples for statistical analysis, each experiment and configuration is trained for 30 epochs and is repeated over 30 runs, for each of the fourteen datasets.
-The experimental results contain performance evaluation data for the training and testing datasets, and includes loss and accuracy measurements.
-Statistical analysis is executed on the results from the testing datasets.
-An average rank is calculated across all 30 runs, for all experimental groups and configurations, at each step, for every epoch of training.
-Each run is executed using a unique random seed, such that each run is identical in its setup and configuration, but unique between runs.
-
-The evaluation of outcome is based on the aggregated statistical results as mentioned above.
-A descriptive analysis is executed on the spread of the data.
-The results are analysed and checked for overfitting and outliers are identified.
-The skewness of the results is evaluated per dataset and the \index{Shapiro-Wilk}Shapiro-Wilk test for normality~\cite{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
-Furthermore, the \index{Levene}Levene's test for equality of variance~\cite{ref:levene:1961} ($\alpha$ = 0.001) is used.
-The output of the full statistical analysis is presented in Appendix \ref{app:statistical_analysis}.
-
-Dependent on the outcomes of the above statistical tests, the appropriate statistical significance test is then executed.
-For experiments where there are only two configurations, the Mann-Whitney U\index{Mann-Whitney U} independent samples t-Test~\cite{ref:mann:1947} ($\alpha$ = 0.001) is executed.
-For experiments with three or more configurations, the \acs{ANOVA} statistical test~\cite{ref:fisher:1921} ($\alpha$ = 0.001) is used.
-The\index{Kruskal-Wallis} Kruskal-Wallis ranked non-parametric test~\cite{ref:kruskal:1952} for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
-
-Regardless of the statistical test that is used, a post-hoc Tukey honest significant difference test~\cite{ref:tukey:1949} ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
-Descriptive and critical difference plots are then retrieved from these results to provide visual aid.
-
-\section{Implementation and Execution}\label{sec:methodology:implementation}
-
-All implementations are done from first principles in Python 3.9 using Tensorflow 2.7 and Tensorflow Probability 0.15.0.
-Most underlying mathematical functions are reused from the Tensorflow library, however, all \index{heuristic}heuristics are implemented from first principles to fit the \acs{HH} framework that was developed.
-The source code and data for this dissertation is provided and made public at \url{https://github.com/arneschreuder/masters}.
-
-It should be noted that this implementation makes heavy use of CPU processing, due to flattening of the \acs{FFNN} weights by the \index{heuristic}heuristics.
-For this reason, execution is much more timely and costly than with GPU training.
-
-All experiments were run on the Centre for High Performance Computing (CHPC) cluster.
-A total of 14 different server were used, each running 24 to 56 cores and 256GB of memory.
-The entire empirical process took six days.
-
-\section{Summary}\label{sec:methodology:summary}
-
-This chapter provided the detail around the methodology that was used to execute the empirical process.
-The datasets, \acp{FFNN} and \index{heuristic}heuristics that are used during the empirical process have been presented in detail, along with details around various \acs{BHH} configurations.
-A baseline \acs{BHH} has been formulated.
-The empirical process was defined in terms of a number of different experimental groups and finally, the process of statistical analysis of the results was provided.
-
-The results and findings of the empirical process are presented in the following chapter.

### 2023-02-01 article/sections/01-introduction.tex
🚧 (article): Save point, WIP

@@
 
-Over the past few years, modern hardware capabilities have improved to the point where workloads in the field of \acs{ML} that were previously computationally infeasible, are now possible.
-One such sub-field of \acs{ML} is \acp{ANN}.
-The performance and capabilities of \acp{ANN} is largely influenced by the learning process used.
-As such, a popular field of focus for studying \acp{ANN} is the process by which these models are trained.
-\acp{ANN} are trained by optimisation algorithms known as heuristics.
-
-Many different heuristics have been developed and used to train \acp{ANN}  \cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
+A popular field of focus for studying \acp{ANN} is the process by which these models are trained.
+\acp{ANN} are trained by optimisation algorithms known as heuristics Many different heuristics have been developed and used to train \acp{ANN}  \cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
 Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses.
@@
 
-A recent suggestion related to the field of \index{meta-learning}meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process.
+A recent suggestion related to the field of meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process.
 This approach focuses on the hybridisation of learning paradigms.
@@
 This research takes a particular interest in developing a population-based, selection \acs{HH} that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process.
-This research presents the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \index{Bayesian analysis}\textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
+This research presents the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
 This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.
-This process takes place dynamically and during the training process (online learning).
 
@@
 Section  \ref{sec:heuristics} provides details on various types of heuristics that have been used to train \acp{FFNN}.
-Section  \ref{sec:hhs} presents background information on \acp{HH} and \index{meta-learning}meta-learning.
+Section  \ref{sec:hhs} presents background information on \acp{HH} and meta-learning.
 Section  \ref{sec:probability} presents background information on probability theory.

### 2023-02-01 article/sections/02-artificial-neural-networks.tex
🚧 (article): Save point, WIP

--- 2023-01-11 article/sections/02-artificial-neural-networks.tex
@@
 \label{sec:anns}
+
+\acp{ANN} can generally be described as well-organised structures of mathematical computation and are inspired by the biological brain  \cite{ref:engelbrecht:2007}.
+\acp{ANN} have been successfully applied to a range of problem classes.
+\citeauthor{ref:engelbrecht:2007}  \cite{ref:engelbrecht:2007} summarises some common problems that are solved using \acp{ANN}.
+These include classification  \cite{ref:khan:2001}, pattern matching  \cite{ref:cannady:1998, ref:kumar:1994}, pattern completion  \cite{ref:dayhoff:2001}, optimisation  \cite{ref:specht:1991} and data mining  \cite{ref:singh:2009}.
+\Acp{AN} provide the fundamental building blocks for \acp{ANN}.
+
+The fundamental building blocks of \acp{ANN} is the \acs{AN}.
+The \acs{AN} implements a non-linear mapping from some $I$-dimensional, real-numbered input space to some $T$-dimensional, real-numbered output space.
+The output space is usually in the ranges $[0,1]$ or $[-1,1]$, depending on the problem being solved \cite{ref:engelbrecht:2007}.
+In essence, the \acs{AN} implements a weighted sum of its inputs and applies some non-linear transformation as a decision making boundary.
+
+Multiple \acp{AN} can be organised and used together forming a ``network'' of \acp{AN} referred to as an \acf{ANN}.
+The architecture of the \acs{ANN} refers to the way in which \acp{AN} are organised.
+\acp{ANN} can be organised in layers where a single layer can contain multiple \acp{AN}.
+Output from one layer is propagated as input to the next layer.
+The topology of the \acs{ANN} refers to the way that layers of \acp{AN} are connected to each other.
+There are many different topologies  \cite{ref:miikkulainen:2010}.
+
+This research focuses on a particular type of \acs{ANN}, referred to as \acp{FFNN}.
+\acp{FFNN} were the first and simplest type of \acp{ANN} developed  \cite{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order.
+Furthermore, \acp{FFNN} implement fully connected topologies, where each \acs{AN} in one layer is connected to all \acp{AN} in the next, without any cycles  \cite{ref:zell:1994}.In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
+
+\textit{Training} is the process whereby the weights of the \acs{FFNN} are systematically changed with the aim of improving the \textit{performance} of the \acs{FFNN}.
+Finding the optimal weights that produce the best performance on a given task is an optimisation problem.
+The optimisation algorithm used to find the optimal weights is referred to as a \textit{heuristic}.
+Heuristics search for possible solutions in the solution-space and make use of information from the search space to guide to process.
+
+During the training process, the \acs{FFNN} is exposed to data while trying to produce some target outcome.
+The degree to which the produced outcome differs from the target outcome is referred to as \textit{loss}.
+Since training of \acp{FFNN} is an optimisation problem, the goal of the training process is to minimise the loss.
+The loss is calculated using an error function.
+
+Supervised learning is the process of training where the data that is presented to the \acs{FFNN} during training, includes the desired solution  \cite{ref:geron:2017}.
+The \acs{FFNN} learns the mapping function from the input to the target output  \cite{ref:brownlee:2016}.

### 2023-02-01 article/sections/03-heuristics.tex
🚧 (article): Save point, WIP

@@
 
-A \index{heuristic}heuristic refers to an algorithmic search technique that serves as a guide to a search process where good solutions to a optimisation problem is being sought out.
+A heuristic refers to an algorithmic search technique that serves as a guide to a search process where good solutions to a optimisation problem is being sought out.
 Many different techniques have been used to train \acp{FFNN} \cite{ref:kingma:2014}.
@@
 
-\subsection{Gradient-Based Heuristics}\label{sec:heuristics:gd}
+Gradient-based heuristics are optimisation techniques that make use of derivates obtained from evaluating the \acs{ANN} being trained.
+In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{ANN} and the desired output.
+When using \acs{GD} to train \acp{ANN}, the loss function is used to adjust the weights of the \acs{ANN} in order to minimise the error \cite{ref:engelbrecht:2007}.
 
-Gradient-based \index{heuristic}heuristics are optimisation techniques that make use of derivates obtained from evaluating the \acs{ANN} being trained.
-In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{ANN} and the desired output.
-When using \acs{GD} to train \acp{ANN}, the \index{loss function}loss function is used to adjust the weights of the \acs{ANN} in order to minimise the error \cite{ref:engelbrecht:2007}.
-
-The simplest type of \acs{GD} algorithm is referred to as \acs{SGD}, which implements a gradient-based weight update step for each training pattern. The weight update step and is given as
-
-\begin{equation}
-	\label{eq:heuristics:gd:sgd}
-	\begin{split}
-		\boldsymbol{w} = \boldsymbol{w} - \eta \boldsymbol{g}
-	\end{split}
-\end{equation}
-
-where $\boldsymbol{w}$ refers to the weight vector, $\eta$ refers to the learning rate, which controls the step size and $\boldsymbol{g}$ refers to the gradient of the error function relative to weight vector.
-
-There are many variants of gradient-based \index{heuristic}heuristics, however, they all fundamentally apply the same generic \acf{GD} framework that propagates the error signal backwards through the \acs{ANN}.
+There are many variants of gradient-based heuristics, however, they all fundamentally apply the same generic \acf{GD} framework that propagates the error signal backwards through the \acs{ANN}.
 This algorithm is known as \acf{BP}.
 \Acs{BP} was popularised by \citeauthor{ref:werbos:1994} \cite{ref:werbos:1994}.
-\citeauthor{ref:engelbrecht:2007} \cite{ref:engelbrecht:2007} describes the \acs{BP} process in two steps.
-During the forward pass step, the output values of the \acs{FFNN} is calculated for each training pattern.
-Then, during the backward propogation step, the error signal is propagated backwards from the output layer, through the hidden layer, to the input layer of the \acs{FFNN}.
-Weights at the output and hidden layers are then adjusted as functions of the backpropagated error signal.
 
+The simplest type of \acs{GD} algorithm is referred to as \acs{SGD}, which implements a gradient-based weight update step for each training pattern.
 In the context of this research, the implementation of \acs{SGD} refers to the mini-batch training implementation of \acs{GD}, where a small batch of training patterns are fed to the \acs{FFNN} at once and the error function is aggregated across all training patterns.
@@
 
-\subsection{Meta-Heuristics}\label{sec:heuristics:mh}
-
 Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus \cite{ref:bengio:2000, ref:feurer:2019}.
 \citeauthor{ref:blum:2003} \cite{ref:blum:2003} mention that since the 1980's, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
-These methods are referred to as \index{meta-heuristic}\textit{meta-heuristics}.
+These methods are referred to as \acp{MH}.
 

### 2023-02-01 article/sections/04-hyper-heuristics.tex
🚧 (article): Save point, WIP

@@
 
-~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} define \acp{HH} as search methods or learning mechanism for selecting or generating heuristics to solve computational search problems.~\citeauthor{ref:burke:2003}~\cite{ref:burke:2003} mentions that a \acs{HH} is a high-level approach that, given a particular problem instance and a number of low-level heuristics, can select and apply an appropriate low-level heuristic at each decision point.
-
-\citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} states that \acp{HH} promote the design of more generally applicable search methodologies and tend to perform relatively well on a large set of different problems, in contrast to specialised algorithms, which typically focus on outperforming the state-of-the-art for a single application.
-
-\acp{HH} implement a form of \index{meta-learning}meta-learning that is concerned with the selection of the best heuristic from a pool of heuristics to solve a given problem.
-In the context of population-based \acp{HH}, an entity pool exists that represent a pool of candidate solutions to the given problem.
-Each entity in the entity pool is assigned its own low-level \index{heuristic}heuristic from the heuristic pool.
-
-The selection of the best heuristic to apply to a candidate solution, is based on the performance of the heuristic relative to that particular candidate solution at a particular point in the search process.
-It can be said that \acp{HH} are concerned with finding the best \index{heuristic}heuristic in \textit{heuristic space}, while the underlying low-level \index{heuristic}heuristics find solutions in the feasible \textit{search/solution space}.
-
-\citeauthor{ref:grobler:2015}~\cite{ref:grobler:2015} highlights two fundamental ideas behind \acp{HH}.
-Firstly, the recognition that the process of selecting or designing efficient hybrid and/or cooperative heuristics can be regarded as a computational search problem in itself.
-Secondly, there is significant potential to improve search methodologies by the incorporation of learning mechanisms that can adaptively guide the search.
-These two fundamental ideas have inspired different types of hyper-heuristics~\cite{ref:burke:2010}.
-
-In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
-Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimization.
-Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
-The following section provides a framework for \acs{HH} classification.
-
-\subsection{Classification of Hyper-Heuristics}\label{sec:hh:classification}
+~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} define \acp{HH} as search methods or learning mechanism for selecting or generating heuristics to solve computational search problems.~\citeauthor{ref:burke:2003}~\cite{ref:burke:2003} mentions that a \acs{HH} is a high-level heuristic approach that, given a particular problem instance and a number of low-level heuristics, can select and apply an appropriate low-level heuristic at each decision point.
+\acp{HH} implement a form of meta-learning that is concerned with the selection of the best heuristic from a pool of heuristics to solve a given problem.
+It can be said that \acp{HH} are concerned with finding the best heuristic in \textit{heuristic space}, while the underlying low-level heuristics find solutions in the feasible \textit{search/solution space}.
 
@@
 These include the \textit{source of feedback} used during learning and the nature of the \textit{heuristic search space}.
-Figure \ref{fig:heuristics:hh:classification} presents the classification scheme as proposed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}.
+For the dimension that involves the source of feedback, \acp{HH} can be classified as either \textit{no learning}, \textit{online learning} or \textit{offline learning}.
+For the dimension that involves the nature of the \textit{heuristic search space}, \acp{HH} can be classified as either \textit{heuristic selection} or \textit{heuristic generation}.
+Further distinction is made between construction heuristics and perturbation heuristics.
 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.85\textwidth]{images/hh_classification.pdf}
-	\caption{A classification of \acs{HH} approaches, according to two dimensions: (i) the source of feedback used during learning, and (ii) the nature of the heuristic search space.}
-	\label{fig:heuristics:hh:classification}
-\end{figure}
+In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
+Some notable examples include \cite{ref:dowsland:2007, ref:burke:2010, ref:grobler:2012, ref:vanderstockt:2018}.
+Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides some of the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
 
-\subsubsection{Source of Feedback}
-
-\acp{HH} make use of feedback from the search process to adapt and guide the search process.
-Some \acp{HH} implement a learning mechanism that utilises this feedback.
-Learning \acp{HH} can implement a form of \index{online learning}\textit{online learning} or \index{offline learning}\textit{offline learning}.
-
-\acp{HH} that implement \index{online learning}online learning, implement a form of learning that continues to takes place while the algorithm is solving an instance of the underlying optimisation problem.
-Task-dependent, local properties can be used by the high-level \index{heuristic}heuristic to determine the appropriate low-level heuristic to apply at various points in the search process.
-Examples of \index{online learning}online learning approaches within \acp{HH} include the use of \acf{RL} and \acfp{MH} as high-level search strategies.
-
-\acp{HH} that implement \index{offline learning}offline learning, implement a form of learning where knowledge, in the form of rules or programs, is gathered from a set of training instances and is then applied independently from the search process itself.
-Examples of offline learning approaches within hyper-heuristics include \textit{learning classifier systems} and \textit{case-based reasoning}.
-
-\subsubsection{Heuristic Search Space}
-According to the classification proposed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the second dimension of classification involves the nature of the \index{heuristic}heuristic search space.
-Distinction is made between \index{heuristic}heuristic \textit{selection} and heuristic \textit{generation}.
-
-\subsubsection{Selection vs. Generation}
-
-Selection \acp{HH} implement a high-level search mechanism that is used to determine which heuristic to apply to the underlying optimisation problem at a given point in the optimisation process.
-Selection mechanisms can include probabilistic approaches or high level \acfp{MH}.
-On the contrary, \index{heuristic}heuristic generation methodologies implement a mechanism that generate new heuristics from a pool of \textit{components} of various heuristics.
-Generation \acp{HH} often make use of \acfp{EA}~\cite{ref:burke:2010}.
-
-Selection \acp{HH} consist of two components, including a low-level \index{heuristic}heuristic selection strategy and a move acceptance strategy.
-Low-level \index{heuristic}heuristic selection can be done in a simple, \textit{non-adaptive} way.
-No learning is involved in these approaches.
-For non-adaptive techniques, heuristic selection is based on a predefined heuristic ordering that is generated either randomly or in a ordered cycle that is repeated throughout the optimisation process~\cite{ref:cowling:2000}.
-As an alternative, heuristic selection may incorporate an \textit{adaptive} (\index{online learning}\textit{online learning}) mechanism, based on the probabilistic weighting of the low-level heuristics~\cite{ref:burke:2003} or some type of performance statistics~\cite{ref:cowling:2000}.
-
-A move acceptance strategy is the mechanism by which the application of a low-level \index{heuristic}heuristic is either accepted or rejected.
-In general, a move is accepted or rejected based on the quality of the move and the current solution during a single point search.~\citeauthor{ref:burke:2003}~\cite{ref:burke:2003} mention that many move acceptance strategies have been explored within \acp{HH}.
-
-Move acceptance strategies can be divided into two categories.
-These include \textit{deterministic} and \textit{non-deterministic} move acceptance strategies.
-Deterministic move acceptance strategies generate the same result for the same candidate solution(s) used for the move acceptance test.
-Non-deterministic move acceptance strategies can involve other parameters, such as the current time, or a sampling operation that yields possibly different outcomes when repeated for the move acceptance test~\cite{ref:burke:2003}.
-
-\subsubsection{Construction vs. Perturbation}
-
-Selection and generation \acp{HH} can be further classified in terms of \textit{construction} and \textit{perturbation} mechanisms.
-According to~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, construction approaches build a solution incrementally.
-Starting with an empty solution, the goal is to intelligently select and use construction heuristics to gradually build a complete solution.
-As such, the \acs{HH} framework is provided with a set of pre-existing construction heuristics.
-
-Perturbation  approaches refer to approaches that start with a complete solution, generated either randomly or using simple construction heuristics.
-Perturbation heuristics try to iteratively improve the current solution.
-As such, the hyper-heuristic framework is provided with a set of neighbourhood structures and/or simple local searchers.
+This research takes a particular interest in a population-based, selection approach for \acp{HH}, with the particular intent of training \acp{FFNN}.
+In the context of population-based \acp{HH}, an entity pool exists that represent a pool of candidate solutions to the given problem.
+Each entity in the entity pool is assigned its own low-level heuristic from the heuristic pool.
+The selection of the best heuristic to apply to a candidate solution, is based on the performance of the heuristic relative to that particular candidate solution at a particular point in the search process.
+Selection methods often make use of probabilistic approaches.

### 2023-02-01 article/sections/05-probability.tex
🚧 (article): Save point, WIP

@@
 
-Probability theory and statistics can be traced back to as early as the 18th century.
-In 1718,~\citeauthor{ref:demoivre:1718}~\cite{ref:demoivre:1718} published the \textit{Doctrine of Chance}; a book that is widely regarded as the first published book on probability theory.
-In 1763, Thomas Bayes~\cite{ref:bayes:1763} published an article titled \textit{An Essay towards solving a Problem in the Doctrine of Chances} where the first version of \index{Bayes' theorem}Bayes' theorem was introduced.
-
-Probability theory, statistics and \acf{ML} are transdisciplinary fields with many shared concepts.
-There are many examples of how probability theory has been incorporated into \acs{ML} research.
-In 1991,~\citeauthor{ref:denker:1991}~\cite{ref:denker:1991} proposed a way to transform \acf{ANN} outputs to probability distributions.
-In 1993, \citeauthor{ref:neal:1993}~\cite{ref:neal:1993} developed a \acf{MCMC} sampling algorithm for \acfp{BNN}.
-These are but a few examples of the role that probability theory has played in \acs{ML} research in the past.
-
-Chapter \ref{chap:hhs} provided the concept of a \acf{HH}.
-This dissertation aims to develop a selection \acs{HH} that makes use of probability theory to select the best \acs{HH} to solve a given problem.
-This chapter aims to provide the necessary background information on probability theory and statistics.
-These are large fields and focus is put on the elements that are required to formulate the proposed \acf{BHH}.
-
-\section{Overview of Probability}\label{sec:probability:overview}
-
-In everyday conversation, the term \textit{probability} is a measure of belief in the occurrence of a future event~\cite{ref:wackerly:2014}.
-Probability is a necessary tool used in many fields including physics, biology, chemistry and computer science.
-These fields contain many cases that generate observations that cannot be predicted with absolute certainty~\cite{ref:wackerly:2014}.
-Probability can be inferred and confirmed through past events.
-These events are referred to as \textit{random} or \textit{stochastic} events.
-The probability that a certain event, $A$, might occur is denoted by $P(A)$.
-Although these random events cannot be predicted with absolute certainty, the relative frequency with which they occur over many trials, is often remarkably stable.
-
-Consider flipping an unbiased, fair coin.
-The coin has two possible outcomes.
-It can conclude that each side has a $\frac{1}{2}$ or $50\%$ chance of occurring.
-In statistics, the decimal probability notation is used, where $0 <= P(A) <= 1$.
-Suppose the fair coin is thrown 10 times, there is no guarantee of observing $0.5$ heads and $0.5$ tails.
-There is some probability (although small) that the coin might fall on heads $0/10$ times.
-The probability of such an event occurring is $0.0009765625$.
-In the coin flip example, the \acf{CLT} shows that the normalised sum of events tends toward a normal distribution with a mean value of $0.5$, if the number of events observed, $N$, is large~\cite{ref:wackerly:2014}.
-The larger the value of $N$, the higher the confidence of mean probability and relative frequency of the event.
-The stable long-term relative frequency by which a random event occurs, provides an intuitive and meaningful measure of belief that a certain event will occur again at some point in the future~\cite{ref:wackerly:2014}.
-
-Probability can also be expressed over multiple random events.
-Multiple random events can be considered together, dependently or conditionally.
-The following sections provide insight into conditional and joint probabilities of multiple random events.
-
-\index{Bayes' theorem}
-\begin{theorem}[\textbf{Bayes' theorem}]
-	\label{th:probability:bayes_theorem:theorem}
-	Assume that $\{B_{1}, B_{2}, \dots, B_{K}\}$ is a partition of $S$ such that $P(B_{i}) > 0$, for $i = 1,2, \dots, K$ then\\
-	\\
-	\begin{equation}
-		P(B_{j} \vert A) = \frac{P(A \vert B_{j})P(B_{j})}{\sum_{i=1}^{K} P(A \vert B_{i})P(B_{i})}
-	\end{equation}
-\end{theorem}
-
-\begin{proof}
-	The proof follows from the definition of conditional probability as was presented in Section~\ref{sec:probability:cond_probability}:
+In general, there are two main views to probability and statistics.
+These include the \textit{frequentist} and the \textit{Bayesian} view of statistics.
+Naturally, Bayesian statistics is based on Bayes' theorem, which is given as
 
 \begin{equation}
-		\begin{split}
-			P(B_{j} \vert A)
-			&= \frac{P(A \cap B_{j})}{P(A)}\\
-			&= \frac{P(A \vert B_{j})P(B_{j})}{\sum_{i=1}^{K} P(A \vert B_{i})P(B_{i})}
-		\end{split}
-	\end{equation}
-\end{proof}
-
-One of the many applications of \index{Bayes' theorem}Bayes' theorem is to do statistical inference.
-\index{Bayes' theorem}Bayes' theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
-
-\section{Conjugate Priors}\label{sec:probability:conjugate_priors}
-
-\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} state that conjugate priors are prior probability distributions that result in posterior distributions that are of the same functional form, $\mathcal{A}(v)$, as the prior, but with different parameter values.
-This section considers the conjugate priors that are used with the Binomial likelihood and Categorical/Multinomial likelihood.
-
-\subsection{Binomial Likelihood}\label{sec:probability:conjugate_priors:binom_likelihood}
-
-The conjugate prior to a \index{Bernoulli probability distribution}Bernoulli probability distribution is the \index{Beta probability distribution}Beta probability distribution
-\cite{ref:wackerly:2014}. This is shown by demonstrating that the posterior distribution has the
-same functional form, $\mathcal{A}(v)$, as the prior distribution as follows. \\\\
-\textbf{Setup}:
-
-\begin{itemize}
-	\item Let $I$ be a number of independent, identical  (iid) random events.
-
-	\item Let $\alpha \in \mathbb{R}, \alpha > 0$ and $\beta \in \mathbb{R}, \beta >0$ be the shape parameters to the \index{Beta probability distribution}Beta probability distribution.
-
-	\item Let $\theta$ be the probability of a success. With $\theta | \alpha, \beta \sim Beta(\alpha, \beta)$.
-
-	\item $P(\theta)$ is the prior probability distribution with the functional form $\mathcal{A}(v)$.
-
-	\item Let $\boldsymbol{X} = (x_{1}, \dots, x_{I})$ be the outcomes of $I$ independent, identical random events, each with Boolean outcome.
-That is $x_{i} | \theta \overset{\text{iid}}{\sim} Ber(\theta)$ and $\mathcal{L}(x_{i} \vert \theta)$ is the Bernoulli likelihood.
-
-	\item Let $\boldsymbol{\mathcal{D}}$ denote all the prior data of $\boldsymbol{X}$, parameterised by $\alpha$, $\beta$.
-
-	\item Let $N_{1} = \sum_{i=1}^{I} \mathbbm{1}(x_{i} = 1)$ and $N_{0} = \sum_{i=1}^{I} \mathbbm{1}(x_{i} = 0)$.
-\end{itemize}
-
-The Bernoulli likelihood is given as
-
-\begin{equation}
-	\label{eq:probability:conjugate_priors:binom_likelihood:likelihood}
-	\begin{split}
-		\mathcal{L}(\boldsymbol{\mathcal{D}}) &=  P(\boldsymbol{\mathcal{D}} | \theta) \\
-		&\propto \theta^{N_{1}}(1-\theta)^{N_{0}}
-	\end{split}
+	\label{eq:bayes}
+	P(A \vert B) = \frac{P(B \vert A)P(A)}{P(B)}
 \end{equation}
 
-By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\boldsymbol{\mathcal{D}}$ is given as
+Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event and the conditions under which the event happened~\cite{ref:hackenberger:2019}.
+Bayes' theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
 
-\begin{equation}
-	\begin{split}
-		\label{eq:probability:conjugate_priors:binom_likelihood:posterior}
-		P(\theta \vert \boldsymbol{\mathcal{D}}) &= \frac{P(\boldsymbol{\mathcal{D}} | \theta) P(\theta)}{P(\boldsymbol{\mathcal{D}})}
-	\end{split}
-\end{equation}
+One of the many applications of Bayes' theorem is to do statistical inference.
+Like \acp{FFNN}, Bayesian models need to be \textit{trained}, a process known as \textit{Bayesian analysis}.
+Bayesian analysis is the process by which prior beliefs are updated as a result of observing new data/evidence.
 
-Since the denominator sums to $1$, the denominator and constants for the Bernoulli likelihood and the Beta prior can be removed by expressing the posterior as proportional to the likelihood times the prior as follows:
-
-\begin{equation}
-	\label{eq:probability:conjugate_priors:binom_likelihood:posterior_propto}
-	\begin{split}
-		P(\theta | \boldsymbol{\mathcal{D}}) &\propto \left[\theta^{N_{1}}(1-\theta)^{N_{0}}\right] \left[\theta^{\alpha - 1} (1 - \theta)^{\beta - 1}\right] \\
-		&\propto \theta^{(N_{1} + \alpha) - 1}(1-\theta)^{(N_{0} + \beta) - 1} \\
-		&\propto Beta(N_{1} + \alpha, N_{0} + \beta)
-	\end{split}
-\end{equation}
-
-The posterior distribution has the same functional form, $\mathcal{A}(v)$, as the prior, but with updated prior parameters $\alpha' = N_{1} + \alpha$ and $\beta' = N_{0} + \beta$.
-This shows that the \index{Beta probability distribution}Beta probability distribution is the conjugate prior used with the Bernoulli likelihood.
-
-\subsection{Categorical and Multinomial Likelihood}
-\label{sec:probability:conjugate_priors:cat_mult_likelihood}
-
-The conjugate prior to a \index{Categorical probability distribution}Categorical and \index{Multinomial probability distribution}Multinomial probability distribution is the \index{Dirichlet probability distribution}Dirichlet probability distribution~\cite{ref:wackerly:2014}.
-The proof of the conjugate prior for the \index{Bernoulli probability distribution}Bernoulli probability distribution is similar to the proof presented in Section \ref{sec:probability:conjugate_priors:binom_likelihood}.
-This means that the posterior distribution must have the same functional form, $\mathcal{A}(v)$, as the prior distribution.
-The proof is shown as follows.
-\\\\
-\textbf{Setup}:
-
-\begin{itemize}
-	\item Let $I$ be a number of independent, identical (iid) random events.
-
-	\item Let $K$ be a number of possible outcomes for each event, with $K \geq 2$.
-
-	\item Let $\boldsymbol{\alpha} = (\alpha_{1}, \dots, \alpha_{K}), \forall_{k=1}^{K} \alpha_{k} \in \mathbb{R}, \alpha_{k} > 0$ be the concentration parameters to the \index{Dirichlet probability distribution}Dirichlet probability distribution.
-
-	\item Let $\boldsymbol{\theta} = (\theta_{1}, \dots, \theta_{K}), \forall_{k=1}^{K} \theta_{k} \in (0,1), \sum_{k}^{K} \theta_{k} = 1$ be the probability of each class in $K$ and $\boldsymbol{\theta}$ belongs to the standard $K-1$ probability simplex $S$.
-With $\boldsymbol{\theta} | \boldsymbol{\alpha} \sim Dir(K, \boldsymbol{\alpha})$.
-
-	\item $P(\boldsymbol{\theta})$ is the prior probability distribution with the functional form $\mathcal{A}(v)$.
-
-	\item Let $\boldsymbol{X} = (\boldsymbol{x_{1}}, \dots, \boldsymbol{x_{I}})$ be the outcomes of $I$ independent, identical random events, each with $K$ possible outcomes.
-That is $\boldsymbol{x_{i}} | \boldsymbol{\theta} \overset{\text{iid}}{\sim} Cat(\boldsymbol{\theta})$ and $\mathcal{L}(\boldsymbol{x_{i}} \vert \boldsymbol{\theta})$ is the Categorical likelihood.
-
-	\item Let $\boldsymbol{\mathcal{D}}$ denote all the prior data of $\boldsymbol{X}$, parameterised by $\boldsymbol{\alpha}$.
-
-	\item Let $\boldsymbol{N} = (N_{1}, \dots, N_{K}), N_{k} = \sum_{i=1}^{I} \mathbbm{1}(x_{i,k} = 1)$, denote the counts for each occurrence of a class $k$.
-\end{itemize}
-
-The likelihood of the Categorical and \index{Multinomial probability distribution}Multinomial probability distributions is given as
-
-\begin{equation}
-	\label{eq:probability:conjugate_priors:mult_likelihood:likelihood}
-	\begin{split}
-		\mathcal{L}(\boldsymbol{\mathcal{D}}) &=  P(\boldsymbol{\mathcal{D}} | \boldsymbol{\theta}) \\
-		&\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}}
-	\end{split}
-\end{equation}
-
-By \index{Bayes' theorem}Bayes' theorem, the posterior distribution with given prior data $\boldsymbol{\mathcal{D}}$ is given as
-
-\begin{equation}
-	\label{eq:probability:conjugate_priors:mult_likelihood:posterior}
-	\begin{split}
-		P(\boldsymbol{\theta} \vert \boldsymbol{\mathcal{D}}) &= \frac{P(\boldsymbol{\mathcal{D}} \vert \boldsymbol{\theta}) P(\boldsymbol{\theta)}}{P(\boldsymbol{\mathcal{D}})}
-	\end{split}
-\end{equation}
-
-Since the denominator sums to $1$, the denominator and constants for the \index{Dirichlet probability distribution}Dirichlet prior can be removed by expressing the posterior as proportional to the likelihood times the prior as follows:
-
-\begin{equation}
-	\label{eq:probability:conjugate_priors:mult_likelihood:posterior_propto}
-	\begin{split}
-		P(\boldsymbol{\theta} \vert \boldsymbol{\mathcal{D}}) &\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}} \prod_{k=1}^{K} \theta_{k}^{\alpha_{k} - 1}\\
-		&\propto \prod_{k=1}^{K} \theta_{k}^{(N_{k} + \alpha_{k}) - 1} \\
-		&\propto Dir(K, \boldsymbol{N} + \boldsymbol{\alpha})
-	\end{split}
-\end{equation}
-
-The posterior distribution has the same form, $\mathcal{A}(v)$, as the prior, but with updated prior parameters $\boldsymbol{\alpha'} = \boldsymbol{N} + \boldsymbol{\alpha}$.
-This shows that the \index{Dirichlet probability distribution}Dirichlet probability distribution is the conjugate prior used with the Categorical/Multinomial likelihood.
-
-\section{Bayesian Statistics}
-\label{sec:probability:bayesian_statistics}
-
-This section provides detailed discussions on various aspects related to Bayesian statistics and probability.
-Brief discussion follow on the frequentist and the Bayesian approach to statistics and probability.
-Finally, the concept of Bayesian analysis is presented in detail.
-
-\subsection{Frequentist vs. Bayesian Statistics}
-\label{sec:probability:bayesian_statistics:frequentist_vs_bayesian}
-
-In general, there are two main views to probability and statistics.
-These include the \textit{frequentist} and the \textit{Bayesian} view of statistics.
-Naturally, Bayesian statistics is based on \index{Bayes' theorem}Bayes' theorem as was presented in Section \ref{sec:probability:bayes_theorem}.
-Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event and the conditions under which the event happened~\cite{ref:hackenberger:2019}.
-To introduce the concept of Bayesian inference and Bayesian analysis, the differences between the frequentist and the Bayesian view of statistics need to be presented.
-
-Bayesian statistics out-date the frequentist approach, but lacked interest in the early days, partly because of the limited applications where the conjugate priors where known~\cite{ref:hackenberger:2019}.
-More recent advancements in mathematical methods popularised the Bayesian approach again.
-A notable contribution to this switch was the development of the \acf{MCMC} algorithm in the 1950s.
-This family of algorithms allowed for the construction of random sampling algorithms from a probability distribution, which allows for the calculation of Bayesian hierarchical models~\cite{ref:hackenberger:2019}.
-Soon after followed one of the earliest papers that use Bayesian statistics in the field of medicine in 1982~\cite{ref:ashby:2006}.
-
-The difference between the frequentist approach and the Bayesian approach can be illustrated using an example.~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} suggests an experiment that investigates whether the gender ratio in some hypothetical mice population is $1:1$.
-Two experiments were designed.
-In the first experiment, mice are randomly selected until the first male is chosen.
-The result in this experiment will then be the total number of mice chosen by gender.
-For the second experiment, exactly seven mice are randomly selected.
-The result of the second experiment would be the number of males and females in a sample of seven.
-Suppose the outcome of the experiment was $FFFFFFM$, where $F$ represents a female and $M$ represents a male.
-If the experimental design is not known ahead of time, the result is useless.
-Consider the $p$-value for each of these experiments.
-The $p$-value is the probability of obtaining results at least as extreme as the observed results of a statistical hypothesis test~\cite{ref:thisted:1998}.
-For the first experiment, the $p$-value is $0.031$ and for the second experiment, the $p$-value is $0.227$.
-Using a confidence level of $\alpha = 0.05$, opposite outcomes could be concluded for these two experiments when it comes to rejecting the null hypothesis, despite using the same data.
-The reason for the difference in outcomes, is due to the difference in their null distributions, which represent the probability distribution of the test statistic when the null hypothesis is true.
-The first approach uses a geometrical approach, and the second used a binomial approach as illustrated in Figure \ref{fig:probability:bayesian_statistics:mouse_experiment_outcome}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=0.6\textwidth]{images/mouse_experiment_outcome.pdf}
-	\caption{The experimental outcomes for the mice-population experiments as was taken from~\cite{ref:hackenberger:2019} .}
-	\label{fig:probability:bayesian_statistics:mouse_experiment_outcome}
-\end{figure}
-
-If Bayesian statistics is used, the experimental design that was chosen does not matter.
-In Bayesian statistics it is common to use a \index{Beta probability distribution}Beta probability distribution as a prior distribution.
-If the prior distribution is sampled from $Beta(3,3)$, then using Bayesian analysis, the posterior distribution, according to the outcomes of this experiment, would yield $Beta(9,4)$.
-
-~\citeauthor{ref:hackenberger:2019}~\cite{ref:hackenberger:2019} mentions that the $Beta$ probability distribution can be seen as a probability distribution of the occurrence of specific parameters.
-From the information that is now known about the $Beta$ probability distribution, it is possible to calculate the probability that the gender ratio in this mice population is not $1:1$, with the $Beta$ probability distribution as a prior, yielding a $p$-value of $0.92$.
-This means that there is a probability of $92\%$ that the mice population is not $1:1$, regardless of experimental design.
-An illustration of this is given in Figure \ref{fig:probability:bayesian_statistics:mouse_distributions}.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.6\textwidth]{images/mouse_experiment_distributions.pdf}
-	\caption{An illustration of the prior and posterior probability distributions for the outcomes of the mice-population experiment, using a $Beta$ prior, as was taken from~\cite{ref:hackenberger:2019}.}
-	\label{fig:probability:bayesian_statistics:mouse_distributions}
-\end{figure}
-
-Figure \ref{fig:probability:bayesian_statistics:mouse_distributions} shows how the posterior distribution differs from the prior distribution.
-
-\subsection{Bayesian Analysis}
-\label{sec:probability:bayesian_statistics:bayesian_analysis}
-
-Bayesian analysis is the process by which prior beliefs are updated as a result of observing new data/evidence.
-Similar to the approaches followed above to explain Bayesian statistics, a proposal is made to explain Bayesian analysis by means of an example taken from~\cite{ref:wackerly:2014}.
-Let $\boldsymbol{Y} = (Y_{1}, Y_{2}, \dots, Y_{N})$ denote the random variable that is observed over a sample size of $N$.
-Then the likelihood of the sample is given as $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$.
-In the discrete case, the likelihood function is defined to be the joint probability, $P(Y_{1} = y_{1}, Y_{2} = y_{2}, \dots, Y_{N} = y_{n})$, and for the continuous case, yields the joint density of $Y_{1}, Y_{2}, \dots, Y_{N}$, evaluated at $y_{1}, y_{2}, \dots, y_{n}$.
-The Bayesian view models the parameter $\theta$ as a random variable with a probability distribution, referred to as the prior distribution of $\theta$.
-The symbol $\theta$, is included in the notation of $\mathcal{L}$ as an argument to illustrate that this function is dependent, explicitly, on the value of $\theta$.
-Importantly, the prior distribution is specified before any data is collected and represents the theoretical prior knowledge about $\theta$.
-Assume that the parameter $\theta$ has a continuous distribution with density $g(\theta)$ that has no unknown parameters.
-Considering the likelihood of the data and the prior on $\theta$, then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ is given as
-
-\begin{equation}
-	\label{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood}
-	f(y_{1}, y_{2}, \dots, y_{n}, \theta) = \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)
-\end{equation}
-
-The marginal density or mass function of $Y_{1}, Y_{2}, \dots, Y_{N}$ is given as
-
-\begin{equation}
-	\label{eq:probability:bayesian_statistic:bayesian_analysis:marginal_density}
-	m(y_{1}, y_{2}, \dots, y_{n}) = \int_{-\infty}^{\infty} \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)d\theta
-\end{equation}
-
-Finally, the posterior density of $\theta \vert y_{1}, y_{2}, \dots, y_{n}$ denoted by $g^{*}(\theta \vert y_{1}, y_{2}, \dots, y_{n})$, according to \index{Bayes' theorem}Bayes' theorem, is given as
-
-\begin{equation}
-	\label{eq:probability:bayesian_statistic:bayesian_analysis:posterior_density}
-	g^{*}(\theta \vert y_{1}, y_{2}, \dots, y_{n}) = \frac{\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)}{\int_{-\infty}^{\infty} \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)d\theta}
-\end{equation}
-
-\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} mention that the posterior density summarises all the pertinent information about the parameter $\theta$ by making use of the information contained in the prior for $\theta$, as well as the information in the observed data/evidence.
-
-Consider now how Bayesian analysis can be used to update the priors on $\theta$ based on newly observed data.
-As with the example above, the discussion below is taken from~\cite{ref:wackerly:2014}.
-Let $Y_{1}, Y_{2}, \dots, Y_{N}$ denote a random sample from a \index{Bernoulli probability distribution}Bernoulli probability distribution, where $P(Y_{i} = 1) = \theta$ and $P(Y_{i} = 0) = 1 - \theta$ and the prior distribution for $\theta$ is $Beta(\alpha, \beta)$.
-The posterior distribution for $\theta$ can be formulated as follows.
-The Bernoulli probability function is written as
-
-\begin{equation}
-	\label{eq:probability:bayesian_statistic:bayesian_analysis:step_1}
-	P(y_{i} \vert \theta) = \theta^{y_{i}}(1 - \theta)^{1-y_{i}}
-\end{equation}
-
-where $y_{i} = \{0,1\}$ and $0 < \theta < 1$. The likelihood $\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)$ is presented as follows:
-
-\begin{equation}
-	\label{eq:probability:bayesian_statistic:bayesian_analysis:step_2}
-	\begin{split}
-		\mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)
-		&= P(y_{1}, y_{2}, \dots, y_{n} \vert \theta)\\
-		&= \theta^{y_{1}}(1-\theta)^{1 - y_{1}} \times \theta^{y_{2}}(1-\theta)^{1 - y_{2}} \times \dots \times \theta^{y_{n}}(1-\theta)^{1 - y_{n}}\\
-		&= \theta^{\sum y_{i}}(1-\theta)^{n-\sum y_{i}}
-	\end{split}
-\end{equation}
-
-Then the joint likelihood of $Y_{1}, Y_{2}, \dots, Y_{N}, \theta$ from Equation~\eqref{eq:probability:bayesian_statistic:bayesian_analysis:joint_likelihood} is formulated as
-
-\begin{equation}
-	\label{eq:probability:bayesian_statistic:bayesian_analysis:step_3}
-	\begin{split}
-		f(y_{1}, y_{2}, \dots, y_{n}, \theta)
-		&= \mathcal{L}(y_{1}, y_{2}, \dots, y_{n} \vert \theta)g(\theta)\\
-		&= \theta^{\sum y_{i}}(1-\theta)^{n-\sum y_{i}} \times \frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\alpha - 1}(1 - \theta)^{\beta  - 1}\\
-		&= \frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}
-	\end{split}
-\end{equation}
-
-The marginal density of $Y_{1}, Y_{2}, \dots Y_{N}$ is then given as
-
-\begin{equation}
-	\label{eq:probability:bayesian_statistic:bayesian_analysis:step_4}
-	\begin{split}
-		m(y_{1}, y_{2}, \dots, y_{n})
-		&= \int_{0}^{1}\frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}d\theta\\
-		&= \frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\frac{\Gamma(\sum y_{i} + \alpha)\Gamma(n - \sum y_{i} + \beta)}{\Gamma(n + \alpha + \beta)}
-	\end{split}
-\end{equation}
-
-Finally, the posterior density of $\theta$, denoted by $g^{*}(\theta \vert y_{1}, y_{2}, \dots, y_{n})$, is given as
-
-\begin{equation}
-	\label{eq:probability:bayesian_statistic:bayesian_analysis:step_5}
-	\begin{split}
-		g^{*}(\theta \vert y_{1}, y_{2}, \dots, y_{n})
-		&= \frac{\frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}}{\frac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}\frac{\Gamma(\sum y_{i} + \alpha)\Gamma(n - \sum y_{i} + \beta)}{\Gamma(n + \alpha + \beta)}}\\
-		&= \frac{\Gamma(n + \alpha + \beta)}{\Gamma(\sum y_{i} + \alpha)\Gamma(n - \sum y_{i} + \beta)}\theta^{\sum y_{i} + \alpha - 1}(1-\theta)^{n - \sum y_{i} + \beta - 1}
-	\end{split}
-\end{equation}
-
-The posterior density has the same functional form, $\mathcal{A}(v)$, as the prior, yielding the update on prior parameters as $\alpha' = \sum y_{i} + \alpha$ and $\beta' = n - \sum y_{i} + \beta$.
+Bayesian analysis utilises the the concept of conjugate priors.
+\citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} state that conjugate priors are prior probability distributions that result in posterior distributions that are of the same functional form, $\mathcal{A}(v)$, as the prior, but with different parameter values.
+The conjugate prior to a Bernoulli probability distribution is the Beta probability distribution The conjugate prior to a Categorical and Multinomial probability distribution is the Dirichlet probability distribution~\cite{ref:wackerly:2014}.

### 2023-02-01 article/sections/06-bayesian-hyper-heuristics.tex
🚧 (article): Save point, WIP

@@
 \label{sec:bhh}
+
+This section presents the novel \acs{BHH}.
+The general concept of the \acs{BHH} can be summarised as follows: The \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and \acs{FFNN} training process.
+The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process.
+These probabilities are then used as heuristic selection probabilities in the next step of the training process.
+
+According to the classification scheme for \acp{HH} by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \Acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.
+An illustration of the high-level architecture of the \Acs{BHH} is given in Appendix \ref{app:appendix_bhh_architecture} and the high level pseudo-code implementation of the \acs{BHH} is given in Appendix \ref{app:appendix_bhh_algorithm}.
+Discussions follow on the most important components of the \acs{BHH}.
+
+\subsection{Heuristic Pool}\label{sec:bhh:heuristic_pool}
+
+Generally speaking, the heuristic pool is a collection of low-level heuristics under consideration by the \acs{BHH}.
+The heuristic pool contains the set of low-level heuristics that, together with their performance information, make up the \text{heuristic space}.
+Importantly, The heuristic pool must consist of a diverse set of low-level heuristics with varying capabilities.
+This research takes an interest in including both gradient-based heuristics as well as \acp{MH} in the heuristic pool.
+
+\subsection{Proxies}\label{sec:bhh:heuristic:proxies}
+
+The concept of proxies arise from the sparsity of state as maintained by different heuristics.
+Since heuristics maintain (possibly) different states, there is an uncertainty of state transition when switching between heuristics.
+A solution to state indifference is to proxy heuristic state update operations.
+State is then maintained in two parts: primary and proxied state.
+Primary state refers to the state that is originally maintained by a heuristic.
+While proxied state refers to the state that is not directly maintained by the heuristic, but can be updated by outsourcing the required state update operation to another heuristic.
+The \acs{BHH} thus incorporates a mapping of proxied state update operations.
+
+\subsection{Entity Pool}\label{sec:bhh:entity_pool}
+
+The entity pool refers to a collection or \textit{population} of \textit{entities} that each represent a candidate solution to the underlying \acs{FFNN} being trained.
+The \acs{BHH} selects from the heuristic pool a low-level heuristic to be applied to an individual entity.
+The outcome of this selection process is a mapping table that tracks which heuristic has been selected for which entity.
+These heuristic-entity combinations are applied to the underlying \acs{FFNN}.
+The \acs{BHH} tracks the performance of each of these combinations throughout the training process in a performance log.
+
+Entities represent candidate solutions to the model's trainable parameters (weights) and other heuristic-specific state parameters.
+These state parameters are referred to as \textit{local} state.
+Entities are treated as physical \textit{particles} in a hyper-dimensional search environment.
+Entities model concepts from physics.
+For example, the candidate solution is represented as the entity's position, and velocity and acceleration is analogous to the gradient and momentum of the entity respectfully.
+Examples of entity state parameters, as derived from various low-level heuristics, include entity position, velocity, gradient, position delta, first and second moments of the gradient, the loss, personal best positions and losses, and so on.
+The entity state parameters are updated by the associated heuristic.
+
+The population state refers to a collection of parameters that are shared between the entities in the population.
+Population state is also referred to as \textit{global} state and represents the population's memory.
+The population state generally contains state parameters that are of importance to multiple heuristics, and usually tracks the state of the population and not individual heuristic.
+Some examples of population state that can arise from different heuristics include the population of entities themselves, the global best entity found so far, the overall best loss achieved thus far, and so on.
+
+\subsection{Performance Log}\label{sec:bhh:performance_log}
+
+Heuristic selection probability is calculated based on heuristic-entity performance over time.
+Evidence of heuristic-entity performance is thus required for the \acs{BHH} to learn.
+Historical heuristic-entity performance outcomes are stored in a performance log.
+The performance log tracks information such as the current step, selected heuristic, associated entity, the loss achieved and so on.
+Since the performance log can become very big, only a sliding window of the performance history is maintained at each step in the learning process.
+The sliding window is also referred to as a \textit{replay} window/buffer.
+
+\subsection{Credit Assignment Strategy}
+\label{sec:bhh:credit_assignment_strategy}
+
+The credit assignment strategy is a mechanism that assigns a discrete credit indicator to heuristics that perform well, based on their performance metrics such as loss.
+The credit assignment strategy implements the ``move acceptance'' process as proposed by~\citeauthor{ref:ozcan:2006}~\cite{ref:ozcan:2006,ref:ozcan:2008} and addresses the credit assignment problem as discussed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}.
+A good credit assignment strategy will correctly allocate credit to the appropriate heuristic-entity combination.
+This research  implements the following credit assignment strategies to choose from: \textit{ibest} (iteration best), \textit{pbest} (personal best), \textit{gbest} (global best), \textit{rbest} (replay window best), and \textit{symmetric}, where credit is assigned to all entity-heuristic combinations, regardless of their performance.
+
+\subsection{Selection Mechanism}\label{sec:bhh:selection_mechanism}
+
+The \acs{BHH} implements a probabilistic, predictive model based on the fundamentals of the Na\"{\i}ve Bayes algorithm.
+The \acs{BHH} thus distinguishes between the following events: \textbf{$\boldsymbol{H}$}, the event of observing \textit{heuristics}, \textbf{$\boldsymbol{E}$}, the event of observing \textit{entities}, \textbf{$\boldsymbol{C}$}, the event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} are met.
+By Bayes' theorem, the selection mechanism implemented by the \acs{BHH} is given as
+
+\begin{equation}
+	\label{eq:bhh:selection_mechanism:predictive_model_prop_to}
+	\begin{split}
+		P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C};  \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi}) &\propto P(\boldsymbol{E} \vert \boldsymbol{H};  \boldsymbol{\phi})  P(\boldsymbol{C} \vert \boldsymbol{H};  \boldsymbol{\psi}) P(\boldsymbol{H} \vert \boldsymbol{\theta})
+	\end{split}
+\end{equation}
+
+The predictive model thus models the \textit{proportional},probability of the event (selection of) heuristic $\boldsymbol{H}$, given allocation to entity $\boldsymbol{E}$ and credit $\boldsymbol{C}$, parameterised by sampled $\boldsymbol{\theta}$, $\boldsymbol{\phi}$ and $\boldsymbol{\psi}$.
+These parameters are in turn parameterised by concentrations $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$, which denote the prior beliefs of the \acs{BHH}.
+
+\subsection{Optimisation Step}\label{sec:bhh:optimisation_step}
+
+The intent of the \acs{BHH} is to gather evidence that can be used to update prior beliefs about which heuristics perform well during training.
+These beliefs are represented by the concentration parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$.
+A change in prior beliefs is represented by a change in these concentration parameters.
+Specifically, it can be said that the optimisation process implemented by the \acs{BHH} updates \textit{pseudo counts} of events that are observed in the performance logs.
+These pseudo counts track the occurrence of a heuristic, an entity, and resulting performance of these two elements.
+Through the credit assignment strategy, these pseudo counts are biased towards entity-heuristic combinations that meet performance requirements and yield credit allocations.
+
+Generally, there are two different techniques that are used to train Naïve Bayes classifiers. The frequentist approach implements \acs{MLE} and the Bayesian approach implements \acs{MAP}.
+
+\subsubsection{Maximum Likelihood Estimation}\label{sec:bhh:optimisation_step:mle}
+
+The values for $\boldsymbol{\theta}$, $\boldsymbol{\phi}$ and $\boldsymbol{\psi}$ can be estimated by \acs{MLE} as follows:
+
+\begin{equation}
+	\label{eq:bhh:optimisation_step:mle:theta}
+	\begin{split}
+		\hat{\theta}_{k} = E[\theta_{k}] = \frac{N_{k}}{N}
+	\end{split}
+\end{equation}
+
+\begin{equation}
+	\label{eq:bhh:optimisation_step:mle:phi}
+	\begin{split}
+		\hat{\phi}_{j,k} = E[\phi_{j,k}] = \frac{N_{j,k}}{N_{j}}
+	\end{split}
+\end{equation}
+
+\begin{equation}
+	\label{eq:bhh:optimisation_step:mle:psi}
+	\begin{split}
+		\hat{\psi}_{k} = E[\psi_{k}] = \frac{N_{1,k}}{N_{k}}
+	\end{split}
+\end{equation}
+
+\subsubsection{Maximum A Posteriori Estimation}\label{sec:bhh:optimisation_step:map}
+
+Another approach to optimise the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ is to optimise the parameters by their probability distributions' parameters.
+This process is referred to as \textit{Bayesian analysis}.
+Bayesian analysis makes use of the \textit{posterior} probability distribution.
+The concentration update operations yielded by \acs{MAP}, are then be given as
+
+\begin{equation}
+	\label{eq:bhh:optimisation_step:map:alpha_update_operation}
+	\begin{split}
+		\alpha_{k}(t+1) = N_{k} + \alpha_{k}(t)
+	\end{split}
+\end{equation}
+
+\begin{equation}
+	\label{eq:bhh:optimisation_step:map:beta_update_operation}
+	\begin{split}
+		\beta_{j,k}(t+1) = N_{j,k} + \beta_{j,k}(t)
+	\end{split}
+\end{equation}
+
+\begin{equation}
+	\label{eq:bhh:optimisation_step:map:gamma1_update_operation}
+	\begin{split}
+		\gamma_{1,k}(t+1) = N_{1,k} + \gamma_{1,k}(t)
+	\end{split}
+\end{equation}
+
+\begin{equation}
+	\label{eq:bhh:optimisation_step:map:gamma2_update_operation}
+	\begin{split}
+		\gamma_{2,k}(t+1) = N_{0,k} + \gamma_{2,k}(t)
+	\end{split}
+\end{equation}
+
+It can be said that the \acs{BHH} implements a Gaussian process~\cite{ref:gortler:2019}.
+Since the reselection of heuristics happens at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acs{HMM}~\cite{ref:rabiner:1986}.
+
+\subsection{Hyper-Parameters}\label{sec:bhh:hyper_parameters}
+
+The following hyper-parameters are implemented by the \acs{BHH}: the \textit{heuristic pool} configures the type of heuristics included in the heuristic pool as gradient-only, meta-heuristic-only or all heuristics, the \textit{population size} specifies the number of entities in the entitiy pool, the \textit{credit assignment strategy} specifies which credit assignment strategy to use, the \textit{reselection interval} determines the frequency of heuristic reselection, the \textit{replay window size} determines the maximum size of the performance log, the \textit{reanalysis interval} determines the frequency at which Bayesian analysis is applied, the \textit{burn in window size} determines the size of an initial window where experience is simply gathered without reanalysis, and finally, \textit{discounted rewards} and \textit{normalisation} flags toggle scaling modifiers on the credit assignment strategies, backwards in the performance log.

### 2023-02-01 article/sections/07-methodology.tex
🚧 (article): Save point, WIP

--- 2022-12-05 dissertation/chapters/07-methodology.tex
@@
-\chapter{Methodology}\label{chap:methodology}
+\section{Methodology}
+\label{sec:methodology}
 
-\begin{quotation}
-      ``Observation, reason and experimentation make up what we call the scientific method.''
-\end{quotation}
-\begin{flushright}
-      - Richard P. Feynman
-\end{flushright}
+This section provides the details of the implementation of the empirical process.
+Two experimental groups are defined.
+These include an empirical study to investigate the behavioural characteristics of the \Acs{BHH} as it is used to train \acp{FFNN} on an example problem, as well as an empirical study to critically evaluate the performance of the \Acs{BHH} compared to individual low-level heuristics as they are used to train \acp{FFNN} on a number of different problems.
 
-So far, this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acp{HH} and probability theory in Chapters \ref{chap:anns} to \ref{chap:probability}.
-Chapter \ref{chap:bhh} provided the detail of the implementation of the proposed \acs{BHH} with all its components and hyper-parameters.
-Scientific experimentation can now be conducted.
-Chapter \ref{chap:introduction} identified a set of empirical goals for this dissertation.
-The goals of this dissertation include an empirical evaluation of the \acs{BHH}, its behaviour and performance, and a comparison to state of the art low-level \index{heuristic}heuristics.
-This chapter provides the detailed specification of the methodology that is followed for the empirical process.
-Details are provided on the implementation of experiments, datasets, selection of hyper-parameters and design decisions.
-The process by which the results are statistically analysed are also presented.
-The remainder of the chapter is structured as follows:
-
-\begin{itemize}
-      \item \textbf{Section \ref{sec:methodology:overview}} provides a brief overview of the overall empirical process.
-
-      \item \textbf{Section \ref{sec:methodology:datasets}} presents the detail around the datasets that are used.
-
-      \item \textbf{Section \ref{sec:methodology:model}} provides the details of the models (\acs{FFNN}s) that are trained.
-
-      \item \textbf{Section \ref{sec:methodology:heuristics}} presents the detail around the different \index{heuristic}heuristics that are used along with their hyper-parameters.
-
-      \item \textbf{Section \ref{sec:methodology:baseline_bhh}} provides the detail of the configuration of the \acs{BHH} baseline.
-
-      \item \textbf{Section \ref{sec:methodology:performance_measures}} sheds light into the performance evaluation measures that are used.
-
-      \item \textbf{Section \ref{sec:methodology:stopping_conditions}} discusses the stopping conditions that are used.
-
-      \item \textbf{Section \ref{sec:methodology:experiments}} presents the different experimental groups that are executed.
-
-      \item \textbf{Section \ref{sec:methodology:implementation}} sheds light on the implementation and execution of the empirical process.
-
-      \item \textbf{Section \ref{sec:methodology:statistical_analysis}} presents the procedures that are followed for the statistical analysis of the results.
-
-      \item \textbf{Section \ref{sec:methodology:summary}} presents a brief summary of the chapter.
-\end{itemize}
-
-\section{Overview of Empirical Process}\label{sec:methodology:overview}
-
-The purpose of the empirical process is to conduct a carefully crafted set of experiments that produce data that can be used to reject of verify a hypothesis about the element under investigation.
-Chapter \ref{chap:introduction} identified a number of empirical tests to execute.
-These include:
-
-\begin{itemize}
-      \item An empirical study to show that the \Acs{BHH} can effectively be used to train \acp{FFNN}.
-
-      \item An empirical study to investigate the behavioural characteristics of the \Acs{BHH} as it is used to train \acp{FFNN} on an example problem.
-
-      \item An empirical study to critically evaluate the performance of the \Acs{BHH} compared to individual low-level \index{heuristic}heuristics in the \index{heuristic}heuristic space as they are used to train \acp{FFNN} on a number of different problems.
-\end{itemize}
-
-These empirical tests represent a set of questions, related to the \acs{BHH}, that need to be answered.
-The empirical process is designed to answer these questions.
-The empirical process is structured as follows.
-
-Each empirical test starts with a question to be answered.
-A hypothesis is formulated for the outcome of the empirical test.
-The empirical tests are then designed around the implementation of the components under evaluation.
-Each empirical test defines the configuration of elements and generally include a set of parameters that are altered between experiments.
-Each experiment is evaluated by means of a performance measurement.
 In the context of training \acp{FFNN}, the underlying model is trained across a number of datasets.
 Each dataset is split into a training set comprising of 80\% of the data, and a test set comprising of 20\% of the data.
-The training set is used to train the model, while the test set is used to evaluate the model's performance on unseen data.
-Training epochs are split into mini-batch iterations with a specified mini-batch size per dataset.
-Evaluation takes place at every mini-batch step.
-Due to the stochastic nature of the experiments, each experiment is repeated over 30 independent runs to provide sufficient sample for statistical certainty about the outcome of the results.
+Each experiment is repeated over 30 independent runs.
 Each run contains a different random seed, such that each run is unique.
-The evaluation data forms the results of the empirical test.
+The evaluation data forms the results of these empirical tests.
 These results are analysed for statistical significance, from which findings and conclusions are then made.
-The null hypothesis is then either rejected or accepted based on these findings.
 
-Details around each of these elements are provided in the following sections.
+\subsection{Datasets}\label{sec:methodology:datasets}
 
-\section{Datasets}
-\label{sec:methodology:datasets}
+All the datasets used in the empirical process originate from the UCI Machine Learning Repository~\cite{ref:uci:2022}.
+Datasets are grouped by problem type and include seven classification and seven regression datasets.
+The details around the datasets used can be found in Appendix \ref{app:appendix_datasets}.
+A number of classification datasets contain an unbalanced representation of classes.
+The empirical process defined in this work does not apply mechanisms to cater for class balancing, in order to eliminate as many variables and factors in the empirical process as possible.
 
-This section provides the detail around the different datasets that are used throughout the empirical process.
-These datasets originate from the UCI Machine Learning Repository~\cite{ref:uci:2022}.
-Datasets are grouped by problem type and include seven classification and seven regression datasets.
-The classification datasets are given in Table \ref{tab:methodology:datasets:classification} and the regression datasets are given in Table \ref{tab:methodology:datasets:regression} below.
+\subsection{Models}\label{sec:methodology:model}
 
-\begin{table}[htb]
-      \centering
-      \caption{Classification datasets}
-      \label{tab:methodology:datasets:classification}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{ccccccccc}
-                  \textbf{dataset} & \textbf{output} & \textbf{types}             & \textbf{attributes} & \textbf{classes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}          \\
-                  \midrule
-                  iris             & multivariate    & real                       & 4                   & 3                & 150                & 16             & 10             & ~\cite{ref:fisher:1936}    \\
-                  car              & multivariate    & categorical                & 6                   & 4                & 1728               & 128            & 14             & ~\cite{ref:bohanec:1988}   \\
-                  abalone          & multivariate    & categorical, integer, real & 8                   & 28               & 4177               & 256            & 17             & ~\cite{ref:waugh:1995}     \\
-                  wine quality     & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & ~\cite{ref:cortez:2009}    \\
-                  mushroom         & multivariate    & categorical                & 22                  & 2                & 8214               & 512            & 17             & ~\cite{ref:schlimmer:1987} \\
-                  bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & ~\cite{ref:moro:2014}      \\
-                  diabetic         & multivariate    & integer                    & 55                  & 3                & 100000             & 1024           & 98             & ~\cite{ref:strack:2014}    \\
-            \end{tabular}%
-      }
-\end{table}%
+All models that are trained in the empirical process follow implementations of shallow \acp{FFNN}, meaning that they only have one hidden layer.
+The number of hidden units used were determined empirically.
+Weights are initialised by means of Glorot uniform sampling~\cite{ref:glorot:2010}.
+The models and their configuration, as it is used for each dataset, are given in Appendix \ref{app:appendix_models}.
+\acf{SparseCatXE} and \acf{BinXE} loss functions are used for classification problems, while \acf{MSE} is used for regression problems.
 
-\begin{table}[htb]
-      \centering
-      \caption{Regression datasets}
-      \label{tab:methodology:datasets:regression}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{cccccccc}
-                  \textbf{dataset}    & \textbf{output}           & \textbf{types} & \textbf{attributes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}         \\
-                  \midrule
-                  fish toxicity       & multivariate              & real           & 7                   & 908                & 64             & 15             & ~\cite{ref:cassotti:2015} \\
-                  housing             & univariate                & real           & 13                  & 506                & 32             & 16             & ~\cite{ref:harrison:1978} \\
-                  forest fires        & multivariate              & real           & 13                  & 517                & 32             & 17             & ~\cite{ref:cortez:2007}   \\
-                  student performance & multivariate              & integer        & 33                  & 649                & 32             & 21             & ~\cite{ref:cortez:2008}   \\
-                  parkinsons          & multivariate              & integer, real  & 26                  & 5875               & 256            & 23             & ~\cite{ref:tsanas:2009}   \\
-                  air quality         & multivariate, time series & real           & 15                  & 9358               & 256            & 37             & ~\cite{ref:de:2008}       \\
-                  bike                & univariate                & integer, real  & 16                  & 17389              & 256            & 68             & ~\cite{ref:fanaee:2014}   \\
-            \end{tabular}%
-      }
-\end{table}%
+\subsection{Heuristics}\label{sec:methodology:heuristics}
 
-Details on how the datasets where preprocessed and prepared is given in Appendix \ref{app:datasets}.
-
-\subsection{Class Balancing}
-
-A number of classification datasets given in Table \ref{tab:methodology:datasets:classification} contain an unbalanced representation of classes.
-The empirical process defined in this dissertation does not apply mechanisms to cater for class balancing, in order to eliminate as many variables and factors in the empirical process as possible.
-It is therefore suggested that the \acs{BHH} first be studied under the assumption of balanced classes, before applying class balancing techniques.
-In future research opportunities, class balancing should be utilised.
-
-\section{Models}\label{sec:methodology:model}
-
-All models that are trained in this dissertation follow implementations of shallow \acp{FFNN}, meaning that they only have one hidden layer.
-The architecture of a model is dependent on the dataset being trained on, the type of optimisation problem, the number of input dimensions and the number of output dimensions.
-The number of hidden layers used were determined empirically.
-Weights are initialised by means of \index{Glorot uniform sampling}Glorot uniform sampling~\cite{ref:glorot:2010}.
-The models and their configuration, as it is used for each dataset, are given in Table \ref{tab:methodology:models:configurations}.
-
-\begin{table}[htb]
-      \centering
-      \caption{Model configurations}
-      \label{tab:methodology:models:configurations}%
-      \par\bigskip
-      \resizebox{\textwidth}{!}{
-            \begin{tabular}{rcccccccc}
-                  \textbf{dataset}    & \textbf{inputs} & \textbf{hidden} & \textbf{output} & \textbf{biases} & \textbf{parameters} & \textbf{topology} & \textbf{l1 activation} & \textbf{l2 activation} \\
-                  \midrule
-                  fish toxicity       & 6               & 3               & 1               & yes             & 25                  & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  iris                & 4               & 5               & 3               & yes             & 43                  & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  air quality         & 12              & 8               & 1               & yes             & 113                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  housing             & 13              & 8               & 1               & yes             & 121                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  wine quality        & 13              & 10              & 7               & yes             & 217                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  parkinsons          & 21              & 10              & 1               & yes             & 231                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  car                 & 21              & 10              & 4               & yes             & 264                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  forest fires        & 43              & 16              & 1               & yes             & 721                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  abalone             & 10              & 36              & 28              & yes             & 1432                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  bank                & 51              & 32              & 1               & yes             & 1697                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  bike                & 61              & 32              & 1               & yes             & 2017                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  student performance & 99              & 32              & 1               & yes             & 3233                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
-                  adult               & 108             & 64              & 1               & yes             & 7041                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  mushroom            & 117             & 64              & 1               & yes             & 7617                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-                  diabetic            & 2369            & 32              & 3               & yes             & 75939               & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
-            \end{tabular}%
-      }
-\end{table}%
-
-For the classification problems presented in Tables \ref{tab:methodology:datasets:classification} and \ref{tab:methodology:models:configurations}, the softmax activation function is added after training and is not included in the model during training.
-The loss functions, \acf{SparseCatXE} and \acf{BinXE}, that are used, contain a \index{softmax}softmax function.
-
-\index{heuristic}
-\section{Heuristics}\label{sec:methodology:heuristics}
-
-This section provides the details of the low-level \index{heuristic}heuristics that are used in the empirical process.
-Each of these low-level \index{heuristic}heuristics are implemented as standalone \index{heuristic}heuristics and are also included in the \index{heuristic pool}heuristic pool of the \acs{BHH}.
-Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level \index{heuristic}heuristics that are used as well as their hyper-parameter configurations.
-
-% Table generated by Excel2LaTeX from sheet 'BHH Baseline'
-\begin{table}[htbp]
-      \centering
-      \caption{Low-level \index{heuristic}heuristics and their hyper-parameter configurations.}
-      \label{tab:methodology:heuristics}%
-      \par\bigskip
-      \resizebox{0.7\textwidth}{!}{
-
-            \begin{tabular}{llll}
-                  \textbf{heuristic} & \textbf{configuration}    & \textbf{value} & \textbf{citation}          \\
-                  \midrule
-                  sgd                & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
-                  momentum           & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
-                                     & momentum                  & 0.9            &                            \\
-                  nag                & learning rate             & 0.1 (0.01)     & ~\cite{ref:sutskever:2013} \\
-                                     & momentum                  & 0.9            &                            \\
-                  adagrad            & learning rate             & 0.1 (0.01)     & ~\cite{ref:duchi:2011}     \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  rmsprop            & learning rate             & 0.1 (0.01)     & ~\cite{ref:hinton:2012}    \\
-                                     & rho                       & 0.95           &                            \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  adadelta           & learning rate             & 1.0 (0.95)     & ~\cite{ref:zeiler:2012}    \\
-                                     & rho                       & 0.95           &                            \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  adam               & learning rate             & 0.1 (0.01)     & ~\cite{ref:kingma:2014}    \\
-                                     & beta1                     & 0.9            &                            \\
-                                     & beta2                     & 0.999          &                            \\
-                                     & epsilon                   & 1E-07          &                            \\
-                  pso                & population size           & 10             & ~\cite{ref:van:2010}       \\
-                                     & learning rate             & 1.0 (0.9)      &                            \\
-                                     & inertia weight (w)        & 0.729844       &                            \\
-                                     & cognitive control (c1)    & 1.49618        &                            \\
-                                     & social control (c2)       & 1.49618        &                            \\
-                                     & velocity clip min         & -1.0           &                            \\
-                                     & velocity clip max         & 1.0            &                            \\
-                  de                 & population size           & 10             & ~\cite{ref:mezura:2006}    \\
-                                     & selection strategy        & best           &                            \\
-                                     & xo strategy               & exp            &                            \\
-                                     & recombination probability & 0.9 (0.1)      &                            \\
-                                     & beta                      & 2.0 (0.1)      &                            \\
-                  ga                 & population size           & 10             & ~\cite{ref:lambora:2019}   \\
-                                     & selection strategy        & rand           &                            \\
-                                     & xo strategy               & bin            &                            \\
-                                     & mutation rate             & 0.2 (0.05)     &                            \\
-            \end{tabular}%
-      }
-\end{table}%
+Each of these low-level heuristics are implemented as standalone heuristics and are also included in the heuristic pool of the \acs{BHH}.
+Appendix \ref{app:appendix_heuristics} contains a list of all the standalone, low-level heuristics that are used as well as their hyper-parameter configurations.
 
@@
 A learning rate parameter does not traditionally form part of \acs{PSO}, but was found to be useful.
-The position update step for \acs{PSO} using a learning rate is then defined as
 
-\begin{equation}
-      \label{eq:heuristics:pso:position_learning_rate}
-      \begin{split}
-            x_{ij}(t+1) = x_{ij}(t) + \eta v_{ij}(t+1)
-      \end{split}
-\end{equation}
+Section \ref{sec:bhh:heuristic:proxies} presented the concept of a mapping of proxied heuristic state update operations.
+The mapping of proxied heuristic state update operations implemented by the \acs{BHH} in the empirical process is given in Figure \ref{fig:methodology:heuristics:proxies}.
 
-where $\eta$ is the added learning rate with $0 \leq \eta \leq 1, \eta \in \mathbb{R}$.
+In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x} indicate that the associated heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
+The required mapping of proxied heuristic state operations is then implemented as a lookup of the table presented in Figure \ref{fig:methodology:heuristics:proxies}.
 
-Section \ref{sec:bhh:heuristic:proxies} presented the concept of a mapping of proxied \index{heuristic}heuristic state update operations.
-The mapping of proxied \index{heuristic}heuristic state update operations implemented by the \acs{BHH} in the empirical process is given in Figure \ref{fig:methodology:heuristics:proxies}.
-
-\begin{figure}[htbp]
-      \centering
-      \includegraphics[width=0.95\textwidth]{images/bhh_heuristic_proxies.pdf}
-      \caption{Mapping of proxied heuristic state update operations as implemented by the \acs{BHH}}
-      \label{fig:methodology:heuristics:proxies}%
-\end{figure}
-
-In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x} indicate that the associated \index{heuristic}heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
-The required mapping of proxied \index{heuristic}heuristic state operations is then implemented as a lookup of the table presented in Figure \ref{fig:methodology:heuristics:proxies}.
-
-\section{BHH Baseline}\label{sec:methodology:baseline_bhh}
+\subsection{BHH Baseline}\label{sec:methodology:baseline_bhh}
 
 The \acs{BHH} baseline is a name given to a specific configuration of the \acs{BHH} which, during development, has been found to provide a reasonable baseline performance.
-The baseline configuration is used as the cornerstone configuration from which all other \index{heuristic}heuristics and their configurations are evaluated.
+The baseline configuration is used as the cornerstone configuration from which all other heuristics and their configurations are evaluated.
 The \acs{BHH} baseline is also used for the behavioural study of the \acs{BHH}.
@@
 
-In Table \ref{tab:methodology:bhh_baseline_configuration}, the \index{heuristic}heuristic pool configuration that is used, is referred to as \textit{all}.
-The \textit{all} configuration refers to a configuration where the \index{heuristic pool}heuristic pool contains all the low-level \index{heuristic}heuristics as presented in Section \ref{sec:methodology:heuristics}, including all gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.
+In Table \ref{tab:methodology:bhh_baseline_configuration}, the heuristic pool configuration that is used, is referred to as \textit{all}.
+The \textit{all} configuration refers to a configuration where the heuristic pool contains all the low-level heuristics as presented in Section \ref{sec:methodology:heuristics}, including all gradient-based heuristics and \acp{MH}
 
-\section{Performance Measures}\label{sec:methodology:performance_measures}
+\subsection{Performance Measures}\label{sec:methodology:performance_measures}
 
-This section provides the performance measures that are used to evaluate the different experimental runs during the empirical process.
-Chapter \ref{chap:anns} provided a number of loss functions.
-These loss functions are used to measure the performance of the \acp{FFNN} being trained.
 In this dissertation, \acs{BinXE} is used for classification problems with two classes and \acs{SparseCatXE} is used for classification problems with more than two classes.
@@
 
-\section{Stopping Conditions}\label{sec:methodology:stopping_conditions}
+\subsection{Stopping Conditions}\label{sec:methodology:stopping_conditions}
 
-This section provides the stopping conditions that are used during the empirical process.
 For this dissertation, the \textit{maximum epoch} stopping condition is used, where a fixed, maximum number of training steps and epochs are executed and training is not halted until the maximum number of epochs have been reached.
 \acp{FFNN} are trained for a maximum of 30 epochs.
-Early stopping is a technique where training is stopped when the \index{heuristic}heuristic is not able to improve the performance of the \acs{FFNN} for a number of steps.
-If the performance has not improved, the training is halted and the last known best model weights are restored.
 Early stopping is not implemented for the empirical process in this dissertation.
-This design decision is made so that the behaviour of the \acs{BHH} can be studied beyond the point of optimal results.
 
-\section{Experiments}
+\subsection{Experiments}
 \label{sec:methodology:experiments}
@@
 
-\subsection{Behavioural Case Study}
+\subsubsection{Behavioural Case Study}
 \label{sec:methodology:experiments:case_study}
@@
 The behavioural case study is used to determine if the \acs{BHH} is learning and that selection is indeed biasing towards better performance.
-These observations also provide an opportunity to observe the outcome of the perturbative nature of the \acs{BHH}, which includes proxied \index{heuristic}heuristic update step operations.
+These observations also provide an opportunity to observe the outcome of the perturbative nature of the \acs{BHH}, which includes proxied heuristic update step operations.
 
@@
 
-\subsection{Standalone Heuristics}
+\subsubsection{Standalone Heuristics}
 \label{sec:methodology:experiments:standalone_optimisers}
 
-For the standalone \index{heuristic}heuristics experimental group, the \index{heuristic}heuristics, as presented in Section \ref{sec:methodology:heuristics}, are used along with their specified hyper-parameters.
-Each of these standalone low-level \index{heuristic}heuristics are compared to that of the \acs{BHH} baseline configuration, across all datasets.
+For the standalone heuristics experimental group, the heuristics, as presented in Section \ref{sec:methodology:heuristics}, are used along with their specified hyper-parameters.
+Each of these standalone low-level heuristics are compared to that of the \acs{BHH} baseline configuration, across all datasets.
 
-The intent of the standalone \index{heuristic}heuristics experimental group is to determine if the \acs{BHH} baseline configuration can generalise to multiple problems in comparison to individual low-level \index{heuristic}heuristics.
+The intent of the standalone heuristics experimental group is to determine if the \acs{BHH} baseline configuration can generalise to multiple problems in comparison to individual low-level heuristics.
 
 Additional to the \acs{BHH} baseline configuration, two more \acs{BHH} configurations are included.
-These include \acs{BHH} configurations where the \index{heuristic pool}heuristic pool only makes use of gradient-based \index{heuristic}heuristics, and a configuration where the \index{heuristic pool}heuristic pool only makes use of \acp{MH}.
-The intent behind the inclusion of these configurations is to determine the effectiveness of multi-method approaches in the \index{heuristic pool}heuristic pool as it applies to training \acp{FFNN}.
+These include \acs{BHH} configurations where the heuristic pool only makes use of gradient-based heuristics, and a configuration where the heuristic pool only makes use of \acp{MH}.
+The intent behind the inclusion of these configurations is to determine the effectiveness of multi-method approaches in the heuristic pool as it applies to training \acp{FFNN}.
 
-\subsection{BHH Variants}
-\label{sec:methodology:experiments:bhh_variants}
-
-This section provides the details of the experimental group that focuses on \acs{BHH} variants and the effect that different hyper-parameter configurations can have on the outcome of the \acs{BHH}.
-The different variants of the \acs{BHH} and their possible configurations are given in Table \ref{tab:methodology:experiments:bhh_variants}.
-
-\begin{table}[htb]
-      \centering
-      \caption{BHH variants and their configuration}
-      \label{tab:methodology:experiments:bhh_variants}%
-      \par\bigskip
-      \resizebox{0.9\textwidth}{!}{
-            \begin{tabular}{rcc}
-                  \multicolumn{1}{c}{\textbf{hyper-heuristic}} & \textbf{variant}   & \textbf{values}                       \\
-                  \midrule
-                  \multicolumn{1}{l}{bhh}                      & heuristic pool     & all, gd, mh                           \\
-                                                               & population         & 5, 10, 15, 20, 25                     \\
-                                                               & credit             & ibest, pbest, rbest, gbest, symmetric \\
-                                                               & reselection        & 1, 5, 10, 15, 20                      \\
-                                                               & replay             & 1, 5, 10, 15, 20                      \\
-                                                               & reanalysis         & 1, 5, 10, 15, 20                      \\
-                                                               & burn in            & 0, 5, 10, 15, 20                      \\
-                                                               & normalise          & false, true                           \\
-                                                               & discounted rewards & false, true                           \\
-            \end{tabular}%
-      }
-\end{table}%
-
-In Table \ref{tab:methodology:experiments:bhh_variants}, the \index{heuristic pool}heuristic pool configuration \textit{gd} refers to the \index{heuristic pool}heuristic pool configuration where only gradient-based \index{heuristic}heuristics are included, and \textit{mh} refers to the \index{heuristic pool}heuristic pool configuration where only \acp{MH} are included.
-
-\section{Statistical Analysis}
+\subsection{Statistical Analysis}
 \label{sec:methodology:statistical_analysis}
 
-This section provides the detail of the process that is used to execute the statistical analysis of the results.
-
-Various experimental groups and configurations have been presented in Sections \ref{sec:methodology:experiments:case_study}, \ref{sec:methodology:experiments:standalone_optimisers} and \ref{sec:methodology:experiments:bhh_variants}.
 The results from each of these experimental groups are statistically analysed.
-To ensure that there are sufficient samples for statistical analysis, each experiment and configuration is trained for 30 epochs and is repeated over 30 runs, for each of the fourteen datasets.
+Eeach experiment and configuration is trained for 30 epochs and is repeated over 30 runs, for each of the fourteen datasets.
 The experimental results contain performance evaluation data for the training and testing datasets, and includes loss and accuracy measurements.
@@
 The results are analysed and checked for overfitting and outliers are identified.
-The skewness of the results is evaluated per dataset and the \index{Shapiro-Wilk}Shapiro-Wilk test for normality~\cite{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
-Furthermore, the \index{Levene}Levene's test for equality of variance~\cite{ref:levene:1961} ($\alpha$ = 0.001) is used.
+The skewness of the results is evaluated per dataset and the Shapiro-Wilk test for normality~\cite{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
+Furthermore, the Levene's test for equality of variance~\cite{ref:levene:1961} ($\alpha$ = 0.001) is used.
 The output of the full statistical analysis is presented in Appendix \ref{app:statistical_analysis}.
@@
 Dependent on the outcomes of the above statistical tests, the appropriate statistical significance test is then executed.
-For experiments where there are only two configurations, the Mann-Whitney U\index{Mann-Whitney U} independent samples t-Test~\cite{ref:mann:1947} ($\alpha$ = 0.001) is executed.
+For experiments where there are only two configurations, the Mann-Whitney U independent samples t-Test~\cite{ref:mann:1947} ($\alpha$ = 0.001) is executed.
 For experiments with three or more configurations, the \acs{ANOVA} statistical test~\cite{ref:fisher:1921} ($\alpha$ = 0.001) is used.
-The\index{Kruskal-Wallis} Kruskal-Wallis ranked non-parametric test~\cite{ref:kruskal:1952} for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
+The Kruskal-Wallis ranked non-parametric test~\cite{ref:kruskal:1952} for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
 
@@
 
-\section{Implementation and Execution}\label{sec:methodology:implementation}
+\subsection{Implementation and Execution}\label{sec:methodology:implementation}
 
 All implementations are done from first principles in Python 3.9 using Tensorflow 2.7 and Tensorflow Probability 0.15.0.
-Most underlying mathematical functions are reused from the Tensorflow library, however, all \index{heuristic}heuristics are implemented from first principles to fit the \acs{HH} framework that was developed.
+Most underlying mathematical functions are reused from the Tensorflow library, however, all heuristics are implemented from first principles to fit the \acs{HH} framework that was developed.
 The source code and data for this dissertation is provided and made public at \url{https://github.com/arneschreuder/masters}.
 
-It should be noted that this implementation makes heavy use of CPU processing, due to flattening of the \acs{FFNN} weights by the \index{heuristic}heuristics.
+It should be noted that this implementation makes heavy use of CPU processing, due to flattening of the \acs{FFNN} weights by the heuristics.
 For this reason, execution is much more timely and costly than with GPU training.
@@
 The entire empirical process took six days.
-
-\section{Summary}\label{sec:methodology:summary}
-
-This chapter provided the detail around the methodology that was used to execute the empirical process.
-The datasets, \acp{FFNN} and \index{heuristic}heuristics that are used during the empirical process have been presented in detail, along with details around various \acs{BHH} configurations.
-A baseline \acs{BHH} has been formulated.
-The empirical process was defined in terms of a number of different experimental groups and finally, the process of statistical analysis of the results was provided.
-
-The results and findings of the empirical process are presented in the following chapter.

### 2023-02-01 article/sections/08-results.tex
🚧 (article): Save point, WIP

@@
 Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results.
-The \acs{BHH} applies a form of \index{online learning}online learning.
+The \acs{BHH} applies a form of online learning.
 As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process.
@@
 After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point.
-Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the \index{heuristic}heuristic space beyond the five epoch mark.
+Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the heuristic space beyond the five epoch mark.
 
@@
 
-Given the stochastic nature of the \index{heuristic}heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn.
+Given the stochastic nature of the heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn.
 This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}.
@@
 
-These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all.
+These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level heuristics in the heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards heuristics that perform well at all.
 
@@
 From Figure \ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed.
-This could simply be a result of momentum that is maintained when switching between low-level \index{heuristic}heuristics in an attempt to find better solutions.
+This could simply be a result of momentum that is maintained when switching between low-level heuristics in an attempt to find better solutions.
 For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions.
@@
 To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
-Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichlet probability distribution}Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
-The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{\index{heuristic}heuristic selection probabilities}.
+Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
+The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{heuristic selection probabilities}.
 Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
-Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool.
+Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the heuristic pool.
 Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
@@
 The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
-\index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequently reselect these \index{heuristic}heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
+Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequently reselect these heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
 Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.
@@
 
-This section provides a detailed investigation into the \textit{probability distribution of \index{heuristic}heuristic selection probabilities} as it changes throughout the training process.
-As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modelling and thus, \index{heuristic}heuristic selection probabilities are defined by an underlying probabilistic distribution themselves.
-The probability distribution of \index{heuristic}heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.
+This section provides a detailed investigation into the \textit{probability distribution of heuristic selection probabilities} as it changes throughout the training process.
+As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modelling and thus, heuristic selection probabilities are defined by an underlying probabilistic distribution themselves.
+The probability distribution of heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.
 
-Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
+Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
 These illustrations are presented in log scale.
-Indices 0, 6, 7, and 8 represent the distribution of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of \index{heuristic}heuristic selection probabilities in $\boldsymbol{\theta}$.
+Indices 0, 6, 7, and 8 represent the distribution of heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of heuristic selection probabilities in $\boldsymbol{\theta}$.
 Similar illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
@@
 	\par\bigskip
-	\caption{The average sampled \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
-The \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average sampled heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
+The heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:thetas}
@@
 The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}.
-As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected mean \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modelling.
+As a reminder, ten low-level heuristics are included in the heuristic pool, yielding an expected mean heuristics selection probability of 0.1, for each heuristic, by the frequentist view of probabilistic modelling.
 
-Towards the end of the training process, the \index{heuristic}heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a \index{heuristic}heuristic selection probability of 0.1, for all \index{heuristic}heuristics.
+Towards the end of the training process, the heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a heuristic selection probability of 0.1, for all heuristics.
 This can be explained as follows: most of the training progress is made in the early stages of the training process, and training converges towards the end of the training process.
@@
 Another observation to make occurs in the first 30 steps of the training process.
-In Figure \ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same \index{heuristic}heuristic selection probabilities in these first 30 steps.
+In Figure \ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same heuristic selection probabilities in these first 30 steps.
 This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number.
@@
 It should be noted that, despite using the same random seed across configurations for the same run number, the behavioural changes between the configurations start to show after about 30 steps.
-As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing \index{heuristic}heuristics.
+As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing heuristics.
 Where the bhh\_baseline and bhh\_replay\_250 configurations then diverge from the behaviour of the bhh\_credit\_symmetric configuration is proof of the effect of performance bias.
 
-Furthermore, it can be observed for small windows, at various steps for multiple runs, that the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, do not yield means that are equal to the expected \index{heuristic}heuristic selection probabilities of 0.1.
+Furthermore, it can be observed for small windows, at various steps for multiple runs, that the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, do not yield means that are equal to the expected heuristic selection probabilities of 0.1.
 This is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations.
@@
 This can be attributed to a very small reanalysis window combined with a small replay window size of 10, that contains very few samples to learn from.
-A small reanalysis interval and a small replay window size allows for more exploration of the \index{heuristic}heuristic space, but can also yield greater variance of the \index{heuristic}heuristic selection probabilities.
+A small reanalysis interval and a small replay window size allows for more exploration of the heuristic space, but can also yield greater variance of the heuristic selection probabilities.
 Once again, any differences then in the behaviour of the bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations and biases by the bhh\_baseline configuration.
@@
 
-This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}.
-The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
+This section provides a brief investigation into the \textit{prior heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}.
+The prior heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
 As such, $P(\boldsymbol{H} \vert \boldsymbol{\theta}) = \boldsymbol{\theta}$ and heuristics are initially sampled such that $\boldsymbol{H} \sim Cat(\boldsymbol{\theta})$.
 
-Figures \ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
+Figures \ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
 Similar to before, these illustrations are also presented in log scale.
@@
 	\par\bigskip
-	\caption{The average prior \index{heuristic}heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8.
-The prior \index{heuristic}heuristic selection probabilities are sampled from the probability distribution of \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average prior heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8.
+The prior heuristic selection probabilities are sampled from the probability distribution of heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_H}
@@
 
-The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of \index{heuristic}heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure \ref{fig:results:case_study:thetas}.
+The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure \ref{fig:results:case_study:thetas}.
 This is because of the \textit{reselection} interval hyper-parameter.
 The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity.
-Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10.
-These illustrations then simply yield rough approximations of the illustrations provided in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of \index{heuristic}heuristic selection probabilities.
+Since the default \textit{reselection} interval is set to 10, the heuristic selection probabilities are only resampled at intervals of 10.
+These illustrations then simply yield rough approximations of the illustrations provided in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of heuristic selection probabilities.
 As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
 
-Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of \index{heuristic}heuristic performances.
-Since these prior \index{heuristic}heuristic selection probabilities change over time, it can be concluded that the change in prior \index{heuristic}heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}.
-Furthermore, the prior \index{heuristic}heuristic selection probability distribution provides an opportunity to utilise prior knowledge by some expert before training starts, by injecting heuristic selection biases, by means of the initial values for the concentration parameter $\boldsymbol{\alpha}$.
+Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of heuristic performances.
+Since these prior heuristic selection probabilities change over time, it can be concluded that the change in prior heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}.
+Furthermore, the prior heuristic selection probability distribution provides an opportunity to utilise prior knowledge by some expert before training starts, by injecting heuristic selection biases, by means of the initial values for the concentration parameter $\boldsymbol{\alpha}$.
 
@@
 These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}.
-The posterior \index{heuristic}heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy.
-Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of \index{heuristic}heuristic selection probabilities and the entity selection probabilities respectively.
+The posterior heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy.
+Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of heuristic selection probabilities and the entity selection probabilities respectively.
 Finally, $\boldsymbol{\psi}$ represents the probability distribution of successful credit allocation probabilities.
 
-Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
+Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
 Similar to before, these illustrations are also presented in log scale.
@@
 	\par\bigskip
-	\caption{The average calculated proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, $c_{1}$, from the \textit{ibest} credit assignment strategy.
-The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{The average calculated proportional posterior heuristic selection probabilities for heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, $c_{1}$, from the \textit{ibest} credit assignment strategy.
+The proportional posterior heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
 	\label{fig:results:case_study:p_HgEC:0}
@@
 
-The main observation to make from Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled.
+The main observation to make from Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a Categorical probability distribution from which new heuristic selections are sampled.
 The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Section \ref{sec:bhh}.
@@
 
-Furthermore, the posterior heuristic selection probability distribution is conditional on the occurrence of a specific entity that the potential \index{heuristic}heuristic will be applied to, as well as a specific performance criterion enforced by a specific credit assignment strategy.
-This means that \index{heuristic}heuristic selection is specific to each entity.
-A particular \index{heuristic}heuristic might be good for one entity, but not for another.
-This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct \index{heuristic}heuristic to the correct entity at the correct time in the training process.
+Furthermore, the posterior heuristic selection probability distribution is conditional on the occurrence of a specific entity that the potential heuristic will be applied to, as well as a specific performance criterion enforced by a specific credit assignment strategy.
+This means that heuristic selection is specific to each entity.
+A particular heuristic might be good for one entity, but not for another.
+This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct heuristic to the correct entity at the correct time in the training process.
 
@@
 As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of \acp{MH}.
-Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics (denoted bhh\_mh).
+Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a heuristic pool that contains only gradient-based heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a heuristics pool that contains only \acp{MH} (denoted bhh\_mh).
 
@@
 	\centering
-	\caption{Empirical results showing test loss and statistics for different low-level \index{heuristic}heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs, measured at the last epoch.}
+	\caption{Empirical results showing test loss and statistics for different low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs, measured at the last epoch.}
 	\label{tab:results:standalone:metrics:loss}%
@@
 Table \ref{tab:results:standalone:metrics:loss} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
-The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.
+The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the heuristics.
 
 Table \ref{tab:results:standalone:metrics:rank} provides the empirical results from Table \ref{tab:results:standalone:metrics:loss} in ranked format.
-The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, across all datasets, for all independent runs and all epochs.
-The average rank across all epochs produces a view on the performance of the \index{heuristic}heuristics as it relates to the entire training process.
-Finally, a normalised average rank is provided for the overall performance of all \index{heuristic}heuristics at the bottom of the table.
+The performance rank is calculated as the average rank produced by each heuristic, across all datasets, for all independent runs and all epochs.
+The average rank across all epochs produces a view on the performance of the heuristics as it relates to the entire training process.
+Finally, a normalised average rank is provided for the overall performance of all heuristics at the bottom of the table.
 The normalised average rank is calculated as a discrete normalisation of the average rank achieved across all datasets, for all independent runs and epochs.
@@
 	\centering
-	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
+	\caption{Empirical results showing normalised average rank and statistics for different low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:standalone:metrics:rank}%
@@
 
-From the normalised average ranks provided in Table \ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen \index{heuristic}heuristic implementations respectively.
+From the normalised average ranks provided in Table \ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen heuristic implementations respectively.
 These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.
 
-Figure \ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each \index{heuristic}heuristic, per dataset.
+Figure \ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each heuristic, per dataset.
 The heuristics are ordered according to the normalised ranks presented in Table \ref{tab:results:standalone:metrics:rank}.
@@
 	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all independent runs and epochs.}
+	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all independent runs and epochs.}
 	\label{fig:results:standalone:descriptive:descriptive}
@@
 
-Figure \ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each \index{heuristic}heuristic as it relates to all datasets, across all independent runs and epochs.
+Figure \ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each heuristic as it relates to all datasets, across all independent runs and epochs.
 
@@
 	\includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of all low-level \index{heuristic}heuristics compared to three \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
+	\caption{Critical difference plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
 	\label{fig:results:standalone:descriptive:cd}
@@
 
-Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all \index{heuristic}heuristics is very small.
+Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all heuristics is very small.
 Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, is statistically only outperformed overall by \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}.
-It should be noted that the standalone low-level \index{heuristic} \index{heuristic}heuristics already produce good results in general across all datasets.
+It should be noted that the standalone low-level  heuristics already produce good results in general across all datasets.
 In this particular case, producing better performance outcomes can be hard to achieve.
@@
 
-Another observation that can be made is that the gradient-based \index{heuristic}heuristics generally performed much better than the \index{meta-heuristic}meta-heuristics on all datasets.
+Another observation that can be made is that the gradient-based heuristics generally performed much better than the \acp{MH} on all datasets.
 State of the art methods for training \acp{FFNN}, such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions \cite{ref:kingma:2014}.
-Exploration of the \index{heuristic}heuristic space leads the \acs{BHH} to consider other \index{heuristic}heuristics during the training process, which could possibly result in worse performances at times.
+Exploration of the heuristic space leads the \acs{BHH} to consider other heuristics during the training process, which could possibly result in worse performances at times.
 As previously mentioned, a suggestion to improve on these results is to include a move-acceptance strategy, where heuristic progressions are discarded if they fail to produce better results.
@@
 	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:standalone:figures:iris}
@@
 	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the car dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the car dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:standalone:figures:car}
@@
 	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:standalone:figures:bank}
@@
 	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:standalone:figures:fish_toxicity}
@@
 	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
+	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
 	\label{fig:results:standalone:figures:parkinsons}

### 2023-02-01 article/sections/09-conclusion.tex
🚧 (article): Save point, WIP

@@
 
-The main area of focus for the research done in this dissertation stems from the problem statement, which identified the difficult and tedious problem of selecting the best \index{heuristic}heuristic for training \acp{FFNN}.
-The research presented in this article identified the possibility of using a different approach, referred to as \acp{HH}, to automate the \index{heuristic}heuristic selection process.
+The main area of focus for the research done in this dissertation stems from the problem statement, which identified the difficult and tedious problem of selecting the best heuristic for training \acp{FFNN}.
+The research presented in this article identified the possibility of using a different approach, referred to as \acp{HH}, to automate the heuristic selection process.
 
-This research then set out to develop a novel high-level \index{heuristic}heuristic that utilises probability theory in an online learning setting to drive the automatic \index{heuristic}heuristic selection process.
+This research then set out to develop a novel high-level heuristic that utilises probability theory in an online learning setting to drive the automatic heuristic selection process.
 As such, the \acs{BHH} was conceptualised.
@@
 A literature study was conducted on all related topics that are relevant to the development of the \acs{BHH}.
-The literature study included background information on \acs{ANN}, existing low-level \index{heuristic}heuristics, meta-learning, \acp{HH}, probability theory, and Bayesian statistics.
+The literature study included background information on \acs{ANN}, existing low-level heuristics, meta-learning, \acp{HH}, probability theory, and Bayesian statistics.
 
-A novel \acs{BHH} that can be used to automate the \index{heuristic}heuristic selection process was proposed in detail and was implemented.
+A novel \acs{BHH} that can be used to automate the heuristic selection process was proposed in detail and was implemented.
 The \acs{BHH} follows an approach that includes a selective and perturbative element in an online learning setting.
 Bayesian statistics and \acs{MAP} is used as the optimisation technique and detailed mathematical derivations of the optimisation process was provided.
-Detailed discussions were provided on the mapping of proxied \index{heuristic}heuristic state update operations.
+Detailed discussions were provided on the mapping of proxied heuristic state update operations.
 Finally, a \acs{BHH} baseline configuration was defined as a cornerstone reference for empirical analysis.
@@
 An empirical study was conducted to study the behavioural characteristics of the \acs{BHH}.
-An empirical study was conducted to critically evaluate the performance of the \acs{BHH} compared to traditional, low-level, standalone \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.
+An empirical study was conducted to critically evaluate the performance of the \acs{BHH} compared to traditional, low-level, standalone heuristic when training \acp{FFNN} on a number of different datasets.
 
@@
 For the behavioural case study of the \acs{BHH} it was found that the \ac{BHH} is able to train a \acf{FFNN} relatively well.
-It was shown that the \ac{BHH} is able to learn and that the \acs{BHH} is able to exploit small performance biases as it relates to \index{heuristic}heuristic selection.
-This enables the \acs{BHH} to select the correct \index{heuristic}heuristics to apply to the correct entities at the correct time in the training process.
+It was shown that the \ac{BHH} is able to learn and that the \acs{BHH} is able to exploit small performance biases as it relates to heuristic selection.
+This enables the \acs{BHH} to select the correct heuristics to apply to the correct entities at the correct time in the training process.
 
@@
 For the experimental group that compares the \acs{BHH} baseline with a number of  low-level heuristics, three different configurations of the \acs{BHH} baseline configuration were implemented.
-These configurations vary in the type of \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool.
+These configurations vary in the type of heuristics in the heuristic pool.
 
-Overall, the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen \index{heuristic}heuristics that were implemented and executed on fourteen datasets.
-The \textit{bhh\_gd} configuration produced performance results close to that of the best low-level \index{heuristic}heuristics and was only statistically outperformed by the top two low-level \index{heuristic}heuristics.
+Overall, the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen heuristics that were implemented and executed on fourteen datasets.
+The \textit{bhh\_gd} configuration produced performance results close to that of the best low-level heuristics and was only statistically outperformed by the top two low-level heuristics.
 The \textit{bhh\_all} configuration achieved an overall rank of sixth and the \textit{bhh\_mh} achieved an overall rank of eighth.
@@
 It was found that, in general, gradient-based heuristics produced the best results, as such, it is understandable that the \textit{bhh\_gd} yielded the best performance outcomes between the different \acs{BHH} variants that were implemented.
-Although the \acs{BHH} variants were not able to produce better results than the top low-level \index{heuristic}heuristics, the \acs{BHH} variants still effectively trained the underlying \acp{FFNN} and produced good training outcomes overall.
+Although the \acs{BHH} variants were not able to produce better results than the top low-level heuristics, the \acs{BHH} variants still effectively trained the underlying \acp{FFNN} and produced good training outcomes overall.
 
-It was shown that the \textit{bhh\_gd} configuration produced the lowest variance in rank between datasets out of all of the \index{heuristic}heuristics implemented, giving the \acs{BHH} the ability to generalise well to other problems.
+It was shown that the \textit{bhh\_gd} configuration produced the lowest variance in rank between datasets out of all of the heuristics implemented, giving the \acs{BHH} the ability to generalise well to other problems.
 
 Finally, it was shown that the \acs{BHH} provides a mechanism whereby prior expert knowledge can be injected, before training starts.
-Future research can exploit this knowledge and provide a significant bias towards \index{heuristic}heuristics that are known to perform well on particular problem types.
+Future research can exploit this knowledge and provide a significant bias towards heuristics that are known to perform well on particular problem types.

### 2023-02-03 article/sections/07-methodology.tex
✨ (article): Methodology done.

@@
 This section provides the details of the implementation of the empirical process.
-Two experimental groups are defined.
-These include an empirical study to investigate the behavioural characteristics of the \Acs{BHH} as it is used to train \acp{FFNN} on an example problem, as well as an empirical study to critically evaluate the performance of the \Acs{BHH} compared to individual low-level heuristics as they are used to train \acp{FFNN} on a number of different problems.
-
-In the context of training \acp{FFNN}, the underlying model is trained across a number of datasets.
-Each dataset is split into a training set comprising of 80\% of the data, and a test set comprising of 20\% of the data.
-Each experiment is repeated over 30 independent runs.
-Each run contains a different random seed, such that each run is unique.
-The evaluation data forms the results of these empirical tests.
-These results are analysed for statistical significance, from which findings and conclusions are then made.
-
-\subsection{Datasets}\label{sec:methodology:datasets}
-
-All the datasets used in the empirical process originate from the UCI Machine Learning Repository~\cite{ref:uci:2022}.
-Datasets are grouped by problem type and include seven classification and seven regression datasets.
-The details around the datasets used can be found in Appendix \ref{app:appendix_datasets}.
-A number of classification datasets contain an unbalanced representation of classes.
-The empirical process defined in this work does not apply mechanisms to cater for class balancing, in order to eliminate as many variables and factors in the empirical process as possible.
-
-\subsection{Models}\label{sec:methodology:model}
-
-All models that are trained in the empirical process follow implementations of shallow \acp{FFNN}, meaning that they only have one hidden layer.
-The number of hidden units used were determined empirically.
-Weights are initialised by means of Glorot uniform sampling~\cite{ref:glorot:2010}.
-The models and their configuration, as it is used for each dataset, are given in Appendix \ref{app:appendix_models}.
-\acf{SparseCatXE} and \acf{BinXE} loss functions are used for classification problems, while \acf{MSE} is used for regression problems.
-
-\subsection{Heuristics}\label{sec:methodology:heuristics}
-
-Each of these low-level heuristics are implemented as standalone heuristics and are also included in the heuristic pool of the \acs{BHH}.
-Appendix \ref{app:appendix_heuristics} contains a list of all the standalone, low-level heuristics that are used as well as their hyper-parameter configurations.
-
-Note from Table \ref{tab:methodology:heuristics} that values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it.
-The number of steps is the total number of mini-batch training steps that are executed for that particular dataset.
-
-Furthermore, it should be noted that a learning rate was added to \acs{PSO} as an attempt to avoid overshooting solutions later in the training process.
-A learning rate parameter does not traditionally form part of \acs{PSO}, but was found to be useful.
-
-Section \ref{sec:bhh:heuristic:proxies} presented the concept of a mapping of proxied heuristic state update operations.
-The mapping of proxied heuristic state update operations implemented by the \acs{BHH} in the empirical process is given in Figure \ref{fig:methodology:heuristics:proxies}.
-
-In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x} indicate that the associated heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
-The required mapping of proxied heuristic state operations is then implemented as a lookup of the table presented in Figure \ref{fig:methodology:heuristics:proxies}.
+At a high level, two experimental groups are executed.
+These include a behavioural case study and a comparison between the \acs{BHH} and standalone low-level heuristics.
+A number of datasets, models and heuristics are specified.
+Throughout the empirical process, the use of a \acs{BHH} baseline configuration is used.
 
@@
 
-The \acs{BHH} baseline is a name given to a specific configuration of the \acs{BHH} which, during development, has been found to provide a reasonable baseline performance.
+The \acs{BHH} baseline is a name given to a specific configuration of the \acs{BHH} which has been found to provide a reasonable baseline performance.
 The baseline configuration is used as the cornerstone configuration from which all other heuristics and their configurations are evaluated.
-The \acs{BHH} baseline is also used for the behavioural study of the \acs{BHH}.
 The \acs{BHH} baseline configuration is given in Table \ref{tab:methodology:bhh_baseline_configuration}.
+In Table \ref{tab:methodology:bhh_baseline_configuration}, the heuristic pool configuration, \textit{all}, refers to a configuration where the heuristic pool contains all the low-level heuristics including all gradient-based heuristics and \acp{MH}.
 
@@
 
-In Table \ref{tab:methodology:bhh_baseline_configuration}, the heuristic pool configuration that is used, is referred to as \textit{all}.
-The \textit{all} configuration refers to a configuration where the heuristic pool contains all the low-level heuristics as presented in Section \ref{sec:methodology:heuristics}, including all gradient-based heuristics and \acp{MH}
-
-\subsection{Performance Measures}\label{sec:methodology:performance_measures}
-
-In this dissertation, \acs{BinXE} is used for classification problems with two classes and \acs{SparseCatXE} is used for classification problems with more than two classes.
-For the classification problems, accuracy is also measured.
-Accuracy refers to the proportion of correct classifications.
-For regression problems, the \acs{RMSE} is used as a performance metric.
-
-The test set is used as a validation set during training.
-All performance metrics are measured for the training set as well as the test/validation set during training.
-As such, a divergence in performance metrics between the training and test/validation set is used to evaluate for overfitting during the training process.
-
-After training has been completed, the \textit{average rank}, based on test loss, for all configurations, is calculated at each mini-batch step.
-A total of 30 independent runs with different random seed configurations are executed for each empirical test.
-The test loss metric and average rank are then statistically analysed across all runs, and are used to derive findings and conclusions.
-
-\subsection{Stopping Conditions}\label{sec:methodology:stopping_conditions}
-
-For this dissertation, the \textit{maximum epoch} stopping condition is used, where a fixed, maximum number of training steps and epochs are executed and training is not halted until the maximum number of epochs have been reached.
-\acp{FFNN} are trained for a maximum of 30 epochs.
-Early stopping is not implemented for the empirical process in this dissertation.
-
 \subsection{Experiments}
@@
 
-This section presents the experimental groups that are executed in the empirical process.
-Three main experimental groups are formulated.
-Each of these are discussed in more detail in the following sections.
+This section provides the details of the two experimental groups that are implemented and executed.
 
@@
 
-The behavioural case study analyses the behaviour of the \acs{BHH} baseline configuration as it relates to an example problem dataset, across 30 independent runs.
+The behavioural case study analyses the behaviour of the \acs{BHH} baseline configuration as it relates to an example problem dataset.
 The example problem dataset is the iris dataset, presented in Table \ref{tab:methodology:datasets:classification}.
-The behavioural case study is meant to provide an introductory analysis of the inner workings of the \acs{BHH} and includes analysis of the selection mechanism, as well as the perturbative nature of the \acs{BHH}.
-The behavioural case study is used to determine if the \acs{BHH} is learning and that selection is indeed biasing towards better performance.
-These observations also provide an opportunity to observe the outcome of the perturbative nature of the \acs{BHH}, which includes proxied heuristic update step operations.
-
-The behavioural case study provides an implementation of the \acs{BHH} baseline which, by default, has a replay window size of 10.
-The baseline configuration is provided and compared to an implementation of a \acs{BHH} configuration where the replay window size is large (250), as well as an implementation of the \acs{BHH} using the \textit{symmetric} credit assignment strategy.
+The behavioural case study provides insight into the inner workings of the \acs{BHH}.
+The \acs{BHH} baseline, by default, has a replay window size of 10.
+The baseline configuration is compared to an implementation of a \acs{BHH} configuration where the replay window size is large (250), as well as an implementation of the \acs{BHH} using the \textit{symmetric} credit assignment strategy.
 The large replay window size configuration is used to show the behaviour of the \acs{BHH} when it has access to a large number of performance log samples, which increases the statistical certainty of the learning outcome.
@@
 
-\subsubsection{Standalone Heuristics}
+\subsection{Standalone Heuristics}
 \label{sec:methodology:experiments:standalone_optimisers}
 
-For the standalone heuristics experimental group, the heuristics, as presented in Section \ref{sec:methodology:heuristics}, are used along with their specified hyper-parameters.
+For the standalone heuristics experimental group, a number of low-level heuristics are used along with their specified hyper-parameters.
 Each of these standalone low-level heuristics are compared to that of the \acs{BHH} baseline configuration, across all datasets.
-
 The intent of the standalone heuristics experimental group is to determine if the \acs{BHH} baseline configuration can generalise to multiple problems in comparison to individual low-level heuristics.
@@
 
+\subsection{Heuristics}\label{sec:methodology:heuristics}
+
+Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level heuristics that are used as well as their hyper-parameter configurations.
+Note from Table \ref{tab:methodology:heuristics} that values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it.
+
+The mapping of proxied heuristic state update operations implemented by the \acs{BHH} in the empirical process is given in Figure \ref{fig:methodology:heuristics:proxies}.
+In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x} indicate that the associated heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
+
+\subsection{Datasets}\label{sec:methodology:datasets}
+
+In the context of training \acp{FFNN}, the underlying models are trained across a number of datasets.
+All the datasets used in the empirical process originate from the UCI Machine Learning Repository~\cite{ref:uci:2022}.
+Datasets are grouped by problem type and include seven classification and seven regression datasets.
+The details around the datasets used can be found in Tables \ref{tab:methodology:datasets:classification} and \ref{tab:methodology:datasets:regression}.
+Each dataset is split into a training set comprising of 80\% of the data, and a test set comprising of 20\% of the data.
+The test set is used as a validation set during training.
+
+A number of classification datasets contain an unbalanced representation of classes.
+This work does not apply mechanisms to cater for class balancing, in order to eliminate as many variables and factors in the empirical process as possible.
+
+\subsection{Models}\label{sec:methodology:model}
+
+All models that are trained in the empirical process follow implementations of shallow \acp{FFNN} with only one hidden layer.
+The number of hidden units used were determined empirically.
+Weights are initialised by means of Glorot uniform sampling~\cite{ref:glorot:2010}.
+The models and their configuration, as it is used for each dataset, are given in Table \ref{tab:methodology:models:configurations}.
+
+\subsection{Performance Measures}\label{sec:methodology:performance_measures}
+
+\acs{BinXE} is used for classification problems with two classes and \acs{SparseCatXE} is used for classification problems with more than two classes.
+For the classification problems, accuracy is also measured.
+For regression problems, the \acs{MSE} is used as a performance metric.
+After training has been completed, the \textit{average rank}, based on test loss, for all configurations, is calculated at each mini-batch step.
+
 \subsection{Statistical Analysis}
@@
 
-The results from each of these experimental groups are statistically analysed.
-Eeach experiment and configuration is trained for 30 epochs and is repeated over 30 runs, for each of the fourteen datasets.
-The experimental results contain performance evaluation data for the training and testing datasets, and includes loss and accuracy measurements.
+Each experiment and configuration is trained for a maximum of 30 epochs and is repeated over 30 independent runs, for each of the applicable datasets.
 Statistical analysis is executed on the results from the testing datasets.
-An average rank is calculated across all 30 runs, for all experimental groups and configurations, at each step, for every epoch of training.
-Each run is executed using a unique random seed, such that each run is identical in its setup and configuration, but unique between runs.
+An average rank is calculated across all 30 runs, for both experimental groups and configurations, at each step, for every epoch of training.
 
-The evaluation of outcome is based on the aggregated statistical results as mentioned above.
-A descriptive analysis is executed on the spread of the data.
-The results are analysed and checked for overfitting and outliers are identified.
-The skewness of the results is evaluated per dataset and the Shapiro-Wilk test for normality~\cite{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
-Furthermore, the Levene's test for equality of variance~\cite{ref:levene:1961} ($\alpha$ = 0.001) is used.
-The output of the full statistical analysis is presented in Appendix \ref{app:statistical_analysis}.
-
-Dependent on the outcomes of the above statistical tests, the appropriate statistical significance test is then executed.
-For experiments where there are only two configurations, the Mann-Whitney U independent samples t-Test~\cite{ref:mann:1947} ($\alpha$ = 0.001) is executed.
+The Shapiro-Wilk test for normality~\cite{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
+The Levene's test for equality of variance~\cite{ref:levene:1961} ($\alpha$ = 0.001) is used.
 For experiments with three or more configurations, the \acs{ANOVA} statistical test~\cite{ref:fisher:1921} ($\alpha$ = 0.001) is used.
 The Kruskal-Wallis ranked non-parametric test~\cite{ref:kruskal:1952} for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
-
-Regardless of the statistical test that is used, a post-hoc Tukey honest significant difference test~\cite{ref:tukey:1949} ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
+Finally, a post-hoc Tukey honest significant difference test~\cite{ref:tukey:1949} ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
 Descriptive and critical difference plots are then retrieved from these results to provide visual aid.
@@
 All implementations are done from first principles in Python 3.9 using Tensorflow 2.7 and Tensorflow Probability 0.15.0.
-Most underlying mathematical functions are reused from the Tensorflow library, however, all heuristics are implemented from first principles to fit the \acs{HH} framework that was developed.
-The source code and data for this dissertation is provided and made public at \url{https://github.com/arneschreuder/masters}.
-
-It should be noted that this implementation makes heavy use of CPU processing, due to flattening of the \acs{FFNN} weights by the heuristics.
-For this reason, execution is much more timely and costly than with GPU training.
-
-All experiments were run on the Centre for High Performance Computing (CHPC) cluster.
-A total of 14 different server were used, each running 24 to 56 cores and 256GB of memory.
-The entire empirical process took six days.
+The source code and data for this research is provided and made public at \url{https://github.com/arneschreuder/masters}.

### 2023-02-04 article/appendices/c-datasets.tex
🚧 (article): WIP save point for revision

@@
 			\midrule
-			iris             & multivariate    & real                       & 4                   & 3                & 150                & 16             & 10             & ~\cite{ref:fisher:1936}    \\
-			car              & multivariate    & categorical                & 6                   & 4                & 1728               & 128            & 14             & ~\cite{ref:bohanec:1988}   \\
-			abalone          & multivariate    & categorical, integer, real & 8                   & 28               & 4177               & 256            & 17             & ~\cite{ref:waugh:1995}     \\
-			wine quality     & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & ~\cite{ref:cortez:2009}    \\
-			mushroom         & multivariate    & categorical                & 22                  & 2                & 8214               & 512            & 17             & ~\cite{ref:schlimmer:1987} \\
-			bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & ~\cite{ref:moro:2014}      \\
-			diabetic         & multivariate    & integer                    & 55                  & 3                & 100000             & 1024           & 98             & ~\cite{ref:strack:2014}    \\
+			iris             & multivariate    & real                       & 4                   & 3                & 150                & 16             & 10             & \cite{ref:fisher:1936}    \\
+			car              & multivariate    & categorical                & 6                   & 4                & 1728               & 128            & 14             & \cite{ref:bohanec:1988}   \\
+			abalone          & multivariate    & categorical, integer, real & 8                   & 28               & 4177               & 256            & 17             & \cite{ref:waugh:1995}     \\
+			wine quality     & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & \cite{ref:cortez:2009}    \\
+			mushroom         & multivariate    & categorical                & 22                  & 2                & 8214               & 512            & 17             & \cite{ref:schlimmer:1987} \\
+			bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & \cite{ref:moro:2014}      \\
+			diabetic         & multivariate    & integer                    & 55                  & 3                & 100000             & 1024           & 98             & \cite{ref:strack:2014}    \\
 		\end{tabular}%
@@
 			\midrule
-			fish toxicity       & multivariate              & real           & 7                   & 908                & 64             & 15             & ~\cite{ref:cassotti:2015} \\
-			housing             & univariate                & real           & 13                  & 506                & 32             & 16             & ~\cite{ref:harrison:1978} \\
-			forest fires        & multivariate              & real           & 13                  & 517                & 32             & 17             & ~\cite{ref:cortez:2007}   \\
-			student performance & multivariate              & integer        & 33                  & 649                & 32             & 21             & ~\cite{ref:cortez:2008}   \\
-			parkinsons          & multivariate              & integer, real  & 26                  & 5875               & 256            & 23             & ~\cite{ref:tsanas:2009}   \\
-			air quality         & multivariate, time series & real           & 15                  & 9358               & 256            & 37             & ~\cite{ref:de:2008}       \\
-			bike                & univariate                & integer, real  & 16                  & 17389              & 256            & 68             & ~\cite{ref:fanaee:2014}   \\
+			fish toxicity       & multivariate              & real           & 7                   & 908                & 64             & 15             & \cite{ref:cassotti:2015} \\
+			housing             & univariate                & real           & 13                  & 506                & 32             & 16             & \cite{ref:harrison:1978} \\
+			forest fires        & multivariate              & real           & 13                  & 517                & 32             & 17             & \cite{ref:cortez:2007}   \\
+			student performance & multivariate              & integer        & 33                  & 649                & 32             & 21             & \cite{ref:cortez:2008}   \\
+			parkinsons          & multivariate              & integer, real  & 26                  & 5875               & 256            & 23             & \cite{ref:tsanas:2009}   \\
+			air quality         & multivariate, time series & real           & 15                  & 9358               & 256            & 37             & \cite{ref:de:2008}       \\
+			bike                & univariate                & integer, real  & 16                  & 17389              & 256            & 68             & \cite{ref:fanaee:2014}   \\
 		\end{tabular}%

### 2023-02-04 article/appendices/h-results-bhh-vs-heuristics-loss.tex
🚧 (article): WIP save point for revision

--- 2023-02-01 article/sections/08-results.tex
@@
-\section{Results}
-\label{sec:results}
-
-This section provides the results of all the experiments that have been conducted.
-Detailed discussions follow on the outcomes of each experiment.
-Discussions are accompanied by figures and plots to help provide visual aid for discussions.
-The output of the statistical analysis that yielded the results is provided in Appendix \ref{app:statistical_analysis}.
-
-\subsection{Overview}\label{sec:results:overview}
-
-This section provides a brief discussion on the general outcome of the empirical process as a whole.
-Overall, the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets.
-In general, the \acs{BHH} performs well and the empirical process provides key insights into the workings of the \acs{BHH}.
-Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.
-
-Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results.
-The \acs{BHH} applies a form of online learning.
-As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process.
-The training process is not repeated iteratively.
-All experiments conducted are executed for 30 epochs.
-The number of training steps executed is dependent on the batch size applied for each dataset.
-
-All of the underlying \acp{FFNN} trained in the empirical process are relatively small.
-As such, most of the training progress is observed to occur within the first five epochs.
-As a result, the \acs{BHH} should apply most learning at the early stages of the training process.
-After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point.
-Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the heuristic space beyond the five epoch mark.
-
-The \acs{BHH} does not implement a move-acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution.
-In some cases the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.
-
-Given the stochastic nature of the heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn.
-This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}.
-The probabilistic model implements \textit{probability distributions of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.
-
-The \textit{reanalysis interval} defines intervals at which the \acs{BHH} reanalyses the performance log, in effect, resetting the concentration parameters to their default values and reapplying the underlying Bayesian analysis process on the performance log.
-Furthermore, the \textit{replay window size} defines the amount of performance evidence in the performance log.
-By default, the \acs{BHH} baseline configuration has a reanalysis interval of 10, and a replay window size of 10, which is a small window to learn from.
-Despite the small reanalysis interval and the small replay window size, it should be observed that the \acs{BHH} exploits small performance biases regardless and does find small performance gains throughout.
-
-\subsection{Behavioural Case Study}\label{sec:results:case_study}
-
-This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset.
-As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records.
-The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process.
-Mini-batch training is executed with a batch size of 30.
-The results that are presented are averaged over 30 independent runs.
-
-The case study focuses on three variants of the \acs{BHH}.
-These include the baseline configuration, as was provided in Section \ref{sec:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}).
-Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}).
-Finally, the case study includes a configuration that makes use of the \textit{symmetric} credit assignment strategy hyper-parameter, and is denoted as bhh\_credit\_symmetric (illustrated throughout in \textcolor{blue}{blue}).
-
-These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level heuristics in the heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards heuristics that perform well at all.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% METRICS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Performance Metrics}\label{sec:results:case_study:performance_metrics}
-
-This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}.
-Figures \ref{fig:results:case_study:metrics:train_loss} to \ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
-		\caption{Train log loss}
-		\label{fig:results:case_study:metrics:train_loss}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
-		\caption{Test log loss}
-		\label{fig:results:case_study:metrics:test_loss}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:case_study:metrics:train_accuracy}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:case_study:metrics:test_accuracy}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average train and test loss and accuracy plots over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:metrics}
-\end{figure}
-
-The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}, observed by the convergence of the training process, yielding good results.
-Figures \ref{fig:results:case_study:metrics:train_accuracy} and \ref{fig:results:case_study:metrics:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%.
-
-Although the different configurations of the \acs{BHH} are all able to successfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.
-
-The volatility and minor divergence of the test loss compared to the training loss, observed in Figure \ref{fig:results:case_study:metrics:test_loss}, is due to overfitting and partly due to the noisiness that results from mini-batch training.
-Early stopping can be applied to the training process to halt training before the model overfits on the training data.
-The training dataset is also very small, with just 120 samples.
-Furthermore, a very small batch size of 16 is used.
-As such, noisiness and overfitting can be expected.
-
-From Figure \ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed.
-This could simply be a result of momentum that is maintained when switching between low-level heuristics in an attempt to find better solutions.
-For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions.
-The \acs{BHH} does not incorporate a \textit{move-acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set.
-A move-acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.
-
-Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figure \ref{fig:results:case_study:metrics} only provides the outcomes of performance metrics at the end of each epoch.
-Further investigation is required at a mini-batch step level and is provided in the following sections.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS ALPHAS
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}
-
-To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
-Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
-The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{heuristic selection probabilities}.
-Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
-Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the heuristic pool.
-Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
-		\caption{$\alpha_{0}$ - \acs{SGD}}
-		\label{fig:results:case_study:alphas:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
-		\caption{$\alpha_{6}$ - \acs{Adam}}
-		\label{fig:results:case_study:alphas:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
-		\caption{$\alpha_{7}$ - \acs{PSO}}
-		\label{fig:results:case_study:alphas:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
-		\caption{$\alpha_{8}$ - \acs{GA}}
-		\label{fig:results:case_study:alphas:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:alphas}
-\end{figure}
-
-The first logical observation to be made from Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
-Since the replay window size is sufficiently large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
-The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process.
-However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$.
-The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}.
-Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly than other heuristics that do not perform well.
-
-The next observations that can be made are for the bhh\_baseline configuration, illustrated in \textcolor{red}{red}, and the bhh\_credit\_symmetric configuration in \textcolor{blue}{blue}.
-Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1.0 as regular intervals.
-This interval is defined by the \textit{reanalysis interval} hyper-parameter.
-The reanalysis interval dictates the frequency at which Bayesian analysis is conducted on the performance log, maintained by the \acs{BHH}.
-Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval.
-As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.
-
-Notice from Figure \ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements.
-This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process.
-Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process.
-
-Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning.
-The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
-Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequently reselect these heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
-Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS THETAS
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Probability Distribution of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
-
-This section provides a detailed investigation into the \textit{probability distribution of heuristic selection probabilities} as it changes throughout the training process.
-As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modelling and thus, heuristic selection probabilities are defined by an underlying probabilistic distribution themselves.
-The probability distribution of heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.
-
-Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
-These illustrations are presented in log scale.
-Indices 0, 6, 7, and 8 represent the distribution of heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of heuristic selection probabilities in $\boldsymbol{\theta}$.
-Similar illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
-		\caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
-		\label{fig:results:case_study:thetas:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
-		\caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
-		\label{fig:results:case_study:thetas:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
-		\caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
-		\label{fig:results:case_study:thetas:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
-		\caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
-		\label{fig:results:case_study:thetas:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average sampled heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
-The heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:thetas}
-\end{figure}
-
-From the illustrations presented in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed.
-The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}.
-As a reminder, ten low-level heuristics are included in the heuristic pool, yielding an expected mean heuristics selection probability of 0.1, for each heuristic, by the frequentist view of probabilistic modelling.
-
-Towards the end of the training process, the heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a heuristic selection probability of 0.1, for all heuristics.
-This can be explained as follows: most of the training progress is made in the early stages of the training process, and training converges towards the end of the training process.
-Since training converges, all heuristics, no matter their past performances, fail to yield better solutions towards the end of the training process.
-As a result of training convergence, heuristics then fail to meet the performance criteria and credit allocations by means of the credit assignment strategy.
-
-Both the bhh\_baseline (\textcolor{red}{red}) and the bhh\_replay\_250 (\textcolor{green}{green}) configurations make use of the \textit{ibest} credit assignment strategy.
-The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yields the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
-However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ is reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.
-
-Another observation to make occurs in the first 30 steps of the training process.
-In Figure \ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same heuristic selection probabilities in these first 30 steps.
-This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number.
-This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches.
-This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.
-
-It should be noted that, despite using the same random seed across configurations for the same run number, the behavioural changes between the configurations start to show after about 30 steps.
-As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing heuristics.
-Where the bhh\_baseline and bhh\_replay\_250 configurations then diverge from the behaviour of the bhh\_credit\_symmetric configuration is proof of the effect of performance bias.
-
-Furthermore, it can be observed for small windows, at various steps for multiple runs, that the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, do not yield means that are equal to the expected heuristic selection probabilities of 0.1.
-This is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations.
-This is also true for the bhh\_credit\_symmetric configuration, as the bhh\_credit\_symmetric configuration biases towards heuristics that happen to be sampled, despite not biasing towards good performance.
-
-Finally, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar volatile behaviour, much more so than with the bhh\_replay\_250 configuration.
-This can be attributed to a very small reanalysis window combined with a small replay window size of 10, that contains very few samples to learn from.
-A small reanalysis interval and a small replay window size allows for more exploration of the heuristic space, but can also yield greater variance of the heuristic selection probabilities.
-Once again, any differences then in the behaviour of the bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations and biases by the bhh\_baseline configuration.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS P_H (Priors)
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Prior Heuristic Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}
-
-This section provides a brief investigation into the \textit{prior heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}.
-The prior heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
-As such, $P(\boldsymbol{H} \vert \boldsymbol{\theta}) = \boldsymbol{\theta}$ and heuristics are initially sampled such that $\boldsymbol{H} \sim Cat(\boldsymbol{\theta})$.
-
-Figures \ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
-Similar to before, these illustrations are also presented in log scale.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
-		\caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
-		\label{fig:results:case_study:p_H:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
-		\caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
-		\label{fig:results:case_study:p_H:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
-		\caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
-		\label{fig:results:case_study:p_H:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
-		\caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
-		\label{fig:results:case_study:p_H:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average prior heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8.
-The prior heuristic selection probabilities are sampled from the probability distribution of heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_H}
-\end{figure}
-
-The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure \ref{fig:results:case_study:thetas}.
-This is because of the \textit{reselection} interval hyper-parameter.
-The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity.
-Since the default \textit{reselection} interval is set to 10, the heuristic selection probabilities are only resampled at intervals of 10.
-These illustrations then simply yield rough approximations of the illustrations provided in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of heuristic selection probabilities.
-As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
-
-Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of heuristic performances.
-Since these prior heuristic selection probabilities change over time, it can be concluded that the change in prior heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}.
-Furthermore, the prior heuristic selection probability distribution provides an opportunity to utilise prior knowledge by some expert before training starts, by injecting heuristic selection biases, by means of the initial values for the concentration parameter $\boldsymbol{\alpha}$.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS P_HgEC (Posterior)
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Posterior Heuristic Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}
-
-This section provides a detailed discussion on the outcomes of the \textit{posterior heuristic selection probabilities}.
-These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}.
-The posterior heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy.
-Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of heuristic selection probabilities and the entity selection probabilities respectively.
-Finally, $\boldsymbol{\psi}$ represents the probability distribution of successful credit allocation probabilities.
-
-Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
-Similar to before, these illustrations are also presented in log scale.
-As before, illustrations for the other indices are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
-		\caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
-		\label{fig:results:case_study:p_HgEC:0:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
-		\caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
-		\label{fig:results:case_study:p_HgEC:0:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
-		\caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
-		\label{fig:results:case_study:p_HgEC:0:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
-		\caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
-		\label{fig:results:case_study:p_HgEC:0:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average calculated proportional posterior heuristic selection probabilities for heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, $c_{1}$, from the \textit{ibest} credit assignment strategy.
-The proportional posterior heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_HgEC:0}
-\end{figure}
-
-The main observation to make from Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a Categorical probability distribution from which new heuristic selections are sampled.
-The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Section \ref{sec:bhh}.
-As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
-
-Another observation to make is for the bhh\_replay\_250 configuration $(\textcolor{green}{green})$.
-Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} show that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities later in the training stages.
-The aforementioned suggests that the \acs{BHH} is not able to find further performance biases and cannot exploit better solutions.
-At this point, the \acs{BHH} starts to explore more as the concentration parameters are reanalysed more uniformly, resolving more and more to a random search in attempt to find better solutions.
-
-Furthermore, the posterior heuristic selection probability distribution is conditional on the occurrence of a specific entity that the potential heuristic will be applied to, as well as a specific performance criterion enforced by a specific credit assignment strategy.
-This means that heuristic selection is specific to each entity.
-A particular heuristic might be good for one entity, but not for another.
-This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct heuristic to the correct entity at the correct time in the training process.
-
-Finally, the posterior heuristic selection probabilities are much less volatile than their prior heuristic selection probability equivalents.
-This is a result of the information that is added in the performance log by tracking the entity and credit allocation as well.
-
-It can be concluded from Sections \ref{sec:results:case_study:performance_metrics} to \ref{sec:results:case_study:posterior_selec_prob} that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset.
-Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases, and thus the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-% BHH vs. Low-Level Heuristics
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsection{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
-
-This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics.
-Detailed discussions and illustrations follow.
-As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of \acp{MH}.
-Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a heuristic pool that contains only gradient-based heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a heuristics pool that contains only \acp{MH} (denoted bhh\_mh).
-
-Table \ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
+\section{Results: BHH vs. Low Level Heuristics - Average Test Loss}
+\label{app:appendix_results_bhh_vs_heuristics_loss}
 
@@
 \end{sidewaystable}%
-
-Table \ref{tab:results:standalone:metrics:loss} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
-The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the heuristics.
-
-Table \ref{tab:results:standalone:metrics:rank} provides the empirical results from Table \ref{tab:results:standalone:metrics:loss} in ranked format.
-The performance rank is calculated as the average rank produced by each heuristic, across all datasets, for all independent runs and all epochs.
-The average rank across all epochs produces a view on the performance of the heuristics as it relates to the entire training process.
-Finally, a normalised average rank is provided for the overall performance of all heuristics at the bottom of the table.
-The normalised average rank is calculated as a discrete normalisation of the average rank achieved across all datasets, for all independent runs and epochs.
-
-\begin{sidewaystable}[htbp]
-	\centering
-	\caption{Empirical results showing normalised average rank and statistics for different low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:standalone:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccc|c|c|c|c|c|ccccc}
-			                             & \multicolumn{13}{c}{\textbf{BHH vs.
-Low-Level Heuristics - Average Rank (Based on Test Loss)}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\
-			\textbf{dataset}             & \textbf{adagrad}                                                                               & \textbf{adam}                                           & \textbf{rmsprop}                                        & \textbf{bhh\_gd}                                        & \textbf{nag}                                            & \textbf{bhh\_all}                                       & \textbf{adadelta}                                       & \textbf{bhh\_mh}                                        & \textbf{ga}                                              & \textbf{pso}                                             & \textbf{sgd}                                             & \textbf{momentum}                                        & \textbf{de}                                              \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.2215 ($\pm$1.591)                                        & \cellcolor[rgb]{ .416,  .753,  .482}2.3989 ($\pm$1.887) & \cellcolor[rgb]{ .78,  .859,  .502}4.6172 ($\pm$2.65)   & \cellcolor[rgb]{ .796,  .863,  .506}4.7032 ($\pm$2.108) & \cellcolor[rgb]{ .725,  .839,  .498}4.2731 ($\pm$1.542) & \cellcolor[rgb]{ 1,  .922,  .518}5.9376 ($\pm$2.399)    & \cellcolor[rgb]{ .894,  .89,  .51}5.3129 ($\pm$1.478)   & \cellcolor[rgb]{ .992,  .749,  .486}8.1882 ($\pm$1.195) & \cellcolor[rgb]{ .98,  .525,  .443}11.1108 ($\pm$1.102)  & \cellcolor[rgb]{ .98,  .514,  .439}11.2559 ($\pm$1.826)  & \cellcolor[rgb]{ .992,  .718,  .478}8.628 ($\pm$1.019)   & \cellcolor[rgb]{ .984,  .624,  .463}9.8151 ($\pm$1.16)   & \cellcolor[rgb]{ .973,  .412,  .42}12.5376 ($\pm$1.329)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                                        & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .455,  .765,  .486}2.5495 ($\pm$1.598)                                        & \cellcolor[rgb]{ .388,  .745,  .482}2.0796 ($\pm$1.587) & \cellcolor[rgb]{ .588,  .8,  .49}3.4645 ($\pm$2.209)    & \cellcolor[rgb]{ .8,  .863,  .506}4.8828 ($\pm$1.702)   & \cellcolor[rgb]{ .71,  .835,  .498}4.2871 ($\pm$1.732)  & \cellcolor[rgb]{ 1,  .922,  .518}6.2419 ($\pm$2.157)    & \cellcolor[rgb]{ .914,  .894,  .51}5.672 ($\pm$1.241)   & \cellcolor[rgb]{ .988,  .639,  .463}9.7495 ($\pm$1.048) & \cellcolor[rgb]{ .98,  .537,  .447}10.9817 ($\pm$1.216)  & \cellcolor[rgb]{ .976,  .467,  .431}11.8376 ($\pm$1.464) & \cellcolor[rgb]{ .992,  .757,  .486}8.2774 ($\pm$1.03)   & \cellcolor[rgb]{ .992,  .741,  .486}8.4774 ($\pm$1.068)  & \cellcolor[rgb]{ .973,  .412,  .42}12.4989 ($\pm$1.224)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}1.7204 ($\pm$1.384)                                        & \cellcolor[rgb]{ .643,  .816,  .494}3.6925 ($\pm$4.004) & \cellcolor[rgb]{ .973,  .914,  .514}6.2624 ($\pm$4.58)  & \cellcolor[rgb]{ .663,  .824,  .498}3.8441 ($\pm$1.398) & \cellcolor[rgb]{ 1,  .922,  .518}6.4516 ($\pm$1.02)     & \cellcolor[rgb]{ .71,  .835,  .498}4.2151 ($\pm$1.361)  & \cellcolor[rgb]{ .859,  .878,  .506}5.3602 ($\pm$1.155) & \cellcolor[rgb]{ .996,  .843,  .506}7.4108 ($\pm$1.008) & \cellcolor[rgb]{ .988,  .686,  .475}9.2269 ($\pm$1.183)  & \cellcolor[rgb]{ .988,  .682,  .475}9.3086 ($\pm$1.761)  & \cellcolor[rgb]{ .984,  .596,  .455}10.3355 ($\pm$1.419) & \cellcolor[rgb]{ .984,  .561,  .451}10.7086 ($\pm$1.423) & \cellcolor[rgb]{ .973,  .412,  .42}12.4634 ($\pm$1.465)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .702,  .835,  .498}4.7634 ($\pm$0.938)                                        & \cellcolor[rgb]{ .388,  .745,  .482}1.6226 ($\pm$1.405) & \cellcolor[rgb]{ .455,  .765,  .486}2.3269 ($\pm$1.409) & \cellcolor[rgb]{ .561,  .792,  .49}3.3473 ($\pm$1.35)   & \cellcolor[rgb]{ .831,  .871,  .506}6.0785 ($\pm$0.799) & \cellcolor[rgb]{ .58,  .8,  .49}3.5624 ($\pm$1.315)     & \cellcolor[rgb]{ 1,  .922,  .518}7.7344 ($\pm$1.746)    & \cellcolor[rgb]{ .996,  .8,  .498}8.8505 ($\pm$1.413)   & \cellcolor[rgb]{ .984,  .592,  .455}10.7763 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .855,  .506}8.3613 ($\pm$1.622)     & \cellcolor[rgb]{ .988,  .651,  .467}10.2452 ($\pm$1.447) & \cellcolor[rgb]{ .984,  .576,  .451}10.9226 ($\pm$1.349) & \cellcolor[rgb]{ .973,  .412,  .42}12.4086 ($\pm$1.492)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .506,  .776,  .486}2.7796 ($\pm$1.659)                                        & \cellcolor[rgb]{ 1,  .886,  .514}7.1484 ($\pm$2.227)    & \cellcolor[rgb]{ 1,  .922,  .518}6.7376 ($\pm$2.577)    & \cellcolor[rgb]{ .812,  .867,  .506}5.2269 ($\pm$2.186) & \cellcolor[rgb]{ .388,  .745,  .482}1.8118 ($\pm$1.413) & \cellcolor[rgb]{ .988,  .69,  .475}9.3968 ($\pm$3.022)  & \cellcolor[rgb]{ .494,  .773,  .486}2.6753 ($\pm$1.629) & \cellcolor[rgb]{ .992,  .765,  .49}8.557 ($\pm$1.17)    & \cellcolor[rgb]{ .98,  .529,  .443}11.2011 ($\pm$1.413)  & \cellcolor[rgb]{ .984,  .573,  .451}10.7022 ($\pm$1.067) & \cellcolor[rgb]{ .898,  .89,  .51}5.9215 ($\pm$1.542)    & \cellcolor[rgb]{ .949,  .906,  .514}6.3355 ($\pm$1.612)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5065 ($\pm$1.242)  \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                                         & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                                        & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\
-			\textbf{housing}             & \cellcolor[rgb]{ .404,  .749,  .482}3.4484 ($\pm$2.025)                                        & \cellcolor[rgb]{ .388,  .745,  .482}3.3344 ($\pm$1.819) & \cellcolor[rgb]{ .439,  .757,  .482}3.6946 ($\pm$2.166) & \cellcolor[rgb]{ .553,  .792,  .49}4.4742 ($\pm$2.312)  & \cellcolor[rgb]{ .584,  .8,  .49}4.6839 ($\pm$2.658)    & \cellcolor[rgb]{ .537,  .788,  .49}4.3763 ($\pm$2.438)  & \cellcolor[rgb]{ 1,  .918,  .518}7.5903 ($\pm$2.748)    & \cellcolor[rgb]{ 1,  .922,  .518}7.5441 ($\pm$1.736)    & \cellcolor[rgb]{ 1,  .878,  .51}7.8839 ($\pm$2.099)      & \cellcolor[rgb]{ .984,  .608,  .459}9.9409 ($\pm$2.317)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4075 ($\pm$1.528)  & \cellcolor[rgb]{ .976,  .431,  .424}11.2731 ($\pm$1.506) & \cellcolor[rgb]{ .976,  .42,  .424}11.3484 ($\pm$2.096)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .965,  .91,  .514}6.3946 ($\pm$1.6)                                           & \cellcolor[rgb]{ .525,  .784,  .49}3.5839 ($\pm$2.511)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6968 ($\pm$1.912) & \cellcolor[rgb]{ .706,  .835,  .498}4.7473 ($\pm$2.275) & \cellcolor[rgb]{ .522,  .78,  .486}3.5548 ($\pm$2.125)  & \cellcolor[rgb]{ .78,  .859,  .502}5.2204 ($\pm$3.041)  & \cellcolor[rgb]{ .973,  .412,  .42}11.3527 ($\pm$1.779) & \cellcolor[rgb]{ 1,  .922,  .518}6.6075 ($\pm$2.555)    & \cellcolor[rgb]{ .992,  .749,  .486}8.2473 ($\pm$1.765)  & \cellcolor[rgb]{ .992,  .745,  .486}8.2731 ($\pm$4.384)  & \cellcolor[rgb]{ .98,  .518,  .443}10.3796 ($\pm$1.294)  & \cellcolor[rgb]{ .976,  .447,  .427}11.0548 ($\pm$1.409) & \cellcolor[rgb]{ .988,  .678,  .471}8.8871 ($\pm$3.251)  \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .71,  .835,  .498}4.4656 ($\pm$1.053)                                         & \cellcolor[rgb]{ .388,  .745,  .482}2.1344 ($\pm$1.883) & \cellcolor[rgb]{ .431,  .757,  .482}2.4656 ($\pm$1.359) & \cellcolor[rgb]{ .569,  .796,  .49}3.4484 ($\pm$1.602)  & \cellcolor[rgb]{ .969,  .91,  .514}6.3323 ($\pm$0.891)  & \cellcolor[rgb]{ .6,  .804,  .494}3.6688 ($\pm$2.469)   & \cellcolor[rgb]{ 1,  .922,  .518}6.5538 ($\pm$1.071)    & \cellcolor[rgb]{ .992,  .718,  .478}9.0452 ($\pm$1.093) & \cellcolor[rgb]{ .98,  .51,  .439}11.5731 ($\pm$1.193)   & \cellcolor[rgb]{ .996,  .816,  .498}7.872 ($\pm$0.92)    & \cellcolor[rgb]{ .988,  .659,  .471}9.7527 ($\pm$1.083)  & \cellcolor[rgb]{ .98,  .557,  .451}10.9785 ($\pm$1.108)  & \cellcolor[rgb]{ .973,  .412,  .42}12.7097 ($\pm$1.478)  \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .412,  .749,  .482}2.4677 ($\pm$1.497)                                        & \cellcolor[rgb]{ .388,  .745,  .482}2.2333 ($\pm$1.742) & \cellcolor[rgb]{ .541,  .788,  .49}3.5656 ($\pm$2.492)  & \cellcolor[rgb]{ .655,  .82,  .494}4.572 ($\pm$1.934)   & \cellcolor[rgb]{ 1,  .922,  .518}7.5355 ($\pm$1.44)     & \cellcolor[rgb]{ .635,  .816,  .494}4.3839 ($\pm$1.861) & \cellcolor[rgb]{ .875,  .882,  .51}6.472 ($\pm$2.423)   & \cellcolor[rgb]{ .996,  .843,  .506}8.3161 ($\pm$1.644) & \cellcolor[rgb]{ 1,  .898,  .514}7.7968 ($\pm$1.719)     & \cellcolor[rgb]{ .996,  .827,  .502}8.4892 ($\pm$1.901)  & \cellcolor[rgb]{ .98,  .494,  .435}11.7516 ($\pm$1.155)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5419 ($\pm$1.351)  & \cellcolor[rgb]{ .984,  .584,  .455}10.8742 ($\pm$1.317) \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                                        & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                                         & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}3.5512 ($\pm$2.25)                                         & \cellcolor[rgb]{ .471,  .769,  .486}3.9314 ($\pm$3.423) & \cellcolor[rgb]{ .616,  .808,  .494}4.5691 ($\pm$3.517) & \cellcolor[rgb]{ .631,  .812,  .494}4.6346 ($\pm$2.364) & \cellcolor[rgb]{ .675,  .827,  .498}4.8394 ($\pm$2.384) & \cellcolor[rgb]{ .808,  .867,  .506}5.4327 ($\pm$2.9)   & \cellcolor[rgb]{ 1,  .922,  .518}6.2727 ($\pm$3.004)    & \cellcolor[rgb]{ .992,  .776,  .49}7.7855 ($\pm$2.271)  & \cellcolor[rgb]{ .988,  .639,  .467}9.1522 ($\pm$2.48)   & \cellcolor[rgb]{ .984,  .612,  .459}9.4451 ($\pm$2.75)   & \cellcolor[rgb]{ .984,  .592,  .455}9.6445 ($\pm$2.214)  & \cellcolor[rgb]{ .98,  .529,  .443}10.2877 ($\pm$2.346)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4538 ($\pm$2.354)  \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                                                          & \cellcolor[rgb]{ .49,  .773,  .486}2                    & \cellcolor[rgb]{ .592,  .804,  .494}3                   & \cellcolor[rgb]{ .694,  .831,  .498}4                   & \cellcolor[rgb]{ .796,  .863,  .506}5                   & \cellcolor[rgb]{ .898,  .89,  .51}6                     & \cellcolor[rgb]{ 1,  .922,  .518}7                      & \cellcolor[rgb]{ .996,  .839,  .502}8                   & \cellcolor[rgb]{ .992,  .753,  .486}9                    & \cellcolor[rgb]{ .988,  .667,  .471}10                   & \cellcolor[rgb]{ .984,  .584,  .455}11                   & \cellcolor[rgb]{ .98,  .498,  .439}12                    & \cellcolor[rgb]{ .973,  .412,  .42}13                    \\
-			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
-
-	}
-\end{sidewaystable}%
-
-From the normalised average ranks provided in Table \ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen heuristic implementations respectively.
-These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.
-
-Figure \ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each heuristic, per dataset.
-The heuristics are ordered according to the normalised ranks presented in Table \ref{tab:results:standalone:metrics:rank}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all independent runs and epochs.}
-	\label{fig:results:standalone:descriptive:descriptive}
-\end{figure}
-
-From Figure \ref{fig:results:standalone:descriptive:descriptive} a few observations can be made.
-Firstly, both \acs{Adam} and \acs{RMSProp} achieved radically different average ranks for the student performance dataset, compared to the other datasets.
-This can also be seen in Table \ref{tab:results:standalone:metrics:rank}.
-Further investigation into the reasons for this is required as both these heuristics perform well on all other datasets, and the other heuristics perform well for the student performance dataset.
-A suggestion is that an invalid learning rate or learning rate schedule leads to a scenario where good solutions are overshot, causing \acs{Adam} and \acs{RMSProp} to struggle to resolve back to good solutions.
-Furthermore, the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
-The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.
-
-Figure \ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each heuristic as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
-	\label{fig:results:standalone:descriptive:cd}
-\end{figure}
-
-Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all heuristics is very small.
-Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, is statistically only outperformed overall by \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}.
-It should be noted that the standalone low-level  heuristics already produce good results in general across all datasets.
-In this particular case, producing better performance outcomes can be hard to achieve.
-However, as mentioned previously, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.
-
-Another observation that can be made is that the gradient-based heuristics generally performed much better than the \acp{MH} on all datasets.
-State of the art methods for training \acp{FFNN}, such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions \cite{ref:kingma:2014}.
-Exploration of the heuristic space leads the \acs{BHH} to consider other heuristics during the training process, which could possibly result in worse performances at times.
-As previously mentioned, a suggestion to improve on these results is to include a move-acceptance strategy, where heuristic progressions are discarded if they fail to produce better results.
-
-Figures \ref{fig:results:standalone:figures:iris} to \ref{fig:results:standalone:figures:bank} provide example illustrations of the train and test loss and accuracy plots for each heuristic as it relates to a selection of classification datasets.
-The train and test loss and accuracy plots provided are illustrated in log scale.
-The other classification datasets are left out for brevity as they produce similar illustrations.
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/iris.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:iris}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/iris.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:iris}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/iris.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:iris}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/iris.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:iris}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:iris}
-\end{figure}
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the car dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:car}
-\end{figure}
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/bank.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/bank.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/bank.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/bank.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:bank}
-\end{figure}
-
-Figures \ref{fig:results:standalone:figures:fish_toxicity} to \ref{fig:results:standalone:figures:parkinsons} provide example illustrations of the train and test loss plots for each heuristic as it relates to a selection of regression datasets.
-The train and test loss plots provided are illustrated in log scale.
-Similar to before, the other regression datasets are left out for brevity as they produce similar illustrations.
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/fish_toxicity.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:fish_toxicity}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/fish_toxicity.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:fish_toxicity}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:fish_toxicity}
-\end{figure}
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/parkinsons.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:parkinsons}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/parkinsons.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:parkinsons}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:parkinsons}
-\end{figure}

### 2023-02-04 article/appendices/i-results-bhh-vs-heuristics-rank.tex
🚧 (article): WIP save point for revision

--- 2023-02-01 article/sections/08-results.tex
@@
-\section{Results}
-\label{sec:results}
-
-This section provides the results of all the experiments that have been conducted.
-Detailed discussions follow on the outcomes of each experiment.
-Discussions are accompanied by figures and plots to help provide visual aid for discussions.
-The output of the statistical analysis that yielded the results is provided in Appendix \ref{app:statistical_analysis}.
-
-\subsection{Overview}\label{sec:results:overview}
-
-This section provides a brief discussion on the general outcome of the empirical process as a whole.
-Overall, the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets.
-In general, the \acs{BHH} performs well and the empirical process provides key insights into the workings of the \acs{BHH}.
-Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.
-
-Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results.
-The \acs{BHH} applies a form of online learning.
-As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process.
-The training process is not repeated iteratively.
-All experiments conducted are executed for 30 epochs.
-The number of training steps executed is dependent on the batch size applied for each dataset.
-
-All of the underlying \acp{FFNN} trained in the empirical process are relatively small.
-As such, most of the training progress is observed to occur within the first five epochs.
-As a result, the \acs{BHH} should apply most learning at the early stages of the training process.
-After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point.
-Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the heuristic space beyond the five epoch mark.
-
-The \acs{BHH} does not implement a move-acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution.
-In some cases the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.
-
-Given the stochastic nature of the heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn.
-This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}.
-The probabilistic model implements \textit{probability distributions of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.
-
-The \textit{reanalysis interval} defines intervals at which the \acs{BHH} reanalyses the performance log, in effect, resetting the concentration parameters to their default values and reapplying the underlying Bayesian analysis process on the performance log.
-Furthermore, the \textit{replay window size} defines the amount of performance evidence in the performance log.
-By default, the \acs{BHH} baseline configuration has a reanalysis interval of 10, and a replay window size of 10, which is a small window to learn from.
-Despite the small reanalysis interval and the small replay window size, it should be observed that the \acs{BHH} exploits small performance biases regardless and does find small performance gains throughout.
-
-\subsection{Behavioural Case Study}\label{sec:results:case_study}
-
-This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset.
-As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records.
-The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process.
-Mini-batch training is executed with a batch size of 30.
-The results that are presented are averaged over 30 independent runs.
-
-The case study focuses on three variants of the \acs{BHH}.
-These include the baseline configuration, as was provided in Section \ref{sec:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}).
-Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}).
-Finally, the case study includes a configuration that makes use of the \textit{symmetric} credit assignment strategy hyper-parameter, and is denoted as bhh\_credit\_symmetric (illustrated throughout in \textcolor{blue}{blue}).
-
-These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level heuristics in the heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards heuristics that perform well at all.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% METRICS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Performance Metrics}\label{sec:results:case_study:performance_metrics}
-
-This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}.
-Figures \ref{fig:results:case_study:metrics:train_loss} to \ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
-		\caption{Train log loss}
-		\label{fig:results:case_study:metrics:train_loss}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
-		\caption{Test log loss}
-		\label{fig:results:case_study:metrics:test_loss}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:case_study:metrics:train_accuracy}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:case_study:metrics:test_accuracy}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average train and test loss and accuracy plots over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:metrics}
-\end{figure}
-
-The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}, observed by the convergence of the training process, yielding good results.
-Figures \ref{fig:results:case_study:metrics:train_accuracy} and \ref{fig:results:case_study:metrics:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%.
-
-Although the different configurations of the \acs{BHH} are all able to successfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.
-
-The volatility and minor divergence of the test loss compared to the training loss, observed in Figure \ref{fig:results:case_study:metrics:test_loss}, is due to overfitting and partly due to the noisiness that results from mini-batch training.
-Early stopping can be applied to the training process to halt training before the model overfits on the training data.
-The training dataset is also very small, with just 120 samples.
-Furthermore, a very small batch size of 16 is used.
-As such, noisiness and overfitting can be expected.
-
-From Figure \ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed.
-This could simply be a result of momentum that is maintained when switching between low-level heuristics in an attempt to find better solutions.
-For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions.
-The \acs{BHH} does not incorporate a \textit{move-acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set.
-A move-acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.
-
-Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figure \ref{fig:results:case_study:metrics} only provides the outcomes of performance metrics at the end of each epoch.
-Further investigation is required at a mini-batch step level and is provided in the following sections.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS ALPHAS
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}
-
-To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
-Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
-The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{heuristic selection probabilities}.
-Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
-Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the heuristic pool.
-Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
-		\caption{$\alpha_{0}$ - \acs{SGD}}
-		\label{fig:results:case_study:alphas:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
-		\caption{$\alpha_{6}$ - \acs{Adam}}
-		\label{fig:results:case_study:alphas:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
-		\caption{$\alpha_{7}$ - \acs{PSO}}
-		\label{fig:results:case_study:alphas:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
-		\caption{$\alpha_{8}$ - \acs{GA}}
-		\label{fig:results:case_study:alphas:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:alphas}
-\end{figure}
-
-The first logical observation to be made from Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
-Since the replay window size is sufficiently large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
-The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process.
-However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$.
-The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}.
-Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly than other heuristics that do not perform well.
-
-The next observations that can be made are for the bhh\_baseline configuration, illustrated in \textcolor{red}{red}, and the bhh\_credit\_symmetric configuration in \textcolor{blue}{blue}.
-Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1.0 as regular intervals.
-This interval is defined by the \textit{reanalysis interval} hyper-parameter.
-The reanalysis interval dictates the frequency at which Bayesian analysis is conducted on the performance log, maintained by the \acs{BHH}.
-Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval.
-As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.
-
-Notice from Figure \ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements.
-This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process.
-Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process.
-
-Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning.
-The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
-Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequently reselect these heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
-Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS THETAS
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Probability Distribution of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
-
-This section provides a detailed investigation into the \textit{probability distribution of heuristic selection probabilities} as it changes throughout the training process.
-As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modelling and thus, heuristic selection probabilities are defined by an underlying probabilistic distribution themselves.
-The probability distribution of heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.
-
-Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
-These illustrations are presented in log scale.
-Indices 0, 6, 7, and 8 represent the distribution of heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of heuristic selection probabilities in $\boldsymbol{\theta}$.
-Similar illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
-		\caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
-		\label{fig:results:case_study:thetas:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
-		\caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
-		\label{fig:results:case_study:thetas:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
-		\caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
-		\label{fig:results:case_study:thetas:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
-		\caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
-		\label{fig:results:case_study:thetas:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average sampled heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
-The heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:thetas}
-\end{figure}
-
-From the illustrations presented in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed.
-The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}.
-As a reminder, ten low-level heuristics are included in the heuristic pool, yielding an expected mean heuristics selection probability of 0.1, for each heuristic, by the frequentist view of probabilistic modelling.
-
-Towards the end of the training process, the heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a heuristic selection probability of 0.1, for all heuristics.
-This can be explained as follows: most of the training progress is made in the early stages of the training process, and training converges towards the end of the training process.
-Since training converges, all heuristics, no matter their past performances, fail to yield better solutions towards the end of the training process.
-As a result of training convergence, heuristics then fail to meet the performance criteria and credit allocations by means of the credit assignment strategy.
-
-Both the bhh\_baseline (\textcolor{red}{red}) and the bhh\_replay\_250 (\textcolor{green}{green}) configurations make use of the \textit{ibest} credit assignment strategy.
-The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yields the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
-However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ is reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.
-
-Another observation to make occurs in the first 30 steps of the training process.
-In Figure \ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same heuristic selection probabilities in these first 30 steps.
-This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number.
-This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches.
-This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.
-
-It should be noted that, despite using the same random seed across configurations for the same run number, the behavioural changes between the configurations start to show after about 30 steps.
-As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing heuristics.
-Where the bhh\_baseline and bhh\_replay\_250 configurations then diverge from the behaviour of the bhh\_credit\_symmetric configuration is proof of the effect of performance bias.
-
-Furthermore, it can be observed for small windows, at various steps for multiple runs, that the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, do not yield means that are equal to the expected heuristic selection probabilities of 0.1.
-This is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations.
-This is also true for the bhh\_credit\_symmetric configuration, as the bhh\_credit\_symmetric configuration biases towards heuristics that happen to be sampled, despite not biasing towards good performance.
-
-Finally, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar volatile behaviour, much more so than with the bhh\_replay\_250 configuration.
-This can be attributed to a very small reanalysis window combined with a small replay window size of 10, that contains very few samples to learn from.
-A small reanalysis interval and a small replay window size allows for more exploration of the heuristic space, but can also yield greater variance of the heuristic selection probabilities.
-Once again, any differences then in the behaviour of the bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations and biases by the bhh\_baseline configuration.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS P_H (Priors)
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Prior Heuristic Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}
-
-This section provides a brief investigation into the \textit{prior heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}.
-The prior heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
-As such, $P(\boldsymbol{H} \vert \boldsymbol{\theta}) = \boldsymbol{\theta}$ and heuristics are initially sampled such that $\boldsymbol{H} \sim Cat(\boldsymbol{\theta})$.
-
-Figures \ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
-Similar to before, these illustrations are also presented in log scale.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
-		\caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
-		\label{fig:results:case_study:p_H:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
-		\caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
-		\label{fig:results:case_study:p_H:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
-		\caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
-		\label{fig:results:case_study:p_H:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
-		\caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
-		\label{fig:results:case_study:p_H:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average prior heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8.
-The prior heuristic selection probabilities are sampled from the probability distribution of heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_H}
-\end{figure}
-
-The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure \ref{fig:results:case_study:thetas}.
-This is because of the \textit{reselection} interval hyper-parameter.
-The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity.
-Since the default \textit{reselection} interval is set to 10, the heuristic selection probabilities are only resampled at intervals of 10.
-These illustrations then simply yield rough approximations of the illustrations provided in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of heuristic selection probabilities.
-As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
-
-Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of heuristic performances.
-Since these prior heuristic selection probabilities change over time, it can be concluded that the change in prior heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}.
-Furthermore, the prior heuristic selection probability distribution provides an opportunity to utilise prior knowledge by some expert before training starts, by injecting heuristic selection biases, by means of the initial values for the concentration parameter $\boldsymbol{\alpha}$.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS P_HgEC (Posterior)
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Posterior Heuristic Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}
-
-This section provides a detailed discussion on the outcomes of the \textit{posterior heuristic selection probabilities}.
-These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}.
-The posterior heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy.
-Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of heuristic selection probabilities and the entity selection probabilities respectively.
-Finally, $\boldsymbol{\psi}$ represents the probability distribution of successful credit allocation probabilities.
-
-Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
-Similar to before, these illustrations are also presented in log scale.
-As before, illustrations for the other indices are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
-		\caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
-		\label{fig:results:case_study:p_HgEC:0:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
-		\caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
-		\label{fig:results:case_study:p_HgEC:0:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
-		\caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
-		\label{fig:results:case_study:p_HgEC:0:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
-		\caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
-		\label{fig:results:case_study:p_HgEC:0:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average calculated proportional posterior heuristic selection probabilities for heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, $c_{1}$, from the \textit{ibest} credit assignment strategy.
-The proportional posterior heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_HgEC:0}
-\end{figure}
-
-The main observation to make from Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a Categorical probability distribution from which new heuristic selections are sampled.
-The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Section \ref{sec:bhh}.
-As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
-
-Another observation to make is for the bhh\_replay\_250 configuration $(\textcolor{green}{green})$.
-Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} show that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities later in the training stages.
-The aforementioned suggests that the \acs{BHH} is not able to find further performance biases and cannot exploit better solutions.
-At this point, the \acs{BHH} starts to explore more as the concentration parameters are reanalysed more uniformly, resolving more and more to a random search in attempt to find better solutions.
-
-Furthermore, the posterior heuristic selection probability distribution is conditional on the occurrence of a specific entity that the potential heuristic will be applied to, as well as a specific performance criterion enforced by a specific credit assignment strategy.
-This means that heuristic selection is specific to each entity.
-A particular heuristic might be good for one entity, but not for another.
-This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct heuristic to the correct entity at the correct time in the training process.
-
-Finally, the posterior heuristic selection probabilities are much less volatile than their prior heuristic selection probability equivalents.
-This is a result of the information that is added in the performance log by tracking the entity and credit allocation as well.
-
-It can be concluded from Sections \ref{sec:results:case_study:performance_metrics} to \ref{sec:results:case_study:posterior_selec_prob} that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset.
-Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases, and thus the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-% BHH vs. Low-Level Heuristics
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsection{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
-
-This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics.
-Detailed discussions and illustrations follow.
-As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of \acp{MH}.
-Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a heuristic pool that contains only gradient-based heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a heuristics pool that contains only \acp{MH} (denoted bhh\_mh).
-
-Table \ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{sidewaystable}[htbp]
-	\centering
-	\caption{Empirical results showing test loss and statistics for different low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs, measured at the last epoch.}
-	\label{tab:results:standalone:metrics:loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|lll|l|l|l|l|l|lllll}
-			                                    & \multicolumn{13}{c}{\textbf{BHH vs.
-Low-Level Heuristics - Average Test Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
-			\cmidrule{2-14}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                           & \multicolumn{1}{c}{\textbf{adam}}                       & \multicolumn{1}{c|}{\textbf{rmsprop}}                   & \multicolumn{1}{c|}{\textbf{bhh\_gd}}                   & \multicolumn{1}{c|}{\textbf{nag}}                       & \multicolumn{1}{c|}{\textbf{bhh\_all}}                  & \multicolumn{1}{c|}{\textbf{adadelta}}                  & \multicolumn{1}{c|}{\textbf{bhh\_mh}}                   & \multicolumn{1}{c}{\textbf{ga}}                         & \multicolumn{1}{c}{\textbf{pso}}                        & \multicolumn{1}{c}{\textbf{sgd}}                        & \multicolumn{1}{c}{\textbf{momentum}}                   & \multicolumn{1}{c}{\textbf{de}}                         \\
-			\midrule
-			\textbf{abalone}                    & \cellcolor[rgb]{ .506,  .776,  .486}1.9678 ($\pm$0.032)                        & \cellcolor[rgb]{ .494,  .773,  .486}1.9651 ($\pm$0.035) & \cellcolor[rgb]{ .388,  .745,  .482}1.9455 ($\pm$0.035) & \cellcolor[rgb]{ .749,  .847,  .502}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .765,  .851,  .502}2.0156 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .788,  .859,  .502}2.0199 ($\pm$0.034) & \cellcolor[rgb]{ .996,  .827,  .502}2.2942 ($\pm$0.055) & \cellcolor[rgb]{ .984,  .612,  .459}2.8155 ($\pm$0.055) & \cellcolor[rgb]{ .98,  .522,  .443}3.0384 ($\pm$0.294)  & \cellcolor[rgb]{ .992,  .773,  .49}2.428 ($\pm$0.029)   & \cellcolor[rgb]{ .992,  .745,  .486}2.4942 ($\pm$0.029) & \cellcolor[rgb]{ .973,  .412,  .42}3.2959 ($\pm$0.016)  \\
-			\textbf{air quality}                & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                         & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\
-			\textbf{bank}                       & \cellcolor[rgb]{ .459,  .765,  .486}0.2096 ($\pm$0.005)                        & \cellcolor[rgb]{ .4,  .745,  .482}0.2065 ($\pm$0.004)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2058 ($\pm$0.006) & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.005)    & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .886,  .514}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .627,  .812,  .494}0.2186 ($\pm$0.004) & \cellcolor[rgb]{ .996,  .839,  .502}0.2562 ($\pm$0.011) & \cellcolor[rgb]{ .988,  .686,  .475}0.2881 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.3454 ($\pm$0.034)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2382 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2386 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .424,  .424}0.3437 ($\pm$0.028) \\
-			\textbf{bike}                       & \cellcolor[rgb]{ .388,  .745,  .482}0.0458 ($\pm$0.002)                        & \cellcolor[rgb]{ .592,  .804,  .494}0.0682 ($\pm$0.068) & \cellcolor[rgb]{ 1,  .922,  .518}0.1123 ($\pm$0.103)    & \cellcolor[rgb]{ .467,  .765,  .486}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .882,  .886,  .51}0.0995 ($\pm$0.002)  & \cellcolor[rgb]{ .565,  .796,  .49}0.0651 ($\pm$0.02)   & \cellcolor[rgb]{ .588,  .8,  .49}0.0679 ($\pm$0.002)    & \cellcolor[rgb]{ 1,  .902,  .514}0.1179 ($\pm$0.006)    & \cellcolor[rgb]{ .992,  .761,  .486}0.1531 ($\pm$0.005) & \cellcolor[rgb]{ .992,  .773,  .49}0.1503 ($\pm$0.025)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1599 ($\pm$0.003) & \cellcolor[rgb]{ .992,  .725,  .482}0.1614 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.2399 ($\pm$0.04)   \\
-			\textbf{car}                        & \cellcolor[rgb]{ .729,  .843,  .502}0.2027 ($\pm$0.018)                        & \cellcolor[rgb]{ .388,  .745,  .482}0.0972 ($\pm$0.024) & \cellcolor[rgb]{ .408,  .749,  .482}0.1039 ($\pm$0.031) & \cellcolor[rgb]{ .62,  .812,  .494}0.169 ($\pm$0.025)   & \cellcolor[rgb]{ .867,  .882,  .51}0.2454 ($\pm$0.029)  & \cellcolor[rgb]{ .58,  .8,  .49}0.1572 ($\pm$0.034)     & \cellcolor[rgb]{ 1,  .922,  .518}0.2859 ($\pm$0.027)    & \cellcolor[rgb]{ .992,  .733,  .482}0.4891 ($\pm$0.077) & \cellcolor[rgb]{ .98,  .502,  .439}0.7374 ($\pm$0.063)  & \cellcolor[rgb]{ .988,  .667,  .471}0.5632 ($\pm$0.158) & \cellcolor[rgb]{ .98,  .533,  .443}0.7035 ($\pm$0.052)  & \cellcolor[rgb]{ .98,  .506,  .439}0.7322 ($\pm$0.043)  & \cellcolor[rgb]{ .973,  .412,  .42}0.8332 ($\pm$0.074)  \\
-			\textbf{diabetic}                   & \cellcolor[rgb]{ .694,  .831,  .498}0.8895 ($\pm$0.004)                        & \cellcolor[rgb]{ 1,  .898,  .514}0.9193 ($\pm$0.01)     & \cellcolor[rgb]{ .918,  .894,  .51}0.8957 ($\pm$0.004)  & \cellcolor[rgb]{ .98,  .914,  .514}0.8976 ($\pm$0.011)  & \cellcolor[rgb]{ .388,  .745,  .482}0.8809 ($\pm$0.004) & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)   & \cellcolor[rgb]{ .49,  .773,  .486}0.8839 ($\pm$0.005)  & \cellcolor[rgb]{ 1,  .902,  .518}0.9137 ($\pm$0.008)    & \cellcolor[rgb]{ .996,  .843,  .506}0.9613 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .835,  .502}0.9661 ($\pm$0.016) & \cellcolor[rgb]{ .976,  .914,  .514}0.8974 ($\pm$0.004) & \cellcolor[rgb]{ 1,  .922,  .518}0.898 ($\pm$0.003)     & \cellcolor[rgb]{ .988,  .694,  .475}1.0774 ($\pm$0.039) \\
-			\textbf{fish toxicity}              & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                           & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
-			\textbf{forest fires}               & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                            & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\
-			\textbf{housing}                    & \cellcolor[rgb]{ .518,  .78,  .486}0.0889 ($\pm$0.012)                         & \cellcolor[rgb]{ .404,  .749,  .482}0.0848 ($\pm$0.011) & \cellcolor[rgb]{ .388,  .745,  .482}0.0842 ($\pm$0.015) & \cellcolor[rgb]{ .69,  .831,  .498}0.0951 ($\pm$0.015)  & \cellcolor[rgb]{ .612,  .808,  .494}0.0923 ($\pm$0.016) & \cellcolor[rgb]{ .663,  .824,  .498}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.106 ($\pm$0.019)     & \cellcolor[rgb]{ 1,  .867,  .51}0.1169 ($\pm$0.019)     & \cellcolor[rgb]{ .996,  .812,  .498}0.1279 ($\pm$0.02)  & \cellcolor[rgb]{ .992,  .722,  .482}0.1452 ($\pm$0.03)  & \cellcolor[rgb]{ .984,  .576,  .455}0.1735 ($\pm$0.023) & \cellcolor[rgb]{ .984,  .588,  .455}0.1713 ($\pm$0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.2057 ($\pm$0.036)  \\
-			\textbf{iris}                       & \cellcolor[rgb]{ .788,  .859,  .502}0.2161 ($\pm$0.059)                        & \cellcolor[rgb]{ .514,  .78,  .486}0.1203 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0753 ($\pm$0.046) & \cellcolor[rgb]{ 1,  .855,  .506}0.3729 ($\pm$1.119)    & \cellcolor[rgb]{ .416,  .753,  .482}0.085 ($\pm$0.042)  & \cellcolor[rgb]{ .859,  .878,  .506}0.2411 ($\pm$0.295) & \cellcolor[rgb]{ .996,  .808,  .498}0.426 ($\pm$0.072)  & \cellcolor[rgb]{ .686,  .831,  .498}0.1809 ($\pm$0.164) & \cellcolor[rgb]{ 1,  .922,  .518}0.2895 ($\pm$0.117)    & \cellcolor[rgb]{ .973,  .412,  .42}0.8965 ($\pm$0.844)  & \cellcolor[rgb]{ .992,  .773,  .49}0.4694 ($\pm$0.088)  & \cellcolor[rgb]{ .992,  .745,  .486}0.5028 ($\pm$0.072) & \cellcolor[rgb]{ .98,  .494,  .435}0.8027 ($\pm$0.684)  \\
-			\textbf{mushroom}                   & \cellcolor[rgb]{ .549,  .792,  .49}0.0026 ($\pm$0.001)                         & \cellcolor[rgb]{ .467,  .765,  .486}0.0013 ($\pm$0.005) & \cellcolor[rgb]{ .388,  .745,  .482}0.0001 ($\pm$0)     & \cellcolor[rgb]{ .439,  .757,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ 1,  .922,  .518}0.0094 ($\pm$0.002)    & \cellcolor[rgb]{ .718,  .839,  .498}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ .655,  .82,  .494}0.0042 ($\pm$0.001)  & \cellcolor[rgb]{ 1,  .871,  .51}0.0774 ($\pm$0.02)      & \cellcolor[rgb]{ .984,  .561,  .451}0.4892 ($\pm$0.025) & \cellcolor[rgb]{ 1,  .886,  .514}0.0611 ($\pm$0.06)     & \cellcolor[rgb]{ .996,  .796,  .494}0.1797 ($\pm$0.009) & \cellcolor[rgb]{ .992,  .749,  .486}0.2418 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.687 ($\pm$0.016)   \\
-			\textbf{parkinsons}                 & \cellcolor[rgb]{ .51,  .776,  .486}0.0563 ($\pm$0.001)                         & \cellcolor[rgb]{ .412,  .749,  .482}0.0545 ($\pm$0.002) & \cellcolor[rgb]{ .388,  .745,  .482}0.054 ($\pm$0.002)  & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0655 ($\pm$0.002)    & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .69,  .831,  .498}0.0597 ($\pm$0.002)  & \cellcolor[rgb]{ 1,  .918,  .518}0.0658 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .898,  .514}0.0669 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .894,  .514}0.0671 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .467,  .431}0.0923 ($\pm$0.008) & \cellcolor[rgb]{ .973,  .412,  .42}0.0954 ($\pm$0.009)  & \cellcolor[rgb]{ .984,  .604,  .459}0.0843 ($\pm$0.009) \\
-			\textbf{student performance}        & \cellcolor[rgb]{ .388,  .745,  .482}0.1656 ($\pm$0.011)                        & \cellcolor[rgb]{ .98,  .522,  .443}0.4929 ($\pm$0.105)  & \cellcolor[rgb]{ .973,  .412,  .42}0.5724 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .855,  .506}0.2454 ($\pm$0.134)    & \cellcolor[rgb]{ .471,  .769,  .486}0.1697 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .871,  .51}0.2359 ($\pm$0.102)     & \cellcolor[rgb]{ .49,  .773,  .486}0.1708 ($\pm$0.01)   & \cellcolor[rgb]{ .969,  .91,  .514}0.1947 ($\pm$0.014)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1962 ($\pm$0.01)     & \cellcolor[rgb]{ .984,  .573,  .451}0.4565 ($\pm$0.049) & \cellcolor[rgb]{ .933,  .902,  .514}0.193 ($\pm$0.011)  & \cellcolor[rgb]{ .925,  .898,  .51}0.1925 ($\pm$0.011)  & \cellcolor[rgb]{ 1,  .918,  .518}0.2014 ($\pm$0.012)    \\
-			\textbf{wine quality}               & \cellcolor[rgb]{ .631,  .816,  .494}1.0651 ($\pm$0.024)                        & \cellcolor[rgb]{ .388,  .745,  .482}1.0395 ($\pm$0.018) & \cellcolor[rgb]{ .502,  .776,  .486}1.0514 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .698,  .831,  .498}1.0718 ($\pm$0.025) & \cellcolor[rgb]{ .804,  .863,  .506}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .788,  .859,  .502}1.0809 ($\pm$0.021) & \cellcolor[rgb]{ .996,  .839,  .502}1.1666 ($\pm$0.03)  & \cellcolor[rgb]{ .992,  .725,  .482}1.2516 ($\pm$0.046) & \cellcolor[rgb]{ .988,  .659,  .467}1.3046 ($\pm$0.114) & \cellcolor[rgb]{ .996,  .843,  .502}1.1648 ($\pm$0.023) & \cellcolor[rgb]{ .996,  .824,  .502}1.1774 ($\pm$0.019) & \cellcolor[rgb]{ .973,  .412,  .42}1.4896 ($\pm$0.093)  \\
-			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
-	}
-\end{sidewaystable}%
-
-Table \ref{tab:results:standalone:metrics:loss} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
-The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the heuristics.
-
-Table \ref{tab:results:standalone:metrics:rank} provides the empirical results from Table \ref{tab:results:standalone:metrics:loss} in ranked format.
-The performance rank is calculated as the average rank produced by each heuristic, across all datasets, for all independent runs and all epochs.
-The average rank across all epochs produces a view on the performance of the heuristics as it relates to the entire training process.
-Finally, a normalised average rank is provided for the overall performance of all heuristics at the bottom of the table.
-The normalised average rank is calculated as a discrete normalisation of the average rank achieved across all datasets, for all independent runs and epochs.
+\section{Results: BHH vs. Low Level Heuristics - Average Test Rank}
+\label{app:appendix_results_bhh_vs_heuristics_rank}
 
@@
 \end{sidewaystable}%
-
-From the normalised average ranks provided in Table \ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen heuristic implementations respectively.
-These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.
-
-Figure \ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each heuristic, per dataset.
-The heuristics are ordered according to the normalised ranks presented in Table \ref{tab:results:standalone:metrics:rank}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all independent runs and epochs.}
-	\label{fig:results:standalone:descriptive:descriptive}
-\end{figure}
-
-From Figure \ref{fig:results:standalone:descriptive:descriptive} a few observations can be made.
-Firstly, both \acs{Adam} and \acs{RMSProp} achieved radically different average ranks for the student performance dataset, compared to the other datasets.
-This can also be seen in Table \ref{tab:results:standalone:metrics:rank}.
-Further investigation into the reasons for this is required as both these heuristics perform well on all other datasets, and the other heuristics perform well for the student performance dataset.
-A suggestion is that an invalid learning rate or learning rate schedule leads to a scenario where good solutions are overshot, causing \acs{Adam} and \acs{RMSProp} to struggle to resolve back to good solutions.
-Furthermore, the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
-The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.
-
-Figure \ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each heuristic as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
-	\label{fig:results:standalone:descriptive:cd}
-\end{figure}
-
-Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all heuristics is very small.
-Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, is statistically only outperformed overall by \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}.
-It should be noted that the standalone low-level  heuristics already produce good results in general across all datasets.
-In this particular case, producing better performance outcomes can be hard to achieve.
-However, as mentioned previously, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.
-
-Another observation that can be made is that the gradient-based heuristics generally performed much better than the \acp{MH} on all datasets.
-State of the art methods for training \acp{FFNN}, such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions \cite{ref:kingma:2014}.
-Exploration of the heuristic space leads the \acs{BHH} to consider other heuristics during the training process, which could possibly result in worse performances at times.
-As previously mentioned, a suggestion to improve on these results is to include a move-acceptance strategy, where heuristic progressions are discarded if they fail to produce better results.
-
-Figures \ref{fig:results:standalone:figures:iris} to \ref{fig:results:standalone:figures:bank} provide example illustrations of the train and test loss and accuracy plots for each heuristic as it relates to a selection of classification datasets.
-The train and test loss and accuracy plots provided are illustrated in log scale.
-The other classification datasets are left out for brevity as they produce similar illustrations.
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/iris.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:iris}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/iris.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:iris}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/iris.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:iris}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/iris.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:iris}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:iris}
-\end{figure}
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the car dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:car}
-\end{figure}
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/bank.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/bank.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/bank.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/bank.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:bank}
-\end{figure}
-
-Figures \ref{fig:results:standalone:figures:fish_toxicity} to \ref{fig:results:standalone:figures:parkinsons} provide example illustrations of the train and test loss plots for each heuristic as it relates to a selection of regression datasets.
-The train and test loss plots provided are illustrated in log scale.
-Similar to before, the other regression datasets are left out for brevity as they produce similar illustrations.
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/fish_toxicity.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:fish_toxicity}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/fish_toxicity.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:fish_toxicity}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:fish_toxicity}
-\end{figure}
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/parkinsons.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:parkinsons}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/parkinsons.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:parkinsons}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:parkinsons}
-\end{figure}

### 2023-02-04 article/appendices/j-results-bhh-vs-heuristics-metrics.tex
🚧 (article): WIP save point for revision

--- 2023-02-01 article/sections/08-results.tex
@@
-\section{Results}
-\label{sec:results}
-
-This section provides the results of all the experiments that have been conducted.
-Detailed discussions follow on the outcomes of each experiment.
-Discussions are accompanied by figures and plots to help provide visual aid for discussions.
-The output of the statistical analysis that yielded the results is provided in Appendix \ref{app:statistical_analysis}.
-
-\subsection{Overview}\label{sec:results:overview}
-
-This section provides a brief discussion on the general outcome of the empirical process as a whole.
-Overall, the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets.
-In general, the \acs{BHH} performs well and the empirical process provides key insights into the workings of the \acs{BHH}.
-Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.
-
-Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results.
-The \acs{BHH} applies a form of online learning.
-As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process.
-The training process is not repeated iteratively.
-All experiments conducted are executed for 30 epochs.
-The number of training steps executed is dependent on the batch size applied for each dataset.
-
-All of the underlying \acp{FFNN} trained in the empirical process are relatively small.
-As such, most of the training progress is observed to occur within the first five epochs.
-As a result, the \acs{BHH} should apply most learning at the early stages of the training process.
-After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point.
-Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the heuristic space beyond the five epoch mark.
-
-The \acs{BHH} does not implement a move-acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution.
-In some cases the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.
-
-Given the stochastic nature of the heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn.
-This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}.
-The probabilistic model implements \textit{probability distributions of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.
-
-The \textit{reanalysis interval} defines intervals at which the \acs{BHH} reanalyses the performance log, in effect, resetting the concentration parameters to their default values and reapplying the underlying Bayesian analysis process on the performance log.
-Furthermore, the \textit{replay window size} defines the amount of performance evidence in the performance log.
-By default, the \acs{BHH} baseline configuration has a reanalysis interval of 10, and a replay window size of 10, which is a small window to learn from.
-Despite the small reanalysis interval and the small replay window size, it should be observed that the \acs{BHH} exploits small performance biases regardless and does find small performance gains throughout.
-
-\subsection{Behavioural Case Study}\label{sec:results:case_study}
-
-This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset.
-As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records.
-The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process.
-Mini-batch training is executed with a batch size of 30.
-The results that are presented are averaged over 30 independent runs.
-
-The case study focuses on three variants of the \acs{BHH}.
-These include the baseline configuration, as was provided in Section \ref{sec:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}).
-Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}).
-Finally, the case study includes a configuration that makes use of the \textit{symmetric} credit assignment strategy hyper-parameter, and is denoted as bhh\_credit\_symmetric (illustrated throughout in \textcolor{blue}{blue}).
-
-These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level heuristics in the heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards heuristics that perform well at all.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% METRICS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Performance Metrics}\label{sec:results:case_study:performance_metrics}
-
-This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}.
-Figures \ref{fig:results:case_study:metrics:train_loss} to \ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
-		\caption{Train log loss}
-		\label{fig:results:case_study:metrics:train_loss}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
-		\caption{Test log loss}
-		\label{fig:results:case_study:metrics:test_loss}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:case_study:metrics:train_accuracy}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:case_study:metrics:test_accuracy}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average train and test loss and accuracy plots over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:metrics}
-\end{figure}
-
-The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}, observed by the convergence of the training process, yielding good results.
-Figures \ref{fig:results:case_study:metrics:train_accuracy} and \ref{fig:results:case_study:metrics:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%.
-
-Although the different configurations of the \acs{BHH} are all able to successfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.
-
-The volatility and minor divergence of the test loss compared to the training loss, observed in Figure \ref{fig:results:case_study:metrics:test_loss}, is due to overfitting and partly due to the noisiness that results from mini-batch training.
-Early stopping can be applied to the training process to halt training before the model overfits on the training data.
-The training dataset is also very small, with just 120 samples.
-Furthermore, a very small batch size of 16 is used.
-As such, noisiness and overfitting can be expected.
-
-From Figure \ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed.
-This could simply be a result of momentum that is maintained when switching between low-level heuristics in an attempt to find better solutions.
-For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions.
-The \acs{BHH} does not incorporate a \textit{move-acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set.
-A move-acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.
-
-Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figure \ref{fig:results:case_study:metrics} only provides the outcomes of performance metrics at the end of each epoch.
-Further investigation is required at a mini-batch step level and is provided in the following sections.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS ALPHAS
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}
-
-To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
-Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
-The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{heuristic selection probabilities}.
-Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
-Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the heuristic pool.
-Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
-		\caption{$\alpha_{0}$ - \acs{SGD}}
-		\label{fig:results:case_study:alphas:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
-		\caption{$\alpha_{6}$ - \acs{Adam}}
-		\label{fig:results:case_study:alphas:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
-		\caption{$\alpha_{7}$ - \acs{PSO}}
-		\label{fig:results:case_study:alphas:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
-		\caption{$\alpha_{8}$ - \acs{GA}}
-		\label{fig:results:case_study:alphas:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:alphas}
-\end{figure}
-
-The first logical observation to be made from Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
-Since the replay window size is sufficiently large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
-The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process.
-However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$.
-The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}.
-Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly than other heuristics that do not perform well.
-
-The next observations that can be made are for the bhh\_baseline configuration, illustrated in \textcolor{red}{red}, and the bhh\_credit\_symmetric configuration in \textcolor{blue}{blue}.
-Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1.0 as regular intervals.
-This interval is defined by the \textit{reanalysis interval} hyper-parameter.
-The reanalysis interval dictates the frequency at which Bayesian analysis is conducted on the performance log, maintained by the \acs{BHH}.
-Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval.
-As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.
-
-Notice from Figure \ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements.
-This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process.
-Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process.
-
-Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning.
-The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
-Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequently reselect these heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
-Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS THETAS
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Probability Distribution of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
-
-This section provides a detailed investigation into the \textit{probability distribution of heuristic selection probabilities} as it changes throughout the training process.
-As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modelling and thus, heuristic selection probabilities are defined by an underlying probabilistic distribution themselves.
-The probability distribution of heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.
-
-Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
-These illustrations are presented in log scale.
-Indices 0, 6, 7, and 8 represent the distribution of heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of heuristic selection probabilities in $\boldsymbol{\theta}$.
-Similar illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
-		\caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
-		\label{fig:results:case_study:thetas:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
-		\caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
-		\label{fig:results:case_study:thetas:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
-		\caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
-		\label{fig:results:case_study:thetas:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
-		\caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
-		\label{fig:results:case_study:thetas:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average sampled heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
-The heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:thetas}
-\end{figure}
-
-From the illustrations presented in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed.
-The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}.
-As a reminder, ten low-level heuristics are included in the heuristic pool, yielding an expected mean heuristics selection probability of 0.1, for each heuristic, by the frequentist view of probabilistic modelling.
-
-Towards the end of the training process, the heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a heuristic selection probability of 0.1, for all heuristics.
-This can be explained as follows: most of the training progress is made in the early stages of the training process, and training converges towards the end of the training process.
-Since training converges, all heuristics, no matter their past performances, fail to yield better solutions towards the end of the training process.
-As a result of training convergence, heuristics then fail to meet the performance criteria and credit allocations by means of the credit assignment strategy.
-
-Both the bhh\_baseline (\textcolor{red}{red}) and the bhh\_replay\_250 (\textcolor{green}{green}) configurations make use of the \textit{ibest} credit assignment strategy.
-The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yields the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
-However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ is reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.
-
-Another observation to make occurs in the first 30 steps of the training process.
-In Figure \ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same heuristic selection probabilities in these first 30 steps.
-This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number.
-This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches.
-This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.
-
-It should be noted that, despite using the same random seed across configurations for the same run number, the behavioural changes between the configurations start to show after about 30 steps.
-As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing heuristics.
-Where the bhh\_baseline and bhh\_replay\_250 configurations then diverge from the behaviour of the bhh\_credit\_symmetric configuration is proof of the effect of performance bias.
-
-Furthermore, it can be observed for small windows, at various steps for multiple runs, that the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, do not yield means that are equal to the expected heuristic selection probabilities of 0.1.
-This is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations.
-This is also true for the bhh\_credit\_symmetric configuration, as the bhh\_credit\_symmetric configuration biases towards heuristics that happen to be sampled, despite not biasing towards good performance.
-
-Finally, the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration both yield similar volatile behaviour, much more so than with the bhh\_replay\_250 configuration.
-This can be attributed to a very small reanalysis window combined with a small replay window size of 10, that contains very few samples to learn from.
-A small reanalysis interval and a small replay window size allows for more exploration of the heuristic space, but can also yield greater variance of the heuristic selection probabilities.
-Once again, any differences then in the behaviour of the bhh\_baseline compared to the bhh\_credit\_symmetric configurations is proof of small performance exploitations and biases by the bhh\_baseline configuration.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS P_H (Priors)
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Prior Heuristic Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}
-
-This section provides a brief investigation into the \textit{prior heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}.
-The prior heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
-As such, $P(\boldsymbol{H} \vert \boldsymbol{\theta}) = \boldsymbol{\theta}$ and heuristics are initially sampled such that $\boldsymbol{H} \sim Cat(\boldsymbol{\theta})$.
-
-Figures \ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
-Similar to before, these illustrations are also presented in log scale.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
-		\caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
-		\label{fig:results:case_study:p_H:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
-		\caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
-		\label{fig:results:case_study:p_H:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
-		\caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
-		\label{fig:results:case_study:p_H:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
-		\caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
-		\label{fig:results:case_study:p_H:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average prior heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8.
-The prior heuristic selection probabilities are sampled from the probability distribution of heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_H}
-\end{figure}
-
-The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure \ref{fig:results:case_study:thetas}.
-This is because of the \textit{reselection} interval hyper-parameter.
-The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity.
-Since the default \textit{reselection} interval is set to 10, the heuristic selection probabilities are only resampled at intervals of 10.
-These illustrations then simply yield rough approximations of the illustrations provided in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of heuristic selection probabilities.
-As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
-
-Finally, it should be mentioned that at each step, the goal of the \acs{BHH} is to update these prior ``beliefs'' based on newly observed evidence of heuristic performances.
-Since these prior heuristic selection probabilities change over time, it can be concluded that the change in prior heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}.
-Furthermore, the prior heuristic selection probability distribution provides an opportunity to utilise prior knowledge by some expert before training starts, by injecting heuristic selection biases, by means of the initial values for the concentration parameter $\boldsymbol{\alpha}$.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS P_HgEC (Posterior)
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Posterior Heuristic Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}
-
-This section provides a detailed discussion on the outcomes of the \textit{posterior heuristic selection probabilities}.
-These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}.
-The posterior heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy.
-Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of heuristic selection probabilities and the entity selection probabilities respectively.
-Finally, $\boldsymbol{\psi}$ represents the probability distribution of successful credit allocation probabilities.
-
-Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
-Similar to before, these illustrations are also presented in log scale.
-As before, illustrations for the other indices are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
-		\caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
-		\label{fig:results:case_study:p_HgEC:0:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
-		\caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
-		\label{fig:results:case_study:p_HgEC:0:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
-		\caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
-		\label{fig:results:case_study:p_HgEC:0:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
-		\caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
-		\label{fig:results:case_study:p_HgEC:0:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average calculated proportional posterior heuristic selection probabilities for heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, $c_{1}$, from the \textit{ibest} credit assignment strategy.
-The proportional posterior heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_HgEC:0}
-\end{figure}
-
-The main observation to make from Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a Categorical probability distribution from which new heuristic selections are sampled.
-The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Section \ref{sec:bhh}.
-As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
-
-Another observation to make is for the bhh\_replay\_250 configuration $(\textcolor{green}{green})$.
-Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} show that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities later in the training stages.
-The aforementioned suggests that the \acs{BHH} is not able to find further performance biases and cannot exploit better solutions.
-At this point, the \acs{BHH} starts to explore more as the concentration parameters are reanalysed more uniformly, resolving more and more to a random search in attempt to find better solutions.
-
-Furthermore, the posterior heuristic selection probability distribution is conditional on the occurrence of a specific entity that the potential heuristic will be applied to, as well as a specific performance criterion enforced by a specific credit assignment strategy.
-This means that heuristic selection is specific to each entity.
-A particular heuristic might be good for one entity, but not for another.
-This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct heuristic to the correct entity at the correct time in the training process.
-
-Finally, the posterior heuristic selection probabilities are much less volatile than their prior heuristic selection probability equivalents.
-This is a result of the information that is added in the performance log by tracking the entity and credit allocation as well.
-
-It can be concluded from Sections \ref{sec:results:case_study:performance_metrics} to \ref{sec:results:case_study:posterior_selec_prob} that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset.
-Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases, and thus the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-% BHH vs. Low-Level Heuristics
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
-\subsection{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
-
-This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics.
-Detailed discussions and illustrations follow.
-As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of \acp{MH}.
-Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a heuristic pool that contains only gradient-based heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a heuristics pool that contains only \acp{MH} (denoted bhh\_mh).
-
-Table \ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-\begin{sidewaystable}[htbp]
-	\centering
-	\caption{Empirical results showing test loss and statistics for different low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs, measured at the last epoch.}
-	\label{tab:results:standalone:metrics:loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|lll|l|l|l|l|l|lllll}
-			                                    & \multicolumn{13}{c}{\textbf{BHH vs.
-Low-Level Heuristics - Average Test Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
-			\cmidrule{2-14}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                           & \multicolumn{1}{c}{\textbf{adam}}                       & \multicolumn{1}{c|}{\textbf{rmsprop}}                   & \multicolumn{1}{c|}{\textbf{bhh\_gd}}                   & \multicolumn{1}{c|}{\textbf{nag}}                       & \multicolumn{1}{c|}{\textbf{bhh\_all}}                  & \multicolumn{1}{c|}{\textbf{adadelta}}                  & \multicolumn{1}{c|}{\textbf{bhh\_mh}}                   & \multicolumn{1}{c}{\textbf{ga}}                         & \multicolumn{1}{c}{\textbf{pso}}                        & \multicolumn{1}{c}{\textbf{sgd}}                        & \multicolumn{1}{c}{\textbf{momentum}}                   & \multicolumn{1}{c}{\textbf{de}}                         \\
-			\midrule
-			\textbf{abalone}                    & \cellcolor[rgb]{ .506,  .776,  .486}1.9678 ($\pm$0.032)                        & \cellcolor[rgb]{ .494,  .773,  .486}1.9651 ($\pm$0.035) & \cellcolor[rgb]{ .388,  .745,  .482}1.9455 ($\pm$0.035) & \cellcolor[rgb]{ .749,  .847,  .502}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .765,  .851,  .502}2.0156 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .788,  .859,  .502}2.0199 ($\pm$0.034) & \cellcolor[rgb]{ .996,  .827,  .502}2.2942 ($\pm$0.055) & \cellcolor[rgb]{ .984,  .612,  .459}2.8155 ($\pm$0.055) & \cellcolor[rgb]{ .98,  .522,  .443}3.0384 ($\pm$0.294)  & \cellcolor[rgb]{ .992,  .773,  .49}2.428 ($\pm$0.029)   & \cellcolor[rgb]{ .992,  .745,  .486}2.4942 ($\pm$0.029) & \cellcolor[rgb]{ .973,  .412,  .42}3.2959 ($\pm$0.016)  \\
-			\textbf{air quality}                & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                         & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\
-			\textbf{bank}                       & \cellcolor[rgb]{ .459,  .765,  .486}0.2096 ($\pm$0.005)                        & \cellcolor[rgb]{ .4,  .745,  .482}0.2065 ($\pm$0.004)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2058 ($\pm$0.006) & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.005)    & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .886,  .514}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .627,  .812,  .494}0.2186 ($\pm$0.004) & \cellcolor[rgb]{ .996,  .839,  .502}0.2562 ($\pm$0.011) & \cellcolor[rgb]{ .988,  .686,  .475}0.2881 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.3454 ($\pm$0.034)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2382 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2386 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .424,  .424}0.3437 ($\pm$0.028) \\
-			\textbf{bike}                       & \cellcolor[rgb]{ .388,  .745,  .482}0.0458 ($\pm$0.002)                        & \cellcolor[rgb]{ .592,  .804,  .494}0.0682 ($\pm$0.068) & \cellcolor[rgb]{ 1,  .922,  .518}0.1123 ($\pm$0.103)    & \cellcolor[rgb]{ .467,  .765,  .486}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .882,  .886,  .51}0.0995 ($\pm$0.002)  & \cellcolor[rgb]{ .565,  .796,  .49}0.0651 ($\pm$0.02)   & \cellcolor[rgb]{ .588,  .8,  .49}0.0679 ($\pm$0.002)    & \cellcolor[rgb]{ 1,  .902,  .514}0.1179 ($\pm$0.006)    & \cellcolor[rgb]{ .992,  .761,  .486}0.1531 ($\pm$0.005) & \cellcolor[rgb]{ .992,  .773,  .49}0.1503 ($\pm$0.025)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1599 ($\pm$0.003) & \cellcolor[rgb]{ .992,  .725,  .482}0.1614 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.2399 ($\pm$0.04)   \\
-			\textbf{car}                        & \cellcolor[rgb]{ .729,  .843,  .502}0.2027 ($\pm$0.018)                        & \cellcolor[rgb]{ .388,  .745,  .482}0.0972 ($\pm$0.024) & \cellcolor[rgb]{ .408,  .749,  .482}0.1039 ($\pm$0.031) & \cellcolor[rgb]{ .62,  .812,  .494}0.169 ($\pm$0.025)   & \cellcolor[rgb]{ .867,  .882,  .51}0.2454 ($\pm$0.029)  & \cellcolor[rgb]{ .58,  .8,  .49}0.1572 ($\pm$0.034)     & \cellcolor[rgb]{ 1,  .922,  .518}0.2859 ($\pm$0.027)    & \cellcolor[rgb]{ .992,  .733,  .482}0.4891 ($\pm$0.077) & \cellcolor[rgb]{ .98,  .502,  .439}0.7374 ($\pm$0.063)  & \cellcolor[rgb]{ .988,  .667,  .471}0.5632 ($\pm$0.158) & \cellcolor[rgb]{ .98,  .533,  .443}0.7035 ($\pm$0.052)  & \cellcolor[rgb]{ .98,  .506,  .439}0.7322 ($\pm$0.043)  & \cellcolor[rgb]{ .973,  .412,  .42}0.8332 ($\pm$0.074)  \\
-			\textbf{diabetic}                   & \cellcolor[rgb]{ .694,  .831,  .498}0.8895 ($\pm$0.004)                        & \cellcolor[rgb]{ 1,  .898,  .514}0.9193 ($\pm$0.01)     & \cellcolor[rgb]{ .918,  .894,  .51}0.8957 ($\pm$0.004)  & \cellcolor[rgb]{ .98,  .914,  .514}0.8976 ($\pm$0.011)  & \cellcolor[rgb]{ .388,  .745,  .482}0.8809 ($\pm$0.004) & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)   & \cellcolor[rgb]{ .49,  .773,  .486}0.8839 ($\pm$0.005)  & \cellcolor[rgb]{ 1,  .902,  .518}0.9137 ($\pm$0.008)    & \cellcolor[rgb]{ .996,  .843,  .506}0.9613 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .835,  .502}0.9661 ($\pm$0.016) & \cellcolor[rgb]{ .976,  .914,  .514}0.8974 ($\pm$0.004) & \cellcolor[rgb]{ 1,  .922,  .518}0.898 ($\pm$0.003)     & \cellcolor[rgb]{ .988,  .694,  .475}1.0774 ($\pm$0.039) \\
-			\textbf{fish toxicity}              & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                           & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
-			\textbf{forest fires}               & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                            & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\
-			\textbf{housing}                    & \cellcolor[rgb]{ .518,  .78,  .486}0.0889 ($\pm$0.012)                         & \cellcolor[rgb]{ .404,  .749,  .482}0.0848 ($\pm$0.011) & \cellcolor[rgb]{ .388,  .745,  .482}0.0842 ($\pm$0.015) & \cellcolor[rgb]{ .69,  .831,  .498}0.0951 ($\pm$0.015)  & \cellcolor[rgb]{ .612,  .808,  .494}0.0923 ($\pm$0.016) & \cellcolor[rgb]{ .663,  .824,  .498}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.106 ($\pm$0.019)     & \cellcolor[rgb]{ 1,  .867,  .51}0.1169 ($\pm$0.019)     & \cellcolor[rgb]{ .996,  .812,  .498}0.1279 ($\pm$0.02)  & \cellcolor[rgb]{ .992,  .722,  .482}0.1452 ($\pm$0.03)  & \cellcolor[rgb]{ .984,  .576,  .455}0.1735 ($\pm$0.023) & \cellcolor[rgb]{ .984,  .588,  .455}0.1713 ($\pm$0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.2057 ($\pm$0.036)  \\
-			\textbf{iris}                       & \cellcolor[rgb]{ .788,  .859,  .502}0.2161 ($\pm$0.059)                        & \cellcolor[rgb]{ .514,  .78,  .486}0.1203 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0753 ($\pm$0.046) & \cellcolor[rgb]{ 1,  .855,  .506}0.3729 ($\pm$1.119)    & \cellcolor[rgb]{ .416,  .753,  .482}0.085 ($\pm$0.042)  & \cellcolor[rgb]{ .859,  .878,  .506}0.2411 ($\pm$0.295) & \cellcolor[rgb]{ .996,  .808,  .498}0.426 ($\pm$0.072)  & \cellcolor[rgb]{ .686,  .831,  .498}0.1809 ($\pm$0.164) & \cellcolor[rgb]{ 1,  .922,  .518}0.2895 ($\pm$0.117)    & \cellcolor[rgb]{ .973,  .412,  .42}0.8965 ($\pm$0.844)  & \cellcolor[rgb]{ .992,  .773,  .49}0.4694 ($\pm$0.088)  & \cellcolor[rgb]{ .992,  .745,  .486}0.5028 ($\pm$0.072) & \cellcolor[rgb]{ .98,  .494,  .435}0.8027 ($\pm$0.684)  \\
-			\textbf{mushroom}                   & \cellcolor[rgb]{ .549,  .792,  .49}0.0026 ($\pm$0.001)                         & \cellcolor[rgb]{ .467,  .765,  .486}0.0013 ($\pm$0.005) & \cellcolor[rgb]{ .388,  .745,  .482}0.0001 ($\pm$0)     & \cellcolor[rgb]{ .439,  .757,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ 1,  .922,  .518}0.0094 ($\pm$0.002)    & \cellcolor[rgb]{ .718,  .839,  .498}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ .655,  .82,  .494}0.0042 ($\pm$0.001)  & \cellcolor[rgb]{ 1,  .871,  .51}0.0774 ($\pm$0.02)      & \cellcolor[rgb]{ .984,  .561,  .451}0.4892 ($\pm$0.025) & \cellcolor[rgb]{ 1,  .886,  .514}0.0611 ($\pm$0.06)     & \cellcolor[rgb]{ .996,  .796,  .494}0.1797 ($\pm$0.009) & \cellcolor[rgb]{ .992,  .749,  .486}0.2418 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.687 ($\pm$0.016)   \\
-			\textbf{parkinsons}                 & \cellcolor[rgb]{ .51,  .776,  .486}0.0563 ($\pm$0.001)                         & \cellcolor[rgb]{ .412,  .749,  .482}0.0545 ($\pm$0.002) & \cellcolor[rgb]{ .388,  .745,  .482}0.054 ($\pm$0.002)  & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0655 ($\pm$0.002)    & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .69,  .831,  .498}0.0597 ($\pm$0.002)  & \cellcolor[rgb]{ 1,  .918,  .518}0.0658 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .898,  .514}0.0669 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .894,  .514}0.0671 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .467,  .431}0.0923 ($\pm$0.008) & \cellcolor[rgb]{ .973,  .412,  .42}0.0954 ($\pm$0.009)  & \cellcolor[rgb]{ .984,  .604,  .459}0.0843 ($\pm$0.009) \\
-			\textbf{student performance}        & \cellcolor[rgb]{ .388,  .745,  .482}0.1656 ($\pm$0.011)                        & \cellcolor[rgb]{ .98,  .522,  .443}0.4929 ($\pm$0.105)  & \cellcolor[rgb]{ .973,  .412,  .42}0.5724 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .855,  .506}0.2454 ($\pm$0.134)    & \cellcolor[rgb]{ .471,  .769,  .486}0.1697 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .871,  .51}0.2359 ($\pm$0.102)     & \cellcolor[rgb]{ .49,  .773,  .486}0.1708 ($\pm$0.01)   & \cellcolor[rgb]{ .969,  .91,  .514}0.1947 ($\pm$0.014)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1962 ($\pm$0.01)     & \cellcolor[rgb]{ .984,  .573,  .451}0.4565 ($\pm$0.049) & \cellcolor[rgb]{ .933,  .902,  .514}0.193 ($\pm$0.011)  & \cellcolor[rgb]{ .925,  .898,  .51}0.1925 ($\pm$0.011)  & \cellcolor[rgb]{ 1,  .918,  .518}0.2014 ($\pm$0.012)    \\
-			\textbf{wine quality}               & \cellcolor[rgb]{ .631,  .816,  .494}1.0651 ($\pm$0.024)                        & \cellcolor[rgb]{ .388,  .745,  .482}1.0395 ($\pm$0.018) & \cellcolor[rgb]{ .502,  .776,  .486}1.0514 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .698,  .831,  .498}1.0718 ($\pm$0.025) & \cellcolor[rgb]{ .804,  .863,  .506}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .788,  .859,  .502}1.0809 ($\pm$0.021) & \cellcolor[rgb]{ .996,  .839,  .502}1.1666 ($\pm$0.03)  & \cellcolor[rgb]{ .992,  .725,  .482}1.2516 ($\pm$0.046) & \cellcolor[rgb]{ .988,  .659,  .467}1.3046 ($\pm$0.114) & \cellcolor[rgb]{ .996,  .843,  .502}1.1648 ($\pm$0.023) & \cellcolor[rgb]{ .996,  .824,  .502}1.1774 ($\pm$0.019) & \cellcolor[rgb]{ .973,  .412,  .42}1.4896 ($\pm$0.093)  \\
-			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
-	}
-\end{sidewaystable}%
-
-Table \ref{tab:results:standalone:metrics:loss} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
-The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the heuristics.
-
-Table \ref{tab:results:standalone:metrics:rank} provides the empirical results from Table \ref{tab:results:standalone:metrics:loss} in ranked format.
-The performance rank is calculated as the average rank produced by each heuristic, across all datasets, for all independent runs and all epochs.
-The average rank across all epochs produces a view on the performance of the heuristics as it relates to the entire training process.
-Finally, a normalised average rank is provided for the overall performance of all heuristics at the bottom of the table.
-The normalised average rank is calculated as a discrete normalisation of the average rank achieved across all datasets, for all independent runs and epochs.
-
-\begin{sidewaystable}[htbp]
-	\centering
-	\caption{Empirical results showing normalised average rank and statistics for different low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:standalone:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccc|c|c|c|c|c|ccccc}
-			                             & \multicolumn{13}{c}{\textbf{BHH vs.
-Low-Level Heuristics - Average Rank (Based on Test Loss)}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\
-			\textbf{dataset}             & \textbf{adagrad}                                                                               & \textbf{adam}                                           & \textbf{rmsprop}                                        & \textbf{bhh\_gd}                                        & \textbf{nag}                                            & \textbf{bhh\_all}                                       & \textbf{adadelta}                                       & \textbf{bhh\_mh}                                        & \textbf{ga}                                              & \textbf{pso}                                             & \textbf{sgd}                                             & \textbf{momentum}                                        & \textbf{de}                                              \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.2215 ($\pm$1.591)                                        & \cellcolor[rgb]{ .416,  .753,  .482}2.3989 ($\pm$1.887) & \cellcolor[rgb]{ .78,  .859,  .502}4.6172 ($\pm$2.65)   & \cellcolor[rgb]{ .796,  .863,  .506}4.7032 ($\pm$2.108) & \cellcolor[rgb]{ .725,  .839,  .498}4.2731 ($\pm$1.542) & \cellcolor[rgb]{ 1,  .922,  .518}5.9376 ($\pm$2.399)    & \cellcolor[rgb]{ .894,  .89,  .51}5.3129 ($\pm$1.478)   & \cellcolor[rgb]{ .992,  .749,  .486}8.1882 ($\pm$1.195) & \cellcolor[rgb]{ .98,  .525,  .443}11.1108 ($\pm$1.102)  & \cellcolor[rgb]{ .98,  .514,  .439}11.2559 ($\pm$1.826)  & \cellcolor[rgb]{ .992,  .718,  .478}8.628 ($\pm$1.019)   & \cellcolor[rgb]{ .984,  .624,  .463}9.8151 ($\pm$1.16)   & \cellcolor[rgb]{ .973,  .412,  .42}12.5376 ($\pm$1.329)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                                        & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .455,  .765,  .486}2.5495 ($\pm$1.598)                                        & \cellcolor[rgb]{ .388,  .745,  .482}2.0796 ($\pm$1.587) & \cellcolor[rgb]{ .588,  .8,  .49}3.4645 ($\pm$2.209)    & \cellcolor[rgb]{ .8,  .863,  .506}4.8828 ($\pm$1.702)   & \cellcolor[rgb]{ .71,  .835,  .498}4.2871 ($\pm$1.732)  & \cellcolor[rgb]{ 1,  .922,  .518}6.2419 ($\pm$2.157)    & \cellcolor[rgb]{ .914,  .894,  .51}5.672 ($\pm$1.241)   & \cellcolor[rgb]{ .988,  .639,  .463}9.7495 ($\pm$1.048) & \cellcolor[rgb]{ .98,  .537,  .447}10.9817 ($\pm$1.216)  & \cellcolor[rgb]{ .976,  .467,  .431}11.8376 ($\pm$1.464) & \cellcolor[rgb]{ .992,  .757,  .486}8.2774 ($\pm$1.03)   & \cellcolor[rgb]{ .992,  .741,  .486}8.4774 ($\pm$1.068)  & \cellcolor[rgb]{ .973,  .412,  .42}12.4989 ($\pm$1.224)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}1.7204 ($\pm$1.384)                                        & \cellcolor[rgb]{ .643,  .816,  .494}3.6925 ($\pm$4.004) & \cellcolor[rgb]{ .973,  .914,  .514}6.2624 ($\pm$4.58)  & \cellcolor[rgb]{ .663,  .824,  .498}3.8441 ($\pm$1.398) & \cellcolor[rgb]{ 1,  .922,  .518}6.4516 ($\pm$1.02)     & \cellcolor[rgb]{ .71,  .835,  .498}4.2151 ($\pm$1.361)  & \cellcolor[rgb]{ .859,  .878,  .506}5.3602 ($\pm$1.155) & \cellcolor[rgb]{ .996,  .843,  .506}7.4108 ($\pm$1.008) & \cellcolor[rgb]{ .988,  .686,  .475}9.2269 ($\pm$1.183)  & \cellcolor[rgb]{ .988,  .682,  .475}9.3086 ($\pm$1.761)  & \cellcolor[rgb]{ .984,  .596,  .455}10.3355 ($\pm$1.419) & \cellcolor[rgb]{ .984,  .561,  .451}10.7086 ($\pm$1.423) & \cellcolor[rgb]{ .973,  .412,  .42}12.4634 ($\pm$1.465)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .702,  .835,  .498}4.7634 ($\pm$0.938)                                        & \cellcolor[rgb]{ .388,  .745,  .482}1.6226 ($\pm$1.405) & \cellcolor[rgb]{ .455,  .765,  .486}2.3269 ($\pm$1.409) & \cellcolor[rgb]{ .561,  .792,  .49}3.3473 ($\pm$1.35)   & \cellcolor[rgb]{ .831,  .871,  .506}6.0785 ($\pm$0.799) & \cellcolor[rgb]{ .58,  .8,  .49}3.5624 ($\pm$1.315)     & \cellcolor[rgb]{ 1,  .922,  .518}7.7344 ($\pm$1.746)    & \cellcolor[rgb]{ .996,  .8,  .498}8.8505 ($\pm$1.413)   & \cellcolor[rgb]{ .984,  .592,  .455}10.7763 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .855,  .506}8.3613 ($\pm$1.622)     & \cellcolor[rgb]{ .988,  .651,  .467}10.2452 ($\pm$1.447) & \cellcolor[rgb]{ .984,  .576,  .451}10.9226 ($\pm$1.349) & \cellcolor[rgb]{ .973,  .412,  .42}12.4086 ($\pm$1.492)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .506,  .776,  .486}2.7796 ($\pm$1.659)                                        & \cellcolor[rgb]{ 1,  .886,  .514}7.1484 ($\pm$2.227)    & \cellcolor[rgb]{ 1,  .922,  .518}6.7376 ($\pm$2.577)    & \cellcolor[rgb]{ .812,  .867,  .506}5.2269 ($\pm$2.186) & \cellcolor[rgb]{ .388,  .745,  .482}1.8118 ($\pm$1.413) & \cellcolor[rgb]{ .988,  .69,  .475}9.3968 ($\pm$3.022)  & \cellcolor[rgb]{ .494,  .773,  .486}2.6753 ($\pm$1.629) & \cellcolor[rgb]{ .992,  .765,  .49}8.557 ($\pm$1.17)    & \cellcolor[rgb]{ .98,  .529,  .443}11.2011 ($\pm$1.413)  & \cellcolor[rgb]{ .984,  .573,  .451}10.7022 ($\pm$1.067) & \cellcolor[rgb]{ .898,  .89,  .51}5.9215 ($\pm$1.542)    & \cellcolor[rgb]{ .949,  .906,  .514}6.3355 ($\pm$1.612)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5065 ($\pm$1.242)  \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                                         & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                                        & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\
-			\textbf{housing}             & \cellcolor[rgb]{ .404,  .749,  .482}3.4484 ($\pm$2.025)                                        & \cellcolor[rgb]{ .388,  .745,  .482}3.3344 ($\pm$1.819) & \cellcolor[rgb]{ .439,  .757,  .482}3.6946 ($\pm$2.166) & \cellcolor[rgb]{ .553,  .792,  .49}4.4742 ($\pm$2.312)  & \cellcolor[rgb]{ .584,  .8,  .49}4.6839 ($\pm$2.658)    & \cellcolor[rgb]{ .537,  .788,  .49}4.3763 ($\pm$2.438)  & \cellcolor[rgb]{ 1,  .918,  .518}7.5903 ($\pm$2.748)    & \cellcolor[rgb]{ 1,  .922,  .518}7.5441 ($\pm$1.736)    & \cellcolor[rgb]{ 1,  .878,  .51}7.8839 ($\pm$2.099)      & \cellcolor[rgb]{ .984,  .608,  .459}9.9409 ($\pm$2.317)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4075 ($\pm$1.528)  & \cellcolor[rgb]{ .976,  .431,  .424}11.2731 ($\pm$1.506) & \cellcolor[rgb]{ .976,  .42,  .424}11.3484 ($\pm$2.096)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .965,  .91,  .514}6.3946 ($\pm$1.6)                                           & \cellcolor[rgb]{ .525,  .784,  .49}3.5839 ($\pm$2.511)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6968 ($\pm$1.912) & \cellcolor[rgb]{ .706,  .835,  .498}4.7473 ($\pm$2.275) & \cellcolor[rgb]{ .522,  .78,  .486}3.5548 ($\pm$2.125)  & \cellcolor[rgb]{ .78,  .859,  .502}5.2204 ($\pm$3.041)  & \cellcolor[rgb]{ .973,  .412,  .42}11.3527 ($\pm$1.779) & \cellcolor[rgb]{ 1,  .922,  .518}6.6075 ($\pm$2.555)    & \cellcolor[rgb]{ .992,  .749,  .486}8.2473 ($\pm$1.765)  & \cellcolor[rgb]{ .992,  .745,  .486}8.2731 ($\pm$4.384)  & \cellcolor[rgb]{ .98,  .518,  .443}10.3796 ($\pm$1.294)  & \cellcolor[rgb]{ .976,  .447,  .427}11.0548 ($\pm$1.409) & \cellcolor[rgb]{ .988,  .678,  .471}8.8871 ($\pm$3.251)  \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .71,  .835,  .498}4.4656 ($\pm$1.053)                                         & \cellcolor[rgb]{ .388,  .745,  .482}2.1344 ($\pm$1.883) & \cellcolor[rgb]{ .431,  .757,  .482}2.4656 ($\pm$1.359) & \cellcolor[rgb]{ .569,  .796,  .49}3.4484 ($\pm$1.602)  & \cellcolor[rgb]{ .969,  .91,  .514}6.3323 ($\pm$0.891)  & \cellcolor[rgb]{ .6,  .804,  .494}3.6688 ($\pm$2.469)   & \cellcolor[rgb]{ 1,  .922,  .518}6.5538 ($\pm$1.071)    & \cellcolor[rgb]{ .992,  .718,  .478}9.0452 ($\pm$1.093) & \cellcolor[rgb]{ .98,  .51,  .439}11.5731 ($\pm$1.193)   & \cellcolor[rgb]{ .996,  .816,  .498}7.872 ($\pm$0.92)    & \cellcolor[rgb]{ .988,  .659,  .471}9.7527 ($\pm$1.083)  & \cellcolor[rgb]{ .98,  .557,  .451}10.9785 ($\pm$1.108)  & \cellcolor[rgb]{ .973,  .412,  .42}12.7097 ($\pm$1.478)  \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .412,  .749,  .482}2.4677 ($\pm$1.497)                                        & \cellcolor[rgb]{ .388,  .745,  .482}2.2333 ($\pm$1.742) & \cellcolor[rgb]{ .541,  .788,  .49}3.5656 ($\pm$2.492)  & \cellcolor[rgb]{ .655,  .82,  .494}4.572 ($\pm$1.934)   & \cellcolor[rgb]{ 1,  .922,  .518}7.5355 ($\pm$1.44)     & \cellcolor[rgb]{ .635,  .816,  .494}4.3839 ($\pm$1.861) & \cellcolor[rgb]{ .875,  .882,  .51}6.472 ($\pm$2.423)   & \cellcolor[rgb]{ .996,  .843,  .506}8.3161 ($\pm$1.644) & \cellcolor[rgb]{ 1,  .898,  .514}7.7968 ($\pm$1.719)     & \cellcolor[rgb]{ .996,  .827,  .502}8.4892 ($\pm$1.901)  & \cellcolor[rgb]{ .98,  .494,  .435}11.7516 ($\pm$1.155)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5419 ($\pm$1.351)  & \cellcolor[rgb]{ .984,  .584,  .455}10.8742 ($\pm$1.317) \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                                        & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                                         & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}3.5512 ($\pm$2.25)                                         & \cellcolor[rgb]{ .471,  .769,  .486}3.9314 ($\pm$3.423) & \cellcolor[rgb]{ .616,  .808,  .494}4.5691 ($\pm$3.517) & \cellcolor[rgb]{ .631,  .812,  .494}4.6346 ($\pm$2.364) & \cellcolor[rgb]{ .675,  .827,  .498}4.8394 ($\pm$2.384) & \cellcolor[rgb]{ .808,  .867,  .506}5.4327 ($\pm$2.9)   & \cellcolor[rgb]{ 1,  .922,  .518}6.2727 ($\pm$3.004)    & \cellcolor[rgb]{ .992,  .776,  .49}7.7855 ($\pm$2.271)  & \cellcolor[rgb]{ .988,  .639,  .467}9.1522 ($\pm$2.48)   & \cellcolor[rgb]{ .984,  .612,  .459}9.4451 ($\pm$2.75)   & \cellcolor[rgb]{ .984,  .592,  .455}9.6445 ($\pm$2.214)  & \cellcolor[rgb]{ .98,  .529,  .443}10.2877 ($\pm$2.346)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4538 ($\pm$2.354)  \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                                                          & \cellcolor[rgb]{ .49,  .773,  .486}2                    & \cellcolor[rgb]{ .592,  .804,  .494}3                   & \cellcolor[rgb]{ .694,  .831,  .498}4                   & \cellcolor[rgb]{ .796,  .863,  .506}5                   & \cellcolor[rgb]{ .898,  .89,  .51}6                     & \cellcolor[rgb]{ 1,  .922,  .518}7                      & \cellcolor[rgb]{ .996,  .839,  .502}8                   & \cellcolor[rgb]{ .992,  .753,  .486}9                    & \cellcolor[rgb]{ .988,  .667,  .471}10                   & \cellcolor[rgb]{ .984,  .584,  .455}11                   & \cellcolor[rgb]{ .98,  .498,  .439}12                    & \cellcolor[rgb]{ .973,  .412,  .42}13                    \\
-			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
-
-	}
-\end{sidewaystable}%
-
-From the normalised average ranks provided in Table \ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen heuristic implementations respectively.
-These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.
-
-Figure \ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each heuristic, per dataset.
-The heuristics are ordered according to the normalised ranks presented in Table \ref{tab:results:standalone:metrics:rank}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all independent runs and epochs.}
-	\label{fig:results:standalone:descriptive:descriptive}
-\end{figure}
-
-From Figure \ref{fig:results:standalone:descriptive:descriptive} a few observations can be made.
-Firstly, both \acs{Adam} and \acs{RMSProp} achieved radically different average ranks for the student performance dataset, compared to the other datasets.
-This can also be seen in Table \ref{tab:results:standalone:metrics:rank}.
-Further investigation into the reasons for this is required as both these heuristics perform well on all other datasets, and the other heuristics perform well for the student performance dataset.
-A suggestion is that an invalid learning rate or learning rate schedule leads to a scenario where good solutions are overshot, causing \acs{Adam} and \acs{RMSProp} to struggle to resolve back to good solutions.
-Furthermore, the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
-The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.
-
-Figure \ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each heuristic as it relates to all datasets, across all independent runs and epochs.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
-	\caption{Critical difference plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
-	\label{fig:results:standalone:descriptive:cd}
-\end{figure}
-
-Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all heuristics is very small.
-Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, is statistically only outperformed overall by \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}.
-It should be noted that the standalone low-level  heuristics already produce good results in general across all datasets.
-In this particular case, producing better performance outcomes can be hard to achieve.
-However, as mentioned previously, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.
-
-Another observation that can be made is that the gradient-based heuristics generally performed much better than the \acp{MH} on all datasets.
-State of the art methods for training \acp{FFNN}, such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions \cite{ref:kingma:2014}.
-Exploration of the heuristic space leads the \acs{BHH} to consider other heuristics during the training process, which could possibly result in worse performances at times.
-As previously mentioned, a suggestion to improve on these results is to include a move-acceptance strategy, where heuristic progressions are discarded if they fail to produce better results.
-
-Figures \ref{fig:results:standalone:figures:iris} to \ref{fig:results:standalone:figures:bank} provide example illustrations of the train and test loss and accuracy plots for each heuristic as it relates to a selection of classification datasets.
-The train and test loss and accuracy plots provided are illustrated in log scale.
-The other classification datasets are left out for brevity as they produce similar illustrations.
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/iris.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:iris}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/iris.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:iris}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/iris.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:iris}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/iris.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:iris}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:iris}
-\end{figure}
+\section{Results: BHH vs. Low Level Heuristics - Accuracy and Loss Plots}
+\label{app:appendix_results_bhh_vs_heuristics_rank}
 
@@
 \end{figure}
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/bank.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/bank.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/bank.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/bank.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:bank}
-\end{figure}
-
-Figures \ref{fig:results:standalone:figures:fish_toxicity} to \ref{fig:results:standalone:figures:parkinsons} provide example illustrations of the train and test loss plots for each heuristic as it relates to a selection of regression datasets.
-The train and test loss plots provided are illustrated in log scale.
-Similar to before, the other regression datasets are left out for brevity as they produce similar illustrations.
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/fish_toxicity.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:fish_toxicity}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/fish_toxicity.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:fish_toxicity}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:fish_toxicity}
-\end{figure}
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/parkinsons.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:parkinsons}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/parkinsons.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:parkinsons}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:parkinsons}
-\end{figure}

### 2023-02-04 article/frontmatter/abstract.tex
✨ (article): Introduction Done
🚧 (article): Save point, WIP
🚧 (article): WIP save point for revision

@@
 \begin{abstract}
-
-	This work introduces a novel population-based \Acf{BHH}.
-An empirical study is done by using the \acs{BHH} to train \acsp{FFNN}.
+	This work introduces a novel population-based \acf{BHH} that is used to train \acfp{FFNN}.
 An in-depth behaviour analysis is done and the performance of the \acs{BHH} is compared to that of ten popular low-level heuristics, each with different search behaviours.
-The chosen heuristic pool consists of classic gradient-based heuristics as well as meta-heuristics.
+The chosen heuristic pool consists of classic gradient-based heuristics as well as \acf{MH}.
 The empirical process is executed on fourteen datasets consisting of classification and regression problems with varying characteristics.
-The \acs{BHH} is shown to be able to train \acsp{FFNN} well and provide an automated method for finding the best heuristic to train the \acsp{FFNN} at various stages of the training process.
-
+The \acs{BHH} is shown to be able to train \acp{FFNN} well and provide an automated method for finding the best heuristic to train the \acp{FFNN} at various stages of the training process.
 \end{abstract}

### 2023-02-04 article/frontmatter/highlights.tex
🚧 (article): WIP save point for revision

@@
-%%Research highlights
 \begin{highlights}
-	\item A novel heuristic selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acp{FFNN}.
+	\item A novel \acf{HH} selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acfp{FFNN}.
 The resulting \acs{HH} is referred to as the \acf{BHH}.
 
-	\item The results of the empirical study show with statistical significance and certainty that the \Acs{BHH} performs generally well on multiple problems.
-It is shown that, for each problem, the \Acs{BHH} performance is comparable to the best low-level heuristics included in the heuristic selection pool.
+	\item The results of the empirical study show with statistical significance and certainty that the \acs{BHH} performs generally well on multiple problems.
+It is shown that, for each problem, the \acs{BHH} performance is comparable to the best low-level heuristics included in the heuristic selection pool.
 
-	\item The results of the empirical study show that the \Acs{BHH} is able to select the best heuristic to train \acp{FFNN} in general.
+	\item The results of the empirical study show that the \acs{BHH} is able to select the best heuristic to train \acp{FFNN} in general.
 This relieves researchers from the burden of having to do this selection process manually through trial and error.
 
-	\item The results of the empirical study show that the \Acs{BHH}, given a diverse set of lower-level heuristics, will generally produce good results when applied to multiple problems at the same time.
+	\item The results of the empirical study show that the \acs{BHH}, given a diverse set of lower-level heuristics, will generally produce good results when applied to multiple problems at the same time.
 
-	\item Finally, the results of the empirical study show that the \Acs{BHH} is capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from what comes before''.} knowledge in which a predefined selection bias is used for heuristics that are known to be well suited for certain problems.
+	\item Finally, the results of the empirical study show that the \acs{BHH} is capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from what comes before''.} knowledge in which a predefined selection bias is used for heuristics that are known to be well suited for certain problems.
 \end{highlights}

### 2023-02-04 article/sections/01-introduction.tex
🚧 (article): WIP save point for revision

@@
 
-A popular field of focus for studying \acp{ANN} is the process by which these models are trained.
-\acp{ANN} are trained by optimisation algorithms known as heuristics Many different heuristics have been developed and used to train \acp{ANN}  \cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
+A popular field of focus for studying \acfp{ANN} is the process by which these models are trained.
+\acp{ANN} are trained by optimisation algorithms known as heuristics.
+Many different heuristics have been developed and used to train \acp{ANN} \cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
 Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses.
-Finding the best heuristic to train the \acs{ANN} is required in order to yield optimal results.
+Finding the best heuristic to train \acp{ANN} is required in order to yield optimal results.
 This process is often non-trivial and could be a time-consuming exercise.
@@
 This research takes a particular interest in developing a population-based, selection \acs{HH} that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process.
-This research presents the novel \Acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
-This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.
+This research presents a novel \acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
+This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acfp{FFNN} during the training process.
 
@@
 Section \ref{sec:probability} presents background information on probability theory.
-Section  \ref{sec:bhh} presents the developed \Acs{BHH}.
+Section \ref{sec:bhh} presents the developed \acs{BHH}.
 Section \ref{sec:methodology} presents a detailed description of the empirical process and the setup of each experiment.

### 2023-02-04 article/sections/02-artificial-neural-networks.tex
🚧 (article): WIP save point for revision

@@
 These include classification \cite{ref:khan:2001}, pattern matching \cite{ref:cannady:1998, ref:kumar:1994}, pattern completion \cite{ref:dayhoff:2001}, optimisation \cite{ref:specht:1991} and data mining \cite{ref:singh:2009}.
-\Acp{AN} provide the fundamental building blocks for \acp{ANN}.
+\acfp{AN} provide the fundamental building blocks for \acp{ANN}.
 
-The fundamental building blocks of \acp{ANN} is the \acs{AN}.
 The \acs{AN} implements a non-linear mapping from some $I$-dimensional, real-numbered input space to some $T$-dimensional, real-numbered output space.
@@
 
-Multiple \acp{AN} can be organised and used together forming a ``network'' of \acp{AN} referred to as an \acf{ANN}.
+Multiple \acp{AN} can be organised and used together forming a ``network'' of \acp{AN}, referred to as an \acs{ANN}.
 The architecture of the \acs{ANN} refers to the way in which \acp{AN} are organised.
@@
 
-This research focuses on a particular type of \acs{ANN}, referred to as \acp{FFNN}.
+This research focuses on a particular type of \acs{ANN}, referred to as \acfp{FFNN}.
 \acp{FFNN} were the first and simplest type of \acp{ANN} developed \cite{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order.
-Furthermore, \acp{FFNN} implement fully connected topologies, where each \acs{AN} in one layer is connected to all \acp{AN} in the next, without any cycles  \cite{ref:zell:1994}.In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
+Furthermore, \acp{FFNN} implement fully connected topologies, where each \acs{AN} in one layer is connected to all the \acp{AN} in the next, without any cycles \cite{ref:zell:1994}.
+In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
 

### 2023-02-04 article/sections/03-heuristics.tex
🚧 (article): WIP save point for revision

@@
 In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{ANN} and the desired output.
-When using \acs{GD} to train \acp{ANN}, the loss function is used to adjust the weights of the \acs{ANN} in order to minimise the error \cite{ref:engelbrecht:2007}.
+When using \acf{GD} to train \acp{ANN}, the loss function is used to adjust the weights of the \acs{ANN} in order to minimise the error \cite{ref:engelbrecht:2007}.
 
-There are many variants of gradient-based heuristics, however, they all fundamentally apply the same generic \acf{GD} framework that propagates the error signal backwards through the \acs{ANN}.
+There are many variants of gradient-based heuristics, however, they all fundamentally apply the same generic \acs{GD} framework that propagates the error signal backwards through the \acs{ANN}.
 This algorithm is known as \acf{BP}.
-\Acs{BP} was popularised by \citeauthor{ref:werbos:1994} \cite{ref:werbos:1994}.
+\acs{BP} was popularised by \citeauthor{ref:werbos:1994} \cite{ref:werbos:1994}.
 
@@
 Alternative variants have been proposed that lead to better control over the convergence characteristics caused by \acs{SGD}.
-This research focusses on a number of these variants that include \Acs{Momentum} \cite{ref:qian:1999}, \Acf{NAG} \cite{ref:sutskever:2013}, \Acf{Adagrad} \cite{ref:duchi:2011}, \acs{Adadelta} \cite{ref:zeiler:2012}, \Acf{RMSProp} \cite{ref:hinton:2012} and \Acf{Adam} \cite{ref:kingma:2014}.
+This research focusses on a number of these variants that include \acf{Momentum} \cite{ref:qian:1999}, \acf{NAG} \cite{ref:sutskever:2013}, \acf{Adagrad} \cite{ref:duchi:2011}, \acs{Adadelta} \cite{ref:zeiler:2012}, \acf{RMSProp} \cite{ref:hinton:2012} and \acf{Adam} \cite{ref:kingma:2014}.
 
@@
 This research takes a particular interest in population-based \acp{MH} that have been used to successfully train \acp{FFNN}.
-These include \acp{PSO} \cite{ref:shi:1998}, \acf{DE} \cite{ref:price:2006} and \Acp{GA} \cite{ref:fraser:1957}.
+These include \acf{PSO} \cite{ref:shi:1998}, \acf{DE} \cite{ref:price:2006} and \acfp{GA} \cite{ref:fraser:1957}.

### 2023-02-04 article/sections/04-hyper-heuristics.tex
🚧 (article): WIP save point for revision

@@
 
-~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} define \acp{HH} as search methods or learning mechanism for selecting or generating heuristics to solve computational search problems.~\citeauthor{ref:burke:2003}~\cite{ref:burke:2003} mentions that a \acs{HH} is a high-level heuristic approach that, given a particular problem instance and a number of low-level heuristics, can select and apply an appropriate low-level heuristic at each decision point.
-\acp{HH} implement a form of meta-learning that is concerned with the selection of the best heuristic from a pool of heuristics to solve a given problem.
+\citeauthor{ref:burke:2010} \cite{ref:burke:2010} define \acp{HH} as search methods or learning mechanism for selecting or generating heuristics to solve computational search problems.
+\citeauthor{ref:burke:2003} \cite{ref:burke:2003} mentions that a \acs{HH} is a high-level heuristic approach that, given a particular problem instance and a number of low-level heuristics, can select and apply an appropriate low-level heuristic at each decision point.
+\acp{HH} implement a form of \textit{meta-learning} that is concerned with the selection of the best heuristic from a pool of heuristics to solve a given problem.
 It can be said that \acp{HH} are concerned with finding the best heuristic in \textit{heuristic space}, while the underlying low-level heuristics find solutions in the feasible \textit{search/solution space}.
 
-\citeauthor{ref:burke:2010}~\cite{ref:burke:2010} proposed a modern classification scheme used to classify \acp{HH}.
+\citeauthor{ref:burke:2010} \cite{ref:burke:2010} proposed a modern classification scheme used to classify \acp{HH}.
 According to the proposed classification scheme, \acp{HH} are classified in two dimensions.
@@
 For the dimension that involves the nature of the \textit{heuristic search space}, \acp{HH} can be classified as either \textit{heuristic selection} or \textit{heuristic generation}.
-Further distinction is made between construction heuristics and perturbation heuristics.
+Further distinction is made between \textit{construction} of heuristics and \textit{perturbation} of heuristics.
 
@@
 Some notable examples include \cite{ref:dowsland:2007, ref:burke:2010, ref:grobler:2012, ref:vanderstockt:2018}.
-Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides some of the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
+Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.
+\citeauthor{ref:nel:2021} \cite{ref:nel:2021} provides some of the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
 

### 2023-02-04 article/sections/05-probability.tex
🚧 (article): WIP save point for revision

@@
 
-Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event and the conditions under which the event happened~\cite{ref:hackenberger:2019}.
+Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event and the conditions under which the event happened \cite{ref:hackenberger:2019}.
 Bayes' theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
@@
 \citeauthor{ref:wackerly:2014}\cite{ref:wackerly:2014} state that conjugate priors are prior probability distributions that result in posterior distributions that are of the same functional form, $\mathcal{A}(v)$, as the prior, but with different parameter values.
-The conjugate prior to a Bernoulli probability distribution is the Beta probability distribution The conjugate prior to a Categorical and Multinomial probability distribution is the Dirichlet probability distribution~\cite{ref:wackerly:2014}.
+The conjugate prior to a Bernoulli probability distribution is the Beta probability distribution and the conjugate prior to a Categorical and Multinomial probability distribution is the Dirichlet probability distribution \cite{ref:wackerly:2014}.

### 2023-02-04 article/sections/06-bayesian-hyper-heuristics.tex
🚧 (article): WIP save point for revision

@@
 
-According to the classification scheme for \acp{HH} by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \Acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.
-An illustration of the high-level architecture of the \Acs{BHH} is given in Appendix \ref{app:appendix_bhh_architecture} and the high level pseudo-code implementation of the \acs{BHH} is given in Appendix \ref{app:appendix_bhh_algorithm}.
+According to the classification scheme for \acp{HH} by \citeauthor{ref:burke:2010} \cite{ref:burke:2010}, the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.
+
+The reader is referred to \cite{ref:schreuder:2022} for an illustration of the high-level architecture of the \acs{BHH} as well as the high level pseudo-code implementation of the \acs{BHH}.
 Discussions follow on the most important components of the \acs{BHH}.
@@
 The heuristic pool contains the set of low-level heuristics that, together with their performance information, make up the \text{heuristic space}.
-Importantly, The heuristic pool must consist of a diverse set of low-level heuristics with varying capabilities.
+Importantly, the heuristic pool must consist of a diverse set of low-level heuristics with varying capabilities.
 This research takes an interest in including both gradient-based heuristics as well as \acp{MH} in the heuristic pool.
+This approach is referred to as a \textit{multi-method} approach.
 
@@
 Since heuristics maintain (possibly) different states, there is an uncertainty of state transition when switching between heuristics.
-A solution to state indifference is to proxy heuristic state update operations.
+A solution to state indifference is to \textit{proxy} heuristic state update operations.
 State is then maintained in two parts: primary and proxied state.
@@
 The \acs{BHH} thus incorporates a mapping of proxied state update operations.
+Similar to before, the reader is referred to \cite{ref:schreuder:2022} for details on the mapped proxied state update operations.
 
@@
 For example, the candidate solution is represented as the entity's position, and velocity and acceleration is analogous to the gradient and momentum of the entity respectfully.
-Examples of entity state parameters, as derived from various low-level heuristics, include entity position, velocity, gradient, position delta, first and second moments of the gradient, the loss, personal best positions and losses, and so on.
+Examples of entity state parameters, as derived from various low-level heuristics, include entity position, velocity, gradient, position delta, first and second moments of the gradient, the loss, personal best positions, losses, and so on.
 The entity state parameters are updated by the associated heuristic.
@@
 The credit assignment strategy is a mechanism that assigns a discrete credit indicator to heuristics that perform well, based on their performance metrics such as loss.
-The credit assignment strategy implements the ``move acceptance'' process as proposed by~\citeauthor{ref:ozcan:2006}~\cite{ref:ozcan:2006,ref:ozcan:2008} and addresses the credit assignment problem as discussed by~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}.
+The credit assignment strategy implements a component of the ``move acceptance'' process as proposed by \citeauthor{ref:ozcan:2006} \cite{ref:ozcan:2006,ref:ozcan:2008} and addresses the credit assignment problem as discussed by \citeauthor{ref:burke:2010} \cite{ref:burke:2010}.
 A good credit assignment strategy will correctly allocate credit to the appropriate heuristic-entity combination.
@@
 
-The predictive model thus models the \textit{proportional},probability of the event (selection of) heuristic $\boldsymbol{H}$, given allocation to entity $\boldsymbol{E}$ and credit $\boldsymbol{C}$, parameterised by sampled $\boldsymbol{\theta}$, $\boldsymbol{\phi}$ and $\boldsymbol{\psi}$.
-These parameters are in turn parameterised by concentrations $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$, which denote the prior beliefs of the \acs{BHH}.
+The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $\boldsymbol{H}$, given allocation to entity $\boldsymbol{E}$ and credit requirement $\boldsymbol{C}$, parameterised by sampled $\boldsymbol{\theta} \vert \boldsymbol{\alpha} \sim Dir(\boldsymbol{\alpha}; K)$, $\boldsymbol{\phi} \vert \boldsymbol{\beta} \sim Dir(\boldsymbol{\beta}; K)^{J}$ and $\boldsymbol{\psi} \vert \gamma_{1}, \gamma_{0}  \sim Beta(\gamma_{1}, \gamma_{0})$.
+In the aforementioned, $K$ is the heuristic pool size, $J$ is the entity pool size and the indices $1$ and $0$ refers to success and failure parameters respectively.
+The concentration parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$ denote the prior beliefs of the \acs{BHH}.
+Similar to before, the reader is referred to \cite{ref:schreuder:2022} for the mathematical derivation of the selection mechanism.
 
@@
 
-Generally, there are two different techniques that are used to train Naïve Bayes classifiers. The frequentist approach implements \acs{MLE} and the Bayesian approach implements \acs{MAP}.
+Generally, there are two different techniques that are used to train Naïve Bayes classifiers. The frequentist approach implements \acf{MLE} and the Bayesian approach implements \acf{MAP}.
 
@@
 
-It can be said that the \acs{BHH} implements a Gaussian process~\cite{ref:gortler:2019}.
-Since the reselection of heuristics happens at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acs{HMM}~\cite{ref:rabiner:1986}.
+It can be said that the \acs{BHH} implements a Gaussian process \cite{ref:gortler:2019}.
+Since the reselection of heuristics happens at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acs{HMM} \cite{ref:rabiner:1986}.
 

### 2023-02-04 article/sections/07-methodology.tex
🚧 (article): WIP save point for revision

@@
 In the context of training \acp{FFNN}, the underlying models are trained across a number of datasets.
-All the datasets used in the empirical process originate from the UCI Machine Learning Repository~\cite{ref:uci:2022}.
+All the datasets used in the empirical process originate from the UCI Machine Learning Repository \cite{ref:uci:2022}.
 Datasets are grouped by problem type and include seven classification and seven regression datasets.
@@
 The number of hidden units used were determined empirically.
-Weights are initialised by means of Glorot uniform sampling~\cite{ref:glorot:2010}.
+Weights are initialised by means of Glorot uniform sampling \cite{ref:glorot:2010}.
 The models and their configuration, as it is used for each dataset, are given in Table \ref{tab:methodology:models:configurations}.
@@
 
-The Shapiro-Wilk test for normality~\cite{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
-The Levene's test for equality of variance~\cite{ref:levene:1961} ($\alpha$ = 0.001) is used.
-For experiments with three or more configurations, the \acs{ANOVA} statistical test~\cite{ref:fisher:1921} ($\alpha$ = 0.001) is used.
-The Kruskal-Wallis ranked non-parametric test~\cite{ref:kruskal:1952} for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
-Finally, a post-hoc Tukey honest significant difference test~\cite{ref:tukey:1949} ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
+The Shapiro-Wilk test for normality \cite{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
+The Levene's test for equality of variance \cite{ref:levene:1961} ($\alpha$ = 0.001) is used.
+For experiments with three or more configurations, the \acs{ANOVA} statistical test \cite{ref:fisher:1921} ($\alpha$ = 0.001) is used.
+The Kruskal-Wallis ranked non-parametric test \cite{ref:kruskal:1952} for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
+Finally, a post-hoc Tukey honest significant difference test \cite{ref:tukey:1949} ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
 Descriptive and critical difference plots are then retrieved from these results to provide visual aid.

### 2023-02-04 article/sections/08-results.tex
🚧 (article): WIP save point for revision

@@
 Discussions are accompanied by figures and plots to help provide visual aid for discussions.
-The output of the statistical analysis that yielded the results is provided in Appendix \ref{app:statistical_analysis}.
 
@@
 
-Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results.
 The \acs{BHH} applies a form of online learning.
@@
 All experiments conducted are executed for 30 epochs.
-The number of training steps executed is dependent on the batch size applied for each dataset.
 
-All of the underlying \acp{FFNN} trained in the empirical process are relatively small.
-As such, most of the training progress is observed to occur within the first five epochs.
+Most of the training progress is observed to occur within the first five epochs.
 As a result, the \acs{BHH} should apply most learning at the early stages of the training process.
@@
 \subsection{Behavioural Case Study}\label{sec:results:case_study}
-
-This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset.
-As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records.
-The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process.
-Mini-batch training is executed with a batch size of 30.
-The results that are presented are averaged over 30 independent runs.
-
-The case study focuses on three variants of the \acs{BHH}.
-These include the baseline configuration, as was provided in Section \ref{sec:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}).
-Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}).
-Finally, the case study includes a configuration that makes use of the \textit{symmetric} credit assignment strategy hyper-parameter, and is denoted as bhh\_credit\_symmetric (illustrated throughout in \textcolor{blue}{blue}).
-
-These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level heuristics in the heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards heuristics that perform well at all.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% METRICS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Performance Metrics}\label{sec:results:case_study:performance_metrics}
 
@@
 
-Although the different configurations of the \acs{BHH} are all able to successfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.
-
-The volatility and minor divergence of the test loss compared to the training loss, observed in Figure \ref{fig:results:case_study:metrics:test_loss}, is due to overfitting and partly due to the noisiness that results from mini-batch training.
-Early stopping can be applied to the training process to halt training before the model overfits on the training data.
-The training dataset is also very small, with just 120 samples.
-Furthermore, a very small batch size of 16 is used.
-As such, noisiness and overfitting can be expected.
-
-From Figure \ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed.
-This could simply be a result of momentum that is maintained when switching between low-level heuristics in an attempt to find better solutions.
-For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions.
-The \acs{BHH} does not incorporate a \textit{move-acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set.
-A move-acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.
-
-Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figure \ref{fig:results:case_study:metrics} only provides the outcomes of performance metrics at the end of each epoch.
-Further investigation is required at a mini-batch step level and is provided in the following sections.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS ALPHAS
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}
-
-To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
-Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
-The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{heuristic selection probabilities}.
-Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
-Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the heuristic pool.
-Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
-
 \begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
-		\caption{$\alpha_{0}$ - \acs{SGD}}
-		\label{fig:results:case_study:alphas:0}
-	\end{subfigure}
 	\begin{subfigure}{0.5\textwidth}
@@
 		\label{fig:results:case_study:alphas:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
-		\caption{$\alpha_{7}$ - \acs{PSO}}
-		\label{fig:results:case_study:alphas:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
-		\caption{$\alpha_{8}$ - \acs{GA}}
-		\label{fig:results:case_study:alphas:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:alphas}
-\end{figure}
-
-The first logical observation to be made from Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
-Since the replay window size is sufficiently large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
-The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process.
-However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$.
-The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}.
-Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly than other heuristics that do not perform well.
-
-The next observations that can be made are for the bhh\_baseline configuration, illustrated in \textcolor{red}{red}, and the bhh\_credit\_symmetric configuration in \textcolor{blue}{blue}.
-Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1.0 as regular intervals.
-This interval is defined by the \textit{reanalysis interval} hyper-parameter.
-The reanalysis interval dictates the frequency at which Bayesian analysis is conducted on the performance log, maintained by the \acs{BHH}.
-Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval.
-As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.
-
-Notice from Figure \ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements.
-This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process.
-Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process.
-
-Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning.
-The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
-Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequently reselect these heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
-Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS THETAS
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Probability Distribution of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}
-
-This section provides a detailed investigation into the \textit{probability distribution of heuristic selection probabilities} as it changes throughout the training process.
-As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modelling and thus, heuristic selection probabilities are defined by an underlying probabilistic distribution themselves.
-The probability distribution of heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.
-
-Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
-These illustrations are presented in log scale.
-Indices 0, 6, 7, and 8 represent the distribution of heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of heuristic selection probabilities in $\boldsymbol{\theta}$.
-Similar illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
-		\caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
-		\label{fig:results:case_study:thetas:0}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
-		\caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
-		\label{fig:results:case_study:thetas:7}
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
+		\caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
+		\label{fig:results:case_study:p_H:6}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
-		\caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
-		\label{fig:results:case_study:thetas:8}
+		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
+		\caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
+		\label{fig:results:case_study:p_HgEC:0:6}
 	\end{subfigure}
 	\par\bigskip
-	\caption{The average sampled heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
-The heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:thetas}
+	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\label{fig:results:case_study}
 \end{figure}
+
+To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
+Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
+The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{heuristic selection probabilities}.
+Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
+Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the heuristic pool.
+Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
+
+The first logical observation to be made from Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
+Since the replay window size is sufficiently large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
+The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process.
+However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$.
+
+The next observations that can be made are for the bhh\_baseline configuration, illustrated in \textcolor{red}{red}, and the bhh\_credit\_symmetric configuration in \textcolor{blue}{blue}.
+Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1.0 as regular intervals.
+This interval is defined by the \textit{reanalysis interval} hyper-parameter.
+The reanalysis interval dictates the frequency at which Bayesian analysis is conducted on the performance log, maintained by the \acs{BHH}.
+Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval.
+As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.
+
+Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning.
+The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
+Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequently reselect these heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}.
+Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.
+
+The probability distribution of heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.
+
+Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
+These illustrations are presented in log scale.
+Indices 0, 6, 7, and 8 represent the distribution of heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of heuristic selection probabilities in $\boldsymbol{\theta}$.
+Similar illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
 
@@
 
-Another observation to make occurs in the first 30 steps of the training process.
-In Figure \ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same heuristic selection probabilities in these first 30 steps.
-This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number.
-This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches.
-This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.
-
 It should be noted that, despite using the same random seed across configurations for the same run number, the behavioural changes between the configurations start to show after about 30 steps.
@@
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS P_H (Priors)
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Prior Heuristic Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}
-
-This section provides a brief investigation into the \textit{prior heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}.
 The prior heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
@@
 Similar to before, these illustrations are also presented in log scale.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
-		\caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
-		\label{fig:results:case_study:p_H:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
-		\caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
-		\label{fig:results:case_study:p_H:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
-		\caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
-		\label{fig:results:case_study:p_H:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
-		\caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
-		\label{fig:results:case_study:p_H:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average prior heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8.
-The prior heuristic selection probabilities are sampled from the probability distribution of heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_H}
-\end{figure}
 
@@
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % PARAMS P_HgEC (Posterior)
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Posterior Heuristic Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}
-
-This section provides a detailed discussion on the outcomes of the \textit{posterior heuristic selection probabilities}.
-These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}.
 The posterior heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy.
@@
 As before, illustrations for the other indices are left out for brevity as they yield similar illustrations.
-
-\begin{figure}[htb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
-		\caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
-		\label{fig:results:case_study:p_HgEC:0:0}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
-		\caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
-		\label{fig:results:case_study:p_HgEC:0:6}
-	\end{subfigure}
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
-		\caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
-		\label{fig:results:case_study:p_HgEC:0:7}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
-		\caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
-		\label{fig:results:case_study:p_HgEC:0:8}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The average calculated proportional posterior heuristic selection probabilities for heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, $c_{1}$, from the \textit{ibest} credit assignment strategy.
-The proportional posterior heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
-	\label{fig:results:case_study:p_HgEC:0}
-\end{figure}
 
@@
 
-\begin{sidewaystable}[htbp]
-	\centering
-	\caption{Empirical results showing test loss and statistics for different low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs, measured at the last epoch.}
-	\label{tab:results:standalone:metrics:loss}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|lll|l|l|l|l|l|lllll}
-			                                    & \multicolumn{13}{c}{\textbf{BHH vs.
-Low-Level Heuristics - Average Test Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
-			\cmidrule{2-14}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                           & \multicolumn{1}{c}{\textbf{adam}}                       & \multicolumn{1}{c|}{\textbf{rmsprop}}                   & \multicolumn{1}{c|}{\textbf{bhh\_gd}}                   & \multicolumn{1}{c|}{\textbf{nag}}                       & \multicolumn{1}{c|}{\textbf{bhh\_all}}                  & \multicolumn{1}{c|}{\textbf{adadelta}}                  & \multicolumn{1}{c|}{\textbf{bhh\_mh}}                   & \multicolumn{1}{c}{\textbf{ga}}                         & \multicolumn{1}{c}{\textbf{pso}}                        & \multicolumn{1}{c}{\textbf{sgd}}                        & \multicolumn{1}{c}{\textbf{momentum}}                   & \multicolumn{1}{c}{\textbf{de}}                         \\
-			\midrule
-			\textbf{abalone}                    & \cellcolor[rgb]{ .506,  .776,  .486}1.9678 ($\pm$0.032)                        & \cellcolor[rgb]{ .494,  .773,  .486}1.9651 ($\pm$0.035) & \cellcolor[rgb]{ .388,  .745,  .482}1.9455 ($\pm$0.035) & \cellcolor[rgb]{ .749,  .847,  .502}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .765,  .851,  .502}2.0156 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .788,  .859,  .502}2.0199 ($\pm$0.034) & \cellcolor[rgb]{ .996,  .827,  .502}2.2942 ($\pm$0.055) & \cellcolor[rgb]{ .984,  .612,  .459}2.8155 ($\pm$0.055) & \cellcolor[rgb]{ .98,  .522,  .443}3.0384 ($\pm$0.294)  & \cellcolor[rgb]{ .992,  .773,  .49}2.428 ($\pm$0.029)   & \cellcolor[rgb]{ .992,  .745,  .486}2.4942 ($\pm$0.029) & \cellcolor[rgb]{ .973,  .412,  .42}3.2959 ($\pm$0.016)  \\
-			\textbf{air quality}                & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                         & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\
-			\textbf{bank}                       & \cellcolor[rgb]{ .459,  .765,  .486}0.2096 ($\pm$0.005)                        & \cellcolor[rgb]{ .4,  .745,  .482}0.2065 ($\pm$0.004)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2058 ($\pm$0.006) & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.005)    & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .886,  .514}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .627,  .812,  .494}0.2186 ($\pm$0.004) & \cellcolor[rgb]{ .996,  .839,  .502}0.2562 ($\pm$0.011) & \cellcolor[rgb]{ .988,  .686,  .475}0.2881 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.3454 ($\pm$0.034)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2382 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2386 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .424,  .424}0.3437 ($\pm$0.028) \\
-			\textbf{bike}                       & \cellcolor[rgb]{ .388,  .745,  .482}0.0458 ($\pm$0.002)                        & \cellcolor[rgb]{ .592,  .804,  .494}0.0682 ($\pm$0.068) & \cellcolor[rgb]{ 1,  .922,  .518}0.1123 ($\pm$0.103)    & \cellcolor[rgb]{ .467,  .765,  .486}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .882,  .886,  .51}0.0995 ($\pm$0.002)  & \cellcolor[rgb]{ .565,  .796,  .49}0.0651 ($\pm$0.02)   & \cellcolor[rgb]{ .588,  .8,  .49}0.0679 ($\pm$0.002)    & \cellcolor[rgb]{ 1,  .902,  .514}0.1179 ($\pm$0.006)    & \cellcolor[rgb]{ .992,  .761,  .486}0.1531 ($\pm$0.005) & \cellcolor[rgb]{ .992,  .773,  .49}0.1503 ($\pm$0.025)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1599 ($\pm$0.003) & \cellcolor[rgb]{ .992,  .725,  .482}0.1614 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.2399 ($\pm$0.04)   \\
-			\textbf{car}                        & \cellcolor[rgb]{ .729,  .843,  .502}0.2027 ($\pm$0.018)                        & \cellcolor[rgb]{ .388,  .745,  .482}0.0972 ($\pm$0.024) & \cellcolor[rgb]{ .408,  .749,  .482}0.1039 ($\pm$0.031) & \cellcolor[rgb]{ .62,  .812,  .494}0.169 ($\pm$0.025)   & \cellcolor[rgb]{ .867,  .882,  .51}0.2454 ($\pm$0.029)  & \cellcolor[rgb]{ .58,  .8,  .49}0.1572 ($\pm$0.034)     & \cellcolor[rgb]{ 1,  .922,  .518}0.2859 ($\pm$0.027)    & \cellcolor[rgb]{ .992,  .733,  .482}0.4891 ($\pm$0.077) & \cellcolor[rgb]{ .98,  .502,  .439}0.7374 ($\pm$0.063)  & \cellcolor[rgb]{ .988,  .667,  .471}0.5632 ($\pm$0.158) & \cellcolor[rgb]{ .98,  .533,  .443}0.7035 ($\pm$0.052)  & \cellcolor[rgb]{ .98,  .506,  .439}0.7322 ($\pm$0.043)  & \cellcolor[rgb]{ .973,  .412,  .42}0.8332 ($\pm$0.074)  \\
-			\textbf{diabetic}                   & \cellcolor[rgb]{ .694,  .831,  .498}0.8895 ($\pm$0.004)                        & \cellcolor[rgb]{ 1,  .898,  .514}0.9193 ($\pm$0.01)     & \cellcolor[rgb]{ .918,  .894,  .51}0.8957 ($\pm$0.004)  & \cellcolor[rgb]{ .98,  .914,  .514}0.8976 ($\pm$0.011)  & \cellcolor[rgb]{ .388,  .745,  .482}0.8809 ($\pm$0.004) & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)   & \cellcolor[rgb]{ .49,  .773,  .486}0.8839 ($\pm$0.005)  & \cellcolor[rgb]{ 1,  .902,  .518}0.9137 ($\pm$0.008)    & \cellcolor[rgb]{ .996,  .843,  .506}0.9613 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .835,  .502}0.9661 ($\pm$0.016) & \cellcolor[rgb]{ .976,  .914,  .514}0.8974 ($\pm$0.004) & \cellcolor[rgb]{ 1,  .922,  .518}0.898 ($\pm$0.003)     & \cellcolor[rgb]{ .988,  .694,  .475}1.0774 ($\pm$0.039) \\
-			\textbf{fish toxicity}              & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                           & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
-			\textbf{forest fires}               & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                            & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\
-			\textbf{housing}                    & \cellcolor[rgb]{ .518,  .78,  .486}0.0889 ($\pm$0.012)                         & \cellcolor[rgb]{ .404,  .749,  .482}0.0848 ($\pm$0.011) & \cellcolor[rgb]{ .388,  .745,  .482}0.0842 ($\pm$0.015) & \cellcolor[rgb]{ .69,  .831,  .498}0.0951 ($\pm$0.015)  & \cellcolor[rgb]{ .612,  .808,  .494}0.0923 ($\pm$0.016) & \cellcolor[rgb]{ .663,  .824,  .498}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.106 ($\pm$0.019)     & \cellcolor[rgb]{ 1,  .867,  .51}0.1169 ($\pm$0.019)     & \cellcolor[rgb]{ .996,  .812,  .498}0.1279 ($\pm$0.02)  & \cellcolor[rgb]{ .992,  .722,  .482}0.1452 ($\pm$0.03)  & \cellcolor[rgb]{ .984,  .576,  .455}0.1735 ($\pm$0.023) & \cellcolor[rgb]{ .984,  .588,  .455}0.1713 ($\pm$0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.2057 ($\pm$0.036)  \\
-			\textbf{iris}                       & \cellcolor[rgb]{ .788,  .859,  .502}0.2161 ($\pm$0.059)                        & \cellcolor[rgb]{ .514,  .78,  .486}0.1203 ($\pm$0.098)  & \cellcolor[rgb]{ .388,  .745,  .482}0.0753 ($\pm$0.046) & \cellcolor[rgb]{ 1,  .855,  .506}0.3729 ($\pm$1.119)    & \cellcolor[rgb]{ .416,  .753,  .482}0.085 ($\pm$0.042)  & \cellcolor[rgb]{ .859,  .878,  .506}0.2411 ($\pm$0.295) & \cellcolor[rgb]{ .996,  .808,  .498}0.426 ($\pm$0.072)  & \cellcolor[rgb]{ .686,  .831,  .498}0.1809 ($\pm$0.164) & \cellcolor[rgb]{ 1,  .922,  .518}0.2895 ($\pm$0.117)    & \cellcolor[rgb]{ .973,  .412,  .42}0.8965 ($\pm$0.844)  & \cellcolor[rgb]{ .992,  .773,  .49}0.4694 ($\pm$0.088)  & \cellcolor[rgb]{ .992,  .745,  .486}0.5028 ($\pm$0.072) & \cellcolor[rgb]{ .98,  .494,  .435}0.8027 ($\pm$0.684)  \\
-			\textbf{mushroom}                   & \cellcolor[rgb]{ .549,  .792,  .49}0.0026 ($\pm$0.001)                         & \cellcolor[rgb]{ .467,  .765,  .486}0.0013 ($\pm$0.005) & \cellcolor[rgb]{ .388,  .745,  .482}0.0001 ($\pm$0)     & \cellcolor[rgb]{ .439,  .757,  .482}0.0009 ($\pm$0.001) & \cellcolor[rgb]{ 1,  .922,  .518}0.0094 ($\pm$0.002)    & \cellcolor[rgb]{ .718,  .839,  .498}0.0052 ($\pm$0.012) & \cellcolor[rgb]{ .655,  .82,  .494}0.0042 ($\pm$0.001)  & \cellcolor[rgb]{ 1,  .871,  .51}0.0774 ($\pm$0.02)      & \cellcolor[rgb]{ .984,  .561,  .451}0.4892 ($\pm$0.025) & \cellcolor[rgb]{ 1,  .886,  .514}0.0611 ($\pm$0.06)     & \cellcolor[rgb]{ .996,  .796,  .494}0.1797 ($\pm$0.009) & \cellcolor[rgb]{ .992,  .749,  .486}0.2418 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.687 ($\pm$0.016)   \\
-			\textbf{parkinsons}                 & \cellcolor[rgb]{ .51,  .776,  .486}0.0563 ($\pm$0.001)                         & \cellcolor[rgb]{ .412,  .749,  .482}0.0545 ($\pm$0.002) & \cellcolor[rgb]{ .388,  .745,  .482}0.054 ($\pm$0.002)  & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ 1,  .922,  .518}0.0655 ($\pm$0.002)    & \cellcolor[rgb]{ .639,  .816,  .494}0.0587 ($\pm$0.003) & \cellcolor[rgb]{ .69,  .831,  .498}0.0597 ($\pm$0.002)  & \cellcolor[rgb]{ 1,  .918,  .518}0.0658 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .898,  .514}0.0669 ($\pm$0.003)    & \cellcolor[rgb]{ 1,  .894,  .514}0.0671 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .467,  .431}0.0923 ($\pm$0.008) & \cellcolor[rgb]{ .973,  .412,  .42}0.0954 ($\pm$0.009)  & \cellcolor[rgb]{ .984,  .604,  .459}0.0843 ($\pm$0.009) \\
-			\textbf{student performance}        & \cellcolor[rgb]{ .388,  .745,  .482}0.1656 ($\pm$0.011)                        & \cellcolor[rgb]{ .98,  .522,  .443}0.4929 ($\pm$0.105)  & \cellcolor[rgb]{ .973,  .412,  .42}0.5724 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .855,  .506}0.2454 ($\pm$0.134)    & \cellcolor[rgb]{ .471,  .769,  .486}0.1697 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .871,  .51}0.2359 ($\pm$0.102)     & \cellcolor[rgb]{ .49,  .773,  .486}0.1708 ($\pm$0.01)   & \cellcolor[rgb]{ .969,  .91,  .514}0.1947 ($\pm$0.014)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1962 ($\pm$0.01)     & \cellcolor[rgb]{ .984,  .573,  .451}0.4565 ($\pm$0.049) & \cellcolor[rgb]{ .933,  .902,  .514}0.193 ($\pm$0.011)  & \cellcolor[rgb]{ .925,  .898,  .51}0.1925 ($\pm$0.011)  & \cellcolor[rgb]{ 1,  .918,  .518}0.2014 ($\pm$0.012)    \\
-			\textbf{wine quality}               & \cellcolor[rgb]{ .631,  .816,  .494}1.0651 ($\pm$0.024)                        & \cellcolor[rgb]{ .388,  .745,  .482}1.0395 ($\pm$0.018) & \cellcolor[rgb]{ .502,  .776,  .486}1.0514 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .698,  .831,  .498}1.0718 ($\pm$0.025) & \cellcolor[rgb]{ .804,  .863,  .506}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .788,  .859,  .502}1.0809 ($\pm$0.021) & \cellcolor[rgb]{ .996,  .839,  .502}1.1666 ($\pm$0.03)  & \cellcolor[rgb]{ .992,  .725,  .482}1.2516 ($\pm$0.046) & \cellcolor[rgb]{ .988,  .659,  .467}1.3046 ($\pm$0.114) & \cellcolor[rgb]{ .996,  .843,  .502}1.1648 ($\pm$0.023) & \cellcolor[rgb]{ .996,  .824,  .502}1.1774 ($\pm$0.019) & \cellcolor[rgb]{ .973,  .412,  .42}1.4896 ($\pm$0.093)  \\
-			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
-	}
-\end{sidewaystable}%
-
 Table \ref{tab:results:standalone:metrics:loss} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
@@
 The normalised average rank is calculated as a discrete normalisation of the average rank achieved across all datasets, for all independent runs and epochs.
-
-\begin{sidewaystable}[htbp]
-	\centering
-	\caption{Empirical results showing normalised average rank and statistics for different low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
-	\label{tab:results:standalone:metrics:rank}%
-	\par\bigskip
-	\resizebox{\textwidth}{!}{
-		\begin{tabular}{r|ccc|c|c|c|c|c|ccccc}
-			                             & \multicolumn{13}{c}{\textbf{BHH vs.
-Low-Level Heuristics - Average Rank (Based on Test Loss)}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\
-			\textbf{dataset}             & \textbf{adagrad}                                                                               & \textbf{adam}                                           & \textbf{rmsprop}                                        & \textbf{bhh\_gd}                                        & \textbf{nag}                                            & \textbf{bhh\_all}                                       & \textbf{adadelta}                                       & \textbf{bhh\_mh}                                        & \textbf{ga}                                              & \textbf{pso}                                             & \textbf{sgd}                                             & \textbf{momentum}                                        & \textbf{de}                                              \\
-			\midrule
-			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.2215 ($\pm$1.591)                                        & \cellcolor[rgb]{ .416,  .753,  .482}2.3989 ($\pm$1.887) & \cellcolor[rgb]{ .78,  .859,  .502}4.6172 ($\pm$2.65)   & \cellcolor[rgb]{ .796,  .863,  .506}4.7032 ($\pm$2.108) & \cellcolor[rgb]{ .725,  .839,  .498}4.2731 ($\pm$1.542) & \cellcolor[rgb]{ 1,  .922,  .518}5.9376 ($\pm$2.399)    & \cellcolor[rgb]{ .894,  .89,  .51}5.3129 ($\pm$1.478)   & \cellcolor[rgb]{ .992,  .749,  .486}8.1882 ($\pm$1.195) & \cellcolor[rgb]{ .98,  .525,  .443}11.1108 ($\pm$1.102)  & \cellcolor[rgb]{ .98,  .514,  .439}11.2559 ($\pm$1.826)  & \cellcolor[rgb]{ .992,  .718,  .478}8.628 ($\pm$1.019)   & \cellcolor[rgb]{ .984,  .624,  .463}9.8151 ($\pm$1.16)   & \cellcolor[rgb]{ .973,  .412,  .42}12.5376 ($\pm$1.329)  \\
-			\textbf{air quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                                        & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\
-			\textbf{bank}                & \cellcolor[rgb]{ .455,  .765,  .486}2.5495 ($\pm$1.598)                                        & \cellcolor[rgb]{ .388,  .745,  .482}2.0796 ($\pm$1.587) & \cellcolor[rgb]{ .588,  .8,  .49}3.4645 ($\pm$2.209)    & \cellcolor[rgb]{ .8,  .863,  .506}4.8828 ($\pm$1.702)   & \cellcolor[rgb]{ .71,  .835,  .498}4.2871 ($\pm$1.732)  & \cellcolor[rgb]{ 1,  .922,  .518}6.2419 ($\pm$2.157)    & \cellcolor[rgb]{ .914,  .894,  .51}5.672 ($\pm$1.241)   & \cellcolor[rgb]{ .988,  .639,  .463}9.7495 ($\pm$1.048) & \cellcolor[rgb]{ .98,  .537,  .447}10.9817 ($\pm$1.216)  & \cellcolor[rgb]{ .976,  .467,  .431}11.8376 ($\pm$1.464) & \cellcolor[rgb]{ .992,  .757,  .486}8.2774 ($\pm$1.03)   & \cellcolor[rgb]{ .992,  .741,  .486}8.4774 ($\pm$1.068)  & \cellcolor[rgb]{ .973,  .412,  .42}12.4989 ($\pm$1.224)  \\
-			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}1.7204 ($\pm$1.384)                                        & \cellcolor[rgb]{ .643,  .816,  .494}3.6925 ($\pm$4.004) & \cellcolor[rgb]{ .973,  .914,  .514}6.2624 ($\pm$4.58)  & \cellcolor[rgb]{ .663,  .824,  .498}3.8441 ($\pm$1.398) & \cellcolor[rgb]{ 1,  .922,  .518}6.4516 ($\pm$1.02)     & \cellcolor[rgb]{ .71,  .835,  .498}4.2151 ($\pm$1.361)  & \cellcolor[rgb]{ .859,  .878,  .506}5.3602 ($\pm$1.155) & \cellcolor[rgb]{ .996,  .843,  .506}7.4108 ($\pm$1.008) & \cellcolor[rgb]{ .988,  .686,  .475}9.2269 ($\pm$1.183)  & \cellcolor[rgb]{ .988,  .682,  .475}9.3086 ($\pm$1.761)  & \cellcolor[rgb]{ .984,  .596,  .455}10.3355 ($\pm$1.419) & \cellcolor[rgb]{ .984,  .561,  .451}10.7086 ($\pm$1.423) & \cellcolor[rgb]{ .973,  .412,  .42}12.4634 ($\pm$1.465)  \\
-			\textbf{car}                 & \cellcolor[rgb]{ .702,  .835,  .498}4.7634 ($\pm$0.938)                                        & \cellcolor[rgb]{ .388,  .745,  .482}1.6226 ($\pm$1.405) & \cellcolor[rgb]{ .455,  .765,  .486}2.3269 ($\pm$1.409) & \cellcolor[rgb]{ .561,  .792,  .49}3.3473 ($\pm$1.35)   & \cellcolor[rgb]{ .831,  .871,  .506}6.0785 ($\pm$0.799) & \cellcolor[rgb]{ .58,  .8,  .49}3.5624 ($\pm$1.315)     & \cellcolor[rgb]{ 1,  .922,  .518}7.7344 ($\pm$1.746)    & \cellcolor[rgb]{ .996,  .8,  .498}8.8505 ($\pm$1.413)   & \cellcolor[rgb]{ .984,  .592,  .455}10.7763 ($\pm$1.471) & \cellcolor[rgb]{ 1,  .855,  .506}8.3613 ($\pm$1.622)     & \cellcolor[rgb]{ .988,  .651,  .467}10.2452 ($\pm$1.447) & \cellcolor[rgb]{ .984,  .576,  .451}10.9226 ($\pm$1.349) & \cellcolor[rgb]{ .973,  .412,  .42}12.4086 ($\pm$1.492)  \\
-			\textbf{diabetic}            & \cellcolor[rgb]{ .506,  .776,  .486}2.7796 ($\pm$1.659)                                        & \cellcolor[rgb]{ 1,  .886,  .514}7.1484 ($\pm$2.227)    & \cellcolor[rgb]{ 1,  .922,  .518}6.7376 ($\pm$2.577)    & \cellcolor[rgb]{ .812,  .867,  .506}5.2269 ($\pm$2.186) & \cellcolor[rgb]{ .388,  .745,  .482}1.8118 ($\pm$1.413) & \cellcolor[rgb]{ .988,  .69,  .475}9.3968 ($\pm$3.022)  & \cellcolor[rgb]{ .494,  .773,  .486}2.6753 ($\pm$1.629) & \cellcolor[rgb]{ .992,  .765,  .49}8.557 ($\pm$1.17)    & \cellcolor[rgb]{ .98,  .529,  .443}11.2011 ($\pm$1.413)  & \cellcolor[rgb]{ .984,  .573,  .451}10.7022 ($\pm$1.067) & \cellcolor[rgb]{ .898,  .89,  .51}5.9215 ($\pm$1.542)    & \cellcolor[rgb]{ .949,  .906,  .514}6.3355 ($\pm$1.612)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5065 ($\pm$1.242)  \\
-			\textbf{fish toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                                         & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
-			\textbf{forest fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                                        & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\
-			\textbf{housing}             & \cellcolor[rgb]{ .404,  .749,  .482}3.4484 ($\pm$2.025)                                        & \cellcolor[rgb]{ .388,  .745,  .482}3.3344 ($\pm$1.819) & \cellcolor[rgb]{ .439,  .757,  .482}3.6946 ($\pm$2.166) & \cellcolor[rgb]{ .553,  .792,  .49}4.4742 ($\pm$2.312)  & \cellcolor[rgb]{ .584,  .8,  .49}4.6839 ($\pm$2.658)    & \cellcolor[rgb]{ .537,  .788,  .49}4.3763 ($\pm$2.438)  & \cellcolor[rgb]{ 1,  .918,  .518}7.5903 ($\pm$2.748)    & \cellcolor[rgb]{ 1,  .922,  .518}7.5441 ($\pm$1.736)    & \cellcolor[rgb]{ 1,  .878,  .51}7.8839 ($\pm$2.099)      & \cellcolor[rgb]{ .984,  .608,  .459}9.9409 ($\pm$2.317)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4075 ($\pm$1.528)  & \cellcolor[rgb]{ .976,  .431,  .424}11.2731 ($\pm$1.506) & \cellcolor[rgb]{ .976,  .42,  .424}11.3484 ($\pm$2.096)  \\
-			\textbf{iris}                & \cellcolor[rgb]{ .965,  .91,  .514}6.3946 ($\pm$1.6)                                           & \cellcolor[rgb]{ .525,  .784,  .49}3.5839 ($\pm$2.511)  & \cellcolor[rgb]{ .388,  .745,  .482}2.6968 ($\pm$1.912) & \cellcolor[rgb]{ .706,  .835,  .498}4.7473 ($\pm$2.275) & \cellcolor[rgb]{ .522,  .78,  .486}3.5548 ($\pm$2.125)  & \cellcolor[rgb]{ .78,  .859,  .502}5.2204 ($\pm$3.041)  & \cellcolor[rgb]{ .973,  .412,  .42}11.3527 ($\pm$1.779) & \cellcolor[rgb]{ 1,  .922,  .518}6.6075 ($\pm$2.555)    & \cellcolor[rgb]{ .992,  .749,  .486}8.2473 ($\pm$1.765)  & \cellcolor[rgb]{ .992,  .745,  .486}8.2731 ($\pm$4.384)  & \cellcolor[rgb]{ .98,  .518,  .443}10.3796 ($\pm$1.294)  & \cellcolor[rgb]{ .976,  .447,  .427}11.0548 ($\pm$1.409) & \cellcolor[rgb]{ .988,  .678,  .471}8.8871 ($\pm$3.251)  \\
-			\textbf{mushroom}            & \cellcolor[rgb]{ .71,  .835,  .498}4.4656 ($\pm$1.053)                                         & \cellcolor[rgb]{ .388,  .745,  .482}2.1344 ($\pm$1.883) & \cellcolor[rgb]{ .431,  .757,  .482}2.4656 ($\pm$1.359) & \cellcolor[rgb]{ .569,  .796,  .49}3.4484 ($\pm$1.602)  & \cellcolor[rgb]{ .969,  .91,  .514}6.3323 ($\pm$0.891)  & \cellcolor[rgb]{ .6,  .804,  .494}3.6688 ($\pm$2.469)   & \cellcolor[rgb]{ 1,  .922,  .518}6.5538 ($\pm$1.071)    & \cellcolor[rgb]{ .992,  .718,  .478}9.0452 ($\pm$1.093) & \cellcolor[rgb]{ .98,  .51,  .439}11.5731 ($\pm$1.193)   & \cellcolor[rgb]{ .996,  .816,  .498}7.872 ($\pm$0.92)    & \cellcolor[rgb]{ .988,  .659,  .471}9.7527 ($\pm$1.083)  & \cellcolor[rgb]{ .98,  .557,  .451}10.9785 ($\pm$1.108)  & \cellcolor[rgb]{ .973,  .412,  .42}12.7097 ($\pm$1.478)  \\
-			\textbf{parkinsons}          & \cellcolor[rgb]{ .412,  .749,  .482}2.4677 ($\pm$1.497)                                        & \cellcolor[rgb]{ .388,  .745,  .482}2.2333 ($\pm$1.742) & \cellcolor[rgb]{ .541,  .788,  .49}3.5656 ($\pm$2.492)  & \cellcolor[rgb]{ .655,  .82,  .494}4.572 ($\pm$1.934)   & \cellcolor[rgb]{ 1,  .922,  .518}7.5355 ($\pm$1.44)     & \cellcolor[rgb]{ .635,  .816,  .494}4.3839 ($\pm$1.861) & \cellcolor[rgb]{ .875,  .882,  .51}6.472 ($\pm$2.423)   & \cellcolor[rgb]{ .996,  .843,  .506}8.3161 ($\pm$1.644) & \cellcolor[rgb]{ 1,  .898,  .514}7.7968 ($\pm$1.719)     & \cellcolor[rgb]{ .996,  .827,  .502}8.4892 ($\pm$1.901)  & \cellcolor[rgb]{ .98,  .494,  .435}11.7516 ($\pm$1.155)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5419 ($\pm$1.351)  & \cellcolor[rgb]{ .984,  .584,  .455}10.8742 ($\pm$1.317) \\
-			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                                        & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
-			\textbf{wine quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                                         & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\
-			\midrule
-			\textbf{avg rank}            & \cellcolor[rgb]{ .388,  .745,  .482}3.5512 ($\pm$2.25)                                         & \cellcolor[rgb]{ .471,  .769,  .486}3.9314 ($\pm$3.423) & \cellcolor[rgb]{ .616,  .808,  .494}4.5691 ($\pm$3.517) & \cellcolor[rgb]{ .631,  .812,  .494}4.6346 ($\pm$2.364) & \cellcolor[rgb]{ .675,  .827,  .498}4.8394 ($\pm$2.384) & \cellcolor[rgb]{ .808,  .867,  .506}5.4327 ($\pm$2.9)   & \cellcolor[rgb]{ 1,  .922,  .518}6.2727 ($\pm$3.004)    & \cellcolor[rgb]{ .992,  .776,  .49}7.7855 ($\pm$2.271)  & \cellcolor[rgb]{ .988,  .639,  .467}9.1522 ($\pm$2.48)   & \cellcolor[rgb]{ .984,  .612,  .459}9.4451 ($\pm$2.75)   & \cellcolor[rgb]{ .984,  .592,  .455}9.6445 ($\pm$2.214)  & \cellcolor[rgb]{ .98,  .529,  .443}10.2877 ($\pm$2.346)  & \cellcolor[rgb]{ .973,  .412,  .42}11.4538 ($\pm$2.354)  \\
-			\midrule
-			\textbf{normalised avg rank} & \cellcolor[rgb]{ .388,  .745,  .482}1                                                          & \cellcolor[rgb]{ .49,  .773,  .486}2                    & \cellcolor[rgb]{ .592,  .804,  .494}3                   & \cellcolor[rgb]{ .694,  .831,  .498}4                   & \cellcolor[rgb]{ .796,  .863,  .506}5                   & \cellcolor[rgb]{ .898,  .89,  .51}6                     & \cellcolor[rgb]{ 1,  .922,  .518}7                      & \cellcolor[rgb]{ .996,  .839,  .502}8                   & \cellcolor[rgb]{ .992,  .753,  .486}9                    & \cellcolor[rgb]{ .988,  .667,  .471}10                   & \cellcolor[rgb]{ .984,  .584,  .455}11                   & \cellcolor[rgb]{ .98,  .498,  .439}12                    & \cellcolor[rgb]{ .973,  .412,  .42}13                    \\
-			\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\end{tabular}%
-
-	}
-\end{sidewaystable}%
 
@@
 As previously mentioned, a suggestion to improve on these results is to include a move-acceptance strategy, where heuristic progressions are discarded if they fail to produce better results.
-
-Figures \ref{fig:results:standalone:figures:iris} to \ref{fig:results:standalone:figures:bank} provide example illustrations of the train and test loss and accuracy plots for each heuristic as it relates to a selection of classification datasets.
-The train and test loss and accuracy plots provided are illustrated in log scale.
-The other classification datasets are left out for brevity as they produce similar illustrations.
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/iris.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:iris}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/iris.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:iris}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/iris.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:iris}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/iris.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:iris}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:iris}
-\end{figure}
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:car}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:car}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the car dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:car}
-\end{figure}
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/bank.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/bank.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\par\bigskip
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/bank.pdf}
-		\caption{Train log accuracy}
-		\label{fig:results:standalone:figures:accuracy:train:bank}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/bank.pdf}
-		\caption{Test log accuracy}
-		\label{fig:results:standalone:figures:accuracy:test:bank}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:bank}
-\end{figure}
-
-Figures \ref{fig:results:standalone:figures:fish_toxicity} to \ref{fig:results:standalone:figures:parkinsons} provide example illustrations of the train and test loss plots for each heuristic as it relates to a selection of regression datasets.
-The train and test loss plots provided are illustrated in log scale.
-Similar to before, the other regression datasets are left out for brevity as they produce similar illustrations.
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/fish_toxicity.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:fish_toxicity}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/fish_toxicity.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:fish_toxicity}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:fish_toxicity}
-\end{figure}
-
-\begin{figure}[htpb]
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/train/loss/parkinsons.pdf}
-		\caption{Train log loss}
-		\label{fig:results:standalone:figures:loss:train:parkinsons}
-	\end{subfigure}
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{standalone/figures/test/loss/parkinsons.pdf}
-		\caption{Test log loss}
-		\label{fig:results:standalone:figures:loss:test:parkinsons}
-	\end{subfigure}
-	\par\bigskip
-	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
-	\label{fig:results:standalone:figures:parkinsons}
-\end{figure}

### 2023-02-04 article/sections/09-conclusion.tex
🚧 (article): WIP save point for revision

@@
 
-The main area of focus for the research done in this dissertation stems from the problem statement, which identified the difficult and tedious problem of selecting the best heuristic for training \acp{FFNN}.
+The main area of focus for the research done in this dissertation stems from the problem statement, which identified the difficult and tedious process of selecting the best heuristic for training \acp{FFNN}.
 The research presented in this article identified the possibility of using a different approach, referred to as \acp{HH}, to automate the heuristic selection process.
 
-This research then set out to develop a novel high-level heuristic that utilises probability theory in an online learning setting to drive the automatic heuristic selection process.
-As such, the \acs{BHH} was conceptualised.
+This research set out to develop a novel high-level heuristic that utilises probability theory in an online learning setting to drive the automatic heuristic selection process.
+A literature study was conducted on all related topics.
+A novel \acs{BHH} was proposed in detail.
+An empirical process was designed and the detail of the implementation for the empirical process and the \acs{BHH} was provided.
+The experiments defined for the empirical study was executed and results were statistically analysed.
 
-A literature study was conducted on all related topics that are relevant to the development of the \acs{BHH}.
-The literature study included background information on \acs{ANN}, existing low-level heuristics, meta-learning, \acp{HH}, probability theory, and Bayesian statistics.
-
-A novel \acs{BHH} that can be used to automate the heuristic selection process was proposed in detail and was implemented.
-The \acs{BHH} follows an approach that includes a selective and perturbative element in an online learning setting.
-Bayesian statistics and \acs{MAP} is used as the optimisation technique and detailed mathematical derivations of the optimisation process was provided.
-Detailed discussions were provided on the mapping of proxied heuristic state update operations.
-Finally, a \acs{BHH} baseline configuration was defined as a cornerstone reference for empirical analysis.
-
-An empirical process was designed and the detail of the implementation for the empirical process and the \acs{BHH} was provided.
-An empirical study was conducted to show that the \ac{BHH} is able to train \acp{FFNN} effectively on a number of different datasets.
-An empirical study was conducted to study the behavioural characteristics of the \acs{BHH}.
-An empirical study was conducted to critically evaluate the performance of the \acs{BHH} compared to traditional, low-level, standalone heuristic when training \acp{FFNN} on a number of different datasets.
-
-Results from the empirical process were statistically analysed over multiple runs and provided statistical significance.
-These results were discussed in detail and was supported through visual illustrations.
-
-\subsection{Summary of Results}
-\label{sec:conclusion:results}
-
-For the behavioural case study of the \acs{BHH} it was found that the \ac{BHH} is able to train a \acf{FFNN} relatively well.
+For the behavioural case study of the \acs{BHH} it was found that the \ac{BHH} is able to train a \acs{FFNN} relatively well.
 It was shown that the \ac{BHH} is able to learn and that the \acs{BHH} is able to exploit small performance biases as it relates to heuristic selection.
@@
 
-The main findings that were made for this experimental group are given as follows: Most of the training progression is made in the early stages of the training process.
-That leads to the conclusion that the \acs{BHH} has a small window from which it should learn and gain the most in the training process.
-After training has converged, the \acs{BHH} resets its concentration parameters and heuristic selection returns to the symmetric heuristic selection case.
-As such, the \acs{BHH} explores other heuristics in an attempt to further improve on the current best solution found.
-The test set was used as a validation set during training.
-Some overfitting can be observed as the \acs{BHH} tried finding better solutions on the train set, but at the cost of generalisation on the test set.
-Minor divergence of the training loss is observed as the \acs{BHH} explores other heuristics in an attempt to improve performance.
-Since no move-acceptance strategy, and no early stopping strategy was used, the \acs{BHH} could select heuristics that are sub-optimal.
-Future research opportunities should incorporate these aforementioned strategies.
-
-For the experimental group that compares the \acs{BHH} baseline with a number of  low-level heuristics, three different configurations of the \acs{BHH} baseline configuration were implemented.
-These configurations vary in the type of heuristics in the heuristic pool.
-
-Overall, the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen heuristics that were implemented and executed on fourteen datasets.
+For the experimental group that compares the \acs{BHH} baseline with a number of low-level heuristics, it was found that the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen heuristics that were implemented and executed on fourteen datasets.
 The \textit{bhh\_gd} configuration produced performance results close to that of the best low-level heuristics and was only statistically outperformed by the top two low-level heuristics.
@@
 Although the \acs{BHH} variants were not able to produce better results than the top low-level heuristics, the \acs{BHH} variants still effectively trained the underlying \acp{FFNN} and produced good training outcomes overall.
-
 It was shown that the \textit{bhh\_gd} configuration produced the lowest variance in rank between datasets out of all of the heuristics implemented, giving the \acs{BHH} the ability to generalise well to other problems.

### 2023-02-04 article/sections/06-bayesian-hyper-heuristics.tex
🚧 (article): Save point

@@
 
-The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $\boldsymbol{H}$, given allocation to entity $\boldsymbol{E}$ and credit requirement $\boldsymbol{C}$, parameterised by sampled $\boldsymbol{\theta} \vert \boldsymbol{\alpha} \sim Dir(\boldsymbol{\alpha}; K)$, $\boldsymbol{\phi} \vert \boldsymbol{\beta} \sim Dir(\boldsymbol{\beta}; K)^{J}$ and $\boldsymbol{\psi} \vert \gamma_{1}, \gamma_{0}  \sim Beta(\gamma_{1}, \gamma_{0})$.
-In the aforementioned, $K$ is the heuristic pool size, $J$ is the entity pool size and the indices $1$ and $0$ refers to success and failure parameters respectively.
+The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $\boldsymbol{H}$, given allocation to entity $\boldsymbol{E}$ and credit requirement $\boldsymbol{C}$, parameterised by sampled $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha}; K)$, $\boldsymbol{\phi} \sim Dir(\boldsymbol{\beta}; K)^{J}$ and $\boldsymbol{\psi} \sim Beta(\gamma_{1}, \gamma_{0})$.
+In the aforementioned, $K$ is the heuristic pool size and $J$ is the entity pool size.
 The concentration parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$ denote the prior beliefs of the \acs{BHH}.
@@
 
+where $N_{k}$ is a summary variable denoting the count of occurrences of heuristic $k$, $N_{j}$ is a summary variable denoting the count of occurrences of entity $j$, $N_{j,k}$ is a summary variable denoting the count of occurrences of heuristic $k$ for entity $j$, and $N_{1,k}$ is a summary variable denoting the count of occurrences of heuristic $k$ that meet performance requirements (credit assignment), and $N$ is a summary variable denoting the total count of events.
+
 \subsubsection{Maximum A Posteriori Estimation}\label{sec:bhh:optimisation_step:map}
@@
 Bayesian analysis makes use of the \textit{posterior} probability distribution.
-The concentration update operations yielded by \acs{MAP}, are then be given as
+The concentration update operations yielded by \acs{MAP}, are then be given as follows:
 
@@
 
-The following hyper-parameters are implemented by the \acs{BHH}: the \textit{heuristic pool} configures the type of heuristics included in the heuristic pool as gradient-only, meta-heuristic-only or all heuristics, the \textit{population size} specifies the number of entities in the entitiy pool, the \textit{credit assignment strategy} specifies which credit assignment strategy to use, the \textit{reselection interval} determines the frequency of heuristic reselection, the \textit{replay window size} determines the maximum size of the performance log, the \textit{reanalysis interval} determines the frequency at which Bayesian analysis is applied, the \textit{burn in window size} determines the size of an initial window where experience is simply gathered without reanalysis, and finally, \textit{discounted rewards} and \textit{normalisation} flags toggle scaling modifiers on the credit assignment strategies, backwards in the performance log.
+The following hyper-parameters are implemented by the \acs{BHH}: the \textit{heuristic pool} configures the type of heuristics included in the heuristic pool as gradient-only, meta-heuristic-only or all heuristics, the \textit{population size} specifies the number of entities in the entity pool, the \textit{credit assignment strategy} specifies which credit assignment strategy to use, the \textit{reselection interval} determines the frequency of heuristic reselection, the \textit{replay window size} determines the maximum size of the performance log, the \textit{reanalysis interval} determines the frequency at which Bayesian analysis is applied, the \textit{burn in window size} determines the size of an initial window where experience is simply gathered without reanalysis, and finally, \textit{discounted rewards} and \textit{normalisation} flags toggle scaling modifiers on values assigned by the credit assignment strategies, backwards in the performance log.

### 2023-02-04 article/sections/07-methodology.tex
🚧 (article): Save point

@@
 The \acs{BHH} baseline configuration is given in Table \ref{tab:methodology:bhh_baseline_configuration}.
-In Table \ref{tab:methodology:bhh_baseline_configuration}, the heuristic pool configuration, \textit{all}, refers to a configuration where the heuristic pool contains all the low-level heuristics including all gradient-based heuristics and \acp{MH}.
+In Table \ref{tab:methodology:bhh_baseline_configuration}, the heuristic pool configuration, \textit{all}, refers to a configuration where the heuristic pool contains all the low-level heuristics, including all gradient-based heuristics and \acp{MH}.
 
@@
 	\par\bigskip
-	\resizebox{0.65\textwidth}{!}{
+	\resizebox{0.70\textwidth}{!}{
 		\begin{tabular}{rrcc}
@@
 
+\begin{table}[htb]
+	\centering
+	\caption{Low-level heuristics and their hyper-parameter configurations.}
+	\label{tab:methodology:heuristics}%
+	\par\bigskip
+	\resizebox{0.7\textwidth}{!}{
+
+		\begin{tabular}{llll}
+			\textbf{heuristic} & \textbf{configuration}    & \textbf{value} & \textbf{citation}         \\
+			\midrule
+			sgd                & learning rate             & 0.1 (0.01)     & \cite{ref:sutskever:2013} \\
+			momentum           & learning rate             & 0.1 (0.01)     & \cite{ref:sutskever:2013} \\
+			                   & momentum                  & 0.9            &                           \\
+			nag                & learning rate             & 0.1 (0.01)     & \cite{ref:sutskever:2013} \\
+			                   & momentum                  & 0.9            &                           \\
+			adagrad            & learning rate             & 0.1 (0.01)     & \cite{ref:duchi:2011}     \\
+			                   & epsilon                   & 1E-07          &                           \\
+			rmsprop            & learning rate             & 0.1 (0.01)     & \cite{ref:hinton:2012}    \\
+			                   & rho                       & 0.95           &                           \\
+			                   & epsilon                   & 1E-07          &                           \\
+			adadelta           & learning rate             & 1.0 (0.95)     & \cite{ref:zeiler:2012}    \\
+			                   & rho                       & 0.95           &                           \\
+			                   & epsilon                   & 1E-07          &                           \\
+			adam               & learning rate             & 0.1 (0.01)     & \cite{ref:kingma:2014}    \\
+			                   & beta1                     & 0.9            &                           \\
+			                   & beta2                     & 0.999          &                           \\
+			                   & epsilon                   & 1E-07          &                           \\
+			pso                & population size           & 10             & \cite{ref:van:2010}       \\
+			                   & learning rate             & 1.0 (0.9)      &                           \\
+			                   & inertia weight (w)        & 0.729844       &                           \\
+			                   & cognitive control (c1)    & 1.49618        &                           \\
+			                   & social control (c2)       & 1.49618        &                           \\
+			                   & velocity clip min         & -1.0           &                           \\
+			                   & velocity clip max         & 1.0            &                           \\
+			de                 & population size           & 10             & \cite{ref:mezura:2006}    \\
+			                   & selection strategy        & best           &                           \\
+			                   & xo strategy               & exp            &                           \\
+			                   & recombination probability & 0.9 (0.1)      &                           \\
+			                   & beta                      & 2.0 (0.1)      &                           \\
+			ga                 & population size           & 10             & \cite{ref:lambora:2019}   \\
+			                   & selection strategy        & rand           &                           \\
+			                   & xo strategy               & bin            &                           \\
+			                   & mutation rate             & 0.2 (0.05)     &                           \\
+		\end{tabular}%
+	}
+\end{table}%
+
 The mapping of proxied heuristic state update operations implemented by the \acs{BHH} in the empirical process is given in Figure \ref{fig:methodology:heuristics:proxies}.
 In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x} indicate that the associated heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.8\textwidth]{images/bhh_heuristic_proxies.pdf}
+	\caption{Mapping of proxied heuristic state update operations as implemented by the \acs{BHH}}
+	\label{fig:methodology:heuristics:proxies}%
+\end{figure}
 
@@
 
+\begin{table}[htb]
+	\centering
+	\caption{Classification datasets}
+	\label{tab:methodology:datasets:classification}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{ccccccccc}
+			\textbf{dataset} & \textbf{output} & \textbf{types}             & \textbf{attributes} & \textbf{classes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}         \\
+			\midrule
+			iris             & multivariate    & real                       & 4                   & 3                & 150                & 16             & 10             & \cite{ref:fisher:1936}    \\
+			car              & multivariate    & categorical                & 6                   & 4                & 1728               & 128            & 14             & \cite{ref:bohanec:1988}   \\
+			abalone          & multivariate    & categorical, integer, real & 8                   & 28               & 4177               & 256            & 17             & \cite{ref:waugh:1995}     \\
+			wine quality     & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & \cite{ref:cortez:2009}    \\
+			mushroom         & multivariate    & categorical                & 22                  & 2                & 8214               & 512            & 17             & \cite{ref:schlimmer:1987} \\
+			bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & \cite{ref:moro:2014}      \\
+			diabetic         & multivariate    & integer                    & 55                  & 3                & 100000             & 1024           & 98             & \cite{ref:strack:2014}    \\
+		\end{tabular}%
+	}
+\end{table}%
+
+\begin{table}[htb]
+	\centering
+	\caption{Regression datasets}
+	\label{tab:methodology:datasets:regression}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{cccccccc}
+			\textbf{dataset}    & \textbf{output}           & \textbf{types} & \textbf{attributes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}        \\
+			\midrule
+			fish toxicity       & multivariate              & real           & 7                   & 908                & 64             & 15             & \cite{ref:cassotti:2015} \\
+			housing             & univariate                & real           & 13                  & 506                & 32             & 16             & \cite{ref:harrison:1978} \\
+			forest fires        & multivariate              & real           & 13                  & 517                & 32             & 17             & \cite{ref:cortez:2007}   \\
+			student performance & multivariate              & integer        & 33                  & 649                & 32             & 21             & \cite{ref:cortez:2008}   \\
+			parkinsons          & multivariate              & integer, real  & 26                  & 5875               & 256            & 23             & \cite{ref:tsanas:2009}   \\
+			air quality         & multivariate, time series & real           & 15                  & 9358               & 256            & 37             & \cite{ref:de:2008}       \\
+			bike                & univariate                & integer, real  & 16                  & 17389              & 256            & 68             & \cite{ref:fanaee:2014}   \\
+		\end{tabular}%
+	}
+\end{table}%
+
 \subsection{Models}\label{sec:methodology:model}
@@
 The number of hidden units used were determined empirically.
-Weights are initialised by means of Glorot uniform sampling \cite{ref:glorot:2010}.
+Weights are initialised by means of \textit{Glorot uniform sampling} \cite{ref:glorot:2010}.
 The models and their configuration, as it is used for each dataset, are given in Table \ref{tab:methodology:models:configurations}.
+
+\begin{table}[htb]
+	\centering
+	\caption{Model configurations}
+	\label{tab:methodology:models:configurations}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{rcccccccc}
+			\textbf{dataset}    & \textbf{inputs} & \textbf{hidden} & \textbf{output} & \textbf{biases} & \textbf{parameters} & \textbf{topology} & \textbf{l1 activation} & \textbf{l2 activation} \\
+			\midrule
+			fish toxicity       & 6               & 3               & 1               & yes             & 25                  & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			iris                & 4               & 5               & 3               & yes             & 43                  & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			air quality         & 12              & 8               & 1               & yes             & 113                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			housing             & 13              & 8               & 1               & yes             & 121                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			wine quality        & 13              & 10              & 7               & yes             & 217                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			parkinsons          & 21              & 10              & 1               & yes             & 231                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			car                 & 21              & 10              & 4               & yes             & 264                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			forest fires        & 43              & 16              & 1               & yes             & 721                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			abalone             & 10              & 36              & 28              & yes             & 1432                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			bank                & 51              & 32              & 1               & yes             & 1697                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			bike                & 61              & 32              & 1               & yes             & 2017                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			student performance & 99              & 32              & 1               & yes             & 3233                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			adult               & 108             & 64              & 1               & yes             & 7041                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			mushroom            & 117             & 64              & 1               & yes             & 7617                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			diabetic            & 2369            & 32              & 3               & yes             & 75939               & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+		\end{tabular}%
+	}
+\end{table}%
 
@@
 
-\acs{BinXE} is used for classification problems with two classes and \acs{SparseCatXE} is used for classification problems with more than two classes.
+\Acf{BinXE} is used for classification problems with two classes and \acf{SparseCatXE} is used for classification problems with more than two classes.
 For the classification problems, accuracy is also measured.
-For regression problems, the \acs{MSE} is used as a performance metric.
+For regression problems, the \acf{MSE} is used as a performance metric.
 After training has been completed, the \textit{average rank}, based on test loss, for all configurations, is calculated at each mini-batch step.
@@
 Each experiment and configuration is trained for a maximum of 30 epochs and is repeated over 30 independent runs, for each of the applicable datasets.
-Statistical analysis is executed on the results from the testing datasets.
+No early-stopping mechanism is used.
+Statistical analysis is executed on the results from the test datasets.
 An average rank is calculated across all 30 runs, for both experimental groups and configurations, at each step, for every epoch of training.
@@
 
-\subsection{Implementation and Execution}\label{sec:methodology:implementation}
+\subsection{Implementation}\label{sec:methodology:implementation}
 

### 2023-02-04 article/sections/08-results.tex
🚧 (article): Save point

@@
 
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing normalised average rank and statistics for the top six low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:standalone:metrics:rank_a}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccc|c|c|c|}
+			                              & \multicolumn{6}{c|}{\textbf{BHH vs.
+Low-Level Heuristics - Average Rank (Part A)}}                                                                                                                                                                                                                                                                                                   \\
+			\midrule
+			\textbf{dataset}              & \textbf{adagrad}                                                                   & \textbf{adam}                                           & \textbf{rmsprop}                                        & \textbf{bhh\_gd}                                        & \textbf{nag}                                            & \textbf{bhh\_all}                                       \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .388,  .745,  .482}2,2215 ($\pm$1,591)                            & \cellcolor[rgb]{ .416,  .753,  .482}2,3989 ($\pm$1,887) & \cellcolor[rgb]{ .78,  .859,  .502}4,6172 ($\pm$2,65)   & \cellcolor[rgb]{ .796,  .863,  .506}4,7032 ($\pm$2,108) & \cellcolor[rgb]{ .725,  .839,  .498}4,2731 ($\pm$1,542) & \cellcolor[rgb]{ 1,  .922,  .518}5,9376 ($\pm$2,399)    \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3,6409 ($\pm$2,259)                            & \cellcolor[rgb]{ .804,  .863,  .506}5,4312 ($\pm$2,62)  & \cellcolor[rgb]{ .388,  .745,  .482}3,4452 ($\pm$2,57)  & \cellcolor[rgb]{ .729,  .843,  .502}5,0817 ($\pm$2,762) & \cellcolor[rgb]{ .467,  .765,  .486}3,8194 ($\pm$2,229) & \cellcolor[rgb]{ 1,  .894,  .514}6,686 ($\pm$3,061)     \\
+			\textbf{bank}                 & \cellcolor[rgb]{ .455,  .765,  .486}2,5495 ($\pm$1,598)                            & \cellcolor[rgb]{ .388,  .745,  .482}2,0796 ($\pm$1,587) & \cellcolor[rgb]{ .588,  .8,  .49}3,4645 ($\pm$2,209)    & \cellcolor[rgb]{ .8,  .863,  .506}4,8828 ($\pm$1,702)   & \cellcolor[rgb]{ .71,  .835,  .498}4,2871 ($\pm$1,732)  & \cellcolor[rgb]{ 1,  .922,  .518}6,2419 ($\pm$2,157)    \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .388,  .745,  .482}1,7204 ($\pm$1,384)                            & \cellcolor[rgb]{ .643,  .816,  .494}3,6925 ($\pm$4,004) & \cellcolor[rgb]{ .973,  .914,  .514}6,2624 ($\pm$4,58)  & \cellcolor[rgb]{ .663,  .824,  .498}3,8441 ($\pm$1,398) & \cellcolor[rgb]{ 1,  .922,  .518}6,4516 ($\pm$1,02)     & \cellcolor[rgb]{ .71,  .835,  .498}4,2151 ($\pm$1,361)  \\
+			\textbf{car}                  & \cellcolor[rgb]{ .702,  .835,  .498}4,7634 ($\pm$0,938)                            & \cellcolor[rgb]{ .388,  .745,  .482}1,6226 ($\pm$1,405) & \cellcolor[rgb]{ .455,  .765,  .486}2,3269 ($\pm$1,409) & \cellcolor[rgb]{ .561,  .792,  .49}3,3473 ($\pm$1,35)   & \cellcolor[rgb]{ .831,  .871,  .506}6,0785 ($\pm$0,799) & \cellcolor[rgb]{ .58,  .8,  .49}3,5624 ($\pm$1,315)     \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .506,  .776,  .486}2,7796 ($\pm$1,659)                            & \cellcolor[rgb]{ 1,  .886,  .514}7,1484 ($\pm$2,227)    & \cellcolor[rgb]{ 1,  .922,  .518}6,7376 ($\pm$2,577)    & \cellcolor[rgb]{ .812,  .867,  .506}5,2269 ($\pm$2,186) & \cellcolor[rgb]{ .388,  .745,  .482}1,8118 ($\pm$1,413) & \cellcolor[rgb]{ .988,  .69,  .475}9,3968 ($\pm$3,022)  \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4,2645 ($\pm$2,614)                             & \cellcolor[rgb]{ .388,  .745,  .482}3,6022 ($\pm$2,445) & \cellcolor[rgb]{ .388,  .745,  .482}3,5946 ($\pm$2,329) & \cellcolor[rgb]{ .784,  .859,  .502}5,4118 ($\pm$2,665) & \cellcolor[rgb]{ .89,  .89,  .51}5,8914 ($\pm$2,629)    & \cellcolor[rgb]{ .875,  .886,  .51}5,829 ($\pm$2,856)   \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5,1559 ($\pm$2,922)                            & \cellcolor[rgb]{ .388,  .745,  .482}4,2688 ($\pm$2,984) & \cellcolor[rgb]{ .718,  .839,  .498}5,0355 ($\pm$3,143) & \cellcolor[rgb]{ .569,  .796,  .49}4,6935 ($\pm$2,759)  & \cellcolor[rgb]{ 1,  .922,  .518}5,6882 ($\pm$2,215)    & \cellcolor[rgb]{ .91,  .894,  .51}5,4839 ($\pm$3,107)   \\
+			\textbf{housing}              & \cellcolor[rgb]{ .404,  .749,  .482}3,4484 ($\pm$2,025)                            & \cellcolor[rgb]{ .388,  .745,  .482}3,3344 ($\pm$1,819) & \cellcolor[rgb]{ .439,  .757,  .482}3,6946 ($\pm$2,166) & \cellcolor[rgb]{ .553,  .792,  .49}4,4742 ($\pm$2,312)  & \cellcolor[rgb]{ .584,  .8,  .49}4,6839 ($\pm$2,658)    & \cellcolor[rgb]{ .537,  .788,  .49}4,3763 ($\pm$2,438)  \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .965,  .91,  .514}6,3946 ($\pm$1,6)                               & \cellcolor[rgb]{ .525,  .784,  .49}3,5839 ($\pm$2,511)  & \cellcolor[rgb]{ .388,  .745,  .482}2,6968 ($\pm$1,912) & \cellcolor[rgb]{ .706,  .835,  .498}4,7473 ($\pm$2,275) & \cellcolor[rgb]{ .522,  .78,  .486}3,5548 ($\pm$2,125)  & \cellcolor[rgb]{ .78,  .859,  .502}5,2204 ($\pm$3,041)  \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ .71,  .835,  .498}4,4656 ($\pm$1,053)                             & \cellcolor[rgb]{ .388,  .745,  .482}2,1344 ($\pm$1,883) & \cellcolor[rgb]{ .431,  .757,  .482}2,4656 ($\pm$1,359) & \cellcolor[rgb]{ .569,  .796,  .49}3,4484 ($\pm$1,602)  & \cellcolor[rgb]{ .969,  .91,  .514}6,3323 ($\pm$0,891)  & \cellcolor[rgb]{ .6,  .804,  .494}3,6688 ($\pm$2,469)   \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .412,  .749,  .482}2,4677 ($\pm$1,497)                            & \cellcolor[rgb]{ .388,  .745,  .482}2,2333 ($\pm$1,742) & \cellcolor[rgb]{ .541,  .788,  .49}3,5656 ($\pm$2,492)  & \cellcolor[rgb]{ .655,  .82,  .494}4,572 ($\pm$1,934)   & \cellcolor[rgb]{ 1,  .922,  .518}7,5355 ($\pm$1,44)     & \cellcolor[rgb]{ .635,  .816,  .494}4,3839 ($\pm$1,861) \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2,5634 ($\pm$1,912)                            & \cellcolor[rgb]{ .98,  .506,  .439}11,3978 ($\pm$2,178) & \cellcolor[rgb]{ .973,  .412,  .42}12,4312 ($\pm$1,34)  & \cellcolor[rgb]{ .843,  .875,  .506}5,6624 ($\pm$3,57)  & \cellcolor[rgb]{ .478,  .769,  .486}3,1935 ($\pm$2,12)  & \cellcolor[rgb]{ .875,  .882,  .51}5,8634 ($\pm$3,159)  \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3,2806 ($\pm$1,931)                             & \cellcolor[rgb]{ .388,  .745,  .482}2,1118 ($\pm$1,666) & \cellcolor[rgb]{ .624,  .812,  .494}3,6301 ($\pm$1,731) & \cellcolor[rgb]{ .808,  .863,  .506}4,7882 ($\pm$2,105) & \cellcolor[rgb]{ .706,  .835,  .498}4,1505 ($\pm$1,916) & \cellcolor[rgb]{ .871,  .882,  .51}5,1925 ($\pm$1,951)  \\
+			\midrule
+			\textbf{avg rank}             & \cellcolor[rgb]{ .388,  .745,  .482}3,5512 ($\pm$2,25)                             & \cellcolor[rgb]{ .471,  .769,  .486}3,9314 ($\pm$3,423) & \cellcolor[rgb]{ .616,  .808,  .494}4,5691 ($\pm$3,517) & \cellcolor[rgb]{ .631,  .812,  .494}4,6346 ($\pm$2,364) & \cellcolor[rgb]{ .675,  .827,  .498}4,8394 ($\pm$2,384) & \cellcolor[rgb]{ .808,  .867,  .506}5,4327 ($\pm$2,9)   \\
+			\midrule
+			\textbf{normalised avg rank}  & \cellcolor[rgb]{ .388,  .745,  .482}1                                              & \cellcolor[rgb]{ .49,  .773,  .486}2                    & \cellcolor[rgb]{ .592,  .804,  .494}3                   & \cellcolor[rgb]{ .694,  .831,  .498}4                   & \cellcolor[rgb]{ .796,  .863,  .506}5                   & \cellcolor[rgb]{ .898,  .89,  .51}6                     \\
+			\cmidrule{5-5}\cmidrule{7-7}\end{tabular}%
+	}
+\end{table}%
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing normalised average rank and statistics for the bottom six low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:standalone:metrics:rank_b}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|c|c|ccccc|}
+			                              & \multicolumn{7}{c}{\textbf{BHH vs.
+Low-Level Heuristics - Average Rank (Part B)}}                                                                                                                                                                                                                                                                                                                                                                  \\
+			\midrule
+			\textbf{dataset}              & \textbf{adadelta}                                                                 & \textbf{bhh\_mh}                                        & \textbf{ga}                                              & \textbf{pso}                                             & \textbf{sgd}                                             & \textbf{momentum}                                        & \textbf{de}                                              \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .894,  .89,  .51}5,3129 ($\pm$1,478)                             & \cellcolor[rgb]{ .992,  .749,  .486}8,1882 ($\pm$1,195) & \cellcolor[rgb]{ .98,  .525,  .443}11,1108 ($\pm$1,102)  & \cellcolor[rgb]{ .98,  .514,  .439}11,2559 ($\pm$1,826)  & \cellcolor[rgb]{ .992,  .718,  .478}8,628 ($\pm$1,019)   & \cellcolor[rgb]{ .984,  .624,  .463}9,8151 ($\pm$1,16)   & \cellcolor[rgb]{ .973,  .412,  .42}12,5376 ($\pm$1,329)  \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ .765,  .851,  .502}5,2441 ($\pm$3,162)                           & \cellcolor[rgb]{ 1,  .922,  .518}6,357 ($\pm$2,303)     & \cellcolor[rgb]{ .996,  .784,  .494}7,8204 ($\pm$2,265)  & \cellcolor[rgb]{ .984,  .588,  .455}9,9151 ($\pm$2,288)  & \cellcolor[rgb]{ .98,  .518,  .443}10,6613 ($\pm$1,606)  & \cellcolor[rgb]{ .973,  .412,  .42}11,7559 ($\pm$1,473)  & \cellcolor[rgb]{ .976,  .471,  .431}11,1419 ($\pm$2,236) \\
+			\textbf{bank}                 & \cellcolor[rgb]{ .914,  .894,  .51}5,672 ($\pm$1,241)                             & \cellcolor[rgb]{ .988,  .639,  .463}9,7495 ($\pm$1,048) & \cellcolor[rgb]{ .98,  .537,  .447}10,9817 ($\pm$1,216)  & \cellcolor[rgb]{ .976,  .467,  .431}11,8376 ($\pm$1,464) & \cellcolor[rgb]{ .992,  .757,  .486}8,2774 ($\pm$1,03)   & \cellcolor[rgb]{ .992,  .741,  .486}8,4774 ($\pm$1,068)  & \cellcolor[rgb]{ .973,  .412,  .42}12,4989 ($\pm$1,224)  \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .859,  .878,  .506}5,3602 ($\pm$1,155)                           & \cellcolor[rgb]{ .996,  .843,  .506}7,4108 ($\pm$1,008) & \cellcolor[rgb]{ .988,  .686,  .475}9,2269 ($\pm$1,183)  & \cellcolor[rgb]{ .988,  .682,  .475}9,3086 ($\pm$1,761)  & \cellcolor[rgb]{ .984,  .596,  .455}10,3355 ($\pm$1,419) & \cellcolor[rgb]{ .984,  .561,  .451}10,7086 ($\pm$1,423) & \cellcolor[rgb]{ .973,  .412,  .42}12,4634 ($\pm$1,465)  \\
+			\textbf{car}                  & \cellcolor[rgb]{ 1,  .922,  .518}7,7344 ($\pm$1,746)                              & \cellcolor[rgb]{ .996,  .8,  .498}8,8505 ($\pm$1,413)   & \cellcolor[rgb]{ .984,  .592,  .455}10,7763 ($\pm$1,471) & \cellcolor[rgb]{ 1,  .855,  .506}8,3613 ($\pm$1,622)     & \cellcolor[rgb]{ .988,  .651,  .467}10,2452 ($\pm$1,447) & \cellcolor[rgb]{ .984,  .576,  .451}10,9226 ($\pm$1,349) & \cellcolor[rgb]{ .973,  .412,  .42}12,4086 ($\pm$1,492)  \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .494,  .773,  .486}2,6753 ($\pm$1,629)                           & \cellcolor[rgb]{ .992,  .765,  .49}8,557 ($\pm$1,17)    & \cellcolor[rgb]{ .98,  .529,  .443}11,2011 ($\pm$1,413)  & \cellcolor[rgb]{ .984,  .573,  .451}10,7022 ($\pm$1,067) & \cellcolor[rgb]{ .898,  .89,  .51}5,9215 ($\pm$1,542)    & \cellcolor[rgb]{ .949,  .906,  .514}6,3355 ($\pm$1,612)  & \cellcolor[rgb]{ .973,  .412,  .42}12,5065 ($\pm$1,242)  \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .996,  .788,  .494}7,914 ($\pm$3,429)                            & \cellcolor[rgb]{ 1,  .922,  .518}6,3849 ($\pm$2,944)    & \cellcolor[rgb]{ 1,  .894,  .514}6,7043 ($\pm$2,82)      & \cellcolor[rgb]{ .996,  .82,  .498}7,5731 ($\pm$2,982)   & \cellcolor[rgb]{ .976,  .471,  .431}11,5785 ($\pm$1,459) & \cellcolor[rgb]{ .973,  .412,  .42}12,2301 ($\pm$1,382)  & \cellcolor[rgb]{ .984,  .608,  .459}10,0215 ($\pm$2,358) \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ 1,  .859,  .506}6,5161 ($\pm$3,082)                              & \cellcolor[rgb]{ .898,  .89,  .51}5,4591 ($\pm$2,668)   & \cellcolor[rgb]{ .996,  .796,  .494}7,3667 ($\pm$2,37)   & \cellcolor[rgb]{ 1,  .863,  .51}6,4796 ($\pm$3,354)      & \cellcolor[rgb]{ .98,  .529,  .443}10,8129 ($\pm$1,207)  & \cellcolor[rgb]{ .976,  .463,  .431}11,7065 ($\pm$1,325) & \cellcolor[rgb]{ .973,  .412,  .42}12,3333 ($\pm$1,923)  \\
+			\textbf{housing}              & \cellcolor[rgb]{ 1,  .918,  .518}7,5903 ($\pm$2,748)                              & \cellcolor[rgb]{ 1,  .922,  .518}7,5441 ($\pm$1,736)    & \cellcolor[rgb]{ 1,  .878,  .51}7,8839 ($\pm$2,099)      & \cellcolor[rgb]{ .984,  .608,  .459}9,9409 ($\pm$2,317)  & \cellcolor[rgb]{ .973,  .412,  .42}11,4075 ($\pm$1,528)  & \cellcolor[rgb]{ .976,  .431,  .424}11,2731 ($\pm$1,506) & \cellcolor[rgb]{ .976,  .42,  .424}11,3484 ($\pm$2,096)  \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .973,  .412,  .42}11,3527 ($\pm$1,779)                           & \cellcolor[rgb]{ 1,  .922,  .518}6,6075 ($\pm$2,555)    & \cellcolor[rgb]{ .992,  .749,  .486}8,2473 ($\pm$1,765)  & \cellcolor[rgb]{ .992,  .745,  .486}8,2731 ($\pm$4,384)  & \cellcolor[rgb]{ .98,  .518,  .443}10,3796 ($\pm$1,294)  & \cellcolor[rgb]{ .976,  .447,  .427}11,0548 ($\pm$1,409) & \cellcolor[rgb]{ .988,  .678,  .471}8,8871 ($\pm$3,251)  \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ 1,  .922,  .518}6,5538 ($\pm$1,071)                              & \cellcolor[rgb]{ .992,  .718,  .478}9,0452 ($\pm$1,093) & \cellcolor[rgb]{ .98,  .51,  .439}11,5731 ($\pm$1,193)   & \cellcolor[rgb]{ .996,  .816,  .498}7,872 ($\pm$0,92)    & \cellcolor[rgb]{ .988,  .659,  .471}9,7527 ($\pm$1,083)  & \cellcolor[rgb]{ .98,  .557,  .451}10,9785 ($\pm$1,108)  & \cellcolor[rgb]{ .973,  .412,  .42}12,7097 ($\pm$1,478)  \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .875,  .882,  .51}6,472 ($\pm$2,423)                             & \cellcolor[rgb]{ .996,  .843,  .506}8,3161 ($\pm$1,644) & \cellcolor[rgb]{ 1,  .898,  .514}7,7968 ($\pm$1,719)     & \cellcolor[rgb]{ .996,  .827,  .502}8,4892 ($\pm$1,901)  & \cellcolor[rgb]{ .98,  .494,  .435}11,7516 ($\pm$1,155)  & \cellcolor[rgb]{ .973,  .412,  .42}12,5419 ($\pm$1,351)  & \cellcolor[rgb]{ .984,  .584,  .455}10,8742 ($\pm$1,317) \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .514,  .78,  .486}3,4194 ($\pm$2,006)                            & \cellcolor[rgb]{ 1,  .902,  .514}6,9333 ($\pm$2,44)     & \cellcolor[rgb]{ 1,  .886,  .514}7,1032 ($\pm$1,989)     & \cellcolor[rgb]{ .98,  .537,  .443}11,0624 ($\pm$1,067)  & \cellcolor[rgb]{ .988,  .918,  .514}6,6366 ($\pm$2,023)  & \cellcolor[rgb]{ 1,  .922,  .518}6,7011 ($\pm$2,242)     & \cellcolor[rgb]{ .996,  .804,  .498}8,0323 ($\pm$1,935)  \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ 1,  .922,  .518}6,0011 ($\pm$2,404)                              & \cellcolor[rgb]{ .988,  .647,  .467}9,5935 ($\pm$1,494) & \cellcolor[rgb]{ .984,  .588,  .455}10,3387 ($\pm$1,62)  & \cellcolor[rgb]{ .98,  .525,  .443}11,1602 ($\pm$1,773)  & \cellcolor[rgb]{ .992,  .722,  .482}8,6344 ($\pm$1,18)   & \cellcolor[rgb]{ .988,  .651,  .467}9,5269 ($\pm$1,341)  & \cellcolor[rgb]{ .973,  .412,  .42}12,5903 ($\pm$1,352)  \\
+			\midrule
+			\textbf{avg rank}             & \cellcolor[rgb]{ 1,  .922,  .518}6,2727 ($\pm$3,004)                              & \cellcolor[rgb]{ .992,  .776,  .49}7,7855 ($\pm$2,271)  & \cellcolor[rgb]{ .988,  .639,  .467}9,1522 ($\pm$2,48)   & \cellcolor[rgb]{ .984,  .612,  .459}9,4451 ($\pm$2,75)   & \cellcolor[rgb]{ .984,  .592,  .455}9,6445 ($\pm$2,214)  & \cellcolor[rgb]{ .98,  .529,  .443}10,2877 ($\pm$2,346)  & \cellcolor[rgb]{ .973,  .412,  .42}11,4538 ($\pm$2,354)  \\
+			\midrule
+			\textbf{normalised avg rank}  & \cellcolor[rgb]{ 1,  .922,  .518}7                                                & \cellcolor[rgb]{ .996,  .839,  .502}8                   & \cellcolor[rgb]{ .992,  .753,  .486}9                    & \cellcolor[rgb]{ .988,  .667,  .471}10                   & \cellcolor[rgb]{ .984,  .584,  .455}11                   & \cellcolor[rgb]{ .98,  .498,  .439}12                    & \cellcolor[rgb]{ .973,  .412,  .42}13                    \\
+			\cmidrule{3-3}\end{tabular}%
+	}
+\end{table}%
+
 From the normalised average ranks provided in Table \ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen heuristic implementations respectively.

### 2023-02-05 article/sections/08-results.tex
🚧 (article): Finalisation before review

@@
 
-This section provides the results of all the experiments that have been conducted.
+This section provides the results of the experimental groups that have been conducted.
 Detailed discussions follow on the outcomes of each experiment.
 Discussions are accompanied by figures and plots to help provide visual aid for discussions.
+Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.
 
@@
 
-This section provides a brief discussion on the general outcome of the empirical process as a whole.
-Overall, the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets.
-In general, the \acs{BHH} performs well and the empirical process provides key insights into the workings of the \acs{BHH}.
-Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.
+This section provides a brief discussion on the general outcome of the empirical process as a whole and identifies some key aspects to be kept in mind when interpreting the results of the experiments.
 
-The \acs{BHH} applies a form of online learning.
+Firstly, the \acs{BHH} applies a form of online learning.
 As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process.
-The training process is not repeated iteratively.
-All experiments conducted are executed for 30 epochs.
+The training process is not repeated iteratively as is the case with some \acp{HH}.
 
@@
 
-The \acs{BHH} does not implement a move-acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution.
-In some cases the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.
+The \acs{BHH} does not implement a type of move-acceptance strategy where the application of a heuristic to an entity is only accepted if it leads to a better solution.
+In some cases, the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.
 
@@
 
-The \textit{reanalysis interval} defines intervals at which the \acs{BHH} reanalyses the performance log, in effect, resetting the concentration parameters to their default values and reapplying the underlying Bayesian analysis process on the performance log.
-Furthermore, the \textit{replay window size} defines the amount of performance evidence in the performance log.
 By default, the \acs{BHH} baseline configuration has a reanalysis interval of 10, and a replay window size of 10, which is a small window to learn from.
@@
 
-This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}.
-Figures \ref{fig:results:case_study:metrics:train_loss} to \ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
+This section provides the results for the behavioural case study on the \acs{BHH}. The first point of interest is to determine if the \acs{BHH} is able to successfully train the underlying \acs{FFNN}.
 
-\begin{figure}[htb]
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 
+Figures \ref{fig:results:case_study:metrics:train_loss} to \ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
+
 The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}, observed by the convergence of the training process, yielding good results.
@@
 
-\begin{figure}[htb]
+To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
+This can be achieved by analysing the outcomes of the change in concentration parameters and the probabilitiy distributions implemented by the \acs{BHH}.
+Figures \ref{fig:results:case_study:alphas:6} to \ref{fig:results:case_study:p_HgEC:0:6} provide illustrations of the change in concentration parameter, $\boldsymbol{\alpha}$ and the effect is has on the probability distributions of heuristic selection probabilities, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, the prior heuristic selection probability distribution, denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, and the posterior heuristic selection probability distribution, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$.
+These illustrations represent an example heuristic, \acs{Adam}, and an example entity, identified by index 6 and 0 respectively in the heuristic and entity pools.
+The illustrations are obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
+Similar illustrations for the rest of the concentration parameters and probability distributions are left out for brevity as they contain similar illustrations.
+The following sections provide interpretations of each of these concepts.
+
+\begin{figure}[H]
 	\begin{subfigure}{0.5\textwidth}
@@
 	\par\bigskip
-	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+	\caption{Illustrations of the change in concentration parameter and probability distributions for an example heuristic, \acs{Adam} (index 6), and an example entity (index 0), in the heuristic and entity pools.}
 	\label{fig:results:case_study}
@@
 
-To illustrate the learning process undergone by the \acs{BHH}, further investigation is required.
-Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
+\subsubsection{Alphas}\label{sec:results:case_study:alphas}
+
+The concentration parameter $\boldsymbol{\alpha}$ parameterises the Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
 The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{heuristic selection probabilities}.
-Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
-Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the heuristic pool.
-Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.
 
-The first logical observation to be made from Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
+The first logical observation to be made from Figure \ref{fig:results:case_study:alphas:6} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}.
 Since the replay window size is sufficiently large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all.
 The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process.
-However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$.
 
@@
 
-Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning.
+It is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning.
 The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$).
@@
 
+\subsubsection{Probability Distribution of Heuristic Selection Probabilities}\label{sec:results:case_study:probabilities_of_probabilities}
+
 The probability distribution of heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.
+From the illustration presented in Figure \ref{fig:results:case_study:thetas:6}, a clearer picture of the learning process of the \acs{BHH} is formed.
 
-Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs.
-These illustrations are presented in log scale.
-Indices 0, 6, 7, and 8 represent the distribution of heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the distribution of heuristic selection probabilities in $\boldsymbol{\theta}$.
-Similar illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.
-
-From the illustrations presented in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed.
 The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}.
 As a reminder, ten low-level heuristics are included in the heuristic pool, yielding an expected mean heuristics selection probability of 0.1, for each heuristic, by the frequentist view of probabilistic modelling.
-
 Towards the end of the training process, the heuristic selection probability converges back to the symmetrical, uniform probability distribution, yielding a heuristic selection probability of 0.1, for all heuristics.
@@
 
+\subsubsection{Prior Heuristic Selection Probabilities}\label{sec:results:case_study:priors}
+
 The prior heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.
 As such, $P(\boldsymbol{H} \vert \boldsymbol{\theta}) = \boldsymbol{\theta}$ and heuristics are initially sampled such that $\boldsymbol{H} \sim Cat(\boldsymbol{\theta})$.
+Figure \ref{fig:results:case_study:p_H:6} provide an illustrations of the prior heuristic selection probabilities for \acs{Adam} throughout the training process.
 
-Figures \ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
-Similar to before, these illustrations are also presented in log scale.
-
-The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section in Figure \ref{fig:results:case_study:thetas}.
+The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the distribution of heuristic selection probabilities, $\boldsymbol{\theta}$, presented in the previous section.
 This is because of the \textit{reselection} interval hyper-parameter.
@@
 Since the default \textit{reselection} interval is set to 10, the heuristic selection probabilities are only resampled at intervals of 10.
-These illustrations then simply yield rough approximations of the illustrations provided in Figures \ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the distribution of heuristic selection probabilities.
-As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.
+This illustration then simply yield rough approximation of the illustration provided in Figure \ref{fig:results:case_study:thetas:6}.
+As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probabilities_of_probabilities} also apply in this section.
 
@@
 
-The posterior heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy.
-Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of heuristic selection probabilities and the entity selection probabilities respectively.
-Finally, $\boldsymbol{\psi}$ represents the probability distribution of successful credit allocation probabilities.
+\subsubsection{Posterior Heuristic Selection Probabilities}\label{sec:results:case_study:posteriors}
 
-Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs.
-Similar to before, these illustrations are also presented in log scale.
-As before, illustrations for the other indices are left out for brevity as they yield similar illustrations.
+The posterior heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$.
+Figure \ref{fig:results:case_study:p_HgEC:0:6} provides an illustration of the calculated posterior heuristic selection probabilities implemented by the \acs{BHH}.
 
-The main observation to make from Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a Categorical probability distribution from which new heuristic selections are sampled.
+The main observation to make from Figure \ref{fig:results:case_study:p_HgEC:0:6} is that the implemented posterior heuristic selection distribution does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a Categorical probability distribution from which new heuristic selections are sampled.
 The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Section \ref{sec:bhh}.
-As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
+Furthermpre, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
 
 Another observation to make is for the bhh\_replay\_250 configuration $(\textcolor{green}{green})$.
-Figures \ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} show that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities later in the training stages.
+Figure \ref{fig:results:case_study:p_HgEC:0:6} show that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities later in the training stages.
 The aforementioned suggests that the \acs{BHH} is not able to find further performance biases and cannot exploit better solutions.
@@
 
-It can be concluded from Sections \ref{sec:results:case_study:performance_metrics} to \ref{sec:results:case_study:posterior_selec_prob} that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset.
+It can be concluded that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset.
 Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases, and thus the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.
@@
 This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics.
-Detailed discussions and illustrations follow.
-As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of \acp{MH}.
 Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a heuristic pool that contains only gradient-based heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a heuristics pool that contains only \acp{MH} (denoted bhh\_mh).
 
-Table \ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented.
-The test loss is measured at the last epoch for each dataset, over all independent runs.
-
-Table \ref{tab:results:standalone:metrics:loss} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
-The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the heuristics.
-
-Table \ref{tab:results:standalone:metrics:rank} provides the empirical results from Table \ref{tab:results:standalone:metrics:loss} in ranked format.
+Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b} provides the empirical results in ranked format.
 The performance rank is calculated as the average rank produced by each heuristic, across all datasets, for all independent runs and all epochs.
@@
 The normalised average rank is calculated as a discrete normalisation of the average rank achieved across all datasets, for all independent runs and epochs.
+
+Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
+The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the heuristics.
 
@@
 
-From the normalised average ranks provided in Table \ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen heuristic implementations respectively.
+From the normalised average ranks provided in Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen heuristic implementations respectively.
 These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.
@@
 Figure \ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each heuristic, per dataset.
-The heuristics are ordered according to the normalised ranks presented in Table \ref{tab:results:standalone:metrics:rank}.
+The heuristics are ordered according to the normalised ranks presented in Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b}.
 
@@
 
-From Figure \ref{fig:results:standalone:descriptive:descriptive} a few observations can be made.
-Firstly, both \acs{Adam} and \acs{RMSProp} achieved radically different average ranks for the student performance dataset, compared to the other datasets.
-This can also be seen in Table \ref{tab:results:standalone:metrics:rank}.
-Further investigation into the reasons for this is required as both these heuristics perform well on all other datasets, and the other heuristics perform well for the student performance dataset.
-A suggestion is that an invalid learning rate or learning rate schedule leads to a scenario where good solutions are overshot, causing \acs{Adam} and \acs{RMSProp} to struggle to resolve back to good solutions.
-Furthermore, the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
+From Figure \ref{fig:results:standalone:descriptive:descriptive} it can be seen that the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
 The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.
@@
 Exploration of the heuristic space leads the \acs{BHH} to consider other heuristics during the training process, which could possibly result in worse performances at times.
-As previously mentioned, a suggestion to improve on these results is to include a move-acceptance strategy, where heuristic progressions are discarded if they fail to produce better results.
+A suggestion to improve on these results is to include a move-acceptance strategy where heuristic progressions are discarded if they fail to produce better results.

### 2023-02-05 article/sections/01-introduction.tex
✨ (article): Done, submitting for review

@@
 \acp{ANN} are trained by optimisation algorithms known as heuristics.
-Many different heuristics have been developed and used to train \acp{ANN} \cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
+Many different heuristics have been developed and used to train \acp{ANN} \cite{ref:rakitianskaia:2012}.
 Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses.
@@
 This process is often non-trivial and could be a time-consuming exercise.
-Selection of the best heuristic to train \acp{ANN}, is often problem specific \cite{ref:allen:1996, ref:drake:2020, ref:pillay:2018}.
+Selection of the best heuristic to train \acp{ANN}, is often problem specific \cite{ref:allen:1996}.
 
-A recent suggestion related to the field of meta-learning is to dynamically select and/or adjust the heuristic used throughout the training process.
+A recent suggestion related to the field of \textit{meta-learning} is to dynamically select and/or adjust the heuristic used throughout the training process.
 This approach focuses on the hybridisation of learning paradigms.
@@
 
-In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
+In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems \cite{ref:burke:2013}.
 However, research on the application of \acp{HH} in the context of \acs{ANN} training is scarce.
-\citeauthor{ref:nel:2021} \cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
+\citeauthor{ref:nel:2021} \cite{ref:nel:2021} provides some of the first research in this field, applying a \acs{HH} to \acf{FFNN} training.
 
@@
 This research presents a novel \acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
-This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acfp{FFNN} during the training process.
+This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.
 

### 2023-02-05 article/sections/03-heuristics.tex
✨ (article): Done, submitting for review

@@
 
-Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus \cite{ref:bengio:2000, ref:feurer:2019}.
+Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus \cite{ref:bengio:2000}.
 \citeauthor{ref:blum:2003} \cite{ref:blum:2003} mention that since the 1980's, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
@@
 \acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space \cite{ref:blum:2003}.
-Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \cite{ref:rakitianskaia:2012, ref:vanwyk:2014, ref:espinal:2011, ref:gupta:1999}.
-This research takes a particular interest in population-based \acp{MH} that have been used to successfully train \acp{FFNN}.
+Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \cite{ref:rakitianskaia:2012, ref:vanwyk:2014, ref:gupta:1999}.
+This research takes a particular interest in population-based \acp{MH} that have been used to train \acp{FFNN}.
 These include \acf{PSO} \cite{ref:shi:1998}, \acf{DE} \cite{ref:price:2006} and \acfp{GA} \cite{ref:fraser:1957}.

### 2023-02-05 article/sections/06-bayesian-hyper-heuristics.tex
✨ (article): Done, submitting for review

@@
 This section presents the novel \acs{BHH}.
-The general concept of the \acs{BHH} can be summarised as follows: The \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and \acs{FFNN} training process.
+The general concept of the \acs{BHH} can be summarised as follows: the \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and \acs{FFNN} training process.
 The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process.
@@
 The credit assignment strategy is a mechanism that assigns a discrete credit indicator to heuristics that perform well, based on their performance metrics such as loss.
-The credit assignment strategy implements a component of the ``move acceptance'' process as proposed by \citeauthor{ref:ozcan:2006} \cite{ref:ozcan:2006,ref:ozcan:2008} and addresses the credit assignment problem as discussed by \citeauthor{ref:burke:2010} \cite{ref:burke:2010}.
+The credit assignment strategy implements a component of the ``move acceptance'' process as proposed by \citeauthor{ref:ozcan:2006} \cite{ref:ozcan:2006} and addresses the credit assignment problem as discussed by \citeauthor{ref:burke:2010} \cite{ref:burke:2010}.
 A good credit assignment strategy will correctly allocate credit to the appropriate heuristic-entity combination.
@@
 
-The \acs{BHH} implements a probabilistic, predictive model based on the fundamentals of the Na\"{\i}ve Bayes algorithm.
-The \acs{BHH} thus distinguishes between the following events: \textbf{$\boldsymbol{H}$}, the event of observing \textit{heuristics}, \textbf{$\boldsymbol{E}$}, the event of observing \textit{entities}, \textbf{$\boldsymbol{C}$}, the event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} are met.
+The \acs{BHH} implements a probabilistic predictive model based on the fundamentals of the Na\"{\i}ve Bayes algorithm.
+The \acs{BHH} thus distinguishes between the following events: \textbf{$\boldsymbol{H}$}, the event of observing \textit{heuristics}, \textbf{$\boldsymbol{E}$}, the event of observing \textit{entities}, and \textbf{$\boldsymbol{C}$}, the event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} are met.
 By Bayes' theorem, the selection mechanism implemented by the \acs{BHH} is given as
@@
 It can be said that the \acs{BHH} implements a Gaussian process \cite{ref:gortler:2019}.
-Since the reselection of heuristics happens at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acs{HMM} \cite{ref:rabiner:1986}.
+Since the reselection of heuristics happens at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acf{HMM} \cite{ref:rabiner:1986}.
 
@@
 
-The following hyper-parameters are implemented by the \acs{BHH}: the \textit{heuristic pool} configures the type of heuristics included in the heuristic pool as gradient-only, meta-heuristic-only or all heuristics, the \textit{population size} specifies the number of entities in the entity pool, the \textit{credit assignment strategy} specifies which credit assignment strategy to use, the \textit{reselection interval} determines the frequency of heuristic reselection, the \textit{replay window size} determines the maximum size of the performance log, the \textit{reanalysis interval} determines the frequency at which Bayesian analysis is applied, the \textit{burn in window size} determines the size of an initial window where experience is simply gathered without reanalysis, and finally, \textit{discounted rewards} and \textit{normalisation} flags toggle scaling modifiers on values assigned by the credit assignment strategies, backwards in the performance log.
+The following hyper-parameters are implemented by the \acs{BHH}: the \textit{heuristic pool} configures the type of heuristics included in the heuristic pool as, the \textit{population size} specifies the number of entities in the entity pool, the \textit{credit assignment strategy} specifies which credit assignment strategy to use, the \textit{reselection interval} determines the frequency of heuristic reselection, the \textit{replay window size} determines the maximum size of the performance log, the \textit{reanalysis interval} determines the frequency at which Bayesian analysis is applied, the \textit{burn in window size} determines the size of an initial window where experience is simply gathered without reanalysis, and finally, the \textit{discounted rewards} and \textit{normalisation} flags toggle scaling modifiers on values assigned by the credit assignment strategies, backwards in the performance log.

### 2023-02-05 article/sections/08-results.tex
✨ (article): Done, submitting for review

@@
 This can be achieved by analysing the outcomes of the change in concentration parameters and the probabilitiy distributions implemented by the \acs{BHH}.
-Figures \ref{fig:results:case_study:alphas:6} to \ref{fig:results:case_study:p_HgEC:0:6} provide illustrations of the change in concentration parameter, $\boldsymbol{\alpha}$ and the effect is has on the probability distributions of heuristic selection probabilities, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, the prior heuristic selection probability distribution, denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, and the posterior heuristic selection probability distribution, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$.
-These illustrations represent an example heuristic, \acs{Adam}, and an example entity, identified by index 6 and 0 respectively in the heuristic and entity pools.
+Figures \ref{fig:results:case_study:alphas:6} to \ref{fig:results:case_study:p_HgEC:0:6} provide illustrations of the change in concentration parameter, $\boldsymbol{\alpha}$, and the effect is has on the probability distributions of heuristic selection probabilities, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, the prior heuristic selection probability distribution, denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, and the posterior heuristic selection probability distribution, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$.
+These illustrations represent an example heuristic, \acs{Adam}, and an example entity, identified by indices 6 and 0 respectively in the heuristic and entity pools.
 The illustrations are obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.
@@
 
-The concentration parameter $\boldsymbol{\alpha}$ parameterises the Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
+The concentration parameter, $\boldsymbol{\alpha}$, parameterises the Dirichlet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$.
 The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{heuristic selection probabilities}.
@@
 The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yields the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance.
-However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ is reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.
+However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter, $\boldsymbol{\alpha}$, is reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.
 
@@
 
-Furthermore, it can be observed for small windows, at various steps for multiple runs, that the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, do not yield means that are equal to the expected heuristic selection probabilities of 0.1.
+Furthermore, it can be observed for small windows, at various steps for multiple runs, that the variance of $\boldsymbol{\theta}$, for the bhh\_baseline configuration and the bhh\_credit\_symmetric configuration, does not yield means that are equal to the expected heuristic selection probabilities of 0.1.
 This is proof that the \acs{BHH} does not just implement a form of random search, despite having small reanalysis interval and replay window size configurations.
@@
 Since the default \textit{reselection} interval is set to 10, the heuristic selection probabilities are only resampled at intervals of 10.
-This illustration then simply yield rough approximation of the illustration provided in Figure \ref{fig:results:case_study:thetas:6}.
+Figure \ref{fig:results:case_study:p_H:6} then simply yields a rough approximation of the illustration provided in Figure \ref{fig:results:case_study:thetas:6}.
 As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probabilities_of_probabilities} also apply in this section.
@@
 Since these prior heuristic selection probabilities change over time, it can be concluded that the change in prior heuristic selection probabilities is a result of the learning mechanism of the \acs{BHH}.
-Furthermore, the prior heuristic selection probability distribution provides an opportunity to utilise prior knowledge by some expert before training starts, by injecting heuristic selection biases, by means of the initial values for the concentration parameter $\boldsymbol{\alpha}$.
+Furthermore, the prior heuristic selection probability distribution provides an opportunity to utilise prior knowledge by some expert before training starts, by injecting heuristic selection biases, by means of the initial values for the concentration parameter, $\boldsymbol{\alpha}$.
 
@@
 The reasons for the aforementioned is because the probabilistic model is evaluated proportionally as was discussed in Section \ref{sec:bhh}.
-Furthermpre, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
+Furthermore, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.
 

### 2023-02-08 article/main.tex
🚧 (article): Section 2 done, WIP
🚧 (article): Save point, WIP
✨ (article): Methodology done.
🚧 (article): WIP save point for revision
🚧 (article): Save point
🚧  (article): Review, Anna part 1 a

@@
-\documentclass[preprint,12pt]{elsarticle}
+% \documentclass[preprint,12pt]{elsarticle}
 %% Use the option review to obtain double line spacing
-% \documentclass[preprint,review,12pt]{elsarticle}
+\documentclass[preprint,review,12pt]{elsarticle}
 
-\input{journal/journal.tex}
+\usepackage{acro}
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{bbm}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{url}
+\usepackage{subcaption}
+\usepackage{rotating}
+\usepackage{booktabs}
+\usepackage{colortbl}
+\usepackage{multirow}
 
-\input{packages/packages.tex}
-\input{acronyms/acronyms.tex}
+% Adam
+\DeclareAcronym{Adam}{
+      short = Adam,
+      long = \textit{adaptive moment estimation}
+}
+
+% ANOVA
+\DeclareAcronym{ANOVA}{
+      short = ANOVA,
+      long = \textit{analysis of variance}
+}
+
+\DeclareAcronym{Adagrad}{
+      short = Adagrad,
+      long = \textit{adaptive gradients}
+}
+
+\DeclareAcronym{Adadelta}{
+      short = Adadelta,
+      long = \textit{adaptive learning rate}
+}
+
+\DeclareAcronym{RMSProp}{
+      short = RMSProp,
+      long = \textit{root mean squared error propagation}
+}
+
+\DeclareAcronym{PSO}{
+      short = PSO,
+      short-plural-form = PSOs,
+      long = \textit{particle swarm optimisation},
+      long-plural-form = \textit{particle swarm optimisers}
+}
+
+\DeclareAcronym{Momentum}{
+      short = Momentum,
+      long = \textit{momentum}
+}
+
+\DeclareAcronym{NAG}{
+      short = NAG,
+      long = \textit{Nesterov accelerated gradients}
+}
+
+\DeclareAcronym{GA}{
+      short = GA,
+      short-plural-form = GAs,
+      long = \textit{genetic algorithm},
+      long-plural-form = \textit{genetic algorithms}
+}
+
+\DeclareAcronym{GP}{
+      short = GP,
+      long = \textit{genetic programming},
+}
+
+% Artificial Intelligence
+\DeclareAcronym{AI}{
+      short = AI,
+      long = \textit{artificial intelligence}
+}
+
+% Artificial Neural Network
+\DeclareAcronym{ANN}{
+      short = ANN,
+      short-plural-form = ANNs,
+      long = \textit{artificial neural network},
+      long-plural-form = \textit{artificial neural networks}
+}
+
+% Artificial Neuron
+\DeclareAcronym{AN}{
+      short = AN,
+      short-plural-form = ANs,
+      long = \textit{artificial neuron},
+      long-plural-form = \textit{artificial neurons}
+}
+
+% Bayesian Hyper-Heuristic
+\DeclareAcronym{BHH}{
+      short = BHH,
+      short-plural-form = BHHs,
+      long = \textit{Bayesian hyper-heuristic},
+      long-plural-form = \textit{Bayesian hyper-heuristics}
+}
+
+% Binary Cross-Entropy
+\DeclareAcronym{BinXE}{
+      short = BinXE,
+      long = \textit{binary cross entropy}
+}
+
+% Categorical Cross-Entropy
+\DeclareAcronym{CatXE}{
+      short = CatEX,
+      long = \textit{categorical cross entropy}
+}
+
+% Feedforward Neural Network
+\DeclareAcronym{FFNN}{
+      short = FFNN,
+      short-plural-form = FFNNs,
+      long = \textit{feedforward neural network},
+      long-plural-form = \textit{feedforward neural networks}
+}
+
+% Hyper-Heuristic
+\DeclareAcronym{HH}{
+      short = HH,
+      short-plural-form = HHs,
+      long = \textit{hyper-heuristic},
+      long-plural-form = \textit{hyper-heuristics}
+}
+
+% Differential Evolution
+\DeclareAcronym{DE}{
+      short = DE,
+      long = \textit{differential evolution}
+}
+
+% Gradient Descent
+\DeclareAcronym{GD}{
+      short = GD,
+      long = \textit{gradient descent}
+}
+
+% Leaky Rectified Linear Unit
+\DeclareAcronym{LReLU}{
+      short = LReLU,
+      long = \textit{leaky rectified linear unit}
+}
+
+% Maximum A Posteriori
+\DeclareAcronym{MAP}{
+      short = MAP,
+      long = \textit{maximum a posteriori estimation}
+}
+
+% Maximum Likelihood Estimation
+\DeclareAcronym{MLE}{
+      short = MLE,
+      long = \textit{maximum likelihood estimation}
+}
+
+% Machine Learning
+\DeclareAcronym{ML}{
+      short = ML,
+      short-plural-form = MLs,
+      long = \textit{machine learning},
+      long-plural-form = \textit{machine learnings}
+}
+
+% Mean Absolute Error
+\DeclareAcronym{MAE}{
+      short = MAE,
+      long = \textit{mean absolute error}
+}
+
+% Mean Squared Error
+\DeclareAcronym{MSE}{
+      short = MSE,
+      long = \textit{mean squared error}
+}
+
+% Rectified Linear Unit
+\DeclareAcronym{ReLU}{
+      short = ReLU,
+      long = \textit{rectified linear unit}
+}
+
+% Root Mean Squared Error
+\DeclareAcronym{RMSE}{
+      short = RMSE,
+      long = \textit{root mean squared error}
+}
+
+% Sparse Categorical Cross-Entropy
+\DeclareAcronym{SparseCatXE}{
+      short = SparseCatXE,
+      long = \textit{sparse categorical cross entropy}
+}
+
+% Stochastic Gradient Descent
+\DeclareAcronym{SGD}{
+      short = SGD,
+      long = \textit{stochastic gradient descent}
+}
+
+% Hidden Markov Model
+\DeclareAcronym{HMM}{
+      short = HMM,
+      short-plural-form = HMMs,
+      long = \textit{hidden Markov model},
+      long-plural-form = \textit{Hidden Markov Models}
+}
+
+% Backpropagation
+\DeclareAcronym{BP}{
+      short = BP,
+      long = \textit{backpropagation}
+}
+
+\DeclareAcronym{MH}{
+      short = MH,
+      short-plural-form = MHs,
+      long = \textit{meta-heuristic},
+      long-plural-form = \textit{meta-heuristics}
+}
+
+% Probability Mass Function
+\DeclareAcronym{PMF}{
+      short = PMF,
+      short-plural-form = PMFs,
+      long = \textit{probability mass function},
+      long-plural-form = \textit{probability mass functions}
+}
+
+\journal{Information Sciences}
 
@@
 
-\input{frontmatter/frontmatter.tex}
-\input{sections/01-introduction.tex}
-\input{sections/02-artificial-neural-networks.tex}
-\input{sections/03-heuristics.tex}
-\input{sections/04-hyper-heuristics.tex}
-\input{sections/05-probability.tex}
-\input{sections/06-bayesian-hyper-heuristics.tex}
-\input{sections/07-methodology.tex}
-\input{sections/08-results.tex}
-\input{sections/09-conclusion.tex}
+\begin{frontmatter}
+	\title{\tnoteref{note1}Training Feedforward Neural Networks with Bayesian Hyper-Heuristics}
+
+	\tnotetext[note1]{It is recommended that the article be viewed/printed in colour.}
+
+	\affiliation[aff:tuks]{
+		organization={University of Pretoria},
+		% addressline={Lynnwood Rd},
+		city={Pretoria},
+		postcode={0002},
+		state={Gauteng},
+		country={South Africa}
+	}
+
+	\affiliation[aff:stellenbosch]{
+		organization={Stellenbosch University},
+		% addressline={Ryneveld Street},
+		city={Stellenbosch},
+		postcode={7602},
+		state={Western Cape},
+		country={South Africa}
+	}
+
+	\affiliation[aff:wits]{
+		organization={University of the Witwatersrand},
+		% addressline={1 Jan Smuts Ave},
+		city={Johannesburg},
+		postcode={2000},
+		state={Gauteng},
+		country={South Africa}
+	}
+
+	\author[aff:tuks]{\corref{cor1}A.N.~Schreuder}
+	\ead{an.schreuder@up.ac.za}
+	\author[aff:tuks]{A.S.~Bosman}
+	\ead{annar@cs.up.ac.za}
+	\author[aff:stellenbosch]{A.P.~Engelbrecht}
+	\ead{engel@sun.ac.za}
+	\author[aff:wits]{C.W.~Cleghorn}
+	\ead{christopher.cleghorn@wits.ac.za}
+
+	\cortext[cor1]{Corresponding author}
+
+	\begin{abstract}
+		The process of training \acfp{FFNN} can benefit from an automated process where the best heuristic to train the network is sought out automatically by means of a high-level probabilistic-based heuristic.
+This research introduces a novel population-based \acf{BHH} that is used to train \acfp{FFNN}.
+The performance of the \acs{BHH} is compared to that of ten popular low-level heuristics, each with different search behaviours.
+The chosen heuristic pool consists of classic gradient-based heuristics as well as \acf{MH}.
+The empirical process is executed on fourteen datasets consisting of classification and regression problems with varying characteristics.
+The \acs{BHH} is shown to be able to train \acp{FFNN} well and provide an automated method for finding the best heuristic to train the \acp{FFNN} at various stages of the training process.
+	\end{abstract}
+
+	\begin{highlights}
+		\item A novel \acf{HH} selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acfp{FFNN}.
+The resulting \acs{HH} is referred to as the \acf{BHH}.
+
+		\item The results of the empirical study show with statistical significance that the \acs{BHH} performs generally well on multiple problems.
+It is shown that, for each problem, the \acs{BHH} performance is comparable to the best low-level heuristics included in the heuristic selection pool.
+
+		\item The results of the empirical study show that the \acs{BHH} is able to select the best heuristic to train \acp{FFNN} in general.
+This relieves researchers from the burden of having to do this selection process manually through trial and error.
+
+		\item The results of the empirical study show that the \acs{BHH}, given a diverse set of lower-level heuristics, will generally produce good results when applied to multiple problems at the same time.
+
+		\item Finally, the results of the empirical study show that the \acs{BHH} is capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from what comes before''.} knowledge in which a predefined selection bias is used for heuristics that are known to be well suited for certain problems.
+	\end{highlights}
+
+	\begin{keyword}
+		hyper-heuristics \sep meta-learning \sep feedforward neural networks \sep supervised learning \sep Bayesian statistics
+	\end{keyword}
+\end{frontmatter}
+
+% INTRODUCTION
+\section{Introduction}
+\label{sec:introduction}
+
+A popular field of focus for studying \acfp{ANN} is the process by which these models are trained.
+\acp{ANN} are trained by optimisation algorithms known as heuristics.
+Many different heuristics have been developed and used to train \acp{ANN} \citep{ref:rakitianskaia:2012}.
+Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses.
+Finding the best heuristic to train \acp{ANN} is required in order to yield optimal results.
+This process is often non-trivial and time-consuming.
+Selection of the best heuristic to train \acp{ANN} is often problem specific \citep{ref:allen:1996}.
+
+A recent suggestion related to the field of \textit{meta-learning} is to dynamically select and/or adjust the heuristic used throughout the training process.
+This approach focuses on the hybridisation of learning paradigms.
+One such form of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem \citep{ref:burke:2013}.
+These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.
+
+In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems \citep{ref:burke:2013}.
+However, research on the application of \acp{HH} in the context of \acs{ANN} training is scarce.
+\citet{ref:nel:2021} provides some of the first research in this field, applying a \acs{HH} to \acf{FFNN} training.
+
+This research takes a particular interest in developing a population-based, selection \acs{HH} that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process.
+This paper presents a novel \acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
+This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.
+
+The remainder of this article is structured as follows: Section \ref{sec:anns} provides background information on \acp{ANN}.
+Section \ref{sec:heuristics} provides details on various types of heuristics that have been used to train \acp{FFNN}.
+Section \ref{sec:hhs} presents background information on \acp{HH} and meta-learning.
+Section \ref{sec:probability} presents background information on probability theory.
+Section \ref{sec:bhh} presents the developed \acs{BHH}.
+Section \ref{sec:methodology} presents a detailed description of the empirical process and the setup of each experiment.
+Section \ref{sec:results} provides and discusses the results of the empirical study.
+Section \ref{sec:conclusion} summarises the research that is done along with a brief overview of the findings.
+
+% ARTIFICIAL NEURAL NETWORKS
+\section{Artifical Neural Networks}
+\label{sec:anns}
+
+This research focuses on a particular type of \acs{ANN}, referred to as \acfp{FFNN}.
+\acp{FFNN} were the first and simplest type of \acp{ANN} developed \citep{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order.
+Furthermore, \acp{FFNN} implement fully connected topologies, where each \acs{AN} in one layer is connected to all the \acp{AN} in the next, without any cycles \citep{ref:zell:1994}.
+In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
+
+\textit{Training} is the process whereby the weights of the \acs{FFNN} are systematically changed with the aim of improving the \textit{performance} of the \acs{FFNN}.
+Finding the optimal weights that produce the best performance on a given task is an optimisation problem.
+The optimisation algorithm used to find the optimal weights is referred to as a \textit{heuristic}.
+Heuristics search for possible solutions in the solution-space and make use of information from the search space to guide to process.
+
+During the training process, the \acs{FFNN} is exposed to data while trying to produce some target outcome.
+The degree to which the produced outcome differs from the target outcome is referred to as \textit{loss}.
+Since training of \acp{FFNN} is an optimisation problem, the goal of the training process is to minimise the loss.
+The loss is calculated using an error function.
+
+% HEURISTICS
+\section{Heuristics}
+\label{sec:heuristics}
+
+A heuristic refers to an algorithmic search technique that serves as a guide to a search process where good solutions to an optimisation problem are being sought out.
+Many different techniques have been used to train \acp{FFNN} \citep{ref:kingma:2014}.
+At the time of writing, the majority of work that is published on the training of \acp{FFNN} involves the use of gradient-based techniques \citep{ref:nel:2021}.
+
+Gradient-based heuristics are optimisation techniques that make use of derivatives obtained from evaluating the \acs{ANN} error function.
+In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{ANN} and the desired output.
+When using \acf{GD} to train \acp{ANN}, the gradients of the loss function is used to adjust the weights of the \acs{ANN} in order to minimise the error \citep{ref:engelbrecht:2007}.
+
+There are many variants of gradient-based heuristics, however, they all fundamentally apply the same generic \acs{GD} framework that propagates the error signal backwards through the \acs{ANN}.
+This algorithm is known as \acf{BP}.
+\acs{BP} was popularised by \citet{ref:werbos:1994}.
+
+The simplest type of \acs{GD} algorithm is referred to as \acs{SGD}, which implements a gradient-based weight update step for each training pattern.
+In the context of this research, the implementation of \acs{SGD} refers to the mini-batch training implementation of \acs{GD}, where a small batch of training patterns are fed to the \acs{FFNN} at once and the error function is aggregated across all training patterns.
+
+Alternative variants have been proposed that lead to better control over the convergence characteristics of \acs{SGD}.
+This research focuses on a number of these variants that include \acf{Momentum} \citep{ref:qian:1999}, \acf{NAG} \citep{ref:sutskever:2013}, \acf{Adagrad} \citep{ref:duchi:2011}, \acs{Adadelta} \citep{ref:zeiler:2012}, \acf{RMSProp} \citep{ref:hinton:2012} and \acf{Adam} \citep{ref:kingma:2014}.
+
+Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus \citep{ref:bengio:2000}.
+\citet{ref:blum:2003} mention that since the 1980's, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
+These methods are referred to as \acp{MH}.
+
+The biggest difference between \acp{MH} and gradient-based heuristics is that \acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space \citep{ref:blum:2003}.
+This also means that \acp{MH} do not necessarily require the error function to be differentiable.
+\citet{ref:blum:2003} provides advantages of \acp{MH} that include the following: they are easy to implement, they are problem independent and do not require problem-specific knowledge, and they are generally designed to find global optima, while gradient-based approaches can get stuck in local optima more often.
+Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \citep{ref:rakitianskaia:2012, ref:vanwyk:2014, ref:gupta:1999}.
+This research takes a particular interest in population-based \acp{MH} that have been used to train \acp{FFNN}.
+These include \acf{PSO} \citep{ref:shi:1998}, \acf{DE} \citep{ref:price:2006} and \acfp{GA} \citep{ref:fraser:1957}.
+
+% HYPER-HEURISTICS
+\section{Hyper-Heuristics}
+\label{sec:hhs}
+
+\citet{ref:burke:2010} define \acp{HH} as search methods or learning mechanism for selecting or generating heuristics to solve computational search problems.
+\citet{ref:burke:2003} mention that a \acs{HH} is a high-level heuristic approach that, given a particular problem instance and a number of low-level heuristics, can select and apply an appropriate low-level heuristic at each decision point.
+\acp{HH} implement a form of \textit{meta-learning} that is concerned with the selection of the best heuristic from a pool of heuristics to solve a given problem.
+It can be said that \acp{HH} are concerned with finding the best heuristic in \textit{heuristic space}, while the underlying low-level heuristics find solutions in the feasible \textit{search/solution space}.
+
+\citet{ref:burke:2010} proposed a classification scheme used to classify \acp{HH}.
+According to the proposed classification scheme, \acp{HH} are classified in two dimensions.
+These include the \textit{source of feedback} used during learning and the nature of the \textit{heuristic search space}.
+For the dimension that involves the source of feedback, \acp{HH} can be classified as either \textit{no learning}, \textit{online learning} or \textit{offline learning}.
+For the dimension that involves the nature of the \textit{heuristic search space}, \acp{HH} can be classified as either \textit{heuristic selection} or \textit{heuristic generation}.
+Further distinction is made between \textit{construction} of heuristics and \textit{perturbation} of heuristics.
+
+In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
+Some notable examples include \citep{ref:dowsland:2007, ref:burke:2010, ref:grobler:2012, ref:vanderstockt:2018}.
+Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.
+\citet{ref:nel:2021} provides some of the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
+
+This research takes a particular interest in a population-based, selection approach for \acp{HH}, with the particular intent of training \acp{FFNN}.
+In the context of population-based \acp{HH}, an entity pool exists that represents a pool of candidate solutions to the given problem.
+Each entity in the entity pool is assigned its own low-level heuristic from the heuristic pool.
+The selection of the best heuristic to apply to a candidate solution is based on the performance of the heuristic relative to that particular candidate solution at a particular point in the search process.
+Selection methods often make use of probabilistic approaches.
+
+% PROBABILITY
+\section{Probability}
+\label{sec:probability}
+
+In general, there are two main views to probability and statistics.
+These include the \textit{frequentist} and the \textit{Bayesian} view of statistics.
+Naturally, Bayesian statistics is based on Bayes' theorem \citep{ref:bayes:1763}.
+
+Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event and the conditions under which the event happened \citep{ref:hackenberger:2019}.
+Bayes' theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
+
+One of the many applications of Bayes' theorem is to do statistical inference.
+Like \acp{FFNN}, Bayesian models need to be \textit{trained}, a process known as \textit{Bayesian analysis}.
+Bayesian analysis is the process by which prior beliefs are updated as a result of observing new data/evidence.
+
+Bayesian analysis utilises the concept of conjugate priors.
+\citet{ref:wackerly:2014} state that conjugate priors are prior probability distributions that result in posterior distributions that are of the same functional form, $\mathcal{A}(v)$, as the prior, but with different parameter values.
+The conjugate prior to a Bernoulli probability distribution is the Beta probability distribution and the conjugate prior to a Categorical and Multinomial probability distribution is the Dirichlet probability distribution \citep{ref:wackerly:2014}.
+
+% BAYESIAN HYPER-HEURISTICS
+\section{Bayesian Hyper-Heuristics}
+\label{sec:bhh}
+
+This section presents the novel \acs{BHH}.
+The general concept of the \acs{BHH} can be summarised as follows: the \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and the \acs{FFNN} training process.
+The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process.
+These probabilities are then used as heuristic selection probabilities in the next step of the training process.
+
+According to the classification scheme for \acp{HH} by \citet{ref:burke:2010}, the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.
+
+Figure \ref{fig:bhh_architecture} provides an illustration of the high-level architecture of the \acs{BHH}.
+Algorithm \ref{algo:bhh} provides the high level pseudo-code implementation of the \acs{BHH}.
+Discussions follow on the most important components of the \acs{BHH}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=1.0\textwidth]{bhh_architecture.pdf}
+	\caption[An illustration of
+		the architecture and high level components of the \acf{BHH}.]{An illustration of
+		the architecture and high level components of the \acf{BHH}.}
+	\label{fig:bhh_architecture}
+\end{figure}
+
+\begin{algorithm}[htbp]
+	\footnotesize
+	\caption{The pseudo-code for the implementation of the \acf{BHH}}
+	\label{algo:bhh}
+	\begin{algorithmic}
+		\State step $\gets 0$
+
+		\State select initial heuristics
+		\State initialise population and entities
+		\State evaluate entities' initial position
+		\State update population state
+
+		\While{stopping condition not met}
+		\For{all entities in entity pool}
+		\If{selected heuristic is gradient-based}
+		\State get gradients
+		\EndIf
+
+		\State apply low-level heuristic and proxy operations
+		\State update population state
+		\State log performance metrics to performance log
+
+		\If {step < burn-in window size}
+		\State select heuristic
+		\Else
+		\If {step $\mathbin{\%}$ reanalysis interval = 0}
+		\State apply Bayesian analysis
+		\EndIf
+
+		\If {step $\mathbin{\%}$ reselection interval = 0}
+		\State select heuristic
+		\EndIf
+
+		\If {step > replay window size}
+		\State prune performance log
+		\EndIf
+		\EndIf
+		\EndFor
+		\State step $\gets$ step + $1$
+		\EndWhile
+	\end{algorithmic}
+\end{algorithm}
+
+\subsection{Heuristic Pool}\label{sec:bhh:heuristic_pool}
+
+Generally speaking, the heuristic pool is a collection of low-level heuristics under consideration by the \acs{BHH}.
+The heuristic pool contains the set of low-level heuristics that, together with their performance information, make up the \text{heuristic space}.
+Importantly, the heuristic pool must consist of a diverse set of low-level heuristics with varying capabilities.
+This research takes an interest in including both gradient-based heuristics as well as \acp{MH} in the heuristic pool.
+This approach is referred to as a \textit{multi-method} approach.
+
+\subsection{Proxies}\label{sec:bhh:heuristic:proxies}
+
+Heuristics often maintain a set of parameters that are used to control the behaviour of the heuristic.
+These parameters are refered to as heuristic \textit{state}.
+The concept of proxies arises from the sparsity of state as maintained by different heuristics.
+Since heuristics maintain (possibly) different states, there is an uncertainty of state transition when switching between heuristics.
+A solution to state indifference is to \textit{proxy} heuristic state update operations.
+State is then maintained in two parts: primary and proxied state.
+Primary state refers to the state that is originally maintained by a heuristic.
+Proxied state refers to the state that is not directly maintained by the heuristic, but can be updated by outsourcing the required state update operation to another heuristic.
+The \acs{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}.
+
+\begin{table}[htbp]
+	\centering
+	\caption{An example of a mapping of proxied state update operation maintained by the \acs{BHH}.}
+	\label{tab:bhh:heuristic_pool:proxy_mapping_example}%
+	\par\bigskip
+	\resizebox{0.38\textwidth}{!}{
+		\begin{tabular}{ccccc}
+			                                                &   & \multicolumn{3}{c}{State Parameter}                                                                                                                                                                                      \\
+			\cmidrule{3-5}                                  &   & 1                                                                      & 2                                                                      & 3                                                                      \\
+			\cmidrule{3-5}    \multirow{3}[1]{*}{Heuristic} & A & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} \\
+			                                                & B & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
+			                                                & C & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
+		\end{tabular}%
+	}
+\end{table}%
+
+From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when \index{heuristic}heuristic A is selected, it will outsource state update operations from \index{heuristic}heuristic B for state parameter 2.
+Heuristic B will outsource from \index{heuristic}heuristic A for state parameter 3.
+Finally, \index{heuristic}heuristic C will outsource from \index{heuristic}heuristic A and B for state parameters 2 and 3 respectively.
+In this way, all \index{heuristic}heuristics maintain all the state parameters.
+
+\subsection{Entity Pool}\label{sec:bhh:entity_pool}
+
+The entity pool refers to a collection or \textit{population} of \textit{entities} that each represent a candidate solution to the underlying \acs{FFNN} being trained.
+The \acs{BHH} selects from the heuristic pool a low-level heuristic to be applied to an individual entity.
+The outcome of this selection process is a mapping table that tracks which heuristic has been selected for which entity.
+These heuristic-entity combinations are applied to the underlying \acs{FFNN}.
+The \acs{BHH} tracks the performance of each of these combinations throughout the training process in a performance log.
+
+Entities represent candidate solutions to the model's trainable parameters (weights) and other heuristic-specific state parameters.
+These state parameters are referred to as \textit{local} state.
+Entities are treated as physical \textit{particles} in a hyper-dimensional search environment.
+Entities model concepts from physics.
+For example, the candidate solution is represented as the entity's position.
+The velocity and acceleration is then analogous to the gradient and momentum of the entity respectfully \cite{ref:eberhart:1995}.
+Examples of entity state parameters, as derived from various low-level heuristics, include entity position, velocity, gradient, position delta, first and second moments of the gradient, the loss, personal best positions, losses, and so on.
+The entity state parameters are updated by the associated heuristic.
+
+The population state refers to a collection of parameters that are shared between the entities in the population.
+Population state is also referred to as \textit{global} state and represents the population's memory.
+The population state generally contains state parameters that are of importance to multiple heuristics, and usually tracks the state of the population and not individual heuristic.
+Some examples of population state that can arise from different heuristics include the population of entities themselves, the global best entity found so far, the overall best loss achieved thus far, and so on.
+
+\subsection{Performance Log}\label{sec:bhh:performance_log}
+
+Heuristic selection probability is calculated based on heuristic-entity performance over time.
+Evidence of heuristic-entity performance is thus required for the \acs{BHH} to learn.
+Historical heuristic-entity performance outcomes are stored in a performance log.
+The performance log tracks information such as the current step, selected heuristic, associated entity, the loss achieved and so on.
+Since the performance log can become very big, only a sliding window of the performance history is maintained at each step in the learning process.
+The sliding window is also referred to as a \textit{replay} window/buffer.
+
+\subsection{Credit Assignment Strategy}
+\label{sec:bhh:credit_assignment_strategy}
+
+The credit assignment strategy is a mechanism that assigns a discrete credit indicator to heuristics that perform well, based on their performance metrics such as loss.
+The credit assignment strategy implements a component of the ``move acceptance'' process as proposed by \citet{ref:ozcan:2006} and addresses the credit assignment problem as discussed by \citet{ref:burke:2010}.
+A good credit assignment strategy will correctly allocate credit to the appropriate heuristic-entity combination.
+This research implements the following credit assignment strategies to choose from: \textit{ibest} (iteration best), \textit{pbest} (personal best), \textit{gbest} (global best), \textit{rbest} (replay window best), and \textit{symmetric}, where credit is assigned to all entity-heuristic combinations, regardless of their performance.
+
+\subsection{Selection Mechanism}\label{sec:bhh:selection_mechanism}
+
+The \acs{BHH} implements a probabilistic predictive model based on the fundamentals of the Na\"{\i}ve Bayes algorithm.
+The \acs{BHH} thus distinguishes between the following events: \textbf{$\boldsymbol{H}$}, the event of observing \textit{heuristics}, \textbf{$\boldsymbol{E}$}, the event of observing \textit{entities}, and \textbf{$\boldsymbol{C}$}, the event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} are met.
+By Bayes' theorem, the selection mechanism implemented by the \acs{BHH} is given as
+
+\begin{equation}
+	\label{eq:bhh:selection_mechanism:predictive_model_prop_to}
+	\begin{split}
+		P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi}) &\propto P(\boldsymbol{E} \vert \boldsymbol{H}; \boldsymbol{\phi}) P(\boldsymbol{C} \vert \boldsymbol{H}; \boldsymbol{\psi}) P(\boldsymbol{H} \vert \boldsymbol{\theta})
+	\end{split}
+\end{equation}
+
+The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $\boldsymbol{H}$, given allocation to entity $\boldsymbol{E}$ and credit requirement $\boldsymbol{C}$, parameterised by sampled $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha}; K)$, $\boldsymbol{\phi} \sim Dir(\boldsymbol{\beta}; K)^{J}$ and $\boldsymbol{\psi} \sim Beta(\gamma_{1}, \gamma_{0})$.
+In the aforementioned, $K$ is the heuristic pool size and $J$ is the entity pool size.
+The parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$ are referred to as concentration parameters.
+The concentration parameters parameterises the prior probability distributions.
+\ref{app:naive_bayes} provides mathematical derivations of the predictive model.
+
+\subsection{Optimisation Step}\label{sec:bhh:optimisation_step}
+
+The intent of the \acs{BHH} is to gather evidence that can be used to update prior beliefs about which heuristics perform well during training.
+These beliefs are represented by the concentration parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$.
+A change in prior beliefs is represented by a change in these concentration parameters.
+Specifically, it can be said that the optimisation process implemented by the \acs{BHH} updates \textit{pseudo counts} of events that are observed in the performance logs.
+These pseudo counts track the occurrence of a heuristic, an entity, and resulting performance of these two elements.
+Through the credit assignment strategy, these pseudo counts are biased towards entity-heuristic combinations that meet performance requirements and yield credit allocations.
+
+Generally, there are two different techniques that are used to train Naïve Bayes classifiers. The frequentist approach implements \acf{MLE} and the Bayesian approach implements \acf{MAP}.
+
+\subsubsection{Maximum A Posteriori Estimation}\label{sec:bhh:optimisation_step:map}
+
+Another approach to optimise the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ is to optimise the parameters by their probability distributions' parameters.
+This process is referred to as \textit{Bayesian analysis}.
+Bayesian analysis makes use of the \textit{posterior} probability distribution.
+The concentration update operations yielded by \acs{MAP} are given as follows:
+
+\begin{equation}
+	\label{eq:bhh:optimisation_step:map:alpha_update_operation}
+	\begin{split}
+		\alpha_{k}(t+1) = N_{k} + \alpha_{k}(t)
+	\end{split}
+\end{equation}
+
+\begin{equation}
+	\label{eq:bhh:optimisation_step:map:beta_update_operation}
+	\begin{split}
+		\beta_{j,k}(t+1) = N_{j,k} + \beta_{j,k}(t)
+	\end{split}
+\end{equation}
+
+\begin{equation}
+	\label{eq:bhh:optimisation_step:map:gamma1_update_operation}
+	\begin{split}
+		\gamma_{1,k}(t+1) = N_{1,k} + \gamma_{1,k}(t)
+	\end{split}
+\end{equation}
+
+\begin{equation}
+	\label{eq:bhh:optimisation_step:map:gamma2_update_operation}
+	\begin{split}
+		\gamma_{2,k}(t+1) = N_{0,k} + \gamma_{2,k}(t)
+	\end{split}
+\end{equation}
+
+\noindent
+where $N_{k}$ is a summary variable denoting the count of occurrences of heuristic $k$, $N_{j}$ is a summary variable denoting the count of occurrences of entity $j$, $N_{j,k}$ is a summary variable denoting the count of occurrences of heuristic $k$ for entity $j$, $N_{1,k}$ and $N_{0,k}$ are summary variables denoting the count of occurrences where heuristic $k$ meets performance requirements and where heuristic $k$ does not not meet performance requirements.
+
+It can be said that the \acs{BHH} implements a Gaussian process \citep{ref:gortler:2019}.
+Since the reselection of heuristics happens at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acf{HMM} \citep{ref:rabiner:1986}.
+
+\subsection{Hyper-Parameters}\label{sec:bhh:hyper_parameters}
+
+The following hyper-parameters are implemented by the \acs{BHH}: the \textit{heuristic pool} configures the type of heuristics included in the heuristic pool as, the \textit{population size} specifies the number of entities in the entity pool, the \textit{credit assignment strategy} specifies which credit assignment strategy to use, the \textit{reselection interval} determines the frequency of heuristic reselection, the \textit{replay window size} determines the maximum size of the performance log, the \textit{reanalysis interval} determines the frequency at which Bayesian analysis is applied, the \textit{burn in window size} determines the size of an initial window where experience is simply gathered without reanalysis, and finally, the \textit{discounted rewards} and \textit{normalisation} flags toggle scaling modifiers on values assigned by the credit assignment strategies, backwards in the performance log.
+
+% METHODOLOGY
+\section{Methodology}
+\label{sec:methodology}
+
+This section provides the details of the implementation of the empirical process.
+At a high level the experimental procedure consist of a comparison between the \acs{BHH} and standalone low-level heuristics.
+A number of datasets, models and heuristics are specified.
+Throughout the empirical process, the use of a \acs{BHH} baseline configuration is used.
+
+\subsection{BHH Baseline}\label{sec:methodology:baseline_bhh}
+
+The \acs{BHH} baseline is a name given to a specific configuration of the \acs{BHH} which has been found to provide a reasonable baseline performance.
+The baseline configuration is used as the cornerstone configuration from which all other heuristics and their configurations are evaluated.
+The \acs{BHH} baseline configuration is given in Table \ref{tab:methodology:bhh_baseline_configuration}.
+In Table \ref{tab:methodology:bhh_baseline_configuration}, the heuristic pool configuration, \textit{all}, refers to a configuration where the heuristic pool contains all the low-level heuristics, including all gradient-based heuristics and \acp{MH}.
+
+% Table generated by Excel2LaTeX from sheet 'BHH Baseline'
+\begin{table}[htb]
+	\centering
+	\caption{The \acs{BHH} baseline configuration as it is used in the empirical study.}
+	\label{tab:methodology:bhh_baseline_configuration}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{ccccccccc}
+			heuristic pool & population & burn in & credit & reselection & replay & reanalysis & normalise & discounted rewards \\
+			\midrule
+			all            & 5          & 0       & ibest  & 10          & 10     & 10         & false     & false              \\
+		\end{tabular}%
+	}
+\end{table}%
+
+\subsection{BHH vs. Low-Level Heuristics}
+\label{sec:methodology:experiments}
+
+For the standalone heuristics experimental group, a number of low-level heuristics are used along with their specified hyper-parameters.
+Each of these standalone low-level heuristics are compared to that of the \acs{BHH} baseline configuration, across all datasets.
+The intent of the standalone heuristics experimental group is to determine if the \acs{BHH} baseline configuration can generalise to multiple problems in comparison to individual low-level heuristics.
+
+Additional to the \acs{BHH} baseline configuration, two more \acs{BHH} configurations are included.
+These include \acs{BHH} configurations where the heuristic pool only makes use of gradient-based heuristics, and a configuration where the heuristic pool only makes use of \acp{MH}.
+The intent behind the inclusion of these configurations is to determine the effectiveness of multi-method approaches in the heuristic pool applied to training \acp{FFNN}.
+
+\subsection{Heuristics}\label{sec:methodology:heuristics}
+
+Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level heuristics that are used as well as their hyper-parameter configurations.
+Note from Table \ref{tab:methodology:heuristics} that values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it.
+
+\begin{table}[htbp]
+	\centering
+	\caption{Low-level heuristics and their hyper-parameter configurations.}
+	\label{tab:methodology:heuristics}%
+	\par\bigskip
+	\resizebox{0.6\textwidth}{!}{
+
+		\begin{tabular}{llll}
+			\textbf{heuristic} & \textbf{configuration}    & \textbf{value} & \textbf{citation}          \\
+			\midrule
+			sgd                & learning rate             & 0.1 (0.01)     & \citep{ref:sutskever:2013} \\
+			momentum           & learning rate             & 0.1 (0.01)     & \citep{ref:sutskever:2013} \\
+			                   & momentum                  & 0.9            &                            \\
+			nag                & learning rate             & 0.1 (0.01)     & \citep{ref:sutskever:2013} \\
+			                   & momentum                  & 0.9            &                            \\
+			adagrad            & learning rate             & 0.1 (0.01)     & \citep{ref:duchi:2011}     \\
+			                   & epsilon                   & 1E-07          &                            \\
+			rmsprop            & learning rate             & 0.1 (0.01)     & \citep{ref:hinton:2012}    \\
+			                   & rho                       & 0.95           &                            \\
+			                   & epsilon                   & 1E-07          &                            \\
+			adadelta           & learning rate             & 1.0 (0.95)     & \citep{ref:zeiler:2012}    \\
+			                   & rho                       & 0.95           &                            \\
+			                   & epsilon                   & 1E-07          &                            \\
+			adam               & learning rate             & 0.1 (0.01)     & \citep{ref:kingma:2014}    \\
+			                   & beta1                     & 0.9            &                            \\
+			                   & beta2                     & 0.999          &                            \\
+			                   & epsilon                   & 1E-07          &                            \\
+			pso                & population size           & 10             & \citep{ref:van:2010}       \\
+			                   & learning rate             & 1.0 (0.9)      &                            \\
+			                   & inertia weight (w)        & 0.729844       &                            \\
+			                   & cognitive control (c1)    & 1.49618        &                            \\
+			                   & social control (c2)       & 1.49618        &                            \\
+			                   & velocity clip min         & -1.0           &                            \\
+			                   & velocity clip max         & 1.0            &                            \\
+			de                 & population size           & 10             & \citep{ref:mezura:2006}    \\
+			                   & selection strategy        & best           &                            \\
+			                   & xo strategy               & exp            &                            \\
+			                   & recombination probability & 0.9 (0.1)      &                            \\
+			                   & beta                      & 2.0 (0.1)      &                            \\
+			ga                 & population size           & 10             & \citep{ref:lambora:2019}   \\
+			                   & selection strategy        & rand           &                            \\
+			                   & xo strategy               & bin            &                            \\
+			                   & mutation rate             & 0.2 (0.05)     &                            \\
+		\end{tabular}%
+	}
+\end{table}%
+
+The mapping of proxied heuristic state update operations implemented by the \acs{BHH} in the empirical process is given in Figure \ref{fig:methodology:heuristics:proxies}.
+In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x} indicate that the associated heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.8\textwidth]{bhh_heuristic_proxies.pdf}
+	\caption{Mapping of proxied heuristic state update operations as implemented by the \acs{BHH}}
+	\label{fig:methodology:heuristics:proxies}%
+\end{figure}
+
+\subsection{Datasets}\label{sec:methodology:datasets}
+
+In the context of training \acp{FFNN}, the underlying models are trained across a number of datasets.
+All the datasets used in the empirical process originate from the UCI Machine Learning Repository \citep{ref:uci:2022}.
+Datasets are grouped by problem type and include seven classification and seven regression datasets.
+The details around the datasets used can be found in Tables \ref{tab:methodology:datasets:classification} and \ref{tab:methodology:datasets:regression}.
+Each dataset is split into a training set comprising 80\% of the data, and a test set comprising 20\% of the data.
+
+A number of classification datasets contain an unbalanced representation of classes.
+This work does not apply mechanisms to cater for class balancing, in order to eliminate as many variables and factors in the empirical process as possible.
+
+\begin{table}[htb]
+	\centering
+	\caption{Classification datasets}
+	\label{tab:methodology:datasets:classification}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{ccccccccc}
+			\textbf{dataset} & \textbf{output} & \textbf{types}             & \textbf{attributes} & \textbf{classes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}          \\
+			\midrule
+			iris             & multivariate    & real                       & 4                   & 3                & 150                & 16             & 10             & \citep{ref:fisher:1936}    \\
+			car              & multivariate    & categorical                & 6                   & 4                & 1728               & 128            & 14             & \citep{ref:bohanec:1988}   \\
+			abalone          & multivariate    & categorical, integer, real & 8                   & 28               & 4177               & 256            & 17             & \citep{ref:waugh:1995}     \\
+			wine quality     & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & \citep{ref:cortez:2009}    \\
+			mushroom         & multivariate    & categorical                & 22                  & 2                & 8214               & 512            & 17             & \citep{ref:schlimmer:1987} \\
+			bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & \citep{ref:moro:2014}      \\
+			diabetic         & multivariate    & integer                    & 55                  & 3                & 100000             & 1024           & 98             & \citep{ref:strack:2014}    \\
+		\end{tabular}%
+	}
+\end{table}%
+
+\begin{table}[htb]
+	\centering
+	\caption{Regression datasets}
+	\label{tab:methodology:datasets:regression}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{cccccccc}
+			\textbf{dataset}    & \textbf{output}           & \textbf{types} & \textbf{attributes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}         \\
+			\midrule
+			fish toxicity       & multivariate              & real           & 7                   & 908                & 64             & 15             & \citep{ref:cassotti:2015} \\
+			housing             & univariate                & real           & 13                  & 506                & 32             & 16             & \citep{ref:harrison:1978} \\
+			forest fires        & multivariate              & real           & 13                  & 517                & 32             & 17             & \citep{ref:cortez:2007}   \\
+			student performance & multivariate              & integer        & 33                  & 649                & 32             & 21             & \citep{ref:cortez:2008}   \\
+			parkinsons          & multivariate              & integer, real  & 26                  & 5875               & 256            & 23             & \citep{ref:tsanas:2009}   \\
+			air quality         & multivariate, time series & real           & 15                  & 9358               & 256            & 37             & \citep{ref:de:2008}       \\
+			bike                & univariate                & integer, real  & 16                  & 17389              & 256            & 68             & \citep{ref:fanaee:2014}   \\
+		\end{tabular}%
+	}
+\end{table}%
+
+\subsection{Models}\label{sec:methodology:model}
+
+All models that are trained in the empirical process follow implementations of shallow \acp{FFNN} with only one hidden layer.
+The number of hidden units used were determined empirically.
+Weights are initialised by means of \textit{Glorot uniform sampling} \citep{ref:glorot:2010}.
+The models and their configuration, as it is used for each dataset, are given in Table \ref{tab:methodology:models:configurations}.
+
+\begin{table}[htb]
+	\centering
+	\caption{Model configurations}
+	\label{tab:methodology:models:configurations}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{rcccccccc}
+			\textbf{dataset}    & \textbf{inputs} & \textbf{hidden} & \textbf{output} & \textbf{biases} & \textbf{parameters} & \textbf{topology} & \textbf{l1 activation} & \textbf{l2 activation} \\
+			\midrule
+			fish toxicity       & 6               & 3               & 1               & yes             & 25                  & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			iris                & 4               & 5               & 3               & yes             & 43                  & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			air quality         & 12              & 8               & 1               & yes             & 113                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			housing             & 13              & 8               & 1               & yes             & 121                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			wine quality        & 13              & 10              & 7               & yes             & 217                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			parkinsons          & 21              & 10              & 1               & yes             & 231                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			car                 & 21              & 10              & 4               & yes             & 264                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			forest fires        & 43              & 16              & 1               & yes             & 721                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			abalone             & 10              & 36              & 28              & yes             & 1432                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			bank                & 51              & 32              & 1               & yes             & 1697                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			bike                & 61              & 32              & 1               & yes             & 2017                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			student performance & 99              & 32              & 1               & yes             & 3233                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
+			adult               & 108             & 64              & 1               & yes             & 7041                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			mushroom            & 117             & 64              & 1               & yes             & 7617                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+			diabetic            & 2369            & 32              & 3               & yes             & 75939               & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
+		\end{tabular}%
+	}
+\end{table}%
+
+\subsection{Performance Measures}\label{sec:methodology:performance_measures}
+
+\Acf{BinXE} is used for classification problems with two classes and \acf{SparseCatXE} is used for classification problems with more than two classes.
+For the classification problems, accuracy is also measured.
+For regression problems, the \acf{MSE} is used as a performance metric.
+After training has been completed, the \textit{average rank}, based on test loss, for all configurations, is calculated at each mini-batch step.
+
+\subsection{Statistical Analysis}
+\label{sec:methodology:statistical_analysis}
+
+Each experiment and configuration is trained for a maximum of 30 epochs and is repeated over 30 independent runs, for each of the applicable datasets.
+No early-stopping mechanism is used.
+Statistical analysis is executed on the results from the test datasets.
+An average rank is calculated across all 30 runs, for both experimental groups and configurations, at each step, for every epoch of training.
+
+The Shapiro-Wilk test for normality \citep{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
+The Levene's test for equality of variance \citep{ref:levene:1961} ($\alpha$ = 0.001) is used.
+For experiments with three or more configurations, the \acs{ANOVA} statistical test \citep{ref:fisher:1921} ($\alpha$ = 0.001) is used.
+The Kruskal-Wallis ranked non-parametric test \citep{ref:kruskal:1952} for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
+Finally, a post-hoc Tukey honest significant difference test \citep{ref:tukey:1949} ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
+Descriptive and critical difference plots are then retrieved from these results to provide visual aid.
+
+\subsection{Implementation}\label{sec:methodology:implementation}
+
+All implementations are done from first principles in Python 3.9 using Tensorflow 2.7 and Tensorflow Probability 0.15.0.
+The source code and data for this research is provided and made public at \url{https://github.com/arneschreuder/masters}.
+
+% RESULTS
+\section{Results}
+\label{sec:results}
+
+This section provides the results of the empirical process that have been conducted.
+Detailed discussions follow on the outcomes of each experiment.
+Discussions are accompanied by figures and plots to help provide visual aid for discussions.
+Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.
+
+\subsection{Overview}\label{sec:results:overview}
+
+This section provides a brief discussion on the general outcome of the empirical process as a whole and identifies some key aspects to be kept in mind when interpreting the results of the experiments.
+
+Firstly, the \acs{BHH} applies a form of online learning.
+As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process.
+The training process is not repeated iteratively as is the case with some \acp{HH}.
+
+Most of the training progress is observed to occur within the first five epochs.
+As a result, the \acs{BHH} should apply most learning at the early stages of the training process.
+After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point.
+Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the heuristic space beyond the five epoch mark.
+
+The \acs{BHH} does not implement a type of move-acceptance strategy where the application of a heuristic to an entity is only accepted if it leads to a better solution.
+In some cases, the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.
+
+Given the stochastic nature of the heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn.
+This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}.
+The probabilistic model implements \textit{probability distributions of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.
+
+By default, the \acs{BHH} baseline configuration has a reanalysis interval of 10, and a replay window size of 10, which is a small window to learn from.
+Despite the small reanalysis interval and the small replay window size, it should be observed that the \acs{BHH} exploits small performance biases regardless and does find small performance gains throughout.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+% BHH vs. Low-Level Heuristics
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+\subsection{BHH vs. Low-Level Heuristics}\label{sec:results:standalone}
+
+This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics.
+Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a heuristic pool that contains only gradient-based heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a heuristics pool that contains only \acp{MH} (denoted bhh\_mh).
+
+Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b} provides the empirical results in ranked format.
+The performance rank is calculated as the average rank produced by each heuristic, across all datasets, for all independent runs and all epochs.
+The average rank across all epochs produces a view on the performance of the heuristics as it relates to the entire training process.
+Finally, a normalised average rank is provided for the overall performance of all heuristics at the bottom of the table.
+The normalised average rank is calculated as a discrete normalisation of the average rank achieved across all datasets, for all independent runs and epochs.
+
+Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
+The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the heuristics.
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing normalised average rank and statistics for the top six low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:standalone:metrics:rank_a}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|ccc|c|c|c|}
+			                              & \multicolumn{6}{c|}{\textbf{BHH vs.
+Low-Level Heuristics - Average Rank (Part A)}}                                                                                                                                                                                                                                                                                                   \\
+			\midrule
+			\textbf{dataset}              & \textbf{adagrad}                                                                   & \textbf{adam}                                           & \textbf{rmsprop}                                        & \textbf{bhh\_gd}                                        & \textbf{nag}                                            & \textbf{bhh\_all}                                       \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .388,  .745,  .482}2,2215 ($\pm$1,591)                            & \cellcolor[rgb]{ .416,  .753,  .482}2,3989 ($\pm$1,887) & \cellcolor[rgb]{ .78,  .859,  .502}4,6172 ($\pm$2,65)   & \cellcolor[rgb]{ .796,  .863,  .506}4,7032 ($\pm$2,108) & \cellcolor[rgb]{ .725,  .839,  .498}4,2731 ($\pm$1,542) & \cellcolor[rgb]{ 1,  .922,  .518}5,9376 ($\pm$2,399)    \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3,6409 ($\pm$2,259)                            & \cellcolor[rgb]{ .804,  .863,  .506}5,4312 ($\pm$2,62)  & \cellcolor[rgb]{ .388,  .745,  .482}3,4452 ($\pm$2,57)  & \cellcolor[rgb]{ .729,  .843,  .502}5,0817 ($\pm$2,762) & \cellcolor[rgb]{ .467,  .765,  .486}3,8194 ($\pm$2,229) & \cellcolor[rgb]{ 1,  .894,  .514}6,686 ($\pm$3,061)     \\
+			\textbf{bank}                 & \cellcolor[rgb]{ .455,  .765,  .486}2,5495 ($\pm$1,598)                            & \cellcolor[rgb]{ .388,  .745,  .482}2,0796 ($\pm$1,587) & \cellcolor[rgb]{ .588,  .8,  .49}3,4645 ($\pm$2,209)    & \cellcolor[rgb]{ .8,  .863,  .506}4,8828 ($\pm$1,702)   & \cellcolor[rgb]{ .71,  .835,  .498}4,2871 ($\pm$1,732)  & \cellcolor[rgb]{ 1,  .922,  .518}6,2419 ($\pm$2,157)    \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .388,  .745,  .482}1,7204 ($\pm$1,384)                            & \cellcolor[rgb]{ .643,  .816,  .494}3,6925 ($\pm$4,004) & \cellcolor[rgb]{ .973,  .914,  .514}6,2624 ($\pm$4,58)  & \cellcolor[rgb]{ .663,  .824,  .498}3,8441 ($\pm$1,398) & \cellcolor[rgb]{ 1,  .922,  .518}6,4516 ($\pm$1,02)     & \cellcolor[rgb]{ .71,  .835,  .498}4,2151 ($\pm$1,361)  \\
+			\textbf{car}                  & \cellcolor[rgb]{ .702,  .835,  .498}4,7634 ($\pm$0,938)                            & \cellcolor[rgb]{ .388,  .745,  .482}1,6226 ($\pm$1,405) & \cellcolor[rgb]{ .455,  .765,  .486}2,3269 ($\pm$1,409) & \cellcolor[rgb]{ .561,  .792,  .49}3,3473 ($\pm$1,35)   & \cellcolor[rgb]{ .831,  .871,  .506}6,0785 ($\pm$0,799) & \cellcolor[rgb]{ .58,  .8,  .49}3,5624 ($\pm$1,315)     \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .506,  .776,  .486}2,7796 ($\pm$1,659)                            & \cellcolor[rgb]{ 1,  .886,  .514}7,1484 ($\pm$2,227)    & \cellcolor[rgb]{ 1,  .922,  .518}6,7376 ($\pm$2,577)    & \cellcolor[rgb]{ .812,  .867,  .506}5,2269 ($\pm$2,186) & \cellcolor[rgb]{ .388,  .745,  .482}1,8118 ($\pm$1,413) & \cellcolor[rgb]{ .988,  .69,  .475}9,3968 ($\pm$3,022)  \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4,2645 ($\pm$2,614)                             & \cellcolor[rgb]{ .388,  .745,  .482}3,6022 ($\pm$2,445) & \cellcolor[rgb]{ .388,  .745,  .482}3,5946 ($\pm$2,329) & \cellcolor[rgb]{ .784,  .859,  .502}5,4118 ($\pm$2,665) & \cellcolor[rgb]{ .89,  .89,  .51}5,8914 ($\pm$2,629)    & \cellcolor[rgb]{ .875,  .886,  .51}5,829 ($\pm$2,856)   \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5,1559 ($\pm$2,922)                            & \cellcolor[rgb]{ .388,  .745,  .482}4,2688 ($\pm$2,984) & \cellcolor[rgb]{ .718,  .839,  .498}5,0355 ($\pm$3,143) & \cellcolor[rgb]{ .569,  .796,  .49}4,6935 ($\pm$2,759)  & \cellcolor[rgb]{ 1,  .922,  .518}5,6882 ($\pm$2,215)    & \cellcolor[rgb]{ .91,  .894,  .51}5,4839 ($\pm$3,107)   \\
+			\textbf{housing}              & \cellcolor[rgb]{ .404,  .749,  .482}3,4484 ($\pm$2,025)                            & \cellcolor[rgb]{ .388,  .745,  .482}3,3344 ($\pm$1,819) & \cellcolor[rgb]{ .439,  .757,  .482}3,6946 ($\pm$2,166) & \cellcolor[rgb]{ .553,  .792,  .49}4,4742 ($\pm$2,312)  & \cellcolor[rgb]{ .584,  .8,  .49}4,6839 ($\pm$2,658)    & \cellcolor[rgb]{ .537,  .788,  .49}4,3763 ($\pm$2,438)  \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .965,  .91,  .514}6,3946 ($\pm$1,6)                               & \cellcolor[rgb]{ .525,  .784,  .49}3,5839 ($\pm$2,511)  & \cellcolor[rgb]{ .388,  .745,  .482}2,6968 ($\pm$1,912) & \cellcolor[rgb]{ .706,  .835,  .498}4,7473 ($\pm$2,275) & \cellcolor[rgb]{ .522,  .78,  .486}3,5548 ($\pm$2,125)  & \cellcolor[rgb]{ .78,  .859,  .502}5,2204 ($\pm$3,041)  \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ .71,  .835,  .498}4,4656 ($\pm$1,053)                             & \cellcolor[rgb]{ .388,  .745,  .482}2,1344 ($\pm$1,883) & \cellcolor[rgb]{ .431,  .757,  .482}2,4656 ($\pm$1,359) & \cellcolor[rgb]{ .569,  .796,  .49}3,4484 ($\pm$1,602)  & \cellcolor[rgb]{ .969,  .91,  .514}6,3323 ($\pm$0,891)  & \cellcolor[rgb]{ .6,  .804,  .494}3,6688 ($\pm$2,469)   \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .412,  .749,  .482}2,4677 ($\pm$1,497)                            & \cellcolor[rgb]{ .388,  .745,  .482}2,2333 ($\pm$1,742) & \cellcolor[rgb]{ .541,  .788,  .49}3,5656 ($\pm$2,492)  & \cellcolor[rgb]{ .655,  .82,  .494}4,572 ($\pm$1,934)   & \cellcolor[rgb]{ 1,  .922,  .518}7,5355 ($\pm$1,44)     & \cellcolor[rgb]{ .635,  .816,  .494}4,3839 ($\pm$1,861) \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2,5634 ($\pm$1,912)                            & \cellcolor[rgb]{ .98,  .506,  .439}11,3978 ($\pm$2,178) & \cellcolor[rgb]{ .973,  .412,  .42}12,4312 ($\pm$1,34)  & \cellcolor[rgb]{ .843,  .875,  .506}5,6624 ($\pm$3,57)  & \cellcolor[rgb]{ .478,  .769,  .486}3,1935 ($\pm$2,12)  & \cellcolor[rgb]{ .875,  .882,  .51}5,8634 ($\pm$3,159)  \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3,2806 ($\pm$1,931)                             & \cellcolor[rgb]{ .388,  .745,  .482}2,1118 ($\pm$1,666) & \cellcolor[rgb]{ .624,  .812,  .494}3,6301 ($\pm$1,731) & \cellcolor[rgb]{ .808,  .863,  .506}4,7882 ($\pm$2,105) & \cellcolor[rgb]{ .706,  .835,  .498}4,1505 ($\pm$1,916) & \cellcolor[rgb]{ .871,  .882,  .51}5,1925 ($\pm$1,951)  \\
+			\midrule
+			\textbf{avg rank}             & \cellcolor[rgb]{ .388,  .745,  .482}3,5512 ($\pm$2,25)                             & \cellcolor[rgb]{ .471,  .769,  .486}3,9314 ($\pm$3,423) & \cellcolor[rgb]{ .616,  .808,  .494}4,5691 ($\pm$3,517) & \cellcolor[rgb]{ .631,  .812,  .494}4,6346 ($\pm$2,364) & \cellcolor[rgb]{ .675,  .827,  .498}4,8394 ($\pm$2,384) & \cellcolor[rgb]{ .808,  .867,  .506}5,4327 ($\pm$2,9)   \\
+			\midrule
+			\textbf{normalised avg rank}  & \cellcolor[rgb]{ .388,  .745,  .482}1                                              & \cellcolor[rgb]{ .49,  .773,  .486}2                    & \cellcolor[rgb]{ .592,  .804,  .494}3                   & \cellcolor[rgb]{ .694,  .831,  .498}4                   & \cellcolor[rgb]{ .796,  .863,  .506}5                   & \cellcolor[rgb]{ .898,  .89,  .51}6                     \\
+			\cmidrule{5-5}\cmidrule{7-7}\end{tabular}%
+	}
+\end{table}%
+
+\begin{table}[htb]
+	\centering
+	\caption{Empirical results showing normalised average rank and statistics for the bottom six low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:standalone:metrics:rank_b}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|c|c|ccccc|}
+			                              & \multicolumn{7}{c}{\textbf{BHH vs.
+Low-Level Heuristics - Average Rank (Part B)}}                                                                                                                                                                                                                                                                                                                                                                  \\
+			\midrule
+			\textbf{dataset}              & \textbf{adadelta}                                                                 & \textbf{bhh\_mh}                                        & \textbf{ga}                                              & \textbf{pso}                                             & \textbf{sgd}                                             & \textbf{momentum}                                        & \textbf{de}                                              \\
+			\midrule
+			\textbf{abalone}              & \cellcolor[rgb]{ .894,  .89,  .51}5,3129 ($\pm$1,478)                             & \cellcolor[rgb]{ .992,  .749,  .486}8,1882 ($\pm$1,195) & \cellcolor[rgb]{ .98,  .525,  .443}11,1108 ($\pm$1,102)  & \cellcolor[rgb]{ .98,  .514,  .439}11,2559 ($\pm$1,826)  & \cellcolor[rgb]{ .992,  .718,  .478}8,628 ($\pm$1,019)   & \cellcolor[rgb]{ .984,  .624,  .463}9,8151 ($\pm$1,16)   & \cellcolor[rgb]{ .973,  .412,  .42}12,5376 ($\pm$1,329)  \\
+			\textbf{air\_quality}         & \cellcolor[rgb]{ .765,  .851,  .502}5,2441 ($\pm$3,162)                           & \cellcolor[rgb]{ 1,  .922,  .518}6,357 ($\pm$2,303)     & \cellcolor[rgb]{ .996,  .784,  .494}7,8204 ($\pm$2,265)  & \cellcolor[rgb]{ .984,  .588,  .455}9,9151 ($\pm$2,288)  & \cellcolor[rgb]{ .98,  .518,  .443}10,6613 ($\pm$1,606)  & \cellcolor[rgb]{ .973,  .412,  .42}11,7559 ($\pm$1,473)  & \cellcolor[rgb]{ .976,  .471,  .431}11,1419 ($\pm$2,236) \\
+			\textbf{bank}                 & \cellcolor[rgb]{ .914,  .894,  .51}5,672 ($\pm$1,241)                             & \cellcolor[rgb]{ .988,  .639,  .463}9,7495 ($\pm$1,048) & \cellcolor[rgb]{ .98,  .537,  .447}10,9817 ($\pm$1,216)  & \cellcolor[rgb]{ .976,  .467,  .431}11,8376 ($\pm$1,464) & \cellcolor[rgb]{ .992,  .757,  .486}8,2774 ($\pm$1,03)   & \cellcolor[rgb]{ .992,  .741,  .486}8,4774 ($\pm$1,068)  & \cellcolor[rgb]{ .973,  .412,  .42}12,4989 ($\pm$1,224)  \\
+			\textbf{bike}                 & \cellcolor[rgb]{ .859,  .878,  .506}5,3602 ($\pm$1,155)                           & \cellcolor[rgb]{ .996,  .843,  .506}7,4108 ($\pm$1,008) & \cellcolor[rgb]{ .988,  .686,  .475}9,2269 ($\pm$1,183)  & \cellcolor[rgb]{ .988,  .682,  .475}9,3086 ($\pm$1,761)  & \cellcolor[rgb]{ .984,  .596,  .455}10,3355 ($\pm$1,419) & \cellcolor[rgb]{ .984,  .561,  .451}10,7086 ($\pm$1,423) & \cellcolor[rgb]{ .973,  .412,  .42}12,4634 ($\pm$1,465)  \\
+			\textbf{car}                  & \cellcolor[rgb]{ 1,  .922,  .518}7,7344 ($\pm$1,746)                              & \cellcolor[rgb]{ .996,  .8,  .498}8,8505 ($\pm$1,413)   & \cellcolor[rgb]{ .984,  .592,  .455}10,7763 ($\pm$1,471) & \cellcolor[rgb]{ 1,  .855,  .506}8,3613 ($\pm$1,622)     & \cellcolor[rgb]{ .988,  .651,  .467}10,2452 ($\pm$1,447) & \cellcolor[rgb]{ .984,  .576,  .451}10,9226 ($\pm$1,349) & \cellcolor[rgb]{ .973,  .412,  .42}12,4086 ($\pm$1,492)  \\
+			\textbf{diabetic}             & \cellcolor[rgb]{ .494,  .773,  .486}2,6753 ($\pm$1,629)                           & \cellcolor[rgb]{ .992,  .765,  .49}8,557 ($\pm$1,17)    & \cellcolor[rgb]{ .98,  .529,  .443}11,2011 ($\pm$1,413)  & \cellcolor[rgb]{ .984,  .573,  .451}10,7022 ($\pm$1,067) & \cellcolor[rgb]{ .898,  .89,  .51}5,9215 ($\pm$1,542)    & \cellcolor[rgb]{ .949,  .906,  .514}6,3355 ($\pm$1,612)  & \cellcolor[rgb]{ .973,  .412,  .42}12,5065 ($\pm$1,242)  \\
+			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .996,  .788,  .494}7,914 ($\pm$3,429)                            & \cellcolor[rgb]{ 1,  .922,  .518}6,3849 ($\pm$2,944)    & \cellcolor[rgb]{ 1,  .894,  .514}6,7043 ($\pm$2,82)      & \cellcolor[rgb]{ .996,  .82,  .498}7,5731 ($\pm$2,982)   & \cellcolor[rgb]{ .976,  .471,  .431}11,5785 ($\pm$1,459) & \cellcolor[rgb]{ .973,  .412,  .42}12,2301 ($\pm$1,382)  & \cellcolor[rgb]{ .984,  .608,  .459}10,0215 ($\pm$2,358) \\
+			\textbf{forest\_fires}        & \cellcolor[rgb]{ 1,  .859,  .506}6,5161 ($\pm$3,082)                              & \cellcolor[rgb]{ .898,  .89,  .51}5,4591 ($\pm$2,668)   & \cellcolor[rgb]{ .996,  .796,  .494}7,3667 ($\pm$2,37)   & \cellcolor[rgb]{ 1,  .863,  .51}6,4796 ($\pm$3,354)      & \cellcolor[rgb]{ .98,  .529,  .443}10,8129 ($\pm$1,207)  & \cellcolor[rgb]{ .976,  .463,  .431}11,7065 ($\pm$1,325) & \cellcolor[rgb]{ .973,  .412,  .42}12,3333 ($\pm$1,923)  \\
+			\textbf{housing}              & \cellcolor[rgb]{ 1,  .918,  .518}7,5903 ($\pm$2,748)                              & \cellcolor[rgb]{ 1,  .922,  .518}7,5441 ($\pm$1,736)    & \cellcolor[rgb]{ 1,  .878,  .51}7,8839 ($\pm$2,099)      & \cellcolor[rgb]{ .984,  .608,  .459}9,9409 ($\pm$2,317)  & \cellcolor[rgb]{ .973,  .412,  .42}11,4075 ($\pm$1,528)  & \cellcolor[rgb]{ .976,  .431,  .424}11,2731 ($\pm$1,506) & \cellcolor[rgb]{ .976,  .42,  .424}11,3484 ($\pm$2,096)  \\
+			\textbf{iris}                 & \cellcolor[rgb]{ .973,  .412,  .42}11,3527 ($\pm$1,779)                           & \cellcolor[rgb]{ 1,  .922,  .518}6,6075 ($\pm$2,555)    & \cellcolor[rgb]{ .992,  .749,  .486}8,2473 ($\pm$1,765)  & \cellcolor[rgb]{ .992,  .745,  .486}8,2731 ($\pm$4,384)  & \cellcolor[rgb]{ .98,  .518,  .443}10,3796 ($\pm$1,294)  & \cellcolor[rgb]{ .976,  .447,  .427}11,0548 ($\pm$1,409) & \cellcolor[rgb]{ .988,  .678,  .471}8,8871 ($\pm$3,251)  \\
+			\textbf{mushroom}             & \cellcolor[rgb]{ 1,  .922,  .518}6,5538 ($\pm$1,071)                              & \cellcolor[rgb]{ .992,  .718,  .478}9,0452 ($\pm$1,093) & \cellcolor[rgb]{ .98,  .51,  .439}11,5731 ($\pm$1,193)   & \cellcolor[rgb]{ .996,  .816,  .498}7,872 ($\pm$0,92)    & \cellcolor[rgb]{ .988,  .659,  .471}9,7527 ($\pm$1,083)  & \cellcolor[rgb]{ .98,  .557,  .451}10,9785 ($\pm$1,108)  & \cellcolor[rgb]{ .973,  .412,  .42}12,7097 ($\pm$1,478)  \\
+			\textbf{parkinsons}           & \cellcolor[rgb]{ .875,  .882,  .51}6,472 ($\pm$2,423)                             & \cellcolor[rgb]{ .996,  .843,  .506}8,3161 ($\pm$1,644) & \cellcolor[rgb]{ 1,  .898,  .514}7,7968 ($\pm$1,719)     & \cellcolor[rgb]{ .996,  .827,  .502}8,4892 ($\pm$1,901)  & \cellcolor[rgb]{ .98,  .494,  .435}11,7516 ($\pm$1,155)  & \cellcolor[rgb]{ .973,  .412,  .42}12,5419 ($\pm$1,351)  & \cellcolor[rgb]{ .984,  .584,  .455}10,8742 ($\pm$1,317) \\
+			\textbf{student\_performance} & \cellcolor[rgb]{ .514,  .78,  .486}3,4194 ($\pm$2,006)                            & \cellcolor[rgb]{ 1,  .902,  .514}6,9333 ($\pm$2,44)     & \cellcolor[rgb]{ 1,  .886,  .514}7,1032 ($\pm$1,989)     & \cellcolor[rgb]{ .98,  .537,  .443}11,0624 ($\pm$1,067)  & \cellcolor[rgb]{ .988,  .918,  .514}6,6366 ($\pm$2,023)  & \cellcolor[rgb]{ 1,  .922,  .518}6,7011 ($\pm$2,242)     & \cellcolor[rgb]{ .996,  .804,  .498}8,0323 ($\pm$1,935)  \\
+			\textbf{wine\_quality}        & \cellcolor[rgb]{ 1,  .922,  .518}6,0011 ($\pm$2,404)                              & \cellcolor[rgb]{ .988,  .647,  .467}9,5935 ($\pm$1,494) & \cellcolor[rgb]{ .984,  .588,  .455}10,3387 ($\pm$1,62)  & \cellcolor[rgb]{ .98,  .525,  .443}11,1602 ($\pm$1,773)  & \cellcolor[rgb]{ .992,  .722,  .482}8,6344 ($\pm$1,18)   & \cellcolor[rgb]{ .988,  .651,  .467}9,5269 ($\pm$1,341)  & \cellcolor[rgb]{ .973,  .412,  .42}12,5903 ($\pm$1,352)  \\
+			\midrule
+			\textbf{avg rank}             & \cellcolor[rgb]{ 1,  .922,  .518}6,2727 ($\pm$3,004)                              & \cellcolor[rgb]{ .992,  .776,  .49}7,7855 ($\pm$2,271)  & \cellcolor[rgb]{ .988,  .639,  .467}9,1522 ($\pm$2,48)   & \cellcolor[rgb]{ .984,  .612,  .459}9,4451 ($\pm$2,75)   & \cellcolor[rgb]{ .984,  .592,  .455}9,6445 ($\pm$2,214)  & \cellcolor[rgb]{ .98,  .529,  .443}10,2877 ($\pm$2,346)  & \cellcolor[rgb]{ .973,  .412,  .42}11,4538 ($\pm$2,354)  \\
+			\midrule
+			\textbf{normalised avg rank}  & \cellcolor[rgb]{ 1,  .922,  .518}7                                                & \cellcolor[rgb]{ .996,  .839,  .502}8                   & \cellcolor[rgb]{ .992,  .753,  .486}9                    & \cellcolor[rgb]{ .988,  .667,  .471}10                   & \cellcolor[rgb]{ .984,  .584,  .455}11                   & \cellcolor[rgb]{ .98,  .498,  .439}12                    & \cellcolor[rgb]{ .973,  .412,  .42}13                    \\
+			\cmidrule{3-3}\end{tabular}%
+	}
+\end{table}%
+
+From the normalised average ranks provided in Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen heuristic implementations respectively.
+These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.
+
+Figure \ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each heuristic, per dataset.
+The heuristics are ordered according to the normalised ranks presented in Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b}.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=\textwidth]{standalone_descriptive.pdf}
+	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all independent runs and epochs.}
+	\label{fig:results:standalone:descriptive:descriptive}
+\end{figure}
+
+From Figure \ref{fig:results:standalone:descriptive:descriptive} it can be seen that the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
+The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.
+
+Figure \ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each heuristic as it relates to all datasets, across all independent runs and epochs.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=\textwidth]{standalone_cd_overall.pdf}
+	\caption{Critical difference plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the baseline \acs{BHH}, across all datasets, runs and epochs.}
+	\label{fig:results:standalone:descriptive:cd}
+\end{figure}
+
+Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all heuristics is very small.
+Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, is statistically only outperformed overall by \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}.
+It should be noted that the standalone low-level heuristics already produce good results in general across all datasets.
+In this particular case, producing better performance outcomes can be hard to achieve.
+However, as mentioned previously, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.
+
+Another observation that can be made is that the gradient-based heuristics generally performed much better than the \acp{MH} on all datasets.
+State of the art methods for training \acp{FFNN}, such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions \citep{ref:kingma:2014}.
+Exploration of the heuristic space leads the \acs{BHH} to consider other heuristics during the training process, which could possibly result in worse performances at times.
+A suggestion to improve on these results is to include a move-acceptance strategy where heuristic progressions are discarded if they fail to produce better results.
+
+% CONCLUSION
+\section{Conclusion}
+\label{sec:conclusion}
+
+The main area of focus for the research done in this dissertation stems from the problem statement, which identified the difficult and tedious process of selecting the best heuristic for training \acp{FFNN}.
+The research presented in this article identified the possibility of using a different approach, referred to as \acp{HH}, to automate the heuristic selection process.
+
+This research set out to develop a novel high-level heuristic that utilises probability theory in an online learning setting to drive the automatic heuristic selection process.
+A literature study was conducted on all related topics.
+A novel \acs{BHH} was proposed in detail.
+An empirical process was designed and the detail of the implementation for the empirical process and the \acs{BHH} was provided.
+The experiments defined for the empirical study was executed and results were statistically analysed.
+
+For the experimental group that compares the \acs{BHH} baseline with a number of low-level heuristics, it was found that the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen heuristics that were implemented and executed on fourteen datasets.
+The \textit{bhh\_gd} configuration produced performance results close to that of the best low-level heuristics and was only statistically outperformed by the top two low-level heuristics.
+The \textit{bhh\_all} configuration achieved an overall rank of sixth and the \textit{bhh\_mh} achieved an overall rank of eighth.
+
+Although the \textit{bhh\_gd} configuration produced performance results comparable to the best low-level heuristics, the \textit{bhh\_all} and \textit{bhh\_mh} configurations produced average results.
+It was found that, in general, gradient-based heuristics produced the best results, as such, it is understandable that the \textit{bhh\_gd} yielded the best performance outcomes between the different \acs{BHH} variants that were implemented.
+Although the \acs{BHH} variants were not able to produce better results than the top low-level heuristics, the \acs{BHH} variants still effectively trained the underlying \acp{FFNN} and produced good training outcomes overall.
+It was shown that the \textit{bhh\_gd} configuration produced the lowest variance in rank between datasets out of all of the heuristics implemented, giving the \acs{BHH} the ability to generalise well to other problems.
+
+Finally, it was shown that the \acs{BHH} provides a mechanism whereby prior expert knowledge can be injected, before training starts.
+Future research can exploit this knowledge and provide a significant bias towards heuristics that are known to perform well on particular problem types.
 
@@
 
-\input{appendices/b.tex}
-\input{appendices/a.tex}
+\section{Naïve Bayes}
+\label{app:naive_bayes}
 
-\input{references/bibliography.tex}
+This appenfix aims to dissect the probabilistic model that is presented in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
+The \acs{BHH} implements a form of Naïve Bayes classifier, and thus independence between events can be assumed.
+The following derived \acp{PMF} are provided as fundamental building blocks to show the mechanism by which the \acs{BHH} learns.
+
+The independence between events for class label $\boldsymbol{H}$, simply yields the \ac{PMF} of the \index{Multinomial probability distribution}Multinomial distribution as presented below:
+
+\begin{equation}
+	\label{eq:bhh:selection_mechanism:naive_bayes:h_pmf}
+	\begin{split}
+		P(\boldsymbol{H} \vert \boldsymbol{\theta})
+		&\propto \prod_{i=1}^{I} \prod_{k=1}^{K} P(h_{i,k} \vert \theta_{k}) \\
+		&\propto \prod_{i=1}^{I} \prod_{k=1}^{K} \theta_{k}^{\mathbbm{1}_{1}(h_{i,k})} \\
+		&\propto \prod_{k=1}^{K} \theta_{k}^{\sum_{i=1}^{I} \mathbbm{1}_{1}(h_{i,k})} \\
+		&\propto \prod_{k=1}^{K} \theta_{k}^{N_{k}}
+	\end{split}
+\end{equation}
+
+where $N_{k}$ is a summary variable such that $N_{k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the event $h_{i}$ taking on class $k$ in $I$ independent, identical runs.
+
+The independence between events $\boldsymbol{E}$, given class label $\boldsymbol{H}$, is denoted by the likelihood of $\boldsymbol{E}$, conditional to the occurrence of heuristic $k$ and model parameter $\boldsymbol{\phi}$ as follows:
+
+\begin{equation}
+	\label{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf}
+	\begin{split}
+		P(\boldsymbol{E} \vert \boldsymbol{H};  \boldsymbol{\phi})
+		&\propto \prod_{i=1}^{I} \prod_{j=1}^{J} \prod_{k=1}^{K} P(e_{i,j,k} \vert h_{i,k} ; \phi_{j,k})  \\
+		&\propto \prod_{i=1}^{I} \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{\mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})} \\
+		&\propto \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{ \sum_{i}^{I} \left[ \mathbbm{1}_{1}(e_{i,j,k}) \mathbbm{1}_{1}(h_{i,k}) \right]} \\
+		&\propto \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}}
+	\end{split}
+\end{equation}
+
+where $N_{j,k}$ is a summary variable such that $N_{j,k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on class $k$, i.e.
+the count of occurrences of both entity $j$ and heuristic $k$ occurring together in $I$ independent, identical runs.
+
+Finally, the independence between events for the performance criteria $\boldsymbol{C}$, given class label $\boldsymbol{H}$, is denoted by the likelihood of $\boldsymbol{C}$, conditional to the occurrence of heuristic $k$ and model parameter $\boldsymbol{\psi}$ as given below:
+
+\begin{equation}
+	\label{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf}
+	\begin{split}
+		P(\boldsymbol{C} \vert \boldsymbol{H}; \boldsymbol{\psi})
+		&\propto\prod_{i=1}^{I} \prod_{k=1}^{K} P(c_{i,k} \vert h_{i,k} ; \psi_{k})  \\
+		&\propto \prod_{i=1}^{I} \prod_{k=1}^{K} \psi_{k}^{\mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})} (1 - \psi_{k})^{\mathbbm{1}_{0}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})}\\
+		&\propto \prod_{k=1}^{K} \psi_{k}^{\sum_{i=1}^{I} \mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})} (1 - \psi_{k})^{\sum_{i=1}^{I} \mathbbm{1}_{0}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})}\\
+		&\propto \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{N_{0,k}} \\
+		&\propto \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})}
+	\end{split}
+\end{equation}
+
+where $N_{k}$ is the same summary variable as described for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}.
+$N_{1,k}$ is a summary variable such that $N_{1,k} = \sum_{i=1}^{I} \mathbbm{1}_{1}(c_{i,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $c_{i}$ taking on a success (i.e.
+$c_{i}=1$) and $h_{i}$ taking on class $k$, i.e.
+the count of occurrences of both succeeding in the performance criteria and heuristic $k$ occurring together in $I$ independent, identical runs.
+Similarly, $N_{0,k} = N_{k} - N_{1,k}$ denotes the count of occurrences of the events $c_{i}$ taking on a failure (i.e.
+$c_{i}=0$) and $h_{i}$ taking on class $k$.
+
+Equations~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}, \eqref{eq:bhh:selection_mechanism:naive_bayes:EgH_pmf} and \eqref{eq:bhh:selection_mechanism:naive_bayes:CgH_pmf} can be substituted into the proportional evaluation of the predictive model as given in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}, resulting in
+
+\begin{equation}
+	\label{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf}
+	\begin{split}
+		P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C};  \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})
+		&\propto P(\boldsymbol{E} \vert \boldsymbol{H};  \boldsymbol{\phi})  P(\boldsymbol{C} \vert \boldsymbol{H}; \boldsymbol{\psi}) P(\boldsymbol{H} \vert \boldsymbol{\theta})  \\
+		&\propto \left[ \prod_{j=1}^{J} \prod_{k=1}^{K} \phi_{j,k}^{N_{j,k}} \right] \left[ \prod_{k=1}^{K} \psi_{k}^{N_{1,k}} (1 - \psi_{k})^{(N_{k} - N_{1,k})} \right] \left[ \prod_{k=1}^{K} \theta_{k}^{N_{k}} \right]
+	\end{split}
+\end{equation}
+
+Consider the practical implementation of the predictive model as shown in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf}.
+Computationally, the equation presented in Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} will underflow on a real computer if the resulting probabilities are very small.
+
+\subsection{Numerical Stability}\label{sec:bhh:selection_mechanism:numerical_stability}
+
+When Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} is evaluated, the numerical stability is shown to underflow if the resulting probabilities from its parts are very small.
+Multiplication of multiple fractional parameters leads to an even smaller fractional number.
+Probabilities might be very low at some points during training.
+A solution to the aforementioned problem is to apply the \textit{log-sum-exp} trick.
+The transformation of Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:HgEC_pmf} using the log-sum-exp trick is given as
+
+\begin{equation}
+	\label{eq:bhh:selection_mechanism:numerical_stability:log_sum_exp}
+	\begin{split}
+		LSE(P(h_{k} \vert e_{j}, c_{1};  \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})) = \ln(\exp(\phi_{j,k}) +  \exp(\psi_{k}) + \exp(\theta_{k}))
+	\end{split}
+\end{equation}
+
+\bibliographystyle{elsarticle-num-names}
+\bibliography{references.bib}
 

### 2023-02-08 dissertation/chapters/01-introduction.tex
🚧  (article): Review, Anna part 1 a

@@
 These include the type of underlying optimisation algorithm used, how the model parameters are initialised, the hyper-parameters used and the constraints of learning such as allowed search space and boundaries.
-Each of these elements influence how much a particular learning technique might focus on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during training.
+Each of these elements influences how much a particular learning technique might focus on a particular solution (exploitation), in comparison to seeking out novel solutions (exploration) during training.
 
@@
 Many different heuristics have been developed and used to train \acp{FFNN}~\cite{ref:gudise:2003, ref:rakitianskaia:2012, ref:montana:1989}.
-Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses.
+Each of these heuristics has different search behaviours, characteristics, strengths and weaknesses.
 Finding the best heuristic to train the \acs{FFNN} is required in order to yield optimal results.
@@
 In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
-Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimization.
+Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimisation.
 However, research on the application of \acp{HH} in the context of \acs{FFNN} training is scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.

### 2023-02-08 dissertation/chapters/04-hyper-heuristics.tex
🍱 (images): Recovered
🚧  (article): Review, Anna part 1 a

@@
 In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
-Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimization.
+Some notable examples include the \index{simulated annealing}simulated annealing-based \acs{HH} by~\citeauthor{ref:dowsland:2007}~\cite{ref:dowsland:2007}, the \index{tabu-search}tabu-search \acs{HH} of~\citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, the \index{heterogeneous meta-hyper-heuristic}heterogeneous meta-hyper-heuristic by~\citeauthor{ref:grobler:2012}~\cite{ref:grobler:2012} and work done by~\citeauthor{ref:vanderstockt:2018}~\cite{ref:vanderstockt:2018} on the analysis of selection hyper-heuristics for population-based \acp{MH} in real-valued dynamic optimisation.
 Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021} provides the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
@@
       \centering
-      \includegraphics[width=\textwidth]{images/hh_classification.pdf}
+      \includegraphics[width=0.85\textwidth]{images/hh_classification.pdf}
       \caption{A classification of \acs{HH} approaches, according to two dimensions: (i) the source of feedback used during learning, and (ii) the nature of the heuristic search space.}

### 2023-02-08 dissertation/chapters/06-bayesian-hyper-heuristic.tex
Symbols done
🚧  (article): Review, Anna part 1 a

@@
 The \index{heuristic pool}heuristic pool is defined in terms of the diversity of heuristics, as well as the number of heuristics in the \index{heuristic pool}heuristic pool.
-Each of these are discussed in the following sections.
+Each of these is discussed in the following sections.
 
@@
 
-The \index{entity pool}entity pool maintains two different types of state. These include entity (local) and population (global) state. Each of these are discussed in more detail next.
+The \index{entity pool}entity pool maintains two different types of state. These include entity (local) and population (global) state. Each of these is discussed in more detail next.
 
@@
 Entities model concepts from physics.
-For example, the candidate solution is represented as the entity's position, and an entity's velocity and acceleration is analogous to the gradient and momentum of the entity respectfully.
+For example, the candidate solution is represented as the entity's position, and an entity's velocity and acceleration are analogous to the gradient and momentum of the entity respectfully.
 Examples of entity state parameters, as derived from various low-level \index{heuristic}heuristics, is given as follows:
@@
       \begin{split}
-            LSE(P(h_{k} \vert e_{j}, c_{1};  \theta, \phi, \psi)) = \ln(\exp(\phi_{j,k}) +  \exp(\psi_{k}) + \exp(\theta_{k}))
+            LSE(P(h_{k} \vert e_{j}, c_{1};  \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})) = \ln(\exp(\phi_{j,k}) +  \exp(\psi_{k}) + \exp(\theta_{k}))
       \end{split}
@@
 \begin{itemize}
-      \item using \textit{symmetric} initialisation of the concentration parameters $\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$;
+      \item using \textit{symmetric} initialisation of the concentration parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$;
 
@@
 
-In probability theory and statistics, \acf{MLE} is a method that estimates the parameters of a prior probability distribution given newly observed data and evidence.
+In probability theory and statistics, \acf{MLE} is a method that estimates the parameters of a prior probability distribution and is based on newly observed data and evidence.
 This section shows that the values for $\boldsymbol{\theta}$, $\boldsymbol{\phi}$ and $\boldsymbol{\psi}$ can be estimated by \acs{MLE} as follows:
@@
 
-      \item The low-level heuristics' hyper-parameters. At a lower-level, each of these heuristics have their own set of hyper-parameters.
+      \item The low-level heuristics' hyper-parameters. At a lower-level, each of these heuristics has their own set of hyper-parameters.
 

### 2023-02-08 dissertation/chapters/08-results.tex
🚧  (article): Review, Anna part 1 a

@@
 The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{\index{heuristic}heuristic selection probabilities}.
-Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively.
+Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, are at indices 0, 6, 7, and 8 respectively.
 Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool.
@@
       \par\bigskip
-      \caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
+      \caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, are at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
       \label{fig:results:case_study:alphas}
@@
       \par\bigskip
-      \caption{The average sampled \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8.
+      \caption{The average sampled \index{heuristic}heuristic selection probabilities, denoted $\boldsymbol{\theta}$, are at indices 0, 6, 7, and 8.
 The \index{heuristic}heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
@@
 
-Figures~\ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
+Figures~\ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, are at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs.
 Similar to before, these illustrations are also presented in log scale.
@@
       \par\bigskip
-      \caption{The average prior \index{heuristic}heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8.
+      \caption{The average prior \index{heuristic}heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, are at indices 0, 6, 7, and 8.
 The prior \index{heuristic}heuristic selection probabilities are sampled from the probability distribution of \index{heuristic}heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}

### 2023-02-09 article/main.tex
🚧 (article): Anna review 1 b

@@
 
+% DNN
+\DeclareAcronym{DNN}{
+      short = DNN,
+      long = \textit{deep neural network}
+}
+
+\DeclareAcronym{AMALGAM}{
+      short = AMALGAM,
+      long = \textit{multialgorithm, genetically adaptive multiobjective}
+}
+
+\DeclareAcronym{HHBOA}{
+      short = HHBOA,
+      long = \textit{hyper-heuristic Bayesian optimisation algorithm}
+}
+
 \journal{Information Sciences}
@@
 Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.
-\citet{ref:nel:2021} provides some of the first research in this field, applying a \acs{HH} to \acs{FFNN} training.
+\citet{ref:nel:2021} provides some of the first research in this field, applying an novel adaptation of an evolutionary-based \acs{HH}, known as the \acf{AMALGAM} \acs{HH} \citep{ref:vrugt:2007}, to \acs{FFNN} training.
+Furthermore, \citet{ref:oliva:2019} provide the \acf{HHBOA}, the first use of Bayesian optimisation in a \acs{HH} context.
+The method proposed by \citet{ref:oliva:2019} uses a Bayesian selection operator to evolve combinations of low-level heuristics  while looking for good problem solutions to a benchmark of optimisation functions, but does not apply a \acs{HH} to the training of \acp{FFNN}.
 
@@
 Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level heuristics that are used as well as their hyper-parameter configurations.
+In some cases, parameters are changed dynamically throughout the training process using a \textit{decay schedule}.
 Note from Table \ref{tab:methodology:heuristics} that values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it.
@@
 
-All models that are trained in the empirical process follow implementations of shallow \acp{FFNN} with only one hidden layer.
+All models trained in the empirical process follow implementations of shallow \acp{FFNN} with only one hidden layer.
 The number of hidden units used were determined empirically.
@@
 For regression problems, the \acf{MSE} is used as a performance metric.
-After training has been completed, the \textit{average rank}, based on test loss, for all configurations, is calculated at each mini-batch step.
+After training has completed, the \textit{average rank}, based on test loss, for all configurations, is calculated at each mini-batch step.
 
@@
 
-Each experiment and configuration is trained for a maximum of 30 epochs and is repeated over 30 independent runs, for each of the applicable datasets.
+Each experiment and configuration is trained for a maximum of 30 epochs and is repeated over 30 independent runs, for each of the datasets.
 No early-stopping mechanism is used.
@@
 
-This section provides the results of the empirical process that have been conducted.
-Detailed discussions follow on the outcomes of each experiment.
-Discussions are accompanied by figures and plots to help provide visual aid for discussions.
-Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.
+This section provides the results of the empirical process that has been conducted. Detailed discussions follow on the outcomes of each experiment.
 
@@
 
-Given the stochastic nature of the heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn.
+Given the stochastic nature of the heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log are required for the \acs{BHH} to learn.
 This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}.
@@
 By default, the \acs{BHH} baseline configuration has a reanalysis interval of 10, and a replay window size of 10, which is a small window to learn from.
-Despite the small reanalysis interval and the small replay window size, it should be observed that the \acs{BHH} exploits small performance biases regardless and does find small performance gains throughout.
+Despite the small reanalysis interval and the small replay window size, it should be observed that the \acs{BHH} exploits small performance biases and finds small performance gains throughout.
 
@@
 
-This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics.
-Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a heuristic pool that contains only gradient-based heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a heuristics pool that contains only \acp{MH} (denoted bhh\_mh).
-
-Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b} provides the empirical results in ranked format.
+Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b} provide the empirical results in ranked format.
 The performance rank is calculated as the average rank produced by each heuristic, across all datasets, for all independent runs and all epochs.
@@
 
-Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
-The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the heuristics.
+Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b} show that the \textit{bhh\_gd} configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets.
+The \textit{bhh\_gd} configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the \textit{bhh\_all} and \textit{bhh\_mh} produced average results compared to all the heuristics.
 
@@
 
-From the normalised average ranks provided in Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eighth amongst all thirteen heuristic implementations respectively.
+The normalised average ranks provided in Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b} show that the \textit{bhh\_gd} configuration ranked fourth, while the \textit{bhh\_al} and \textit{bhh\_mh} configurations ranked sixth and eighth amongst all thirteen heuristic implementations respectively.
 These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.
@@
 The heuristics are ordered according to the normalised ranks presented in Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b}.
+Figure \ref{fig:results:standalone:descriptive:descriptive} shows that the \textit{bhh\_gd} heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
+The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.
 
@@
 
-From Figure \ref{fig:results:standalone:descriptive:descriptive} it can be seen that the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
-The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.
-
 Figure \ref{fig:results:standalone:descriptive:cd} provides an illustration of the overall critical difference plots that illustrate the statistically significant differences in ranked performance for each heuristic as it relates to all datasets, across all independent runs and epochs.
+Although the outcomes of the \textit{bhh\_al} and \textit{bhh\_mh} configurations seem to produce average performance results, it should be noted that the performance difference between all heuristics is very small.
+Furthermore, the best configuration of the \acs{BHH}, namely the \textit{bhh\_gd} configuration, is statistically outperformed overall by only \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}.
+It should be noted that the standalone low-level heuristics already produce good results in general across all datasets.
+In this particular case, producing better performance outcomes can be hard to achieve.
+However, as mentioned previously, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.
 
@@
 
-Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all heuristics is very small.
-Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, is statistically only outperformed overall by \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}.
-It should be noted that the standalone low-level heuristics already produce good results in general across all datasets.
-In this particular case, producing better performance outcomes can be hard to achieve.
-However, as mentioned previously, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.
-
 Another observation that can be made is that the gradient-based heuristics generally performed much better than the \acp{MH} on all datasets.
@@
 
-The main area of focus for the research done in this dissertation stems from the problem statement, which identified the difficult and tedious process of selecting the best heuristic for training \acp{FFNN}.
+The research done in this study stems from the difficult and tedious process of selecting the best heuristic for training \acp{FFNN}.
 The research presented in this article identified the possibility of using a different approach, referred to as \acp{HH}, to automate the heuristic selection process.
@@
 This research set out to develop a novel high-level heuristic that utilises probability theory in an online learning setting to drive the automatic heuristic selection process.
-A literature study was conducted on all related topics.
-A novel \acs{BHH} was proposed in detail.
-An empirical process was designed and the detail of the implementation for the empirical process and the \acs{BHH} was provided.
-The experiments defined for the empirical study was executed and results were statistically analysed.
-
-For the experimental group that compares the \acs{BHH} baseline with a number of low-level heuristics, it was found that the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen heuristics that were implemented and executed on fourteen datasets.
-The \textit{bhh\_gd} configuration produced performance results close to that of the best low-level heuristics and was only statistically outperformed by the top two low-level heuristics.
-The \textit{bhh\_all} configuration achieved an overall rank of sixth and the \textit{bhh\_mh} achieved an overall rank of eighth.
+
+For the experimental group that compares the \acs{BHH} baseline with a number of low-level heuristics, it was found that the \textit{bhh\_gd} configuration, which contains only gradient-based heuristics in the heuristic pool, performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen heuristics that were implemented and executed on fourteen datasets.
+The \textit{bhh\_gd} configuration produced performance results close to that of the best low-level heuristics and was statistically outperformed only by the top two low-level heuristics.
+The \textit{bhh\_all} configuration, which contains only gradient-based heuristics and \acp{MH} in the heuristic pool, achieved an overall rank of sixth, and the \textit{bhh\_mh} configuration, which contains only \acp{MH} in the heuristic pool, achieved an overall rank of eighth.
 
@@
 Future research can exploit this knowledge and provide a significant bias towards heuristics that are known to perform well on particular problem types.
+Future research can also investigate the scalability and effectiveness of the \acs{BHH} on other model architectures such as \acfp{DNN}.
+Furthermore, the selection mechanism of the \acs{BHH} can be extended to not just select heuristics from a heuristic pool, but also different model architectures from a model architecture pool.
 

### 2023-02-09 article/main.tex
💚 Dedicated to Taylah, Beané and Aleah

@@
 \usepackage{subcaption}
-\usepackage{rotating}
 \usepackage{booktabs}
@@
       long = \textit{hyper-heuristic Bayesian optimisation algorithm}
+}
+
+\DeclareAcronym{BOHTA}{
+      short = BOHTA,
+      long = \textit{bi-objective hyperheuristic training algorithm}
 }
@@
 The performance of the \acs{BHH} is compared to that of ten popular low-level heuristics, each with different search behaviours.
-The chosen heuristic pool consists of classic gradient-based heuristics as well as \acf{MH}.
+The chosen heuristic pool consists of classic gradient-based heuristics as well as \acfp{MH}.
 The empirical process is executed on fourteen datasets consisting of classification and regression problems with varying characteristics.
@@
 Many different heuristics have been developed and used to train \acp{ANN} \citep{ref:rakitianskaia:2012}.
-Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses.
-Finding the best heuristic to train \acp{ANN} is required in order to yield optimal results.
+Each of these heuristics has different search behaviours, characteristics, strengths and weaknesses.
+It is necessary to find the best heuristic to train \acp{ANN} in order to yield optimal results.
 This process is often non-trivial and time-consuming.
@@
 This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.
+
+The selection mechanism implemented by the \acs{BHH} is different from the \acf{AMALGAM} and \acf{BOHTA} methods used by \citet{ref:nel:2021}, as well as the \acf{HHBOA} proposed by \citet{ref:oliva:2019}.
+The key differences include that the \acs{BHH} does not follow an evolutionary approach to the selected low-level heuristics.
+As such the population does not generate offspring, but rather reuses entities in the population.
+Furthermore, the \acs{BHH} implements a discrete credit assignment mechanism, not making use of pareto fronts as in the \acs{AMALGAM} and \acs{BOHTA} methods.
 
@@
 \acp{FFNN} were the first and simplest type of \acp{ANN} developed \citep{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order.
-Furthermore, \acp{FFNN} implement fully connected topologies, where each \acs{AN} in one layer is connected to all the \acp{AN} in the next, without any cycles \citep{ref:zell:1994}.
+Furthermore, \acp{FFNN} implement fully connected topologies, where each \acf{AN} in one layer is connected to all the \acp{AN} in the next, without any cycles \citep{ref:zell:1994}.
 In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
@@
 Gradient-based heuristics are optimisation techniques that make use of derivatives obtained from evaluating the \acs{ANN} error function.
-In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{ANN} and the desired output.
+In the context of supervised learning, loss functions produce a scalar value that represents the error between the output of the \acs{ANN} and the desired output.
 When using \acf{GD} to train \acp{ANN}, the gradients of the loss function is used to adjust the weights of the \acs{ANN} in order to minimise the error \citep{ref:engelbrecht:2007}.
 
-There are many variants of gradient-based heuristics, however, they all fundamentally apply the same generic \acs{GD} framework that propagates the error signal backwards through the \acs{ANN}.
-This algorithm is known as \acf{BP}.
-\acs{BP} was popularised by \citet{ref:werbos:1994}.
-
-The simplest type of \acs{GD} algorithm is referred to as \acs{SGD}, which implements a gradient-based weight update step for each training pattern.
+There are many variants of gradient-based heuristics.
+However, they all fundamentally apply the same generic \acs{GD} framework that propagates the error signal backwards through the \acs{ANN}.
+This algorithm is known as \acf{BP}, was popularised by \citet{ref:werbos:1994}.
+
+The simplest type of \acs{GD} algorithm is referred to as \acf{SGD}, which implements a gradient-based weight update step for each training pattern.
 In the context of this research, the implementation of \acs{SGD} refers to the mini-batch training implementation of \acs{GD}, where a small batch of training patterns are fed to the \acs{FFNN} at once and the error function is aggregated across all training patterns.
@@
 Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus \citep{ref:bengio:2000}.
-\citet{ref:blum:2003} mention that since the 1980's, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
+\citet{ref:blum:2003} mention that since the 1980s, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space.
 These methods are referred to as \acp{MH}.
@@
 In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
-Some notable examples include \citep{ref:dowsland:2007, ref:burke:2010, ref:grobler:2012, ref:vanderstockt:2018}.
+Some notable examples include \citep{ref:burke:2010, ref:dowsland:2007, ref:grobler:2012, ref:vanderstockt:2018}.
 Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.
-\citet{ref:nel:2021} provides some of the first research in this field, applying an novel adaptation of an evolutionary-based \acs{HH}, known as the \acf{AMALGAM} \acs{HH} \citep{ref:vrugt:2007}, to \acs{FFNN} training.
-Furthermore, \citet{ref:oliva:2019} provide the \acf{HHBOA}, the first use of Bayesian optimisation in a \acs{HH} context.
+\citet{ref:nel:2021} provides some of the first research in this field, applying \acs{BOHTA}, a novel adaptation of an evolutionary-based \acs{HH}, known as the \acs{AMALGAM} \acs{HH} \citep{ref:vrugt:2007}, to \acs{FFNN} training.
+Furthermore, \citet{ref:oliva:2019} provide \acs{HHBOA}, the first use of Bayesian optimisation in a \acs{HH} context.
 The method proposed by \citet{ref:oliva:2019} uses a Bayesian selection operator to evolve combinations of low-level heuristics  while looking for good problem solutions to a benchmark of optimisation functions, but does not apply a \acs{HH} to the training of \acp{FFNN}.
@@
 Bayesian analysis utilises the concept of conjugate priors.
-\citet{ref:wackerly:2014} state that conjugate priors are prior probability distributions that result in posterior distributions that are of the same functional form, $\mathcal{A}(v)$, as the prior, but with different parameter values.
-The conjugate prior to a Bernoulli probability distribution is the Beta probability distribution and the conjugate prior to a Categorical and Multinomial probability distribution is the Dirichlet probability distribution \citep{ref:wackerly:2014}.
+\citet{ref:wackerly:2014} state that conjugate priors are prior probability distributions that result in posterior distributions that are of the same functional form as the prior, but with different parameter values.
+The conjugate prior to a Bernoulli probability distribution is the Beta probability distribution and the conjugate prior to a categorical and multinomial probability distribution is the Dirichlet probability distribution \citep{ref:wackerly:2014}.
 
@@
 This section presents the novel \acs{BHH}.
-The general concept of the \acs{BHH} can be summarised as follows: the \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and the \acs{FFNN} training process.
+The general concept of the \acs{BHH} is summarised as follows: the \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics.
+These low-level heuristics are applied to a population of entities, each implementing a candidate solution to a \acs{FFNN}.
+The  intent of the \acs{BHH} is to optimise both the underlying \acs{FFNN} and the \acs{FFNN} training process.
 The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process.
@@
 According to the classification scheme for \acp{HH} by \citet{ref:burke:2010}, the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.
-
 Figure \ref{fig:bhh_architecture} provides an illustration of the high-level architecture of the \acs{BHH}.
@@
 
-		\If {step > replay window size}
+		\If {step $<$ replay window size}
 		\State prune performance log
@@
 Proxied state refers to the state that is not directly maintained by the heuristic, but can be updated by outsourcing the required state update operation to another heuristic.
-The \acs{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}.
+The \acs{BHH} thus incorporates a mapping of proxied state update operations as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}.
 
@@
 \end{table}%
-
+\noindent
 From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when \index{heuristic}heuristic A is selected, it will outsource state update operations from \index{heuristic}heuristic B for state parameter 2.
@@
 The parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$ are referred to as concentration parameters.
-The concentration parameters parameterises the prior probability distributions.
+The concentration parameters are used to parameterise the prior probability distributions.
 \ref{app:naive_bayes} provides mathematical derivations of the predictive model.
@@
 
-Another approach to optimise the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ is to optimise the parameters by their probability distributions' parameters.
+\Acs{MAP} is an approach to optimise the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ by optimising the parameters of their probability distributions.
 This process is referred to as \textit{Bayesian analysis}.
 Bayesian analysis makes use of the \textit{posterior} probability distribution.
-The concentration update operations yielded by \acs{MAP} are given as follows:
+The concentration update operations yielded by \acs{MAP}, are given as follows:
 
@@
 
-The following hyper-parameters are implemented by the \acs{BHH}: the \textit{heuristic pool} configures the type of heuristics included in the heuristic pool as, the \textit{population size} specifies the number of entities in the entity pool, the \textit{credit assignment strategy} specifies which credit assignment strategy to use, the \textit{reselection interval} determines the frequency of heuristic reselection, the \textit{replay window size} determines the maximum size of the performance log, the \textit{reanalysis interval} determines the frequency at which Bayesian analysis is applied, the \textit{burn in window size} determines the size of an initial window where experience is simply gathered without reanalysis, and finally, the \textit{discounted rewards} and \textit{normalisation} flags toggle scaling modifiers on values assigned by the credit assignment strategies, backwards in the performance log.
+The following hyper-parameters are implemented by the \acs{BHH}: the \textit{heuristic pool} configures the type of heuristics included in the heuristic pool, the \textit{population size} specifies the number of entities in the entity pool, the \textit{credit assignment strategy} specifies which credit assignment strategy to use, the \textit{reselection interval} determines the frequency of heuristic reselection, the \textit{replay window size} determines the maximum size of the performance log, the \textit{reanalysis interval} determines the frequency at which Bayesian analysis is applied, the \textit{burn in window size} determines the size of an initial window where experience is simply gathered without reanalysis, and finally, the \textit{discounted rewards} and \textit{normalisation} flags toggle scaling modifiers on values assigned by the credit assignment strategies, backwards in the performance log.
 
@@
 A number of datasets, models and heuristics are specified.
-Throughout the empirical process, the use of a \acs{BHH} baseline configuration is used.
+Throughout the empirical process, a \acs{BHH} baseline configuration is used.
 
@@
 For the standalone heuristics experimental group, a number of low-level heuristics are used along with their specified hyper-parameters.
-Each of these standalone low-level heuristics are compared to that of the \acs{BHH} baseline configuration, across all datasets.
+Each of these standalone low-level heuristics is compared to that of the \acs{BHH} baseline configuration, across all datasets.
 The intent of the standalone heuristics experimental group is to determine if the \acs{BHH} baseline configuration can generalise to multiple problems in comparison to individual low-level heuristics.
@@
 
-\begin{table}[htb]
+\begin{table}[!tb]
 	\centering
@@
 
-This appenfix aims to dissect the probabilistic model that is presented in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
+This section aims to dissect the probabilistic model that is presented in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}.
 The \acs{BHH} implements a form of Naïve Bayes classifier, and thus independence between events can be assumed.
@@
 \end{equation}
-
+\noindent
 where $N_{k}$ is a summary variable such that $N_{k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the event $h_{i}$ taking on class $k$ in $I$ independent, identical runs.
@@
 \end{equation}
-
+\noindent
 where $N_{j,k}$ is a summary variable such that $N_{j,k} = \sum_{i=i}^{I} \mathbbm{1}_{1}(e_{i,j,k})\mathbbm{1}_{1}(h_{i,k})$, denoting the count of occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on class $k$, i.e.
@@
 \end{equation}
-
+\noindent
 where $N_{k}$ is the same summary variable as described for Equation~\eqref{eq:bhh:selection_mechanism:naive_bayes:h_pmf}.

### 2024-01-11 article/main.tex
💚 Dedicated to Taylah, Beané and Aleah

@@
 \usepackage{multirow}
+\usepackage{lineno}
+\usepackage{xcolor}
 
@@
 		city={Pretoria},
-		postcode={0002},
+		% postcode={0002},
 		state={Gauteng},
@@
 		city={Stellenbosch},
-		postcode={7602},
+		% postcode={7602},
 		state={Western Cape},
 		country={South Africa}
+	}
+
+	% Center for Applied Mathematics and Bioinformatics, Gulf University for Science and Technology, Kuwait
+	\affiliation[aff:kuwait]{
+		organization={Center for Applied Mathematics and Bioinformatics, Gulf University for Science and Technology},
+		% addressline={Ryneveld Street},
+		city={Mishref},
+		country={Kuwait}
 	}
@@
 		city={Johannesburg},
-		postcode={2000},
+		% postcode={2000},
 		state={Gauteng},
@@
 	\ead{annar@cs.up.ac.za}
-	\author[aff:stellenbosch]{A.P.~Engelbrecht}
+	\author[aff:stellenbosch,aff:kuwait]{A.P.~Engelbrecht}
 	\ead{engel@sun.ac.za}
@@
 
+\linenumbers
+
 % INTRODUCTION
@@
 Many different heuristics have been developed and used to train \acp{ANN} \citep{ref:rakitianskaia:2012}.
-Each of these heuristics has different search behaviours, characteristics, strengths and weaknesses.
+Each heuristic has different search behaviours, characteristics, strengths and weaknesses.
 It is necessary to find the best heuristic to train \acp{ANN} in order to yield optimal results.
@@
 This research takes a particular interest in developing a population-based, selection \acs{HH} that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process.
-This paper presents a novel \acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution.
-This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.
+This paper presents a novel \acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a heuristic selection probability distribution.
+
+The general concept of the \acs{BHH} is summarised as follows: the \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics.
+These low-level heuristics are applied to a population of entities, each implementing a candidate solution to a \acs{FFNN}.
+The intent of the \acs{BHH} is to optimise both the underlying \acs{FFNN} and the \acs{FFNN} training process.
+The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process.
+These probabilities are then used as heuristic selection probabilities in the next step of the training process.
+
+The update of selection probabilities is guided by Bayesian analysis, where prior probabilities are updated with new evidence to form posterior probabilities.
+The performance of each heuristic-entity combination is logged, which captures the efficacy of each heuristic applied to their respective entity, at different stages of the training process.
+The logged performance data acts as new evidence for the Bayesian analysis process.
+The \acs{BHH} also incorporates a novel proxied heuristic update step, where various components of the update step for low-level heuristics are sourced from other heuristics in the pool of heuristics, when the direct application of a heuristic is not feasible/possible.
 
@@
 Furthermore, the \acs{BHH} implements a discrete credit assignment mechanism, not making use of pareto fronts as in the \acs{AMALGAM} and \acs{BOHTA} methods.
+
+Although this research takes a particular interest in training \acp{FFNN}, the \acs{BHH} is not limited to these types of models and can generally be applied to any \acs{ANN} as long as the \acs{ANN} can be trained by all of the low-level heuristics.
+Experimentation with other \acp{ANN} architectures besides \acp{FFNN} is left for future research.
 
@@
 % ARTIFICIAL NEURAL NETWORKS
-\section{Artifical Neural Networks}
+\section{Artificial Neural Networks}
 \label{sec:anns}
@@
 This also means that \acp{MH} do not necessarily require the error function to be differentiable.
-\citet{ref:blum:2003} provides advantages of \acp{MH} that include the following: they are easy to implement, they are problem independent and do not require problem-specific knowledge, and they are generally designed to find global optima, while gradient-based approaches can get stuck in local optima more often.
+\citet{ref:blum:2003} provide advantages of \acp{MH} that include the following: they are easy to implement, they are problem independent and do not require problem-specific knowledge, and they are generally designed to find global optima, while gradient-based approaches can get stuck in local optima more often.
 Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \citep{ref:rakitianskaia:2012, ref:vanwyk:2014, ref:gupta:1999}.
 This research takes a particular interest in population-based \acp{MH} that have been used to train \acp{FFNN}.
-These include \acf{PSO} \citep{ref:shi:1998}, \acf{DE} \citep{ref:price:2006} and \acfp{GA} \citep{ref:fraser:1957}.
+These include \acf{PSO} \citep{ref:abdulkarim:2021}, \acf{DE} \citep{ref:xue:2022}, and \acfp{GA} \citep{ref:khan:2012}.
 
@@
 
-\citet{ref:burke:2010} proposed a classification scheme used to classify \acp{HH}.
+\citet{ref:burke:2010} propose a classification scheme used to classify \acp{HH}.
 According to the proposed classification scheme, \acp{HH} are classified in two dimensions.
@@
 
-In general, there are two main views to probability and statistics.
-These include the \textit{frequentist} and the \textit{Bayesian} view of statistics.
-Naturally, Bayesian statistics is based on Bayes' theorem \citep{ref:bayes:1763}.
-
 Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event and the conditions under which the event happened \citep{ref:hackenberger:2019}.
@@
 
-This section presents the novel \acs{BHH}.
-The general concept of the \acs{BHH} is summarised as follows: the \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics.
+This section presents the novel \acs{BHH} and is structured as follows: Section \ref{sec:bhh:overview} presents an overview of the \acs{BHH}, Sections \ref{sec:bhh:heuristic_pool} - \ref{sec:bhh:selection_mechanism} provide details on the most important components of the \acs{BHH}, Section \ref{sec:bhh:optimisation_step} describes the optimisation step implemented by the \acs{BHH} and Section \ref{sec:bhh:hyper_parameters} discusses the hyper-parameters used by the \acs{BHH}.
+
+\subsection{Overview}\label{sec:bhh:overview}
+
+According to the classification scheme for \acp{HH} by \citet{ref:burke:2010}, the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.
+
+The \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics.
 These low-level heuristics are applied to a population of entities, each implementing a candidate solution to a \acs{FFNN}.
@@
 
-According to the classification scheme for \acp{HH} by \citet{ref:burke:2010}, the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.
+The update of selection probabilities is guided by Bayesian analysis, where prior probabilities are updated with new evidence to form posterior probabilities.
+The performance of each heuristic-entity combination is logged, which captures the efficacy of each heuristic applied to their respective entity, at different stages of the training process.
+The logged performance data acts as new evidence for the Bayesian analysis process.
+The \acs{BHH} also incorporates a novel proxied heuristic update step, where various components of the update step for low-level heuristics are sourced from other heuristics in the pool of heuristics, when the direct application of a heuristic is not feasible/possible.
+
 Figure \ref{fig:bhh_architecture} provides an illustration of the high-level architecture of the \acs{BHH}.
@@
 	\label{eq:bhh:optimisation_step:map:alpha_update_operation}
-	\begin{split}
 	\alpha_{k}(t+1) = N_{k} + \alpha_{k}(t)
-	\end{split}
 \end{equation}
@@
 	\label{eq:bhh:optimisation_step:map:beta_update_operation}
-	\begin{split}
 	\beta_{j,k}(t+1) = N_{j,k} + \beta_{j,k}(t)
-	\end{split}
 \end{equation}
@@
 	\label{eq:bhh:optimisation_step:map:gamma1_update_operation}
-	\begin{split}
 	\gamma_{1,k}(t+1) = N_{1,k} + \gamma_{1,k}(t)
-	\end{split}
 \end{equation}
@@
 	\label{eq:bhh:optimisation_step:map:gamma2_update_operation}
-	\begin{split}
 	\gamma_{2,k}(t+1) = N_{0,k} + \gamma_{2,k}(t)
-	\end{split}
 \end{equation}
+
+\vspace{5mm}
 
@@
 \end{table}%
+
+A population size of 5 is chosen as it empirically and consistently provides good results.
+The population size has a lower bound of 4, which is the highest, minimum number of entities required by any low-level heuristic used in this research.
+Furthermore, ablation studies \citep{ref:schreuder:2022} have shown that a smaller population size is generally better, since the Bayesian analysis process implemented by the \acs{BHH} has less, but more concentrated performance information from which it has to learn.
 
@@
 	\centering
-	\caption{Empirical results showing normalised average rank and statistics for the bottom six low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
+	\caption{Empirical results showing normalised average rank and statistics for the bottom seven low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
 	\label{tab:results:standalone:metrics:rank_b}%
@@
 
-Figure \ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each heuristic, per dataset.
-The heuristics are ordered according to the normalised ranks presented in Tables \ref{tab:results:standalone:metrics:rank_a} and \ref{tab:results:standalone:metrics:rank_b}.
-Figure \ref{fig:results:standalone:descriptive:descriptive} shows that the \textit{bhh\_gd} heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics.
-The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\textwidth]{standalone_descriptive.pdf}
-	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all independent runs and epochs.}
-	\label{fig:results:standalone:descriptive:descriptive}
-\end{figure}
+Tables \ref{tab:results:standalone:metrics:accuracy_a} and \ref{tab:results:standalone:metrics:accuracy_b} provide the empirical results in accuracy format for the classification datasets.
+The accuracy is measured at the maximum epoch (30).
+
+\begin{table}[!tb]
+	\centering
+	\caption{Empirical results showing average accuracy at the max epoch (30) along with statistics for the top six low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:standalone:metrics:accuracy_a}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|llllll}
+			                                   & \multicolumn{6}{c}{\textbf{BHH vs.
+Low-Level Heuristics - Average accuracy at 30 epochs (Part A)}}                                                                                                                                                                                                                                                                                         \\
+			\cmidrule{2-7}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                                               & \multicolumn{1}{c}{\textbf{adam}}                     & \multicolumn{1}{c}{\textbf{rmsprop}}                  & \multicolumn{1}{c}{\textbf{bhh\_gd}}                  & \multicolumn{1}{c}{\textbf{nag}}                      & \multicolumn{1}{c}{\textbf{bhh\_all}}                 \\
+			\midrule
+			\textbf{abalone}                   & \cellcolor[rgb]{ .412,  .753,  .486}27.66\% (+-0.014)                                              & \cellcolor[rgb]{ .545,  .792,  .494}27.17\% (+-0.013) & \cellcolor[rgb]{ .388,  .745,  .482}27.74\% (+-0.016) & \cellcolor[rgb]{ .824,  .871,  .51}26.17\% (+-0.014)  & \cellcolor[rgb]{ .557,  .796,  .494}27.14\% (+-0.014) & \cellcolor[rgb]{ 1,  .922,  .518}25.52\% (+-0.021)    \\
+			\textbf{bank}                      & \cellcolor[rgb]{ .608,  .808,  .498}90.15\% (+-0.003)                                              & \cellcolor[rgb]{ .388,  .745,  .482}90.33\% (+-0.003) & \cellcolor[rgb]{ .482,  .773,  .49}90.25\% (+-0.003)  & \cellcolor[rgb]{ .949,  .906,  .518}89.88\% (+-0.003) & \cellcolor[rgb]{ .882,  .89,  .514}89.94\% (+-0.003)  & \cellcolor[rgb]{ 1,  .922,  .518}89.84\% (+-0.003)    \\
+			\textbf{car}                       & \cellcolor[rgb]{ .71,  .839,  .502}92.24\% (+-0.013)                                               & \cellcolor[rgb]{ .388,  .745,  .482}96.64\% (+-0.011) & \cellcolor[rgb]{ .427,  .757,  .486}96.13\% (+-0.018) & \cellcolor[rgb]{ .647,  .82,  .498}93.13\% (+-0.013)  & \cellcolor[rgb]{ .918,  .898,  .514}89.39\% (+-0.019) & \cellcolor[rgb]{ .612,  .812,  .498}93.59\% (+-0.017) \\
+			\textbf{diabetic}                  & \cellcolor[rgb]{ .604,  .808,  .498}58.14\% (+-0.004)                                              & \cellcolor[rgb]{ .996,  .902,  .514}57.23\% (+-0.004) & \cellcolor[rgb]{ .769,  .855,  .506}57.85\% (+-0.004) & \cellcolor[rgb]{ .82,  .871,  .51}57.76\% (+-0.006)   & \cellcolor[rgb]{ .388,  .745,  .482}58.53\% (+-0.003) & \cellcolor[rgb]{ .988,  .757,  .482}55.42\% (+-0.024) \\
+			\textbf{iris}                      & \cellcolor[rgb]{ .996,  .902,  .514}92\% (+-0.046)                                                 & \cellcolor[rgb]{ .627,  .816,  .498}94.89\% (+-0.042) & \cellcolor[rgb]{ .408,  .753,  .486}96.33\% (+-0.035) & \cellcolor[rgb]{ 1,  .922,  .518}92.44\% (+-0.077)    & \cellcolor[rgb]{ .388,  .745,  .482}96.44\% (+-0.037) & \cellcolor[rgb]{ .902,  .894,  .514}93.11\% (+-0.056) \\
+			\textbf{mushroom}                  & \cellcolor[rgb]{ .522,  .784,  .49}99.97\% (+-0)                                                   & \cellcolor[rgb]{ .471,  .769,  .49}99.98\% (+-0.001)  & \cellcolor[rgb]{ .388,  .745,  .482}100\% (+-0)       & \cellcolor[rgb]{ .471,  .769,  .49}99.98\% (+-0)      & \cellcolor[rgb]{ 1,  .922,  .518}99.84\% (+-0.001)    & \cellcolor[rgb]{ .537,  .788,  .494}99.96\% (+-0.001) \\
+			\textbf{wine\_quality}             & \cellcolor[rgb]{ .541,  .788,  .494}55.06\% (+-0.014)                                              & \cellcolor[rgb]{ .388,  .745,  .482}55.62\% (+-0.013) & \cellcolor[rgb]{ .592,  .804,  .494}54.86\% (+-0.011) & \cellcolor[rgb]{ 1,  .922,  .518}53.35\% (+-0.017)    & \cellcolor[rgb]{ .651,  .824,  .498}54.64\% (+-0.015) & \cellcolor[rgb]{ .941,  .906,  .518}53.57\% (+-0.015) \\
+		\end{tabular}%
+	}
+\end{table}%
+
+\begin{table}[!tb]
+	\centering
+	\caption{Empirical results showing average accuracy at the max epoch (30) along with statistics for the bottom seven low-level heuristics and three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}
+	\label{tab:results:standalone:metrics:accuracy_b}%
+	\par\bigskip
+	\resizebox{\textwidth}{!}{
+		\begin{tabular}{r|lllllll}
+			                                   & \multicolumn{7}{c}{\textbf{BHH vs.
+Low-Level Heuristics - Average accuracy at 30 epochs (Part B)}}                                                                                                                                                                                                                                                                                                                                                \\
+			\cmidrule{2-8}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adadelta}}                                                              & \multicolumn{1}{c}{\textbf{bhh\_mh}}                  & \multicolumn{1}{c}{\textbf{ga}}                       & \multicolumn{1}{c}{\textbf{pso}}                      & \multicolumn{1}{c}{\textbf{sgd}}                      & \multicolumn{1}{c}{\textbf{momentum}}                 & \multicolumn{1}{c}{\textbf{de}}                      \\
+			\midrule
+			\textbf{abalone}                   & \cellcolor[rgb]{ .659,  .824,  .498}26.76\% (+-0.013)                                              & \cellcolor[rgb]{ .992,  .839,  .498}23.32\% (+-0.018) & \cellcolor[rgb]{ .988,  .733,  .478}20.52\% (+-0.019) & \cellcolor[rgb]{ .984,  .651,  .463}18.31\% (+-0.029) & \cellcolor[rgb]{ .996,  .878,  .506}24.42\% (+-0.017) & \cellcolor[rgb]{ .996,  .875,  .506}24.29\% (+-0.015) & \cellcolor[rgb]{ .973,  .412,  .42}11.81\% (+-0.044) \\
+			\textbf{bank}                      & \cellcolor[rgb]{ .988,  .918,  .518}89.85\% (+-0.003)                                              & \cellcolor[rgb]{ .992,  .784,  .49}89.44\% (+-0.004)  & \cellcolor[rgb]{ .98,  .573,  .447}88.79\% (+-0.004)  & \cellcolor[rgb]{ .976,  .494,  .435}88.56\% (+-0.006) & \cellcolor[rgb]{ .98,  .596,  .455}88.86\% (+-0.004)  & \cellcolor[rgb]{ .984,  .643,  .463}89.01\% (+-0.003) & \cellcolor[rgb]{ .973,  .412,  .42}88.3\% (+-0.004)  \\
+			\textbf{car}                       & \cellcolor[rgb]{ 1,  .922,  .518}88.25\% (+-0.018)                                                 & \cellcolor[rgb]{ .988,  .714,  .475}80.74\% (+-0.034) & \cellcolor[rgb]{ .973,  .459,  .427}71.52\% (+-0.022) & \cellcolor[rgb]{ .988,  .725,  .478}81.16\% (+-0.035) & \cellcolor[rgb]{ .973,  .412,  .42}69.78\% (+-0.027)  & \cellcolor[rgb]{ .973,  .439,  .424}70.86\% (+-0.019) & \cellcolor[rgb]{ .973,  .416,  .42}69.98\% (+-0.034) \\
+			\textbf{diabetic}                  & \cellcolor[rgb]{ .482,  .773,  .49}58.36\% (+-0.003)                                               & \cellcolor[rgb]{ .992,  .847,  .502}56.53\% (+-0.006) & \cellcolor[rgb]{ .98,  .624,  .459}53.82\% (+-0.003)  & \cellcolor[rgb]{ .984,  .655,  .467}54.22\% (+-0.011) & \cellcolor[rgb]{ .992,  .922,  .518}57.45\% (+-0.004) & \cellcolor[rgb]{ 1,  .922,  .518}57.43\% (+-0.002)    & \cellcolor[rgb]{ .973,  .412,  .42}51.21\% (+-0.059) \\
+			\textbf{iris}                      & \cellcolor[rgb]{ .976,  .525,  .439}83.22\% (+-0.063)                                              & \cellcolor[rgb]{ .984,  .918,  .518}92.56\% (+-0.062) & \cellcolor[rgb]{ .988,  .757,  .486}88.67\% (+-0.091) & \cellcolor[rgb]{ .816,  .871,  .51}93.67\% (+-0.042)  & \cellcolor[rgb]{ .973,  .412,  .42}80.56\% (+-0.098)  & \cellcolor[rgb]{ .973,  .424,  .42}80.89\% (+-0.084)  & \cellcolor[rgb]{ .98,  .596,  .455}84.89\% (+-0.099) \\
+			\textbf{mushroom}                  & \cellcolor[rgb]{ .569,  .796,  .494}99.95\% (+-0.001)                                              & \cellcolor[rgb]{ .996,  .898,  .51}97.77\% (+-0.007)  & \cellcolor[rgb]{ .984,  .671,  .467}76.78\% (+-0.112) & \cellcolor[rgb]{ .996,  .906,  .514}98.67\% (+-0.009) & \cellcolor[rgb]{ .992,  .824,  .498}91.08\% (+-0.008) & \cellcolor[rgb]{ .992,  .804,  .494}89.11\% (+-0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}52.58\% (+-0.028) \\
+			\textbf{wine\_quality}             & \cellcolor[rgb]{ .647,  .82,  .498}54.66\% (+-0.012)                                               & \cellcolor[rgb]{ .992,  .835,  .498}51.52\% (+-0.014) & \cellcolor[rgb]{ .988,  .733,  .478}49.26\% (+-0.017) & \cellcolor[rgb]{ .984,  .686,  .471}48.21\% (+-0.038) & \cellcolor[rgb]{ .996,  .867,  .506}52.14\% (+-0.014) & \cellcolor[rgb]{ .992,  .831,  .498}51.38\% (+-0.014) & \cellcolor[rgb]{ .973,  .412,  .42}42.1\% (+-0.042)  \\
+		\end{tabular}%
+	}
+\end{table}%
 
@@
 
-\begin{figure}[htb]
+\begin{figure}[htbp]
 	\centering
@@
 A suggestion to improve on these results is to include a move-acceptance strategy where heuristic progressions are discarded if they fail to produce better results.
+
+Section \ref{sec:bhh:hyper_parameters} presented the \acs{BHH} hyper-parameters.
+A number of ablation studies were done in the interest of finding good hyper-parameters for the baseline \acs{BHH} \citep{ref:schreuder:2022}.
+A summary of these ablation studies on different hyper-parameter configurations is given in Table \ref{tab:methodology:experiments:bhh_variants} along with a brief conclusion of the outcomes.
+
+\begin{table}[htbp]
+	\centering
+	\caption{BHH variants and their configuration.
+The \index{heuristic pool}heuristic pool configuration \textit{gd} refers to the \index{heuristic pool}heuristic pool configuration where only gradient-based \index{heuristic}heuristics are included, and \textit{mh} refers to the \index{heuristic pool}heuristic pool configuration where only \acp{MH} are included.}
+	\label{tab:methodology:experiments:bhh_variants}%
+	\par\bigskip
+	\resizebox{0.9\textwidth}{!}{
+		\begin{tabular}{ccc}
+			\textbf{hyper-parameter} & \textbf{considered}                   & \textbf{conclusion}       \\
+			\midrule
+			heuristic pool           & all, gd, mh                           & gd performed best         \\
+			population               & 5, 10, 15, 20, 25                     & smaller is better         \\
+			credit                   & ibest, pbest, rbest, gbest, symmetric & problem dependent         \\
+			reselection              & 1, 5, 10, 15, 20                      & larger is better          \\
+			replay                   & 1, 5, 10, 15, 20                      & problem dependent         \\
+			reanalysis               & 1, 5, 10, 15, 20                      & problem dependent         \\
+			burn in                  & 0, 5, 10, 15, 20                      & lower is better           \\
+			normalise                & false, true                           & no significant difference \\
+			discounted rewards       & false, true                           & no significant difference \\
+		\end{tabular}%
+	}
+\end{table}%
+
+A general finding in the ablations studies revealed the inter-dependencies between the hyper-parameters.
+For example, there is an inter-dependency between the \textit{reselection}, \textit{replay}, and \textit{reanalysis} hyper-parameters.
+This can be seen in the ablation studies that focussed on the \textit{normalise} and \textit{discounted rewards} hyper-parameters.
+The default \textit{replay window size} (10) hyper-parameter, results in a scenario where the logged performance data is too little for the \textit{normalise} and \textit{discounted rewards} hyper-parameters to make a statistically significant impact.
+
+Furthermore, the ablation studies on the \textit{replay} and \textit{reanalysis} hyper-parameters, which resulted in problem dependent outcomes, illustrates that a dynamic, online-learning approach is required, since some problems benefit from maintaining many records in the performance log, while others do not.
 

### 2024-01-11 article/rebuttal/main.tex
💚 Dedicated to Taylah, Beané and Aleah

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{lipsum} % to generate some filler text
\usepackage{fullpage}
\usepackage{mathrsfs}
\usepackage{svg}
\usepackage{xr}
\usepackage{amsthm,cite,url,graphicx,booktabs,lipsum,color,bm,caption,subcaption,soul}
\usepackage{pifont,tikz,paralist,multirow,amssymb}
\usepackage{xifthen}
\usepackage{enumerate}
\usepackage{titlesec}
\usepackage[numbers]{natbib}
\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}

% This refines the format of how the reviewer/point reference will appear.
%\renewcommand{\thepoint}{C\,\thereviewer.\arabic{point}}

\renewcommand{\thepoint}{Comment\,\thereviewer.\arabic{point}}

% command declarations for reviewer points and our responses

\newenvironment{point1}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Editor Comment~}} ---\ }
   {\par }

\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule
                  \section*{Reviewer \thereviewer}}

% \newenvironment{point}

%    {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~\thepoint} } ---\ }
%    {\par }

\newenvironment{point}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~\thepoint} } ---\ }
   {\par }

\newcommand{\shortpoint}[1]{\refstepcounter{point}   \bigskip \noindent 
	{\textbf{Reviewer~Point~\thepoint} } ---~#1  }

\newenvironment{reply}
   {\medskip \noindent \color{blue} \begin{sf}\textbf{Reply}:\  }
   {\medskip \par \end{sf}}

\newcommand{\shortreply}[2][]{\medskip \noindent \begin{sf}\textbf{Reply}:\  #2
	\ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
	\medskip \end{sf}}

\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}

\myexternaldocument{main}
%\externaldocument[I-]{main}

\def\thesubsubsection{\arabic{subsubsection}}
\titleformat{\subsubsection}[runin]
{\normalfont\bfseries}
{\indent\thesubsubsection)}{0.5em}{}

\begin{document}
\section*{Response to reviewer comments for the paper:\\INS-D-23-781}
\vspace{10pt}

\textbf{Title:} Training Feedforward Neural Networks with Bayesian Hyper-Heuristics\\
\textbf{Authors:} A.N. Schreuder, A.S. Bosman, A.P. Engelbrecht, C.W. Cleghorn\\
\textbf{Manuscript number:} 1\\
\textbf{Revision Version:} 1\\
\textbf{Editor’s Decision Received Date:} 24 November 2023\\
\textbf{Revision Submission Date:} 10 January 2024\\

\vspace{10pt}

\noindent
The authors would like to thank the editor and reviewers for their constructive comments and suggestions that have helped improve the quality of this manuscript. The manuscript has undergone a thorough revision according to the editor's and reviewer's comments. Please see below our responses. For the editor's and reviewer's convenience, we have highlighted our responses to the comments and described how each comment is addressed in the revised manuscript in \textcolor{blue}{blue}.

\section*{Response to the Editor}
% General intro text goes here

\begin{point1}
	Dear authors, I want to apologize for the long process of peer review. We had severe issues to find suitable candidates. The second reviewer keeps ignoring all reminders, so that the decision of the first review round will be based on only a single reviewer. At the same time, I am pleased to inform you that R1 sees merit in your paper, along with several suggestions for further improvement. I wish you good luck in the revision!
\end{point1}

\begin{reply}
	The authors would like to thank the editor and reviewer again for their comments and the time taken to read the manuscript. All the issues raised by the reviewers are addressed in the following document. For each reviewer comment, the corresponding manuscript adjustment is discussed in detail. Where possible, we have highlighted the changes in the revised manuscript in \textcolor{blue}{blue} and provided line numbers for ease of reference.
\end{reply}

\section*{Response to the Reviewers}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reviewersection
This paper proposes a hyper-heuristic for neural network training. The paper has potential to be accepted, while it needs revision. Some comments in detail are below:

\begin{point}
	In the introduction section, the authors should briefly explain their heuristic. Please again explain the proposed method briefly in this section
\end{point}

\begin{reply}
	We have added a brief overview of the BHH algorithm in the introduction section. Please see the revised manuscript, page 3, lines 29-46.
\end{reply}

\begin{point}
	``This research takes a particular interest in population
	based MHs that have been used to train FFNNs. These include particle
	swarm optimisation (PSO) [20], differential evolution (DE) [21] and genetic
	algorithms (GAs) [22].''\\
	Please add some more recent papers.
\end{point}

\begin{reply}
	We have updated these references to reflect the latest, highly cited journal articles we could find on each of the topics. These include \cite{ref:abdulkarim:2021}, \cite{ref:khan:2012}, and \cite{ref:xue:2022} (See references at the end of this document).
\end{reply}

\begin{point}
	Is there any reasons to select the population size as 5?
\end{point}

\begin{reply}
	A population size of 5 was chosen as it empirically and consistently provided good results. The population size has a lower bound of 4, which is the highest, minimum number of entities required by any low-level heuristic used in this research. Furthermore, our ablation studies \cite{ref:schreuder:2022} have shown that a smaller population size is generally better, since the Bayesian analysis process implemented by the BHH has less, but more concentrated performance information from which it has to learn. We have added a brief discussion on the population size in the revised manuscript. Please see page 20, lines 337-383.
\end{reply}

\begin{point}
	In Figure 3, the points are connected together, while I believe that using a connection between two points is not right! For instance between ``momentum'' and ``de'', there is a connected line. What does mean this connection?
\end{point}

\begin{reply}
	We agree with the comments made and as such we have decided to remove the original Figure 3, since we felt that the figure shows redundant information which is already given in Tables 7 and 8. Furthermore, we felt that the other suggestions made by the reviewer, such as adding classification results, adds more value.
\end{reply}

\begin{point}
	Please provide more classification results such as accuracy!
\end{point}

\begin{reply}
	We have added Tables 9 and 10 which contain classification results as requested. Please see the revised manuscript, pages 31-32.
\end{reply}

\begin{point}
	Please provide a sensitivity analysis on the proposed algorithm?
\end{point}

\begin{reply}
	This is a great suggestion! We have done extensive ablation studies on the BHH algorithm, but originally left this out for brevity. These studies can be found in \cite{ref:schreuder:2022}. We have added a brief discussion and summary of the findings in the ablation studies in the revised manuscript. Please see page 33, lines 542-553.
\end{reply}

\begin{point}
	Can the algorithm extend on other type of ANNs simply?
\end{point}

\begin{reply}
	Yes it can! Although this research takes a particular interest in training FFNNs, the BHH is not limited to these types of models and can generally be applied to any ANN as long as the ANN can be trained by all of the low-level heuristics. Experimentation with other ANN architectures besides FFNNs was left for future research. We have added this context to the introduction section. Please see page 4, lines 57-61.
\end{reply}

\bibliographystyle{plainnat}
\bibliography{references.bib}

\end{document}

### 2024-08-15 article/main.tex
💚 For Taylah, Beané & Aleah

@@
 Although this research takes a particular interest in training \acp{FFNN}, the \acs{BHH} is not limited to these types of models and can generally be applied to any \acs{ANN} as long as the \acs{ANN} can be trained by all of the low-level heuristics.
-Experimentation with other \acp{ANN} architectures besides \acp{FFNN} is left for future research.
+Experimentation with other \acs{ANN} architectures besides \acp{FFNN} is left for future research.
 
@@
 \acp{FFNN} were the first and simplest type of \acp{ANN} developed \citep{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order.
-Furthermore, \acp{FFNN} implement fully connected topologies, where each \acf{AN} in one layer is connected to all the \acp{AN} in the next, without any cycles \citep{ref:zell:1994}.
+Furthermore, \acp{FFNN} implement fully connected topologies, where each \acf{AN} in one layer is connected to all the \acp{AN} in the next, without any cycles.
 In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.
@@
 However, they all fundamentally apply the same generic \acs{GD} framework that propagates the error signal backwards through the \acs{ANN}.
-This algorithm is known as \acf{BP}, was popularised by \citet{ref:werbos:1994}.
+This algorithm is known as \acf{BP}.
 
@@
 \citet{ref:blum:2003} provide advantages of \acp{MH} that include the following: they are easy to implement, they are problem independent and do not require problem-specific knowledge, and they are generally designed to find global optima, while gradient-based approaches can get stuck in local optima more often.
-Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \citep{ref:rakitianskaia:2012, ref:vanwyk:2014, ref:gupta:1999}.
+Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \citep{ref:rakitianskaia:2012, ref:vanwyk:2014}.
 This research takes a particular interest in population-based \acp{MH} that have been used to train \acp{FFNN}.
@@
 \citet{ref:burke:2010} propose a classification scheme used to classify \acp{HH}.
-According to the proposed classification scheme, \acp{HH} are classified in two dimensions.
+According to the proposed classification scheme, \acp{HH} are classified in two categories.
 These include the \textit{source of feedback} used during learning and the nature of the \textit{heuristic search space}.
-For the dimension that involves the source of feedback, \acp{HH} can be classified as either \textit{no learning}, \textit{online learning} or \textit{offline learning}.
-For the dimension that involves the nature of the \textit{heuristic search space}, \acp{HH} can be classified as either \textit{heuristic selection} or \textit{heuristic generation}.
+For the category that involves the source of feedback, \acp{HH} can be classified as either \textit{no learning}, \textit{online learning} or \textit{offline learning}.
+For the category that involves the nature of the \textit{heuristic search space}, \acp{HH} can be classified as either \textit{heuristic selection} or \textit{heuristic generation}.
 Further distinction is made between \textit{construction} of heuristics and \textit{perturbation} of heuristics.
@@
 In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems.
-Some notable examples include \citep{ref:burke:2010, ref:dowsland:2007, ref:grobler:2012, ref:vanderstockt:2018}.
+Some notable examples include \citep{ref:burke:2010, ref:grobler:2012, ref:vanderstockt:2018}.
 Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce.
@@
 Population state is also referred to as \textit{global} state and represents the population's memory.
-The population state generally contains state parameters that are of importance to multiple heuristics, and usually tracks the state of the population and not individual heuristic.
+The population state generally contains state parameters that are of importance to multiple heuristics, and usually tracks the state of the population and not the state of individual heuristics.
 Some examples of population state that can arise from different heuristics include the population of entities themselves, the global best entity found so far, the overall best loss achieved thus far, and so on.
@@
 The number of hidden units used were determined empirically.
-Weights are initialised by means of \textit{Glorot uniform sampling} \citep{ref:glorot:2010}.
+Weights are initialised by means of \textit{Glorot uniform sampling}.
 The models and their configuration, as it is used for each dataset, are given in Table \ref{tab:methodology:models:configurations}.
@@
 
-The Shapiro-Wilk test for normality \citep{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
-The Levene's test for equality of variance \citep{ref:levene:1961} ($\alpha$ = 0.001) is used.
-For experiments with three or more configurations, the \acs{ANOVA} statistical test \citep{ref:fisher:1921} ($\alpha$ = 0.001) is used.
-The Kruskal-Wallis ranked non-parametric test \citep{ref:kruskal:1952} for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
-Finally, a post-hoc Tukey honest significant difference test \citep{ref:tukey:1949} ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
+The Shapiro-Wilk test for normality ($\alpha$ = 0.001) is used to determine if the results are normally distributed.
+The Levene's test for equality of variance ($\alpha$ = 0.001) is used.
+For experiments with three or more configurations, the \acs{ANOVA} statistical test ($\alpha$ = 0.001) is used.
+The Kruskal-Wallis ranked non-parametric test for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed.
+Finally, a post-hoc Tukey honest significant difference test ($\alpha$ = 0.001) is used from which significant ranking is retrieved.
 Descriptive and critical difference plots are then retrieved from these results to provide visual aid.

### 2024-08-15 article/rebuttal_v2/main.tex
💚 For Taylah, Beané & Aleah

--- 2024-01-11 article/rebuttal/main.tex
@@
 \textbf{Manuscript number:} 1\\
-\textbf{Revision Version:} 1\\
-\textbf{Editor’s Decision Received Date:} 24 November 2023\\
-\textbf{Revision Submission Date:} 10 January 2024\\
+\textbf{Revision Version:} 2\\
+\textbf{Editor’s Decision Received Date:} 7 August 2024\\
+\textbf{Revision Submission Date:} 16 Aug 2024\\
 
@@
 The authors would like to thank the editor and reviewers for their constructive comments and suggestions that have helped improve the quality of this manuscript.
-The manuscript has undergone a thorough revision according to the editor's and reviewer's comments.
-Please see below our responses.
+The manuscript has undergone a final thorough revision (version 2) according to the editor's and reviewer's comments.
+Please see below our responses to the latest feedback.
 For the editor's and reviewer's convenience, we have highlighted our responses to the comments and described how each comment is addressed in the revised manuscript in \textcolor{blue}{blue}.
@@
 \begin{point1}
-	Dear authors, I want to apologize for the long process of peer review.
-We had severe issues to find suitable candidates.
-The second reviewer keeps ignoring all reminders, so that the decision of the first review round will be based on only a single reviewer.
-At the same time, I am pleased to inform you that R1 sees merit in your paper, along with several suggestions for further improvement.
-I wish you good luck in the revision!
+	\begin{itemize}
+		\item A thorough editing is required; show all changes made to the revised manuscript.
+		\item References: max 50 entries. Make sure the references are recent and highly pertinent to the contents of the manuscript.
+	\end{itemize}
 \end{point1}
@@
 	The authors would like to thank the editor and reviewer again for their comments and the time taken to read the manuscript.
-All the issues raised by the reviewers are addressed in the following document.
-For each reviewer comment, the corresponding manuscript adjustment is discussed in detail.
-Where possible, we have highlighted the changes in the revised manuscript in \textcolor{blue}{blue} and provided line numbers for ease of reference.
-\end{reply}
+All the issues raised by the editor/reviewers are addressed in the following document.
+A number of grammatical and language improvements have been made, and the references are updated and now capped at 49 as requested.
+A summary of the changes made is given as follows:
 
-\section*{Response to the Reviewers}
+	\begin{itemize}
+		\item Changed FFNNs to FFNN in the paragraph about the BHH's applicability to different ANN types.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\reviewersection
-This paper proposes a hyper-heuristic for neural network training. The paper has potential to be accepted, while it needs revision. Some comments in detail are below:
+		\item Removed citation ``\citep{ref:zell:1994}'' from the sentence about FFNN topologies.
+		\item Removed ``was popularised by \citet{ref:werbos:1994}'' from the sentence about the backpropagation algorithm.
+		\item Removed citation ``\citep{ref:gupta:1999}'' from the list of references about meta-heuristics used to train FFNNs.
+		\item Changed ``dimensions'' to ``categories'' when describing the classification scheme for hyper-heuristics. Also changed subsequent uses of ``dimension'' to ``category''.
+		\item Removed citation ``\citep{ref:dowsland:2007}'' from the list of examples of hyper-heuristics in optimization.
+		\item Changed ``not individual heuristic'' to ``not the state of individual heuristics'' when describing what the population state tracks.
+		\item Removed citation ``\citep{ref:glorot:2010}'' from the sentence about Glorot uniform sampling for weight initialization.
+		\item Removed citations for various statistical tests: Shapiro-Wilk test, Levene's test, ANOVA test, Kruskal-Wallis test, and Tukey honest significant difference test.
+	\end{itemize}
 
-\begin{point}
-	In the introduction section, the authors should briefly explain their heuristic. Please again explain the proposed method briefly in this section
-\end{point}
-
-\begin{reply}
-	We have added a brief overview of the BHH algorithm in the introduction section. Please see the revised manuscript, page 3, lines 29-46.
-\end{reply}
-
-\begin{point}
-	``This research takes a particular interest in population
-	based MHs that have been used to train FFNNs. These include particle
-	swarm optimisation (PSO) [20], differential evolution (DE) [21] and genetic
-	algorithms (GAs) [22].''\\
-	Please add some more recent papers.
-\end{point}
-
-\begin{reply}
-	We have updated these references to reflect the latest, highly cited journal articles we could find on each of the topics.
-These include \cite{ref:abdulkarim:2021}, \cite{ref:khan:2012}, and \cite{ref:xue:2022} (See references at the end of this document).
-\end{reply}
-
-\begin{point}
-	Is there any reasons to select the population size as 5?
-\end{point}
-
-\begin{reply}
-	A population size of 5 was chosen as it empirically and consistently provided good results.
-The population size has a lower bound of 4, which is the highest, minimum number of entities required by any low-level heuristic used in this research.
-Furthermore, our ablation studies \cite{ref:schreuder:2022} have shown that a smaller population size is generally better, since the Bayesian analysis process implemented by the BHH has less, but more concentrated performance information from which it has to learn.
-We have added a brief discussion on the population size in the revised manuscript.
-Please see page 20, lines 337-383.
-\end{reply}
-
-\begin{point}
-	In Figure 3, the points are connected together, while I believe that using a connection between two points is not right!
-For instance between ``momentum'' and ``de'', there is a connected line.
-What does mean this connection?
-\end{point}
-
-\begin{reply}
-	We agree with the comments made and as such we have decided to remove the original Figure 3, since we felt that the figure shows redundant information which is already given in Tables 7 and 8.
-Furthermore, we felt that the other suggestions made by the reviewer, such as adding classification results, adds more value.
-\end{reply}
-
-\begin{point}
-	Please provide more classification results such as accuracy!
-\end{point}
-
-\begin{reply}
-	We have added Tables 9 and 10 which contain classification results as requested. Please see the revised manuscript, pages 31-32.
-\end{reply}
-
-\begin{point}
-	Please provide a sensitivity analysis on the proposed algorithm?
-\end{point}
-
-\begin{reply}
-	This is a great suggestion!
-We have done extensive ablation studies on the BHH algorithm, but originally left this out for brevity.
-These studies can be found in \cite{ref:schreuder:2022}.
-We have added a brief discussion and summary of the findings in the ablation studies in the revised manuscript.
-Please see page 33, lines 542-553.
-\end{reply}
-
-\begin{point}
-	Can the algorithm extend on other type of ANNs simply?
-\end{point}
-
-\begin{reply}
-	Yes it can!
-Although this research takes a particular interest in training FFNNs, the BHH is not limited to these types of models and can generally be applied to any ANN as long as the ANN can be trained by all of the low-level heuristics.
-Experimentation with other ANN architectures besides FFNNs was left for future research.
-We have added this context to the introduction section.
-Please see page 4, lines 57-61.
 \end{reply}

### 2025-01-13 dissertation/appendix/symbols.tex
💚 For Taylah, Beané & Aleah

--- 2022-12-09 dissertation/appendix/symbols.tex
@@
 This appendix summarises the important symbols used throughout the dissertation.
-For each symbol, a short description is provided as well as the reference to the equation that makes use it.
+A short description is provided for each symbol.
 Symbols are divided according to the chapter in which they were introduced and are ordered alphabetically.
@@
 	% \item
-	%       [\parbox{2cm}{$EXAMPLE$}] THIS IS AN EXAMPLE DESCRIPTION. \lbrack Eq.~\eqref{eq:an_function_mapping} pg.~\pageref{eq:an_function_mapping} \rbrack
+	%       [\parbox{2cm}{$EXAMPLE$}] \parbox{12.5cm}{THIS IS AN EXAMPLE DESCRIPTION. \lbrack Eq.~\eqref{eq:an_function_mapping} pg.~\pageref{eq:an_function_mapping} \rbrack}
 
-	\item [\parbox{2cm}{$I$}] The input pattern's dimension size.
-	\item [\parbox{2cm}{$T$}] The target pattern's dimension size.
-	\item [\parbox{2cm}{$\mathbb{R}$}] The real-number space.
-	\item [\parbox{2cm}{$\mathbb{R}^{I}$}] The real-number space in I dimensions.
-	\item [\parbox{2cm}{$\mathbb{R}^{T}$}] The real-number space in T dimensions.
-	\item [\parbox{2cm}{$f_{AN}$}] The mapping function realised by the \acs{AN}.
-	\item [\parbox{2cm}{$\boldsymbol{x}$}] The input pattern/vector.
-	\item [\parbox{2cm}{$x_{i}$}] The $i$-th dimension of the input pattern/vector.
-	\item [\parbox{2cm}{$\theta$}] The bias unit.
-	\item [\parbox{2cm}{$\boldsymbol{v}$}] The weight vector.
-	\item [\parbox{2cm}{$v_{i}$}] The $i$-th dimension of the weight vector.
-	\item [\parbox{2cm}{$net$}] The net input signal to the \acs{AN}.
-	\item [\parbox{2cm}{$f(net)$}] The activation function over net input signal.
-	\item [\parbox{2cm}{$\boldsymbol{y}$}] The output vector.
-	\item [\parbox{2cm}{$\boldsymbol{y}_{p}$}] The output vector for pattern $p$.
-	\item [\parbox{2cm}{$k$}] Index for the output vector.
-	\item [\parbox{2cm}{$x_{i,p}^{'}$}] The normalised form of the input at dimension $i$, pattern $p$.
-	\item [\parbox{2cm}{$x_{i,p}$}] The original input at dimension $i$, pattern $p$.
-	\item [\parbox{2cm}{$x_{i_{min}}$}] The input's minimum value at dimension $i$.
-	\item [\parbox{2cm}{$x_{i_{max}}$}] The input's maximum value at dimension $i$.
-	\item [\parbox{2cm}{$p$}] Index for the input data patterns.
-	\item [\parbox{2cm}{$P$}] Total number of input data patterns.
-	\item [\parbox{2cm}{$\boldsymbol{x}_p$}] The $p$-th input vector/pattern.
-	\item [\parbox{2cm}{$\mu_i$}] The mean of the input at dimension $i$.
-	\item [\parbox{2cm}{$\sigma^2_i$}] The unit variance of the input at dimension $i$.
-	\item [\parbox{2cm}{$i$}] Index for the input vector.
-	\item [\parbox{2cm}{$\omega$}] The general weight vector used for normalisation.
-	\item [\parbox{2cm}{$\omega_{i}$}] The general weight vector used for normalisation at dimension $i$.
-	\item [\parbox{2cm}{$\omega_{min}$}] The lower bound of the uniform distribution used for weights initialisation.
-	\item [\parbox{2cm}{$\omega_{max}$}] The upper bound of the uniform distribution used for weights initialisation.
-	\item [\parbox{2cm}{$fanin$}] The number of input neurons to the weight vector.
-	\item [\parbox{2cm}{$fanout$}] The number of output neurons from the weight vector.
-	\item [\parbox{2cm}{$\sigma$}] The standard deviation of the truncated normal distribution used for weight initialisation.
-	\item [\parbox{2cm}{$K$}] Number of output units.
-	\item [\parbox{2cm}{$x_{i+1}$}] The $i+1$-th dimension of the input pattern/vector.
-	\item [\parbox{2cm}{$v_{i+1}$}] The $i+1$-th dimension of the weight vector.
-	\item [\parbox{2cm}{$net^{'}$}] The augmented net input signal that includes the bias term.
-	\item [\parbox{2cm}{$\tau$}] Phase shift threshold parameter.
-	\item [\parbox{2cm}{$f(x)$}] The function used to describe the \acs{LReLU} activation function.
-	\item [\parbox{2cm}{$f$}] A shorted form of the activation function.
-	\item [\parbox{2cm}{$x^{+}$}] The positive part of the input parameter's domain.
-	\item [\parbox{2cm}{$\alpha$}] Scaling parameter used by the \acs{LReLU} activation function.
-	\item [\parbox{2cm}{$\lambda$}] Scaling/control parameter used by the sigmoid and tanh activation functions.
-	\item [\parbox{2cm}{$x_{min}$}] The input's minimum value used by the min-max scaler.
-	\item [\parbox{2cm}{$x_{max}$}] The input's maximum value used by the min-max scaler.
-	\item [\parbox{2cm}{$\mathbb{R}^{K}$}] The real-number space in $K$ dimensions.
-	\item [\parbox{2cm}{$y_{k}$}] The $k$-th dimension of the output vector.
-	\item [\parbox{2cm}{$y^{'}_k$}] The softmax value of the output at dimension $k$.
-	\item [\parbox{2cm}{$\boldsymbol{y^{'}}$}] The softmax form of the output vector.
-	\item [\parbox{2cm}{$h_{j}$}] The $j$-th dimension of the hidden layer.
-	\item [\parbox{2cm}{$j$}] Index used for the hidden layer.
-	\item [\parbox{2cm}{$v_{i,j}$}] The weight associated with input node $x_{i}$ and the hidden node $h_{j}$.
-	\item [\parbox{2cm}{$w_{j,k}$}] The weight associated with hidden node $h_{j}$ and the output node $y_{k}$.
-	\item [\parbox{2cm}{$net_{i,h}$}] The net input signal at the hidden layer.
-	\item [\parbox{2cm}{$net_{h,y}$}] The net input signal at the output layer.
-	\item [\parbox{2cm}{$\epsilon$}] The cost/loss produced by the loss function.
-	\item [\parbox{2cm}{$y_{k,p}$}] The output produced by the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.
-	\item [\parbox{2cm}{$\hat{y}_{k,p}$}] The target output for the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.
-	\item [\parbox{2cm}{$\beta$}] Mini-batch size.
-	\item [\parbox{2cm}{$\mathbbm{1}$}] The indicator function.
-	\item [\parbox{2cm}{$c$}] Index used for $c$-th class.
-	\item [\parbox{2cm}{$C$}] Total number of classes.
+	\item [\parbox{2cm}{$\alpha$}] \parbox{12.5cm}{Scaling parameter used by the \acs{LReLU} activation function.}
+	\item [\parbox{2cm}{$\beta$}] \parbox{12.5cm}{Mini-batch size.}
+	\item [\parbox{2cm}{$\boldsymbol{v}$}] \parbox{12.5cm}{The weight vector.}
+	\item [\parbox{2cm}{$\boldsymbol{x}_p$}] \parbox{12.5cm}{The $p$-th input vector/pattern.}
+	\item [\parbox{2cm}{$\boldsymbol{x}$}] \parbox{12.5cm}{The input pattern/vector.}
+	\item [\parbox{2cm}{$\boldsymbol{y}_{p}$}] \parbox{12.5cm}{The output vector for pattern $p$.}
+	\item [\parbox{2cm}{$\boldsymbol{y}$}] \parbox{12.5cm}{The output vector.}
+	\item [\parbox{2cm}{$\boldsymbol{y^{'}}$}] \parbox{12.5cm}{The softmax form of the output vector.}
+	\item [\parbox{2cm}{$\epsilon$}] \parbox{12.5cm}{The cost/loss produced by the loss function.}
+	\item [\parbox{2cm}{$\hat{y}_{k,p}$}] \parbox{12.5cm}{The target output for the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.}
+	\item [\parbox{2cm}{$\lambda$}] \parbox{12.5cm}{Scaling/control parameter used by the sigmoid and tanh activation functions.}
+	\item [\parbox{2cm}{$\mathbb{R}^{I}$}] \parbox{12.5cm}{The real-number space in I dimensions.}
+	\item [\parbox{2cm}{$\mathbb{R}^{K}$}] \parbox{12.5cm}{The real-number space in $K$ dimensions.}
+	\item [\parbox{2cm}{$\mathbb{R}^{T}$}] \parbox{12.5cm}{The real-number space in T dimensions.}
+	\item [\parbox{2cm}{$\mathbb{R}$}] \parbox{12.5cm}{The real-number space.}
+	\item [\parbox{2cm}{$\mathbbm{1}$}] \parbox{12.5cm}{The indicator function.}
+	\item [\parbox{2cm}{$\mu_i$}] \parbox{12.5cm}{The mean of the input at dimension $i$.}
+	\item [\parbox{2cm}{$\omega_{i}$}] \parbox{12.5cm}{The general weight vector used for normalisation at dimension $i$.}
+	\item [\parbox{2cm}{$\omega_{max}$}] \parbox{12.5cm}{The upper bound of the uniform distribution used for weights initialisation.}
+	\item [\parbox{2cm}{$\omega_{min}$}] \parbox{12.5cm}{The lower bound of the uniform distribution used for weights initialisation.}
+	\item [\parbox{2cm}{$\omega$}] \parbox{12.5cm}{The general weight vector used for normalisation.}
+	\item [\parbox{2cm}{$\sigma^2_i$}] \parbox{12.5cm}{The unit variance of the input at dimension $i$.}
+	\item [\parbox{2cm}{$\sigma$}] \parbox{12.5cm}{The standard deviation of the truncated normal distribution used for weight initialisation.}
+	\item [\parbox{2cm}{$\tau$}] \parbox{12.5cm}{Phase shift threshold parameter.}
+	\item [\parbox{2cm}{$\theta$}] \parbox{12.5cm}{The bias unit.}
+	\item [\parbox{2cm}{$c$}] \parbox{12.5cm}{Index used for $c$-th class.}
+	\item [\parbox{2cm}{$C$}] \parbox{12.5cm}{Total number of classes.}
+	\item [\parbox{2cm}{$f_{AN}$}] \parbox{12.5cm}{The mapping function realised by the \acs{AN}.}
+	\item [\parbox{2cm}{$f(net)$}] \parbox{12.5cm}{The activation function over net input signal.}
+	\item [\parbox{2cm}{$f(x)$}] \parbox{12.5cm}{The function used to describe the \acs{LReLU} activation function.}
+	\item [\parbox{2cm}{$f$}] \parbox{12.5cm}{A shortened form of the activation function.}
+	\item [\parbox{2cm}{$fanin$}] \parbox{12.5cm}{The number of input neurons to the weight vector.}
+	\item [\parbox{2cm}{$fanout$}] \parbox{12.5cm}{The number of output neurons from the weight vector.}
+	\item [\parbox{2cm}{$h_{j}$}] \parbox{12.5cm}{The $j$-th dimension of the hidden layer.}
+	\item [\parbox{2cm}{$i$}] \parbox{12.5cm}{Index for the input vector.}
+	\item [\parbox{2cm}{$I$}] \parbox{12.5cm}{The input pattern's dimension size.}
+	\item [\parbox{2cm}{$j$}] \parbox{12.5cm}{Index used for the hidden layer.}
+	\item [\parbox{2cm}{$k$}] \parbox{12.5cm}{Index for the output vector.}
+	\item [\parbox{2cm}{$K$}] \parbox{12.5cm}{Number of output units.}
+	\item [\parbox{2cm}{$net_{h,y}$}] \parbox{12.5cm}{The net input signal at the output layer.}
+	\item [\parbox{2cm}{$net_{i,h}$}] \parbox{12.5cm}{The net input signal at the hidden layer.}
+	\item [\parbox{2cm}{$net^{'}$}] \parbox{12.5cm}{The augmented net input signal that includes the bias term.}
+	\item [\parbox{2cm}{$net$}] \parbox{12.5cm}{The net input signal to the \acs{AN}.}
+	\item [\parbox{2cm}{$p$}] \parbox{12.5cm}{Index for the input data patterns.}
+	\item [\parbox{2cm}{$P$}] \parbox{12.5cm}{Total number of input data patterns.}
+	\item [\parbox{2cm}{$T$}] \parbox{12.5cm}{The target pattern's dimension size.}
+	\item [\parbox{2cm}{$v_{i,j}$}] \parbox{12.5cm}{The weight associated with input node $x_{i}$ and the hidden node $h_{j}$.}
+	\item [\parbox{2cm}{$v_{i}$}] \parbox{12.5cm}{The $i$-th dimension of the weight vector.}
+	\item [\parbox{2cm}{$v_{i+1}$}] \parbox{12.5cm}{The $i+1$-th dimension of the weight vector.}
+	\item [\parbox{2cm}{$w_{j,k}$}] \parbox{12.5cm}{The weight associated with hidden node $h_{j}$ and the output node $y_{k}$.}
+	\item [\parbox{2cm}{$x_{i_{max}}$}] \parbox{12.5cm}{The input's maximum value at dimension $i$.}
+	\item [\parbox{2cm}{$x_{i_{min}}$}] \parbox{12.5cm}{The input's minimum value at dimension $i$.}
+	\item [\parbox{2cm}{$x_{i,p}^{'}$}] \parbox{12.5cm}{The normalised form of the input at dimension $i$, pattern $p$.}
+	\item [\parbox{2cm}{$x_{i,p}$}] \parbox{12.5cm}{The original input at dimension $i$, pattern $p$.}
+	\item [\parbox{2cm}{$x_{i}$}] \parbox{12.5cm}{The $i$-th dimension of the input pattern/vector.}
+	\item [\parbox{2cm}{$x_{i+1}$}] \parbox{12.5cm}{The $i+1$-th dimension of the input pattern/vector.}
+	\item [\parbox{2cm}{$x_{max}$}] \parbox{12.5cm}{The input's maximum value used by the min-max scaler.}
+	\item [\parbox{2cm}{$x_{min}$}] \parbox{12.5cm}{The input's minimum value used by the min-max scaler.}
+	\item [\parbox{2cm}{$x^{+}$}] \parbox{12.5cm}{The positive part of the input parameter's domain.}
+	\item [\parbox{2cm}{$y_{k,p}$}] \parbox{12.5cm}{The output produced by the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.}
+	\item [\parbox{2cm}{$y_{k}$}] \parbox{12.5cm}{The $k$-th dimension of the output vector.}
+	\item [\parbox{2cm}{$y^{'}_k$}] \parbox{12.5cm}{The softmax value of the output at dimension $k$.}
 
@@
 \begin{description}
-	\item [\parbox{2cm}{$f$}] A shortened form of the objective function being optimised.
-	\item [\parbox{2cm}{$x$}] The independent variables to the objective function. Also used in \acs{DE} notation to denote the selection mechanism for the trial vector.
-	\item [\parbox{2cm}{$f(x)$}] The objective function over $x$.
-	\item [\parbox{2cm}{$\epsilon$}] The error between the output of the \acs{FFNN} and the target pattern, produced by the loss function.
-Also used as a small error value used by heuristics to avoid division by 0.
-	\item [\parbox{2cm}{$\mathcal{E}$}] The error function.
-	\item [\parbox{2cm}{$w_{i}(t)$}] The $i$-th dimension of the weight vector at time step $t$.
-	\item [\parbox{2cm}{$w_{i}(t-1)$}] The $i$-th dimension of the weight vector at time step $t-1$.
-	\item [\parbox{2cm}{$\Delta w_{i}(t)$}] The change in the $i$-th dimension of the weight vector at time step $t$.
-	\item [\parbox{2cm}{$w_{i}$}] The $i$-th dimension of the weight vector.
-	\item [\parbox{2cm}{$i$}] Index used for the weight vector. Also used as the index for the $i$-th particle in the population, implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$\boldsymbol{w}$}] The weight vector.
-	\item [\parbox{2cm}{$p$}] Index used for input data patterns.
-	\item [\parbox{2cm}{$o_{i,p}$}] The $i$-th dimension of the output for pattern $p$.
-	\item [\parbox{2cm}{$t_{i,p}$}] The $i$-th dimension of the target for pattern $p$.
-	      item [\parbox{2cm}{$o_{k,p}$}] The $k$-th dimension of the output for pattern $p$.
-	\item [\parbox{2cm}{$t_{k,p}$}] The $k$-th dimension of the target for pattern $p$.
-	\item [\parbox{2cm}{$net_{p}$}] The net input signal for pattern $p$.
-	\item [\parbox{2cm}{$z_{i,p}$}] The input value at index $i$ for pattern $p$.
-	\item [\parbox{2cm}{$\boldsymbol{g}$}] General symbol used to represent the gradient vector, retrieved from the error function relative to the weight vector.
-	\item [\parbox{2cm}{$\boldsymbol{v}$}] The velocity vector resulting from \acs{Momentum}.
-	\item [\parbox{2cm}{$\boldsymbol{w}$}] General symbol used to represent the weight vector.
-	\item [\parbox{2cm}{$\epsilon_{T}$}] The error at time step $T$.
-	\item [\parbox{2cm}{$\epsilon_{T_{p}}$}] The error produced for pattern $p$ at time step $T$.
-	\item [\parbox{2cm}{$\eta$}] Learning rate.
-	\item [\parbox{2cm}{$k$}] Index used for the output layer.
-	\item [\parbox{2cm}{$K$}] Total number of output units.
-	\item [\parbox{2cm}{$t$}] Time step.
-	\item [\parbox{2cm}{$T$}] Time step.
-	\item [\parbox{2cm}{$\alpha$}] The momentum hyper-parameter.
-	\item [\parbox{2cm}{$w_{t,i}$}] The $i$-th dimension of the weight vector at time step $t$.
-	\item [\parbox{2cm}{$w_{t+1,i}$}] The $i$-th dimension of the weight vector at time step $t+1$.
-	\item [\parbox{2cm}{$G_{t,ii}$}] Diagonal matrix containing the sum of the squared gradients with regards to the $i$-th dimension of the weight vector.
-	\item [\parbox{2cm}{$g_{t,i}$}] The $i$-th dimension of the gradient vector at time step $t$.
-	\item [\parbox{2cm}{$\boldsymbol{G_{t}}$}] The sum of the squares of the gradients.
-	\item [\parbox{2cm}{$G_{t,i}$}] The sum of the squared gradients with regards to the $i$-th dimension of the weight vector.
-	\item [\parbox{2cm}{$\odot$}] The matrix-vector product.
-	\item [\parbox{2cm}{$W$}] Window size of previous squared gradients.
-	\item [\parbox{2cm}{$E[\boldsymbol{g}^{2}]_{t}$}] The expected value of the squared gradients at time step $t$.
-	\item [\parbox{2cm}{$E[\boldsymbol{g}^{2}]_{t - 1}$}] The expected value of the squared gradients at time step $t-1$.
-	\item [\parbox{2cm}{$\boldsymbol{g}^{2}_{t}$}] The squared gradient vector at time step $t$.
-	\item [\parbox{2cm}{$\boldsymbol{w}_{t+1}$}] The weight vector at time step $t+1$.
-	\item [\parbox{2cm}{$\boldsymbol{w}_{t}^{2}$}] The squared weight vector at time step $t$.
-	\item [\parbox{2cm}{$\boldsymbol{g}_{t}$}] The gradient vector at time step $t$.
-	\item [\parbox{2cm}{$RMS$}] The root mean squared error criterion.
-	\item [\parbox{2cm}{$E[\Delta \boldsymbol{w}^{2}]_{t}$}] The expected value of the delta of the squared weight vector at time step $t$.
-	\item [\parbox{2cm}{$E[\Delta \boldsymbol{w}^{2}]_{t - 1}$}] The expected value of the delta of the squared weight vector at time step $t-1$.
-	\item [\parbox{2cm}{$\Delta \boldsymbol{w}^{2}_{t}$}] The delta of the squared weight vector at time step $t$.
-	\item [\parbox{2cm}{$RMS[\Delta \boldsymbol{w}]_{t}$}] The root mean squared delta of the weight vector at time step $t$.
-	\item [\parbox{2cm}{$RMS[\Delta \boldsymbol{w}]_{t-1}$}] The root mean squared delta of the weight vector at time step $t-1$.
-	\item [\parbox{2cm}{$RMS[\boldsymbol{g}]_{t}$}] The root mean squared gradient vector at time step $t$.
-	\item [\parbox{2cm}{$\boldsymbol{g}_{t}$}] The gradient vector at time step $t$.
-	\item [\parbox{2cm}{$\boldsymbol{m}_{t}$}] The estimate of the first moment at time step $t$.
-	\item [\parbox{2cm}{$\boldsymbol{m}_{t+1}$}] The estimate of the first moment at time step $t+1$.
-	\item [\parbox{2cm}{$\boldsymbol{v}_{t}$}] The estimate of the second moment at time step $t$.
-	\item [\parbox{2cm}{$\boldsymbol{v}_{t+1}$}] The estimate of the second moment at time step $t+1$.
-	\item [\parbox{2cm}{$\beta_{1}$}] First decay rate parameter for \acs{Adam}.
-	\item [\parbox{2cm}{$\beta_{2}$}] Second decay rate parameter for \acs{Adam}.
-	\item [\parbox{2cm}{$\hat{\boldsymbol{m}}_{t}$}] The bias-corrected first moment at time step $t$.
-	\item [\parbox{2cm}{$\hat{\boldsymbol{v}}_{t}$}] The bias-corrected second moment at time step $t$.
-	\item [\parbox{2cm}{$\beta^{t}_{1}$}] First decay rate parameter for \acs{Adam} at time step $t$.
-	\item [\parbox{2cm}{$\beta^{t}_{2}$}] Second decay rate parameter for \acs{Adam} at time step $t$.
-	\item [\parbox{2cm}{$\boldsymbol{x}_{i}$}] The $i$-th particle's position vector as implemented by \acs{PSO}. Also represents the $i$-th parent's position vector as implemented by \acs{DE}.
-	\item [\parbox{2cm}{$\boldsymbol{x}_{i}(t)$}] The $i$-th particle's position vector at time step $t$ as implemented by \acs{PSO}.
-Also represents the $i$-th parent's position vector at time step $t$ as implemented by \acs{DE}.
-	\item [\parbox{2cm}{$\boldsymbol{v}_{i}(t)$}] The $i$-th particle's velocity vector at time step $t$ as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$f(x_{i})$}] The evaluation of the $i$-th particle's solution with respect to the objective function.
-	\item [\parbox{2cm}{$\boldsymbol{y}_{i}(t)$}] The $i$-th particle's personal best position vector at time step $t$ as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$\boldsymbol{x}_{i}(0)$}] The $i$-th particle's position vector at time step $0$ as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$\boldsymbol{y}_{i}(0)$}] The $i$-th particle's personal best position vector at time step $0$ as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$\boldsymbol{\hat{y}}_{i}(t)$}] The $i$-th particle's global best position vector as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$\boldsymbol{x}_{i}$}] The $i$-th particle's position vector as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$\boldsymbol{x}_{min}$}] The lower bound constraint vector of the position vector's values.
-	\item [\parbox{2cm}{$\boldsymbol{x}_{max}$}] The upper bound constraint vector of the position vector's values.
-	\item [\parbox{2cm}{$v_{ij}(t+1)$}] The $i$-th particle's $j$-th dimension of the velocity vector at time step $t+1$.
-	\item [\parbox{2cm}{$v_{ij}(t)$}] The $i$-th particle's $j$-th dimension of the velocity vector at time step $t$.
-Also used in the mutation operator for \acp{GA} to represent some sampled mutation update value.
-	\item [\parbox{2cm}{$w$}] The inertia weight hyper-parameter as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$c_{1}$}] The cognitive control parameter as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$c_{2}$}] The social control parameter as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$r_{1_{j}}(t)$}] The $j$-th dimension of the first stochastic scaling parameter at time step $t$ as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$r_{2_{j}}(t)$}] The $j$-th dimension of the second stochastic scaling parameter at time step $t$ as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$x_{ij}$}] The $i$-th particle's/entity's $j$-th dimension of the position vector.
-	\item [\parbox{2cm}{$x_{ij}(t)$}] The $i$-th particle's/entity's $j$-th dimension of the position vector at time step $t$.
-	\item [\parbox{2cm}{$y_{ij}$}] The $i$-th particle's $j$-th dimension of the personal best position vector.
-	\item [\parbox{2cm}{$y_{ij}(t)$}] The $i$-th particle's $j$-th dimension of the personal best position vector at time step $t$.
-	\item [\parbox{2cm}{$\boldsymbol{\hat{y}}$}] Short form of the global best position vector.
-	\item [\parbox{2cm}{$\hat{y}_{ij}$}] The $i$-th particle's $j$-th dimension of the global best position vector.
-	\item [\parbox{2cm}{$\hat{y}_{ij}(t)$}] The $i$-th particle's $j$-th dimension of the global best position vector at time step $t$.
-	\item [\parbox{2cm}{$f(\hat{y})$}] The evaluation of the global best position.
-	\item [\parbox{2cm}{$x_{ij}(t+1)$}] The $i$-th particle's $j$-th dimension of the position vector at time step $t+1$.
-	\item [\parbox{2cm}{$\boldsymbol{r}_{1}$}] The vector for the first stochastic scaling parameter as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$\boldsymbol{r}_{2}$}] The vector for the second stochastic scaling parameter as implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$I$}] The total number of particles in the swarm (particle swarm size).
-	\item [\parbox{2cm}{$N$}] An alternative to the particle swarm size.
-	\item [\parbox{2cm}{$j$}] Index used for the dimensions of candidate solutions.
-	\item [\parbox{2cm}{$J$}] The total number of dimensions in the position vector for particles in \acs{PSO}.
-	\item [\parbox{2cm}{$U$}] The uniform distribution.
-	\item [\parbox{2cm}{$v'_{ij}(t+1)$}] The $i$-th particle's $j$-th dimension of the clamped velocity vector at time step $t+1$.
-	\item [\parbox{2cm}{$\boldsymbol{V}_{max}$}] The upper bound of the velocity clamping vector.
-	\item [\parbox{2cm}{$V_{max,j}$}] The $j$-th dimension of the upper bound of the velocity clamping vector.
-	\item [\parbox{2cm}{$\boldsymbol{u}_{i}(t)$}] The $i$-th entity's trial vector at time step $t$ implemented by \acs{DE}.
-	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{1}}(t)$}] The $i$-th entity's target vector at time step $t$ implemented by \acs{DE}.
-	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{2}}(t)$}] The $i$-th entity's first selected individual's position vector at time step $t$ implemented by \acs{DE}.
-	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{3}}(t)$}] The $i$-th entity's second selected individual's position vector at time step $t$ implemented by \acs{DE}.
-	\item [\parbox{2cm}{$i_{1}$}] Index for the target vector in \acs{DE}.
-	\item [\parbox{2cm}{$i_{2}$}] Index for the first selected individual in \acs{DE}.
-	\item [\parbox{2cm}{$i_{3}$}] Index for the second selected individual in \acs{DE}.
-	\item [\parbox{2cm}{$\beta$}] Scale factor as implemented by \acs{DE}.
-	\item [\parbox{2cm}{$\boldsymbol{x}'_{i}(t)$}] The $i$-th offspring's position vector at time step $t$ as implemented by \acs{DE}.
-	\item [\parbox{2cm}{$x'_{ij}(t)$}] The $i$-th offspring's $j$-th dimension of the position vector at time step $t$.
-	\item [\parbox{2cm}{$u_{ij}(t)$}] The $j$-th dimension of the $i$-th entity's trial vector at time step $t$ implemented by \acs{DE}.
-	\item [\parbox{2cm}{$\mathcal{J}$}] The set of crossover points.
-	\item [\parbox{2cm}{$j^{*}$}] Randomly selected crossover point.
-	\item [\parbox{2cm}{$\emptyset$}] The empty set.
-	\item [\parbox{2cm}{$p_{r}$}] The crossover probability i.e. recombination probability.
-	\item [\parbox{2cm}{$f(\boldsymbol{x}_{i}(t))$}] The evaluation of the $i$-th entity's candidate solution at time step $t$.
-	\item [\parbox{2cm}{$f(\boldsymbol{x}'_{i}(t))$}] The evaluation of the $i$-th offspring's candidate solution at time step $t$.
-	\item [\parbox{2cm}{$f(\boldsymbol{y}_{i})$}] The evaluation of the $i$-th particle's personal best position.
-	\item [\parbox{2cm}{$f(\boldsymbol{\hat{y}})$}] The evaluation of the global best position.
-	\item [\parbox{2cm}{$x_{min,j}$}] The $j$-th dimension of the lower bound constraint for an entity's position.
-	\item [\parbox{2cm}{$x_{max,j}$}] The $j$-th dimension of the upper bound constraint for an entity's position.
-	\item [\parbox{2cm}{$\mathcal{C}$}] The set of entities in the population.
-	\item [\parbox{2cm}{$\mathcal{C}(0)$}] The set of entities in the population at time step $0$.
-	\item [\parbox{2cm}{$\mathcal{C}(t)$}] The set of entities in the population at time step $t$.
-	\item [\parbox{2cm}{$\mathcal{C}(t+1)$}] The set of entities in the population at time step $t+1$.
-	\item [\parbox{2cm}{$y$}] Used in \acs{DE} notation to denote the number of difference vectors to include.
-	\item [\parbox{2cm}{$z$}] Used in \acs{DE} notation to denote the type of crossover operator to use.
-	\item [\parbox{2cm}{$p_{c}$}] Probability of producing offspring.
-	\item [\parbox{2cm}{$p_{x}$}] Bitswapping probability.
-	\item [\parbox{2cm}{$m_{j}(t)$}] The $j$-th dimension of the crossover mask, $m$, at time step $t$.
-	\item [\parbox{2cm}{$p_{m}$}] The mutation probability.
-	\item [\parbox{2cm}{$N_{t}$}] Tournament selection size.
+	\item [\parbox{2cm}{$\alpha$}] \parbox{12.5cm}{The momentum hyper-parameter.}
+	\item [\parbox{2cm}{$\beta_{1}$}] \parbox{12.5cm}{First decay rate parameter for \acs{Adam}.}
+	\item [\parbox{2cm}{$\beta_{2}$}] \parbox{12.5cm}{Second decay rate parameter for \acs{Adam}.}
+	\item [\parbox{2cm}{$\beta^{t}_{1}$}] \parbox{12.5cm}{First decay rate parameter for \acs{Adam} at time step $t$.}
+	\item [\parbox{2cm}{$\beta^{t}_{2}$}] \parbox{12.5cm}{Second decay rate parameter for \acs{Adam} at time step $t$.}
+	\item [\parbox{2cm}{$\beta$}] \parbox{12.5cm}{Scale factor as implemented by \acs{DE}.}
+	\item [\parbox{2cm}{$\boldsymbol{\hat{y}}_{i}(t)$}] \parbox{12.5cm}{The $i$-th particle's global best position vector as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$\boldsymbol{\hat{y}}$}] \parbox{12.5cm}{Short form of the global best position vector.}
+	\item [\parbox{2cm}{$\boldsymbol{G_{t}}$}] \parbox{12.5cm}{The sum of the squares of the gradients.}
+	\item [\parbox{2cm}{$\boldsymbol{g}_{t}$}] \parbox{12.5cm}{The gradient vector at time step $t$.}
+	\item [\parbox{2cm}{$\boldsymbol{g}^{2}_{t}$}] \parbox{12.5cm}{The squared gradient vector at time step $t$.}
+	\item [\parbox{2cm}{$\boldsymbol{g}$}] \parbox{12.5cm}{General symbol used to represent the gradient vector, retrieved from the error function relative to the weight vector.}
+	\item [\parbox{2cm}{$\boldsymbol{m}_{t}$}] \parbox{12.5cm}{The estimate of the first moment at time step $t$.}
+	\item [\parbox{2cm}{$\boldsymbol{m}_{t+1}$}] \parbox{12.5cm}{The estimate of the first moment at time step $t+1$.}
+	\item [\parbox{2cm}{$\boldsymbol{r}_{1}$}] \parbox{12.5cm}{The vector for the first stochastic scaling parameter as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$\boldsymbol{r}_{2}$}] \parbox{12.5cm}{The vector for the second stochastic scaling parameter as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$\boldsymbol{u}_{i}(t)$}] \parbox{12.5cm}{The $i$-th entity's trial vector at time step $t$ implemented by \acs{DE}.}
+	\item [\parbox{2cm}{$\boldsymbol{v}_{i}(t)$}] \parbox{12.5cm}{The $i$-th particle's velocity vector at time step $t$ as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$\boldsymbol{V}_{max}$}] \parbox{12.5cm}{The upper bound of the velocity clamping vector.}
+	\item [\parbox{2cm}{$\boldsymbol{v}_{t}$}] \parbox{12.5cm}{The estimate of the second moment at time step $t$.}
+	\item [\parbox{2cm}{$\boldsymbol{v}_{t+1}$}] \parbox{12.5cm}{The estimate of the second moment at time step $t+1$.}
+	\item [\parbox{2cm}{$\boldsymbol{v}$}] \parbox{12.5cm}{The velocity vector resulting from \acs{Momentum}.}
+	\item [\parbox{2cm}{$\boldsymbol{w}_{t}^{2}$}] \parbox{12.5cm}{The squared weight vector at time step $t$.}
+	\item [\parbox{2cm}{$\boldsymbol{w}_{t+1}$}] \parbox{12.5cm}{The weight vector at time step $t+1$.}
+	\item [\parbox{2cm}{$\boldsymbol{w}$}] \parbox{12.5cm}{General symbol used to represent the weight vector.}
+	\item [\parbox{2cm}{$\boldsymbol{w}$}] \parbox{12.5cm}{The weight vector.}
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{1}}(t)$}] \parbox{12.5cm}{The $i$-th entity's target vector at time step $t$ implemented by \acs{DE}.}
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{2}}(t)$}] \parbox{12.5cm}{The $i$-th entity's first selected individual's position vector at time step $t$ implemented by \acs{DE}.}
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{3}}(t)$}] \parbox{12.5cm}{The $i$-th entity's second selected individual's position vector at time step $t$ implemented by \acs{DE}.}
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i}(0)$}] \parbox{12.5cm}{The $i$-th particle's position vector at time step $0$ as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i}(t)$}] \parbox{12.5cm}{The $i$-th particle's position vector at time step $t$ as implemented by \acs{PSO}.
+Also represents the $i$-th parent's position vector at time step $t$ as implemented by \acs{DE}.}
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i}$}] \parbox{12.5cm}{The $i$-th particle's position vector as implemented by \acs{PSO}.
+Also represents the $i$-th parent's position vector as implemented by \acs{DE}.}
+	\item [\parbox{2cm}{$\boldsymbol{x}_{i}$}] \parbox{12.5cm}{The $i$-th particle's position vector as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$\boldsymbol{x}_{max}$}] \parbox{12.5cm}{The upper bound constraint vector of the position vector's values.}
+	\item [\parbox{2cm}{$\boldsymbol{x}_{min}$}] \parbox{12.5cm}{The lower bound constraint vector of the position vector's values.}
+	\item [\parbox{2cm}{$\boldsymbol{x}'_{i}(t)$}] \parbox{12.5cm}{The $i$-th offspring's position vector at time step $t$ as implemented by \acs{DE}.}
+	\item [\parbox{2cm}{$\boldsymbol{y}_{i}(0)$}] \parbox{12.5cm}{The $i$-th particle's personal best position vector at time step $0$ as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$\boldsymbol{y}_{i}(t)$}] \parbox{12.5cm}{The $i$-th particle's personal best position vector at time step $t$ as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$\Delta \boldsymbol{w}^{2}_{t}$}] \parbox{12.5cm}{The delta of the squared weight vector at time step $t$.}
+	\item [\parbox{2cm}{$\Delta w_{i}(t)$}] \parbox{12.5cm}{The change in the $i$-th dimension of the weight vector at time step $t$.}
+	\item [\parbox{2cm}{$\emptyset$}] \parbox{12.5cm}{The empty set.}
+	\item [\parbox{2cm}{$\epsilon_{T_{p}}$}] \parbox{12.5cm}{The error produced for pattern $p$ at time step $T$.}
+	\item [\parbox{2cm}{$\epsilon_{T}$}] \parbox{12.5cm}{The error at time step $T$.}
+	\item [\parbox{2cm}{$\epsilon$}] \parbox{12.5cm}{The error between the output of the \acs{FFNN} and the target pattern, produced by the loss function.
+Also used as a small error value used by heuristics to avoid division by 0.}
+	\item [\parbox{2cm}{$\eta$}] \parbox{12.5cm}{Learning rate.}
+	\item [\parbox{2cm}{$\hat{\boldsymbol{m}}_{t}$}] \parbox{12.5cm}{The bias-corrected first moment at time step $t$.}
+	\item [\parbox{2cm}{$\hat{\boldsymbol{v}}_{t}$}] \parbox{12.5cm}{The bias-corrected second moment at time step $t$.}
+	\item [\parbox{2cm}{$\hat{y}_{ij}(t)$}] \parbox{12.5cm}{The $i$-th particle's $j$-th dimension of the global best position vector at time step $t$.}
+	\item [\parbox{2cm}{$\hat{y}_{ij}$}] \parbox{12.5cm}{The $i$-th particle's $j$-th dimension of the global best position vector.}
+	\item [\parbox{2cm}{$\mathcal{C}(0)$}] \parbox{12.5cm}{The set of entities in the population at time step $0$.}
+	\item [\parbox{2cm}{$\mathcal{C}(t)$}] \parbox{12.5cm}{The set of entities in the population at time step $t$.}
+	\item [\parbox{2cm}{$\mathcal{C}(t+1)$}] \parbox{12.5cm}{The set of entities in the population at time step $t+1$.}
+	\item [\parbox{2cm}{$\mathcal{C}$}] \parbox{12.5cm}{The set of entities in the population.}
+	\item [\parbox{2cm}{$\mathcal{E}$}] \parbox{12.5cm}{The error function.}
+	\item [\parbox{2cm}{$\mathcal{J}$}] \parbox{12.5cm}{The set of crossover points.}
+	\item [\parbox{2cm}{$\odot$}] \parbox{12.5cm}{The matrix-vector product.}
+	\item [\parbox{2cm}{$c_{1}$}] \parbox{12.5cm}{The cognitive control parameter as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$c_{2}$}] \parbox{12.5cm}{The social control parameter as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$E[\boldsymbol{g}^{2}]_{t - 1}$}] \parbox{12.5cm}{The expected value of the squared gradients at time step $t-1$.}
+	\item [\parbox{2cm}{$E[\boldsymbol{g}^{2}]_{t}$}] \parbox{12.5cm}{The expected value of the squared gradients at time step $t$.}
+	\item [\parbox{2cm}{$E[\Delta \boldsymbol{w}^{2}]_{t - 1}$}] \parbox{12.5cm}{The expected value of the delta of the squared weight vector at time step $t-1$.}
+	\item [\parbox{2cm}{$E[\Delta \boldsymbol{w}^{2}]_{t}$}] \parbox{12.5cm}{The expected value of the delta of the squared weight vector at time step $t$.}
+	\item [\parbox{2cm}{$f(\boldsymbol{\hat{y}})$}] \parbox{12.5cm}{The evaluation of the global best position.}
+	\item [\parbox{2cm}{$f(\boldsymbol{x}_{i}(t))$}] \parbox{12.5cm}{The evaluation of the $i$-th entity's candidate solution at time step $t$.}
+	\item [\parbox{2cm}{$f(\boldsymbol{x}'_{i}(t))$}] \parbox{12.5cm}{The evaluation of the $i$-th offspring's candidate solution at time step $t$.}
+	\item [\parbox{2cm}{$f(\boldsymbol{y}_{i})$}] \parbox{12.5cm}{The evaluation of the $i$-th particle's personal best position.}
+	\item [\parbox{2cm}{$f(\hat{y})$}] \parbox{12.5cm}{The evaluation of the global best position.}
+	\item [\parbox{2cm}{$f(x_{i})$}] \parbox{12.5cm}{The evaluation of the $i$-th particle's solution with respect to the objective function.}
+	\item [\parbox{2cm}{$f(x)$}] \parbox{12.5cm}{The objective function over $x$.}
+	\item [\parbox{2cm}{$f$}] \parbox{12.5cm}{A shortened form of the objective function being optimised.}
+	\item [\parbox{2cm}{$g_{t,i}$}] \parbox{12.5cm}{The $i$-th dimension of the gradient vector at time step $t$.}
+	\item [\parbox{2cm}{$G_{t,i}$}] \parbox{12.5cm}{The sum of the squared gradients with regards to the $i$-th dimension of the weight vector.}
+	\item [\parbox{2cm}{$G_{t,ii}$}] \parbox{12.5cm}{Diagonal matrix containing the sum of the squared gradients with regards to the $i$-th dimension of the weight vector.}
+	\item [\parbox{2cm}{$i_{1}$}] \parbox{12.5cm}{Index for the target vector in \acs{DE}.}
+	\item [\parbox{2cm}{$i_{2}$}] \parbox{12.5cm}{Index for the first selected individual in \acs{DE}.}
+	\item [\parbox{2cm}{$i_{3}$}] \parbox{12.5cm}{Index for the second selected individual in \acs{DE}.}
+	\item [\parbox{2cm}{$i$}] \parbox{12.5cm}{Index used for the weight vector. Also used as the index for the $i$-th particle in the population, implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$I$}] \parbox{12.5cm}{The total number of particles in the swarm (particle swarm size).}
+	\item [\parbox{2cm}{$j^{*}$}] \parbox{12.5cm}{Randomly selected crossover point.}
+	\item [\parbox{2cm}{$j$}] \parbox{12.5cm}{Index used for the dimensions of candidate solutions.}
+	\item [\parbox{2cm}{$J$}] \parbox{12.5cm}{The total number of dimensions in the position vector for particles in \acs{PSO}.}
+	\item [\parbox{2cm}{$k$}] \parbox{12.5cm}{Index used for the output layer.}
+	\item [\parbox{2cm}{$K$}] \parbox{12.5cm}{Total number of output units.}
+	\item [\parbox{2cm}{$m_{j}(t)$}] \parbox{12.5cm}{The $j$-th dimension of the crossover mask, $m$, at time step $t$.}
+	\item [\parbox{2cm}{$N_{t}$}] \parbox{12.5cm}{Tournament selection size.}
+	\item [\parbox{2cm}{$N$}] \parbox{12.5cm}{An alternative to the particle swarm size.}
+	\item [\parbox{2cm}{$net_{p}$}] \parbox{12.5cm}{The net input signal for pattern $p$.}
+	\item [\parbox{2cm}{$o_{i,p}$}] \parbox{12.5cm}{The $i$-th dimension of the output for pattern $p$.}
+	\item [\parbox{2cm}{$o_{k,p}$}] \parbox{12.5cm}{The $k$-th dimension of the output for pattern $p$.}
+	\item [\parbox{2cm}{$p_{c}$}] \parbox{12.5cm}{Probability of producing offspring.}
+	\item [\parbox{2cm}{$p_{m}$}] \parbox{12.5cm}{The mutation probability.}
+	\item [\parbox{2cm}{$p_{r}$}] \parbox{12.5cm}{The crossover probability i.e. recombination probability.}
+	\item [\parbox{2cm}{$p_{x}$}] \parbox{12.5cm}{Bitswapping probability.}
+	\item [\parbox{2cm}{$p$}] \parbox{12.5cm}{Index used for input data patterns.}
+	\item [\parbox{2cm}{$r_{1_{j}}(t)$}] \parbox{12.5cm}{The $j$-th dimension of the first stochastic scaling parameter at time step $t$ as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$r_{2_{j}}(t)$}] \parbox{12.5cm}{The $j$-th dimension of the second stochastic scaling parameter at time step $t$ as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$RMS[\boldsymbol{g}]_{t}$}] \parbox{12.5cm}{The root mean squared gradient vector at time step $t$.}
+	\item [\parbox{2cm}{$RMS$}] \parbox{12.5cm}{The root mean squared error criterion.}
+	\item [\parbox{2cm}{$t_{i,p}$}] \parbox{12.5cm}{The $i$-th dimension of the target for pattern $p$.}
+	\item [\parbox{2cm}{$t_{k,p}$}] \parbox{12.5cm}{The $k$-th dimension of the target for pattern $p$.}
+	\item [\parbox{2cm}{$t$}] \parbox{12.5cm}{Time step.}
+	\item [\parbox{2cm}{$T$}] \parbox{12.5cm}{Time step.}
+	\item [\parbox{2cm}{$u_{ij}(t)$}] \parbox{12.5cm}{The $j$-th dimension of the $i$-th entity's trial vector at time step $t$ implemented by \acs{DE}.}
+	\item [\parbox{2cm}{$U$}] \parbox{12.5cm}{The uniform distribution.}
+	\item [\parbox{2cm}{$v_{ij}(t)$}] \parbox{12.5cm}{The $i$-th particle's $j$-th dimension of the velocity vector at time step $t$.
+Also used in the mutation operator for \acp{GA} to represent some sampled mutation update value.}
+	\item [\parbox{2cm}{$v_{ij}(t+1)$}] \parbox{12.5cm}{The $i$-th particle's $j$-th dimension of the velocity vector at time step $t+1$.}
+	\item [\parbox{2cm}{$V_{max,j}$}] \parbox{12.5cm}{The $j$-th dimension of the upper bound of the velocity clamping vector.}
+	\item [\parbox{2cm}{$v'_{ij}(t+1)$}] \parbox{12.5cm}{The $i$-th particle's $j$-th dimension of the clamped velocity vector at time step $t+1$.}
+	\item [\parbox{2cm}{$w_{i}(t-1)$}] \parbox{12.5cm}{The $i$-th dimension of the weight vector at time step $t-1$.}
+	\item [\parbox{2cm}{$w_{i}(t)$}] \parbox{12.5cm}{The $i$-th dimension of the weight vector at time step $t$.}
+	\item [\parbox{2cm}{$w_{i}$}] \parbox{12.5cm}{The $i$-th dimension of the weight vector.}
+	\item [\parbox{2cm}{$w_{t,i}$}] \parbox{12.5cm}{The $i$-th dimension of the weight vector at time step $t$.}
+	\item [\parbox{2cm}{$w_{t+1,i}$}] \parbox{12.5cm}{The $i$-th dimension of the weight vector at time step $t+1$.}
+	\item [\parbox{2cm}{$w$}] \parbox{12.5cm}{The inertia weight hyper-parameter as implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$W$}] \parbox{12.5cm}{Window size of previous squared gradients.}
+	\item [\parbox{2cm}{$x_{ij}(t)$}] \parbox{12.5cm}{The $i$-th particle's/entity's $j$-th dimension of the position vector at time step $t$.}
+	\item [\parbox{2cm}{$x_{ij}(t+1)$}] \parbox{12.5cm}{The $i$-th particle's $j$-th dimension of the position vector at time step $t+1$.}
+	\item [\parbox{2cm}{$x_{ij}$}] \parbox{12.5cm}{The $i$-th particle's/entity's $j$-th dimension of the position vector.}
+	\item [\parbox{2cm}{$x_{max,j}$}] \parbox{12.5cm}{The $j$-th dimension of the upper bound constraint for an entity's position.}
+	\item [\parbox{2cm}{$x_{min,j}$}] \parbox{12.5cm}{The $j$-th dimension of the lower bound constraint for an entity's position.}
+	\item [\parbox{2cm}{$x'_{ij}(t)$}] \parbox{12.5cm}{The $i$-th offspring's $j$-th dimension of the position vector at time step $t$.}
+	\item [\parbox{2cm}{$x$}] \parbox{12.5cm}{The independent variables to the objective function. Also used in \acs{DE} notation to denote the selection mechanism for the trial vector.}
+	\item [\parbox{2cm}{$y_{ij}(t)$}] \parbox{12.5cm}{The $i$-th particle's $j$-th dimension of the personal best position vector at time step $t$.}
+	\item [\parbox{2cm}{$y_{ij}$}] \parbox{12.5cm}{The $i$-th particle's $j$-th dimension of the personal best position vector.}
+	\item [\parbox{2cm}{$y$}] \parbox{12.5cm}{Used in \acs{DE} notation to denote the number of difference vectors to include.}
+	\item [\parbox{2cm}{$z_{i,p}$}] \parbox{12.5cm}{The input value at index $i$ for pattern $p$.}
+	\item [\parbox{2cm}{$z$}] \parbox{12.5cm}{Used in \acs{DE} notation to denote the type of crossover operator to use.}
 \end{description}
@@
 \begin{description}
-	\item [\parbox{2cm}{$K$}] The number of folds to execute for $K$-fold crossover validation.
+	\item [\parbox{2cm}{$K$}] \parbox{12.5cm}{The number of folds to execute for $K$-fold crossover validation.}
 \end{description}
@@
 \begin{description}
-	\item [\parbox{2cm}{$\alpha_{0}$}]
-	\item [\parbox{2cm}{$\alpha_{1}$}]
-	\item [\parbox{2cm}{$\alpha_{k}$}]
-	\item [\parbox{2cm}{$\alpha_{K}$}]
-	\item [\parbox{2cm}{$\alpha$}]
-	\item [\parbox{2cm}{$\bar{A}$}]
-	\item [\parbox{2cm}{$\beta'$ }]
-	\item [\parbox{2cm}{$\beta$}]
-	\item [\parbox{2cm}{$Bin$}]
-	\item [\parbox{2cm}{$\boldsymbol{\alpha'}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\mathcal{D}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
-	\item [\parbox{2cm}{$\boldsymbol{N}$}]
-	\item [\parbox{2cm}{$\boldsymbol{x_{1}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{x_{i}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{x_{I}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{x}$}]
-	\item [\parbox{2cm}{$\boldsymbol{X}$}]
-	\item [\parbox{2cm}{$\boldsymbol{Y}$}]
-	\item [\parbox{2cm}{$\emptyset$}]
-	\item [\parbox{2cm}{$\Gamma'(n)$}]
-	\item [\parbox{2cm}{$\Gamma(n)$}]
-	\item [\parbox{2cm}{$\Gamma$}]
-	\item [\parbox{2cm}{$\mathbb{R}$}]
-	\item [\parbox{2cm}{$\mathbbm{1}$}]
-	\item [\parbox{2cm}{$\mathcal{A}$}]
-	\item [\parbox{2cm}{$\mathcal{L}$}]
-	\item [\parbox{2cm}{$\overset{\text{iid}}{\sim}$}]
-	\item [\parbox{2cm}{$\psi$}]
-	\item [\parbox{2cm}{$\theta_{1}$}]
-	\item [\parbox{2cm}{$\theta_{k}$}]
-	\item [\parbox{2cm}{$\theta_{K}$}]
-	\item [\parbox{2cm}{$\theta$}]
-	\item [\parbox{2cm}{$A$}]
-	\item [\parbox{2cm}{$B_{1}$}]
-	\item [\parbox{2cm}{$B_{2}$}]
-	\item [\parbox{2cm}{$B_{i}$}]
-	\item [\parbox{2cm}{$B_{j}$}]
-	\item [\parbox{2cm}{$B_{K}$}]
-	\item [\parbox{2cm}{$B(\boldsymbol{\alpha})$}]
-	\item [\parbox{2cm}{$B$}]
-	\item [\parbox{2cm}{$Ber(\theta)$}]
-	\item [\parbox{2cm}{$Beta$}]
-	\item [\parbox{2cm}{$Bin$}]
-	\item [\parbox{2cm}{$c$}]
-	\item [\parbox{2cm}{$Cat$}]
-	\item [\parbox{2cm}{$d$}]
-	\item [\parbox{2cm}{$Dir$}]
-	\item [\parbox{2cm}{$dn$}]
-	\item [\parbox{2cm}{$E[{x_{k}}]$}]
-	\item [\parbox{2cm}{$E[\ln(x_{k})]$}]
-	\item [\parbox{2cm}{$E[\ln(x)]$}]
-	\item [\parbox{2cm}{$E[x_{k}]$}]
-	\item [\parbox{2cm}{$E[x]$}]
-	\item [\parbox{2cm}{$f_{Ber}$}]
-	\item [\parbox{2cm}{$f_{Beta}$}]
-	\item [\parbox{2cm}{$f_{Bin}$}]
-	\item [\parbox{2cm}{$f_{Cat}$}]
-	\item [\parbox{2cm}{$f_{Dir}$}]
-	\item [\parbox{2cm}{$f_{Mul}$}]
-	\item [\parbox{2cm}{$f$}]
-	\item [\parbox{2cm}{$F$}]
-	\item [\parbox{2cm}{$g^{*}$}]
-	\item [\parbox{2cm}{$g$}]
-	\item [\parbox{2cm}{$i$}]
-	\item [\parbox{2cm}{$I$}]
-	\item [\parbox{2cm}{$j$}]
-	\item [\parbox{2cm}{$K$}]
-	\item [\parbox{2cm}{$k$}]
-	\item [\parbox{2cm}{$K$}]
-	\item [\parbox{2cm}{$M[x_{k}]$}]
-	\item [\parbox{2cm}{$M[x]$}]
-	\item [\parbox{2cm}{$m$}]
-	\item [\parbox{2cm}{$M$}]
-	\item [\parbox{2cm}{$Mul$}]
-	\item [\parbox{2cm}{$N_{0}$}]
-	\item [\parbox{2cm}{$N_{1}$}]
-	\item [\parbox{2cm}{$N_{k}$}]
-	\item [\parbox{2cm}{$N_{K}$}]
-	\item [\parbox{2cm}{$n$}]
-	\item [\parbox{2cm}{$N$}]
-	\item [\parbox{2cm}{$p$}]
-	\item [\parbox{2cm}{$S$}]
-	\item [\parbox{2cm}{$v$}]
-	\item [\parbox{2cm}{$x_{1}$}]
-	\item [\parbox{2cm}{$x_{i,k}$}]
-	\item [\parbox{2cm}{$x_{i}$}]
-	\item [\parbox{2cm}{$x_{I}$}]
-	\item [\parbox{2cm}{$x_{j}$}]
-	\item [\parbox{2cm}{$x_{k}$}]
-	\item [\parbox{2cm}{$x_{K}$}]
-	\item [\parbox{2cm}{$x$}]
-	\item [\parbox{2cm}{$y_{1}$}]
-	\item [\parbox{2cm}{$Y_{1}$}]
-	\item [\parbox{2cm}{$y_{2}$}]
-	\item [\parbox{2cm}{$Y_{2}$}]
-	\item [\parbox{2cm}{$y_{i}$}]
-	\item [\parbox{2cm}{$Y_{i}$}]
-	\item [\parbox{2cm}{$y_{n}$}]
-	\item [\parbox{2cm}{$Y_{N}$}]
+	\item [\parbox{2cm}{$\alpha_{0}$}] \parbox{12.5cm}{The sum of all the values in each dimension of the concentration parameter $\boldsymbol{\alpha}$.}
+	\item [\parbox{2cm}{$\alpha_{1}$}] \parbox{12.5cm}{The first dimension of the concentration parameter $\boldsymbol{\alpha}$.}
+	\item [\parbox{2cm}{$\alpha_{k}$}] \parbox{12.5cm}{The $k$-th dimension of the concentration parameter $\boldsymbol{\alpha}$.}
+	\item [\parbox{2cm}{$\alpha_{K}$}] \parbox{12.5cm}{The last dimension of the concentration parameter $\boldsymbol{\alpha}$.}
+	\item [\parbox{2cm}{$\alpha'$}] \parbox{12.5cm}{The update form of the prior parameter, $\alpha$, for a Beta probability distribution.}
+	\item [\parbox{2cm}{$\alpha$}] \parbox{12.5cm}{Shape parameter for the Beta probability distribution. Also used for confidence levels for the statistical tests.}
+	\item [\parbox{2cm}{$\bar{A}$}] \parbox{12.5cm}{Not observing random event $A$.}
+	\item [\parbox{2cm}{$\beta'$}] \parbox{12.5cm}{The update form of the prior parameter, $\beta$, for a Beta probability distribution.}
+	\item [\parbox{2cm}{$\beta$}] \parbox{12.5cm}{Shape parameter for the Beta probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{\alpha'}$}] \parbox{12.5cm}{Update form of the prior parameter, $\boldsymbol{\alpha}$, for a Dirichlet probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}] \parbox{12.5cm}{The concentration parameter vector that parameterises the Dirichlet probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{\mathcal{D}}$}] \parbox{12.5cm}{All the prior data of $\boldsymbol{X}$}
+	\item [\parbox{2cm}{$\boldsymbol{\theta}$}] \parbox{12.5cm}{The probability vector in multiple dimensions used by multiple probability distributions.}
+	\item [\parbox{2cm}{$\boldsymbol{N}$}] \parbox{12.5cm}{The counts for each occurrence of a category $k$ over $I$ independent, identical (iid) events.}
+	\item [\parbox{2cm}{$\boldsymbol{x_{1}}$}] \parbox{12.5cm}{The outcomes of the first random event in $I$ independent, identical (iid) events for $k$ categories.}
+	\item [\parbox{2cm}{$\boldsymbol{x_{i}}$}] \parbox{12.5cm}{The outcomes of the $i$-th random event in $I$ independent, identical (iid) events for $k$ categories.}
+	\item [\parbox{2cm}{$\boldsymbol{x_{I}}$}] \parbox{12.5cm}{The outcomes of the last random event in $I$ independent, identical (iid) events for $k$ categories.}
+	\item [\parbox{2cm}{$\boldsymbol{X}$}] \parbox{12.5cm}{Matrix of Bernoulli probability distributions. Also used to represent the outcomes of $I$ independent, identical (iid) random events.}
+	\item [\parbox{2cm}{$\boldsymbol{x}$}] \parbox{12.5cm}{The random variable for various probability distributions in multiple dimensions.}
+	\item [\parbox{2cm}{$\boldsymbol{Y}$}] \parbox{12.5cm}{A vector of random events.}
+	\item [\parbox{2cm}{$\emptyset$}] \parbox{12.5cm}{The empty set.}
+	\item [\parbox{2cm}{$\Gamma'(n)$}] \parbox{12.5cm}{The first derivative of the Gamma function over input $n$.}
+	\item [\parbox{2cm}{$\Gamma(n)$}] \parbox{12.5cm}{The Gamma function over input $n$.}
+	\item [\parbox{2cm}{$\Gamma$}] \parbox{12.5cm}{The Gamma function.}
+	\item [\parbox{2cm}{$\mathbb{R}$}] \parbox{12.5cm}{Real-number space.}
+	\item [\parbox{2cm}{$\mathbb{R}$}] \parbox{12.5cm}{The real-number space.}
+	\item [\parbox{2cm}{$\mathbbm{1}$}] \parbox{12.5cm}{Indicator function.}
+	\item [\parbox{2cm}{$\mathcal{A}(v)$}] \parbox{12.5cm}{Functional form of priors.}
+	\item [\parbox{2cm}{$\mathcal{L}$}] \parbox{12.5cm}{The likelihood function.}
+	\item [\parbox{2cm}{$\overset{\text{iid}}{\sim}$}] \parbox{12.5cm}{Independent, identical (iid) random events.}
+	\item [\parbox{2cm}{$\psi$}] \parbox{12.5cm}{The logarithmic derivative of the Gamma function, called the Digamma Function.}
+	\item [\parbox{2cm}{$\theta_{1}$}] \parbox{12.5cm}{The first dimension of the probability vector $\boldsymbol{\theta}$.}
+	\item [\parbox{2cm}{$\theta_{k}$}] \parbox{12.5cm}{The $k$-th dimension of the probability vector $\boldsymbol{\theta}$.}
+	\item [\parbox{2cm}{$\theta_{K}$}] \parbox{12.5cm}{The last dimension of the probability vector $\boldsymbol{\theta}$.}
+	\item [\parbox{2cm}{$\theta$}] \parbox{12.5cm}{Success probability for the Bernoulli probability distribution.}
+	\item [\parbox{2cm}{$A$}] \parbox{12.5cm}{Random event.}
+	\item [\parbox{2cm}{$B_{1}$}] \parbox{12.5cm}{The first set in the partition $S$.}
+	\item [\parbox{2cm}{$B_{2}$}] \parbox{12.5cm}{The second set in the partition $S$.}
+	\item [\parbox{2cm}{$B_{i}$}] \parbox{12.5cm}{The $i$-th set in the partition $S$.}
+	\item [\parbox{2cm}{$B_{j}$}] \parbox{12.5cm}{The $j$-th set in the partition $S$.}
+	\item [\parbox{2cm}{$B_{K}$}] \parbox{12.5cm}{The last set in the partition $S$.}
+	\item [\parbox{2cm}{$B(\alpha, \beta)$}] \parbox{12.5cm}{The normalising constant used in the \acs{PDF} of the Beta probability distribution.}
+	\item [\parbox{2cm}{$B(\boldsymbol{\alpha})$}] \parbox{12.5cm}{The normalising constant used in the \acs{PDF} of the Dirichlet probability distribution.}
+	\item [\parbox{2cm}{$B$}] \parbox{12.5cm}{Random event.}
+	\item [\parbox{2cm}{$Ber$}] \parbox{12.5cm}{The Bernoulli probability distribution.}
+	\item [\parbox{2cm}{$Beta$}] \parbox{12.5cm}{The Beta probability distribution.}
+	\item [\parbox{2cm}{$Bin$}] \parbox{12.5cm}{The Binomial probability distribution.}
+	\item [\parbox{2cm}{$c$}] \parbox{12.5cm}{Symmetric distribution constant.}
+	\item [\parbox{2cm}{$Cat$}] \parbox{12.5cm}{The Categorical probability distribution.}
+	\item [\parbox{2cm}{$Dir$}] \parbox{12.5cm}{The Dirichlet probability distribution.}
+	\item [\parbox{2cm}{$E[\ln(x_{k})]$}] \parbox{12.5cm}{The expected value of the natural logarithm of the $k$-th dimension of the random variable.}
+	\item [\parbox{2cm}{$E[\ln(x)]$}] \parbox{12.5cm}{The expected value of the natural logarithm of $x$.}
+	\item [\parbox{2cm}{$E[x_{k}]$}] \parbox{12.5cm}{The expected value of the $k$-th dimension of the random variable.}
+	\item [\parbox{2cm}{$E[x]$}] \parbox{12.5cm}{The expected value of the distribution of $x$.}
+	\item [\parbox{2cm}{$f_{Ber}$}] \parbox{12.5cm}{The \acs{PMF} for the Bernoulli probability distribution.}
+	\item [\parbox{2cm}{$f_{Beta}$}] \parbox{12.5cm}{The \acs{PDF} of the Beta probability distribution.}
+	\item [\parbox{2cm}{$f_{Bin}$}] \parbox{12.5cm}{The \acs{PMF} for the Binomial probability distribution.}
+	\item [\parbox{2cm}{$f_{Cat}$}] \parbox{12.5cm}{The \acs{PMF} for the Categorical probability distribution.}
+	\item [\parbox{2cm}{$f_{Dir}$}] \parbox{12.5cm}{The \acs{PDF} of the Dirichlet probability distribution.}
+	\item [\parbox{2cm}{$f_{Mul}$}] \parbox{12.5cm}{The \acs{PMF} for the Multinomial probability distribution.}
+	\item [\parbox{2cm}{$f$}] \parbox{12.5cm}{General symbol used for functions. Used for likelihood functions, \acp{PMF} and \acp{PDF}.}
+	\item [\parbox{2cm}{$F$}] \parbox{12.5cm}{The symbol used for a female outcome in the mice experiment.}
+	\item [\parbox{2cm}{$g^{*}$}] \parbox{12.5cm}{Posterior density.}
+	\item [\parbox{2cm}{$g$}] \parbox{12.5cm}{Prior density.}
+	\item [\parbox{2cm}{$i$}] \parbox{12.5cm}{Index to track sets in partition $S$. Also used as a general index in random variables in $I$ dimensions.}
+	\item [\parbox{2cm}{$I$}] \parbox{12.5cm}{The total number of independent, identical (iid) random events.}
+	\item [\parbox{2cm}{$j$}] \parbox{12.5cm}{Index to track sets in partition $S$. Also used as a general index in random variables in $J$ dimensions.}
+	\item [\parbox{2cm}{$k$}] \parbox{12.5cm}{Index used to denote class $k$ in $K$ classes. Also used as a general index in random variables in $K$ dimensions.}
+	\item [\parbox{2cm}{$K$}] \parbox{12.5cm}{The total number of sets in the partition $S$. Also used to denote the number of classes in the Dirichlet probability distribution.}
+	\item [\parbox{2cm}{$M[x_{k}]$}] \parbox{12.5cm}{The mode of the $k$-th dimension of the random variable.}
+	\item [\parbox{2cm}{$M[x]$}] \parbox{12.5cm}{The mode of the distribution of $x$.}
+	\item [\parbox{2cm}{$m$}] \parbox{12.5cm}{The marginal density function.}
+	\item [\parbox{2cm}{$M$}] \parbox{12.5cm}{The symbol used for a male outcome in the mice experiment.}
+	\item [\parbox{2cm}{$Mul$}] \parbox{12.5cm}{The Multinomial probability distribution.}
+	\item [\parbox{2cm}{$N_{0}$}] \parbox{12.5cm}{Summary variable tracking the number of unsuccessful Boolean outcomes.}
+	\item [\parbox{2cm}{$N_{1}$}] \parbox{12.5cm}{Summary variable tracking the number of successful Boolean outcomes.}
+	\item [\parbox{2cm}{$N_{k}$}] \parbox{12.5cm}{Summary variable, denoting the number of times a category $k$ occurs over all trials in $N$.}
+	\item [\parbox{2cm}{$N_{K}$}] \parbox{12.5cm}{Summary variable denoting the number of times category $k$ occurs.}
+	\item [\parbox{2cm}{$n$}] \parbox{12.5cm}{Input parameter to the Gamma function.}
+	\item [\parbox{2cm}{$N$}] \parbox{12.5cm}{The total number of events observed.}
+	\item [\parbox{2cm}{$P$}] \parbox{12.5cm}{The probability of some event.}
+	\item [\parbox{2cm}{$p$}] \parbox{12.5cm}{The statistical $p$-value.}
+	\item [\parbox{2cm}{$S$}] \parbox{12.5cm}{The union of mutually exclusive subsets. Also referred to as the probability simplex.}
+	\item [\parbox{2cm}{$x_{1}$}] \parbox{12.5cm}{The first dimension of the random variable. Also used as the first random event.}
+	\item [\parbox{2cm}{$x_{i,k}$}] \parbox{12.5cm}{The $k$-th dimension of the $i$-th random event vector $\boldsymbol{x}$.}
+	\item [\parbox{2cm}{$x_{i}$}] \parbox{12.5cm}{The $i$-th dimension of the random variable. Also used as the $i$-th random event.}
+	\item [\parbox{2cm}{$x_{I}$}] \parbox{12.5cm}{The last dimension of the random variable with $I$ dimensions. Also used as the last random event in $I$ random events.}
+	\item [\parbox{2cm}{$x_{j}$}] \parbox{12.5cm}{The $j$-th dimension of the random variable. Also used as the $j$-th random event.}
+	\item [\parbox{2cm}{$x_{k}$}] \parbox{12.5cm}{The $k$-th dimension of the random variable. Also used as the $k$-th random event.}
+	\item [\parbox{2cm}{$x_{K}$}] \parbox{12.5cm}{The last dimension of the random variable with $K$ dimensions. Also used as the last random event in $K$ random events.}
+	\item [\parbox{2cm}{$x$}] \parbox{12.5cm}{Random variable used by various probability distributions. Also referred to as a realisation of an event that occurred as a results of a random process $X$.}
+	\item [\parbox{2cm}{$Y_{1}$}] \parbox{12.5cm}{The first random event in $\boldsymbol{Y}$.}
+	\item [\parbox{2cm}{$y_{1}$}] \parbox{12.5cm}{The realisation of the first random event in $\boldsymbol{Y}$.}
+	\item [\parbox{2cm}{$y_{2}$}] \parbox{12.5cm}{The realisation of the second random event in $\boldsymbol{Y}$.}
+	\item [\parbox{2cm}{$Y_{2}$}] \parbox{12.5cm}{The second random event in $\boldsymbol{Y}$.}
+	\item [\parbox{2cm}{$Y_{i}$}] \parbox{12.5cm}{The $i$-th random event in $\boldsymbol{Y}$.}
+	\item [\parbox{2cm}{$y_{i}$}] \parbox{12.5cm}{The realisation of the $i$-th random event in $\boldsymbol{Y}$.}
+	\item [\parbox{2cm}{$Y_{N}$}] \parbox{12.5cm}{The last random event in $\boldsymbol{Y}$ with $N$ events.}
+	\item [\parbox{2cm}{$y_{n}$}] \parbox{12.5cm}{The realisation of the $n$-th random event in $\boldsymbol{Y}$ with $N$ events.}
 \end{description}
@@
 \begin{description}
-	\item [\parbox{2cm}{$\alpha_{1}$}]
-	\item [\parbox{2cm}{$\alpha_{k}$}]
-	\item [\parbox{2cm}{$\alpha_{K}$}]
-	\item [\parbox{2cm}{$\alpha$}]
-	\item [\parbox{2cm}{$\beta_{1}$}]
-	\item [\parbox{2cm}{$\beta_{2}$}]
-	\item [\parbox{2cm}{$\beta_{j,k}$}]
-	\item [\parbox{2cm}{$\beta_{K}^{J}$}]
-	\item [\parbox{2cm}{$\beta$}]
-	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\beta}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\gamma}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\hat{\phi}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\hat{\psi}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\hat{\theta}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\lambda}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\phi}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\psi}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
-	\item [\parbox{2cm}{$\boldsymbol{C}$}]
-	\item [\parbox{2cm}{$\boldsymbol{E}$}]
-	\item [\parbox{2cm}{$\boldsymbol{H}$}]
-	\item [\parbox{2cm}{$\epsilon(-1)$}]
-	\item [\parbox{2cm}{$\epsilon$}]
-	\item [\parbox{2cm}{$\eta$}]
-	\item [\parbox{2cm}{$\gamma_{0}$}]
-	\item [\parbox{2cm}{$\gamma_{1,k}$}]
-	\item [\parbox{2cm}{$\gamma_{1}$}]
-	\item [\parbox{2cm}{$\gamma_{2,k}$}]
-	\item [\parbox{2cm}{$\gamma_{K}$}]
-	\item [\parbox{2cm}{$\hat{\phi}_{j,k}$}]
-	\item [\parbox{2cm}{$\hat{\psi_{k}}$}]
-	\item [\parbox{2cm}{$\hat{\psi}_{k}$}]
-	\item [\parbox{2cm}{$\hat{\theta_{k}}$}]
-	\item [\parbox{2cm}{$\hat{\theta}_{k}$}]
-	\item [\parbox{2cm}{$\lambda_{1}$}]
-	\item [\parbox{2cm}{$\lambda_{j}$}]
-	\item [\parbox{2cm}{$\lambda_{J}$}]
-	\item [\parbox{2cm}{$\mathbbm{1}_{0}$}]
-	\item [\parbox{2cm}{$\mathbbm{1}_{1}$}]
-	\item [\parbox{2cm}{$\mathbin{\%}$}]
-	\item [\parbox{2cm}{$\mathcal{A}(v)$}]
-	\item [\parbox{2cm}{$\mathcal{L}$}]
-	\item [\parbox{2cm}{$\phi_{j,k}$}]
-	\item [\parbox{2cm}{$\phi_{jk}$}]
-	\item [\parbox{2cm}{$\phi$}]
-	\item [\parbox{2cm}{$\psi_{k}$}]
-	\item [\parbox{2cm}{$\psi_{k}N_{k}$}]
-	\item [\parbox{2cm}{$\psi$}]
-	\item [\parbox{2cm}{$\theta_{k}$}]
-	\item [\parbox{2cm}{$\theta$}]
-	\item [\parbox{2cm}{$A$}]
-	\item [\parbox{2cm}{$B$}]
-	\item [\parbox{2cm}{$Beta$}]
-	\item [\parbox{2cm}{$Bin$}]
-	\item [\parbox{2cm}{$c_{1}$}]
-	\item [\parbox{2cm}{$c_{i,k}$}]
-	\item [\parbox{2cm}{$c_{i}$}]
-	\item [\parbox{2cm}{$Dir$}]
-	\item [\parbox{2cm}{$e_{i,j,k}$}]
-	\item [\parbox{2cm}{$e_{i}$}]
-	\item [\parbox{2cm}{$e_{j}$}]
-	\item [\parbox{2cm}{$E[\phi_{j,k}]$}]
-	\item [\parbox{2cm}{$E[\psi_{k}]$}]
-	\item [\parbox{2cm}{$E[\theta_{k}]$}]
-	\item [\parbox{2cm}{$h_{i,k}$}]
-	\item [\parbox{2cm}{$h_{i}$}]
-	\item [\parbox{2cm}{$h_{k}$}]
-	\item [\parbox{2cm}{$i$}]
-	\item [\parbox{2cm}{$I$}]
-	\item [\parbox{2cm}{$j$}]
-	\item [\parbox{2cm}{$J$}]
-	\item [\parbox{2cm}{$K-1$}]
-	\item [\parbox{2cm}{$k$}]
-	\item [\parbox{2cm}{$K$}]
-	\item [\parbox{2cm}{$L$}]
-	\item [\parbox{2cm}{$LSE$}]
-	\item [\parbox{2cm}{$Mult$}]
-	\item [\parbox{2cm}{$N_{0,k}$}]
-	\item [\parbox{2cm}{$N_{1,k}$}]
-	\item [\parbox{2cm}{$N_{j,k}$}]
-	\item [\parbox{2cm}{$N_{j}$}]
-	\item [\parbox{2cm}{$N_{k}$}]
-	\item [\parbox{2cm}{$N$}]
-	\item [\parbox{2cm}{$S$}]
-	\item [\parbox{2cm}{$t$}]
+
+	\item [\parbox{2cm}{$\alpha_{1}$}] \parbox{12.5cm}{The first dimension of the concentration parameter, $\boldsymbol{\alpha}$.}
+	\item [\parbox{2cm}{$\alpha_{K}$}] \parbox{12.5cm}{The $k$-th dimension of the concentration parameter, $\boldsymbol{\alpha}$.}
+	\item [\parbox{2cm}{$\alpha_{k}$}] \parbox{12.5cm}{The dimension of $\boldsymbol{\alpha}$ associated with class $k$.}
+	\item [\parbox{2cm}{$\alpha$}] \parbox{12.5cm}{Concentration parameter for the Beta probability distribution.}
+	\item [\parbox{2cm}{$\beta_{1}$}] \parbox{12.5cm}{The first dimension of the concentration parameter, $\boldsymbol{\beta}$.}
+	\item [\parbox{2cm}{$\beta_{2}$}] \parbox{12.5cm}{The second dimension of the concentration parameter, $\boldsymbol{\beta}$.}
+	\item [\parbox{2cm}{$\beta_{j,k}$}] \parbox{12.5cm}{The $j$-th entity's concentration parameter associated with heuristic $k$.}
+	\item [\parbox{2cm}{$\beta$}] \parbox{12.5cm}{Concentration parameter for the Beta probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}] \parbox{12.5cm}{The concentration parameters for the heuristic probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{\beta}$}] \parbox{12.5cm}{The concentration parameters for the entity-heuristic probability distributions.}
+	\item [\parbox{2cm}{$\boldsymbol{\gamma}$}] \parbox{12.5cm}{The concentration parameters for the credit-heuristic probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{\hat{\phi}}$}] \parbox{12.5cm}{The expected value of the entity-heuristic probabilities.}
+	\item [\parbox{2cm}{$\boldsymbol{\hat{\psi}}$}] \parbox{12.5cm}{The expected value of the heuristic-credit-assignment probabilities.}
+	\item [\parbox{2cm}{$\boldsymbol{\hat{\theta}}$}] \parbox{12.5cm}{The expected value of the heuristic selection probabilities.}
+	\item [\parbox{2cm}{$\boldsymbol{\lambda}$}] \parbox{12.5cm}{Error vector.}
+	\item [\parbox{2cm}{$\boldsymbol{\phi}$}] \parbox{12.5cm}{The entity-heuristic probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{\psi}$}] \parbox{12.5cm}{The credit-heuristic probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{\theta}$}] \parbox{12.5cm}{The heuristic probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{C}$}] \parbox{12.5cm}{The event of observing credit assignments upon meeting credit assignment criteria.}
+	\item [\parbox{2cm}{$\boldsymbol{E}$}] \parbox{12.5cm}{The event of observing entities.}
+	\item [\parbox{2cm}{$\boldsymbol{H}$}] \parbox{12.5cm}{The event of observing heuristics.}
+	\item [\parbox{2cm}{$\epsilon$}] \parbox{12.5cm}{Error factor.}
+	\item [\parbox{2cm}{$\eta$}] \parbox{12.5cm}{Learning rate.}
+	\item [\parbox{2cm}{$\gamma_{0}$}] \parbox{12.5cm}{The zeroth dimension of the concentration parameter, $\boldsymbol{\gamma}$.}
+	\item [\parbox{2cm}{$\gamma_{1,k}$}] \parbox{12.5cm}{The first dimension of the concentration parameter, $\boldsymbol{\gamma}$ associated with heuristic $k$.}
+	\item [\parbox{2cm}{$\gamma_{1}$}] \parbox{12.5cm}{The first dimension of the concentration parameter, $\boldsymbol{\gamma}$.}
+	\item [\parbox{2cm}{$\gamma_{2,k}$}] \parbox{12.5cm}{The second dimension of the concentration parameter, $\boldsymbol{\gamma}$ associated with heuristic $k$.}
+	\item [\parbox{2cm}{$\gamma_{K}$}] \parbox{12.5cm}{The $k$-th dimension of the concentration parameter, $\boldsymbol{\gamma}$.}
+	\item [\parbox{2cm}{$\hat{\phi}_{j,k}$}] \parbox{12.5cm}{The expected value of the probability of selecting heuristic $k$ for entity $j$.}
+	\item [\parbox{2cm}{$\hat{\psi}_{k}$}] \parbox{12.5cm}{The expected value of the probability of selecting heuristic $k$ and observing credit assignments.}
+	\item [\parbox{2cm}{$\hat{\theta}_{k}$}] \parbox{12.5cm}{The expected value of the probability of selecting heuristic $k$.}
+	\item [\parbox{2cm}{$\lambda_{j}$}] \parbox{12.5cm}{The $j$-th dimension of the error vector, $\boldsymbol{\lambda}$.}
+	\item [\parbox{2cm}{$\lambda_{J}$}] \parbox{12.5cm}{The last dimension of the error vector, $\boldsymbol{\lambda}$ in $J$ dimensions.}
+	\item [\parbox{2cm}{$\mathbbm{1}_{0}$}] \parbox{12.5cm}{The indicator function yielding a failure/non-occurrence.}
+	\item [\parbox{2cm}{$\mathbbm{1}_{1}$}] \parbox{12.5cm}{The indicator function yielding a success/occurrence.}
+	\item [\parbox{2cm}{$\mathcal{A}(v)$}] \parbox{12.5cm}{Functional form of priors.}
+	\item [\parbox{2cm}{$\mathcal{L}$}] \parbox{12.5cm}{The likelihood function.}
+	\item [\parbox{2cm}{$\phi_{j,k}$}] \parbox{12.5cm}{The entity-heuristic selection probability for entity $j$ and heuristic $k$.}
+	\item [\parbox{2cm}{$\psi_{k}$}] \parbox{12.5cm}{The successful credit assignment probability for heuristic $k$.}
+	\item [\parbox{2cm}{$\theta_{k}$}] \parbox{12.5cm}{The heuristic selection probability for heuristic $k$.}
+	\item [\parbox{2cm}{$A$}] \parbox{12.5cm}{A random event.}
+	\item [\parbox{2cm}{$B$}] \parbox{12.5cm}{A random event.}
+	\item [\parbox{2cm}{$Beta$}] \parbox{12.5cm}{The Beta probability distribution.}
+	\item [\parbox{2cm}{$Bin$}] \parbox{12.5cm}{The Binomial probability distribution.}
+	\item [\parbox{2cm}{$c_{1}$}] \parbox{12.5cm}{Successful credit allocation.}
+	\item [\parbox{2cm}{$c_{i,k}$}] \parbox{12.5cm}{The realisation of the $i$-th event of observing a credit assignment $i$ to heuristic $k$.}
+	\item [\parbox{2cm}{$c_{i}$}] \parbox{12.5cm}{The $i$-th event of observing credit assignments.}
+	\item [\parbox{2cm}{$Dir$}] \parbox{12.5cm}{The Dirichlet probability distribution.}
+	\item [\parbox{2cm}{$e_{i,j,k}$}] \parbox{12.5cm}{The realisation of the $i$-th event of observing heuristic $k$ for selected for entity $j$.}
+	\item [\parbox{2cm}{$e_{i}$}] \parbox{12.5cm}{The $i$-th event of observing entities.}
+	\item [\parbox{2cm}{$e_{j}$}] \parbox{12.5cm}{The $j$-th entity.}
+	\item [\parbox{2cm}{$E[\phi_{j,k}]$}] \parbox{12.5cm}{The expected value of the probability of selecting heuristic $k$ for entity $j$.}
+	\item [\parbox{2cm}{$E[\psi_{k}]$}] \parbox{12.5cm}{The expected value of the probability of selecting heuristic $k$ and observing credit assignments.}
+	\item [\parbox{2cm}{$E[\theta_{k}]$}] \parbox{12.5cm}{The expected value of the probability of selecting heuristic $k$.}
+	\item [\parbox{2cm}{$h_{i,k}$}] \parbox{12.5cm}{The realisation of the $i$-th event of observing heuristic $k$.}
+	\item [\parbox{2cm}{$h_{i}$}] \parbox{12.5cm}{The $i$-th event of observing heuristics.}
+	\item [\parbox{2cm}{$h_{k}$}] \parbox{12.5cm}{The $k$-th heuristic.}
+	\item [\parbox{2cm}{$i$}] \parbox{12.5cm}{Index generally associated with event/run $i$.}
+	\item [\parbox{2cm}{$I$}] \parbox{12.5cm}{The maximum number of instances in the replay window.}
+	\item [\parbox{2cm}{$j$}] \parbox{12.5cm}{Index generally associated to entity $j$.}
+	\item [\parbox{2cm}{$J$}] \parbox{12.5cm}{The entity pool (population) size.}
+	\item [\parbox{2cm}{$k$}] \parbox{12.5cm}{Index generally associated to heuristic $k$.}
+	\item [\parbox{2cm}{$K$}] \parbox{12.5cm}{The heuristic pool size.}
+	\item [\parbox{2cm}{$L$}] \parbox{12.5cm}{The number of credit assignment output classes.}
+	\item [\parbox{2cm}{$LSE$}] \parbox{12.5cm}{The log-sum-exp trick/function.}
+	\item [\parbox{2cm}{$Mult$}] \parbox{12.5cm}{The Multinomial probability distribution.}
+	\item [\parbox{2cm}{$N_{0,k}$}] \parbox{12.5cm}{The count of occurrences of the events $c_{i}$ taking on a failure.}
+	\item [\parbox{2cm}{$N_{1,k}$}] \parbox{12.5cm}{The count of occurrences of the events $c_{i}$ taking on a success.}
+	\item [\parbox{2cm}{$N_{j,k}$}] \parbox{12.5cm}{A summary variable denoting the count of occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on class $k$ in $I$ independent, identical runs.}
+	\item [\parbox{2cm}{$N_{j}$}] \parbox{12.5cm}{The count of the occurrences of observing entity $j$.}
+	\item [\parbox{2cm}{$N_{k}$}] \parbox{12.5cm}{A summary variable denoting the count of occurrences of the event $h_{i}$ taking on class $k$ in $I$ independent, identical runs.}
+	\item [\parbox{2cm}{$N$}] \parbox{12.5cm}{The maximum number of random events observed.}
+	\item [\parbox{2cm}{$S$}] \parbox{12.5cm}{The probability simplex.}
+	\item [\parbox{2cm}{$t$}] \parbox{12.5cm}{Time step.}
+	\item [\parbox{2cm}{$\lambda_{1}$}] \parbox{12.5cm}{The first dimension of the error vector, $\boldsymbol{\lambda}$.}
 \end{description}
@@
 \begin{description}
-	\item [\parbox{2cm}{$\alpha$}] Used as a scaling parameter for the \acs{LReLU} activation function. Also used as a threshold parameter for the statistical significance tests.
-	\item [\parbox{2cm}{$\eta$}] Learning rate.
-	\item [\parbox{2cm}{$\mathbb{R}$}] Real-number space.
-	\item [\parbox{2cm}{$v_{ij}$}] The $j$-th dimension of the velocity vector of the $i$-th particle in the population implemented by \acs{PSO}.
-	\item [\parbox{2cm}{$x_{ij}$}] The $j$-th dimension of the position vector of the $i$-th particle in the population implemented by \acs{PSO}.
+	\item [\parbox{2cm}{$\alpha$}] \parbox{12.5cm}{Used as a scaling parameter for the \acs{LReLU} activation function. Also used as a threshold parameter for the statistical significance tests.}
+	\item [\parbox{2cm}{$\eta$}] \parbox{12.5cm}{Learning rate.}
+	\item [\parbox{2cm}{$\mathbb{R}$}] \parbox{12.5cm}{Real-number space.}
+	\item [\parbox{2cm}{$v_{ij}$}] \parbox{12.5cm}{The $j$-th dimension of the velocity vector of the $i$-th particle in the population implemented by \acs{PSO}.}
+	\item [\parbox{2cm}{$x_{ij}$}] \parbox{12.5cm}{The $j$-th dimension of the position vector of the $i$-th particle in the population implemented by \acs{PSO}.}
 \end{description}
@@
 \begin{description}
-	\item [\parbox{2cm}{$\alpha_{0}$}]
-	\item [\parbox{2cm}{$\alpha_{6}$}]
-	\item [\parbox{2cm}{$\alpha_{7}$}]
-	\item [\parbox{2cm}{$\alpha_{8}$}]
-	\item [\parbox{2cm}{$\alpha_{i} = 50$}]
-	\item [\parbox{2cm}{$\boldsymbol{{H}}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\phi}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\psi}$}]
-	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
-	\item [\parbox{2cm}{$\boldsymbol{C}$}]
-	\item [\parbox{2cm}{$\boldsymbol{E}$}]
-	\item [\parbox{2cm}{$\boldsymbol{H}$}]
-	\item [\parbox{2cm}{$\pm$}]
-	\item [\parbox{2cm}{$\theta_{0}$}]
-	\item [\parbox{2cm}{$\theta_{6}$}]
-	\item [\parbox{2cm}{$\theta_{7}$}]
-	\item [\parbox{2cm}{$\theta_{8}$}]
-	\item [\parbox{2cm}{$c_{1}$}]
-	\item [\parbox{2cm}{$Cat$}]
-	\item [\parbox{2cm}{$Dir$}]
-	\item [\parbox{2cm}{$e_{0}$}]
-	\item [\parbox{2cm}{$h_{0}$}]
-	\item [\parbox{2cm}{$h_{6}$}]
-	\item [\parbox{2cm}{$h_{7}$}]
-	\item [\parbox{2cm}{$h_{8}$}]
-	\item [\parbox{2cm}{$i$}]
-	\item [\parbox{2cm}{$K$}]
+	\item [\parbox{2cm}{$\alpha_{0}$}] \parbox{12.5cm}{The zeroth dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $0$ (\acs{SGD}).}
+	\item [\parbox{2cm}{$\alpha_{6}$}] \parbox{12.5cm}{The sixth dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $6$ (\acs{Adam}).}
+	\item [\parbox{2cm}{$\alpha_{7}$}] \parbox{12.5cm}{The seventh dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $7$ (\acs{PSO}).}
+	\item [\parbox{2cm}{$\alpha_{8}$}] \parbox{12.5cm}{The eight dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $8$ (\acs{GA}).}
+	\item [\parbox{2cm}{$\alpha_{i}$}] \parbox{12.5cm}{The $i$-th dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $i$.}
+	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}] \parbox{12.5cm}{The concentration parameters for the heuristic probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{\phi}$}] \parbox{12.5cm}{The entity-heuristic probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{\psi}$}] \parbox{12.5cm}{The credit-heuristic probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{\theta}$}] \parbox{12.5cm}{The heuristic probability distribution.}
+	\item [\parbox{2cm}{$\boldsymbol{C}$}] \parbox{12.5cm}{The event of observing credit assignments upon meeting credit assignment criteria.}
+	\item [\parbox{2cm}{$\boldsymbol{E}$}] \parbox{12.5cm}{The event of observing entities.}
+	\item [\parbox{2cm}{$\boldsymbol{H}$}] \parbox{12.5cm}{The event of observing heuristics.}
+	\item [\parbox{2cm}{$\theta_{0}$}] \parbox{12.5cm}{The zeroth dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $0$ (\acs{SGD}).}
+	\item [\parbox{2cm}{$\theta_{6}$}] \parbox{12.5cm}{The sixth dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $6$ (\acs{Adam}).}
+	\item [\parbox{2cm}{$\theta_{7}$}] \parbox{12.5cm}{The seventh dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $7$ (\acs{PSO}).}
+	\item [\parbox{2cm}{$\theta_{8}$}] \parbox{12.5cm}{The eight dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $8$ (\acs{GA}).}
+	\item [\parbox{2cm}{$c_{1}$}] \parbox{12.5cm}{Successful credit allocation.}
+	\item [\parbox{2cm}{$Cat$}] \parbox{12.5cm}{The Categorical probability distribution.}
+	\item [\parbox{2cm}{$Dir$}] \parbox{12.5cm}{The Dirichlet probability distribution.}
+	\item [\parbox{2cm}{$e_{0}$}] \parbox{12.5cm}{Entity $0$.}
+	\item [\parbox{2cm}{$h_{0}$}] \parbox{12.5cm}{Heuristic $0$ (\acs{SGD}).}
+	\item [\parbox{2cm}{$h_{6}$}] \parbox{12.5cm}{Heuristic $6$ (\acs{Adam}).}
+	\item [\parbox{2cm}{$h_{7}$}] \parbox{12.5cm}{Heuristic $7$ (\acs{PSO}).}
+	\item [\parbox{2cm}{$h_{8}$}] \parbox{12.5cm}{Heuristic $8$ (\acs{GA}).}
+	\item [\parbox{2cm}{$i$}] \parbox{12.5cm}{General index associated with event/run number.}
+	\item [\parbox{2cm}{$K$}] \parbox{12.5cm}{Heuristic pool size.}
 \end{description}

### 2025-01-13 dissertation/chapters/02-artificial-neural-networks.tex
💚 For Taylah, Beané & Aleah

@@
 \begin{equation}
-      x_{i,p}^{'} = \frac{x_{i,p} - \mu_i}{\sigma^2_i}
+      x_{i,p}^{'} = \frac{x_{i,p} - \mu_i}{\sigma_i}
       \label{eq:standard_score_scaler}
@@
 
-\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of \index{random uniform sampling}random uniform sampling, whereby $\omega_{i} = \sqrt{\frac{6}{fanin + fanout}}$ and $fanin$ is the number of input neurons to the weight vector and $fanout$ is the number of output neurons from the weight vector.
+\index{Glorot uniform sampling}Glorot uniform sampling is a specialisation of \index{random uniform sampling}random uniform sampling, whereby $\omega_{max} = \sqrt{\frac{6}{fanin + fanout}}$ and $fanin$ is the number of input neurons to the weight vector and $fanout$ is the number of output neurons from the weight vector.
 

### 2025-01-13 dissertation/chapters/05-probability.tex
💚 For Taylah, Beané & Aleah

@@
       \label{eq:probability:probability_distributions:beta:mode}
-      M[x] = E[x] - 1 = \frac{\alpha - 1}{\alpha + \beta - 1}
+      M[x] = E[x] - 1 = \frac{\alpha - 1}{\alpha + \beta - 2}
 \end{equation}
@@
 The \index{Dirichlet probability distribution}Dirichlet probability distribution is a family of multivariate continuous probability distributions over some $\boldsymbol{x}$ in $K$ dimensions~\cite{ref:wackerly:2014}.
-The \index{Dirichlet probability distribution}Dirichlet probability distribution is a multivariate generalization of the \index{Beta probability distribution}Beta probability distribution and is thus sometimes referred to by its alternative name, i.e.
+The \index{Dirichlet probability distribution}Dirichlet probability distribution is a multivariate generalisation of the \index{Beta probability distribution}Beta probability distribution and is thus sometimes referred to by its alternative name, i.e.
 the multivariate Beta probability distribution.
@@
 This means that the probability $P(x=k)=\theta_{k}$ has support $x \in \{1, \dots, K\}$.
-The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\boldsymbol{\theta})$, is a generalization of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, i.e.
+The \index{Categorical probability distribution}Categorical probability distribution, denoted $Cat(\boldsymbol{\theta})$, is a generalisation of the \index{Bernoulli probability distribution}Bernoulli probability distribution and is sometimes referred to it by its alternative names, i.e.
 the generalised \index{Bernoulli probability distribution}Bernoulli probability distribution or the Multinoulli probability distribution.
@@
 The probabilities for all possible outcomes in a single trial is given by the probability vector, $\boldsymbol{\theta} = (\theta_{1}, \dots, \theta_{K})$.
-The \index{Multinomial probability distribution}Multinomial probability distribution, denoted $Mul(N, K, \boldsymbol{\theta})$, is thus a generalization of the \index{Binomial probability distribution}Binomial probability distribution to $K$ dimensions.
+The \index{Multinomial probability distribution}Multinomial probability distribution, denoted $Mul(N, K, \boldsymbol{\theta})$, is thus a generalisation of the \index{Binomial probability distribution}Binomial probability distribution to $K$ dimensions.
 Consider the following special cases:
@@
       \includegraphics[width=0.6\textwidth]{images/mouse_experiment_outcome.pdf}
-      \caption{The experimental outcomes for the mice-population experiments as was taken from~\cite{ref:hackenberger:2019} .}
+      \caption{The experimental outcomes for the mice-population experiments as were taken from~\cite{ref:hackenberger:2019} .}
       \label{fig:probability:bayesian_statistics:mouse_experiment_outcome}

### 2025-01-13 dissertation/chapters/07-methodology.tex
🍱 (images): Recovered
💚 Dedicated to Taylah, Beané & Aleah
💚 For Taylah, Beané & Aleah

@@
 
+      \item \textbf{Section \ref{sec:methodology:statistical_analysis}} presents the procedures that are followed for the statistical analysis of the results.
+
       \item \textbf{Section \ref{sec:methodology:implementation}} sheds light on the implementation and execution of the empirical process.
-
-      \item \textbf{Section \ref{sec:methodology:statistical_analysis}} presents the procedures that are followed for the statistical analysis of the results.
 
@@
 
-Details around each of these elements are provided in the following sections.
+Details around each of these elements is provided in the following sections.
 
@@
 This section provides the details of the low-level \index{heuristic}heuristics that are used in the empirical process.
-Each of these low-level \index{heuristic}heuristics are implemented as standalone \index{heuristic}heuristics and are also included in the \index{heuristic pool}heuristic pool of the \acs{BHH}.
+Each of these low-level \index{heuristic}heuristics is implemented as standalone \index{heuristic}heuristics and is also included in the \index{heuristic pool}heuristic pool of the \acs{BHH}.
 Table \ref{tab:methodology:heuristics} contains a list of all the standalone, low-level \index{heuristic}heuristics that are used as well as their hyper-parameter configurations.
@@
       \centering
-      \includegraphics[width=0.95\textwidth]{images/bhh_heuristic_proxies.pdf}
+      \includegraphics[width=0.7\textwidth]{images/bhh_heuristic_proxies.pdf}
       \caption{Mapping of proxied heuristic state update operations as implemented by the \acs{BHH}}
@@
 Three main experimental groups are formulated.
-Each of these are discussed in more detail in the following sections.
+Each of these is discussed in more detail in the following sections.
 
@@
 For the standalone \index{heuristic}heuristics experimental group, the \index{heuristic}heuristics, as presented in Section \ref{sec:methodology:heuristics}, are used along with their specified hyper-parameters.
-Each of these standalone low-level \index{heuristic}heuristics are compared to that of the \acs{BHH} baseline configuration, across all datasets.
+Each of these standalone low-level \index{heuristic}heuristics is compared to that of the \acs{BHH} baseline configuration, across all datasets.
 
@@
 Various experimental groups and configurations have been presented in Sections \ref{sec:methodology:experiments:case_study}, \ref{sec:methodology:experiments:standalone_optimisers} and \ref{sec:methodology:experiments:bhh_variants}.
-The results from each of these experimental groups are statistically analysed.
+The results from each of these experimental groups is statistically analysed.
 To ensure that there are sufficient samples for statistical analysis, each experiment and configuration is trained for 30 epochs and is repeated over 30 runs, for each of the fourteen datasets.

### 2025-01-13 dissertation/preamble/acknowledgements.tex
✨ (dissertation): Chapter 1 done
✨ (final-review): Done up till chapter 1
💚 For Taylah, Beané & Aleah

@@
 \begin{quotation}
-    \noindent
-    ``I've made the most important discovery of my life. It's only in
+    \noindent ``I've made the most important discovery of my life. It's only in
     the mysterious equation of love that any logical reasons can be found. I'm
@@
 \begin{flushright}
-    Prof. J.F. Nash, Jr.
+    - Prof. J.F. Nash, Jr.
 \end{flushright}
@@
 
-    \item To my supervisors, Dr. A. Bosman, Prof. C.W. Cleghorn and Prof. A.P. Engelbrecht. Thank you for not giving up on me.
+    \item To my supervisors, Dr. A.S. Bosman, Prof. C.W. Cleghorn and Prof. A.P. Engelbrecht. Thank you for not giving up on me.
+
+    \item To EPI-USE. Thank you for helping out where I needed it.
 
@@
 \begin{center}
-    This project was made possible by the National Research Foundation (NRF) and the Center for High Performance Computing (CHPC) Cluster at the Council for Scientific and Industrial Research (CSIR).
+    This project was made possible by the National Research Foundation (NRF) and the Centre for High Performance Computing (CHPC) Cluster at the Council for Scientific and Industrial Research (CSIR).
 \end{center}

### 2025-01-13 dissertation/preamble/supervisors.tex
📝 (review): First set of changes
✨ (feat): Review, analysis script updated
✨ (dissertation): Chapter 1 done
💚 For Taylah, Beané & Aleah

--- 2022-01-07 thesis/preamble/supervisors.tex
@@
 \noindent
-\parbox{4cm}{\textbf{Supervisor:}} Dr. A. Bosman \\*[2mm]
-\parbox{4cm}{\textbf{~}} University of the Pretoria \\*[2mm]
-\parbox{4cm}{\textbf{~}} Department of Computer Science\\*[1cm]
-\parbox{4cm}{\textbf{Co-Supervisor:}} Dr. C.W. Cleghorn \\*[2mm]
-\parbox{4cm}{\textbf{~}} University of the Witwatersrand\\*[2mm]
-\parbox{4cm}{\textbf{~}} Department of Computer Science\\*[1cm]
-\parbox{4cm}{\textbf{Co-Supervisor:}} Prof. A.P. Engelbrecht \\*[2mm]
-\parbox{4cm}{\textbf{~}} University of Stellenbosch\\*[2mm]
-\parbox{4cm}{\textbf{~}} Department of Industrial Engineering\\*[1cm]
-\parbox{4cm}{\textbf{Degree:}} Master of Science, Computer Science (Artificial
-Intelligence)
+\parbox{4cm}{\textbf{Supervisor:}}\parbox{12cm}{Dr. A.S. Bosman}\\*[2mm]
+\parbox{4cm}{\textbf{~}}\parbox{12cm}{University of the Pretoria}\\*[2mm]
+\parbox{4cm}{\textbf{~}}\parbox{12cm}{Department of Computer Science}\\*[1cm]
+\parbox{4cm}{\textbf{Supervisor:}}\parbox{12cm}{Prof. C.W. Cleghorn}\\*[2mm]
+\parbox{4cm}{\textbf{~}}\parbox{12cm}{University of the Witwatersrand}\\*[2mm]
+\parbox{4cm}{\textbf{~}}\parbox{12cm}{Department of Computer Science}\\*[1cm]
+\parbox{4cm}{\textbf{Supervisor:}}\parbox{12cm}{Prof. A.P. Engelbrecht}\\*[2mm]
+\parbox{4cm}{\textbf{~}}\parbox{12cm}{Stellenbosch University}\\*[2mm]
+\parbox{4cm}{\textbf{~}}\parbox{12cm}{Department of Industrial Engineering, Computer Science Division}\\*[1cm]
+\parbox{4cm}{\textbf{Degree:}}\parbox{12cm}{Master of Science, Computer Science (Artificial Intelligence)}
 \newpage

### 2025-01-13 bhh.py

@@ -1,0 +1,307 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright 2021 Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+
+import argparse
+import os
+
+import framework as fw
+import params
+
+# Globals
+DATASET = None
+OPTIMISER = None
+SEED = None
+LOG_LEVEL = None
+PARAMS = None
+LOG = None
+HEURISTIC_POOL = None
+POPULATION_SIZE = None
+BURN_IN = None
+REPLAY = None
+RESELECTION = None
+REANALYSIS = None
+NORMALISE = None
+CREDIT = None
+DISCOUNTED_REWARDS = None
+
+
+def parse_bhh_arguments():
+    global DATASET
+    global OPTIMISER
+    global SEED
+    global LOG_LEVEL
+    global PARAMS
+    global LOG
+    global HEURISTIC_POOL
+    global POPULATION_SIZE
+    global BURN_IN
+    global REPLAY
+    global RESELECTION
+    global REANALYSIS
+    global NORMALISE
+    global CREDIT
+    global DISCOUNTED_REWARDS
+
+    # Parser
[…]

### 2025-01-13 experiments/chpc/again2.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+
+#PBS -N again2
+#PBS -q serial
+#PBS -P CSCI0886
+#PBS -l select=1:ncpus=24:mem=120gb:ngpus=0
+#PBS -l walltime=48:00:00
+#PBS -o /mnt/lustre/users/aschreuder/tracking/stdin/again.out
+#PBS -e /mnt/lustre/users/aschreuder/tracking/stderr/again.err
+#PBS -m abe -M arneschreuder@icloud.com
+
+ulimit -s unlimited
+
+# Move to the directory of interest
+cd /mnt/lustre/users/aschreuder/masters.ai/
+
+# Can activate your python environment here
+module purge
+module load chpc/python/3.7.0
+
+# Run your script
+source .venv/bin/activate
+bash experiments/scripts/again2.sh

### 2025-01-13 experiments/chpc/again3.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+
+#PBS -N again3
+#PBS -q serial
+#PBS -P CSCI0886
+#PBS -l select=1:ncpus=24:mem=120gb:ngpus=0
+#PBS -l walltime=48:00:00
+#PBS -o /mnt/lustre/users/aschreuder/tracking/stdin/again.out
+#PBS -e /mnt/lustre/users/aschreuder/tracking/stderr/again.err
+#PBS -m abe -M arneschreuder@icloud.com
+
+ulimit -s unlimited
+
+# Move to the directory of interest
+cd /mnt/lustre/users/aschreuder/masters.ai/
+
+# Can activate your python environment here
+module purge
+module load chpc/python/3.7.0
+
+# Run your script
+source .venv/bin/activate
+bash experiments/scripts/again3.sh

### 2025-01-13 experiments/chpc/again7.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+
+#PBS -N again7
+#PBS -q serial
+#PBS -P CSCI0886
+#PBS -l select=1:ncpus=24:mem=120gb:ngpus=0
+#PBS -l walltime=48:00:00
+#PBS -o /mnt/lustre/users/aschreuder/tracking/stdin/again.out
+#PBS -e /mnt/lustre/users/aschreuder/tracking/stderr/again.err
+#PBS -m abe -M arneschreuder@icloud.com
+
+ulimit -s unlimited
+
+# Move to the directory of interest
+cd /mnt/lustre/users/aschreuder/masters.ai/
+
+# Can activate your python environment here
+module purge
+module load chpc/python/3.7.0
+
+# Run your script
+source .venv/bin/activate
+bash experiments/scripts/again7.sh

### 2025-01-13 experiments/chpc/bhh_credit2.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+
+#PBS -N bhh_ct2
+#PBS -q bigmem
+#PBS -P CSCI0886
+#PBS -l select=1:ncpus=56:mem=256gb:ngpus=0
+#PBS -l walltime=48:00:00
+#PBS -o /mnt/lustre/users/aschreuder/tracking/stdin/bhh_ct.out
+#PBS -e /mnt/lustre/users/aschreuder/tracking/stderr/bhh_ct.err
+#PBS -m abe -M arneschreuder@icloud.com
+
+ulimit -s unlimited
+
+# Move to the directory of interest
+cd /mnt/lustre/users/aschreuder/masters.ai/
+
+# Can activate your python environment here
+module purge
+module load chpc/python/3.7.0
+
+# Run your script
+source .venv/bin/activate
+bash experiments/scripts/bhh_credit2.sh

### 2025-01-13 experiments/chpc/bhh_heuristic_pool.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+
+#PBS -N bhh_hp
+#PBS -q serial
+#PBS -P CSCI0886
+#PBS -l select=1:ncpus=24:mem=120gb:ngpus=0
+#PBS -l walltime=48:00:00
+#PBS -o /mnt/lustre/users/aschreuder/tracking/stdin/bhh_hp.out
+#PBS -e /mnt/lustre/users/aschreuder/tracking/stderr/bhh_hp.err
+#PBS -m abe -M arneschreuder@icloud.com
+
+ulimit -s unlimited
+
+# Move to the directory of interest
+cd /mnt/lustre/users/aschreuder/masters.ai/
+
+# Can activate your python environment here
+module purge
+module load chpc/python/3.7.0
+
+# Run your script
+source .venv/bin/activate
+bash experiments/scripts/bhh_heuristic_pool.sh

### 2025-01-13 experiments/chpc/bhh_normalise.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+
+#PBS -N bhh_nm
+#PBS -q serial
+#PBS -P CSCI0886
+#PBS -l select=1:ncpus=24:mem=120gb:ngpus=0
+#PBS -l walltime=48:00:00
+#PBS -o /mnt/lustre/users/aschreuder/tracking/stdin/bhh_nm.out
+#PBS -e /mnt/lustre/users/aschreuder/tracking/stderr/bhh_nm.err
+#PBS -m abe -M arneschreuder@icloud.com
+
+ulimit -s unlimited
+
+# Move to the directory of interest
+cd /mnt/lustre/users/aschreuder/masters.ai/
+
+# Can activate your python environment here
+module purge
+module load chpc/python/3.7.0
+
+# Run your script
+source .venv/bin/activate
+bash experiments/scripts/bhh_normalise.sh

### 2025-01-13 experiments/chpc/bhh_population7.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+
+#PBS -N bhh_ps7
+#PBS -q serial
+#PBS -P CSCI0886
+#PBS -l select=1:ncpus=24:mem=120gb:ngpus=0
+#PBS -l walltime=48:00:00
+#PBS -o /mnt/lustre/users/aschreuder/tracking/stdin/bhh_ps.out
+#PBS -e /mnt/lustre/users/aschreuder/tracking/stderr/bhh_ps.err
+#PBS -m abe -M arneschreuder@icloud.com
+
+ulimit -s unlimited
+
+# Move to the directory of interest
+cd /mnt/lustre/users/aschreuder/masters.ai/
+
+# Can activate your python environment here
+module purge
+module load chpc/python/3.7.0
+
+# Run your script
+source .venv/bin/activate
+bash experiments/scripts/bhh_population7.sh

### 2025-01-13 experiments/chpc/bhh_reanalysis.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+
+#PBS -N bhh_ra
+#PBS -q serial
+#PBS -P CSCI0886
+#PBS -l select=1:ncpus=24:mem=120gb:ngpus=0
+#PBS -l walltime=48:00:00
+#PBS -o /mnt/lustre/users/aschreuder/tracking/stdin/bhh_ra.out
+#PBS -e /mnt/lustre/users/aschreuder/tracking/stderr/bhh_ra.err
+#PBS -m abe -M arneschreuder@icloud.com
+
+ulimit -s unlimited
+
+# Move to the directory of interest
+cd /mnt/lustre/users/aschreuder/masters.ai/
+
+# Can activate your python environment here
+module purge
+module load chpc/python/3.7.0
+
+# Run your script
+source .venv/bin/activate
+bash experiments/scripts/bhh_reanalysis.sh

### 2025-01-13 experiments/chpc/bhh_reanalysis2.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+
+#PBS -N bhh_ra2
+#PBS -q serial
+#PBS -P CSCI0886
+#PBS -l select=1:ncpus=24:mem=120gb:ngpus=0
+#PBS -l walltime=48:00:00
+#PBS -o /mnt/lustre/users/aschreuder/tracking/stdin/bhh_ra.out
+#PBS -e /mnt/lustre/users/aschreuder/tracking/stderr/bhh_ra.err
+#PBS -m abe -M arneschreuder@icloud.com
+
+ulimit -s unlimited
+
+# Move to the directory of interest
+cd /mnt/lustre/users/aschreuder/masters.ai/
+
+# Can activate your python environment here
+module purge
+module load chpc/python/3.7.0
+
+# Run your script
+source .venv/bin/activate
+bash experiments/scripts/bhh_reanalysis2.sh

### 2025-01-13 experiments/chpc/bhh_replay.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+
+#PBS -N bhh_rp
+#PBS -q bigmem
+#PBS -P CSCI0886
+#PBS -l select=1:ncpus=56:mem=256gb:ngpus=0
+#PBS -l walltime=48:00:00
+#PBS -o /mnt/lustre/users/aschreuder/tracking/stdin/bhh_rp.out
+#PBS -e /mnt/lustre/users/aschreuder/tracking/stderr/bhh_rp.err
+#PBS -m abe -M arneschreuder@icloud.com
+
+ulimit -s unlimited
+
+# Move to the directory of interest
+cd /mnt/lustre/users/aschreuder/masters.ai/
+
+# Can activate your python environment here
+module purge
+module load chpc/python/3.7.0
+
+# Run your script
+source .venv/bin/activate
+bash experiments/scripts/bhh_replay.sh

### 2025-01-13 experiments/generators/bhh_burn_in.sh

@@ -1,0 +1,24 @@
+# BHH Variant: Burn In
+# This runs the BHH with variant burn_in
+
+#!/usr/bin/env bash
+
+# set -ex
+
+echo "export TF_CPP_MIN_LOG_LEVEL=3"
+echo "export CUDA_VISIBLE_DEVICES=''"
+echo "export LOG_LEVEL=0"
+
+RUNS=30
+
+declare -a DATASETS=("iris" "abalone" "housing" "forest_fires" "fish_toxicity" "student_performance" "car" "parkinsons" "wine_quality" "mushroom" "air_quality" "adult" "bike" "bank" "diabetic")
+declare -a BURN_INS=(5 10 15 20) # Default is 0
+
+for DATASET in ${DATASETS[@]}; do
+	for BURN_IN in ${BURN_INS[@]}; do
+		for ((RUN = 1; RUN <= RUNS; RUN++)); do
+			echo "python bhh.py --dataset=$DATASET --seed=$RUN --heuristic-pool=all --population-size=5 --burn_in=${BURN_IN} --replay=10 --reselection=10 --reanalysis=10 --credit=ibest"
+			echo "echo 'bhh_burn_in,${DATASET},${BURN_IN},${RUN}' >> tracking/progress/bhh_burn_in.txt"
+		done
+	done
+done

### 2025-01-13 experiments/generators/bhh_credit.sh

@@ -1,0 +1,24 @@
+# BHH Variant: Credit
+# This runs the BHH with variant credit
+
+#!/usr/bin/env bash
+
+# set -ex
+
+echo "export TF_CPP_MIN_LOG_LEVEL=3"
+echo "export CUDA_VISIBLE_DEVICES=''"
+echo "export LOG_LEVEL=0"
+
+RUNS=30
+
+declare -a DATASETS=("iris" "abalone" "housing" "forest_fires" "fish_toxicity" "student_performance" "car" "parkinsons" "wine_quality" "mushroom" "air_quality" "adult" "bike" "bank" "diabetic")
+declare -a CREDITS=("pbest" "rbest" "gbest" "symmetric") # Default is ibest
+
+for DATASET in ${DATASETS[@]}; do
+	for CREDIT in ${CREDITS[@]}; do
+		for ((RUN = 1; RUN <= RUNS; RUN++)); do
+			echo "python bhh.py --dataset=$DATASET --seed=$RUN --heuristic-pool=all --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=${CREDIT}"
+			echo "echo 'bhh_credit,${DATASET},${CREDIT},${RUN}' >> tracking/progress/bhh_credit.txt"
+		done
+	done
+done

### 2025-01-13 experiments/generators/bhh_heuristic_pool.sh

@@ -1,0 +1,24 @@
+# BHH Variant: Heuristic Pool
+# This runs the baseline BHH variants with varying
+
+#!/usr/bin/env bash
+
+# set -ex
+
+echo "export TF_CPP_MIN_LOG_LEVEL=3"
+echo "export CUDA_VISIBLE_DEVICES=''"
+echo "export LOG_LEVEL=0"
+
+RUNS=30
+
+declare -a DATASETS=("iris" "abalone" "housing" "forest_fires" "fish_toxicity" "student_performance" "car" "parkinsons" "wine_quality" "mushroom" "air_quality" "adult" "bike" "bank" "diabetic")
+declare -a HEURISTIC_POOLS=("all" "gd" "mh") # Default is "all", but we run it here
+
+for DATASET in ${DATASETS[@]}; do
+	for HEURISTIC_POOL in ${HEURISTIC_POOLS[@]}; do
+		for ((RUN = 1; RUN <= RUNS; RUN++)); do
+			echo "python bhh.py --dataset=$DATASET --seed=$RUN --heuristic-pool=${HEURISTIC_POOL} --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest"
+			echo "echo 'bhh_heuristic_pool,${DATASET},${HEURISTIC_POOL},${RUN}' >> tracking/progress/bhh_heuristic_pool.txt"
+		done
+	done
+done

### 2025-01-13 experiments/generators/bhh_normalise.sh

@@ -1,0 +1,22 @@
+# BHH Variant: Normalise
+# This runs the BHH with variant discounted rewards
+
+#!/usr/bin/env bash
+
+# set -ex
+
+echo "export TF_CPP_MIN_LOG_LEVEL=3"
+echo "export CUDA_VISIBLE_DEVICES=''"
+echo "export LOG_LEVEL=0"
+
+RUNS=30
+
+declare -a DATASETS=("iris" "abalone" "housing" "forest_fires" "fish_toxicity" "student_performance" "car" "parkinsons" "wine_quality" "mushroom" "air_quality" "adult" "bike" "bank" "diabetic")
+# Default is false
+
+for DATASET in ${DATASETS[@]}; do
+	for ((RUN = 1; RUN <= RUNS; RUN++)); do
+		echo "python bhh.py --dataset=$DATASET --seed=$RUN --heuristic-pool=all --population-size=5 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest --normalise=true"
+		echo "echo 'bhh_normalise,${DATASET},true,${RUN}' >> tracking/progress/bhh_normalise.txt"
+	done
+done

### 2025-01-13 experiments/generators/bhh_reselection.sh

@@ -1,0 +1,24 @@
+# BHH Variant: Reselection
+# This runs the BHH with variant reselection
+
+#!/usr/bin/env bash
+
+# set -ex
+
+echo "export TF_CPP_MIN_LOG_LEVEL=3"
+echo "export CUDA_VISIBLE_DEVICES=''"
+echo "export LOG_LEVEL=0"
+
+RUNS=30
+
+declare -a DATASETS=("iris" "abalone" "housing" "forest_fires" "fish_toxicity" "student_performance" "car" "parkinsons" "wine_quality" "mushroom" "air_quality" "adult" "bike" "bank" "diabetic")
+declare -a RESELECTIONS=(1 5 15 20) # Default is 10
+
+for DATASET in ${DATASETS[@]}; do
+	for RESELECTION in ${RESELECTIONS[@]}; do
+		for ((RUN = 1; RUN <= RUNS; RUN++)); do
+			echo "python bhh.py --dataset=$DATASET --seed=$RUN --heuristic-pool=all --population-size=5 --burn_in=0 --replay=10 --reselection=${RESELECTION} --reanalysis=10 --credit=ibest"
+			echo "echo 'bhh_reselection,${DATASET},${RESELECTION},${RUN}' >> tracking/progress/bhh_reselection.txt"
+		done
+	done
+done

### 2025-01-13 experiments/generators/standalone.sh

@@ -1,0 +1,24 @@
+# Standalone Optimisers
+# This experiment runs all lower level heuristics with default configuration on all datasets.
+
+#!/usr/bin/env bash
+
+# set -ex
+
+echo "export TF_CPP_MIN_LOG_LEVEL=3"
+echo "export CUDA_VISIBLE_DEVICES=''"
+echo "export LOG_LEVEL=0"
+
+RUNS=30
+
+declare -a DATASETS=("iris" "abalone" "housing" "forest_fires" "fish_toxicity" "student_performance" "car" "parkinsons" "wine_quality" "mushroom" "air_quality" "adult" "bike" "bank" "diabetic")
+declare -a OPTIMISERS=("sgd" "momentum" "nag" "adagrad" "rmsprop" "adadelta" "adam" "pso" "de" "ga")
+
+for DATASET in ${DATASETS[@]}; do
+	for OPTIMISER in ${OPTIMISERS[@]}; do
+		for ((RUN = 1; RUN <= RUNS; RUN++)); do
+			echo "python heuristic.py --dataset=$DATASET --optimiser=$OPTIMISER --seed=$RUN"
+			echo "echo 'standalone,${DATASET},${OPTIMISER},${RUN}' >> tracking/progress/standalone.txt"
+		done
+	done
+done

### 2025-01-13 experiments/scripts/again5.sh

@@ -1,0 +1,6 @@
+export TF_CPP_MIN_LOG_LEVEL=3
+export CUDA_VISIBLE_DEVICES=''
+export LOG_LEVEL=0
+
+python bhh.py --dataset=adult --seed=5 --heuristic-pool=all --population-size=20 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
+echo "python bhh.py --dataset=adult --seed=5 --heuristic-pool=all --population-size=20 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest" >>tracking/progress/again.txt

### 2025-01-13 experiments/scripts/again8.sh

@@ -1,0 +1,6 @@
+export TF_CPP_MIN_LOG_LEVEL=3
+export CUDA_VISIBLE_DEVICES=''
+export LOG_LEVEL=0
+
+python bhh.py --dataset=adult --seed=8 --heuristic-pool=all --population-size=20 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest
+echo "python bhh.py --dataset=adult --seed=8 --heuristic-pool=all --population-size=20 --burn_in=0 --replay=10 --reselection=10 --reanalysis=10 --credit=ibest" >>tracking/progress/again.txt

### 2025-01-13 framework/activations/__init__.py

@@ -1,0 +1,3 @@
+from .activation import Activation
+from .leaky_relu import LeakyReLU
+from .sigmoid import Sigmoid

### 2025-01-13 framework/activations/activation.py

@@ -1,0 +1,34 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+
+
+class Activation:
+    """
+    A class used to model phase shift or neural network activations.
+    """
+    pass

### 2025-01-13 framework/credits/__init__.py

@@ -1,0 +1,6 @@
+from .credit import Credit
+from .gbest import GBest
+from .ibest import IBest
+from .pbest import PBest
+from .rbest import RBest
+from .symmetric import Symmetric

### 2025-01-13 framework/credits/credit.py

@@ -1,0 +1,97 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from typing import List
+
+import numpy as np
+
+
+class Credit:
+    """
+    Abstract class for credit assingment strategies
+
+    Attributes
+    -----------
+    discounted_rewards = None
+        Flag to enable discounted/diminishing rewards. Default = None
+    columns: List[str] = None
+        List of columns to consider for credit. Default = None
+    dtypes: List[np.dtype] = None
+        The data type for each colun. Default = none
+    """
+    discounted_rewards = None
+    columns: List[str] = None
+    dtypes: List[np.dtype] = None
+
+    def __init__(self, discounted_rewards: bool = True):
+        """
+        Parameters
+        ----------
+        discounted_rewards: boolean
+            Flag to enable discounted/diminishing rewards. Default = True
+        """
+        self.discounted_rewards = discounted_rewards
+        self.columns = [
+            "step",
+            "entity",
+            "heuristic",
+            "credit"
+        ]
+        self.dtypes = {
+            "step": int,
+            "entity": int,
[…]

### 2025-01-13 framework/credits/ibest.py

@@ -1,0 +1,79 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import pandas as pd
+from framework.credits.credit import Credit
+from framework.performance_log.performance_log import PerformanceLog
+
+
+class IBest(Credit):
+    """
+    Concrete class for IBest (Iteration Best) credit assingment strategy
+    """
+
+    def __init__(self, discounted_rewards=True):
+        """
+        Parameters
+        ----------
+        discounted_rewards: boolean
+            Flag to enable discounted/diminishing rewards. Default = True
+        """
+        super(IBest, self).__init__(discounted_rewards=discounted_rewards)
+
+    def __call__(self, log: PerformanceLog):
+        """
+        Parameters
+        ----------
+        log: PerformanceLog
+            The performance log that stores the performance of the hh population.
+        """
+        credit = pd.DataFrame(columns=self.columns)
+        credit = credit.astype(self.dtypes)
+        max_step = log.log["step"].max()
+
+        for _, row in log.log.iterrows():
+            step = row["step"]
+            entity = row["entity"]
[…]

### 2025-01-13 framework/datasets/__init__.py

@@ -1,0 +1,15 @@
+from .abalone import Abalone
+from .air_quality import AirQuality
+from .bank import Bank
+from .bike import Bike
+from .car import Car
+from .dataset import Dataset
+from .diabetic import Diabetic
+from .fish_toxicity import FishToxicity
+from .forest_fires import ForestFires
+from .housing import Housing
+from .iris import Iris
+from .mushroom import Mushroom
+from .parkinsons import Parkinsons
+from .student_performance import StudentPerformance
+from .wine_quality import WineQuality

### 2025-01-13 framework/datasets/bank/bank.py

@@ -1,0 +1,156 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import os
+import random
+
+import pandas as pd
+import tensorflow as tf
+import tensorflow_datasets as tfds
+from framework.datasets.dataset import Dataset
+from sklearn import preprocessing
+from sklearn.model_selection import train_test_split
+
+
+class Bank(Dataset):
+    """
+    The implementation of the Bank dataset
+    """
+
+    def __init__(self, batch_size: int = 30, seed: int = None):
+        """
+        Params
+        ------
+        batch_size: int
+            Batch size. Default = 30
+        seed: int
+            Random seed value. Default = None
+        """
+        super(Bank, self).__init__(seed=seed)
+        # Set attribute values
+        self.train_url = 'framework/datasets/bank/bank.csv'
+        self.test_url = None
+        self.features = [
+            "age",
+            "job",
+            "marital",
+            "education",
+            "default",
+            "balance",
+            "housing",
+            "loan",
+            "contact",
+            "day",
+            "month",
+            "duration",
+            "campaign",
+            "pdays",
[…]

### 2025-01-13 framework/datasets/car/car.py

@@ -1,0 +1,137 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import os
+import random
+
+import pandas as pd
+import tensorflow as tf
+import tensorflow_datasets as tfds
+from framework.datasets.dataset import Dataset
+from sklearn import preprocessing
+from sklearn.model_selection import train_test_split
+
+
+class Car(Dataset):
+    """
+    The implementation of the Car dataset
+    """
+
+    def __init__(self, batch_size: int = 30, seed: int = None):
+        """
+        Params
+        ------
+        batch_size: int
+            Batch size. Default = 30
+        seed: int
+            Random seed value. Default = None
+        """
+        super(Car, self).__init__(seed=seed)
+        # Set attribute values
+        self.train_url = 'framework/datasets/car/car.data'
+        self.test_url = None
+        self.features = [
+            "buying",
+            "maint",
+            "doors",
+            "persons",
+            "lug_boot",
+            "safety"
+        ]
+        self.label = "evaluation"
+        self.columns = self.features + [self.label]
+        self.dtype = {
+            "buying": "category",
[…]

### 2025-01-13 framework/datasets/dataset.py

@@ -1,0 +1,92 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from typing import Dict, List
+
+import tensorflow as tf
+
+
+class Dataset:
+    """
+    The base class used for datasets
+
+    Attributes
+    -----------
+    batch_size: int
+        Specifies the mini-batch size. Default = None
+    columns: List[str]
+        A list of strings that contain the different column headings. Default = None
+    dtype: Dict
+        The dtypes for each column. Default = None.
+    features: List[str]
+        A list of strings that contain the different features' headings. Default = None
+    label: str
+        The column heading of the label column. Default = None
+    seed: int
+        Random seed value. Default = None
+    shuffle_size: int
+        Specifies the number of items to include in shuffle process. Default = None
+    train_url: str
+        The URL to the training set data. Default = None
+    train: tf.data.Dataset
+        Contains the training dataset. Default = None
+    test_url: str
+        The URL to the testing set data. Default = None
+    test: tf.data.Dataset
+        Contains the test dataset. Default = None
+    """
+    batch_size: int = None
[…]

### 2025-01-13 framework/datasets/diabetic/diabetic.py

@@ -1,0 +1,233 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import os
+import random
+
+import pandas as pd
+import tensorflow as tf
+import tensorflow_datasets as tfds
+from framework.datasets.dataset import Dataset
+from sklearn import preprocessing
+from sklearn.model_selection import train_test_split
+
+
+class Diabetic(Dataset):
+    """
+    The implementation of the Diabetic dataset
+    """
+
+    def __init__(self, batch_size: int = 30, seed: int = None):
+        """
+        Params
+        ------
+        batch_size: int
+            Batch size. Default = 30
+        seed: int
+            Random seed value. Default = None
+        """
+        super(Diabetic, self).__init__(seed=seed)
+        # Set attribute values
+        self.train_url = 'framework/datasets/diabetic/diabetic.csv'
+        self.test_url = None
+        self.features = [
+            "encounter_id",
+            "patient_nbr",
+            "race",
+            "gender",
+            "age",
+            "weight",
+            "admission_type_id",
+            "discharge_disposition_id",
+            "admission_source_id",
+            "time_in_hospital",
[…]

### 2025-01-13 framework/datasets/forest_fires/forest_fires.py

@@ -1,0 +1,155 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import os
+import random
+
+import pandas as pd
+import tensorflow as tf
+import tensorflow_datasets as tfds
+from framework.datasets.dataset import Dataset
+from sklearn import preprocessing
+from sklearn.model_selection import train_test_split
+
+
+class ForestFires(Dataset):
+    """
+    The implementation of the ForestFires dataset
+    """
+
+    def __init__(self, batch_size: int = 30, seed: int = None):
+        """
+        Params
+        ------
+        batch_size: int
+            Batch size. Default = 30
+        seed: int
+            Random seed value. Default = None
+        """
+        super(ForestFires, self).__init__(seed=seed)
+        # Set attribute values
+        self.train_url = 'framework/datasets/forest_fires/forest_fires.csv'
+        self.test_url = None
+        self.features = [
+            "x",
+            "y",
+            "month",
+            "day",
+            "ffmc",
+            "dmc",
+            "dc",
+            "isi",
+            "temp",
+            "rh",
+            "wind",
+            "rain"
+        ]
[…]

### 2025-01-13 framework/datasets/housing/housing.py

@@ -1,0 +1,157 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import os
+import random
+
+import pandas as pd
+import tensorflow as tf
+import tensorflow_datasets as tfds
+from framework.datasets.dataset import Dataset
+from sklearn import preprocessing
+from sklearn.model_selection import train_test_split
+
+
+class Housing(Dataset):
+    """
+    The implementation of the Housing dataset
+    """
+
+    def __init__(self, batch_size: int = 30, seed: int = None):
+        """
+        Params
+        ------
+        batch_size: int
+            Batch size. Default = 30
+        seed: int
+            Random seed value. Default = None
+        """
+        super(Housing, self).__init__(seed=seed)
+        # Set attribute values
+        self.train_url = 'framework/datasets/housing/housing.data'
+        self.test_url = None
+        self.features = [
+            "crim",
+            "zn",
+            "indus",
+            "chas",
+            "nox",
+            "rm",
+            "age",
+            "dis",
+            "rad",
+            "tax",
+            "ptratio",
+            "b",
+            "lstat"
+        ]
[…]

### 2025-01-13 framework/datasets/iris/iris.py

@@ -1,0 +1,133 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import os
+import random
+
+import pandas as pd
+import tensorflow as tf
+import tensorflow_datasets as tfds
+from framework.datasets.dataset import Dataset
+from sklearn import preprocessing
+from sklearn.model_selection import train_test_split
+
+
+class Iris(Dataset):
+    """
+    The implementation of the Iris dataset
+    """
+
+    def __init__(self, batch_size: int = 30, seed: int = None):
+        """
+        Params
+        ------
+        batch_size: int
+            Batch size. Default = 30
+        seed: int
+            Random seed value. Default = None
+        """
+        super(Iris, self).__init__(seed=seed)
+        # Set attribute values
+        self.train_url = 'framework/datasets/iris/iris.data'
+        self.test_url = None
+        self.features = [
+            "sepal_length",
+            "sepal_width",
+            "petal_length",
+            "petal_width"
+        ]
+        self.label = "species"
+        self.columns = self.features + [self.label]
+        self.dtype = {
+            "sepal_length": "float32",
[…]

### 2025-01-13 framework/datasets/student_performance/__init__.py

@@ -1,0 +1,1 @@
+from .student_performance import StudentPerformance

### 2025-01-13 framework/distributions/__init__.py

@@ -1,0 +1,6 @@
+from .bernoulli import Bernoulli
+from .beta import Beta
+from .binomial import Binomial
+from .categorical import Categorical
+from .dirichlet import Dirichlet
+from .distribution import Distribution

### 2025-01-13 framework/distributions/dirichlet.py

@@ -1,0 +1,50 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+import tensorflow_probability as tfp
+from framework.distributions.distribution import Distribution
+
+
+class Dirichlet(Distribution):
+    """
+    The Dirichlet probability distribution.
+    """
+
+    def __init__(self, concentration: tf.Tensor):
+        """
+        Parameters
+        ----------
+        concentration: tf.Tensor
+            The concentration/bias/pseudo count for each category
+            represented by the Dirichlet probability distribution.
+        """
+
+        super(Dirichlet, self).__init__(
+            instance=tfp.distributions.Dirichlet(
+                concentration=concentration
+            )
+        )

### 2025-01-13 framework/entities/entity.py

@@ -1,0 +1,275 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import os
+
+import tensorflow as tf
+from framework.initialisers.glorot_uniform import GlorotUniform
+from framework.initialisers.initialiser import Initialiser
+from framework.initialisers.zeros import Zeros
+from framework.logger.logger import Logger
+from framework.neural_networks.neural_network import NeuralNetwork
+
+
+class Entity:
+    """
+    A class that represents the physical properties of a candidate solution.
+    This class is often used in swarm-based optimisation techniques, but
+    is a useful general container of properties related to physics-based movements.
+
+    Attributes
+    ----------
+    model: NeuralNetwork
+        The model. Default = None
+    shape: tf.TensorShape
+        The shape of canidate solution. Default = None
+    position: tf.Variable
+        The container for the candidate solution. Default = None
+    velocity: tf.Variable
+        The entity's velocity. Default = None
+    gradient: tf.Variable
+        The entity's last gradient. Default = None
+    position_delta: tf.Variable
+        The entity's position delta. Default = None
[…]

### 2025-01-13 framework/experiments/diabetic.py

@@ -1,0 +1,74 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from framework.datasets.diabetic import Diabetic as DiabeticDataset
+from framework.experiments.experiment import Experiment
+from framework.losses.sparse_categorical_crossentropy import \
+    SparseCategoricalCrossentropy
+from framework.metrics.sparse_categorical_accuracy import \
+    SparseCategoricalAccuracy as SparseCategoricalAccuracyMetric
+from framework.metrics.sparse_categorical_crossentropy import \
+    SparseCategoricalCrossentropy as SparseCategoricalCrossentropyMetric
+from framework.models.diabetic import Diabetic as DiabeticModel
+from framework.optimisers.optimiser import Optimiser
+
+
+class Diabetic(Experiment):
+    def __init__(self,
+                 optimiser: Optimiser,
+                 log_dir: str,
+                 seed: int = None):
+        """
+        Parameters
+        ----------
+        optimiser: Optimiser
+            The optimiser to use
+        epochs: int
+            The number of epochs to train. Default = None
+        batch_size: int
+            The batch_size. Default = None
+        log_dir: str
[…]

### 2025-01-13 framework/experiments/forest_fires.py

@@ -1,0 +1,64 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from framework.datasets.forest_fires import ForestFires as ForestFiresDataset
+from framework.experiments.experiment import Experiment
+from framework.losses.rmse import RMSE
+from framework.metrics.rmse import RMSE as RMSEMetric
+from framework.models.forest_fires import ForestFires as ForestFiresModel
+from framework.optimisers.optimiser import Optimiser
+
+
+class ForestFires(Experiment):
+    def __init__(self,
+                 optimiser: Optimiser,
+                 log_dir: str,
+                 seed: int = None):
+        """
+        Parameters
+        ----------
+        optimiser: Optimiser
+            The optimiser to use
+        log_dir: str
+            The log output directory. Default = None
+        seed: int
+            Random seed. Default = None
+        """
+        super(ForestFires, self).__init__(
+            dataset=ForestFiresDataset(seed=seed, batch_size=32),
+            model=ForestFiresModel(),
+            loss_fn=RMSE(),
+            optimiser=optimiser,
+            train_metrics=[
[…]

### 2025-01-13 framework/experiments/housing.py

@@ -1,0 +1,64 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from framework.datasets.housing import Housing as HousingDataset
+from framework.experiments.experiment import Experiment
+from framework.losses.rmse import RMSE
+from framework.metrics.rmse import RMSE as RMSEMetric
+from framework.models.housing import Housing as HousingModel
+from framework.optimisers.optimiser import Optimiser
+
+
+class Housing(Experiment):
+    def __init__(self,
+                 optimiser: Optimiser,
+                 log_dir: str,
+                 seed: int = None):
+        """
+        Parameters
+        ----------
+        optimiser: Optimiser
+            The optimiser to use
+        log_dir: str
+            The log output directory. Default = None
+        seed: int
+            Random seed. Default = None
+        """
+        super(Housing, self).__init__(
+            dataset=HousingDataset(seed=seed, batch_size=32),
+            model=HousingModel(),
+            loss_fn=RMSE(),
+            optimiser=optimiser,
+            train_metrics=[
+                RMSEMetric(name="train_loss")
+            ],
[…]

### 2025-01-13 framework/experiments/wine_quality.py

@@ -1,0 +1,74 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from framework.datasets.wine_quality import WineQuality as WineQualityDataset
+from framework.experiments.experiment import Experiment
+from framework.losses.sparse_categorical_crossentropy import \
+    SparseCategoricalCrossentropy
+from framework.metrics.sparse_categorical_accuracy import \
+    SparseCategoricalAccuracy as SparseCategoricalAccuracyMetric
+from framework.metrics.sparse_categorical_crossentropy import \
+    SparseCategoricalCrossentropy as SparseCategoricalCrossentropyMetric
+from framework.models.wine_quality import WineQuality as WineQualityModel
+from framework.optimisers.optimiser import Optimiser
+
+
+class WineQuality(Experiment):
+    def __init__(self,
+                 optimiser: Optimiser,
+                 log_dir: str,
+                 seed: int = None):
+        """
+        Parameters
+        ----------
+        optimiser: Optimiser
+            The optimiser to use
+        epochs: int
+            The number of epochs to train. Default = None
+        batch_size: int
+            The batch_size. Default = None
+        log_dir: str
[…]

### 2025-01-13 framework/heuristics/__init__.py

@@ -1,0 +1,12 @@
+from .adadelta import Adadelta
+from .adagrad import Adagrad
+from .adam import Adam
+from .bhh import BHH
+from .de import DE
+from .ga import GA
+from .heuristic import Heuristic
+from .momentum import Momentum
+from .nag import NAG
+from .pso import PSO
+from .rmsprop import RMSProp
+from .sgd import SGD

### 2025-01-13 framework/heuristics/adadelta.py

@@ -1,0 +1,222 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+
+import tensorflow as tf
+from framework.entities.entity import Entity
+from framework.heuristics.heuristic import Heuristic
+from framework.hyper_parameters.adadelta import Adadelta as AdadeltaParameters
+
+
+class Adadelta(Heuristic):
+    """
+    The Adaptive Gradients (Delta) concrete heuristic.
+    Adadelta is a varient of Adade where the decay of the learning rate is 
+    controlled by only the last few gradients and not the entire gradient history.
+    over time.
+
+    See: https://github.com/tensorflow/tensorflow/blob/master/tensorflow/python/training/adadelta.py
+
+    References:
+    ADADELTA - An Adaptive Learning Rate Method:
+      [Zeiler, 2012](http://arxiv.org/abs/1212.5701)
+      ([pdf](http://arxiv.org/pdf/1212.5701v1.pdf))
+
+    Attributes
+    ----------
+    params: AdadeltaParameters
+        Hyper Parameters. Default = None
+    """
+    params: AdadeltaParameters = None
+
+    def __init__(self,
[…]

### 2025-01-13 framework/heuristics/nag.py

@@ -1,0 +1,178 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+
+from framework.entities.entity import Entity
+from framework.heuristics.heuristic import Heuristic
+from framework.hyper_parameters.nag import NAG as NAGParameters
+
+
+class NAG(Heuristic):
+    """
+    The Nesterov Adaptive Gradients concrete heuristic.
+
+    Attributes
+    ----------
+    params: NAGParameters
+        Hyper Parameters. Default = None
+    """
+    params: NAGParameters = None
+
+    def __init__(self,
+                 params: NAGParameters = NAGParameters()):
+        """
+        Parameters
+        ----------
+        params: NAGParameters
+            Hyper parameters. Default = NAGParameters()
+        """
+        super(NAG, self).__init__()
+        self.params = params
+
+    @staticmethod
+    def get_learning_rate(params: NAGParameters, step: int) -> float:
+        """
+        Gets the learning rate.
+
+        Parameters
+        ----------
+        params: NAGParameters
+            Hyper parameters.
+        step: int
+            The step number.
+
+        Returns
+        -------
[…]

### 2025-01-13 framework/heuristics/pso.py

@@ -1,0 +1,237 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+from framework.entities import Entity
+from framework.heuristics.heuristic import Heuristic
+from framework.hyper_parameters.pso import PSO as PSOParameters
+from framework.population import Population
+
+
+class PSO(Heuristic):
+    """
+    The Particle Swarm Optimiser concrete heuristic.
+
+    Attributes
+    ----------
+    params: PSOParameters
+        Hyper Parameters. Default = None
+    """
+    params: PSOParameters = None
+
+    def __init__(self, params: PSOParameters = PSOParameters()):
+        """
+        Parameters
+        ----------
+        params: PSOParameters
+            Hyper parameters. Default = PSOParameters()
+        """
+        super(PSO, self).__init__()
+        self.params = params
+
+    @staticmethod
+    def get_learning_rate(params: PSOParameters, step: int) -> float:
+        """
+        Gets the learning rate.
+
+        Parameters
+        ----------
+        params: PSOParameters
+            Hyper parameters.
+        step: int
+            The step number.
+
+        Returns
[…]

### 2025-01-13 framework/hyper_parameters/adadelta.py

@@ -1,0 +1,65 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from framework.hyper_parameters.parameters import Parameters
+from framework.schedules.schedule import Schedule
+
+
+class Adadelta(Parameters):
+    """
+    Hyper Parameters for Adadelta
+
+    Attributes
+    ----------
+    learning_rate: float or Schedule
+        The step size. Default = None
+    rho: float
+        Decay rate. Default = None
+    epsilon: float
+        Small error value. Default = None
+    """
+    learning_rate: float or Schedule = None
+    rho: float = None
+    epsilon: float = None
+
+    def __init__(self,
+                 learning_rate: float or Schedule = 1.0,
+                 rho: float = 0.95,
+                 epsilon: float = 1e-7):
+        """
+        Parameters
+        ----------
+        learning_rate: float
+            The step size. Default = 1.0
+        rho: float
+            Decay rate. Default = 0.95
+        epsilon: float
+            Small error value. Default = 1e-7
+        """
+        super(Adadelta, self).__init__()
[…]

### 2025-01-13 framework/hyper_parameters/adam.py

@@ -1,0 +1,76 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+
+from framework.hyper_parameters.parameters import Parameters
+from framework.schedules.schedule import Schedule
+
+
+class Adam(Parameters):
+    """
+    Hyper Parameters for Adam
+
+    Attributes
+    ----------
+    learning_rate: float or Schedule
+        The step size. Default = None
+    beta1: float
+        Decay rate for the first moment. Default = None
+    beta2: float
+        Decay rate for the second moment. Default = None
+    epsilon: float
+        Small error value. Default = None
+    """
+
+    learning_rate: float or Schedule = None
+    beta1: float = None
+    beta2: float = None
+    epsilon: float = None
+
+    def __init__(
+        self,
+        learning_rate: float or Schedule = 0.001,
+        beta1: float = 0.9,
+        beta2: float = 0.999,
+        epsilon: float = 1e-7,
+    ):
+        """
+        Parameters
+        ----------
+        learning_rate: float
+            The step size. Default = 0.001
+        beta1: float
+            Decay rate for the first moment. Default = 0.9
[…]

### 2025-01-13 framework/hyper_parameters/bhh.py

@@ -1,0 +1,114 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+
+from typing import Dict, List
+
+from framework.credits.credit import Credit
+from framework.credits.ibest import IBest
+from framework.heuristics.heuristic import Heuristic
+from framework.hyper_parameters.parameters import Parameters
+
+
+class BHH(Parameters):
+    """
+    Hyper Parameters for BHH
+
+    Attributes
+    ----------
+    population_size: int
+        The number of entities in the swarm/population. Default = None
+    burn_in: int
+        The burn-in window size. Default = None
+    replay: int
+        The replay window size. Default = None
+    reselection: int
+        The reselection interval. Default = None
+    reanalysis: int
+        The reanalysis interval. Default = None
+    normalise: bool
+        Flag to normalise pseudo counts. Default = None
+    credit: List[Credit]
+        The credit assignment strategy to use. Default = None
+    defaults: Dict[Parameters]
+        The default parameters for all lower level heuristics. Default = None
+    heuristics: List[Heuristic]
[…]

### 2025-01-13 framework/hyper_parameters/ga.py

@@ -1,0 +1,72 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from framework.hyper_parameters.parameters import Parameters
+from framework.schedules.schedule import Schedule
+
+
+class GA(Parameters):
+    """
+    Hyper Parameters for Genetic Algorithm
+
+    Attributes
+    ----------
+    population_size: int
+        The number of entities in the swarm. Default = None
+    selection_strategy: str
+        The selection strategy to use. Default = None
+    xo_strategy: str
+        The cross-over strategy to use. Default = None
+    mutation_rate: float or Schedule
+        The probability of a mutation in a gene. Default = None
+    """
+    population_size: int = None
+    selection_strategy: str = None
+    xo_strategy: str = None
+    mutation_rate: float or Schedule = None
+
+    def __init__(self,
+                 population_size: int = 10,
+                 selection_strategy: str = 'rand',
+                 xo_strategy: str = 'bin',
+                 mutation_rate: float = 0.1):
+        """
+        Parameters
+        ----------
+        population_size: int
+            The number of entities in the swarm. Default = 10
+        selection_strategy: str
[…]

### 2025-01-13 framework/hyper_parameters/parameters.py

@@ -1,0 +1,34 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+
+class Parameters:
+    """
+    The Parameters abstract class.
+    """
+
+    def __init__(self):
+        pass

### 2025-01-13 framework/hyper_parameters/pso.py

@@ -1,0 +1,91 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from framework.hyper_parameters.parameters import Parameters
+from framework.schedules.schedule import Schedule
+
+
+class PSO(Parameters):
+    """
+    Hyper Parameters for PSO
+
+    Attributes
+    ----------
+    population_size: int
+        The number of entities in the swarm. Default = None
+    learning_rate: float or Schedule
+        The step size. Default = None
+    inertia_weight: float
+        The inertia weight (w). Default = None
+    cognitive_control: float
+        The cognative control (c1). Default = None
+    social_control: float
+        The social control (c2). Default = None
+    velocity_clip_min: float
+        The velocity minimum bound. Default = None
+    velocity_clip_max: float
+        The velocity maximum bound. Default = None
+    """
+    population_size: int = None
+    learning_rate: float or Schedule = None
+    inertia_weight: float = None
+    cognitive_control: float = None
+    social_control: float = None
+    velocity_clip_min: float = None
+    velocity_clip_max: float = None
+
+    def __init__(self,
[…]

### 2025-01-13 framework/initialisers/initialiser.py

@@ -1,0 +1,65 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+
+
+class Initialiser:
+    """
+    The base class for tensor initialisers.
+    This class is essentially just a wrapper around
+    tf.initializers.Initialiser, but is provided to make 
+    the framework "complete"
+
+    Attributes
+    ----------
+    instance: tf.initializers.Initializer
+        The initialiser instance. Default = None
+    """
+    instance: tf.initializers.Initializer = None
+
+    def __init__(self, instance: tf.initializers.Initializer = None):
+        """
+        Parameters
+        ----------
+        instance: tf.initializers.Initializer
+            The initialiser instance. Default = None
+        """
+        self.instance = instance
+
+    def __call__(self, shape: tf.TensorShape) -> tf.Tensor:
+        """
+        Parameters
+        ----------
+        shape: tf.TensorShape
+            The dimensionality of the tensor to be initialised
+
+        Returns
+        ----------
+        tf.Tensor
+            The initialised tensor
+        """
+        return self.instance(shape)

### 2025-01-13 framework/initialisers/zeros.py

@@ -1,0 +1,39 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+from framework.initialisers.initialiser import Initialiser
+
+
+class Zeros(Initialiser):
+    """
+    The Zeros concrete initialiser.
+    """
+
+    def __init__(self) -> None:
+        super(Zeros, self).__init__(
+            instance=tf.initializers.zeros(),
+        )

### 2025-01-13 framework/layers/__init__.py

@@ -1,0 +1,2 @@
+from .dense import Dense
+from .layer import Layer

### 2025-01-13 framework/logger/logger.py

@@ -1,0 +1,100 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from datetime import datetime
+
+import tensorflow as tf
+
+
+class Logger:
+    """
+    The summary writer wrapped into a logger class.
+
+    Attributes
+    ----------
+    log_dir: str
+        The path to the log directory where output must
+        be written. Default = None
+    instance: tf.summary.SummaryWriter
+        The summary writer instance. Default = None
+    """
+    log_dir: str = None
+    instance: tf.summary.SummaryWriter = None
+
+    def __init__(self, log_dir: str):
+        """
+        Attributes
+        ----------
+        log_dir: str
+            The path to the log directory where output must
+            be written. Default = None
+        """
+        current_time = datetime.now().strftime('%Y%m%d-%H%M%S')
+        # self.log_dir = "{}/{}".format(log_dir, current_time)
+        self.log_dir = "{}".format(log_dir)
+        self.instance = tf.summary.create_file_writer(self.log_dir)
+
+    def log_scalar_results(self, name, result, step):
+        """
+        Logs scalar values.
+
+        Parameters
+        ----------
[…]

### 2025-01-13 framework/losses/rmse.py

@@ -1,0 +1,57 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+from framework.losses.loss import Loss
+
+
+class RMSE(Loss):
+    """
+    The Root Mean Squared Error concrete implementation of the loss function class.
+    """
+
+    def __init__(self):
+        super(RMSE, self).__init__(
+            instance=tf.keras.losses.MeanSquaredError()
+        )
+
+    def call(self, y_true: tf.Tensor, y_pred: tf.Tensor):
+        """
+        Calculated the RMSE.
+
+        Parameters
+        ----------
+         y_true: tf.Tensor
+            The target value. Default = None.
+         y_pred: tf.Tensor
+            The predicted value. Default = None.
+
+        Returns
+        -------
+        tf.Tensor
+            The RMSE
+        """
+        return tf.sqrt(self.instance(y_true, y_pred))

### 2025-01-13 framework/metrics/__init__.py

@@ -1,0 +1,7 @@
+from .binary_accuracy import BinaryAccuracy
+from .binary_crossentropy import BinaryCrossentropy
+from .metric import Metric
+from .mse import MSE
+from .rmse import RMSE
+from .sparse_categorical_accuracy import SparseCategoricalAccuracy
+from .sparse_categorical_crossentropy import SparseCategoricalCrossentropy

### 2025-01-13 framework/metrics/mse.py

@@ -1,0 +1,48 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+from framework.metrics.metric import Metric
+
+
+class MSE(Metric):
+    """
+    The Mean Squared Error metric.
+    """
+    name: str = None
+
+    def __init__(self, name: str):
+        """
+        Parameters
+        ----------
+        name: str
+            The metric name.
+        """
+        super(MSE, self).__init__(
+            instance=tf.keras.metrics.MeanSquaredError(),
+            name=name
+        )
+        self.name = name

### 2025-01-13 framework/metrics/sparse_categorical_accuracy.py

@@ -1,0 +1,50 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+from framework.metrics.metric import Metric
+
+
+class SparseCategoricalAccuracy(Metric):
+    """
+    The Sparse Categorical Accuracy metric.
+    Calculates the accuracy between logits and labels using 
+    a sparse representation of the labels as such: [1 3 2 1 2 1 3 2 3 3 1]
+    """
+    name: str = None
+
+    def __init__(self, name: str):
+        """
+        Parameters
+        ----------
+        name: str
+            The metric name.
+        """
+        super(SparseCategoricalAccuracy, self).__init__(
+            instance=tf.keras.metrics.SparseCategoricalAccuracy(),
+            name=name
+        )
+        self.name = name

### 2025-01-13 framework/models/abalone.py

@@ -1,0 +1,57 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+from framework.activations.leaky_relu import LeakyReLU
+from framework.activations.sigmoid import Sigmoid
+from framework.layers.dense import Dense
+from framework.neural_networks.feed_forward import Feedforward
+
+
+class Abalone(Feedforward):
+    """
+    Abalone model. 
+
+    Input Units: 10
+    Hidden Units: 36
+    Output Units: 28
+
+    Consists out of 2 layers.
+    Last layer has no activation as it is not needed during training.
+    """
+
+    def __init__(self):
+        super(Abalone, self).__init__(
+            layers=[
+                Dense(
+                    shape=[10, 36],
+                    activation=LeakyReLU(alpha=0.3)
+                ),
+                Dense(
+                    shape=[36, 28]
+                )
+            ]
+        )

### 2025-01-13 framework/models/adult.py

@@ -1,0 +1,54 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+from framework.activations.leaky_relu import LeakyReLU
+from framework.layers.dense import Dense
+from framework.neural_networks.feed_forward import Feedforward
+
+
+class Adult(Feedforward):
+    """
+    Adult model. 
+
+    Input Units: 108
+    Hidden Units: 64
+    Output Units: 1
+
+    Consists out of 2 layers.
+    Last layer has no activation as it is not needed during training.
+    """
+
+    def __init__(self):
+        super(Adult, self).__init__(
+            layers=[
+                Dense(
+                    shape=[108, 64],
+                    activation=LeakyReLU(alpha=0.3)
+                ),
+                Dense(shape=[64, 1])
+            ]
+        )

### 2025-01-13 framework/models/bike.py

@@ -1,0 +1,57 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from framework.activations.leaky_relu import LeakyReLU
+from framework.activations.sigmoid import Sigmoid
+from framework.layers.dense import Dense
+from framework.neural_networks.feed_forward import Feedforward
+
+
+class Bike(Feedforward):
+    """
+    Bike model. 
+
+    Input Units: 61
+    Hidden Units: 32
+    Output Units: 1
+
+    Consists out of 2 layers.
+    Last layer has no activation as it is not needed during training.
+    """
+
+    def __init__(self):
+        super(Bike, self).__init__(
+            layers=[
+                Dense(
+                    shape=[61, 32],
+                    activation=LeakyReLU(alpha=0.3)
+                ),
+                Dense(
+                    shape=[32, 1],
+                    activation=Sigmoid()
+                )
+            ]
+        )

### 2025-01-13 framework/models/car.py

@@ -1,0 +1,53 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from framework.activations.leaky_relu import LeakyReLU
+from framework.layers.dense import Dense
+from framework.neural_networks.feed_forward import Feedforward
+
+
+class Car(Feedforward):
+    """
+    Car model. 
+
+    Input Units: 21
+    Hidden Units: 10
+    Output Units: 4
+
+    Consists out of 2 layers.
+    Last layer has no activation as it is not needed during training.
+    """
+
+    def __init__(self):
+        super(Car, self).__init__(
+            layers=[
+                Dense(
+                    shape=[21, 10],
+                    activation=LeakyReLU(alpha=0.3)
+                ),
+                Dense(shape=[10, 4])
+            ]
+        )

### 2025-01-13 framework/models/iris.py

@@ -1,0 +1,54 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+from framework.activations.leaky_relu import LeakyReLU
+from framework.layers.dense import Dense
+from framework.neural_networks.feed_forward import Feedforward
+
+
+class Iris(Feedforward):
+    """
+    Iris model. 
+
+    Input Units: 4
+    Hidden Units: 5
+    Output Units: 3
+
+    Consists out of 2 layers.
+    Last layer has no activation as it is not needed during training.
+    """
+
+    def __init__(self):
+        super(Iris, self).__init__(
+            layers=[
+                Dense(
+                    shape=[4, 5],
+                    activation=LeakyReLU(alpha=0.3)
+                ),
+                Dense(shape=[5, 3])
+            ]
+        )

### 2025-01-13 framework/models/mushroom.py

@@ -1,0 +1,54 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+from framework.activations.leaky_relu import LeakyReLU
+from framework.layers.dense import Dense
+from framework.neural_networks.feed_forward import Feedforward
+
+
+class Mushroom(Feedforward):
+    """
+    Mushroom model. 
+
+    Input Units: 117
+    Hidden Units: 64
+    Output Units: 1
+
+    Consists out of 1 layers.
+    Last layer has no activation as it is not needed during training.
+    """
+
+    def __init__(self):
+        super(Mushroom, self).__init__(
+            layers=[
+                Dense(
+                    shape=[117, 64],
+                    activation=LeakyReLU(alpha=0.3)
+                ),
+                Dense(shape=[64, 1])
+            ]
+        )

### 2025-01-13 framework/neural_networks/feed_forward.py

@@ -1,0 +1,68 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from typing import List
+
+import tensorflow as tf
+from framework.layers.layer import Layer
+from framework.neural_networks.neural_network import NeuralNetwork
+
+
+class Feedforward(NeuralNetwork):
+    """
+    The Feedforward Neural Network concrete implementation.
+    """
+
+    def __init__(self, layers: List[Layer]):
+        """
+        Parameters
+        ----------
+        layers: List[Layer]
+            The layers to construct the Neural Network
+        """
+        super(Feedforward, self).__init__(layers=layers)
+
+    def __call__(self, features: tf.Tensor) -> tf.Tensor:
+        """
+        Invocation function. Executes the model.
+
+        Parameters
+        ----------
+        features: tf.Tensor
+            Input data.
+
+        Returns
+        ----------
+        tf.Tensor
+            Output data.  
+        """
+
+        output = features
+
+        for layer in self.layers:
+            output = layer(features=output)
+
+        return output

### 2025-01-13 framework/optimisers/bhh.py

@@ -1,0 +1,751 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import os
+from typing import List, Tuple
+
+import tensorflow as tf
+from framework.distributions.bernoulli import Bernoulli
+from framework.distributions.beta import Beta
+from framework.distributions.categorical import Categorical
+from framework.distributions.dirichlet import Dirichlet
+from framework.distributions.distribution import Distribution
+from framework.entities.entity import Entity
+from framework.heuristics.adadelta import Adadelta
+from framework.heuristics.adagrad import Adagrad
+from framework.heuristics.adam import Adam
+from framework.heuristics.bhh import BHH as BHHHeuristic
+from framework.heuristics.de import DE
+from framework.heuristics.ga import GA
+from framework.heuristics.heuristic import Heuristic
+from framework.heuristics.momentum import Momentum
+from framework.heuristics.nag import NAG
+from framework.heuristics.pso import PSO
+from framework.heuristics.rmsprop import RMSProp
+from framework.heuristics.sgd import SGD
+from framework.hyper_parameters.bhh import BHH as BHHParameters
[…]

### 2025-01-13 framework/optimisers/de.py

@@ -1,0 +1,175 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from typing import Tuple
+
+import tensorflow as tf
+from framework.entities.entity import Entity
+from framework.heuristics.de import DE as DEHeuristic
+from framework.hyper_parameters.de import DE as DEParameters
+from framework.optimisers.optimiser import Optimiser
+from framework.population import Population
+
+
+class DE(Optimiser):
+    """
+    The Differential Evolution Optimiser.
+
+    Attributes
+    ----------
+    entity: Entity
+        The entity that represents the candidate solution to the model.
+        Default = None
+    population: Population
+        The population of entities that make up the swarm. Default = None.
+    """
+    population: Population = None
+
+    def __init__(self, params: DEParameters = DEParameters()):
+        """
+        Parameters
+        ----------
+        params: DEParameters
+            The hyper parameters. Default = DEParameters()
+        """
+        super(DE, self).__init__(
+            heuristic=DEHeuristic(params=params)
+        )
+        self.population = Population(population_size=params.population_size)
+
+    def initialise(self):
+        """
+        Initialiser function.
[…]

### 2025-01-13 framework/optimisers/momentum.py

@@ -1,0 +1,146 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from typing import List, Tuple
+
+import tensorflow as tf
+from framework.entities.entity import Entity
+from framework.heuristics.momentum import Momentum as MomentumHeuristic
+from framework.hyper_parameters.momentum import Momentum as MomentumParameters
+from framework.optimisers.optimiser import Optimiser
+from framework.utilities.utilities import flatten
+
+
+class Momentum(Optimiser):
+    """
+    The Momentum Stochastic Gradient Descent concrete optimiser.
+
+    Attributes
+    ----------
+    entity: Entity
+        The entity that represents the candidate solution to the model.
+        Default = None
+
+    """
+    entity: Entity = None
+
+    def __init__(self, params: MomentumParameters = MomentumParameters()):
+        """
+        Parameters
+        ----------
+        params: MomentumParameters
+            The hyper parameters. Default = MomentumParameters()
+        """
+        super(Momentum, self).__init__(
+            heuristic=MomentumHeuristic(params=params)
+        )
+        self.entity = None
+
[…]

### 2025-01-13 framework/optimisers/pso.py

@@ -1,0 +1,172 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from typing import Tuple
+
+import tensorflow as tf
+from framework.entities.entity import Entity
+from framework.heuristics.pso import PSO as PSOHeuristic
+from framework.hyper_parameters.pso import PSO as PSOParameters
+from framework.optimisers.optimiser import Optimiser
+from framework.population import Population
+
+
+class PSO(Optimiser):
+    """
+    The Particle Swarm concrete Optimiser.
+
+    Attributes
+    ----------
+    entity: Entity
+        The entity that represents the candidate solution to the model.
+        Default = None
+    population: Population
+        The population of entities that make up the swarm. Default = None.
+    """
+    population: Population = None
+
+    def __init__(self, params: PSOParameters = PSOParameters()):
+        """
+        Parameters
+        ----------
+        params: PSOParameters
+            The hyper parameters. Default = PSOParameters()
+        """
+        super(PSO, self).__init__(
+            heuristic=PSOHeuristic(params=params)
+        )
+        self.population = Population(population_size=params.population_size)
+
+    def initialise(self):
[…]

### 2025-01-13 framework/schedules/schedule.py

@@ -1,0 +1,59 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+import tensorflow as tf
+
+
+class Schedule:
+    """
+    The abstract class for schedules.
+
+    Attributes
+    ----------
+    instance: tf.keras.optimizers.schedules.LearningRateSchedule = None
+        The scheduler instance.
+    """
+    instance: tf.keras.optimizers.schedules.LearningRateSchedule = None
+
+    def __init__(self, instance: tf.keras.optimizers.schedules.LearningRateSchedule):
+        """
+        Parameters
+        ----------
+        instance: tf.keras.optimizers.schedules.LearningRateSchedule = None
+            The scheduler instance.
+        """
+        self.instance = instance
+
+    def __call__(self, step) -> float:
+        """
+        Produces the resulting decayed/scheduled value.
+
+        Parameters
+        ----------
+        step: int   
+            The step number.
+        """
+        return self.instance(step=step)

### 2025-01-13 framework/utilities/utilities.py

@@ -1,0 +1,117 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright  Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+from typing import List
+
+import tensorflow as tf
+
+
+def flatten(x: List[List[tf.Tensor]]) -> tf.Tensor:
+    """
+    Flattens a model's x from it's layered representation
+    into a single, flat tensor.
+
+    Parameters
+    ----------
+    x: List[List[tf.Tensor]]
+        The model x to flatten
+
+
+    Returns
+    -------
+    tf.Tensor
+        The flattened x
+    """
+    # Make temporary array for x
+    x_flat = []
+
+    for p in x:
+        # Flatten weights and biases by reshaping and removing 1 dimension
+        weights = tf.reshape(p[0], [-1])
+        biases = tf.reshape(p[1], [-1])
+
+        # Join flattened weights and biases
+        temp = tf.concat([weights, biases], axis=0)
+
+        # Add flattened segment to x
+        x_flat.append(temp)
+
+    # Join all flattened segments into one tensor
[…]

### 2025-01-13 heuristic.py

@@ -1,0 +1,150 @@
+# The MIT License (MIT)
+# =====================
+
+# Copyright 2021 Arné Schreuder
+
+# Permission is hereby granted, free of charge, to any person
+# obtaining a copy of this software and associated documentation
+# files (the “Software”), to deal in the Software without
+# restriction, including without limitation the rights to use,
+# copy, modify, merge, publish, distribute, sublicense, and/or sell
+# copies of the Software, and to permit persons to whom the
+# Software is furnished to do so, subject to the following
+# conditions:
+
+# The above copyright notice and this permission notice shall be
+# included in all copies or substantial portions of the Software.
+
+# THE SOFTWARE IS PROVIDED “AS IS”, WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
+# OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
+# NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
+# HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
+# WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
+# FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+
+
+import argparse
+import os
+
+import params
+
+# Globals
+DATASET = None
+OPTIMISER = None
+SEED = None
+LOG_LEVEL = None
+PARAMS = None
+LOG = None
+
+
+def parse_basic_arguments():
+    global DATASET
+    global OPTIMISER
+    global SEED
+    global PARAMS
+    global LOG
+    global LOG_LEVEL
+
+    # Parser
+    parser = argparse.ArgumentParser(
+        description="Training Feedforward Neural Networks using Bayesian Hyper-Heuristics"
+    )
+    parser.add_argument(
+        "--dataset",
+        type=str,
+        required=True,
+        choices=[
+            "abalone",
+            "air_quality",
+            "bank",
+            "bike",
+            "car",
+            "iris",
+            "diabetic",
+            "fish_toxicity",
+            "forest_fires",
+            "housing",
+            "mushroom",
+            "parkinsons",
+            "student_performance",
+            "wine_quality",
+        ],
+        help="The dataset to use",
+    )
+    parser.add_argument(
[…]

### 2025-01-13 scripts/analyse.py

@@ -1,0 +1,383 @@
+import argparse
+import os
+
+import matplotlib.pyplot as plt
+import numpy as np
+import Orange
+import pandas as pd
+import seaborn as sns
+
+ANALYSIS = None
+ANALYSIS_PATH = None
+
+ANALYSIS_CONFIG = {
+    "bhh_burn_in": {
+        "view": "bhh_burn_in",
+        "friendly": "Burn In",
+        "column": "burn_in",
+        "param_count": 5,
+        "order": [0, 5, 10, 15, 20],
+        "fig_size_x": 12,
+        "fig_size_y": 6,
+    },
+    "bhh_credit": {
+        "view": "bhh_credit",
+        "friendly": "Credit",
+        "column": "credit",
+        "param_count": 5,
+        "order": ["ibest", "pbest", "rbest", "gbest", "symmetric"],
+        "fig_size_x": 12,
+        "fig_size_y": 6,
+    },
+    "bhh_discounted_rewards": {
+        "view": "bhh_discounted_rewards",
+        "friendly": "Discounted Rewards",
+        "column": "discounted_rewards",
+        "param_count": 2,
+        "order": [True, False],
+        "fig_size_x": 12,
+        "fig_size_y": 5,
+    },
+    "bhh_heuristic_pool": {
+        "view": "bhh_heuristic_pool",
+        "friendly": "Heuristic Pool",
+        "column": "heuristic_pool",
+        "param_count": 3,
+        "order": ["all", "gd", "mh"],
+        "fig_size_x": 12,
+        "fig_size_y": 5,
+    },
+    "bhh_normalise": {
+        "view": "bhh_normalise",
+        "friendly": "Normalisation",
+        "column": "normalisation",
+        "param_count": 2,
+        "order": [True, False],
+        "fig_size_x": 12,
+        "fig_size_y": 5,
+    },
+    "bhh_population": {
+        "view": "bhh_population",
+        "friendly": "Population",
+        "column": "population",
+        "param_count": 5,
+        "order": [5, 10, 15, 20, 25],
+        "fig_size_x": 12,
+        "fig_size_y": 6,
+    },
+    "bhh_reanalysis": {
+        "view": "bhh_reanalysis",
+        "friendly": "Reanalysis",
+        "column": "reanalysis",
+        "param_count": 5,
+        "order": [1, 5, 10, 15, 20],
+        "fig_size_x": 12,
+        "fig_size_y": 6,
+    },
[…]

### 2025-01-13 scripts/analyse_all.sh

@@ -1,0 +1,14 @@
+#!/usr/bin/env bash
+
+set -ex
+
+python scripts/analyse.py --analysis=bhh_burn_in
+python scripts/analyse.py --analysis=bhh_credit
+python scripts/analyse.py --analysis=bhh_discounted_rewards
+python scripts/analyse.py --analysis=bhh_heuristic_pool
+python scripts/analyse.py --analysis=bhh_normalise
+python scripts/analyse.py --analysis=bhh_population
+python scripts/analyse.py --analysis=bhh_reanalysis
+python scripts/analyse.py --analysis=bhh_replay
+python scripts/analyse.py --analysis=bhh_reselection
+python scripts/analyse.py --analysis=standalone

### 2025-01-13 scripts/clear_csvs_case_study.sh

@@ -1,0 +1,5 @@
+#!/usr/bin/env bash
+
+set -ex
+
+find logs -name '*.csv' -exec rm -f {} \;

### 2025-01-13 scripts/concat_csvs_case_study.sh

@@ -1,0 +1,7 @@
+#!/usr/bin/env bash
+
+set -ex
+
+rm -rf logs/master_case_study.csv
+echo "id,dataset,heuristic,heuristic_pool,population,burn_in,replay,reselection,reanalysis,normalisation,credit,discounted_rewards,run,step,wall_time,tag,value" >logs/master_case_study.csv
+find logs -name '*.csv' -not -name 'master_case_study.csv' | while read fn; do cat "$fn" >>logs/master_case_study.csv; done

### 2025-01-13 scripts/do_you_still_love_me.sh

@@ -1,0 +1,12 @@
+#!/usr/bin/env bash
+
+set -ex
+
+bash scripts/clear_csvs.sh
+bash scripts/clear_figures.sh
+# bash scripts/get_progress.sh
+python scripts/export.py --data-dir=data
+bash scripts/concat_csvs.sh
+bash scripts/upload_master_data.sh
+bash scripts/fetch_bq_all.sh
+bash scripts/analyse_all.sh

### 2025-01-13 scripts/get_tracking.sh

@@ -1,0 +1,6 @@
+#!/usr/bin/env bash
+
+set -ex
+
+mkdir -p tracking
+rsync -avz -e "ssh -o StrictHostKeyChecking=no -o UserKnownHostsFile=/dev/null" --progress aschreuder@lengau.chpc.ac.za:/mnt/lustre/users/aschreuder/masters.ai/tracking/ tracking/

### 2025-01-13 scripts/upload_master_data.sh

@@ -1,0 +1,9 @@
+#!/usr/bin/env bash
+
+gsutil cp data/master.csv gs://masters-363209/master.csv
+
+bq rm --force=true masters-363209:raw.raw
+
+bq mk --force=true \
+	--external_table_definition=id:STRING,dataset:STRING,heuristic:STRING,heuristic_pool:STRING,population:INTEGER,burn_in:INTEGER,replay:INTEGER,reselection:INTEGER,reanalysis:INTEGER,normalisation:BOOLEAN,credit:STRING,discounted_rewards:BOOLEAN,run:INTEGER,step:INTEGER,wall_time:FLOAT,tag:STRING,value:FLOAT@CSV=gs://masters-363209/master.csv \
+	masters-363209:raw.raw
